### 2019-03-21 report/MSc_Report.Rnw
OMG

\documentclass[11pt,a4paper,twoside]{book}
\input{header.sty}   % packages, layout and standard macros

\usepackage{verbatim}
\usepackage{tikz}
\usetikzlibrary{trees}

\begin{document}
\input{title}

<<'main-setup',include=FALSE,purl=FALSE>>=
library(knitr)
opts_chunk$set(
    concordance=TRUE,
    child.command = 'include',
    cache=TRUE)
@

\graphicspath{{./figure/}}
\DeclareGraphicsExtensions{.pdf,.png}
\setcounter{tocdepth}{1}

\thispagestyle{empty}
\begin{center}
  \vspace*{6cm}{\bfseries\Huge
  $p$-values:\\[5mm] their use, abuse and proper use \\[5mm]
  illustrated with seven facets 
  }
  \vfill
  \rm

  \LARGE
  M\"axli Musterli\\[12mm]

  \normalsize
  Version \today
\end{center}
\newpage
\thispagestyle{empty}~
\newpage
\pagenumbering{roman}

\thispagestyle{plain}\markboth{Contents}{Contents}
\tableofcontents
\setkeys{Gin}{width=.8\textwidth}

\chapter*{Preface}
\addtocontents{toc}{\protect \vspace*{13.mm}}
\addcontentsline{toc}{chapter}{\bfseries{Preface}}
\thispagestyle{plain}\markboth{Preface}{Preface}

Howdy!

\bigskip

\begin{flushright}
  Max Muster\\
  June 2018
\end{flushright}

\addtocontents{toc}{\protect \vspace*{10mm}}

\cleardoublepage
\pagenumbering{arabic}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<'child-chapter01', child='chapter01.Rnw'>>=
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<'child-chapter02', child='chapter02.Rnw'>>=
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<'child-chapter03', child='chapter03.Rnw'>>=
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<'child-chapter04', child='chapter04.Rnw'>>=
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<'child-chapter05', child='chapter05.Rnw'>>=
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix
<<'child-chapterA1', child='chapterA1.Rnw'>>=
@

\cleardoublepage
\phantomsection
\addtocontents{toc}{\protect \vspace*{10mm}}
\addcontentsline{toc}{chapter}{\bfseries Bibliography}

\bibliographystyle{mywiley} 
\bibliography{biblio}

\cleardoublepage

\end{document}

### 2019-03-21 report/MSc_Report.tex
OMG

\documentclass[11pt,a4paper,twoside]{book}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\input{header.sty}   % packages, layout and standard macros

\usepackage{verbatim}
\usepackage{tikz}
\usetikzlibrary{trees}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\input{title}

\graphicspath{{./figure/}}
\DeclareGraphicsExtensions{.pdf,.png}
\setcounter{tocdepth}{1}

\thispagestyle{empty}
\begin{center}
  \vspace*{6cm}{\bfseries\Huge
  $p$-values:\\[5mm] their use, abuse and proper use \\[5mm]
  illustrated with seven facets 
  }
  \vfill
  \rm

  \LARGE
  M\"axli Musterli\\[12mm]

  \normalsize
  Version \today
\end{center}
\newpage
\thispagestyle{empty}~
\newpage
\pagenumbering{roman}

\thispagestyle{plain}\markboth{Contents}{Contents}
\tableofcontents
\setkeys{Gin}{width=.8\textwidth}

\chapter*{Preface}
\addtocontents{toc}{\protect \vspace*{13.mm}}
\addcontentsline{toc}{chapter}{\bfseries{Preface}}
\thispagestyle{plain}\markboth{Preface}{Preface}

Howdy!

\bigskip

\begin{flushright}
  Max Muster\\
  June 2018
\end{flushright}

\addtocontents{toc}{\protect \vspace*{10mm}}

\cleardoublepage
\pagenumbering{arabic}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% LaTeX file for Chapter 01

\chapter{Introduction}

In science, there is not only a need for accumulation of knowledge, but also for concentration. For the same reason as statistical analysis is performed on single experiments, it can also be used for results of multiple experiments or studies: to simplify and summarize the data at hand to a degree that is understandable for humans. The latter procedure goes usually under the term of meta-analysis. Meta analyses are used to summarize results and evidence over multiple studies when they are considered to be similar enough.

\vspace{0mm}
In the face of the large amount of research that is done in some fields of empirical science, meta-analysis becomes increasingly important, for looking at all evidence would simply take very long for one person. Meta-analysises are often part of a systematic review, an effort of experts of a field to provide an overlook over the evidence. In the course of a review, all literature and data with respect to a scientific question is collected and a meta-analysis is operated at the end to summarize the findings.

\vspace{0mm}
In the case of clinical science, systematic reviews and meta-analyses do not only benefit scientists but also patients and clinicians, for both are provided with up-to-date summaries of current evidence with respect to a certain treatment. Therefore, meta-analysis is at the core of what is called evidence-based medicine.

\vspace{0mm}
However, there are problems that potentially limit the validity of meta-analysis; studies at hand can be biased or heterogeneity between study results can be large and the number of studies small. The importance and the issues of meta-analysis are the reasons why they have been chosen as one general topic of the masters thesis. One particular problem will furthermore be investigated in more detail: reporting bias and meta-analysis. Not only will the methods to deal with issues as reporting bias be discussed, but also will they be applied on a dataset of systematic reviews that can be used for meta-analysis. So at the end of the report, the reader will not only have an impression of the technical issues caused by reporting bias, but also of the abundance and extent of it in the dataset. Since the dataset is very large and of good quality, results might be again be generalizable to some extent to reporting bias in clinical science in general.

\subsection{Cochrane and the Cochrane Database of Systematic Reviews}
The Cochrane Organization has specialized on systematic reviews in clinical science. It publishes and maintains a library with a large number of systematic reviews that are available in some countries to the public.

\vspace{0mm}
The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite). The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests. This might further improve the validity and precision of findings and conclusions that have been made based on this data.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% LaTeX file for Chapter 02

\chapter{The Cochrane Dataset}

\subsection{Structure and Content}
The dataset consists of 5016 systematic reviews from the Cochrane Library with 52995 studies.
Each study provides data of (multiple) comparisons of clinical interventions. 
% It can not be ruled out that some comparisons are retrospective, e.g. from observational studies. 
In Table \ref{barbiturate.row}, two comparisons from a systematic review about effects of barbiturates are shown as they are given in the dataset. As can be seen, the comparison is further specified by the variables in the columns. One row of the dataset is one comparison.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Mar 21 11:15:04 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lllrrrr}
  \hline
Study & Comparison\_type & Outcome & Events & Total & Events\_c & Total\_c \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up &  11 &  41 &  11 &  41 \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up &  14 &  27 &  13 &  26 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Example of two comparisons as given in the dataset. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted} 
\label{barbiturate.row}
\end{table}

A complete listing of the variables is given in Table \ref{variable}. They can roughly be separated into variables that specify the review in which the comparison is contained and variables that specify the comparison itself (separated by a horizontal line in Table \ref{variable}).

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{l l}
      \textbf{Variable} & \textbf{Description}\\
      \hline
      \textbf{File name} & The name of the file from which the review data has been . \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
      \textbf{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
      \textbf{File index} & Internal index of the file in the Cochrane library.\\
      \textbf{File version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
      %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
      \hline
      \textbf{Comparison type} & Specification of the interventions compared in the study\\
      \textbf{Outcome} & Specification by which outcome the interventions are compared\\
      \textbf{Subgroup} & Potentially indication of affiliation to subgroups\\
      \textbf{Study name} & Name of the study to which the comparison belongs\\
      \textbf{Study publication year} & Year in which the study was published\\
      \textbf{Outcome measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
      \textbf{Effect} & Measure of the effect given in the quantity denoted by \\ &``outcome measure''.\\
      \textbf{Events (1/2)} & The counts of patients with an outcome \textit{if}\\ & measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
      \textbf{Total (1/2)} & Number of patients in groups.\\
      \textbf{Mean (1/2)} & Mean of patient measurements \textit{if} outcome is continuous.\\
      \textbf{Standard deviation (1/2)} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
    \end{tabular}
  \caption{Dataset variable descriptions}
  \label{variable}
  \end{center}
\end{table}

The structure of a hypothetical review is shown in Figure \ref{review}. 
% Comparisons of a review can consecutively be subdivided into different comparison types, different outcome measures and different subgroups. 
The comparison type variable specifies what is compared, the outcome variable how it is compared, and the subgroup variable indicates if the comparison belongs to a certain subgroup. If desired, Figure \ref{review} can be compared to Table \ref{barbiturates} where an examplary review is listed.

\begin{figure}
\tikzstyle{every node}=[draw=black,thick,anchor=west]
\tikzstyle{selected}=[draw=red,fill=red!30]
\tikzstyle{optional}=[dashed,fill=gray!50]
\begin{tikzpicture}
[grow = right, anchor = west, 
  growth parent anchor=east, % added code
  parent anchor=east]
  \node {Review} [edge from parent fork right]
    child { node {Comparison type 2}
      child { node {Outcome 2}}
      child { node {Outcome 1}
        child { node {Subgroup 2}}
        child { node {Subgroup 1}}}
    }
    child [missing] {}		
    child { node {Comparison type 1  }};
\end{tikzpicture}
\caption{Structure of a hypothetical review with two different comparisons.}
\label{review.structure}
\end{figure}

% \vspace{0mm}
% Lets consider the previously mentioned barbiturate and head injury review. The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates''. The medical background is that one knew that barbiturates could cause relief in intra-cranial pressure, but also reduce cerebral blood flow. Because one effect is thought to be beneficial for persons with severe head injuries while the other isn't, the authors of the review wanted to find out if there is a net benefit of barbiturates.
% 
% \vspace{0mm}
% The review comprises five studies in total. Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental, which would be the comparison/research subject to speak in the previously introduced notions. 
% 
% \vspace{0mm}
% All the studies convey multiple information to the review. As an example, that could be death or death \textit{and} severe disability at follow up as an outcome. Again, the study can be further split up in different subgroups, here for example in a group with - and without haematoma. 
% 
% \vspace{0mm}
% The complete listing of outcomes is in table \ref{barbiturates}. The table also gives an illustration of the variety of data that can be included in a review. We have for example continuous and binary outcome data, that again is divided into a variety of different things that have been measured. Often, additionally to the main study result, also adverse effects are for example included which are in this case separate outcomes and possibly subgroups.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Mar 21 11:15:04 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Study & Comparison & Outcome \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
   \hline
\end{tabular}
\endgroup
\caption{Barbiturate and head injury review. In the columns, study names, comparison types and outcome measure of the comparisons are given.} 
\label{barbiturates}
\end{table}

% The research subject or outcome type can possibly already be well defined in the general review question. Conversely, research subject or comparison has to be further specified in outcome and subgroup categories. As may have been implied, the terminology does not rely to a hundred percent on strict functional definitions.

It is important to not confuse comparisons with studies. A study can contribute multiple comparisons to a systematic review. Also, despite a comparison has variables concerning event counts and means, it can only have one of the two, either means (if the outcome measure is continuous) or event counts (for binary outcomes).

\vspace{0mm}
Having provided a rough overview over the dataset, now, some more specific information is provided. The dataset consists of 463820 comparisons and has 25 variables that specify the comparisons. The abundancy of some missing values in the dataset is given in Table \ref{missing}. For variables as research subject, outcome and subgroup name and event counts there are no missing values. The relative abundancy of missing values is very low except for study years.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Mar 21 11:15:04 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lr}
  \hline
  \hline
Missing mean values & 1287 \\ 
  Missing standard deviations & 999 \\ 
  Missing effects & 158 \\ 
  Missing study year & 27234 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number of missing variables and measurements in the dataset.} 
\label{missing}
\end{table}

More properties of the reviews, the studies and the comparisons in the dataset will be provided on the following pages. The publication dates of the studies included in the dataset are shown in Figure \ref{study.years}.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-8-1}

}

\end{knitrout}
\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications.}
\label{study.years}
\end{figure}

Figure \ref{study.outcomes} provides the frequencies of outcome types of the comparisons. Note that the abundancy of mean differences and standardized mean differences can also give an impression of the proportion of continuous outcome comparisons vs. binary outcome comparisons in the dataset.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-9-1}

}

\end{knitrout}
\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded.}
\label{study.outcomes}
\end{figure}

It is also possible to look at the properties of the reviews. One question could be how many studies or comparisons that a review comprises. The former is shown in Figure \ref{studies.per.review} and the latter in Figure \ref{comparisons.per.review}. It can be seen that while almost 400 reviews consist of one study only, there are more than 150 with equal or more than 30 distinct studies. A similar variance between reviews can also be observed when looking at the number of comparisons.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-10-1}

}

\end{knitrout}
\caption{Empirical distribution of number of studies per review.}
\label{studies.per.review}
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-11-1}

}

\end{knitrout}
\caption{Empirical distribution of number of comparisons per review.}
\label{comparisons.per.review}
\end{figure}

A question not to be mistaken with the previous would be how many comparison \textit{types} there are per review. This gives an additional impression of the scope of a review. Analogously to the previous figures, the empirical distribution of comparison types is depicted in Figure \ref{subjects.per.review}.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-12-1}

}

\end{knitrout}
\caption{Empirical distribution of number of different research subjects per review.}
\label{subjects.per.review}
\end{figure}

% At the end, a main goal of the thesis is to analyze reviews with respect to reporting bias in meta analyses. 
For comparisons to be suitable for usage in meta-analysis, they have to be somewhat identical (same comparison type, outcome measure and possibly subgroup). For an analysis of reporting bias, again a certain number of studies is required in order for reporting bias to be detectable by the methods. One question would therefore be: How many groups of identical comparisons of a certain size are given in the dataset? This depends on which degree of similarity between comparisons is considered to be sufficient.

\vspace{0mm}
In Table \ref{repr.groups}, two different similarity criteria have been used. One is based on the same comparison type and outcome measure, the other includes additionally subgroup affiliation of comparisons, i.e. only comparisons in the same subgroups are considered to be similar enough.

\vspace{0mm}
Table \ref{repr.groups} shows the cumulative number of \textit{groups} of comparisons with equal or more than $n$ comparisons. Practically, this means that this number of meta analyses can be performed with each having at least $n$ comparisons.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Mar 21 11:15:10 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
n & Cumulative sum (without subgroups) & Cumulative sum (with subgroups) \\ 
  \hline
1 & 109177 & 186267 \\ 
  2 & 67685 & 83924 \\ 
  3 & 47786 & 52245 \\ 
  4 & 36155 & 36176 \\ 
  5 & 28077 & 26552 \\ 
  6 & 22689 & 20113 \\ 
  7 & 18536 & 15888 \\ 
  8 & 15466 & 12931 \\ 
  9 & 13000 & 10817 \\ 
  10 & 11001 & 9226 \\ 
  11 & 9356 & 7988 \\ 
  12 & 8052 & 7067 \\ 
  13 & 6984 & 6365 \\ 
  14 & 6041 & 5780 \\ 
  15 & 5325 & 5325 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Cumulative number of groups with number of reproduction trials >= n} 
\label{repr.groups}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% LaTeX file for Chapter 03

\chapter{Results}

One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect. This is termed reporting bias in the scientific world. If reporting bias is present, the classical approaches to merge single study results in to an overall intervention effect may fail because the underlying studies are biased. There are tests that can be applied to find out if reporting bias is present in the meta analysis.

\vspace{0mm}
For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test. The following three figures show the distribution of p-values of the corresponding tests. Note that only meta analyses with more than 10 comparisons have been included.

\vspace{0mm}
Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05. The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}

}

\end{knitrout}
\caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
\label{egger.cont}
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}

}

\end{knitrout}
\caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
\label{thomson.cont}
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}

}

\end{knitrout}
\caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
\label{begg.cont}
\end{figure}

For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}

}

\end{knitrout}
\caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
\label{peters.bin}
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}

}

\end{knitrout}
\caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
\label{harbord.bin}
\end{figure}

Another less conventional way to look for publication bias is to see how many studies are ``reflected'' by the trim and fill method. As a first impression, a histogram with the fraction of trimmed of all comparisons is shown in figure \ref{trimfill.cont}.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}

}

\end{knitrout}
\caption{Histogram of fractions of trimmed comparisons from meta analyses with continuous outcomes.}
\label{trimfill.cont}
\end{figure}

The mean fraction of trimmed comparisons for continuous outcomes is 0.22 and the median 0.2.

The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}

}

\end{knitrout}
\caption{Histogram of fractions of trimmed comparisons from meta analyses with binary outcomes.}
\label{trimfill.bin}
\end{figure}

The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.17.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% LaTeX file for Chapter 04

\chapter{Discussion and Outlook}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% LaTeX file for Chapter 05

\chapter{Conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

% LaTeX file for Chapter 01

\chapter{Appendix}

Maybe some R code here, probably a \rr{sessionInfo()}

\cleardoublepage
\phantomsection
\addtocontents{toc}{\protect \vspace*{10mm}}
\addcontentsline{toc}{chapter}{\bfseries Bibliography}

\bibliographystyle{mywiley} 
\bibliography{biblio}

\cleardoublepage

\end{document}

### 2019-03-21 report/chapter01.Rnw
OMG

--- 2019-03-21 report/MSc_Report.tex
@@
-\documentclass[11pt,a4paper,twoside]{book}\usepackage[]{graphicx}\usepackage[]{color}
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
+% LaTeX file for Chapter 01
+<<'preamble01',include=FALSE>>=
+library(knitr)
+opts_chunk$set(
+    fig.path='figure/ch01_fig', 
+    self.contained=FALSE,
+    cache=TRUE
+)
 
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
-
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
-
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-\usepackage{alltt}
-\input{header.sty}   % packages, layout and standard macros
-
-\usepackage{verbatim}
-\usepackage{tikz}
-\usetikzlibrary{trees}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\begin{document}
-\input{title}
-
-\graphicspath{{./figure/}}
-\DeclareGraphicsExtensions{.pdf,.png}
-\setcounter{tocdepth}{1}
-
-\thispagestyle{empty}
-\begin{center}
-  \vspace*{6cm}{\bfseries\Huge
-  $p$-values:\\[5mm] their use, abuse and proper use \\[5mm]
-  illustrated with seven facets 
-  }
-  \vfill
-  \rm
-
-  \LARGE
-  M\"axli Musterli\\[12mm]
-
-  \normalsize
-  Version \today
-\end{center}
-\newpage
-\thispagestyle{empty}~
-\newpage
-\pagenumbering{roman}
-
-\thispagestyle{plain}\markboth{Contents}{Contents}
-\tableofcontents
-\setkeys{Gin}{width=.8\textwidth}
-
-\chapter*{Preface}
-\addtocontents{toc}{\protect \vspace*{13.mm}}
-\addcontentsline{toc}{chapter}{\bfseries{Preface}}
-\thispagestyle{plain}\markboth{Preface}{Preface}
-
-Howdy!
-
-\bigskip
-
-\begin{flushright}
-  Max Muster\\
-  June 2018
-\end{flushright}
-
-\addtocontents{toc}{\protect \vspace*{10mm}}
-
-\cleardoublepage
-\pagenumbering{arabic}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 01
+@
 
@@
 This might further improve the validity and precision of findings and conclusions that have been made based on this data.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 02
-
-\chapter{The Cochrane Dataset}
-
-\subsection{Structure and Content}
-The dataset consists of 5016 systematic reviews from the Cochrane Library with 52995 studies.
-Each study provides data of (multiple) comparisons of clinical interventions. 
-% It can not be ruled out that some comparisons are retrospective, e.g. from observational studies. 
-In Table \ref{barbiturate.row}, two comparisons from a systematic review about effects of barbiturates are shown as they are given in the dataset.
-As can be seen, the comparison is further specified by the variables in the columns.
-One row of the dataset is one comparison.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 11:15:04 2019
-\begin{table}[ht]
-\centering
-\begingroup\scriptsize
-\begin{tabular}{lllrrrr}
-  \hline
-Study & Comparison\_type & Outcome & Events & Total & Events\_c & Total\_c \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up &  11 &  41 &  11 &  41 \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up &  14 &  27 &  13 &  26 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Example of two comparisons as given in the dataset.
-Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
-Further descriptive variables have been ommitted}
-\label{barbiturate.row}
-\end{table}
-
-A complete listing of the variables is given in Table \ref{variable}.
-They can roughly be separated into variables that specify the review in which the comparison is contained and variables that specify the comparison itself (separated by a horizontal line in Table \ref{variable}).
-
-\begin{table}[ht]
-  \begin{center}
-    \begin{tabular}{l l}
-      \textbf{Variable} & \textbf{Description}\\
-      \hline
-      \textbf{File name} & The name of the file from which the review data has been . \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
-      \textbf{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
-      \textbf{File index} & Internal index of the file in the Cochrane library.\\
-      \textbf{File version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
-      %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
-      \hline
-      \textbf{Comparison type} & Specification of the interventions compared in the study\\
-      \textbf{Outcome} & Specification by which outcome the interventions are compared\\
-      \textbf{Subgroup} & Potentially indication of affiliation to subgroups\\
-      \textbf{Study name} & Name of the study to which the comparison belongs\\
-      \textbf{Study publication year} & Year in which the study was published\\
-      \textbf{Outcome measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
-      \textbf{Effect} & Measure of the effect given in the quantity denoted by \\ &``outcome measure''.\\
-      \textbf{Events (1/2)} & The counts of patients with an outcome \textit{if}\\ & measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
-      \textbf{Total (1/2)} & Number of patients in groups.\\
-      \textbf{Mean (1/2)} & Mean of patient measurements \textit{if} outcome is continuous.\\
-      \textbf{Standard deviation (1/2)} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
-    \end{tabular}
-  \caption{Dataset variable descriptions}
-  \label{variable}
-  \end{center}
-\end{table}
-
-The structure of a hypothetical review is shown in Figure \ref{review}. 
-% Comparisons of a review can consecutively be subdivided into different comparison types, different outcome measures and different subgroups. 
-The comparison type variable specifies what is compared, the outcome variable how it is compared, and the subgroup variable indicates if the comparison belongs to a certain subgroup.
-If desired, Figure \ref{review} can be compared to Table \ref{barbiturates} where an examplary review is listed.
-
-\begin{figure}
-\tikzstyle{every node}=[draw=black,thick,anchor=west]
-\tikzstyle{selected}=[draw=red,fill=red!30]
-\tikzstyle{optional}=[dashed,fill=gray!50]
-\begin{tikzpicture}
-[grow = right, anchor = west, 
-  growth parent anchor=east, % added code
-  parent anchor=east]
-  \node {Review} [edge from parent fork right]
-    child { node {Comparison type 2}
-      child { node {Outcome 2}}
-      child { node {Outcome 1}
-        child { node {Subgroup 2}}
-        child { node {Subgroup 1}}}
-    }
-    child [missing] {}		
-    child { node {Comparison type 1  }};
-\end{tikzpicture}
-\caption{Structure of a hypothetical review with two different comparisons.}
-\label{review.structure}
-\end{figure}
-
-% \vspace{0mm}
-% Lets consider the previously mentioned barbiturate and head injury review.
-The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates''.
-The medical background is that one knew that barbiturates could cause relief in intra-cranial pressure, but also reduce cerebral blood flow.
-Because one effect is thought to be beneficial for persons with severe head injuries while the other isn't, the authors of the review wanted to find out if there is a net benefit of barbiturates.
-% 
-% \vspace{0mm}
-% The review comprises five studies in total.
-Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental, which would be the comparison/research subject to speak in the previously introduced notions.
-% 
-% \vspace{0mm}
-% All the studies convey multiple information to the review.
-As an example, that could be death or death \textit{and} severe disability at follow up as an outcome.
-Again, the study can be further split up in different subgroups, here for example in a group with - and without haematoma.
-% 
-% \vspace{0mm}
-% The complete listing of outcomes is in table \ref{barbiturates}.
-The table also gives an illustration of the variety of data that can be included in a review.
-We have for example continuous and binary outcome data, that again is divided into a variety of different things that have been measured.
-Often, additionally to the main study result, also adverse effects are for example included which are in this case separate outcomes and possibly subgroups.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 11:15:04 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-Study & Comparison & Outcome \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Barbiturate and head injury review. In the columns, study names, comparison types and outcome measure of the comparisons are given.} 
-\label{barbiturates}
-\end{table}
-
-% The research subject or outcome type can possibly already be well defined in the general review question.
-Conversely, research subject or comparison has to be further specified in outcome and subgroup categories.
-As may have been implied, the terminology does not rely to a hundred percent on strict functional definitions.
-
-It is important to not confuse comparisons with studies.
-A study can contribute multiple comparisons to a systematic review.
-Also, despite a comparison has variables concerning event counts and means, it can only have one of the two, either means (if the outcome measure is continuous) or event counts (for binary outcomes).
-
-\vspace{0mm}
-Having provided a rough overview over the dataset, now, some more specific information is provided.
-The dataset consists of 463820 comparisons and has 25 variables that specify the comparisons.
-The abundancy of some missing values in the dataset is given in Table \ref{missing}.
-For variables as research subject, outcome and subgroup name and event counts there are no missing values.
-The relative abundancy of missing values is very low except for study years.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 11:15:04 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lr}
-  \hline
-  \hline
-Missing mean values & 1287 \\ 
-  Missing standard deviations & 999 \\ 
-  Missing effects & 158 \\ 
-  Missing study year & 27234 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Number of missing variables and measurements in the dataset.} 
-\label{missing}
-\end{table}
-
-More properties of the reviews, the studies and the comparisons in the dataset will be provided on the following pages.
-The publication dates of the studies included in the dataset are shown in Figure \ref{study.years}.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-8-1}
-
-}
-
-\end{knitrout}
-\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications.}
-\label{study.years}
-\end{figure}
-
-Figure \ref{study.outcomes} provides the frequencies of outcome types of the comparisons.
-Note that the abundancy of mean differences and standardized mean differences can also give an impression of the proportion of continuous outcome comparisons vs.
-binary outcome comparisons in the dataset.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-9-1}
-
-}
-
-\end{knitrout}
-\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded.}
-\label{study.outcomes}
-\end{figure}
-
-It is also possible to look at the properties of the reviews.
-One question could be how many studies or comparisons that a review comprises.
-The former is shown in Figure \ref{studies.per.review} and the latter in Figure \ref{comparisons.per.review}.
-It can be seen that while almost 400 reviews consist of one study only, there are more than 150 with equal or more than 30 distinct studies.
-A similar variance between reviews can also be observed when looking at the number of comparisons.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-10-1}
-
-}
-
-\end{knitrout}
-\caption{Empirical distribution of number of studies per review.}
-\label{studies.per.review}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-11-1}
-
-}
-
-\end{knitrout}
-\caption{Empirical distribution of number of comparisons per review.}
-\label{comparisons.per.review}
-\end{figure}
-
-A question not to be mistaken with the previous would be how many comparison \textit{types} there are per review.
-This gives an additional impression of the scope of a review.
-Analogously to the previous figures, the empirical distribution of comparison types is depicted in Figure \ref{subjects.per.review}.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-12-1}
-
-}
-
-\end{knitrout}
-\caption{Empirical distribution of number of different research subjects per review.}
-\label{subjects.per.review}
-\end{figure}
-
-% At the end, a main goal of the thesis is to analyze reviews with respect to reporting bias in meta analyses. 
-For comparisons to be suitable for usage in meta-analysis, they have to be somewhat identical (same comparison type, outcome measure and possibly subgroup).
-For an analysis of reporting bias, again a certain number of studies is required in order for reporting bias to be detectable by the methods.
-One question would therefore be: How many groups of identical comparisons of a certain size are given in the dataset?
-This depends on which degree of similarity between comparisons is considered to be sufficient.
-
-\vspace{0mm}
-In Table \ref{repr.groups}, two different similarity criteria have been used.
-One is based on the same comparison type and outcome measure, the other includes additionally subgroup affiliation of comparisons, i.e.
-only comparisons in the same subgroups are considered to be similar enough.
-
-\vspace{0mm}
-Table \ref{repr.groups} shows the cumulative number of \textit{groups} of comparisons with equal or more than $n$ comparisons.
-Practically, this means that this number of meta analyses can be performed with each having at least $n$ comparisons.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 11:15:10 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-n & Cumulative sum (without subgroups) & Cumulative sum (with subgroups) \\ 
-  \hline
-1 & 109177 & 186267 \\ 
-  2 & 67685 & 83924 \\ 
-  3 & 47786 & 52245 \\ 
-  4 & 36155 & 36176 \\ 
-  5 & 28077 & 26552 \\ 
-  6 & 22689 & 20113 \\ 
-  7 & 18536 & 15888 \\ 
-  8 & 15466 & 12931 \\ 
-  9 & 13000 & 10817 \\ 
-  10 & 11001 & 9226 \\ 
-  11 & 9356 & 7988 \\ 
-  12 & 8052 & 7067 \\ 
-  13 & 6984 & 6365 \\ 
-  14 & 6041 & 5780 \\ 
-  15 & 5325 & 5325 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Cumulative number of groups with number of reproduction trials >= n} 
-\label{repr.groups}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 03
-
-\chapter{Results}
-
-One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect.
-This is termed reporting bias in the scientific world.
-If reporting bias is present, the classical approaches to merge single study results in to an overall intervention effect may fail because the underlying studies are biased.
-There are tests that can be applied to find out if reporting bias is present in the meta analysis.
-
-\vspace{0mm}
-For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
-The following three figures show the distribution of p-values of the corresponding tests.
-Note that only meta analyses with more than 10 comparisons have been included.
-
-\vspace{0mm}
-Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
-The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
-\label{egger.cont}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
-\label{thomson.cont}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{begg.cont}
-\end{figure}
-
-For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{peters.bin}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{harbord.bin}
-\end{figure}
-
-Another less conventional way to look for publication bias is to see how many studies are ``reflected'' by the trim and fill method.
-As a first impression, a histogram with the fraction of trimmed of all comparisons is shown in figure \ref{trimfill.cont}.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of fractions of trimmed comparisons from meta analyses with continuous outcomes.}
-\label{trimfill.cont}
-\end{figure}
-
-The mean fraction of trimmed comparisons for continuous outcomes is 0.22 and the median 0.2.
-
-The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of fractions of trimmed comparisons from meta analyses with binary outcomes.}
-\label{trimfill.bin}
-\end{figure}
-
-The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.17.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 04
-
-\chapter{Discussion and Outlook}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 05
-
-\chapter{Conclusions}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-% LaTeX file for Chapter 01
-
-\chapter{Appendix}
-
-Maybe some R code here, probably a \rr{sessionInfo()}
-
-\cleardoublepage
-\phantomsection
-\addtocontents{toc}{\protect \vspace*{10mm}}
-\addcontentsline{toc}{chapter}{\bfseries Bibliography}
-
-\bibliographystyle{mywiley} 
-\bibliography{biblio}
-
-\cleardoublepage
-
-\end{document}

### 2019-03-21 report/chapter02.Rnw
OMG

--- 2019-03-21 report/MSc_Report.tex
@@
-\documentclass[11pt,a4paper,twoside]{book}\usepackage[]{graphicx}\usepackage[]{color}
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
+% LaTeX file for Chapter 02
 
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
+<<echo=FALSE>>=
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'thesis/code')
+source(file.path(PATH, 'prepare.R'))
 
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
+require(biostatUZH)
+require(tidyverse)
+require(meta)
+require(xtable)
+@
 
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+<<echo=FALSE>>=
+library(knitr)
+opts_chunk$set(
+    fig.path='figure/ch02_fig',
+    self.contained=FALSE,
+    cache=TRUE
+)
+@
 
-\usepackage{alltt}
-\input{header.sty}   % packages, layout and standard macros
-
-\usepackage{verbatim}
-\usepackage{tikz}
-\usetikzlibrary{trees}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\begin{document}
-\input{title}
-
-\graphicspath{{./figure/}}
-\DeclareGraphicsExtensions{.pdf,.png}
-\setcounter{tocdepth}{1}
-
-\thispagestyle{empty}
-\begin{center}
-  \vspace*{6cm}{\bfseries\Huge
-  $p$-values:\\[5mm] their use, abuse and proper use \\[5mm]
-  illustrated with seven facets 
-  }
-  \vfill
-  \rm
-
-  \LARGE
-  M\"axli Musterli\\[12mm]
-
-  \normalsize
-  Version \today
-\end{center}
-\newpage
-\thispagestyle{empty}~
-\newpage
-\pagenumbering{roman}
-
-\thispagestyle{plain}\markboth{Contents}{Contents}
-\tableofcontents
-\setkeys{Gin}{width=.8\textwidth}
-
-\chapter*{Preface}
-\addtocontents{toc}{\protect \vspace*{13.mm}}
-\addcontentsline{toc}{chapter}{\bfseries{Preface}}
-\thispagestyle{plain}\markboth{Preface}{Preface}
-
-Howdy!
-
-\bigskip
-
-\begin{flushright}
-  Max Muster\\
-  June 2018
-\end{flushright}
-
-\addtocontents{toc}{\protect \vspace*{10mm}}
-
-\cleardoublepage
-\pagenumbering{arabic}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 01
-
-\chapter{Introduction}
-
-In science, there is not only a need for accumulation of knowledge, but also for concentration.
-For the same reason as statistical analysis is performed on single experiments, it can also be used for results of multiple experiments or studies: to simplify and summarize the data at hand to a degree that is understandable for humans.
-The latter procedure goes usually under the term of meta-analysis.
-Meta analyses are used to summarize results and evidence over multiple studies when they are considered to be similar enough.
-
-\vspace{0mm}
-In the face of the large amount of research that is done in some fields of empirical science, meta-analysis becomes increasingly important, for looking at all evidence would simply take very long for one person.
-Meta-analysises are often part of a systematic review, an effort of experts of a field to provide an overlook over the evidence.
-In the course of a review, all literature and data with respect to a scientific question is collected and a meta-analysis is operated at the end to summarize the findings.
-
-\vspace{0mm}
-In the case of clinical science, systematic reviews and meta-analyses do not only benefit scientists but also patients and clinicians, for both are provided with up-to-date summaries of current evidence with respect to a certain treatment.
-Therefore, meta-analysis is at the core of what is called evidence-based medicine.
-
-\vspace{0mm}
-However, there are problems that potentially limit the validity of meta-analysis; studies at hand can be biased or heterogeneity between study results can be large and the number of studies small.
-The importance and the issues of meta-analysis are the reasons why they have been chosen as one general topic of the masters thesis.
-One particular problem will furthermore be investigated in more detail: reporting bias and meta-analysis.
-Not only will the methods to deal with issues as reporting bias be discussed, but also will they be applied on a dataset of systematic reviews that can be used for meta-analysis.
-So at the end of the report, the reader will not only have an impression of the technical issues caused by reporting bias, but also of the abundance and extent of it in the dataset.
-Since the dataset is very large and of good quality, results might be again be generalizable to some extent to reporting bias in clinical science in general.
-
-\subsection{Cochrane and the Cochrane Database of Systematic Reviews}
-The Cochrane Organization has specialized on systematic reviews in clinical science.
-It publishes and maintains a library with a large number of systematic reviews that are available in some countries to the public.
-
-\vspace{0mm}
-The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite).
-The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests.
-This might further improve the validity and precision of findings and conclusions that have been made based on this data.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 02
+<<echo=FALSE>>=
+library(knitr)
+opts_chunk$set(fig.path='figure/ch02_fig',
+               echo=TRUE, message=FALSE,
+               fig.width=8.5, fig.height=3,
+               out.width='\\textwidth-3cm',
+               message=FALSE, fig.align='center',
+               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
+               cache=TRUE
+)
+options(width=74)
+@
 
@@
 \subsection{Structure and Content}
-The dataset consists of 5016 systematic reviews from the Cochrane Library with 52995 studies.
+The dataset consists of \Sexpr{length(unique(madata$file.nr))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(madata$study.name))} studies.
 Each study provides data of (multiple) comparisons of clinical interventions. 
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 11:15:04 2019
-\begin{table}[ht]
-\centering
-\begingroup\scriptsize
-\begin{tabular}{lllrrrr}
-  \hline
-Study & Comparison\_type & Outcome & Events & Total & Events\_c & Total\_c \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up &  11 &  41 &  11 &  41 \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up &  14 &  27 &  13 &  26 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Example of two comparisons as given in the dataset.
+<<echo=FALSE, results = 'asis'>>=
+tp1 <- arrange(filter(madata, file.nr == 21) %>% 
+          select(Study = study.name, Comparison_type = comparison.name, Outcome = outcome.name, 
+                 Events = events1, Total = total1, Events_c = events2, Total_c = total2) %>% 
+            slice(c(1,3)), Study)
+print(xtable(tp1, label = "barbiturate.row", caption = "Example of two comparisons as given in the dataset.
 Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
-Further descriptive variables have been ommitted}
-\label{barbiturate.row}
-\end{table}
+Further descriptive variables have been ommitted"), include.rownames = F, size = "scriptsize")
+@
 
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 11:15:04 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-Study & Comparison & Outcome \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Barbiturate and head injury review. In the columns, study names, comparison types and outcome measure of the comparisons are given.} 
-\label{barbiturates}
-\end{table}
+<<echo=FALSE, results='asis'>>=
+tp1 <- arrange(filter(madata, file.nr == 21) %>% 
+          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study)
+tp1[tp1$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
+print(xtable(tp1, label = "barbiturates", caption = "Barbiturate and head injury review.
+In the columns, study names, comparison types and outcome measure of the comparisons are given."), include.rownames = F, size = "footnotesize")
+@
 
@@
 Having provided a rough overview over the dataset, now, some more specific information is provided.
-The dataset consists of 463820 comparisons and has 25 variables that specify the comparisons.
+The dataset consists of \Sexpr{dim(madata)[1]} comparisons and has \Sexpr{dim(madata)[2]} variables that specify the comparisons.
 The abundancy of some missing values in the dataset is given in Table \ref{missing}.
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 11:15:04 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lr}
-  \hline
-  \hline
-Missing mean values & 1287 \\ 
-  Missing standard deviations & 999 \\ 
-  Missing effects & 158 \\ 
-  Missing study year & 27234 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Number of missing variables and measurements in the dataset.} 
-\label{missing}
-\end{table}
+<<echo=FALSE>>=
+missing.mean <- madata %>% filter(!is.na(sd1) & sd1 > 0) %>% filter(!is.na(sd2) & sd2 > 0) %>% 
+  summarise(total = length(sd1), na  = sum(is.na(mean1) | is.na(mean1))) %>% select(na)
+
+missing.sd <- madata %>% filter(!is.na(mean1) & !is.na(mean2)) %>% filter(mean1 != 0 & mean2 != 0) %>%
+  summarise(total = length(mean1), na.sd  = sum(is.na(sd1) | is.na(sd1)), null.sd = length(sd1[sd1 <= 0 | sd2 <= 0])) %>% 
+  mutate(miss = na.sd + null.sd) %>% select(miss)
+
+missing.ssize <- madata %>% summarize(total = length(total1), null.ss = length(total1[total1 <= 0 | total2 <= 0])) %>% 
+  select(null.ss)
+
+missing.effect <- sum(is.na(madata$effect))
+
+missing.year <- sum(is.na(madata$study.year)) + length(madata$study.year[madata$study.year == 0])
+
+# missing.outcome <- sum(is.na(madata$effect))
+
+# null.events <- madata %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
+#   filter(is.na(sd1) | sd1 <= 0) %>% filter(is.na(sd2) | sd2 <= 0) %>% 
+#   summarise(null.ev = length(total1[events1 <= 0 & events2 <= 0]), total = length(events1)) %>% 
+#   mutate(f = null.ev/total) %>% select(f)
+# 
+# null.events.single <- madata %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
+#   filter(is.na(sd1) | sd1 <= 0) %>% filter(is.na(sd2) | sd2 <= 0) %>% 
+#   summarise(null.ev = length(total1[events1 <= 0 | events2 <= 0]), total = length(events1)) %>% 
+#   mutate(f = null.ev/total) %>% select(f)
+# 
+# missing.events <- madata %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
+#   filter(is.na(sd1) | sd1 <= 0) %>% filter(is.na(sd2) | sd2 <= 0) %>% 
+#   summarise(na.ev = sum(is.na(events1) | is.na(events2)), total = length(events1)) %>% 
+#   mutate(f = na.ev/total) %>% select(f)
+@
+
+<<echo=FALSE, results='asis'>>=
+  missing.table <- rbind("Missing mean values" = missing.mean[1,1],
+                         "Missing standard deviations" = missing.sd[1,1],
+                         "Missing sample sizes" = missing.ssize[1,2],
+                         "Missing effects" = missing.effect,
+                         "Missing study year" = missing.year)
+
+print(xtable(missing.table, label = "missing", caption = "Number of missing variables and measurements in the dataset.", align = "lr"), include.colnames = F,
+      size = "footnotesize", digits = 0)
+@
 
@@
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-8-1}
-
-}
-
-\end{knitrout}
+<<echo=FALSE>>=
+madata %>% filter(study.year < 2019 & study.year > 1920) %>% ggplot(aes(x = study.year)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
+  theme_bw() + xlab("Year") + ylab("Study frequency")
+@
 \caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications.}
@@
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-9-1}
-
-}
-
-\end{knitrout}
+<<echo=FALSE>>=
+yodata %>% group_by(outcome.measure) %>% count() %>% arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9) %>% 
+  ggplot(aes(x = outcome.measure, y = n)) +
+  geom_col(col = "gray15", fill = "dodgerblue") +
+  theme_bw() + ylab("Comparison frequency") + xlab("Outcome measure")
+@
 \caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded.}
@@
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-10-1}
-
-}
-
-\end{knitrout}
+<<echo=FALSE>>=
+madata %>% group_by(file.nr) %>% distinct(study.name) %>% count() %>%
+  filter(n < 50) %>%
+  full_join( madata %>% group_by(file.nr) %>% distinct(study.name) %>% count %>%
+               filter(n > 49) %>% mutate(n = 50)) %>%
+  group_by(n) %>% count() %>%
+  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
+  theme_bw() + xlab("Study number") + ylab("Reviews Frequency")
+@
 \caption{Empirical distribution of number of studies per review.}
@@
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-11-1}
-
-}
-
-\end{knitrout}
+<<echo=FALSE>>=
+madata %>% group_by(file.nr) %>% count() %>%
+  filter(n < 50) %>%
+  full_join( madata %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
+               filter(n > 49) %>% mutate(n = 50)) %>%
+  group_by(n) %>% count() %>%
+  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
+  theme_bw() +  xlab("Comparisons") + ylab("Review Frequency")
+# mean.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
+#   ungroup() %>% group_by(file.nr) %>% 
+#   count() %>% ungroup %>% summarise(mean = mean(n))
+# 
+# median.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
+#   ungroup() %>% group_by(file.nr) %>% 
+#   count() %>% ungroup %>% summarise(mean = median(n))
+@
 \caption{Empirical distribution of number of comparisons per review.}
@@
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+<<echo=FALSE>>=
+madata %>% group_by(file.nr) %>% distinct(comparison.name) %>% count() %>%
+  filter(n < 15) %>%
+  full_join( madata %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
+               filter(n > 14) %>% mutate(n = 15)) %>%
+  group_by(n) %>% count() %>%
+  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
+  theme_bw() +  xlab("Comparison type number") + ylab("Review frequency")
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-12-1}
+mean.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
+  ungroup() %>% group_by(file.nr) %>% 
+  count() %>% ungroup %>% summarise(mean = mean(n))
 
-}
-
-\end{knitrout}
+median.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
+  ungroup() %>% group_by(file.nr) %>% 
+  count() %>% ungroup %>% summarise(mean = median(n))
+@
 \caption{Empirical distribution of number of different research subjects per review.}
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 11:15:10 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-n & Cumulative sum (without subgroups) & Cumulative sum (with subgroups) \\ 
-  \hline
-1 & 109177 & 186267 \\ 
-  2 & 67685 & 83924 \\ 
-  3 & 47786 & 52245 \\ 
-  4 & 36155 & 36176 \\ 
-  5 & 28077 & 26552 \\ 
-  6 & 22689 & 20113 \\ 
-  7 & 18536 & 15888 \\ 
-  8 & 15466 & 12931 \\ 
-  9 & 13000 & 10817 \\ 
-  10 & 11001 & 9226 \\ 
-  11 & 9356 & 7988 \\ 
-  12 & 8052 & 7067 \\ 
-  13 & 6984 & 6365 \\ 
-  14 & 6041 & 5780 \\ 
-  15 & 5325 & 5325 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Cumulative number of groups with number of reproduction trials >= n} 
-\label{repr.groups}
-\end{table}
+<<echo=FALSE, results='asis'>>=
+cum.repr.trials.nosub <- yodata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+  filter(n < 15) %>%
+  full_join( yodata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
+  ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+cum.repr.trials.subg <- yodata %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
+  filter(n < 15) %>%
+  full_join( yodata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
+  ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
 
-% LaTeX file for Chapter 03
+cum.repr.trials <- cbind(cum.repr.trials.nosub, cum.repr.trials.subg)[,c(1,3,6)]
 
-\chapter{Results}
+colnames(cum.repr.trials)  <- c("n", "Cumulative sum (without subgroups)", "Cumulative sum (with subgroups)")
 
-One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect.
-This is termed reporting bias in the scientific world.
-If reporting bias is present, the classical approaches to merge single study results in to an overall intervention effect may fail because the underlying studies are biased.
-There are tests that can be applied to find out if reporting bias is present in the meta analysis.
-
-\vspace{0mm}
-For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
-The following three figures show the distribution of p-values of the corresponding tests.
-Note that only meta analyses with more than 10 comparisons have been included.
-
-\vspace{0mm}
-Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
-The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
-\label{egger.cont}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
-\label{thomson.cont}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{begg.cont}
-\end{figure}
-
-For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{peters.bin}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{harbord.bin}
-\end{figure}
-
-Another less conventional way to look for publication bias is to see how many studies are ``reflected'' by the trim and fill method.
-As a first impression, a histogram with the fraction of trimmed of all comparisons is shown in figure \ref{trimfill.cont}.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of fractions of trimmed comparisons from meta analyses with continuous outcomes.}
-\label{trimfill.cont}
-\end{figure}
-
-The mean fraction of trimmed comparisons for continuous outcomes is 0.22 and the median 0.2.
-
-The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of fractions of trimmed comparisons from meta analyses with binary outcomes.}
-\label{trimfill.bin}
-\end{figure}
-
-The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.17.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 04
-
-\chapter{Discussion and Outlook}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 05
-
-\chapter{Conclusions}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-% LaTeX file for Chapter 01
-
-\chapter{Appendix}
-
-Maybe some R code here, probably a \rr{sessionInfo()}
-
-\cleardoublepage
-\phantomsection
-\addtocontents{toc}{\protect \vspace*{10mm}}
-\addcontentsline{toc}{chapter}{\bfseries Bibliography}
-
-\bibliographystyle{mywiley} 
-\bibliography{biblio}
-
-\cleardoublepage
-
-\end{document}
+print(xtable(cum.repr.trials, label = "repr.groups", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
+@

### 2019-03-21 report/chapter03.Rnw
OMG

% LaTeX file for Chapter 03
<<'preamble03',include=FALSE>>=
library(knitr)
opts_chunk$set(
    fig.path='figure/ch03_fig', 
    self.contained=FALSE,
    cache=FALSE
) 
@

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(
    fig.path='figure/ch02_fig',
    self.contained=FALSE,
    cache=TRUE
)
@

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch02_fig',
               echo=TRUE, message=FALSE,
               fig.width=8, fig.height=3,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@

<<echo=FALSE>>=
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'thesis/code')
source(file.path(PATH, 'prepare.R'))

require(biostatUZH)
require(tidyverse)
require(meta)
require(xtable)
@

\chapter{Results}

One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect. This is termed reporting bias in the scientific world. If reporting bias is present, the classical approaches to merge single study results in to an overall intervention effect may fail because the underlying studies are biased. There are tests that can be applied to find out if reporting bias is present in the meta analysis.

\vspace{0mm}
For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test. The following three figures show the distribution of p-values of the corresponding tests. Note that only meta analyses with more than 10 comparisons have been included.

\vspace{0mm}
Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05. The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.

\begin{figure}
<<echo=FALSE>>=
yodata %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
                            method = "linreg")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
\label{egger.cont}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
yodata %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
                            method = "mm")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
\label{thomson.cont}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
yodata %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
                            method = "rank")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
\label{begg.cont}
\end{figure}

For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.

\begin{figure}
<<echo=FALSE>>=
yodata %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
  filter(events1 > 0 | events2 > 0) %>% 
  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
\label{peters.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
yodata %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
  filter(events1 > 0 | events2 > 0) %>% 
  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
  theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
@
\caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
\label{harbord.bin}
\end{figure}

Another less conventional way to look for publication bias is to see how many studies are ``reflected'' by the trim and fill method. As a first impression, a histogram with the fraction of trimmed of all comparisons is shown in figure \ref{trimfill.cont}.

\begin{figure}
<<echo=FALSE>>=
trimfill.cont <- yodata %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 50) %>% 
  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(trim = trimfill(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2))$k0 / n())

trimfill.cont.mean <- trimfill.cont %>% ungroup %>% summarise(mean = mean(trim)) %>% select(mean)
trimfill.cont.median <- trimfill.cont %>% ungroup %>% summarise(median = median(trim)) %>% select(median)

trimfill.cont %>% ggplot(aes(x = trim)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Fraction of Trimmed Comparisons (continuous outcome)") + xlab("Fraction") + ylab("Frequency")
@
\caption{Histogram of fractions of trimmed comparisons from meta analyses with continuous outcomes.}
\label{trimfill.cont}
\end{figure}

The mean fraction of trimmed comparisons for continuous outcomes is \Sexpr{round(trimfill.cont.mean,2)} and the median \Sexpr{round(trimfill.cont.median,2)}.

The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
\begin{figure}
<<echo=FALSE>>=
trimfill.bin <- yodata %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% #filter(file.nr < 503) %>% 
  filter(events1 > 0 | events2 > 0) %>% 
  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(trim = trimfill(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2))$k0 / n())

trimfill.bin.mean <- trimfill.bin %>% ungroup %>% summarise(mean = mean(trim)) %>% select(mean)
trimfill.bin.median <- trimfill.bin %>% ungroup %>% summarise(median = median(trim)) %>% select(median)

trimfill.bin %>% ggplot(aes(x = trim)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Fraction of Trimmed Comparisons (binary outcome)") + xlab("Fraction") + ylab("Frequency")
@
\caption{Histogram of fractions of trimmed comparisons from meta analyses with binary outcomes.}
\label{trimfill.bin}
\end{figure}

The mean fraction of trimmed comparisons for binary outcomes is \Sexpr{round(trimfill.bin.mean,2)} and the median \Sexpr{round(trimfill.bin.median,2)}.

### 2019-03-21 cochrane/cochrane.Rmd
OMG2

---
title: "Cochrane"
author: "Simon Schwab"
date: "09 Jan 2019"
output:
  pdf_document: default
  html_notebook: default
---

# Vars
```{r}
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'thesis/cochrane')
```

# Read data
```{r}
source(file.path(PATH, 'prepare.R'))
```

# Inspect data frame
```{r}
str(madata)

names(madata)
```

# Inspect single study
https://www.cochranelibrary.com/cdsr/doi/10.1002/14651858.CD012713.pub2/full
```{r}
madata[madata$file.nr==6242, ]

```

```{r}
# check first entry, corresponding to first Cochrane review:
madata[madata$file.nr==1, ]

# example: show Richer-et-al review's data
# (see http://doi.org/10.1002/14651858.CD005220.pub2):
madata[madata$file.name=="MYdwnld_CD005220StatsDataOnly_Version2.csv", c(2,5,7,10,12)]

# show outcome measures and their frequencies:
t(t(sort(table(madata$outcome.measure), decreasing=TRUE)))

# non-zero entries for event counts only for RR/OR/RD/HR outcomes: 
t(t(sort(table(madata$outcome.measure[(madata$events1>0) | (madata$events2>0)]),dec=TRUE)))

# binary outcomes' names:
outcomenames <- unique(madata$outcome.measure[(madata$events1>0) | (madata$events2>0)])
# studies with binary outcomes:
binstudies <- is.element(madata$outcome.measure, outcomenames)
# fraction of binary outcomes:
mean(binstudies)  # 67%
# fraction of zero counts among binary outcomes:
mean((madata$events1[binstudies] == 0)
     | (madata$events1[binstudies] == madata$total1[binstudies])
     | (madata$events2[binstudies] == 0)
     | (madata$events2[binstudies] == madata$total2[binstudies]))
#  26 % (!)

##########################################
# distribution of analysis sizes;
# overall analyses:
tab1 <- table(table(paste(madata$file.nr, madata$comparison.nr, madata$outcome.nr, sep=".")))
tab1 <- c(tab1[1:15], ">15"=sum(tab1[-(1:15)]))
tab1 <- tab1/sum(tab1)
round(cbind("prob"=tab1, "cumulative"=cumsum(tab1)),3)
barplot(tab1, col="red3")

# subgroup analyses:
tab2 <- table(table(paste(madata$file.nr, madata$comparison.nr, madata$outcome.nr, madata$subgroup.nr, sep=".")))
tab2 <- c(tab2[1:15], ">15"=sum(tab2[-(1:15)]))
tab2 <- tab2/sum(tab2)
round(cbind("prob"=tab2, "cumulative"=cumsum(tab2)),3)
barplot(tab2, col="blue3")

# both analysis types:
barplot(rbind(tab1, tab2), beside=TRUE, col=c("red3","blue3"),
        xlab="number of studies included", ylab="frequency")
legend("topright", c("overall analyses","subgroup analyses"),
       pch=15, col=c("red3","blue3"))

```

### 2019-03-21 code_excess/explore_maill.Rmd
OMG2

---
title: "Cochrane Dataset"
output: html_notebook
---

```{r}
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'thesis/code')
```

# Read data
```{r}
source(file.path(PATH, 'prepare.R'))
```

```{r}
require(tidyverse)
require(meta)
```

###Example Reviews
Anti-D administration in pregnancy for preventing Rhesus alloimmunisation: 2 Trials, 3 Identical outcome measures, but with different subgroups.

```{r}
# arrange(filter(madata, file.nr==10) %>% select(comparison.name, outcome.name, outcome.measure, subgroup.name, study.name), study.name)
```

Comparison of

```{r}
# arrange(filter(madata, file.nr==21) %>% select(comparison.name, outcome.name, outcome.measure, subgroup.name, study.name), study.name)
```

###Frequencies of Trials in the Reviews

Frequencies of trials analyzing the same subject in a review (with the same outcome measure):

```{r}
madata %>% group_by(file.nr, outcome.nr, comparison.nr) %>% count %>% group_by(n) %>% count %>% 
  filter(n < 15) %>% 
  full_join( madata %>% group_by(file.nr, outcome.nr, comparison.nr) %>% count %>% group_by(n) %>% count %>% 
    filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>%  
  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Trials Comparing the Same Subject per Review") + ylab("Trials")
```

Frequencies of trials analyzing the same subject with the same subgroups in a review (and the same outcome measure):

```{r}
madata %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>% filter(n < 15) %>% 
  full_join( madata %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>% 
               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>%  
  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Trials Comparing the Same Subject in the Same Subgroups per Review") +  ylab ("Trials")
```

###Frequencies of Different Outcome Subjects per Review

```{r}
# madata %>% group_by(file.nr) %>% summarise(diff.out = length(unique(outcome.name))) %>% count(diff.out) %>%  
#   ggplot(aes(x = diff.out, y = n)) + geom_col(col = "gray15", fill = "dodgerblue") +
#   theme_bw() + labs(title = "Different subjects per Review") + xlab("study subjects per review")
```

###Analysis Study Year Frequencies

```{r}
madata %>% filter(study.year > 1900 & study.year < 2019) %>% ggplot(aes(x = study.year)) + geom_histogram(col = "gray15", fill = "dodgerblue") + theme_bw() + labs(title = "Study years of analyses")
```

###Effect sizes over time

Odds ratios with initial finding > 1:

```{r}
madata %>% filter(outcome.measure == "Odds Ratio") %>% filter(!is.na(study.year)) %>% 
  group_by(file.nr, comparison.nr, subgroup.nr) %>% 
  mutate(counts = n()) %>% filter(counts > 1) %>% 
  mutate(first.effect = effect[which.min(study.year)]) %>% 
  filter(first.effect > 1) %>% 
  mutate(scaled.effect = scale(effect), scaled.time = scale(study.year)) %>% 
  ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + 
  geom_smooth(method = lm) + theme_bw()  + 
  labs(title = "Scaled and centered OR over time", subtitle = "Initial finding > 1") + ylab("Odds Ratio")  + ylab("Time")
```

Odds ratios with initial finding < 1:

```{r}
madata %>% filter(outcome.measure == "Odds Ratio") %>% filter(!is.na(study.year)) %>% 
  group_by(file.nr, comparison.nr, subgroup.nr) %>% 
  mutate(counts = n()) %>% filter(counts > 1) %>% 
  mutate(first.effect = effect[which.min(study.year)]) %>% 
  filter(first.effect < 1) %>% 
  mutate(scaled.effect = scale(effect), scaled.time = scale(study.year)) %>% 
  ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .35, alpha = 0.1)  + 
  geom_smooth(method = lm) + theme_bw() + 
  labs(title = "Scaled and centered OR over time", subtitle = "Initial finding < 1") + ylab("Odds Ratio")  + ylab("Time")
```

Risk ratios with initial finding > 1:

```{r}
#Scaled RR over time with initial RR > 1
madata %>% filter(outcome.measure == "Risk Ratio") %>% filter(!is.na(study.year)) %>% 
  group_by(file.nr, comparison.nr, subgroup.nr) %>% 
  mutate(counts = n()) %>% filter(counts > 1) %>% 
  mutate(first.effect = effect[which.min(study.year)]) %>% 
  filter(first.effect > 1) %>% 
  mutate(scaled.effect = scale(effect), scaled.time = scale(study.year)) %>% 
  ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .25, alpha = 0.025)  + 
  geom_smooth(method = lm) + theme_bw() + 
  labs(title = "Scaled and centered RR over time", subtitle = "Initial finding > 1") + ylab("Risk Ratio")  + xlab("Time") + xlim(c(-4,4)) + ylim(c(-5,7))
```

Risk ratios with initial finding < 1:

```{r}
#Scaled RR over time with initial RR > 1
madata %>% filter(outcome.measure == "Risk Ratio") %>% filter(!is.na(study.year)) %>% 
  group_by(file.nr, comparison.nr, subgroup.nr) %>% 
  mutate(counts = n()) %>% filter(counts > 1) %>% 
  mutate(first.effect = effect[which.min(study.year)]) %>% 
  filter(first.effect < 1) %>% 
  mutate(scaled.effect = scale(effect), scaled.time = scale(study.year)) %>% 
  ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .2, alpha = 0.025)  + 
  geom_smooth(method = lm) + theme_bw() + 
  labs(title = "Scaled and centered RR over time", subtitle = "Initial finding < 1") + ylab("Risk Ratio")  + ylab("Time") + xlim(c(-5,5)) + ylim(c(-5, 10))
```

Statistical test to see if incorporation of a time - intial RR estimate improves a linear model for RR and time:

```{r}
regression.temp <- madata %>% filter(outcome.measure == "Risk Ratio") %>% filter(!is.na(study.year)) %>% 
  group_by(file.nr, comparison.nr, subgroup.nr) %>% 
  mutate(counts = n()) %>% filter(counts > 1) %>% 
  mutate(first.effect = effect[which.min(study.year)]) %>% 
  mutate(effect.sign = ifelse(first.effect > 1, "pos", "neg"), scaled.effect = scale(effect), scaled.time = scale(study.year))
regression.temp$effect.sign <- as.factor(regression.temp$effect.sign)

m1 <- lm(scaled.effect ~ scaled.time, data = regression.temp)
m2 <- lm(scaled.effect ~ scaled.time + effect.sign, data = regression.temp)
m3 <- lm(scaled.effect ~ scaled.time * effect.sign, data = regression.temp)
anova(m1, m2, m3)
```

###Cochrane Heterogeneity test

Cochrane heterogeneity test for Odds Ratios (with meta::metabin()):

```{r}
madata %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>% 
  filter(outcome.measure == "Odds Ratio") %>% 
  mutate(counts = n()) %>% filter(counts > 1) %>%
  filter(events1 > 0 & events2 > 0) %>% 
  summarise(
    Q = metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, method = "Inverse", sm = "OR")$Q,
    p.value = metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, 
                      method = "Inverse", sm =  "OR")$pval.Q) %>% 
  ggplot(aes(x = p.value)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Cochrane Heterogeneity Test P-values of ORs")
```

##Transformation to fishers z-scaled correlation

Mean differences and binary outcomes can be compared by transformation to standardized mean difference to correlation and finally to fishers z-scaled correlation.

```{r}
#Transform Binary outcomes to odds ratios -> standardized mean difference -> correlation -> fisher scala correlation
madata <- madata %>% 
  filter(!is.na(outcome.measure)) %>% 
  mutate(odds.ratio = (events1/(total1 - events1)) / (events2/(total2 - events2))) %>% 
  mutate(std.mean.d = log(odds.ratio) * (sqrt(3)/pi)) %>% 
  mutate(correlation = std.mean.d/sqrt((std.mean.d^2) + ((total1 + total2)^2)/(total2*total1))) %>% 
  mutate(fishersz = 0.5 * log( (1 + correlation)/(1 - correlation) ), variance = 1/(total1 + total2 - 3))

#Transform mean difference to standardized mean difference -> correlation -> fisher scala correlation
madata[madata$outcome.measure == "Mean Difference", ] <- madata %>% filter(outcome.measure == "Mean Difference") %>% 
  mutate(std.mean.d = effect/se) %>% 
  mutate(correlation = std.mean.d/sqrt(std.mean.d^2 + ((total1 + total2)^2)/(total2*total1))) %>% 
  mutate(fishersz = 0.5 * log( (1 + correlation)/(1 - correlation) ), variance = 1/(total1 + total2 - 3))

madata[madata$outcome.measure == "Std. Mean Difference", ] <- madata %>% filter(outcome.measure == "Std. Mean Difference") %>% 
  mutate(std.mean.d = effect) %>% 
  mutate(correlation = std.mean.d/sqrt(std.mean.d^2 + ((total1 + total2)^2)/(total2*total1))) %>% 
  mutate(fishersz = 0.5 * log( (1 + correlation)/(1 - correlation) ), variance = 1/(total1 + total2 - 3))

madata[madata$outcome.measure == "Mean difference", ] <- madata %>% filter(outcome.measure == "Mean difference") %>% 
  mutate(std.mean.d = effect) %>% 
  mutate(correlation = std.mean.d/sqrt(std.mean.d^2 + ((total1 + total2)^2)/(total2*total1))) %>% 
  mutate(fishersz = 0.5 * log( (1 + correlation)/(1 - correlation) ), variance = 1/(total1 + total2 - 3))

madata[madata$outcome.measure == "mean difference", ] <- madata %>% filter(outcome.measure == "mean difference") %>% 
  mutate(std.mean.d = effect) %>% 
  mutate(correlation = std.mean.d/sqrt(std.mean.d^2 + ((total1 + total2)^2)/(total2*total1))) %>% 
  mutate(fishersz = 0.5 * log( (1 + correlation)/(1 - correlation) ), variance = 1/(total1 + total2 - 3))
```

```{r}
madata %>% filter(!is.na(fishersz)) %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
  ungroup %>% arrange(desc(n)) %>% mutate(trials = cumsum(n * nn)) %>% 
  filter(n < 50) %>% 
  full_join( madata %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>% 
               filter(n > 49) %>% ungroup %>% summarise(n = 50, nn = sum(nn))) %>%  
  ggplot(aes(x = n, y = trials)) + geom_point(col = "gray15") + 
  theme_bw() + labs(title = "Sum of Trials with Number of Replicate (Trials) >= n") + ylab("Number of trials") + xlab("n, number of replicates")
```

```{r}
madata %>% filter(!is.na(fishersz)) %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
  ungroup %>% arrange(desc(n)) %>% mutate(trials = cumsum(nn)) %>% 
  filter(n < 50) %>% 
  full_join( madata %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>% 
               filter(n > 49) %>% ungroup %>% summarise(n = 50, nn = sum(nn))) %>%  
  ggplot(aes(x = n, y = trials)) + geom_point(col = "gray15") + 
  theme_bw() + labs(title = "Total Number of Studies with Number of Replicate (Trials) >= n") + ylab("Number of Studies") + xlab("n, number of replicates")
```

### 2019-03-21 cochrane/cochrane-example03.R

@@ -1,0 +1,86 @@
+##########################################################
+# read the generated (single) CSV file into a data frame:
+madata <- read.csv("~/Data/cochrane/cochrane_2018-06-09.csv",
+                   colClasses=c("integer", "character", "character",  # file       :  nr, name, doi
+                                "integer", "integer",                 # file       :  index, version
+                                "integer", "character",               # comparison :  nr, name
+                                "integer", "character", "character",  # outcome    :  nr, name, measure
+                                "integer", "character",               # subgroup   :  nr, name
+                                "character", "integer",               # study      :  name, year
+                                "numeric", "numeric",                 # effect, std.err.
+                                "integer", "numeric",                 # group 1    :  events, total
+                                "numeric", "numeric",                 # group 1    :  mean, se
+                                "integer", "numeric",                 # group 2    :  events, total
+                                "numeric", "numeric",                 # group 2    :  mean, se
+                                "integer"))                           # total N
+madata$total1 <- as.integer(madata$total1)
+madata$total2 <- as.integer(madata$total2)
+
+
+######################################
+# generate & show some summary stats:
+sumstats <- c("reviews"    =length(unique(madata$file.nr)),
+              "comparisons"=length(unique(paste(madata$file.nr, madata$comparison.nr, sep="."))),
+              "outcomes"   =length(unique(paste(madata$file.nr, madata$comparison.nr, madata$outcome.nr, sep="."))),
+              "subgroups"  =length(unique(paste(madata$file.nr, madata$comparison.nr, madata$outcome.nr, madata$subgroup.nr, sep="."))),
+              "studies"    =nrow(madata))
+print(t(t(sumstats)))
+
+
+##############################
+# show details of data frame:
+str(madata)
+
+head(madata)
+
+# check first entry, corresponding to first Cochrane review:
+madata[madata$file.nr==1, ]
+
+# example: show Richer-et-al review's data
+# (see http://doi.org/10.1002/14651858.CD005220.pub2):
[…]

### 2019-03-21 code_excess/excess.R

@@ -1,0 +1,407 @@
+##################################################################################################################################
+#Scaled OR over time with initial OR > 1
+madata %>% filter(outcome.measure == "Odds Ratio") %>% filter(!is.na(study.year)) %>% 
+  group_by(file.nr, comparison.nr, subgroup.nr) %>% 
+  mutate(counts = n()) %>% filter(counts > 1) %>% 
+  mutate(first.effect = effect[which.min(study.year)]) %>% 
+  filter(first.effect > 1) %>% 
+  mutate(scaled.effect = scale(effect), scaled.time = scale(study.year)) %>% 
+  ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = 1, alpha = 0.7)  + 
+  geom_smooth(method = lm) + theme_bw()  + 
+  labs(title = "Scaled and centered OR over time", subtitle = "Initial finding > 1") + ylab("Odds Ratio")  + ylab("Time")
+
+#Scaled OR over time with initial OR < 1
+madata %>% filter(outcome.measure == "Odds Ratio") %>% filter(!is.na(study.year)) %>% 
+  group_by(file.nr, comparison.nr, subgroup.nr) %>% 
+  mutate(counts = n()) %>% filter(counts > 1) %>% 
+  mutate(first.effect = effect[which.min(study.year)]) %>% 
+  filter(first.effect < 1) %>% 
+  mutate(scaled.effect = scale(effect), scaled.time = scale(study.year)) %>% 
+  ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = 1.2, alpha = 0.2)  + 
+  geom_smooth(method = lm) + theme_bw() + 
+  labs(title = "Scaled and centered OR over time", subtitle = "Initial finding < 1") + ylab("Odds Ratio")  + ylab("Time")
+
+#Scaled RR over time with initial RR > 1
+madata %>% filter(outcome.measure == "Risk Ratio") %>% filter(!is.na(study.year)) %>% 
+  group_by(file.nr, comparison.nr, subgroup.nr) %>% 
+  mutate(counts = n()) %>% filter(counts > 1) %>% 
+  mutate(first.effect = effect[which.min(study.year)]) %>% 
+  filter(first.effect > 1) %>% 
+  mutate(scaled.effect = scale(effect), scaled.time = scale(study.year)) %>% 
[…]

### 2019-03-21 code_excess/prediction.R

@@ -1,0 +1,111 @@
+rm(list = ls())
+require(biostatUZH)
+require(tidyverse)
+require(meta)
+load(file = "cochrane.RData")
+load(file = "yodata.RData")
+
+yodata <- yodata %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>% 
+  mutate(counts = n()) %>% filter(counts > 2)
+
+#Fishersz transformation applied has probably rounding errors.. :
+
+#Random effects prediction intervals, empirical vs. nominal coverage
+loo.metacor.upr <- function(cor, n, lev){
+  result <- c()
+  for ( i in seq_along(cor) ) {
+    result[i] <- metacor(cor = cor[-i], n = n[-i], sm = "COR", prediction = T, comb.random = T, level.predict = lev)$upper.predict
+  }
+  return(result)
+}
+
+loo.metacor.lwr <- function(cor, n, lev){
+  result <- c()
+  for ( i in seq_along(cor) ) {
+    result[i] <- metacor(cor = cor[-i], n = n[-i], sm = "COR", prediction = T, comb.random = T, level.predict = lev)$lower.predict
+  }
+  return(result)
+}
+
+#Empirical vs nominal coverage comparison for fixed effect prediction intervals
+#Loop:
+levels <- seq(0.5, 0.99, by = 0.1)
+e.cs <- c()
+temp.loop <- yodata %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>%  
+  filter(file.nr < 500)
+for(level in levels){
+  empirical.coverage <-  temp.loop %>% 
+    mutate(upr.pred = loo.metacor.upr(cor = fishersz, n = total1 + total2, lev = level),
+           lwr.pred = loo.metacor.lwr(cor = fishersz, n = total1 + total2, lev = level)) %>% 
+    filter(!is.na(lwr.pred) & !is.na(upr.pred)) %>% arrange(study.year) %>% 
+    mutate(covered = ifelse(fishersz < upr.pred & fishersz > lwr.pred, 1, 0), id = row_number()) %>%
+    filter(row_number() > 1) %>% 
+    ungroup() %>% summarise(sum(covered)/length(covered))
+  e.cs <- c(e.cs, empirical.coverage)
+}
+
[…]

### 2019-03-21 code_excess/process.R

@@ -1,0 +1,204 @@
+rm(list = ls())
+require(biostatUZH)
+require(tidyverse)
+require(meta)
+require(psych)
+
+##########################################################
+# read the generated (single) CSV file into a data frame:
+# PATH_HOME = path.expand("~") # user home
+# PATH = file.path(PATH_HOME, 'thesis/cochrane')
+# source(file.path(PATH, 'prepare.R'))
+# madata <- read.csv("~/thesis/cochrane/cochrane_2018-06-09.csv",
+#                    colClasses=c("integer", "character", "character",  # file       :  nr, name, doi
+#                                 "integer", "integer",                 # file       :  index, version
+#                                 "integer", "character",               # comparison :  nr, name
+#                                 "integer", "character", "character",  # outcome    :  nr, name, measure
+#                                 "integer", "character",               # subgroup   :  nr, name
+#                                 "character", "integer",               # study      :  name, year
+#                                 "numeric", "numeric",                 # effect, std.err.
+#                                 "integer", "numeric",                 # group 1    :  events, total
+#                                 "numeric", "numeric",                 # group 1    :  mean, se
+#                                 "integer", "numeric",                 # group 2    :  events, total
+#                                 "numeric", "numeric",                 # group 2    :  mean, se
+#                                 "integer"))                           # total N
+# madata$total1 <- as.integer(madata$total1)
+# madata$total2 <- as.integer(madata$total2)
+##########################################################
+# read the generated (single) CSV file into a data frame:
+
+yodata <- madata %>% filter(!is.na(outcome.measure))
+
+#Convert identical but differently spelled outcome names (~ 50).
+
[…]

### 2019-03-21 report/MSc_Report.tex
Small

@@
 In science, there is not only a need for accumulation of knowledge, but also for concentration.
-For the same reason as statistical analysis is performed on single experiments, it can also be used for results of multiple experiments or studies: to simplify and summarize the data at hand to a degree that is understandable for humans.
-The latter procedure goes usually under the term of meta-analysis.
+For the same reason as statistical analysis is performed on single experiments, it can also be used for results of multiple experiments or studies: to simplify and summarize the data at hand to a degree that is understandable.
+The latter procedure goes usually under the name of meta-analysis.
 Meta analyses are used to summarize results and evidence over multiple studies when they are considered to be similar enough.
@@
 In the face of the large amount of research that is done in some fields of empirical science, meta-analysis becomes increasingly important, for looking at all evidence would simply take very long for one person.
-Meta-analysises are often part of a systematic review, an effort of experts of a field to provide an overlook over the evidence.
+Meta-analyses are often part of a systematic review, an effort of experts of a field to provide an overlook over the evidence.
 In the course of a review, all literature and data with respect to a scientific question is collected and a meta-analysis is operated at the end to summarize the findings.
@@
 So at the end of the report, the reader will not only have an impression of the technical issues caused by reporting bias, but also of the abundance and extent of it in the dataset.
-Since the dataset is very large and of good quality, results might be again be generalizable to some extent to reporting bias in clinical science in general.
+Since the dataset is very large and of good quality, results might also be representative to some extent for reporting bias in clinical science.
 
@@
 The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite).
+
+\vspace{0mm}
 The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 11:15:04 2019
+% Thu Mar 21 12:54:57 2019
 \begin{table}[ht]
@@
     \end{tabular}
-  \caption{Dataset variable descriptions}
-  \label{variable}
+  \caption{Dataset variable descriptions  \label{variable}}
+
   \end{center}
@@
 The comparison type variable specifies what is compared, the outcome variable how it is compared, and the subgroup variable indicates if the comparison belongs to a certain subgroup.
-If desired, Figure \ref{review} can be compared to Table \ref{barbiturates} where an examplary review is listed.
+If desired, Figure \ref{review} can be compared to Table \ref{barbiturates} where an exemplary review is listed.
 
@@
 \end{tikzpicture}
-\caption{Structure of a hypothetical review with two different comparisons.}
+\caption{Structure of a hypothetical review with two different comparisons\label{review.structure}}
 \label{review.structure}
@@
 \endgroup
-\caption{Barbiturate and head injury review. In the columns, study names, comparison types and outcome measure of the comparisons are given.} 
+\caption{Barbiturate and head injury review. In the columns, study names, comparison types and outcome measure of the comparisons are given} 
 \label{barbiturates}
@@
 The dataset consists of 463820 comparisons and has 25 variables that specify the comparisons.
-The abundancy of some missing values in the dataset is given in Table \ref{missing}.
+The abundance of some missing values in the dataset is given in Table \ref{missing}.
 For variables as research subject, outcome and subgroup name and event counts there are no missing values.
-The relative abundancy of missing values is very low except for study years.
+The relative abundance of missing values is very low except for study years.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 11:15:04 2019
+% Thu Mar 21 12:54:58 2019
 \begin{table}[ht]
@@
 \endgroup
-\caption{Number of missing variables and measurements in the dataset.} 
+\caption{Number of missing variables and measurements in the dataset} 
 \label{missing}
@@
 \end{knitrout}
-\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications.}
+\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications}
 \label{study.years}
@@
 Figure \ref{study.outcomes} provides the frequencies of outcome types of the comparisons.
-Note that the abundancy of mean differences and standardized mean differences can also give an impression of the proportion of continuous outcome comparisons vs.
+Note that the abundance of mean differences and standardized mean differences can also give an impression of the proportion of continuous outcome comparisons vs.
 binary outcome comparisons in the dataset.
@@
 \end{knitrout}
-\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded.}
+\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded}
 \label{study.outcomes}
@@
 \end{knitrout}
-\caption{Empirical distribution of number of studies per review.}
+\caption{Empirical distribution of number of studies per review}
 \label{studies.per.review}
@@
 \end{knitrout}
-\caption{Empirical distribution of number of comparisons per review.}
+\caption{Empirical distribution of number of comparisons per review}
 \label{comparisons.per.review}
@@
 \end{knitrout}
-\caption{Empirical distribution of number of different research subjects per review.}
+\caption{Empirical distribution of number of different research subjects per review}
 \label{subjects.per.review}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 11:15:10 2019
+% Thu Mar 21 12:55:03 2019
 \begin{table}[ht]

### 2019-03-21 report/chapter02.Rnw
Small

@@
 print(xtable(tp1, label = "barbiturates", caption = "Barbiturate and head injury review.
-In the columns, study names, comparison types and outcome measure of the comparisons are given."), include.rownames = F, size = "footnotesize")
+In the columns, study names, comparison types and outcome measure of the comparisons are given"), include.rownames = F, size = "footnotesize")
 @
@@
 The dataset consists of \Sexpr{dim(madata)[1]} comparisons and has \Sexpr{dim(madata)[2]} variables that specify the comparisons.
-The abundancy of some missing values in the dataset is given in Table \ref{missing}.
+The abundance of some missing values in the dataset is given in Table \ref{missing}.
 For variables as research subject, outcome and subgroup name and event counts there are no missing values.
-The relative abundancy of missing values is very low except for study years.
+The relative abundance of missing values is very low except for study years.
 
@@
 
-print(xtable(missing.table, label = "missing", caption = "Number of missing variables and measurements in the dataset.", align = "lr"), include.colnames = F,
+print(xtable(missing.table, label = "missing", caption = "Number of missing variables and measurements in the dataset", align = "lr"), include.colnames = F,
       size = "footnotesize", digits = 0)
@@
 @
-\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications.}
+\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications}
 \label{study.years}
@@
 @
-\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded.}
+\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded}
 \label{study.outcomes}
@@
 @
-\caption{Empirical distribution of number of studies per review.}
+\caption{Empirical distribution of number of studies per review}
 \label{studies.per.review}
@@
 @
-\caption{Empirical distribution of number of comparisons per review.}
+\caption{Empirical distribution of number of comparisons per review}
 \label{comparisons.per.review}
@@
 @
-\caption{Empirical distribution of number of different research subjects per review.}
+\caption{Empirical distribution of number of different research subjects per review}
 \label{subjects.per.review}

### 2019-03-28 report/MSc_Report.tex
Update 28.03

@@
 
-In science, there is not only a need for accumulation of knowledge, but also for concentration.
+Meta-analysis is at the core of evidence based medicine because it allows to summarise evidence over multiple studies and provide a more broad view on success and effectivity of clinical treatments.
+The necessity of meta-analyses is also increased by the abundance of data and publications.
+Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to keep decisions based on quantitative and scientific criteria.
+
+\vspace{0mm}
+For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention.
+However, since the amount of empirical research is expanding, meta-analysis can be part in any field where repeated experiments are performed.
+The usefulness of meta-analysis expands therefore well over clinical science.
+
+\vspace{0mm}
+Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question.
+Systematic reviews may also incorporate results that can not be included in a meta-analysis, such as adverse effects reported in one trial, but a meta-analysis is the central part of a systematic review if results from multiple studies are available.
+The authors usually take their conclusions largely based on the results of the meta-analysis.
+
+% In science, there is not only a need for accumulation of knowledge, but also for concentration.
 For the same reason as statistical analysis is performed on single experiments, it can also be used for results of multiple experiments or studies: to simplify and summarize the data at hand to a degree that is understandable.
@@
 Meta analyses are used to summarize results and evidence over multiple studies when they are considered to be similar enough.
-
-\vspace{0mm}
-In the face of the large amount of research that is done in some fields of empirical science, meta-analysis becomes increasingly important, for looking at all evidence would simply take very long for one person.
+% 
+% \vspace{0mm}
+% In the face of the large amount of research that is done in some fields of empirical science, meta-analysis becomes increasingly important, for looking at all evidence would simply take very long for one person.
 Meta-analyses are often part of a systematic review, an effort of experts of a field to provide an overlook over the evidence.
 In the course of a review, all literature and data with respect to a scientific question is collected and a meta-analysis is operated at the end to summarize the findings.
-
-\vspace{0mm}
-In the case of clinical science, systematic reviews and meta-analyses do not only benefit scientists but also patients and clinicians, for both are provided with up-to-date summaries of current evidence with respect to a certain treatment.
+% 
+% \vspace{0mm}
+% In the case of clinical science, systematic reviews and meta-analyses do not only benefit scientists but also patients and clinicians, for both are provided with up-to-date summaries of current evidence with respect to a certain treatment.
 Therefore, meta-analysis is at the core of what is called evidence-based medicine.
+%
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 12:54:57 2019
+% Thu Mar 28 18:28:12 2019
 \begin{table}[ht]
@@
   \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up &  11 &  41 &  11 &  41 \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up &  14 &  27 &  13 &  26 \\ 
+Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11.00 & 41.00 & 11.00 & 41.00 \\ 
+  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14.00 & 27.00 & 13.00 & 26.00 \\ 
    \hline
@@
       \hline
-      \textbf{File name} & The name of the file from which the review data has been . \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
+      \textbf{file.nr} & The number of the file from which the review data has been . \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
       \textbf{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
-      \textbf{File index} & Internal index of the file in the Cochrane library.\\
-      \textbf{File version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
+      \textbf{file.index} & Internal index of the file in the Cochrane library.\\
+      \textbf{file.version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
       %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
       \hline
-      \textbf{Comparison type} & Specification of the interventions compared in the study\\
-      \textbf{Outcome} & Specification by which outcome the interventions are compared\\
-      \textbf{Subgroup} & Potentially indication of affiliation to subgroups\\
-      \textbf{Study name} & Name of the study to which the comparison belongs\\
-      \textbf{Study publication year} & Year in which the study was published\\
-      \textbf{Outcome measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
-      \textbf{Effect} & Measure of the effect given in the quantity denoted by \\ &``outcome measure''.\\
-      \textbf{Events (1/2)} & The counts of patients with an outcome \textit{if}\\ & measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
-      \textbf{Total (1/2)} & Number of patients in groups.\\
-      \textbf{Mean (1/2)} & Mean of patient measurements \textit{if} outcome is continuous.\\
-      \textbf{Standard deviation (1/2)} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
+      \textbf{comparison.name/.nr} & Specification of the interventions compared in the study  \\ and a unique number for the comparison\\
+      \textbf{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ and a unique number for the outcome\\
+      \textbf{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a \\ unique number for the subgroup\\
+      \textbf{study.name} & Name of the study to which the comparison belongs\\
+      \textbf{study.year} & Year in which the study was published\\
+      \textbf{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
+      \textbf{effect} & Measure of the effect given in the quantity denoted by \\ &``outcome measure''.\\
+      \textbf{events1/events2} & The counts of patients with an outcome \textit{if}\\ & measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
+      \textbf{total1/total2} & Number of patients in groups.\\
+      \textbf{mean1/mean2)} & Mean of patient measurements \textit{if} outcome is continuous.\\
+      \textbf{sd1/sd2} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
     \end{tabular}
-  \caption{Dataset variable descriptions  \label{variable}}
+  \caption{Dataset variable names and descriptions  \label{variable}}
 
@@
 
-The structure of a hypothetical review is shown in Figure \ref{review}. 
+The structure of a review is shown in Figure \ref{review}. 
 % Comparisons of a review can consecutively be subdivided into different comparison types, different outcome measures and different subgroups. 
@@
 \vspace{0mm}
-Having provided a rough overview over the dataset, now, some more specific information is provided.
-The dataset consists of 463820 comparisons and has 25 variables that specify the comparisons.
-The abundance of some missing values in the dataset is given in Table \ref{missing}.
+Having provided an overview over the dataset, now, some more specific information is provided.
+The dataset consists of 463820 comparisons and has 26 variables that specify the comparisons.
+Information about missing values in the dataset is given in Table \ref{missing}.
 For variables as research subject, outcome and subgroup name and event counts there are no missing values.
-The relative abundance of missing values is very low except for study years.
+The relative amount of missing values is very low except for study years.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 12:54:58 2019
+% Thu Mar 28 18:28:12 2019
 \begin{table}[ht]
@@
 The publication dates of the studies included in the dataset are shown in Figure \ref{study.years}.
+Most studies were published after 2000.
 
@@
 \end{knitrout}
-\caption{Empirical distribution of number of different research subjects per review}
+\caption{Empirical distribution of number of different comparison types per review}
 \label{subjects.per.review}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 21 12:55:03 2019
+% Thu Mar 28 18:28:18 2019
 \begin{table}[ht]
@@
   \hline
-1 & 109177 & 186267 \\ 
-  2 & 67685 & 83924 \\ 
-  3 & 47786 & 52245 \\ 
-  4 & 36155 & 36176 \\ 
-  5 & 28077 & 26552 \\ 
-  6 & 22689 & 20113 \\ 
-  7 & 18536 & 15888 \\ 
-  8 & 15466 & 12931 \\ 
-  9 & 13000 & 10817 \\ 
-  10 & 11001 & 9226 \\ 
-  11 & 9356 & 7988 \\ 
-  12 & 8052 & 7067 \\ 
-  13 & 6984 & 6365 \\ 
-  14 & 6041 & 5780 \\ 
-  15 & 5325 & 5325 \\ 
+1 & 109191 & 186300 \\ 
+  2 & 67699 & 83956 \\ 
+  3 & 47800 & 52270 \\ 
+  4 & 36169 & 36198 \\ 
+  5 & 28090 & 26570 \\ 
+  6 & 22702 & 20126 \\ 
+  7 & 18547 & 15896 \\ 
+  8 & 15475 & 12935 \\ 
+  9 & 13008 & 10821 \\ 
+  10 & 11008 & 9229 \\ 
+  11 & 9362 & 7991 \\ 
+  12 & 8057 & 7070 \\ 
+  13 & 6988 & 6368 \\ 
+  14 & 6044 & 5783 \\ 
+  15 & 5328 & 5328 \\ 
    \hline
@@
 
+\section{Meta Analysis}
+There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
+First the fixed effect meta-analysis will be explained.
+For convenience, notatotion will be identical whenever possible for both methods.
+Note that both methods can be used for continuous or dichotomous outcomes.
+For more details about the methods, see chapter 11 and 12 in \citep{metaanalysis}
+
+\vspace{0mm}
+Let $y_{i}$ be the effect size estimate of the study $i$ and $v_{i}$ be the corresponding variance of the effect size estimate.
+Effect measures have to be identical for all studies.
+Furthermore, let $w_i$ be the inverse of the variance of the estimate from study $i$, $1/v_{i}$ and $n$ the total number of studies.
+
+\vspace{0mm}
+The pooled estimate of the fixed effects model is then simply the weighted average with the weights given by the inverses of the variances, $w_{i}$.
+
+\begin{align*}
+\Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}}
+\end{align*}
+
+and the variance is the reciprocal of the sum of the weights,
+
+\begin{align*}
+\nu &= \frac{1}{\sum_{i = 1}^n w_{i}}
+\end{align*}
+
+\section{Reporting Bias Adjustment}
+One method to account for publication bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
+Its basic working principle is to mirror studies in a funnel plot that cause the funnel plot to be asymmetric and then to perform one of the meta-analyses as described in section {meta-analysis} with the mirrored studies.
+In the subsequent equations, the same terminology as for meta analyses will be used.
+
+% \begin{align} \label{cox reg}
+% P(Y < y|\mathbf{x}) = 1 - exp(-exp(h(y) - (\mathbf{x})^\top\beta)
+% \end{align}
+% 
+% See \cite{hothorn} for further information. It specifies the instantaneous risk of an event at time t to be
+% 
+% \begin{align}
+% \lambda_{0}(t)exp((\mathbf{x})^\top\beta) \nonumber
+% \end{align}
+% 
+% The model is regarded as a semi parametric model since it includes the covariates in a linear fashion but leaves the baseline hazard $\lambda_{0}(t)$ unspecified.
+The factor $exp((\mathbf{x})^\top\beta)$ has the interpretation of a hazard ratio between the reference with $\mathbf{x} = 0$.
+The formal definition of the hazard is
+% 
+% \begin{align}
+% h(t) = \lim_{h \to 0} \frac{P(t < T < t + h| T > t)}{h}
+% \end{align}
+% 
+% 
+% \begin{align} \label{generalized linear model}
+% \mathbf{Y}{_{ij}}|U{_i},\epsilon{_{ij}} = (1,x{_i}^\top)\beta + U{_i} + \epsilon{_{ij}}
+% \end{align}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-03-28 report/chapter02.Rnw
Update 28.03

@@
 <<echo=FALSE>>=
+# PATH_HOME = path.expand("~") # user home
+# PATH = file.path(PATH_HOME, 'thesis/code')
+# source(file.path(PATH, 'prepare.R'))
+
 PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'thesis/code')
-source(file.path(PATH, 'prepare.R'))
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH, 'code')
+PATH_RESULTS = file.path(PATH, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+data = pb.readData(path = PATH_DATA, file = FILE)
+tmp = pb.clean(data)
+data = tmp[[1]]
+aliases = tmp[[2]]
 
@@
                echo=TRUE, message=FALSE,
-               fig.width=8.5, fig.height=3,
+               fig.width=8, fig.height=3,
                out.width='\\textwidth-3cm',
@@
 \subsection{Structure and Content}
-The dataset consists of \Sexpr{length(unique(madata$file.nr))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(madata$study.name))} studies.
+The dataset consists of \Sexpr{length(unique(data$file.nr))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(data$study.name))} studies.
 Each study provides data of (multiple) comparisons of clinical interventions. 
@@
 <<echo=FALSE, results = 'asis'>>=
-tp1 <- arrange(filter(madata, file.nr == 21) %>% 
+tp1 <- arrange(filter(data, file.nr == 21) %>% 
           select(Study = study.name, Comparison_type = comparison.name, Outcome = outcome.name, 
@@
 <<echo=FALSE, results='asis'>>=
-tp1 <- arrange(filter(madata, file.nr == 21) %>% 
+tp1 <- arrange(filter(data, file.nr == 21) %>% 
           select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study)
@@
 \vspace{0mm}
-Having provided a rough overview over the dataset, now, some more specific information is provided.
-The dataset consists of \Sexpr{dim(madata)[1]} comparisons and has \Sexpr{dim(madata)[2]} variables that specify the comparisons.
-The abundance of some missing values in the dataset is given in Table \ref{missing}.
+Having provided an overview over the dataset, now, some more specific information is provided.
+The dataset consists of \Sexpr{dim(data)[1]} comparisons and has \Sexpr{dim(data)[2]} variables that specify the comparisons.
+Information about missing values in the dataset is given in Table \ref{missing}.
 For variables as research subject, outcome and subgroup name and event counts there are no missing values.
-The relative abundance of missing values is very low except for study years.
+The relative amount of missing values is very low except for study years.
 
 <<echo=FALSE>>=
-missing.mean <- madata %>% filter(!is.na(sd1) & sd1 > 0) %>% filter(!is.na(sd2) & sd2 > 0) %>% 
+missing.mean <- data %>% filter(!is.na(sd1) & sd1 > 0) %>% filter(!is.na(sd2) & sd2 > 0) %>% 
   summarise(total = length(sd1), na  = sum(is.na(mean1) | is.na(mean1))) %>% select(na)
 
-missing.sd <- madata %>% filter(!is.na(mean1) & !is.na(mean2)) %>% filter(mean1 != 0 & mean2 != 0) %>%
+missing.sd <- data %>% filter(!is.na(mean1) & !is.na(mean2)) %>% filter(mean1 != 0 & mean2 != 0) %>%
   summarise(total = length(mean1), na.sd  = sum(is.na(sd1) | is.na(sd1)), null.sd = length(sd1[sd1 <= 0 | sd2 <= 0])) %>% 
@@
 
-missing.ssize <- madata %>% summarize(total = length(total1), null.ss = length(total1[total1 <= 0 | total2 <= 0])) %>% 
+missing.ssize <- data %>% summarize(total = length(total1), null.ss = length(total1[total1 <= 0 | total2 <= 0])) %>% 
   select(null.ss)
 
-missing.effect <- sum(is.na(madata$effect))
+missing.effect <- sum(is.na(data$effect))
 
-missing.year <- sum(is.na(madata$study.year)) + length(madata$study.year[madata$study.year == 0])
+missing.year <- sum(is.na(data$study.year)) + length(data$study.year[data$study.year == 0])
 
-# missing.outcome <- sum(is.na(madata$effect))
+# missing.outcome <- sum(is.na(data$effect))
 
-# null.events <- madata %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
+# null.events <- data %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
 #   filter(is.na(sd1) | sd1 <= 0) %>% filter(is.na(sd2) | sd2 <= 0) %>% 
@@
 # 
-# null.events.single <- madata %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
+# null.events.single <- data %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
 #   filter(is.na(sd1) | sd1 <= 0) %>% filter(is.na(sd2) | sd2 <= 0) %>% 
@@
 # 
-# missing.events <- madata %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
+# missing.events <- data %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
 #   filter(is.na(sd1) | sd1 <= 0) %>% filter(is.na(sd2) | sd2 <= 0) %>% 
@@
 <<echo=FALSE>>=
-madata %>% filter(study.year < 2019 & study.year > 1920) %>% ggplot(aes(x = study.year)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
+data %>% filter(study.year < 2019 & study.year > 1920) %>% ggplot(aes(x = study.year)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
   theme_bw() + xlab("Year") + ylab("Study frequency")
@@
 <<echo=FALSE>>=
-yodata %>% group_by(outcome.measure) %>% count() %>% arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9) %>% 
-  ggplot(aes(x = outcome.measure, y = n)) +
+data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9) %>% 
+  ggplot(aes(x = outcome.measure.new, y = n)) +
   geom_col(col = "gray15", fill = "dodgerblue") +
@@
 <<echo=FALSE>>=
-madata %>% group_by(file.nr) %>% distinct(study.name) %>% count() %>%
+data %>% group_by(file.nr) %>% distinct(study.name) %>% count() %>%
   filter(n < 50) %>%
-  full_join( madata %>% group_by(file.nr) %>% distinct(study.name) %>% count %>%
+  full_join( data %>% group_by(file.nr) %>% distinct(study.name) %>% count %>%
                filter(n > 49) %>% mutate(n = 50)) %>%
@@
 <<echo=FALSE>>=
-madata %>% group_by(file.nr) %>% count() %>%
+data %>% group_by(file.nr) %>% count() %>%
   filter(n < 50) %>%
-  full_join( madata %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
+  full_join( data %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
                filter(n > 49) %>% mutate(n = 50)) %>%
@@
   theme_bw() +  xlab("Comparisons") + ylab("Review Frequency")
-# mean.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
+# mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
 #   ungroup() %>% group_by(file.nr) %>% 
@@
 # 
-# median.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
+# median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
 #   ungroup() %>% group_by(file.nr) %>% 
@@
 <<echo=FALSE>>=
-madata %>% group_by(file.nr) %>% distinct(comparison.name) %>% count() %>%
+data %>% group_by(file.nr) %>% distinct(comparison.name) %>% count() %>%
   filter(n < 15) %>%
-  full_join( madata %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
+  full_join( data %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
                filter(n > 14) %>% mutate(n = 15)) %>%
@@
 
-mean.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
+mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
   ungroup() %>% group_by(file.nr) %>% 
@@
 
-median.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
+median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
   ungroup() %>% group_by(file.nr) %>% 
@@
 @
-\caption{Empirical distribution of number of different research subjects per review}
+\caption{Empirical distribution of number of different comparison types per review}
 \label{subjects.per.review}
@@
 <<echo=FALSE, results='asis'>>=
-cum.repr.trials.nosub <- yodata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+cum.repr.trials.nosub <- data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
   filter(n < 15) %>%
-  full_join( yodata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+  full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
@@
 
-cum.repr.trials.subg <- yodata %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
+cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
   filter(n < 15) %>%
-  full_join( yodata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+  full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 

### 2019-03-28 report/chapter03.Rnw
Update 28.03

@@
                echo=TRUE, message=FALSE,
-               fig.width=8, fig.height=3,
+               fig.width=8.5, fig.height=3,
                out.width='\\textwidth-3cm',
@@
 <<echo=FALSE>>=
-yodata %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
+data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
@@
 <<echo=FALSE>>=
-yodata %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
+data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
   filter(events1 > 0 | events2 > 0) %>% 
@@
 <<echo=FALSE>>=
-trimfill.cont <- yodata %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 50) %>% 
+trimfill.cont <- data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 50) %>% 
   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
@@
 <<echo=FALSE>>=
-trimfill.bin <- yodata %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% #filter(file.nr < 503) %>% 
+trimfill.bin <- data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% #filter(file.nr < 503) %>% 
   filter(events1 > 0 | events2 > 0) %>% 

### 2019-03-28 report/chapter04.Rnw
Update 28.03

--- 2019-03-28 report/MSc_Report.tex
@@
-\documentclass[11pt,a4paper,twoside]{book}\usepackage[]{graphicx}\usepackage[]{color}
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
-
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
-
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
-
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-\usepackage{alltt}
-\input{header.sty}   % packages, layout and standard macros
-
-\usepackage{verbatim}
-\usepackage{tikz}
-\usetikzlibrary{trees}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\begin{document}
-\input{title}
-
-\graphicspath{{./figure/}}
-\DeclareGraphicsExtensions{.pdf,.png}
-\setcounter{tocdepth}{1}
-
-\thispagestyle{empty}
-\begin{center}
-  \vspace*{6cm}{\bfseries\Huge
-  $p$-values:\\[5mm] their use, abuse and proper use \\[5mm]
-  illustrated with seven facets 
-  }
-  \vfill
-  \rm
-
-  \LARGE
-  M\"axli Musterli\\[12mm]
-
-  \normalsize
-  Version \today
-\end{center}
-\newpage
-\thispagestyle{empty}~
-\newpage
-\pagenumbering{roman}
-
-\thispagestyle{plain}\markboth{Contents}{Contents}
-\tableofcontents
-\setkeys{Gin}{width=.8\textwidth}
-
-\chapter*{Preface}
-\addtocontents{toc}{\protect \vspace*{13.mm}}
-\addcontentsline{toc}{chapter}{\bfseries{Preface}}
-\thispagestyle{plain}\markboth{Preface}{Preface}
-
-Howdy!
-
-\bigskip
-
-\begin{flushright}
-  Max Muster\\
-  June 2018
-\end{flushright}
-
-\addtocontents{toc}{\protect \vspace*{10mm}}
-
-\cleardoublepage
-\pagenumbering{arabic}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 01
-
-\chapter{Introduction}
-
-Meta-analysis is at the core of evidence based medicine because it allows to summarise evidence over multiple studies and provide a more broad view on success and effectivity of clinical treatments.
-The necessity of meta-analyses is also increased by the abundance of data and publications.
-Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to keep decisions based on quantitative and scientific criteria.
-
-\vspace{0mm}
-For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention.
-However, since the amount of empirical research is expanding, meta-analysis can be part in any field where repeated experiments are performed.
-The usefulness of meta-analysis expands therefore well over clinical science.
-
-\vspace{0mm}
-Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question.
-Systematic reviews may also incorporate results that can not be included in a meta-analysis, such as adverse effects reported in one trial, but a meta-analysis is the central part of a systematic review if results from multiple studies are available.
-The authors usually take their conclusions largely based on the results of the meta-analysis.
-
-% In science, there is not only a need for accumulation of knowledge, but also for concentration.
-For the same reason as statistical analysis is performed on single experiments, it can also be used for results of multiple experiments or studies: to simplify and summarize the data at hand to a degree that is understandable.
-The latter procedure goes usually under the name of meta-analysis.
-Meta analyses are used to summarize results and evidence over multiple studies when they are considered to be similar enough.
-% 
-% \vspace{0mm}
-% In the face of the large amount of research that is done in some fields of empirical science, meta-analysis becomes increasingly important, for looking at all evidence would simply take very long for one person.
-Meta-analyses are often part of a systematic review, an effort of experts of a field to provide an overlook over the evidence.
-In the course of a review, all literature and data with respect to a scientific question is collected and a meta-analysis is operated at the end to summarize the findings.
-% 
-% \vspace{0mm}
-% In the case of clinical science, systematic reviews and meta-analyses do not only benefit scientists but also patients and clinicians, for both are provided with up-to-date summaries of current evidence with respect to a certain treatment.
-Therefore, meta-analysis is at the core of what is called evidence-based medicine.
-%
-
-\vspace{0mm}
-However, there are problems that potentially limit the validity of meta-analysis; studies at hand can be biased or heterogeneity between study results can be large and the number of studies small.
-The importance and the issues of meta-analysis are the reasons why they have been chosen as one general topic of the masters thesis.
-One particular problem will furthermore be investigated in more detail: reporting bias and meta-analysis.
-Not only will the methods to deal with issues as reporting bias be discussed, but also will they be applied on a dataset of systematic reviews that can be used for meta-analysis.
-So at the end of the report, the reader will not only have an impression of the technical issues caused by reporting bias, but also of the abundance and extent of it in the dataset.
-Since the dataset is very large and of good quality, results might also be representative to some extent for reporting bias in clinical science.
-
-\subsection{Cochrane and the Cochrane Database of Systematic Reviews}
-The Cochrane Organization has specialized on systematic reviews in clinical science.
-It publishes and maintains a library with a large number of systematic reviews that are available in some countries to the public.
-
-\vspace{0mm}
-The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite).
-
-\vspace{0mm}
-The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests.
-This might further improve the validity and precision of findings and conclusions that have been made based on this data.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 02
-
-\chapter{The Cochrane Dataset}
-
-\subsection{Structure and Content}
-The dataset consists of 5016 systematic reviews from the Cochrane Library with 52995 studies.
-Each study provides data of (multiple) comparisons of clinical interventions. 
-% It can not be ruled out that some comparisons are retrospective, e.g. from observational studies. 
-In Table \ref{barbiturate.row}, two comparisons from a systematic review about effects of barbiturates are shown as they are given in the dataset.
-As can be seen, the comparison is further specified by the variables in the columns.
-One row of the dataset is one comparison.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 28 18:28:12 2019
-\begin{table}[ht]
-\centering
-\begingroup\scriptsize
-\begin{tabular}{lllrrrr}
-  \hline
-Study & Comparison\_type & Outcome & Events & Total & Events\_c & Total\_c \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11.00 & 41.00 & 11.00 & 41.00 \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14.00 & 27.00 & 13.00 & 26.00 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Example of two comparisons as given in the dataset.
-Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
-Further descriptive variables have been ommitted}
-\label{barbiturate.row}
-\end{table}
-
-A complete listing of the variables is given in Table \ref{variable}.
-They can roughly be separated into variables that specify the review in which the comparison is contained and variables that specify the comparison itself (separated by a horizontal line in Table \ref{variable}).
-
-\begin{table}[ht]
-  \begin{center}
-    \begin{tabular}{l l}
-      \textbf{Variable} & \textbf{Description}\\
-      \hline
-      \textbf{file.nr} & The number of the file from which the review data has been . \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
-      \textbf{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
-      \textbf{file.index} & Internal index of the file in the Cochrane library.\\
-      \textbf{file.version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
-      %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
-      \hline
-      \textbf{comparison.name/.nr} & Specification of the interventions compared in the study  \\ and a unique number for the comparison\\
-      \textbf{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ and a unique number for the outcome\\
-      \textbf{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a \\ unique number for the subgroup\\
-      \textbf{study.name} & Name of the study to which the comparison belongs\\
-      \textbf{study.year} & Year in which the study was published\\
-      \textbf{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
-      \textbf{effect} & Measure of the effect given in the quantity denoted by \\ &``outcome measure''.\\
-      \textbf{events1/events2} & The counts of patients with an outcome \textit{if}\\ & measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
-      \textbf{total1/total2} & Number of patients in groups.\\
-      \textbf{mean1/mean2)} & Mean of patient measurements \textit{if} outcome is continuous.\\
-      \textbf{sd1/sd2} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
-    \end{tabular}
-  \caption{Dataset variable names and descriptions  \label{variable}}
-
-  \end{center}
-\end{table}
-
-The structure of a review is shown in Figure \ref{review}. 
-% Comparisons of a review can consecutively be subdivided into different comparison types, different outcome measures and different subgroups. 
-The comparison type variable specifies what is compared, the outcome variable how it is compared, and the subgroup variable indicates if the comparison belongs to a certain subgroup.
-If desired, Figure \ref{review} can be compared to Table \ref{barbiturates} where an exemplary review is listed.
-
-\begin{figure}
-\tikzstyle{every node}=[draw=black,thick,anchor=west]
-\tikzstyle{selected}=[draw=red,fill=red!30]
-\tikzstyle{optional}=[dashed,fill=gray!50]
-\begin{tikzpicture}
-[grow = right, anchor = west, 
-  growth parent anchor=east, % added code
-  parent anchor=east]
-  \node {Review} [edge from parent fork right]
-    child { node {Comparison type 2}
-      child { node {Outcome 2}}
-      child { node {Outcome 1}
-        child { node {Subgroup 2}}
-        child { node {Subgroup 1}}}
-    }
-    child [missing] {}		
-    child { node {Comparison type 1  }};
-\end{tikzpicture}
-\caption{Structure of a hypothetical review with two different comparisons\label{review.structure}}
-\label{review.structure}
-\end{figure}
-
-% \vspace{0mm}
-% Lets consider the previously mentioned barbiturate and head injury review.
-The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates''.
-The medical background is that one knew that barbiturates could cause relief in intra-cranial pressure, but also reduce cerebral blood flow.
-Because one effect is thought to be beneficial for persons with severe head injuries while the other isn't, the authors of the review wanted to find out if there is a net benefit of barbiturates.
-% 
-% \vspace{0mm}
-% The review comprises five studies in total.
-Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental, which would be the comparison/research subject to speak in the previously introduced notions.
-% 
-% \vspace{0mm}
-% All the studies convey multiple information to the review.
-As an example, that could be death or death \textit{and} severe disability at follow up as an outcome.
-Again, the study can be further split up in different subgroups, here for example in a group with - and without haematoma.
-% 
-% \vspace{0mm}
-% The complete listing of outcomes is in table \ref{barbiturates}.
-The table also gives an illustration of the variety of data that can be included in a review.
-We have for example continuous and binary outcome data, that again is divided into a variety of different things that have been measured.
-Often, additionally to the main study result, also adverse effects are for example included which are in this case separate outcomes and possibly subgroups.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 28 18:28:12 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-Study & Comparison & Outcome \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Barbiturate and head injury review. In the columns, study names, comparison types and outcome measure of the comparisons are given} 
-\label{barbiturates}
-\end{table}
-
-% The research subject or outcome type can possibly already be well defined in the general review question.
-Conversely, research subject or comparison has to be further specified in outcome and subgroup categories.
-As may have been implied, the terminology does not rely to a hundred percent on strict functional definitions.
-
-It is important to not confuse comparisons with studies.
-A study can contribute multiple comparisons to a systematic review.
-Also, despite a comparison has variables concerning event counts and means, it can only have one of the two, either means (if the outcome measure is continuous) or event counts (for binary outcomes).
-
-\vspace{0mm}
-Having provided an overview over the dataset, now, some more specific information is provided.
-The dataset consists of 463820 comparisons and has 26 variables that specify the comparisons.
-Information about missing values in the dataset is given in Table \ref{missing}.
-For variables as research subject, outcome and subgroup name and event counts there are no missing values.
-The relative amount of missing values is very low except for study years.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 28 18:28:12 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lr}
-  \hline
-  \hline
-Missing mean values & 1287 \\ 
-  Missing standard deviations & 999 \\ 
-  Missing effects & 158 \\ 
-  Missing study year & 27234 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Number of missing variables and measurements in the dataset} 
-\label{missing}
-\end{table}
-
-More properties of the reviews, the studies and the comparisons in the dataset will be provided on the following pages.
-The publication dates of the studies included in the dataset are shown in Figure \ref{study.years}.
-Most studies were published after 2000.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-8-1}
-
-}
-
-\end{knitrout}
-\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications}
-\label{study.years}
-\end{figure}
-
-Figure \ref{study.outcomes} provides the frequencies of outcome types of the comparisons.
-Note that the abundance of mean differences and standardized mean differences can also give an impression of the proportion of continuous outcome comparisons vs.
-binary outcome comparisons in the dataset.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-9-1}
-
-}
-
-\end{knitrout}
-\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded}
-\label{study.outcomes}
-\end{figure}
-
-It is also possible to look at the properties of the reviews.
-One question could be how many studies or comparisons that a review comprises.
-The former is shown in Figure \ref{studies.per.review} and the latter in Figure \ref{comparisons.per.review}.
-It can be seen that while almost 400 reviews consist of one study only, there are more than 150 with equal or more than 30 distinct studies.
-A similar variance between reviews can also be observed when looking at the number of comparisons.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-10-1}
-
-}
-
-\end{knitrout}
-\caption{Empirical distribution of number of studies per review}
-\label{studies.per.review}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-11-1}
-
-}
-
-\end{knitrout}
-\caption{Empirical distribution of number of comparisons per review}
-\label{comparisons.per.review}
-\end{figure}
-
-A question not to be mistaken with the previous would be how many comparison \textit{types} there are per review.
-This gives an additional impression of the scope of a review.
-Analogously to the previous figures, the empirical distribution of comparison types is depicted in Figure \ref{subjects.per.review}.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-12-1}
-
-}
-
-\end{knitrout}
-\caption{Empirical distribution of number of different comparison types per review}
-\label{subjects.per.review}
-\end{figure}
-
-% At the end, a main goal of the thesis is to analyze reviews with respect to reporting bias in meta analyses. 
-For comparisons to be suitable for usage in meta-analysis, they have to be somewhat identical (same comparison type, outcome measure and possibly subgroup).
-For an analysis of reporting bias, again a certain number of studies is required in order for reporting bias to be detectable by the methods.
-One question would therefore be: How many groups of identical comparisons of a certain size are given in the dataset?
-This depends on which degree of similarity between comparisons is considered to be sufficient.
-
-\vspace{0mm}
-In Table \ref{repr.groups}, two different similarity criteria have been used.
-One is based on the same comparison type and outcome measure, the other includes additionally subgroup affiliation of comparisons, i.e.
-only comparisons in the same subgroups are considered to be similar enough.
-
-\vspace{0mm}
-Table \ref{repr.groups} shows the cumulative number of \textit{groups} of comparisons with equal or more than $n$ comparisons.
-Practically, this means that this number of meta analyses can be performed with each having at least $n$ comparisons.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 28 18:28:18 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-n & Cumulative sum (without subgroups) & Cumulative sum (with subgroups) \\ 
-  \hline
-1 & 109191 & 186300 \\ 
-  2 & 67699 & 83956 \\ 
-  3 & 47800 & 52270 \\ 
-  4 & 36169 & 36198 \\ 
-  5 & 28090 & 26570 \\ 
-  6 & 22702 & 20126 \\ 
-  7 & 18547 & 15896 \\ 
-  8 & 15475 & 12935 \\ 
-  9 & 13008 & 10821 \\ 
-  10 & 11008 & 9229 \\ 
-  11 & 9362 & 7991 \\ 
-  12 & 8057 & 7070 \\ 
-  13 & 6988 & 6368 \\ 
-  14 & 6044 & 5783 \\ 
-  15 & 5328 & 5328 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Cumulative number of groups with number of reproduction trials >= n} 
-\label{repr.groups}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 03
-
-\chapter{Results}
-
-One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect.
-This is termed reporting bias in the scientific world.
-If reporting bias is present, the classical approaches to merge single study results in to an overall intervention effect may fail because the underlying studies are biased.
-There are tests that can be applied to find out if reporting bias is present in the meta analysis.
-
-\vspace{0mm}
-For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
-The following three figures show the distribution of p-values of the corresponding tests.
-Note that only meta analyses with more than 10 comparisons have been included.
-
-\vspace{0mm}
-Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
-The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
-\label{egger.cont}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
-\label{thomson.cont}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{begg.cont}
-\end{figure}
-
-For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{peters.bin}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{harbord.bin}
-\end{figure}
-
-Another less conventional way to look for publication bias is to see how many studies are ``reflected'' by the trim and fill method.
-As a first impression, a histogram with the fraction of trimmed of all comparisons is shown in figure \ref{trimfill.cont}.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of fractions of trimmed comparisons from meta analyses with continuous outcomes.}
-\label{trimfill.cont}
-\end{figure}
-
-The mean fraction of trimmed comparisons for continuous outcomes is 0.22 and the median 0.2.
-
-The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of fractions of trimmed comparisons from meta analyses with binary outcomes.}
-\label{trimfill.bin}
-\end{figure}
-
-The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.17.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 % LaTeX file for Chapter 04
+<<'preamble04',include=FALSE>>=
+library(knitr)
+opts_chunk$set(
+    fig.path='figure/ch04_fig', 
+    self.contained=FALSE,
+    cache=FALSE
+) 
+@
 
@@
 % \end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 05
-
-\chapter{Conclusions}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-% LaTeX file for Chapter 01
-
-\chapter{Appendix}
-
-Maybe some R code here, probably a \rr{sessionInfo()}
-
-\cleardoublepage
-\phantomsection
-\addtocontents{toc}{\protect \vspace*{10mm}}
-\addcontentsline{toc}{chapter}{\bfseries Bibliography}
-
-\bibliographystyle{mywiley} 
-\bibliography{biblio}
-
-\cleardoublepage
-
-\end{document}

### 2019-03-28 code/PubBias_functions.R

@@ -1,0 +1,146 @@
+# by Simon Schwab, 2019
+
+# Reads the data
+pb.readData = function(path, file) {
+  
+  data = read.csv(file.path(path, file),
+                  colClasses=c("integer", "character", "character",  # file       :  nr, name, doi
+                               "integer", "integer",                 # file       :  index, version
+                               "integer", "character",               # comparison :  nr, name
+                               "integer", "character", "character",  # outcome    :  nr, name, measure
+                               "integer", "character",               # subgroup   :  nr, name
+                               "character", "integer",               # study      :  name, year
+                               "numeric", "numeric",                 # effect, std.err.
+                               "numeric", "numeric",                 # group 1    :  events, total
+                               "numeric", "numeric",                 # group 1    :  mean, se
+                               "numeric", "numeric",                 # group 2    :  events, total
+                               "numeric", "numeric",                 # group 2    :  mean, se
+                               "numeric"))                           # total N
+  # some cleanup
+  data$outcome.measure[grep("&#223;-agonist", data$outcome.measure)] = "beta-agonist"
+  data$outcome.measure[grep("Hedge[s ]*&#180", data$outcome.measure)] = "Hedges' g"
+  
+  return(data)
+}
+
+# Cleans the raw data with some reg expressions
+pb.clean = function(data) {
+  
+  names = unique(data$outcome.measure)
+  data$outcome.measure.new = data$outcome.measure
+  
+  # Define aliases, first element will be used for all aliases
+  aliases=list()
+  aliases[[1]] = grep("risk ratio|RR|relat[ive]* risk", names, perl = TRUE, ignore.case = TRUE, value = TRUE)
+  aliases[[2]] = grep("^mean dif|^MD|change in", names, perl = TRUE, ignore.case = TRUE, value = TRUE)
+  aliases[[3]] = grep("Std. mean|SMD", names, perl = TRUE, ignore.case = TRUE, value = TRUE)
[…]

### 2019-04-07 report/MSc_Report.tex
Results update

@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 28 18:28:12 2019
+% Sun Apr  7 21:19:44 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 28 18:28:12 2019
+% Sun Apr  7 21:19:45 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Mar 28 18:28:18 2019
+% Sun Apr  7 21:19:51 2019
 \begin{table}[ht]
@@
 
-One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect.
-This is termed reporting bias in the scientific world.
-If reporting bias is present, the classical approaches to merge single study results in to an overall intervention effect may fail because the underlying studies are biased.
-There are tests that can be applied to find out if reporting bias is present in the meta analysis.
+One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
+If this is not given, one often speaks of publication bias.
+In fact, there can also be other reasons for this (see discussion section).
+A more appropriate term for the phenomenon is small study effect.
+If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
 
 \vspace{0mm}
-For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
-The following three figures show the distribution of p-values of the corresponding tests.
-Note that only meta analyses with more than 10 comparisons have been included.
-
-\vspace{0mm}
-Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
-The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
+To provide an overview over the issue, first it is shown how mean effect size decreases with increasing sample size of the comparisons in Figure \ref{effect.samplesize}.
+All effects are normalized by subtracting the mean effect size of the dataset and dividng through the standard deviation.
+Then, the mean of the absolute value for a given sample size is plotted against its sample size.
+Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all sample sizes.
 
@@
 \end{knitrout}
-\caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
-\label{egger.cont}
+\caption{Mean of the absolute of the normalized effect size plotted against the total sample size.}
+\label{effect.samplesize}
 \end{figure}
+
+\vspace{0mm}
+There are tests that can be applied to find out if reporting bias is present in the meta analysis.
+For the precise description, see the methods section.
+Application of the tests is only recommended if there are ten or more studies that can be used, so all meta-analyses with less than ten studies have been excluded.
+
+\vspace{0mm}
+There are modifications to make tests more appropriate in case of binary outcomes, therefore, the results of the tests are separated in continuous outcome test results and dichotomoized outcome results.
+In Figure \ref{bias.results.bin} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for dichotomous outcomes.
+The same is shown in Figure \ref{bias.results.cont} for continuous outcome measures.
+
+% # <<results = 'asis', Echo = FALSE>>=
+% # rejection.bin <- data.bin.ext %>% summarize(egger.rejection = mean(egger.test),
+% #                                             schwarzer.rejection = mean(schwarzer.test),
+% #                                             rucker.rejection = mean(rucker.test),
+% #                                             harbord.rejection = mean(harbord.test),
+% #                                             peter.rejection = mean(peter.test))
+% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
+% # @
 
@@
 \end{knitrout}
-\caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
-\label{thomson.cont}
+\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
+\label{bias.results.bin}
 \end{figure}
@@
 \end{knitrout}
-\caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{begg.cont}
+\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
+\label{bias.results.cont}
 \end{figure}
 
-For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
+Furthermore, one can investigate how well the tests give the same results, i.e.
+classify the same study collections as having publication bias.
+This is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
+
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Apr  7 21:20:02 2019
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lll}
+  \hline
+ & Test Agreement & P-value Correlation \\ 
+  \hline
+egger.schwarzer & 0.84 & 0.38 \\ 
+  egger.peter & 0.84 & 0.44 \\ 
+  egger.rucker & 0.83 & 0.39 \\ 
+  egger.harbord & 0.91 & 0.75 \\ 
+  schwarzer.peter & 0.85 & 0.24 \\ 
+  schwarzer.rucker & 0.83 & 0.30 \\ 
+  schwarzer.harbord & 0.88 & 0.52 \\ 
+  rucker.peter & 0.89 & 0.67 \\ 
+  harbord.peter & 0.86 & 0.45 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)} 
+\label{agreement.bin}
+\end{table}
+
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Apr  7 21:20:02 2019
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lll}
+  \hline
+ & Test Agreement & P-value Correlation \\ 
+  \hline
+thomson.egger & 0.85 & 0.67 \\ 
+  thomson.begg & 0.75 & 0.45 \\ 
+  egger.begg & 0.75 & 0.38 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)} 
+\label{agreement.cont}
+\end{table}
+
+\vspace{0mm}
+Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
+The p-values of two tests are shown with respect to the sample size of the studies in Figure \ref{pvalues.samplesize.bin} for peters test based on dichotomous outcomes and in Figure \ref{pvalues.samplesize.cont} for thomson and sharp's test based on continuous outcomes.
+%(Suggests that 10 is likely too small)
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
 
@@
 \end{knitrout}
-\caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{peters.bin}
+\caption{P-values of peters test for small study effects and their corresponding sample size (dichotomous outcomes)}
+\label{pvalues.samplesize.bin}
 \end{figure}
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
 
@@
 \end{knitrout}
-\caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{harbord.bin}
+\caption{P-values of thomson and sharp's test for small study effects and their corresponding sample size (continuous outcomes)}
+\label{pvalues.samplesize.cont}
 \end{figure}
 
-Another less conventional way to look for publication bias is to see how many studies are ``reflected'' by the trim and fill method.
-As a first impression, a histogram with the fraction of trimmed of all comparisons is shown in figure \ref{trimfill.cont}.
+\vspace{0mm}
+One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
+A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
+The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.17.
+In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-25-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-26-1}
 
@@
 
-The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.17.
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}
+
+}
+
+\end{knitrout}
+\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of peters test and dichotomous outcomes}
+\label{trimfill.pvalues.bin}
+\end{figure}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}
+
+}
+
+\end{knitrout}
+\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of thomson and sharp's test and continuous outcomes}
+\label{trimfill.pvalues.cont}
+\end{figure}
+
+% 
+% For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
+The following three figures show the distribution of p-values of the corresponding tests.
+Note that only meta analyses with more than 10 comparisons have been included.
+% 
+% \vspace{0mm}
+% Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
+The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
+%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
+%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
+%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+%   mutate(n = n()) %>% filter(n > 9) %>% 
+%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
+%                             method = "linreg")$p.val) %>% 
+%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+%   theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% @
+% \caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
+% \label{egger.cont}
+% \end{figure}
+% 
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
+%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
+%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
+%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+%   mutate(n = n()) %>% filter(n > 9) %>% 
+%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
+%                             method = "mm")$p.val) %>% 
+%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+%   theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% @
+% \caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
+% \label{thomson.cont}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
+%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
+%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
+%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+%   mutate(n = n()) %>% filter(n > 9) %>% 
+%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
+%                             method = "rank")$p.val) %>% 
+%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+%   theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% @
+% \caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
+% \label{begg.cont}
+% \end{figure}
+% 
+% 
+% For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
+%   filter(events1 > 0 | events2 > 0) %>% 
+%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
+%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+%   mutate(n = n()) %>% filter(n > 9) %>% 
+%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
+%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+%   theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% @
+% \caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
+% \label{peters.bin}
+% \end{figure}
+% 
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
+%   filter(events1 > 0 | events2 > 0) %>% 
+%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
+%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+%   mutate(n = n()) %>% filter(n > 9) %>% 
+%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
+%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+%   theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% @
+% \caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
+% \label{harbord.bin}
+% \end{figure}
 
@@
 Note that both methods can be used for continuous or dichotomous outcomes.
-For more details about the methods, see chapter 11 and 12 in \citep{metaanalysis}
+For more details about the methods, see chapter 11 and 12 in \citet{metaanalysis}
 
@@
 \vspace{0mm}
-The pooled estimate of the fixed effects model is then simply the weighted average with the weights given by the inverses of the variances, $w_{i}$.
+The pooled estimate $\Delta_{f}$ of the fixed effects model is then simply the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
+The variance $\nu_{f}$ is the reciprocal of the sum of the weights as in \ref{reciproce.variance}.
 
-\begin{align*}
-\Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}}
-\end{align*}
+\begin{align}
+\Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
+\nu_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
+\end{align}
 
-and the variance is the reciprocal of the sum of the weights,
+The computation of random effects meta-analysis is more complicated.
+Random effects meta-analysis will give smaller studies with larger variance of their estimates more weight in the pooled estimate.
+The key principle is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
+Thus a within - and between study variance has to be computed.
+Let $Q$ be the heterogeneity of study estimates as given in \ref{Q.heterogeneity}.
+The degrees of freedom $d$ are equal to $n-1$.
+$C$ is defined in \ref{C.definition}.
+The between study variance $\tau^2$ is then defined as in \ref{Tao.definition}.
+The definition follows \citet{tau.estimator}, but other methods are available such as maximum likelihood or restricted maximum likelihood estimators.
 
-\begin{align*}
-\nu &= \frac{1}{\sum_{i = 1}^n w_{i}}
-\end{align*}
+\begin{align}
+Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta_{f})^2 \label{Q.heterogeneity} \\
+C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
+\tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
+\end{align}
+
+The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is then defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
+It is used to calculate a new kind of weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
+The variance of $\Delta_{r}$, $\nu_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
+
+\begin{align}
+v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
+\Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
+\nu_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
+\end{align}
+
+A p-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Z.value}) and the usual computation as in (\ref{p.value.calculation}), $\Phi$ being the cumulative distribution function of a standard normal distribution.
+
+\begin{align}
+Z &= \frac{\Delta}{\sqrt{\nu}} \label{Z-value} \\
+p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
+\end{align}
+
+\section{Reporting Bias Test}
+Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. Five of them will be presented.
+First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
+
+\vspace{0mm}
+Again, let $y_{i}$ be the effect size estimate and $v_{i}$ the variance estimate of study $i$.
+Then, the standardized effect size $y_{i}^\star$ is given in \ref{begg.stand.eff}.
+$\Delta_{f}$ is the pooled estimate for fixed effect estimate defined in \ref{weighted.mean}.
+Let $v_{i}^\star$ be the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
+
+\begin{align}
+v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} \\
+y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff}
+\end{align}
+
+Then, a rank correlation test based on Kendall's tau is used.
+The pairs of $y_{i}^\star$ and $v_{i}^\star$ that are ranked in the same order are enumerated.
+Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (e.g.
+larger standardized effect size and smaller variance).
+Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
+$n$ is the number of studies.
+
+\begin{align}
+Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
+\end{align}
+
+The changes in the case of ties are negligible \cite[410]{begg.ties}.
+
+\vspace{0mm}
+Alternatively, one can use Eggers test \citep{Egger} that is based on simple linear regression.
+Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$, $x_{i} = 1/\sqrt{v_{i}}$.
+Furthermore, let $\hat{y_{i}} = \beta_{0} + \beta_{1}x_{i}$.
+Using linear regression, one obtains a least-squares estimate for $\beta_{0}$, and the null hypothesis $\beta_{0} = 0$ can be tested using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the t-distribution.
+The p-value for $\beta_{0} = 0$ (no reporting bias) is given in \ref{egger.pvalue}.
+
+\begin{align}
+p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
+\end{align}
+
+A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
+Let $\tau^2$ be equal to \ref{Tau.definition}.
+The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
+Then, a weighted regression is carried out with weigths $1/v_{i}^\star$ as given in \ref{ranef.study.variance}.
+Analagous to Eggers test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta{0} = 0$.
+
+\begin{align}
+y_{i} \sim N(\beta_{0} + \beta{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
+\end{align}
+
+A rank based alternative to Peters test for binary outcomes is the Harbords test \citep{Harbord}.
+Let $e_{t}$ be the number of events in a two-armed study $i$ and $n_{t}$ be the total number of patients in the treatment arm and the same for $n_{c}$ and $e_{c}$ for the control arm.
+Then the score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
+
+\begin{align}
+r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
+v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
+\end{align}
+
+Similarly to Eggers or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ depending on the standard error $1/\sqrt{v_{i}}$ with the $1/v_{i}$ used as weigths.
+$r_{i}/v_{i}$ is also known as peto odds ratio.
 
 \section{Reporting Bias Adjustment}
-One method to account for publication bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
-Its basic working principle is to mirror studies in a funnel plot that cause the funnel plot to be asymmetric and then to perform one of the meta-analyses as described in section {meta-analysis} with the mirrored studies.
-In the subsequent equations, the same terminology as for meta analyses will be used.
+One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
+It is based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
+If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies.
+Trim and Fill is a nonparametric approach.
+
+\vspace{0mm}
+The algorithm for the method tries to estimate the number of studies that are not available due to reporting bias, $k$.
+There are different estimators for $k$.
+First, $\Delta$ is estimated using a fixed or random effects model.
+Then, the $k$ effect size estimates with the smallest standard errors are trimmed, and $\Delta$ is estimated again.
+The procedure is repeated until $k$ is 0 and the funnel plot is symmetric.
+The total number of missing studies is then mirrored with respect to the final effect size estimate $\Delta$, and $\Delta$ and its standard error is then computed to obtain an unbiased estimate.
 

### 2019-04-07 report/chapter03.Rnw
Results update

@@
                echo=TRUE, message=FALSE,
-               fig.width=8.5, fig.height=3,
+               fig.width=8, fig.height=3.5,
                out.width='\\textwidth-3cm',
@@
 PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
 FILE = 'cochrane_2018-06-09.csv'
 PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH, 'code')
-PATH_RESULTS = file.path(PATH, 'results')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
 PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
@@
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+load(file.path(PATH_RESULTS, 'PubBias_results1.RData'))
+load(file.path(PATH_RESULTS, 'PubBias_results2.RData'))
 
@@
 <<echo=FALSE>>=
-data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-  mutate(n = n()) %>% filter(n > 9) %>% 
-  summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-                            method = "linreg")$p.val) %>% 
-  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-  theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+data %>% filter(total1 + total2 > 5 & total1 + total2 < 500) %>% 
+  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
+  group_by(sample.size) %>% 
+  summarize(mean.effect = mean(scaled.effect, na.rm = T)) %>% 
+  ggplot(aes(x = sample.size, y = mean.effect)) + geom_point() + theme_bw() + xlab("sample size") + ylab("mean absolute normalized effect size")
 @
-\caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
-\label{egger.cont}
+\caption{Mean of the absolute of the normalized effect size plotted against the total sample size.}
+\label{effect.samplesize}
+\end{figure}
+
+\vspace{0mm}
+There are tests that can be applied to find out if reporting bias is present in the meta analysis.
+For the precise description, see the methods section.
+Application of the tests is only recommended if there are ten or more studies that can be used, so all meta-analyses with less than ten studies have been excluded.
+
+\vspace{0mm}
+There are modifications to make tests more appropriate in case of binary outcomes, therefore, the results of the tests are separated in continuous outcome test results and dichotomoized outcome results.
+In Figure \ref{bias.results.bin} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for dichotomous outcomes.
+The same is shown in Figure \ref{bias.results.cont} for continuous outcome measures.
+
+% # <<results = 'asis', Echo = FALSE>>=
+% # rejection.bin <- data.bin.ext %>% summarize(egger.rejection = mean(egger.test),
+% #                                             schwarzer.rejection = mean(schwarzer.test),
+% #                                             rucker.rejection = mean(rucker.test),
+% #                                             harbord.rejection = mean(harbord.test),
+% #                                             peter.rejection = mean(peter.test))
+% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
+% # @
+
+\begin{figure}
+<<echo=FALSE>>=
+bin.spread <- data.bin.ext %>% select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% gather(key = test.type)
+bin.spread$value <- ifelse(bin.spread$value == 1, "rejected", "accepted")
+bin.spread$value <- factor(bin.spread$value)
+bin.spread %>% ggplot(aes(x = test.type, fill = value)) + geom_bar() + coord_flip() + theme_bw()
+@
+\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
+\label{bias.results.bin}
 \end{figure}
@@
 <<echo=FALSE>>=
-data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-  mutate(n = n()) %>% filter(n > 9) %>% 
-  summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-                            method = "mm")$p.val) %>% 
-  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-  theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+cont.spread <- data.cont.ext %>% select(egger.test, begg.test, thomson.test) %>% gather(key = test.type)
+cont.spread$value <- ifelse(cont.spread$value == 1, "rejected", "accepted")
+cont.spread$value <- factor(cont.spread$value)
+cont.spread %>% ggplot(aes(x = test.type, fill = value)) + geom_bar() + coord_flip() + theme_bw()
 @
-\caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
-\label{thomson.cont}
+\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
+\label{bias.results.cont}
+\end{figure}
+
+Furthermore, one can investigate how well the tests give the same results, i.e.
+classify the same study collections as having publication bias.
+This is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
+
+<<results = 'asis', echo = FALSE>>=
+data.bin.ext <- data.bin.ext %>% mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
+                                         egger.peter = ifelse(egger.test == peter.test, "agree", "disagree"),
+                                         egger.rucker = ifelse(egger.test == rucker.test, "agree", "disagree"),
+                                         egger.harbord = ifelse(egger.test == harbord.test, "agree", "disagree"),
+                                         schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
+                                         schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
+                                         schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
+                                         rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
+                                         rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
+                                         harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
+
+agreement.bin <- data.bin.ext %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
+                                        egger.peter = sum(egger.peter == "agree")/n(),
+                                        egger.rucker = sum(egger.rucker == "agree")/n(),
+                                        egger.harbord = sum(egger.harbord == "agree")/n(),
+                                        schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
+                                        schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
+                                        schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
+                                        rucker.peter = sum(rucker.peter == "agree")/n(),
+                                        harbord.peter = sum(harbord.peter == "agree")/n())
+
+correlation.bin <- data.bin.ext %>% summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
+                                            egger.peter = cor(pval.egger.bin, pval.peter.bin),
+                                            egger.rucker = cor(pval.egger.bin, pval.rucker.bin),
+                                            egger.harbord = cor(pval.egger.bin, pval.harbord.bin),
+                                            schwarzer.peter = cor(pval.schwarzer.bin, pval.peter.bin),
+                                            schwarzer.rucker = cor(pval.schwarzer.bin, pval.rucker.bin),
+                                            schwarzer.harbord = cor(pval.schwarzer.bin, pval.harbord.bin),
+                                            rucker.peter = cor(pval.rucker.bin, pval.peter.bin),
+                                            harbord.peter = cor(pval.harbord.bin, pval.peter.bin))
+
+binary.tests.agreement <- rbind(agreement.bin, correlation.bin)
+rownames(binary.tests.agreement) <- c("Test Agreement","P-value Correlation")
+
+print(xtable(x = t(binary.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)", label = "agreement.bin",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
+@
+
+<<results = 'asis', echo = FALSE>>=
+data.cont.ext <- data.cont.ext %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
+                                          thomson.begg = ifelse(thomson.test == begg.test, "agree", "disagree"),
+                                          egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"))
+
+agreement.cont <- data.cont.ext %>% summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
+                                              thomson.begg = sum(thomson.begg == "agree")/n(),
+                                              egger.begg = sum(egger.begg == "agree")/n())
+
+correlation.cont <- data.cont.ext %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
+                                                thomson.begg = cor(pval.thomson.cont, pval.begg.cont),
+                                                egger.begg = cor(pval.egger.cont, pval.begg.cont))
+
+cont.tests.agreement <- rbind(agreement.cont, correlation.cont)
+rownames(cont.tests.agreement) <- c("Test Agreement","P-value Correlation")
+
+print(xtable(x = t(cont.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)", label = "agreement.cont",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
+@
+
+\vspace{0mm}
+Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
+The p-values of two tests are shown with respect to the sample size of the studies in Figure \ref{pvalues.samplesize.bin} for peters test based on dichotomous outcomes and in Figure \ref{pvalues.samplesize.cont} for thomson and sharp's test based on continuous outcomes.
+%(Suggests that 10 is likely too small)
+
+\begin{figure}
+<<echo=FALSE>>=
+data.bin.ext %>% filter(n < 100)%>% ggplot(aes(y = pval.peter.bin, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
+@
+\caption{P-values of peters test for small study effects and their corresponding sample size (dichotomous outcomes)}
+\label{pvalues.samplesize.bin}
 \end{figure}
@@
 <<echo=FALSE>>=
-data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-  mutate(n = n()) %>% filter(n > 9) %>% 
-  summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-                            method = "rank")$p.val) %>% 
-  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-  theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+data.cont.ext %>% filter(n < 100) %>% ggplot(aes(y = pval.thomson.cont, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
 @
-\caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{begg.cont}
+\caption{P-values of thomson and sharp's test for small study effects and their corresponding sample size (continuous outcomes)}
+\label{pvalues.samplesize.cont}
 \end{figure}
 
-For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
-
-\begin{figure}
-<<echo=FALSE>>=
-data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-  filter(events1 > 0 | events2 > 0) %>% 
-  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-  mutate(n = n()) %>% filter(n > 9) %>% 
-  summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
-  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-  theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-@
-\caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{peters.bin}
-\end{figure}
-
-\begin{figure}
-<<echo=FALSE>>=
-data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-  filter(events1 > 0 | events2 > 0) %>% 
-  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-  mutate(n = n()) %>% filter(n > 9) %>% 
-  summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
-  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-  theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-@
-\caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
-\label{harbord.bin}
-\end{figure}
-
-Another less conventional way to look for publication bias is to see how many studies are ``reflected'' by the trim and fill method.
-As a first impression, a histogram with the fraction of trimmed of all comparisons is shown in figure \ref{trimfill.cont}.
-
-\begin{figure}
 <<echo=FALSE>>=
@@
 
+trimfill.bin <- data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% #filter(file.nr < 503) %>% 
+  filter(events1 > 0 | events2 > 0) %>% 
+  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
+  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+  mutate(n = n()) %>% filter(n > 9) %>% 
+  summarize(trim = trimfill(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2))$k0 / n())
+
+trimfill.bin.mean <- trimfill.bin %>% ungroup %>% summarise(mean = mean(trim)) %>% select(mean)
+trimfill.bin.median <- trimfill.bin %>% ungroup %>% summarise(median = median(trim)) %>% select(median)
+@
+
+\vspace{0mm}
+One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
+A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
+The mean fraction of trimmed comparisons for binary outcomes is \Sexpr{round(trimfill.bin.mean,2)} and the median \Sexpr{round(trimfill.bin.median,2)}.
+In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
+
+\begin{figure}
+<<echo=FALSE>>=
 trimfill.cont %>% ggplot(aes(x = trim)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
@@
 <<echo=FALSE>>=
-trimfill.bin <- data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% #filter(file.nr < 503) %>% 
-  filter(events1 > 0 | events2 > 0) %>% 
-  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-  mutate(n = n()) %>% filter(n > 9) %>% 
-  summarize(trim = trimfill(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2))$k0 / n())
-
-trimfill.bin.mean <- trimfill.bin %>% ungroup %>% summarise(mean = mean(trim)) %>% select(mean)
-trimfill.bin.median <- trimfill.bin %>% ungroup %>% summarise(median = median(trim)) %>% select(median)
-
 trimfill.bin %>% ggplot(aes(x = trim)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
@@
 
-The mean fraction of trimmed comparisons for binary outcomes is \Sexpr{round(trimfill.bin.mean,2)} and the median \Sexpr{round(trimfill.bin.median,2)}.
+\begin{figure}
+<<echo=FALSE>>=
+cdplot(x = data.bin.ext$trim.bin, y = as.factor(ifelse(data.bin.ext$peter.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
+@
+\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of peters test and dichotomous outcomes}
+\label{trimfill.pvalues.bin}
+\end{figure}
+
+\begin{figure}
+<<echo=FALSE>>=
+cdplot(x = data.cont.ext$trim.cont, y = as.factor(ifelse(data.cont.ext$thomson.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
+@
+\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of thomson and sharp's test and continuous outcomes}
+\label{trimfill.pvalues.cont}
+\end{figure}
+
+% 
+% For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
+The following three figures show the distribution of p-values of the corresponding tests.
+Note that only meta analyses with more than 10 comparisons have been included.
+% 
+% \vspace{0mm}
+% Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
+The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
+%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
+%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
+%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+%   mutate(n = n()) %>% filter(n > 9) %>% 
+%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
+%                             method = "linreg")$p.val) %>% 
+%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+%   theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% @
+% \caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
+% \label{egger.cont}
+% \end{figure}
+% 
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
+%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
+%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
+%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+%   mutate(n = n()) %>% filter(n > 9) %>% 
+%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
+%                             method = "mm")$p.val) %>% 
+%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+%   theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% @
+% \caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
+% \label{thomson.cont}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
+%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
+%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
+%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+%   mutate(n = n()) %>% filter(n > 9) %>% 
+%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
+%                             method = "rank")$p.val) %>% 
+%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+%   theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% @
+% \caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
+% \label{begg.cont}
+% \end{figure}
+% 
+% 
+% For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
+%   filter(events1 > 0 | events2 > 0) %>% 
+%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
+%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+%   mutate(n = n()) %>% filter(n > 9) %>% 
+%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
+%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+%   theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% @
+% \caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
+% \label{peters.bin}
+% \end{figure}
+% 
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
+%   filter(events1 > 0 | events2 > 0) %>% 
+%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
+%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+%   mutate(n = n()) %>% filter(n > 9) %>% 
+%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
+%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+%   theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% @
+% \caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
+% \label{harbord.bin}
+% \end{figure}

### 2019-04-07 code/PubBias.R

@@ -1,0 +1,413 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+data = pb.readData(path = PATH_DATA, file = FILE)
+tmp = pb.clean(data)
+data = tmp[[1]]
+aliases = tmp[[2]]
+
+require(biostatUZH)
+require(tidyverse)
+require(meta)
+require(xtable)
+library(car)
+
+####################################################################################################
+#Look for sample size effect on effect size
+####################################################################################################
+
+data %>% filter(total1 + total2 < 100 & total1 + total2 > 5) %>%
+  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
+  group_by(sample.size) %>% 
+  summarize(mean.scaled.effect = mean(scaled.effect, na.rm = T)) %>% 
+  ggplot(aes(x = sample.size, y = mean.scaled.effect)) + geom_point() + geom_smooth(method = "lm")
+
+data %>%  filter(total1 + total2 < 100 & total1 + total2 > 5) %>%
+  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
+  ggplot(aes(x = sample.size, y = scaled.effect)) + geom_point(alpha = 0.15, size = 0.5) + geom_smooth(method = "lm")
+
+data %>% filter(total1 + total2 > 5 & total1 + total2 < 300) %>% 
+  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
+  group_by(sample.size) %>% 
+  summarize(mean.effect = mean(scaled.effect, na.rm = T)) %>% 
+  ggplot(aes(x = sample.size, y = mean.effect)) + geom_point() + geom_smooth(method = "lm") + geom_smooth(method = "loess", color = "red")
+
[…]

### 2019-04-07 code/explore.R

@@ -5,9 +5,10 @@
 
 PATH_HOME = path.expand("~") # user home
 PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
 FILE = 'cochrane_2018-06-09.csv'
 PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH, 'code')
+PATH_CODE = file.path(PATH2, 'code')
 PATH_RESULTS = file.path(PATH, 'results')
 PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
 
@@ -313,88 +314,16 @@ print(arrange(filter(data, file.nr == 21) %>%
           select(comparison.name, study.name), study.name))
 
 
+#Check out metabin and metabias function with one meta-analysis.
+ds <- data %>% filter(file.nr == 11) %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>% 
+  filter(outcome.measure == "Odds Ratio" | outcome.measure == "Risk Ratio") %>% filter(events1 > 0 & events2 > 0) %>% 
+  mutate(counts = n()) %>% filter(counts == 18)
+print(ds %>% select(effect, events1, events2, study.name, outcome.name, counts), n = 200)
 
+meta.ds <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, data = ds, method = "Inverse")
+trimfill.ds <- trimfill(meta.ds)
+funnel(trimfill.ds)
 
-#Meta-analysis dataset creation: Pubias test p-values, Q-heterogeneity statistic, trimfill number of mirrored studies
-data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>%# filter(file.nr < 503) %>% 
-  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-  mutate(n = n()) %>% filter(n > 9) %>% 
-  summarize(doi = unique(doi),
-    pval.egger.cont = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-                            method = "linreg")$p.val,
[…]

### 2019-04-15 report/MSc_Report.tex
Update

@@
 \usepackage{tikz}
+\usepackage{amssymb}
 \usetikzlibrary{trees}
@@
 The necessity of meta-analyses is also increased by the abundance of data and publications.
-Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to keep decisions based on quantitative and scientific criteria.
+Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to make decisions based on quantitative and scientific criteria.
 
@@
 For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention.
-However, since the amount of empirical research is expanding, meta-analysis can be part in any field where repeated experiments are performed.
-The usefulness of meta-analysis expands therefore well over clinical science.
+However, the usefulness of meta-analysis does not restrict to clinical science, but to any empirical and quantiative science.
 
@@
 Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question.
-Systematic reviews may also incorporate results that can not be included in a meta-analysis, such as adverse effects reported in one trial, but a meta-analysis is the central part of a systematic review if results from multiple studies are available.
-The authors usually take their conclusions largely based on the results of the meta-analysis.
-
-% In science, there is not only a need for accumulation of knowledge, but also for concentration.
-For the same reason as statistical analysis is performed on single experiments, it can also be used for results of multiple experiments or studies: to simplify and summarize the data at hand to a degree that is understandable.
-The latter procedure goes usually under the name of meta-analysis.
-Meta analyses are used to summarize results and evidence over multiple studies when they are considered to be similar enough.
-% 
-% \vspace{0mm}
-% In the face of the large amount of research that is done in some fields of empirical science, meta-analysis becomes increasingly important, for looking at all evidence would simply take very long for one person.
-Meta-analyses are often part of a systematic review, an effort of experts of a field to provide an overlook over the evidence.
-In the course of a review, all literature and data with respect to a scientific question is collected and a meta-analysis is operated at the end to summarize the findings.
-% 
-% \vspace{0mm}
-% In the case of clinical science, systematic reviews and meta-analyses do not only benefit scientists but also patients and clinicians, for both are provided with up-to-date summaries of current evidence with respect to a certain treatment.
-Therefore, meta-analysis is at the core of what is called evidence-based medicine.
-%
-
-\vspace{0mm}
-However, there are problems that potentially limit the validity of meta-analysis; studies at hand can be biased or heterogeneity between study results can be large and the number of studies small.
-The importance and the issues of meta-analysis are the reasons why they have been chosen as one general topic of the masters thesis.
-One particular problem will furthermore be investigated in more detail: reporting bias and meta-analysis.
-Not only will the methods to deal with issues as reporting bias be discussed, but also will they be applied on a dataset of systematic reviews that can be used for meta-analysis.
-So at the end of the report, the reader will not only have an impression of the technical issues caused by reporting bias, but also of the abundance and extent of it in the dataset.
-Since the dataset is very large and of good quality, results might also be representative to some extent for reporting bias in clinical science.
+Meta-analysis can be applied to all studies that are approximately identical in their experimental setup and the way the outcome of the experiments is measured.
+In systematic reviews where meta-analyses are used, the conclusions are most often strongly based on the results and the interpretation of the meta-analysis.
+
+\vspace{0mm}
+However, there are problems that potentially limit the validity of meta-analysis; the number of studies available can be incomplete or the results of the studies can be biased.
+Some of those problems can be solved or asserted by special statistical methods.
+
+\subsection{Small Study Effects or Publication Bias}
+When study sample size decreases, the probability of extreme and missleading results in a study increases.
+This becomes a problem if results are selectively published, and therefore available, based on their results.
+When this is the case, one speaks of a small study effect or of ``Publication bias''.
+
+\vspace{0mm}
+The issue has been discussed extensively in the last years, most often in the context of what has came to be known as the replication crisis.
+The reasons for small study effects are manifold, but originate most often in the myopical acting of agents in science and the lack of statistical education.
+Studies are reported by scientists, published by journals and noticed by readers more often if their findigs are positive and find e.g.
+a substantive difference or effect.
+When doing a meta-analysis, one again obtains biased results.
+
+\vspace{0mm}
+The reason why that is less of an issue for larger studies is that extreme results are in general less likely and that due to larger effort, a result is published although there has been no clear and positive findings.
+
+\vspace{0mm}
+While there is generally no way to assert poor study quality, small study effect can in principle be asserted and corrected for statistically.
+This masters thesis will mainly be about statistical methods to detect and adjust for small study effects.
+It can furthermore be divided in two parts:
+\begin{itemize}
+\item Methodological part: Collection and discussion of statistical tests and correction methods for small study effects.
+\item Applied part: Application of the methods to studies of the Cochrane Library of systematic Reviews. Subsequent discussion of the implications
+of the results for clinical science.
+\end{itemize}
+
+In contrast to simulation studies, it is not possible to assess critical properties of the methods such as the power of a test, since the truth is not known.
+But based on the amount of data, one can of course try to make extrapolation to tendencies in clinical science in general.
+Moreover, it is still interesting to see how the methods behave in general, especially with respect to each other.
+It may, as an example, be possible to answer the question which statistical test is most conservative and which pooling method is most optimistic on average.
+Comparison with results from simulations may allow to speculate about the reasons when simulation and real world results diverge.
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Apr  7 21:19:44 2019
+% Sat Apr 13 14:58:52 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Apr  7 21:19:45 2019
+% Sat Apr 13 14:58:52 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Apr  7 21:19:45 2019
+% Sat Apr 13 14:58:53 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Apr  7 21:19:51 2019
+% Sat Apr 13 14:58:58 2019
 \begin{table}[ht]
@@
 
+\section{Small Study Effects}
 One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
@@
 \vspace{0mm}
-To provide an overview over the issue, first it is shown how mean effect size decreases with increasing sample size of the comparisons in Figure \ref{effect.samplesize}.
+To provide an overview over the issue, first it is shown how mean absolute effect size decreases with increasing sample size of the comparisons in Figure \ref{effect.samplesize}.
+The decrease is particularly substantive from very small trials ($n$ = 5) to medium sample size ($n$ = 100), afterwards the trend is less pronounced.
+With increasing sample size, there are fewer results, therefore, the variation between means increases.
 All effects are normalized by subtracting the mean effect size of the dataset and dividng through the standard deviation.
-Then, the mean of the absolute value for a given sample size is plotted against its sample size.
 Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all sample sizes.
@@
 
-\vspace{0mm}
+\subsection{Small Study Effect Tests}
+
 There are tests that can be applied to find out if reporting bias is present in the meta analysis.
 For the precise description, see the methods section.
-Application of the tests is only recommended if there are ten or more studies that can be used, so all meta-analyses with less than ten studies have been excluded.
-
-\vspace{0mm}
-There are modifications to make tests more appropriate in case of binary outcomes, therefore, the results of the tests are separated in continuous outcome test results and dichotomoized outcome results.
-In Figure \ref{bias.results.bin} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for dichotomous outcomes.
-The same is shown in Figure \ref{bias.results.cont} for continuous outcome measures.
+Application of the tests is only recommended if there are ten or more studies \citep{cochrane.handbook} that can be used, so all meta-analyses with less than ten studies have been excluded.
+
+\vspace{0mm}
+There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
+In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes.
+From 2312 meta-analyses with continouos outcomes, most meta-analyses with rejected null hypotheses have been found by the Thompson and Sharp test (0.319), followed closely by Eggers test (0.309) and Begg and Mazumdar's test (0.131).
+The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 5717).
+The test that rejects most null hypotheses is here Egger's test (0.186), followed by R\"ucker's test (0.163), Harbord's test (0.144), Peters test (0.142) and Schwarzer's test (0.088).
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
+
+}
+
+\end{knitrout}
+\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
+\label{bias.results.cont}
+\end{figure}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
+
+}
+
+\end{knitrout}
+\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
+\label{bias.results.bin}
+\end{figure}
+
+The agreement of the tests, i.e.
+the proportion of meta-analyses where the rest results are equal between tests, is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
+Agreement in tests for binary outcomes is better than continuous outcomes, with some variation between tests (binary outcomes: 83 to 91\%).
+Correlation varies more between tests, both for continuous and binary outcome tests.
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sat Apr 13 14:59:07 2019
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lll}
+  \hline
+ & Test Agreement & P-value Correlation \\ 
+  \hline
+egger.schwarzer & 0.83 & 0.38 \\ 
+  egger.peter & 0.84 & 0.44 \\ 
+  egger.rucker & 0.83 & 0.39 \\ 
+  egger.harbord & 0.91 & 0.75 \\ 
+  schwarzer.peter & 0.85 & 0.24 \\ 
+  schwarzer.rucker & 0.83 & 0.30 \\ 
+  schwarzer.harbord & 0.88 & 0.52 \\ 
+  rucker.peter & 0.89 & 0.66 \\ 
+  harbord.peter & 0.86 & 0.45 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)} 
+\label{agreement.bin}
+\end{table}
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sat Apr 13 14:59:07 2019
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lll}
+  \hline
+ & Test Agreement & P-value Correlation \\ 
+  \hline
+thomson.egger & 0.85 & 0.67 \\ 
+  thomson.begg & 0.75 & 0.45 \\ 
+  egger.begg & 0.75 & 0.38 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)} 
+\label{agreement.cont}
+\end{table}
+
+\vspace{0mm}
+Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
+The p-values of two tests are shown with respect to the sample size of the studies in Figure \ref{pvalues.samplesize.bin} for peters test based on dichotomous outcomes and in Figure \ref{pvalues.samplesize.cont} for thomson and sharp's test based on continuous outcomes.
+%(Suggests that 10 is likely too small)
+A trend towards more significant p-values is visible for larger sample sizes.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
+
+}
+
+\end{knitrout}
+\caption{P-values of peters test for small study effects and their corresponding sample size (dichotomous outcomes)}
+\label{pvalues.samplesize.bin}
+\end{figure}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-24-1}
+
+}
+
+\end{knitrout}
+\caption{P-values of thomson and sharp's test for small study effects and their corresponding sample size (continuous outcomes)}
+\label{pvalues.samplesize.cont}
+\end{figure}
+
+\vspace{0mm}
+One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
+The mean fraction of trimmed comparisons for binary outcomes is 0.17 and the median 0.15.
+A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
+In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses.
+In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
+In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-25-1}
+
+}
+
+\end{knitrout}
+\caption{Histogram of fractions of trimmed comparisons from meta analyses with continuous outcomes.}
+\label{trimfill.cont}
+\end{figure}
+
+The mean fraction of trimmed comparisons for continuous outcomes is 0.22 and the median 0.2.
+
+The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-26-1}
+
+}
+
+\end{knitrout}
+\caption{Histogram of fractions of trimmed comparisons from meta analyses with binary outcomes.}
+\label{trimfill.bin}
+\end{figure}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}
+
+}
+
+\end{knitrout}
+\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
+\label{trimfill.pvalues.bin}
+\end{figure}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}
+
+}
+
+\end{knitrout}
+\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
+\label{trimfill.pvalues.cont}
+\end{figure}
+
+\subsection{Small Study Effect Correction}
+
+Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
 
@@
 % # @
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-\label{bias.results.bin}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-\label{bias.results.cont}
-\end{figure}
-
-Furthermore, one can investigate how well the tests give the same results, i.e.
-classify the same study collections as having publication bias.
-This is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
-
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Apr  7 21:20:02 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
- & Test Agreement & P-value Correlation \\ 
-  \hline
-egger.schwarzer & 0.84 & 0.38 \\ 
-  egger.peter & 0.84 & 0.44 \\ 
-  egger.rucker & 0.83 & 0.39 \\ 
-  egger.harbord & 0.91 & 0.75 \\ 
-  schwarzer.peter & 0.85 & 0.24 \\ 
-  schwarzer.rucker & 0.83 & 0.30 \\ 
-  schwarzer.harbord & 0.88 & 0.52 \\ 
-  rucker.peter & 0.89 & 0.67 \\ 
-  harbord.peter & 0.86 & 0.45 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)} 
-\label{agreement.bin}
-\end{table}
-
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Apr  7 21:20:02 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
- & Test Agreement & P-value Correlation \\ 
-  \hline
-thomson.egger & 0.85 & 0.67 \\ 
-  thomson.begg & 0.75 & 0.45 \\ 
-  egger.begg & 0.75 & 0.38 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)} 
-\label{agreement.cont}
-\end{table}
-
-\vspace{0mm}
-Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
-The p-values of two tests are shown with respect to the sample size of the studies in Figure \ref{pvalues.samplesize.bin} for peters test based on dichotomous outcomes and in Figure \ref{pvalues.samplesize.cont} for thomson and sharp's test based on continuous outcomes.
-%(Suggests that 10 is likely too small)
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
-
-}
-
-\end{knitrout}
-\caption{P-values of peters test for small study effects and their corresponding sample size (dichotomous outcomes)}
-\label{pvalues.samplesize.bin}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
-
-}
-
-\end{knitrout}
-\caption{P-values of thomson and sharp's test for small study effects and their corresponding sample size (continuous outcomes)}
-\label{pvalues.samplesize.cont}
-\end{figure}
-
-\vspace{0mm}
-One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
-A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
-The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.17.
-In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-25-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of fractions of trimmed comparisons from meta analyses with continuous outcomes.}
-\label{trimfill.cont}
-\end{figure}
-
-The mean fraction of trimmed comparisons for continuous outcomes is 0.22 and the median 0.2.
-
-The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-26-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of fractions of trimmed comparisons from meta analyses with binary outcomes.}
-\label{trimfill.bin}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}
-
-}
-
-\end{knitrout}
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of peters test and dichotomous outcomes}
-\label{trimfill.pvalues.bin}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}
-
-}
-
-\end{knitrout}
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of thomson and sharp's test and continuous outcomes}
-\label{trimfill.pvalues.cont}
-\end{figure}
 
@@
 
-\chapter{Discussion and Outlook}
+\chapter{Methods}
+
+\section{Basic notation}
+The notation used here will be used throughout the chapter and exceptions will be noted.
+Let $i$ be the number of a study of a meta analysis with $n$ being the total number of studies.
+$y_{i}$ is then the effect size estimate (usually log odds ratio or mean difference) and $v_{i}$ the variance of the estimate of study $i$.
+$w_{i}$ is used for weights which are defined when necessary, and $\Delta$ usually denotes the summarized or pooled effect estimate of the meta-analysis, and $\eta$ the variance thereof.
+
+\vspace{0mm}
+In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
+
+\section{Heterogeneity}
+In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
+This is called between study variation in contrast to within study variation (noise).
+
+\vspace{0mm}
+The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
+Let $w_i$ be the inverse of the variance and $\Delta$ be a summarized effect estimate of your choice as for example a variance-weighted mean \ref{weighted.mean}.
+Then $Q$ can be calculated as in \ref{Q.heterogeneity}
+
+\begin{align}
+\Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
+Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
+\end{align}
+
+Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
+Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
+$1 - F(Q)$ will provide the $p$-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
+
+\vspace{0mm}
+Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
+For this purpose, $\tau^2$, the variance of true effects, can be calculated.
+$\tau^2$ is on the same scale as the effect size and reflects the absolute amount of dispersion.
+In practice, $\tau^2$ can be smaller than zero, then it is set to zero.
+
+\begin{align}
+C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
+\tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
+\end{align}
+
+The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
+Note that their estimate can differ substantially and consequently also the estimate of the pooled effect size estimate.
+
+\vspace{0mm}
+To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
+
+\begin{align}
+I^2 &= (Q - n + 1)/Q \label{I2.proportion}
+\end{align}
+
+There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
 
@@
 First the fixed effect meta-analysis will be explained.
-For convenience, notatotion will be identical whenever possible for both methods.
 Note that both methods can be used for continuous or dichotomous outcomes.
@@
 \vspace{0mm}
-Let $y_{i}$ be the effect size estimate of the study $i$ and $v_{i}$ be the corresponding variance of the effect size estimate.
-Effect measures have to be identical for all studies.
-Furthermore, let $w_i$ be the inverse of the variance of the estimate from study $i$, $1/v_{i}$ and $n$ the total number of studies.
-
-\vspace{0mm}
-The pooled estimate $\Delta_{f}$ of the fixed effects model is then simply the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
-The variance $\nu_{f}$ is the reciprocal of the sum of the weights as in \ref{reciproce.variance}.
+Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
+The pooled estimate $\Delta_{f}$ of the fixed effects model is then the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
+The variance $\eta_{f}$ is the reciprocal of the sum of the weights as shown in \ref{reciproce.variance}.
 
@@
 \Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-\nu_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
+\eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
 \end{align}
@@
 The computation of random effects meta-analysis is more complicated.
-Random effects meta-analysis will give smaller studies with larger variance of their estimates more weight in the pooled estimate.
-The key principle is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
-Thus a within - and between study variance has to be computed.
-Let $Q$ be the heterogeneity of study estimates as given in \ref{Q.heterogeneity}.
-The degrees of freedom $d$ are equal to $n-1$.
-$C$ is defined in \ref{C.definition}.
-The between study variance $\tau^2$ is then defined as in \ref{Tao.definition}.
-The definition follows \citet{tau.estimator}, but other methods are available such as maximum likelihood or restricted maximum likelihood estimators.
-
-\begin{align}
-Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta_{f})^2 \label{Q.heterogeneity} \\
-C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
-\tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
-\end{align}
-
-The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is then defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
-It is used to calculate a new kind of weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
-The variance of $\Delta_{r}$, $\nu_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
+Random effects meta-analysis will give smaller studies with larger variance more weight in the pooled estimate.
+Shortly, the idea is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
+
+\vspace{0mm}
+The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
+It is used to calculate a new weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
+The variance of $\Delta_{r}$, $\eta_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
 
@@
 \Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
-\nu_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
-\end{align}
-
-A p-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Z.value}) and the usual computation as in (\ref{p.value.calculation}), $\Phi$ being the cumulative distribution function of a standard normal distribution.
-
-\begin{align}
-Z &= \frac{\Delta}{\sqrt{\nu}} \label{Z-value} \\
+\eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
+\end{align}
+
+A p-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
+
+\begin{align}
+Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
 p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
@@
 
-\section{Reporting Bias Test}
-Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. Five of them will be presented.
-First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
-
-\vspace{0mm}
-Again, let $y_{i}$ be the effect size estimate and $v_{i}$ the variance estimate of study $i$.
-Then, the standardized effect size $y_{i}^\star$ is given in \ref{begg.stand.eff}.
+\section{Small Study Effects Tests}
+\subsection{Continuous Outcome Tests}
+% Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. 
+% First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
+
+\subsubsection{Begg and Mazumdar: Rank Correlation Test}
+\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+A standardized effect size $y_{i}^\star$ can be computed as in \ref{begg.stand.eff}.
+$v_{i}^\star$ is the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
 $\Delta_{f}$ is the pooled estimate for fixed effect estimate defined in \ref{weighted.mean}.
-Let $v_{i}^\star$ be the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
-
-\begin{align}
-v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} \\
-y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff}
-\end{align}
-
-Then, a rank correlation test based on Kendall's tau is used.
-The pairs of $y_{i}^\star$ and $v_{i}^\star$ that are ranked in the same order are enumerated.
+
+\begin{align}
+y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff} \\
+v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} 
+\end{align}
+
+A rank correlation test based on Kendall's tau is then used.
+The pairs $(y_{i}^\star, v_{i}^\star)$ that are ranked in the same order are enumerated.
 Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (e.g.
@@
 Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
-$n$ is the number of studies.
 
@@
 
-\vspace{0mm}
-Alternatively, one can use Eggers test \citep{Egger} that is based on simple linear regression.
-Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$, $x_{i} = 1/\sqrt{v_{i}}$.
-Furthermore, let $\hat{y_{i}} = \beta_{0} + \beta_{1}x_{i}$.
-Using linear regression, one obtains a least-squares estimate for $\beta_{0}$, and the null hypothesis $\beta_{0} = 0$ can be tested using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the t-distribution.
-The p-value for $\beta_{0} = 0$ (no reporting bias) is given in \ref{egger.pvalue}.
+\subsubsection{Egger's Test: Linear Regression Test}
+Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
+Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope.
+
+\vspace{0mm}
+If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
+The p-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
 
@@
 
+\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test}
 A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
@@
 The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
-Then, a weighted regression is carried out with weigths $1/v_{i}^\star$ as given in \ref{ranef.study.variance}.
-Analagous to Eggers test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta{0} = 0$.
 
@@
 
-A rank based alternative to Peters test for binary outcomes is the Harbords test \citep{Harbord}.
-Let $e_{t}$ be the number of events in a two-armed study $i$ and $n_{t}$ be the total number of patients in the treatment arm and the same for $n_{c}$ and $e_{c}$ for the control arm.
-Then the score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
+Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
+Analogous to Edger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta{0} = 0$.
+
+\subsection{Dichotomous Outcomes Tests}
+
+The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
+Consequently, the tests above will tend to reject the null-hypothesis too often, i.e.
+that they are not conservative enough.
+A number of solutions to this problem are existing in the literature.
+
+\subsubsection{Peters Test: Weighted Linear Regression Test}
+A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
+
+\vspace{0mm}
+Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
+
+\begin{align}
+y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
+v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
+\end{align}
+
+and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
+Instead of taking the variance as explanatory or independent variable in regression as in Egger's Test, the inverse of the total sample size $x_{i}$ is used, and the variance $v_{i}$ is used as a weight.
+The subsequent test procedure is then identical to Egger's test.
+
+\vspace{0mm}
+Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
+
+\subsubsection{Harbord's Test: Score based Test}
+A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
+The score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
 
@@
 
-Similarly to Eggers or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ depending on the standard error $1/\sqrt{v_{i}}$ with the $1/v_{i}$ used as weigths.
-$r_{i}/v_{i}$ is also known as peto odds ratio.
-
-\section{Reporting Bias Adjustment}
+Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
+Note that $r_{i}/v_{i}$ is also known as peto odds ratio.
+
+\subsubsection{Schwarzer's Test: Rank Correlation Test}
+\citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
+$\mathbb{E}(E_{t})$ and variance of $E_{t}$ are then estimated based on $e_{t}$.
+
+\vspace{0mm}
+The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
+
+\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
+The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let
+
+\begin{align}
+y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}}// 
+v_{i} = 1/4n_{t} + +/4n_{c}
+\end{align}
+
+Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances.
+
+\section{Small Study Effect Adjustment}
+\subsection{Trim and Fill}
 One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
-It is based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
-If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies.
-Trim and Fill is a nonparametric approach.
-
-\vspace{0mm}
-The algorithm for the method tries to estimate the number of studies that are not available due to reporting bias, $k$.
-There are different estimators for $k$.
+It is a nonparametric test based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
+%If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
+
+\vspace{0mm}
+The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
 First, $\Delta$ is estimated using a fixed or random effects model.
@@
 
+\subsection{Copas Selection Model}
+
+A method proposed in \cite{Copas1,Copas2,Copas3} assumes that there is a population of studies of which only a part has been published dependent on the variance and size of their estimated effects.
+Studies with small variance and large effect sizes are more likely to be published than studies with large variance and small effect sizes.
+Note that small effect size means here a treatment effect close to the control effect.
+
+Let $y_i$ be the effect size estimate of study $i$. Then
+
+\begin{align}
+y_{i} \sim N(\mu_{i}, \sigma_{i}^2) \\
+\mu_{i} \sim N(\mu, \tau^2)
+\end{align}
+
+corresponding to a standard random effects model.
+$\mu$ is the overall mean effect, $\sigma_{i}^2$ the within study variance and $\tau^2$ the between study variance.
+This is the \textit{population model}.
+
+\vspace{0mm}
+The \textit{selection model} is defined as follows. Suppose a selection of studies with reported standard errors $s$ (likely different from $\sigma$). Only a proportion
+
+\begin{align}
+P(\textrm{select}|s) &= \Phi(a + b/s) \label{copas.selection1}
+\end{align}
+
+of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
+\ref{copas.selection1} can be rewritten as
+
+\begin{align}
+z = a + b/s + \delta \label{copas.selection2}
+\end{align}
+
+with $\delta \sim N(0,1)$. The study with standard error $s$ is only selected if $z$ is positive. Therefore, the larger $z$, the more likely the study is selected.
+Combining population and selection model for study $i$, we have
+
+\begin{align}
+y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \\
+\mu_{i} \sim N(\mu, \tau^2) \\
+z_{i} = a + b/s_{i} + \delta_{i}
+\end{align}
+
+where $(\epsilon_{i}, \delta_{i})$ are standard normal residuals and jointly normal with correlation $\rho = cor(y_{i}, z_{i})$.
+Every given study $i$ in the meta-analysis has $z_{i} > 0$.
+If $\rho$ is large and positive and $z_{i} > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_{i}$ and $\delta_{i}$.
+Thus, the true mean $\mu$ is likely to be overestimated.
+
+\vspace{0mm}
+Let $u = a + b/s$, $\lambda(u) = \phi(u)/\Phi(u)$ ($\phi$ is the standard normal density function) and $\tilde{\rho} = \sigma/\sqrt(\tau^2 + \sigma^2) \rho$.
+The probability of a study being selected is
+
+\begin{align}
+P(\textrm{select}|s, y) = P(a,b,s,y) = \Phi(\frac{u + \tilde{\rho}((y - \mu)/\sqrt(\tau^2 + \sigma^2))}{\sqrt{1 - \tilde{\rho^2}}})
+\end{align}
+
+It can also be shown that the expected value
+
+\begin{align}
+\mathbb{E}(y|s, select) = \mu + \rho\sigma\lambda(u) \label{copas.expectation}
+\end{align}
+
+which shows that the expected value for a study is larger for larger $\sigma$.
+
+\vspace{0mm}
+One can compute a likelihood function based on the distribution of $y$ conditional on $z > 0$.
+The likelihood can be maximized for any given pair $a,b$ (can not be estimated since the number of missing studies is not known), and a maximum likelihood estimate $\hat{\mu}$ for the true mean $\mu$ can be obtained.
+One can then perform a sensitivity analysis.
+First, one looks how $\hat{\mu}$ changes for different values of $a,b$.
+One can then compare the fitted values in \ref{copas.expectation} with the real values.
+To test the fit of the model (while keeping all other parts unchanged), the model can be extended in the following way :
+
+\begin{align}
+y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
+\end{align}
+
+If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
+Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
+The p-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
+
+\vspace{0mm}
+To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
+
+\vspace{0mm}
+In practice, only a range of values for $a,b$ are reasonable.
+For those values, the quantities above can be calculated and illustrated.
+Values for $\mu$ that have p-values over a predefined significance threshold can be used for inference of the effect size.
+
+\subsection{Adjustment by Regression}
+There are multiple ways to adjust for small study effects by regression. The general idea is to regress the effect size of a study with a variance of zero based on the given effects and variances.
+
+\citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
+Similarly to what has been seen in Copas selection model, we let $y_{i}$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_{i}}$ as in \ref{limitmeta.regression}.
+
+\begin{align}
+y_{i}& = \beta_{0} + \beta{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \stackrel{\textrm{iid}}{\sim} N(0,1)  \ref{limitmeta.regression}
+\end{align}
+
+$\beta{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
+
+\begin{align}
+\mathbb{E}((y_{i} - \beta_{})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{if} \sqrt{v_{i}} \rightarrow \infty \\
+\mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
+\end{align}
+
+After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test.
+
+\vspace{0mm}
+To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
+
+\begin{align}
+y_{i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{s_{i}/M + \tau^2}) \label{limitmeta.regression}
+\end{align}
+
+Letting $M \rightarrow \infty$, we obtain:
+
+\begin{align}
+y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
+\end{align}
+
+Note that:
+
+\begin{align}
+y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
+\end{align}
+
+$\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
+
+\begin{align}
+\epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
+\end{align}
+
+Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get
+
+\begin{align}
+y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
+\end{align}
+
+By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
+
 % \begin{align} \label{cox reg}

### 2019-04-15 report/chapter01.Rnw
Update

--- 2019-03-21 report/chapter01.Rnw
@@
 
-In science, there is not only a need for accumulation of knowledge, but also for concentration.
-For the same reason as statistical analysis is performed on single experiments, it can also be used for results of multiple experiments or studies: to simplify and summarize the data at hand to a degree that is understandable.
-The latter procedure goes usually under the name of meta-analysis.
-Meta analyses are used to summarize results and evidence over multiple studies when they are considered to be similar enough.
+Meta-analysis is at the core of evidence based medicine because it allows to summarise evidence over multiple studies and provide a more broad view on success and effectivity of clinical treatments.
+The necessity of meta-analyses is also increased by the abundance of data and publications.
+Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to make decisions based on quantitative and scientific criteria.
 
 \vspace{0mm}
-In the face of the large amount of research that is done in some fields of empirical science, meta-analysis becomes increasingly important, for looking at all evidence would simply take very long for one person.
-Meta-analyses are often part of a systematic review, an effort of experts of a field to provide an overlook over the evidence.
-In the course of a review, all literature and data with respect to a scientific question is collected and a meta-analysis is operated at the end to summarize the findings.
+For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention.
+However, the usefulness of meta-analysis does not restrict to clinical science, but to any empirical and quantiative science.
 
 \vspace{0mm}
-In the case of clinical science, systematic reviews and meta-analyses do not only benefit scientists but also patients and clinicians, for both are provided with up-to-date summaries of current evidence with respect to a certain treatment.
-Therefore, meta-analysis is at the core of what is called evidence-based medicine.
+Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question.
+Meta-analysis can be applied to all studies that are approximately identical in their experimental setup and the way the outcome of the experiments is measured.
+In systematic reviews where meta-analyses are used, the conclusions are most often strongly based on the results and the interpretation of the meta-analysis.
 
 \vspace{0mm}
-However, there are problems that potentially limit the validity of meta-analysis; studies at hand can be biased or heterogeneity between study results can be large and the number of studies small.
-The importance and the issues of meta-analysis are the reasons why they have been chosen as one general topic of the masters thesis.
-One particular problem will furthermore be investigated in more detail: reporting bias and meta-analysis.
-Not only will the methods to deal with issues as reporting bias be discussed, but also will they be applied on a dataset of systematic reviews that can be used for meta-analysis.
-So at the end of the report, the reader will not only have an impression of the technical issues caused by reporting bias, but also of the abundance and extent of it in the dataset.
-Since the dataset is very large and of good quality, results might also be representative to some extent for reporting bias in clinical science.
+However, there are problems that potentially limit the validity of meta-analysis; the number of studies available can be incomplete or the results of the studies can be biased.
+Some of those problems can be solved or asserted by special statistical methods.
+
+\subsection{Small Study Effects or Publication Bias}
+When study sample size decreases, the probability of extreme and missleading results in a study increases.
+This becomes a problem if results are selectively published, and therefore available, based on their results.
+When this is the case, one speaks of a small study effect or of ``Publication bias''.
+
+\vspace{0mm}
+The issue has been discussed extensively in the last years, most often in the context of what has came to be known as the replication crisis.
+The reasons for small study effects are manifold, but originate most often in the myopical acting of agents in science and the lack of statistical education.
+Studies are reported by scientists, published by journals and noticed by readers more often if their findigs are positive and find e.g.
+a substantive difference or effect.
+When doing a meta-analysis, one again obtains biased results.
+
+\vspace{0mm}
+The reason why that is less of an issue for larger studies is that extreme results are in general less likely and that due to larger effort, a result is published although there has been no clear and positive findings.
+
+\vspace{0mm}
+While there is generally no way to assert poor study quality, small study effect can in principle be asserted and corrected for statistically.
+This masters thesis will mainly be about statistical methods to detect and adjust for small study effects.
+It can furthermore be divided in two parts:
+\begin{itemize}
+\item Methodological part: Collection and discussion of statistical tests and correction methods for small study effects.
+\item Applied part: Application of the methods to studies of the Cochrane Library of systematic Reviews. Subsequent discussion of the implications
+of the results for clinical science.
+\end{itemize}
+
+In contrast to simulation studies, it is not possible to assess critical properties of the methods such as the power of a test, since the truth is not known.
+But based on the amount of data, one can of course try to make extrapolation to tendencies in clinical science in general.
+Moreover, it is still interesting to see how the methods behave in general, especially with respect to each other.
+It may, as an example, be possible to answer the question which statistical test is most conservative and which pooling method is most optimistic on average.
+Comparison with results from simulations may allow to speculate about the reasons when simulation and real world results diverge.
 

### 2019-04-15 report/chapter03.Rnw
Update

@@
 load(file.path(PATH_RESULTS, 'PubBias_results2.RData'))
+load(file.path(PATH_RESULTS, 'PubBias_results3.RData'))
+load(file.path(PATH_RESULTS, 'PubBias_results4.RData'))
 
@@
 
-\vspace{0mm}
-There are tests that can be applied to find out if reporting bias is present in the meta analysis.
-For the precise description, see the methods section.
-Application of the tests is only recommended if there are ten or more studies that can be used, so all meta-analyses with less than ten studies have been excluded.
+\subsection{Small Study Effect Tests}
 
-\vspace{0mm}
-There are modifications to make tests more appropriate in case of binary outcomes, therefore, the results of the tests are separated in continuous outcome test results and dichotomoized outcome results.
-In Figure \ref{bias.results.bin} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for dichotomous outcomes.
-The same is shown in Figure \ref{bias.results.cont} for continuous outcome measures.
+<<echo=FALSE, warning=FALSE>>=
+n.bin <- dim(meta.bin)[1]
+rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
+                                            schwarzer.rejection = mean(schwarzer.test),
+                                            rucker.rejection = mean(rucker.test),
+                                            harbord.rejection = mean(harbord.test),
+                                            peter.rejection = mean(peter.test))
 
-% # <<results = 'asis', Echo = FALSE>>=
-% # rejection.bin <- data.bin.ext %>% summarize(egger.rejection = mean(egger.test),
-% #                                             schwarzer.rejection = mean(schwarzer.test),
-% #                                             rucker.rejection = mean(rucker.test),
-% #                                             harbord.rejection = mean(harbord.test),
-% #                                             peter.rejection = mean(peter.test))
-% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
-% # @
+bin.spread <- meta.bin %>% select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% gather(key = test.type, value = "null.hypothesis")
+bin.spread$null.hypothesis <- ifelse(bin.spread$null.hypothesis == 1, "rejected", "not rejected")
+bin.spread$null.hypothesis <- factor(bin.spread$null.hypothesis)
 
-\begin{figure}
-<<echo=FALSE>>=
-bin.spread <- data.bin.ext %>% select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% gather(key = test.type)
-bin.spread$value <- ifelse(bin.spread$value == 1, "rejected", "accepted")
-bin.spread$value <- factor(bin.spread$value)
-bin.spread %>% ggplot(aes(x = test.type, fill = value)) + geom_bar() + coord_flip() + theme_bw()
-@
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-\label{bias.results.bin}
-\end{figure}
-
-\begin{figure}
-<<echo=FALSE>>=
-cont.spread <- data.cont.ext %>% select(egger.test, begg.test, thomson.test) %>% gather(key = test.type)
-cont.spread$value <- ifelse(cont.spread$value == 1, "rejected", "accepted")
-cont.spread$value <- factor(cont.spread$value)
-cont.spread %>% ggplot(aes(x = test.type, fill = value)) + geom_bar() + coord_flip() + theme_bw()
-@
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-\label{bias.results.cont}
-\end{figure}
-
-Furthermore, one can investigate how well the tests give the same results, i.e.
-classify the same study collections as having publication bias.
-This is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
-
-<<results = 'asis', echo = FALSE>>=
-data.bin.ext <- data.bin.ext %>% mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
+meta.bin <- meta.bin %>% mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
                                          egger.peter = ifelse(egger.test == peter.test, "agree", "disagree"),
@@
 
-agreement.bin <- data.bin.ext %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
+agreement.bin <- meta.bin %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
                                         egger.peter = sum(egger.peter == "agree")/n(),
@@
 
-correlation.bin <- data.bin.ext %>% summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
+correlation.bin <- meta.bin %>% summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
                                             egger.peter = cor(pval.egger.bin, pval.peter.bin),
@@
 
-print(xtable(x = t(binary.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)", label = "agreement.bin",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
-@
+#Continuous outcomes:
+n.cont <- dim(meta.cont)[1]
+rejection.cont <- meta.cont %>% summarize(egger.rejection = mean(egger.test),
+                                              begg.rejection = mean(begg.test),
+                                              thomson.rejection = mean(thomson.test))
 
-<<results = 'asis', echo = FALSE>>=
-data.cont.ext <- data.cont.ext %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
+cont.spread <- meta.cont %>% select(egger.test, begg.test, thomson.test) %>% gather(key = test.type, value = "null.hypothesis")
+cont.spread$null.hypothesis <- ifelse(cont.spread$null.hypothesis == 1, "rejected", "not rejected")
+cont.spread$null.hypothesis <- factor(cont.spread$null.hypothesis)
+
+meta.cont <- meta.cont %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
                                           thomson.begg = ifelse(thomson.test == begg.test, "agree", "disagree"),
@@
 
-agreement.cont <- data.cont.ext %>% summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
+agreement.cont <- meta.cont %>% summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
                                               thomson.begg = sum(thomson.begg == "agree")/n(),
@@
 
-correlation.cont <- data.cont.ext %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
+correlation.cont <- meta.cont %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
                                                 thomson.begg = cor(pval.thomson.cont, pval.begg.cont),
@@
 
+#Trimfill missing studies fractions statistics:
+trimfill.cont.mean <- meta.cont %>% ungroup %>% summarise(mean = mean(missing.trim.cont)) %>% select(mean)
+trimfill.cont.median <- meta.cont %>% ungroup %>% summarise(median = median(missing.trim.cont)) %>% select(median)
+
+trimfill.bin.mean <- meta.bin %>% ungroup %>% summarise(mean = mean(missing.trim.bin)) %>% select(mean)
+trimfill.bin.median <- meta.bin %>% ungroup %>% summarise(median = median(missing.trim.bin)) %>% select(median)
+@
+
+There are tests that can be applied to find out if reporting bias is present in the meta analysis.
+For the precise description, see the methods section.
+Application of the tests is only recommended if there are ten or more studies \citep{cochrane.handbook} that can be used, so all meta-analyses with less than ten studies have been excluded.
+
+\vspace{0mm}
+There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
+In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes.
+From \Sexpr{n.cont} meta-analyses with continouos outcomes, most meta-analyses with rejected null hypotheses have been found by the Thompson and Sharp test (\Sexpr{round(rejection.cont$thomson.rejection, 3)}), followed closely by Eggers test (\Sexpr{round(rejection.cont$egger.rejection, 3)}) and Begg and Mazumdar's test (\Sexpr{round(rejection.cont$begg.rejection, 3)}).
+The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = \Sexpr{n.bin}).
+The test that rejects most null hypotheses is here Egger's test (\Sexpr{round(rejection.bin$egger.rejection, 3)}), followed by R\"ucker's test (\Sexpr{round(rejection.bin$rucker.rejection, 3)}), Harbord's test (\Sexpr{round(rejection.bin$harbord.rejection, 3)}), Peters test (\Sexpr{round(rejection.bin$peter.rejection, 3)}) and Schwarzer's test (\Sexpr{round(rejection.bin$schwarzer.rejection, 3)}).
+
+\begin{figure}
+<<echo=FALSE>>=
+cont.spread %>% ggplot(aes(x = test.type, fill = null.hypothesis )) + geom_bar() + coord_flip() + theme_bw()
+@
+\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
+\label{bias.results.cont}
+\end{figure}
+
+\begin{figure}
+<<echo=FALSE>>=
+
+bin.spread %>% ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + theme_bw()
+@
+\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
+\label{bias.results.bin}
+\end{figure}
+
+The agreement of the tests, i.e.
+the proportion of meta-analyses where the rest results are equal between tests, is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
+Agreement in tests for binary outcomes is better than continuous outcomes, with some variation between tests (binary outcomes: 83 to 91\%).
+Correlation varies more between tests, both for continuous and binary outcome tests.
+
+<<results = 'asis', echo = FALSE, warnings = FALSE>>=
+print(xtable(x = t(binary.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)", label = "agreement.bin",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
+@
+
+<<results = 'asis', echo = FALSE, warnings = FALSE>>=
 print(xtable(x = t(cont.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)", label = "agreement.cont",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
@@
 %(Suggests that 10 is likely too small)
+A trend towards more significant p-values is visible for larger sample sizes.
 
@@
 <<echo=FALSE>>=
-data.bin.ext %>% filter(n < 100)%>% ggplot(aes(y = pval.peter.bin, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
+meta.bin %>% filter(n < 100)%>% ggplot(aes(y = pval.peter.bin, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
 @
@@
 <<echo=FALSE>>=
-data.cont.ext %>% filter(n < 100) %>% ggplot(aes(y = pval.thomson.cont, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
+meta.cont %>% filter(n < 100) %>% ggplot(aes(y = pval.thomson.cont, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
 @
@@
 
-<<echo=FALSE>>=
-trimfill.cont <- data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 50) %>% 
-  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-  mutate(n = n()) %>% filter(n > 9) %>% 
-  summarize(trim = trimfill(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2))$k0 / n())
-
-trimfill.cont.mean <- trimfill.cont %>% ungroup %>% summarise(mean = mean(trim)) %>% select(mean)
-trimfill.cont.median <- trimfill.cont %>% ungroup %>% summarise(median = median(trim)) %>% select(median)
-
-trimfill.bin <- data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% #filter(file.nr < 503) %>% 
-  filter(events1 > 0 | events2 > 0) %>% 
-  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-  mutate(n = n()) %>% filter(n > 9) %>% 
-  summarize(trim = trimfill(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2))$k0 / n())
-
-trimfill.bin.mean <- trimfill.bin %>% ungroup %>% summarise(mean = mean(trim)) %>% select(mean)
-trimfill.bin.median <- trimfill.bin %>% ungroup %>% summarise(median = median(trim)) %>% select(median)
-@
-
 \vspace{0mm}
 One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
+The mean fraction of trimmed comparisons for binary outcomes is \Sexpr{round(trimfill.bin.mean,2)} and the median \Sexpr{round(trimfill.bin.median,2)}.
 A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
-The mean fraction of trimmed comparisons for binary outcomes is \Sexpr{round(trimfill.bin.mean,2)} and the median \Sexpr{round(trimfill.bin.median,2)}.
+In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses.
 In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
+In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.
 
@@
 <<echo=FALSE>>=
-trimfill.cont %>% ggplot(aes(x = trim)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
+meta.cont %>% ggplot(aes(x = missing.trim.cont)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
   theme_bw() + labs(title = "Fraction of Trimmed Comparisons (continuous outcome)") + xlab("Fraction") + ylab("Frequency")
@@
 <<echo=FALSE>>=
-trimfill.bin %>% ggplot(aes(x = trim)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
+meta.bin %>% ggplot(aes(x = missing.trim.bin)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
   theme_bw() + labs(title = "Fraction of Trimmed Comparisons (binary outcome)") + xlab("Fraction") + ylab("Frequency")
@@
 <<echo=FALSE>>=
-cdplot(x = data.bin.ext$trim.bin, y = as.factor(ifelse(data.bin.ext$peter.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
+cdplot(x = meta.bin$missing.trim.bin, y = as.factor(ifelse(meta.bin$peter.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
 @
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of peters test and dichotomous outcomes}
+\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
 \label{trimfill.pvalues.bin}
@@
 <<echo=FALSE>>=
-cdplot(x = data.cont.ext$trim.cont, y = as.factor(ifelse(data.cont.ext$thomson.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
+cdplot(x = meta.cont$missing.trim.cont, y = as.factor(ifelse(meta.cont$thomson.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
 @
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of thomson and sharp's test and continuous outcomes}
+\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
 \label{trimfill.pvalues.cont}
 \end{figure}
+
+\subsection{Small Study Effect Correction}
+
+Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
+
+% # <<results = 'asis', Echo = FALSE>>=
+% # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
+% #                                             schwarzer.rejection = mean(schwarzer.test),
+% #                                             rucker.rejection = mean(rucker.test),
+% #                                             harbord.rejection = mean(harbord.test),
+% #                                             peter.rejection = mean(peter.test))
+% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
+% # @
 

### 2019-04-15 report/chapter04.Rnw
Update

--- 2019-03-28 report/chapter04.Rnw
@@
 First the fixed effect meta-analysis will be explained.
-For convenience, notatotion will be identical whenever possible for both methods.
 Note that both methods can be used for continuous or dichotomous outcomes.
-For more details about the methods, see chapter 11 and 12 in \citep{metaanalysis}
+For more details about the methods, see chapter 11 and 12 in \citet{metaanalysis}
 
 \vspace{0mm}
-Let $y_{i}$ be the effect size estimate of the study $i$ and $v_{i}$ be the corresponding variance of the effect size estimate.
-Effect measures have to be identical for all studies.
-Furthermore, let $w_i$ be the inverse of the variance of the estimate from study $i$, $1/v_{i}$ and $n$ the total number of studies.
+Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
+The pooled estimate $\Delta_{f}$ of the fixed effects model is then the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
+The variance $\eta_{f}$ is the reciprocal of the sum of the weights as shown in \ref{reciproce.variance}.
+
+\begin{align}
+\Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
+\eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
+\end{align}
+
+The computation of random effects meta-analysis is more complicated.
+Random effects meta-analysis will give smaller studies with larger variance more weight in the pooled estimate.
+Shortly, the idea is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
 
 \vspace{0mm}
-The pooled estimate of the fixed effects model is then simply the weighted average with the weights given by the inverses of the variances, $w_{i}$.
+The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
+It is used to calculate a new weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
+The variance of $\Delta_{r}$, $\eta_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
 
-\begin{align*}
-\Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}}
-\end{align*}
+\begin{align}
+v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
+\Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
+\eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
+\end{align}
 
-and the variance is the reciprocal of the sum of the weights,
+A p-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
 
-\begin{align*}
-\nu &= \frac{1}{\sum_{i = 1}^n w_{i}}
-\end{align*}
+\begin{align}
+Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
+p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
+\end{align}
 
-\section{Reporting Bias Adjustment}
-One method to account for publication bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
-Its basic working principle is to mirror studies in a funnel plot that cause the funnel plot to be asymmetric and then to perform one of the meta-analyses as described in section {meta-analysis} with the mirrored studies.
-In the subsequent equations, the same terminology as for meta analyses will be used.
+\section{Small Study Effects Tests}
+\subsection{Continuous Outcome Tests}
+% Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. 
+% First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
+
+\subsubsection{Begg and Mazumdar: Rank Correlation Test}
+\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+A standardized effect size $y_{i}^\star$ can be computed as in \ref{begg.stand.eff}.
+$v_{i}^\star$ is the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
+$\Delta_{f}$ is the pooled estimate for fixed effect estimate defined in \ref{weighted.mean}.
+
+\begin{align}
+y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff} \\
+v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} 
+\end{align}
+
+A rank correlation test based on Kendall's tau is then used.
+The pairs $(y_{i}^\star, v_{i}^\star)$ that are ranked in the same order are enumerated.
+Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (e.g.
+larger standardized effect size and smaller variance).
+Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
+
+\begin{align}
+Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
+\end{align}
+
+The changes in the case of ties are negligible \cite[410]{begg.ties}.
+
+\subsubsection{Egger's Test: Linear Regression Test}
+Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
+Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope.
+
+\vspace{0mm}
+If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
+The p-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
+
+\begin{align}
+p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
+\end{align}
+
+\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test}
+A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
+Let $\tau^2$ be equal to \ref{Tau.definition}.
+The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
+
+\begin{align}
+y_{i} \sim N(\beta_{0} + \beta{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
+\end{align}
+
+Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
+Analogous to Edger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta{0} = 0$.
+
+\subsection{Dichotomous Outcomes Tests}
+
+The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
+Consequently, the tests above will tend to reject the null-hypothesis too often, i.e.
+that they are not conservative enough.
+A number of solutions to this problem are existing in the literature.
+
+\subsubsection{Peters Test: Weighted Linear Regression Test}
+A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
+
+\vspace{0mm}
+Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
+
+\begin{align}
+y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
+v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
+\end{align}
+
+and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
+Instead of taking the variance as explanatory or independent variable in regression as in Egger's Test, the inverse of the total sample size $x_{i}$ is used, and the variance $v_{i}$ is used as a weight.
+The subsequent test procedure is then identical to Egger's test.
+
+\vspace{0mm}
+Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
+
+\subsubsection{Harbord's Test: Score based Test}
+A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
+The score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
+
+\begin{align}
+r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
+v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
+\end{align}
+
+Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
+Note that $r_{i}/v_{i}$ is also known as peto odds ratio.
+
+\subsubsection{Schwarzer's Test: Rank Correlation Test}
+\citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
+$\mathbb{E}(E_{t})$ and variance of $E_{t}$ are then estimated based on $e_{t}$.
+
+\vspace{0mm}
+The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
+
+\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
+The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let
+
+\begin{align}
+y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}}// 
+v_{i} = 1/4n_{t} + +/4n_{c}
+\end{align}
+
+Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances.
+
+\section{Small Study Effect Adjustment}
+\subsection{Trim and Fill}
+One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
+It is a nonparametric test based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
+%If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
+
+\vspace{0mm}
+The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
+First, $\Delta$ is estimated using a fixed or random effects model.
+Then, the $k$ effect size estimates with the smallest standard errors are trimmed, and $\Delta$ is estimated again.
+The procedure is repeated until $k$ is 0 and the funnel plot is symmetric.
+The total number of missing studies is then mirrored with respect to the final effect size estimate $\Delta$, and $\Delta$ and its standard error is then computed to obtain an unbiased estimate.
+
+\subsection{Copas Selection Model}
+
+A method proposed in \cite{Copas1,Copas2,Copas3} assumes that there is a population of studies of which only a part has been published dependent on the variance and size of their estimated effects.
+Studies with small variance and large effect sizes are more likely to be published than studies with large variance and small effect sizes.
+Note that small effect size means here a treatment effect close to the control effect.
+
+Let $y_i$ be the effect size estimate of study $i$. Then
+
+\begin{align}
+y_{i} \sim N(\mu_{i}, \sigma_{i}^2) \\
+\mu_{i} \sim N(\mu, \tau^2)
+\end{align}
+
+corresponding to a standard random effects model.
+$\mu$ is the overall mean effect, $\sigma_{i}^2$ the within study variance and $\tau^2$ the between study variance.
+This is the \textit{population model}.
+
+\vspace{0mm}
+The \textit{selection model} is defined as follows. Suppose a selection of studies with reported standard errors $s$ (likely different from $\sigma$). Only a proportion
+
+\begin{align}
+P(\textrm{select}|s) &= \Phi(a + b/s) \label{copas.selection1}
+\end{align}
+
+of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
+\ref{copas.selection1} can be rewritten as
+
+\begin{align}
+z = a + b/s + \delta \label{copas.selection2}
+\end{align}
+
+with $\delta \sim N(0,1)$. The study with standard error $s$ is only selected if $z$ is positive. Therefore, the larger $z$, the more likely the study is selected.
+Combining population and selection model for study $i$, we have
+
+\begin{align}
+y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \\
+\mu_{i} \sim N(\mu, \tau^2) \\
+z_{i} = a + b/s_{i} + \delta_{i}
+\end{align}
+
+where $(\epsilon_{i}, \delta_{i})$ are standard normal residuals and jointly normal with correlation $\rho = cor(y_{i}, z_{i})$.
+Every given study $i$ in the meta-analysis has $z_{i} > 0$.
+If $\rho$ is large and positive and $z_{i} > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_{i}$ and $\delta_{i}$.
+Thus, the true mean $\mu$ is likely to be overestimated.
+
+\vspace{0mm}
+Let $u = a + b/s$, $\lambda(u) = \phi(u)/\Phi(u)$ ($\phi$ is the standard normal density function) and $\tilde{\rho} = \sigma/\sqrt(\tau^2 + \sigma^2) \rho$.
+The probability of a study being selected is
+
+\begin{align}
+P(\textrm{select}|s, y) = P(a,b,s,y) = \Phi(\frac{u + \tilde{\rho}((y - \mu)/\sqrt(\tau^2 + \sigma^2))}{\sqrt{1 - \tilde{\rho^2}}})
+\end{align}
+
+It can also be shown that the expected value
+
+\begin{align}
+\mathbb{E}(y|s, select) = \mu + \rho\sigma\lambda(u) \label{copas.expectation}
+\end{align}
+
+which shows that the expected value for a study is larger for larger $\sigma$.
+
+\vspace{0mm}
+One can compute a likelihood function based on the distribution of $y$ conditional on $z > 0$.
+The likelihood can be maximized for any given pair $a,b$ (can not be estimated since the number of missing studies is not known), and a maximum likelihood estimate $\hat{\mu}$ for the true mean $\mu$ can be obtained.
+One can then perform a sensitivity analysis.
+First, one looks how $\hat{\mu}$ changes for different values of $a,b$.
+One can then compare the fitted values in \ref{copas.expectation} with the real values.
+To test the fit of the model (while keeping all other parts unchanged), the model can be extended in the following way :
+
+\begin{align}
+y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
+\end{align}
+
+If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
+Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
+The p-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
+
+\vspace{0mm}
+To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
+
+\vspace{0mm}
+In practice, only a range of values for $a,b$ are reasonable.
+For those values, the quantities above can be calculated and illustrated.
+Values for $\mu$ that have p-values over a predefined significance threshold can be used for inference of the effect size.
+
+\subsection{Adjustment by Regression}
+There are multiple ways to adjust for small study effects by regression. The general idea is to regress the effect size of a study with a variance of zero based on the given effects and variances.
+
+\citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
+Similarly to what has been seen in Copas selection model, we let $y_{i}$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_{i}}$ as in \ref{limitmeta.regression}.
+
+\begin{align}
+y_{i}& = \beta_{0} + \beta{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \stackrel{\textrm{iid}}{\sim} N(0,1)  \ref{limitmeta.regression}
+\end{align}
+
+$\beta{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
+
+\begin{align}
+\mathbb{E}((y_{i} - \beta_{})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{if} \sqrt{v_{i}} \rightarrow \infty \\
+\mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
+\end{align}
+
+After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test.
+
+\vspace{0mm}
+To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
+
+\begin{align}
+y_{i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{s_{i}/M + \tau^2}) \label{limitmeta.regression}
+\end{align}
+
+Letting $M \rightarrow \infty$, we obtain:
+
+\begin{align}
+y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
+\end{align}
+
+Note that:
+
+\begin{align}
+y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
+\end{align}
+
+$\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
+
+\begin{align}
+\epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
+\end{align}
+
+Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get
+
+\begin{align}
+y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
+\end{align}
+
+By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
 

### 2019-04-15 code/PubBias.R

@@ -1,16 +1,19 @@
-rm(list = ls())
 PATH_HOME = path.expand("~") # user home
 PATH = file.path(PATH_HOME, 'Data/PubBias')
 PATH2 = file.path(PATH_HOME, 'PubBias')
 FILE = 'cochrane_2018-06-09.csv'
 PATH_DATA = file.path(PATH, 'data')
 PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH, 'results')
+PATH_RESULTS = file.path(PATH2, 'results')
 PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
 
 file_results = "pb.RData"
 
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+load(file.path(PATH_RESULTS, 'PubBias_results1.RData'))
+load(file.path(PATH_RESULTS, 'PubBias_results2.RData'))
+
 
 data = pb.readData(path = PATH_DATA, file = FILE)
 tmp = pb.clean(data)
@@ -21,86 +24,8 @@ require(biostatUZH)
 require(tidyverse)
 require(meta)
 require(xtable)
-library(car)
-
-####################################################################################################
-#Look for sample size effect on effect size
-####################################################################################################
-
-data %>% filter(total1 + total2 < 100 & total1 + total2 > 5) %>%
-  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
-  group_by(sample.size) %>% 
-  summarize(mean.scaled.effect = mean(scaled.effect, na.rm = T)) %>% 
-  ggplot(aes(x = sample.size, y = mean.scaled.effect)) + geom_point() + geom_smooth(method = "lm")
-
-data %>%  filter(total1 + total2 < 100 & total1 + total2 > 5) %>%
-  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
-  ggplot(aes(x = sample.size, y = scaled.effect)) + geom_point(alpha = 0.15, size = 0.5) + geom_smooth(method = "lm")
-
-data %>% filter(total1 + total2 > 5 & total1 + total2 < 300) %>% 
-  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
-  group_by(sample.size) %>% 
-  summarize(mean.effect = mean(scaled.effect, na.rm = T)) %>% 
[…]

### 2019-04-15 code/explore.R

@@ -24,7 +24,7 @@ aliases = tmp[[2]]
 require(biostatUZH)
 require(tidyverse)
 require(meta)
-require(xtable)
+require(metasens)
 
 
 #Look at Migraine sympton relieve review
@@ -267,6 +267,14 @@ data %>% filter(file.nr < 5016) %>% group_by(file.nr, outcome.nr, comparison.nr,
   mutate(counts = n()) %>% filter(counts > 1) %>% mutate(scaled.effect = scale(effect), scaled.time = scale(study.year)) %>% 
   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .005, alpha = 0.15) 
 
+data %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>% 
+  filter(study.year > 1950 | study.year < 2019) %>% 
+  mutate(counts = n()) %>% filter(counts > 1) %>% 
+  filter(max(diff(study.year)) < 50) %>% 
+  mutate(abs.scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
+  ggplot(aes(x = scaled.time, y = abs.scaled.effect)) + geom_point(size = .005, alpha = 0.15) + geom_smooth()
+
+
 #Pvalues over time
 temp.pval <- data %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>%
   distinct(study.year, .keep_all = T) %>% 
@@ -306,6 +314,23 @@ data %>% filter(!is.na(fishersz)) %>% group_by(file.nr, comparison.nr, outcome.n
   ggplot(aes(x = nn, y = trials)) + geom_line(col = "gray15") +
   theme_bw() + labs(title = "Trials Comparing the Same Subject per Review")
 
+#Look for sample size effect on effect size
+data %>% filter(total1 + total2 < 100 & total1 + total2 > 5) %>%
+  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
+  group_by(sample.size) %>% 
+  summarize(mean.scaled.effect = mean(scaled.effect, na.rm = T)) %>% 
+  ggplot(aes(x = sample.size, y = mean.scaled.effect)) + geom_point() + geom_smooth(method = "lm")
+
+data %>%  filter(total1 + total2 < 100 & total1 + total2 > 5) %>%
[…]

### 2019-04-17 report/MSc_Report.tex
Function update

@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sat Apr 13 14:58:52 2019
+% Tue Apr 16 13:54:44 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sat Apr 13 14:58:53 2019
+% Tue Apr 16 13:54:44 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sat Apr 13 14:58:58 2019
+% Tue Apr 16 13:54:49 2019
 \begin{table}[ht]
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
 
@@
 \label{effect.samplesize}
+\end{figure}
+
+It is also possible to look how the amount of meta-analysis with significant pooled effect size estimates changes over time, e.g.
+mean publication year (of studies included in the meta-analysis).
+0.05 is used here as the threshold for $p$-value significance and subsequent null-hypothesis rejection.
+To constrict random fluctuation in the proportion, only mean publication years with a certain amount of meta-analyses are shown ($n < 180$).
+The $p$-value of the fixed effects meta analysis model is used to decide about rejection of the null-hypothesis.
+As Figure \ref{treatment.effect.significance.overtime} shows, the proportion of meta-analyses with significant treatment effect estimates stays roughly constant over time.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
+
+}
+
+\end{knitrout}
+\caption{Proportion of significant treatment effect estimates over time (mean publication year).}
+\label{effect.samplesize}
+\end{figure}
+
+A somewhat different question is how statistical power of studies changed over time.
+As an approximation, the total sample size of a study can be used.
+Figure \ref{median.samplesize.overtime} shows the median sample size of all studies of a given year.
+Again, to reduce the effects of distortion due to random fluctuation, only the medians for the years 1980 to 2017 are used ($n$ > 50,000).
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
+
+}
+
+\end{knitrout}
+\caption{Median sample size over time (years).}
+\label{median.samplesize.overtime}
 \end{figure}
@@
 There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
-In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes.
-From 2312 meta-analyses with continouos outcomes, most meta-analyses with rejected null hypotheses have been found by the Thompson and Sharp test (0.319), followed closely by Eggers test (0.309) and Begg and Mazumdar's test (0.131).
-The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 5717).
-The test that rejects most null hypotheses is here Egger's test (0.186), followed by R\"ucker's test (0.163), Harbord's test (0.144), Peters test (0.142) and Schwarzer's test (0.088).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
+In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = 1383)
+The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3350).
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
 
@@
 \label{bias.results.bin}
+\end{figure}
+
+The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
+This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-24-1}
+
+}
+
+\end{knitrout}
+\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
+\label{bias.results.cont.sep}
+\end{figure}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-25-1}
+
+}
+
+\end{knitrout}
+\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
+\label{bias.results.bin.sep}
+\end{figure}
+
+Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses).
+The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}.
+The Figure suggests that the frequency of publication bias remains constant over time.
+The mean publication years have been restricted such that at least 180 meta-analyses are available per year such that random fluctuation is restricted to some extent.
+The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-26-1}
+
+}
+
+\end{knitrout}
+\caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
+\label{pub.bias.overtime}
 \end{figure}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sat Apr 13 14:59:07 2019
+% Tue Apr 16 13:55:01 2019
 \begin{table}[ht]
@@
   \hline
-egger.schwarzer & 0.83 & 0.38 \\ 
-  egger.peter & 0.84 & 0.44 \\ 
-  egger.rucker & 0.83 & 0.39 \\ 
-  egger.harbord & 0.91 & 0.75 \\ 
-  schwarzer.peter & 0.85 & 0.24 \\ 
-  schwarzer.rucker & 0.83 & 0.30 \\ 
-  schwarzer.harbord & 0.88 & 0.52 \\ 
-  rucker.peter & 0.89 & 0.66 \\ 
-  harbord.peter & 0.86 & 0.45 \\ 
+egger.schwarzer & 0.88 & 0.38 \\ 
+  egger.peter & 0.89 & 0.52 \\ 
+  egger.rucker & 0.89 & 0.48 \\ 
+  egger.harbord & 0.94 & 0.76 \\ 
+  schwarzer.peter & 0.89 & 0.29 \\ 
+  schwarzer.rucker & 0.88 & 0.34 \\ 
+  schwarzer.harbord & 0.92 & 0.51 \\ 
+  rucker.peter & 0.92 & 0.67 \\ 
+  harbord.peter & 0.91 & 0.53 \\ 
    \hline
@@
   \hline
-thomson.egger & 0.85 & 0.67 \\ 
-  thomson.begg & 0.75 & 0.45 \\ 
-  egger.begg & 0.75 & 0.38 \\ 
+thomson.egger & 0.89 & 0.69 \\ 
+  thomson.begg & 0.82 & 0.47 \\ 
+  egger.begg & 0.79 & 0.36 \\ 
    \hline
@@
 Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
-The p-values of two tests are shown with respect to the sample size of the studies in Figure \ref{pvalues.samplesize.bin} for peters test based on dichotomous outcomes and in Figure \ref{pvalues.samplesize.cont} for thomson and sharp's test based on continuous outcomes.
+The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}.
 %(Suggests that 10 is likely too small)
-A trend towards more significant p-values is visible for larger sample sizes.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
-
-}
-
-\end{knitrout}
-\caption{P-values of peters test for small study effects and their corresponding sample size (dichotomous outcomes)}
-\label{pvalues.samplesize.bin}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-24-1}
-
-}
-
-\end{knitrout}
-\caption{P-values of thomson and sharp's test for small study effects and their corresponding sample size (continuous outcomes)}
-\label{pvalues.samplesize.cont}
+In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
+A s trend towards more rejections for larger sample sizes can be seen.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-29-1}
+
+}
+
+\end{knitrout}
+\caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
+\label{pvalues.samplesize}
 \end{figure}
@@
 One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
-The mean fraction of trimmed comparisons for binary outcomes is 0.17 and the median 0.15.
-A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
+The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.18.
+% A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
 In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses.
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-25-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of fractions of trimmed comparisons from meta analyses with continuous outcomes.}
-\label{trimfill.cont}
-\end{figure}
-
-The mean fraction of trimmed comparisons for continuous outcomes is 0.22 and the median 0.2.
-
-The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-26-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of fractions of trimmed comparisons from meta analyses with binary outcomes.}
-\label{trimfill.bin}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-30-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-31-1}
 
@@
 \subsection{Small Study Effect Correction}
-
 Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
@@
 % # <<results = 'asis', Echo = FALSE>>=
-% # rejection.bin <- data.bin.ext %>% summarize(egger.rejection = mean(egger.test),
+% # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
 % #                                             schwarzer.rejection = mean(schwarzer.test),

### 2019-04-17 report/chapter02.Rnw
Function update

@@
 PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
 FILE = 'cochrane_2018-06-09.csv'
 PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH, 'code')
+PATH_CODE = file.path(PATH2, 'code')
 PATH_RESULTS = file.path(PATH, 'results')
@@
                echo=TRUE, message=FALSE,
-               fig.width=8, fig.height=3,
+               fig.width=8.1, fig.height=3,
                out.width='\\textwidth-3cm',

### 2019-04-17 report/chapter03.Rnw
Function update

@@
                echo=TRUE, message=FALSE,
-               fig.width=8, fig.height=3.5,
+               fig.width=8.1, fig.height=3.5,
                out.width='\\textwidth-3cm',
@@
 require(tidyverse)
+require(gridExtra)
 require(meta)
@@
 \chapter{Results}
+
+<<echo=FALSE>>=
+meta <- bind_rows(meta.bin, meta.cont)
+meta <- meta %>% mutate(sig.ranef = ifelse(!is.na(sig.ranef.bin), sig.ranef.bin, sig.ranef.cont),
+                        thomson.test = ifelse(!is.na(thomson.test), thomson.test, rucker.test),
+                        sig.fixef = ifelse(!is.na(sig.fixef.bin), sig.fixef.bin, sig.fixef.cont),
+                        sig.reg.random = ifelse(!is.na(sig.reg.random.bin), sig.reg.random.bin, sig.reg.random.cont),
+                        missing.trim = ifelse(!is.na(missing.trim.bin), missing.trim.bin, missing.trim.cont),
+                        pval.thomson = ifelse(!is.na(pval.rucker.bin), pval.rucker.bin, pval.thomson.cont))
+@
 
@@
 
+It is also possible to look how the amount of meta-analysis with significant pooled effect size estimates changes over time, e.g.
+mean publication year (of studies included in the meta-analysis).
+0.05 is used here as the threshold for $p$-value significance and subsequent null-hypothesis rejection.
+To constrict random fluctuation in the proportion, only mean publication years with a certain amount of meta-analyses are shown ($n < 180$).
+The $p$-value of the fixed effects meta analysis model is used to decide about rejection of the null-hypothesis.
+As Figure \ref{treatment.effect.significance.overtime} shows, the proportion of meta-analyses with significant treatment effect estimates stays roughly constant over time.
+
+\begin{figure}
+<<echo=FALSE>>=
+meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
+  ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef), stat(count))) + geom_density(na.rm = T, position = "fill") + 
+  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+@
+\caption{Proportion of significant treatment effect estimates over time (mean publication year).}
+\label{effect.samplesize}
+\end{figure}
+
+A somewhat different question is how statistical power of studies changed over time.
+As an approximation, the total sample size of a study can be used.
+Figure \ref{median.samplesize.overtime} shows the median sample size of all studies of a given year.
+Again, to reduce the effects of distortion due to random fluctuation, only the medians for the years 1980 to 2017 are used ($n$ > 50,000).
+
+\begin{figure}
+<<echo=FALSE>>=
+data %>% distinct(study.name, .keep_all = T) %>%  filter(study.year < 2018 & study.year > 1980) %>% group_by(study.year) %>% 
+  summarize(samplesize = median(total1 + total2, na.rm = T)) %>% 
+  ggplot(aes(y = samplesize, x = study.year)) + geom_line()
+@
+\caption{Median sample size over time (years).}
+\label{median.samplesize.overtime}
+\end{figure}
+
 \subsection{Small Study Effect Tests}
@@
 <<echo=FALSE, warning=FALSE>>=
+#Test Results: Binary
+test.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                          schwarzer.test = mean(schwarzer.test),
+                                                          rucker.test = mean(rucker.test),
+                                                          harbord.test = mean(harbord.test),
+                                                          peter.test = mean(peter.test))
+test.bin <- test.bin %>% gather(key = "test.type", value = "mean")
+
+p.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% 
+  select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
+  gather(key = "test.type", value = "null.hypothesis") %>%  
+  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+  theme_bw() + xlab(label = NULL) +
+  annotate("text", x = test.bin$test.type, y = 1000, 
+           label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
+           color = "white")
+
+test.sig.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                              schwarzer.test = mean(schwarzer.test),
+                                                              rucker.test = mean(rucker.test),
+                                                              harbord.test = mean(harbord.test),
+                                                              peter.test = mean(peter.test))
+test.sig.bin <- test.sig.bin %>% gather(key = "test.type", value = "mean")
+
+p1 <- meta.bin %>% ungroup() %>% 
+select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
+  gather(key = "test.type", value = "null.hypothesis") %>% 
+  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+  theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
+  annotate("text", x = test.sig.bin$test.type, y = 1750, 
+           label = paste(round(test.sig.bin$mean, 2)*100, "% rejected"), 
+           color = "white")
+
+test.nonsig.bin <- meta.bin %>% filter(sig.fixef.bin == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                                                                schwarzer.test = mean(schwarzer.test),
+                                                                                                rucker.test = mean(rucker.test),
+                                                                                                harbord.test = mean(harbord.test),
+                                                                                                peter.test = mean(peter.test))
+test.nonsig.bin <- test.nonsig.bin %>% gather(key = "test.type", value = "mean")
+
+p2 <- meta.bin %>% 
+  filter(sig.fixef.bin == 0) %>% ungroup() %>% 
+  select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
+  gather(key = "test.type", value = "null.hypothesis") %>% 
+  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+  theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) +theme(legend.position="none") +
+  annotate("text", x = test.nonsig.bin$test.type, y = 650, 
+           label = paste(round(test.nonsig.bin$mean, 2)*100, "% rejected"), 
+           color = "white")
+
+#Test Results: Continuous
+test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                            begg.test = mean(begg.test),
+                                                            thomson.test = mean(thomson.test))
+
+test.cont <- test.cont %>% gather(key = "test.type", value = "mean")
+
+p.cont <- meta.cont %>% ungroup() %>% 
+  select(egger.test, thomson.test, begg.test) %>% 
+  gather(key = "test.type", value = "null.hypothesis") %>% 
+  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+  theme_bw() + xlab(label = NULL) +
+  annotate("text", x = test.cont$test.type, y = 750, 
+           label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
+           color = "white")
+
+test.sig.cont <- meta.cont %>% filter(sig.fixef.cont == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                                                                begg.test = mean(begg.test),
+                                                                                                thomson.test = mean(thomson.test))
+
+test.sig.cont <- test.sig.cont %>% gather(key = "test.type", value = "mean")
+
+p3 <- meta.cont %>% 
+  filter(sig.fixef.cont == 1) %>% ungroup() %>% 
+  select(egger.test, thomson.test, begg.test) %>% 
+  gather(key = "test.type", value = "null.hypothesis") %>% 
+  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+  theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
+  annotate("text", x = test.sig.cont$test.type, y = 600, 
+           label = paste(round(test.sig.cont$mean, 2)*100, "% rejected"), 
+           color = "white")
+
+test.nonsig.cont <- meta.cont %>% filter(sig.fixef.cont == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                                                                   begg.test = mean(begg.test),
+                                                                                                   thomson.test = mean(thomson.test))
+
+test.nonsig.cont <- test.nonsig.cont %>% gather(key = "test.type", value = "mean")
+
+p4 <- meta.cont %>% 
+  filter(sig.fixef.cont == 0) %>% ungroup() %>% 
+  select(egger.test, thomson.test, begg.test) %>% 
+  gather(key = "test.type", value = "null.hypothesis") %>% 
+  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+  theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
+  annotate("text", x = test.nonsig.cont$test.type, y = 100, 
+           label = paste(round(test.nonsig.cont$mean, 2)*100, "% rejected"), 
+           color = "white")
+
+########################################################################################################################################
+########################################################################################################################################
+
+#Agreement proportions of publication bias tests:
+
+#Binary:
 n.bin <- dim(meta.bin)[1]
-rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
-                                            schwarzer.rejection = mean(schwarzer.test),
-                                            rucker.rejection = mean(rucker.test),
-                                            harbord.rejection = mean(harbord.test),
-                                            peter.rejection = mean(peter.test))
-
-bin.spread <- meta.bin %>% select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% gather(key = test.type, value = "null.hypothesis")
-bin.spread$null.hypothesis <- ifelse(bin.spread$null.hypothesis == 1, "rejected", "not rejected")
-bin.spread$null.hypothesis <- factor(bin.spread$null.hypothesis)
-
-meta.bin <- meta.bin %>% mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
+meta.bin <- meta.bin %>%ungroup() %>%  mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
                                         egger.peter = ifelse(egger.test == peter.test, "agree", "disagree"),
@@
 
-agreement.bin <- meta.bin %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
+agreement.bin <- meta.bin %>% ungroup() %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
                                             egger.peter = sum(egger.peter == "agree")/n(),
@@
 
-correlation.bin <- meta.bin %>% summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
+correlation.bin <- meta.bin %>%ungroup() %>%  summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
                                               egger.peter = cor(pval.egger.bin, pval.peter.bin),
@@
 
-#Continuous outcomes:
+#Continuous:
 n.cont <- dim(meta.cont)[1]
-rejection.cont <- meta.cont %>% summarize(egger.rejection = mean(egger.test),
-                                              begg.rejection = mean(begg.test),
-                                              thomson.rejection = mean(thomson.test))
-
-cont.spread <- meta.cont %>% select(egger.test, begg.test, thomson.test) %>% gather(key = test.type, value = "null.hypothesis")
-cont.spread$null.hypothesis <- ifelse(cont.spread$null.hypothesis == 1, "rejected", "not rejected")
-cont.spread$null.hypothesis <- factor(cont.spread$null.hypothesis)
-
-meta.cont <- meta.cont %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
+meta.cont <- meta.cont %>% ungroup() %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
                                           thomson.begg = ifelse(thomson.test == begg.test, "agree", "disagree"),
@@
 
-agreement.cont <- meta.cont %>% summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
+agreement.cont <- meta.cont %>% ungroup() %>%  summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
                                               thomson.begg = sum(thomson.begg == "agree")/n(),
@@
 
-correlation.cont <- meta.cont %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
+correlation.cont <- meta.cont %>% ungroup() %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
                                                 thomson.begg = cor(pval.thomson.cont, pval.begg.cont),
@@
 rownames(cont.tests.agreement) <- c("Test Agreement","P-value Correlation")
+
+########################################################################################################################################
+########################################################################################################################################
 
@@
 trimfill.bin.median <- meta.bin %>% ungroup %>% summarise(median = median(missing.trim.bin)) %>% select(median)
+
+# meta.bin %>% ggplot(aes(x = missing.trim.bin)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
+#   theme_bw() + labs(title = "Fraction of Trimmed Comparisons (binary outcome)") + xlab("Fraction") + ylab("Frequency")
+# 
+# meta.cont %>% ggplot(aes(x = missing.missing.trim.cont)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
+#   theme_bw() + labs(title = "Fraction of Trimmed Comparisons (continuous outcome)") + xlab("Fraction") + ylab("Frequency")
+# 
+# meta.bin %>% ggplot(aes(x = missing.trim.bin, fill = factor(peter.test))) + geom_density(na.rm = T, position = "fill")
+# 
+# meta.bin %>% ggplot(aes(x = missing.trim.bin, fill = factor(harbord.test))) + geom_density(na.rm = T, position = "fill")
+# 
+# meta.cont %>% ggplot(aes(x = missing.missing.trim.cont, fill = factor(thomson.test))) + geom_density(na.rm = T, position = "fill")
+# 
+# #Time trends in significance of tests
+# meta.bin %>% filter(mean.publication.year < 2019 & mean.publication.year > 1960) %>% 
+#   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef.bin))) + geom_histogram()
+# 
+# meta.bin %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
+#   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef.bin))) + geom_density(na.rm = T, position = "fill")
+# 
+# meta.bin %>% filter(first.publication.year < 2013 & first.publication.year > 1990) %>% 
+#   ggplot(aes(x = first.publication.year, fill = factor(sig.fixef.bin))) + geom_density(na.rm = T, position = "fill")
+# 
+# meta.bin %>% filter(first.publication.year < 2013 & first.publication.year > 1990) %>% 
+#   ggplot(aes(x = first.publication.year, fill = factor(peter.test))) + geom_density(na.rm = T, position = "fill")
+# 
+# meta.bin %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
+#   ggplot(aes(x = mean.publication.year, fill = factor(rucker.test))) + geom_density(na.rm = T, position = "fill")
+# 
+# 
+# meta.cont %>% filter(mean.publication.year < 2019 & mean.publication.year > 1960) %>% 
+#   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef.cont))) + geom_histogram()
+# 
+# meta.cont %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
+#   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef.cont))) + geom_density(na.rm = T, position = "fill")
+# 
+# meta.cont %>% filter(first.publication.year < 2013 & first.publication.year > 1990) %>% 
+#   ggplot(aes(x = first.publication.year, fill = factor(sig.fixef.cont))) + geom_density(na.rm = T, position = "fill")
+# 
+# meta.cont %>% filter(first.publication.year < 2013 & first.publication.year > 1990) %>% 
+#   ggplot(aes(x = first.publication.year, fill = factor(thomson.test))) + geom_density(na.rm = T, position = "fill")
+# 
+# meta.cont %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
+#   ggplot(aes(x = mean.publication.year, fill = factor(egger.test))) + geom_density(na.rm = T, position = "fill")
+# 
+# 
+# data %>% filter(study.year < 2019 & study.year > 1980) %>% group_by(study.year) %>% summarize(samplesize = mean(total1 + total2, na.rm = T)) %>% 
+#   ggplot(aes(y = samplesize, x = study.year)) + geom_line()
+
 @
@@
 There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
-In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes.
-From \Sexpr{n.cont} meta-analyses with continouos outcomes, most meta-analyses with rejected null hypotheses have been found by the Thompson and Sharp test (\Sexpr{round(rejection.cont$thomson.rejection, 3)}), followed closely by Eggers test (\Sexpr{round(rejection.cont$egger.rejection, 3)}) and Begg and Mazumdar's test (\Sexpr{round(rejection.cont$begg.rejection, 3)}).
+In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = \Sexpr{n.cont})
 The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = \Sexpr{n.bin}).
-The test that rejects most null hypotheses is here Egger's test (\Sexpr{round(rejection.bin$egger.rejection, 3)}), followed by R\"ucker's test (\Sexpr{round(rejection.bin$rucker.rejection, 3)}), Harbord's test (\Sexpr{round(rejection.bin$harbord.rejection, 3)}), Peters test (\Sexpr{round(rejection.bin$peter.rejection, 3)}) and Schwarzer's test (\Sexpr{round(rejection.bin$schwarzer.rejection, 3)}).
 
@@
 <<echo=FALSE>>=
-cont.spread %>% ggplot(aes(x = test.type, fill = null.hypothesis )) + geom_bar() + coord_flip() + theme_bw()
+plot(p.cont)
 @
@@
 <<echo=FALSE>>=
-
-bin.spread %>% ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + theme_bw()
+plot(p.bin)
 @
@@
 \label{bias.results.bin}
+\end{figure}
+
+The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
+This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
+
+\begin{figure}
+<<echo=FALSE>>=
+grid.arrange(p3, p4, ncol = 2)
+@
+\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
+\label{bias.results.cont.sep}
+\end{figure}
+
+\begin{figure}
+<<echo=FALSE>>=
+grid.arrange(p1, p2, ncol = 2)
+@
+\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
+\label{bias.results.bin.sep}
+\end{figure}
+
+Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses).
+The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}.
+The Figure suggests that the frequency of publication bias remains constant over time.
+The mean publication years have been restricted such that at least 180 meta-analyses are available per year such that random fluctuation is restricted to some extent.
+The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).
+
+\begin{figure}
+<<echo=FALSE>>=
+meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
+  ggplot(aes(x = mean.publication.year, fill = factor(thomson.test), stat(count))) + geom_density(na.rm = T, position = "fill") + 
+  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+@
+\caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
+\label{pub.bias.overtime}
 \end{figure}
@@
 Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
-The p-values of two tests are shown with respect to the sample size of the studies in Figure \ref{pvalues.samplesize.bin} for peters test based on dichotomous outcomes and in Figure \ref{pvalues.samplesize.cont} for thomson and sharp's test based on continuous outcomes.
+The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}.
 %(Suggests that 10 is likely too small)
-A trend towards more significant p-values is visible for larger sample sizes.
+In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
+A s trend towards more rejections for larger sample sizes can be seen.
 
@@
 <<echo=FALSE>>=
-meta.bin %>% filter(n < 100)%>% ggplot(aes(y = pval.peter.bin, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
+meta %>% filter(n < 40) %>% ggplot(aes(stat(count), x = n, fill = factor(thomson.test))) + 
+  geom_density(position = "fill")
 @
-\caption{P-values of peters test for small study effects and their corresponding sample size (dichotomous outcomes)}
-\label{pvalues.samplesize.bin}
-\end{figure}
-
-\begin{figure}
-<<echo=FALSE>>=
-meta.cont %>% filter(n < 100) %>% ggplot(aes(y = pval.thomson.cont, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
-@
-\caption{P-values of thomson and sharp's test for small study effects and their corresponding sample size (continuous outcomes)}
-\label{pvalues.samplesize.cont}
+\caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
+\label{pvalues.samplesize}
 \end{figure}
@@
 The mean fraction of trimmed comparisons for binary outcomes is \Sexpr{round(trimfill.bin.mean,2)} and the median \Sexpr{round(trimfill.bin.median,2)}.
-A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
+% A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
 In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses.
@@
 <<echo=FALSE>>=
-meta.cont %>% ggplot(aes(x = missing.trim.cont)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
-  theme_bw() + labs(title = "Fraction of Trimmed Comparisons (continuous outcome)") + xlab("Fraction") + ylab("Frequency")
-@
-\caption{Histogram of fractions of trimmed comparisons from meta analyses with continuous outcomes.}
-\label{trimfill.cont}
-\end{figure}
-
-The mean fraction of trimmed comparisons for continuous outcomes is \Sexpr{round(trimfill.cont.mean,2)} and the median \Sexpr{round(trimfill.cont.median,2)}.
-
-The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
-\begin{figure}
-<<echo=FALSE>>=
-meta.bin %>% ggplot(aes(x = missing.trim.bin)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
-  theme_bw() + labs(title = "Fraction of Trimmed Comparisons (binary outcome)") + xlab("Fraction") + ylab("Frequency")
-@
-\caption{Histogram of fractions of trimmed comparisons from meta analyses with binary outcomes.}
-\label{trimfill.bin}
-\end{figure}
-
-\begin{figure}
-<<echo=FALSE>>=
-cdplot(x = meta.bin$missing.trim.bin, y = as.factor(ifelse(meta.bin$peter.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
+meta.bin %>% filter(missing.trim.bin < 0.5) %>% 
+  ggplot(aes(x = missing.trim.bin, fill = factor(peter.test), stat(count))) + 
+  geom_density(na.rm = T, position = "fill") + 
+  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
 @
@@
 <<echo=FALSE>>=
-cdplot(x = meta.cont$missing.trim.cont, y = as.factor(ifelse(meta.cont$thomson.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
+meta.cont %>% filter(missing.trim.cont < 0.5) %>% 
+  ggplot(aes(x = missing.trim.cont, fill = factor(thomson.test), stat(count))) + 
+  geom_density(na.rm = T, position = "fill") + 
+  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
 @

### 2019-04-17 code/PubBias.R

@@ -13,6 +13,8 @@ source(file.path(PATH_CODE, 'PubBias_functions.R'))
 
 load(file.path(PATH_RESULTS, 'PubBias_results1.RData'))
 load(file.path(PATH_RESULTS, 'PubBias_results2.RData'))
+load(file.path(PATH_RESULTS, 'PubBias_results3.RData'))
+load(file.path(PATH_RESULTS, 'PubBias_results4.RData'))
 
 
 data = pb.readData(path = PATH_DATA, file = FILE)
@@ -23,7 +25,805 @@ aliases = tmp[[2]]
 require(biostatUZH)
 require(tidyverse)
 require(meta)
+require(metasens)
+require(gridExtra)
 require(xtable)
+
+########################################################################################################################################
+########################################################################################################################################
+#########################################################################################################################################
+########################################################################################################################################
+########################################################################################################################################
+#########################################################################################################################################
+########################################################################################################################################
+########################################################################################################################################
+#########################################################################################################################################
+
+
+auto.copas <- function(meta.obj, sig.level){
+  sig.level <- sig.level + 0.05
+  gamma0 <- -1.7 #analog to P(select|small trial w. sd = 0.4) = 0.1 and P(select|large trial w. sd  = 0.05) = 0.9
+  gamma1 <- 0.16 #from limitmeta paper (Rücker 2011): "small range" procedure - if no nonsignificance - "broad range"
+  copas <- copas(meta.obj, gamma0.range = c(gamma0, 2), gamma1.range = c(0, gamma1))
+  pval.rsb <- copas$pval.rsb
+  N.unpubl <- copas$N.unpubl
+  if(all(pval.rsb < sig.level)){
[…]

### 2019-04-17 code/explore.R

@@ -9,12 +9,14 @@ PATH2 = file.path(PATH_HOME, 'PubBias')
 FILE = 'cochrane_2018-06-09.csv'
 PATH_DATA = file.path(PATH, 'data')
 PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH, 'results')
+PATH_RESULTS = file.path(PATH2, 'results')
 PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
 
 file_results = "pb.RData"
 
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
+load(file.path(PATH_RESULTS, 'PubBias_results3.RData'))
+load(file.path(PATH_RESULTS, 'PubBias_results4.RData'))
 
 data = pb.readData(path = PATH_DATA, file = FILE)
 tmp = pb.clean(data)
@@ -274,7 +276,6 @@ data %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>%
   mutate(abs.scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
   ggplot(aes(x = scaled.time, y = abs.scaled.effect)) + geom_point(size = .005, alpha = 0.15) + geom_smooth()
 
-
 #Pvalues over time
 temp.pval <- data %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>%
   distinct(study.year, .keep_all = T) %>% 
@@ -284,7 +285,8 @@ temp.pval <- data %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) 
 temp.pval %>% filter(time.rank < 10) %>% ggplot(aes(x = time.rank, y = pval)) + 
   geom_jitter(col = "gray15", size = 0.3, alpha = .25) + 
   theme_bw() + xlab("Time rank") + ylab("P-value") + labs(title = "P-values over (ranked) Time")
-
+########################################################################################################################################
+########################################################################################################################################
 # Cumulative number of total trials with
 data %>% filter(!is.na(fishersz)) %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
   ungroup %>% arrange(desc(n)) %>% mutate(trials = cumsum(n * nn)) %>% 
[…]

### 2019-04-18 report/chapter03.Rnw
Meta-analysis u.a.

@@
 \vspace{0mm}
-To provide an overview over the issue, first it is shown how mean absolute effect size decreases with increasing sample size of the comparisons in Figure \ref{effect.samplesize}.
-The decrease is particularly substantive from very small trials ($n$ = 5) to medium sample size ($n$ = 100), afterwards the trend is less pronounced.
-With increasing sample size, there are fewer results, therefore, the variation between means increases.
-All effects are normalized by subtracting the mean effect size of the dataset and dividng through the standard deviation.
-Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all sample sizes.
+To provide an overview over the issue, first it is shown how median absolute effect size decreases with increasing sample size of the comparisons in Figure \ref{effect.samplesize}.
+In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.
+
+\vspace{0mm}
+A clear trend of decrease of absolute effect size with increasing sample size (i.e.
+smaller variance) is visible.
+It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off.
+With increasing sample size, there are fewer results, therefore, the variation between medians increases.
+All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation.
+Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.
 
@@
 <<echo=FALSE>>=
-data %>% filter(total1 + total2 > 5 & total1 + total2 < 500) %>% 
+data %>% filter(total1 + total2 > 10 & total1 + total2 < 200) %>% 
   mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
   group_by(sample.size) %>% 
-  summarize(mean.effect = mean(scaled.effect, na.rm = T)) %>% 
-  ggplot(aes(x = sample.size, y = mean.effect)) + geom_point() + theme_bw() + xlab("sample size") + ylab("mean absolute normalized effect size")
+  summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
+  ggplot(aes(x = sample.size, y = median.effect)) + geom_point() + theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size")
 @
-\caption{Mean of the absolute of the normalized effect size plotted against the total sample size.}
+\caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
 \label{effect.samplesize}
@@
 
-It is also possible to look how the amount of meta-analysis with significant pooled effect size estimates changes over time, e.g.
+The median absolute normalized effect size can be visualized for the different outcome measures separately.
+Then it is well visible in Figure \ref{effect.samplesize.separated} that the trend of effect size decrease holds in particualar for risk and odds ratios, while it is way more stable for mean differences and standardized mean differences.
+Instead of normalizing the effects (i.e.
+subtracting mean and dividing through the standard deviation) for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.
+
+\begin{figure}
+<<echo=FALSE>>=
+data %>% filter(total1 + total2 > 10 & total1 + total2 < 100) %>% 
+  filter(outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio" | outcome.measure.new == "Mean Difference" |
+           outcome.measure.new == "Std. Mean Difference") %>% 
+  group_by(outcome.measure.new) %>% 
+  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
+  group_by(sample.size, outcome.measure.new) %>% 
+  summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
+  ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point() + facet_wrap(~outcome.measure) + 
+  theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size")
+@
+\caption{Mean of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
+\label{effect.samplesize.separated}
+\end{figure}
+
+A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
+This can again be done for the entire dataset, i.e.
+for all effect estimates and their ordering in time.
+It is important to scale the effect estimates here with respect to the estimates of the replication studies that are about the same subject, have the same outcome measure, etc.
+Also, only effect estimates that can be compared to other estimates before are included, i.e.
+only study results with one or more replica are included.
+Time needs to be scaled and normalized in order to compare multiple time-trends in effect size to each other and gain insights in the overall trend.
+This is done in Figure \ref{effects.over.time}.
+In blue, the fit of a linear regression is depicted with grey 95 \% confidence intervals.
+
+\begin{figure}
+<<echo=FALSE>>=
+data %>% filter(total1 + total2 > 10 & total1 + total2 < 100) %>% filter(!is.na(study.year)) %>% 
+  filter(outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio" | outcome.measure.new == "Mean Difference" |
+           outcome.measure.new == "Std. Mean Difference") %>% 
+  group_by(outcome.measure.new, comparison.nr, outcome.nr, subgroup.nr) %>% count() %>% filter(n > 1) %>% 
+  mutate(scaled.effect = scale(effect), scaled.time = scale(study.year)) %>% 
+  ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + 
+  geom_smooth(method = lm) + theme_bw() + 
+  labs(title = "Scaled and centered RR over time", subtitle = "Initial finding > 1") + ylab("Risk Ratio")  + ylab("Time")
+@
+\caption{Mean of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
+\label{effect.samplesize.separated}
+\end{figure}
+
+% It is also possible to look how the amount of meta-analysis with significant pooled effect size estimates changes over time, e.g.
 mean publication year (of studies included in the meta-analysis).
@@
 As Figure \ref{treatment.effect.significance.overtime} shows, the proportion of meta-analyses with significant treatment effect estimates stays roughly constant over time.
-
-\begin{figure}
-<<echo=FALSE>>=
-meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
-  ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-@
-\caption{Proportion of significant treatment effect estimates over time (mean publication year).}
-\label{effect.samplesize}
-\end{figure}
-
-A somewhat different question is how statistical power of studies changed over time.
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
+%   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef), stat(count))) + geom_density(na.rm = T, position = "fill") + 
+%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+% @
+% \caption{Proportion of significant treatment effect estimates over time (mean publication year).}
+% \label{effect.samplesize}
+% \end{figure}
+% 
+% A different question is how statistical power of studies changed over time.
 As an approximation, the total sample size of a study can be used.
@@
 Again, to reduce the effects of distortion due to random fluctuation, only the medians for the years 1980 to 2017 are used ($n$ > 50,000).
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data %>% distinct(study.name, .keep_all = T) %>%  filter(study.year < 2018 & study.year > 1980) %>% group_by(study.year) %>% 
+%   summarize(samplesize = median(total1 + total2, na.rm = T)) %>% 
+%   ggplot(aes(y = samplesize, x = study.year)) + geom_line()
+% @
+% \caption{Median sample size over time (years).}
+% \label{median.samplesize.overtime}
+% \end{figure}
 
-\begin{figure}
-<<echo=FALSE>>=
-data %>% distinct(study.name, .keep_all = T) %>%  filter(study.year < 2018 & study.year > 1980) %>% group_by(study.year) %>% 
-  summarize(samplesize = median(total1 + total2, na.rm = T)) %>% 
-  ggplot(aes(y = samplesize, x = study.year)) + geom_line()
-@
-\caption{Median sample size over time (years).}
-\label{median.samplesize.overtime}
-\end{figure}
+\subsection{Meta-analyses}
+
+Meta-analyses can be applied on the dataset given that there are studies that have one or more replica (i.e. same comparison type, outcome type and subgroup type).
 
@@
 trimfill.bin.median <- meta.bin %>% ungroup %>% summarise(median = median(missing.trim.bin)) %>% select(median)
-
-# meta.bin %>% ggplot(aes(x = missing.trim.bin)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
-#   theme_bw() + labs(title = "Fraction of Trimmed Comparisons (binary outcome)") + xlab("Fraction") + ylab("Frequency")
-# 
-# meta.cont %>% ggplot(aes(x = missing.missing.trim.cont)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
-#   theme_bw() + labs(title = "Fraction of Trimmed Comparisons (continuous outcome)") + xlab("Fraction") + ylab("Frequency")
-# 
-# meta.bin %>% ggplot(aes(x = missing.trim.bin, fill = factor(peter.test))) + geom_density(na.rm = T, position = "fill")
-# 
-# meta.bin %>% ggplot(aes(x = missing.trim.bin, fill = factor(harbord.test))) + geom_density(na.rm = T, position = "fill")
-# 
-# meta.cont %>% ggplot(aes(x = missing.missing.trim.cont, fill = factor(thomson.test))) + geom_density(na.rm = T, position = "fill")
-# 
-# #Time trends in significance of tests
-# meta.bin %>% filter(mean.publication.year < 2019 & mean.publication.year > 1960) %>% 
-#   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef.bin))) + geom_histogram()
-# 
-# meta.bin %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
-#   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef.bin))) + geom_density(na.rm = T, position = "fill")
-# 
-# meta.bin %>% filter(first.publication.year < 2013 & first.publication.year > 1990) %>% 
-#   ggplot(aes(x = first.publication.year, fill = factor(sig.fixef.bin))) + geom_density(na.rm = T, position = "fill")
-# 
-# meta.bin %>% filter(first.publication.year < 2013 & first.publication.year > 1990) %>% 
-#   ggplot(aes(x = first.publication.year, fill = factor(peter.test))) + geom_density(na.rm = T, position = "fill")
-# 
-# meta.bin %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
-#   ggplot(aes(x = mean.publication.year, fill = factor(rucker.test))) + geom_density(na.rm = T, position = "fill")
-# 
-# 
-# meta.cont %>% filter(mean.publication.year < 2019 & mean.publication.year > 1960) %>% 
-#   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef.cont))) + geom_histogram()
-# 
-# meta.cont %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
-#   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef.cont))) + geom_density(na.rm = T, position = "fill")
-# 
-# meta.cont %>% filter(first.publication.year < 2013 & first.publication.year > 1990) %>% 
-#   ggplot(aes(x = first.publication.year, fill = factor(sig.fixef.cont))) + geom_density(na.rm = T, position = "fill")
-# 
-# meta.cont %>% filter(first.publication.year < 2013 & first.publication.year > 1990) %>% 
-#   ggplot(aes(x = first.publication.year, fill = factor(thomson.test))) + geom_density(na.rm = T, position = "fill")
-# 
-# meta.cont %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
-#   ggplot(aes(x = mean.publication.year, fill = factor(egger.test))) + geom_density(na.rm = T, position = "fill")
-# 
-# 
-# data %>% filter(study.year < 2019 & study.year > 1980) %>% group_by(study.year) %>% summarize(samplesize = mean(total1 + total2, na.rm = T)) %>% 
-#   ggplot(aes(y = samplesize, x = study.year)) + geom_line()
 

### 2019-04-18 code/Metaly.R

@@ -1,0 +1,95 @@
+# #Transform Binary outcomes to odds ratios -> standardized mean difference -> correlation -> fisher scala correlation
+
+
+data <- data %>% mutate(odds.ratio = NA,
+               std.mean.d = NA,
+               correlation = NA,
+               fishersz = NA)
+
+data[data$events1 > 0 & data$events2 > 0,] <- data[data$events1 > 0 & data$events2 > 0,] %>%
+  mutate(odds.ratio = (events1/(total1 - events1)) / (events2/(total2 - events2)),
+         std.mean.d = log(odds.ratio) * (sqrt(3)/pi),
+         correlation = std.mean.d/sqrt((std.mean.d^2) + ((total1 + total2)^2)/(total2*total1)),
+         fishersz = 0.5 * log( (1 + correlation)/(1 - correlation) ), variance = 1/(total1 + total2 - 3))
+#
+# #Transform mean difference to standardized mean difference -> correlation -> fisher scala correlation
+data[data$outcome.measure == "Mean Difference", ] <- data %>% 
+  filter(outcome.measure == "Mean Difference") %>%
+  mutate(std.mean.d = effect/se,
+         correlation = std.mean.d/sqrt(std.mean.d^2 + ((total1 + total2)^2)/(total2*total1)),
+         fishersz = 0.5 * log( (1 + correlation)/(1 - correlation) ), 
+         variance = 1/(total1 + total2 - 3))
+#
+data[data$outcome.measure == "Std. Mean Difference", ] <- data %>% 
+  filter(outcome.measure == "Std. Mean Difference") %>%
+  mutate(std.mean.d = effect,
+         correlation = std.mean.d/sqrt(std.mean.d^2 + ((total1 + total2)^2)/(total2*total1)),
+         fishersz = 0.5 * log( (1 + correlation)/(1 - correlation) ), 
+         variance = 1/(total1 + total2 - 3))
+#
+data[data$outcome.measure == "Mean difference", ] <- data %>% 
+  filter(outcome.measure == "Mean difference") %>%
+  mutate(std.mean.d = effect, 
+         correlation = std.mean.d/sqrt(std.mean.d^2 + ((total1 + total2)^2)/(total2*total1)),
+         fishersz = 0.5 * log( (1 + correlation)/(1 - correlation) ), 
+         variance = 1/(total1 + total2 - 3))
+#
+data[data$outcome.measure == "mean difference", ] <- data %>% 
[…]

### 2019-04-18 code/PubBias.R

@@ -1,3 +1,4 @@
+rm(list = ls())
 PATH_HOME = path.expand("~") # user home
 PATH = file.path(PATH_HOME, 'Data/PubBias')
 PATH2 = file.path(PATH_HOME, 'PubBias')
@@ -11,16 +12,37 @@ file_results = "pb.RData"
 
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
 
-load(file.path(PATH_RESULTS, 'PubBias_results1.RData'))
-load(file.path(PATH_RESULTS, 'PubBias_results2.RData'))
-load(file.path(PATH_RESULTS, 'PubBias_results3.RData'))
-load(file.path(PATH_RESULTS, 'PubBias_results4.RData'))
-
 
 data = pb.readData(path = PATH_DATA, file = FILE)
 tmp = pb.clean(data)
 data = tmp[[1]]
 aliases = tmp[[2]]
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+  load(file.path(PATH_RESULTS, file.bin))
+} else { 
+  meta.bin <- meta.bin.complete(data, min.study.number = 10, sig.level = 0.05)
+  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+  load(file.path(PATH_RESULTS, file.bin))
+} else { 
+  meta.cont <- meta.cont.complete(data, min.study.number = 10, sig.level = 0.05)
+  save(meta.bin, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+
+save(meta.bin.complete(data[c(1:1000),], min.study.number = 10, sig.level = 0.05), file = file.path(PATH_RESULTS, file_fetch))
+load(file.path(PATH_RESULTS, file_fetch))
+
+pb.meta.binary(data[c(1:1000),], min.study.number = 10, sig.level = 0.05)
+pb.meta.continuous(data, min.study.number = 10, sig.level = 0.05)
+
+meta <- pb.meta.merge(meta.binary = meta.bin, meta.continuous = meta.cont)
+pb.meta.merge(meta.binary = meta.bin, meta.continous = meta.cont)
 
 require(biostatUZH)
 require(tidyverse)
@@ -29,278 +51,11 @@ require(metasens)
 require(gridExtra)
 require(xtable)
 
-########################################################################################################################################
[…]

### 2019-04-18 code/Unused.R

@@ -1,0 +1,695 @@
+
+
+pb.meta.binary = function(data, sig.level, min.study.number) {
+  file_fetch = 'pb.bin.RData'
+  
+  # do not run if file already exists, takes ~60 min 
+  if (file.exists(file.path(PATH_RESULTS, file_fetch))) {
+    load(file.path(PATH_RESULTS, file_fetch))
+  } else {
+    meta.bin <- data %>% filter(outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio" | outcome.measure.new == "Risk Difference") %>%  
+      filter(file.nr != 3014) %>% #file.nr 3014 gibt eine seltsame Fehlermeldung, muss ausgeschlossen werden
+      filter(events1 > 0 | events2 > 0) %>% #comparisons mit events  = 0 ausschliessen
+      filter(total1 - events1 > 0 | total2 - events2 > 0) %>% #comparisons mit events = total ausschliessen - vertraegt der alg. irgendwie nicht.
+      group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% #Die nachfolgenden Rechnungen werden jeweils fuer diese Gruppen gemacht.
+      mutate(n = n()) %>% filter(n > 9) %>% #Nur meta-analysen mit mehr als 9 comparisons behalten
+      mutate(study.year = ifelse(study.year < 2019, study.year, NA)) %>% 
+      mutate(study.year = ifelse(study.year > 1950, study.year, NA)) %>% 
+      summarize(doi = unique(doi),
+                comparison.name = unique(comparison.name),
+                outcome.name = unique(outcome.name),
+                sungroup.name = unique(subgroup.name),
+                outcome.measure.new = unique(outcome.measure.new),
+                n = n(), #Number of studies in meta-analysis
+                mean.samplesize = mean(total1 + total2, na.rm = T),
+                total.samplesize = sum(total1 + total2),
+                var.samplesize = var(total1 + total2, na.rm = T),
+                total.events = sum(events1 + events2),
+                mean.events = mean(events1 + events2),
+                mean.publication.year = mean(study.year, na.rm = TRUE),
+                first.publication.year = min(study.year, na.rm = T),
+                OR.fixef.bin = #Pooled odds ratio estimate of fixed effects meta-analysis model
+                  exp(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, sm= "OR")$TE.fixed),
+                pval.fixef.bin = #P-value
[…]

### 2019-04-18 code/explore.R

@@ -2,7 +2,7 @@
 # PATH = file.path(PATH_HOME, 'thesis/code')
 # source(file.path(PATH, 'prepare.R'))
 
-
+rm(list = ls())
 PATH_HOME = path.expand("~") # user home
 PATH = file.path(PATH_HOME, 'Data/PubBias')
 PATH2 = file.path(PATH_HOME, 'PubBias')
@@ -15,18 +15,25 @@ PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
 file_results = "pb.RData"
 
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
-load(file.path(PATH_RESULTS, 'PubBias_results3.RData'))
-load(file.path(PATH_RESULTS, 'PubBias_results4.RData'))
+
 
 data = pb.readData(path = PATH_DATA, file = FILE)
 tmp = pb.clean(data)
 data = tmp[[1]]
 aliases = tmp[[2]]
 
+meta.b <-  pb.meta.binary(data, min.study.number = 10, sig.level = 0.05)
+meta.cont <- pb.meta.continuous(data, min.study.number = 10, sig.level = 0.05)
+
+meta <- pb.meta.merge(meta.binary = meta.bin, meta.continuous = meta.cont)
+
 require(biostatUZH)
 require(tidyverse)
 require(meta)
 require(metasens)
+require(gridExtra)
+require(xtable)
+
 
 
 #Look at Migraine sympton relieve review

### 2019-04-21 report/chapter03.Rnw
metaly

@@
 <<echo=FALSE>>= 
-# PATH_HOME = path.expand("~") # user home
-# PATH = file.path(PATH_HOME, 'thesis/code')
-# source(file.path(PATH, 'prepare.R'))
-
 PATH_HOME = path.expand("~") # user home
@@
 
-load(file.path(PATH_RESULTS, 'PubBias_results1.RData'))
-load(file.path(PATH_RESULTS, 'PubBias_results2.RData'))
-load(file.path(PATH_RESULTS, 'PubBias_results3.RData'))
-load(file.path(PATH_RESULTS, 'PubBias_results4.RData'))
-
 data = pb.readData(path = PATH_DATA, file = FILE)
@@
 
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+  load(file.path(PATH_RESULTS, file.bin))
+} else { 
+  meta.bin <- meta.bin.complete(data, min.study.number = 10, sig.level = 0.05)
+  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+  load(file.path(PATH_RESULTS, file.cont))
+} else { 
+  meta.cont <- meta.cont.complete(data, min.study.number = 10, sig.level = 0.05)
+  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+meta <- pb.meta.merge(meta.bin, meta.cont)
+
+file.cont <- "mly.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+  load(file.path(PATH_RESULTS, file.cont))
+} else { 
+  data.cont <- mly.cont(data.ext, 0.05, min.study.number = 2)
+  save(data.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.bin <- "mly.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+  load(file.path(PATH_RESULTS, file.bin))
+} else { 
+  data.bin <- mly.bin(data.ext, 0.05, min.study.number = 2)
+  save(data.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+load(file.path(PATH_RESULTS, file = "mly.RData"))
+load(file.path(PATH_RESULTS, file = "data.processed.RData"))
+
 require(biostatUZH)
 require(tidyverse)
+require(meta)
+require(metasens)
 require(gridExtra)
-require(meta)
 require(xtable)
@@
 
-<<echo=FALSE>>=
-meta <- bind_rows(meta.bin, meta.cont)
-meta <- meta %>% mutate(sig.ranef = ifelse(!is.na(sig.ranef.bin), sig.ranef.bin, sig.ranef.cont),
-                        thomson.test = ifelse(!is.na(thomson.test), thomson.test, rucker.test),
-                        sig.fixef = ifelse(!is.na(sig.fixef.bin), sig.fixef.bin, sig.fixef.cont),
-                        sig.reg.random = ifelse(!is.na(sig.reg.random.bin), sig.reg.random.bin, sig.reg.random.cont),
-                        missing.trim = ifelse(!is.na(missing.trim.bin), missing.trim.bin, missing.trim.cont),
-                        pval.thomson = ifelse(!is.na(pval.rucker.bin), pval.rucker.bin, pval.thomson.cont))
+\section{Meta-analysis}
+It is possible to analyse all studies with one or more replica by meta-analysis.
+There are different meta-analyses that can be applied.
+First, it is investigated how well the significance of a effect size estimate of a study replicates in significance of the pooled effect size estimate of a meta-analysis.
+First, the amount of significant study effect estimates is shown over time.
+The fraction of significant effect size estimates on the $p$-value threshold of $0.05$ is only shown for times where a reasonbly large number of effect estimates is available in order to reduce random fluctuation ($n > 800$).
+Shown are p-values for significance tests where the outcome measure of the study was either a risk ratio, odds ratio, mean difference and standardized mean difference.
+Additionally, only study years between 1970 and 2017 have been included and the sample size for each arm of the study had to $> 12$.
+
+\begin{figure}
+<<>>=
+data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
+  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
 @
+\caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
+\label{study.significance.overtime}
+\end{figure}
 
-\section{Small Study Effects}
+\section{Small study effects}
 One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
@@
 
+########################################################################################################################################
+########################################################################################################################################
+
+change.ranef.bin <- meta.bin %>% ungroup() %>% select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>% mutate(sig.change = factor(sig.change)) %>% group_by(sig.change, correction.method) %>% count()
+
+p.change.ranef.bin <- meta.bin %>% ungroup() %>% 
+  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>%  
+  mutate(sig.change = factor(sig.change)) %>% 
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+ 
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  annotate("text", x = change.ranef.bin[change.ranef.bin$sig.change == 3,]$correction.method, y = 300, 
+         label = paste(change.ranef.bin[change.ranef.bin$sig.change == 3,]$n, "changed to nonsig."), 
+         color = "white")
+
+change.ranef.cont <- meta.cont %>% ungroup() %>% select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()
+
+p.change.ranef.cont <- meta.cont %>% ungroup() %>% 
+  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>%  
+  mutate(sig.change = factor(sig.change)) %>% 
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes") +
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  annotate("text", x = change.ranef.cont[change.ranef.cont$sig.change == 3,]$correction.method, y = 200, 
+         label = paste(change.ranef.cont[change.ranef.cont$sig.change == 3,]$n, "changed to nonsig."), 
+         color = "white")
+
+change.ranef <- meta %>% ungroup() %>% select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()
+
+p.ranef.change <- meta %>% ungroup() %>% 
+  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>%  
+  mutate(sig.change = factor(sig.change)) %>% 
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  annotate("text", x = change.ranef[change.ranef$sig.change == 3,]$correction.method, y = 500, 
+         label = paste(change.ranef[change.ranef$sig.change == 3,]$n, "changed to nonsig."), 
+         color = "white")
+
+#Fixed effects meta-analysis significance
+change.fixef.bin <- meta.bin %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()
+
+p.change.fixef.bin <- meta.bin %>% ungroup() %>% 
+  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>%  
+  mutate(sig.change = factor(sig.change)) %>% 
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+  
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  annotate("text", x = change.fixef.bin[change.fixef.bin$sig.change == 3,]$correction.method, y = 200, 
+         label = paste(change.fixef.bin[change.fixef.bin$sig.change == 3,]$n, "changed to nonsig."), 
+         color = "white")
+
+change.fixef.cont <- meta.cont %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()
+
+p.change.fixef.cont <- meta.cont %>% ungroup() %>% 
+  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>%  
+  mutate(sig.change = factor(sig.change)) %>% 
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes")+ 
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.nonsig", "unchanged.sig", "change.to.sig")) +
+  annotate("text", x = change.fixef.cont[change.fixef.cont$sig.change == 3,]$correction.method, y = 300, 
+         label = paste(change.fixef.cont[change.fixef.cont$sig.change == 3,]$n, "changed to nonsig."), 
+         color = "white")
+
+change.fixef <- meta %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()
+
+p.fixef.change <- meta %>% ungroup() %>% 
+  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>%  
+  mutate(sig.change = factor(sig.change)) %>% 
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.nonsig", "unchanged.sig", "change.to.sig")) +
+  annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 500, 
+         label = paste(change.fixef[change.fixef$sig.change == 3,]$n, "changed to nonsig."), 
+         color = "white")
+
+########################################################################################################################################
+########################################################################################################################################
+
+p.missing.copas <- meta %>% ggplot(aes(x = missing.copas/n)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20)
+p.missing.trim <- meta %>% ggplot(aes(x = missing.trim)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20)
 @
 
-There are tests that can be applied to find out if reporting bias is present in the meta analysis.
+\subsubsection{Small Study Effect Tests}
+There are tests that can be applied to find out if small study effects are present in the meta analysis.
 For the precise description, see the methods section.
@@
 Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
+Three of them will be applied to the meta-analyses shown previously that have ten or more study results and are therefore eligible for testing for publication bias.
+
+\vspace{0mm}
+The extent to what the results of the meta-analysis results are changed can be investigated.
+Because statistical significance is often used to decide if there is a treatment effect, a non-significant corrected effect size estimate can indicate that an observed treatment effect has been accepted because of small study effects.
+Therefore, the cases have been counted in which
+\begin{enumerate}
+\item Significance or non-significance of pooled estimate of meta-analysis did not change after correction for small study effects.
+\item Significance of pooled estimate of meta-analysis did change to non-significance after correction for small study effects.
+\item Non-significance of pooled estimate of meta-analysis did change to significance after correction for small study effects.
+\end{enumerate}
+
+The results of this can be seen in Figure \ref{significance.change.fixed} for all three methods, comparing the significance of the corrected pooled effect size estimate with the significance of the pooled effect size estimate of the fixed effects meta-analysis.
+The same for significance of random effects meta-analysis is shown in Figure \ref{significance.change.random}.
+The significance threshold was chosen such that the $p$-value had to be $< 0.05$ for rejection of the null hypothesis of no treatment effect.
+The correction methods were trim-and-fill, copas selection model and regression with random effects and shrinkage of within-study-variance methods.
+More details to the applied correction methods and their application are in the methods section \ref{methods}.
+Notably, the correction methods has been applied to all meta-analyses, thus also for such that had no significant small study effect test result.
+
+\begin{figure}
+<<echo=FALSE>>=
+plot(p.fixef.change)
+@
+\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction.}
+\label{significance.change.fixed}
+\end{figure}
+
+\begin{figure}
+<<echo=FALSE>>=
+plot(p.ranef.change)
+@
+\caption{Change in signficance of random effects meta-analysis pooled estimate after correction.}
+\label{significance.change.random}
+\end{figure}
+
+Since it has been previously seen in Figure \ref{test.results} that the results of small study effects vary considerably between continuous outcomes, the results in significance change from fixed effects meta-analysis can be seen separately in Figure \ref{significance.change.fixed.sep} for continuous and binary outcomes.
+The change in significance from random effects meta-analysis to significance of corrected estimate can be seen in Figure \ref{significance.change.fixed.sep}
+
+\begin{figure}
+<<echo=FALSE>>=
+grid.arrange(p.fixef.change.bin, p.fixef.change.cont, ncol = 2)
+@
+\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
+\label{significance.change.fixed.sep}
+\end{figure}
+
+\begin{figure}
+<<echo=FALSE>>=
+grid.arrange(p.ranef.change.bin, p.ranef.change.cont, ncol = 2)
+@
+\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
+\label{significance.change.random}
+\end{figure}
+
+Similarly, the number of missing studies per meta-analysis, i.e.
+those which have not been included because of small study effects, are estimated by the copas and trim-and-fill method and their empirical distribution is shown in histograms in Figure \ref{missing.studies.distribution}.
+For visualisation, the fraction of unpublished studies from the total fraction of available studies is shown.
+
+\begin{figure}
+<<echo=FALSE>>=
+grid.arrange(p.missing.copas, p.missing.trim, ncol = 1)
+@
+\caption{Fraction of missing studies estimated of the number of total studies included in the meta-analysis for copas selection and trim-and-fill method.}
+\label{missing.studies.distribution}
+\end{figure}
 

### 2019-04-21 code/PubBias.R

@@ -28,21 +28,36 @@ if (file.exists(file.path(PATH_RESULTS, file.bin))) {
 
 file.cont <- "pb.cont.RData"
 if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-  load(file.path(PATH_RESULTS, file.bin))
+  load(file.path(PATH_RESULTS, file.cont))
 } else { 
   meta.cont <- meta.cont.complete(data, min.study.number = 10, sig.level = 0.05)
-  save(meta.bin, file =  file.path(PATH_RESULTS, file.cont))
+  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
 }
 
+meta.cont <- meta.cont %>% mutate(sig.change.ranef.reg = sig.change(sig.before = sig.ranef.cont, sig.after =  sig.reg.ranef.cont),
+                                            sig.change.ranef.copas = sig.change(sig.before = sig.ranef.cont, sig.after =  sig.copas.cont),
+                                            sig.change.ranef.trimfill = sig.change(sig.before = sig.ranef.cont, sig.after =  sig.trimfill.cont),
+                                            sig.change.fixef.reg = sig.change(sig.before = sig.fixef.cont, sig.after =  sig.reg.ranef.cont),
+                                            sig.change.fixef.copas = sig.change(sig.before = sig.fixef.cont, sig.after =  sig.copas.cont),
+                                            sig.change.fixef.trimfill = sig.change(sig.before = sig.fixef.cont, sig.after =  sig.trimfill.cont))
 
-save(meta.bin.complete(data[c(1:1000),], min.study.number = 10, sig.level = 0.05), file = file.path(PATH_RESULTS, file_fetch))
-load(file.path(PATH_RESULTS, file_fetch))
+meta.bin <- meta.bin %>% mutate(sig.copas.bin = ifelse(pval.copas.bin > 0.05, 0, 1),
+  sig.change.ranef.reg = sig.change(sig.before = sig.ranef.bin, sig.after =  sig.reg.ranef.bin), 
+                                                sig.change.ranef.copas = sig.change(sig.before = sig.ranef.bin, sig.after =  sig.copas.bin),
+                                                sig.change.ranef.trimfill = sig.change(sig.before = sig.ranef.bin, sig.after =  sig.trimfill.bin),
[…]

### 2019-04-23 report/MSc_Report.tex
Meta analysis finish

@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Apr 16 13:54:44 2019
+% Tue Apr 23 12:23:04 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Apr 16 13:54:49 2019
+% Tue Apr 23 12:23:09 2019
 \begin{table}[ht]
@@
 
-\section{Small Study Effects}
+\section{Meta-analysis}
+The data at hand is composed of over 400,000 comparisons with balanced sample size $n > 24$, which has been chosen as a threshold to assess the significance of treatment effect.
+The significance of the p-values of treatment effect estimates was calculated for all comparisons in the dataset with acceptable sample size and outcome measures as odds ratios, risk ratios, risk differences and mean and standardized mean differences.
+This led to somewhat more than 400,000 significance test results.
+Since most of the times, the study publication year is available, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.The $p$-value was chosen to be $0.05$  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n > 800$).
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
+
+}
+
+\end{knitrout}
+\caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
+\label{study.significance.overtime}
+\end{figure}
+
+It is possible to analyse all studies with one or more replica by meta-analysis.
+There are different meta-analys methods that can be applied.
+While fixed effects meta-analysis pools the estimates and their variance, random effects meta-analysis additionally estimates the between study variances and adds this variance to the pooled within-study variances when assessing the uncertainity of the pooled effect estimate.
+The Hartung and Knapp adjustment of p-values and confidence intervals for random effects meta-analysis is more conservative than random-effects meta-analysis and will yieild less significant results than the latter.
+
+\vspace{0mm}
+In the following, the study results are combined with the results of their corresponding meta-analysis.
+Thus, every study that has one or more replicate was analysed by meta-analysis.
+In the following, the significance of the study, the primary significance, is compared with the significance of the meta-analysis or secondary significance.
+
+\vspace{0mm}
+In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
+The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure.
+One can see the overall fraction of rejected null-hypotheses of no treatment effect.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
+
+}
+
+\end{knitrout}
+\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
+by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+\label{primary.secondary.significance}
+\end{figure}
+
+One can visualise the fraction of studies with significant treatment effect separately for studies with significant primary treatment effect, i.e.
+non-pooled effect, and non-significant primary treatment effect.
+This can be seen in Figure \ref{primary.secondary.significance.sep.sig}.
+One can see that primary significance and non-significance is often overruled when performing a meta-analysis.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
+
+}
+
+\end{knitrout}
+\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
+The fractions have been calculated
+by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+\label{primary.secondary.significance}
+\end{figure}
+
+The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
+Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
+The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested.
+This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
+
+}
+
+\end{knitrout}
+\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
+The fractions have been calculated
+by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+\label{primary.secondary.significance.sep.sig}
+\end{figure}
+
+\section{Small study effects}
 One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
@@
 \vspace{0mm}
-To provide an overview over the issue, first it is shown how mean absolute effect size decreases with increasing sample size of the comparisons in Figure \ref{effect.samplesize}.
-The decrease is particularly substantive from very small trials ($n$ = 5) to medium sample size ($n$ = 100), afterwards the trend is less pronounced.
-With increasing sample size, there are fewer results, therefore, the variation between means increases.
-All effects are normalized by subtracting the mean effect size of the dataset and dividng through the standard deviation.
-Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all sample sizes.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
-
-}
-
-\end{knitrout}
-\caption{Mean of the absolute of the normalized effect size plotted against the total sample size.}
+To provide an overview over the issue, first it is shown how median absolute effect size decreases with increasing sample size of the comparisons in Figure \ref{effect.samplesize}.
+In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.
+
+\vspace{0mm}
+A clear trend of decrease of absolute effect size with increasing sample size (i.e.
+smaller variance) is visible.
+It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off.
+With increasing sample size, there are fewer results, therefore, the variation between medians increases.
+All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation.
+Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
+
+}
+
+\end{knitrout}
+\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
 \label{effect.samplesize}
@@
 
-It is also possible to look how the amount of meta-analysis with significant pooled effect size estimates changes over time, e.g.
+The median absolute normalized effect size can be visualized for the different outcome measures separately.
+Then it is well visible in Figure \ref{effect.samplesize.separated} that the trend of effect size decrease holds in particualar for risk and odds ratios, while it is way more stable for mean differences and standardized mean differences.
+Instead of normalizing the effects (i.e.
+subtracting mean and dividing through the standard deviation) for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
+
+}
+
+\end{knitrout}
+\caption{Median of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
+\label{effect.samplesize.separated}
+\end{figure}
+
+A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
+This can again be done for the entire dataset, i.e.
+for all effect estimates and their ordering in time.
+It is important to scale the effect estimates here with respect to the estimates of the replication studies that are about the same subject, have the same outcome measure, etc.
+Also, only effect estimates that can be compared to other estimates before are included, i.e.
+only study results with one or more replica are included.
+Time needs to be scaled and normalized in order to compare multiple time-trends in effect size to each other and gain insights in the overall trend.
+This is done in Figure \ref{effects.overtime.separated}, separared for odds rati, risk ratio, and mean and standardized difference outcome measures.
+In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 9701 rows containing non-finite values (stat\_smooth).}}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 9701 rows containing missing values (geom\_point).}}\end{kframe}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-24-1}
+
+}
+
+\end{knitrout}
+\caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
+\label{effects.overtime.separated}
+\end{figure}
+
+% It is also possible to look how the amount of meta-analysis with significant pooled effect size estimates changes over time, e.g.
 mean publication year (of studies included in the meta-analysis).
@@
 As Figure \ref{treatment.effect.significance.overtime} shows, the proportion of meta-analyses with significant treatment effect estimates stays roughly constant over time.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion of significant treatment effect estimates over time (mean publication year).}
-\label{effect.samplesize}
-\end{figure}
-
-A somewhat different question is how statistical power of studies changed over time.
-As an approximation, the total sample size of a study can be used.
-Figure \ref{median.samplesize.overtime} shows the median sample size of all studies of a given year.
-Again, to reduce the effects of distortion due to random fluctuation, only the medians for the years 1980 to 2017 are used ($n$ > 50,000).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
-
-}
-
-\end{knitrout}
-\caption{Median sample size over time (years).}
-\label{median.samplesize.overtime}
-\end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
+%   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef), stat(count))) + geom_density(na.rm = T, position = "fill") + 
+%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+% @
+% \caption{Proportion of significant treatment effect estimates over time (mean publication year).}
+% \label{effect.samplesize}
+% \end{figure}
+%
 
@@
 
-There are tests that can be applied to find out if reporting bias is present in the meta analysis.
+There are tests that can be applied to find out if small study effects are present in the meta analysis.
 For the precise description, see the methods section.
@@
 In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = 1383)
-The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3350).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
+The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3442).
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-26-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-24-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-25-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-29-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-26-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-30-1}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Apr 16 13:55:01 2019
+% Tue Apr 23 12:24:31 2019
 \begin{table}[ht]
@@
   \hline
-egger.schwarzer & 0.88 & 0.38 \\ 
-  egger.peter & 0.89 & 0.52 \\ 
-  egger.rucker & 0.89 & 0.48 \\ 
-  egger.harbord & 0.94 & 0.76 \\ 
+egger.schwarzer & 0.87 & 0.39 \\ 
+  egger.peter & 0.89 & 0.51 \\ 
+  egger.rucker & 0.88 & 0.48 \\ 
+  egger.harbord & 0.93 & 0.76 \\ 
   schwarzer.peter & 0.89 & 0.29 \\ 
@@
   rucker.peter & 0.92 & 0.67 \\ 
-  harbord.peter & 0.91 & 0.53 \\ 
+  harbord.peter & 0.91 & 0.52 \\ 
    \hline
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-29-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-33-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-30-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-34-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-31-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-35-1}
 
@@
 Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
+Three of them will be applied to the meta-analyses shown previously that have ten or more study results and are therefore eligible for testing for publication bias.
+
+\vspace{0mm}
+The extent to what the results of the meta-analysis results are changed can be investigated.
+Because statistical significance is often used to decide if there is a treatment effect, a non-significant corrected effect size estimate can indicate that an observed treatment effect has been accepted because of small study effects.
+Therefore, the cases have been counted in which
+\begin{enumerate}
+\item Significance or non-significance of pooled estimate of meta-analysis did not change after correction for small study effects.
+\item Significance of pooled estimate of meta-analysis did change to non-significance after correction for small study effects.
+\item Non-significance of pooled estimate of meta-analysis did change to significance after correction for small study effects.
+\end{enumerate}
+
+The results of this can be seen in Figure \ref{significance.change.fixed} for all three methods, comparing the significance of the corrected pooled effect size estimate with the significance of the pooled effect size estimate of the fixed effects meta-analysis.
+The same for significance of random effects meta-analysis is shown in Figure \ref{significance.change.random}.
+The significance threshold was chosen such that the $p$-value had to be $< 0.05$ for rejection of the null hypothesis of no treatment effect.
+The correction methods were trim-and-fill, copas selection model and regression with random effects and shrinkage of within-study-variance methods.
+More details to the applied correction methods and their application are in the methods section \ref{methods}.
+Notably, the correction methods has been applied to all meta-analyses, thus also for such that had no significant small study effect test result.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-36-1}
+
+}
+
+\end{knitrout}
+\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction.}
+\label{significance.change.fixed}
+\end{figure}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-37-1}
+
+}
+
+\end{knitrout}
+\caption{Change in signficance of random effects meta-analysis pooled estimate after correction.}
+\label{significance.change.random}
+\end{figure}
+
+Since it has been previously seen in Figure \ref{test.results} that the results of small study effects vary considerably between continuous outcomes, the results in significance change from fixed effects meta-analysis can be seen separately in Figure \ref{significance.change.fixed.sep} for continuous and binary outcomes.
+The change in significance from random effects meta-analysis to significance of corrected estimate can be seen in Figure \ref{significance.change.fixed.sep}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-38-1}
+
+}
+
+\end{knitrout}
+\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
+\label{significance.change.fixed.sep}
+\end{figure}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-39-1}
+
+}
+
+\end{knitrout}
+\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
+\label{significance.change.random}
+\end{figure}
+
+Similarly, the number of missing studies per meta-analysis, i.e.
+those which have not been included because of small study effects, are estimated by the copas and trim-and-fill method and their empirical distribution is shown in histograms in Figure \ref{missing.studies.distribution}.
+For visualisation, the fraction of unpublished studies from the total fraction of available studies is shown.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-40-1}
+
+}
+
+\end{knitrout}
+\caption{Fraction of missing studies estimated of the number of total studies included in the meta-analysis for copas selection and trim-and-fill method.}
+\label{missing.studies.distribution}
+\end{figure}
 

### 2019-04-23 report/chapter02.Rnw
Meta analysis finish

@@
                echo=TRUE, message=FALSE,
-               fig.width=8.1, fig.height=3,
+               fig.width=8, fig.height=3,
                out.width='\\textwidth-3cm',

### 2019-04-23 report/chapter03.Rnw
Meta analysis finish

@@
                echo=TRUE, message=FALSE,
-               fig.width=8.1, fig.height=3.5,
+               fig.width=8, fig.height=3.7,
                out.width='\\textwidth-3cm',
@@
 
+<<echo = FALSE, warning =FALSE>>=
+#Merge comparisons with meta-analysis result:
+mly.tomerge <- mly %>% select(meta.id, sig.Q, n.sig.type, n.sig.fishersz, sig.fixef, sig.ranef, sig.ranef.hkn)
+
+data.mly <- merge(x = data.ext, y = mly.tomerge, by = c("meta.id")) #ideally, 278626 comparisons ( = sum(mly$n)), 
+# but 300831 (18261 have smaller sample size than mly, but same meta.id)
+
+data.mly <- data.mly %>% filter(total1 > 11 & total2 > 11) #Now 282550
+
+sig.meta.c <- data.mly %>% select(sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
+  gather(key = "meta.analysis.method", value = "sig.meta.analysis") %>% mutate(sig.meta.analysis = factor(sig.meta.analysis))
+
+sig.meta.count.c <- sig.meta.c %>% 
+  group_by(sig.meta.analysis, meta.analysis.method) %>% count()
+
+sig.meta.c <- sig.meta.c %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
+  geom_bar() + coord_flip() +
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("meta.nonsig", "meta.sig")) +
+  annotate("text", x = sig.meta.count.c[sig.meta.count.c$sig.meta.analysis == 0,]$meta.analysis.method, y = 100000, 
+           label = paste(sig.meta.count.c[sig.meta.count.c$sig.meta.analysis == 0,]$n, "nonsig."), 
+           color = "white")
+
+#Change in significance after meta-analysis, separated by significant effect size estimate
+sig.meta <- data.mly %>% 
+  select(meta.id, study.id, sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
+  gather(key = "meta.analysis.method", value = "sig.meta.analysis", sig.fixef:sig.ranef.hkn) %>% mutate(sig.meta.analysis = factor(sig.meta.analysis))
+
+# duplicate.studies <- data.mly %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr, study.name) %>% 
+#   count() %>% filter(n > 1) #Merging is not possible for these since studies bear multiple results, but are not distinguishable and are multiplied while merging.
+
+sig.meta.plot <- merge(y = select(data.ext, meta.id, study.id, sig.type), 
+                       x = sig.meta, by = c("meta.id", "study.id")) %>% 
+  mutate(sig.type = factor(sig.type))
+
+sig.meta.count <- sig.meta.plot %>% 
+  group_by(sig.meta.analysis, meta.analysis.method, sig.type) %>% count()
+
+sig.meta.plot1 <- sig.meta.plot %>% filter(sig.type == 1) %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
+  geom_bar() + coord_flip() + ggtitle("Significant studies") +
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("non-significant", "significant")) +
+  annotate("text", x = sig.meta.count[which(sig.meta.count$sig.type == 1)[1:3],]$meta.analysis.method, y = 20000, 
+           label = paste(sig.meta.count[which(sig.meta.count$sig.type == 1)[1:3],]$n, "changed to nonsig."), 
+           color = "white")
+
+nonsig.meta.plot <- sig.meta.plot %>% filter(sig.type == 0) %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
+  geom_bar() + coord_flip() + ggtitle("Non-significant studies") +
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("non-significant", "significant")) +
+  annotate("text", x = sig.meta.count[which(sig.meta.count$sig.type == 0)[4:6],]$meta.analysis.method, y = 100000, 
+           label = paste(sig.meta.count[which(sig.meta.count$sig.type == 0)[4:6],]$n, "changed to sig."), 
+           color = "white")
+
+#Change in significance after meta-analysis, separated by significant heterogeneity
+sig.meta.Q <- data.mly %>% 
+  select(meta.id, sig.Q, sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
+  gather(key = "meta.analysis.method", value = "sig.meta.analysis", sig.fixef:sig.ranef.hkn) %>% 
+  mutate(sig.meta.analysis = factor(sig.meta.analysis))
+
+sig.meta.count.Q <- sig.meta.Q %>% 
+  group_by(sig.meta.analysis, meta.analysis.method, sig.Q) %>% count()
+
+sig.meta.Q1 <- sig.meta.Q %>% filter(sig.Q == 1) %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
+  geom_bar() + coord_flip() + ggtitle("Significant heterogeneity Q studies") +
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("non-significant", "significant")) +
+  annotate("text", x = sig.meta.count.Q[which(sig.meta.count.Q$sig.Q == 1)[1:3],]$meta.analysis.method, y = 20000, 
+           label = paste(sig.meta.count.Q[which(sig.meta.count.Q$sig.Q == 1)[1:3],]$n, "nonsig."), 
+           color = "white")
+
+nonsig.meta.Q <- sig.meta.Q %>% filter(sig.Q == 0) %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
+  geom_bar() + coord_flip() + ggtitle("Non-significant heterogeneity Q studies") +
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("non-significant", "significant")) +
+  annotate("text", x = sig.meta.count.Q[which(sig.meta.count.Q$sig.Q == 0)[1:3],]$meta.analysis.method, y = 100000, 
+           label = paste(sig.meta.count.Q[which(sig.meta.count.Q$sig.Q == 0)[1:3],]$n, "nonsig."), 
+           color = "white")
+
+@
+
 \section{Meta-analysis}
-It is possible to analyse all studies with one or more replica by meta-analysis.
-There are different meta-analyses that can be applied.
-First, it is investigated how well the significance of a effect size estimate of a study replicates in significance of the pooled effect size estimate of a meta-analysis.
-First, the amount of significant study effect estimates is shown over time.
-The fraction of significant effect size estimates on the $p$-value threshold of $0.05$ is only shown for times where a reasonbly large number of effect estimates is available in order to reduce random fluctuation ($n > 800$).
-Shown are p-values for significance tests where the outcome measure of the study was either a risk ratio, odds ratio, mean difference and standardized mean difference.
-Additionally, only study years between 1970 and 2017 have been included and the sample size for each arm of the study had to $> 12$.
+The data at hand is composed of over 400,000 comparisons with balanced sample size $n > 24$, which has been chosen as a threshold to assess the significance of treatment effect.
+The significance of the p-values of treatment effect estimates was calculated for all comparisons in the dataset with acceptable sample size and outcome measures as odds ratios, risk ratios, risk differences and mean and standardized mean differences.
+This led to somewhat more than 400,000 significance test results.
+Since most of the times, the study publication year is available, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.The $p$-value was chosen to be $0.05$  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n > 800$).
 
 \begin{figure}
-<<>>=
+<<echo=FALSE, warning=FALSE>>=
 data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
@@
 \label{study.significance.overtime}
+\end{figure}
+
+It is possible to analyse all studies with one or more replica by meta-analysis.
+There are different meta-analys methods that can be applied.
+While fixed effects meta-analysis pools the estimates and their variance, random effects meta-analysis additionally estimates the between study variances and adds this variance to the pooled within-study variances when assessing the uncertainity of the pooled effect estimate.
+The Hartung and Knapp adjustment of p-values and confidence intervals for random effects meta-analysis is more conservative than random-effects meta-analysis and will yieild less significant results than the latter.
+
+\vspace{0mm}
+In the following, the study results are combined with the results of their corresponding meta-analysis.
+Thus, every study that has one or more replicate was analysed by meta-analysis.
+In the following, the significance of the study, the primary significance, is compared with the significance of the meta-analysis or secondary significance.
+
+\vspace{0mm}
+In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
+The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure.
+One can see the overall fraction of rejected null-hypotheses of no treatment effect.
+
+\begin{figure}
+<<echo=FALSE, warning=FALSE>>=
+plot(sig.meta.c)
+@
+\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
+by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+\label{primary.secondary.significance}
+\end{figure}
+
+One can visualise the fraction of studies with significant treatment effect separately for studies with significant primary treatment effect, i.e.
+non-pooled effect, and non-significant primary treatment effect.
+This can be seen in Figure \ref{primary.secondary.significance.sep.sig}.
+One can see that primary significance and non-significance is often overruled when performing a meta-analysis.
+
+\begin{figure}
+<<echo=FALSE, warning=FALSE>>=
+grid.arrange(sig.meta.plot1, nonsig.meta.plot, ncol= 1)
+@
+\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
+The fractions have been calculated
+by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+\label{primary.secondary.significance}
+\end{figure}
+
+The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
+Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
+The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested.
+This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
+
+\begin{figure}
+<<echo=FALSE, warning=FALSE>>=
+grid.arrange(sig.meta.Q1, nonsig.meta.Q, ncol= 1)
+@
+\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
+The fractions have been calculated
+by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+\label{primary.secondary.significance.sep.sig}
 \end{figure}
@@
 @
-\caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
+\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
 \label{effect.samplesize}
@@
   summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
-  ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point() + facet_wrap(~outcome.measure) + 
+  ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point() + facet_wrap(~outcome.measure.new) + 
   theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size")
 @
-\caption{Mean of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
+\caption{Median of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
 \label{effect.samplesize.separated}
@@
 Time needs to be scaled and normalized in order to compare multiple time-trends in effect size to each other and gain insights in the overall trend.
-This is done in Figure \ref{effects.over.time}.
-In blue, the fit of a linear regression is depicted with grey 95 \% confidence intervals.
+This is done in Figure \ref{effects.overtime.separated}, separared for odds rati, risk ratio, and mean and standardized difference outcome measures.
+In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
 
@@
 <<echo=FALSE>>=
-data %>% filter(total1 + total2 > 10 & total1 + total2 < 100) %>% filter(!is.na(study.year)) %>% 
-  filter(outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio" | outcome.measure.new == "Mean Difference" |
-           outcome.measure.new == "Std. Mean Difference") %>% 
-  group_by(outcome.measure.new, comparison.nr, outcome.nr, subgroup.nr) %>% count() %>% filter(n > 1) %>% 
-  mutate(scaled.effect = scale(effect), scaled.time = scale(study.year)) %>% 
-  ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + 
-  geom_smooth(method = lm) + theme_bw() + 
-  labs(title = "Scaled and centered RR over time", subtitle = "Initial finding > 1") + ylab("Risk Ratio")  + ylab("Time")
+data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
+                outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
+  filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
+  group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
+  mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
+  ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
+  geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
 @
-\caption{Mean of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
-\label{effect.samplesize.separated}
+\caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
+\label{effects.overtime.separated}
 \end{figure}
@@
 %
-% A different question is how statistical power of studies changed over time.
-As an approximation, the total sample size of a study can be used.
-Figure \ref{median.samplesize.overtime} shows the median sample size of all studies of a given year.
-Again, to reduce the effects of distortion due to random fluctuation, only the medians for the years 1980 to 2017 are used ($n$ > 50,000).
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% distinct(study.name, .keep_all = T) %>%  filter(study.year < 2018 & study.year > 1980) %>% group_by(study.year) %>% 
-%   summarize(samplesize = median(total1 + total2, na.rm = T)) %>% 
-%   ggplot(aes(y = samplesize, x = study.year)) + geom_line()
-% @
-% \caption{Median sample size over time (years).}
-% \label{median.samplesize.overtime}
-% \end{figure}
-
-\subsection{Meta-analyses}
-
-Meta-analyses can be applied on the dataset given that there are studies that have one or more replica (i.e. same comparison type, outcome type and subgroup type).
 
@@
   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
-  annotate("text", x = change.ranef.bin[change.ranef.bin$sig.change == 3,]$correction.method, y = 300, 
+  annotate("text", x = change.ranef.bin[change.ranef.bin$sig.change == 3,]$correction.method, y = 1000, 
          label = paste(change.ranef.bin[change.ranef.bin$sig.change == 3,]$n, "changed to nonsig."), 
@@
   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
-  annotate("text", x = change.ranef.cont[change.ranef.cont$sig.change == 3,]$correction.method, y = 200, 
+  annotate("text", x = change.ranef.cont[change.ranef.cont$sig.change == 3,]$correction.method, y = 500, 
          label = paste(change.ranef.cont[change.ranef.cont$sig.change == 3,]$n, "changed to nonsig."), 
@@
   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
-  annotate("text", x = change.ranef[change.ranef$sig.change == 3,]$correction.method, y = 500, 
+  annotate("text", x = change.ranef[change.ranef$sig.change == 3,]$correction.method, y = 1500, 
          label = paste(change.ranef[change.ranef$sig.change == 3,]$n, "changed to nonsig."), 
@@
   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
-  annotate("text", x = change.fixef.bin[change.fixef.bin$sig.change == 3,]$correction.method, y = 200, 
+  annotate("text", x = change.fixef.bin[change.fixef.bin$sig.change == 3,]$correction.method, y = 800, 
          label = paste(change.fixef.bin[change.fixef.bin$sig.change == 3,]$n, "changed to nonsig."), 
@@
   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.nonsig", "unchanged.sig", "change.to.sig")) +
-  annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 500, 
+  annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 1500, 
          label = paste(change.fixef[change.fixef$sig.change == 3,]$n, "changed to nonsig."), 
@@
 
-\subsubsection{Small Study Effect Tests}
 There are tests that can be applied to find out if small study effects are present in the meta analysis.
@@
 \begin{figure}
-<<echo=FALSE>>=
+<<echo=FALSE, warning=FALSE>>=
 plot(p.cont)
@@
 \begin{figure}
-<<echo=FALSE>>=
+<<echo=FALSE, warning=FALSE>>=
 plot(p.bin)
@@
 \begin{figure}
-<<echo=FALSE>>=
+<<echo=FALSE, warning=FALSE>>=
 grid.arrange(p3, p4, ncol = 2)
@@
 \begin{figure}
-<<echo=FALSE>>=
+<<echo=FALSE, warning=FALSE>>=
 grid.arrange(p1, p2, ncol = 2)
@@
 \begin{figure}
-<<echo=FALSE>>=
+<<echo=FALSE, warning=FALSE>>=
 meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
@@
 
-<<results = 'asis', echo = FALSE, warnings = FALSE>>=
+<<results = 'asis', echo = FALSE, warning = FALSE>>=
 print(xtable(x = t(binary.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)", label = "agreement.bin",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
@@
 
-<<results = 'asis', echo = FALSE, warnings = FALSE>>=
+<<results = 'asis', echo = FALSE, warning = FALSE>>=
 print(xtable(x = t(cont.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)", label = "agreement.cont",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
@@
 \begin{figure}
-<<echo=FALSE>>=
+<<echo=FALSE, warning=FALSE>>=
 meta %>% filter(n < 40) %>% ggplot(aes(stat(count), x = n, fill = factor(thomson.test))) + 
@@
 \begin{figure}
-<<echo=FALSE>>=
+<<echo=FALSE, warning=FALSE>>=
 meta.bin %>% filter(missing.trim.bin < 0.5) %>% 
@@
 \begin{figure}
-<<echo=FALSE>>=
+<<echo=FALSE, warning=FALSE>>=
 meta.cont %>% filter(missing.trim.cont < 0.5) %>% 
@@
 \begin{figure}
-<<echo=FALSE>>=
+<<echo=FALSE, warning=FALSE>>=
 plot(p.fixef.change)
@@
 \begin{figure}
-<<echo=FALSE>>=
+<<echo=FALSE, warning=FALSE>>=
 plot(p.ranef.change)
@@
 \begin{figure}
-<<echo=FALSE>>=
-grid.arrange(p.fixef.change.bin, p.fixef.change.cont, ncol = 2)
+<<echo=FALSE, warning=FALSE>>=
+grid.arrange(p.change.fixef.bin, p.change.fixef.cont, ncol = 1)
 @
@@
 \begin{figure}
-<<echo=FALSE>>=
-grid.arrange(p.ranef.change.bin, p.ranef.change.cont, ncol = 2)
+<<echo=FALSE, warning=FALSE>>=
+grid.arrange(p.change.ranef.bin, p.change.ranef.cont, ncol = 1)
 @
@@
 \begin{figure}
-<<echo=FALSE>>=
+<<echo=FALSE, warning=FALSE>>=
 grid.arrange(p.missing.copas, p.missing.trim, ncol = 1)

### 2019-04-24 report/chapter03.Rnw
test

@@
                echo=TRUE, message=FALSE,
-               fig.width=8, fig.height=3.7,
+               fig.width=8.1, fig.height=3.7,
                out.width='\\textwidth-3cm',
@@
 
-sig.meta.c <- data.mly %>% select(sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
+sig.meta.c <- data.mly %>% select(sig.type, sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
   gather(key = "meta.analysis.method", value = "sig.meta.analysis") %>% mutate(sig.meta.analysis = factor(sig.meta.analysis))

### 2019-04-24 code/Metaly.R

@@ -228,7 +228,6 @@ mly.bin = function(data, sig.level, min.study.number) {
     mutate(study.year = ifelse(study.year < 2019, study.year, NA)) %>% 
     mutate(study.year = ifelse(study.year > 1920, study.year, NA)) %>% 
     summarize(doi = unique(doi),
-              meta.id = unique(meta.id),
               n = n(),
               #outcome.type = unique(outcome.type),
               comparison.name = unique(comparison.name),
@@ -304,7 +303,6 @@ mly.cont = function(data, sig.level, min.study.number) {
     mutate(study.year = ifelse(study.year < 2019, study.year, NA)) %>% 
     mutate(study.year = ifelse(study.year > 1920, study.year, NA)) %>% 
     summarize(doi = unique(doi),
-              meta.id = unique(meta.id),
               #outcome.type = unique(outcome.type),
               comparison.name = unique(comparison.name),
               outcome.name = unique(outcome.name),
@@ -373,12 +371,9 @@ mly.merge <- function(mly.result.bin, mly.result.cont){
                                       pval.ranef = ifelse(!is.na(pval.ranef.bin), pval.ranef.bin, pval.ranef.cont),
                                       sig.fixef = ifelse(!is.na(sig.fixef.bin), sig.fixef.bin, sig.fixef.cont),
                                       sig.ranef = ifelse(!is.na(sig.ranef.bin), sig.ranef.bin, sig.fixef.cont),
-                                      est.fixef.hkn = ifelse(!is.na(lor.fixef.hkn.bin), lor.fixef.hkn.bin, est.fixef.hkn.cont),
                                       est.ranef.hkn = ifelse(!is.na(lor.ranef.hkn.bin), lor.ranef.hkn.bin, est.ranef.hkn.cont),
-                                      pval.fixef.hkn = ifelse(!is.na(pval.fixef.hkn.bin), pval.fixef.hkn.bin, pval.fixef.hkn.cont),
                                       pval.ranef.hkn = ifelse(!is.na(pval.ranef.hkn.bin), pval.ranef.hkn.bin, pval.ranef.hkn.cont),
-                                      sig.fixef.hkn = ifelse(!is.na(sig.fixef.hkn.bin), sig.fixef.hkn.bin, sig.fixef.hkn.cont),
[…]

### 2019-04-25 Presentation/present.Rnw
presentation u.a.

\documentclass[english]{beamer}

%% The most common packages are already included in:
\usetheme{biostat}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\usepackage{amsmath,amsfonts,tikz}
\usetikzlibrary{trees}

%% Header data: (adjust to your needs:
\def\uzhunit{Biostatistics}             %% if (not) needed comment/uncomment
%\def\uzhunitext{STA480}

\title{Publication Bias in the Cochrane Library of Systematic Reviews}
%% Optional Argument in [Brackets]: Short Title for Footline

%% The following are all optional, simply comment them
%\subtitle{Subtitle (optional)}
%\institute{Biostatistics Journal Club}  %% optional
\author{Giuachin Kreiliger}
%\date{\today}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{document}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%% Start with slides here: put them between `\begin{frame}` and `\end{frame}`

<<echo=FALSE, warning = FALSE, message=FALSE>>= 
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH2, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

file_results = "pb.RData"

source(file.path(PATH_CODE, 'PubBias_functions.R'))

data = pb.readData(path = PATH_DATA, file = FILE)
tmp = pb.clean(data)
data = tmp[[1]]
aliases = tmp[[2]]

file.bin <- "pb.bin.RData"
if (file.exists(file.path(PATH_RESULTS, file.bin))) {
  load(file.path(PATH_RESULTS, file.bin))
} else {
  meta.bin <- meta.bin.complete(data, min.study.number = 10, sig.level = 0.05)
  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
}

file.cont <- "pb.cont.RData"
if (file.exists(file.path(PATH_RESULTS, file.cont))) {
  load(file.path(PATH_RESULTS, file.cont))
} else {
  meta.cont <- meta.cont.complete(data, min.study.number = 10, sig.level = 0.05)
  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
}

meta <- pb.meta.merge(meta.bin, meta.cont)

file.cont <- "mly.cont.RData"
if (file.exists(file.path(PATH_RESULTS, file.cont))) {
  load(file.path(PATH_RESULTS, file.cont))
} else {
  data.cont <- mly.cont(data.ext, 0.05, min.study.number = 2)
  save(data.cont, file =  file.path(PATH_RESULTS, file.cont))
}

file.bin <- "mly.bin.RData"
if (file.exists(file.path(PATH_RESULTS, file.bin))) {
  load(file.path(PATH_RESULTS, file.bin))
} else {
  data.bin <- mly.bin(data.ext, 0.05, min.study.number = 2)
  save(data.bin, file =  file.path(PATH_RESULTS, file.bin))
}

load(file.path(PATH_RESULTS, file = "mly.RData"))
load(file.path(PATH_RESULTS, file = "data.processed.RData"))

require(biostatUZH)
require(tidyverse)
require(meta)
require(metasens)
require(gridExtra)
require(xtable)

###################################################################################################################
###################################################################################################################

#Barbiturate Examples
barbi1 <- arrange(filter(data, file.nr == 21) %>% 
          select(Study = study.name, Comparison = comparison.name, Outcome = outcome.name, 
                 Events = events1, Total = total1, Events_c = events2, Total_c = total2) %>% 
            slice(c(1,3)), Study) 
barbi1 <- barbi1 %>% mutate(Comparison = "Barbiturate vs ..", Outcome = "Death at ..")

barbi2 <- arrange(filter(data, file.nr == 21) %>% 
          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study) %>% group_by(Comparison) %>% distinct(Outcome, .keep_all = T)
barbi2[barbi2$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"

#Missing values
cont.out <- data %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
                                 outcome.measure.new == "Hedges' G")

missing.mean <- which(is.na(cont.out$mean1) | is.na(cont.out$mean2))
missing.effect <- which(is.na(cont.out$effect))
missing.means <- intersect(missing.mean, missing.effect) #Cont. results that have neither complete means nor an effect
wrong.effect <- which(cont.out$mean1 == 0 & cont.out$mean2 == 0 & cont.out$effect == 0) #Cont.results that have only zeros
missing.effects <- length(c(missing.means, wrong.effect))

missing.sd <- which(is.na(cont.out$sd1) | is.na(cont.out$sd2))
missing.se <- which(is.na(cont.out$se))
missing.sds <- intersect(missing.se, missing.sd) #Cont. results that have neither complete means nor an effect
wrong.sds <- which(cont.out$sd1 == 0 & cont.out$sd2 == 0 & cont.out$se == 0) #Cont.results that have only zeros
missing.sds <- length(c(missing.sds, wrong.sds))

missing.ss <- which(is.na(data$total1) | is.na(data$total2))
wrong.ss <- which(data$total1 <= 0 | data$total2 <= 0)
missing.ssize <- length(c(missing.ss, wrong.ss))

missing.year <- sum(is.na(data$study.year)) + length(c(which(data$study.year < 1920), which(data$study.year > 2019)))

missing.table <- rbind("Missing mean values and mean differences" = missing.effects,
                         "Missing standard deviations and standard errors" = missing.sds,
                         "Missing sample sizes" = missing.ssize,
                         "Missing study year" = missing.year)

#Mean and median number of different outcome types of reviews
mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
  ungroup() %>% group_by(file.nr) %>%
  count() %>% ungroup %>% summarise(mean = mean(n))

median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
  ungroup() %>% group_by(file.nr) %>%
  count() %>% ungroup %>% summarise(mean = median(n))

#Study.year quantiles:
data.ext <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
publication.year.range <- c(quantile(data.ext$study.year, 0.05, na.rm = T), quantile(data.ext$study.year, 0.25, na.rm = T), 
                            quantile(data.ext$study.year, 0.5, na.rm = T), quantile(data.ext$study.year, 0.75, na.rm = T),
                            round(mean(data.ext$study.year, na.rm = T), 2))

#Outcome.measure frequency table:
outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.new) %>% count() %>% 
                                       arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9),
                                     data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% 
                                       ungroup() %>% filter(row_number() > 8) %>% 
                                       summarise(outcome.measure.new = "other", n = sum(n)))

outcome.measure.frequencies <- outcome.measure.frequencies %>% mutate(percentage = round(n/sum(n),3)*100)
names(outcome.measure.frequencies) <- c("Outcome measure", "n", "Percentage")
outcome.measure.frequencies$Percentage <- paste(outcome.measure.frequencies$Percentage, "%", sep = "")

#Total and group size quantiles:
data.ext <- data.ext %>% ungroup() %>%  mutate(total.n = total1 + total2)
samplesize.range <- c(quantile(data.ext$total.n, 0.05, na.rm = T), quantile(data.ext$total.n, 0.25, na.rm = T), 
                            quantile(data.ext$total.n, 0.5, na.rm = T), quantile(data.ext$total.n, 0.75, na.rm = T),
                            round(mean(data.ext$total.n, na.rm = T), 2))
treatment.group.size.range <- c(quantile(data.ext$total1, 0.05, na.rm = T), quantile(data.ext$total1, 0.25, na.rm = T), 
                      quantile(data.ext$total1, 0.5, na.rm = T), quantile(data.ext$total1, 0.75, na.rm = T),
                      round(mean(data.ext$total1, na.rm = T), 2))

#Frequencies of results:
comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
                      quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
                      round(mean(comp.freq$n, na.rm = T), 2))

#Frequencies of studies:
study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
                      quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
                      round(mean(study.freq$n, na.rm = T), 2))

#Pooling studies
cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
  filter(n < 15) %>%
  full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
  ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
# cum.repr.trials.nosub <- data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
#   filter(n < 15) %>%
#   full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
#                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
#   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)

# cum.repr.trials <- cbind(cum.repr.trials.nosub, cum.repr.trials.subg)[,c(1,3,6)]

colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
@

\begin{frame}{Cochrane Library}
Database of high-quality, systematic reviews in clinical science.

Currently $\sim$ 8,000 reviews, prepared by independet groups.

Reviews are peer-reviewed and prepared after guidelines.
\end{frame}

\begin{frame}{Cochrane Library Dataset}
% \Sexpr{length(unique(data$file.nr))} systematic reviews with studies published until 2018.
% 
% \Sexpr{length(unique(data$study.name))} studies.
% 
% \Sexpr{dim(data)[1]} study results.
\end{frame}

\begin{frame}{Dataset structure}

\begin{figure}
\tikzstyle{every node}=[draw=black,thick,anchor=west,scale=.65]
\tikzstyle{selected}=[draw=red,fill=red!30]
\tikzstyle{optional}=[dashed,fill=gray!50]
\begin{tikzpicture}
[grow = right, anchor = west, 
  growth parent anchor=east, % added code
  parent anchor=east, level distance=.5cm,
  sibling distance=2em, level 1/.style={sibling distance=2em}, level 2/.style={sibling distance=2em}, 
  level 3/.style={sibling distance=2em}, level 4/.style={sibling distance=1.2em}]
  \node {Review} [edge from parent fork right]
    child { node {Comparison 2}
      child { node {Outcome 2}}
      child { node {Outcome 1}
        child { node {Subgroup 2}}
        child { node {Subgroup 1}
          child  { node {Result 3}}
          child  { node {Result 2}}
          child  { node {Result 1}}
          }}
    }
    child [missing] {}		
    child { node {Comparison 1  }};
\end{tikzpicture}
%\caption{Structure of a hypothetical review with two different comparisons\label{review.structure}}
\label{review.structure}
\end{figure}

\end{frame}

\begin{frame}{Review Example}
\vspace{-5mm}
<<echo = FALSE, results = 'asis'>>=
print(xtable(barbi2, label = "barbiturates"), include.rownames = F, size = "tiny")
@

\vspace{-6mm}
<<echo = FALSE, results = 'asis'>>=
print(xtable(barbi1, label = "barbiturate.row", digits = 0), 
      include.rownames = F, size = "tiny")
@
\end{frame}

\begin{frame}{Pooling studies}
Studies of the same outcome, comparison and subgroup can be pooled by meta analyis.

Evidence synthesis - more reliable results.

Different methods - f.ex. random or fixed effects meta-analysis.
\end{frame}

\begin{frame}{Publication bias}
Selection of studies with treatment effects.

Stronger selection for smaller studies - small study effect.

Distort findings of meta-analyses.
\end{frame}

\begin{frame}{References}
  \small
  \bibliographystyle{apalike}
\bibliography{illustration}
\end{frame}

%\appendix
%% Possible backup slides...

%% chapter division is accomplished with:
%% \part{Appendix}

\end{document}

### 2019-04-25 report/MSc_Report.tex
test
presentation u.a.

@@
 \subsection{Structure and Content}
-The dataset consists of 5016 systematic reviews from the Cochrane Library with 52995 studies.
-Each study provides data of (multiple) comparisons of clinical interventions. 
-% It can not be ruled out that some comparisons are retrospective, e.g. from observational studies. 
-In Table \ref{barbiturate.row}, two comparisons from a systematic review about effects of barbiturates are shown as they are given in the dataset.
-As can be seen, the comparison is further specified by the variables in the columns.
-One row of the dataset is one comparison.
+The dataset consists of 5016 systematic reviews from the Cochrane Library with 52995 studies and 463820 results.
+A result compares clinical or medical interventions or treatments.
+Each study provides (multiple) results of clinical interventions.
+
+In Table \ref{barbiturate.row}, two results from a systematic review about effects of barbiturates are shown as they are given in the dataset.
+As can be seen, the result is further specified by the variables in the columns.
+The comparison variable specifies what treatments or interventions are compared, the outcome variable how it is compared, and the subgroup variable (not given in table) indicates if the result belongs to a certain subgroup.
+Here, the result is of a binary outcome, so the events in the barbiturate treatment group and the total number of participants are given in columns ``Events'' and ``Total'' and the number of events in the control group ``Events\_c'' and participants ``Total\_c''.
+Events denotes here number of deaths at the end of follow up.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Apr 23 12:23:04 2019
+% Thu Apr 25 14:26:47 2019
 \begin{table}[ht]
@@
   \hline
-Study & Comparison\_type & Outcome & Events & Total & Events\_c & Total\_c \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11.00 & 41.00 & 11.00 & 41.00 \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14.00 & 27.00 & 13.00 & 26.00 \\ 
+Study & Comparison & Outcome & Events & Total & Events\_c & Total\_c \\ 
+  \hline
+Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11 & 41 & 11 & 41 \\ 
+  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14 & 27 & 13 & 26 \\ 
    \hline
@@
 \endgroup
-\caption{Example of two comparisons as given in the dataset.
+\caption{Example of two results as given in the dataset.
 Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
@@
 
-A complete listing of the variables is given in Table \ref{variable}.
-They can roughly be separated into variables that specify the review in which the comparison is contained and variables that specify the comparison itself (separated by a horizontal line in Table \ref{variable}).
+A complete listing of the variables of a result is given in Table \ref{variable}.
+They can roughly be separated into variables that specify the review in which the result is contained and variables that specify the result itself (separated by a horizontal line in Table \ref{variable}).
 
@@
       \hline
-      \textbf{file.nr} & The number of the file from which the review data has been . \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
+      \textbf{file.nr} & The number of the file from which the review data has been \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
       \textbf{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
@@
       \hline
-      \textbf{comparison.name/.nr} & Specification of the interventions compared in the study  \\ and a unique number for the comparison\\
-      \textbf{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ and a unique number for the outcome\\
-      \textbf{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a \\ unique number for the subgroup\\
-      \textbf{study.name} & Name of the study to which the comparison belongs\\
+      \textbf{study.name} & Name of the study to which the result belongs\\
       \textbf{study.year} & Year in which the study was published\\
+      \hline
+      \textbf{comparison.name/.nr} & Specification of the interventions compared in the study  \\ &and a unique number for the comparison\\
+      \textbf{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ &and a unique number for the outcome\\
+      \textbf{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a \\ &unique number for the subgroup\\
       \textbf{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
       \textbf{effect} & Measure of the effect given in the quantity denoted by \\ &``outcome measure''.\\
-      \textbf{events1/events2} & The counts of patients with an outcome \textit{if}\\ & measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
+      \textbf{se} & Standard error of the measure of the effect,\\
+      \textbf{events1/events2} & The counts of patients with an outcome \textit{if}\\ &measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
       \textbf{total1/total2} & Number of patients in groups.\\
-      \textbf{mean1/mean2)} & Mean of patient measurements \textit{if} outcome is continuous.\\
+      \textbf{mean1/mean2} & Mean of patient measurements \textit{if} outcome is continuous.\\
       \textbf{sd1/sd2} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
@@
 
-The structure of a review is shown in Figure \ref{review}. 
-% Comparisons of a review can consecutively be subdivided into different comparison types, different outcome measures and different subgroups. 
-The comparison type variable specifies what is compared, the outcome variable how it is compared, and the subgroup variable indicates if the comparison belongs to a certain subgroup.
-If desired, Figure \ref{review} can be compared to Table \ref{barbiturates} where an exemplary review is listed.
+Results are part of studies that are again part of a (systematic) review. This structure of a review is shown in Figure \ref{review}.
 
@@
   \node {Review} [edge from parent fork right]
-    child { node {Comparison type 2}
+    child { node {Comparison 2}
       child { node {Outcome 2}}
@@
         child { node {Subgroup 2}}
-        child { node {Subgroup 1}}}
+        child { node {Subgroup 1}
+          child  { node {Result 2}}
+          child  { node {Result 1}}
+          }}
     }
     child [missing] {}		
-    child { node {Comparison type 1  }};
+    child { node {Comparison 1  }};
 \end{tikzpicture}
@@
 
-% \vspace{0mm}
-% Lets consider the previously mentioned barbiturate and head injury review.
+\vspace{0mm}
+The structure of a review will now be outlined based on an example of the dataset.
+Lets consider the previously mentioned barbiturate and head injury review.
 The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates''.
-The medical background is that one knew that barbiturates could cause relief in intra-cranial pressure, but also reduce cerebral blood flow.
-Because one effect is thought to be beneficial for persons with severe head injuries while the other isn't, the authors of the review wanted to find out if there is a net benefit of barbiturates.
-% 
-% \vspace{0mm}
-% The review comprises five studies in total.
-Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental, which would be the comparison/research subject to speak in the previously introduced notions.
-% 
-% \vspace{0mm}
-% All the studies convey multiple information to the review.
-As an example, that could be death or death \textit{and} severe disability at follow up as an outcome.
-Again, the study can be further split up in different subgroups, here for example in a group with - and without haematoma.
-% 
-% \vspace{0mm}
-% The complete listing of outcomes is in table \ref{barbiturates}.
+Since there are arguments for and against use of barbiturates, the authors of the review did a comprehensive literature search and collected all available study findings.
+
+\vspace{0mm}
+The review comprises five studies in total.
+Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental, which would be the comparison to speak in the previously introduced notion.
+The studies have different outcomes, for example, death or death and severe disability at follow up.
+One study split up outcomes for patients with and without haematoma, which would be subgroups.
+
+\vspace{0mm}
+The complete listing of outcomes is in table \ref{barbiturates}.
 The table also gives an illustration of the variety of data that can be included in a review.
-We have for example continuous and binary outcome data, that again is divided into a variety of different things that have been measured.
-Often, additionally to the main study result, also adverse effects are for example included which are in this case separate outcomes and possibly subgroups.
+We have for example continuous (mean body temperature) and binary outcome data (death).
+Additionally to primary and secondary outcomes, often also dropouts and adverse effects are included in a review.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Apr 23 12:23:04 2019
+% Thu Apr 25 14:26:47 2019
 \begin{table}[ht]
@@
 \endgroup
-\caption{Barbiturate and head injury review. In the columns, study names, comparison types and outcome measure of the comparisons are given} 
+\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given} 
 \label{barbiturates}
@@
 
-% The research subject or outcome type can possibly already be well defined in the general review question.
-Conversely, research subject or comparison has to be further specified in outcome and subgroup categories.
-As may have been implied, the terminology does not rely to a hundred percent on strict functional definitions.
-
-It is important to not confuse comparisons with studies.
-A study can contribute multiple comparisons to a systematic review.
-Also, despite a comparison has variables concerning event counts and means, it can only have one of the two, either means (if the outcome measure is continuous) or event counts (for binary outcomes).
-
-\vspace{0mm}
-Having provided an overview over the dataset, now, some more specific information is provided.
-The dataset consists of 463820 comparisons and has 26 variables that specify the comparisons.
+It is important not to confuse results with studies. A study can contribute multiple results to a systematic review, for example, primary and secondary outcomes and adverse effects.
+
+\vspace{0mm}
 Information about missing values in the dataset is given in Table \ref{missing}.
@@
 The relative amount of missing values is very low except for study years.
+In the case of continuous outcomes, the cases have been counted were effect sizes and standard errors of effect sizes are not available.
+This means that neither mean values of groups nor mean differences are given, or that neither standard deviation nor standard error is given for a result.
+Study years before 1920 and after 2019 have been counted as missing, as well as sample sizes below zero.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Apr 23 12:23:04 2019
+% Thu Apr 25 14:26:47 2019
 \begin{table}[ht]
@@
   \hline
-Missing mean values & 1287 \\ 
-  Missing standard deviations & 999 \\ 
-  Missing effects & 158 \\ 
-  Missing study year & 27234 \\ 
+Missing mean values and mean differences & 984 \\ 
+  Missing standard deviations and standard errors & 1300 \\ 
+  Missing sample sizes & 12173 \\ 
+  Missing study year & 44649 \\ 
    \hline
@@
 
-More properties of the reviews, the studies and the comparisons in the dataset will be provided on the following pages.
-The publication dates of the studies included in the dataset are shown in Figure \ref{study.years}.
-Most studies were published after 2000.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-8-1}
-
-}
-
-\end{knitrout}
-\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications}
-\label{study.years}
-\end{figure}
-
-Figure \ref{study.outcomes} provides the frequencies of outcome types of the comparisons.
-Note that the abundance of mean differences and standardized mean differences can also give an impression of the proportion of continuous outcome comparisons vs.
-binary outcome comparisons in the dataset.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-9-1}
-
-}
-
-\end{knitrout}
-\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded}
-\label{study.outcomes}
-\end{figure}
-
-It is also possible to look at the properties of the reviews.
-One question could be how many studies or comparisons that a review comprises.
-The former is shown in Figure \ref{studies.per.review} and the latter in Figure \ref{comparisons.per.review}.
-It can be seen that while almost 400 reviews consist of one study only, there are more than 150 with equal or more than 30 distinct studies.
-A similar variance between reviews can also be observed when looking at the number of comparisons.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-10-1}
-
-}
-
-\end{knitrout}
-\caption{Empirical distribution of number of studies per review}
-\label{studies.per.review}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-11-1}
-
-}
-
-\end{knitrout}
-\caption{Empirical distribution of number of comparisons per review}
-\label{comparisons.per.review}
-\end{figure}
-
-A question not to be mistaken with the previous would be how many comparison \textit{types} there are per review.
-This gives an additional impression of the scope of a review.
-Analogously to the previous figures, the empirical distribution of comparison types is depicted in Figure \ref{subjects.per.review}.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-12-1}
-
-}
-
-\end{knitrout}
-\caption{Empirical distribution of number of different comparison types per review}
-\label{subjects.per.review}
-\end{figure}
-
-% At the end, a main goal of the thesis is to analyze reviews with respect to reporting bias in meta analyses. 
-For comparisons to be suitable for usage in meta-analysis, they have to be somewhat identical (same comparison type, outcome measure and possibly subgroup).
-For an analysis of reporting bias, again a certain number of studies is required in order for reporting bias to be detectable by the methods.
-One question would therefore be: How many groups of identical comparisons of a certain size are given in the dataset?
-This depends on which degree of similarity between comparisons is considered to be sufficient.
-
-\vspace{0mm}
-In Table \ref{repr.groups}, two different similarity criteria have been used.
-One is based on the same comparison type and outcome measure, the other includes additionally subgroup affiliation of comparisons, i.e.
-only comparisons in the same subgroups are considered to be similar enough.
-
-\vspace{0mm}
-Table \ref{repr.groups} shows the cumulative number of \textit{groups} of comparisons with equal or more than $n$ comparisons.
-Practically, this means that this number of meta analyses can be performed with each having at least $n$ comparisons.
+The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982).
+The median of the publication years is 2003, the mean 2006.13 and the quartiles are 1996 and 2008.
+Only a handful ($n$ = 18) have been published in 2018, none in 2019.
+No information is available concerning unpublished results and studies.
+
+\vspace{0mm}
+The results of a study are summarised in a result by a effect measure.
+This effect measure varies, depending on whether data is continuous, binary or time-to-event.
+The most abundant effect measures used are summarised in Table \ref{outcome.measure.frequencies}.
+One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the being some sort of discrete or binary outcomes, most often binary (> 65\%).
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Apr 23 12:23:09 2019
+% Thu Apr 25 14:26:47 2019
 \begin{table}[ht]
@@
   \hline
-n & Cumulative sum (without subgroups) & Cumulative sum (with subgroups) \\ 
-  \hline
-1 & 109191 & 186300 \\ 
-  2 & 67699 & 83956 \\ 
-  3 & 47800 & 52270 \\ 
-  4 & 36169 & 36198 \\ 
-  5 & 28090 & 26570 \\ 
-  6 & 22702 & 20126 \\ 
-  7 & 18547 & 15896 \\ 
-  8 & 15475 & 12935 \\ 
-  9 & 13008 & 10821 \\ 
-  10 & 11008 & 9229 \\ 
-  11 & 9362 & 7991 \\ 
-  12 & 8057 & 7070 \\ 
-  13 & 6988 & 6368 \\ 
-  14 & 6044 & 5783 \\ 
+Outcome measure & n & Percentage \\ 
+  \hline
+Risk Ratio & 232583 & 50.1\% \\ 
+  Mean Difference & 102315 & 22.1\% \\ 
+  Odds Ratio & 49372 & 10.6\% \\ 
+  Std. Mean Difference & 40535 & 8.7\% \\ 
+  Peto Odds Ratio & 19122 & 4.1\% \\ 
+  Hazard Ratio & 6566 & 1.4\% \\ 
+  Risk Difference & 6234 & 1.3\% \\ 
+  Rate Ratio & 2283 & 0.5\% \\ 
+  other & 4810 & 1\% \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Frequencies of outcome measures among results. n denotes the total number 
+             of results with the outcome measure and percentage the percentage of the outcome measure,} 
+\label{outcome.measure.frequencies}
+\end{table}
+
+The sample sizes amongst results vary to some extent.
+There are 5\% of treatment group sample sizes that are smaller tha 8, the 5\% quantile.
+The first quartile is 22, the median 48, the mean 302.03 and the third quartile 119.
+The large difference between median and mean is caused by very large groups with over 2,000,000 participants.
+Analogously, the quantiles of the total sample size are: 5\% quantile = 15, first quartile = 44, median = 94 and third quartile = 229.
+The mean is 617.81.
+
+\vspace{0mm}
+The mean and median number of results per review are 12.42 and 7.
+There are 417 reviews with five or fewer results, and the quartiles are 16 and 102.
+Similarly, the number of reviews with a maximum of two studies included is 836, the mean study number is 12.42, the median 7 and the interquartile range 4 and 15.
+The discrepancy between mean and median is again due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxisfor preventing infection after cesarean section, with 95 studies and 1497 results in total.
+
+\vspace{0mm}
+For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome.
+More speicifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis since their research subject and experimental setup can be considered sufficiently homogeneous.
+%Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
+\vspace{0mm}
+The amount of studies that can be pooled for meta-analyses is of special interest in this masters thesis.
+Thus, the dataset is divided in groups whith identical experimental setup.
+The size of the group denotes how many results are included in a group.
+
+\vspace{0mm}
+Table \ref{repr.groups} shows the number of \textit{groups} of groups with equal or more than $n$ results.
+Practically, this means that a given number of meta analyses can be performed with each having at least $n$ results.
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Thu Apr 25 14:26:47 2019
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lll}
+  \hline
+n & Number of groups & Cumulative sum of groups \\ 
+  \hline
+1 & 102344 & 186300 \\ 
+  2 & 31686 & 83956 \\ 
+  3 & 16072 & 52270 \\ 
+  4 & 9628 & 36198 \\ 
+  5 & 6444 & 26570 \\ 
+  6 & 4230 & 20126 \\ 
+  7 & 2961 & 15896 \\ 
+  8 & 2114 & 12935 \\ 
+  9 & 1592 & 10821 \\ 
+  10 & 1238 & 9229 \\ 
+  11 & 921 & 7991 \\ 
+  12 & 702 & 7070 \\ 
+  13 & 585 & 6368 \\ 
+  14 & 455 & 5783 \\ 
   15 & 5328 & 5328 \\ 
@@
 This led to somewhat more than 400,000 significance test results.
-Since most of the times, the study publication year is available, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.The $p$-value was chosen to be $0.05$  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n > 800$).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
+Since most of the times, the study publication year is available, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-14-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-15-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-16-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
 
@@
 
-A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
+% A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
 This can again be done for the entire dataset, i.e.
@@
 In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 9701 rows containing non-finite values (stat\_smooth).}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 9701 rows containing missing values (geom\_point).}}\end{kframe}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-24-1}
-
-}
-
-\end{knitrout}
-\caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
-\label{effects.overtime.separated}
-\end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
+%                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
+%   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
+%   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
+%   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
+%   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
+%   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
+% @
+% \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
+% \label{effects.overtime.separated}
+% \end{figure}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-26-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-29-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-30-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-24-1}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Apr 23 12:24:31 2019
+% Thu Apr 25 14:27:29 2019
 \begin{table}[ht]
@@
 In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
-A s trend towards more rejections for larger sample sizes can be seen.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-33-1}
+A trend towards more rejections for larger sample sizes can be seen.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-34-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-35-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-29-1}
 
@@
 The same for significance of random effects meta-analysis is shown in Figure \ref{significance.change.random}.
-The significance threshold was chosen such that the $p$-value had to be $< 0.05$ for rejection of the null hypothesis of no treatment effect.
+The significance threshold was chosen such that the $p$-value had to be < 0.05 for rejection of the null hypothesis of no treatment effect.
 The correction methods were trim-and-fill, copas selection model and regression with random effects and shrinkage of within-study-variance methods.
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-36-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-30-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-37-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-31-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-38-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-32-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-39-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-33-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-40-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-34-1}
 

### 2019-04-25 report/chapter03.Rnw
presentation u.a.

@@
                echo=TRUE, message=FALSE,
-               fig.width=8.1, fig.height=3.7,
+               fig.width=8.1, fig.height=3.4,
                out.width='\\textwidth-3cm',
@@
 This led to somewhat more than 400,000 significance test results.
-Since most of the times, the study publication year is available, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.The $p$-value was chosen to be $0.05$  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n > 800$).
+Since most of the times, the study publication year is available, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
 
@@
 <<echo=FALSE>>=
+levels(data$outcome.measure.new) <- c("Mean Difference", "Std. Mean Difference", "Odds Ratio", "Risk Ratio")
+
 data %>% filter(total1 + total2 > 10 & total1 + total2 < 100) %>% 
@@
   summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
-  ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point() + facet_wrap(~outcome.measure.new) + 
+  ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point() + facet_wrap(~outcome.measure.new, scales = "free") + 
   theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size")
@@
 In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
-
-\begin{figure}
-<<echo=FALSE>>=
-data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
-                outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
-  filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
-  group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
-  mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
-  ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
-  geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
-@
-\caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
-\label{effects.overtime.separated}
-\end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
+%                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
+%   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
+%   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
+%   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
+%   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
+%   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
+% @
+% \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
+% \label{effects.overtime.separated}
+% \end{figure}
 
@@
 In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
-A s trend towards more rejections for larger sample sizes can be seen.
+A trend towards more rejections for larger sample sizes can be seen.
 

### 2019-04-29 Presentation/present.Rnw
Presentation upload

@@
 
-<<echo=FALSE, warning = FALSE, message=FALSE>>= 
+<<echo=FALSE, warning = FALSE, warnings = FALSE, message = FALSE>>= 
 PATH_HOME = path.expand("~") # user home
@@
 
+# data = pb.readData(path = PATH_DATA, file = FILE)
+# tmp = pb.clean(data)
+# data = tmp[[1]]
+# aliases = tmp[[2]]
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+  load(file.path(PATH_RESULTS, file.dat))
+} else {
   data = pb.readData(path = PATH_DATA, file = FILE)
@@
 	aliases = tmp[[2]]
+  save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
 
@@
 
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
+  load(file.path(PATH_RESULTS, file.meta))
+} else {
   meta <- pb.meta.merge(meta.bin, meta.cont)
+  save(meta, file =  file.path(PATH_RESULTS, file.meta))
+}
+
+# meta <- pb.meta.merge(meta.bin, meta.cont)
 
@@
 barbi2[barbi2$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
-
-#Missing values
-cont.out <- data %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
-                                 outcome.measure.new == "Hedges' G")
-
-missing.mean <- which(is.na(cont.out$mean1) | is.na(cont.out$mean2))
-missing.effect <- which(is.na(cont.out$effect))
-missing.means <- intersect(missing.mean, missing.effect) #Cont. results that have neither complete means nor an effect
-wrong.effect <- which(cont.out$mean1 == 0 & cont.out$mean2 == 0 & cont.out$effect == 0) #Cont.results that have only zeros
-missing.effects <- length(c(missing.means, wrong.effect))
-
-missing.sd <- which(is.na(cont.out$sd1) | is.na(cont.out$sd2))
-missing.se <- which(is.na(cont.out$se))
-missing.sds <- intersect(missing.se, missing.sd) #Cont. results that have neither complete means nor an effect
-wrong.sds <- which(cont.out$sd1 == 0 & cont.out$sd2 == 0 & cont.out$se == 0) #Cont.results that have only zeros
-missing.sds <- length(c(missing.sds, wrong.sds))
-
-missing.ss <- which(is.na(data$total1) | is.na(data$total2))
-wrong.ss <- which(data$total1 <= 0 | data$total2 <= 0)
-missing.ssize <- length(c(missing.ss, wrong.ss))
-
-missing.year <- sum(is.na(data$study.year)) + length(c(which(data$study.year < 1920), which(data$study.year > 2019)))
-
-missing.table <- rbind("Missing mean values and mean differences" = missing.effects,
-                         "Missing standard deviations and standard errors" = missing.sds,
-                         "Missing sample sizes" = missing.ssize,
-                         "Missing study year" = missing.year)
-
-#Mean and median number of different outcome types of reviews
-mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
-  ungroup() %>% group_by(file.nr) %>%
-  count() %>% ungroup %>% summarise(mean = mean(n))
-
-median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
-  ungroup() %>% group_by(file.nr) %>%
-  count() %>% ungroup %>% summarise(mean = median(n))
-
-#Study.year quantiles:
-data.ext <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
-publication.year.range <- c(quantile(data.ext$study.year, 0.05, na.rm = T), quantile(data.ext$study.year, 0.25, na.rm = T), 
-                            quantile(data.ext$study.year, 0.5, na.rm = T), quantile(data.ext$study.year, 0.75, na.rm = T),
-                            round(mean(data.ext$study.year, na.rm = T), 2))
-
-#Outcome.measure frequency table:
-outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.new) %>% count() %>% 
-                                       arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9),
-                                     data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% 
-                                       ungroup() %>% filter(row_number() > 8) %>% 
-                                       summarise(outcome.measure.new = "other", n = sum(n)))
-
-outcome.measure.frequencies <- outcome.measure.frequencies %>% mutate(percentage = round(n/sum(n),3)*100)
-names(outcome.measure.frequencies) <- c("Outcome measure", "n", "Percentage")
-outcome.measure.frequencies$Percentage <- paste(outcome.measure.frequencies$Percentage, "%", sep = "")
-
-#Total and group size quantiles:
-data.ext <- data.ext %>% ungroup() %>%  mutate(total.n = total1 + total2)
-samplesize.range <- c(quantile(data.ext$total.n, 0.05, na.rm = T), quantile(data.ext$total.n, 0.25, na.rm = T), 
-                            quantile(data.ext$total.n, 0.5, na.rm = T), quantile(data.ext$total.n, 0.75, na.rm = T),
-                            round(mean(data.ext$total.n, na.rm = T), 2))
-treatment.group.size.range <- c(quantile(data.ext$total1, 0.05, na.rm = T), quantile(data.ext$total1, 0.25, na.rm = T), 
-                      quantile(data.ext$total1, 0.5, na.rm = T), quantile(data.ext$total1, 0.75, na.rm = T),
-                      round(mean(data.ext$total1, na.rm = T), 2))
-
-#Frequencies of results:
-comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
-comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
-                      quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
-                      round(mean(comp.freq$n, na.rm = T), 2))
-
-#Frequencies of studies:
-study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
-study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
-                      quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
-                      round(mean(study.freq$n, na.rm = T), 2))
-
-#Pooling studies
-cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
-  filter(n < 15) %>%
-  full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
-               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
-  ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
-# cum.repr.trials.nosub <- data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+# 
+# #Missing values
+# cont.out <- data %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
+#                                  outcome.measure.new == "Hedges' G") 
+# 
+# missing.mean <- which(is.na(cont.out$mean1) | is.na(cont.out$mean2))
+# missing.effect <- which(is.na(cont.out$effect))
+# missing.means <- intersect(missing.mean, missing.effect) #Cont. results that have neither complete means nor an effect
+# wrong.effect <- which(cont.out$mean1 == 0 & cont.out$mean2 == 0 & cont.out$effect == 0) #Cont.results that have only zeros
+# missing.effects <- length(c(missing.means, wrong.effect))
+# 
+# missing.sd <- which(is.na(cont.out$sd1) | is.na(cont.out$sd2))
+# missing.se <- which(is.na(cont.out$se))
+# missing.sds <- intersect(missing.se, missing.sd) #Cont. results that have neither complete means nor an effect
+# wrong.sds <- which(cont.out$sd1 == 0 & cont.out$sd2 == 0 & cont.out$se == 0) #Cont.results that have only zeros
+# missing.sds <- length(c(missing.sds, wrong.sds))
+# 
+# missing.ss <- which(is.na(data$total1) | is.na(data$total2))
+# wrong.ss <- which(data$total1 <= 0 | data$total2 <= 0)
+# missing.ssize <- length(c(missing.ss, wrong.ss))
+# 
+# missing.year <- sum(is.na(data$study.year)) + length(c(which(data$study.year < 1920), which(data$study.year > 2019)))
+# 
+# missing.table <- rbind("Missing mean values and mean differences" = missing.effects,
+#                          "Missing standard deviations and standard errors" = missing.sds,
+#                          "Missing sample sizes" = missing.ssize,
+#                          "Missing study year" = missing.year)
+# 
+# #Mean and median number of different outcome types of reviews
+# mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
+#   ungroup() %>% group_by(file.nr) %>%
+#   count() %>% ungroup %>% summarise(mean = mean(n))
+# 
+# median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
+#   ungroup() %>% group_by(file.nr) %>%
+#   count() %>% ungroup %>% summarise(mean = median(n))
+# 
+# #Study.year quantiles:
+# data.ext <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
+# publication.year.range <- c(quantile(data.ext$study.year, 0.05, na.rm = T), quantile(data.ext$study.year, 0.25, na.rm = T), 
+#                             quantile(data.ext$study.year, 0.5, na.rm = T), quantile(data.ext$study.year, 0.75, na.rm = T),
+#                             round(mean(data.ext$study.year, na.rm = T), 2))
+# 
+# #Outcome.measure frequency table:
+# outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.new) %>% count() %>% 
+#                                        arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9),
+#                                      data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% 
+#                                        ungroup() %>% filter(row_number() > 8) %>% 
+#                                        summarise(outcome.measure.new = "other", n = sum(n)))
+# 
+# outcome.measure.frequencies <- outcome.measure.frequencies %>% mutate(percentage = round(n/sum(n),3)*100)
+# names(outcome.measure.frequencies) <- c("Outcome measure", "n", "Percentage")
+# outcome.measure.frequencies$Percentage <- paste(outcome.measure.frequencies$Percentage, "%", sep = "")
+# 
+# #Total and group size quantiles:
+# data.ext <- data.ext %>% ungroup() %>%  mutate(total.n = total1 + total2)
+# samplesize.range <- c(quantile(data.ext$total.n, 0.05, na.rm = T), quantile(data.ext$total.n, 0.25, na.rm = T), 
+#                             quantile(data.ext$total.n, 0.5, na.rm = T), quantile(data.ext$total.n, 0.75, na.rm = T),
+#                             round(mean(data.ext$total.n, na.rm = T), 2))
+# treatment.group.size.range <- c(quantile(data.ext$total1, 0.05, na.rm = T), quantile(data.ext$total1, 0.25, na.rm = T), 
+#                       quantile(data.ext$total1, 0.5, na.rm = T), quantile(data.ext$total1, 0.75, na.rm = T),
+#                       round(mean(data.ext$total1, na.rm = T), 2))
+# 
+# #Frequencies of results:
+# comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
+# comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
+#                       quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
+#                       round(mean(comp.freq$n, na.rm = T), 2))
+# 
+# #Frequencies of studies:
+# study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
+# study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
+#                       quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
+#                       round(mean(study.freq$n, na.rm = T), 2))
+# 
+# #Pooling studies
+# cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
 #   filter(n < 15) %>%
@@
 #   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
+# # cum.repr.trials.nosub <- data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+# #   filter(n < 15) %>%
+# #   full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+# #                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
+# #   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
+# 
+# # cum.repr.trials <- cbind(cum.repr.trials.nosub, cum.repr.trials.subg)[,c(1,3,6)]
+# 
+# colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
 
-# cum.repr.trials <- cbind(cum.repr.trials.nosub, cum.repr.trials.subg)[,c(1,3,6)]
+###################################################################################################################
+###################################################################################################################
+#Meta-analyses
+###################################################################################################################
+###################################################################################################################
 
-colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
+#Funnel plot example:
+biased.rev <- data %>% filter(file.nr == 76 & comparison.nr == 2 & outcome.nr == 2 & subgroup.nr == 4)
+meta.example <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, 
+												studlab = study.name, sm= "OR", data = biased.rev)
+
+#Publication Bias test plots:
+test.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                 schwarzer.test = mean(schwarzer.test),
+                                                 rucker.test = mean(rucker.test),
+                                                 harbord.test = mean(harbord.test),
+                                                 peter.test = mean(peter.test))
+test.bin <- test.bin %>% gather(key = "test.type", value = "mean")
+p.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% 
+  select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
+  gather(key = "test.type", value = "null.hypothesis") %>%  
+  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
+  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+  theme_bw() + xlab(label = NULL) + ggtitle("Binary Outcomes") + theme(legend.position = "top") +
+  guides(fill=guide_legend(title=NULL))+
+  annotate("text", x = test.bin$test.type, y = 1000, 
+           label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
+           color = "white")
+
+test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                   begg.test = mean(begg.test),
+                                                   thomson.test = mean(thomson.test))
+test.cont <- test.cont %>% gather(key = "test.type", value = "mean")
+p.cont <- meta.cont %>% ungroup() %>% 
+  select(egger.test, thomson.test, begg.test) %>% 
+  gather(key = "test.type", value = "null.hypothesis") %>% 
+  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
+  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+  theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
+	guides(fill=guide_legend(title=NULL))+
+  annotate("text", x = test.cont$test.type, y = 750, 
+           label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
+           color = "white")
+
+#Significance change after adjustment plot:
+change.fixef <- meta %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()
+
+p.fixef.change <- meta %>% ungroup() %>% 
+  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>%  
+  mutate(sig.change = factor(sig.change)) %>% 
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.nonsig", "unchanged.sig", "change.to.sig")) +
+  annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 1500, 
+         label = paste(change.fixef[change.fixef$sig.change == 3,]$n, "changed to nonsig."), 
+         color = "white")
+
+# Significance after correction plots, separated for meta-analyses with significant publication bias test.
+change.fixef.bias <- meta %>% 
+  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+  filter(thomson.test == 1) %>% group_by(sig.change, correction.method) %>% count()
+
+p.change.fixef.bias <- meta %>% 
+  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+  filter(thomson.test == 0) %>% 
+	mutate(sig.change = factor(sig.change)) %>% 
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+  ggtitle("Meta analysis with non-significant small study effect (peters")+ 
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 100, 
+           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
+           color = "white")
+
+change.fixef.unbias <- meta %>% 
+  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+  filter(thomson.test == 0) %>% group_by(sig.change, correction.method) %>% count()
+
+p.change.fixef.unbias <- meta %>% 
+  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+  filter(thomson.test == 1) %>% 
+	mutate(sig.change = factor(sig.change)) %>% 
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+  ggtitle("Meta analysis with significant small study effect (peters")+ 
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 900, 
+           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
+           color = "white")
+
+#Publication bias over time and for different sample size:
+pbias.time <- meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
+  ggplot(aes(x = mean.publication.year, fill = factor(thomson.test), stat(count))) + geom_density(na.rm = T, position = "fill") + 
+  guides(fill=guide_legend(title=NULL)) + theme(legend.position = "top") + xlab(label = NULL) +
+	scale_fill_discrete(labels= c("Significant", "Not significant"))
+
+pbias.ss <- meta %>% filter(n < 40) %>% ggplot(aes(x = n, fill = factor(thomson.test), stat(count))) + 
+  geom_density(position = "fill") + guides(fill=guide_legend(title=NULL)) + xlab(label = NULL) + 
+	theme(legend.position = "top") + 
+	scale_fill_discrete(labels= c("Significant", "Not significant"))
+
+#Significance proportion plots (before and after correction):
+significance <- meta %>% ungroup() %>% 
+  select(thomson.test, sig.ranef, sig.fixef, sig.trimfill, sig.reg.ranef, sig.copas) %>% 
+  gather(key = "estimation.method", value = "significance", sig.ranef:sig.copas)  %>% #filter(thomson.test == 1) %>% 
+  group_by(significance, estimation.method) %>% count()
+
+p.significance <- meta %>% ungroup() %>% 
+  select(thomson.test, sig.ranef, sig.fixef, sig.trimfill, sig.reg.ranef, sig.copas) %>% 
+  gather(key = "estimation.method", value = "significance", sig.ranef:sig.copas) %>% #filter(thomson.test == 1) %>% 
+  ggplot(aes(x = estimation.method, fill = factor(significance))) + geom_bar() + coord_flip() + theme(legend.position = "top") +
+	guides(fill=guide_legend(title=NULL)) + 
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("Significant", "Non-significant"))+
+  annotate("text", x = significance[significance$significance == 1,]$estimation.method, y = 1500, 
+           label = paste(significance[significance$significance == 1,]$n, "significant"), 
+           color = "white")
+
+significance <- meta %>% ungroup() %>% 
+  select(thomson.test, sig.ranef, sig.fixef, sig.trimfill, sig.reg.ranef, sig.copas) %>% 
+  gather(key = "estimation.method", value = "significance", sig.ranef:sig.copas) %>% filter(thomson.test == 1) %>% 
+  group_by(significance, estimation.method) %>% count()
+
+p.significance.bias <- meta %>% ungroup() %>% 
+  select(thomson.test, sig.ranef, sig.fixef, sig.trimfill, sig.reg.ranef, sig.copas) %>% 
+  gather(key = "estimation.method", value = "significance", sig.ranef:sig.copas) %>% filter(thomson.test == 1) %>% 
+  ggplot(aes(x = estimation.method, fill = factor(significance))) + geom_bar() + coord_flip() + theme(legend.position = "top") +
+	guides(fill=guide_legend(title=NULL)) + xlab(label = NULL) + scale_fill_discrete(labels= c("Significant", "Non-significant")) +
+	ggtitle("Meta analysis with significant small study effect") +
+  annotate("text", x = significance[significance$significance == 1,]$estimation.method, y = 250, 
+           label = paste(significance[significance$significance == 1,]$n, "significant"), 
+           color = "white")
+
+significance <- meta %>% ungroup() %>% 
+  select(thomson.test, sig.ranef, sig.fixef, sig.trimfill, sig.reg.ranef, sig.copas) %>% 
+  gather(key = "estimation.method", value = "significance", sig.ranef:sig.copas) %>% filter(thomson.test == 0) %>% 
+  group_by(significance, estimation.method) %>% count()
+
+p.significance.unbias <- meta %>% ungroup() %>% 
+  select(thomson.test, sig.ranef, sig.fixef, sig.trimfill, sig.reg.ranef, sig.copas) %>% 
+  gather(key = "estimation.method", value = "significance", sig.ranef:sig.copas) %>% filter(thomson.test == 0) %>% 
+  ggplot(aes(x = estimation.method, fill = factor(significance))) + geom_bar() + coord_flip() + theme(legend.position = "top") +
+	guides(fill=guide_legend(title=NULL)) + 
+  xlab(label = NULL) + scale_fill_discrete(labels= c("Significant", "Non-significant")) +
+	ggtitle("Meta analysis with non-significant small study effect") + 
+  annotate("text", x = significance[significance$significance == 1,]$estimation.method, y = 1500, 
+           label = paste(significance[significance$significance == 1,]$n, "significant"), 
+           color = "white")
+
+#Significance after adjustment separated by significant publication bias tests
+change.fixef.bias <- meta %>% 
+  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+  filter(thomson.test == 1) %>% group_by(sig.change, correction.method) %>% count()
+
+p.change.fixef.bias <- meta %>% 
+  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+  filter(thomson.test == 1) %>% mutate(sig.change = factor(sig.change)) %>% 
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+  ggtitle("Meta analysis with significant small study effect")+ 
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 100, 
+           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
+           color = "white")
+
+change.fixef.unbias <- meta %>% 
+  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+  filter(thomson.test == 0) %>% group_by(sig.change, correction.method) %>% count()
+
+p.change.fixef.unbias <- meta %>% 
+  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+  filter(thomson.test == 0) %>%   mutate(sig.change = factor(sig.change)) %>% 
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+  ggtitle("Meta analysis with non-significant small study effect")+ 
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 900, 
+           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
+           color = "white")
+
+###################################################################################################################
+###################################################################################################################
+# Results
+###################################################################################################################
+###################################################################################################################
+
+#Merge comparisons with meta-analysis result:
+mly.tomerge <- mly %>% select(meta.id, sig.Q, n.sig.type, n.sig.fishersz, sig.fixef, sig.ranef, sig.ranef.hkn)
+
+data.mly <- merge(x = data.ext, y = mly.tomerge, by = c("meta.id")) #ideally, 278626 comparisons ( = sum(mly$n)), 
+# but 300831 (18261 have smaller sample size than mly, but same meta.id)
+
+data.mly <- data.mly %>% filter(total1 > 11 & total2 > 11) #Now 282550
+
+sig.meta.c <- data.mly %>% select(sig.type, sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
+  gather(key = "meta.analysis.method", value = "sig.meta.analysis") %>% mutate(sig.meta.analysis = factor(sig.meta.analysis))
+
+sig.meta.count.c <- sig.meta.c %>% 
+  group_by(sig.meta.analysis, meta.analysis.method) %>% count()
+
+sig.meta.c <- sig.meta.c %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
+  geom_bar() + coord_flip() +
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("meta.nonsig", "meta.sig")) +
+  annotate("text", x = sig.meta.count.c[sig.meta.count.c$sig.meta.analysis == 0,]$meta.analysis.method, y = 100000, 
+           label = paste(sig.meta.count.c[sig.meta.count.c$sig.meta.analysis == 0,]$n, "nonsig."), 
+           color = "white")
+
+#Change in significance after meta-analysis, separated by significant effect size estimate
+sig.meta <- data.mly %>% 
+  select(meta.id, study.id, sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
+  gather(key = "meta.analysis.method", value = "sig.meta.analysis", sig.fixef:sig.ranef.hkn) %>% mutate(sig.meta.analysis = factor(sig.meta.analysis))
+
+# duplicate.studies <- data.mly %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr, study.name) %>% 
+#   count() %>% filter(n > 1) #Merging is not possible for these since studies bear multiple results, but are not distinguishable and are multiplied while merging.
+
+sig.meta.plot <- merge(y = select(data.ext, meta.id, study.id, sig.type), 
+                       x = sig.meta, by = c("meta.id", "study.id")) %>% 
+  mutate(sig.type = factor(sig.type))
+
+sig.meta.count <- sig.meta.plot %>% 
+  group_by(sig.meta.analysis, meta.analysis.method, sig.type) %>% count()
+
+sig.meta.plot1 <- sig.meta.plot %>% filter(sig.type == 1) %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
+  geom_bar() + coord_flip() + ggtitle("Significant results") + theme(legend.position = "top") +
+	guides(fill=guide_legend(title=NULL)) + 
+  xlab(label = NULL) + scale_fill_discrete(labels= c("Significant", "Non-significant")) +
+  annotate("text", x = sig.meta.count[which(sig.meta.count$sig.type == 1)[1:3],]$meta.analysis.method, y = 30000, 
+           label = paste(sig.meta.count[which(sig.meta.count$sig.type == 1)[1:3],]$n, "changed to nonsig."), 
+           color = "white")
+
+nonsig.meta.plot <- sig.meta.plot %>% filter(sig.type == 0) %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
+  geom_bar() + coord_flip() + ggtitle("Non-significant results") + theme(legend.position = "top") +
+	guides(fill=guide_legend(title=NULL)) + 
+  xlab(label = NULL) + scale_fill_discrete(labels= c("Significant", "Non-significant")) +
+  annotate("text", x = sig.meta.count[which(sig.meta.count$sig.type == 0)[4:6],]$meta.analysis.method, y = 100000, 
+           label = paste(sig.meta.count[which(sig.meta.count$sig.type == 0)[4:6],]$n, "changed to sig."), 
+           color = "white")
+
+p.secondary.over.meansig <- mly %>% filter(NA.sig.type != 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
+  geom_density(na.rm = T, position = "fill") + 
+  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+
 @
@@
 \begin{frame}{Cochrane Library Dataset}
-% \Sexpr{length(unique(data$file.nr))} systematic reviews with studies published until 2018.
-% 
-% \Sexpr{length(unique(data$study.name))} studies.
-% 
-% \Sexpr{dim(data)[1]} study results.
+\Sexpr{length(unique(data$file.nr))} systematic reviews with studies published until 2018.
+
+\Sexpr{length(unique(data$study.name))} studies.
+
+\Sexpr{dim(data)[1]} study results.
 \end{frame}
@@
 
-\begin{frame}{Pooling studies}
-Studies of the same outcome, comparison and subgroup can be pooled by meta analyis.
+\begin{frame}{Pooling studies - Meta-analysis}
+Possible if results have same outcome, comparison and subgroup.
 
@@
 
-Distort findings of meta-analyses.
+Leads to biased results of meta-analysis.
+\end{frame}
+
+\begin{frame}{Publication Bias Tests}
+Test for funnel plot asymmetry:
+
+\vspace{-1cm}
+\begin{figure}[fragile]
+<<echo=FALSE, fig.height = 3, fig.width = 4 >>=
+funnel(meta.example)
+@
+\end{figure}
+\end{frame}
+
+\begin{frame}{Publication Bias Tests}
+Critical: Number of studies in meta-analysis must be large (>10).
+
+Various tests for meta-analyses with continuous and binary outcomes:
+
+Regression based: Egger's, Peter's or Thompson and Sharp's test
+
+Rank based: Begg and Mazumdar's Test
+\end{frame}
+
+\begin{frame}{Publication Bias in Cochrane Library}
+Publication bias tests applied for any meta analysis with n > 10
+
+\vspace{-1.7cm}
+\begin{figure}[fragile]
+<<echo=FALSE, fig.height = 3.1, fig.width = 6.5 >>=
+grid.arrange(p.bin, p.cont, ncol = 2)
+@
+\end{figure}
+\end{frame}
+
+\begin{frame}{Publication Bias}
+Publication bias variation for time and sample size
+\begin{figure}
+<<echo=FALSE, fig.height = 3.1, fig.width = 6.5 >>=
+grid.arrange(pbias.time, pbias.ss, ncol = 2)
+# pbias.time
+@
+\end{figure}
+\end{frame}
+
+\begin{frame}{Publication Bias Adjustment}
+Three approaches:
+
+Trim-and-fill: Non-parametric
+
+Copas: Selection modelling, estimation by sensitivity analysis
+
+Regression: Estimation of a treatment effect with infinite sample size
+\end{frame}
+
+\begin{frame}{Correction of significance}
+% Treatment effect significance change:
+
+%\vspace{-1.2cm}
+\begin{figure}[fragile]
+<<echo=FALSE, fig.height = 2.7, fig.width = 6.5, warning = FALSE>>=
+plot(p.fixef.change)
+@
+\end{figure}
+\end{frame}
+
+\begin{frame}{Corrected Significance for Biased Meta-Analyses}
+% Significance change for meta-analysis with signficant small study effect:
+
+%\vspace{-1.2cm}
+\begin{figure}[fragile]
+<<echo=FALSE, fig.height = 2.7, fig.width = 6.5, warning = FALSE>>=
+plot(p.change.fixef.bias)
+@
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Corrected Significance for Unbiased Meta-Analyses}
+% Significance change for meta-analysis with non-signficant small study effect:
+
+%\vspace{-1.2cm}
+\begin{figure}[fragile]
+<<echo=FALSE, fig.height = 2.7, fig.width = 6.5, warning = FALSE>>=
+plot(p.change.fixef.unbias)
+@
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Significance of different Estimates}
+Significance of random, fixed effects and adjusted meta-analyses:
+
+%\vspace{-1.2cm}
+\begin{figure}[fragile]
+<<echo=FALSE, fig.height = 2.7, fig.width = 6.5, warning = FALSE>>=
+plot(p.significance)
+@
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Significance separated for biased and unbiased meta-analyses}
+% Significance of random, fixed effects and adjusted meta-analyses:
+
+%\vspace{-1.7cm}
+\begin{figure}[fragile]
+<<echo=FALSE, fig.height = 3.6, fig.width = 6.7, warning = FALSE>>=
+grid.arrange(p.significance.bias, p.significance.unbias, ncol = 2)
+@
+\end{figure}
+\end{frame}
+
+\begin{frame}{Significance after meta-analysis}
+
+%\vspace{-1.7cm}
+\begin{figure}[fragile]
+<<echo=FALSE, fig.height = 3.6, fig.width = 6.7, warning = FALSE>>=
+grid.arrange(sig.meta.plot1, nonsig.meta.plot, ncol = 2)
+@
+\end{figure}
+\end{frame}
+
+\begin{frame}{Significance after meta-analysis}
+
+%pace{-1.7cm}
+\begin{figure}[fragile]
+<<echo=FALSE, fig.height = 2.1, fig.width = 4, warning = FALSE>>=
+plot(p.secondary.over.meansig)
+@
+\end{figure}
 \end{frame}

### 2019-04-29 report/MSc_Report.tex
Presentation upload

@@
 
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}mutate\_"{}): no applicable method for 'mutate\_' applied to an object of class "{}function"{}}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pb.meta.merge(meta.bin, meta.cont): could not find function "{}pb.meta.merge"{}}}\end{kframe}
+\end{knitrout}
+
 \chapter{The Cochrane Dataset}
+
+\section{Cochrane Systematic Reviews}
+As has been mentioned before, the Cochrane Group has specialized on systematic reviews in clinical science.
+Certain knowledge of standards and principles of the Cochrane Group may help to assess the quality and the properties of the dataset.
+The following information stems from the Cochrane Handbook for Systematic Reviews \citep{cochrane.handbook}.
+
+\vspace{0mm}
+The definition of a systematic review is that it ``attempts to collate all empirical evidence that fits pre-specified eligibility criteria in order to answer a specific research question.'' Thus, the ``key properties of a review are'':
+
+\begin{itemize}
+\item``a clearly stated set of objectives with pre-defined eligibility criteria for studies''
+\item ``an explicit, reproducible methodology''
+\item ``a systematic search that attempts to identify all studies that would meet the eligibility criteria''
+\item ``an assessment of the validity of the findings of the included studies, for example through the assessment of risk of bias''
+\end{itemize}
+
+At the end of a systematic review, ``a systematic presentation, and synthesis, of the characteristics and findings of the included studies'' is done.
+
+\vspace{0mm}
+53 Cochrane Review Groups prepare and maintain the reviews within specific areas of health care.
+A group consists of ``researchers, healthcare professionals and people using healthcare services (consumers)''.
+
+\vspace{0mm}
+The groups are supported by Method Groups, Centres and Fields.
+The Cochrane Method Groups aim to discuss and consult the groups in methodological questions concerning review preparation.
+The Centres play a main role in training and support of the Groups.
+The Fields are responsible for broad medical research areas and follow priorities in those areas by advice and control of the groups.
+
+\vspace{0mm}
+The first step in a review is writing a protocoll, specifying the research question, the methods to be used in literature search and analysis and the eligibility criteria of the study.
+Changes in protocolls are possible but have to be documented and the protocol is published in advance of the publication of the full review.
+The choices of methodology as well as the changes should not be made ``on the basis of how they affec the outcome of the research study''.
+
+\vspace{0mm}
+In order to avoid potential conflicts of interests, there is a code of conduct that all entities of the Cochrane Organization have to agree on: conflicts of interest must be disclosed and possibly be forwarded to the Cochrane Centre, and participation of review authors in the studies used have to be acknowledged.
+Additionally, a Steering Group publishes a report of potential conflicts of interests based on information about external funding of Cochrane Groups.
+
+\vspace{0mm}
+In order for keeping the reviews up-to-date, they are revised in a two-year cicle with exceptions.
+In addition to inclusion of new evidence in a field, the revision and maintenance process may as well includes change in analysis methods.
+This can reflect some advance in clinical science as for example new informations about important subgroups, as well as new methods for conducting a Cochrane Review.
+However, there are no clear guidelines and the Cochrane Groups are free in the rate and extent of up-dating their reviews.
+
+\subsection{Methods for Cochrane Reviews}
+A research question defines the following points: ``the types of population (participants), types of interventions (and comparisons), and the types of outcomes that are of interest''.
+From the research question, ususally the eligibility criteria follow.
+Usually, outcomes are not part of eligibility criteria, except for special cases such as adverse effect reviews.
+
+\vspace{0mm}
+The type of study is an important eligibility criterium.
+The Cochrane Collaboration focuses ``primarily on randomized controlled trials'', and also, the methods of study identification in literature search are focused on randomized trials.
+Furthermore, study characteristics such as blinding of study operators with respect to treatment and cluster-randomizing might be additional eligibility criteria which have to be chosen by the review authors.
+
+\vspace{0mm}
+After having specified the eligibility criteria, studies have to be collected.
+The central idea of systematic reviews, and also meta-analyses, is that the collected studies are a random sample of a population of studies, i.e.
+that they are representative and can be used to assess population properties.
+Therefore, the search process is crucial, as a selective search result may impose bias on the sample of studies available, making it a non-random sample.
+For this purpose, the Cochrane Groups are advised to go beyond MEDLINE !!cite!!, because a search restricted to it has been shown to deliver only 30\% to 80\% of available studies.
+``Time and budget restraints require the review author to balance the thoroughness of the search with efficiency in use of time and funds and the best way of achieving this balance is to be aware of, and try to minimize, the biases such as publication bias and language bias that can result from restricting searches in different ways.'' It is important to note that not only studies, but also study reports are occasionally used in the reviews, as they may provide useful information.
+
+\vspace{0mm}
+There are different sources that are being used to search for studies. 
+\begin{itemize}
+\item The Cochrane Central Register of Controlled Trials is a source of reports of controlled trials.
+``As of January 2008 (Issue 1, 2008), CENTRAL contains nearly 530,000 citations to reports of trials and other studies potentially eligible for inclusion in Cochrane reviews, of which 310,000 trial reports are from MEDLINE, 50,000 additional trial reports are from EMBASE and the remaining 170,000 are from other sources such as other databases and handsearching.'' It includes citations published in many languages, citations only available in conference proceedings, citations from trials registers and trials results registers.
+\item MEDLINE.
+MEDLINE includes over 16 million references to journal articles.
+5,200 journals publishing in 27 languages are indexed for MEDLINE.
+PubMed gives access to a free version of MEDLINE with up-to-date citations.
+NLM gateway such as the Health Services Research Project, Meeting Abstracts and TOXLINE Subset for toxicology citations allows for search in both databases together with additional data from the US National Library of Medicine.
+\item EMBASE.
+4,800 Journals publishing in 30 languages are indexed to EMBASE, which includes more than 11 million records from 1974 onwards.
+EMBASE.com also includes 7 million unique records from MEDLINE (1966 up to date) together with its own records.
+Additionally, EMBASE Classic allows access to digitized records from 1947 to 1973.
+EMBASE and MEDLINE each have around 1,800 journals not indexed in the other databse.
+\item Regional or national and subject specific databases can additionally be consulted and often provide important information. Financial considerations may limit the use of such databases.
+\item General search engines such as Google Scholar, Intute and Turning Research into Practice (TRIP) database can be used.
+\item Citation Indexes.
+The database lists articles published in around 6,000 Journals with articles in which they have been cited and is available online as SciSearch.
+This form of search is known as cited reference searching.
+\item Dissertation sources. Dissertations are often listed in MEDLINE or EMBASE but one is advised to also search in specific dissertation sources.
+\item Grey Literature Databases.
+Approximately 10\% of the results in the Cochrane Database stems from conference abstracts and other grey literature.
+The Institute for Scientific and Technical Information in France provides access to entries of the previously closed System for Information on Grey Literature database of the European Association for Grey Literature Exploitation).
+Another source is the Healthcare Management Information Consortium (HMIC) database containing records from the Library and Information Services department of the Department of Health (DH) in England and the King's Fund Information and Library Service.
+The National Technical Information Service (NTIS) gives access to the results of US and non-US government-sponsored research, as well as technical report for most published results.
+References from newsletters, magazines and technical and annual reports in behavioral science, psychology and health are provided in the PsycEXTRA database which is linked to PsycINFO database.
+\end{itemize}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:26:47 2019
+% Mon Apr 29 12:57:33 2019
 \begin{table}[ht]
@@
 \section{Meta-analysis}
-The data at hand is composed of over 400,000 comparisons with balanced sample size $n > 24$, which has been chosen as a threshold to assess the significance of treatment effect.
-The significance of the p-values of treatment effect estimates was calculated for all comparisons in the dataset with acceptable sample size and outcome measures as odds ratios, risk ratios, risk differences and mean and standardized mean differences.
-This led to somewhat more than 400,000 significance test results.
-Since most of the times, the study publication year is available, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}
-
-}
-
-\end{knitrout}
-\caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
-\label{study.significance.overtime}
-\end{figure}
-
-It is possible to analyse all studies with one or more replica by meta-analysis.
-There are different meta-analys methods that can be applied.
-While fixed effects meta-analysis pools the estimates and their variance, random effects meta-analysis additionally estimates the between study variances and adds this variance to the pooled within-study variances when assessing the uncertainity of the pooled effect estimate.
-The Hartung and Knapp adjustment of p-values and confidence intervals for random effects meta-analysis is more conservative than random-effects meta-analysis and will yieild less significant results than the latter.
-
-\vspace{0mm}
-In the following, the study results are combined with the results of their corresponding meta-analysis.
-Thus, every study that has one or more replicate was analysed by meta-analysis.
-In the following, the significance of the study, the primary significance, is compared with the significance of the meta-analysis or secondary significance.
-
-\vspace{0mm}
+The data at hand is composed of over 400,000 results with balanced sample size $n > 24$.
+The significance of the p-values of treatment effect estimates was calculated for all results in the dataset with acceptable sample size and outcome measures as odds ratios, peto odds ratios, risk ratios, risk differences and mean and standardized mean differences.
+
+%Significance over time? Chunck 1
+
+It is possible to analyse all results that are not unique in their comparison, outcome and subgroup in the dataset by meta-analysis.
+So each study that has been repeated with respect to experimental setup is included.
+There are different meta-analys methods that can be applied, here, fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis using the Hartung-Knapp method are used.
+
+\vspace{0mm}
+In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e.
+if studies were not unique in the dataset with respect to their experimental setup).
+The significant of the treatment effect in a single result is then compared to the significance of the pooled treatment effect.
 In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
 The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure.
-One can see the overall fraction of rejected null-hypotheses of no treatment effect.
+The colors indicate the overall fraction of rejected or accepted null-hypotheses of no treatment effect.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-14-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}
 
@@
 
-One can visualise the fraction of studies with significant treatment effect separately for studies with significant primary treatment effect, i.e.
-non-pooled effect, and non-significant primary treatment effect.
-This can be seen in Figure \ref{primary.secondary.significance.sep.sig}.
-One can see that primary significance and non-significance is often overruled when performing a meta-analysis.
+One can visualise the fraction of studies with significant treatment effect separately for studies with significant primary treatment effect, and non-significant primary treatment effect, as done in Figure \ref{primary.secondary.significance.sep.sig}.
+It can be seen that primary significance and non-significance is often overruled when performing a meta-analysis.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-15-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-14-1}
 
@@
 
-The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
-Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
-The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested.
-This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-16-1}
-
-}
-
-\end{knitrout}
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance.sep.sig}
-\end{figure}
+The amount of significant heterogeneity in the results used by the meta-analyses is 53350 and corresponds to 81.5936377\% of the total number of meta-analyses.
+
+%Comparison of significance separated for significant Q? Chunck 2
+
+%Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5
 
 \section{Small study effects}
-One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
-If this is not given, one often speaks of publication bias.
-In fact, there can also be other reasons for this (see discussion section).
-A more appropriate term for the phenomenon is small study effect.
-If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
-
-\vspace{0mm}
-To provide an overview over the issue, first it is shown how median absolute effect size decreases with increasing sample size of the comparisons in Figure \ref{effect.samplesize}.
-In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.
-
-\vspace{0mm}
-A clear trend of decrease of absolute effect size with increasing sample size (i.e.
-smaller variance) is visible.
-It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off.
+
+To provide an overview over the abundance of small study effects in the dataset, first it is shown how median absolute effect size decreases with increasing sample size of the results (Figure \ref{effect.samplesize}).
+%In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.
+
+\vspace{0mm}
+A clear trend of decrease of absolute effect size with increasing sample size (i.e. smaller variance) is visible. 
+%It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off.
 With increasing sample size, there are fewer results, therefore, the variation between medians increases.
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-16-1}
 
@@
 
-The median absolute normalized effect size can be visualized for the different outcome measures separately.
-Then it is well visible in Figure \ref{effect.samplesize.separated} that the trend of effect size decrease holds in particualar for risk and odds ratios, while it is way more stable for mean differences and standardized mean differences.
-Instead of normalizing the effects (i.e.
-subtracting mean and dividing through the standard deviation) for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.
+The median absolute normalized effect size can be visualized for the different outcome measures separately (Figure \ref{effect.samplesize.separated}).
+The plot confirms the trend of median effect size decrease towards lower sample size (e.g.
+for Risk Ratios: decrease $> 0.1$ standard deviations from 10 to 50 study participants).
+Instead of normalizing the effects
+%(i.e. subtracting mean and dividing through the standard deviation) 
+for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
 
@@
 
-% A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
-This can again be done for the entire dataset, i.e.
-for all effect estimates and their ordering in time.
-It is important to scale the effect estimates here with respect to the estimates of the replication studies that are about the same subject, have the same outcome measure, etc.
-Also, only effect estimates that can be compared to other estimates before are included, i.e.
-only study results with one or more replica are included.
-Time needs to be scaled and normalized in order to compare multiple time-trends in effect size to each other and gain insights in the overall trend.
-This is done in Figure \ref{effects.overtime.separated}, separared for odds rati, risk ratio, and mean and standardized difference outcome measures.
-In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
-%                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
-%   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
-%   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
-%   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
-%   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
-%   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
-% @
-% \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
-% \label{effects.overtime.separated}
-% \end{figure}
-
-% It is also possible to look how the amount of meta-analysis with significant pooled effect size estimates changes over time, e.g.
-mean publication year (of studies included in the meta-analysis).
-0.05 is used here as the threshold for $p$-value significance and subsequent null-hypothesis rejection.
-To constrict random fluctuation in the proportion, only mean publication years with a certain amount of meta-analyses are shown ($n < 180$).
-The $p$-value of the fixed effects meta analysis model is used to decide about rejection of the null-hypothesis.
-As Figure \ref{treatment.effect.significance.overtime} shows, the proportion of meta-analyses with significant treatment effect estimates stays roughly constant over time.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
-%   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% @
-% \caption{Proportion of significant treatment effect estimates over time (mean publication year).}
-% \label{effect.samplesize}
-% \end{figure}
-%
+%Show absolute effect size depending on scaled time? Chunck 3
 
@@
 The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3442).
+The amount of studies varies from 5\% (Schwarzer's Test) to 13 \% (Egger's Test) for binary outcomes and 9\% (Begg and Mazumdar's Test) to 25 \% (Egger's Test) for continuous outcomes.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
 
@@
 
-The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
-This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-\label{bias.results.cont.sep}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-\label{bias.results.bin.sep}
-\end{figure}
+There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not.
+Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by 0.0768414 (the minimal increase is 0.0103761 for Schwarzer's Test).
+
+%Show plots of significant meta-analyses separated? Chunck 4
 
@@
 The Figure suggests that the frequency of publication bias remains constant over time.
-The mean publication years have been restricted such that at least 180 meta-analyses are available per year such that random fluctuation is restricted to some extent.
+The mean publication years have been restricted such that at least 180 meta-analyses are available per year, such that random fluctuation is restricted to some extent.
 The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-24-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:27:29 2019
+% Mon Apr 29 12:58:07 2019
 \begin{table}[ht]
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-24-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-25-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-29-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-26-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-30-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-31-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-32-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-29-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-33-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-30-1}
+
+}
+
+\end{knitrout}
+\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
+\label{significance.change.random}
+\end{figure}
+
+Because the real amount of publication bias in the dataset is not known, the correction method can also be applied only to meta-analyses that have publication bias according to the small study effect tests in the previous section.
+Because the test developed by \citet{thomson.sharp} has been applied to both binary and continuous outcome meta-analyses (in the case of binary outcomes to arcsine variance stabilized proportions), it is used as a criterium to distinguish biased from unbiased meta-analyses.
+The proportions of significance tests of pooled treatment effects that turned from significant to non-significant, non-significant to significant etc.
+are shown in Figure \ref{significance.change.fixed.sep}.
+Fixed effects meta-analysis has been used to determine signficance of the uncorrected estimate.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-31-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-34-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-32-1}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Since most of the times the study publication year is available for a given result, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.
+The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
+%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
+% @
+% \caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
+% \label{study.significance.overtime}
+% \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 2
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
+Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
+The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested.
+This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(sig.meta.Q1, nonsig.meta.Q, ncol= 1)
+% @
+% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
+The fractions have been calculated
+% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+% \label{primary.secondary.significance.sep.sig}
+% \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 3
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
+This can again be done for the entire dataset, i.e.
+for all effect estimates and their ordering in time.
+It is important to scale the effect estimates here with respect to the estimates of the replication studies that are about the same subject, have the same outcome measure, etc.
+Also, only effect estimates that can be compared to other estimates before are included, i.e.
+only study results with one or more replica are included.
+Time needs to be scaled and normalized in order to compare multiple time-trends in effect size to each other and gain insights in the overall trend.
+This is done in Figure \ref{effects.overtime.separated}, separared for odds rati, risk ratio, and mean and standardized difference outcome measures.
+In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
+%                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
+%   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
+%   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
+%   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
+%   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
+%   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
+% @
+% \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
+% \label{effects.overtime.separated}
+% \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 4
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
+This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(p3, p4, ncol = 2)
+% @
+% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
+% \label{bias.results.cont.sep}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(p1, p2, ncol = 2)
+% @
+% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
+% \label{bias.results.bin.sep}
+% \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% #Proportion of significant pooled estimates based on proportion of single pooled estimates
+% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type)) + geom_histogram()
+% 
+% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
+%   geom_density(na.rm = T, position = "fill") + 
+%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+% 
+% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
+%   geom_histogram(position = "fill")
+% 
+% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef))) + 
+%   geom_histogram()
+
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(p.secondary.over.meansig)
+% @
+% \caption{Fraction of significant meta-analysis, dependent on the fraction of significant single results.}
+% \label{secondary.significance.over.meansig}
+% \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Small Study Effects Tests}
+One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
+If this is not given, one often speaks of publication bias.
+In fact, there can also be other reasons for this (see discussion section).
+A more appropriate term for the phenomenon is small study effect.
+If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
+
 \subsection{Continuous Outcome Tests}

### 2019-04-29 report/chapter02?.Rnw
Presentation upload

--- 2019-04-25 report/MSc_Report.tex
@@
-\documentclass[11pt,a4paper,twoside]{book}\usepackage[]{graphicx}\usepackage[]{color}
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
+% LaTeX file for Chapter 02
+
+<<echo=FALSE>>=
+library(knitr)
+opts_chunk$set(
+    fig.path='figure/ch02_fig',
+    self.contained=FALSE,
+    cache=TRUE
+)
+@
+
+<<echo=FALSE>>=
+library(knitr)
+opts_chunk$set(fig.path='figure/ch02_fig',
+               echo=TRUE, message=FALSE,
+               fig.width=8.1, fig.height=3,
+               out.width='\\textwidth-3cm',
+               message=FALSE, fig.align='center',
+               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
+               cache=TRUE
+)
+options(width=74)
+@
+
+<<echo = FALSE>>=
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+data = pb.readData(path = PATH_DATA, file = FILE)
+tmp = pb.clean(data)
+data = tmp[[1]]
+aliases = tmp[[2]]
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+  load(file.path(PATH_RESULTS, file.bin))
+} else { 
+  meta.bin <- meta.bin.complete(data, min.study.number = 10, sig.level = 0.05)
+  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
 }
-\makeatother
 
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+  load(file.path(PATH_RESULTS, file.cont))
+} else { 
+  meta.cont <- meta.cont.complete(data, min.study.number = 10, sig.level = 0.05)
+  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
 
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
+meta <- pb.meta.merge(meta.bin, meta.cont)
 
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+file.cont <- "mly.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+  load(file.path(PATH_RESULTS, file.cont))
+} else { 
+  data.cont <- mly.cont(data.ext, 0.05, min.study.number = 2)
+  save(data.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
 
-\usepackage{alltt}
-\input{header.sty}   % packages, layout and standard macros
+file.bin <- "mly.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+  load(file.path(PATH_RESULTS, file.bin))
+} else { 
+  data.bin <- mly.bin(data.ext, 0.05, min.study.number = 2)
+  save(data.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
 
-\usepackage{verbatim}
-\usepackage{tikz}
-\usepackage{amssymb}
-\usetikzlibrary{trees}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\begin{document}
-\input{title}
+load(file.path(PATH_RESULTS, file = "mly.RData"))
+load(file.path(PATH_RESULTS, file = "data.processed.RData"))
 
-\graphicspath{{./figure/}}
-\DeclareGraphicsExtensions{.pdf,.png}
-\setcounter{tocdepth}{1}
+require(biostatUZH)
+require(tidyverse)
+require(meta)
+require(metasens)
+require(gridExtra)
+require(xtable)
 
-\thispagestyle{empty}
-\begin{center}
-  \vspace*{6cm}{\bfseries\Huge
-  $p$-values:\\[5mm] their use, abuse and proper use \\[5mm]
-  illustrated with seven facets 
-  }
-  \vfill
-  \rm
+###################################################################################################################
+###################################################################################################################
 
-  \LARGE
-  M\"axli Musterli\\[12mm]
+#Barbiturate Examples
+barbi1 <- arrange(filter(data, file.nr == 21) %>% 
+          select(Study = study.name, Comparison = comparison.name, Outcome = outcome.name, 
+                 Events = events1, Total = total1, Events_c = events2, Total_c = total2) %>% 
+            slice(c(1,3)), Study) 
+barbi2 <- arrange(filter(data, file.nr == 21) %>% 
+          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study)
+barbi2[barbi2$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
 
-  \normalsize
-  Version \today
-\end{center}
-\newpage
-\thispagestyle{empty}~
-\newpage
-\pagenumbering{roman}
+#Missing values
+cont.out <- data %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
+                                 outcome.measure.new == "Hedges' G")
 
-\thispagestyle{plain}\markboth{Contents}{Contents}
-\tableofcontents
-\setkeys{Gin}{width=.8\textwidth}
+missing.mean <- which(is.na(cont.out$mean1) | is.na(cont.out$mean2))
+missing.effect <- which(is.na(cont.out$effect))
+missing.means <- intersect(missing.mean, missing.effect) #Cont. results that have neither complete means nor an effect
+wrong.effect <- which(cont.out$mean1 == 0 & cont.out$mean2 == 0 & cont.out$effect == 0) #Cont.results that have only zeros
+missing.effects <- length(c(missing.means, wrong.effect))
 
-\chapter*{Preface}
-\addtocontents{toc}{\protect \vspace*{13.mm}}
-\addcontentsline{toc}{chapter}{\bfseries{Preface}}
-\thispagestyle{plain}\markboth{Preface}{Preface}
+missing.sd <- which(is.na(cont.out$sd1) | is.na(cont.out$sd2))
+missing.se <- which(is.na(cont.out$se))
+missing.sds <- intersect(missing.se, missing.sd) #Cont. results that have neither complete means nor an effect
+wrong.sds <- which(cont.out$sd1 == 0 & cont.out$sd2 == 0 & cont.out$se == 0) #Cont.results that have only zeros
+missing.sds <- length(c(missing.sds, wrong.sds))
 
-Howdy!
+missing.ss <- which(is.na(data$total1) | is.na(data$total2))
+wrong.ss <- which(data$total1 <= 0 | data$total2 <= 0)
+missing.ssize <- length(c(missing.ss, wrong.ss))
 
-\bigskip
+missing.year <- sum(is.na(data$study.year)) + length(c(which(data$study.year < 1920), which(data$study.year > 2019)))
 
-\begin{flushright}
-  Max Muster\\
-  June 2018
-\end{flushright}
+missing.table <- rbind("Missing mean values and mean differences" = missing.effects,
+                         "Missing standard deviations and standard errors" = missing.sds,
+                         "Missing sample sizes" = missing.ssize,
+                         "Missing study year" = missing.year)
 
-\addtocontents{toc}{\protect \vspace*{10mm}}
+#Mean and median number of different outcome types of reviews
+mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
+  ungroup() %>% group_by(file.nr) %>%
+  count() %>% ungroup %>% summarise(mean = mean(n))
 
-\cleardoublepage
-\pagenumbering{arabic}
+median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
+  ungroup() %>% group_by(file.nr) %>%
+  count() %>% ungroup %>% summarise(mean = median(n))
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+#Study.year quantiles:
+data.ext <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
+publication.year.range <- c(quantile(data.ext$study.year, 0.05, na.rm = T), quantile(data.ext$study.year, 0.25, na.rm = T), 
+                            quantile(data.ext$study.year, 0.5, na.rm = T), quantile(data.ext$study.year, 0.75, na.rm = T),
+                            round(mean(data.ext$study.year, na.rm = T), 2))
 
-% LaTeX file for Chapter 01
+#Outcome.measure frequency table:
+outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.new) %>% count() %>% 
+                                       arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9),
+                                     data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% 
+                                       ungroup() %>% filter(row_number() > 8) %>% 
+                                       summarise(outcome.measure.new = "other", n = sum(n)))
 
-\chapter{Introduction}
+outcome.measure.frequencies <- outcome.measure.frequencies %>% mutate(percentage = round(n/sum(n),3)*100)
+names(outcome.measure.frequencies) <- c("Outcome measure", "n", "Percentage")
+outcome.measure.frequencies$Percentage <- paste(outcome.measure.frequencies$Percentage, "%", sep = "")
 
-Meta-analysis is at the core of evidence based medicine because it allows to summarise evidence over multiple studies and provide a more broad view on success and effectivity of clinical treatments.
-The necessity of meta-analyses is also increased by the abundance of data and publications.
-Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to make decisions based on quantitative and scientific criteria.
+#Total and group size quantiles:
+data.ext <- data.ext %>% ungroup() %>%  mutate(total.n = total1 + total2)
+samplesize.range <- c(quantile(data.ext$total.n, 0.05, na.rm = T), quantile(data.ext$total.n, 0.25, na.rm = T), 
+                            quantile(data.ext$total.n, 0.5, na.rm = T), quantile(data.ext$total.n, 0.75, na.rm = T),
+                            round(mean(data.ext$total.n, na.rm = T), 2))
+treatment.group.size.range <- c(quantile(data.ext$total1, 0.05, na.rm = T), quantile(data.ext$total1, 0.25, na.rm = T), 
+                      quantile(data.ext$total1, 0.5, na.rm = T), quantile(data.ext$total1, 0.75, na.rm = T),
+                      round(mean(data.ext$total1, na.rm = T), 2))
 
-\vspace{0mm}
-For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention.
-However, the usefulness of meta-analysis does not restrict to clinical science, but to any empirical and quantiative science.
+#Frequencies of results:
+comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
+comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
+                      quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
+                      round(mean(comp.freq$n, na.rm = T), 2))
 
-\vspace{0mm}
-Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question.
-Meta-analysis can be applied to all studies that are approximately identical in their experimental setup and the way the outcome of the experiments is measured.
-In systematic reviews where meta-analyses are used, the conclusions are most often strongly based on the results and the interpretation of the meta-analysis.
+#Frequencies of studies:
+study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
+study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
+                      quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
+                      round(mean(study.freq$n, na.rm = T), 2))
 
-\vspace{0mm}
-However, there are problems that potentially limit the validity of meta-analysis; the number of studies available can be incomplete or the results of the studies can be biased.
-Some of those problems can be solved or asserted by special statistical methods.
+#Pooling studies
+cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
+  filter(n < 15) %>%
+  full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
+  ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
+# cum.repr.trials.nosub <- data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+#   filter(n < 15) %>%
+#   full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+#                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
+#   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
 
-\subsection{Small Study Effects or Publication Bias}
-When study sample size decreases, the probability of extreme and missleading results in a study increases.
-This becomes a problem if results are selectively published, and therefore available, based on their results.
-When this is the case, one speaks of a small study effect or of ``Publication bias''.
+# cum.repr.trials <- cbind(cum.repr.trials.nosub, cum.repr.trials.subg)[,c(1,3,6)]
 
-\vspace{0mm}
-The issue has been discussed extensively in the last years, most often in the context of what has came to be known as the replication crisis.
-The reasons for small study effects are manifold, but originate most often in the myopical acting of agents in science and the lack of statistical education.
-Studies are reported by scientists, published by journals and noticed by readers more often if their findigs are positive and find e.g.
-a substantive difference or effect.
-When doing a meta-analysis, one again obtains biased results.
-
-\vspace{0mm}
-The reason why that is less of an issue for larger studies is that extreme results are in general less likely and that due to larger effort, a result is published although there has been no clear and positive findings.
-
-\vspace{0mm}
-While there is generally no way to assert poor study quality, small study effect can in principle be asserted and corrected for statistically.
-This masters thesis will mainly be about statistical methods to detect and adjust for small study effects.
-It can furthermore be divided in two parts:
-\begin{itemize}
-\item Methodological part: Collection and discussion of statistical tests and correction methods for small study effects.
-\item Applied part: Application of the methods to studies of the Cochrane Library of systematic Reviews. Subsequent discussion of the implications
-of the results for clinical science.
-\end{itemize}
-
-In contrast to simulation studies, it is not possible to assess critical properties of the methods such as the power of a test, since the truth is not known.
-But based on the amount of data, one can of course try to make extrapolation to tendencies in clinical science in general.
-Moreover, it is still interesting to see how the methods behave in general, especially with respect to each other.
-It may, as an example, be possible to answer the question which statistical test is most conservative and which pooling method is most optimistic on average.
-Comparison with results from simulations may allow to speculate about the reasons when simulation and real world results diverge.
-
-\subsection{Cochrane and the Cochrane Database of Systematic Reviews}
-The Cochrane Organization has specialized on systematic reviews in clinical science.
-It publishes and maintains a library with a large number of systematic reviews that are available in some countries to the public.
-
-\vspace{0mm}
-The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite).
-
-\vspace{0mm}
-The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests.
-This might further improve the validity and precision of findings and conclusions that have been made based on this data.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 02
+colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
+@
 
@@
 \subsection{Structure and Content}
-The dataset consists of 5016 systematic reviews from the Cochrane Library with 52995 studies and 463820 results.
+The dataset consists of \Sexpr{length(unique(data$file.nr))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(data$study.name))} studies and \Sexpr{dim(data)[1]} results.
 A result compares clinical or medical interventions or treatments.
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:26:47 2019
-\begin{table}[ht]
-\centering
-\begingroup\scriptsize
-\begin{tabular}{lllrrrr}
-  \hline
-Study & Comparison & Outcome & Events & Total & Events\_c & Total\_c \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11 & 41 & 11 & 41 \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14 & 27 & 13 & 26 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Example of two results as given in the dataset.
+<<echo=FALSE, results = 'asis'>>=
+print(xtable(barbi1, label = "barbiturate.row", digits = 0,
+             caption = "Example of two results as given in the dataset.
 Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
-Further descriptive variables have been ommitted}
-\label{barbiturate.row}
-\end{table}
+Further descriptive variables have been ommitted"),
+      include.rownames = F, size = "scriptsize")
+@
 
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:26:47 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-Study & Comparison & Outcome \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given} 
-\label{barbiturates}
-\end{table}
+<<echo=FALSE, results='asis'>>=
+print(xtable(barbi2, label = "barbiturates", caption = "Barbiturate and head injury review.
+In the columns, study names, comparison and outcome measure of the results are given"), include.rownames = F, size = "footnotesize")
+@
 
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:26:47 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lr}
-  \hline
-  \hline
-Missing mean values and mean differences & 984 \\ 
-  Missing standard deviations and standard errors & 1300 \\ 
-  Missing sample sizes & 12173 \\ 
-  Missing study year & 44649 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Number of missing variables and measurements in the dataset} 
-\label{missing}
-\end{table}
+<<echo=FALSE, results='asis'>>=
+print(xtable(missing.table, label = "missing", caption = "Number of missing variables and measurements in the dataset", align = "lr"), include.colnames = F,
+      size = "footnotesize", digits = 0)
+@
 
-The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982).
-The median of the publication years is 2003, the mean 2006.13 and the quartiles are 1996 and 2008.
+The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = \Sexpr{publication.year.range[1]}).
+The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{publication.year.range[5]} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}.
 Only a handful ($n$ = 18) have been published in 2018, none in 2019.
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:26:47 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-Outcome measure & n & Percentage \\ 
-  \hline
-Risk Ratio & 232583 & 50.1\% \\ 
-  Mean Difference & 102315 & 22.1\% \\ 
-  Odds Ratio & 49372 & 10.6\% \\ 
-  Std. Mean Difference & 40535 & 8.7\% \\ 
-  Peto Odds Ratio & 19122 & 4.1\% \\ 
-  Hazard Ratio & 6566 & 1.4\% \\ 
-  Risk Difference & 6234 & 1.3\% \\ 
-  Rate Ratio & 2283 & 0.5\% \\ 
-  other & 4810 & 1\% \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Frequencies of outcome measures among results. n denotes the total number 
-             of results with the outcome measure and percentage the percentage of the outcome measure,} 
-\label{outcome.measure.frequencies}
-\end{table}
+<<echo=FALSE, results='asis'>>=
+print(xtable(outcome.measure.frequencies, label = "outcome.measure.frequencies", 
+             caption = "Frequencies of outcome measures among results. n denotes the total number 
+             of results with the outcome measure and percentage the percentage of the outcome measure,", 
+             align = "llll", digits = 1), include.rownames = F, size = "footnotesize")
+@
 
 The sample sizes amongst results vary to some extent.
-There are 5\% of treatment group sample sizes that are smaller tha 8, the 5\% quantile.
-The first quartile is 22, the median 48, the mean 302.03 and the third quartile 119.
+There are 5\% of treatment group sample sizes that are smaller tha \Sexpr{treatment.group.size.range[1]}, the 5\% quantile.
+The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{treatment.group.size.range[5]} and the third quartile \Sexpr{treatment.group.size.range[4]}.
 The large difference between median and mean is caused by very large groups with over 2,000,000 participants.
-Analogously, the quantiles of the total sample size are: 5\% quantile = 15, first quartile = 44, median = 94 and third quartile = 229.
-The mean is 617.81.
+Analogously, the quantiles of the total sample size are: 5\% quantile = \Sexpr{samplesize.range[1]}, first quartile = \Sexpr{samplesize.range[2]}, median = \Sexpr{samplesize.range[3]} and third quartile = \Sexpr{samplesize.range[4]}.
+The mean is \Sexpr{samplesize.range[5]}.
 
 \vspace{0mm}
-The mean and median number of results per review are 12.42 and 7.
-There are 417 reviews with five or fewer results, and the quartiles are 16 and 102.
-Similarly, the number of reviews with a maximum of two studies included is 836, the mean study number is 12.42, the median 7 and the interquartile range 4 and 15.
+The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}.
+There are \Sexpr{comp.range[1]} reviews with five or fewer results, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}.
+Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]}.
 The discrepancy between mean and median is again due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxisfor preventing infection after cesarean section, with 95 studies and 1497 results in total.
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:26:47 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-n & Number of groups & Cumulative sum of groups \\ 
-  \hline
-1 & 102344 & 186300 \\ 
-  2 & 31686 & 83956 \\ 
-  3 & 16072 & 52270 \\ 
-  4 & 9628 & 36198 \\ 
-  5 & 6444 & 26570 \\ 
-  6 & 4230 & 20126 \\ 
-  7 & 2961 & 15896 \\ 
-  8 & 2114 & 12935 \\ 
-  9 & 1592 & 10821 \\ 
-  10 & 1238 & 9229 \\ 
-  11 & 921 & 7991 \\ 
-  12 & 702 & 7070 \\ 
-  13 & 585 & 6368 \\ 
-  14 & 455 & 5783 \\ 
-  15 & 5328 & 5328 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Cumulative number of groups with number of reproduction trials >= n} 
-\label{repr.groups}
-\end{table}
+<<echo=FALSE, results='asis'>>=
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 03
-
-\chapter{Results}
-
-\section{Meta-analysis}
-The data at hand is composed of over 400,000 comparisons with balanced sample size $n > 24$, which has been chosen as a threshold to assess the significance of treatment effect.
-The significance of the p-values of treatment effect estimates was calculated for all comparisons in the dataset with acceptable sample size and outcome measures as odds ratios, risk ratios, risk differences and mean and standardized mean differences.
-This led to somewhat more than 400,000 significance test results.
-Since most of the times, the study publication year is available, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}
-
-}
-
-\end{knitrout}
-\caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
-\label{study.significance.overtime}
-\end{figure}
-
-It is possible to analyse all studies with one or more replica by meta-analysis.
-There are different meta-analys methods that can be applied.
-While fixed effects meta-analysis pools the estimates and their variance, random effects meta-analysis additionally estimates the between study variances and adds this variance to the pooled within-study variances when assessing the uncertainity of the pooled effect estimate.
-The Hartung and Knapp adjustment of p-values and confidence intervals for random effects meta-analysis is more conservative than random-effects meta-analysis and will yieild less significant results than the latter.
-
-\vspace{0mm}
-In the following, the study results are combined with the results of their corresponding meta-analysis.
-Thus, every study that has one or more replicate was analysed by meta-analysis.
-In the following, the significance of the study, the primary significance, is compared with the significance of the meta-analysis or secondary significance.
-
-\vspace{0mm}
-In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
-The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure.
-One can see the overall fraction of rejected null-hypotheses of no treatment effect.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-14-1}
-
-}
-
-\end{knitrout}
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance}
-\end{figure}
-
-One can visualise the fraction of studies with significant treatment effect separately for studies with significant primary treatment effect, i.e.
-non-pooled effect, and non-significant primary treatment effect.
-This can be seen in Figure \ref{primary.secondary.significance.sep.sig}.
-One can see that primary significance and non-significance is often overruled when performing a meta-analysis.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-15-1}
-
-}
-
-\end{knitrout}
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance}
-\end{figure}
-
-The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
-Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
-The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested.
-This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-16-1}
-
-}
-
-\end{knitrout}
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance.sep.sig}
-\end{figure}
-
-\section{Small study effects}
-One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
-If this is not given, one often speaks of publication bias.
-In fact, there can also be other reasons for this (see discussion section).
-A more appropriate term for the phenomenon is small study effect.
-If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
-
-\vspace{0mm}
-To provide an overview over the issue, first it is shown how median absolute effect size decreases with increasing sample size of the comparisons in Figure \ref{effect.samplesize}.
-In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.
-
-\vspace{0mm}
-A clear trend of decrease of absolute effect size with increasing sample size (i.e.
-smaller variance) is visible.
-It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off.
-With increasing sample size, there are fewer results, therefore, the variation between medians increases.
-All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation.
-Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
-
-}
-
-\end{knitrout}
-\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
-\label{effect.samplesize}
-\end{figure}
-
-The median absolute normalized effect size can be visualized for the different outcome measures separately.
-Then it is well visible in Figure \ref{effect.samplesize.separated} that the trend of effect size decrease holds in particualar for risk and odds ratios, while it is way more stable for mean differences and standardized mean differences.
-Instead of normalizing the effects (i.e.
-subtracting mean and dividing through the standard deviation) for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
-
-}
-
-\end{knitrout}
-\caption{Median of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
-\label{effect.samplesize.separated}
-\end{figure}
-
-% A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
-This can again be done for the entire dataset, i.e.
-for all effect estimates and their ordering in time.
-It is important to scale the effect estimates here with respect to the estimates of the replication studies that are about the same subject, have the same outcome measure, etc.
-Also, only effect estimates that can be compared to other estimates before are included, i.e.
-only study results with one or more replica are included.
-Time needs to be scaled and normalized in order to compare multiple time-trends in effect size to each other and gain insights in the overall trend.
-This is done in Figure \ref{effects.overtime.separated}, separared for odds rati, risk ratio, and mean and standardized difference outcome measures.
-In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
-%                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
-%   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
-%   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
-%   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
-%   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
-%   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
-% @
-% \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
-% \label{effects.overtime.separated}
-% \end{figure}
-
-% It is also possible to look how the amount of meta-analysis with significant pooled effect size estimates changes over time, e.g.
-mean publication year (of studies included in the meta-analysis).
-0.05 is used here as the threshold for $p$-value significance and subsequent null-hypothesis rejection.
-To constrict random fluctuation in the proportion, only mean publication years with a certain amount of meta-analyses are shown ($n < 180$).
-The $p$-value of the fixed effects meta analysis model is used to decide about rejection of the null-hypothesis.
-As Figure \ref{treatment.effect.significance.overtime} shows, the proportion of meta-analyses with significant treatment effect estimates stays roughly constant over time.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
-%   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% @
-% \caption{Proportion of significant treatment effect estimates over time (mean publication year).}
-% \label{effect.samplesize}
-% \end{figure}
-%
-
-\subsection{Small Study Effect Tests}
-
-There are tests that can be applied to find out if small study effects are present in the meta analysis.
-For the precise description, see the methods section.
-Application of the tests is only recommended if there are ten or more studies \citep{cochrane.handbook} that can be used, so all meta-analyses with less than ten studies have been excluded.
-
-\vspace{0mm}
-There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
-In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = 1383)
-The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3442).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-\label{bias.results.cont}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-\label{bias.results.bin}
-\end{figure}
-
-The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
-This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-\label{bias.results.cont.sep}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-\label{bias.results.bin.sep}
-\end{figure}
-
-Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses).
-The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}.
-The Figure suggests that the frequency of publication bias remains constant over time.
-The mean publication years have been restricted such that at least 180 meta-analyses are available per year such that random fluctuation is restricted to some extent.
-The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-24-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
-\label{pub.bias.overtime}
-\end{figure}
-
-The agreement of the tests, i.e.
-the proportion of meta-analyses where the rest results are equal between tests, is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
-Agreement in tests for binary outcomes is better than continuous outcomes, with some variation between tests (binary outcomes: 83 to 91\%).
-Correlation varies more between tests, both for continuous and binary outcome tests.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:27:29 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
- & Test Agreement & P-value Correlation \\ 
-  \hline
-egger.schwarzer & 0.87 & 0.39 \\ 
-  egger.peter & 0.89 & 0.51 \\ 
-  egger.rucker & 0.88 & 0.48 \\ 
-  egger.harbord & 0.93 & 0.76 \\ 
-  schwarzer.peter & 0.89 & 0.29 \\ 
-  schwarzer.rucker & 0.88 & 0.34 \\ 
-  schwarzer.harbord & 0.92 & 0.51 \\ 
-  rucker.peter & 0.92 & 0.67 \\ 
-  harbord.peter & 0.91 & 0.52 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)} 
-\label{agreement.bin}
-\end{table}
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:27:29 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
- & Test Agreement & P-value Correlation \\ 
-  \hline
-thomson.egger & 0.89 & 0.69 \\ 
-  thomson.begg & 0.82 & 0.47 \\ 
-  egger.begg & 0.79 & 0.36 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)} 
-\label{agreement.cont}
-\end{table}
-
-\vspace{0mm}
-Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
-The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}.
-%(Suggests that 10 is likely too small)
-In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
-A trend towards more rejections for larger sample sizes can be seen.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}
-
-}
-
-\end{knitrout}
-\caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
-\label{pvalues.samplesize}
-\end{figure}
-
-\vspace{0mm}
-One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
-The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.18.
-% A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
-In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses.
-In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
-In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}
-
-}
-
-\end{knitrout}
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
-\label{trimfill.pvalues.bin}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-29-1}
-
-}
-
-\end{knitrout}
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
-\label{trimfill.pvalues.cont}
-\end{figure}
-
-\subsection{Small Study Effect Correction}
-Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
-Three of them will be applied to the meta-analyses shown previously that have ten or more study results and are therefore eligible for testing for publication bias.
-
-\vspace{0mm}
-The extent to what the results of the meta-analysis results are changed can be investigated.
-Because statistical significance is often used to decide if there is a treatment effect, a non-significant corrected effect size estimate can indicate that an observed treatment effect has been accepted because of small study effects.
-Therefore, the cases have been counted in which
-\begin{enumerate}
-\item Significance or non-significance of pooled estimate of meta-analysis did not change after correction for small study effects.
-\item Significance of pooled estimate of meta-analysis did change to non-significance after correction for small study effects.
-\item Non-significance of pooled estimate of meta-analysis did change to significance after correction for small study effects.
-\end{enumerate}
-
-The results of this can be seen in Figure \ref{significance.change.fixed} for all three methods, comparing the significance of the corrected pooled effect size estimate with the significance of the pooled effect size estimate of the fixed effects meta-analysis.
-The same for significance of random effects meta-analysis is shown in Figure \ref{significance.change.random}.
-The significance threshold was chosen such that the $p$-value had to be < 0.05 for rejection of the null hypothesis of no treatment effect.
-The correction methods were trim-and-fill, copas selection model and regression with random effects and shrinkage of within-study-variance methods.
-More details to the applied correction methods and their application are in the methods section \ref{methods}.
-Notably, the correction methods has been applied to all meta-analyses, thus also for such that had no significant small study effect test result.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-30-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction.}
-\label{significance.change.fixed}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-31-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction.}
-\label{significance.change.random}
-\end{figure}
-
-Since it has been previously seen in Figure \ref{test.results} that the results of small study effects vary considerably between continuous outcomes, the results in significance change from fixed effects meta-analysis can be seen separately in Figure \ref{significance.change.fixed.sep} for continuous and binary outcomes.
-The change in significance from random effects meta-analysis to significance of corrected estimate can be seen in Figure \ref{significance.change.fixed.sep}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-32-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.fixed.sep}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-33-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.random}
-\end{figure}
-
-Similarly, the number of missing studies per meta-analysis, i.e.
-those which have not been included because of small study effects, are estimated by the copas and trim-and-fill method and their empirical distribution is shown in histograms in Figure \ref{missing.studies.distribution}.
-For visualisation, the fraction of unpublished studies from the total fraction of available studies is shown.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-34-1}
-
-}
-
-\end{knitrout}
-\caption{Fraction of missing studies estimated of the number of total studies included in the meta-analysis for copas selection and trim-and-fill method.}
-\label{missing.studies.distribution}
-\end{figure}
-
-% # <<results = 'asis', Echo = FALSE>>=
-% # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
-% #                                             schwarzer.rejection = mean(schwarzer.test),
-% #                                             rucker.rejection = mean(rucker.test),
-% #                                             harbord.rejection = mean(harbord.test),
-% #                                             peter.rejection = mean(peter.test))
-% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
-% # @
-
-% 
-% For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
-The following three figures show the distribution of p-values of the corresponding tests.
-Note that only meta analyses with more than 10 comparisons have been included.
-% 
-% \vspace{0mm}
-% Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
-The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "linreg")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
-% \label{egger.cont}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "mm")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
-% \label{thomson.cont}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "rank")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{begg.cont}
-% \end{figure}
-% 
-% 
-% For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-%   filter(events1 > 0 | events2 > 0) %>% 
-%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{peters.bin}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-%   filter(events1 > 0 | events2 > 0) %>% 
-%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{harbord.bin}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 04
-
-\chapter{Methods}
-
-\section{Basic notation}
-The notation used here will be used throughout the chapter and exceptions will be noted.
-Let $i$ be the number of a study of a meta analysis with $n$ being the total number of studies.
-$y_{i}$ is then the effect size estimate (usually log odds ratio or mean difference) and $v_{i}$ the variance of the estimate of study $i$.
-$w_{i}$ is used for weights which are defined when necessary, and $\Delta$ usually denotes the summarized or pooled effect estimate of the meta-analysis, and $\eta$ the variance thereof.
-
-\vspace{0mm}
-In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
-
-\section{Heterogeneity}
-In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
-This is called between study variation in contrast to within study variation (noise).
-
-\vspace{0mm}
-The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
-Let $w_i$ be the inverse of the variance and $\Delta$ be a summarized effect estimate of your choice as for example a variance-weighted mean \ref{weighted.mean}.
-Then $Q$ can be calculated as in \ref{Q.heterogeneity}
-
-\begin{align}
-\Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
-\end{align}
-
-Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
-Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
-$1 - F(Q)$ will provide the $p$-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
-
-\vspace{0mm}
-Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
-For this purpose, $\tau^2$, the variance of true effects, can be calculated.
-$\tau^2$ is on the same scale as the effect size and reflects the absolute amount of dispersion.
-In practice, $\tau^2$ can be smaller than zero, then it is set to zero.
-
-\begin{align}
-C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
-\tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
-\end{align}
-
-The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
-Note that their estimate can differ substantially and consequently also the estimate of the pooled effect size estimate.
-
-\vspace{0mm}
-To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
-
-\begin{align}
-I^2 &= (Q - n + 1)/Q \label{I2.proportion}
-\end{align}
-
-There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
-
-\section{Meta Analysis}
-There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
-First the fixed effect meta-analysis will be explained.
-Note that both methods can be used for continuous or dichotomous outcomes.
-For more details about the methods, see chapter 11 and 12 in \citet{metaanalysis}
-
-\vspace{0mm}
-Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
-The pooled estimate $\Delta_{f}$ of the fixed effects model is then the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
-The variance $\eta_{f}$ is the reciprocal of the sum of the weights as shown in \ref{reciproce.variance}.
-
-\begin{align}
-\Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-\eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
-\end{align}
-
-The computation of random effects meta-analysis is more complicated.
-Random effects meta-analysis will give smaller studies with larger variance more weight in the pooled estimate.
-Shortly, the idea is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
-
-\vspace{0mm}
-The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
-It is used to calculate a new weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
-The variance of $\Delta_{r}$, $\eta_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
-
-\begin{align}
-v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
-\Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
-\eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
-\end{align}
-
-A p-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
-
-\begin{align}
-Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
-p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
-\end{align}
-
-\section{Small Study Effects Tests}
-\subsection{Continuous Outcome Tests}
-% Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. 
-% First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
-
-\subsubsection{Begg and Mazumdar: Rank Correlation Test}
-\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
-A standardized effect size $y_{i}^\star$ can be computed as in \ref{begg.stand.eff}.
-$v_{i}^\star$ is the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
-$\Delta_{f}$ is the pooled estimate for fixed effect estimate defined in \ref{weighted.mean}.
-
-\begin{align}
-y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff} \\
-v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} 
-\end{align}
-
-A rank correlation test based on Kendall's tau is then used.
-The pairs $(y_{i}^\star, v_{i}^\star)$ that are ranked in the same order are enumerated.
-Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (e.g.
-larger standardized effect size and smaller variance).
-Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
-
-\begin{align}
-Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
-\end{align}
-
-The changes in the case of ties are negligible \cite[410]{begg.ties}.
-
-\subsubsection{Egger's Test: Linear Regression Test}
-Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
-Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope.
-
-\vspace{0mm}
-If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
-The p-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
-
-\begin{align}
-p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
-\end{align}
-
-\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test}
-A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
-Let $\tau^2$ be equal to \ref{Tau.definition}.
-The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
-
-\begin{align}
-y_{i} \sim N(\beta_{0} + \beta{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
-\end{align}
-
-Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
-Analogous to Edger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta{0} = 0$.
-
-\subsection{Dichotomous Outcomes Tests}
-
-The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
-Consequently, the tests above will tend to reject the null-hypothesis too often, i.e.
-that they are not conservative enough.
-A number of solutions to this problem are existing in the literature.
-
-\subsubsection{Peters Test: Weighted Linear Regression Test}
-A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
-
-\vspace{0mm}
-Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
-
-\begin{align}
-y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
-v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
-\end{align}
-
-and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
-Instead of taking the variance as explanatory or independent variable in regression as in Egger's Test, the inverse of the total sample size $x_{i}$ is used, and the variance $v_{i}$ is used as a weight.
-The subsequent test procedure is then identical to Egger's test.
-
-\vspace{0mm}
-Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
-
-\subsubsection{Harbord's Test: Score based Test}
-A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
-The score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
-
-\begin{align}
-r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
-v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
-\end{align}
-
-Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
-Note that $r_{i}/v_{i}$ is also known as peto odds ratio.
-
-\subsubsection{Schwarzer's Test: Rank Correlation Test}
-\citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
-$\mathbb{E}(E_{t})$ and variance of $E_{t}$ are then estimated based on $e_{t}$.
-
-\vspace{0mm}
-The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
-
-\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
-The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let
-
-\begin{align}
-y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}}// 
-v_{i} = 1/4n_{t} + +/4n_{c}
-\end{align}
-
-Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances.
-
-\section{Small Study Effect Adjustment}
-\subsection{Trim and Fill}
-One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
-It is a nonparametric test based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
-%If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
-
-\vspace{0mm}
-The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
-First, $\Delta$ is estimated using a fixed or random effects model.
-Then, the $k$ effect size estimates with the smallest standard errors are trimmed, and $\Delta$ is estimated again.
-The procedure is repeated until $k$ is 0 and the funnel plot is symmetric.
-The total number of missing studies is then mirrored with respect to the final effect size estimate $\Delta$, and $\Delta$ and its standard error is then computed to obtain an unbiased estimate.
-
-\subsection{Copas Selection Model}
-
-A method proposed in \cite{Copas1,Copas2,Copas3} assumes that there is a population of studies of which only a part has been published dependent on the variance and size of their estimated effects.
-Studies with small variance and large effect sizes are more likely to be published than studies with large variance and small effect sizes.
-Note that small effect size means here a treatment effect close to the control effect.
-
-Let $y_i$ be the effect size estimate of study $i$. Then
-
-\begin{align}
-y_{i} \sim N(\mu_{i}, \sigma_{i}^2) \\
-\mu_{i} \sim N(\mu, \tau^2)
-\end{align}
-
-corresponding to a standard random effects model.
-$\mu$ is the overall mean effect, $\sigma_{i}^2$ the within study variance and $\tau^2$ the between study variance.
-This is the \textit{population model}.
-
-\vspace{0mm}
-The \textit{selection model} is defined as follows. Suppose a selection of studies with reported standard errors $s$ (likely different from $\sigma$). Only a proportion
-
-\begin{align}
-P(\textrm{select}|s) &= \Phi(a + b/s) \label{copas.selection1}
-\end{align}
-
-of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
-\ref{copas.selection1} can be rewritten as
-
-\begin{align}
-z = a + b/s + \delta \label{copas.selection2}
-\end{align}
-
-with $\delta \sim N(0,1)$. The study with standard error $s$ is only selected if $z$ is positive. Therefore, the larger $z$, the more likely the study is selected.
-Combining population and selection model for study $i$, we have
-
-\begin{align}
-y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \\
-\mu_{i} \sim N(\mu, \tau^2) \\
-z_{i} = a + b/s_{i} + \delta_{i}
-\end{align}
-
-where $(\epsilon_{i}, \delta_{i})$ are standard normal residuals and jointly normal with correlation $\rho = cor(y_{i}, z_{i})$.
-Every given study $i$ in the meta-analysis has $z_{i} > 0$.
-If $\rho$ is large and positive and $z_{i} > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_{i}$ and $\delta_{i}$.
-Thus, the true mean $\mu$ is likely to be overestimated.
-
-\vspace{0mm}
-Let $u = a + b/s$, $\lambda(u) = \phi(u)/\Phi(u)$ ($\phi$ is the standard normal density function) and $\tilde{\rho} = \sigma/\sqrt(\tau^2 + \sigma^2) \rho$.
-The probability of a study being selected is
-
-\begin{align}
-P(\textrm{select}|s, y) = P(a,b,s,y) = \Phi(\frac{u + \tilde{\rho}((y - \mu)/\sqrt(\tau^2 + \sigma^2))}{\sqrt{1 - \tilde{\rho^2}}})
-\end{align}
-
-It can also be shown that the expected value
-
-\begin{align}
-\mathbb{E}(y|s, select) = \mu + \rho\sigma\lambda(u) \label{copas.expectation}
-\end{align}
-
-which shows that the expected value for a study is larger for larger $\sigma$.
-
-\vspace{0mm}
-One can compute a likelihood function based on the distribution of $y$ conditional on $z > 0$.
-The likelihood can be maximized for any given pair $a,b$ (can not be estimated since the number of missing studies is not known), and a maximum likelihood estimate $\hat{\mu}$ for the true mean $\mu$ can be obtained.
-One can then perform a sensitivity analysis.
-First, one looks how $\hat{\mu}$ changes for different values of $a,b$.
-One can then compare the fitted values in \ref{copas.expectation} with the real values.
-To test the fit of the model (while keeping all other parts unchanged), the model can be extended in the following way :
-
-\begin{align}
-y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
-\end{align}
-
-If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
-Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
-The p-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
-
-\vspace{0mm}
-To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
-
-\vspace{0mm}
-In practice, only a range of values for $a,b$ are reasonable.
-For those values, the quantities above can be calculated and illustrated.
-Values for $\mu$ that have p-values over a predefined significance threshold can be used for inference of the effect size.
-
-\subsection{Adjustment by Regression}
-There are multiple ways to adjust for small study effects by regression. The general idea is to regress the effect size of a study with a variance of zero based on the given effects and variances.
-
-\citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
-Similarly to what has been seen in Copas selection model, we let $y_{i}$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_{i}}$ as in \ref{limitmeta.regression}.
-
-\begin{align}
-y_{i}& = \beta_{0} + \beta{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \stackrel{\textrm{iid}}{\sim} N(0,1)  \ref{limitmeta.regression}
-\end{align}
-
-$\beta{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
-
-\begin{align}
-\mathbb{E}((y_{i} - \beta_{})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{if} \sqrt{v_{i}} \rightarrow \infty \\
-\mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
-\end{align}
-
-After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test.
-
-\vspace{0mm}
-To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
-
-\begin{align}
-y_{i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{s_{i}/M + \tau^2}) \label{limitmeta.regression}
-\end{align}
-
-Letting $M \rightarrow \infty$, we obtain:
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
-\end{align}
-
-Note that:
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
-\end{align}
-
-$\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
-
-\begin{align}
-\epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
-\end{align}
-
-Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-\end{align}
-
-By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
-
-% \begin{align} \label{cox reg}
-% P(Y < y|\mathbf{x}) = 1 - exp(-exp(h(y) - (\mathbf{x})^\top\beta)
-% \end{align}
-% 
-% See \cite{hothorn} for further information. It specifies the instantaneous risk of an event at time t to be
-% 
-% \begin{align}
-% \lambda_{0}(t)exp((\mathbf{x})^\top\beta) \nonumber
-% \end{align}
-% 
-% The model is regarded as a semi parametric model since it includes the covariates in a linear fashion but leaves the baseline hazard $\lambda_{0}(t)$ unspecified.
-The factor $exp((\mathbf{x})^\top\beta)$ has the interpretation of a hazard ratio between the reference with $\mathbf{x} = 0$.
-The formal definition of the hazard is
-% 
-% \begin{align}
-% h(t) = \lim_{h \to 0} \frac{P(t < T < t + h| T > t)}{h}
-% \end{align}
-% 
-% 
-% \begin{align} \label{generalized linear model}
-% \mathbf{Y}{_{ij}}|U{_i},\epsilon{_{ij}} = (1,x{_i}^\top)\beta + U{_i} + \epsilon{_{ij}}
-% \end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 05
-
-\chapter{Conclusions}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-% LaTeX file for Chapter 01
-
-\chapter{Appendix}
-
-Maybe some R code here, probably a \rr{sessionInfo()}
-
-\cleardoublepage
-\phantomsection
-\addtocontents{toc}{\protect \vspace*{10mm}}
-\addcontentsline{toc}{chapter}{\bfseries Bibliography}
-
-\bibliographystyle{mywiley} 
-\bibliography{biblio}
-
-\cleardoublepage
-
-\end{document}
+print(xtable(cum.repr.trials.subg, label = "repr.groups", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
+@

### 2019-04-29 report/chapter03.Rnw
Presentation upload

@@
 
+p.secondary.over.meansig <- mly %>% filter(NA.sig.type != 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
+  geom_density(na.rm = T, position = "fill") + 
+  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
 @
@@
 \section{Meta-analysis}
-The data at hand is composed of over 400,000 comparisons with balanced sample size $n > 24$, which has been chosen as a threshold to assess the significance of treatment effect.
-The significance of the p-values of treatment effect estimates was calculated for all comparisons in the dataset with acceptable sample size and outcome measures as odds ratios, risk ratios, risk differences and mean and standardized mean differences.
-This led to somewhat more than 400,000 significance test results.
-Since most of the times, the study publication year is available, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
+The data at hand is composed of over 400,000 results with balanced sample size $n > 24$.
+The significance of the p-values of treatment effect estimates was calculated for all results in the dataset with acceptable sample size and outcome measures as odds ratios, peto odds ratios, risk ratios, risk differences and mean and standardized mean differences.
 
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
-@
-\caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
-\label{study.significance.overtime}
-\end{figure}
+%Significance over time? Chunck 1
 
-It is possible to analyse all studies with one or more replica by meta-analysis.
-There are different meta-analys methods that can be applied.
-While fixed effects meta-analysis pools the estimates and their variance, random effects meta-analysis additionally estimates the between study variances and adds this variance to the pooled within-study variances when assessing the uncertainity of the pooled effect estimate.
-The Hartung and Knapp adjustment of p-values and confidence intervals for random effects meta-analysis is more conservative than random-effects meta-analysis and will yieild less significant results than the latter.
+It is possible to analyse all results that are not unique in their comparison, outcome and subgroup in the dataset by meta-analysis.
+So each study that has been repeated with respect to experimental setup is included.
+There are different meta-analys methods that can be applied, here, fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis using the Hartung-Knapp method are used.
 
 \vspace{0mm}
-In the following, the study results are combined with the results of their corresponding meta-analysis.
-Thus, every study that has one or more replicate was analysed by meta-analysis.
-In the following, the significance of the study, the primary significance, is compared with the significance of the meta-analysis or secondary significance.
-
-\vspace{0mm}
+In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e.
+if studies were not unique in the dataset with respect to their experimental setup).
+The significant of the treatment effect in a single result is then compared to the significance of the pooled treatment effect.
 In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
 The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure.
-One can see the overall fraction of rejected null-hypotheses of no treatment effect.
+The colors indicate the overall fraction of rejected or accepted null-hypotheses of no treatment effect.
 
@@
 
-The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
-Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
-The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested.
-This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
+The amount of significant heterogeneity in the results used by the meta-analyses is \Sexpr{length(which(mly$sig.Q == 0))} and corresponds to \Sexpr{(length(which(mly$sig.Q == 0))/ dim(mly)[1])*100}\% of the total number of meta-analyses.
 
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-grid.arrange(sig.meta.Q1, nonsig.meta.Q, ncol= 1)
-@
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance.sep.sig}
-\end{figure}
+%Comparison of significance separated for significant Q? Chunck 2
+
+%Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5
 
 \section{Small study effects}
-One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
-If this is not given, one often speaks of publication bias.
-In fact, there can also be other reasons for this (see discussion section).
-A more appropriate term for the phenomenon is small study effect.
-If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
 
-\vspace{0mm}
-To provide an overview over the issue, first it is shown how median absolute effect size decreases with increasing sample size of the comparisons in Figure \ref{effect.samplesize}.
-In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.
-
-\vspace{0mm}
-A clear trend of decrease of absolute effect size with increasing sample size (i.e.
-smaller variance) is visible.
-It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off.
-With increasing sample size, there are fewer results, therefore, the variation between medians increases.
-All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation.
-Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.
-
-\begin{figure}
 <<echo=FALSE>>=
-data %>% filter(total1 + total2 > 10 & total1 + total2 < 200) %>% 
+p.samplesize.effect <- data %>% filter(total1 + total2 > 10 & total1 + total2 < 200) %>% 
   mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
@@
   ggplot(aes(x = sample.size, y = median.effect)) + geom_point() + theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size")
-@
-\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
-\label{effect.samplesize}
-\end{figure}
 
-The median absolute normalized effect size can be visualized for the different outcome measures separately.
-Then it is well visible in Figure \ref{effect.samplesize.separated} that the trend of effect size decrease holds in particualar for risk and odds ratios, while it is way more stable for mean differences and standardized mean differences.
-Instead of normalizing the effects (i.e.
-subtracting mean and dividing through the standard deviation) for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.
+#levels(data$outcome.measure.new) <- c("Mean Difference", "Std. Mean Difference", "Odds Ratio", "Risk Ratio")
 
-\begin{figure}
-<<echo=FALSE>>=
-levels(data$outcome.measure.new) <- c("Mean Difference", "Std. Mean Difference", "Odds Ratio", "Risk Ratio")
-
-data %>% filter(total1 + total2 > 10 & total1 + total2 < 100) %>% 
+p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 10 & total1 + total2 < 100) %>% 
   filter(outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio" | outcome.measure.new == "Mean Difference" |
@@
 @
+
+To provide an overview over the abundance of small study effects in the dataset, first it is shown how median absolute effect size decreases with increasing sample size of the results (Figure \ref{effect.samplesize}).
+%In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.
+
+\vspace{0mm}
+A clear trend of decrease of absolute effect size with increasing sample size (i.e. smaller variance) is visible. 
+%It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off.
+With increasing sample size, there are fewer results, therefore, the variation between medians increases.
+All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation.
+Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.
+
+\begin{figure}
+<<echo=FALSE>>=
+plot(p.samplesize.effect)
+@
+\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
+\label{effect.samplesize}
+\end{figure}
+
+The median absolute normalized effect size can be visualized for the different outcome measures separately (Figure \ref{effect.samplesize.separated}).
+The plot confirms the trend of median effect size decrease towards lower sample size (e.g.
+for Risk Ratios: decrease $> 0.1$ standard deviations from 10 to 50 study participants).
+Instead of normalizing the effects
+%(i.e. subtracting mean and dividing through the standard deviation) 
+for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.
+
+\begin{figure}
+<<echo=FALSE>>=
+plot(p.samplesize.effect.sep)
+@
 \caption{Median of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
@@
 
-p.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% 
+p.bin <- meta.bin %>% ungroup() %>% 
   select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
@@
 
-test.sig.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+test.sig.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                               schwarzer.test = mean(schwarzer.test),
@@
 
-p1 <- meta.bin %>% ungroup() %>% 
+p1 <- meta.bin %>% ungroup() %>% filter(sig.fixef.bin == 1) %>% 
 select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
@@
            color = "white")
+
+range.pb.difference.bin <- range(test.sig.bin$mean - test.nonsig.bin$mean)
 
@@
            color = "white")
+
+range.pb.difference.cont <- range(test.sig.cont$mean - test.nonsig.cont$mean)
 
@@
 
+# Significance after correction plots, separated for meta-analyses with significant publication bias test.
+change.fixef.bias <- meta %>% 
+  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+  filter(thomson.test == 1) %>% group_by(sig.change, correction.method) %>% count()
+
+p.change.fixef.bias <- meta %>% 
+  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+  filter(thomson.test == 1) %>% mutate(sig.change = factor(sig.change)) %>% 
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+  ggtitle("Meta analysis with significant small study effect")+ 
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 100, 
+           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
+           color = "white")
+
+change.fixef.unbias <- meta %>% 
+  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+  filter(thomson.test == 0) %>% group_by(sig.change, correction.method) %>% count()
+
+p.change.fixef.unbias <- meta %>% 
+  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+  filter(thomson.test == 0) %>%   mutate(sig.change = factor(sig.change)) %>% 
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+  ggtitle("Meta analysis with non-significant small study effect")+ 
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 900, 
+           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
+           color = "white")
+
 ########################################################################################################################################
@@
 The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = \Sexpr{n.bin}).
+The amount of studies varies from 5\% (Schwarzer's Test) to 13 \% (Egger's Test) for binary outcomes and 9\% (Begg and Mazumdar's Test) to 25 \% (Egger's Test) for continuous outcomes.
 
@@
 
-The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
-This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
+There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not.
+Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by \Sexpr{range.pb.difference.bin[2]} (the minimal increase is \Sexpr{range.pb.difference.bin[1]} for Schwarzer's Test).
 
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-grid.arrange(p3, p4, ncol = 2)
-@
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-\label{bias.results.cont.sep}
-\end{figure}
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-grid.arrange(p1, p2, ncol = 2)
-@
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-\label{bias.results.bin.sep}
-\end{figure}
+%Show plots of significant meta-analyses separated? Chunck 4
 
@@
 
+Because the real amount of publication bias in the dataset is not known, the correction method can also be applied only to meta-analyses that have publication bias according to the small study effect tests in the previous section.
+Because the test developed by \citet{thomson.sharp} has been applied to both binary and continuous outcome meta-analyses (in the case of binary outcomes to arcsine variance stabilized proportions), it is used as a criterium to distinguish biased from unbiased meta-analyses.
+The proportions of significance tests of pooled treatment effects that turned from significant to non-significant, non-significant to significant etc.
+are shown in Figure \ref{significance.change.fixed.sep}.
+Fixed effects meta-analysis has been used to determine signficance of the uncorrected estimate.
+
+\begin{figure}
+<<echo=FALSE, warning=FALSE>>=
+grid.arrange(p.change.fixef.bias, p.change.fixef.unbias, ncol = 1)
+@
+\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
+\label{significance.change.random}
+\end{figure}
+
 Similarly, the number of missing studies per meta-analysis, i.e.
@@
 % \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Since most of the times the study publication year is available for a given result, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.
+The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
+%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
+% @
+% \caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
+% \label{study.significance.overtime}
+% \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 2
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
+Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
+The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested.
+This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(sig.meta.Q1, nonsig.meta.Q, ncol= 1)
+% @
+% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
+The fractions have been calculated
+% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+% \label{primary.secondary.significance.sep.sig}
+% \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 3
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
+This can again be done for the entire dataset, i.e.
+for all effect estimates and their ordering in time.
+It is important to scale the effect estimates here with respect to the estimates of the replication studies that are about the same subject, have the same outcome measure, etc.
+Also, only effect estimates that can be compared to other estimates before are included, i.e.
+only study results with one or more replica are included.
+Time needs to be scaled and normalized in order to compare multiple time-trends in effect size to each other and gain insights in the overall trend.
+This is done in Figure \ref{effects.overtime.separated}, separared for odds rati, risk ratio, and mean and standardized difference outcome measures.
+In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
+%                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
+%   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
+%   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
+%   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
+%   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
+%   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
+% @
+% \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
+% \label{effects.overtime.separated}
+% \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 4
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
+This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(p3, p4, ncol = 2)
+% @
+% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
+% \label{bias.results.cont.sep}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(p1, p2, ncol = 2)
+% @
+% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
+% \label{bias.results.bin.sep}
+% \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% #Proportion of significant pooled estimates based on proportion of single pooled estimates
+% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type)) + geom_histogram()
+% 
+% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
+%   geom_density(na.rm = T, position = "fill") + 
+%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+% 
+% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
+%   geom_histogram(position = "fill")
+% 
+% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef))) + 
+%   geom_histogram()
+
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(p.secondary.over.meansig)
+% @
+% \caption{Fraction of significant meta-analysis, dependent on the fraction of significant single results.}
+% \label{secondary.significance.over.meansig}
+% \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Chunck 1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-04-29 code_excess/excess.R

@@ -1,6 +1,6 @@
 ##################################################################################################################################
 #Scaled OR over time with initial OR > 1
-madata %>% filter(outcome.measure == "Odds Ratio") %>% filter(!is.na(study.year)) %>% 
+data %>% filter(outcome.measure == "Odds Ratio") %>% filter(!is.na(study.year)) %>% 
   group_by(file.nr, comparison.nr, subgroup.nr) %>% 
   mutate(counts = n()) %>% filter(counts > 1) %>% 
   mutate(first.effect = effect[which.min(study.year)]) %>% 
@@ -11,7 +11,7 @@ madata %>% filter(outcome.measure == "Odds Ratio") %>% filter(!is.na(study.year)
   labs(title = "Scaled and centered OR over time", subtitle = "Initial finding > 1") + ylab("Odds Ratio")  + ylab("Time")
 
 #Scaled OR over time with initial OR < 1
-madata %>% filter(outcome.measure == "Odds Ratio") %>% filter(!is.na(study.year)) %>% 
+data %>% filter(outcome.measure == "Odds Ratio") %>% filter(!is.na(study.year)) %>% 
   group_by(file.nr, comparison.nr, subgroup.nr) %>% 
   mutate(counts = n()) %>% filter(counts > 1) %>% 
   mutate(first.effect = effect[which.min(study.year)]) %>% 
@@ -22,7 +22,7 @@ madata %>% filter(outcome.measure == "Odds Ratio") %>% filter(!is.na(study.year)
   labs(title = "Scaled and centered OR over time", subtitle = "Initial finding < 1") + ylab("Odds Ratio")  + ylab("Time")
 
 #Scaled RR over time with initial RR > 1
-madata %>% filter(outcome.measure == "Risk Ratio") %>% filter(!is.na(study.year)) %>% 
+data %>% filter(outcome.measure == "Risk Ratio") %>% filter(!is.na(study.year)) %>% 
   group_by(file.nr, comparison.nr, subgroup.nr) %>% 
   mutate(counts = n()) %>% filter(counts > 1) %>% 
   mutate(first.effect = effect[which.min(study.year)]) %>% 
@@ -33,7 +33,7 @@ madata %>% filter(outcome.measure == "Risk Ratio") %>% filter(!is.na(study.year)
[…]

### 2019-05-13 Presentation/present.Rnw
Changes after Discussion w Prof. Held

--- 2019-04-25 Presentation/present.Rnw
@@
 
-<<echo=FALSE, warning = FALSE, message=FALSE>>= 
+<<echo=FALSE, warning = FALSE, warnings = FALSE, message = FALSE, cache = FALSE>>= 
 PATH_HOME = path.expand("~") # user home
@@
 
+data.ext <- data.ext %>% mutate(study.year = ifelse(study.year < 2019, study.year, NA)) %>% 
+    mutate(study.year = ifelse(study.year > 1920, study.year, NA))
+
 ###################################################################################################################
@@
 barbi2 <- arrange(filter(data, file.nr == 21) %>%
-          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study) %>% group_by(Comparison) %>% distinct(Outcome, .keep_all = T)
+          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name,
+                 Events = events1, Total = total1, Events_c = events2, Total_c = total2), Study) %>% group_by(Comparison) %>% distinct(Outcome, .keep_all = T)
 barbi2[barbi2$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
+
+barbi2$Comparison <- strtrim(barbi2$Comparison, 19)
+barbi2$Outcome <- strtrim(barbi2$Outcome, 19)
 
@@
 
-#Mean and median number of different outcome types of reviews
-mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
-  ungroup() %>% group_by(file.nr) %>%
-  count() %>% ungroup %>% summarise(mean = mean(n))
+# ????????
+# #Mean and median number of different outcome types of reviews
+# mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
+#   ungroup() %>% group_by(file.nr) %>%
+#   count() %>% ungroup %>% summarise(mean = mean(n))
+# 
+# median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
+#   ungroup() %>% group_by(file.nr) %>%
+#   count() %>% ungroup %>% summarise(mean = median(n))
+# 
+# #Outcome.measure frequency table:
+# outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.new) %>% count() %>% 
+#                                        arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9),
+#                                      data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% 
+#                                        ungroup() %>% filter(row_number() > 8) %>% 
+#                                        summarise(outcome.measure.new = "other", n = sum(n)))
 
-median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
-  ungroup() %>% group_by(file.nr) %>%
-  count() %>% ungroup %>% summarise(mean = median(n))
+#Review level
+study.rev <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count() %>% ungroup() %>% 
+	summarise(lower = quantile(n, 0.05), median = quantile(n, 0.5), mean = mean(n), upper = quantile(n, 0.95))
+comparison.rev <- data %>% group_by(file.nr) %>% distinct(comparison.name) %>% count() %>% ungroup() %>% 
+	summarise(lower = quantile(n, 0.05), median = quantile(n, 0.5), mean = mean(n), upper = quantile(n, 0.95))
+meta.rev <- data.ext %>% group_by(file.nr) %>% distinct(meta.id) %>% count() %>% ungroup() %>% 
+	summarise(lower = quantile(n, 0.05), median = quantile(n, 0.5), mean = mean(n), upper = quantile(n, 0.95))
 
-#Study.year quantiles:
-data.ext <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
-publication.year.range <- c(quantile(data.ext$study.year, 0.05, na.rm = T), quantile(data.ext$study.year, 0.25, na.rm = T), 
-                            quantile(data.ext$study.year, 0.5, na.rm = T), quantile(data.ext$study.year, 0.75, na.rm = T),
-                            round(mean(data.ext$study.year, na.rm = T), 2))
+#Global level
+study.years <- data.ext %>% group_by(file.nr) %>% distinct(study.name, .keep_all = T) %>% ungroup() %>% 
+	summarise(lower = quantile(study.year, 0.05, na.rm = T), median = quantile(study.year, 0.5, na.rm = T),
+						mean = mean(study.year, na.rm = T), upper = quantile(study.year, 0.95, na.rm = T))
+sample.size <- data.ext %>% group_by(file.nr) %>% distinct(study.name, .keep_all = T) %>% ungroup() %>% 
+	mutate(samplesize = total1 + total2) %>% 
+	summarise(lower = quantile(samplesize, 0.05, na.rm = T), median = quantile(samplesize, 0.5, na.rm = T),
+						mean = mean(samplesize, na.rm = T), upper = quantile(samplesize, 0.95, na.rm = T))
 
-#Outcome.measure frequency table:
-outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.new) %>% count() %>% 
-                                       arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9),
-                                     data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% 
-                                       ungroup() %>% filter(row_number() > 8) %>% 
-                                       summarise(outcome.measure.new = "other", n = sum(n)))
-
-outcome.measure.frequencies <- outcome.measure.frequencies %>% mutate(percentage = round(n/sum(n),3)*100)
-names(outcome.measure.frequencies) <- c("Outcome measure", "n", "Percentage")
-outcome.measure.frequencies$Percentage <- paste(outcome.measure.frequencies$Percentage, "%", sep = "")
-
-#Total and group size quantiles:
-data.ext <- data.ext %>% ungroup() %>%  mutate(total.n = total1 + total2)
-samplesize.range <- c(quantile(data.ext$total.n, 0.05, na.rm = T), quantile(data.ext$total.n, 0.25, na.rm = T), 
-                            quantile(data.ext$total.n, 0.5, na.rm = T), quantile(data.ext$total.n, 0.75, na.rm = T),
-                            round(mean(data.ext$total.n, na.rm = T), 2))
-treatment.group.size.range <- c(quantile(data.ext$total1, 0.05, na.rm = T), quantile(data.ext$total1, 0.25, na.rm = T), 
-                      quantile(data.ext$total1, 0.5, na.rm = T), quantile(data.ext$total1, 0.75, na.rm = T),
-                      round(mean(data.ext$total1, na.rm = T), 2))
-
-#Frequencies of results:
-comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
-comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
-                      quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
-                      round(mean(comp.freq$n, na.rm = T), 2))
-
-#Frequencies of studies:
-study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
-study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
-                      quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
-                      round(mean(study.freq$n, na.rm = T), 2))
+dataset.properties <- rbind(study.rev, comparison.rev, meta.rev, study.years, sample.size)
+rownames(dataset.properties) <- c("Study number", "Comparison number", "Group number", "Study years", "Study sample size")
+colnames(dataset.properties) <- c("5% quantile", "median", "mean", "95% quantile")
 
@@
 cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
-  filter(n < 15) %>%
+  filter(n < 10) %>%
   full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
-               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
+               filter(n > 9) %>% ungroup %>% summarise(n = 10, nn = sum(nn))) %>%
   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
@@
 colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
+
+###################################################################################################################
+###################################################################################################################
+#Meta-analyses
+###################################################################################################################
+###################################################################################################################
+
+#Funnel plot example:
+biased.rev <- data %>% filter(file.nr == 76 & comparison.nr == 2 & outcome.nr == 2 & subgroup.nr == 4)
+meta.example <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, 
+												studlab = study.name, sm= "OR", data = biased.rev)
+
+#Publication Bias test plots:
+test.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                 schwarzer.test = mean(schwarzer.test),
+                                                 rucker.test = mean(rucker.test),
+                                                 harbord.test = mean(harbord.test),
+                                                 peter.test = mean(peter.test))
+test.bin <- test.bin %>% gather(key = "test.type", value = "mean")
+p.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% 
+  select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
+  gather(key = "test.type", value = "null.hypothesis") %>%  
+  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
+  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+  theme_bw() + xlab(label = NULL) + ggtitle("Binary Outcomes") + theme(legend.position = "top") +
+  guides(fill=guide_legend(title=NULL))+
+  annotate("text", x = test.bin$test.type, y = 1000, 
+           label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
+           color = "white")
+
+test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                   begg.test = mean(begg.test),
+                                                   thomson.test = mean(thomson.test))
+test.cont <- test.cont %>% gather(key = "test.type", value = "mean")
+p.cont <- meta.cont %>% ungroup() %>% 
+  select(egger.test, thomson.test, begg.test) %>% 
+  gather(key = "test.type", value = "null.hypothesis") %>% 
+  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
+  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+  theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
+	guides(fill=guide_legend(title=NULL))+
+  annotate("text", x = test.cont$test.type, y = 750, 
+           label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
+           color = "white")
+
+#Significance change after adjustment plot:
+change.fixef <- meta %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+	mutate(n = n/sum(n))
+
+p.fixef.change <- meta %>% ungroup() %>% 
+  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>%  
+  mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+  theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
+	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+  annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 1500, 
+         label = paste(round(change.fixef[change.fixef$sig.change == 3,]$n*100,2), "% changed to nonsig."), 
+         color = "white")
+
 @
@@
 
-Currently $\sim$ 8,000 reviews, prepared by independet groups.
+Currently $\sim$ 8,000 reviews, prepared by independent groups.
 
@@
 \begin{frame}{Cochrane Library Dataset}
-% \Sexpr{length(unique(data$file.nr))} systematic reviews with studies published until 2018.
-% 
-% \Sexpr{length(unique(data$study.name))} studies.
-% 
-% \Sexpr{dim(data)[1]} study results.
+\Sexpr{format(length(unique(data$file.nr)), big.mark=",")} systematic reviews with studies published until 2018.
+
+\Sexpr{format(length(unique(data$study.name)), big.mark=",")} studies.
+
+\Sexpr{format(dim(data)[1], big.mark=",")} study results.
 \end{frame}
 
-\begin{frame}{Dataset structure}
+\begin{frame}{Dataset Structure}
 
@@
 
-\begin{frame}{Review Example}
+\begin{frame}{Dataset Structure}
+\begin{itemize}
+\item Comparison: What is compared, e.g. treatment vs. control
+\item Outcome: How it is compared
+\item Subgroup: Subgroup affiliation
+\item Meta-Analysis Group: Results from same comparison, outcome and subgroup
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Review Example: binary outcome}
+Barbiturate efficacy in head injury
 \vspace{-5mm}
 <<echo = FALSE, results = 'asis'>>=
-print(xtable(barbi2, label = "barbiturates"), include.rownames = F, size = "tiny")
+print(xtable(barbi2, label = "barbiturates", digits = 0), include.rownames = F, size = "tiny")
 @
 
-\vspace{-6mm}
-<<echo = FALSE, results = 'asis'>>=
-print(xtable(barbi1, label = "barbiturate.row", digits = 0), 
-      include.rownames = F, size = "tiny")
+% \vspace{-6mm}
+% echo = FALSE, results = 'asis'>>=
+% print(xtable(barbi1, label = "barbiturate.row", digits = 0),
+%       include.rownames = F, size = "tiny")
+% @
+
+\end{frame}
+
+\begin{frame}{Dataset Properties}
+Missing data:
+<<echo=FALSE, results = 'asis'>>=
+print(xtable(missing.table, align = "lr"), include.rownames = T, include.colnames = F)
 @
@@
 
-\begin{frame}{Pooling studies}
-Studies of the same outcome, comparison and subgroup can be pooled by meta analyis.
-
-Evidence synthesis - more reliable results.
-
-Different methods - f.ex. random or fixed effects meta-analysis.
+\begin{frame}{Dataset Properties}
+Review and study properties:
+<<echo=FALSE, results = 'asis'>>=
+print(xtable(dataset.properties, digits = 0, align = "lrrrr"), include.rownames = T, size = "footnotesize", hline = c(0,1,1,4))
+@
 \end{frame}
 
-\begin{frame}{Publication bias}
-Selection of studies with treatment effects.
+\begin{frame}{Pooling Studies - Meta-Analysis}
+Multiple results in a meta-analysis group can be pooled:
 
-Stronger selection for smaller studies - small study effect.
+<<echo=FALSE, results = 'asis'>>=
+print(xtable(cum.repr.trials.subg, label = "repr.groups", align = "lrrr", digits = 0), include.rownames = F, size = "footnotesize")
+@
 
-Distort findings of meta-analyses.
 \end{frame}
+
+\begin{frame}{Meta-analysis}
+Benefits:
+\begin{itemize}
+\item Summary of evidence (e.g. of a treatment)
+\item More reliable evidence (?)
+\end{itemize}
+
+Assumptions:
+\begin{itemize}
+\item Identical study settings (can be relaxed)
+\item Random sample of studies
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Small Study Effects}
+``The tendency for the smaller studies to show larger treatment effects'' \citep{Sterne}
+\end{frame}
+
+\begin{frame}{Small Study Effects}
+Causes:
+\begin{itemize}
+\item Selective publication of studies with large effects
+\item Bias in smaller studies
+\item Systematical differences in study settings
+\item \ldots
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Publication Bias Tests}
+Test for funnel plot asymmetry:
+
+\vspace{-1.7cm}
+\begin{figure}
+<<echo=FALSE, fig.height = 4>>=
+par(las = 1, mfrow = c(1,2))
+
+funnel(meta.example)
+radial(meta.example)
+@
+\end{figure}
+\end{frame}
+
+\begin{frame}{Publication Bias Tests}
+Critical: Number of studies in meta-analysis must be large ($\geq$ 10).
+
+Various tests for meta-analyses with continuous and binary outcomes:
+
+Regression based: Egger's, Peter's or Thompson and Sharp's test
+
+Rank based: Begg and Mazumdar's Test
+\end{frame}
+% 
+% \begin{frame}{Publication Bias in the Cochrane Library}
+% Publication bias tests applied for any meta analysis with n > 10
+% 
+% \vspace{-1.7cm}
+% \begin{figure}[fragile]
+% <<echo=FALSE, fig.height = 3.1, fig.width = 6.5 >>=
+% grid.arrange(p.bin, p.cont, ncol = 2)
+% @
+% \end{figure}
+% \end{frame}
+% 
+% \begin{frame}{Publication Bias}
+% 
+% \begin{figure}
+% <<echo=FALSE, fig.height = 3.2, fig.width = 6.5 >>=
+% grid.arrange(pbias.time, pbias.ss, ncol = 2)
+% @
+% \end{figure}
+% \end{frame}
+% 
+% 
+% 
+% \begin{frame}{Publication Bias Adjustment}
+% Three approaches:
+% 
+% Trim-and-fill: Non-parametric
+% 
+% Copas: Selection modelling, estimation by sensitivity analysis
+% 
+% Regression: Estimation of a treatment effect with infinite sample size
+% \end{frame}
 

### 2019-05-13 communication/newplots_discussion.Rmd
Changes after Discussion w Prof. Held

---
title: "Plots for Presentation and Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, echo=FALSE, warning=FALSE}
rm(list = ls())
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH2, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

file_results = "pb.RData"

source(file.path(PATH_CODE, 'PubBias_functions.R'))

# data = pb.readData(path = PATH_DATA, file = FILE)
# tmp = pb.clean(data)
# data = tmp[[1]]
# aliases = tmp[[2]]

file.dat <- "data.RData"
if (file.exists(file.path(PATH_RESULTS, file.dat))) {
  load(file.path(PATH_RESULTS, file.dat))
} else {
  data = pb.readData(path = PATH_DATA, file = FILE)
  tmp = pb.clean(data)
  data = tmp[[1]]
  aliases = tmp[[2]]
  save(data, file =  file.path(PATH_RESULTS, file.dat))
}

load(file.path(PATH_RESULTS, file = "mly.RData"))
load(file.path(PATH_RESULTS, file = "data.processed.RData"))

file.bin <- "pb.bin.RData"
if (file.exists(file.path(PATH_RESULTS, file.bin))) {
  load(file.path(PATH_RESULTS, file.bin))
} else {
  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
}

file.cont <- "pb.cont.RData"
if (file.exists(file.path(PATH_RESULTS, file.cont))) {
  load(file.path(PATH_RESULTS, file.cont))
} else {
  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
}

file.meta <- "meta.RData"
if (file.exists(file.path(PATH_RESULTS, file.meta))) {
  load(file.path(PATH_RESULTS, file.meta))
} else {
  meta <- pb.meta.merge(meta.bin, meta.cont)
  save(meta, file =  file.path(PATH_RESULTS, file.meta))
}

file.cont <- "mly.cont.RData"
if (file.exists(file.path(PATH_RESULTS, file.cont))) {
  load(file.path(PATH_RESULTS, file.cont))
} else {
  data.cont <- mly.cont(data.ext, 0.05, min.study.number = 2)
  save(data.cont, file =  file.path(PATH_RESULTS, file.cont))
}

file.bin <- "mly.bin.RData"
if (file.exists(file.path(PATH_RESULTS, file.bin))) {
  load(file.path(PATH_RESULTS, file.bin))
} else {
  data.bin <- mly.bin(data.ext, 0.05, min.study.number = 2)
  save(data.bin, file =  file.path(PATH_RESULTS, file.bin))
}

require(biostatUZH)
require(tidyverse)
require(meta)
require(metasens)
require(gridExtra)

#Meta filtering: 
metac.bin <- meta.bin %>% filter(n.sig.type.bin > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
metac.cont <- meta.cont %>% filter(n.sig.type.cont > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
metac <- meta %>% filter(n.sig.type > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)

#Significant proportion
test.bin <- metac.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                          schwarzer.test = mean(schwarzer.test),
                                                          rucker.test = mean(rucker.test),
                                                          harbord.test = mean(harbord.test),
                                                          peter.test = mean(peter.test))
test.bin <- test.bin %>% gather(key = "test.type", value = "mean")

p.bin <- metac.bin %>% ungroup() %>% 
  select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>%  
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) + ggtitle("Binary Outcomes") + theme(legend.position = "top") +
  guides(fill=guide_legend(title=NULL))+
  annotate("text", x = test.bin$test.type, y = 500, 
           label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
           color = "white")

#Test Results: Continuous
test.cont <- metac.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                            begg.test = mean(begg.test),
                                                            thomson.test = mean(thomson.test))

test.cont <- test.cont %>% gather(key = "test.type", value = "mean")

p.cont <- metac.cont %>% ungroup() %>% 
  select(egger.test, thomson.test, begg.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>% 
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
	guides(fill=guide_legend(title=NULL))+
  annotate("text", x = test.cont$test.type, y = 150, 
           label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
           color = "white")

#P-value distribution:
pval.bin <- metac.bin %>% ungroup() %>% 
  select(pval.egger.bin, pval.schwarzer.bin, pval.rucker.bin, pval.harbord.bin, pval.peter.bin) %>% 
  gather(key = "test.type", value = "p.value") %>% 
  ggplot(aes(x = p.value)) + geom_histogram() + theme_bw() + facet_wrap(~test.type)

pval.cont <- metac.cont %>% ungroup() %>% 
  select(pval.egger.cont, pval.thomson.cont, pval.begg.cont) %>% 
  gather(key = "test.type", value = "p.value") %>% 
  ggplot(aes(x = p.value)) + geom_histogram() + theme_bw() + facet_wrap(~test.type)

#Sum of significant tests
agree.bin <- meta.bin %>% mutate(n.sig = peter.test + rucker.test + egger.test + harbord.test + schwarzer.test) %>% 
  group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
  ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + xlab("Number of significant tests") + ylab("count") + ggtitle("Binary Outcomes")

agree.cont <- meta.cont %>% mutate(n.sig = egger.test + thomson.test + begg.test) %>% 
  group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
  ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + xlab("Number of significant tests") + ylab("count") + ggtitle("Binary Outcomes")
```

#Publication Bias/Small study effects tests

Publication bias tests for all meta-analyses with n<= 10, $I^2$ < 0.5, largest se/smallest se > 4 and at least one significant single study result. Continuous and binary results are shown separatedly. The first plot shows the proportion of tests with p-values < 0.05. Afterwards, a histogramm with the p-values for the tests is shown.

```{r, fig.height = 3, message = FALSE, echo = FALSE}
grid.arrange(p.bin, p.cont, ncol = 2)
```

```{r, fig.height = 3.2, message = FALSE, echo = FALSE}
plot(pval.bin)
plot(pval.cont)
```

The following plot shows how many meta-analyses were significant when tested only with one test, two tests etc..

```{r, fig.height = 2.5, echo = FALSE}
grid.arrange(agree.bin, agree.cont, ncol = 2)
```

### 2019-05-13 communication/pb_adjustment.Rmd
Changes after Discussion w Prof. Held

---
title: "Treatment Effect Reduction after Adjustment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, message=FALSE, warning=FALSE}
rm(list = ls())
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH2, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

file_results = "pb.RData"

source(file.path(PATH_CODE, 'PubBias_functions.R'))

# data = pb.readData(path = PATH_DATA, file = FILE)
# tmp = pb.clean(data)
# data = tmp[[1]]
# aliases = tmp[[2]]

file.dat <- "data.RData"
if (file.exists(file.path(PATH_RESULTS, file.dat))) {
  load(file.path(PATH_RESULTS, file.dat))
} else {
  data = pb.readData(path = PATH_DATA, file = FILE)
  tmp = pb.clean(data)
  data = tmp[[1]]
  aliases = tmp[[2]]
  save(data, file =  file.path(PATH_RESULTS, file.dat))
}

load(file.path(PATH_RESULTS, file = "mly.RData"))
load(file.path(PATH_RESULTS, file = "data.processed.RData"))

file.bin <- "pb.bin.RData"
if (file.exists(file.path(PATH_RESULTS, file.bin))) {
  load(file.path(PATH_RESULTS, file.bin))
} else {
  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05)
  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
}

file.cont <- "pb.cont.RData"
if (file.exists(file.path(PATH_RESULTS, file.cont))) {
  load(file.path(PATH_RESULTS, file.cont))
} else {
  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
}

file.meta <- "meta.RData"
if (file.exists(file.path(PATH_RESULTS, file.meta))) {
  load(file.path(PATH_RESULTS, file.meta))
} else {
  meta <- pb.meta.merge(meta.bin, meta.cont)
  save(meta, file =  file.path(PATH_RESULTS, file.meta))
}

file.cont <- "mly.cont.RData"
if (file.exists(file.path(PATH_RESULTS, file.cont))) {
  load(file.path(PATH_RESULTS, file.cont))
} else {
  data.cont <- mly.cont(data.ext, 0.05, min.study.number = 2)
  save(data.cont, file =  file.path(PATH_RESULTS, file.cont))
}

file.bin <- "mly.bin.RData"
if (file.exists(file.path(PATH_RESULTS, file.bin))) {
  load(file.path(PATH_RESULTS, file.bin))
} else {
  data.bin <- mly.bin(data.ext, 0.05, min.study.number = 2)
  save(data.bin, file =  file.path(PATH_RESULTS, file.bin))
}

require(biostatUZH)
require(tidyverse)
require(meta)
require(metasens)
require(gridExtra)

metac.bin <- meta.bin %>% filter(n.sig.type.cont > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
metac.cont <- meta.cont %>% filter(n.sig.type.cont > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
# metac <- meta %>% filter(n.sig.type > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
```

The relative change of treatment effect after adjustment for small study effects is investigated in this document. Three adjustment methods are applied: Trim and fill, copas selection model and the regression model. The estimates of this methods are compared to fixed effects and random effects meta-analysis estimates.

The relative change of treatment effect after adjustment is defined as:

$1 - |{\frac{\theta_{C}}{\theta_{M}}}|$

were $\theta_{M}$ is the estimate of the meta-analysis and $\theta_{C}$ is the estimate of the adjustment method and $||$ denotes the absolute value.

The number can be interpreted as the fraction by which the original treatment effect is reduced after adjustment. If the number is positive, the treatment estimate has been reduced by the adjustment method. If the relative change is negative, then the adjusted treatment effect estimate is larger than the estimate of the meta-analysis

##Trim-and-fill

First, the number of treatment effects that are smaller or larger than the treatment effects are counted:

```{r, echo = FALSE, message=FALSE}
#Summaries:
metac.bin %>% mutate(xx = 1 - abs(logest.trimfill.fixef.bin/log(est.fixef.bin))) %>% filter(xx > 0) %>% ungroup() %>% 
  summarise(biased = sum(peter.test), larger.meta.effects = n())

metac.bin %>% mutate(xx = 1 - abs(logest.trimfill.fixef.bin/log(est.fixef.bin))) %>% filter(xx < 0) %>% ungroup() %>% 
  summarise(biased = sum(peter.test), smaller.meta.effects = n())

metac.bin %>% mutate(xx = 1 - abs(logest.trimfill.fixef.bin/log(est.ranef.bin))) %>% filter(xx < 0) %>% ungroup() %>% 
  summarise(biased = sum(peter.test), smaller.meta.effects.random = n())
```

The empirical distribution of relative effect changes are shown in the following plots. Different ranges and different plots are shown for random and fixed effects meta-analysis and continuous and binary outcomes. Additionally, the fraction of meta-analyses with significant peters publication bias test (binary outcomes) and eggers test (continuous outcomes) is color-coded within the histogramms.

###Binary Outcomes

```{r, echo = FALSE, fig.height=3, message=FALSE}
metac.bin %>% mutate(xx = 1 - abs(logest.trimfill.fixef.bin/log(est.fixef.bin))) %>% filter(xx > 0) %>% 
  ggplot(aes(x = xx, fill = factor(peter.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Trimfill")

metac.bin %>% mutate(xx = 1 - abs(logest.trimfill.fixef.bin/log(est.fixef.bin))) %>% filter(xx > -1) %>% 
  ggplot(aes(x = xx, fill = factor(peter.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Trimfill")

metac.bin %>% mutate(xx = 1 - abs(logest.trimfill.fixef.bin/log(est.ranef.bin))) %>% filter(xx > 0) %>% 
  ggplot(aes(x = xx, fill = factor(peter.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Trimfill")

metac.bin %>% mutate(xx = 1 - abs(logest.trimfill.fixef.bin/log(est.ranef.bin))) %>% filter(xx > -1) %>% 
  ggplot(aes(x = xx, fill = factor(peter.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Trimfill")

metac.bin %>% mutate(xx = 1 - abs(logest.trimfill.fixef.bin/log(est.fixef.bin))) %>% 
  ggplot(aes(x = xx)) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Trimfill")

metac.bin %>% mutate(xx = 1 - abs(logest.trimfill.fixef.bin/log(est.ranef.bin))) %>% 
  ggplot(aes(x = xx)) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Trimfill")
```

The absolute values of the treatment effect estimates can be plotted against each other. This is shown, again for different meta-analysis methods.

```{r, echo = FALSE, fig.height=3, message=FALSE}
metac.bin %>% ggplot(aes(x = abs(log(est.fixef.bin)), y = abs(logest.trimfill.fixef.bin))) + geom_point() + 
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  xlab("Fixed effects estimate") + ylab("Trimfill estimate") + ggtitle("Fixed effects to Trimfill")

metac.bin %>% ggplot(aes(x = abs(log(est.ranef.bin)), y = abs(logest.trimfill.fixef.bin))) + geom_point() + 
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  xlab("Random effects estimate") + ylab("Trimfill estimate") + ggtitle("Random effects to Trimfill")

```

```{r, echo = FALSE, fig.height=3, message=FALSE}
#Scatterplots of test-statistics:
metac.bin %>% ggplot(aes(x = zval.fixef.bin, y = logest.trimfill.fixef.bin/se.logest.trimfill.fixef.bin)) + geom_point() +
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  ggtitle("Fixed effects and trimfill test statistics") + ylab("Trimfill statistic") + xlab("Fixed effects statistic")

metac.bin %>% ggplot(aes(x = zval.ranef.bin, y = logest.trimfill.fixef.bin/se.logest.trimfill.fixef.bin)) + geom_point() +
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  ggtitle("Random effects and trimfill test statistics") + ylab("Trimfill statistic") + xlab("Random effects statistic")
```

###Continuous Outcomes

```{r}
metac.cont %>% mutate(xx = 1 - abs(est.trimfill.fixef.cont/est.fixef.cont)) %>% filter(xx > 0) %>% ungroup() %>% 
  summarise(biased = sum(egger.test), larger.meta.effects = n())

metac.cont %>% mutate(xx = 1 - abs(est.trimfill.fixef.cont/est.fixef.cont)) %>% filter(xx < 0) %>% ungroup() %>% 
  summarise(biased = sum(egger.test), smaller.meta.effects = n())

metac.cont %>% mutate(xx = 1 - abs(est.trimfill.fixef.cont/est.ranef.cont)) %>% filter(xx < 0) %>% ungroup() %>% 
  summarise(biased = sum(egger.test), smaller.meta.effects.random = n())
```

```{r, echo = FALSE, fig.height=3, message=FALSE}
#Histogramms of changes +- 100%
metac.cont %>% mutate(xx = 1 - abs(est.trimfill.fixef.cont/est.fixef.cont)) %>% filter(xx > 0) %>% 
  ggplot(aes(x = xx, fill = factor(egger.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Trimfill")

metac.cont %>% mutate(xx = 1 - abs(est.trimfill.fixef.cont/est.fixef.cont)) %>% filter(xx > -1) %>% 
  ggplot(aes(x = xx, fill = factor(egger.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Trimfill")

metac.cont %>% mutate(xx = 1 - abs(est.trimfill.fixef.cont/est.ranef.cont)) %>% filter(xx > 0) %>% 
  ggplot(aes(x = xx, fill = factor(egger.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Trimfill")

metac.cont %>% mutate(xx = 1 - abs(est.trimfill.fixef.cont/est.ranef.cont)) %>% filter(xx > -1) %>% 
  ggplot(aes(x = xx, fill = factor(egger.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Trimfill")

metac.cont %>% mutate(xx = 1 - abs(est.trimfill.fixef.cont/est.fixef.cont)) %>% 
  ggplot(aes(x = xx)) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Trimfill")

metac.cont %>% mutate(xx = 1 - abs(est.trimfill.fixef.cont/est.ranef.cont)) %>% 
  ggplot(aes(x = xx)) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Trimfill")
```

The absolute values of the treatment effect estimates can be plotted against each other. This is shown, again for different meta-analysis methods.

```{r, echo = FALSE, fig.height=3, message=FALSE}
#Scatterplots of meta-analysis and corrected estimates
metac.cont %>% ggplot(aes(x = abs(est.fixef.cont), y = abs(est.trimfill.fixef.cont))) + geom_point() + 
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  xlab("Fixed effects estimate") + ylab("Trimfill estimate") + ggtitle("Fixed effects to Trimfill")

metac.cont %>% ggplot(aes(x = abs(est.ranef.cont), y = abs(est.trimfill.fixef.cont))) + geom_point() + 
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  xlab("Random effects estimate") + ylab("Trimfill estimate") + ggtitle("Random effects to Trimfill")

#Scatterplots of test-statistics:
meta.cont %>% ggplot(aes(x = abs(zval.fixef.cont), y = abs(est.trimfill.fixef.cont/se.est.trimfill.fixef.cont))) + geom_point() +
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  ggtitle("Fixed effects and trimfill test statistics") + ylab("Trimfill statistic") + xlab("Fixed effects statistic")

meta.cont %>% ggplot(aes(x = abs(zval.ranef.cont), y = abs(est.trimfill.fixef.cont/se.est.trimfill.fixef.cont))) + geom_point() +
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  ggtitle("Random effects and trimfill test statistics") + ylab("Trimfill statistic") + xlab("Random effects statistic")
```

##Copas Method

The structure of the example of trim-and-fill is maintained:

###Binary Outcomes:
```{r, echo = FALSE, fig.height=3, message=FALSE, warning=FALSE}
#Summaries
metac.bin %>% mutate(xx = 1 - abs(logest.copas.bin/log(est.fixef.bin))) %>% filter(xx > 0) %>% ungroup() %>% 
  summarise(biased = sum(peter.test), larger.meta.effects = n())

metac.bin %>% mutate(xx = 1 - abs(logest.copas.bin/log(est.fixef.bin))) %>% filter(xx < 0) %>% ungroup() %>% 
  summarise(biased = sum(peter.test), smaller.meta.effects = n())

metac.bin %>% mutate(xx = 1 - abs(logest.copas.bin/log(est.ranef.bin))) %>% filter(xx < 0) %>% ungroup() %>% 
  summarise(biased = sum(peter.test), smaller.meta.effects.random = n())

#Histogramms of changes +- 100%
metac.bin %>% mutate(xx = 1 - abs(logest.copas.bin/log(est.fixef.bin))) %>% filter(xx > 0) %>% 
  ggplot(aes(x = xx, fill = factor(peter.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Copas")

metac.bin %>% mutate(xx = 1 - abs(logest.copas.bin/log(est.fixef.bin))) %>% filter(xx > -1) %>% 
  ggplot(aes(x = xx, fill = factor(peter.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Copas")

metac.bin %>% mutate(xx = 1 - abs(logest.copas.bin/log(est.ranef.bin))) %>% filter(xx > 0) %>% 
  ggplot(aes(x = xx, fill = factor(peter.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Copas")

metac.bin %>% mutate(xx = 1 - abs(logest.copas.bin/log(est.ranef.bin))) %>% filter(xx > -1) %>% 
  ggplot(aes(x = xx, fill = factor(peter.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Copas")

metac.bin %>% mutate(xx = 1 - abs(logest.copas.bin/log(est.fixef.bin))) %>% 
  ggplot(aes(x = xx)) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Copas")

metac.bin %>% mutate(xx = 1 - abs(logest.copas.bin/log(est.ranef.bin))) %>% 
  ggplot(aes(x = xx)) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Copas")

#Scatterplots of meta-analysis and corrected estimates
metac.bin %>% ggplot(aes(x = abs(log(est.fixef.bin)), y = abs(logest.copas.bin))) + geom_point() + 
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  xlab("Fixed effects estimate") + ylab("Copas estimate") + ggtitle("Fixed effects to Copas")

metac.bin %>% ggplot(aes(x = abs(log(est.ranef.bin)), y = abs(logest.copas.bin))) + geom_point() + 
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  xlab("Random effects estimate") + ylab("Copas estimate") + ggtitle("Random effects to Copas")

#Scatterplots of test-statistics:
metac.bin %>% ggplot(aes(x = abs(zval.fixef.bin), y = abs(logest.copas.bin/se.logest.copas.bin))) + geom_point() +
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  ggtitle("Fixed effects and copas test statistics") + ylab("copas statistic") + xlab("Fixed effects statistic")

metac.bin %>% ggplot(aes(x = abs(zval.ranef.bin), y = abs(logest.copas.bin/se.logest.copas.bin))) + geom_point() +
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  ggtitle("Random effects and copas test statistics") + ylab("copas statistic") + xlab("Random effects statistic")
```

###Continuous Outcomes:
```{r, echo = FALSE, fig.height=3, message=FALSE, warning=FALSE}
#Summaries:
metac.cont %>% mutate(xx = 1 - abs(est.copas.cont/est.fixef.cont)) %>% filter(xx > 0) %>% ungroup() %>% 
  summarise(biased = sum(egger.test), larger.meta.effects = n())

metac.cont %>% mutate(xx = 1 - abs(est.copas.cont/est.fixef.cont)) %>% filter(xx < 0) %>% ungroup() %>% 
  summarise(biased = sum(egger.test), smaller.meta.effects = n())

metac.cont %>% mutate(xx = 1 - abs(est.copas.cont/est.ranef.cont)) %>% filter(xx < 0) %>% ungroup() %>% 
  summarise(biased = sum(egger.test), smaller.meta.effects.random = n())

#Histogramms of changes +- 100%
metac.cont %>% mutate(xx = 1 - abs(est.copas.cont/est.fixef.cont)) %>% filter(xx > 0) %>% 
  ggplot(aes(x = xx, fill = factor(egger.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to copas")

metac.cont %>% mutate(xx = 1 - abs(est.copas.cont/est.fixef.cont)) %>% filter(xx > -1) %>% 
  ggplot(aes(x = xx, fill = factor(egger.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to copas")

metac.cont %>% mutate(xx = 1 - abs(est.copas.cont/est.ranef.cont)) %>% filter(xx > 0) %>% 
  ggplot(aes(x = xx, fill = factor(egger.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to copas")

metac.cont %>% mutate(xx = 1 - abs(est.copas.cont/est.ranef.cont)) %>% filter(xx > -1) %>% 
  ggplot(aes(x = xx, fill = factor(egger.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to copas")

metac.cont %>% mutate(xx = 1 - abs(est.copas.cont/est.fixef.cont)) %>% 
  ggplot(aes(x = xx)) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to copas")

metac.cont %>% mutate(xx = 1 - abs(est.copas.cont/est.ranef.cont)) %>% 
  ggplot(aes(x = xx)) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to copas")

#Scatterplots of meta-analysis and corrected estimates
metac.cont %>% ggplot(aes(x = abs(est.fixef.cont), y = abs(est.copas.cont))) + geom_point() + 
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  xlab("Fixed effects estimate") + ylab("copas estimate") + ggtitle("Fixed effects to copas")

metac.cont %>% ggplot(aes(x = abs(est.ranef.cont), y = abs(est.copas.cont))) + geom_point() + 
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  xlab("Random effects estimate") + ylab("copas estimate") + ggtitle("Random effects to copas")

#Scatterplots of test-statistics:
metac.cont %>% ggplot(aes(x = abs(zval.fixef.cont), y = abs(est.copas.cont/se.est.copas.cont))) + geom_point() +
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  ggtitle("Fixed effects and copas test statistics") + ylab("copas statistic") + xlab("Fixed effects statistic")

metac.cont %>% ggplot(aes(x = abs(zval.ranef.cont), y = abs(est.copas.cont/se.est.copas.cont))) + geom_point() +
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  ggtitle("Random effects and copas test statistics") + ylab("copas statistic") + xlab("Random effects statistic")
```

##Regression

###Binary Outcomes:
```{r, echo = FALSE, fig.height=3, message=FALSE}
#Summaries
metac.bin %>% mutate(xx = 1 - abs(logest.reg.ranef.bin/log(est.fixef.bin))) %>% filter(xx > 0) %>% ungroup() %>% 
  summarise(biased = sum(peter.test), larger.meta.effects = n())

metac.bin %>% mutate(xx = 1 - abs(logest.reg.ranef.bin/log(est.fixef.bin))) %>% filter(xx < 0) %>% ungroup() %>% 
  summarise(biased = sum(peter.test), smaller.meta.effects = n())

metac.bin %>% mutate(xx = 1 - abs(logest.reg.ranef.bin/log(est.ranef.bin))) %>% filter(xx < 0) %>% ungroup() %>% 
  summarise(biased = sum(peter.test), smaller.meta.effects.random = n())

#Histogramms of changes +- 100%
metac.bin %>% mutate(xx = 1 - abs(logest.reg.ranef.bin/log(est.fixef.bin))) %>% filter(xx > 0) %>% 
  ggplot(aes(x = xx, fill = factor(peter.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Regression")

metac.bin %>% mutate(xx = 1 - abs(logest.reg.ranef.bin/log(est.fixef.bin))) %>% filter(xx > -1) %>% 
  ggplot(aes(x = xx, fill = factor(peter.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Regression")

metac.bin %>% mutate(xx = 1 - abs(logest.reg.ranef.bin/log(est.ranef.bin))) %>% filter(xx > 0) %>% 
  ggplot(aes(x = xx, fill = factor(peter.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Regression")

metac.bin %>% mutate(xx = 1 - abs(logest.reg.ranef.bin/log(est.ranef.bin))) %>% filter(xx > -1) %>% 
  ggplot(aes(x = xx, fill = factor(peter.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Regression")

metac.bin %>% mutate(xx = 1 - abs(logest.reg.ranef.bin/log(est.fixef.bin))) %>% 
  ggplot(aes(x = xx)) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Regression")

metac.bin %>% mutate(xx = 1 - abs(logest.reg.ranef.bin/log(est.ranef.bin))) %>% 
  ggplot(aes(x = xx)) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Regression")

#Scatterplots of meta-analysis and corrected estimates
metac.bin %>% ggplot(aes(x = abs(log(est.fixef.bin)), y = abs(logest.reg.ranef.bin))) + geom_point() + 
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  xlab("Fixed effects estimate") + ylab("Regression estimate") + ggtitle("Fixed effects to Regression")

metac.bin %>% ggplot(aes(x = abs(log(est.ranef.bin)), y = abs(logest.reg.ranef.bin))) + geom_point() + 
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  xlab("Random effects estimate") + ylab("Regression estimate") + ggtitle("Random effects to Regression")

#Scatterplots of test-statistics:
metac.bin %>% ggplot(aes(x = abs(zval.fixef.bin), y = abs(logest.reg.ranef.bin/se.logest.reg.ranef.bin))) + geom_point() +
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  ggtitle("Fixed effects and reg.ranef test statistics") + ylab("reg.ranef statistic") + xlab("Fixed effects statistic")

metac.bin %>% ggplot(aes(x = abs(zval.ranef.bin), y = abs(logest.reg.ranef.bin/se.logest.reg.ranef.bin))) + geom_point() +
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  ggtitle("Random effects and reg.ranef test statistics") + ylab("reg.ranef statistic") + xlab("Random effects statistic")
```

###Continuous Outcomes:
```{r echo = FALSE, fig.height=3, message=FALSE}
#Summaries:
metac.cont %>% mutate(xx = 1 - abs(est.reg.ranef.cont/est.fixef.cont)) %>% filter(xx > 0) %>% ungroup() %>% 
  summarise(biased = sum(egger.test), larger.meta.effects = n())

metac.cont %>% mutate(xx = 1 - abs(est.reg.ranef.cont/est.fixef.cont)) %>% filter(xx < 0) %>% ungroup() %>% 
  summarise(biased = sum(egger.test), smaller.meta.effects = n())

metac.cont %>% mutate(xx = 1 - abs(est.reg.ranef.cont/est.ranef.cont)) %>% filter(xx < 0) %>% ungroup() %>% 
  summarise(biased = sum(egger.test), smaller.meta.effects.random = n())

#Histogramms of changes +- 100%
metac.cont %>% mutate(xx = 1 - abs(est.reg.ranef.cont/est.fixef.cont)) %>% filter(xx > 0) %>% 
  ggplot(aes(x = xx, fill = factor(egger.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Regression")

metac.cont %>% mutate(xx = 1 - abs(est.reg.ranef.cont/est.fixef.cont)) %>% filter(xx > -1) %>% 
  ggplot(aes(x = xx, fill = factor(egger.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Regression")

metac.cont %>% mutate(xx = 1 - abs(est.reg.ranef.cont/est.ranef.cont)) %>% filter(xx > 0) %>% 
  ggplot(aes(x = xx, fill = factor(egger.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Regression")

metac.cont %>% mutate(xx = 1 - abs(est.reg.ranef.cont/est.ranef.cont)) %>% filter(xx > -1) %>% 
  ggplot(aes(x = xx, fill = factor(egger.test))) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Regression")

metac.cont %>% mutate(xx = 1 - abs(est.reg.ranef.cont/est.fixef.cont)) %>% 
  ggplot(aes(x = xx)) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Fixed effects to Regression")

metac.cont %>% mutate(xx = 1 - abs(est.reg.ranef.cont/est.ranef.cont)) %>% 
  ggplot(aes(x = xx)) + geom_histogram() + xlab("Fraction of Meta-analysis estimate") + ggtitle("Random effects to Regression")

#Scatterplots of meta-analysis and corrected estimates
metac.cont %>% ggplot(aes(x = abs(est.fixef.cont), y = abs(est.reg.ranef.cont))) + geom_point() + 
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  xlab("Fixed effects estimate") + ylab("Regression estimate") + ggtitle("Fixed effects to Regression")

metac.cont %>% ggplot(aes(x = abs(est.ranef.cont), y = abs(est.reg.ranef.cont))) + geom_point() + 
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  xlab("Random effects estimate") + ylab("Regression estimate") + ggtitle("Random effects to Regression")

#Scatterplots of test-statistics:
metac.cont %>% ggplot(aes(x = abs(zval.fixef.cont), y = abs(est.reg.ranef.cont/se.est.reg.ranef.cont))) + geom_point() +
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  ggtitle("Fixed effects and reg.ranef test statistics") + ylab("reg.ranef statistic") + xlab("Fixed effects statistic")

metac.cont %>% ggplot(aes(x = abs(zval.ranef.cont), y = abs(est.reg.ranef.cont/se.est.reg.ranef.cont))) + geom_point() +
  geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm") + 
  ggtitle("Random effects and reg.ranef test statistics") + ylab("reg.ranef statistic") + xlab("Random effects statistic")
```

### 2019-05-13 report/MSc_Report.tex
Changes after Discussion w Prof. Held

@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}mutate\_"{}): no applicable method for 'mutate\_' applied to an object of class "{}function"{}}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pb.meta.merge(meta.bin, meta.cont): could not find function "{}pb.meta.merge"{}}}\end{kframe}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Joining, by = c("{}n"{}, "{}nn"{})}}\end{kframe}
 \end{knitrout}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:57:33 2019
+% Sun May 12 15:22:08 2019
 \begin{table}[ht]
@@
 
-It is possible to analyse all results that are not unique in their comparison, outcome and subgroup in the dataset by meta-analysis.
-So each study that has been repeated with respect to experimental setup is included.
-There are different meta-analys methods that can be applied, here, fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis using the Hartung-Knapp method are used.
+The results that can be pooled are analysed by fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis with Hartung-Knapp method.
 
@@
 if studies were not unique in the dataset with respect to their experimental setup).
-The significant of the treatment effect in a single result is then compared to the significance of the pooled treatment effect.
+The significance of the treatment effect (primary significance) in a single result is then compared to the significance of the pooled treatment effect (secondary significance).
 In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
@@
 
-One can visualise the fraction of studies with significant treatment effect separately for studies with significant primary treatment effect, and non-significant primary treatment effect, as done in Figure \ref{primary.secondary.significance.sep.sig}.
-It can be seen that primary significance and non-significance is often overruled when performing a meta-analysis.
+What has been found is that even the meta-analysis that for all meta-analysis methods, the amount of secondary significance is higher than the amount of primary significance.
+Thus more primarily non-significant results can be attached to a secondarily significant result than vice-versa.
+
+\vspace{0mm}
+To illustrate this, the fraction of studies with significant primary treatment effect and primary non-significant treatment effect can be plotted separately (Figure \ref{primary.secondary.significance.sep.sig}).
 
@@
 
+It can be seen that the extent of overlap between primary and secondary significance varies between meta-analysis.
+A considerable amount of both primary significant and primary non-significant results are overruled by meta-analysis hypothesis tests.
+
 The amount of significant heterogeneity in the results used by the meta-analyses is 53350 and corresponds to 81.5936377\% of the total number of meta-analyses.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:58:07 2019
+% Tue May  7 13:05:39 2019
 \begin{table}[ht]
@@
 
-\chapter{Conclusions}
+\chapter{Discussion}
+
+It is tempting to claim to have a perspective that spans the entire clinical research when looking at the cochrane dataset.
+Several points can be made to argue in this favor (see chapter 2 CITE for details).
+
+\begin{itemize}
+\item Size: Over 52,000 studies, 20,000 comparisons and 47 millions study participants.
+A vast diversity of topics and studies that stem from different institutions and researchers and have been conducted in different countries.
+\item Quality: An organization of field and analysis experts controls quality of both studies and methods.
+\end{itemize}
+
+The dataset is certainly unique with respect to this features.
+The effort of the Cochrane Organization in reprocession, classification and integration of studies in a larger scientific framework is unmatched, not only in clinical science, but in empirical science in general CITE?CITE.
+Regardless whether it is representative of the field of clinical research, it thus provides an exceptional perspective, not only on clinical science, but on empirical science in general.
+
+\vspace{0mm}
+Concerning the generalizability of results of this thesis on clinical science, there are important caveats.
+First of all, intrinisically, the Cochrane Organization focuses on established research of public interest.
+By definition, it can not comprise the full diversity of the field, and especially where research and evidence is new, sparse and not established, it is almost certainly not included.
+The aim of Cochrane is to concentrate scientifical knowledge, thus it can not incorporate studies that are unique in their research subjects and are on the ``periphery'' of science.
+
+\vspace{0mm}
+It is said in the Cochrane Handbook that Cochrane Field groups orchestrate the efforts of their groups and set emphasis on certain research.
+It is thus clear, that the Cochrane Library only comprises a selective fraction of clinical research.
+
+\vspace{0mm}
+Although Cochrane strives to include unpublished study results, it almost certainly provides a selective view by including more published studies.
+Apart from language issues, publication bias might be the largest source of bias.
+This leads us to the main topic of this masters thesis: small study effects and publication bias in the Cochrane Library.
+Thus, the research question of this thesis is in fact connected to the question of how representative the Cochrane Library is for clinical research.
+The answer to this question is insofar important, as that the issues treated in this thesis have to be addressed to the Cochrane Organization or to clinical science in general.
+This distinction is very important and will be encountered throughout the next pages.
+
+%The conclusions to which one comes with regard to this question directly influence the meaning of the results. 
+% If one decides that the results can not be representative for clinical science, the results mainly concern the work of the Cochrane organization.
+If one decides that the results do at least partially hold for clinical science and science in general, the interpretation of the results change also.
+
+\section{Meta-analyses}
+If one investigates the success of a treatment, the first way of doing so is to investigate to what extent the treatment effect estimate differs from no treatment effect.
+This is usually done by a hypothesis test, where the null hypothesis of no treatment effect is rejected if the p-value of the treatment effect estimate is above a given threshold.
+One decides in this case in favor of the treatment.
+
+\vspace{0mm}
+The aim of a meta-analysis is to re-calculate the treatment effect based on multiple results.
+The treatment effects are pooled and the pooled treatment effect estimate can then again be tested based on the null-hypothesis.
+Although not commonly accepted, this may be a stronger argument for the success of treatment, because meta-analysis can capture consistency among treatment effect estimates among different studies and will result in rejection of a null hypothesis if consistency is given.
+It is thus in line with the empirical principle that experimental findings should be validated based on their reproducibility.
+Consequently, a meta-analysis may provide a significant treatment effect estimate, even if the single results do not.
+
+\vspace{0mm}
+It was the aim of the first section CITE of the results part to compare significance of the treatment effect of single studies with the significance of the pooled effect.
+So the question to be answered was: How does significance in single studies relate to significance when all evidence is included?
+The first kind of significance has been termed primary significance and the second, secondary significance.
+One can imagine 3 scenarios:
+\begin{itemize}
+\item A primary significant study belongs to a group which, overall, can not reject the null-hypothesis of no treatment effect in meta-analysis.
+The study result is then overruled by the result of the meta-analysis (if one is to accept that meta-analysis is a more stringent rule for decision about treatment effects).
+\item The opposite: A non-significant primary study belongs to a group which has a significant pooled treatment effect estimate. The study failed to find evidence for a ``true'' effect.
+\item Primary and secondary significance remain unchanged after meta-analysis.
+\end{itemize}
+
+The amount of overlap between primary and secondary significance was moderate, as it had to be expected based on the methodology of meta-analysis.
+The vast amount of non-significant primary results that contribute in the end to a significant secondary meta-analysis result is compelling.
+This links to the topic of the masters thesis of small study effects and publication bias.
+One ad-hoc interpretation of publication bias is that results that are not significant are less likely to be published (arguably because they show no treatment effect).
+
+\vspace{0mm}
+If one is to prefer, or accept meta-analysis as a way to assess treatment effect evidence, the result provides a strong argument for publication of non-significant results, because they can contribute to evidence for treatment effects in meta-analysis (in a Cochrane review).
+Significant treatment effects that are found may find their into clinical practice and potentially benefit there patients and consumers.
 

### 2019-05-13 report/chapter02.Rnw
Changes after Discussion w Prof. Held

--- 2019-03-28 report/chapter02.Rnw
@@
 % LaTeX file for Chapter 02
-
-<<echo=FALSE>>=
-# PATH_HOME = path.expand("~") # user home
-# PATH = file.path(PATH_HOME, 'thesis/code')
-# source(file.path(PATH, 'prepare.R'))
-
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'Data/PubBias')
-FILE = 'cochrane_2018-06-09.csv'
-PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH, 'code')
-PATH_RESULTS = file.path(PATH, 'results')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-file_results = "pb.RData"
-
-source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-data = pb.readData(path = PATH_DATA, file = FILE)
-tmp = pb.clean(data)
-data = tmp[[1]]
-aliases = tmp[[2]]
-
-require(biostatUZH)
-require(tidyverse)
-require(meta)
-require(xtable)
-@
 
@@
 
+<<echo = FALSE>>=
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+# data = pb.readData(path = PATH_DATA, file = FILE)
+# tmp = pb.clean(data)
+# data = tmp[[1]]
+# aliases = tmp[[2]]
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+  load(file.path(PATH_RESULTS, file.dat))
+} else {
+  data = pb.readData(path = PATH_DATA, file = FILE)
+  tmp = pb.clean(data)
+  data = tmp[[1]]
+  aliases = tmp[[2]]
+  save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+  load(file.path(PATH_RESULTS, file.bin))
+} else {
+  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
+  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+  load(file.path(PATH_RESULTS, file.cont))
+} else {
+  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
+  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
+  load(file.path(PATH_RESULTS, file.meta))
+} else {
+  meta <- pb.meta.merge(meta.bin, meta.cont)
+  save(meta, file =  file.path(PATH_RESULTS, file.meta))
+}
+
+file.cont <- "mly.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+  load(file.path(PATH_RESULTS, file.cont))
+} else {
+  data.cont <- mly.cont(data.ext, 0.05, min.study.number = 2)
+  save(data.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.bin <- "mly.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+  load(file.path(PATH_RESULTS, file.bin))
+} else {
+  data.bin <- mly.bin(data.ext, 0.05, min.study.number = 2)
+  save(data.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+load(file.path(PATH_RESULTS, file = "mly.RData"))
+load(file.path(PATH_RESULTS, file = "data.processed.RData"))
+
+require(biostatUZH)
+require(tidyverse)
+require(meta)
+require(metasens)
+require(gridExtra)
+
+###################################################################################################################
+###################################################################################################################
+
+#Barbiturate Examples
+barbi1 <- arrange(filter(data, file.nr == 21) %>% 
+          select(Study = study.name, Comparison = comparison.name, Outcome = outcome.name, 
+                 Events = events1, Total = total1, Events_c = events2, Total_c = total2) %>% 
+            slice(c(1,3)), Study) 
+barbi2 <- arrange(filter(data, file.nr == 21) %>% 
+          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study)
+barbi2[barbi2$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
+
+#Missing values
+cont.out <- data %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
+                                 outcome.measure.new == "Hedges' G")
+
+missing.mean <- which(is.na(cont.out$mean1) | is.na(cont.out$mean2))
+missing.effect <- which(is.na(cont.out$effect))
+missing.means <- intersect(missing.mean, missing.effect) #Cont. results that have neither complete means nor an effect
+wrong.effect <- which(cont.out$mean1 == 0 & cont.out$mean2 == 0 & cont.out$effect == 0) #Cont.results that have only zeros
+missing.effects <- length(c(missing.means, wrong.effect))
+
+missing.sd <- which(is.na(cont.out$sd1) | is.na(cont.out$sd2))
+missing.se <- which(is.na(cont.out$se))
+missing.sds <- intersect(missing.se, missing.sd) #Cont. results that have neither complete means nor an effect
+wrong.sds <- which(cont.out$sd1 == 0 & cont.out$sd2 == 0 & cont.out$se == 0) #Cont.results that have only zeros
+missing.sds <- length(c(missing.sds, wrong.sds))
+
+missing.ss <- which(is.na(data$total1) | is.na(data$total2))
+wrong.ss <- which(data$total1 <= 0 | data$total2 <= 0)
+missing.ssize <- length(c(missing.ss, wrong.ss))
+
+missing.year <- sum(is.na(data$study.year)) + length(c(which(data$study.year < 1920), which(data$study.year > 2019)))
+
+missing.table <- rbind("Missing mean values and mean differences" = missing.effects,
+                         "Missing standard deviations and standard errors" = missing.sds,
+                         "Missing sample sizes" = missing.ssize,
+                         "Missing study year" = missing.year)
+
+#Mean and median number of different outcome types of reviews
+mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
+  ungroup() %>% group_by(file.nr) %>%
+  count() %>% ungroup %>% summarise(mean = mean(n))
+
+median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
+  ungroup() %>% group_by(file.nr) %>%
+  count() %>% ungroup %>% summarise(mean = median(n))
+
+#Study.year quantiles:
+data.ext <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
+publication.year.range <- c(quantile(data.ext$study.year, 0.05, na.rm = T), quantile(data.ext$study.year, 0.25, na.rm = T), 
+                            quantile(data.ext$study.year, 0.5, na.rm = T), quantile(data.ext$study.year, 0.75, na.rm = T),
+                            round(mean(data.ext$study.year, na.rm = T), 2))
+
+#Outcome.measure frequency table:
+outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.new) %>% count() %>% 
+                                       arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9),
+                                     data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% 
+                                       ungroup() %>% filter(row_number() > 8) %>% 
+                                       summarise(outcome.measure.new = "other", n = sum(n)))
+
+outcome.measure.frequencies <- outcome.measure.frequencies %>% mutate(percentage = round(n/sum(n),3)*100)
+names(outcome.measure.frequencies) <- c("Outcome measure", "n", "Percentage")
+outcome.measure.frequencies$Percentage <- paste(outcome.measure.frequencies$Percentage, "%", sep = "")
+
+#Total and group size quantiles:
+data.ext <- data.ext %>% ungroup() %>%  mutate(total.n = total1 + total2)
+samplesize.range <- c(quantile(data.ext$total.n, 0.05, na.rm = T), quantile(data.ext$total.n, 0.25, na.rm = T), 
+                            quantile(data.ext$total.n, 0.5, na.rm = T), quantile(data.ext$total.n, 0.75, na.rm = T),
+                            round(mean(data.ext$total.n, na.rm = T), 2))
+treatment.group.size.range <- c(quantile(data.ext$total1, 0.05, na.rm = T), quantile(data.ext$total1, 0.25, na.rm = T), 
+                      quantile(data.ext$total1, 0.5, na.rm = T), quantile(data.ext$total1, 0.75, na.rm = T),
+                      round(mean(data.ext$total1, na.rm = T), 2))
+
+#Frequencies of results:
+comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
+comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
+                      quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
+                      round(mean(comp.freq$n, na.rm = T), 2))
+
+#Frequencies of studies:
+study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
+study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
+                      quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
+                      round(mean(study.freq$n, na.rm = T), 2))
+
+#Pooling studies
+cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
+  filter(n < 15) %>%
+  full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
+  ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
+# cum.repr.trials.nosub <- data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+#   filter(n < 15) %>%
+#   full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+#                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
+#   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
+
+# cum.repr.trials <- cbind(cum.repr.trials.nosub, cum.repr.trials.subg)[,c(1,3,6)]
+
+colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
+@
+
 \chapter{The Cochrane Dataset}
 
+\section{Cochrane Systematic Reviews}
+As has been mentioned before, the Cochrane Group has specialized on systematic reviews in clinical science.
+Certain knowledge of standards and principles of the Cochrane Group may help to assess the quality and the properties of the dataset.
+The following information stems from the Cochrane Handbook for Systematic Reviews \citep{cochrane.handbook}.
+
+\vspace{0mm}
+The definition of a systematic review is that it ``attempts to collate all empirical evidence that fits pre-specified eligibility criteria in order to answer a specific research question.'' Thus, the ``key properties of a review are'':
+
+\begin{itemize}
+\item``a clearly stated set of objectives with pre-defined eligibility criteria for studies''
+\item ``an explicit, reproducible methodology''
+\item ``a systematic search that attempts to identify all studies that would meet the eligibility criteria''
+\item ``an assessment of the validity of the findings of the included studies, for example through the assessment of risk of bias''
+\end{itemize}
+
+At the end of a systematic review, ``a systematic presentation, and synthesis, of the characteristics and findings of the included studies'' is done.
+
+\vspace{0mm}
+53 Cochrane Review Groups prepare and maintain the reviews within specific areas of health care.
+A group consists of ``researchers, healthcare professionals and people using healthcare services (consumers)''.
+
+\vspace{0mm}
+The groups are supported by Method Groups, Centres and Fields.
+The Cochrane Method Groups aim to discuss and consult the groups in methodological questions concerning review preparation.
+The Centres play a main role in training and support of the Groups.
+The Fields are responsible for broad medical research areas and follow priorities in those areas by advice and control of the groups.
+
+\vspace{0mm}
+The first step in a review is writing a protocoll, specifying the research question, the methods to be used in literature search and analysis and the eligibility criteria of the study.
+Changes in protocolls are possible but have to be documented and the protocol is published in advance of the publication of the full review.
+The choices of methodology as well as the changes should not be made ``on the basis of how they affec the outcome of the research study''.
+
+\vspace{0mm}
+In order to avoid potential conflicts of interests, there is a code of conduct that all entities of the Cochrane Organization have to agree on: conflicts of interest must be disclosed and possibly be forwarded to the Cochrane Centre, and participation of review authors in the studies used have to be acknowledged.
+Additionally, a Steering Group publishes a report of potential conflicts of interests based on information about external funding of Cochrane Groups.
+
+\vspace{0mm}
+In order for keeping the reviews up-to-date, they are revised in a two-year cicle with exceptions.
+In addition to inclusion of new evidence in a field, the revision and maintenance process may as well includes change in analysis methods.
+This can reflect some advance in clinical science as for example new informations about important subgroups, as well as new methods for conducting a Cochrane Review.
+However, there are no clear guidelines and the Cochrane Groups are free in the rate and extent of up-dating their reviews.
+
+\subsection{Methods for Cochrane Reviews}
+A research question defines the following points: ``the types of population (participants), types of interventions (and comparisons), and the types of outcomes that are of interest''.
+From the research question, ususally the eligibility criteria follow.
+Usually, outcomes are not part of eligibility criteria, except for special cases such as adverse effect reviews.
+
+\vspace{0mm}
+The type of study is an important eligibility criterium.
+The Cochrane Collaboration focuses ``primarily on randomized controlled trials'', and also, the methods of study identification in literature search are focused on randomized trials.
+Furthermore, study characteristics such as blinding of study operators with respect to treatment and cluster-randomizing might be additional eligibility criteria which have to be chosen by the review authors.
+
+\vspace{0mm}
+After having specified the eligibility criteria, studies have to be collected.
+The central idea of systematic reviews, and also meta-analyses, is that the collected studies are a random sample of a population of studies, i.e.
+that they are representative and can be used to assess population properties.
+Therefore, the search process is crucial, as a selective search result may impose bias on the sample of studies available, making it a non-random sample.
+For this purpose, the Cochrane Groups are advised to go beyond MEDLINE !!cite!!, because a search restricted to it has been shown to deliver only 30\% to 80\% of available studies.
+``Time and budget restraints require the review author to balance the thoroughness of the search with efficiency in use of time and funds and the best way of achieving this balance is to be aware of, and try to minimize, the biases such as publication bias and language bias that can result from restricting searches in different ways.'' It is important to note that not only studies, but also study reports are occasionally used in the reviews, as they may provide useful information.
+
+\vspace{0mm}
+There are different sources that are being used to search for studies. 
+\begin{itemize}
+\item The Cochrane Central Register of Controlled Trials is a source of reports of controlled trials.
+``As of January 2008 (Issue 1, 2008), CENTRAL contains nearly 530,000 citations to reports of trials and other studies potentially eligible for inclusion in Cochrane reviews, of which 310,000 trial reports are from MEDLINE, 50,000 additional trial reports are from EMBASE and the remaining 170,000 are from other sources such as other databases and handsearching.'' It includes citations published in many languages, citations only available in conference proceedings, citations from trials registers and trials results registers.
+\item MEDLINE.
+MEDLINE includes over 16 million references to journal articles.
+5,200 journals publishing in 27 languages are indexed for MEDLINE.
+PubMed gives access to a free version of MEDLINE with up-to-date citations.
+NLM gateway such as the Health Services Research Project, Meeting Abstracts and TOXLINE Subset for toxicology citations allows for search in both databases together with additional data from the US National Library of Medicine.
+\item EMBASE.
+4,800 Journals publishing in 30 languages are indexed to EMBASE, which includes more than 11 million records from 1974 onwards.
+EMBASE.com also includes 7 million unique records from MEDLINE (1966 up to date) together with its own records.
+Additionally, EMBASE Classic allows access to digitized records from 1947 to 1973.
+EMBASE and MEDLINE each have around 1,800 journals not indexed in the other databse.
+\item Regional or national and subject specific databases can additionally be consulted and often provide important information. Financial considerations may limit the use of such databases.
+\item General search engines such as Google Scholar, Intute and Turning Research into Practice (TRIP) database can be used.
+\item Citation Indexes.
+The database lists articles published in around 6,000 Journals with articles in which they have been cited and is available online as SciSearch.
+This form of search is known as cited reference searching.
+\item Dissertation sources. Dissertations are often listed in MEDLINE or EMBASE but one is advised to also search in specific dissertation sources.
+\item Grey Literature Databases.
+Approximately 10\% of the results in the Cochrane Database stems from conference abstracts and other grey literature.
+The Institute for Scientific and Technical Information in France provides access to entries of the previously closed System for Information on Grey Literature database of the European Association for Grey Literature Exploitation).
+Another source is the Healthcare Management Information Consortium (HMIC) database containing records from the Library and Information Services department of the Department of Health (DH) in England and the King's Fund Information and Library Service.
+The National Technical Information Service (NTIS) gives access to the results of US and non-US government-sponsored research, as well as technical report for most published results.
+References from newsletters, magazines and technical and annual reports in behavioral science, psychology and health are provided in the PsycEXTRA database which is linked to PsycINFO database.
+\end{itemize}
+
 \subsection{Structure and Content}
-The dataset consists of \Sexpr{length(unique(data$file.nr))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(data$study.name))} studies.
-Each study provides data of (multiple) comparisons of clinical interventions. 
-% It can not be ruled out that some comparisons are retrospective, e.g. from observational studies. 
-In Table \ref{barbiturate.row}, two comparisons from a systematic review about effects of barbiturates are shown as they are given in the dataset.
-As can be seen, the comparison is further specified by the variables in the columns.
-One row of the dataset is one comparison.
+The dataset consists of \Sexpr{length(unique(data$file.nr))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(data$study.name))} studies and \Sexpr{dim(data)[1]} results.
+A result compares clinical or medical interventions or treatments.
+Each study provides (multiple) results of clinical interventions.
+
+In Table \ref{barbiturate.row}, two results from a systematic review about effects of barbiturates are shown as they are given in the dataset.
+As can be seen, the result is further specified by the variables in the columns.
+The comparison variable specifies what treatments or interventions are compared, the outcome variable how it is compared, and the subgroup variable (not given in table) indicates if the result belongs to a certain subgroup.
+Here, the result is of a binary outcome, so the events in the barbiturate treatment group and the total number of participants are given in columns ``Events'' and ``Total'' and the number of events in the control group ``Events\_c'' and participants ``Total\_c''.
+Events denotes here number of deaths at the end of follow up.
 
 <<echo=FALSE, results = 'asis'>>=
-tp1 <- arrange(filter(data, file.nr == 21) %>% 
-          select(Study = study.name, Comparison_type = comparison.name, Outcome = outcome.name, 
-                 Events = events1, Total = total1, Events_c = events2, Total_c = total2) %>% 
-            slice(c(1,3)), Study)
-print(xtable(tp1, label = "barbiturate.row", caption = "Example of two comparisons as given in the dataset.
+print(xtable(barbi1, label = "barbiturate.row", digits = 0,
+             caption = "Example of two results as given in the dataset.
 Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
-Further descriptive variables have been ommitted"), include.rownames = F, size = "scriptsize")
+Further descriptive variables have been ommitted"),
+      include.rownames = F, size = "scriptsize")
 @
 
-A complete listing of the variables is given in Table \ref{variable}.
-They can roughly be separated into variables that specify the review in which the comparison is contained and variables that specify the comparison itself (separated by a horizontal line in Table \ref{variable}).
+A complete listing of the variables of a result is given in Table \ref{variable}.
+They can roughly be separated into variables that specify the review in which the result is contained and variables that specify the result itself (separated by a horizontal line in Table \ref{variable}).
 
@@
 
-% \vspace{0mm}
-% Lets consider the previously mentioned barbiturate and head injury review.
+\vspace{0mm}
+The structure of a review will now be outlined based on an example of the dataset.
+Lets consider the previously mentioned barbiturate and head injury review.
 The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates''.
-The medical background is that one knew that barbiturates could cause relief in intra-cranial pressure, but also reduce cerebral blood flow.
-Because one effect is thought to be beneficial for persons with severe head injuries while the other isn't, the authors of the review wanted to find out if there is a net benefit of barbiturates.
-% 
-% \vspace{0mm}
-% The review comprises five studies in total.
-Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental, which would be the comparison/research subject to speak in the previously introduced notions.
-% 
-% \vspace{0mm}
-% All the studies convey multiple information to the review.
-As an example, that could be death or death \textit{and} severe disability at follow up as an outcome.
-Again, the study can be further split up in different subgroups, here for example in a group with - and without haematoma.
-% 
-% \vspace{0mm}
-% The complete listing of outcomes is in table \ref{barbiturates}.
+Since there are arguments for and against use of barbiturates, the authors of the review did a comprehensive literature search and collected all available study findings.
+
+\vspace{0mm}
+The review comprises five studies in total.
+Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental, which would be the comparison to speak in the previously introduced notion.
+The studies have different outcomes, for example, death or death and severe disability at follow up.
+One study split up outcomes for patients with and without haematoma, which would be subgroups.
+
+\vspace{0mm}
+The complete listing of outcomes is in table \ref{barbiturates}.
 The table also gives an illustration of the variety of data that can be included in a review.
-We have for example continuous and binary outcome data, that again is divided into a variety of different things that have been measured.
-Often, additionally to the main study result, also adverse effects are for example included which are in this case separate outcomes and possibly subgroups.
+We have for example continuous (mean body temperature) and binary outcome data (death).
+Additionally to primary and secondary outcomes, often also dropouts and adverse effects are included in a review.
 
 <<echo=FALSE, results='asis'>>=
-tp1 <- arrange(filter(data, file.nr == 21) %>% 
-          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study)
-tp1[tp1$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
-print(xtable(tp1, label = "barbiturates", caption = "Barbiturate and head injury review.
-In the columns, study names, comparison types and outcome measure of the comparisons are given"), include.rownames = F, size = "footnotesize")
+print(xtable(barbi2, label = "barbiturates", caption = "Barbiturate and head injury review.
+In the columns, study names, comparison and outcome measure of the results are given"), include.rownames = F, size = "footnotesize")
 @
 
-% The research subject or outcome type can possibly already be well defined in the general review question.
-Conversely, research subject or comparison has to be further specified in outcome and subgroup categories.
-As may have been implied, the terminology does not rely to a hundred percent on strict functional definitions.
-
-It is important to not confuse comparisons with studies.
-A study can contribute multiple comparisons to a systematic review.
-Also, despite a comparison has variables concerning event counts and means, it can only have one of the two, either means (if the outcome measure is continuous) or event counts (for binary outcomes).
+It is important not to confuse results with studies. A study can contribute multiple results to a systematic review, for example, primary and secondary outcomes and adverse effects.
 
 \vspace{0mm}
-Having provided an overview over the dataset, now, some more specific information is provided.
-The dataset consists of \Sexpr{dim(data)[1]} comparisons and has \Sexpr{dim(data)[2]} variables that specify the comparisons.
 Information about missing values in the dataset is given in Table \ref{missing}.
@@
 The relative amount of missing values is very low except for study years.
-
-<<echo=FALSE>>=
-missing.mean <- data %>% filter(!is.na(sd1) & sd1 > 0) %>% filter(!is.na(sd2) & sd2 > 0) %>% 
-  summarise(total = length(sd1), na  = sum(is.na(mean1) | is.na(mean1))) %>% select(na)
-
-missing.sd <- data %>% filter(!is.na(mean1) & !is.na(mean2)) %>% filter(mean1 != 0 & mean2 != 0) %>%
-  summarise(total = length(mean1), na.sd  = sum(is.na(sd1) | is.na(sd1)), null.sd = length(sd1[sd1 <= 0 | sd2 <= 0])) %>% 
-  mutate(miss = na.sd + null.sd) %>% select(miss)
-
-missing.ssize <- data %>% summarize(total = length(total1), null.ss = length(total1[total1 <= 0 | total2 <= 0])) %>% 
-  select(null.ss)
-
-missing.effect <- sum(is.na(data$effect))
-
-missing.year <- sum(is.na(data$study.year)) + length(data$study.year[data$study.year == 0])
-
-# missing.outcome <- sum(is.na(data$effect))
-
-# null.events <- data %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
-#   filter(is.na(sd1) | sd1 <= 0) %>% filter(is.na(sd2) | sd2 <= 0) %>% 
-#   summarise(null.ev = length(total1[events1 <= 0 & events2 <= 0]), total = length(events1)) %>% 
-#   mutate(f = null.ev/total) %>% select(f)
-# 
-# null.events.single <- data %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
-#   filter(is.na(sd1) | sd1 <= 0) %>% filter(is.na(sd2) | sd2 <= 0) %>% 
-#   summarise(null.ev = length(total1[events1 <= 0 | events2 <= 0]), total = length(events1)) %>% 
-#   mutate(f = null.ev/total) %>% select(f)
-# 
-# missing.events <- data %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
-#   filter(is.na(sd1) | sd1 <= 0) %>% filter(is.na(sd2) | sd2 <= 0) %>% 
-#   summarise(na.ev = sum(is.na(events1) | is.na(events2)), total = length(events1)) %>% 
-#   mutate(f = na.ev/total) %>% select(f)
-@
+In the case of continuous outcomes, the cases have been counted were effect sizes and standard errors of effect sizes are not available.
+This means that neither mean values of groups nor mean differences are given, or that neither standard deviation nor standard error is given for a result.
+Study years before 1920 and after 2019 have been counted as missing, as well as sample sizes below zero.
 
 <<echo=FALSE, results='asis'>>=
-  missing.table <- rbind("Missing mean values" = missing.mean[1,1],
-                         "Missing standard deviations" = missing.sd[1,1],
-                         "Missing sample sizes" = missing.ssize[1,2],
-                         "Missing effects" = missing.effect,
-                         "Missing study year" = missing.year)
-
 print(xtable(missing.table, label = "missing", caption = "Number of missing variables and measurements in the dataset", align = "lr"), include.colnames = F,
@@
 
-More properties of the reviews, the studies and the comparisons in the dataset will be provided on the following pages.
-The publication dates of the studies included in the dataset are shown in Figure \ref{study.years}.
-Most studies were published after 2000.
-
-\begin{figure}
-<<echo=FALSE>>=
-data %>% filter(study.year < 2019 & study.year > 1920) %>% ggplot(aes(x = study.year)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
-  theme_bw() + xlab("Year") + ylab("Study frequency")
-@
-\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications}
-\label{study.years}
-\end{figure}
-
-Figure \ref{study.outcomes} provides the frequencies of outcome types of the comparisons.
-Note that the abundance of mean differences and standardized mean differences can also give an impression of the proportion of continuous outcome comparisons vs.
-binary outcome comparisons in the dataset.
-
-\begin{figure}
-<<echo=FALSE>>=
-data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9) %>% 
-  ggplot(aes(x = outcome.measure.new, y = n)) +
-  geom_col(col = "gray15", fill = "dodgerblue") +
-  theme_bw() + ylab("Comparison frequency") + xlab("Outcome measure")
-@
-\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded}
-\label{study.outcomes}
-\end{figure}
-
-It is also possible to look at the properties of the reviews.
-One question could be how many studies or comparisons that a review comprises.
-The former is shown in Figure \ref{studies.per.review} and the latter in Figure \ref{comparisons.per.review}.
-It can be seen that while almost 400 reviews consist of one study only, there are more than 150 with equal or more than 30 distinct studies.
-A similar variance between reviews can also be observed when looking at the number of comparisons.
-
-\begin{figure}
-<<echo=FALSE>>=
-data %>% group_by(file.nr) %>% distinct(study.name) %>% count() %>%
-  filter(n < 50) %>%
-  full_join( data %>% group_by(file.nr) %>% distinct(study.name) %>% count %>%
-               filter(n > 49) %>% mutate(n = 50)) %>%
-  group_by(n) %>% count() %>%
-  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
-  theme_bw() + xlab("Study number") + ylab("Reviews Frequency")
-@
-\caption{Empirical distribution of number of studies per review}
-\label{studies.per.review}
-\end{figure}
-
-\begin{figure}
-<<echo=FALSE>>=
-data %>% group_by(file.nr) %>% count() %>%
-  filter(n < 50) %>%
-  full_join( data %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
-               filter(n > 49) %>% mutate(n = 50)) %>%
-  group_by(n) %>% count() %>%
-  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
-  theme_bw() +  xlab("Comparisons") + ylab("Review Frequency")
-# mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
-#   ungroup() %>% group_by(file.nr) %>% 
-#   count() %>% ungroup %>% summarise(mean = mean(n))
-# 
-# median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
-#   ungroup() %>% group_by(file.nr) %>% 
-#   count() %>% ungroup %>% summarise(mean = median(n))
-@
-\caption{Empirical distribution of number of comparisons per review}
-\label{comparisons.per.review}
-\end{figure}
-
-A question not to be mistaken with the previous would be how many comparison \textit{types} there are per review.
-This gives an additional impression of the scope of a review.
-Analogously to the previous figures, the empirical distribution of comparison types is depicted in Figure \ref{subjects.per.review}.
-
-\begin{figure}
-<<echo=FALSE>>=
-data %>% group_by(file.nr) %>% distinct(comparison.name) %>% count() %>%
-  filter(n < 15) %>%
-  full_join( data %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
-               filter(n > 14) %>% mutate(n = 15)) %>%
-  group_by(n) %>% count() %>%
-  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
-  theme_bw() +  xlab("Comparison type number") + ylab("Review frequency")
-
-mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
-  ungroup() %>% group_by(file.nr) %>% 
-  count() %>% ungroup %>% summarise(mean = mean(n))
-
-median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
-  ungroup() %>% group_by(file.nr) %>% 
-  count() %>% ungroup %>% summarise(mean = median(n))
-@
-\caption{Empirical distribution of number of different comparison types per review}
-\label{subjects.per.review}
-\end{figure}
-
-% At the end, a main goal of the thesis is to analyze reviews with respect to reporting bias in meta analyses. 
-For comparisons to be suitable for usage in meta-analysis, they have to be somewhat identical (same comparison type, outcome measure and possibly subgroup).
-For an analysis of reporting bias, again a certain number of studies is required in order for reporting bias to be detectable by the methods.
-One question would therefore be: How many groups of identical comparisons of a certain size are given in the dataset?
-This depends on which degree of similarity between comparisons is considered to be sufficient.
+The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = \Sexpr{publication.year.range[1]}).
+The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{publication.year.range[5]} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}.
+Only a handful ($n$ = 18) have been published in 2018, none in 2019.
+No information is available concerning unpublished results and studies.
 
 \vspace{0mm}
-In Table \ref{repr.groups}, two different similarity criteria have been used.
-One is based on the same comparison type and outcome measure, the other includes additionally subgroup affiliation of comparisons, i.e.
-only comparisons in the same subgroups are considered to be similar enough.
+The results of a study are summarised in a result by a effect measure.
+This effect measure varies, depending on whether data is continuous, binary or time-to-event.
+The most abundant effect measures used are summarised in Table \ref{outcome.measure.frequencies}.
+One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the being some sort of discrete or binary outcomes, most often binary (> 65\%).
+
+<<echo=FALSE, results='asis'>>=
+print(xtable(outcome.measure.frequencies, label = "outcome.measure.frequencies", 
+             caption = "Frequencies of outcome measures among results. n denotes the total number 
+             of results with the outcome measure and percentage the percentage of the outcome measure,", 
+             align = "llll", digits = 1), include.rownames = F, size = "footnotesize")
+@
+
+The sample sizes amongst results vary to some extent.
+There are 5\% of treatment group sample sizes that are smaller tha \Sexpr{treatment.group.size.range[1]}, the 5\% quantile.
+The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{treatment.group.size.range[5]} and the third quartile \Sexpr{treatment.group.size.range[4]}.
+The large difference between median and mean is caused by very large groups with over 2,000,000 participants.
+Analogously, the quantiles of the total sample size are: 5\% quantile = \Sexpr{samplesize.range[1]}, first quartile = \Sexpr{samplesize.range[2]}, median = \Sexpr{samplesize.range[3]} and third quartile = \Sexpr{samplesize.range[4]}.
+The mean is \Sexpr{samplesize.range[5]}.
 
 \vspace{0mm}
-Table \ref{repr.groups} shows the cumulative number of \textit{groups} of comparisons with equal or more than $n$ comparisons.
-Practically, this means that this number of meta analyses can be performed with each having at least $n$ comparisons.
+The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}.
+There are \Sexpr{comp.range[1]} reviews with five or fewer results, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}.
+Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]}.
+The discrepancy between mean and median is again due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxisfor preventing infection after cesarean section, with 95 studies and 1497 results in total.
+
+\vspace{0mm}
+For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome.
+More speicifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis since their research subject and experimental setup can be considered sufficiently homogeneous.
+%Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
+\vspace{0mm}
+The amount of studies that can be pooled for meta-analyses is of special interest in this masters thesis.
+Thus, the dataset is divided in groups whith identical experimental setup.
+The size of the group denotes how many results are included in a group.
+
+\vspace{0mm}
+Table \ref{repr.groups} shows the number of \textit{groups} of groups with equal or more than $n$ results.
+Practically, this means that a given number of meta analyses can be performed with each having at least $n$ results.
 
 <<echo=FALSE, results='asis'>>=
-cum.repr.trials.nosub <- data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
-  filter(n < 15) %>%
-  full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
-               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
-  ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
 
-cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
-  filter(n < 15) %>%
-  full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
-               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
-  ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
-
-cum.repr.trials <- cbind(cum.repr.trials.nosub, cum.repr.trials.subg)[,c(1,3,6)]
-
-colnames(cum.repr.trials)  <- c("n", "Cumulative sum (without subgroups)", "Cumulative sum (with subgroups)")
-
-print(xtable(cum.repr.trials, label = "repr.groups", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
+print(xtable(cum.repr.trials.subg, label = "repr.groups", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
 @

### 2019-05-13 report/chapter03.Rnw
Changes after Discussion w Prof. Held

@@
                echo=TRUE, message=FALSE,
-               fig.width=8.1, fig.height=3.4,
+               fig.width=8.1, fig.height=3,
                out.width='\\textwidth-3cm',
@@
 <<echo=FALSE>>= 
+rm(list = ls())
 PATH_HOME = path.expand("~") # user home
@@
   aliases = tmp[[2]]
+  save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
 
@@
 } else {
-  meta.bin <- meta.bin.complete(data, min.study.number = 10, sig.level = 0.05)
+  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
   save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
@@
 } else {
-  meta.cont <- meta.cont.complete(data, min.study.number = 10, sig.level = 0.05)
+  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
   save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
@@
 
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
+  load(file.path(PATH_RESULTS, file.meta))
+} else {
   meta <- pb.meta.merge(meta.bin, meta.cont)
+  save(meta, file =  file.path(PATH_RESULTS, file.meta))
+}
 
@@
 require(gridExtra)
-require(xtable)
 @
@@
 \end{figure}
+
+It can be seen that the extent of overlap between primary and secondary significance varies between meta-analysis.
+A considerable amount of both primary significant and primary non-significant results are overruled by meta-analysis hypothesis tests.
 
@@
 
-change.ranef.bin <- meta.bin %>% ungroup() %>% select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>% mutate(sig.change = factor(sig.change)) %>% group_by(sig.change, correction.method) %>% count()
+change.ranef.bin <- meta.bin %>% ungroup() %>% 
+  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+	mutate(n = n/sum(n))
 
@@
   gather(key = "correction.method", value = "sig.change") %>%  
-  mutate(sig.change = factor(sig.change)) %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+ 
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
   annotate("text", x = change.ranef.bin[change.ranef.bin$sig.change == 3,]$correction.method, y = 1000, 
-         label = paste(change.ranef.bin[change.ranef.bin$sig.change == 3,]$n, "changed to nonsig."), 
-         color = "white")
-
-change.ranef.cont <- meta.cont %>% ungroup() %>% select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()
+         label = paste(round(change.ranef.bin[change.ranef.bin$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
+         color = "white")
+
+change.ranef.cont <- meta.cont %>% ungroup() %>% 
+  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
+  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+	mutate(n = n/sum(n))
 
@@
   gather(key = "correction.method", value = "sig.change") %>%  
-  mutate(sig.change = factor(sig.change)) %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes") +
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
   annotate("text", x = change.ranef.cont[change.ranef.cont$sig.change == 3,]$correction.method, y = 500, 
-         label = paste(change.ranef.cont[change.ranef.cont$sig.change == 3,]$n, "changed to nonsig."), 
-         color = "white")
-
-change.ranef <- meta %>% ungroup() %>% select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()
+         label = paste(round(change.ranef.cont[change.ranef.cont$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
+         color = "white")
+
+change.ranef <- meta %>% ungroup() %>% 
+  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
+  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+	mutate(n = n/sum(n))
 
@@
   gather(key = "correction.method", value = "sig.change") %>%  
-  mutate(sig.change = factor(sig.change)) %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
   annotate("text", x = change.ranef[change.ranef$sig.change == 3,]$correction.method, y = 1500, 
-         label = paste(change.ranef[change.ranef$sig.change == 3,]$n, "changed to nonsig."), 
-         color = "white")
-
+         label = paste(round(change.ranef[change.ranef$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
+         color = "white")
+# Significance after correction plots, separated for meta-analyses with significant publication bias test.
 #Fixed effects meta-analysis significance
-change.fixef.bin <- meta.bin %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()
+#Binary outcomes:
+change.fixef.bin <- meta.bin %>% ungroup() %>% 
+  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
+  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+	mutate(n = n/sum(n))
 
@@
   gather(key = "correction.method", value = "sig.change") %>%  
-  mutate(sig.change = factor(sig.change)) %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+  
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
   annotate("text", x = change.fixef.bin[change.fixef.bin$sig.change == 3,]$correction.method, y = 800, 
-         label = paste(change.fixef.bin[change.fixef.bin$sig.change == 3,]$n, "changed to nonsig."), 
-         color = "white")
-
-change.fixef.cont <- meta.cont %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()
+         label = paste(round(change.fixef.bin[change.fixef.bin$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
+         color = "white")
+
+#Continuous outcomes:
+change.fixef.cont <- meta.cont %>% ungroup() %>% 
+  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+  gather(key = "correction.method", value = "sig.change") %>% 
+  mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+	mutate(n = n/sum(n))
 
@@
   gather(key = "correction.method", value = "sig.change") %>%  
-  mutate(sig.change = factor(sig.change)) %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes")+ 
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.nonsig", "unchanged.sig", "change.to.sig")) +
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
   annotate("text", x = change.fixef.cont[change.fixef.cont$sig.change == 3,]$correction.method, y = 300, 
-         label = paste(change.fixef.cont[change.fixef.cont$sig.change == 3,]$n, "changed to nonsig."), 
-         color = "white")
-
+         label = paste(round(change.fixef.cont[change.fixef.cont$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
+         color = "white")
+
+#Overall:
 change.fixef <- meta %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>% group_by(sig.change, correction.method) %>% count()
+  gather(key = "correction.method", value = "sig.change") %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+	mutate(n = n/sum(n))
 
@@
   gather(key = "correction.method", value = "sig.change") %>%  
-  mutate(sig.change = factor(sig.change)) %>% 
+  mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.nonsig", "unchanged.sig", "change.to.sig")) +
+  theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
+	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
   annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 1500, 
-         label = paste(change.fixef[change.fixef$sig.change == 3,]$n, "changed to nonsig."), 
-         color = "white")
-
-# Significance after correction plots, separated for meta-analyses with significant publication bias test.
+         label = paste(round(change.fixef[change.fixef$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
+         color = "white")
+
+#Separated for meta-analyses with significant publication bias test.
 change.fixef.bias <- meta %>% 
@@
   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-  filter(thomson.test == 1) %>% group_by(sig.change, correction.method) %>% count()
+  filter(thomson.test == 1) %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+	mutate(n = n/sum(n))
 
@@
   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-  filter(thomson.test == 1) %>% mutate(sig.change = factor(sig.change)) %>% 
+  filter(thomson.test == 1) %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-  ggtitle("Meta analysis with significant small study effect")+ 
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
-  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 100, 
-           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
+  theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
+	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 250, 
+           label = paste(round(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
            color = "white")
@@
   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-  filter(thomson.test == 0) %>% group_by(sig.change, correction.method) %>% count()
+  filter(thomson.test == 0) %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>%  
+	mutate(n = n/sum(n))
 
@@
   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-  filter(thomson.test == 0) %>%   mutate(sig.change = factor(sig.change)) %>% 
+  filter(thomson.test == 0) %>% 
+	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-  ggtitle("Meta analysis with non-significant small study effect")+ 
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged.nonsig", "change.to.sig", "unchanged.sig", "change.to.nonsig")) +
-  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 900, 
-           label = paste(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n, "changed to nonsig."), 
+  theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
+	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+  annotate("text", x = change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$correction.method, y = 1300, 
+           label = paste(round(change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
            color = "white")

### 2019-05-13 report/chapter05.Rnw
Changes after Discussion w Prof. Held

--- 2019-04-25 report/MSc_Report.tex
@@
-\documentclass[11pt,a4paper,twoside]{book}\usepackage[]{graphicx}\usepackage[]{color}
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
+% LaTeX file for Chapter 05
+<<'preamble05',include=FALSE>>=
+library(knitr)
+opts_chunk$set(
+    fig.path='figure/ch05_fig', 
+    self.contained=FALSE,
+    cache=TRUE
+) 
+@
 
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
+\chapter{Discussion}
 
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
+It is tempting to claim to have a perspective that spans the entire clinical research when looking at the cochrane dataset.
+Several points can be made to argue in this favor (see chapter 2 CITE for details).
 
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+\begin{itemize}
+\item Size: Over 52,000 studies, 20,000 comparisons and 47 millions study participants.
+A vast diversity of topics and studies that stem from different institutions and researchers and have been conducted in different countries.
+\item Quality: An organization of field and analysis experts controls quality of both studies and methods.
+\end{itemize}
 
-\usepackage{alltt}
-\input{header.sty}   % packages, layout and standard macros
-
-\usepackage{verbatim}
-\usepackage{tikz}
-\usepackage{amssymb}
-\usetikzlibrary{trees}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\begin{document}
-\input{title}
-
-\graphicspath{{./figure/}}
-\DeclareGraphicsExtensions{.pdf,.png}
-\setcounter{tocdepth}{1}
-
-\thispagestyle{empty}
-\begin{center}
-  \vspace*{6cm}{\bfseries\Huge
-  $p$-values:\\[5mm] their use, abuse and proper use \\[5mm]
-  illustrated with seven facets 
-  }
-  \vfill
-  \rm
-
-  \LARGE
-  M\"axli Musterli\\[12mm]
-
-  \normalsize
-  Version \today
-\end{center}
-\newpage
-\thispagestyle{empty}~
-\newpage
-\pagenumbering{roman}
-
-\thispagestyle{plain}\markboth{Contents}{Contents}
-\tableofcontents
-\setkeys{Gin}{width=.8\textwidth}
-
-\chapter*{Preface}
-\addtocontents{toc}{\protect \vspace*{13.mm}}
-\addcontentsline{toc}{chapter}{\bfseries{Preface}}
-\thispagestyle{plain}\markboth{Preface}{Preface}
-
-Howdy!
-
-\bigskip
-
-\begin{flushright}
-  Max Muster\\
-  June 2018
-\end{flushright}
-
-\addtocontents{toc}{\protect \vspace*{10mm}}
-
-\cleardoublepage
-\pagenumbering{arabic}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 01
-
-\chapter{Introduction}
-
-Meta-analysis is at the core of evidence based medicine because it allows to summarise evidence over multiple studies and provide a more broad view on success and effectivity of clinical treatments.
-The necessity of meta-analyses is also increased by the abundance of data and publications.
-Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to make decisions based on quantitative and scientific criteria.
+The dataset is certainly unique with respect to this features.
+The effort of the Cochrane Organization in reprocession, classification and integration of studies in a larger scientific framework is unmatched, not only in clinical science, but in empirical science in general CITE?CITE.
+Regardless whether it is representative of the field of clinical research, it thus provides an exceptional perspective, not only on clinical science, but on empirical science in general.
 
 \vspace{0mm}
-For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention.
-However, the usefulness of meta-analysis does not restrict to clinical science, but to any empirical and quantiative science.
+Concerning the generalizability of results of this thesis on clinical science, there are important caveats.
+First of all, intrinisically, the Cochrane Organization focuses on established research of public interest.
+By definition, it can not comprise the full diversity of the field, and especially where research and evidence is new, sparse and not established, it is almost certainly not included.
+The aim of Cochrane is to concentrate scientifical knowledge, thus it can not incorporate studies that are unique in their research subjects and are on the ``periphery'' of science.
 
 \vspace{0mm}
-Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question.
-Meta-analysis can be applied to all studies that are approximately identical in their experimental setup and the way the outcome of the experiments is measured.
-In systematic reviews where meta-analyses are used, the conclusions are most often strongly based on the results and the interpretation of the meta-analysis.
+It is said in the Cochrane Handbook that Cochrane Field groups orchestrate the efforts of their groups and set emphasis on certain research.
+It is thus clear, that the Cochrane Library only comprises a selective fraction of clinical research.
 
 \vspace{0mm}
-However, there are problems that potentially limit the validity of meta-analysis; the number of studies available can be incomplete or the results of the studies can be biased.
-Some of those problems can be solved or asserted by special statistical methods.
+Although Cochrane strives to include unpublished study results, it almost certainly provides a selective view by including more published studies.
+Apart from language issues, publication bias might be the largest source of bias.
+This leads us to the main topic of this masters thesis: small study effects and publication bias in the Cochrane Library.
+Thus, the research question of this thesis is in fact connected to the question of how representative the Cochrane Library is for clinical research.
+The answer to this question is insofar important, as that the issues treated in this thesis have to be addressed to the Cochrane Organization or to clinical science in general.
+This distinction is very important and will be encountered throughout the next pages.
 
-\subsection{Small Study Effects or Publication Bias}
-When study sample size decreases, the probability of extreme and missleading results in a study increases.
-This becomes a problem if results are selectively published, and therefore available, based on their results.
-When this is the case, one speaks of a small study effect or of ``Publication bias''.
+%The conclusions to which one comes with regard to this question directly influence the meaning of the results. 
+% If one decides that the results can not be representative for clinical science, the results mainly concern the work of the Cochrane organization.
+If one decides that the results do at least partially hold for clinical science and science in general, the interpretation of the results change also.
+
+\section{Meta-analyses}
+If one investigates the success of a treatment, the first way of doing so is to investigate to what extent the treatment effect estimate differs from no treatment effect.
+This is usually done by a hypothesis test, where the null hypothesis of no treatment effect is rejected if the p-value of the treatment effect estimate is above a given threshold.
+One decides in this case in favor of the treatment.
 
 \vspace{0mm}
-The issue has been discussed extensively in the last years, most often in the context of what has came to be known as the replication crisis.
-The reasons for small study effects are manifold, but originate most often in the myopical acting of agents in science and the lack of statistical education.
-Studies are reported by scientists, published by journals and noticed by readers more often if their findigs are positive and find e.g.
-a substantive difference or effect.
-When doing a meta-analysis, one again obtains biased results.
+The aim of a meta-analysis is to re-calculate the treatment effect based on multiple results.
+The treatment effects are pooled and the pooled treatment effect estimate can then again be tested based on the null-hypothesis.
+Although not commonly accepted, this may be a stronger argument for the success of treatment, because meta-analysis can capture consistency among treatment effect estimates among different studies and will result in rejection of a null hypothesis if consistency is given.
+It is thus in line with the empirical principle that experimental findings should be validated based on their reproducibility.
+Consequently, a meta-analysis may provide a significant treatment effect estimate, even if the single results do not.
 
 \vspace{0mm}
-The reason why that is less of an issue for larger studies is that extreme results are in general less likely and that due to larger effort, a result is published although there has been no clear and positive findings.
+It was the aim of the first section CITE of the results part to compare significance of the treatment effect of single studies with the significance of the pooled effect.
+So the question to be answered was: How does significance in single studies relate to significance when all evidence is included?
+The first kind of significance has been termed primary significance and the second, secondary significance.
+One can imagine 3 scenarios:
+\begin{itemize}
+\item A primary significant study belongs to a group which, overall, can not reject the null-hypothesis of no treatment effect in meta-analysis.
+The study result is then overruled by the result of the meta-analysis (if one is to accept that meta-analysis is a more stringent rule for decision about treatment effects).
+\item The opposite: A non-significant primary study belongs to a group which has a significant pooled treatment effect estimate. The study failed to find evidence for a ``true'' effect.
+\item Primary and secondary significance remain unchanged after meta-analysis.
+\end{itemize}
+
+The amount of overlap between primary and secondary significance was moderate, as it had to be expected based on the methodology of meta-analysis.
+The vast amount of non-significant primary results that contribute in the end to a significant secondary meta-analysis result is compelling.
+This links to the topic of the masters thesis of small study effects and publication bias.
+One ad-hoc interpretation of publication bias is that results that are not significant are less likely to be published (arguably because they show no treatment effect).
 
 \vspace{0mm}
-While there is generally no way to assert poor study quality, small study effect can in principle be asserted and corrected for statistically.
-This masters thesis will mainly be about statistical methods to detect and adjust for small study effects.
-It can furthermore be divided in two parts:
-\begin{itemize}
-\item Methodological part: Collection and discussion of statistical tests and correction methods for small study effects.
-\item Applied part: Application of the methods to studies of the Cochrane Library of systematic Reviews. Subsequent discussion of the implications
-of the results for clinical science.
-\end{itemize}
-
-In contrast to simulation studies, it is not possible to assess critical properties of the methods such as the power of a test, since the truth is not known.
-But based on the amount of data, one can of course try to make extrapolation to tendencies in clinical science in general.
-Moreover, it is still interesting to see how the methods behave in general, especially with respect to each other.
-It may, as an example, be possible to answer the question which statistical test is most conservative and which pooling method is most optimistic on average.
-Comparison with results from simulations may allow to speculate about the reasons when simulation and real world results diverge.
-
-\subsection{Cochrane and the Cochrane Database of Systematic Reviews}
-The Cochrane Organization has specialized on systematic reviews in clinical science.
-It publishes and maintains a library with a large number of systematic reviews that are available in some countries to the public.
-
-\vspace{0mm}
-The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite).
-
-\vspace{0mm}
-The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests.
-This might further improve the validity and precision of findings and conclusions that have been made based on this data.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 02
-
-\chapter{The Cochrane Dataset}
-
-\subsection{Structure and Content}
-The dataset consists of 5016 systematic reviews from the Cochrane Library with 52995 studies and 463820 results.
-A result compares clinical or medical interventions or treatments.
-Each study provides (multiple) results of clinical interventions.
-
-In Table \ref{barbiturate.row}, two results from a systematic review about effects of barbiturates are shown as they are given in the dataset.
-As can be seen, the result is further specified by the variables in the columns.
-The comparison variable specifies what treatments or interventions are compared, the outcome variable how it is compared, and the subgroup variable (not given in table) indicates if the result belongs to a certain subgroup.
-Here, the result is of a binary outcome, so the events in the barbiturate treatment group and the total number of participants are given in columns ``Events'' and ``Total'' and the number of events in the control group ``Events\_c'' and participants ``Total\_c''.
-Events denotes here number of deaths at the end of follow up.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:26:47 2019
-\begin{table}[ht]
-\centering
-\begingroup\scriptsize
-\begin{tabular}{lllrrrr}
-  \hline
-Study & Comparison & Outcome & Events & Total & Events\_c & Total\_c \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11 & 41 & 11 & 41 \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14 & 27 & 13 & 26 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Example of two results as given in the dataset.
-Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
-Further descriptive variables have been ommitted}
-\label{barbiturate.row}
-\end{table}
-
-A complete listing of the variables of a result is given in Table \ref{variable}.
-They can roughly be separated into variables that specify the review in which the result is contained and variables that specify the result itself (separated by a horizontal line in Table \ref{variable}).
-
-\begin{table}[ht]
-  \begin{center}
-    \begin{tabular}{l l}
-      \textbf{Variable} & \textbf{Description}\\
-      \hline
-      \textbf{file.nr} & The number of the file from which the review data has been \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
-      \textbf{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
-      \textbf{file.index} & Internal index of the file in the Cochrane library.\\
-      \textbf{file.version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
-      %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
-      \hline
-      \textbf{study.name} & Name of the study to which the result belongs\\
-      \textbf{study.year} & Year in which the study was published\\
-      \hline
-      \textbf{comparison.name/.nr} & Specification of the interventions compared in the study  \\ &and a unique number for the comparison\\
-      \textbf{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ &and a unique number for the outcome\\
-      \textbf{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a \\ &unique number for the subgroup\\
-      \textbf{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
-      \textbf{effect} & Measure of the effect given in the quantity denoted by \\ &``outcome measure''.\\
-      \textbf{se} & Standard error of the measure of the effect,\\
-      \textbf{events1/events2} & The counts of patients with an outcome \textit{if}\\ &measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
-      \textbf{total1/total2} & Number of patients in groups.\\
-      \textbf{mean1/mean2} & Mean of patient measurements \textit{if} outcome is continuous.\\
-      \textbf{sd1/sd2} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
-    \end{tabular}
-  \caption{Dataset variable names and descriptions  \label{variable}}
-
-  \end{center}
-\end{table}
-
-Results are part of studies that are again part of a (systematic) review. This structure of a review is shown in Figure \ref{review}.
-
-\begin{figure}
-\tikzstyle{every node}=[draw=black,thick,anchor=west]
-\tikzstyle{selected}=[draw=red,fill=red!30]
-\tikzstyle{optional}=[dashed,fill=gray!50]
-\begin{tikzpicture}
-[grow = right, anchor = west, 
-  growth parent anchor=east, % added code
-  parent anchor=east]
-  \node {Review} [edge from parent fork right]
-    child { node {Comparison 2}
-      child { node {Outcome 2}}
-      child { node {Outcome 1}
-        child { node {Subgroup 2}}
-        child { node {Subgroup 1}
-          child  { node {Result 2}}
-          child  { node {Result 1}}
-          }}
-    }
-    child [missing] {}		
-    child { node {Comparison 1  }};
-\end{tikzpicture}
-\caption{Structure of a hypothetical review with two different comparisons\label{review.structure}}
-\label{review.structure}
-\end{figure}
-
-\vspace{0mm}
-The structure of a review will now be outlined based on an example of the dataset.
-Lets consider the previously mentioned barbiturate and head injury review.
-The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates''.
-Since there are arguments for and against use of barbiturates, the authors of the review did a comprehensive literature search and collected all available study findings.
-
-\vspace{0mm}
-The review comprises five studies in total.
-Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental, which would be the comparison to speak in the previously introduced notion.
-The studies have different outcomes, for example, death or death and severe disability at follow up.
-One study split up outcomes for patients with and without haematoma, which would be subgroups.
-
-\vspace{0mm}
-The complete listing of outcomes is in table \ref{barbiturates}.
-The table also gives an illustration of the variety of data that can be included in a review.
-We have for example continuous (mean body temperature) and binary outcome data (death).
-Additionally to primary and secondary outcomes, often also dropouts and adverse effects are included in a review.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:26:47 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-Study & Comparison & Outcome \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given} 
-\label{barbiturates}
-\end{table}
-
-It is important not to confuse results with studies. A study can contribute multiple results to a systematic review, for example, primary and secondary outcomes and adverse effects.
-
-\vspace{0mm}
-Information about missing values in the dataset is given in Table \ref{missing}.
-For variables as research subject, outcome and subgroup name and event counts there are no missing values.
-The relative amount of missing values is very low except for study years.
-In the case of continuous outcomes, the cases have been counted were effect sizes and standard errors of effect sizes are not available.
-This means that neither mean values of groups nor mean differences are given, or that neither standard deviation nor standard error is given for a result.
-Study years before 1920 and after 2019 have been counted as missing, as well as sample sizes below zero.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:26:47 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lr}
-  \hline
-  \hline
-Missing mean values and mean differences & 984 \\ 
-  Missing standard deviations and standard errors & 1300 \\ 
-  Missing sample sizes & 12173 \\ 
-  Missing study year & 44649 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Number of missing variables and measurements in the dataset} 
-\label{missing}
-\end{table}
-
-The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982).
-The median of the publication years is 2003, the mean 2006.13 and the quartiles are 1996 and 2008.
-Only a handful ($n$ = 18) have been published in 2018, none in 2019.
-No information is available concerning unpublished results and studies.
-
-\vspace{0mm}
-The results of a study are summarised in a result by a effect measure.
-This effect measure varies, depending on whether data is continuous, binary or time-to-event.
-The most abundant effect measures used are summarised in Table \ref{outcome.measure.frequencies}.
-One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the being some sort of discrete or binary outcomes, most often binary (> 65\%).
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:26:47 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-Outcome measure & n & Percentage \\ 
-  \hline
-Risk Ratio & 232583 & 50.1\% \\ 
-  Mean Difference & 102315 & 22.1\% \\ 
-  Odds Ratio & 49372 & 10.6\% \\ 
-  Std. Mean Difference & 40535 & 8.7\% \\ 
-  Peto Odds Ratio & 19122 & 4.1\% \\ 
-  Hazard Ratio & 6566 & 1.4\% \\ 
-  Risk Difference & 6234 & 1.3\% \\ 
-  Rate Ratio & 2283 & 0.5\% \\ 
-  other & 4810 & 1\% \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Frequencies of outcome measures among results. n denotes the total number 
-             of results with the outcome measure and percentage the percentage of the outcome measure,} 
-\label{outcome.measure.frequencies}
-\end{table}
-
-The sample sizes amongst results vary to some extent.
-There are 5\% of treatment group sample sizes that are smaller tha 8, the 5\% quantile.
-The first quartile is 22, the median 48, the mean 302.03 and the third quartile 119.
-The large difference between median and mean is caused by very large groups with over 2,000,000 participants.
-Analogously, the quantiles of the total sample size are: 5\% quantile = 15, first quartile = 44, median = 94 and third quartile = 229.
-The mean is 617.81.
-
-\vspace{0mm}
-The mean and median number of results per review are 12.42 and 7.
-There are 417 reviews with five or fewer results, and the quartiles are 16 and 102.
-Similarly, the number of reviews with a maximum of two studies included is 836, the mean study number is 12.42, the median 7 and the interquartile range 4 and 15.
-The discrepancy between mean and median is again due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxisfor preventing infection after cesarean section, with 95 studies and 1497 results in total.
-
-\vspace{0mm}
-For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome.
-More speicifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis since their research subject and experimental setup can be considered sufficiently homogeneous.
-%Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
-\vspace{0mm}
-The amount of studies that can be pooled for meta-analyses is of special interest in this masters thesis.
-Thus, the dataset is divided in groups whith identical experimental setup.
-The size of the group denotes how many results are included in a group.
-
-\vspace{0mm}
-Table \ref{repr.groups} shows the number of \textit{groups} of groups with equal or more than $n$ results.
-Practically, this means that a given number of meta analyses can be performed with each having at least $n$ results.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:26:47 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-n & Number of groups & Cumulative sum of groups \\ 
-  \hline
-1 & 102344 & 186300 \\ 
-  2 & 31686 & 83956 \\ 
-  3 & 16072 & 52270 \\ 
-  4 & 9628 & 36198 \\ 
-  5 & 6444 & 26570 \\ 
-  6 & 4230 & 20126 \\ 
-  7 & 2961 & 15896 \\ 
-  8 & 2114 & 12935 \\ 
-  9 & 1592 & 10821 \\ 
-  10 & 1238 & 9229 \\ 
-  11 & 921 & 7991 \\ 
-  12 & 702 & 7070 \\ 
-  13 & 585 & 6368 \\ 
-  14 & 455 & 5783 \\ 
-  15 & 5328 & 5328 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Cumulative number of groups with number of reproduction trials >= n} 
-\label{repr.groups}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 03
-
-\chapter{Results}
-
-\section{Meta-analysis}
-The data at hand is composed of over 400,000 comparisons with balanced sample size $n > 24$, which has been chosen as a threshold to assess the significance of treatment effect.
-The significance of the p-values of treatment effect estimates was calculated for all comparisons in the dataset with acceptable sample size and outcome measures as odds ratios, risk ratios, risk differences and mean and standardized mean differences.
-This led to somewhat more than 400,000 significance test results.
-Since most of the times, the study publication year is available, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}
-
-}
-
-\end{knitrout}
-\caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
-\label{study.significance.overtime}
-\end{figure}
-
-It is possible to analyse all studies with one or more replica by meta-analysis.
-There are different meta-analys methods that can be applied.
-While fixed effects meta-analysis pools the estimates and their variance, random effects meta-analysis additionally estimates the between study variances and adds this variance to the pooled within-study variances when assessing the uncertainity of the pooled effect estimate.
-The Hartung and Knapp adjustment of p-values and confidence intervals for random effects meta-analysis is more conservative than random-effects meta-analysis and will yieild less significant results than the latter.
-
-\vspace{0mm}
-In the following, the study results are combined with the results of their corresponding meta-analysis.
-Thus, every study that has one or more replicate was analysed by meta-analysis.
-In the following, the significance of the study, the primary significance, is compared with the significance of the meta-analysis or secondary significance.
-
-\vspace{0mm}
-In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
-The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure.
-One can see the overall fraction of rejected null-hypotheses of no treatment effect.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-14-1}
-
-}
-
-\end{knitrout}
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance}
-\end{figure}
-
-One can visualise the fraction of studies with significant treatment effect separately for studies with significant primary treatment effect, i.e.
-non-pooled effect, and non-significant primary treatment effect.
-This can be seen in Figure \ref{primary.secondary.significance.sep.sig}.
-One can see that primary significance and non-significance is often overruled when performing a meta-analysis.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-15-1}
-
-}
-
-\end{knitrout}
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance}
-\end{figure}
-
-The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
-Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
-The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested.
-This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-16-1}
-
-}
-
-\end{knitrout}
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance.sep.sig}
-\end{figure}
-
-\section{Small study effects}
-One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
-If this is not given, one often speaks of publication bias.
-In fact, there can also be other reasons for this (see discussion section).
-A more appropriate term for the phenomenon is small study effect.
-If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
-
-\vspace{0mm}
-To provide an overview over the issue, first it is shown how median absolute effect size decreases with increasing sample size of the comparisons in Figure \ref{effect.samplesize}.
-In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.
-
-\vspace{0mm}
-A clear trend of decrease of absolute effect size with increasing sample size (i.e.
-smaller variance) is visible.
-It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off.
-With increasing sample size, there are fewer results, therefore, the variation between medians increases.
-All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation.
-Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
-
-}
-
-\end{knitrout}
-\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
-\label{effect.samplesize}
-\end{figure}
-
-The median absolute normalized effect size can be visualized for the different outcome measures separately.
-Then it is well visible in Figure \ref{effect.samplesize.separated} that the trend of effect size decrease holds in particualar for risk and odds ratios, while it is way more stable for mean differences and standardized mean differences.
-Instead of normalizing the effects (i.e.
-subtracting mean and dividing through the standard deviation) for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
-
-}
-
-\end{knitrout}
-\caption{Median of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
-\label{effect.samplesize.separated}
-\end{figure}
-
-% A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
-This can again be done for the entire dataset, i.e.
-for all effect estimates and their ordering in time.
-It is important to scale the effect estimates here with respect to the estimates of the replication studies that are about the same subject, have the same outcome measure, etc.
-Also, only effect estimates that can be compared to other estimates before are included, i.e.
-only study results with one or more replica are included.
-Time needs to be scaled and normalized in order to compare multiple time-trends in effect size to each other and gain insights in the overall trend.
-This is done in Figure \ref{effects.overtime.separated}, separared for odds rati, risk ratio, and mean and standardized difference outcome measures.
-In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
-%                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
-%   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
-%   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
-%   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
-%   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
-%   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
-% @
-% \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
-% \label{effects.overtime.separated}
-% \end{figure}
-
-% It is also possible to look how the amount of meta-analysis with significant pooled effect size estimates changes over time, e.g.
-mean publication year (of studies included in the meta-analysis).
-0.05 is used here as the threshold for $p$-value significance and subsequent null-hypothesis rejection.
-To constrict random fluctuation in the proportion, only mean publication years with a certain amount of meta-analyses are shown ($n < 180$).
-The $p$-value of the fixed effects meta analysis model is used to decide about rejection of the null-hypothesis.
-As Figure \ref{treatment.effect.significance.overtime} shows, the proportion of meta-analyses with significant treatment effect estimates stays roughly constant over time.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
-%   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% @
-% \caption{Proportion of significant treatment effect estimates over time (mean publication year).}
-% \label{effect.samplesize}
-% \end{figure}
-%
-
-\subsection{Small Study Effect Tests}
-
-There are tests that can be applied to find out if small study effects are present in the meta analysis.
-For the precise description, see the methods section.
-Application of the tests is only recommended if there are ten or more studies \citep{cochrane.handbook} that can be used, so all meta-analyses with less than ten studies have been excluded.
-
-\vspace{0mm}
-There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
-In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = 1383)
-The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3442).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-\label{bias.results.cont}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-\label{bias.results.bin}
-\end{figure}
-
-The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
-This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-\label{bias.results.cont.sep}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-\label{bias.results.bin.sep}
-\end{figure}
-
-Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses).
-The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}.
-The Figure suggests that the frequency of publication bias remains constant over time.
-The mean publication years have been restricted such that at least 180 meta-analyses are available per year such that random fluctuation is restricted to some extent.
-The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-24-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
-\label{pub.bias.overtime}
-\end{figure}
-
-The agreement of the tests, i.e.
-the proportion of meta-analyses where the rest results are equal between tests, is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
-Agreement in tests for binary outcomes is better than continuous outcomes, with some variation between tests (binary outcomes: 83 to 91\%).
-Correlation varies more between tests, both for continuous and binary outcome tests.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:27:29 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
- & Test Agreement & P-value Correlation \\ 
-  \hline
-egger.schwarzer & 0.87 & 0.39 \\ 
-  egger.peter & 0.89 & 0.51 \\ 
-  egger.rucker & 0.88 & 0.48 \\ 
-  egger.harbord & 0.93 & 0.76 \\ 
-  schwarzer.peter & 0.89 & 0.29 \\ 
-  schwarzer.rucker & 0.88 & 0.34 \\ 
-  schwarzer.harbord & 0.92 & 0.51 \\ 
-  rucker.peter & 0.92 & 0.67 \\ 
-  harbord.peter & 0.91 & 0.52 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)} 
-\label{agreement.bin}
-\end{table}
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Apr 25 14:27:29 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
- & Test Agreement & P-value Correlation \\ 
-  \hline
-thomson.egger & 0.89 & 0.69 \\ 
-  thomson.begg & 0.82 & 0.47 \\ 
-  egger.begg & 0.79 & 0.36 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)} 
-\label{agreement.cont}
-\end{table}
-
-\vspace{0mm}
-Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
-The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}.
-%(Suggests that 10 is likely too small)
-In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
-A trend towards more rejections for larger sample sizes can be seen.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}
-
-}
-
-\end{knitrout}
-\caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
-\label{pvalues.samplesize}
-\end{figure}
-
-\vspace{0mm}
-One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
-The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.18.
-% A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
-In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses.
-In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
-In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}
-
-}
-
-\end{knitrout}
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
-\label{trimfill.pvalues.bin}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-29-1}
-
-}
-
-\end{knitrout}
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
-\label{trimfill.pvalues.cont}
-\end{figure}
-
-\subsection{Small Study Effect Correction}
-Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
-Three of them will be applied to the meta-analyses shown previously that have ten or more study results and are therefore eligible for testing for publication bias.
-
-\vspace{0mm}
-The extent to what the results of the meta-analysis results are changed can be investigated.
-Because statistical significance is often used to decide if there is a treatment effect, a non-significant corrected effect size estimate can indicate that an observed treatment effect has been accepted because of small study effects.
-Therefore, the cases have been counted in which
-\begin{enumerate}
-\item Significance or non-significance of pooled estimate of meta-analysis did not change after correction for small study effects.
-\item Significance of pooled estimate of meta-analysis did change to non-significance after correction for small study effects.
-\item Non-significance of pooled estimate of meta-analysis did change to significance after correction for small study effects.
-\end{enumerate}
-
-The results of this can be seen in Figure \ref{significance.change.fixed} for all three methods, comparing the significance of the corrected pooled effect size estimate with the significance of the pooled effect size estimate of the fixed effects meta-analysis.
-The same for significance of random effects meta-analysis is shown in Figure \ref{significance.change.random}.
-The significance threshold was chosen such that the $p$-value had to be < 0.05 for rejection of the null hypothesis of no treatment effect.
-The correction methods were trim-and-fill, copas selection model and regression with random effects and shrinkage of within-study-variance methods.
-More details to the applied correction methods and their application are in the methods section \ref{methods}.
-Notably, the correction methods has been applied to all meta-analyses, thus also for such that had no significant small study effect test result.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-30-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction.}
-\label{significance.change.fixed}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-31-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction.}
-\label{significance.change.random}
-\end{figure}
-
-Since it has been previously seen in Figure \ref{test.results} that the results of small study effects vary considerably between continuous outcomes, the results in significance change from fixed effects meta-analysis can be seen separately in Figure \ref{significance.change.fixed.sep} for continuous and binary outcomes.
-The change in significance from random effects meta-analysis to significance of corrected estimate can be seen in Figure \ref{significance.change.fixed.sep}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-32-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.fixed.sep}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-33-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.random}
-\end{figure}
-
-Similarly, the number of missing studies per meta-analysis, i.e.
-those which have not been included because of small study effects, are estimated by the copas and trim-and-fill method and their empirical distribution is shown in histograms in Figure \ref{missing.studies.distribution}.
-For visualisation, the fraction of unpublished studies from the total fraction of available studies is shown.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-34-1}
-
-}
-
-\end{knitrout}
-\caption{Fraction of missing studies estimated of the number of total studies included in the meta-analysis for copas selection and trim-and-fill method.}
-\label{missing.studies.distribution}
-\end{figure}
-
-% # <<results = 'asis', Echo = FALSE>>=
-% # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
-% #                                             schwarzer.rejection = mean(schwarzer.test),
-% #                                             rucker.rejection = mean(rucker.test),
-% #                                             harbord.rejection = mean(harbord.test),
-% #                                             peter.rejection = mean(peter.test))
-% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
-% # @
-
-% 
-% For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
-The following three figures show the distribution of p-values of the corresponding tests.
-Note that only meta analyses with more than 10 comparisons have been included.
-% 
-% \vspace{0mm}
-% Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
-The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "linreg")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
-% \label{egger.cont}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "mm")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
-% \label{thomson.cont}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "rank")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{begg.cont}
-% \end{figure}
-% 
-% 
-% For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-%   filter(events1 > 0 | events2 > 0) %>% 
-%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{peters.bin}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-%   filter(events1 > 0 | events2 > 0) %>% 
-%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{harbord.bin}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 04
-
-\chapter{Methods}
-
-\section{Basic notation}
-The notation used here will be used throughout the chapter and exceptions will be noted.
-Let $i$ be the number of a study of a meta analysis with $n$ being the total number of studies.
-$y_{i}$ is then the effect size estimate (usually log odds ratio or mean difference) and $v_{i}$ the variance of the estimate of study $i$.
-$w_{i}$ is used for weights which are defined when necessary, and $\Delta$ usually denotes the summarized or pooled effect estimate of the meta-analysis, and $\eta$ the variance thereof.
-
-\vspace{0mm}
-In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
-
-\section{Heterogeneity}
-In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
-This is called between study variation in contrast to within study variation (noise).
-
-\vspace{0mm}
-The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
-Let $w_i$ be the inverse of the variance and $\Delta$ be a summarized effect estimate of your choice as for example a variance-weighted mean \ref{weighted.mean}.
-Then $Q$ can be calculated as in \ref{Q.heterogeneity}
-
-\begin{align}
-\Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
-\end{align}
-
-Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
-Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
-$1 - F(Q)$ will provide the $p$-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
-
-\vspace{0mm}
-Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
-For this purpose, $\tau^2$, the variance of true effects, can be calculated.
-$\tau^2$ is on the same scale as the effect size and reflects the absolute amount of dispersion.
-In practice, $\tau^2$ can be smaller than zero, then it is set to zero.
-
-\begin{align}
-C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
-\tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
-\end{align}
-
-The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
-Note that their estimate can differ substantially and consequently also the estimate of the pooled effect size estimate.
-
-\vspace{0mm}
-To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
-
-\begin{align}
-I^2 &= (Q - n + 1)/Q \label{I2.proportion}
-\end{align}
-
-There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
-
-\section{Meta Analysis}
-There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
-First the fixed effect meta-analysis will be explained.
-Note that both methods can be used for continuous or dichotomous outcomes.
-For more details about the methods, see chapter 11 and 12 in \citet{metaanalysis}
-
-\vspace{0mm}
-Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
-The pooled estimate $\Delta_{f}$ of the fixed effects model is then the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
-The variance $\eta_{f}$ is the reciprocal of the sum of the weights as shown in \ref{reciproce.variance}.
-
-\begin{align}
-\Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-\eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
-\end{align}
-
-The computation of random effects meta-analysis is more complicated.
-Random effects meta-analysis will give smaller studies with larger variance more weight in the pooled estimate.
-Shortly, the idea is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
-
-\vspace{0mm}
-The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
-It is used to calculate a new weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
-The variance of $\Delta_{r}$, $\eta_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
-
-\begin{align}
-v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
-\Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
-\eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
-\end{align}
-
-A p-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
-
-\begin{align}
-Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
-p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
-\end{align}
-
-\section{Small Study Effects Tests}
-\subsection{Continuous Outcome Tests}
-% Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. 
-% First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
-
-\subsubsection{Begg and Mazumdar: Rank Correlation Test}
-\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
-A standardized effect size $y_{i}^\star$ can be computed as in \ref{begg.stand.eff}.
-$v_{i}^\star$ is the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
-$\Delta_{f}$ is the pooled estimate for fixed effect estimate defined in \ref{weighted.mean}.
-
-\begin{align}
-y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff} \\
-v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} 
-\end{align}
-
-A rank correlation test based on Kendall's tau is then used.
-The pairs $(y_{i}^\star, v_{i}^\star)$ that are ranked in the same order are enumerated.
-Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (e.g.
-larger standardized effect size and smaller variance).
-Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
-
-\begin{align}
-Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
-\end{align}
-
-The changes in the case of ties are negligible \cite[410]{begg.ties}.
-
-\subsubsection{Egger's Test: Linear Regression Test}
-Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
-Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope.
-
-\vspace{0mm}
-If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
-The p-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
-
-\begin{align}
-p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
-\end{align}
-
-\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test}
-A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
-Let $\tau^2$ be equal to \ref{Tau.definition}.
-The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
-
-\begin{align}
-y_{i} \sim N(\beta_{0} + \beta{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
-\end{align}
-
-Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
-Analogous to Edger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta{0} = 0$.
-
-\subsection{Dichotomous Outcomes Tests}
-
-The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
-Consequently, the tests above will tend to reject the null-hypothesis too often, i.e.
-that they are not conservative enough.
-A number of solutions to this problem are existing in the literature.
-
-\subsubsection{Peters Test: Weighted Linear Regression Test}
-A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
-
-\vspace{0mm}
-Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
-
-\begin{align}
-y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
-v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
-\end{align}
-
-and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
-Instead of taking the variance as explanatory or independent variable in regression as in Egger's Test, the inverse of the total sample size $x_{i}$ is used, and the variance $v_{i}$ is used as a weight.
-The subsequent test procedure is then identical to Egger's test.
-
-\vspace{0mm}
-Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
-
-\subsubsection{Harbord's Test: Score based Test}
-A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
-The score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
-
-\begin{align}
-r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
-v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
-\end{align}
-
-Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
-Note that $r_{i}/v_{i}$ is also known as peto odds ratio.
-
-\subsubsection{Schwarzer's Test: Rank Correlation Test}
-\citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
-$\mathbb{E}(E_{t})$ and variance of $E_{t}$ are then estimated based on $e_{t}$.
-
-\vspace{0mm}
-The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
-
-\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
-The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let
-
-\begin{align}
-y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}}// 
-v_{i} = 1/4n_{t} + +/4n_{c}
-\end{align}
-
-Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances.
-
-\section{Small Study Effect Adjustment}
-\subsection{Trim and Fill}
-One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
-It is a nonparametric test based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
-%If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
-
-\vspace{0mm}
-The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
-First, $\Delta$ is estimated using a fixed or random effects model.
-Then, the $k$ effect size estimates with the smallest standard errors are trimmed, and $\Delta$ is estimated again.
-The procedure is repeated until $k$ is 0 and the funnel plot is symmetric.
-The total number of missing studies is then mirrored with respect to the final effect size estimate $\Delta$, and $\Delta$ and its standard error is then computed to obtain an unbiased estimate.
-
-\subsection{Copas Selection Model}
-
-A method proposed in \cite{Copas1,Copas2,Copas3} assumes that there is a population of studies of which only a part has been published dependent on the variance and size of their estimated effects.
-Studies with small variance and large effect sizes are more likely to be published than studies with large variance and small effect sizes.
-Note that small effect size means here a treatment effect close to the control effect.
-
-Let $y_i$ be the effect size estimate of study $i$. Then
-
-\begin{align}
-y_{i} \sim N(\mu_{i}, \sigma_{i}^2) \\
-\mu_{i} \sim N(\mu, \tau^2)
-\end{align}
-
-corresponding to a standard random effects model.
-$\mu$ is the overall mean effect, $\sigma_{i}^2$ the within study variance and $\tau^2$ the between study variance.
-This is the \textit{population model}.
-
-\vspace{0mm}
-The \textit{selection model} is defined as follows. Suppose a selection of studies with reported standard errors $s$ (likely different from $\sigma$). Only a proportion
-
-\begin{align}
-P(\textrm{select}|s) &= \Phi(a + b/s) \label{copas.selection1}
-\end{align}
-
-of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
-\ref{copas.selection1} can be rewritten as
-
-\begin{align}
-z = a + b/s + \delta \label{copas.selection2}
-\end{align}
-
-with $\delta \sim N(0,1)$. The study with standard error $s$ is only selected if $z$ is positive. Therefore, the larger $z$, the more likely the study is selected.
-Combining population and selection model for study $i$, we have
-
-\begin{align}
-y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \\
-\mu_{i} \sim N(\mu, \tau^2) \\
-z_{i} = a + b/s_{i} + \delta_{i}
-\end{align}
-
-where $(\epsilon_{i}, \delta_{i})$ are standard normal residuals and jointly normal with correlation $\rho = cor(y_{i}, z_{i})$.
-Every given study $i$ in the meta-analysis has $z_{i} > 0$.
-If $\rho$ is large and positive and $z_{i} > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_{i}$ and $\delta_{i}$.
-Thus, the true mean $\mu$ is likely to be overestimated.
-
-\vspace{0mm}
-Let $u = a + b/s$, $\lambda(u) = \phi(u)/\Phi(u)$ ($\phi$ is the standard normal density function) and $\tilde{\rho} = \sigma/\sqrt(\tau^2 + \sigma^2) \rho$.
-The probability of a study being selected is
-
-\begin{align}
-P(\textrm{select}|s, y) = P(a,b,s,y) = \Phi(\frac{u + \tilde{\rho}((y - \mu)/\sqrt(\tau^2 + \sigma^2))}{\sqrt{1 - \tilde{\rho^2}}})
-\end{align}
-
-It can also be shown that the expected value
-
-\begin{align}
-\mathbb{E}(y|s, select) = \mu + \rho\sigma\lambda(u) \label{copas.expectation}
-\end{align}
-
-which shows that the expected value for a study is larger for larger $\sigma$.
-
-\vspace{0mm}
-One can compute a likelihood function based on the distribution of $y$ conditional on $z > 0$.
-The likelihood can be maximized for any given pair $a,b$ (can not be estimated since the number of missing studies is not known), and a maximum likelihood estimate $\hat{\mu}$ for the true mean $\mu$ can be obtained.
-One can then perform a sensitivity analysis.
-First, one looks how $\hat{\mu}$ changes for different values of $a,b$.
-One can then compare the fitted values in \ref{copas.expectation} with the real values.
-To test the fit of the model (while keeping all other parts unchanged), the model can be extended in the following way :
-
-\begin{align}
-y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
-\end{align}
-
-If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
-Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
-The p-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
-
-\vspace{0mm}
-To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
-
-\vspace{0mm}
-In practice, only a range of values for $a,b$ are reasonable.
-For those values, the quantities above can be calculated and illustrated.
-Values for $\mu$ that have p-values over a predefined significance threshold can be used for inference of the effect size.
-
-\subsection{Adjustment by Regression}
-There are multiple ways to adjust for small study effects by regression. The general idea is to regress the effect size of a study with a variance of zero based on the given effects and variances.
-
-\citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
-Similarly to what has been seen in Copas selection model, we let $y_{i}$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_{i}}$ as in \ref{limitmeta.regression}.
-
-\begin{align}
-y_{i}& = \beta_{0} + \beta{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \stackrel{\textrm{iid}}{\sim} N(0,1)  \ref{limitmeta.regression}
-\end{align}
-
-$\beta{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
-
-\begin{align}
-\mathbb{E}((y_{i} - \beta_{})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{if} \sqrt{v_{i}} \rightarrow \infty \\
-\mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
-\end{align}
-
-After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test.
-
-\vspace{0mm}
-To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
-
-\begin{align}
-y_{i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{s_{i}/M + \tau^2}) \label{limitmeta.regression}
-\end{align}
-
-Letting $M \rightarrow \infty$, we obtain:
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
-\end{align}
-
-Note that:
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
-\end{align}
-
-$\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
-
-\begin{align}
-\epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
-\end{align}
-
-Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-\end{align}
-
-By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
-
-% \begin{align} \label{cox reg}
-% P(Y < y|\mathbf{x}) = 1 - exp(-exp(h(y) - (\mathbf{x})^\top\beta)
-% \end{align}
-% 
-% See \cite{hothorn} for further information. It specifies the instantaneous risk of an event at time t to be
-% 
-% \begin{align}
-% \lambda_{0}(t)exp((\mathbf{x})^\top\beta) \nonumber
-% \end{align}
-% 
-% The model is regarded as a semi parametric model since it includes the covariates in a linear fashion but leaves the baseline hazard $\lambda_{0}(t)$ unspecified.
-The factor $exp((\mathbf{x})^\top\beta)$ has the interpretation of a hazard ratio between the reference with $\mathbf{x} = 0$.
-The formal definition of the hazard is
-% 
-% \begin{align}
-% h(t) = \lim_{h \to 0} \frac{P(t < T < t + h| T > t)}{h}
-% \end{align}
-% 
-% 
-% \begin{align} \label{generalized linear model}
-% \mathbf{Y}{_{ij}}|U{_i},\epsilon{_{ij}} = (1,x{_i}^\top)\beta + U{_i} + \epsilon{_{ij}}
-% \end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 05
-
-\chapter{Conclusions}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-% LaTeX file for Chapter 01
-
-\chapter{Appendix}
-
-Maybe some R code here, probably a \rr{sessionInfo()}
-
-\cleardoublepage
-\phantomsection
-\addtocontents{toc}{\protect \vspace*{10mm}}
-\addcontentsline{toc}{chapter}{\bfseries Bibliography}
-
-\bibliographystyle{mywiley} 
-\bibliography{biblio}
-
-\cleardoublepage
-
-\end{document}
+If one is to prefer, or accept meta-analysis as a way to assess treatment effect evidence, the result provides a strong argument for publication of non-significant results, because they can contribute to evidence for treatment effects in meta-analysis (in a Cochrane review).
+Significant treatment effects that are found may find their into clinical practice and potentially benefit there patients and consumers.

### 2019-05-13 code/Metaly.R

@@ -16,10 +16,73 @@ file_results = "pb.RData"
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
 
 
-data = pb.readData(path = PATH_DATA, file = FILE)
-tmp = pb.clean(data)
-data = tmp[[1]]
-aliases = tmp[[2]]
+# data = pb.readData(path = PATH_DATA, file = FILE)
+# tmp = pb.clean(data)
+# data = tmp[[1]]
+# aliases = tmp[[2]]
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+  load(file.path(PATH_RESULTS, file.dat))
+} else {
+  data = pb.readData(path = PATH_DATA, file = FILE)
+  tmp = pb.clean(data)
+  data = tmp[[1]]
+  aliases = tmp[[2]]
+  save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+  load(file.path(PATH_RESULTS, file.bin))
+} else {
+  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
+  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+  load(file.path(PATH_RESULTS, file.cont))
+} else {
+  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
+  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
+  load(file.path(PATH_RESULTS, file.meta))
+} else {
+  meta <- pb.meta.merge(meta.bin, meta.cont)
+  save(meta, file =  file.path(PATH_RESULTS, file.meta))
+}
+
+
+file.cont <- "mly.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+  load(file.path(PATH_RESULTS, file.cont))
+} else {
+  data.cont <- mly.cont(data.ext, 0.05, min.study.number = 2)
[…]

### 2019-05-13 code/PubBias.R

@@ -13,15 +13,27 @@ file_results = "pb.RData"
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
 
 
-data = pb.readData(path = PATH_DATA, file = FILE)
-tmp = pb.clean(data)
-data = tmp[[1]]
-aliases = tmp[[2]]
+# data = pb.readData(path = PATH_DATA, file = FILE)
+# tmp = pb.clean(data)
+# data = tmp[[1]]
+# aliases = tmp[[2]]
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+  load(file.path(PATH_RESULTS, file.dat))
+} else {
+  data = pb.readData(path = PATH_DATA, file = FILE)
+  tmp = pb.clean(data)
+  data = tmp[[1]]
+  aliases = tmp[[2]]
+  save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
 
 file.bin <- "pb.bin.RData"
 if (file.exists(file.path(PATH_RESULTS, file.bin))) {
   load(file.path(PATH_RESULTS, file.bin))
-} else { 
+} else {
   meta.bin <- meta.bin.complete(data, min.study.number = 10, sig.level = 0.05)
   save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
 }
@@ -29,31 +41,68 @@ if (file.exists(file.path(PATH_RESULTS, file.bin))) {
 file.cont <- "pb.cont.RData"
 if (file.exists(file.path(PATH_RESULTS, file.cont))) {
   load(file.path(PATH_RESULTS, file.cont))
-} else { 
+} else {
   meta.cont <- meta.cont.complete(data, min.study.number = 10, sig.level = 0.05)
   save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
 }
 
-meta.cont <- meta.cont %>% mutate(sig.change.ranef.reg = sig.change(sig.before = sig.ranef.cont, sig.after =  sig.reg.ranef.cont),
-                                            sig.change.ranef.copas = sig.change(sig.before = sig.ranef.cont, sig.after =  sig.copas.cont),
-                                            sig.change.ranef.trimfill = sig.change(sig.before = sig.ranef.cont, sig.after =  sig.trimfill.cont),
-                                            sig.change.fixef.reg = sig.change(sig.before = sig.fixef.cont, sig.after =  sig.reg.ranef.cont),
[…]

### 2019-05-13 code/adjustment.R

@@ -1,0 +1,423 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+
+# data = pb.readData(path = PATH_DATA, file = FILE)
+# tmp = pb.clean(data)
+# data = tmp[[1]]
+# aliases = tmp[[2]]
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+  load(file.path(PATH_RESULTS, file.dat))
+} else {
+  data = pb.readData(path = PATH_DATA, file = FILE)
+  tmp = pb.clean(data)
+  data = tmp[[1]]
+  aliases = tmp[[2]]
+  save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+load(file.path(PATH_RESULTS, file = "mly.RData"))
+load(file.path(PATH_RESULTS, file = "data.processed.RData"))
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+  load(file.path(PATH_RESULTS, file.bin))
+} else {
+  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
+  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+  load(file.path(PATH_RESULTS, file.cont))
+} else {
+  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
+  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
[…]

### 2019-05-13 code/correctures.R

@@ -1,0 +1,336 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+
+# data = pb.readData(path = PATH_DATA, file = FILE)
+# tmp = pb.clean(data)
+# data = tmp[[1]]
+# aliases = tmp[[2]]
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+  load(file.path(PATH_RESULTS, file.dat))
+} else {
+  data = pb.readData(path = PATH_DATA, file = FILE)
+  tmp = pb.clean(data)
+  data = tmp[[1]]
+  aliases = tmp[[2]]
+  save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+load(file.path(PATH_RESULTS, file = "mly.RData"))
+load(file.path(PATH_RESULTS, file = "data.processed.RData"))
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+  load(file.path(PATH_RESULTS, file.bin))
+} else {
+  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
+  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+  load(file.path(PATH_RESULTS, file.cont))
+} else {
+  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
+  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
[…]

### 2019-05-13 code/cumaly.R

@@ -1,0 +1,189 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+
+# data = pb.readData(path = PATH_DATA, file = FILE)
+# tmp = pb.clean(data)
+# data = tmp[[1]]
+# aliases = tmp[[2]]
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+  load(file.path(PATH_RESULTS, file.dat))
+} else {
+  data = pb.readData(path = PATH_DATA, file = FILE)
+  tmp = pb.clean(data)
+  data = tmp[[1]]
+  aliases = tmp[[2]]
+  save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+  load(file.path(PATH_RESULTS, file.bin))
+} else {
+  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
+  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+  load(file.path(PATH_RESULTS, file.cont))
+} else {
+  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
+  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
+  load(file.path(PATH_RESULTS, file.meta))
+} else {
+  meta <- pb.meta.merge(meta.bin, meta.cont)
[…]

### 2019-05-13 code_excess/prediction.R

@@ -1,9 +1,85 @@
 rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+
+# data = pb.readData(path = PATH_DATA, file = FILE)
+# tmp = pb.clean(data)
+# data = tmp[[1]]
+# aliases = tmp[[2]]
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+  load(file.path(PATH_RESULTS, file.dat))
+} else {
+  data = pb.readData(path = PATH_DATA, file = FILE)
+  tmp = pb.clean(data)
+  data = tmp[[1]]
+  aliases = tmp[[2]]
+  save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+  load(file.path(PATH_RESULTS, file.bin))
+} else {
+  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
+  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+  load(file.path(PATH_RESULTS, file.cont))
+} else {
+  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
+  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
+  load(file.path(PATH_RESULTS, file.meta))
+} else {
+  meta <- pb.meta.merge(meta.bin, meta.cont)
+  save(meta, file =  file.path(PATH_RESULTS, file.meta))
+}
+
+
[…]

### 2019-05-14 Presentation/present.Rnw
presentation

--- 2019-04-25 Presentation/present.Rnw
@@
 \documentclass[english]{beamer}
-
 %% The most common packages are already included in:
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\usepackage{amsmath,amsfonts,tikz}
+\usepackage{amsmath,amsfonts,tikz, amssymb}
 \usetikzlibrary{trees}
@@
 
-\title{Publication Bias in the Cochrane Library of Systematic Reviews}
+\title{Publication Bias in Meta-Analysis}%[Publication Bias]
 %% Optional Argument in [Brackets]: Short Title for Footline
@@
 %% The following are all optional, simply comment them
-%\subtitle{Subtitle (optional)}
+%\subtitle{Publication Bias in the Cochrane Libary}
 %\institute{Biostatistics Journal Club}  %% optional
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\begin{document}
-\maketitle
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-%% Start with slides here: put them between `\begin{frame}` and `\end{frame}`
-
-<<echo=FALSE, warning = FALSE, message=FALSE>>= 
+<<include = FALSE>>= 
+library(knitr)
 PATH_HOME = path.expand("~") # user home
@@
 
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+  load(file.path(PATH_RESULTS, file.dat))
+} else {
   data = pb.readData(path = PATH_DATA, file = FILE)
@@
 	aliases = tmp[[2]]
-
-file.bin <- "pb.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-  load(file.path(PATH_RESULTS, file.bin))
-} else {
-  meta.bin <- meta.bin.complete(data, min.study.number = 10, sig.level = 0.05)
-  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+  save(data, file =  file.path(PATH_RESULTS, file.dat))
 }
 
-file.cont <- "pb.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-  load(file.path(PATH_RESULTS, file.cont))
-} else {
-  meta.cont <- meta.cont.complete(data, min.study.number = 10, sig.level = 0.05)
-  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-meta <- pb.meta.merge(meta.bin, meta.cont)
-
-file.cont <- "mly.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-  load(file.path(PATH_RESULTS, file.cont))
-} else {
-  data.cont <- mly.cont(data.ext, 0.05, min.study.number = 2)
-  save(data.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.bin <- "mly.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-  load(file.path(PATH_RESULTS, file.bin))
-} else {
-  data.bin <- mly.bin(data.ext, 0.05, min.study.number = 2)
-  save(data.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-load(file.path(PATH_RESULTS, file = "mly.RData"))
 load(file.path(PATH_RESULTS, file = "data.processed.RData"))
 
-require(biostatUZH)
 require(tidyverse)
 require(meta)
-require(metasens)
-require(gridExtra)
 require(xtable)
 
-###################################################################################################################
-###################################################################################################################
+#Meta-analysis example
+data.ext <- data.ext %>% mutate(study.year = ifelse(study.year < 2019, study.year, NA)) %>% 
+    mutate(study.year = ifelse(study.year > 1920, study.year, NA))
+biased.rev <- data.ext %>% filter(meta.id == 122943)
+unbiased.rev <- data.ext %>% filter(meta.id == 181863)
+meta.example <- metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, 
+												 studlab = study.name, data = biased.rev)
+meta.nexample <- metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, 
+												 studlab = study.name, data = unbiased.rev)
 
@@
 
-#Mean and median number of different outcome types of reviews
-mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
-  ungroup() %>% group_by(file.nr) %>%
-  count() %>% ungroup %>% summarise(mean = mean(n))
+#Dataset properties:
+#Review level
+study.rev <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count() %>% ungroup() %>% 
+	summarise(lower = quantile(n, 0.05), median = quantile(n, 0.5), mean = mean(n), upper = quantile(n, 0.95))
+comparison.rev <- data %>% group_by(file.nr) %>% distinct(comparison.name) %>% count() %>% ungroup() %>% 
+	summarise(lower = quantile(n, 0.05), median = quantile(n, 0.5), mean = mean(n), upper = quantile(n, 0.95))
+meta.rev <- data.ext %>% group_by(file.nr) %>% distinct(meta.id) %>% count() %>% ungroup() %>% 
+	summarise(lower = quantile(n, 0.05), median = quantile(n, 0.5), mean = mean(n), upper = quantile(n, 0.95))
 
-median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
-  ungroup() %>% group_by(file.nr) %>%
-  count() %>% ungroup %>% summarise(mean = median(n))
+#Global level
+study.years <- data.ext %>% group_by(file.nr) %>% distinct(study.name, .keep_all = T) %>% ungroup() %>% 
+	summarise(lower = quantile(study.year, 0.05, na.rm = T), median = quantile(study.year, 0.5, na.rm = T),
+						mean = mean(study.year, na.rm = T), upper = quantile(study.year, 0.95, na.rm = T))
+sample.size <- data.ext %>% group_by(file.nr) %>% distinct(study.name, .keep_all = T) %>% ungroup() %>% 
+	mutate(samplesize = total1 + total2) %>% 
+	summarise(lower = quantile(samplesize, 0.05, na.rm = T), median = quantile(samplesize, 0.5, na.rm = T),
+						mean = mean(samplesize, na.rm = T), upper = quantile(samplesize, 0.95, na.rm = T))
 
-#Study.year quantiles:
-data.ext <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
-publication.year.range <- c(quantile(data.ext$study.year, 0.05, na.rm = T), quantile(data.ext$study.year, 0.25, na.rm = T), 
-                            quantile(data.ext$study.year, 0.5, na.rm = T), quantile(data.ext$study.year, 0.75, na.rm = T),
-                            round(mean(data.ext$study.year, na.rm = T), 2))
-
-#Outcome.measure frequency table:
-outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.new) %>% count() %>% 
-                                       arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9),
-                                     data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% 
-                                       ungroup() %>% filter(row_number() > 8) %>% 
-                                       summarise(outcome.measure.new = "other", n = sum(n)))
-
-outcome.measure.frequencies <- outcome.measure.frequencies %>% mutate(percentage = round(n/sum(n),3)*100)
-names(outcome.measure.frequencies) <- c("Outcome measure", "n", "Percentage")
-outcome.measure.frequencies$Percentage <- paste(outcome.measure.frequencies$Percentage, "%", sep = "")
-
-#Total and group size quantiles:
-data.ext <- data.ext %>% ungroup() %>%  mutate(total.n = total1 + total2)
-samplesize.range <- c(quantile(data.ext$total.n, 0.05, na.rm = T), quantile(data.ext$total.n, 0.25, na.rm = T), 
-                            quantile(data.ext$total.n, 0.5, na.rm = T), quantile(data.ext$total.n, 0.75, na.rm = T),
-                            round(mean(data.ext$total.n, na.rm = T), 2))
-treatment.group.size.range <- c(quantile(data.ext$total1, 0.05, na.rm = T), quantile(data.ext$total1, 0.25, na.rm = T), 
-                      quantile(data.ext$total1, 0.5, na.rm = T), quantile(data.ext$total1, 0.75, na.rm = T),
-                      round(mean(data.ext$total1, na.rm = T), 2))
-
-#Frequencies of results:
-comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
-comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
-                      quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
-                      round(mean(comp.freq$n, na.rm = T), 2))
-
-#Frequencies of studies:
-study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
-study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
-                      quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
-                      round(mean(study.freq$n, na.rm = T), 2))
+dataset.properties <- rbind(study.rev, comparison.rev, meta.rev, study.years, sample.size)
+rownames(dataset.properties) <- c("Study number", "Comparison number", "Group number", "Study years", "Study sample size")
+colnames(dataset.properties) <- c("5% quantile", "median", "mean", "95% quantile")
 
@@
 cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
-  filter(n < 15) %>%
+  filter(n < 10) %>%
   full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
-               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
+               filter(n > 9) %>% ungroup %>% summarise(n = 10, nn = sum(nn))) %>%
   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
-# cum.repr.trials.nosub <- data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
-#   filter(n < 15) %>%
-#   full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
-#                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
-#   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
-
-# cum.repr.trials <- cbind(cum.repr.trials.nosub, cum.repr.trials.subg)[,c(1,3,6)]
 
 colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
+
+#Loading meta-analysis results:
+file.bin <- "pb.bin.RData"
+load(file.path(PATH_RESULTS, file.bin))
+
+file.cont <- "pb.cont.RData"
+load(file.path(PATH_RESULTS, file.cont))
+
+file.meta <- "meta.RData"
+load(file.path(PATH_RESULTS, file.meta))
+
+library(gridExtra)
+
+#Meta filtering: 
+metac.bin <- meta.bin %>% filter(n.sig.type.bin > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+metac.cont <- meta.cont %>% filter(n.sig.type.cont > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+metac <- meta %>% filter(n.sig.type > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+
+#Significant proportion
+test.bin <- metac.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                          schwarzer.test = mean(schwarzer.test),
+                                                          rucker.test = mean(rucker.test),
+                                                          harbord.test = mean(harbord.test),
+                                                          peter.test = mean(peter.test))
+test.bin <- test.bin %>% gather(key = "test.type", value = "mean")
+
+p.bin <- metac.bin %>% ungroup() %>% 
+  select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
+  gather(key = "test.type", value = "null.hypothesis") %>%  
+  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
+  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+  theme_bw() + xlab(label = NULL) + ggtitle("Binary Outcomes") + theme(legend.position = "top") +
+  guides(fill=guide_legend(title=NULL))+
+  annotate("text", x = test.bin$test.type, y = 500, 
+           label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
+           color = "white")
+
+test.cont <- metac.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                            begg.test = mean(begg.test),
+                                                            thomson.test = mean(thomson.test))
+
+test.cont <- test.cont %>% gather(key = "test.type", value = "mean")
+
+p.cont <- metac.cont %>% ungroup() %>% 
+  select(egger.test, thomson.test, begg.test) %>% 
+  gather(key = "test.type", value = "null.hypothesis") %>% 
+  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
+  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+  theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
+	guides(fill=guide_legend(title=NULL))+
+  annotate("text", x = test.cont$test.type, y = 150, 
+           label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
+           color = "white")
+
+dat_text <- data.frame(
+  label = paste(c(sum(metac.cont$begg.test), sum(metac.cont$egger.test), sum(metac.cont$thomson.test)), "> 0.05"),
+  test.type   = c("pval.begg.cont", "pval.egger.cont", "pval.thomson.cont"))
+
+p.dist.cont <- metac.cont %>% ungroup() %>% 
+  select(pval.egger.cont, pval.thomson.cont, pval.begg.cont) %>% 
+  gather(key = "test.type", value = "p.value") %>% 
+  ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + facet_wrap(~test.type) + 
+	geom_text(data = dat_text, mapping = aes(x = -Inf, y = -Inf, label = label), hjust   = -1,
+  vjust   = -4, color = "white")
+
+dat_text <- data.frame(
+  label = paste(c(sum(metac.bin$egger.test), sum(metac.bin$harbord.test), sum(metac.bin$peter.test), 
+  										sum(metac.bin$rucker.test), sum(metac.bin$schwarzer.test)), "> 0.05"),
+  test.type   = c("pval.egger.bin", "pval.harbord.bin", "pval.peter.bin", "pval.rucker.bin", "pval.schwarzer.bin"))
+
+p.dist.bin <- metac.bin %>% ungroup() %>% 
+  select(pval.egger.bin, pval.harbord.bin, pval.peter.bin, pval.rucker.bin, pval.schwarzer.bin) %>% 
+  gather(key = "test.type", value = "p.value") %>% 
+  ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + facet_wrap(~test.type) + 
+	geom_text(data = dat_text, mapping = aes(x = -Inf, y = -Inf, label = label), hjust   = -0.65,
+  vjust   = -4, color = "white")
+
+#Test agreement
+agree.bin <- meta.bin %>% mutate(n.sig = peter.test + rucker.test + egger.test + harbord.test + schwarzer.test) %>% 
+  group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
+  ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + xlab("Number of significant tests") + ylab("count") + ggtitle("Binary Outcomes")
+
+agree.cont <- meta.cont %>% mutate(n.sig = egger.test + thomson.test + begg.test) %>% 
+  group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
+  ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")
+
+#Adjustment example plots regression:
+reg.1 <- qplot(x = biased.rev$se, y = biased.rev$effect, xlim = c(0, 1.2)) + geom_point() + 
+	stat_smooth(method="lm", fullrange=TRUE, se = F) + coord_flip() + theme_bw() +
+	ylab("Std. Mean Difference") + xlab("Standard error")
+
+reg.2 <- qplot(x = unbiased.rev$se, y = unbiased.rev$effect, xlim = c(0, 6.5)) + geom_point() + 
+	stat_smooth(method="lm", fullrange=TRUE, se = F) + coord_flip() + theme_bw() +
+	ylab("Std. Mean Difference") + xlab("Standard error")
+
 @
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\begin{document}
+\maketitle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
     child [missing] {}
-    child { node {Comparison 1  }};
+    child { node {Comparison 1}};
 \end{tikzpicture}
@@
 \end{figure}
+\end{frame}
+
+\begin{frame}{Dataset Structure}
+\begin{itemize}
+\item Comparison: What is compared, e.g. treatment vs. control
+\item Outcome: How it is compared
+\item Subgroup: Subgroup affiliation
+\item Meta-Analysis Group: Results from same comparison, outcome and subgroup
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]{Review Example: binary outcome}
+Barbiturate efficacy for head injury treatment
+\vspace{-5mm}
+<<echo = FALSE, results = 'asis'>>=
+print(xtable(barbi2, label = "barbiturates", digits = 0), include.rownames = F, size = "tiny")
+@
+\end{frame}
+
+\begin{frame}[fragile]{Dataset Properties}
+Missing data:
+<<echo=FALSE, results = 'asis'>>=
+print(xtable(missing.table, align = "lr"), include.rownames = T, include.colnames = F)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Dataset Properties}
+Review and study properties:
+<<echo=FALSE, results = 'asis'>>=
+print(xtable(dataset.properties, digits = 0, align = "lrrrr"), include.rownames = T, size = "footnotesize", hline = c(0,1,1,4))
+@
+\end{frame}
+
+\begin{frame}[fragile]{Pooling Studies - Meta-Analysis}
+Multiple results in a meta-analysis group can be pooled:
+<<echo=FALSE, results = 'asis'>>=
+print(xtable(cum.repr.trials.subg, label = "repr.groups", align = "lrrr", digits = 0), include.rownames = F, size = "footnotesize")
+@
+\end{frame}
+
+\begin{frame}{Meta-analysis}
+Benefits:
+\begin{itemize}
+\item Summary of evidence (e.g. of a treatment)
+\item More reliable evidence (?)
+\end{itemize}
+
+Assumptions:
+\begin{itemize}
+\item Identical study settings (can be relaxed)
+\item Random sample of studies
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Small Study Effects}
+``The tendency for the smaller studies to show larger treatment effects'' \citep{Sterne}
+\end{frame}
+
+\begin{frame}{Small Study Effects}
+Causes:
+\begin{itemize}
+\item Selective publication of studies with large effects
+\item Bias in smaller studies
+\item Systematical differences in study settings
+\item \ldots
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Small Study Effect Tests}
+Tests applicable if:
+\begin{itemize}
+\item $n$ large
+\item variation in the estimated variances of effects \\(here: $\frac{\sigma_{\textrm{max}}}{\sigma_{\textrm{min}}} > 4$)
+\end{itemize}
+Adjustments required if variance is dependent on effect size (e.g. log odds ratios)
+\end{frame}
+
+\begin{frame}[fragile]{Small Study Effect Tests}
+Funnel plots (continuous outcome examples):
+
+\vspace{-1.2cm}
+
+<<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
+par(las = 1, mfrow = c(1, 2))
+funnel(meta.example)
+funnel(meta.nexample)
+@
 
@@
 
-\begin{frame}{Review Example}
-\vspace{-5mm}
-<<echo = FALSE, results = 'asis'>>=
-print(xtable(barbi2, label = "barbiturates"), include.rownames = F, size = "tiny")
+\begin{frame}[fragile]{Regression based Tests}
+Radial plots (continuous outcome examples):
+
+\vspace{-1.2cm}
+
+<<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
+par(las = 1, mfrow = c(1,2))
+radial(meta.example, comb.fixed = F)
+radial(meta.nexample, comb.fixed = F)
 @
 
-\vspace{-6mm}
-<<echo = FALSE, results = 'asis'>>=
-print(xtable(barbi1, label = "barbiturate.row", digits = 0), 
-      include.rownames = F, size = "tiny")
+\end{frame}
+
+\begin{frame}{Regression based Tests}
+Continuous outcomes tests:
+
+$i$ being the $i$th study in a meta-analysis:
+
+Let $y_{i} = \textrm{effect}_{i}/\textrm{se}_{i}$ and $x_{i} = 1/\textrm{se}_{i}$
+\begin{itemize}
+\item \citet{Egger} : \\ $y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i})$
+\item \citet{thompson.sharp} : \\ $y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i} + \tau^2)$
+\end{itemize}
+%Test for non-zero intercept $\beta_{0}$
+\end{frame}
+
+\begin{frame}[fragile]{Egger's Tests}
+
+\vspace{-6cm}
+
+<<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
+par(las = 1, mfrow = c(1,2))
+metabias(meta.example, plotit = TRUE, method.bias = "linreg")
+metabias(meta.nexample, plotit = TRUE, method.bias = "linreg")
+@
+
+\end{frame}
+
+\begin{frame}[fragile]{Thompson and Sharp's Tests}
+
+\vspace{-6.5cm}
+
+<<message = FALSE, echo=FALSE, warning = FALSE, fig.height= 4>>=
+par(las = 1, mfrow = c(1,2))
+metabias(meta.example, plotit = TRUE, method.bias = "mm")
+metabias(meta.nexample, plotit = TRUE, method.bias = "mm")
+@
+
+\end{frame}
+
+\begin{frame}{Regression based Tests}
+Adjustments for binary outcomes:
+\begin{itemize}
+\item \citet{Peters} :$x_{i}$ = inverse of total sample size, $\textrm{variance}_{i}$ as weight.
+\item \citet{Harbord} :$x:{i}$ = score of the log-likelihood of a proportion, $\textrm{variance}_{i}$ as weight.
+\item \citet{Rucker} :Use arcsine variance stabilizing transformation for variances and effects, do e.g. Egger's test.
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Rank based tests}
+\citet{begg.ties}
+Let $y_{i}$ the standardized effect size of a study $i$, $v_{i}$ it's variance and $n$ the number of studies
+
+$u$ the number of pairs $(y_{i}, v_{i})$ ranked in the same order, $l$
+the number of pairs in the opposite order
+
+$Z = (u - l)/\sqrt{n(n-1)(2n + 5)/18}$ \\ can be used as a test statistic (based on Kendall's Tau)
+\end{frame}
+
+\begin{frame}{Rank based tests}
+\citet{Schwarzer}
+Let $e_{t}$ the number of events in the treatment group
+
+Given constant log odds ratio, $E_{t}$ follows a hypergeometric distribution.
+
+$\mathbb{E}(E_{t})$ and the variance can be estimated and used as in 
+\citet{begg.ties}
+\end{frame}
+
+\begin{frame}{Test Results}
+Application of tests if:
+\begin{itemize}
+\item $n \geq 10$
+\item at least one statistically significant effect in a study
+\item $\frac{\sigma_{\textrm{max}}}{\sigma_{\textrm{min}}} > 4$
+\item $I^2 < 0.5$
+\end{itemize}
+
+From \Sexpr{dim(meta)[1]} with $n \geq 10$, \Sexpr{dim(metac)[1]} remain.
+\end{frame}
+
+% \begin{frame}[fragile]{Test Results: Significance}
+% 
+% <<echo = FALSE, fig.height = 4>>=
+% grid.arrange(p.bin, p.cont, ncol = 2)
+% @
+% \end{frame}
+
+\begin{frame}[fragile]{Continuous Outcome Test Results}
+$p$-values distribution:
+
+<<echo = FALSE, fig.height = 4, message = FALSE>>=
+plot(p.dist.cont)
 @
@@
 
-\begin{frame}{Pooling studies}
-Studies of the same outcome, comparison and subgroup can be pooled by meta analyis.
+\begin{frame}[fragile]{Binary Outcome Test Results}
+$p$-values distribution:
 
-Evidence synthesis - more reliable results.
-
-Different methods - f.ex. random or fixed effects meta-analysis.
+<<echo = FALSE, fig.height = 4, message = FALSE>>=
+plot(p.dist.bin)
+@
 \end{frame}
 
-\begin{frame}{Publication bias}
-Selection of studies with treatment effects.
+\begin{frame}[fragile]{Agreement in significance}
+Number of significant test results per meta-analysis:
 
-Stronger selection for smaller studies - small study effect.
+<<echo = FALSE, fig.height = 3.8, message = FALSE>>=
+grid.arrange(agree.cont, agree.bin, ncol = 2)
+@
+\end{frame}
 
-Distort findings of meta-analyses.
+\begin{frame}{Small Study Effect Adjustment}
+Three methods:
+\begin{itemize}
+\item Regression
+\item Copas selection model
+\item Trim-and-fill
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Adjustment by regression}
+Similar to the tests, but with unnormalized effect $y_{i}$:
+
+\begin{align}
+y_{i} = \beta_{0} + \beta_{1}x_{i}
+\end{align}
+
+$\beta_{0}$	 corresponds to $y_{i}$ with $x_{i} = 0$
+\end{frame}
+
+\begin{frame}[fragile]{Adjustment by regression}
+Linear regression method:
+
+<<echo = FALSE, fig.height = 3>>=
+grid.arrange(reg.1, reg.2, ncol = 2)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Shrinkage Regression}
+Extended random effects model:
+
+\vspace{-4mm}
+\begin{align}
+y_{i} = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}),  
+\epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \nonumber
+\end{align}
+
+\vspace{-8mm}
+\begin{align}
+\mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{ if } \sqrt{v_{i}} \rightarrow 0 \nonumber
+\end{align}
+
+$\beta_{0}, \beta_{1}$ and $\tau$ can be estimated e.g. by ML and REML.
+\end{frame}
+
+\begin{frame}[fragile]{Shrinkage Regression}
+shrinking the within study variance:
+
+\vspace{-4mm}
+\begin{align}
+y_{i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{s_{i}/M + \tau^2}) \nonumber
+\end{align}
+
+Letting $M \rightarrow \infty$ and substituting for all parameters and the observed residual
+
+\vspace{-8mm}
+\begin{align}
+y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
+\end{align}
+
+\end{frame}
+
+\begin{frame}[fragile]{Shrinkage Regression}
+Three different treatment effect estimates:
+
+\begin{align}
+y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
+\end{align}
+
 \end{frame}

### 2019-05-14 report/chapter04.Rnw
presentation

@@
 
-\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test}
+\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{Thompson}
 A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
@@
 \begin{align}
-y_{i} \sim N(\beta_{0} + \beta{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
+y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
 \end{align}
@@
 Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
-Analogous to Edger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta{0} = 0$.
+Analogous to Egger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta_{0} = 0$.
 
@@
 \begin{align}
-y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}}// 
+y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}} \\
 v_{i} = 1/4n_{t} + +/4n_{c}
@@
 \subsection{Adjustment by Regression}
-There are multiple ways to adjust for small study effects by regression. The general idea is to regress the effect size of a study with a variance of zero based on the given effects and variances.
+There are multiple ways to adjust for small study effects by regression. The general idea is to extrapolate the effect size of a study with a variance of zero based on the given effects and variances.
 
@@
 \begin{align}
-y_{i}& = \beta_{0} + \beta{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \stackrel{\textrm{iid}}{\sim} N(0,1)  \ref{limitmeta.regression}
+y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
 \end{align}
 
-$\beta{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
+$\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
 
 \begin{align}
-\mathbb{E}((y_{i} - \beta_{})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{if} \sqrt{v_{i}} \rightarrow \infty \\
+\mathbb{E}((y_{i} - \beta_{0})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{ if } \sqrt{v_{i}} \rightarrow \infty \label{limitmeta.infinitesample} \\
 \mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
@@
 
-After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test.
+After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test (see \ref{Thompson}).
 

### 2019-05-14 code/adjustment.R

@@ -98,7 +98,7 @@ meta.cont %>% mutate(n.sig = egger.test + thomson.test + begg.test) %>%
 
 
 #Meta filtering: 
-metac.bin <- meta.bin %>% filter(n.sig.type.cont > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+metac.bin <- meta.bin %>% filter(n.sig.type.bin > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
 metac.cont <- meta.cont %>% filter(n.sig.type.cont > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
 metac <- meta %>% filter(n.sig.type > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
 

### 2019-05-14 code/correctures.R

@@ -82,9 +82,10 @@ require(gridExtra)
 
 
 #Meta filtering: 
-metac.bin <- meta.bin %>% filter(n.sig.type > 1) %>% filter((min.se^2)/(max.se^2) > 4) %>% filter(I2 < 0.5)
-metac.cont <- meta.cont %>% filter(n.sig.type > 1) %>% filter((min.se^2)/(max.se^2) > 4) %>% filter(I2 < 0.5)
-metac <- meta %>% filter(n.sig.type > 1) %>% filter((min.se^2)/(max.se^2) > 4)
+#Meta filtering: 
+metac.bin <- meta.bin %>% filter(n.sig.type.bin > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+metac.cont <- meta.cont %>% filter(n.sig.type.cont > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+metac <- meta %>% filter(n.sig.type > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
 
 #Publication Bias Test Agreement:
 meta.bin %>% mutate(n.sig = peter.test + rucker.test + egger.test + harbord.test + schwarzer.test) %>% 

### 2019-05-20 Presentation/present.Rnw
Präsentation

@@
 dataset.properties <- rbind(study.rev, comparison.rev, meta.rev, study.years, sample.size)
-rownames(dataset.properties) <- c("Study number", "Comparison number", "Group number", "Study years", "Study sample size")
+rownames(dataset.properties) <- c("Number of studies", "Number of comparisons", "Number of meta-analyses", "Study years", "Study sample size")
 colnames(dataset.properties) <- c("5% quantile", "median", "mean", "95% quantile")
@@
 library(gridExtra)
+
+meta.id <- function(meta.id.tolook){
+	dt <- data.ext %>% filter(meta.id == meta.id.tolook)
+	if(any(is.na(dt$events1)) | all(dt$events1 == 0)){
+		meta.ex <- metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, studlab = study.name, data = dt)
+	} else{
+		meta.ex <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, sm = "RR", data = dt)
+	}
+	return(meta.ex)
+}
 
@@
 dat_text <- data.frame(
-  label = paste(c(sum(metac.cont$begg.test), sum(metac.cont$egger.test), sum(metac.cont$thomson.test)), "> 0.05"),
+  label = paste(c(sum(metac.cont$begg.test), sum(metac.cont$egger.test), sum(metac.cont$thomson.test)), "< 0.05"),
   test.type   = c("pval.begg.cont", "pval.egger.cont", "pval.thomson.cont"))
@@
   label = paste(c(sum(metac.bin$egger.test), sum(metac.bin$harbord.test), sum(metac.bin$peter.test), 
-  										sum(metac.bin$rucker.test), sum(metac.bin$schwarzer.test)), "> 0.05"),
+  										sum(metac.bin$rucker.test), sum(metac.bin$schwarzer.test)), "< 0.05"),
   test.type   = c("pval.egger.bin", "pval.harbord.bin", "pval.peter.bin", "pval.rucker.bin", "pval.schwarzer.bin"))
@@
 	geom_text(data = dat_text, mapping = aes(x = -Inf, y = -Inf, label = label), hjust   = -0.65,
-  vjust   = -4, color = "white")
+  vjust   = -2, color = "white")
 
 #Test agreement
-agree.bin <- meta.bin %>% mutate(n.sig = peter.test + rucker.test + egger.test + harbord.test + schwarzer.test) %>% 
+agree.bin <- metac.bin %>% mutate(n.sig = peter.test + rucker.test + egger.test + harbord.test + schwarzer.test) %>% 
   group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
@@
 
-agree.cont <- meta.cont %>% mutate(n.sig = egger.test + thomson.test + begg.test) %>% 
+agree.cont <- metac.cont %>% mutate(n.sig = egger.test + thomson.test + begg.test) %>% 
   group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
@@
 
+#Adjustment results: Effect difference histograms
+effect.diff <- metac %>% mutate(
+	est.fixef = ifelse(!is.na(est.fixef.bin), est.fixef - 1, est.fixef),
+	est.ranef = ifelse(!is.na(est.fixef.bin), est.ranef - 1, est.ranef),
+	est.trimfill.fixef = ifelse(!is.na(est.fixef.bin), est.trimfill.fixef - 1, est.trimfill.fixef),
+	est.copas = ifelse(!is.na(est.fixef.bin), est.copas - 1, est.copas),
+	est.reg.ranef = ifelse(!is.na(est.fixef.bin), est.reg.ranef - 1, est.reg.ranef),
+	fixef.trimfill = ifelse(abs(est.fixef) > abs(est.trimfill.fixef), "Reduction", "Amplification"),
+	fixef.copas = ifelse(abs(est.fixef) > abs(est.copas), "Reduction", "Amplification"),
+	fixef.reg = ifelse(abs(est.fixef) > abs(est.reg.ranef), "Reduction", "Amplification"),
+	fixef.trimfill.s = ifelse(sign(est.fixef) == sign(est.trimfill.fixef), "Unchanged", "Reversed"),
+	fixef.copas.s = ifelse(sign(est.fixef) == sign(est.copas), "Unchanged", "Reversed"),
+	fixef.reg.s = ifelse(sign(est.fixef) == sign(est.reg.ranef), "Unchanged", "Reversed"))
+
+trimfill.miss <- effect.diff %>% group_by(fixef.trimfill) %>% mutate(dif = abs(est.fixef - est.trimfill.fixef)) %>% 
+	filter(dif > 2) %>% mutate(label = round(dif, 1), type = !is.na(est.fixef.bin)) %>% arrange(label) %>% select(label, fixef.trimfill.s, meta.id, type)
+
+trimfill.label <- data.frame(label = paste("missing:", c(paste(trimfill.miss$label[trimfill.miss$fixef.trimfill == "Reduction"], collapse = ", "),
+																												 paste(trimfill.miss$label[trimfill.miss$fixef.trimfill == "Amplification"], collapse = ", "))),
+														fixef.trimfill = unique(trimfill.miss$fixef.trimfill), 
+														fixef.trimfill.s  = "Reversed")
+
+trimfill.label$label <- as.character(trimfill.label$label)
+trimfill.label$label[1] <- sub("2.5,", "2.5, \n   ", trimfill.label$label[1])
+
+hist.trimfill <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.trimfill.fixef), fill = factor(fixef.trimfill.s))) +
+	geom_histogram() + facet_grid(~factor(fixef.trimfill)) + xlim(0, 2)+ xlab("Effect difference") +
+	geom_text(data = trimfill.label, mapping = aes(label = label, x = 0, hjust = 0, y = 300), 
+						color = "black") + scale_fill_discrete(name="Effect direction") + theme_bw() + 
+	theme(legend.position = "bottom", strip.text.x = element_text(size=15))
+
+hist.trimfill1 <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.trimfill.fixef))) +
+	geom_histogram() + facet_grid(~factor(fixef.trimfill)) + xlim(0, 2)+ xlab("Effect difference") +
+	geom_text(data = trimfill.label, mapping = aes(label = label, x = 0, hjust = 0.05, y = 300), 
+						color = "black") + theme_bw() + 
+	theme(legend.position = "bottom", strip.text.x = element_text(size=15))
+
+funnel(trimfill(meta.id(165815)))
+
+copas.miss <- effect.diff %>% filter(!is.na(est.copas)) %>% group_by(fixef.copas) %>% mutate(dif = abs(est.fixef - est.copas)) %>% 
+	filter(dif > 2) %>% mutate(label = round(dif, 1), type = !is.na(est.fixef.bin)) %>% arrange(label) %>% select(label, fixef.copas.s, meta.id, type)
+
+copas.label <- data.frame(label = paste("missing:", c(paste(copas.miss$label[copas.miss$fixef.copas == "Reduction"], collapse = ", "),
+																												 paste(copas.miss$label[copas.miss$fixef.copas == "Amplification"], collapse = ", "))),
+														 fixef.copas = unique(copas.miss$fixef.copas), 
+														 fixef.copas.s  = "Reversed")
+
+copas.label$label <- as.character(copas.label$label)
+copas.label$label[1] <- sub("3.5,", "3.5, \n   ", copas.label$label[1])
+
+hist.copas <- effect.diff %>% filter(!is.na(est.copas)) %>% ggplot(aes(x = abs(est.fixef - est.copas), fill = factor(fixef.copas.s))) +
+	geom_histogram() + facet_grid(~factor(fixef.copas)) + xlim(0, 2) + xlab("Effect difference") +
+	geom_text(data = copas.label, mapping = aes(label = label, x = 0, hjust = 0, y = 175), 
+						color = "black") + scale_fill_discrete(name="Effect direction") + theme_bw() +
+	theme(legend.position = "bottom", strip.text.x = element_text(size=15))
+
+hist.copas1 <- effect.diff %>% filter(!is.na(est.copas)) %>% ggplot(aes(x = abs(est.fixef - est.copas))) +
+	geom_histogram() + facet_grid(~factor(fixef.copas)) + xlim(0, 2) + xlab("Effect difference") +
+	geom_text(data = copas.label, mapping = aes(label = label, x = 0, hjust = 0.05, y = 175), 
+						color = "black") + theme_bw() +
+	theme(legend.position = "bottom", strip.text.x = element_text(size=15))
+
+funnel(meta.id(56200))
+
+reg.ranef.miss <- effect.diff %>% group_by(fixef.reg) %>% mutate(dif = abs(est.fixef - est.reg.ranef)) %>% 
+	filter(dif > 3) %>% mutate(label = round(dif, 1), type = !is.na(est.fixef.bin)) %>% arrange(label) %>% select(label, fixef.reg.s, meta.id, type)
+
+reg.ranef.label <- data.frame(label = paste("missing:", c(paste(reg.ranef.miss$label[reg.ranef.miss$fixef.reg == "Reduction"], collapse = ", "),
+																											paste(reg.ranef.miss$label[reg.ranef.miss$fixef.reg == "Amplification"], collapse = ", "))),
+													fixef.reg = unique(reg.ranef.miss$fixef.reg), 
+													fixef.reg.s  = "Reversed")
+
+reg.ranef.label$label <- as.character(reg.ranef.label$label)
+reg.ranef.label$label[1] <- sub("4.8,", "4.8,\n   ", reg.ranef.label$label[1])
+
+hist.reg <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.reg.ranef), fill = factor(fixef.reg.s))) +
+	geom_histogram() + facet_grid(~factor(fixef.reg)) + xlim(0, 3)+ xlab("Effect difference") +
+	geom_text(data = reg.ranef.label, mapping = aes(label = label, x= 0, y = 250, hjust = 0.05), 
+						color = "black", size = 2.8) + theme_bw() + scale_fill_discrete(name="Effect direction") +
+	theme(legend.position = "bottom", strip.text.x = element_text(size=15))
+
+hist.reg1 <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.reg.ranef))) +
+	geom_histogram() + facet_grid(~factor(fixef.reg)) + xlim(0, 3)+ xlab("Effect difference") +
+	geom_text(data = reg.ranef.label, mapping = aes(label = label, x= 0, y = 250, hjust = 0.05), 
+						color = "black", size = 2.8) + theme_bw() + 
+	theme(legend.position = "bottom", strip.text.x = element_text(size=15))
+
+metac %>% filter(meta.id == 101436) %>% select(comparison.name, outcome.name, sungroup.name, est.fixef, est.copas, 
+																							 est.trimfill.fixef, est.reg.ranef, est.copas)
+par(mfrow = c(1,3))
+funnel(meta.id(101436))
+funnel(trimfill(meta.id(101436)))
+funnel(limitmeta(meta.id(101436)))
+
+print(effect.diff %>% group_by(fixef.reg) %>% mutate(dif = abs(est.fixef - est.reg.ranef)) %>% 
+				filter(dif > 3) %>% mutate(label = round(dif, 1), type = !is.na(est.fixef.bin)) %>% 
+				arrange(label) %>% select(label, type, meta.id, comparison.name, outcome.name), n = 200)
+
+#Scatterplots of metac-analysis and corrected log(abs(abs estimates
+trimfill.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.trimfill.fixef)))) + geom_point() + 
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
+	xlab("Fixed effects log estimate") + ylab("Trimfill log estimate") + ggtitle("Fixed effects to Trimfill")
+
+trimfill.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.trimfill.fixef)))) + geom_point() + 
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
+	xlab("Random effects log estimate") + ylab("Trimfill log estimate") + ggtitle("Random effects to Trimfill")
+
+#Scatterplots of metac-analysis and corrected log estimates
+copas.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.copas)))) + geom_point() + 
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
+	xlab("Fixed effects log estimate") + ylab("Copas log estimate") + ggtitle("Fixed effects to Copas")
+
+copas.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.copas)))) + geom_point() + 
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE, show.legend = T) + 
+	xlab("Random effects log estimate") + ylab("Copas log estimate") + ggtitle("Random effects to Copas")
+
+#Scatterplots of metac-analysis and corrected log estimates
+reg.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs(log(abs((est.fixef))))), y = log(abs(log(abs(est.reg.ranef)))))) + geom_point() + 
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
+	xlab("Fixed effects log estimate") + ylab("Regression log estimate") + ggtitle("Fixed effects to Regression")
+
+reg.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.reg.ranef)))) + geom_point() + 
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
+	xlab("Random effects log estimate") + ylab("Regression log estimate") + ggtitle("Random effects to Regression")
+
+#Scatterplots of test- statistics:
+trimfill.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.trimfill.fixef))) + geom_point() +
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
+	ggtitle("Fixed effects and trimfill z statistics") + ylab("Trimfill  statistic") + xlab("Fixed effects  statistic")
+
+trimfill.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.trimfill.fixef))) + geom_point() +
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
+	ggtitle("Random effects and trimfill z statistics") + ylab("Trimfill  statistic") + xlab("Random effects  statistic")
+
+#Scatterplots of test- statistics:
+copas.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.copas))) + geom_point() +
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
+	ggtitle("Fixed effects and Copas z statistics") + ylab("Copas  statistic") + xlab("Fixed effects  statistic")
+
+copas.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.copas))) + geom_point() +
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
+	ggtitle("Random effects and Copas z statistics") + ylab("Copas  statistic") + xlab("Random effects  statistic")
+
+#Scatterplots of test- statistics:
+reg.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.reg.ranef))) + geom_point() +
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
+	ggtitle("Fixed effects and Regression z statistics") + ylab("Regression  statistic") + xlab("Fixed effects  statistic")
+
+reg.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.reg.ranef))) + geom_point() +
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
+	ggtitle("Random effects and Regression z statistics") + ylab("Regression  statistic") + xlab("Random effects  statistic")
 @
@@
 
-\begin{frame}{Cochrane Library}
-Database of high-quality, systematic reviews in clinical science.
+% \begin{frame}{Evidence Synthesis}
+% Summarise evidence over fields and studies
+% 
+% Quantitatively by meta-analysis
+% 
+% \end{frame}
 
-Currently $\sim$ 8,000 reviews, prepared by independent groups.
+\begin{frame}{Cochrane Organisation}
+Aim: summarise findings in primary clinical research and health care
 
-Reviews are peer-reviewed and prepared after guidelines.
+Provide peer-reviewed, systematic reviews
+
+Public access (for some countries)
 \end{frame}
@@
 \Sexpr{format(dim(data)[1], big.mark=",")} study results.
+\end{frame}
+
+\begin{frame}[fragile]{Review Example: Binary Outcome}
+Barbiturate efficacy for head injury treatment
+\vspace{-5mm}
+<<echo = FALSE, results = 'asis'>>=
+print(xtable(barbi2, label = "barbiturates", digits = 0), include.rownames = F, size = "tiny")
+@
 \end{frame}
@@
 
-\begin{frame}{Dataset Structure}
-\begin{itemize}
-\item Comparison: What is compared, e.g. treatment vs. control
-\item Outcome: How it is compared
-\item Subgroup: Subgroup affiliation
-\item Meta-Analysis Group: Results from same comparison, outcome and subgroup
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]{Review Example: binary outcome}
-Barbiturate efficacy for head injury treatment
-\vspace{-5mm}
-<<echo = FALSE, results = 'asis'>>=
-print(xtable(barbi2, label = "barbiturates", digits = 0), include.rownames = F, size = "tiny")
-@
-\end{frame}
-
 \begin{frame}[fragile]{Dataset Properties}
-Missing data:
+Review or study level:
 <<echo=FALSE, results = 'asis'>>=
-print(xtable(missing.table, align = "lr"), include.rownames = T, include.colnames = F)
-@
-\end{frame}
-
-\begin{frame}[fragile]{Dataset Properties}
-Review and study properties:
-<<echo=FALSE, results = 'asis'>>=
-print(xtable(dataset.properties, digits = 0, align = "lrrrr"), include.rownames = T, size = "footnotesize", hline = c(0,1,1,4))
-@
-\end{frame}
-
-\begin{frame}[fragile]{Pooling Studies - Meta-Analysis}
-Multiple results in a meta-analysis group can be pooled:
-<<echo=FALSE, results = 'asis'>>=
-print(xtable(cum.repr.trials.subg, label = "repr.groups", align = "lrrr", digits = 0), include.rownames = F, size = "footnotesize")
+print(xtable(dataset.properties, digits = 0, align = "lrrrr"), include.rownames = T, size = "footnotesize", hline = c(0,1,1,3))
 @
@@
 \begin{itemize}
-\item Summary of evidence (e.g. of a treatment)
+\item Summary of evidence (e.g. of a treatment effect)
 \item More reliable evidence (?)
@@
 \begin{itemize}
-\item Selective publication of studies with large effects
-\item Bias in smaller studies
+\item Selective publication of studies with significant results - publication bias
+\item Selective reporting of most favorable outcomes
 \item Systematical differences in study settings
-\item \ldots
 \end{itemize}
@@
 \begin{itemize}
-\item $n$ large
-\item variation in the estimated variances of effects \\(here: $\frac{\sigma_{\textrm{max}}}{\sigma_{\textrm{min}}} > 4$)
+\item Number of studies $n$ large
+\item variation in the estimated variances of effects %\\(here: $\frac{\sigma_{\textrm{max}}}{\sigma_{\textrm{min}}} > 4$)
 \end{itemize}
@@
 
-\vspace{-1.2cm}
+\vspace{-1.1cm}
 
@@
 par(las = 1, mfrow = c(1,2))
-radial(meta.example, comb.fixed = F)
-radial(meta.nexample, comb.fixed = F)
+biased.rev$inv <- 1/biased.rev$se
+plot(y = (biased.rev$effect/biased.rev$se), x = (biased.rev$se^-1), xlim = c(0, 6), xlab = "inverse standard error", 
+		 ylab = "mean diff. / std. error")
+
+unbiased.rev$inv <- 1/unbiased.rev$se
+plot(y = (unbiased.rev$effect/unbiased.rev$se), x = (unbiased.rev$inv), xlim = c(0, 1.2), 
+		 ylim = c(-18, 0), xlab = "inverse standard error", ylab = "mean diff. / std. error")
 @
@@
 \begin{frame}{Regression based Tests}
-Continuous outcomes tests:
+studies $i,.. ,n$, effects $\theta_i$ and variances $v_i$, s.e. $s_i$
 
-$i$ being the $i$th study in a meta-analysis:
+$\theta_M$ is the pooled effect and $\tau^2$ the between-study variance.
 
-Let $y_{i} = \textrm{effect}_{i}/\textrm{se}_{i}$ and $x_{i} = 1/\textrm{se}_{i}$
+Let $y_{i} = \theta_{i}/_{i}$ and $x_i = 1/s_i$
 \begin{itemize}
-\item \citet{Egger} : \\ $y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i})$
-\item \citet{thompson.sharp} : \\ $y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i} + \tau^2)$
+\item \citet{Egger} : Simple linear regression \\ $y_i = \beta_0 + \beta_1 x_i, \epsilon_i \sim N(0, \sigma)$
+\item \citet{thompson.sharp} : extension of Egger with study weights $v_{i} + \tau^2$ 
 \end{itemize}
-%Test for non-zero intercept $\beta_{0}$
-\end{frame}
-
-\begin{frame}[fragile]{Egger's Tests}
-
-\vspace{-6cm}
-
-<<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
-par(las = 1, mfrow = c(1,2))
-metabias(meta.example, plotit = TRUE, method.bias = "linreg")
-metabias(meta.nexample, plotit = TRUE, method.bias = "linreg")
-@
 
@@
 
-\begin{frame}[fragile]{Thompson and Sharp's Tests}
+\begin{frame}[fragile]{Egger's Test examples}
+Test for non-zero intercept $\beta_{0}$
 
-\vspace{-6.5cm}
+\vspace{-1.1cm}
+<<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
+par(las = 1, mfrow = c(1,2))
+biased.rev$inv <- 1/biased.rev$se
+m.ex <- lm(formula = (biased.rev$effect/biased.rev$se) ~ (biased.rev$inv))
+plot(y = (biased.rev$effect/biased.rev$se), x = (biased.rev$se^-1), xlim = c(0, 6), xlab = "inverse standard error", 
+		 ylab = "mean diff. / std. error")
+abline(coef = coef(m.ex), lty = 2, col = 2)
 
-<<message = FALSE, echo=FALSE, warning = FALSE, fig.height= 4>>=
-par(las = 1, mfrow = c(1,2))
-metabias(meta.example, plotit = TRUE, method.bias = "mm")
-metabias(meta.nexample, plotit = TRUE, method.bias = "mm")
+unbiased.rev$inv <- 1/unbiased.rev$se
+m.nex <- lm(formula = (unbiased.rev$effect/unbiased.rev$se) ~ (unbiased.rev$inv))
+plot(y = (unbiased.rev$effect/unbiased.rev$se), x = (unbiased.rev$inv), xlim = c(0, 1.2), 
+		 ylim = c(-18, 0), xlab = "inverse standard error", ylab = "mean diff. / std. error")
+abline(coef = coef(m.nex), lty = 2, col = 2)
 @
-
 \end{frame}
 
-\begin{frame}{Regression based Tests}
-Adjustments for binary outcomes:
+\begin{frame}{Regression Tests for Binary Outcomes}
+
 \begin{itemize}
-\item \citet{Peters} :$x_{i}$ = inverse of total sample size, $\textrm{variance}_{i}$ as weight.
-\item \citet{Harbord} :$x:{i}$ = score of the log-likelihood of a proportion, $\textrm{variance}_{i}$ as weight.
+\item \citet{Peters} :$x_i = 1/n_i$ instead $1/s_i$, inverse variances as weight.
+\item \citet{Harbord} :$x_i$ = score of the log-likelihood of a proportion and inverse variances as weights.
 \item \citet{Rucker} :Use arcsine variance stabilizing transformation for variances and effects, do e.g. Egger's test.
@@
 \begin{frame}{Rank based tests}
-\citet{begg.ties}
-Let $y_{i}$ the standardized effect size of a study $i$, $v_{i}$ it's variance and $n$ the number of studies
+\citet{begg.ties}: \\
+Let $y_{i}$ be $frac{\theta_i - \theta_M}{v_i}$ and $x_i$ its variance ($\neq v_i$)
 
-$u$ the number of pairs $(y_{i}, v_{i})$ ranked in the same order, $l$
+$u$ the number of pairs $(y_{i}, x_{i})$ ranked in the same order, $l$
 the number of pairs in the opposite order
 
-$Z = (u - l)/\sqrt{n(n-1)(2n + 5)/18}$ \\ can be used as a test statistic (based on Kendall's Tau)
+$Z = \frac{(u - l)}{\sqrt{n(n-1)(2n + 5)/18}}$  is a test statistic
 \end{frame}
@@
 \begin{frame}{Rank based tests}
-\citet{Schwarzer}
-Let $e_{t}$ the number of events in the treatment group
+\citet{Schwarzer}: \\
+$e_t$ number of events in the treatment group
 
-Given constant log odds ratio, $E_{t}$ follows a hypergeometric distribution.
+$E_t$ follows hypergeometric distribution: calculate $\mathbb{E}(E_{t})$ and variances
 
-$\mathbb{E}(E_{t})$ and the variance can be estimated and used as in 
-\citet{begg.ties}
+proceed as in \citet{begg.ties}
 \end{frame}
@@
 \begin{frame}{Test Results}
-Application of tests if:
+Inclusion criteria (from \citet{Ioannidis2007}):
 \begin{itemize}
@@
 \item at least one statistically significant effect in a study
-\item $\frac{\sigma_{\textrm{max}}}{\sigma_{\textrm{min}}} > 4$
+\item $\frac{\sigma_{\textrm{max}}^2}{\sigma_{\textrm{min}}^2} > 4$
 \item $I^2 < 0.5$
@@
 
-% \begin{frame}[fragile]{Test Results: Significance}
-% 
-% <<echo = FALSE, fig.height = 4>>=
-% grid.arrange(p.bin, p.cont, ncol = 2)
-% @
-% \end{frame}
+\begin{frame}[fragile]{Continuous Outcome Test Results}
+$p$-values distribution, $n$ = \Sexpr{dim(metac.cont)[1]}:
 
-\begin{frame}[fragile]{Continuous Outcome Test Results}
-$p$-values distribution:
-
+\vspace{-2mm}
 <<echo = FALSE, fig.height = 4, message = FALSE>>=
@@
 \begin{frame}[fragile]{Binary Outcome Test Results}
-$p$-values distribution:
+$p$-values distribution, $n$ = \Sexpr{dim(metac.bin)[1]}:
 
-<<echo = FALSE, fig.height = 4, message = FALSE>>=
+\vspace{-2mm}
+<<echo = FALSE, fig.height = 3.6, message = FALSE>>=
 plot(p.dist.bin)
@@
 
-<<echo = FALSE, fig.height = 3.8, message = FALSE>>=
+\vspace{-2mm}
+<<echo = FALSE, fig.height = 3.2, message = FALSE>>=
 grid.arrange(agree.cont, agree.bin, ncol = 2)
@@
 \begin{frame}{Adjustment by regression}
-Similar to the tests, but with unnormalized effect $y_{i}$:
+$y_i = \theta_i/s_i, x_i = 1/s_i$
 
-\begin{align}
-y_{i} = \beta_{0} + \beta_{1}x_{i}
-\end{align}
+$y_i = \beta_0 + \beta_1 x_i, \epsilon_i \sim N(0, \sigma)$
 
-$\beta_{0}$	 corresponds to $y_{i}$ with $x_{i} = 0$
+$\beta_{1}$ is the weighted mean treatment effect if $\beta_{0} = 0$
 \end{frame}
 
-\begin{frame}[fragile]{Adjustment by regression}
-Linear regression method:
+\begin{frame}{Adjustment by regression}
+Radial plots (continuous outcome examples):
 
-<<echo = FALSE, fig.height = 3>>=
-grid.arrange(reg.1, reg.2, ncol = 2)
+\vspace{-1.1cm}
+
+<<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
+par(las = 1, mfrow = c(1,2))
+biased.rev$inv <- 1/biased.rev$se
+m.ex.0 <- lm(formula = (biased.rev$effect/biased.rev$se) ~ 0 + (biased.rev$inv))
+m.ex <- lm(formula = (biased.rev$effect/biased.rev$se) ~ (biased.rev$inv))
+plot(y = (biased.rev$effect/biased.rev$se), x = (biased.rev$se^-1), xlim = c(0, 6), xlab = "inverse standard error", 
+		 ylab = "mean diff. / std. error")
+abline(coef = c(0,coef(m.ex.0)), lty = 2)
+abline(coef = coef(m.ex), lty = 2, col = 2)
+
+unbiased.rev$inv <- 1/unbiased.rev$se
+m.nex.0 <- lm(formula = (unbiased.rev$effect/unbiased.rev$se) ~ 0 + (unbiased.rev$inv))
+m.nex <- lm(formula = (unbiased.rev$effect/unbiased.rev$se) ~ (unbiased.rev$inv))
+plot(y = (unbiased.rev$effect/unbiased.rev$se), x = (unbiased.rev$inv), xlim = c(0, 1), 
+		 ylim = c(-18, 0), xlab = "inverse standard error", ylab = "mean diff. / std. error")
+abline(coef = c(0,coef(m.nex.0)), lty = 2)
+abline(coef = coef(m.nex), lty = 2, col = 2)
 @
@@
 
-\begin{frame}[fragile]{Shrinkage Regression}
+\begin{frame}[fragile]{Limit Meta-Analysis}
 Extended random effects model:
@@
 \begin{align}
-y_{i} = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}),  
+y_{i} = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{v_{i} + \tau^2}), \nonumber \\
 \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \nonumber
@@
 
-\vspace{-8mm}
-\begin{align}
-\mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{ if } \sqrt{v_{i}} \rightarrow 0 \nonumber
-\end{align}
-
-$\beta_{0}, \beta_{1}$ and $\tau$ can be estimated e.g. by ML and REML.
+Use $\mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau$ for $\sqrt{v_{i}} \rightarrow 0$
+as corrected treatment efffect.
 \end{frame}
@@
 \begin{frame}[fragile]{Shrinkage Regression}
-shrinking the within study variance:
+Funnel plot with effect with infinite precision:
 
-\vspace{-4mm}
-\begin{align}
-y_{i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{s_{i}/M + \tau^2}) \nonumber
-\end{align}
+\vspace{-1.1cm}
+<<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
+par(las = 1, mfrow = c(1,2))
+funnel(limitmeta(meta.example))
+funnel(limitmeta(meta.nexample))
+@
+\end{frame}
 
-Letting $M \rightarrow \infty$ and substituting for all parameters and the observed residual
+\begin{frame}{Copas selection model}
+\citet{Copas1}: Bivariate normal model with two parts:
 
@@
 \begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
+y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \label{population.model} \\
+\mu_{i} \sim N(\mu, \tau^2) \label{population.model} \\
+z_{i} = a + b/s_{i} + \delta_{i} \label{selection.model}
 \end{align}
 
+\ref{population.model} is called population model, \ref{selection.model} the selection model
+
+$(\epsilon_{i}, \delta_{i})$ are standard normal residuals with correlation $\rho = cor(y_{i}, z_{i})$.
 \end{frame}
 
-\begin{frame}[fragile]{Shrinkage Regression}
-Three different treatment effect estimates:
+\begin{frame}[fragile]{Sensitivity Analysis}
+Model the selection process with different $a,b$
 
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-\end{align}
+Test if small study effect is significant, by including \\ $y_{i} = \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}$
 
+Estimation: Select $a, b$ such that $H0$ can not be rejected and estimated
+number of unpublished studies is minimal.
+\end{frame}
+
+\begin{frame}{Trim-and-Fill}
+Non-parametric, iterative method:
+
+Cut away smallest study until funnel plot is symmetric
+
+Mirror studies that are responsible for asymmetry
+\end{frame}
+
+\begin{frame}[fragile]{Adjustment Results: Trim-and-fill}
+Difference between adjusted and fixed effects meta-analysis estimate:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+plot(hist.trimfill1)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Adjustment Results: Copas}
+Difference between adjusted and fixed effects meta-analysis estimate:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+plot(hist.copas1)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Adjustment Results: Regression}
+Difference between adjusted and fixed effects meta-analysis estimate:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+plot(hist.reg1)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Adjustment Results: Trim-and-fill}
+Adjusted and meta-analysis test statistics:
+
+\vspace{-3mm} 
+<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+grid.arrange(trimfill.fixef.sc.zval, trimfill.ranef.sc.zval, ncol = 2)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Adjustment Results: Copas}
+Adjusted and meta-analysis test statistics:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+grid.arrange(copas.fixef.sc.zval, copas.ranef.sc.zval, ncol = 2)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Adjustment Results: Regression}
+Adjusted and meta-analysis test statistics:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+grid.arrange(reg.fixef.sc.zval, reg.ranef.sc.zval, ncol = 2)
+@
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Backup Slides%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{frame}[fragile]{Adjustment Results: Trim-and-fill}
+Treatment effect difference:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+plot(hist.trimfill)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Adjustment Results: Copas}
+Treatment effect difference:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+plot(hist.copas)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Adjustment Results: Regression}
+Treatment effect difference:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+plot(hist.reg)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Adjustment Results: Trim-and-fill}
+log treatment effect estimates:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+grid.arrange(trimfill.fixef.sc.effect, trimfill.ranef.sc.effect, ncol = 2)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Adjustment Results: Copas}
+log treatment effect estimates:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+grid.arrange(copas.fixef.sc.effect, copas.ranef.sc.effect, ncol = 2)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Adjustment Results: Regression}
+log treatment effect estimates:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+grid.arrange(reg.fixef.sc.effect, reg.ranef.sc.effect, ncol = 2)
+@
 \end{frame}
@@
 
+% \begin{frame}[fragile]{Test Results: Significance}
+% 
+% <<echo = FALSE, fig.height = 4>>=
+% grid.arrange(p.bin, p.cont, ncol = 2)
+% @
+% \end{frame}
+
+% \begin{frame}[fragile]{Pooling Studies - Meta-Analysis}
+% Multiple results in a meta-analysis group can be pooled:
+% <<echo=FALSE, results = 'asis'>>=
+% print(xtable(cum.repr.trials.subg, label = "repr.groups", align = "lrrr", digits = 0), include.rownames = F, size = "footnotesize")
+% @
+% \end{frame}
+
+% \begin{frame}{Dataset Structure}
+% \begin{itemize}
+% \item Comparison: What is compared, e.g. treatment vs. control
+% \item Outcome: How it is compared
+% \item Subgroup: Subgroup affiliation
+% \item Meta-Analysis Group: Results from same comparison, outcome and subgroup
+% \end{itemize}
+% \end{frame}
+
+% \begin{frame}[fragile]{Dataset Properties}
+% Missing data:
+% <<echo=FALSE, results = 'asis'>>=
+% print(xtable(missing.table, align = "lr"), include.rownames = T, include.colnames = F)
+% @
+% \end{frame}
+
+% \begin{frame}{Adjustment by regression}
+% Similar to the tests, but with unnormalized effect $y_{i}$:
+% 
+% \begin{align}
+% y_{i} = \beta_{0} + \beta_{1}x_{i}
+% \end{align}
+% 
+% $\beta_{0}$	 corresponds to $y_{i}$ with $x_{i} = 0$
+% \end{frame}
+% 
+% \begin{frame}[fragile]{Adjustment by regression}
+% Linear regression method:
+% 
+% <<echo = FALSE, fig.height = 3>>=
+% grid.arrange(reg.1, reg.2, ncol = 2)
+% @
+% \end{frame}
+
+% \begin{frame}[fragile]{Thompson and Sharp's Tests}
+% Generalised radial plot with new standard error $x_i = s_i + \tau$
+% 
+% \vspace{-1.1cm}
+% <<message = FALSE, echo=FALSE, warning = FALSE, fig.height= 4>>=
+% par(las = 1, mfrow = c(1,2))
+% tau.ex <- meta.example$tau
+% biased.rev$inv <- 1/sqrt((biased.rev$se^2 + tau.ex^2))
+% m.ex <- lm(formula = (biased.rev$effect*biased.rev$inv) ~ (biased.rev$inv), weights = biased.rev$se)
+% biased.rev$inv <- 1/biased.rev$se
+% plot(y = (biased.rev$effect/biased.rev$se), x = (biased.rev$inv), xlim = c(0, 4), xlab = "inverse standard error", 
+% 		 ylab = "mean diff. / std. error")
+% abline(coef = coef(m.ex), lty = 2, col = 2)
+% 
+% tau.nex <- meta.nexample$tau
+% unbiased.rev$inv <- 1/sqrt((unbiased.rev$se^2 + tau.nex^2))
+% m.nex <- lm(formula = (unbiased.rev$effect*unbiased.rev$inv) ~ (unbiased.rev$inv), weights = unbiased.rev$se)
+% plot(y = (unbiased.rev$effect/unbiased.rev$se), x = (unbiased.rev$inv), xlim = c(0, .6), 
+% 		 ylim = c(-18, 0), xlab = "inverse standard error", ylab = "mean diff. / std. error")
+% abline(coef = coef(m.nex), lty = 2, col = 2)
+% @
+% 
+% \end{frame}
+% 
+% 
+% \begin{frame}[fragile]{Limit Meta-Analysis}
+% \begin{align}
+% y_{M,i} &= \beta_{0} + \beta_{1}(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{s_{i}/M + \tau^2}) \nonumber
+% \end{align}
+% 
+% Letting $M \rightarrow \infty$ and substituting for all parameters and the observed residual
+% 
+% \vspace{-8mm}
+% \begin{align}
+% y_{\infty,i} &= \beta_{0} + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_i - \beta_0)
+% \end{align}
+% \end{frame}
+% 
+% \begin{frame}[fragile]{Limit Meta-Analysis}
+% By plugging in $s_i$ for $v_i$, $\hat{tau}$ for $\tau$ and $\hat{\beta_0}$, get new study effects:
+% 
+% Three different treatment effect estimates:
+% \begin{itemize}
+% \item Expectated adjusted treatment effect with infinite precision: $\hat{\beta_{0}^\star} + \hat{\beta_{1}}\hat{\tau}$
+% \item Fixed effect estimate based on $(y_{\infty,1},.. , y_{\infty,n}$
+% \item Slope $\beta_{\textrm{lim}}$ of best-fitting regression line in radial plot with $(y_{\infty,i}, s_{i})$
+% \end{itemize}
+% \end{frame}
+
 \end{document}

### 2019-05-20 code/adjustment2.R

@@ -1,0 +1,196 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+
+# data = pb.readData(path = PATH_DATA, file = FILE)
+# tmp = pb.clean(data)
+# data = tmp[[1]]
+# aliases = tmp[[2]]
+
+
+meta.id <- function(meta.id.tolook){
+	dt <- data.ext %>% filter(meta.id == meta.id.tolook)
+	if(any(is.na(dt$events1)) | all(dt$events1 == 0)){
+		meta.ex <- metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, studlab = study.name, data = dt)
+	} else{
+		meta.ex <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, sm = "OR", data = dt)
+	}
+	return(meta.ex)
+}
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+load(file.path(PATH_RESULTS, file = "mly.RData"))
+load(file.path(PATH_RESULTS, file = "data.processed.RData"))
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+	load(file.path(PATH_RESULTS, file.bin))
+} else {
+	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
[…]

### 2019-05-20 Presentation/present.Rnw
Presentation update

@@
 
+meta.id <- function(meta.id.tolook){
+	dt <- data.ext %>% filter(meta.id == meta.id.tolook)
+	if(any(is.na(dt$events1)) | all(dt$events1 == 0)){
+		meta.ex <- metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, studlab = study.name, data = dt)
+	} else{
+		meta.ex <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, sm = "RR", data = dt, method = "Inverse")
+	}
+	return(meta.ex)
+}
+
+funnel.id <- function(meta.id.tolook){
+	funnel(meta.id(meta.id.tolook))
+}
+
+trimfill.id <- function(meta.id.tolook){
+	funnel(trimfill(meta.id(meta.id.tolook)))
+}
+
+limitmeta.id <- function(meta.id.tolook){
+	funnel(limitmeta(meta.id(meta.id.tolook)))
+}
+
+copas.id <- function(meta.id.tolook){
+	auto.copas(meta.id(meta.id.tolook), 0.1)
+}
+
+setting.id <- function(meta.id.tolook){
+	return(meta %>% filter(meta.id == meta.id.tolook) %>% select(comparison.name, comparison.nr, outcome.name, sungroup.name))
+}
+
+est.id <- function(meta.id.tolook){
+	return(meta %>% filter(meta.id == meta.id.tolook) %>% select(est.fixef, est.ranef, est.copas, est.trimfill.fixef, est.reg.ranef))
+}
+
+single.study.id <- function(meta.id.tolook){
+	return(print(data.ext %>% filter(meta.id == meta.id.tolook) %>% select(study.name, effect, se, total1, total2, events1, events2, mean1, mean2) %>% 
+							 	arrange(se), n = 200))
+}
+
 #Meta-analysis example
@@
 dat_text <- data.frame(
-  label = paste(c(sum(metac.cont$begg.test), sum(metac.cont$egger.test), sum(metac.cont$thomson.test)), "< 0.05"),
+  label = paste(c(sum(metac.cont$begg.test), sum(metac.cont$egger.test), sum(metac.cont$thomson.test)), "< 0.05,",
+  							round(c(mean(metac.cont$begg.test), mean(metac.cont$egger.test), mean(metac.cont$thomson.test)),2)*100, "%"),
   test.type   = c("pval.begg.cont", "pval.egger.cont", "pval.thomson.cont"))
 
+labels <- c(pval.begg.cont = "Begg Mazumdar", pval.egger.cont = "Egger", pval.thomson.cont = "Thompson Sharp")
 p.dist.cont <- metac.cont %>% ungroup() %>% 
@@
   gather(key = "test.type", value = "p.value") %>% 
-  ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + facet_wrap(~test.type) + 
-	geom_text(data = dat_text, mapping = aes(x = -Inf, y = -Inf, label = label), hjust   = -1,
-  vjust   = -4, color = "white")
+  ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + 
+	facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 25, label = label),  color = "black") + 
+	theme(strip.text.x = element_text(size=15))
 
 	dat_text <- data.frame(
-  label = paste(c(sum(metac.bin$egger.test), sum(metac.bin$harbord.test), sum(metac.bin$peter.test), 
-  										sum(metac.bin$rucker.test), sum(metac.bin$schwarzer.test)), "< 0.05"),
-  test.type   = c("pval.egger.bin", "pval.harbord.bin", "pval.peter.bin", "pval.rucker.bin", "pval.schwarzer.bin"))
+  label = paste(c(sum(metac.bin$harbord.test), sum(metac.bin$peter.test), 
+  										sum(metac.bin$rucker.test), sum(metac.bin$schwarzer.test)), "< 0.05,",
+  							round(c(mean(metac.bin$harbord.test), mean(metac.bin$peter.test), 
+  										mean(metac.bin$rucker.test), mean(metac.bin$schwarzer.test)),2)*100, "%"),
+  test.type   = c("pval.harbord.bin", "pval.peter.bin", "pval.rucker.bin", "pval.schwarzer.bin"))
+
+labels <- c(pval.harbord.bin = "Harbord", pval.peter.bin = "Peter", pval.rucker.bin = "Rucker", pval.schwarzer.bin = "Schwarzer")
 
 p.dist.bin <- metac.bin %>% ungroup() %>% 
-  select(pval.egger.bin, pval.harbord.bin, pval.peter.bin, pval.rucker.bin, pval.schwarzer.bin) %>% 
+  select(pval.harbord.bin, pval.peter.bin, pval.rucker.bin, pval.schwarzer.bin) %>% 
   gather(key = "test.type", value = "p.value") %>% 
-  ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + facet_wrap(~test.type) + 
-	geom_text(data = dat_text, mapping = aes(x = -Inf, y = -Inf, label = label), hjust   = -0.65,
-  vjust   = -2, color = "white")
+  ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 100, label = label), color = "black") + 
+	theme(strip.text.x = element_text(size=15))
 
@@
 	est.reg.ranef = ifelse(!is.na(est.fixef.bin), est.reg.ranef - 1, est.reg.ranef),
+	fixef.ranef = ifelse(abs(est.ranef) > abs(est.fixef), "Reduction", "Amplification"),
 	fixef.trimfill = ifelse(abs(est.fixef) > abs(est.trimfill.fixef), "Reduction", "Amplification"),
@@
 
+hist.ranef <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.ranef))) +
+	geom_histogram() + facet_grid(~factor(fixef.ranef)) + xlim(0, 2) + xlab("Effect difference") + 
+	theme_bw() + theme(legend.position = "bottom", strip.text.x = element_text(size=15)) + ylim(0, 250)
+
 trimfill.miss <- effect.diff %>% group_by(fixef.trimfill) %>% mutate(dif = abs(est.fixef - est.trimfill.fixef)) %>% 
@@
 	geom_histogram() + facet_grid(~factor(fixef.trimfill)) + xlim(0, 2)+ xlab("Effect difference") +
-	geom_text(data = trimfill.label, mapping = aes(label = label, x = 0, hjust = 0.05, y = 300), 
+	geom_text(data = trimfill.label, mapping = aes(label = label, x = 0, hjust = 0, y = 300), 
 						color = "black") + theme_bw() + 
@@
 copas.label$label[1] <- sub("3.5,", "3.5, \n   ", copas.label$label[1])
+copas.label$label[2] <- sub("11.5,", "11.5, \n   ", copas.label$label[2])
 
@@
 	geom_histogram() + facet_grid(~factor(fixef.copas)) + xlim(0, 2) + xlab("Effect difference") +
-	geom_text(data = copas.label, mapping = aes(label = label, x = 0, hjust = 0.05, y = 175), 
+	geom_text(data = copas.label, mapping = aes(label = label, x = 0, hjust = 0, y = 175), 
 						color = "black") + theme_bw() +
@@
 	geom_histogram() + facet_grid(~factor(fixef.reg)) + xlim(0, 3)+ xlab("Effect difference") +
-	geom_text(data = reg.ranef.label, mapping = aes(label = label, x= 0, y = 250, hjust = 0.05), 
+	geom_text(data = reg.ranef.label, mapping = aes(label = label, x= 0, y = 250, hjust = 0), 
 						color = "black", size = 2.8) + theme_bw() + scale_fill_discrete(name="Effect direction") +
@@
 	geom_histogram() + facet_grid(~factor(fixef.reg)) + xlim(0, 3)+ xlab("Effect difference") +
-	geom_text(data = reg.ranef.label, mapping = aes(label = label, x= 0, y = 250, hjust = 0.05), 
+	geom_text(data = reg.ranef.label, mapping = aes(label = label, x= 0, y = 250, hjust = 0), 
 						color = "black", size = 2.8) + theme_bw() + 
@@
 #Scatterplots of metac-analysis and corrected log(abs(abs estimates
+ranef.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.ranef)))) + geom_point() + 
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
+	xlab("Fixed effects log estimate") + ylab("Random effects log estimate") + ggtitle("Fixed effects to Random effects")
+
+# metac %>% ggplot(aes(y = log(abs((est.ranef))), x = log(abs(est.trimfill.fixef)))) + geom_point() + 
+# 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
+# 	xlab("Random effects log estimate") + ylab("Trimfill log estimate") + ggtitle("Random effects to Trimfill")
+
+#Scatterplots of metac-analysis and corrected log(abs(abs estimates
 trimfill.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.trimfill.fixef)))) + geom_point() + 
@@
 copas.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.copas)))) + geom_point() + 
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + xlim(0, 25) +
 	xlab("Fixed effects log estimate") + ylab("Copas log estimate") + ggtitle("Fixed effects to Copas")
@@
 copas.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.copas)))) + geom_point() + 
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE, show.legend = T) + 
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE, show.legend = T) + xlim(0, 20) +
 	xlab("Random effects log estimate") + ylab("Copas log estimate") + ggtitle("Random effects to Copas")
@@
 #Scatterplots of metac-analysis and corrected log estimates
-reg.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs(log(abs((est.fixef))))), y = log(abs(log(abs(est.reg.ranef)))))) + geom_point() + 
+reg.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.reg.ranef)))) + geom_point() + 
 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
@@
 	xlab("Random effects log estimate") + ylab("Regression log estimate") + ggtitle("Random effects to Regression")
+
+#Scatterplots of test- statistics:
+ranef.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.ranef))) + geom_point() +
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
+	ggtitle("Fixed effects and Random effects z statistics") + ylab("Random effects statistic") + xlab("Fixed effects statistic")
+
+metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.trimfill.fixef))) + geom_point() +
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
+	ggtitle("Fixed effects and Random effects z statistics") + ylab("Random effects statistic") + xlab("Fixed effects statistic")
 
@@
 	ggtitle("Random effects and Regression z statistics") + ylab("Regression  statistic") + xlab("Random effects  statistic")
+
+#Missing study proportions:
+p.missing.copas <- metac %>% ggplot(aes(x = missing.copas/n)) + geom_histogram(bins = 20) + 
+	xlim(0, 0.5) + ylim(0, 200) + xlab("Proportion of missing studies") + ggtitle("Copas selection model") + theme_bw()
+p.missing.trim <- metac %>% ggplot(aes(x = missing.trim)) + geom_histogram(bins = 20) + 
+	xlim(0, 0.5) + ylim(0, 200) + xlab("Proportion of missing studies") + ggtitle("Trim-and-fill") + theme_bw()
 @
@@
 % \end{frame}
+
+\begin{frame}{Publication Bias}
+Availability of studies depends on the effect sizes thereof
+
+Thesis topic: Abundancy and extent of publication bias in clinical science
+\end{frame}
 
@@
 \item Selective reporting of most favorable outcomes
-\item Systematical differences in study settings
+\item Systematic differences in study settings
 \end{itemize}
@@
 \begin{frame}{Small Study Effect Tests}
-Tests applicable if:
+Different approaches:
 \begin{itemize}
-\item Number of studies $n$ large
-\item variation in the estimated variances of effects %\\(here: $\frac{\sigma_{\textrm{max}}}{\sigma_{\textrm{min}}} > 4$)
+\item Simple linear regression
+\item Rank correlation
 \end{itemize}
-Adjustments required if variance is dependent on effect size (e.g. log odds ratios)
-\end{frame}
-
-\begin{frame}[fragile]{Small Study Effect Tests}
-Funnel plots (continuous outcome examples):
-
-\vspace{-1.2cm}
-
-<<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
-par(las = 1, mfrow = c(1, 2))
-funnel(meta.example)
-funnel(meta.nexample)
-@
-
-\end{frame}
-
-\begin{frame}[fragile]{Regression based Tests}
-Radial plots (continuous outcome examples):
-
-\vspace{-1.1cm}
-
-<<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
-par(las = 1, mfrow = c(1,2))
-biased.rev$inv <- 1/biased.rev$se
-plot(y = (biased.rev$effect/biased.rev$se), x = (biased.rev$se^-1), xlim = c(0, 6), xlab = "inverse standard error", 
-		 ylab = "mean diff. / std. error")
-
-unbiased.rev$inv <- 1/unbiased.rev$se
-plot(y = (unbiased.rev$effect/unbiased.rev$se), x = (unbiased.rev$inv), xlim = c(0, 1.2), 
-		 ylim = c(-18, 0), xlab = "inverse standard error", ylab = "mean diff. / std. error")
-@
-
-\end{frame}
+
+Special methods for binary outcomes	
+\end{frame}
+
+% \begin{frame}[fragile]{Small Study Effect Tests}
+% Funnel plots (continuous outcome examples):
+% 
+% \vspace{-1.2cm}
+% 
+% <<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
+% par(las = 1, mfrow = c(1, 2))
+% funnel(meta.example)
+% funnel(meta.nexample)
+% @
+% 
+% \end{frame}
+% 
+% 
+% \begin{frame}[fragile]{Regression based Tests}
+% Radial plots (continuous outcome examples):
+% 
+% \vspace{-1.1cm}
+% 
+% <<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
+% par(las = 1, mfrow = c(1,2))
+% biased.rev$inv <- 1/biased.rev$se
+% plot(y = (biased.rev$effect/biased.rev$se), x = (biased.rev$se^-1), xlim = c(0, 6), xlab = "inverse standard error", 
+% 		 ylab = "mean diff. / std. error")
+% 
+% unbiased.rev$inv <- 1/unbiased.rev$se
+% plot(y = (unbiased.rev$effect/unbiased.rev$se), x = (unbiased.rev$inv), xlim = c(0, 1.2), 
+% 		 ylim = c(-18, 0), xlab = "inverse standard error", ylab = "mean diff. / std. error")
+% @
+% 
+% \end{frame}
 
@@
 
-\begin{frame}[fragile]{Shrinkage Regression}
+\begin{frame}[fragile]{Limit Meta-Analysis}
 Funnel plot with effect with infinite precision:
@@
 
-\begin{frame}{Copas selection model}
-\citet{Copas1}: Bivariate normal model with two parts:
+\begin{frame}{Selection model}
+\citet{Copas1}: model based on a bivariate normal distribution:
 
@@
 \begin{frame}{Trim-and-Fill}
-Non-parametric, iterative method:
-
-Cut away smallest study until funnel plot is symmetric
-
-Mirror studies that are responsible for asymmetry
+Mirror studies that cause asymmetry:
+\vspace{-1.2cm}
+
+<<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
+par(las = 1, mfrow = c(1, 2))
+funnel(meta.example)
+funnel(meta.nexample)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Results:}
+Difference between random and fixed effects meta-analysis estimate:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 3.6, message = FALSE, warning=FALSE>>=
+plot(hist.ranef)
+@
 \end{frame}
@@
 \vspace{-3mm}
-<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+<<echo = FALSE, fig.height = 3.6, message = FALSE, warning=FALSE>>=
 plot(hist.trimfill1)
@@
 \vspace{-3mm}
-<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+<<echo = FALSE, fig.height = 3.6, message = FALSE, warning=FALSE>>=
 plot(hist.copas1)
@@
 \vspace{-3mm}
-<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+<<echo = FALSE, fig.height = 3.6, message = FALSE, warning=FALSE>>=
 plot(hist.reg1)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Results:}
+Random and fixed effects meta-analyses test statistics:
+
+\vspace{-3mm} 
+<<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
+plot(ranef.fixef.sc.zval)
 @
@@
 \vspace{-3mm} 
-<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+<<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
 grid.arrange(trimfill.fixef.sc.zval, trimfill.ranef.sc.zval, ncol = 2)
@@
 \vspace{-3mm}
-<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+<<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
 grid.arrange(copas.fixef.sc.zval, copas.ranef.sc.zval, ncol = 2)
@@
 \vspace{-3mm}
-<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+<<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
 grid.arrange(reg.fixef.sc.zval, reg.ranef.sc.zval, ncol = 2)
 @
+\end{frame}
+
+\begin{frame}[fragile]{Adjustment Results}
+Missing study proportions:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
+grid.arrange(p.missing.copas, p.missing.trim, ncol = 2) 
+@
+\end{frame}
+
+\begin{frame}[fragile]{Extreme Results}
+RR reduction by trimfill (-3.9), side effects
+
+<<echo = FALSE, fig.height = 3.5>>=
+trimfill.id(165815)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Extreme Results}
+RR Reduction by copas selection model (-4), pain relief
+
+<<echo = FALSE, fig.height = 3.5>>=
+funnel.id(73169)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Extreme Results}
+RR Amplification by regression (+14), side effects
+
+<<echo = FALSE, fig.height = 3.5>>=
+limitmeta.id(119537)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Discussion}
+\begin{itemize}
+\item Proportion of positive tests is well above 10\%
+\item Effect sizes and evidence for treatment effect is diminishued
+\item Limitations: not only primary outcomes, adjustment methods known to
+perform poorly under the 0
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]{Outlook}
+\begin{itemize}
+\item Connect results with different medical fields, look for differences
+\item Connect results with single studies and journals (?)
+\end{itemize}
 \end{frame}
@@
 plot(hist.reg)
+@
+\end{frame}
+
+\begin{frame}[fragile]{Results}
+log treatment effect estimates:
+
+\vspace{-3mm}
+<<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
+plot(ranef.fixef.sc.effect)
 @

### 2019-05-20 code/adjustment.R

@@ -56,24 +56,6 @@ if (file.exists(file.path(PATH_RESULTS, file.meta))) {
   save(meta, file =  file.path(PATH_RESULTS, file.meta))
 }
 
-
-file.cont <- "mly.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-  load(file.path(PATH_RESULTS, file.cont))
-} else {
-  data.cont <- mly.cont(data.ext, 0.05, min.study.number = 2)
-  save(data.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.bin <- "mly.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-  load(file.path(PATH_RESULTS, file.bin))
-} else {
-  data.bin <- mly.bin(data.ext, 0.05, min.study.number = 2)
-  save(data.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-
 require(biostatUZH)
 require(tidyverse)
 require(meta)

### 2019-05-20 Presentation/present.Rnw
update

@@
 dat_text <- data.frame(
-  label = paste(c(sum(metac.cont$begg.test), sum(metac.cont$egger.test), sum(metac.cont$thomson.test)), "< 0.05,",
+  label = paste(c(sum(metac.cont$begg.test), sum(metac.cont$egger.test), sum(metac.cont$thomson.test)), "< 0.1,",
   							round(c(mean(metac.cont$begg.test), mean(metac.cont$egger.test), mean(metac.cont$thomson.test)),2)*100, "%"),
@@
   label = paste(c(sum(metac.bin$harbord.test), sum(metac.bin$peter.test), 
-  										sum(metac.bin$rucker.test), sum(metac.bin$schwarzer.test)), "< 0.05,",
+  										sum(metac.bin$rucker.test), sum(metac.bin$schwarzer.test)), "< 0.1,",
   							round(c(mean(metac.bin$harbord.test), mean(metac.bin$peter.test), 
@@
 	geom_histogram() + facet_grid(~factor(fixef.copas)) + xlim(0, 2) + xlab("Effect difference") +
-	geom_text(data = copas.label, mapping = aes(label = label, x = 0, hjust = 0, y = 175), 
+	geom_text(data = copas.label, mapping = aes(label = label, x = 0, hjust = 0, y = 160), 
 						color = "black") + scale_fill_discrete(name="Effect direction") + theme_bw() +
@@
 	geom_histogram() + facet_grid(~factor(fixef.copas)) + xlim(0, 2) + xlab("Effect difference") +
-	geom_text(data = copas.label, mapping = aes(label = label, x = 0, hjust = 0, y = 175), 
+	geom_text(data = copas.label, mapping = aes(label = label, x = 0, hjust = 0, y = 160), 
 						color = "black") + theme_bw() +
@@
 #Scatterplots of metac-analysis and corrected log(abs(abs estimates
-ranef.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.ranef)))) + geom_point() + 
+ranef.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.ranef)))) + geom_point(size = 0.8) + 
 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
@@
 #Scatterplots of metac-analysis and corrected log(abs(abs estimates
-trimfill.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.trimfill.fixef)))) + geom_point() + 
+trimfill.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.trimfill.fixef)))) + geom_point(size = 0.8) + 
 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
@@
 
-trimfill.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.trimfill.fixef)))) + geom_point() + 
+trimfill.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.trimfill.fixef)))) + geom_point(size = 0.8) + 
 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
@@
 #Scatterplots of metac-analysis and corrected log estimates
-copas.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.copas)))) + geom_point() + 
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + xlim(0, 25) +
+copas.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.copas)))) + geom_point(size = 0.8) + 
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
 	xlab("Fixed effects log estimate") + ylab("Copas log estimate") + ggtitle("Fixed effects to Copas")
 
-copas.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.copas)))) + geom_point() + 
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE, show.legend = T) + xlim(0, 20) +
+copas.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.copas)))) + geom_point(size = 0.8) + 
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE, show.legend = T) + 
 	xlab("Random effects log estimate") + ylab("Copas log estimate") + ggtitle("Random effects to Copas")
@@
 #Scatterplots of metac-analysis and corrected log estimates
-reg.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.reg.ranef)))) + geom_point() + 
+reg.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.reg.ranef)))) + geom_point(size = 0.8) + 
 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
@@
 
-reg.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.reg.ranef)))) + geom_point() + 
+reg.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.reg.ranef)))) + geom_point(size = 0.8) + 
 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
@@
 #Scatterplots of test- statistics:
-ranef.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.ranef))) + geom_point() +
+ranef.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.ranef))) + geom_point(size = 0.8) +
 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
@@
 
-metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.trimfill.fixef))) + geom_point() +
+metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.trimfill.fixef))) + geom_point(size = 0.8) +
 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
@@
 #Scatterplots of test- statistics:
-trimfill.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.trimfill.fixef))) + geom_point() +
+trimfill.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.trimfill.fixef))) + geom_point(size = 0.8) +
 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
@@
 
-trimfill.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.trimfill.fixef))) + geom_point() +
+trimfill.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.trimfill.fixef))) + geom_point(size = 0.8) +
 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
@@
 #Scatterplots of test- statistics:
-copas.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.copas))) + geom_point() +
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
+copas.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.copas))) + geom_point(size = 0.8) +
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + xlim(0, 25) +
 	ggtitle("Fixed effects and Copas z statistics") + ylab("Copas  statistic") + xlab("Fixed effects  statistic")
 
-copas.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.copas))) + geom_point() +
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
+copas.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.copas))) + geom_point(size = 0.8) +
+	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + xlim(0, 20) +
 	ggtitle("Random effects and Copas z statistics") + ylab("Copas  statistic") + xlab("Random effects  statistic")
@@
 #Scatterplots of test- statistics:
-reg.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.reg.ranef))) + geom_point() +
+reg.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.reg.ranef))) + geom_point(size = 0.8) +
 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
@@
 
-reg.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.reg.ranef))) + geom_point() +
+reg.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.reg.ranef))) + geom_point(size = 0.8) +
 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
@@
 \begin{frame}{Publication Bias}
-Availability of studies depends on the effect sizes thereof
-
-Thesis topic: Abundancy and extent of publication bias in clinical science
+Studies with large effects are more likely to be published
+
+Incentives for bad research practices ($p$-hacking...)
+\end{frame}
+
+\begin{frame}{Meta-Analysis}
+Aim to summarize evidence \& reach conclusions
+
+classical meta-analyses rely on random sample assumption
+\end{frame}
+
+\begin{frame}{Fixed Effects Meta-Analysis}
+Study $i$ of $n$ studies, effects $\theta_i$ and variances $v_i$, s.e. $s_i$
+
+Fixed effects estimate: weighted mean with $w_i = 1/\hat{v_i}$:
+
+\begin{align}
+\theta_f &= \frac{\sum_{i = 1}^n w_{i}\theta_i}{\sum_{i = 1}^n w_i} \nonumber \\ 
+\textrm{se}(\theta_f) &= \frac{1}{\sqrt{\sum_{i = 1}^n w_i}} \nonumber
+\end{align}
+\end{frame}
+
+\begin{frame}{Random Effects Meta-Analysis}
+Let $\hat{\theta_i}|\theta_i \sim N(\theta_i, v_i) 
+\theta_i \sim N(\theta, \tau^2)$
+
+Random effects estimate: weigthed mean of $\hat{\theta_i}$ with weights $w_i = 1/(\hat{v_i} + \tau^2)$
+\end{frame}
+
+\begin{frame}{Evidence Based Medicine}
+Likely to base decisions on over-optimistic findings
+
+Direct consequences: patient harm and unnecessary research
 \end{frame}
@@
 Public access (for some countries)
+\end{frame}
+
+\begin{frame}{Research Question}
+Quantify the abundance and impact of publication bias in the Cochrane Library
 \end{frame}
@@
 
-\begin{frame}{Meta-analysis}
-Benefits:
-\begin{itemize}
-\item Summary of evidence (e.g. of a treatment effect)
-\item More reliable evidence (?)
-\end{itemize}
-
-Assumptions:
-\begin{itemize}
-\item Identical study settings (can be relaxed)
-\item Random sample of studies
-\end{itemize}
-\end{frame}
-
 \begin{frame}{Small Study Effects}
@@
 \item Selective publication of studies with significant results - publication bias
-\item Selective reporting of most favorable outcomes
 \item Systematic differences in study settings
@@
 \begin{frame}{Regression based Tests}
-studies $i,.. ,n$, effects $\theta_i$ and variances $v_i$, s.e. $s_i$
+study $i$ of $n$ studies, effects $\theta_i$ and variances $v_i$, s.e. $s_i$
 
@@
 \citet{begg.ties}: \\
-Let $y_{i}$ be $frac{\theta_i - \theta_M}{v_i}$ and $x_i$ its variance ($\neq v_i$)
+Let $y_{i}$ be $\frac{\theta_i - \theta_M}{v_i}$ and $x_i$ its variance ($\neq v_i$)
 
@@
 \item at least one statistically significant effect in a study
-\item $\frac{\sigma_{\textrm{max}}^2}{\sigma_{\textrm{min}}^2} > 4$
+\item $\frac{\hat{v_{\textrm{max}}}^2}{\hat{v_{\textrm{min}}}^2} > 4$
 \item $I^2 < 0.5$
@@
 
-$\beta_{1}$ is the weighted mean treatment effect if $\beta_{0} = 0$
+$\beta_1$ is the weighted mean treatment effect if $\beta_0 = 0$
 \end{frame}
@@
 \begin{align}
-y_{i} = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{v_{i} + \tau^2}), \nonumber \\
+\theta_i = \beta_0 + \beta_1(\sqrt{v_i + \tau^2}) + \epsilon_i(\sqrt{v_i + \tau^2}), \nonumber \\
 \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \nonumber
@@
 \begin{align}
-y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \label{population.model} \\
-\mu_{i} \sim N(\mu, \tau^2) \label{population.model} \\
-z_{i} = a + b/s_{i} + \delta_{i} \label{selection.model}
+\hat{\theta_i} = \theta_{i} + v_i\epsilon_i \label{population.model2} \\
+\theta_i \sim N(\theta, \tau^2) \label{population.model} \\
+z_i = a + b/s_i + \delta_i \label{selection.model}
 \end{align}
 
-\ref{population.model} is called population model, \ref{selection.model} the selection model
-
-$(\epsilon_{i}, \delta_{i})$ are standard normal residuals with correlation $\rho = cor(y_{i}, z_{i})$.
+\ref{population.model}, \ref{population.model2} is called population model, \ref{selection.model} the selection model
+
+$(\epsilon_i, \delta_i)$ are standard normal residuals with correlation $\rho = cor(y_i, z_i)$.
 \end{frame}
@@
 
-Test if small study effect is significant, by including \\ $y_{i} = \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}$
+Test if small study effect is significant, by including \\ $\theta_i = \theta_i + \beta s_i + v_{i}\epsilon_i$
 
@@
 \begin{frame}[fragile]{Results:}
-Difference between random and fixed effects meta-analysis estimate:
+Difference between random and fixed effects meta-analysis estimate: $|\theta_f - \theta_{r}|$
 
@@
 \begin{frame}[fragile]{Adjustment Results: Trim-and-fill}
-Difference between adjusted and fixed effects meta-analysis estimate:
+Absolute difference between adjusted and fixed effects meta-analysis estimate: $|{\theta_f} - {\theta_{\textrm{adjusted}}}|$
 
@@
 \begin{frame}[fragile]{Adjustment Results: Copas}
-Difference between adjusted and fixed effects meta-analysis estimate:
+Absolute difference between adjusted and fixed effects meta-analysis estimate: $|{\theta_f} - {\theta_{\textrm{adjusted}}}|$
 
@@
 \begin{frame}[fragile]{Adjustment Results: Regression}
-Difference between adjusted and fixed effects meta-analysis estimate:
+Absolute difference between adjusted and fixed effects meta-analysis estimate: $|{\theta_f} - {\theta_{\textrm{adjusted}}}|$
 
@@
 
-<<echo = FALSE, fig.height = 3.5>>=
+<<echo = FALSE, fig.height = 3.5, warning=FALSE>>=
 limitmeta.id(119537)

### 2019-05-26 Presentation/present.Rnw
After presentation update

@@
 
-Use $\mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau$ for $\sqrt{v_{i}} \rightarrow 0$
+Use $\mathbb{E}(\theta_{i}) \rightarrow \beta_{0} + \beta_{1}\tau$ for $\sqrt{v_{i}} \rightarrow 0$
 as corrected treatment efffect.
@@
 \begin{align}
-\hat{\theta_i} = \theta_{i} + v_i\epsilon_i \label{population.model2} \\
+\hat{\theta_i} = \theta_{i} + \sigma_i\epsilon_i \label{population.model2} \\
 \theta_i \sim N(\theta, \tau^2) \label{population.model} \\
-z_i = a + b/s_i + \delta_i \label{selection.model}
+z_i = a + b/\hat{s_i} + \delta_i \label{selection.model}
 \end{align}
 
-\ref{population.model}, \ref{population.model2} is called population model, \ref{selection.model} the selection model
+\ref{population.model2},\ref{population.model} is called population model, \ref{selection.model} the selection model
 

### 2019-05-26 report/MSc_Report.tex
After presentation update

@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in mly.cont(data.ext, 0.05, min.study.number = 2): could not find function "{}mly.cont"{}}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in mly.bin(data.ext, 0.05, min.study.number = 2): could not find function "{}mly.bin"{}}}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in readChar(con, 5L, useBytes = TRUE): cannot open compressed file '/Users/p.galiot/PubBias/results/mly.RData', probable reason 'No such file or directory'}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun May 12 15:22:08 2019
+% Tue May 21 16:18:00 2019
 \begin{table}[ht]
@@
 
-\section{Meta-analysis}
-The data at hand is composed of over 400,000 results with balanced sample size $n > 24$.
+% 
+% \section{Meta-analysis}
+% The data at hand is composed of over 400,000 results with balanced sample size $n > 24$.
 The significance of the p-values of treatment effect estimates was calculated for all results in the dataset with acceptable sample size and outcome measures as odds ratios, peto odds ratios, risk ratios, risk differences and mean and standardized mean differences.
-
-%Significance over time? Chunck 1
-
-The results that can be pooled are analysed by fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis with Hartung-Knapp method.
-
-\vspace{0mm}
-In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e.
+% 
+% %Significance over time? Chunck 1
+% 
+% The results that can be pooled are analysed by fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis with Hartung-Knapp method.
+% 
+% \vspace{0mm}
+% In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e.
 if studies were not unique in the dataset with respect to their experimental setup).
 The significance of the treatment effect (primary significance) in a single result is then compared to the significance of the pooled treatment effect (secondary significance).
-In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
+% In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
 The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure.
 The colors indicate the overall fraction of rejected or accepted null-hypotheses of no treatment effect.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}
-
-}
-
-\end{knitrout}
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance}
-\end{figure}
-
-What has been found is that even the meta-analysis that for all meta-analysis methods, the amount of secondary significance is higher than the amount of primary significance.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% #plot(sig.meta.c)
+% @
+% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
+% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+% \label{primary.secondary.significance}
+% \end{figure}
+% 
+% What has been found is that even the meta-analysis that for all meta-analysis methods, the amount of secondary significance is higher than the amount of primary significance.
 Thus more primarily non-significant results can be attached to a secondarily significant result than vice-versa.
-
-\vspace{0mm}
-To illustrate this, the fraction of studies with significant primary treatment effect and primary non-significant treatment effect can be plotted separately (Figure \ref{primary.secondary.significance.sep.sig}).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-14-1}
-
-}
-
-\end{knitrout}
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
+% 
+% \vspace{0mm}
+% To illustrate this, the fraction of studies with significant primary treatment effect and primary non-significant treatment effect can be plotted separately (Figure \ref{primary.secondary.significance.sep.sig}).
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% #grid.arrange(sig.meta.plot1, nonsig.meta.plot, ncol= 1)
+% @
+% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
 The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance}
-\end{figure}
-
-It can be seen that the extent of overlap between primary and secondary significance varies between meta-analysis.
+% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+% \label{primary.secondary.significance}
+% \end{figure}
+% 
+% It can be seen that the extent of overlap between primary and secondary significance varies between meta-analysis.
 A considerable amount of both primary significant and primary non-significant results are overruled by meta-analysis hypothesis tests.
-
-The amount of significant heterogeneity in the results used by the meta-analyses is 53350 and corresponds to 81.5936377\% of the total number of meta-analyses.
-
-%Comparison of significance separated for significant Q? Chunck 2
-
-%Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5
+% 
+% 
+% The amount of significant heterogeneity in the results used by the meta-analyses is length(which(mly$sig.Q == 0)) and corresponds to (length(which(mly$sig.Q == 0))/ dim(mly)[1])*100\% of the total number of meta-analyses.
+% 
+% %Comparison of significance separated for significant Q? Chunck 2
+% 
+% %Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-16-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-14-1}
 
@@
 In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = 1383)
-The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3442).
+The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3955).
 The amount of studies varies from 5\% (Schwarzer's Test) to 13 \% (Egger's Test) for binary outcomes and 9\% (Begg and Mazumdar's Test) to 25 \% (Egger's Test) for continuous outcomes.
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-16-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
 
@@
 There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not.
-Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by 0.0768414 (the minimal increase is 0.0103761 for Schwarzer's Test).
+Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by 0.1825716 (the minimal increase is -0.0032246 for Schwarzer's Test).
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue May  7 13:05:39 2019
+% Tue May 21 16:14:47 2019
 \begin{table}[ht]
@@
   \hline
-egger.schwarzer & 0.87 & 0.39 \\ 
-  egger.peter & 0.89 & 0.51 \\ 
-  egger.rucker & 0.88 & 0.48 \\ 
-  egger.harbord & 0.93 & 0.76 \\ 
-  schwarzer.peter & 0.89 & 0.29 \\ 
-  schwarzer.rucker & 0.88 & 0.34 \\ 
-  schwarzer.harbord & 0.92 & 0.51 \\ 
-  rucker.peter & 0.92 & 0.67 \\ 
-  harbord.peter & 0.91 & 0.52 \\ 
+egger.schwarzer & 0.73 & 0.23 \\ 
+  egger.peter & 0.75 & 0.37 \\ 
+  egger.rucker & 0.75 & 0.34 \\ 
+  egger.harbord & 0.79 & 0.51 \\ 
+  schwarzer.peter & 0.81 & 0.26 \\ 
+  schwarzer.rucker & 0.81 & 0.25 \\ 
+  schwarzer.harbord & 0.86 & 0.47 \\ 
+  rucker.peter & 0.87 & 0.64 \\ 
+  harbord.peter & 0.84 & 0.50 \\ 
    \hline
@@
   \hline
-thomson.egger & 0.89 & 0.69 \\ 
-  thomson.begg & 0.82 & 0.47 \\ 
-  egger.begg & 0.79 & 0.36 \\ 
+thomson.egger & 0.85 & 0.69 \\ 
+  thomson.begg & 0.77 & 0.47 \\ 
+  egger.begg & 0.73 & 0.36 \\ 
    \hline
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-25-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-22-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-26-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-23-1}
 
@@
 
+\section{Transformation between effect sizes}
+Binary and continuous outcome measures can both be transformed into correlations and fishers z-scaled correlations in order to be compared.
+
 \section{Heterogeneity}
@@
 This is called between study variation in contrast to within study variation (noise).
+Let $\theta$ be a log odds ratio.
+A standardized mean difference $d$ (also known as Cohen's $d$) is calculated by multiplying $\theta$ with $\sqrt{3}/\pi$.
+\\
+We get from a standardized mean difference $d$ to a correlation $r$ by using 
+\begin{align}
+r &= \frac{d}{\sqrt{d^2 + a}} \nonumber
+\end{align}
+where $a$ is a correction factor if $n_t \neq n_c, a = (n_c + n_t)^2 / n_c n_t$
 
@@
 
-corresponding to a standard random effects model.
+corresponding to a standard random effects meta-analysis.
 $\mu$ is the overall mean effect, $\sigma_{i}^2$ the within study variance and $\tau^2$ the between study variance.
@@
 \begin{align}
-y_{i}& = \beta_{0} + \beta{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \stackrel{\textrm{iid}}{\sim} N(0,1)  \ref{limitmeta.regression}
-\end{align}
-
-$\beta{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
-
-\begin{align}
-\mathbb{E}((y_{i} - \beta_{})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{if} \sqrt{v_{i}} \rightarrow \infty \\
+y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{v_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
+\end{align}
+
+$\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
+
+\begin{align}
+\mathbb{E}((y_{i} - \beta_{0})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{ if } \sqrt{v_{i}} \rightarrow \infty \label{limitmeta.infinitesample} \\
 \mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
@@
 \begin{align}
-y_{i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{s_{i}/M + \tau^2}) \label{limitmeta.regression}
+y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
 \end{align}

### 2019-05-26 report/chapter03.Rnw
After presentation update

@@
 
-file.cont <- "mly.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-  load(file.path(PATH_RESULTS, file.cont))
-} else {
-  data.cont <- mly.cont(data.ext, 0.05, min.study.number = 2)
-  save(data.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.bin <- "mly.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-  load(file.path(PATH_RESULTS, file.bin))
-} else {
-  data.bin <- mly.bin(data.ext, 0.05, min.study.number = 2)
-  save(data.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-load(file.path(PATH_RESULTS, file = "mly.RData"))
 load(file.path(PATH_RESULTS, file = "data.processed.RData"))
@@
 require(gridExtra)
+require(xtable)
 @
@@
 
-<<echo = FALSE, warning =FALSE>>=
-#Merge comparisons with meta-analysis result:
-mly.tomerge <- mly %>% select(meta.id, sig.Q, n.sig.type, n.sig.fishersz, sig.fixef, sig.ranef, sig.ranef.hkn)
-
-data.mly <- merge(x = data.ext, y = mly.tomerge, by = c("meta.id")) #ideally, 278626 comparisons ( = sum(mly$n)), 
-# but 300831 (18261 have smaller sample size than mly, but same meta.id)
-
-data.mly <- data.mly %>% filter(total1 > 11 & total2 > 11) #Now 282550
-
-sig.meta.c <- data.mly %>% select(sig.type, sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
-  gather(key = "meta.analysis.method", value = "sig.meta.analysis") %>% mutate(sig.meta.analysis = factor(sig.meta.analysis))
-
-sig.meta.count.c <- sig.meta.c %>% 
-  group_by(sig.meta.analysis, meta.analysis.method) %>% count()
-
-sig.meta.c <- sig.meta.c %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
-  geom_bar() + coord_flip() +
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("meta.nonsig", "meta.sig")) +
-  annotate("text", x = sig.meta.count.c[sig.meta.count.c$sig.meta.analysis == 0,]$meta.analysis.method, y = 100000, 
-           label = paste(sig.meta.count.c[sig.meta.count.c$sig.meta.analysis == 0,]$n, "nonsig."), 
-           color = "white")
-
-#Change in significance after meta-analysis, separated by significant effect size estimate
-sig.meta <- data.mly %>% 
-  select(meta.id, study.id, sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
-  gather(key = "meta.analysis.method", value = "sig.meta.analysis", sig.fixef:sig.ranef.hkn) %>% mutate(sig.meta.analysis = factor(sig.meta.analysis))
-
-# duplicate.studies <- data.mly %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr, study.name) %>% 
-#   count() %>% filter(n > 1) #Merging is not possible for these since studies bear multiple results, but are not distinguishable and are multiplied while merging.
-
-sig.meta.plot <- merge(y = select(data.ext, meta.id, study.id, sig.type), 
-                       x = sig.meta, by = c("meta.id", "study.id")) %>% 
-  mutate(sig.type = factor(sig.type))
-
-sig.meta.count <- sig.meta.plot %>% 
-  group_by(sig.meta.analysis, meta.analysis.method, sig.type) %>% count()
-
-sig.meta.plot1 <- sig.meta.plot %>% filter(sig.type == 1) %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
-  geom_bar() + coord_flip() + ggtitle("Significant studies") +
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("non-significant", "significant")) +
-  annotate("text", x = sig.meta.count[which(sig.meta.count$sig.type == 1)[1:3],]$meta.analysis.method, y = 20000, 
-           label = paste(sig.meta.count[which(sig.meta.count$sig.type == 1)[1:3],]$n, "changed to nonsig."), 
-           color = "white")
-
-nonsig.meta.plot <- sig.meta.plot %>% filter(sig.type == 0) %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
-  geom_bar() + coord_flip() + ggtitle("Non-significant studies") +
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("non-significant", "significant")) +
-  annotate("text", x = sig.meta.count[which(sig.meta.count$sig.type == 0)[4:6],]$meta.analysis.method, y = 100000, 
-           label = paste(sig.meta.count[which(sig.meta.count$sig.type == 0)[4:6],]$n, "changed to sig."), 
-           color = "white")
-
-#Change in significance after meta-analysis, separated by significant heterogeneity
-sig.meta.Q <- data.mly %>% 
-  select(meta.id, sig.Q, sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
-  gather(key = "meta.analysis.method", value = "sig.meta.analysis", sig.fixef:sig.ranef.hkn) %>% 
-  mutate(sig.meta.analysis = factor(sig.meta.analysis))
-
-sig.meta.count.Q <- sig.meta.Q %>% 
-  group_by(sig.meta.analysis, meta.analysis.method, sig.Q) %>% count()
-
-sig.meta.Q1 <- sig.meta.Q %>% filter(sig.Q == 1) %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
-  geom_bar() + coord_flip() + ggtitle("Significant heterogeneity Q studies") +
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("non-significant", "significant")) +
-  annotate("text", x = sig.meta.count.Q[which(sig.meta.count.Q$sig.Q == 1)[1:3],]$meta.analysis.method, y = 20000, 
-           label = paste(sig.meta.count.Q[which(sig.meta.count.Q$sig.Q == 1)[1:3],]$n, "nonsig."), 
-           color = "white")
-
-nonsig.meta.Q <- sig.meta.Q %>% filter(sig.Q == 0) %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
-  geom_bar() + coord_flip() + ggtitle("Non-significant heterogeneity Q studies") +
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("non-significant", "significant")) +
-  annotate("text", x = sig.meta.count.Q[which(sig.meta.count.Q$sig.Q == 0)[1:3],]$meta.analysis.method, y = 100000, 
-           label = paste(sig.meta.count.Q[which(sig.meta.count.Q$sig.Q == 0)[1:3],]$n, "nonsig."), 
-           color = "white")
-
-p.secondary.over.meansig <- mly %>% filter(NA.sig.type != 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
-  geom_density(na.rm = T, position = "fill") + 
-  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-@
-
-\section{Meta-analysis}
-The data at hand is composed of over 400,000 results with balanced sample size $n > 24$.
+% 
+% \section{Meta-analysis}
+% The data at hand is composed of over 400,000 results with balanced sample size $n > 24$.
 The significance of the p-values of treatment effect estimates was calculated for all results in the dataset with acceptable sample size and outcome measures as odds ratios, peto odds ratios, risk ratios, risk differences and mean and standardized mean differences.
-
-%Significance over time? Chunck 1
-
-The results that can be pooled are analysed by fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis with Hartung-Knapp method.
-
-\vspace{0mm}
-In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e.
+% 
+% %Significance over time? Chunck 1
+% 
+% The results that can be pooled are analysed by fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis with Hartung-Knapp method.
+% 
+% \vspace{0mm}
+% In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e.
 if studies were not unique in the dataset with respect to their experimental setup).
 The significance of the treatment effect (primary significance) in a single result is then compared to the significance of the pooled treatment effect (secondary significance).
-In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
+% In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
 The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure.
 The colors indicate the overall fraction of rejected or accepted null-hypotheses of no treatment effect.
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-plot(sig.meta.c)
-@
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance}
-\end{figure}
-
-What has been found is that even the meta-analysis that for all meta-analysis methods, the amount of secondary significance is higher than the amount of primary significance.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% #plot(sig.meta.c)
+% @
+% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
+% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+% \label{primary.secondary.significance}
+% \end{figure}
+% 
+% What has been found is that even the meta-analysis that for all meta-analysis methods, the amount of secondary significance is higher than the amount of primary significance.
 Thus more primarily non-significant results can be attached to a secondarily significant result than vice-versa.
-
-\vspace{0mm}
-To illustrate this, the fraction of studies with significant primary treatment effect and primary non-significant treatment effect can be plotted separately (Figure \ref{primary.secondary.significance.sep.sig}).
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-grid.arrange(sig.meta.plot1, nonsig.meta.plot, ncol= 1)
-@
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
+% 
+% \vspace{0mm}
+% To illustrate this, the fraction of studies with significant primary treatment effect and primary non-significant treatment effect can be plotted separately (Figure \ref{primary.secondary.significance.sep.sig}).
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% #grid.arrange(sig.meta.plot1, nonsig.meta.plot, ncol= 1)
+% @
+% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
 The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance}
-\end{figure}
-
-It can be seen that the extent of overlap between primary and secondary significance varies between meta-analysis.
+% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+% \label{primary.secondary.significance}
+% \end{figure}
+% 
+% It can be seen that the extent of overlap between primary and secondary significance varies between meta-analysis.
 A considerable amount of both primary significant and primary non-significant results are overruled by meta-analysis hypothesis tests.
-
-The amount of significant heterogeneity in the results used by the meta-analyses is \Sexpr{length(which(mly$sig.Q == 0))} and corresponds to \Sexpr{(length(which(mly$sig.Q == 0))/ dim(mly)[1])*100}\% of the total number of meta-analyses.
-
-%Comparison of significance separated for significant Q? Chunck 2
-
-%Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5
+% 
+% 
+% The amount of significant heterogeneity in the results used by the meta-analyses is \Sexpr{length(which(mly$sig.Q == 0))} and corresponds to \Sexpr{(length(which(mly$sig.Q == 0))/ dim(mly)[1])*100}\% of the total number of meta-analyses.
+% 
+% %Comparison of significance separated for significant Q? Chunck 2
+% 
+% %Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5
 

### 2019-05-26 report/chapter03.tex
After presentation update

--- 2019-04-29 report/MSc_Report.tex
@@
-\documentclass[11pt,a4paper,twoside]{book}\usepackage[]{graphicx}\usepackage[]{color}
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
-
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
-
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
-
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-\usepackage{alltt}
-\input{header.sty}   % packages, layout and standard macros
-
-\usepackage{verbatim}
-\usepackage{tikz}
-\usepackage{amssymb}
-\usetikzlibrary{trees}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\begin{document}
-\input{title}
-
-\graphicspath{{./figure/}}
-\DeclareGraphicsExtensions{.pdf,.png}
-\setcounter{tocdepth}{1}
-
-\thispagestyle{empty}
-\begin{center}
-  \vspace*{6cm}{\bfseries\Huge
-  $p$-values:\\[5mm] their use, abuse and proper use \\[5mm]
-  illustrated with seven facets 
-  }
-  \vfill
-  \rm
-
-  \LARGE
-  M\"axli Musterli\\[12mm]
-
-  \normalsize
-  Version \today
-\end{center}
-\newpage
-\thispagestyle{empty}~
-\newpage
-\pagenumbering{roman}
-
-\thispagestyle{plain}\markboth{Contents}{Contents}
-\tableofcontents
-\setkeys{Gin}{width=.8\textwidth}
-
-\chapter*{Preface}
-\addtocontents{toc}{\protect \vspace*{13.mm}}
-\addcontentsline{toc}{chapter}{\bfseries{Preface}}
-\thispagestyle{plain}\markboth{Preface}{Preface}
-
-Howdy!
-
-\bigskip
-
-\begin{flushright}
-  Max Muster\\
-  June 2018
-\end{flushright}
-
-\addtocontents{toc}{\protect \vspace*{10mm}}
-
-\cleardoublepage
-\pagenumbering{arabic}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 01
-
-\chapter{Introduction}
-
-Meta-analysis is at the core of evidence based medicine because it allows to summarise evidence over multiple studies and provide a more broad view on success and effectivity of clinical treatments.
-The necessity of meta-analyses is also increased by the abundance of data and publications.
-Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to make decisions based on quantitative and scientific criteria.
-
-\vspace{0mm}
-For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention.
-However, the usefulness of meta-analysis does not restrict to clinical science, but to any empirical and quantiative science.
-
-\vspace{0mm}
-Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question.
-Meta-analysis can be applied to all studies that are approximately identical in their experimental setup and the way the outcome of the experiments is measured.
-In systematic reviews where meta-analyses are used, the conclusions are most often strongly based on the results and the interpretation of the meta-analysis.
-
-\vspace{0mm}
-However, there are problems that potentially limit the validity of meta-analysis; the number of studies available can be incomplete or the results of the studies can be biased.
-Some of those problems can be solved or asserted by special statistical methods.
-
-\subsection{Small Study Effects or Publication Bias}
-When study sample size decreases, the probability of extreme and missleading results in a study increases.
-This becomes a problem if results are selectively published, and therefore available, based on their results.
-When this is the case, one speaks of a small study effect or of ``Publication bias''.
-
-\vspace{0mm}
-The issue has been discussed extensively in the last years, most often in the context of what has came to be known as the replication crisis.
-The reasons for small study effects are manifold, but originate most often in the myopical acting of agents in science and the lack of statistical education.
-Studies are reported by scientists, published by journals and noticed by readers more often if their findigs are positive and find e.g.
-a substantive difference or effect.
-When doing a meta-analysis, one again obtains biased results.
-
-\vspace{0mm}
-The reason why that is less of an issue for larger studies is that extreme results are in general less likely and that due to larger effort, a result is published although there has been no clear and positive findings.
-
-\vspace{0mm}
-While there is generally no way to assert poor study quality, small study effect can in principle be asserted and corrected for statistically.
-This masters thesis will mainly be about statistical methods to detect and adjust for small study effects.
-It can furthermore be divided in two parts:
-\begin{itemize}
-\item Methodological part: Collection and discussion of statistical tests and correction methods for small study effects.
-\item Applied part: Application of the methods to studies of the Cochrane Library of systematic Reviews. Subsequent discussion of the implications
-of the results for clinical science.
-\end{itemize}
-
-In contrast to simulation studies, it is not possible to assess critical properties of the methods such as the power of a test, since the truth is not known.
-But based on the amount of data, one can of course try to make extrapolation to tendencies in clinical science in general.
-Moreover, it is still interesting to see how the methods behave in general, especially with respect to each other.
-It may, as an example, be possible to answer the question which statistical test is most conservative and which pooling method is most optimistic on average.
-Comparison with results from simulations may allow to speculate about the reasons when simulation and real world results diverge.
-
-\subsection{Cochrane and the Cochrane Database of Systematic Reviews}
-The Cochrane Organization has specialized on systematic reviews in clinical science.
-It publishes and maintains a library with a large number of systematic reviews that are available in some countries to the public.
-
-\vspace{0mm}
-The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite).
-
-\vspace{0mm}
-The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests.
-This might further improve the validity and precision of findings and conclusions that have been made based on this data.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 02
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}mutate\_"{}): no applicable method for 'mutate\_' applied to an object of class "{}function"{}}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pb.meta.merge(meta.bin, meta.cont): could not find function "{}pb.meta.merge"{}}}\end{kframe}
-\end{knitrout}
-
-\chapter{The Cochrane Dataset}
-
-\section{Cochrane Systematic Reviews}
-As has been mentioned before, the Cochrane Group has specialized on systematic reviews in clinical science.
-Certain knowledge of standards and principles of the Cochrane Group may help to assess the quality and the properties of the dataset.
-The following information stems from the Cochrane Handbook for Systematic Reviews \citep{cochrane.handbook}.
-
-\vspace{0mm}
-The definition of a systematic review is that it ``attempts to collate all empirical evidence that fits pre-specified eligibility criteria in order to answer a specific research question.'' Thus, the ``key properties of a review are'':
-
-\begin{itemize}
-\item``a clearly stated set of objectives with pre-defined eligibility criteria for studies''
-\item ``an explicit, reproducible methodology''
-\item ``a systematic search that attempts to identify all studies that would meet the eligibility criteria''
-\item ``an assessment of the validity of the findings of the included studies, for example through the assessment of risk of bias''
-\end{itemize}
-
-At the end of a systematic review, ``a systematic presentation, and synthesis, of the characteristics and findings of the included studies'' is done.
-
-\vspace{0mm}
-53 Cochrane Review Groups prepare and maintain the reviews within specific areas of health care.
-A group consists of ``researchers, healthcare professionals and people using healthcare services (consumers)''.
-
-\vspace{0mm}
-The groups are supported by Method Groups, Centres and Fields.
-The Cochrane Method Groups aim to discuss and consult the groups in methodological questions concerning review preparation.
-The Centres play a main role in training and support of the Groups.
-The Fields are responsible for broad medical research areas and follow priorities in those areas by advice and control of the groups.
-
-\vspace{0mm}
-The first step in a review is writing a protocoll, specifying the research question, the methods to be used in literature search and analysis and the eligibility criteria of the study.
-Changes in protocolls are possible but have to be documented and the protocol is published in advance of the publication of the full review.
-The choices of methodology as well as the changes should not be made ``on the basis of how they affec the outcome of the research study''.
-
-\vspace{0mm}
-In order to avoid potential conflicts of interests, there is a code of conduct that all entities of the Cochrane Organization have to agree on: conflicts of interest must be disclosed and possibly be forwarded to the Cochrane Centre, and participation of review authors in the studies used have to be acknowledged.
-Additionally, a Steering Group publishes a report of potential conflicts of interests based on information about external funding of Cochrane Groups.
-
-\vspace{0mm}
-In order for keeping the reviews up-to-date, they are revised in a two-year cicle with exceptions.
-In addition to inclusion of new evidence in a field, the revision and maintenance process may as well includes change in analysis methods.
-This can reflect some advance in clinical science as for example new informations about important subgroups, as well as new methods for conducting a Cochrane Review.
-However, there are no clear guidelines and the Cochrane Groups are free in the rate and extent of up-dating their reviews.
-
-\subsection{Methods for Cochrane Reviews}
-A research question defines the following points: ``the types of population (participants), types of interventions (and comparisons), and the types of outcomes that are of interest''.
-From the research question, ususally the eligibility criteria follow.
-Usually, outcomes are not part of eligibility criteria, except for special cases such as adverse effect reviews.
-
-\vspace{0mm}
-The type of study is an important eligibility criterium.
-The Cochrane Collaboration focuses ``primarily on randomized controlled trials'', and also, the methods of study identification in literature search are focused on randomized trials.
-Furthermore, study characteristics such as blinding of study operators with respect to treatment and cluster-randomizing might be additional eligibility criteria which have to be chosen by the review authors.
-
-\vspace{0mm}
-After having specified the eligibility criteria, studies have to be collected.
-The central idea of systematic reviews, and also meta-analyses, is that the collected studies are a random sample of a population of studies, i.e.
-that they are representative and can be used to assess population properties.
-Therefore, the search process is crucial, as a selective search result may impose bias on the sample of studies available, making it a non-random sample.
-For this purpose, the Cochrane Groups are advised to go beyond MEDLINE !!cite!!, because a search restricted to it has been shown to deliver only 30\% to 80\% of available studies.
-``Time and budget restraints require the review author to balance the thoroughness of the search with efficiency in use of time and funds and the best way of achieving this balance is to be aware of, and try to minimize, the biases such as publication bias and language bias that can result from restricting searches in different ways.'' It is important to note that not only studies, but also study reports are occasionally used in the reviews, as they may provide useful information.
-
-\vspace{0mm}
-There are different sources that are being used to search for studies. 
-\begin{itemize}
-\item The Cochrane Central Register of Controlled Trials is a source of reports of controlled trials.
-``As of January 2008 (Issue 1, 2008), CENTRAL contains nearly 530,000 citations to reports of trials and other studies potentially eligible for inclusion in Cochrane reviews, of which 310,000 trial reports are from MEDLINE, 50,000 additional trial reports are from EMBASE and the remaining 170,000 are from other sources such as other databases and handsearching.'' It includes citations published in many languages, citations only available in conference proceedings, citations from trials registers and trials results registers.
-\item MEDLINE.
-MEDLINE includes over 16 million references to journal articles.
-5,200 journals publishing in 27 languages are indexed for MEDLINE.
-PubMed gives access to a free version of MEDLINE with up-to-date citations.
-NLM gateway such as the Health Services Research Project, Meeting Abstracts and TOXLINE Subset for toxicology citations allows for search in both databases together with additional data from the US National Library of Medicine.
-\item EMBASE.
-4,800 Journals publishing in 30 languages are indexed to EMBASE, which includes more than 11 million records from 1974 onwards.
-EMBASE.com also includes 7 million unique records from MEDLINE (1966 up to date) together with its own records.
-Additionally, EMBASE Classic allows access to digitized records from 1947 to 1973.
-EMBASE and MEDLINE each have around 1,800 journals not indexed in the other databse.
-\item Regional or national and subject specific databases can additionally be consulted and often provide important information. Financial considerations may limit the use of such databases.
-\item General search engines such as Google Scholar, Intute and Turning Research into Practice (TRIP) database can be used.
-\item Citation Indexes.
-The database lists articles published in around 6,000 Journals with articles in which they have been cited and is available online as SciSearch.
-This form of search is known as cited reference searching.
-\item Dissertation sources. Dissertations are often listed in MEDLINE or EMBASE but one is advised to also search in specific dissertation sources.
-\item Grey Literature Databases.
-Approximately 10\% of the results in the Cochrane Database stems from conference abstracts and other grey literature.
-The Institute for Scientific and Technical Information in France provides access to entries of the previously closed System for Information on Grey Literature database of the European Association for Grey Literature Exploitation).
-Another source is the Healthcare Management Information Consortium (HMIC) database containing records from the Library and Information Services department of the Department of Health (DH) in England and the King's Fund Information and Library Service.
-The National Technical Information Service (NTIS) gives access to the results of US and non-US government-sponsored research, as well as technical report for most published results.
-References from newsletters, magazines and technical and annual reports in behavioral science, psychology and health are provided in the PsycEXTRA database which is linked to PsycINFO database.
-\end{itemize}
-
-\subsection{Structure and Content}
-The dataset consists of 5016 systematic reviews from the Cochrane Library with 52995 studies and 463820 results.
-A result compares clinical or medical interventions or treatments.
-Each study provides (multiple) results of clinical interventions.
-
-In Table \ref{barbiturate.row}, two results from a systematic review about effects of barbiturates are shown as they are given in the dataset.
-As can be seen, the result is further specified by the variables in the columns.
-The comparison variable specifies what treatments or interventions are compared, the outcome variable how it is compared, and the subgroup variable (not given in table) indicates if the result belongs to a certain subgroup.
-Here, the result is of a binary outcome, so the events in the barbiturate treatment group and the total number of participants are given in columns ``Events'' and ``Total'' and the number of events in the control group ``Events\_c'' and participants ``Total\_c''.
-Events denotes here number of deaths at the end of follow up.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:57:33 2019
-\begin{table}[ht]
-\centering
-\begingroup\scriptsize
-\begin{tabular}{lllrrrr}
-  \hline
-Study & Comparison & Outcome & Events & Total & Events\_c & Total\_c \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11 & 41 & 11 & 41 \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14 & 27 & 13 & 26 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Example of two results as given in the dataset.
-Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
-Further descriptive variables have been ommitted}
-\label{barbiturate.row}
-\end{table}
-
-A complete listing of the variables of a result is given in Table \ref{variable}.
-They can roughly be separated into variables that specify the review in which the result is contained and variables that specify the result itself (separated by a horizontal line in Table \ref{variable}).
-
-\begin{table}[ht]
-  \begin{center}
-    \begin{tabular}{l l}
-      \textbf{Variable} & \textbf{Description}\\
-      \hline
-      \textbf{file.nr} & The number of the file from which the review data has been \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
-      \textbf{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
-      \textbf{file.index} & Internal index of the file in the Cochrane library.\\
-      \textbf{file.version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
-      %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
-      \hline
-      \textbf{study.name} & Name of the study to which the result belongs\\
-      \textbf{study.year} & Year in which the study was published\\
-      \hline
-      \textbf{comparison.name/.nr} & Specification of the interventions compared in the study  \\ &and a unique number for the comparison\\
-      \textbf{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ &and a unique number for the outcome\\
-      \textbf{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a \\ &unique number for the subgroup\\
-      \textbf{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
-      \textbf{effect} & Measure of the effect given in the quantity denoted by \\ &``outcome measure''.\\
-      \textbf{se} & Standard error of the measure of the effect,\\
-      \textbf{events1/events2} & The counts of patients with an outcome \textit{if}\\ &measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
-      \textbf{total1/total2} & Number of patients in groups.\\
-      \textbf{mean1/mean2} & Mean of patient measurements \textit{if} outcome is continuous.\\
-      \textbf{sd1/sd2} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
-    \end{tabular}
-  \caption{Dataset variable names and descriptions  \label{variable}}
-
-  \end{center}
-\end{table}
-
-Results are part of studies that are again part of a (systematic) review. This structure of a review is shown in Figure \ref{review}.
-
-\begin{figure}
-\tikzstyle{every node}=[draw=black,thick,anchor=west]
-\tikzstyle{selected}=[draw=red,fill=red!30]
-\tikzstyle{optional}=[dashed,fill=gray!50]
-\begin{tikzpicture}
-[grow = right, anchor = west, 
-  growth parent anchor=east, % added code
-  parent anchor=east]
-  \node {Review} [edge from parent fork right]
-    child { node {Comparison 2}
-      child { node {Outcome 2}}
-      child { node {Outcome 1}
-        child { node {Subgroup 2}}
-        child { node {Subgroup 1}
-          child  { node {Result 2}}
-          child  { node {Result 1}}
-          }}
-    }
-    child [missing] {}		
-    child { node {Comparison 1  }};
-\end{tikzpicture}
-\caption{Structure of a hypothetical review with two different comparisons\label{review.structure}}
-\label{review.structure}
-\end{figure}
-
-\vspace{0mm}
-The structure of a review will now be outlined based on an example of the dataset.
-Lets consider the previously mentioned barbiturate and head injury review.
-The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates''.
-Since there are arguments for and against use of barbiturates, the authors of the review did a comprehensive literature search and collected all available study findings.
-
-\vspace{0mm}
-The review comprises five studies in total.
-Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental, which would be the comparison to speak in the previously introduced notion.
-The studies have different outcomes, for example, death or death and severe disability at follow up.
-One study split up outcomes for patients with and without haematoma, which would be subgroups.
-
-\vspace{0mm}
-The complete listing of outcomes is in table \ref{barbiturates}.
-The table also gives an illustration of the variety of data that can be included in a review.
-We have for example continuous (mean body temperature) and binary outcome data (death).
-Additionally to primary and secondary outcomes, often also dropouts and adverse effects are included in a review.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:57:33 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-Study & Comparison & Outcome \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
-  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
-  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
-  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given} 
-\label{barbiturates}
-\end{table}
-
-It is important not to confuse results with studies. A study can contribute multiple results to a systematic review, for example, primary and secondary outcomes and adverse effects.
-
-\vspace{0mm}
-Information about missing values in the dataset is given in Table \ref{missing}.
-For variables as research subject, outcome and subgroup name and event counts there are no missing values.
-The relative amount of missing values is very low except for study years.
-In the case of continuous outcomes, the cases have been counted were effect sizes and standard errors of effect sizes are not available.
-This means that neither mean values of groups nor mean differences are given, or that neither standard deviation nor standard error is given for a result.
-Study years before 1920 and after 2019 have been counted as missing, as well as sample sizes below zero.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:57:33 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lr}
-  \hline
-  \hline
-Missing mean values and mean differences & 984 \\ 
-  Missing standard deviations and standard errors & 1300 \\ 
-  Missing sample sizes & 12173 \\ 
-  Missing study year & 44649 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Number of missing variables and measurements in the dataset} 
-\label{missing}
-\end{table}
-
-The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982).
-The median of the publication years is 2003, the mean 2006.13 and the quartiles are 1996 and 2008.
-Only a handful ($n$ = 18) have been published in 2018, none in 2019.
-No information is available concerning unpublished results and studies.
-
-\vspace{0mm}
-The results of a study are summarised in a result by a effect measure.
-This effect measure varies, depending on whether data is continuous, binary or time-to-event.
-The most abundant effect measures used are summarised in Table \ref{outcome.measure.frequencies}.
-One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the being some sort of discrete or binary outcomes, most often binary (> 65\%).
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:57:33 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-Outcome measure & n & Percentage \\ 
-  \hline
-Risk Ratio & 232583 & 50.1\% \\ 
-  Mean Difference & 102315 & 22.1\% \\ 
-  Odds Ratio & 49372 & 10.6\% \\ 
-  Std. Mean Difference & 40535 & 8.7\% \\ 
-  Peto Odds Ratio & 19122 & 4.1\% \\ 
-  Hazard Ratio & 6566 & 1.4\% \\ 
-  Risk Difference & 6234 & 1.3\% \\ 
-  Rate Ratio & 2283 & 0.5\% \\ 
-  other & 4810 & 1\% \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Frequencies of outcome measures among results. n denotes the total number 
-             of results with the outcome measure and percentage the percentage of the outcome measure,} 
-\label{outcome.measure.frequencies}
-\end{table}
-
-The sample sizes amongst results vary to some extent.
-There are 5\% of treatment group sample sizes that are smaller tha 8, the 5\% quantile.
-The first quartile is 22, the median 48, the mean 302.03 and the third quartile 119.
-The large difference between median and mean is caused by very large groups with over 2,000,000 participants.
-Analogously, the quantiles of the total sample size are: 5\% quantile = 15, first quartile = 44, median = 94 and third quartile = 229.
-The mean is 617.81.
-
-\vspace{0mm}
-The mean and median number of results per review are 12.42 and 7.
-There are 417 reviews with five or fewer results, and the quartiles are 16 and 102.
-Similarly, the number of reviews with a maximum of two studies included is 836, the mean study number is 12.42, the median 7 and the interquartile range 4 and 15.
-The discrepancy between mean and median is again due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxisfor preventing infection after cesarean section, with 95 studies and 1497 results in total.
-
-\vspace{0mm}
-For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome.
-More speicifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis since their research subject and experimental setup can be considered sufficiently homogeneous.
-%Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
-\vspace{0mm}
-The amount of studies that can be pooled for meta-analyses is of special interest in this masters thesis.
-Thus, the dataset is divided in groups whith identical experimental setup.
-The size of the group denotes how many results are included in a group.
-
-\vspace{0mm}
-Table \ref{repr.groups} shows the number of \textit{groups} of groups with equal or more than $n$ results.
-Practically, this means that a given number of meta analyses can be performed with each having at least $n$ results.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:57:33 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
-n & Number of groups & Cumulative sum of groups \\ 
-  \hline
-1 & 102344 & 186300 \\ 
-  2 & 31686 & 83956 \\ 
-  3 & 16072 & 52270 \\ 
-  4 & 9628 & 36198 \\ 
-  5 & 6444 & 26570 \\ 
-  6 & 4230 & 20126 \\ 
-  7 & 2961 & 15896 \\ 
-  8 & 2114 & 12935 \\ 
-  9 & 1592 & 10821 \\ 
-  10 & 1238 & 9229 \\ 
-  11 & 921 & 7991 \\ 
-  12 & 702 & 7070 \\ 
-  13 & 585 & 6368 \\ 
-  14 & 455 & 5783 \\ 
-  15 & 5328 & 5328 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Cumulative number of groups with number of reproduction trials >= n} 
-\label{repr.groups}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 % LaTeX file for Chapter 03
@@
 
-\section{Meta-analysis}
-The data at hand is composed of over 400,000 results with balanced sample size $n > 24$.
+% 
+% \section{Meta-analysis}
+% The data at hand is composed of over 400,000 results with balanced sample size $n > 24$.
 The significance of the p-values of treatment effect estimates was calculated for all results in the dataset with acceptable sample size and outcome measures as odds ratios, peto odds ratios, risk ratios, risk differences and mean and standardized mean differences.
-
-%Significance over time? Chunck 1
-
-It is possible to analyse all results that are not unique in their comparison, outcome and subgroup in the dataset by meta-analysis.
-So each study that has been repeated with respect to experimental setup is included.
-There are different meta-analys methods that can be applied, here, fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis using the Hartung-Knapp method are used.
-
-\vspace{0mm}
-In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e.
+% 
+% %Significance over time? Chunck 1
+% 
+% The results that can be pooled are analysed by fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis with Hartung-Knapp method.
+% 
+% \vspace{0mm}
+% In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e.
 if studies were not unique in the dataset with respect to their experimental setup).
-The significant of the treatment effect in a single result is then compared to the significance of the pooled treatment effect.
-In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
+The significance of the treatment effect (primary significance) in a single result is then compared to the significance of the pooled treatment effect (secondary significance).
+% In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
 The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure.
 The colors indicate the overall fraction of rejected or accepted null-hypotheses of no treatment effect.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}
-
-}
-
-\end{knitrout}
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance}
-\end{figure}
-
-One can visualise the fraction of studies with significant treatment effect separately for studies with significant primary treatment effect, and non-significant primary treatment effect, as done in Figure \ref{primary.secondary.significance.sep.sig}.
-It can be seen that primary significance and non-significance is often overruled when performing a meta-analysis.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-14-1}
-
-}
-
-\end{knitrout}
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% #plot(sig.meta.c)
+% @
+% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
+% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+% \label{primary.secondary.significance}
+% \end{figure}
+% 
+% What has been found is that even the meta-analysis that for all meta-analysis methods, the amount of secondary significance is higher than the amount of primary significance.
+Thus more primarily non-significant results can be attached to a secondarily significant result than vice-versa.
+% 
+% \vspace{0mm}
+% To illustrate this, the fraction of studies with significant primary treatment effect and primary non-significant treatment effect can be plotted separately (Figure \ref{primary.secondary.significance.sep.sig}).
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% #grid.arrange(sig.meta.plot1, nonsig.meta.plot, ncol= 1)
+% @
+% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
 The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance}
-\end{figure}
-
-The amount of significant heterogeneity in the results used by the meta-analyses is 53350 and corresponds to 81.5936377\% of the total number of meta-analyses.
-
-%Comparison of significance separated for significant Q? Chunck 2
-
-%Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5
+% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+% \label{primary.secondary.significance}
+% \end{figure}
+% 
+% It can be seen that the extent of overlap between primary and secondary significance varies between meta-analysis.
+A considerable amount of both primary significant and primary non-significant results are overruled by meta-analysis hypothesis tests.
+% 
+% 
+% The amount of significant heterogeneity in the results used by the meta-analyses is length(which(mly$sig.Q == 0)) and corresponds to (length(which(mly$sig.Q == 0))/ dim(mly)[1])*100\% of the total number of meta-analyses.
+% 
+% %Comparison of significance separated for significant Q? Chunck 2
+% 
+% %Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-16-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-5-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-6-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-8-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-9-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-10-1}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:58:07 2019
+% Tue May 21 16:11:40 2019
 \begin{table}[ht]
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-24-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-25-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-14-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-26-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-15-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-16-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-29-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-30-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-31-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-32-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 04
-
-\chapter{Methods}
-
-\section{Basic notation}
-The notation used here will be used throughout the chapter and exceptions will be noted.
-Let $i$ be the number of a study of a meta analysis with $n$ being the total number of studies.
-$y_{i}$ is then the effect size estimate (usually log odds ratio or mean difference) and $v_{i}$ the variance of the estimate of study $i$.
-$w_{i}$ is used for weights which are defined when necessary, and $\Delta$ usually denotes the summarized or pooled effect estimate of the meta-analysis, and $\eta$ the variance thereof.
-
-\vspace{0mm}
-In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
-
-\section{Heterogeneity}
-In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
-This is called between study variation in contrast to within study variation (noise).
-
-\vspace{0mm}
-The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
-Let $w_i$ be the inverse of the variance and $\Delta$ be a summarized effect estimate of your choice as for example a variance-weighted mean \ref{weighted.mean}.
-Then $Q$ can be calculated as in \ref{Q.heterogeneity}
-
-\begin{align}
-\Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
-\end{align}
-
-Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
-Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
-$1 - F(Q)$ will provide the $p$-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
-
-\vspace{0mm}
-Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
-For this purpose, $\tau^2$, the variance of true effects, can be calculated.
-$\tau^2$ is on the same scale as the effect size and reflects the absolute amount of dispersion.
-In practice, $\tau^2$ can be smaller than zero, then it is set to zero.
-
-\begin{align}
-C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
-\tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
-\end{align}
-
-The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
-Note that their estimate can differ substantially and consequently also the estimate of the pooled effect size estimate.
-
-\vspace{0mm}
-To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
-
-\begin{align}
-I^2 &= (Q - n + 1)/Q \label{I2.proportion}
-\end{align}
-
-There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
-
-\section{Meta Analysis}
-There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
-First the fixed effect meta-analysis will be explained.
-Note that both methods can be used for continuous or dichotomous outcomes.
-For more details about the methods, see chapter 11 and 12 in \citet{metaanalysis}
-
-\vspace{0mm}
-Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
-The pooled estimate $\Delta_{f}$ of the fixed effects model is then the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
-The variance $\eta_{f}$ is the reciprocal of the sum of the weights as shown in \ref{reciproce.variance}.
-
-\begin{align}
-\Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-\eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
-\end{align}
-
-The computation of random effects meta-analysis is more complicated.
-Random effects meta-analysis will give smaller studies with larger variance more weight in the pooled estimate.
-Shortly, the idea is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
-
-\vspace{0mm}
-The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
-It is used to calculate a new weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
-The variance of $\Delta_{r}$, $\eta_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
-
-\begin{align}
-v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
-\Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
-\eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
-\end{align}
-
-A p-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
-
-\begin{align}
-Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
-p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
-\end{align}
-
-\section{Small Study Effects Tests}
-One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
-If this is not given, one often speaks of publication bias.
-In fact, there can also be other reasons for this (see discussion section).
-A more appropriate term for the phenomenon is small study effect.
-If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
-
-\subsection{Continuous Outcome Tests}
-% Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. 
-% First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
-
-\subsubsection{Begg and Mazumdar: Rank Correlation Test}
-\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
-A standardized effect size $y_{i}^\star$ can be computed as in \ref{begg.stand.eff}.
-$v_{i}^\star$ is the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
-$\Delta_{f}$ is the pooled estimate for fixed effect estimate defined in \ref{weighted.mean}.
-
-\begin{align}
-y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff} \\
-v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} 
-\end{align}
-
-A rank correlation test based on Kendall's tau is then used.
-The pairs $(y_{i}^\star, v_{i}^\star)$ that are ranked in the same order are enumerated.
-Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (e.g.
-larger standardized effect size and smaller variance).
-Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
-
-\begin{align}
-Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
-\end{align}
-
-The changes in the case of ties are negligible \cite[410]{begg.ties}.
-
-\subsubsection{Egger's Test: Linear Regression Test}
-Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
-Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope.
-
-\vspace{0mm}
-If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
-The p-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
-
-\begin{align}
-p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
-\end{align}
-
-\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test}
-A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
-Let $\tau^2$ be equal to \ref{Tau.definition}.
-The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
-
-\begin{align}
-y_{i} \sim N(\beta_{0} + \beta{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
-\end{align}
-
-Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
-Analogous to Edger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta{0} = 0$.
-
-\subsection{Dichotomous Outcomes Tests}
-
-The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
-Consequently, the tests above will tend to reject the null-hypothesis too often, i.e.
-that they are not conservative enough.
-A number of solutions to this problem are existing in the literature.
-
-\subsubsection{Peters Test: Weighted Linear Regression Test}
-A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
-
-\vspace{0mm}
-Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
-
-\begin{align}
-y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
-v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
-\end{align}
-
-and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
-Instead of taking the variance as explanatory or independent variable in regression as in Egger's Test, the inverse of the total sample size $x_{i}$ is used, and the variance $v_{i}$ is used as a weight.
-The subsequent test procedure is then identical to Egger's test.
-
-\vspace{0mm}
-Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
-
-\subsubsection{Harbord's Test: Score based Test}
-A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
-The score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
-
-\begin{align}
-r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
-v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
-\end{align}
-
-Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
-Note that $r_{i}/v_{i}$ is also known as peto odds ratio.
-
-\subsubsection{Schwarzer's Test: Rank Correlation Test}
-\citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
-$\mathbb{E}(E_{t})$ and variance of $E_{t}$ are then estimated based on $e_{t}$.
-
-\vspace{0mm}
-The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
-
-\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
-The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let
-
-\begin{align}
-y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}}// 
-v_{i} = 1/4n_{t} + +/4n_{c}
-\end{align}
-
-Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances.
-
-\section{Small Study Effect Adjustment}
-\subsection{Trim and Fill}
-One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
-It is a nonparametric test based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
-%If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
-
-\vspace{0mm}
-The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
-First, $\Delta$ is estimated using a fixed or random effects model.
-Then, the $k$ effect size estimates with the smallest standard errors are trimmed, and $\Delta$ is estimated again.
-The procedure is repeated until $k$ is 0 and the funnel plot is symmetric.
-The total number of missing studies is then mirrored with respect to the final effect size estimate $\Delta$, and $\Delta$ and its standard error is then computed to obtain an unbiased estimate.
-
-\subsection{Copas Selection Model}
-
-A method proposed in \cite{Copas1,Copas2,Copas3} assumes that there is a population of studies of which only a part has been published dependent on the variance and size of their estimated effects.
-Studies with small variance and large effect sizes are more likely to be published than studies with large variance and small effect sizes.
-Note that small effect size means here a treatment effect close to the control effect.
-
-Let $y_i$ be the effect size estimate of study $i$. Then
-
-\begin{align}
-y_{i} \sim N(\mu_{i}, \sigma_{i}^2) \\
-\mu_{i} \sim N(\mu, \tau^2)
-\end{align}
-
-corresponding to a standard random effects model.
-$\mu$ is the overall mean effect, $\sigma_{i}^2$ the within study variance and $\tau^2$ the between study variance.
-This is the \textit{population model}.
-
-\vspace{0mm}
-The \textit{selection model} is defined as follows. Suppose a selection of studies with reported standard errors $s$ (likely different from $\sigma$). Only a proportion
-
-\begin{align}
-P(\textrm{select}|s) &= \Phi(a + b/s) \label{copas.selection1}
-\end{align}
-
-of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
-\ref{copas.selection1} can be rewritten as
-
-\begin{align}
-z = a + b/s + \delta \label{copas.selection2}
-\end{align}
-
-with $\delta \sim N(0,1)$. The study with standard error $s$ is only selected if $z$ is positive. Therefore, the larger $z$, the more likely the study is selected.
-Combining population and selection model for study $i$, we have
-
-\begin{align}
-y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \\
-\mu_{i} \sim N(\mu, \tau^2) \\
-z_{i} = a + b/s_{i} + \delta_{i}
-\end{align}
-
-where $(\epsilon_{i}, \delta_{i})$ are standard normal residuals and jointly normal with correlation $\rho = cor(y_{i}, z_{i})$.
-Every given study $i$ in the meta-analysis has $z_{i} > 0$.
-If $\rho$ is large and positive and $z_{i} > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_{i}$ and $\delta_{i}$.
-Thus, the true mean $\mu$ is likely to be overestimated.
-
-\vspace{0mm}
-Let $u = a + b/s$, $\lambda(u) = \phi(u)/\Phi(u)$ ($\phi$ is the standard normal density function) and $\tilde{\rho} = \sigma/\sqrt(\tau^2 + \sigma^2) \rho$.
-The probability of a study being selected is
-
-\begin{align}
-P(\textrm{select}|s, y) = P(a,b,s,y) = \Phi(\frac{u + \tilde{\rho}((y - \mu)/\sqrt(\tau^2 + \sigma^2))}{\sqrt{1 - \tilde{\rho^2}}})
-\end{align}
-
-It can also be shown that the expected value
-
-\begin{align}
-\mathbb{E}(y|s, select) = \mu + \rho\sigma\lambda(u) \label{copas.expectation}
-\end{align}
-
-which shows that the expected value for a study is larger for larger $\sigma$.
-
-\vspace{0mm}
-One can compute a likelihood function based on the distribution of $y$ conditional on $z > 0$.
-The likelihood can be maximized for any given pair $a,b$ (can not be estimated since the number of missing studies is not known), and a maximum likelihood estimate $\hat{\mu}$ for the true mean $\mu$ can be obtained.
-One can then perform a sensitivity analysis.
-First, one looks how $\hat{\mu}$ changes for different values of $a,b$.
-One can then compare the fitted values in \ref{copas.expectation} with the real values.
-To test the fit of the model (while keeping all other parts unchanged), the model can be extended in the following way :
-
-\begin{align}
-y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
-\end{align}
-
-If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
-Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
-The p-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
-
-\vspace{0mm}
-To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
-
-\vspace{0mm}
-In practice, only a range of values for $a,b$ are reasonable.
-For those values, the quantities above can be calculated and illustrated.
-Values for $\mu$ that have p-values over a predefined significance threshold can be used for inference of the effect size.
-
-\subsection{Adjustment by Regression}
-There are multiple ways to adjust for small study effects by regression. The general idea is to regress the effect size of a study with a variance of zero based on the given effects and variances.
-
-\citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
-Similarly to what has been seen in Copas selection model, we let $y_{i}$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_{i}}$ as in \ref{limitmeta.regression}.
-
-\begin{align}
-y_{i}& = \beta_{0} + \beta{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \stackrel{\textrm{iid}}{\sim} N(0,1)  \ref{limitmeta.regression}
-\end{align}
-
-$\beta{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
-
-\begin{align}
-\mathbb{E}((y_{i} - \beta_{})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{if} \sqrt{v_{i}} \rightarrow \infty \\
-\mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
-\end{align}
-
-After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test.
-
-\vspace{0mm}
-To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
-
-\begin{align}
-y_{i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{s_{i}/M + \tau^2}) \label{limitmeta.regression}
-\end{align}
-
-Letting $M \rightarrow \infty$, we obtain:
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
-\end{align}
-
-Note that:
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
-\end{align}
-
-$\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
-
-\begin{align}
-\epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
-\end{align}
-
-Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-\end{align}
-
-By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
-
-% \begin{align} \label{cox reg}
-% P(Y < y|\mathbf{x}) = 1 - exp(-exp(h(y) - (\mathbf{x})^\top\beta)
-% \end{align}
-% 
-% See \cite{hothorn} for further information. It specifies the instantaneous risk of an event at time t to be
-% 
-% \begin{align}
-% \lambda_{0}(t)exp((\mathbf{x})^\top\beta) \nonumber
-% \end{align}
-% 
-% The model is regarded as a semi parametric model since it includes the covariates in a linear fashion but leaves the baseline hazard $\lambda_{0}(t)$ unspecified.
-The factor $exp((\mathbf{x})^\top\beta)$ has the interpretation of a hazard ratio between the reference with $\mathbf{x} = 0$.
-The formal definition of the hazard is
-% 
-% \begin{align}
-% h(t) = \lim_{h \to 0} \frac{P(t < T < t + h| T > t)}{h}
-% \end{align}
-% 
-% 
-% \begin{align} \label{generalized linear model}
-% \mathbf{Y}{_{ij}}|U{_i},\epsilon{_{ij}} = (1,x{_i}^\top)\beta + U{_i} + \epsilon{_{ij}}
-% \end{align}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 05
-
-\chapter{Conclusions}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-% LaTeX file for Chapter 01
-
-\chapter{Appendix}
-
-Maybe some R code here, probably a \rr{sessionInfo()}
-
-\cleardoublepage
-\phantomsection
-\addtocontents{toc}{\protect \vspace*{10mm}}
-\addcontentsline{toc}{chapter}{\bfseries Bibliography}
-
-\bibliographystyle{mywiley} 
-\bibliography{biblio}
-
-\cleardoublepage
-
-\end{document}

### 2019-05-26 report/chapter04.Rnw
Präsentation
Presentation update
After presentation update

@@
 In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
+
+\section{Transformation between effect sizes}
+Binary and continuous outcome measures can both be transformed into correlations and fishers z-scaled correlations in order to be compared.
+Let $\theta$ be a log odds ratio.
+A standardized mean difference $d$ (also known as Cohen's $d$) is calculated by multiplying $\theta$ with $\sqrt{3}/\pi$.
+The variance of the standardized mean difference is attained as $v_d = v_\theta \sqrt{3}/\pi$.\\
+We get from a standardized mean difference $d$ to a correlation $r$ by using 
+\begin{align}
+r &= \frac{d}{\sqrt{d^2 + a}} \nonumber
+\end{align}
+where $a$ is a correction factor if $n_t \neq n_c, a = (n_c + n_t)^2 / n_c n_t$. The variance of $r$ is computed by using 
+\begin{align}
+v_r &= v_d
+\end{align}
+
+Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $v_z$ by using
+\begin{align}
+z &= 0.5 \ln(\frac{1 + r}{1 - r}) \nonumber
+v_z &= \frac{1}{n-3}
+\end{align}
 
@@
 \begin{align}
-y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
+y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{v_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
 \end{align}

### 2019-05-26 code/Metaly.R

@@ -599,5 +599,86 @@ sig.meta.Q %>% filter(sig.Q == 0) %>%  ggplot(aes(x = meta.analysis.method, fill
 
 
 
+######Report Backup:
+#Merge comparisons with meta-analysis result:
+mly.tomerge <- mly %>% select(meta.id, sig.Q, n.sig.type, n.sig.fishersz, sig.fixef, sig.ranef, sig.ranef.hkn)
 
+data.mly <- merge(x = data.ext, y = mly.tomerge, by = c("meta.id")) #ideally, 278626 comparisons ( = sum(mly$n)), 
+# but 300831 (18261 have smaller sample size than mly, but same meta.id)
+
+data.mly <- data.mly %>% filter(total1 > 11 & total2 > 11) #Now 282550
+
+
+
+sig.meta.c <- data.mly %>% select(sig.type, sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
+  gather(key = "meta.analysis.method", value = "sig.meta.analysis") %>% mutate(sig.meta.analysis = factor(sig.meta.analysis))
+
+sig.meta.count.c <- sig.meta.c %>% 
+  group_by(sig.meta.analysis, meta.analysis.method) %>% count()
+
+sig.meta.c <- sig.meta.c %>%  ggplot(aes(x = meta.analysis.method, fill = sig.meta.analysis)) + 
+  geom_bar() + coord_flip() +
+  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("meta.nonsig", "meta.sig")) +
+  annotate("text", x = sig.meta.count.c[sig.meta.count.c$sig.meta.analysis == 0,]$meta.analysis.method, y = 100000, 
+           label = paste(sig.meta.count.c[sig.meta.count.c$sig.meta.analysis == 0,]$n, "nonsig."), 
+           color = "white")
+
+
+#Change in significance after meta-analysis, separated by significant effect size estimate
+sig.meta <- data.mly %>% 
+  select(meta.id, study.id, sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
+  gather(key = "meta.analysis.method", value = "sig.meta.analysis", sig.fixef:sig.ranef.hkn) %>% mutate(sig.meta.analysis = factor(sig.meta.analysis))
+
+# duplicate.studies <- data.mly %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr, study.name) %>% 
[…]

### 2019-05-26 code/Presentation_plots.R

@@ -1,0 +1,309 @@
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+  load(file.path(PATH_RESULTS, file.dat))
+} else {
+  data = pb.readData(path = PATH_DATA, file = FILE)
+  tmp = pb.clean(data)
+  data = tmp[[1]]
+  aliases = tmp[[2]]
+  save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+
+load(file.path(PATH_RESULTS, file = "data.processed.RData"))
+
+
+require(tidyverse)
+require(meta)
+require(xtable)
+require(gridExtra)
+
+file.bin <- "pb.bin.RData"
+load(file.path(PATH_RESULTS, file.bin))
+
+file.cont <- "pb.cont.RData"
+load(file.path(PATH_RESULTS, file.cont))
+
+file.meta <- "meta.RData"
+load(file.path(PATH_RESULTS, file.meta))
+
+
+
+metac.bin <- meta.bin %>% filter(n.sig.type.bin > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+metac.cont <- meta.cont %>% filter(n.sig.type.cont > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+metac <- meta %>% filter(n.sig.type > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+
+
+#Significant proportion
+test.bin <- metac.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                  schwarzer.test = mean(schwarzer.test),
+                                                  rucker.test = mean(rucker.test),
+                                                  harbord.test = mean(harbord.test),
[…]

### 2019-05-26 code/Questions.R

@@ -1,0 +1,69 @@
+#New Data process function
+
+#Import data
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+if (file.exists(file.path(PATH_RESULTS, "data.RData"))) {
+  load(file.path(PATH_RESULTS, "data.RData"))
+} else {
+  data = pb.readData(path = PATH_DATA, file = FILE)
+  tmp = pb.clean(data)
+  data = tmp[[1]]
+  aliases = tmp[[2]]
+  save(data, file =  file.path(PATH_RESULTS, "data.RData"))
+}
+
+if (file.exists(file.path(PATH_RESULTS, "data.ext.RData"))) {
+  load(file.path(PATH_RESULTS, "data.ext.RData"))
+} else {
+  data.ext <- pb.process(data)
+  save(data.ext, file =  file.path(PATH_RESULTS, "data.ext.RData"))
+}
+
+
+
+#Meta-analysis function for any type "bin", "cont" and "surv":
+#data has to be processed by pb.readData() and cleaned by pb.clean(), 
+#processed by pb.process() (all functions in global environment from "PubBias_functions.R" script)
+
+mtd <- data.ext %>% filter(meta.id == 101436)
+
+meta.cor <- metacor(cor = fishersz, n = total1 + total2, studlab = study.name, sm = "ZCOR", 
+                    comb.fixed = TRUE, method.tau = "REML", null.effect = 0, data = mtd)
+meta.bin <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, method = "Inverse", 
+                    method.tau = "REML", data = mtd, sm = "RR")
+
+forest(meta.cor)
+forest(meta.bin)
+
+mtd.c <- data.ext %>% filter(meta.id == 122943)
+
[…]

### 2019-05-26 code/SMD_Correlation_Metas.R

@@ -1,0 +1,106 @@
+#Due to issues with correlations in binary cases, try to use metafor package:
+#New Data process function
+
+#Import data
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+if (file.exists(file.path(PATH_RESULTS, "data.RData"))) {
+  load(file.path(PATH_RESULTS, "data.RData"))
+} else {
+  data = pb.readData(path = PATH_DATA, file = FILE)
+  tmp = pb.clean(data)
+  data = tmp[[1]]
+  aliases = tmp[[2]]
+  save(data, file =  file.path(PATH_RESULTS, "data.RData"))
+}
+
+if (file.exists(file.path(PATH_RESULTS, "data.ext.RData"))) {
+  load(file.path(PATH_RESULTS, "data.ext.RData"))
+} else {
+  data.ext <- pb.process(data)
+  save(data.ext, file =  file.path(PATH_RESULTS, "data.ext.RData"))
+}
+
+
+
+require(metafor)
+
+#Metafor package part
+
+mtd <- data.ext %>% filter(meta.id == 101436)
+mtd$n <- mtd$total1 + mtd$total2
+mtd$var.log.OR <- mtd$se.log.OR^2
+mtd.c <- data.ext %>% filter(meta.id == 122943)
+
+mtd <- escalc(ai = events1, bi = total1 - events1, ci = events2, di = total2 - events2, 
+       measure = "RTET", data = mtd, append = T, var.names = c("rtet", "var.rtet"))
+mtd <- escalc(ri = rtet, ni = n, measure = "ZCOR", data = mtd, append = T, 
+              var.names = c("zcor", "var.zcor"))
+mtd <- escalc(ai = events1, bi = total1 - events1, ci = events2, di = total2 - events2, 
+              measure = "OR", data = mtd, append = T, var.names = c("OR", "var.OR"))
[…]

### 2019-05-29 Presentation/present.Rnw
code cleaned in new_meta_analysis.R

@@
 library(knitr)
+rm(list = ls())
 PATH_HOME = path.expand("~") # user home
@@
 
+load(file.path(PATH_RESULTS, file = "mly.RData"))
 load(file.path(PATH_RESULTS, file = "data.processed.RData"))
 
-require(tidyverse)
-require(meta)
-require(xtable)
-
-meta.id <- function(meta.id.tolook){
-	dt <- data.ext %>% filter(meta.id == meta.id.tolook)
-	if(any(is.na(dt$events1)) | all(dt$events1 == 0)){
-		meta.ex <- metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, studlab = study.name, data = dt)
-	} else{
-		meta.ex <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, sm = "RR", data = dt, method = "Inverse")
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+	load(file.path(PATH_RESULTS, file.bin))
+} else {
+	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
+	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
 }
-	return(meta.ex)
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+	load(file.path(PATH_RESULTS, file.cont))
+} else {
+	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
+	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
 }
 
-funnel.id <- function(meta.id.tolook){
-	funnel(meta.id(meta.id.tolook))
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
+	load(file.path(PATH_RESULTS, file.meta))
+} else {
+	meta <- pb.meta.merge(meta.bin, meta.cont)
+	save(meta, file =  file.path(PATH_RESULTS, file.meta))
 }
 
-trimfill.id <- function(meta.id.tolook){
-	funnel(trimfill(meta.id(meta.id.tolook)))
-}
-
-limitmeta.id <- function(meta.id.tolook){
-	funnel(limitmeta(meta.id(meta.id.tolook)))
-}
-
-copas.id <- function(meta.id.tolook){
-	auto.copas(meta.id(meta.id.tolook), 0.1)
-}
-
-setting.id <- function(meta.id.tolook){
-	return(meta %>% filter(meta.id == meta.id.tolook) %>% select(comparison.name, comparison.nr, outcome.name, sungroup.name))
-}
-
-est.id <- function(meta.id.tolook){
-	return(meta %>% filter(meta.id == meta.id.tolook) %>% select(est.fixef, est.ranef, est.copas, est.trimfill.fixef, est.reg.ranef))
-}
-
-single.study.id <- function(meta.id.tolook){
-	return(print(data.ext %>% filter(meta.id == meta.id.tolook) %>% select(study.name, effect, se, total1, total2, events1, events2, mean1, mean2) %>% 
-							 	arrange(se), n = 200))
-}
+data.ext2 <- pb.process2(data)
+
+#Meta filtering: 
+metac.bin <- meta.bin %>% filter(n.sig.type.bin > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+metac.cont <- meta.cont %>% filter(n.sig.type.cont > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+metac <- meta %>% filter(n.sig.type > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
 

### 2019-05-29 flowchart.Rnw
code cleaned in new_meta_analysis.R

\documentclass{article}

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\begin{document}

\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]

\begin{tikzpicture}[node distance = 2cm, auto]
    % Place nodes
    \node [block] (init) {Cochrane Library};
    \node [cloud, left of=init] (expert) {expert};
    \node [cloud, right of=init] (system) {system};
    \node [block, below of=init] (identify) {scraped dataset};
    \node [block, below of=identify] (evaluate) {cleaned dataset};
    \node [block, left of=evaluate, node distance=3cm] (update) {update model};
    \node [block, below of=evaluate] (decide) {Meta-Analysis of groups with n > 9};
    \node [block, below of=decide, node distance=3cm] (stop) {Adjustment and Publication Bias tests for meta-analyses with I2 < 0.5, ..};
    % Draw edges
    \path [line] (init) -- (identify);
    \path [line] (identify) -- (evaluate);
    \path [line] (evaluate) -- (decide);
    \path [line] (decide) -| node [near start] {yes} (update);
    \path [line] (update) |- (identify);
    \path [line] (decide) -- node {no}(stop);
    \path [line,dashed] (expert) -- (init);
    \path [line,dashed] (system) -- (init);
    \path [line,dashed] (system) |- (evaluate);
\end{tikzpicture}

\end{document}

### 2019-05-29 report/chapter03.Rnw
code cleaned in new_meta_analysis.R

@@
 
-# data = pb.readData(path = PATH_DATA, file = FILE)
-# tmp = pb.clean(data)
-# data = tmp[[1]]
-# aliases = tmp[[2]]
-
 file.dat <- "data.RData"
@@
 
+load(file.path(PATH_RESULTS, file = "mly.RData"))
+load(file.path(PATH_RESULTS, file = "data.processed.RData"))
+
 file.bin <- "pb.bin.RData"
@@
 } else {
-  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
+	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
 	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
@@
 } else {
-  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
+	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
 	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
@@
 
-load(file.path(PATH_RESULTS, file = "data.processed.RData"))
+data.ext2 <- pb.process2(data)
 
-require(biostatUZH)
-require(tidyverse)
-require(meta)
-require(metasens)
-require(gridExtra)
-require(xtable)
+#Meta filtering: 
+metac.bin <- meta.bin %>% filter(n.sig.type.bin > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+metac.cont <- meta.cont %>% filter(n.sig.type.cont > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+metac <- meta %>% filter(n.sig.type > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
 @

### 2019-05-29 code/PubBias.R

@@ -12,6 +12,75 @@ file_results = "pb.RData"
 
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
 
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.dat <- "data.processed.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data.ext2 = pb.process2(data)
+	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+	load(file.path(PATH_RESULTS, file.bin))
+} else {
+	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
+	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+	load(file.path(PATH_RESULTS, file.cont))
+} else {
+	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
+	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
+	load(file.path(PATH_RESULTS, file.meta))
+} else {
+	meta <- pb.meta.merge(meta.bin, meta.cont)
+	save(meta, file =  file.path(PATH_RESULTS, file.meta))
+}
+
+load(file.path(PATH_RESULTS, "meta.complete.RData"))
+
+
+#Applying test and adjustment criteria:
+metac.bin <- meta.bin %>% filter(n.sig.single > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
[…]

### 2019-05-29 code/SMD_Correlation_Metas.R

@@ -1,3 +1,72 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.dat <- "data.processed.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data.ext2 = pb.process2(data)
+	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+	load(file.path(PATH_RESULTS, file.bin))
+} else {
+	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
+	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+	load(file.path(PATH_RESULTS, file.cont))
+} else {
+	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
+	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
+	load(file.path(PATH_RESULTS, file.meta))
+} else {
[…]

### 2019-05-29 code/Unused.R

@@ -1,3 +1,70 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.dat <- "data.processed.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data.ext2 = pb.process2(data)
+	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+	load(file.path(PATH_RESULTS, file.bin))
+} else {
+	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
+	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+	load(file.path(PATH_RESULTS, file.cont))
+} else {
+	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
+	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
[…]

### 2019-05-29 code/adjustment3.R

@@ -12,51 +12,74 @@ file_results = "pb.RData"
 
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
 
-
-# data = pb.readData(path = PATH_DATA, file = FILE)
-# tmp = pb.clean(data)
-# data = tmp[[1]]
-# aliases = tmp[[2]]
-
-
-meta.id <- function(meta.id.tolook){
-	dt <- data.ext %>% filter(meta.id == meta.id.tolook)
-	if(any(is.na(dt$events1)) | all(dt$events1 == 0)){
-		meta.ex <- metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, studlab = study.name, data = dt)
-	} else{
-		meta.ex <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, sm = "RR", data = dt, method = "Inverse")
-	}
-	return(meta.ex)
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
 }
 
-funnel.id <- function(meta.id.tolook){
-	funnel(meta.id(meta.id.tolook))
+file.dat <- "data.processed.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data.ext2 = pb.process2(data)
+	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
 }
 
-trimfill.id <- function(meta.id.tolook){
-	funnel(trimfill(meta.id(meta.id.tolook)))
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+	load(file.path(PATH_RESULTS, file.bin))
+} else {
+	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
+	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
 }
 
-limitmeta.id <- function(meta.id.tolook){
[…]

### 2019-05-29 code/complete_vs_single_review.R

@@ -1,0 +1,401 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.dat <- "data.processed.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data.ext2 = pb.process2(data)
+	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+	load(file.path(PATH_RESULTS, file.bin))
+} else {
+	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
+	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+	load(file.path(PATH_RESULTS, file.cont))
+} else {
+	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
+	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
[…]

### 2019-05-29 code/correctures.R

@@ -12,21 +12,84 @@ file_results = "pb.RData"
 
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
 
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
 
-# data = pb.readData(path = PATH_DATA, file = FILE)
-# tmp = pb.clean(data)
-# data = tmp[[1]]
-# aliases = tmp[[2]]
+file.dat <- "data.processed.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data.ext2 = pb.process2(data)
+	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+	load(file.path(PATH_RESULTS, file.bin))
+} else {
+	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
+	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+	load(file.path(PATH_RESULTS, file.cont))
+} else {
+	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
+	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
+	load(file.path(PATH_RESULTS, file.meta))
+} else {
+	meta <- pb.meta.merge(meta.bin, meta.cont)
+	save(meta, file =  file.path(PATH_RESULTS, file.meta))
+}
+
+load(file.path(PATH_RESULTS, "meta.complete.RData"))
+
+
+#Applying test and adjustment criteria:
[…]

### 2019-05-29 code/cumaly.R

@@ -12,6 +12,75 @@ file_results = "pb.RData"
 
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
 
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.dat <- "data.processed.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data.ext2 = pb.process2(data)
+	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+	load(file.path(PATH_RESULTS, file.bin))
+} else {
+	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
+	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+	load(file.path(PATH_RESULTS, file.cont))
+} else {
+	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
+	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
+	load(file.path(PATH_RESULTS, file.meta))
+} else {
+	meta <- pb.meta.merge(meta.bin, meta.cont)
+	save(meta, file =  file.path(PATH_RESULTS, file.meta))
+}
+
+load(file.path(PATH_RESULTS, "meta.complete.RData"))
+
+
+#Applying test and adjustment criteria:
+metac.bin <- meta.bin %>% filter(n.sig.single > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
[…]

### 2019-05-29 code/explore.R

@@ -1,3 +1,72 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.dat <- "data.processed.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data.ext2 = pb.process2(data)
+	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+	load(file.path(PATH_RESULTS, file.bin))
+} else {
+	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
+	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+	load(file.path(PATH_RESULTS, file.cont))
+} else {
+	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
+	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
[…]

### 2019-05-29 code/meta_ct_surv.R

@@ -1,0 +1,279 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.dat <- "data.processed.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data.ext2 = pb.process2(data)
+	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+	load(file.path(PATH_RESULTS, file.bin))
+} else {
+	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
+	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+	load(file.path(PATH_RESULTS, file.cont))
+} else {
+	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
+	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
[…]

### 2019-05-29 code/meta_fct_update.R

@@ -1,0 +1,641 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.dat <- "data.processed.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data.ext2 = pb.process2(data)
+	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+file.bin <- "pb.bin.RData"
+if (file.exists(file.path(PATH_RESULTS, file.bin))) {
+	load(file.path(PATH_RESULTS, file.bin))
+} else {
+	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
+	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
+}
+
+file.cont <- "pb.cont.RData"
+if (file.exists(file.path(PATH_RESULTS, file.cont))) {
+	load(file.path(PATH_RESULTS, file.cont))
+} else {
+	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
+	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
+}
+
+file.meta <- "meta.RData"
+if (file.exists(file.path(PATH_RESULTS, file.meta))) {
[…]

### 2019-05-29 code/new_meta_analysis.R

@@ -1,0 +1,516 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+data.ext2 <- pb.process2(data)
+
+# load(file.path(PATH_RESULTS, "meta_analyses_summary_bin_cont_surv.RData"))
+# load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+# load(file.path(PATH_RESULTS, "data_used_for_summary.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_bin.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_cont.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_surv.RData"))
+
+settings.meta(hakn=TRUE, method.tau="PM", method = "Inverse")
+
+##########################################################################################
+##########################################################################################
+##########################################################################################
+##########################################################################################
+#META-ANALYSIS CALCULATION:
+#Binary outcomes:
+##########################################################################################
+##########################################################################################
+##########################################################################################
[…]

### 2019-05-30 Presentation/present.Rnw
analysis cleanup 2.

@@
 
-load(file.path(PATH_RESULTS, file = "mly.RData"))
-load(file.path(PATH_RESULTS, file = "data.processed.RData"))
-
-file.bin <- "pb.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-	load(file.path(PATH_RESULTS, file.bin))
-} else {
-	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
-	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-file.cont <- "pb.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-	load(file.path(PATH_RESULTS, file.cont))
-} else {
-	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
-	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.meta <- "meta.RData"
-if (file.exists(file.path(PATH_RESULTS, file.meta))) {
-	load(file.path(PATH_RESULTS, file.meta))
-} else {
-	meta <- pb.meta.merge(meta.bin, meta.cont)
-	save(meta, file =  file.path(PATH_RESULTS, file.meta))
-}
-
-data.ext2 <- pb.process2(data)
-
-#Meta filtering: 
-metac.bin <- meta.bin %>% filter(n.sig.type.bin > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
-metac.cont <- meta.cont %>% filter(n.sig.type.cont > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
-metac <- meta %>% filter(n.sig.type > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "meta.bin.RData"))
+load(file.path(PATH_RESULTS, "meta.cont.RData"))
+load(file.path(PATH_RESULTS, "meta.surv.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+
+library(gridExtra)
 
 #Meta-analysis example
-data.ext <- data.ext %>% mutate(study.year = ifelse(study.year < 2019, study.year, NA)) %>% 
+data.ext2 <- data.ext2 %>% mutate(study.year = ifelse(study.year < 2019, study.year, NA)) %>% 
     mutate(study.year = ifelse(study.year > 1920, study.year, NA))
-biased.rev <- data.ext %>% filter(meta.id == 122943)
-unbiased.rev <- data.ext %>% filter(meta.id == 181863)
-meta.example <- metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, 
+biased.rev <- data.ext2 %>% filter(meta.id == 122943)
+unbiased.rev <- data.ext2 %>% filter(meta.id == 181863)
+meta.example <- meta.font(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, 
 												 studlab = study.name, data = biased.rev)
-meta.nexample <- metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, 
+meta.nexample <- meta.font(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, 
 												 studlab = study.name, data = unbiased.rev)
@@
 	summarise(lower = quantile(n, 0.05), median = quantile(n, 0.5), mean = mean(n), upper = quantile(n, 0.95))
-meta.rev <- data.ext %>% group_by(file.nr) %>% distinct(meta.id) %>% count() %>% ungroup() %>% 
+meta.rev <- data.ext2 %>% group_by(file.nr) %>% distinct(meta.id) %>% count() %>% ungroup() %>% 
 	summarise(lower = quantile(n, 0.05), median = quantile(n, 0.5), mean = mean(n), upper = quantile(n, 0.95))
@@
 #Global level
-study.years <- data.ext %>% group_by(file.nr) %>% distinct(study.name, .keep_all = T) %>% ungroup() %>% 
+study.years <- data.ext2 %>% group_by(file.nr) %>% distinct(study.name, .keep_all = T) %>% ungroup() %>% 
 	summarise(lower = quantile(study.year, 0.05, na.rm = T), median = quantile(study.year, 0.5, na.rm = T),
 						mean = mean(study.year, na.rm = T), upper = quantile(study.year, 0.95, na.rm = T))
-sample.size <- data.ext %>% group_by(file.nr) %>% distinct(study.name, .keep_all = T) %>% ungroup() %>% 
+sample.size <- data.ext2 %>% group_by(file.nr) %>% distinct(study.name, .keep_all = T) %>% ungroup() %>% 
 	mutate(samplesize = total1 + total2) %>% 
@@
 
-#Loading meta-analysis results:
-file.bin <- "pb.bin.RData"
-load(file.path(PATH_RESULTS, file.bin))
-
-file.cont <- "pb.cont.RData"
-load(file.path(PATH_RESULTS, file.cont))
-
-file.meta <- "meta.RData"
-load(file.path(PATH_RESULTS, file.meta))
-
 library(gridExtra)
 
-meta.id <- function(meta.id.tolook){
-	dt <- data.ext %>% filter(meta.id == meta.id.tolook)
-	if(any(is.na(dt$events1)) | all(dt$events1 == 0)){
-		meta.ex <- metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, studlab = study.name, data = dt)
-	} else{
-		meta.ex <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, sm = "RR", data = dt)
-	}
-	return(meta.ex)
-}
-
-#Meta filtering: 
-metac.bin <- meta.bin %>% filter(n.sig.type.bin > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
-metac.cont <- meta.cont %>% filter(n.sig.type.cont > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
-metac <- meta %>% filter(n.sig.type > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
-
 #Significant proportion
-test.bin <- metac.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+meta.f <- meta.f %>% 
+	mutate(egger.test = ifelse(pval.peter < sig.level, 1, 0),
+				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
+				 begg.test = ifelse(pval.begg < sig.level, 1, 0),
+
+				 schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
+				 rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
+				 harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
+				 peter.test = ifelse(pval.peter < sig.level, 1, 0))
+
+meta.bin <- meta.f %>% filter(outcome.type == "bin")
+meta.cont <- meta.f %>% filter(outcome.type == "cont")
+meta.surv <- meta.f %>% filter(outcome.type == "surv")
+
+test.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                           schwarzer.test = mean(schwarzer.test),
@@
 
-p.bin <- metac.bin %>% ungroup() %>% 
+p.bin <- meta.bin %>% ungroup() %>% 
   select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
@@
 
-test.cont <- metac.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+dat_text <- data.frame(
+  label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
+  										sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test)), "< 0.1,",
+  							round(c(mean(meta.bin$harbord.test), mean(meta.bin$peter.test), 
+  										mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test)),2)*100, "%"),
+  test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer"))
+
+labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer")
+
+p.dist.bin <- meta.bin %>% ungroup() %>% 
+  select(pval.harbord, pval.peter, pval.rucker, pval.schwarzer) %>% 
+  gather(key = "test.type", value = "p.value") %>% 
+  ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 100, label = label), color = "black") + 
+	theme(strip.text.x = element_text(size=15))
+
+test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                             begg.test = mean(begg.test),
@@
 
-p.cont <- metac.cont %>% ungroup() %>% 
+p.cont <- meta.cont %>% ungroup() %>% 
   select(egger.test, thomson.test, begg.test) %>% 
@@
 dat_text <- data.frame(
-  label = paste(c(sum(metac.cont$begg.test), sum(metac.cont$egger.test), sum(metac.cont$thomson.test)), "< 0.1,",
-  							round(c(mean(metac.cont$begg.test), mean(metac.cont$egger.test), mean(metac.cont$thomson.test)),2)*100, "%"),
-  test.type   = c("pval.begg.cont", "pval.egger.cont", "pval.thomson.cont"))
-
-labels <- c(pval.begg.cont = "Begg Mazumdar", pval.egger.cont = "Egger", pval.thomson.cont = "Thompson Sharp")
-p.dist.cont <- metac.cont %>% ungroup() %>% 
-  select(pval.egger.cont, pval.thomson.cont, pval.begg.cont) %>% 
+  label = paste(c(sum(meta.cont$begg.test), sum(meta.cont$egger.test), sum(meta.cont$thomson.test)), "< 0.1,",
+  							round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thomson.test)),2)*100, "%"),
+  test.type   = c("pval.begg", "pval.egger", "pval.thomson"))
+
+labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thomson = "Thompson Sharp")
+p.dist.cont <- meta.cont %>% ungroup() %>% 
+  select(pval.egger, pval.thomson, pval.begg) %>% 
   gather(key = "test.type", value = "p.value") %>% 
@@
 
+test.surv <- meta.surv %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+                                                            begg.test = mean(begg.test),
+                                                            thomson.test = mean(thomson.test))
+
+test.surv <- test.surv %>% gather(key = "test.type", value = "mean")
+
+p.surv <- meta.surv %>% ungroup() %>% 
+  select(egger.test, thomson.test, begg.test) %>% 
+  gather(key = "test.type", value = "null.hypothesis") %>% 
+  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
+  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+  theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
+	guides(fill=guide_legend(title=NULL))+
+  annotate("text", x = test.surv$test.type, y = 150, 
+           label = paste(round(test.surv$mean, 2)*100, "% rejected"), 
+           color = "white")
+
 dat_text <- data.frame(
-  label = paste(c(sum(metac.bin$harbord.test), sum(metac.bin$peter.test), 
-  										sum(metac.bin$rucker.test), sum(metac.bin$schwarzer.test)), "< 0.1,",
-  							round(c(mean(metac.bin$harbord.test), mean(metac.bin$peter.test), 
-  										mean(metac.bin$rucker.test), mean(metac.bin$schwarzer.test)),2)*100, "%"),
-  test.type   = c("pval.harbord.bin", "pval.peter.bin", "pval.rucker.bin", "pval.schwarzer.bin"))
-
-labels <- c(pval.harbord.bin = "Harbord", pval.peter.bin = "Peter", pval.rucker.bin = "Rucker", pval.schwarzer.bin = "Schwarzer")
-
-p.dist.bin <- metac.bin %>% ungroup() %>% 
-  select(pval.harbord.bin, pval.peter.bin, pval.rucker.bin, pval.schwarzer.bin) %>% 
+  label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), sum(meta.surv$thomson.test)), "< 0.1,",
+  							round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), mean(meta.surv$thomson.test)),2)*100, "%"),
+  test.type   = c("pval.begg", "pval.egger", "pval.thomson"))
+
+labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thomson = "Thompson Sharp")
+p.dist.surv <- meta.surv %>% ungroup() %>% 
+  select(pval.egger, pval.thomson, pval.begg) %>% 
   gather(key = "test.type", value = "p.value") %>% 
-  ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 100, label = label), color = "black") + 
+  ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + 
+	facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 25, label = label),  color = "black") + 
 	theme(strip.text.x = element_text(size=15))
@@
 #Test agreement
-agree.bin <- metac.bin %>% mutate(n.sig = peter.test + rucker.test + egger.test + harbord.test + schwarzer.test) %>% 
+agree.bin <- meta.bin %>% mutate(n.sig = peter.test + rucker.test + harbord.test + schwarzer.test) %>% 
   group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
@@
 
-agree.cont <- metac.cont %>% mutate(n.sig = egger.test + thomson.test + begg.test) %>% 
+agree.cont <- meta.cont %>% mutate(n.sig = egger.test + thomson.test + begg.test) %>% 
+  group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
+  ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")
+
+agree.surv <- meta.surv %>% mutate(n.sig = egger.test + thomson.test + begg.test) %>% 
   group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
@@
 
-#Adjustment results: Effect difference histograms
-effect.diff <- metac %>% mutate(
-	est.fixef = ifelse(!is.na(est.fixef.bin), est.fixef - 1, est.fixef),
-	est.ranef = ifelse(!is.na(est.fixef.bin), est.ranef - 1, est.ranef),
-	est.trimfill.fixef = ifelse(!is.na(est.fixef.bin), est.trimfill.fixef - 1, est.trimfill.fixef),
-	est.copas = ifelse(!is.na(est.fixef.bin), est.copas - 1, est.copas),
-	est.reg.ranef = ifelse(!is.na(est.fixef.bin), est.reg.ranef - 1, est.reg.ranef),
+#Comparison of "original effect sizes":
+effect.diff <- meta.f %>% mutate(
+	est.fixef = ifelse(outcome.type == "bin", exp(est.fixef), est.fixef),
+	est.ranef = ifelse(outcome.type == "bin", exp(est.ranef), est.ranef),
+	est.copas = ifelse(outcome.type == "bin", exp(est.copas), est.copas),
+	est.reg = ifelse(outcome.type == "bin", exp(est.reg.ranef), est.reg.ranef)
+)
+
+effect.diff <- effect.diff %>% mutate(
+	est.fixef = ifelse(outcome.type == "bin", est.fixef - 1, est.fixef),
+	est.ranef = ifelse(outcome.type == "bin", est.ranef - 1, est.ranef),
+	est.copas = ifelse(outcome.type == "bin", est.copas - 1, est.copas),
+	est.reg = ifelse(outcome.type == "bin", est.reg.ranef - 1, est.reg.ranef),
 	fixef.ranef = ifelse(abs(est.ranef) > abs(est.fixef), "Reduction", "Amplification"),
-	fixef.trimfill = ifelse(abs(est.fixef) > abs(est.trimfill.fixef), "Reduction", "Amplification"),
 	fixef.copas = ifelse(abs(est.fixef) > abs(est.copas), "Reduction", "Amplification"),
-	fixef.reg = ifelse(abs(est.fixef) > abs(est.reg.ranef), "Reduction", "Amplification"),
-	fixef.trimfill.s = ifelse(sign(est.fixef) == sign(est.trimfill.fixef), "Unchanged", "Reversed"),
+	fixef.reg = ifelse(abs(est.fixef) > abs(est.reg), "Reduction", "Amplification"),
 	fixef.copas.s = ifelse(sign(est.fixef) == sign(est.copas), "Unchanged", "Reversed"),
-	fixef.reg.s = ifelse(sign(est.fixef) == sign(est.reg.ranef), "Unchanged", "Reversed"))
+	fixef.reg.s = ifelse(sign(est.fixef) == sign(est.reg), "Unchanged", "Reversed"))
 
@@
 
-trimfill.miss <- effect.diff %>% group_by(fixef.trimfill) %>% mutate(dif = abs(est.fixef - est.trimfill.fixef)) %>% 
-	filter(dif > 2) %>% mutate(label = round(dif, 1), type = !is.na(est.fixef.bin)) %>% arrange(label) %>% select(label, fixef.trimfill.s, meta.id, type)
-
-trimfill.label <- data.frame(label = paste("missing:", c(paste(trimfill.miss$label[trimfill.miss$fixef.trimfill == "Reduction"], collapse = ", "),
-																												 paste(trimfill.miss$label[trimfill.miss$fixef.trimfill == "Amplification"], collapse = ", "))),
-														fixef.trimfill = unique(trimfill.miss$fixef.trimfill), 
-														fixef.trimfill.s  = "Reversed")
-
-trimfill.label$label <- as.character(trimfill.label$label)
-trimfill.label$label[1] <- sub("2.5,", "2.5, \n   ", trimfill.label$label[1])
-
-hist.trimfill <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.trimfill.fixef), fill = factor(fixef.trimfill.s))) +
-	geom_histogram() + facet_grid(~factor(fixef.trimfill)) + xlim(0, 2)+ xlab("Effect difference") +
-	geom_text(data = trimfill.label, mapping = aes(label = label, x = 0, hjust = 0, y = 300), 
-						color = "black") + scale_fill_discrete(name="Effect direction") + theme_bw() + 
-	theme(legend.position = "bottom", strip.text.x = element_text(size=15))
-
-hist.trimfill1 <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.trimfill.fixef))) +
-	geom_histogram() + facet_grid(~factor(fixef.trimfill)) + xlim(0, 2)+ xlab("Effect difference") +
-	geom_text(data = trimfill.label, mapping = aes(label = label, x = 0, hjust = 0, y = 300), 
-						color = "black") + theme_bw() + 
-	theme(legend.position = "bottom", strip.text.x = element_text(size=15))
-
-funnel(trimfill(meta.id(165815)))
+# trimfill.miss <- effect.diff %>% group_by(fixef.trimfill) %>% mutate(dif = abs(est.fixef - est.trimfill.fixef)) %>% 
+# 	filter(dif > 2) %>% mutate(label = round(dif, 1), type = outcome.type == "bin") %>% arrange(label) %>% select(label, fixef.trimfill.s, meta.id, type)
+
+# trimfill.label <- data.frame(label = paste("missing:", c(paste(trimfill.miss$label[trimfill.miss$fixef.trimfill == "Reduction"], collapse = ", "),
+# 																												 paste(trimfill.miss$label[trimfill.miss$fixef.trimfill == "Amplification"], collapse = ", "))),
+# 														fixef.trimfill = unique(trimfill.miss$fixef.trimfill), 
+# 														fixef.trimfill.s  = "Reversed")
+# 
+# trimfill.label$label <- as.character(trimfill.label$label)
+# trimfill.label$label[1] <- sub("2.5,", "2.5, \n   ", trimfill.label$label[1])
+# 
+# 
+# hist.trimfill <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.trimfill.fixef), fill = factor(fixef.trimfill.s))) +
+# 	geom_histogram() + facet_grid(~factor(fixef.trimfill)) + xlim(0, 2)+ xlab("Effect difference") +
+# 	geom_text(data = trimfill.label, mapping = aes(label = label, x = 0, hjust = 0, y = 300), 
+# 						color = "black") + scale_fill_discrete(name="Effect direction") + theme_bw() + 
+# 	theme(legend.position = "bottom", strip.text.x = element_text(size=15))
+# 
+# hist.trimfill1 <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.trimfill.fixef))) +
+# 	geom_histogram() + facet_grid(~factor(fixef.trimfill)) + xlim(0, 2)+ xlab("Effect difference") +
+# 	geom_text(data = trimfill.label, mapping = aes(label = label, x = 0, hjust = 0, y = 300), 
+# 						color = "black") + theme_bw() + 
+# 	theme(legend.position = "bottom", strip.text.x = element_text(size=15))
+# 
+# funnel(trimfill(meta.id(165815)))
 
 copas.miss <- effect.diff %>% filter(!is.na(est.copas)) %>% group_by(fixef.copas) %>% mutate(dif = abs(est.fixef - est.copas)) %>% 
-	filter(dif > 2) %>% mutate(label = round(dif, 1), type = !is.na(est.fixef.bin)) %>% arrange(label) %>% select(label, fixef.copas.s, meta.id, type)
+	filter(dif > 2) %>% mutate(label = round(dif, 1), type = outcome.type == "bin") %>% arrange(label) %>% select(label, fixef.copas.s, meta.id, type)
 
@@
 
-funnel(meta.id(56200))
-
 reg.ranef.miss <- effect.diff %>% group_by(fixef.reg) %>% mutate(dif = abs(est.fixef - est.reg.ranef)) %>% 
-	filter(dif > 3) %>% mutate(label = round(dif, 1), type = !is.na(est.fixef.bin)) %>% arrange(label) %>% select(label, fixef.reg.s, meta.id, type)
+	filter(dif > 3) %>% mutate(label = round(dif, 1), type = outcome.type == "bin") %>% arrange(label) %>% select(label, fixef.reg.s, meta.id, type)
 
@@
 
-metac %>% filter(meta.id == 101436) %>% select(comparison.name, outcome.name, sungroup.name, est.fixef, est.copas, 
-																							 est.trimfill.fixef, est.reg.ranef, est.copas)
-par(mfrow = c(1,3))
-funnel(meta.id(101436))
-funnel(trimfill(meta.id(101436)))
-funnel(limitmeta(meta.id(101436)))
-
-print(effect.diff %>% group_by(fixef.reg) %>% mutate(dif = abs(est.fixef - est.reg.ranef)) %>% 
-				filter(dif > 3) %>% mutate(label = round(dif, 1), type = !is.na(est.fixef.bin)) %>% 
-				arrange(label) %>% select(label, type, meta.id, comparison.name, outcome.name), n = 200)
-
-#Scatterplots of metac-analysis and corrected log(abs(abs estimates
-ranef.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.ranef)))) + geom_point(size = 0.8) + 
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
-	xlab("Fixed effects log estimate") + ylab("Random effects log estimate") + ggtitle("Fixed effects to Random effects")
-
-# metac %>% ggplot(aes(y = log(abs((est.ranef))), x = log(abs(est.trimfill.fixef)))) + geom_point() + 
-# 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
-# 	xlab("Random effects log estimate") + ylab("Trimfill log estimate") + ggtitle("Random effects to Trimfill")
-
-#Scatterplots of metac-analysis and corrected log(abs(abs estimates
-trimfill.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.trimfill.fixef)))) + geom_point(size = 0.8) + 
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
-	xlab("Fixed effects log estimate") + ylab("Trimfill log estimate") + ggtitle("Fixed effects to Trimfill")
-
-trimfill.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.trimfill.fixef)))) + geom_point(size = 0.8) + 
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
-	xlab("Random effects log estimate") + ylab("Trimfill log estimate") + ggtitle("Random effects to Trimfill")
-
-#Scatterplots of metac-analysis and corrected log estimates
-copas.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.copas)))) + geom_point(size = 0.8) + 
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
-	xlab("Fixed effects log estimate") + ylab("Copas log estimate") + ggtitle("Fixed effects to Copas")
-
-copas.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.copas)))) + geom_point(size = 0.8) + 
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE, show.legend = T) + 
-	xlab("Random effects log estimate") + ylab("Copas log estimate") + ggtitle("Random effects to Copas")
-
-#Scatterplots of metac-analysis and corrected log estimates
-reg.fixef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.fixef))), y = log(abs(est.reg.ranef)))) + geom_point(size = 0.8) + 
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
-	xlab("Fixed effects log estimate") + ylab("Regression log estimate") + ggtitle("Fixed effects to Regression")
-
-reg.ranef.sc.effect <- metac %>% ggplot(aes(x = log(abs((est.ranef))), y = log(abs(est.reg.ranef)))) + geom_point(size = 0.8) + 
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + 
-	xlab("Random effects log estimate") + ylab("Regression log estimate") + ggtitle("Random effects to Regression")
-
-#Scatterplots of test- statistics:
-ranef.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.ranef))) + geom_point(size = 0.8) +
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
-	ggtitle("Fixed effects and Random effects z statistics") + ylab("Random effects statistic") + xlab("Fixed effects statistic")
-
-metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.trimfill.fixef))) + geom_point(size = 0.8) +
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
-	ggtitle("Fixed effects and Random effects z statistics") + ylab("Random effects statistic") + xlab("Fixed effects statistic")
-
-#Scatterplots of test- statistics:
-trimfill.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.trimfill.fixef))) + geom_point(size = 0.8) +
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
-	ggtitle("Fixed effects and trimfill z statistics") + ylab("Trimfill  statistic") + xlab("Fixed effects  statistic")
-
-trimfill.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.trimfill.fixef))) + geom_point(size = 0.8) +
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
-	ggtitle("Random effects and trimfill z statistics") + ylab("Trimfill statistic") + xlab("Random effects  statistic")
-
-#Scatterplots of test- statistics:
-copas.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.copas))) + geom_point(size = 0.8) +
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + xlim(0, 25) +
-	ggtitle("Fixed effects and Copas z statistics") + ylab("Copas  statistic") + xlab("Fixed effects  statistic")
-
-copas.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.copas))) + geom_point(size = 0.8) +
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + xlim(0, 20) +
-	ggtitle("Random effects and Copas z statistics") + ylab("Copas  statistic") + xlab("Random effects  statistic")
-
-#Scatterplots of test- statistics:
-reg.fixef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.reg.ranef))) + geom_point(size = 0.8) +
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
-	ggtitle("Fixed effects and Regression z statistics") + ylab("Regression  statistic") + xlab("Fixed effects  statistic")
-
-reg.ranef.sc.zval <- metac %>% ggplot(aes(x = abs(zval.ranef), y = abs(zval.reg.ranef))) + geom_point(size = 0.8) +
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
-	ggtitle("Random effects and Regression z statistics") + ylab("Regression  statistic") + xlab("Random effects  statistic")
-
-#Missing study proportions:
-p.missing.copas <- metac %>% ggplot(aes(x = missing.copas/n)) + geom_histogram(bins = 20) + 
-	xlim(0, 0.5) + ylim(0, 200) + xlab("Proportion of missing studies") + ggtitle("Copas selection model") + theme_bw()
-p.missing.trim <- metac %>% ggplot(aes(x = missing.trim)) + geom_histogram(bins = 20) + 
-	xlim(0, 0.5) + ylim(0, 200) + xlab("Proportion of missing studies") + ggtitle("Trim-and-fill") + theme_bw()
+# print(effect.diff %>% group_by(fixef.reg) %>% mutate(dif = abs(est.fixef - est.reg.ranef)) %>% 
+# 				filter(dif > 3) %>% mutate(label = round(dif, 1), outcome.type) %>% 
+# 				arrange(label) %>% select(label, type, meta.id, comparison.name, outcome.name), n = 200)
 @
@@
 
-From \Sexpr{dim(meta)[1]} with $n \geq 10$, \Sexpr{dim(metac)[1]} remain.
+From \Sexpr{dim(meta)[1]} with $n \geq 10$, \Sexpr{dim(meta.f)[1]} remain.
 \end{frame}
@@
 \begin{frame}[fragile]{Continuous Outcome Test Results}
-$p$-values distribution, $n$ = \Sexpr{dim(metac.cont)[1]}:
+$p$-values distribution, $n$ = \Sexpr{dim(meta.cont)[1]}:
 
@@
 \begin{frame}[fragile]{Binary Outcome Test Results}
-$p$-values distribution, $n$ = \Sexpr{dim(metac.bin)[1]}:
+$p$-values distribution, $n$ = \Sexpr{dim(meta.bin)[1]}:
 

### 2019-05-30 communication/explore.Rmd
analysis cleanup 2.

--- 2019-03-21 code_excess/explore_maill.Rmd
@@
 PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'thesis/code')
+PATH = file.path(PATH_HOME, 'thesis/cochrane')
 ```
@@
 ```{r}
+# load(file = "cochrane.RData")
+
 require(tidyverse)
@@
   geom_smooth(method = lm) + theme_bw() + 
-  labs(title = "Scaled and centered RR over time", subtitle = "Initial finding > 1") + ylab("Risk Ratio")  + xlab("Time") + xlim(c(-4,4)) + ylim(c(-5,7))
+  labs(title = "Scaled and centered RR over time", subtitle = "Initial finding > 1") + ylab("Risk Ratio")  + ylab("Time") + xlim(c(-4,4)) + ylim(c(-5,7))
 ```
@@
 
+By hand computation of Cochrane's Q is not equal to Q computed with metabin package, as can be seen when comparing the histogramm.
+The shape of the histogramms suggest that the by hand computed one ist wrong (large right tail).
+The formula used for computing is:
+
+\begin{align} 
+Q = sum_{i=1}^{n} w_{i} (\hat{\theta} - \theta_{i}) 
+\end{align}
+
+with $n$ = number of trials, $w_{i}$ the inverse of the variance of the log effect estimate, $\theta_{i}$ the log effect estimate and $\hat{\theta}$ the weigthed average of the log effect estimates.
+The variance of the log odds ratio was computed as $(1/a + 1/b + 1/c + 1/d)$, $a,b,c,d$ being the entries in a two-by-two table.
+
+Cochrane heterogeneity test for Odds Ratios (``manual''):
+
+```{r}
+madata %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>% 
+  filter(outcome.measure == "Odds Ratio") %>% 
+  mutate(counts = n()) %>% filter(counts > 1) %>%
+  mutate(log.OR = log(effect), 
+         se.log.OR = sqrt( (1/events1) + (1/(total1 - events1)) + (1/events2) + (1/(total2 - events2)))) %>% 
+  filter(!is.na(se.log.OR) & se.log.OR != Inf) %>% mutate(summary.effect = sum( log.OR/se.log.OR^2 ) / sum( 1/se.log.OR^2 )) %>% 
+  summarise(Q = sum(((log.OR - summary.effect)^2)/se.log.OR^2), n = n(), OR =  exp(min(summary.effect))) %>% 
+  mutate(p.value = 1 - pchisq(Q, df = n - 1)) %>% 
+  ggplot(aes(x = p.value)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
+  theme_bw() + labs(title = "Cochrane Heterogeneity Test P-values of ORs")
+```
+
 Cochrane heterogeneity test for Odds Ratios (with meta::metabin()):
@@
   theme_bw() + labs(title = "Cochrane Heterogeneity Test P-values of ORs")
+```
+
+For comparison, the single Q's are shown computed by the two methods:
+
+```{r}
+file.number.to.compare <- 23
+ds <- madata %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>% filter(file.nr == file.number.to.compare) %>% 
+  filter(outcome.measure == "Odds Ratio") %>% filter(events1 > 0 & events2 > 0) %>% 
+  mutate(counts = n()) %>% filter(counts > 1) %>%
+  summarise(
+    Q = metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, method = "Inverse", sm = "OR")$Q,
+    p.value = metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, 
+                      method = "Inverse", sm =  "OR")$pval.Q)
+
+ds2 <- madata %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>% filter(file.nr == file.number.to.compare) %>% 
+  filter(outcome.measure == "Odds Ratio") %>% filter(events1 > 0 & events2 > 0) %>%
+  mutate(counts = n()) %>% filter(counts > 1) %>%
+  mutate(log.OR = log(effect), 
+         se.log.OR = sqrt( (1/events1) + (1/(total1 - events1)) + (1/events2) + (1/(total2 - events2)))) %>% 
+  filter(!is.na(se.log.OR)) %>% mutate(summary.effect = sum( log.OR/se.log.OR^2 ) / sum( 1/se.log.OR^2 )) %>% 
+  summarise(Q = sum(((log.OR - summary.effect)^2)/se.log.OR^2), n = n(), OR =  exp(min(summary.effect))) %>% 
+  mutate(p.value = 1 - pchisq(Q, df = n - 1))
+
+identical(ds$Q, ds2$Q)
+print(data_frame(metabin = ds$Q, manual = ds2$Q, ds$p.value, ds2$p.value), n = 11)
+```
+
+One example where the Qs were different:
+
+```{r}
+madata %>% filter(file.nr == 23, outcome.nr == 3, comparison.nr == 1, subgroup.nr == 3) %>% mutate(log.OR = log(effect), 
+         se.log.OR = sqrt( (1/events1) + (1/(total1 - events1)) + (1/events2) + (1/(total2 - events2)))) %>% 
+  filter(!is.na(se.log.OR) ) %>% mutate(summary.effect = sum( log.OR/se.log.OR^2 ) / sum( 1/se.log.OR^2 )) %>% 
+  select(effect, events1, events2, total1, total2, log.OR, se.log.OR, summary.effect)
+```
+
+```{r}
+
+madata %>% filter(file.nr == 23, outcome.nr == 3, comparison.nr == 1, subgroup.nr == 3) %>%
+mutate(log.OR = log(effect), 
+         se.log.OR = sqrt( (1/events1) + (1/(total1 - events1)) + (1/events2) + (1/(total2 - events2)))) %>% 
+  filter(!is.na(se.log.OR)) %>% mutate(summary.effect = sum( log.OR/se.log.OR^2 ) / sum( 1/se.log.OR^2 )) %>% 
+  summarise(Q = sum(((log.OR - summary.effect)^2)/se.log.OR^2), n = n())
+```
+
+Cochrane heterogeneity test for Risk Ratios:
+```{r}
+# madata %>% group_by(file.nr, outcome.nr, comparison.nr, subgroup.nr) %>% 
+#   filter(outcome.measure == "Risk Ratio") %>% 
+#   mutate(counts = n()) %>% filter(counts > 1) %>%
+#   mutate(log.RR = log(effect), 
+#          se.log.RR = sqrt( (total1 - events1)/(events1*total1)) + (total2 - events2)/(events2*total2)) %>% 
+#   filter(!is.na(se.log.RR)) %>% mutate(summary.effect = sum( log.RR/se.log.RR^2 ) / sum( 1/se.log.RR^2 )) %>% 
+#   summarise(Q = sum(((log.RR - summary.effect)^2)/se.log.RR^2), n = n(), RR =  exp(min(summary.effect))) %>% 
+#   mutate(p.value = 1 - pchisq(Q, df = n - 1)) %>% 
+#   ggplot(aes(x = p.value)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
+#   theme_bw() + labs(title = "Cochrane Heterogeneity Test P-values of RRs")
 ```
@@
   ggplot(aes(x = n, y = trials)) + geom_point(col = "gray15") + 
-  theme_bw() + labs(title = "Sum of Trials with Number of Replicate (Trials) >= n") + ylab("Number of trials") + xlab("n, number of replicates")
+  theme_bw() + labs(title = "Total Number of Trials with Number of Replicates >= n") + ylab("Number of trials") + xlab("n, number of replicates")
 ```

### 2019-05-30 report/chapter02.Rnw
analysis cleanup 2.

@@
 
-file.bin <- "pb.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-  load(file.path(PATH_RESULTS, file.bin))
-} else {
-  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
-  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-file.cont <- "pb.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-  load(file.path(PATH_RESULTS, file.cont))
-} else {
-  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
-  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.meta <- "meta.RData"
-if (file.exists(file.path(PATH_RESULTS, file.meta))) {
-  load(file.path(PATH_RESULTS, file.meta))
-} else {
-  meta <- pb.meta.merge(meta.bin, meta.cont)
-  save(meta, file =  file.path(PATH_RESULTS, file.meta))
-}
-
-file.cont <- "mly.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-  load(file.path(PATH_RESULTS, file.cont))
-} else {
-  data.cont <- mly.cont(data.ext, 0.05, min.study.number = 2)
-  save(data.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.bin <- "mly.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-  load(file.path(PATH_RESULTS, file.bin))
-} else {
-  data.bin <- mly.bin(data.ext, 0.05, min.study.number = 2)
-  save(data.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-load(file.path(PATH_RESULTS, file = "mly.RData"))
-load(file.path(PATH_RESULTS, file = "data.processed.RData"))
-
-require(biostatUZH)
-require(tidyverse)
-require(meta)
-require(metasens)
-require(gridExtra)
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "meta.bin.RData"))
+load(file.path(PATH_RESULTS, "meta.cont.RData"))
+load(file.path(PATH_RESULTS, "meta.surv.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
 

### 2019-05-30 report/chapter03.Rnw
analysis cleanup 2.

--- 2019-05-26 report/chapter03.Rnw
@@
 
-file.bin <- "pb.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-  load(file.path(PATH_RESULTS, file.bin))
-} else {
-  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
-  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "meta.bin.RData"))
+load(file.path(PATH_RESULTS, "meta.cont.RData"))
+load(file.path(PATH_RESULTS, "meta.surv.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
 
-file.cont <- "pb.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-  load(file.path(PATH_RESULTS, file.cont))
-} else {
-  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
-  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
+#Explanation of coding: 0 = (unsig, unsig), 1 = (unsig, sig), 2 = (sig, sig), 3 = (sig, unsig)
+sig.level <- 0.05
+meta.f <- meta.f %>% 
+	mutate(
+		pval.copas = 2*(1-pnorm(abs(est.copas/se.est.copas))),
 
-file.meta <- "meta.RData"
-if (file.exists(file.path(PATH_RESULTS, file.meta))) {
-  load(file.path(PATH_RESULTS, file.meta))
-} else {
-  meta <- pb.meta.merge(meta.bin, meta.cont)
-  save(meta, file =  file.path(PATH_RESULTS, file.meta))
-}
+		sig.fixef = ifelse(pval.fixef > sig.level, 0, 1),
+		sig.ranef = ifelse(pval.ranef > sig.level, 0, 1),
+		sig.reg.ranef = ifelse(pval.reg > sig.level, 0, 1),
+		sig.copas = ifelse(pval.copas > sig.level, 0, 1),
 
-load(file.path(PATH_RESULTS, file = "data.processed.RData"))
+		sig.change.ranef.reg = sig.change(sig.before = sig.ranef, sig.after =  sig.reg), #Function to register if significance of estimate has changed after correction
+		sig.change.ranef.copas = sig.change(sig.before = sig.ranef, sig.after =  sig.copas),
+		sig.change.fixef.reg = sig.change(sig.before = sig.fixef, sig.after =  sig.reg),
+		sig.change.fixef.copas = sig.change(sig.before = sig.fixef, sig.after =  sig.copas))
 
-require(biostatUZH)
-require(tidyverse)
-require(meta)
-require(metasens)
-require(gridExtra)
-require(xtable)
+sig.level <- 0.1
+meta.f <- meta.f %>% 
+	mutate(egger.test = ifelse(pval.peter < sig.level, 1, 0),
+				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
+				 begg.test = ifelse(pval.begg < sig.level, 1, 0),
+
+				 schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
+				 rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
+				 harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
+				 peter.test = ifelse(pval.peter < sig.level, 1, 0))
+
+meta.bin <- meta.f %>% filter(outcome.type == "bin")
+meta.cont <- meta.f %>% filter(outcome.type == "cont")
+meta.surv <- meta.f %>% filter(outcome.type == "surv")
+
+#Comparison of "original effect sizes":
+effect.diff <- meta.f %>% mutate(
+	est.fixef = ifelse(outcome.type == "bin", exp(est.fixef), est.fixef),
+	est.ranef = ifelse(outcome.type == "bin", exp(est.ranef), est.ranef),
+	est.copas = ifelse(outcome.type == "bin", exp(est.copas), est.copas),
+	est.reg = ifelse(outcome.type == "bin", exp(est.reg.ranef), est.reg.ranef)
+)
+
+effect.diff <- effect.diff %>% mutate(
+	est.fixef = ifelse(outcome.type == "bin", est.fixef - 1, est.fixef),
+	est.ranef = ifelse(outcome.type == "bin", est.ranef - 1, est.ranef),
+	est.copas = ifelse(outcome.type == "bin", est.copas - 1, est.copas),
+	est.reg = ifelse(outcome.type == "bin", est.reg.ranef - 1, est.reg.ranef),
+	fixef.ranef = ifelse(abs(est.ranef) > abs(est.fixef), "Reduction", "Amplification"),
+	fixef.copas = ifelse(abs(est.fixef) > abs(est.copas), "Reduction", "Amplification"),
+	fixef.reg = ifelse(abs(est.fixef) > abs(est.reg), "Reduction", "Amplification"),
+	fixef.copas.s = ifelse(sign(est.fixef) == sign(est.copas), "Unchanged", "Reversed"),
+	fixef.reg.s = ifelse(sign(est.fixef) == sign(est.reg), "Unchanged", "Reversed"))
+
 @

### 2019-05-30 trash/Chapter02.Rnw
analysis cleanup 2.

% LaTeX file for Chapter 02

<<echo=FALSE>>=
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'thesis/code')
source(file.path(PATH, 'prepare.R'))

require(biostatUZH)
require(tidyverse)
require(meta)
require(xtable)
@

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(
    fig.path='figure/ch02_fig',
    self.contained=FALSE,
    cache=TRUE
)
@

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch02_fig',
               echo=TRUE, message=FALSE,
               fig.width=8, fig.height=3,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@

\chapter{The Cochrane Dataset}

\subsection{Structure and Content}
The dataset consists of 5,006 reviews from the Cochrane Library. The sum of studies in the single reviews is 62,278 (some of them might being shared between reviews). In figure \ref{studies.per.review}, the empirical distribution of the number of distinct studies per review is depicted. It can be seen that while almost 400 reviews consist of one study only, there are more than 150 with equal or more than 30 distinct studies.

\begin{figure}
<<echo=FALSE>>=
madata %>% group_by(file.nr) %>% distinct(study.name) %>% count() %>%
  filter(n < 50) %>%
  full_join( madata %>% group_by(file.nr) %>% distinct(study.name) %>% count %>%
               filter(n > 49) %>% mutate(n = 50)) %>%
  group_by(n) %>% count() %>%
  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Study Number per Review") + xlab("Study number") + ylab("Number of reviews")
@
\caption{Empirical distribution of number of studies per review.}
\label{studies.per.review}
\end{figure}

% (DOI: 10.1002/14651858.CD000033.pub2). 
The research question of a review can often be further subdivided into multiple research subjects or comparisons. As an example, consider a review about barbiturate effect on head injuries: there are different drugs of the barbiturate class that can again be compared to different alternatives (as other drugs or placebo). Therefore, the studies in a review often have their own research subject. Again, figure \ref{subjects.per.review} provides an illustration of the distribution of the number of different research subjects or comparisons per review.

\begin{figure}
<<echo=FALSE>>=
madata %>% group_by(file.nr) %>% distinct(comparison.name) %>% count() %>%
  filter(n < 15) %>%
  full_join( madata %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
               filter(n > 14) %>% mutate(n = 15)) %>%
  group_by(n) %>% count() %>%
  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Research Subject Number per Review") + xlab("Research subject number") + ylab("Number of reviews")

mean.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
  ungroup() %>% group_by(file.nr) %>% 
  count() %>% ungroup %>% summarise(mean = mean(n))

median.diff.out <- madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
  ungroup() %>% group_by(file.nr) %>% 
  count() %>% ungroup %>% summarise(mean = median(n))
@
\caption{Empirical distribution of number of different research subjects per review.}
\label{subjects.per.review}
\end{figure}

Despite that studies within a review compare the same things/interventions, they could still be different with respect to their outcome. For example, in the case of the barbiturate and head injury review, different measurements of mortality (e.g. after 6 or 12 months) could be considered. Considering this, one might want to look at the distribution of number of different outcomes within a review (given that the research subject is the same). If one sums up the number of different outcomes given that they share the research subject, the empirical distribution of the sums per review can be seen in figure \ref{outcomes.per.review}. It is necessary to consider the research subject, because it can be that the outcome is the same (mortality after ..) but not the research subject (other barbiturate). One can see that the heterogeneity considering research subjects and outcomes between reviews is considerably large. Almost 500 reviews have more than 50 different study settings, i.e. different research subjects and outcome measures. The mean number of different outcome measures is \Sexpr{round(mean.diff.out,2)} and the median \Sexpr{median.diff.out}.

\begin{figure}
<<echo=FALSE>>=
madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
  ungroup() %>% group_by(file.nr) %>%
  count() %>% filter(n < 50) %>%
  full_join( madata %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% ungroup() %>% group_by(file.nr) %>%
               count() %>% filter(n > 49) %>% mutate(n = 50)) %>%
  group_by(n) %>% count() %>%
  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Outcome Number per Review") + xlab("Outcome number") + ylab("Number of reviews")

mean.diff.subg <- madata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% distinct(subgroup.name) %>% 
  ungroup() %>% group_by(file.nr) %>% 
  count() %>% ungroup() %>% summarise(mean = mean(n))

median.diff.subg <- madata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% distinct(subgroup.name) %>% 
  ungroup() %>% group_by(file.nr) %>% 
  count() %>% ungroup() %>% summarise(median = median(n))

@
\caption{Empirical distribution of number of outcomes per subject per review.}
\label{outcomes.per.review}
\end{figure}

Still it could be that studies with the same research subjects and the same outcome differ in important details. An example for such details could be the exact dosage of barbiturate or its application to a specific age group. Such further details specify subgroups in the dataset. Another important property of the dataset is how many subgroups are present in a review (given that they share research subject and outcome). This is shown in figure \ref{subgroups.per.review}. We can see that compared to figure \ref{outcomes.per.review}, we have to further adjust our idea of heterogeneity within reviews towards larger experimental design diversity within a review: most reviews bear quite a lot more than 20 experimental setups. The mean subgroup number is \Sexpr{round(mean.diff.subg,2)} and the median \Sexpr{median.diff.subg}.

\begin{figure}
<<echo=FALSE>>=
madata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% distinct(subgroup.name) %>% 
  ungroup() %>% group_by(file.nr) %>% 
  count() %>% filter(n < 100) %>%
  full_join( madata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% distinct(subgroup.name) %>% 
               ungroup() %>% group_by(file.nr) %>% 
               count() %>% filter(n > 99) %>% mutate(n = 100)) %>%
  ggplot(aes(x = n)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Subgroup Number per Review") + xlab("Subgroup number") + ylab("Number of reviews")
@
\caption{Empirical distribution of the number of subgroups per review (given that they share subject and outcome).}
\label{subgroups.per.review}
\end{figure}

To summarize what has been described up to now, the structure of a review as provided in the dataset is presented visually as in figure \ref{review.structure}.
Experimental data of studies in a review can be subdivided into different research subjects, different outcomes and different subgroups.

\begin{figure}
\tikzstyle{every node}=[draw=black,thick,anchor=west]
\tikzstyle{selected}=[draw=red,fill=red!30]
\tikzstyle{optional}=[dashed,fill=gray!50]
\begin{tikzpicture}
[grow = right, anchor = west, 
  growth parent anchor=east, % added code
  parent anchor=east]
  \node {Review} [edge from parent fork right]
    child { node {Comparison 2}
      child { node {Outcome 2}}
      child { node {Outcome 1}
        child { node {Subgroup 2}}
        child { node {Subgroup 1}}}
    }
    child [missing] {}		
    child { node {Comparison 1  }};
\end{tikzpicture}
\caption{Structure of a hypothetical review with two different comparisons.}
\label{review.structure}
\end{figure}

The data that is given in different outcomes and different subgroups must not necessarily stem from different studies. It can be that the authors of the study did measure multiple outcomes or further divide their groups into subgroups for special analyses. To illustrate this, the previously mentioned barbiturate review is explained in detail for the matter to become more understandable.

\vspace{0mm}
Lets consider the previously mentioned barbiturate and head injury review. The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates''. The medical background is that one knew that barbiturates could cause relief in intra-cranial pressure, but also reduce cerebral blood flow. Because one effect is thought to be beneficial for persons with severe head injuries while the other isn't, the authors of the review wanted to find out if there is a net benefit of barbiturates.

\vspace{0mm}
The review comprises five studies in total. Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental, which would be the comparison/research subject to speak in the previously introduced notions.

\vspace{0mm}
All the studies convey multiple information to the review. As an example, that could be death or death \textit{and} severe disability at follow up as an outcome. Again, the study can be further split up in different subgroups, here for example in a group with - and without haematoma.

\vspace{0mm}
The complete listing of outcomes is in table \ref{barbiturates}. The table also gives an illustration of the variety of data that can be included in a review. We have for example continuous and binary outcome data, that again is divided into a variety of different things that have been measured. Often, additionally to the main study result, also adverse effects are for example included which are in this case separate outcomes and possibly subgroups.

<<echo=FALSE, results='asis'>>=
tp1 <- arrange(filter(madata, file.nr == 21) %>% 
          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study)
tp1[tp1$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
print(xtable(tp1, label = "barbiturates", caption = "Barbiturate and head injury review listing of studies, their research subjects and outcomes"), include.rownames = F, size = "footnotesize")
@

The research subject or outcome type can possibly already be well defined in the general review question. Conversely, research subject or comparison has to be further specified in outcome and subgroup categories. As may have been implied, the terminology does not rely to a hundred percent on strict functional definitions.

% The categories that have been brung up und are used throughout the report do not necessarily represent precisely what their name implies. They are rather functional indicators of the similarity of the data, i.e. the experiment or data collection that resulted in the data. It might well be that a review uses the classifier ``research subject'' already to distinguish dosages, or conversely that a ``subgroup'' comes with a very important difference between data (not as the name would suggest). As an example, serious concerns about biasness of the results could have prompted the review authors to classify some data in a different subgroup.
% 
% \vspace{0mm}
% However, the categories are reliable in general such that outcome really means most often the outcome of the study. The dataset covers a large variety of topics such as clinical research or prevention measures and corporal activity, and therefore, also the subdivision of topics and the data is heterogeneous to some extent.

\vspace{0mm}
After this rough description of the scope of the dataset, a more detailed and complete description has to be made. Speaking in very broad terms, the dataset is set up such that each observation is a comparison between two groups, which are most often interventions, which are further specified by additional variables. Their similarity with respect to experimental design compared to other studies in the review is specified by additional variables.  
%Considering those variables, one can find conceptually meaningful (~ identical) comparisons, i.e. comparisons that are sufficiently homogeneous in experimental design and data collection.

\vspace{0mm}
In technical terms, the dataset is rather large data frame with 463,820 rows and 25 columns. It is structured after the tidy format, meaning that every row is an ``observation'' (here: results from a study) and each column a variable, so some form of classification or property of the observation, as for example study name etc.
In general, there are variables that describe properties of the review, i.e. are on the level of the review, and variables that describe properties of the comparisons and are therefore on the level of the study data. Both are listed and explained in table \ref{variables}.

\begin{table}%[h!]
  \begin{center}
    \label{Variables}
    \begin{tabular}{l l}
      \textbf{Variable} & \textbf{Description}\\
      \hline
      \textbf{File name} & The name of the file from which the review data has been . \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
      \textbf{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
      \textbf{File index} & Internal index of the file in the Cochrane library.\\
      \textbf{File version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
      %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
      \hline
      \textbf{Comparison} & Specification of the interventions compared in the study\\
      \textbf{Outcome} & Specification by which outcome the interventions are compared\\
      \textbf{Subgroup} & Potentially indication of affiliation to subgroups\\
      \textbf{Study name} & Name of the study to which the comparison belongs\\
      \textbf{Study publication year} & Year in which the study was published\\
      \textbf{Outcome measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
      \textbf{Effect} & Measure of the effect given in the quantity denoted by \\ &``outcome measure''.\\
      \textbf{Events (1/2)} & The counts of patients with an outcome if\\ & measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
      \textbf{Total (1/2)} & Number of patients in groups.\\
      \textbf{Mean (1/2)} & Mean of patient measurements if outcome is continuous.\\
      \textbf{Standard deviation (1/2)} & Standard deviation of mean.\\
    \end{tabular}
  \caption{Dataset variable descriptions}
  \end{center}
\end{table}

One might be interested in the distribution of some of the mentioned variables in the dataset. For example, the variety of different outcome measures types could partly impose problems since they are not easily comparable. The eight most abundant outcome measures are given in figure \ref{study.outcomes}

\begin{figure}
<<echo=FALSE>>=
yodata %>% group_by(outcome.measure) %>% count() %>% arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9) %>% 
  ggplot(aes(x = outcome.measure, y = n)) +
  geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Outcome measure frequencies") + xlab("Frequency") + ylab("Outcome measure")
@
\caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded.}
\label{study.outcomes}
\end{figure}

Since standards in trial design and research in general are also not independent of time, also the distribution of study publication years of the studies are given in figure \ref{study.years}.

\begin{figure}
<<echo=FALSE>>=
madata %>% filter(study.year < 2019 & study.year > 1920) %>% ggplot(aes(x = study.year)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Study publication year frequency") + xlab("Year") + ylab("Frequency")
@
\caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications.}
\label{study.years}
\end{figure}

The frequency of missing or erroneous variables is also important. No missing values can be reported for variables as research subject, outcome and subgroup name. Table \ref{missing.table} presents five fractions of missing or erroneous variables in the dataset. Note that an event count equal to zero is per se not erroneous, but can cause computation issues if not taken into account, therefore it is also included. The difference between zero and missing event counts specified in the table refer to the situations where only one event count is zero versus both event counts being zero (``missing'').

<<echo=FALSE>>=
missing.mean <- madata %>% filter(!is.na(sd1) & sd1 > 0) %>% filter(!is.na(sd2) & sd2 > 0) %>% 
  summarise(total = length(sd1), na  = sum(is.na(mean1) | is.na(mean1))) %>% mutate(f = na/total) %>% select(f)

missing.sd <- madata %>% filter(!is.na(mean1) & !is.na(mean2)) %>% filter(mean1 != 0 & mean2 != 0) %>%
  summarise(total = length(mean1), na.sd  = sum(is.na(sd1) | is.na(sd1)), null.sd = length(sd1[sd1 <= 0 | sd2 <= 0])) %>% 
  mutate(f = (na.sd + null.sd)/total) %>% select(f)

missing.ssize <- madata %>% summarize(total = length(total1), null.ss = length(total1[total1 <= 0 | total2 <= 0])) %>% 
  mutate(f = null.ss / total) %>% select(f)

missing.events <- madata %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
  filter(is.na(sd1) | sd1 <= 0) %>% filter(is.na(sd2) | sd2 <= 0) %>% 
  summarise(null.ev = length(total1[events1 <= 0 & events2 <= 0]), total = length(events1)) %>% mutate(f = null.ev/total) %>% select(f)

null.events <- madata %>% filter(is.na(mean1) | mean1 == 0) %>% filter(is.na(mean2) | mean2 == 0) %>% 
  filter(is.na(sd1) | sd1 <= 0) %>% filter(is.na(sd2) | sd2 <= 0) %>% 
  summarise(null.ev = length(total1[events1 <= 0 | events2 <= 0]), total = length(events1)) %>% mutate(f = null.ev/total) %>% select(f)

missing.table <- rbind("missing mean value fraction (among all data with standard devitations)" = missing.mean,
                       "missing standard deviations (among all data with means)" = missing.sd,
                       "missing sample size" = missing.ssize,
                       "missing events (among all data with no mean and standard deviation)" = missing.events,
                       "missing or zero events (among all data with no mean and standard deviation)" = null.events)
@

<<echo=FALSE, results='asis'>>=
print(xtable(missing.table, label = "missing.table", caption = "Fraction of some erronous and missing variables", align = "lr"), include.colnames = F, size = "small")
@

One particular question that remains is how many identical comparisons, i.e. comparisons with same outcome (and potentially same subgroup) there are. This is shown in figure \ref{repr.trials}. The identical comparisons can just be called reproduction trials.

% \begin{figure}
% <<echo=FALSE>>=
% yodata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
%   filter(n < 20) %>%
%   full_join( yodata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
%                filter(n > 19) %>% ungroup %>% summarise(n = 20, nn = sum(nn))) %>%
%   ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
%   theme_bw() + labs(title = "Number of groups with number of reproduction trials = n (ignoring subgroups)") + xlab("n") + ylab("Number of groups")
% @
% \caption{Number of groups with n identical experiments or reproduction trials. Groups with more than 20 identical experiments are summed up in n = 20.
% Subgroups have not been taken into account for assessment of trial homogeneity.}
% \label{repr.trials}
% \end{figure}

\begin{figure}
<<echo=FALSE>>=
yodata %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
  filter(n < 20) %>%
  full_join( yodata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
               filter(n > 19) %>% ungroup %>% summarise(n = 20, nn = sum(nn))) %>%
  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Number of groups with number of reproduction trials = n") + xlab("n") + ylab("Number of groups")
@
\caption{Number of groups with n identical experiments or reproduction trials. Groups with more than 20 identical experiments are summed up in n = 20.
Subgroups have been taken into account for assessment of trial homogeneity.}
\label{sum.repr.trials}
\end{figure}

Since the availability of a certain number of reproduction trial groups might be of special interest (as some sort of sample size for statistical tests with the groups), the cumulative number of groups with number of reproduction trials larger or equal than $n$ is listed in table \ref{repr.groups}.

<<echo=FALSE, results='asis'>>=
cum.repr.trials <- yodata %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
  filter(n < 15) %>%
  full_join( yodata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
  ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)

colnames(cum.repr.trials)  <- c("n", "", "Cumulative sum")

print(xtable(cum.repr.trials[,-2], label = "repr.groups", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llr", digits = 0), include.rownames = F, size = "footnotesize")
@

% The same data but with the cumulative sum of groups for $n$ being larger or equal the number of reproduction trials can also be of interest, therefore this is shown in figure \ref{cumsum.repr.trials}. 
% 
% \begin{figure}
% <<echo=FALSE>>=
% yodata %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
%   filter(n < 20) %>%
%   full_join( yodata %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
%                filter(n > 19) %>% ungroup %>% summarise(n = 20, nn = sum(nn))) %>% 
%   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% 
%   ggplot(aes(x = n, y = csum)) + geom_point(col = "gray15", fill = "dodgerblue") +
%   theme_bw() + labs(title = "Number of groups with number of reproduction trials >= n") + xlab("n") + ylab("Number of groups")
% @

% \subsection{General Properties according to the Cochrane Guidelines}
% 
% It has already been mentioned that Cochrane tries to ensure quality of its review by the application of protocols and guidelines. Those protocols are open to the public. From those guidelines, it is tried to further infer properties of the dataset. The information is all taken from version 5.1.0 of the Handbook for Systematic Reviews of Interventions \Citep{cochrane.handbook}.
% 
% \vspace{0mm}
% The handbook provides not strict rules, but guidelines to the review authors. However, there is a basic principle that all groups should follow: the scientific question of the review, the objectives and the inclusion criteria for studies have to be pre-specified. A review protocoll has therefore to be published in advance. This is important because it supposedly prevents the authors from going back and forth between data and conclusions when for example the conclusions do not match the expectations, and makes therefore the results more reliable. 
% 
% \vspace{0mm}
% Also it imposes a code of conduct to avoid potential financial conflicts of interest. Funding of the reviews as well as of the studies included is made public and there are steering groups that are responsible for tracking down possible conflicts of interests.
% 
% \vspace{0mm}

% So in terms of outcome, there are 10 different outcomes within the review. For example, mortality after different time spans and intracranial pressure after treatment are considered, but also mean body temperature (after treatment). One study contritubes with 5 different outcomes to the study. 
% 
% \vspace{0mm}
% In general, no subgroups are present within the studies or outcomes, with one exception. The study that compares Barbiturates with Mannitol is divided into two subgroups with patients with and without haematoma.   
% 
% \vspace{0mm}

% Maybe it is the methods section. Here however, we give a couple hints.
% Note that you can wisely use \rr{preamble}-chunks. Minimal, is likely:
% 
% \bigskip
% 
% \hrule
% <<echo=TRUE>>=
% library(knitr)
% opts_chunk$set(
%     fig.path='figure/ch02_fig',
%     self.contained=FALSE,
%     cache=TRUE
% )
% @
% \hrule
% 
% \bigskip
% 
% Defining figure options is very helpful:
% 
% 
% \bigskip
% 
% 
% \hrule
% <<echo=TRUE>>=
% library(knitr)
% opts_chunk$set(fig.path='figure/ch02_fig',
%                echo=TRUE, message=FALSE,
%                fig.width=8, fig.height=2.5,
%                out.width='\\textwidth-3cm',
%                message=FALSE, fig.align='center',
%                background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
%                cache=TRUE
% )
% options(width=74)
% @
% \hrule
% 
% \bigskip
% 
% Notice how in Figure~\ref{f02:1} everything is properly scaled.
% 
% \begin{figure}
% <<echo=FALSE>>=
% par(mai=c(.8,.8,.1,.1))
% set.seed(12)
% plot( runif(30), type='l')
% @
%   \caption{Test figure to illustrate figure options used by knitr.}
%   \label{f02:1}
% \end{figure}

### 2019-05-30 trash/latex.trash.Rnw
analysis cleanup 2.

\documentclass{article}

\begin{document}

A histogram of publication dates of the studies included in the dataset is shown in Figure \ref{study.years}. A large part of studies has been published after 2000, and very few before 1960. Only 18 studies published in 2018 are included.

\begin{figure}
<<echo=FALSE>>=
  data %>% filter(study.year < 2019 & study.year > 1920) %>% ggplot(aes(x = study.year)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + xlab("Year") + ylab("Study frequency")
@
  \caption{Frequencies of study publication years in the dataset. 44655 were excluded due to likely wrong indications}
\label{study.years}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Figure \ref{study.outcomes} provides the frequencies of outcome types of the comparisons. Note that the abundance of mean differences and standardized mean differences can also give an impression of the proportion of continuous outcome comparisons vs. binary outcome comparisons in the dataset.

\begin{figure}
<<echo=FALSE>>=
  data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9) %>% 
  ggplot(aes(x = outcome.measure.new, y = n)) +
  geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() + ylab("Comparison frequency") + xlab("Outcome measure")
@
  \caption{Frequencies of some outcome measures for the effects in the dataset. 5593 measures with other outcome measures are excluded}
\label{study.outcomes}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<>>=
study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count() %>%
  filter(n < 50) %>%
  full_join( data %>% group_by(file.nr) %>% distinct(study.name) %>% count %>%
               filter(n > 49) %>% mutate(n = 50)) %>%
  group_by(n) %>% count()

comparison.freq <- data %>% group_by(file.nr) %>% count() %>%
  filter(n < 50) %>%
  full_join( data %>% group_by(file.nr) %>% count %>%
               filter(n > 49) %>% mutate(n = 50)) %>%
  group_by(n) %>% count()

study.comp.freq <- merge(x = study.freq, y = comparison.freq, by = "n")
names(study.comp.freq) <- c("n", "studies", "comparisons")

study.comp.freq <- study.comp.freq %>% gather(key = "type", value = "total", studies:comparisons) 
@

The numbers of studies and comparisons per review can be seen in Figure \ref{review.study/comparison.frequencies}. A certain amount of reviews is comprised of single studies and single comparisons only. Most reviews have fewer than 50

\begin{figure}
<<echo = FALSE>>=
study.comp.freq %>%  
  ggplot(aes(x = n, y = total)) + geom_col() + facet_wrap(~type, scales = "free") + theme_bw() +
  scale_x_continuous(labels = c("0", "10", "20", "30", "40", ">=50"))
@
\caption{Frequencies of studies and comparisons per review. Comparisons are shown on the right-hand plot and studies on the left-hand plot. Note the difference in the scales.}
\label{review.study/comparison.frequencies}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
It is also possible to look at the properties of the reviews. One question could be how many studies or comparisons that a review comprises. The former is shown in Figure \ref{studies.per.review} and the latter in Figure \ref{comparisons.per.review}. It can be seen that while almost 400 reviews consist of one study only, there are more than 150 with equal or more than 30 distinct studies. A similar variance between reviews can also be observed when looking at the number of comparisons.

\begin{figure}
<<echo=FALSE>>=
data %>% group_by(file.nr) %>% distinct(study.name) %>% count() %>%
  filter(n < 50) %>%
  full_join( data %>% group_by(file.nr) %>% distinct(study.name) %>% count %>%
               filter(n > 49) %>% mutate(n = 50)) %>%
  group_by(n) %>% count() %>%
  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() + xlab("Study number") + ylab("Reviews Frequency")
@
\caption{Empirical distribution of number of studies per review}
\label{studies.per.review}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
data %>% group_by(file.nr) %>% count() %>%
  filter(n < 50) %>%
  full_join( data %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
               filter(n > 49) %>% mutate(n = 50)) %>%
  group_by(n) %>% count() %>%
  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() +  xlab("Comparisons") + ylab("Review Frequency")
@
\caption{Empirical distribution of number of comparisons per review}
\label{comparisons.per.review}
\end{figure}

A question not to be mistaken with the previous would be how many comparison \textit{types} there are per review. This gives an additional impression of the scope of a review. Analogously to the previous figures, the empirical distribution of comparison types is depicted in Figure \ref{subjects.per.review}.

\begin{figure}
<<echo=FALSE>>=
data %>% group_by(file.nr) %>% distinct(comparison.name) %>% count() %>%
  filter(n < 15) %>%
  full_join( data %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
               filter(n > 14) %>% mutate(n = 15)) %>%
  group_by(n) %>% count() %>%
  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
  theme_bw() +  xlab("Comparison type number") + ylab("Review frequency")

mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
  ungroup() %>% group_by(file.nr) %>% 
  count() %>% ungroup %>% summarise(mean = mean(n))

median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>% 
  ungroup() %>% group_by(file.nr) %>% 
  count() %>% ungroup %>% summarise(mean = median(n))
@
\caption{Empirical distribution of number of different comparison types per review}
\label{subjects.per.review}
\end{figure}

% At the end, a main goal of the thesis is to analyze reviews with respect to reporting bias in meta analyses.

### 2019-05-30 code/Unused.R

@@ -1,762 +1,0 @@
-rm(list = ls())
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'Data/PubBias')
-PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2018-06-09.csv'
-PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-file_results = "pb.RData"
-
-source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-file.dat <- "data.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.dat <- "data.processed.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data.ext2 = pb.process2(data)
-	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.bin <- "pb.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-	load(file.path(PATH_RESULTS, file.bin))
-} else {
-	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
-	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-file.cont <- "pb.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-	load(file.path(PATH_RESULTS, file.cont))
-} else {
-	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
-	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.meta <- "meta.RData"
-if (file.exists(file.path(PATH_RESULTS, file.meta))) {
[…]

### 2019-05-30 code/additional_plots.R

@@ -1,0 +1,369 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "meta.bin.RData"))
+load(file.path(PATH_RESULTS, "meta.cont.RData"))
+load(file.path(PATH_RESULTS, "meta.surv.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+
+
+
+#Explanation of coding: 0 = (unsig, unsig), 1 = (unsig, sig), 2 = (sig, sig), 3 = (sig, unsig)
+sig.level <- 0.05
+meta.f <- meta.f %>% 
+	mutate(
+		pval.copas = 2*(1-pnorm(abs(est.copas/se.est.copas))),
+		
+		sig.fixef = ifelse(pval.fixef > sig.level, 0, 1),
+		sig.ranef = ifelse(pval.ranef > sig.level, 0, 1),
+		sig.reg.ranef = ifelse(pval.reg > sig.level, 0, 1),
+		sig.copas = ifelse(pval.copas > sig.level, 0, 1),
+		
+		sig.change.ranef.reg = sig.change(sig.before = sig.ranef, sig.after =  sig.reg), #Function to register if significance of estimate has changed after correction
[…]

### 2019-05-30 code/adjustment.R

@@ -1,464 +1,0 @@
-rm(list = ls())
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'Data/PubBias')
-PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2018-06-09.csv'
-PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-file_results = "pb.RData"
-
-source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-file.dat <- "data.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.dat <- "data.processed.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data.ext2 = pb.process2(data)
-	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.bin <- "pb.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-	load(file.path(PATH_RESULTS, file.bin))
-} else {
-	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
-	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-file.cont <- "pb.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-	load(file.path(PATH_RESULTS, file.cont))
-} else {
-	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
-	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.meta <- "meta.RData"
-if (file.exists(file.path(PATH_RESULTS, file.meta))) {
[…]

### 2019-05-30 code/analysis_plots.R

@@ -1,0 +1,364 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "meta.bin.RData"))
+load(file.path(PATH_RESULTS, "meta.cont.RData"))
+load(file.path(PATH_RESULTS, "meta.surv.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+
+
+################################################################################################
+################################################################################################
+#PROPORTION OF SIGNIFICANT PUBLICATION BIAS TESTS
+################################################################################################
+################################################################################################
+
+sig.level <- 0.1
+meta.f <- meta.f %>% 
+	mutate(egger.test = ifelse(pval.peter < sig.level, 1, 0),
+				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
+				 begg.test = ifelse(pval.begg < sig.level, 1, 0),
+				 
+				 schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
+				 rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
+				 harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
+				 peter.test = ifelse(pval.peter < sig.level, 1, 0))
+
[…]

### 2019-05-30 code/correctures.R

@@ -1,377 +1,0 @@
-rm(list = ls())
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'Data/PubBias')
-PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2018-06-09.csv'
-PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-file_results = "pb.RData"
-
-source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-file.dat <- "data.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.dat <- "data.processed.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data.ext2 = pb.process2(data)
-	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.bin <- "pb.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-	load(file.path(PATH_RESULTS, file.bin))
-} else {
-	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
-	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-file.cont <- "pb.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-	load(file.path(PATH_RESULTS, file.cont))
-} else {
-	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
-	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.meta <- "meta.RData"
-if (file.exists(file.path(PATH_RESULTS, file.meta))) {
[…]

### 2019-05-30 code/explore.R

@@ -23,99 +23,69 @@ if (file.exists(file.path(PATH_RESULTS, file.dat))) {
 	save(data, file =  file.path(PATH_RESULTS, file.dat))
 }
 
-file.dat <- "data.processed.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data.ext2 = pb.process2(data)
-	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.bin <- "pb.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-	load(file.path(PATH_RESULTS, file.bin))
-} else {
-	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
-	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-file.cont <- "pb.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-	load(file.path(PATH_RESULTS, file.cont))
-} else {
-	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
-	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.meta <- "meta.RData"
-if (file.exists(file.path(PATH_RESULTS, file.meta))) {
-	load(file.path(PATH_RESULTS, file.meta))
-} else {
-	meta <- pb.meta.merge(meta.bin, meta.cont)
-	save(meta, file =  file.path(PATH_RESULTS, file.meta))
-}
-
-load(file.path(PATH_RESULTS, "meta.complete.RData"))
-
-
-#Applying test and adjustment criteria:
-metac.bin <- meta.bin %>% filter(n.sig.single > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
-metac.cont <- meta.cont %>% filter(n.sig.single > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
-metac <- meta %>% filter(n.sig.single > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
[…]

### 2019-05-30 code/meta_connect.R

@@ -1,116 +1,0 @@
-rm(list = ls())
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'Data/PubBias')
-PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2018-06-09.csv'
-PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-file_results = "pb.RData"
-
-source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-file.dat <- "data.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-data.ext2 <- pb.process2(data)
-
-meta.surv <- meta.surv.complete2(data = data.ext2, sig.level = 0.1, min.study.number = 10)
-meta.bin <- meta.bin.complete2(data = data.ext2, sig.level = 0.1, min.study.number = 10, sm1 = "RR")
-meta.cont <- meta.cont.complete2(data = data.ext2, sig.level = 0.1, min.study.number = 10)
-
-meta <- bind_rows(meta.bin, meta.cont, meta.surv)
-
-metac.bin <- meta.bin %>% filter(n.sig.single > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
-metac.cont <- meta.cont %>% filter(n.sig.single > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
-metac <- meta %>% filter(n.sig.single > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
-
-
-
-#Adding adjusted correlation and z-score treatment effects:
-tmp <- data.ext2
-
-meta.id.vector <- metac$meta.id
-meta.id.vector <- meta.id.vector[-which(meta.id.vector == 159329)]
-meta.analyses <- list()
[…]

### 2019-05-30 code/meta_ct_surv.R

@@ -1,279 +1,0 @@
-rm(list = ls())
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'Data/PubBias')
-PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2018-06-09.csv'
-PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-file_results = "pb.RData"
-
-source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-file.dat <- "data.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.dat <- "data.processed.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data.ext2 = pb.process2(data)
-	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.bin <- "pb.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-	load(file.path(PATH_RESULTS, file.bin))
-} else {
-	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
-	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-file.cont <- "pb.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-	load(file.path(PATH_RESULTS, file.cont))
-} else {
-	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
-	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.meta <- "meta.RData"
-if (file.exists(file.path(PATH_RESULTS, file.meta))) {
[…]

### 2019-05-30 code/training_test_data.R

@@ -1,0 +1,86 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "meta.bin.RData"))
+load(file.path(PATH_RESULTS, "meta.cont.RData"))
+load(file.path(PATH_RESULTS, "meta.surv.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+
+
+
+
+#Binary data examples:
+meta1 <- data %>% filter(file.nr == 8 & comparison.nr == 1 & outcome.nr == 1 & subgroup.nr == 1)
+meta2 <- data %>% filter(file.nr == 76 & comparison.nr == 2 & outcome.nr == 2 & subgroup.nr == 4)
+meta3 <- data %>% filter(file.nr == 953 & comparison.nr == 2 & outcome.nr == 4 & subgroup.nr == 1)
+meta4 <- data %>% filter(file.nr == 944 & comparison.nr == 12 & outcome.nr == 6 & subgroup.nr == 4)
+meta5 <- data %>% filter(file.nr == 544 & comparison.nr == 1 & outcome.nr == 1 & subgroup.nr == 3)
+
+metay.1 <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, sm= "OR", data = meta1)
[…]

### 2019-05-30 code/zscore_correlation_adjustment.R

@@ -1,194 +1,0 @@
-rm(list = ls())
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'Data/PubBias')
-PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2018-06-09.csv'
-PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-file_results = "pb.RData"
-
-source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-file.dat <- "data.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.dat <- "data.processed.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data.ext2 = pb.process2(data)
-	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.bin <- "pb.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-	load(file.path(PATH_RESULTS, file.bin))
-} else {
-	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
-	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-file.cont <- "pb.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-	load(file.path(PATH_RESULTS, file.cont))
-} else {
-	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
-	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.meta <- "meta.RData"
-if (file.exists(file.path(PATH_RESULTS, file.meta))) {
-	load(file.path(PATH_RESULTS, file.meta))
-} else {
[…]

### 2019-05-30 code_excess/Metaly.R

@@ -23,331 +23,69 @@ if (file.exists(file.path(PATH_RESULTS, file.dat))) {
 	save(data, file =  file.path(PATH_RESULTS, file.dat))
 }
 
-file.dat <- "data.processed.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data.ext2 = pb.process2(data)
-	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.bin <- "pb.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-	load(file.path(PATH_RESULTS, file.bin))
-} else {
-	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
-	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-file.cont <- "pb.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-	load(file.path(PATH_RESULTS, file.cont))
-} else {
-	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
-	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.meta <- "meta.RData"
-if (file.exists(file.path(PATH_RESULTS, file.meta))) {
-	load(file.path(PATH_RESULTS, file.meta))
-} else {
-	meta <- pb.meta.merge(meta.bin, meta.cont)
-	save(meta, file =  file.path(PATH_RESULTS, file.meta))
-}
-
-load(file.path(PATH_RESULTS, "meta.complete.RData"))
-
-
-#Applying test and adjustment criteria:
-metac.bin <- meta.bin %>% filter(n.sig.single > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
-metac.cont <- meta.cont %>% filter(n.sig.single > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
-metac <- meta %>% filter(n.sig.single > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
[…]

### 2019-05-30 code_excess/explore.R

@@ -1,269 +1,0 @@
-load(file = "cochrane.RData")
-load(file = "yodata.RData")
-
-require(tidyverse)
-require(biostatUZH)
-
-#Look at Migraine sympton relieve review
-arrange(filter(madata, file.name=="MYdwnld_CD005220StatsDataOnly_Version2.csv") %>% 
-          select(file.nr, comparison.nr, comparison.name, outcome.nr, subgroup.nr, study.name), study.name)
-
-arrange(filter(madata, file.nr == 21) %>% 
-          select(file.nr, comparison.nr, outcome.nr, subgroup.nr, study.name), study.name)
-
-arrange(filter(madata, file.nr == 21) %>% 
-          select(file.nr, comparison.name, outcome.name, subgroup.name, study.name), study.name)
-
-
-arrange(filter(madata, file.nr == 761) %>% 
-          select(study.name, comparison.name, outcome.name), study.name)
-
-arrange(filter(madata, file.nr == 2897) %>% 
-          select(study.name, comparison.name, outcome.name), study.name)
-
-
-#How many studies are in the dataset?
-madata %>% group_by(file.nr) %>% distinct(study.name) %>% ungroup %>% count()
-
-#Distribution of number of distinct studies per review (1: >=30):
-madata %>% group_by(file.nr) %>% distinct(study.name) %>% count() %>% 
-  filter(n < 30) %>% 
-  full_join( madata %>% group_by(file.nr) %>% distinct(study.name) %>% count %>% 
-               filter(n > 29) %>% mutate(n = 30)) %>% 
-  group_by(n) %>% count() %>% 
-  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
-  theme_bw() + labs(title = "Histogram of Study Number per Review") + xlab("Study number per review")
-
-#Number of different research subjects per review:
-madata %>% group_by(file.nr) %>% distinct(comparison.name) %>% count() %>%
-  filter(n < 50) %>%
-  full_join( madata %>% group_by(file.nr) %>% distinct(comparison.name) %>% count %>%
-               filter(n > 49) %>% mutate(n = 50)) %>%
-  group_by(n) %>% count() %>%
-  ggplot(aes(x = n, y = nn)) + geom_col(col = "gray15", fill = "dodgerblue") +
[…]

### 2019-05-30 code_excess/repbias.R

@@ -1,130 +1,0 @@
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'thesis/code')
-source(file.path(PATH, 'prepare.R'))
-
-require(tidyverse)
-require(biostatUZH)
-require(meta)
-
-#Do a Peterts Test for Publication bias for all reproduction trial groups with Odds ratios or Risk Ratios and 
-#more than 10 trials per group. 
-
-#Problem child subgroup: Metabias regression test fails because solve.default(t(X) %*% W %*% X) doesnt work.
-print(yodata %>% filter(file.nr == 3014 & outcome.nr == 3 & subgroup.nr == 1) %>% select(events1, events2, total1, total2))
-#excluded from analysis.
-
-yodata <- yodata %>% filter(file.nr != 3014)
-
-yodata %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% #filter(file.nr < 503) %>% 
-  filter(events1 > 0 | events2 > 0) %>% 
-  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-  mutate(n = n()) %>% filter(n > 9) %>% 
-  summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
-  ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-  theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-
-#Do a Eggers and Thompson Sharp and ?Begg and Mazumdar test for continuous outcomes.
-yodata %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
[…]

### 2019-06-11 communication/Complete_Analysis.Rmd
Methods update

---
title: "R Notebook"
output: html_notebook
---

This is an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*.

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r, echo=FALSE}
rm(list = ls())
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH2, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

file_results = "pb.RData"

source(file.path(PATH_CODE, 'PubBias_functions.R'))

file.dat <- "data.RData"
if (file.exists(file.path(PATH_RESULTS, file.dat))) {
	load(file.path(PATH_RESULTS, file.dat))
} else {
	data = pb.readData(path = PATH_DATA, file = FILE)
	tmp = pb.clean(data)
	data = tmp[[1]]
	aliases = tmp[[2]]
	save(data, file =  file.path(PATH_RESULTS, file.dat))
}

load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
load(file.path(PATH_RESULTS, "meta.bin.RData"))
load(file.path(PATH_RESULTS, "meta.cont.RData"))
load(file.path(PATH_RESULTS, "meta.surv.RData"))
load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
```

##Main analysis

```{r}
sig.level <- 0.1
meta.f <- meta.f %>% 
	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
				 begg.test = ifelse(pval.begg < sig.level, 1, 0),

				 schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
				 rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
				 harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
				 peter.test = ifelse(pval.peter < sig.level, 1, 0))

meta.bin <- meta.f %>% filter(outcome.type == "bin")
meta.cont <- meta.f %>% filter(outcome.type == "cont")
meta.surv <- meta.f %>% filter(outcome.type == "surv")

#Overall proportions, to be finsihed yet:
# test <- meta.f %>% group_by(outcome.type) %>% summarize(
#   schwarzer.test = mean(schwarzer.test),
#   rucker.test = mean(rucker.test),
#   harbord.test = mean(harbord.test),
#   peter.test = mean(peter.test),
#   egger.test = mean(egger.test),
#   begg.test = mean(begg.test),
#   thompson.test = mean(thompson.test))
# test <- test %>% gather(key = "test.type", value = "mean", schwarzer.test:thompson.test) 
# # test$mean[which(!is.na(test$mean))] <- round(test$mean[which(!is.na(test$mean))], 2)
# 
# #Compare proportions of total concordance vs. proportion of at least single positive test results among all
# meta.f %>% ungroup() %>% 
#   select(outcome.type, schwarzer.test, rucker.test, harbord.test, peter.test, egger.test, begg.test, thompson.test) %>% 
#   gather(key = "test.type", value = "null.hypothesis", schwarzer.test:thompson.test) %>%  
#   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
#   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
#   theme_bw() + xlab(label = NULL) + facet_wrap(~outcome.type, scales = "free") + theme(legend.position = "top") +
#   guides(fill=guide_legend(title=NULL)) 
# 
# # + annotate("text", x = test$test.type, y = 10,
# #            label = paste(round(test$mean, 2,)*100, "% rejected"),
# #            color = "white")

test.bin <- meta.bin %>% ungroup() %>% summarize(
																								 schwarzer.test = mean(schwarzer.test),
																								 rucker.test = mean(rucker.test),
																								 harbord.test = mean(harbord.test),
																								 peter.test = mean(peter.test))
test.bin <- test.bin %>% gather(key = "test.type", value = "mean")

p.bin <- meta.bin %>% ungroup() %>% 
	select(schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
	gather(key = "test.type", value = "null.hypothesis") %>%  
	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
	theme_bw() + xlab(label = NULL) + ggtitle("Binary Outcomes") + theme(legend.position = "top") +
	guides(fill=guide_legend(title=NULL))+
	annotate("text", x = test.bin$test.type, y = 500, 
					 label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
					 color = "white")

dat_text <- data.frame(
	label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
									sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test)), "< 0.1,",
								round(c(mean(meta.bin$harbord.test), mean(meta.bin$peter.test), 
												mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test)),2)*100, "%"),
	test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer"))

labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer")

p.dist.bin <- meta.bin %>% ungroup() %>% 
	select(pval.harbord, pval.peter, pval.rucker, pval.schwarzer) %>% 
	gather(key = "test.type", value = "p.value") %>% 
	ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 100, label = label), color = "black") + 
	theme(strip.text.x = element_text(size=15))

test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
																									 begg.test = mean(begg.test),
																									 thompson.test = mean(thompson.test))

test.cont <- test.cont %>% gather(key = "test.type", value = "mean")

p.cont <- meta.cont %>% ungroup() %>% 
	select(egger.test, thompson.test, begg.test) %>% 
	gather(key = "test.type", value = "null.hypothesis") %>% 
	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
	theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
	guides(fill=guide_legend(title=NULL))+
	annotate("text", x = test.cont$test.type, y = 150, 
					 label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
					 color = "white")

dat_text <- data.frame(
	label = paste(c(sum(meta.cont$begg.test), sum(meta.cont$egger.test), sum(meta.cont$thompson.test)), "< 0.1,",
								round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test)),2)*100, "%"),
	test.type   = c("pval.begg", "pval.egger", "pval.thompson"))

labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp")
p.dist.cont <- meta.cont %>% ungroup() %>% 
	select(pval.egger, pval.thompson, pval.begg) %>% 
	gather(key = "test.type", value = "p.value") %>% 
	ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + 
	facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 25, label = label),  color = "black") + 
	theme(strip.text.x = element_text(size=15))

test.surv <- meta.surv %>% ungroup() %>% summarize(egger.test = mean(egger.test),
																									 begg.test = mean(begg.test),
																									 thompson.test = mean(thompson.test))

test.surv <- test.surv %>% gather(key = "test.type", value = "mean")

p.surv <- meta.surv %>% ungroup() %>% 
	select(egger.test, thompson.test, begg.test) %>% 
	gather(key = "test.type", value = "null.hypothesis") %>% 
	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
	theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
	guides(fill=guide_legend(title=NULL))+
	annotate("text", x = test.surv$test.type, y = 150, 
					 label = paste(round(test.surv$mean, 2)*100, "% rejected"), 
					 color = "white")

dat_text <- data.frame(
	label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), sum(meta.surv$thompson.test)), "< 0.1,",
								round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), mean(meta.surv$thompson.test)),2)*100, "%"),
	test.type   = c("pval.begg", "pval.egger", "pval.thompson"))

labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp")
p.dist.surv <- meta.surv %>% ungroup() %>% 
	select(pval.egger, pval.thompson, pval.begg) %>% 
	gather(key = "test.type", value = "p.value") %>% 
	ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + 
	facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 25, label = label),  color = "black") + 
	theme(strip.text.x = element_text(size=15))

#Test agreement
agree.bin <- meta.bin %>% mutate(n.sig = peter.test + rucker.test + harbord.test + schwarzer.test) %>% 
	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + xlab("Number of significant tests") + ylab("count") + ggtitle("Binary Outcomes")

agree.cont <- meta.cont %>% mutate(n.sig = egger.test + thompson.test + begg.test) %>% 
	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")

agree.surv <- meta.surv %>% mutate(n.sig = egger.test + thompson.test + begg.test) %>% 
	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")

################################################################################################
################################################################################################
#CHANGE OF EFFECT SIZES AFTER ADJUSTMENT
################################################################################################
################################################################################################

#Comparison of z-scores:
sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
																 z.ranef = est.z.ranef/se.est.z.ranef,
																 z.reg = est.z.reg/se.est.z.reg,
																 z.copas = est.z.copas/se.est.z.copas) %>%  
	select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>% 
	group_by(method) %>% 
	summarise(significant = length(which(abs(fisher.z) > 1.96)),
						p.significant = significant/length(fisher.z))
sig.zcor <- data.frame(method = sig.zcor$method,
											 label = paste("n = ", sig.zcor$significant, ", ", round(sig.zcor$p.significant,3)*100, "% significant", sep = ""))

meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
										 z.ranef = est.z.ranef/se.est.z.ranef,
										 z.reg = est.z.reg/se.est.z.reg,
										 z.copas = est.z.copas/se.est.z.copas) %>%  
	select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>% 
	# filter(abs(fisher.z) < 10) %>% 
	ggplot(aes(x = abs(fisher.z))) + geom_histogram() + theme_bw() + facet_wrap(~method, ncol = 2) + 
	geom_vline(xintercept = 1.96, color = "red") + 
	geom_text(data = sig.zcor, aes(x = 30, y = 500, label = label), position = "dodge")

#Comparison of m.a. with copas correction method applied:
sig.zcor <- meta.f %>% filter(!is.na(est.z.copas)) %>% 
	mutate(z.fixef = est.z.fixef/se.est.z.fixef,
				 z.ranef = est.z.ranef/se.est.z.ranef,
				 z.reg = est.z.reg/se.est.z.reg,
				 z.copas = est.z.copas/se.est.z.copas) %>%  
	select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>% 
	group_by(method) %>% 
	summarise(significant = length(which(abs(fisher.z) > 1.96)),
						p.significant = significant/length(fisher.z))
sig.zcor <- data.frame(method = sig.zcor$method,
											 label = paste("n = ", sig.zcor$significant, ", ", round(sig.zcor$p.significant,3)*100, "% significant", sep = ""))

meta.f %>% filter(!is.na(est.z.copas)) %>% 
	mutate(z.fixef = est.z.fixef/se.est.z.fixef,
				 z.ranef = est.z.ranef/se.est.z.ranef,
				 z.reg = est.z.reg/se.est.z.reg,
				 z.copas = est.z.copas/se.est.z.copas) %>%  
	select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>% 
	# filter(abs(fisher.z) < 10) %>% 
	ggplot(aes(x = abs(fisher.z))) + geom_histogram() + theme_bw() + facet_wrap(~method, ncol = 2) + 
	geom_vline(xintercept = 1.96, color = "red") + 
	geom_text(data = sig.zcor, aes(x = 10, y = 125, label = label), position = "dodge")

#Comparison of "original effect sizes":
effect.diff <- meta.f %>% mutate(
	est.fixef = ifelse(outcome.type == "bin", exp(est.fixef), est.fixef),
	est.ranef = ifelse(outcome.type == "bin", exp(est.ranef), est.ranef),
	est.copas = ifelse(outcome.type == "bin", exp(est.copas), est.copas),
	est.reg = ifelse(outcome.type == "bin", exp(est.reg), est.reg)
)

effect.diff <- effect.diff %>% mutate(
	est.fixef = ifelse(outcome.type == "bin", est.fixef - 1, est.fixef),
	est.ranef = ifelse(outcome.type == "bin", est.ranef - 1, est.ranef),
	est.copas = ifelse(outcome.type == "bin", est.copas - 1, est.copas),
	est.reg = ifelse(outcome.type == "bin", est.reg - 1, est.reg),
	fixef.ranef = ifelse(abs(est.ranef) > abs(est.fixef), "Reduction", "Amplification"),
	fixef.copas = ifelse(abs(est.fixef) > abs(est.copas), "Reduction", "Amplification"),
	fixef.reg = ifelse(abs(est.fixef) > abs(est.reg), "Reduction", "Amplification"),
	fixef.copas.s = ifelse(sign(est.fixef) == sign(est.copas), "Unchanged", "Reversed"),
	fixef.reg.s = ifelse(sign(est.fixef) == sign(est.reg), "Unchanged", "Reversed"))

effect.diff <- effect.diff %>% 
  mutate(change.fixef.copas = ifelse(fixef.copas == "Reduction", -abs(est.fixef - est.copas),
                                     abs(est.fixef - est.copas)),
         change.fixef.reg = ifelse(fixef.ranef == "Reduction", -abs(est.fixef - est.reg),
                                   abs(est.fixef - est.reg)))

# hist.ranef <- effect.diff %>% ggplot(aes(x = abs(est.fixef - est.ranef))) +
# 	geom_histogram() + facet_grid(~factor(fixef.ranef)) + xlim(0, 2) + xlab("Effect difference") + 
# 	theme_bw() + theme(legend.position = "bottom", strip.text.x = element_text(size=15)) + ylim(0, 250)

#Copas selection model:
copas.miss <- effect.diff %>% group_by(outcome.type) %>% mutate(dif = abs(est.fixef - est.copas)) %>% 
	filter(dif > 2) %>% mutate(label = round(dif, 1)) %>% arrange(label) %>% select(label, meta.id, outcome.measure.new)
copas.label <- data.frame(label = paste("missing:", c(paste(copas.miss$label[copas.miss$outcome.type == "bin"], collapse = ", "),
																											paste(copas.miss$label[copas.miss$outcome.type == "cont"], collapse = ", "),
																											paste(copas.miss$label[copas.miss$outcome.type == "surv"], collapse = ", "))),
													outcome.type = c("bin", "cont", "surv"), 
													outcome.measure.new = c("Risk Ratio", "Mean Difference", "Hazard Ratio"))
copas.label$label <- as.character(copas.label$label)
copas.label$label[2] <- sub("2.8,", "2.8,\n", copas.label$label[2])

effect.diff %>% ggplot(aes(x = change.fixef.copas, fill = outcome.measure.new)) + 
	facet_wrap(outcome.type~., scales = "free", labeller = labeller(outcome.type = NULL)) +
	geom_histogram() + xlim(-2, 2) + xlab("Effect change") + 
	theme_bw() + theme(legend.position = "bottom", strip.text = element_blank(), legend.title = element_blank())  +
	geom_text(data = copas.label, 
						mapping = aes(x = 0, y = c(220, 47.4, 10), label = label, vjust = "center"), position = "dodge") #+ ylim(0, 250)

#Regression model:
reg.miss <- effect.diff %>% group_by(outcome.type) %>% mutate(dif = abs(est.fixef - est.reg)) %>% 
	filter(dif > 2) %>% mutate(label = round(dif, 1)) %>% arrange(label) %>% select(label, meta.id, outcome.measure.new)
reg.label <- data.frame(label = paste("missing:", c(paste(reg.miss$label[reg.miss$outcome.type == "bin"], collapse = ", "),
																										paste(reg.miss$label[reg.miss$outcome.type == "cont"], collapse = ", "),
																										paste(reg.miss$label[reg.miss$outcome.type == "surv"], collapse = ", "))),
												outcome.type = c("bin", "cont", "surv"), 
												outcome.measure.new = c("Risk Ratio", "Mean Difference", "Hazard Ratio"))
reg.label$label <- as.character(reg.label$label)
reg.label$label[2] <- sub("2.2,","2.2,\n ", reg.label$label[2])
reg.label$label[2] <- sub("2.6,","2.6,\n ", reg.label$label[2])
reg.label$label[2] <- sub(", 3.1,",", 3.1,\n ", reg.label$label[2])
reg.label$label[2] <- sub("4.4, 4.4,", "4.4, 4.4,\n", reg.label$label[2])
reg.label$label[2] <- sub(", 9.5,", ", 9.5,\n", reg.label$label[2])

reg.label$label[1] <- sub(", 3.3,", ", 3.3,\n", reg.label$label[1])
reg.label$label[1] <- sub(", 7.6,", ", 7.6,\n", reg.label$label[1])

effect.diff %>% ggplot(aes(x = est.fixef - est.reg, fill = outcome.measure.new)) + 
	facet_wrap(outcome.type~., scales = "free", labeller = labeller(outcome.type = NULL)) +
	geom_histogram() + xlim(-2, 2) + xlab("Effect change") + 
	theme_bw() + theme(legend.position = "bottom", strip.text = element_blank(), legend.title = element_blank())  +
	geom_text(data = reg.label, 
						mapping = aes(x = 0, y = c(330, 50, 10), label = label, vjust = "center"), position = "dodge") #+ ylim(0, 250)

################################################################################################
################################################################################################
#CHANGE OF SIGNIFICANT TREATMENT EFFECT AFTER ADJUSTMENT
################################################################################################
################################################################################################

#Explanation of coding: 0 = (unsig, unsig), 1 = (unsig, sig), 2 = (sig, sig), 3 = (sig, unsig)

sig.level <- 0.05
meta.f <- meta.f %>% rowwise() %>% 
	mutate(
		pval.copas = 2*(1-pnorm(abs(est.copas/se.est.copas))),

		sig.fixef = ifelse(pval.fixef > sig.level, 0, 1),
		sig.ranef = ifelse(pval.ranef > sig.level, 0, 1),
		sig.reg = ifelse(pval.reg > sig.level, 0, 1),
		sig.copas = ifelse(pval.copas > sig.level, 0, 1),

		sig.change.ranef.reg = sig.change(sig.before = sig.ranef, sig.after =  sig.reg), #Function to register if significance of estimate has changed after correction
		sig.change.ranef.copas = sig.change(sig.before = sig.ranef, sig.after =  sig.copas),
		sig.change.fixef.reg = sig.change(sig.before = sig.fixef, sig.after =  sig.reg),
		sig.change.fixef.copas = sig.change(sig.before = sig.fixef, sig.after =  sig.copas))

################################################################################################
################################################################################################
#PUBLICATION BIAS TEST RESULTS ANALYSIS
################################################################################################
################################################################################################

#Agreement proportions of publication bias tests:

#Binary:
meta.bin <- meta.bin %>%ungroup() %>%  mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
																							egger.peter = ifelse(egger.test == peter.test, "agree", "disagree"),
																							egger.rucker = ifelse(egger.test == rucker.test, "agree", "disagree"),
																							egger.harbord = ifelse(egger.test == harbord.test, "agree", "disagree"),
																							schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
																							schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
																							schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
																							rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
																							rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
																							harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
agreement.bin <- meta.bin %>% ungroup() %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
																											egger.peter = sum(egger.peter == "agree")/n(),
																											egger.rucker = sum(egger.rucker == "agree")/n(),
																											egger.harbord = sum(egger.harbord == "agree")/n(),
																											schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
																											schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
																											schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
																											rucker.peter = sum(rucker.peter == "agree")/n(),
																											harbord.peter = sum(harbord.peter == "agree")/n())
correlation.bin <- meta.bin %>%ungroup() %>%  summarise(egger.schwarzer = cor(pval.egger, pval.schwarzer),
																												egger.peter = cor(pval.egger, pval.peter),
																												egger.rucker = cor(pval.egger, pval.rucker),
																												egger.harbord = cor(pval.egger, pval.harbord),
																												schwarzer.peter = cor(pval.schwarzer, pval.peter),
																												schwarzer.rucker = cor(pval.schwarzer, pval.rucker),
																												schwarzer.harbord = cor(pval.schwarzer, pval.harbord),
																												rucker.peter = cor(pval.rucker, pval.peter),
																												harbord.peter = cor(pval.harbord, pval.peter))

binary.tests.agreement <- rbind(agreement.bin, correlation.bin)
rownames(binary.tests.agreement) <- c("Test Agreement","P-value Correlation")

#Continuous:
meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
																								thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
																								egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"))
agreement.cont <- meta.cont %>% ungroup() %>%  summarise(thompson.egger = sum(thompson.egger == "agree")/n(),
																												 thompson.begg = sum(thompson.begg == "agree")/n(),
																												 egger.begg = sum(egger.begg == "agree")/n())
correlation.cont <- meta.cont %>% ungroup() %>% summarise(thompson.egger = cor(pval.thompson, pval.egger),
																													thompson.begg = cor(pval.thompson, pval.begg),
																													egger.begg = cor(pval.egger, pval.begg))

cont.tests.agreement <- rbind(agreement.cont, correlation.cont)
rownames(cont.tests.agreement) <- c("Test Agreement","P-value Correlation")
```

```{r}

```

### 2019-06-11 report/chapter01.Rnw
Methods update

@@
 \chapter{Introduction}
+
+Typically, we expect empirical scientific results to be distorted by random noise, such that the results are not equal to the real process that they describe.
+Additionally, one can reasonably assume that the results are also biased to some extent, as the statistical paradigm of precision versus bias would predict: The smaller the noise part of distortion, the more the result should be distorted by bias.
+However, the trade-off is not inevitable and can be minimized by scientific rigour and foresightful experimental design.
+Large efforts have been made both in theory and practice to improve the quality of experiments and their analysis, such as defining experimental settings that prohibit influence of expectations of the researcher (e.g.
+blinding) or increase sample size in experiments.
+The introduction of randomized clinical trials is for example seen nowadays as a benchmark in clinical science, heavily improving the reliability of its findings.
+\\
+It is more and more considered a new scientific field by itself to think of and argue about circumstances that improve the quality of scientific findings.
+Statistics is in some sense predestined to contribute to it, because probability and chance concepts provide are already at the core of understanding of each empirical science.
+\\
+There are however issues in which statistics is not thought to be able to contribute much understanding and to offer little help.
+For example, the selective attention that agents in modern science are paying to new, strong and clear findings in each science is considered merely a psychological, socioeconomic issue.
+It is often explained by the affinity of humans for stories rather than mere facts and for novelties.
+This issue, that scientific findings get more attention, and today, are more likely to be published, read and cited, is known for many years now, but has only gained new traction in meta science when the reproducibility crisis emerged in 2003 to 2005.
+It was the studies of ...
+that showed that even rigid prosecution of study protocolls did often not lead to reproduction of previous results when experiments were repeated, and struck empirical science in its core.
+Most reasonably, ...
+concluded that it was a large missunderstanding of statistical tools such as the p-value in the scientific community that lead to this situation.
+Although that some measures have been taken since then, and some progress is made, the non-reproducibility of scientific fiendings remain an accute threat to the relevance and reliability of science.
+Some even argue that certain scientific fields sooner or later will repeat the experience that for example psychology or medicine have made, and are yet to encounter their own reproducibility crisis.
+\\
+Clearly, reproduction of experimental results is the gold standard of testing empirical science, because it reassures the universality and reliability by which certain procedures or effects appear if measured in the correct experimental context.
+However, there are also problems there.
+One can almost never fully exclude chance events to have played a major role in negating or reafirming the experimental findings (which is of course always the case where noise is present in the data).
+Furthermore, reproduction studies are generally costly and the precise experimental conditions might be hard to reproduce because of lack of information or other reasons.
+There is another way to assess the strength of scientific results if the experiment has been conducted more than once (however not with the same study protocoll as in reproduction studies): Meta-analyses.
+In a meta-analyses, results of multiple (fairly identical) experiments (studies) are summarized to a single result.
+Very often, meta-analyses are not only a synthesis of results, but of evidence, thus reflecting the overall and summarized evidence regarding to a scientific question.
+It is on purpose that selective attention to positive, strong results in the scientific literature have been mentioned beforehand, because it is now clear how they will affect this second way of reassurance of scientific findigs: The meta-analysis will again lead to irreproducible findings if it is based on a set of results that are all positive since they are easier available and more prominent in the scientific literature.
+Thus, meta-analyses will in this case not reach their purpose of assessing reliability of science, but worsen the problem by reinforcing the confidence in the overestimated effects in the experiment.
+However, and this is the main topic in this masters thesis, there are some ways to detect irregularities in the body of results that can provide indirect hints that a selective rather than a random sample out of a hypothetical population of experiments is present.
+The abundance of the methods to link some features of the sample of experiments to publication bias, as the tendency of scientific literature to include over-proportionally large effects is generally termed, also speaks for the relevance of the topic.
+A review in 2017 identified alone 147 (!) conceptually differing methods.\\
+This speaks as well for the inevitable difficulties that such methods encounter.
+First of all, it is most often impossible to estimate the real selection process, that is the rate by which smaller effects go unnoticed because of selective publication and reporting, because the number of missing results in the studies is not known at the first place and impossible to retrieve.
+Secondly, there is almost no real world data of complete and unbiased meta-analyses, such that evaluations of methods is most often dependent on simulations.
+So we have, after applying the methods, only indirect information of publication bias, and the extent to what it might influences scientific findings.
+There are, almost all the time, alternative explanations for the results of the methods that relieve the operators and publishers from the reproval of publication bias.
+However, given the large body of evidence for publication bias to play a role in science that has been collected in other ways, those can be expelled most of the time, such that those methods can give a quantitative measure of publication bias.
+Before beginning with the main part of this masters thesis, I want to recall some of the most pointed evidence for publication bias that has been collected for publication bias so far.
+\\
 

### 2019-06-11 report/chapter04.Rnw
Methods update

--- 2019-05-14 report/chapter04.Rnw
@@
 \chapter{Methods}
+\section{Introduction and Notation}
+The analysis has already been said to be restricted on clinical or health care interventions.
+The interventions are restricted to two participant arms of which some measure of sanity or worsening of health is measured and compared.
+The difference between these two is referred to as the effect of the treatment.
+Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or Hedges $g$, fisher's z score or pearson correlation.
+\\
+Let us consider a meta-analysis with $n$ study treatment effects ($n > 1$, but typically small).
+A study is indexed by $i$, and it's treatment effect by  $\theta_i$.
+The observed treatment effect is $\hat{\theta}_i$.
+The pooled treatment effect of a meta-analysis will be denoted as $\theta_M$, and consequently, the observed pooled treatment effect as $\hat{\theta}_M$.
+Furthermore, each treatment effect is typically measured with some standard error $s_i$ and an estimate of $s_i$ is given by $\hat{s}_i$.
+\\
+For continuous outcomes, let $m_t$ be the mean of the treatment group, $m_c$ the mean of the control group, and equivalentyl $sd_t$ and $sd_c$ the corresponding standard deviations.
+$n_t$ and $n_c$ are the total number of participants in the groups.
+In the case of binary outcomes, let $e_t$ be the count of events in the treatment arm $e_c$ the count of events in the control group.
+The observed counts in a study $i$ are referred to as $e_{t,i}$ and analogously $e_{c,i}$.
 
-\section{Basic notation}
-The notation used here will be used throughout the chapter and exceptions will be noted.
-Let $i$ be the number of a study of a meta analysis with $n$ being the total number of studies.
-$y_{i}$ is then the effect size estimate (usually log odds ratio or mean difference) and $v_{i}$ the variance of the estimate of study $i$.
-$w_{i}$ is used for weights which are defined when necessary, and $\Delta$ usually denotes the summarized or pooled effect estimate of the meta-analysis, and $\eta$ the variance thereof.
-
-\vspace{0mm}
-In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
-
-\section{Heterogeneity}
-In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
-This is called between study variation in contrast to within study variation (noise).
-
-\vspace{0mm}
-The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
-Let $w_i$ be the inverse of the variance and $\Delta$ be a summarized effect estimate of your choice as for example a variance-weighted mean \ref{weighted.mean}.
-Then $Q$ can be calculated as in \ref{Q.heterogeneity}
+\section{Effect Measures and p-values}
+\subsection{Continuous Outcomes}
+For given $(m_t, m_c), (sd_t, sd_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Hedges $g$) and  a standard error thereof.
+Note that the definition of Hedges $g$ and its standard error $s$ varies amongst the literature, the following applies for this report:
 
 \begin{align}
-\Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
+s &= \sqrt{\frac{(n_t - 1)sd_t^2 + (n_c - 1)sd_c^2}{n_t + n_c - 2}} & g &= \frac{m_t - m_c}{s} \label{eq:hedges.g}
 \end{align}
 
-Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
-Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
-$1 - F(Q)$ will provide the $p$-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
-
-\vspace{0mm}
-Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
-For this purpose, $\tau^2$, the variance of true effects, can be calculated.
-$\tau^2$ is on the same scale as the effect size and reflects the absolute amount of dispersion.
-In practice, $\tau^2$ can be smaller than zero, then it is set to zero.
+The mean difference $\theta$ and its standard error $s$ can similarly be obtained by
 
 \begin{align}
-C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
-\tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
+\theta &= m_t - m_c & s &= \sqrt{sd_t^2/n_t + sd_c^2/n_t}
 \end{align}
 
-The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
-Note that their estimate can differ substantially and consequently also the estimate of the pooled effect size estimate.
+Both estimators take into account that the two groups might have unequal variances.
+A p-value to test the null hypothesis that the mean between group is equal is commonly obtained with the students $t$ test.
+The $t$ statistic is obtained, using $s$ and $g$ from \ref{eq:hedges.g}, by
 
-\vspace{0mm}
-To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
+\begin{align}
+t &= g/(s\sqrt{(1/n_t)+(1/n_c)}) \nonumber
+\end{align}
+and the $p$-value can be obtained with the cumulative student's $t$-distibution $F$ with $n_t + n_c - 2$ degrees of freedom:
+
+\begin{align}
+p &= 2(1-F(|t|)) \nonumber
+\end{align}
+
+The t-test is known to be less reliable if combined sample size is small ($n < 30$), see for example \citet{t.test}.
+
+\subsection{Binary Outcomes}
+Two commonly used effect measures for binary outcome data are risk ratios and odds ratios between treatment and control group. 
+The methods presented here can also be found, for example in \citet{Intro.meta}, pg. 34.
+Let $\theta$ be the logarithm to base 10 of the odds ratio. $\hat{\theta}$ and its variance $s^2$ can be obtained by
+
+\begin{align}
+\hat{\theta} &= \log(\frac{e_t*(n_c - e_c)}{e_c*(n_t - e_t)}) \nonumber \\
+\hat{s}^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
+\end{align}
+
+The logarithm of the risk ratio $\theta$ and its variance $s^2$, can be estimated by
+
+\begin{align}
+\hat{\theta} &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
+\hat{s^2} &= 1/e_t + 1/n_t + 1/e_c + 1/e_t \label{eq:risk.ratio.variance}
+\end{align}
+
+Using likelihood theory, one could show that the estimates are maximum likelihood estimates and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$-value (\citet{held2014}, pg.98).
+\\
+Thus, with $\Phi$ as the cumulative standard normal distribution, we get
+\begin{align}
+p &= 2*(1-\Phi(|\hat{\theta}/\hat{s}|) \nonumber
+\end{align}
+which summarizes the evidence against $\theta$ being zero (i.e. the true risk/odds ratio being 1). \\
+Binary and continuous effect measures can be converted into each other. In section \ref{sec:transformation.effectsizes} at the end of this chapter, this is readily described.
+
+\subsection{Survival Outcomes}
+Time-to-event data with censoring present have to be analyzed by special means.
+One frequently used method to take into account right-censoring is the Cox proportional hazards regression model \citep{Cox}.
+Because the method itself is not applied in this thesis, but only the resulting estimates of the parameters are used, the reader is referred to the extensive literature covering this topic (e.g.
+\citet{Surv}).
+The so-called hazard ratio estimated by cox p.h.
+regression is the ratio of the instanteneous risk of experiencing the event between the two groups.
+Because it is a maximum likelihood estimator, one can again use its wald test statistic to test for equal hazards.
+\\
+Let $\hat{\theta}$ be an estimate of the log hazard ratio and $\hat{s}$ an estimate of the standard error of it. As before
+\begin{align}
+p &= 2*(1-\phi(|\hat{\theta}/\hat{s}|) \nonumber
+\end{align}
+will give a $p$-value for the evidence against the null hypothesis.
+
+\section{Fixed and Random Effects Meta-Analysis} \label{sec:meta.analysis}
+The fixed effects meta-analysis estimator of the pooled treatment effect is a mean of the single treatment effect estimators, weighted by their standard errors \cite{fixed.effects.rosenthal}.
+Let $w_i = 1/s_i^2$ be the weights, and $\theta_M$ be the pooled estimator and $s_M^2$ its variance.
+Then
+
+\begin{align}
+\theta_M &= \frac{\sum_{i = 1}^n w_i \theta_i}{\sum_{i = 1}^n w_i} &
+s_M^2 &= \frac{1}{\sum_{i = 1}^n w_i} \label{eq:fixed.effects}
+\end{align}
+
+This estimator minimizes the variance, an estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and standard errors $\hat{\theta}_i, \hat{s}_i^2$.
+The underlying idea is that we assume $\hat{\theta}_i \sim N(\theta_M, s_i^2)$, $\theta_M$ being the true effect, such that all $\theta_i$ are disitributed equally.
+\\
+The random effects model \citep{whitehead} assumes instead that 
+\begin{align}
+\theta_i \sim N(\mu_i, s_i^2) &&
+\mu_i \sim N(\theta_M, \tau^2) \label{eq:random.effects} 
+\end{align}
+
+So marginally, we have $\theta_i$ being distributed around a common mean $\theta_M$ with additional variance $\tau^2$:
+
+\begin{align}
+\theta_i | \mu_i \sim N(\theta_M, s_i^2 + \tau^2) \label{eq:random.effects.marginal}
+\end{align}
+
+$\tau^2$ is often referred to as a population variance or between-study variance, whereas $s_i^2$ can be interpreted as sampling error.
+The pooled treatment effect and its variance is obtained by replacing the weights $w_i$ in equation \ref{eq:fixed.effects} with $w_i = 1/(s_i^2 + \tau^2)$.
+\\
+The model is clearly superior to the fixed effects model whenever the standard errors of the treatment effects alone are unlikely to fully account for the entire variability between studies.
+Note that as $\tau^2$ increases, each $\theta_i$ will eventually get equal weights, irrespective of sampling error.\\
+The estimation of $\tau^2$ has been subject to some debate in the statistical literature. Oftentimes, the method of moment estimator of \citet{tau.estimator} is used.
+We use the measure of heterogeneity, $Q$, and divide by $C$ after having subtracted the degrees of freedom $n-1$:
+
+\begin{align}
+Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i}\label{eq:Q.heterogeneity} \\
+\tau^2 &= \max(0, \frac{Q - (n-1)}{C}) \label{eq:Tau.definition}
+\end{align}
+
+Again, $w_i, \theta_i ...$ have to be replaced by their estimates in order to get an estimate $\hat{\tau}^2$. \\
+The Paule-Madel estimator \citep{paulemandel} is considered to have most often better properties than the method of moments estimator \citep{tau.estimator.evaluation}.
+Since we defined $w_i = 1/(s_i^2 + \tau^2)$, it is straightforward that
+
+% \begin{align}
+% w_i \textrm{Var}(\theta_i) &= 1 & \textrm{Var}(\sqrt{w_i}\theta_i) = 1 \nolabel
+% \end{align}
+
+For any $w_i$, the variance can be estimated and equated to its expected value:
+
+\begin{align}
+s^2(w_i\theta_i) &= \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} & \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} = 1 \label{eq:paulemandel}
+\end{align}
+
+$\theta_M$ can be estimated using equation \ref{eq:fixed.effects} and the new weights $w_i$, thus, the only problem is to estimate $\tau^2$.
+It can be obtained through an iterative process, using a newly defined function
+
+\begin{align}
+F(\tau^2) &= \sum_{i = 1}^n w_i(\theta_i - \theta_M)^2 - (n-1) \nonumber
+\end{align}
+
+In view of equation \ref{eq:paulemandel}, $\tau^2$ must be such that $F(\tau^2) = 0$.
+We start with a arbitrary $\tau^2$, iteratively add a term $\tau_0^2$ and update $\tau^2$ until $F(\tau^2 + \tau_0^2)$ is close to zero.
+Using a truncated taylor series expansion, one can obtain the partial derivative after $\tau^2$, which is a reasonable choice for $\tau_0^2$.
+Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{theta}$, we can update $F(\tau^2)$ and check convergence to zero.
+\\
+The estimation of $\tau^2$ is accompained by uncertainity.
+A common procedure is to test if it is there is significant heterogeneity between the studies (\citet{Intro.meta}, pg.
+109).
+Compute $Q$, as given in \ref{eq:Q.heterogeneity}, based on one of the estimators of $\tau^2$.
+It is assumed that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equally distributed effect sizes.
+Thus, the expected value of $Q$ is $n-1$, and the excess dispersion is $Q - n + 1$.
+The $p$-value against the null hypothesis of equally distributed effect sizes is, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
+= $n-1$, $1 - F(Q)$.
+\\
+An advantage of the $\tau^2$ is that it is directly linked to the variability in the data.
+Additionally, one can use the $I^2$ statistic to see what portion the between study variance has of the overall variance.
+It is computed as
 
@@
 
-There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
+Large values for $\hat{I}^2$ are of great importance when analysing e.g. small study effects. \\
+Importantly, all proposed methods above assume normality and proper estimation of standard errors.
+This assumptions are not met for very small sample sizes and very few event counts.
+An alternative in the latter case is the mantel-haenszel method for risk and odds ratios (see e.g.
+\citet{mantel.haenszel}).
 
-\section{Meta Analysis}
-There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
-First the fixed effect meta-analysis will be explained.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small Study Effects Tests}
+The tests that will be presented on the following pages are a common way to detect publication bias.
+Importantly, they are however not interpretable directly as evidence for publication bias, but this is left for the discussion chapter.
+The tests are also often referred to as funnel plot asymmetry tests, because of the popularity of a recent test that has been used frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citet{trimfill}.
+However, it is known for some time that the method has disadvantageous properties, therefore, it will not be discussed here, as well as the funnel plot (the radial plot will be used as an alternative).\\
+A test for small study effects will test in some ways if the size of the estimated treatment effect of a study depends on some measure of its size.
+An association between study size and treatment effect size can be interpreted as an artifact of publication bias.
+
+\subsection{Continuous Outcome Tests}
+For a continuous outcomes that are normally distributed, the sample mean and variance are independent of each other (\citet{meta.w.R}, pg 120).
+Thus, the estimated standard errors of treatment effects can be used as a proxy for study size, as they should in principle not be tied to the effect size.
+
+\subsubsection{Begg and Mazumdar: Rank Correlation Test}
+\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+A standardized effect size $\theta_i^\star$ can be computed as in \ref{begg.stand.eff}.
+$s_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \ref{begg.stand.var}, $\theta_M$ being the fixed effects pooled treatment effect (\ref{eq:fixed.effects}.
+
+\begin{align}
+\theta_i^\star &= (\theta_i - \theta_M)/s_i^{2\star} \label{begg.stand.eff}  \\
+s_i^{2\star} &= s_i^2 - 1/\sum_{i = 1}^n\frac{1}{s_i^2}1 \label{begg.stand.var} 
+\end{align}
+
+A rank correlation test based on Kendall's tau is then used.
+First, the pairs are ordered after their ranks based on $s^{2\star}$.
+Then, for each $s^{2\star}$ rank, the corresponding ranks based on $\theta^{2\star}$ that are larger are counted and summed up to $u$.
+The number of ranks based on $\theta^{2\star}$ that are in contrary, smaller, are counted and summed up to $l$.
+Then the normalized test statistic $Z$ is given as
+
+\begin{align}
+Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \nonumber
+\end{align}
+
+Thus, large number of concordance between pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$.
+The $p$-value is obtained using the standard normal distribution $\Phi$:
+\begin{align}
+p &= 2*(1-\Phi(|Z|)) \nonumber
+\end{align}
+
+The changes that have to be made int the case of ties are small and can be found in \cite[410]{begg.ties}.
+
+\subsubsection{Egger's Test: Weighted Linear Regression Test}
+First, the concept of simple linear regression is introduced. In short, the model assumes a dependent variable $y$ to be a linear function of another explanatory variable $x$:
+
+\begin{align}
+y &= \beta_0 + \beta_1 x + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:simple.regression}
+\end{align}
+
+$\epsilon$ is the residual noise term that becomes necessary when $n$ pairs $(x_i, y_i)$ are given and there is no exact solution.
+Then it is common to look for the solution that minimizes the squared residuals, the least-squares solution.
+Formally,
+
+\begin{align}
+\operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i) \label{eq:least.squares}
+\end{align}
+
+Let $\mathbf{X}$ be a matrix whith the explanatory variables $x$ and $\mathbf{y}$ a corresponding vector for all $y$:
+
+\begin{equation*}
+\mathbf{X} = 
+\begin{bmatrix}
+1 & x_{12} \\
+1 & x_{22} \\
+1 & x_{32} \\
+\vdots & \vdots \\
+1 & x_{n2} \\
+\end{bmatrix} 
+\qquad
+\mathbf{y} = 
+\begin{bmatrix}
+y_1 \\
+y_2 \\
+y_3 \\
+\vdots \\
+y_n \\
+\end{bmatrix}
+\end{equation*}
+
+Let $\mathbf{\beta} = (\beta_0, \beta_1)^\top$. It can be shown that
+
+\begin{align}
+\hat{\mathbf{\beta}} &= (\mathbf{X}^\top \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
+\end{align}
+
+Is an estimator of $\mathbf{\beta}$ that mimizes the squared residuals.
+Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\mathbf{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$.
+The variance estimates $\hat{\sigma}^2$ and $\hat{\mathbf{s}}_\beta^2$ are
+
+\begin{align}
+\hat{\sigma}^2 &= \frac{1}{n-2}\mathbf{r}^\top \hat{\mathbf{r}} & \hat{\mathbf{s}}_\beta^2 &= \hat{\sigma}^2 (\mathbf{X}^\top \mathbf{X})^{-1} \label{eq:regression.variances}
+\end{align}
+
+The estimate $\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the regression line. Furthermore, in the simple linear regression setting, $\hat{\beta}_0$ can also be obtained by:
+
+\begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} &
+\hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \nonumber
+\end{align}
+
+$\bar{x}, \bar{y}$ denoting the sample means of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$. Thus, $\hat{\beta}_0$ is also called global mean.
+To test whether there is evidence for the intercept $\beta_0$ to be unequal to some value $\beta_{H0}$, a $t$-test can be used.
+
+\begin{align}
+p &= 2(1-F(|(\beta_0 - \beta_{H0})/s_{\beta_0}|)) \nonumber
+\end{align}
+
+where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. $p$ will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
+The concept is extendable to weigthed linear regression.
+Weigthed linear regression may be used if the residuals $\mathbf{r}$ have unequal variances, which is equivalent to ascribe different precision to the observed $y$.
+The least squares equation \ref{eq:least.squares} is extended to
+
+\begin{align}
+\operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
+\end{align}
+
+with positive weigths $w_i$ that penalize large squared residuals for some $i$ more if $w_i$ is larger compared to other $w_i$. \\
+Let $\mathbf{W}$ be a $n \times n$ matrix with $\mathbf{W}_{ii} = w_i$, the weigths on the diagonal and zeros on the off-diagonals.
+The estimates in \ref{eq:regression.parameters} and \ref{eq:regression.variances} can stil be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$.
+\label{weighted.regression} \\
+Now it is shown how linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citet{Egger}.
+Let $\theta/s$ be the dependent variable $y$ and $1/s$ the explanatory variable $x$.
+If plotted, this corresponds to a radial or galbraith plot \citet{galbraith}.
+The linear regression equation as introduced before in \ref{eq:simple.regression} can be written in two ways:
+
+\begin{align}
+\theta/s &= \beta_0 + \beta_1/s + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:radial.plot} 
+\end{align}
+
+\ref{eq:radial.plot} is often provided due to the correspondance to the radial plot. However, it is equivalent to
+
+\begin{align}
+\theta &= \beta_0 + \beta_1 s + \epsilon, & \epsilon \sim N(0, w^{-1}\sigma^2) \label{eq:egger.plot}
+\end{align}
+
+with weigths $w = 1/s^2$.
+Thus testing $\beta_0$ of \ref{eq:radial.plot} or $\beta_1$ is equivalent.
+The corresponding $p$-value is then used as evidence for a small study effect.
+Plugging in  $\theta_i/s_i, 1/s_i$ as $y_i, x_i$ into equation \ref{eq:regression.parameters} and \ref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{s}_{\beta_0}$ and $\hat{s}_{\beta_1}$.
+
+% \begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (\varphi_i - \bar{\varphi})(\theta^\star_i - \bar{\theta}^\star)}{\sum_{i = 1}^n (\varphi_i - \bar{\varphi})^2} &
+% \hat{\beta}_0 &= \bar{\theta}^\star - \hat{\beta}_1 \bar{\varphi} \nonumber
+% \end{align}
+
+\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{Thompson}
+A method proposed in \citet{thompson.sharp} allows for between study variance $\tau^2$, as introduced before in section \ref{sec:meta.analysis}.
+It extends the previously seen linear regression approach with $x = 1/s$ and $y = \theta/s$ by introducing weights.
+The effect size $\theta_i$ is assumed to be distributed as
+
+\begin{align}
+\theta_i \sim N(\beta_0 + \beta_1 s_i, s_i^2 + \tau^2) \label{t.sharp.regression}
+\end{align}
+
+$\tau^2$ is estimated as in equation \ref{eq:Tau.definition} (method of moments). %or \ref{eq:paule.mandel}. 
+The weigths are set as $w_i = 1/\sqrt{s_i^2 + \tau^2})$.
+After adjusting for the weights as described in \ref{weighted.regression}, we can proceed analogous to Egger's test.
+The p-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
+
+\subsection{Dichotomous Outcomes Tests}
+
+The issue with dichotomous outcomes is that effect size and variance of effect size are correlated, which can readily be seen in \ref{eq:risk.ratio} and \ref{eq:risk.ratio.variance}.
+For example, a small number of event counts in one or group will inflate the variance and the effect size.
+Consequently, the tests above will tend to reject the null-hypothesis too often, i.e.
+report false positives.
+A number of solutions to this problem are provided in the literature.
+
+\subsubsection{Peters Test: Weighted Linear Regression Test}
+Instead of taking the standard error $s$ as explanatory variable $x$ as in Egger's Test, the inverse of the total sample size is used.
+Additionally, the variances $s_i^2$ are used as weights.
+Thus, the subsequent test procedure is identical to Egger's test.
+Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
+
+\subsubsection{Harbord's Test: Score based Test}
+A rank based alternative to Peters test for binary outcomes is Harbord's test \citep{Harbord}.
+It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated at log odds ratio $\theta_0 = 0$ and its inverse Fisher information $s^2$. Formally,
+
+\begin{align}
+\varphi &= e_t - (e_t - e_c)(e_t + (n_t - e_t))/(n_t + n_c) \label{harbord.score} \\
+s^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \label{harbord.variance}
+\end{align}
+
+It can be shown that they are both good approximations of the log odds ratio and its variance if the real $\theta$ is not too far from zero.
+The standardized estimator $r_i/v_i$ is also known as peto odds ratio.
+The obtained scores and variances can be used in Egger's test as treatment effects and variances.
+
+\subsubsection{Schwarzer's Test: Rank Correlation Test}
+\citet{Schwarzer} developed a test for the correlation between $E_t - \mathbb{E}(E_t)$ and the variance of $E_t$, $E_t$ being a random variable from the non-central hypergeometric distribution, assuming a fixed log odds ratio.
+\\
+$\mathbb{E}(E_t)$ and variance of $E_t$ are then estimated based on $e_t$. The standardized cell count deviation 
+\begin{align}
+(e_t - \mathbb{E}(E_t))/\sqrt(s_i^2)
+\end{align}
+and the inverse of $s_i^2$ is then used as before in Begg and Mazumdar's test.
+
+\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
+The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables.
+We use that the arcsine function is the variance stabilizing transformation for a proportion.
+Let
+
+\begin{align}
+\theta_i = \arcsin{e_t/n_t} - \arcsin{e_c/n_c} \nonumber &
+s_i^2 = 1/4n_t + +/4n_c \nonumber
+\end{align}
+
+Then one can optionally apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained estimates.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small study effect and Publication Bias Adjustment}
+There are different approaches to correct for small study effects and publication bias.
+They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinte precision (i.e.
+very small standard error) or to a summary effect, corrected for publication bias.
+Selection modells aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:
+
+\subsection{Adjustment by Regression}
+\citet{limitmeta} use a random effects model %together with shrinkage procedure 
+to obtain an unbiased estimate. Similarly to 
+%what has been seen in Copas selection model, we let $y_i$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_i}$ as in \ref{limitmeta.regression}.
+regression based tests for small study effects, we have
+
+\begin{align}
+\theta_i & = \beta_0 + \beta_1\sqrt{s_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \epsilon_i \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{eq:limitmeta.regression}
+\end{align}
+
+The only difference between Thompson and Sharp's variant is $x = \sqrt{s^2 + \tau^2}$ instead of $x = \sqrt{s^2}$.
+$\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
+
+\begin{align}
+\mathbb{E}((\theta_i - \beta_0)/\sqrt{s_i^2}) \rightarrow \beta_1 \textrm{ if } s_i \rightarrow \infty \label{limitmeta.infinitesample} \\
+\mathbb{E}(theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} s_i \rightarrow 0
+\end{align}
+
+After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before in the simple linear regression framework. Now we have basically two possible estimates at hand:
+\begin{itemize}
+\item $\beta_0$ the treatment effect without any influence of study precision with standard error $s_{\beta_0}$
+\item $\beta_0 + \beta_1 \tau$ the treatment effect of a hypothetical study with infinite precision, corresponding standard error $s_{\beta_0} + s_{\beta_1}$
+\end{itemize}
+
+\subsection{Copas Selection Model}
+
+A method proposed in \cite{Copas1,Copas2,Copas3} 
+assumes that the given sample of treatment effects and standard errors is a selected part of a larger random sample.
+Selection of studies depends on their effect size and variance.
+Smaller variance is always accompained by larger selection probability.
+\\
+Let $\theta_i$ be the effect size estimate of study $i$. Then
+
+\begin{align}
+\theta_i \sim N(\mu_i, \sigma_i^2) &
+\mu_i \sim N(\theta, \tau^2) \label{eq:population.model}
+\end{align}
+
+which is similar to the random-effects meta-analysis setting.
+$\theta$ is the population mean effect, $\sigma_i^2$ the within study variance and $\tau^2$ the between study variance.
+Equations in \ref{eq:population.model} are termed the \textit{population model}.
+\\
+The \textit{selection model} is defined as follows.
+Suppose a selection of studies with reported ($\neq$ estimated) standard errors $s$ (likely different from $\sigma$).
+Only a proportion of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
+Formally,
+
+\begin{align}
+P(\textrm{select}|s) &= \Phi(a + b/s) \nonumber %\label{copas.selection1}
+\end{align}
+
+The equation can be rewritten as
+
+\begin{align}
+z = a + b/s + \delta \nonumber %\label{copas.selection2}
+\end{align}
+
+with $\delta \sim N(0,1)$.
+$z$ is interpreted as the \textit{propensity for selection}.
+It's sign must be positive in order for the study to be selected.
+Thus, the larger $z$, the more likely the study will be selected.
+Also, $a$ is somewhat like to global retention or selection rate for each study, while $b$ decides about the decline of selection probability with increasing $s$.\\
+So far, we have, for a study $i$
+
+\begin{align}
+\theta_i = \mu_i + \sigma_i\epsilon_i \\
+\mu_i \sim N(\theta, \tau^2) \\
+z_i = a + b/s_i + \delta_i
+\end{align}
+
+where $(\epsilon_i, \delta_i)$ are standard normal residuals.
+The two models are coupled by introducing a correlation $\rho = cor(\theta_i, z_i)$ by defining $(\epsilon_i, \delta_i)$ as bivariate standard normals.
+It follows that,
+%Every given study $i$ in the meta-analysis has $z_i > 0$. 
+if $\rho_i$ is large and positive and $z_i > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_i$ and $\delta_i$ and thus, the true mean $\mu$ is likely to be overestimated.
+\\
+Let $u_i = a + b/s_i$, $\lambda(u_i)$ the Mill's ratio $\phi(u_i)/\Phi(u_i)$ ($\phi$ is the standard normal density function and $\Phi$ the cdf) and $\tilde{\rho_i} = \sigma/\sqrt(\tau^2 + \sigma_i^2) \rho_i$.
+The probability of a study being selected, given $s_i$ and $\theta_i$, is
+
+\begin{align}
+P(\textrm{select}|s_i, \theta_i) = %P(a,b,s,y) = 
+\Phi(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i^2}}}) \nonumber
+\end{align}
+
+Which again shows that larger $s_i$ and $\theta_i$ lead to a larger selection probability. It can also be shown that the expected value
+
+\begin{align}
+\mathbb{E}(\theta_i|s_i, \textrm{select}) = \mu + \rho_i\sigma_i\lambda(u_i) \label{eq:copas.expectation}
+\end{align}
+
+which shows that the expected value for a study is larger for larger $\sigma$. \\
+A likelihood for $\theta_i$, conditional on $z>0$ can be formulated to estimate the parameters of the model.
+Regarding $a$ and $b$, there is no way that they can be estimated because the number of missing studies and their effect sizes is not known.
+Instead, fixed values for $a$ and $b$ have to be chosen.
+The nuisance parameter $\sigma_i$ can be replaced by an estimate if the sample size in the studies is large enough. Since
+
+\begin{align}
+\textrm{Var}(\theta_i| s_i, z_i > 0) = \sigma_i^2 (1 - c_i^2\rho_i^2) \nonumber
+\end{align}
+
+with $c^2 = \lambda(u_i)(u_i + \lambda(u_i))$, we can replace $\sigma_i^2$ by $\hat{\sigma}_i^2 = \frac{1}{1-c_i^2\rho_i^2}$.
+Although one has to evaluate the likelihood for fixed pairs $(a,b)$, one can compare the fit of the model to evaluate which one is more suitable:
+With equation \ref{eq:copas.expectation}, one can obtain fitted values of $\theta_i$ based on $s_i$. Also, for two different pairs $(a,b)$, $(a^\star, b^\star)$,
+
+\begin{align}
+\mathbb{E}(\theta_i|z_i > 0, a^\star, b^\star) - \mathbb{E}(\theta_i|z_i > 0, a, b) \approx c^\star + \rho(\lambda(a^\star) - \lambda(a))s_i \nonumber
+\end{align}
+
+and that local departures of $\theta_i$ can be approximated by adding a linear term in $s_i$ to the expectation of $\theta_i$. Thus, to test a pair $(a,b)$, it is sufficient to test $\beta \neq 0$ in
+
+\begin{align}
+\theta_i &= \theta + \beta s_i + \sigma_i \epsilon_i \nonumber
+\end{align}
+
+with restriction that $\rho \geq 0$.
+To test some pair $(a,b)$ against the scenario with no selection, we set $a^\star = \infty$ (or $\rho = 0$).
+A likelihood ratio test will give a test statistic to test against $H0 =$ no selection:
+
+\begin{align}
+\chi^2 &= 2*(\operatorname*{max1}_{\theta, \tau, \beta}\tilde{L}(\theta, \tau, \beta) - \operatorname*{max}_{\theta, \tau}\tilde{L}(\theta, \tau, 0)) \label{eq:copas.small.study}
+\end{align}
+
+with 
+\begin{align}
+\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta s_i)^2}{(\tau^2 + \sigma_i^2)}] \nonumber
+\end{align}
+
+$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$-value.
+Note that the test is almost equivalent to Egger's small study effect test with $\tau^2 = 0$.
+Thus, although the copas selection model models publication bias, it is dependent on the small study effects to find the most suitable pair $(a,b)$.
+\\
+If one applies the model to a single meta-analysis, a sensitivity analysis is suggested.
+One can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process.
+Selection models are in general not recommended for inference \citep{selection.assessment}.
+\citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes. \\
+A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \ref{eq:copas.small.study} is applied.
+If all obtained $p$-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for modelling, and the standard, classical random effects meta-analysis is retained.
+If none of the $p$-values is above the threshold, a wider range of values for $(a,b)$ is used.
+When some $p$-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the least intense underlying selection model is chosen).\\
+Currently, there is no test to detect missspecifications in the model itself, the authors themselves have argued that a nonparametric test of the residuals would lack power.
+
+\section{Transformation between effect sizes} \label{sec:transformation.effectsizes}
+Assumon that binary outcomes result from a dichtomozation of originally continuous random variables, in this case, the logistic distribution, a transformation from typical binary effect measures to Cohen's $d$ can be achieved (\citet{Intro.meta}, pg.
+47).
+\\
+Let $\theta$ be a log odds ratio and $s$ its standard error. Cohen's $d$ and it's variance $s_d^2$ is obtained by
+
+\begin{align}
+d &= \theta \frac{\sqrt{3}}{\pi} & s_d^2 = s^2 \frac{\sqrt{3}}{\pi} \nonumber
+\end{align}
+
+$\frac{\pi}{\sqrt{3}} = 1.81$ is the standard deviation of the logistic distribution $L(\mu, \eta)$ with scale parameter $\eta = 1$, so we just divide the log odds ratio and it's variance throught the standard deviation.
+The approximation works only well if $e_t$ and $e_c$ are not very small, especially in the case of $s_d^2$.
+Plugging in the observed log odds ratio $\hat{\theta}$ and $\hat{s}^2$ will give an estimate of Cohen's $d$.\\
+Pearsons correlation can be attained by the formulas (\citet{olkin1985dtor}, \citet{Intro.meta} pg. 48-49)
+
+\begin{align}
+r &= \frac{d}{\sqrt{d^2 + a}} & a = (n_c + n_t)^2 / n_c n_t \nonumber
+\end{align}
+where $a$ is a correction factor if $n_t \neq n_c$. The variance of $r$, $s_r^2$ is computed by
+\begin{align}
+s_r^2 &= \frac{a^2 s_d^2}{(d^2 + a)^3} \nonumber
+\end{align}
+
+Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $s_z^2$ by using
+\begin{align}
+z &= 0.5 \ln(\frac{1 + r}{1 - r}) & \nonumber
+s_z^2 &= \frac{1}{n-3}
+\end{align}
+
+%SIMPLE LINEAR REGRESSION
+% \begin{align}
+% \hat{\mathbf{\beta}} &= (\mathbf{X}^\top  \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
+% \end{align}
+
+% There is a closed form solution for $\hat{\beta_0}, \hat{\beta}_1$ that minimize the sum of squares:
+% 
+% \begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} & 
+% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
+% \end{align}
+% 
+% $\bar{x}, \bar{y}$ denotes the sample mean of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$.
+$\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the fitted line.
+Let $\hat{y}_i = \beta_0 + \beta_1 x_i$ and $e_i = y_i - \hat{y}_i$.
+The variances $s^2_\beta$
+% 
+% 
+% 
+% To test whether the intercept or the slope is close to a certain value, a $t$-test can be used. Simply taking the absolute value of $\beta_0/s_\beta_0$,
+% \begin{align}
+% p &= 2(1-F(|\beta_0/s_\beta_0|)) \nonumber
+% \end{align}
+% 
+% where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom.
+The $p$-value will give the evidence against the null-hypothesis $\beta_0 = 0$.
+The procedure for $\beta_1$ is equivalent.
+\\
+% To extend the model to weighted simple linear regression is straightforward.
+Let $w_i$ be the corresponding weight that will be attributed to the pair $x_i, y_i$.
+The least squares minimization problem can be restated
+% 
+% \begin{align}
+% \operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
+% \end{align}
+% 
+% And the corresponding estimators are thus
+% 
+% \begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n w_i(x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n w_i(x_i - \bar{x})^2} & 
+% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
+% \end{align}
+%
+
+% LIMITMETa
+% \vspace{0mm}
+% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
+% 
+% \begin{align}
+% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
+% \end{align}
+% 
+% Letting $M \rightarrow \infty$, we obtain:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
+% \end{align}
+% 
+% Note that:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
+% \end{align}
+% 
+% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
+% 
+% \begin{align}
+% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
+% \end{align}
+% 
+% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
+% \end{align}
+% 
+% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
+
+% \section{Basic notation}
+% The notation used here will be used throughout the chapter and exceptions will be noted.
+Let $i$ be the number of a study of a meta analysis with $n$ being the total number of studies.
+$y_{i}$ is then the effect size estimate (usually log odds ratio or mean difference) and $v_{i}$ the variance of the estimate of study $i$.
+$w_{i}$ is used for weights which are defined when necessary, and $\Delta$ usually denotes the summarized or pooled effect estimate of the meta-analysis, and $\eta$ the variance thereof.
+% 
+% \vspace{0mm}
+% In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
+% 
+% 
+% \section{Transformation between effect sizes}
+% Binary and continuous outcome measures can both be transformed into correlations and fishers z-scaled correlations in order to be compared.
+Let $\theta$ be a log odds ratio.
+A standardized mean difference $d$ (also known as Cohen's $d$) is calculated by multiplying $\theta$ with $\sqrt{3}/\pi$.
+The variance of the standardized mean difference is attained as $v_d = v_\theta \sqrt{3}/\pi$.\\
+% We get from a standardized mean difference $d$ to a correlation $r$ by using 
+% \begin{align}
+% r &= \frac{d}{\sqrt{d^2 + a}} \nonumber
+% \end{align}
+% where $a$ is a correction factor if $n_t \neq n_c, a = (n_c + n_t)^2 / n_c n_t$. The variance of $r$ is computed by using 
+% \begin{align}
+% v_r &= v_d
+% \end{align}
+% 
+% Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $v_z$ by using
+% \begin{align}
+% z &= 0.5 \ln(\frac{1 + r}{1 - r}) \nonumber
+% v_z &= \frac{1}{n-3}
+% \end{align}
+% 
+% 
+% 
+% \section{Heterogeneity}
+% In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
+This is called between study variation in contrast to within study variation (noise).
+% 
+% 
+% \vspace{0mm}
+% The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
+Let $w_i$ be the inverse of the variance and $\Delta$ be a summarized effect estimate of your choice as for example a variance-weighted mean \ref{weighted.mean}.
+Then $Q$ can be calculated as in \ref{Q.heterogeneity}
+% 
+% \begin{align}
+% \Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
+% Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
+% \end{align}
+% 
+% Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
+Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
+$1 - F(Q)$ will provide the $p$-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
+% 
+% \vspace{0mm}
+% Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
+For this purpose, $\tau^2$, the variance of true effects, can be calculated.
+$\tau^2$ is on the same scale as the effect size and reflects the absolute amount of dispersion.
+In practice, $\tau^2$ can be smaller than zero, then it is set to zero.
+% 
+% \begin{align}
+% C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
+% \tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
+% \end{align}
+% 
+% The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
+Note that their estimate can differ substantially and consequently also the estimate of the pooled effect size estimate.
+% 
+% \vspace{0mm}
+% To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
+% 
+% \begin{align}
+% I^2 &= (Q - n + 1)/Q \label{I2.proportion}
+% \end{align}
+% 
+% There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
+% 
+% \section{Meta Analysis}
+% There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
+% First the fixed effect meta-analysis will be explained.
 Note that both methods can be used for continuous or dichotomous outcomes.
 For more details about the methods, see chapter 11 and 12 in \citet{metaanalysis}
-
-\vspace{0mm}
-Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
+% 
+% 
+% \vspace{0mm}
+% Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
 The pooled estimate $\Delta_{f}$ of the fixed effects model is then the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
 The variance $\eta_{f}$ is the reciprocal of the sum of the weights as shown in \ref{reciproce.variance}.
-
-\begin{align}
-\Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-\eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
-\end{align}
-
-The computation of random effects meta-analysis is more complicated.
+% 
+% \begin{align}
+% \Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
+% \eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
+% \end{align}
+% 
+% The computation of random effects meta-analysis is more complicated.
 Random effects meta-analysis will give smaller studies with larger variance more weight in the pooled estimate.
 Shortly, the idea is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
-
-\vspace{0mm}
-The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
+% 
+% \vspace{0mm}
+% The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
 It is used to calculate a new weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
 The variance of $\Delta_{r}$, $\eta_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
-
-\begin{align}
-v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
-\Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
-\eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
-\end{align}
-
-A p-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
-
-\begin{align}
-Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
-p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
-\end{align}
-
-\section{Small Study Effects Tests}
-One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
+% 
+% \begin{align}
+% v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
+% \Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
+% \eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
+% \end{align}
+% 
+% A p-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
+% 
+% \begin{align}
+% Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
+% p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
+% \end{align}
+% 
+% \section{Small Study Effects Tests}
+% One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
 If this is not given, one often speaks of publication bias.
@@
 If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
-
-\subsection{Continuous Outcome Tests}
-% Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. 
-% First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
-
-\subsubsection{Begg and Mazumdar: Rank Correlation Test}
-\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
-A standardized effect size $y_{i}^\star$ can be computed as in \ref{begg.stand.eff}.
+% 
+% \subsection{Continuous Outcome Tests}
+% % Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. 
+% % First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
+% 
+% \subsubsection{Begg and Mazumdar: Rank Correlation Test}
+% \citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+% A standardized effect size $y_{i}^\star$ can be computed as in \ref{begg.stand.eff}.
 $v_{i}^\star$ is the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
 $\Delta_{f}$ is the pooled estimate for fixed effect estimate defined in \ref{weighted.mean}.
-
-\begin{align}
-y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff} \\
-v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} 
-\end{align}
-
-A rank correlation test based on Kendall's tau is then used.
+% 
+% \begin{align}
+% y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff} \\
+% v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} 
+% \end{align}
+% 
+% A rank correlation test based on Kendall's tau is then used.
 The pairs $(y_{i}^\star, v_{i}^\star)$ that are ranked in the same order are enumerated.
@@
 Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
-
-\begin{align}
-Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
-\end{align}
-
-The changes in the case of ties are negligible \cite[410]{begg.ties}.
-
-\subsubsection{Egger's Test: Linear Regression Test}
-Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
-Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope.
-
-\vspace{0mm}
-If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
+% 
+% \begin{align}
+% Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
+% \end{align}
+% 
+% The changes in the case of ties are negligible \cite[410]{begg.ties}.
+% 
+% \subsubsection{Egger's Test: Linear Regression Test}
+% Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
+% Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope. 
+% 
+% \vspace{0mm}
+% If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
 The p-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
-
-\begin{align}
-p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
-\end{align}
-
-\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{Thompson}
-A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
+% 
+% \begin{align}
+% p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
+% \end{align}
+% 
+% \subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{Thompson}
+% A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
 Let $\tau^2$ be equal to \ref{Tau.definition}.
 The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
-
-\begin{align}
-y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
-\end{align}
-
-Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
+% 
+% \begin{align}
+% y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
+% \end{align}
+% 
+% Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
 Analogous to Egger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta_{0} = 0$.
-
-\subsection{Dichotomous Outcomes Tests}
-
-The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
+% 
+% \subsection{Dichotomous Outcomes Tests}
+% 
+% The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
 Consequently, the tests above will tend to reject the null-hypothesis too often, i.e.
@@
 A number of solutions to this problem are existing in the literature.
-
-\subsubsection{Peters Test: Weighted Linear Regression Test}
-A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
-
-\vspace{0mm}
-Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
-
-\begin{align}
-y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
-v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
-\end{align}
-
-and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
+% 
+% 
+% \subsubsection{Peters Test: Weighted Linear Regression Test}
+% A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
+% 
+% \vspace{0mm}
+% Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
+% 
+% \begin{align}
+% y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
+% v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
+% \end{align}
+% 
+% and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
 Instead of taking the variance as explanatory or independent variable in regression as in Egger's Test, the inverse of the total sample size $x_{i}$ is used, and the variance $v_{i}$ is used as a weight.
 The subsequent test procedure is then identical to Egger's test.
-
-\vspace{0mm}
-Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
-
-\subsubsection{Harbord's Test: Score based Test}
-A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
+% 
+% \vspace{0mm}
+% Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
+% 
+% 
+% \subsubsection{Harbord's Test: Score based Test}
+% A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
 The score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
-
-\begin{align}
-r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
-v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
-\end{align}
-
-Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
+% 
+% \begin{align}
+% r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
+% v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
+% \end{align}
+% 
+% Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
 Note that $r_{i}/v_{i}$ is also known as peto odds ratio.
-
-\subsubsection{Schwarzer's Test: Rank Correlation Test}
-\citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
+% 
+% \subsubsection{Schwarzer's Test: Rank Correlation Test}
+% \citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
 $\mathbb{E}(E_{t})$ and variance of $E_{t}$ are then estimated based on $e_{t}$.
-
-\vspace{0mm}
-The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
-
-\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
-The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let
-
-\begin{align}
-y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}} \\
-v_{i} = 1/4n_{t} + +/4n_{c}
-\end{align}
-
-Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances.
-
-\section{Small Study Effect Adjustment}
-\subsection{Trim and Fill}
-One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
+% 
+% \vspace{0mm}
+% The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
+% 
+% \subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
+% The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let 
+% 
+% \begin{align}
+% y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}} \\
+% v_{i} = 1/4n_{t} + +/4n_{c}
+% \end{align}
+% 
+% Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances. 
+% 
+% 
+% \section{Small Study Effect Adjustment}
+% \subsection{Trim and Fill}
+% One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
 It is a nonparametric test based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
-%If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
-
-\vspace{0mm}
-The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
+% %If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
+% 
+% \vspace{0mm}
+% The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
 First, $\Delta$ is estimated using a fixed or random effects model.
@@
 The total number of missing studies is then mirrored with respect to the final effect size estimate $\Delta$, and $\Delta$ and its standard error is then computed to obtain an unbiased estimate.
-
-\subsection{Copas Selection Model}
-
-A method proposed in \cite{Copas1,Copas2,Copas3} assumes that there is a population of studies of which only a part has been published dependent on the variance and size of their estimated effects.
+% 
+% \subsection{Copas Selection Model}
+% 
+% A method proposed in \cite{Copas1,Copas2,Copas3} assumes that there is a population of studies of which only a part has been published dependent on the variance and size of their estimated effects.
 Studies with small variance and large effect sizes are more likely to be published than studies with large variance and small effect sizes.
 Note that small effect size means here a treatment effect close to the control effect.
-
-Let $y_i$ be the effect size estimate of study $i$. Then
-
-\begin{align}
-y_{i} \sim N(\mu_{i}, \sigma_{i}^2) \\
-\mu_{i} \sim N(\mu, \tau^2)
-\end{align}
-
-corresponding to a standard random effects model.
+% 
+% Let $y_i$ be the effect size estimate of study $i$. Then 
+% 
+% \begin{align}
+% y_{i} \sim N(\mu_{i}, \sigma_{i}^2) \\
+% \mu_{i} \sim N(\mu, \tau^2)
+% \end{align}
+% 
+% corresponding to a standard random effects meta-analysis.
 $\mu$ is the overall mean effect, $\sigma_{i}^2$ the within study variance and $\tau^2$ the between study variance.
 This is the \textit{population model}.
-
-\vspace{0mm}
-The \textit{selection model} is defined as follows. Suppose a selection of studies with reported standard errors $s$ (likely different from $\sigma$). Only a proportion
-
-\begin{align}
-P(\textrm{select}|s) &= \Phi(a + b/s) \label{copas.selection1}
-\end{align}
-
-of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
+% 
+% \vspace{0mm}
+% The \textit{selection model} is defined as follows. Suppose a selection of studies with reported standard errors $s$ (likely different from $\sigma$). Only a proportion 
+% 
+% \begin{align}
+% P(\textrm{select}|s) &= \Phi(a + b/s) \label{copas.selection1}
+% \end{align}
+% 
+% of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
 \ref{copas.selection1} can be rewritten as
-
-\begin{align}
-z = a + b/s + \delta \label{copas.selection2}
-\end{align}
-
-with $\delta \sim N(0,1)$. The study with standard error $s$ is only selected if $z$ is positive. Therefore, the larger $z$, the more likely the study is selected.
-Combining population and selection model for study $i$, we have
-
-\begin{align}
-y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \\
-\mu_{i} \sim N(\mu, \tau^2) \\
-z_{i} = a + b/s_{i} + \delta_{i}
-\end{align}
-
-where $(\epsilon_{i}, \delta_{i})$ are standard normal residuals and jointly normal with correlation $\rho = cor(y_{i}, z_{i})$.
+% 
+% \begin{align}
+% z = a + b/s + \delta \label{copas.selection2}
+% \end{align}
+% 
+% with $\delta \sim N(0,1)$. The study with standard error $s$ is only selected if $z$ is positive. Therefore, the larger $z$, the more likely the study is selected.
+% Combining population and selection model for study $i$, we have 
+% 
+% \begin{align}
+% y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \\
+% \mu_{i} \sim N(\mu, \tau^2) \\
+% z_{i} = a + b/s_{i} + \delta_{i}
+% \end{align}
+% 
+% where $(\epsilon_{i}, \delta_{i})$ are standard normal residuals and jointly normal with correlation $\rho = cor(y_{i}, z_{i})$.
 Every given study $i$ in the meta-analysis has $z_{i} > 0$.
@@
 Thus, the true mean $\mu$ is likely to be overestimated.
-
-\vspace{0mm}
-Let $u = a + b/s$, $\lambda(u) = \phi(u)/\Phi(u)$ ($\phi$ is the standard normal density function) and $\tilde{\rho} = \sigma/\sqrt(\tau^2 + \sigma^2) \rho$.
+% 
+% \vspace{0mm}
+% Let $u = a + b/s$, $\lambda(u) = \phi(u)/\Phi(u)$ ($\phi$ is the standard normal density function) and $\tilde{\rho} = \sigma/\sqrt(\tau^2 + \sigma^2) \rho$.
 The probability of a study being selected is
-
-\begin{align}
-P(\textrm{select}|s, y) = P(a,b,s,y) = \Phi(\frac{u + \tilde{\rho}((y - \mu)/\sqrt(\tau^2 + \sigma^2))}{\sqrt{1 - \tilde{\rho^2}}})
-\end{align}
-
-It can also be shown that the expected value
-
-\begin{align}
-\mathbb{E}(y|s, select) = \mu + \rho\sigma\lambda(u) \label{copas.expectation}
-\end{align}
-
-which shows that the expected value for a study is larger for larger $\sigma$.
-
-\vspace{0mm}
-One can compute a likelihood function based on the distribution of $y$ conditional on $z > 0$.
+% 
+% \begin{align}
+% P(\textrm{select}|s, y) = P(a,b,s,y) = \Phi(\frac{u + \tilde{\rho}((y - \mu)/\sqrt(\tau^2 + \sigma^2))}{\sqrt{1 - \tilde{\rho^2}}})
+% \end{align}
+% 
+% It can also be shown that the expected value 
+% 
+% \begin{align}
+% \mathbb{E}(y|s, select) = \mu + \rho\sigma\lambda(u) \label{copas.expectation}
+% \end{align}
+% 
+% which shows that the expected value for a study is larger for larger $\sigma$. 
+% 
+% \vspace{0mm}
+% One can compute a likelihood function based on the distribution of $y$ conditional on $z > 0$.
 The likelihood can be maximized for any given pair $a,b$ (can not be estimated since the number of missing studies is not known), and a maximum likelihood estimate $\hat{\mu}$ for the true mean $\mu$ can be obtained.
@@
 To test the fit of the model (while keeping all other parts unchanged), the model can be extended in the following way :
-
-\begin{align}
-y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
-\end{align}
-
-If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
+% 
+% \begin{align}
+% y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
+% \end{align}
+% 
+% If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
 Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
 The p-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
-
-\vspace{0mm}
-To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
-
-\vspace{0mm}
-In practice, only a range of values for $a,b$ are reasonable.
+% 
+% \vspace{0mm}
+% To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
+% 
+% \vspace{0mm}
+% In practice, only a range of values for $a,b$ are reasonable.
 For those values, the quantities above can be calculated and illustrated.
 Values for $\mu$ that have p-values over a predefined significance threshold can be used for inference of the effect size.
-
-\subsection{Adjustment by Regression}
-There are multiple ways to adjust for small study effects by regression. The general idea is to extrapolate the effect size of a study with a variance of zero based on the given effects and variances.
-
-\citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
+% 
+% \subsection{Adjustment by Regression}
+% There are multiple ways to adjust for small study effects by regression.
+The general idea is to extrapolate the effect size of a study with a variance of zero based on the given effects and variances.
+% 
+% \citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
 Similarly to what has been seen in Copas selection model, we let $y_{i}$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_{i}}$ as in \ref{limitmeta.regression}.
-
-\begin{align}
-y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
-\end{align}
-
-$\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
-
-\begin{align}
-\mathbb{E}((y_{i} - \beta_{0})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{ if } \sqrt{v_{i}} \rightarrow \infty \label{limitmeta.infinitesample} \\
-\mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
-\end{align}
-
-After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test (see \ref{Thompson}).
-
-\vspace{0mm}
-To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
-
-\begin{align}
-y_{i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{s_{i}/M + \tau^2}) \label{limitmeta.regression}
-\end{align}
-
-Letting $M \rightarrow \infty$, we obtain:
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
-\end{align}
-
-Note that:
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
-\end{align}
-
-$\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
-
-\begin{align}
-\epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
-\end{align}
-
-Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-\end{align}
-
-By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
+% 
+% \begin{align}
+% y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{v_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
+% \end{align}
+% 
+% $\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
+% 
+% \begin{align}
+% \mathbb{E}((y_{i} - \beta_{0})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{ if } \sqrt{v_{i}} \rightarrow \infty \label{limitmeta.infinitesample} \\
+% \mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
+% \end{align}
+% 
+% After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test (see \ref{Thompson}).
+% 
+% \vspace{0mm}
+% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
+% 
+% \begin{align}
+% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
+% \end{align}
+% 
+% Letting $M \rightarrow \infty$, we obtain:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
+% \end{align}
+% 
+% Note that:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
+% \end{align}
+% 
+% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
+% 
+% \begin{align}
+% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
+% \end{align}
+% 
+% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
+% \end{align}
+% 
+% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
 

### 2019-06-11 code_excess/SMD_Correlation_Metas.R

@@ -14,104 +14,31 @@ source(file.path(PATH_CODE, 'PubBias_functions.R'))
 
 file.dat <- "data.RData"
 if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.dat <- "data.processed.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data.ext2 = pb.process2(data)
-	save(data.ext2, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-file.bin <- "pb.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-	load(file.path(PATH_RESULTS, file.bin))
-} else {
-	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
-	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-file.cont <- "pb.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-	load(file.path(PATH_RESULTS, file.cont))
-} else {
-	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
-	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.meta <- "meta.RData"
-if (file.exists(file.path(PATH_RESULTS, file.meta))) {
-	load(file.path(PATH_RESULTS, file.meta))
-} else {
-	meta <- pb.meta.merge(meta.bin, meta.cont)
-	save(meta, file =  file.path(PATH_RESULTS, file.meta))
-}
-
-load(file.path(PATH_RESULTS, "meta.complete.RData"))
-
-
-#Applying test and adjustment criteria:
-metac.bin <- meta.bin %>% filter(n.sig.single > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
[…]

### 2019-06-17 report/MSc_Report.tex
Results section update

--- 2019-04-29 report/MSc_Report.tex
@@
 
-Meta-analysis is at the core of evidence based medicine because it allows to summarise evidence over multiple studies and provide a more broad view on success and effectivity of clinical treatments.
+Typically, we expect empirical scientific results to be distorted by random noise, such that the results are not equal to the real process that they describe.
+Additionally, one can reasonably assume that the results are also biased to some extent, as the statistical paradigm of precision versus bias would predict: The smaller the noise part of distortion, the more the result should be distorted by bias.
+However, the trade-off is not inevitable and can be minimized by scientific rigor and foresightfull experimental design.
+Large efforts have been made both in theory and practice to improve the quality of experiments and their analysis, such as defining experimental settings that prohibit influence of expectations of the researcher (e.g.
+blinding) or increase sample size in experiments.
+The introduction of randomized clinical trials is for example seen nowadays as a benchmark in clinical science, heavily improving the reliability of its findings.
+\\
+It is more and more considered a new scientific field by itself to think of and argue about circumstances that improve the quality of scientific findings.
+Statistics is in some sense predestined to contribute to it, because probability and chance concepts are key to understanding of any empirical science.
+\\
+There are also issues, in which statistics is not thought to be able to contribute much to understanding and to be of little help for solving them.
+For example, the selective attention that the agents in science are paying to new, strong and clear findings in each science is considered merely a psychological and social%, socioeconomic
+issue.
+It is often explained by the affinity of humans for stories rather than mere facts and for novelties.
+The issue that scientific findings get more attention and are more likely to be published, read and cited is known for many years, but has gained new traction in meta science when the so-called reproducibility crisis emerged in (2003 to 2005).
+Studies such as ...
+showed that even rigid prosecution of study protocols did often not lead to reproduction of previous results when experiments were repeated, which struck empirical science in its core.
+Most reasonably, some concluded that it was a large misunderstanding of statistical tools such as the p-value in the scientific community that lead to this situation (...).
+Although that some measures have been taken since then, and some progress is made, the non-reproducibility of scientific findings remain an acute threat to the relevance and reliability of science.
+Some even argue that certain scientific fields sooner or later will repeat the experience that for example psychology or medicine have made, and are yet to encounter their own reproducibility crisis (...).
+\\
+Clearly, reproduction of experimental results is the gold standard of testing empirical science, because it reassures the universality and reliability by which certain procedures or effects appear if measured in the correct experimental context.
+However, there are also problems there.
+One can almost never fully exclude chance events to have played a major role in negating or reaffirming the experimental findings (which is of course always the case where noise is present in the data).
+Furthermore, reproduction studies are generally costly and the precise experimental conditions might be hard to reproduce because of lack of information or other reasons.
+\\
+There is another way to assess the strength of scientific results if the experiment has been conducted more than once (however not with exactly identical protocol as in reproduction studies): Meta-analyses.
+In a meta-analyses, results of multiple (fairly identical) experiments (studies) are summarized to a single result.
+Very often, meta-analyses are not only regarded to be a synthesis of results, but of evidence, thus reflecting the overall and summarized evidence regarding to a scientific question.
+It is on purpose that selective attention to positive, strong results in the scientific literature have been mentioned beforehand, because it is clear how they will affect this second way of reassurance of scientific findings: The meta-analysis will again lead to irreproducible findings if it is based on a set of results that is itself biased.
+Thus, meta-analysis will in this case not reach its purpose of assessing reliability of science, but worsen the problem by reinforcing the confidence in the overestimated over-optimistic effects.
+However, and this is the main topic in this masters thesis, there are some ways to detect irregularities in the body of results that can provide indirect hints that a selective rather than a random sample from a hypothetical population of experiments is present.
+The abundance of the methods to link some features of the sample of experiments to publication bias, as the tendency of scientific literature to over-proportionally include large effects is generally called, also speaks for the relevance of the topic.
+A review in 2017 (...) for example identified 147 (!) conceptually differing methods.\\
+This speaks as well for the inevitable difficulties that such methods encounter.
+First of all, it is most often impossible to estimate the real selection process, that is the rate by which smaller effects go unnoticed because of selective publication and reporting, because the number of missing results in the studies is not known at the first place and impossible to retrieve.
+Secondly, there is almost no real world data of complete and unbiased meta-analyses, such that evaluations of methods is dependent on simulations.
+So we have, after applying the methods, only indirect information of publication bias, and the extent to what it might influences scientific findings.
+Almost all the time, alternative explanations for the results of the methods might relieve the operators and publishers from the reproval of publication bias.
+However, given the large body of evidence for publication bias collected in other ways, those can probably be expelled most of the time, such that those methods indeed give a quantitative measure of publication bias.
+\\
+In this masters thesis, the answers for two questions are investigated: What is the extent and effect of publication bias in clinical science?
+For this purpose, a dataset from the Cochrane Organization is analysed with commonly used techniques to detect and adjust for publication bias (more precisely, small study effects, as it will be seen later).
+The discussion of the results of the analysis will result in the light of the literature to publication bias.
+%Because the extent of the analysis that is operated here is, to my knowledge, unmatched so far, this dataset
+
+%Before beginning with the main part of this masters thesis, I want to recall some of the most pointed evidence for publication bias that has been collected for publication bias so far. \\
+
+% Meta-analysis is at the core of evidence based medicine because it allows to summarise evidence over multiple studies and provide a more broad view on success and effectivity of clinical treatments.
 The necessity of meta-analyses is also increased by the abundance of data and publications.
 Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to make decisions based on quantitative and scientific criteria.
-
-\vspace{0mm}
-For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention.
+% 
+% \vspace{0mm}
+% For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention.
 However, the usefulness of meta-analysis does not restrict to clinical science, but to any empirical and quantiative science.
-
-\vspace{0mm}
-Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question.
+% 
+% \vspace{0mm}
+% Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question.
 Meta-analysis can be applied to all studies that are approximately identical in their experimental setup and the way the outcome of the experiments is measured.
 In systematic reviews where meta-analyses are used, the conclusions are most often strongly based on the results and the interpretation of the meta-analysis.
-
-\vspace{0mm}
-However, there are problems that potentially limit the validity of meta-analysis; the number of studies available can be incomplete or the results of the studies can be biased.
+% 
+% \vspace{0mm}
+% However, there are problems that potentially limit the validity of meta-analysis; the number of studies available can be incomplete or the results of the studies can be biased.
 Some of those problems can be solved or asserted by special statistical methods.
-
-\subsection{Small Study Effects or Publication Bias}
-When study sample size decreases, the probability of extreme and missleading results in a study increases.
+% 
+% \subsection{Small Study Effects or Publication Bias}
+% When study sample size decreases, the probability of extreme and missleading results in a study increases.
 This becomes a problem if results are selectively published, and therefore available, based on their results.
 When this is the case, one speaks of a small study effect or of ``Publication bias''.
-
-\vspace{0mm}
-The issue has been discussed extensively in the last years, most often in the context of what has came to be known as the replication crisis.
+% 
+% \vspace{0mm}
+% The issue has been discussed extensively in the last years, most often in the context of what has came to be known as the replication crisis.
 The reasons for small study effects are manifold, but originate most often in the myopical acting of agents in science and the lack of statistical education.
@@
 When doing a meta-analysis, one again obtains biased results.
-
-\vspace{0mm}
-The reason why that is less of an issue for larger studies is that extreme results are in general less likely and that due to larger effort, a result is published although there has been no clear and positive findings.
-
-\vspace{0mm}
-While there is generally no way to assert poor study quality, small study effect can in principle be asserted and corrected for statistically.
+% 
+% \vspace{0mm}
+% The reason why that is less of an issue for larger studies is that extreme results are in general less likely and that due to larger effort, a result is published although there has been no clear and positive findings.
+% 
+% \vspace{0mm}
+% While there is generally no way to assert poor study quality, small study effect can in principle be asserted and corrected for statistically.
 This masters thesis will mainly be about statistical methods to detect and adjust for small study effects.
 It can furthermore be divided in two parts:
-\begin{itemize}
-\item Methodological part: Collection and discussion of statistical tests and correction methods for small study effects.
-\item Applied part: Application of the methods to studies of the Cochrane Library of systematic Reviews. Subsequent discussion of the implications
-of the results for clinical science.
-\end{itemize}
-
-In contrast to simulation studies, it is not possible to assess critical properties of the methods such as the power of a test, since the truth is not known.
+% \begin{itemize}
+% \item Methodological part: Collection and discussion of statistical tests and correction methods for small study effects.
+% \item Applied part: Application of the methods to studies of the Cochrane Library of systematic Reviews. Subsequent discussion of the implications
+% of the results for clinical science.
+% \end{itemize}
+% 
+% In contrast to simulation studies, it is not possible to assess critical properties of the methods such as the power of a test, since the truth is not known.
 But based on the amount of data, one can of course try to make extrapolation to tendencies in clinical science in general.
@@
 Comparison with results from simulations may allow to speculate about the reasons when simulation and real world results diverge.
-
-\subsection{Cochrane and the Cochrane Database of Systematic Reviews}
-The Cochrane Organization has specialized on systematic reviews in clinical science.
+% 
+% 
+% \subsection{Cochrane and the Cochrane Database of Systematic Reviews}
+% The Cochrane Organization has specialized on systematic reviews in clinical science.
 It publishes and maintains a library with a large number of systematic reviews that are available in some countries to the public.
-
-\vspace{0mm}
-The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite).
-
-\vspace{0mm}
-The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests.
+% 
+% \vspace{0mm}
+% The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite). 
+% 
+% \vspace{0mm}
+% The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests.
 This might further improve the validity and precision of findings and conclusions that have been made based on this data.
+%
 
@@
 
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in UseMethod("{}mutate\_"{}): no applicable method for 'mutate\_' applied to an object of class "{}function"{}}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in pb.meta.merge(meta.bin, meta.cont): could not find function "{}pb.meta.merge"{}}}\end{kframe}
-\end{knitrout}
-
 \chapter{The Cochrane Dataset}
@@
 \section{Cochrane Systematic Reviews}
-As has been mentioned before, the Cochrane Group has specialized on systematic reviews in clinical science.
+The Cochrane Group has specialized on systematic reviews in clinical science.
 Certain knowledge of standards and principles of the Cochrane Group may help to assess the quality and the properties of the dataset.
 The following information stems from the Cochrane Handbook for Systematic Reviews \citep{cochrane.handbook}.
-
-\vspace{0mm}
+\\
 The definition of a systematic review is that it ``attempts to collate all empirical evidence that fits pre-specified eligibility criteria in order to answer a specific research question.'' Thus, the ``key properties of a review are'':
@@
 
-At the end of a systematic review, ``a systematic presentation, and synthesis, of the characteristics and findings of the included studies'' is done.
-
-\vspace{0mm}
+At the end of a systematic review, ``a systematic presentation, and synthesis, of the characteristics and findings of the included studies'' is done. \\
 53 Cochrane Review Groups prepare and maintain the reviews within specific areas of health care.
 A group consists of ``researchers, healthcare professionals and people using healthcare services (consumers)''.
-
-\vspace{0mm}
-The groups are supported by Method Groups, Centres and Fields.
+\\
+The groups are supported by Method Groups, Centers and Fields.
 The Cochrane Method Groups aim to discuss and consult the groups in methodological questions concerning review preparation.
-The Centres play a main role in training and support of the Groups.
+The Centers play a main role in training and support of the Groups.
 The Fields are responsible for broad medical research areas and follow priorities in those areas by advice and control of the groups.
-
-\vspace{0mm}
-The first step in a review is writing a protocoll, specifying the research question, the methods to be used in literature search and analysis and the eligibility criteria of the study.
-Changes in protocolls are possible but have to be documented and the protocol is published in advance of the publication of the full review.
-The choices of methodology as well as the changes should not be made ``on the basis of how they affec the outcome of the research study''.
-
-\vspace{0mm}
-In order to avoid potential conflicts of interests, there is a code of conduct that all entities of the Cochrane Organization have to agree on: conflicts of interest must be disclosed and possibly be forwarded to the Cochrane Centre, and participation of review authors in the studies used have to be acknowledged.
+\\
+The first step in a review is writing a protocol, specifying the research question, the methods to be used in literature search and analysis and the eligibility criteria of the study.
+Changes in protocols are possible but have to be documented and the protocol is published in advance of the publication of the full review.
+The choices of methodology as well as the changes should not be made ``on the basis of how they affect the outcome of the research study''.
+\\
+In order to avoid potential conflicts of interests, there is a code of conduct that all entities of the Cochrane Organization have to agree on: conflicts of interest must be disclosed and possibly be forwarded to the Cochrane Center, and participation of review authors in the studies used have to be acknowledged.
 Additionally, a Steering Group publishes a report of potential conflicts of interests based on information about external funding of Cochrane Groups.
-
-\vspace{0mm}
-In order for keeping the reviews up-to-date, they are revised in a two-year cicle with exceptions.
+\\
+In order for keeping the reviews up-to-date, they are revised in a two-year circle with exceptions.
 In addition to inclusion of new evidence in a field, the revision and maintenance process may as well includes change in analysis methods.
-This can reflect some advance in clinical science as for example new informations about important subgroups, as well as new methods for conducting a Cochrane Review.
+This can reflect some advance in clinical science as for example new information about important subgroups, as well as new methods for conducting a Cochrane Review.
 However, there are no clear guidelines and the Cochrane Groups are free in the rate and extent of up-dating their reviews.
@@
 A research question defines the following points: ``the types of population (participants), types of interventions (and comparisons), and the types of outcomes that are of interest''.
-From the research question, ususally the eligibility criteria follow.
+From the research question, usually the eligibility criteria follow.
 Usually, outcomes are not part of eligibility criteria, except for special cases such as adverse effect reviews.
-
-\vspace{0mm}
+\\
 The type of study is an important eligibility criterium.
@@
 Furthermore, study characteristics such as blinding of study operators with respect to treatment and cluster-randomizing might be additional eligibility criteria which have to be chosen by the review authors.
-
-\vspace{0mm}
+\\
 After having specified the eligibility criteria, studies have to be collected.
@@
 ``Time and budget restraints require the review author to balance the thoroughness of the search with efficiency in use of time and funds and the best way of achieving this balance is to be aware of, and try to minimize, the biases such as publication bias and language bias that can result from restricting searches in different ways.'' It is important to note that not only studies, but also study reports are occasionally used in the reviews, as they may provide useful information.
-
-\vspace{0mm}
+\\
 There are different sources that are being used to search for studies. 
@@
 \item EMBASE.
-4,800 Journals publishing in 30 languages are indexed to EMBASE, which includes more than 11 million records from 1974 onwards.
+4,800 Journals publishing in 30 languages are indexed to EMBASE, which includes more than 11 million records from 1974 onward.
 EMBASE.com also includes 7 million unique records from MEDLINE (1966 up to date) together with its own records.
 Additionally, EMBASE Classic allows access to digitized records from 1947 to 1973.
-EMBASE and MEDLINE each have around 1,800 journals not indexed in the other databse.
+EMBASE and MEDLINE each have around 1,800 journals not indexed in the other database.
 \item Regional or national and subject specific databases can additionally be consulted and often provide important information. Financial considerations may limit the use of such databases.
@@
 The dataset consists of 5016 systematic reviews from the Cochrane Library with 52995 studies and 463820 results.
-A result compares clinical or medical interventions or treatments.
+A result compares a clinical or medical intervention or treatments to a control.
 Each study provides (multiple) results of clinical interventions.
-
+\\
 In Table \ref{barbiturate.row}, two results from a systematic review about effects of barbiturates are shown as they are given in the dataset.
-As can be seen, the result is further specified by the variables in the columns.
-The comparison variable specifies what treatments or interventions are compared, the outcome variable how it is compared, and the subgroup variable (not given in table) indicates if the result belongs to a certain subgroup.
-Here, the result is of a binary outcome, so the events in the barbiturate treatment group and the total number of participants are given in columns ``Events'' and ``Total'' and the number of events in the control group ``Events\_c'' and participants ``Total\_c''.
-Events denotes here number of deaths at the end of follow up.
+As can be seen, further specifications are provided by the variables in the columns.
+\\
+The comparison variable specifies \textit{what kind} of treatments or interventions are compared, the outcome variable \textit{how} it is compared, and the subgroup variable (not indicated in table) if the result belongs to a certain subgroup.
+Here, the result is of a binary type, so the counts of events in the barbiturate treatment group and the total number of participants are given in columns ``Events'' and ``Total'' and the number of events in the control group ``Events\_c'' and participants ``Total\_c''.
+A event is here death at the end of follow up.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:57:33 2019
+% Mon Jun 17 16:15:38 2019
 \begin{table}[ht]
@@
 A complete listing of the variables of a result is given in Table \ref{variable}.
-They can roughly be separated into variables that specify the review in which the result is contained and variables that specify the result itself (separated by a horizontal line in Table \ref{variable}).
+They can roughly be separated into variables that \textit{specify the review} in which the result is contained and variables that \textit{specify the result} itself (separated by a horizontal line in Table \ref{variable}):
 
@@
 The structure of a review will now be outlined based on an example of the dataset.
-Lets consider the previously mentioned barbiturate and head injury review.
+Let us consider the previously mentioned barbiturate and head injury review.
 The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates''.
-Since there are arguments for and against use of barbiturates, the authors of the review did a comprehensive literature search and collected all available study findings.
-
-\vspace{0mm}
+\\
+%Since there are arguments for and against use of barbiturates, the authors of the review did a comprehensive literature search and collected all available study findings. 
 The review comprises five studies in total.
-Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental, which would be the comparison to speak in the previously introduced notion.
-The studies have different outcomes, for example, death or death and severe disability at follow up.
+Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental.
+The studies have different outcomes, for example, death or death and severe disability at follow up, but also dropout counts or adverse effects (secondary outcomes).
+We have continuous (e.g.
+mean body temperature) and binary outcome data (e.g.
+death/no death).
 One study split up outcomes for patients with and without haematoma, which would be subgroups.
-
-\vspace{0mm}
-The complete listing of outcomes is in table \ref{barbiturates}.
-The table also gives an illustration of the variety of data that can be included in a review.
-We have for example continuous (mean body temperature) and binary outcome data (death).
-Additionally to primary and secondary outcomes, often also dropouts and adverse effects are included in a review.
+Thus, it is important not to confuse results with studies.
+A study can contribute multiple results to a systematic review, for example, primary and secondary outcomes and adverse effects.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:57:33 2019
+% Mon Jun 17 16:15:38 2019
 \begin{table}[ht]
@@
 
-It is important not to confuse results with studies. A study can contribute multiple results to a systematic review, for example, primary and secondary outcomes and adverse effects.
-
-\vspace{0mm}
 Information about missing values in the dataset is given in Table \ref{missing}.
@@
 The relative amount of missing values is very low except for study years.
-In the case of continuous outcomes, the cases have been counted were effect sizes and standard errors of effect sizes are not available.
-This means that neither mean values of groups nor mean differences are given, or that neither standard deviation nor standard error is given for a result.
-Study years before 1920 and after 2019 have been counted as missing, as well as sample sizes below zero.
+For continuous outcomes, the cases have been counted were no treatment effect and standard error is available: neither mean values and standard deviations, nor mean differences and standard error.
+Also Study years before 1920 and after 2019 are declared as missing, as well as sample sizes below zero.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:57:33 2019
+% Mon Jun 17 16:15:38 2019
 \begin{table}[ht]
@@
 The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982).
-The median of the publication years is 2003, the mean 2006.13 and the quartiles are 1996 and 2008.
-Only a handful ($n$ = 18) have been published in 2018, none in 2019.
-No information is available concerning unpublished results and studies.
-
-\vspace{0mm}
-The results of a study are summarised in a result by a effect measure.
-This effect measure varies, depending on whether data is continuous, binary or time-to-event.
-The most abundant effect measures used are summarised in Table \ref{outcome.measure.frequencies}.
-One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the being some sort of discrete or binary outcomes, most often binary (> 65\%).
+The median of the publication years is 2003, the mean 2001 and the quartiles are 1996 and 2008.
+Only a handful ($n = 18$) have been published in 2018, none in 2019.
+\\
+%No information is available concerning unpublished results and studies.
+The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}.
+One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (> 65\%).
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:57:33 2019
+% Mon Jun 17 16:15:38 2019
 \begin{table}[ht]
@@
 
-The sample sizes amongst results vary to some extent.
-There are 5\% of treatment group sample sizes that are smaller tha 8, the 5\% quantile.
+The sample sizes among results vary to some extent.
+There are 5\% of treatment group sample sizes that are smaller than 8, the 5\% quantile.
 The first quartile is 22, the median 48, the mean 302.03 and the third quartile 119.
@@
 The mean is 617.81.
-
-\vspace{0mm}
+\\
 The mean and median number of results per review are 12.42 and 7.
@@
 Similarly, the number of reviews with a maximum of two studies included is 836, the mean study number is 12.42, the median 7 and the interquartile range 4 and 15.
-The discrepancy between mean and median is again due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxisfor preventing infection after cesarean section, with 95 studies and 1497 results in total.
-
-\vspace{0mm}
+The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1497 results in total.
+\\
 For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome.
-More speicifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis since their research subject and experimental setup can be considered sufficiently homogeneous.
-%Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
-\vspace{0mm}
-The amount of studies that can be pooled for meta-analyses is of special interest in this masters thesis.
-Thus, the dataset is divided in groups whith identical experimental setup.
-The size of the group denotes how many results are included in a group.
-
-\vspace{0mm}
-Table \ref{repr.groups} shows the number of \textit{groups} of groups with equal or more than $n$ results.
-Practically, this means that a given number of meta analyses can be performed with each having at least $n$ results.
+More specifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis, since their research subject and experimental setup can be considered sufficiently homogeneous.
+Importantly, this distinction is also used by the Cochrane Organization itself, i.e.
+the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\%Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
+The dataset is divided in meta-analyses with identical experimental setup. The size of a meta-analysis denotes how many results are included in a group.
+Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results. Practically, this number of meta analyses can be performed, with each having at least $n$ results:
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:57:33 2019
+% Mon Jun 17 16:15:38 2019
 \begin{table}[ht]
@@
 
+\section{Data Tidying and Processing} \label{sec:Processing}
+The original dataset was provided by .. (some words how the dataset was obtained and processed by C.R.). \\
+The information in the previous pages are from a tidied and processed version of this dataset. \\
+
+\subsection{Modification of old variables}
+In some cases, reasonable assumptions led to small changes in the originally provided variables:
+\begin{itemize}
+\item \textbf{study.year}: It was assumed that studies that are declared to have been published before 1920 ($n$ = 30664) are mis-specified, as well as after 2019 ($n$ = 384), so these have been set to NA.
+\item \textbf{mean1} and \textbf{mean2}: When both ``mean1'' and ``mean2'' are equal to zero or NA, ``outcome.measure.new'' is equal to ``(Std.) Mean Difference'', but a mean difference is given in ``effect'', ``mean1'' is set equal to ``effect'' ($n$ = 1593).
+\end{itemize}
+
+\subsection{Newly Introduced Variables}
+Some new variables are added to the obtained dataset:
+\begin{itemize}
+\item \textbf{outcome.measure.new}: Outcome measure specifications given in ``outcome.measure'' were standardized whenever they were supposed to denote the same outcome measure.
+An example would be the formally different notations for odds ratios: ``Odds Ratio'', ``odds ratio'', ``OR'', which were all denoted as ``Odds Ratio''.
+\item \textbf{outcome.type}: A simplification of ``outcome.measure.new''.
+The outcome.type ``bin'' indicates if ``outcome.measure.new'' is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
+``cont'' is equivalent to ``outcome.measure.new'' equal to "Std.
+Mean Difference'' or ``Mean Difference''.
+``surv'' equal to ``Hazard Ratio'' and ``rate'' equal to ''Rate Ratio'' or ``Rate Difference''.
+\item \textbf{lrr} and \textbf{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.type ``bin''.
+\item \textbf{smd} and \textbf{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.type ``cont''.
+If not computable from ``mean1'', ``mean2'', ``sd1'' and ``sd2'', and ``outcome.measure.new'' was equal to ``Std.
+Mean Difference'', it was set equal to ``effect'' (and ``var.smd'' equal to ``se'' squared, $n$ =  6938).
+\item \textbf{smd.ordl} and \textbf{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.type ``bin''.
+\item \textbf{cor.Pearson} and \textbf{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.type ``bin'') or $g$ (for outcome.type ``cont'') to $r$ transformation.
+\item \textbf{z} and \textbf{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
+\item \textbf{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.type ``cont'' or Wald test for outcome.type ``bin''.
+\item \textbf{events1c} and \textbf{events2c}: Correction of ``events1'' and ``events2'' zero event counts or event counts = patient number.
+When no events occurred, 0.5 was added, and when all patients experienced the event, 0.5 was subtracted.
+When one of ``events'' had zero counts while the other had maximum counts, no adjustment occurred.
+\item \textbf{meta.id}: Meta-analysis ID variable to uniquely identify any potential meta-analysis in the dataset.
+Consistent to what has been discussed before, all results that share a common comparison, outcome and subgroup (optional, subgroups not given in any case) may be combined in a meta-analysis.
+% \item \textbf{}:
+% \item \textbf{}:
+\end{itemize}
+
+\subsection{Eligibility criteria for Publication Bias Test and Adjustment} \
+Initially, the analysis is restricted to binary, continuous and survival outcomes. More formally:
+\begin{itemize}
+\item \textbf{Outcome measures}: The analysis has been restricted on the following outcome measures (from ``outcome.measure.new''): ``Odds Ratio'', ``Risk Ratio'', ``Risk difference'', ``Peto Odds Ratio'', ``Std.
+Mean Difference'', ``Mean Difference'', ``Hazard Ratio''
+($n$ = 456727 out of a total of 463820 results)
+\end{itemize}
+
+The suggestions of criteria for eligibility for publication bias tests of \citet{Ioannidis2007} have largely been followed:
+\begin{itemize}
+\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = 5797 remaining). 
+\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 4038 remaining).
+\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 4006 remaining).
+\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 2673 remaining)
+\end{itemize}
+
+After having excluded meta-analyses with less than ten studies, additional criteria for excluding inconvenient meta-analyses are:
+\begin{itemize}
+\item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = 141 out of meta-analyses with at least ten studies).
+\item \textbf{Missing means and sd's}: In the case of continuous outcomes, meta-analyses with means and sd's in any group being equal to zero are excluded ($n$ = 306 out of meta-analyses with at least ten studies).
+\item \textbf{Single patient data}: Meta-analyses that are comprised of single patient data are excluded ($n$ = 8 out of meta-analyses with at least ten studies)
+\end{itemize}
+
+--Make Flowchart--
+
+\subsubsection{Exclusions due to Computational Errors}
+In exceptional cases, the applied meta-analysis methods and publication bias tests and adjustment algorithms failed due to various reasons.
+Here, those cases are listed and if known, the reasons why computation failed are given.\\
+\textbf{Binary Outcomes}: Out of the meta-analyses that are of ``outcome.type'' bin, and have at least ten studies, two studies hat to be excluded:
+\begin{itemize}
+\item meta.id = 62301 (file.nr = 1531, comparison.nr = 8, outcome.nr = 6, subgroup.nr = 1):
+%A subgroup analysis for women with increased adverse pregnancy outcomes, where the effect of vitamin C supplements is tested on pre-eclampsia: 
+Largest study (se = 0.1) has risk ratio 1 and smallest study (se = 1) risk ratio 0.07. Copas publication bias adjustment methods has likelihood optimization issues.
+\item meta.id = 94519 (2519, 14, 1, 2): Largest study (se = 0.05) has risk ratio 0.9 and smallest study (se = 0.4) risk ratio 3.
+Again Copas publication bias adjustment methods has likelihood optimization issues.
+\end{itemize}
+
+There were no issues with ``outcome.type'' ``cont'' and ``surv''.
+For the subsequent information, it is important to know that meta-analyses are only repeated with Hedges $g$, Pearson correlation coefficient and Fisher's Z-scores, if the outcome type is not survival and all of the above criteria are met ($n$ = 0).
+\\
+\textbf{Pearson Correlation Coefficient}: Three studies had to be excluded when analyzing the Pearson correlation coefficients:
+\begin{itemize}
+\item meta.id = 157083 (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2): A meta-analysis with all results from the same study, and equal sample size (5 each group).
+The Copas selection model algorithm issued an error when optimizing the likelihood.
+\item meta.id = 159329 (5183, 3, 13): One very small study with group sizes of 2 and 1 patients and small risk ratio of 0.222 (compared to the largest of 1.05, se = 0.04).
+Also, the Copas selection model algorithm issued an error when optimizing the likelihood.
+\item meta.id = 182298 (6211, 1, 8, -): One very small study with 8 patients in each group and 0 event counts in both.
+The Copas selection model algorithm issued an error when optimizing the likelihood.
+\end{itemize}
+
+\textbf{Fisher's Z score}: The same issues as encountered for Pearson correlation coefficients (meta.id = 157083 and 159329).
+The variance of the z score $s_z^2$ can be calculated as:  $s_z^2 = \frac{1}{n-3}$, $n$ being the total sample size.
+Thus, studies that have total sample size $n \geq 3$ are discarded in the meta-analyses ($n$ = 72 studies).
+2 meta-analyses have then less than 10 studies left for pooling:
+\begin{itemize}
+\item meta.id = 10671: (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2), 7 studies left.
+\item meta.id = 43324: (1019, 1, 3, 2), 9 studies left.
+\end{itemize}
+
+\subsubsection{The Publication Bias Test and Adjustment Dataset}
+The dataset that was ultimately tested and adjusted for publication bias comprises 2673 meta-analyses and 42789 results. ..
+
+% \begin{itemize}
+% \item meta.id = 5229 (file.nr = 137, comparison.nr = 1, outcome.nr = 3, subgroup.nr = 1): ``Luken 1979'' (3), ``Miller-Fisher 1978'' (3), ``Müller Forell 1978'' (2).
+% \item meta.id = 136563 (4218, 1, 1, 1): ``Roberts 2010'' (3)
+% \item meta.id = 136566 (4218, 1, 3, 1): ``Roberts 2010'' (3)
+% \end{itemize}
+
+%which leads to a reduction of the meta-analyses that can be calculated based on the Fisher's z score by $n$ = \Sexpr{}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%<<echo=FALSE>>=
+% library(knitr)
+% opts_chunk$set(
+%      fig.path='figure/ch03_fig',
+%      self.contained=FALSE,
+%      cache=TRUE
+%  )
+%@
+
 \chapter{Results}
 
-\section{Meta-analysis}
-The data at hand is composed of over 400,000 results with balanced sample size $n > 24$.
-The significance of the p-values of treatment effect estimates was calculated for all results in the dataset with acceptable sample size and outcome measures as odds ratios, peto odds ratios, risk ratios, risk differences and mean and standardized mean differences.
-
-%Significance over time? Chunck 1
-
-It is possible to analyse all results that are not unique in their comparison, outcome and subgroup in the dataset by meta-analysis.
-So each study that has been repeated with respect to experimental setup is included.
-There are different meta-analys methods that can be applied, here, fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis using the Hartung-Knapp method are used.
-
-\vspace{0mm}
-In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e.
-if studies were not unique in the dataset with respect to their experimental setup).
-The significant of the treatment effect in a single result is then compared to the significance of the pooled treatment effect.
-In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
-The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure.
-The colors indicate the overall fraction of rejected or accepted null-hypotheses of no treatment effect.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small study effects}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Scale for 'x' is already present.
+Adding another scale for 'x', which\\\#\# will replace the existing scale.\\\#\# Scale for 'x' is already present.
+Adding another scale for 'x', which\\\#\# will replace the existing scale.}}\end{kframe}
+\end{knitrout}
+
+The median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
+It is clearly visible that the absolute value decreases with increasing sample size, i.e.
+that the effect size is becoming smaller.
+The trend flattens off after $\sim$ sample size = 400 (not shown).
+-- Appendix --
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-10-1}
 
 \end{knitrout}
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance}
+\caption{Median of the absolute $z$-score plotted against the total sample size.}
+\label{z.samplesize}
 \end{figure}
 
-One can visualise the fraction of studies with significant treatment effect separately for studies with significant primary treatment effect, and non-significant primary treatment effect, as done in Figure \ref{primary.secondary.significance.sep.sig}.
-It can be seen that primary significance and non-significance is often overruled when performing a meta-analysis.
+Only for illustration, the same trend is reproduced in Figure \ref{effect.samplesize.separated} with a similar method, using the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std.
+Mean Difference'' (the most commonly used in the dataset).
+The ``normalized effect'' is the original effect size, normalized with respect to all other effect sizes of the same measure (i.e.
+subtraction of mean and division through standard error of the mean).
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-14-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-11-1}
 
 \end{knitrout}
-\caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-\label{primary.secondary.significance}
+\caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
+\label{effect.samplesize.separated}
 \end{figure}
 
-The amount of significant heterogeneity in the results used by the meta-analyses is 53350 and corresponds to 81.5936377\% of the total number of meta-analyses.
-
-%Comparison of significance separated for significant Q? Chunck 2
-
-%Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5
-
-\section{Small study effects}
-
-To provide an overview over the abundance of small study effects in the dataset, first it is shown how median absolute effect size decreases with increasing sample size of the results (Figure \ref{effect.samplesize}).
-%In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.
-
-\vspace{0mm}
-A clear trend of decrease of absolute effect size with increasing sample size (i.e. smaller variance) is visible. 
-%It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off.
-With increasing sample size, there are fewer results, therefore, the variation between medians increases.
-All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation.
-Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.
+%Show absolute effect size depending on scaled time? Chunck 3
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small Study Effect Tests}
+
+The results of the test for small study effects for the meta-analyses fullfilling the criteria from chapter \ref{chapter01}, section \ref{sec:Processing}, are presented in Figures \ref{fig:test.bin}, \ref{fig:test.cont} and \ref{fig:test.surv}.
+The histogram of the $p$-values appears most often skewed to the right, indicating evidence for small study effects.
+Because different tests are applied depending on outcome type, the results are displayed separately for binary, continuous and survival outcome types (as previously defined in the dataset variable ``outcome.type'', see chapter \ref{ch:chapter01}, section \ref{sec:Processing}.
+\\
+For continuous and survival outcomes, the names refer to:
+
+\begin{itemize}
+\item Egger's test, the weigthed linear regression test as described in section \ref{sec:Egger}
+\item Thompson and Sharp's test, the weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
+\item Begg and Mazumdar's test, the rank test described in section \ref{sec:Begg}
+\end{itemize}
+
+For binary outcomes, the names refer to:
+\begin{itemize}
+\item Harbord's test, the likelihood score based test (section \ref{sec:Harbord})
+\item Peter's test, the weighted linear regression with inverse sample size as explanatory variable (study size proxy) described in section \ref{sec:Peter}
+\item R\"ucker's test, the test based on the arcsine transformation of proportions, in combination with Thompson and Sharp's regression test (section \ref{sec:Rucker})
+\item Schwarzer's test, the rank based test using the expected event counts computed with the hypergeometric distribution (section \ref{sec:Schwarzer})
+\end{itemize}
+
+\begin{figure}[!ht]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-13-1}
+
+\end{knitrout}
+\caption{Histogram of the $p$-values for small study effect in binary outcome meta-analyses.
+The testing method is indicated in the header, binwidth is equal to 0.1.
+The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
+\label{fig:test.bin}
+\end{figure}
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-16-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-14-1}
 
 \end{knitrout}
-\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
-\label{effect.samplesize}
+\caption{Histogram of the $p$-values for the small study effect in continuous outcome meta-analyses.
+The testing method is indicated in the header, binwidth is equal to 0.1.
+The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
+\label{fig:test.cont}
 \end{figure}
-
-The median absolute normalized effect size can be visualized for the different outcome measures separately (Figure \ref{effect.samplesize.separated}).
-The plot confirms the trend of median effect size decrease towards lower sample size (e.g.
-for Risk Ratios: decrease $> 0.1$ standard deviations from 10 to 50 study participants).
-Instead of normalizing the effects
-%(i.e. subtracting mean and dividing through the standard deviation) 
-for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-15-1}
 
 \end{knitrout}
-\caption{Median of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
-\label{effect.samplesize.separated}
+\caption{Histogram of the $p$-values for the small study effect in survival outcome meta-analyses.
+The testing method is indicated in the header, binwidth is equal to 0.1.
+The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
+\label{fig:test.surv}
 \end{figure}
 
-%Show absolute effect size depending on scaled time? Chunck 3
-
-\subsection{Small Study Effect Tests}
-
-There are tests that can be applied to find out if small study effects are present in the meta analysis.
+\subsection{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% 
+% <<echo=FALSE, warning=FALSE>>=
+% #Test Results: Binary
+% test.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+%                                                           schwarzer.test = mean(schwarzer.test),
+%                                                           rucker.test = mean(rucker.test),
+%                                                           harbord.test = mean(harbord.test),
+%                                                           peter.test = mean(peter.test))
+% test.bin <- test.bin %>% gather(key = "test.type", value = "mean")
+% 
+% p.bin <- meta.bin %>% ungroup() %>% 
+%   select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
+%   gather(key = "test.type", value = "null.hypothesis") %>%  
+%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+%   theme_bw() + xlab(label = NULL) +
+%   annotate("text", x = test.bin$test.type, y = 1000, 
+%            label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
+%            color = "white")
+% 
+% 
+% 
+% test.sig.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+%                                                               schwarzer.test = mean(schwarzer.test),
+%                                                               rucker.test = mean(rucker.test),
+%                                                               harbord.test = mean(harbord.test),
+%                                                               peter.test = mean(peter.test))
+% test.sig.bin <- test.sig.bin %>% gather(key = "test.type", value = "mean")
+% 
+% p1 <- meta.bin %>% ungroup() %>% filter(sig.fixef.bin == 1) %>% 
+% select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
+%   gather(key = "test.type", value = "null.hypothesis") %>% 
+%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+%   theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
+%   annotate("text", x = test.sig.bin$test.type, y = 1750, 
+%            label = paste(round(test.sig.bin$mean, 2)*100, "% rejected"), 
+%            color = "white")
+% 
+% test.nonsig.bin <- meta.bin %>% filter(sig.fixef.bin == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+%                                                                                                 schwarzer.test = mean(schwarzer.test),
+%                                                                                                 rucker.test = mean(rucker.test),
+%                                                                                                 harbord.test = mean(harbord.test),
+%                                                                                                 peter.test = mean(peter.test))
+% test.nonsig.bin <- test.nonsig.bin %>% gather(key = "test.type", value = "mean")
+% 
+% p2 <- meta.bin %>% 
+%   filter(sig.fixef.bin == 0) %>% ungroup() %>% 
+%   select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
+%   gather(key = "test.type", value = "null.hypothesis") %>% 
+%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+%   theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) +theme(legend.position="none") +
+%   annotate("text", x = test.nonsig.bin$test.type, y = 650, 
+%            label = paste(round(test.nonsig.bin$mean, 2)*100, "% rejected"), 
+%            color = "white")
+% 
+% range.pb.difference.bin <- range(test.sig.bin$mean - test.nonsig.bin$mean)
+% 
+% #Test Results: Continuous
+% test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+%                                                             begg.test = mean(begg.test),
+%                                                             thomson.test = mean(thomson.test))
+% 
+% test.cont <- test.cont %>% gather(key = "test.type", value = "mean")
+% 
+% p.cont <- meta.cont %>% ungroup() %>% 
+%   select(egger.test, thomson.test, begg.test) %>% 
+%   gather(key = "test.type", value = "null.hypothesis") %>% 
+%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+%   theme_bw() + xlab(label = NULL) +
+%   annotate("text", x = test.cont$test.type, y = 750, 
+%            label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
+%            color = "white")
+% 
+% 
+% test.sig.cont <- meta.cont %>% filter(sig.fixef.cont == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+%                                                                                                 begg.test = mean(begg.test),
+%                                                                                                 thomson.test = mean(thomson.test))
+% 
+% test.sig.cont <- test.sig.cont %>% gather(key = "test.type", value = "mean")
+% 
+% p3 <- meta.cont %>% 
+%   filter(sig.fixef.cont == 1) %>% ungroup() %>% 
+%   select(egger.test, thomson.test, begg.test) %>% 
+%   gather(key = "test.type", value = "null.hypothesis") %>% 
+%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+%   theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
+%   annotate("text", x = test.sig.cont$test.type, y = 600, 
+%            label = paste(round(test.sig.cont$mean, 2)*100, "% rejected"), 
+%            color = "white")
+% 
+% test.nonsig.cont <- meta.cont %>% filter(sig.fixef.cont == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+%                                                                                                    begg.test = mean(begg.test),
+%                                                                                                    thomson.test = mean(thomson.test))
+% 
+% test.nonsig.cont <- test.nonsig.cont %>% gather(key = "test.type", value = "mean")
+% 
+% p4 <- meta.cont %>% 
+%   filter(sig.fixef.cont == 0) %>% ungroup() %>% 
+%   select(egger.test, thomson.test, begg.test) %>% 
+%   gather(key = "test.type", value = "null.hypothesis") %>% 
+%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+%   theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
+%   annotate("text", x = test.nonsig.cont$test.type, y = 100, 
+%            label = paste(round(test.nonsig.cont$mean, 2)*100, "% rejected"), 
+%            color = "white")
+% 
+% range.pb.difference.cont <- range(test.sig.cont$mean - test.nonsig.cont$mean)
+% 
+% ########################################################################################################################################
+% ########################################################################################################################################
+% 
+% #Agreement proportions of publication bias tests:
+% 
+% #Binary:
+% n.bin <- dim(meta.bin)[1]
+% meta.bin <- meta.bin %>%ungroup() %>%  mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
+%                                         egger.peter = ifelse(egger.test == peter.test, "agree", "disagree"),
+%                                         egger.rucker = ifelse(egger.test == rucker.test, "agree", "disagree"),
+%                                         egger.harbord = ifelse(egger.test == harbord.test, "agree", "disagree"),
+%                                         schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
+%                                         schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
+%                                         schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
+%                                         rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
+%                                         rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
+%                                         harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
+% 
+% agreement.bin <- meta.bin %>% ungroup() %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
+%                                             egger.peter = sum(egger.peter == "agree")/n(),
+%                                             egger.rucker = sum(egger.rucker == "agree")/n(),
+%                                             egger.harbord = sum(egger.harbord == "agree")/n(),
+%                                             schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
+%                                             schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
+%                                             schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
+%                                             rucker.peter = sum(rucker.peter == "agree")/n(),
+%                                             harbord.peter = sum(harbord.peter == "agree")/n())
+% 
+% correlation.bin <- meta.bin %>%ungroup() %>%  summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
+%                                               egger.peter = cor(pval.egger.bin, pval.peter.bin),
+%                                               egger.rucker = cor(pval.egger.bin, pval.rucker.bin),
+%                                               egger.harbord = cor(pval.egger.bin, pval.harbord.bin),
+%                                               schwarzer.peter = cor(pval.schwarzer.bin, pval.peter.bin),
+%                                               schwarzer.rucker = cor(pval.schwarzer.bin, pval.rucker.bin),
+%                                               schwarzer.harbord = cor(pval.schwarzer.bin, pval.harbord.bin),
+%                                               rucker.peter = cor(pval.rucker.bin, pval.peter.bin),
+%                                               harbord.peter = cor(pval.harbord.bin, pval.peter.bin))
+% 
+% binary.tests.agreement <- rbind(agreement.bin, correlation.bin)
+% rownames(binary.tests.agreement) <- c("Test Agreement","P-value Correlation")
+% 
+% 
+% #Continuous:
+% n.cont <- dim(meta.cont)[1]
+% meta.cont <- meta.cont %>% ungroup() %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
+%                                           thomson.begg = ifelse(thomson.test == begg.test, "agree", "disagree"),
+%                                           egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"))
+% 
+% agreement.cont <- meta.cont %>% ungroup() %>%  summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
+%                                               thomson.begg = sum(thomson.begg == "agree")/n(),
+%                                               egger.begg = sum(egger.begg == "agree")/n())
+% 
+% correlation.cont <- meta.cont %>% ungroup() %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
+%                                                 thomson.begg = cor(pval.thomson.cont, pval.begg.cont),
+%                                                 egger.begg = cor(pval.egger.cont, pval.begg.cont))
+% 
+% cont.tests.agreement <- rbind(agreement.cont, correlation.cont)
+% rownames(cont.tests.agreement) <- c("Test Agreement","P-value Correlation")
+% 
+% ########################################################################################################################################
+% ########################################################################################################################################
+% 
+% 
+% #Trimfill missing studies fractions statistics:
+% trimfill.cont.mean <- meta.cont %>% ungroup %>% summarise(mean = mean(missing.trim.cont)) %>% select(mean)
+% trimfill.cont.median <- meta.cont %>% ungroup %>% summarise(median = median(missing.trim.cont)) %>% select(median)
+% 
+% trimfill.bin.mean <- meta.bin %>% ungroup %>% summarise(mean = mean(missing.trim.bin)) %>% select(mean)
+% trimfill.bin.median <- meta.bin %>% ungroup %>% summarise(median = median(missing.trim.bin)) %>% select(median)
+% 
+% ########################################################################################################################################
+% ########################################################################################################################################
+% 
+% change.ranef.bin <- meta.bin %>% ungroup() %>% 
+%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n)) 
+% 
+% p.change.ranef.bin <- meta.bin %>% ungroup() %>% 
+%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>%  
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+ 
+%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.ranef.bin[change.ranef.bin$sig.change == 3,]$correction.method, y = 1000, 
+%          label = paste(round(change.ranef.bin[change.ranef.bin$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
+%          color = "white")
+% 
+% change.ranef.cont <- meta.cont %>% ungroup() %>% 
+%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
+%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n))
+% 
+% p.change.ranef.cont <- meta.cont %>% ungroup() %>% 
+%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>%  
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes") +
+%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.ranef.cont[change.ranef.cont$sig.change == 3,]$correction.method, y = 500, 
+%          label = paste(round(change.ranef.cont[change.ranef.cont$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
+%          color = "white")
+% 
+% change.ranef <- meta %>% ungroup() %>% 
+%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
+%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n))
+% 
+% p.ranef.change <- meta %>% ungroup() %>% 
+%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>%  
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.ranef[change.ranef$sig.change == 3,]$correction.method, y = 1500, 
+%          label = paste(round(change.ranef[change.ranef$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
+%          color = "white")
+% # Significance after correction plots, separated for meta-analyses with significant publication bias test.
+% #Fixed effects meta-analysis significance
+% #Binary outcomes:
+% change.fixef.bin <- meta.bin %>% ungroup() %>% 
+%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
+%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n))
+% 
+% p.change.fixef.bin <- meta.bin %>% ungroup() %>% 
+%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>%  
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+  
+%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.fixef.bin[change.fixef.bin$sig.change == 3,]$correction.method, y = 800, 
+%          label = paste(round(change.fixef.bin[change.fixef.bin$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
+%          color = "white")
+% 
+% #Continuous outcomes:
+% change.fixef.cont <- meta.cont %>% ungroup() %>% 
+%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>% 
+%   mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n))
+% 
+% p.change.fixef.cont <- meta.cont %>% ungroup() %>% 
+%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>%  
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes")+ 
+%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.fixef.cont[change.fixef.cont$sig.change == 3,]$correction.method, y = 300, 
+%          label = paste(round(change.fixef.cont[change.fixef.cont$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
+%          color = "white")
+% 
+% #Overall:
+% change.fixef <- meta %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+% 	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n))
+% 
+% p.fixef.change <- meta %>% ungroup() %>% 
+%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>%  
+%   mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+%   theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
+% 	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 1500, 
+%          label = paste(round(change.fixef[change.fixef$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
+%          color = "white")
+% 
+% #Separated for meta-analyses with significant publication bias test.
+% change.fixef.bias <- meta %>% 
+%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+%   filter(thomson.test == 1) %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+% 	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n))
+% 
+% p.change.fixef.bias <- meta %>% 
+%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+%   filter(thomson.test == 1) %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+%   theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
+% 	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 250, 
+%            label = paste(round(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
+%            color = "white")
+% 
+% change.fixef.unbias <- meta %>% 
+%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+%   filter(thomson.test == 0) %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+% 	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>%  
+% 	mutate(n = n/sum(n))
+% 
+% p.change.fixef.unbias <- meta %>% 
+%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+%   filter(thomson.test == 0) %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+%   theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
+% 	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$correction.method, y = 1300, 
+%            label = paste(round(change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
+%            color = "white")
+% 
+% 
+% ########################################################################################################################################
+% ########################################################################################################################################
+% 
+% p.missing.copas <- meta %>% ggplot(aes(x = missing.copas/n)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20)
+% p.missing.trim <- meta %>% ggplot(aes(x = missing.trim)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20)
+% @
+% 
+% There are tests that can be applied to find out if small study effects are present in the meta analysis.
 For the precise description, see the methods section.
 Application of the tests is only recommended if there are ten or more studies \citep{cochrane.handbook} that can be used, so all meta-analyses with less than ten studies have been excluded.
-
-\vspace{0mm}
-There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
-In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = 1383)
-The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3442).
+% 
+% \vspace{0mm}
+% There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
+In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = n.cont)
+% The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = n.bin).
 The amount of studies varies from 5\% (Schwarzer's Test) to 13 \% (Egger's Test) for binary outcomes and 9\% (Begg and Mazumdar's Test) to 25 \% (Egger's Test) for continuous outcomes.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-\label{bias.results.cont}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-\label{bias.results.bin}
-\end{figure}
-
-There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not.
-Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by 0.0768414 (the minimal increase is 0.0103761 for Schwarzer's Test).
-
-%Show plots of significant meta-analyses separated? Chunck 4
-
-Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses).
+% 
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(p.cont)
+% @
+% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
+% \label{bias.results.cont}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(p.bin)
+% @
+% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
+% \label{bias.results.bin}
+% \end{figure}
+% 
+% There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not.
+Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by range.pb.difference.bin[2] (the minimal increase is range.pb.difference.bin[1] for Schwarzer's Test).
+% 
+% %Show plots of significant meta-analyses separated? Chunck 4
+% 
+% Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses).
 The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}.
@@
 The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
-\label{pub.bias.overtime}
-\end{figure}
-
-The agreement of the tests, i.e.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
+%   ggplot(aes(x = mean.publication.year, fill = factor(thomson.test), stat(count))) + geom_density(na.rm = T, position = "fill") + 
+%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+% @
+% \caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
+% \label{pub.bias.overtime}
+% \end{figure}
+% 
+% 
+% The agreement of the tests, i.e.
 the proportion of meta-analyses where the rest results are equal between tests, is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
@@
 Correlation varies more between tests, both for continuous and binary outcome tests.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:58:07 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
- & Test Agreement & P-value Correlation \\ 
-  \hline
-egger.schwarzer & 0.87 & 0.39 \\ 
-  egger.peter & 0.89 & 0.51 \\ 
-  egger.rucker & 0.88 & 0.48 \\ 
-  egger.harbord & 0.93 & 0.76 \\ 
-  schwarzer.peter & 0.89 & 0.29 \\ 
-  schwarzer.rucker & 0.88 & 0.34 \\ 
-  schwarzer.harbord & 0.92 & 0.51 \\ 
-  rucker.peter & 0.92 & 0.67 \\ 
-  harbord.peter & 0.91 & 0.52 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)} 
-\label{agreement.bin}
-\end{table}
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Apr 29 12:58:07 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
- & Test Agreement & P-value Correlation \\ 
-  \hline
-thomson.egger & 0.89 & 0.69 \\ 
-  thomson.begg & 0.82 & 0.47 \\ 
-  egger.begg & 0.79 & 0.36 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)} 
-\label{agreement.cont}
-\end{table}
-
-\vspace{0mm}
-Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
+% 
+% <<results = 'asis', echo = FALSE, warning = FALSE>>=
+% print(xtable(x = t(binary.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)", label = "agreement.bin",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
+% @
+% 
+% 
+% <<results = 'asis', echo = FALSE, warning = FALSE>>=
+% print(xtable(x = t(cont.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)", label = "agreement.cont",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
+% @
+% 
+% \vspace{0mm}
+% Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
 The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}.
 %(Suggests that 10 is likely too small)
-In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
+% In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
 A trend towards more rejections for larger sample sizes can be seen.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-24-1}
-
-}
-
-\end{knitrout}
-\caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
-\label{pvalues.samplesize}
-\end{figure}
-
-\vspace{0mm}
-One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
-The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.18.
-% A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% meta %>% filter(n < 40) %>% ggplot(aes(stat(count), x = n, fill = factor(thomson.test))) + 
+%   geom_density(position = "fill")
+% @
+% \caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
+% \label{pvalues.samplesize}
+% \end{figure}
+% 
+% 
+% 
+% \vspace{0mm}
+% One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
+The mean fraction of trimmed comparisons for binary outcomes is round(trimfill.bin.mean,2) and the median round(trimfill.bin.median,2).
+% % A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
 In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses.
-In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
+% In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
 In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-25-1}
-
-}
-
-\end{knitrout}
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
-\label{trimfill.pvalues.bin}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-26-1}
-
-}
-
-\end{knitrout}
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
-\label{trimfill.pvalues.cont}
-\end{figure}
-
-\subsection{Small Study Effect Correction}
-Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% meta.bin %>% filter(missing.trim.bin < 0.5) %>% 
+%   ggplot(aes(x = missing.trim.bin, fill = factor(peter.test), stat(count))) + 
+%   geom_density(na.rm = T, position = "fill") + 
+%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+% @
+% \caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
+% \label{trimfill.pvalues.bin}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% meta.cont %>% filter(missing.trim.cont < 0.5) %>% 
+%   ggplot(aes(x = missing.trim.cont, fill = factor(thomson.test), stat(count))) + 
+%   geom_density(na.rm = T, position = "fill") + 
+%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+% @
+% \caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
+% \label{trimfill.pvalues.cont}
+% \end{figure}
+% 
+% 
+% \subsection{Small Study Effect Correction}
+% Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
 Three of them will be applied to the meta-analyses shown previously that have ten or more study results and are therefore eligible for testing for publication bias.
-
-\vspace{0mm}
-The extent to what the results of the meta-analysis results are changed can be investigated.
+% 
+% \vspace{0mm}
+% The extent to what the results of the meta-analysis results are changed can be investigated.
 Because statistical significance is often used to decide if there is a treatment effect, a non-significant corrected effect size estimate can indicate that an observed treatment effect has been accepted because of small study effects.
 Therefore, the cases have been counted in which
-\begin{enumerate}
-\item Significance or non-significance of pooled estimate of meta-analysis did not change after correction for small study effects.
-\item Significance of pooled estimate of meta-analysis did change to non-significance after correction for small study effects.
-\item Non-significance of pooled estimate of meta-analysis did change to significance after correction for small study effects.
-\end{enumerate}
-
-The results of this can be seen in Figure \ref{significance.change.fixed} for all three methods, comparing the significance of the corrected pooled effect size estimate with the significance of the pooled effect size estimate of the fixed effects meta-analysis.
+% \begin{enumerate}
+% \item Significance or non-significance of pooled estimate of meta-analysis did not change after correction for small study effects.
+% \item Significance of pooled estimate of meta-analysis did change to non-significance after correction for small study effects.
+% \item Non-significance of pooled estimate of meta-analysis did change to significance after correction for small study effects.
+% \end{enumerate}
+% 
+% The results of this can be seen in Figure \ref{significance.change.fixed} for all three methods, comparing the significance of the corrected pooled effect size estimate with the significance of the pooled effect size estimate of the fixed effects meta-analysis.
 The same for significance of random effects meta-analysis is shown in Figure \ref{significance.change.random}.
@@
 Notably, the correction methods has been applied to all meta-analyses, thus also for such that had no significant small study effect test result.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-27-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction.}
-\label{significance.change.fixed}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-28-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction.}
-\label{significance.change.random}
-\end{figure}
-
-Since it has been previously seen in Figure \ref{test.results} that the results of small study effects vary considerably between continuous outcomes, the results in significance change from fixed effects meta-analysis can be seen separately in Figure \ref{significance.change.fixed.sep} for continuous and binary outcomes.
+% 
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(p.fixef.change)
+% @
+% \caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction.}
+% \label{significance.change.fixed}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(p.ranef.change)
+% @
+% \caption{Change in signficance of random effects meta-analysis pooled estimate after correction.}
+% \label{significance.change.random}
+% \end{figure}
+% 
+% Since it has been previously seen in Figure \ref{test.results} that the results of small study effects vary considerably between continuous outcomes, the results in significance change from fixed effects meta-analysis can be seen separately in Figure \ref{significance.change.fixed.sep} for continuous and binary outcomes.
 The change in significance from random effects meta-analysis to significance of corrected estimate can be seen in Figure \ref{significance.change.fixed.sep}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-29-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.fixed.sep}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-30-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.random}
-\end{figure}
-
-Because the real amount of publication bias in the dataset is not known, the correction method can also be applied only to meta-analyses that have publication bias according to the small study effect tests in the previous section.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(p.change.fixef.bin, p.change.fixef.cont, ncol = 1)
+% @
+% \caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
+% \label{significance.change.fixed.sep}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(p.change.ranef.bin, p.change.ranef.cont, ncol = 1)
+% @
+% \caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
+% \label{significance.change.random}
+% \end{figure}
+% 
+% Because the real amount of publication bias in the dataset is not known, the correction method can also be applied only to meta-analyses that have publication bias according to the small study effect tests in the previous section.
 Because the test developed by \citet{thomson.sharp} has been applied to both binary and continuous outcome meta-analyses (in the case of binary outcomes to arcsine variance stabilized proportions), it is used as a criterium to distinguish biased from unbiased meta-analyses.
@@
 Fixed effects meta-analysis has been used to determine signficance of the uncorrected estimate.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-31-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.random}
-\end{figure}
-
-Similarly, the number of missing studies per meta-analysis, i.e.
+% 
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(p.change.fixef.bias, p.change.fixef.unbias, ncol = 1)
+% @
+% \caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
+% \label{significance.change.random}
+% \end{figure}
+% 
+% Similarly, the number of missing studies per meta-analysis, i.e.
 those which have not been included because of small study effects, are estimated by the copas and trim-and-fill method and their empirical distribution is shown in histograms in Figure \ref{missing.studies.distribution}.
 For visualisation, the fraction of unpublished studies from the total fraction of available studies is shown.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-32-1}
-
-}
-
-\end{knitrout}
-\caption{Fraction of missing studies estimated of the number of total studies included in the meta-analysis for copas selection and trim-and-fill method.}
-\label{missing.studies.distribution}
-\end{figure}
-
-% # <<results = 'asis', Echo = FALSE>>=
-% # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
-% #                                             schwarzer.rejection = mean(schwarzer.test),
-% #                                             rucker.rejection = mean(rucker.test),
-% #                                             harbord.rejection = mean(harbord.test),
-% #                                             peter.rejection = mean(peter.test))
-% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
-% # @
-
-% 
-% For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(p.missing.copas, p.missing.trim, ncol = 1)
+% @
+% \caption{Fraction of missing studies estimated of the number of total studies included in the meta-analysis for copas selection and trim-and-fill method.}
+% \label{missing.studies.distribution}
+% \end{figure}
+% 
+% 
+% 
+% 
+% % # <<results = 'asis', Echo = FALSE>>=
+% % # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
+% % #                                             schwarzer.rejection = mean(schwarzer.test),
+% % #                                             rucker.rejection = mean(rucker.test),
+% % #                                             harbord.rejection = mean(harbord.test),
+% % #                                             peter.rejection = mean(peter.test))
+% % # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
+% % # @
+% 
+% 
+% 
+% 
+% 
+% 
+% % 
+% % For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
 The following three figures show the distribution of p-values of the corresponding tests.
 Note that only meta analyses with more than 10 comparisons have been included.
-% 
-% \vspace{0mm}
-% Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
+% % 
+% % \vspace{0mm}
+% % Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
 The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "linreg")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
-% \label{egger.cont}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "mm")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
-% \label{thomson.cont}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "rank")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{begg.cont}
-% \end{figure}
-% 
-% 
-% For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-%   filter(events1 > 0 | events2 > 0) %>% 
-%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{peters.bin}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-%   filter(events1 > 0 | events2 > 0) %>% 
-%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{harbord.bin}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Since most of the times the study publication year is available for a given result, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.
+% % 
+% % \begin{figure}
+% % <<echo=FALSE>>=
+% % data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
+% %   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
+% %   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
+% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+% %   mutate(n = n()) %>% filter(n > 9) %>% 
+% %   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
+% %                             method = "linreg")$p.val) %>% 
+% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+% %   theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% % @
+% % \caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
+% % \label{egger.cont}
+% % \end{figure}
+% % 
+% % 
+% % \begin{figure}
+% % <<echo=FALSE>>=
+% % data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
+% %   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
+% %   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
+% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+% %   mutate(n = n()) %>% filter(n > 9) %>% 
+% %   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
+% %                             method = "mm")$p.val) %>% 
+% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+% %   theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% % @
+% % \caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
+% % \label{thomson.cont}
+% % \end{figure}
+% % 
+% % \begin{figure}
+% % <<echo=FALSE>>=
+% % data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
+% %   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
+% %   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
+% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+% %   mutate(n = n()) %>% filter(n > 9) %>% 
+% %   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
+% %                             method = "rank")$p.val) %>% 
+% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+% %   theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% % @
+% % \caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
+% % \label{begg.cont}
+% % \end{figure}
+% % 
+% % 
+% % For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
+% % 
+% % \begin{figure}
+% % <<echo=FALSE>>=
+% % data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
+% %   filter(events1 > 0 | events2 > 0) %>% 
+% %   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
+% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+% %   mutate(n = n()) %>% filter(n > 9) %>% 
+% %   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
+% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+% %   theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% % @
+% % \caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
+% % \label{peters.bin}
+% % \end{figure}
+% % 
+% % 
+% % \begin{figure}
+% % <<echo=FALSE>>=
+% % data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
+% %   filter(events1 > 0 | events2 > 0) %>% 
+% %   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
+% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+% %   mutate(n = n()) %>% filter(n > 9) %>% 
+% %   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
+% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+% %   theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% % @
+% % \caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
+% % \label{harbord.bin}
+% % \end{figure}
+% 
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% % Since most of the times the study publication year is available for a given result, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.
 The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
-% @
-% \caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
-% \label{study.significance.overtime}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 2
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
+% % 
+% % \begin{figure}
+% % <<echo=FALSE, warning=FALSE>>=
+% % data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
+% %   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
+% % @
+% % \caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
+% % \label{study.significance.overtime}
+% % \end{figure}
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 2
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% % The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
 Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
@@
 This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(sig.meta.Q1, nonsig.meta.Q, ncol= 1)
-% @
-% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
+% % 
+% % \begin{figure}
+% % <<echo=FALSE, warning=FALSE>>=
+% % grid.arrange(sig.meta.Q1, nonsig.meta.Q, ncol= 1)
+% % @
+% % \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
 The fractions have been calculated
-% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-% \label{primary.secondary.significance.sep.sig}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 3
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
+% % by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
+% % \label{primary.secondary.significance.sep.sig}
+% % \end{figure}
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 3
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% % A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
 This can again be done for the entire dataset, i.e.
@@
 In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
-%                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
-%   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
-%   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
-%   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
-%   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
-%   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
-% @
-% \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
-% \label{effects.overtime.separated}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 4
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
+% % 
+% % \begin{figure}
+% % <<echo=FALSE>>=
+% % data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
+% %                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
+% %   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
+% %   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
+% %   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
+% %   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
+% %   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
+% % @
+% % \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
+% % \label{effects.overtime.separated}
+% % \end{figure}
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 4
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% % The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
 This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p3, p4, ncol = 2)
-% @
-% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-% \label{bias.results.cont.sep}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p1, p2, ncol = 2)
-% @
-% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-% \label{bias.results.bin.sep}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% #Proportion of significant pooled estimates based on proportion of single pooled estimates
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type)) + geom_histogram()
-% 
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
-%   geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% 
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
-%   geom_histogram(position = "fill")
-% 
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef))) + 
-%   geom_histogram()
-
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.secondary.over.meansig)
-% @
-% \caption{Fraction of significant meta-analysis, dependent on the fraction of significant single results.}
-% \label{secondary.significance.over.meansig}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % 
+% % \begin{figure}
+% % <<echo=FALSE, warning=FALSE>>=
+% % grid.arrange(p3, p4, ncol = 2)
+% % @
+% % \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
+% % \label{bias.results.cont.sep}
+% % \end{figure}
+% % 
+% % \begin{figure}
+% % <<echo=FALSE, warning=FALSE>>=
+% % grid.arrange(p1, p2, ncol = 2)
+% % @
+% % \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
+% % \label{bias.results.bin.sep}
+% % \end{figure}
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 5
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% % #Proportion of significant pooled estimates based on proportion of single pooled estimates
+% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type)) + geom_histogram()
+% % 
+% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
+% %   geom_density(na.rm = T, position = "fill") + 
+% %   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+% % 
+% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
+% %   geom_histogram(position = "fill")
+% % 
+% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef))) + 
+% %   geom_histogram()
+% 
+% % \begin{figure}
+% % <<echo=FALSE, warning=FALSE>>=
+% % plot(p.secondary.over.meansig)
+% % @
+% % \caption{Fraction of significant meta-analysis, dependent on the fraction of significant single results.}
+% % \label{secondary.significance.over.meansig}
+% % \end{figure}
+% 
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
 
@@
 \chapter{Methods}
-
-\section{Basic notation}
-The notation used here will be used throughout the chapter and exceptions will be noted.
+\section{Introduction and Notation}
+The analysis has already been said to be restricted on clinical or health care interventions.
+The interventions are restricted to comparisons of two treatment arms by some measure of sanity or worsening of health.
+The difference in this measure between the grouops is referred to as the treatment effect.
+Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or Hedges $g$, Fisher's z score or Pearsons correlation coefficient.
+\\
+Let us consider a meta-analysis with $n$ study treatment effects ($n > 1$, but typically small).
+A study is indexed by $i$, and it's treatment effect by  $\theta_i$.
+The observed treatment effect is $\hat{\theta}_i$.
+The pooled treatment effect of a meta-analysis will be denoted as $\theta_M$, and consequently, the observed pooled treatment effect as $\hat{\theta}_M$.
+Furthermore, each treatment effect is typically measured with some standard error $s_i$ and an estimate of $s_i$ is denoted as $\hat{s}_i$.
+The $\hat{}$ sign thus indicates if it is an estimate.\\
+For continuous outcomes, let $m_t$ be the mean of the treatment group, $m_c$ the mean of the control group, and equivalently $\textrm{sd}_t$ and $\textrm{sd}_c$ the corresponding standard deviations.
+$n_t$ and $n_c$ are the total number of participants in the groups.
+In the case of binary outcomes, let $e_t$ be the count of events in the treatment arm $e_c$ the count of events in the control group.
+The observed counts in a study $i$ are referred to as $e_{t,i}$ and analogously $e_{c,i}$.
+
+\section{Effect Measures and $p$-values}
+\subsection{Continuous Outcomes}
+For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Hedges $g$) and  a standard error thereof.
+Note that the definition of Hedges $g$ and its standard error $s$ varies among the literature, the following applies for this report:
+
+\begin{align}
+s &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}} & g &= \frac{m_t - m_c}{s} \label{eq:hedges.g}
+\end{align}
+
+The mean difference $\theta$ and its standard error $s$ can similarly be obtained by
+
+\begin{align}
+\theta &= m_t - m_c & s &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_t}
+\end{align}
+
+Both estimators take into account that the two groups might have unequal variances.
+A $p$-value to test the null hypothesis that the mean between group is equal is commonly obtained with the students $t$ test.
+The $t$ statistic is obtained, using $s$ and $g$ from \ref{eq:hedges.g}, by
+
+\begin{align}
+t &= g/(s\sqrt{(1/n_t)+(1/n_c)}) \nonumber
+\end{align}
+and the $p$-value can be obtained with the cumulative student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
+
+\begin{align}
+p &= 2(1-F(|t|)) \nonumber
+\end{align}
+
+The t-test is known to be not very reliable if combined sample size is small ($n < 30$), see for example \citet{t.test}.
+
+\subsection{Binary Outcomes}
+Two commonly used effect measures for binary outcome data are risk ratios and odds ratios between treatment and control group. 
+The methods presented here can also be found, for example, in \cite[34]{Intro.meta}.
+Let $\theta$ be the logarithm to base 10 of the odds ratio. $\theta$ and its variance $s^2$ can be obtained by
+
+\begin{align}
+\hat{\theta} &= \log(\frac{e_t*(n_c - e_c)}{e_c*(n_t - e_t)}) \nonumber \\
+\hat{s}^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
+\end{align}
+
+Plugging in the observed counts will give the corresponding estimates. The logarithm of the risk ratio $\theta$ and its variance $s^2$ is similarly defined as
+
+\begin{align}
+\theta &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
+s^2 &= 1/e_t + 1/n_t + 1/e_c + 1/e_t \label{eq:risk.ratio.variance}
+\end{align}
+
+Using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$-value, e..g.
+\cite[98]{held2014}.
+\\
+Thus, with $\Phi$ as the cumulative standard normal distribution, we get
+\begin{align}
+p &= 2*(1-\Phi(|\hat{\theta}/\hat{s}|) \nonumber
+\end{align}
+, a $p$-value for the corresponding estimates, which summarizes the evidence against $\hat{\theta}$ being zero (i.e. the true risk/odds ratio being 1). \\
+Binary and continuous effect measures can be converted into each other, as described in section \ref{sec:transformation.effectsizes}.
+
+\subsection{Survival Outcomes}
+Time-to-event data with censoring has to be analyzed by special means.
+One frequently used method to take into account right-censoring is the Cox proportional hazards regression model \citep{Cox}.
+Because the method itself is not applied in this thesis, but only the resulting estimates of the parameters are used, the reader is referred to the extensive literature covering this topic (e.g.
+\citet{Surv}).
+\\
+The so-called hazard ratio estimated by cox p.h.
+regression is the ratio of the instantaneous risk of experiencing the event between two groups.
+Because it is a maximum likelihood estimator, one can again use its Wald test statistic to test for equal hazards.
+Let $\hat{\theta}$ be an estimate of the log hazard ratio and $\hat{s}$ an estimate of the standard error of it.
+As before
+\begin{align}
+p &= 2*(1-\phi(|\hat{\theta}/\hat{s}|) \nonumber
+\end{align}
+will give a $p$-value for the evidence against the null hypothesis.
+
+\section{Fixed and Random Effects Meta-Analysis} \label{sec:meta.analysis}
+The fixed effects meta-analysis estimator of the pooled treatment effect is a mean of the single treatment effect estimators, weighted by their standard errors \citep{fixed.effects.rosenthal}.
+Let $w_i = 1/s_i^2$ be the weights, and $\theta_M$ be the pooled estimator and $s_M^2$ its variance.
+Then
+
+\begin{align}
+\theta_M &= \frac{\sum_{i = 1}^n w_i \theta_i}{\sum_{i = 1}^n w_i} &
+s_M^2 &= \frac{1}{\sum_{i = 1}^n w_i} \label{eq:fixed.effects}
+\end{align}
+
+This estimator minimizes the variance between the effects.
+An estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and variances $\hat{\theta}_i, \hat{s}_i^2$.
+The underlying idea is that we assume $\theta_i \sim N(\theta_M, s_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.
+\\
+The random effects model \citep{whitehead} assumes instead that 
+\begin{align}
+\theta_i \sim N(\mu_i, s_i^2) &&
+\mu_i \sim N(\theta_M, \tau^2) \label{eq:random.effects} 
+\end{align}
+
+Marginally, we have $\theta_i$ being distributed around a common mean $\theta_M$ with additional variance $\tau^2$:
+
+\begin{align}
+\theta_i | \mu_i \sim N(\theta_M, s_i^2 + \tau^2) \nonumber %\label{eq:random.effects.marginal}
+\end{align}
+
+$\tau^2$ is often referred to as a population variance or between-study variance, whereas $s_i^2$ can be interpreted as sampling error.
+The pooled treatment effect estimate $\theta_M$ of the random effects model and its variance is obtained by replacing the weights $w_i$ in equation \ref{eq:fixed.effects} with $w_i = 1/(s_i^2 + \tau^2)$.
+\\
+The model is superior to the fixed effects model whenever the standard errors of the treatment effects alone are unlikely to fully account for the entire variability observed between studies.
+Note that as $\tau^2$ increases, each $\theta_i$ will eventually get equal weights, irrespective of it's sampling error $s_i^2$.\\
+The estimation of $\tau^2$ has been subject to some debate in the statistical literature. Oftentimes, the method of moment estimator of \citet{tau.estimator} is used.
+We use the measure of heterogeneity, $Q$, and divide by $C$ after having subtracted the degrees of freedom $n-1$:
+
+\begin{align}
+Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i}\label{eq:Q.heterogeneity} \\
+\tau^2 &= \max(0, \frac{Q - (n-1)}{C}) \label{eq:Tau.definition}
+\end{align}
+
+Again, $w_i, \theta_i ...$ have to be replaced by their estimates in order to get an estimate $\hat{\tau}^2$. \\
+The Paule-Mandel estimator \citep{paulemandel} is considered to have most often better properties than the method of moments estimator (e.g. \citet{tau.estimator.evaluation}).
+Since we defined $w_i = 1/(s_i^2 + \tau^2)$, it als holds that
+
+\begin{align}
+w_i \textrm{Var}(\theta_i) &= 1 & \textrm{Var}(\sqrt{w_i}\theta_i) = 1 \nonumber
+\end{align}
+
+For any $w_i$, the variance can be estimated and equated to its expected value:
+
+\begin{align}
+s^2(w_i\theta_i) &= \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} & \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} = 1 \label{eq:paulemandel}
+\end{align}
+
+$\theta_M$ can be estimated using equation \ref{eq:fixed.effects}, the only problem is to estimate $\tau^2$. It can be obtained through an iterative process, using a newly defined function
+
+\begin{align}
+F(\tau^2) &= \sum_{i = 1}^n w_i(\theta_i - \theta_M)^2 - (n-1) \nonumber
+\end{align}
+
+In view of equation \ref{eq:paulemandel}, $\tau^2$ must be such that $F(\tau^2) = 0$.
+Then, we start with a arbitrary $\tau^2$ and repeatedly add a term $\tau_0^2$ to update $\tau^2$ until $F(\tau^2 + \tau_0^2)$ is close to zero (using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{\theta}_M$).
+Using a truncated Taylor series expansion, one can obtain the partial derivative after $\tau^2$, which is a reasonable choice for $\tau_0^2$.
+\\
+%Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{theta}$, we can update $F(\tau^2)$ and check convergence to zero. \\
+The estimation of $\tau^2$ is accompanied by uncertainty.
+A common procedure is to test if it is there is significant heterogeneity between the studies \cite[109]{Intro.meta}.
+Compute $Q$, as given in \ref{eq:Q.heterogeneity}, based on one of the estimators of $\tau^2$.
+It is assumed that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equally distributed effect sizes.
+Thus, the expected value of $Q$ is $n-1$, and the excess dispersion is $Q - n + 1$.
+The $p$-value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
+= $n-1$.
+\\
+An advantage of the $\tau^2$ is that it is directly linked to the variability in the data.
+Additionally, one can use the $I^2$ statistic to see what portion the between study variance has of the overall variance.
+It is computed as
+
+\begin{align}
+I^2 &= (Q - n + 1)/Q \nonumber%\label{I2.proportion}
+\end{align}
+
+%Large values for $\hat{I}^2$ are of great importance when analyzing e.g. small study effects. \\
+Importantly, all proposed methods above assume normally distributed effect sizes and proper estimates $\hat{s}$ of the true standard error.
+This assumptions are not met for very small sample sizes and very few event counts.
+Alternatively, the mantel-haenszel method for risk and odds ratios (see e.g.
+\citet{mantel.haenszel}) could be used in the latter case.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small Study Effects Tests}
+The tests that will be presented on the following pages are a common way to detect publication bias.
+Importantly, they are however not interpretable directly as evidence for publication bias, but this is left for the discussion chapter.
+The tests are also often referred to as funnel plot asymmetry tests, because of the popularity of a recent test that has been used frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citet{trimfill}.
+However, it is known for some time that the method has disadvantageous properties, therefore, it will not be discussed here, as well as the funnel plot (the radial plot will be used as an alternative).\\
+A test for small study effects will test in some ways if the size of the estimated treatment effect of a study depends on some measure of its size.
+An association between study size and treatment effect size can be interpreted as an artifact of publication bias.
+
+\subsection{Continuous Outcome Tests}
+For a continuous outcomes that are normally distributed, the sample mean and variance are independent of each other \cite[120]{meta.w.R}.
+Thus, the estimated standard errors of treatment effects can be used as a proxy for study size, as they should in principle not be tied to the effect size.
+
+\subsubsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
+\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+A standardized effect size $\theta_i^\star$ can be computed as in \ref{begg.stand.eff}.
+$s_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \ref{begg.stand.var}, $\theta_M$ being the fixed effects pooled treatment effect (\ref{eq:fixed.effects}.
+
+\begin{align}
+\theta_i^\star &= (\theta_i - \theta_M)/s_i^{2\star} \label{begg.stand.eff}  \\
+s_i^{2\star} &= s_i^2 - 1/\sum_{i = 1}^n\frac{1}{s_i^2}1 \label{begg.stand.var} 
+\end{align}
+
+A rank correlation test based on Kendall's tau is then used.
+First, the pairs are ordered after their ranks based on $s^{2\star}$.
+Then, for each $s^{2\star}$ rank, the corresponding ranks based on $\theta^{2\star}$ that are larger are counted and summed up to $u$.
+The number of ranks based on $\theta^{2\star}$ that are in contrary, smaller, are counted and summed up to $l$.
+Then the normalized test statistic $Z$ is given as
+
+\begin{align}
+Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \nonumber
+\end{align}
+
+Thus, large number of concordance between pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$.
+The $p$-value is obtained using the standard normal distribution $\Phi$:
+\begin{align}
+p &= 2*(1-\Phi(|Z|)) \nonumber
+\end{align}
+
+The changes that have to be made int the case of ties are small and can be found in \cite[410]{begg.ties}.
+
+\subsubsection{Egger's Test: Weighted Linear Regression Test} \label{sec:Egger}
+First, the concept of simple linear regression is introduced. In short, the model assumes a dependent variable $y$ to be a linear function of another explanatory variable $x$:
+
+\begin{align}
+y &= \beta_0 + \beta_1 x + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:simple.regression}
+\end{align}
+
+$\epsilon$ is the residual noise term that becomes necessary when $n$ pairs $(x_i, y_i)$ are given and there is no exact solution.
+Then it is common to look for the solution that minimizes the squared residuals, the least-squares solution.
+Formally,
+
+\begin{align}
+\operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i) \label{eq:least.squares}
+\end{align}
+
+Let $\mathbf{X}$ be a matrix with the explanatory variables $x$ and $\mathbf{y}$ a corresponding vector for all $y$:
+
+\begin{equation*}
+\mathbf{X} = 
+\begin{bmatrix}
+1 & x_{12} \\
+1 & x_{22} \\
+1 & x_{32} \\
+\vdots & \vdots \\
+1 & x_{n2} \\
+\end{bmatrix} 
+\qquad
+\mathbf{y} = 
+\begin{bmatrix}
+y_1 \\
+y_2 \\
+y_3 \\
+\vdots \\
+y_n \\
+\end{bmatrix}
+\end{equation*}
+
+Let $\mathbf{\beta} = (\beta_0, \beta_1)^\top$. It can be shown that
+
+\begin{align}
+\hat{\mathbf{\beta}} &= (\mathbf{X}^\top \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
+\end{align}
+
+Is an estimator of $\mathbf{\beta}$ that minimizes the squared residuals.
+Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\mathbf{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$.
+The variance estimates $\hat{\sigma}^2$ and $\hat{\mathbf{s}}_\beta^2$ are
+
+\begin{align}
+\hat{\sigma}^2 &= \frac{1}{n-2}\mathbf{r}^\top \hat{\mathbf{r}} & \hat{\mathbf{s}}_\beta^2 &= \hat{\sigma}^2 (\mathbf{X}^\top \mathbf{X})^{-1} \label{eq:regression.variances}
+\end{align}
+
+The estimate $\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the regression line. Furthermore, in the simple linear regression setting, $\hat{\beta}_0$ can also be obtained by:
+
+\begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} &
+\hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \nonumber
+\end{align}
+
+$\bar{x}, \bar{y}$ denoting the sample means of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$. Thus, $\hat{\beta}_0$ is also called global mean.
+To test whether there is evidence for the intercept $\beta_0$ to be unequal to some value $\beta_{H0}$, a $t$-test can be used.
+
+\begin{align}
+p &= 2(1-F(|(\beta_0 - \beta_{H0})/s_{\beta_0}|)) \nonumber
+\end{align}
+
+where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. $p$ will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
+The concept is extendable to weighted linear regression.
+Weighted linear regression may be used if the residuals $\mathbf{r}$ have unequal variances, which is equivalent to ascribe different precision to the observed $y$.
+The least squares equation \ref{eq:least.squares} is extended to
+
+\begin{align}
+\operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
+\end{align}
+
+with positive weights $w_i$ that penalize large squared residuals for some $i$ more if $w_i$ is larger compared to other $w_i$. \\
+Let $\mathbf{W}$ be a $n \times n$ matrix with $\mathbf{W}_{ii} = w_i$, the weights on the diagonal and zeros on the off-diagonals.
+The estimates in \ref{eq:regression.parameters} and \ref{eq:regression.variances} can still be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$.
+\label{weighted.regression} \\
+Now it is shown how linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citet{Egger}.
+Let $\theta/s$ be the dependent variable $y$ and $1/s$ the explanatory variable $x$.
+If plotted, this corresponds to a radial or Galbraith plot \citet{galbraith}.
+The linear regression equation as introduced before in \ref{eq:simple.regression} can be written in two ways:
+
+\begin{align}
+\theta/s &= \beta_0 + \beta_1/s + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:radial.plot} 
+\end{align}
+
+\ref{eq:radial.plot} is often provided due to the correspondence to the radial plot. However, it is equivalent to
+
+\begin{align}
+\theta &= \beta_0 + \beta_1 s + \epsilon, & \epsilon \sim N(0, w^{-1}\sigma^2) \label{eq:egger.plot}
+\end{align}
+
+with weights $w = 1/s^2$.
+Thus testing $\beta_0$ of \ref{eq:radial.plot} or $\beta_1$ is equivalent.
+The corresponding $p$-value is then used as evidence for a small study effect.
+Plugging in  $\theta_i/s_i, 1/s_i$ as $y_i, x_i$ into equation \ref{eq:regression.parameters} and \ref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{s}_{\beta_0}$ and $\hat{s}_{\beta_1}$.
+
+% \begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (\varphi_i - \bar{\varphi})(\theta^\star_i - \bar{\theta}^\star)}{\sum_{i = 1}^n (\varphi_i - \bar{\varphi})^2} &
+% \hat{\beta}_0 &= \bar{\theta}^\star - \hat{\beta}_1 \bar{\varphi} \nonumber
+% \end{align}
+
+\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{sec:Thompson}
+A method proposed in \citet{thompson.sharp} allows for between study variance $\tau^2$, as introduced before in section \ref{sec:meta.analysis}.
+It extends the previously seen linear regression approach with $x = 1/s$ and $y = \theta/s$ by introducing weights.
+The effect size $\theta_i$ is assumed to be distributed as
+
+\begin{align}
+\theta_i \sim N(\beta_0 + \beta_1 s_i, s_i^2 + \tau^2) \label{t.sharp.regression}
+\end{align}
+
+$\tau^2$ is estimated as in equation \ref{eq:Tau.definition} (method of moments). %or \ref{eq:paule.mandel}. 
+The weights are set as $w_i = 1/\sqrt{s_i^2 + \tau^2})$.
+After adjusting for the weights as described in \ref{weighted.regression}, we can proceed analogous to Egger's test.
+The $p$-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
+
+\subsection{Dichotomous Outcomes Tests}
+
+The issue with dichotomous outcomes is that effect size and variance of effect size are correlated, which can readily be seen in \ref{eq:risk.ratio} and \ref{eq:risk.ratio.variance}.
+For example, a small number of event counts in one or group will inflate the variance and the effect size.
+Consequently, the tests above will tend to reject the null-hypothesis too often, i.e.
+report false positives.
+A number of solutions to this problem are provided in the literature.
+
+\subsubsection{Peters Test: Weighted Linear Regression Test} \label{sec:Peter}
+Instead of taking the standard error $s$ as explanatory variable $x$ as in Egger's Test, the inverse of the total sample size is used.
+Additionally, the variances $s_i^2$ are used as weights.
+Thus, the subsequent test procedure is identical to Egger's test.
+Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
+
+\subsubsection{Harbord's Test: Score based Test} \label{sec:Harbord}
+A rank based alternative to Peters test for binary outcomes is Harbord's test \citep{Harbord}.
+It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated at log odds ratio $\theta_0 = 0$ and its inverse Fisher information $s^2$. Formally,
+
+\begin{align}
+\varphi &= e_t - (e_t - e_c)(e_t + (n_t - e_t))/(n_t + n_c) \label{harbord.score} \\
+s^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \label{harbord.variance}
+\end{align}
+
+It can be shown that they are both good approximations of the log odds ratio and its variance if the real $\theta$ is not too far from zero.
+The standardized estimator $r_i/v_i$ is also known as Pet0 odds ratio.
+The obtained scores and variances can be used in Egger's test as treatment effects and variances.
+
+\subsubsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
+\citet{Schwarzer} developed a test for the correlation between $E_t - \mathbb{E}(E_t)$ and the variance of $E_t$, $E_t$ being a random variable from the non-central hypergeometric distribution, assuming a fixed log odds ratio.
+\\
+$\mathbb{E}(E_t)$ and variance of $E_t$ are then estimated based on $e_t$. The standardized cell count deviation 
+\begin{align}
+(e_t - \mathbb{E}(E_t))/\sqrt(s_i^2)
+\end{align}
+and the inverse of $s_i^2$ is then used as before in Begg and Mazumdar's test.
+
+\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables} \label{sec:Rucker}
+The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables.
+We use that the arcsine function is the variance stabilizing transformation for a proportion.
+Let
+
+\begin{align}
+\theta_i = \arcsin{e_t/n_t} - \arcsin{e_c/n_c} \nonumber &
+s_i^2 = 1/4n_t + +/4n_c \nonumber
+\end{align}
+
+Then one can optionally apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained estimates.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small study effect and Publication Bias Adjustment}
+There are different approaches to correct for small study effects and publication bias.
+They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinite precision (i.e.
+very small standard error) or to a summary effect, corrected for publication bias.
+Selection models aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:
+
+\subsection{Adjustment by Regression}
+\citet{limitmeta} use a random effects model %together with shrinkage procedure 
+to obtain an unbiased estimate. Similarly to 
+%what has been seen in Copas selection model, we let $y_i$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_i}$ as in \ref{limitmeta.regression}.
+regression based tests for small study effects, we have
+
+\begin{align}
+\theta_i & = \beta_0 + \beta_1\sqrt{s_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \epsilon_i \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{eq:limitmeta.regression}
+\end{align}
+
+The only difference between Thompson and Sharp's variant is $x = \sqrt{s^2 + \tau^2}$ instead of $x = \sqrt{s^2}$.
+$\beta_{1}$ represents the bias introduced by small study effects, as illustrated in the following equations:
+
+\begin{align}
+\mathbb{E}((\theta_i - \beta_0)/\sqrt{s_i^2}) \rightarrow \beta_1 \textrm{ if } s_i \rightarrow \infty \nonumber \\ %\label{limitmeta.infinitesample} \\
+\mathbb{E}(theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} s_i \rightarrow 0 \nonumber
+\end{align}
+
+After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before in the simple linear regression framework. Now we have basically two possible estimates at hand:
+\begin{itemize}
+\item $\beta_0$ the treatment effect without any influence of study precision with standard error $s_{\beta_0}$
+\item $\beta_0 + \beta_1 \tau$ the treatment effect of a hypothetical study with infinite precision, corresponding standard error $s_{\beta_0} + s_{\beta_1}$
+\end{itemize}
+
+Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior with respect to coverage (and mean squared error).
+
+\subsection{Copas Selection Model}
+
+A method proposed in \cite{Copas1,Copas2,Copas3} 
+assumes that the given sample of treatment effects and standard errors is a selected part of a larger random sample.
+Selection of studies depends on their effect size and variance.
+Smaller variance is always accompanied by larger selection probability.
+\\
+Let $\theta_i$ be the effect size estimate of study $i$. Then
+
+\begin{align}
+\theta_i \sim N(\mu_i, \sigma_i^2) &
+\mu_i \sim N(\theta, \tau^2) \label{eq:population.model}
+\end{align}
+
+which is similar to the random-effects meta-analysis setting.
+$\theta$ is the population mean effect, $\sigma_i^2$ the within study variance and $\tau^2$ the between study variance.
+Equations in \ref{eq:population.model} are termed the \textit{population model}.
+\\
+The \textit{selection model} is defined as follows.
+Suppose a selection of studies with reported ($\neq$ estimated) standard errors $s$ (likely different from $\sigma$).
+Only a proportion of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
+Formally,
+
+\begin{align}
+P(\textrm{select}|s) &= \Phi(a + b/s) \nonumber %\label{copas.selection1}
+\end{align}
+
+The equation can be rewritten as
+
+\begin{align}
+z = a + b/s + \delta \nonumber %\label{copas.selection2}
+\end{align}
+
+with $\delta \sim N(0,1)$.
+$z$ is interpreted as the \textit{propensity for selection}.
+It's sign must be positive in order for the study to be selected.
+Thus, the larger $z$, the more likely the study will be selected.
+Also, $a$ is somewhat like to global retention or selection rate for each study, while $b$ decides about the decline of selection probability with increasing $s$.\\
+So far, we have, for a study $i$
+
+\begin{align}
+\theta_i = \mu_i + \sigma_i\epsilon_i \nonumber \\ 
+\mu_i \sim N(\theta, \tau^2) \nonumber \\
+z_i = a + b/s_i + \delta_i \nonumber
+\end{align}
+
+where $(\epsilon_i, \delta_i)$ are standard normal residuals.
+The two models are coupled by introducing a correlation $\rho = cor(\theta_i, z_i)$ by defining $(\epsilon_i, \delta_i)$ as bivariate standard normals.
+It follows that,
+%Every given study $i$ in the meta-analysis has $z_i > 0$. 
+if $\rho_i$ is large and positive and $z_i > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_i$ and $\delta_i$ and thus, the true mean $\mu$ is likely to be overestimated.
+\\
+Let $u_i = a + b/s_i$, $\lambda(u_i)$ the Mill's ratio $\phi(u_i)/\Phi(u_i)$ ($\phi$ is the standard normal density function and $\Phi$ the cdf) and $\tilde{\rho_i} = \sigma/\sqrt(\tau^2 + \sigma_i^2) \rho_i$.
+The probability of a study being selected, given $s_i$ and $\theta_i$, is
+
+\begin{align}
+P(\textrm{select}|s_i, \theta_i) = %P(a,b,s,y) = 
+\Phi(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i^2}}}) \nonumber
+\end{align}
+
+Which again shows that larger $s_i$ and $\theta_i$ lead to a larger selection probability. It can also be shown that the expected value
+
+\begin{align}
+\mathbb{E}(\theta_i|s_i, \textrm{select}) = \mu + \rho_i\sigma_i\lambda(u_i) \label{eq:copas.expectation}
+\end{align}
+
+which shows that the expected value for a study is larger for larger $\sigma$. \\
+A likelihood for $\theta_i$, conditional on $z>0$ can be formulated to estimate the parameters of the model.
+Regarding $a$ and $b$, there is no way that they can be estimated because the number of missing studies and their effect sizes is not known.
+Instead, fixed values for $a$ and $b$ have to be chosen.
+The nuisance parameter $\sigma_i$ can be replaced by an estimate if the sample size in the studies is large enough. Since
+
+\begin{align}
+\textrm{Var}(\theta_i| s_i, z_i > 0) = \sigma_i^2 (1 - c_i^2\rho_i^2) \nonumber
+\end{align}
+
+with $c^2 = \lambda(u_i)(u_i + \lambda(u_i))$, we can replace $\sigma_i^2$ by $\hat{\sigma}_i^2 = \frac{1}{1-c_i^2\rho_i^2}$.
+Although one has to evaluate the likelihood for fixed pairs $(a,b)$, one can compare the fit of the model to evaluate which one is more suitable:
+With equation \ref{eq:copas.expectation}, one can obtain fitted values of $\theta_i$ based on $s_i$. Also, for two different pairs $(a,b)$, $(a^\star, b^\star)$,
+
+\begin{align}
+\mathbb{E}(\theta_i|z_i > 0, a^\star, b^\star) - \mathbb{E}(\theta_i|z_i > 0, a, b) \approx c^\star + \rho(\lambda(a^\star) - \lambda(a))s_i \nonumber
+\end{align}
+
+and that local departures of $\theta_i$ can be approximated by adding a linear term in $s_i$ to the expectation of $\theta_i$. Thus, to test a pair $(a,b)$, it is sufficient to test $\beta \neq 0$ in
+
+\begin{align}
+\theta_i &= \theta + \beta s_i + \sigma_i \epsilon_i \nonumber
+\end{align}
+
+with restriction that $\rho \geq 0$.
+To test some pair $(a,b)$ against the scenario with no selection, we set $a^\star = \infty$ (or $\rho = 0$).
+A likelihood ratio test will give a test statistic to test against $H0 =$ no selection:
+
+\begin{align}
+\chi^2 &= 2*(\operatorname*{max1}_{\theta, \tau, \beta}\tilde{L}(\theta, \tau, \beta) - \operatorname*{max}_{\theta, \tau}\tilde{L}(\theta, \tau, 0)) \label{eq:copas.small.study}
+\end{align}
+
+with 
+\begin{align}
+\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta s_i)^2}{(\tau^2 + \sigma_i^2)}] \nonumber
+\end{align}
+
+$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$-value.
+Note that the test is almost equivalent to Egger's small study effect test with $\tau^2 = 0$.
+Thus, although the copas selection model models publication bias, it is dependent on the small study effects to find the most suitable pair $(a,b)$.
+\\
+If one applies the model to a single meta-analysis, a sensitivity analysis is suggested.
+One can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process.
+Selection models are in general not recommended for inference (e.g.
+\citet{selection.assessment}).
+\citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes. \\
+A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \ref{eq:copas.small.study} is applied.
+If all obtained $p$-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for modelling, and the standard, classical random effects meta-analysis is retained.
+If none of the $p$-values is above the threshold, a wider range of values for $(a,b)$ is used.
+When some $p$-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the least intense underlying selection model is chosen).\\
+Currently, there is no test to detect miss-specifications in the model itself, the authors themselves have argued that a non-parametric test of the residuals would lack power.
+
+\section{Transformation between effect sizes} \label{sec:transformation.effectsizes}
+Assuming that binary outcomes result from a dichotomization of originally continuous random variables, in this case, the logistic distribution, a transformation from typical binary effect measures to Cohen's $d$ can be achieved \cite[47]{Intro.meta}.
+\\
+Let $\theta$ be a log odds ratio and $s$ its standard error. Cohen's $d$ and it's variance $s_d^2$ is obtained by
+
+\begin{align}
+d &= \theta \frac{\sqrt{3}}{\pi} & s_d^2 = s^2 \frac{\sqrt{3}}{\pi} \nonumber
+\end{align}
+
+$\frac{\pi}{\sqrt{3}} = 1.81$ is the standard deviation of the logistic distribution $L(\mu, \eta)$ with scale parameter $\eta = 1$, so we just divide the log odds ratio and it's variance through the standard deviation.
+The approximation works only well if $e_t$ and $e_c$ are not very small, especially in the case of $s_d^2$.
+Plugging in the observed log odds ratio $\hat{\theta}$ and $\hat{s}^2$ will give an estimate of Cohen's $d$.\\
+Pearson's correlation can be attained by the formulas (\citet{olkin1985dtor}, \cite[48]{Intro.meta})
+
+\begin{align}
+r &= \frac{d}{\sqrt{d^2 + a}} & a = (n_c + n_t)^2 / n_c n_t \nonumber
+\end{align}
+where $a$ is a correction factor if $n_t \neq n_c$. The variance of $r$, $s_r^2$ is computed by
+\begin{align}
+s_r^2 &= \frac{a^2 s_d^2}{(d^2 + a)^3} \nonumber
+\end{align}
+
+Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $s_z^2$ by using
+\begin{align}
+z &= 0.5 \ln(\frac{1 + r}{1 - r}) & \nonumber
+s_z^2 &= \frac{1}{n-3}
+\end{align}
+
+%SIMPLE LINEAR REGRESSION
+% \begin{align}
+% \hat{\mathbf{\beta}} &= (\mathbf{X}^\top  \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
+% \end{align}
+
+% There is a closed form solution for $\hat{\beta_0}, \hat{\beta}_1$ that minimize the sum of squares:
+% 
+% \begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} & 
+% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
+% \end{align}
+% 
+% $\bar{x}, \bar{y}$ denotes the sample mean of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$.
+$\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the fitted line.
+Let $\hat{y}_i = \beta_0 + \beta_1 x_i$ and $e_i = y_i - \hat{y}_i$.
+The variances $s^2_\beta$
+% 
+% 
+% 
+% To test whether the intercept or the slope is close to a certain value, a $t$-test can be used. Simply taking the absolute value of $\beta_0/s_\beta_0$,
+% \begin{align}
+% p &= 2(1-F(|\beta_0/s_\beta_0|)) \nonumber
+% \end{align}
+% 
+% where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom.
+The $p$-value will give the evidence against the null-hypothesis $\beta_0 = 0$.
+The procedure for $\beta_1$ is equivalent.
+\\
+% To extend the model to weighted simple linear regression is straightforward.
+Let $w_i$ be the corresponding weight that will be attributed to the pair $x_i, y_i$.
+The least squares minimization problem can be restated
+% 
+% \begin{align}
+% \operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
+% \end{align}
+% 
+% And the corresponding estimators are thus
+% 
+% \begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n w_i(x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n w_i(x_i - \bar{x})^2} & 
+% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
+% \end{align}
+%
+
+% LIMITMETa
+% \vspace{0mm}
+% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
+% 
+% \begin{align}
+% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
+% \end{align}
+% 
+% Letting $M \rightarrow \infty$, we obtain:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
+% \end{align}
+% 
+% Note that:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
+% \end{align}
+% 
+% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
+% 
+% \begin{align}
+% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
+% \end{align}
+% 
+% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
+% \end{align}
+% 
+% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
+
+% \section{Basic notation}
+% The notation used here will be used throughout the chapter and exceptions will be noted.
 Let $i$ be the number of a study of a meta analysis with $n$ being the total number of studies.
@@
 $w_{i}$ is used for weights which are defined when necessary, and $\Delta$ usually denotes the summarized or pooled effect estimate of the meta-analysis, and $\eta$ the variance thereof.
-
-\vspace{0mm}
-In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
-
-\section{Heterogeneity}
-In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
+% 
+% \vspace{0mm}
+% In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
+% 
+% 
+% \section{Transformation between effect sizes}
+% Binary and continuous outcome measures can both be transformed into correlations and fishers z-scaled correlations in order to be compared.
+Let $\theta$ be a log odds ratio.
+A standardized mean difference $d$ (also known as Cohen's $d$) is calculated by multiplying $\theta$ with $\sqrt{3}/\pi$.
+The variance of the standardized mean difference is attained as $v_d = v_\theta \sqrt{3}/\pi$.\\
+% We get from a standardized mean difference $d$ to a correlation $r$ by using 
+% \begin{align}
+% r &= \frac{d}{\sqrt{d^2 + a}} \nonumber
+% \end{align}
+% where $a$ is a correction factor if $n_t \neq n_c, a = (n_c + n_t)^2 / n_c n_t$. The variance of $r$ is computed by using 
+% \begin{align}
+% v_r &= v_d
+% \end{align}
+% 
+% Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $v_z$ by using
+% \begin{align}
+% z &= 0.5 \ln(\frac{1 + r}{1 - r}) \nonumber
+% v_z &= \frac{1}{n-3}
+% \end{align}
+% 
+% 
+% 
+% \section{Heterogeneity}
+% In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
 This is called between study variation in contrast to within study variation (noise).
-
-\vspace{0mm}
-The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
+% 
+% 
+% \vspace{0mm}
+% The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
 Let $w_i$ be the inverse of the variance and $\Delta$ be a summarized effect estimate of your choice as for example a variance-weighted mean \ref{weighted.mean}.
 Then $Q$ can be calculated as in \ref{Q.heterogeneity}
-
-\begin{align}
-\Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
-\end{align}
-
-Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
+% 
+% \begin{align}
+% \Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
+% Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
+% \end{align}
+% 
+% Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
 Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
 $1 - F(Q)$ will provide the $p$-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
-
-\vspace{0mm}
-Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
+% 
+% \vspace{0mm}
+% Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
 For this purpose, $\tau^2$, the variance of true effects, can be calculated.
@@
 In practice, $\tau^2$ can be smaller than zero, then it is set to zero.
-
-\begin{align}
-C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
-\tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
-\end{align}
-
-The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
+% 
+% \begin{align}
+% C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
+% \tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
+% \end{align}
+% 
+% The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
 Note that their estimate can differ substantially and consequently also the estimate of the pooled effect size estimate.
-
-\vspace{0mm}
-To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
-
-\begin{align}
-I^2 &= (Q - n + 1)/Q \label{I2.proportion}
-\end{align}
-
-There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
-
-\section{Meta Analysis}
-There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
-First the fixed effect meta-analysis will be explained.
+% 
+% \vspace{0mm}
+% To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
+% 
+% \begin{align}
+% I^2 &= (Q - n + 1)/Q \label{I2.proportion}
+% \end{align}
+% 
+% There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
+% 
+% \section{Meta Analysis}
+% There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
+% First the fixed effect meta-analysis will be explained.
 Note that both methods can be used for continuous or dichotomous outcomes.
 For more details about the methods, see chapter 11 and 12 in \citet{metaanalysis}
-
-\vspace{0mm}
-Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
+% 
+% 
+% \vspace{0mm}
+% Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
 The pooled estimate $\Delta_{f}$ of the fixed effects model is then the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
 The variance $\eta_{f}$ is the reciprocal of the sum of the weights as shown in \ref{reciproce.variance}.
-
-\begin{align}
-\Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-\eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
-\end{align}
-
-The computation of random effects meta-analysis is more complicated.
+% 
+% \begin{align}
+% \Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
+% \eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
+% \end{align}
+% 
+% The computation of random effects meta-analysis is more complicated.
 Random effects meta-analysis will give smaller studies with larger variance more weight in the pooled estimate.
 Shortly, the idea is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
-
-\vspace{0mm}
-The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
+% 
+% \vspace{0mm}
+% The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
 It is used to calculate a new weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
 The variance of $\Delta_{r}$, $\eta_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
-
-\begin{align}
-v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
-\Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
-\eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
-\end{align}
-
-A p-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
-
-\begin{align}
-Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
-p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
-\end{align}
-
-\section{Small Study Effects Tests}
-One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
+% 
+% \begin{align}
+% v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
+% \Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
+% \eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
+% \end{align}
+% 
+% A $p$-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
+% 
+% \begin{align}
+% Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
+% p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
+% \end{align}
+% 
+% \section{Small Study Effects Tests}
+% One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
 If this is not given, one often speaks of publication bias.
@@
 Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
-
-\begin{align}
-Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
-\end{align}
-
-The changes in the case of ties are negligible \cite[410]{begg.ties}.
-
-\subsubsection{Egger's Test: Linear Regression Test}
-Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
-Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope.
-
-\vspace{0mm}
-If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
-The p-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
-
-\begin{align}
-p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
-\end{align}
-
-\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test}
-A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
+% 
+% \begin{align}
+% Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
+% \end{align}
+% 
+% The changes in the case of ties are negligible \cite[410]{begg.ties}.
+% 
+% \subsubsection{Egger's Test: Linear Regression Test}
+% Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
+% Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope. 
+% 
+% \vspace{0mm}
+% If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
+The $p$-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
+% 
+% \begin{align}
+% p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
+% \end{align}
+% 
+% \subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{Thompson}
+% A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
 Let $\tau^2$ be equal to \ref{Tau.definition}.
 The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
-
-\begin{align}
-y_{i} \sim N(\beta_{0} + \beta{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
-\end{align}
-
-Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
-Analogous to Edger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta{0} = 0$.
-
-\subsection{Dichotomous Outcomes Tests}
-
-The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
+% 
+% \begin{align}
+% y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
+% \end{align}
+% 
+% Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
+Analogous to Egger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta_{0} = 0$.
+% 
+% \subsection{Dichotomous Outcomes Tests}
+% 
+% The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
 Consequently, the tests above will tend to reject the null-hypothesis too often, i.e.
@@
 A number of solutions to this problem are existing in the literature.
-
-\subsubsection{Peters Test: Weighted Linear Regression Test}
-A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
-
-\vspace{0mm}
-Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
-
-\begin{align}
-y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
-v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
-\end{align}
-
-and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
+% 
+% 
+% \subsubsection{Peters Test: Weighted Linear Regression Test}
+% A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
+% 
+% \vspace{0mm}
+% Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
+% 
+% \begin{align}
+% y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
+% v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
+% \end{align}
+% 
+% and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
 Instead of taking the variance as explanatory or independent variable in regression as in Egger's Test, the inverse of the total sample size $x_{i}$ is used, and the variance $v_{i}$ is used as a weight.
 The subsequent test procedure is then identical to Egger's test.
-
-\vspace{0mm}
-Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
-
-\subsubsection{Harbord's Test: Score based Test}
-A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
+% 
+% \vspace{0mm}
+% Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
+% 
+% 
+% \subsubsection{Harbord's Test: Score based Test}
+% A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
 The score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
-
-\begin{align}
-r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
-v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
-\end{align}
-
-Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
+% 
+% \begin{align}
+% r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
+% v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
+% \end{align}
+% 
+% Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
 Note that $r_{i}/v_{i}$ is also known as peto odds ratio.
-
-\subsubsection{Schwarzer's Test: Rank Correlation Test}
-\citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
+% 
+% \subsubsection{Schwarzer's Test: Rank Correlation Test}
+% \citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
 $\mathbb{E}(E_{t})$ and variance of $E_{t}$ are then estimated based on $e_{t}$.
-
-\vspace{0mm}
-The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
-
-\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
-The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let
-
-\begin{align}
-y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}}// 
-v_{i} = 1/4n_{t} + +/4n_{c}
-\end{align}
-
-Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances.
-
-\section{Small Study Effect Adjustment}
-\subsection{Trim and Fill}
-One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
+% 
+% \vspace{0mm}
+% The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
+% 
+% \subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
+% The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let 
+% 
+% \begin{align}
+% y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}} \\
+% v_{i} = 1/4n_{t} + +/4n_{c}
+% \end{align}
+% 
+% Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances. 
+% 
+% 
+% \section{Small Study Effect Adjustment}
+% \subsection{Trim and Fill}
+% One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
 It is a nonparametric test based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
-%If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
-
-\vspace{0mm}
-The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
+% %If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
+% 
+% \vspace{0mm}
+% The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
 First, $\Delta$ is estimated using a fixed or random effects model.
@@
 To test the fit of the model (while keeping all other parts unchanged), the model can be extended in the following way :
-
-\begin{align}
-y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
-\end{align}
-
-If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
+% 
+% \begin{align}
+% y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
+% \end{align}
+% 
+% If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
 Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
-The p-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
-
-\vspace{0mm}
-To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
-
-\vspace{0mm}
-In practice, only a range of values for $a,b$ are reasonable.
+The $p$-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
+% 
+% \vspace{0mm}
+% To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
+% 
+% \vspace{0mm}
+% In practice, only a range of values for $a,b$ are reasonable.
 For those values, the quantities above can be calculated and illustrated.
-Values for $\mu$ that have p-values over a predefined significance threshold can be used for inference of the effect size.
-
-\subsection{Adjustment by Regression}
-There are multiple ways to adjust for small study effects by regression. The general idea is to regress the effect size of a study with a variance of zero based on the given effects and variances.
-
-\citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
+Values for $\mu$ that have $p$-values over a predefined significance threshold can be used for inference of the effect size.
+% 
+% \subsection{Adjustment by Regression}
+% There are multiple ways to adjust for small study effects by regression.
+The general idea is to extrapolate the effect size of a study with a variance of zero based on the given effects and variances.
+% 
+% \citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
 Similarly to what has been seen in Copas selection model, we let $y_{i}$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_{i}}$ as in \ref{limitmeta.regression}.
-
-\begin{align}
-y_{i}& = \beta_{0} + \beta{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{s_{i} + \tau^2}), \stackrel{\textrm{iid}}{\sim} N(0,1)  \ref{limitmeta.regression}
-\end{align}
-
-$\beta{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
-
-\begin{align}
-\mathbb{E}((y_{i} - \beta_{})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{if} \sqrt{v_{i}} \rightarrow \infty \\
-\mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
-\end{align}
-
-After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test.
-
-\vspace{0mm}
-To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
-
-\begin{align}
-y_{i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{s_{i}/M + \tau^2}) \label{limitmeta.regression}
-\end{align}
-
-Letting $M \rightarrow \infty$, we obtain:
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
-\end{align}
-
-Note that:
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
-\end{align}
-
-$\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
-
-\begin{align}
-\epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
-\end{align}
-
-Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get
-
-\begin{align}
-y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-\end{align}
-
-By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
+% 
+% \begin{align}
+% y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{v_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
+% \end{align}
+% 
+% $\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
+% 
+% \begin{align}
+% \mathbb{E}((y_{i} - \beta_{0})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{ if } \sqrt{v_{i}} \rightarrow \infty \label{limitmeta.infinitesample} \\
+% \mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
+% \end{align}
+% 
+% After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test (see \ref{Thompson}).
+% 
+% \vspace{0mm}
+% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
+% 
+% \begin{align}
+% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
+% \end{align}
+% 
+% Letting $M \rightarrow \infty$, we obtain:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
+% \end{align}
+% 
+% Note that:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
+% \end{align}
+% 
+% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
+% 
+% \begin{align}
+% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
+% \end{align}
+% 
+% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
+% \end{align}
+% 
+% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
 
@@
 
-% LaTeX file for Chapter 05
-
-\chapter{Conclusions}
+%<<'child-chapter05', child='chapter05.Rnw'>>=
+%@
 

### 2019-06-17 report/chapter01.Rnw
Results section update

--- 2019-03-28 report/chapter01.Rnw
@@
 
-Meta-analysis is at the core of evidence based medicine because it allows to summarise evidence over multiple studies and provide a more broad view on success and effectivity of clinical treatments.
+Typically, we expect empirical scientific results to be distorted by random noise, such that the results are not equal to the real process that they describe.
+Additionally, one can reasonably assume that the results are also biased to some extent, as the statistical paradigm of precision versus bias would predict: The smaller the noise part of distortion, the more the result should be distorted by bias.
+However, the trade-off is not inevitable and can be minimized by scientific rigor and foresightfull experimental design.
+Large efforts have been made both in theory and practice to improve the quality of experiments and their analysis, such as defining experimental settings that prohibit influence of expectations of the researcher (e.g.
+blinding) or increase sample size in experiments.
+The introduction of randomized clinical trials is for example seen nowadays as a benchmark in clinical science, heavily improving the reliability of its findings.
+\\
+It is more and more considered a new scientific field by itself to think of and argue about circumstances that improve the quality of scientific findings.
+Statistics is in some sense predestined to contribute to it, because probability and chance concepts are key to understanding of any empirical science.
+\\
+There are also issues, in which statistics is not thought to be able to contribute much to understanding and to be of little help for solving them.
+For example, the selective attention that the agents in science are paying to new, strong and clear findings in each science is considered merely a psychological and social%, socioeconomic
+issue.
+It is often explained by the affinity of humans for stories rather than mere facts and for novelties.
+The issue that scientific findings get more attention and are more likely to be published, read and cited is known for many years, but has gained new traction in meta science when the so-called reproducibility crisis emerged in (2003 to 2005).
+Studies such as ...
+showed that even rigid prosecution of study protocols did often not lead to reproduction of previous results when experiments were repeated, which struck empirical science in its core.
+Most reasonably, some concluded that it was a large misunderstanding of statistical tools such as the p-value in the scientific community that lead to this situation (...).
+Although that some measures have been taken since then, and some progress is made, the non-reproducibility of scientific findings remain an acute threat to the relevance and reliability of science.
+Some even argue that certain scientific fields sooner or later will repeat the experience that for example psychology or medicine have made, and are yet to encounter their own reproducibility crisis (...).
+\\
+Clearly, reproduction of experimental results is the gold standard of testing empirical science, because it reassures the universality and reliability by which certain procedures or effects appear if measured in the correct experimental context.
+However, there are also problems there.
+One can almost never fully exclude chance events to have played a major role in negating or reaffirming the experimental findings (which is of course always the case where noise is present in the data).
+Furthermore, reproduction studies are generally costly and the precise experimental conditions might be hard to reproduce because of lack of information or other reasons.
+\\
+There is another way to assess the strength of scientific results if the experiment has been conducted more than once (however not with exactly identical protocol as in reproduction studies): Meta-analyses.
+In a meta-analyses, results of multiple (fairly identical) experiments (studies) are summarized to a single result.
+Very often, meta-analyses are not only regarded to be a synthesis of results, but of evidence, thus reflecting the overall and summarized evidence regarding to a scientific question.
+It is on purpose that selective attention to positive, strong results in the scientific literature have been mentioned beforehand, because it is clear how they will affect this second way of reassurance of scientific findings: The meta-analysis will again lead to irreproducible findings if it is based on a set of results that is itself biased.
+Thus, meta-analysis will in this case not reach its purpose of assessing reliability of science, but worsen the problem by reinforcing the confidence in the overestimated over-optimistic effects.
+However, and this is the main topic in this masters thesis, there are some ways to detect irregularities in the body of results that can provide indirect hints that a selective rather than a random sample from a hypothetical population of experiments is present.
+The abundance of the methods to link some features of the sample of experiments to publication bias, as the tendency of scientific literature to over-proportionally include large effects is generally called, also speaks for the relevance of the topic.
+A review in 2017 (...) for example identified 147 (!) conceptually differing methods.\\
+This speaks as well for the inevitable difficulties that such methods encounter.
+First of all, it is most often impossible to estimate the real selection process, that is the rate by which smaller effects go unnoticed because of selective publication and reporting, because the number of missing results in the studies is not known at the first place and impossible to retrieve.
+Secondly, there is almost no real world data of complete and unbiased meta-analyses, such that evaluations of methods is dependent on simulations.
+So we have, after applying the methods, only indirect information of publication bias, and the extent to what it might influences scientific findings.
+Almost all the time, alternative explanations for the results of the methods might relieve the operators and publishers from the reproval of publication bias.
+However, given the large body of evidence for publication bias collected in other ways, those can probably be expelled most of the time, such that those methods indeed give a quantitative measure of publication bias.
+\\
+In this masters thesis, the answers for two questions are investigated: What is the extent and effect of publication bias in clinical science?
+For this purpose, a dataset from the Cochrane Organization is analysed with commonly used techniques to detect and adjust for publication bias (more precisely, small study effects, as it will be seen later).
+The discussion of the results of the analysis will result in the light of the literature to publication bias.
+%Because the extent of the analysis that is operated here is, to my knowledge, unmatched so far, this dataset
+
+%Before beginning with the main part of this masters thesis, I want to recall some of the most pointed evidence for publication bias that has been collected for publication bias so far. \\
+
+% Meta-analysis is at the core of evidence based medicine because it allows to summarise evidence over multiple studies and provide a more broad view on success and effectivity of clinical treatments.
 The necessity of meta-analyses is also increased by the abundance of data and publications.
-Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to keep decisions based on quantitative and scientific criteria.
-
-\vspace{0mm}
-For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention.
-However, since the amount of empirical research is expanding, meta-analysis can be part in any field where repeated experiments are performed.
-The usefulness of meta-analysis expands therefore well over clinical science.
-
-\vspace{0mm}
-Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question.
-Systematic reviews may also incorporate results that can not be included in a meta-analysis, such as adverse effects reported in one trial, but a meta-analysis is the central part of a systematic review if results from multiple studies are available.
-The authors usually take their conclusions largely based on the results of the meta-analysis.
-
-% In science, there is not only a need for accumulation of knowledge, but also for concentration.
-For the same reason as statistical analysis is performed on single experiments, it can also be used for results of multiple experiments or studies: to simplify and summarize the data at hand to a degree that is understandable.
-The latter procedure goes usually under the name of meta-analysis.
-Meta analyses are used to summarize results and evidence over multiple studies when they are considered to be similar enough.
+Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to make decisions based on quantitative and scientific criteria.
 % 
 % \vspace{0mm}
-% In the face of the large amount of research that is done in some fields of empirical science, meta-analysis becomes increasingly important, for looking at all evidence would simply take very long for one person.
-Meta-analyses are often part of a systematic review, an effort of experts of a field to provide an overlook over the evidence.
-In the course of a review, all literature and data with respect to a scientific question is collected and a meta-analysis is operated at the end to summarize the findings.
+% For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention.
+However, the usefulness of meta-analysis does not restrict to clinical science, but to any empirical and quantiative science.
 % 
 % \vspace{0mm}
-% In the case of clinical science, systematic reviews and meta-analyses do not only benefit scientists but also patients and clinicians, for both are provided with up-to-date summaries of current evidence with respect to a certain treatment.
-Therefore, meta-analysis is at the core of what is called evidence-based medicine.
+% Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question.
+Meta-analysis can be applied to all studies that are approximately identical in their experimental setup and the way the outcome of the experiments is measured.
+In systematic reviews where meta-analyses are used, the conclusions are most often strongly based on the results and the interpretation of the meta-analysis.
 % 
-
-\vspace{0mm}
-However, there are problems that potentially limit the validity of meta-analysis; studies at hand can be biased or heterogeneity between study results can be large and the number of studies small.
-The importance and the issues of meta-analysis are the reasons why they have been chosen as one general topic of the masters thesis.
-One particular problem will furthermore be investigated in more detail: reporting bias and meta-analysis.
-Not only will the methods to deal with issues as reporting bias be discussed, but also will they be applied on a dataset of systematic reviews that can be used for meta-analysis.
-So at the end of the report, the reader will not only have an impression of the technical issues caused by reporting bias, but also of the abundance and extent of it in the dataset.
-Since the dataset is very large and of good quality, results might also be representative to some extent for reporting bias in clinical science.
-
-\subsection{Cochrane and the Cochrane Database of Systematic Reviews}
-The Cochrane Organization has specialized on systematic reviews in clinical science.
+% \vspace{0mm}
+% However, there are problems that potentially limit the validity of meta-analysis; the number of studies available can be incomplete or the results of the studies can be biased.
+Some of those problems can be solved or asserted by special statistical methods.
+% 
+% \subsection{Small Study Effects or Publication Bias}
+% When study sample size decreases, the probability of extreme and missleading results in a study increases.
+This becomes a problem if results are selectively published, and therefore available, based on their results.
+When this is the case, one speaks of a small study effect or of ``Publication bias''.
+% 
+% \vspace{0mm}
+% The issue has been discussed extensively in the last years, most often in the context of what has came to be known as the replication crisis.
+The reasons for small study effects are manifold, but originate most often in the myopical acting of agents in science and the lack of statistical education.
+Studies are reported by scientists, published by journals and noticed by readers more often if their findigs are positive and find e.g.
+a substantive difference or effect.
+When doing a meta-analysis, one again obtains biased results.
+% 
+% \vspace{0mm}
+% The reason why that is less of an issue for larger studies is that extreme results are in general less likely and that due to larger effort, a result is published although there has been no clear and positive findings.
+% 
+% \vspace{0mm}
+% While there is generally no way to assert poor study quality, small study effect can in principle be asserted and corrected for statistically.
+This masters thesis will mainly be about statistical methods to detect and adjust for small study effects.
+It can furthermore be divided in two parts:
+% \begin{itemize}
+% \item Methodological part: Collection and discussion of statistical tests and correction methods for small study effects.
+% \item Applied part: Application of the methods to studies of the Cochrane Library of systematic Reviews. Subsequent discussion of the implications
+% of the results for clinical science.
+% \end{itemize}
+% 
+% In contrast to simulation studies, it is not possible to assess critical properties of the methods such as the power of a test, since the truth is not known.
+But based on the amount of data, one can of course try to make extrapolation to tendencies in clinical science in general.
+Moreover, it is still interesting to see how the methods behave in general, especially with respect to each other.
+It may, as an example, be possible to answer the question which statistical test is most conservative and which pooling method is most optimistic on average.
+Comparison with results from simulations may allow to speculate about the reasons when simulation and real world results diverge.
+% 
+% 
+% \subsection{Cochrane and the Cochrane Database of Systematic Reviews}
+% The Cochrane Organization has specialized on systematic reviews in clinical science.
 It publishes and maintains a library with a large number of systematic reviews that are available in some countries to the public.
-
-\vspace{0mm}
-The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite).
-
-\vspace{0mm}
-The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests.
+% 
+% \vspace{0mm}
+% The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite). 
+% 
+% \vspace{0mm}
+% The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests.
 This might further improve the validity and precision of findings and conclusions that have been made based on this data.
+%

### 2019-06-17 report/chapter02.Rnw
Results section update

@@
 
-<<echo = FALSE>>=
+<<echo = FALSE, warning=FALSE, message=FALSE>>=
 rm(list = ls())
@@
 
+load(file.path(PATH_RESULTS, "meta_analyses_summary_bin_cont_surv.RData"))
 load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
@@
 #Study.year quantiles:
-data.ext <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
-publication.year.range <- c(quantile(data.ext$study.year, 0.05, na.rm = T), quantile(data.ext$study.year, 0.25, na.rm = T), 
-                            quantile(data.ext$study.year, 0.5, na.rm = T), quantile(data.ext$study.year, 0.75, na.rm = T),
-                            round(mean(data.ext$study.year, na.rm = T), 2))
+#data.ext2 <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
+publication.year.range <- c(quantile(data.ext2$study.year, 0.05, na.rm = T), quantile(data.ext2$study.year, 0.25, na.rm = T), 
+                            quantile(data.ext2$study.year, 0.5, na.rm = T), quantile(data.ext2$study.year, 0.75, na.rm = T),
+                            round(mean(data.ext2$study.year, na.rm = T), 2))
 
@@
 #Total and group size quantiles:
-data.ext <- data.ext %>% ungroup() %>%  mutate(total.n = total1 + total2)
-samplesize.range <- c(quantile(data.ext$total.n, 0.05, na.rm = T), quantile(data.ext$total.n, 0.25, na.rm = T), 
-                            quantile(data.ext$total.n, 0.5, na.rm = T), quantile(data.ext$total.n, 0.75, na.rm = T),
-                            round(mean(data.ext$total.n, na.rm = T), 2))
-treatment.group.size.range <- c(quantile(data.ext$total1, 0.05, na.rm = T), quantile(data.ext$total1, 0.25, na.rm = T), 
-                      quantile(data.ext$total1, 0.5, na.rm = T), quantile(data.ext$total1, 0.75, na.rm = T),
-                      round(mean(data.ext$total1, na.rm = T), 2))
+data.ext2 <- data.ext2 %>% ungroup() %>%  mutate(total.n = total1 + total2)
+samplesize.range <- c(quantile(data.ext2$total.n, 0.05, na.rm = T), quantile(data.ext2$total.n, 0.25, na.rm = T), 
+                            quantile(data.ext2$total.n, 0.5, na.rm = T), quantile(data.ext2$total.n, 0.75, na.rm = T),
+                            round(mean(data.ext2$total.n, na.rm = T), 2))
+treatment.group.size.range <- c(quantile(data.ext2$total1, 0.05, na.rm = T), quantile(data.ext2$total1, 0.25, na.rm = T), 
+                      quantile(data.ext2$total1, 0.5, na.rm = T), quantile(data.ext2$total1, 0.75, na.rm = T),
+                      round(mean(data.ext2$total1, na.rm = T), 2))
 
@@
 colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
+
+	data <- data %>% mutate(
+		outcome.type = ifelse(outcome.measure.new == "Hazard Ratio", "surv", 
+													ifelse(outcome.measure.new == "Odds Ratio" | outcome.measure.new == "Risk Ratio" |
+																 	outcome.measure.new == "Peto Odds Ratio" | outcome.measure.new == "Risk Difference", "bin", "cont")),
+		outcome.type = ifelse(outcome.measure.new == "Rate Ratio" | outcome.measure.new == "Rate difference", "rate", outcome.type),
+		lrr = NA,
+		var.lrr = NA,
+		smd = NA,
+		var.smd = NA,
+		smd.pbit = NA,
+		var.smd.pbit = NA,
+		smd.ordl = NA,
+		var.smd.ordl = NA,
+		cor.phi = NA,
+		var.cor.phi = NA,
+		pval.single = NA, 
+		cor.pearson = NA,
+		var.cor.pearson = NA,
+		z = NA,
+		var.z = NA,
+		events1c = NA,
+		events2c = NA,
+		sig.single = NA)
+	cont.ind <- which(data$outcome.type == "cont" & !is.na(data$outcome.type))
+
+	data[cont.ind, "outcome.type"] <- data[cont.ind, ] %>% 
+		mutate(outcome.type = ifelse(outcome.measure.new == "Std. Mean Difference"  | outcome.measure.new == "Mean Difference", 
+																 outcome.type, NA)) %>% select(outcome.type)
+
+	cont.ind <- which(data$outcome.type == "cont" & !is.na(data$outcome.type))
+
+	nomean1.ind <- which(data$outcome.type == "cont" & is.na(data$mean1))
+	nomean2.ind <- which(data$outcome.type == "cont" & is.na(data$mean2))
+	noeffects.ind <- which(data$outcome.type == "cont" & !is.na(data$effect))
+	nomeans.ind <- intersect(nomean1.ind, nomean2.ind)
+	nomeans.ind <- intersect(noeffects.ind, nomeans.ind) #no means, but a (std.) mean difference is provided.
+
+	data[nomeans.ind,"mean1"] <- data[nomeans.ind,"effect"]
+	data[nomeans.ind,"mean2"] <- 0
+
+	data[cont.ind,] <- escalc(data = data[cont.ind,], m1i = mean1, m2i = mean2, 
+														sd1i = sd1, sd2i = sd2, n1i = total1, n2i = total2,
+														measure = "SMD" , append = T, var.names = c("smd", "var.smd"))
+
+	inpute.given.ind <- which(is.na(data[cont.ind, "smd"]) & data[cont.ind, "outcome.measure.new"] == "Std. Mean Difference")
+
+	#Counts of meta-analyses with only zeros:
+all.zero.events.number <- data.ext2 %>% filter(outcome.type == "bin") %>% 
+  group_by(meta.id) %>% 
+    mutate(n = n()) %>% filter(n >= 10) %>% 
+  filter(all(events1 == 0) & all(events2 == 0)) %>% 
+  distinct(meta.id) %>% ungroup() %>%  count()
+
+#Counts of meta-analyses with means and sds only zeros:
+all.zero.means.number <- data.ext2 %>% filter(outcome.type == "cont") %>% group_by(meta.id) %>% 
+    mutate(n = n()) %>% filter(n >= 10) %>% filter(all(mean1 == 0) & all(mean2 == 0)) %>% 
+    filter(all(sd1 == 0) | all(sd2 == 0)) %>% distinct(meta.id) %>% ungroup() %>% count()
+
+#Counts of meta-analyses with n larger ten:
+m.a.largerten.number <- meta %>% filter(k > 9) %>% ungroup %>% count()
+#smaller I2 than 0.5:
+m.a.smaller.5.number <- meta %>% filter(k > 9 & I2 < 0.5) %>% ungroup %>% count()
+#variance ratio > 4:
+m.a.variance4.number <- meta %>% filter(k > 9 & I2 < 0.5) %>% filter((se.max^2)/(se.min^2) > 4) %>% ungroup %>% count()
+#At least on sig. estimate:
+m.a.one.sig.number <- meta %>% filter(k > 9 & I2 < 0.5) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(n.sig.single > 0) %>% ungroup %>% count()
+#Single patient meta-analyses:
+tmp <- data.ext2 %>% filter(outcome.type == "cont") %>% group_by(meta.id) %>% 
+	mutate(n = n()) %>% filter(n >= 10) %>% filter(!all(mean1 == 0) & !all(mean2 == 0)) %>% 
+	filter(!all(sd1 == 0) | !all(sd2 == 0))
+
+meta.id.vector <- unique(tmp$meta.id)
+m.a.singlepatient.number <- length(meta.id.vector[c(which(meta.id.vector > 42716 & meta.id.vector < 42725))] )
+#How many z-score meta-analyses are excluded due to total <= 3, and how many m.a. have then n < 10:
+tmp <- data.ext2 %>% group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 9) %>%
+	filter(outcome.type != "rate" & !is.na(outcome.type))
+
+metac <- meta %>% filter(k > 9) %>% filter(n.sig.single > 0) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+
+meta.id.vector <- metac$meta.id[-which(metac$outcome.type == "surv")]
+meta.id.vector <- meta.id.vector[-c(which(meta.id.vector == 157083),
+																which(meta.id.vector == 159329),
+																# which(meta.id.vector == 12459),
+																# which(meta.id.vector == 12465),
+																# which(meta.id.vector == 22087),
+																which(meta.id.vector == 182298))]
+
+meta.data.zscore <- tmp[which(tmp$meta.id %in% meta.id.vector),]
+total.seq3.number <- meta.data.zscore %>% filter(total1 + total2 < 4) %>% select(var.z) %>% ungroup() %>% count() 
+m.a.seq3.seq10.number <- meta.data.zscore %>% filter(total1 + total2 > 3) %>% count() %>% filter(nn < 10) %>% ungroup %>% count()
+
+meta.id.vector <- metac$meta.id
+meta.data <- data.ext2[which(data.ext2$meta.id %in% meta.id.vector),]
+
 @
@@
 The dataset consists of \Sexpr{length(unique(data$file.nr))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(data$study.name))} studies and \Sexpr{dim(data)[1]} results.
-A result compares clinical or medical interventions or treatments.
+A result compares a clinical or medical intervention or treatments to a control.
 Each study provides (multiple) results of clinical interventions.
-
+\\
 In Table \ref{barbiturate.row}, two results from a systematic review about effects of barbiturates are shown as they are given in the dataset.
-As can be seen, the result is further specified by the variables in the columns.
-The comparison variable specifies what treatments or interventions are compared, the outcome variable how it is compared, and the subgroup variable (not given in table) indicates if the result belongs to a certain subgroup.
-Here, the result is of a binary outcome, so the events in the barbiturate treatment group and the total number of participants are given in columns ``Events'' and ``Total'' and the number of events in the control group ``Events\_c'' and participants ``Total\_c''.
-Events denotes here number of deaths at the end of follow up.
+As can be seen, further specifications are provided by the variables in the columns.
+\\
+The comparison variable specifies \textit{what kind} of treatments or interventions are compared, the outcome variable \textit{how} it is compared, and the subgroup variable (not indicated in table) if the result belongs to a certain subgroup.
+Here, the result is of a binary type, so the counts of events in the barbiturate treatment group and the total number of participants are given in columns ``Events'' and ``Total'' and the number of events in the control group ``Events\_c'' and participants ``Total\_c''.
+A event is here death at the end of follow up.
 
@@
 The structure of a review will now be outlined based on an example of the dataset.
-Lets consider the previously mentioned barbiturate and head injury review.
+Let us consider the previously mentioned barbiturate and head injury review.
 The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates''.
-Since there are arguments for and against use of barbiturates, the authors of the review did a comprehensive literature search and collected all available study findings.
-
-\vspace{0mm}
+\\
+%Since there are arguments for and against use of barbiturates, the authors of the review did a comprehensive literature search and collected all available study findings. 
 The review comprises five studies in total.
-Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental, which would be the comparison to speak in the previously introduced notion.
-The studies have different outcomes, for example, death or death and severe disability at follow up.
+Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental.
+The studies have different outcomes, for example, death or death and severe disability at follow up, but also dropout counts or adverse effects (secondary outcomes).
+We have continuous (e.g.
+mean body temperature) and binary outcome data (e.g.
+death/no death).
 One study split up outcomes for patients with and without haematoma, which would be subgroups.
-
-\vspace{0mm}
-The complete listing of outcomes is in table \ref{barbiturates}.
-The table also gives an illustration of the variety of data that can be included in a review.
-We have for example continuous (mean body temperature) and binary outcome data (death).
-Additionally to primary and secondary outcomes, often also dropouts and adverse effects are included in a review.
+Thus, it is important not to confuse results with studies.
+A study can contribute multiple results to a systematic review, for example, primary and secondary outcomes and adverse effects.
 
@@
 The relative amount of missing values is very low except for study years.
-In the case of continuous outcomes, the cases have been counted were effect sizes and standard errors of effect sizes are not available.
-This means that neither mean values of groups nor mean differences are given, or that neither standard deviation nor standard error is given for a result.
-Study years before 1920 and after 2019 have been counted as missing, as well as sample sizes below zero.
+For continuous outcomes, the cases have been counted were no treatment effect and standard error is available: neither mean values and standard deviations, nor mean differences and standard error.
+Also Study years before 1920 and after 2019 are declared as missing, as well as sample sizes below zero.
 
@@
 The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{publication.year.range[5]} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}.
-Only a handful ($n$ = 18) have been published in 2018, none in 2019.
-No information is available concerning unpublished results and studies.
-
-\vspace{0mm}
-The results of a study are summarised in a result by a effect measure.
-This effect measure varies, depending on whether data is continuous, binary or time-to-event.
-The most abundant effect measures used are summarised in Table \ref{outcome.measure.frequencies}.
-One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the being some sort of discrete or binary outcomes, most often binary (> 65\%).
+Only a handful ($n = 18$) have been published in 2018, none in 2019.
+\\
+%No information is available concerning unpublished results and studies.
+The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}.
+One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (> 65\%).
 
@@
 
-The sample sizes amongst results vary to some extent.
-There are 5\% of treatment group sample sizes that are smaller tha \Sexpr{treatment.group.size.range[1]}, the 5\% quantile.
+The sample sizes among results vary to some extent.
+There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, the 5\% quantile.
 The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{treatment.group.size.range[5]} and the third quartile \Sexpr{treatment.group.size.range[4]}.
@@
 The mean is \Sexpr{samplesize.range[5]}.
-
-\vspace{0mm}
+\\
 The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}.
@@
 Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]}.
-The discrepancy between mean and median is again due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxisfor preventing infection after cesarean section, with 95 studies and 1497 results in total.
-
-\vspace{0mm}
+The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1497 results in total.
+\\
 For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome.
-More speicifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis since their research subject and experimental setup can be considered sufficiently homogeneous.
-%Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
-\vspace{0mm}
-The amount of studies that can be pooled for meta-analyses is of special interest in this masters thesis.
-Thus, the dataset is divided in groups whith identical experimental setup.
-The size of the group denotes how many results are included in a group.
-
-\vspace{0mm}
-Table \ref{repr.groups} shows the number of \textit{groups} of groups with equal or more than $n$ results.
-Practically, this means that a given number of meta analyses can be performed with each having at least $n$ results.
+More specifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis, since their research subject and experimental setup can be considered sufficiently homogeneous.
+Importantly, this distinction is also used by the Cochrane Organization itself, i.e.
+the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\%Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
+The dataset is divided in meta-analyses with identical experimental setup. The size of a meta-analysis denotes how many results are included in a group.
+Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results. Practically, this number of meta analyses can be performed, with each having at least $n$ results:
 
@@
 @
+
+\section{Data Tidying and Processing} \label{sec:Processing}
+The original dataset was provided by .. (some words how the dataset was obtained and processed by C.R.). \\
+The information in the previous pages are from a tidied and processed version of this dataset. \\
+
+\subsection{Modification of old variables}
+In some cases, reasonable assumptions led to small changes in the originally provided variables:
+\begin{itemize}
+\item \textbf{study.year}: It was assumed that studies that are declared to have been published before 1920 ($n$ = \Sexpr{length(which(data$study.year < 1920))}) are mis-specified, as well as after 2019 ($n$ = \Sexpr{length(which(data$study.year > 2019))}), so these have been set to NA.
+\item \textbf{mean1} and \textbf{mean2}: When both ``mean1'' and ``mean2'' are equal to zero or NA, ``outcome.measure.new'' is equal to ``(Std.) Mean Difference'', but a mean difference is given in ``effect'', ``mean1'' is set equal to ``effect'' ($n$ = \Sexpr{length(nomeans.ind)}).
+\end{itemize}
+
+\subsection{Newly Introduced Variables}
+Some new variables are added to the obtained dataset:
+\begin{itemize}
+\item \textbf{outcome.measure.new}: Outcome measure specifications given in ``outcome.measure'' were standardized whenever they were supposed to denote the same outcome measure.
+An example would be the formally different notations for odds ratios: ``Odds Ratio'', ``odds ratio'', ``OR'', which were all denoted as ``Odds Ratio''.
+\item \textbf{outcome.type}: A simplification of ``outcome.measure.new''.
+The outcome.type ``bin'' indicates if ``outcome.measure.new'' is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
+``cont'' is equivalent to ``outcome.measure.new'' equal to "Std.
+Mean Difference'' or ``Mean Difference''.
+``surv'' equal to ``Hazard Ratio'' and ``rate'' equal to ''Rate Ratio'' or ``Rate Difference''.
+\item \textbf{lrr} and \textbf{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.type ``bin''.
+\item \textbf{smd} and \textbf{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.type ``cont''.
+If not computable from ``mean1'', ``mean2'', ``sd1'' and ``sd2'', and ``outcome.measure.new'' was equal to ``Std.
+Mean Difference'', it was set equal to ``effect'' (and ``var.smd'' equal to ``se'' squared, $n$ =  \Sexpr{length(inpute.given.ind)}).
+\item \textbf{smd.ordl} and \textbf{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.type ``bin''.
+\item \textbf{cor.Pearson} and \textbf{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.type ``bin'') or $g$ (for outcome.type ``cont'') to $r$ transformation.
+\item \textbf{z} and \textbf{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
+\item \textbf{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.type ``cont'' or Wald test for outcome.type ``bin''.
+\item \textbf{events1c} and \textbf{events2c}: Correction of ``events1'' and ``events2'' zero event counts or event counts = patient number.
+When no events occurred, 0.5 was added, and when all patients experienced the event, 0.5 was subtracted.
+When one of ``events'' had zero counts while the other had maximum counts, no adjustment occurred.
+\item \textbf{meta.id}: Meta-analysis ID variable to uniquely identify any potential meta-analysis in the dataset.
+Consistent to what has been discussed before, all results that share a common comparison, outcome and subgroup (optional, subgroups not given in any case) may be combined in a meta-analysis.
+% \item \textbf{}:
+% \item \textbf{}:
+\end{itemize}
+
+\subsection{Eligibility criteria for Publication Bias Test and Adjustment} \
+Initially, the analysis is restricted to binary, continuous and survival outcomes. More formally:
+\begin{itemize}
+\item \textbf{Outcome measures}: The analysis has been restricted on the following outcome measures (from ``outcome.measure.new''): ``Odds Ratio'', ``Risk Ratio'', ``Risk difference'', ``Peto Odds Ratio'', ``Std.
+Mean Difference'', ``Mean Difference'', ``Hazard Ratio''
+($n$ = \Sexpr{length(data.ext2$outcome.type[which(data.ext2$outcome.type == "bin" | data.ext2$outcome.type == "cont" | data.ext2$outcome.type == "surv")])} out of a total of \Sexpr{length(data.ext2$outcome.type)} results)
+\end{itemize}
+
+The suggestions of criteria for eligibility for publication bias tests of \citet{Ioannidis2007} have largely been followed:
+\begin{itemize}
+\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = \Sexpr{m.a.largerten.number} remaining). 
+\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = \Sexpr{m.a.smaller.5.number} remaining).
+\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = \Sexpr{m.a.variance4.number} remaining).
+\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = \Sexpr{m.a.one.sig.number} remaining)
+\end{itemize}
+
+After having excluded meta-analyses with less than ten studies, additional criteria for excluding inconvenient meta-analyses are:
+\begin{itemize}
+\item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = \Sexpr{all.zero.events.number} out of meta-analyses with at least ten studies).
+\item \textbf{Missing means and sd's}: In the case of continuous outcomes, meta-analyses with means and sd's in any group being equal to zero are excluded ($n$ = \Sexpr{all.zero.means.number} out of meta-analyses with at least ten studies).
+\item \textbf{Single patient data}: Meta-analyses that are comprised of single patient data are excluded ($n$ = \Sexpr{m.a.singlepatient.number} out of meta-analyses with at least ten studies)
+\end{itemize}
+
+--Make Flowchart--
+
+\subsubsection{Exclusions due to Computational Errors}
+In exceptional cases, the applied meta-analysis methods and publication bias tests and adjustment algorithms failed due to various reasons.
+Here, those cases are listed and if known, the reasons why computation failed are given.\\
+\textbf{Binary Outcomes}: Out of the meta-analyses that are of ``outcome.type'' bin, and have at least ten studies, two studies hat to be excluded:
+\begin{itemize}
+\item meta.id = 62301 (file.nr = 1531, comparison.nr = 8, outcome.nr = 6, subgroup.nr = 1):
+%A subgroup analysis for women with increased adverse pregnancy outcomes, where the effect of vitamin C supplements is tested on pre-eclampsia: 
+Largest study (se = 0.1) has risk ratio 1 and smallest study (se = 1) risk ratio 0.07. Copas publication bias adjustment methods has likelihood optimization issues.
+\item meta.id = 94519 (2519, 14, 1, 2): Largest study (se = 0.05) has risk ratio 0.9 and smallest study (se = 0.4) risk ratio 3.
+Again Copas publication bias adjustment methods has likelihood optimization issues.
+\end{itemize}
+
+There were no issues with ``outcome.type'' ``cont'' and ``surv''.
+For the subsequent information, it is important to know that meta-analyses are only repeated with Hedges $g$, Pearson correlation coefficient and Fisher's Z-scores, if the outcome type is not survival and all of the above criteria are met ($n$ = \Sexpr{length(meta.f$n.sig.type[which(meta.f$outcome.type != "surv")])}).
+\\
+\textbf{Pearson Correlation Coefficient}: Three studies had to be excluded when analyzing the Pearson correlation coefficients:
+\begin{itemize}
+\item meta.id = 157083 (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2): A meta-analysis with all results from the same study, and equal sample size (5 each group).
+The Copas selection model algorithm issued an error when optimizing the likelihood.
+\item meta.id = 159329 (5183, 3, 13): One very small study with group sizes of 2 and 1 patients and small risk ratio of 0.222 (compared to the largest of 1.05, se = 0.04).
+Also, the Copas selection model algorithm issued an error when optimizing the likelihood.
+\item meta.id = 182298 (6211, 1, 8, -): One very small study with 8 patients in each group and 0 event counts in both.
+The Copas selection model algorithm issued an error when optimizing the likelihood.
+\end{itemize}
+
+\textbf{Fisher's Z score}: The same issues as encountered for Pearson correlation coefficients (meta.id = 157083 and 159329).
+The variance of the z score $s_z^2$ can be calculated as:  $s_z^2 = \frac{1}{n-3}$, $n$ being the total sample size.
+Thus, studies that have total sample size $n \geq 3$ are discarded in the meta-analyses ($n$ = \Sexpr{total.seq3.number} studies).
+\Sexpr{m.a.seq3.seq10.number} meta-analyses have then less than 10 studies left for pooling:
+\begin{itemize}
+\item meta.id = 10671: (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2), 7 studies left.
+\item meta.id = 43324: (1019, 1, 3, 2), 9 studies left.
+\end{itemize}
+
+\subsubsection{The Publication Bias Test and Adjustment Dataset}
+The dataset that was ultimately tested and adjusted for publication bias comprises \Sexpr{dim(metac)[1]} meta-analyses and \Sexpr{dim(meta.data)[1]} results. ..
+
+% \begin{itemize}
+% \item meta.id = 5229 (file.nr = 137, comparison.nr = 1, outcome.nr = 3, subgroup.nr = 1): ``Luken 1979'' (3), ``Miller-Fisher 1978'' (3), ``Müller Forell 1978'' (2).
+% \item meta.id = 136563 (4218, 1, 1, 1): ``Roberts 2010'' (3)
+% \item meta.id = 136566 (4218, 1, 3, 1): ``Roberts 2010'' (3)
+% \end{itemize}
+
+%which leads to a reduction of the meta-analyses that can be calculated based on the Fisher's z score by $n$ = \Sexpr{}

### 2019-06-17 report/chapter03.Rnw
Results section update

--- 2019-05-26 report/chapter03.Rnw
@@
 % LaTeX file for Chapter 03
-<<'preamble03',include=FALSE>>=
+
+%<<echo=FALSE>>=
+% library(knitr)
+% opts_chunk$set(
+%      fig.path='figure/ch03_fig',
+%      self.contained=FALSE,
+%      cache=TRUE
+%  )
+%@
+
+<<'preamble03',include=FALSE, echo=FALSE>>=
 library(knitr)
-opts_chunk$set(
-    fig.path='figure/ch03_fig', 
-    self.contained=FALSE,
-    cache=FALSE
-) 
-@
-
-<<echo=FALSE>>=
-library(knitr)
-opts_chunk$set(
-    fig.path='figure/ch02_fig',
-    self.contained=FALSE,
-    cache=TRUE
-)
-@
-
-<<echo=FALSE>>=
-library(knitr)
-opts_chunk$set(fig.path='figure/ch02_fig',
+opts_chunk$set(fig.path='figure/ch03_fig',
                echo=TRUE, message=FALSE,
-               fig.width=8.1, fig.height=3,
+               fig.width=8, fig.height=3,
+               self.contained = FALSE,
                out.width='\\textwidth-3cm',
@@
 
-<<echo=FALSE>>= 
+<<'Data03', echo=FALSE, warning=FALSE>>= 
 rm(list = ls())
@@
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-# data = pb.readData(path = PATH_DATA, file = FILE)
-# tmp = pb.clean(data)
-# data = tmp[[1]]
-# aliases = tmp[[2]]
 
@@
 
-file.bin <- "pb.bin.RData"
-if (file.exists(file.path(PATH_RESULTS, file.bin))) {
-  load(file.path(PATH_RESULTS, file.bin))
-} else {
-  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
-  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
-}
-
-file.cont <- "pb.cont.RData"
-if (file.exists(file.path(PATH_RESULTS, file.cont))) {
-  load(file.path(PATH_RESULTS, file.cont))
-} else {
-  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
-  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
-}
-
-file.meta <- "meta.RData"
-if (file.exists(file.path(PATH_RESULTS, file.meta))) {
-  load(file.path(PATH_RESULTS, file.meta))
-} else {
-  meta <- pb.meta.merge(meta.bin, meta.cont)
-  save(meta, file =  file.path(PATH_RESULTS, file.meta))
-}
-
-load(file.path(PATH_RESULTS, file = "data.processed.RData"))
-
-require(biostatUZH)
-require(tidyverse)
-require(meta)
-require(metasens)
-require(gridExtra)
-require(xtable)
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "meta.bin.RData"))
+load(file.path(PATH_RESULTS, "meta.cont.RData"))
+load(file.path(PATH_RESULTS, "meta.surv.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+
+data.ext2 <- pb.process2(data)
 @
@@
 
-% 
-% \section{Meta-analysis}
-% The data at hand is composed of over 400,000 results with balanced sample size $n > 24$.
-The significance of the p-values of treatment effect estimates was calculated for all results in the dataset with acceptable sample size and outcome measures as odds ratios, peto odds ratios, risk ratios, risk differences and mean and standardized mean differences.
-% 
-% %Significance over time? Chunck 1
-% 
-% The results that can be pooled are analysed by fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis with Hartung-Knapp method.
-% 
-% \vspace{0mm}
-% In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e.
-if studies were not unique in the dataset with respect to their experimental setup).
-The significance of the treatment effect (primary significance) in a single result is then compared to the significance of the pooled treatment effect (secondary significance).
-% In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
-The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure.
-The colors indicate the overall fraction of rejected or accepted null-hypotheses of no treatment effect.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% #plot(sig.meta.c)
-% @
-% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
-% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-% \label{primary.secondary.significance}
-% \end{figure}
-% 
-% What has been found is that even the meta-analysis that for all meta-analysis methods, the amount of secondary significance is higher than the amount of primary significance.
-Thus more primarily non-significant results can be attached to a secondarily significant result than vice-versa.
-% 
-% \vspace{0mm}
-% To illustrate this, the fraction of studies with significant primary treatment effect and primary non-significant treatment effect can be plotted separately (Figure \ref{primary.secondary.significance.sep.sig}).
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% #grid.arrange(sig.meta.plot1, nonsig.meta.plot, ncol= 1)
-% @
-% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-% \label{primary.secondary.significance}
-% \end{figure}
-% 
-% It can be seen that the extent of overlap between primary and secondary significance varies between meta-analysis.
-A considerable amount of both primary significant and primary non-significant results are overruled by meta-analysis hypothesis tests.
-% 
-% 
-% The amount of significant heterogeneity in the results used by the meta-analyses is \Sexpr{length(which(mly$sig.Q == 0))} and corresponds to \Sexpr{(length(which(mly$sig.Q == 0))/ dim(mly)[1])*100}\% of the total number of meta-analyses.
-% 
-% %Comparison of significance separated for significant Q? Chunck 2
-% 
-% %Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section{Small study effects}
-
-<<echo=FALSE>>=
-p.samplesize.effect <- data %>% filter(total1 + total2 > 10 & total1 + total2 < 200) %>% 
-  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
+<<echo=FALSE, warning=FALSE>>=
+p.samplesize.z  <- data.ext2 %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% ungroup() %>% 
+  mutate(std.z = abs(z), sample.size = total1 + total2) %>%
   group_by(sample.size) %>% 
-  summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
-  ggplot(aes(x = sample.size, y = median.effect)) + geom_point() + theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size")
-
-#levels(data$outcome.measure.new) <- c("Mean Difference", "Std. Mean Difference", "Odds Ratio", "Risk Ratio")
-
-p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 10 & total1 + total2 < 100) %>% 
-  filter(outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio" | outcome.measure.new == "Mean Difference" |
+  summarize(median.effect = median(std.z, na.rm = T)) %>% 
+  ggplot(aes(x = sample.size, y = median.effect)) + geom_point(size = 0.8) + 
+  theme_bw() + xlab("sample size") + ylab("median absolute z-score") +
+  xlim(c(15, 300)) + ylim(c(0, 0.25)) +
+  scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
+
+p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% 
+  filter(outcome.measure.new == "Risk Ratio" | 
+           outcome.measure.new == "Odds Ratio" | 
+           outcome.measure.new == "Mean Difference" |
            outcome.measure.new == "Std. Mean Difference") %>% 
@@
   summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
-  ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point() + facet_wrap(~outcome.measure.new, scales = "free") + 
-  theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size")
+  ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point(size = .5) + facet_wrap(~outcome.measure.new, scales = "free") + 
+  theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size") +
+  xlim(c(15, 300)) +
+  scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
 @
 
-To provide an overview over the abundance of small study effects in the dataset, first it is shown how median absolute effect size decreases with increasing sample size of the results (Figure \ref{effect.samplesize}).
-%In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.
-
-\vspace{0mm}
-A clear trend of decrease of absolute effect size with increasing sample size (i.e. smaller variance) is visible. 
-%It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off.
-With increasing sample size, there are fewer results, therefore, the variation between medians increases.
-All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation.
-Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.
+The median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
+It is clearly visible that the absolute value decreases with increasing sample size, i.e.
+that the effect size is becoming smaller.
+The trend flattens off after $\sim$ sample size = 400 (not shown).
+-- Appendix --
 
 \begin{figure}
-<<echo=FALSE>>=
-plot(p.samplesize.effect)
+<<echo=FALSE, warning=FALSE>>=
+plot(p.samplesize.z)
 @
-\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
-\label{effect.samplesize}
+\caption{Median of the absolute $z$-score plotted against the total sample size.}
+\label{z.samplesize}
 \end{figure}
 
-The median absolute normalized effect size can be visualized for the different outcome measures separately (Figure \ref{effect.samplesize.separated}).
-The plot confirms the trend of median effect size decrease towards lower sample size (e.g.
-for Risk Ratios: decrease $> 0.1$ standard deviations from 10 to 50 study participants).
-Instead of normalizing the effects
-%(i.e. subtracting mean and dividing through the standard deviation) 
-for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.
+Only for illustration, the same trend is reproduced in Figure \ref{effect.samplesize.separated} with a similar method, using the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std.
+Mean Difference'' (the most commonly used in the dataset).
+The ``normalized effect'' is the original effect size, normalized with respect to all other effect sizes of the same measure (i.e.
+subtraction of mean and division through standard error of the mean).
 
@@
 @
-\caption{Median of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
+\caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
 \label{effect.samplesize.separated}
@@
 
-\subsection{Small Study Effect Tests}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small Study Effect Tests}
 <<echo=FALSE, warning=FALSE>>=
-#Test Results: Binary
-test.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+sig.level <- 0.1
+meta.f <- meta.f %>% 
+	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
+				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
+				 begg.test = ifelse(pval.begg < sig.level, 1, 0),
+
+				 schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
+				 rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
+				 harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
+				 peter.test = ifelse(pval.peter < sig.level, 1, 0))
+
+meta.bin <- meta.f %>% filter(outcome.type == "bin")
+meta.cont <- meta.f %>% filter(outcome.type == "cont")
+meta.surv <- meta.f %>% filter(outcome.type == "surv")
+
+test.bin <- meta.bin %>% ungroup() %>% summarize(
 																								 schwarzer.test = mean(schwarzer.test),
@@
 p.bin <- meta.bin %>% ungroup() %>% 
-  select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
+	select(schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
 	gather(key = "test.type", value = "null.hypothesis") %>%  
-  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
 	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-  theme_bw() + xlab(label = NULL) +
-  annotate("text", x = test.bin$test.type, y = 1000, 
+	theme_bw() + xlab(label = NULL) + ggtitle("Binary Outcomes") + theme(legend.position = "top") +
+	guides(fill=guide_legend(title=NULL))+
+	annotate("text", x = test.bin$test.type, y = 500, 
 					 label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
 					 color = "white")
-
-test.sig.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-                                                              schwarzer.test = mean(schwarzer.test),
-                                                              rucker.test = mean(rucker.test),
-                                                              harbord.test = mean(harbord.test),
-                                                              peter.test = mean(peter.test))
-test.sig.bin <- test.sig.bin %>% gather(key = "test.type", value = "mean")
-
-p1 <- meta.bin %>% ungroup() %>% filter(sig.fixef.bin == 1) %>% 
-select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
-  gather(key = "test.type", value = "null.hypothesis") %>% 
-  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-  theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
-  annotate("text", x = test.sig.bin$test.type, y = 1750, 
-           label = paste(round(test.sig.bin$mean, 2)*100, "% rejected"), 
-           color = "white")
-
-test.nonsig.bin <- meta.bin %>% filter(sig.fixef.bin == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-                                                                                                schwarzer.test = mean(schwarzer.test),
-                                                                                                rucker.test = mean(rucker.test),
-                                                                                                harbord.test = mean(harbord.test),
-                                                                                                peter.test = mean(peter.test))
-test.nonsig.bin <- test.nonsig.bin %>% gather(key = "test.type", value = "mean")
-
-p2 <- meta.bin %>% 
-  filter(sig.fixef.bin == 0) %>% ungroup() %>% 
-  select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
-  gather(key = "test.type", value = "null.hypothesis") %>% 
-  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-  theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) +theme(legend.position="none") +
-  annotate("text", x = test.nonsig.bin$test.type, y = 650, 
-           label = paste(round(test.nonsig.bin$mean, 2)*100, "% rejected"), 
-           color = "white")
-
-range.pb.difference.bin <- range(test.sig.bin$mean - test.nonsig.bin$mean)
-
-#Test Results: Continuous
+#--------------------------------------------------------------------------------------------------------------------#
+
+dat_text <- data.frame(
+	label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
+									sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test)), "< 0.1,",
+								round(c(mean(meta.bin$harbord.test), mean(meta.bin$peter.test), 
+												mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test)),2)*100, "%"),
+	test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer"))
+
+labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer")
+
+p.dist.bin <- meta.bin %>% ungroup() %>% 
+	select(pval.harbord, pval.peter, pval.rucker, pval.schwarzer) %>% 
+	gather(key = "test.type", value = "p.value") %>% 
+	ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 300, label = label), color = "black") + 
+	theme(strip.text.x = element_text(size=10))
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Survival Outcomes:
 test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
 																									 begg.test = mean(begg.test),
-                                                            thomson.test = mean(thomson.test))
+																									 thompson.test = mean(thompson.test))
 
@@
 p.cont <- meta.cont %>% ungroup() %>% 
-  select(egger.test, thomson.test, begg.test) %>% 
+	select(egger.test, thompson.test, begg.test) %>% 
 	gather(key = "test.type", value = "null.hypothesis") %>% 
-  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
 	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-  theme_bw() + xlab(label = NULL) +
-  annotate("text", x = test.cont$test.type, y = 750, 
+	theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
+	guides(fill=guide_legend(title=NULL))+
+	annotate("text", x = test.cont$test.type, y = 150, 
 					 label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
 					 color = "white")
-
-test.sig.cont <- meta.cont %>% filter(sig.fixef.cont == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+#--------------------------------------------------------------------------------------------------------------------#
+
+dat_text <- data.frame(
+	label = paste(c(sum(meta.cont$begg.test), sum(meta.cont$egger.test), sum(meta.cont$thompson.test)), "< 0.1,",
+								round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test)),2)*100, "%"),
+	test.type   = c("pval.begg", "pval.egger", "pval.thompson"))
+
+labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp")
+p.dist.cont <- meta.cont %>% ungroup() %>% 
+	select(pval.egger, pval.thompson, pval.begg) %>% 
+	gather(key = "test.type", value = "p.value") %>% 
+	ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
+	facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 90, label = label),  color = "black") + 
+	theme(strip.text.x = element_text(size=10))
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Survival Outcomes:
+test.surv <- meta.surv %>% ungroup() %>% summarize(egger.test = mean(egger.test),
 																									 begg.test = mean(begg.test),
-                                                                                                thomson.test = mean(thomson.test))
-
-test.sig.cont <- test.sig.cont %>% gather(key = "test.type", value = "mean")
-
-p3 <- meta.cont %>% 
-  filter(sig.fixef.cont == 1) %>% ungroup() %>% 
-  select(egger.test, thomson.test, begg.test) %>% 
+																									 thompson.test = mean(thompson.test))
+
+test.surv <- test.surv %>% gather(key = "test.type", value = "mean")
+
+p.surv <- meta.surv %>% ungroup() %>% 
+	select(egger.test, thompson.test, begg.test) %>% 
 	gather(key = "test.type", value = "null.hypothesis") %>% 
-  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
 	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-  theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
-  annotate("text", x = test.sig.cont$test.type, y = 600, 
-           label = paste(round(test.sig.cont$mean, 2)*100, "% rejected"), 
+	theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
+	guides(fill=guide_legend(title=NULL))+
+	annotate("text", x = test.surv$test.type, y = 10, 
+					 label = paste(round(test.surv$mean, 2)*100, "% rejected"), 
 					 color = "white")
-
-test.nonsig.cont <- meta.cont %>% filter(sig.fixef.cont == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-                                                                                                   begg.test = mean(begg.test),
-                                                                                                   thomson.test = mean(thomson.test))
-
-test.nonsig.cont <- test.nonsig.cont %>% gather(key = "test.type", value = "mean")
-
-p4 <- meta.cont %>% 
-  filter(sig.fixef.cont == 0) %>% ungroup() %>% 
-  select(egger.test, thomson.test, begg.test) %>% 
-  gather(key = "test.type", value = "null.hypothesis") %>% 
-  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-  theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
-  annotate("text", x = test.nonsig.cont$test.type, y = 100, 
-           label = paste(round(test.nonsig.cont$mean, 2)*100, "% rejected"), 
-           color = "white")
-
-range.pb.difference.cont <- range(test.sig.cont$mean - test.nonsig.cont$mean)
-
-########################################################################################################################################
-########################################################################################################################################
-
-#Agreement proportions of publication bias tests:
-
-#Binary:
-n.bin <- dim(meta.bin)[1]
-meta.bin <- meta.bin %>%ungroup() %>%  mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
-                                        egger.peter = ifelse(egger.test == peter.test, "agree", "disagree"),
-                                        egger.rucker = ifelse(egger.test == rucker.test, "agree", "disagree"),
-                                        egger.harbord = ifelse(egger.test == harbord.test, "agree", "disagree"),
-                                        schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
-                                        schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
-                                        schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
-                                        rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
-                                        rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
-                                        harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
-
-agreement.bin <- meta.bin %>% ungroup() %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
-                                            egger.peter = sum(egger.peter == "agree")/n(),
-                                            egger.rucker = sum(egger.rucker == "agree")/n(),
-                                            egger.harbord = sum(egger.harbord == "agree")/n(),
-                                            schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
-                                            schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
-                                            schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
-                                            rucker.peter = sum(rucker.peter == "agree")/n(),
-                                            harbord.peter = sum(harbord.peter == "agree")/n())
-
-correlation.bin <- meta.bin %>%ungroup() %>%  summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
-                                              egger.peter = cor(pval.egger.bin, pval.peter.bin),
-                                              egger.rucker = cor(pval.egger.bin, pval.rucker.bin),
-                                              egger.harbord = cor(pval.egger.bin, pval.harbord.bin),
-                                              schwarzer.peter = cor(pval.schwarzer.bin, pval.peter.bin),
-                                              schwarzer.rucker = cor(pval.schwarzer.bin, pval.rucker.bin),
-                                              schwarzer.harbord = cor(pval.schwarzer.bin, pval.harbord.bin),
-                                              rucker.peter = cor(pval.rucker.bin, pval.peter.bin),
-                                              harbord.peter = cor(pval.harbord.bin, pval.peter.bin))
-
-binary.tests.agreement <- rbind(agreement.bin, correlation.bin)
-rownames(binary.tests.agreement) <- c("Test Agreement","P-value Correlation")
-
-#Continuous:
-n.cont <- dim(meta.cont)[1]
-meta.cont <- meta.cont %>% ungroup() %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
-                                          thomson.begg = ifelse(thomson.test == begg.test, "agree", "disagree"),
-                                          egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"))
-
-agreement.cont <- meta.cont %>% ungroup() %>%  summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
-                                              thomson.begg = sum(thomson.begg == "agree")/n(),
-                                              egger.begg = sum(egger.begg == "agree")/n())
-
-correlation.cont <- meta.cont %>% ungroup() %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
-                                                thomson.begg = cor(pval.thomson.cont, pval.begg.cont),
-                                                egger.begg = cor(pval.egger.cont, pval.begg.cont))
-
-cont.tests.agreement <- rbind(agreement.cont, correlation.cont)
-rownames(cont.tests.agreement) <- c("Test Agreement","P-value Correlation")
-
-########################################################################################################################################
-########################################################################################################################################
-
-#Trimfill missing studies fractions statistics:
-trimfill.cont.mean <- meta.cont %>% ungroup %>% summarise(mean = mean(missing.trim.cont)) %>% select(mean)
-trimfill.cont.median <- meta.cont %>% ungroup %>% summarise(median = median(missing.trim.cont)) %>% select(median)
-
-trimfill.bin.mean <- meta.bin %>% ungroup %>% summarise(mean = mean(missing.trim.bin)) %>% select(mean)
-trimfill.bin.median <- meta.bin %>% ungroup %>% summarise(median = median(missing.trim.bin)) %>% select(median)
-
-########################################################################################################################################
-########################################################################################################################################
-
-change.ranef.bin <- meta.bin %>% ungroup() %>% 
-  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>% 
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-	mutate(n = n/sum(n))
-
-p.change.ranef.bin <- meta.bin %>% ungroup() %>% 
-  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>%  
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+ 
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-  annotate("text", x = change.ranef.bin[change.ranef.bin$sig.change == 3,]$correction.method, y = 1000, 
-         label = paste(round(change.ranef.bin[change.ranef.bin$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-         color = "white")
-
-change.ranef.cont <- meta.cont %>% ungroup() %>% 
-  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>% 
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
-  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-	mutate(n = n/sum(n))
-
-p.change.ranef.cont <- meta.cont %>% ungroup() %>% 
-  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>%  
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes") +
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-  annotate("text", x = change.ranef.cont[change.ranef.cont$sig.change == 3,]$correction.method, y = 500, 
-         label = paste(round(change.ranef.cont[change.ranef.cont$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-         color = "white")
-
-change.ranef <- meta %>% ungroup() %>% 
-  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>% 
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
-  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-	mutate(n = n/sum(n))
-
-p.ranef.change <- meta %>% ungroup() %>% 
-  select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>%  
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-  annotate("text", x = change.ranef[change.ranef$sig.change == 3,]$correction.method, y = 1500, 
-         label = paste(round(change.ranef[change.ranef$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
-         color = "white")
-# Significance after correction plots, separated for meta-analyses with significant publication bias test.
-#Fixed effects meta-analysis significance
-#Binary outcomes:
-change.fixef.bin <- meta.bin %>% ungroup() %>% 
-  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>% 
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
-  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-	mutate(n = n/sum(n))
-
-p.change.fixef.bin <- meta.bin %>% ungroup() %>% 
-  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>%  
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
-  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+  
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-  annotate("text", x = change.fixef.bin[change.fixef.bin$sig.change == 3,]$correction.method, y = 800, 
-         label = paste(round(change.fixef.bin[change.fixef.bin$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
-         color = "white")
-
-#Continuous outcomes:
-change.fixef.cont <- meta.cont %>% ungroup() %>% 
-  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>% 
-  mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-  group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-	mutate(n = n/sum(n))
-
-p.change.fixef.cont <- meta.cont %>% ungroup() %>% 
-  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>%  
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes")+ 
-  theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-  annotate("text", x = change.fixef.cont[change.fixef.cont$sig.change == 3,]$correction.method, y = 300, 
-         label = paste(round(change.fixef.cont[change.fixef.cont$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
-         color = "white")
-
-#Overall:
-change.fixef <- meta %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>% 
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-	mutate(n = n/sum(n))
-
-p.fixef.change <- meta %>% ungroup() %>% 
-  select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change") %>%  
-  mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-  theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
-	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-  annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 1500, 
-         label = paste(round(change.fixef[change.fixef$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-         color = "white")
-
-#Separated for meta-analyses with significant publication bias test.
-change.fixef.bias <- meta %>% 
-  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-  filter(thomson.test == 1) %>% 
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-	mutate(n = n/sum(n))
-
-p.change.fixef.bias <- meta %>% 
-  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-  filter(thomson.test == 1) %>% 
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-  theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
-	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-  annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 250, 
-           label = paste(round(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-           color = "white")
-
-change.fixef.unbias <- meta %>% 
-  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-  filter(thomson.test == 0) %>% 
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>%  
-	mutate(n = n/sum(n))
-
-p.change.fixef.unbias <- meta %>% 
-  select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-  gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-  filter(thomson.test == 0) %>% 
-	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-  ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-  theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
-	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-  annotate("text", x = change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$correction.method, y = 1300, 
-           label = paste(round(change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-           color = "white")
-
-########################################################################################################################################
-########################################################################################################################################
-
-p.missing.copas <- meta %>% ggplot(aes(x = missing.copas/n)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20)
-p.missing.trim <- meta %>% ggplot(aes(x = missing.trim)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20)
+#--------------------------------------------------------------------------------------------------------------------#
+
+dat_text <- data.frame(
+	label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), sum(meta.surv$thompson.test)), 
+	              "< 0.1,",
+								round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), mean(meta.surv$thompson.test)),2)*100, 
+								"%"),
+	test.type   = c("pval.begg", "pval.egger", "pval.thompson"))
+
+labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp")
+p.dist.surv <- meta.surv %>% ungroup() %>% 
+	select(pval.egger, pval.thompson, pval.begg) %>% 
+	gather(key = "test.type", value = "p.value") %>% 
+	ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
+	facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 11, label = label),  color = "black") + 
+	theme(strip.text.x = element_text(size=10))
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Test agreement
+agree.bin <- meta.bin %>% mutate(n.sig = peter.test + rucker.test + harbord.test + schwarzer.test) %>% 
+	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
+	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
+  xlab("Number of significant tests") + ylab("count") + ggtitle("Binary Outcomes")
+#--------------------------------------------------------------------------------------------------------------------#
+
+agree.cont <- meta.cont %>% mutate(n.sig = egger.test + thompson.test + begg.test) %>% 
+	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
+	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
+  xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")
+#--------------------------------------------------------------------------------------------------------------------#
+
+agree.surv <- meta.surv %>% mutate(n.sig = egger.test + thompson.test + begg.test) %>% 
+	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
+	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
+  xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")
+#--------------------------------------------------------------------------------------------------------------------#
 @
 
-There are tests that can be applied to find out if small study effects are present in the meta analysis.
+The results of the test for small study effects for the meta-analyses fullfilling the criteria from chapter \ref{chapter01}, section \ref{sec:Processing}, are presented in Figures \ref{fig:test.bin}, \ref{fig:test.cont} and \ref{fig:test.surv}.
+The histogram of the $p$-values appears most often skewed to the right, indicating evidence for small study effects.
+Because different tests are applied depending on outcome type, the results are displayed separately for binary, continuous and survival outcome types (as previously defined in the dataset variable ``outcome.type'', see chapter \ref{ch:chapter01}, section \ref{sec:Processing}.
+\\
+For continuous and survival outcomes, the names refer to:
+
+\begin{itemize}
+\item Egger's test, the weigthed linear regression test as described in section \ref{sec:Egger}
+\item Thompson and Sharp's test, the weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
+\item Begg and Mazumdar's test, the rank test described in section \ref{sec:Begg}
+\end{itemize}
+
+For binary outcomes, the names refer to:
+\begin{itemize}
+\item Harbord's test, the likelihood score based test (section \ref{sec:Harbord})
+\item Peter's test, the weighted linear regression with inverse sample size as explanatory variable (study size proxy) described in section \ref{sec:Peter}
+\item R\"ucker's test, the test based on the arcsine transformation of proportions, in combination with Thompson and Sharp's regression test (section \ref{sec:Rucker})
+\item Schwarzer's test, the rank based test using the expected event counts computed with the hypergeometric distribution (section \ref{sec:Schwarzer})
+\end{itemize}
+
+\begin{figure}[!ht]
+<<echo=FALSE>>=
+plot(p.dist.bin)
+@
+\caption{Histogram of the $p$-values for small study effect in binary outcome meta-analyses.
+The testing method is indicated in the header, binwidth is equal to 0.1.
+The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
+\label{fig:test.bin}
+\end{figure}
+
+\begin{figure}
+<<echo=FALSE>>=
+plot(p.dist.cont)
+@
+\caption{Histogram of the $p$-values for the small study effect in continuous outcome meta-analyses.
+The testing method is indicated in the header, binwidth is equal to 0.1.
+The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
+\label{fig:test.cont}
+\end{figure}
+
+\begin{figure}
+<<echo=FALSE>>=
+plot(p.dist.surv)
+@
+\caption{Histogram of the $p$-values for the small study effect in survival outcome meta-analyses.
+The testing method is indicated in the header, binwidth is equal to 0.1.
+The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
+\label{fig:test.surv}
+\end{figure}
+
+\section{Small Study Effects Adjustment}
+When adjusting for small study effects, the newly obtained test statistics, as well as the corrected effect size is of interest.
+The former is displayed in Figures \ref{fig:adjustment.z} for the adjusted $z$-scores, \ref{fig:adjustment.smd} for the adjusted Hedges $g$ and Cohen's $d$ and \ref{fig:adjustment.log.hazard.ratio} for the adjusted log hazard ratios.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% 
+% <<echo=FALSE, warning=FALSE>>=
+% #Test Results: Binary
+% test.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+%                                                           schwarzer.test = mean(schwarzer.test),
+%                                                           rucker.test = mean(rucker.test),
+%                                                           harbord.test = mean(harbord.test),
+%                                                           peter.test = mean(peter.test))
+% test.bin <- test.bin %>% gather(key = "test.type", value = "mean")
+% 
+% p.bin <- meta.bin %>% ungroup() %>% 
+%   select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
+%   gather(key = "test.type", value = "null.hypothesis") %>%  
+%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+%   theme_bw() + xlab(label = NULL) +
+%   annotate("text", x = test.bin$test.type, y = 1000, 
+%            label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
+%            color = "white")
+% 
+% 
+% 
+% test.sig.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+%                                                               schwarzer.test = mean(schwarzer.test),
+%                                                               rucker.test = mean(rucker.test),
+%                                                               harbord.test = mean(harbord.test),
+%                                                               peter.test = mean(peter.test))
+% test.sig.bin <- test.sig.bin %>% gather(key = "test.type", value = "mean")
+% 
+% p1 <- meta.bin %>% ungroup() %>% filter(sig.fixef.bin == 1) %>% 
+% select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
+%   gather(key = "test.type", value = "null.hypothesis") %>% 
+%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+%   theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
+%   annotate("text", x = test.sig.bin$test.type, y = 1750, 
+%            label = paste(round(test.sig.bin$mean, 2)*100, "% rejected"), 
+%            color = "white")
+% 
+% test.nonsig.bin <- meta.bin %>% filter(sig.fixef.bin == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+%                                                                                                 schwarzer.test = mean(schwarzer.test),
+%                                                                                                 rucker.test = mean(rucker.test),
+%                                                                                                 harbord.test = mean(harbord.test),
+%                                                                                                 peter.test = mean(peter.test))
+% test.nonsig.bin <- test.nonsig.bin %>% gather(key = "test.type", value = "mean")
+% 
+% p2 <- meta.bin %>% 
+%   filter(sig.fixef.bin == 0) %>% ungroup() %>% 
+%   select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
+%   gather(key = "test.type", value = "null.hypothesis") %>% 
+%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+%   theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) +theme(legend.position="none") +
+%   annotate("text", x = test.nonsig.bin$test.type, y = 650, 
+%            label = paste(round(test.nonsig.bin$mean, 2)*100, "% rejected"), 
+%            color = "white")
+% 
+% range.pb.difference.bin <- range(test.sig.bin$mean - test.nonsig.bin$mean)
+% 
+% #Test Results: Continuous
+% test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+%                                                             begg.test = mean(begg.test),
+%                                                             thomson.test = mean(thomson.test))
+% 
+% test.cont <- test.cont %>% gather(key = "test.type", value = "mean")
+% 
+% p.cont <- meta.cont %>% ungroup() %>% 
+%   select(egger.test, thomson.test, begg.test) %>% 
+%   gather(key = "test.type", value = "null.hypothesis") %>% 
+%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+%   theme_bw() + xlab(label = NULL) +
+%   annotate("text", x = test.cont$test.type, y = 750, 
+%            label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
+%            color = "white")
+% 
+% 
+% test.sig.cont <- meta.cont %>% filter(sig.fixef.cont == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+%                                                                                                 begg.test = mean(begg.test),
+%                                                                                                 thomson.test = mean(thomson.test))
+% 
+% test.sig.cont <- test.sig.cont %>% gather(key = "test.type", value = "mean")
+% 
+% p3 <- meta.cont %>% 
+%   filter(sig.fixef.cont == 1) %>% ungroup() %>% 
+%   select(egger.test, thomson.test, begg.test) %>% 
+%   gather(key = "test.type", value = "null.hypothesis") %>% 
+%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+%   theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
+%   annotate("text", x = test.sig.cont$test.type, y = 600, 
+%            label = paste(round(test.sig.cont$mean, 2)*100, "% rejected"), 
+%            color = "white")
+% 
+% test.nonsig.cont <- meta.cont %>% filter(sig.fixef.cont == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
+%                                                                                                    begg.test = mean(begg.test),
+%                                                                                                    thomson.test = mean(thomson.test))
+% 
+% test.nonsig.cont <- test.nonsig.cont %>% gather(key = "test.type", value = "mean")
+% 
+% p4 <- meta.cont %>% 
+%   filter(sig.fixef.cont == 0) %>% ungroup() %>% 
+%   select(egger.test, thomson.test, begg.test) %>% 
+%   gather(key = "test.type", value = "null.hypothesis") %>% 
+%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
+%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
+%   theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
+%   annotate("text", x = test.nonsig.cont$test.type, y = 100, 
+%            label = paste(round(test.nonsig.cont$mean, 2)*100, "% rejected"), 
+%            color = "white")
+% 
+% range.pb.difference.cont <- range(test.sig.cont$mean - test.nonsig.cont$mean)
+% 
+% ########################################################################################################################################
+% ########################################################################################################################################
+% 
+% #Agreement proportions of publication bias tests:
+% 
+% #Binary:
+% n.bin <- dim(meta.bin)[1]
+% meta.bin <- meta.bin %>%ungroup() %>%  mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
+%                                         egger.peter = ifelse(egger.test == peter.test, "agree", "disagree"),
+%                                         egger.rucker = ifelse(egger.test == rucker.test, "agree", "disagree"),
+%                                         egger.harbord = ifelse(egger.test == harbord.test, "agree", "disagree"),
+%                                         schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
+%                                         schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
+%                                         schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
+%                                         rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
+%                                         rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
+%                                         harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
+% 
+% agreement.bin <- meta.bin %>% ungroup() %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
+%                                             egger.peter = sum(egger.peter == "agree")/n(),
+%                                             egger.rucker = sum(egger.rucker == "agree")/n(),
+%                                             egger.harbord = sum(egger.harbord == "agree")/n(),
+%                                             schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
+%                                             schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
+%                                             schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
+%                                             rucker.peter = sum(rucker.peter == "agree")/n(),
+%                                             harbord.peter = sum(harbord.peter == "agree")/n())
+% 
+% correlation.bin <- meta.bin %>%ungroup() %>%  summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
+%                                               egger.peter = cor(pval.egger.bin, pval.peter.bin),
+%                                               egger.rucker = cor(pval.egger.bin, pval.rucker.bin),
+%                                               egger.harbord = cor(pval.egger.bin, pval.harbord.bin),
+%                                               schwarzer.peter = cor(pval.schwarzer.bin, pval.peter.bin),
+%                                               schwarzer.rucker = cor(pval.schwarzer.bin, pval.rucker.bin),
+%                                               schwarzer.harbord = cor(pval.schwarzer.bin, pval.harbord.bin),
+%                                               rucker.peter = cor(pval.rucker.bin, pval.peter.bin),
+%                                               harbord.peter = cor(pval.harbord.bin, pval.peter.bin))
+% 
+% binary.tests.agreement <- rbind(agreement.bin, correlation.bin)
+% rownames(binary.tests.agreement) <- c("Test Agreement","P-value Correlation")
+% 
+% 
+% #Continuous:
+% n.cont <- dim(meta.cont)[1]
+% meta.cont <- meta.cont %>% ungroup() %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
+%                                           thomson.begg = ifelse(thomson.test == begg.test, "agree", "disagree"),
+%                                           egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"))
+% 
+% agreement.cont <- meta.cont %>% ungroup() %>%  summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
+%                                               thomson.begg = sum(thomson.begg == "agree")/n(),
+%                                               egger.begg = sum(egger.begg == "agree")/n())
+% 
+% correlation.cont <- meta.cont %>% ungroup() %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
+%                                                 thomson.begg = cor(pval.thomson.cont, pval.begg.cont),
+%                                                 egger.begg = cor(pval.egger.cont, pval.begg.cont))
+% 
+% cont.tests.agreement <- rbind(agreement.cont, correlation.cont)
+% rownames(cont.tests.agreement) <- c("Test Agreement","P-value Correlation")
+% 
+% ########################################################################################################################################
+% ########################################################################################################################################
+% 
+% 
+% #Trimfill missing studies fractions statistics:
+% trimfill.cont.mean <- meta.cont %>% ungroup %>% summarise(mean = mean(missing.trim.cont)) %>% select(mean)
+% trimfill.cont.median <- meta.cont %>% ungroup %>% summarise(median = median(missing.trim.cont)) %>% select(median)
+% 
+% trimfill.bin.mean <- meta.bin %>% ungroup %>% summarise(mean = mean(missing.trim.bin)) %>% select(mean)
+% trimfill.bin.median <- meta.bin %>% ungroup %>% summarise(median = median(missing.trim.bin)) %>% select(median)
+% 
+% ########################################################################################################################################
+% ########################################################################################################################################
+% 
+% change.ranef.bin <- meta.bin %>% ungroup() %>% 
+%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n)) 
+% 
+% p.change.ranef.bin <- meta.bin %>% ungroup() %>% 
+%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>%  
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+ 
+%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.ranef.bin[change.ranef.bin$sig.change == 3,]$correction.method, y = 1000, 
+%          label = paste(round(change.ranef.bin[change.ranef.bin$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
+%          color = "white")
+% 
+% change.ranef.cont <- meta.cont %>% ungroup() %>% 
+%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
+%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n))
+% 
+% p.change.ranef.cont <- meta.cont %>% ungroup() %>% 
+%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>%  
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes") +
+%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.ranef.cont[change.ranef.cont$sig.change == 3,]$correction.method, y = 500, 
+%          label = paste(round(change.ranef.cont[change.ranef.cont$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
+%          color = "white")
+% 
+% change.ranef <- meta %>% ungroup() %>% 
+%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
+%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n))
+% 
+% p.ranef.change <- meta %>% ungroup() %>% 
+%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>%  
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.ranef[change.ranef$sig.change == 3,]$correction.method, y = 1500, 
+%          label = paste(round(change.ranef[change.ranef$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
+%          color = "white")
+% # Significance after correction plots, separated for meta-analyses with significant publication bias test.
+% #Fixed effects meta-analysis significance
+% #Binary outcomes:
+% change.fixef.bin <- meta.bin %>% ungroup() %>% 
+%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
+%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n))
+% 
+% p.change.fixef.bin <- meta.bin %>% ungroup() %>% 
+%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>%  
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+  
+%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.fixef.bin[change.fixef.bin$sig.change == 3,]$correction.method, y = 800, 
+%          label = paste(round(change.fixef.bin[change.fixef.bin$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
+%          color = "white")
+% 
+% #Continuous outcomes:
+% change.fixef.cont <- meta.cont %>% ungroup() %>% 
+%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>% 
+%   mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n))
+% 
+% p.change.fixef.cont <- meta.cont %>% ungroup() %>% 
+%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>%  
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes")+ 
+%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.fixef.cont[change.fixef.cont$sig.change == 3,]$correction.method, y = 300, 
+%          label = paste(round(change.fixef.cont[change.fixef.cont$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
+%          color = "white")
+% 
+% #Overall:
+% change.fixef <- meta %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+% 	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n))
+% 
+% p.fixef.change <- meta %>% ungroup() %>% 
+%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change") %>%  
+%   mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+%   theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
+% 	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 1500, 
+%          label = paste(round(change.fixef[change.fixef$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
+%          color = "white")
+% 
+% #Separated for meta-analyses with significant publication bias test.
+% change.fixef.bias <- meta %>% 
+%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+%   filter(thomson.test == 1) %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+% 	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
+% 	mutate(n = n/sum(n))
+% 
+% p.change.fixef.bias <- meta %>% 
+%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+%   filter(thomson.test == 1) %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+%   theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
+% 	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 250, 
+%            label = paste(round(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
+%            color = "white")
+% 
+% change.fixef.unbias <- meta %>% 
+%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+%   filter(thomson.test == 0) %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+% 	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>%  
+% 	mutate(n = n/sum(n))
+% 
+% p.change.fixef.unbias <- meta %>% 
+%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
+%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
+%   filter(thomson.test == 0) %>% 
+% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
+%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
+%   theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
+% 	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
+%   annotate("text", x = change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$correction.method, y = 1300, 
+%            label = paste(round(change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
+%            color = "white")
+% 
+% 
+% ########################################################################################################################################
+% ########################################################################################################################################
+% 
+% p.missing.copas <- meta %>% ggplot(aes(x = missing.copas/n)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20)
+% p.missing.trim <- meta %>% ggplot(aes(x = missing.trim)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20)
+% @
+% 
+% There are tests that can be applied to find out if small study effects are present in the meta analysis.
 For the precise description, see the methods section.
 Application of the tests is only recommended if there are ten or more studies \citep{cochrane.handbook} that can be used, so all meta-analyses with less than ten studies have been excluded.
-
-\vspace{0mm}
-There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
+% 
+% \vspace{0mm}
+% There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
 In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = \Sexpr{n.cont})
-The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = \Sexpr{n.bin}).
+% The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = \Sexpr{n.bin}).
 The amount of studies varies from 5\% (Schwarzer's Test) to 13 \% (Egger's Test) for binary outcomes and 9\% (Begg and Mazumdar's Test) to 25 \% (Egger's Test) for continuous outcomes.
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-plot(p.cont)
-@
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-\label{bias.results.cont}
-\end{figure}
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-plot(p.bin)
-@
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-\label{bias.results.bin}
-\end{figure}
-
-There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not.
+% 
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(p.cont)
+% @
+% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
+% \label{bias.results.cont}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(p.bin)
+% @
+% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
+% \label{bias.results.bin}
+% \end{figure}
+% 
+% There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not.
 Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by \Sexpr{range.pb.difference.bin[2]} (the minimal increase is \Sexpr{range.pb.difference.bin[1]} for Schwarzer's Test).
-
-%Show plots of significant meta-analyses separated? Chunck 4
-
-Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses).
+% 
+% %Show plots of significant meta-analyses separated? Chunck 4
+% 
+% Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses).
 The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}.
@@
 The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
-  ggplot(aes(x = mean.publication.year, fill = factor(thomson.test), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-@
-\caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
-\label{pub.bias.overtime}
-\end{figure}
-
-The agreement of the tests, i.e.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
+%   ggplot(aes(x = mean.publication.year, fill = factor(thomson.test), stat(count))) + geom_density(na.rm = T, position = "fill") + 
+%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+% @
+% \caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
+% \label{pub.bias.overtime}
+% \end{figure}
+% 
+% 
+% The agreement of the tests, i.e.
 the proportion of meta-analyses where the rest results are equal between tests, is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
@@
 Correlation varies more between tests, both for continuous and binary outcome tests.
-
-<<results = 'asis', echo = FALSE, warning = FALSE>>=
-print(xtable(x = t(binary.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)", label = "agreement.bin",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
-@
-
-<<results = 'asis', echo = FALSE, warning = FALSE>>=
-print(xtable(x = t(cont.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)", label = "agreement.cont",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
-@
-
-\vspace{0mm}
-Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
+% 
+% <<results = 'asis', echo = FALSE, warning = FALSE>>=
+% print(xtable(x = t(binary.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)", label = "agreement.bin",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
+% @
+% 
+% 
+% <<results = 'asis', echo = FALSE, warning = FALSE>>=
+% print(xtable(x = t(cont.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)", label = "agreement.cont",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
+% @
+% 
+% \vspace{0mm}
+% Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
 The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}.
 %(Suggests that 10 is likely too small)
-In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
+% In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
 A trend towards more rejections for larger sample sizes can be seen.
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-meta %>% filter(n < 40) %>% ggplot(aes(stat(count), x = n, fill = factor(thomson.test))) + 
-  geom_density(position = "fill")
-@
-\caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
-\label{pvalues.samplesize}
-\end{figure}
-
-\vspace{0mm}
-One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% meta %>% filter(n < 40) %>% ggplot(aes(stat(count), x = n, fill = factor(thomson.test))) + 
+%   geom_density(position = "fill")
+% @
+% \caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
+% \label{pvalues.samplesize}
+% \end{figure}
+% 
+% 
+% 
+% \vspace{0mm}
+% One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
 The mean fraction of trimmed comparisons for binary outcomes is \Sexpr{round(trimfill.bin.mean,2)} and the median \Sexpr{round(trimfill.bin.median,2)}.
-% A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
+% % A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
 In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses.
-In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
+% In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
 In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-meta.bin %>% filter(missing.trim.bin < 0.5) %>% 
-  ggplot(aes(x = missing.trim.bin, fill = factor(peter.test), stat(count))) + 
-  geom_density(na.rm = T, position = "fill") + 
-  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-@
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
-\label{trimfill.pvalues.bin}
-\end{figure}
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-meta.cont %>% filter(missing.trim.cont < 0.5) %>% 
-  ggplot(aes(x = missing.trim.cont, fill = factor(thomson.test), stat(count))) + 
-  geom_density(na.rm = T, position = "fill") + 
-  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-@
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
-\label{trimfill.pvalues.cont}
-\end{figure}
-
-\subsection{Small Study Effect Correction}
-Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% meta.bin %>% filter(missing.trim.bin < 0.5) %>% 
+%   ggplot(aes(x = missing.trim.bin, fill = factor(peter.test), stat(count))) + 
+%   geom_density(na.rm = T, position = "fill") + 
+%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+% @
+% \caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
+% \label{trimfill.pvalues.bin}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% meta.cont %>% filter(missing.trim.cont < 0.5) %>% 
+%   ggplot(aes(x = missing.trim.cont, fill = factor(thomson.test), stat(count))) + 
+%   geom_density(na.rm = T, position = "fill") + 
+%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+% @
+% \caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
+% \label{trimfill.pvalues.cont}
+% \end{figure}
+% 
+% 
+% \subsection{Small Study Effect Correction}
+% Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
 Three of them will be applied to the meta-analyses shown previously that have ten or more study results and are therefore eligible for testing for publication bias.
-
-\vspace{0mm}
-The extent to what the results of the meta-analysis results are changed can be investigated.
+% 
+% \vspace{0mm}
+% The extent to what the results of the meta-analysis results are changed can be investigated.
 Because statistical significance is often used to decide if there is a treatment effect, a non-significant corrected effect size estimate can indicate that an observed treatment effect has been accepted because of small study effects.
 Therefore, the cases have been counted in which
-\begin{enumerate}
-\item Significance or non-significance of pooled estimate of meta-analysis did not change after correction for small study effects.
-\item Significance of pooled estimate of meta-analysis did change to non-significance after correction for small study effects.
-\item Non-significance of pooled estimate of meta-analysis did change to significance after correction for small study effects.
-\end{enumerate}
-
-The results of this can be seen in Figure \ref{significance.change.fixed} for all three methods, comparing the significance of the corrected pooled effect size estimate with the significance of the pooled effect size estimate of the fixed effects meta-analysis.
+% \begin{enumerate}
+% \item Significance or non-significance of pooled estimate of meta-analysis did not change after correction for small study effects.
+% \item Significance of pooled estimate of meta-analysis did change to non-significance after correction for small study effects.
+% \item Non-significance of pooled estimate of meta-analysis did change to significance after correction for small study effects.
+% \end{enumerate}
+% 
+% The results of this can be seen in Figure \ref{significance.change.fixed} for all three methods, comparing the significance of the corrected pooled effect size estimate with the significance of the pooled effect size estimate of the fixed effects meta-analysis.
 The same for significance of random effects meta-analysis is shown in Figure \ref{significance.change.random}.
@@
 Notably, the correction methods has been applied to all meta-analyses, thus also for such that had no significant small study effect test result.
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-plot(p.fixef.change)
-@
-\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction.}
-\label{significance.change.fixed}
-\end{figure}
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-plot(p.ranef.change)
-@
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction.}
-\label{significance.change.random}
-\end{figure}
-
-Since it has been previously seen in Figure \ref{test.results} that the results of small study effects vary considerably between continuous outcomes, the results in significance change from fixed effects meta-analysis can be seen separately in Figure \ref{significance.change.fixed.sep} for continuous and binary outcomes.
+% 
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(p.fixef.change)
+% @
+% \caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction.}
+% \label{significance.change.fixed}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(p.ranef.change)
+% @
+% \caption{Change in signficance of random effects meta-analysis pooled estimate after correction.}
+% \label{significance.change.random}
+% \end{figure}
+% 
+% Since it has been previously seen in Figure \ref{test.results} that the results of small study effects vary considerably between continuous outcomes, the results in significance change from fixed effects meta-analysis can be seen separately in Figure \ref{significance.change.fixed.sep} for continuous and binary outcomes.
 The change in significance from random effects meta-analysis to significance of corrected estimate can be seen in Figure \ref{significance.change.fixed.sep}
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-grid.arrange(p.change.fixef.bin, p.change.fixef.cont, ncol = 1)
-@
-\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.fixed.sep}
-\end{figure}
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-grid.arrange(p.change.ranef.bin, p.change.ranef.cont, ncol = 1)
-@
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.random}
-\end{figure}
-
-Because the real amount of publication bias in the dataset is not known, the correction method can also be applied only to meta-analyses that have publication bias according to the small study effect tests in the previous section.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(p.change.fixef.bin, p.change.fixef.cont, ncol = 1)
+% @
+% \caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
+% \label{significance.change.fixed.sep}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(p.change.ranef.bin, p.change.ranef.cont, ncol = 1)
+% @
+% \caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
+% \label{significance.change.random}
+% \end{figure}
+% 
+% Because the real amount of publication bias in the dataset is not known, the correction method can also be applied only to meta-analyses that have publication bias according to the small study effect tests in the previous section.
 Because the test developed by \citet{thomson.sharp} has been applied to both binary and continuous outcome meta-analyses (in the case of binary outcomes to arcsine variance stabilized proportions), it is used as a criterium to distinguish biased from unbiased meta-analyses.
@@
 Fixed effects meta-analysis has been used to determine signficance of the uncorrected estimate.
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-grid.arrange(p.change.fixef.bias, p.change.fixef.unbias, ncol = 1)
-@
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.random}
-\end{figure}
-
-Similarly, the number of missing studies per meta-analysis, i.e.
+% 
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(p.change.fixef.bias, p.change.fixef.unbias, ncol = 1)
+% @
+% \caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
+% \label{significance.change.random}
+% \end{figure}
+% 
+% Similarly, the number of missing studies per meta-analysis, i.e.
 those which have not been included because of small study effects, are estimated by the copas and trim-and-fill method and their empirical distribution is shown in histograms in Figure \ref{missing.studies.distribution}.
 For visualisation, the fraction of unpublished studies from the total fraction of available studies is shown.
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-grid.arrange(p.missing.copas, p.missing.trim, ncol = 1)
-@
-\caption{Fraction of missing studies estimated of the number of total studies included in the meta-analysis for copas selection and trim-and-fill method.}
-\label{missing.studies.distribution}
-\end{figure}
-
-% # <<results = 'asis', Echo = FALSE>>=
-% # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
-% #                                             schwarzer.rejection = mean(schwarzer.test),
-% #                                             rucker.rejection = mean(rucker.test),
-% #                                             harbord.rejection = mean(harbord.test),
-% #                                             peter.rejection = mean(peter.test))
-% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
-% # @
-
-% 
-% For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% grid.arrange(p.missing.copas, p.missing.trim, ncol = 1)
+% @
+% \caption{Fraction of missing studies estimated of the number of total studies included in the meta-analysis for copas selection and trim-and-fill method.}
+% \label{missing.studies.distribution}
+% \end{figure}
+% 
+% 
+% 
+% 
+% % # <<results = 'asis', Echo = FALSE>>=
+% % # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
+% % #                                             schwarzer.rejection = mean(schwarzer.test),
+% % #                                             rucker.rejection = mean(rucker.test),
+% % #                                             harbord.rejection = mean(harbord.test),
+% % #                                             peter.rejection = mean(peter.test))
+% % # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
+% % # @
+% 
+% 
+% 
+% 
+% 
+% 
+% % 
+% % For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
 The following three figures show the distribution of p-values of the corresponding tests.
 Note that only meta analyses with more than 10 comparisons have been included.
-% 
-% \vspace{0mm}
-% Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
+% % 
+% % \vspace{0mm}
+% % Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
 The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "linreg")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
-% \label{egger.cont}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "mm")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
-% \label{thomson.cont}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "rank")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{begg.cont}
-% \end{figure}
-% 
-% 
-% For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-%   filter(events1 > 0 | events2 > 0) %>% 
-%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{peters.bin}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-%   filter(events1 > 0 | events2 > 0) %>% 
-%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{harbord.bin}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Since most of the times the study publication year is available for a given result, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.
+% % 
+% % \begin{figure}
+% % <<echo=FALSE>>=
+% % data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
+% %   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
+% %   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
+% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+% %   mutate(n = n()) %>% filter(n > 9) %>% 
+% %   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
+% %                             method = "linreg")$p.val) %>% 
+% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+% %   theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% % @
+% % \caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
+% % \label{egger.cont}
+% % \end{figure}
+% % 
+% % 
+% % \begin{figure}
+% % <<echo=FALSE>>=
+% % data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
+% %   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
+% %   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
+% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+% %   mutate(n = n()) %>% filter(n > 9) %>% 
+% %   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
+% %                             method = "mm")$p.val) %>% 
+% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+% %   theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% % @
+% % \caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
+% % \label{thomson.cont}
+% % \end{figure}
+% % 
+% % \begin{figure}
+% % <<echo=FALSE>>=
+% % data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
+% %   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
+% %   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
+% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+% %   mutate(n = n()) %>% filter(n > 9) %>% 
+% %   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
+% %                             method = "rank")$p.val) %>% 
+% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+% %   theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% % @
+% % \caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
+% % \label{begg.cont}
+% % \end{figure}
+% % 
+% % 
+% % For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
+% % 
+% % \begin{figure}
+% % <<echo=FALSE>>=
+% % data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
+% %   filter(events1 > 0 | events2 > 0) %>% 
+% %   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
+% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+% %   mutate(n = n()) %>% filter(n > 9) %>% 
+% %   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
+% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+% %   theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% % @
+% % \caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
+% % \label{peters.bin}
+% % \end{figure}
+% % 
+% % 
+% % \begin{figure}
+% % <<echo=FALSE>>=
+% % data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
+% %   filter(events1 > 0 | events2 > 0) %>% 
+% %   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
+% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
+% %   mutate(n = n()) %>% filter(n > 9) %>% 
+% %   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
+% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
+% %   theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
+% % @
+% % \caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
+% % \label{harbord.bin}
+% % \end{figure}
+% 
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% % Since most of the times the study publication year is available for a given result, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.
 The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
-% @
-% \caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
-% \label{study.significance.overtime}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 2
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
+% % 
+% % \begin{figure}
+% % <<echo=FALSE, warning=FALSE>>=
+% % data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
+% %   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
+% % @
+% % \caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
+% % \label{study.significance.overtime}
+% % \end{figure}
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 2
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% % The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
 Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
@@
 In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
-%                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
-%   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
-%   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
-%   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
-%   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
-%   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
-% @
-% \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
-% \label{effects.overtime.separated}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 4
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
+% % 
+% % \begin{figure}
+% % <<echo=FALSE>>=
+% % data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
+% %                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
+% %   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
+% %   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
+% %   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
+% %   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
+% %   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
+% % @
+% % \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
+% % \label{effects.overtime.separated}
+% % \end{figure}
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 4
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% % The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
 This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p3, p4, ncol = 2)
-% @
-% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-% \label{bias.results.cont.sep}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p1, p2, ncol = 2)
-% @
-% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-% \label{bias.results.bin.sep}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% #Proportion of significant pooled estimates based on proportion of single pooled estimates
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type)) + geom_histogram()
-% 
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
-%   geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% 
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
-%   geom_histogram(position = "fill")
-% 
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef))) + 
-%   geom_histogram()
-
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.secondary.over.meansig)
-% @
-% \caption{Fraction of significant meta-analysis, dependent on the fraction of significant single results.}
-% \label{secondary.significance.over.meansig}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % 
+% % \begin{figure}
+% % <<echo=FALSE, warning=FALSE>>=
+% % grid.arrange(p3, p4, ncol = 2)
+% % @
+% % \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
+% % \label{bias.results.cont.sep}
+% % \end{figure}
+% % 
+% % \begin{figure}
+% % <<echo=FALSE, warning=FALSE>>=
+% % grid.arrange(p1, p2, ncol = 2)
+% % @
+% % \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
+% % \label{bias.results.bin.sep}
+% % \end{figure}
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 5
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% % #Proportion of significant pooled estimates based on proportion of single pooled estimates
+% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type)) + geom_histogram()
+% % 
+% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
+% %   geom_density(na.rm = T, position = "fill") + 
+% %   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
+% % 
+% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
+% %   geom_histogram(position = "fill")
+% % 
+% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef))) + 
+% %   geom_histogram()
+% 
+% % \begin{figure}
+% % <<echo=FALSE, warning=FALSE>>=
+% % plot(p.secondary.over.meansig)
+% % @
+% % \caption{Fraction of significant meta-analysis, dependent on the fraction of significant single results.}
+% % \label{secondary.significance.over.meansig}
+% % \end{figure}
+% 
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 1
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%

### 2019-06-17 report/chapter04.Rnw
Results section update

@@
 The analysis has already been said to be restricted on clinical or health care interventions.
-The interventions are restricted to two participant arms of which some measure of sanity or worsening of health is measured and compared.
-The difference between these two is referred to as the effect of the treatment.
-Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or Hedges $g$, fisher's z score or pearson correlation.
+The interventions are restricted to comparisons of two treatment arms by some measure of sanity or worsening of health.
+The difference in this measure between the grouops is referred to as the treatment effect.
+Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or Hedges $g$, Fisher's z score or Pearsons correlation coefficient.
 \\
@@
 The pooled treatment effect of a meta-analysis will be denoted as $\theta_M$, and consequently, the observed pooled treatment effect as $\hat{\theta}_M$.
-Furthermore, each treatment effect is typically measured with some standard error $s_i$ and an estimate of $s_i$ is given by $\hat{s}_i$.
-\\
-For continuous outcomes, let $m_t$ be the mean of the treatment group, $m_c$ the mean of the control group, and equivalentyl $sd_t$ and $sd_c$ the corresponding standard deviations.
+Furthermore, each treatment effect is typically measured with some standard error $s_i$ and an estimate of $s_i$ is denoted as $\hat{s}_i$.
+The $\hat{}$ sign thus indicates if it is an estimate.\\
+For continuous outcomes, let $m_t$ be the mean of the treatment group, $m_c$ the mean of the control group, and equivalently $\textrm{sd}_t$ and $\textrm{sd}_c$ the corresponding standard deviations.
 $n_t$ and $n_c$ are the total number of participants in the groups.
@@
 
-\section{Effect Measures and p-values}
+\section{Effect Measures and $p$-values}
 \subsection{Continuous Outcomes}
-For given $(m_t, m_c), (sd_t, sd_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Hedges $g$) and  a standard error thereof.
-Note that the definition of Hedges $g$ and its standard error $s$ varies amongst the literature, the following applies for this report:
-
-\begin{align}
-s &= \sqrt{\frac{(n_t - 1)sd_t^2 + (n_c - 1)sd_c^2}{n_t + n_c - 2}} & g &= \frac{m_t - m_c}{s} \label{eq:hedges.g}
+For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Hedges $g$) and  a standard error thereof.
+Note that the definition of Hedges $g$ and its standard error $s$ varies among the literature, the following applies for this report:
+
+\begin{align}
+s &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}} & g &= \frac{m_t - m_c}{s} \label{eq:hedges.g}
 \end{align}
@@
 \begin{align}
-\theta &= m_t - m_c & s &= \sqrt{sd_t^2/n_t + sd_c^2/n_t}
+\theta &= m_t - m_c & s &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_t}
 \end{align}
@@
 Both estimators take into account that the two groups might have unequal variances.
-A p-value to test the null hypothesis that the mean between group is equal is commonly obtained with the students $t$ test.
+A $p$-value to test the null hypothesis that the mean between group is equal is commonly obtained with the students $t$ test.
 The $t$ statistic is obtained, using $s$ and $g$ from \ref{eq:hedges.g}, by
@@
 \end{align}
-and the $p$-value can be obtained with the cumulative student's $t$-distibution $F$ with $n_t + n_c - 2$ degrees of freedom:
+and the $p$-value can be obtained with the cumulative student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
 
@@
 
-The t-test is known to be less reliable if combined sample size is small ($n < 30$), see for example \citet{t.test}.
+The t-test is known to be not very reliable if combined sample size is small ($n < 30$), see for example \citet{t.test}.
 
@@
 Two commonly used effect measures for binary outcome data are risk ratios and odds ratios between treatment and control group. 
-The methods presented here can also be found, for example in \citet{Intro.meta}, pg. 34.
-Let $\theta$ be the logarithm to base 10 of the odds ratio. $\hat{\theta}$ and its variance $s^2$ can be obtained by
+The methods presented here can also be found, for example, in \cite[34]{Intro.meta}.
+Let $\theta$ be the logarithm to base 10 of the odds ratio. $\theta$ and its variance $s^2$ can be obtained by
 
@@
 
-The logarithm of the risk ratio $\theta$ and its variance $s^2$, can be estimated by
-
-\begin{align}
-\hat{\theta} &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
-\hat{s^2} &= 1/e_t + 1/n_t + 1/e_c + 1/e_t \label{eq:risk.ratio.variance}
-\end{align}
-
-Using likelihood theory, one could show that the estimates are maximum likelihood estimates and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$-value (\citet{held2014}, pg.98).
+Plugging in the observed counts will give the corresponding estimates. The logarithm of the risk ratio $\theta$ and its variance $s^2$ is similarly defined as
+
+\begin{align}
+\theta &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
+s^2 &= 1/e_t + 1/n_t + 1/e_c + 1/e_t \label{eq:risk.ratio.variance}
+\end{align}
+
+Using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$-value, e..g.
+\cite[98]{held2014}.
 \\
@@
 \end{align}
-which summarizes the evidence against $\theta$ being zero (i.e. the true risk/odds ratio being 1). \\
-Binary and continuous effect measures can be converted into each other. In section \ref{sec:transformation.effectsizes} at the end of this chapter, this is readily described.
+, a $p$-value for the corresponding estimates, which summarizes the evidence against $\hat{\theta}$ being zero (i.e. the true risk/odds ratio being 1). \\
+Binary and continuous effect measures can be converted into each other, as described in section \ref{sec:transformation.effectsizes}.
 
 \subsection{Survival Outcomes}
-Time-to-event data with censoring present have to be analyzed by special means.
+Time-to-event data with censoring has to be analyzed by special means.
 One frequently used method to take into account right-censoring is the Cox proportional hazards regression model \citep{Cox}.
@@
 \citet{Surv}).
+\\
 The so-called hazard ratio estimated by cox p.h.
-regression is the ratio of the instanteneous risk of experiencing the event between the two groups.
-Because it is a maximum likelihood estimator, one can again use its wald test statistic to test for equal hazards.
-\\
-Let $\hat{\theta}$ be an estimate of the log hazard ratio and $\hat{s}$ an estimate of the standard error of it. As before
+regression is the ratio of the instantaneous risk of experiencing the event between two groups.
+Because it is a maximum likelihood estimator, one can again use its Wald test statistic to test for equal hazards.
+Let $\hat{\theta}$ be an estimate of the log hazard ratio and $\hat{s}$ an estimate of the standard error of it.
+As before
 \begin{align}
@@
 \section{Fixed and Random Effects Meta-Analysis} \label{sec:meta.analysis}
-The fixed effects meta-analysis estimator of the pooled treatment effect is a mean of the single treatment effect estimators, weighted by their standard errors \cite{fixed.effects.rosenthal}.
+The fixed effects meta-analysis estimator of the pooled treatment effect is a mean of the single treatment effect estimators, weighted by their standard errors \citep{fixed.effects.rosenthal}.
 Let $w_i = 1/s_i^2$ be the weights, and $\theta_M$ be the pooled estimator and $s_M^2$ its variance.
@@
 
-This estimator minimizes the variance, an estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and standard errors $\hat{\theta}_i, \hat{s}_i^2$.
-The underlying idea is that we assume $\hat{\theta}_i \sim N(\theta_M, s_i^2)$, $\theta_M$ being the true effect, such that all $\theta_i$ are disitributed equally.
+This estimator minimizes the variance between the effects.
+An estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and variances $\hat{\theta}_i, \hat{s}_i^2$.
+The underlying idea is that we assume $\theta_i \sim N(\theta_M, s_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.
 \\
@@
 
-So marginally, we have $\theta_i$ being distributed around a common mean $\theta_M$ with additional variance $\tau^2$:
-
-\begin{align}
-\theta_i | \mu_i \sim N(\theta_M, s_i^2 + \tau^2) \label{eq:random.effects.marginal}
+Marginally, we have $\theta_i$ being distributed around a common mean $\theta_M$ with additional variance $\tau^2$:
+
+\begin{align}
+\theta_i | \mu_i \sim N(\theta_M, s_i^2 + \tau^2) \nonumber %\label{eq:random.effects.marginal}
 \end{align}
@@
 $\tau^2$ is often referred to as a population variance or between-study variance, whereas $s_i^2$ can be interpreted as sampling error.
-The pooled treatment effect and its variance is obtained by replacing the weights $w_i$ in equation \ref{eq:fixed.effects} with $w_i = 1/(s_i^2 + \tau^2)$.
-\\
-The model is clearly superior to the fixed effects model whenever the standard errors of the treatment effects alone are unlikely to fully account for the entire variability between studies.
-Note that as $\tau^2$ increases, each $\theta_i$ will eventually get equal weights, irrespective of sampling error.\\
+The pooled treatment effect estimate $\theta_M$ of the random effects model and its variance is obtained by replacing the weights $w_i$ in equation \ref{eq:fixed.effects} with $w_i = 1/(s_i^2 + \tau^2)$.
+\\
+The model is superior to the fixed effects model whenever the standard errors of the treatment effects alone are unlikely to fully account for the entire variability observed between studies.
+Note that as $\tau^2$ increases, each $\theta_i$ will eventually get equal weights, irrespective of it's sampling error $s_i^2$.\\
 The estimation of $\tau^2$ has been subject to some debate in the statistical literature. Oftentimes, the method of moment estimator of \citet{tau.estimator} is used.
@@
 Again, $w_i, \theta_i ...$ have to be replaced by their estimates in order to get an estimate $\hat{\tau}^2$. \\
-The Paule-Madel estimator \citep{paulemandel} is considered to have most often better properties than the method of moments estimator \citep{tau.estimator.evaluation}.
-Since we defined $w_i = 1/(s_i^2 + \tau^2)$, it is straightforward that
-
-% \begin{align}
-% w_i \textrm{Var}(\theta_i) &= 1 & \textrm{Var}(\sqrt{w_i}\theta_i) = 1 \nolabel
-% \end{align}
+The Paule-Mandel estimator \citep{paulemandel} is considered to have most often better properties than the method of moments estimator (e.g. \citet{tau.estimator.evaluation}).
+Since we defined $w_i = 1/(s_i^2 + \tau^2)$, it als holds that
+
+\begin{align}
+w_i \textrm{Var}(\theta_i) &= 1 & \textrm{Var}(\sqrt{w_i}\theta_i) = 1 \nonumber
+\end{align}
 
@@
 
-$\theta_M$ can be estimated using equation \ref{eq:fixed.effects} and the new weights $w_i$, thus, the only problem is to estimate $\tau^2$.
-It can be obtained through an iterative process, using a newly defined function
+$\theta_M$ can be estimated using equation \ref{eq:fixed.effects}, the only problem is to estimate $\tau^2$. It can be obtained through an iterative process, using a newly defined function
 
@@
 In view of equation \ref{eq:paulemandel}, $\tau^2$ must be such that $F(\tau^2) = 0$.
-We start with a arbitrary $\tau^2$, iteratively add a term $\tau_0^2$ and update $\tau^2$ until $F(\tau^2 + \tau_0^2)$ is close to zero.
-Using a truncated taylor series expansion, one can obtain the partial derivative after $\tau^2$, which is a reasonable choice for $\tau_0^2$.
-Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{theta}$, we can update $F(\tau^2)$ and check convergence to zero.
-\\
-The estimation of $\tau^2$ is accompained by uncertainity.
-A common procedure is to test if it is there is significant heterogeneity between the studies (\citet{Intro.meta}, pg.
-109).
+Then, we start with a arbitrary $\tau^2$ and repeatedly add a term $\tau_0^2$ to update $\tau^2$ until $F(\tau^2 + \tau_0^2)$ is close to zero (using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{\theta}_M$).
+Using a truncated Taylor series expansion, one can obtain the partial derivative after $\tau^2$, which is a reasonable choice for $\tau_0^2$.
+\\
+%Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{theta}$, we can update $F(\tau^2)$ and check convergence to zero. \\
+The estimation of $\tau^2$ is accompanied by uncertainty.
+A common procedure is to test if it is there is significant heterogeneity between the studies \cite[109]{Intro.meta}.
 Compute $Q$, as given in \ref{eq:Q.heterogeneity}, based on one of the estimators of $\tau^2$.
@@
 Thus, the expected value of $Q$ is $n-1$, and the excess dispersion is $Q - n + 1$.
-The $p$-value against the null hypothesis of equally distributed effect sizes is, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
-= $n-1$, $1 - F(Q)$.
+The $p$-value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
+= $n-1$.
 \\
@@
 \begin{align}
-I^2 &= (Q - n + 1)/Q \label{I2.proportion}
-\end{align}
-
-Large values for $\hat{I}^2$ are of great importance when analysing e.g. small study effects. \\
-Importantly, all proposed methods above assume normality and proper estimation of standard errors.
+I^2 &= (Q - n + 1)/Q \nonumber%\label{I2.proportion}
+\end{align}
+
+%Large values for $\hat{I}^2$ are of great importance when analyzing e.g. small study effects. \\
+Importantly, all proposed methods above assume normally distributed effect sizes and proper estimates $\hat{s}$ of the true standard error.
 This assumptions are not met for very small sample sizes and very few event counts.
-An alternative in the latter case is the mantel-haenszel method for risk and odds ratios (see e.g.
-\citet{mantel.haenszel}).
+Alternatively, the mantel-haenszel method for risk and odds ratios (see e.g.
+\citet{mantel.haenszel}) could be used in the latter case.
 
@@
 \subsection{Continuous Outcome Tests}
-For a continuous outcomes that are normally distributed, the sample mean and variance are independent of each other (\citet{meta.w.R}, pg 120).
+For a continuous outcomes that are normally distributed, the sample mean and variance are independent of each other \cite[120]{meta.w.R}.
 Thus, the estimated standard errors of treatment effects can be used as a proxy for study size, as they should in principle not be tied to the effect size.
 
-\subsubsection{Begg and Mazumdar: Rank Correlation Test}
+\subsubsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
 \citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
@@
 
-\subsubsection{Egger's Test: Weighted Linear Regression Test}
+\subsubsection{Egger's Test: Weighted Linear Regression Test} \label{sec:Egger}
 First, the concept of simple linear regression is introduced. In short, the model assumes a dependent variable $y$ to be a linear function of another explanatory variable $x$:
@@
 
-Let $\mathbf{X}$ be a matrix whith the explanatory variables $x$ and $\mathbf{y}$ a corresponding vector for all $y$:
+Let $\mathbf{X}$ be a matrix with the explanatory variables $x$ and $\mathbf{y}$ a corresponding vector for all $y$:
 
@@
 
-Is an estimator of $\mathbf{\beta}$ that mimizes the squared residuals.
+Is an estimator of $\mathbf{\beta}$ that minimizes the squared residuals.
 Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\mathbf{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$.
@@
 where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. $p$ will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
-The concept is extendable to weigthed linear regression.
-Weigthed linear regression may be used if the residuals $\mathbf{r}$ have unequal variances, which is equivalent to ascribe different precision to the observed $y$.
+The concept is extendable to weighted linear regression.
+Weighted linear regression may be used if the residuals $\mathbf{r}$ have unequal variances, which is equivalent to ascribe different precision to the observed $y$.
 The least squares equation \ref{eq:least.squares} is extended to
@@
 
-with positive weigths $w_i$ that penalize large squared residuals for some $i$ more if $w_i$ is larger compared to other $w_i$. \\
-Let $\mathbf{W}$ be a $n \times n$ matrix with $\mathbf{W}_{ii} = w_i$, the weigths on the diagonal and zeros on the off-diagonals.
-The estimates in \ref{eq:regression.parameters} and \ref{eq:regression.variances} can stil be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$.
+with positive weights $w_i$ that penalize large squared residuals for some $i$ more if $w_i$ is larger compared to other $w_i$. \\
+Let $\mathbf{W}$ be a $n \times n$ matrix with $\mathbf{W}_{ii} = w_i$, the weights on the diagonal and zeros on the off-diagonals.
+The estimates in \ref{eq:regression.parameters} and \ref{eq:regression.variances} can still be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$.
 \label{weighted.regression} \\
@@
 Let $\theta/s$ be the dependent variable $y$ and $1/s$ the explanatory variable $x$.
-If plotted, this corresponds to a radial or galbraith plot \citet{galbraith}.
+If plotted, this corresponds to a radial or Galbraith plot \citet{galbraith}.
 The linear regression equation as introduced before in \ref{eq:simple.regression} can be written in two ways:
@@
 
-\ref{eq:radial.plot} is often provided due to the correspondance to the radial plot. However, it is equivalent to
+\ref{eq:radial.plot} is often provided due to the correspondence to the radial plot. However, it is equivalent to
 
@@
 
-with weigths $w = 1/s^2$.
+with weights $w = 1/s^2$.
 Thus testing $\beta_0$ of \ref{eq:radial.plot} or $\beta_1$ is equivalent.
@@
 
-\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{Thompson}
+\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{sec:Thompson}
 A method proposed in \citet{thompson.sharp} allows for between study variance $\tau^2$, as introduced before in section \ref{sec:meta.analysis}.
@@
 $\tau^2$ is estimated as in equation \ref{eq:Tau.definition} (method of moments). %or \ref{eq:paule.mandel}. 
-The weigths are set as $w_i = 1/\sqrt{s_i^2 + \tau^2})$.
+The weights are set as $w_i = 1/\sqrt{s_i^2 + \tau^2})$.
 After adjusting for the weights as described in \ref{weighted.regression}, we can proceed analogous to Egger's test.
-The p-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
+The $p$-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
 
@@
 
-\subsubsection{Peters Test: Weighted Linear Regression Test}
+\subsubsection{Peters Test: Weighted Linear Regression Test} \label{sec:Peter}
 Instead of taking the standard error $s$ as explanatory variable $x$ as in Egger's Test, the inverse of the total sample size is used.
@@
 
-\subsubsection{Harbord's Test: Score based Test}
+\subsubsection{Harbord's Test: Score based Test} \label{sec:Harbord}
 A rank based alternative to Peters test for binary outcomes is Harbord's test \citep{Harbord}.
@@
 It can be shown that they are both good approximations of the log odds ratio and its variance if the real $\theta$ is not too far from zero.
-The standardized estimator $r_i/v_i$ is also known as peto odds ratio.
+The standardized estimator $r_i/v_i$ is also known as Pet0 odds ratio.
 The obtained scores and variances can be used in Egger's test as treatment effects and variances.
 
-\subsubsection{Schwarzer's Test: Rank Correlation Test}
+\subsubsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
 \citet{Schwarzer} developed a test for the correlation between $E_t - \mathbb{E}(E_t)$ and the variance of $E_t$, $E_t$ being a random variable from the non-central hypergeometric distribution, assuming a fixed log odds ratio.
@@
 
-\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
+\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables} \label{sec:Rucker}
 The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables.
@@
 There are different approaches to correct for small study effects and publication bias.
-They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinte precision (i.e.
+They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinite precision (i.e.
 very small standard error) or to a summary effect, corrected for publication bias.
-Selection modells aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:
+Selection models aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:
 
@@
 The only difference between Thompson and Sharp's variant is $x = \sqrt{s^2 + \tau^2}$ instead of $x = \sqrt{s^2}$.
-$\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
-
-\begin{align}
-\mathbb{E}((\theta_i - \beta_0)/\sqrt{s_i^2}) \rightarrow \beta_1 \textrm{ if } s_i \rightarrow \infty \label{limitmeta.infinitesample} \\
-\mathbb{E}(theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} s_i \rightarrow 0
+$\beta_{1}$ represents the bias introduced by small study effects, as illustrated in the following equations:
+
+\begin{align}
+\mathbb{E}((\theta_i - \beta_0)/\sqrt{s_i^2}) \rightarrow \beta_1 \textrm{ if } s_i \rightarrow \infty \nonumber \\ %\label{limitmeta.infinitesample} \\
+\mathbb{E}(theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} s_i \rightarrow 0 \nonumber
 \end{align}
@@
 
+Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior with respect to coverage (and mean squared error).
+
 \subsection{Copas Selection Model}
@@
 Selection of studies depends on their effect size and variance.
-Smaller variance is always accompained by larger selection probability.
+Smaller variance is always accompanied by larger selection probability.
 \\
@@
 \begin{align}
-\theta_i = \mu_i + \sigma_i\epsilon_i \\
-\mu_i \sim N(\theta, \tau^2) \\
-z_i = a + b/s_i + \delta_i
+\theta_i = \mu_i + \sigma_i\epsilon_i \nonumber \\ 
+\mu_i \sim N(\theta, \tau^2) \nonumber \\
+z_i = a + b/s_i + \delta_i \nonumber
 \end{align}
@@
 One can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process.
-Selection models are in general not recommended for inference \citep{selection.assessment}.
+Selection models are in general not recommended for inference (e.g.
+\citet{selection.assessment}).
 \citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes. \\
@@
 When some $p$-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the least intense underlying selection model is chosen).\\
-Currently, there is no test to detect missspecifications in the model itself, the authors themselves have argued that a nonparametric test of the residuals would lack power.
+Currently, there is no test to detect miss-specifications in the model itself, the authors themselves have argued that a non-parametric test of the residuals would lack power.
 
 \section{Transformation between effect sizes} \label{sec:transformation.effectsizes}
-Assumon that binary outcomes result from a dichtomozation of originally continuous random variables, in this case, the logistic distribution, a transformation from typical binary effect measures to Cohen's $d$ can be achieved (\citet{Intro.meta}, pg.
-47).
+Assuming that binary outcomes result from a dichotomization of originally continuous random variables, in this case, the logistic distribution, a transformation from typical binary effect measures to Cohen's $d$ can be achieved \cite[47]{Intro.meta}.
 \\
@@
 
-$\frac{\pi}{\sqrt{3}} = 1.81$ is the standard deviation of the logistic distribution $L(\mu, \eta)$ with scale parameter $\eta = 1$, so we just divide the log odds ratio and it's variance throught the standard deviation.
+$\frac{\pi}{\sqrt{3}} = 1.81$ is the standard deviation of the logistic distribution $L(\mu, \eta)$ with scale parameter $\eta = 1$, so we just divide the log odds ratio and it's variance through the standard deviation.
 The approximation works only well if $e_t$ and $e_c$ are not very small, especially in the case of $s_d^2$.
 Plugging in the observed log odds ratio $\hat{\theta}$ and $\hat{s}^2$ will give an estimate of Cohen's $d$.\\
-Pearsons correlation can be attained by the formulas (\citet{olkin1985dtor}, \citet{Intro.meta} pg. 48-49)
+Pearson's correlation can be attained by the formulas (\citet{olkin1985dtor}, \cite[48]{Intro.meta})
 
@@
 % 
-% A p-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
+% A $p$-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
 % 
@@
 % If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
-The p-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
+The $p$-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
 % 
@@
 Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
-The p-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
+The $p$-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
 % 
@@
 For those values, the quantities above can be calculated and illustrated.
-Values for $\mu$ that have p-values over a predefined significance threshold can be used for inference of the effect size.
+Values for $\mu$ that have $p$-values over a predefined significance threshold can be used for inference of the effect size.
 % 

### 2019-06-17 code/additional_plots.R

@@ -29,6 +29,8 @@ load(file.path(PATH_RESULTS, "meta.cont.RData"))
 load(file.path(PATH_RESULTS, "meta.surv.RData"))
 load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
 
+data.ext2 <- pb.process2(data)
+
 
 
 #Explanation of coding: 0 = (unsig, unsig), 1 = (unsig, sig), 2 = (sig, sig), 3 = (sig, unsig)
@@ -310,9 +312,9 @@ ranef.fixef.sc.zval <- effect.diff %>% ggplot(aes(x = abs(zval.fixef), y = abs(z
 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
 	ggtitle("Fixed effects and Random effects z statistics") + ylab("Random effects statistic") + xlab("Fixed effects statistic")
 
-effect.diff %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.trimfill.fixef))) + geom_point(size = 0.8) +
-	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
-	ggtitle("Fixed effects and Random effects z statistics") + ylab("Random effects statistic") + xlab("Fixed effects statistic")
+# effect.diff %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.trimfill.fixef))) + geom_point(size = 0.8) +
+# 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
+# 	ggtitle("Fixed effects and Random effects z statistics") + ylab("Random effects statistic") + xlab("Fixed effects statistic")
 
 # trimfill.fixef.sc.zval <- effect.diff %>% ggplot(aes(x = abs(zval.fixef), y = abs(zval.trimfill.fixef))) + geom_point(size = 0.8) +
 # 	geom_abline(slope = 1, color = "red") + geom_smooth(method = "lm", se = FALSE) + theme_bw() + 
@@ -370,4 +372,37 @@ meta.cont %>% filter(missing.trim.cont < 0.5) %>%
 	geom_density(na.rm = T, position = "fill") + 
 	labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
 #--------------------------------------------------------------------------------------------------------------------#
+
+#Median standardized z-scores for various sample size
[…]

### 2019-06-17 code/analysis_plots.R

@@ -30,6 +30,8 @@ load(file.path(PATH_RESULTS, "meta.surv.RData"))
 load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
 
 
+# data.ext2 <- pb.process2(data)
+
 ################################################################################################
 ################################################################################################
 #PROPORTION OF SIGNIFICANT PUBLICATION BIAS TESTS
@@ -96,6 +98,7 @@ p.bin <- meta.bin %>% ungroup() %>%
 	annotate("text", x = test.bin$test.type, y = 500, 
 					 label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
 					 color = "white")
+#--------------------------------------------------------------------------------------------------------------------#
 
 dat_text <- data.frame(
 	label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
@@ -109,10 +112,12 @@ labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucke
 p.dist.bin <- meta.bin %>% ungroup() %>% 
 	select(pval.harbord, pval.peter, pval.rucker, pval.schwarzer) %>% 
 	gather(key = "test.type", value = "p.value") %>% 
-	ggplot(aes(x = p.value)) + geom_histogram(bins = 20) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 100, label = label), color = "black") + 
+	ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 170, label = label), color = "black") + 
 	theme(strip.text.x = element_text(size=15))
+#--------------------------------------------------------------------------------------------------------------------#
 
+#Survival Outcomes:
 test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
 																									 begg.test = mean(begg.test),
 																									 thompson.test = mean(thompson.test))
@@ -129,6 +134,7 @@ p.cont <- meta.cont %>% ungroup() %>%
[…]

### 2019-06-17 code/new_meta_analysis.R

@@ -50,22 +50,22 @@ settings.meta(hakn=TRUE, method.tau="PM", method = "Inverse")
 
 tmp <- data.ext2 %>% filter(outcome.type == "bin") %>% group_by(meta.id) %>% 
 	mutate(n = n()) %>% filter(n >= 10) %>% filter(!all(events1 == 0) & !all(events2 == 0)) 
-
 meta.id.vector <- unique(tmp$meta.id)
 meta.id.vector <- meta.id.vector[-c(which(meta.id.vector == 94519),
                                    which(meta.id.vector == 62301))] #Copas likelihood conv. problems..
-meta.analyses <- list()
-meta.analyses.asd <- list()
-meta.analyses.limitmeta <- list()
-meta.analyses.copas <- list()
-meta.analyses.trimfill <- list()
-meta.tests.harbord <- list()
-meta.tests.peter <- list()
-meta.tests.rucker <- list()
-meta.tests.schwarzer <- list()
-counter <- 0
 
-
+# meta.analyses <- list()
+# meta.analyses.asd <- list()
+# meta.analyses.limitmeta <- list()
+# meta.analyses.copas <- list()
+# meta.analyses.trimfill <- list()
+# meta.tests.harbord <- list()
+# meta.tests.peter <- list()
+# meta.tests.rucker <- list()
+# meta.tests.schwarzer <- list()
+# counter <- 0
+# 
+#
 # for(u in meta.id.vector){
 # 	counter <- counter + 1
 # 	print(c(u, counter))
@@ -102,15 +102,15 @@ meta.tests.peter <- bin.meta.list[[9]]
 meta.tests.rucker <- bin.meta.list[[10]]
 meta.tests.schwarzer <- bin.meta.list[[11]]
 
-bin.meta.list <- list(tmp, meta.id.vector, meta.analyses,
-											meta.analyses.asd,
-											meta.analyses.limitmeta,
-											meta.analyses.copas,
-											meta.analyses.trimfill,
-											meta.tests.harbord,
-											meta.tests.peter,
-											meta.tests.rucker,
-											meta.tests.schwarzer)
+# bin.meta.list <- list(tmp, meta.id.vector, meta.analyses,
+# 											meta.analyses.asd,
+# 											meta.analyses.limitmeta,
+# 											meta.analyses.copas,
+# 											meta.analyses.trimfill,
[…]

### 2019-06-24 report/MSc_Report.tex
Results first draft

@@
   \vspace*{6cm}{\bfseries\Huge
-  $p$-values:\\[5mm] their use, abuse and proper use \\[5mm]
-  illustrated with seven facets 
+  Publication Bias in the Cochrane Database of Systematic Reviews
   }
@@
   \LARGE
-  M\"axli Musterli\\[12mm]
+  Giuachin Kreiliger\\[12mm]
 
@@
 
-Howdy!
+% Howdy!
 
@@
 \begin{flushright}
-  Max Muster\\
-  June 2018
+  Giuachin Kreiliger\\
+  June 2019
 \end{flushright}
@@
       \hline
-      \textbf{file.nr} & The number of the file from which the review data has been \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
-      \textbf{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
-      \textbf{file.index} & Internal index of the file in the Cochrane library.\\
-      \textbf{file.version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
+      \texttt{file.nr} & The number of the file from which the review data has been \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
+      \texttt{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
+      \texttt{file.index} & Internal index of the file in the Cochrane library.\\
+      \texttt{file.version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
       %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
       \hline
-      \textbf{study.name} & Name of the study to which the result belongs\\
-      \textbf{study.year} & Year in which the study was published\\
+      \texttt{study.name} & Name of the study to which the result belongs\\
+      \texttt{study.year} & Year in which the study was published\\
       \hline
-      \textbf{comparison.name/.nr} & Specification of the interventions compared in the study  \\ &and a unique number for the comparison\\
-      \textbf{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ &and a unique number for the outcome\\
-      \textbf{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a \\ &unique number for the subgroup\\
-      \textbf{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
-      \textbf{effect} & Measure of the effect given in the quantity denoted by \\ &``outcome measure''.\\
-      \textbf{se} & Standard error of the measure of the effect,\\
-      \textbf{events1/events2} & The counts of patients with an outcome \textit{if}\\ &measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
-      \textbf{total1/total2} & Number of patients in groups.\\
-      \textbf{mean1/mean2} & Mean of patient measurements \textit{if} outcome is continuous.\\
-      \textbf{sd1/sd2} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
+      \texttt{comparison.name/.nr} & Specification of the interventions compared in the study  \\ &and a unique number for the comparison\\
+      \texttt{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ &and a unique number for the outcome\\
+      \texttt{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a \\ &unique number for the subgroup\\
+      \texttt{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
+      \texttt{effect} & Measure of the effect given in the quantity denoted by \\ &\texttt{outcome measure}.\\
+      \texttt{se} & Standard error of the measure of the effect,\\
+      \texttt{events1/events2} & The counts of patients with an outcome \textit{if}\\ &measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
+      \texttt{total1/total2} & Number of patients in groups.\\
+      \texttt{mean1/mean2} & Mean of patient measurements \textit{if} outcome is continuous.\\
+      \texttt{sd1/sd2} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
     \end{tabular}
@@
 \begin{itemize}
-\item \textbf{study.year}: It was assumed that studies that are declared to have been published before 1920 ($n$ = 30664) are mis-specified, as well as after 2019 ($n$ = 384), so these have been set to NA.
-\item \textbf{mean1} and \textbf{mean2}: When both ``mean1'' and ``mean2'' are equal to zero or NA, ``outcome.measure.new'' is equal to ``(Std.) Mean Difference'', but a mean difference is given in ``effect'', ``mean1'' is set equal to ``effect'' ($n$ = 1593).
+\item \texttt{study.year}: It was assumed that studies that are declared to have been published before 1920 ($n$ = 30664) are mis-specified, as well as after 2019 ($n$ = 384), so these have been set to NA.
+\item \texttt{mean1} and \texttt{mean2}: When both \texttt{mean1} and \texttt{mean2} are equal to zero or NA, \texttt{outcome.measure.new} is equal to \texttt{(Std.) Mean Difference}, but a mean difference is given in \texttt{effect}, \texttt{mean1} is set equal to \texttt{effect} ($n$ = 1593).
 \end{itemize}
@@
 \begin{itemize}
-\item \textbf{outcome.measure.new}: Outcome measure specifications given in ``outcome.measure'' were standardized whenever they were supposed to denote the same outcome measure.
+\item \texttt{outcome.measure.new}: Outcome measure specifications given in \texttt{outcome.measure} were standardized whenever they were supposed to denote the same outcome measure.
 An example would be the formally different notations for odds ratios: ``Odds Ratio'', ``odds ratio'', ``OR'', which were all denoted as ``Odds Ratio''.
-\item \textbf{outcome.type}: A simplification of ``outcome.measure.new''.
-The outcome.type ``bin'' indicates if ``outcome.measure.new'' is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
-``cont'' is equivalent to ``outcome.measure.new'' equal to "Std.
+\item \texttt{outcome.type}: A simplification of \texttt{outcome.measure.new}.
+The outcome.type ``bin'' indicates if \texttt{outcome.measure.new} is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
+``cont'' is equivalent to \texttt{outcome.measure.new} equal to "Std.
 Mean Difference'' or ``Mean Difference''.
 ``surv'' equal to ``Hazard Ratio'' and ``rate'' equal to ''Rate Ratio'' or ``Rate Difference''.
-\item \textbf{lrr} and \textbf{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.type ``bin''.
-\item \textbf{smd} and \textbf{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.type ``cont''.
-If not computable from ``mean1'', ``mean2'', ``sd1'' and ``sd2'', and ``outcome.measure.new'' was equal to ``Std.
-Mean Difference'', it was set equal to ``effect'' (and ``var.smd'' equal to ``se'' squared, $n$ =  6938).
-\item \textbf{smd.ordl} and \textbf{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.type ``bin''.
-\item \textbf{cor.Pearson} and \textbf{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.type ``bin'') or $g$ (for outcome.type ``cont'') to $r$ transformation.
-\item \textbf{z} and \textbf{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
-\item \textbf{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.type ``cont'' or Wald test for outcome.type ``bin''.
-\item \textbf{events1c} and \textbf{events2c}: Correction of ``events1'' and ``events2'' zero event counts or event counts = patient number.
+\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.type ``bin''.
+\item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.type ``cont''.
+If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.new} was equal to ``Std.
+Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  6938).
+\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.type ``bin''.
+\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.type ``bin'') or $g$ (for outcome.type ``cont'') to $r$ transformation.
+\item \texttt{z} and \texttt{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
+\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.type ``cont'' or Wald test for outcome.type ``bin''.
+\item \texttt{events1c} and \texttt{events2c}: Correction of \texttt{events1} and \texttt{events2} zero event counts or event counts = patient number.
 When no events occurred, 0.5 was added, and when all patients experienced the event, 0.5 was subtracted.
-When one of ``events'' had zero counts while the other had maximum counts, no adjustment occurred.
-\item \textbf{meta.id}: Meta-analysis ID variable to uniquely identify any potential meta-analysis in the dataset.
+When one of \texttt{events} had zero counts while the other had maximum counts, no adjustment occurred.
+\item \texttt{meta.id}: Meta-analysis ID variable to uniquely identify any potential meta-analysis in the dataset.
 Consistent to what has been discussed before, all results that share a common comparison, outcome and subgroup (optional, subgroups not given in any case) may be combined in a meta-analysis.
-% \item \textbf{}:
-% \item \textbf{}:
+% \item \texttt{}:
+% \item \texttt{}:
 \end{itemize}
 
-\subsection{Eligibility criteria for Publication Bias Test and Adjustment} \
+\subsection{Eligibility criteria for Publication Bias Test and Adjustment} 
 Initially, the analysis is restricted to binary, continuous and survival outcomes. More formally:
 \begin{itemize}
-\item \textbf{Outcome measures}: The analysis has been restricted on the following outcome measures (from ``outcome.measure.new''): ``Odds Ratio'', ``Risk Ratio'', ``Risk difference'', ``Peto Odds Ratio'', ``Std.
+\item \textbf{Outcome measures}: The analysis has been restricted on the following outcome measures (from \texttt{outcome.measure.new}): ``Odds Ratio'', ``Risk Ratio'', ``Risk difference'', ``Peto Odds Ratio'', ``Std.
 Mean Difference'', ``Mean Difference'', ``Hazard Ratio''
@@
 \begin{itemize}
+\item \textbf{Sensitivity Analyses}: When the same results are used multiple times for different meta-analyses, only one is retained.
+More precisely, if a study hat the same \texttt{study.name} and same \texttt{effect}, it was considered a duplicate, and the smaller meta-analysis of the two was excluded.
+The intention is to exclude sensitivity analyses which are operated on subsets of the available results.
 \item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = 141 out of meta-analyses with at least ten studies).
@@
 Here, those cases are listed and if known, the reasons why computation failed are given.\\
-\textbf{Binary Outcomes}: Out of the meta-analyses that are of ``outcome.type'' bin, and have at least ten studies, two studies hat to be excluded:
+\textbf{Binary Outcomes}: Out of the meta-analyses that are of \texttt{outcome.type} bin, and have at least ten studies, two studies hat to be excluded:
 \begin{itemize}
@@
 
-There were no issues with ``outcome.type'' ``cont'' and ``surv''.
+There were no issues with \texttt{outcome.type} ``cont'' and ``surv''.
 For the subsequent information, it is important to know that meta-analyses are only repeated with Hedges $g$, Pearson correlation coefficient and Fisher's Z-scores, if the outcome type is not survival and all of the above criteria are met ($n$ = 0).
@@
 % \begin{itemize}
-% \item meta.id = 5229 (file.nr = 137, comparison.nr = 1, outcome.nr = 3, subgroup.nr = 1): ``Luken 1979'' (3), ``Miller-Fisher 1978'' (3), ``Müller Forell 1978'' (2).
 % \item meta.id = 136563 (4218, 1, 1, 1): ``Roberts 2010'' (3)
@@
 % LaTeX file for Chapter 03
-
-%<<echo=FALSE>>=
-% library(knitr)
-% opts_chunk$set(
-%      fig.path='figure/ch03_fig',
-%      self.contained=FALSE,
-%      cache=TRUE
-%  )
-%@
 
@@
 
-\section{Small study effects}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Scale for 'x' is already present.
-Adding another scale for 'x', which\\\#\# will replace the existing scale.\\\#\# Scale for 'x' is already present.
-Adding another scale for 'x', which\\\#\# will replace the existing scale.}}\end{kframe}
-\end{knitrout}
-
-The median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
-It is clearly visible that the absolute value decreases with increasing sample size, i.e.
-that the effect size is becoming smaller.
-The trend flattens off after $\sim$ sample size = 400 (not shown).
--- Appendix --
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-10-1}
-
-\end{knitrout}
-\caption{Median of the absolute $z$-score plotted against the total sample size.}
-\label{z.samplesize}
-\end{figure}
-
-Only for illustration, the same trend is reproduced in Figure \ref{effect.samplesize.separated} with a similar method, using the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std.
-Mean Difference'' (the most commonly used in the dataset).
-The ``normalized effect'' is the original effect size, normalized with respect to all other effect sizes of the same measure (i.e.
-subtraction of mean and division through standard error of the mean).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-11-1}
-
-\end{knitrout}
-\caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
-\label{effect.samplesize.separated}
-\end{figure}
-
-%Show absolute effect size depending on scaled time? Chunck 3
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Small Study Effect Tests}
-
-The results of the test for small study effects for the meta-analyses fullfilling the criteria from chapter \ref{chapter01}, section \ref{sec:Processing}, are presented in Figures \ref{fig:test.bin}, \ref{fig:test.cont} and \ref{fig:test.surv}.
-The histogram of the $p$-values appears most often skewed to the right, indicating evidence for small study effects.
-Because different tests are applied depending on outcome type, the results are displayed separately for binary, continuous and survival outcome types (as previously defined in the dataset variable ``outcome.type'', see chapter \ref{ch:chapter01}, section \ref{sec:Processing}.
-\\
-For continuous and survival outcomes, the names refer to:
+\section{Small Study Effect and Excess of Singificance Tests}
+
+The results of the test for small study effects and excess of significance for the meta-analyses fullfilling the criteria from chapter \ref{chapter02}, section \ref{sec:Processing}, are presented in Figure \ref{fig:test}.
+%Figures \ref{fig:test.bin}, \ref{fig:test.cont} and \ref{fig:test.surv}. 
+The histogram of the $p$-values is displayed separately for binary, continuous and survival outcome types (as previously defined in the dataset variable \texttt{outcome.type}, see chapter \ref{ch:chapter02}, section \ref{sec:Processing}.
+The distributions are (with the exception of Schwarzer's test) skewed to the right, indicating evidence for small study effects.
+Moreover, the excess significance tests have a mode around $p = 0.4$.
+Large differences between small study effect tests for binary and continuous outcomes will be subject to discussion.
+\\
+``Excess significance'' denotes the excess of significance $p$-values from the test of \citet{excess.significance}. For continuous and survival outcomes, the names refer to:
 
@@
 
-\begin{figure}[!ht]
+\begin{figure}[ht!]
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-13-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-10-1}
+
+}
 
 \end{knitrout}
-\caption{Histogram of the $p$-values for small study effect in binary outcome meta-analyses.
+\caption{Histogram of the $p$-values for small study effect in meta-analyses.
 The testing method is indicated in the header, binwidth is equal to 0.1.
 The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-\label{fig:test.bin}
+\label{fig:test}
 \end{figure}
+
+The agreement/coinicidence between between small study effect and excess significance tests is often not pronounced, thus, it will be compared by different methods.
+This is displayed in Table \ref{test.agreement}.
+The row names indicate which two tests are compared.
+First, the column ``Test Agreement'' quantifies the overall proportion by which the two tests agree in their rejection or ``acceptance'' of the null-hypothesis.
+``Test Agreement'' being equal one thus indicates equivalent results, zero no correspondence whatsoever.
+The second column, ``Correlation'' gives the correlation between the $p$-values.
+A positive correlation indicates psotive coincidence of $p$-values, negative correlation coincidence in opposite directions.
+However, the scale might be different for this agreement measure.
+The ``R-squared'' value indicates to what extent one $p$-value can be predicted by another, and ignores additive differences between $p$-values (as for correlation), as well as multiplicative constants between them (i.e.
+$y ~ a + b*x$, $y$ and $x$ being two $p$-values of test-statistics).
+An R-squared value of 1 indicates perfect fit.
+Importantly, the order of the variables does not matter for the $p$-values for all indicators (i.e.
+$p$-values for $x$ and $y$ can be exchanged and the table stays the same).
+If a test is completely replaceable by another, all values in a row are equal to one.
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Mon Jun 24 17:05:43 2019
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lccc}
+  & Test Agreement & p-value Correlation & p-value R-squared \\ 
+  \hline
+\hline
+Excess significance, Schwarzer & 0.83 & -0.02 & 0.00 \\ 
+  Excess significance, Peter & 0.80 & 0.05 & 0.00 \\ 
+  Excess significance, Rucker & 0.82 & 0.12 & 0.02 \\ 
+  Excess significance, Harbord & 0.81 & 0.02 & 0.00 \\ 
+  Peter, Schwarzer & 0.82 & 0.29 & 0.09 \\ 
+  Schwarzer, Rucker & 0.82 & 0.29 & 0.08 \\ 
+  Schwarzer, Harbord & 0.86 & 0.51 & 0.26 \\ 
+  Rucker, Peter & 0.89 & 0.64 & 0.41 \\ 
+  Harbord, Peter & 0.86 & 0.48 & 0.23 \\ 
+   \hline
+Excess significance, Egger & 0.79 & 0.14 & 0.02 \\ 
+  Excess significance, Thompson & 0.80 & 0.16 & 0.02 \\ 
+  Excess significance, Begg & 0.81 & 0.10 & 0.01 \\ 
+  Thompson, Egger & 0.95 & 0.91 & 0.83 \\ 
+  Thompson, Begg & 0.87 & 0.70 & 0.49 \\ 
+  Egger, Begg & 0.86 & 0.65 & 0.42 \\ 
+   \hline
+Excess significance, Egger (survival) & 0.69 & 0.03 & 0.00 \\ 
+  Excess significance, Thompson (survival) & 0.64 & 0.05 & 0.00 \\ 
+  Excess significance, Begg (survival) & 0.62 & 0.18 & 0.03 \\ 
+  Thompson, Egger (survival) & 0.90 & 0.92 & 0.85 \\ 
+  Thompson, Begg (survival) & 0.92 & 0.66 & 0.43 \\ 
+  Egger, Begg (survival) & 0.87 & 0.70 & 0.48 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Agreement in significance proportion, correlation and R-squared of linear regression
+             between the p-values of the publication bias tests. Horizontal lines separate binary, continuous and survival outcomes (order as in table).} 
+\label{test.agreement}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small Study Effects Adjustment}
+
+\subsection{Change in Effect Size after Adjustment}
+
+If one is interested in the mere change in effect size and if the effect size did decrease or increase after adjustment, one can look at Figure \ref{fig:adjustment.size}.
+It displays the difference between the meta-analysis pooled treatment effect and the adjusted treatment effect.
+To compare the overall effect of adjustment for small study effects, the absolute value of the effect size is used.
+Thus, a negative difference indicates larger adjusted treatment effect size than meta-analysis pooled effect size.
+For better illustration, some very large and very small differences have been ommitted in the $z$-score and Hedges $g$ histogramms; the missing differences are provided in Table \ref{missing.differences}.
+Additionally to the histogramms, Table \ref{adjustment.difference} shows the quantiles and means for the various differences.
+%For sake of interpretability, negative effect sizes are changed to positive, such that a negative difference always means that the adjusted treatment effect is larger than the meta-analysis effect.
+Vice versa, a positive difference will indicate smaller adjusted effects.
+\\
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-14-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-13-1}
+
+}
 
 \end{knitrout}
-\caption{Histogram of the $p$-values for the small study effect in continuous outcome meta-analyses.
+\caption{Histogram of the treatment effect differences between meta-analysis and adjusted meta-analysis.
+Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes.
+The bins are centered at zero.}
+\label{fig:adjustment.size}
+\end{figure}
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Mon Jun 24 17:05:45 2019
+\begin{table}[ht]
+\centering
+\begingroup\tiny
+\begin{tabular}{lcccrrrrrrrr}
+  \hline
+meta.id & file.nr & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
+  \hline
+2009 & 2009 & 1 & 1 & 0.31 & 0.36 & 0.31 & 0.43 & 0.70 & 0.70 & 0.70 & 2.48 \\ 
+  2068 & 2068 & 2 & 0 & 0.29 & 0.35 & 0.29 & 0.43 & 0.68 & 0.68 & 0.68 & 2.57 \\ 
+  18658 & 18658 & 2 & 0 & 1.16 & 1.14 & 1.16 & 1.17 & 1.40 & 2.85 & 1.40 & 1.74 \\ 
+  46472 & 46472 & 1 & 1 & 1.79 & 1.44 & 1.79 & 0.66 & 0.12 & 6.97 & 6.97 & 0.79 \\ 
+  52528 & 52528 & 1 & 0 & -0.75 & -0.69 & -0.50 & -0.26 & -1.19 & -1.53 & 0.18 & -0.52 \\ 
+  60546 & 60546 & 1 & 1 & 0.17 & 0.24 & 0.17 & 0.34 & 0.53 & 0.53 & 0.53 & 1.65 \\ 
+  70389 & 70389 & 1 & 1 & -0.08 & -0.07 & 15.58 & -0.04 & -0.13 & -0.13 & -0.13 & -0.05 \\ 
+  73769 & 73769 & 3 & 1 & -0.14 & 0.00 & 214760.42 & -0.04 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
+  79113 & 79113 & 2 & 0 & -0.38 & -0.38 & -0.38 & -0.48 & -0.93 & -0.93 & -2.00 & -3.47 \\ 
+  90138 & 90138 & 3 & 0 & 0.31 & 0.80 & 0.31 & 0.55 & 0.72 & 0.71 & 0.71 & 2.16 \\ 
+  97356 & 97356 & 2 & 0 & -0.08 & -0.33 & -0.08 & -0.17 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
+  98030 & 98030 & 1 & 0 & -0.09 & -0.07 & -0.09 & -0.04 & -0.41 & -0.41 & -1.50 & -2.79 \\ 
+  101436 & 101436 & 1 & 5 & 0.54 & 0.62 & 0.80 & 0.91 & 1.21 & 1.21 & 1.21 & 2.74 \\ 
+  118121 & 118121 & 4 & 1 & 0.25 & 0.23 & 71.80 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
+  119537 & 119537 & 3 & 0 & 0.07 & 0.15 & 0.07 & 0.29 & 0.50 & 0.50 & 1.43 & 1.81 \\ 
+  119818 & 119818 & 3 & 3 & -0.25 & -0.25 & -0.11 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
+  146301 & 146301 & 1 & 0 & 0.14 & 0.26 & 498188.34 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects
+             of Figure 
+ef{fig:adjustment.size}. Abbreviations are used for z-score (z) and Hedges g (g)} 
+\label{missing.differences}
+\end{table}
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Mon Jun 24 17:05:45 2019
+\begin{table}[ht]
+\centering
+\begingroup\scriptsize
+\begin{tabular}{lcccccc}
+  \hline
+ & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
+  \hline
+z-score: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.05 & 402.37 \\ 
+  z-score: Random - Copas & -0.04 & 0.00 & 0.00 & 0.00 & 0.01 & 159.98 \\ 
+  z-score: Fixed - Regression & -0.15 & -0.05 & -0.01 & 0.04 & 0.13 & -0.01 \\ 
+  z-score: Random - Regression & -0.18 & -0.07 & -0.02 & 0.03 & 0.16 & -0.02 \\ 
+  Hedges g: Fixed - Copas & -0.09 & -0.01 & 0.00 & 0.01 & 0.05 & -0.02 \\ 
+  Hedges g: Random - Copas & -0.14 & 0.00 & 0.00 & 0.00 & 0.00 & -0.04 \\ 
+  Hedges g: Fixed - Regression & -0.39 & -0.13 & -0.04 & 0.04 & 0.24 & -0.05 \\ 
+  Hedges g: Random - Regression & -0.43 & -0.17 & -0.05 & 0.03 & 0.23 & -0.07 \\ 
+  Log hazard ratio: Fixed - Copas & -0.02 & -0.00 & 0.00 & 0.00 & 0.03 & 0.01 \\ 
+  Log hazard ratio: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.03 & 0.01 \\ 
+  Log hazard ratio: Fixed - Regression & -0.15 & -0.01 & 0.07 & 0.14 & 0.21 & 0.06 \\ 
+  Log hazard ratio: Random - Regression & -0.15 & -0.03 & 0.07 & 0.15 & 0.23 & 0.06 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects.
+The row names indicate which outcome measure, meta-analysis and adjustment method is used}
+\label{adjustment.difference}
+\end{table}
+
+\subsection{Change in Evidence for Treatment Effects}
+Adjustment for small study effects in meta-analysis will not only provide new effect sizes, but also standard errors thereof.
+Thus, also the evidence for efficacy of a treatment can be obtained, which is usually summarized in a suitable test statistic or $p$-value.
+\\
+The wald test statistics $p$-value for fixed and random effects meta-analyses and copas and regression adjusted treatment effects have been calculated.
+They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and log hazard ratio.
+The $p$-values get larger changing from fixed effects to random effects, and from Copas to regression adjusted $p$-values for $z$-scores and Hedges $g$.
+Also, they are larger for Hedges $g$ based meta-analyses compared to $z$-score based meta-analyses.
+Meanwhile, they stay approximately equal for log odds ratios, with the exception of regression adjusted test statistics.
+Thus, after adjusting for small study effects, the evidence for treatment efficacy shrinks at least partially, which is also indicated by the smaller number of significant $p$-values (0.05 threshold).
+Note that while $z$-score and Hedges $g$ based meta-analyses use the same data, only with different effect measure transformations, this is not true for meta-analyses based on log odds ratios.\\
+%Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
+%Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted Hedges $g$ and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-16-1}
+
+}
+
+\end{knitrout}
+\caption{Histogram of the wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
+The method is indicated in the header, binwidth is set to 0.05.
+The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
+\label{fig:adjustment.stat}
+\end{figure}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% \section{Small study effects}
+% <<echo=FALSE, warning=FALSE>>=
+% p.samplesize.z  <- data.ext2 %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% ungroup() %>% 
+%   mutate(std.z = abs(z), sample.size = total1 + total2) %>%
+%   group_by(sample.size) %>% 
+%   summarize(median.effect = median(std.z, na.rm = T)) %>% 
+%   ggplot(aes(x = sample.size, y = median.effect)) + geom_point(size = 0.8) + 
+%   theme_bw() + xlab("sample size") + ylab("median absolute z-score") +
+%   xlim(c(15, 300)) + ylim(c(0, 0.25)) +
+%   scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
+% 
+% p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% 
+%   filter(outcome.measure.new == "Risk Ratio" | 
+%            outcome.measure.new == "Odds Ratio" | 
+%            outcome.measure.new == "Mean Difference" |
+%            outcome.measure.new == "Std. Mean Difference") %>% 
+%   group_by(outcome.measure.new) %>% 
+%   mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
+%   group_by(sample.size, outcome.measure.new) %>% 
+%   summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
+%   ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point(size = .5) + facet_wrap(~outcome.measure.new, scales = "free") + 
+%   theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size") +
+%   xlim(c(15, 300)) +
+%   scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
+% @
+% 
+% The median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
+It is clearly visible that the absolute value decreases with increasing sample size, i.e.
+that the effect size is becoming smaller.
+The trend flattens off after $\sim$ sample size = 400 (not shown).
+% -- Appendix -- \\
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(p.samplesize.z)
+% @
+% \caption{Median of the absolute $z$-score plotted against the total sample size.}
+% \label{z.samplesize}
+% \end{figure}
+% 
+% Only for illustration, the same trend is reproduced in Figure \ref{effect.samplesize.separated} with a similar method, using the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std.
+Mean Difference'' (the most commonly used in the dataset).
+The ``normalized effect'' is the original effect size, normalized with respect to all other effect sizes of the same measure (i.e.
+subtraction of mean and division through standard error of the mean).
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% plot(p.samplesize.effect.sep)
+% @
+% \caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
+% \label{effect.samplesize.separated}
+% \end{figure}
+% 
+% %Show absolute effect size depending on scaled time? Chunck 3
+
+% Since the tests have different properties, the agreement between the tests can be visualized.
+Here, agreement is specified as classifying the same meta-analysis as significant, based on the 0.1 $p$-value threshold.
+Again, this is done separately for the different outcome types.
+The result can be seen in Figure \ref{fig:test.agreement}.
+In the Figure, the number of agreeing tests is displayed, i.e., how many meta-analyses had only one significant test result etc.
+% 
+% \begin{figure}
+% <<echo = FALSE, fig.height = 5>>=
+% grid.arrange(agree.bin,
+%               agree.cont, 
+%               agree.surv, ncol = 1)
+% @
+% \caption{Barplot for the number of significant test results per meta-analyses, separated for outcome.types}
+% \label{fig:test.agreement}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% <<echo=FALSE>>=
+% plot(p.dist.bin)
+% @
+% \caption{Histogram of the $p$-values for small study effect in binary outcome meta-analyses.
 The testing method is indicated in the header, binwidth is equal to 0.1.
 The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-\label{fig:test.cont}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-15-1}
-
-\end{knitrout}
-\caption{Histogram of the $p$-values for the small study effect in survival outcome meta-analyses.
+% \label{fig:test.bin}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% plot(p.dist.cont)
+% @
+% \caption{Histogram of the $p$-values for the small study effect in continuous outcome meta-analyses.
 The testing method is indicated in the header, binwidth is equal to 0.1.
 The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-\label{fig:test.surv}
-\end{figure}
-
-\subsection{}
+% \label{fig:test.cont}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% plot(p.dist.surv)
+% @
+% \caption{Histogram of the $p$-values for the small study effect in survival outcome meta-analyses.
+The testing method is indicated in the header, binwidth is equal to 0.1.
+The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
+% \label{fig:test.surv}
+% \end{figure}
+
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(adjustment.stat.z)
+% @
+% \caption{Histogram of the wald test-statistic of meta-analysis and adjusted pooled treatment effect, based on the z-score.
+The method is indicated in the header, binwidth is set to 1.
+The significant proportion based on the threshold of 0.05 is displayed inside the figures (The red line displays the corresponding quantile of the std.
+normal, 1.96).}
+% \label{fig:adjustment.stat.z}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(adjustment.stat.d)
+% @
+% \caption{Histogram of the wald test-statistic of meta-analysis and adjusted pooled treatment effect, based on Hedges $g$ or Cohen's $d$.
+The method is indicated in the header, binwidth is set to 1.
+The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
+% \label{fig:adjustment.stat.d}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(adjustment.stat.log.hazard.ratio)
+% @
+% \caption{Histogram of the wald test-statistic of meta-analysis and adjusted pooled treatment effect, based on the $z$-score.
+The method is indicated in the header, binwidth is set to 1.
+The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
+% \label{fig:adjustment.stat.log.hazard.ratio}
+% \end{figure}
 
@@
 
+\section{Excess Significance Test}
+\citet{excess.significance} developped an exploratory test to detect if the proportion of significant findings is larger than expected.
+Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study.
+\\
+We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated as for example by fixed effects Meta-Analysis \ref{eq:fixed.effects}.
+Let $O$ be the number of significant study results out of $n$ studies and $\alpha$ the significance threshold.
+Corresponding to the study effect $\theta_i$, we can specify the power $1 - \beta_i$, the probability to accepting a true result.
+Let $z_{\alpha,i}$ be the $1-\alpha$ quantile of a normal distribution with standard error $\hat{s}_i$.
+The power of study $i$ can be estimated as:
+
+\begin{align}
+1 - \hat{\beta}_i &= F(z_\alpha) 
+\end{align}
+
+with $F$ being the cumulative distribution of a normal with mean $\hat{\theta}_M$ and standard deviation $\hat{s}_i$. \\
+If we assume no bias in $\theta_i, \theta_M$, the expected number of significant study results is then just
+
+\begin{align}
+E &= \sum_{i = 1}^n (1 - \beta_i) \nonumber
+\end{align}
+
+$E$ can then be compared to $O$ by constructing a test statistic $\chi$:
+
+\begin{align}
+\chi  &= \big( \frac{(O - E)^2}{E} + \frac{(O - E)^2}{n - E}\big) \nonumber
+\end{align}
+
+and consecutively, calculating a $p$-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
+Alternatively, one can also use a binomial proportion test, which tests if the probability of significance is the same as expected.
+A simple Wald test statistic $Z$ is given by:
+
+\begin{align}
+Z = \frac{O/n - E/n}{\sqrt{(O/n(1-O/n))/n}}
+\end{align}
+
+The one sided $p$-value for the alternative hypothesis $O/n > E/n$ is
+
+\begin{align}
+p &= 1 - \Phi(Z) \nonumber
+\end{align}
+
+with $\Phi$ being the cumulative distribution function of a standard normal. \citet{excess.significance} propose it to be more suitable if $n$ is small.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Small study effect and Publication Bias Adjustment}
+\section{Small Study Effect and Publication Bias Adjustment}
 There are different approaches to correct for small study effects and publication bias.

### 2019-06-24 report/chapter02.Rnw
Results first draft

@@
 \begin{itemize}
-\item \textbf{study.year}: It was assumed that studies that are declared to have been published before 1920 ($n$ = \Sexpr{length(which(data$study.year < 1920))}) are mis-specified, as well as after 2019 ($n$ = \Sexpr{length(which(data$study.year > 2019))}), so these have been set to NA.
-\item \textbf{mean1} and \textbf{mean2}: When both ``mean1'' and ``mean2'' are equal to zero or NA, ``outcome.measure.new'' is equal to ``(Std.) Mean Difference'', but a mean difference is given in ``effect'', ``mean1'' is set equal to ``effect'' ($n$ = \Sexpr{length(nomeans.ind)}).
+\item \texttt{study.year}: It was assumed that studies that are declared to have been published before 1920 ($n$ = \Sexpr{length(which(data$study.year < 1920))}) are mis-specified, as well as after 2019 ($n$ = \Sexpr{length(which(data$study.year > 2019))}), so these have been set to NA.
+\item \texttt{mean1} and \texttt{mean2}: When both \texttt{mean1} and \texttt{mean2} are equal to zero or NA, \texttt{outcome.measure.new} is equal to \texttt{(Std.) Mean Difference}, but a mean difference is given in \texttt{effect}, \texttt{mean1} is set equal to \texttt{effect} ($n$ = \Sexpr{length(nomeans.ind)}).
 \end{itemize}
@@
 \begin{itemize}
-\item \textbf{outcome.measure.new}: Outcome measure specifications given in ``outcome.measure'' were standardized whenever they were supposed to denote the same outcome measure.
+\item \texttt{outcome.measure.new}: Outcome measure specifications given in \texttt{outcome.measure} were standardized whenever they were supposed to denote the same outcome measure.
 An example would be the formally different notations for odds ratios: ``Odds Ratio'', ``odds ratio'', ``OR'', which were all denoted as ``Odds Ratio''.
-\item \textbf{outcome.type}: A simplification of ``outcome.measure.new''.
-The outcome.type ``bin'' indicates if ``outcome.measure.new'' is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
-``cont'' is equivalent to ``outcome.measure.new'' equal to "Std.
+\item \texttt{outcome.type}: A simplification of \texttt{outcome.measure.new}.
+The outcome.type ``bin'' indicates if \texttt{outcome.measure.new} is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
+``cont'' is equivalent to \texttt{outcome.measure.new} equal to "Std.
 Mean Difference'' or ``Mean Difference''.
 ``surv'' equal to ``Hazard Ratio'' and ``rate'' equal to ''Rate Ratio'' or ``Rate Difference''.
-\item \textbf{lrr} and \textbf{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.type ``bin''.
-\item \textbf{smd} and \textbf{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.type ``cont''.
-If not computable from ``mean1'', ``mean2'', ``sd1'' and ``sd2'', and ``outcome.measure.new'' was equal to ``Std.
-Mean Difference'', it was set equal to ``effect'' (and ``var.smd'' equal to ``se'' squared, $n$ =  \Sexpr{length(inpute.given.ind)}).
-\item \textbf{smd.ordl} and \textbf{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.type ``bin''.
-\item \textbf{cor.Pearson} and \textbf{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.type ``bin'') or $g$ (for outcome.type ``cont'') to $r$ transformation.
-\item \textbf{z} and \textbf{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
-\item \textbf{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.type ``cont'' or Wald test for outcome.type ``bin''.
-\item \textbf{events1c} and \textbf{events2c}: Correction of ``events1'' and ``events2'' zero event counts or event counts = patient number.
+\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.type ``bin''.
+\item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.type ``cont''.
+If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.new} was equal to ``Std.
+Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  \Sexpr{length(inpute.given.ind)}).
+\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.type ``bin''.
+\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.type ``bin'') or $g$ (for outcome.type ``cont'') to $r$ transformation.
+\item \texttt{z} and \texttt{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
+\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.type ``cont'' or Wald test for outcome.type ``bin''.
+\item \texttt{events1c} and \texttt{events2c}: Correction of \texttt{events1} and \texttt{events2} zero event counts or event counts = patient number.
 When no events occurred, 0.5 was added, and when all patients experienced the event, 0.5 was subtracted.
-When one of ``events'' had zero counts while the other had maximum counts, no adjustment occurred.
-\item \textbf{meta.id}: Meta-analysis ID variable to uniquely identify any potential meta-analysis in the dataset.
+When one of \texttt{events} had zero counts while the other had maximum counts, no adjustment occurred.
+\item \texttt{meta.id}: Meta-analysis ID variable to uniquely identify any potential meta-analysis in the dataset.
 Consistent to what has been discussed before, all results that share a common comparison, outcome and subgroup (optional, subgroups not given in any case) may be combined in a meta-analysis.
-% \item \textbf{}:
-% \item \textbf{}:
+% \item \texttt{}:
+% \item \texttt{}:
 \end{itemize}
 
-\subsection{Eligibility criteria for Publication Bias Test and Adjustment} \
+\subsection{Eligibility criteria for Publication Bias Test and Adjustment} 
 Initially, the analysis is restricted to binary, continuous and survival outcomes. More formally:
 \begin{itemize}
-\item \textbf{Outcome measures}: The analysis has been restricted on the following outcome measures (from ``outcome.measure.new''): ``Odds Ratio'', ``Risk Ratio'', ``Risk difference'', ``Peto Odds Ratio'', ``Std.
+\item \textbf{Outcome measures}: The analysis has been restricted on the following outcome measures (from \texttt{outcome.measure.new}): ``Odds Ratio'', ``Risk Ratio'', ``Risk difference'', ``Peto Odds Ratio'', ``Std.
 Mean Difference'', ``Mean Difference'', ``Hazard Ratio''
@@
 \begin{itemize}
+\item \textbf{Sensitivity Analyses}: When the same results are used multiple times for different meta-analyses, only one is retained.
+More precisely, if a study hat the same \texttt{study.name} and same \texttt{effect}, it was considered a duplicate, and the smaller meta-analysis of the two was excluded.
+The intention is to exclude sensitivity analyses which are operated on subsets of the available results.
 \item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = \Sexpr{all.zero.events.number} out of meta-analyses with at least ten studies).
@@
 
-There were no issues with ``outcome.type'' ``cont'' and ``surv''.
+There were no issues with \texttt{outcome.type} ``cont'' and ``surv''.
 For the subsequent information, it is important to know that meta-analyses are only repeated with Hedges $g$, Pearson correlation coefficient and Fisher's Z-scores, if the outcome type is not survival and all of the above criteria are met ($n$ = \Sexpr{length(meta.f$n.sig.type[which(meta.f$outcome.type != "surv")])}).

### 2019-06-24 report/chapter03.Rnw
Results first draft

@@
 
-data.ext2 <- pb.process2(data)
+# data.ext2 <- pb.process2(data)
 @
@@
 
-\section{Small study effects}
-<<echo=FALSE, warning=FALSE>>=
-p.samplesize.z  <- data.ext2 %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% ungroup() %>% 
-  mutate(std.z = abs(z), sample.size = total1 + total2) %>%
-  group_by(sample.size) %>% 
-  summarize(median.effect = median(std.z, na.rm = T)) %>% 
-  ggplot(aes(x = sample.size, y = median.effect)) + geom_point(size = 0.8) + 
-  theme_bw() + xlab("sample size") + ylab("median absolute z-score") +
-  xlim(c(15, 300)) + ylim(c(0, 0.25)) +
-  scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
-
-p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% 
-  filter(outcome.measure.new == "Risk Ratio" | 
-           outcome.measure.new == "Odds Ratio" | 
-           outcome.measure.new == "Mean Difference" |
-           outcome.measure.new == "Std. Mean Difference") %>% 
-  group_by(outcome.measure.new) %>% 
-  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
-  group_by(sample.size, outcome.measure.new) %>% 
-  summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
-  ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point(size = .5) + facet_wrap(~outcome.measure.new, scales = "free") + 
-  theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size") +
-  xlim(c(15, 300)) +
-  scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
-@
-
-The median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
-It is clearly visible that the absolute value decreases with increasing sample size, i.e.
-that the effect size is becoming smaller.
-The trend flattens off after $\sim$ sample size = 400 (not shown).
--- Appendix --
-
-\begin{figure}
-<<echo=FALSE, warning=FALSE>>=
-plot(p.samplesize.z)
-@
-\caption{Median of the absolute $z$-score plotted against the total sample size.}
-\label{z.samplesize}
-\end{figure}
-
-Only for illustration, the same trend is reproduced in Figure \ref{effect.samplesize.separated} with a similar method, using the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std.
-Mean Difference'' (the most commonly used in the dataset).
-The ``normalized effect'' is the original effect size, normalized with respect to all other effect sizes of the same measure (i.e.
-subtraction of mean and division through standard error of the mean).
-
-\begin{figure}
-<<echo=FALSE>>=
-plot(p.samplesize.effect.sep)
-@
-\caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
-\label{effect.samplesize.separated}
-\end{figure}
-
-%Show absolute effect size depending on scaled time? Chunck 3
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Small Study Effect Tests}
+\section{Small Study Effect and Excess of Singificance Tests}
 <<echo=FALSE, warning=FALSE>>=
@@
 				 begg.test = ifelse(pval.begg < sig.level, 1, 0),
+
+				 tes.d.test = ifelse(pval.d.tes < sig.level, 1, 0),
 
@@
   label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
-									sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test)), "< 0.1,",
+                  sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test), sum(meta.bin$tes.d.test, na.rm = T)), "< 0.1,",
                 round(c(mean(meta.bin$harbord.test), mean(meta.bin$peter.test), 
-												mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test)),2)*100, "%"),
-	test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer"))
-
-labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer")
+                        mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test), mean(meta.bin$tes.d.test, na.rm = T)),2)*100, "%"),
+  test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer", "pval.d.tes"))
+
+labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer", pval.d.tes = "Excess Significance")
 
 p.dist.bin <- meta.bin %>% ungroup() %>% 
-	select(pval.harbord, pval.peter, pval.rucker, pval.schwarzer) %>% 
+  select(pval.harbord, pval.peter, pval.rucker, pval.schwarzer, pval.d.tes) %>% 
   gather(key = "test.type", value = "p.value") %>% 
   ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 300, label = label), color = "black") + 
-	theme(strip.text.x = element_text(size=10))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Survival Outcomes:
+  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 250, label = label), color = "black") + 
+  theme(strip.text.x = element_text(size=7)) + ggtitle("Binary Outcomes")
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Continuous Outcomes:
 test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
@@
 dat_text <- data.frame(
-	label = paste(c(sum(meta.cont$begg.test), sum(meta.cont$egger.test), sum(meta.cont$thompson.test)), "< 0.1,",
-								round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test)),2)*100, "%"),
-	test.type   = c("pval.begg", "pval.egger", "pval.thompson"))
-
-labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp")
+  label = paste(c(sum(meta.cont$begg.test), sum(meta.cont$egger.test), sum(meta.cont$thompson.test), sum(meta.cont$tes.d.test, na.rm = T)), "< 0.1,",
+                round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test), mean(meta.cont$tes.d.test, na.rm = T)),2)*100, "%"),
+  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"))
+
+labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp", pval.d.tes = "Excess significance")
 p.dist.cont <- meta.cont %>% ungroup() %>% 
-	select(pval.egger, pval.thompson, pval.begg) %>% 
+  select(pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
   gather(key = "test.type", value = "p.value") %>% 
@@
   facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 90, label = label),  color = "black") + 
-	theme(strip.text.x = element_text(size=10))
+  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 60, label = label),  color = "black") + 
+  theme(strip.text.x = element_text(size=7)) + ggtitle("Continuous Outcomes")
 #--------------------------------------------------------------------------------------------------------------------#
@@
 dat_text <- data.frame(
-	label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), sum(meta.surv$thompson.test)), 
-	              "< 0.1,",
-								round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), mean(meta.surv$thompson.test)),2)*100, 
-								"%"),
-	test.type   = c("pval.begg", "pval.egger", "pval.thompson"))
-
-labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp")
+  label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), sum(meta.surv$thompson.test), sum(meta.surv$tes.d.test, na.rm = T)), "< 0.1,",
+                round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), mean(meta.surv$thompson.test), mean(meta.surv$tes.d.test, na.rm = T)),2)*100, "%"),
+  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"))
 p.dist.surv <- meta.surv %>% ungroup() %>% 
-	select(pval.egger, pval.thompson, pval.begg) %>% 
+	select(pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
 	gather(key = "test.type", value = "p.value") %>% 
@@
 	facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 11, label = label),  color = "black") + 
-	theme(strip.text.x = element_text(size=10))
+	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 10, label = label),  color = "black") + 
+	theme(strip.text.x = element_text(size=7)) + ggtitle("Survival Outcomes")
 #--------------------------------------------------------------------------------------------------------------------#
@@
 #--------------------------------------------------------------------------------------------------------------------#
+
+################################################################################################
+################################################################################################
+#PUBLICATION BIAS TEST AGREEMENT
+################################################################################################
+################################################################################################
+
+#Agreement proportions of publication bias tests:
+
+#Binary:
+meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
+																							tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
+																							tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
+																							tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
+																							schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
+																							schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
+																							schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
+																							rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
+																							rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
+																							harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
+agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
+																											tes.d.peter = sum(tes.d.peter == "agree")/n(),
+																											tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
+																											tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
+																											schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
+																											schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
+																											schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
+																											rucker.peter = sum(rucker.peter == "agree")/n(),
+																											harbord.peter = sum(harbord.peter == "agree")/n())
+correlation.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = cor(pval.d.tes, pval.schwarzer),
+																												tes.d.peter = cor(pval.d.tes, pval.peter),
+																												tes.d.rucker = cor(pval.d.tes, pval.rucker),
+																												tes.d.harbord = cor(pval.d.tes, pval.harbord),
+																												schwarzer.peter = cor(pval.schwarzer, pval.peter),
+																												schwarzer.rucker = cor(pval.schwarzer, pval.rucker),
+																												schwarzer.harbord = cor(pval.schwarzer, pval.harbord),
+																												rucker.peter = cor(pval.rucker, pval.peter),
+																												harbord.peter = cor(pval.harbord, pval.peter))
+rsquared.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = summary(lm(pval.d.tes~ pval.schwarzer))$r.squared,
+                                                        tes.d.peter = summary(lm(pval.d.tes~ pval.peter))$r.squared,
+                                                        tes.d.rucker = summary(lm(pval.d.tes~ pval.rucker))$r.squared,
+                                                        tes.d.harbord = summary(lm(pval.d.tes~ pval.harbord))$r.squared,
+                                                        schwarzer.peter = summary(lm(pval.schwarzer~ pval.peter))$r.squared,
+                                                        schwarzer.rucker = summary(lm(pval.schwarzer~ pval.rucker))$r.squared,
+                                                        schwarzer.harbord = summary(lm(pval.schwarzer~ pval.harbord))$r.squared,
+                                                        rucker.peter = summary(lm(pval.rucker~ pval.peter))$r.squared,
+                                                        harbord.peter = summary(lm(pval.harbord~ pval.peter))$r.squared)
+
+binary.tests.agreement <- rbind(agreement.bin, correlation.bin, rsquared.bin)
+rownames(binary.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
+colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
+                                      "Excess significance, Rucker", "Excess significance, Harbord",
+                                      "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
+                                      "Rucker, Peter", "Harbord, Peter")
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Continuous:
+meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
+																								thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
+																								egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
+																								tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
+																								thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
+																								tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
+agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+																												 thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
+																												 tes.d.begg = sum(tes.d.begg == "agree")/n(),
+																												 thompson.egger = sum(thompson.egger == "agree")/n(),
+																												 thompson.begg = sum(thompson.begg == "agree")/n(),
+																												 egger.begg = sum(egger.begg == "agree")/n())
+correlation.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = cor(pval.egger, pval.d.tes),
+																													thompson.tes.d = cor(pval.thompson, pval.d.tes),
+																													tes.d.begg = cor(pval.d.tes, pval.begg),
+																													thompson.egger = cor(pval.thompson, pval.egger),
+																													thompson.begg = cor(pval.thompson, pval.begg),
+																													egger.begg = cor(pval.egger, pval.begg))
+rsquared.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = summary(lm(pval.egger~ pval.d.tes))$r.squared,
+                                                          thompson.tes.d = summary(lm(pval.thompson~ pval.d.tes))$r.squared,
+                                                          tes.d.begg = summary(lm(pval.d.tes~ pval.begg))$r.squared,
+                                                          thompson.egger = summary(lm(pval.thompson~ pval.egger))$r.squared,
+                                                          thompson.begg = summary(lm(pval.thompson~ pval.begg))$r.squared,
+                                                          egger.begg = summary(lm(pval.egger~ pval.begg))$r.squared)
+
+cont.tests.agreement <- rbind(agreement.cont, correlation.cont, rsquared.cont)
+rownames(cont.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
+colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson", 
+                                     "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Survival:
+meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
+                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
+                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
+                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
+                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
+                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
+agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
+                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
+                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
+                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
+                                                         egger.begg = sum(egger.begg == "agree")/n())
+correlation.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = cor(pval.egger, pval.d.tes),
+																													thompson.tes.d = cor(pval.thompson, pval.d.tes),
+																													tes.d.begg = cor(pval.d.tes, pval.begg),
+																													thompson.egger = cor(pval.thompson, pval.egger),
+																													thompson.begg = cor(pval.thompson, pval.begg),
+																													egger.begg = cor(pval.egger, pval.begg))
+rsquared.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = summary(lm(pval.egger~ pval.d.tes))$r.squared,
+                                                          thompson.tes.d = summary(lm(pval.thompson~ pval.d.tes))$r.squared,
+                                                          tes.d.begg = summary(lm(pval.d.tes~ pval.begg))$r.squared,
+                                                          thompson.egger = summary(lm(pval.thompson~ pval.egger))$r.squared,
+                                                          thompson.begg = summary(lm(pval.thompson~ pval.begg))$r.squared,
+                                                          egger.begg = summary(lm(pval.egger~ pval.begg))$r.squared)
+
+surv.tests.agreement <- rbind(agreement.surv, correlation.surv, rsquared.surv)
+rownames(surv.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
+colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)", 
+                                    "Excess significance, Begg (survival)", "Thompson, Egger (survival)", 
+                                    "Thompson, Begg (survival)", "Egger, Begg (survival)")
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Merging:
+test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
+
+#--------------------------------------------------------------------------------------------------------------------#
+
 @
 
-The results of the test for small study effects for the meta-analyses fullfilling the criteria from chapter \ref{chapter01}, section \ref{sec:Processing}, are presented in Figures \ref{fig:test.bin}, \ref{fig:test.cont} and \ref{fig:test.surv}.
-The histogram of the $p$-values appears most often skewed to the right, indicating evidence for small study effects.
-Because different tests are applied depending on outcome type, the results are displayed separately for binary, continuous and survival outcome types (as previously defined in the dataset variable ``outcome.type'', see chapter \ref{ch:chapter01}, section \ref{sec:Processing}.
+The results of the test for small study effects and excess of significance for the meta-analyses fullfilling the criteria from chapter \ref{chapter02}, section \ref{sec:Processing}, are presented in Figure \ref{fig:test}.
+%Figures \ref{fig:test.bin}, \ref{fig:test.cont} and \ref{fig:test.surv}. 
+The histogram of the $p$-values is displayed separately for binary, continuous and survival outcome types (as previously defined in the dataset variable \texttt{outcome.type}, see chapter \ref{ch:chapter02}, section \ref{sec:Processing}.
+The distributions are (with the exception of Schwarzer's test) skewed to the right, indicating evidence for small study effects.
+Moreover, the excess significance tests have a mode around $p = 0.4$.
+Large differences between small study effect tests for binary and continuous outcomes will be subject to discussion.
 \\
-For continuous and survival outcomes, the names refer to:
+``Excess significance'' denotes the excess of significance $p$-values from the test of \citet{excess.significance}. For continuous and survival outcomes, the names refer to:
 
@@
 
-\begin{figure}[!ht]
-<<echo=FALSE>>=
-plot(p.dist.bin)
+\begin{figure}[ht!]
+<<echo=FALSE, fig.height = 9>>=
+grid.arrange(p.dist.bin,
+             p.dist.cont,
+             p.dist.surv, ncol = 1)
 @
-\caption{Histogram of the $p$-values for small study effect in binary outcome meta-analyses.
+\caption{Histogram of the $p$-values for small study effect in meta-analyses.
 The testing method is indicated in the header, binwidth is equal to 0.1.
 The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-\label{fig:test.bin}
+\label{fig:test}
 \end{figure}
 
+The agreement/coinicidence between between small study effect and excess significance tests is often not pronounced, thus, it will be compared by different methods.
+This is displayed in Table \ref{test.agreement}.
+The row names indicate which two tests are compared.
+First, the column ``Test Agreement'' quantifies the overall proportion by which the two tests agree in their rejection or ``acceptance'' of the null-hypothesis.
+``Test Agreement'' being equal one thus indicates equivalent results, zero no correspondence whatsoever.
+The second column, ``Correlation'' gives the correlation between the $p$-values.
+A positive correlation indicates psotive coincidence of $p$-values, negative correlation coincidence in opposite directions.
+However, the scale might be different for this agreement measure.
+The ``R-squared'' value indicates to what extent one $p$-value can be predicted by another, and ignores additive differences between $p$-values (as for correlation), as well as multiplicative constants between them (i.e.
+$y ~ a + b*x$, $y$ and $x$ being two $p$-values of test-statistics).
+An R-squared value of 1 indicates perfect fit.
+Importantly, the order of the variables does not matter for the $p$-values for all indicators (i.e.
+$p$-values for $x$ and $y$ can be exchanged and the table stays the same).
+If a test is completely replaceable by another, all values in a row are equal to one.
+
+<<echo=FALSE, results='asis'>>=
+print(xtable(test.agreement, align = "lccc", caption = "Agreement in significance proportion, correlation and R-squared of linear regression
+             between the p-values of the publication bias tests. Horizontal lines separate binary, continuous and survival outcomes (order as in table).",
+             label = "test.agreement"), hline = c(0,0,9, 15, 21), size = "footnotesize")
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small Study Effects Adjustment}
+<<echo=FALSE, warning=FALSE, message=FALSE>>=
+#HISTOGRAMS:
+
+#Comparison of treatment effect p-values:
+sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+                              z.ranef = est.z.ranef/se.est.z.ranef,
+                              z.reg = est.z.reg/se.est.z.reg,
+                              z.copas = est.z.copas/se.est.z.copas) %>%  
+  select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>% 
+  mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>% 
+  group_by(method) %>% 
+  summarise(significant = length(which(abs(fisher.z) > 1.96)),
+            p.significant = significant/length(fisher.z))
+sig.zcor <- data.frame(method = sig.zcor$method,
+                       label = paste(round(sig.zcor$p.significant,3)*100, "% significant", ", (n = ", sig.zcor$significant, ")", sep = ""))
+
+method_names <- c(
+  z.fixef = "Fixed Effects",
+  z.ranef = "Random Effects",
+  z.reg = "Regression",
+  z.copas = "Copas"
+)
+
+adjustment.p.z <- meta.f %>% 
+  mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+         z.ranef = est.z.ranef/se.est.z.ranef,
+         z.reg = est.z.reg/se.est.z.reg,
+         z.copas = est.z.copas/se.est.z.copas) %>%  
+  select(z.fixef, z.ranef, z.reg, z.copas) %>% 
+  gather(key = "method", value = "fisher.z") %>% 
+  mutate(method = factor(method, levels = c("z.fixef", "z.ranef", "z.reg", "z.copas"))) %>% 
+  mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>% 
+  ggplot(aes(x = p.fisher.z)) + 
+  geom_histogram(boundary = 0, bins = 20) + 
+  theme_bw() + 
+  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+  geom_text(data = sig.zcor, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
+  xlab(expression(paste(italic(p),"-value of test statistic of the ", italic(z),"-score"))) +
+  ggtitle(expression(paste(italic(z), " Score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Comparison of SMD's:
+sig.d <- meta.f %>% mutate(d.fixef = est.d.fixef/se.est.d.fixef,
+                           d.ranef = est.d.ranef/se.est.d.ranef,
+                           d.reg = est.d.reg/se.est.d.reg,
+                           d.copas = est.d.copas/se.est.d.copas) %>%  
+  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+  group_by(method) %>% 
+  summarise(significant = length(which(abs(smd) > 1.96)),
+            p.significant = significant/length(smd))
+sig.d <- data.frame(method = sig.d$method,
+                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
+
+method_names <- c(
+  d.fixef = "Fixed Effects",
+  d.ranef = "Random Effects",
+  d.reg = "Regression",
+  d.copas = "Copas"
+)
+
+adjustment.p.d <- meta.f %>% 
+  mutate(d.fixef = est.d.fixef/se.est.d.fixef,
+         d.ranef = est.d.ranef/se.est.d.ranef,
+         d.reg = est.d.reg/se.est.d.reg,
+         d.copas = est.d.copas/se.est.d.copas) %>%  
+  select(d.fixef, d.ranef, d.reg, d.copas) %>% 
+  gather(key = "method", value = "smd") %>% 
+  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
+  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+  ggplot(aes(x = p.smd)) + 
+  geom_histogram(boundary = 0, bins = 20) + 
+  theme_bw() + 
+  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+  geom_text(data = sig.d, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
+  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
+  ggtitle(expression(paste("Hedges ", italic(g), " ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Comparison of log hazard ratios:
+sig.d <- meta.f %>% filter(outcome.type == "surv") %>% 
+  mutate(d.fixef = est.fixef/se.est.fixef,
+         d.ranef = est.ranef/se.est.ranef,
+         d.reg = est.reg/se.est.reg,
+         d.copas = est.copas/se.est.copas) %>%  
+  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+  group_by(method) %>% 
+  summarise(significant = length(which(abs(smd) > 1.96)),
+            p.significant = (significant + sum(is.na(smd)))/(length(smd)))
+sig.d <- data.frame(method = sig.d$method,
+                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
+
+method_names <- c(
+  d.fixef = "Fixed Effects",
+  d.ranef = "Random Effects",
+  d.reg = "Regression",
+  d.copas = "Copas"
+)
+
+adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.type == "surv") %>% 
+  mutate(d.fixef = est.fixef/se.est.fixef,
+         d.ranef = est.ranef/se.est.ranef,
+         d.reg = est.reg/se.est.reg,
+         d.copas = est.copas/se.est.copas) %>%  
+  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
+  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+  ggplot(aes(x = p.smd)) + 
+  geom_histogram(boundary = 0, bins = 20) + 
+  theme_bw() + 
+  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+  geom_text(data = sig.d, aes(x = 0.00003, y = 20, label = label), position = "dodge") + 
+  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
+  ggtitle(expression(paste("Log hazard ratio ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Meta-Analysis and adjusted treatment effect estimate difference:
+
+#Z-score:
+diff.z.fixef <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+                  copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+    fixef = abs(fixef),
+    ranef = abs(ranef)) %>% 
+  select(fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
+  mutate(difference = fixef - adjusted.z.score) %>% 
+  filter(difference > -.75 & difference < .75) %>% 
+  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
+  facet_wrap(~method) + theme_bw() + 
+  xlab(expression(paste("Fixed effects - adjusted ", z, "-score")))
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.z.ranef <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
+  mutate(difference = ranef - adjusted.z.score) %>% 
+  filter(difference > -.75 & difference < .75) %>% 
+  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
+  facet_wrap(~method) + theme_bw() + 
+  xlab(expression(paste("Random effects - adjusted ", z, "-score")))
+#--------------------------------------------------------------------------------------------------------------------#
+
+#SMD:
+diff.d.fixef <- meta.f %>% 
+  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
+         copas = est.d.copas, regression = est.d.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
+  mutate(difference = fixef - adjusted.smd) %>% 
+  filter(difference > -1 & difference < 1) %>% 
+  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
+  facet_wrap(~method) + theme_bw() + 
+  xlab(expression(paste("Fixed effects - adjusted Hedges ", g)))
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.d.ranef <- meta.f  %>% 
+  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
+         copas = est.d.copas, regression = est.d.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
+  mutate(difference = ranef - adjusted.smd) %>% 
+  filter(difference > -1 & difference < 1) %>% 
+  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
+  facet_wrap(~method) + theme_bw() + 
+  xlab(expression(paste("Random effects - adjusted Hedges ", g)))
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Log hazard ratios:
+diff.log.hazard.ratio.fixef <- meta.surv %>% 
+  mutate(fixef = est.fixef, ranef = est.ranef,
+         copas = est.copas, regression = est.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
+  ggplot(aes(x = (fixef - adjusted.log.hazard.ratio))) + 
+  geom_histogram(binwidth = 0.1, center = 0) +
+  facet_wrap(~method) + theme_bw() + xlab("Fixed effects - adjusted log hazard ratio")
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.log.hazard.ratio.ranef <- meta.surv %>% 
+  mutate(fixef = est.fixef, ranef = est.ranef,
+         copas = est.copas, regression = est.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
+  ggplot(aes(x = (ranef - adjusted.log.hazard.ratio))) + 
+  geom_histogram(binwidth = 0.1, center = 0) +
+  facet_wrap(~method) + theme_bw() + xlab("Random effects - adjusted log hazard ratio")
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Quantile and mean table of differences:
+adjustment.diff <- meta.f %>% 
+  transmute(est.d.copas.f = case_when(sign(est.d.copas) == sign(est.d.fixef) ~  abs(est.d.copas),
+                           sign(est.d.copas) != sign(est.d.fixef) ~ -abs(est.d.copas)),
+         est.d.reg.f = case_when(sign(est.d.reg) == sign(est.d.fixef) ~  abs(est.d.reg),
+                                sign(est.d.reg) != sign(est.d.fixef) ~ -abs(est.d.reg)),
+         est.d.copas.r = case_when(sign(est.d.copas) == sign(est.d.ranef) ~  abs(est.d.copas),
+                                   sign(est.d.copas) != sign(est.d.ranef) ~ -abs(est.d.copas)),
+         est.d.reg.r = case_when(sign(est.d.reg) == sign(est.d.ranef) ~  abs(est.d.reg),
+                                 sign(est.d.reg) != sign(est.d.ranef) ~ -abs(est.d.reg)),
+
+         est.z.copas.f = case_when(sign(est.z.copas) == sign(est.z.fixef) ~  abs(est.z.copas),
+                                   sign(est.z.copas) != sign(est.z.fixef) ~ -abs(est.z.copas)),
+         est.z.reg.f = case_when(sign(est.z.reg) == sign(est.z.fixef) ~  abs(est.z.reg),
+                                 sign(est.z.reg) != sign(est.z.fixef) ~ -abs(est.z.reg)),
+         est.z.copas.r = case_when(sign(est.z.copas) == sign(est.z.ranef) ~  abs(est.z.copas),
+                                   sign(est.z.copas) != sign(est.z.ranef) ~ -abs(est.z.copas)),
+         est.z.reg.r = case_when(sign(est.z.reg) == sign(est.z.ranef) ~  abs(est.z.reg),
+                                 sign(est.z.reg) != sign(est.z.ranef) ~ -abs(est.z.reg)),
+
+         est.z.fixef = abs(est.z.fixef),
+         est.z.ranef = abs(est.z.ranef),
+         est.d.fixef = abs(est.d.fixef),
+         est.d.ranef = abs(est.d.ranef)) %>%
+
+  transmute(copas.z.f = est.z.copas.f - est.z.fixef,
+            copas.z.r = est.z.copas.r - est.z.ranef,
+            reg.z.f = est.z.reg.f - est.z.fixef,
+            reg.z.r = est.z.reg.r - est.z.ranef,
+
+            copas.d.f = est.d.copas.f - est.d.fixef,
+            copas.d.r = est.d.copas.r - est.d.ranef,
+            reg.d.f = est.d.reg.f - est.d.fixef,
+            reg.d.r = est.d.reg.r - est.d.ranef)
+
+m.adjustment.diff <- as.matrix(adjustment.diff)
+
+adjustmend.diff.surv <- meta.surv %>% 
+  transmute(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
+                                     sign(est.copas) != sign(est.fixef) ~ -abs(est.copas)),
+            est.copas.r = case_when(sign(est.copas) == sign(est.ranef) ~  abs(est.copas),
+                                     sign(est.copas) != sign(est.ranef) ~ -abs(est.copas)),
+
+            est.reg.f = case_when(sign(est.reg) == sign(est.fixef) ~  abs(est.reg),
+                                     sign(est.reg) != sign(est.fixef) ~ -abs(est.reg)),
+            est.reg.r = case_when(sign(est.reg) == sign(est.ranef) ~  abs(est.reg),
+                                     sign(est.reg) != sign(est.ranef) ~ -abs(est.reg)),
+
+            est.fixef = abs(est.fixef),
+            est.ranef = abs(est.ranef)) %>%
+
+  transmute(copas.surv.f = est.copas.f - est.fixef,
+            copas.surv.r = est.copas.r - est.ranef,
+
+            reg.surv.f = est.reg.f - est.fixef,
+            reg.surv.r = est.reg.r - est.ranef)
+
+m.adjustment.diff.surv <- as.matrix(adjustmend.diff.surv)
+
+adjustment.diff.quantile.table <- apply(m.adjustment.diff, 2, 
+                                        FUN = function(column){quantile(x = column, 
+                                              probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T)})
+adjustment.diff.mean <- apply(m.adjustment.diff, 2, FUN = function(column) mean(column, na.rm = T))
+adjustment.diff.table <- rbind(adjustment.diff.quantile.table, mean = adjustment.diff.mean)
+
+adjustment.diff.quantile.table.surv <- apply(m.adjustment.diff.surv, 2, 
+                                             FUN = function(column){quantile(x = column, 
+                                                   probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T)})
+adjustment.diff.mean.surv <- apply(m.adjustment.diff.surv, 2, FUN = function(column) mean(column, na.rm = T))
+adjustment.diff.table.surv <- rbind(adjustment.diff.quantile.table.surv, mean = adjustment.diff.mean.surv)
+
+adjustment.diff.table <- cbind(adjustment.diff.table, adjustment.diff.table.surv)
+
+adjustment.diff.table <- round(t(adjustment.diff.table), 3)
+
+rownames(adjustment.diff.table) <- c(paste("z-score:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
+                                     paste("Hedges g:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
+                                     paste("Log hazard ratio:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")))
+
+#--------------------------------------------------------------------------------------------------------------------#
+#Meta-Analysis and adjusted treatment effect estimate difference, missing values:
+
+#Z-score:
+missing.z.fixef <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(meta.id, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
+  mutate(difference = fixef - adjusted.z.score) %>% 
+  filter(difference < -.75 | difference > .75) %>% 
+  select(meta.id)
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+missing.z.ranef <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(meta.id, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
+  mutate(difference = ranef - adjusted.z.score) %>% 
+  filter(difference < -.75 | difference > .75) %>% 
+  select(meta.id)
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+#SMD:
+missing.d.fixef <- meta.f %>% 
+  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
+         copas = est.d.copas, regression = est.d.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(meta.id, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
+  mutate(difference = fixef - adjusted.smd) %>% 
+  filter(difference < -1 | difference > 1) %>% select(meta.id)
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+missing.d.ranef <- meta.f %>% 
+  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
+         copas = est.d.copas, regression = est.d.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(meta.id, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
+  mutate(difference = ranef - adjusted.smd) %>% 
+  filter(difference < -1 | difference > 1) %>% select(meta.id)
+
+missing.differences <- rbind(missing.z.fixef, missing.z.ranef, missing.d.fixef, missing.d.ranef)
+missing.differences <- missing.differences %>% distinct(meta.id)
+
+missing.differences <- merge(meta.f[,
+        c("meta.id", "file.nr", "comparison.nr", "subgroup.nr",
+          "est.z.ranef", "est.z.fixef", "est.z.copas", "est.z.reg", 
+          "est.d.fixef", "est.d.ranef", "est.d.copas", "est.d.reg")],
+        missing.differences, by = "meta.id")
+
+missing.differences <- round(missing.differences, 2)
+
+missing.differences <- missing.differences %>% mutate(meta.id = as.character(meta.id), file.nr = as.character(meta.id),
+                                                      comparison.nr = as.character(comparison.nr), subgroup.nr = as.character(subgroup.nr))
+
+colnames(missing.differences) <- c("meta.id", "file.nr", "comparison.nr", "subgroup.nr",
+                                   "z fixed", "z random", "z Copas", "z regression",
+                                   "g fixed", "g random", "g Copas", "g regression")
+@
+
+\subsection{Change in Effect Size after Adjustment}
+
+If one is interested in the mere change in effect size and if the effect size did decrease or increase after adjustment, one can look at Figure \ref{fig:adjustment.size}.
+It displays the difference between the meta-analysis pooled treatment effect and the adjusted treatment effect.
+To compare the overall effect of adjustment for small study effects, the absolute value of the effect size is used.
+Thus, a negative difference indicates larger adjusted treatment effect size than meta-analysis pooled effect size.
+For better illustration, some very large and very small differences have been ommitted in the $z$-score and Hedges $g$ histogramms; the missing differences are provided in Table \ref{missing.differences}.
+Additionally to the histogramms, Table \ref{adjustment.difference} shows the quantiles and means for the various differences.
+%For sake of interpretability, negative effect sizes are changed to positive, such that a negative difference always means that the adjusted treatment effect is larger than the meta-analysis effect.
+Vice versa, a positive difference will indicate smaller adjusted effects.
+\\
+
 \begin{figure}
-<<echo=FALSE>>=
-plot(p.dist.cont)
+<<echo=FALSE, fig.height = 9, warning=FALSE>>=
+grid.arrange(diff.z.fixef, diff.z.ranef,
+             diff.d.fixef, diff.d.ranef,
+             diff.log.hazard.ratio.fixef, diff.log.hazard.ratio.ranef, ncol = 2)
 @
-\caption{Histogram of the $p$-values for the small study effect in continuous outcome meta-analyses.
+\caption{Histogram of the treatment effect differences between meta-analysis and adjusted meta-analysis.
+Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes.
+The bins are centered at zero.}
+\label{fig:adjustment.size}
+\end{figure}
+
+<<echo=FALSE, results='asis'>>=
+print(xtable(missing.differences, 
+             caption = "Missing meta-analysis pooled treatment effect and adjusted treatment effects
+             of Figure \ref{fig:adjustment.size}. Abbreviations are used for z-score (z) and Hedges g (g)", label = "missing.differences", align = "llcccrrrrrrrr"), 
+      include.rownames = F, size = "tiny")
+@
+
+<<echo=FALSE, results='asis'>>=
+print(xtable(adjustment.diff.table, label = "adjustment.difference", caption = "Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects.
+The row names indicate which outcome measure, meta-analysis and adjustment method is used", align = "lcccccc"), include.rownames = T, size = "scriptsize"#, sanitize.text.function=function(x){x}
+      )
+@
+
+\subsection{Change in Evidence for Treatment Effects}
+Adjustment for small study effects in meta-analysis will not only provide new effect sizes, but also standard errors thereof.
+Thus, also the evidence for efficacy of a treatment can be obtained, which is usually summarized in a suitable test statistic or $p$-value.
+\\
+The wald test statistics $p$-value for fixed and random effects meta-analyses and copas and regression adjusted treatment effects have been calculated.
+They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and log hazard ratio.
+The $p$-values get larger changing from fixed effects to random effects, and from Copas to regression adjusted $p$-values for $z$-scores and Hedges $g$.
+Also, they are larger for Hedges $g$ based meta-analyses compared to $z$-score based meta-analyses.
+Meanwhile, they stay approximately equal for log odds ratios, with the exception of regression adjusted test statistics.
+Thus, after adjusting for small study effects, the evidence for treatment efficacy shrinks at least partially, which is also indicated by the smaller number of significant $p$-values (0.05 threshold).
+Note that while $z$-score and Hedges $g$ based meta-analyses use the same data, only with different effect measure transformations, this is not true for meta-analyses based on log odds ratios.\\
+%Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
+%Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted Hedges $g$ and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.
+
+\begin{figure}
+<<echo=FALSE, fig.height = 9, warning=FALSE>>=
+grid.arrange(adjustment.p.z,
+             adjustment.p.d,
+             adjustment.p.log.hazard.ratio, ncol = 1)
+@
+\caption{Histogram of the wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
+The method is indicated in the header, binwidth is set to 0.05.
+The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
+\label{fig:adjustment.stat}
+\end{figure}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% \section{Small study effects}
+% <<echo=FALSE, warning=FALSE>>=
+% p.samplesize.z  <- data.ext2 %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% ungroup() %>% 
+%   mutate(std.z = abs(z), sample.size = total1 + total2) %>%
+%   group_by(sample.size) %>% 
+%   summarize(median.effect = median(std.z, na.rm = T)) %>% 
+%   ggplot(aes(x = sample.size, y = median.effect)) + geom_point(size = 0.8) + 
+%   theme_bw() + xlab("sample size") + ylab("median absolute z-score") +
+%   xlim(c(15, 300)) + ylim(c(0, 0.25)) +
+%   scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
+% 
+% p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% 
+%   filter(outcome.measure.new == "Risk Ratio" | 
+%            outcome.measure.new == "Odds Ratio" | 
+%            outcome.measure.new == "Mean Difference" |
+%            outcome.measure.new == "Std. Mean Difference") %>% 
+%   group_by(outcome.measure.new) %>% 
+%   mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
+%   group_by(sample.size, outcome.measure.new) %>% 
+%   summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
+%   ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point(size = .5) + facet_wrap(~outcome.measure.new, scales = "free") + 
+%   theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size") +
+%   xlim(c(15, 300)) +
+%   scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
+% @
+% 
+% The median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
+It is clearly visible that the absolute value decreases with increasing sample size, i.e.
+that the effect size is becoming smaller.
+The trend flattens off after $\sim$ sample size = 400 (not shown).
+% -- Appendix -- \\
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(p.samplesize.z)
+% @
+% \caption{Median of the absolute $z$-score plotted against the total sample size.}
+% \label{z.samplesize}
+% \end{figure}
+% 
+% Only for illustration, the same trend is reproduced in Figure \ref{effect.samplesize.separated} with a similar method, using the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std.
+Mean Difference'' (the most commonly used in the dataset).
+The ``normalized effect'' is the original effect size, normalized with respect to all other effect sizes of the same measure (i.e.
+subtraction of mean and division through standard error of the mean).
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% plot(p.samplesize.effect.sep)
+% @
+% \caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
+% \label{effect.samplesize.separated}
+% \end{figure}
+% 
+% %Show absolute effect size depending on scaled time? Chunck 3
+
+% Since the tests have different properties, the agreement between the tests can be visualized.
+Here, agreement is specified as classifying the same meta-analysis as significant, based on the 0.1 $p$-value threshold.
+Again, this is done separately for the different outcome types.
+The result can be seen in Figure \ref{fig:test.agreement}.
+In the Figure, the number of agreeing tests is displayed, i.e., how many meta-analyses had only one significant test result etc.
+% 
+% \begin{figure}
+% <<echo = FALSE, fig.height = 5>>=
+% grid.arrange(agree.bin,
+%               agree.cont, 
+%               agree.surv, ncol = 1)
+% @
+% \caption{Barplot for the number of significant test results per meta-analyses, separated for outcome.types}
+% \label{fig:test.agreement}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% <<echo=FALSE>>=
+% plot(p.dist.bin)
+% @
+% \caption{Histogram of the $p$-values for small study effect in binary outcome meta-analyses.
 The testing method is indicated in the header, binwidth is equal to 0.1.
 The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-\label{fig:test.cont}
-\end{figure}
-
-\begin{figure}
-<<echo=FALSE>>=
-plot(p.dist.surv)
-@
-\caption{Histogram of the $p$-values for the small study effect in survival outcome meta-analyses.
+% \label{fig:test.bin}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% plot(p.dist.cont)
+% @
+% \caption{Histogram of the $p$-values for the small study effect in continuous outcome meta-analyses.
 The testing method is indicated in the header, binwidth is equal to 0.1.
 The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-\label{fig:test.surv}
-\end{figure}
-
-\section{Small Study Effects Adjustment}
-When adjusting for small study effects, the newly obtained test statistics, as well as the corrected effect size is of interest.
-The former is displayed in Figures \ref{fig:adjustment.z} for the adjusted $z$-scores, \ref{fig:adjustment.smd} for the adjusted Hedges $g$ and Cohen's $d$ and \ref{fig:adjustment.log.hazard.ratio} for the adjusted log hazard ratios.
+% \label{fig:test.cont}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE>>=
+% plot(p.dist.surv)
+% @
+% \caption{Histogram of the $p$-values for the small study effect in survival outcome meta-analyses.
+The testing method is indicated in the header, binwidth is equal to 0.1.
+The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
+% \label{fig:test.surv}
+% \end{figure}
+
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(adjustment.stat.z)
+% @
+% \caption{Histogram of the wald test-statistic of meta-analysis and adjusted pooled treatment effect, based on the z-score.
+The method is indicated in the header, binwidth is set to 1.
+The significant proportion based on the threshold of 0.05 is displayed inside the figures (The red line displays the corresponding quantile of the std.
+normal, 1.96).}
+% \label{fig:adjustment.stat.z}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(adjustment.stat.d)
+% @
+% \caption{Histogram of the wald test-statistic of meta-analysis and adjusted pooled treatment effect, based on Hedges $g$ or Cohen's $d$.
+The method is indicated in the header, binwidth is set to 1.
+The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
+% \label{fig:adjustment.stat.d}
+% \end{figure}
+% 
+% \begin{figure}
+% <<echo=FALSE, warning=FALSE>>=
+% plot(adjustment.stat.log.hazard.ratio)
+% @
+% \caption{Histogram of the wald test-statistic of meta-analysis and adjusted pooled treatment effect, based on the $z$-score.
+The method is indicated in the header, binwidth is set to 1.
+The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
+% \label{fig:adjustment.stat.log.hazard.ratio}
+% \end{figure}
 

### 2019-06-24 code/analysis_plots.R

@@ -206,6 +206,125 @@ agree.surv <- meta.surv %>% mutate(n.sig = egger.test + thompson.test + begg.tes
   xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")
 #--------------------------------------------------------------------------------------------------------------------#
 
+################################################################################################
+################################################################################################
+#CHANGE OF P VALUES AFTER ADJUSTMENT
+################################################################################################
+################################################################################################
+
+#Comparison of z-scores:
+sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+                              z.ranef = est.z.ranef/se.est.z.ranef,
+                              z.reg = est.z.reg/se.est.z.reg,
+                              z.copas = est.z.copas/se.est.z.copas) %>%  
+  select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>% 
+  mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>% 
+  group_by(method) %>% 
+  summarise(significant = length(which(abs(fisher.z) > 1.96)),
+            p.significant = significant/length(fisher.z))
+sig.zcor <- data.frame(method = sig.zcor$method,
+                       label = paste(round(sig.zcor$p.significant,3)*100, "% significant", ", (n = ", sig.zcor$significant, ")", sep = ""))
+
+method_names <- c(
+  z.fixef = "Fixed Effects",
+  z.ranef = "Random Effects",
+  z.reg = "Regression",
+  z.copas = "Copas"
+)
+
+adjustment.p.z <- meta.f %>% 
+  mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+         z.ranef = est.z.ranef/se.est.z.ranef,
+         z.reg = est.z.reg/se.est.z.reg,
+         z.copas = est.z.copas/se.est.z.copas) %>%  
+  select(z.fixef, z.ranef, z.reg, z.copas) %>% 
+  gather(key = "method", value = "fisher.z") %>% 
[…]

### 2019-06-24 code/tes.R

@@ -14,7 +14,7 @@ tes <- function(yi, sei, alpha, side)
   # statistically significant results
   if (side == "right") { 
     pow <- pnorm(qnorm(alpha, lower.tail = FALSE, sd = sei), mean = est.fe,
-                 sd = sei, lower.tail = FALSE)
+                 sd = sei, lower.tail = FALSE) #Probability to 
     O <- sum(pnorm(yi/sei, lower.tail = FALSE) < alpha)
   } else if (side == "left") {
     pow <- pnorm(qnorm(alpha, sd = sei), mean = est.fe, sd = sei)
@@ -28,5 +28,46 @@ tes <- function(yi, sei, alpha, side)
   pval.tes <- ifelse(pval.tes < 0.5, pval.tes*2, (1-pval.tes)*2)
   
   return(data.frame(A = A, pval.tes = pval.tes, O = O, E = E, n = n))
+  
+}
+
+
+
+data <- data.ext2 %>% filter(meta.id == 168988)
+168988 171006 171029 171032 171592 178208 178210
+tes(ts)
+
+tes <- function(data){
+  yi = data$z
+  sei = sqrt(data$var.z)
+  alpha = 0.05
+  
+  ### FE meta-analysis for statistical power analysis
+  est.fe <- rma(yi = yi, sei = sei, method = "FE")$b[1] 
+  
+  side <- ifelse(sign(est.fe) == -1, "left", "right")
+  
+  ### Compute statistical power and determine the number of observed 
+  # statistically significant results
+  if (side == "right") { 
+    pow <- pnorm(qnorm(alpha, lower.tail = FALSE, sd = sei), mean = est.fe,
+                 sd = sei, lower.tail = FALSE) #Probability to 
+    O <- sum(pnorm(yi/sei, lower.tail = FALSE) < alpha)
+  } else if (side == "left") {
+    pow <- pnorm(qnorm(alpha, sd = sei), mean = est.fe, sd = sei)
+    O <- sum(pnorm(yi/sei) < alpha)
+  }
+  
+  E <- sum(pow) # Expected number of statistically significant result  
+  n <- length(yi) # Number of studies in meta-analysis
+  A <- (O - E)^2/E + (O - E)^2/(n - E) # Compute chi-square statistic
+  pval.chi <- pchisq(A, 1, lower.tail = FALSE) # Compute p-value
[…]

### 2019-06-27 report/MSc_Report.tex
Results update

@@
 
-\chapter{The Cochrane Dataset}
+\chapter{The Cochrane Dataset} \label{ch:dataset}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jun 17 16:15:38 2019
+% Thu Jun 27 15:14:56 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jun 17 16:15:38 2019
+% Thu Jun 27 15:14:57 2019
 \begin{table}[ht]
@@
 
-The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982).
-The median of the publication years is 2003, the mean 2001 and the quartiles are 1996 and 2008.
+The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1983).
+The median of the publication years is 2003, the mean 2001.03 and the quartiles are 1996 and 2008.
 Only a handful ($n = 18$) have been published in 2018, none in 2019.
@@
 
-\chapter{Results}
+\chapter{Results} \label{ch:Results}
 
@@
 
-The results of the test for small study effects and excess of significance for the meta-analyses fullfilling the criteria from chapter \ref{chapter02}, section \ref{sec:Processing}, are presented in Figure \ref{fig:test}.
-%Figures \ref{fig:test.bin}, \ref{fig:test.cont} and \ref{fig:test.surv}. 
-The histogram of the $p$-values is displayed separately for binary, continuous and survival outcome types (as previously defined in the dataset variable \texttt{outcome.type}, see chapter \ref{ch:chapter02}, section \ref{sec:Processing}.
-The distributions are (with the exception of Schwarzer's test) skewed to the right, indicating evidence for small study effects.
+The meta-analyses fullfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with small study effects tests and excess significance tests.
+The $p$-values for all meta-analyses can be displayed in histograms.
+Because the tests are methodologically different, the results of each testing method is displayed separately.
+Furthermore, the outcome types (as defined previously by the variable \texttt{outcome.type}) are also kept separated.\\
+The histograms in Figure \ref{fig:test} show that the distributions are (with the exception of Schwarzer's test) skewed to the right for all outcome types, indicating evidence for small study effects and excess significance.
 Moreover, the excess significance tests have a mode around $p = 0.4$.
-Large differences between small study effect tests for binary and continuous outcomes will be subject to discussion.
-\\
-``Excess significance'' denotes the excess of significance $p$-values from the test of \citet{excess.significance}. For continuous and survival outcomes, the names refer to:
+The large differences between small study effect tests for binary and continuous outcomes will be subject to discussion.\\
+``Excess significance'' denotes the excess of significance $p$-values from the test of \citet{excess.significance}, see \ref{sex:excess.significance}.
+For continuous and survival outcomes, the names refer to:
 
@@
 
-\begin{figure}[ht!]
+\begin{figure}
 \begin{knitrout}
@@
 
-The agreement/coinicidence between between small study effect and excess significance tests is often not pronounced, thus, it will be compared by different methods.
-This is displayed in Table \ref{test.agreement}.
-The row names indicate which two tests are compared.
-First, the column ``Test Agreement'' quantifies the overall proportion by which the two tests agree in their rejection or ``acceptance'' of the null-hypothesis.
-``Test Agreement'' being equal one thus indicates equivalent results, zero no correspondence whatsoever.
-The second column, ``Correlation'' gives the correlation between the $p$-values.
-A positive correlation indicates psotive coincidence of $p$-values, negative correlation coincidence in opposite directions.
-However, the scale might be different for this agreement measure.
-The ``R-squared'' value indicates to what extent one $p$-value can be predicted by another, and ignores additive differences between $p$-values (as for correlation), as well as multiplicative constants between them (i.e.
-$y ~ a + b*x$, $y$ and $x$ being two $p$-values of test-statistics).
-An R-squared value of 1 indicates perfect fit.
-Importantly, the order of the variables does not matter for the $p$-values for all indicators (i.e.
-$p$-values for $x$ and $y$ can be exchanged and the table stays the same).
-If a test is completely replaceable by another, all values in a row are equal to one.
+%Agreement table -> Chunck 1
+
+It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects/excess significance for the same meta-analyses.
+Especially between small study effects and excess significance tests, we expect some disagreement between tests.
+A simple method to check the coincidence of test results is to compare scatterplots and empirical spearman correlations between test statistics.
+This is done in Figure \ref{fig:test.agreement}.
+\\
+Here, there is no separation between survival and continuous outcomes. The upper left rectangle is displaying binary outcomes and the lower right about continuous and survival outcomes.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-11-1}
+
+}
+
+\end{knitrout}
+\caption{Pairs-plot for test statistics of small study effect and excess significance.
+The lower panel gives the spearman correlations for the different test statistics, and the upper panel displays a scatterplot.
+The colours indicate magnitude and direction of the correlation coefficients.
+The rectangle with white borders displays the area within which both tests have absolute value < 1.96.}
+\label{fig:test.agreement}
+\end{figure}
+
+The observed patterns on the scatterplots differ: Excess significance and small study effect test statistics do usually not align with each other, forming rather randomly scattered bulks of points.
+Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is also reflected in large correlation coefficients.
+In general, small study effect tests align, but the extent to which they align differs.
+Harbord's test statistic has similar correlation coefficients with all other small study effect test statistics for binary outcomes, while the correlation coefficients between them is varying.\\
+Because scatterplots and correlation coefficients can be missleading, also a Tukey mean-difference or Bland-Altmann plot is shown for three scenarios in Figure \ref{fig:mean.diff.test}:
+\begin{itemize}
+\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
+\item For Harbord's and Rucker's tests
+\item For Harbord's and excess significance tests
+\end{itemize}
+
+This can be justified since all tests are supposed to measure the evidence for publication bias.
+For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation.
+The mean $p$-value ((logit($p$-value 1) + logit($p$-value 2))/2) is then displayed against the differnec between the $p$-value.
+If no systematic errors and biases exist between the measurement methods, then
+
+\begin{itemize}
+\item the mean of the differences (systematic error) should be around zero
+\item the points should scatter independent of the mean of the $p$-values
+\end{itemize}
+
+The last criterium seems not to be given when comparing Harbords and Excess significance tests. 
+-- In the appendix, it can be seen that this is reproducible with the remainig small study effect tests (not there yet) -- 
+With decreasing mean, the difference gets more negative, and vice versa, such that one would predict that the excess significance $p$-values are more ``extreme'' in both directions.
+This finding suggests that correspondence between the tests is poor.
+The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger and Thompson test, and around 0.99 for Harbord and Rucker.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-12-1}
+
+}
+
+\end{knitrout}
+\caption{Mean - difference plots for logit transformed $p$-values.
+The mean of logit transformed $p$-values is displayed on the $x$-axis and the difference on the $y$-axis.
+Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).}
+\label{fig:mean.diff.test}
+\end{figure}
+
+The previous results suggest that the results will also differ substantially after applying the common dichotomization of $p$-values.
+We expect that some proportion of the meta-analysis will only be significant for a certain test, and this is indeed observed in Table \ref{number.sig.tests}.
+It displays the percentage of meta-analyses with a certain number of significant test results.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jun 24 17:05:43 2019
+% Thu Jun 27 15:14:57 2019
 \begin{table}[ht]
@@
 \begingroup\footnotesize
-\begin{tabular}{lccc}
-  & Test Agreement & p-value Correlation & p-value R-squared \\ 
+\begin{tabular}{ccc}
   \hline
+Count & Binary Outcomes & Continuous and Survival \\ 
   \hline
-Excess significance, Schwarzer & 0.83 & -0.02 & 0.00 \\ 
-  Excess significance, Peter & 0.80 & 0.05 & 0.00 \\ 
-  Excess significance, Rucker & 0.82 & 0.12 & 0.02 \\ 
-  Excess significance, Harbord & 0.81 & 0.02 & 0.00 \\ 
-  Peter, Schwarzer & 0.82 & 0.29 & 0.09 \\ 
-  Schwarzer, Rucker & 0.82 & 0.29 & 0.08 \\ 
-  Schwarzer, Harbord & 0.86 & 0.51 & 0.26 \\ 
-  Rucker, Peter & 0.89 & 0.64 & 0.41 \\ 
-  Harbord, Peter & 0.86 & 0.48 & 0.23 \\ 
-   \hline
-Excess significance, Egger & 0.79 & 0.14 & 0.02 \\ 
-  Excess significance, Thompson & 0.80 & 0.16 & 0.02 \\ 
-  Excess significance, Begg & 0.81 & 0.10 & 0.01 \\ 
-  Thompson, Egger & 0.95 & 0.91 & 0.83 \\ 
-  Thompson, Begg & 0.87 & 0.70 & 0.49 \\ 
-  Egger, Begg & 0.86 & 0.65 & 0.42 \\ 
-   \hline
-Excess significance, Egger (survival) & 0.69 & 0.03 & 0.00 \\ 
-  Excess significance, Thompson (survival) & 0.64 & 0.05 & 0.00 \\ 
-  Excess significance, Begg (survival) & 0.62 & 0.18 & 0.03 \\ 
-  Thompson, Egger (survival) & 0.90 & 0.92 & 0.85 \\ 
-  Thompson, Begg (survival) & 0.92 & 0.66 & 0.43 \\ 
-  Egger, Begg (survival) & 0.87 & 0.70 & 0.48 \\ 
+  0 & 65.9 \% & 68.4 \% \\ 
+    1 & 16.4 \% & 9.6 \% \\ 
+    2 & 8.6 \% & 9.1 \% \\ 
+    3 & 5.6 \% & 10.6 \% \\ 
+    4 & 2.9 \% & 2.3 \% \\ 
+    5 & 0.6 \% & NA \% \\ 
    \hline
@@
 \endgroup
-\caption{Agreement in significance proportion, correlation and R-squared of linear regression
-             between the p-values of the publication bias tests. Horizontal lines separate binary, continuous and survival outcomes (order as in table).} 
-\label{test.agreement}
+\caption{Counts Number of significant test results per meta-analysis, separated
+       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
+       applied} 
+\label{number.sig.tests}
 \end{table}
+
+When only looking at small study effect tests, 29.1\% of binary outcome tests and 26.5\% of survival and continuous outcome tests had at least one significant result.
+After applying the bonferroni correction for multiple testing, this shrinks to 10.9\& for binary and 12.1\% for continuous and survival outcomes.
+\\
+When comparing significant findings for small study effect tests and excess significance tests, we will only do so with Harbord's or Egger's test.
+22.4\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 28\% for continuous and survival outcomes.
+Again, the numbers change to 13.3\% for binary outcomes and 17.2\% for continuous and survival outcomes after applying the bonferroni correction.
+\\
+3\% have significant Harbord's test result and significant excesss significance test result  (1.1\% with bonferroni).
+Of the continuous outcomes, we have 6.1 \% with Egger's test and 1.8 with Bonferroni correction.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-13-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-15-1}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jun 24 17:05:45 2019
+% Thu Jun 27 15:12:39 2019
 \begin{table}[ht]
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-16-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-18-1}
 
@@
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
+% %Chunck 6
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% #Agreement proportions of publication bias tests:
+% 
+% #Binary:
+% meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
+%                                               tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
+%                                               tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
+%                                               tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
+%                                               schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
+%                                               schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
+%                                               schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
+%                                               rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
+%                                               rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
+%                                               harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
+% agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
+%                                                       tes.d.peter = sum(tes.d.peter == "agree")/n(),
+%                                                       tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
+%                                                       tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
+%                                                       schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
+%                                                       schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
+%                                                       schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
+%                                                       rucker.peter = sum(rucker.peter == "agree")/n(),
+%                                                       harbord.peter = sum(harbord.peter == "agree")/n())
+% correlation.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = cor(stat.d.tes, stat.schwarzer),
+%                                                         tes.d.peter = cor(stat.d.tes, stat.peter),
+%                                                         tes.d.rucker = cor(stat.d.tes, stat.rucker),
+%                                                         tes.d.harbord = cor(stat.d.tes, stat.harbord),
+%                                                         schwarzer.peter = cor(stat.schwarzer, stat.peter),
+%                                                         schwarzer.rucker = cor(stat.schwarzer, stat.rucker),
+%                                                         schwarzer.harbord = cor(stat.schwarzer, stat.harbord),
+%                                                         rucker.peter = cor(stat.rucker, stat.peter),
+%                                                         harbord.peter = cor(stat.harbord, stat.peter))
+% # rsquared.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = summary(lm(stat.d.tes~ stat.schwarzer))$r.squared,
+% #                                                         tes.d.peter = summary(lm(stat.d.tes~ stat.peter))$r.squared,
+% #                                                         tes.d.rucker = summary(lm(stat.d.tes~ stat.rucker))$r.squared,
+% #                                                         tes.d.harbord = summary(lm(stat.d.tes~ stat.harbord))$r.squared,
+% #                                                         schwarzer.peter = summary(lm(stat.schwarzer~ stat.peter))$r.squared,
+% #                                                         schwarzer.rucker = summary(lm(stat.schwarzer~ stat.rucker))$r.squared,
+% #                                                         schwarzer.harbord = summary(lm(stat.schwarzer~ stat.harbord))$r.squared,
+% #                                                         rucker.peter = summary(lm(stat.rucker~ stat.peter))$r.squared,
+% #                                                         harbord.peter = summary(lm(stat.harbord~ stat.peter))$r.squared)
+% meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test + schwarzer.test > 1, "agree", "disagree"),
+%                                               tes.d.peter = ifelse(tes.d.test + peter.test > 1, "agree", "disagree"),
+%                                               tes.d.rucker = ifelse(tes.d.test + rucker.test > 1, "agree", "disagree"),
+%                                               tes.d.harbord = ifelse(tes.d.test + harbord.test > 1, "agree", "disagree"),
+%                                               schwarzer.peter = ifelse(schwarzer.test + peter.test > 1, "agree", "disagree"),
+%                                               schwarzer.rucker = ifelse(schwarzer.test + rucker.test > 1, "agree", "disagree"),
+%                                               schwarzer.harbord = ifelse(schwarzer.test + harbord.test > 1, "agree", "disagree"),
+%                                               rucker.peter = ifelse(rucker.test + peter.test > 1, "agree", "disagree"),
+%                                               rucker.harbord = ifelse(rucker.test + harbord.test > 1, "agree", "disagree"),
+%                                               harbord.peter = ifelse(harbord.test + peter.test > 1, "agree", "disagree"))
+% agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/sum(schwarzer.test),
+%                                                       tes.d.peter = sum(tes.d.peter == "agree")/sum(peter.test),
+%                                                       tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
+%                                                       tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
+%                                                       schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
+%                                                       schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
+%                                                       schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
+%                                                       rucker.peter = sum(rucker.peter == "agree")/n(),
+%                                                       harbord.peter = sum(harbord.peter == "agree")/n())
+% 
+% binary.tests.agreement <- rbind(agreement.bin, correlation.bin, rsquared.bin)
+% rownames(binary.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
+% colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
+%                                       "Excess significance, Rucker", "Excess significance, Harbord",
+%                                       "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
+%                                       "Rucker, Peter", "Harbord, Peter")
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% 
+% #Continuous:
+% meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
+%                                                 thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
+%                                                 egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
+%                                                 tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
+%                                                 thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
+%                                                 tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
+% agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+%                                                          thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
+%                                                          tes.d.begg = sum(tes.d.begg == "agree")/n(),
+%                                                          thompson.egger = sum(thompson.egger == "agree")/n(),
+%                                                          thompson.begg = sum(thompson.begg == "agree")/n(),
+%                                                          egger.begg = sum(egger.begg == "agree")/n())
+% correlation.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = cor(stat.egger, stat.d.tes),
+%                                                           thompson.tes.d = cor(stat.thompson, stat.d.tes),
+%                                                           tes.d.begg = cor(stat.d.tes, stat.begg),
+%                                                           thompson.egger = cor(stat.thompson, stat.egger),
+%                                                           thompson.begg = cor(stat.thompson, stat.begg),
+%                                                           egger.begg = cor(stat.egger, stat.begg))
+% rsquared.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = summary(lm(stat.egger~ stat.d.tes))$r.squared,
+%                                                        thompson.tes.d = summary(lm(stat.thompson~ stat.d.tes))$r.squared,
+%                                                        tes.d.begg = summary(lm(stat.d.tes~ stat.begg))$r.squared,
+%                                                        thompson.egger = summary(lm(stat.thompson~ stat.egger))$r.squared,
+%                                                        thompson.begg = summary(lm(stat.thompson~ stat.begg))$r.squared,
+%                                                        egger.begg = summary(lm(stat.egger~ stat.begg))$r.squared)
+% agreement.sig.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
+%                                                              thompson.tes.d = sum(thompson.tes.d == "agree")/sum(thompsom.test),
+%                                                              tes.d.begg = sum(tes.d.begg == "agree")/sum(begg.test),
+%                                                              thompson.egger = sum(thompson.egger == "agree")/sum(egger.test),
+%                                                              thompson.begg = sum(thompson.begg == "agree")/sum(thompson.test),
+%                                                              egger.begg = sum(egger.begg == "agree")/sum(egger.test))
+% 
+% 
+% 
+% cont.tests.agreement <- rbind(agreement.cont, correlation.cont, rsquared.cont)
+% rownames(cont.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
+% colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson", 
+%                                      "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% 
+% #Survival:
+% meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
+%                                                 thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
+%                                                 egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
+%                                                 tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
+%                                                 thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
+%                                                 tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
+% agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+%                                                          thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
+%                                                          tes.d.begg = sum(tes.d.begg == "agree")/n(),
+%                                                          thompson.egger = sum(thompson.egger == "agree")/n(),
+%                                                          thompson.begg = sum(thompson.begg == "agree")/n(),
+%                                                          egger.begg = sum(egger.begg == "agree")/n())
+% correlation.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = cor(stat.egger, stat.d.tes),
+%                                                           thompson.tes.d = cor(stat.thompson, stat.d.tes),
+%                                                           tes.d.begg = cor(stat.d.tes, stat.begg),
+%                                                           thompson.egger = cor(stat.thompson, stat.egger),
+%                                                           thompson.begg = cor(stat.thompson, stat.begg),
+%                                                           egger.begg = cor(stat.egger, stat.begg))
+% # rsquared.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = summary(lm(stat.egger~ stat.d.tes))$r.squared,
+% #                                                           thompson.tes.d = summary(lm(stat.thompson~ stat.d.tes))$r.squared,
+% #                                                           tes.d.begg = summary(lm(stat.d.tes~ stat.begg))$r.squared,
+% #                                                           thompson.egger = summary(lm(stat.thompson~ stat.egger))$r.squared,
+% #                                                           thompson.begg = summary(lm(stat.thompson~ stat.begg))$r.squared,
+% #                                                           egger.begg = summary(lm(stat.egger~ stat.begg))$r.squared)
+% meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
+%                                                 thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
+%                                                 egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
+%                                                 tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
+%                                                 thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
+%                                                 tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
+% agreement.sig.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
+%                                                              thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
+%                                                              tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
+%                                                              thompson.egger = sum(thompson.egger == "agree")/sum(egger.test),
+%                                                              thompson.begg = sum(thompson.begg == "agree")/sum(thompson.test),
+%                                                              egger.begg = sum(egger.begg == "agree")/sum(egger.test))
+% 
+% surv.tests.agreement <- rbind(agreement.surv, correlation.surv, rsquared.surv)
+% rownames(surv.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
+% colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)", 
+%                                     "Excess significance, Begg (survival)", "Thompson, Egger (survival)", 
+%                                     "Thompson, Begg (survival)", "Egger, Begg (survival)")
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Merging:
+% test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% 
+% 
+% 
+% The agreement/coinicidence between between small study effect and excess significance tests is often not pronounced, thus, it will be compared by different methods.
+The results of it are displayed in Table \ref{test.agreement}.
+\\
+% The row names indicate which two tests are compared.
+First, the column ``Test Agreement'' quantifies the overall proportion by which the two tests agree in their dichotomous classification of $p$-values with respect to the 0.1 threshold, i.e.
+rejection or ``acceptance'' of the null-hypothesis.
+A ``Test Agreement'' equal to one thus indicates equivalent results, zero no correspondence whatsoever.
+The second column, ``Correlation'' gives the correlation between the test statistics.
+A positive correlation indicates positive correlation of $p$-values, negative correlation correlation in opposite directions.
+Notably, for a high correlation, the scales must not be equal.
+The ``R-squared'' value indicates to what extent one test-statistic can be predicted by another, and ignores additive differences between $p$-values (as for correlation), as well as multiplicative constants between them (i.e.
+$y ~ a + b*x$, $y$ and $x$ being two test-statistics).
+An R-squared value of 1 indicates complete predictability.
+\\
+% %Importantly, the order of the variables does not matter for the test-statistics for all indicators (i.e.
+test-statistics for $x$ and $y$ can be exchanged and the table stays the same).
+If a test is completely replaceable by another, all values in a row are equal to one.
+\\
+% The analysis is again done separately for the outcome types.
+Overall, the test agreement is always above 0.62, and excluding survival outcomes, even above 0.79 (survival outcomes have only 39 test results, and thus more stochastic variation).
+Correlation ranges from near perfect (Thompson, Egger continuous, 0.91) to negative correlation (Excess significance, Thompson survival: -0.17).
+The R-squared values also indicate that some tests are similar, while others are not.
+% 
+% <<echo=FALSE, results='asis'>>=
+% print(xtable(test.agreement, align = "lccc", caption = "Agreement in significance proportion, correlation and R-squared of linear regression
+%              between the p-values of the publication bias tests. Horizontal lines separate binary, continuous and survival outcomes (order as in table).",
+%              label = "test.agreement"), hline = c(0,0,9, 15, 21), size = "footnotesize")
+@
 % 
@@
 
-\section{Excess Significance Test}
+\subsection{Excess Significance Test} \label{sec:excess.significance}
 \citet{excess.significance} developped an exploratory test to detect if the proportion of significant findings is larger than expected.

### 2019-06-27 report/chapter03.Rnw
Results update

@@
                echo=TRUE, message=FALSE,
-               fig.width=8, fig.height=3,
+               fig.width=8.1, fig.height=3,
                self.contained = FALSE,
@@
 
+require(corrgram)
+
 # data.ext2 <- pb.process2(data)
@@
 
-#Agreement proportions of publication bias tests:
-
-#Binary:
-meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
-																							tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
-																							tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
-																							tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
-																							schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
-																							schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
-																							schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
-																							rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
-																							rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
-																							harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
-agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
-																											tes.d.peter = sum(tes.d.peter == "agree")/n(),
-																											tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
-																											tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
-																											schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
-																											schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
-																											schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
-																											rucker.peter = sum(rucker.peter == "agree")/n(),
-																											harbord.peter = sum(harbord.peter == "agree")/n())
-correlation.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = cor(pval.d.tes, pval.schwarzer),
-																												tes.d.peter = cor(pval.d.tes, pval.peter),
-																												tes.d.rucker = cor(pval.d.tes, pval.rucker),
-																												tes.d.harbord = cor(pval.d.tes, pval.harbord),
-																												schwarzer.peter = cor(pval.schwarzer, pval.peter),
-																												schwarzer.rucker = cor(pval.schwarzer, pval.rucker),
-																												schwarzer.harbord = cor(pval.schwarzer, pval.harbord),
-																												rucker.peter = cor(pval.rucker, pval.peter),
-																												harbord.peter = cor(pval.harbord, pval.peter))
-rsquared.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = summary(lm(pval.d.tes~ pval.schwarzer))$r.squared,
-                                                        tes.d.peter = summary(lm(pval.d.tes~ pval.peter))$r.squared,
-                                                        tes.d.rucker = summary(lm(pval.d.tes~ pval.rucker))$r.squared,
-                                                        tes.d.harbord = summary(lm(pval.d.tes~ pval.harbord))$r.squared,
-                                                        schwarzer.peter = summary(lm(pval.schwarzer~ pval.peter))$r.squared,
-                                                        schwarzer.rucker = summary(lm(pval.schwarzer~ pval.rucker))$r.squared,
-                                                        schwarzer.harbord = summary(lm(pval.schwarzer~ pval.harbord))$r.squared,
-                                                        rucker.peter = summary(lm(pval.rucker~ pval.peter))$r.squared,
-                                                        harbord.peter = summary(lm(pval.harbord~ pval.peter))$r.squared)
-
-binary.tests.agreement <- rbind(agreement.bin, correlation.bin, rsquared.bin)
-rownames(binary.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
-colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
-                                      "Excess significance, Rucker", "Excess significance, Harbord",
-                                      "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
-                                      "Rucker, Peter", "Harbord, Peter")
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Continuous:
-meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
-																								thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
-																								egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
-																								tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
-																								thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
-																								tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
-																												 thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
-																												 tes.d.begg = sum(tes.d.begg == "agree")/n(),
-																												 thompson.egger = sum(thompson.egger == "agree")/n(),
-																												 thompson.begg = sum(thompson.begg == "agree")/n(),
-																												 egger.begg = sum(egger.begg == "agree")/n())
-correlation.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = cor(pval.egger, pval.d.tes),
-																													thompson.tes.d = cor(pval.thompson, pval.d.tes),
-																													tes.d.begg = cor(pval.d.tes, pval.begg),
-																													thompson.egger = cor(pval.thompson, pval.egger),
-																													thompson.begg = cor(pval.thompson, pval.begg),
-																													egger.begg = cor(pval.egger, pval.begg))
-rsquared.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = summary(lm(pval.egger~ pval.d.tes))$r.squared,
-                                                          thompson.tes.d = summary(lm(pval.thompson~ pval.d.tes))$r.squared,
-                                                          tes.d.begg = summary(lm(pval.d.tes~ pval.begg))$r.squared,
-                                                          thompson.egger = summary(lm(pval.thompson~ pval.egger))$r.squared,
-                                                          thompson.begg = summary(lm(pval.thompson~ pval.begg))$r.squared,
-                                                          egger.begg = summary(lm(pval.egger~ pval.begg))$r.squared)
-
-cont.tests.agreement <- rbind(agreement.cont, correlation.cont, rsquared.cont)
-rownames(cont.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
-colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson", 
-                                     "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Survival:
-meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
-                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
-                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
-                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
-                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
-                                                         egger.begg = sum(egger.begg == "agree")/n())
-correlation.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = cor(pval.egger, pval.d.tes),
-																													thompson.tes.d = cor(pval.thompson, pval.d.tes),
-																													tes.d.begg = cor(pval.d.tes, pval.begg),
-																													thompson.egger = cor(pval.thompson, pval.egger),
-																													thompson.begg = cor(pval.thompson, pval.begg),
-																													egger.begg = cor(pval.egger, pval.begg))
-rsquared.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = summary(lm(pval.egger~ pval.d.tes))$r.squared,
-                                                          thompson.tes.d = summary(lm(pval.thompson~ pval.d.tes))$r.squared,
-                                                          tes.d.begg = summary(lm(pval.d.tes~ pval.begg))$r.squared,
-                                                          thompson.egger = summary(lm(pval.thompson~ pval.egger))$r.squared,
-                                                          thompson.begg = summary(lm(pval.thompson~ pval.begg))$r.squared,
-                                                          egger.begg = summary(lm(pval.egger~ pval.begg))$r.squared)
-
-surv.tests.agreement <- rbind(agreement.surv, correlation.surv, rsquared.surv)
-rownames(surv.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
-colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)", 
-                                    "Excess significance, Begg (survival)", "Thompson, Egger (survival)", 
-                                    "Thompson, Begg (survival)", "Egger, Begg (survival)")
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Merging:
-test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
-
+cor.data <- meta.f %>% select(stat.rucker, stat.harbord, stat.peter, stat.schwarzer, stat.d.tes, 
+                             stat.egger, stat.thompson, stat.begg)
+colnames(cor.data) <- c("Rucker", "Harbord", "Peter", "Schwarzer", "Excess s.",  "Egger", "Thompson",
+                        "Begg")
+
+panel.pts.new <- function (x, y, corr = NULL, col.regions, cor.method, ...) 
+{
+
+  plot.xy(xy.coords(x, y), type = "p", ...)
+  box(col = "lightgray")
+  rect(xleft = -1.96, ybottom = -1.96, xright = 1.96, ytop = 1.96, density = NULL, angle = 45,
+       col = NA, border = "white", lty = 1, lwd = 1.4, 
+       ...)
+  if (!is.null(corr)) 
+    return()
+
+}
+
+# Tukey Mean difference plots;
+#--------------------------------------------------------------------------------------------------------------------#
+
+egger.thompson.plot <- meta.f %>% 
+  mutate(mean = ((logit(pval.egger)+ logit(pval.thompson)))/2, 
+         difference = logit(pval.egger) - logit(pval.thompson)) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point() + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + theme(legend.position = "none") +
+  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+                     values = c("red", "blue")) +
+  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value Thompson)" )))
+#--------------------------------------------------------------------------------------------------------------------#
+
+harbord.rucker.plot <- meta.f %>% 
+  mutate(mean = ((logit(pval.harbord)+ logit(pval.rucker)))/2, 
+         difference = logit(pval.harbord) - logit(pval.rucker)) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + theme(legend.position = "none") +
+  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+                     values = c("red", "blue")) +
+  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value Rucker)" )))
+#--------------------------------------------------------------------------------------------------------------------#
+
+harbord.excess.plot <- meta.f %>% 
+  mutate(mean = ((logit(pval.harbord)+ logit(pval.d.tes)))/2, 
+         difference = logit(pval.harbord) - logit(pval.d.tes)) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + theme(legend.position = "bottom") +
+  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+                     values = c("red", "blue")) +
+  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value excess significance)" )))
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Table with proportions of significant test results:
+meta.f <- meta.f %>% 
+mutate(test.sum.bin = tes.d.test + schwarzer.test + harbord.test + peter.test + rucker.test,
+       test.sum.else = tes.d.test + egger.test + thompson.test + begg.test, 
+       test.sum.bin2 = tes.d.test + harbord.test,
+       test.sum.else2 = tes.d.test + egger.test, 
+       test.min.bin = ifelse(schwarzer.test + harbord.test + peter.test + rucker.test > 0, 1, 0),
+       test.min.else = ifelse(egger.test + thompson.test + begg.test > 0, 1, 0),
+       test.min.bin2 = ifelse(test.sum.bin2 > 0, 1, 0),
+       test.min.else2 = ifelse(test.sum.else2 > 0, 1, 0))
+
+mean.min.bin <- round(mean(meta.f$test.min.bin, na.rm = T)*100, 1)
+mean.min.else <- round(mean(meta.f$test.min.else, na.rm = T)*100, 1)
+
+mean.min.bin2 <- round(mean(meta.f$test.min.bin2, na.rm = T)*100, 1)
+mean.min.else2 <- round(mean(meta.f$test.min.else2, na.rm = T)*100, 1)
+
+both.bin <- round(length(which(meta.f$test.sum.bin2 == 2))/
+                    length(which(!is.na(meta.f$test.sum.bin2)))*100, 1)
+
+both.else <- round(length(which(meta.f$test.sum.else2 == 2))/
+                     length(which(!is.na(meta.f$test.sum.else2)))*100, 1)
+
+summary.bin <- round(meta.f %>% 
+  group_by(test.sum.bin) %>% summarise(n = n()) %>% select(n)/dim(meta.bin)[1] * 100, 1)
+
+summary.else <- round(meta.f %>% group_by(test.sum.else) %>% 
+                        summarise(n = n()) %>% 
+                        select(n)/(dim(meta.cont)[1] + dim(meta.surv)[1]) * 100, 1)
+
+number.sig.tests <- data.frame(number = seq(from = 0, to = 5),
+                               binary = paste(summary.bin$n[-7], "%"),
+                               cont = paste(c(summary.else$n[-6], NA), "%"))
+colnames(number.sig.tests) <- c("Count", "Binary Outcomes", "Continuous and Survival")
+
+meta.f <- meta.f %>% mutate(tes.d.test.b = ifelse(pval.d.tes < 0.05, 1, 0),
+                            harbord.test.b = ifelse(pval.harbord < 0.05, 1, 0),
+                            egger.test.b = ifelse(pval.egger < 0.05, 1, 0),
+                            test.sum.bin2 = tes.d.test.b + harbord.test.b,
+                            test.sum.else2 = tes.d.test.b + egger.test.b, 
+                            test.min.bin2 = ifelse(test.sum.bin2 > 0, 1, 0),
+                            test.min.else2 = ifelse(test.sum.else2 > 0, 1, 0))
+
+mean.min.bin2.b <- round(mean(meta.f$test.min.bin2, na.rm = T)*100, 1)
+mean.min.else2.b <- round(mean(meta.f$test.min.else2, na.rm = T)*100, 1)
+
+both.bin.b <- round(length(which(meta.f$test.sum.bin2 == 2))/
+                    length(which(!is.na(meta.f$test.sum.bin2)))*100, 1)
+
+both.else.b <- round(length(which(meta.f$test.sum.else2 == 2))/
+                     length(which(!is.na(meta.f$test.sum.else2)))*100, 1)
+
+meta.f <- meta.f %>% mutate(egger.test = ifelse(pval.egger < 0.1/3, 1, 0),
+                            thompson.test = ifelse(pval.thompson < 0.1/3, 1, 0),
+                            begg.test = ifelse(pval.begg < 0.1/3, 1, 0),
+
+                            schwarzer.test = ifelse(pval.schwarzer < 0.1/4, 1, 0),
+                            rucker.test = ifelse(pval.rucker < 0.1/4, 1, 0),
+                            harbord.test = ifelse(pval.harbord < 0.1/4, 1, 0),
+                            peter.test = ifelse(pval.peter < 0.1/4, 1, 0),
+                            test.sum.bin = tes.d.test + schwarzer.test + harbord.test + peter.test + rucker.test,
+                            test.sum.else = tes.d.test + egger.test + thompson.test + begg.test, 
+                            test.min.bin = ifelse(schwarzer.test + harbord.test + peter.test + rucker.test > 0, 1, 0),
+                            test.min.else = ifelse(egger.test + thompson.test + begg.test > 0, 1, 0))
+
+mean.min.bin.b <- round(mean(meta.f$test.min.bin, na.rm = T)*100, 1)
+mean.min.else.b <- round(mean(meta.f$test.min.else, na.rm = T)*100, 1)
+
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
 #--------------------------------------------------------------------------------------------------------------------#
@@
 
-\begin{figure}[ht!]
+\begin{figure}
 <<echo=FALSE, fig.height = 9>>=
@@
 
-The agreement/coinicidence between between small study effect and excess significance tests is often not pronounced, thus, it will be compared by different methods.
-This is displayed in Table \ref{test.agreement}.
-The row names indicate which two tests are compared.
-First, the column ``Test Agreement'' quantifies the overall proportion by which the two tests agree in their rejection or ``acceptance'' of the null-hypothesis.
-``Test Agreement'' being equal one thus indicates equivalent results, zero no correspondence whatsoever.
-The second column, ``Correlation'' gives the correlation between the $p$-values.
-A positive correlation indicates psotive coincidence of $p$-values, negative correlation coincidence in opposite directions.
-However, the scale might be different for this agreement measure.
-The ``R-squared'' value indicates to what extent one $p$-value can be predicted by another, and ignores additive differences between $p$-values (as for correlation), as well as multiplicative constants between them (i.e.
-$y ~ a + b*x$, $y$ and $x$ being two $p$-values of test-statistics).
-An R-squared value of 1 indicates perfect fit.
-Importantly, the order of the variables does not matter for the $p$-values for all indicators (i.e.
-$p$-values for $x$ and $y$ can be exchanged and the table stays the same).
-If a test is completely replaceable by another, all values in a row are equal to one.
-
-<<echo=FALSE, results='asis'>>=
-print(xtable(test.agreement, align = "lccc", caption = "Agreement in significance proportion, correlation and R-squared of linear regression
-             between the p-values of the publication bias tests. Horizontal lines separate binary, continuous and survival outcomes (order as in table).",
-             label = "test.agreement"), hline = c(0,0,9, 15, 21), size = "footnotesize")
+%Agreement table -> Chunck 1
+
+It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects/excess significance for the same meta-analyses.
+Especially between small study effects and excess significance tests, we expect some disagreement between tests.
+A simple method to check the coincidence of test results is to compare scatterplots and empirical spearman correlations between test statistics.
+This is done in Figure \ref{fig:test.agreement}.
+\\
+Here, there is no separation between survival and continuous outcomes. The upper left rectangle is displaying binary outcomes and the lower right about continuous and survival outcomes.
+
+\begin{figure}
+<<echo=FALSE, fig.height = 6, warning=FALSE>>=
+corrgram(cor.data, 
+         upper.panel=panel.pts.new, lower.panel=panel.cor, 
+         cex.labels = 1, cex = .3, cex.cor = 2, pch = 1,
+         text.panel=panel.txt, cor.method = "spearman")
 @
+\caption{Pairs-plot for test statistics of small study effect and excess significance.
+The lower panel gives the spearman correlations for the different test statistics, and the upper panel displays a scatterplot.
+The colours indicate magnitude and direction of the correlation coefficients.
+The rectangle with white borders displays the area within which both tests have absolute value < 1.96.}
+\label{fig:test.agreement}
+\end{figure}
+
+The observed patterns on the scatterplots differ: Excess significance and small study effect test statistics do usually not align with each other, forming rather randomly scattered bulks of points.
+Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is also reflected in large correlation coefficients.
+In general, small study effect tests align, but the extent to which they align differs.
+Harbord's test statistic has similar correlation coefficients with all other small study effect test statistics for binary outcomes, while the correlation coefficients between them is varying.\\
+Because scatterplots and correlation coefficients can be missleading, also a Tukey mean-difference or Bland-Altmann plot is shown for three scenarios in Figure \ref{fig:mean.diff.test}:
+\begin{itemize}
+\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
+\item For Harbord's and Rucker's tests
+\item For Harbord's and excess significance tests
+\end{itemize}
+
+This can be justified since all tests are supposed to measure the evidence for publication bias.
+For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation.
+The mean $p$-value ((logit($p$-value 1) + logit($p$-value 2))/2) is then displayed against the differnec between the $p$-value.
+If no systematic errors and biases exist between the measurement methods, then
+
+\begin{itemize}
+\item the mean of the differences (systematic error) should be around zero
+\item the points should scatter independent of the mean of the $p$-values
+\end{itemize}
+
+The last criterium seems not to be given when comparing Harbords and Excess significance tests. 
+-- In the appendix, it can be seen that this is reproducible with the remainig small study effect tests (not there yet) -- 
+With decreasing mean, the difference gets more negative, and vice versa, such that one would predict that the excess significance $p$-values are more ``extreme'' in both directions.
+This finding suggests that correspondence between the tests is poor.
+The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger and Thompson test, and around 0.99 for Harbord and Rucker.
+
+\begin{figure}
+<<echo=FALSE, fig.height = 6.5, warning=FALSE>>=
+grid.arrange(egger.thompson.plot, 
+             harbord.rucker.plot, 
+             harbord.excess.plot, ncol = 1)
+@
+\caption{Mean - difference plots for logit transformed $p$-values.
+The mean of logit transformed $p$-values is displayed on the $x$-axis and the difference on the $y$-axis.
+Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).}
+\label{fig:mean.diff.test}
+\end{figure}
+
+The previous results suggest that the results will also differ substantially after applying the common dichotomization of $p$-values.
+We expect that some proportion of the meta-analysis will only be significant for a certain test, and this is indeed observed in Table \ref{number.sig.tests}.
+It displays the percentage of meta-analyses with a certain number of significant test results.
+
+<<echo = FALSE, results='asis'>>=
+print(xtable(number.sig.tests, caption = "Counts Number of significant test results per meta-analysis, separated
+       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
+       applied", label = "number.sig.tests", align = "lccc"), include.rownames = F, size = "footnotesize")
+@
+
+When only looking at small study effect tests, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of survival and continuous outcome tests had at least one significant result.
+After applying the bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\& for binary and \Sexpr{mean.min.else.b}\% for continuous and survival outcomes.
+\\
+When comparing significant findings for small study effect tests and excess significance tests, we will only do so with Harbord's or Egger's test.
+\Sexpr{mean.min.bin2}\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, \Sexpr{mean.min.else2}\% for continuous and survival outcomes.
+Again, the numbers change to \Sexpr{mean.min.bin2.b}\% for binary outcomes and \Sexpr{mean.min.else2.b}\% for continuous and survival outcomes after applying the bonferroni correction.
+\\
+\Sexpr{both.bin}\% have significant Harbord's test result and significant excesss significance test result  (\Sexpr{both.bin.b}\% with bonferroni).
+Of the continuous outcomes, we have \Sexpr{both.else} \% with Egger's test and \Sexpr{both.else.b} with Bonferroni correction.
 
@@
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %Chunck 6
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% #Agreement proportions of publication bias tests:
+% 
+% #Binary:
+% meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
+%                                               tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
+%                                               tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
+%                                               tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
+%                                               schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
+%                                               schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
+%                                               schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
+%                                               rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
+%                                               rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
+%                                               harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
+% agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
+%                                                       tes.d.peter = sum(tes.d.peter == "agree")/n(),
+%                                                       tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
+%                                                       tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
+%                                                       schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
+%                                                       schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
+%                                                       schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
+%                                                       rucker.peter = sum(rucker.peter == "agree")/n(),
+%                                                       harbord.peter = sum(harbord.peter == "agree")/n())
+% correlation.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = cor(stat.d.tes, stat.schwarzer),
+%                                                         tes.d.peter = cor(stat.d.tes, stat.peter),
+%                                                         tes.d.rucker = cor(stat.d.tes, stat.rucker),
+%                                                         tes.d.harbord = cor(stat.d.tes, stat.harbord),
+%                                                         schwarzer.peter = cor(stat.schwarzer, stat.peter),
+%                                                         schwarzer.rucker = cor(stat.schwarzer, stat.rucker),
+%                                                         schwarzer.harbord = cor(stat.schwarzer, stat.harbord),
+%                                                         rucker.peter = cor(stat.rucker, stat.peter),
+%                                                         harbord.peter = cor(stat.harbord, stat.peter))
+% # rsquared.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = summary(lm(stat.d.tes~ stat.schwarzer))$r.squared,
+% #                                                         tes.d.peter = summary(lm(stat.d.tes~ stat.peter))$r.squared,
+% #                                                         tes.d.rucker = summary(lm(stat.d.tes~ stat.rucker))$r.squared,
+% #                                                         tes.d.harbord = summary(lm(stat.d.tes~ stat.harbord))$r.squared,
+% #                                                         schwarzer.peter = summary(lm(stat.schwarzer~ stat.peter))$r.squared,
+% #                                                         schwarzer.rucker = summary(lm(stat.schwarzer~ stat.rucker))$r.squared,
+% #                                                         schwarzer.harbord = summary(lm(stat.schwarzer~ stat.harbord))$r.squared,
+% #                                                         rucker.peter = summary(lm(stat.rucker~ stat.peter))$r.squared,
+% #                                                         harbord.peter = summary(lm(stat.harbord~ stat.peter))$r.squared)
+% meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test + schwarzer.test > 1, "agree", "disagree"),
+%                                               tes.d.peter = ifelse(tes.d.test + peter.test > 1, "agree", "disagree"),
+%                                               tes.d.rucker = ifelse(tes.d.test + rucker.test > 1, "agree", "disagree"),
+%                                               tes.d.harbord = ifelse(tes.d.test + harbord.test > 1, "agree", "disagree"),
+%                                               schwarzer.peter = ifelse(schwarzer.test + peter.test > 1, "agree", "disagree"),
+%                                               schwarzer.rucker = ifelse(schwarzer.test + rucker.test > 1, "agree", "disagree"),
+%                                               schwarzer.harbord = ifelse(schwarzer.test + harbord.test > 1, "agree", "disagree"),
+%                                               rucker.peter = ifelse(rucker.test + peter.test > 1, "agree", "disagree"),
+%                                               rucker.harbord = ifelse(rucker.test + harbord.test > 1, "agree", "disagree"),
+%                                               harbord.peter = ifelse(harbord.test + peter.test > 1, "agree", "disagree"))
+% agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/sum(schwarzer.test),
+%                                                       tes.d.peter = sum(tes.d.peter == "agree")/sum(peter.test),
+%                                                       tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
+%                                                       tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
+%                                                       schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
+%                                                       schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
+%                                                       schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
+%                                                       rucker.peter = sum(rucker.peter == "agree")/n(),
+%                                                       harbord.peter = sum(harbord.peter == "agree")/n())
+% 
+% binary.tests.agreement <- rbind(agreement.bin, correlation.bin, rsquared.bin)
+% rownames(binary.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
+% colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
+%                                       "Excess significance, Rucker", "Excess significance, Harbord",
+%                                       "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
+%                                       "Rucker, Peter", "Harbord, Peter")
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% 
+% #Continuous:
+% meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
+%                                                 thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
+%                                                 egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
+%                                                 tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
+%                                                 thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
+%                                                 tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
+% agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+%                                                          thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
+%                                                          tes.d.begg = sum(tes.d.begg == "agree")/n(),
+%                                                          thompson.egger = sum(thompson.egger == "agree")/n(),
+%                                                          thompson.begg = sum(thompson.begg == "agree")/n(),
+%                                                          egger.begg = sum(egger.begg == "agree")/n())
+% correlation.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = cor(stat.egger, stat.d.tes),
+%                                                           thompson.tes.d = cor(stat.thompson, stat.d.tes),
+%                                                           tes.d.begg = cor(stat.d.tes, stat.begg),
+%                                                           thompson.egger = cor(stat.thompson, stat.egger),
+%                                                           thompson.begg = cor(stat.thompson, stat.begg),
+%                                                           egger.begg = cor(stat.egger, stat.begg))
+% rsquared.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = summary(lm(stat.egger~ stat.d.tes))$r.squared,
+%                                                        thompson.tes.d = summary(lm(stat.thompson~ stat.d.tes))$r.squared,
+%                                                        tes.d.begg = summary(lm(stat.d.tes~ stat.begg))$r.squared,
+%                                                        thompson.egger = summary(lm(stat.thompson~ stat.egger))$r.squared,
+%                                                        thompson.begg = summary(lm(stat.thompson~ stat.begg))$r.squared,
+%                                                        egger.begg = summary(lm(stat.egger~ stat.begg))$r.squared)
+% agreement.sig.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
+%                                                              thompson.tes.d = sum(thompson.tes.d == "agree")/sum(thompsom.test),
+%                                                              tes.d.begg = sum(tes.d.begg == "agree")/sum(begg.test),
+%                                                              thompson.egger = sum(thompson.egger == "agree")/sum(egger.test),
+%                                                              thompson.begg = sum(thompson.begg == "agree")/sum(thompson.test),
+%                                                              egger.begg = sum(egger.begg == "agree")/sum(egger.test))
+% 
+% 
+% 
+% cont.tests.agreement <- rbind(agreement.cont, correlation.cont, rsquared.cont)
+% rownames(cont.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
+% colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson", 
+%                                      "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% 
+% #Survival:
+% meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
+%                                                 thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
+%                                                 egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
+%                                                 tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
+%                                                 thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
+%                                                 tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
+% agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+%                                                          thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
+%                                                          tes.d.begg = sum(tes.d.begg == "agree")/n(),
+%                                                          thompson.egger = sum(thompson.egger == "agree")/n(),
+%                                                          thompson.begg = sum(thompson.begg == "agree")/n(),
+%                                                          egger.begg = sum(egger.begg == "agree")/n())
+% correlation.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = cor(stat.egger, stat.d.tes),
+%                                                           thompson.tes.d = cor(stat.thompson, stat.d.tes),
+%                                                           tes.d.begg = cor(stat.d.tes, stat.begg),
+%                                                           thompson.egger = cor(stat.thompson, stat.egger),
+%                                                           thompson.begg = cor(stat.thompson, stat.begg),
+%                                                           egger.begg = cor(stat.egger, stat.begg))
+% # rsquared.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = summary(lm(stat.egger~ stat.d.tes))$r.squared,
+% #                                                           thompson.tes.d = summary(lm(stat.thompson~ stat.d.tes))$r.squared,
+% #                                                           tes.d.begg = summary(lm(stat.d.tes~ stat.begg))$r.squared,
+% #                                                           thompson.egger = summary(lm(stat.thompson~ stat.egger))$r.squared,
+% #                                                           thompson.begg = summary(lm(stat.thompson~ stat.begg))$r.squared,
+% #                                                           egger.begg = summary(lm(stat.egger~ stat.begg))$r.squared)
+% meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
+%                                                 thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
+%                                                 egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
+%                                                 tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
+%                                                 thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
+%                                                 tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
+% agreement.sig.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
+%                                                              thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
+%                                                              tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
+%                                                              thompson.egger = sum(thompson.egger == "agree")/sum(egger.test),
+%                                                              thompson.begg = sum(thompson.begg == "agree")/sum(thompson.test),
+%                                                              egger.begg = sum(egger.begg == "agree")/sum(egger.test))
+% 
+% surv.tests.agreement <- rbind(agreement.surv, correlation.surv, rsquared.surv)
+% rownames(surv.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
+% colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)", 
+%                                     "Excess significance, Begg (survival)", "Thompson, Egger (survival)", 
+%                                     "Thompson, Begg (survival)", "Egger, Begg (survival)")
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Merging:
+% test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% 
+% 
+% 
+% The agreement/coinicidence between between small study effect and excess significance tests is often not pronounced, thus, it will be compared by different methods.
+The results of it are displayed in Table \ref{test.agreement}.
+\\
+% The row names indicate which two tests are compared.
+First, the column ``Test Agreement'' quantifies the overall proportion by which the two tests agree in their dichotomous classification of $p$-values with respect to the 0.1 threshold, i.e.
+rejection or ``acceptance'' of the null-hypothesis.
+A ``Test Agreement'' equal to one thus indicates equivalent results, zero no correspondence whatsoever.
+The second column, ``Correlation'' gives the correlation between the test statistics.
+A positive correlation indicates positive correlation of $p$-values, negative correlation correlation in opposite directions.
+Notably, for a high correlation, the scales must not be equal.
+The ``R-squared'' value indicates to what extent one test-statistic can be predicted by another, and ignores additive differences between $p$-values (as for correlation), as well as multiplicative constants between them (i.e.
+$y ~ a + b*x$, $y$ and $x$ being two test-statistics).
+An R-squared value of 1 indicates complete predictability.
+\\
+% %Importantly, the order of the variables does not matter for the test-statistics for all indicators (i.e.
+test-statistics for $x$ and $y$ can be exchanged and the table stays the same).
+If a test is completely replaceable by another, all values in a row are equal to one.
+\\
+% The analysis is again done separately for the outcome types.
+Overall, the test agreement is always above 0.62, and excluding survival outcomes, even above 0.79 (survival outcomes have only 39 test results, and thus more stochastic variation).
+Correlation ranges from near perfect (Thompson, Egger continuous, 0.91) to negative correlation (Excess significance, Thompson survival: -0.17).
+The R-squared values also indicate that some tests are similar, while others are not.
+% 
+% <<echo=FALSE, results='asis'>>=
+% print(xtable(test.agreement, align = "lccc", caption = "Agreement in significance proportion, correlation and R-squared of linear regression
+%              between the p-values of the publication bias tests. Horizontal lines separate binary, continuous and survival outcomes (order as in table).",
+%              label = "test.agreement"), hline = c(0,0,9, 15, 21), size = "footnotesize")
+@
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % %Chunck 1
@@
 %
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%

### 2019-06-27 report/chapter04.tex
Methods update
Results update

--- 2019-06-11 report/chapter04.Rnw
@@
 % LaTeX file for Chapter 04
-<<'preamble04',include=FALSE>>=
-library(knitr)
-opts_chunk$set(
-    fig.path='figure/ch04_fig', 
-    self.contained=FALSE,
-    cache=FALSE
-) 
-@
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Small study effect and Publication Bias Adjustment}
+\section{Excess Significance Test}
+\citet{excess.significance} developped an exploratory test to detect if the proportion of significant findings is larger than expected.
+Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study.
+\\
+We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated as for example by fixed effects Meta-Analysis \ref{eq:fixed.effects}.
+Let $O$ be the number of significant study results out of $n$ studies and $\alpha$ the significance threshold.
+Corresponding to the study effect $\theta_i$, we can specify the power $1 - \beta_i$, the probability to accepting a true result.
+Let $z_{\alpha,i}$ be the $1-\alpha$ quantile of a normal distribution with standard error $\hat{s}_i$.
+The power of study $i$ can be estimated as:
+
+\begin{align}
+1 - \hat{\beta}_i &= F(z_\alpha) 
+\end{align}
+
+with $F$ being the cumulative distribution of a normal with mean $\hat{\theta}_M$ and standard deviation $\hat{s}_i$. \\
+If we assume no bias in $\theta_i, \theta_M$, the expected number of significant study results is then just
+
+\begin{align}
+E &= \sum_{i = 1}^n (1 - \beta_i) \nonumber
+\end{align}
+
+$E$ can then be compared to $O$ by constructing a test statistic $\chi$:
+
+\begin{align}
+\chi  &= \big( \frac{(O - E)^2}{E} + \frac{(O - E)^2}{n - E}\big) \nonumber
+\end{align}
+
+and consecutively, calculating a $p$-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
+Alternatively, one can also use a binomial proportion test, which tests if the probability of significance is the same as expected.
+A simple Wald test statistic $Z$ is given by:
+
+\begin{align}
+Z = \frac{O/n - E/n}{\sqrt{(O/n(1-O/n))/n}}
+\end{align}
+
+The one sided $p$-value for the alternative hypothesis $O/n > E/n$ is
+
+\begin{align}
+p &= 1 - \Phi(Z) \nonumber
+\end{align}
+
+with $\Phi$ being the cumulative distribution function of a standard normal. \citet{excess.significance} propose it to be more suitable if $n$ is small.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small Study Effect and Publication Bias Adjustment}
 There are different approaches to correct for small study effects and publication bias.
-They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinte precision (i.e.
+They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinite precision (i.e.
 very small standard error) or to a summary effect, corrected for publication bias.
-Selection modells aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:
+Selection models aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:
 

### 2019-06-27 code/new_meta_analysis.R

@@ -632,39 +632,39 @@ tmp.z <- data.ext2 %>% group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 9) %
   filter(outcome.type != "rate" & !is.na(outcome.type)) %>% filter(total1 + total2 > 3)
 
 meta.id.vector <- metac$meta.id
+# 
+# excess.significance.z <- list()
+# excess.significance.d <- list()
+# 
+# counter <- 0
+# for(u in meta.id.vector){
+#   counter <- counter + 1
+#   print(c(u,counter))
+#   excess.significance.z[[counter]] <- tes.z(tmp.z[tmp.z$meta.id == u,])
+# 
+#   excess.significance.d[[counter]] <- tes.d(tmp[tmp$meta.id == u,])
+# 
+#   print(c(u, (tes.d(tmp[tmp$meta.id == u,])[4])))
+#   if(is.na(tes.d(tmp[tmp$meta.id == u,])[4])) break
+# }
+# 
+# excess.sig.list <- list(meta.id.vector, tmp.z, tmp, excess.significance.z, excess.significance.d)
 
-excess.significance.z <- list()
-excess.significance.d <- list()
-
-counter <- 0
-for(u in meta.id.vector){
-  counter <- counter + 1
-  print(c(u,counter))
-  excess.significance.z[[counter]] <- tes.z(tmp.z[tmp.z$meta.id == u,])
-
-  excess.significance.d[[counter]] <- tes.d(tmp[tmp$meta.id == u,])
-
-  print(c(u, (tes.d(tmp[tmp$meta.id == u,])[4])))
-  if(is.na(tes.d(tmp[tmp$meta.id == u,])[4])) break
-}
-
-excess.sig.list <- list(meta.id.vector, tmp.z, tmp, excess.significance.z, excess.significance.d)
-
-# excess.significance.z <- excess.sig.list[[4]]
-# excess.significance.d <- excess.sig.list[[5]]
+excess.significance.z <- excess.sig.list[[4]]
+excess.significance.d <- excess.sig.list[[5]]
 
 #List extraction:
 excess.significance.results <- cbind(
   meta.id = meta.id.vector,
   pval.z.tes.org = unlist(lapply(excess.significance.z, FUN = function(object){object[3]})),
   pval.z.tes = unlist(lapply(excess.significance.z, FUN = function(object){object[4]})),
-  stat.z.tes = unlist(lapply(excess.significance.z, FUN = function(object){object[3]})),
[…]

### 2019-06-28 report/MSc_Report.tex
update

@@
 \input{header.sty}   % packages, layout and standard macros
+\input{newCommands.tex}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Jun 27 15:14:56 2019
+% Fri Jun 28 14:09:15 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Jun 27 15:14:57 2019
+% Fri Jun 28 14:09:15 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Jun 27 15:14:57 2019
+% Fri Jun 28 16:35:30 2019
 \begin{table}[ht]
@@
 3\% have significant Harbord's test result and significant excesss significance test result  (1.1\% with bonferroni).
-Of the continuous outcomes, we have 6.1 \% with Egger's test and 1.8 with Bonferroni correction.
+Of the continuous outcomes, we have 6.1\% with Egger's test and 1.8\% with Bonferroni correction.
 
@@
 
-If one is interested in the mere change in effect size and if the effect size did decrease or increase after adjustment, one can look at Figure \ref{fig:adjustment.size}.
-It displays the difference between the meta-analysis pooled treatment effect and the adjusted treatment effect.
-To compare the overall effect of adjustment for small study effects, the absolute value of the effect size is used.
-Thus, a negative difference indicates larger adjusted treatment effect size than meta-analysis pooled effect size.
+There are two possibilities when adjusting the pooled treatment effect of meta-analyses for publication bias.
+The absolute size of the treatment effect can be smaller, or larger after adjustment.
+Additionally, it is of interest by how much the treatment effect is diminishued or increased.
+\\
+Figure \ref{fig:adjustment.size} displays the difference between the meta-analysis pooled treatment effect $\theta_M$ and the adjusted treatment effect $\theta_\textrm{Adj.}$ for the copas and regression adjustment methods and fixed and random effects meta-analysis.
+The treatment effects are mirrored on the positive side, such that a positive difference indicates that the effect size was smaller after adjustment (and analogously, larger if the difference is negative).
 For better illustration, some very large and very small differences have been ommitted in the $z$-score and Hedges $g$ histogramms; the missing differences are provided in Table \ref{missing.differences}.
-Additionally to the histogramms, Table \ref{adjustment.difference} shows the quantiles and means for the various differences.
-%For sake of interpretability, negative effect sizes are changed to positive, such that a negative difference always means that the adjusted treatment effect is larger than the meta-analysis effect.
-Vice versa, a positive difference will indicate smaller adjusted effects.
-\\
+Additionally to the histogramms, Table \ref{adjustment.difference} shows the quantiles and means for the various differences.\\
+Copas estimates are equal to random effect in 1331 for $z$-score based analysis, 1144 for Hedges $g$ based analysis (and 1056 for analysis based on original effect measures). \\
+We see in Figure \ref{fig:adjustment.size} that bot reduction and amplification of original effect size occurs frequently.
+Nevertheless, there are more adjustments towards smaller effects for $z$-scores and Hedges $g$, regardless of the reference meta-analysis method.
+Survival outcomes, and $z$-scores meta-analyses and copas adjustment differences are exception to this.
+The larger proportion of reduction is mostly also reflected in the means and medians in Table \ref{adjustment.difference}.
+They are mostly around zero or larger, although not to a large extent.
+There is more extensive downward correction of effect sizes if random effects meta-analysis is used as the reference.
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Jun 27 15:12:39 2019
+% Fri Jun 28 16:35:32 2019
 \begin{table}[ht]
@@
   \hline
-z-score: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.05 & 402.37 \\ 
-  z-score: Random - Copas & -0.04 & 0.00 & 0.00 & 0.00 & 0.01 & 159.98 \\ 
-  z-score: Fixed - Regression & -0.15 & -0.05 & -0.01 & 0.04 & 0.13 & -0.01 \\ 
-  z-score: Random - Regression & -0.18 & -0.07 & -0.02 & 0.03 & 0.16 & -0.02 \\ 
-  Hedges g: Fixed - Copas & -0.09 & -0.01 & 0.00 & 0.01 & 0.05 & -0.02 \\ 
-  Hedges g: Random - Copas & -0.14 & 0.00 & 0.00 & 0.00 & 0.00 & -0.04 \\ 
-  Hedges g: Fixed - Regression & -0.39 & -0.13 & -0.04 & 0.04 & 0.24 & -0.05 \\ 
-  Hedges g: Random - Regression & -0.43 & -0.17 & -0.05 & 0.03 & 0.23 & -0.07 \\ 
-  Log hazard ratio: Fixed - Copas & -0.02 & -0.00 & 0.00 & 0.00 & 0.03 & 0.01 \\ 
-  Log hazard ratio: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.03 & 0.01 \\ 
-  Log hazard ratio: Fixed - Regression & -0.15 & -0.01 & 0.07 & 0.14 & 0.21 & 0.06 \\ 
-  Log hazard ratio: Random - Regression & -0.15 & -0.03 & 0.07 & 0.15 & 0.23 & 0.06 \\ 
+z-score: Fixed - Copas & -0.05 & -0.01 & -0.00 & 0.01 & 0.05 & -402.37 \\ 
+  z-score: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.04 & -159.98 \\ 
+  z-score: Fixed - Regression & -0.13 & -0.04 & 0.01 & 0.05 & 0.15 & 0.01 \\ 
+  z-score: Random - Regression & -0.16 & -0.03 & 0.02 & 0.07 & 0.18 & 0.02 \\ 
+  Hedges g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.09 & 0.02 \\ 
+  Hedges g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.14 & 0.04 \\ 
+  Hedges g: Fixed - Regression & -0.24 & -0.04 & 0.04 & 0.13 & 0.39 & 0.05 \\ 
+  Hedges g: Random - Regression & -0.23 & -0.03 & 0.05 & 0.17 & 0.43 & 0.07 \\ 
+  Log hazard ratio: Fixed - Copas & -0.03 & 0.00 & 0.00 & 0.00 & 0.02 & -0.01 \\ 
+  Log hazard ratio: Random - Copas & -0.03 & 0.00 & 0.00 & 0.00 & 0.00 & -0.01 \\ 
+  Log hazard ratio: Fixed - Regression & -0.21 & -0.14 & -0.07 & 0.01 & 0.15 & -0.06 \\ 
+  Log hazard ratio: Random - Regression & -0.23 & -0.15 & -0.07 & 0.03 & 0.15 & -0.06 \\ 
    \hline

### 2019-06-28 report/chapter03.Rnw
update

@@
 \Sexpr{both.bin}\% have significant Harbord's test result and significant excesss significance test result  (\Sexpr{both.bin.b}\% with bonferroni).
-Of the continuous outcomes, we have \Sexpr{both.else} \% with Egger's test and \Sexpr{both.else.b} with Bonferroni correction.
+Of the continuous outcomes, we have \Sexpr{both.else}\% with Egger's test and \Sexpr{both.else.b}\% with Bonferroni correction.
 
@@
 
-  transmute(copas.z.f = est.z.copas.f - est.z.fixef,
-            copas.z.r = est.z.copas.r - est.z.ranef,
-            reg.z.f = est.z.reg.f - est.z.fixef,
-            reg.z.r = est.z.reg.r - est.z.ranef,
-
-            copas.d.f = est.d.copas.f - est.d.fixef,
-            copas.d.r = est.d.copas.r - est.d.ranef,
-            reg.d.f = est.d.reg.f - est.d.fixef,
-            reg.d.r = est.d.reg.r - est.d.ranef)
+  transmute(copas.z.f = est.z.fixef - est.z.copas.f,
+            copas.z.r = est.z.ranef - est.z.copas.r,
+            reg.z.f = est.z.fixef - est.z.reg.f,
+            reg.z.r = est.z.ranef - est.z.reg.r,
+
+            copas.d.f = est.d.fixef - est.d.copas.f,
+            copas.d.r = est.d.ranef - est.d.copas.r,
+            reg.d.f = est.d.fixef - est.d.reg.f,
+            reg.d.r = est.d.ranef - est.d.reg.r)
 
@@
 
-  transmute(copas.surv.f = est.copas.f - est.fixef,
-            copas.surv.r = est.copas.r - est.ranef,
-
-            reg.surv.f = est.reg.f - est.fixef,
-            reg.surv.r = est.reg.r - est.ranef)
+  transmute(copas.surv.f = est.fixef - est.copas.f,
+            copas.surv.r = est.ranef - est.copas.r,
+
+            reg.surv.f =  est.fixef - est.reg.f,
+            reg.surv.r = est.ranef - est.reg.r)
 
@@
                                    "g fixed", "g random", "g Copas", "g regression")
+
+adjustment.smaller.reg.z.f <- round(length(which(adjustment.diff$reg.z.f > 0))/length(which(!is.na(adjustment.diff$reg.z.f)))*100, 1)
+
+adjustment.smaller.reg.z.r <- round(length(which(adjustment.diff$reg.z.r > 0))/length(which(!is.na(adjustment.diff$reg.z.r)))*100, 1)
 @
@@
 
-If one is interested in the mere change in effect size and if the effect size did decrease or increase after adjustment, one can look at Figure \ref{fig:adjustment.size}.
-It displays the difference between the meta-analysis pooled treatment effect and the adjusted treatment effect.
-To compare the overall effect of adjustment for small study effects, the absolute value of the effect size is used.
-Thus, a negative difference indicates larger adjusted treatment effect size than meta-analysis pooled effect size.
+There are two possibilities when adjusting the pooled treatment effect of meta-analyses for publication bias.
+The absolute size of the treatment effect can be smaller, or larger after adjustment.
+Additionally, it is of interest by how much the treatment effect is diminishued or increased.
+\\
+Figure \ref{fig:adjustment.size} displays the difference between the meta-analysis pooled treatment effect $\theta_M$ and the adjusted treatment effect $\theta_\textrm{Adj.}$ for the copas and regression adjustment methods and fixed and random effects meta-analysis.
+The treatment effects are mirrored on the positive side, such that a positive difference indicates that the effect size was smaller after adjustment (and analogously, larger if the difference is negative).
 For better illustration, some very large and very small differences have been ommitted in the $z$-score and Hedges $g$ histogramms; the missing differences are provided in Table \ref{missing.differences}.
-Additionally to the histogramms, Table \ref{adjustment.difference} shows the quantiles and means for the various differences.
-%For sake of interpretability, negative effect sizes are changed to positive, such that a negative difference always means that the adjusted treatment effect is larger than the meta-analysis effect.
-Vice versa, a positive difference will indicate smaller adjusted effects.
+Additionally to the histogramms, Table \ref{adjustment.difference} shows the quantiles and means for the various differences.\\
+Copas estimates are equal to random effect in \Sexpr{meta.f$se.est.z.copas.missing[1]} for $z$-score based analysis, \Sexpr{meta.f$se.est.d.copas.missing[1]} for Hedges $g$ based analysis (and \Sexpr{meta.f$se.est.copas.missing[1]} for analysis based on original effect measures).
 \\
+We see in Figure \ref{fig:adjustment.size} that bot reduction and amplification of original effect size occurs frequently.
+Nevertheless, there are more adjustments towards smaller effects for $z$-scores and Hedges $g$, regardless of the reference meta-analysis method.
+Survival outcomes, and $z$-scores meta-analyses and copas adjustment differences are exception to this.
+The larger proportion of reduction is mostly also reflected in the means and medians in Table \ref{adjustment.difference}.
+They are mostly around zero or larger, although not to a large extent.
+There is more extensive downward correction of effect sizes if random effects meta-analysis is used as the reference.
 

### 2019-06-28 code/new_meta_analysis.R

@@ -680,13 +680,19 @@ meta.f <- merge(meta.f, excess.significance.results, by = c("meta.id"), all.x = 
 #Inpute random effect estimate for missing copas:
 copas.names <- c("est.copas", "se.est.copas", "est.z.copas", "se.est.z.copas", "est.d.copas", "se.est.d.copas")
 ranef.names <- c("est.ranef", "se.est.ranef", "est.z.ranef", "se.est.z.ranef", "est.d.ranef", "se.est.d.ranef")
+missing.names <- paste(copas.names, ".missing", sep = "")
+missing <- c()
 
 for(u in 1:length(copas.names)){
+  missing.count <- 0
   for(k in 1:dim(meta.f)[1]){
     if(is.na(meta.f[k, copas.names[u]])){
+      missing.count <- missing.count + 1
       meta.f[k, copas.names[u]] <- meta.f[k, ranef.names[u]]
     }
   }
+  missing[u] <- missing.count
+  meta.f[, missing.names[u]] <- missing.count
 }
 
 

### 2019-07-01 report/MSc_Report.tex
correction of tes

--- 2019-06-24 report/MSc_Report.tex
@@
 There are also issues, in which statistics is not thought to be able to contribute much to understanding and to be of little help for solving them.
-For example, the selective attention that the agents in science are paying to new, strong and clear findings in each science is considered merely a psychological and social%, socioeconomic
+For example, the selective attention that the agents in science are paying to new, strong and clear findings in each science is considered merely a psychological and social %, socioeconomic
 issue.
@@
 Almost all the time, alternative explanations for the results of the methods might relieve the operators and publishers from the reproval of publication bias.
-However, given the large body of evidence for publication bias collected in other ways, those can probably be expelled most of the time, such that those methods indeed give a quantitative measure of publication bias.
-\\
+However, given the large body of evidence for publication bias collected from other sources (...), in many cases, the results from these methods indeed give a quantitative measure of publication bias.\\
 In this masters thesis, the answers for two questions are investigated: What is the extent and effect of publication bias in clinical science?
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jun 17 16:15:38 2019
+% Mon Jul  1 17:02:14 2019
 \begin{table}[ht]
@@
 \end{tikzpicture}
-\caption{Structure of a hypothetical review with two different comparisons\label{review.structure}}
+\caption{Structure of a hypothetical review with two different comparisons}
 \label{review.structure}
@@
 
-The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982).
+The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982, 95\% quantile = 2013,).
 The median of the publication years is 2003, the mean 2001 and the quartiles are 1996 and 2008.
@@
 \begingroup\footnotesize
-\begin{tabular}{lll}
+\begin{tabular}{lrr}
   \hline
@@
 The sample sizes among results vary to some extent.
-There are 5\% of treatment group sample sizes that are smaller than 8, the 5\% quantile.
+There are 5\% of treatment group sample sizes that are smaller than 8, the 5\% quantile and 95\% smaller than 551.
 The first quartile is 22, the median 48, the mean 302.03 and the third quartile 119.
 The large difference between median and mean is caused by very large groups with over 2,000,000 participants.
-Analogously, the quantiles of the total sample size are: 5\% quantile = 15, first quartile = 44, median = 94 and third quartile = 229.
+Analogously, the quantiles of the total sample size are: 5\% quantile = 15, first quartile = 44, median = 94, third quartile = 229 and 95\% = 1044.
 The mean is 617.81.
@@
 There are 417 reviews with five or fewer results, and the quartiles are 16 and 102.
-Similarly, the number of reviews with a maximum of two studies included is 836, the mean study number is 12.42, the median 7 and the interquartile range 4 and 15.
-The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1497 results in total.
-\\
+Similarly, the number of reviews with a maximum of two studies included is 836, the mean study number is 12.42, the median 7 and the interquartile range 4 and 15 and the 95\% quantile 40.
+The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1497 results in total.\\
 For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome.
@@
 Importantly, this distinction is also used by the Cochrane Organization itself, i.e.
-the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\%Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
+the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
 The dataset is divided in meta-analyses with identical experimental setup. The size of a meta-analysis denotes how many results are included in a group.
-Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results. Practically, this number of meta analyses can be performed, with each having at least $n$ results:
+Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results. Practically, this number of meta analyses can be performed, with each having at least $n$ results.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jun 17 16:15:38 2019
+% Mon Jul  1 17:02:14 2019
 \begin{table}[ht]
@@
 \endgroup
-\caption{Cumulative number of groups with number of reproduction trials >= n} 
+\caption{Cumulative number of groups with number of reproduction trials $\geq$ n} 
 \label{repr.groups}
@@
 
-\section{Small Study Effect and Excess of Singificance Tests}
-
-The results of the test for small study effects and excess of significance for the meta-analyses fullfilling the criteria from chapter \ref{chapter02}, section \ref{sec:Processing}, are presented in Figure \ref{fig:test}.
-%Figures \ref{fig:test.bin}, \ref{fig:test.cont} and \ref{fig:test.surv}. 
-The histogram of the $p$-values is displayed separately for binary, continuous and survival outcome types (as previously defined in the dataset variable \texttt{outcome.type}, see chapter \ref{ch:chapter02}, section \ref{sec:Processing}.
-The distributions are (with the exception of Schwarzer's test) skewed to the right, indicating evidence for small study effects.
-Moreover, the excess significance tests have a mode around $p = 0.4$.
-Large differences between small study effect tests for binary and continuous outcomes will be subject to discussion.
-\\
-``Excess significance'' denotes the excess of significance $p$-values from the test of \citet{excess.significance}. For continuous and survival outcomes, the names refer to:
+\section{Small Study Effect and Excess of Significance Tests} \label{sec:publication.bias.tests}
+
+The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with small study effects tests and excess significance tests.
+We will apply the tests on the original effect size measures, i.e.
+risk ratios, Hedges $g$ or log hazard ratios.
+Different tests are applied depending on if the outcomes are of type binary or continuous or survival.\\
+Thus, we apply multiple tests on the same data.
+The results can then be displayed separately to compare the different tests.
+A histogram of $p$-values will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.
+\\
+``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}.
+For continuous and survival outcomes, the names refer to:
 
 \begin{itemize}
-\item Egger's test, the weigthed linear regression test as described in section \ref{sec:Egger}
+\item Egger's test, the weighted linear regression test as described in section \ref{sec:Egger}
 \item Thompson and Sharp's test, the weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
@@
 \caption{Histogram of the $p$-values for small study effect in meta-analyses.
-The testing method is indicated in the header, binwidth is equal to 0.1.
+The testing method is indicated in the header, bin width is equal to 0.1.
 The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
@@
 
-The agreement/coinicidence between between small study effect and excess significance tests is often not pronounced, thus, it will be compared by different methods.
-This is displayed in Table \ref{test.agreement}.
-The row names indicate which two tests are compared.
-First, the column ``Test Agreement'' quantifies the overall proportion by which the two tests agree in their rejection or ``acceptance'' of the null-hypothesis.
-``Test Agreement'' being equal one thus indicates equivalent results, zero no correspondence whatsoever.
-The second column, ``Correlation'' gives the correlation between the $p$-values.
-A positive correlation indicates psotive coincidence of $p$-values, negative correlation coincidence in opposite directions.
-However, the scale might be different for this agreement measure.
-The ``R-squared'' value indicates to what extent one $p$-value can be predicted by another, and ignores additive differences between $p$-values (as for correlation), as well as multiplicative constants between them (i.e.
-$y ~ a + b*x$, $y$ and $x$ being two $p$-values of test-statistics).
-An R-squared value of 1 indicates perfect fit.
-Importantly, the order of the variables does not matter for the $p$-values for all indicators (i.e.
-$p$-values for $x$ and $y$ can be exchanged and the table stays the same).
-If a test is completely replaceable by another, all values in a row are equal to one.
+%Agreement table -> Chunck 1
+The histograms in Figure \ref{fig:test} show that the distributions are (with the exception of Schwarzer's test) skewed to the right for all outcome types, indicating evidence for small study effects and excess significance, respectively.
+Moreover, the excess significance tests have a mode around $p = 0.4$.
+There is some discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger.
+Survival outcome type results are quite different with very few evidence for small study effects and excess significance.
+Note that the sample size of survival outcomes is small ($n$ = 39).\\
+It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects/excess significance for the same meta-analyses.
+A simple method to check the coincidence of test results is to compare scatterplots and empirical Spearman correlations between the test statistics.
+This is done in Figure \ref{fig:test.agreement}.
+Here, there is no separation between survival and continuous outcomes.
+The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-11-1}
+
+}
+
+\end{knitrout}
+\caption{Pairs-plot for test statistics of small study effect and excess significance.
+The lower panel gives the Spearman correlations for the different test statistics, and the upper panel displays a scatterplot.
+The colors indicate magnitude and direction of the correlation coefficients.
+The rectangle with white borders displays the area within which both tests have absolute value < 1.64 (dots outside are statistically significant using the 0.1 threshold).}
+\label{fig:test.agreement}
+\end{figure}
+
+The observed patterns on the scatterplots differ: Excess significance and small study effect test statistics do usually not align with each other, forming rather randomly scattered bulks of points.
+Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients.
+In general, small study effect tests align on the diagonal, but the extent to which they align differs.
+Continuous and survival outcome type tests align more closely than binary outcome tests.
+While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics .\\
+Because scatterplots and correlation coefficients can be misleading, also a Tukey mean-difference or Bland-Altman of transformed $p$-values plot is shown for four scenarios in Figure \ref{fig:mean.diff.test}:
+\begin{itemize}
+\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
+\item For Egger's and excess significance tests
+\item For Harbord's and R\"ucker's tests
+\item For Harbord's and excess significance tests
+\end{itemize}
+
+This can be justified since all tests are supposed to measure the evidence for publication bias.
+For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation $f(x)  = \log\frac{p}{1-p}$).
+The mean $p$-value (($f$($p$-value no.
+1) + $f$($p$-value no.
+2))/2) is then displayed against the difference between the $f$($p$-value).
+If no systematic errors and biases exist between the measurement methods, then
+
+\begin{itemize}
+\item the mean of the differences should be around zero (systematic error) 
+\item the points should scatter independently on the $y$-axis and no general increase or decrease with the mean of the transformed $p$-values should be visible
+\end{itemize}
+
+Although this is not formally tested, the last criterium seems not to be given when comparing small study effect and excess significance tests.
+With decreasing mean, the difference gets more negative, and vice versa, such that one would predict that the excess significance $p$-values are more ``extreme'' in both directions.
+-- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- However, the systematic error between the compared tests is close to zero, and small study effect tests do probably not show bias when compared to each other.
+\\
+The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests.
+This suggests that correspondence between the tests is not very good in general.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-12-1}
+
+}
+
+\end{knitrout}
+\caption{Mean - difference plots for logit transformed $p$-values.
+The mean of logit transformed $p$-values is displayed on the $x$-axis and the difference on the $y$-axis.
+Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).}
+\label{fig:mean.diff.test}
+\end{figure}
+
+The previous results suggest that the results will also differ substantially after applying the common dichotomization of $p$-values.
+We expect that some proportion of the meta-analysis will only be significant for a certain test, and this is indeed observed in Table \ref{number.sig.tests}.
+It displays the percentage of meta-analyses with a certain number of significant test results.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jun 24 17:05:43 2019
+% Mon Jul  1 17:11:00 2019
 \begin{table}[ht]
@@
 \begingroup\footnotesize
-\begin{tabular}{lccc}
-  & Test Agreement & p-value Correlation & p-value R-squared \\ 
-  \hline
-\hline
-Excess significance, Schwarzer & 0.83 & -0.02 & 0.00 \\ 
-  Excess significance, Peter & 0.80 & 0.05 & 0.00 \\ 
-  Excess significance, Rucker & 0.82 & 0.12 & 0.02 \\ 
-  Excess significance, Harbord & 0.81 & 0.02 & 0.00 \\ 
-  Peter, Schwarzer & 0.82 & 0.29 & 0.09 \\ 
-  Schwarzer, Rucker & 0.82 & 0.29 & 0.08 \\ 
-  Schwarzer, Harbord & 0.86 & 0.51 & 0.26 \\ 
-  Rucker, Peter & 0.89 & 0.64 & 0.41 \\ 
-  Harbord, Peter & 0.86 & 0.48 & 0.23 \\ 
-   \hline
-Excess significance, Egger & 0.79 & 0.14 & 0.02 \\ 
-  Excess significance, Thompson & 0.80 & 0.16 & 0.02 \\ 
-  Excess significance, Begg & 0.81 & 0.10 & 0.01 \\ 
-  Thompson, Egger & 0.95 & 0.91 & 0.83 \\ 
-  Thompson, Begg & 0.87 & 0.70 & 0.49 \\ 
-  Egger, Begg & 0.86 & 0.65 & 0.42 \\ 
-   \hline
-Excess significance, Egger (survival) & 0.69 & 0.03 & 0.00 \\ 
-  Excess significance, Thompson (survival) & 0.64 & 0.05 & 0.00 \\ 
-  Excess significance, Begg (survival) & 0.62 & 0.18 & 0.03 \\ 
-  Thompson, Egger (survival) & 0.90 & 0.92 & 0.85 \\ 
-  Thompson, Begg (survival) & 0.92 & 0.66 & 0.43 \\ 
-  Egger, Begg (survival) & 0.87 & 0.70 & 0.48 \\ 
+\begin{tabular}{ccc}
+  \hline
+Count & Binary Outcomes & Continuous and Survival \\ 
+  \hline
+0 & 66.1 \% & 72.5 \% \\ 
+  1 & 16.1 \% & 7.5 \% \\ 
+  2 & 8.8 \% & 8 \% \\ 
+  3 & 5.7 \% & 10.5 \% \\ 
+  4 & 3 \% & 1.5 \% \\ 
+  5 & 0.4 \% & - \\ 
    \hline
@@
 \endgroup
-\caption{Agreement in significance proportion, correlation and R-squared of linear regression
-             between the p-values of the publication bias tests. Horizontal lines separate binary, continuous and survival outcomes (order as in table).} 
-\label{test.agreement}
+\caption{Counts Number of significant test results per meta-analysis, separated
+       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
+       applied} 
+\label{number.sig.tests}
 \end{table}
+
+Here, it is difficult to say if continuous and survival or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and survival outcome type tests have in general more positive findings.
+Very few meta-analyses are significant, irrespective of the test used, but around 67\% of the dataset is not significant, no matter which test is used.
+\\
+When only looking at small study effect tests, 29.1\% of binary outcome tests and 26.2\% of survival and continuous outcome tests had at least one significant result.
+This also suggests that the overlap between small study effect tests and excess significance is small.
+After applying the Bonferroni correction for multiple testing, this shrinks to 10.9\% for binary and 12.1\% for continuous and survival outcomes.
+\\
+To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test.
+22.4\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 23.4\% for continuous and survival outcomes.
+The numbers change to 13.4\% for binary outcomes and 13.4\% for continuous and survival outcomes after applying the Bonferroni correction.
+\\
+2.7\% have significant Harbord's test result and significant excess significance test result  (1.1\% with Bonferroni).
+Of the continuous outcomes, we have 3.3\% with Egger's test and 0.8\% with Bonferroni correction.
 
@@
 
-\subsection{Change in Effect Size after Adjustment}
-
-If one is interested in the mere change in effect size and if the effect size did decrease or increase after adjustment, one can look at Figure \ref{fig:adjustment.size}.
-It displays the difference between the meta-analysis pooled treatment effect and the adjusted treatment effect.
-To compare the overall effect of adjustment for small study effects, the absolute value of the effect size is used.
-Thus, a negative difference indicates larger adjusted treatment effect size than meta-analysis pooled effect size.
-For better illustration, some very large and very small differences have been ommitted in the $z$-score and Hedges $g$ histogramms; the missing differences are provided in Table \ref{missing.differences}.
-Additionally to the histogramms, Table \ref{adjustment.difference} shows the quantiles and means for the various differences.
-%For sake of interpretability, negative effect sizes are changed to positive, such that a negative difference always means that the adjusted treatment effect is larger than the meta-analysis effect.
-Vice versa, a positive difference will indicate smaller adjusted effects.
-\\
+\subsection{Change in Effect Size after Adjustment} \label{sec:change.size}
+
+Since there's evidence for publication bias when applying small study effect and excess significance tests, we apply small study effect adjustment methods to correct for small study effect tests. \\
+We will see that consequences of adjustment can be; 
+\begin{itemize}
+\item first, the absolute size of the treatment effect can be smaller than the classical meta-analysis treatment effect, which is expected if publication bias
+is the cause for the small study effect.
+\item secondly, the effect can be larger than before in meta-analysis.
+In this case, the small study effect must be not due to publication bias for large effects (``true'' publication bias), but due to bias for small effects (``negative publication bias'').
+\end{itemize}
+
+In section \ref{sec:comparison.tests.adjustment}, it will be followed up on the latter point. For now, we will examine the extent and the frequencies of the two scenarios. \\
+To compare the effects of adjustment between meta-analyses, the outcome measures are transformed to Hedges $g$ (standardized mean differences) and Fisher's $z$-score (see section \ref{sec:transformation.effectsizes} for details).
+The effect of adjustment can additionally be compared to either random or fixed effects meta-analysis.
+\\
+Figure \ref{fig:adjustment.size} displays the difference $\delta$ between the observed meta-analysis pooled treatment effect and the adjusted treatment effect, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
+The absolute value $|\hat{\theta}_M|$ is taken and the sign of $\hat{\theta}_\textrm{Adj.}$ is adjusted accordingly such that all effects are mirrored to one side.
+$\delta > 0$ is equivalent to $\hat{\theta}_\textrm{Adj} < \hat{\theta}_M$, a reduction of the original effect size.
+For better illustration, some very large and very small differences have been omitted in the $z$-score and Hedges $g$ histograms; they are shown in Table \ref{missing.differences}.
+Table \ref{adjustment.difference} shows the quantiles and means for the various differences and additional information.\\
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jun 24 17:05:45 2019
+% Mon Jul  1 17:11:03 2019
+\begin{table}[ht]
+\centering
+\begingroup\scriptsize
+\begin{tabular}{lcccccccccr}
+  \hline
+ & 5\% & 25\% & 50\% & 75\% & 95\% & mean & = 0 (\%) & $>$= 0 (\%) & $>$ 0 (\%) & No adj. est. (\%) \\ 
+  \hline
+z: Fixed - Copas & -0.05 & -0.01 & -0.00 & 0.01 & 0.05 & -271.73 & 4.76 & 48.67 & 43.91 & 71.54 \\ 
+  z: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.04 & -263.62 & 71.65 & 89.42 & 17.77 & 71.54 \\ 
+  z: Fixed - Regression & -0.13 & -0.03 & 0.01 & 0.05 & 0.14 & 0.01 & 0.00 & 52.44 & 52.44 & 0.17 \\ 
+  z: Random - Regression & -0.15 & -0.03 & 0.02 & 0.07 & 0.18 & 0.02 & 0.00 & 57.64 & 57.64 & 0.17 \\ 
+  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.09 & 0.02 & 22.76 & 59.14 & 36.38 & 60.96 \\ 
+  g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.14 & 0.03 & 63.29 & 87.49 & 24.20 & 60.96 \\ 
+  g: Fixed - Regression & -0.23 & -0.04 & 0.03 & 0.13 & 0.38 & 0.05 & 0.00 & 61.96 & 61.96 & 0.00 \\ 
+  g: Random - Regression & -0.24 & -0.03 & 0.05 & 0.16 & 0.42 & 0.06 & 0.00 & 64.06 & 64.06 & 0.00 \\ 
+  Log h.r.: Fixed - Copas & -0.02 & 0.00 & 0.00 & 0.00 & 0.02 & -0.00 & 46.15 & 35.90 & 82.05 & 56.41 \\ 
+  Log h.r.: Random - Copas & -0.02 & 0.00 & 0.00 & 0.00 & 0.00 & -0.01 & 61.54 & 17.95 & 79.49 & 56.41 \\ 
+  Log h.r.: Fixed - Regression & -0.20 & -0.13 & -0.06 & 0.02 & 0.14 & -0.05 & 0.00 & 33.33 & 33.33 & 0.00 \\ 
+  Log h.r.: Random - Regression & -0.22 & -0.14 & -0.07 & 0.03 & 0.14 & -0.06 & 0.00 & 33.33 & 33.33 & 0.00 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects.
+The column with the names ``> 0'' give the percentages of estimates larger than zero or larger or equal zero.
+The column ``No adj.
+est.'' gives the percentage of missing estimates due to non-significant publication bias test (for Copas) and computational errors.
+The row names indicate which outcome measure, meta-analysis method and adjustment method is used.
+Abbreviations are used for z-score (= z) and Hedges g (= g).}
+\label{adjustment.difference}
+\end{table}
+
+Adjustment leads most often to reduction of treatment effect estimates, as can be seen by the size of the bins of the right part of the histograms in Figure \ref{fig:adjustment.sue}.
+The difference between the bins on the right and left side of the zero-centered bin is however not very large in general.
+The seeming exception of the Copas selection model in the case with $z$-scores and fixed effects reference requires closer examination: Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
+Thus, when comparing Copas with Fixed effects, we compare most often random effects with fixed effects estimates.
+The effect of adjustment by Copas can therefore only be seen when comparing random effects estimates with fixed effect estimates: we can see in Table \ref{adjustment.difference} that we have, for $z$-score, 18.4\% reduced effect sizes compared to 10.3\% (= 100\% - 89.69\%) increased effect sizes.
+Thus, the Copas selection model also has a larger proportion of reduced effect sizes compared to amplified.\\
+%This resolves the case for the seeming exception and for Hedges $g$'s, 24.4\% and 12.46\% (Table \ref{adjustment.difference}. 
+Also, there are more reduced effect sizes if random effects meta-analysis is used as a reference effect size.
+When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
+\\
+The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 90 cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or 90 increased by -0.13, fixed effects reference).
+Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or 90 meta-analyses (or increased by 0.24).
+
+\subsection{Change in Evidence for Treatment Effects} \label{sec:change.evidence}
+Adjustment for small study effects in meta-analysis will not only provide new effect sizes, but also standard errors thereof.
+Thus, also the evidence for efficacy of a treatment can be obtained, which is usually summarized in a suitable test statistic or $p$-value.
+It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.\\
+The Wald test statistics $p$-value for fixed and random effects meta-analyses and Copas and regression adjusted treatment effects have been calculated.
+They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and log hazard ratios.
+\\
+It can be seen that evidence for a treatment effect decreases after adjusting for publication bias.
+It does so more for Hedge's $g$ compared to $z$-scores, and for regression adjustment compared to Copas selection model.
+%Also, the evidence decreases for random effects meta-analyses compared to fixed effects meta-analyses. 
+In the case of log-hazard ratio adjustment, the adjustment has only negligible impact on the $p$-values. \\
+Also, Copas selection method has a very small impact on the evidence compared to random effects meta-analysis, at least using $z$-scores (again, we should rely on comparisons to random effects meta-analysis to evaluate Copas method).
+\\
+% Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
+%Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted Hedges $g$ and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-17-1}
+
+}
+
+\end{knitrout}
+\caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
+The method is indicated in the header, bin width is set to 0.05.
+The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
+\label{fig:adjustment.stat}
+\end{figure}
+
+The Copas selection model also gives an estimate of the number of missing studies.
+It finds that 0 are missing, which corresponds to 0\% from all \ensuremath{2.8945\times 10^{4}} analysed studies.
+Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
+Note that we have excluded 0 out of 1806, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-18-1}
+
+}
+
+\end{knitrout}
+\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ 0)}
+\label{fig:copas.missing}
+\end{figure}
+
+We can see that in some occasions, the method finds more than half of all studies are missing.
+In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
+The discrepancy between mean and median may indicate that the estimate of 0\% missing studies depends somewhat on these extreme cases.
+As can be written of from Table \ref{copas.missing}, 5\%, \ie 0 meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for 0, more than 30\% of missing studies.
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Mon Jul  1 17:11:05 2019
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lrrrrrrr}
+  \hline
+ & = 0 & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
+  \hline
+Missing fraction & 323 & 0 & 0 & 0.1 & 0.3 & 1.0 & 0.2 \\ 
+  Missing study number & 323 & 0 & 0 & 1.4 & 5.2 & 17.9 & 4.2 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.} 
+\label{copas.missing}
+\end{table}
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Mon Jul  1 17:11:05 2019
 \begin{table}[ht]
@@
 2009 & 2009 & 1 & 1 & 0.31 & 0.36 & 0.31 & 0.43 & 0.70 & 0.70 & 0.70 & 2.48 \\ 
-  2068 & 2068 & 2 & 0 & 0.29 & 0.35 & 0.29 & 0.43 & 0.68 & 0.68 & 0.68 & 2.57 \\ 
-  18658 & 18658 & 2 & 0 & 1.16 & 1.14 & 1.16 & 1.17 & 1.40 & 2.85 & 1.40 & 1.74 \\ 
-  46472 & 46472 & 1 & 1 & 1.79 & 1.44 & 1.79 & 0.66 & 0.12 & 6.97 & 6.97 & 0.79 \\ 
+  2068 & 2068 & 2 & 0 & 0.29 & 0.35 & 0.29 & 0.42 & 0.68 & 0.68 & 0.68 & 2.57 \\ 
   52528 & 52528 & 1 & 0 & -0.75 & -0.69 & -0.50 & -0.26 & -1.19 & -1.53 & 0.18 & -0.52 \\ 
   60546 & 60546 & 1 & 1 & 0.17 & 0.24 & 0.17 & 0.34 & 0.53 & 0.53 & 0.53 & 1.65 \\ 
-  70389 & 70389 & 1 & 1 & -0.08 & -0.07 & 15.58 & -0.04 & -0.13 & -0.13 & -0.13 & -0.05 \\ 
-  73769 & 73769 & 3 & 1 & -0.14 & 0.00 & 214760.42 & -0.04 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
+  70389 & 70389 & 1 & 1 & -0.08 & -0.07 & 15.62 & -0.04 & -0.13 & -0.13 & -0.13 & -0.05 \\ 
+  73769 & 73769 & 3 & 1 & -0.09 & 0.00 & 7148.96 & 0.02 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
   79113 & 79113 & 2 & 0 & -0.38 & -0.38 & -0.38 & -0.48 & -0.93 & -0.93 & -2.00 & -3.47 \\ 
-  90138 & 90138 & 3 & 0 & 0.31 & 0.80 & 0.31 & 0.55 & 0.72 & 0.71 & 0.71 & 2.16 \\ 
-  97356 & 97356 & 2 & 0 & -0.08 & -0.33 & -0.08 & -0.17 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
+  90138 & 90138 & 3 & 0 & 0.30 & 0.80 & 0.30 & 0.53 & 0.72 & 0.71 & 0.71 & 2.16 \\ 
+  97356 & 97356 & 2 & 0 & -0.06 & -0.33 & -0.06 & -0.11 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
   98030 & 98030 & 1 & 0 & -0.09 & -0.07 & -0.09 & -0.04 & -0.41 & -0.41 & -1.50 & -2.79 \\ 
-  101436 & 101436 & 1 & 5 & 0.54 & 0.62 & 0.80 & 0.91 & 1.21 & 1.21 & 1.21 & 2.74 \\ 
-  118121 & 118121 & 4 & 1 & 0.25 & 0.23 & 71.80 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
+  101436 & 101436 & 1 & 5 & 0.54 & 0.62 & 0.80 & 0.90 & 1.21 & 1.21 & 1.21 & 2.74 \\ 
+  118121 & 118121 & 4 & 1 & 0.25 & 0.23 & 47.73 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
   119537 & 119537 & 3 & 0 & 0.07 & 0.15 & 0.07 & 0.29 & 0.50 & 0.50 & 1.43 & 1.81 \\ 
-  119818 & 119818 & 3 & 3 & -0.25 & -0.25 & -0.11 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
-  146301 & 146301 & 1 & 0 & 0.14 & 0.26 & 498188.34 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
+  119818 & 119818 & 3 & 3 & -0.25 & -0.25 & -0.20 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
+  146301 & 146301 & 1 & 0 & 0.14 & 0.26 & 472149.03 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
    \hline
@@
 \endgroup
-\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects
-             of Figure 
-ef{fig:adjustment.size}. Abbreviations are used for z-score (z) and Hedges g (g)} 
+\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects. Abbreviations are used for z-score (= z) and Hedges g (= g).} 
 \label{missing.differences}
@@
 
+\subsection{Comparison of adjustment methods}
+Regression adjusted estimates are compared to the estimates of Copas selection model if these are not equal to random effects meta-analysis.
+A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
+We will compare estimates based on all three outcome measures, i.e.
+original measure, $z$-score and Hedges $g$ in Figure \ref{fig:adjustment.mean.diff}.
+Note that the 39 survival outcome data is not included when using $z$-score and Hedges $g$.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-21-1}
+
+}
+
+\end{knitrout}
+\caption{Mean - difference plots for publication bias adjustment methods.
+The mean of the adjusted treatment effects is displayed on the $x$-axis and the difference on the $y$-axis.
+Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).
+Two values have been omitted in the middle plot for Hedges $g$ and one for $z$-score (see Table \ref{missing.differences}).}
+\label{fig:adjustment.mean.diff}
+\end{figure}
+
+No formal tests are provided, but the at least there seems to be no clear bias or systematic.
+The limits of agreement in Figure \ref{fig:adjustment.mean.diff} are large.
+We conclude thus that the impact of regression adjustment on the effect sizes is in general not substantially larger than the impact of Copas selection model in the subset of data where the estimate of the Copas selection model is not equal to a random effects estimate.
+\\
+
+\section{Comparison of Tests and Adjustments} \label{sec:comparison.tests.adjustment}
+
+In section \ref{sec:change.size}, we have seen that some adjustments for small study effects are not in line with our previous definition of publication bias: Some times, the adjustment for small study effects leads to a larger treatment effect.
+We want to take this into account when considering evidence for publication bias.
+Whenever adjustment leads to larger effect sizes, the small study effect test result from section \ref{sec:publication.bias.tests} is revised and changed to negative.
+We will revisit the results from section \ref{sec:publication.bias.tests} and first visualize which proportion of the data finds rather ``negative publication bias'' than the predefined type of publication bias.
+Figure \ref{fig:test.corrected} is equal to Figure \ref{fig:test} with sole difference that now the proportion of ``negative publication bias'' is colored, and the count of significant findings is corrected (not significant for negative publication bias).
+\\
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-23-1}
+
+}
+
+\end{knitrout}
+\caption{Histogram of the $p$-values for small study effect in meta-analyses.
+The testing method is indicated in the header, bin width is equal to 0.1.
+The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
+\label{fig:test.corrected}
+\end{figure}
+
+The proportion of findings where we found amplification by adjustment was 34.5\%.
+Most often, the proportion of tests with evidence for small study effects (and especially, excess significance), is lower, though.
+There are exceptions to this, such as Schwarzer's test results, where we have 143 - 60 = 83 significant test results, which corresponds to $\sim$ 40\%.
+Since excess significance is not necessarily connected with small study effects, we can furthermore reject the newly obtained, slightly smaller number of significant excess significance test results, and stick to the previous findings.
+\\
+We can see how the agreement in significance is before, and after having removed negative publication bias significant results in Table \ref{test.agreement}.
+The proportion of agreement in significance is defined as the proportion of cases where, when the test with less significant findings is significant, also the other is significant.
+\\
+After the adjustment of the test results, the agreement for small study effects tests and excess significance tests increases a bit.
+This seems also to be the general trend, but not without exceptions.
+The two right-most columns indicate the agreement in significance, and we see that agreement is never larger than 0.3 (with Egger's test, continuous outcomes).
+Furthermore, only Egger and Thompson show a goof agreement for significance ($\sim$ 0.83).
+In contrast, some small study effect tests for binary outcomes seem rather to be exclusive, see for example the example of Schwarzer's test (6\% after adjustment) and R\"ucker's test (11\%): Only 19 \% of the cases where Schwarzer's Test is significant have also a significant finding using R\"ucker's test.
+Almost all binary small study effect tests have agreement in significance > 0.5.
+Thus, we see that large overall agreement is rather due to the large proportion of non-significant findings.
+
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jun 24 17:05:45 2019
+% Mon Jul  1 17:11:08 2019
 \begin{table}[ht]
@@
 \begingroup\scriptsize
-\begin{tabular}{lcccccc}
-  \hline
- & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
-  \hline
-z-score: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.05 & 402.37 \\ 
-  z-score: Random - Copas & -0.04 & 0.00 & 0.00 & 0.00 & 0.01 & 159.98 \\ 
-  z-score: Fixed - Regression & -0.15 & -0.05 & -0.01 & 0.04 & 0.13 & -0.01 \\ 
-  z-score: Random - Regression & -0.18 & -0.07 & -0.02 & 0.03 & 0.16 & -0.02 \\ 
-  Hedges g: Fixed - Copas & -0.09 & -0.01 & 0.00 & 0.01 & 0.05 & -0.02 \\ 
-  Hedges g: Random - Copas & -0.14 & 0.00 & 0.00 & 0.00 & 0.00 & -0.04 \\ 
-  Hedges g: Fixed - Regression & -0.39 & -0.13 & -0.04 & 0.04 & 0.24 & -0.05 \\ 
-  Hedges g: Random - Regression & -0.43 & -0.17 & -0.05 & 0.03 & 0.23 & -0.07 \\ 
-  Log hazard ratio: Fixed - Copas & -0.02 & -0.00 & 0.00 & 0.00 & 0.03 & 0.01 \\ 
-  Log hazard ratio: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.03 & 0.01 \\ 
-  Log hazard ratio: Fixed - Regression & -0.15 & -0.01 & 0.07 & 0.14 & 0.21 & 0.06 \\ 
-  Log hazard ratio: Random - Regression & -0.15 & -0.03 & 0.07 & 0.15 & 0.23 & 0.06 \\ 
+\begin{tabular}{lcccc}
+  & pre, overall & post, overall & pre, significance & post, significance \\ 
+  \hline
+\hline
+Excess significance, Schwarzer & 0.82 & 0.87 & 0.14 & 0.19 \\ 
+  Excess significance, Peter & 0.80 & 0.84 & 0.27 & 0.21 \\ 
+  Excess significance, Rucker & 0.83 & 0.85 & 0.32 & 0.26 \\ 
+  Excess significance, Harbord & 0.80 & 0.85 & 0.27 & 0.24 \\ 
+  Peter, Schwarzer & 0.82 & 0.88 & 0.38 & 0.39 \\ 
+  Schwarzer, Rucker & 0.82 & 0.87 & 0.32 & 0.35 \\ 
+  Schwarzer, Harbord & 0.86 & 0.91 & 0.58 & 0.54 \\ 
+  Rucker, Peter & 0.89 & 0.92 & 0.64 & 0.62 \\ 
+  Harbord, Peter & 0.86 & 0.90 & 0.53 & 0.48 \\ 
+   \hline
+Excess significance, Egger & 0.79 & 0.81 & 0.72 & 0.61 \\ 
+  Excess significance, Thompson & 0.82 & 0.83 & 0.72 & 0.61 \\ 
+  Excess significance, Begg & 0.81 & 0.84 & 0.33 & 0.28 \\ 
+  Thompson, Egger & 0.95 & 0.96 & 0.96 & 0.95 \\ 
+  Thompson, Begg & 0.87 & 0.89 & 0.69 & 0.73 \\ 
+  Egger, Begg & 0.86 & 0.87 & 0.78 & 0.77 \\ 
+   \hline
+Excess significance, Egger (survival) & 0.87 & 0.97 & 0.00 &  \\ 
+  Excess significance, Thompson (survival) & 0.92 & 0.97 & 0.00 &  \\ 
+  Excess significance, Begg (survival) & 0.95 & 1.00 & 0.00 &  \\ 
+  Thompson, Egger (survival) & 0.90 & 0.95 & 0.67 & 0.00 \\ 
+  Thompson, Begg (survival) & 0.92 & 0.97 & 0.50 & 0.00 \\ 
+  Egger, Begg (survival) & 0.87 & 0.97 & 0.50 & 0.00 \\ 
    \hline
@@
 \endgroup
-\caption{Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects.
-The row names indicate which outcome measure, meta-analysis and adjustment method is used}
-\label{adjustment.difference}
+\caption{Overall proportion of agreement if significant or unsignificant, and for significance only.
+Horizontal lines separate binary, continuous and survival outcomes (order as in table).
+The reference significance test is the one with more significant results.}
+\label{test.agreement}
 \end{table}
-
-\subsection{Change in Evidence for Treatment Effects}
-Adjustment for small study effects in meta-analysis will not only provide new effect sizes, but also standard errors thereof.
-Thus, also the evidence for efficacy of a treatment can be obtained, which is usually summarized in a suitable test statistic or $p$-value.
-\\
-The wald test statistics $p$-value for fixed and random effects meta-analyses and copas and regression adjusted treatment effects have been calculated.
-They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and log hazard ratio.
-The $p$-values get larger changing from fixed effects to random effects, and from Copas to regression adjusted $p$-values for $z$-scores and Hedges $g$.
-Also, they are larger for Hedges $g$ based meta-analyses compared to $z$-score based meta-analyses.
-Meanwhile, they stay approximately equal for log odds ratios, with the exception of regression adjusted test statistics.
-Thus, after adjusting for small study effects, the evidence for treatment efficacy shrinks at least partially, which is also indicated by the smaller number of significant $p$-values (0.05 threshold).
-Note that while $z$-score and Hedges $g$ based meta-analyses use the same data, only with different effect measure transformations, this is not true for meta-analyses based on log odds ratios.\\
-%Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
-%Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted Hedges $g$ and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-16-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of the wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
-The method is indicated in the header, binwidth is set to 0.05.
-The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
-\label{fig:adjustment.stat}
-\end{figure}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% \section{Small study effects}
-% <<echo=FALSE, warning=FALSE>>=
-% p.samplesize.z  <- data.ext2 %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% ungroup() %>% 
-%   mutate(std.z = abs(z), sample.size = total1 + total2) %>%
-%   group_by(sample.size) %>% 
-%   summarize(median.effect = median(std.z, na.rm = T)) %>% 
-%   ggplot(aes(x = sample.size, y = median.effect)) + geom_point(size = 0.8) + 
-%   theme_bw() + xlab("sample size") + ylab("median absolute z-score") +
-%   xlim(c(15, 300)) + ylim(c(0, 0.25)) +
-%   scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
-% 
-% p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% 
-%   filter(outcome.measure.new == "Risk Ratio" | 
-%            outcome.measure.new == "Odds Ratio" | 
-%            outcome.measure.new == "Mean Difference" |
-%            outcome.measure.new == "Std. Mean Difference") %>% 
-%   group_by(outcome.measure.new) %>% 
-%   mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
-%   group_by(sample.size, outcome.measure.new) %>% 
-%   summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
-%   ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point(size = .5) + facet_wrap(~outcome.measure.new, scales = "free") + 
-%   theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size") +
-%   xlim(c(15, 300)) +
-%   scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
-% @
-% 
-% The median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
-It is clearly visible that the absolute value decreases with increasing sample size, i.e.
-that the effect size is becoming smaller.
-The trend flattens off after $\sim$ sample size = 400 (not shown).
-% -- Appendix -- \\
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.samplesize.z)
-% @
-% \caption{Median of the absolute $z$-score plotted against the total sample size.}
-% \label{z.samplesize}
-% \end{figure}
-% 
-% Only for illustration, the same trend is reproduced in Figure \ref{effect.samplesize.separated} with a similar method, using the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std.
-Mean Difference'' (the most commonly used in the dataset).
-The ``normalized effect'' is the original effect size, normalized with respect to all other effect sizes of the same measure (i.e.
-subtraction of mean and division through standard error of the mean).
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% plot(p.samplesize.effect.sep)
-% @
-% \caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
-% \label{effect.samplesize.separated}
-% \end{figure}
-% 
-% %Show absolute effect size depending on scaled time? Chunck 3
-
-% Since the tests have different properties, the agreement between the tests can be visualized.
-Here, agreement is specified as classifying the same meta-analysis as significant, based on the 0.1 $p$-value threshold.
-Again, this is done separately for the different outcome types.
-The result can be seen in Figure \ref{fig:test.agreement}.
-In the Figure, the number of agreeing tests is displayed, i.e., how many meta-analyses had only one significant test result etc.
-% 
-% \begin{figure}
-% <<echo = FALSE, fig.height = 5>>=
-% grid.arrange(agree.bin,
-%               agree.cont, 
-%               agree.surv, ncol = 1)
-% @
-% \caption{Barplot for the number of significant test results per meta-analyses, separated for outcome.types}
-% \label{fig:test.agreement}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% <<echo=FALSE>>=
-% plot(p.dist.bin)
-% @
-% \caption{Histogram of the $p$-values for small study effect in binary outcome meta-analyses.
-The testing method is indicated in the header, binwidth is equal to 0.1.
-The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-% \label{fig:test.bin}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% plot(p.dist.cont)
-% @
-% \caption{Histogram of the $p$-values for the small study effect in continuous outcome meta-analyses.
-The testing method is indicated in the header, binwidth is equal to 0.1.
-The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-% \label{fig:test.cont}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% plot(p.dist.surv)
-% @
-% \caption{Histogram of the $p$-values for the small study effect in survival outcome meta-analyses.
-The testing method is indicated in the header, binwidth is equal to 0.1.
-The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-% \label{fig:test.surv}
-% \end{figure}
-
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(adjustment.stat.z)
-% @
-% \caption{Histogram of the wald test-statistic of meta-analysis and adjusted pooled treatment effect, based on the z-score.
-The method is indicated in the header, binwidth is set to 1.
-The significant proportion based on the threshold of 0.05 is displayed inside the figures (The red line displays the corresponding quantile of the std.
-normal, 1.96).}
-% \label{fig:adjustment.stat.z}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(adjustment.stat.d)
-% @
-% \caption{Histogram of the wald test-statistic of meta-analysis and adjusted pooled treatment effect, based on Hedges $g$ or Cohen's $d$.
-The method is indicated in the header, binwidth is set to 1.
-The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
-% \label{fig:adjustment.stat.d}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(adjustment.stat.log.hazard.ratio)
-% @
-% \caption{Histogram of the wald test-statistic of meta-analysis and adjusted pooled treatment effect, based on the $z$-score.
-The method is indicated in the header, binwidth is set to 1.
-The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
-% \label{fig:adjustment.stat.log.hazard.ratio}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% 
-% <<echo=FALSE, warning=FALSE>>=
-% #Test Results: Binary
-% test.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-%                                                           schwarzer.test = mean(schwarzer.test),
-%                                                           rucker.test = mean(rucker.test),
-%                                                           harbord.test = mean(harbord.test),
-%                                                           peter.test = mean(peter.test))
-% test.bin <- test.bin %>% gather(key = "test.type", value = "mean")
-% 
-% p.bin <- meta.bin %>% ungroup() %>% 
-%   select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
-%   gather(key = "test.type", value = "null.hypothesis") %>%  
-%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-%   theme_bw() + xlab(label = NULL) +
-%   annotate("text", x = test.bin$test.type, y = 1000, 
-%            label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
-%            color = "white")
-% 
-% 
-% 
-% test.sig.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-%                                                               schwarzer.test = mean(schwarzer.test),
-%                                                               rucker.test = mean(rucker.test),
-%                                                               harbord.test = mean(harbord.test),
-%                                                               peter.test = mean(peter.test))
-% test.sig.bin <- test.sig.bin %>% gather(key = "test.type", value = "mean")
-% 
-% p1 <- meta.bin %>% ungroup() %>% filter(sig.fixef.bin == 1) %>% 
-% select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
-%   gather(key = "test.type", value = "null.hypothesis") %>% 
-%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-%   theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
-%   annotate("text", x = test.sig.bin$test.type, y = 1750, 
-%            label = paste(round(test.sig.bin$mean, 2)*100, "% rejected"), 
-%            color = "white")
-% 
-% test.nonsig.bin <- meta.bin %>% filter(sig.fixef.bin == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-%                                                                                                 schwarzer.test = mean(schwarzer.test),
-%                                                                                                 rucker.test = mean(rucker.test),
-%                                                                                                 harbord.test = mean(harbord.test),
-%                                                                                                 peter.test = mean(peter.test))
-% test.nonsig.bin <- test.nonsig.bin %>% gather(key = "test.type", value = "mean")
-% 
-% p2 <- meta.bin %>% 
-%   filter(sig.fixef.bin == 0) %>% ungroup() %>% 
-%   select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
-%   gather(key = "test.type", value = "null.hypothesis") %>% 
-%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-%   theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) +theme(legend.position="none") +
-%   annotate("text", x = test.nonsig.bin$test.type, y = 650, 
-%            label = paste(round(test.nonsig.bin$mean, 2)*100, "% rejected"), 
-%            color = "white")
-% 
-% range.pb.difference.bin <- range(test.sig.bin$mean - test.nonsig.bin$mean)
-% 
-% #Test Results: Continuous
-% test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-%                                                             begg.test = mean(begg.test),
-%                                                             thomson.test = mean(thomson.test))
-% 
-% test.cont <- test.cont %>% gather(key = "test.type", value = "mean")
-% 
-% p.cont <- meta.cont %>% ungroup() %>% 
-%   select(egger.test, thomson.test, begg.test) %>% 
-%   gather(key = "test.type", value = "null.hypothesis") %>% 
-%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-%   theme_bw() + xlab(label = NULL) +
-%   annotate("text", x = test.cont$test.type, y = 750, 
-%            label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
-%            color = "white")
-% 
-% 
-% test.sig.cont <- meta.cont %>% filter(sig.fixef.cont == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-%                                                                                                 begg.test = mean(begg.test),
-%                                                                                                 thomson.test = mean(thomson.test))
-% 
-% test.sig.cont <- test.sig.cont %>% gather(key = "test.type", value = "mean")
-% 
-% p3 <- meta.cont %>% 
-%   filter(sig.fixef.cont == 1) %>% ungroup() %>% 
-%   select(egger.test, thomson.test, begg.test) %>% 
-%   gather(key = "test.type", value = "null.hypothesis") %>% 
-%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-%   theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
-%   annotate("text", x = test.sig.cont$test.type, y = 600, 
-%            label = paste(round(test.sig.cont$mean, 2)*100, "% rejected"), 
-%            color = "white")
-% 
-% test.nonsig.cont <- meta.cont %>% filter(sig.fixef.cont == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-%                                                                                                    begg.test = mean(begg.test),
-%                                                                                                    thomson.test = mean(thomson.test))
-% 
-% test.nonsig.cont <- test.nonsig.cont %>% gather(key = "test.type", value = "mean")
-% 
-% p4 <- meta.cont %>% 
-%   filter(sig.fixef.cont == 0) %>% ungroup() %>% 
-%   select(egger.test, thomson.test, begg.test) %>% 
-%   gather(key = "test.type", value = "null.hypothesis") %>% 
-%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-%   theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
-%   annotate("text", x = test.nonsig.cont$test.type, y = 100, 
-%            label = paste(round(test.nonsig.cont$mean, 2)*100, "% rejected"), 
-%            color = "white")
-% 
-% range.pb.difference.cont <- range(test.sig.cont$mean - test.nonsig.cont$mean)
-% 
-% ########################################################################################################################################
-% ########################################################################################################################################
-% 
-% #Agreement proportions of publication bias tests:
-% 
-% #Binary:
-% n.bin <- dim(meta.bin)[1]
-% meta.bin <- meta.bin %>%ungroup() %>%  mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
-%                                         egger.peter = ifelse(egger.test == peter.test, "agree", "disagree"),
-%                                         egger.rucker = ifelse(egger.test == rucker.test, "agree", "disagree"),
-%                                         egger.harbord = ifelse(egger.test == harbord.test, "agree", "disagree"),
-%                                         schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
-%                                         schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
-%                                         schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
-%                                         rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
-%                                         rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
-%                                         harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
-% 
-% agreement.bin <- meta.bin %>% ungroup() %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
-%                                             egger.peter = sum(egger.peter == "agree")/n(),
-%                                             egger.rucker = sum(egger.rucker == "agree")/n(),
-%                                             egger.harbord = sum(egger.harbord == "agree")/n(),
-%                                             schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
-%                                             schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
-%                                             schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
-%                                             rucker.peter = sum(rucker.peter == "agree")/n(),
-%                                             harbord.peter = sum(harbord.peter == "agree")/n())
-% 
-% correlation.bin <- meta.bin %>%ungroup() %>%  summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
-%                                               egger.peter = cor(pval.egger.bin, pval.peter.bin),
-%                                               egger.rucker = cor(pval.egger.bin, pval.rucker.bin),
-%                                               egger.harbord = cor(pval.egger.bin, pval.harbord.bin),
-%                                               schwarzer.peter = cor(pval.schwarzer.bin, pval.peter.bin),
-%                                               schwarzer.rucker = cor(pval.schwarzer.bin, pval.rucker.bin),
-%                                               schwarzer.harbord = cor(pval.schwarzer.bin, pval.harbord.bin),
-%                                               rucker.peter = cor(pval.rucker.bin, pval.peter.bin),
-%                                               harbord.peter = cor(pval.harbord.bin, pval.peter.bin))
-% 
-% binary.tests.agreement <- rbind(agreement.bin, correlation.bin)
-% rownames(binary.tests.agreement) <- c("Test Agreement","P-value Correlation")
-% 
-% 
-% #Continuous:
-% n.cont <- dim(meta.cont)[1]
-% meta.cont <- meta.cont %>% ungroup() %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
-%                                           thomson.begg = ifelse(thomson.test == begg.test, "agree", "disagree"),
-%                                           egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"))
-% 
-% agreement.cont <- meta.cont %>% ungroup() %>%  summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
-%                                               thomson.begg = sum(thomson.begg == "agree")/n(),
-%                                               egger.begg = sum(egger.begg == "agree")/n())
-% 
-% correlation.cont <- meta.cont %>% ungroup() %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
-%                                                 thomson.begg = cor(pval.thomson.cont, pval.begg.cont),
-%                                                 egger.begg = cor(pval.egger.cont, pval.begg.cont))
-% 
-% cont.tests.agreement <- rbind(agreement.cont, correlation.cont)
-% rownames(cont.tests.agreement) <- c("Test Agreement","P-value Correlation")
-% 
-% ########################################################################################################################################
-% ########################################################################################################################################
-% 
-% 
-% #Trimfill missing studies fractions statistics:
-% trimfill.cont.mean <- meta.cont %>% ungroup %>% summarise(mean = mean(missing.trim.cont)) %>% select(mean)
-% trimfill.cont.median <- meta.cont %>% ungroup %>% summarise(median = median(missing.trim.cont)) %>% select(median)
-% 
-% trimfill.bin.mean <- meta.bin %>% ungroup %>% summarise(mean = mean(missing.trim.bin)) %>% select(mean)
-% trimfill.bin.median <- meta.bin %>% ungroup %>% summarise(median = median(missing.trim.bin)) %>% select(median)
-% 
-% ########################################################################################################################################
-% ########################################################################################################################################
-% 
-% change.ranef.bin <- meta.bin %>% ungroup() %>% 
-%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n)) 
-% 
-% p.change.ranef.bin <- meta.bin %>% ungroup() %>% 
-%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>%  
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+ 
-%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.ranef.bin[change.ranef.bin$sig.change == 3,]$correction.method, y = 1000, 
-%          label = paste(round(change.ranef.bin[change.ranef.bin$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-%          color = "white")
-% 
-% change.ranef.cont <- meta.cont %>% ungroup() %>% 
-%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
-%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n))
-% 
-% p.change.ranef.cont <- meta.cont %>% ungroup() %>% 
-%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>%  
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes") +
-%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.ranef.cont[change.ranef.cont$sig.change == 3,]$correction.method, y = 500, 
-%          label = paste(round(change.ranef.cont[change.ranef.cont$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-%          color = "white")
-% 
-% change.ranef <- meta %>% ungroup() %>% 
-%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
-%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n))
-% 
-% p.ranef.change <- meta %>% ungroup() %>% 
-%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>%  
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.ranef[change.ranef$sig.change == 3,]$correction.method, y = 1500, 
-%          label = paste(round(change.ranef[change.ranef$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
-%          color = "white")
-% # Significance after correction plots, separated for meta-analyses with significant publication bias test.
-% #Fixed effects meta-analysis significance
-% #Binary outcomes:
-% change.fixef.bin <- meta.bin %>% ungroup() %>% 
-%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
-%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n))
-% 
-% p.change.fixef.bin <- meta.bin %>% ungroup() %>% 
-%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>%  
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+  
-%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.fixef.bin[change.fixef.bin$sig.change == 3,]$correction.method, y = 800, 
-%          label = paste(round(change.fixef.bin[change.fixef.bin$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
-%          color = "white")
-% 
-% #Continuous outcomes:
-% change.fixef.cont <- meta.cont %>% ungroup() %>% 
-%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>% 
-%   mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n))
-% 
-% p.change.fixef.cont <- meta.cont %>% ungroup() %>% 
-%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>%  
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes")+ 
-%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.fixef.cont[change.fixef.cont$sig.change == 3,]$correction.method, y = 300, 
-%          label = paste(round(change.fixef.cont[change.fixef.cont$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
-%          color = "white")
-% 
-% #Overall:
-% change.fixef <- meta %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-% 	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n))
-% 
-% p.fixef.change <- meta %>% ungroup() %>% 
-%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>%  
-%   mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-%   theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
-% 	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 1500, 
-%          label = paste(round(change.fixef[change.fixef$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-%          color = "white")
-% 
-% #Separated for meta-analyses with significant publication bias test.
-% change.fixef.bias <- meta %>% 
-%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-%   filter(thomson.test == 1) %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-% 	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n))
-% 
-% p.change.fixef.bias <- meta %>% 
-%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-%   filter(thomson.test == 1) %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-%   theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
-% 	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 250, 
-%            label = paste(round(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-%            color = "white")
-% 
-% change.fixef.unbias <- meta %>% 
-%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-%   filter(thomson.test == 0) %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-% 	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>%  
-% 	mutate(n = n/sum(n))
-% 
-% p.change.fixef.unbias <- meta %>% 
-%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-%   filter(thomson.test == 0) %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-%   theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
-% 	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$correction.method, y = 1300, 
-%            label = paste(round(change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-%            color = "white")
-% 
-% 
-% ########################################################################################################################################
-% ########################################################################################################################################
-% 
-% p.missing.copas <- meta %>% ggplot(aes(x = missing.copas/n)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20)
-% p.missing.trim <- meta %>% ggplot(aes(x = missing.trim)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20)
-% @
-% 
-% There are tests that can be applied to find out if small study effects are present in the meta analysis.
-For the precise description, see the methods section.
-Application of the tests is only recommended if there are ten or more studies \citep{cochrane.handbook} that can be used, so all meta-analyses with less than ten studies have been excluded.
-% 
-% \vspace{0mm}
-% There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
-In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = n.cont)
-% The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = n.bin).
-The amount of studies varies from 5\% (Schwarzer's Test) to 13 \% (Egger's Test) for binary outcomes and 9\% (Begg and Mazumdar's Test) to 25 \% (Egger's Test) for continuous outcomes.
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.cont)
-% @
-% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-% \label{bias.results.cont}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.bin)
-% @
-% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-% \label{bias.results.bin}
-% \end{figure}
-% 
-% There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not.
-Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by range.pb.difference.bin[2] (the minimal increase is range.pb.difference.bin[1] for Schwarzer's Test).
-% 
-% %Show plots of significant meta-analyses separated? Chunck 4
-% 
-% Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses).
-The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}.
-The Figure suggests that the frequency of publication bias remains constant over time.
-The mean publication years have been restricted such that at least 180 meta-analyses are available per year, such that random fluctuation is restricted to some extent.
-The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
-%   ggplot(aes(x = mean.publication.year, fill = factor(thomson.test), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% @
-% \caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
-% \label{pub.bias.overtime}
-% \end{figure}
-% 
-% 
-% The agreement of the tests, i.e.
-the proportion of meta-analyses where the rest results are equal between tests, is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
-Agreement in tests for binary outcomes is better than continuous outcomes, with some variation between tests (binary outcomes: 83 to 91\%).
-Correlation varies more between tests, both for continuous and binary outcome tests.
-% 
-% <<results = 'asis', echo = FALSE, warning = FALSE>>=
-% print(xtable(x = t(binary.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)", label = "agreement.bin",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
-% @
-% 
-% 
-% <<results = 'asis', echo = FALSE, warning = FALSE>>=
-% print(xtable(x = t(cont.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)", label = "agreement.cont",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
-% @
-% 
-% \vspace{0mm}
-% Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
-The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}.
-%(Suggests that 10 is likely too small)
-% In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
-A trend towards more rejections for larger sample sizes can be seen.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% meta %>% filter(n < 40) %>% ggplot(aes(stat(count), x = n, fill = factor(thomson.test))) + 
-%   geom_density(position = "fill")
-% @
-% \caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
-% \label{pvalues.samplesize}
-% \end{figure}
-% 
-% 
-% 
-% \vspace{0mm}
-% One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
-The mean fraction of trimmed comparisons for binary outcomes is round(trimfill.bin.mean,2) and the median round(trimfill.bin.median,2).
-% % A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
-In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses.
-% In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
-In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% meta.bin %>% filter(missing.trim.bin < 0.5) %>% 
-%   ggplot(aes(x = missing.trim.bin, fill = factor(peter.test), stat(count))) + 
-%   geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% @
-% \caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
-% \label{trimfill.pvalues.bin}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% meta.cont %>% filter(missing.trim.cont < 0.5) %>% 
-%   ggplot(aes(x = missing.trim.cont, fill = factor(thomson.test), stat(count))) + 
-%   geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% @
-% \caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
-% \label{trimfill.pvalues.cont}
-% \end{figure}
-% 
-% 
-% \subsection{Small Study Effect Correction}
-% Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
-Three of them will be applied to the meta-analyses shown previously that have ten or more study results and are therefore eligible for testing for publication bias.
-% 
-% \vspace{0mm}
-% The extent to what the results of the meta-analysis results are changed can be investigated.
-Because statistical significance is often used to decide if there is a treatment effect, a non-significant corrected effect size estimate can indicate that an observed treatment effect has been accepted because of small study effects.
-Therefore, the cases have been counted in which
-% \begin{enumerate}
-% \item Significance or non-significance of pooled estimate of meta-analysis did not change after correction for small study effects.
-% \item Significance of pooled estimate of meta-analysis did change to non-significance after correction for small study effects.
-% \item Non-significance of pooled estimate of meta-analysis did change to significance after correction for small study effects.
-% \end{enumerate}
-% 
-% The results of this can be seen in Figure \ref{significance.change.fixed} for all three methods, comparing the significance of the corrected pooled effect size estimate with the significance of the pooled effect size estimate of the fixed effects meta-analysis.
-The same for significance of random effects meta-analysis is shown in Figure \ref{significance.change.random}.
-The significance threshold was chosen such that the $p$-value had to be < 0.05 for rejection of the null hypothesis of no treatment effect.
-The correction methods were trim-and-fill, copas selection model and regression with random effects and shrinkage of within-study-variance methods.
-More details to the applied correction methods and their application are in the methods section \ref{methods}.
-Notably, the correction methods has been applied to all meta-analyses, thus also for such that had no significant small study effect test result.
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.fixef.change)
-% @
-% \caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction.}
-% \label{significance.change.fixed}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.ranef.change)
-% @
-% \caption{Change in signficance of random effects meta-analysis pooled estimate after correction.}
-% \label{significance.change.random}
-% \end{figure}
-% 
-% Since it has been previously seen in Figure \ref{test.results} that the results of small study effects vary considerably between continuous outcomes, the results in significance change from fixed effects meta-analysis can be seen separately in Figure \ref{significance.change.fixed.sep} for continuous and binary outcomes.
-The change in significance from random effects meta-analysis to significance of corrected estimate can be seen in Figure \ref{significance.change.fixed.sep}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p.change.fixef.bin, p.change.fixef.cont, ncol = 1)
-% @
-% \caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-% \label{significance.change.fixed.sep}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p.change.ranef.bin, p.change.ranef.cont, ncol = 1)
-% @
-% \caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-% \label{significance.change.random}
-% \end{figure}
-% 
-% Because the real amount of publication bias in the dataset is not known, the correction method can also be applied only to meta-analyses that have publication bias according to the small study effect tests in the previous section.
-Because the test developed by \citet{thomson.sharp} has been applied to both binary and continuous outcome meta-analyses (in the case of binary outcomes to arcsine variance stabilized proportions), it is used as a criterium to distinguish biased from unbiased meta-analyses.
-The proportions of significance tests of pooled treatment effects that turned from significant to non-significant, non-significant to significant etc.
-are shown in Figure \ref{significance.change.fixed.sep}.
-Fixed effects meta-analysis has been used to determine signficance of the uncorrected estimate.
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p.change.fixef.bias, p.change.fixef.unbias, ncol = 1)
-% @
-% \caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-% \label{significance.change.random}
-% \end{figure}
-% 
-% Similarly, the number of missing studies per meta-analysis, i.e.
-those which have not been included because of small study effects, are estimated by the copas and trim-and-fill method and their empirical distribution is shown in histograms in Figure \ref{missing.studies.distribution}.
-For visualisation, the fraction of unpublished studies from the total fraction of available studies is shown.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p.missing.copas, p.missing.trim, ncol = 1)
-% @
-% \caption{Fraction of missing studies estimated of the number of total studies included in the meta-analysis for copas selection and trim-and-fill method.}
-% \label{missing.studies.distribution}
-% \end{figure}
-% 
-% 
-% 
-% 
-% % # <<results = 'asis', Echo = FALSE>>=
-% % # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
-% % #                                             schwarzer.rejection = mean(schwarzer.test),
-% % #                                             rucker.rejection = mean(rucker.test),
-% % #                                             harbord.rejection = mean(harbord.test),
-% % #                                             peter.rejection = mean(peter.test))
-% % # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
-% % # @
-% 
-% 
-% 
-% 
-% 
-% 
-% % 
-% % For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
-The following three figures show the distribution of p-values of the corresponding tests.
-Note that only meta analyses with more than 10 comparisons have been included.
-% % 
-% % \vspace{0mm}
-% % Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
-The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
-% % 
-% % \begin{figure}
-% % <<echo=FALSE>>=
-% % data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-% %   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-% %   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-% %   mutate(n = n()) %>% filter(n > 9) %>% 
-% %   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-% %                             method = "linreg")$p.val) %>% 
-% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-% %   theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% % @
-% % \caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
-% % \label{egger.cont}
-% % \end{figure}
-% % 
-% % 
-% % \begin{figure}
-% % <<echo=FALSE>>=
-% % data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-% %   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-% %   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-% %   mutate(n = n()) %>% filter(n > 9) %>% 
-% %   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-% %                             method = "mm")$p.val) %>% 
-% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-% %   theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% % @
-% % \caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
-% % \label{thomson.cont}
-% % \end{figure}
-% % 
-% % \begin{figure}
-% % <<echo=FALSE>>=
-% % data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-% %   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-% %   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-% %   mutate(n = n()) %>% filter(n > 9) %>% 
-% %   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-% %                             method = "rank")$p.val) %>% 
-% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-% %   theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% % @
-% % \caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
-% % \label{begg.cont}
-% % \end{figure}
-% % 
-% % 
-% % For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
-% % 
-% % \begin{figure}
-% % <<echo=FALSE>>=
-% % data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-% %   filter(events1 > 0 | events2 > 0) %>% 
-% %   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-% %   mutate(n = n()) %>% filter(n > 9) %>% 
-% %   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
-% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-% %   theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% % @
-% % \caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
-% % \label{peters.bin}
-% % \end{figure}
-% % 
-% % 
-% % \begin{figure}
-% % <<echo=FALSE>>=
-% % data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-% %   filter(events1 > 0 | events2 > 0) %>% 
-% %   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-% %   mutate(n = n()) %>% filter(n > 9) %>% 
-% %   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
-% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-% %   theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% % @
-% % \caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
-% % \label{harbord.bin}
-% % \end{figure}
-% 
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% % Since most of the times the study publication year is available for a given result, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.
-The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
-% % 
-% % \begin{figure}
-% % <<echo=FALSE, warning=FALSE>>=
-% % data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-% %   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
-% % @
-% % \caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
-% % \label{study.significance.overtime}
-% % \end{figure}
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 2
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% % The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
-Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
-The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested.
-This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
-% % 
-% % \begin{figure}
-% % <<echo=FALSE, warning=FALSE>>=
-% % grid.arrange(sig.meta.Q1, nonsig.meta.Q, ncol= 1)
-% % @
-% % \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-% % by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-% % \label{primary.secondary.significance.sep.sig}
-% % \end{figure}
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 3
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% % A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
-This can again be done for the entire dataset, i.e.
-for all effect estimates and their ordering in time.
-It is important to scale the effect estimates here with respect to the estimates of the replication studies that are about the same subject, have the same outcome measure, etc.
-Also, only effect estimates that can be compared to other estimates before are included, i.e.
-only study results with one or more replica are included.
-Time needs to be scaled and normalized in order to compare multiple time-trends in effect size to each other and gain insights in the overall trend.
-This is done in Figure \ref{effects.overtime.separated}, separared for odds rati, risk ratio, and mean and standardized difference outcome measures.
-In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
-% % 
-% % \begin{figure}
-% % <<echo=FALSE>>=
-% % data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
-% %                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
-% %   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
-% %   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
-% %   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
-% %   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
-% %   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
-% % @
-% % \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
-% % \label{effects.overtime.separated}
-% % \end{figure}
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 4
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% % The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
-This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
-% % 
-% % \begin{figure}
-% % <<echo=FALSE, warning=FALSE>>=
-% % grid.arrange(p3, p4, ncol = 2)
-% % @
-% % \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-% % \label{bias.results.cont.sep}
-% % \end{figure}
-% % 
-% % \begin{figure}
-% % <<echo=FALSE, warning=FALSE>>=
-% % grid.arrange(p1, p2, ncol = 2)
-% % @
-% % \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-% % \label{bias.results.bin.sep}
-% % \end{figure}
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 5
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% % #Proportion of significant pooled estimates based on proportion of single pooled estimates
-% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type)) + geom_histogram()
-% % 
-% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
-% %   geom_density(na.rm = T, position = "fill") + 
-% %   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% % 
-% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
-% %   geom_histogram(position = "fill")
-% % 
-% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef))) + 
-% %   geom_histogram()
-% 
-% % \begin{figure}
-% % <<echo=FALSE, warning=FALSE>>=
-% % plot(p.secondary.over.meansig)
-% % @
-% % \caption{Fraction of significant meta-analysis, dependent on the fraction of significant single results.}
-% % \label{secondary.significance.over.meansig}
-% % \end{figure}
-% 
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
 
@@
 The pooled treatment effect of a meta-analysis will be denoted as $\theta_M$, and consequently, the observed pooled treatment effect as $\hat{\theta}_M$.
-Furthermore, each treatment effect is typically measured with some standard error $s_i$ and an estimate of $s_i$ is denoted as $\hat{s}_i$.
+Furthermore, each treatment effect is typically measured with some standard error $\se_i$ and an estimate of $\se_i$ is denoted as $\hat{\se}_i$.
 The $\hat{}$ sign thus indicates if it is an estimate.\\
@@
 For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Hedges $g$) and  a standard error thereof.
-Note that the definition of Hedges $g$ and its standard error $s$ varies among the literature, the following applies for this report:
-
-\begin{align}
-s &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}} & g &= \frac{m_t - m_c}{s} \label{eq:hedges.g}
-\end{align}
-
-The mean difference $\theta$ and its standard error $s$ can similarly be obtained by
-
-\begin{align}
-\theta &= m_t - m_c & s &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_t}
+Note that the definition of Hedges $g$ and its standard error $\se$ varies among the literature, the following applies for this report:
+
+\begin{align}
+\se &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}} & g &= \frac{m_t - m_c}{\se} \label{eq:hedges.g}
+\end{align}
+
+The mean difference $\theta$ and its standard error $\se$ can similarly be obtained by
+
+\begin{align}
+\theta &= m_t - m_c & \se &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_t}
 \end{align}
@@
 Both estimators take into account that the two groups might have unequal variances.
-A $p$-value to test the null hypothesis that the mean between group is equal is commonly obtained with the students $t$ test.
+A $p$-value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$ test.
 The $t$ statistic is obtained, using $s$ and $g$ from \ref{eq:hedges.g}, by
@@
 \end{align}
-and the $p$-value can be obtained with the cumulative student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
-
-\begin{align}
-p &= 2(1-F(|t|)) \nonumber
+and the $p$-value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
+
+\begin{align}
+p &= 2(1-F(\abs{t})) \nonumber
 \end{align}
@@
 The methods presented here can also be found, for example, in \cite[34]{Intro.meta}.
-Let $\theta$ be the logarithm to base 10 of the odds ratio. $\theta$ and its variance $s^2$ can be obtained by
-
-\begin{align}
-\hat{\theta} &= \log(\frac{e_t*(n_c - e_c)}{e_c*(n_t - e_t)}) \nonumber \\
-\hat{s}^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
-\end{align}
-
-Plugging in the observed counts will give the corresponding estimates. The logarithm of the risk ratio $\theta$ and its variance $s^2$ is similarly defined as
+Let $\theta$ be the natural logarithm of the odds ratio. $\theta$ and its variance $\se^2$ can be obtained by
+
+\begin{align}
+\theta &= \log(\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}) \nonumber \\
+\se^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
+\end{align}
+
+Plugging in the observed counts will give the corresponding estimates. The logarithm of the risk ratio $\theta$ and its variance $\se^2$ is similarly defined as
 
@@
 \theta &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
-s^2 &= 1/e_t + 1/n_t + 1/e_c + 1/e_t \label{eq:risk.ratio.variance}
-\end{align}
-
-Using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$-value, e..g.
-\cite[98]{held2014}.
+\se^2&= 1/e_t + 1/n_t + 1/e_c + 1/e_t \label{eq:risk.ratio.variance}
+\end{align}
+
+Using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$-value, \eg \cite[98]{held2014}.
 \\
@@
 \begin{align}
-p &= 2*(1-\Phi(|\hat{\theta}/\hat{s}|) \nonumber
-\end{align}
-, a $p$-value for the corresponding estimates, which summarizes the evidence against $\hat{\theta}$ being zero (i.e. the true risk/odds ratio being 1). \\
-Binary and continuous effect measures can be converted into each other, as described in section \ref{sec:transformation.effectsizes}.
+p &= 2\cdot(1-\Phi(\abs{\hat{\theta}/\hat{\se}}), \nonumber
+\end{align}
+a $p$-value for the corresponding estimate, which summarizes the evidence against $\hat{\theta}$ being zero (\ie the true risk/odds ratio being 1). \\
+Binary and continuous effect measures can be converted into each other, as described in Section \ref{sec:transformation.effectsizes}.
 
@@
 One frequently used method to take into account right-censoring is the Cox proportional hazards regression model \citep{Cox}.
-Because the method itself is not applied in this thesis, but only the resulting estimates of the parameters are used, the reader is referred to the extensive literature covering this topic (e.g.
-\citet{Surv}).
-\\
-The so-called hazard ratio estimated by cox p.h.
-regression is the ratio of the instantaneous risk of experiencing the event between two groups.
+Because the method itself is not applied in this thesis, but only the resulting estimates of the parameters are used, the reader is referred to the extensive literature covering this topic (\eg \citet{Surv}).
+\\
+The so-called hazard ratio estimated by Cox regression is the ratio of the instantaneous risk of experiencing the event between two groups.
 Because it is a maximum likelihood estimator, one can again use its Wald test statistic to test for equal hazards.
-Let $\hat{\theta}$ be an estimate of the log hazard ratio and $\hat{s}$ an estimate of the standard error of it.
+Let $\hat{\theta}$ be an estimate of the log hazard ratio and $\hat{\se}$ an estimate of the standard error of it.
 As before
 \begin{align}
-p &= 2*(1-\phi(|\hat{\theta}/\hat{s}|) \nonumber
+p &= 2\cdot(1-\phi(\abs{\hat{\theta}/\hat{\se}(\hat{\theta})}) \nonumber
 \end{align}
@@
 The fixed effects meta-analysis estimator of the pooled treatment effect is a mean of the single treatment effect estimators, weighted by their standard errors \citep{fixed.effects.rosenthal}.
-Let $w_i = 1/s_i^2$ be the weights, and $\theta_M$ be the pooled estimator and $s_M^2$ its variance.
+Let $w_i = 1/\se_i^2$ be the weights, and $\theta_M$ be the pooled estimator and $s_M^2$ its variance.
 Then
@@
 This estimator minimizes the variance between the effects.
-An estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and variances $\hat{\theta}_i, \hat{s}_i^2$.
-The underlying idea is that we assume $\theta_i \sim N(\theta_M, s_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.
+An estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and variances $\hat{\theta}_i$ and $\hat{\se}_i^2$.
+The underlying idea is that we assume $\theta_i \sim N(\theta_M, \se_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.
 \\
@@
 \begin{align}
-\theta_i \sim N(\mu_i, s_i^2) &&
+\theta_i \sim N(\mu_i, \se_i^2) &&
 \mu_i \sim N(\theta_M, \tau^2) \label{eq:random.effects} 
@@
 \begin{align}
-\theta_i | \mu_i \sim N(\theta_M, s_i^2 + \tau^2) \nonumber %\label{eq:random.effects.marginal}
-\end{align}
-
-$\tau^2$ is often referred to as a population variance or between-study variance, whereas $s_i^2$ can be interpreted as sampling error.
-The pooled treatment effect estimate $\theta_M$ of the random effects model and its variance is obtained by replacing the weights $w_i$ in equation \ref{eq:fixed.effects} with $w_i = 1/(s_i^2 + \tau^2)$.
+\theta_i \given \mu_i \sim N(\theta_M, \se_i^2 + \tau^2) \nonumber %\label{eq:random.effects.marginal}
+\end{align}
+
+$\tau^2$ is often referred to as a population variance or between-study variance, whereas $\se_i^2$ can be interpreted as sampling error.
+The pooled treatment effect estimate $\theta_M$ of the random effects model and its variance is obtained by replacing the weights $w_i$ in equation \ref{eq:fixed.effects} with $w_i = 1/(\se_i^2 + \tau^2)$.
 \\
 The model is superior to the fixed effects model whenever the standard errors of the treatment effects alone are unlikely to fully account for the entire variability observed between studies.
-Note that as $\tau^2$ increases, each $\theta_i$ will eventually get equal weights, irrespective of it's sampling error $s_i^2$.\\
+Note that as $\tau^2$ increases, each $\theta_i$ will eventually get equal weights, irrespective of it's sampling error $\se_i^2$.\\
 The estimation of $\tau^2$ has been subject to some debate in the statistical literature. Oftentimes, the method of moment estimator of \citet{tau.estimator} is used.
@@
 Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i}\label{eq:Q.heterogeneity} \\
-\tau^2 &= \max(0, \frac{Q - (n-1)}{C}) \label{eq:Tau.definition}
+\tau^2 &= \max\big(0, \frac{Q - (n-1)}{C}\big) \label{eq:Tau.definition}
 \end{align}
@@
 Again, $w_i, \theta_i ...$ have to be replaced by their estimates in order to get an estimate $\hat{\tau}^2$. \\
-The Paule-Mandel estimator \citep{paulemandel} is considered to have most often better properties than the method of moments estimator (e.g. \citet{tau.estimator.evaluation}).
-Since we defined $w_i = 1/(s_i^2 + \tau^2)$, it als holds that
+The Paule-Mandel estimator \citep{paulemandel} is considered to have most often better properties than the method of moments estimator (\eg \citet{tau.estimator.evaluation}).
+Since we defined $w_i = 1/(\se_i^2 + \tau^2)$, it als holds that
 
@@
 \begin{align}
-s^2(w_i\theta_i) &= \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} & \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} = 1 \label{eq:paulemandel}
+\se^2(w_i\theta_i) &= \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} & \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} = 1 \label{eq:paulemandel}
 \end{align}
@@
 \begin{align}
-I^2 &= (Q - n + 1)/Q \nonumber%\label{I2.proportion}
-\end{align}
-
-%Large values for $\hat{I}^2$ are of great importance when analyzing e.g. small study effects. \\
-Importantly, all proposed methods above assume normally distributed effect sizes and proper estimates $\hat{s}$ of the true standard error.
+I^2 &= \max\big(0, 1 - \frac{n-1}{Q}\big) \nonumber%\label{I2.proportion}
+\end{align}
+
+%Large values for $\hat{I}^2$ are of great importance when analyzing \eg small study effects. \\
+Importantly, all proposed methods above assume normally distributed effect sizes and proper estimates $\hat{\se}$ of the true standard error.
 This assumptions are not met for very small sample sizes and very few event counts.
-Alternatively, the mantel-haenszel method for risk and odds ratios (see e.g.
-\citet{mantel.haenszel}) could be used in the latter case.
+Alternatively, the Mantel-Haenszel method for risk and odds ratios (see \eg \citet{mantel.haenszel}) could be used in the latter case.
 
@@
 Importantly, they are however not interpretable directly as evidence for publication bias, but this is left for the discussion chapter.
-The tests are also often referred to as funnel plot asymmetry tests, because of the popularity of a recent test that has been used frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citet{trimfill}.
+The tests are also often referred to as funnel plot asymmetry tests, because of the popularity of a recent test that has been used frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill}.
 However, it is known for some time that the method has disadvantageous properties, therefore, it will not be discussed here, as well as the funnel plot (the radial plot will be used as an alternative).\\
@@
 A standardized effect size $\theta_i^\star$ can be computed as in \ref{begg.stand.eff}.
-$s_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \ref{begg.stand.var}, $\theta_M$ being the fixed effects pooled treatment effect (\ref{eq:fixed.effects}.
-
-\begin{align}
-\theta_i^\star &= (\theta_i - \theta_M)/s_i^{2\star} \label{begg.stand.eff}  \\
-s_i^{2\star} &= s_i^2 - 1/\sum_{i = 1}^n\frac{1}{s_i^2}1 \label{begg.stand.var} 
+$\se_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \ref{begg.stand.var}, $\theta_M$ being the fixed effects pooled treatment effect (\ref{eq:fixed.effects}.
+
+\begin{align}
+\theta_i^\star &= (\theta_i - \theta_M)/\se_i^{2\star} \label{begg.stand.eff}  \\
+\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2}1 \label{begg.stand.var} 
 \end{align}
@@
 \begin{align}
-p &= 2*(1-\Phi(|Z|)) \nonumber
+p &= 2\cdot(1-\Phi(\abs{Z})) \nonumber
 \end{align}
@@
 \begin{align}
-\operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i) \label{eq:least.squares}
+\operatorname*{argmin}_{\beta_0, \beta_1}\big(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i\big) \label{eq:least.squares}
 \end{align}
@@
 \begin{align}
-p &= 2(1-F(|(\beta_0 - \beta_{H0})/s_{\beta_0}|)) \nonumber
+p &= 2(1-F(\abs{(\beta_0 - \beta_{H0})/s_{\beta_0}})) \nonumber
 \end{align}
@@
 Let $\theta/s$ be the dependent variable $y$ and $1/s$ the explanatory variable $x$.
-If plotted, this corresponds to a radial or Galbraith plot \citet{galbraith}.
+If plotted, this corresponds to a radial or Galbraith plot \citep{galbraith}.
 The linear regression equation as introduced before in \ref{eq:simple.regression} can be written in two ways:
@@
 
-\ref{eq:radial.plot} is often provided due to the correspondence to the radial plot. However, it is equivalent to
-
-\begin{align}
-\theta &= \beta_0 + \beta_1 s + \epsilon, & \epsilon \sim N(0, w^{-1}\sigma^2) \label{eq:egger.plot}
-\end{align}
-
-with weights $w = 1/s^2$.
+Equation \eqref{eq:radial.plot} is often provided due to the correspondence to the radial plot. However, it is equivalent to
+
+\begin{align}
+\theta &= \beta_0 + \beta_1 \se + \epsilon, & \epsilon \sim N(0, w^{-1}\sigma^2) \label{eq:egger.plot}
+\end{align}
+
+with weights $w = 1/\se^2$.
 Thus testing $\beta_0$ of \ref{eq:radial.plot} or $\beta_1$ is equivalent.
 The corresponding $p$-value is then used as evidence for a small study effect.
-Plugging in  $\theta_i/s_i, 1/s_i$ as $y_i, x_i$ into equation \ref{eq:regression.parameters} and \ref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{s}_{\beta_0}$ and $\hat{s}_{\beta_1}$.
+Plugging in  $\theta_i/\se_i, 1/\se_i$ as $y_i, x_i$ into equation \ref{eq:regression.parameters} and \ref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{\se}_{\beta_0}$ and $\hat{\se}_{\beta_1}$.
 
@@
 \begin{align}
-\theta_i \sim N(\beta_0 + \beta_1 s_i, s_i^2 + \tau^2) \label{t.sharp.regression}
+\theta_i \sim N(\beta_0 + \beta_1 \se_i, \se_i^2 + \tau^2) \label{t.sharp.regression}
 \end{align}
@@
 $\tau^2$ is estimated as in equation \ref{eq:Tau.definition} (method of moments). %or \ref{eq:paule.mandel}. 
-The weights are set as $w_i = 1/\sqrt{s_i^2 + \tau^2})$.
+The weights are set as $w_i = 1/\sqrt{\se_i^2 + \tau^2})$.
 After adjusting for the weights as described in \ref{weighted.regression}, we can proceed analogous to Egger's test.
@@
 For example, a small number of event counts in one or group will inflate the variance and the effect size.
-Consequently, the tests above will tend to reject the null-hypothesis too often, i.e.
-report false positives.
+Consequently, the tests above will tend to reject the null-hypothesis too often, \ie report false positives.
 A number of solutions to this problem are provided in the literature.
@@
 Instead of taking the standard error $s$ as explanatory variable $x$ as in Egger's Test, the inverse of the total sample size is used.
-Additionally, the variances $s_i^2$ are used as weights.
+Additionally, the variances $\se_i^2$ are used as weights.
 Thus, the subsequent test procedure is identical to Egger's test.
@@
 A rank based alternative to Peters test for binary outcomes is Harbord's test \citep{Harbord}.
-It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated at log odds ratio $\theta_0 = 0$ and its inverse Fisher information $s^2$. Formally,
+It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated at log odds ratio $\theta_0 = 0$ and its inverse Fisher information $\se^2$. Formally,
 
@@
 \varphi &= e_t - (e_t - e_c)(e_t + (n_t - e_t))/(n_t + n_c) \label{harbord.score} \\
-s^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \label{harbord.variance}
+ \se^2&= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \label{harbord.variance}
 \end{align}
@@
 \begin{align}
-(e_t - \mathbb{E}(E_t))/\sqrt(s_i^2)
-\end{align}
-and the inverse of $s_i^2$ is then used as before in Begg and Mazumdar's test.
+(e_t - \mathbb{E}(E_t))/\sqrt(\se_i^2)
+\end{align}
+and the inverse of $\se_i^2$ is then used as before in Begg and Mazumdar's test.
 
@@
 \begin{align}
-\theta_i = \arcsin{e_t/n_t} - \arcsin{e_c/n_c} \nonumber &
-s_i^2 = 1/4n_t + +/4n_c \nonumber
+\theta_i &= \arcsin{e_t/n_t} - \arcsin{e_c/n_c} \nonumber &
+\se_i^2 &= 1/4n_t + /4n_c \nonumber
 \end{align}
@@
 \\
-We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated as for example by fixed effects Meta-Analysis \ref{eq:fixed.effects}.
+We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated by fixed effects Meta-Analysis \ref{eq:fixed.effects}.
 Let $O$ be the number of significant study results out of $n$ studies and $\alpha$ the significance threshold.
 Corresponding to the study effect $\theta_i$, we can specify the power $1 - \beta_i$, the probability to accepting a true result.
-Let $z_{\alpha,i}$ be the $1-\alpha$ quantile of a normal distribution with standard error $\hat{s}_i$.
+Let $z_{\alpha,i}$ be the $1-\alpha$ quantile of a normal distribution with standard error $\hat{\se}_i$.
 The power of study $i$ can be estimated as:
@@
 
-with $F$ being the cumulative distribution of a normal with mean $\hat{\theta}_M$ and standard deviation $\hat{s}_i$. \\
-If we assume no bias in $\theta_i, \theta_M$, the expected number of significant study results is then just
+with $F$ being the cumulative distribution of a normal with mean $\hat{\theta}_M$ and standard deviation $\hat{\se}_i$. \\
+If we assume no bias in $\theta_i$ and $\theta_M$, the expected number of significant study results is then just
 
@@
 and consecutively, calculating a $p$-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
-Alternatively, one can also use a binomial proportion test, which tests if the probability of significance is the same as expected.
-A simple Wald test statistic $Z$ is given by:
-
-\begin{align}
-Z = \frac{O/n - E/n}{\sqrt{(O/n(1-O/n))/n}}
-\end{align}
-
-The one sided $p$-value for the alternative hypothesis $O/n > E/n$ is
-
-\begin{align}
-p &= 1 - \Phi(Z) \nonumber
-\end{align}
-
-with $\Phi$ being the cumulative distribution function of a standard normal. \citet{excess.significance} propose it to be more suitable if $n$ is small.
+Alternatively, one can also use a binomial test, which is encouraged when $n$ and $O$ is small.
+We will get a one sided $p$-value for excess significance, $\P(X \geq O)$, by
+
+\begin{align}
+p &= \sum_{i = O}^n(n \choose i p^i (1-p)^{n - i})
+\end{align}
+
+with $p = E/n$ and $X$ being a binomial random variable with probability $p$.
 
@@
 There are different approaches to correct for small study effects and publication bias.
-They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinite precision (i.e.
-very small standard error) or to a summary effect, corrected for publication bias.
+They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinite precision (\ie very small standard error) or to a summary effect, corrected for publication bias.
 Selection models aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:
@@
 \begin{align}
-\theta_i & = \beta_0 + \beta_1\sqrt{s_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \epsilon_i \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{eq:limitmeta.regression}
-\end{align}
-
-The only difference between Thompson and Sharp's variant is $x = \sqrt{s^2 + \tau^2}$ instead of $x = \sqrt{s^2}$.
+\theta_i & = \beta_0 + \beta_1\sqrt{\se_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \epsilon_i \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{eq:limitmeta.regression}
+\end{align}
+
+The only difference between Thompson and Sharp's variant is $x = \sqrt{\se^2 + \tau^2}$ instead of $x = \sqrt{\se^2}$.
 $\beta_{1}$ represents the bias introduced by small study effects, as illustrated in the following equations:
@@
 \begin{align}
-\mathbb{E}((\theta_i - \beta_0)/\sqrt{s_i^2}) \rightarrow \beta_1 \textrm{ if } s_i \rightarrow \infty \nonumber \\ %\label{limitmeta.infinitesample} \\
-\mathbb{E}(theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} s_i \rightarrow 0 \nonumber
+\mathbb{E}((\theta_i - \beta_0)/\sqrt{\se_i^2}) \rightarrow \beta_1 \textrm{ if } \se_i \rightarrow \infty \nonumber \\ %\label{limitmeta.infinitesample} \\
+\mathbb{E}(theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} \se_i \rightarrow 0 \nonumber
 \end{align}
@@
 \begin{align}
-P(\textrm{select}|s) &= \Phi(a + b/s) \nonumber %\label{copas.selection1}
+P(\textrm{select}\given s) &= \Phi(a + b/s) \nonumber %\label{copas.selection1}
 \end{align}
@@
 \mu_i \sim N(\theta, \tau^2) \nonumber \\
-z_i = a + b/s_i + \delta_i \nonumber
+z_i = a + b/\se_i + \delta_i \nonumber
 \end{align}
@@
 \\
-Let $u_i = a + b/s_i$, $\lambda(u_i)$ the Mill's ratio $\phi(u_i)/\Phi(u_i)$ ($\phi$ is the standard normal density function and $\Phi$ the cdf) and $\tilde{\rho_i} = \sigma/\sqrt(\tau^2 + \sigma_i^2) \rho_i$.
-The probability of a study being selected, given $s_i$ and $\theta_i$, is
-
-\begin{align}
-P(\textrm{select}|s_i, \theta_i) = %P(a,b,s,y) = 
-\Phi(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i^2}}}) \nonumber
-\end{align}
-
-Which again shows that larger $s_i$ and $\theta_i$ lead to a larger selection probability. It can also be shown that the expected value
-
-\begin{align}
-\mathbb{E}(\theta_i|s_i, \textrm{select}) = \mu + \rho_i\sigma_i\lambda(u_i) \label{eq:copas.expectation}
+Let $u_i = a + b/\se_i$, $\lambda(u_i)$ the Mill's ratio $\phi(u_i)/\Phi(u_i)$ ($\phi$ is the standard normal density function and $\Phi$ the cdf) and $\tilde{\rho_i} = \sigma/\sqrt(\tau^2 + \sigma_i^2) \rho_i$.
+The probability of a study being selected, given $\se_i$ and $\theta_i$, is
+
+\begin{align}
+P(\textrm{select} \given \se_i, \theta_i) = %P(a,b,s,y) = 
+\Phi\big(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i^2}}}\big) \nonumber
+\end{align}
+
+Which again shows that larger $\se_i$ and $\theta_i$ lead to a larger selection probability. It can also be shown that the expected value
+
+\begin{align}
+\mathbb{E}(\theta_i \given \se_i, \textrm{select}) = \mu + \rho_i\sigma_i\lambda(u_i) \label{eq:copas.expectation}
 \end{align}
@@
 \begin{align}
-\textrm{Var}(\theta_i| s_i, z_i > 0) = \sigma_i^2 (1 - c_i^2\rho_i^2) \nonumber
+\textrm{Var}(\theta_i\given \se_i, z_i > 0) = \sigma_i^2 (1 - c_i^2\rho_i^2) \nonumber
 \end{align}
@@
 Although one has to evaluate the likelihood for fixed pairs $(a,b)$, one can compare the fit of the model to evaluate which one is more suitable:
-With equation \ref{eq:copas.expectation}, one can obtain fitted values of $\theta_i$ based on $s_i$. Also, for two different pairs $(a,b)$, $(a^\star, b^\star)$,
-
-\begin{align}
-\mathbb{E}(\theta_i|z_i > 0, a^\star, b^\star) - \mathbb{E}(\theta_i|z_i > 0, a, b) \approx c^\star + \rho(\lambda(a^\star) - \lambda(a))s_i \nonumber
-\end{align}
-
-and that local departures of $\theta_i$ can be approximated by adding a linear term in $s_i$ to the expectation of $\theta_i$. Thus, to test a pair $(a,b)$, it is sufficient to test $\beta \neq 0$ in
-
-\begin{align}
-\theta_i &= \theta + \beta s_i + \sigma_i \epsilon_i \nonumber
+With equation \ref{eq:copas.expectation}, one can obtain fitted values of $\theta_i$ based on $\se_i$. Also, for two different pairs $(a,b)$, $(a^\star, b^\star)$,
+
+\begin{align}
+\mathbb{E}(\theta_i\given z_i > 0, a^\star, b^\star) - \mathbb{E}(\theta_i\given z_i > 0, a, b) \approx c^\star + \rho(\lambda(a^\star) - \lambda(a))\se_i \nonumber
+\end{align}
+
+and that local departures of $\theta_i$ can be approximated by adding a linear term in $\se_i$ to the expectation of $\theta_i$.
+Thus, to test a pair $(a,b)$, it is sufficient to test $\beta \neq 0$ in
+
+\begin{align}
+\theta_i &= \theta + \beta \se_i + \sigma_i \epsilon_i \nonumber
 \end{align}
@@
 \begin{align}
-\chi^2 &= 2*(\operatorname*{max1}_{\theta, \tau, \beta}\tilde{L}(\theta, \tau, \beta) - \operatorname*{max}_{\theta, \tau}\tilde{L}(\theta, \tau, 0)) \label{eq:copas.small.study}
+\chi^2 &= 2\cdot(\operatorname*{max1}_{\theta, \tau, \beta}\tilde{L}(\theta, \tau, \beta) - \operatorname*{max}_{\theta, \tau}\tilde{L}(\theta, \tau, 0)) \label{eq:copas.small.study}
 \end{align}
@@
 \begin{align}
-\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta s_i)^2}{(\tau^2 + \sigma_i^2)}] \nonumber
+\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta \se_i)^2}{(\tau^2 + \sigma_i^2)}] \nonumber
 \end{align}
@@
 One can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process.
-Selection models are in general not recommended for inference (e.g.
-\citet{selection.assessment}).
+Selection models are in general not recommended for inference (\eg \citet{selection.assessment}).
 \citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes. \\
@@
 \\
-Let $\theta$ be a log odds ratio and $s$ its standard error. Cohen's $d$ and it's variance $s_d^2$ is obtained by
-
-\begin{align}
-d &= \theta \frac{\sqrt{3}}{\pi} & s_d^2 = s^2 \frac{\sqrt{3}}{\pi} \nonumber
-\end{align}
-
-$\frac{\pi}{\sqrt{3}} = 1.81$ is the standard deviation of the logistic distribution $L(\mu, \eta)$ with scale parameter $\eta = 1$, so we just divide the log odds ratio and it's variance through the standard deviation.
+Let $\theta$ be a log odds ratio and $s$ it's standard error. Cohen's $d$ and it's variance $s_d^2$ is obtained by
+
+\begin{align}
+d &= \theta \frac{\sqrt{3}}{\pi} & s_d^2 =  \se^2\frac{\sqrt{3}}{\pi} \nonumber
+\end{align}
+
+The factor $\frac{\pi}{\sqrt{3}} = 1.81$ is the standard deviation of the logistic distribution $L(\mu, \eta)$ with scale parameter $\eta = 1$, so we just divide the log odds ratio and it's variance through the standard deviation.
 The approximation works only well if $e_t$ and $e_c$ are not very small, especially in the case of $s_d^2$.
-Plugging in the observed log odds ratio $\hat{\theta}$ and $\hat{s}^2$ will give an estimate of Cohen's $d$.\\
+Plugging in the observed log odds ratio $\hat{\theta}$ and $\hat{\se}^2$ will give an estimate of Cohen's $d$.\\
 Pearson's correlation can be attained by the formulas (\citet{olkin1985dtor}, \cite[48]{Intro.meta})
@@
 \begin{align}
-z &= 0.5 \ln(\frac{1 + r}{1 - r}) & \nonumber
+z &= 0.5 \ln\big(\frac{1 + r}{1 - r}\big) & \nonumber
 s_z^2 &= \frac{1}{n-3}
@@
 Let $\hat{y}_i = \beta_0 + \beta_1 x_i$ and $e_i = y_i - \hat{y}_i$.
-The variances $s^2_\beta$
+The variances $\se^2_\beta$
 % 
@@
 The pairs $(y_{i}^\star, v_{i}^\star)$ that are ranked in the same order are enumerated.
-Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (e.g.
-larger standardized effect size and smaller variance).
+Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (\eg larger standardized effect size and smaller variance).
 Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
@@
 % The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
-Consequently, the tests above will tend to reject the null-hypothesis too often, i.e.
-that they are not conservative enough.
+Consequently, the tests above will tend to reject the null-hypothesis too often, \ie that they are not conservative enough.
 A number of solutions to this problem are existing in the literature.
@@
 % 
-% After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test (see \ref{Thompson}).
+% After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before \eg in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test (see \ref{Thompson}).
 % 

### 2019-07-01 report/chapter02.Rnw
correction of tes

@@
                             quantile(data.ext2$study.year, 0.5, na.rm = T), quantile(data.ext2$study.year, 0.75, na.rm = T),
-                            round(mean(data.ext2$study.year, na.rm = T), 2))
+                            round(mean(data.ext2$study.year, na.rm = T), 2), quantile(data.ext2$study.year, 0.95, na.rm = T))
 
@@
                             quantile(data.ext2$total.n, 0.5, na.rm = T), quantile(data.ext2$total.n, 0.75, na.rm = T),
-                            round(mean(data.ext2$total.n, na.rm = T), 2))
+                            round(mean(data.ext2$total.n, na.rm = T), 2), quantile(data.ext2$total.n, 0.95, na.rm = T))
 treatment.group.size.range <- c(quantile(data.ext2$total1, 0.05, na.rm = T), quantile(data.ext2$total1, 0.25, na.rm = T), 
                       quantile(data.ext2$total1, 0.5, na.rm = T), quantile(data.ext2$total1, 0.75, na.rm = T),
-                      round(mean(data.ext2$total1, na.rm = T), 2))
+                      round(mean(data.ext2$total1, na.rm = T), 2), quantile(data.ext2$total1, 0.95, na.rm = T))
 
@@
                       quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
-                      round(mean(comp.freq$n, na.rm = T), 2))
+                      round(mean(comp.freq$n, na.rm = T), 2), quantile(comp.freq$n, 0.95, na.rm = T))
 
@@
                       quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
-                      round(mean(study.freq$n, na.rm = T), 2))
+                      round(mean(study.freq$n, na.rm = T), 2), quantile(study.freq$n, 0.95, na.rm = T))
 
@@
 
-The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = \Sexpr{publication.year.range[1]}).
+The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = \Sexpr{publication.year.range[1]}, 95\% quantile = \Sexpr{publication.year.range[6]},).
 The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{publication.year.range[5]} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}.
@@
              of results with the outcome measure and percentage the percentage of the outcome measure,", 
-             align = "llll", digits = 1), include.rownames = F, size = "footnotesize")
+             align = "llrr", digits = 1), include.rownames = F, size = "footnotesize")
 @
@@
 The sample sizes among results vary to some extent.
-There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, the 5\% quantile.
+There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, the 5\% quantile and 95\% smaller than \Sexpr{treatment.group.size.range[6]}.
 The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{treatment.group.size.range[5]} and the third quartile \Sexpr{treatment.group.size.range[4]}.
 The large difference between median and mean is caused by very large groups with over 2,000,000 participants.
-Analogously, the quantiles of the total sample size are: 5\% quantile = \Sexpr{samplesize.range[1]}, first quartile = \Sexpr{samplesize.range[2]}, median = \Sexpr{samplesize.range[3]} and third quartile = \Sexpr{samplesize.range[4]}.
+Analogously, the quantiles of the total sample size are: 5\% quantile = \Sexpr{samplesize.range[1]}, first quartile = \Sexpr{samplesize.range[2]}, median = \Sexpr{samplesize.range[3]}, third quartile = \Sexpr{samplesize.range[4]} and 95\% = \Sexpr{samplesize.range[6]}.
 The mean is \Sexpr{samplesize.range[5]}.
@@
 There are \Sexpr{comp.range[1]} reviews with five or fewer results, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}.
-Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]}.
-The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1497 results in total.
-\\
+Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]} and the 95\% quantile \Sexpr{study.range[6]}.
+The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1497 results in total.\\
 For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome.
@@
 Importantly, this distinction is also used by the Cochrane Organization itself, i.e.
-the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\%Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
+the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
 The dataset is divided in meta-analyses with identical experimental setup. The size of a meta-analysis denotes how many results are included in a group.
-Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results. Practically, this number of meta analyses can be performed, with each having at least $n$ results:
+Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results. Practically, this number of meta analyses can be performed, with each having at least $n$ results.
 
@@
 
-print(xtable(cum.repr.trials.subg, label = "repr.groups", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
+print(xtable(cum.repr.trials.subg, label = "repr.groups", caption = "Cumulative number of groups with number of reproduction trials $\\geq$ n", align = "llrr", digits = 0), include.rownames = F, size = "footnotesize")
 @

### 2019-07-01 report/chapter03.Rnw
correction of tes

@@
 
-\section{Small Study Effect and Excess of Singificance Tests}
+\section{Small Study Effect and Excess of Significance Tests} \label{sec:publication.bias.tests}
 <<echo=FALSE, warning=FALSE>>=
@@
 meta.surv <- meta.f %>% filter(outcome.type == "surv")
+
+#Agreement proportions of publication bias tests:
+
+#Binary:
+meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
+                                              tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
+                                              tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
+                                              tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
+                                              schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
+                                              schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
+                                              schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
+                                              rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
+                                              rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
+                                              harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
+agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
+                                                      tes.d.peter = sum(tes.d.peter == "agree")/n(),
+                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
+                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
+                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
+                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
+                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
+                                                      rucker.peter = sum(rucker.peter == "agree")/n(),
+                                                      harbord.peter = sum(harbord.peter == "agree")/n())
+meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test + schwarzer.test > 1, "agree", "disagree"),
+                                              tes.d.peter = ifelse(tes.d.test + peter.test > 1, "agree", "disagree"),
+                                              tes.d.rucker = ifelse(tes.d.test + rucker.test > 1, "agree", "disagree"),
+                                              tes.d.harbord = ifelse(tes.d.test + harbord.test > 1, "agree", "disagree"),
+                                              schwarzer.peter = ifelse(schwarzer.test + peter.test > 1, "agree", "disagree"),
+                                              schwarzer.rucker = ifelse(schwarzer.test + rucker.test > 1, "agree", "disagree"),
+                                              schwarzer.harbord = ifelse(schwarzer.test + harbord.test > 1, "agree", "disagree"),
+                                              rucker.peter = ifelse(rucker.test + peter.test > 1, "agree", "disagree"),
+                                              rucker.harbord = ifelse(rucker.test + harbord.test > 1, "agree", "disagree"),
+                                              harbord.peter = ifelse(harbord.test + peter.test > 1, "agree", "disagree"))
+agreement.sig.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/sum(tes.d.test),
+                                                      tes.d.peter = sum(tes.d.peter == "agree")/sum(tes.d.test),
+                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/sum(tes.d.test),
+                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/sum(tes.d.test),
+                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/sum(schwarzer.test),
+                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/sum(schwarzer.test),
+                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/sum(schwarzer.test),
+                                                      rucker.peter = sum(rucker.peter == "agree")/sum(rucker.test),
+                                                      harbord.peter = sum(harbord.peter == "agree")/sum(peter.test))
+
+binary.tests.agreement <- rbind(agreement.bin, agreement.sig.bin)
+rownames(binary.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
+colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
+                                      "Excess significance, Rucker", "Excess significance, Harbord",
+                                      "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
+                                      "Rucker, Peter", "Harbord, Peter")
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Continuous:
+meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
+                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
+                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
+                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
+                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
+                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
+agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
+                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
+                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
+                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
+                                                         egger.begg = sum(egger.begg == "agree")/n())
+meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
+                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
+                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
+                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
+                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
+                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
+agreement.sig.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
+                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
+                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
+                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
+                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
+                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))
+
+cont.tests.agreement <- rbind(agreement.cont, agreement.sig.cont)
+rownames(cont.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
+colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson",
+                                     "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Survival:
+meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
+                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
+                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
+                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
+                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
+                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
+agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
+                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
+                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
+                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
+                                                         egger.begg = sum(egger.begg == "agree")/n())
+meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
+                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
+                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
+                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
+                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
+                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
+agreement.sig.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
+                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(thompson.test),
+                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(begg.test),
+                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
+                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
+                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))
+
+surv.tests.agreement <- rbind(agreement.surv, agreement.sig.surv)
+rownames(surv.tests.agreement) <- c("Agreement (overall)","Agreement (significance)")
+colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)",
+                                    "Excess significance, Begg (survival)", "Thompson, Egger (survival)",
+                                    "Thompson, Begg (survival)", "Egger, Begg (survival)")
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Merging:
+test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
+
+#--------------------------------------------------------------------------------------------------------------------#
 
@@
   ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 250, label = label), color = "black") + 
+  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 200, label = label), color = "black") + 
   theme(strip.text.x = element_text(size=7)) + ggtitle("Binary Outcomes")
@@
   box(col = "lightgray")
-  rect(xleft = -1.96, ybottom = -1.96, xright = 1.96, ytop = 1.96, density = NULL, angle = 45,
+  rect(xleft = -1.644854, ybottom = -1.644854, xright = 1.644854, ytop = 1.644854, density = NULL, angle = 45,
        col = NA, border = "white", lty = 1, lwd = 1.4, 
@@
 
+egger.excess.plot <- meta.f %>% 
+  mutate(mean = ((logit(pval.egger)+ logit(pval.d.tes)))/2, 
+         difference = logit(pval.egger) - logit(pval.d.tes)) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point() + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + theme(legend.position = "none") +
+  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+                     values = c("red", "blue")) +
+  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value excess significance)" )))
+#--------------------------------------------------------------------------------------------------------------------#
+
 harbord.rucker.plot <- meta.f %>% 
@@
   # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + theme(legend.position = "bottom") +
-  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+  theme_bw() + #theme(legend.position = "bottom") +
+  scale_color_manual(labels = c("systematic error", "95 % conf. int."), 
                      values = c("red", "blue")) +
@@
                                binary = paste(summary.bin$n[-7], "%"),
-                               cont = paste(c(summary.else$n[-6], NA), "%"))
+                               cont = as.character(paste(c(summary.else$n[-6], NA), "%")))
+number.sig.tests <- as.matrix(number.sig.tests)
+number.sig.tests[6,3][1] <- "-"
+
 colnames(number.sig.tests) <- c("Count", "Binary Outcomes", "Continuous and Survival")
@@
 
-The meta-analyses fullfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with small study effects tests and excess significance tests.
-The $p$-values for all meta-analyses can be displayed in histograms.
-Because the tests are methodologically different, the results of each testing method is displayed separately.
-Furthermore, the outcome types (as defined previously by the variable \texttt{outcome.type}) are also kept separated.\\
-The histograms in Figure \ref{fig:test} show that the distributions are (with the exception of Schwarzer's test) skewed to the right for all outcome types, indicating evidence for small study effects and excess significance.
-Moreover, the excess significance tests have a mode around $p = 0.4$.
-The large differences between small study effect tests for binary and continuous outcomes will be subject to discussion.\\
-``Excess significance'' denotes the excess of significance $p$-values from the test of \citet{excess.significance}, see \ref{sex:excess.significance}.
+The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with small study effects tests and excess significance tests.
+We will apply the tests on the original effect size measures, i.e.
+risk ratios, Hedges $g$ or log hazard ratios.
+Different tests are applied depending on if the outcomes are of type binary or continuous or survival.\\
+Thus, we apply multiple tests on the same data.
+The results can then be displayed separately to compare the different tests.
+A histogram of $p$-values will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.
+\\
+``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}.
 For continuous and survival outcomes, the names refer to:
@@
 \begin{itemize}
-\item Egger's test, the weigthed linear regression test as described in section \ref{sec:Egger}
+\item Egger's test, the weighted linear regression test as described in section \ref{sec:Egger}
 \item Thompson and Sharp's test, the weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
@@
 %Agreement table -> Chunck 1
-
+The histograms in Figure \ref{fig:test} show that the distributions are (with the exception of Schwarzer's test) skewed to the right for all outcome types, indicating evidence for small study effects and excess significance, respectively.
+Moreover, the excess significance tests have a mode around $p = 0.4$.
+There is some discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger.
+Survival outcome type results are quite different with very few evidence for small study effects and excess significance.
+Note that the sample size of survival outcomes is small ($n$ = \Sexpr{dim(meta.surv)[1]}).\\
 It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects/excess significance for the same meta-analyses.
-Especially between small study effects and excess significance tests, we expect some disagreement between tests.
-A simple method to check the coincidence of test results is to compare scatterplots and empirical spearman correlations between test statistics.
+A simple method to check the coincidence of test results is to compare scatterplots and empirical Spearman correlations between the test statistics.
 This is done in Figure \ref{fig:test.agreement}.
-\\
-Here, there is no separation between survival and continuous outcomes. The upper left rectangle is displaying binary outcomes and the lower right about continuous and survival outcomes.
+Here, there is no separation between survival and continuous outcomes.
+The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results.
 
@@
          upper.panel=panel.pts.new, lower.panel=panel.cor, 
-         cex.labels = 1, cex = .3, cex.cor = 2, pch = 1,
+         cex.labels = 1, cex = .25, cex.cor = 2, pch = 1,
          text.panel=panel.txt, cor.method = "spearman")
@@
 \caption{Pairs-plot for test statistics of small study effect and excess significance.
-The lower panel gives the spearman correlations for the different test statistics, and the upper panel displays a scatterplot.
-The colours indicate magnitude and direction of the correlation coefficients.
-The rectangle with white borders displays the area within which both tests have absolute value < 1.96.}
+The lower panel gives the Spearman correlations for the different test statistics, and the upper panel displays a scatterplot.
+The colors indicate magnitude and direction of the correlation coefficients.
+The rectangle with white borders displays the area within which both tests have absolute value < 1.64 (dots outside are statistically significant using the 0.1 threshold).}
 \label{fig:test.agreement}
@@
 The observed patterns on the scatterplots differ: Excess significance and small study effect test statistics do usually not align with each other, forming rather randomly scattered bulks of points.
-Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is also reflected in large correlation coefficients.
-In general, small study effect tests align, but the extent to which they align differs.
-Harbord's test statistic has similar correlation coefficients with all other small study effect test statistics for binary outcomes, while the correlation coefficients between them is varying.\\
-Because scatterplots and correlation coefficients can be missleading, also a Tukey mean-difference or Bland-Altmann plot is shown for three scenarios in Figure \ref{fig:mean.diff.test}:
+Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients.
+In general, small study effect tests align on the diagonal, but the extent to which they align differs.
+Continuous and survival outcome type tests align more closely than binary outcome tests.
+While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics .\\
+Because scatterplots and correlation coefficients can be misleading, also a Tukey mean-difference or Bland-Altman of transformed $p$-values plot is shown for four scenarios in Figure \ref{fig:mean.diff.test}:
 \begin{itemize}
 \item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
-\item For Harbord's and Rucker's tests
+\item For Egger's and excess significance tests
+\item For Harbord's and R\"ucker's tests
 \item For Harbord's and excess significance tests
@@
 This can be justified since all tests are supposed to measure the evidence for publication bias.
-For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation.
-The mean $p$-value ((logit($p$-value 1) + logit($p$-value 2))/2) is then displayed against the differnec between the $p$-value.
+For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation $f(x)  = \log\frac{p}{1-p}$).
+The mean $p$-value (($f$($p$-value no.
+1) + $f$($p$-value no.
+2))/2) is then displayed against the difference between the $f$($p$-value).
 If no systematic errors and biases exist between the measurement methods, then
@@
 \begin{itemize}
-\item the mean of the differences (systematic error) should be around zero
-\item the points should scatter independent of the mean of the $p$-values
+\item the mean of the differences should be around zero (systematic error) 
+\item the points should scatter independently on the $y$-axis and no general increase or decrease with the mean of the transformed $p$-values should be visible
 \end{itemize}
 
-The last criterium seems not to be given when comparing Harbords and Excess significance tests. 
--- In the appendix, it can be seen that this is reproducible with the remainig small study effect tests (not there yet) -- 
+Although this is not formally tested, the last criterium seems not to be given when comparing small study effect and excess significance tests.
 With decreasing mean, the difference gets more negative, and vice versa, such that one would predict that the excess significance $p$-values are more ``extreme'' in both directions.
-This finding suggests that correspondence between the tests is poor.
-The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger and Thompson test, and around 0.99 for Harbord and Rucker.
+-- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- However, the systematic error between the compared tests is close to zero, and small study effect tests do probably not show bias when compared to each other.
+\\
+The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests.
+This suggests that correspondence between the tests is not very good in general.
 
 \begin{figure}
-<<echo=FALSE, fig.height = 6.5, warning=FALSE>>=
+<<echo=FALSE, fig.height = 8.5, warning=FALSE>>=
 grid.arrange(egger.thompson.plot, 
+             egger.excess.plot,
              harbord.rucker.plot, 
@@
 
+Here, it is difficult to say if continuous and survival or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and survival outcome type tests have in general more positive findings.
+Very few meta-analyses are significant, irrespective of the test used, but around 67\% of the dataset is not significant, no matter which test is used.
+\\
 When only looking at small study effect tests, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of survival and continuous outcome tests had at least one significant result.
-After applying the bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\& for binary and \Sexpr{mean.min.else.b}\% for continuous and survival outcomes.
+This also suggests that the overlap between small study effect tests and excess significance is small.
+After applying the Bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\% for binary and \Sexpr{mean.min.else.b}\% for continuous and survival outcomes.
 \\
-When comparing significant findings for small study effect tests and excess significance tests, we will only do so with Harbord's or Egger's test.
+To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test.
 \Sexpr{mean.min.bin2}\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, \Sexpr{mean.min.else2}\% for continuous and survival outcomes.
-Again, the numbers change to \Sexpr{mean.min.bin2.b}\% for binary outcomes and \Sexpr{mean.min.else2.b}\% for continuous and survival outcomes after applying the bonferroni correction.
+The numbers change to \Sexpr{mean.min.bin2.b}\% for binary outcomes and \Sexpr{mean.min.else2.b}\% for continuous and survival outcomes after applying the Bonferroni correction.
 \\
-\Sexpr{both.bin}\% have significant Harbord's test result and significant excesss significance test result  (\Sexpr{both.bin.b}\% with bonferroni).
+\Sexpr{both.bin}\% have significant Harbord's test result and significant excess significance test result  (\Sexpr{both.bin.b}\% with Bonferroni).
 Of the continuous outcomes, we have \Sexpr{both.else}\% with Egger's test and \Sexpr{both.else.b}\% with Bonferroni correction.
@@
 #--------------------------------------------------------------------------------------------------------------------#
-
-#Quantile and mean table of differences:
-adjustment.diff <- meta.f %>% 
-  transmute(est.d.copas.f = case_when(sign(est.d.copas) == sign(est.d.fixef) ~  abs(est.d.copas),
+sig.level <- 0.1
+meta.f <- meta.f %>% 
+	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
+				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
+				 begg.test = ifelse(pval.begg < sig.level, 1, 0),
+
+				 tes.d.test = ifelse(pval.d.tes < sig.level, 1, 0),
+
+				 schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
+				 rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
+				 harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
+				 peter.test = ifelse(pval.peter < sig.level, 1, 0))
+
+#Quantile, mean, largerthan and missing table of differences:
+adjustment.diff.keep <- meta.f %>% 
+  mutate(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
+                                 sign(est.copas) != sign(est.fixef) ~ -abs(est.copas)),
+         est.reg.f = case_when(sign(est.reg) == sign(est.fixef) ~  abs(est.reg),
+                               sign(est.reg) != sign(est.fixef) ~ -abs(est.reg)),
+         est.copas.r = case_when(sign(est.copas) == sign(est.ranef) ~  abs(est.copas),
+                                 sign(est.copas) != sign(est.ranef) ~ -abs(est.copas)),
+         est.reg.r = case_when(sign(est.reg) == sign(est.ranef) ~  abs(est.reg),
+                               sign(est.reg) != sign(est.ranef) ~ -abs(est.reg)),
+
+         est.d.copas.f = case_when(sign(est.d.copas) == sign(est.d.fixef) ~  abs(est.d.copas),
                                    sign(est.d.copas) != sign(est.d.fixef) ~ -abs(est.d.copas)),
@@
 
+         est.fixef = abs(est.fixef),
+         est.ranef = abs(est.ranef),
          est.z.fixef = abs(est.z.fixef),
@@
          est.d.fixef = abs(est.d.fixef),
-         est.d.ranef = abs(est.d.ranef)) %>%
+         est.d.ranef = abs(est.d.ranef))
+
+adjustment.diff.keep <- adjustment.diff.keep %>% 
+  mutate(bias.side = ifelse(est.fixef - est.reg.f > 0, 1, 0), #Decide if effect size declines or increases
+
+         egger.test = ifelse(bias.side == 1, egger.test, 0),
+         thompson.test = ifelse(bias.side == 1, thompson.test, 0),
+         begg.test = ifelse(bias.side == 1, begg.test, 0),
+
+         schwarzer.test = ifelse(bias.side == 1, schwarzer.test, 0),
+         peter.test = ifelse(bias.side == 1, peter.test, 0),
+         rucker.test = ifelse(bias.side == 1, rucker.test, 0),
+         harbord.test = ifelse(bias.side == 1, harbord.test, 0))
+
+adjustment.diff <- adjustment.diff.keep %>%
 
@@
 adjustment.diff.mean <- apply(m.adjustment.diff, 2, FUN = function(column) mean(column, na.rm = T))
-adjustment.diff.table <- rbind(adjustment.diff.quantile.table, mean = adjustment.diff.mean)
+adjustment.diff.largerzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
+adjustment.diff.equalzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
+adjustment.diff.largerequalzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
+adjustment.diff.comp.errors <- c(4,4,0,0,0,0,0,0)
+adjustment.diff.noest <- c(sum(meta.f$est.z.copas.na[meta.f$outcome.type != "surv"]), 
+                                sum(meta.f$est.z.copas.na[meta.f$outcome.type != "surv"]),
+                                sum(meta.f$est.z.reg.na[meta.f$outcome.type != "surv"]), 
+                                sum(meta.f$est.z.reg.na[meta.f$outcome.type != "surv"]),
+                                sum(meta.f$est.d.copas.na[meta.f$outcome.type != "surv"]), 
+                                sum(meta.f$est.d.copas.na[meta.f$outcome.type != "surv"]),
+                                sum(meta.f$est.d.reg.na[meta.f$outcome.type != "surv"]), 
+                                sum(meta.f$est.d.reg.na[meta.f$outcome.type != "surv"]))
+adjustment.diff.missing <- (adjustment.diff.comp.errors + adjustment.diff.noest)/apply(m.adjustment.diff, 2, FUN = function(column) length(column))*100
+
+adjustment.diff.table <- rbind(adjustment.diff.quantile.table, mean = adjustment.diff.mean,
+                               equalzero = adjustment.diff.equalzero,
+                               largerequal = adjustment.diff.largerequalzero, larger = adjustment.diff.largerzero,
+                               missing = adjustment.diff.missing)
 
@@
 adjustment.diff.mean.surv <- apply(m.adjustment.diff.surv, 2, FUN = function(column) mean(column, na.rm = T))
-adjustment.diff.table.surv <- rbind(adjustment.diff.quantile.table.surv, mean = adjustment.diff.mean.surv)
-
-adjustment.diff.table <- cbind(adjustment.diff.table, adjustment.diff.table.surv)
-
-adjustment.diff.table <- round(t(adjustment.diff.table), 3)
-
-rownames(adjustment.diff.table) <- c(paste("z-score:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
-                                     paste("Hedges g:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
-                                     paste("Log hazard ratio:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")))
+adjustment.diff.largerzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
+adjustment.diff.equalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
+adjustment.diff.largerequalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
+adjustment.diff.comp.errors.surv <- c(0,0,0,0)
+adjustment.diff.noest.surv <- c(sum(meta.surv$est.copas.na), sum(meta.surv$est.copas.na),
+                                sum(meta.surv$est.reg.na), sum(meta.surv$est.reg.na))
+adjustment.diff.missing.surv <- ((adjustment.diff.comp.errors.surv + adjustment.diff.noest.surv)/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
+
+adjustment.diff.table.surv <- rbind(adjustment.diff.quantile.table.surv, mean = adjustment.diff.mean.surv,
+                                    equalzero = adjustment.diff.equalzero.surv,
+                                    largerequal = adjustment.diff.largerequalzero.surv, larger = adjustment.diff.largerzero.surv,
+                                    missing = adjustment.diff.missing.surv)
+
+adjustment.diff.table <- cbind(adjustment.diff.table, (adjustment.diff.table.surv))
+
+adjustment.diff.table <- round(t(adjustment.diff.table), 4)
+
+rownames(adjustment.diff.table) <- c(paste("z:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
+                                     paste("g:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
+                                     paste("Log h.r.:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")))
+
+colnames(adjustment.diff.table) <- c(colnames(adjustment.diff.table)[1:6], "= 0 (%)", ">= 0 (%)", "> 0 (%)", "No adj. est. (%)")
 
@@
 
-adjustment.smaller.reg.z.f <- round(length(which(adjustment.diff$reg.z.f > 0))/length(which(!is.na(adjustment.diff$reg.z.f)))*100, 1)
-
-adjustment.smaller.reg.z.r <- round(length(which(adjustment.diff$reg.z.r > 0))/length(which(!is.na(adjustment.diff$reg.z.r)))*100, 1)
-@
-
-\subsection{Change in Effect Size after Adjustment}
-
-There are two possibilities when adjusting the pooled treatment effect of meta-analyses for publication bias.
-The absolute size of the treatment effect can be smaller, or larger after adjustment.
-Additionally, it is of interest by how much the treatment effect is diminishued or increased.
+#--------------------------------------------------------------------------------------------------------------------#
+#Tukey mean difference plots for adjustment methods:
+
+adjustment.mean.diff.orig <- meta.f %>% filter(est.copas.na != 1) %>% 
+  mutate(mean = (est.copas + est.reg)/2, 
+         difference = est.copas - est.reg) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + theme(legend.position = "none") +
+  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+                     values = c("red", "blue")) +
+  ggtitle(expression(paste("Copas adjusted estimate - Regression adjusted estimate (original)" )))
+
+adjustment.mean.diff.z <- meta.f %>% filter(est.z.copas.na != 1) %>% 
+  mutate(mean = (est.z.copas + est.z.reg)/2, 
+         difference = est.z.copas - est.z.reg) %>% filter(mean < 7) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = 0.5) + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + theme(legend.position = "none") +
+  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+                     values = c("red", "blue")) +
+  ggtitle(expression(paste("Copas adjusted ", italic(z),"-score estimate - Regression adjusted ", italic(z),"-score estimate (original)" )))
+
+adjustment.mean.diff.d <- meta.f %>% filter(est.d.copas.na != 1) %>% 
+  mutate(mean = (est.d.copas + est.d.reg)/2, 
+         difference = est.d.copas - est.d.reg) %>% filter(difference < 7 & mean < 10) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + #theme(legend.position = "bottom") +
+  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+                     values = c("red", "blue")) + guides(fill=guide_legend(title=NULL)) +
+  ggtitle(expression(paste("Copas adjusted Hedges ", italic(g)," estimate - Regression adjusted Hedges ", italic(g), " estimate (original)" )))
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Missing study number by copas:
+missing.copas.histogram <- meta.f %>% ggplot(aes(x = missing.copas/k)) + geom_histogram(binwidth = 0.05, boundary = 0) + theme_bw() + xlab("Missing study fraction")
+missing.copas.zeros <- length(which(meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)] == 0))
+missing.copas.range.frac <- c(missing.copas.zeros, quantile(x = meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)], c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)],na.rm = T) )
+missing.copas.range.count <- c(missing.copas.zeros, quantile(x = meta.f$missing.copas[!is.na(meta.f$missing.copas)], c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(na.rm = T,meta.f$missing.copas[!is.na(meta.f$missing.copas)]))
+missing.copas.table <- rbind(missing.copas.range.frac, missing.copas.range.count)
+rownames(missing.copas.table) <- c("Missing fraction", "Missing study number")
+colnames(missing.copas.table) <- c("= 0", colnames(missing.copas.table)[2:6], "mean")
+
+@
+
+\subsection{Change in Effect Size after Adjustment} \label{sec:change.size}
+
+Since there's evidence for publication bias when applying small study effect and excess significance tests, we apply small study effect adjustment methods to correct for small study effect tests. \\
+We will see that consequences of adjustment can be; 
+\begin{itemize}
+\item first, the absolute size of the treatment effect can be smaller than the classical meta-analysis treatment effect, which is expected if publication bias
+is the cause for the small study effect.
+\item secondly, the effect can be larger than before in meta-analysis.
+In this case, the small study effect must be not due to publication bias for large effects (``true'' publication bias), but due to bias for small effects (``negative publication bias'').
+\end{itemize}
+
+In section \ref{sec:comparison.tests.adjustment}, it will be followed up on the latter point. For now, we will examine the extent and the frequencies of the two scenarios. \\
+To compare the effects of adjustment between meta-analyses, the outcome measures are transformed to Hedges $g$ (standardized mean differences) and Fisher's $z$-score (see section \ref{sec:transformation.effectsizes} for details).
+The effect of adjustment can additionally be compared to either random or fixed effects meta-analysis.
 \\
-Figure \ref{fig:adjustment.size} displays the difference between the meta-analysis pooled treatment effect $\theta_M$ and the adjusted treatment effect $\theta_\textrm{Adj.}$ for the copas and regression adjustment methods and fixed and random effects meta-analysis.
-The treatment effects are mirrored on the positive side, such that a positive difference indicates that the effect size was smaller after adjustment (and analogously, larger if the difference is negative).
-For better illustration, some very large and very small differences have been ommitted in the $z$-score and Hedges $g$ histogramms; the missing differences are provided in Table \ref{missing.differences}.
-Additionally to the histogramms, Table \ref{adjustment.difference} shows the quantiles and means for the various differences.\\
-Copas estimates are equal to random effect in \Sexpr{meta.f$se.est.z.copas.missing[1]} for $z$-score based analysis, \Sexpr{meta.f$se.est.d.copas.missing[1]} for Hedges $g$ based analysis (and \Sexpr{meta.f$se.est.copas.missing[1]} for analysis based on original effect measures).
-\\
-We see in Figure \ref{fig:adjustment.size} that bot reduction and amplification of original effect size occurs frequently.
-Nevertheless, there are more adjustments towards smaller effects for $z$-scores and Hedges $g$, regardless of the reference meta-analysis method.
-Survival outcomes, and $z$-scores meta-analyses and copas adjustment differences are exception to this.
-The larger proportion of reduction is mostly also reflected in the means and medians in Table \ref{adjustment.difference}.
-They are mostly around zero or larger, although not to a large extent.
-There is more extensive downward correction of effect sizes if random effects meta-analysis is used as the reference.
+Figure \ref{fig:adjustment.size} displays the difference $\delta$ between the observed meta-analysis pooled treatment effect and the adjusted treatment effect, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
+The absolute value $|\hat{\theta}_M|$ is taken and the sign of $\hat{\theta}_\textrm{Adj.}$ is adjusted accordingly such that all effects are mirrored to one side.
+$\delta > 0$ is equivalent to $\hat{\theta}_\textrm{Adj} < \hat{\theta}_M$, a reduction of the original effect size.
+For better illustration, some very large and very small differences have been omitted in the $z$-score and Hedges $g$ histograms; they are shown in Table \ref{missing.differences}.
+Table \ref{adjustment.difference} shows the quantiles and means for the various differences and additional information.\\
 
@@
 <<echo=FALSE, results='asis'>>=
-print(xtable(missing.differences, 
-             caption = "Missing meta-analysis pooled treatment effect and adjusted treatment effects
-             of Figure \ref{fig:adjustment.size}. Abbreviations are used for z-score (z) and Hedges g (g)", label = "missing.differences", align = "llcccrrrrrrrr"), 
-      include.rownames = F, size = "tiny")
-@
-
-<<echo=FALSE, results='asis'>>=
 print(xtable(adjustment.diff.table, label = "adjustment.difference", caption = "Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects.
-The row names indicate which outcome measure, meta-analysis and adjustment method is used", align = "lcccccc"), include.rownames = T, size = "scriptsize"#, sanitize.text.function=function(x){x}
+The column with the names ``> 0'' give the percentages of estimates larger than zero or larger or equal zero.
+The column ``No adj.
+est.'' gives the percentage of missing estimates due to non-significant publication bias test (for Copas) and computational errors.
+The row names indicate which outcome measure, meta-analysis method and adjustment method is used.
+Abbreviations are used for z-score (= z) and Hedges g (= g).", align = "lcccccccccr"), include.rownames = T, size = "scriptsize",# sanitize.text.function=function(x){x},
+      # table.placement = "p"
       )
@@
 
-\subsection{Change in Evidence for Treatment Effects}
+Adjustment leads most often to reduction of treatment effect estimates, as can be seen by the size of the bins of the right part of the histograms in Figure \ref{fig:adjustment.sue}.
+The difference between the bins on the right and left side of the zero-centered bin is however not very large in general.
+The seeming exception of the Copas selection model in the case with $z$-scores and fixed effects reference requires closer examination: Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
+Thus, when comparing Copas with Fixed effects, we compare most often random effects with fixed effects estimates.
+The effect of adjustment by Copas can therefore only be seen when comparing random effects estimates with fixed effect estimates: we can see in Table \ref{adjustment.difference} that we have, for $z$-score, 18.4\% reduced effect sizes compared to 10.3\% (= 100\% - 89.69\%) increased effect sizes.
+Thus, the Copas selection model also has a larger proportion of reduced effect sizes compared to amplified.\\
+%This resolves the case for the seeming exception and for Hedges $g$'s, 24.4\% and 12.46\% (Table \ref{adjustment.difference}. 
+Also, there are more reduced effect sizes if random effects meta-analysis is used as a reference effect size.
+When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
+\\
+The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} increased by -0.13, fixed effects reference).
+Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or \Sexpr{floor(length(!is.na(meta.f$est.d.reg))*0.05)} meta-analyses (or increased by 0.24).
+
+\subsection{Change in Evidence for Treatment Effects} \label{sec:change.evidence}
 Adjustment for small study effects in meta-analysis will not only provide new effect sizes, but also standard errors thereof.
 Thus, also the evidence for efficacy of a treatment can be obtained, which is usually summarized in a suitable test statistic or $p$-value.
+It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.\\
+The Wald test statistics $p$-value for fixed and random effects meta-analyses and Copas and regression adjusted treatment effects have been calculated.
+They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and log hazard ratios.
 \\
-The wald test statistics $p$-value for fixed and random effects meta-analyses and copas and regression adjusted treatment effects have been calculated.
-They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and log hazard ratio.
-The $p$-values get larger changing from fixed effects to random effects, and from Copas to regression adjusted $p$-values for $z$-scores and Hedges $g$.
-Also, they are larger for Hedges $g$ based meta-analyses compared to $z$-score based meta-analyses.
-Meanwhile, they stay approximately equal for log odds ratios, with the exception of regression adjusted test statistics.
-Thus, after adjusting for small study effects, the evidence for treatment efficacy shrinks at least partially, which is also indicated by the smaller number of significant $p$-values (0.05 threshold).
-Note that while $z$-score and Hedges $g$ based meta-analyses use the same data, only with different effect measure transformations, this is not true for meta-analyses based on log odds ratios.\\
-%Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
+It can be seen that evidence for a treatment effect decreases after adjusting for publication bias.
+It does so more for Hedge's $g$ compared to $z$-scores, and for regression adjustment compared to Copas selection model.
+%Also, the evidence decreases for random effects meta-analyses compared to fixed effects meta-analyses. 
+In the case of log-hazard ratio adjustment, the adjustment has only negligible impact on the $p$-values. \\
+Also, Copas selection method has a very small impact on the evidence compared to random effects meta-analysis, at least using $z$-scores (again, we should rely on comparisons to random effects meta-analysis to evaluate Copas method).
+\\
+% Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
 %Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted Hedges $g$ and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.
@@
 @
-\caption{Histogram of the wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
-The method is indicated in the header, binwidth is set to 0.05.
+\caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
+The method is indicated in the header, bin width is set to 0.05.
 The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
@@
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% \section{Small study effects}
-% <<echo=FALSE, warning=FALSE>>=
-% p.samplesize.z  <- data.ext2 %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% ungroup() %>% 
-%   mutate(std.z = abs(z), sample.size = total1 + total2) %>%
-%   group_by(sample.size) %>% 
-%   summarize(median.effect = median(std.z, na.rm = T)) %>% 
-%   ggplot(aes(x = sample.size, y = median.effect)) + geom_point(size = 0.8) + 
-%   theme_bw() + xlab("sample size") + ylab("median absolute z-score") +
-%   xlim(c(15, 300)) + ylim(c(0, 0.25)) +
-%   scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
-% 
-% p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% 
-%   filter(outcome.measure.new == "Risk Ratio" | 
-%            outcome.measure.new == "Odds Ratio" | 
-%            outcome.measure.new == "Mean Difference" |
-%            outcome.measure.new == "Std. Mean Difference") %>% 
-%   group_by(outcome.measure.new) %>% 
-%   mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
-%   group_by(sample.size, outcome.measure.new) %>% 
-%   summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
-%   ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point(size = .5) + facet_wrap(~outcome.measure.new, scales = "free") + 
-%   theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size") +
-%   xlim(c(15, 300)) +
-%   scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
-% @
-% 
-% The median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
-It is clearly visible that the absolute value decreases with increasing sample size, i.e.
-that the effect size is becoming smaller.
-The trend flattens off after $\sim$ sample size = 400 (not shown).
-% -- Appendix -- \\
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.samplesize.z)
-% @
-% \caption{Median of the absolute $z$-score plotted against the total sample size.}
-% \label{z.samplesize}
-% \end{figure}
-% 
-% Only for illustration, the same trend is reproduced in Figure \ref{effect.samplesize.separated} with a similar method, using the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std.
-Mean Difference'' (the most commonly used in the dataset).
-The ``normalized effect'' is the original effect size, normalized with respect to all other effect sizes of the same measure (i.e.
-subtraction of mean and division through standard error of the mean).
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% plot(p.samplesize.effect.sep)
-% @
-% \caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
-% \label{effect.samplesize.separated}
-% \end{figure}
-% 
-% %Show absolute effect size depending on scaled time? Chunck 3
-
-% Since the tests have different properties, the agreement between the tests can be visualized.
-Here, agreement is specified as classifying the same meta-analysis as significant, based on the 0.1 $p$-value threshold.
-Again, this is done separately for the different outcome types.
-The result can be seen in Figure \ref{fig:test.agreement}.
-In the Figure, the number of agreeing tests is displayed, i.e., how many meta-analyses had only one significant test result etc.
-% 
-% \begin{figure}
-% <<echo = FALSE, fig.height = 5>>=
-% grid.arrange(agree.bin,
-%               agree.cont, 
-%               agree.surv, ncol = 1)
-% @
-% \caption{Barplot for the number of significant test results per meta-analyses, separated for outcome.types}
-% \label{fig:test.agreement}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% <<echo=FALSE>>=
-% plot(p.dist.bin)
-% @
-% \caption{Histogram of the $p$-values for small study effect in binary outcome meta-analyses.
-The testing method is indicated in the header, binwidth is equal to 0.1.
+The Copas selection model also gives an estimate of the number of missing studies.
+It finds that \Sexpr{round(sum(meta.f$missing.Copas, na.rm = T))} are missing, which corresponds to \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% from all \Sexpr{round(sum(meta.f$k))} analysed studies.
+Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
+Note that we have excluded \Sexpr{sum(is.na(meta.f$missing.Copas))} out of \Sexpr{dim(meta.f)[1]}, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
+
+\begin{figure}
+<<echo = FALSE, warning = FALSE>>=
+missing.copas.histogram
+@
+\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ \Sexpr{sum(!is.na(meta.f$missing.Copas))})}
+\label{fig:copas.missing}
+\end{figure}
+
+We can see that in some occasions, the method finds more than half of all studies are missing.
+In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
+The discrepancy between mean and median may indicate that the estimate of \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% missing studies depends somewhat on these extreme cases.
+As can be written of from Table \ref{copas.missing}, 5\%, \ie \Sexpr{round(sum(!is.na(meta.f$missing.Copas))*0.05)} meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for \Sexpr{sum(meta.f$missing.Copas[which(meta.f$missing.Copas >= 17.60)], na.rm = T)}, more than 30\% of missing studies.
+
+<<echo= FALSE, results='asis'>>=
+print(xtable(missing.copas.table, caption = "Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.",
+             label = "copas.missing", align = "lrrrrrrr", digits = c(0,0,0,0,1,1,1,1)),
+      size = "footnotesize")
+@
+
+<<echo=FALSE, results='asis'>>=
+print(xtable(missing.differences, 
+             caption = "Missing meta-analysis pooled treatment effect and adjusted treatment effects.
+Abbreviations are used for z-score (= z) and Hedges g (= g).", label = "missing.differences", align = "llcccrrrrrrrr"),
+      include.rownames = F, size = "tiny")
+@
+
+\subsection{Comparison of adjustment methods}
+Regression adjusted estimates are compared to the estimates of Copas selection model if these are not equal to random effects meta-analysis.
+A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
+We will compare estimates based on all three outcome measures, i.e.
+original measure, $z$-score and Hedges $g$ in Figure \ref{fig:adjustment.mean.diff}.
+Note that the 39 survival outcome data is not included when using $z$-score and Hedges $g$.
+
+\begin{figure}
+<<echo = FALSE, fig.height = 7.5>>=
+grid.arrange(adjustment.mean.diff.orig,
+             adjustment.mean.diff.z,
+             adjustment.mean.diff.d, ncol = 1)
+@
+\caption{Mean - difference plots for publication bias adjustment methods.
+The mean of the adjusted treatment effects is displayed on the $x$-axis and the difference on the $y$-axis.
+Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).
+Two values have been omitted in the middle plot for Hedges $g$ and one for $z$-score (see Table \ref{missing.differences}).}
+\label{fig:adjustment.mean.diff}
+\end{figure}
+
+No formal tests are provided, but the at least there seems to be no clear bias or systematic.
+The limits of agreement in Figure \ref{fig:adjustment.mean.diff} are large.
+We conclude thus that the impact of regression adjustment on the effect sizes is in general not substantially larger than the impact of Copas selection model in the subset of data where the estimate of the Copas selection model is not equal to a random effects estimate.
+\\
+
+\section{Comparison of Tests and Adjustments} \label{sec:comparison.tests.adjustment}
+<<echo = FALSE, warnings = FALSE>>=
+#--------------------------------------------------------------------------------------------------------------------#
+meta.bin <- adjustment.diff.keep %>% filter(outcome.type == "bin")
+meta.cont <- adjustment.diff.keep %>% filter(outcome.type == "cont")
+meta.surv <- adjustment.diff.keep %>% filter(outcome.type == "surv")
+
+dat_text <- data.frame(
+  label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
+                  sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test), sum(meta.bin$tes.d.test, na.rm = T)), "< 0.1,",
+                round(c(mean(meta.bin$harbord.test), mean(meta.bin$peter.test), 
+                        mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test), mean(meta.bin$tes.d.test, na.rm = T)),2)*100, "%"),
+  test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer", "pval.d.tes"),
+  bias.side = rep(0, times = 5))
+
+labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer", pval.d.tes = "Excess Significance")
+
+p.dist.bin.corrected <- meta.bin  %>% ungroup() %>% 
+  select(bias.side, pval.harbord, pval.peter, pval.rucker, pval.schwarzer, pval.d.tes) %>% 
+  gather(key = "test.type", value = "p.value", pval.harbord:pval.d.tes) %>% 
+  ggplot(aes(x = p.value, fill = factor(bias.side))) + 
+  geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + theme(legend.position = "none") +
+  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 200, label = label), color = "black") + 
+  theme(strip.text.x = element_text(size=7)) + 
+  ggtitle("Binary Outcomes")
+
+#--------------------------------------------------------------------------------------------------------------------#
+#Continuous Outcomes:
+dat_text <- data.frame(
+  label = paste(c(sum(meta.cont$begg.test), sum(meta.cont$egger.test), sum(meta.cont$thompson.test), sum(meta.cont$tes.d.test, na.rm = T)), "< 0.1,",
+                round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test), mean(meta.cont$tes.d.test, na.rm = T)),2)*100, "%"),
+  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"),
+  bias.side = rep(0, times = 4))
+
+labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp", pval.d.tes = "Excess significance")
+
+p.dist.cont.corrected <- meta.cont %>% ungroup() %>% 
+  select(bias.side, pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
+  gather(key = "test.type", value = "p.value", pval.egger:pval.d.tes) %>% 
+  ggplot(aes(x = p.value, fill = factor(bias.side))) + 
+  geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + theme(legend.position = "none") +
+  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 60, label = label),  color = "black") + 
+  theme(strip.text.x = element_text(size=7)) + ggtitle("Continuous Outcomes")
+
+#--------------------------------------------------------------------------------------------------------------------#
+dat_text <- data.frame(
+  label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), 
+                  sum(meta.surv$thompson.test), sum(meta.surv$tes.d.test, na.rm = T)), "< 0.1,",
+                round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), 
+                        mean(meta.surv$thompson.test), 
+                        mean(meta.surv$tes.d.test, na.rm = T)),2)*100, "%"),
+  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"),
+  bias.side = rep("publication bias", times = 4))
+p.dist.surv.corrected <- meta.surv %>% ungroup() %>% 
+  mutate(bias.side = factor(ifelse(bias.side == 1, "publication bias", "negative publication bias"))) %>% 
+  select(bias.side, pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
+  gather(key = "test.type", value = "p.value", pval.egger:pval.d.tes) %>% 
+  ggplot(aes(x = p.value, fill = factor(bias.side))) + 
+  geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + guides(fill=guide_legend(title=NULL))+
+  theme(legend.position = "bottom") +
+  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 10, label = label),  color = "black") + 
+  theme(strip.text.x = element_text(size=7)) + ggtitle("Survival Outcomes")
+@
+
+In section \ref{sec:change.size}, we have seen that some adjustments for small study effects are not in line with our previous definition of publication bias: Some times, the adjustment for small study effects leads to a larger treatment effect.
+We want to take this into account when considering evidence for publication bias.
+Whenever adjustment leads to larger effect sizes, the small study effect test result from section \ref{sec:publication.bias.tests} is revised and changed to negative.
+We will revisit the results from section \ref{sec:publication.bias.tests} and first visualize which proportion of the data finds rather ``negative publication bias'' than the predefined type of publication bias.
+Figure \ref{fig:test.corrected} is equal to Figure \ref{fig:test} with sole difference that now the proportion of ``negative publication bias'' is colored, and the count of significant findings is corrected (not significant for negative publication bias).
+\\
+
+\begin{figure}
+<<echo=FALSE, fig.height = 9>>=
+grid.arrange(p.dist.bin.corrected,
+             p.dist.cont.corrected,
+             p.dist.surv.corrected, ncol = 1)
+@
+\caption{Histogram of the $p$-values for small study effect in meta-analyses.
+The testing method is indicated in the header, bin width is equal to 0.1.
 The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-% \label{fig:test.bin}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% plot(p.dist.cont)
-% @
-% \caption{Histogram of the $p$-values for the small study effect in continuous outcome meta-analyses.
-The testing method is indicated in the header, binwidth is equal to 0.1.
-The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-% \label{fig:test.cont}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% plot(p.dist.surv)
-% @
-% \caption{Histogram of the $p$-values for the small study effect in survival outcome meta-analyses.
-The testing method is indicated in the header, binwidth is equal to 0.1.
-The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-% \label{fig:test.surv}
-% \end{figure}
-
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(adjustment.stat.z)
-% @
-% \caption{Histogram of the wald test-statistic of meta-analysis and adjusted pooled treatment effect, based on the z-score.
-The method is indicated in the header, binwidth is set to 1.
-The significant proportion based on the threshold of 0.05 is displayed inside the figures (The red line displays the corresponding quantile of the std.
-normal, 1.96).}
-% \label{fig:adjustment.stat.z}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(adjustment.stat.d)
-% @
-% \caption{Histogram of the wald test-statistic of meta-analysis and adjusted pooled treatment effect, based on Hedges $g$ or Cohen's $d$.
-The method is indicated in the header, binwidth is set to 1.
-The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
-% \label{fig:adjustment.stat.d}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(adjustment.stat.log.hazard.ratio)
-% @
-% \caption{Histogram of the wald test-statistic of meta-analysis and adjusted pooled treatment effect, based on the $z$-score.
-The method is indicated in the header, binwidth is set to 1.
-The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
-% \label{fig:adjustment.stat.log.hazard.ratio}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% 
-% <<echo=FALSE, warning=FALSE>>=
-% #Test Results: Binary
-% test.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-%                                                           schwarzer.test = mean(schwarzer.test),
-%                                                           rucker.test = mean(rucker.test),
-%                                                           harbord.test = mean(harbord.test),
-%                                                           peter.test = mean(peter.test))
-% test.bin <- test.bin %>% gather(key = "test.type", value = "mean")
-% 
-% p.bin <- meta.bin %>% ungroup() %>% 
-%   select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
-%   gather(key = "test.type", value = "null.hypothesis") %>%  
-%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-%   theme_bw() + xlab(label = NULL) +
-%   annotate("text", x = test.bin$test.type, y = 1000, 
-%            label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
-%            color = "white")
-% 
-% 
-% 
-% test.sig.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-%                                                               schwarzer.test = mean(schwarzer.test),
-%                                                               rucker.test = mean(rucker.test),
-%                                                               harbord.test = mean(harbord.test),
-%                                                               peter.test = mean(peter.test))
-% test.sig.bin <- test.sig.bin %>% gather(key = "test.type", value = "mean")
-% 
-% p1 <- meta.bin %>% ungroup() %>% filter(sig.fixef.bin == 1) %>% 
-% select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
-%   gather(key = "test.type", value = "null.hypothesis") %>% 
-%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-%   theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
-%   annotate("text", x = test.sig.bin$test.type, y = 1750, 
-%            label = paste(round(test.sig.bin$mean, 2)*100, "% rejected"), 
-%            color = "white")
-% 
-% test.nonsig.bin <- meta.bin %>% filter(sig.fixef.bin == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-%                                                                                                 schwarzer.test = mean(schwarzer.test),
-%                                                                                                 rucker.test = mean(rucker.test),
-%                                                                                                 harbord.test = mean(harbord.test),
-%                                                                                                 peter.test = mean(peter.test))
-% test.nonsig.bin <- test.nonsig.bin %>% gather(key = "test.type", value = "mean")
-% 
-% p2 <- meta.bin %>% 
-%   filter(sig.fixef.bin == 0) %>% ungroup() %>% 
-%   select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
-%   gather(key = "test.type", value = "null.hypothesis") %>% 
-%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-%   theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) +theme(legend.position="none") +
-%   annotate("text", x = test.nonsig.bin$test.type, y = 650, 
-%            label = paste(round(test.nonsig.bin$mean, 2)*100, "% rejected"), 
-%            color = "white")
-% 
-% range.pb.difference.bin <- range(test.sig.bin$mean - test.nonsig.bin$mean)
-% 
-% #Test Results: Continuous
-% test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-%                                                             begg.test = mean(begg.test),
-%                                                             thomson.test = mean(thomson.test))
-% 
-% test.cont <- test.cont %>% gather(key = "test.type", value = "mean")
-% 
-% p.cont <- meta.cont %>% ungroup() %>% 
-%   select(egger.test, thomson.test, begg.test) %>% 
-%   gather(key = "test.type", value = "null.hypothesis") %>% 
-%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-%   theme_bw() + xlab(label = NULL) +
-%   annotate("text", x = test.cont$test.type, y = 750, 
-%            label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
-%            color = "white")
-% 
-% 
-% test.sig.cont <- meta.cont %>% filter(sig.fixef.cont == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-%                                                                                                 begg.test = mean(begg.test),
-%                                                                                                 thomson.test = mean(thomson.test))
-% 
-% test.sig.cont <- test.sig.cont %>% gather(key = "test.type", value = "mean")
-% 
-% p3 <- meta.cont %>% 
-%   filter(sig.fixef.cont == 1) %>% ungroup() %>% 
-%   select(egger.test, thomson.test, begg.test) %>% 
-%   gather(key = "test.type", value = "null.hypothesis") %>% 
-%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-%   theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
-%   annotate("text", x = test.sig.cont$test.type, y = 600, 
-%            label = paste(round(test.sig.cont$mean, 2)*100, "% rejected"), 
-%            color = "white")
-% 
-% test.nonsig.cont <- meta.cont %>% filter(sig.fixef.cont == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-%                                                                                                    begg.test = mean(begg.test),
-%                                                                                                    thomson.test = mean(thomson.test))
-% 
-% test.nonsig.cont <- test.nonsig.cont %>% gather(key = "test.type", value = "mean")
-% 
-% p4 <- meta.cont %>% 
-%   filter(sig.fixef.cont == 0) %>% ungroup() %>% 
-%   select(egger.test, thomson.test, begg.test) %>% 
-%   gather(key = "test.type", value = "null.hypothesis") %>% 
-%   mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
-%   ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-%   theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
-%   annotate("text", x = test.nonsig.cont$test.type, y = 100, 
-%            label = paste(round(test.nonsig.cont$mean, 2)*100, "% rejected"), 
-%            color = "white")
-% 
-% range.pb.difference.cont <- range(test.sig.cont$mean - test.nonsig.cont$mean)
-% 
-% ########################################################################################################################################
-% ########################################################################################################################################
-% 
-% #Agreement proportions of publication bias tests:
-% 
-% #Binary:
-% n.bin <- dim(meta.bin)[1]
-% meta.bin <- meta.bin %>%ungroup() %>%  mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
-%                                         egger.peter = ifelse(egger.test == peter.test, "agree", "disagree"),
-%                                         egger.rucker = ifelse(egger.test == rucker.test, "agree", "disagree"),
-%                                         egger.harbord = ifelse(egger.test == harbord.test, "agree", "disagree"),
-%                                         schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
-%                                         schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
-%                                         schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
-%                                         rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
-%                                         rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
-%                                         harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
-% 
-% agreement.bin <- meta.bin %>% ungroup() %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
-%                                             egger.peter = sum(egger.peter == "agree")/n(),
-%                                             egger.rucker = sum(egger.rucker == "agree")/n(),
-%                                             egger.harbord = sum(egger.harbord == "agree")/n(),
-%                                             schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
-%                                             schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
-%                                             schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
-%                                             rucker.peter = sum(rucker.peter == "agree")/n(),
-%                                             harbord.peter = sum(harbord.peter == "agree")/n())
-% 
-% correlation.bin <- meta.bin %>%ungroup() %>%  summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
-%                                               egger.peter = cor(pval.egger.bin, pval.peter.bin),
-%                                               egger.rucker = cor(pval.egger.bin, pval.rucker.bin),
-%                                               egger.harbord = cor(pval.egger.bin, pval.harbord.bin),
-%                                               schwarzer.peter = cor(pval.schwarzer.bin, pval.peter.bin),
-%                                               schwarzer.rucker = cor(pval.schwarzer.bin, pval.rucker.bin),
-%                                               schwarzer.harbord = cor(pval.schwarzer.bin, pval.harbord.bin),
-%                                               rucker.peter = cor(pval.rucker.bin, pval.peter.bin),
-%                                               harbord.peter = cor(pval.harbord.bin, pval.peter.bin))
-% 
-% binary.tests.agreement <- rbind(agreement.bin, correlation.bin)
-% rownames(binary.tests.agreement) <- c("Test Agreement","P-value Correlation")
-% 
-% 
-% #Continuous:
-% n.cont <- dim(meta.cont)[1]
-% meta.cont <- meta.cont %>% ungroup() %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
-%                                           thomson.begg = ifelse(thomson.test == begg.test, "agree", "disagree"),
-%                                           egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"))
-% 
-% agreement.cont <- meta.cont %>% ungroup() %>%  summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
-%                                               thomson.begg = sum(thomson.begg == "agree")/n(),
-%                                               egger.begg = sum(egger.begg == "agree")/n())
-% 
-% correlation.cont <- meta.cont %>% ungroup() %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
-%                                                 thomson.begg = cor(pval.thomson.cont, pval.begg.cont),
-%                                                 egger.begg = cor(pval.egger.cont, pval.begg.cont))
-% 
-% cont.tests.agreement <- rbind(agreement.cont, correlation.cont)
-% rownames(cont.tests.agreement) <- c("Test Agreement","P-value Correlation")
-% 
-% ########################################################################################################################################
-% ########################################################################################################################################
-% 
-% 
-% #Trimfill missing studies fractions statistics:
-% trimfill.cont.mean <- meta.cont %>% ungroup %>% summarise(mean = mean(missing.trim.cont)) %>% select(mean)
-% trimfill.cont.median <- meta.cont %>% ungroup %>% summarise(median = median(missing.trim.cont)) %>% select(median)
-% 
-% trimfill.bin.mean <- meta.bin %>% ungroup %>% summarise(mean = mean(missing.trim.bin)) %>% select(mean)
-% trimfill.bin.median <- meta.bin %>% ungroup %>% summarise(median = median(missing.trim.bin)) %>% select(median)
-% 
-% ########################################################################################################################################
-% ########################################################################################################################################
-% 
-% change.ranef.bin <- meta.bin %>% ungroup() %>% 
-%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n)) 
-% 
-% p.change.ranef.bin <- meta.bin %>% ungroup() %>% 
-%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>%  
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+ 
-%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.ranef.bin[change.ranef.bin$sig.change == 3,]$correction.method, y = 1000, 
-%          label = paste(round(change.ranef.bin[change.ranef.bin$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-%          color = "white")
-% 
-% change.ranef.cont <- meta.cont %>% ungroup() %>% 
-%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
-%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n))
-% 
-% p.change.ranef.cont <- meta.cont %>% ungroup() %>% 
-%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>%  
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes") +
-%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.ranef.cont[change.ranef.cont$sig.change == 3,]$correction.method, y = 500, 
-%          label = paste(round(change.ranef.cont[change.ranef.cont$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-%          color = "white")
-% 
-% change.ranef <- meta %>% ungroup() %>% 
-%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
-%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n))
-% 
-% p.ranef.change <- meta %>% ungroup() %>% 
-%   select(sig.change.ranef.reg, sig.change.ranef.copas, sig.change.ranef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>%  
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.ranef[change.ranef$sig.change == 3,]$correction.method, y = 1500, 
-%          label = paste(round(change.ranef[change.ranef$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
-%          color = "white")
-% # Significance after correction plots, separated for meta-analyses with significant publication bias test.
-% #Fixed effects meta-analysis significance
-% #Binary outcomes:
-% change.fixef.bin <- meta.bin %>% ungroup() %>% 
-%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
-%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n))
-% 
-% p.change.fixef.bin <- meta.bin %>% ungroup() %>% 
-%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>%  
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%   
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Binary outcomes")+  
-%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.fixef.bin[change.fixef.bin$sig.change == 3,]$correction.method, y = 800, 
-%          label = paste(round(change.fixef.bin[change.fixef.bin$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
-%          color = "white")
-% 
-% #Continuous outcomes:
-% change.fixef.cont <- meta.cont %>% ungroup() %>% 
-%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>% 
-%   mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n))
-% 
-% p.change.fixef.cont <- meta.cont %>% ungroup() %>% 
-%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>%  
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + ggtitle("Continuous outcomes")+ 
-%   theme_bw() + xlab(label = NULL) + scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.fixef.cont[change.fixef.cont$sig.change == 3,]$correction.method, y = 300, 
-%          label = paste(round(change.fixef.cont[change.fixef.cont$sig.change == 3,]$n*100, 2), "changed to nonsig."), 
-%          color = "white")
-% 
-% #Overall:
-% change.fixef <- meta %>% ungroup() %>% select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-% 	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n))
-% 
-% p.fixef.change <- meta %>% ungroup() %>% 
-%   select(sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change") %>%  
-%   mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-%   theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
-% 	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.fixef[change.fixef$sig.change == 3,]$correction.method, y = 1500, 
-%          label = paste(round(change.fixef[change.fixef$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-%          color = "white")
-% 
-% #Separated for meta-analyses with significant publication bias test.
-% change.fixef.bias <- meta %>% 
-%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-%   filter(thomson.test == 1) %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-% 	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>% 
-% 	mutate(n = n/sum(n))
-% 
-% p.change.fixef.bias <- meta %>% 
-%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-%   filter(thomson.test == 1) %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>% 
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-%   theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
-% 	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.fixef.bias[change.fixef.bias$sig.change == 3,]$correction.method, y = 250, 
-%            label = paste(round(change.fixef.bias[change.fixef.bias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-%            color = "white")
-% 
-% change.fixef.unbias <- meta %>% 
-%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-%   filter(thomson.test == 0) %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-% 	group_by(sig.change, correction.method) %>% count() %>% group_by(correction.method) %>%  
-% 	mutate(n = n/sum(n))
-% 
-% p.change.fixef.unbias <- meta %>% 
-%   select(thomson.test, rucker.test, sig.change.fixef.reg, sig.change.fixef.copas, sig.change.fixef.trimfill) %>% 
-%   gather(key = "correction.method", value = "sig.change", sig.change.fixef.reg:sig.change.fixef.trimfill) %>% 
-%   filter(thomson.test == 0) %>% 
-% 	mutate(sig.change = factor(ifelse(sig.change == 0 |sig.change == 2, 0, sig.change))) %>%
-%   ggplot(aes(x = correction.method, fill = sig.change)) + geom_bar() + coord_flip() + 
-%   theme_bw() + xlab(label = NULL) + guides(fill=guide_legend(title=NULL)) +
-% 	scale_fill_discrete(labels= c("unchanged", "change.to.sig", "change.to.nonsig")) +
-%   annotate("text", x = change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$correction.method, y = 1300, 
-%            label = paste(round(change.fixef.unbias[change.fixef.unbias$sig.change == 3,]$n*100, 2), "% changed to nonsig."), 
-%            color = "white")
-% 
-% 
-% ########################################################################################################################################
-% ########################################################################################################################################
-% 
-% p.missing.copas <- meta %>% ggplot(aes(x = missing.copas/n)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20)
-% p.missing.trim <- meta %>% ggplot(aes(x = missing.trim)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20)
-% @
-% 
-% There are tests that can be applied to find out if small study effects are present in the meta analysis.
-For the precise description, see the methods section.
-Application of the tests is only recommended if there are ten or more studies \citep{cochrane.handbook} that can be used, so all meta-analyses with less than ten studies have been excluded.
-% 
-% \vspace{0mm}
-% There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
-In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = \Sexpr{n.cont})
-% The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = \Sexpr{n.bin}).
-The amount of studies varies from 5\% (Schwarzer's Test) to 13 \% (Egger's Test) for binary outcomes and 9\% (Begg and Mazumdar's Test) to 25 \% (Egger's Test) for continuous outcomes.
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.cont)
-% @
-% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-% \label{bias.results.cont}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.bin)
-% @
-% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-% \label{bias.results.bin}
-% \end{figure}
-% 
-% There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not.
-Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by \Sexpr{range.pb.difference.bin[2]} (the minimal increase is \Sexpr{range.pb.difference.bin[1]} for Schwarzer's Test).
-% 
-% %Show plots of significant meta-analyses separated? Chunck 4
-% 
-% Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses).
-The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}.
-The Figure suggests that the frequency of publication bias remains constant over time.
-The mean publication years have been restricted such that at least 180 meta-analyses are available per year, such that random fluctuation is restricted to some extent.
-The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
-%   ggplot(aes(x = mean.publication.year, fill = factor(thomson.test), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% @
-% \caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
-% \label{pub.bias.overtime}
-% \end{figure}
-% 
-% 
-% The agreement of the tests, i.e.
-the proportion of meta-analyses where the rest results are equal between tests, is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
-Agreement in tests for binary outcomes is better than continuous outcomes, with some variation between tests (binary outcomes: 83 to 91\%).
-Correlation varies more between tests, both for continuous and binary outcome tests.
-% 
-% <<results = 'asis', echo = FALSE, warning = FALSE>>=
-% print(xtable(x = t(binary.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)", label = "agreement.bin",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
-% @
-% 
-% 
-% <<results = 'asis', echo = FALSE, warning = FALSE>>=
-% print(xtable(x = t(cont.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)", label = "agreement.cont",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
-% @
-% 
-% \vspace{0mm}
-% Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
-The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}.
-%(Suggests that 10 is likely too small)
-% In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
-A trend towards more rejections for larger sample sizes can be seen.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% meta %>% filter(n < 40) %>% ggplot(aes(stat(count), x = n, fill = factor(thomson.test))) + 
-%   geom_density(position = "fill")
-% @
-% \caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
-% \label{pvalues.samplesize}
-% \end{figure}
-% 
-% 
-% 
-% \vspace{0mm}
-% One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
-The mean fraction of trimmed comparisons for binary outcomes is \Sexpr{round(trimfill.bin.mean,2)} and the median \Sexpr{round(trimfill.bin.median,2)}.
-% % A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
-In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses.
-% In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
-In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% meta.bin %>% filter(missing.trim.bin < 0.5) %>% 
-%   ggplot(aes(x = missing.trim.bin, fill = factor(peter.test), stat(count))) + 
-%   geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% @
-% \caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
-% \label{trimfill.pvalues.bin}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% meta.cont %>% filter(missing.trim.cont < 0.5) %>% 
-%   ggplot(aes(x = missing.trim.cont, fill = factor(thomson.test), stat(count))) + 
-%   geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% @
-% \caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
-% \label{trimfill.pvalues.cont}
-% \end{figure}
-% 
-% 
-% \subsection{Small Study Effect Correction}
-% Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
-Three of them will be applied to the meta-analyses shown previously that have ten or more study results and are therefore eligible for testing for publication bias.
-% 
-% \vspace{0mm}
-% The extent to what the results of the meta-analysis results are changed can be investigated.
-Because statistical significance is often used to decide if there is a treatment effect, a non-significant corrected effect size estimate can indicate that an observed treatment effect has been accepted because of small study effects.
-Therefore, the cases have been counted in which
-% \begin{enumerate}
-% \item Significance or non-significance of pooled estimate of meta-analysis did not change after correction for small study effects.
-% \item Significance of pooled estimate of meta-analysis did change to non-significance after correction for small study effects.
-% \item Non-significance of pooled estimate of meta-analysis did change to significance after correction for small study effects.
-% \end{enumerate}
-% 
-% The results of this can be seen in Figure \ref{significance.change.fixed} for all three methods, comparing the significance of the corrected pooled effect size estimate with the significance of the pooled effect size estimate of the fixed effects meta-analysis.
-The same for significance of random effects meta-analysis is shown in Figure \ref{significance.change.random}.
-The significance threshold was chosen such that the $p$-value had to be < 0.05 for rejection of the null hypothesis of no treatment effect.
-The correction methods were trim-and-fill, copas selection model and regression with random effects and shrinkage of within-study-variance methods.
-More details to the applied correction methods and their application are in the methods section \ref{methods}.
-Notably, the correction methods has been applied to all meta-analyses, thus also for such that had no significant small study effect test result.
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.fixef.change)
-% @
-% \caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction.}
-% \label{significance.change.fixed}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.ranef.change)
-% @
-% \caption{Change in signficance of random effects meta-analysis pooled estimate after correction.}
-% \label{significance.change.random}
-% \end{figure}
-% 
-% Since it has been previously seen in Figure \ref{test.results} that the results of small study effects vary considerably between continuous outcomes, the results in significance change from fixed effects meta-analysis can be seen separately in Figure \ref{significance.change.fixed.sep} for continuous and binary outcomes.
-The change in significance from random effects meta-analysis to significance of corrected estimate can be seen in Figure \ref{significance.change.fixed.sep}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p.change.fixef.bin, p.change.fixef.cont, ncol = 1)
-% @
-% \caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-% \label{significance.change.fixed.sep}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p.change.ranef.bin, p.change.ranef.cont, ncol = 1)
-% @
-% \caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-% \label{significance.change.random}
-% \end{figure}
-% 
-% Because the real amount of publication bias in the dataset is not known, the correction method can also be applied only to meta-analyses that have publication bias according to the small study effect tests in the previous section.
-Because the test developed by \citet{thomson.sharp} has been applied to both binary and continuous outcome meta-analyses (in the case of binary outcomes to arcsine variance stabilized proportions), it is used as a criterium to distinguish biased from unbiased meta-analyses.
-The proportions of significance tests of pooled treatment effects that turned from significant to non-significant, non-significant to significant etc.
-are shown in Figure \ref{significance.change.fixed.sep}.
-Fixed effects meta-analysis has been used to determine signficance of the uncorrected estimate.
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p.change.fixef.bias, p.change.fixef.unbias, ncol = 1)
-% @
-% \caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-% \label{significance.change.random}
-% \end{figure}
-% 
-% Similarly, the number of missing studies per meta-analysis, i.e.
-those which have not been included because of small study effects, are estimated by the copas and trim-and-fill method and their empirical distribution is shown in histograms in Figure \ref{missing.studies.distribution}.
-For visualisation, the fraction of unpublished studies from the total fraction of available studies is shown.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p.missing.copas, p.missing.trim, ncol = 1)
-% @
-% \caption{Fraction of missing studies estimated of the number of total studies included in the meta-analysis for copas selection and trim-and-fill method.}
-% \label{missing.studies.distribution}
-% \end{figure}
-% 
-% 
-% 
-% 
-% % # <<results = 'asis', Echo = FALSE>>=
-% % # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
-% % #                                             schwarzer.rejection = mean(schwarzer.test),
-% % #                                             rucker.rejection = mean(rucker.test),
-% % #                                             harbord.rejection = mean(harbord.test),
-% % #                                             peter.rejection = mean(peter.test))
-% % # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
-% % # @
-% 
-% 
-% 
-% 
-% 
-% 
-% % 
-% % For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
-The following three figures show the distribution of p-values of the corresponding tests.
-Note that only meta analyses with more than 10 comparisons have been included.
-% % 
-% % \vspace{0mm}
-% % Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
-The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
-% % 
-% % \begin{figure}
-% % <<echo=FALSE>>=
-% % data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-% %   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-% %   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-% %   mutate(n = n()) %>% filter(n > 9) %>% 
-% %   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-% %                             method = "linreg")$p.val) %>% 
-% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-% %   theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% % @
-% % \caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
-% % \label{egger.cont}
-% % \end{figure}
-% % 
-% % 
-% % \begin{figure}
-% % <<echo=FALSE>>=
-% % data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-% %   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-% %   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-% %   mutate(n = n()) %>% filter(n > 9) %>% 
-% %   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-% %                             method = "mm")$p.val) %>% 
-% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-% %   theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% % @
-% % \caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
-% % \label{thomson.cont}
-% % \end{figure}
-% % 
-% % \begin{figure}
-% % <<echo=FALSE>>=
-% % data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-% %   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-% %   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-% %   mutate(n = n()) %>% filter(n > 9) %>% 
-% %   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-% %                             method = "rank")$p.val) %>% 
-% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-% %   theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% % @
-% % \caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
-% % \label{begg.cont}
-% % \end{figure}
-% % 
-% % 
-% % For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
-% % 
-% % \begin{figure}
-% % <<echo=FALSE>>=
-% % data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-% %   filter(events1 > 0 | events2 > 0) %>% 
-% %   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-% %   mutate(n = n()) %>% filter(n > 9) %>% 
-% %   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
-% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-% %   theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% % @
-% % \caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
-% % \label{peters.bin}
-% % \end{figure}
-% % 
-% % 
-% % \begin{figure}
-% % <<echo=FALSE>>=
-% % data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-% %   filter(events1 > 0 | events2 > 0) %>% 
-% %   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-% %   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-% %   mutate(n = n()) %>% filter(n > 9) %>% 
-% %   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
-% %   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-% %   theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% % @
-% % \caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
-% % \label{harbord.bin}
-% % \end{figure}
-% 
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% % Since most of the times the study publication year is available for a given result, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.
-The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
-% % 
-% % \begin{figure}
-% % <<echo=FALSE, warning=FALSE>>=
-% % data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-% %   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
-% % @
-% % \caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
-% % \label{study.significance.overtime}
-% % \end{figure}
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 2
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% % The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
-Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
-The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested.
-This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
-% % 
-% % \begin{figure}
-% % <<echo=FALSE, warning=FALSE>>=
-% % grid.arrange(sig.meta.Q1, nonsig.meta.Q, ncol= 1)
-% % @
-% % \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-% % by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-% % \label{primary.secondary.significance.sep.sig}
-% % \end{figure}
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 3
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% % A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
-This can again be done for the entire dataset, i.e.
-for all effect estimates and their ordering in time.
-It is important to scale the effect estimates here with respect to the estimates of the replication studies that are about the same subject, have the same outcome measure, etc.
-Also, only effect estimates that can be compared to other estimates before are included, i.e.
-only study results with one or more replica are included.
-Time needs to be scaled and normalized in order to compare multiple time-trends in effect size to each other and gain insights in the overall trend.
-This is done in Figure \ref{effects.overtime.separated}, separared for odds rati, risk ratio, and mean and standardized difference outcome measures.
-In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
-% % 
-% % \begin{figure}
-% % <<echo=FALSE>>=
-% % data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
-% %                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
-% %   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
-% %   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
-% %   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
-% %   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
-% %   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
-% % @
-% % \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
-% % \label{effects.overtime.separated}
-% % \end{figure}
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 4
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% % The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
-This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
-% % 
-% % \begin{figure}
-% % <<echo=FALSE, warning=FALSE>>=
-% % grid.arrange(p3, p4, ncol = 2)
-% % @
-% % \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-% % \label{bias.results.cont.sep}
-% % \end{figure}
-% % 
-% % \begin{figure}
-% % <<echo=FALSE, warning=FALSE>>=
-% % grid.arrange(p1, p2, ncol = 2)
-% % @
-% % \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-% % \label{bias.results.bin.sep}
-% % \end{figure}
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 5
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% % #Proportion of significant pooled estimates based on proportion of single pooled estimates
-% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type)) + geom_histogram()
-% % 
-% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
-% %   geom_density(na.rm = T, position = "fill") + 
-% %   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% % 
-% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
-% %   geom_histogram(position = "fill")
-% % 
-% % mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef))) + 
-% %   geom_histogram()
-% 
-% % \begin{figure}
-% % <<echo=FALSE, warning=FALSE>>=
-% % plot(p.secondary.over.meansig)
-% % @
-% % \caption{Fraction of significant meta-analysis, dependent on the fraction of significant single results.}
-% % \label{secondary.significance.over.meansig}
-% % \end{figure}
-% 
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 6
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% #Agreement proportions of publication bias tests:
-% 
-% #Binary:
-% meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
-%                                               tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
-%                                               tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
-%                                               tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
-%                                               schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
-%                                               schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
-%                                               schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
-%                                               rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
-%                                               rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
-%                                               harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
-% agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
-%                                                       tes.d.peter = sum(tes.d.peter == "agree")/n(),
-%                                                       tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
-%                                                       tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
-%                                                       schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
-%                                                       schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
-%                                                       schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
-%                                                       rucker.peter = sum(rucker.peter == "agree")/n(),
-%                                                       harbord.peter = sum(harbord.peter == "agree")/n())
-% correlation.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = cor(stat.d.tes, stat.schwarzer),
-%                                                         tes.d.peter = cor(stat.d.tes, stat.peter),
-%                                                         tes.d.rucker = cor(stat.d.tes, stat.rucker),
-%                                                         tes.d.harbord = cor(stat.d.tes, stat.harbord),
-%                                                         schwarzer.peter = cor(stat.schwarzer, stat.peter),
-%                                                         schwarzer.rucker = cor(stat.schwarzer, stat.rucker),
-%                                                         schwarzer.harbord = cor(stat.schwarzer, stat.harbord),
-%                                                         rucker.peter = cor(stat.rucker, stat.peter),
-%                                                         harbord.peter = cor(stat.harbord, stat.peter))
-% # rsquared.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = summary(lm(stat.d.tes~ stat.schwarzer))$r.squared,
-% #                                                         tes.d.peter = summary(lm(stat.d.tes~ stat.peter))$r.squared,
-% #                                                         tes.d.rucker = summary(lm(stat.d.tes~ stat.rucker))$r.squared,
-% #                                                         tes.d.harbord = summary(lm(stat.d.tes~ stat.harbord))$r.squared,
-% #                                                         schwarzer.peter = summary(lm(stat.schwarzer~ stat.peter))$r.squared,
-% #                                                         schwarzer.rucker = summary(lm(stat.schwarzer~ stat.rucker))$r.squared,
-% #                                                         schwarzer.harbord = summary(lm(stat.schwarzer~ stat.harbord))$r.squared,
-% #                                                         rucker.peter = summary(lm(stat.rucker~ stat.peter))$r.squared,
-% #                                                         harbord.peter = summary(lm(stat.harbord~ stat.peter))$r.squared)
-% meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test + schwarzer.test > 1, "agree", "disagree"),
-%                                               tes.d.peter = ifelse(tes.d.test + peter.test > 1, "agree", "disagree"),
-%                                               tes.d.rucker = ifelse(tes.d.test + rucker.test > 1, "agree", "disagree"),
-%                                               tes.d.harbord = ifelse(tes.d.test + harbord.test > 1, "agree", "disagree"),
-%                                               schwarzer.peter = ifelse(schwarzer.test + peter.test > 1, "agree", "disagree"),
-%                                               schwarzer.rucker = ifelse(schwarzer.test + rucker.test > 1, "agree", "disagree"),
-%                                               schwarzer.harbord = ifelse(schwarzer.test + harbord.test > 1, "agree", "disagree"),
-%                                               rucker.peter = ifelse(rucker.test + peter.test > 1, "agree", "disagree"),
-%                                               rucker.harbord = ifelse(rucker.test + harbord.test > 1, "agree", "disagree"),
-%                                               harbord.peter = ifelse(harbord.test + peter.test > 1, "agree", "disagree"))
-% agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/sum(schwarzer.test),
-%                                                       tes.d.peter = sum(tes.d.peter == "agree")/sum(peter.test),
-%                                                       tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
-%                                                       tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
-%                                                       schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
-%                                                       schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
-%                                                       schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
-%                                                       rucker.peter = sum(rucker.peter == "agree")/n(),
-%                                                       harbord.peter = sum(harbord.peter == "agree")/n())
-% 
-% binary.tests.agreement <- rbind(agreement.bin, correlation.bin, rsquared.bin)
-% rownames(binary.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
-% colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
-%                                       "Excess significance, Rucker", "Excess significance, Harbord",
-%                                       "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
-%                                       "Rucker, Peter", "Harbord, Peter")
-% #--------------------------------------------------------------------------------------------------------------------#
-% 
-% 
-% #Continuous:
-% meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
-%                                                 thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
-%                                                 egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
-%                                                 tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
-%                                                 thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
-%                                                 tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-% agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
-%                                                          thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
-%                                                          tes.d.begg = sum(tes.d.begg == "agree")/n(),
-%                                                          thompson.egger = sum(thompson.egger == "agree")/n(),
-%                                                          thompson.begg = sum(thompson.begg == "agree")/n(),
-%                                                          egger.begg = sum(egger.begg == "agree")/n())
-% correlation.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = cor(stat.egger, stat.d.tes),
-%                                                           thompson.tes.d = cor(stat.thompson, stat.d.tes),
-%                                                           tes.d.begg = cor(stat.d.tes, stat.begg),
-%                                                           thompson.egger = cor(stat.thompson, stat.egger),
-%                                                           thompson.begg = cor(stat.thompson, stat.begg),
-%                                                           egger.begg = cor(stat.egger, stat.begg))
-% rsquared.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = summary(lm(stat.egger~ stat.d.tes))$r.squared,
-%                                                        thompson.tes.d = summary(lm(stat.thompson~ stat.d.tes))$r.squared,
-%                                                        tes.d.begg = summary(lm(stat.d.tes~ stat.begg))$r.squared,
-%                                                        thompson.egger = summary(lm(stat.thompson~ stat.egger))$r.squared,
-%                                                        thompson.begg = summary(lm(stat.thompson~ stat.begg))$r.squared,
-%                                                        egger.begg = summary(lm(stat.egger~ stat.begg))$r.squared)
-% agreement.sig.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
-%                                                              thompson.tes.d = sum(thompson.tes.d == "agree")/sum(thompsom.test),
-%                                                              tes.d.begg = sum(tes.d.begg == "agree")/sum(begg.test),
-%                                                              thompson.egger = sum(thompson.egger == "agree")/sum(egger.test),
-%                                                              thompson.begg = sum(thompson.begg == "agree")/sum(thompson.test),
-%                                                              egger.begg = sum(egger.begg == "agree")/sum(egger.test))
-% 
-% 
-% 
-% cont.tests.agreement <- rbind(agreement.cont, correlation.cont, rsquared.cont)
-% rownames(cont.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
-% colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson", 
-%                                      "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")
-% 
-% #--------------------------------------------------------------------------------------------------------------------#
-% 
-% 
-% #Survival:
-% meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
-%                                                 thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
-%                                                 egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
-%                                                 tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
-%                                                 thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
-%                                                 tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-% agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
-%                                                          thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
-%                                                          tes.d.begg = sum(tes.d.begg == "agree")/n(),
-%                                                          thompson.egger = sum(thompson.egger == "agree")/n(),
-%                                                          thompson.begg = sum(thompson.begg == "agree")/n(),
-%                                                          egger.begg = sum(egger.begg == "agree")/n())
-% correlation.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = cor(stat.egger, stat.d.tes),
-%                                                           thompson.tes.d = cor(stat.thompson, stat.d.tes),
-%                                                           tes.d.begg = cor(stat.d.tes, stat.begg),
-%                                                           thompson.egger = cor(stat.thompson, stat.egger),
-%                                                           thompson.begg = cor(stat.thompson, stat.begg),
-%                                                           egger.begg = cor(stat.egger, stat.begg))
-% # rsquared.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = summary(lm(stat.egger~ stat.d.tes))$r.squared,
-% #                                                           thompson.tes.d = summary(lm(stat.thompson~ stat.d.tes))$r.squared,
-% #                                                           tes.d.begg = summary(lm(stat.d.tes~ stat.begg))$r.squared,
-% #                                                           thompson.egger = summary(lm(stat.thompson~ stat.egger))$r.squared,
-% #                                                           thompson.begg = summary(lm(stat.thompson~ stat.begg))$r.squared,
-% #                                                           egger.begg = summary(lm(stat.egger~ stat.begg))$r.squared)
-% meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
-%                                                 thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
-%                                                 egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
-%                                                 tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
-%                                                 thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
-%                                                 tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
-% agreement.sig.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
-%                                                              thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
-%                                                              tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
-%                                                              thompson.egger = sum(thompson.egger == "agree")/sum(egger.test),
-%                                                              thompson.begg = sum(thompson.begg == "agree")/sum(thompson.test),
-%                                                              egger.begg = sum(egger.begg == "agree")/sum(egger.test))
-% 
-% surv.tests.agreement <- rbind(agreement.surv, correlation.surv, rsquared.surv)
-% rownames(surv.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
-% colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)", 
-%                                     "Excess significance, Begg (survival)", "Thompson, Egger (survival)", 
-%                                     "Thompson, Begg (survival)", "Egger, Begg (survival)")
-% 
-% #--------------------------------------------------------------------------------------------------------------------#
-% 
-% #Merging:
-% test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
-% 
-% #--------------------------------------------------------------------------------------------------------------------#
-% 
-% 
-% 
-% 
-% The agreement/coinicidence between between small study effect and excess significance tests is often not pronounced, thus, it will be compared by different methods.
-The results of it are displayed in Table \ref{test.agreement}.
+\label{fig:test.corrected}
+\end{figure}
+
+The proportion of findings where we found amplification by adjustment was \Sexpr{round((1-sum(adjustment.diff.keep$bias.side)/dim(adjustment.diff.keep)[1])*100, 1)}\%.
+Most often, the proportion of tests with evidence for small study effects (and especially, excess significance), is lower, though.
+There are exceptions to this, such as Schwarzer's test results, where we have 143 - 60 = 83 significant test results, which corresponds to $\sim$ 40\%.
+Since excess significance is not necessarily connected with small study effects, we can furthermore reject the newly obtained, slightly smaller number of significant excess significance test results, and stick to the previous findings.
 \\
-% The row names indicate which two tests are compared.
-First, the column ``Test Agreement'' quantifies the overall proportion by which the two tests agree in their dichotomous classification of $p$-values with respect to the 0.1 threshold, i.e.
-rejection or ``acceptance'' of the null-hypothesis.
-A ``Test Agreement'' equal to one thus indicates equivalent results, zero no correspondence whatsoever.
-The second column, ``Correlation'' gives the correlation between the test statistics.
-A positive correlation indicates positive correlation of $p$-values, negative correlation correlation in opposite directions.
-Notably, for a high correlation, the scales must not be equal.
-The ``R-squared'' value indicates to what extent one test-statistic can be predicted by another, and ignores additive differences between $p$-values (as for correlation), as well as multiplicative constants between them (i.e.
-$y ~ a + b*x$, $y$ and $x$ being two test-statistics).
-An R-squared value of 1 indicates complete predictability.
+We can see how the agreement in significance is before, and after having removed negative publication bias significant results in Table \ref{test.agreement}.
+The proportion of agreement in significance is defined as the proportion of cases where, when the test with less significant findings is significant, also the other is significant.
 \\
-% %Importantly, the order of the variables does not matter for the test-statistics for all indicators (i.e.
-test-statistics for $x$ and $y$ can be exchanged and the table stays the same).
-If a test is completely replaceable by another, all values in a row are equal to one.
-\\
-% The analysis is again done separately for the outcome types.
-Overall, the test agreement is always above 0.62, and excluding survival outcomes, even above 0.79 (survival outcomes have only 39 test results, and thus more stochastic variation).
-Correlation ranges from near perfect (Thompson, Egger continuous, 0.91) to negative correlation (Excess significance, Thompson survival: -0.17).
-The R-squared values also indicate that some tests are similar, while others are not.
-% 
-% <<echo=FALSE, results='asis'>>=
-% print(xtable(test.agreement, align = "lccc", caption = "Agreement in significance proportion, correlation and R-squared of linear regression
-%              between the p-values of the publication bias tests. Horizontal lines separate binary, continuous and survival outcomes (order as in table).",
-%              label = "test.agreement"), hline = c(0,0,9, 15, 21), size = "footnotesize")
-@
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Chunck 1
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
+After the adjustment of the test results, the agreement for small study effects tests and excess significance tests increases a bit.
+This seems also to be the general trend, but not without exceptions.
+The two right-most columns indicate the agreement in significance, and we see that agreement is never larger than 0.3 (with Egger's test, continuous outcomes).
+Furthermore, only Egger and Thompson show a goof agreement for significance ($\sim$ 0.83).
+In contrast, some small study effect tests for binary outcomes seem rather to be exclusive, see for example the example of Schwarzer's test (6\% after adjustment) and R\"ucker's test (11\%): Only 19 \% of the cases where Schwarzer's Test is significant have also a significant finding using R\"ucker's test.
+Almost all binary small study effect tests have agreement in significance > 0.5.
+Thus, we see that large overall agreement is rather due to the large proportion of non-significant findings.
+
+<<echo = FALSE, warning= FALSE>>=
+#Agreement proportions of publication bias tests:
+
+#Binary:
+meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
+                                              tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
+                                              tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
+                                              tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
+                                              schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
+                                              schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
+                                              schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
+                                              rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
+                                              rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
+                                              harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
+agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
+                                                      tes.d.peter = sum(tes.d.peter == "agree")/n(),
+                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
+                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
+                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
+                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
+                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
+                                                      rucker.peter = sum(rucker.peter == "agree")/n(),
+                                                      harbord.peter = sum(harbord.peter == "agree")/n())
+meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test + schwarzer.test > 1, "agree", "disagree"),
+                                              tes.d.peter = ifelse(tes.d.test + peter.test > 1, "agree", "disagree"),
+                                              tes.d.rucker = ifelse(tes.d.test + rucker.test > 1, "agree", "disagree"),
+                                              tes.d.harbord = ifelse(tes.d.test + harbord.test > 1, "agree", "disagree"),
+                                              schwarzer.peter = ifelse(schwarzer.test + peter.test > 1, "agree", "disagree"),
+                                              schwarzer.rucker = ifelse(schwarzer.test + rucker.test > 1, "agree", "disagree"),
+                                              schwarzer.harbord = ifelse(schwarzer.test + harbord.test > 1, "agree", "disagree"),
+                                              rucker.peter = ifelse(rucker.test + peter.test > 1, "agree", "disagree"),
+                                              rucker.harbord = ifelse(rucker.test + harbord.test > 1, "agree", "disagree"),
+                                              harbord.peter = ifelse(harbord.test + peter.test > 1, "agree", "disagree"))
+agreement.sig.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/sum(schwarzer.test),
+                                                      tes.d.peter = sum(tes.d.peter == "agree")/sum(peter.test),
+                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/sum(rucker.test),
+                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/sum(harbord.test),
+                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/sum(schwarzer.test),
+                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/sum(schwarzer.test),
+                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/sum(schwarzer.test),
+                                                      rucker.peter = sum(rucker.peter == "agree")/sum(peter.test),
+                                                      harbord.peter = sum(harbord.peter == "agree")/sum(peter.test))
+
+binary.tests.agreement <- rbind(agreement.bin, agreement.sig.bin)
+rownames(binary.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
+colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
+                                      "Excess significance, Rucker", "Excess significance, Harbord",
+                                      "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
+                                      "Rucker, Peter", "Harbord, Peter")
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Continuous:
+meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
+                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
+                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
+                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
+                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
+                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
+agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
+                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
+                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
+                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
+                                                         egger.begg = sum(egger.begg == "agree")/n())
+meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
+                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
+                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
+                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
+                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
+                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
+agreement.sig.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
+                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
+                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
+                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
+                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
+                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))
+
+cont.tests.agreement <- rbind(agreement.cont, agreement.sig.cont)
+rownames(cont.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
+colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson",
+                                     "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Survival:
+meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
+                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
+                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
+                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
+                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
+                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
+agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
+                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
+                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
+                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
+                                                         egger.begg = sum(egger.begg == "agree")/n())
+meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
+                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
+                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
+                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
+                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
+                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
+agreement.sig.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
+                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
+                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
+                                                             thompson.egger = sum(thompson.egger == "agree")/sum(egger.test),
+                                                             thompson.begg = sum(thompson.begg == "agree")/sum(thompson.test),
+                                                             egger.begg = sum(egger.begg == "agree")/sum(egger.test))
+
+surv.tests.agreement <- rbind(agreement.surv, agreement.sig.surv)
+rownames(surv.tests.agreement) <- c("Agreement (overall)","Agreement (significance)")
+colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)",
+                                    "Excess significance, Begg (survival)", "Thompson, Egger (survival)",
+                                    "Thompson, Begg (survival)", "Egger, Begg (survival)")
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Merging:
+test.agreement.new <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
+
+test.agreement.together <- data.frame(test.agreement[,1], test.agreement.new[,1],
+                                      test.agreement[,2], test.agreement.new[,2])
+
+colnames(test.agreement.together) <- c("pre, overall", "post, overall", "pre, significance",
+                                      "post, significance")
+
+#--------------------------------------------------------------------------------------------------------------------#
+@
+
+<<echo=FALSE, results='asis'>>=
+print(xtable(test.agreement.together, align = "lcccc", caption = "Overall proportion of agreement if significant or unsignificant, and for significance only.
+Horizontal lines separate binary, continuous and survival outcomes (order as in table).
+The reference significance test is the one with more significant results.",
+             label = "test.agreement"), hline = c(0, 0, 9, 15, 21), size = "scriptsize")
+@

### 2019-07-01 report/chapter03.tex
correction of tes

@@
 
-\chapter{Results}
+\chapter{Results} \label{ch:Results}
 
-% 
-% \section{Meta-analysis}
-% The data at hand is composed of over 400,000 results with balanced sample size $n > 24$.
-The significance of the p-values of treatment effect estimates was calculated for all results in the dataset with acceptable sample size and outcome measures as odds ratios, peto odds ratios, risk ratios, risk differences and mean and standardized mean differences.
-% 
-% %Significance over time? Chunck 1
-% 
-% The results that can be pooled are analysed by fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis with Hartung-Knapp method.
-% 
-% \vspace{0mm}
-% In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e.
-if studies were not unique in the dataset with respect to their experimental setup).
-The significance of the treatment effect (primary significance) in a single result is then compared to the significance of the pooled treatment effect (secondary significance).
-% In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
-The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure.
-The colors indicate the overall fraction of rejected or accepted null-hypotheses of no treatment effect.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% #plot(sig.meta.c)
-% @
-% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
-% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-% \label{primary.secondary.significance}
-% \end{figure}
-% 
-% What has been found is that even the meta-analysis that for all meta-analysis methods, the amount of secondary significance is higher than the amount of primary significance.
-Thus more primarily non-significant results can be attached to a secondarily significant result than vice-versa.
-% 
-% \vspace{0mm}
-% To illustrate this, the fraction of studies with significant primary treatment effect and primary non-significant treatment effect can be plotted separately (Figure \ref{primary.secondary.significance.sep.sig}).
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% #grid.arrange(sig.meta.plot1, nonsig.meta.plot, ncol= 1)
-% @
-% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-% \label{primary.secondary.significance}
-% \end{figure}
-% 
-% It can be seen that the extent of overlap between primary and secondary significance varies between meta-analysis.
-A considerable amount of both primary significant and primary non-significant results are overruled by meta-analysis hypothesis tests.
-% 
-% 
-% The amount of significant heterogeneity in the results used by the meta-analyses is length(which(mly$sig.Q == 0)) and corresponds to (length(which(mly$sig.Q == 0))/ dim(mly)[1])*100\% of the total number of meta-analyses.
-% 
-% %Comparison of significance separated for significant Q? Chunck 2
-% 
-% %Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Small study effects}
+\section{Small Study Effect and Excess of Significance Tests} \label{sec:publication.bias.tests}
 
-To provide an overview over the abundance of small study effects in the dataset, first it is shown how median absolute effect size decreases with increasing sample size of the results (Figure \ref{effect.samplesize}).
-%In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.
+The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with small study effects tests and excess significance tests.
+We will apply the tests on the original effect size measures, i.e.
+risk ratios, Hedges $g$ or log hazard ratios.
+Different tests are applied depending on if the outcomes are of type binary or continuous or survival.\\
+Thus, we apply multiple tests on the same data.
+The results can then be displayed separately to compare the different tests.
+A histogram of $p$-values will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.
+\\
+``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}.
+For continuous and survival outcomes, the names refer to:
 
-\vspace{0mm}
-A clear trend of decrease of absolute effect size with increasing sample size (i.e. smaller variance) is visible. 
-%It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off.
-With increasing sample size, there are fewer results, therefore, the variation between medians increases.
-All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation.
-Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.
+\begin{itemize}
+\item Egger's test, the weighted linear regression test as described in section \ref{sec:Egger}
+\item Thompson and Sharp's test, the weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
+\item Begg and Mazumdar's test, the rank test described in section \ref{sec:Begg}
+\end{itemize}
+
+For binary outcomes, the names refer to:
+\begin{itemize}
+\item Harbord's test, the likelihood score based test (section \ref{sec:Harbord})
+\item Peter's test, the weighted linear regression with inverse sample size as explanatory variable (study size proxy) described in section \ref{sec:Peter}
+\item R\"ucker's test, the test based on the arcsine transformation of proportions, in combination with Thompson and Sharp's regression test (section \ref{sec:Rucker})
+\item Schwarzer's test, the rank based test using the expected event counts computed with the hypergeometric distribution (section \ref{sec:Schwarzer})
+\end{itemize}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-5-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-2-1}
 
@@
 \end{knitrout}
-\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
-\label{effect.samplesize}
+\caption{Histogram of the $p$-values for small study effect in meta-analyses.
+The testing method is indicated in the header, bin width is equal to 0.1.
+The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
+\label{fig:test}
 \end{figure}
 
-The median absolute normalized effect size can be visualized for the different outcome measures separately (Figure \ref{effect.samplesize.separated}).
-The plot confirms the trend of median effect size decrease towards lower sample size (e.g.
-for Risk Ratios: decrease $> 0.1$ standard deviations from 10 to 50 study participants).
-Instead of normalizing the effects
-%(i.e. subtracting mean and dividing through the standard deviation) 
-for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.
+%Agreement table -> Chunck 1
+The histograms in Figure \ref{fig:test} show that the distributions are (with the exception of Schwarzer's test) skewed to the right for all outcome types, indicating evidence for small study effects and excess significance, respectively.
+Moreover, the excess significance tests have a mode around $p = 0.4$.
+There is some discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger.
+Survival outcome type results are quite different with very few evidence for small study effects, but almost 50\% of meta-analysis with significant excess significance tests.
+Note that the sample size of survival outcomes is small ($n$ = 39).\\
+It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects/excess significance for the same meta-analyses.
+A simple method to check the coincidence of test results is to compare scatterplots and empirical Spearman correlations between the test statistics.
+This is done in Figure \ref{fig:test.agreement}.
+Here, there is no separation between survival and continuous outcomes.
+The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-6-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-3-1}
 
@@
 \end{knitrout}
-\caption{Median of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
-\label{effect.samplesize.separated}
+\caption{Pairs-plot for test statistics of small study effect and excess significance.
+The lower panel gives the Spearman correlations for the different test statistics, and the upper panel displays a scatterplot.
+The colors indicate magnitude and direction of the correlation coefficients.
+The rectangle with white borders displays the area within which both tests have absolute value < 1.64 (dots outside are statistically significant using the 0.1 threshold).}
+\label{fig:test.agreement}
 \end{figure}
 
-%Show absolute effect size depending on scaled time? Chunck 3
+The observed patterns on the scatterplots differ: Excess significance and small study effect test statistics do usually not align with each other, forming rather randomly scattered bulks of points.
+Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients.
+In general, small study effect tests align on the diagonal, but the extent to which they align differs.
+Continuous and survival outcome type tests align more closely than binary outcome tests.
+While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics .\\
+Because scatterplots and correlation coefficients can be misleading, also a Tukey mean-difference or Bland-Altman of transformed $p$-values plot is shown for four scenarios in Figure \ref{fig:mean.diff.test}:
+\begin{itemize}
+\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
+\item For Egger's and excess significance tests
+\item For Harbord's and R\"ucker's tests
+\item For Harbord's and excess significance tests
+\end{itemize}
 
-\subsection{Small Study Effect Tests}
+This can be justified since all tests are supposed to measure the evidence for publication bias.
+For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation $f(x)  = \log\frac{p}{1-p}$).
+The mean $p$-value (($f$($p$-value no.
+1) + $f$($p$-value no.
+2))/2) is then displayed against the difference between the $f$($p$-value).
+If no systematic errors and biases exist between the measurement methods, then
 
-There are tests that can be applied to find out if small study effects are present in the meta analysis.
-For the precise description, see the methods section.
-Application of the tests is only recommended if there are ten or more studies \citep{cochrane.handbook} that can be used, so all meta-analyses with less than ten studies have been excluded.
+\begin{itemize}
+\item the mean of the differences should be around zero (systematic error) 
+\item the points should scatter independently on the $y$-axis and no general increase or decrease with the mean of the transformed $p$-values should be visible
+\end{itemize}
 
-\vspace{0mm}
-There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
-In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = 1383)
-The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3955).
-The amount of studies varies from 5\% (Schwarzer's Test) to 13 \% (Egger's Test) for binary outcomes and 9\% (Begg and Mazumdar's Test) to 25 \% (Egger's Test) for continuous outcomes.
+Although this is not formally tested, the last criterium seems not to be given when comparing small study effect and excess significance tests.
+With decreasing mean, the difference gets more negative, and vice versa, such that one would predict that the excess significance $p$-values are more ``extreme'' in both directions.
+-- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- However, the systematic error between the compared tests is close to zero, and small study effect tests do probably not show bias when compared to each other.
+\\
+The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests.
+This suggests that correspondence between the tests is not very good in general.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-8-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-4-1}
 
@@
 \end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-\label{bias.results.cont}
+\caption{Mean - difference plots for logit transformed $p$-values.
+The mean of logit transformed $p$-values is displayed on the $x$-axis and the difference on the $y$-axis.
+Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).}
+\label{fig:mean.diff.test}
 \end{figure}
+
+The previous results suggest that the results will also differ substantially after applying the common dichotomization of $p$-values.
+We expect that some proportion of the meta-analysis will only be significant for a certain test, and this is indeed observed in Table \ref{number.sig.tests}.
+It displays the percentage of meta-analyses with a certain number of significant test results.
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Mon Jul  1 14:05:10 2019
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{ccc}
+  \hline
+Count & Binary Outcomes & Continuous and Survival \\ 
+  \hline
+0 & 65.1 \% & 70.4 \% \\ 
+  1 & 16.8 \% & 9 \% \\ 
+  2 & 8.8 \% & 7.5 \% \\ 
+  3 & 5.9 \% & 10.8 \% \\ 
+  4 & 3.1 \% & 2.3 \% \\ 
+  5 & 0.4 \% & - \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Counts Number of significant test results per meta-analysis, separated
+       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
+       applied} 
+\label{number.sig.tests}
+\end{table}
+
+Here, it is difficult to say if continuous and survival or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and survival outcome type tests have in general more positive findings.
+Very few meta-analyses are significant, irrespective of the test used, but around 67\% of the dataset is not significant, no matter which test is used.
+\\
+When only looking at small study effect tests, 29.1\% of binary outcome tests and 26.2\% of survival and continuous outcome tests had at least one significant result.
+This also suggests that the overlap between small study effect tests and excess significance is small.
+After applying the Bonferroni correction for multiple testing, this shrinks to 10.9\% for binary and 12.1\% for continuous and survival outcomes.
+\\
+To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test.
+23.5\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 25.4\% for continuous and survival outcomes.
+The numbers change to 14\% for binary outcomes and 14.4\% for continuous and survival outcomes after applying the Bonferroni correction.
+\\
+3.2\% have significant Harbord's test result and significant excess significance test result  (1.1\% with Bonferroni).
+Of the continuous outcomes, we have 5.7\% with Egger's test and 1.8\% with Bonferroni correction.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small Study Effects Adjustment}
+
+\subsection{Change in Effect Size after Adjustment} \label{sec:change.size}
+
+Since there's evidence for publication bias when applying small study effect and excess significance tests, we apply small study effect adjustment methods to correct for small study effect tests. \\
+We will see that consequences of adjustment can be; 
+\begin{itemize}
+\item first, the absolute size of the treatment effect can be smaller than the classical meta-analysis treatment effect, which is expected if publication bias
+is the cause for the small study effect.
+\item secondly, the effect can be larger than before in meta-analysis.
+In this case, the small study effect must be not due to publication bias for large effects (``true'' publication bias), but due to bias for small effects (``negative publication bias'').
+\end{itemize}
+
+In section \ref{sec:comparison.tests.adjustment}, it will be followed up on the latter point. For now, we will examine the extent and the frequencies of the two scenarios. \\
+To compare the effects of adjustment between meta-analyses, the outcome measures are transformed to Hedges $g$ (standardized mean differences) and Fisher's $z$-score (see section \ref{sec:transformation.effectsizes} for details).
+The effect of adjustment can additionally be compared to either random or fixed effects meta-analysis.
+\\
+Figure \ref{fig:adjustment.size} displays the difference $\delta$ between the observed meta-analysis pooled treatment effect and the adjusted treatment effect, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
+The absolute value $|\hat{\theta}_M|$ is taken and the sign of $\hat{\theta}_\textrm{Adj.}$ is adjusted accordingly such that all effects are mirrored to one side.
+$\delta > 0$ is equivalent to $\hat{\theta}_\textrm{Adj} < \hat{\theta}_M$, a reduction of the original effect size.
+For better illustration, some very large and very small differences have been omitted in the $z$-score and Hedges $g$ histograms; they are shown in Table \ref{missing.differences}.
+Table \ref{adjustment.difference} shows the quantiles and means for the various differences and additional information.\\
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-9-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-7-1}
 
@@
 \end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-\label{bias.results.bin}
+\caption{Histogram of the treatment effect differences between meta-analysis and adjusted meta-analysis.
+Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes.
+The bins are centered at zero.}
+\label{fig:adjustment.size}
 \end{figure}
 
-There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not.
-Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by 0.1825716 (the minimal increase is -0.0032246 for Schwarzer's Test).
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Mon Jul  1 14:05:13 2019
+\begin{table}[ht]
+\centering
+\begingroup\scriptsize
+\begin{tabular}{lcccccccccr}
+  \hline
+ & 5\% & 25\% & 50\% & 75\% & 95\% & mean & = 0 (\%) & $>$= 0 (\%) & $>$ 0 (\%) & No adj. est. (\%) \\ 
+  \hline
+z: Fixed - Copas & -0.05 & -0.01 & -0.00 & 0.01 & 0.05 & -271.73 & 4.76 & 48.67 & 43.91 & 71.54 \\ 
+  z: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.04 & -263.62 & 71.65 & 89.42 & 17.77 & 71.54 \\ 
+  z: Fixed - Regression & -0.13 & -0.03 & 0.01 & 0.05 & 0.14 & 0.01 & 0.00 & 52.44 & 52.44 & 0.17 \\ 
+  z: Random - Regression & -0.15 & -0.03 & 0.02 & 0.07 & 0.18 & 0.02 & 0.00 & 57.64 & 57.64 & 0.17 \\ 
+  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.09 & 0.02 & 22.76 & 59.14 & 36.38 & 60.96 \\ 
+  g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.14 & 0.03 & 63.29 & 87.49 & 24.20 & 60.96 \\ 
+  g: Fixed - Regression & -0.23 & -0.04 & 0.03 & 0.13 & 0.38 & 0.05 & 0.00 & 61.96 & 61.96 & 0.00 \\ 
+  g: Random - Regression & -0.24 & -0.03 & 0.05 & 0.16 & 0.42 & 0.06 & 0.00 & 64.06 & 64.06 & 0.00 \\ 
+  Log h.r.: Fixed - Copas & -0.03 & 0.00 & 0.00 & 0.00 & 0.02 & -0.01 & 41.03 & 38.46 & 79.49 & 61.54 \\ 
+  Log h.r.: Random - Copas & -0.03 & 0.00 & 0.00 & 0.00 & 0.00 & -0.01 & 66.67 & 15.38 & 82.05 & 61.54 \\ 
+  Log h.r.: Fixed - Regression & -0.21 & -0.14 & -0.07 & 0.01 & 0.15 & -0.06 & 0.00 & 33.33 & 33.33 & 0.00 \\ 
+  Log h.r.: Random - Regression & -0.22 & -0.15 & -0.07 & 0.03 & 0.15 & -0.06 & 0.00 & 33.33 & 33.33 & 0.00 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects.
+The column with the names ``> 0'' give the percentages of estimates larger than zero or larger or equal zero.
+The column ``No adj.
+est.'' gives the percentage of missing estimates due to non-significant publication bias test (for Copas) and computational errors.
+The row names indicate which outcome measure, meta-analysis method and adjustment method is used.
+Abbreviations are used for z-score (= z) and Hedges g (= g).}
+\label{adjustment.difference}
+\end{table}
 
-%Show plots of significant meta-analyses separated? Chunck 4
+Adjustment leads most often to reduction of treatment effect estimates, as can be seen by the size of the bins of the right part of the histograms in Figure \ref{fig:adjustment.sue}.
+The difference between the bins on the right and left side of the zero-centered bin is however not very large in general.
+The seeming exception of the Copas selection model in the case with $z$-scores and fixed effects reference requires closer examination: Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
+Thus, when comparing Copas with Fixed effects, we compare most often random effects with fixed effects estimates.
+The effect of adjustment by Copas can therefore only be seen when comparing random effects estimates with fixed effect estimates: we can see in Table \ref{adjustment.difference} that we have, for $z$-score, 18.4\% reduced effect sizes compared to 10.3\% (= 100\% - 89.69\%) increased effect sizes.
+Thus, the Copas selection model also has a larger proportion of reduced effect sizes compared to amplified.\\
+%This resolves the case for the seeming exception and for Hedges $g$'s, 24.4\% and 12.46\% (Table \ref{adjustment.difference}. 
+Also, there are more reduced effect sizes if random effects meta-analysis is used as a reference effect size.
+When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
+\\
+The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 90 cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or 90 increased by -0.13, fixed effects reference).
+Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or 90 meta-analyses (or increased by 0.24).
 
-Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses).
-The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}.
-The Figure suggests that the frequency of publication bias remains constant over time.
-The mean publication years have been restricted such that at least 180 meta-analyses are available per year, such that random fluctuation is restricted to some extent.
-The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).
+\subsection{Change in Evidence for Treatment Effects} \label{sec:change.evidence}
+Adjustment for small study effects in meta-analysis will not only provide new effect sizes, but also standard errors thereof.
+Thus, also the evidence for efficacy of a treatment can be obtained, which is usually summarized in a suitable test statistic or $p$-value.
+It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.\\
+The Wald test statistics $p$-value for fixed and random effects meta-analyses and Copas and regression adjusted treatment effects have been calculated.
+They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and log hazard ratios.
+\\
+It can be seen that evidence for a treatment effect decreases after adjusting for publication bias.
+It does so more for Hedge's $g$ compared to $z$-scores, and for regression adjustment compared to Copas selection model.
+%Also, the evidence decreases for random effects meta-analyses compared to fixed effects meta-analyses. 
+In the case of log-hazard ratio adjustment, the adjustment has only negligible impact on the $p$-values. \\
+Also, Copas selection method has a very small impact on the evidence compared to random effects meta-analysis, at least using $z$-scores (again, we should rely on comparisons to random effects meta-analysis to evaluate Copas method).
+\\
+% Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
+%Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted Hedges $g$ and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-10-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-9-1}
 
@@
 \end{knitrout}
-\caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
-\label{pub.bias.overtime}
+\caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
+The method is indicated in the header, bin width is set to 0.05.
+The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
+\label{fig:adjustment.stat}
 \end{figure}
 
-The agreement of the tests, i.e.
-the proportion of meta-analyses where the rest results are equal between tests, is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
-Agreement in tests for binary outcomes is better than continuous outcomes, with some variation between tests (binary outcomes: 83 to 91\%).
-Correlation varies more between tests, both for continuous and binary outcome tests.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue May 21 16:11:40 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
- & Test Agreement & P-value Correlation \\ 
-  \hline
-egger.schwarzer & 0.73 & 0.23 \\ 
-  egger.peter & 0.75 & 0.37 \\ 
-  egger.rucker & 0.75 & 0.34 \\ 
-  egger.harbord & 0.79 & 0.51 \\ 
-  schwarzer.peter & 0.81 & 0.26 \\ 
-  schwarzer.rucker & 0.81 & 0.25 \\ 
-  schwarzer.harbord & 0.86 & 0.47 \\ 
-  rucker.peter & 0.87 & 0.64 \\ 
-  harbord.peter & 0.84 & 0.50 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)} 
-\label{agreement.bin}
-\end{table}
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue May 21 16:11:40 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lll}
-  \hline
- & Test Agreement & P-value Correlation \\ 
-  \hline
-thomson.egger & 0.85 & 0.69 \\ 
-  thomson.begg & 0.77 & 0.47 \\ 
-  egger.begg & 0.73 & 0.36 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)} 
-\label{agreement.cont}
-\end{table}
-
-\vspace{0mm}
-Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
-The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}.
-%(Suggests that 10 is likely too small)
-In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
-A trend towards more rejections for larger sample sizes can be seen.
+The Copas selection model also gives an estimate of the number of missing studies.
+It finds that 0 are missing, which corresponds to 0\% from all \ensuremath{2.8945\times 10^{4}} analysed studies.
+Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
+Note that we have excluded 0 out of 1806, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-10-1}
 
@@
 \end{knitrout}
-\caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
-\label{pvalues.samplesize}
+\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ 0)}
+\label{fig:copas.missing}
 \end{figure}
 
-\vspace{0mm}
-One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
-The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.18.
-% A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
-In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses.
-In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
-In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.
+We can see that in some occasions, the method finds more than half of all studies are missing.
+In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
+The discrepancy between mean and median may indicate that the estimate of 0\% missing studies depends somewhat on these extreme cases.
+As can be written of from Table \ref{copas.missing}, 5\%, \ie 0 meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for 0, more than 30\% of missing studies.
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Mon Jul  1 14:05:15 2019
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lrrrrrrr}
+  \hline
+ & = 0 & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
+  \hline
+Missing fraction & 321 & 0 & 0 & 0.1 & 0.3 & 0.9 & 0.2 \\ 
+  Missing study number & 321 & 0 & 0 & 1.4 & 5.2 & 17.6 & 4.1 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.} 
+\label{copas.missing}
+\end{table}
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Mon Jul  1 14:05:15 2019
+\begin{table}[ht]
+\centering
+\begingroup\tiny
+\begin{tabular}{lcccrrrrrrrr}
+  \hline
+meta.id & file.nr & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
+  \hline
+2009 & 2009 & 1 & 1 & 0.31 & 0.36 & 0.31 & 0.43 & 0.70 & 0.70 & 0.70 & 2.48 \\ 
+  2068 & 2068 & 2 & 0 & 0.29 & 0.35 & 0.29 & 0.42 & 0.68 & 0.68 & 0.68 & 2.57 \\ 
+  52528 & 52528 & 1 & 0 & -0.75 & -0.69 & -0.50 & -0.26 & -1.19 & -1.53 & 0.18 & -0.52 \\ 
+  60546 & 60546 & 1 & 1 & 0.17 & 0.24 & 0.17 & 0.34 & 0.53 & 0.53 & 0.53 & 1.65 \\ 
+  70389 & 70389 & 1 & 1 & -0.08 & -0.07 & 15.62 & -0.04 & -0.13 & -0.13 & -0.13 & -0.05 \\ 
+  73769 & 73769 & 3 & 1 & -0.09 & 0.00 & 7148.96 & 0.02 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
+  79113 & 79113 & 2 & 0 & -0.38 & -0.38 & -0.38 & -0.48 & -0.93 & -0.93 & -2.00 & -3.47 \\ 
+  90138 & 90138 & 3 & 0 & 0.30 & 0.80 & 0.30 & 0.53 & 0.72 & 0.71 & 0.71 & 2.16 \\ 
+  97356 & 97356 & 2 & 0 & -0.06 & -0.33 & -0.06 & -0.11 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
+  98030 & 98030 & 1 & 0 & -0.09 & -0.07 & -0.09 & -0.04 & -0.41 & -0.41 & -1.50 & -2.79 \\ 
+  101436 & 101436 & 1 & 5 & 0.54 & 0.62 & 0.80 & 0.90 & 1.21 & 1.21 & 1.21 & 2.74 \\ 
+  118121 & 118121 & 4 & 1 & 0.25 & 0.23 & 47.73 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
+  119537 & 119537 & 3 & 0 & 0.07 & 0.15 & 0.07 & 0.29 & 0.50 & 0.50 & 1.43 & 1.81 \\ 
+  119818 & 119818 & 3 & 3 & -0.25 & -0.25 & -0.20 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
+  146301 & 146301 & 1 & 0 & 0.14 & 0.26 & 472149.03 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects. Abbreviations are used for z-score (= z) and Hedges g (= g).} 
+\label{missing.differences}
+\end{table}
+
+\subsection{Comparison of adjustment methods}
+Regression adjusted estimates are compared to the estimates of Copas selection model if these are not equal to random effects meta-analysis.
+A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
+We will compare estimates based on all three outcome measures, i.e.
+original measure, $z$-score and Hedges $g$ in Figure \ref{fig:adjustment.mean.diff}.
+Note that the 39 survival outcome data is not included when using $z$-score and Hedges $g$.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-14-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-13-1}
 
@@
 \end{knitrout}
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
-\label{trimfill.pvalues.bin}
+\caption{Mean - difference plots for publication bias adjustment methods.
+The mean of the adjusted treatment effects is displayed on the $x$-axis and the difference on the $y$-axis.
+Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).
+Two values have been omitted in the middle plot for Hedges $g$ and one for $z$-score (see Table \ref{missing.differences}).}
+\label{fig:adjustment.mean.diff}
 \end{figure}
+
+No formal tests are provided, but the at least there seems to be no clear bias or systematic.
+The limits of agreement in Figure \ref{fig:adjustment.mean.diff} are large.
+We conclude thus that the impact of regression adjustment on the effect sizes is in general not substantially larger than the impact of Copas selection model in the subset of data where the estimate of the Copas selection model is not equal to a random effects estimate.
+\\
+
+\section{Comparison of Tests and Adjustments} \label{sec:comparison.tests.adjustment}
+
+In section \ref{sec:change.size}, we have seen that some adjustments for small study effects are not in line with our previous definition of publication bias: Some times, the adjustment for small study effects leads to a larger treatment effect.
+We want to take this into account when considering evidence for publication bias.
+Whenever adjustment leads to larger effect sizes, the small study effect test result from section \ref{sec:publication.bias.tests} is revised and changed to negative.
+We will revisit the results from section \ref{sec:publication.bias.tests} and first visualize which proportion of the data finds rather ``negative publication bias'' than the predefined type of publication bias.
+Figure \ref{fig:test.corrected} is equal to Figure \ref{fig:test} with sole difference that now the proportion of ``negative publication bias'' is colored, and the count of significant findings is corrected (not significant for negative publication bias).
+\\
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-15-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-15-1}
 
@@
 \end{knitrout}
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
-\label{trimfill.pvalues.cont}
+\caption{Histogram of the $p$-values for small study effect in meta-analyses.
+The testing method is indicated in the header, bin width is equal to 0.1.
+The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
+\label{fig:test.corrected}
 \end{figure}
 
-\subsection{Small Study Effect Correction}
-Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
-Three of them will be applied to the meta-analyses shown previously that have ten or more study results and are therefore eligible for testing for publication bias.
+The proportion of findings where we found amplification by adjustment was 33.9\%.
+Most often, the proportion of tests with evidence for small study effects (and especially, excess significance), is lower, though.
+There are exceptions to this, such as Schwarzer's test results, where we have 143 - 60 = 83 significant test results, which corresponds to $\sim$ 40\%.
+Since excess significance is not necessarily connected with small study effects, we can furthermore reject the newly obtained, slightly smaller number of significant excess significance test results, and stick to the previous findings.
+\\
+We can see how the agreement in significance is before, and after having removed negative publication bias significant results in Table \ref{test.agreement}.
+The proportion of agreement in significance is defined as the proportion of cases where, when the test with less significant findings is significant, also the other is significant.
+\\
+After the adjustment of the test results, the agreement for small study effects tests and excess significance tests increases a bit.
+This seems also to be the general trend, but not without exceptions.
+The two right-most columns indicate the agreement in significance, and we see that agreement is never larger than 0.3 (with Egger's test, continuous outcomes).
+Furthermore, only Egger and Thompson show a goof agreement for significance ($\sim$ 0.83).
+In contrast, some small study effect tests for binary outcomes seem rather to be exclusive, see for example the example of Schwarzer's test (6\% after adjustment) and R\"ucker's test (11\%): Only 19 \% of the cases where Schwarzer's Test is significant have also a significant finding using R\"ucker's test.
+Almost all binary small study effect tests have agreement in significance > 0.5.
+Thus, we see that large overall agreement is rather due to the large proportion of non-significant findings.
 
-\vspace{0mm}
-The extent to what the results of the meta-analysis results are changed can be investigated.
-Because statistical significance is often used to decide if there is a treatment effect, a non-significant corrected effect size estimate can indicate that an observed treatment effect has been accepted because of small study effects.
-Therefore, the cases have been counted in which
-\begin{enumerate}
-\item Significance or non-significance of pooled estimate of meta-analysis did not change after correction for small study effects.
-\item Significance of pooled estimate of meta-analysis did change to non-significance after correction for small study effects.
-\item Non-significance of pooled estimate of meta-analysis did change to significance after correction for small study effects.
-\end{enumerate}
-
-The results of this can be seen in Figure \ref{significance.change.fixed} for all three methods, comparing the significance of the corrected pooled effect size estimate with the significance of the pooled effect size estimate of the fixed effects meta-analysis.
-The same for significance of random effects meta-analysis is shown in Figure \ref{significance.change.random}.
-The significance threshold was chosen such that the $p$-value had to be < 0.05 for rejection of the null hypothesis of no treatment effect.
-The correction methods were trim-and-fill, copas selection model and regression with random effects and shrinkage of within-study-variance methods.
-More details to the applied correction methods and their application are in the methods section \ref{methods}.
-Notably, the correction methods has been applied to all meta-analyses, thus also for such that had no significant small study effect test result.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-16-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction.}
-\label{significance.change.fixed}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction.}
-\label{significance.change.random}
-\end{figure}
-
-Since it has been previously seen in Figure \ref{test.results} that the results of small study effects vary considerably between continuous outcomes, the results in significance change from fixed effects meta-analysis can be seen separately in Figure \ref{significance.change.fixed.sep} for continuous and binary outcomes.
-The change in significance from random effects meta-analysis to significance of corrected estimate can be seen in Figure \ref{significance.change.fixed.sep}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.fixed.sep}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.random}
-\end{figure}
-
-Because the real amount of publication bias in the dataset is not known, the correction method can also be applied only to meta-analyses that have publication bias according to the small study effect tests in the previous section.
-Because the test developed by \citet{thomson.sharp} has been applied to both binary and continuous outcome meta-analyses (in the case of binary outcomes to arcsine variance stabilized proportions), it is used as a criterium to distinguish biased from unbiased meta-analyses.
-The proportions of significance tests of pooled treatment effects that turned from significant to non-significant, non-significant to significant etc.
-are shown in Figure \ref{significance.change.fixed.sep}.
-Fixed effects meta-analysis has been used to determine signficance of the uncorrected estimate.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.random}
-\end{figure}
-
-Similarly, the number of missing studies per meta-analysis, i.e.
-those which have not been included because of small study effects, are estimated by the copas and trim-and-fill method and their empirical distribution is shown in histograms in Figure \ref{missing.studies.distribution}.
-For visualisation, the fraction of unpublished studies from the total fraction of available studies is shown.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
-
-}
-
-\end{knitrout}
-\caption{Fraction of missing studies estimated of the number of total studies included in the meta-analysis for copas selection and trim-and-fill method.}
-\label{missing.studies.distribution}
-\end{figure}
-
-% # <<results = 'asis', Echo = FALSE>>=
-% # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
-% #                                             schwarzer.rejection = mean(schwarzer.test),
-% #                                             rucker.rejection = mean(rucker.test),
-% #                                             harbord.rejection = mean(harbord.test),
-% #                                             peter.rejection = mean(peter.test))
-% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
-% # @
-
-% 
-% For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
-The following three figures show the distribution of p-values of the corresponding tests.
-Note that only meta analyses with more than 10 comparisons have been included.
-% 
-% \vspace{0mm}
-% Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
-The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "linreg")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
-% \label{egger.cont}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "mm")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
-% \label{thomson.cont}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "rank")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{begg.cont}
-% \end{figure}
-% 
-% 
-% For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-%   filter(events1 > 0 | events2 > 0) %>% 
-%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{peters.bin}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-%   filter(events1 > 0 | events2 > 0) %>% 
-%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{harbord.bin}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Since most of the times the study publication year is available for a given result, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.
-The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
-% @
-% \caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
-% \label{study.significance.overtime}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 2
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
-Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
-The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested.
-This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(sig.meta.Q1, nonsig.meta.Q, ncol= 1)
-% @
-% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-% \label{primary.secondary.significance.sep.sig}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 3
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
-This can again be done for the entire dataset, i.e.
-for all effect estimates and their ordering in time.
-It is important to scale the effect estimates here with respect to the estimates of the replication studies that are about the same subject, have the same outcome measure, etc.
-Also, only effect estimates that can be compared to other estimates before are included, i.e.
-only study results with one or more replica are included.
-Time needs to be scaled and normalized in order to compare multiple time-trends in effect size to each other and gain insights in the overall trend.
-This is done in Figure \ref{effects.overtime.separated}, separared for odds rati, risk ratio, and mean and standardized difference outcome measures.
-In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
-%                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
-%   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
-%   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
-%   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
-%   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
-%   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
-% @
-% \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
-% \label{effects.overtime.separated}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 4
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
-This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p3, p4, ncol = 2)
-% @
-% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-% \label{bias.results.cont.sep}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p1, p2, ncol = 2)
-% @
-% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-% \label{bias.results.bin.sep}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% #Proportion of significant pooled estimates based on proportion of single pooled estimates
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type)) + geom_histogram()
-% 
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
-%   geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% 
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
-%   geom_histogram(position = "fill")
-% 
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef))) + 
-%   geom_histogram()
-
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.secondary.over.meansig)
-% @
-% \caption{Fraction of significant meta-analysis, dependent on the fraction of significant single results.}
-% \label{secondary.significance.over.meansig}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Mon Jul  1 14:05:18 2019
+\begin{table}[ht]
+\centering
+\begingroup\scriptsize
+\begin{tabular}{lcccc}
+  & pre, overall & post, overall & pre, significance & post, significance \\ 
+  \hline
+\hline
+Excess significance, Schwarzer & 0.81 & 0.85 & 0.12 & 0.22 \\ 
+  Excess significance, Peter & 0.79 & 0.83 & 0.25 & 0.24 \\ 
+  Excess significance, Rucker & 0.82 & 0.84 & 0.30 & 0.29 \\ 
+  Excess significance, Harbord & 0.80 & 0.85 & 0.28 & 0.29 \\ 
+  Peter, Schwarzer & 0.82 & 0.88 & 0.38 & 0.39 \\ 
+  Schwarzer, Rucker & 0.82 & 0.87 & 0.32 & 0.35 \\ 
+  Schwarzer, Harbord & 0.86 & 0.91 & 0.58 & 0.54 \\ 
+  Rucker, Peter & 0.89 & 0.92 & 0.64 & 0.62 \\ 
+  Harbord, Peter & 0.86 & 0.90 & 0.53 & 0.48 \\ 
+   \hline
+Excess significance, Egger & 0.80 & 0.83 & 0.67 & 0.64 \\ 
+  Excess significance, Thompson & 0.81 & 0.83 & 0.55 & 0.52 \\ 
+  Excess significance, Begg & 0.80 & 0.83 & 0.33 & 0.33 \\ 
+  Thompson, Egger & 0.95 & 0.96 & 0.96 & 0.95 \\ 
+  Thompson, Begg & 0.87 & 0.89 & 0.69 & 0.73 \\ 
+  Egger, Begg & 0.86 & 0.87 & 0.78 & 0.77 \\ 
+   \hline
+Excess significance, Egger (survival) & 0.82 & 0.92 & 0.00 & 0.00 \\ 
+  Excess significance, Thompson (survival) & 0.87 & 0.92 & 0.00 & 0.00 \\ 
+  Excess significance, Begg (survival) & 0.90 & 0.95 & 0.00 & 0.00 \\ 
+  Thompson, Egger (survival) & 0.90 & 0.95 & 0.67 & 0.00 \\ 
+  Thompson, Begg (survival) & 0.92 & 0.97 & 0.50 & 0.00 \\ 
+  Egger, Begg (survival) & 0.87 & 0.97 & 0.50 & 0.00 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Overall proportion of agreement if significant or unsignificant, and for significance only.
+Horizontal lines separate binary, continuous and survival outcomes (order as in table).
+The reference significance test is the one with more significant results.}
+\label{test.agreement}
+\end{table}

### 2019-07-01 code/new_meta_analysis.R

@@ -632,26 +632,26 @@ tmp.z <- data.ext2 %>% group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 9) %
   filter(outcome.type != "rate" & !is.na(outcome.type)) %>% filter(total1 + total2 > 3)
 
 meta.id.vector <- metac$meta.id
-# 
-# excess.significance.z <- list()
-# excess.significance.d <- list()
-# 
-# counter <- 0
-# for(u in meta.id.vector){
-#   counter <- counter + 1
-#   print(c(u,counter))
-#   excess.significance.z[[counter]] <- tes.z(tmp.z[tmp.z$meta.id == u,])
-# 
-#   excess.significance.d[[counter]] <- tes.d(tmp[tmp$meta.id == u,])
-# 
-#   print(c(u, (tes.d(tmp[tmp$meta.id == u,])[4])))
-#   if(is.na(tes.d(tmp[tmp$meta.id == u,])[4])) break
-# }
-# 
-# excess.sig.list <- list(meta.id.vector, tmp.z, tmp, excess.significance.z, excess.significance.d)
 
-excess.significance.z <- excess.sig.list[[4]]
-excess.significance.d <- excess.sig.list[[5]]
+excess.significance.z <- list()
+excess.significance.d <- list()
+
+counter <- 0
+for(u in meta.id.vector){
+  counter <- counter + 1
+  print(c(u,counter))
+  excess.significance.z[[counter]] <- tes.z(tmp.z[tmp.z$meta.id == u,])
+
+  excess.significance.d[[counter]] <- tes.d(tmp[tmp$meta.id == u,])
+
+  print(c(u, (tes.d(tmp[tmp$meta.id == u,])[4])))
+  if(is.na(tes.d(tmp[tmp$meta.id == u,])[4])) break
+}
+
+excess.sig.list <- list(meta.id.vector, tmp.z, tmp, excess.significance.z, excess.significance.d)
+
+# excess.significance.z <- excess.sig.list[[4]]
+# excess.significance.d <- excess.sig.list[[5]]
 
 #List extraction:
 excess.significance.results <- cbind(
@@ -676,6 +676,22 @@ meta.f <- merge(meta.f, excess.significance.results, by = c("meta.id"), all.x = 
 #Round-up:
 ##########################################################################################
[…]

### 2019-07-01 code/tes.R

@@ -64,10 +64,28 @@ tes <- function(data){
   pval.chi <- pchisq(A, 1, lower.tail = FALSE) # Compute p-value
   pval.chi <- ifelse(pval.chi < 0.5, pval.chi*2, (1-pval.chi)*2)
   
-  est.p <- O/n
-  A.wald <- ((est.p) - (E/n)) / sqrt((est.p)*(1-est.p)/n)
-  pval.bin <- 1 - pnorm(A.wald)
+  pval.bin <- 1 - pbinom(q = O, n = n, prob = E/n)
   
   return(c(A = A, A.wald = A.wald, pval.chi = pval.chi, pval.bin = pval.bin, O = O, E = E, n = n))
   
 }
+
+O <- 3
+E <- 1.06 # Expected number of statistically significant result  
+n <- 20 # Number of studies in meta-analysis
+A <- (O - E)^2/E + (O - E)^2/(n - E) # Compute chi-square statistic
+pval.chi <- pchisq(A, 1, lower.tail = FALSE) # Compute p-value
+pval.chi <- ifelse(pval.chi < 0.5, pval.chi*2, (1-pval.chi)*2)
+
+est.p <- O/n
+
+# pval.chi <- (1- pchisq(A, 1) )
+pval.bin <- pbinom(q = O-1, size = n, prob = E/n, lower.tail = F)
+
+c(A = A, A.wald = A.wald, pval.chi = pval.chi, pval.bin = pval.bin, O = O, E = E, n = n)
+
+
+
+
+
+

### 2019-07-01 code_excess/report_trash.R

@@ -1,0 +1,1118 @@
+
+
+
+
+
+
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% \section{Small study effects}
+% <<echo=FALSE, warning=FALSE>>=
+  % p.samplesize.z  <- data.ext2 %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% ungroup() %>% 
+%   mutate(std.z = abs(z), sample.size = total1 + total2) %>%
+%   group_by(sample.size) %>% 
+%   summarize(median.effect = median(std.z, na.rm = T)) %>% 
+%   ggplot(aes(x = sample.size, y = median.effect)) + geom_point(size = 0.8) + 
+  %   theme_bw() + xlab("sample size") + ylab("median absolute z-score") +
+  %   xlim(c(15, 300)) + ylim(c(0, 0.25)) +
+  %   scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
+% 
+% p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% 
+%   filter(outcome.measure.new == "Risk Ratio" | 
+             %            outcome.measure.new == "Odds Ratio" | 
+             %            outcome.measure.new == "Mean Difference" |
+             %            outcome.measure.new == "Std. Mean Difference") %>% 
+           %   group_by(outcome.measure.new) %>% 
[…]

### 2019-07-02 report/MSc_Report.tex
onesided

@@
 
-The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with small study effects tests and excess significance tests.
-We will apply the tests on the original effect size measures, i.e.
+The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with one-sided small study effects tests and excess significance tests.
+The direction in which bias is expected is the one on which more significant results are ($p$-value < 0.05, two-sided).
+The tests are applied on the original effect size measures, i.e.
 risk ratios, Hedges $g$ or log hazard ratios.
-Different tests are applied depending on if the outcomes are of type binary or continuous or survival.\\
-Thus, we apply multiple tests on the same data.
-The results can then be displayed separately to compare the different tests.
+Different tests are applied depending on the outcome type being binary or continuous and survival.\\
+Thus, multiple tests are applied on the same data.
+The results can then be displayed separately to compare the results from the different tests.
 A histogram of $p$-values will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.
@@
 \end{knitrout}
-\caption{Histogram of the $p$-values for small study effect in meta-analyses.
+\caption{Histogram of one-sided $p$-values for small study effect in direction of larger effect sizes.
 The testing method is indicated in the header, bin width is equal to 0.1.
@@
 %Agreement table -> Chunck 1
-The histograms in Figure \ref{fig:test} show that the distributions are (with the exception of Schwarzer's test) skewed to the right for all outcome types, indicating evidence for small study effects and excess significance, respectively.
-Moreover, the excess significance tests have a mode around $p = 0.4$.
-There is some discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger.
-Survival outcome type results are quite different with very few evidence for small study effects and excess significance.
-Note that the sample size of survival outcomes is small ($n$ = 39).\\
-It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects/excess significance for the same meta-analyses.
+The histograms in Figure \ref{fig:test} show that most distributions are clearly skewed to the right, indicating evidence for small study effects.
+Exceptions from this are the excess significance and Schwarzer's test, and the tests for survival outcomes.
+There, there is no evidence for publication bias, and the histograms are even skewed to the left (Schwarzer).
+But note that the sample size of survival outcomes is small ($n$ = 39).
+\\
+There is discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger.
+Also, we see that the $I^2$ statistic of the proportion of overall between-study heterogeneity is distributed differently for the tests, with results with $I^2 = 0$ being evenly distributed in binary outcomes along the range of $p$-values, while they are more similar to the meta-analyses with larger heterogeneity for continuous outcome.\\
+In the literature, the excess significance test is advised to be used in the case of no between study heterogeneity.
+Since there are no small $p$-values for such meta-analyses, one must conclude that there is no excess significance in the dataset.
+The obvious correspondence with the heterogeneity statistic however rather suggests that the test itself is just another was to assess between study heterogeneity.
+Thompson test and R\"ucker's test are designed such that they take into account the between study heterogeneity when assessing small study effects.
+When no heterogeneity is given, Thompsons test results and Eggers test result should be equal, however, the $I^2$ statistic is computed by a more suitable estimator \citep{paulemandel} of $\tau^2$ as the estimator that Thompson and Sharp's test uses (method of moment estimator of \citet{tau.estimator}, which is more conservative by usually finding larger $\tau^2$).
+In the part of the histogram with $I^2 > 0$, the two tests are more reliable than the remaining tests, while the opposite is expected from simulations \citep{limitmeta} when $I^2 = 0$.\\
+
+It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects for the same meta-analyses.
 A simple method to check the coincidence of test results is to compare scatterplots and empirical Spearman correlations between the test statistics.
@@
 The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results.
+Also, the $I^2$ statistic is included.
+Since no test statistic is used for excess significance tests, it is not shown here
 
@@
 The colors indicate magnitude and direction of the correlation coefficients.
-The rectangle with white borders displays the area within which both tests have absolute value < 1.64 (dots outside are statistically significant using the 0.1 threshold).}
+The rectangle with white borders displays the area within which both tests have absolute value < 1.64 (dots outside are statistically significant by 0.1 $p$-value threshold).}
 \label{fig:test.agreement}
@@
 
-The observed patterns on the scatterplots differ: Excess significance and small study effect test statistics do usually not align with each other, forming rather randomly scattered bulks of points.
-Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients.
-In general, small study effect tests align on the diagonal, but the extent to which they align differs.
+The observed patterns on the scatterplots differ, and some small study effect test statistics do align better than others.
+Regression based tests as Egger and Thompsons test which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients.
 Continuous and survival outcome type tests align more closely than binary outcome tests.
@@
 
-Although this is not formally tested, the last criterium seems not to be given when comparing small study effect and excess significance tests.
-With decreasing mean, the difference gets more negative, and vice versa, such that one would predict that the excess significance $p$-values are more ``extreme'' in both directions.
--- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- However, the systematic error between the compared tests is close to zero, and small study effect tests do probably not show bias when compared to each other.
-\\
+Although this is not formally tested, there are likely systematic errors and bias between excess significance tests, although more so for continuous tests.
+-- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- \\
 The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jul  1 17:11:00 2019
+% Tue Jul  2 18:53:37 2019
 \begin{table}[ht]
@@
   \hline
-0 & 66.1 \% & 72.5 \% \\ 
-  1 & 16.1 \% & 7.5 \% \\ 
-  2 & 8.8 \% & 8 \% \\ 
-  3 & 5.7 \% & 10.5 \% \\ 
-  4 & 3 \% & 1.5 \% \\ 
-  5 & 0.4 \% & - \\ 
+0 & 68 \% & 64.3 \% \\ 
+  1 & 13.5 \% & 10 \% \\ 
+  2 & 7.5 \% & 6.9 \% \\ 
+  3 & 5.2 \% & 16.5 \% \\ 
+  4 & 4.9 \% & 2.3 \% \\ 
+  5 & 0.8 \% & - \\ 
    \hline
@@
 \\
-When only looking at small study effect tests, 29.1\% of binary outcome tests and 26.2\% of survival and continuous outcome tests had at least one significant result.
-This also suggests that the overlap between small study effect tests and excess significance is small.
-After applying the Bonferroni correction for multiple testing, this shrinks to 10.9\% for binary and 12.1\% for continuous and survival outcomes.
-\\
-To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test.
-22.4\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 23.4\% for continuous and survival outcomes.
-The numbers change to 13.4\% for binary outcomes and 13.4\% for continuous and survival outcomes after applying the Bonferroni correction.
-\\
-2.7\% have significant Harbord's test result and significant excess significance test result  (1.1\% with Bonferroni).
-Of the continuous outcomes, we have 3.3\% with Egger's test and 0.8\% with Bonferroni correction.
+When only looking at small study effect tests, 27.3\% of binary outcome tests and 34.4\% of survival and continuous outcome tests had at least one significant result.
+After applying the Bonferroni correction for multiple testing, this shrinks to 10.5\% for binary and 17.5\% for continuous and survival outcomes.
+\\
+% To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test.
+mean.min.bin2\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, mean.min.else2\% for continuous and survival outcomes.
+The numbers change to mean.min.bin2.b\% for binary outcomes and mean.min.else2.b\% for continuous and survival outcomes after applying the Bonferroni correction.
+\\
+% both.bin\% have significant Harbord's test result and significant excess significance test result  (both.bin.b\% with Bonferroni).
+Of the continuous outcomes, we have both.else\% with Egger's test and both.else.b\% with Bonferroni correction.
 
@@
 
-Since there's evidence for publication bias when applying small study effect and excess significance tests, we apply small study effect adjustment methods to correct for small study effect tests. \\
-We will see that consequences of adjustment can be; 
+Since there's evidence for publication bias when applying small study effect and excess significance tests, we apply small study effect adjustment methods to take into account that small studies are likely overestimating the treatment effect.
+\\
+However, we will see that consequences of adjustment can be; 
 \begin{itemize}
@@
 \item secondly, the effect can be larger than before in meta-analysis.
-In this case, the small study effect must be not due to publication bias for large effects (``true'' publication bias), but due to bias for small effects (``negative publication bias'').
+In this case, the small study effect must be not due to publication bias for large effects (``true'' publication bias), but due to bias for small effects (``null effect publication bias'' or even ``reversed effect publication bias'', sometimes refer erred to as ``Proteus phenomenon'' \citep{proteus}).
 \end{itemize}
 
-In section \ref{sec:comparison.tests.adjustment}, it will be followed up on the latter point. For now, we will examine the extent and the frequencies of the two scenarios. \\
+This is because, in contrast to the small study effect tests, the applied adjustment method does not pre-specify the direction in which bias is expected. \\
 To compare the effects of adjustment between meta-analyses, the outcome measures are transformed to Hedges $g$ (standardized mean differences) and Fisher's $z$-score (see section \ref{sec:transformation.effectsizes} for details).
-The effect of adjustment can additionally be compared to either random or fixed effects meta-analysis.
-\\
-Figure \ref{fig:adjustment.size} displays the difference $\delta$ between the observed meta-analysis pooled treatment effect and the adjusted treatment effect, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
+The effect of adjustments can be compared to either random or fixed effects meta-analysis estimates.
+\\
+Figure \ref{fig:adjustment.reg} displays the difference $\delta$ between the observed meta-analysis pooled treatment effect and the regression adjusted treatment effect, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
 The absolute value $|\hat{\theta}_M|$ is taken and the sign of $\hat{\theta}_\textrm{Adj.}$ is adjusted accordingly such that all effects are mirrored to one side.
 $\delta > 0$ is equivalent to $\hat{\theta}_\textrm{Adj} < \hat{\theta}_M$, a reduction of the original effect size.
-For better illustration, some very large and very small differences have been omitted in the $z$-score and Hedges $g$ histograms; they are shown in Table \ref{missing.differences}.
-Table \ref{adjustment.difference} shows the quantiles and means for the various differences and additional information.\\
+Additionally, the test statistic of heterogeneity adjusted small study effect tests (R\"ucker's and Thompson's test) is displayed with green color.
+Test statitics smaller $< 1$ are equivalent to no evidence for small study effect, test statistics between one and two to weak evidence, and above two they indicate evidence for small study effects.
+Some very large and very small differences have been omitted in the $z$-score and Hedges $g$ histograms; they are shown in Table \ref{missing.differences}.
 
@@
 \end{knitrout}
-\caption{Histogram of the treatment effect differences between meta-analysis and adjusted meta-analysis.
+\caption{Histogram of the treatment effect differences between meta-analysis and regression adjusted meta-analysis.
 Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes.
-The bins are centered at zero.}
-\label{fig:adjustment.size}
+The bins are centered at zero and binwidth is equal to 0.1.
+Deeper green color indicates more evidence for small study effects.}
+\label{fig:adjustment.reg}
 \end{figure}
 
+We see that more treatment effect sizes are negatively adjusted and diminished.
+Furthermore, we see that large adjustment is not necessarily connected with evidence for small study effects, but there is of course strong coincidence.
+The cases with no evidence and large adjustment indicate that between-study heterogeneity was not resolved by adjustment for small study effects.
+Adjustment was larger when random effects meta-analysis effect is used as reference, because there larger weights are given to small studies.\\
+Figure \ref{fig:adjustment.copas} shows the same for effect sizes adjusted by Copas; Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
+Therefore, the effect of adjustment by Copas can be seen when comparing adjusted with random effects estimates.
+Again, we clearly see that more effect sizes are adjusted downwards.
+Additionally, there is more coincidence with the small study effect test statistics and adjustment, which is as expected.
+\\
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-16-1}
+
+}
+
+\end{knitrout}
+\caption{Histogram of the treatment effect differences between meta-analysis and Copas adjusted meta-analysis.
+Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes.
+The bins are centered at zero and binwidth is equal to 0.1.
+Deeper green color indicates more evidence for small study effects.}
+\label{fig:adjustment.copas}
+\end{figure}
+
+Table \ref{adjustment.difference} shows the quantiles and means for the various differences and additional information.
+When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
+The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 90 cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or 90 increased by -0.13, fixed effects reference).
+Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or 90 meta-analyses (or increased by 0.24).
+
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jul  1 17:11:03 2019
+% Tue Jul  2 18:53:53 2019
 \begin{table}[ht]
@@
 
-Adjustment leads most often to reduction of treatment effect estimates, as can be seen by the size of the bins of the right part of the histograms in Figure \ref{fig:adjustment.sue}.
-The difference between the bins on the right and left side of the zero-centered bin is however not very large in general.
-The seeming exception of the Copas selection model in the case with $z$-scores and fixed effects reference requires closer examination: Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
-Thus, when comparing Copas with Fixed effects, we compare most often random effects with fixed effects estimates.
-The effect of adjustment by Copas can therefore only be seen when comparing random effects estimates with fixed effect estimates: we can see in Table \ref{adjustment.difference} that we have, for $z$-score, 18.4\% reduced effect sizes compared to 10.3\% (= 100\% - 89.69\%) increased effect sizes.
-Thus, the Copas selection model also has a larger proportion of reduced effect sizes compared to amplified.\\
-%This resolves the case for the seeming exception and for Hedges $g$'s, 24.4\% and 12.46\% (Table \ref{adjustment.difference}. 
-Also, there are more reduced effect sizes if random effects meta-analysis is used as a reference effect size.
-When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
-\\
-The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 90 cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or 90 increased by -0.13, fixed effects reference).
-Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or 90 meta-analyses (or increased by 0.24).
-
 \subsection{Change in Evidence for Treatment Effects} \label{sec:change.evidence}
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-17-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-18-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-18-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-19-1}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jul  1 17:11:05 2019
+% Tue Jul  2 18:53:54 2019
 \begin{table}[ht]
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-21-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-22-1}
 
@@
 
-No formal tests are provided, but the at least there seems to be no clear bias or systematic.
+No formal tests are provided, but the at least there seems to be no clear bias or systematic error.
 The limits of agreement in Figure \ref{fig:adjustment.mean.diff} are large.
@@
 \\
-
-\section{Comparison of Tests and Adjustments} \label{sec:comparison.tests.adjustment}
-
-In section \ref{sec:change.size}, we have seen that some adjustments for small study effects are not in line with our previous definition of publication bias: Some times, the adjustment for small study effects leads to a larger treatment effect.
-We want to take this into account when considering evidence for publication bias.
-Whenever adjustment leads to larger effect sizes, the small study effect test result from section \ref{sec:publication.bias.tests} is revised and changed to negative.
-We will revisit the results from section \ref{sec:publication.bias.tests} and first visualize which proportion of the data finds rather ``negative publication bias'' than the predefined type of publication bias.
-Figure \ref{fig:test.corrected} is equal to Figure \ref{fig:test} with sole difference that now the proportion of ``negative publication bias'' is colored, and the count of significant findings is corrected (not significant for negative publication bias).
-\\
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-23-1}
-
-}
-
-\end{knitrout}
-\caption{Histogram of the $p$-values for small study effect in meta-analyses.
-The testing method is indicated in the header, bin width is equal to 0.1.
-The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-\label{fig:test.corrected}
-\end{figure}
-
-The proportion of findings where we found amplification by adjustment was 34.5\%.
-Most often, the proportion of tests with evidence for small study effects (and especially, excess significance), is lower, though.
-There are exceptions to this, such as Schwarzer's test results, where we have 143 - 60 = 83 significant test results, which corresponds to $\sim$ 40\%.
-Since excess significance is not necessarily connected with small study effects, we can furthermore reject the newly obtained, slightly smaller number of significant excess significance test results, and stick to the previous findings.
-\\
-We can see how the agreement in significance is before, and after having removed negative publication bias significant results in Table \ref{test.agreement}.
-The proportion of agreement in significance is defined as the proportion of cases where, when the test with less significant findings is significant, also the other is significant.
-\\
-After the adjustment of the test results, the agreement for small study effects tests and excess significance tests increases a bit.
-This seems also to be the general trend, but not without exceptions.
-The two right-most columns indicate the agreement in significance, and we see that agreement is never larger than 0.3 (with Egger's test, continuous outcomes).
-Furthermore, only Egger and Thompson show a goof agreement for significance ($\sim$ 0.83).
-In contrast, some small study effect tests for binary outcomes seem rather to be exclusive, see for example the example of Schwarzer's test (6\% after adjustment) and R\"ucker's test (11\%): Only 19 \% of the cases where Schwarzer's Test is significant have also a significant finding using R\"ucker's test.
-Almost all binary small study effect tests have agreement in significance > 0.5.
-Thus, we see that large overall agreement is rather due to the large proportion of non-significant findings.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jul  1 17:11:08 2019
-\begin{table}[ht]
-\centering
-\begingroup\scriptsize
-\begin{tabular}{lcccc}
-  & pre, overall & post, overall & pre, significance & post, significance \\ 
-  \hline
-\hline
-Excess significance, Schwarzer & 0.82 & 0.87 & 0.14 & 0.19 \\ 
-  Excess significance, Peter & 0.80 & 0.84 & 0.27 & 0.21 \\ 
-  Excess significance, Rucker & 0.83 & 0.85 & 0.32 & 0.26 \\ 
-  Excess significance, Harbord & 0.80 & 0.85 & 0.27 & 0.24 \\ 
-  Peter, Schwarzer & 0.82 & 0.88 & 0.38 & 0.39 \\ 
-  Schwarzer, Rucker & 0.82 & 0.87 & 0.32 & 0.35 \\ 
-  Schwarzer, Harbord & 0.86 & 0.91 & 0.58 & 0.54 \\ 
-  Rucker, Peter & 0.89 & 0.92 & 0.64 & 0.62 \\ 
-  Harbord, Peter & 0.86 & 0.90 & 0.53 & 0.48 \\ 
-   \hline
-Excess significance, Egger & 0.79 & 0.81 & 0.72 & 0.61 \\ 
-  Excess significance, Thompson & 0.82 & 0.83 & 0.72 & 0.61 \\ 
-  Excess significance, Begg & 0.81 & 0.84 & 0.33 & 0.28 \\ 
-  Thompson, Egger & 0.95 & 0.96 & 0.96 & 0.95 \\ 
-  Thompson, Begg & 0.87 & 0.89 & 0.69 & 0.73 \\ 
-  Egger, Begg & 0.86 & 0.87 & 0.78 & 0.77 \\ 
-   \hline
-Excess significance, Egger (survival) & 0.87 & 0.97 & 0.00 &  \\ 
-  Excess significance, Thompson (survival) & 0.92 & 0.97 & 0.00 &  \\ 
-  Excess significance, Begg (survival) & 0.95 & 1.00 & 0.00 &  \\ 
-  Thompson, Egger (survival) & 0.90 & 0.95 & 0.67 & 0.00 \\ 
-  Thompson, Begg (survival) & 0.92 & 0.97 & 0.50 & 0.00 \\ 
-  Egger, Begg (survival) & 0.87 & 0.97 & 0.50 & 0.00 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Overall proportion of agreement if significant or unsignificant, and for significance only.
-Horizontal lines separate binary, continuous and survival outcomes (order as in table).
-The reference significance test is the one with more significant results.}
-\label{test.agreement}
-\end{table}
 
@@
 The interventions are restricted to comparisons of two treatment arms by some measure of sanity or worsening of health.
-The difference in this measure between the grouops is referred to as the treatment effect.
+The difference in this measure between the groups is referred to as the treatment effect.
 Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or Hedges $g$, Fisher's z score or Pearsons correlation coefficient.
@@
 The Paule-Mandel estimator \citep{paulemandel} is considered to have most often better properties than the method of moments estimator (\eg \citet{tau.estimator.evaluation}).
-Since we defined $w_i = 1/(\se_i^2 + \tau^2)$, it als holds that
+Since we defined $w_i = 1/(\se_i^2 + \tau^2)$, it also holds that
 
@@
 Now it is shown how linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citet{Egger}.
-Let $\theta/s$ be the dependent variable $y$ and $1/s$ the explanatory variable $x$.
+Let $\theta/s$ be the dependent variable $y$ and $1/\se$ the explanatory variable $x$.
 If plotted, this corresponds to a radial or Galbraith plot \citep{galbraith}.
@@
 \begin{align}
-\theta/s &= \beta_0 + \beta_1/s + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:radial.plot} 
+\theta/s &= \beta_0 + \beta_1/\se + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:radial.plot} 
 \end{align}
@@
 A method proposed in \citet{thompson.sharp} allows for between study variance $\tau^2$, as introduced before in section \ref{sec:meta.analysis}.
-It extends the previously seen linear regression approach with $x = 1/s$ and $y = \theta/s$ by introducing weights.
+It extends the previously seen linear regression approach with $x = 1/\se$ and $y = \theta/s$ by introducing weights.
 The effect size $\theta_i$ is assumed to be distributed as
@@
 A rank based alternative to Peters test for binary outcomes is Harbord's test \citep{Harbord}.
-It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated at log odds ratio $\theta_0 = 0$ and its inverse Fisher information $\se^2$. Formally,
+It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated at log odds ratio $\theta_0 = 0$ and its inverse Fisher information $s^2$. Formally,
 
@@
 \varphi &= e_t - (e_t - e_c)(e_t + (n_t - e_t))/(n_t + n_c) \label{harbord.score} \\
- \se^2&= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \label{harbord.variance}
+ s^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \label{harbord.variance}
 \end{align}
@@
 It can be shown that they are both good approximations of the log odds ratio and its variance if the real $\theta$ is not too far from zero.
-The standardized estimator $r_i/v_i$ is also known as Pet0 odds ratio.
+The standardized estimator $r_i/v_i$ is also known as Peto odds ratio.
 The obtained scores and variances can be used in Egger's test as treatment effects and variances.
@@
 \subsection{Excess Significance Test} \label{sec:excess.significance}
-\citet{excess.significance} developped an exploratory test to detect if the proportion of significant findings is larger than expected.
+\citet{excess.significance} developed an exploratory test to detect if the proportion of significant findings is larger than expected.
 Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study.
@@
 \begin{align}
-p &= \sum_{i = O}^n(n \choose i p^i (1-p)^{n - i})
+p &= \sum_{i = O}^n\Big({n \choose i} p^i (1-p)^{n - i}\Big)
 \end{align}

### 2019-07-02 report/chapter03twosided.Rnw
onesided

--- 2019-07-01 report/chapter03.Rnw
@@
                echo=TRUE, message=FALSE,
-               fig.width=8.1, fig.height=3,
+               fig.width=8, fig.height=3,
                self.contained = FALSE,
@@
 <<echo=FALSE, warning=FALSE>>=
+meta.f <- meta.f %>% rowwise() %>% mutate(pval1.egger = onesided.p(stat = stat.egger, side = side, n = k, test.type = "reg"),
+                                pval1.thompson = onesided.p(stat = stat.thompson, side = side, n = k, test.type = "reg"),
+                                pval1.begg = onesided.p(stat = stat.begg, side = side, n = k, test.type = "rank"),
+
+                                pval1.harbord = onesided.p(stat = stat.harbord, side = side, n = k, test.type = "reg"),
+                                pval1.rucker = onesided.p(stat = stat.rucker, side = side, n = k, test.type = "reg"),
+                                pval1.peter = onesided.p(stat = stat.peter, side = side, n = k, test.type = "reg"),
+                                pval1.schwarzer = onesided.p(stat = stat.schwarzer, side = side, n = k, test.type = "rank"),
+                                pval1.d.tes = pval.d.tes)
+
 sig.level <- 0.1
 meta.f <- meta.f %>% 
-	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
-				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
-				 begg.test = ifelse(pval.begg < sig.level, 1, 0),
-
-				 tes.d.test = ifelse(pval.d.tes < sig.level, 1, 0),
-
-				 schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
-				 rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
-				 harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
-				 peter.test = ifelse(pval.peter < sig.level, 1, 0))
+	mutate(egger.test = ifelse(pval1.egger < sig.level, 1, 0),
+				 thompson.test = ifelse(pval1.thompson < sig.level, 1, 0),
+				 begg.test = ifelse(pval1.begg < sig.level, 1, 0),
+
+				 tes.d.test = ifelse(pval1.d.tes < sig.level, 1, 0),
+
+				 schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
+				 rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
+				 harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
+				 peter.test = ifelse(pval1.peter < sig.level, 1, 0))
 
@@
 
-#--------------------------------------------------------------------------------------------------------------------#
-
-test.bin <- meta.bin %>% ungroup() %>% summarize(
-																								 schwarzer.test = mean(schwarzer.test),
-																								 rucker.test = mean(rucker.test),
-																								 harbord.test = mean(harbord.test),
-																								 peter.test = mean(peter.test))
-test.bin <- test.bin %>% gather(key = "test.type", value = "mean")
-
-p.bin <- meta.bin %>% ungroup() %>% 
-	select(schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
-	gather(key = "test.type", value = "null.hypothesis") %>%  
-	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
-	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-	theme_bw() + xlab(label = NULL) + ggtitle("Binary Outcomes") + theme(legend.position = "top") +
-	guides(fill=guide_legend(title=NULL))+
-	annotate("text", x = test.bin$test.type, y = 500, 
-					 label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
-					 color = "white")
-#--------------------------------------------------------------------------------------------------------------------#
+sig.level <- 0.1
+meta.f <- meta.f %>% rowwise() %>% 
+  mutate(egger.test = ifelse(pval1.egger < sig.level, 1, 0),
+         thompson.test = ifelse(pval1.thompson < sig.level, 1, 0),
+         begg.test = ifelse(pval1.begg < sig.level, 1, 0),
+
+         schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
+         rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
+         harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
+         peter.test = ifelse(pval1.peter < sig.level, 1, 0),
+         I2 = max(c(0, 1 - (k-1)/Q)),
+         i2f = factor(ifelse(I2 == 0, 1, 0)))
+
+meta.bin <- meta.f %>% filter(outcome.type == "bin")
+meta.cont <- meta.f %>% filter(outcome.type == "cont")
+meta.surv <- meta.f %>% filter(outcome.type == "surv")
 
@@
                         mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test), mean(meta.bin$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer", "pval.d.tes"))
-
-labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer", pval.d.tes = "Excess Significance")
+  test.type   = c("pval1.harbord", "pval1.peter", "pval1.rucker", "pval1.schwarzer", "pval1.d.tes"),
+  i2f = factor(rep(0, times = 5)))
+
+labels <- c(pval1.harbord = "Harbord", pval1.peter = "Peter", pval1.rucker = "Rucker", pval1.schwarzer = "Schwarzer", pval1.d.tes = "Excess Significance")
 
 p.dist.bin <- meta.bin %>% ungroup() %>% 
-  select(pval.harbord, pval.peter, pval.rucker, pval.schwarzer, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value") %>% 
-  ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+  select(i2f, pval1.harbord, pval1.peter, pval1.rucker, pval1.d.tes, pval1.schwarzer) %>% 
+  gather(key = "test.type", value = "p.value", pval1.harbord:pval1.schwarzer) %>% 
+  ggplot(aes(x = p.value, fill = i2f)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
   geom_text(data = dat_text, mapping = aes(x = 0.5, y = 200, label = label), color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + ggtitle("Binary Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Continuous Outcomes:
-test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-																									 begg.test = mean(begg.test),
-																									 thompson.test = mean(thompson.test))
-
-test.cont <- test.cont %>% gather(key = "test.type", value = "mean")
-
-p.cont <- meta.cont %>% ungroup() %>% 
-	select(egger.test, thompson.test, begg.test) %>% 
-	gather(key = "test.type", value = "null.hypothesis") %>% 
-	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
-	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-	theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
-	guides(fill=guide_legend(title=NULL))+
-	annotate("text", x = test.cont$test.type, y = 150, 
-					 label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
-					 color = "white")
+  theme(strip.text.x = element_text(size=7)) + ggtitle("Binary Outcomes") + 
+  theme(legend.position = "none")
+
 #--------------------------------------------------------------------------------------------------------------------#
@@
                 round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test), mean(meta.cont$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"))
-
-labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp", pval.d.tes = "Excess significance")
+  test.type   = c("pval1.begg", "pval1.egger", "pval1.thompson", "pval1.d.tes"),
+  i2f = factor(rep(0, times = 4)))
+
+labels <- c(pval1.begg = "Begg Mazumdar", pval1.egger = "Egger", pval1.thompson = "Thompson Sharp", pval1.d.tes = "Excess significance")
 p.dist.cont <- meta.cont %>% ungroup() %>% 
-  select(pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value") %>% 
-  ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
+  select(i2f, pval1.egger, pval1.thompson, pval1.begg, pval1.d.tes) %>% 
+  gather(key = "test.type", value = "p.value", pval1.egger:pval1.d.tes) %>% 
+  ggplot(aes(x = p.value, fill = i2f)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
   facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
   geom_text(data = dat_text, mapping = aes(x = 0.5, y = 60, label = label),  color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + ggtitle("Continuous Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Survival Outcomes:
-test.surv <- meta.surv %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-																									 begg.test = mean(begg.test),
-																									 thompson.test = mean(thompson.test))
-
-test.surv <- test.surv %>% gather(key = "test.type", value = "mean")
-
-p.surv <- meta.surv %>% ungroup() %>% 
-	select(egger.test, thompson.test, begg.test) %>% 
-	gather(key = "test.type", value = "null.hypothesis") %>% 
-	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
-	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-	theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
-	guides(fill=guide_legend(title=NULL))+
-	annotate("text", x = test.surv$test.type, y = 10, 
-					 label = paste(round(test.surv$mean, 2)*100, "% rejected"), 
-					 color = "white") 
+  theme(strip.text.x = element_text(size=7)) + ggtitle("Continuous Outcomes") + 
+  theme(legend.position = "none")
+
 #--------------------------------------------------------------------------------------------------------------------#
@@
                 round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), mean(meta.surv$thompson.test), mean(meta.surv$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"))
+  test.type   = c("pval1.begg", "pval1.egger", "pval1.thompson", "pval1.d.tes"),
+  i2f = factor(rep(0, times = 4)))
+
 p.dist.surv <- meta.surv %>% ungroup() %>% 
-	select(pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
-	gather(key = "test.type", value = "p.value") %>% 
-	ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
+  select(i2f, pval1.egger, pval1.thompson, pval1.begg, pval1.d.tes) %>% 
+  gather(key = "test.type", value = "p.value", pval1.egger:pval1.d.tes) %>% 
+  ggplot(aes(x = p.value, fill = i2f)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
   facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+  guides(fill=guide_legend(title=expression(paste(I^2, " Heterogeneity")))) + 
   geom_text(data = dat_text, mapping = aes(x = 0.5, y = 10, label = label),  color = "black")  + 
-	theme(strip.text.x = element_text(size=7)) + ggtitle("Survival Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Test agreement
-agree.bin <- meta.bin %>% mutate(n.sig = peter.test + rucker.test + harbord.test + schwarzer.test) %>% 
-	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
-	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
-  xlab("Number of significant tests") + ylab("count") + ggtitle("Binary Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-agree.cont <- meta.cont %>% mutate(n.sig = egger.test + thompson.test + begg.test) %>% 
-	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
-	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
-  xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-agree.surv <- meta.surv %>% mutate(n.sig = egger.test + thompson.test + begg.test) %>% 
-	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
-	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
-  xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")
+  scale_fill_discrete(labels = c("0", "> 0")) +
+  theme(strip.text.x = element_text(size=7)) + 
+  ggtitle("Survival Outcomes") 
 #--------------------------------------------------------------------------------------------------------------------#
@@
 
-cor.data <- meta.f %>% select(stat.rucker, stat.harbord, stat.peter, stat.schwarzer, stat.d.tes, 
-                             stat.egger, stat.thompson, stat.begg)
+cor.data <- meta.f %>% mutate(stat.d.tes = stat.d.tes/k) %>%  select(stat.rucker, stat.harbord, stat.peter, stat.schwarzer, stat.d.tes, 
+                             stat.egger, stat.thompson, stat.begg, I2)
 colnames(cor.data) <- c("Rucker", "Harbord", "Peter", "Schwarzer", "Excess s.",  "Egger", "Thompson",
-                        "Begg")
+                        "Begg", "I-squared")
 
@@
 egger.thompson.plot <- meta.f %>% 
-  mutate(mean = ((logit(pval.egger)+ logit(pval.thompson)))/2, 
-         difference = logit(pval.egger) - logit(pval.thompson)) %>% 
+  mutate(mean = ((logit(pval1.egger)+ logit(pval1.thompson)))/2, 
+         difference = logit(pval1.egger) - logit(pval1.thompson)) %>% 
   ggplot(aes(x = mean, y = difference)) + geom_point() + 
@@
 egger.excess.plot <- meta.f %>% 
-  mutate(mean = ((logit(pval.egger)+ logit(pval.d.tes)))/2, 
-         difference = logit(pval.egger) - logit(pval.d.tes)) %>% 
+  mutate(mean = ((logit(pval1.egger)+ logit(pval1.d.tes)))/2, 
+         difference = logit(pval1.egger) - logit(pval1.d.tes)) %>% 
   ggplot(aes(x = mean, y = difference)) + geom_point() + 
@@
 harbord.rucker.plot <- meta.f %>% 
-  mutate(mean = ((logit(pval.harbord)+ logit(pval.rucker)))/2, 
-         difference = logit(pval.harbord) - logit(pval.rucker)) %>% 
+  mutate(mean = ((logit(pval1.harbord)+ logit(pval1.rucker)))/2, 
+         difference = logit(pval1.harbord) - logit(pval1.rucker)) %>% 
   ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
@@
 harbord.excess.plot <- meta.f %>% 
-  mutate(mean = ((logit(pval.harbord)+ logit(pval.d.tes)))/2, 
-         difference = logit(pval.harbord) - logit(pval.d.tes)) %>% 
+  mutate(mean = ((logit(pval1.harbord)+ logit(pval1.d.tes)))/2, 
+         difference = logit(pval1.harbord) - logit(pval1.d.tes)) %>% 
   ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
@@
                                binary = paste(summary.bin$n[-7], "%"),
-                               cont = as.character(paste(c(summary.else$n[-6], NA), "%")))
+                               cont = as.character(paste(c(summary.else$n[-c(6,7)], NA), "%")))
 number.sig.tests <- as.matrix(number.sig.tests)
@@
 
-meta.f <- meta.f %>% mutate(tes.d.test.b = ifelse(pval.d.tes < 0.05, 1, 0),
-                            harbord.test.b = ifelse(pval.harbord < 0.05, 1, 0),
-                            egger.test.b = ifelse(pval.egger < 0.05, 1, 0),
+meta.f <- meta.f %>% mutate(tes.d.test.b = ifelse(pval1.d.tes < 0.05, 1, 0),
+                            harbord.test.b = ifelse(pval1.harbord < 0.05, 1, 0),
+                            egger.test.b = ifelse(pval1.egger < 0.05, 1, 0),
                             test.sum.bin2 = tes.d.test.b + harbord.test.b,
@@
 
-meta.f <- meta.f %>% mutate(egger.test = ifelse(pval.egger < 0.1/3, 1, 0),
-                            thompson.test = ifelse(pval.thompson < 0.1/3, 1, 0),
-                            begg.test = ifelse(pval.begg < 0.1/3, 1, 0),
-
-                            schwarzer.test = ifelse(pval.schwarzer < 0.1/4, 1, 0),
-                            rucker.test = ifelse(pval.rucker < 0.1/4, 1, 0),
-                            harbord.test = ifelse(pval.harbord < 0.1/4, 1, 0),
-                            peter.test = ifelse(pval.peter < 0.1/4, 1, 0),
+meta.f <- meta.f %>% mutate(egger.test = ifelse(pval1.egger < 0.1/3, 1, 0),
+                            thompson.test = ifelse(pval1.thompson < 0.1/3, 1, 0),
+                            begg.test = ifelse(pval1.begg < 0.1/3, 1, 0),
+
+                            schwarzer.test = ifelse(pval1.schwarzer < 0.1/4, 1, 0),
+                            rucker.test = ifelse(pval1.rucker < 0.1/4, 1, 0),
+                            harbord.test = ifelse(pval1.harbord < 0.1/4, 1, 0),
+                            peter.test = ifelse(pval1.peter < 0.1/4, 1, 0),
                             test.sum.bin = tes.d.test + schwarzer.test + harbord.test + peter.test + rucker.test,
@@
 @
-\caption{Histogram of the $p$-values for small study effect in meta-analyses.
+\caption{Histogram of one-sided $p$-values for small study effect in direction of larger effect sizes.
 The testing method is indicated in the header, bin width is equal to 0.1.
@@
 <<echo=FALSE, warning=FALSE, message=FALSE>>=
+
 #HISTOGRAMS:
@@
 
+#Plots separated by effect measure:
+
+sig.level <- 0.1
+meta.f <- meta.f %>% rowwise() %>% 
+  mutate(egger.test = ifelse(pval1.egger < sig.level, 1, 0),
+         thompson.test = ifelse(pval1.thompson < sig.level, 1, 0),
+         begg.test = ifelse(pval1.begg < sig.level, 1, 0),
+
+         schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
+         rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
+         harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
+         peter.test = ifelse(pval1.peter < sig.level, 1, 0),
+         I2 = max(c(0, 1 - (k-1)/Q)),
+         i2f = factor(ifelse(I2 == 0, 1, 0)),
+         se.stat.c = ifelse(outcome.type == "bin", stat.rucker, stat.thompson),
+         se.stat = cut(se.stat.c,
+                       breaks =  c(-7,1, 2, 4.5)))
+
+meta.bin <- meta.f %>% filter(outcome.type == "bin")
+meta.cont <- meta.f %>% filter(outcome.type == "cont")
+meta.surv <- meta.f %>% filter(outcome.type == "surv")
+
 #Meta-Analysis and adjusted treatment effect estimate difference:
@@
 #Z-score:
-diff.z.fixef <- meta.f %>% 
+diff.z.fixef.reg <- meta.f %>% 
   mutate(fixef = est.z.fixef, ranef = est.z.ranef,
@@
          ranef = abs(ranef)) %>% 
-  select(fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
+  select(se.stat, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", regression) %>% 
   mutate(difference = fixef - adjusted.z.score) %>% 
   filter(difference > -.75 & difference < .75) %>% 
-  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + theme(legend.position = "none") + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) +
   xlab(expression(paste("Fixed effects - adjusted ", z, "-score"))) 
@@
 
-diff.z.ranef <- meta.f %>% 
+diff.z.fixef.copas <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(se.stat, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", copas) %>% 
+  mutate(difference = fixef - adjusted.z.score) %>% 
+  filter(difference > -.75 & difference < .75) %>% 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + theme(legend.position = "none") + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) +
+  xlab(expression(paste("Fixed effects - adjusted ", z, "-score"))) 
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.z.ranef.reg <- meta.f %>% 
   mutate(fixef = est.z.fixef, ranef = est.z.ranef,
@@
          ranef = abs(ranef)) %>% 
-  select(fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
+  select(se.stat, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", regression) %>% 
   mutate(difference = ranef - adjusted.z.score) %>% 
   filter(difference > -.75 & difference < .75) %>% 
-  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + theme(legend.position = "none") + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + ylab("") + 
   xlab(expression(paste("Random effects - adjusted ", z, "-score")))
@@
 
+diff.z.ranef.copas <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(se.stat, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", copas) %>% 
+  mutate(difference = ranef - adjusted.z.score) %>% 
+  filter(difference > -.75 & difference < .75) %>% 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + theme(legend.position = "none") + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + 
+  xlab(expression(paste("Random effects - adjusted ", z, "-score")))
+#--------------------------------------------------------------------------------------------------------------------#
+
 #SMD:
-diff.d.fixef <- meta.f %>% 
+diff.d.fixef.reg <- meta.f %>% 
   mutate(fixef = est.d.fixef, ranef = est.d.ranef,
@@
          ranef = abs(ranef)) %>% 
-  select(fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
+  select(se.stat, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.smd", regression) %>% 
   mutate(difference = fixef - adjusted.smd) %>% 
   filter(difference > -1 & difference < 1) %>% 
-  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + theme(legend.position = "none") + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + 
   xlab(expression(paste("Fixed effects - adjusted Hedges ", g)))
@@
 
-diff.d.ranef <- meta.f  %>% 
+diff.d.fixef.copas <- meta.f %>% 
+  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
+         copas = est.d.copas, regression = est.d.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(se.stat, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.smd", copas) %>% 
+  mutate(difference = fixef - adjusted.smd) %>% 
+  filter(difference > -1 & difference < 1) %>% 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + theme(legend.position = "none") + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + 
+  xlab(expression(paste("Fixed effects - adjusted Hedges ", g)))
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.d.ranef.reg <- meta.f  %>% 
   mutate(fixef = est.d.fixef, ranef = est.d.ranef,
@@
          ranef = abs(ranef)) %>% 
-  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
+  gather(key = "method", value = "adjusted.smd", regression) %>% 
   mutate(difference = ranef - adjusted.smd) %>% 
   filter(difference > -1 & difference < 1) %>% 
-  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + guides(fill=guide_legend(title="test stat.")) + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) +  ylab("") +
 xlab(expression(paste("Random effects - adjusted Hedges ", g)))
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.d.ranef.copas <- meta.f  %>% 
+  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
+         copas = est.d.copas, regression = est.d.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  gather(key = "method", value = "adjusted.smd", copas) %>% 
+  mutate(difference = ranef - adjusted.smd) %>% 
+  filter(difference > -1 & difference < 1) %>% 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + guides(fill=guide_legend(title="test stat.")) +
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) +  ylab("") +
+xlab(expression(paste("Random effects - adjusted Hedges ", italic(g))))
 #--------------------------------------------------------------------------------------------------------------------#
@@
 #--------------------------------------------------------------------------------------------------------------------#
+
 sig.level <- 0.1
 meta.f <- meta.f %>% 
-	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
-				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
-				 begg.test = ifelse(pval.begg < sig.level, 1, 0),
-
-				 tes.d.test = ifelse(pval.d.tes < sig.level, 1, 0),
-
-				 schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
-				 rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
-				 harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
-				 peter.test = ifelse(pval.peter < sig.level, 1, 0))
+	mutate(egger.test = ifelse(pval1.egger < sig.level, 1, 0),
+				 thompson.test = ifelse(pval1.thompson < sig.level, 1, 0),
+				 begg.test = ifelse(pval1.begg < sig.level, 1, 0),
+
+				 tes.d.test = ifelse(pval1.d.tes < sig.level, 1, 0),
+
+				 schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
+				 rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
+				 harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
+				 peter.test = ifelse(pval1.peter < sig.level, 1, 0))
 
@@
 \\
-Figure \ref{fig:adjustment.size} displays the difference $\delta$ between the observed meta-analysis pooled treatment effect and the adjusted treatment effect, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
+Figure \ref{fig:adjustment.reg} displays the difference $\delta$ between the observed meta-analysis pooled treatment effect and the regression adjusted treatment effect, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
 The absolute value $|\hat{\theta}_M|$ is taken and the sign of $\hat{\theta}_\textrm{Adj.}$ is adjusted accordingly such that all effects are mirrored to one side.
 $\delta > 0$ is equivalent to $\hat{\theta}_\textrm{Adj} < \hat{\theta}_M$, a reduction of the original effect size.
-For better illustration, some very large and very small differences have been omitted in the $z$-score and Hedges $g$ histograms; they are shown in Table \ref{missing.differences}.
-Table \ref{adjustment.difference} shows the quantiles and means for the various differences and additional information.\\
+Additionally, the test statistic of heterogeneity adjusted small study effect tests (R\"ucker's and Thompson's test) is displayed with green color.
+Test statitics smaller than one are equivalent to no evidence for small study effect, test statistics between one and two weak evidence, and above two evidence for small study effects.
+Some very large and very small differences have been omitted in the $z$-score and Hedges $g$ histograms; they are shown in Table \ref{missing.differences}.
 
 \begin{figure}
-<<echo=FALSE, fig.height = 9, warning=FALSE>>=
-grid.arrange(diff.z.fixef, diff.z.ranef,
-             diff.d.fixef, diff.d.ranef,
-             diff.log.hazard.ratio.fixef, diff.log.hazard.ratio.ranef, ncol = 2)
-@
-\caption{Histogram of the treatment effect differences between meta-analysis and adjusted meta-analysis.
+<<echo=FALSE, fig.height = 5.2, warning=FALSE>>=
+grid.arrange(diff.z.fixef.reg, diff.z.ranef.reg, diff.d.fixef.reg, diff.d.ranef.reg,
+             ncol = 2)
+@
+\caption{Histogram of the treatment effect differences between meta-analysis and regression adjusted meta-analysis.
 Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes.
-The bins are centered at zero.}
-\label{fig:adjustment.size}
+The bins are centered at zero and binwidth is equal to 0.1.
+Deeper green color indicates more evidence for small study effects.}
+\label{fig:adjustment.reg}
 \end{figure}
+
+We see that more treatment effect sizes are negatively adjusted and diminuished.
+Furthermore, we see that large adjustment is not necessarily connected with evidence for small study effects, but there is of course strong coincidence.
+The cases with no evidence and large adjustment indicate that between-study heterogeneity was not resolved by adjustment for small study effects.
+Adjustment was larger when random effects meta-analysis effect is used as reference, because of the larger weights that are given for small studies.\\
+Figure \ref{fig:adjustment.copas} shows the same for effect sizes adjusted by Copas; Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
+Therefore, the effect of adjustment by Copas can be seen when comparing adjusted with random effects estimates.
+Again, we clearly see that more effect sizes are adjusted downwards.
+Additionally, there is more coincidence with the small study effec test statistics and adjustment, which is as expected.
+\\
+
+\begin{figure}
+<<echo=FALSE, fig.height = 4, warning=FALSE>>=
+grid.arrange(diff.z.ranef.copas, diff.d.ranef.copas, ncol = 2)
+@
+\caption{Histogram of the treatment effect differences between meta-analysis and Copas adjusted meta-analysis.
+Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes.
+The bins are centered at zero and binwidth is equal to 0.1.
+Deeper green color indicates more evidence for small study effects.}
+\label{fig:adjustment.copas}
+\end{figure}
+
+Table \ref{adjustment.difference} shows the quantiles and means for the various differences and additional information.
+When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
+The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} increased by -0.13, fixed effects reference).
+Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or \Sexpr{floor(length(!is.na(meta.f$est.d.reg))*0.05)} meta-analyses (or increased by 0.24).
 
@@
 @
-
-Adjustment leads most often to reduction of treatment effect estimates, as can be seen by the size of the bins of the right part of the histograms in Figure \ref{fig:adjustment.sue}.
-The difference between the bins on the right and left side of the zero-centered bin is however not very large in general.
-The seeming exception of the Copas selection model in the case with $z$-scores and fixed effects reference requires closer examination: Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
-Thus, when comparing Copas with Fixed effects, we compare most often random effects with fixed effects estimates.
-The effect of adjustment by Copas can therefore only be seen when comparing random effects estimates with fixed effect estimates: we can see in Table \ref{adjustment.difference} that we have, for $z$-score, 18.4\% reduced effect sizes compared to 10.3\% (= 100\% - 89.69\%) increased effect sizes.
-Thus, the Copas selection model also has a larger proportion of reduced effect sizes compared to amplified.\\
-%This resolves the case for the seeming exception and for Hedges $g$'s, 24.4\% and 12.46\% (Table \ref{adjustment.difference}. 
-Also, there are more reduced effect sizes if random effects meta-analysis is used as a reference effect size.
-When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
-\\
-The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} increased by -0.13, fixed effects reference).
-Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or \Sexpr{floor(length(!is.na(meta.f$est.d.reg))*0.05)} meta-analyses (or increased by 0.24).
 
@@
 \\
-
-\section{Comparison of Tests and Adjustments} \label{sec:comparison.tests.adjustment}
-<<echo = FALSE, warnings = FALSE>>=
-#--------------------------------------------------------------------------------------------------------------------#
-meta.bin <- adjustment.diff.keep %>% filter(outcome.type == "bin")
-meta.cont <- adjustment.diff.keep %>% filter(outcome.type == "cont")
-meta.surv <- adjustment.diff.keep %>% filter(outcome.type == "surv")
-
-dat_text <- data.frame(
-  label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
-                  sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test), sum(meta.bin$tes.d.test, na.rm = T)), "< 0.1,",
-                round(c(mean(meta.bin$harbord.test), mean(meta.bin$peter.test), 
-                        mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test), mean(meta.bin$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer", "pval.d.tes"),
-  bias.side = rep(0, times = 5))
-
-labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer", pval.d.tes = "Excess Significance")
-
-p.dist.bin.corrected <- meta.bin  %>% ungroup() %>% 
-  select(bias.side, pval.harbord, pval.peter, pval.rucker, pval.schwarzer, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value", pval.harbord:pval.d.tes) %>% 
-  ggplot(aes(x = p.value, fill = factor(bias.side))) + 
-  geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + theme(legend.position = "none") +
-  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 200, label = label), color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + 
-  ggtitle("Binary Outcomes")
-
-#--------------------------------------------------------------------------------------------------------------------#
-#Continuous Outcomes:
-dat_text <- data.frame(
-  label = paste(c(sum(meta.cont$begg.test), sum(meta.cont$egger.test), sum(meta.cont$thompson.test), sum(meta.cont$tes.d.test, na.rm = T)), "< 0.1,",
-                round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test), mean(meta.cont$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"),
-  bias.side = rep(0, times = 4))
-
-labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp", pval.d.tes = "Excess significance")
-
-p.dist.cont.corrected <- meta.cont %>% ungroup() %>% 
-  select(bias.side, pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value", pval.egger:pval.d.tes) %>% 
-  ggplot(aes(x = p.value, fill = factor(bias.side))) + 
-  geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + theme(legend.position = "none") +
-  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 60, label = label),  color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + ggtitle("Continuous Outcomes")
-
-#--------------------------------------------------------------------------------------------------------------------#
-dat_text <- data.frame(
-  label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), 
-                  sum(meta.surv$thompson.test), sum(meta.surv$tes.d.test, na.rm = T)), "< 0.1,",
-                round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), 
-                        mean(meta.surv$thompson.test), 
-                        mean(meta.surv$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"),
-  bias.side = rep("publication bias", times = 4))
-p.dist.surv.corrected <- meta.surv %>% ungroup() %>% 
-  mutate(bias.side = factor(ifelse(bias.side == 1, "publication bias", "negative publication bias"))) %>% 
-  select(bias.side, pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value", pval.egger:pval.d.tes) %>% 
-  ggplot(aes(x = p.value, fill = factor(bias.side))) + 
-  geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + guides(fill=guide_legend(title=NULL))+
-  theme(legend.position = "bottom") +
-  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 10, label = label),  color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + ggtitle("Survival Outcomes")
-@
-
-In section \ref{sec:change.size}, we have seen that some adjustments for small study effects are not in line with our previous definition of publication bias: Some times, the adjustment for small study effects leads to a larger treatment effect.
-We want to take this into account when considering evidence for publication bias.
-Whenever adjustment leads to larger effect sizes, the small study effect test result from section \ref{sec:publication.bias.tests} is revised and changed to negative.
-We will revisit the results from section \ref{sec:publication.bias.tests} and first visualize which proportion of the data finds rather ``negative publication bias'' than the predefined type of publication bias.
-Figure \ref{fig:test.corrected} is equal to Figure \ref{fig:test} with sole difference that now the proportion of ``negative publication bias'' is colored, and the count of significant findings is corrected (not significant for negative publication bias).
-\\
-
-\begin{figure}
-<<echo=FALSE, fig.height = 9>>=
-grid.arrange(p.dist.bin.corrected,
-             p.dist.cont.corrected,
-             p.dist.surv.corrected, ncol = 1)
-@
-\caption{Histogram of the $p$-values for small study effect in meta-analyses.
-The testing method is indicated in the header, bin width is equal to 0.1.
-The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-\label{fig:test.corrected}
-\end{figure}
-
-The proportion of findings where we found amplification by adjustment was \Sexpr{round((1-sum(adjustment.diff.keep$bias.side)/dim(adjustment.diff.keep)[1])*100, 1)}\%.
-Most often, the proportion of tests with evidence for small study effects (and especially, excess significance), is lower, though.
-There are exceptions to this, such as Schwarzer's test results, where we have 143 - 60 = 83 significant test results, which corresponds to $\sim$ 40\%.
-Since excess significance is not necessarily connected with small study effects, we can furthermore reject the newly obtained, slightly smaller number of significant excess significance test results, and stick to the previous findings.
-\\
-We can see how the agreement in significance is before, and after having removed negative publication bias significant results in Table \ref{test.agreement}.
-The proportion of agreement in significance is defined as the proportion of cases where, when the test with less significant findings is significant, also the other is significant.
-\\
-After the adjustment of the test results, the agreement for small study effects tests and excess significance tests increases a bit.
-This seems also to be the general trend, but not without exceptions.
-The two right-most columns indicate the agreement in significance, and we see that agreement is never larger than 0.3 (with Egger's test, continuous outcomes).
-Furthermore, only Egger and Thompson show a goof agreement for significance ($\sim$ 0.83).
-In contrast, some small study effect tests for binary outcomes seem rather to be exclusive, see for example the example of Schwarzer's test (6\% after adjustment) and R\"ucker's test (11\%): Only 19 \% of the cases where Schwarzer's Test is significant have also a significant finding using R\"ucker's test.
-Almost all binary small study effect tests have agreement in significance > 0.5.
-Thus, we see that large overall agreement is rather due to the large proportion of non-significant findings.
-
-<<echo = FALSE, warning= FALSE>>=
-#Agreement proportions of publication bias tests:
-
-#Binary:
-meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
-                                              tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
-                                              tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
-                                              tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
-                                              schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
-                                              schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
-                                              schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
-                                              rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
-                                              rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
-                                              harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
-agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
-                                                      tes.d.peter = sum(tes.d.peter == "agree")/n(),
-                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
-                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
-                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
-                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
-                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
-                                                      rucker.peter = sum(rucker.peter == "agree")/n(),
-                                                      harbord.peter = sum(harbord.peter == "agree")/n())
-meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test + schwarzer.test > 1, "agree", "disagree"),
-                                              tes.d.peter = ifelse(tes.d.test + peter.test > 1, "agree", "disagree"),
-                                              tes.d.rucker = ifelse(tes.d.test + rucker.test > 1, "agree", "disagree"),
-                                              tes.d.harbord = ifelse(tes.d.test + harbord.test > 1, "agree", "disagree"),
-                                              schwarzer.peter = ifelse(schwarzer.test + peter.test > 1, "agree", "disagree"),
-                                              schwarzer.rucker = ifelse(schwarzer.test + rucker.test > 1, "agree", "disagree"),
-                                              schwarzer.harbord = ifelse(schwarzer.test + harbord.test > 1, "agree", "disagree"),
-                                              rucker.peter = ifelse(rucker.test + peter.test > 1, "agree", "disagree"),
-                                              rucker.harbord = ifelse(rucker.test + harbord.test > 1, "agree", "disagree"),
-                                              harbord.peter = ifelse(harbord.test + peter.test > 1, "agree", "disagree"))
-agreement.sig.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/sum(schwarzer.test),
-                                                      tes.d.peter = sum(tes.d.peter == "agree")/sum(peter.test),
-                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/sum(rucker.test),
-                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/sum(harbord.test),
-                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/sum(schwarzer.test),
-                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/sum(schwarzer.test),
-                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/sum(schwarzer.test),
-                                                      rucker.peter = sum(rucker.peter == "agree")/sum(peter.test),
-                                                      harbord.peter = sum(harbord.peter == "agree")/sum(peter.test))
-
-binary.tests.agreement <- rbind(agreement.bin, agreement.sig.bin)
-rownames(binary.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
-colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
-                                      "Excess significance, Rucker", "Excess significance, Harbord",
-                                      "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
-                                      "Rucker, Peter", "Harbord, Peter")
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Continuous:
-meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
-                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
-                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
-                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
-                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
-                                                         egger.begg = sum(egger.begg == "agree")/n())
-meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
-agreement.sig.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
-                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
-                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
-                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
-                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
-                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))
-
-cont.tests.agreement <- rbind(agreement.cont, agreement.sig.cont)
-rownames(cont.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
-colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson",
-                                     "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Survival:
-meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
-                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
-                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
-                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
-                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
-                                                         egger.begg = sum(egger.begg == "agree")/n())
-meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
-agreement.sig.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
-                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
-                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
-                                                             thompson.egger = sum(thompson.egger == "agree")/sum(egger.test),
-                                                             thompson.begg = sum(thompson.begg == "agree")/sum(thompson.test),
-                                                             egger.begg = sum(egger.begg == "agree")/sum(egger.test))
-
-surv.tests.agreement <- rbind(agreement.surv, agreement.sig.surv)
-rownames(surv.tests.agreement) <- c("Agreement (overall)","Agreement (significance)")
-colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)",
-                                    "Excess significance, Begg (survival)", "Thompson, Egger (survival)",
-                                    "Thompson, Begg (survival)", "Egger, Begg (survival)")
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Merging:
-test.agreement.new <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
-
-test.agreement.together <- data.frame(test.agreement[,1], test.agreement.new[,1],
-                                      test.agreement[,2], test.agreement.new[,2])
-
-colnames(test.agreement.together) <- c("pre, overall", "post, overall", "pre, significance",
-                                      "post, significance")
-
-#--------------------------------------------------------------------------------------------------------------------#
-@
-
-<<echo=FALSE, results='asis'>>=
-print(xtable(test.agreement.together, align = "lcccc", caption = "Overall proportion of agreement if significant or unsignificant, and for significance only.
-Horizontal lines separate binary, continuous and survival outcomes (order as in table).
-The reference significance test is the one with more significant results.",
-             label = "test.agreement"), hline = c(0, 0, 9, 15, 21), size = "scriptsize")
-@

### 2019-07-02 report/chapter06.Rnw
onesided

--- 2019-07-01 report/chapter03.Rnw
@@
-% LaTeX file for Chapter 03
+% LaTeX file for Chapter 06
 
@@
 
-\chapter{Results} \label{ch:Results}
+\chapter{Additional Results} \label{ch:Additional.Results}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Small Study Effect and Excess of Significance Tests} \label{sec:publication.bias.tests}
-<<echo=FALSE, warning=FALSE>>=
-sig.level <- 0.1
-meta.f <- meta.f %>% 
-	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
-				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
-				 begg.test = ifelse(pval.begg < sig.level, 1, 0),
-
-				 tes.d.test = ifelse(pval.d.tes < sig.level, 1, 0),
-
-				 schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
-				 rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
-				 harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
-				 peter.test = ifelse(pval.peter < sig.level, 1, 0))
-
-meta.bin <- meta.f %>% filter(outcome.type == "bin")
-meta.cont <- meta.f %>% filter(outcome.type == "cont")
-meta.surv <- meta.f %>% filter(outcome.type == "surv")
-
-#Agreement proportions of publication bias tests:
-
-#Binary:
-meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
-                                              tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
-                                              tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
-                                              tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
-                                              schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
-                                              schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
-                                              schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
-                                              rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
-                                              rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
-                                              harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
-agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
-                                                      tes.d.peter = sum(tes.d.peter == "agree")/n(),
-                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
-                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
-                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
-                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
-                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
-                                                      rucker.peter = sum(rucker.peter == "agree")/n(),
-                                                      harbord.peter = sum(harbord.peter == "agree")/n())
-meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test + schwarzer.test > 1, "agree", "disagree"),
-                                              tes.d.peter = ifelse(tes.d.test + peter.test > 1, "agree", "disagree"),
-                                              tes.d.rucker = ifelse(tes.d.test + rucker.test > 1, "agree", "disagree"),
-                                              tes.d.harbord = ifelse(tes.d.test + harbord.test > 1, "agree", "disagree"),
-                                              schwarzer.peter = ifelse(schwarzer.test + peter.test > 1, "agree", "disagree"),
-                                              schwarzer.rucker = ifelse(schwarzer.test + rucker.test > 1, "agree", "disagree"),
-                                              schwarzer.harbord = ifelse(schwarzer.test + harbord.test > 1, "agree", "disagree"),
-                                              rucker.peter = ifelse(rucker.test + peter.test > 1, "agree", "disagree"),
-                                              rucker.harbord = ifelse(rucker.test + harbord.test > 1, "agree", "disagree"),
-                                              harbord.peter = ifelse(harbord.test + peter.test > 1, "agree", "disagree"))
-agreement.sig.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/sum(tes.d.test),
-                                                      tes.d.peter = sum(tes.d.peter == "agree")/sum(tes.d.test),
-                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/sum(tes.d.test),
-                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/sum(tes.d.test),
-                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/sum(schwarzer.test),
-                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/sum(schwarzer.test),
-                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/sum(schwarzer.test),
-                                                      rucker.peter = sum(rucker.peter == "agree")/sum(rucker.test),
-                                                      harbord.peter = sum(harbord.peter == "agree")/sum(peter.test))
-
-binary.tests.agreement <- rbind(agreement.bin, agreement.sig.bin)
-rownames(binary.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
-colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
-                                      "Excess significance, Rucker", "Excess significance, Harbord",
-                                      "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
-                                      "Rucker, Peter", "Harbord, Peter")
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Continuous:
-meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
-                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
-                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
-                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
-                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
-                                                         egger.begg = sum(egger.begg == "agree")/n())
-meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
-agreement.sig.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
-                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
-                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
-                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
-                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
-                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))
-
-cont.tests.agreement <- rbind(agreement.cont, agreement.sig.cont)
-rownames(cont.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
-colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson",
-                                     "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Survival:
-meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
-                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
-                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
-                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
-                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
-                                                         egger.begg = sum(egger.begg == "agree")/n())
-meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
-agreement.sig.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
-                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(thompson.test),
-                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(begg.test),
-                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
-                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
-                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))
-
-surv.tests.agreement <- rbind(agreement.surv, agreement.sig.surv)
-rownames(surv.tests.agreement) <- c("Agreement (overall)","Agreement (significance)")
-colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)",
-                                    "Excess significance, Begg (survival)", "Thompson, Egger (survival)",
-                                    "Thompson, Begg (survival)", "Egger, Begg (survival)")
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Merging:
-test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-test.bin <- meta.bin %>% ungroup() %>% summarize(
-																								 schwarzer.test = mean(schwarzer.test),
-																								 rucker.test = mean(rucker.test),
-																								 harbord.test = mean(harbord.test),
-																								 peter.test = mean(peter.test))
-test.bin <- test.bin %>% gather(key = "test.type", value = "mean")
-
-p.bin <- meta.bin %>% ungroup() %>% 
-	select(schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
-	gather(key = "test.type", value = "null.hypothesis") %>%  
-	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
-	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-	theme_bw() + xlab(label = NULL) + ggtitle("Binary Outcomes") + theme(legend.position = "top") +
-	guides(fill=guide_legend(title=NULL))+
-	annotate("text", x = test.bin$test.type, y = 500, 
-					 label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
-					 color = "white")
-#--------------------------------------------------------------------------------------------------------------------#
-
-dat_text <- data.frame(
-  label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
-                  sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test), sum(meta.bin$tes.d.test, na.rm = T)), "< 0.1,",
-                round(c(mean(meta.bin$harbord.test), mean(meta.bin$peter.test), 
-                        mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test), mean(meta.bin$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer", "pval.d.tes"))
-
-labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer", pval.d.tes = "Excess Significance")
-
-p.dist.bin <- meta.bin %>% ungroup() %>% 
-  select(pval.harbord, pval.peter, pval.rucker, pval.schwarzer, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value") %>% 
-  ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 200, label = label), color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + ggtitle("Binary Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Continuous Outcomes:
-test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-																									 begg.test = mean(begg.test),
-																									 thompson.test = mean(thompson.test))
-
-test.cont <- test.cont %>% gather(key = "test.type", value = "mean")
-
-p.cont <- meta.cont %>% ungroup() %>% 
-	select(egger.test, thompson.test, begg.test) %>% 
-	gather(key = "test.type", value = "null.hypothesis") %>% 
-	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
-	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-	theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
-	guides(fill=guide_legend(title=NULL))+
-	annotate("text", x = test.cont$test.type, y = 150, 
-					 label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
-					 color = "white")
-#--------------------------------------------------------------------------------------------------------------------#
-
-dat_text <- data.frame(
-  label = paste(c(sum(meta.cont$begg.test), sum(meta.cont$egger.test), sum(meta.cont$thompson.test), sum(meta.cont$tes.d.test, na.rm = T)), "< 0.1,",
-                round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test), mean(meta.cont$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"))
-
-labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp", pval.d.tes = "Excess significance")
-p.dist.cont <- meta.cont %>% ungroup() %>% 
-  select(pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value") %>% 
-  ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
-  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 60, label = label),  color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + ggtitle("Continuous Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Survival Outcomes:
-test.surv <- meta.surv %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-																									 begg.test = mean(begg.test),
-																									 thompson.test = mean(thompson.test))
-
-test.surv <- test.surv %>% gather(key = "test.type", value = "mean")
-
-p.surv <- meta.surv %>% ungroup() %>% 
-	select(egger.test, thompson.test, begg.test) %>% 
-	gather(key = "test.type", value = "null.hypothesis") %>% 
-	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
-	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-	theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
-	guides(fill=guide_legend(title=NULL))+
-	annotate("text", x = test.surv$test.type, y = 10, 
-					 label = paste(round(test.surv$mean, 2)*100, "% rejected"), 
-					 color = "white") 
-#--------------------------------------------------------------------------------------------------------------------#
-
-dat_text <- data.frame(
-  label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), sum(meta.surv$thompson.test), sum(meta.surv$tes.d.test, na.rm = T)), "< 0.1,",
-                round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), mean(meta.surv$thompson.test), mean(meta.surv$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"))
-p.dist.surv <- meta.surv %>% ungroup() %>% 
-	select(pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
-	gather(key = "test.type", value = "p.value") %>% 
-	ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
-	facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 10, label = label),  color = "black") + 
-	theme(strip.text.x = element_text(size=7)) + ggtitle("Survival Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Test agreement
-agree.bin <- meta.bin %>% mutate(n.sig = peter.test + rucker.test + harbord.test + schwarzer.test) %>% 
-	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
-	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
-  xlab("Number of significant tests") + ylab("count") + ggtitle("Binary Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-agree.cont <- meta.cont %>% mutate(n.sig = egger.test + thompson.test + begg.test) %>% 
-	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
-	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
-  xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-agree.surv <- meta.surv %>% mutate(n.sig = egger.test + thompson.test + begg.test) %>% 
-	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
-	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
-  xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-################################################################################################
-################################################################################################
-#PUBLICATION BIAS TEST AGREEMENT
-################################################################################################
-################################################################################################
-
-cor.data <- meta.f %>% select(stat.rucker, stat.harbord, stat.peter, stat.schwarzer, stat.d.tes, 
-                             stat.egger, stat.thompson, stat.begg)
-colnames(cor.data) <- c("Rucker", "Harbord", "Peter", "Schwarzer", "Excess s.",  "Egger", "Thompson",
-                        "Begg")
-
-panel.pts.new <- function (x, y, corr = NULL, col.regions, cor.method, ...) 
-{
-
-  plot.xy(xy.coords(x, y), type = "p", ...)
-  box(col = "lightgray")
-  rect(xleft = -1.644854, ybottom = -1.644854, xright = 1.644854, ytop = 1.644854, density = NULL, angle = 45,
-       col = NA, border = "white", lty = 1, lwd = 1.4, 
-       ...)
-  if (!is.null(corr)) 
-    return()
-
-}
-
-# Tukey Mean difference plots;
-#--------------------------------------------------------------------------------------------------------------------#
-
-egger.thompson.plot <- meta.f %>% 
-  mutate(mean = ((logit(pval.egger)+ logit(pval.thompson)))/2, 
-         difference = logit(pval.egger) - logit(pval.thompson)) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point() + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + theme(legend.position = "none") +
-  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
-                     values = c("red", "blue")) +
-  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value Thompson)" )))
-#--------------------------------------------------------------------------------------------------------------------#
-
-egger.excess.plot <- meta.f %>% 
-  mutate(mean = ((logit(pval.egger)+ logit(pval.d.tes)))/2, 
-         difference = logit(pval.egger) - logit(pval.d.tes)) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point() + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + theme(legend.position = "none") +
-  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
-                     values = c("red", "blue")) +
-  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value excess significance)" )))
-#--------------------------------------------------------------------------------------------------------------------#
-
-harbord.rucker.plot <- meta.f %>% 
-  mutate(mean = ((logit(pval.harbord)+ logit(pval.rucker)))/2, 
-         difference = logit(pval.harbord) - logit(pval.rucker)) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + theme(legend.position = "none") +
-  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
-                     values = c("red", "blue")) +
-  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value Rucker)" )))
-#--------------------------------------------------------------------------------------------------------------------#
-
-harbord.excess.plot <- meta.f %>% 
-  mutate(mean = ((logit(pval.harbord)+ logit(pval.d.tes)))/2, 
-         difference = logit(pval.harbord) - logit(pval.d.tes)) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + #theme(legend.position = "bottom") +
-  scale_color_manual(labels = c("systematic error", "95 % conf. int."), 
-                     values = c("red", "blue")) +
-  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value excess significance)" )))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Table with proportions of significant test results:
-meta.f <- meta.f %>% 
-mutate(test.sum.bin = tes.d.test + schwarzer.test + harbord.test + peter.test + rucker.test,
-       test.sum.else = tes.d.test + egger.test + thompson.test + begg.test, 
-       test.sum.bin2 = tes.d.test + harbord.test,
-       test.sum.else2 = tes.d.test + egger.test, 
-       test.min.bin = ifelse(schwarzer.test + harbord.test + peter.test + rucker.test > 0, 1, 0),
-       test.min.else = ifelse(egger.test + thompson.test + begg.test > 0, 1, 0),
-       test.min.bin2 = ifelse(test.sum.bin2 > 0, 1, 0),
-       test.min.else2 = ifelse(test.sum.else2 > 0, 1, 0))
-
-mean.min.bin <- round(mean(meta.f$test.min.bin, na.rm = T)*100, 1)
-mean.min.else <- round(mean(meta.f$test.min.else, na.rm = T)*100, 1)
-
-mean.min.bin2 <- round(mean(meta.f$test.min.bin2, na.rm = T)*100, 1)
-mean.min.else2 <- round(mean(meta.f$test.min.else2, na.rm = T)*100, 1)
-
-both.bin <- round(length(which(meta.f$test.sum.bin2 == 2))/
-                    length(which(!is.na(meta.f$test.sum.bin2)))*100, 1)
-
-both.else <- round(length(which(meta.f$test.sum.else2 == 2))/
-                     length(which(!is.na(meta.f$test.sum.else2)))*100, 1)
-
-summary.bin <- round(meta.f %>% 
-  group_by(test.sum.bin) %>% summarise(n = n()) %>% select(n)/dim(meta.bin)[1] * 100, 1)
-
-summary.else <- round(meta.f %>% group_by(test.sum.else) %>% 
-                        summarise(n = n()) %>% 
-                        select(n)/(dim(meta.cont)[1] + dim(meta.surv)[1]) * 100, 1)
-
-number.sig.tests <- data.frame(number = seq(from = 0, to = 5),
-                               binary = paste(summary.bin$n[-7], "%"),
-                               cont = as.character(paste(c(summary.else$n[-6], NA), "%")))
-number.sig.tests <- as.matrix(number.sig.tests)
-number.sig.tests[6,3][1] <- "-"
-
-colnames(number.sig.tests) <- c("Count", "Binary Outcomes", "Continuous and Survival")
-
-meta.f <- meta.f %>% mutate(tes.d.test.b = ifelse(pval.d.tes < 0.05, 1, 0),
-                            harbord.test.b = ifelse(pval.harbord < 0.05, 1, 0),
-                            egger.test.b = ifelse(pval.egger < 0.05, 1, 0),
-                            test.sum.bin2 = tes.d.test.b + harbord.test.b,
-                            test.sum.else2 = tes.d.test.b + egger.test.b, 
-                            test.min.bin2 = ifelse(test.sum.bin2 > 0, 1, 0),
-                            test.min.else2 = ifelse(test.sum.else2 > 0, 1, 0))
-
-mean.min.bin2.b <- round(mean(meta.f$test.min.bin2, na.rm = T)*100, 1)
-mean.min.else2.b <- round(mean(meta.f$test.min.else2, na.rm = T)*100, 1)
-
-both.bin.b <- round(length(which(meta.f$test.sum.bin2 == 2))/
-                    length(which(!is.na(meta.f$test.sum.bin2)))*100, 1)
-
-both.else.b <- round(length(which(meta.f$test.sum.else2 == 2))/
-                     length(which(!is.na(meta.f$test.sum.else2)))*100, 1)
-
-meta.f <- meta.f %>% mutate(egger.test = ifelse(pval.egger < 0.1/3, 1, 0),
-                            thompson.test = ifelse(pval.thompson < 0.1/3, 1, 0),
-                            begg.test = ifelse(pval.begg < 0.1/3, 1, 0),
-
-                            schwarzer.test = ifelse(pval.schwarzer < 0.1/4, 1, 0),
-                            rucker.test = ifelse(pval.rucker < 0.1/4, 1, 0),
-                            harbord.test = ifelse(pval.harbord < 0.1/4, 1, 0),
-                            peter.test = ifelse(pval.peter < 0.1/4, 1, 0),
-                            test.sum.bin = tes.d.test + schwarzer.test + harbord.test + peter.test + rucker.test,
-                            test.sum.else = tes.d.test + egger.test + thompson.test + begg.test, 
-                            test.min.bin = ifelse(schwarzer.test + harbord.test + peter.test + rucker.test > 0, 1, 0),
-                            test.min.else = ifelse(egger.test + thompson.test + begg.test > 0, 1, 0))
-
-mean.min.bin.b <- round(mean(meta.f$test.min.bin, na.rm = T)*100, 1)
-mean.min.else.b <- round(mean(meta.f$test.min.else, na.rm = T)*100, 1)
-
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-
-@
-
-The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with small study effects tests and excess significance tests.
-We will apply the tests on the original effect size measures, i.e.
-risk ratios, Hedges $g$ or log hazard ratios.
-Different tests are applied depending on if the outcomes are of type binary or continuous or survival.\\
-Thus, we apply multiple tests on the same data.
-The results can then be displayed separately to compare the different tests.
-A histogram of $p$-values will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.
-\\
-``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}.
-For continuous and survival outcomes, the names refer to:
-
-\begin{itemize}
-\item Egger's test, the weighted linear regression test as described in section \ref{sec:Egger}
-\item Thompson and Sharp's test, the weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
-\item Begg and Mazumdar's test, the rank test described in section \ref{sec:Begg}
-\end{itemize}
-
-For binary outcomes, the names refer to:
-\begin{itemize}
-\item Harbord's test, the likelihood score based test (section \ref{sec:Harbord})
-\item Peter's test, the weighted linear regression with inverse sample size as explanatory variable (study size proxy) described in section \ref{sec:Peter}
-\item R\"ucker's test, the test based on the arcsine transformation of proportions, in combination with Thompson and Sharp's regression test (section \ref{sec:Rucker})
-\item Schwarzer's test, the rank based test using the expected event counts computed with the hypergeometric distribution (section \ref{sec:Schwarzer})
-\end{itemize}
-
-\begin{figure}
-<<echo=FALSE, fig.height = 9>>=
-grid.arrange(p.dist.bin,
-             p.dist.cont,
-             p.dist.surv, ncol = 1)
-@
-\caption{Histogram of the $p$-values for small study effect in meta-analyses.
-The testing method is indicated in the header, bin width is equal to 0.1.
-The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-\label{fig:test}
-\end{figure}
-
-%Agreement table -> Chunck 1
-The histograms in Figure \ref{fig:test} show that the distributions are (with the exception of Schwarzer's test) skewed to the right for all outcome types, indicating evidence for small study effects and excess significance, respectively.
-Moreover, the excess significance tests have a mode around $p = 0.4$.
-There is some discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger.
-Survival outcome type results are quite different with very few evidence for small study effects and excess significance.
-Note that the sample size of survival outcomes is small ($n$ = \Sexpr{dim(meta.surv)[1]}).\\
-It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects/excess significance for the same meta-analyses.
-A simple method to check the coincidence of test results is to compare scatterplots and empirical Spearman correlations between the test statistics.
-This is done in Figure \ref{fig:test.agreement}.
-Here, there is no separation between survival and continuous outcomes.
-The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results.
-
-\begin{figure}
-<<echo=FALSE, fig.height = 6, warning=FALSE>>=
-corrgram(cor.data, 
-         upper.panel=panel.pts.new, lower.panel=panel.cor, 
-         cex.labels = 1, cex = .25, cex.cor = 2, pch = 1,
-         text.panel=panel.txt, cor.method = "spearman")
-@
-\caption{Pairs-plot for test statistics of small study effect and excess significance.
-The lower panel gives the Spearman correlations for the different test statistics, and the upper panel displays a scatterplot.
-The colors indicate magnitude and direction of the correlation coefficients.
-The rectangle with white borders displays the area within which both tests have absolute value < 1.64 (dots outside are statistically significant using the 0.1 threshold).}
-\label{fig:test.agreement}
-\end{figure}
-
-The observed patterns on the scatterplots differ: Excess significance and small study effect test statistics do usually not align with each other, forming rather randomly scattered bulks of points.
-Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients.
-In general, small study effect tests align on the diagonal, but the extent to which they align differs.
-Continuous and survival outcome type tests align more closely than binary outcome tests.
-While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics .\\
-Because scatterplots and correlation coefficients can be misleading, also a Tukey mean-difference or Bland-Altman of transformed $p$-values plot is shown for four scenarios in Figure \ref{fig:mean.diff.test}:
-\begin{itemize}
-\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
-\item For Egger's and excess significance tests
-\item For Harbord's and R\"ucker's tests
-\item For Harbord's and excess significance tests
-\end{itemize}
-
-This can be justified since all tests are supposed to measure the evidence for publication bias.
-For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation $f(x)  = \log\frac{p}{1-p}$).
-The mean $p$-value (($f$($p$-value no.
-1) + $f$($p$-value no.
-2))/2) is then displayed against the difference between the $f$($p$-value).
-If no systematic errors and biases exist between the measurement methods, then
-
-\begin{itemize}
-\item the mean of the differences should be around zero (systematic error) 
-\item the points should scatter independently on the $y$-axis and no general increase or decrease with the mean of the transformed $p$-values should be visible
-\end{itemize}
-
-Although this is not formally tested, the last criterium seems not to be given when comparing small study effect and excess significance tests.
-With decreasing mean, the difference gets more negative, and vice versa, such that one would predict that the excess significance $p$-values are more ``extreme'' in both directions.
--- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- However, the systematic error between the compared tests is close to zero, and small study effect tests do probably not show bias when compared to each other.
-\\
-The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests.
-This suggests that correspondence between the tests is not very good in general.
-
-\begin{figure}
-<<echo=FALSE, fig.height = 8.5, warning=FALSE>>=
-grid.arrange(egger.thompson.plot, 
-             egger.excess.plot,
-             harbord.rucker.plot, 
-             harbord.excess.plot, ncol = 1)
-@
-\caption{Mean - difference plots for logit transformed $p$-values.
-The mean of logit transformed $p$-values is displayed on the $x$-axis and the difference on the $y$-axis.
-Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).}
-\label{fig:mean.diff.test}
-\end{figure}
-
-The previous results suggest that the results will also differ substantially after applying the common dichotomization of $p$-values.
-We expect that some proportion of the meta-analysis will only be significant for a certain test, and this is indeed observed in Table \ref{number.sig.tests}.
-It displays the percentage of meta-analyses with a certain number of significant test results.
-
-<<echo = FALSE, results='asis'>>=
-print(xtable(number.sig.tests, caption = "Counts Number of significant test results per meta-analysis, separated
-       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
-       applied", label = "number.sig.tests", align = "lccc"), include.rownames = F, size = "footnotesize")
-@
-
-Here, it is difficult to say if continuous and survival or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and survival outcome type tests have in general more positive findings.
-Very few meta-analyses are significant, irrespective of the test used, but around 67\% of the dataset is not significant, no matter which test is used.
-\\
-When only looking at small study effect tests, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of survival and continuous outcome tests had at least one significant result.
-This also suggests that the overlap between small study effect tests and excess significance is small.
-After applying the Bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\% for binary and \Sexpr{mean.min.else.b}\% for continuous and survival outcomes.
-\\
-To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test.
-\Sexpr{mean.min.bin2}\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, \Sexpr{mean.min.else2}\% for continuous and survival outcomes.
-The numbers change to \Sexpr{mean.min.bin2.b}\% for binary outcomes and \Sexpr{mean.min.else2.b}\% for continuous and survival outcomes after applying the Bonferroni correction.
-\\
-\Sexpr{both.bin}\% have significant Harbord's test result and significant excess significance test result  (\Sexpr{both.bin.b}\% with Bonferroni).
-Of the continuous outcomes, we have \Sexpr{both.else}\% with Egger's test and \Sexpr{both.else.b}\% with Bonferroni correction.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Small Study Effects Adjustment}
-<<echo=FALSE, warning=FALSE, message=FALSE>>=
-#HISTOGRAMS:
-
-#Comparison of treatment effect p-values:
-sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
-                              z.ranef = est.z.ranef/se.est.z.ranef,
-                              z.reg = est.z.reg/se.est.z.reg,
-                              z.copas = est.z.copas/se.est.z.copas) %>%  
-  select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>% 
-  mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>% 
-  group_by(method) %>% 
-  summarise(significant = length(which(abs(fisher.z) > 1.96)),
-            p.significant = significant/length(fisher.z))
-sig.zcor <- data.frame(method = sig.zcor$method,
-                       label = paste(round(sig.zcor$p.significant,3)*100, "% significant", ", (n = ", sig.zcor$significant, ")", sep = ""))
-
-method_names <- c(
-  z.fixef = "Fixed Effects",
-  z.ranef = "Random Effects",
-  z.reg = "Regression",
-  z.copas = "Copas"
-)
-
-adjustment.p.z <- meta.f %>% 
-  mutate(z.fixef = est.z.fixef/se.est.z.fixef,
-         z.ranef = est.z.ranef/se.est.z.ranef,
-         z.reg = est.z.reg/se.est.z.reg,
-         z.copas = est.z.copas/se.est.z.copas) %>%  
-  select(z.fixef, z.ranef, z.reg, z.copas) %>% 
-  gather(key = "method", value = "fisher.z") %>% 
-  mutate(method = factor(method, levels = c("z.fixef", "z.ranef", "z.reg", "z.copas"))) %>% 
-  mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>% 
-  ggplot(aes(x = p.fisher.z)) + 
-  geom_histogram(boundary = 0, bins = 20) + 
-  theme_bw() + 
-  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-  geom_text(data = sig.zcor, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
-  xlab(expression(paste(italic(p),"-value of test statistic of the ", italic(z),"-score"))) +
-  ggtitle(expression(paste(italic(z), " Score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Comparison of SMD's:
-sig.d <- meta.f %>% mutate(d.fixef = est.d.fixef/se.est.d.fixef,
-                           d.ranef = est.d.ranef/se.est.d.ranef,
-                           d.reg = est.d.reg/se.est.d.reg,
-                           d.copas = est.d.copas/se.est.d.copas) %>%  
-  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-  group_by(method) %>% 
-  summarise(significant = length(which(abs(smd) > 1.96)),
-            p.significant = significant/length(smd))
-sig.d <- data.frame(method = sig.d$method,
-                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
-
-method_names <- c(
-  d.fixef = "Fixed Effects",
-  d.ranef = "Random Effects",
-  d.reg = "Regression",
-  d.copas = "Copas"
-)
-
-adjustment.p.d <- meta.f %>% 
-  mutate(d.fixef = est.d.fixef/se.est.d.fixef,
-         d.ranef = est.d.ranef/se.est.d.ranef,
-         d.reg = est.d.reg/se.est.d.reg,
-         d.copas = est.d.copas/se.est.d.copas) %>%  
-  select(d.fixef, d.ranef, d.reg, d.copas) %>% 
-  gather(key = "method", value = "smd") %>% 
-  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
-  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-  ggplot(aes(x = p.smd)) + 
-  geom_histogram(boundary = 0, bins = 20) + 
-  theme_bw() + 
-  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-  geom_text(data = sig.d, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
-  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
-  ggtitle(expression(paste("Hedges ", italic(g), " ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Comparison of log hazard ratios:
-sig.d <- meta.f %>% filter(outcome.type == "surv") %>% 
-  mutate(d.fixef = est.fixef/se.est.fixef,
-         d.ranef = est.ranef/se.est.ranef,
-         d.reg = est.reg/se.est.reg,
-         d.copas = est.copas/se.est.copas) %>%  
-  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-  group_by(method) %>% 
-  summarise(significant = length(which(abs(smd) > 1.96)),
-            p.significant = (significant + sum(is.na(smd)))/(length(smd)))
-sig.d <- data.frame(method = sig.d$method,
-                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
-
-method_names <- c(
-  d.fixef = "Fixed Effects",
-  d.ranef = "Random Effects",
-  d.reg = "Regression",
-  d.copas = "Copas"
-)
-
-adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.type == "surv") %>% 
-  mutate(d.fixef = est.fixef/se.est.fixef,
-         d.ranef = est.ranef/se.est.ranef,
-         d.reg = est.reg/se.est.reg,
-         d.copas = est.copas/se.est.copas) %>%  
-  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
-  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-  ggplot(aes(x = p.smd)) + 
-  geom_histogram(boundary = 0, bins = 20) + 
-  theme_bw() + 
-  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-  geom_text(data = sig.d, aes(x = 0.00003, y = 20, label = label), position = "dodge") + 
-  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
-  ggtitle(expression(paste("Log hazard ratio ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Meta-Analysis and adjusted treatment effect estimate difference:
-
-#Z-score:
-diff.z.fixef <- meta.f %>% 
-  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
-                  copas = est.z.copas, regression = est.z.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
-                           sign(copas) != sign(fixef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
-                                sign(regression) != sign(fixef) ~ -abs(regression)),
-    fixef = abs(fixef),
-    ranef = abs(ranef)) %>% 
-  select(fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
-  mutate(difference = fixef - adjusted.z.score) %>% 
-  filter(difference > -.75 & difference < .75) %>% 
-  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + 
-  xlab(expression(paste("Fixed effects - adjusted ", z, "-score")))
-#--------------------------------------------------------------------------------------------------------------------#
-
-diff.z.ranef <- meta.f %>% 
-  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
-         copas = est.z.copas, regression = est.z.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
-                           sign(copas) != sign(ranef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
-                                sign(regression) != sign(ranef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  select(fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
-  mutate(difference = ranef - adjusted.z.score) %>% 
-  filter(difference > -.75 & difference < .75) %>% 
-  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + 
-  xlab(expression(paste("Random effects - adjusted ", z, "-score")))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#SMD:
-diff.d.fixef <- meta.f %>% 
-  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
-         copas = est.d.copas, regression = est.d.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
-                           sign(copas) != sign(fixef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
-                                sign(regression) != sign(fixef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  select(fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
-  mutate(difference = fixef - adjusted.smd) %>% 
-  filter(difference > -1 & difference < 1) %>% 
-  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + 
-  xlab(expression(paste("Fixed effects - adjusted Hedges ", g)))
-#--------------------------------------------------------------------------------------------------------------------#
-
-diff.d.ranef <- meta.f  %>% 
-  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
-         copas = est.d.copas, regression = est.d.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
-                           sign(copas) != sign(ranef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
-                                sign(regression) != sign(ranef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
-  mutate(difference = ranef - adjusted.smd) %>% 
-  filter(difference > -1 & difference < 1) %>% 
-  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + 
-  xlab(expression(paste("Random effects - adjusted Hedges ", g)))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Log hazard ratios:
-diff.log.hazard.ratio.fixef <- meta.surv %>% 
-  mutate(fixef = est.fixef, ranef = est.ranef,
-         copas = est.copas, regression = est.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
-                           sign(copas) != sign(fixef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
-                                sign(regression) != sign(fixef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
-  ggplot(aes(x = (fixef - adjusted.log.hazard.ratio))) + 
-  geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + xlab("Fixed effects - adjusted log hazard ratio")
-#--------------------------------------------------------------------------------------------------------------------#
-
-diff.log.hazard.ratio.ranef <- meta.surv %>% 
-  mutate(fixef = est.fixef, ranef = est.ranef,
-         copas = est.copas, regression = est.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
-                           sign(copas) != sign(ranef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
-                                sign(regression) != sign(ranef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
-  ggplot(aes(x = (ranef - adjusted.log.hazard.ratio))) + 
-  geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + xlab("Random effects - adjusted log hazard ratio")
-#--------------------------------------------------------------------------------------------------------------------#
-sig.level <- 0.1
-meta.f <- meta.f %>% 
-	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
-				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
-				 begg.test = ifelse(pval.begg < sig.level, 1, 0),
-
-				 tes.d.test = ifelse(pval.d.tes < sig.level, 1, 0),
-
-				 schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
-				 rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
-				 harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
-				 peter.test = ifelse(pval.peter < sig.level, 1, 0))
-
-#Quantile, mean, largerthan and missing table of differences:
+\section{Comparison of Two-sided test and adjustments results} \label{sec:comparison.tests.adjustment}
+<<echo = FALSE, warnings = FALSE>>=
 adjustment.diff.keep <- meta.f %>% 
@@
 
-adjustment.diff.keep <- adjustment.diff.keep %>% 
-  mutate(bias.side = ifelse(est.fixef - est.reg.f > 0, 1, 0), #Decide if effect size declines or increases
+sig.level <- 0.1
+meta.f <- meta.f %>% 
+	mutate(egger.test = ifelse(pval1.egger < sig.level, 1, 0),
+				 thompson.test = ifelse(pval1.thompson < sig.level, 1, 0),
+				 begg.test = ifelse(pval1.begg < sig.level, 1, 0),
 
-         egger.test = ifelse(bias.side == 1, egger.test, 0),
-         thompson.test = ifelse(bias.side == 1, thompson.test, 0),
-         begg.test = ifelse(bias.side == 1, begg.test, 0),
+				 tes.d.test = ifelse(pval1.d.tes < sig.level, 1, 0),
 
-         schwarzer.test = ifelse(bias.side == 1, schwarzer.test, 0),
-         peter.test = ifelse(bias.side == 1, peter.test, 0),
-         rucker.test = ifelse(bias.side == 1, rucker.test, 0),
-         harbord.test = ifelse(bias.side == 1, harbord.test, 0))
+				 schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
+				 rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
+				 harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
+				 peter.test = ifelse(pval1.peter < sig.level, 1, 0))
 
-adjustment.diff <- adjustment.diff.keep %>%
-
-  transmute(copas.z.f = est.z.fixef - est.z.copas.f,
-            copas.z.r = est.z.ranef - est.z.copas.r,
-            reg.z.f = est.z.fixef - est.z.reg.f,
-            reg.z.r = est.z.ranef - est.z.reg.r,
-
-            copas.d.f = est.d.fixef - est.d.copas.f,
-            copas.d.r = est.d.ranef - est.d.copas.r,
-            reg.d.f = est.d.fixef - est.d.reg.f,
-            reg.d.r = est.d.ranef - est.d.reg.r)
-
-m.adjustment.diff <- as.matrix(adjustment.diff)
-
-adjustmend.diff.surv <- meta.surv %>% 
-  transmute(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
-                                    sign(est.copas) != sign(est.fixef) ~ -abs(est.copas)),
-            est.copas.r = case_when(sign(est.copas) == sign(est.ranef) ~  abs(est.copas),
-                                    sign(est.copas) != sign(est.ranef) ~ -abs(est.copas)),
-
-            est.reg.f = case_when(sign(est.reg) == sign(est.fixef) ~  abs(est.reg),
-                                  sign(est.reg) != sign(est.fixef) ~ -abs(est.reg)),
-            est.reg.r = case_when(sign(est.reg) == sign(est.ranef) ~  abs(est.reg),
-                                  sign(est.reg) != sign(est.ranef) ~ -abs(est.reg)),
-
-            est.fixef = abs(est.fixef),
-            est.ranef = abs(est.ranef)) %>%
-
-  transmute(copas.surv.f = est.fixef - est.copas.f,
-            copas.surv.r = est.ranef - est.copas.r,
-
-            reg.surv.f =  est.fixef - est.reg.f,
-            reg.surv.r = est.ranef - est.reg.r)
-
-m.adjustment.diff.surv <- as.matrix(adjustmend.diff.surv)
-
-adjustment.diff.quantile.table <- apply(m.adjustment.diff, 2, 
-                                        FUN = function(column){quantile(x = column, 
-                                                                        probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T)})
-adjustment.diff.mean <- apply(m.adjustment.diff, 2, FUN = function(column) mean(column, na.rm = T))
-adjustment.diff.largerzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
-adjustment.diff.equalzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
-adjustment.diff.largerequalzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
-adjustment.diff.comp.errors <- c(4,4,0,0,0,0,0,0)
-adjustment.diff.noest <- c(sum(meta.f$est.z.copas.na[meta.f$outcome.type != "surv"]), 
-                                sum(meta.f$est.z.copas.na[meta.f$outcome.type != "surv"]),
-                                sum(meta.f$est.z.reg.na[meta.f$outcome.type != "surv"]), 
-                                sum(meta.f$est.z.reg.na[meta.f$outcome.type != "surv"]),
-                                sum(meta.f$est.d.copas.na[meta.f$outcome.type != "surv"]), 
-                                sum(meta.f$est.d.copas.na[meta.f$outcome.type != "surv"]),
-                                sum(meta.f$est.d.reg.na[meta.f$outcome.type != "surv"]), 
-                                sum(meta.f$est.d.reg.na[meta.f$outcome.type != "surv"]))
-adjustment.diff.missing <- (adjustment.diff.comp.errors + adjustment.diff.noest)/apply(m.adjustment.diff, 2, FUN = function(column) length(column))*100
-
-adjustment.diff.table <- rbind(adjustment.diff.quantile.table, mean = adjustment.diff.mean,
-                               equalzero = adjustment.diff.equalzero,
-                               largerequal = adjustment.diff.largerequalzero, larger = adjustment.diff.largerzero,
-                               missing = adjustment.diff.missing)
-
-adjustment.diff.quantile.table.surv <- apply(m.adjustment.diff.surv, 2, 
-                                             FUN = function(column){quantile(x = column, 
-                                                                             probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T)})
-adjustment.diff.mean.surv <- apply(m.adjustment.diff.surv, 2, FUN = function(column) mean(column, na.rm = T))
-adjustment.diff.largerzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
-adjustment.diff.equalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
-adjustment.diff.largerequalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
-adjustment.diff.comp.errors.surv <- c(0,0,0,0)
-adjustment.diff.noest.surv <- c(sum(meta.surv$est.copas.na), sum(meta.surv$est.copas.na),
-                                sum(meta.surv$est.reg.na), sum(meta.surv$est.reg.na))
-adjustment.diff.missing.surv <- ((adjustment.diff.comp.errors.surv + adjustment.diff.noest.surv)/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
-
-adjustment.diff.table.surv <- rbind(adjustment.diff.quantile.table.surv, mean = adjustment.diff.mean.surv,
-                                    equalzero = adjustment.diff.equalzero.surv,
-                                    largerequal = adjustment.diff.largerequalzero.surv, larger = adjustment.diff.largerzero.surv,
-                                    missing = adjustment.diff.missing.surv)
-
-adjustment.diff.table <- cbind(adjustment.diff.table, (adjustment.diff.table.surv))
-
-adjustment.diff.table <- round(t(adjustment.diff.table), 4)
-
-rownames(adjustment.diff.table) <- c(paste("z:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
-                                     paste("g:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
-                                     paste("Log h.r.:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")))
-
-colnames(adjustment.diff.table) <- c(colnames(adjustment.diff.table)[1:6], "= 0 (%)", ">= 0 (%)", "> 0 (%)", "No adj. est. (%)")
-
-#--------------------------------------------------------------------------------------------------------------------#
-#Meta-Analysis and adjusted treatment effect estimate difference, missing values:
-
-#Z-score:
-missing.z.fixef <- meta.f %>% 
-  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
-         copas = est.z.copas, regression = est.z.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
-                           sign(copas) != sign(fixef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
-                                sign(regression) != sign(fixef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  select(meta.id, fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
-  mutate(difference = fixef - adjusted.z.score) %>% 
-  filter(difference < -.75 | difference > .75) %>% 
-  select(meta.id)
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-missing.z.ranef <- meta.f %>% 
-  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
-         copas = est.z.copas, regression = est.z.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
-                           sign(copas) != sign(ranef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
-                                sign(regression) != sign(ranef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  select(meta.id, fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
-  mutate(difference = ranef - adjusted.z.score) %>% 
-  filter(difference < -.75 | difference > .75) %>% 
-  select(meta.id)
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-#SMD:
-missing.d.fixef <- meta.f %>% 
-  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
-         copas = est.d.copas, regression = est.d.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
-                           sign(copas) != sign(fixef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
-                                sign(regression) != sign(fixef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  select(meta.id, fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
-  mutate(difference = fixef - adjusted.smd) %>% 
-  filter(difference < -1 | difference > 1) %>% select(meta.id)
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-missing.d.ranef <- meta.f %>% 
-  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
-         copas = est.d.copas, regression = est.d.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
-                           sign(copas) != sign(ranef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
-                                sign(regression) != sign(ranef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  select(meta.id, fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
-  mutate(difference = ranef - adjusted.smd) %>% 
-  filter(difference < -1 | difference > 1) %>% select(meta.id)
-
-missing.differences <- rbind(missing.z.fixef, missing.z.ranef, missing.d.fixef, missing.d.ranef)
-missing.differences <- missing.differences %>% distinct(meta.id)
-
-missing.differences <- merge(meta.f[,
-        c("meta.id", "file.nr", "comparison.nr", "subgroup.nr",
-          "est.z.ranef", "est.z.fixef", "est.z.copas", "est.z.reg", 
-          "est.d.fixef", "est.d.ranef", "est.d.copas", "est.d.reg")],
-        missing.differences, by = "meta.id")
-
-missing.differences <- round(missing.differences, 2)
-
-missing.differences <- missing.differences %>% mutate(meta.id = as.character(meta.id), file.nr = as.character(meta.id),
-                                                      comparison.nr = as.character(comparison.nr), subgroup.nr = as.character(subgroup.nr))
-
-colnames(missing.differences) <- c("meta.id", "file.nr", "comparison.nr", "subgroup.nr",
-                                   "z fixed", "z random", "z Copas", "z regression",
-                                   "g fixed", "g random", "g Copas", "g regression")
-
-#--------------------------------------------------------------------------------------------------------------------#
-#Tukey mean difference plots for adjustment methods:
-
-adjustment.mean.diff.orig <- meta.f %>% filter(est.copas.na != 1) %>% 
-  mutate(mean = (est.copas + est.reg)/2, 
-         difference = est.copas - est.reg) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + theme(legend.position = "none") +
-  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
-                     values = c("red", "blue")) +
-  ggtitle(expression(paste("Copas adjusted estimate - Regression adjusted estimate (original)" )))
-
-adjustment.mean.diff.z <- meta.f %>% filter(est.z.copas.na != 1) %>% 
-  mutate(mean = (est.z.copas + est.z.reg)/2, 
-         difference = est.z.copas - est.z.reg) %>% filter(mean < 7) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point(size = 0.5) + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + theme(legend.position = "none") +
-  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
-                     values = c("red", "blue")) +
-  ggtitle(expression(paste("Copas adjusted ", italic(z),"-score estimate - Regression adjusted ", italic(z),"-score estimate (original)" )))
-
-adjustment.mean.diff.d <- meta.f %>% filter(est.d.copas.na != 1) %>% 
-  mutate(mean = (est.d.copas + est.d.reg)/2, 
-         difference = est.d.copas - est.d.reg) %>% filter(difference < 7 & mean < 10) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + #theme(legend.position = "bottom") +
-  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
-                     values = c("red", "blue")) + guides(fill=guide_legend(title=NULL)) +
-  ggtitle(expression(paste("Copas adjusted Hedges ", italic(g)," estimate - Regression adjusted Hedges ", italic(g), " estimate (original)" )))
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Missing study number by copas:
-missing.copas.histogram <- meta.f %>% ggplot(aes(x = missing.copas/k)) + geom_histogram(binwidth = 0.05, boundary = 0) + theme_bw() + xlab("Missing study fraction")
-missing.copas.zeros <- length(which(meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)] == 0))
-missing.copas.range.frac <- c(missing.copas.zeros, quantile(x = meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)], c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)],na.rm = T) )
-missing.copas.range.count <- c(missing.copas.zeros, quantile(x = meta.f$missing.copas[!is.na(meta.f$missing.copas)], c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(na.rm = T,meta.f$missing.copas[!is.na(meta.f$missing.copas)]))
-missing.copas.table <- rbind(missing.copas.range.frac, missing.copas.range.count)
-rownames(missing.copas.table) <- c("Missing fraction", "Missing study number")
-colnames(missing.copas.table) <- c("= 0", colnames(missing.copas.table)[2:6], "mean")
-
-@
-
-\subsection{Change in Effect Size after Adjustment} \label{sec:change.size}
-
-Since there's evidence for publication bias when applying small study effect and excess significance tests, we apply small study effect adjustment methods to correct for small study effect tests. \\
-We will see that consequences of adjustment can be; 
-\begin{itemize}
-\item first, the absolute size of the treatment effect can be smaller than the classical meta-analysis treatment effect, which is expected if publication bias
-is the cause for the small study effect.
-\item secondly, the effect can be larger than before in meta-analysis.
-In this case, the small study effect must be not due to publication bias for large effects (``true'' publication bias), but due to bias for small effects (``negative publication bias'').
-\end{itemize}
-
-In section \ref{sec:comparison.tests.adjustment}, it will be followed up on the latter point. For now, we will examine the extent and the frequencies of the two scenarios. \\
-To compare the effects of adjustment between meta-analyses, the outcome measures are transformed to Hedges $g$ (standardized mean differences) and Fisher's $z$-score (see section \ref{sec:transformation.effectsizes} for details).
-The effect of adjustment can additionally be compared to either random or fixed effects meta-analysis.
-\\
-Figure \ref{fig:adjustment.size} displays the difference $\delta$ between the observed meta-analysis pooled treatment effect and the adjusted treatment effect, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
-The absolute value $|\hat{\theta}_M|$ is taken and the sign of $\hat{\theta}_\textrm{Adj.}$ is adjusted accordingly such that all effects are mirrored to one side.
-$\delta > 0$ is equivalent to $\hat{\theta}_\textrm{Adj} < \hat{\theta}_M$, a reduction of the original effect size.
-For better illustration, some very large and very small differences have been omitted in the $z$-score and Hedges $g$ histograms; they are shown in Table \ref{missing.differences}.
-Table \ref{adjustment.difference} shows the quantiles and means for the various differences and additional information.\\
-
-\begin{figure}
-<<echo=FALSE, fig.height = 9, warning=FALSE>>=
-grid.arrange(diff.z.fixef, diff.z.ranef,
-             diff.d.fixef, diff.d.ranef,
-             diff.log.hazard.ratio.fixef, diff.log.hazard.ratio.ranef, ncol = 2)
-@
-\caption{Histogram of the treatment effect differences between meta-analysis and adjusted meta-analysis.
-Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes.
-The bins are centered at zero.}
-\label{fig:adjustment.size}
-\end{figure}
-
-<<echo=FALSE, results='asis'>>=
-print(xtable(adjustment.diff.table, label = "adjustment.difference", caption = "Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects.
-The column with the names ``> 0'' give the percentages of estimates larger than zero or larger or equal zero.
-The column ``No adj.
-est.'' gives the percentage of missing estimates due to non-significant publication bias test (for Copas) and computational errors.
-The row names indicate which outcome measure, meta-analysis method and adjustment method is used.
-Abbreviations are used for z-score (= z) and Hedges g (= g).", align = "lcccccccccr"), include.rownames = T, size = "scriptsize",# sanitize.text.function=function(x){x},
-      # table.placement = "p"
-      )
-@
-
-Adjustment leads most often to reduction of treatment effect estimates, as can be seen by the size of the bins of the right part of the histograms in Figure \ref{fig:adjustment.sue}.
-The difference between the bins on the right and left side of the zero-centered bin is however not very large in general.
-The seeming exception of the Copas selection model in the case with $z$-scores and fixed effects reference requires closer examination: Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
-Thus, when comparing Copas with Fixed effects, we compare most often random effects with fixed effects estimates.
-The effect of adjustment by Copas can therefore only be seen when comparing random effects estimates with fixed effect estimates: we can see in Table \ref{adjustment.difference} that we have, for $z$-score, 18.4\% reduced effect sizes compared to 10.3\% (= 100\% - 89.69\%) increased effect sizes.
-Thus, the Copas selection model also has a larger proportion of reduced effect sizes compared to amplified.\\
-%This resolves the case for the seeming exception and for Hedges $g$'s, 24.4\% and 12.46\% (Table \ref{adjustment.difference}. 
-Also, there are more reduced effect sizes if random effects meta-analysis is used as a reference effect size.
-When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
-\\
-The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} increased by -0.13, fixed effects reference).
-Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or \Sexpr{floor(length(!is.na(meta.f$est.d.reg))*0.05)} meta-analyses (or increased by 0.24).
-
-\subsection{Change in Evidence for Treatment Effects} \label{sec:change.evidence}
-Adjustment for small study effects in meta-analysis will not only provide new effect sizes, but also standard errors thereof.
-Thus, also the evidence for efficacy of a treatment can be obtained, which is usually summarized in a suitable test statistic or $p$-value.
-It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.\\
-The Wald test statistics $p$-value for fixed and random effects meta-analyses and Copas and regression adjusted treatment effects have been calculated.
-They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and log hazard ratios.
-\\
-It can be seen that evidence for a treatment effect decreases after adjusting for publication bias.
-It does so more for Hedge's $g$ compared to $z$-scores, and for regression adjustment compared to Copas selection model.
-%Also, the evidence decreases for random effects meta-analyses compared to fixed effects meta-analyses. 
-In the case of log-hazard ratio adjustment, the adjustment has only negligible impact on the $p$-values. \\
-Also, Copas selection method has a very small impact on the evidence compared to random effects meta-analysis, at least using $z$-scores (again, we should rely on comparisons to random effects meta-analysis to evaluate Copas method).
-\\
-% Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
-%Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted Hedges $g$ and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.
-
-\begin{figure}
-<<echo=FALSE, fig.height = 9, warning=FALSE>>=
-grid.arrange(adjustment.p.z,
-             adjustment.p.d,
-             adjustment.p.log.hazard.ratio, ncol = 1)
-@
-\caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
-The method is indicated in the header, bin width is set to 0.05.
-The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
-\label{fig:adjustment.stat}
-\end{figure}
-
-The Copas selection model also gives an estimate of the number of missing studies.
-It finds that \Sexpr{round(sum(meta.f$missing.Copas, na.rm = T))} are missing, which corresponds to \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% from all \Sexpr{round(sum(meta.f$k))} analysed studies.
-Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
-Note that we have excluded \Sexpr{sum(is.na(meta.f$missing.Copas))} out of \Sexpr{dim(meta.f)[1]}, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
-
-\begin{figure}
-<<echo = FALSE, warning = FALSE>>=
-missing.copas.histogram
-@
-\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ \Sexpr{sum(!is.na(meta.f$missing.Copas))})}
-\label{fig:copas.missing}
-\end{figure}
-
-We can see that in some occasions, the method finds more than half of all studies are missing.
-In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
-The discrepancy between mean and median may indicate that the estimate of \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% missing studies depends somewhat on these extreme cases.
-As can be written of from Table \ref{copas.missing}, 5\%, \ie \Sexpr{round(sum(!is.na(meta.f$missing.Copas))*0.05)} meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for \Sexpr{sum(meta.f$missing.Copas[which(meta.f$missing.Copas >= 17.60)], na.rm = T)}, more than 30\% of missing studies.
-
-<<echo= FALSE, results='asis'>>=
-print(xtable(missing.copas.table, caption = "Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.",
-             label = "copas.missing", align = "lrrrrrrr", digits = c(0,0,0,0,1,1,1,1)),
-      size = "footnotesize")
-@
-
-<<echo=FALSE, results='asis'>>=
-print(xtable(missing.differences, 
-             caption = "Missing meta-analysis pooled treatment effect and adjusted treatment effects.
-Abbreviations are used for z-score (= z) and Hedges g (= g).", label = "missing.differences", align = "llcccrrrrrrrr"),
-      include.rownames = F, size = "tiny")
-@
-
-\subsection{Comparison of adjustment methods}
-Regression adjusted estimates are compared to the estimates of Copas selection model if these are not equal to random effects meta-analysis.
-A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
-We will compare estimates based on all three outcome measures, i.e.
-original measure, $z$-score and Hedges $g$ in Figure \ref{fig:adjustment.mean.diff}.
-Note that the 39 survival outcome data is not included when using $z$-score and Hedges $g$.
-
-\begin{figure}
-<<echo = FALSE, fig.height = 7.5>>=
-grid.arrange(adjustment.mean.diff.orig,
-             adjustment.mean.diff.z,
-             adjustment.mean.diff.d, ncol = 1)
-@
-\caption{Mean - difference plots for publication bias adjustment methods.
-The mean of the adjusted treatment effects is displayed on the $x$-axis and the difference on the $y$-axis.
-Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).
-Two values have been omitted in the middle plot for Hedges $g$ and one for $z$-score (see Table \ref{missing.differences}).}
-\label{fig:adjustment.mean.diff}
-\end{figure}
-
-No formal tests are provided, but the at least there seems to be no clear bias or systematic.
-The limits of agreement in Figure \ref{fig:adjustment.mean.diff} are large.
-We conclude thus that the impact of regression adjustment on the effect sizes is in general not substantially larger than the impact of Copas selection model in the subset of data where the estimate of the Copas selection model is not equal to a random effects estimate.
-\\
-
-\section{Comparison of Tests and Adjustments} \label{sec:comparison.tests.adjustment}
-<<echo = FALSE, warnings = FALSE>>=
 #--------------------------------------------------------------------------------------------------------------------#
@@
                         mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test), mean(meta.bin$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer", "pval.d.tes"),
+  test.type   = c("pval1.harbord", "pval1.peter", "pval1.rucker", "pval1.schwarzer", "pval1.d.tes"),
   bias.side = rep(0, times = 5))
 
-labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer", pval.d.tes = "Excess Significance")
+labels <- c(pval1.harbord = "Harbord", pval1.peter = "Peter", pval1.rucker = "Rucker", pval1.schwarzer = "Schwarzer", pval1.d.tes = "Excess Significance")
 
 p.dist.bin.corrected <- meta.bin  %>% ungroup() %>% 
-  select(bias.side, pval.harbord, pval.peter, pval.rucker, pval.schwarzer, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value", pval.harbord:pval.d.tes) %>% 
+  select(bias.side, pval1.harbord, pval1.peter, pval1.rucker, pval1.schwarzer, pval1.d.tes) %>% 
+  gather(key = "test.type", value = "p.value", pval1.harbord:pval1.d.tes) %>% 
   ggplot(aes(x = p.value, fill = factor(bias.side))) + 
@@
                 round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test), mean(meta.cont$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"),
+  test.type   = c("pval1.begg", "pval1.egger", "pval1.thompson", "pval1.d.tes"),
   bias.side = rep(0, times = 4))
 
-labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp", pval.d.tes = "Excess significance")
+labels <- c(pval1.begg = "Begg Mazumdar", pval1.egger = "Egger", pval1.thompson = "Thompson Sharp", pval1.d.tes = "Excess significance")
 
 p.dist.cont.corrected <- meta.cont %>% ungroup() %>% 
-  select(bias.side, pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value", pval.egger:pval.d.tes) %>% 
+  select(bias.side, pval1.egger, pval1.thompson, pval1.begg, pval1.d.tes) %>% 
+  gather(key = "test.type", value = "p.value", pval1.egger:pval1.d.tes) %>% 
   ggplot(aes(x = p.value, fill = factor(bias.side))) + 
@@
                         mean(meta.surv$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"),
+  test.type   = c("pval1.begg", "pval1.egger", "pval1.thompson", "pval1.d.tes"),
   bias.side = rep("publication bias", times = 4))
@@
   mutate(bias.side = factor(ifelse(bias.side == 1, "publication bias", "negative publication bias"))) %>% 
-  select(bias.side, pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value", pval.egger:pval.d.tes) %>% 
+  select(bias.side, pval1.egger, pval1.thompson, pval1.begg, pval1.d.tes) %>% 
+  gather(key = "test.type", value = "p.value", pval1.egger:pval1.d.tes) %>% 
   ggplot(aes(x = p.value, fill = factor(bias.side))) + 

### 2019-07-02 code/adjustment.plots.R

@@ -1,0 +1,147 @@
+grid.arrange(diff.z.fixef, diff.z.ranef,
+             diff.d.fixef, diff.d.ranef,
+             diff.log.hazard.ratio.fixef, diff.log.hazard.ratio.ranef, ncol = 2)
+
+
+#Plots separated by Method:
+
+
+sig.level <- 0.1
+meta.f <- meta.f %>% rowwise() %>% 
+  mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
+         thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
+         begg.test = ifelse(pval.begg < sig.level, 1, 0),
+         
+         schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
+         rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
+         harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
+         peter.test = ifelse(pval.peter < sig.level, 1, 0),
+         I2 = max(c(0, 1 - (k-1)/Q)),
+         i2f = factor(ifelse(I2 == 0, 1, 0)),
+         se.stat = cut(abs(ifelse(outcome.type == "bin", stat.rucker, stat.thompson)),
+                      breaks =  c(0,1,2, 7)),
+         se.stat.ct = abs(ifelse(outcome.type == "bin", stat.rucker, stat.thompson)))
+
+meta.bin <- meta.f %>% filter(outcome.type == "bin")
+meta.cont <- meta.f %>% filter(outcome.type == "cont")
+meta.surv <- meta.f %>% filter(outcome.type == "surv")
+
+#Meta-Analysis and adjusted treatment effect estimate difference:
+
+#Z-score:
+diff.z.fixef <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(se.stat, fixef, ranef, copas, regression) %>% 
[…]

### 2019-07-02 code/analysis_plots.R

@@ -39,7 +39,7 @@ load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
 ################################################################################################
 
 sig.level <- 0.1
-meta.f <- meta.f %>% 
+meta.f <- meta.f %>% rowwise() %>% 
 	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
 				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
 				 begg.test = ifelse(pval.begg < sig.level, 1, 0),
@@ -47,7 +47,9 @@ meta.f <- meta.f %>%
 				 schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
 				 rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
 				 harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
-				 peter.test = ifelse(pval.peter < sig.level, 1, 0))
+				 peter.test = ifelse(pval.peter < sig.level, 1, 0),
+				 I2 = max(c(0, 1 - (k-1)/Q)),
+				 i2f = factor(ifelse(I2 == 0, 1, 0)))
 
 meta.bin <- meta.f %>% filter(outcome.type == "bin")
 meta.cont <- meta.f %>% filter(outcome.type == "cont")
@@ -80,25 +82,63 @@ meta.surv <- meta.f %>% filter(outcome.type == "surv")
 
 
 
-
 test.bin <- meta.bin %>% ungroup() %>% summarize(
-																								 schwarzer.test = mean(schwarzer.test),
-																								 rucker.test = mean(rucker.test),
-																								 harbord.test = mean(harbord.test),
-																								 peter.test = mean(peter.test))
+  schwarzer.test = mean(schwarzer.test),
+  rucker.test = mean(rucker.test),
+  harbord.test = mean(harbord.test),
+  peter.test = mean(peter.test))
 test.bin <- test.bin %>% gather(key = "test.type", value = "mean")
 
 p.bin <- meta.bin %>% ungroup() %>% 
-	select(schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
-	gather(key = "test.type", value = "null.hypothesis") %>%  
-	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
[…]

### 2019-07-05 report/MSc_Report.tex
adjustments after correction

@@
 % LaTeX file for Chapter 02
+
+\chapter{Methods} \label{ch:methods}
+\section{Introduction and Notation}
+The analysis has already been said to be restricted on clinical or health care interventions.
+The interventions are restricted to comparisons of two treatment arms by some measure of sanity or worsening of health.
+The difference in this measure between the groups is referred to as the treatment effect.
+Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or Hedges $g$, Fisher's z score or Pearsons correlation coefficient.
+\\
+Let us consider a meta-analysis with $n$ study treatment effects ($n > 1$, but typically small).
+A study is indexed by $i$, and it's treatment effect by  $\theta_i$.
+The observed treatment effect is $\hat{\theta}_i$.
+The pooled treatment effect of a meta-analysis will be denoted as $\theta_M$, and consequently, the observed pooled treatment effect as $\hat{\theta}_M$.
+Furthermore, each treatment effect is typically measured with some standard error $\se_i$ and an estimate of $\se_i$ is denoted as $\hat{\se}_i$.
+The $\hat{}$ sign thus indicates if it is an estimate.\\
+For continuous outcomes, let $m_t$ be the mean of the treatment group, $m_c$ the mean of the control group, and equivalently $\textrm{sd}_t$ and $\textrm{sd}_c$ the corresponding standard deviations.
+$n_t$ and $n_c$ are the total number of participants in the groups.
+In the case of binary outcomes, let $e_t$ be the count of events in the treatment arm $e_c$ the count of events in the control group.
+The observed counts in a study $i$ are referred to as $e_{t,i}$ and analogously $e_{c,i}$.
+
+\section{Effect Measures and $p$-values}
+\subsection{Continuous Outcomes}
+For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Hedges $g$) and  a standard error thereof.
+Note that the definition of Hedges $g$ and its standard error $\se$ varies among the literature, the following applies for this report:
+
+\begin{align}
+\se &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}} & g &= \frac{m_t - m_c}{\se} \label{eq:hedges.g}
+\end{align}
+
+The mean difference $\theta$ and its standard error $\se$ can similarly be obtained by
+
+\begin{align}
+\theta &= m_t - m_c & \se &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_t}
+\end{align}
+
+Both estimators take into account that the two groups might have unequal variances.
+A $p$-value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$ test.
+The $t$ statistic is obtained, using $s$ and $g$ from \ref{eq:hedges.g}, by
+
+\begin{align}
+t &= g/(s\sqrt{(1/n_t)+(1/n_c)}) \nonumber
+\end{align}
+and the $p$-value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
+
+\begin{align}
+p &= 2(1-F(\abs{t})) \nonumber
+\end{align}
+
+The t-test is known to be not very reliable if combined sample size is small ($n < 30$), see for example \citet{t.test}.
+
+\subsection{Binary Outcomes}
+Two commonly used effect measures for binary outcome data are risk ratios and odds ratios between treatment and control group. 
+The methods presented here can also be found, for example, in \cite[34]{Intro.meta}.
+Let $\theta$ be the natural logarithm of the odds ratio. $\theta$ and its variance $\se^2$ can be obtained by
+
+\begin{align}
+\theta &= \log(\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}) \nonumber \\
+\se^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
+\end{align}
+
+Plugging in the observed counts will give the corresponding estimates. The logarithm of the risk ratio $\theta$ and its variance $\se^2$ is similarly defined as
+
+\begin{align}
+\theta &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
+\se^2&= 1/e_t + 1/n_t + 1/e_c + 1/e_t \label{eq:risk.ratio.variance}
+\end{align}
+
+Using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$-value, \eg \cite[98]{held2014}.
+\\
+Thus, with $\Phi$ as the cumulative standard normal distribution, we get
+\begin{align}
+p &= 2\cdot(1-\Phi(\abs{\hat{\theta}/\hat{\se}}), \nonumber
+\end{align}
+a $p$-value for the corresponding estimate, which summarizes the evidence against $\hat{\theta}$ being zero (\ie the true risk/odds ratio being 1). \\
+Binary and continuous effect measures can be converted into each other, as described in Section \ref{sec:transformation.effectsizes}.
+
+\subsection{Survival Outcomes}
+Time-to-event data with censoring has to be analyzed by special means.
+One frequently used method to take into account right-censoring is the Cox proportional hazards regression model \citep{Cox}.
+Because the method itself is not applied in this thesis, but only the resulting estimates of the parameters are used, the reader is referred to the extensive literature covering this topic (\eg \citet{Surv}).
+\\
+The so-called hazard ratio estimated by Cox regression is the ratio of the instantaneous risk of experiencing the event between two groups.
+Because it is a maximum likelihood estimator, one can again use its Wald test statistic to test for equal hazards.
+Let $\hat{\theta}$ be an estimate of the log hazard ratio and $\hat{\se}$ an estimate of the standard error of it.
+As before
+\begin{align}
+p &= 2\cdot(1-\phi(\abs{\hat{\theta}/\hat{\se}(\hat{\theta})}) \nonumber
+\end{align}
+will give a $p$-value for the evidence against the null hypothesis.
+
+\section{Fixed and Random Effects Meta-Analysis} \label{sec:meta.analysis}
+The fixed effects meta-analysis estimator of the pooled treatment effect is a mean of the single treatment effect estimators, weighted by their standard errors \citep{fixed.effects.rosenthal}.
+Let $w_i = 1/\se_i^2$ be the weights, and $\theta_M$ be the pooled estimator and $s_M^2$ its variance.
+Then
+
+\begin{align}
+\theta_M &= \frac{\sum_{i = 1}^n w_i \theta_i}{\sum_{i = 1}^n w_i} &
+s_M^2 &= \frac{1}{\sum_{i = 1}^n w_i} \label{eq:fixed.effects}
+\end{align}
+
+This estimator minimizes the variance between the effects.
+An estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and variances $\hat{\theta}_i$ and $\hat{\se}_i^2$.
+The underlying idea is that we assume $\theta_i \sim N(\theta_M, \se_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.
+\\
+The random effects model \citep{whitehead} assumes instead that 
+\begin{align}
+\theta_i \sim N(\mu_i, \se_i^2) &&
+\mu_i \sim N(\theta_M, \tau^2) \label{eq:random.effects} 
+\end{align}
+
+Marginally, we have $\theta_i$ being distributed around a common mean $\theta_M$ with additional variance $\tau^2$:
+
+\begin{align}
+\theta_i \given \mu_i \sim N(\theta_M, \se_i^2 + \tau^2) \nonumber %\label{eq:random.effects.marginal}
+\end{align}
+
+$\tau^2$ is often referred to as a population variance or between-study variance, whereas $\se_i^2$ can be interpreted as sampling error.
+The pooled treatment effect estimate $\theta_M$ of the random effects model and its variance is obtained by replacing the weights $w_i$ in equation \ref{eq:fixed.effects} with $w_i = 1/(\se_i^2 + \tau^2)$.
+\\
+The model is superior to the fixed effects model whenever the standard errors of the treatment effects alone are unlikely to fully account for the entire variability observed between studies.
+Note that as $\tau^2$ increases, each $\theta_i$ will eventually get equal weights, irrespective of it's sampling error $\se_i^2$.\\
+The estimation of $\tau^2$ has been subject to some debate in the statistical literature. Oftentimes, the method of moment estimator of \citet{tau.estimator} is used.
+We use the measure of heterogeneity, $Q$, and divide by $C$ after having subtracted the degrees of freedom $n-1$:
+
+\begin{align}
+Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i}\label{eq:Q.heterogeneity} \\
+\tau^2 &= \max\big(0, \frac{Q - (n-1)}{C}\big) \label{eq:Tau.definition}
+\end{align}
+
+Again, $w_i, \theta_i ...$ have to be replaced by their estimates in order to get an estimate $\hat{\tau}^2$. \\
+The Paule-Mandel estimator \citep{paulemandel} is considered to have most often better properties than the method of moments estimator (\eg \citet{tau.estimator.evaluation}).
+Since we defined $w_i = 1/(\se_i^2 + \tau^2)$, it also holds that
+
+\begin{align}
+w_i \textrm{Var}(\theta_i) &= 1 & \textrm{Var}(\sqrt{w_i}\theta_i) = 1 \nonumber
+\end{align}
+
+For any $w_i$, the variance can be estimated and equated to its expected value:
+
+\begin{align}
+\se^2(w_i\theta_i) &= \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} & \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} = 1 \label{eq:paulemandel}
+\end{align}
+
+$\theta_M$ can be estimated using equation \ref{eq:fixed.effects}, the only problem is to estimate $\tau^2$. It can be obtained through an iterative process, using a newly defined function
+
+\begin{align}
+F(\tau^2) &= \sum_{i = 1}^n w_i(\theta_i - \theta_M)^2 - (n-1) \nonumber
+\end{align}
+
+In view of equation \ref{eq:paulemandel}, $\tau^2$ must be such that $F(\tau^2) = 0$.
+Then, we start with a arbitrary $\tau^2$ and repeatedly add a term $\tau_0^2$ to update $\tau^2$ until $F(\tau^2 + \tau_0^2)$ is close to zero (using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{\theta}_M$).
+Using a truncated Taylor series expansion, one can obtain the partial derivative after $\tau^2$, which is a reasonable choice for $\tau_0^2$.
+\\
+%Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{theta}$, we can update $F(\tau^2)$ and check convergence to zero. \\
+The estimation of $\tau^2$ is accompanied by uncertainty.
+A common procedure is to test if it is there is significant heterogeneity between the studies \cite[109]{Intro.meta}.
+Compute $Q$, as given in \ref{eq:Q.heterogeneity}, based on one of the estimators of $\tau^2$.
+It is assumed that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equally distributed effect sizes.
+Thus, the expected value of $Q$ is $n-1$, and the excess dispersion is $Q - n + 1$.
+The $p$-value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
+= $n-1$.
+\\
+An advantage of the $\tau^2$ is that it is directly linked to the variability in the data.
+Additionally, one can use the $I^2$ statistic to see what portion the between study variance has of the overall variance.
+It is computed as
+
+\begin{align}
+I^2 &= \max\Big(0, 1 - \frac{n-1}{Q}\Big) \nonumber%\label{I2.proportion}
+\end{align}
+
+%Large values for $\hat{I}^2$ are of great importance when analyzing \eg small study effects. \\
+Importantly, all proposed methods above assume normally distributed effect sizes and proper estimates $\hat{\se}$ of the true standard error.
+This assumptions are not met for very small sample sizes and very few event counts.
+Alternatively, the Mantel-Haenszel method for risk and odds ratios (see \eg \citet{mantel.haenszel}) could be used in the latter case.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small Study Effects Tests}
+The tests that will be presented on the following pages are a common way to detect publication bias.
+Importantly, they are however not interpretable directly as evidence for publication bias, but this is left for the discussion chapter.
+The tests are also often referred to as funnel plot asymmetry tests, because of the popularity of a recent test that has been used frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill}.
+However, it is known for some time that the method has disadvantageous properties, therefore, it will not be discussed here, as well as the funnel plot (the radial plot will be used as an alternative).\\
+A test for small study effects will test in some ways if the size of the estimated treatment effect of a study depends on some measure of its size.
+An association between study size and treatment effect size can be interpreted as an artifact of publication bias.
+
+\subsection{Continuous Outcome Tests}
+For a continuous outcomes that are normally distributed, the sample mean and variance are independent of each other \cite[120]{meta.w.R}.
+Thus, the estimated standard errors of treatment effects can be used as a proxy for study size, as they should in principle not be tied to the effect size.
+
+\subsubsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
+\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+A standardized effect size $\theta_i^\star$ can be computed as in \ref{begg.stand.eff}.
+$\se_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \ref{begg.stand.var}, $\theta_M$ being the fixed effects pooled treatment effect (\ref{eq:fixed.effects}.
+
+\begin{align}
+\theta_i^\star &= (\theta_i - \theta_M)/\se_i^{2\star} \label{begg.stand.eff}  \\
+\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2}1 \label{begg.stand.var} 
+\end{align}
+
+A rank correlation test based on Kendall's tau is then used.
+First, the pairs are ordered after their ranks based on $s^{2\star}$.
+Then, for each $s^{2\star}$ rank, the corresponding ranks based on $\theta^{2\star}$ that are larger are counted and summed up to $u$.
+The number of ranks based on $\theta^{2\star}$ that are in contrary, smaller, are counted and summed up to $l$.
+Then the normalized test statistic $Z$ is given as
+
+\begin{align}
+Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \nonumber
+\end{align}
+
+Thus, large number of concordance between pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$.
+The $p$-value is obtained using the standard normal distribution $\Phi$:
+\begin{align}
+p &= 2\cdot(1-\Phi(\abs{Z})) \nonumber
+\end{align}
+
+The changes that have to be made int the case of ties are small and can be found in \cite[410]{begg.ties}.
+
+\subsubsection{Egger's Test: Weighted Linear Regression Test} \label{sec:Egger}
+First, the concept of simple linear regression is introduced. In short, the model assumes a dependent variable $y$ to be a linear function of another explanatory variable $x$:
+
+\begin{align}
+y &= \beta_0 + \beta_1 x + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:simple.regression}
+\end{align}
+
+$\epsilon$ is the residual noise term that becomes necessary when $n$ pairs $(x_i, y_i)$ are given and there is no exact solution.
+Then it is common to look for the solution that minimizes the squared residuals, the least-squares solution.
+Formally,
+
+\begin{align}
+\operatorname*{argmin}_{\beta_0, \beta_1}\big(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i\big) \label{eq:least.squares}
+\end{align}
+
+Let $\mathbf{X}$ be a matrix with the explanatory variables $x$ and $\mathbf{y}$ a corresponding vector for all $y$:
+
+\begin{equation*}
+\mathbf{X} = 
+\begin{bmatrix}
+1 & x_{12} \\
+1 & x_{22} \\
+1 & x_{32} \\
+\vdots & \vdots \\
+1 & x_{n2} \\
+\end{bmatrix} 
+\qquad
+\mathbf{y} = 
+\begin{bmatrix}
+y_1 \\
+y_2 \\
+y_3 \\
+\vdots \\
+y_n \\
+\end{bmatrix}
+\end{equation*}
+
+Let $\mathbf{\beta} = (\beta_0, \beta_1)^\top$. It can be shown that
+
+\begin{align}
+\hat{\mathbf{\beta}} &= (\mathbf{X}^\top \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
+\end{align}
+
+Is an estimator of $\mathbf{\beta}$ that minimizes the squared residuals.
+Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\mathbf{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$.
+The variance estimates $\hat{\sigma}^2$ and $\hat{\mathbf{s}}_\beta^2$ are
+
+\begin{align}
+\hat{\sigma}^2 &= \frac{1}{n-2}\mathbf{r}^\top \hat{\mathbf{r}} & \hat{\mathbf{s}}_\beta^2 &= \hat{\sigma}^2 (\mathbf{X}^\top \mathbf{X})^{-1} \label{eq:regression.variances}
+\end{align}
+
+The estimate $\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the regression line. Furthermore, in the simple linear regression setting, $\hat{\beta}_0$ can also be obtained by:
+
+\begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} &
+\hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \nonumber
+\end{align}
+
+$\bar{x}, \bar{y}$ denoting the sample means of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$. Thus, $\hat{\beta}_0$ is also called global mean.
+To test whether there is evidence for the intercept $\beta_0$ to be unequal to some value $\beta_{H0}$, a $t$-test can be used.
+
+\begin{align}
+p &= 2(1-F(\abs{(\beta_0 - \beta_{H0})/s_{\beta_0}})) \nonumber
+\end{align}
+
+where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. $p$ will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
+The concept is extendable to weighted linear regression.
+Weighted linear regression may be used if the residuals $\mathbf{r}$ have unequal variances, which is equivalent to ascribe different precision to the observed $y$.
+The least squares equation \ref{eq:least.squares} is extended to
+
+\begin{align}
+\operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
+\end{align}
+
+with positive weights $w_i$ that penalize large squared residuals for some $i$ more if $w_i$ is larger compared to other $w_i$. \\
+Let $\mathbf{W}$ be a $n \times n$ matrix with $\mathbf{W}_{ii} = w_i$, the weights on the diagonal and zeros on the off-diagonals.
+The estimates in \ref{eq:regression.parameters} and \ref{eq:regression.variances} can still be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$.
+\label{weighted.regression} \\
+Now it is shown how linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citet{Egger}.
+Let $\theta/s$ be the dependent variable $y$ and $1/\se$ the explanatory variable $x$.
+If plotted, this corresponds to a radial or Galbraith plot \citep{galbraith}.
+The linear regression equation as introduced before in \ref{eq:simple.regression} can be written in two ways:
+
+\begin{align}
+\theta/s &= \beta_0 + \beta_1/\se + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:radial.plot} 
+\end{align}
+
+Equation \eqref{eq:radial.plot} is often provided due to the correspondence to the radial plot. However, it is equivalent to
+
+\begin{align}
+\theta &= \beta_0 + \beta_1 \se + \epsilon, & \epsilon \sim N(0, w^{-1}\sigma^2) \label{eq:egger.plot}
+\end{align}
+
+with weights $w = 1/\se^2$.
+Thus testing $\beta_0$ of \ref{eq:radial.plot} or $\beta_1$ is equivalent.
+The corresponding $p$-value is then used as evidence for a small study effect.
+Plugging in  $\theta_i/\se_i, 1/\se_i$ as $y_i, x_i$ into equation \ref{eq:regression.parameters} and \ref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{\se}_{\beta_0}$ and $\hat{\se}_{\beta_1}$.
+
+% \begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (\varphi_i - \bar{\varphi})(\theta^\star_i - \bar{\theta}^\star)}{\sum_{i = 1}^n (\varphi_i - \bar{\varphi})^2} &
+% \hat{\beta}_0 &= \bar{\theta}^\star - \hat{\beta}_1 \bar{\varphi} \nonumber
+% \end{align}
+
+\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{sec:Thompson}
+A method proposed in \citet{thompson.sharp} allows for between study variance $\tau^2$, as introduced before in section \ref{sec:meta.analysis}.
+It extends the previously seen linear regression approach with $x = 1/\se$ and $y = \theta/s$ by introducing weights.
+The effect size $\theta_i$ is assumed to be distributed as
+
+\begin{align}
+\theta_i \sim N(\beta_0 + \beta_1 \se_i, \se_i^2 + \tau^2) \label{t.sharp.regression}
+\end{align}
+
+$\tau^2$ is estimated as in equation \ref{eq:Tau.definition} (method of moments). %or \ref{eq:paule.mandel}. 
+The weights are set as $w_i = 1/\sqrt{\se_i^2 + \tau^2})$.
+After adjusting for the weights as described in \ref{weighted.regression}, we can proceed analogous to Egger's test.
+The $p$-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
+
+\subsection{Dichotomous Outcomes Tests}
+
+The issue with dichotomous outcomes is that effect size and variance of effect size are correlated, which can readily be seen in \ref{eq:risk.ratio} and \ref{eq:risk.ratio.variance}.
+For example, a small number of event counts in one or group will inflate the variance and the effect size.
+Consequently, the tests above will tend to reject the null-hypothesis too often, \ie report false positives.
+A number of solutions to this problem are provided in the literature.
+
+\subsubsection{Peters Test: Weighted Linear Regression Test} \label{sec:Peter}
+Instead of taking the standard error $s$ as explanatory variable $x$ as in Egger's Test, the inverse of the total sample size is used.
+Additionally, the variances $\se_i^2$ are used as weights.
+Thus, the subsequent test procedure is identical to Egger's test.
+Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
+
+\subsubsection{Harbord's Test: Score based Test} \label{sec:Harbord}
+A rank based alternative to Peters test for binary outcomes is Harbord's test \citep{Harbord}.
+It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated at log odds ratio $\theta_0 = 0$ and its inverse Fisher information $s^2$. Formally,
+
+\begin{align}
+\varphi &= e_t - (e_t - e_c)(e_t + (n_t - e_t))/(n_t + n_c) \label{harbord.score} \\
+ s^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \label{harbord.variance}
+\end{align}
+
+It can be shown that they are both good approximations of the log odds ratio and its variance if the real $\theta$ is not too far from zero.
+The standardized estimator $r_i/v_i$ is also known as Peto odds ratio.
+The obtained scores and variances can be used in Egger's test as treatment effects and variances.
+
+\subsubsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
+\citet{Schwarzer} developed a test for the correlation between $E_t - \mathbb{E}(E_t)$ and the variance of $E_t$, $E_t$ being a random variable from the non-central hypergeometric distribution, assuming a fixed log odds ratio.
+\\
+$\mathbb{E}(E_t)$ and variance of $E_t$ are then estimated based on $e_t$. The standardized cell count deviation 
+\begin{align}
+(e_t - \mathbb{E}(E_t))/\sqrt(\se_i^2)
+\end{align}
+and the inverse of $\se_i^2$ is then used as before in Begg and Mazumdar's test.
+
+\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables} \label{sec:Rucker}
+The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables.
+We use that the arcsine function is the variance stabilizing transformation for a proportion.
+Let
+
+\begin{align}
+\theta_i &= \arcsin{e_t/n_t} - \arcsin{e_c/n_c} \nonumber &
+\se_i^2 &= 1/4n_t + /4n_c \nonumber
+\end{align}
+
+Then one can optionally apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained estimates.
+
+\subsection{Excess Significance Test} \label{sec:excess.significance}
+\citet{excess.significance} developed an exploratory test to detect if the proportion of significant findings is larger than expected.
+Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study.
+\\
+We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated by fixed effects Meta-Analysis \ref{eq:fixed.effects}.
+Let $O$ be the number of significant study results out of $n$ studies and $\alpha$ the significance threshold.
+Corresponding to the study effect $\theta_i$, we can specify the power $1 - \beta_i$, the probability to accepting a true result.
+Let $z_{\alpha,i}$ be the $1-\alpha$ quantile of a normal distribution with standard error $\hat{\se}_i$.
+The power of study $i$ can be estimated as:
+
+\begin{align}
+1 - \hat{\beta}_i &= F(z_\alpha) 
+\end{align}
+
+with $F$ being the cumulative distribution of a normal with mean $\hat{\theta}_M$ and standard deviation $\hat{\se}_i$. \\
+If we assume no bias in $\theta_i$ and $\theta_M$, the expected number of significant study results is then just
+
+\begin{align}
+E &= \sum_{i = 1}^n (1 - \beta_i) \nonumber
+\end{align}
+
+$E$ can then be compared to $O$ by constructing a test statistic $\chi$:
+
+\begin{align}
+\chi  &= \big( \frac{(O - E)^2}{E} + \frac{(O - E)^2}{n - E}\big) \nonumber
+\end{align}
+
+and consecutively, calculating a $p$-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
+Alternatively, one can also use a binomial test, which is encouraged when $n$ and $O$ is small.
+We will get a one sided $p$-value for excess significance, $\P(X \geq O)$, by
+
+\begin{align}
+p &= \sum_{i = O}^n\Big({n \choose i} p^i (1-p)^{n - i}\Big)
+\end{align}
+
+with $p = E/n$ and $X$ being a binomial random variable with probability $p$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small Study Effect and Publication Bias Adjustment}
+There are different approaches to correct for small study effects and publication bias.
+They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinite precision (\ie very small standard error) or to a summary effect, corrected for publication bias.
+Selection models aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:
+
+\subsection{Adjustment by Regression}
+\citet{limitmeta} use a random effects model %together with shrinkage procedure 
+to obtain an unbiased estimate. Similarly to 
+%what has been seen in Copas selection model, we let $y_i$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_i}$ as in \ref{limitmeta.regression}.
+regression based tests for small study effects, we have
+
+\begin{align}
+\theta_i & = \beta_0 + \beta_1\sqrt{\se_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \epsilon_i \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{eq:limitmeta.regression}
+\end{align}
+
+The only difference between Thompson and Sharp's variant is $x = \sqrt{\se^2 + \tau^2}$ instead of $x = \sqrt{\se^2}$.
+$\beta_{1}$ represents the bias introduced by small study effects, as illustrated in the following equations:
+
+\begin{align}
+\mathbb{E}((\theta_i - \beta_0)/\sqrt{\se_i^2}) \rightarrow \beta_1 \textrm{ if } \se_i \rightarrow \infty \nonumber \\ %\label{limitmeta.infinitesample} \\
+\mathbb{E}(theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} \se_i \rightarrow 0 \nonumber
+\end{align}
+
+After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before in the simple linear regression framework. Now we have basically two possible estimates at hand:
+\begin{itemize}
+\item $\beta_0$ the treatment effect without any influence of study precision with standard error $s_{\beta_0}$
+\item $\beta_0 + \beta_1 \tau$ the treatment effect of a hypothetical study with infinite precision, corresponding standard error $s_{\beta_0} + s_{\beta_1}$
+\end{itemize}
+
+Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior with respect to coverage (and mean squared error).
+
+\subsection{Copas Selection Model}
+
+A method proposed in \cite{Copas1,Copas2,Copas3} 
+assumes that the given sample of treatment effects and standard errors is a selected part of a larger random sample.
+Selection of studies depends on their effect size and variance.
+Smaller variance is always accompanied by larger selection probability.
+\\
+Let $\theta_i$ be the effect size estimate of study $i$. Then
+
+\begin{align}
+\theta_i \sim N(\mu_i, \sigma_i^2) &
+\mu_i \sim N(\theta, \tau^2) \label{eq:population.model}
+\end{align}
+
+which is similar to the random-effects meta-analysis setting.
+$\theta$ is the population mean effect, $\sigma_i^2$ the within study variance and $\tau^2$ the between study variance.
+Equations in \ref{eq:population.model} are termed the \textit{population model}.
+\\
+The \textit{selection model} is defined as follows.
+Suppose a selection of studies with reported ($\neq$ estimated) standard errors $s$ (likely different from $\sigma$).
+Only a proportion of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
+Formally,
+
+\begin{align}
+P(\textrm{select}\given s) &= \Phi(a + b/s) \nonumber %\label{copas.selection1}
+\end{align}
+
+The equation can be rewritten as
+
+\begin{align}
+z = a + b/s + \delta \nonumber %\label{copas.selection2}
+\end{align}
+
+with $\delta \sim N(0,1)$.
+$z$ is interpreted as the \textit{propensity for selection}.
+It's sign must be positive in order for the study to be selected.
+Thus, the larger $z$, the more likely the study will be selected.
+Also, $a$ is somewhat like to global retention or selection rate for each study, while $b$ decides about the decline of selection probability with increasing $s$.\\
+So far, we have, for a study $i$
+
+\begin{align}
+\theta_i = \mu_i + \sigma_i\epsilon_i \nonumber \\ 
+\mu_i \sim N(\theta, \tau^2) \nonumber \\
+z_i = a + b/\se_i + \delta_i \nonumber
+\end{align}
+
+where $(\epsilon_i, \delta_i)$ are standard normal residuals.
+The two models are coupled by introducing a correlation $\rho = cor(\theta_i, z_i)$ by defining $(\epsilon_i, \delta_i)$ as bivariate standard normals.
+It follows that,
+%Every given study $i$ in the meta-analysis has $z_i > 0$. 
+if $\rho_i$ is large and positive and $z_i > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_i$ and $\delta_i$ and thus, the true mean $\mu$ is likely to be overestimated.
+\\
+Let $u_i = a + b/\se_i$, $\lambda(u_i)$ the Mill's ratio $\phi(u_i)/\Phi(u_i)$ ($\phi$ is the standard normal density function and $\Phi$ the cdf) and $\tilde{\rho_i} = \sigma/\sqrt(\tau^2 + \sigma_i^2) \rho_i$.
+The probability of a study being selected, given $\se_i$ and $\theta_i$, is
+
+\begin{align}
+P(\textrm{select} \given \se_i, \theta_i) = %P(a,b,s,y) = 
+\Phi\big(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i^2}}}\big) \nonumber
+\end{align}
+
+Which again shows that larger $\se_i$ and $\theta_i$ lead to a larger selection probability. It can also be shown that the expected value
+
+\begin{align}
+\mathbb{E}(\theta_i \given \se_i, \textrm{select}) = \mu + \rho_i\sigma_i\lambda(u_i) \label{eq:copas.expectation}
+\end{align}
+
+which shows that the expected value for a study is larger for larger $\sigma$. \\
+A likelihood for $\theta_i$, conditional on $z>0$ can be formulated to estimate the parameters of the model.
+Regarding $a$ and $b$, there is no way that they can be estimated because the number of missing studies and their effect sizes is not known.
+Instead, fixed values for $a$ and $b$ have to be chosen.
+The nuisance parameter $\sigma_i$ can be replaced by an estimate if the sample size in the studies is large enough. Since
+
+\begin{align}
+\textrm{Var}(\theta_i\given \se_i, z_i > 0) = \sigma_i^2 (1 - c_i^2\rho_i^2) \nonumber
+\end{align}
+
+with $c^2 = \lambda(u_i)(u_i + \lambda(u_i))$, we can replace $\sigma_i^2$ by $\hat{\sigma}_i^2 = \frac{1}{1-c_i^2\rho_i^2}$.
+Although one has to evaluate the likelihood for fixed pairs $(a,b)$, one can compare the fit of the model to evaluate which one is more suitable:
+With equation \ref{eq:copas.expectation}, one can obtain fitted values of $\theta_i$ based on $\se_i$. Also, for two different pairs $(a,b)$, $(a^\star, b^\star)$,
+
+\begin{align}
+\mathbb{E}(\theta_i\given z_i > 0, a^\star, b^\star) - \mathbb{E}(\theta_i\given z_i > 0, a, b) \approx c^\star + \rho(\lambda(a^\star) - \lambda(a))\se_i \nonumber
+\end{align}
+
+and that local departures of $\theta_i$ can be approximated by adding a linear term in $\se_i$ to the expectation of $\theta_i$.
+Thus, to test a pair $(a,b)$, it is sufficient to test $\beta \neq 0$ in
+
+\begin{align}
+\theta_i &= \theta + \beta \se_i + \sigma_i \epsilon_i \nonumber
+\end{align}
+
+with restriction that $\rho \geq 0$.
+To test some pair $(a,b)$ against the scenario with no selection, we set $a^\star = \infty$ (or $\rho = 0$).
+A likelihood ratio test will give a test statistic to test against $H0 =$ no selection:
+
+\begin{align}
+\chi^2 &= 2\cdot(\operatorname*{max1}_{\theta, \tau, \beta}\tilde{L}(\theta, \tau, \beta) - \operatorname*{max}_{\theta, \tau}\tilde{L}(\theta, \tau, 0)) \label{eq:copas.small.study}
+\end{align}
+
+with 
+\begin{align}
+\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta \se_i)^2}{(\tau^2 + \sigma_i^2)}] \nonumber
+\end{align}
+
+$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$-value.
+Note that the test is almost equivalent to Egger's small study effect test with $\tau^2 = 0$.
+Thus, although the copas selection model models publication bias, it is dependent on the small study effects to find the most suitable pair $(a,b)$.
+\\
+If one applies the model to a single meta-analysis, a sensitivity analysis is suggested.
+One can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process.
+Selection models are in general not recommended for inference (\eg \citet{selection.assessment}).
+\citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes. \\
+A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \ref{eq:copas.small.study} is applied.
+If all obtained $p$-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for modelling, and the standard, classical random effects meta-analysis is retained.
+If none of the $p$-values is above the threshold, a wider range of values for $(a,b)$ is used.
+When some $p$-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the least intense underlying selection model is chosen).\\
+Currently, there is no test to detect miss-specifications in the model itself, the authors themselves have argued that a non-parametric test of the residuals would lack power.
+
+\section{Transformation between effect sizes} \label{sec:transformation.effectsizes}
+Assuming that binary outcomes result from a dichotomization of originally continuous random variables, in this case, the logistic distribution, a transformation from typical binary effect measures to Cohen's $d$ can be achieved \cite[47]{Intro.meta}.
+\\
+Let $\theta$ be a log odds ratio and $s$ it's standard error. Cohen's $d$ and it's variance $s_d^2$ is obtained by
+
+\begin{align}
+d &= \theta \frac{\sqrt{3}}{\pi} & s_d^2 =  \se^2\frac{\sqrt{3}}{\pi} \nonumber
+\end{align}
+
+The factor $\frac{\pi}{\sqrt{3}} = 1.81$ is the standard deviation of the logistic distribution $L(\mu, \eta)$ with scale parameter $\eta = 1$, so we just divide the log odds ratio and it's variance through the standard deviation.
+The approximation works only well if $e_t$ and $e_c$ are not very small, especially in the case of $s_d^2$.
+Plugging in the observed log odds ratio $\hat{\theta}$ and $\hat{\se}^2$ will give an estimate of Cohen's $d$.\\
+Pearson's correlation can be attained by the formulas (\citet{olkin1985dtor}, \cite[48]{Intro.meta})
+
+\begin{align}
+r &= \frac{d}{\sqrt{d^2 + a}} & a = (n_c + n_t)^2 / n_c n_t \nonumber
+\end{align}
+where $a$ is a correction factor if $n_t \neq n_c$. The variance of $r$, $s_r^2$ is computed by
+\begin{align}
+s_r^2 &= \frac{a^2 s_d^2}{(d^2 + a)^3} \nonumber
+\end{align}
+
+Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $s_z^2$ by using
+\begin{align}
+z &= 0.5 \ln\big(\frac{1 + r}{1 - r}\big) & \nonumber
+s_z^2 &= \frac{1}{n-3}
+\end{align}
+
+%SIMPLE LINEAR REGRESSION
+% \begin{align}
+% \hat{\mathbf{\beta}} &= (\mathbf{X}^\top  \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
+% \end{align}
+
+% There is a closed form solution for $\hat{\beta_0}, \hat{\beta}_1$ that minimize the sum of squares:
+% 
+% \begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} & 
+% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
+% \end{align}
+% 
+% $\bar{x}, \bar{y}$ denotes the sample mean of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$.
+$\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the fitted line.
+Let $\hat{y}_i = \beta_0 + \beta_1 x_i$ and $e_i = y_i - \hat{y}_i$.
+The variances $\se^2_\beta$
+% 
+% 
+% 
+% To test whether the intercept or the slope is close to a certain value, a $t$-test can be used. Simply taking the absolute value of $\beta_0/s_\beta_0$,
+% \begin{align}
+% p &= 2(1-F(|\beta_0/s_\beta_0|)) \nonumber
+% \end{align}
+% 
+% where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom.
+The $p$-value will give the evidence against the null-hypothesis $\beta_0 = 0$.
+The procedure for $\beta_1$ is equivalent.
+\\
+% To extend the model to weighted simple linear regression is straightforward.
+Let $w_i$ be the corresponding weight that will be attributed to the pair $x_i, y_i$.
+The least squares minimization problem can be restated
+% 
+% \begin{align}
+% \operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
+% \end{align}
+% 
+% And the corresponding estimators are thus
+% 
+% \begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n w_i(x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n w_i(x_i - \bar{x})^2} & 
+% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
+% \end{align}
+%
+
+% LIMITMETa
+% \vspace{0mm}
+% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
+% 
+% \begin{align}
+% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
+% \end{align}
+% 
+% Letting $M \rightarrow \infty$, we obtain:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
+% \end{align}
+% 
+% Note that:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
+% \end{align}
+% 
+% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
+% 
+% \begin{align}
+% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
+% \end{align}
+% 
+% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
+% \end{align}
+% 
+% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
+
+% \section{Basic notation}
+% The notation used here will be used throughout the chapter and exceptions will be noted.
+Let $i$ be the number of a study of a meta analysis with $n$ being the total number of studies.
+$y_{i}$ is then the effect size estimate (usually log odds ratio or mean difference) and $v_{i}$ the variance of the estimate of study $i$.
+$w_{i}$ is used for weights which are defined when necessary, and $\Delta$ usually denotes the summarized or pooled effect estimate of the meta-analysis, and $\eta$ the variance thereof.
+% 
+% \vspace{0mm}
+% In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
+% 
+% 
+% \section{Transformation between effect sizes}
+% Binary and continuous outcome measures can both be transformed into correlations and fishers z-scaled correlations in order to be compared.
+Let $\theta$ be a log odds ratio.
+A standardized mean difference $d$ (also known as Cohen's $d$) is calculated by multiplying $\theta$ with $\sqrt{3}/\pi$.
+The variance of the standardized mean difference is attained as $v_d = v_\theta \sqrt{3}/\pi$.\\
+% We get from a standardized mean difference $d$ to a correlation $r$ by using 
+% \begin{align}
+% r &= \frac{d}{\sqrt{d^2 + a}} \nonumber
+% \end{align}
+% where $a$ is a correction factor if $n_t \neq n_c, a = (n_c + n_t)^2 / n_c n_t$. The variance of $r$ is computed by using 
+% \begin{align}
+% v_r &= v_d
+% \end{align}
+% 
+% Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $v_z$ by using
+% \begin{align}
+% z &= 0.5 \ln(\frac{1 + r}{1 - r}) \nonumber
+% v_z &= \frac{1}{n-3}
+% \end{align}
+% 
+% 
+% 
+% \section{Heterogeneity}
+% In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
+This is called between study variation in contrast to within study variation (noise).
+% 
+% 
+% \vspace{0mm}
+% The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
+Let $w_i$ be the inverse of the variance and $\Delta$ be a summarized effect estimate of your choice as for example a variance-weighted mean \ref{weighted.mean}.
+Then $Q$ can be calculated as in \ref{Q.heterogeneity}
+% 
+% \begin{align}
+% \Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
+% Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
+% \end{align}
+% 
+% Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
+Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
+$1 - F(Q)$ will provide the $p$-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
+% 
+% \vspace{0mm}
+% Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
+For this purpose, $\tau^2$, the variance of true effects, can be calculated.
+$\tau^2$ is on the same scale as the effect size and reflects the absolute amount of dispersion.
+In practice, $\tau^2$ can be smaller than zero, then it is set to zero.
+% 
+% \begin{align}
+% C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
+% \tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
+% \end{align}
+% 
+% The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
+Note that their estimate can differ substantially and consequently also the estimate of the pooled effect size estimate.
+% 
+% \vspace{0mm}
+% To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
+% 
+% \begin{align}
+% I^2 &= (Q - n + 1)/Q \label{I2.proportion}
+% \end{align}
+% 
+% There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
+% 
+% \section{Meta Analysis}
+% There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
+% First the fixed effect meta-analysis will be explained.
+Note that both methods can be used for continuous or dichotomous outcomes.
+For more details about the methods, see chapter 11 and 12 in \citet{metaanalysis}
+% 
+% 
+% \vspace{0mm}
+% Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
+The pooled estimate $\Delta_{f}$ of the fixed effects model is then the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
+The variance $\eta_{f}$ is the reciprocal of the sum of the weights as shown in \ref{reciproce.variance}.
+% 
+% \begin{align}
+% \Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
+% \eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
+% \end{align}
+% 
+% The computation of random effects meta-analysis is more complicated.
+Random effects meta-analysis will give smaller studies with larger variance more weight in the pooled estimate.
+Shortly, the idea is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
+% 
+% \vspace{0mm}
+% The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
+It is used to calculate a new weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
+The variance of $\Delta_{r}$, $\eta_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
+% 
+% \begin{align}
+% v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
+% \Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
+% \eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
+% \end{align}
+% 
+% A $p$-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
+% 
+% \begin{align}
+% Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
+% p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
+% \end{align}
+% 
+% \section{Small Study Effects Tests}
+% One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
+If this is not given, one often speaks of publication bias.
+In fact, there can also be other reasons for this (see discussion section).
+A more appropriate term for the phenomenon is small study effect.
+If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
+% 
+% \subsection{Continuous Outcome Tests}
+% % Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. 
+% % First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
+% 
+% \subsubsection{Begg and Mazumdar: Rank Correlation Test}
+% \citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+% A standardized effect size $y_{i}^\star$ can be computed as in \ref{begg.stand.eff}.
+$v_{i}^\star$ is the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
+$\Delta_{f}$ is the pooled estimate for fixed effect estimate defined in \ref{weighted.mean}.
+% 
+% \begin{align}
+% y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff} \\
+% v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} 
+% \end{align}
+% 
+% A rank correlation test based on Kendall's tau is then used.
+The pairs $(y_{i}^\star, v_{i}^\star)$ that are ranked in the same order are enumerated.
+Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (\eg larger standardized effect size and smaller variance).
+Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
+% 
+% \begin{align}
+% Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
+% \end{align}
+% 
+% The changes in the case of ties are negligible \cite[410]{begg.ties}.
+% 
+% \subsubsection{Egger's Test: Linear Regression Test}
+% Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
+% Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope. 
+% 
+% \vspace{0mm}
+% If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
+The $p$-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
+% 
+% \begin{align}
+% p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
+% \end{align}
+% 
+% \subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{Thompson}
+% A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
+Let $\tau^2$ be equal to \ref{Tau.definition}.
+The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
+% 
+% \begin{align}
+% y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
+% \end{align}
+% 
+% Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
+Analogous to Egger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta_{0} = 0$.
+% 
+% \subsection{Dichotomous Outcomes Tests}
+% 
+% The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
+Consequently, the tests above will tend to reject the null-hypothesis too often, \ie that they are not conservative enough.
+A number of solutions to this problem are existing in the literature.
+% 
+% 
+% \subsubsection{Peters Test: Weighted Linear Regression Test}
+% A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
+% 
+% \vspace{0mm}
+% Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
+% 
+% \begin{align}
+% y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
+% v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
+% \end{align}
+% 
+% and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
+Instead of taking the variance as explanatory or independent variable in regression as in Egger's Test, the inverse of the total sample size $x_{i}$ is used, and the variance $v_{i}$ is used as a weight.
+The subsequent test procedure is then identical to Egger's test.
+% 
+% \vspace{0mm}
+% Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
+% 
+% 
+% \subsubsection{Harbord's Test: Score based Test}
+% A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
+The score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
+% 
+% \begin{align}
+% r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
+% v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
+% \end{align}
+% 
+% Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
+Note that $r_{i}/v_{i}$ is also known as peto odds ratio.
+% 
+% \subsubsection{Schwarzer's Test: Rank Correlation Test}
+% \citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
+$\mathbb{E}(E_{t})$ and variance of $E_{t}$ are then estimated based on $e_{t}$.
+% 
+% \vspace{0mm}
+% The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
+% 
+% \subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
+% The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let 
+% 
+% \begin{align}
+% y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}} \\
+% v_{i} = 1/4n_{t} + +/4n_{c}
+% \end{align}
+% 
+% Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances. 
+% 
+% 
+% \section{Small Study Effect Adjustment}
+% \subsection{Trim and Fill}
+% One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
+It is a nonparametric test based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
+% %If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
+% 
+% \vspace{0mm}
+% The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
+First, $\Delta$ is estimated using a fixed or random effects model.
+Then, the $k$ effect size estimates with the smallest standard errors are trimmed, and $\Delta$ is estimated again.
+The procedure is repeated until $k$ is 0 and the funnel plot is symmetric.
+The total number of missing studies is then mirrored with respect to the final effect size estimate $\Delta$, and $\Delta$ and its standard error is then computed to obtain an unbiased estimate.
+% 
+% \subsection{Copas Selection Model}
+% 
+% A method proposed in \cite{Copas1,Copas2,Copas3} assumes that there is a population of studies of which only a part has been published dependent on the variance and size of their estimated effects.
+Studies with small variance and large effect sizes are more likely to be published than studies with large variance and small effect sizes.
+Note that small effect size means here a treatment effect close to the control effect.
+% 
+% Let $y_i$ be the effect size estimate of study $i$. Then 
+% 
+% \begin{align}
+% y_{i} \sim N(\mu_{i}, \sigma_{i}^2) \\
+% \mu_{i} \sim N(\mu, \tau^2)
+% \end{align}
+% 
+% corresponding to a standard random effects meta-analysis.
+$\mu$ is the overall mean effect, $\sigma_{i}^2$ the within study variance and $\tau^2$ the between study variance.
+This is the \textit{population model}.
+% 
+% \vspace{0mm}
+% The \textit{selection model} is defined as follows. Suppose a selection of studies with reported standard errors $s$ (likely different from $\sigma$). Only a proportion 
+% 
+% \begin{align}
+% P(\textrm{select}|s) &= \Phi(a + b/s) \label{copas.selection1}
+% \end{align}
+% 
+% of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
+\ref{copas.selection1} can be rewritten as
+% 
+% \begin{align}
+% z = a + b/s + \delta \label{copas.selection2}
+% \end{align}
+% 
+% with $\delta \sim N(0,1)$. The study with standard error $s$ is only selected if $z$ is positive. Therefore, the larger $z$, the more likely the study is selected.
+% Combining population and selection model for study $i$, we have 
+% 
+% \begin{align}
+% y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \\
+% \mu_{i} \sim N(\mu, \tau^2) \\
+% z_{i} = a + b/s_{i} + \delta_{i}
+% \end{align}
+% 
+% where $(\epsilon_{i}, \delta_{i})$ are standard normal residuals and jointly normal with correlation $\rho = cor(y_{i}, z_{i})$.
+Every given study $i$ in the meta-analysis has $z_{i} > 0$.
+If $\rho$ is large and positive and $z_{i} > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_{i}$ and $\delta_{i}$.
+Thus, the true mean $\mu$ is likely to be overestimated.
+% 
+% \vspace{0mm}
+% Let $u = a + b/s$, $\lambda(u) = \phi(u)/\Phi(u)$ ($\phi$ is the standard normal density function) and $\tilde{\rho} = \sigma/\sqrt(\tau^2 + \sigma^2) \rho$.
+The probability of a study being selected is
+% 
+% \begin{align}
+% P(\textrm{select}|s, y) = P(a,b,s,y) = \Phi(\frac{u + \tilde{\rho}((y - \mu)/\sqrt(\tau^2 + \sigma^2))}{\sqrt{1 - \tilde{\rho^2}}})
+% \end{align}
+% 
+% It can also be shown that the expected value 
+% 
+% \begin{align}
+% \mathbb{E}(y|s, select) = \mu + \rho\sigma\lambda(u) \label{copas.expectation}
+% \end{align}
+% 
+% which shows that the expected value for a study is larger for larger $\sigma$. 
+% 
+% \vspace{0mm}
+% One can compute a likelihood function based on the distribution of $y$ conditional on $z > 0$.
+The likelihood can be maximized for any given pair $a,b$ (can not be estimated since the number of missing studies is not known), and a maximum likelihood estimate $\hat{\mu}$ for the true mean $\mu$ can be obtained.
+One can then perform a sensitivity analysis.
+First, one looks how $\hat{\mu}$ changes for different values of $a,b$.
+One can then compare the fitted values in \ref{copas.expectation} with the real values.
+To test the fit of the model (while keeping all other parts unchanged), the model can be extended in the following way :
+% 
+% \begin{align}
+% y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
+% \end{align}
+% 
+% If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
+Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
+The $p$-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
+% 
+% \vspace{0mm}
+% To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
+% 
+% \vspace{0mm}
+% In practice, only a range of values for $a,b$ are reasonable.
+For those values, the quantities above can be calculated and illustrated.
+Values for $\mu$ that have $p$-values over a predefined significance threshold can be used for inference of the effect size.
+% 
+% \subsection{Adjustment by Regression}
+% There are multiple ways to adjust for small study effects by regression.
+The general idea is to extrapolate the effect size of a study with a variance of zero based on the given effects and variances.
+% 
+% \citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
+Similarly to what has been seen in Copas selection model, we let $y_{i}$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_{i}}$ as in \ref{limitmeta.regression}.
+% 
+% \begin{align}
+% y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{v_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
+% \end{align}
+% 
+% $\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
+% 
+% \begin{align}
+% \mathbb{E}((y_{i} - \beta_{0})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{ if } \sqrt{v_{i}} \rightarrow \infty \label{limitmeta.infinitesample} \\
+% \mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
+% \end{align}
+% 
+% After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before \eg in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test (see \ref{Thompson}).
+% 
+% \vspace{0mm}
+% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
+% 
+% \begin{align}
+% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
+% \end{align}
+% 
+% Letting $M \rightarrow \infty$, we obtain:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
+% \end{align}
+% 
+% Note that:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
+% \end{align}
+% 
+% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
+% 
+% \begin{align}
+% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
+% \end{align}
+% 
+% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
+% \end{align}
+% 
+% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
+
+% \begin{align} \label{cox reg}
+% P(Y < y|\mathbf{x}) = 1 - exp(-exp(h(y) - (\mathbf{x})^\top\beta)
+% \end{align}
+% 
+% See \cite{hothorn} for further information. It specifies the instantaneous risk of an event at time t to be
+% 
+% \begin{align}
+% \lambda_{0}(t)exp((\mathbf{x})^\top\beta) \nonumber
+% \end{align}
+% 
+% The model is regarded as a semi parametric model since it includes the covariates in a linear fashion but leaves the baseline hazard $\lambda_{0}(t)$ unspecified.
+The factor $exp((\mathbf{x})^\top\beta)$ has the interpretation of a hazard ratio between the reference with $\mathbf{x} = 0$.
+The formal definition of the hazard is
+% 
+% \begin{align}
+% h(t) = \lim_{h \to 0} \frac{P(t < T < t + h| T > t)}{h}
+% \end{align}
+% 
+% 
+% \begin{align} \label{generalized linear model}
+% \mathbf{Y}{_{ij}}|U{_i},\epsilon{_{ij}} = (1,x{_i}^\top)\beta + U{_i} + \epsilon{_{ij}}
+% \end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% LaTeX file for Chapter 03
 
@@
 
-\section{Small Study Effect and Excess of Significance Tests} \label{sec:publication.bias.tests}
+\section{Publication Bias Test Results} \label{sec:publication.bias.tests}
 
@@
 risk ratios, Hedges $g$ or log hazard ratios.
-Different tests are applied depending on the outcome type being binary or continuous and survival.\\
+Different tests are applied depending on the outcome type being binary, continuous or survival.\\
 Thus, multiple tests are applied on the same data.
@@
 The testing method is indicated in the header, bin width is equal to 0.1.
-The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
+The proportion of meta-analyses with signifiant publication bias based on the threshold of 0.1 is displayed inside the figures.}
 \label{fig:test}
@@
 Since there are no small $p$-values for such meta-analyses, one must conclude that there is no excess significance in the dataset.
-The obvious correspondence with the heterogeneity statistic however rather suggests that the test itself is just another was to assess between study heterogeneity.
+The obvious correspondence with the heterogeneity statistic however rather suggests that the test is another way to assess between study heterogeneity.
 Thompson test and R\"ucker's test are designed such that they take into account the between study heterogeneity when assessing small study effects.
-When no heterogeneity is given, Thompsons test results and Eggers test result should be equal, however, the $I^2$ statistic is computed by a more suitable estimator \citep{paulemandel} of $\tau^2$ as the estimator that Thompson and Sharp's test uses (method of moment estimator of \citet{tau.estimator}, which is more conservative by usually finding larger $\tau^2$).
+When no heterogeneity is given, Thompson's test results and Egger's test result should be equal, however, the $I^2$ statistic is computed by a more suitable estimator \citep{paulemandel} of $\tau^2$ as the estimator that Thompson and Sharp's test uses (method of moment estimator of \citet{tau.estimator}, which is more conservative by usually finding larger $\tau^2$).
 In the part of the histogram with $I^2 > 0$, the two tests are more reliable than the remaining tests, while the opposite is expected from simulations \citep{limitmeta} when $I^2 = 0$.\\
@@
 It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects for the same meta-analyses.
-A simple method to check the coincidence of test results is to compare scatterplots and empirical Spearman correlations between the test statistics.
+A simple method to check the consistency of test results is to compare scatterplots and empirical Spearman correlations between the test statistics.
 This is done in Figure \ref{fig:test.agreement}.
@@
 Continuous and survival outcome type tests align more closely than binary outcome tests.
-While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics .\\
+While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics.\\
 Because scatterplots and correlation coefficients can be misleading, also a Tukey mean-difference or Bland-Altman of transformed $p$-values plot is shown for four scenarios in Figure \ref{fig:mean.diff.test}:
@@
 \begin{itemize}
-\item the mean of the differences should be around zero (systematic error) 
+\item the mean of the differences should be around zero (no systematic error) 
 \item the points should scatter independently on the $y$-axis and no general increase or decrease with the mean of the transformed $p$-values should be visible
@@
 -- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- \\
-The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests.
+The confidence intervals from Figure \ref{fig:mean.diff.test} can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests.
 This suggests that correspondence between the tests is not very good in general.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Jul  2 18:53:37 2019
+% Fri Jul  5 16:13:26 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Jul  2 18:53:53 2019
+% Fri Jul  5 16:13:41 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Jul  2 18:53:54 2019
+% Fri Jul  5 16:13:42 2019
 \begin{table}[ht]
@@
 We conclude thus that the impact of regression adjustment on the effect sizes is in general not substantially larger than the impact of Copas selection model in the subset of data where the estimate of the Copas selection model is not equal to a random effects estimate.
-\\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% LaTeX file for Chapter 04
-
-\chapter{Methods} 
-\section{Introduction and Notation}
-The analysis has already been said to be restricted on clinical or health care interventions.
-The interventions are restricted to comparisons of two treatment arms by some measure of sanity or worsening of health.
-The difference in this measure between the groups is referred to as the treatment effect.
-Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or Hedges $g$, Fisher's z score or Pearsons correlation coefficient.
-\\
-Let us consider a meta-analysis with $n$ study treatment effects ($n > 1$, but typically small).
-A study is indexed by $i$, and it's treatment effect by  $\theta_i$.
-The observed treatment effect is $\hat{\theta}_i$.
-The pooled treatment effect of a meta-analysis will be denoted as $\theta_M$, and consequently, the observed pooled treatment effect as $\hat{\theta}_M$.
-Furthermore, each treatment effect is typically measured with some standard error $\se_i$ and an estimate of $\se_i$ is denoted as $\hat{\se}_i$.
-The $\hat{}$ sign thus indicates if it is an estimate.\\
-For continuous outcomes, let $m_t$ be the mean of the treatment group, $m_c$ the mean of the control group, and equivalently $\textrm{sd}_t$ and $\textrm{sd}_c$ the corresponding standard deviations.
-$n_t$ and $n_c$ are the total number of participants in the groups.
-In the case of binary outcomes, let $e_t$ be the count of events in the treatment arm $e_c$ the count of events in the control group.
-The observed counts in a study $i$ are referred to as $e_{t,i}$ and analogously $e_{c,i}$.
-
-\section{Effect Measures and $p$-values}
-\subsection{Continuous Outcomes}
-For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Hedges $g$) and  a standard error thereof.
-Note that the definition of Hedges $g$ and its standard error $\se$ varies among the literature, the following applies for this report:
-
-\begin{align}
-\se &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}} & g &= \frac{m_t - m_c}{\se} \label{eq:hedges.g}
-\end{align}
-
-The mean difference $\theta$ and its standard error $\se$ can similarly be obtained by
-
-\begin{align}
-\theta &= m_t - m_c & \se &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_t}
-\end{align}
-
-Both estimators take into account that the two groups might have unequal variances.
-A $p$-value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$ test.
-The $t$ statistic is obtained, using $s$ and $g$ from \ref{eq:hedges.g}, by
-
-\begin{align}
-t &= g/(s\sqrt{(1/n_t)+(1/n_c)}) \nonumber
-\end{align}
-and the $p$-value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
-
-\begin{align}
-p &= 2(1-F(\abs{t})) \nonumber
-\end{align}
-
-The t-test is known to be not very reliable if combined sample size is small ($n < 30$), see for example \citet{t.test}.
-
-\subsection{Binary Outcomes}
-Two commonly used effect measures for binary outcome data are risk ratios and odds ratios between treatment and control group. 
-The methods presented here can also be found, for example, in \cite[34]{Intro.meta}.
-Let $\theta$ be the natural logarithm of the odds ratio. $\theta$ and its variance $\se^2$ can be obtained by
-
-\begin{align}
-\theta &= \log(\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}) \nonumber \\
-\se^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
-\end{align}
-
-Plugging in the observed counts will give the corresponding estimates. The logarithm of the risk ratio $\theta$ and its variance $\se^2$ is similarly defined as
-
-\begin{align}
-\theta &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
-\se^2&= 1/e_t + 1/n_t + 1/e_c + 1/e_t \label{eq:risk.ratio.variance}
-\end{align}
-
-Using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$-value, \eg \cite[98]{held2014}.
-\\
-Thus, with $\Phi$ as the cumulative standard normal distribution, we get
-\begin{align}
-p &= 2\cdot(1-\Phi(\abs{\hat{\theta}/\hat{\se}}), \nonumber
-\end{align}
-a $p$-value for the corresponding estimate, which summarizes the evidence against $\hat{\theta}$ being zero (\ie the true risk/odds ratio being 1). \\
-Binary and continuous effect measures can be converted into each other, as described in Section \ref{sec:transformation.effectsizes}.
-
-\subsection{Survival Outcomes}
-Time-to-event data with censoring has to be analyzed by special means.
-One frequently used method to take into account right-censoring is the Cox proportional hazards regression model \citep{Cox}.
-Because the method itself is not applied in this thesis, but only the resulting estimates of the parameters are used, the reader is referred to the extensive literature covering this topic (\eg \citet{Surv}).
-\\
-The so-called hazard ratio estimated by Cox regression is the ratio of the instantaneous risk of experiencing the event between two groups.
-Because it is a maximum likelihood estimator, one can again use its Wald test statistic to test for equal hazards.
-Let $\hat{\theta}$ be an estimate of the log hazard ratio and $\hat{\se}$ an estimate of the standard error of it.
-As before
-\begin{align}
-p &= 2\cdot(1-\phi(\abs{\hat{\theta}/\hat{\se}(\hat{\theta})}) \nonumber
-\end{align}
-will give a $p$-value for the evidence against the null hypothesis.
-
-\section{Fixed and Random Effects Meta-Analysis} \label{sec:meta.analysis}
-The fixed effects meta-analysis estimator of the pooled treatment effect is a mean of the single treatment effect estimators, weighted by their standard errors \citep{fixed.effects.rosenthal}.
-Let $w_i = 1/\se_i^2$ be the weights, and $\theta_M$ be the pooled estimator and $s_M^2$ its variance.
-Then
-
-\begin{align}
-\theta_M &= \frac{\sum_{i = 1}^n w_i \theta_i}{\sum_{i = 1}^n w_i} &
-s_M^2 &= \frac{1}{\sum_{i = 1}^n w_i} \label{eq:fixed.effects}
-\end{align}
-
-This estimator minimizes the variance between the effects.
-An estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and variances $\hat{\theta}_i$ and $\hat{\se}_i^2$.
-The underlying idea is that we assume $\theta_i \sim N(\theta_M, \se_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.
-\\
-The random effects model \citep{whitehead} assumes instead that 
-\begin{align}
-\theta_i \sim N(\mu_i, \se_i^2) &&
-\mu_i \sim N(\theta_M, \tau^2) \label{eq:random.effects} 
-\end{align}
-
-Marginally, we have $\theta_i$ being distributed around a common mean $\theta_M$ with additional variance $\tau^2$:
-
-\begin{align}
-\theta_i \given \mu_i \sim N(\theta_M, \se_i^2 + \tau^2) \nonumber %\label{eq:random.effects.marginal}
-\end{align}
-
-$\tau^2$ is often referred to as a population variance or between-study variance, whereas $\se_i^2$ can be interpreted as sampling error.
-The pooled treatment effect estimate $\theta_M$ of the random effects model and its variance is obtained by replacing the weights $w_i$ in equation \ref{eq:fixed.effects} with $w_i = 1/(\se_i^2 + \tau^2)$.
-\\
-The model is superior to the fixed effects model whenever the standard errors of the treatment effects alone are unlikely to fully account for the entire variability observed between studies.
-Note that as $\tau^2$ increases, each $\theta_i$ will eventually get equal weights, irrespective of it's sampling error $\se_i^2$.\\
-The estimation of $\tau^2$ has been subject to some debate in the statistical literature. Oftentimes, the method of moment estimator of \citet{tau.estimator} is used.
-We use the measure of heterogeneity, $Q$, and divide by $C$ after having subtracted the degrees of freedom $n-1$:
-
-\begin{align}
-Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i}\label{eq:Q.heterogeneity} \\
-\tau^2 &= \max\big(0, \frac{Q - (n-1)}{C}\big) \label{eq:Tau.definition}
-\end{align}
-
-Again, $w_i, \theta_i ...$ have to be replaced by their estimates in order to get an estimate $\hat{\tau}^2$. \\
-The Paule-Mandel estimator \citep{paulemandel} is considered to have most often better properties than the method of moments estimator (\eg \citet{tau.estimator.evaluation}).
-Since we defined $w_i = 1/(\se_i^2 + \tau^2)$, it also holds that
-
-\begin{align}
-w_i \textrm{Var}(\theta_i) &= 1 & \textrm{Var}(\sqrt{w_i}\theta_i) = 1 \nonumber
-\end{align}
-
-For any $w_i$, the variance can be estimated and equated to its expected value:
-
-\begin{align}
-\se^2(w_i\theta_i) &= \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} & \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} = 1 \label{eq:paulemandel}
-\end{align}
-
-$\theta_M$ can be estimated using equation \ref{eq:fixed.effects}, the only problem is to estimate $\tau^2$. It can be obtained through an iterative process, using a newly defined function
-
-\begin{align}
-F(\tau^2) &= \sum_{i = 1}^n w_i(\theta_i - \theta_M)^2 - (n-1) \nonumber
-\end{align}
-
-In view of equation \ref{eq:paulemandel}, $\tau^2$ must be such that $F(\tau^2) = 0$.
-Then, we start with a arbitrary $\tau^2$ and repeatedly add a term $\tau_0^2$ to update $\tau^2$ until $F(\tau^2 + \tau_0^2)$ is close to zero (using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{\theta}_M$).
-Using a truncated Taylor series expansion, one can obtain the partial derivative after $\tau^2$, which is a reasonable choice for $\tau_0^2$.
-\\
-%Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{theta}$, we can update $F(\tau^2)$ and check convergence to zero. \\
-The estimation of $\tau^2$ is accompanied by uncertainty.
-A common procedure is to test if it is there is significant heterogeneity between the studies \cite[109]{Intro.meta}.
-Compute $Q$, as given in \ref{eq:Q.heterogeneity}, based on one of the estimators of $\tau^2$.
-It is assumed that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equally distributed effect sizes.
-Thus, the expected value of $Q$ is $n-1$, and the excess dispersion is $Q - n + 1$.
-The $p$-value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
-= $n-1$.
-\\
-An advantage of the $\tau^2$ is that it is directly linked to the variability in the data.
-Additionally, one can use the $I^2$ statistic to see what portion the between study variance has of the overall variance.
-It is computed as
-
-\begin{align}
-I^2 &= \max\big(0, 1 - \frac{n-1}{Q}\big) \nonumber%\label{I2.proportion}
-\end{align}
-
-%Large values for $\hat{I}^2$ are of great importance when analyzing \eg small study effects. \\
-Importantly, all proposed methods above assume normally distributed effect sizes and proper estimates $\hat{\se}$ of the true standard error.
-This assumptions are not met for very small sample sizes and very few event counts.
-Alternatively, the Mantel-Haenszel method for risk and odds ratios (see \eg \citet{mantel.haenszel}) could be used in the latter case.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Small Study Effects Tests}
-The tests that will be presented on the following pages are a common way to detect publication bias.
-Importantly, they are however not interpretable directly as evidence for publication bias, but this is left for the discussion chapter.
-The tests are also often referred to as funnel plot asymmetry tests, because of the popularity of a recent test that has been used frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill}.
-However, it is known for some time that the method has disadvantageous properties, therefore, it will not be discussed here, as well as the funnel plot (the radial plot will be used as an alternative).\\
-A test for small study effects will test in some ways if the size of the estimated treatment effect of a study depends on some measure of its size.
-An association between study size and treatment effect size can be interpreted as an artifact of publication bias.
-
-\subsection{Continuous Outcome Tests}
-For a continuous outcomes that are normally distributed, the sample mean and variance are independent of each other \cite[120]{meta.w.R}.
-Thus, the estimated standard errors of treatment effects can be used as a proxy for study size, as they should in principle not be tied to the effect size.
-
-\subsubsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
-\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
-A standardized effect size $\theta_i^\star$ can be computed as in \ref{begg.stand.eff}.
-$\se_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \ref{begg.stand.var}, $\theta_M$ being the fixed effects pooled treatment effect (\ref{eq:fixed.effects}.
-
-\begin{align}
-\theta_i^\star &= (\theta_i - \theta_M)/\se_i^{2\star} \label{begg.stand.eff}  \\
-\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2}1 \label{begg.stand.var} 
-\end{align}
-
-A rank correlation test based on Kendall's tau is then used.
-First, the pairs are ordered after their ranks based on $s^{2\star}$.
-Then, for each $s^{2\star}$ rank, the corresponding ranks based on $\theta^{2\star}$ that are larger are counted and summed up to $u$.
-The number of ranks based on $\theta^{2\star}$ that are in contrary, smaller, are counted and summed up to $l$.
-Then the normalized test statistic $Z$ is given as
-
-\begin{align}
-Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \nonumber
-\end{align}
-
-Thus, large number of concordance between pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$.
-The $p$-value is obtained using the standard normal distribution $\Phi$:
-\begin{align}
-p &= 2\cdot(1-\Phi(\abs{Z})) \nonumber
-\end{align}
-
-The changes that have to be made int the case of ties are small and can be found in \cite[410]{begg.ties}.
-
-\subsubsection{Egger's Test: Weighted Linear Regression Test} \label{sec:Egger}
-First, the concept of simple linear regression is introduced. In short, the model assumes a dependent variable $y$ to be a linear function of another explanatory variable $x$:
-
-\begin{align}
-y &= \beta_0 + \beta_1 x + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:simple.regression}
-\end{align}
-
-$\epsilon$ is the residual noise term that becomes necessary when $n$ pairs $(x_i, y_i)$ are given and there is no exact solution.
-Then it is common to look for the solution that minimizes the squared residuals, the least-squares solution.
-Formally,
-
-\begin{align}
-\operatorname*{argmin}_{\beta_0, \beta_1}\big(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i\big) \label{eq:least.squares}
-\end{align}
-
-Let $\mathbf{X}$ be a matrix with the explanatory variables $x$ and $\mathbf{y}$ a corresponding vector for all $y$:
-
-\begin{equation*}
-\mathbf{X} = 
-\begin{bmatrix}
-1 & x_{12} \\
-1 & x_{22} \\
-1 & x_{32} \\
-\vdots & \vdots \\
-1 & x_{n2} \\
-\end{bmatrix} 
-\qquad
-\mathbf{y} = 
-\begin{bmatrix}
-y_1 \\
-y_2 \\
-y_3 \\
-\vdots \\
-y_n \\
-\end{bmatrix}
-\end{equation*}
-
-Let $\mathbf{\beta} = (\beta_0, \beta_1)^\top$. It can be shown that
-
-\begin{align}
-\hat{\mathbf{\beta}} &= (\mathbf{X}^\top \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
-\end{align}
-
-Is an estimator of $\mathbf{\beta}$ that minimizes the squared residuals.
-Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\mathbf{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$.
-The variance estimates $\hat{\sigma}^2$ and $\hat{\mathbf{s}}_\beta^2$ are
-
-\begin{align}
-\hat{\sigma}^2 &= \frac{1}{n-2}\mathbf{r}^\top \hat{\mathbf{r}} & \hat{\mathbf{s}}_\beta^2 &= \hat{\sigma}^2 (\mathbf{X}^\top \mathbf{X})^{-1} \label{eq:regression.variances}
-\end{align}
-
-The estimate $\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the regression line. Furthermore, in the simple linear regression setting, $\hat{\beta}_0$ can also be obtained by:
-
-\begin{align}
-% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} &
-\hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \nonumber
-\end{align}
-
-$\bar{x}, \bar{y}$ denoting the sample means of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$. Thus, $\hat{\beta}_0$ is also called global mean.
-To test whether there is evidence for the intercept $\beta_0$ to be unequal to some value $\beta_{H0}$, a $t$-test can be used.
-
-\begin{align}
-p &= 2(1-F(\abs{(\beta_0 - \beta_{H0})/s_{\beta_0}})) \nonumber
-\end{align}
-
-where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. $p$ will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
-The concept is extendable to weighted linear regression.
-Weighted linear regression may be used if the residuals $\mathbf{r}$ have unequal variances, which is equivalent to ascribe different precision to the observed $y$.
-The least squares equation \ref{eq:least.squares} is extended to
-
-\begin{align}
-\operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
-\end{align}
-
-with positive weights $w_i$ that penalize large squared residuals for some $i$ more if $w_i$ is larger compared to other $w_i$. \\
-Let $\mathbf{W}$ be a $n \times n$ matrix with $\mathbf{W}_{ii} = w_i$, the weights on the diagonal and zeros on the off-diagonals.
-The estimates in \ref{eq:regression.parameters} and \ref{eq:regression.variances} can still be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$.
-\label{weighted.regression} \\
-Now it is shown how linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citet{Egger}.
-Let $\theta/s$ be the dependent variable $y$ and $1/\se$ the explanatory variable $x$.
-If plotted, this corresponds to a radial or Galbraith plot \citep{galbraith}.
-The linear regression equation as introduced before in \ref{eq:simple.regression} can be written in two ways:
-
-\begin{align}
-\theta/s &= \beta_0 + \beta_1/\se + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:radial.plot} 
-\end{align}
-
-Equation \eqref{eq:radial.plot} is often provided due to the correspondence to the radial plot. However, it is equivalent to
-
-\begin{align}
-\theta &= \beta_0 + \beta_1 \se + \epsilon, & \epsilon \sim N(0, w^{-1}\sigma^2) \label{eq:egger.plot}
-\end{align}
-
-with weights $w = 1/\se^2$.
-Thus testing $\beta_0$ of \ref{eq:radial.plot} or $\beta_1$ is equivalent.
-The corresponding $p$-value is then used as evidence for a small study effect.
-Plugging in  $\theta_i/\se_i, 1/\se_i$ as $y_i, x_i$ into equation \ref{eq:regression.parameters} and \ref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{\se}_{\beta_0}$ and $\hat{\se}_{\beta_1}$.
-
-% \begin{align}
-% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (\varphi_i - \bar{\varphi})(\theta^\star_i - \bar{\theta}^\star)}{\sum_{i = 1}^n (\varphi_i - \bar{\varphi})^2} &
-% \hat{\beta}_0 &= \bar{\theta}^\star - \hat{\beta}_1 \bar{\varphi} \nonumber
-% \end{align}
-
-\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{sec:Thompson}
-A method proposed in \citet{thompson.sharp} allows for between study variance $\tau^2$, as introduced before in section \ref{sec:meta.analysis}.
-It extends the previously seen linear regression approach with $x = 1/\se$ and $y = \theta/s$ by introducing weights.
-The effect size $\theta_i$ is assumed to be distributed as
-
-\begin{align}
-\theta_i \sim N(\beta_0 + \beta_1 \se_i, \se_i^2 + \tau^2) \label{t.sharp.regression}
-\end{align}
-
-$\tau^2$ is estimated as in equation \ref{eq:Tau.definition} (method of moments). %or \ref{eq:paule.mandel}. 
-The weights are set as $w_i = 1/\sqrt{\se_i^2 + \tau^2})$.
-After adjusting for the weights as described in \ref{weighted.regression}, we can proceed analogous to Egger's test.
-The $p$-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
-
-\subsection{Dichotomous Outcomes Tests}
-
-The issue with dichotomous outcomes is that effect size and variance of effect size are correlated, which can readily be seen in \ref{eq:risk.ratio} and \ref{eq:risk.ratio.variance}.
-For example, a small number of event counts in one or group will inflate the variance and the effect size.
-Consequently, the tests above will tend to reject the null-hypothesis too often, \ie report false positives.
-A number of solutions to this problem are provided in the literature.
-
-\subsubsection{Peters Test: Weighted Linear Regression Test} \label{sec:Peter}
-Instead of taking the standard error $s$ as explanatory variable $x$ as in Egger's Test, the inverse of the total sample size is used.
-Additionally, the variances $\se_i^2$ are used as weights.
-Thus, the subsequent test procedure is identical to Egger's test.
-Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
-
-\subsubsection{Harbord's Test: Score based Test} \label{sec:Harbord}
-A rank based alternative to Peters test for binary outcomes is Harbord's test \citep{Harbord}.
-It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated at log odds ratio $\theta_0 = 0$ and its inverse Fisher information $s^2$. Formally,
-
-\begin{align}
-\varphi &= e_t - (e_t - e_c)(e_t + (n_t - e_t))/(n_t + n_c) \label{harbord.score} \\
- s^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \label{harbord.variance}
-\end{align}
-
-It can be shown that they are both good approximations of the log odds ratio and its variance if the real $\theta$ is not too far from zero.
-The standardized estimator $r_i/v_i$ is also known as Peto odds ratio.
-The obtained scores and variances can be used in Egger's test as treatment effects and variances.
-
-\subsubsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
-\citet{Schwarzer} developed a test for the correlation between $E_t - \mathbb{E}(E_t)$ and the variance of $E_t$, $E_t$ being a random variable from the non-central hypergeometric distribution, assuming a fixed log odds ratio.
-\\
-$\mathbb{E}(E_t)$ and variance of $E_t$ are then estimated based on $e_t$. The standardized cell count deviation 
-\begin{align}
-(e_t - \mathbb{E}(E_t))/\sqrt(\se_i^2)
-\end{align}
-and the inverse of $\se_i^2$ is then used as before in Begg and Mazumdar's test.
-
-\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables} \label{sec:Rucker}
-The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables.
-We use that the arcsine function is the variance stabilizing transformation for a proportion.
-Let
-
-\begin{align}
-\theta_i &= \arcsin{e_t/n_t} - \arcsin{e_c/n_c} \nonumber &
-\se_i^2 &= 1/4n_t + /4n_c \nonumber
-\end{align}
-
-Then one can optionally apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained estimates.
-
-\subsection{Excess Significance Test} \label{sec:excess.significance}
-\citet{excess.significance} developed an exploratory test to detect if the proportion of significant findings is larger than expected.
-Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study.
-\\
-We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated by fixed effects Meta-Analysis \ref{eq:fixed.effects}.
-Let $O$ be the number of significant study results out of $n$ studies and $\alpha$ the significance threshold.
-Corresponding to the study effect $\theta_i$, we can specify the power $1 - \beta_i$, the probability to accepting a true result.
-Let $z_{\alpha,i}$ be the $1-\alpha$ quantile of a normal distribution with standard error $\hat{\se}_i$.
-The power of study $i$ can be estimated as:
-
-\begin{align}
-1 - \hat{\beta}_i &= F(z_\alpha) 
-\end{align}
-
-with $F$ being the cumulative distribution of a normal with mean $\hat{\theta}_M$ and standard deviation $\hat{\se}_i$. \\
-If we assume no bias in $\theta_i$ and $\theta_M$, the expected number of significant study results is then just
-
-\begin{align}
-E &= \sum_{i = 1}^n (1 - \beta_i) \nonumber
-\end{align}
-
-$E$ can then be compared to $O$ by constructing a test statistic $\chi$:
-
-\begin{align}
-\chi  &= \big( \frac{(O - E)^2}{E} + \frac{(O - E)^2}{n - E}\big) \nonumber
-\end{align}
-
-and consecutively, calculating a $p$-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
-Alternatively, one can also use a binomial test, which is encouraged when $n$ and $O$ is small.
-We will get a one sided $p$-value for excess significance, $\P(X \geq O)$, by
-
-\begin{align}
-p &= \sum_{i = O}^n\Big({n \choose i} p^i (1-p)^{n - i}\Big)
-\end{align}
-
-with $p = E/n$ and $X$ being a binomial random variable with probability $p$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Small Study Effect and Publication Bias Adjustment}
-There are different approaches to correct for small study effects and publication bias.
-They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinite precision (\ie very small standard error) or to a summary effect, corrected for publication bias.
-Selection models aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:
-
-\subsection{Adjustment by Regression}
-\citet{limitmeta} use a random effects model %together with shrinkage procedure 
-to obtain an unbiased estimate. Similarly to 
-%what has been seen in Copas selection model, we let $y_i$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_i}$ as in \ref{limitmeta.regression}.
-regression based tests for small study effects, we have
-
-\begin{align}
-\theta_i & = \beta_0 + \beta_1\sqrt{\se_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \epsilon_i \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{eq:limitmeta.regression}
-\end{align}
-
-The only difference between Thompson and Sharp's variant is $x = \sqrt{\se^2 + \tau^2}$ instead of $x = \sqrt{\se^2}$.
-$\beta_{1}$ represents the bias introduced by small study effects, as illustrated in the following equations:
-
-\begin{align}
-\mathbb{E}((\theta_i - \beta_0)/\sqrt{\se_i^2}) \rightarrow \beta_1 \textrm{ if } \se_i \rightarrow \infty \nonumber \\ %\label{limitmeta.infinitesample} \\
-\mathbb{E}(theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} \se_i \rightarrow 0 \nonumber
-\end{align}
-
-After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before in the simple linear regression framework. Now we have basically two possible estimates at hand:
-\begin{itemize}
-\item $\beta_0$ the treatment effect without any influence of study precision with standard error $s_{\beta_0}$
-\item $\beta_0 + \beta_1 \tau$ the treatment effect of a hypothetical study with infinite precision, corresponding standard error $s_{\beta_0} + s_{\beta_1}$
-\end{itemize}
-
-Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior with respect to coverage (and mean squared error).
-
-\subsection{Copas Selection Model}
-
-A method proposed in \cite{Copas1,Copas2,Copas3} 
-assumes that the given sample of treatment effects and standard errors is a selected part of a larger random sample.
-Selection of studies depends on their effect size and variance.
-Smaller variance is always accompanied by larger selection probability.
-\\
-Let $\theta_i$ be the effect size estimate of study $i$. Then
-
-\begin{align}
-\theta_i \sim N(\mu_i, \sigma_i^2) &
-\mu_i \sim N(\theta, \tau^2) \label{eq:population.model}
-\end{align}
-
-which is similar to the random-effects meta-analysis setting.
-$\theta$ is the population mean effect, $\sigma_i^2$ the within study variance and $\tau^2$ the between study variance.
-Equations in \ref{eq:population.model} are termed the \textit{population model}.
-\\
-The \textit{selection model} is defined as follows.
-Suppose a selection of studies with reported ($\neq$ estimated) standard errors $s$ (likely different from $\sigma$).
-Only a proportion of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
-Formally,
-
-\begin{align}
-P(\textrm{select}\given s) &= \Phi(a + b/s) \nonumber %\label{copas.selection1}
-\end{align}
-
-The equation can be rewritten as
-
-\begin{align}
-z = a + b/s + \delta \nonumber %\label{copas.selection2}
-\end{align}
-
-with $\delta \sim N(0,1)$.
-$z$ is interpreted as the \textit{propensity for selection}.
-It's sign must be positive in order for the study to be selected.
-Thus, the larger $z$, the more likely the study will be selected.
-Also, $a$ is somewhat like to global retention or selection rate for each study, while $b$ decides about the decline of selection probability with increasing $s$.\\
-So far, we have, for a study $i$
-
-\begin{align}
-\theta_i = \mu_i + \sigma_i\epsilon_i \nonumber \\ 
-\mu_i \sim N(\theta, \tau^2) \nonumber \\
-z_i = a + b/\se_i + \delta_i \nonumber
-\end{align}
-
-where $(\epsilon_i, \delta_i)$ are standard normal residuals.
-The two models are coupled by introducing a correlation $\rho = cor(\theta_i, z_i)$ by defining $(\epsilon_i, \delta_i)$ as bivariate standard normals.
-It follows that,
-%Every given study $i$ in the meta-analysis has $z_i > 0$. 
-if $\rho_i$ is large and positive and $z_i > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_i$ and $\delta_i$ and thus, the true mean $\mu$ is likely to be overestimated.
-\\
-Let $u_i = a + b/\se_i$, $\lambda(u_i)$ the Mill's ratio $\phi(u_i)/\Phi(u_i)$ ($\phi$ is the standard normal density function and $\Phi$ the cdf) and $\tilde{\rho_i} = \sigma/\sqrt(\tau^2 + \sigma_i^2) \rho_i$.
-The probability of a study being selected, given $\se_i$ and $\theta_i$, is
-
-\begin{align}
-P(\textrm{select} \given \se_i, \theta_i) = %P(a,b,s,y) = 
-\Phi\big(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i^2}}}\big) \nonumber
-\end{align}
-
-Which again shows that larger $\se_i$ and $\theta_i$ lead to a larger selection probability. It can also be shown that the expected value
-
-\begin{align}
-\mathbb{E}(\theta_i \given \se_i, \textrm{select}) = \mu + \rho_i\sigma_i\lambda(u_i) \label{eq:copas.expectation}
-\end{align}
-
-which shows that the expected value for a study is larger for larger $\sigma$. \\
-A likelihood for $\theta_i$, conditional on $z>0$ can be formulated to estimate the parameters of the model.
-Regarding $a$ and $b$, there is no way that they can be estimated because the number of missing studies and their effect sizes is not known.
-Instead, fixed values for $a$ and $b$ have to be chosen.
-The nuisance parameter $\sigma_i$ can be replaced by an estimate if the sample size in the studies is large enough. Since
-
-\begin{align}
-\textrm{Var}(\theta_i\given \se_i, z_i > 0) = \sigma_i^2 (1 - c_i^2\rho_i^2) \nonumber
-\end{align}
-
-with $c^2 = \lambda(u_i)(u_i + \lambda(u_i))$, we can replace $\sigma_i^2$ by $\hat{\sigma}_i^2 = \frac{1}{1-c_i^2\rho_i^2}$.
-Although one has to evaluate the likelihood for fixed pairs $(a,b)$, one can compare the fit of the model to evaluate which one is more suitable:
-With equation \ref{eq:copas.expectation}, one can obtain fitted values of $\theta_i$ based on $\se_i$. Also, for two different pairs $(a,b)$, $(a^\star, b^\star)$,
-
-\begin{align}
-\mathbb{E}(\theta_i\given z_i > 0, a^\star, b^\star) - \mathbb{E}(\theta_i\given z_i > 0, a, b) \approx c^\star + \rho(\lambda(a^\star) - \lambda(a))\se_i \nonumber
-\end{align}
-
-and that local departures of $\theta_i$ can be approximated by adding a linear term in $\se_i$ to the expectation of $\theta_i$.
-Thus, to test a pair $(a,b)$, it is sufficient to test $\beta \neq 0$ in
-
-\begin{align}
-\theta_i &= \theta + \beta \se_i + \sigma_i \epsilon_i \nonumber
-\end{align}
-
-with restriction that $\rho \geq 0$.
-To test some pair $(a,b)$ against the scenario with no selection, we set $a^\star = \infty$ (or $\rho = 0$).
-A likelihood ratio test will give a test statistic to test against $H0 =$ no selection:
-
-\begin{align}
-\chi^2 &= 2\cdot(\operatorname*{max1}_{\theta, \tau, \beta}\tilde{L}(\theta, \tau, \beta) - \operatorname*{max}_{\theta, \tau}\tilde{L}(\theta, \tau, 0)) \label{eq:copas.small.study}
-\end{align}
-
-with 
-\begin{align}
-\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta \se_i)^2}{(\tau^2 + \sigma_i^2)}] \nonumber
-\end{align}
-
-$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$-value.
-Note that the test is almost equivalent to Egger's small study effect test with $\tau^2 = 0$.
-Thus, although the copas selection model models publication bias, it is dependent on the small study effects to find the most suitable pair $(a,b)$.
-\\
-If one applies the model to a single meta-analysis, a sensitivity analysis is suggested.
-One can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process.
-Selection models are in general not recommended for inference (\eg \citet{selection.assessment}).
-\citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes. \\
-A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \ref{eq:copas.small.study} is applied.
-If all obtained $p$-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for modelling, and the standard, classical random effects meta-analysis is retained.
-If none of the $p$-values is above the threshold, a wider range of values for $(a,b)$ is used.
-When some $p$-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the least intense underlying selection model is chosen).\\
-Currently, there is no test to detect miss-specifications in the model itself, the authors themselves have argued that a non-parametric test of the residuals would lack power.
-
-\section{Transformation between effect sizes} \label{sec:transformation.effectsizes}
-Assuming that binary outcomes result from a dichotomization of originally continuous random variables, in this case, the logistic distribution, a transformation from typical binary effect measures to Cohen's $d$ can be achieved \cite[47]{Intro.meta}.
-\\
-Let $\theta$ be a log odds ratio and $s$ it's standard error. Cohen's $d$ and it's variance $s_d^2$ is obtained by
-
-\begin{align}
-d &= \theta \frac{\sqrt{3}}{\pi} & s_d^2 =  \se^2\frac{\sqrt{3}}{\pi} \nonumber
-\end{align}
-
-The factor $\frac{\pi}{\sqrt{3}} = 1.81$ is the standard deviation of the logistic distribution $L(\mu, \eta)$ with scale parameter $\eta = 1$, so we just divide the log odds ratio and it's variance through the standard deviation.
-The approximation works only well if $e_t$ and $e_c$ are not very small, especially in the case of $s_d^2$.
-Plugging in the observed log odds ratio $\hat{\theta}$ and $\hat{\se}^2$ will give an estimate of Cohen's $d$.\\
-Pearson's correlation can be attained by the formulas (\citet{olkin1985dtor}, \cite[48]{Intro.meta})
-
-\begin{align}
-r &= \frac{d}{\sqrt{d^2 + a}} & a = (n_c + n_t)^2 / n_c n_t \nonumber
-\end{align}
-where $a$ is a correction factor if $n_t \neq n_c$. The variance of $r$, $s_r^2$ is computed by
-\begin{align}
-s_r^2 &= \frac{a^2 s_d^2}{(d^2 + a)^3} \nonumber
-\end{align}
-
-Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $s_z^2$ by using
-\begin{align}
-z &= 0.5 \ln\big(\frac{1 + r}{1 - r}\big) & \nonumber
-s_z^2 &= \frac{1}{n-3}
-\end{align}
-
-%SIMPLE LINEAR REGRESSION
-% \begin{align}
-% \hat{\mathbf{\beta}} &= (\mathbf{X}^\top  \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
-% \end{align}
-
-% There is a closed form solution for $\hat{\beta_0}, \hat{\beta}_1$ that minimize the sum of squares:
-% 
-% \begin{align}
-% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} & 
-% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
-% \end{align}
-% 
-% $\bar{x}, \bar{y}$ denotes the sample mean of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$.
-$\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the fitted line.
-Let $\hat{y}_i = \beta_0 + \beta_1 x_i$ and $e_i = y_i - \hat{y}_i$.
-The variances $\se^2_\beta$
-% 
-% 
-% 
-% To test whether the intercept or the slope is close to a certain value, a $t$-test can be used. Simply taking the absolute value of $\beta_0/s_\beta_0$,
-% \begin{align}
-% p &= 2(1-F(|\beta_0/s_\beta_0|)) \nonumber
-% \end{align}
-% 
-% where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom.
-The $p$-value will give the evidence against the null-hypothesis $\beta_0 = 0$.
-The procedure for $\beta_1$ is equivalent.
-\\
-% To extend the model to weighted simple linear regression is straightforward.
-Let $w_i$ be the corresponding weight that will be attributed to the pair $x_i, y_i$.
-The least squares minimization problem can be restated
-% 
-% \begin{align}
-% \operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
-% \end{align}
-% 
-% And the corresponding estimators are thus
-% 
-% \begin{align}
-% \hat{\beta_1} &= \frac{\sum_{i = 1}^n w_i(x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n w_i(x_i - \bar{x})^2} & 
-% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
-% \end{align}
-%
-
-% LIMITMETa
-% \vspace{0mm}
-% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
-% 
-% \begin{align}
-% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
-% \end{align}
-% 
-% Letting $M \rightarrow \infty$, we obtain:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
-% \end{align}
-% 
-% Note that:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
-% \end{align}
-% 
-% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
-% 
-% \begin{align}
-% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
-% \end{align}
-% 
-% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-% \end{align}
-% 
-% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
-
-% \section{Basic notation}
-% The notation used here will be used throughout the chapter and exceptions will be noted.
-Let $i$ be the number of a study of a meta analysis with $n$ being the total number of studies.
-$y_{i}$ is then the effect size estimate (usually log odds ratio or mean difference) and $v_{i}$ the variance of the estimate of study $i$.
-$w_{i}$ is used for weights which are defined when necessary, and $\Delta$ usually denotes the summarized or pooled effect estimate of the meta-analysis, and $\eta$ the variance thereof.
-% 
-% \vspace{0mm}
-% In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
-% 
-% 
-% \section{Transformation between effect sizes}
-% Binary and continuous outcome measures can both be transformed into correlations and fishers z-scaled correlations in order to be compared.
-Let $\theta$ be a log odds ratio.
-A standardized mean difference $d$ (also known as Cohen's $d$) is calculated by multiplying $\theta$ with $\sqrt{3}/\pi$.
-The variance of the standardized mean difference is attained as $v_d = v_\theta \sqrt{3}/\pi$.\\
-% We get from a standardized mean difference $d$ to a correlation $r$ by using 
-% \begin{align}
-% r &= \frac{d}{\sqrt{d^2 + a}} \nonumber
-% \end{align}
-% where $a$ is a correction factor if $n_t \neq n_c, a = (n_c + n_t)^2 / n_c n_t$. The variance of $r$ is computed by using 
-% \begin{align}
-% v_r &= v_d
-% \end{align}
-% 
-% Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $v_z$ by using
-% \begin{align}
-% z &= 0.5 \ln(\frac{1 + r}{1 - r}) \nonumber
-% v_z &= \frac{1}{n-3}
-% \end{align}
-% 
-% 
-% 
-% \section{Heterogeneity}
-% In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
-This is called between study variation in contrast to within study variation (noise).
-% 
-% 
-% \vspace{0mm}
-% The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
-Let $w_i$ be the inverse of the variance and $\Delta$ be a summarized effect estimate of your choice as for example a variance-weighted mean \ref{weighted.mean}.
-Then $Q$ can be calculated as in \ref{Q.heterogeneity}
-% 
-% \begin{align}
-% \Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-% Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
-% \end{align}
-% 
-% Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
-Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
-$1 - F(Q)$ will provide the $p$-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
-% 
-% \vspace{0mm}
-% Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
-For this purpose, $\tau^2$, the variance of true effects, can be calculated.
-$\tau^2$ is on the same scale as the effect size and reflects the absolute amount of dispersion.
-In practice, $\tau^2$ can be smaller than zero, then it is set to zero.
-% 
-% \begin{align}
-% C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
-% \tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
-% \end{align}
-% 
-% The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
-Note that their estimate can differ substantially and consequently also the estimate of the pooled effect size estimate.
-% 
-% \vspace{0mm}
-% To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
-% 
-% \begin{align}
-% I^2 &= (Q - n + 1)/Q \label{I2.proportion}
-% \end{align}
-% 
-% There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
-% 
-% \section{Meta Analysis}
-% There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
-% First the fixed effect meta-analysis will be explained.
-Note that both methods can be used for continuous or dichotomous outcomes.
-For more details about the methods, see chapter 11 and 12 in \citet{metaanalysis}
-% 
-% 
-% \vspace{0mm}
-% Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
-The pooled estimate $\Delta_{f}$ of the fixed effects model is then the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
-The variance $\eta_{f}$ is the reciprocal of the sum of the weights as shown in \ref{reciproce.variance}.
-% 
-% \begin{align}
-% \Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-% \eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
-% \end{align}
-% 
-% The computation of random effects meta-analysis is more complicated.
-Random effects meta-analysis will give smaller studies with larger variance more weight in the pooled estimate.
-Shortly, the idea is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
-% 
-% \vspace{0mm}
-% The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
-It is used to calculate a new weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
-The variance of $\Delta_{r}$, $\eta_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
-% 
-% \begin{align}
-% v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
-% \Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
-% \eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
-% \end{align}
-% 
-% A $p$-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
-% 
-% \begin{align}
-% Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
-% p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
-% \end{align}
-% 
-% \section{Small Study Effects Tests}
-% One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
-If this is not given, one often speaks of publication bias.
-In fact, there can also be other reasons for this (see discussion section).
-A more appropriate term for the phenomenon is small study effect.
-If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
-% 
-% \subsection{Continuous Outcome Tests}
-% % Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. 
-% % First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
-% 
-% \subsubsection{Begg and Mazumdar: Rank Correlation Test}
-% \citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
-% A standardized effect size $y_{i}^\star$ can be computed as in \ref{begg.stand.eff}.
-$v_{i}^\star$ is the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
-$\Delta_{f}$ is the pooled estimate for fixed effect estimate defined in \ref{weighted.mean}.
-% 
-% \begin{align}
-% y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff} \\
-% v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} 
-% \end{align}
-% 
-% A rank correlation test based on Kendall's tau is then used.
-The pairs $(y_{i}^\star, v_{i}^\star)$ that are ranked in the same order are enumerated.
-Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (\eg larger standardized effect size and smaller variance).
-Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
-% 
-% \begin{align}
-% Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
-% \end{align}
-% 
-% The changes in the case of ties are negligible \cite[410]{begg.ties}.
-% 
-% \subsubsection{Egger's Test: Linear Regression Test}
-% Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
-% Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope. 
-% 
-% \vspace{0mm}
-% If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
-The $p$-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
-% 
-% \begin{align}
-% p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
-% \end{align}
-% 
-% \subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{Thompson}
-% A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
-Let $\tau^2$ be equal to \ref{Tau.definition}.
-The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
-% 
-% \begin{align}
-% y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
-% \end{align}
-% 
-% Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
-Analogous to Egger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta_{0} = 0$.
-% 
-% \subsection{Dichotomous Outcomes Tests}
-% 
-% The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
-Consequently, the tests above will tend to reject the null-hypothesis too often, \ie that they are not conservative enough.
-A number of solutions to this problem are existing in the literature.
-% 
-% 
-% \subsubsection{Peters Test: Weighted Linear Regression Test}
-% A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
-% 
-% \vspace{0mm}
-% Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
-% 
-% \begin{align}
-% y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
-% v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
-% \end{align}
-% 
-% and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
-Instead of taking the variance as explanatory or independent variable in regression as in Egger's Test, the inverse of the total sample size $x_{i}$ is used, and the variance $v_{i}$ is used as a weight.
-The subsequent test procedure is then identical to Egger's test.
-% 
-% \vspace{0mm}
-% Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
-% 
-% 
-% \subsubsection{Harbord's Test: Score based Test}
-% A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
-The score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
-% 
-% \begin{align}
-% r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
-% v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
-% \end{align}
-% 
-% Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
-Note that $r_{i}/v_{i}$ is also known as peto odds ratio.
-% 
-% \subsubsection{Schwarzer's Test: Rank Correlation Test}
-% \citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
-$\mathbb{E}(E_{t})$ and variance of $E_{t}$ are then estimated based on $e_{t}$.
-% 
-% \vspace{0mm}
-% The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
-% 
-% \subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
-% The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let 
-% 
-% \begin{align}
-% y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}} \\
-% v_{i} = 1/4n_{t} + +/4n_{c}
-% \end{align}
-% 
-% Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances. 
-% 
-% 
-% \section{Small Study Effect Adjustment}
-% \subsection{Trim and Fill}
-% One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
-It is a nonparametric test based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
-% %If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
-% 
-% \vspace{0mm}
-% The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
-First, $\Delta$ is estimated using a fixed or random effects model.
-Then, the $k$ effect size estimates with the smallest standard errors are trimmed, and $\Delta$ is estimated again.
-The procedure is repeated until $k$ is 0 and the funnel plot is symmetric.
-The total number of missing studies is then mirrored with respect to the final effect size estimate $\Delta$, and $\Delta$ and its standard error is then computed to obtain an unbiased estimate.
-% 
-% \subsection{Copas Selection Model}
-% 
-% A method proposed in \cite{Copas1,Copas2,Copas3} assumes that there is a population of studies of which only a part has been published dependent on the variance and size of their estimated effects.
-Studies with small variance and large effect sizes are more likely to be published than studies with large variance and small effect sizes.
-Note that small effect size means here a treatment effect close to the control effect.
-% 
-% Let $y_i$ be the effect size estimate of study $i$. Then 
-% 
-% \begin{align}
-% y_{i} \sim N(\mu_{i}, \sigma_{i}^2) \\
-% \mu_{i} \sim N(\mu, \tau^2)
-% \end{align}
-% 
-% corresponding to a standard random effects meta-analysis.
-$\mu$ is the overall mean effect, $\sigma_{i}^2$ the within study variance and $\tau^2$ the between study variance.
-This is the \textit{population model}.
-% 
-% \vspace{0mm}
-% The \textit{selection model} is defined as follows. Suppose a selection of studies with reported standard errors $s$ (likely different from $\sigma$). Only a proportion 
-% 
-% \begin{align}
-% P(\textrm{select}|s) &= \Phi(a + b/s) \label{copas.selection1}
-% \end{align}
-% 
-% of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
-\ref{copas.selection1} can be rewritten as
-% 
-% \begin{align}
-% z = a + b/s + \delta \label{copas.selection2}
-% \end{align}
-% 
-% with $\delta \sim N(0,1)$. The study with standard error $s$ is only selected if $z$ is positive. Therefore, the larger $z$, the more likely the study is selected.
-% Combining population and selection model for study $i$, we have 
-% 
-% \begin{align}
-% y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \\
-% \mu_{i} \sim N(\mu, \tau^2) \\
-% z_{i} = a + b/s_{i} + \delta_{i}
-% \end{align}
-% 
-% where $(\epsilon_{i}, \delta_{i})$ are standard normal residuals and jointly normal with correlation $\rho = cor(y_{i}, z_{i})$.
-Every given study $i$ in the meta-analysis has $z_{i} > 0$.
-If $\rho$ is large and positive and $z_{i} > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_{i}$ and $\delta_{i}$.
-Thus, the true mean $\mu$ is likely to be overestimated.
-% 
-% \vspace{0mm}
-% Let $u = a + b/s$, $\lambda(u) = \phi(u)/\Phi(u)$ ($\phi$ is the standard normal density function) and $\tilde{\rho} = \sigma/\sqrt(\tau^2 + \sigma^2) \rho$.
-The probability of a study being selected is
-% 
-% \begin{align}
-% P(\textrm{select}|s, y) = P(a,b,s,y) = \Phi(\frac{u + \tilde{\rho}((y - \mu)/\sqrt(\tau^2 + \sigma^2))}{\sqrt{1 - \tilde{\rho^2}}})
-% \end{align}
-% 
-% It can also be shown that the expected value 
-% 
-% \begin{align}
-% \mathbb{E}(y|s, select) = \mu + \rho\sigma\lambda(u) \label{copas.expectation}
-% \end{align}
-% 
-% which shows that the expected value for a study is larger for larger $\sigma$. 
-% 
-% \vspace{0mm}
-% One can compute a likelihood function based on the distribution of $y$ conditional on $z > 0$.
-The likelihood can be maximized for any given pair $a,b$ (can not be estimated since the number of missing studies is not known), and a maximum likelihood estimate $\hat{\mu}$ for the true mean $\mu$ can be obtained.
-One can then perform a sensitivity analysis.
-First, one looks how $\hat{\mu}$ changes for different values of $a,b$.
-One can then compare the fitted values in \ref{copas.expectation} with the real values.
-To test the fit of the model (while keeping all other parts unchanged), the model can be extended in the following way :
-% 
-% \begin{align}
-% y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
-% \end{align}
-% 
-% If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
-Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
-The $p$-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
-% 
-% \vspace{0mm}
-% To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
-% 
-% \vspace{0mm}
-% In practice, only a range of values for $a,b$ are reasonable.
-For those values, the quantities above can be calculated and illustrated.
-Values for $\mu$ that have $p$-values over a predefined significance threshold can be used for inference of the effect size.
-% 
-% \subsection{Adjustment by Regression}
-% There are multiple ways to adjust for small study effects by regression.
-The general idea is to extrapolate the effect size of a study with a variance of zero based on the given effects and variances.
-% 
-% \citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
-Similarly to what has been seen in Copas selection model, we let $y_{i}$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_{i}}$ as in \ref{limitmeta.regression}.
-% 
-% \begin{align}
-% y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{v_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
-% \end{align}
-% 
-% $\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
-% 
-% \begin{align}
-% \mathbb{E}((y_{i} - \beta_{0})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{ if } \sqrt{v_{i}} \rightarrow \infty \label{limitmeta.infinitesample} \\
-% \mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
-% \end{align}
-% 
-% After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before \eg in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test (see \ref{Thompson}).
-% 
-% \vspace{0mm}
-% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
-% 
-% \begin{align}
-% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
-% \end{align}
-% 
-% Letting $M \rightarrow \infty$, we obtain:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
-% \end{align}
-% 
-% Note that:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
-% \end{align}
-% 
-% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
-% 
-% \begin{align}
-% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
-% \end{align}
-% 
-% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-% \end{align}
-% 
-% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
-
-% \begin{align} \label{cox reg}
-% P(Y < y|\mathbf{x}) = 1 - exp(-exp(h(y) - (\mathbf{x})^\top\beta)
-% \end{align}
-% 
-% See \cite{hothorn} for further information. It specifies the instantaneous risk of an event at time t to be
-% 
-% \begin{align}
-% \lambda_{0}(t)exp((\mathbf{x})^\top\beta) \nonumber
-% \end{align}
-% 
-% The model is regarded as a semi parametric model since it includes the covariates in a linear fashion but leaves the baseline hazard $\lambda_{0}(t)$ unspecified.
-The factor $exp((\mathbf{x})^\top\beta)$ has the interpretation of a hazard ratio between the reference with $\mathbf{x} = 0$.
-The formal definition of the hazard is
-% 
-% \begin{align}
-% h(t) = \lim_{h \to 0} \frac{P(t < T < t + h| T > t)}{h}
-% \end{align}
-% 
-% 
-% \begin{align} \label{generalized linear model}
-% \mathbf{Y}{_{ij}}|U{_i},\epsilon{_{ij}} = (1,x{_i}^\top)\beta + U{_i} + \epsilon{_{ij}}
-% \end{align}
+There is however a small difference, with regression estimates to have a little bit a larger absolute value.
+There might be some bias between adjusted $z$-scores, where regression estimates seem to be somewhat smaller when the mean is a little above zero, and somewhat larger when the mean is a little below zero.
+\\
 

### 2019-07-05 report/chapter02.Rnw
adjustments after correction

--- 2019-06-24 report/chapter02.Rnw
@@
 % LaTeX file for Chapter 02
-
-<<echo=FALSE>>=
+<<'preamble04',include=FALSE>>=
 library(knitr)
 opts_chunk$set(
-    fig.path='figure/ch02_fig',
+    fig.path='figure/ch04_fig', 
     self.contained=FALSE,
-    cache=TRUE
+    cache=FALSE
 ) 
@@
 
-<<echo=FALSE>>=
-library(knitr)
-opts_chunk$set(fig.path='figure/ch02_fig',
-               echo=TRUE, message=FALSE,
-               fig.width=8, fig.height=3,
-               out.width='\\textwidth-3cm',
-               message=FALSE, fig.align='center',
-               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
-               cache=TRUE
-)
-options(width=74)
-@
+\chapter{Methods} \label{ch:methods}
+\section{Introduction and Notation}
+The analysis has already been said to be restricted on clinical or health care interventions.
+The interventions are restricted to comparisons of two treatment arms by some measure of sanity or worsening of health.
+The difference in this measure between the groups is referred to as the treatment effect.
+Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or Hedges $g$, Fisher's z score or Pearsons correlation coefficient.
+\\
+Let us consider a meta-analysis with $n$ study treatment effects ($n > 1$, but typically small).
+A study is indexed by $i$, and it's treatment effect by  $\theta_i$.
+The observed treatment effect is $\hat{\theta}_i$.
+The pooled treatment effect of a meta-analysis will be denoted as $\theta_M$, and consequently, the observed pooled treatment effect as $\hat{\theta}_M$.
+Furthermore, each treatment effect is typically measured with some standard error $\se_i$ and an estimate of $\se_i$ is denoted as $\hat{\se}_i$.
+The $\hat{}$ sign thus indicates if it is an estimate.\\
+For continuous outcomes, let $m_t$ be the mean of the treatment group, $m_c$ the mean of the control group, and equivalently $\textrm{sd}_t$ and $\textrm{sd}_c$ the corresponding standard deviations.
+$n_t$ and $n_c$ are the total number of participants in the groups.
+In the case of binary outcomes, let $e_t$ be the count of events in the treatment arm $e_c$ the count of events in the control group.
+The observed counts in a study $i$ are referred to as $e_{t,i}$ and analogously $e_{c,i}$.
 
-<<echo = FALSE, warning=FALSE, message=FALSE>>=
-rm(list = ls())
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'Data/PubBias')
-PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2018-06-09.csv'
-PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+\section{Effect Measures and $p$-values}
+\subsection{Continuous Outcomes}
+For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Hedges $g$) and  a standard error thereof.
+Note that the definition of Hedges $g$ and its standard error $\se$ varies among the literature, the following applies for this report:
 
-file_results = "pb.RData"
+\begin{align}
+\se &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}} & g &= \frac{m_t - m_c}{\se} \label{eq:hedges.g}
+\end{align}
 
-source(file.path(PATH_CODE, 'PubBias_functions.R'))
+The mean difference $\theta$ and its standard error $\se$ can similarly be obtained by
 
-file.dat <- "data.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
+\begin{align}
+\theta &= m_t - m_c & \se &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_t}
+\end{align}
 
-load(file.path(PATH_RESULTS, "meta_analyses_summary_bin_cont_surv.RData"))
-load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
-load(file.path(PATH_RESULTS, "meta.bin.RData"))
-load(file.path(PATH_RESULTS, "meta.cont.RData"))
-load(file.path(PATH_RESULTS, "meta.surv.RData"))
-load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+Both estimators take into account that the two groups might have unequal variances.
+A $p$-value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$ test.
+The $t$ statistic is obtained, using $s$ and $g$ from \ref{eq:hedges.g}, by
 
-###################################################################################################################
-###################################################################################################################
+\begin{align}
+t &= g/(s\sqrt{(1/n_t)+(1/n_c)}) \nonumber
+\end{align}
+and the $p$-value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
 
-#Barbiturate Examples
-barbi1 <- arrange(filter(data, file.nr == 21) %>% 
-          select(Study = study.name, Comparison = comparison.name, Outcome = outcome.name, 
-                 Events = events1, Total = total1, Events_c = events2, Total_c = total2) %>% 
-            slice(c(1,3)), Study) 
-barbi2 <- arrange(filter(data, file.nr == 21) %>% 
-          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study)
-barbi2[barbi2$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
+\begin{align}
+p &= 2(1-F(\abs{t})) \nonumber
+\end{align}
 
-#Missing values
-cont.out <- data %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
-                                 outcome.measure.new == "Hedges' G")
+The t-test is known to be not very reliable if combined sample size is small ($n < 30$), see for example \citet{t.test}.
 
-missing.mean <- which(is.na(cont.out$mean1) | is.na(cont.out$mean2))
-missing.effect <- which(is.na(cont.out$effect))
-missing.means <- intersect(missing.mean, missing.effect) #Cont. results that have neither complete means nor an effect
-wrong.effect <- which(cont.out$mean1 == 0 & cont.out$mean2 == 0 & cont.out$effect == 0) #Cont.results that have only zeros
-missing.effects <- length(c(missing.means, wrong.effect))
+\subsection{Binary Outcomes}
+Two commonly used effect measures for binary outcome data are risk ratios and odds ratios between treatment and control group. 
+The methods presented here can also be found, for example, in \cite[34]{Intro.meta}.
+Let $\theta$ be the natural logarithm of the odds ratio. $\theta$ and its variance $\se^2$ can be obtained by
 
-missing.sd <- which(is.na(cont.out$sd1) | is.na(cont.out$sd2))
-missing.se <- which(is.na(cont.out$se))
-missing.sds <- intersect(missing.se, missing.sd) #Cont. results that have neither complete means nor an effect
-wrong.sds <- which(cont.out$sd1 == 0 & cont.out$sd2 == 0 & cont.out$se == 0) #Cont.results that have only zeros
-missing.sds <- length(c(missing.sds, wrong.sds))
+\begin{align}
+\theta &= \log(\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}) \nonumber \\
+\se^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
+\end{align}
 
-missing.ss <- which(is.na(data$total1) | is.na(data$total2))
-wrong.ss <- which(data$total1 <= 0 | data$total2 <= 0)
-missing.ssize <- length(c(missing.ss, wrong.ss))
+Plugging in the observed counts will give the corresponding estimates. The logarithm of the risk ratio $\theta$ and its variance $\se^2$ is similarly defined as
 
-missing.year <- sum(is.na(data$study.year)) + length(c(which(data$study.year < 1920), which(data$study.year > 2019)))
+\begin{align}
+\theta &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
+\se^2&= 1/e_t + 1/n_t + 1/e_c + 1/e_t \label{eq:risk.ratio.variance}
+\end{align}
 
-missing.table <- rbind("Missing mean values and mean differences" = missing.effects,
-                         "Missing standard deviations and standard errors" = missing.sds,
-                         "Missing sample sizes" = missing.ssize,
-                         "Missing study year" = missing.year)
+Using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$-value, \eg \cite[98]{held2014}.
+\\
+Thus, with $\Phi$ as the cumulative standard normal distribution, we get
+\begin{align}
+p &= 2\cdot(1-\Phi(\abs{\hat{\theta}/\hat{\se}}), \nonumber
+\end{align}
+a $p$-value for the corresponding estimate, which summarizes the evidence against $\hat{\theta}$ being zero (\ie the true risk/odds ratio being 1). \\
+Binary and continuous effect measures can be converted into each other, as described in Section \ref{sec:transformation.effectsizes}.
 
-#Mean and median number of different outcome types of reviews
-mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
-  ungroup() %>% group_by(file.nr) %>%
-  count() %>% ungroup %>% summarise(mean = mean(n))
+\subsection{Survival Outcomes}
+Time-to-event data with censoring has to be analyzed by special means.
+One frequently used method to take into account right-censoring is the Cox proportional hazards regression model \citep{Cox}.
+Because the method itself is not applied in this thesis, but only the resulting estimates of the parameters are used, the reader is referred to the extensive literature covering this topic (\eg \citet{Surv}).
+\\
+The so-called hazard ratio estimated by Cox regression is the ratio of the instantaneous risk of experiencing the event between two groups.
+Because it is a maximum likelihood estimator, one can again use its Wald test statistic to test for equal hazards.
+Let $\hat{\theta}$ be an estimate of the log hazard ratio and $\hat{\se}$ an estimate of the standard error of it.
+As before
+\begin{align}
+p &= 2\cdot(1-\phi(\abs{\hat{\theta}/\hat{\se}(\hat{\theta})}) \nonumber
+\end{align}
+will give a $p$-value for the evidence against the null hypothesis.
 
-median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
-  ungroup() %>% group_by(file.nr) %>%
-  count() %>% ungroup %>% summarise(mean = median(n))
+\section{Fixed and Random Effects Meta-Analysis} \label{sec:meta.analysis}
+The fixed effects meta-analysis estimator of the pooled treatment effect is a mean of the single treatment effect estimators, weighted by their standard errors \citep{fixed.effects.rosenthal}.
+Let $w_i = 1/\se_i^2$ be the weights, and $\theta_M$ be the pooled estimator and $s_M^2$ its variance.
+Then
 
-#Study.year quantiles:
-#data.ext2 <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
-publication.year.range <- c(quantile(data.ext2$study.year, 0.05, na.rm = T), quantile(data.ext2$study.year, 0.25, na.rm = T), 
-                            quantile(data.ext2$study.year, 0.5, na.rm = T), quantile(data.ext2$study.year, 0.75, na.rm = T),
-                            round(mean(data.ext2$study.year, na.rm = T), 2))
+\begin{align}
+\theta_M &= \frac{\sum_{i = 1}^n w_i \theta_i}{\sum_{i = 1}^n w_i} &
+s_M^2 &= \frac{1}{\sum_{i = 1}^n w_i} \label{eq:fixed.effects}
+\end{align}
 
-#Outcome.measure frequency table:
-outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.new) %>% count() %>% 
-                                       arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9),
-                                     data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% 
-                                       ungroup() %>% filter(row_number() > 8) %>% 
-                                       summarise(outcome.measure.new = "other", n = sum(n)))
+This estimator minimizes the variance between the effects.
+An estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and variances $\hat{\theta}_i$ and $\hat{\se}_i^2$.
+The underlying idea is that we assume $\theta_i \sim N(\theta_M, \se_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.
+\\
+The random effects model \citep{whitehead} assumes instead that 
+\begin{align}
+\theta_i \sim N(\mu_i, \se_i^2) &&
+\mu_i \sim N(\theta_M, \tau^2) \label{eq:random.effects} 
+\end{align}
 
-outcome.measure.frequencies <- outcome.measure.frequencies %>% mutate(percentage = round(n/sum(n),3)*100)
-names(outcome.measure.frequencies) <- c("Outcome measure", "n", "Percentage")
-outcome.measure.frequencies$Percentage <- paste(outcome.measure.frequencies$Percentage, "%", sep = "")
+Marginally, we have $\theta_i$ being distributed around a common mean $\theta_M$ with additional variance $\tau^2$:
 
-#Total and group size quantiles:
-data.ext2 <- data.ext2 %>% ungroup() %>%  mutate(total.n = total1 + total2)
-samplesize.range <- c(quantile(data.ext2$total.n, 0.05, na.rm = T), quantile(data.ext2$total.n, 0.25, na.rm = T), 
-                            quantile(data.ext2$total.n, 0.5, na.rm = T), quantile(data.ext2$total.n, 0.75, na.rm = T),
-                            round(mean(data.ext2$total.n, na.rm = T), 2))
-treatment.group.size.range <- c(quantile(data.ext2$total1, 0.05, na.rm = T), quantile(data.ext2$total1, 0.25, na.rm = T), 
-                      quantile(data.ext2$total1, 0.5, na.rm = T), quantile(data.ext2$total1, 0.75, na.rm = T),
-                      round(mean(data.ext2$total1, na.rm = T), 2))
+\begin{align}
+\theta_i \given \mu_i \sim N(\theta_M, \se_i^2 + \tau^2) \nonumber %\label{eq:random.effects.marginal}
+\end{align}
 
-#Frequencies of results:
-comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
-comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
-                      quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
-                      round(mean(comp.freq$n, na.rm = T), 2))
+$\tau^2$ is often referred to as a population variance or between-study variance, whereas $\se_i^2$ can be interpreted as sampling error.
+The pooled treatment effect estimate $\theta_M$ of the random effects model and its variance is obtained by replacing the weights $w_i$ in equation \ref{eq:fixed.effects} with $w_i = 1/(\se_i^2 + \tau^2)$.
+\\
+The model is superior to the fixed effects model whenever the standard errors of the treatment effects alone are unlikely to fully account for the entire variability observed between studies.
+Note that as $\tau^2$ increases, each $\theta_i$ will eventually get equal weights, irrespective of it's sampling error $\se_i^2$.\\
+The estimation of $\tau^2$ has been subject to some debate in the statistical literature. Oftentimes, the method of moment estimator of \citet{tau.estimator} is used.
+We use the measure of heterogeneity, $Q$, and divide by $C$ after having subtracted the degrees of freedom $n-1$:
 
-#Frequencies of studies:
-study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
-study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
-                      quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
-                      round(mean(study.freq$n, na.rm = T), 2))
+\begin{align}
+Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i}\label{eq:Q.heterogeneity} \\
+\tau^2 &= \max\big(0, \frac{Q - (n-1)}{C}\big) \label{eq:Tau.definition}
+\end{align}
 
-#Pooling studies
-cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
-  filter(n < 15) %>%
-  full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
-               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
-  ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
-# cum.repr.trials.nosub <- data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
-#   filter(n < 15) %>%
-#   full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
-#                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
-#   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
+Again, $w_i, \theta_i ...$ have to be replaced by their estimates in order to get an estimate $\hat{\tau}^2$. \\
+The Paule-Mandel estimator \citep{paulemandel} is considered to have most often better properties than the method of moments estimator (\eg \citet{tau.estimator.evaluation}).
+Since we defined $w_i = 1/(\se_i^2 + \tau^2)$, it also holds that
 
-# cum.repr.trials <- cbind(cum.repr.trials.nosub, cum.repr.trials.subg)[,c(1,3,6)]
+\begin{align}
+w_i \textrm{Var}(\theta_i) &= 1 & \textrm{Var}(\sqrt{w_i}\theta_i) = 1 \nonumber
+\end{align}
 
-colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
+For any $w_i$, the variance can be estimated and equated to its expected value:
 
-	data <- data %>% mutate(
-		outcome.type = ifelse(outcome.measure.new == "Hazard Ratio", "surv", 
-													ifelse(outcome.measure.new == "Odds Ratio" | outcome.measure.new == "Risk Ratio" |
-																 	outcome.measure.new == "Peto Odds Ratio" | outcome.measure.new == "Risk Difference", "bin", "cont")),
-		outcome.type = ifelse(outcome.measure.new == "Rate Ratio" | outcome.measure.new == "Rate difference", "rate", outcome.type),
-		lrr = NA,
-		var.lrr = NA,
-		smd = NA,
-		var.smd = NA,
-		smd.pbit = NA,
-		var.smd.pbit = NA,
-		smd.ordl = NA,
-		var.smd.ordl = NA,
-		cor.phi = NA,
-		var.cor.phi = NA,
-		pval.single = NA, 
-		cor.pearson = NA,
-		var.cor.pearson = NA,
-		z = NA,
-		var.z = NA,
-		events1c = NA,
-		events2c = NA,
-		sig.single = NA)
-	cont.ind <- which(data$outcome.type == "cont" & !is.na(data$outcome.type))
+\begin{align}
+\se^2(w_i\theta_i) &= \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} & \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} = 1 \label{eq:paulemandel}
+\end{align}
 
-	data[cont.ind, "outcome.type"] <- data[cont.ind, ] %>% 
-		mutate(outcome.type = ifelse(outcome.measure.new == "Std. Mean Difference"  | outcome.measure.new == "Mean Difference", 
-																 outcome.type, NA)) %>% select(outcome.type)
+$\theta_M$ can be estimated using equation \ref{eq:fixed.effects}, the only problem is to estimate $\tau^2$. It can be obtained through an iterative process, using a newly defined function
 
-	cont.ind <- which(data$outcome.type == "cont" & !is.na(data$outcome.type))
+\begin{align}
+F(\tau^2) &= \sum_{i = 1}^n w_i(\theta_i - \theta_M)^2 - (n-1) \nonumber
+\end{align}
 
-	nomean1.ind <- which(data$outcome.type == "cont" & is.na(data$mean1))
-	nomean2.ind <- which(data$outcome.type == "cont" & is.na(data$mean2))
-	noeffects.ind <- which(data$outcome.type == "cont" & !is.na(data$effect))
-	nomeans.ind <- intersect(nomean1.ind, nomean2.ind)
-	nomeans.ind <- intersect(noeffects.ind, nomeans.ind) #no means, but a (std.) mean difference is provided.
+In view of equation \ref{eq:paulemandel}, $\tau^2$ must be such that $F(\tau^2) = 0$.
+Then, we start with a arbitrary $\tau^2$ and repeatedly add a term $\tau_0^2$ to update $\tau^2$ until $F(\tau^2 + \tau_0^2)$ is close to zero (using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{\theta}_M$).
+Using a truncated Taylor series expansion, one can obtain the partial derivative after $\tau^2$, which is a reasonable choice for $\tau_0^2$.
+\\
+%Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{theta}$, we can update $F(\tau^2)$ and check convergence to zero. \\
+The estimation of $\tau^2$ is accompanied by uncertainty.
+A common procedure is to test if it is there is significant heterogeneity between the studies \cite[109]{Intro.meta}.
+Compute $Q$, as given in \ref{eq:Q.heterogeneity}, based on one of the estimators of $\tau^2$.
+It is assumed that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equally distributed effect sizes.
+Thus, the expected value of $Q$ is $n-1$, and the excess dispersion is $Q - n + 1$.
+The $p$-value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
+= $n-1$.
+\\
+An advantage of the $\tau^2$ is that it is directly linked to the variability in the data.
+Additionally, one can use the $I^2$ statistic to see what portion the between study variance has of the overall variance.
+It is computed as
 
-	data[nomeans.ind,"mean1"] <- data[nomeans.ind,"effect"]
-	data[nomeans.ind,"mean2"] <- 0
+\begin{align}
+I^2 &= \max\Big(0, 1 - \frac{n-1}{Q}\Big) \nonumber%\label{I2.proportion}
+\end{align}
 
-	data[cont.ind,] <- escalc(data = data[cont.ind,], m1i = mean1, m2i = mean2, 
-														sd1i = sd1, sd2i = sd2, n1i = total1, n2i = total2,
-														measure = "SMD" , append = T, var.names = c("smd", "var.smd"))
+%Large values for $\hat{I}^2$ are of great importance when analyzing \eg small study effects. \\
+Importantly, all proposed methods above assume normally distributed effect sizes and proper estimates $\hat{\se}$ of the true standard error.
+This assumptions are not met for very small sample sizes and very few event counts.
+Alternatively, the Mantel-Haenszel method for risk and odds ratios (see \eg \citet{mantel.haenszel}) could be used in the latter case.
 
-	inpute.given.ind <- which(is.na(data[cont.ind, "smd"]) & data[cont.ind, "outcome.measure.new"] == "Std. Mean Difference")
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-	#Counts of meta-analyses with only zeros:
-all.zero.events.number <- data.ext2 %>% filter(outcome.type == "bin") %>% 
-  group_by(meta.id) %>% 
-    mutate(n = n()) %>% filter(n >= 10) %>% 
-  filter(all(events1 == 0) & all(events2 == 0)) %>% 
-  distinct(meta.id) %>% ungroup() %>%  count()
+\section{Small Study Effects Tests}
+The tests that will be presented on the following pages are a common way to detect publication bias.
+Importantly, they are however not interpretable directly as evidence for publication bias, but this is left for the discussion chapter.
+The tests are also often referred to as funnel plot asymmetry tests, because of the popularity of a recent test that has been used frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill}.
+However, it is known for some time that the method has disadvantageous properties, therefore, it will not be discussed here, as well as the funnel plot (the radial plot will be used as an alternative).\\
+A test for small study effects will test in some ways if the size of the estimated treatment effect of a study depends on some measure of its size.
+An association between study size and treatment effect size can be interpreted as an artifact of publication bias.
 
-#Counts of meta-analyses with means and sds only zeros:
-all.zero.means.number <- data.ext2 %>% filter(outcome.type == "cont") %>% group_by(meta.id) %>% 
-    mutate(n = n()) %>% filter(n >= 10) %>% filter(all(mean1 == 0) & all(mean2 == 0)) %>% 
-    filter(all(sd1 == 0) | all(sd2 == 0)) %>% distinct(meta.id) %>% ungroup() %>% count()
+\subsection{Continuous Outcome Tests}
+For a continuous outcomes that are normally distributed, the sample mean and variance are independent of each other \cite[120]{meta.w.R}.
+Thus, the estimated standard errors of treatment effects can be used as a proxy for study size, as they should in principle not be tied to the effect size.
 
-#Counts of meta-analyses with n larger ten:
-m.a.largerten.number <- meta %>% filter(k > 9) %>% ungroup %>% count()
-#smaller I2 than 0.5:
-m.a.smaller.5.number <- meta %>% filter(k > 9 & I2 < 0.5) %>% ungroup %>% count()
-#variance ratio > 4:
-m.a.variance4.number <- meta %>% filter(k > 9 & I2 < 0.5) %>% filter((se.max^2)/(se.min^2) > 4) %>% ungroup %>% count()
-#At least on sig. estimate:
-m.a.one.sig.number <- meta %>% filter(k > 9 & I2 < 0.5) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(n.sig.single > 0) %>% ungroup %>% count()
-#Single patient meta-analyses:
-tmp <- data.ext2 %>% filter(outcome.type == "cont") %>% group_by(meta.id) %>% 
-	mutate(n = n()) %>% filter(n >= 10) %>% filter(!all(mean1 == 0) & !all(mean2 == 0)) %>% 
-	filter(!all(sd1 == 0) | !all(sd2 == 0))
+\subsubsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
+\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+A standardized effect size $\theta_i^\star$ can be computed as in \ref{begg.stand.eff}.
+$\se_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \ref{begg.stand.var}, $\theta_M$ being the fixed effects pooled treatment effect (\ref{eq:fixed.effects}.
 
-meta.id.vector <- unique(tmp$meta.id)
-m.a.singlepatient.number <- length(meta.id.vector[c(which(meta.id.vector > 42716 & meta.id.vector < 42725))] )
-#How many z-score meta-analyses are excluded due to total <= 3, and how many m.a. have then n < 10:
-tmp <- data.ext2 %>% group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 9) %>%
-	filter(outcome.type != "rate" & !is.na(outcome.type))
+\begin{align}
+\theta_i^\star &= (\theta_i - \theta_M)/\se_i^{2\star} \label{begg.stand.eff}  \\
+\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2}1 \label{begg.stand.var} 
+\end{align}
 
-metac <- meta %>% filter(k > 9) %>% filter(n.sig.single > 0) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
+A rank correlation test based on Kendall's tau is then used.
+First, the pairs are ordered after their ranks based on $s^{2\star}$.
+Then, for each $s^{2\star}$ rank, the corresponding ranks based on $\theta^{2\star}$ that are larger are counted and summed up to $u$.
+The number of ranks based on $\theta^{2\star}$ that are in contrary, smaller, are counted and summed up to $l$.
+Then the normalized test statistic $Z$ is given as
 
-meta.id.vector <- metac$meta.id[-which(metac$outcome.type == "surv")]
-meta.id.vector <- meta.id.vector[-c(which(meta.id.vector == 157083),
-																which(meta.id.vector == 159329),
-																# which(meta.id.vector == 12459),
-																# which(meta.id.vector == 12465),
-																# which(meta.id.vector == 22087),
-																which(meta.id.vector == 182298))]
+\begin{align}
+Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \nonumber
+\end{align}
 
-meta.data.zscore <- tmp[which(tmp$meta.id %in% meta.id.vector),]
-total.seq3.number <- meta.data.zscore %>% filter(total1 + total2 < 4) %>% select(var.z) %>% ungroup() %>% count() 
-m.a.seq3.seq10.number <- meta.data.zscore %>% filter(total1 + total2 > 3) %>% count() %>% filter(nn < 10) %>% ungroup %>% count()
+Thus, large number of concordance between pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$.
+The $p$-value is obtained using the standard normal distribution $\Phi$:
+\begin{align}
+p &= 2\cdot(1-\Phi(\abs{Z})) \nonumber
+\end{align}
 
-meta.id.vector <- metac$meta.id
-meta.data <- data.ext2[which(data.ext2$meta.id %in% meta.id.vector),]
+The changes that have to be made int the case of ties are small and can be found in \cite[410]{begg.ties}.
 
-@
+\subsubsection{Egger's Test: Weighted Linear Regression Test} \label{sec:Egger}
+First, the concept of simple linear regression is introduced. In short, the model assumes a dependent variable $y$ to be a linear function of another explanatory variable $x$:
 
-\chapter{The Cochrane Dataset}
+\begin{align}
+y &= \beta_0 + \beta_1 x + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:simple.regression}
+\end{align}
 
-\section{Cochrane Systematic Reviews}
-The Cochrane Group has specialized on systematic reviews in clinical science.
-Certain knowledge of standards and principles of the Cochrane Group may help to assess the quality and the properties of the dataset.
-The following information stems from the Cochrane Handbook for Systematic Reviews \citep{cochrane.handbook}.
+$\epsilon$ is the residual noise term that becomes necessary when $n$ pairs $(x_i, y_i)$ are given and there is no exact solution.
+Then it is common to look for the solution that minimizes the squared residuals, the least-squares solution.
+Formally,
+
+\begin{align}
+\operatorname*{argmin}_{\beta_0, \beta_1}\big(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i\big) \label{eq:least.squares}
+\end{align}
+
+Let $\mathbf{X}$ be a matrix with the explanatory variables $x$ and $\mathbf{y}$ a corresponding vector for all $y$:
+
+\begin{equation*}
+\mathbf{X} = 
+\begin{bmatrix}
+1 & x_{12} \\
+1 & x_{22} \\
+1 & x_{32} \\
+\vdots & \vdots \\
+1 & x_{n2} \\
+\end{bmatrix} 
+\qquad
+\mathbf{y} = 
+\begin{bmatrix}
+y_1 \\
+y_2 \\
+y_3 \\
+\vdots \\
+y_n \\
+\end{bmatrix}
+\end{equation*}
+
+Let $\mathbf{\beta} = (\beta_0, \beta_1)^\top$. It can be shown that
+
+\begin{align}
+\hat{\mathbf{\beta}} &= (\mathbf{X}^\top \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
+\end{align}
+
+Is an estimator of $\mathbf{\beta}$ that minimizes the squared residuals.
+Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\mathbf{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$.
+The variance estimates $\hat{\sigma}^2$ and $\hat{\mathbf{s}}_\beta^2$ are
+
+\begin{align}
+\hat{\sigma}^2 &= \frac{1}{n-2}\mathbf{r}^\top \hat{\mathbf{r}} & \hat{\mathbf{s}}_\beta^2 &= \hat{\sigma}^2 (\mathbf{X}^\top \mathbf{X})^{-1} \label{eq:regression.variances}
+\end{align}
+
+The estimate $\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the regression line. Furthermore, in the simple linear regression setting, $\hat{\beta}_0$ can also be obtained by:
+
+\begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} &
+\hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \nonumber
+\end{align}
+
+$\bar{x}, \bar{y}$ denoting the sample means of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$. Thus, $\hat{\beta}_0$ is also called global mean.
+To test whether there is evidence for the intercept $\beta_0$ to be unequal to some value $\beta_{H0}$, a $t$-test can be used.
+
+\begin{align}
+p &= 2(1-F(\abs{(\beta_0 - \beta_{H0})/s_{\beta_0}})) \nonumber
+\end{align}
+
+where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. $p$ will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
+The concept is extendable to weighted linear regression.
+Weighted linear regression may be used if the residuals $\mathbf{r}$ have unequal variances, which is equivalent to ascribe different precision to the observed $y$.
+The least squares equation \ref{eq:least.squares} is extended to
+
+\begin{align}
+\operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
+\end{align}
+
+with positive weights $w_i$ that penalize large squared residuals for some $i$ more if $w_i$ is larger compared to other $w_i$. \\
+Let $\mathbf{W}$ be a $n \times n$ matrix with $\mathbf{W}_{ii} = w_i$, the weights on the diagonal and zeros on the off-diagonals.
+The estimates in \ref{eq:regression.parameters} and \ref{eq:regression.variances} can still be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$.
+\label{weighted.regression} \\
+Now it is shown how linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citet{Egger}.
+Let $\theta/s$ be the dependent variable $y$ and $1/\se$ the explanatory variable $x$.
+If plotted, this corresponds to a radial or Galbraith plot \citep{galbraith}.
+The linear regression equation as introduced before in \ref{eq:simple.regression} can be written in two ways:
+
+\begin{align}
+\theta/s &= \beta_0 + \beta_1/\se + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:radial.plot} 
+\end{align}
+
+Equation \eqref{eq:radial.plot} is often provided due to the correspondence to the radial plot. However, it is equivalent to
+
+\begin{align}
+\theta &= \beta_0 + \beta_1 \se + \epsilon, & \epsilon \sim N(0, w^{-1}\sigma^2) \label{eq:egger.plot}
+\end{align}
+
+with weights $w = 1/\se^2$.
+Thus testing $\beta_0$ of \ref{eq:radial.plot} or $\beta_1$ is equivalent.
+The corresponding $p$-value is then used as evidence for a small study effect.
+Plugging in  $\theta_i/\se_i, 1/\se_i$ as $y_i, x_i$ into equation \ref{eq:regression.parameters} and \ref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{\se}_{\beta_0}$ and $\hat{\se}_{\beta_1}$.
+
+% \begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (\varphi_i - \bar{\varphi})(\theta^\star_i - \bar{\theta}^\star)}{\sum_{i = 1}^n (\varphi_i - \bar{\varphi})^2} &
+% \hat{\beta}_0 &= \bar{\theta}^\star - \hat{\beta}_1 \bar{\varphi} \nonumber
+% \end{align}
+
+\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{sec:Thompson}
+A method proposed in \citet{thompson.sharp} allows for between study variance $\tau^2$, as introduced before in section \ref{sec:meta.analysis}.
+It extends the previously seen linear regression approach with $x = 1/\se$ and $y = \theta/s$ by introducing weights.
+The effect size $\theta_i$ is assumed to be distributed as
+
+\begin{align}
+\theta_i \sim N(\beta_0 + \beta_1 \se_i, \se_i^2 + \tau^2) \label{t.sharp.regression}
+\end{align}
+
+$\tau^2$ is estimated as in equation \ref{eq:Tau.definition} (method of moments). %or \ref{eq:paule.mandel}. 
+The weights are set as $w_i = 1/\sqrt{\se_i^2 + \tau^2})$.
+After adjusting for the weights as described in \ref{weighted.regression}, we can proceed analogous to Egger's test.
+The $p$-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
+
+\subsection{Dichotomous Outcomes Tests}
+
+The issue with dichotomous outcomes is that effect size and variance of effect size are correlated, which can readily be seen in \ref{eq:risk.ratio} and \ref{eq:risk.ratio.variance}.
+For example, a small number of event counts in one or group will inflate the variance and the effect size.
+Consequently, the tests above will tend to reject the null-hypothesis too often, \ie report false positives.
+A number of solutions to this problem are provided in the literature.
+
+\subsubsection{Peters Test: Weighted Linear Regression Test} \label{sec:Peter}
+Instead of taking the standard error $s$ as explanatory variable $x$ as in Egger's Test, the inverse of the total sample size is used.
+Additionally, the variances $\se_i^2$ are used as weights.
+Thus, the subsequent test procedure is identical to Egger's test.
+Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
+
+\subsubsection{Harbord's Test: Score based Test} \label{sec:Harbord}
+A rank based alternative to Peters test for binary outcomes is Harbord's test \citep{Harbord}.
+It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated at log odds ratio $\theta_0 = 0$ and its inverse Fisher information $s^2$. Formally,
+
+\begin{align}
+\varphi &= e_t - (e_t - e_c)(e_t + (n_t - e_t))/(n_t + n_c) \label{harbord.score} \\
+ s^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \label{harbord.variance}
+\end{align}
+
+It can be shown that they are both good approximations of the log odds ratio and its variance if the real $\theta$ is not too far from zero.
+The standardized estimator $r_i/v_i$ is also known as Peto odds ratio.
+The obtained scores and variances can be used in Egger's test as treatment effects and variances.
+
+\subsubsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
+\citet{Schwarzer} developed a test for the correlation between $E_t - \mathbb{E}(E_t)$ and the variance of $E_t$, $E_t$ being a random variable from the non-central hypergeometric distribution, assuming a fixed log odds ratio.
 \\
-The definition of a systematic review is that it ``attempts to collate all empirical evidence that fits pre-specified eligibility criteria in order to answer a specific research question.'' Thus, the ``key properties of a review are'':
+$\mathbb{E}(E_t)$ and variance of $E_t$ are then estimated based on $e_t$. The standardized cell count deviation 
+\begin{align}
+(e_t - \mathbb{E}(E_t))/\sqrt(\se_i^2)
+\end{align}
+and the inverse of $\se_i^2$ is then used as before in Begg and Mazumdar's test.
 
+\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables} \label{sec:Rucker}
+The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables.
+We use that the arcsine function is the variance stabilizing transformation for a proportion.
+Let
+
+\begin{align}
+\theta_i &= \arcsin{e_t/n_t} - \arcsin{e_c/n_c} \nonumber &
+\se_i^2 &= 1/4n_t + /4n_c \nonumber
+\end{align}
+
+Then one can optionally apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained estimates.
+
+\subsection{Excess Significance Test} \label{sec:excess.significance}
+\citet{excess.significance} developed an exploratory test to detect if the proportion of significant findings is larger than expected.
+Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study.
+\\
+We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated by fixed effects Meta-Analysis \ref{eq:fixed.effects}.
+Let $O$ be the number of significant study results out of $n$ studies and $\alpha$ the significance threshold.
+Corresponding to the study effect $\theta_i$, we can specify the power $1 - \beta_i$, the probability to accepting a true result.
+Let $z_{\alpha,i}$ be the $1-\alpha$ quantile of a normal distribution with standard error $\hat{\se}_i$.
+The power of study $i$ can be estimated as:
+
+\begin{align}
+1 - \hat{\beta}_i &= F(z_\alpha) 
+\end{align}
+
+with $F$ being the cumulative distribution of a normal with mean $\hat{\theta}_M$ and standard deviation $\hat{\se}_i$. \\
+If we assume no bias in $\theta_i$ and $\theta_M$, the expected number of significant study results is then just
+
+\begin{align}
+E &= \sum_{i = 1}^n (1 - \beta_i) \nonumber
+\end{align}
+
+$E$ can then be compared to $O$ by constructing a test statistic $\chi$:
+
+\begin{align}
+\chi  &= \big( \frac{(O - E)^2}{E} + \frac{(O - E)^2}{n - E}\big) \nonumber
+\end{align}
+
+and consecutively, calculating a $p$-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
+Alternatively, one can also use a binomial test, which is encouraged when $n$ and $O$ is small.
+We will get a one sided $p$-value for excess significance, $\P(X \geq O)$, by
+
+\begin{align}
+p &= \sum_{i = O}^n\Big({n \choose i} p^i (1-p)^{n - i}\Big)
+\end{align}
+
+with $p = E/n$ and $X$ being a binomial random variable with probability $p$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small Study Effect and Publication Bias Adjustment}
+There are different approaches to correct for small study effects and publication bias.
+They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinite precision (\ie very small standard error) or to a summary effect, corrected for publication bias.
+Selection models aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:
+
+\subsection{Adjustment by Regression}
+\citet{limitmeta} use a random effects model %together with shrinkage procedure 
+to obtain an unbiased estimate. Similarly to 
+%what has been seen in Copas selection model, we let $y_i$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_i}$ as in \ref{limitmeta.regression}.
+regression based tests for small study effects, we have
+
+\begin{align}
+\theta_i & = \beta_0 + \beta_1\sqrt{\se_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \epsilon_i \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{eq:limitmeta.regression}
+\end{align}
+
+The only difference between Thompson and Sharp's variant is $x = \sqrt{\se^2 + \tau^2}$ instead of $x = \sqrt{\se^2}$.
+$\beta_{1}$ represents the bias introduced by small study effects, as illustrated in the following equations:
+
+\begin{align}
+\mathbb{E}((\theta_i - \beta_0)/\sqrt{\se_i^2}) \rightarrow \beta_1 \textrm{ if } \se_i \rightarrow \infty \nonumber \\ %\label{limitmeta.infinitesample} \\
+\mathbb{E}(theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} \se_i \rightarrow 0 \nonumber
+\end{align}
+
+After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before in the simple linear regression framework. Now we have basically two possible estimates at hand:
 \begin{itemize}
-\item``a clearly stated set of objectives with pre-defined eligibility criteria for studies''
-\item ``an explicit, reproducible methodology''
-\item ``a systematic search that attempts to identify all studies that would meet the eligibility criteria''
-\item ``an assessment of the validity of the findings of the included studies, for example through the assessment of risk of bias''
+\item $\beta_0$ the treatment effect without any influence of study precision with standard error $s_{\beta_0}$
+\item $\beta_0 + \beta_1 \tau$ the treatment effect of a hypothetical study with infinite precision, corresponding standard error $s_{\beta_0} + s_{\beta_1}$
 \end{itemize}
 
-At the end of a systematic review, ``a systematic presentation, and synthesis, of the characteristics and findings of the included studies'' is done. \\
-53 Cochrane Review Groups prepare and maintain the reviews within specific areas of health care.
-A group consists of ``researchers, healthcare professionals and people using healthcare services (consumers)''.
+Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior with respect to coverage (and mean squared error).
+
+\subsection{Copas Selection Model}
+
+A method proposed in \cite{Copas1,Copas2,Copas3} 
+assumes that the given sample of treatment effects and standard errors is a selected part of a larger random sample.
+Selection of studies depends on their effect size and variance.
+Smaller variance is always accompanied by larger selection probability.
 \\
-The groups are supported by Method Groups, Centers and Fields.
-The Cochrane Method Groups aim to discuss and consult the groups in methodological questions concerning review preparation.
-The Centers play a main role in training and support of the Groups.
-The Fields are responsible for broad medical research areas and follow priorities in those areas by advice and control of the groups.
+Let $\theta_i$ be the effect size estimate of study $i$. Then
+
+\begin{align}
+\theta_i \sim N(\mu_i, \sigma_i^2) &
+\mu_i \sim N(\theta, \tau^2) \label{eq:population.model}
+\end{align}
+
+which is similar to the random-effects meta-analysis setting.
+$\theta$ is the population mean effect, $\sigma_i^2$ the within study variance and $\tau^2$ the between study variance.
+Equations in \ref{eq:population.model} are termed the \textit{population model}.
 \\
-The first step in a review is writing a protocol, specifying the research question, the methods to be used in literature search and analysis and the eligibility criteria of the study.
-Changes in protocols are possible but have to be documented and the protocol is published in advance of the publication of the full review.
-The choices of methodology as well as the changes should not be made ``on the basis of how they affect the outcome of the research study''.
+The \textit{selection model} is defined as follows.
+Suppose a selection of studies with reported ($\neq$ estimated) standard errors $s$ (likely different from $\sigma$).
+Only a proportion of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
+Formally,
+
+\begin{align}
+P(\textrm{select}\given s) &= \Phi(a + b/s) \nonumber %\label{copas.selection1}
+\end{align}
+
+The equation can be rewritten as
+
+\begin{align}
+z = a + b/s + \delta \nonumber %\label{copas.selection2}
+\end{align}
+
+with $\delta \sim N(0,1)$.
+$z$ is interpreted as the \textit{propensity for selection}.
+It's sign must be positive in order for the study to be selected.
+Thus, the larger $z$, the more likely the study will be selected.
+Also, $a$ is somewhat like to global retention or selection rate for each study, while $b$ decides about the decline of selection probability with increasing $s$.\\
+So far, we have, for a study $i$
+
+\begin{align}
+\theta_i = \mu_i + \sigma_i\epsilon_i \nonumber \\ 
+\mu_i \sim N(\theta, \tau^2) \nonumber \\
+z_i = a + b/\se_i + \delta_i \nonumber
+\end{align}
+
+where $(\epsilon_i, \delta_i)$ are standard normal residuals.
+The two models are coupled by introducing a correlation $\rho = cor(\theta_i, z_i)$ by defining $(\epsilon_i, \delta_i)$ as bivariate standard normals.
+It follows that,
+%Every given study $i$ in the meta-analysis has $z_i > 0$. 
+if $\rho_i$ is large and positive and $z_i > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_i$ and $\delta_i$ and thus, the true mean $\mu$ is likely to be overestimated.
 \\
-In order to avoid potential conflicts of interests, there is a code of conduct that all entities of the Cochrane Organization have to agree on: conflicts of interest must be disclosed and possibly be forwarded to the Cochrane Center, and participation of review authors in the studies used have to be acknowledged.
-Additionally, a Steering Group publishes a report of potential conflicts of interests based on information about external funding of Cochrane Groups.
+Let $u_i = a + b/\se_i$, $\lambda(u_i)$ the Mill's ratio $\phi(u_i)/\Phi(u_i)$ ($\phi$ is the standard normal density function and $\Phi$ the cdf) and $\tilde{\rho_i} = \sigma/\sqrt(\tau^2 + \sigma_i^2) \rho_i$.
+The probability of a study being selected, given $\se_i$ and $\theta_i$, is
+
+\begin{align}
+P(\textrm{select} \given \se_i, \theta_i) = %P(a,b,s,y) = 
+\Phi\big(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i^2}}}\big) \nonumber
+\end{align}
+
+Which again shows that larger $\se_i$ and $\theta_i$ lead to a larger selection probability. It can also be shown that the expected value
+
+\begin{align}
+\mathbb{E}(\theta_i \given \se_i, \textrm{select}) = \mu + \rho_i\sigma_i\lambda(u_i) \label{eq:copas.expectation}
+\end{align}
+
+which shows that the expected value for a study is larger for larger $\sigma$. \\
+A likelihood for $\theta_i$, conditional on $z>0$ can be formulated to estimate the parameters of the model.
+Regarding $a$ and $b$, there is no way that they can be estimated because the number of missing studies and their effect sizes is not known.
+Instead, fixed values for $a$ and $b$ have to be chosen.
+The nuisance parameter $\sigma_i$ can be replaced by an estimate if the sample size in the studies is large enough. Since
+
+\begin{align}
+\textrm{Var}(\theta_i\given \se_i, z_i > 0) = \sigma_i^2 (1 - c_i^2\rho_i^2) \nonumber
+\end{align}
+
+with $c^2 = \lambda(u_i)(u_i + \lambda(u_i))$, we can replace $\sigma_i^2$ by $\hat{\sigma}_i^2 = \frac{1}{1-c_i^2\rho_i^2}$.
+Although one has to evaluate the likelihood for fixed pairs $(a,b)$, one can compare the fit of the model to evaluate which one is more suitable:
+With equation \ref{eq:copas.expectation}, one can obtain fitted values of $\theta_i$ based on $\se_i$. Also, for two different pairs $(a,b)$, $(a^\star, b^\star)$,
+
+\begin{align}
+\mathbb{E}(\theta_i\given z_i > 0, a^\star, b^\star) - \mathbb{E}(\theta_i\given z_i > 0, a, b) \approx c^\star + \rho(\lambda(a^\star) - \lambda(a))\se_i \nonumber
+\end{align}
+
+and that local departures of $\theta_i$ can be approximated by adding a linear term in $\se_i$ to the expectation of $\theta_i$.
+Thus, to test a pair $(a,b)$, it is sufficient to test $\beta \neq 0$ in
+
+\begin{align}
+\theta_i &= \theta + \beta \se_i + \sigma_i \epsilon_i \nonumber
+\end{align}
+
+with restriction that $\rho \geq 0$.
+To test some pair $(a,b)$ against the scenario with no selection, we set $a^\star = \infty$ (or $\rho = 0$).
+A likelihood ratio test will give a test statistic to test against $H0 =$ no selection:
+
+\begin{align}
+\chi^2 &= 2\cdot(\operatorname*{max1}_{\theta, \tau, \beta}\tilde{L}(\theta, \tau, \beta) - \operatorname*{max}_{\theta, \tau}\tilde{L}(\theta, \tau, 0)) \label{eq:copas.small.study}
+\end{align}
+
+with 
+\begin{align}
+\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta \se_i)^2}{(\tau^2 + \sigma_i^2)}] \nonumber
+\end{align}
+
+$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$-value.
+Note that the test is almost equivalent to Egger's small study effect test with $\tau^2 = 0$.
+Thus, although the copas selection model models publication bias, it is dependent on the small study effects to find the most suitable pair $(a,b)$.
 \\
-In order for keeping the reviews up-to-date, they are revised in a two-year circle with exceptions.
-In addition to inclusion of new evidence in a field, the revision and maintenance process may as well includes change in analysis methods.
-This can reflect some advance in clinical science as for example new information about important subgroups, as well as new methods for conducting a Cochrane Review.
-However, there are no clear guidelines and the Cochrane Groups are free in the rate and extent of up-dating their reviews.
+If one applies the model to a single meta-analysis, a sensitivity analysis is suggested.
+One can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process.
+Selection models are in general not recommended for inference (\eg \citet{selection.assessment}).
+\citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes. \\
+A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \ref{eq:copas.small.study} is applied.
+If all obtained $p$-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for modelling, and the standard, classical random effects meta-analysis is retained.
+If none of the $p$-values is above the threshold, a wider range of values for $(a,b)$ is used.
+When some $p$-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the least intense underlying selection model is chosen).\\
+Currently, there is no test to detect miss-specifications in the model itself, the authors themselves have argued that a non-parametric test of the residuals would lack power.
 
-\subsection{Methods for Cochrane Reviews}
-A research question defines the following points: ``the types of population (participants), types of interventions (and comparisons), and the types of outcomes that are of interest''.
-From the research question, usually the eligibility criteria follow.
-Usually, outcomes are not part of eligibility criteria, except for special cases such as adverse effect reviews.
+\section{Transformation between effect sizes} \label{sec:transformation.effectsizes}
+Assuming that binary outcomes result from a dichotomization of originally continuous random variables, in this case, the logistic distribution, a transformation from typical binary effect measures to Cohen's $d$ can be achieved \cite[47]{Intro.meta}.
 \\
-The type of study is an important eligibility criterium.
-The Cochrane Collaboration focuses ``primarily on randomized controlled trials'', and also, the methods of study identification in literature search are focused on randomized trials.
-Furthermore, study characteristics such as blinding of study operators with respect to treatment and cluster-randomizing might be additional eligibility criteria which have to be chosen by the review authors.
+Let $\theta$ be a log odds ratio and $s$ it's standard error. Cohen's $d$ and it's variance $s_d^2$ is obtained by
+
+\begin{align}
+d &= \theta \frac{\sqrt{3}}{\pi} & s_d^2 =  \se^2\frac{\sqrt{3}}{\pi} \nonumber
+\end{align}
+
+The factor $\frac{\pi}{\sqrt{3}} = 1.81$ is the standard deviation of the logistic distribution $L(\mu, \eta)$ with scale parameter $\eta = 1$, so we just divide the log odds ratio and it's variance through the standard deviation.
+The approximation works only well if $e_t$ and $e_c$ are not very small, especially in the case of $s_d^2$.
+Plugging in the observed log odds ratio $\hat{\theta}$ and $\hat{\se}^2$ will give an estimate of Cohen's $d$.\\
+Pearson's correlation can be attained by the formulas (\citet{olkin1985dtor}, \cite[48]{Intro.meta})
+
+\begin{align}
+r &= \frac{d}{\sqrt{d^2 + a}} & a = (n_c + n_t)^2 / n_c n_t \nonumber
+\end{align}
+where $a$ is a correction factor if $n_t \neq n_c$. The variance of $r$, $s_r^2$ is computed by
+\begin{align}
+s_r^2 &= \frac{a^2 s_d^2}{(d^2 + a)^3} \nonumber
+\end{align}
+
+Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $s_z^2$ by using
+\begin{align}
+z &= 0.5 \ln\big(\frac{1 + r}{1 - r}\big) & \nonumber
+s_z^2 &= \frac{1}{n-3}
+\end{align}
+
+%SIMPLE LINEAR REGRESSION
+% \begin{align}
+% \hat{\mathbf{\beta}} &= (\mathbf{X}^\top  \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
+% \end{align}
+
+% There is a closed form solution for $\hat{\beta_0}, \hat{\beta}_1$ that minimize the sum of squares:
+% 
+% \begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} & 
+% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
+% \end{align}
+% 
+% $\bar{x}, \bar{y}$ denotes the sample mean of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$.
+$\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the fitted line.
+Let $\hat{y}_i = \beta_0 + \beta_1 x_i$ and $e_i = y_i - \hat{y}_i$.
+The variances $\se^2_\beta$
+% 
+% 
+% 
+% To test whether the intercept or the slope is close to a certain value, a $t$-test can be used. Simply taking the absolute value of $\beta_0/s_\beta_0$,
+% \begin{align}
+% p &= 2(1-F(|\beta_0/s_\beta_0|)) \nonumber
+% \end{align}
+% 
+% where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom.
+The $p$-value will give the evidence against the null-hypothesis $\beta_0 = 0$.
+The procedure for $\beta_1$ is equivalent.
 \\
-After having specified the eligibility criteria, studies have to be collected.
-The central idea of systematic reviews, and also meta-analyses, is that the collected studies are a random sample of a population of studies, i.e.
-that they are representative and can be used to assess population properties.
-Therefore, the search process is crucial, as a selective search result may impose bias on the sample of studies available, making it a non-random sample.
-For this purpose, the Cochrane Groups are advised to go beyond MEDLINE !!cite!!, because a search restricted to it has been shown to deliver only 30\% to 80\% of available studies.
-``Time and budget restraints require the review author to balance the thoroughness of the search with efficiency in use of time and funds and the best way of achieving this balance is to be aware of, and try to minimize, the biases such as publication bias and language bias that can result from restricting searches in different ways.'' It is important to note that not only studies, but also study reports are occasionally used in the reviews, as they may provide useful information.
-\\
-There are different sources that are being used to search for studies. 
-\begin{itemize}
-\item The Cochrane Central Register of Controlled Trials is a source of reports of controlled trials.
-``As of January 2008 (Issue 1, 2008), CENTRAL contains nearly 530,000 citations to reports of trials and other studies potentially eligible for inclusion in Cochrane reviews, of which 310,000 trial reports are from MEDLINE, 50,000 additional trial reports are from EMBASE and the remaining 170,000 are from other sources such as other databases and handsearching.'' It includes citations published in many languages, citations only available in conference proceedings, citations from trials registers and trials results registers.
-\item MEDLINE.
-MEDLINE includes over 16 million references to journal articles.
-5,200 journals publishing in 27 languages are indexed for MEDLINE.
-PubMed gives access to a free version of MEDLINE with up-to-date citations.
-NLM gateway such as the Health Services Research Project, Meeting Abstracts and TOXLINE Subset for toxicology citations allows for search in both databases together with additional data from the US National Library of Medicine.
-\item EMBASE.
-4,800 Journals publishing in 30 languages are indexed to EMBASE, which includes more than 11 million records from 1974 onward.
-EMBASE.com also includes 7 million unique records from MEDLINE (1966 up to date) together with its own records.
-Additionally, EMBASE Classic allows access to digitized records from 1947 to 1973.
-EMBASE and MEDLINE each have around 1,800 journals not indexed in the other database.
-\item Regional or national and subject specific databases can additionally be consulted and often provide important information. Financial considerations may limit the use of such databases.
-\item General search engines such as Google Scholar, Intute and Turning Research into Practice (TRIP) database can be used.
-\item Citation Indexes.
-The database lists articles published in around 6,000 Journals with articles in which they have been cited and is available online as SciSearch.
-This form of search is known as cited reference searching.
-\item Dissertation sources. Dissertations are often listed in MEDLINE or EMBASE but one is advised to also search in specific dissertation sources.
-\item Grey Literature Databases.
-Approximately 10\% of the results in the Cochrane Database stems from conference abstracts and other grey literature.
-The Institute for Scientific and Technical Information in France provides access to entries of the previously closed System for Information on Grey Literature database of the European Association for Grey Literature Exploitation).
-Another source is the Healthcare Management Information Consortium (HMIC) database containing records from the Library and Information Services department of the Department of Health (DH) in England and the King's Fund Information and Library Service.
-The National Technical Information Service (NTIS) gives access to the results of US and non-US government-sponsored research, as well as technical report for most published results.
-References from newsletters, magazines and technical and annual reports in behavioral science, psychology and health are provided in the PsycEXTRA database which is linked to PsycINFO database.
-\end{itemize}
+% To extend the model to weighted simple linear regression is straightforward.
+Let $w_i$ be the corresponding weight that will be attributed to the pair $x_i, y_i$.
+The least squares minimization problem can be restated
+% 
+% \begin{align}
+% \operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
+% \end{align}
+% 
+% And the corresponding estimators are thus
+% 
+% \begin{align}
+% \hat{\beta_1} &= \frac{\sum_{i = 1}^n w_i(x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n w_i(x_i - \bar{x})^2} & 
+% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
+% \end{align}
+%
 
-\subsection{Structure and Content}
-The dataset consists of \Sexpr{length(unique(data$file.nr))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(data$study.name))} studies and \Sexpr{dim(data)[1]} results.
-A result compares a clinical or medical intervention or treatments to a control.
-Each study provides (multiple) results of clinical interventions.
-\\
-In Table \ref{barbiturate.row}, two results from a systematic review about effects of barbiturates are shown as they are given in the dataset.
-As can be seen, further specifications are provided by the variables in the columns.
-\\
-The comparison variable specifies \textit{what kind} of treatments or interventions are compared, the outcome variable \textit{how} it is compared, and the subgroup variable (not indicated in table) if the result belongs to a certain subgroup.
-Here, the result is of a binary type, so the counts of events in the barbiturate treatment group and the total number of participants are given in columns ``Events'' and ``Total'' and the number of events in the control group ``Events\_c'' and participants ``Total\_c''.
-A event is here death at the end of follow up.
+% LIMITMETa
+% \vspace{0mm}
+% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
+% 
+% \begin{align}
+% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
+% \end{align}
+% 
+% Letting $M \rightarrow \infty$, we obtain:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
+% \end{align}
+% 
+% Note that:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
+% \end{align}
+% 
+% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
+% 
+% \begin{align}
+% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
+% \end{align}
+% 
+% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
+% \end{align}
+% 
+% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
 
-<<echo=FALSE, results = 'asis'>>=
-print(xtable(barbi1, label = "barbiturate.row", digits = 0,
-             caption = "Example of two results as given in the dataset.
-Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
-Further descriptive variables have been ommitted"),
-      include.rownames = F, size = "scriptsize")
-@
+% \section{Basic notation}
+% The notation used here will be used throughout the chapter and exceptions will be noted.
+Let $i$ be the number of a study of a meta analysis with $n$ being the total number of studies.
+$y_{i}$ is then the effect size estimate (usually log odds ratio or mean difference) and $v_{i}$ the variance of the estimate of study $i$.
+$w_{i}$ is used for weights which are defined when necessary, and $\Delta$ usually denotes the summarized or pooled effect estimate of the meta-analysis, and $\eta$ the variance thereof.
+% 
+% \vspace{0mm}
+% In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
+% 
+% 
+% \section{Transformation between effect sizes}
+% Binary and continuous outcome measures can both be transformed into correlations and fishers z-scaled correlations in order to be compared.
+Let $\theta$ be a log odds ratio.
+A standardized mean difference $d$ (also known as Cohen's $d$) is calculated by multiplying $\theta$ with $\sqrt{3}/\pi$.
+The variance of the standardized mean difference is attained as $v_d = v_\theta \sqrt{3}/\pi$.\\
+% We get from a standardized mean difference $d$ to a correlation $r$ by using 
+% \begin{align}
+% r &= \frac{d}{\sqrt{d^2 + a}} \nonumber
+% \end{align}
+% where $a$ is a correction factor if $n_t \neq n_c, a = (n_c + n_t)^2 / n_c n_t$. The variance of $r$ is computed by using 
+% \begin{align}
+% v_r &= v_d
+% \end{align}
+% 
+% Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $v_z$ by using
+% \begin{align}
+% z &= 0.5 \ln(\frac{1 + r}{1 - r}) \nonumber
+% v_z &= \frac{1}{n-3}
+% \end{align}
+% 
+% 
+% 
+% \section{Heterogeneity}
+% In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
+This is called between study variation in contrast to within study variation (noise).
+% 
+% 
+% \vspace{0mm}
+% The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
+Let $w_i$ be the inverse of the variance and $\Delta$ be a summarized effect estimate of your choice as for example a variance-weighted mean \ref{weighted.mean}.
+Then $Q$ can be calculated as in \ref{Q.heterogeneity}
+% 
+% \begin{align}
+% \Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
+% Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
+% \end{align}
+% 
+% Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
+Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
+$1 - F(Q)$ will provide the $p$-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
+% 
+% \vspace{0mm}
+% Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
+For this purpose, $\tau^2$, the variance of true effects, can be calculated.
+$\tau^2$ is on the same scale as the effect size and reflects the absolute amount of dispersion.
+In practice, $\tau^2$ can be smaller than zero, then it is set to zero.
+% 
+% \begin{align}
+% C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
+% \tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
+% \end{align}
+% 
+% The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
+Note that their estimate can differ substantially and consequently also the estimate of the pooled effect size estimate.
+% 
+% \vspace{0mm}
+% To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
+% 
+% \begin{align}
+% I^2 &= (Q - n + 1)/Q \label{I2.proportion}
+% \end{align}
+% 
+% There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
+% 
+% \section{Meta Analysis}
+% There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
+% First the fixed effect meta-analysis will be explained.
+Note that both methods can be used for continuous or dichotomous outcomes.
+For more details about the methods, see chapter 11 and 12 in \citet{metaanalysis}
+% 
+% 
+% \vspace{0mm}
+% Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
+The pooled estimate $\Delta_{f}$ of the fixed effects model is then the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
+The variance $\eta_{f}$ is the reciprocal of the sum of the weights as shown in \ref{reciproce.variance}.
+% 
+% \begin{align}
+% \Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
+% \eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
+% \end{align}
+% 
+% The computation of random effects meta-analysis is more complicated.
+Random effects meta-analysis will give smaller studies with larger variance more weight in the pooled estimate.
+Shortly, the idea is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
+% 
+% \vspace{0mm}
+% The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
+It is used to calculate a new weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
+The variance of $\Delta_{r}$, $\eta_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
+% 
+% \begin{align}
+% v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
+% \Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
+% \eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
+% \end{align}
+% 
+% A $p$-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
+% 
+% \begin{align}
+% Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
+% p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
+% \end{align}
+% 
+% \section{Small Study Effects Tests}
+% One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
+If this is not given, one often speaks of publication bias.
+In fact, there can also be other reasons for this (see discussion section).
+A more appropriate term for the phenomenon is small study effect.
+If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
+% 
+% \subsection{Continuous Outcome Tests}
+% % Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. 
+% % First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
+% 
+% \subsubsection{Begg and Mazumdar: Rank Correlation Test}
+% \citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+% A standardized effect size $y_{i}^\star$ can be computed as in \ref{begg.stand.eff}.
+$v_{i}^\star$ is the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
+$\Delta_{f}$ is the pooled estimate for fixed effect estimate defined in \ref{weighted.mean}.
+% 
+% \begin{align}
+% y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff} \\
+% v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} 
+% \end{align}
+% 
+% A rank correlation test based on Kendall's tau is then used.
+The pairs $(y_{i}^\star, v_{i}^\star)$ that are ranked in the same order are enumerated.
+Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (\eg larger standardized effect size and smaller variance).
+Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
+% 
+% \begin{align}
+% Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
+% \end{align}
+% 
+% The changes in the case of ties are negligible \cite[410]{begg.ties}.
+% 
+% \subsubsection{Egger's Test: Linear Regression Test}
+% Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
+% Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope. 
+% 
+% \vspace{0mm}
+% If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
+The $p$-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
+% 
+% \begin{align}
+% p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
+% \end{align}
+% 
+% \subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{Thompson}
+% A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
+Let $\tau^2$ be equal to \ref{Tau.definition}.
+The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
+% 
+% \begin{align}
+% y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
+% \end{align}
+% 
+% Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
+Analogous to Egger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta_{0} = 0$.
+% 
+% \subsection{Dichotomous Outcomes Tests}
+% 
+% The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
+Consequently, the tests above will tend to reject the null-hypothesis too often, \ie that they are not conservative enough.
+A number of solutions to this problem are existing in the literature.
+% 
+% 
+% \subsubsection{Peters Test: Weighted Linear Regression Test}
+% A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
+% 
+% \vspace{0mm}
+% Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
+% 
+% \begin{align}
+% y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
+% v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
+% \end{align}
+% 
+% and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
+Instead of taking the variance as explanatory or independent variable in regression as in Egger's Test, the inverse of the total sample size $x_{i}$ is used, and the variance $v_{i}$ is used as a weight.
+The subsequent test procedure is then identical to Egger's test.
+% 
+% \vspace{0mm}
+% Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
+% 
+% 
+% \subsubsection{Harbord's Test: Score based Test}
+% A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
+The score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
+% 
+% \begin{align}
+% r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
+% v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
+% \end{align}
+% 
+% Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
+Note that $r_{i}/v_{i}$ is also known as peto odds ratio.
+% 
+% \subsubsection{Schwarzer's Test: Rank Correlation Test}
+% \citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
+$\mathbb{E}(E_{t})$ and variance of $E_{t}$ are then estimated based on $e_{t}$.
+% 
+% \vspace{0mm}
+% The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
+% 
+% \subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
+% The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let 
+% 
+% \begin{align}
+% y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}} \\
+% v_{i} = 1/4n_{t} + +/4n_{c}
+% \end{align}
+% 
+% Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances. 
+% 
+% 
+% \section{Small Study Effect Adjustment}
+% \subsection{Trim and Fill}
+% One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
+It is a nonparametric test based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
+% %If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
+% 
+% \vspace{0mm}
+% The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
+First, $\Delta$ is estimated using a fixed or random effects model.
+Then, the $k$ effect size estimates with the smallest standard errors are trimmed, and $\Delta$ is estimated again.
+The procedure is repeated until $k$ is 0 and the funnel plot is symmetric.
+The total number of missing studies is then mirrored with respect to the final effect size estimate $\Delta$, and $\Delta$ and its standard error is then computed to obtain an unbiased estimate.
+% 
+% \subsection{Copas Selection Model}
+% 
+% A method proposed in \cite{Copas1,Copas2,Copas3} assumes that there is a population of studies of which only a part has been published dependent on the variance and size of their estimated effects.
+Studies with small variance and large effect sizes are more likely to be published than studies with large variance and small effect sizes.
+Note that small effect size means here a treatment effect close to the control effect.
+% 
+% Let $y_i$ be the effect size estimate of study $i$. Then 
+% 
+% \begin{align}
+% y_{i} \sim N(\mu_{i}, \sigma_{i}^2) \\
+% \mu_{i} \sim N(\mu, \tau^2)
+% \end{align}
+% 
+% corresponding to a standard random effects meta-analysis.
+$\mu$ is the overall mean effect, $\sigma_{i}^2$ the within study variance and $\tau^2$ the between study variance.
+This is the \textit{population model}.
+% 
+% \vspace{0mm}
+% The \textit{selection model} is defined as follows. Suppose a selection of studies with reported standard errors $s$ (likely different from $\sigma$). Only a proportion 
+% 
+% \begin{align}
+% P(\textrm{select}|s) &= \Phi(a + b/s) \label{copas.selection1}
+% \end{align}
+% 
+% of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
+\ref{copas.selection1} can be rewritten as
+% 
+% \begin{align}
+% z = a + b/s + \delta \label{copas.selection2}
+% \end{align}
+% 
+% with $\delta \sim N(0,1)$. The study with standard error $s$ is only selected if $z$ is positive. Therefore, the larger $z$, the more likely the study is selected.
+% Combining population and selection model for study $i$, we have 
+% 
+% \begin{align}
+% y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \\
+% \mu_{i} \sim N(\mu, \tau^2) \\
+% z_{i} = a + b/s_{i} + \delta_{i}
+% \end{align}
+% 
+% where $(\epsilon_{i}, \delta_{i})$ are standard normal residuals and jointly normal with correlation $\rho = cor(y_{i}, z_{i})$.
+Every given study $i$ in the meta-analysis has $z_{i} > 0$.
+If $\rho$ is large and positive and $z_{i} > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_{i}$ and $\delta_{i}$.
+Thus, the true mean $\mu$ is likely to be overestimated.
+% 
+% \vspace{0mm}
+% Let $u = a + b/s$, $\lambda(u) = \phi(u)/\Phi(u)$ ($\phi$ is the standard normal density function) and $\tilde{\rho} = \sigma/\sqrt(\tau^2 + \sigma^2) \rho$.
+The probability of a study being selected is
+% 
+% \begin{align}
+% P(\textrm{select}|s, y) = P(a,b,s,y) = \Phi(\frac{u + \tilde{\rho}((y - \mu)/\sqrt(\tau^2 + \sigma^2))}{\sqrt{1 - \tilde{\rho^2}}})
+% \end{align}
+% 
+% It can also be shown that the expected value 
+% 
+% \begin{align}
+% \mathbb{E}(y|s, select) = \mu + \rho\sigma\lambda(u) \label{copas.expectation}
+% \end{align}
+% 
+% which shows that the expected value for a study is larger for larger $\sigma$. 
+% 
+% \vspace{0mm}
+% One can compute a likelihood function based on the distribution of $y$ conditional on $z > 0$.
+The likelihood can be maximized for any given pair $a,b$ (can not be estimated since the number of missing studies is not known), and a maximum likelihood estimate $\hat{\mu}$ for the true mean $\mu$ can be obtained.
+One can then perform a sensitivity analysis.
+First, one looks how $\hat{\mu}$ changes for different values of $a,b$.
+One can then compare the fitted values in \ref{copas.expectation} with the real values.
+To test the fit of the model (while keeping all other parts unchanged), the model can be extended in the following way :
+% 
+% \begin{align}
+% y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
+% \end{align}
+% 
+% If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
+Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
+The $p$-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
+% 
+% \vspace{0mm}
+% To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
+% 
+% \vspace{0mm}
+% In practice, only a range of values for $a,b$ are reasonable.
+For those values, the quantities above can be calculated and illustrated.
+Values for $\mu$ that have $p$-values over a predefined significance threshold can be used for inference of the effect size.
+% 
+% \subsection{Adjustment by Regression}
+% There are multiple ways to adjust for small study effects by regression.
+The general idea is to extrapolate the effect size of a study with a variance of zero based on the given effects and variances.
+% 
+% \citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
+Similarly to what has been seen in Copas selection model, we let $y_{i}$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_{i}}$ as in \ref{limitmeta.regression}.
+% 
+% \begin{align}
+% y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{v_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
+% \end{align}
+% 
+% $\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
+% 
+% \begin{align}
+% \mathbb{E}((y_{i} - \beta_{0})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{ if } \sqrt{v_{i}} \rightarrow \infty \label{limitmeta.infinitesample} \\
+% \mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
+% \end{align}
+% 
+% After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before \eg in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test (see \ref{Thompson}).
+% 
+% \vspace{0mm}
+% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
+% 
+% \begin{align}
+% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
+% \end{align}
+% 
+% Letting $M \rightarrow \infty$, we obtain:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
+% \end{align}
+% 
+% Note that:
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
+% \end{align}
+% 
+% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
+% 
+% \begin{align}
+% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
+% \end{align}
+% 
+% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
+% 
+% \begin{align}
+% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
+% \end{align}
+% 
+% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
 
-A complete listing of the variables of a result is given in Table \ref{variable}.
-They can roughly be separated into variables that \textit{specify the review} in which the result is contained and variables that \textit{specify the result} itself (separated by a horizontal line in Table \ref{variable}):
-
-\begin{table}[ht]
-  \begin{center}
-    \begin{tabular}{l l}
-      \textbf{Variable} & \textbf{Description}\\
-      \hline
-      \texttt{file.nr} & The number of the file from which the review data has been \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
-      \texttt{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
-      \texttt{file.index} & Internal index of the file in the Cochrane library.\\
-      \texttt{file.version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
-      %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
-      \hline
-      \texttt{study.name} & Name of the study to which the result belongs\\
-      \texttt{study.year} & Year in which the study was published\\
-      \hline
-      \texttt{comparison.name/.nr} & Specification of the interventions compared in the study  \\ &and a unique number for the comparison\\
-      \texttt{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ &and a unique number for the outcome\\
-      \texttt{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a \\ &unique number for the subgroup\\
-      \texttt{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
-      \texttt{effect} & Measure of the effect given in the quantity denoted by \\ &\texttt{outcome measure}.\\
-      \texttt{se} & Standard error of the measure of the effect,\\
-      \texttt{events1/events2} & The counts of patients with an outcome \textit{if}\\ &measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
-      \texttt{total1/total2} & Number of patients in groups.\\
-      \texttt{mean1/mean2} & Mean of patient measurements \textit{if} outcome is continuous.\\
-      \texttt{sd1/sd2} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
-    \end{tabular}
-  \caption{Dataset variable names and descriptions  \label{variable}}
-
-  \end{center}
-\end{table}
-
-Results are part of studies that are again part of a (systematic) review. This structure of a review is shown in Figure \ref{review}.
-
-\begin{figure}
-\tikzstyle{every node}=[draw=black,thick,anchor=west]
-\tikzstyle{selected}=[draw=red,fill=red!30]
-\tikzstyle{optional}=[dashed,fill=gray!50]
-\begin{tikzpicture}
-[grow = right, anchor = west, 
-  growth parent anchor=east, % added code
-  parent anchor=east]
-  \node {Review} [edge from parent fork right]
-    child { node {Comparison 2}
-      child { node {Outcome 2}}
-      child { node {Outcome 1}
-        child { node {Subgroup 2}}
-        child { node {Subgroup 1}
-          child  { node {Result 2}}
-          child  { node {Result 1}}
-          }}
-    }
-    child [missing] {}		
-    child { node {Comparison 1  }};
-\end{tikzpicture}
-\caption{Structure of a hypothetical review with two different comparisons\label{review.structure}}
-\label{review.structure}
-\end{figure}
-
-\vspace{0mm}
-The structure of a review will now be outlined based on an example of the dataset.
-Let us consider the previously mentioned barbiturate and head injury review.
-The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates''.
-\\
-%Since there are arguments for and against use of barbiturates, the authors of the review did a comprehensive literature search and collected all available study findings. 
-The review comprises five studies in total.
-Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental.
-The studies have different outcomes, for example, death or death and severe disability at follow up, but also dropout counts or adverse effects (secondary outcomes).
-We have continuous (e.g.
-mean body temperature) and binary outcome data (e.g.
-death/no death).
-One study split up outcomes for patients with and without haematoma, which would be subgroups.
-Thus, it is important not to confuse results with studies.
-A study can contribute multiple results to a systematic review, for example, primary and secondary outcomes and adverse effects.
-
-<<echo=FALSE, results='asis'>>=
-print(xtable(barbi2, label = "barbiturates", caption = "Barbiturate and head injury review.
-In the columns, study names, comparison and outcome measure of the results are given"), include.rownames = F, size = "footnotesize")
-@
-
-Information about missing values in the dataset is given in Table \ref{missing}.
-For variables as research subject, outcome and subgroup name and event counts there are no missing values.
-The relative amount of missing values is very low except for study years.
-For continuous outcomes, the cases have been counted were no treatment effect and standard error is available: neither mean values and standard deviations, nor mean differences and standard error.
-Also Study years before 1920 and after 2019 are declared as missing, as well as sample sizes below zero.
-
-<<echo=FALSE, results='asis'>>=
-print(xtable(missing.table, label = "missing", caption = "Number of missing variables and measurements in the dataset", align = "lr"), include.colnames = F,
-      size = "footnotesize", digits = 0)
-@
-
-The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = \Sexpr{publication.year.range[1]}).
-The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{publication.year.range[5]} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}.
-Only a handful ($n = 18$) have been published in 2018, none in 2019.
-\\
-%No information is available concerning unpublished results and studies.
-The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}.
-One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (> 65\%).
-
-<<echo=FALSE, results='asis'>>=
-print(xtable(outcome.measure.frequencies, label = "outcome.measure.frequencies", 
-             caption = "Frequencies of outcome measures among results. n denotes the total number 
-             of results with the outcome measure and percentage the percentage of the outcome measure,", 
-             align = "llll", digits = 1), include.rownames = F, size = "footnotesize")
-@
-
-The sample sizes among results vary to some extent.
-There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, the 5\% quantile.
-The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{treatment.group.size.range[5]} and the third quartile \Sexpr{treatment.group.size.range[4]}.
-The large difference between median and mean is caused by very large groups with over 2,000,000 participants.
-Analogously, the quantiles of the total sample size are: 5\% quantile = \Sexpr{samplesize.range[1]}, first quartile = \Sexpr{samplesize.range[2]}, median = \Sexpr{samplesize.range[3]} and third quartile = \Sexpr{samplesize.range[4]}.
-The mean is \Sexpr{samplesize.range[5]}.
-\\
-The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}.
-There are \Sexpr{comp.range[1]} reviews with five or fewer results, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}.
-Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]}.
-The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1497 results in total.
-\\
-For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome.
-More specifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis, since their research subject and experimental setup can be considered sufficiently homogeneous.
-Importantly, this distinction is also used by the Cochrane Organization itself, i.e.
-the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\%Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
-The dataset is divided in meta-analyses with identical experimental setup. The size of a meta-analysis denotes how many results are included in a group.
-Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results. Practically, this number of meta analyses can be performed, with each having at least $n$ results:
-
-<<echo=FALSE, results='asis'>>=
-
-print(xtable(cum.repr.trials.subg, label = "repr.groups", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
-@
-
-\section{Data Tidying and Processing} \label{sec:Processing}
-The original dataset was provided by .. (some words how the dataset was obtained and processed by C.R.). \\
-The information in the previous pages are from a tidied and processed version of this dataset. \\
-
-\subsection{Modification of old variables}
-In some cases, reasonable assumptions led to small changes in the originally provided variables:
-\begin{itemize}
-\item \texttt{study.year}: It was assumed that studies that are declared to have been published before 1920 ($n$ = \Sexpr{length(which(data$study.year < 1920))}) are mis-specified, as well as after 2019 ($n$ = \Sexpr{length(which(data$study.year > 2019))}), so these have been set to NA.
-\item \texttt{mean1} and \texttt{mean2}: When both \texttt{mean1} and \texttt{mean2} are equal to zero or NA, \texttt{outcome.measure.new} is equal to \texttt{(Std.) Mean Difference}, but a mean difference is given in \texttt{effect}, \texttt{mean1} is set equal to \texttt{effect} ($n$ = \Sexpr{length(nomeans.ind)}).
-\end{itemize}
-
-\subsection{Newly Introduced Variables}
-Some new variables are added to the obtained dataset:
-\begin{itemize}
-\item \texttt{outcome.measure.new}: Outcome measure specifications given in \texttt{outcome.measure} were standardized whenever they were supposed to denote the same outcome measure.
-An example would be the formally different notations for odds ratios: ``Odds Ratio'', ``odds ratio'', ``OR'', which were all denoted as ``Odds Ratio''.
-\item \texttt{outcome.type}: A simplification of \texttt{outcome.measure.new}.
-The outcome.type ``bin'' indicates if \texttt{outcome.measure.new} is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
-``cont'' is equivalent to \texttt{outcome.measure.new} equal to "Std.
-Mean Difference'' or ``Mean Difference''.
-``surv'' equal to ``Hazard Ratio'' and ``rate'' equal to ''Rate Ratio'' or ``Rate Difference''.
-\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.type ``bin''.
-\item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.type ``cont''.
-If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.new} was equal to ``Std.
-Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  \Sexpr{length(inpute.given.ind)}).
-\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.type ``bin''.
-\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.type ``bin'') or $g$ (for outcome.type ``cont'') to $r$ transformation.
-\item \texttt{z} and \texttt{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
-\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.type ``cont'' or Wald test for outcome.type ``bin''.
-\item \texttt{events1c} and \texttt{events2c}: Correction of \texttt{events1} and \texttt{events2} zero event counts or event counts = patient number.
-When no events occurred, 0.5 was added, and when all patients experienced the event, 0.5 was subtracted.
-When one of \texttt{events} had zero counts while the other had maximum counts, no adjustment occurred.
-\item \texttt{meta.id}: Meta-analysis ID variable to uniquely identify any potential meta-analysis in the dataset.
-Consistent to what has been discussed before, all results that share a common comparison, outcome and subgroup (optional, subgroups not given in any case) may be combined in a meta-analysis.
-% \item \texttt{}:
-% \item \texttt{}:
-\end{itemize}
-
-\subsection{Eligibility criteria for Publication Bias Test and Adjustment} 
-Initially, the analysis is restricted to binary, continuous and survival outcomes. More formally:
-\begin{itemize}
-\item \textbf{Outcome measures}: The analysis has been restricted on the following outcome measures (from \texttt{outcome.measure.new}): ``Odds Ratio'', ``Risk Ratio'', ``Risk difference'', ``Peto Odds Ratio'', ``Std.
-Mean Difference'', ``Mean Difference'', ``Hazard Ratio''
-($n$ = \Sexpr{length(data.ext2$outcome.type[which(data.ext2$outcome.type == "bin" | data.ext2$outcome.type == "cont" | data.ext2$outcome.type == "surv")])} out of a total of \Sexpr{length(data.ext2$outcome.type)} results)
-\end{itemize}
-
-The suggestions of criteria for eligibility for publication bias tests of \citet{Ioannidis2007} have largely been followed:
-\begin{itemize}
-\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = \Sexpr{m.a.largerten.number} remaining). 
-\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = \Sexpr{m.a.smaller.5.number} remaining).
-\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = \Sexpr{m.a.variance4.number} remaining).
-\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = \Sexpr{m.a.one.sig.number} remaining)
-\end{itemize}
-
-After having excluded meta-analyses with less than ten studies, additional criteria for excluding inconvenient meta-analyses are:
-\begin{itemize}
-\item \textbf{Sensitivity Analyses}: When the same results are used multiple times for different meta-analyses, only one is retained.
-More precisely, if a study hat the same \texttt{study.name} and same \texttt{effect}, it was considered a duplicate, and the smaller meta-analysis of the two was excluded.
-The intention is to exclude sensitivity analyses which are operated on subsets of the available results.
-\item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = \Sexpr{all.zero.events.number} out of meta-analyses with at least ten studies).
-\item \textbf{Missing means and sd's}: In the case of continuous outcomes, meta-analyses with means and sd's in any group being equal to zero are excluded ($n$ = \Sexpr{all.zero.means.number} out of meta-analyses with at least ten studies).
-\item \textbf{Single patient data}: Meta-analyses that are comprised of single patient data are excluded ($n$ = \Sexpr{m.a.singlepatient.number} out of meta-analyses with at least ten studies)
-\end{itemize}
-
---Make Flowchart--
-
-\subsubsection{Exclusions due to Computational Errors}
-In exceptional cases, the applied meta-analysis methods and publication bias tests and adjustment algorithms failed due to various reasons.
-Here, those cases are listed and if known, the reasons why computation failed are given.\\
-\textbf{Binary Outcomes}: Out of the meta-analyses that are of \texttt{outcome.type} bin, and have at least ten studies, two studies hat to be excluded:
-\begin{itemize}
-\item meta.id = 62301 (file.nr = 1531, comparison.nr = 8, outcome.nr = 6, subgroup.nr = 1):
-%A subgroup analysis for women with increased adverse pregnancy outcomes, where the effect of vitamin C supplements is tested on pre-eclampsia: 
-Largest study (se = 0.1) has risk ratio 1 and smallest study (se = 1) risk ratio 0.07. Copas publication bias adjustment methods has likelihood optimization issues.
-\item meta.id = 94519 (2519, 14, 1, 2): Largest study (se = 0.05) has risk ratio 0.9 and smallest study (se = 0.4) risk ratio 3.
-Again Copas publication bias adjustment methods has likelihood optimization issues.
-\end{itemize}
-
-There were no issues with \texttt{outcome.type} ``cont'' and ``surv''.
-For the subsequent information, it is important to know that meta-analyses are only repeated with Hedges $g$, Pearson correlation coefficient and Fisher's Z-scores, if the outcome type is not survival and all of the above criteria are met ($n$ = \Sexpr{length(meta.f$n.sig.type[which(meta.f$outcome.type != "surv")])}).
-\\
-\textbf{Pearson Correlation Coefficient}: Three studies had to be excluded when analyzing the Pearson correlation coefficients:
-\begin{itemize}
-\item meta.id = 157083 (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2): A meta-analysis with all results from the same study, and equal sample size (5 each group).
-The Copas selection model algorithm issued an error when optimizing the likelihood.
-\item meta.id = 159329 (5183, 3, 13): One very small study with group sizes of 2 and 1 patients and small risk ratio of 0.222 (compared to the largest of 1.05, se = 0.04).
-Also, the Copas selection model algorithm issued an error when optimizing the likelihood.
-\item meta.id = 182298 (6211, 1, 8, -): One very small study with 8 patients in each group and 0 event counts in both.
-The Copas selection model algorithm issued an error when optimizing the likelihood.
-\end{itemize}
-
-\textbf{Fisher's Z score}: The same issues as encountered for Pearson correlation coefficients (meta.id = 157083 and 159329).
-The variance of the z score $s_z^2$ can be calculated as:  $s_z^2 = \frac{1}{n-3}$, $n$ being the total sample size.
-Thus, studies that have total sample size $n \geq 3$ are discarded in the meta-analyses ($n$ = \Sexpr{total.seq3.number} studies).
-\Sexpr{m.a.seq3.seq10.number} meta-analyses have then less than 10 studies left for pooling:
-\begin{itemize}
-\item meta.id = 10671: (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2), 7 studies left.
-\item meta.id = 43324: (1019, 1, 3, 2), 9 studies left.
-\end{itemize}
-
-\subsubsection{The Publication Bias Test and Adjustment Dataset}
-The dataset that was ultimately tested and adjusted for publication bias comprises \Sexpr{dim(metac)[1]} meta-analyses and \Sexpr{dim(meta.data)[1]} results. ..
-
-% \begin{itemize}
-% \item meta.id = 136563 (4218, 1, 1, 1): ``Roberts 2010'' (3)
-% \item meta.id = 136566 (4218, 1, 3, 1): ``Roberts 2010'' (3)
-% \end{itemize}
-
-%which leads to a reduction of the meta-analyses that can be calculated based on the Fisher's z score by $n$ = \Sexpr{}
+% \begin{align} \label{cox reg}
+% P(Y < y|\mathbf{x}) = 1 - exp(-exp(h(y) - (\mathbf{x})^\top\beta)
+% \end{align}
+% 
+% See \cite{hothorn} for further information. It specifies the instantaneous risk of an event at time t to be
+% 
+% \begin{align}
+% \lambda_{0}(t)exp((\mathbf{x})^\top\beta) \nonumber
+% \end{align}
+% 
+% The model is regarded as a semi parametric model since it includes the covariates in a linear fashion but leaves the baseline hazard $\lambda_{0}(t)$ unspecified.
+The factor $exp((\mathbf{x})^\top\beta)$ has the interpretation of a hazard ratio between the reference with $\mathbf{x} = 0$.
+The formal definition of the hazard is
+% 
+% \begin{align}
+% h(t) = \lim_{h \to 0} \frac{P(t < T < t + h| T > t)}{h}
+% \end{align}
+% 
+% 
+% \begin{align} \label{generalized linear model}
+% \mathbf{Y}{_{ij}}|U{_i},\epsilon{_{ij}} = (1,x{_i}^\top)\beta + U{_i} + \epsilon{_{ij}}
+% \end{align}

### 2019-07-05 report/chapter03.Rnw
adjustments after correction

@@
 
-<<'preamble03',include=FALSE, echo=FALSE>>=
+<<echo=FALSE>>=
 library(knitr)
-opts_chunk$set(fig.path='figure/ch03_fig',
+opts_chunk$set(
+    fig.path='figure/ch02_fig',
+    self.contained=FALSE,
+    cache=TRUE
+)
+@
+
+<<echo=FALSE>>=
+library(knitr)
+opts_chunk$set(fig.path='figure/ch02_fig',
                echo=TRUE, message=FALSE,
                fig.width=8.1, fig.height=3,
-               self.contained = FALSE,
                out.width='\\textwidth-3cm',
@@
 
-<<'Data03', echo=FALSE, warning=FALSE>>= 
+<<echo = FALSE, warning=FALSE, message=FALSE>>=
 rm(list = ls())
@@
 
-require(corrgram)
+###################################################################################################################
+###################################################################################################################
 
-# data.ext2 <- pb.process2(data)
-@
+#Barbiturate Examples
+barbi1 <- arrange(filter(data, file.nr == 21) %>% 
+          select(Study = study.name, Comparison = comparison.name, Outcome = outcome.name, 
+                 Events = events1, Total = total1, Events_c = events2, Total_c = total2) %>% 
+            slice(c(1,3)), Study) 
+barbi2 <- arrange(filter(data, file.nr == 21) %>% 
+          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study)
+barbi2[barbi2$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
 
-\chapter{Results} \label{ch:Results}
+#Missing values
+cont.out <- data %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
+                                 outcome.measure.new == "Hedges' G")
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+missing.mean <- which(is.na(cont.out$mean1) | is.na(cont.out$mean2))
+missing.effect <- which(is.na(cont.out$effect))
+missing.means <- intersect(missing.mean, missing.effect) #Cont. results that have neither complete means nor an effect
+wrong.effect <- which(cont.out$mean1 == 0 & cont.out$mean2 == 0 & cont.out$effect == 0) #Cont.results that have only zeros
+missing.effects <- length(c(missing.means, wrong.effect))
 
-\section{Small Study Effect and Excess of Significance Tests} \label{sec:publication.bias.tests}
-<<echo=FALSE, warning=FALSE>>=
-sig.level <- 0.1
-meta.f <- meta.f %>% 
-	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
-				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
-				 begg.test = ifelse(pval.begg < sig.level, 1, 0),
+missing.sd <- which(is.na(cont.out$sd1) | is.na(cont.out$sd2))
+missing.se <- which(is.na(cont.out$se))
+missing.sds <- intersect(missing.se, missing.sd) #Cont. results that have neither complete means nor an effect
+wrong.sds <- which(cont.out$sd1 == 0 & cont.out$sd2 == 0 & cont.out$se == 0) #Cont.results that have only zeros
+missing.sds <- length(c(missing.sds, wrong.sds))
 
-				 tes.d.test = ifelse(pval.d.tes < sig.level, 1, 0),
+missing.ss <- which(is.na(data$total1) | is.na(data$total2))
+wrong.ss <- which(data$total1 <= 0 | data$total2 <= 0)
+missing.ssize <- length(c(missing.ss, wrong.ss))
 
-				 schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
-				 rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
-				 harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
-				 peter.test = ifelse(pval.peter < sig.level, 1, 0))
+missing.year <- sum(is.na(data$study.year)) + length(c(which(data$study.year < 1920), which(data$study.year > 2019)))
 
-meta.bin <- meta.f %>% filter(outcome.type == "bin")
-meta.cont <- meta.f %>% filter(outcome.type == "cont")
-meta.surv <- meta.f %>% filter(outcome.type == "surv")
+missing.table <- rbind("Missing mean values and mean differences" = missing.effects,
+                         "Missing standard deviations and standard errors" = missing.sds,
+                         "Missing sample sizes" = missing.ssize,
+                         "Missing study year" = missing.year)
 
-#Agreement proportions of publication bias tests:
+#Mean and median number of different outcome types of reviews
+mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
+  ungroup() %>% group_by(file.nr) %>%
+  count() %>% ungroup %>% summarise(mean = mean(n))
 
-#Binary:
-meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
-                                              tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
-                                              tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
-                                              tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
-                                              schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
-                                              schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
-                                              schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
-                                              rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
-                                              rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
-                                              harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
-agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
-                                                      tes.d.peter = sum(tes.d.peter == "agree")/n(),
-                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
-                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
-                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
-                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
-                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
-                                                      rucker.peter = sum(rucker.peter == "agree")/n(),
-                                                      harbord.peter = sum(harbord.peter == "agree")/n())
-meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test + schwarzer.test > 1, "agree", "disagree"),
-                                              tes.d.peter = ifelse(tes.d.test + peter.test > 1, "agree", "disagree"),
-                                              tes.d.rucker = ifelse(tes.d.test + rucker.test > 1, "agree", "disagree"),
-                                              tes.d.harbord = ifelse(tes.d.test + harbord.test > 1, "agree", "disagree"),
-                                              schwarzer.peter = ifelse(schwarzer.test + peter.test > 1, "agree", "disagree"),
-                                              schwarzer.rucker = ifelse(schwarzer.test + rucker.test > 1, "agree", "disagree"),
-                                              schwarzer.harbord = ifelse(schwarzer.test + harbord.test > 1, "agree", "disagree"),
-                                              rucker.peter = ifelse(rucker.test + peter.test > 1, "agree", "disagree"),
-                                              rucker.harbord = ifelse(rucker.test + harbord.test > 1, "agree", "disagree"),
-                                              harbord.peter = ifelse(harbord.test + peter.test > 1, "agree", "disagree"))
-agreement.sig.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/sum(tes.d.test),
-                                                      tes.d.peter = sum(tes.d.peter == "agree")/sum(tes.d.test),
-                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/sum(tes.d.test),
-                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/sum(tes.d.test),
-                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/sum(schwarzer.test),
-                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/sum(schwarzer.test),
-                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/sum(schwarzer.test),
-                                                      rucker.peter = sum(rucker.peter == "agree")/sum(rucker.test),
-                                                      harbord.peter = sum(harbord.peter == "agree")/sum(peter.test))
+median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
+  ungroup() %>% group_by(file.nr) %>%
+  count() %>% ungroup %>% summarise(mean = median(n))
 
-binary.tests.agreement <- rbind(agreement.bin, agreement.sig.bin)
-rownames(binary.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
-colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
-                                      "Excess significance, Rucker", "Excess significance, Harbord",
-                                      "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
-                                      "Rucker, Peter", "Harbord, Peter")
-#--------------------------------------------------------------------------------------------------------------------#
+#Study.year quantiles:
+#data.ext2 <- data.ext %>% mutate(study.year = ifelse(study.year > 1920, study.year, NA))
+publication.year.range <- c(quantile(data.ext2$study.year, 0.05, na.rm = T), quantile(data.ext2$study.year, 0.25, na.rm = T), 
+                            quantile(data.ext2$study.year, 0.5, na.rm = T), quantile(data.ext2$study.year, 0.75, na.rm = T),
+                            round(mean(data.ext2$study.year, na.rm = T), 2), quantile(data.ext2$study.year, 0.95, na.rm = T))
 
-#Continuous:
-meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
-                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
-                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
-                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
-                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
-                                                         egger.begg = sum(egger.begg == "agree")/n())
-meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
-agreement.sig.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
-                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
-                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
-                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
-                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
-                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))
+#Outcome.measure frequency table:
+outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.new) %>% count() %>% 
+                                       arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9),
+                                     data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% 
+                                       ungroup() %>% filter(row_number() > 8) %>% 
+                                       summarise(outcome.measure.new = "other", n = sum(n)))
 
-cont.tests.agreement <- rbind(agreement.cont, agreement.sig.cont)
-rownames(cont.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
-colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson",
-                                     "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")
+outcome.measure.frequencies <- outcome.measure.frequencies %>% mutate(percentage = round(n/sum(n),3)*100)
+names(outcome.measure.frequencies) <- c("Outcome measure", "n", "Percentage")
+outcome.measure.frequencies$Percentage <- paste(outcome.measure.frequencies$Percentage, "%", sep = "")
 
-#--------------------------------------------------------------------------------------------------------------------#
+#Total and group size quantiles:
+data.ext2 <- data.ext2 %>% ungroup() %>%  mutate(total.n = total1 + total2)
+samplesize.range <- c(quantile(data.ext2$total.n, 0.05, na.rm = T), quantile(data.ext2$total.n, 0.25, na.rm = T), 
+                            quantile(data.ext2$total.n, 0.5, na.rm = T), quantile(data.ext2$total.n, 0.75, na.rm = T),
+                            round(mean(data.ext2$total.n, na.rm = T), 2), quantile(data.ext2$total.n, 0.95, na.rm = T))
+treatment.group.size.range <- c(quantile(data.ext2$total1, 0.05, na.rm = T), quantile(data.ext2$total1, 0.25, na.rm = T), 
+                      quantile(data.ext2$total1, 0.5, na.rm = T), quantile(data.ext2$total1, 0.75, na.rm = T),
+                      round(mean(data.ext2$total1, na.rm = T), 2), quantile(data.ext2$total1, 0.95, na.rm = T))
 
-#Survival:
-meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
-                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
-                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
-                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
-                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
-                                                         egger.begg = sum(egger.begg == "agree")/n())
-meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
-agreement.sig.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
-                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(thompson.test),
-                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(begg.test),
-                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
-                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
-                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))
+#Frequencies of results:
+comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
+comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
+                      quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
+                      round(mean(comp.freq$n, na.rm = T), 2), quantile(comp.freq$n, 0.95, na.rm = T))
 
-surv.tests.agreement <- rbind(agreement.surv, agreement.sig.surv)
-rownames(surv.tests.agreement) <- c("Agreement (overall)","Agreement (significance)")
-colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)",
-                                    "Excess significance, Begg (survival)", "Thompson, Egger (survival)",
-                                    "Thompson, Begg (survival)", "Egger, Begg (survival)")
+#Frequencies of studies:
+study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
+study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
+                      quantile(study.freq$n, 0.5, na.rm = T), quantile(study.freq$n, 0.75, na.rm = T),
+                      round(mean(study.freq$n, na.rm = T), 2), quantile(study.freq$n, 0.95, na.rm = T))
 
-#--------------------------------------------------------------------------------------------------------------------#
+#Pooling studies
+cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
+  filter(n < 15) %>%
+  full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+               filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
+  ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
+# cum.repr.trials.nosub <- data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+#   filter(n < 15) %>%
+#   full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+#                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
+#   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
 
-#Merging:
-test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
+# cum.repr.trials <- cbind(cum.repr.trials.nosub, cum.repr.trials.subg)[,c(1,3,6)]
 
-#--------------------------------------------------------------------------------------------------------------------#
+colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
 
-test.bin <- meta.bin %>% ungroup() %>% summarize(
-																								 schwarzer.test = mean(schwarzer.test),
-																								 rucker.test = mean(rucker.test),
-																								 harbord.test = mean(harbord.test),
-																								 peter.test = mean(peter.test))
-test.bin <- test.bin %>% gather(key = "test.type", value = "mean")
+	data <- data %>% mutate(
+		outcome.type = ifelse(outcome.measure.new == "Hazard Ratio", "surv", 
+													ifelse(outcome.measure.new == "Odds Ratio" | outcome.measure.new == "Risk Ratio" |
+																 	outcome.measure.new == "Peto Odds Ratio" | outcome.measure.new == "Risk Difference", "bin", "cont")),
+		outcome.type = ifelse(outcome.measure.new == "Rate Ratio" | outcome.measure.new == "Rate difference", "rate", outcome.type),
+		lrr = NA,
+		var.lrr = NA,
+		smd = NA,
+		var.smd = NA,
+		smd.pbit = NA,
+		var.smd.pbit = NA,
+		smd.ordl = NA,
+		var.smd.ordl = NA,
+		cor.phi = NA,
+		var.cor.phi = NA,
+		pval.single = NA, 
+		cor.pearson = NA,
+		var.cor.pearson = NA,
+		z = NA,
+		var.z = NA,
+		events1c = NA,
+		events2c = NA,
+		sig.single = NA)
+	cont.ind <- which(data$outcome.type == "cont" & !is.na(data$outcome.type))
 
-p.bin <- meta.bin %>% ungroup() %>% 
-	select(schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
-	gather(key = "test.type", value = "null.hypothesis") %>%  
-	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
-	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-	theme_bw() + xlab(label = NULL) + ggtitle("Binary Outcomes") + theme(legend.position = "top") +
-	guides(fill=guide_legend(title=NULL))+
-	annotate("text", x = test.bin$test.type, y = 500, 
-					 label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
-					 color = "white")
-#--------------------------------------------------------------------------------------------------------------------#
+	data[cont.ind, "outcome.type"] <- data[cont.ind, ] %>% 
+		mutate(outcome.type = ifelse(outcome.measure.new == "Std. Mean Difference"  | outcome.measure.new == "Mean Difference", 
+																 outcome.type, NA)) %>% select(outcome.type)
 
-dat_text <- data.frame(
-  label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
-                  sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test), sum(meta.bin$tes.d.test, na.rm = T)), "< 0.1,",
-                round(c(mean(meta.bin$harbord.test), mean(meta.bin$peter.test), 
-                        mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test), mean(meta.bin$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer", "pval.d.tes"))
+	cont.ind <- which(data$outcome.type == "cont" & !is.na(data$outcome.type))
 
-labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer", pval.d.tes = "Excess Significance")
+	nomean1.ind <- which(data$outcome.type == "cont" & is.na(data$mean1))
+	nomean2.ind <- which(data$outcome.type == "cont" & is.na(data$mean2))
+	noeffects.ind <- which(data$outcome.type == "cont" & !is.na(data$effect))
+	nomeans.ind <- intersect(nomean1.ind, nomean2.ind)
+	nomeans.ind <- intersect(noeffects.ind, nomeans.ind) #no means, but a (std.) mean difference is provided.
 
-p.dist.bin <- meta.bin %>% ungroup() %>% 
-  select(pval.harbord, pval.peter, pval.rucker, pval.schwarzer, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value") %>% 
-  ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 200, label = label), color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + ggtitle("Binary Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
+	data[nomeans.ind,"mean1"] <- data[nomeans.ind,"effect"]
+	data[nomeans.ind,"mean2"] <- 0
 
-#Continuous Outcomes:
-test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-																									 begg.test = mean(begg.test),
-																									 thompson.test = mean(thompson.test))
+	data[cont.ind,] <- escalc(data = data[cont.ind,], m1i = mean1, m2i = mean2, 
+														sd1i = sd1, sd2i = sd2, n1i = total1, n2i = total2,
+														measure = "SMD" , append = T, var.names = c("smd", "var.smd"))
 
-test.cont <- test.cont %>% gather(key = "test.type", value = "mean")
+	inpute.given.ind <- which(is.na(data[cont.ind, "smd"]) & data[cont.ind, "outcome.measure.new"] == "Std. Mean Difference")
 
-p.cont <- meta.cont %>% ungroup() %>% 
-	select(egger.test, thompson.test, begg.test) %>% 
-	gather(key = "test.type", value = "null.hypothesis") %>% 
-	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
-	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-	theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
-	guides(fill=guide_legend(title=NULL))+
-	annotate("text", x = test.cont$test.type, y = 150, 
-					 label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
-					 color = "white")
-#--------------------------------------------------------------------------------------------------------------------#
+	#Counts of meta-analyses with only zeros:
+all.zero.events.number <- data.ext2 %>% filter(outcome.type == "bin") %>% 
+  group_by(meta.id) %>% 
+    mutate(n = n()) %>% filter(n >= 10) %>% 
+  filter(all(events1 == 0) & all(events2 == 0)) %>% 
+  distinct(meta.id) %>% ungroup() %>%  count()
 
-dat_text <- data.frame(
-  label = paste(c(sum(meta.cont$begg.test), sum(meta.cont$egger.test), sum(meta.cont$thompson.test), sum(meta.cont$tes.d.test, na.rm = T)), "< 0.1,",
-                round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test), mean(meta.cont$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"))
+#Counts of meta-analyses with means and sds only zeros:
+all.zero.means.number <- data.ext2 %>% filter(outcome.type == "cont") %>% group_by(meta.id) %>% 
+    mutate(n = n()) %>% filter(n >= 10) %>% filter(all(mean1 == 0) & all(mean2 == 0)) %>% 
+    filter(all(sd1 == 0) | all(sd2 == 0)) %>% distinct(meta.id) %>% ungroup() %>% count()
 
-labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp", pval.d.tes = "Excess significance")
-p.dist.cont <- meta.cont %>% ungroup() %>% 
-  select(pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value") %>% 
-  ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
-  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 60, label = label),  color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + ggtitle("Continuous Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
+#Counts of meta-analyses with n larger ten:
+m.a.largerten.number <- meta %>% filter(k > 9) %>% ungroup %>% count()
+#smaller I2 than 0.5:
+m.a.smaller.5.number <- meta %>% filter(k > 9 & I2 < 0.5) %>% ungroup %>% count()
+#variance ratio > 4:
+m.a.variance4.number <- meta %>% filter(k > 9 & I2 < 0.5) %>% filter((se.max^2)/(se.min^2) > 4) %>% ungroup %>% count()
+#At least on sig. estimate:
+m.a.one.sig.number <- meta %>% filter(k > 9 & I2 < 0.5) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(n.sig.single > 0) %>% ungroup %>% count()
+#Single patient meta-analyses:
+tmp <- data.ext2 %>% filter(outcome.type == "cont") %>% group_by(meta.id) %>% 
+	mutate(n = n()) %>% filter(n >= 10) %>% filter(!all(mean1 == 0) & !all(mean2 == 0)) %>% 
+	filter(!all(sd1 == 0) | !all(sd2 == 0))
 
-#Survival Outcomes:
-test.surv <- meta.surv %>% ungroup() %>% summarize(egger.test = mean(egger.test),
-																									 begg.test = mean(begg.test),
-																									 thompson.test = mean(thompson.test))
+meta.id.vector <- unique(tmp$meta.id)
+m.a.singlepatient.number <- length(meta.id.vector[c(which(meta.id.vector > 42716 & meta.id.vector < 42725))] )
+#How many z-score meta-analyses are excluded due to total <= 3, and how many m.a. have then n < 10:
+tmp <- data.ext2 %>% group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 9) %>%
+	filter(outcome.type != "rate" & !is.na(outcome.type))
 
-test.surv <- test.surv %>% gather(key = "test.type", value = "mean")
+metac <- meta %>% filter(k > 9) %>% filter(n.sig.single > 0) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
 
-p.surv <- meta.surv %>% ungroup() %>% 
-	select(egger.test, thompson.test, begg.test) %>% 
-	gather(key = "test.type", value = "null.hypothesis") %>% 
-	mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "significant", "not significant"))) %>% 
-	ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
-	theme_bw() + xlab(label = NULL) + ggtitle("Continuous Outcomes") + theme(legend.position = "top") +
-	guides(fill=guide_legend(title=NULL))+
-	annotate("text", x = test.surv$test.type, y = 10, 
-					 label = paste(round(test.surv$mean, 2)*100, "% rejected"), 
-					 color = "white") 
-#--------------------------------------------------------------------------------------------------------------------#
+meta.id.vector <- metac$meta.id[-which(metac$outcome.type == "surv")]
+meta.id.vector <- meta.id.vector[-c(which(meta.id.vector == 157083),
+																which(meta.id.vector == 159329),
+																# which(meta.id.vector == 12459),
+																# which(meta.id.vector == 12465),
+																# which(meta.id.vector == 22087),
+																which(meta.id.vector == 182298))]
 
-dat_text <- data.frame(
-  label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), sum(meta.surv$thompson.test), sum(meta.surv$tes.d.test, na.rm = T)), "< 0.1,",
-                round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), mean(meta.surv$thompson.test), mean(meta.surv$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"))
-p.dist.surv <- meta.surv %>% ungroup() %>% 
-	select(pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
-	gather(key = "test.type", value = "p.value") %>% 
-	ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
-	facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 10, label = label),  color = "black") + 
-	theme(strip.text.x = element_text(size=7)) + ggtitle("Survival Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
+meta.data.zscore <- tmp[which(tmp$meta.id %in% meta.id.vector),]
+total.seq3.number <- meta.data.zscore %>% filter(total1 + total2 < 4) %>% select(var.z) %>% ungroup() %>% count() 
+m.a.seq3.seq10.number <- meta.data.zscore %>% filter(total1 + total2 > 3) %>% count() %>% filter(nn < 10) %>% ungroup %>% count()
 
-#Test agreement
-agree.bin <- meta.bin %>% mutate(n.sig = peter.test + rucker.test + harbord.test + schwarzer.test) %>% 
-	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
-	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
-  xlab("Number of significant tests") + ylab("count") + ggtitle("Binary Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-agree.cont <- meta.cont %>% mutate(n.sig = egger.test + thompson.test + begg.test) %>% 
-	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
-	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
-  xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-agree.surv <- meta.surv %>% mutate(n.sig = egger.test + thompson.test + begg.test) %>% 
-	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
-	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
-  xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")
-#--------------------------------------------------------------------------------------------------------------------#
-
-################################################################################################
-################################################################################################
-#PUBLICATION BIAS TEST AGREEMENT
-################################################################################################
-################################################################################################
-
-cor.data <- meta.f %>% select(stat.rucker, stat.harbord, stat.peter, stat.schwarzer, stat.d.tes, 
-                             stat.egger, stat.thompson, stat.begg)
-colnames(cor.data) <- c("Rucker", "Harbord", "Peter", "Schwarzer", "Excess s.",  "Egger", "Thompson",
-                        "Begg")
-
-panel.pts.new <- function (x, y, corr = NULL, col.regions, cor.method, ...) 
-{
-
-  plot.xy(xy.coords(x, y), type = "p", ...)
-  box(col = "lightgray")
-  rect(xleft = -1.644854, ybottom = -1.644854, xright = 1.644854, ytop = 1.644854, density = NULL, angle = 45,
-       col = NA, border = "white", lty = 1, lwd = 1.4, 
-       ...)
-  if (!is.null(corr)) 
-    return()
-
-}
-
-# Tukey Mean difference plots;
-#--------------------------------------------------------------------------------------------------------------------#
-
-egger.thompson.plot <- meta.f %>% 
-  mutate(mean = ((logit(pval.egger)+ logit(pval.thompson)))/2, 
-         difference = logit(pval.egger) - logit(pval.thompson)) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point() + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + theme(legend.position = "none") +
-  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
-                     values = c("red", "blue")) +
-  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value Thompson)" )))
-#--------------------------------------------------------------------------------------------------------------------#
-
-egger.excess.plot <- meta.f %>% 
-  mutate(mean = ((logit(pval.egger)+ logit(pval.d.tes)))/2, 
-         difference = logit(pval.egger) - logit(pval.d.tes)) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point() + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + theme(legend.position = "none") +
-  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
-                     values = c("red", "blue")) +
-  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value excess significance)" )))
-#--------------------------------------------------------------------------------------------------------------------#
-
-harbord.rucker.plot <- meta.f %>% 
-  mutate(mean = ((logit(pval.harbord)+ logit(pval.rucker)))/2, 
-         difference = logit(pval.harbord) - logit(pval.rucker)) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + theme(legend.position = "none") +
-  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
-                     values = c("red", "blue")) +
-  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value Rucker)" )))
-#--------------------------------------------------------------------------------------------------------------------#
-
-harbord.excess.plot <- meta.f %>% 
-  mutate(mean = ((logit(pval.harbord)+ logit(pval.d.tes)))/2, 
-         difference = logit(pval.harbord) - logit(pval.d.tes)) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + #theme(legend.position = "bottom") +
-  scale_color_manual(labels = c("systematic error", "95 % conf. int."), 
-                     values = c("red", "blue")) +
-  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value excess significance)" )))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Table with proportions of significant test results:
-meta.f <- meta.f %>% 
-mutate(test.sum.bin = tes.d.test + schwarzer.test + harbord.test + peter.test + rucker.test,
-       test.sum.else = tes.d.test + egger.test + thompson.test + begg.test, 
-       test.sum.bin2 = tes.d.test + harbord.test,
-       test.sum.else2 = tes.d.test + egger.test, 
-       test.min.bin = ifelse(schwarzer.test + harbord.test + peter.test + rucker.test > 0, 1, 0),
-       test.min.else = ifelse(egger.test + thompson.test + begg.test > 0, 1, 0),
-       test.min.bin2 = ifelse(test.sum.bin2 > 0, 1, 0),
-       test.min.else2 = ifelse(test.sum.else2 > 0, 1, 0))
-
-mean.min.bin <- round(mean(meta.f$test.min.bin, na.rm = T)*100, 1)
-mean.min.else <- round(mean(meta.f$test.min.else, na.rm = T)*100, 1)
-
-mean.min.bin2 <- round(mean(meta.f$test.min.bin2, na.rm = T)*100, 1)
-mean.min.else2 <- round(mean(meta.f$test.min.else2, na.rm = T)*100, 1)
-
-both.bin <- round(length(which(meta.f$test.sum.bin2 == 2))/
-                    length(which(!is.na(meta.f$test.sum.bin2)))*100, 1)
-
-both.else <- round(length(which(meta.f$test.sum.else2 == 2))/
-                     length(which(!is.na(meta.f$test.sum.else2)))*100, 1)
-
-summary.bin <- round(meta.f %>% 
-  group_by(test.sum.bin) %>% summarise(n = n()) %>% select(n)/dim(meta.bin)[1] * 100, 1)
-
-summary.else <- round(meta.f %>% group_by(test.sum.else) %>% 
-                        summarise(n = n()) %>% 
-                        select(n)/(dim(meta.cont)[1] + dim(meta.surv)[1]) * 100, 1)
-
-number.sig.tests <- data.frame(number = seq(from = 0, to = 5),
-                               binary = paste(summary.bin$n[-7], "%"),
-                               cont = as.character(paste(c(summary.else$n[-6], NA), "%")))
-number.sig.tests <- as.matrix(number.sig.tests)
-number.sig.tests[6,3][1] <- "-"
-
-colnames(number.sig.tests) <- c("Count", "Binary Outcomes", "Continuous and Survival")
-
-meta.f <- meta.f %>% mutate(tes.d.test.b = ifelse(pval.d.tes < 0.05, 1, 0),
-                            harbord.test.b = ifelse(pval.harbord < 0.05, 1, 0),
-                            egger.test.b = ifelse(pval.egger < 0.05, 1, 0),
-                            test.sum.bin2 = tes.d.test.b + harbord.test.b,
-                            test.sum.else2 = tes.d.test.b + egger.test.b, 
-                            test.min.bin2 = ifelse(test.sum.bin2 > 0, 1, 0),
-                            test.min.else2 = ifelse(test.sum.else2 > 0, 1, 0))
-
-mean.min.bin2.b <- round(mean(meta.f$test.min.bin2, na.rm = T)*100, 1)
-mean.min.else2.b <- round(mean(meta.f$test.min.else2, na.rm = T)*100, 1)
-
-both.bin.b <- round(length(which(meta.f$test.sum.bin2 == 2))/
-                    length(which(!is.na(meta.f$test.sum.bin2)))*100, 1)
-
-both.else.b <- round(length(which(meta.f$test.sum.else2 == 2))/
-                     length(which(!is.na(meta.f$test.sum.else2)))*100, 1)
-
-meta.f <- meta.f %>% mutate(egger.test = ifelse(pval.egger < 0.1/3, 1, 0),
-                            thompson.test = ifelse(pval.thompson < 0.1/3, 1, 0),
-                            begg.test = ifelse(pval.begg < 0.1/3, 1, 0),
-
-                            schwarzer.test = ifelse(pval.schwarzer < 0.1/4, 1, 0),
-                            rucker.test = ifelse(pval.rucker < 0.1/4, 1, 0),
-                            harbord.test = ifelse(pval.harbord < 0.1/4, 1, 0),
-                            peter.test = ifelse(pval.peter < 0.1/4, 1, 0),
-                            test.sum.bin = tes.d.test + schwarzer.test + harbord.test + peter.test + rucker.test,
-                            test.sum.else = tes.d.test + egger.test + thompson.test + begg.test, 
-                            test.min.bin = ifelse(schwarzer.test + harbord.test + peter.test + rucker.test > 0, 1, 0),
-                            test.min.else = ifelse(egger.test + thompson.test + begg.test > 0, 1, 0))
-
-mean.min.bin.b <- round(mean(meta.f$test.min.bin, na.rm = T)*100, 1)
-mean.min.else.b <- round(mean(meta.f$test.min.else, na.rm = T)*100, 1)
-
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
+meta.id.vector <- metac$meta.id
+meta.data <- data.ext2[which(data.ext2$meta.id %in% meta.id.vector),]
 
@@
 
-The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with small study effects tests and excess significance tests.
-We will apply the tests on the original effect size measures, i.e.
-risk ratios, Hedges $g$ or log hazard ratios.
-Different tests are applied depending on if the outcomes are of type binary or continuous or survival.\\
-Thus, we apply multiple tests on the same data.
-The results can then be displayed separately to compare the different tests.
-A histogram of $p$-values will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.
+\chapter{The Cochrane Dataset} \label{ch:dataset}
+
+\section{Cochrane Systematic Reviews}
+The Cochrane Group has specialized on systematic reviews in clinical science.
+Certain knowledge of standards and principles of the Cochrane Group may help to assess the quality and the properties of the dataset.
+The following information stems from the Cochrane Handbook for Systematic Reviews \citep{cochrane.handbook}.
 \\
-``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}.
-For continuous and survival outcomes, the names refer to:
+The definition of a systematic review is that it ``attempts to collate all empirical evidence that fits pre-specified eligibility criteria in order to answer a specific research question.'' Thus, the ``key properties of a review are'':
 
 \begin{itemize}
-\item Egger's test, the weighted linear regression test as described in section \ref{sec:Egger}
-\item Thompson and Sharp's test, the weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
-\item Begg and Mazumdar's test, the rank test described in section \ref{sec:Begg}
+\item``a clearly stated set of objectives with pre-defined eligibility criteria for studies''
+\item ``an explicit, reproducible methodology''
+\item ``a systematic search that attempts to identify all studies that would meet the eligibility criteria''
+\item ``an assessment of the validity of the findings of the included studies, for example through the assessment of risk of bias''
 \end{itemize}
 
-For binary outcomes, the names refer to:
+At the end of a systematic review, ``a systematic presentation, and synthesis, of the characteristics and findings of the included studies'' is done. \\
+53 Cochrane Review Groups prepare and maintain the reviews within specific areas of health care.
+A group consists of ``researchers, healthcare professionals and people using healthcare services (consumers)''.
+\\
+The groups are supported by Method Groups, Centers and Fields.
+The Cochrane Method Groups aim to discuss and consult the groups in methodological questions concerning review preparation.
+The Centers play a main role in training and support of the Groups.
+The Fields are responsible for broad medical research areas and follow priorities in those areas by advice and control of the groups.
+\\
+The first step in a review is writing a protocol, specifying the research question, the methods to be used in literature search and analysis and the eligibility criteria of the study.
+Changes in protocols are possible but have to be documented and the protocol is published in advance of the publication of the full review.
+The choices of methodology as well as the changes should not be made ``on the basis of how they affect the outcome of the research study''.
+\\
+In order to avoid potential conflicts of interests, there is a code of conduct that all entities of the Cochrane Organization have to agree on: conflicts of interest must be disclosed and possibly be forwarded to the Cochrane Center, and participation of review authors in the studies used have to be acknowledged.
+Additionally, a Steering Group publishes a report of potential conflicts of interests based on information about external funding of Cochrane Groups.
+\\
+In order for keeping the reviews up-to-date, they are revised in a two-year circle with exceptions.
+In addition to inclusion of new evidence in a field, the revision and maintenance process may as well includes change in analysis methods.
+This can reflect some advance in clinical science as for example new information about important subgroups, as well as new methods for conducting a Cochrane Review.
+However, there are no clear guidelines and the Cochrane Groups are free in the rate and extent of up-dating their reviews.
+
+\subsection{Methods for Cochrane Reviews}
+A research question defines the following points: ``the types of population (participants), types of interventions (and comparisons), and the types of outcomes that are of interest''.
+From the research question, usually the eligibility criteria follow.
+Usually, outcomes are not part of eligibility criteria, except for special cases such as adverse effect reviews.
+\\
+The type of study is an important eligibility criterium.
+The Cochrane Collaboration focuses ``primarily on randomized controlled trials'', and also, the methods of study identification in literature search are focused on randomized trials.
+Furthermore, study characteristics such as blinding of study operators with respect to treatment and cluster-randomizing might be additional eligibility criteria which have to be chosen by the review authors.
+\\
+After having specified the eligibility criteria, studies have to be collected.
+The central idea of systematic reviews, and also meta-analyses, is that the collected studies are a random sample of a population of studies, i.e.
+that they are representative and can be used to assess population properties.
+Therefore, the search process is crucial, as a selective search result may impose bias on the sample of studies available, making it a non-random sample.
+For this purpose, the Cochrane Groups are advised to go beyond MEDLINE !!cite!!, because a search restricted to it has been shown to deliver only 30\% to 80\% of available studies.
+``Time and budget restraints require the review author to balance the thoroughness of the search with efficiency in use of time and funds and the best way of achieving this balance is to be aware of, and try to minimize, the biases such as publication bias and language bias that can result from restricting searches in different ways.'' It is important to note that not only studies, but also study reports are occasionally used in the reviews, as they may provide useful information.
+\\
+There are different sources that are being used to search for studies. 
 \begin{itemize}
-\item Harbord's test, the likelihood score based test (section \ref{sec:Harbord})
-\item Peter's test, the weighted linear regression with inverse sample size as explanatory variable (study size proxy) described in section \ref{sec:Peter}
-\item R\"ucker's test, the test based on the arcsine transformation of proportions, in combination with Thompson and Sharp's regression test (section \ref{sec:Rucker})
-\item Schwarzer's test, the rank based test using the expected event counts computed with the hypergeometric distribution (section \ref{sec:Schwarzer})
+\item The Cochrane Central Register of Controlled Trials is a source of reports of controlled trials.
+``As of January 2008 (Issue 1, 2008), CENTRAL contains nearly 530,000 citations to reports of trials and other studies potentially eligible for inclusion in Cochrane reviews, of which 310,000 trial reports are from MEDLINE, 50,000 additional trial reports are from EMBASE and the remaining 170,000 are from other sources such as other databases and handsearching.'' It includes citations published in many languages, citations only available in conference proceedings, citations from trials registers and trials results registers.
+\item MEDLINE.
+MEDLINE includes over 16 million references to journal articles.
+5,200 journals publishing in 27 languages are indexed for MEDLINE.
+PubMed gives access to a free version of MEDLINE with up-to-date citations.
+NLM gateway such as the Health Services Research Project, Meeting Abstracts and TOXLINE Subset for toxicology citations allows for search in both databases together with additional data from the US National Library of Medicine.
+\item EMBASE.
+4,800 Journals publishing in 30 languages are indexed to EMBASE, which includes more than 11 million records from 1974 onward.
+EMBASE.com also includes 7 million unique records from MEDLINE (1966 up to date) together with its own records.
+Additionally, EMBASE Classic allows access to digitized records from 1947 to 1973.
+EMBASE and MEDLINE each have around 1,800 journals not indexed in the other database.
+\item Regional or national and subject specific databases can additionally be consulted and often provide important information. Financial considerations may limit the use of such databases.
+\item General search engines such as Google Scholar, Intute and Turning Research into Practice (TRIP) database can be used.
+\item Citation Indexes.
+The database lists articles published in around 6,000 Journals with articles in which they have been cited and is available online as SciSearch.
+This form of search is known as cited reference searching.
+\item Dissertation sources. Dissertations are often listed in MEDLINE or EMBASE but one is advised to also search in specific dissertation sources.
+\item Grey Literature Databases.
+Approximately 10\% of the results in the Cochrane Database stems from conference abstracts and other grey literature.
+The Institute for Scientific and Technical Information in France provides access to entries of the previously closed System for Information on Grey Literature database of the European Association for Grey Literature Exploitation).
+Another source is the Healthcare Management Information Consortium (HMIC) database containing records from the Library and Information Services department of the Department of Health (DH) in England and the King's Fund Information and Library Service.
+The National Technical Information Service (NTIS) gives access to the results of US and non-US government-sponsored research, as well as technical report for most published results.
+References from newsletters, magazines and technical and annual reports in behavioral science, psychology and health are provided in the PsycEXTRA database which is linked to PsycINFO database.
 \end{itemize}
 
+\subsection{Structure and Content}
+The dataset consists of \Sexpr{length(unique(data$file.nr))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(data$study.name))} studies and \Sexpr{dim(data)[1]} results.
+A result compares a clinical or medical intervention or treatments to a control.
+Each study provides (multiple) results of clinical interventions.
+\\
+In Table \ref{barbiturate.row}, two results from a systematic review about effects of barbiturates are shown as they are given in the dataset.
+As can be seen, further specifications are provided by the variables in the columns.
+\\
+The comparison variable specifies \textit{what kind} of treatments or interventions are compared, the outcome variable \textit{how} it is compared, and the subgroup variable (not indicated in table) if the result belongs to a certain subgroup.
+Here, the result is of a binary type, so the counts of events in the barbiturate treatment group and the total number of participants are given in columns ``Events'' and ``Total'' and the number of events in the control group ``Events\_c'' and participants ``Total\_c''.
+A event is here death at the end of follow up.
+
+<<echo=FALSE, results = 'asis'>>=
+print(xtable(barbi1, label = "barbiturate.row", digits = 0,
+             caption = "Example of two results as given in the dataset.
+Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
+Further descriptive variables have been ommitted"),
+      include.rownames = F, size = "scriptsize")
+@
+
+A complete listing of the variables of a result is given in Table \ref{variable}.
+They can roughly be separated into variables that \textit{specify the review} in which the result is contained and variables that \textit{specify the result} itself (separated by a horizontal line in Table \ref{variable}):
+
+\begin{table}[ht]
+  \begin{center}
+    \begin{tabular}{l l}
+      \textbf{Variable} & \textbf{Description}\\
+      \hline
+      \texttt{file.nr} & The number of the file from which the review data has been \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
+      \texttt{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
+      \texttt{file.index} & Internal index of the file in the Cochrane library.\\
+      \texttt{file.version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
+      %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
+      \hline
+      \texttt{study.name} & Name of the study to which the result belongs\\
+      \texttt{study.year} & Year in which the study was published\\
+      \hline
+      \texttt{comparison.name/.nr} & Specification of the interventions compared in the study  \\ &and a unique number for the comparison\\
+      \texttt{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ &and a unique number for the outcome\\
+      \texttt{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a \\ &unique number for the subgroup\\
+      \texttt{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
+      \texttt{effect} & Measure of the effect given in the quantity denoted by \\ &\texttt{outcome measure}.\\
+      \texttt{se} & Standard error of the measure of the effect,\\
+      \texttt{events1/events2} & The counts of patients with an outcome \textit{if}\\ &measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
+      \texttt{total1/total2} & Number of patients in groups.\\
+      \texttt{mean1/mean2} & Mean of patient measurements \textit{if} outcome is continuous.\\
+      \texttt{sd1/sd2} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
+    \end{tabular}
+  \caption{Dataset variable names and descriptions  \label{variable}}
+
+  \end{center}
+\end{table}
+
+Results are part of studies that are again part of a (systematic) review. This structure of a review is shown in Figure \ref{review}.
+
 \begin{figure}
-<<echo=FALSE, fig.height = 9>>=
-grid.arrange(p.dist.bin,
-             p.dist.cont,
-             p.dist.surv, ncol = 1)
-@
-\caption{Histogram of the $p$-values for small study effect in meta-analyses.
-The testing method is indicated in the header, bin width is equal to 0.1.
-The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-\label{fig:test}
+\tikzstyle{every node}=[draw=black,thick,anchor=west]
+\tikzstyle{selected}=[draw=red,fill=red!30]
+\tikzstyle{optional}=[dashed,fill=gray!50]
+\begin{tikzpicture}
+[grow = right, anchor = west, 
+  growth parent anchor=east, % added code
+  parent anchor=east]
+  \node {Review} [edge from parent fork right]
+    child { node {Comparison 2}
+      child { node {Outcome 2}}
+      child { node {Outcome 1}
+        child { node {Subgroup 2}}
+        child { node {Subgroup 1}
+          child  { node {Result 2}}
+          child  { node {Result 1}}
+          }}
+    }
+    child [missing] {}		
+    child { node {Comparison 1  }};
+\end{tikzpicture}
+\caption{Structure of a hypothetical review with two different comparisons}
+\label{review.structure}
 \end{figure}
 
-%Agreement table -> Chunck 1
-The histograms in Figure \ref{fig:test} show that the distributions are (with the exception of Schwarzer's test) skewed to the right for all outcome types, indicating evidence for small study effects and excess significance, respectively.
-Moreover, the excess significance tests have a mode around $p = 0.4$.
-There is some discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger.
-Survival outcome type results are quite different with very few evidence for small study effects and excess significance.
-Note that the sample size of survival outcomes is small ($n$ = \Sexpr{dim(meta.surv)[1]}).\\
-It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects/excess significance for the same meta-analyses.
-A simple method to check the coincidence of test results is to compare scatterplots and empirical Spearman correlations between the test statistics.
-This is done in Figure \ref{fig:test.agreement}.
-Here, there is no separation between survival and continuous outcomes.
-The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results.
+\vspace{0mm}
+The structure of a review will now be outlined based on an example of the dataset.
+Let us consider the previously mentioned barbiturate and head injury review.
+The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates''.
+\\
+%Since there are arguments for and against use of barbiturates, the authors of the review did a comprehensive literature search and collected all available study findings. 
+The review comprises five studies in total.
+Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental.
+The studies have different outcomes, for example, death or death and severe disability at follow up, but also dropout counts or adverse effects (secondary outcomes).
+We have continuous (e.g.
+mean body temperature) and binary outcome data (e.g.
+death/no death).
+One study split up outcomes for patients with and without haematoma, which would be subgroups.
+Thus, it is important not to confuse results with studies.
+A study can contribute multiple results to a systematic review, for example, primary and secondary outcomes and adverse effects.
 
-\begin{figure}
-<<echo=FALSE, fig.height = 6, warning=FALSE>>=
-corrgram(cor.data, 
-         upper.panel=panel.pts.new, lower.panel=panel.cor, 
-         cex.labels = 1, cex = .25, cex.cor = 2, pch = 1,
-         text.panel=panel.txt, cor.method = "spearman")
+<<echo=FALSE, results='asis'>>=
+print(xtable(barbi2, label = "barbiturates", caption = "Barbiturate and head injury review.
+In the columns, study names, comparison and outcome measure of the results are given"), include.rownames = F, size = "footnotesize")
 @
-\caption{Pairs-plot for test statistics of small study effect and excess significance.
-The lower panel gives the Spearman correlations for the different test statistics, and the upper panel displays a scatterplot.
-The colors indicate magnitude and direction of the correlation coefficients.
-The rectangle with white borders displays the area within which both tests have absolute value < 1.64 (dots outside are statistically significant using the 0.1 threshold).}
-\label{fig:test.agreement}
-\end{figure}
 
-The observed patterns on the scatterplots differ: Excess significance and small study effect test statistics do usually not align with each other, forming rather randomly scattered bulks of points.
-Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients.
-In general, small study effect tests align on the diagonal, but the extent to which they align differs.
-Continuous and survival outcome type tests align more closely than binary outcome tests.
-While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics .\\
-Because scatterplots and correlation coefficients can be misleading, also a Tukey mean-difference or Bland-Altman of transformed $p$-values plot is shown for four scenarios in Figure \ref{fig:mean.diff.test}:
+Information about missing values in the dataset is given in Table \ref{missing}.
+For variables as research subject, outcome and subgroup name and event counts there are no missing values.
+The relative amount of missing values is very low except for study years.
+For continuous outcomes, the cases have been counted were no treatment effect and standard error is available: neither mean values and standard deviations, nor mean differences and standard error.
+Also Study years before 1920 and after 2019 are declared as missing, as well as sample sizes below zero.
+
+<<echo=FALSE, results='asis'>>=
+print(xtable(missing.table, label = "missing", caption = "Number of missing variables and measurements in the dataset", align = "lr"), include.colnames = F,
+      size = "footnotesize", digits = 0)
+@
+
+The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = \Sexpr{publication.year.range[1]}, 95\% quantile = \Sexpr{publication.year.range[6]},).
+The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{publication.year.range[5]} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}.
+Only a handful ($n = 18$) have been published in 2018, none in 2019.
+\\
+%No information is available concerning unpublished results and studies.
+The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}.
+One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (> 65\%).
+
+<<echo=FALSE, results='asis'>>=
+print(xtable(outcome.measure.frequencies, label = "outcome.measure.frequencies", 
+             caption = "Frequencies of outcome measures among results. n denotes the total number 
+             of results with the outcome measure and percentage the percentage of the outcome measure,", 
+             align = "llrr", digits = 1), include.rownames = F, size = "footnotesize")
+@
+
+The sample sizes among results vary to some extent.
+There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, the 5\% quantile and 95\% smaller than \Sexpr{treatment.group.size.range[6]}.
+The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{treatment.group.size.range[5]} and the third quartile \Sexpr{treatment.group.size.range[4]}.
+The large difference between median and mean is caused by very large groups with over 2,000,000 participants.
+Analogously, the quantiles of the total sample size are: 5\% quantile = \Sexpr{samplesize.range[1]}, first quartile = \Sexpr{samplesize.range[2]}, median = \Sexpr{samplesize.range[3]}, third quartile = \Sexpr{samplesize.range[4]} and 95\% = \Sexpr{samplesize.range[6]}.
+The mean is \Sexpr{samplesize.range[5]}.
+\\
+The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}.
+There are \Sexpr{comp.range[1]} reviews with five or fewer results, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}.
+Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]} and the 95\% quantile \Sexpr{study.range[6]}.
+The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1497 results in total.\\
+For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome.
+More specifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis, since their research subject and experimental setup can be considered sufficiently homogeneous.
+Importantly, this distinction is also used by the Cochrane Organization itself, i.e.
+the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
+The dataset is divided in meta-analyses with identical experimental setup. The size of a meta-analysis denotes how many results are included in a group.
+Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results. Practically, this number of meta analyses can be performed, with each having at least $n$ results.
+
+<<echo=FALSE, results='asis'>>=
+
+print(xtable(cum.repr.trials.subg, label = "repr.groups", caption = "Cumulative number of groups with number of reproduction trials $\\geq$ n", align = "llrr", digits = 0), include.rownames = F, size = "footnotesize")
+@
+
+\section{Data Tidying and Processing} \label{sec:Processing}
+The original dataset was provided by .. (some words how the dataset was obtained and processed by C.R.). \\
+The information in the previous pages are from a tidied and processed version of this dataset. \\
+
+\subsection{Modification of old variables}
+In some cases, reasonable assumptions led to small changes in the originally provided variables:
 \begin{itemize}
-\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
-\item For Egger's and excess significance tests
-\item For Harbord's and R\"ucker's tests
-\item For Harbord's and excess significance tests
+\item \texttt{study.year}: It was assumed that studies that are declared to have been published before 1920 ($n$ = \Sexpr{length(which(data$study.year < 1920))}) are mis-specified, as well as after 2019 ($n$ = \Sexpr{length(which(data$study.year > 2019))}), so these have been set to NA.
+\item \texttt{mean1} and \texttt{mean2}: When both \texttt{mean1} and \texttt{mean2} are equal to zero or NA, \texttt{outcome.measure.new} is equal to \texttt{(Std.) Mean Difference}, but a mean difference is given in \texttt{effect}, \texttt{mean1} is set equal to \texttt{effect} ($n$ = \Sexpr{length(nomeans.ind)}).
 \end{itemize}
 
-This can be justified since all tests are supposed to measure the evidence for publication bias.
-For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation $f(x)  = \log\frac{p}{1-p}$).
-The mean $p$-value (($f$($p$-value no.
-1) + $f$($p$-value no.
-2))/2) is then displayed against the difference between the $f$($p$-value).
-If no systematic errors and biases exist between the measurement methods, then
-
+\subsection{Newly Introduced Variables}
+Some new variables are added to the obtained dataset:
 \begin{itemize}
-\item the mean of the differences should be around zero (systematic error) 
-\item the points should scatter independently on the $y$-axis and no general increase or decrease with the mean of the transformed $p$-values should be visible
+\item \texttt{outcome.measure.new}: Outcome measure specifications given in \texttt{outcome.measure} were standardized whenever they were supposed to denote the same outcome measure.
+An example would be the formally different notations for odds ratios: ``Odds Ratio'', ``odds ratio'', ``OR'', which were all denoted as ``Odds Ratio''.
+\item \texttt{outcome.type}: A simplification of \texttt{outcome.measure.new}.
+The outcome.type ``bin'' indicates if \texttt{outcome.measure.new} is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
+``cont'' is equivalent to \texttt{outcome.measure.new} equal to "Std.
+Mean Difference'' or ``Mean Difference''.
+``surv'' equal to ``Hazard Ratio'' and ``rate'' equal to ''Rate Ratio'' or ``Rate Difference''.
+\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.type ``bin''.
+\item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.type ``cont''.
+If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.new} was equal to ``Std.
+Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  \Sexpr{length(inpute.given.ind)}).
+\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.type ``bin''.
+\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.type ``bin'') or $g$ (for outcome.type ``cont'') to $r$ transformation.
+\item \texttt{z} and \texttt{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
+\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.type ``cont'' or Wald test for outcome.type ``bin''.
+\item \texttt{events1c} and \texttt{events2c}: Correction of \texttt{events1} and \texttt{events2} zero event counts or event counts = patient number.
+When no events occurred, 0.5 was added, and when all patients experienced the event, 0.5 was subtracted.
+When one of \texttt{events} had zero counts while the other had maximum counts, no adjustment occurred.
+\item \texttt{meta.id}: Meta-analysis ID variable to uniquely identify any potential meta-analysis in the dataset.
+Consistent to what has been discussed before, all results that share a common comparison, outcome and subgroup (optional, subgroups not given in any case) may be combined in a meta-analysis.
+% \item \texttt{}:
+% \item \texttt{}:
 \end{itemize}
 
-Although this is not formally tested, the last criterium seems not to be given when comparing small study effect and excess significance tests.
-With decreasing mean, the difference gets more negative, and vice versa, such that one would predict that the excess significance $p$-values are more ``extreme'' in both directions.
--- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- However, the systematic error between the compared tests is close to zero, and small study effect tests do probably not show bias when compared to each other.
-\\
-The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests.
-This suggests that correspondence between the tests is not very good in general.
-
-\begin{figure}
-<<echo=FALSE, fig.height = 8.5, warning=FALSE>>=
-grid.arrange(egger.thompson.plot, 
-             egger.excess.plot,
-             harbord.rucker.plot, 
-             harbord.excess.plot, ncol = 1)
-@
-\caption{Mean - difference plots for logit transformed $p$-values.
-The mean of logit transformed $p$-values is displayed on the $x$-axis and the difference on the $y$-axis.
-Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).}
-\label{fig:mean.diff.test}
-\end{figure}
-
-The previous results suggest that the results will also differ substantially after applying the common dichotomization of $p$-values.
-We expect that some proportion of the meta-analysis will only be significant for a certain test, and this is indeed observed in Table \ref{number.sig.tests}.
-It displays the percentage of meta-analyses with a certain number of significant test results.
-
-<<echo = FALSE, results='asis'>>=
-print(xtable(number.sig.tests, caption = "Counts Number of significant test results per meta-analysis, separated
-       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
-       applied", label = "number.sig.tests", align = "lccc"), include.rownames = F, size = "footnotesize")
-@
-
-Here, it is difficult to say if continuous and survival or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and survival outcome type tests have in general more positive findings.
-Very few meta-analyses are significant, irrespective of the test used, but around 67\% of the dataset is not significant, no matter which test is used.
-\\
-When only looking at small study effect tests, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of survival and continuous outcome tests had at least one significant result.
-This also suggests that the overlap between small study effect tests and excess significance is small.
-After applying the Bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\% for binary and \Sexpr{mean.min.else.b}\% for continuous and survival outcomes.
-\\
-To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test.
-\Sexpr{mean.min.bin2}\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, \Sexpr{mean.min.else2}\% for continuous and survival outcomes.
-The numbers change to \Sexpr{mean.min.bin2.b}\% for binary outcomes and \Sexpr{mean.min.else2.b}\% for continuous and survival outcomes after applying the Bonferroni correction.
-\\
-\Sexpr{both.bin}\% have significant Harbord's test result and significant excess significance test result  (\Sexpr{both.bin.b}\% with Bonferroni).
-Of the continuous outcomes, we have \Sexpr{both.else}\% with Egger's test and \Sexpr{both.else.b}\% with Bonferroni correction.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Small Study Effects Adjustment}
-<<echo=FALSE, warning=FALSE, message=FALSE>>=
-#HISTOGRAMS:
-
-#Comparison of treatment effect p-values:
-sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
-                              z.ranef = est.z.ranef/se.est.z.ranef,
-                              z.reg = est.z.reg/se.est.z.reg,
-                              z.copas = est.z.copas/se.est.z.copas) %>%  
-  select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>% 
-  mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>% 
-  group_by(method) %>% 
-  summarise(significant = length(which(abs(fisher.z) > 1.96)),
-            p.significant = significant/length(fisher.z))
-sig.zcor <- data.frame(method = sig.zcor$method,
-                       label = paste(round(sig.zcor$p.significant,3)*100, "% significant", ", (n = ", sig.zcor$significant, ")", sep = ""))
-
-method_names <- c(
-  z.fixef = "Fixed Effects",
-  z.ranef = "Random Effects",
-  z.reg = "Regression",
-  z.copas = "Copas"
-)
-
-adjustment.p.z <- meta.f %>% 
-  mutate(z.fixef = est.z.fixef/se.est.z.fixef,
-         z.ranef = est.z.ranef/se.est.z.ranef,
-         z.reg = est.z.reg/se.est.z.reg,
-         z.copas = est.z.copas/se.est.z.copas) %>%  
-  select(z.fixef, z.ranef, z.reg, z.copas) %>% 
-  gather(key = "method", value = "fisher.z") %>% 
-  mutate(method = factor(method, levels = c("z.fixef", "z.ranef", "z.reg", "z.copas"))) %>% 
-  mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>% 
-  ggplot(aes(x = p.fisher.z)) + 
-  geom_histogram(boundary = 0, bins = 20) + 
-  theme_bw() + 
-  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-  geom_text(data = sig.zcor, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
-  xlab(expression(paste(italic(p),"-value of test statistic of the ", italic(z),"-score"))) +
-  ggtitle(expression(paste(italic(z), " Score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Comparison of SMD's:
-sig.d <- meta.f %>% mutate(d.fixef = est.d.fixef/se.est.d.fixef,
-                           d.ranef = est.d.ranef/se.est.d.ranef,
-                           d.reg = est.d.reg/se.est.d.reg,
-                           d.copas = est.d.copas/se.est.d.copas) %>%  
-  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-  group_by(method) %>% 
-  summarise(significant = length(which(abs(smd) > 1.96)),
-            p.significant = significant/length(smd))
-sig.d <- data.frame(method = sig.d$method,
-                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
-
-method_names <- c(
-  d.fixef = "Fixed Effects",
-  d.ranef = "Random Effects",
-  d.reg = "Regression",
-  d.copas = "Copas"
-)
-
-adjustment.p.d <- meta.f %>% 
-  mutate(d.fixef = est.d.fixef/se.est.d.fixef,
-         d.ranef = est.d.ranef/se.est.d.ranef,
-         d.reg = est.d.reg/se.est.d.reg,
-         d.copas = est.d.copas/se.est.d.copas) %>%  
-  select(d.fixef, d.ranef, d.reg, d.copas) %>% 
-  gather(key = "method", value = "smd") %>% 
-  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
-  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-  ggplot(aes(x = p.smd)) + 
-  geom_histogram(boundary = 0, bins = 20) + 
-  theme_bw() + 
-  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-  geom_text(data = sig.d, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
-  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
-  ggtitle(expression(paste("Hedges ", italic(g), " ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Comparison of log hazard ratios:
-sig.d <- meta.f %>% filter(outcome.type == "surv") %>% 
-  mutate(d.fixef = est.fixef/se.est.fixef,
-         d.ranef = est.ranef/se.est.ranef,
-         d.reg = est.reg/se.est.reg,
-         d.copas = est.copas/se.est.copas) %>%  
-  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-  group_by(method) %>% 
-  summarise(significant = length(which(abs(smd) > 1.96)),
-            p.significant = (significant + sum(is.na(smd)))/(length(smd)))
-sig.d <- data.frame(method = sig.d$method,
-                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
-
-method_names <- c(
-  d.fixef = "Fixed Effects",
-  d.ranef = "Random Effects",
-  d.reg = "Regression",
-  d.copas = "Copas"
-)
-
-adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.type == "surv") %>% 
-  mutate(d.fixef = est.fixef/se.est.fixef,
-         d.ranef = est.ranef/se.est.ranef,
-         d.reg = est.reg/se.est.reg,
-         d.copas = est.copas/se.est.copas) %>%  
-  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
-  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-  ggplot(aes(x = p.smd)) + 
-  geom_histogram(boundary = 0, bins = 20) + 
-  theme_bw() + 
-  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-  geom_text(data = sig.d, aes(x = 0.00003, y = 20, label = label), position = "dodge") + 
-  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
-  ggtitle(expression(paste("Log hazard ratio ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Meta-Analysis and adjusted treatment effect estimate difference:
-
-#Z-score:
-diff.z.fixef <- meta.f %>% 
-  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
-                  copas = est.z.copas, regression = est.z.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
-                           sign(copas) != sign(fixef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
-                                sign(regression) != sign(fixef) ~ -abs(regression)),
-    fixef = abs(fixef),
-    ranef = abs(ranef)) %>% 
-  select(fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
-  mutate(difference = fixef - adjusted.z.score) %>% 
-  filter(difference > -.75 & difference < .75) %>% 
-  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + 
-  xlab(expression(paste("Fixed effects - adjusted ", z, "-score")))
-#--------------------------------------------------------------------------------------------------------------------#
-
-diff.z.ranef <- meta.f %>% 
-  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
-         copas = est.z.copas, regression = est.z.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
-                           sign(copas) != sign(ranef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
-                                sign(regression) != sign(ranef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  select(fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
-  mutate(difference = ranef - adjusted.z.score) %>% 
-  filter(difference > -.75 & difference < .75) %>% 
-  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + 
-  xlab(expression(paste("Random effects - adjusted ", z, "-score")))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#SMD:
-diff.d.fixef <- meta.f %>% 
-  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
-         copas = est.d.copas, regression = est.d.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
-                           sign(copas) != sign(fixef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
-                                sign(regression) != sign(fixef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  select(fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
-  mutate(difference = fixef - adjusted.smd) %>% 
-  filter(difference > -1 & difference < 1) %>% 
-  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + 
-  xlab(expression(paste("Fixed effects - adjusted Hedges ", g)))
-#--------------------------------------------------------------------------------------------------------------------#
-
-diff.d.ranef <- meta.f  %>% 
-  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
-         copas = est.d.copas, regression = est.d.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
-                           sign(copas) != sign(ranef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
-                                sign(regression) != sign(ranef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
-  mutate(difference = ranef - adjusted.smd) %>% 
-  filter(difference > -1 & difference < 1) %>% 
-  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + 
-  xlab(expression(paste("Random effects - adjusted Hedges ", g)))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Log hazard ratios:
-diff.log.hazard.ratio.fixef <- meta.surv %>% 
-  mutate(fixef = est.fixef, ranef = est.ranef,
-         copas = est.copas, regression = est.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
-                           sign(copas) != sign(fixef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
-                                sign(regression) != sign(fixef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
-  ggplot(aes(x = (fixef - adjusted.log.hazard.ratio))) + 
-  geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + xlab("Fixed effects - adjusted log hazard ratio")
-#--------------------------------------------------------------------------------------------------------------------#
-
-diff.log.hazard.ratio.ranef <- meta.surv %>% 
-  mutate(fixef = est.fixef, ranef = est.ranef,
-         copas = est.copas, regression = est.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
-                           sign(copas) != sign(ranef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
-                                sign(regression) != sign(ranef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
-  ggplot(aes(x = (ranef - adjusted.log.hazard.ratio))) + 
-  geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + xlab("Random effects - adjusted log hazard ratio")
-#--------------------------------------------------------------------------------------------------------------------#
-sig.level <- 0.1
-meta.f <- meta.f %>% 
-	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
-				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
-				 begg.test = ifelse(pval.begg < sig.level, 1, 0),
-
-				 tes.d.test = ifelse(pval.d.tes < sig.level, 1, 0),
-
-				 schwarzer.test = ifelse(pval.schwarzer < sig.level, 1, 0),
-				 rucker.test = ifelse(pval.rucker < sig.level, 1, 0),
-				 harbord.test = ifelse(pval.harbord < sig.level, 1, 0),
-				 peter.test = ifelse(pval.peter < sig.level, 1, 0))
-
-#Quantile, mean, largerthan and missing table of differences:
-adjustment.diff.keep <- meta.f %>% 
-  mutate(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
-                                 sign(est.copas) != sign(est.fixef) ~ -abs(est.copas)),
-         est.reg.f = case_when(sign(est.reg) == sign(est.fixef) ~  abs(est.reg),
-                               sign(est.reg) != sign(est.fixef) ~ -abs(est.reg)),
-         est.copas.r = case_when(sign(est.copas) == sign(est.ranef) ~  abs(est.copas),
-                                 sign(est.copas) != sign(est.ranef) ~ -abs(est.copas)),
-         est.reg.r = case_when(sign(est.reg) == sign(est.ranef) ~  abs(est.reg),
-                               sign(est.reg) != sign(est.ranef) ~ -abs(est.reg)),
-
-         est.d.copas.f = case_when(sign(est.d.copas) == sign(est.d.fixef) ~  abs(est.d.copas),
-                                   sign(est.d.copas) != sign(est.d.fixef) ~ -abs(est.d.copas)),
-         est.d.reg.f = case_when(sign(est.d.reg) == sign(est.d.fixef) ~  abs(est.d.reg),
-                                 sign(est.d.reg) != sign(est.d.fixef) ~ -abs(est.d.reg)),
-         est.d.copas.r = case_when(sign(est.d.copas) == sign(est.d.ranef) ~  abs(est.d.copas),
-                                   sign(est.d.copas) != sign(est.d.ranef) ~ -abs(est.d.copas)),
-         est.d.reg.r = case_when(sign(est.d.reg) == sign(est.d.ranef) ~  abs(est.d.reg),
-                                 sign(est.d.reg) != sign(est.d.ranef) ~ -abs(est.d.reg)),
-
-         est.z.copas.f = case_when(sign(est.z.copas) == sign(est.z.fixef) ~  abs(est.z.copas),
-                                   sign(est.z.copas) != sign(est.z.fixef) ~ -abs(est.z.copas)),
-         est.z.reg.f = case_when(sign(est.z.reg) == sign(est.z.fixef) ~  abs(est.z.reg),
-                                 sign(est.z.reg) != sign(est.z.fixef) ~ -abs(est.z.reg)),
-         est.z.copas.r = case_when(sign(est.z.copas) == sign(est.z.ranef) ~  abs(est.z.copas),
-                                   sign(est.z.copas) != sign(est.z.ranef) ~ -abs(est.z.copas)),
-         est.z.reg.r = case_when(sign(est.z.reg) == sign(est.z.ranef) ~  abs(est.z.reg),
-                                 sign(est.z.reg) != sign(est.z.ranef) ~ -abs(est.z.reg)),
-
-         est.fixef = abs(est.fixef),
-         est.ranef = abs(est.ranef),
-         est.z.fixef = abs(est.z.fixef),
-         est.z.ranef = abs(est.z.ranef),
-         est.d.fixef = abs(est.d.fixef),
-         est.d.ranef = abs(est.d.ranef))
-
-adjustment.diff.keep <- adjustment.diff.keep %>% 
-  mutate(bias.side = ifelse(est.fixef - est.reg.f > 0, 1, 0), #Decide if effect size declines or increases
-
-         egger.test = ifelse(bias.side == 1, egger.test, 0),
-         thompson.test = ifelse(bias.side == 1, thompson.test, 0),
-         begg.test = ifelse(bias.side == 1, begg.test, 0),
-
-         schwarzer.test = ifelse(bias.side == 1, schwarzer.test, 0),
-         peter.test = ifelse(bias.side == 1, peter.test, 0),
-         rucker.test = ifelse(bias.side == 1, rucker.test, 0),
-         harbord.test = ifelse(bias.side == 1, harbord.test, 0))
-
-adjustment.diff <- adjustment.diff.keep %>%
-
-  transmute(copas.z.f = est.z.fixef - est.z.copas.f,
-            copas.z.r = est.z.ranef - est.z.copas.r,
-            reg.z.f = est.z.fixef - est.z.reg.f,
-            reg.z.r = est.z.ranef - est.z.reg.r,
-
-            copas.d.f = est.d.fixef - est.d.copas.f,
-            copas.d.r = est.d.ranef - est.d.copas.r,
-            reg.d.f = est.d.fixef - est.d.reg.f,
-            reg.d.r = est.d.ranef - est.d.reg.r)
-
-m.adjustment.diff <- as.matrix(adjustment.diff)
-
-adjustmend.diff.surv <- meta.surv %>% 
-  transmute(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
-                                    sign(est.copas) != sign(est.fixef) ~ -abs(est.copas)),
-            est.copas.r = case_when(sign(est.copas) == sign(est.ranef) ~  abs(est.copas),
-                                    sign(est.copas) != sign(est.ranef) ~ -abs(est.copas)),
-
-            est.reg.f = case_when(sign(est.reg) == sign(est.fixef) ~  abs(est.reg),
-                                  sign(est.reg) != sign(est.fixef) ~ -abs(est.reg)),
-            est.reg.r = case_when(sign(est.reg) == sign(est.ranef) ~  abs(est.reg),
-                                  sign(est.reg) != sign(est.ranef) ~ -abs(est.reg)),
-
-            est.fixef = abs(est.fixef),
-            est.ranef = abs(est.ranef)) %>%
-
-  transmute(copas.surv.f = est.fixef - est.copas.f,
-            copas.surv.r = est.ranef - est.copas.r,
-
-            reg.surv.f =  est.fixef - est.reg.f,
-            reg.surv.r = est.ranef - est.reg.r)
-
-m.adjustment.diff.surv <- as.matrix(adjustmend.diff.surv)
-
-adjustment.diff.quantile.table <- apply(m.adjustment.diff, 2, 
-                                        FUN = function(column){quantile(x = column, 
-                                                                        probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T)})
-adjustment.diff.mean <- apply(m.adjustment.diff, 2, FUN = function(column) mean(column, na.rm = T))
-adjustment.diff.largerzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
-adjustment.diff.equalzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
-adjustment.diff.largerequalzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
-adjustment.diff.comp.errors <- c(4,4,0,0,0,0,0,0)
-adjustment.diff.noest <- c(sum(meta.f$est.z.copas.na[meta.f$outcome.type != "surv"]), 
-                                sum(meta.f$est.z.copas.na[meta.f$outcome.type != "surv"]),
-                                sum(meta.f$est.z.reg.na[meta.f$outcome.type != "surv"]), 
-                                sum(meta.f$est.z.reg.na[meta.f$outcome.type != "surv"]),
-                                sum(meta.f$est.d.copas.na[meta.f$outcome.type != "surv"]), 
-                                sum(meta.f$est.d.copas.na[meta.f$outcome.type != "surv"]),
-                                sum(meta.f$est.d.reg.na[meta.f$outcome.type != "surv"]), 
-                                sum(meta.f$est.d.reg.na[meta.f$outcome.type != "surv"]))
-adjustment.diff.missing <- (adjustment.diff.comp.errors + adjustment.diff.noest)/apply(m.adjustment.diff, 2, FUN = function(column) length(column))*100
-
-adjustment.diff.table <- rbind(adjustment.diff.quantile.table, mean = adjustment.diff.mean,
-                               equalzero = adjustment.diff.equalzero,
-                               largerequal = adjustment.diff.largerequalzero, larger = adjustment.diff.largerzero,
-                               missing = adjustment.diff.missing)
-
-adjustment.diff.quantile.table.surv <- apply(m.adjustment.diff.surv, 2, 
-                                             FUN = function(column){quantile(x = column, 
-                                                                             probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T)})
-adjustment.diff.mean.surv <- apply(m.adjustment.diff.surv, 2, FUN = function(column) mean(column, na.rm = T))
-adjustment.diff.largerzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
-adjustment.diff.equalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
-adjustment.diff.largerequalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
-adjustment.diff.comp.errors.surv <- c(0,0,0,0)
-adjustment.diff.noest.surv <- c(sum(meta.surv$est.copas.na), sum(meta.surv$est.copas.na),
-                                sum(meta.surv$est.reg.na), sum(meta.surv$est.reg.na))
-adjustment.diff.missing.surv <- ((adjustment.diff.comp.errors.surv + adjustment.diff.noest.surv)/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
-
-adjustment.diff.table.surv <- rbind(adjustment.diff.quantile.table.surv, mean = adjustment.diff.mean.surv,
-                                    equalzero = adjustment.diff.equalzero.surv,
-                                    largerequal = adjustment.diff.largerequalzero.surv, larger = adjustment.diff.largerzero.surv,
-                                    missing = adjustment.diff.missing.surv)
-
-adjustment.diff.table <- cbind(adjustment.diff.table, (adjustment.diff.table.surv))
-
-adjustment.diff.table <- round(t(adjustment.diff.table), 4)
-
-rownames(adjustment.diff.table) <- c(paste("z:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
-                                     paste("g:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
-                                     paste("Log h.r.:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")))
-
-colnames(adjustment.diff.table) <- c(colnames(adjustment.diff.table)[1:6], "= 0 (%)", ">= 0 (%)", "> 0 (%)", "No adj. est. (%)")
-
-#--------------------------------------------------------------------------------------------------------------------#
-#Meta-Analysis and adjusted treatment effect estimate difference, missing values:
-
-#Z-score:
-missing.z.fixef <- meta.f %>% 
-  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
-         copas = est.z.copas, regression = est.z.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
-                           sign(copas) != sign(fixef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
-                                sign(regression) != sign(fixef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  select(meta.id, fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
-  mutate(difference = fixef - adjusted.z.score) %>% 
-  filter(difference < -.75 | difference > .75) %>% 
-  select(meta.id)
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-missing.z.ranef <- meta.f %>% 
-  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
-         copas = est.z.copas, regression = est.z.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
-                           sign(copas) != sign(ranef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
-                                sign(regression) != sign(ranef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  select(meta.id, fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
-  mutate(difference = ranef - adjusted.z.score) %>% 
-  filter(difference < -.75 | difference > .75) %>% 
-  select(meta.id)
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-#SMD:
-missing.d.fixef <- meta.f %>% 
-  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
-         copas = est.d.copas, regression = est.d.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
-                           sign(copas) != sign(fixef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
-                                sign(regression) != sign(fixef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  select(meta.id, fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
-  mutate(difference = fixef - adjusted.smd) %>% 
-  filter(difference < -1 | difference > 1) %>% select(meta.id)
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-missing.d.ranef <- meta.f %>% 
-  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
-         copas = est.d.copas, regression = est.d.reg) %>% 
-  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
-                           sign(copas) != sign(ranef) ~ -abs(copas)),
-         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
-                                sign(regression) != sign(ranef) ~ -abs(regression)),
-         fixef = abs(fixef),
-         ranef = abs(ranef)) %>% 
-  select(meta.id, fixef, ranef, copas, regression) %>% 
-  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
-  mutate(difference = ranef - adjusted.smd) %>% 
-  filter(difference < -1 | difference > 1) %>% select(meta.id)
-
-missing.differences <- rbind(missing.z.fixef, missing.z.ranef, missing.d.fixef, missing.d.ranef)
-missing.differences <- missing.differences %>% distinct(meta.id)
-
-missing.differences <- merge(meta.f[,
-        c("meta.id", "file.nr", "comparison.nr", "subgroup.nr",
-          "est.z.ranef", "est.z.fixef", "est.z.copas", "est.z.reg", 
-          "est.d.fixef", "est.d.ranef", "est.d.copas", "est.d.reg")],
-        missing.differences, by = "meta.id")
-
-missing.differences <- round(missing.differences, 2)
-
-missing.differences <- missing.differences %>% mutate(meta.id = as.character(meta.id), file.nr = as.character(meta.id),
-                                                      comparison.nr = as.character(comparison.nr), subgroup.nr = as.character(subgroup.nr))
-
-colnames(missing.differences) <- c("meta.id", "file.nr", "comparison.nr", "subgroup.nr",
-                                   "z fixed", "z random", "z Copas", "z regression",
-                                   "g fixed", "g random", "g Copas", "g regression")
-
-#--------------------------------------------------------------------------------------------------------------------#
-#Tukey mean difference plots for adjustment methods:
-
-adjustment.mean.diff.orig <- meta.f %>% filter(est.copas.na != 1) %>% 
-  mutate(mean = (est.copas + est.reg)/2, 
-         difference = est.copas - est.reg) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + theme(legend.position = "none") +
-  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
-                     values = c("red", "blue")) +
-  ggtitle(expression(paste("Copas adjusted estimate - Regression adjusted estimate (original)" )))
-
-adjustment.mean.diff.z <- meta.f %>% filter(est.z.copas.na != 1) %>% 
-  mutate(mean = (est.z.copas + est.z.reg)/2, 
-         difference = est.z.copas - est.z.reg) %>% filter(mean < 7) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point(size = 0.5) + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + theme(legend.position = "none") +
-  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
-                     values = c("red", "blue")) +
-  ggtitle(expression(paste("Copas adjusted ", italic(z),"-score estimate - Regression adjusted ", italic(z),"-score estimate (original)" )))
-
-adjustment.mean.diff.d <- meta.f %>% filter(est.d.copas.na != 1) %>% 
-  mutate(mean = (est.d.copas + est.d.reg)/2, 
-         difference = est.d.copas - est.d.reg) %>% filter(difference < 7 & mean < 10) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
-  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  geom_abline(aes(slope = 0,
-                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
-                  col = "red")) +
-  # geom_smooth(method = "loess", se = F) + 
-  theme_bw() + #theme(legend.position = "bottom") +
-  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
-                     values = c("red", "blue")) + guides(fill=guide_legend(title=NULL)) +
-  ggtitle(expression(paste("Copas adjusted Hedges ", italic(g)," estimate - Regression adjusted Hedges ", italic(g), " estimate (original)" )))
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Missing study number by copas:
-missing.copas.histogram <- meta.f %>% ggplot(aes(x = missing.copas/k)) + geom_histogram(binwidth = 0.05, boundary = 0) + theme_bw() + xlab("Missing study fraction")
-missing.copas.zeros <- length(which(meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)] == 0))
-missing.copas.range.frac <- c(missing.copas.zeros, quantile(x = meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)], c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)],na.rm = T) )
-missing.copas.range.count <- c(missing.copas.zeros, quantile(x = meta.f$missing.copas[!is.na(meta.f$missing.copas)], c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(na.rm = T,meta.f$missing.copas[!is.na(meta.f$missing.copas)]))
-missing.copas.table <- rbind(missing.copas.range.frac, missing.copas.range.count)
-rownames(missing.copas.table) <- c("Missing fraction", "Missing study number")
-colnames(missing.copas.table) <- c("= 0", colnames(missing.copas.table)[2:6], "mean")
-
-@
-
-\subsection{Change in Effect Size after Adjustment} \label{sec:change.size}
-
-Since there's evidence for publication bias when applying small study effect and excess significance tests, we apply small study effect adjustment methods to correct for small study effect tests. \\
-We will see that consequences of adjustment can be; 
+\subsection{Eligibility criteria for Publication Bias Test and Adjustment} 
+Initially, the analysis is restricted to binary, continuous and survival outcomes. More formally:
 \begin{itemize}
-\item first, the absolute size of the treatment effect can be smaller than the classical meta-analysis treatment effect, which is expected if publication bias
-is the cause for the small study effect.
-\item secondly, the effect can be larger than before in meta-analysis.
-In this case, the small study effect must be not due to publication bias for large effects (``true'' publication bias), but due to bias for small effects (``negative publication bias'').
+\item \textbf{Outcome measures}: The analysis has been restricted on the following outcome measures (from \texttt{outcome.measure.new}): ``Odds Ratio'', ``Risk Ratio'', ``Risk difference'', ``Peto Odds Ratio'', ``Std.
+Mean Difference'', ``Mean Difference'', ``Hazard Ratio''
+($n$ = \Sexpr{length(data.ext2$outcome.type[which(data.ext2$outcome.type == "bin" | data.ext2$outcome.type == "cont" | data.ext2$outcome.type == "surv")])} out of a total of \Sexpr{length(data.ext2$outcome.type)} results)
 \end{itemize}
 
-In section \ref{sec:comparison.tests.adjustment}, it will be followed up on the latter point. For now, we will examine the extent and the frequencies of the two scenarios. \\
-To compare the effects of adjustment between meta-analyses, the outcome measures are transformed to Hedges $g$ (standardized mean differences) and Fisher's $z$-score (see section \ref{sec:transformation.effectsizes} for details).
-The effect of adjustment can additionally be compared to either random or fixed effects meta-analysis.
+The suggestions of criteria for eligibility for publication bias tests of \citet{Ioannidis2007} have largely been followed:
+\begin{itemize}
+\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = \Sexpr{m.a.largerten.number} remaining). 
+\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = \Sexpr{m.a.smaller.5.number} remaining).
+\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = \Sexpr{m.a.variance4.number} remaining).
+\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = \Sexpr{m.a.one.sig.number} remaining)
+\end{itemize}
+
+After having excluded meta-analyses with less than ten studies, additional criteria for excluding inconvenient meta-analyses are:
+\begin{itemize}
+\item \textbf{Sensitivity Analyses}: When the same results are used multiple times for different meta-analyses, only one is retained.
+More precisely, if a study hat the same \texttt{study.name} and same \texttt{effect}, it was considered a duplicate, and the smaller meta-analysis of the two was excluded.
+The intention is to exclude sensitivity analyses which are operated on subsets of the available results.
+\item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = \Sexpr{all.zero.events.number} out of meta-analyses with at least ten studies).
+\item \textbf{Missing means and sd's}: In the case of continuous outcomes, meta-analyses with means and sd's in any group being equal to zero are excluded ($n$ = \Sexpr{all.zero.means.number} out of meta-analyses with at least ten studies).
+\item \textbf{Single patient data}: Meta-analyses that are comprised of single patient data are excluded ($n$ = \Sexpr{m.a.singlepatient.number} out of meta-analyses with at least ten studies)
+\end{itemize}
+
+--Make Flowchart--
+
+\subsubsection{Exclusions due to Computational Errors}
+In exceptional cases, the applied meta-analysis methods and publication bias tests and adjustment algorithms failed due to various reasons.
+Here, those cases are listed and if known, the reasons why computation failed are given.\\
+\textbf{Binary Outcomes}: Out of the meta-analyses that are of \texttt{outcome.type} bin, and have at least ten studies, two studies hat to be excluded:
+\begin{itemize}
+\item meta.id = 62301 (file.nr = 1531, comparison.nr = 8, outcome.nr = 6, subgroup.nr = 1):
+%A subgroup analysis for women with increased adverse pregnancy outcomes, where the effect of vitamin C supplements is tested on pre-eclampsia: 
+Largest study (se = 0.1) has risk ratio 1 and smallest study (se = 1) risk ratio 0.07. Copas publication bias adjustment methods has likelihood optimization issues.
+\item meta.id = 94519 (2519, 14, 1, 2): Largest study (se = 0.05) has risk ratio 0.9 and smallest study (se = 0.4) risk ratio 3.
+Again Copas publication bias adjustment methods has likelihood optimization issues.
+\end{itemize}
+
+There were no issues with \texttt{outcome.type} ``cont'' and ``surv''.
+For the subsequent information, it is important to know that meta-analyses are only repeated with Hedges $g$, Pearson correlation coefficient and Fisher's Z-scores, if the outcome type is not survival and all of the above criteria are met ($n$ = \Sexpr{length(meta.f$n.sig.type[which(meta.f$outcome.type != "surv")])}).
 \\
-Figure \ref{fig:adjustment.size} displays the difference $\delta$ between the observed meta-analysis pooled treatment effect and the adjusted treatment effect, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
-The absolute value $|\hat{\theta}_M|$ is taken and the sign of $\hat{\theta}_\textrm{Adj.}$ is adjusted accordingly such that all effects are mirrored to one side.
-$\delta > 0$ is equivalent to $\hat{\theta}_\textrm{Adj} < \hat{\theta}_M$, a reduction of the original effect size.
-For better illustration, some very large and very small differences have been omitted in the $z$-score and Hedges $g$ histograms; they are shown in Table \ref{missing.differences}.
-Table \ref{adjustment.difference} shows the quantiles and means for the various differences and additional information.\\
+\textbf{Pearson Correlation Coefficient}: Three studies had to be excluded when analyzing the Pearson correlation coefficients:
+\begin{itemize}
+\item meta.id = 157083 (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2): A meta-analysis with all results from the same study, and equal sample size (5 each group).
+The Copas selection model algorithm issued an error when optimizing the likelihood.
+\item meta.id = 159329 (5183, 3, 13): One very small study with group sizes of 2 and 1 patients and small risk ratio of 0.222 (compared to the largest of 1.05, se = 0.04).
+Also, the Copas selection model algorithm issued an error when optimizing the likelihood.
+\item meta.id = 182298 (6211, 1, 8, -): One very small study with 8 patients in each group and 0 event counts in both.
+The Copas selection model algorithm issued an error when optimizing the likelihood.
+\end{itemize}
 
-\begin{figure}
-<<echo=FALSE, fig.height = 9, warning=FALSE>>=
-grid.arrange(diff.z.fixef, diff.z.ranef,
-             diff.d.fixef, diff.d.ranef,
-             diff.log.hazard.ratio.fixef, diff.log.hazard.ratio.ranef, ncol = 2)
-@
-\caption{Histogram of the treatment effect differences between meta-analysis and adjusted meta-analysis.
-Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes.
-The bins are centered at zero.}
-\label{fig:adjustment.size}
-\end{figure}
+\textbf{Fisher's Z score}: The same issues as encountered for Pearson correlation coefficients (meta.id = 157083 and 159329).
+The variance of the z score $s_z^2$ can be calculated as:  $s_z^2 = \frac{1}{n-3}$, $n$ being the total sample size.
+Thus, studies that have total sample size $n \geq 3$ are discarded in the meta-analyses ($n$ = \Sexpr{total.seq3.number} studies).
+\Sexpr{m.a.seq3.seq10.number} meta-analyses have then less than 10 studies left for pooling:
+\begin{itemize}
+\item meta.id = 10671: (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2), 7 studies left.
+\item meta.id = 43324: (1019, 1, 3, 2), 9 studies left.
+\end{itemize}
 
-<<echo=FALSE, results='asis'>>=
-print(xtable(adjustment.diff.table, label = "adjustment.difference", caption = "Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects.
-The column with the names ``> 0'' give the percentages of estimates larger than zero or larger or equal zero.
-The column ``No adj.
-est.'' gives the percentage of missing estimates due to non-significant publication bias test (for Copas) and computational errors.
-The row names indicate which outcome measure, meta-analysis method and adjustment method is used.
-Abbreviations are used for z-score (= z) and Hedges g (= g).", align = "lcccccccccr"), include.rownames = T, size = "scriptsize",# sanitize.text.function=function(x){x},
-      # table.placement = "p"
-      )
-@
+\subsubsection{The Publication Bias Test and Adjustment Dataset}
+The dataset that was ultimately tested and adjusted for publication bias comprises \Sexpr{dim(metac)[1]} meta-analyses and \Sexpr{dim(meta.data)[1]} results. ..
 
-Adjustment leads most often to reduction of treatment effect estimates, as can be seen by the size of the bins of the right part of the histograms in Figure \ref{fig:adjustment.sue}.
-The difference between the bins on the right and left side of the zero-centered bin is however not very large in general.
-The seeming exception of the Copas selection model in the case with $z$-scores and fixed effects reference requires closer examination: Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
-Thus, when comparing Copas with Fixed effects, we compare most often random effects with fixed effects estimates.
-The effect of adjustment by Copas can therefore only be seen when comparing random effects estimates with fixed effect estimates: we can see in Table \ref{adjustment.difference} that we have, for $z$-score, 18.4\% reduced effect sizes compared to 10.3\% (= 100\% - 89.69\%) increased effect sizes.
-Thus, the Copas selection model also has a larger proportion of reduced effect sizes compared to amplified.\\
-%This resolves the case for the seeming exception and for Hedges $g$'s, 24.4\% and 12.46\% (Table \ref{adjustment.difference}. 
-Also, there are more reduced effect sizes if random effects meta-analysis is used as a reference effect size.
-When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
-\\
-The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} increased by -0.13, fixed effects reference).
-Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or \Sexpr{floor(length(!is.na(meta.f$est.d.reg))*0.05)} meta-analyses (or increased by 0.24).
+% \begin{itemize}
+% \item meta.id = 136563 (4218, 1, 1, 1): ``Roberts 2010'' (3)
+% \item meta.id = 136566 (4218, 1, 3, 1): ``Roberts 2010'' (3)
+% \end{itemize}
 
-\subsection{Change in Evidence for Treatment Effects} \label{sec:change.evidence}
-Adjustment for small study effects in meta-analysis will not only provide new effect sizes, but also standard errors thereof.
-Thus, also the evidence for efficacy of a treatment can be obtained, which is usually summarized in a suitable test statistic or $p$-value.
-It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.\\
-The Wald test statistics $p$-value for fixed and random effects meta-analyses and Copas and regression adjusted treatment effects have been calculated.
-They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and log hazard ratios.
-\\
-It can be seen that evidence for a treatment effect decreases after adjusting for publication bias.
-It does so more for Hedge's $g$ compared to $z$-scores, and for regression adjustment compared to Copas selection model.
-%Also, the evidence decreases for random effects meta-analyses compared to fixed effects meta-analyses. 
-In the case of log-hazard ratio adjustment, the adjustment has only negligible impact on the $p$-values. \\
-Also, Copas selection method has a very small impact on the evidence compared to random effects meta-analysis, at least using $z$-scores (again, we should rely on comparisons to random effects meta-analysis to evaluate Copas method).
-\\
-% Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
-%Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted Hedges $g$ and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.
-
-\begin{figure}
-<<echo=FALSE, fig.height = 9, warning=FALSE>>=
-grid.arrange(adjustment.p.z,
-             adjustment.p.d,
-             adjustment.p.log.hazard.ratio, ncol = 1)
-@
-\caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
-The method is indicated in the header, bin width is set to 0.05.
-The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
-\label{fig:adjustment.stat}
-\end{figure}
-
-The Copas selection model also gives an estimate of the number of missing studies.
-It finds that \Sexpr{round(sum(meta.f$missing.Copas, na.rm = T))} are missing, which corresponds to \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% from all \Sexpr{round(sum(meta.f$k))} analysed studies.
-Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
-Note that we have excluded \Sexpr{sum(is.na(meta.f$missing.Copas))} out of \Sexpr{dim(meta.f)[1]}, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
-
-\begin{figure}
-<<echo = FALSE, warning = FALSE>>=
-missing.copas.histogram
-@
-\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ \Sexpr{sum(!is.na(meta.f$missing.Copas))})}
-\label{fig:copas.missing}
-\end{figure}
-
-We can see that in some occasions, the method finds more than half of all studies are missing.
-In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
-The discrepancy between mean and median may indicate that the estimate of \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% missing studies depends somewhat on these extreme cases.
-As can be written of from Table \ref{copas.missing}, 5\%, \ie \Sexpr{round(sum(!is.na(meta.f$missing.Copas))*0.05)} meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for \Sexpr{sum(meta.f$missing.Copas[which(meta.f$missing.Copas >= 17.60)], na.rm = T)}, more than 30\% of missing studies.
-
-<<echo= FALSE, results='asis'>>=
-print(xtable(missing.copas.table, caption = "Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.",
-             label = "copas.missing", align = "lrrrrrrr", digits = c(0,0,0,0,1,1,1,1)),
-      size = "footnotesize")
-@
-
-<<echo=FALSE, results='asis'>>=
-print(xtable(missing.differences, 
-             caption = "Missing meta-analysis pooled treatment effect and adjusted treatment effects.
-Abbreviations are used for z-score (= z) and Hedges g (= g).", label = "missing.differences", align = "llcccrrrrrrrr"),
-      include.rownames = F, size = "tiny")
-@
-
-\subsection{Comparison of adjustment methods}
-Regression adjusted estimates are compared to the estimates of Copas selection model if these are not equal to random effects meta-analysis.
-A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
-We will compare estimates based on all three outcome measures, i.e.
-original measure, $z$-score and Hedges $g$ in Figure \ref{fig:adjustment.mean.diff}.
-Note that the 39 survival outcome data is not included when using $z$-score and Hedges $g$.
-
-\begin{figure}
-<<echo = FALSE, fig.height = 7.5>>=
-grid.arrange(adjustment.mean.diff.orig,
-             adjustment.mean.diff.z,
-             adjustment.mean.diff.d, ncol = 1)
-@
-\caption{Mean - difference plots for publication bias adjustment methods.
-The mean of the adjusted treatment effects is displayed on the $x$-axis and the difference on the $y$-axis.
-Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).
-Two values have been omitted in the middle plot for Hedges $g$ and one for $z$-score (see Table \ref{missing.differences}).}
-\label{fig:adjustment.mean.diff}
-\end{figure}
-
-No formal tests are provided, but the at least there seems to be no clear bias or systematic.
-The limits of agreement in Figure \ref{fig:adjustment.mean.diff} are large.
-We conclude thus that the impact of regression adjustment on the effect sizes is in general not substantially larger than the impact of Copas selection model in the subset of data where the estimate of the Copas selection model is not equal to a random effects estimate.
-\\
-
-\section{Comparison of Tests and Adjustments} \label{sec:comparison.tests.adjustment}
-<<echo = FALSE, warnings = FALSE>>=
-#--------------------------------------------------------------------------------------------------------------------#
-meta.bin <- adjustment.diff.keep %>% filter(outcome.type == "bin")
-meta.cont <- adjustment.diff.keep %>% filter(outcome.type == "cont")
-meta.surv <- adjustment.diff.keep %>% filter(outcome.type == "surv")
-
-dat_text <- data.frame(
-  label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
-                  sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test), sum(meta.bin$tes.d.test, na.rm = T)), "< 0.1,",
-                round(c(mean(meta.bin$harbord.test), mean(meta.bin$peter.test), 
-                        mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test), mean(meta.bin$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer", "pval.d.tes"),
-  bias.side = rep(0, times = 5))
-
-labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer", pval.d.tes = "Excess Significance")
-
-p.dist.bin.corrected <- meta.bin  %>% ungroup() %>% 
-  select(bias.side, pval.harbord, pval.peter, pval.rucker, pval.schwarzer, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value", pval.harbord:pval.d.tes) %>% 
-  ggplot(aes(x = p.value, fill = factor(bias.side))) + 
-  geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + theme(legend.position = "none") +
-  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 200, label = label), color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + 
-  ggtitle("Binary Outcomes")
-
-#--------------------------------------------------------------------------------------------------------------------#
-#Continuous Outcomes:
-dat_text <- data.frame(
-  label = paste(c(sum(meta.cont$begg.test), sum(meta.cont$egger.test), sum(meta.cont$thompson.test), sum(meta.cont$tes.d.test, na.rm = T)), "< 0.1,",
-                round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test), mean(meta.cont$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"),
-  bias.side = rep(0, times = 4))
-
-labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp", pval.d.tes = "Excess significance")
-
-p.dist.cont.corrected <- meta.cont %>% ungroup() %>% 
-  select(bias.side, pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value", pval.egger:pval.d.tes) %>% 
-  ggplot(aes(x = p.value, fill = factor(bias.side))) + 
-  geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + theme(legend.position = "none") +
-  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 60, label = label),  color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + ggtitle("Continuous Outcomes")
-
-#--------------------------------------------------------------------------------------------------------------------#
-dat_text <- data.frame(
-  label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), 
-                  sum(meta.surv$thompson.test), sum(meta.surv$tes.d.test, na.rm = T)), "< 0.1,",
-                round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), 
-                        mean(meta.surv$thompson.test), 
-                        mean(meta.surv$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"),
-  bias.side = rep("publication bias", times = 4))
-p.dist.surv.corrected <- meta.surv %>% ungroup() %>% 
-  mutate(bias.side = factor(ifelse(bias.side == 1, "publication bias", "negative publication bias"))) %>% 
-  select(bias.side, pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
-  gather(key = "test.type", value = "p.value", pval.egger:pval.d.tes) %>% 
-  ggplot(aes(x = p.value, fill = factor(bias.side))) + 
-  geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + guides(fill=guide_legend(title=NULL))+
-  theme(legend.position = "bottom") +
-  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 10, label = label),  color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + ggtitle("Survival Outcomes")
-@
-
-In section \ref{sec:change.size}, we have seen that some adjustments for small study effects are not in line with our previous definition of publication bias: Some times, the adjustment for small study effects leads to a larger treatment effect.
-We want to take this into account when considering evidence for publication bias.
-Whenever adjustment leads to larger effect sizes, the small study effect test result from section \ref{sec:publication.bias.tests} is revised and changed to negative.
-We will revisit the results from section \ref{sec:publication.bias.tests} and first visualize which proportion of the data finds rather ``negative publication bias'' than the predefined type of publication bias.
-Figure \ref{fig:test.corrected} is equal to Figure \ref{fig:test} with sole difference that now the proportion of ``negative publication bias'' is colored, and the count of significant findings is corrected (not significant for negative publication bias).
-\\
-
-\begin{figure}
-<<echo=FALSE, fig.height = 9>>=
-grid.arrange(p.dist.bin.corrected,
-             p.dist.cont.corrected,
-             p.dist.surv.corrected, ncol = 1)
-@
-\caption{Histogram of the $p$-values for small study effect in meta-analyses.
-The testing method is indicated in the header, bin width is equal to 0.1.
-The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
-\label{fig:test.corrected}
-\end{figure}
-
-The proportion of findings where we found amplification by adjustment was \Sexpr{round((1-sum(adjustment.diff.keep$bias.side)/dim(adjustment.diff.keep)[1])*100, 1)}\%.
-Most often, the proportion of tests with evidence for small study effects (and especially, excess significance), is lower, though.
-There are exceptions to this, such as Schwarzer's test results, where we have 143 - 60 = 83 significant test results, which corresponds to $\sim$ 40\%.
-Since excess significance is not necessarily connected with small study effects, we can furthermore reject the newly obtained, slightly smaller number of significant excess significance test results, and stick to the previous findings.
-\\
-We can see how the agreement in significance is before, and after having removed negative publication bias significant results in Table \ref{test.agreement}.
-The proportion of agreement in significance is defined as the proportion of cases where, when the test with less significant findings is significant, also the other is significant.
-\\
-After the adjustment of the test results, the agreement for small study effects tests and excess significance tests increases a bit.
-This seems also to be the general trend, but not without exceptions.
-The two right-most columns indicate the agreement in significance, and we see that agreement is never larger than 0.3 (with Egger's test, continuous outcomes).
-Furthermore, only Egger and Thompson show a goof agreement for significance ($\sim$ 0.83).
-In contrast, some small study effect tests for binary outcomes seem rather to be exclusive, see for example the example of Schwarzer's test (6\% after adjustment) and R\"ucker's test (11\%): Only 19 \% of the cases where Schwarzer's Test is significant have also a significant finding using R\"ucker's test.
-Almost all binary small study effect tests have agreement in significance > 0.5.
-Thus, we see that large overall agreement is rather due to the large proportion of non-significant findings.
-
-<<echo = FALSE, warning= FALSE>>=
-#Agreement proportions of publication bias tests:
-
-#Binary:
-meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
-                                              tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
-                                              tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
-                                              tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
-                                              schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
-                                              schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
-                                              schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
-                                              rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
-                                              rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
-                                              harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
-agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
-                                                      tes.d.peter = sum(tes.d.peter == "agree")/n(),
-                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
-                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
-                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
-                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
-                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
-                                                      rucker.peter = sum(rucker.peter == "agree")/n(),
-                                                      harbord.peter = sum(harbord.peter == "agree")/n())
-meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test + schwarzer.test > 1, "agree", "disagree"),
-                                              tes.d.peter = ifelse(tes.d.test + peter.test > 1, "agree", "disagree"),
-                                              tes.d.rucker = ifelse(tes.d.test + rucker.test > 1, "agree", "disagree"),
-                                              tes.d.harbord = ifelse(tes.d.test + harbord.test > 1, "agree", "disagree"),
-                                              schwarzer.peter = ifelse(schwarzer.test + peter.test > 1, "agree", "disagree"),
-                                              schwarzer.rucker = ifelse(schwarzer.test + rucker.test > 1, "agree", "disagree"),
-                                              schwarzer.harbord = ifelse(schwarzer.test + harbord.test > 1, "agree", "disagree"),
-                                              rucker.peter = ifelse(rucker.test + peter.test > 1, "agree", "disagree"),
-                                              rucker.harbord = ifelse(rucker.test + harbord.test > 1, "agree", "disagree"),
-                                              harbord.peter = ifelse(harbord.test + peter.test > 1, "agree", "disagree"))
-agreement.sig.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/sum(schwarzer.test),
-                                                      tes.d.peter = sum(tes.d.peter == "agree")/sum(peter.test),
-                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/sum(rucker.test),
-                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/sum(harbord.test),
-                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/sum(schwarzer.test),
-                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/sum(schwarzer.test),
-                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/sum(schwarzer.test),
-                                                      rucker.peter = sum(rucker.peter == "agree")/sum(peter.test),
-                                                      harbord.peter = sum(harbord.peter == "agree")/sum(peter.test))
-
-binary.tests.agreement <- rbind(agreement.bin, agreement.sig.bin)
-rownames(binary.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
-colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
-                                      "Excess significance, Rucker", "Excess significance, Harbord",
-                                      "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
-                                      "Rucker, Peter", "Harbord, Peter")
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Continuous:
-meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
-                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
-                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
-                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
-                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
-                                                         egger.begg = sum(egger.begg == "agree")/n())
-meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
-agreement.sig.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
-                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
-                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
-                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
-                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
-                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))
-
-cont.tests.agreement <- rbind(agreement.cont, agreement.sig.cont)
-rownames(cont.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
-colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson",
-                                     "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Survival:
-meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
-                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
-                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
-                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
-                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
-                                                         egger.begg = sum(egger.begg == "agree")/n())
-meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
-                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
-                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
-                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
-                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
-agreement.sig.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
-                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
-                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
-                                                             thompson.egger = sum(thompson.egger == "agree")/sum(egger.test),
-                                                             thompson.begg = sum(thompson.begg == "agree")/sum(thompson.test),
-                                                             egger.begg = sum(egger.begg == "agree")/sum(egger.test))
-
-surv.tests.agreement <- rbind(agreement.surv, agreement.sig.surv)
-rownames(surv.tests.agreement) <- c("Agreement (overall)","Agreement (significance)")
-colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)",
-                                    "Excess significance, Begg (survival)", "Thompson, Egger (survival)",
-                                    "Thompson, Begg (survival)", "Egger, Begg (survival)")
-
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Merging:
-test.agreement.new <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
-
-test.agreement.together <- data.frame(test.agreement[,1], test.agreement.new[,1],
-                                      test.agreement[,2], test.agreement.new[,2])
-
-colnames(test.agreement.together) <- c("pre, overall", "post, overall", "pre, significance",
-                                      "post, significance")
-
-#--------------------------------------------------------------------------------------------------------------------#
-@
-
-<<echo=FALSE, results='asis'>>=
-print(xtable(test.agreement.together, align = "lcccc", caption = "Overall proportion of agreement if significant or unsignificant, and for significance only.
-Horizontal lines separate binary, continuous and survival outcomes (order as in table).
-The reference significance test is the one with more significant results.",
-             label = "test.agreement"), hline = c(0, 0, 9, 15, 21), size = "scriptsize")
-@
+%which leads to a reduction of the meta-analyses that can be calculated based on the Fisher's z score by $n$ = \Sexpr{}

### 2019-07-05 report/chapter04.Rnw
adjustments after correction

--- 2019-06-24 report/chapter04.Rnw
@@
-% LaTeX file for Chapter 04
-<<'preamble04',include=FALSE>>=
+% LaTeX file for Chapter 03
+
+<<'preamble03',include=FALSE, echo=FALSE>>=
 library(knitr)
-opts_chunk$set(
-    fig.path='figure/ch04_fig', 
-    self.contained=FALSE,
-    cache=FALSE
+opts_chunk$set(fig.path='figure/ch03_fig',
+               echo=TRUE, message=FALSE,
+               fig.width=8.1, fig.height=3,
+               self.contained = FALSE,
+               out.width='\\textwidth-3cm',
+               message=FALSE, fig.align='center',
+               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
+               cache=TRUE
 )
-@
-
-\chapter{Methods}
-\section{Introduction and Notation}
-The analysis has already been said to be restricted on clinical or health care interventions.
-The interventions are restricted to comparisons of two treatment arms by some measure of sanity or worsening of health.
-The difference in this measure between the grouops is referred to as the treatment effect.
-Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or Hedges $g$, Fisher's z score or Pearsons correlation coefficient.
+options(width=74)
+@
+
+<<'Data03', echo=FALSE, warning=FALSE>>= 
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "meta.bin.RData"))
+load(file.path(PATH_RESULTS, "meta.cont.RData"))
+load(file.path(PATH_RESULTS, "meta.surv.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+
+require(corrgram)
+
+# data.ext2 <- pb.process2(data)
+@
+
+\chapter{Results} \label{ch:Results}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Publication Bias Test Results} \label{sec:publication.bias.tests}
+<<echo=FALSE, warning=FALSE>>=
+meta.f <- meta.f %>% rowwise() %>% mutate(pval1.egger = onesided.p(stat = stat.egger, side = side, n = k, test.type = "reg"),
+                                pval1.thompson = onesided.p(stat = stat.thompson, side = side, n = k, test.type = "reg"),
+                                pval1.begg = onesided.p(stat = stat.begg, side = side, n = k, test.type = "rank"),
+
+                                pval1.harbord = onesided.p(stat = stat.harbord, side = side, n = k, test.type = "reg"),
+                                pval1.rucker = onesided.p(stat = stat.rucker, side = side, n = k, test.type = "reg"),
+                                pval1.peter = onesided.p(stat = stat.peter, side = side, n = k, test.type = "reg"),
+                                pval1.schwarzer = onesided.p(stat = stat.schwarzer, side = side, n = k, test.type = "rank"),
+                                pval1.d.tes = pval.d.tes)
+
+sig.level <- 0.1
+meta.f <- meta.f %>% 
+	mutate(egger.test = ifelse(pval1.egger < sig.level, 1, 0),
+				 thompson.test = ifelse(pval1.thompson < sig.level, 1, 0),
+				 begg.test = ifelse(pval1.begg < sig.level, 1, 0),
+
+				 tes.d.test = ifelse(pval1.d.tes < sig.level, 1, 0),
+
+				 schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
+				 rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
+				 harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
+				 peter.test = ifelse(pval1.peter < sig.level, 1, 0))
+
+meta.bin <- meta.f %>% filter(outcome.type == "bin")
+meta.cont <- meta.f %>% filter(outcome.type == "cont")
+meta.surv <- meta.f %>% filter(outcome.type == "surv")
+
+#Agreement proportions of publication bias tests:
+
+#Binary:
+meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
+                                              tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
+                                              tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
+                                              tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
+                                              schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
+                                              schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
+                                              schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
+                                              rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
+                                              rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
+                                              harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
+agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
+                                                      tes.d.peter = sum(tes.d.peter == "agree")/n(),
+                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
+                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
+                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
+                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
+                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
+                                                      rucker.peter = sum(rucker.peter == "agree")/n(),
+                                                      harbord.peter = sum(harbord.peter == "agree")/n())
+meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test + schwarzer.test > 1, "agree", "disagree"),
+                                              tes.d.peter = ifelse(tes.d.test + peter.test > 1, "agree", "disagree"),
+                                              tes.d.rucker = ifelse(tes.d.test + rucker.test > 1, "agree", "disagree"),
+                                              tes.d.harbord = ifelse(tes.d.test + harbord.test > 1, "agree", "disagree"),
+                                              schwarzer.peter = ifelse(schwarzer.test + peter.test > 1, "agree", "disagree"),
+                                              schwarzer.rucker = ifelse(schwarzer.test + rucker.test > 1, "agree", "disagree"),
+                                              schwarzer.harbord = ifelse(schwarzer.test + harbord.test > 1, "agree", "disagree"),
+                                              rucker.peter = ifelse(rucker.test + peter.test > 1, "agree", "disagree"),
+                                              rucker.harbord = ifelse(rucker.test + harbord.test > 1, "agree", "disagree"),
+                                              harbord.peter = ifelse(harbord.test + peter.test > 1, "agree", "disagree"))
+agreement.sig.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/sum(tes.d.test),
+                                                      tes.d.peter = sum(tes.d.peter == "agree")/sum(tes.d.test),
+                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/sum(tes.d.test),
+                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/sum(tes.d.test),
+                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/sum(schwarzer.test),
+                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/sum(schwarzer.test),
+                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/sum(schwarzer.test),
+                                                      rucker.peter = sum(rucker.peter == "agree")/sum(rucker.test),
+                                                      harbord.peter = sum(harbord.peter == "agree")/sum(peter.test))
+
+binary.tests.agreement <- rbind(agreement.bin, agreement.sig.bin)
+rownames(binary.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
+colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
+                                      "Excess significance, Rucker", "Excess significance, Harbord",
+                                      "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
+                                      "Rucker, Peter", "Harbord, Peter")
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Continuous:
+meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
+                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
+                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
+                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
+                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
+                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
+agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
+                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
+                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
+                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
+                                                         egger.begg = sum(egger.begg == "agree")/n())
+meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
+                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
+                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
+                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
+                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
+                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
+agreement.sig.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
+                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
+                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
+                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
+                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
+                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))
+
+cont.tests.agreement <- rbind(agreement.cont, agreement.sig.cont)
+rownames(cont.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
+colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson",
+                                     "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Survival:
+meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
+                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
+                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
+                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
+                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
+                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
+agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
+                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
+                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
+                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
+                                                         egger.begg = sum(egger.begg == "agree")/n())
+meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
+                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
+                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
+                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
+                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
+                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
+agreement.sig.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
+                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(thompson.test),
+                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(begg.test),
+                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
+                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
+                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))
+
+surv.tests.agreement <- rbind(agreement.surv, agreement.sig.surv)
+rownames(surv.tests.agreement) <- c("Agreement (overall)","Agreement (significance)")
+colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)",
+                                    "Excess significance, Begg (survival)", "Thompson, Egger (survival)",
+                                    "Thompson, Begg (survival)", "Egger, Begg (survival)")
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Merging:
+test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
+
+sig.level <- 0.1
+meta.f <- meta.f %>% rowwise() %>% 
+  mutate(egger.test = ifelse(pval1.egger < sig.level, 1, 0),
+         thompson.test = ifelse(pval1.thompson < sig.level, 1, 0),
+         begg.test = ifelse(pval1.begg < sig.level, 1, 0),
+
+         schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
+         rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
+         harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
+         peter.test = ifelse(pval1.peter < sig.level, 1, 0),
+         I2 = max(c(0, 1 - (k-1)/Q)),
+         i2f = factor(ifelse(I2 == 0, 1, 0)))
+
+meta.bin <- meta.f %>% filter(outcome.type == "bin")
+meta.cont <- meta.f %>% filter(outcome.type == "cont")
+meta.surv <- meta.f %>% filter(outcome.type == "surv")
+
+dat_text <- data.frame(
+  label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
+                  sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test), sum(meta.bin$tes.d.test, na.rm = T)), "< 0.1,",
+                round(c(mean(meta.bin$harbord.test), mean(meta.bin$peter.test), 
+                        mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test), mean(meta.bin$tes.d.test, na.rm = T)),2)*100, "%"),
+  test.type   = c("pval1.harbord", "pval1.peter", "pval1.rucker", "pval1.schwarzer", "pval1.d.tes"),
+  i2f = factor(rep(0, times = 5)))
+
+labels <- c(pval1.harbord = "Harbord", pval1.peter = "Peter", pval1.rucker = "Rucker", pval1.schwarzer = "Schwarzer", pval1.d.tes = "Excess Significance")
+
+p.dist.bin <- meta.bin %>% ungroup() %>% 
+  select(i2f, pval1.harbord, pval1.peter, pval1.rucker, pval1.d.tes, pval1.schwarzer) %>% 
+  gather(key = "test.type", value = "p.value", pval1.harbord:pval1.schwarzer) %>% 
+  ggplot(aes(x = p.value, fill = i2f)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 200, label = label), color = "black") + 
+  theme(strip.text.x = element_text(size=7)) + ggtitle("Binary Outcomes") + 
+  theme(legend.position = "none")
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+dat_text <- data.frame(
+  label = paste(c(sum(meta.cont$begg.test), sum(meta.cont$egger.test), sum(meta.cont$thompson.test), sum(meta.cont$tes.d.test, na.rm = T)), "< 0.1,",
+                round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test), mean(meta.cont$tes.d.test, na.rm = T)),2)*100, "%"),
+  test.type   = c("pval1.begg", "pval1.egger", "pval1.thompson", "pval1.d.tes"),
+  i2f = factor(rep(0, times = 4)))
+
+labels <- c(pval1.begg = "Begg Mazumdar", pval1.egger = "Egger", pval1.thompson = "Thompson Sharp", pval1.d.tes = "Excess significance")
+p.dist.cont <- meta.cont %>% ungroup() %>% 
+  select(i2f, pval1.egger, pval1.thompson, pval1.begg, pval1.d.tes) %>% 
+  gather(key = "test.type", value = "p.value", pval1.egger:pval1.d.tes) %>% 
+  ggplot(aes(x = p.value, fill = i2f)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
+  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 60, label = label),  color = "black") + 
+  theme(strip.text.x = element_text(size=7)) + ggtitle("Continuous Outcomes") + 
+  theme(legend.position = "none")
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+dat_text <- data.frame(
+  label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), sum(meta.surv$thompson.test), sum(meta.surv$tes.d.test, na.rm = T)), "< 0.1,",
+                round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), mean(meta.surv$thompson.test), mean(meta.surv$tes.d.test, na.rm = T)),2)*100, "%"),
+  test.type   = c("pval1.begg", "pval1.egger", "pval1.thompson", "pval1.d.tes"),
+  i2f = factor(rep(0, times = 4)))
+
+p.dist.surv <- meta.surv %>% ungroup() %>% 
+  select(i2f, pval1.egger, pval1.thompson, pval1.begg, pval1.d.tes) %>% 
+  gather(key = "test.type", value = "p.value", pval1.egger:pval1.d.tes) %>% 
+  ggplot(aes(x = p.value, fill = i2f)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
+  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+  guides(fill=guide_legend(title=expression(paste(I^2, " Heterogeneity")))) + 
+  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 10, label = label),  color = "black")  + 
+  scale_fill_discrete(labels = c("> 0", "= 0")) +
+  theme(strip.text.x = element_text(size=7)) + 
+  ggtitle("Survival Outcomes") 
+#--------------------------------------------------------------------------------------------------------------------#
+
+################################################################################################
+################################################################################################
+#PUBLICATION BIAS TEST AGREEMENT
+################################################################################################
+################################################################################################
+
+cor.data <- meta.f %>% select(stat.rucker, stat.harbord, stat.peter, stat.schwarzer, 
+                             stat.egger, stat.thompson, stat.begg, I2)
+colnames(cor.data) <- c("Rucker", "Harbord", "Peter", "Schwarzer", "Egger", "Thompson",
+                        "Begg", "I-squared")
+
+panel.pts.new <- function (x, y, corr = NULL, col.regions, cor.method, ...) 
+{
+
+  plot.xy(xy.coords(x, y), type = "p", ...)
+  box(col = "lightgray")
+  rect(xleft = -1.644854, ybottom = -1.644854, xright = 1.644854, ytop = 1.644854, density = NULL, angle = 45,
+       col = NA, border = "white", lty = 1, lwd = 1.4, 
+       ...)
+  if (!is.null(corr)) 
+    return()
+
+}
+
+# Tukey Mean difference plots;
+#--------------------------------------------------------------------------------------------------------------------#
+
+egger.thompson.plot <- meta.f %>% 
+  mutate(mean = ((logit(pval1.egger)+ logit(pval1.thompson)))/2, 
+         difference = logit(pval1.egger) - logit(pval1.thompson)) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point() + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + theme(legend.position = "none") +
+  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+                     values = c("red", "blue")) +
+  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value Thompson)" )))
+#--------------------------------------------------------------------------------------------------------------------#
+
+egger.excess.plot <- meta.f %>% 
+  mutate(mean = ((logit(pval1.egger)+ logit(pval1.d.tes)))/2, 
+         difference = logit(pval1.egger) - logit(pval1.d.tes)) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point() + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + theme(legend.position = "none") +
+  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+                     values = c("red", "blue")) +
+  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value excess significance)" )))
+#--------------------------------------------------------------------------------------------------------------------#
+
+harbord.rucker.plot <- meta.f %>% 
+  mutate(mean = ((logit(pval1.harbord)+ logit(pval1.rucker)))/2, 
+         difference = logit(pval1.harbord) - logit(pval1.rucker)) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + theme(legend.position = "none") +
+  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+                     values = c("red", "blue")) +
+  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value Rucker)" )))
+#--------------------------------------------------------------------------------------------------------------------#
+
+harbord.excess.plot <- meta.f %>% 
+  mutate(mean = ((logit(pval1.harbord)+ logit(pval1.d.tes)))/2, 
+         difference = logit(pval1.harbord) - logit(pval1.d.tes)) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + #theme(legend.position = "bottom") +
+  scale_color_manual(labels = c("systematic error", "95 % conf. int."), 
+                     values = c("red", "blue")) +
+  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value excess significance)" )))
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Table with proportions of significant test results:
+meta.f <- meta.f %>% 
+mutate(test.sum.bin = tes.d.test + schwarzer.test + harbord.test + peter.test + rucker.test,
+       test.sum.else = tes.d.test + egger.test + thompson.test + begg.test, 
+       test.sum.bin2 = tes.d.test + harbord.test,
+       test.sum.else2 = tes.d.test + egger.test, 
+       test.min.bin = ifelse(schwarzer.test + harbord.test + peter.test + rucker.test > 0, 1, 0),
+       test.min.else = ifelse(egger.test + thompson.test + begg.test > 0, 1, 0),
+       test.min.bin2 = ifelse(test.sum.bin2 > 0, 1, 0),
+       test.min.else2 = ifelse(test.sum.else2 > 0, 1, 0))
+
+mean.min.bin <- round(mean(meta.f$test.min.bin, na.rm = T)*100, 1)
+mean.min.else <- round(mean(meta.f$test.min.else, na.rm = T)*100, 1)
+
+mean.min.bin2 <- round(mean(meta.f$test.min.bin2, na.rm = T)*100, 1)
+mean.min.else2 <- round(mean(meta.f$test.min.else2, na.rm = T)*100, 1)
+
+both.bin <- round(length(which(meta.f$test.sum.bin2 == 2))/
+                    length(which(!is.na(meta.f$test.sum.bin2)))*100, 1)
+
+both.else <- round(length(which(meta.f$test.sum.else2 == 2))/
+                     length(which(!is.na(meta.f$test.sum.else2)))*100, 1)
+
+summary.bin <- round(meta.f %>% 
+  group_by(test.sum.bin) %>% summarise(n = n()) %>% select(n)/dim(meta.bin)[1] * 100, 1)
+
+summary.else <- round(meta.f %>% group_by(test.sum.else) %>% 
+                        summarise(n = n()) %>% 
+                        select(n)/(dim(meta.cont)[1] + dim(meta.surv)[1]) * 100, 1)
+
+number.sig.tests <- data.frame(number = seq(from = 0, to = 5),
+                               binary = paste(summary.bin$n[-7], "%"),
+                               cont = as.character(paste(c(summary.else$n[-c(6,7)], NA), "%")))
+number.sig.tests <- as.matrix(number.sig.tests)
+number.sig.tests[6,3][1] <- "-"
+
+colnames(number.sig.tests) <- c("Count", "Binary Outcomes", "Continuous and Survival")
+
+meta.f <- meta.f %>% mutate(tes.d.test.b = ifelse(pval1.d.tes < 0.05, 1, 0),
+                            harbord.test.b = ifelse(pval1.harbord < 0.05, 1, 0),
+                            egger.test.b = ifelse(pval1.egger < 0.05, 1, 0),
+                            test.sum.bin2 = tes.d.test.b + harbord.test.b,
+                            test.sum.else2 = tes.d.test.b + egger.test.b, 
+                            test.min.bin2 = ifelse(test.sum.bin2 > 0, 1, 0),
+                            test.min.else2 = ifelse(test.sum.else2 > 0, 1, 0))
+
+mean.min.bin2.b <- round(mean(meta.f$test.min.bin2, na.rm = T)*100, 1)
+mean.min.else2.b <- round(mean(meta.f$test.min.else2, na.rm = T)*100, 1)
+
+both.bin.b <- round(length(which(meta.f$test.sum.bin2 == 2))/
+                    length(which(!is.na(meta.f$test.sum.bin2)))*100, 1)
+
+both.else.b <- round(length(which(meta.f$test.sum.else2 == 2))/
+                     length(which(!is.na(meta.f$test.sum.else2)))*100, 1)
+
+meta.f <- meta.f %>% mutate(egger.test = ifelse(pval1.egger < 0.1/3, 1, 0),
+                            thompson.test = ifelse(pval1.thompson < 0.1/3, 1, 0),
+                            begg.test = ifelse(pval1.begg < 0.1/3, 1, 0),
+
+                            schwarzer.test = ifelse(pval1.schwarzer < 0.1/4, 1, 0),
+                            rucker.test = ifelse(pval1.rucker < 0.1/4, 1, 0),
+                            harbord.test = ifelse(pval1.harbord < 0.1/4, 1, 0),
+                            peter.test = ifelse(pval1.peter < 0.1/4, 1, 0),
+                            test.sum.bin = tes.d.test + schwarzer.test + harbord.test + peter.test + rucker.test,
+                            test.sum.else = tes.d.test + egger.test + thompson.test + begg.test, 
+                            test.min.bin = ifelse(schwarzer.test + harbord.test + peter.test + rucker.test > 0, 1, 0),
+                            test.min.else = ifelse(egger.test + thompson.test + begg.test > 0, 1, 0))
+
+mean.min.bin.b <- round(mean(meta.f$test.min.bin, na.rm = T)*100, 1)
+mean.min.else.b <- round(mean(meta.f$test.min.else, na.rm = T)*100, 1)
+
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+
+@
+
+The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with one-sided small study effects tests and excess significance tests.
+The direction in which bias is expected is the one on which more significant results are ($p$-value < 0.05, two-sided).
+The tests are applied on the original effect size measures, i.e.
+risk ratios, Hedges $g$ or log hazard ratios.
+Different tests are applied depending on the outcome type being binary, continuous or survival.\\
+Thus, multiple tests are applied on the same data.
+The results can then be displayed separately to compare the results from the different tests.
+A histogram of $p$-values will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.
 \\
-Let us consider a meta-analysis with $n$ study treatment effects ($n > 1$, but typically small).
-A study is indexed by $i$, and it's treatment effect by  $\theta_i$.
-The observed treatment effect is $\hat{\theta}_i$.
-The pooled treatment effect of a meta-analysis will be denoted as $\theta_M$, and consequently, the observed pooled treatment effect as $\hat{\theta}_M$.
-Furthermore, each treatment effect is typically measured with some standard error $s_i$ and an estimate of $s_i$ is denoted as $\hat{s}_i$.
-The $\hat{}$ sign thus indicates if it is an estimate.\\
-For continuous outcomes, let $m_t$ be the mean of the treatment group, $m_c$ the mean of the control group, and equivalently $\textrm{sd}_t$ and $\textrm{sd}_c$ the corresponding standard deviations.
-$n_t$ and $n_c$ are the total number of participants in the groups.
-In the case of binary outcomes, let $e_t$ be the count of events in the treatment arm $e_c$ the count of events in the control group.
-The observed counts in a study $i$ are referred to as $e_{t,i}$ and analogously $e_{c,i}$.
-
-\section{Effect Measures and $p$-values}
-\subsection{Continuous Outcomes}
-For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Hedges $g$) and  a standard error thereof.
-Note that the definition of Hedges $g$ and its standard error $s$ varies among the literature, the following applies for this report:
-
-\begin{align}
-s &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}} & g &= \frac{m_t - m_c}{s} \label{eq:hedges.g}
-\end{align}
-
-The mean difference $\theta$ and its standard error $s$ can similarly be obtained by
-
-\begin{align}
-\theta &= m_t - m_c & s &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_t}
-\end{align}
-
-Both estimators take into account that the two groups might have unequal variances.
-A $p$-value to test the null hypothesis that the mean between group is equal is commonly obtained with the students $t$ test.
-The $t$ statistic is obtained, using $s$ and $g$ from \ref{eq:hedges.g}, by
-
-\begin{align}
-t &= g/(s\sqrt{(1/n_t)+(1/n_c)}) \nonumber
-\end{align}
-and the $p$-value can be obtained with the cumulative student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
-
-\begin{align}
-p &= 2(1-F(|t|)) \nonumber
-\end{align}
-
-The t-test is known to be not very reliable if combined sample size is small ($n < 30$), see for example \citet{t.test}.
-
-\subsection{Binary Outcomes}
-Two commonly used effect measures for binary outcome data are risk ratios and odds ratios between treatment and control group. 
-The methods presented here can also be found, for example, in \cite[34]{Intro.meta}.
-Let $\theta$ be the logarithm to base 10 of the odds ratio. $\theta$ and its variance $s^2$ can be obtained by
-
-\begin{align}
-\hat{\theta} &= \log(\frac{e_t*(n_c - e_c)}{e_c*(n_t - e_t)}) \nonumber \\
-\hat{s}^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
-\end{align}
-
-Plugging in the observed counts will give the corresponding estimates. The logarithm of the risk ratio $\theta$ and its variance $s^2$ is similarly defined as
-
-\begin{align}
-\theta &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
-s^2 &= 1/e_t + 1/n_t + 1/e_c + 1/e_t \label{eq:risk.ratio.variance}
-\end{align}
-
-Using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$-value, e..g.
-\cite[98]{held2014}.
+``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}.
+For continuous and survival outcomes, the names refer to:
+
+\begin{itemize}
+\item Egger's test, the weighted linear regression test as described in section \ref{sec:Egger}
+\item Thompson and Sharp's test, the weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
+\item Begg and Mazumdar's test, the rank test described in section \ref{sec:Begg}
+\end{itemize}
+
+For binary outcomes, the names refer to:
+\begin{itemize}
+\item Harbord's test, the likelihood score based test (section \ref{sec:Harbord})
+\item Peter's test, the weighted linear regression with inverse sample size as explanatory variable (study size proxy) described in section \ref{sec:Peter}
+\item R\"ucker's test, the test based on the arcsine transformation of proportions, in combination with Thompson and Sharp's regression test (section \ref{sec:Rucker})
+\item Schwarzer's test, the rank based test using the expected event counts computed with the hypergeometric distribution (section \ref{sec:Schwarzer})
+\end{itemize}
+
+\begin{figure}
+<<echo=FALSE, fig.height = 9>>=
+grid.arrange(p.dist.bin,
+             p.dist.cont,
+             p.dist.surv, ncol = 1)
+@
+\caption{Histogram of one-sided $p$-values for small study effect in direction of larger effect sizes.
+The testing method is indicated in the header, bin width is equal to 0.1.
+The proportion of meta-analyses with signifiant publication bias based on the threshold of 0.1 is displayed inside the figures.}
+\label{fig:test}
+\end{figure}
+
+%Agreement table -> Chunck 1
+The histograms in Figure \ref{fig:test} show that most distributions are clearly skewed to the right, indicating evidence for small study effects.
+Exceptions from this are the excess significance and Schwarzer's test, and the tests for survival outcomes.
+There, there is no evidence for publication bias, and the histograms are even skewed to the left (Schwarzer).
+But note that the sample size of survival outcomes is small ($n$ = \Sexpr{dim(meta.surv)[1]}).
 \\
-Thus, with $\Phi$ as the cumulative standard normal distribution, we get
-\begin{align}
-p &= 2*(1-\Phi(|\hat{\theta}/\hat{s}|) \nonumber
-\end{align}
-, a $p$-value for the corresponding estimates, which summarizes the evidence against $\hat{\theta}$ being zero (i.e. the true risk/odds ratio being 1). \\
-Binary and continuous effect measures can be converted into each other, as described in section \ref{sec:transformation.effectsizes}.
-
-\subsection{Survival Outcomes}
-Time-to-event data with censoring has to be analyzed by special means.
-One frequently used method to take into account right-censoring is the Cox proportional hazards regression model \citep{Cox}.
-Because the method itself is not applied in this thesis, but only the resulting estimates of the parameters are used, the reader is referred to the extensive literature covering this topic (e.g.
-\citet{Surv}).
+There is discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger.
+Also, we see that the $I^2$ statistic of the proportion of overall between-study heterogeneity is distributed differently for the tests, with results with $I^2 = 0$ being evenly distributed in binary outcomes along the range of $p$-values, while they are more similar to the meta-analyses with larger heterogeneity for continuous outcome.\\
+In the literature, the excess significance test is advised to be used in the case of no between study heterogeneity.
+Since there are no small $p$-values for such meta-analyses, one must conclude that there is no excess significance in the dataset.
+The obvious correspondence with the heterogeneity statistic however rather suggests that the test is another way to assess between study heterogeneity.
+Thompson test and R\"ucker's test are designed such that they take into account the between study heterogeneity when assessing small study effects.
+When no heterogeneity is given, Thompson's test results and Egger's test result should be equal, however, the $I^2$ statistic is computed by a more suitable estimator \citep{paulemandel} of $\tau^2$ as the estimator that Thompson and Sharp's test uses (method of moment estimator of \citet{tau.estimator}, which is more conservative by usually finding larger $\tau^2$).
+In the part of the histogram with $I^2 > 0$, the two tests are more reliable than the remaining tests, while the opposite is expected from simulations \citep{limitmeta} when $I^2 = 0$.\\
+
+It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects for the same meta-analyses.
+A simple method to check the consistency of test results is to compare scatterplots and empirical Spearman correlations between the test statistics.
+This is done in Figure \ref{fig:test.agreement}.
+Here, there is no separation between survival and continuous outcomes.
+The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results.
+Also, the $I^2$ statistic is included.
+Since no test statistic is used for excess significance tests, it is not shown here
+
+\begin{figure}
+<<echo=FALSE, fig.height = 7, fig.width = 8.5, warning=FALSE>>=
+corrgram(cor.data, 
+         upper.panel=panel.pts.new, lower.panel=panel.cor, 
+         cex.labels = 1, cex = .25, cex.cor = 2, pch = 1,
+         text.panel=panel.txt, cor.method = "spearman")
+@
+\caption{Pairs-plot for test statistics of small study effect and excess significance.
+The lower panel gives the Spearman correlations for the different test statistics, and the upper panel displays a scatterplot.
+The colors indicate magnitude and direction of the correlation coefficients.
+The rectangle with white borders displays the area within which both tests have absolute value < 1.64 (dots outside are statistically significant by 0.1 $p$-value threshold).}
+\label{fig:test.agreement}
+\end{figure}
+
+The observed patterns on the scatterplots differ, and some small study effect test statistics do align better than others.
+Regression based tests as Egger and Thompsons test which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients.
+Continuous and survival outcome type tests align more closely than binary outcome tests.
+While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics.\\
+Because scatterplots and correlation coefficients can be misleading, also a Tukey mean-difference or Bland-Altman of transformed $p$-values plot is shown for four scenarios in Figure \ref{fig:mean.diff.test}:
+\begin{itemize}
+\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
+\item For Egger's and excess significance tests
+\item For Harbord's and R\"ucker's tests
+\item For Harbord's and excess significance tests
+\end{itemize}
+
+This can be justified since all tests are supposed to measure the evidence for publication bias.
+For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation $f(x)  = \log\frac{p}{1-p}$).
+The mean $p$-value (($f$($p$-value no.
+1) + $f$($p$-value no.
+2))/2) is then displayed against the difference between the $f$($p$-value).
+If no systematic errors and biases exist between the measurement methods, then
+
+\begin{itemize}
+\item the mean of the differences should be around zero (no systematic error) 
+\item the points should scatter independently on the $y$-axis and no general increase or decrease with the mean of the transformed $p$-values should be visible
+\end{itemize}
+
+Although this is not formally tested, there are likely systematic errors and bias between excess significance tests, although more so for continuous tests.
+-- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- \\
+The confidence intervals from Figure \ref{fig:mean.diff.test} can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests.
+This suggests that correspondence between the tests is not very good in general.
+
+\begin{figure}
+<<echo=FALSE, fig.height = 8.5, warning=FALSE>>=
+grid.arrange(egger.thompson.plot, 
+             egger.excess.plot,
+             harbord.rucker.plot, 
+             harbord.excess.plot, ncol = 1)
+@
+\caption{Mean - difference plots for logit transformed $p$-values.
+The mean of logit transformed $p$-values is displayed on the $x$-axis and the difference on the $y$-axis.
+Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).}
+\label{fig:mean.diff.test}
+\end{figure}
+
+The previous results suggest that the results will also differ substantially after applying the common dichotomization of $p$-values.
+We expect that some proportion of the meta-analysis will only be significant for a certain test, and this is indeed observed in Table \ref{number.sig.tests}.
+It displays the percentage of meta-analyses with a certain number of significant test results.
+
+<<echo = FALSE, results='asis'>>=
+print(xtable(number.sig.tests, caption = "Counts Number of significant test results per meta-analysis, separated
+       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
+       applied", label = "number.sig.tests", align = "lccc"), include.rownames = F, size = "footnotesize")
+@
+
+Here, it is difficult to say if continuous and survival or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and survival outcome type tests have in general more positive findings.
+Very few meta-analyses are significant, irrespective of the test used, but around 67\% of the dataset is not significant, no matter which test is used.
 \\
-The so-called hazard ratio estimated by cox p.h.
-regression is the ratio of the instantaneous risk of experiencing the event between two groups.
-Because it is a maximum likelihood estimator, one can again use its Wald test statistic to test for equal hazards.
-Let $\hat{\theta}$ be an estimate of the log hazard ratio and $\hat{s}$ an estimate of the standard error of it.
-As before
-\begin{align}
-p &= 2*(1-\phi(|\hat{\theta}/\hat{s}|) \nonumber
-\end{align}
-will give a $p$-value for the evidence against the null hypothesis.
-
-\section{Fixed and Random Effects Meta-Analysis} \label{sec:meta.analysis}
-The fixed effects meta-analysis estimator of the pooled treatment effect is a mean of the single treatment effect estimators, weighted by their standard errors \citep{fixed.effects.rosenthal}.
-Let $w_i = 1/s_i^2$ be the weights, and $\theta_M$ be the pooled estimator and $s_M^2$ its variance.
-Then
-
-\begin{align}
-\theta_M &= \frac{\sum_{i = 1}^n w_i \theta_i}{\sum_{i = 1}^n w_i} &
-s_M^2 &= \frac{1}{\sum_{i = 1}^n w_i} \label{eq:fixed.effects}
-\end{align}
-
-This estimator minimizes the variance between the effects.
-An estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and variances $\hat{\theta}_i, \hat{s}_i^2$.
-The underlying idea is that we assume $\theta_i \sim N(\theta_M, s_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.
+When only looking at small study effect tests, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of survival and continuous outcome tests had at least one significant result.
+After applying the Bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\% for binary and \Sexpr{mean.min.else.b}\% for continuous and survival outcomes.
 \\
-The random effects model \citep{whitehead} assumes instead that 
-\begin{align}
-\theta_i \sim N(\mu_i, s_i^2) &&
-\mu_i \sim N(\theta_M, \tau^2) \label{eq:random.effects} 
-\end{align}
-
-Marginally, we have $\theta_i$ being distributed around a common mean $\theta_M$ with additional variance $\tau^2$:
-
-\begin{align}
-\theta_i | \mu_i \sim N(\theta_M, s_i^2 + \tau^2) \nonumber %\label{eq:random.effects.marginal}
-\end{align}
-
-$\tau^2$ is often referred to as a population variance or between-study variance, whereas $s_i^2$ can be interpreted as sampling error.
-The pooled treatment effect estimate $\theta_M$ of the random effects model and its variance is obtained by replacing the weights $w_i$ in equation \ref{eq:fixed.effects} with $w_i = 1/(s_i^2 + \tau^2)$.
+% To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test.
+\Sexpr{mean.min.bin2}\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, \Sexpr{mean.min.else2}\% for continuous and survival outcomes.
+The numbers change to \Sexpr{mean.min.bin2.b}\% for binary outcomes and \Sexpr{mean.min.else2.b}\% for continuous and survival outcomes after applying the Bonferroni correction.
 \\
-The model is superior to the fixed effects model whenever the standard errors of the treatment effects alone are unlikely to fully account for the entire variability observed between studies.
-Note that as $\tau^2$ increases, each $\theta_i$ will eventually get equal weights, irrespective of it's sampling error $s_i^2$.\\
-The estimation of $\tau^2$ has been subject to some debate in the statistical literature. Oftentimes, the method of moment estimator of \citet{tau.estimator} is used.
-We use the measure of heterogeneity, $Q$, and divide by $C$ after having subtracted the degrees of freedom $n-1$:
-
-\begin{align}
-Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i}\label{eq:Q.heterogeneity} \\
-\tau^2 &= \max(0, \frac{Q - (n-1)}{C}) \label{eq:Tau.definition}
-\end{align}
-
-Again, $w_i, \theta_i ...$ have to be replaced by their estimates in order to get an estimate $\hat{\tau}^2$. \\
-The Paule-Mandel estimator \citep{paulemandel} is considered to have most often better properties than the method of moments estimator (e.g. \citet{tau.estimator.evaluation}).
-Since we defined $w_i = 1/(s_i^2 + \tau^2)$, it als holds that
-
-\begin{align}
-w_i \textrm{Var}(\theta_i) &= 1 & \textrm{Var}(\sqrt{w_i}\theta_i) = 1 \nonumber
-\end{align}
-
-For any $w_i$, the variance can be estimated and equated to its expected value:
-
-\begin{align}
-s^2(w_i\theta_i) &= \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} & \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} = 1 \label{eq:paulemandel}
-\end{align}
-
-$\theta_M$ can be estimated using equation \ref{eq:fixed.effects}, the only problem is to estimate $\tau^2$. It can be obtained through an iterative process, using a newly defined function
-
-\begin{align}
-F(\tau^2) &= \sum_{i = 1}^n w_i(\theta_i - \theta_M)^2 - (n-1) \nonumber
-\end{align}
-
-In view of equation \ref{eq:paulemandel}, $\tau^2$ must be such that $F(\tau^2) = 0$.
-Then, we start with a arbitrary $\tau^2$ and repeatedly add a term $\tau_0^2$ to update $\tau^2$ until $F(\tau^2 + \tau_0^2)$ is close to zero (using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{\theta}_M$).
-Using a truncated Taylor series expansion, one can obtain the partial derivative after $\tau^2$, which is a reasonable choice for $\tau_0^2$.
+% \Sexpr{both.bin}\% have significant Harbord's test result and significant excess significance test result  (\Sexpr{both.bin.b}\% with Bonferroni).
+Of the continuous outcomes, we have \Sexpr{both.else}\% with Egger's test and \Sexpr{both.else.b}\% with Bonferroni correction.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Small Study Effects Adjustment}
+<<echo=FALSE, warning=FALSE, message=FALSE>>=
+
+#HISTOGRAMS:
+
+#Comparison of treatment effect p-values:
+sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+                              z.ranef = est.z.ranef/se.est.z.ranef,
+                              z.reg = est.z.reg/se.est.z.reg,
+                              z.copas = est.z.copas/se.est.z.copas) %>%  
+  select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>% 
+  mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>% 
+  group_by(method) %>% 
+  summarise(significant = length(which(abs(fisher.z) > 1.96)),
+            p.significant = significant/length(fisher.z))
+sig.zcor <- data.frame(method = sig.zcor$method,
+                       label = paste(round(sig.zcor$p.significant,3)*100, "% significant", ", (n = ", sig.zcor$significant, ")", sep = ""))
+
+method_names <- c(
+  z.fixef = "Fixed Effects",
+  z.ranef = "Random Effects",
+  z.reg = "Regression",
+  z.copas = "Copas"
+)
+
+adjustment.p.z <- meta.f %>% 
+  mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+         z.ranef = est.z.ranef/se.est.z.ranef,
+         z.reg = est.z.reg/se.est.z.reg,
+         z.copas = est.z.copas/se.est.z.copas) %>%  
+  select(z.fixef, z.ranef, z.reg, z.copas) %>% 
+  gather(key = "method", value = "fisher.z") %>% 
+  mutate(method = factor(method, levels = c("z.fixef", "z.ranef", "z.reg", "z.copas"))) %>% 
+  mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>% 
+  ggplot(aes(x = p.fisher.z)) + 
+  geom_histogram(boundary = 0, bins = 20) + 
+  theme_bw() + 
+  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+  geom_text(data = sig.zcor, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
+  xlab(expression(paste(italic(p),"-value of test statistic of the ", italic(z),"-score"))) +
+  ggtitle(expression(paste(italic(z), " Score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Comparison of SMD's:
+sig.d <- meta.f %>% mutate(d.fixef = est.d.fixef/se.est.d.fixef,
+                           d.ranef = est.d.ranef/se.est.d.ranef,
+                           d.reg = est.d.reg/se.est.d.reg,
+                           d.copas = est.d.copas/se.est.d.copas) %>%  
+  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+  group_by(method) %>% 
+  summarise(significant = length(which(abs(smd) > 1.96)),
+            p.significant = significant/length(smd))
+sig.d <- data.frame(method = sig.d$method,
+                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
+
+method_names <- c(
+  d.fixef = "Fixed Effects",
+  d.ranef = "Random Effects",
+  d.reg = "Regression",
+  d.copas = "Copas"
+)
+
+adjustment.p.d <- meta.f %>% 
+  mutate(d.fixef = est.d.fixef/se.est.d.fixef,
+         d.ranef = est.d.ranef/se.est.d.ranef,
+         d.reg = est.d.reg/se.est.d.reg,
+         d.copas = est.d.copas/se.est.d.copas) %>%  
+  select(d.fixef, d.ranef, d.reg, d.copas) %>% 
+  gather(key = "method", value = "smd") %>% 
+  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
+  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+  ggplot(aes(x = p.smd)) + 
+  geom_histogram(boundary = 0, bins = 20) + 
+  theme_bw() + 
+  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+  geom_text(data = sig.d, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
+  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
+  ggtitle(expression(paste("Hedges ", italic(g), " ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Comparison of log hazard ratios:
+sig.d <- meta.f %>% filter(outcome.type == "surv") %>% 
+  mutate(d.fixef = est.fixef/se.est.fixef,
+         d.ranef = est.ranef/se.est.ranef,
+         d.reg = est.reg/se.est.reg,
+         d.copas = est.copas/se.est.copas) %>%  
+  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+  group_by(method) %>% 
+  summarise(significant = length(which(abs(smd) > 1.96)),
+            p.significant = (significant + sum(is.na(smd)))/(length(smd)))
+sig.d <- data.frame(method = sig.d$method,
+                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
+
+method_names <- c(
+  d.fixef = "Fixed Effects",
+  d.ranef = "Random Effects",
+  d.reg = "Regression",
+  d.copas = "Copas"
+)
+
+adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.type == "surv") %>% 
+  mutate(d.fixef = est.fixef/se.est.fixef,
+         d.ranef = est.ranef/se.est.ranef,
+         d.reg = est.reg/se.est.reg,
+         d.copas = est.copas/se.est.copas) %>%  
+  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
+  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+  ggplot(aes(x = p.smd)) + 
+  geom_histogram(boundary = 0, bins = 20) + 
+  theme_bw() + 
+  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+  geom_text(data = sig.d, aes(x = 0.00003, y = 20, label = label), position = "dodge") + 
+  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
+  ggtitle(expression(paste("Log hazard ratio ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Plots separated by effect measure:
+
+sig.level <- 0.1
+meta.f <- meta.f %>% rowwise() %>% 
+  mutate(egger.test = ifelse(pval1.egger < sig.level, 1, 0),
+         thompson.test = ifelse(pval1.thompson < sig.level, 1, 0),
+         begg.test = ifelse(pval1.begg < sig.level, 1, 0),
+
+         schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
+         rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
+         harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
+         peter.test = ifelse(pval1.peter < sig.level, 1, 0),
+         I2 = max(c(0, 1 - (k-1)/Q)),
+         i2f = factor(ifelse(I2 == 0, 1, 0)),
+         se.stat.c = ifelse(outcome.type == "bin", stat.rucker, stat.thompson),
+         se.stat = cut(se.stat.c,
+                       breaks =  c(-7,1, 2, 4.5)))
+
+meta.bin <- meta.f %>% filter(outcome.type == "bin")
+meta.cont <- meta.f %>% filter(outcome.type == "cont")
+meta.surv <- meta.f %>% filter(outcome.type == "surv")
+
+#Meta-Analysis and adjusted treatment effect estimate difference:
+
+#Z-score:
+diff.z.fixef.reg <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(se.stat, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", regression) %>% 
+  mutate(difference = fixef - adjusted.z.score) %>% 
+  filter(difference > -.75 & difference < .75) %>% 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + theme(legend.position = "none") + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) +
+  xlab(expression(paste("Fixed effects - adjusted ", z, "-score"))) + geom_vline(xintercept = 0, linetype = "dashed" )
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.z.fixef.copas <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(se.stat, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", copas) %>% 
+  mutate(difference = fixef - adjusted.z.score) %>% 
+  filter(difference > -.75 & difference < .75) %>% 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + theme(legend.position = "none") + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) +
+  xlab(expression(paste("Fixed effects - adjusted ", z, "-score"))) + geom_vline(xintercept = 0, linetype = "dashed" )
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.z.ranef.reg <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(se.stat, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", regression) %>% 
+  mutate(difference = ranef - adjusted.z.score) %>% 
+  filter(difference > -.75 & difference < .75) %>% 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + theme(legend.position = "none") + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + ylab("") + 
+  xlab(expression(paste("Random effects - adjusted ", z, "-score"))) + geom_vline(xintercept = 0, linetype = "dashed" )
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.z.ranef.copas <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(se.stat, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", copas) %>% 
+  mutate(difference = ranef - adjusted.z.score) %>% 
+  filter(difference > -.75 & difference < .75) %>% 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + theme(legend.position = "none") + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + 
+  xlab(expression(paste("Random effects - adjusted ", z, "-score"))) + geom_vline(xintercept = 0, linetype = "dashed" )
+#--------------------------------------------------------------------------------------------------------------------#
+
+#SMD:
+diff.d.fixef.reg <- meta.f %>% 
+  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
+         copas = est.d.copas, regression = est.d.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(se.stat, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.smd", regression) %>% 
+  mutate(difference = fixef - adjusted.smd) %>% 
+  filter(difference > -1 & difference < 1) %>% 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + theme(legend.position = "none") + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + 
+  xlab(expression(paste("Fixed effects - adjusted Hedges ", g))) + geom_vline(xintercept = 0, linetype = "dashed" )
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.d.fixef.copas <- meta.f %>% 
+  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
+         copas = est.d.copas, regression = est.d.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(se.stat, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.smd", copas) %>% 
+  mutate(difference = fixef - adjusted.smd) %>% 
+  filter(difference > -1 & difference < 1) %>% 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + theme(legend.position = "none") + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + 
+  xlab(expression(paste("Fixed effects - adjusted Hedges ", g))) + geom_vline(xintercept = 0, linetype = "dashed" )
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.d.ranef.reg <- meta.f  %>% 
+  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
+         copas = est.d.copas, regression = est.d.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  gather(key = "method", value = "adjusted.smd", regression) %>% 
+  mutate(difference = ranef - adjusted.smd) %>% 
+  filter(difference > -1 & difference < 1) %>% 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + guides(fill=guide_legend(title="test stat.")) + 
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) +  ylab("") +
+xlab(expression(paste("Random effects - adjusted Hedges ", g))) + geom_vline(xintercept = 0, linetype = "dashed" )
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.d.ranef.copas <- meta.f  %>% 
+  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
+         copas = est.d.copas, regression = est.d.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  gather(key = "method", value = "adjusted.smd", copas) %>% 
+  mutate(difference = ranef - adjusted.smd) %>% 
+  filter(difference > -1 & difference < 1) %>% 
+  ggplot(aes(x = difference, fill = se.stat)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + guides(fill=guide_legend(title="test stat.")) +
+  scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + ylab("") +
+xlab(expression(paste("Random effects - adjusted Hedges ", italic(g)))) + geom_vline(xintercept = 0, linetype = "dashed" )
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Log hazard ratios:
+diff.log.hazard.ratio.fixef <- meta.surv %>% 
+  mutate(fixef = est.fixef, ranef = est.ranef,
+         copas = est.copas, regression = est.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
+  ggplot(aes(x = (fixef - adjusted.log.hazard.ratio))) + 
+  geom_histogram(binwidth = 0.1, center = 0) +
+  facet_wrap(~method) + theme_bw() + xlab("Fixed effects - adjusted log hazard ratio") + geom_vline(xintercept = 0, linetype = "dashed" )
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.log.hazard.ratio.ranef <- meta.surv %>% 
+  mutate(fixef = est.fixef, ranef = est.ranef,
+         copas = est.copas, regression = est.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
+  ggplot(aes(x = (ranef - adjusted.log.hazard.ratio))) + 
+  geom_histogram(binwidth = 0.1, center = 0) +
+  facet_wrap(~method) + theme_bw() + xlab("Random effects - adjusted log hazard ratio") + geom_vline(xintercept = 0, linetype = "dashed" )
+#--------------------------------------------------------------------------------------------------------------------#
+
+sig.level <- 0.1
+meta.f <- meta.f %>% 
+	mutate(egger.test = ifelse(pval1.egger < sig.level, 1, 0),
+				 thompson.test = ifelse(pval1.thompson < sig.level, 1, 0),
+				 begg.test = ifelse(pval1.begg < sig.level, 1, 0),
+
+				 tes.d.test = ifelse(pval1.d.tes < sig.level, 1, 0),
+
+				 schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
+				 rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
+				 harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
+				 peter.test = ifelse(pval1.peter < sig.level, 1, 0))
+
+#Quantile, mean, largerthan and missing table of differences:
+adjustment.diff.keep <- meta.f %>% 
+  mutate(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
+                                 sign(est.copas) != sign(est.fixef) ~ -abs(est.copas)),
+         est.reg.f = case_when(sign(est.reg) == sign(est.fixef) ~  abs(est.reg),
+                               sign(est.reg) != sign(est.fixef) ~ -abs(est.reg)),
+         est.copas.r = case_when(sign(est.copas) == sign(est.ranef) ~  abs(est.copas),
+                                 sign(est.copas) != sign(est.ranef) ~ -abs(est.copas)),
+         est.reg.r = case_when(sign(est.reg) == sign(est.ranef) ~  abs(est.reg),
+                               sign(est.reg) != sign(est.ranef) ~ -abs(est.reg)),
+
+         est.d.copas.f = case_when(sign(est.d.copas) == sign(est.d.fixef) ~  abs(est.d.copas),
+                                   sign(est.d.copas) != sign(est.d.fixef) ~ -abs(est.d.copas)),
+         est.d.reg.f = case_when(sign(est.d.reg) == sign(est.d.fixef) ~  abs(est.d.reg),
+                                 sign(est.d.reg) != sign(est.d.fixef) ~ -abs(est.d.reg)),
+         est.d.copas.r = case_when(sign(est.d.copas) == sign(est.d.ranef) ~  abs(est.d.copas),
+                                   sign(est.d.copas) != sign(est.d.ranef) ~ -abs(est.d.copas)),
+         est.d.reg.r = case_when(sign(est.d.reg) == sign(est.d.ranef) ~  abs(est.d.reg),
+                                 sign(est.d.reg) != sign(est.d.ranef) ~ -abs(est.d.reg)),
+
+         est.z.copas.f = case_when(sign(est.z.copas) == sign(est.z.fixef) ~  abs(est.z.copas),
+                                   sign(est.z.copas) != sign(est.z.fixef) ~ -abs(est.z.copas)),
+         est.z.reg.f = case_when(sign(est.z.reg) == sign(est.z.fixef) ~  abs(est.z.reg),
+                                 sign(est.z.reg) != sign(est.z.fixef) ~ -abs(est.z.reg)),
+         est.z.copas.r = case_when(sign(est.z.copas) == sign(est.z.ranef) ~  abs(est.z.copas),
+                                   sign(est.z.copas) != sign(est.z.ranef) ~ -abs(est.z.copas)),
+         est.z.reg.r = case_when(sign(est.z.reg) == sign(est.z.ranef) ~  abs(est.z.reg),
+                                 sign(est.z.reg) != sign(est.z.ranef) ~ -abs(est.z.reg)),
+
+         est.fixef = abs(est.fixef),
+         est.ranef = abs(est.ranef),
+         est.z.fixef = abs(est.z.fixef),
+         est.z.ranef = abs(est.z.ranef),
+         est.d.fixef = abs(est.d.fixef),
+         est.d.ranef = abs(est.d.ranef))
+
+adjustment.diff.keep <- adjustment.diff.keep %>% 
+  mutate(bias.side = ifelse(est.fixef - est.reg.f > 0, 1, 0), #Decide if effect size declines or increases
+
+         egger.test = ifelse(bias.side == 1, egger.test, 0),
+         thompson.test = ifelse(bias.side == 1, thompson.test, 0),
+         begg.test = ifelse(bias.side == 1, begg.test, 0),
+
+         schwarzer.test = ifelse(bias.side == 1, schwarzer.test, 0),
+         peter.test = ifelse(bias.side == 1, peter.test, 0),
+         rucker.test = ifelse(bias.side == 1, rucker.test, 0),
+         harbord.test = ifelse(bias.side == 1, harbord.test, 0))
+
+adjustment.diff <- adjustment.diff.keep %>%
+
+  transmute(copas.z.f = est.z.fixef - est.z.copas.f,
+            copas.z.r = est.z.ranef - est.z.copas.r,
+            reg.z.f = est.z.fixef - est.z.reg.f,
+            reg.z.r = est.z.ranef - est.z.reg.r,
+
+            copas.d.f = est.d.fixef - est.d.copas.f,
+            copas.d.r = est.d.ranef - est.d.copas.r,
+            reg.d.f = est.d.fixef - est.d.reg.f,
+            reg.d.r = est.d.ranef - est.d.reg.r)
+
+m.adjustment.diff <- as.matrix(adjustment.diff)
+
+adjustmend.diff.surv <- meta.surv %>% 
+  transmute(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
+                                    sign(est.copas) != sign(est.fixef) ~ -abs(est.copas)),
+            est.copas.r = case_when(sign(est.copas) == sign(est.ranef) ~  abs(est.copas),
+                                    sign(est.copas) != sign(est.ranef) ~ -abs(est.copas)),
+
+            est.reg.f = case_when(sign(est.reg) == sign(est.fixef) ~  abs(est.reg),
+                                  sign(est.reg) != sign(est.fixef) ~ -abs(est.reg)),
+            est.reg.r = case_when(sign(est.reg) == sign(est.ranef) ~  abs(est.reg),
+                                  sign(est.reg) != sign(est.ranef) ~ -abs(est.reg)),
+
+            est.fixef = abs(est.fixef),
+            est.ranef = abs(est.ranef)) %>%
+
+  transmute(copas.surv.f = est.fixef - est.copas.f,
+            copas.surv.r = est.ranef - est.copas.r,
+
+            reg.surv.f =  est.fixef - est.reg.f,
+            reg.surv.r = est.ranef - est.reg.r)
+
+m.adjustment.diff.surv <- as.matrix(adjustmend.diff.surv)
+
+adjustment.diff.quantile.table <- apply(m.adjustment.diff, 2, 
+                                        FUN = function(column){quantile(x = column, 
+                                                                        probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T)})
+adjustment.diff.mean <- apply(m.adjustment.diff, 2, FUN = function(column) mean(column, na.rm = T))
+adjustment.diff.largerzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
+adjustment.diff.equalzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
+adjustment.diff.largerequalzero <- (apply(m.adjustment.diff, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff, 2, FUN = function(column) length(column)))*100
+adjustment.diff.comp.errors <- c(4,4,0,0,0,0,0,0)
+adjustment.diff.noest <- c(sum(meta.f$est.z.copas.na[meta.f$outcome.type != "surv"]), 
+                                sum(meta.f$est.z.copas.na[meta.f$outcome.type != "surv"]),
+                                sum(meta.f$est.z.reg.na[meta.f$outcome.type != "surv"]), 
+                                sum(meta.f$est.z.reg.na[meta.f$outcome.type != "surv"]),
+                                sum(meta.f$est.d.copas.na[meta.f$outcome.type != "surv"]), 
+                                sum(meta.f$est.d.copas.na[meta.f$outcome.type != "surv"]),
+                                sum(meta.f$est.d.reg.na[meta.f$outcome.type != "surv"]), 
+                                sum(meta.f$est.d.reg.na[meta.f$outcome.type != "surv"]))
+adjustment.diff.missing <- (adjustment.diff.comp.errors + adjustment.diff.noest)/apply(m.adjustment.diff, 2, FUN = function(column) length(column))*100
+
+adjustment.diff.table <- rbind(adjustment.diff.quantile.table, mean = adjustment.diff.mean,
+                               equalzero = adjustment.diff.equalzero,
+                               largerequal = adjustment.diff.largerequalzero, larger = adjustment.diff.largerzero,
+                               missing = adjustment.diff.missing)
+
+adjustment.diff.quantile.table.surv <- apply(m.adjustment.diff.surv, 2, 
+                                             FUN = function(column){quantile(x = column, 
+                                                                             probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T)})
+adjustment.diff.mean.surv <- apply(m.adjustment.diff.surv, 2, FUN = function(column) mean(column, na.rm = T))
+adjustment.diff.largerzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
+adjustment.diff.equalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
+adjustment.diff.largerequalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
+adjustment.diff.comp.errors.surv <- c(0,0,0,0)
+adjustment.diff.noest.surv <- c(sum(meta.surv$est.copas.na), sum(meta.surv$est.copas.na),
+                                sum(meta.surv$est.reg.na), sum(meta.surv$est.reg.na))
+adjustment.diff.missing.surv <- ((adjustment.diff.comp.errors.surv + adjustment.diff.noest.surv)/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
+
+adjustment.diff.table.surv <- rbind(adjustment.diff.quantile.table.surv, mean = adjustment.diff.mean.surv,
+                                    equalzero = adjustment.diff.equalzero.surv,
+                                    largerequal = adjustment.diff.largerequalzero.surv, larger = adjustment.diff.largerzero.surv,
+                                    missing = adjustment.diff.missing.surv)
+
+adjustment.diff.table <- cbind(adjustment.diff.table, (adjustment.diff.table.surv))
+
+adjustment.diff.table <- round(t(adjustment.diff.table), 4)
+
+rownames(adjustment.diff.table) <- c(paste("z:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
+                                     paste("g:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
+                                     paste("Log h.r.:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")))
+
+colnames(adjustment.diff.table) <- c(colnames(adjustment.diff.table)[1:6], "= 0 (%)", ">= 0 (%)", "> 0 (%)", "No adj. est. (%)")
+
+#--------------------------------------------------------------------------------------------------------------------#
+#Meta-Analysis and adjusted treatment effect estimate difference, missing values:
+
+#Z-score:
+missing.z.fixef <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(meta.id, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
+  mutate(difference = fixef - adjusted.z.score) %>% 
+  filter(difference < -.75 | difference > .75) %>% 
+  select(meta.id)
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+missing.z.ranef <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(meta.id, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
+  mutate(difference = ranef - adjusted.z.score) %>% 
+  filter(difference < -.75 | difference > .75) %>% 
+  select(meta.id)
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+#SMD:
+missing.d.fixef <- meta.f %>% 
+  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
+         copas = est.d.copas, regression = est.d.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
+                           sign(copas) != sign(fixef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
+                                sign(regression) != sign(fixef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(meta.id, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
+  mutate(difference = fixef - adjusted.smd) %>% 
+  filter(difference < -1 | difference > 1) %>% select(meta.id)
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+missing.d.ranef <- meta.f %>% 
+  mutate(fixef = est.d.fixef, ranef = est.d.ranef,
+         copas = est.d.copas, regression = est.d.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(meta.id, fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.smd", copas:regression) %>% 
+  mutate(difference = ranef - adjusted.smd) %>% 
+  filter(difference < -1 | difference > 1) %>% select(meta.id)
+
+missing.differences <- rbind(missing.z.fixef, missing.z.ranef, missing.d.fixef, missing.d.ranef)
+missing.differences <- missing.differences %>% distinct(meta.id)
+
+missing.differences <- merge(meta.f[,
+        c("meta.id", "file.nr", "comparison.nr", "subgroup.nr",
+          "est.z.ranef", "est.z.fixef", "est.z.copas", "est.z.reg", 
+          "est.d.fixef", "est.d.ranef", "est.d.copas", "est.d.reg")],
+        missing.differences, by = "meta.id")
+
+missing.differences <- round(missing.differences, 2)
+
+missing.differences <- missing.differences %>% mutate(meta.id = as.character(meta.id), file.nr = as.character(meta.id),
+                                                      comparison.nr = as.character(comparison.nr), subgroup.nr = as.character(subgroup.nr))
+
+colnames(missing.differences) <- c("meta.id", "file.nr", "comparison.nr", "subgroup.nr",
+                                   "z fixed", "z random", "z Copas", "z regression",
+                                   "g fixed", "g random", "g Copas", "g regression")
+
+#--------------------------------------------------------------------------------------------------------------------#
+#Tukey mean difference plots for adjustment methods:
+
+adjustment.mean.diff.orig <- adjustment.diff.keep %>% filter(est.copas.na != 1) %>% 
+  mutate(mean = (est.copas + est.reg)/2, 
+         difference = est.copas - est.reg) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + theme(legend.position = "none") +
+  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+                     values = c("red", "blue")) +
+  ggtitle(expression(paste("Copas adjusted estimate - Regression adjusted estimate (original)" )))
+
+adjustment.mean.diff.z <- adjustment.diff.keep %>% filter(est.z.copas.na != 1) %>% 
+  mutate(mean = (est.z.copas + est.z.reg)/2, 
+         difference = est.z.copas - est.z.reg) %>% filter(mean < 7) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = 0.5) + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + theme(legend.position = "none") +
+  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+                     values = c("red", "blue")) +
+  ggtitle(expression(paste("Copas adjusted ", italic(z),"-score estimate - Regression adjusted ", italic(z),"-score estimate (original)" )))
+
+adjustment.mean.diff.d <- adjustment.diff.keep %>% filter(est.d.copas.na != 1) %>% 
+  mutate(mean = (est.d.copas + est.d.reg)/2, 
+         difference = est.d.copas - est.d.reg) %>% filter(difference < 7 & mean < 10) %>% 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
+  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  geom_abline(aes(slope = 0,
+                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
+                  col = "red")) +
+  # geom_smooth(method = "loess", se = F) + 
+  theme_bw() + #theme(legend.position = "bottom") +
+  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
+                     values = c("red", "blue")) + guides(fill=guide_legend(title=NULL)) +
+  ggtitle(expression(paste("Copas adjusted Hedges ", italic(g)," estimate - Regression adjusted Hedges ", italic(g), " estimate (original)" )))
+
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Missing study number by copas:
+missing.copas.histogram <- meta.f %>% ggplot(aes(x = missing.copas/k)) + geom_histogram(binwidth = 0.05, boundary = 0) + theme_bw() + xlab("Missing study fraction")
+missing.copas.zeros <- length(which(meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)] == 0))
+missing.copas.range.frac <- c(missing.copas.zeros, quantile(x = meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)], c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)],na.rm = T) )
+missing.copas.range.count <- c(missing.copas.zeros, quantile(x = meta.f$missing.copas[!is.na(meta.f$missing.copas)], c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(na.rm = T,meta.f$missing.copas[!is.na(meta.f$missing.copas)]))
+missing.copas.table <- rbind(missing.copas.range.frac, missing.copas.range.count)
+rownames(missing.copas.table) <- c("Missing fraction", "Missing study number")
+colnames(missing.copas.table) <- c("= 0", colnames(missing.copas.table)[2:6], "mean")
+
+@
+
+\subsection{Change in Effect Size after Adjustment} \label{sec:change.size}
+
+Since there's evidence for publication bias when applying small study effect and excess significance tests, we apply small study effect adjustment methods to take into account that small studies are likely overestimating the treatment effect.
 \\
-%Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{theta}$, we can update $F(\tau^2)$ and check convergence to zero. \\
-The estimation of $\tau^2$ is accompanied by uncertainty.
-A common procedure is to test if it is there is significant heterogeneity between the studies \cite[109]{Intro.meta}.
-Compute $Q$, as given in \ref{eq:Q.heterogeneity}, based on one of the estimators of $\tau^2$.
-It is assumed that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equally distributed effect sizes.
-Thus, the expected value of $Q$ is $n-1$, and the excess dispersion is $Q - n + 1$.
-The $p$-value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
-= $n-1$.
+However, we will see that consequences of adjustment can be; 
+\begin{itemize}
+\item first, the absolute size of the treatment effect can be smaller than the classical meta-analysis treatment effect, which is expected if publication bias
+is the cause for the small study effect.
+\item secondly, the effect can be larger than before in meta-analysis.
+In this case, the small study effect must be not due to publication bias for large effects (``true'' publication bias), but due to bias for small effects (``null effect publication bias'' or even ``reversed effect publication bias'', sometimes refer erred to as ``Proteus phenomenon'' \citep{proteus}).
+\end{itemize}
+
+This is because, in contrast to the small study effect tests, the applied adjustment method does not pre-specify the direction in which bias is expected. \\
+To compare the effects of adjustment between meta-analyses, the outcome measures are transformed to Hedges $g$ (standardized mean differences) and Fisher's $z$-score (see section \ref{sec:transformation.effectsizes} for details).
+The effect of adjustments can be compared to either random or fixed effects meta-analysis estimates.
 \\
-An advantage of the $\tau^2$ is that it is directly linked to the variability in the data.
-Additionally, one can use the $I^2$ statistic to see what portion the between study variance has of the overall variance.
-It is computed as
-
-\begin{align}
-I^2 &= (Q - n + 1)/Q \nonumber%\label{I2.proportion}
-\end{align}
-
-%Large values for $\hat{I}^2$ are of great importance when analyzing e.g. small study effects. \\
-Importantly, all proposed methods above assume normally distributed effect sizes and proper estimates $\hat{s}$ of the true standard error.
-This assumptions are not met for very small sample sizes and very few event counts.
-Alternatively, the mantel-haenszel method for risk and odds ratios (see e.g.
-\citet{mantel.haenszel}) could be used in the latter case.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Small Study Effects Tests}
-The tests that will be presented on the following pages are a common way to detect publication bias.
-Importantly, they are however not interpretable directly as evidence for publication bias, but this is left for the discussion chapter.
-The tests are also often referred to as funnel plot asymmetry tests, because of the popularity of a recent test that has been used frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citet{trimfill}.
-However, it is known for some time that the method has disadvantageous properties, therefore, it will not be discussed here, as well as the funnel plot (the radial plot will be used as an alternative).\\
-A test for small study effects will test in some ways if the size of the estimated treatment effect of a study depends on some measure of its size.
-An association between study size and treatment effect size can be interpreted as an artifact of publication bias.
-
-\subsection{Continuous Outcome Tests}
-For a continuous outcomes that are normally distributed, the sample mean and variance are independent of each other \cite[120]{meta.w.R}.
-Thus, the estimated standard errors of treatment effects can be used as a proxy for study size, as they should in principle not be tied to the effect size.
-
-\subsubsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
-\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
-A standardized effect size $\theta_i^\star$ can be computed as in \ref{begg.stand.eff}.
-$s_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \ref{begg.stand.var}, $\theta_M$ being the fixed effects pooled treatment effect (\ref{eq:fixed.effects}.
-
-\begin{align}
-\theta_i^\star &= (\theta_i - \theta_M)/s_i^{2\star} \label{begg.stand.eff}  \\
-s_i^{2\star} &= s_i^2 - 1/\sum_{i = 1}^n\frac{1}{s_i^2}1 \label{begg.stand.var} 
-\end{align}
-
-A rank correlation test based on Kendall's tau is then used.
-First, the pairs are ordered after their ranks based on $s^{2\star}$.
-Then, for each $s^{2\star}$ rank, the corresponding ranks based on $\theta^{2\star}$ that are larger are counted and summed up to $u$.
-The number of ranks based on $\theta^{2\star}$ that are in contrary, smaller, are counted and summed up to $l$.
-Then the normalized test statistic $Z$ is given as
-
-\begin{align}
-Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \nonumber
-\end{align}
-
-Thus, large number of concordance between pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$.
-The $p$-value is obtained using the standard normal distribution $\Phi$:
-\begin{align}
-p &= 2*(1-\Phi(|Z|)) \nonumber
-\end{align}
-
-The changes that have to be made int the case of ties are small and can be found in \cite[410]{begg.ties}.
-
-\subsubsection{Egger's Test: Weighted Linear Regression Test} \label{sec:Egger}
-First, the concept of simple linear regression is introduced. In short, the model assumes a dependent variable $y$ to be a linear function of another explanatory variable $x$:
-
-\begin{align}
-y &= \beta_0 + \beta_1 x + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:simple.regression}
-\end{align}
-
-$\epsilon$ is the residual noise term that becomes necessary when $n$ pairs $(x_i, y_i)$ are given and there is no exact solution.
-Then it is common to look for the solution that minimizes the squared residuals, the least-squares solution.
-Formally,
-
-\begin{align}
-\operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i) \label{eq:least.squares}
-\end{align}
-
-Let $\mathbf{X}$ be a matrix with the explanatory variables $x$ and $\mathbf{y}$ a corresponding vector for all $y$:
-
-\begin{equation*}
-\mathbf{X} = 
-\begin{bmatrix}
-1 & x_{12} \\
-1 & x_{22} \\
-1 & x_{32} \\
-\vdots & \vdots \\
-1 & x_{n2} \\
-\end{bmatrix} 
-\qquad
-\mathbf{y} = 
-\begin{bmatrix}
-y_1 \\
-y_2 \\
-y_3 \\
-\vdots \\
-y_n \\
-\end{bmatrix}
-\end{equation*}
-
-Let $\mathbf{\beta} = (\beta_0, \beta_1)^\top$. It can be shown that
-
-\begin{align}
-\hat{\mathbf{\beta}} &= (\mathbf{X}^\top \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
-\end{align}
-
-Is an estimator of $\mathbf{\beta}$ that minimizes the squared residuals.
-Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\mathbf{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$.
-The variance estimates $\hat{\sigma}^2$ and $\hat{\mathbf{s}}_\beta^2$ are
-
-\begin{align}
-\hat{\sigma}^2 &= \frac{1}{n-2}\mathbf{r}^\top \hat{\mathbf{r}} & \hat{\mathbf{s}}_\beta^2 &= \hat{\sigma}^2 (\mathbf{X}^\top \mathbf{X})^{-1} \label{eq:regression.variances}
-\end{align}
-
-The estimate $\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the regression line. Furthermore, in the simple linear regression setting, $\hat{\beta}_0$ can also be obtained by:
-
-\begin{align}
-% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} &
-\hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \nonumber
-\end{align}
-
-$\bar{x}, \bar{y}$ denoting the sample means of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$. Thus, $\hat{\beta}_0$ is also called global mean.
-To test whether there is evidence for the intercept $\beta_0$ to be unequal to some value $\beta_{H0}$, a $t$-test can be used.
-
-\begin{align}
-p &= 2(1-F(|(\beta_0 - \beta_{H0})/s_{\beta_0}|)) \nonumber
-\end{align}
-
-where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. $p$ will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
-The concept is extendable to weighted linear regression.
-Weighted linear regression may be used if the residuals $\mathbf{r}$ have unequal variances, which is equivalent to ascribe different precision to the observed $y$.
-The least squares equation \ref{eq:least.squares} is extended to
-
-\begin{align}
-\operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
-\end{align}
-
-with positive weights $w_i$ that penalize large squared residuals for some $i$ more if $w_i$ is larger compared to other $w_i$. \\
-Let $\mathbf{W}$ be a $n \times n$ matrix with $\mathbf{W}_{ii} = w_i$, the weights on the diagonal and zeros on the off-diagonals.
-The estimates in \ref{eq:regression.parameters} and \ref{eq:regression.variances} can still be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$.
-\label{weighted.regression} \\
-Now it is shown how linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citet{Egger}.
-Let $\theta/s$ be the dependent variable $y$ and $1/s$ the explanatory variable $x$.
-If plotted, this corresponds to a radial or Galbraith plot \citet{galbraith}.
-The linear regression equation as introduced before in \ref{eq:simple.regression} can be written in two ways:
-
-\begin{align}
-\theta/s &= \beta_0 + \beta_1/s + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:radial.plot} 
-\end{align}
-
-\ref{eq:radial.plot} is often provided due to the correspondence to the radial plot. However, it is equivalent to
-
-\begin{align}
-\theta &= \beta_0 + \beta_1 s + \epsilon, & \epsilon \sim N(0, w^{-1}\sigma^2) \label{eq:egger.plot}
-\end{align}
-
-with weights $w = 1/s^2$.
-Thus testing $\beta_0$ of \ref{eq:radial.plot} or $\beta_1$ is equivalent.
-The corresponding $p$-value is then used as evidence for a small study effect.
-Plugging in  $\theta_i/s_i, 1/s_i$ as $y_i, x_i$ into equation \ref{eq:regression.parameters} and \ref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{s}_{\beta_0}$ and $\hat{s}_{\beta_1}$.
-
-% \begin{align}
-% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (\varphi_i - \bar{\varphi})(\theta^\star_i - \bar{\theta}^\star)}{\sum_{i = 1}^n (\varphi_i - \bar{\varphi})^2} &
-% \hat{\beta}_0 &= \bar{\theta}^\star - \hat{\beta}_1 \bar{\varphi} \nonumber
-% \end{align}
-
-\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{sec:Thompson}
-A method proposed in \citet{thompson.sharp} allows for between study variance $\tau^2$, as introduced before in section \ref{sec:meta.analysis}.
-It extends the previously seen linear regression approach with $x = 1/s$ and $y = \theta/s$ by introducing weights.
-The effect size $\theta_i$ is assumed to be distributed as
-
-\begin{align}
-\theta_i \sim N(\beta_0 + \beta_1 s_i, s_i^2 + \tau^2) \label{t.sharp.regression}
-\end{align}
-
-$\tau^2$ is estimated as in equation \ref{eq:Tau.definition} (method of moments). %or \ref{eq:paule.mandel}. 
-The weights are set as $w_i = 1/\sqrt{s_i^2 + \tau^2})$.
-After adjusting for the weights as described in \ref{weighted.regression}, we can proceed analogous to Egger's test.
-The $p$-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
-
-\subsection{Dichotomous Outcomes Tests}
-
-The issue with dichotomous outcomes is that effect size and variance of effect size are correlated, which can readily be seen in \ref{eq:risk.ratio} and \ref{eq:risk.ratio.variance}.
-For example, a small number of event counts in one or group will inflate the variance and the effect size.
-Consequently, the tests above will tend to reject the null-hypothesis too often, i.e.
-report false positives.
-A number of solutions to this problem are provided in the literature.
-
-\subsubsection{Peters Test: Weighted Linear Regression Test} \label{sec:Peter}
-Instead of taking the standard error $s$ as explanatory variable $x$ as in Egger's Test, the inverse of the total sample size is used.
-Additionally, the variances $s_i^2$ are used as weights.
-Thus, the subsequent test procedure is identical to Egger's test.
-Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
-
-\subsubsection{Harbord's Test: Score based Test} \label{sec:Harbord}
-A rank based alternative to Peters test for binary outcomes is Harbord's test \citep{Harbord}.
-It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated at log odds ratio $\theta_0 = 0$ and its inverse Fisher information $s^2$. Formally,
-
-\begin{align}
-\varphi &= e_t - (e_t - e_c)(e_t + (n_t - e_t))/(n_t + n_c) \label{harbord.score} \\
-s^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \label{harbord.variance}
-\end{align}
-
-It can be shown that they are both good approximations of the log odds ratio and its variance if the real $\theta$ is not too far from zero.
-The standardized estimator $r_i/v_i$ is also known as Pet0 odds ratio.
-The obtained scores and variances can be used in Egger's test as treatment effects and variances.
-
-\subsubsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
-\citet{Schwarzer} developed a test for the correlation between $E_t - \mathbb{E}(E_t)$ and the variance of $E_t$, $E_t$ being a random variable from the non-central hypergeometric distribution, assuming a fixed log odds ratio.
+Figure \ref{fig:adjustment.reg} displays the difference $\delta$ between the observed meta-analysis pooled treatment effect and the regression adjusted treatment effect, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
+The absolute value $|\hat{\theta}_M|$ is taken and the sign of $\hat{\theta}_\textrm{Adj.}$ is adjusted accordingly such that all effects are mirrored to one side.
+$\delta > 0$ is equivalent to $\hat{\theta}_\textrm{Adj} < \hat{\theta}_M$, a reduction of the original effect size.
+Additionally, the test statistic of heterogeneity adjusted small study effect tests (R\"ucker's and Thompson's test) is displayed with green color.
+Test statitics smaller $< 1$ are equivalent to no evidence for small study effect, test statistics between one and two to weak evidence, and above two they indicate evidence for small study effects.
+Some very large and very small differences have been omitted in the $z$-score and Hedges $g$ histograms; they are shown in Table \ref{missing.differences}.
+
+\begin{figure}
+<<echo=FALSE, fig.height = 5.2, warning=FALSE>>=
+grid.arrange(diff.z.fixef.reg, diff.z.ranef.reg, diff.d.fixef.reg, diff.d.ranef.reg,
+             ncol = 2)
+@
+\caption{Histogram of the treatment effect differences between meta-analysis and regression adjusted meta-analysis.
+Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes.
+The bins are centered at zero and binwidth is equal to 0.1.
+Deeper green color indicates more evidence for small study effects.}
+\label{fig:adjustment.reg}
+\end{figure}
+
+We see that more treatment effect sizes are negatively adjusted and diminished.
+Furthermore, we see that large adjustment is not necessarily connected with evidence for small study effects, but there is of course strong coincidence.
+The cases with no evidence and large adjustment indicate that between-study heterogeneity was not resolved by adjustment for small study effects.
+Adjustment was larger when random effects meta-analysis effect is used as reference, because there larger weights are given to small studies.\\
+Figure \ref{fig:adjustment.copas} shows the same for effect sizes adjusted by Copas; Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
+Therefore, the effect of adjustment by Copas can be seen when comparing adjusted with random effects estimates.
+Again, we clearly see that more effect sizes are adjusted downwards.
+Additionally, there is more coincidence with the small study effect test statistics and adjustment, which is as expected.
 \\
-$\mathbb{E}(E_t)$ and variance of $E_t$ are then estimated based on $e_t$. The standardized cell count deviation 
-\begin{align}
-(e_t - \mathbb{E}(E_t))/\sqrt(s_i^2)
-\end{align}
-and the inverse of $s_i^2$ is then used as before in Begg and Mazumdar's test.
-
-\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables} \label{sec:Rucker}
-The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables.
-We use that the arcsine function is the variance stabilizing transformation for a proportion.
-Let
-
-\begin{align}
-\theta_i = \arcsin{e_t/n_t} - \arcsin{e_c/n_c} \nonumber &
-s_i^2 = 1/4n_t + +/4n_c \nonumber
-\end{align}
-
-Then one can optionally apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained estimates.
-
-\section{Excess Significance Test}
-\citet{excess.significance} developped an exploratory test to detect if the proportion of significant findings is larger than expected.
-Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study.
+
+\begin{figure}
+<<echo=FALSE, fig.height = 4, warning=FALSE>>=
+grid.arrange(diff.z.ranef.copas, diff.d.ranef.copas, ncol = 2)
+@
+\caption{Histogram of the treatment effect differences between meta-analysis and Copas adjusted meta-analysis.
+Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes.
+The bins are centered at zero and binwidth is equal to 0.1.
+Deeper green color indicates more evidence for small study effects.}
+\label{fig:adjustment.copas}
+\end{figure}
+
+Table \ref{adjustment.difference} shows the quantiles and means for the various differences and additional information.
+When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
+The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} increased by -0.13, fixed effects reference).
+Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or \Sexpr{floor(length(!is.na(meta.f$est.d.reg))*0.05)} meta-analyses (or increased by 0.24).
+
+<<echo=FALSE, results='asis'>>=
+print(xtable(adjustment.diff.table, label = "adjustment.difference", caption = "Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects.
+The column with the names ``> 0'' give the percentages of estimates larger than zero or larger or equal zero.
+The column ``No adj.
+est.'' gives the percentage of missing estimates due to non-significant publication bias test (for Copas) and computational errors.
+The row names indicate which outcome measure, meta-analysis method and adjustment method is used.
+Abbreviations are used for z-score (= z) and Hedges g (= g).", align = "lcccccccccr"), include.rownames = T, size = "scriptsize",# sanitize.text.function=function(x){x},
+      # table.placement = "p"
+      )
+@
+
+\subsection{Change in Evidence for Treatment Effects} \label{sec:change.evidence}
+Adjustment for small study effects in meta-analysis will not only provide new effect sizes, but also standard errors thereof.
+Thus, also the evidence for efficacy of a treatment can be obtained, which is usually summarized in a suitable test statistic or $p$-value.
+It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.\\
+The Wald test statistics $p$-value for fixed and random effects meta-analyses and Copas and regression adjusted treatment effects have been calculated.
+They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and log hazard ratios.
 \\
-We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated as for example by fixed effects Meta-Analysis \ref{eq:fixed.effects}.
-Let $O$ be the number of significant study results out of $n$ studies and $\alpha$ the significance threshold.
-Corresponding to the study effect $\theta_i$, we can specify the power $1 - \beta_i$, the probability to accepting a true result.
-Let $z_{\alpha,i}$ be the $1-\alpha$ quantile of a normal distribution with standard error $\hat{s}_i$.
-The power of study $i$ can be estimated as:
-
-\begin{align}
-1 - \hat{\beta}_i &= F(z_\alpha) 
-\end{align}
-
-with $F$ being the cumulative distribution of a normal with mean $\hat{\theta}_M$ and standard deviation $\hat{s}_i$. \\
-If we assume no bias in $\theta_i, \theta_M$, the expected number of significant study results is then just
-
-\begin{align}
-E &= \sum_{i = 1}^n (1 - \beta_i) \nonumber
-\end{align}
-
-$E$ can then be compared to $O$ by constructing a test statistic $\chi$:
-
-\begin{align}
-\chi  &= \big( \frac{(O - E)^2}{E} + \frac{(O - E)^2}{n - E}\big) \nonumber
-\end{align}
-
-and consecutively, calculating a $p$-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
-Alternatively, one can also use a binomial proportion test, which tests if the probability of significance is the same as expected.
-A simple Wald test statistic $Z$ is given by:
-
-\begin{align}
-Z = \frac{O/n - E/n}{\sqrt{(O/n(1-O/n))/n}}
-\end{align}
-
-The one sided $p$-value for the alternative hypothesis $O/n > E/n$ is
-
-\begin{align}
-p &= 1 - \Phi(Z) \nonumber
-\end{align}
-
-with $\Phi$ being the cumulative distribution function of a standard normal. \citet{excess.significance} propose it to be more suitable if $n$ is small.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Small Study Effect and Publication Bias Adjustment}
-There are different approaches to correct for small study effects and publication bias.
-They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinite precision (i.e.
-very small standard error) or to a summary effect, corrected for publication bias.
-Selection models aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:
-
-\subsection{Adjustment by Regression}
-\citet{limitmeta} use a random effects model %together with shrinkage procedure 
-to obtain an unbiased estimate. Similarly to 
-%what has been seen in Copas selection model, we let $y_i$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_i}$ as in \ref{limitmeta.regression}.
-regression based tests for small study effects, we have
-
-\begin{align}
-\theta_i & = \beta_0 + \beta_1\sqrt{s_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \epsilon_i \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{eq:limitmeta.regression}
-\end{align}
-
-The only difference between Thompson and Sharp's variant is $x = \sqrt{s^2 + \tau^2}$ instead of $x = \sqrt{s^2}$.
-$\beta_{1}$ represents the bias introduced by small study effects, as illustrated in the following equations:
-
-\begin{align}
-\mathbb{E}((\theta_i - \beta_0)/\sqrt{s_i^2}) \rightarrow \beta_1 \textrm{ if } s_i \rightarrow \infty \nonumber \\ %\label{limitmeta.infinitesample} \\
-\mathbb{E}(theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} s_i \rightarrow 0 \nonumber
-\end{align}
-
-After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before in the simple linear regression framework. Now we have basically two possible estimates at hand:
-\begin{itemize}
-\item $\beta_0$ the treatment effect without any influence of study precision with standard error $s_{\beta_0}$
-\item $\beta_0 + \beta_1 \tau$ the treatment effect of a hypothetical study with infinite precision, corresponding standard error $s_{\beta_0} + s_{\beta_1}$
-\end{itemize}
-
-Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior with respect to coverage (and mean squared error).
-
-\subsection{Copas Selection Model}
-
-A method proposed in \cite{Copas1,Copas2,Copas3} 
-assumes that the given sample of treatment effects and standard errors is a selected part of a larger random sample.
-Selection of studies depends on their effect size and variance.
-Smaller variance is always accompanied by larger selection probability.
+It can be seen that evidence for a treatment effect decreases after adjusting for publication bias.
+It does so more for Hedge's $g$ compared to $z$-scores, and for regression adjustment compared to Copas selection model.
+%Also, the evidence decreases for random effects meta-analyses compared to fixed effects meta-analyses. 
+In the case of log-hazard ratio adjustment, the adjustment has only negligible impact on the $p$-values. \\
+Also, Copas selection method has a very small impact on the evidence compared to random effects meta-analysis, at least using $z$-scores (again, we should rely on comparisons to random effects meta-analysis to evaluate Copas method).
 \\
-Let $\theta_i$ be the effect size estimate of study $i$. Then
-
-\begin{align}
-\theta_i \sim N(\mu_i, \sigma_i^2) &
-\mu_i \sim N(\theta, \tau^2) \label{eq:population.model}
-\end{align}
-
-which is similar to the random-effects meta-analysis setting.
-$\theta$ is the population mean effect, $\sigma_i^2$ the within study variance and $\tau^2$ the between study variance.
-Equations in \ref{eq:population.model} are termed the \textit{population model}.
+% Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
+%Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted Hedges $g$ and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.
+
+\begin{figure}
+<<echo=FALSE, fig.height = 9, warning=FALSE>>=
+grid.arrange(adjustment.p.z,
+             adjustment.p.d,
+             adjustment.p.log.hazard.ratio, ncol = 1)
+@
+\caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
+The method is indicated in the header, bin width is set to 0.05.
+The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
+\label{fig:adjustment.stat}
+\end{figure}
+
+The Copas selection model also gives an estimate of the number of missing studies.
+It finds that \Sexpr{round(sum(meta.f$missing.Copas, na.rm = T))} are missing, which corresponds to \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% from all \Sexpr{round(sum(meta.f$k))} analysed studies.
+Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
+Note that we have excluded \Sexpr{sum(is.na(meta.f$missing.Copas))} out of \Sexpr{dim(meta.f)[1]}, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
+
+\begin{figure}
+<<echo = FALSE, warning = FALSE>>=
+missing.copas.histogram
+@
+\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ \Sexpr{sum(!is.na(meta.f$missing.Copas))})}
+\label{fig:copas.missing}
+\end{figure}
+
+We can see that in some occasions, the method finds more than half of all studies are missing.
+In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
+The discrepancy between mean and median may indicate that the estimate of \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% missing studies depends somewhat on these extreme cases.
+As can be written of from Table \ref{copas.missing}, 5\%, \ie \Sexpr{round(sum(!is.na(meta.f$missing.Copas))*0.05)} meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for \Sexpr{sum(meta.f$missing.Copas[which(meta.f$missing.Copas >= 17.60)], na.rm = T)}, more than 30\% of missing studies.
+
+<<echo= FALSE, results='asis'>>=
+print(xtable(missing.copas.table, caption = "Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.",
+             label = "copas.missing", align = "lrrrrrrr", digits = c(0,0,0,0,1,1,1,1)),
+      size = "footnotesize")
+@
+
+<<echo=FALSE, results='asis'>>=
+print(xtable(missing.differences, 
+             caption = "Missing meta-analysis pooled treatment effect and adjusted treatment effects.
+Abbreviations are used for z-score (= z) and Hedges g (= g).", label = "missing.differences", align = "llcccrrrrrrrr"),
+      include.rownames = F, size = "tiny")
+@
+
+\subsection{Comparison of adjustment methods}
+Regression adjusted estimates are compared to the estimates of Copas selection model if these are not equal to random effects meta-analysis.
+A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
+We will compare estimates based on all three outcome measures, i.e.
+original measure, $z$-score and Hedges $g$ in Figure \ref{fig:adjustment.mean.diff}.
+Note that the 39 survival outcome data is not included when using $z$-score and Hedges $g$.
+
+\begin{figure}
+<<echo = FALSE, fig.height = 7.5>>=
+grid.arrange(adjustment.mean.diff.orig,
+             adjustment.mean.diff.z,
+             adjustment.mean.diff.d, ncol = 1)
+@
+\caption{Mean - difference plots for publication bias adjustment methods.
+The mean of the adjusted treatment effects is displayed on the $x$-axis and the difference on the $y$-axis.
+Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).
+Two values have been omitted in the middle plot for Hedges $g$ and one for $z$-score (see Table \ref{missing.differences}).}
+\label{fig:adjustment.mean.diff}
+\end{figure}
+
+No formal tests are provided, but the at least there seems to be no clear bias or systematic error.
+The limits of agreement in Figure \ref{fig:adjustment.mean.diff} are large.
+We conclude thus that the impact of regression adjustment on the effect sizes is in general not substantially larger than the impact of Copas selection model in the subset of data where the estimate of the Copas selection model is not equal to a random effects estimate.
+There is however a small difference, with regression estimates to have a little bit a larger absolute value.
+There might be some bias between adjusted $z$-scores, where regression estimates seem to be somewhat smaller when the mean is a little above zero, and somewhat larger when the mean is a little below zero.
 \\
-The \textit{selection model} is defined as follows.
-Suppose a selection of studies with reported ($\neq$ estimated) standard errors $s$ (likely different from $\sigma$).
-Only a proportion of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
-Formally,
-
-\begin{align}
-P(\textrm{select}|s) &= \Phi(a + b/s) \nonumber %\label{copas.selection1}
-\end{align}
-
-The equation can be rewritten as
-
-\begin{align}
-z = a + b/s + \delta \nonumber %\label{copas.selection2}
-\end{align}
-
-with $\delta \sim N(0,1)$.
-$z$ is interpreted as the \textit{propensity for selection}.
-It's sign must be positive in order for the study to be selected.
-Thus, the larger $z$, the more likely the study will be selected.
-Also, $a$ is somewhat like to global retention or selection rate for each study, while $b$ decides about the decline of selection probability with increasing $s$.\\
-So far, we have, for a study $i$
-
-\begin{align}
-\theta_i = \mu_i + \sigma_i\epsilon_i \nonumber \\ 
-\mu_i \sim N(\theta, \tau^2) \nonumber \\
-z_i = a + b/s_i + \delta_i \nonumber
-\end{align}
-
-where $(\epsilon_i, \delta_i)$ are standard normal residuals.
-The two models are coupled by introducing a correlation $\rho = cor(\theta_i, z_i)$ by defining $(\epsilon_i, \delta_i)$ as bivariate standard normals.
-It follows that,
-%Every given study $i$ in the meta-analysis has $z_i > 0$. 
-if $\rho_i$ is large and positive and $z_i > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_i$ and $\delta_i$ and thus, the true mean $\mu$ is likely to be overestimated.
-\\
-Let $u_i = a + b/s_i$, $\lambda(u_i)$ the Mill's ratio $\phi(u_i)/\Phi(u_i)$ ($\phi$ is the standard normal density function and $\Phi$ the cdf) and $\tilde{\rho_i} = \sigma/\sqrt(\tau^2 + \sigma_i^2) \rho_i$.
-The probability of a study being selected, given $s_i$ and $\theta_i$, is
-
-\begin{align}
-P(\textrm{select}|s_i, \theta_i) = %P(a,b,s,y) = 
-\Phi(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i^2}}}) \nonumber
-\end{align}
-
-Which again shows that larger $s_i$ and $\theta_i$ lead to a larger selection probability. It can also be shown that the expected value
-
-\begin{align}
-\mathbb{E}(\theta_i|s_i, \textrm{select}) = \mu + \rho_i\sigma_i\lambda(u_i) \label{eq:copas.expectation}
-\end{align}
-
-which shows that the expected value for a study is larger for larger $\sigma$. \\
-A likelihood for $\theta_i$, conditional on $z>0$ can be formulated to estimate the parameters of the model.
-Regarding $a$ and $b$, there is no way that they can be estimated because the number of missing studies and their effect sizes is not known.
-Instead, fixed values for $a$ and $b$ have to be chosen.
-The nuisance parameter $\sigma_i$ can be replaced by an estimate if the sample size in the studies is large enough. Since
-
-\begin{align}
-\textrm{Var}(\theta_i| s_i, z_i > 0) = \sigma_i^2 (1 - c_i^2\rho_i^2) \nonumber
-\end{align}
-
-with $c^2 = \lambda(u_i)(u_i + \lambda(u_i))$, we can replace $\sigma_i^2$ by $\hat{\sigma}_i^2 = \frac{1}{1-c_i^2\rho_i^2}$.
-Although one has to evaluate the likelihood for fixed pairs $(a,b)$, one can compare the fit of the model to evaluate which one is more suitable:
-With equation \ref{eq:copas.expectation}, one can obtain fitted values of $\theta_i$ based on $s_i$. Also, for two different pairs $(a,b)$, $(a^\star, b^\star)$,
-
-\begin{align}
-\mathbb{E}(\theta_i|z_i > 0, a^\star, b^\star) - \mathbb{E}(\theta_i|z_i > 0, a, b) \approx c^\star + \rho(\lambda(a^\star) - \lambda(a))s_i \nonumber
-\end{align}
-
-and that local departures of $\theta_i$ can be approximated by adding a linear term in $s_i$ to the expectation of $\theta_i$. Thus, to test a pair $(a,b)$, it is sufficient to test $\beta \neq 0$ in
-
-\begin{align}
-\theta_i &= \theta + \beta s_i + \sigma_i \epsilon_i \nonumber
-\end{align}
-
-with restriction that $\rho \geq 0$.
-To test some pair $(a,b)$ against the scenario with no selection, we set $a^\star = \infty$ (or $\rho = 0$).
-A likelihood ratio test will give a test statistic to test against $H0 =$ no selection:
-
-\begin{align}
-\chi^2 &= 2*(\operatorname*{max1}_{\theta, \tau, \beta}\tilde{L}(\theta, \tau, \beta) - \operatorname*{max}_{\theta, \tau}\tilde{L}(\theta, \tau, 0)) \label{eq:copas.small.study}
-\end{align}
-
-with 
-\begin{align}
-\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta s_i)^2}{(\tau^2 + \sigma_i^2)}] \nonumber
-\end{align}
-
-$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$-value.
-Note that the test is almost equivalent to Egger's small study effect test with $\tau^2 = 0$.
-Thus, although the copas selection model models publication bias, it is dependent on the small study effects to find the most suitable pair $(a,b)$.
-\\
-If one applies the model to a single meta-analysis, a sensitivity analysis is suggested.
-One can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process.
-Selection models are in general not recommended for inference (e.g.
-\citet{selection.assessment}).
-\citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes. \\
-A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \ref{eq:copas.small.study} is applied.
-If all obtained $p$-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for modelling, and the standard, classical random effects meta-analysis is retained.
-If none of the $p$-values is above the threshold, a wider range of values for $(a,b)$ is used.
-When some $p$-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the least intense underlying selection model is chosen).\\
-Currently, there is no test to detect miss-specifications in the model itself, the authors themselves have argued that a non-parametric test of the residuals would lack power.
-
-\section{Transformation between effect sizes} \label{sec:transformation.effectsizes}
-Assuming that binary outcomes result from a dichotomization of originally continuous random variables, in this case, the logistic distribution, a transformation from typical binary effect measures to Cohen's $d$ can be achieved \cite[47]{Intro.meta}.
-\\
-Let $\theta$ be a log odds ratio and $s$ its standard error. Cohen's $d$ and it's variance $s_d^2$ is obtained by
-
-\begin{align}
-d &= \theta \frac{\sqrt{3}}{\pi} & s_d^2 = s^2 \frac{\sqrt{3}}{\pi} \nonumber
-\end{align}
-
-$\frac{\pi}{\sqrt{3}} = 1.81$ is the standard deviation of the logistic distribution $L(\mu, \eta)$ with scale parameter $\eta = 1$, so we just divide the log odds ratio and it's variance through the standard deviation.
-The approximation works only well if $e_t$ and $e_c$ are not very small, especially in the case of $s_d^2$.
-Plugging in the observed log odds ratio $\hat{\theta}$ and $\hat{s}^2$ will give an estimate of Cohen's $d$.\\
-Pearson's correlation can be attained by the formulas (\citet{olkin1985dtor}, \cite[48]{Intro.meta})
-
-\begin{align}
-r &= \frac{d}{\sqrt{d^2 + a}} & a = (n_c + n_t)^2 / n_c n_t \nonumber
-\end{align}
-where $a$ is a correction factor if $n_t \neq n_c$. The variance of $r$, $s_r^2$ is computed by
-\begin{align}
-s_r^2 &= \frac{a^2 s_d^2}{(d^2 + a)^3} \nonumber
-\end{align}
-
-Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $s_z^2$ by using
-\begin{align}
-z &= 0.5 \ln(\frac{1 + r}{1 - r}) & \nonumber
-s_z^2 &= \frac{1}{n-3}
-\end{align}
-
-%SIMPLE LINEAR REGRESSION
-% \begin{align}
-% \hat{\mathbf{\beta}} &= (\mathbf{X}^\top  \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
-% \end{align}
-
-% There is a closed form solution for $\hat{\beta_0}, \hat{\beta}_1$ that minimize the sum of squares:
-% 
-% \begin{align}
-% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} & 
-% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
-% \end{align}
-% 
-% $\bar{x}, \bar{y}$ denotes the sample mean of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$.
-$\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the fitted line.
-Let $\hat{y}_i = \beta_0 + \beta_1 x_i$ and $e_i = y_i - \hat{y}_i$.
-The variances $s^2_\beta$
-% 
-% 
-% 
-% To test whether the intercept or the slope is close to a certain value, a $t$-test can be used. Simply taking the absolute value of $\beta_0/s_\beta_0$,
-% \begin{align}
-% p &= 2(1-F(|\beta_0/s_\beta_0|)) \nonumber
-% \end{align}
-% 
-% where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom.
-The $p$-value will give the evidence against the null-hypothesis $\beta_0 = 0$.
-The procedure for $\beta_1$ is equivalent.
-\\
-% To extend the model to weighted simple linear regression is straightforward.
-Let $w_i$ be the corresponding weight that will be attributed to the pair $x_i, y_i$.
-The least squares minimization problem can be restated
-% 
-% \begin{align}
-% \operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
-% \end{align}
-% 
-% And the corresponding estimators are thus
-% 
-% \begin{align}
-% \hat{\beta_1} &= \frac{\sum_{i = 1}^n w_i(x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n w_i(x_i - \bar{x})^2} & 
-% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
-% \end{align}
-%
-
-% LIMITMETa
-% \vspace{0mm}
-% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
-% 
-% \begin{align}
-% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
-% \end{align}
-% 
-% Letting $M \rightarrow \infty$, we obtain:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
-% \end{align}
-% 
-% Note that:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
-% \end{align}
-% 
-% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
-% 
-% \begin{align}
-% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
-% \end{align}
-% 
-% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-% \end{align}
-% 
-% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
-
-% \section{Basic notation}
-% The notation used here will be used throughout the chapter and exceptions will be noted.
-Let $i$ be the number of a study of a meta analysis with $n$ being the total number of studies.
-$y_{i}$ is then the effect size estimate (usually log odds ratio or mean difference) and $v_{i}$ the variance of the estimate of study $i$.
-$w_{i}$ is used for weights which are defined when necessary, and $\Delta$ usually denotes the summarized or pooled effect estimate of the meta-analysis, and $\eta$ the variance thereof.
-% 
-% \vspace{0mm}
-% In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
-% 
-% 
-% \section{Transformation between effect sizes}
-% Binary and continuous outcome measures can both be transformed into correlations and fishers z-scaled correlations in order to be compared.
-Let $\theta$ be a log odds ratio.
-A standardized mean difference $d$ (also known as Cohen's $d$) is calculated by multiplying $\theta$ with $\sqrt{3}/\pi$.
-The variance of the standardized mean difference is attained as $v_d = v_\theta \sqrt{3}/\pi$.\\
-% We get from a standardized mean difference $d$ to a correlation $r$ by using 
-% \begin{align}
-% r &= \frac{d}{\sqrt{d^2 + a}} \nonumber
-% \end{align}
-% where $a$ is a correction factor if $n_t \neq n_c, a = (n_c + n_t)^2 / n_c n_t$. The variance of $r$ is computed by using 
-% \begin{align}
-% v_r &= v_d
-% \end{align}
-% 
-% Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $v_z$ by using
-% \begin{align}
-% z &= 0.5 \ln(\frac{1 + r}{1 - r}) \nonumber
-% v_z &= \frac{1}{n-3}
-% \end{align}
-% 
-% 
-% 
-% \section{Heterogeneity}
-% In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
-This is called between study variation in contrast to within study variation (noise).
-% 
-% 
-% \vspace{0mm}
-% The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
-Let $w_i$ be the inverse of the variance and $\Delta$ be a summarized effect estimate of your choice as for example a variance-weighted mean \ref{weighted.mean}.
-Then $Q$ can be calculated as in \ref{Q.heterogeneity}
-% 
-% \begin{align}
-% \Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-% Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
-% \end{align}
-% 
-% Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
-Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
-$1 - F(Q)$ will provide the $p$-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
-% 
-% \vspace{0mm}
-% Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
-For this purpose, $\tau^2$, the variance of true effects, can be calculated.
-$\tau^2$ is on the same scale as the effect size and reflects the absolute amount of dispersion.
-In practice, $\tau^2$ can be smaller than zero, then it is set to zero.
-% 
-% \begin{align}
-% C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
-% \tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
-% \end{align}
-% 
-% The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
-Note that their estimate can differ substantially and consequently also the estimate of the pooled effect size estimate.
-% 
-% \vspace{0mm}
-% To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
-% 
-% \begin{align}
-% I^2 &= (Q - n + 1)/Q \label{I2.proportion}
-% \end{align}
-% 
-% There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
-% 
-% \section{Meta Analysis}
-% There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
-% First the fixed effect meta-analysis will be explained.
-Note that both methods can be used for continuous or dichotomous outcomes.
-For more details about the methods, see chapter 11 and 12 in \citet{metaanalysis}
-% 
-% 
-% \vspace{0mm}
-% Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
-The pooled estimate $\Delta_{f}$ of the fixed effects model is then the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
-The variance $\eta_{f}$ is the reciprocal of the sum of the weights as shown in \ref{reciproce.variance}.
-% 
-% \begin{align}
-% \Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-% \eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
-% \end{align}
-% 
-% The computation of random effects meta-analysis is more complicated.
-Random effects meta-analysis will give smaller studies with larger variance more weight in the pooled estimate.
-Shortly, the idea is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
-% 
-% \vspace{0mm}
-% The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
-It is used to calculate a new weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
-The variance of $\Delta_{r}$, $\eta_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
-% 
-% \begin{align}
-% v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
-% \Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
-% \eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
-% \end{align}
-% 
-% A $p$-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
-% 
-% \begin{align}
-% Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
-% p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
-% \end{align}
-% 
-% \section{Small Study Effects Tests}
-% One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
-If this is not given, one often speaks of publication bias.
-In fact, there can also be other reasons for this (see discussion section).
-A more appropriate term for the phenomenon is small study effect.
-If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
-% 
-% \subsection{Continuous Outcome Tests}
-% % Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. 
-% % First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
-% 
-% \subsubsection{Begg and Mazumdar: Rank Correlation Test}
-% \citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
-% A standardized effect size $y_{i}^\star$ can be computed as in \ref{begg.stand.eff}.
-$v_{i}^\star$ is the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
-$\Delta_{f}$ is the pooled estimate for fixed effect estimate defined in \ref{weighted.mean}.
-% 
-% \begin{align}
-% y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff} \\
-% v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} 
-% \end{align}
-% 
-% A rank correlation test based on Kendall's tau is then used.
-The pairs $(y_{i}^\star, v_{i}^\star)$ that are ranked in the same order are enumerated.
-Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (e.g.
-larger standardized effect size and smaller variance).
-Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
-% 
-% \begin{align}
-% Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
-% \end{align}
-% 
-% The changes in the case of ties are negligible \cite[410]{begg.ties}.
-% 
-% \subsubsection{Egger's Test: Linear Regression Test}
-% Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
-% Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope. 
-% 
-% \vspace{0mm}
-% If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
-The $p$-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
-% 
-% \begin{align}
-% p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
-% \end{align}
-% 
-% \subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{Thompson}
-% A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
-Let $\tau^2$ be equal to \ref{Tau.definition}.
-The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
-% 
-% \begin{align}
-% y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
-% \end{align}
-% 
-% Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
-Analogous to Egger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta_{0} = 0$.
-% 
-% \subsection{Dichotomous Outcomes Tests}
-% 
-% The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
-Consequently, the tests above will tend to reject the null-hypothesis too often, i.e.
-that they are not conservative enough.
-A number of solutions to this problem are existing in the literature.
-% 
-% 
-% \subsubsection{Peters Test: Weighted Linear Regression Test}
-% A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
-% 
-% \vspace{0mm}
-% Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
-% 
-% \begin{align}
-% y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
-% v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
-% \end{align}
-% 
-% and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
-Instead of taking the variance as explanatory or independent variable in regression as in Egger's Test, the inverse of the total sample size $x_{i}$ is used, and the variance $v_{i}$ is used as a weight.
-The subsequent test procedure is then identical to Egger's test.
-% 
-% \vspace{0mm}
-% Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
-% 
-% 
-% \subsubsection{Harbord's Test: Score based Test}
-% A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
-The score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
-% 
-% \begin{align}
-% r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
-% v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
-% \end{align}
-% 
-% Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
-Note that $r_{i}/v_{i}$ is also known as peto odds ratio.
-% 
-% \subsubsection{Schwarzer's Test: Rank Correlation Test}
-% \citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
-$\mathbb{E}(E_{t})$ and variance of $E_{t}$ are then estimated based on $e_{t}$.
-% 
-% \vspace{0mm}
-% The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
-% 
-% \subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
-% The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let 
-% 
-% \begin{align}
-% y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}} \\
-% v_{i} = 1/4n_{t} + +/4n_{c}
-% \end{align}
-% 
-% Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances. 
-% 
-% 
-% \section{Small Study Effect Adjustment}
-% \subsection{Trim and Fill}
-% One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
-It is a nonparametric test based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
-% %If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
-% 
-% \vspace{0mm}
-% The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
-First, $\Delta$ is estimated using a fixed or random effects model.
-Then, the $k$ effect size estimates with the smallest standard errors are trimmed, and $\Delta$ is estimated again.
-The procedure is repeated until $k$ is 0 and the funnel plot is symmetric.
-The total number of missing studies is then mirrored with respect to the final effect size estimate $\Delta$, and $\Delta$ and its standard error is then computed to obtain an unbiased estimate.
-% 
-% \subsection{Copas Selection Model}
-% 
-% A method proposed in \cite{Copas1,Copas2,Copas3} assumes that there is a population of studies of which only a part has been published dependent on the variance and size of their estimated effects.
-Studies with small variance and large effect sizes are more likely to be published than studies with large variance and small effect sizes.
-Note that small effect size means here a treatment effect close to the control effect.
-% 
-% Let $y_i$ be the effect size estimate of study $i$. Then 
-% 
-% \begin{align}
-% y_{i} \sim N(\mu_{i}, \sigma_{i}^2) \\
-% \mu_{i} \sim N(\mu, \tau^2)
-% \end{align}
-% 
-% corresponding to a standard random effects meta-analysis.
-$\mu$ is the overall mean effect, $\sigma_{i}^2$ the within study variance and $\tau^2$ the between study variance.
-This is the \textit{population model}.
-% 
-% \vspace{0mm}
-% The \textit{selection model} is defined as follows. Suppose a selection of studies with reported standard errors $s$ (likely different from $\sigma$). Only a proportion 
-% 
-% \begin{align}
-% P(\textrm{select}|s) &= \Phi(a + b/s) \label{copas.selection1}
-% \end{align}
-% 
-% of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
-\ref{copas.selection1} can be rewritten as
-% 
-% \begin{align}
-% z = a + b/s + \delta \label{copas.selection2}
-% \end{align}
-% 
-% with $\delta \sim N(0,1)$. The study with standard error $s$ is only selected if $z$ is positive. Therefore, the larger $z$, the more likely the study is selected.
-% Combining population and selection model for study $i$, we have 
-% 
-% \begin{align}
-% y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \\
-% \mu_{i} \sim N(\mu, \tau^2) \\
-% z_{i} = a + b/s_{i} + \delta_{i}
-% \end{align}
-% 
-% where $(\epsilon_{i}, \delta_{i})$ are standard normal residuals and jointly normal with correlation $\rho = cor(y_{i}, z_{i})$.
-Every given study $i$ in the meta-analysis has $z_{i} > 0$.
-If $\rho$ is large and positive and $z_{i} > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_{i}$ and $\delta_{i}$.
-Thus, the true mean $\mu$ is likely to be overestimated.
-% 
-% \vspace{0mm}
-% Let $u = a + b/s$, $\lambda(u) = \phi(u)/\Phi(u)$ ($\phi$ is the standard normal density function) and $\tilde{\rho} = \sigma/\sqrt(\tau^2 + \sigma^2) \rho$.
-The probability of a study being selected is
-% 
-% \begin{align}
-% P(\textrm{select}|s, y) = P(a,b,s,y) = \Phi(\frac{u + \tilde{\rho}((y - \mu)/\sqrt(\tau^2 + \sigma^2))}{\sqrt{1 - \tilde{\rho^2}}})
-% \end{align}
-% 
-% It can also be shown that the expected value 
-% 
-% \begin{align}
-% \mathbb{E}(y|s, select) = \mu + \rho\sigma\lambda(u) \label{copas.expectation}
-% \end{align}
-% 
-% which shows that the expected value for a study is larger for larger $\sigma$. 
-% 
-% \vspace{0mm}
-% One can compute a likelihood function based on the distribution of $y$ conditional on $z > 0$.
-The likelihood can be maximized for any given pair $a,b$ (can not be estimated since the number of missing studies is not known), and a maximum likelihood estimate $\hat{\mu}$ for the true mean $\mu$ can be obtained.
-One can then perform a sensitivity analysis.
-First, one looks how $\hat{\mu}$ changes for different values of $a,b$.
-One can then compare the fitted values in \ref{copas.expectation} with the real values.
-To test the fit of the model (while keeping all other parts unchanged), the model can be extended in the following way :
-% 
-% \begin{align}
-% y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
-% \end{align}
-% 
-% If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
-Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
-The $p$-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
-% 
-% \vspace{0mm}
-% To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
-% 
-% \vspace{0mm}
-% In practice, only a range of values for $a,b$ are reasonable.
-For those values, the quantities above can be calculated and illustrated.
-Values for $\mu$ that have $p$-values over a predefined significance threshold can be used for inference of the effect size.
-% 
-% \subsection{Adjustment by Regression}
-% There are multiple ways to adjust for small study effects by regression.
-The general idea is to extrapolate the effect size of a study with a variance of zero based on the given effects and variances.
-% 
-% \citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
-Similarly to what has been seen in Copas selection model, we let $y_{i}$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_{i}}$ as in \ref{limitmeta.regression}.
-% 
-% \begin{align}
-% y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{v_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
-% \end{align}
-% 
-% $\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
-% 
-% \begin{align}
-% \mathbb{E}((y_{i} - \beta_{0})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{ if } \sqrt{v_{i}} \rightarrow \infty \label{limitmeta.infinitesample} \\
-% \mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
-% \end{align}
-% 
-% After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before e.g. in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test (see \ref{Thompson}).
-% 
-% \vspace{0mm}
-% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
-% 
-% \begin{align}
-% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
-% \end{align}
-% 
-% Letting $M \rightarrow \infty$, we obtain:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
-% \end{align}
-% 
-% Note that:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
-% \end{align}
-% 
-% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
-% 
-% \begin{align}
-% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
-% \end{align}
-% 
-% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-% \end{align}
-% 
-% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
-
-% \begin{align} \label{cox reg}
-% P(Y < y|\mathbf{x}) = 1 - exp(-exp(h(y) - (\mathbf{x})^\top\beta)
-% \end{align}
-% 
-% See \cite{hothorn} for further information. It specifies the instantaneous risk of an event at time t to be
-% 
-% \begin{align}
-% \lambda_{0}(t)exp((\mathbf{x})^\top\beta) \nonumber
-% \end{align}
-% 
-% The model is regarded as a semi parametric model since it includes the covariates in a linear fashion but leaves the baseline hazard $\lambda_{0}(t)$ unspecified.
-The factor $exp((\mathbf{x})^\top\beta)$ has the interpretation of a hazard ratio between the reference with $\mathbf{x} = 0$.
-The formal definition of the hazard is
-% 
-% \begin{align}
-% h(t) = \lim_{h \to 0} \frac{P(t < T < t + h| T > t)}{h}
-% \end{align}
-% 
-% 
-% \begin{align} \label{generalized linear model}
-% \mathbf{Y}{_{ij}}|U{_i},\epsilon{_{ij}} = (1,x{_i}^\top)\beta + U{_i} + \epsilon{_{ij}}
-% \end{align}

### 2019-07-05 report/chapter05.Rnw
adjustments after correction

@@
 
+<<'Data03', echo=FALSE, warning=FALSE>>= 
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "meta.bin.RData"))
+load(file.path(PATH_RESULTS, "meta.cont.RData"))
+load(file.path(PATH_RESULTS, "meta.surv.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+load(file.path(PATH_RESULTS, "meta_id_I2.RData"))
+
+adjustment.diff.keep <- meta.f %>% 
+  mutate(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
+                                 sign(est.copas) != sign(est.fixef) ~ -abs(est.copas)),
+         est.reg.f = case_when(sign(est.reg) == sign(est.fixef) ~  abs(est.reg),
+                               sign(est.reg) != sign(est.fixef) ~ -abs(est.reg)),
+         est.copas.r = case_when(sign(est.copas) == sign(est.ranef) ~  abs(est.copas),
+                                 sign(est.copas) != sign(est.ranef) ~ -abs(est.copas)),
+         est.reg.r = case_when(sign(est.reg) == sign(est.ranef) ~  abs(est.reg),
+                               sign(est.reg) != sign(est.ranef) ~ -abs(est.reg)),
+
+         est.d.copas.f = case_when(sign(est.d.copas) == sign(est.d.fixef) ~  abs(est.d.copas),
+                                   sign(est.d.copas) != sign(est.d.fixef) ~ -abs(est.d.copas)),
+         est.d.reg.f = case_when(sign(est.d.reg) == sign(est.d.fixef) ~  abs(est.d.reg),
+                                 sign(est.d.reg) != sign(est.d.fixef) ~ -abs(est.d.reg)),
+         est.d.copas.r = case_when(sign(est.d.copas) == sign(est.d.ranef) ~  abs(est.d.copas),
+                                   sign(est.d.copas) != sign(est.d.ranef) ~ -abs(est.d.copas)),
+         est.d.reg.r = case_when(sign(est.d.reg) == sign(est.d.ranef) ~  abs(est.d.reg),
+                                 sign(est.d.reg) != sign(est.d.ranef) ~ -abs(est.d.reg)),
+
+         est.z.copas.f = case_when(sign(est.z.copas) == sign(est.z.fixef) ~  abs(est.z.copas),
+                                   sign(est.z.copas) != sign(est.z.fixef) ~ -abs(est.z.copas)),
+         est.z.reg.f = case_when(sign(est.z.reg) == sign(est.z.fixef) ~  abs(est.z.reg),
+                                 sign(est.z.reg) != sign(est.z.fixef) ~ -abs(est.z.reg)),
+         est.z.copas.r = case_when(sign(est.z.copas) == sign(est.z.ranef) ~  abs(est.z.copas),
+                                   sign(est.z.copas) != sign(est.z.ranef) ~ -abs(est.z.copas)),
+         est.z.reg.r = case_when(sign(est.z.reg) == sign(est.z.ranef) ~  abs(est.z.reg),
+                                 sign(est.z.reg) != sign(est.z.ranef) ~ -abs(est.z.reg)),
+
+         est.fixef = abs(est.fixef),
+         est.ranef = abs(est.ranef),
+         est.z.fixef = abs(est.z.fixef),
+         est.z.ranef = abs(est.z.ranef),
+         est.d.fixef = abs(est.d.fixef),
+         est.d.ranef = abs(est.d.ranef))
+
+truebias.bin.percentage <- round(adjustment.diff.keep %>% filter(outcome.type == "bin") %>% filter(est.fixef - est.reg > 0) %>% count()/(dim(meta.bin)[1])*100,1)
+
+wider.dataset.ioannidis.comparison <- data.ext2 %>% filter(outcome.type == "bin") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% summarise(n()) %>% ungroup() %>% count()
+
+restr.dataset.ioannidis.comparison <- (data.ext2 %>% filter(outcome.type == "bin") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>%  ungroup() %>% distinct(file.nr, .keep_all = T) %>% count() / wider.dataset.ioannidis.comparison)*100
+
+largerten.ioannidis.comparison <- (data.ext2 %>% filter(outcome.type == "bin") %>% group_by(meta.id) %>% filter(n() > 9) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>% summarise(n()) %>% ungroup() %>% count() / wider.dataset.ioannidis.comparison)*100
+
+variance.ratio.ioannidis.comparison <- (data.ext2 %>% filter(outcome.type == "bin") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>% filter((max(se)^2)/(min(se)^2) > 4) %>% summarise(n()) %>% ungroup() %>% count() / wider.dataset.ioannidis.comparison)*100
+
+onesig.ioannidis.comparison <- (data.ext2 %>% filter(outcome.type == "bin") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>%
+  filter(sum(pval.single < 0.05, na.rm = T) > 0) %>% summarise(n()) %>% ungroup() %>% count() / wider.dataset.ioannidis.comparison)*100
+
+allcriteria <- (dim(meta.bin)[1]/wider.dataset.ioannidis.comparison)*100
+
+harbord.ioannidis.comparison <- (meta.bin %>% filter(pval.harbord < 0.1) %>% count()/dim(meta.bin)[1])*100
+
+own.results <- c(wider.dataset.ioannidis.comparison$n, paste(round(c(largerten.ioannidis.comparison$n, variance.ratio.ioannidis.comparison$n, onesig.ioannidis.comparison$n, allcriteria$n,
+                       harbord.ioannidis.comparison$n)), "%", sep = ""))
+
+ioannidis.results <- c(6873, paste(c(13, 72, 55, 5, 12), "%", sep = ""))
+
+comparison.ioannidis <- data.frame(Ioannidis = ioannidis.results, Thesis = own.results)
+rownames(comparison.ioannidis) <- c("Wider dataset (n)", "study number > 10", "variance ratio > 4",
+                                    "study sig. number > 1", "all exclusion criteria", "harbord test p-value < 0.1")
+
+@
+
 \chapter{Discussion}
 
-It is tempting to claim to have a perspective that spans the entire clinical research when looking at the cochrane dataset.
+\section{Results in the light of the Literature}\label{sec:discussion.results}
+
+Extensive research already revealed the presence of small study effects and adjustment for it.
+Thus, before drawing conclusions, the resulty of these studies are reviewed, and it will be seen if we are to add to the findings, reafirm them or even have to correct some of them.
+The methodological approaches, as well as the data differs between the publications.
+When clear methodological drawbacks are found in the analysis, the results are resumed for completeness, but left uncommented, and the reader is referred to chapter \ref{ch:methods} for ciriticism of the methods.
+Sometimes, the results are adjusted such that they can be compared to the application of two-sided small study effect tests used in most publications.
+
+\subsection{\citet{Egger}}
+The first attempt, to our knowledge, to obtain an overview over the issue of publication bias for meta-analysis in clinical science.
+The Cochrane database (1996 issue 2) and publications from the four leading medicine journals (the Lancet, BMJ, JAMA and Annals of Internal Medicine) between 1993 and 1996 were used to find systematic reviews with randomized controlled trials for the application of Egger's small study effect test.
+They included 38 meta-analyses with at least 5 studies and binary outcomes from the Cochrane Library and 37 from the journals.
+Five (13\%) meta-analyses from Cochrane and 13 (38\%) from the journals had significant two sided small study effect test results (P < 0.01).
+Also, they found that the test-statistics were more often negative, which correspondend in their setup to larger small studies, i.e.
+``true publication bias'' (\Sexpr{round(((24/38))*100, 1)} among Cochrane meta-analyses and \Sexpr{round(((26/37))*100, 1)} for journal meta-analyses).
+The results from this report with R\"ucker's test are: \Sexpr{length(which(meta.bin$pval.rucker < 0.1))/dim(meta.bin)[1]}\%, and when using regression adjustment to decide about the direction of publication bias, we get \Sexpr{truebias.bin.percentage}\%.
+
+\subsection{\citet{sutton.2000}}
+Out of 397 systematic reviews from the Cochrane database (complete number for 1998, issue 3), 49 had more than ten included studies and binary outcomes and 48 compared two treatments.
+They were analysed by trim-and-fill method \citep{trimfill} to detect and adjust for funnel plot asymmetry (similar to small study effect tests, but the method is known to overestimate bias).
+23 were found to have missing studies, and eight had more than three missing studies which was considered to be significant publication bias.
+Additionally, they found that three estimates of random effects meta-analysis became non-significant after adjustment, and one became significant (by negative adjustment).
+The results are difficult to compare, but the methodological limitations make this findings unreliable.
+
+\subsection{\citet{Ioannidis2007}}
+Very similar work compared to this thesis, especially because extensive use of the Cochrane Library was made with a large number of meta-analyses.
+The data processing steps were however different, and only binary outcomes as used in two-by-two tables were analysed.
+The approximately corresponding numbers are put in parentheses for comparison.
+The Cochrane Library from 2003 (issue 2) was used.
+After removal of duplicates and intractable meta-analyses, they had 6,873 meta-analyses with more than two studies left (\Sexpr{wider.dataset.ioannidis.comparison}).
+When only using one meta-analysis per review, this reduced to 846 (\Sexpr{restr.dataset.ioannidis.comparison}).
+Then, the criteria that have also been applied in this masters thesis are applied: $I^2 < 0.5$, variance ratio of smallest and largest effects > 4, at least one significant study result and at least 10 studies to be used.
+Afterwards, they applied Harbord's, Egger's and Begg's Test to the dataset.
+The reader can compare some corresponding numbers in Table \ref{ioannidis}.
+The results seem to be similar enough to claim that neither the methods nor the data and it's results are differing substantially.
+Because the thesis relies on more data, it is likely to be more accurate and can possibly add to the findings of \citet{Ioannidis2007}.
+
+<<echo = FALSE, results = 'asis'>>=
+print(xtable(comparison.ioannidis, caption = "Comparison of results from Ioannidis et.al.
+(2007) to the results of the thesis.
+The percentage of meta-analysis which match all exclusion criteria denotes the ones that apply to all criteria in the table plus the small heterogeneity criterium.", label = "ioannidis", align = "lrr"))
+@
+
+\subsection{\citet{souza.2007}} 
+Reviews of the World Health Organization (WHO) Reproductive Health Library (RHL), issue 9, were analysed with the trim-and-fill method.
+The RHL reproduces and expands reviews from the Cochrane Library with implications for developping countries.
+21 of 105 reviews contained more than ten studies and were used.
+Trim-and-fill found asymmetry in 18 of 21 studies, and 10 had more than 3 missing studies (``significance'').
+Two of those and one with one missing studies found no evidence for treatment effects after the 0.05 $p$-value threshold after adjustment by trim-and-fill.
+
+\subsection{\citet{kicinsky}}
+The author provides an estimate of the probability of including significant findings versus non-significant findings in Cochrane meta-analyses over time.
+This work is by far the most complete and qualitatively satisfying analysis to estimate publication bias based on significance.
+The data is from the Cochrane Library from 2013 (issue number not provided).
+The method by which treatment-placebo and treatment-treatment comparisons, safety and efficacy meta-analyses were separated is not known, but it allowed to do a more specific analysis than in this thesis.
+\\
+From 3845 reviews, the author separated 907 reviews with more than ten studies.
+From those, 539 compared placebo to treatment.
+After removing duplicates and sensitivity analyses, 358 analyses with 1297 meta-analyses remained.
+From these 191 were excluded because they comprised overall mortality and withdrawal, because these could not clearly be specified as safety or efficacy, respectively.
+\\
+1106 meta-analyses from 329 meta-analyses, which contained 802 efficacy and 304 safety meta-analyses.
+The median publication year per meta-analysis was 1997 for efficacy meta-analyses and 1999 for safety meta-analyses.
+Then, a bayesian two-step hierarchical selection model was applied (\citet{bayesian.selection.model}, \citet{bayesian.selection.model2}).
+The model allows to estimate a ratio of publication probability between significant and non-significant study estimates using a two-step weight function.
+The model was fitted with the Monte-Carlo Markov-Chain algorithm STAN and the geometric mean was used as an estimate for the publication probability ratio.
+It shall be noted that some authors are critical on the use of selection models for inference, since the true selection process is unknown as $n$ unpublished studies is not known.
+They argue that selection models should solely be used for inference.
+Simulations performed in \citep{bayesian.selection.model} indicated that the method performed well if the true mean effect size was not small, and also robust to small study effects.
+It outperformed the Egger's test and Begg's test, especially when small study effects were absent, and had lower false-positive rates.
+Put ad-hoc, the model uses the between-study heterogeneity between significant and non-significant results and allows the model to downsize the weights for the former to attain a more coherent distribution of the overall mean effect size.
+\\
+The results showed a clear publication bias for significant results for efficacy meta-analyses (27\% higher for significant studies, 95\%CI credible intervals: 1.18 to 1.36).
+The probability was more than twice as high in 27\% of the meta-analyses (95\% CI: 23\% to 31\%).
+But the probability decreased: from 1.65 (95\% CI: 1.31 to 2.15) in 1980 (average publication year) to 1.36 (95\% CI: 1.17 to 1.62) in 1990 to 1.18 (95\% CI: 1.04 to 1.33) in 2000.
+For sake of completeness, the probability of inclusion was  1.78 (95\% CI: 1.51 to 2.13) larger for non-significant safety effect estimates, but again, decreased with time (1.77, 95\% CI: 1.46 to 2.21 in 2000).
+\\
+
+Applying the last crieria on the wider dataset, they were left with $n =$ 868 (\Sexpr{largerten.ioannidis.comparison}).
+
+They analyse the Cochrane Library (2003, issue 2) to find meta-analyses suited for small-study effect tests.
+From 1669 reviews, they excluded all but reviews with binary outcomes(12,709 meta-analyses), and further excluded no-event meta-analyses and all-event meta-analyses (-906 = 11,803).
+They furthermore removed 761 meta-analyses with studies with identical data in other meta-analyses (effects, events and totals, keeping the larger meta-analysis), and meta-analyses with two studies only (4169 left).
+When they restricted to take only one meta-analysis per review, they were left with 846s
+
+Already in 1978, scientists raised concern that effect sizes could be overestimated systematically if journals were not willing to drop their policy to use ``statistical significance'' as one of their criteria for publication \citep{dunlap1978}.
+This results in a ``file drawer'' \citep{file.drawer.1979} full of effect sizes on the other side of the $p < 0.05$ significance threshold, publicly inaccessible, and likely to be neglected over time.
+In the course of the years, this could be verified repeatedly.
+For example, a Cochrane Methodology review states that effect sizes from the grey literature are systematically smaller than published effect sizes (\citet{hopewell.2007}, but see also \citet{grey.literature.2}, \citet{grey.literature.3}, \citet{grey.literature.4} (registered btw.
+1987 - 2004), \citet{grey.literature.5} (registered btw.
+1998 - 2000) which are not restricted to Cochrane).
+In social sciences, \citet{social.sciences.publication.bias} found that ``positive'' results were 40\% more likely to be reported.
+\\
+The introduction of registries for clinical trials and some legal force to make results available have clearly adapted to this issue in clinical science, but the evidence indicates that it is not resolved yet.
+
+Of course, it is unfair to blame journals alone for disrupting proc
+
+\section{Implications}\label{sec:implications}
+
+Some aggravations
+
+The primary implication of the results is that still, more statistical education and understanding is required from scientists and journal editors.
+First, it has to be achieved that the common fallacy to think of statistical significance as scientific relevance has to be overcome.
+Second, the practical use of more diverse approaches than just the usual analysis of evidence against the null-hypothesis of no treatment effect should be encouraged, as for example, non-inferiority analysis setups \etc.
+The possibilities and the importance of negative findings is generally under-appreciated and could be promoted systematically.
+Generally, this points to the need for more discourse-oriented culture in science, opposite to the discovery oriented modern research \citet{ioannidis.2005}.
+This, together with efforts like from Cochrane to systematically collect and connect empirical data, and open source study protocols, data and publications might resolve the issue to large parts.
+
+It is tempting to claim to have a perspective that spans the entire clinical research when looking at the Cochrane dataset.
 Several points can be made to argue in this favor (see chapter 2 CITE for details).
@@
 Concerning the generalizability of results of this thesis on clinical science, there are important caveats.
-First of all, intrinisically, the Cochrane Organization focuses on established research of public interest.
+First of all, intrinsically, the Cochrane Organization focuses on established research of public interest.
 By definition, it can not comprise the full diversity of the field, and especially where research and evidence is new, sparse and not established, it is almost certainly not included.
-The aim of Cochrane is to concentrate scientifical knowledge, thus it can not incorporate studies that are unique in their research subjects and are on the ``periphery'' of science.
+The aim of Cochrane is to concentrate scientific knowledge, thus it can not incorporate studies that are unique in their research subjects and are on the ``periphery'' of science.
 
@@
 If one decides that the results do at least partially hold for clinical science and science in general, the interpretation of the results change also.
-
-\section{Meta-analyses}
-If one investigates the success of a treatment, the first way of doing so is to investigate to what extent the treatment effect estimate differs from no treatment effect.
+% 
+% 
+% \section{Meta-analyses}
+% If one investigates the success of a treatment, the first way of doing so is to investigate to what extent the treatment effect estimate differs from no treatment effect.
 This is usually done by a hypothesis test, where the null hypothesis of no treatment effect is rejected if the p-value of the treatment effect estimate is above a given threshold.
 One decides in this case in favor of the treatment.
-
-\vspace{0mm}
-The aim of a meta-analysis is to re-calculate the treatment effect based on multiple results.
+% 
+% \vspace{0mm}
+% The aim of a meta-analysis is to re-calculate the treatment effect based on multiple results.
 The treatment effects are pooled and the pooled treatment effect estimate can then again be tested based on the null-hypothesis.
@@
 Consequently, a meta-analysis may provide a significant treatment effect estimate, even if the single results do not.
-
-\vspace{0mm}
-It was the aim of the first section CITE of the results part to compare significance of the treatment effect of single studies with the significance of the pooled effect.
+% 
+% \vspace{0mm}
+% It was the aim of the first section CITE of the results part to compare significance of the treatment effect of single studies with the significance of the pooled effect.
 So the question to be answered was: How does significance in single studies relate to significance when all evidence is included?
@@
 One can imagine 3 scenarios:
-\begin{itemize}
-\item A primary significant study belongs to a group which, overall, can not reject the null-hypothesis of no treatment effect in meta-analysis.
+% \begin{itemize}
+% \item A primary significant study belongs to a group which, overall, can not reject the null-hypothesis of no treatment effect in meta-analysis.
 The study result is then overruled by the result of the meta-analysis (if one is to accept that meta-analysis is a more stringent rule for decision about treatment effects).
-\item The opposite: A non-significant primary study belongs to a group which has a significant pooled treatment effect estimate. The study failed to find evidence for a ``true'' effect.
-\item Primary and secondary significance remain unchanged after meta-analysis.
-\end{itemize}
-
-The amount of overlap between primary and secondary significance was moderate, as it had to be expected based on the methodology of meta-analysis.
+% \item The opposite: A non-significant primary study belongs to a group which has a significant pooled treatment effect estimate. The study failed to find evidence for a ``true'' effect.
+% \item Primary and secondary significance remain unchanged after meta-analysis.
+% \end{itemize}
+% 
+% The amount of overlap between primary and secondary significance was moderate, as it had to be expected based on the methodology of meta-analysis.
 The vast amount of non-significant primary results that contribute in the end to a significant secondary meta-analysis result is compelling.
@@
 One ad-hoc interpretation of publication bias is that results that are not significant are less likely to be published (arguably because they show no treatment effect).
-
-\vspace{0mm}
-If one is to prefer, or accept meta-analysis as a way to assess treatment effect evidence, the result provides a strong argument for publication of non-significant results, because they can contribute to evidence for treatment effects in meta-analysis (in a Cochrane review).
+% 
+% \vspace{0mm}
+% If one is to prefer, or accept meta-analysis as a way to assess treatment effect evidence, the result provides a strong argument for publication of non-significant results, because they can contribute to evidence for treatment effects in meta-analysis (in a Cochrane review).
 Significant treatment effects that are found may find their into clinical practice and potentially benefit there patients and consumers.

### 2019-07-05 code/analysis.R

@@ -45,7 +45,7 @@ load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
 #--------------------------------------------------------------------------------------------------------------------#
 
 # # ---------- Uncomment to run pre-analysis --------------
-# Get exclusion critetia (I-squared, n. sig. findings, s.e. ratio, dupl.index):
+# # Get exclusion critetia (I-squared, n. sig. findings, s.e. ratio, dupl.index):
 # meta.info.bin <- data.ext2 %>%
 #   group_by(meta.id) %>%
 #   mutate(n = n()) %>% filter(n >= 10) %>% filter(!is.na(outcome.type)) %>%
@@ -103,12 +103,13 @@ load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
 # 
 # meta.info.pre2 <- merge(meta.info, exclusion.estimates, by = "meta.id")
 # 
-# meta.info.pre2 <- meta.info.pre2 %>% rowwise() %>% mutate(I2  = max(0, (Q - n + 1)/Q)) #calculate I2
+# meta.info.I2 <- meta.info.pre2 %>% rowwise() %>% mutate(I2  = max(0, (Q - n + 1)/Q)) #calculate I2
 # 
-# meta.info <- meta.info.pre2 %>% filter(n > 9) %>% filter(I2 < 0.5)
+# meta.info <- meta.info.I2 %>% filter(n > 9) %>% filter(I2 < 0.5)
 # 
 # meta.id.vector <- meta.info$meta.id #Vector of meta-ids that match the criteria.
 # save(meta.id.vector, file =  file.path(PATH_RESULTS, "meta_id_vector.RData"))
+# save(meta.info.I2, file =  file.path(PATH_RESULTS, "meta_id_I2.RData"))
 #--------------------------------------------------------------------------------------------------------------------#
 
 #Get more extensive information from the original dataset about the meta-analyses:

### 2019-07-05 report/chapter04.Rnw
subsection

@@
 
+\subsection{Publication Bias Test Consistency}
 It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects for the same meta-analyses.

### 2019-07-12 report/MSc_Report.tex
subsection
Report based on the new data

@@
 \usetikzlibrary{trees}
+\usetikzlibrary{shapes,arrows}
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
@@
   \vspace*{6cm}{\bfseries\Huge
-  Publication Bias in the Cochrane Database of Systematic Reviews
+  Publication Bias in the Cochrane \vspace{3mm} Database of Systematic Reviews
   }
@@
 
-Typically, we expect empirical scientific results to be distorted by random noise, such that the results are not equal to the real process that they describe.
+Already in 1978, scientists raised concern that effect sizes could be overestimated systematically if journals were ``not willing to drop their policy to use statistical significance as one of their criteria for publication'' \citep{dunlap1978}.
+Scientific findings get more attention and are more likely to be published, read and cited if they are implying large effects.
+The issue has been pin-pointed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}).
+The concern is that overestimated efficacy of the treatments could lead to harm to patients.
+\\
+A measure to counter the presence of single, overestimated study results is a meta-analysis \citep{metaanalysis}, a practice originally developped in psychology.
+Summarized treatment effects and uncertainities should be more robust and reliable.
+The pitfall is that when the entire body of evidence is again a biased sample of studies with high effects, the estimate is again overestimating the true effect.
+There is extensive literature on publication bias in meta-analyses, e.g.
+(\citet{pb.clinicalscience.2013}, %\citet{Hopewell02},
+\citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}). 
+All authors agree in that the inclusion of unpublished results in meta-analyses is insufficient and responsible for overestimation of treatment efficacy.
+Although there are policies that make it mandatory to make accessible all study results \citep{fda}, it is not clear if the situation has improved yet.\\
+The Cochrane Organisation has specialized on systematic reviews of healthcare interventions.
+Methodological and field experts collect data, review them and try to provide up-to-date information about specific treatment efficacies \citep{cochrane.handbook}.
+By extensive literature scrutinization, they try to circumvent the issue of publication bias.
+Earlier research however suggests that the efforts are only partially succesfull, and that there still is publication bias within the reviews (\citet{Egger}, \citet{Ioannidis2007}, \citet{kicinsky}, \citet{vanAert.2019}).
+However, none of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods.
+Also, the results are often presented in the form of dichotomized hypothesis tests, a practice known to contribute to publication bias itself (cite sb).\\
+The aim of this thesis is to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides.
+At the end, an up-to-date estimate of the prevalence of publication bias in the data shall be given, as well as its implications regarding the effect sizes of the treatments.
+To achieve this, methods to detect and adjust for publication bias in meta-analysis are applied on the data.
+
+% 
+% 
+% Also after the introduction of mandatory registration of clinical trials
+% 
+% 
+% 
+% Typically, we expect empirical scientific results to be distorted by random noise, such that the results are not equal to the real process that they describe.
 Additionally, one can reasonably assume that the results are also biased to some extent, as the statistical paradigm of precision versus bias would predict: The smaller the noise part of distortion, the more the result should be distorted by bias.
@@
 \\
-It is more and more considered a new scientific field by itself to think of and argue about circumstances that improve the quality of scientific findings.
+% It is more and more considered a new scientific field by itself to think of and argue about circumstances that improve the quality of scientific findings.
 Statistics is in some sense predestined to contribute to it, because probability and chance concepts are key to understanding of any empirical science.
 \\
-There are also issues, in which statistics is not thought to be able to contribute much to understanding and to be of little help for solving them.
+% There are also issues, in which statistics is not thought to be able to contribute much to understanding and to be of little help for solving them.
 For example, the selective attention that the agents in science are paying to new, strong and clear findings in each science is considered merely a psychological and social %, socioeconomic
-issue.
+% issue.
 It is often explained by the affinity of humans for stories rather than mere facts and for novelties.
@@
 \\
-Clearly, reproduction of experimental results is the gold standard of testing empirical science, because it reassures the universality and reliability by which certain procedures or effects appear if measured in the correct experimental context.
+% Clearly, reproduction of experimental results is the gold standard of testing empirical science, because it reassures the universality and reliability by which certain procedures or effects appear if measured in the correct experimental context.
 However, there are also problems there.
@@
 \\
-There is another way to assess the strength of scientific results if the experiment has been conducted more than once (however not with exactly identical protocol as in reproduction studies): Meta-analyses.
+% There is another way to assess the strength of scientific results if the experiment has been conducted more than once (however not with exactly identical protocol as in reproduction studies): Meta-analyses.
 In a meta-analyses, results of multiple (fairly identical) experiments (studies) are summarized to a single result.
@@
 A review in 2017 (...) for example identified 147 (!) conceptually differing methods.\\
-This speaks as well for the inevitable difficulties that such methods encounter.
+% This speaks as well for the inevitable difficulties that such methods encounter.
 First of all, it is most often impossible to estimate the real selection process, that is the rate by which smaller effects go unnoticed because of selective publication and reporting, because the number of missing results in the studies is not known at the first place and impossible to retrieve.
@@
 However, given the large body of evidence for publication bias collected from other sources (...), in many cases, the results from these methods indeed give a quantitative measure of publication bias.\\
-In this masters thesis, the answers for two questions are investigated: What is the extent and effect of publication bias in clinical science?
+% In this masters thesis, the answers for two questions are investigated: What is the extent and effect of publication bias in clinical science?
 For this purpose, a dataset from the Cochrane Organization is analysed with commonly used techniques to detect and adjust for publication bias (more precisely, small study effects, as it will be seen later).
@@
 
-\subsection{Copas Selection Model}
+\subsection{Copas Selection Model} \label{sec:copas}
 
@@
 % LaTeX file for Chapter 03
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in arrange\_impl(.data, dots): Evaluation error: object 'Study' not found.}}\end{kframe}
+\end{knitrout}
 
@@
 \subsection{Structure and Content}
-The dataset consists of 5016 systematic reviews from the Cochrane Library with 52995 studies and 463820 results.
-A result compares a clinical or medical intervention or treatments to a control.
-Each study provides (multiple) results of clinical interventions.
-\\
-In Table \ref{barbiturate.row}, two results from a systematic review about effects of barbiturates are shown as they are given in the dataset.
+The dataset consists of 6353 systematic reviews from the Cochrane Library with 70662 studies and 744717 results.
+The results all stem from comparisons of a healthcare interventions or treatments to a reference.
+The reference may be a placebo control group or a other intervention or treatment.
+A result can not only be about efficacy of the treatments, but also about safety (adverse effects).\\
+In Table \ref{barbiturate.row}, two results from a systematic review about barbiturates are shown as they are given in the dataset.
 As can be seen, further specifications are provided by the variables in the columns.
 \\
-The comparison variable specifies \textit{what kind} of treatments or interventions are compared, the outcome variable \textit{how} it is compared, and the subgroup variable (not indicated in table) if the result belongs to a certain subgroup.
-Here, the result is of a binary type, so the counts of events in the barbiturate treatment group and the total number of participants are given in columns ``Events'' and ``Total'' and the number of events in the control group ``Events\_c'' and participants ``Total\_c''.
-A event is here death at the end of follow up.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jul  1 17:02:14 2019
-\begin{table}[ht]
-\centering
-\begingroup\scriptsize
-\begin{tabular}{lllrrrr}
-  \hline
-Study & Comparison & Outcome & Events & Total & Events\_c & Total\_c \\ 
-  \hline
-Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11 & 41 & 11 & 41 \\ 
-  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14 & 27 & 13 & 26 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Example of two results as given in the dataset.
+The \texttt{comparison.name} variable specifies \textit{what kind} of treatments or interventions are compared, the \texttt{outcome.name} variable \textit{how} it is compared, and the \texttt{subgroup.name} variable (not indicated in table) \textit{if and to what experimental subgroup} the result belongs.
+\\
+The result is of a binary type, and the counts of events in the treatment group are in \texttt{events1} and of the control group in \texttt{events2} and the total number of participants are given in columns \texttt{total1} and \texttt{total2}.
+As can be seen, events denote here "death at the end of follow-up".
+
+\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(barbi1, label = "{}barbiturate.row"{}, digits = 0, caption = "{}Example of two results as given in the dataset.
 Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
-Further descriptive variables have been ommitted}
-\label{barbiturate.row}
-\end{table}
+Further descriptive variables have been ommitted"{}): object 'barbi1' not found}}\end{kframe}
 
 A complete listing of the variables of a result is given in Table \ref{variable}.
-They can roughly be separated into variables that \textit{specify the review} in which the result is contained and variables that \textit{specify the result} itself (separated by a horizontal line in Table \ref{variable}):
+Depending on the type of the data, \eg if it is binary or continuous, some variables are missing for the specific results.
 
@@
       \hline
-      \texttt{file.nr} & The number of the file from which the review data has been \\&gathered. This file corresponds to a file available in the. \\& Cochrane library\\
-      \texttt{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
-      \texttt{file.index} & Internal index of the file in the Cochrane library.\\
-      \texttt{file.version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
+      \texttt{id} & An id of the review for identification purposes \\
+      %\texttt{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
+      % \texttt{file.index} & Internal index of the file in the Cochrane library.\\
+      % \texttt{file.version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
       %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
@@
       \texttt{study.name} & Name of the study to which the result belongs\\
-      \texttt{study.year} & Year in which the study was published\\
+      \texttt{study.year} & Year in which the study was published \\
+      \texttt{study.data.source} & Source of the study, either ``Publ \\
       \hline
@@
   \caption{Dataset variable names and descriptions  \label{variable}}
-
+  \label{variable}
   \end{center}
@@
 Let us consider the previously mentioned barbiturate and head injury review.
-The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates''.
+The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates'' %\citep{barbiturate}.
 \\
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jul  1 17:02:14 2019
+% Fri Jul 12 10:30:39 2019
 \begin{table}[ht]
@@
 Information about missing values in the dataset is given in Table \ref{missing}.
-For variables as research subject, outcome and subgroup name and event counts there are no missing values.
-The relative amount of missing values is very low except for study years.
-For continuous outcomes, the cases have been counted were no treatment effect and standard error is available: neither mean values and standard deviations, nor mean differences and standard error.
-Also Study years before 1920 and after 2019 are declared as missing, as well as sample sizes below zero.
+The relative amount of missing values is low, except for study years.
+For continuous outcomes, the cases are counted were neither a mean difference nor means are available.
+Similarly, the counts of cases where neither standard errors nor standard deviations are available are provided.
+Study years before 1920 and after 2019 are declared as missing, as well as sample sizes equal to zero.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jul  1 17:02:14 2019
+% Fri Jul 12 10:30:39 2019
 \begin{table}[ht]
@@
   \hline
-Missing mean values and mean differences & 984 \\ 
-  Missing standard deviations and standard errors & 1300 \\ 
-  Missing sample sizes & 12173 \\ 
-  Missing study year & 44649 \\ 
+Neither means nor standard deviations (CONT) & 775 \\ 
+  Zero participants in one group & 15162 \\ 
+  Missing study publication year & 7942 \\ 
    \hline
@@
 
-The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982, 95\% quantile = 2013,).
-The median of the publication years is 2003, the mean 2001 and the quartiles are 1996 and 2008.
-Only a handful ($n = 18$) have been published in 2018, none in 2019.
-\\
-%No information is available concerning unpublished results and studies.
+The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982, 95\% quantile = 2014,).
+The median of the publication years is 2003, the mean 2000.97 and the quartiles are 1996 and 2008.
+1075 studies have been published in 2018, none in 2019.
+\\
 The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}.
-One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (> 65\%).
+One can conclude of the table that roughly 31 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (more than 65\%).
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jul  1 17:02:14 2019
+% Fri Jul 12 10:30:39 2019
 \begin{table}[ht]
@@
   \hline
-Risk Ratio & 232583 & 50.1\% \\ 
-  Mean Difference & 102315 & 22.1\% \\ 
-  Odds Ratio & 49372 & 10.6\% \\ 
-  Std. Mean Difference & 40535 & 8.7\% \\ 
-  Peto Odds Ratio & 19122 & 4.1\% \\ 
-  Hazard Ratio & 6566 & 1.4\% \\ 
-  Risk Difference & 6234 & 1.3\% \\ 
-  Rate Ratio & 2283 & 0.5\% \\ 
-  other & 4810 & 1\% \\ 
+RR & 361902 & 48.6\% \\ 
+  MD & 164920 & 22.1\% \\ 
+  OR & 72012 & 9.7\% \\ 
+  SMD & 70717 & 9.5\% \\ 
+  PETO\_OR & 39710 & 5.3\% \\ 
+  RD & 11068 & 1.5\% \\ 
+  Hazard Ratio & 8054 & 1.1\% \\ 
+  Odds Ratio & 4055 & 0.5\% \\ 
+  other & 12279 & 1.6\% \\ 
    \hline
@@
 The sample sizes among results vary to some extent.
-There are 5\% of treatment group sample sizes that are smaller than 8, the 5\% quantile and 95\% smaller than 551.
-The first quartile is 22, the median 48, the mean 302.03 and the third quartile 119.
+There are 5\% of treatment group sample sizes that are smaller than 9, 95\% smaller than 510.
+The first quartile is 23, the median 48, the mean 256.71 and the third quartile 116.
 The large difference between median and mean is caused by very large groups with over 2,000,000 participants.
-Analogously, the quantiles of the total sample size are: 5\% quantile = 15, first quartile = 44, median = 94, third quartile = 229 and 95\% = 1044.
-The mean is 617.81.
-\\
-The mean and median number of results per review are 12.42 and 7.
-There are 417 reviews with five or fewer results, and the quartiles are 16 and 102.
-Similarly, the number of reviews with a maximum of two studies included is 836, the mean study number is 12.42, the median 7 and the interquartile range 4 and 15 and the 95\% quantile 40.
-The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1497 results in total.\\
+Analogously, the quantiles of the total sample size are: 5\% quantile = 17, first quartile = 44, median = 94, third quartile = 223 and 95\% = 983.
+The mean is 623.16.
+\\
+There are 518 reviews with five or fewer results.
+The 5\% and 95\% quantiles are 4 and 447.
+The mean and median number of results per review are 13.6 and 8, and the quartiles are 16 and 109.
+Similarly, the number of reviews with a maximum of two studies included is 1039, the mean study number is 13.6, the median 8 and the interquartile range 4 and 16 and the 95\% quantile 45.
+The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citet{largest.review}
+which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1,497 results in total.\\
 For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome.
-More specifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis, since their research subject and experimental setup can be considered sufficiently homogeneous.
-Importantly, this distinction is also used by the Cochrane Organization itself, i.e.
-the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
-The dataset is divided in meta-analyses with identical experimental setup. The size of a meta-analysis denotes how many results are included in a group.
-Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results. Practically, this number of meta analyses can be performed, with each having at least $n$ results.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Jul  1 17:02:14 2019
+The studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis.
+This distinction is also used by the Cochrane Organization itself, \ie the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
+The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.
+
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Fri Jul 12 10:30:39 2019
 \begin{table}[ht]
@@
   \hline
-1 & 102344 & 186300 \\ 
-  2 & 31686 & 83956 \\ 
-  3 & 16072 & 52270 \\ 
-  4 & 9628 & 36198 \\ 
-  5 & 6444 & 26570 \\ 
-  6 & 4230 & 20126 \\ 
-  7 & 2961 & 15896 \\ 
-  8 & 2114 & 12935 \\ 
-  9 & 1592 & 10821 \\ 
-  10 & 1238 & 9229 \\ 
-  11 & 921 & 7991 \\ 
-  12 & 702 & 7070 \\ 
-  13 & 585 & 6368 \\ 
-  14 & 455 & 5783 \\ 
-  15 & 5328 & 5328 \\ 
+1 & 143375 & 268903 \\ 
+  2 & 45459 & 125528 \\ 
+  3 & 23232 & 80069 \\ 
+  4 & 14184 & 56837 \\ 
+  5 & 9493 & 42653 \\ 
+  6 & 6449 & 33160 \\ 
+  7 & 4583 & 26711 \\ 
+  8 & 3412 & 22128 \\ 
+  9 & 2585 & 18716 \\ 
+  10 & 2046 & 16131 \\ 
+  11 & 1524 & 14085 \\ 
+  12 & 1197 & 12561 \\ 
+  13 & 1022 & 11364 \\ 
+  14 & 785 & 10342 \\ 
+  15 & 9557 & 9557 \\ 
    \hline
@@
 \endgroup
-\caption{Cumulative number of groups with number of reproduction trials $\geq$ n} 
+\caption{Number and cumulative number of groups with meta-analysis size n.} 
 \label{repr.groups}
@@
 \section{Data Tidying and Processing} \label{sec:Processing}
-The original dataset was provided by .. (some words how the dataset was obtained and processed by C.R.). \\
-The information in the previous pages are from a tidied and processed version of this dataset. \\
-
-\subsection{Modification of old variables}
-In some cases, reasonable assumptions led to small changes in the originally provided variables:
-\begin{itemize}
-\item \texttt{study.year}: It was assumed that studies that are declared to have been published before 1920 ($n$ = 30664) are mis-specified, as well as after 2019 ($n$ = 384), so these have been set to NA.
-\item \texttt{mean1} and \texttt{mean2}: When both \texttt{mean1} and \texttt{mean2} are equal to zero or NA, \texttt{outcome.measure.new} is equal to \texttt{(Std.) Mean Difference}, but a mean difference is given in \texttt{effect}, \texttt{mean1} is set equal to \texttt{effect} ($n$ = 1593).
-\end{itemize}
+The dataset was scraped from the Cochrane Database of Systematic Reviews at the ... . A specialized code was used to convert the xtml. files from the webpage into the data at hand cite... .
 
@@
 An example would be the formally different notations for odds ratios: ``Odds Ratio'', ``odds ratio'', ``OR'', which were all denoted as ``Odds Ratio''.
-\item \texttt{outcome.type}: A simplification of \texttt{outcome.measure.new}.
-The outcome.type ``bin'' indicates if \texttt{outcome.measure.new} is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
+% \item \texttt{outcome.flag}: A simplification of \texttt{outcome.measure.new}.
+The outcome.flag ``bin'' indicates if \texttt{outcome.measure.new} is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
 ``cont'' is equivalent to \texttt{outcome.measure.new} equal to "Std.
@@
 ``surv'' equal to ``Hazard Ratio'' and ``rate'' equal to ''Rate Ratio'' or ``Rate Difference''.
-\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.type ``bin''.
-\item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.type ``cont''.
-If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.new} was equal to ``Std.
-Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  6938).
-\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.type ``bin''.
-\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.type ``bin'') or $g$ (for outcome.type ``cont'') to $r$ transformation.
+\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.flag ``bin''.
+\item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.flag ``cont''. 
+% If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.new} was equal to ``Std.
+Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  length(inpute.given.ind)).
+\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.flag ``bin''.
+\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.flag ``bin'') or $g$ (for outcome.flag ``cont'') to $r$ transformation.
 \item \texttt{z} and \texttt{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
-\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.type ``cont'' or Wald test for outcome.type ``bin''.
+\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.flag ``cont'' or Wald test for outcome.flag ``bin''.
 \item \texttt{events1c} and \texttt{events2c}: Correction of \texttt{events1} and \texttt{events2} zero event counts or event counts = patient number.
@@
 Consistent to what has been discussed before, all results that share a common comparison, outcome and subgroup (optional, subgroups not given in any case) may be combined in a meta-analysis.
-% \item \texttt{}:
+\item \texttt{se.new}: Depending on \texttt{outcome.flag}, \texttt{se.new} is equal to the square-root of \texttt{var.lrr} (\texttt{outcome.flag} = \texttt{DICH}), square-root of \texttt{var.smd} (\texttt{CONT})
+or \texttt{se} (\texttt{IV}).
 % \item \texttt{}:
@@
 \subsection{Eligibility criteria for Publication Bias Test and Adjustment}
-Initially, the analysis is restricted to binary, continuous and survival outcomes. More formally:
+
+Initially, the analysis is restricted to results with \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}.
+binary, continuous and survival outcomes.
+This corresponds to 734951 out of a total of 744717 results.
+\citet{Ioannidis2007} outlined criteria for application of small study effect tests:
 \begin{itemize}
-\item \textbf{Outcome measures}: The analysis has been restricted on the following outcome measures (from \texttt{outcome.measure.new}): ``Odds Ratio'', ``Risk Ratio'', ``Risk difference'', ``Peto Odds Ratio'', ``Std.
-Mean Difference'', ``Mean Difference'', ``Hazard Ratio''
-($n$ = 456727 out of a total of 463820 results)
+\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = 11463 remaining). 
+\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 10830 remaining).
+\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 8575 remaining)
+\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 3075 remaining).
 \end{itemize}
-
-The suggestions of criteria for eligibility for publication bias tests of \citet{Ioannidis2007} have largely been followed:
-\begin{itemize}
-\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = 5797 remaining). 
-\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 4038 remaining).
-\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 4006 remaining).
-\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 2673 remaining)
-\end{itemize}
-
-After having excluded meta-analyses with less than ten studies, additional criteria for excluding inconvenient meta-analyses are:
+Additionally, the following criteria have been applied:
 \begin{itemize}
@@
 The intention is to exclude sensitivity analyses which are operated on subsets of the available results.
-\item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = 141 out of meta-analyses with at least ten studies).
-\item \textbf{Missing means and sd's}: In the case of continuous outcomes, meta-analyses with means and sd's in any group being equal to zero are excluded ($n$ = 306 out of meta-analyses with at least ten studies).
-\item \textbf{Single patient data}: Meta-analyses that are comprised of single patient data are excluded ($n$ = 8 out of meta-analyses with at least ten studies)
+\item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = 20 out of meta-analyses with at least ten studies).
 \end{itemize}
 
---Make Flowchart--
+The results of this reduction of the dataset are shown in the flow-chart in Figure \ref{Inclusion.criteria}. By applying the criteria, we are only able to analyse a subset of the original data. \\
+Only the data that had accesible all results data available was used for adjustment.
+Thus, all meta-analyses with \texttt{outcome.flag} == \texttt{IV} are ommitted in a second step of the analysis (Analysis dataset (1) and (2) in Figure \ref{Inclusion.criteria}).
+
+\begin{figure}
+\begin{center}
+\tikzstyle{block} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=2.5em]
+\tikzstyle{btw} = [rectangle, node distance=0cm, minimum height =2em, fill= white]
+\tikzstyle{ublock} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=4em, text width = 10em]
+\tikzstyle{line} = [draw, -latex']
+\tikzstyle{final} = [rectangle, draw, fill=red!20, text centered, rounded corners, minimum height=2.8em]
+
+\begin{tikzpicture}[node distance = 2cm, auto]
+    % Place nodes
+        \node [final] (1) {Inital dataset: 
+    6,353 reviews,
+    70,662 studies,
+    744,717 results};
+
+    \node [block, below of=1, node distance=2.2cm] (2) {
+    6,324 reviews,
+    69,873 studies,
+    734,951 results};
+
+    \node [block, below of=2, node distance=2.2cm] (3) {
+    1,262 reviews,
+    29,109 studies,
+    208,391 results,
+    11,463 meta-analyses};
+
+    \node [block, below of=3, node distance=2.2cm] (4) {
+    1,241 reviews,
+    28,698 studies,
+    196,539 results,
+    10,830 meta-analyses};
+
+    \node [block, below of=4, node distance=2.2cm] (5) {
+    1,157 reviews,
+    26,590 studies,
+    162,298 results,
+    8,575 meta-analyses};
+
+    \node [block, below of=5, node distance=2.2cm] (6) {
+    1,150 reviews,
+    26,261 studies,
+    92,956 results,
+    5,244 meta-analyses};
+
+    \node [final, below of=6, node distance=2.2cm] (7) {Analysis dataset (1):
+    912 reviews,
+    19,342 studies,
+    53,012 results,
+    3,075 meta-analyses};
+
+    % \node [final] (7) {Analysis dataset:
+    % format(I2.id.count, big.mark = ",") reviews,
+    % format(I2.study.count, big.mark = ",") studies,
+    % format(I2.result.count, big.mark = ",") results,
+    % format(m.a.smaller.5.count$nn, big.mark = ",") meta-analyses};
+
+    \node [ublock, below of=7, node distance=4cm] (8) {Binary data: \\
+    2,226 meta-analyses};
+
+    \node [ublock, right of=8, node distance=5cm] (9) {Continuous data: \\
+    629 meta-analyses};
+
+    \node [ublock, left of=8, node distance=5cm] (10) {Other data (IV): \\
+    238 meta-analyses};
+
+    \node [final, below of=8, node distance=2.4cm] (11) {Analysis dataset (2):
+    860 reviews,
+    18,238 studies,
+    49,568 results,
+    2,855 meta-analyses};
+
+    % Draw edges
+    \path [line] (1) -- node [btw, xshift = -1.8cm] {\texttt{outcome.flag} restriction} (2);
+    \path [line] (2) -- node [btw, xshift = -1.7cm] {study number $\geq$ 10}(3);
+    \path [line] (3) -- node [btw, xshift = -1.6cm] {variance ratio $>$ 4} (4);
+    \path [line] (4) -- node [btw, xshift = -2cm] {at least one significant result} (5);
+    \path [line] (5) -- node [btw, xshift = -1.2cm] {no duplicates} (6);
+    \path [line] (6) -- node [btw, xshift = -0.8cm] {$I^2$ $\leq$ 0.5} (7);
+
+    \path [line] (7) -- node [btw, xshift = -1.8cm, yshift = 0.45cm] {\texttt{outcome.flag} = \texttt{DICH}} (8);
+    \path [line] (7) -- node [btw, xshift = -1.3cm, yshift = -0.75cm] {\texttt{outcome.flag} = \texttt{CONT}} (9);
+    \path [line] (7) -- node [btw, xshift = -1.8cm] {\texttt{outcome.flag} = \texttt{IV}} (10);
+    \path [line] (8) -- (11);
+    \path [line] (9) -- (11);
+
+\end{tikzpicture}
+\caption{Flow-chart of the exclusion of meta-analyses for the final analysis. The exclusion criteria are given at the right of the arrows.}
+\label{Inclusion.criteria}
+\end{center}
+\end{figure}
 
 \subsubsection{Exclusions due to Computational Errors}
-In exceptional cases, the applied meta-analysis methods and publication bias tests and adjustment algorithms failed due to various reasons.
-Here, those cases are listed and if known, the reasons why computation failed are given.\\
-\textbf{Binary Outcomes}: Out of the meta-analyses that are of \texttt{outcome.type} bin, and have at least ten studies, two studies hat to be excluded:
-\begin{itemize}
-\item meta.id = 62301 (file.nr = 1531, comparison.nr = 8, outcome.nr = 6, subgroup.nr = 1):
-%A subgroup analysis for women with increased adverse pregnancy outcomes, where the effect of vitamin C supplements is tested on pre-eclampsia: 
-Largest study (se = 0.1) has risk ratio 1 and smallest study (se = 1) risk ratio 0.07. Copas publication bias adjustment methods has likelihood optimization issues.
-\item meta.id = 94519 (2519, 14, 1, 2): Largest study (se = 0.05) has risk ratio 0.9 and smallest study (se = 0.4) risk ratio 3.
-Again Copas publication bias adjustment methods has likelihood optimization issues.
-\end{itemize}
-
-There were no issues with \texttt{outcome.type} ``cont'' and ``surv''.
-For the subsequent information, it is important to know that meta-analyses are only repeated with Hedges $g$, Pearson correlation coefficient and Fisher's Z-scores, if the outcome type is not survival and all of the above criteria are met ($n$ = 0).
-\\
-\textbf{Pearson Correlation Coefficient}: Three studies had to be excluded when analyzing the Pearson correlation coefficients:
-\begin{itemize}
-\item meta.id = 157083 (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2): A meta-analysis with all results from the same study, and equal sample size (5 each group).
-The Copas selection model algorithm issued an error when optimizing the likelihood.
-\item meta.id = 159329 (5183, 3, 13): One very small study with group sizes of 2 and 1 patients and small risk ratio of 0.222 (compared to the largest of 1.05, se = 0.04).
-Also, the Copas selection model algorithm issued an error when optimizing the likelihood.
-\item meta.id = 182298 (6211, 1, 8, -): One very small study with 8 patients in each group and 0 event counts in both.
-The Copas selection model algorithm issued an error when optimizing the likelihood.
-\end{itemize}
-
-\textbf{Fisher's Z score}: The same issues as encountered for Pearson correlation coefficients (meta.id = 157083 and 159329).
-The variance of the z score $s_z^2$ can be calculated as:  $s_z^2 = \frac{1}{n-3}$, $n$ being the total sample size.
-Thus, studies that have total sample size $n \geq 3$ are discarded in the meta-analyses ($n$ = 72 studies).
-2 meta-analyses have then less than 10 studies left for pooling:
-\begin{itemize}
-\item meta.id = 10671: (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2), 7 studies left.
-\item meta.id = 43324: (1019, 1, 3, 2), 9 studies left.
-\end{itemize}
-
-\subsubsection{The Publication Bias Test and Adjustment Dataset}
-The dataset that was ultimately tested and adjusted for publication bias comprises 2673 meta-analyses and 42789 results. ..
+There has been cases where meta-analyses could not be analysed with Copas selection model because the likelihood function could not be optimized based on the settings.
+It was ommitted in this case.
+The analysis failed when using $z$-scores, but not standardized mean differences, and in that case, it was not ommitted.\\
+The specific information about the meta-analysis is: \texttt{meta.id} = 220949, \texttt{id} = ``CD009908'', \texttt{subgroup.id} = ``CMP-001.05.02''.
+
+\subsubsection{The Analysis Dataset}
+The dataset that was ultimately tested and adjusted for publication bias comprises 1 meta-analyses and 53012 results.
+The mean number of participants in the treatment group is 212.6072021 vs 256.7062871 in the unrestricted dataset and the mean total number of participants 465.5000189 vs 623.15692.
+The mean publication year is 2000.0251806 vs 2000.9710727 in the unrestricted dataset.
+\\
+From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}}), there are 1 with \texttt{outcome.measure.new} = ..., 1 ...,  1 ... and 2 ... .
+
+\subsection{Analysis Procedure}
+All compuations were performed in the \texttt{R} computing environment \citep{R.base}.
+The \texttt{R} packages \texttt{meta} \citep{meta.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments.
+The excess significance test was adapted from \citet{vanAert.2019}.
+For data manipulation procedures, the \texttt{tidyverse} packages were used \citep{tidyverse.package}, and for plotting the \texttt{ggplot2} package \citep{ggplot2}.\\
+The methods described in the methods chapter \ref{ch:methods} most often apply directly to the algorithms used in \texttt{meta} and \texttt{metafor}.
+For binary outcomes, log risk ratios were used as treatment effect estimates in the meta-analysis, and for continuous outcomes, Hedge's $g$.
+For the other outcomes, the \texttt{effect} and \texttt{se} as provided in the dataset was passed to \texttt{meta::metagen}.
+\\
+The effect sizes were transformed for adjustment in the way described in section \ref{sec:transformation.effectsizes}.
+The $p$-values for adjusted treatment effect estimates were calculated by the Wald method.
+\\
+In the case of the one-sided test procedure (small study effect and excess significance tests), the effect side in which bias was expected had to be prespecified.
+This was solved by comparing the number of significant findings on each side (original effect scale, i.e.
+for binary outcomes log risk ratios, \etc); the side with more significant findings (two-sided $p$-value < 0.05) was considered the side of potential bias.
+If numbers were equal, the side of the fixed effects treatment was used.
+\\
+Details to Copas selection model algorithm and its application can be found in \citet{limitmeta}.
+In short, two values for $a$ and $b$ in section \ref{sec:copas} were used; a limited range with $a$ between -1.7 and 2, and $b$ between 0.16 and 0.32 was applied first (analog to a most extreme selection process of $P$(select|small trial with sd = 0.4) = 0.1 and P(select|large trial w.
+sd  = 0.05) = 0.9).
+If the most extreme selection process is unable to pass the significance test of no small study effect ($p$-value > 0.1), then a wider range was applied ($a$  between -5.4 and 2 and $b$ between 0 and 0.32).
+If there is still no non-significant small study effect, the result was \texttt{NA}.
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-10-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-10-1}
 
@@
 There, there is no evidence for publication bias, and the histograms are even skewed to the left (Schwarzer).
-But note that the sample size of survival outcomes is small ($n$ = 39).
+But note that the sample size of survival outcomes is small ($n$ = 238).
 \\
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-11-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-11-1}
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-12-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-12-1}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Jul  5 16:13:26 2019
+% Fri Jul 12 20:14:43 2019
 \begin{table}[ht]
@@
   \hline
-0 & 68 \% & 64.3 \% \\ 
-  1 & 13.5 \% & 10 \% \\ 
-  2 & 7.5 \% & 6.9 \% \\ 
-  3 & 5.2 \% & 16.5 \% \\ 
-  4 & 4.9 \% & 2.3 \% \\ 
-  5 & 0.8 \% & - \\ 
+0 & 66.3 \% & 68.1 \% \\ 
+  1 & 13.7 \% & 11.8 \% \\ 
+  2 & 7.7 \% & 6.8 \% \\ 
+  3 & 6.2 \% & 11.4 \% \\ 
+  4 & 5.2 \% & 2 \% \\ 
+  5 & 0.9 \% & - \\ 
    \hline
@@
 \\
-When only looking at small study effect tests, 27.3\% of binary outcome tests and 34.4\% of survival and continuous outcome tests had at least one significant result.
-After applying the Bonferroni correction for multiple testing, this shrinks to 10.5\% for binary and 17.5\% for continuous and survival outcomes.
+When only looking at small study effect tests, 29.5\% of binary outcome tests and 29.5\% of survival and continuous outcome tests had at least one significant result.
+After applying the Bonferroni correction for multiple testing, this shrinks to 12.6\% for binary and 12.7\% for continuous and survival outcomes.
 \\
@@
 \section{Small Study Effects Adjustment}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in Math.data.frame(structure(list(meta.id = c(9957L, 12985L, 49559L, : non-numeric variable(s) in data frame: id}}\end{kframe}
+\end{knitrout}
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-15-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-15-1}
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-16-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-16-1}
 
@@
 The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 90 cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or 90 increased by -0.13, fixed effects reference).
-Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or 90 meta-analyses (or increased by 0.24).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 152 cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or 152 increased by -0.13, fixed effects reference).
+Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or 152 meta-analyses (or increased by 0.24).
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Jul  5 16:13:41 2019
+% Fri Jul 12 20:15:09 2019
 \begin{table}[ht]
@@
   \hline
-z: Fixed - Copas & -0.05 & -0.01 & -0.00 & 0.01 & 0.05 & -271.73 & 4.76 & 48.67 & 43.91 & 71.54 \\ 
-  z: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.04 & -263.62 & 71.65 & 89.42 & 17.77 & 71.54 \\ 
-  z: Fixed - Regression & -0.13 & -0.03 & 0.01 & 0.05 & 0.14 & 0.01 & 0.00 & 52.44 & 52.44 & 0.17 \\ 
-  z: Random - Regression & -0.15 & -0.03 & 0.02 & 0.07 & 0.18 & 0.02 & 0.00 & 57.64 & 57.64 & 0.17 \\ 
-  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.09 & 0.02 & 22.76 & 59.14 & 36.38 & 60.96 \\ 
-  g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.14 & 0.03 & 63.29 & 87.49 & 24.20 & 60.96 \\ 
-  g: Fixed - Regression & -0.23 & -0.04 & 0.03 & 0.13 & 0.38 & 0.05 & 0.00 & 61.96 & 61.96 & 0.00 \\ 
-  g: Random - Regression & -0.24 & -0.03 & 0.05 & 0.16 & 0.42 & 0.06 & 0.00 & 64.06 & 64.06 & 0.00 \\ 
-  Log h.r.: Fixed - Copas & -0.02 & 0.00 & 0.00 & 0.00 & 0.02 & -0.00 & 46.15 & 35.90 & 82.05 & 56.41 \\ 
-  Log h.r.: Random - Copas & -0.02 & 0.00 & 0.00 & 0.00 & 0.00 & -0.01 & 61.54 & 17.95 & 79.49 & 56.41 \\ 
-  Log h.r.: Fixed - Regression & -0.20 & -0.13 & -0.06 & 0.02 & 0.14 & -0.05 & 0.00 & 33.33 & 33.33 & 0.00 \\ 
-  Log h.r.: Random - Regression & -0.22 & -0.14 & -0.07 & 0.03 & 0.14 & -0.06 & 0.00 & 33.33 & 33.33 & 0.00 \\ 
+z: Fixed - Copas & -0.05 & -0.01 & -0.00 & 0.01 & 0.05 & -252.84 & 4.97 & 45.54 & 40.57 & 66.17 \\ 
+  z: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.05 & -100.49 & 66.75 & 84.18 & 17.42 & 66.17 \\ 
+  z: Fixed - Regression & -0.12 & -0.03 & 0.01 & 0.05 & 0.14 & 0.01 & 0.00 & 49.98 & 49.98 & 0.03 \\ 
+  z: Random - Regression & -0.14 & -0.03 & 0.02 & 0.07 & 0.17 & 0.02 & 0.00 & 55.15 & 55.15 & 0.03 \\ 
+  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.09 & 0.03 & 21.25 & 56.72 & 35.47 & 55.90 \\ 
+  g: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.15 & 0.04 & 58.03 & 82.15 & 24.13 & 55.90 \\ 
+  g: Fixed - Regression & -0.22 & -0.04 & 0.04 & 0.13 & 0.39 & 0.06 & 0.00 & 58.52 & 58.52 & 0.03 \\ 
+  g: Random - Regression & -0.22 & -0.03 & 0.05 & 0.16 & 0.42 & 0.07 & 0.00 & 60.31 & 60.31 & 0.03 \\ 
+  Log h.r.: Fixed - Copas & -0.14 & -0.00 & 0.00 & 0.00 & 0.11 & 0.16 & 31.51 & 35.29 & 66.81 & 57.98 \\ 
+  Log h.r.: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.13 & 0.22 & 63.45 & 23.53 & 86.97 & 57.98 \\ 
+  Log h.r.: Fixed - Regression & -0.39 & -0.08 & -0.00 & 0.07 & 0.97 & 0.27 & 0.00 & 47.90 & 47.90 & 0.00 \\ 
+  Log h.r.: Random - Regression & -0.41 & -0.08 & -0.01 & 0.08 & 1.44 & 0.33 & 0.00 & 48.32 & 48.32 & 0.00 \\ 
    \hline
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-18-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-18-1}
 
@@
 The Copas selection model also gives an estimate of the number of missing studies.
-It finds that 0 are missing, which corresponds to 0\% from all \ensuremath{2.8945\times 10^{4}} analysed studies.
+It finds that 0 are missing, which corresponds to 0\% from all \ensuremath{5.2733\times 10^{4}} analysed studies.
 Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
-Note that we have excluded 0 out of 1806, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
+Note that we have excluded 0 out of 3059, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-19-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-19-1}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Jul  5 16:13:42 2019
+% Fri Jul 12 20:15:10 2019
 \begin{table}[ht]
@@
   \hline
-Missing fraction & 323 & 0 & 0 & 0.1 & 0.3 & 1.0 & 0.2 \\ 
-  Missing study number & 323 & 0 & 0 & 1.4 & 5.2 & 17.9 & 4.2 \\ 
+Missing fraction & 576 & 0 & 0 & 0.1 & 0.3 & 0.9 & 0.2 \\ 
+  Missing study number & 576 & 0 & 0 & 1.2 & 5.3 & 17.9 & 4.4 \\ 
    \hline
@@
   \hline
-meta.id & file.nr & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
-  \hline
-2009 & 2009 & 1 & 1 & 0.31 & 0.36 & 0.31 & 0.43 & 0.70 & 0.70 & 0.70 & 2.48 \\ 
-  2068 & 2068 & 2 & 0 & 0.29 & 0.35 & 0.29 & 0.42 & 0.68 & 0.68 & 0.68 & 2.57 \\ 
-  52528 & 52528 & 1 & 0 & -0.75 & -0.69 & -0.50 & -0.26 & -1.19 & -1.53 & 0.18 & -0.52 \\ 
-  60546 & 60546 & 1 & 1 & 0.17 & 0.24 & 0.17 & 0.34 & 0.53 & 0.53 & 0.53 & 1.65 \\ 
-  70389 & 70389 & 1 & 1 & -0.08 & -0.07 & 15.62 & -0.04 & -0.13 & -0.13 & -0.13 & -0.05 \\ 
-  73769 & 73769 & 3 & 1 & -0.09 & 0.00 & 7148.96 & 0.02 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
-  79113 & 79113 & 2 & 0 & -0.38 & -0.38 & -0.38 & -0.48 & -0.93 & -0.93 & -2.00 & -3.47 \\ 
-  90138 & 90138 & 3 & 0 & 0.30 & 0.80 & 0.30 & 0.53 & 0.72 & 0.71 & 0.71 & 2.16 \\ 
-  97356 & 97356 & 2 & 0 & -0.06 & -0.33 & -0.06 & -0.11 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
-  98030 & 98030 & 1 & 0 & -0.09 & -0.07 & -0.09 & -0.04 & -0.41 & -0.41 & -1.50 & -2.79 \\ 
-  101436 & 101436 & 1 & 5 & 0.54 & 0.62 & 0.80 & 0.90 & 1.21 & 1.21 & 1.21 & 2.74 \\ 
-  118121 & 118121 & 4 & 1 & 0.25 & 0.23 & 47.73 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
-  119537 & 119537 & 3 & 0 & 0.07 & 0.15 & 0.07 & 0.29 & 0.50 & 0.50 & 1.43 & 1.81 \\ 
-  119818 & 119818 & 3 & 3 & -0.25 & -0.25 & -0.20 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
-  146301 & 146301 & 1 & 0 & 0.14 & 0.26 & 472149.03 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
+meta.id & id & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
+  \hline
+9957 & 9957 & 8 & 2 & 0.80 & 0.81 & 0.80 & 0.97 & 1.59 & 1.59 & 1.40 & 0.28 \\ 
+  12985 & 12985 & 3 & 1 & -0.24 & -0.05 & -0.12 & -0.16 & -0.08 & -0.26 & 33.85 & -0.03 \\ 
+  49559 & 49559 & 2 & 1 & -0.13 & -0.11 & -0.13 & 0.04 & -0.47 & -0.42 & -0.41 & -3.00 \\ 
+  71800 & 71800 & 7 & 1 & -0.08 & 0.05 & 56.48 & 0.27 & 0.09 & 0.07 & 0.60 & 1.15 \\ 
+  79309 & 79309 & 1 & 0 & -0.75 & -0.69 & -0.50 & -0.26 & -1.19 & -1.53 & 0.18 & -0.52 \\ 
+  90890 & 90890 & 1 & 1 & 0.17 & 0.24 & 0.17 & 0.34 & 0.53 & 0.53 & 0.53 & 1.65 \\ 
+  111673 & 111673 & 3 & 1 & -0.14 & 0.00 & 214760.42 & -0.04 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
+  132957 & 132957 & 1 & 1 & -0.26 & -0.14 & 77.99 & -0.12 & -0.25 & -0.33 & -0.16 & 0.08 \\ 
+  141198 & 141198 & 2 & 0 & -0.08 & -0.33 & -0.08 & -0.17 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
+  158380 & 158380 & 1 & 9 & -0.91 & -0.90 & -0.70 & -0.24 & -2.02 & -2.02 & -2.02 & -0.97 \\ 
+  158415 & 158415 & 1 & 6 & -0.71 & -0.70 & -0.71 & -0.38 & -1.28 & -1.34 & -0.21 & -0.35 \\ 
+  169175 & 169175 & 2 & 2 & 0.40 & 0.36 & 34.40 & 0.13 & 0.74 & 0.74 & 0.70 & 0.23 \\ 
+  171013 & 171013 & 4 & 1 & 0.25 & 0.23 & 71.80 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
+  172921 & 172921 & 3 & 0 & 0.07 & 0.15 & 0.07 & 0.29 & 0.50 & 0.50 & 1.43 & 1.81 \\ 
+  173202 & 173202 & 3 & 3 & -0.25 & -0.25 & -0.11 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
+  197677 & 197677 & 3 & 1 & -0.56 & -0.56 & -0.40 & -0.07 & -1.31 & -1.34 & 0.02 & -0.08 \\ 
+  206994 & 206994 & 1 & 0 & 0.14 & 0.26 & 498188.34 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
+  217028 & 217028 & 7 & 1 & 0.38 & 0.37 & 0.38 & 0.07 & 0.66 & 0.69 & -0.38 & 0.09 \\ 
+  217032 & 217032 & 8 & 1 & 0.38 & 0.38 & 0.38 & 0.10 & 0.69 & 0.71 & 20.28 & 0.12 \\ 
+  222624 & 222624 & 2 & 1 & -0.19 & -0.12 & 13.72 & -0.01 & -0.20 & -0.24 & 0.06 & 0.08 \\ 
+  222764 & 222764 & 1 & 0 & 0.33 & 0.34 & 0.33 & 0.25 & 0.50 & 0.52 & 0.20 & -0.49 \\ 
+  245139 & 245139 & 2 & 4 & -0.10 & -0.09 & -0.10 & -0.08 & -0.09 & -0.09 & 8.25 & -0.02 \\ 
+  247940 & 247940 & 10 & 0 & -0.16 & 0.03 & -0.16 & -0.07 & 0.05 & 0.05 & 2.81 & 0.11 \\ 
+  255734 & 255734 & 1 & 0 & -0.32 & -0.29 & -0.15 & -0.08 & -0.56 & -0.58 & 16.55 & -0.25 \\ 
    \hline
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-22-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-22-1}
 
@@
 
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Fri Jul 12 20:15:11 2019
+\begin{table}[ht]
+\centering
+\begingroup\scriptsize
+\begin{tabular}{lcc}
+  \hline
+ & Agreement (overall) & Agreement (significance) \\ 
+  \hline
+Excess significance, Schwarzer & 0.85 & 0.20 \\ 
+  Excess significance, Peter & 0.78 & 0.32 \\ 
+  Excess significance, Rucker & 0.78 & 0.39 \\ 
+  Excess significance, Harbord & 0.81 & 0.39 \\ 
+  Peter, Schwarzer & 0.84 & 0.62 \\ 
+  Schwarzer, Rucker & 0.84 & 0.71 \\ 
+  Schwarzer, Harbord & 0.88 & 0.74 \\ 
+  Rucker, Peter & 0.88 & 0.67 \\ 
+  Harbord, Peter & 0.87 & 0.59 \\ 
+  Excess significance, Egger & 0.75 & 0.55 \\ 
+  Excess significance, Thompson & 0.78 & 0.53 \\ 
+  Excess significance, Begg & 0.77 & 0.37 \\ 
+  Thompson, Egger & 0.94 & 0.93 \\ 
+  Thompson, Begg & 0.87 & 0.73 \\ 
+  Egger, Begg & 0.84 & 0.72 \\ 
+  Excess significance, Egger (survival) & 0.84 & 0.08 \\ 
+  Excess significance, Thompson (survival) & 0.86 & 0.09 \\ 
+  Excess significance, Begg (survival) & 0.86 & 0.09 \\ 
+  Thompson, Egger (survival) & 0.96 & 0.94 \\ 
+  Thompson, Begg (survival) & 0.88 & 0.56 \\ 
+  Egger, Begg (survival) & 0.87 & 0.59 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Overall proportion of agreement if significant or unsignificant, and for significance only.
+Horizontal lines separate binary, continuous and IV outcomes (order as in table).
+The reference significance test is the one with more significant results.}
+\label{test.agreement}
+\end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-07-12 report/chapter01.Rnw
Report based on the new data

@@
 
-Typically, we expect empirical scientific results to be distorted by random noise, such that the results are not equal to the real process that they describe.
+Studies get more attention and are more likely to be published, read and cited if they are implying large effects.
+Studies with no evidence for an effect are less likely to get published.
+This generates a bias called ``publication bias'', which distorts the view of the evidence for an effect.
+Recently, publication bias has been identified as one of the major concerns in irreproducible research \citep{Bishop.2019}.
+The issue has been pin-pointed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}).
+In medical research, clinical trials study the efficacy of therapies and drugs.
+The gold standard in such intervention studies are randomized, (placebo) controlled, trials (RCTs).
+Results from such clinical studies influence the treatment of patients in daily clinical practice.
+The results from multiple intervention studies are summarized in meta-analyses and reflect the overall evidence for a treatment effect.
+Summarized treatment effects and uncertainities should be more robust and reliable.
+Publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm.
+\\
+There is extensive literature on publication bias in meta-analyses, e.g. (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02}, 
+\citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}). 
+All authors agree in that the exclusion of unpublished results in meta-analyses is responsible for overestimation of treatment effects.
+Although there are policies that make it mandatory to make accessible all study results \citep{fda}, it is not clear if the situation has improved yet.\\
+The Cochrane Organisation has specialized on systematic reviews of healthcare interventions.
+Researchers that write a systematic review collect data across studies, review them and try to provide up-to-date information about specific treatment efficacies \citep{cochrane.handbook}.
+By extensive literature scrutinization, they try to circumvent the issue of publication bias.
+Earlier research however suggests that the efforts are only partially succesful, and that there still is publication bias within the reviews (\citet{Egger}, \citet{Ioannidis2007}, \citet{kicinsky}, \citet{vanAert.2019}).
+In this publications, the results of a part of the Cochrane Database of systematic reviews is analysed with small study effect tests or bayesian hierarchical selection models \citep{kicinsky}.
+They all find moderate to large evidence for publication bias in the Database.
+A more thorough discussion of their methods and results will follow in chapter \ref{ch:Discussion}.
+However, none of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods.
+Also, the results are often presented in the form of dichotomized hypothesis tests, a practice known to contribute to publication bias itself (cite sb).\\
+The aim of this thesis is to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides.
+At the end, an up-to-date estimate of the prevalence of publication bias in the data shall be given, as well as its implications regarding the effect sizes of the treatments.
+To achieve this, methods to detect and adjust for publication bias in meta-analysis are applied on the data.
+
+Already in 1978, scientists raised concern that effect sizes could be overestimated systematically if journals were ``not willing to drop their policy to use statistical significance as one of their criteria for publication'' \citep{dunlap1978}.
+Scientific findings get more attention and are more likely to be published, read and cited if they are implying large effects.
+The issue has been pin-pointed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}).
+The concern is that overestimated efficacy of the treatments could lead to harm to patients.
+\\
+A measure to counter the presence of single, overestimated study results is a meta-analysis \citep{metaanalysis}, a practice originally developped in psychology.
+Summarized treatment effects and uncertainities should be more robust and reliable.
+The pitfall is that when the entire body of evidence is again a biased sample of studies with high effects, the estimate is again overestimating the true effect.
+% 
+% 
+% Also after the introduction of mandatory registration of clinical trials
+% 
+% 
+% 
+% Typically, we expect empirical scientific results to be distorted by random noise, such that the results are not equal to the real process that they describe.
 Additionally, one can reasonably assume that the results are also biased to some extent, as the statistical paradigm of precision versus bias would predict: The smaller the noise part of distortion, the more the result should be distorted by bias.

### 2019-07-12 report/chapter03.Rnw
Report based on the new data

@@
 
-<<echo = FALSE, warning=FALSE, message=FALSE>>=
+<<echo = FALSE, warning=FALSE, message=FALSE, cache = TRUE>>=
 rm(list = ls())
@@
 PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2018-06-09.csv'
+FILE = 'cochrane_2019-07-04.csv'
 PATH_DATA = file.path(PATH, 'data')
 PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results')
+PATH_RESULTS = file.path(PATH2, 'results_new')
 PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
@@
 } else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
+	data = pb.readData2(path = PATH_DATA, file = FILE)
 	tmp = pb.clean(data)
@@
 
-load(file.path(PATH_RESULTS, "meta_analyses_summary_bin_cont_surv.RData"))
 load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
@@
 load(file.path(PATH_RESULTS, "meta.cont.RData"))
-load(file.path(PATH_RESULTS, "meta.surv.RData"))
+load(file.path(PATH_RESULTS, "meta.iv.RData"))
 load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+load(file.path(PATH_RESULTS, "meta_id_I2.RData"))
 
@@
 #Barbiturate Examples
-barbi1 <- arrange(filter(data, file.nr == 21) %>% 
-          select(Study = study.name, Comparison = comparison.name, Outcome = outcome.name, 
-                 Events = events1, Total = total1, Events_c = events2, Total_c = total2) %>% 
+barbi1 <- arrange(filter(data, id == "CD000033") %>% 
+          select(study.name, comparison.name, outcome.name, 
+                 events1, total1, events2, total2) %>% 
             slice(c(1,3)), Study) 
-barbi2 <- arrange(filter(data, file.nr == 21) %>% 
+barbi2 <- arrange(filter(data, id == "CD000033") %>% 
           select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study)
 barbi2[barbi2$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
+#----------------------------------------------------------------------------------------------#
 
 #Missing values
-cont.out <- data %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
-                                 outcome.measure.new == "Hedges' G")
+cont.out <- data %>% filter(outcome.flag == "CONT")
 
-missing.mean <- which(is.na(cont.out$mean1) | is.na(cont.out$mean2))
-missing.effect <- which(is.na(cont.out$effect))
-missing.means <- intersect(missing.mean, missing.effect) #Cont. results that have neither complete means nor an effect
-wrong.effect <- which(cont.out$mean1 == 0 & cont.out$mean2 == 0 & cont.out$effect == 0) #Cont.results that have only zeros
-missing.effects <- length(c(missing.means, wrong.effect))
+zero.effect.cont <- which(cont.out$mean1 == 0 & cont.out$mean2 == 0 & cont.out$effect == 0) #Cont.results that have only zeros
+zero.sds.cont <- which(cont.out$sd1 == 0 & cont.out$sd2 == 0 & cont.out$se == 0) #Cont.results that have only zeros
+zero.both.cont <- intersect(zero.effect.cont, zero.sds.cont)
+zero.counts.cont <- length(zero.both.cont)
 
-missing.sd <- which(is.na(cont.out$sd1) | is.na(cont.out$sd2))
-missing.se <- which(is.na(cont.out$se))
-missing.sds <- intersect(missing.se, missing.sd) #Cont. results that have neither complete means nor an effect
-wrong.sds <- which(cont.out$sd1 == 0 & cont.out$sd2 == 0 & cont.out$se == 0) #Cont.results that have only zeros
-missing.sds <- length(c(missing.sds, wrong.sds))
+missing.arm <- which(data$total1 == 0 | data$total2 == 0) #One arm without patients..
+missing.arm.count <- length(missing.arm)
 
-missing.ss <- which(is.na(data$total1) | is.na(data$total2))
-wrong.ss <- which(data$total1 <= 0 | data$total2 <= 0)
-missing.ssize <- length(c(missing.ss, wrong.ss))
+missing.year.count <- sum(is.na(data$study.year)) + length(c(which(data$study.year < 1920), which(data$study.year > 2019)))
 
-missing.year <- sum(is.na(data$study.year)) + length(c(which(data$study.year < 1920), which(data$study.year > 2019)))
-
-missing.table <- rbind("Missing mean values and mean differences" = missing.effects,
-                         "Missing standard deviations and standard errors" = missing.sds,
-                         "Missing sample sizes" = missing.ssize,
-                         "Missing study year" = missing.year)
+missing.table <- rbind("Neither means nor standard deviations (CONT)" = zero.counts.cont,
+                         "Zero participants in one group" = missing.arm.count,
+                         "Missing study publication year" = missing.year.count)
+#----------------------------------------------------------------------------------------------#
 
 #Mean and median number of different outcome types of reviews
-mean.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
-  ungroup() %>% group_by(file.nr) %>%
+mean.diff.out <- data %>% group_by(id, comparison.nr) %>% distinct(outcome.name) %>%
+  ungroup() %>% group_by(id) %>%
   count() %>% ungroup %>% summarise(mean = mean(n))
 
-median.diff.out <- data %>% group_by(file.nr, comparison.nr) %>% distinct(outcome.name) %>%
-  ungroup() %>% group_by(file.nr) %>%
+median.diff.out <- data %>% group_by(id, comparison.nr) %>% distinct(outcome.name) %>%
+  ungroup() %>% group_by(id) %>%
   count() %>% ungroup %>% summarise(mean = median(n))
+#----------------------------------------------------------------------------------------------#
 
@@
                             round(mean(data.ext2$study.year, na.rm = T), 2), quantile(data.ext2$study.year, 0.95, na.rm = T))
+publication.year.2018 <- data.ext2 %>% filter(study.year == 2018) %>% count
+publication.year.2019 <- data.ext2 %>% filter(study.year == 2019) %>% count
+#----------------------------------------------------------------------------------------------#
 
@@
 outcome.measure.frequencies$Percentage <- paste(outcome.measure.frequencies$Percentage, "%", sep = "")
+#----------------------------------------------------------------------------------------------#
 
@@
                       round(mean(data.ext2$total1, na.rm = T), 2), quantile(data.ext2$total1, 0.95, na.rm = T))
+#----------------------------------------------------------------------------------------------#
 
 #Frequencies of results:
-comp.freq <- data %>% group_by(file.nr) %>% summarise(n = n())
+comp.freq <- data %>% group_by(id) %>% summarise(n = n())
 comp.range <- c(length(which(comp.freq$n < 6)), quantile(comp.freq$n, 0.25, na.rm = T), 
                       quantile(comp.freq$n, 0.5, na.rm = T), quantile(comp.freq$n, 0.75, na.rm = T),
-                      round(mean(comp.freq$n, na.rm = T), 2), quantile(comp.freq$n, 0.95, na.rm = T))
+                      round(mean(comp.freq$n, na.rm = T), 2), quantile(comp.freq$n, 0.95, na.rm = T),
+                quantile(comp.freq$n, 0.05, na.rm = T))
+#----------------------------------------------------------------------------------------------#
 
 #Frequencies of studies:
-study.freq <- data %>% group_by(file.nr) %>% distinct(study.name) %>% count()
+study.freq <- data %>% group_by(id) %>% distinct(study.name) %>% count()
 study.range <- c(length(which(study.freq$n < 3)), quantile(study.freq$n, 0.25, na.rm = T), 
@@
                       round(mean(study.freq$n, na.rm = T), 2), quantile(study.freq$n, 0.95, na.rm = T))
+#----------------------------------------------------------------------------------------------#
 
 #Pooling studies
-cum.repr.trials.subg <- data %>% group_by(file.nr, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
+cum.repr.trials.subg <- data %>% group_by(id, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% count %>%
   filter(n < 15) %>%
-  full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
+  full_join( data %>% group_by(id, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
-# cum.repr.trials.nosub <- data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
-#   filter(n < 15) %>%
-#   full_join( data %>% group_by(file.nr, comparison.nr, outcome.nr) %>% count %>% group_by(n) %>% count %>%
-#                filter(n > 14) %>% ungroup %>% summarise(n = 15, nn = sum(nn))) %>% 
-#   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
-
-# cum.repr.trials <- cbind(cum.repr.trials.nosub, cum.repr.trials.subg)[,c(1,3,6)]
 
 colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
-
-	data <- data %>% mutate(
-		outcome.type = ifelse(outcome.measure.new == "Hazard Ratio", "surv", 
-													ifelse(outcome.measure.new == "Odds Ratio" | outcome.measure.new == "Risk Ratio" |
-																 	outcome.measure.new == "Peto Odds Ratio" | outcome.measure.new == "Risk Difference", "bin", "cont")),
-		outcome.type = ifelse(outcome.measure.new == "Rate Ratio" | outcome.measure.new == "Rate difference", "rate", outcome.type),
-		lrr = NA,
-		var.lrr = NA,
-		smd = NA,
-		var.smd = NA,
-		smd.pbit = NA,
-		var.smd.pbit = NA,
-		smd.ordl = NA,
-		var.smd.ordl = NA,
-		cor.phi = NA,
-		var.cor.phi = NA,
-		pval.single = NA, 
-		cor.pearson = NA,
-		var.cor.pearson = NA,
-		z = NA,
-		var.z = NA,
-		events1c = NA,
-		events2c = NA,
-		sig.single = NA)
-	cont.ind <- which(data$outcome.type == "cont" & !is.na(data$outcome.type))
-
-	data[cont.ind, "outcome.type"] <- data[cont.ind, ] %>% 
-		mutate(outcome.type = ifelse(outcome.measure.new == "Std. Mean Difference"  | outcome.measure.new == "Mean Difference", 
-																 outcome.type, NA)) %>% select(outcome.type)
-
-	cont.ind <- which(data$outcome.type == "cont" & !is.na(data$outcome.type))
-
-	nomean1.ind <- which(data$outcome.type == "cont" & is.na(data$mean1))
-	nomean2.ind <- which(data$outcome.type == "cont" & is.na(data$mean2))
-	noeffects.ind <- which(data$outcome.type == "cont" & !is.na(data$effect))
-	nomeans.ind <- intersect(nomean1.ind, nomean2.ind)
-	nomeans.ind <- intersect(noeffects.ind, nomeans.ind) #no means, but a (std.) mean difference is provided.
-
-	data[nomeans.ind,"mean1"] <- data[nomeans.ind,"effect"]
-	data[nomeans.ind,"mean2"] <- 0
-
-	data[cont.ind,] <- escalc(data = data[cont.ind,], m1i = mean1, m2i = mean2, 
-														sd1i = sd1, sd2i = sd2, n1i = total1, n2i = total2,
-														measure = "SMD" , append = T, var.names = c("smd", "var.smd"))
-
-	inpute.given.ind <- which(is.na(data[cont.ind, "smd"]) & data[cont.ind, "outcome.measure.new"] == "Std. Mean Difference")
+#----------------------------------------------------------------------------------------------#
 
 	#Counts of meta-analyses with only zeros:
-all.zero.events.number <- data.ext2 %>% filter(outcome.type == "bin") %>% 
+both.arms.zero.events.count <- data.ext2 %>% filter(outcome.flag == "DICH") %>% 
   group_by(meta.id) %>% 
@@
   distinct(meta.id) %>% ungroup() %>%  count()
+#----------------------------------------------------------------------------------------------#
 
-#Counts of meta-analyses with means and sds only zeros:
-all.zero.means.number <- data.ext2 %>% filter(outcome.type == "cont") %>% group_by(meta.id) %>% 
-    mutate(n = n()) %>% filter(n >= 10) %>% filter(all(mean1 == 0) & all(mean2 == 0)) %>% 
-    filter(all(sd1 == 0) | all(sd2 == 0)) %>% distinct(meta.id) %>% ungroup() %>% count()
+#Inital dataset properties:
+initial.id.count <- length(unique(data$id))
+initial.study.count <- length(unique(data$study.name))
+initial.result.count <- dim(data)[1]
+
+#outcome.flag reduction:
+tp <- data %>% filter(outcome.flag == "DICH" | outcome.flag == "CONT" | outcome.flag == "IV")
+flag.id.count <- length(unique(tp$id))
+flag.study.count <- length(unique(tp$study.name))
+flag.result.count <- dim(tp)[1]
+
+#----------------------------------------------------------------------------------------------#
 
 #Counts of meta-analyses with n larger ten:
-m.a.largerten.number <- meta %>% filter(k > 9) %>% ungroup %>% count()
+m.a.largerten.bin <- data.ext2 %>% filter(outcome.flag == "DICH") %>% 
+  filter(total1 != 0 & total2 != 0) %>% 
+  group_by(meta.id) %>% filter(n() > 9) %>%  filter(any(events1 != 0) | any(events2 != 0)) %>% 
+  distinct(meta.id) %>% ungroup() %>% mutate(n = n())
+
+m.a.largerten.cont <- data.ext2 %>% filter(outcome.flag == "CONT") %>% 
+  filter(sd1 != 0 & sd2 != 0) %>% 
+  filter(total1 > 0 & total2 > 0) %>% group_by(meta.id) %>% 
+  filter(n() > 9) %>% distinct(meta.id) %>% ungroup() %>% mutate(n = n())
+
+m.a.largerten.iv <- data.ext2 %>% filter(outcome.flag == "IV") %>% 
+  filter(se != 0) %>% group_by(meta.id) %>% filter(n() > 9) %>% 
+  distinct(meta.id) %>% ungroup() %>% mutate(n = n())
+
+m.a.largerten.id <- rbind(m.a.largerten.bin, m.a.largerten.cont, m.a.largerten.iv)
+tp2 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id)
+
+ten.id.count <- length(unique(tp2$id))
+ten.study.count <- length(unique(tp2$study.name))
+ten.result.count <- dim(tp2)[1]
+m.a.largerten.count <- unique(m.a.largerten.bin$n) + unique(m.a.largerten.cont$n) + unique(m.a.largerten.iv$n)
+
+#----------------------------------------------------------------------------------------------#
+
+#variance ratio > 4:
+m.a.variance4.count <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
+  group_by(meta.id) %>% summarise(ratio = (max(se.new)^2)/(min(se.new)^2)) %>% 
+  filter(ratio >= 4) %>% count
+tp3 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
+  group_by(meta.id) %>% mutate(ratio = (max(se.new)^2)/(min(se.new)^2)) %>% 
+  filter(ratio >= 4)
+var.id.count <- length(unique(tp3$id))
+var.study.count <- length(unique(tp3$study.name))
+var.result.count <- dim(tp3)[1]
+
+#At least on sig. estimate:
+m.a.one.sig.count <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
+  group_by(meta.id) %>% summarise(ratio = (max(se.new)^2)/(min(se.new)^2),
+                                  n.sig = sum(sig.single)) %>% 
+  filter(ratio >= 4 & n.sig > 0) %>% count
+tp4 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
+  group_by(meta.id) %>% mutate(ratio = (max(se.new)^2)/(min(se.new)^2),
+                                  n.sig = sum(sig.single)) %>% 
+  filter(ratio >= 4 & n.sig > 0)
+sig.id.count <- length(unique(tp4$id))
+sig.study.count <- length(unique(tp4$study.name))
+sig.result.count <- dim(tp4)[1]
+
+#Without duplicates:
+m.a.no.dupl.number <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
+  group_by(meta.id) %>% summarise(ratio = (max(se.new)^2)/(min(se.new)^2),
+                                  n.sig = sum(sig.single),
+                                  dupl = unique(dupl.remove)) %>% 
+  filter(ratio >= 4 & n.sig > 0 & dupl == 0) %>% count
+tp5 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
+  group_by(meta.id) %>% mutate(ratio = (max(se.new)^2)/(min(se.new)^2),
+                                  n.sig = sum(sig.single),
+                                  dupl = unique(dupl.remove)) %>% 
+  filter(ratio >= 4 & n.sig > 0 & dupl == 0)
+dupl.id.count <- length(unique(tp5$id))
+dupl.study.count <- length(unique(tp5$study.name))
+dupl.result.count <- dim(tp5)[1]
+
 #smaller I2 than 0.5:
-m.a.smaller.5.number <- meta %>% filter(k > 9 & I2 < 0.5) %>% ungroup %>% count()
-#variance ratio > 4:
-m.a.variance4.number <- meta %>% filter(k > 9 & I2 < 0.5) %>% filter((se.max^2)/(se.min^2) > 4) %>% ungroup %>% count()
-#At least on sig. estimate:
-m.a.one.sig.number <- meta %>% filter(k > 9 & I2 < 0.5) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(n.sig.single > 0) %>% ungroup %>% count()
-#Single patient meta-analyses:
-tmp <- data.ext2 %>% filter(outcome.type == "cont") %>% group_by(meta.id) %>% 
-	mutate(n = n()) %>% filter(n >= 10) %>% filter(!all(mean1 == 0) & !all(mean2 == 0)) %>% 
-	filter(!all(sd1 == 0) | !all(sd2 == 0))
+m.a.smaller.5.count <- meta.info.I2 %>% filter(I2 < 0.5) %>% ungroup %>% count()
 
-meta.id.vector <- unique(tmp$meta.id)
-m.a.singlepatient.number <- length(meta.id.vector[c(which(meta.id.vector > 42716 & meta.id.vector < 42725))] )
+meta.id.vector <- meta.info.I2 %>% filter(I2 < 0.5) %>% select(meta.id)
+meta.data <- data.ext2 %>% filter(meta.id %in% meta.id.vector$meta.id)
+
+I2.id.count <- length(unique(meta.data$id))
+I2.study.count <- length(unique(meta.data$study.name))
+I2.result.count <- dim(meta.data)[1]
+#----------------------------------------------------------------------------------------------#
+
+#Adjustment dataset:
+meta.adj <- meta.f %>% filter(outcome.flag == "DICH" | outcome.flag == "CONT")
+tp6 <- data.ext2 %>% filter(meta.id %in% meta.adj$meta.id)
+#----------------------------------------------------------------------------------------------#
+
+#Adjustment dataset:
+meta.adj <- meta.f %>% filter(outcome.flag == "DICH" | outcome.flag == "CONT")
+tp6 <- data.ext2 %>% filter(meta.id %in% meta.adj$meta.id)
+
+adj.id.count <- length(unique(tp6$id))
+adj.study.count <- length(unique(tp6$study.name))
+adj.result.count <- dim(tp6)[1]
+#----------------------------------------------------------------------------------------------#
+
 #How many z-score meta-analyses are excluded due to total <= 3, and how many m.a. have then n < 10:
-tmp <- data.ext2 %>% group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 9) %>%
-	filter(outcome.type != "rate" & !is.na(outcome.type))
+# meta.id.vector <- meta.info.I2 %>% filter(I2 < 0.5) %>% select(meta.id)
+# tmp <- data.ext2 %>% filter(meta.id %in% meta.id.vector) %>% filter(outcome.flag != "IV")
+# 
+# meta.id.vector.z <- unique(tmp$meta.id)
+# tobe.excluded.z <- c(which(meta.id.vector.z == 220949))
+# meta.id.vector.z <- meta.id.vector.z[-tobe.excluded.z]
+# 
+# tmp <- tmp %>% filter(meta.id %in% meta.id.vector.z)
+# z.seq3.count <- tmp %>% filter(total1 + total2 < 4) %>% ungroup() %>% count() 
+# m.a.seq3.seq10.number <- tmp %>% filter(total1 + total2 > 3) %>% count() %>% 
+#   filter(nn < 10) %>% ungroup %>% count()
 
-metac <- meta %>% filter(k > 9) %>% filter(n.sig.single > 0) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
-
-meta.id.vector <- metac$meta.id[-which(metac$outcome.type == "surv")]
-meta.id.vector <- meta.id.vector[-c(which(meta.id.vector == 157083),
-																which(meta.id.vector == 159329),
-																# which(meta.id.vector == 12459),
-																# which(meta.id.vector == 12465),
-																# which(meta.id.vector == 22087),
-																which(meta.id.vector == 182298))]
-
-meta.data.zscore <- tmp[which(tmp$meta.id %in% meta.id.vector),]
-total.seq3.number <- meta.data.zscore %>% filter(total1 + total2 < 4) %>% select(var.z) %>% ungroup() %>% count() 
-m.a.seq3.seq10.number <- meta.data.zscore %>% filter(total1 + total2 > 3) %>% count() %>% filter(nn < 10) %>% ungroup %>% count()
-
-meta.id.vector <- metac$meta.id
-meta.data <- data.ext2[which(data.ext2$meta.id %in% meta.id.vector),]
+#----------------------------------------------------------------------------------------------#
+# "IV" outcome.flag meta-analyses
+dt <- meta.iv %>% group_by(outcome.measure.new) %>% count
+first.iv.outcome.count <- dt$n[1]
+second.iv.outcome.count <- dt$n[2]
+third.iv.outcome.count <- dt$n[3]
+fourth.iv.outcome.count <- dt$n[4]
 
@@
 \subsection{Structure and Content}
-The dataset consists of \Sexpr{length(unique(data$file.nr))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(data$study.name))} studies and \Sexpr{dim(data)[1]} results.
-A result compares a clinical or medical intervention or treatments to a control.
-Each study provides (multiple) results of clinical interventions.
-\\
-In Table \ref{barbiturate.row}, two results from a systematic review about effects of barbiturates are shown as they are given in the dataset.
+The dataset consists of \Sexpr{length(unique(data$id))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(data$study.name))} studies and \Sexpr{dim(data)[1]} results.
+The results all stem from comparisons of a healthcare interventions or treatments to a reference.
+The reference may be a placebo control group or a other intervention or treatment.
+A result can not only be about efficacy of the treatments, but also about safety (adverse effects).\\
+In Table \ref{barbiturate.row}, two results from a systematic review about barbiturates are shown as they are given in the dataset.
 As can be seen, further specifications are provided by the variables in the columns.
 \\
-The comparison variable specifies \textit{what kind} of treatments or interventions are compared, the outcome variable \textit{how} it is compared, and the subgroup variable (not indicated in table) if the result belongs to a certain subgroup.
-Here, the result is of a binary type, so the counts of events in the barbiturate treatment group and the total number of participants are given in columns ``Events'' and ``Total'' and the number of events in the control group ``Events\_c'' and participants ``Total\_c''.
-A event is here death at the end of follow up.
+The \texttt{comparison.name} variable specifies \textit{what kind} of treatments or interventions are compared, the \texttt{outcome.name} variable \textit{how} it is compared, and the \texttt{subgroup.name} variable (not indicated in table) \textit{if and to what experimental subgroup} the result belongs.
+\\
+The result is of a binary type, and the counts of events in the treatment group are in \texttt{events1} and of the control group in \texttt{events2} and the total number of participants are given in columns \texttt{total1} and \texttt{total2}.
+As can be seen, events denote here "death at the end of follow-up".
 
@@
 A complete listing of the variables of a result is given in Table \ref{variable}.
-They can roughly be separated into variables that \textit{specify the review} in which the result is contained and variables that \textit{specify the result} itself (separated by a horizontal line in Table \ref{variable}):
+Depending on the type of the data, \eg if it is binary or continuous, some variables are missing for the specific results.
 
@@
 Information about missing values in the dataset is given in Table \ref{missing}.
-For variables as research subject, outcome and subgroup name and event counts there are no missing values.
-The relative amount of missing values is very low except for study years.
-For continuous outcomes, the cases have been counted were no treatment effect and standard error is available: neither mean values and standard deviations, nor mean differences and standard error.
-Also Study years before 1920 and after 2019 are declared as missing, as well as sample sizes below zero.
+The relative amount of missing values is low, except for study years.
+For continuous outcomes, the cases are counted were neither a mean difference nor means are available.
+Similarly, the counts of cases where neither standard errors nor standard deviations are available are provided.
+Study years before 1920 and after 2019 are declared as missing, as well as sample sizes equal to zero.
 
@@
 The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{publication.year.range[5]} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}.
-Only a handful ($n = 18$) have been published in 2018, none in 2019.
+\Sexpr{publication.year.2018} studies have been published in 2018, none in 2019.
 \\
-%No information is available concerning unpublished results and studies.
 The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}.
-One can conclude of the table that roughly 30 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (> 65\%).
+One can conclude of the table that roughly 31 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (more than 65\%).
 
@@
 The sample sizes among results vary to some extent.
-There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, the 5\% quantile and 95\% smaller than \Sexpr{treatment.group.size.range[6]}.
+There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, 95\% smaller than \Sexpr{treatment.group.size.range[6]}.
 The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{treatment.group.size.range[5]} and the third quartile \Sexpr{treatment.group.size.range[4]}.
@@
 \\
-The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}.
-There are \Sexpr{comp.range[1]} reviews with five or fewer results, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}.
+There are \Sexpr{comp.range[1]} reviews with five or fewer results.
+The 5\% and 95\% quantiles are \Sexpr{comp.range[7]} and \Sexpr{comp.range[6]}.
+The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}.
 Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]} and the 95\% quantile \Sexpr{study.range[6]}.
-The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in \citet{largest.review} which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1497 results in total.\\
+The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citet{largest.review}
+which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1,497 results in total.\\
 For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome.
-More specifically, the studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis, since their research subject and experimental setup can be considered sufficiently homogeneous.
-Importantly, this distinction is also used by the Cochrane Organization itself, i.e.
-the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
-The dataset is divided in meta-analyses with identical experimental setup. The size of a meta-analysis denotes how many results are included in a group.
-Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results. Practically, this number of meta analyses can be performed, with each having at least $n$ results.
+The studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis.
+This distinction is also used by the Cochrane Organization itself, \ie the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
+The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.
 
 <<echo=FALSE, results='asis'>>=
-
-print(xtable(cum.repr.trials.subg, label = "repr.groups", caption = "Cumulative number of groups with number of reproduction trials $\\geq$ n", align = "llrr", digits = 0), include.rownames = F, size = "footnotesize")
+rownames(cum.repr.trials.subg)[15] <- "$\\geq$ 15"
+print(xtable(cum.repr.trials.subg, label = "repr.groups", caption = "Number and cumulative number of groups with meta-analysis size n.", align = "llrr", digits = 0), include.rownames = F, size = "footnotesize")
 @
@@
 \section{Data Tidying and Processing} \label{sec:Processing}
-The original dataset was provided by .. (some words how the dataset was obtained and processed by C.R.). \\
-The information in the previous pages are from a tidied and processed version of this dataset. \\
-
-\subsection{Modification of old variables}
-In some cases, reasonable assumptions led to small changes in the originally provided variables:
-\begin{itemize}
-\item \texttt{study.year}: It was assumed that studies that are declared to have been published before 1920 ($n$ = \Sexpr{length(which(data$study.year < 1920))}) are mis-specified, as well as after 2019 ($n$ = \Sexpr{length(which(data$study.year > 2019))}), so these have been set to NA.
-\item \texttt{mean1} and \texttt{mean2}: When both \texttt{mean1} and \texttt{mean2} are equal to zero or NA, \texttt{outcome.measure.new} is equal to \texttt{(Std.) Mean Difference}, but a mean difference is given in \texttt{effect}, \texttt{mean1} is set equal to \texttt{effect} ($n$ = \Sexpr{length(nomeans.ind)}).
-\end{itemize}
+The dataset was scraped from the Cochrane Database of Systematic Reviews at the ... . A specialized code was used to convert the xtml. files from the webpage into the data at hand cite... .
 
@@
 ``surv'' equal to ``Hazard Ratio'' and ``rate'' equal to ''Rate Ratio'' or ``Rate Difference''.
-\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.type ``bin''.
-\item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.type ``cont''.
-If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.new} was equal to ``Std.
+\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.flag ``bin''.
+\item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.flag ``cont''. 
+% If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.new} was equal to ``Std.
 Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  \Sexpr{length(inpute.given.ind)}).
-\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.type ``bin''.
-\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.type ``bin'') or $g$ (for outcome.type ``cont'') to $r$ transformation.
+\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.flag ``bin''.
+\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.flag ``bin'') or $g$ (for outcome.flag ``cont'') to $r$ transformation.
 \item \texttt{z} and \texttt{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
-\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.type ``cont'' or Wald test for outcome.type ``bin''.
+\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.flag ``cont'' or Wald test for outcome.flag ``bin''.
 \item \texttt{events1c} and \texttt{events2c}: Correction of \texttt{events1} and \texttt{events2} zero event counts or event counts = patient number.
@@
 \subsection{Eligibility criteria for Publication Bias Test and Adjustment}
-Initially, the analysis is restricted to binary, continuous and survival outcomes. More formally:
+
+Initially, the analysis is restricted to results with \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}.
+binary, continuous and survival outcomes.
+This corresponds to \Sexpr{length(data.ext2$outcome.flag[which(data.ext2$outcome.flag == "DICH" | data.ext2$outcome.flag == "CONT" | data.ext2$outcome.flag == "IV")])} out of a total of \Sexpr{length(data.ext2$outcome.flag)} results.
+\citet{Ioannidis2007} outlined criteria for application of small study effect tests:
 \begin{itemize}
-\item \textbf{Outcome measures}: The analysis has been restricted on the following outcome measures (from \texttt{outcome.measure.new}): ``Odds Ratio'', ``Risk Ratio'', ``Risk difference'', ``Peto Odds Ratio'', ``Std.
-Mean Difference'', ``Mean Difference'', ``Hazard Ratio''
-($n$ = \Sexpr{length(data.ext2$outcome.type[which(data.ext2$outcome.type == "bin" | data.ext2$outcome.type == "cont" | data.ext2$outcome.type == "surv")])} out of a total of \Sexpr{length(data.ext2$outcome.type)} results)
+\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = \Sexpr{m.a.largerten.count} remaining). 
+\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = \Sexpr{m.a.variance4.count} remaining).
+\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = \Sexpr{m.a.one.sig.count} remaining)
+\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = \Sexpr{m.a.smaller.5.count} remaining).
 \end{itemize}
-
-The suggestions of criteria for eligibility for publication bias tests of \citet{Ioannidis2007} have largely been followed:
-\begin{itemize}
-\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = \Sexpr{m.a.largerten.number} remaining). 
-\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = \Sexpr{m.a.smaller.5.number} remaining).
-\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = \Sexpr{m.a.variance4.number} remaining).
-\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = \Sexpr{m.a.one.sig.number} remaining)
-\end{itemize}
-
-After having excluded meta-analyses with less than ten studies, additional criteria for excluding inconvenient meta-analyses are:
+Additionally, the following criteria have been applied:
 \begin{itemize}
@@
 The intention is to exclude sensitivity analyses which are operated on subsets of the available results.
-\item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = \Sexpr{all.zero.events.number} out of meta-analyses with at least ten studies).
-\item \textbf{Missing means and sd's}: In the case of continuous outcomes, meta-analyses with means and sd's in any group being equal to zero are excluded ($n$ = \Sexpr{all.zero.means.number} out of meta-analyses with at least ten studies).
-\item \textbf{Single patient data}: Meta-analyses that are comprised of single patient data are excluded ($n$ = \Sexpr{m.a.singlepatient.number} out of meta-analyses with at least ten studies)
+\item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = \Sexpr{both.arms.zero.events.count} out of meta-analyses with at least ten studies).
 \end{itemize}
 
---Make Flowchart--
+The results of this reduction of the dataset are shown in the flow-chart in Figure \ref{Inclusion.criteria}. By applying the criteria, we are only able to analyse a subset of the original data. \\
+Only the data that had accesible all results data available was used for adjustment.
+Thus, all meta-analyses with \texttt{outcome.flag} == \texttt{IV} are ommitted in a second step of the analysis (Analysis dataset (1) and (2) in Figure \ref{Inclusion.criteria}).
+
+\begin{figure}
+\begin{center}
+\tikzstyle{block} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=2.5em]
+\tikzstyle{btw} = [rectangle, node distance=0cm, minimum height =2em, fill= white]
+\tikzstyle{ublock} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=4em, text width = 10em]
+\tikzstyle{line} = [draw, -latex']
+\tikzstyle{final} = [rectangle, draw, fill=red!20, text centered, rounded corners, minimum height=2.8em]
+
+\begin{tikzpicture}[node distance = 2cm, auto]
+    % Place nodes
+        \node [final] (1) {Inital dataset: 
+    \Sexpr{format(initial.id.count, big.mark = ",")} reviews,
+    \Sexpr{format(initial.study.count, big.mark = ",")} studies,
+    \Sexpr{format(initial.result.count, big.mark = ",")} results};
+
+    \node [block, below of=1, node distance=2.2cm] (2) {
+    \Sexpr{format(flag.id.count, big.mark = ",")} reviews,
+    \Sexpr{format(flag.study.count, big.mark = ",")} studies,
+    \Sexpr{format(flag.result.count, big.mark = ",")} results};
+
+    \node [block, below of=2, node distance=2.2cm] (3) {
+    \Sexpr{format(ten.id.count, big.mark = ",")} reviews,
+    \Sexpr{format(ten.study.count, big.mark = ",")} studies,
+    \Sexpr{format(ten.result.count, big.mark = ",")} results,
+    \Sexpr{format(m.a.largerten.count, big.mark = ",")} meta-analyses};
+
+    \node [block, below of=3, node distance=2.2cm] (4) {
+    \Sexpr{format(var.id.count, big.mark = ",")} reviews,
+    \Sexpr{format(var.study.count, big.mark = ",")} studies,
+    \Sexpr{format(var.result.count, big.mark = ",")} results,
+    \Sexpr{format(m.a.variance4.count$n, big.mark = ",")} meta-analyses};
+
+    \node [block, below of=4, node distance=2.2cm] (5) {
+    \Sexpr{format(sig.id.count, big.mark = ",")} reviews,
+    \Sexpr{format(sig.study.count, big.mark = ",")} studies,
+    \Sexpr{format(sig.result.count, big.mark = ",")} results,
+    \Sexpr{format(m.a.one.sig.count$n, big.mark = ",")} meta-analyses};
+
+    \node [block, below of=5, node distance=2.2cm] (6) {
+    \Sexpr{format(dupl.id.count, big.mark = ",")} reviews,
+    \Sexpr{format(dupl.study.count, big.mark = ",")} studies,
+    \Sexpr{format(dupl.result.count, big.mark = ",")} results,
+    \Sexpr{format(m.a.no.dupl.number$n, big.mark = ",")} meta-analyses};
+
+    \node [final, below of=6, node distance=2.2cm] (7) {Analysis dataset (1):
+    \Sexpr{format(I2.id.count, big.mark = ",")} reviews,
+    \Sexpr{format(I2.study.count, big.mark = ",")} studies,
+    \Sexpr{format(I2.result.count, big.mark = ",")} results,
+    \Sexpr{format(m.a.smaller.5.count$nn, big.mark = ",")} meta-analyses};
+
+    % \node [final] (7) {Analysis dataset:
+    % \Sexpr{format(I2.id.count, big.mark = ",")} reviews,
+    % \Sexpr{format(I2.study.count, big.mark = ",")} studies,
+    % \Sexpr{format(I2.result.count, big.mark = ",")} results,
+    % \Sexpr{format(m.a.smaller.5.count$nn, big.mark = ",")} meta-analyses};
+
+    \node [ublock, below of=7, node distance=4cm] (8) {Binary data: \\
+    \Sexpr{format(dim(meta.bin)[1], big.mark = ",")} meta-analyses};
+
+    \node [ublock, right of=8, node distance=5cm] (9) {Continuous data: \\
+    \Sexpr{format(dim(meta.cont)[1], big.mark = ",")} meta-analyses};
+
+    \node [ublock, left of=8, node distance=5cm] (10) {Other data (IV): \\
+    \Sexpr{format(dim(meta.iv[1])[1], big.mark = ",")} meta-analyses};
+
+    \node [final, below of=8, node distance=2.4cm] (11) {Analysis dataset (2):
+    \Sexpr{format(adj.id.count, big.mark = ",")} reviews,
+    \Sexpr{format(adj.study.count, big.mark = ",")} studies,
+    \Sexpr{format(adj.result.count, big.mark = ",")} results,
+    \Sexpr{format(dim(meta.bin)[1] + dim(meta.cont)[1], big.mark = ",")} meta-analyses};
+
+    % Draw edges
+    \path [line] (1) -- node [btw, xshift = -1.8cm] {\texttt{outcome.flag} restriction} (2);
+    \path [line] (2) -- node [btw, xshift = -1.7cm] {study number $\geq$ 10}(3);
+    \path [line] (3) -- node [btw, xshift = -1.6cm] {variance ratio $>$ 4} (4);
+    \path [line] (4) -- node [btw, xshift = -2cm] {at least one significant result} (5);
+    \path [line] (5) -- node [btw, xshift = -1.2cm] {no duplicates} (6);
+    \path [line] (6) -- node [btw, xshift = -0.8cm] {$I^2$ $\leq$ 0.5} (7);
+
+    \path [line] (7) -- node [btw, xshift = -1.8cm, yshift = 0.45cm] {\texttt{outcome.flag} = \texttt{DICH}} (8);
+    \path [line] (7) -- node [btw, xshift = -1.3cm, yshift = -0.75cm] {\texttt{outcome.flag} = \texttt{CONT}} (9);
+    \path [line] (7) -- node [btw, xshift = -1.8cm] {\texttt{outcome.flag} = \texttt{IV}} (10);
+    \path [line] (8) -- (11);
+    \path [line] (9) -- (11);
+
+\end{tikzpicture}
+\caption{Flow-chart of the exclusion of meta-analyses for the final analysis. The exclusion criteria are given at the right of the arrows.}
+\label{Inclusion.criteria}
+\end{center}
+\end{figure}
 
 \subsubsection{Exclusions due to Computational Errors}
-In exceptional cases, the applied meta-analysis methods and publication bias tests and adjustment algorithms failed due to various reasons.
-Here, those cases are listed and if known, the reasons why computation failed are given.\\
-\textbf{Binary Outcomes}: Out of the meta-analyses that are of \texttt{outcome.type} bin, and have at least ten studies, two studies hat to be excluded:
-\begin{itemize}
-\item meta.id = 62301 (file.nr = 1531, comparison.nr = 8, outcome.nr = 6, subgroup.nr = 1):
-%A subgroup analysis for women with increased adverse pregnancy outcomes, where the effect of vitamin C supplements is tested on pre-eclampsia: 
-Largest study (se = 0.1) has risk ratio 1 and smallest study (se = 1) risk ratio 0.07. Copas publication bias adjustment methods has likelihood optimization issues.
-\item meta.id = 94519 (2519, 14, 1, 2): Largest study (se = 0.05) has risk ratio 0.9 and smallest study (se = 0.4) risk ratio 3.
-Again Copas publication bias adjustment methods has likelihood optimization issues.
-\end{itemize}
+There has been cases where meta-analyses could not be analysed with Copas selection model because the likelihood function could not be optimized based on the settings.
+It was ommitted in this case.
+The analysis failed when using $z$-scores, but not standardized mean differences, and in that case, it was not ommitted.\\
+The specific information about the meta-analysis is: \texttt{meta.id} = 220949, \texttt{id} = ``CD009908'', \texttt{subgroup.id} = ``CMP-001.05.02''.
 
-There were no issues with \texttt{outcome.type} ``cont'' and ``surv''.
-For the subsequent information, it is important to know that meta-analyses are only repeated with Hedges $g$, Pearson correlation coefficient and Fisher's Z-scores, if the outcome type is not survival and all of the above criteria are met ($n$ = \Sexpr{length(meta.f$n.sig.type[which(meta.f$outcome.type != "surv")])}).
+\subsubsection{The Analysis Dataset}
+The dataset that was ultimately tested and adjusted for publication bias comprises \Sexpr{length(meta.id.vector)} meta-analyses and \Sexpr{dim(meta.data)[1]} results.
+The mean number of participants in the treatment group is \Sexpr{mean(meta.data$total1, na.rm = T)} vs \Sexpr{mean(data.ext2$total1, na.rm = T)} in the unrestricted dataset and the mean total number of participants \Sexpr{mean(meta.data$total1 + meta.data$total2)} vs \Sexpr{mean(data.ext2$total1 + data.ext2$total2)}.
+The mean publication year is \Sexpr{mean(meta.data$study.year, na.rm = TRUE)} vs \Sexpr{mean(data.ext2$study.year, na.rm = TRUE)} in the unrestricted dataset.
 \\
-\textbf{Pearson Correlation Coefficient}: Three studies had to be excluded when analyzing the Pearson correlation coefficients:
-\begin{itemize}
-\item meta.id = 157083 (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2): A meta-analysis with all results from the same study, and equal sample size (5 each group).
-The Copas selection model algorithm issued an error when optimizing the likelihood.
-\item meta.id = 159329 (5183, 3, 13): One very small study with group sizes of 2 and 1 patients and small risk ratio of 0.222 (compared to the largest of 1.05, se = 0.04).
-Also, the Copas selection model algorithm issued an error when optimizing the likelihood.
-\item meta.id = 182298 (6211, 1, 8, -): One very small study with 8 patients in each group and 0 event counts in both.
-The Copas selection model algorithm issued an error when optimizing the likelihood.
-\end{itemize}
+From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}}), there are \Sexpr{first.iv.outcome.count} with \texttt{outcome.measure.new} = ..., \Sexpr{second.iv.outcome.count} ...,  \Sexpr{third.iv.outcome.count} ...
+and \Sexpr{fourth.iv.outcome.count} ...
+.
 
-\textbf{Fisher's Z score}: The same issues as encountered for Pearson correlation coefficients (meta.id = 157083 and 159329).
-The variance of the z score $s_z^2$ can be calculated as:  $s_z^2 = \frac{1}{n-3}$, $n$ being the total sample size.
-Thus, studies that have total sample size $n \geq 3$ are discarded in the meta-analyses ($n$ = \Sexpr{total.seq3.number} studies).
-\Sexpr{m.a.seq3.seq10.number} meta-analyses have then less than 10 studies left for pooling:
-\begin{itemize}
-\item meta.id = 10671: (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2), 7 studies left.
-\item meta.id = 43324: (1019, 1, 3, 2), 9 studies left.
-\end{itemize}
-
-\subsubsection{The Publication Bias Test and Adjustment Dataset}
-The dataset that was ultimately tested and adjusted for publication bias comprises \Sexpr{dim(metac)[1]} meta-analyses and \Sexpr{dim(meta.data)[1]} results. ..
+\subsection{Analysis Procedure}
+All compuations were performed in the \texttt{R} computing environment \citep{R.base}.
+The \texttt{R} packages \texttt{meta} \citep{meta.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments.
+The excess significance test was adapted from \citet{vanAert.2019}.
+For data manipulation procedures, the \texttt{tidyverse} packages were used \citep{tidyverse.package}, and for plotting the \texttt{ggplot2} package \citep{ggplot2}.\\
+The methods described in the methods chapter \ref{ch:methods} most often apply directly to the algorithms used in \texttt{meta} and \texttt{metafor}.
+For binary outcomes, log risk ratios were used as treatment effect estimates in the meta-analysis, and for continuous outcomes, Hedge's $g$.
+For the other outcomes, the \texttt{effect} and \texttt{se} as provided in the dataset was passed to \texttt{meta::metagen}.
+\\
+The effect sizes were transformed for adjustment in the way described in section \ref{sec:transformation.effectsizes}.
+The $p$-values for adjusted treatment effect estimates were calculated by the Wald method.
+\\
+In the case of the one-sided test procedure (small study effect and excess significance tests), the effect side in which bias was expected had to be prespecified.
+This was solved by comparing the number of significant findings on each side (original effect scale, i.e.
+for binary outcomes log risk ratios, \etc); the side with more significant findings (two-sided $p$-value < 0.05) was considered the side of potential bias.
+If numbers were equal, the side of the fixed effects treatment was used.
+\\
+Details to Copas selection model algorithm and its application can be found in \citet{limitmeta}.
+In short, two values for $a$ and $b$ in section \ref{sec:copas} were used; a limited range with $a$ between -1.7 and 2, and $b$ between 0.16 and 0.32 was applied first (analog to a most extreme selection process of $P$(select|small trial with sd = 0.4) = 0.1 and P(select|large trial w.
+sd  = 0.05) = 0.9).
+If the most extreme selection process is unable to pass the significance test of no small study effect ($p$-value > 0.1), then a wider range was applied ($a$  between -5.4 and 2 and $b$ between 0 and 0.32).
+If there is still no non-significant small study effect, the result was \texttt{NA}.
 

### 2019-07-12 report/chapter03.tex
Report based on the new data

--- 2019-05-26 report/chapter03.tex
@@
 
-\chapter{Results}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
 
-% 
-% \section{Meta-analysis}
-% The data at hand is composed of over 400,000 results with balanced sample size $n > 24$.
-The significance of the p-values of treatment effect estimates was calculated for all results in the dataset with acceptable sample size and outcome measures as odds ratios, peto odds ratios, risk ratios, risk differences and mean and standardized mean differences.
-% 
-% %Significance over time? Chunck 1
-% 
-% The results that can be pooled are analysed by fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis with Hartung-Knapp method.
-% 
-% \vspace{0mm}
-% In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e.
-if studies were not unique in the dataset with respect to their experimental setup).
-The significance of the treatment effect (primary significance) in a single result is then compared to the significance of the pooled treatment effect (secondary significance).
-% In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown.
-The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure.
-The colors indicate the overall fraction of rejected or accepted null-hypotheses of no treatment effect.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% #plot(sig.meta.c)
-% @
-% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
-% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-% \label{primary.secondary.significance}
-% \end{figure}
-% 
-% What has been found is that even the meta-analysis that for all meta-analysis methods, the amount of secondary significance is higher than the amount of primary significance.
-Thus more primarily non-significant results can be attached to a secondarily significant result than vice-versa.
-% 
-% \vspace{0mm}
-% To illustrate this, the fraction of studies with significant primary treatment effect and primary non-significant treatment effect can be plotted separately (Figure \ref{primary.secondary.significance.sep.sig}).
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% #grid.arrange(sig.meta.plot1, nonsig.meta.plot, ncol= 1)
-% @
-% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-% \label{primary.secondary.significance}
-% \end{figure}
-% 
-% It can be seen that the extent of overlap between primary and secondary significance varies between meta-analysis.
-A considerable amount of both primary significant and primary non-significant results are overruled by meta-analysis hypothesis tests.
-% 
-% 
-% The amount of significant heterogeneity in the results used by the meta-analyses is length(which(mly$sig.Q == 0)) and corresponds to (length(which(mly$sig.Q == 0))/ dim(mly)[1])*100\% of the total number of meta-analyses.
-% 
-% %Comparison of significance separated for significant Q? Chunck 2
-% 
-% %Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in arrange\_impl(.data, dots): Evaluation error: object 'Study' not found.}}\end{kframe}
+\end{knitrout}
 
-\section{Small study effects}
+\chapter{The Cochrane Dataset} \label{ch:dataset}
 
-To provide an overview over the abundance of small study effects in the dataset, first it is shown how median absolute effect size decreases with increasing sample size of the results (Figure \ref{effect.samplesize}).
-%In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.
+\section{Cochrane Systematic Reviews}
+The Cochrane Group has specialized on systematic reviews in clinical science.
+Certain knowledge of standards and principles of the Cochrane Group may help to assess the quality and the properties of the dataset.
+The following information stems from the Cochrane Handbook for Systematic Reviews \citep{cochrane.handbook}.
+\\
+The definition of a systematic review is that it ``attempts to collate all empirical evidence that fits pre-specified eligibility criteria in order to answer a specific research question.'' Thus, the ``key properties of a review are'':
+
+\begin{itemize}
+\item``a clearly stated set of objectives with pre-defined eligibility criteria for studies''
+\item ``an explicit, reproducible methodology''
+\item ``a systematic search that attempts to identify all studies that would meet the eligibility criteria''
+\item ``an assessment of the validity of the findings of the included studies, for example through the assessment of risk of bias''
+\end{itemize}
+
+At the end of a systematic review, ``a systematic presentation, and synthesis, of the characteristics and findings of the included studies'' is done. \\
+53 Cochrane Review Groups prepare and maintain the reviews within specific areas of health care.
+A group consists of ``researchers, healthcare professionals and people using healthcare services (consumers)''.
+\\
+The groups are supported by Method Groups, Centers and Fields.
+The Cochrane Method Groups aim to discuss and consult the groups in methodological questions concerning review preparation.
+The Centers play a main role in training and support of the Groups.
+The Fields are responsible for broad medical research areas and follow priorities in those areas by advice and control of the groups.
+\\
+The first step in a review is writing a protocol, specifying the research question, the methods to be used in literature search and analysis and the eligibility criteria of the study.
+Changes in protocols are possible but have to be documented and the protocol is published in advance of the publication of the full review.
+The choices of methodology as well as the changes should not be made ``on the basis of how they affect the outcome of the research study''.
+\\
+In order to avoid potential conflicts of interests, there is a code of conduct that all entities of the Cochrane Organization have to agree on: conflicts of interest must be disclosed and possibly be forwarded to the Cochrane Center, and participation of review authors in the studies used have to be acknowledged.
+Additionally, a Steering Group publishes a report of potential conflicts of interests based on information about external funding of Cochrane Groups.
+\\
+In order for keeping the reviews up-to-date, they are revised in a two-year circle with exceptions.
+In addition to inclusion of new evidence in a field, the revision and maintenance process may as well includes change in analysis methods.
+This can reflect some advance in clinical science as for example new information about important subgroups, as well as new methods for conducting a Cochrane Review.
+However, there are no clear guidelines and the Cochrane Groups are free in the rate and extent of up-dating their reviews.
+
+\subsection{Methods for Cochrane Reviews}
+A research question defines the following points: ``the types of population (participants), types of interventions (and comparisons), and the types of outcomes that are of interest''.
+From the research question, usually the eligibility criteria follow.
+Usually, outcomes are not part of eligibility criteria, except for special cases such as adverse effect reviews.
+\\
+The type of study is an important eligibility criterium.
+The Cochrane Collaboration focuses ``primarily on randomized controlled trials'', and also, the methods of study identification in literature search are focused on randomized trials.
+Furthermore, study characteristics such as blinding of study operators with respect to treatment and cluster-randomizing might be additional eligibility criteria which have to be chosen by the review authors.
+\\
+After having specified the eligibility criteria, studies have to be collected.
+The central idea of systematic reviews, and also meta-analyses, is that the collected studies are a random sample of a population of studies, i.e.
+that they are representative and can be used to assess population properties.
+Therefore, the search process is crucial, as a selective search result may impose bias on the sample of studies available, making it a non-random sample.
+For this purpose, the Cochrane Groups are advised to go beyond MEDLINE !!cite!!, because a search restricted to it has been shown to deliver only 30\% to 80\% of available studies.
+``Time and budget restraints require the review author to balance the thoroughness of the search with efficiency in use of time and funds and the best way of achieving this balance is to be aware of, and try to minimize, the biases such as publication bias and language bias that can result from restricting searches in different ways.'' It is important to note that not only studies, but also study reports are occasionally used in the reviews, as they may provide useful information.
+\\
+There are different sources that are being used to search for studies. 
+\begin{itemize}
+\item The Cochrane Central Register of Controlled Trials is a source of reports of controlled trials.
+``As of January 2008 (Issue 1, 2008), CENTRAL contains nearly 530,000 citations to reports of trials and other studies potentially eligible for inclusion in Cochrane reviews, of which 310,000 trial reports are from MEDLINE, 50,000 additional trial reports are from EMBASE and the remaining 170,000 are from other sources such as other databases and handsearching.'' It includes citations published in many languages, citations only available in conference proceedings, citations from trials registers and trials results registers.
+\item MEDLINE.
+MEDLINE includes over 16 million references to journal articles.
+5,200 journals publishing in 27 languages are indexed for MEDLINE.
+PubMed gives access to a free version of MEDLINE with up-to-date citations.
+NLM gateway such as the Health Services Research Project, Meeting Abstracts and TOXLINE Subset for toxicology citations allows for search in both databases together with additional data from the US National Library of Medicine.
+\item EMBASE.
+4,800 Journals publishing in 30 languages are indexed to EMBASE, which includes more than 11 million records from 1974 onward.
+EMBASE.com also includes 7 million unique records from MEDLINE (1966 up to date) together with its own records.
+Additionally, EMBASE Classic allows access to digitized records from 1947 to 1973.
+EMBASE and MEDLINE each have around 1,800 journals not indexed in the other database.
+\item Regional or national and subject specific databases can additionally be consulted and often provide important information. Financial considerations may limit the use of such databases.
+\item General search engines such as Google Scholar, Intute and Turning Research into Practice (TRIP) database can be used.
+\item Citation Indexes.
+The database lists articles published in around 6,000 Journals with articles in which they have been cited and is available online as SciSearch.
+This form of search is known as cited reference searching.
+\item Dissertation sources. Dissertations are often listed in MEDLINE or EMBASE but one is advised to also search in specific dissertation sources.
+\item Grey Literature Databases.
+Approximately 10\% of the results in the Cochrane Database stems from conference abstracts and other grey literature.
+The Institute for Scientific and Technical Information in France provides access to entries of the previously closed System for Information on Grey Literature database of the European Association for Grey Literature Exploitation).
+Another source is the Healthcare Management Information Consortium (HMIC) database containing records from the Library and Information Services department of the Department of Health (DH) in England and the King's Fund Information and Library Service.
+The National Technical Information Service (NTIS) gives access to the results of US and non-US government-sponsored research, as well as technical report for most published results.
+References from newsletters, magazines and technical and annual reports in behavioral science, psychology and health are provided in the PsycEXTRA database which is linked to PsycINFO database.
+\end{itemize}
+
+\subsection{Structure and Content}
+The dataset consists of 6353 systematic reviews from the Cochrane Library with 70662 studies and 744717 results.
+The results all stem from comparisons of a healthcare interventions or treatments to a reference.
+The reference may be a placebo control group or a other intervention or treatment.
+A result can not only be about efficacy of the treatments, but also about safety (adverse effects).\\
+In Table \ref{barbiturate.row}, two results from a systematic review about barbiturates are shown as they are given in the dataset.
+As can be seen, further specifications are provided by the variables in the columns.
+\\
+The \texttt{comparison.name} variable specifies \textit{what kind} of treatments or interventions are compared, the \texttt{outcome.name} variable \textit{how} it is compared, and the \texttt{subgroup.name} variable (not indicated in table) \textit{if and to what experimental subgroup} the result belongs.
+\\
+The result is of a binary type, and the counts of events in the treatment group are in \texttt{events1} and of the control group in \texttt{events2} and the total number of participants are given in columns \texttt{total1} and \texttt{total2}.
+As can be seen, events denote here "death at the end of follow-up".
+
+\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(barbi1, label = "{}barbiturate.row"{}, digits = 0, caption = "{}Example of two results as given in the dataset.
+Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
+Further descriptive variables have been ommitted"{}): object 'barbi1' not found}}\end{kframe}
+
+A complete listing of the variables of a result is given in Table \ref{variable}.
+Depending on the type of the data, \eg if it is binary or continuous, some variables are missing for the specific results.
+
+\begin{table}[ht]
+  \begin{center}
+    \begin{tabular}{l l}
+      \textbf{Variable} & \textbf{Description}\\
+      \hline
+      \texttt{id} & An id of the review for identification purposes \\
+      %\texttt{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
+      % \texttt{file.index} & Internal index of the file in the Cochrane library.\\
+      % \texttt{file.version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
+      %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
+      \hline
+      \texttt{study.name} & Name of the study to which the result belongs\\
+      \texttt{study.year} & Year in which the study was published \\
+      \texttt{study.data.source} & Source of the study, either ``Publ \\
+      \hline
+      \texttt{comparison.name/.nr} & Specification of the interventions compared in the study  \\ &and a unique number for the comparison\\
+      \texttt{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ &and a unique number for the outcome\\
+      \texttt{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a \\ &unique number for the subgroup\\
+      \texttt{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
+      \texttt{effect} & Measure of the effect given in the quantity denoted by \\ &\texttt{outcome measure}.\\
+      \texttt{se} & Standard error of the measure of the effect,\\
+      \texttt{events1/events2} & The counts of patients with an outcome \textit{if}\\ &measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
+      \texttt{total1/total2} & Number of patients in groups.\\
+      \texttt{mean1/mean2} & Mean of patient measurements \textit{if} outcome is continuous.\\
+      \texttt{sd1/sd2} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
+    \end{tabular}
+  \caption{Dataset variable names and descriptions  \label{variable}}
+  \label{variable}
+  \end{center}
+\end{table}
+
+Results are part of studies that are again part of a (systematic) review. This structure of a review is shown in Figure \ref{review}.
+
+\begin{figure}
+\tikzstyle{every node}=[draw=black,thick,anchor=west]
+\tikzstyle{selected}=[draw=red,fill=red!30]
+\tikzstyle{optional}=[dashed,fill=gray!50]
+\begin{tikzpicture}
+[grow = right, anchor = west, 
+  growth parent anchor=east, % added code
+  parent anchor=east]
+  \node {Review} [edge from parent fork right]
+    child { node {Comparison 2}
+      child { node {Outcome 2}}
+      child { node {Outcome 1}
+        child { node {Subgroup 2}}
+        child { node {Subgroup 1}
+          child  { node {Result 2}}
+          child  { node {Result 1}}
+          }}
+    }
+    child [missing] {}		
+    child { node {Comparison 1  }};
+\end{tikzpicture}
+\caption{Structure of a hypothetical review with two different comparisons}
+\label{review.structure}
+\end{figure}
 
 \vspace{0mm}
-A clear trend of decrease of absolute effect size with increasing sample size (i.e. smaller variance) is visible. 
-%It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off.
-With increasing sample size, there are fewer results, therefore, the variation between medians increases.
-All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation.
-Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-5-1}
-
-}
-
-\end{knitrout}
-\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
-\label{effect.samplesize}
-\end{figure}
-
-The median absolute normalized effect size can be visualized for the different outcome measures separately (Figure \ref{effect.samplesize.separated}).
-The plot confirms the trend of median effect size decrease towards lower sample size (e.g.
-for Risk Ratios: decrease $> 0.1$ standard deviations from 10 to 50 study participants).
-Instead of normalizing the effects
-%(i.e. subtracting mean and dividing through the standard deviation) 
-for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-6-1}
-
-}
-
-\end{knitrout}
-\caption{Median of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
-\label{effect.samplesize.separated}
-\end{figure}
-
-%Show absolute effect size depending on scaled time? Chunck 3
-
-\subsection{Small Study Effect Tests}
-
-There are tests that can be applied to find out if small study effects are present in the meta analysis.
-For the precise description, see the methods section.
-Application of the tests is only recommended if there are ten or more studies \citep{cochrane.handbook} that can be used, so all meta-analyses with less than ten studies have been excluded.
-
-\vspace{0mm}
-There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results.
-In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = 1383)
-The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3955).
-The amount of studies varies from 5\% (Schwarzer's Test) to 13 \% (Egger's Test) for binary outcomes and 9\% (Begg and Mazumdar's Test) to 25 \% (Egger's Test) for continuous outcomes.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-8-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-\label{bias.results.cont}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-9-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-\label{bias.results.bin}
-\end{figure}
-
-There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not.
-Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by 0.1825716 (the minimal increase is -0.0032246 for Schwarzer's Test).
-
-%Show plots of significant meta-analyses separated? Chunck 4
-
-Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses).
-The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}.
-The Figure suggests that the frequency of publication bias remains constant over time.
-The mean publication years have been restricted such that at least 180 meta-analyses are available per year, such that random fluctuation is restricted to some extent.
-The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-10-1}
-
-}
-
-\end{knitrout}
-\caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
-\label{pub.bias.overtime}
-\end{figure}
-
-The agreement of the tests, i.e.
-the proportion of meta-analyses where the rest results are equal between tests, is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.
-Agreement in tests for binary outcomes is better than continuous outcomes, with some variation between tests (binary outcomes: 83 to 91\%).
-Correlation varies more between tests, both for continuous and binary outcome tests.
+The structure of a review will now be outlined based on an example of the dataset.
+Let us consider the previously mentioned barbiturate and head injury review.
+The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates'' %\citep{barbiturate}.
+\\
+%Since there are arguments for and against use of barbiturates, the authors of the review did a comprehensive literature search and collected all available study findings. 
+The review comprises five studies in total.
+Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental.
+The studies have different outcomes, for example, death or death and severe disability at follow up, but also dropout counts or adverse effects (secondary outcomes).
+We have continuous (e.g.
+mean body temperature) and binary outcome data (e.g.
+death/no death).
+One study split up outcomes for patients with and without haematoma, which would be subgroups.
+Thus, it is important not to confuse results with studies.
+A study can contribute multiple results to a systematic review, for example, primary and secondary outcomes and adverse effects.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue May 21 16:11:40 2019
+% Thu Jul 11 14:21:43 2019
 \begin{table}[ht]
@@
   \hline
- & Test Agreement & P-value Correlation \\ 
+Study & Comparison & Outcome \\ 
   \hline
-egger.schwarzer & 0.73 & 0.23 \\ 
-  egger.peter & 0.75 & 0.37 \\ 
-  egger.rucker & 0.75 & 0.34 \\ 
-  egger.harbord & 0.79 & 0.51 \\ 
-  schwarzer.peter & 0.81 & 0.26 \\ 
-  schwarzer.rucker & 0.81 & 0.25 \\ 
-  schwarzer.harbord & 0.86 & 0.47 \\ 
-  rucker.peter & 0.87 & 0.64 \\ 
-  harbord.peter & 0.84 & 0.50 \\ 
+Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
+  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
+  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
+  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
+  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
+  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
+  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
+  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
+  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
+  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
+  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
+  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
+  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
+  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
+  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
+  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
+  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
+  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
    \hline
@@
 \endgroup
-\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)} 
-\label{agreement.bin}
+\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given} 
+\label{barbiturates}
 \end{table}
 
+Information about missing values in the dataset is given in Table \ref{missing}.
+The relative amount of missing values is low, except for study years.
+For continuous outcomes, the cases are counted were neither a mean difference nor means are available.
+Similarly, the counts of cases where neither standard errors nor standard deviations are available are provided.
+Study years before 1920 and after 2019 are declared as missing, as well as sample sizes equal to zero.
+
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue May 21 16:11:40 2019
+% Thu Jul 11 14:21:43 2019
 \begin{table}[ht]
@@
 \begingroup\footnotesize
-\begin{tabular}{lll}
+\begin{tabular}{lr}
   \hline
- & Test Agreement & P-value Correlation \\ 
   \hline
-thomson.egger & 0.85 & 0.69 \\ 
-  thomson.begg & 0.77 & 0.47 \\ 
-  egger.begg & 0.73 & 0.36 \\ 
+Neither means nor standard deviations (CONT) & 775 \\ 
+  Zero participants in one group & 15162 \\ 
+  Missing study publication year & 7942 \\ 
    \hline
@@
 \endgroup
-\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)} 
-\label{agreement.cont}
+\caption{Number of missing variables and measurements in the dataset} 
+\label{missing}
 \end{table}
 
-\vspace{0mm}
-Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies.
-The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}.
-%(Suggests that 10 is likely too small)
-In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test.
-A trend towards more rejections for larger sample sizes can be seen.
+The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982, 95\% quantile = 2014,).
+The median of the publication years is 2003, the mean 2000.97 and the quartiles are 1996 and 2008.
+1075 studies have been published in 2018, none in 2019.
+\\
+The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}.
+One can conclude of the table that roughly 31 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (more than 65\%).
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Thu Jul 11 14:21:43 2019
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lrr}
+  \hline
+Outcome measure & n & Percentage \\ 
+  \hline
+RR & 361902 & 48.6\% \\ 
+  MD & 164920 & 22.1\% \\ 
+  OR & 72012 & 9.7\% \\ 
+  SMD & 70717 & 9.5\% \\ 
+  PETO\_OR & 39710 & 5.3\% \\ 
+  RD & 11068 & 1.5\% \\ 
+  Hazard Ratio & 8054 & 1.1\% \\ 
+  Odds Ratio & 4055 & 0.5\% \\ 
+  other & 12279 & 1.6\% \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Frequencies of outcome measures among results. n denotes the total number 
+             of results with the outcome measure and percentage the percentage of the outcome measure,} 
+\label{outcome.measure.frequencies}
+\end{table}
+
+The sample sizes among results vary to some extent.
+There are 5\% of treatment group sample sizes that are smaller than 9, 95\% smaller than 510.
+The first quartile is 23, the median 48, the mean 256.71 and the third quartile 116.
+The large difference between median and mean is caused by very large groups with over 2,000,000 participants.
+Analogously, the quantiles of the total sample size are: 5\% quantile = 17, first quartile = 44, median = 94, third quartile = 223 and 95\% = 983.
+The mean is 623.16.
+\\
+There are 518 reviews with five or fewer results.
+The 5\% and 95\% quantiles are 4 and 447.
+The mean and median number of results per review are 13.6 and 8, and the quartiles are 16 and 109.
+Similarly, the number of reviews with a maximum of two studies included is 1039, the mean study number is 13.6, the median 8 and the interquartile range 4 and 16 and the 95\% quantile 45.
+The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citet{largest.review}
+which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1,497 results in total.\\
+For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome.
+The studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis.
+This distinction is also used by the Cochrane Organization itself, \ie the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
+The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.
+
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Thu Jul 11 14:21:43 2019
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lrr}
+  \hline
+n & Number of groups & Cumulative sum of groups \\ 
+  \hline
+1 & 143375 & 268903 \\ 
+  2 & 45459 & 125528 \\ 
+  3 & 23232 & 80069 \\ 
+  4 & 14184 & 56837 \\ 
+  5 & 9493 & 42653 \\ 
+  6 & 6449 & 33160 \\ 
+  7 & 4583 & 26711 \\ 
+  8 & 3412 & 22128 \\ 
+  9 & 2585 & 18716 \\ 
+  10 & 2046 & 16131 \\ 
+  11 & 1524 & 14085 \\ 
+  12 & 1197 & 12561 \\ 
+  13 & 1022 & 11364 \\ 
+  14 & 785 & 10342 \\ 
+  15 & 9557 & 9557 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Number and cumulative number of groups with meta-analysis size n.} 
+\label{repr.groups}
+\end{table}
+
+\section{Data Tidying and Processing} \label{sec:Processing}
+The dataset was scraped from the Cochrane Database of Systematic Reviews at the ... . A specialized code was used to convert the xtml. files from the webpage into the data at hand cite... .
+
+\subsection{Newly Introduced Variables}
+Some new variables are added to the obtained dataset:
+\begin{itemize}
+\item \texttt{outcome.measure.new}: Outcome measure specifications given in \texttt{outcome.measure} were standardized whenever they were supposed to denote the same outcome measure.
+An example would be the formally different notations for odds ratios: ``Odds Ratio'', ``odds ratio'', ``OR'', which were all denoted as ``Odds Ratio''.
+% \item \texttt{outcome.flag}: A simplification of \texttt{outcome.measure.new}.
+The outcome.flag ``bin'' indicates if \texttt{outcome.measure.new} is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
+``cont'' is equivalent to \texttt{outcome.measure.new} equal to "Std.
+Mean Difference'' or ``Mean Difference''.
+``surv'' equal to ``Hazard Ratio'' and ``rate'' equal to ''Rate Ratio'' or ``Rate Difference''.
+\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.flag ``bin''.
+\item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.flag ``cont''. 
+% If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.new} was equal to ``Std.
+Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  length(inpute.given.ind)).
+\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.flag ``bin''.
+\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.flag ``bin'') or $g$ (for outcome.flag ``cont'') to $r$ transformation.
+\item \texttt{z} and \texttt{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
+\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.flag ``cont'' or Wald test for outcome.flag ``bin''.
+\item \texttt{events1c} and \texttt{events2c}: Correction of \texttt{events1} and \texttt{events2} zero event counts or event counts = patient number.
+When no events occurred, 0.5 was added, and when all patients experienced the event, 0.5 was subtracted.
+When one of \texttt{events} had zero counts while the other had maximum counts, no adjustment occurred.
+\item \texttt{meta.id}: Meta-analysis ID variable to uniquely identify any potential meta-analysis in the dataset.
+Consistent to what has been discussed before, all results that share a common comparison, outcome and subgroup (optional, subgroups not given in any case) may be combined in a meta-analysis.
+\item \texttt{se.new}: Depending on \texttt{outcome.flag}, \texttt{se.new} is equal to the square-root of \texttt{var.lrr} (\texttt{outcome.flag} = \texttt{DICH}), square-root of \texttt{var.smd} (\texttt{CONT})
+or \texttt{se} (\texttt{IV}).
+% \item \texttt{}:
+\end{itemize}
+
+\subsection{Eligibility criteria for Publication Bias Test and Adjustment}
 
 \begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+\begin{center}
+\tikzstyle{block} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=4em]
+\tikzstyle{line} = [draw, -latex']
+\tikzstyle{final} = [rectangle, draw, fill=red!20, text centered, minimum height=4em]
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}
-
-}
-
-\end{knitrout}
-\caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
-\label{pvalues.samplesize}
+\begin{tikzpicture}[node distance = 2cm, auto]
+    % Place nodes
+    \node [final] (1) {Inital dataset: 6,353};
+    \node [block, below of=1, node distance=2.4cm] (2) {Simplified dataset};
+    \node [block, below of=2, node distance=2.4cm] (3) {Reduced dataset};
+    \node [block, below of=3, node distance=2.4cm] (4) {Suitable size differences};
+    \node [block, below of=4, node distance=2.4cm] (5) {blabla};
+    \node [block, below of=5, node distance=2.4cm] (6) {blabla};
+    \node [final, below of=6, node distance=2.4cm] (7) {blabla};
+    % Draw edges
+    \path [line] (1) -- node {outcome.flag restriction} (2);
+    \path [line] (2) -- node {study number $\geq$ 10}(3);
+    \path [line] (3) -- node {variance ratio $>$ 4} (4);
+    \path [line] (4) -- node {at least one significant result} (5);
+    \path [line] (5) -- node {no duplicates} (6);
+    \path [line] (6) -- node {$I^2$ $\leq$ 0.5} (7);
+\end{tikzpicture}
+\caption{Flow-chart of the exclusion of meta-analyses for the final analysis. The exclusion criteria are given at the right of the arrows.}
+\end{center}
 \end{figure}
 
-\vspace{0mm}
-One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects.
-The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.18.
-% A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes.
-In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses.
-In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.
-In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.
+Initially, the analysis is restricted to results wiht \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}.
+binary, continuous and survival outcomes.
+This corresponds to 734951 out of a total of 744717 results.
+\begin{itemize}
+\item \textbf{Outcome measures}: The analysis has been restricted on the following outcome measures (from \texttt{outcome.measure.new}): ``Odds Ratio'', ``Risk Ratio'', ``Risk difference'', ``Peto Odds Ratio'', ``Std.
+Mean Difference'', ``Mean Difference'', ``Hazard Ratio''
+($n$ = 734951 out of a total of 744717 results)
+\end{itemize}
 
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+The suggestions of criteria for eligibility for publication bias tests of \citet{Ioannidis2007} have largely been followed:
+\begin{itemize}
+\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = 11463 remaining). 
+\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 10830 remaining).
+\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 8575 remaining)
+\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 3108 remaining).
+\end{itemize}
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-14-1}
+After having excluded meta-analyses with less than ten studies, additional criteria for excluding inconvenient meta-analyses are:
+\begin{itemize}
+\item \textbf{Sensitivity Analyses}: When the same results are used multiple times for different meta-analyses, only one is retained.
+More precisely, if a study hat the same \texttt{study.name} and same \texttt{effect}, it was considered a duplicate, and the smaller meta-analysis of the two was excluded.
+The intention is to exclude sensitivity analyses which are operated on subsets of the available results.
+\item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = 20 out of meta-analyses with at least ten studies).
+% \item \textbf{Missing means and sd's}: In the case of continuous outcomes, meta-analyses with means and sd's in any group being equal to zero are excluded ($n$ = all.zero.means.number out of meta-analyses with at least ten studies).
+% \item \textbf{Single patient data}: Meta-analyses that are comprised of single patient data are excluded ($n$ = m.a.singlepatient.number out of meta-analyses with at least ten studies)
+\end{itemize}
 
-}
+--Make Flowchart--
 
-\end{knitrout}
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
-\label{trimfill.pvalues.bin}
-\end{figure}
+\subsubsection{Exclusions due to Computational Errors}
+In exceptional cases, the applied meta-analysis methods and publication bias tests and adjustment algorithms failed due to various reasons.
+Here, those cases are listed and if known, the reasons why computation failed are given.\\
+\textbf{Binary Outcomes}: Out of the meta-analyses that are of \texttt{outcome.flag} bin, and have at least ten studies, two studies hat to be excluded:
+\begin{itemize}
+\item meta.id = 62301 (id = 1531, comparison.nr = 8, outcome.nr = 6, subgroup.nr = 1):
+%A subgroup analysis for women with increased adverse pregnancy outcomes, where the effect of vitamin C supplements is tested on pre-eclampsia: 
+Largest study (se = 0.1) has risk ratio 1 and smallest study (se = 1) risk ratio 0.07. Copas publication bias adjustment methods has likelihood optimization issues.
+\item meta.id = 94519 (2519, 14, 1, 2): Largest study (se = 0.05) has risk ratio 0.9 and smallest study (se = 0.4) risk ratio 3.
+Again Copas publication bias adjustment methods has likelihood optimization issues.
+\end{itemize}
 
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+There were no issues with \texttt{outcome.flag} ``cont'' and ``surv''.
+For the subsequent information, it is important to know that meta-analyses are only repeated with Hedges $g$, Pearson correlation coefficient and Fisher's Z-scores, if the outcome type is not survival and all of the above criteria are met ($n$ = 2855).
+\\
+\textbf{Pearson Correlation Coefficient}: Three studies had to be excluded when analyzing the Pearson correlation coefficients:
+\begin{itemize}
+\item meta.id = 157083 (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2): A meta-analysis with all results from the same study, and equal sample size (5 each group).
+The Copas selection model algorithm issued an error when optimizing the likelihood.
+\item meta.id = 159329 (5183, 3, 13): One very small study with group sizes of 2 and 1 patients and small risk ratio of 0.222 (compared to the largest of 1.05, se = 0.04).
+Also, the Copas selection model algorithm issued an error when optimizing the likelihood.
+\item meta.id = 182298 (6211, 1, 8, -): One very small study with 8 patients in each group and 0 event counts in both.
+The Copas selection model algorithm issued an error when optimizing the likelihood.
+\end{itemize}
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-15-1}
+% \textbf{Fisher's Z score}: The same issues as encountered for Pearson correlation coefficients (meta.id = 157083 and 159329).
+The variance of the z score $s_z^2$ can be calculated as:  $s_z^2 = \frac{1}{n-3}$, $n$ being the total sample size.
+Thus, studies that have total sample size $n \geq 3$ are discarded in the meta-analyses ($n$ = z.seq3.number studies).
+m.a.seq3.seq10.number meta-analyses have then less than 10 studies left for pooling:
+\begin{itemize}
+\item meta.id = 10671: (file.nr = 5061, comparison.nr = 1, outcome.nr = 5, subgroup.nr = 2), 7 studies left.
+\item meta.id = 43324: (1019, 1, 3, 2), 9 studies left.
+\end{itemize}
 
-}
+\subsubsection{The Publication Bias Test and Adjustment Dataset}
+The dataset that was ultimately tested and adjusted for publication bias comprises 1 meta-analyses and 0 results. ..
 
-\end{knitrout}
-\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
-\label{trimfill.pvalues.cont}
-\end{figure}
+% \begin{itemize}
+% \item meta.id = 136563 (4218, 1, 1, 1): ``Roberts 2010'' (3)
+% \item meta.id = 136566 (4218, 1, 3, 1): ``Roberts 2010'' (3)
+% \end{itemize}
 
-\subsection{Small Study Effect Correction}
-Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
-Three of them will be applied to the meta-analyses shown previously that have ten or more study results and are therefore eligible for testing for publication bias.
-
-\vspace{0mm}
-The extent to what the results of the meta-analysis results are changed can be investigated.
-Because statistical significance is often used to decide if there is a treatment effect, a non-significant corrected effect size estimate can indicate that an observed treatment effect has been accepted because of small study effects.
-Therefore, the cases have been counted in which
-\begin{enumerate}
-\item Significance or non-significance of pooled estimate of meta-analysis did not change after correction for small study effects.
-\item Significance of pooled estimate of meta-analysis did change to non-significance after correction for small study effects.
-\item Non-significance of pooled estimate of meta-analysis did change to significance after correction for small study effects.
-\end{enumerate}
-
-The results of this can be seen in Figure \ref{significance.change.fixed} for all three methods, comparing the significance of the corrected pooled effect size estimate with the significance of the pooled effect size estimate of the fixed effects meta-analysis.
-The same for significance of random effects meta-analysis is shown in Figure \ref{significance.change.random}.
-The significance threshold was chosen such that the $p$-value had to be < 0.05 for rejection of the null hypothesis of no treatment effect.
-The correction methods were trim-and-fill, copas selection model and regression with random effects and shrinkage of within-study-variance methods.
-More details to the applied correction methods and their application are in the methods section \ref{methods}.
-Notably, the correction methods has been applied to all meta-analyses, thus also for such that had no significant small study effect test result.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-16-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction.}
-\label{significance.change.fixed}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction.}
-\label{significance.change.random}
-\end{figure}
-
-Since it has been previously seen in Figure \ref{test.results} that the results of small study effects vary considerably between continuous outcomes, the results in significance change from fixed effects meta-analysis can be seen separately in Figure \ref{significance.change.fixed.sep} for continuous and binary outcomes.
-The change in significance from random effects meta-analysis to significance of corrected estimate can be seen in Figure \ref{significance.change.fixed.sep}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.fixed.sep}
-\end{figure}
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.random}
-\end{figure}
-
-Because the real amount of publication bias in the dataset is not known, the correction method can also be applied only to meta-analyses that have publication bias according to the small study effect tests in the previous section.
-Because the test developed by \citet{thomson.sharp} has been applied to both binary and continuous outcome meta-analyses (in the case of binary outcomes to arcsine variance stabilized proportions), it is used as a criterium to distinguish biased from unbiased meta-analyses.
-The proportions of significance tests of pooled treatment effects that turned from significant to non-significant, non-significant to significant etc.
-are shown in Figure \ref{significance.change.fixed.sep}.
-Fixed effects meta-analysis has been used to determine signficance of the uncorrected estimate.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}
-
-}
-
-\end{knitrout}
-\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
-\label{significance.change.random}
-\end{figure}
-
-Similarly, the number of missing studies per meta-analysis, i.e.
-those which have not been included because of small study effects, are estimated by the copas and trim-and-fill method and their empirical distribution is shown in histograms in Figure \ref{missing.studies.distribution}.
-For visualisation, the fraction of unpublished studies from the total fraction of available studies is shown.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-21-1}
-
-}
-
-\end{knitrout}
-\caption{Fraction of missing studies estimated of the number of total studies included in the meta-analysis for copas selection and trim-and-fill method.}
-\label{missing.studies.distribution}
-\end{figure}
-
-% # <<results = 'asis', Echo = FALSE>>=
-% # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
-% #                                             schwarzer.rejection = mean(schwarzer.test),
-% #                                             rucker.rejection = mean(rucker.test),
-% #                                             harbord.rejection = mean(harbord.test),
-% #                                             peter.rejection = mean(peter.test))
-% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
-% # @
-
-% 
-% For continuous outcomes, three tests are available: Eggers (based on linear regression), Thompson and Sharp (weighted linear regression) and Begg and Mazumdar (rank based) test.
-The following three figures show the distribution of p-values of the corresponding tests.
-Note that only meta analyses with more than 10 comparisons have been included.
-% 
-% \vspace{0mm}
-% Since each histogram of p-values has 20 bins, the content of the bin with the smallest p-values is equal to the number of meta-analyses whose reporting bias test reports a p-value < 0.05.
-The fraction of those analyses in which we would reject the null-hypothesis based on the 5 \% threshold can therefore be assessed by eye, and would be for example for Eggers test somewhat less than one third of all analyses.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "linreg")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Eggers Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Eggers reporting bias test (linear regression based) for continuous outcome meta analysis.}
-% \label{egger.cont}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "mm")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Thomson Sharp Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Thompsom and Sharp reporting bias test (weighted linear regression based) for continuous outcome meta analysis.}
-% \label{thomson.cont}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 503) %>% 
-%   filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
-%   filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2), 
-%                             method = "rank")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Begg and Mazumdar Reporting Bias Test P-values for Continuous Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Begg and Mazumdar reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{begg.cont}
-% \end{figure}
-% 
-% 
-% For binary outcomes, Peters and Harbords reporting bias test have been chosen. Also here, only meta-analyses with more than 10 comparisons are included.
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-%   filter(events1 > 0 | events2 > 0) %>% 
-%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "peters")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Peters Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Peters reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{peters.bin}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% filter(file.nr != 3014) %>% 
-%   filter(events1 > 0 | events2 > 0) %>% 
-%   filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
-%   group_by(file.nr, outcome.nr, subgroup.nr) %>% 
-%   mutate(n = n()) %>% filter(n > 9) %>% 
-%   summarize(pval = metabias(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, sm = "OR"), method = "score")$p.val) %>% 
-%   ggplot(aes(x = pval)) + geom_histogram(col = "gray15", fill = "dodgerblue", bins = 20) +
-%   theme_bw() + labs(title = "Harbord Reporting Bias Test P-values for Binary Outcome Meta-Analyses") + xlab("P-value") + ylab("Frequency")
-% @
-% \caption{Histogram of p-values for Harbord reporting bias test (rank based) for continuous outcome meta analysis.}
-% \label{harbord.bin}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Since most of the times the study publication year is available for a given result, the fraction of significant treatment effects found is shown over time in Figure \ref{study.significance.overtime}.
-The $p$-value was chosen to be 0.05  only times where a reasonbly large number of effect estimates is available is shown in order to reduce random fluctuation ($n$ > 800).
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% data.ext %>% filter(!is.na(sig.type)) %>%  ggplot(aes(x = study.year, fill = factor(sig.type), stat(count))) + geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))+ scale_x_continuous(limits = c(1970, 2017))
-% @
-% \caption{Mean of the absolute value of the normalized effect size plotted against the total sample size.}
-% \label{study.significance.overtime}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 2
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The separation of studies can also be made based on the significance of heterogeneity between them when pooling them by means of a meta-analysis.
-Significant heterogeneity between studies corresponds to a rejection of the null-hypothesis that all the study treatment effect estimates share the same underlying distribution.
-The test used to assess heterogeneity was based on the between-study heterogeneity estimate $Q$ estimated as \citet{tau.estimator} suggested.
-This is shown in Figure \ref{primary.secondary.significance.sep.sig}.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(sig.meta.Q1, nonsig.meta.Q, ncol= 1)
-% @
-% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate.
-The fractions have been calculated
-% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
-% \label{primary.secondary.significance.sep.sig}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 3
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% A second way to analyse meta-analyses is a cumulative meta-analysis that should reveal shifts in treatment effect sizes over time.
-This can again be done for the entire dataset, i.e.
-for all effect estimates and their ordering in time.
-It is important to scale the effect estimates here with respect to the estimates of the replication studies that are about the same subject, have the same outcome measure, etc.
-Also, only effect estimates that can be compared to other estimates before are included, i.e.
-only study results with one or more replica are included.
-Time needs to be scaled and normalized in order to compare multiple time-trends in effect size to each other and gain insights in the overall trend.
-This is done in Figure \ref{effects.overtime.separated}, separared for odds rati, risk ratio, and mean and standardized difference outcome measures.
-In order to reduce the spread over time of effect sizes, only studies between 1970 and 2019 were included, as well as studies with a minimal group size of 12 participants (each group).
-% 
-% \begin{figure}
-% <<echo=FALSE>>=
-% data.ext %>% filter(outcome.measure.new == "Mean Difference" | outcome.measure.new == "Std. Mean Difference" | 
-%                 outcome.measure.new == "Risk Ratio" | outcome.measure.new == "Odds Ratio") %>% 
-%   filter(total1 > 11 & total2 > 11) %>% filter(!is.na(study.year) & study.year > 1970 & study.year < 2019) %>% 
-%   group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 1) %>% 
-%   mutate(scaled.effect = abs(scale(effect)), scaled.time = scale(study.year)) %>% 
-%   ggplot(aes(x = scaled.time, y = scaled.effect)) + geom_point(size = .5, alpha = 0.2)  + facet_wrap(~outcome.measure.new) +
-%   geom_smooth() + theme_bw() +  ylab("absolute scaled effect")  + ylab("scaled time")
-% @
-% \caption{Absolute values of scaled effect sizes over scaled time, separated for outcome measures.}
-% \label{effects.overtime.separated}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 4
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes.
-This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p3, p4, ncol = 2)
-% @
-% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
-% \label{bias.results.cont.sep}
-% \end{figure}
-% 
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% grid.arrange(p1, p2, ncol = 2)
-% @
-% \caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
-% \label{bias.results.bin.sep}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 5
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% #Proportion of significant pooled estimates based on proportion of single pooled estimates
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type)) + geom_histogram()
-% 
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
-%   geom_density(na.rm = T, position = "fill") + 
-%   labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
-% 
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef), stat(count))) + 
-%   geom_histogram(position = "fill")
-% 
-% mly %>% filter(NA.sig.type == 0) %>% ggplot(aes(x = mean.sig.type, fill = factor(sig.ranef))) + 
-%   geom_histogram()
-
-% \begin{figure}
-% <<echo=FALSE, warning=FALSE>>=
-% plot(p.secondary.over.meansig)
-% @
-% \caption{Fraction of significant meta-analysis, dependent on the fraction of significant single results.}
-% \label{secondary.significance.over.meansig}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Chunck 1
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%which leads to a reduction of the meta-analyses that can be calculated based on the Fisher's z score by $n$ = \Sexpr{}

### 2019-07-12 report/chapter04.Rnw
Report based on the new data

--- 2019-07-05 report/chapter04.Rnw
@@
 load(file.path(PATH_RESULTS, "meta.cont.RData"))
-load(file.path(PATH_RESULTS, "meta.surv.RData"))
+load(file.path(PATH_RESULTS, "meta.iv.RData"))
 load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
@@
 
-# data.ext2 <- pb.process2(data)
+# data.ext2 <- pb.process3(data)
 @
@@
 <<echo=FALSE, warning=FALSE>>=
-meta.f <- meta.f %>% rowwise() %>% mutate(pval1.egger = onesided.p(stat = stat.egger, side = side, n = k, test.type = "reg"),
-                                pval1.thompson = onesided.p(stat = stat.thompson, side = side, n = k, test.type = "reg"),
-                                pval1.begg = onesided.p(stat = stat.begg, side = side, n = k, test.type = "rank"),
-
-                                pval1.harbord = onesided.p(stat = stat.harbord, side = side, n = k, test.type = "reg"),
-                                pval1.rucker = onesided.p(stat = stat.rucker, side = side, n = k, test.type = "reg"),
-                                pval1.peter = onesided.p(stat = stat.peter, side = side, n = k, test.type = "reg"),
-                                pval1.schwarzer = onesided.p(stat = stat.schwarzer, side = side, n = k, test.type = "rank"),
-                                pval1.d.tes = pval.d.tes)
-
-sig.level <- 0.1
-meta.f <- meta.f %>% 
-	mutate(egger.test = ifelse(pval1.egger < sig.level, 1, 0),
-				 thompson.test = ifelse(pval1.thompson < sig.level, 1, 0),
-				 begg.test = ifelse(pval1.begg < sig.level, 1, 0),
-
-				 tes.d.test = ifelse(pval1.d.tes < sig.level, 1, 0),
-
-				 schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
-				 rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
-				 harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
-				 peter.test = ifelse(pval1.peter < sig.level, 1, 0))
-
-meta.bin <- meta.f %>% filter(outcome.type == "bin")
-meta.cont <- meta.f %>% filter(outcome.type == "cont")
-meta.surv <- meta.f %>% filter(outcome.type == "surv")
-
 #Agreement proportions of publication bias tests:
@@
 
-#Survival:
-meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
+#IV:
+meta.iv <- meta.iv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
                                                 thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
@@
                                                 tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+agreement.surv <- meta.iv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
                                                          thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
@@
                                                          egger.begg = sum(egger.begg == "agree")/n())
-meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
+meta.iv <- meta.iv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
                                                 thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
@@
                                                 tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
-agreement.sig.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
+agreement.sig.surv <- meta.iv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
                                                              thompson.tes.d = sum(thompson.tes.d == "agree")/sum(thompson.test),
@@
 test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
+#--------------------------------------------------------------------------------------------------------------------#
 
@@
 meta.f <- meta.f %>% rowwise() %>% 
-  mutate(egger.test = ifelse(pval1.egger < sig.level, 1, 0),
-         thompson.test = ifelse(pval1.thompson < sig.level, 1, 0),
-         begg.test = ifelse(pval1.begg < sig.level, 1, 0),
-
-         schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
-         rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
-         harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
-         peter.test = ifelse(pval1.peter < sig.level, 1, 0),
-         I2 = max(c(0, 1 - (k-1)/Q)),
-         i2f = factor(ifelse(I2 == 0, 1, 0)))
-
-meta.bin <- meta.f %>% filter(outcome.type == "bin")
-meta.cont <- meta.f %>% filter(outcome.type == "cont")
-meta.surv <- meta.f %>% filter(outcome.type == "surv")
+  mutate(i2f = factor(ifelse(I2 == 0, 1, 0)))
+
+meta.bin <- meta.f %>% filter(outcome.flag == "DICH")
+meta.cont <- meta.f %>% filter(outcome.flag == "CONT")
+meta.iv <- meta.f %>% filter(outcome.flag == "IV")
 
@@
 dat_text <- data.frame(
-  label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), sum(meta.surv$thompson.test), sum(meta.surv$tes.d.test, na.rm = T)), "< 0.1,",
-                round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), mean(meta.surv$thompson.test), mean(meta.surv$tes.d.test, na.rm = T)),2)*100, "%"),
+  label = paste(c(sum(meta.iv$begg.test), sum(meta.iv$egger.test), sum(meta.iv$thompson.test), sum(meta.iv$tes.d.test, na.rm = T)), "< 0.1,",
+                round(c(mean(meta.iv$begg.test), mean(meta.iv$egger.test), mean(meta.iv$thompson.test), mean(meta.iv$tes.d.test, na.rm = T)),2)*100, "%"),
   test.type   = c("pval1.begg", "pval1.egger", "pval1.thompson", "pval1.d.tes"),
@@
 
-p.dist.surv <- meta.surv %>% ungroup() %>% 
+p.dist.surv <- meta.iv %>% ungroup() %>% 
   select(i2f, pval1.egger, pval1.thompson, pval1.begg, pval1.d.tes) %>% 
@@
 #--------------------------------------------------------------------------------------------------------------------#
+logit <- function(x) log(x/(1-x))
 
@@
                         summarise(n = n()) %>% 
-                        select(n)/(dim(meta.cont)[1] + dim(meta.surv)[1]) * 100, 1)
+                        select(n)/(dim(meta.cont)[1] + dim(meta.iv)[1]) * 100, 1)
 
@@
 
-meta.f <- meta.f %>% mutate(egger.test = ifelse(pval1.egger < 0.1/3, 1, 0),
+meta.f <- meta.f %>% rowwise() %>% mutate(egger.test = ifelse(pval1.egger < 0.1/3, 1, 0),
                             thompson.test = ifelse(pval1.thompson < 0.1/3, 1, 0),
@@
 There, there is no evidence for publication bias, and the histograms are even skewed to the left (Schwarzer).
-But note that the sample size of survival outcomes is small ($n$ = \Sexpr{dim(meta.surv)[1]}).
+But note that the sample size of survival outcomes is small ($n$ = \Sexpr{dim(meta.iv)[1]}).
 \\
@@
 #Comparison of log hazard ratios:
-sig.d <- meta.f %>% filter(outcome.type == "surv") %>% 
+sig.d <- meta.f %>% filter(outcome.flag == "IV") %>% 
   mutate(d.fixef = est.fixef/se.est.fixef,
@@
 
-adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.type == "surv") %>% 
+adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.flag == "IV") %>% 
   mutate(d.fixef = est.fixef/se.est.fixef,
@@
          i2f = factor(ifelse(I2 == 0, 1, 0)),
-         se.stat.c = ifelse(outcome.type == "bin", stat.rucker, stat.thompson),
+         se.stat.c = ifelse(outcome.flag == "DICH", stat.rucker, stat.thompson),
          se.stat = cut(se.stat.c,
@@
 
-meta.bin <- meta.f %>% filter(outcome.type == "bin")
-meta.cont <- meta.f %>% filter(outcome.type == "cont")
-meta.surv <- meta.f %>% filter(outcome.type == "surv")
+meta.bin <- meta.f %>% filter(outcome.flag == "DICH")
+meta.cont <- meta.f %>% filter(outcome.flag == "CONT")
+meta.iv <- meta.f %>% filter(outcome.flag == "IV")
 
@@
 #Log hazard ratios:
-diff.log.hazard.ratio.fixef <- meta.surv %>% 
+diff.log.hazard.ratio.fixef <- meta.iv %>% 
   mutate(fixef = est.fixef, ranef = est.ranef,
@@
 
-diff.log.hazard.ratio.ranef <- meta.surv %>% 
+diff.log.hazard.ratio.ranef <- meta.iv %>% 
   mutate(fixef = est.fixef, ranef = est.ranef,
@@
 
-adjustmend.diff.surv <- meta.surv %>% 
+adjustmend.diff.surv <- meta.iv %>% 
   transmute(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
@@
 adjustment.diff.comp.errors <- c(4,4,0,0,0,0,0,0)
-adjustment.diff.noest <- c(sum(meta.f$est.z.copas.na[meta.f$outcome.type != "surv"]), 
-                                sum(meta.f$est.z.copas.na[meta.f$outcome.type != "surv"]),
-                                sum(meta.f$est.z.reg.na[meta.f$outcome.type != "surv"]), 
-                                sum(meta.f$est.z.reg.na[meta.f$outcome.type != "surv"]),
-                                sum(meta.f$est.d.copas.na[meta.f$outcome.type != "surv"]), 
-                                sum(meta.f$est.d.copas.na[meta.f$outcome.type != "surv"]),
-                                sum(meta.f$est.d.reg.na[meta.f$outcome.type != "surv"]), 
-                                sum(meta.f$est.d.reg.na[meta.f$outcome.type != "surv"]))
+adjustment.diff.noest <- c(sum(meta.f$est.z.copas.na[meta.f$outcome.flag != "IV"]), 
+                                sum(meta.f$est.z.copas.na[meta.f$outcome.flag != "IV"]),
+                                sum(meta.f$est.z.reg.na[meta.f$outcome.flag != "IV"]), 
+                                sum(meta.f$est.z.reg.na[meta.f$outcome.flag != "IV"]),
+                                sum(meta.f$est.d.copas.na[meta.f$outcome.flag != "IV"]), 
+                                sum(meta.f$est.d.copas.na[meta.f$outcome.flag != "IV"]),
+                                sum(meta.f$est.d.reg.na[meta.f$outcome.flag != "IV"]), 
+                                sum(meta.f$est.d.reg.na[meta.f$outcome.flag != "IV"]))
 adjustment.diff.missing <- (adjustment.diff.comp.errors + adjustment.diff.noest)/apply(m.adjustment.diff, 2, FUN = function(column) length(column))*100
@@
 adjustment.diff.comp.errors.surv <- c(0,0,0,0)
-adjustment.diff.noest.surv <- c(sum(meta.surv$est.copas.na), sum(meta.surv$est.copas.na),
-                                sum(meta.surv$est.reg.na), sum(meta.surv$est.reg.na))
+adjustment.diff.noest.surv <- c(sum(meta.iv$est.copas.na), sum(meta.iv$est.copas.na),
+                                sum(meta.iv$est.reg.na), sum(meta.iv$est.reg.na))
 adjustment.diff.missing.surv <- ((adjustment.diff.comp.errors.surv + adjustment.diff.noest.surv)/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
@@
 missing.differences <- merge(meta.f[,
-        c("meta.id", "file.nr", "comparison.nr", "subgroup.nr",
+        c("meta.id", "id", "comparison.nr", "subgroup.nr",
           "est.z.ranef", "est.z.fixef", "est.z.copas", "est.z.reg", 
@@
 
-missing.differences <- missing.differences %>% mutate(meta.id = as.character(meta.id), file.nr = as.character(meta.id),
+missing.differences <- missing.differences %>% mutate(meta.id = as.character(meta.id), id = as.character(meta.id),
                                                       comparison.nr = as.character(comparison.nr), subgroup.nr = as.character(subgroup.nr))
 
-colnames(missing.differences) <- c("meta.id", "file.nr", "comparison.nr", "subgroup.nr",
+colnames(missing.differences) <- c("meta.id", "id", "comparison.nr", "subgroup.nr",
                                    "z fixed", "z random", "z Copas", "z regression",
@@
 \\
+
+<<echo = FALSE, results = 'asis'>>=
+print(xtable(test.agreement, align = "lcc", caption = "Overall proportion of agreement if significant or unsignificant, and for significance only.
+Horizontal lines separate binary, continuous and IV outcomes (order as in table).
+The reference significance test is the one with more significant results.",
+             label = "test.agreement"),, size = "scriptsize")
+@

### 2019-07-12 code/EDA.R

@@ -1,0 +1,114 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2019-07-04.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results_new')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+require(lme4)
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+load(file.path(PATH_RESULTS, "data2.RData"))
+# data.ext2 <- pb.process3(data)
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+
+load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
+
+
+eda.dat <- data.ext2 %>% filter(meta.id %in% meta.id.vector) #Filter meta-analysis data
+#--------------------------------------------------------------------------------------------------------------------#
+
+#Results meta-analysis properties:
+studies.per.meta <- c(quantile(x = meta.f$k, probs = c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(meta.f$k))
+totalsample.per.meta <- c(quantile(x = meta.f$total.samplesize, probs = c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(meta.f$total.samplesize))
+I2.per.meta <- c(quantile(x = meta.f$I2, probs = c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(meta.f$I2))
+tau.per.meta <- c(quantile(x = meta.f$tau, probs = c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(meta.f$tau))
+variance.ratio.per.meta <- c(quantile(x = meta.f$var.ratio, probs = c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(meta.f$var.ratio))
+
+total.events.per.meta <- c(quantile(x = meta.f$tau, probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T), mean(meta.f$tau, na.rm = T))
+
+meta.properties <- rbind(studies.per.meta, totalsample.per.meta, total.events.per.meta, 
[…]

### 2019-07-12 code/analysis.R

@@ -9,21 +9,21 @@ rm(list = ls())
 PATH_HOME = path.expand("~") # user home
 PATH = file.path(PATH_HOME, 'Data/PubBias')
 PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2018-06-09.csv'
+FILE = 'cochrane_2019-07-04.csv'
 PATH_DATA = file.path(PATH, 'data')
 PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results')
+PATH_RESULTS = file.path(PATH2, 'results_new')
 PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
 
 file_results = "pb.RData"
 
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
 
-file.dat <- "data.RData"
+file.dat <- "data2.RData"
 if (file.exists(file.path(PATH_RESULTS, file.dat))) {
   load(file.path(PATH_RESULTS, file.dat))
 } else {
-  data = pb.readData(path = PATH_DATA, file = FILE)
+  data = pb.readData2(path = PATH_DATA, file = FILE)
   tmp = pb.clean(data)
   data = tmp[[1]]
   aliases = tmp[[2]]
@@ -31,8 +31,7 @@ if (file.exists(file.path(PATH_RESULTS, file.dat))) {
   
 }
 
-
-# data.ext2 <- pb.process2(data)
+# data.ext2 <- pb.process3(data)
 load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
 
 
@@ -46,37 +45,38 @@ load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
 
 # # ---------- Uncomment to run pre-analysis --------------
 # # Get exclusion critetia (I-squared, n. sig. findings, s.e. ratio, dupl.index):
-# meta.info.bin <- data.ext2 %>%
+# meta.info.bin <- data.ext2 %>% filter(outcome.flag == "DICH") %>%
 #   group_by(meta.id) %>%
-#   mutate(n = n()) %>% filter(n >= 10) %>% filter(!is.na(outcome.type)) %>%
-#   filter(meta.id != 94519 & meta.id != 62301) %>%  #Copas convergence..
+#   mutate(n.pre = n()) %>% filter(n.pre >= 10) %>%
+#   # filter(meta.id != 94519 & meta.id != 62301) %>%  #Copas convergence..
[…]

### 2019-07-14 report/MSc_Report.tex
introduction update

@@
 
-Already in 1978, scientists raised concern that effect sizes could be overestimated systematically if journals were ``not willing to drop their policy to use statistical significance as one of their criteria for publication'' \citep{dunlap1978}.
-Scientific findings get more attention and are more likely to be published, read and cited if they are implying large effects.
+Studies get more attention and are more likely to be published, read and cited if they are implying large effects.
+Studies with no evidence for an effect are less likely to get published.
+This generates a bias called ``publication bias'', which distorts the view of the evidence for an effect.
+Recently, publication bias has been identified as one of the major concerns in irreproducible research \citep{Bishop.2019}.
 The issue has been pin-pointed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}).
-The concern is that overestimated efficacy of the treatments could lead to harm to patients.
-\\
-A measure to counter the presence of single, overestimated study results is a meta-analysis \citep{metaanalysis}, a practice originally developped in psychology.
+In medical research, clinical trials study the efficacy of therapies and drugs.
+The gold standard in such intervention studies are randomized, (placebo) controlled, trials (RCTs).
+Results from such clinical studies influence the treatment of patients in daily clinical practice.
+The results from multiple intervention studies are summarized in meta-analyses and reflect the overall evidence for a treatment effect.
 Summarized treatment effects and uncertainities should be more robust and reliable.
-The pitfall is that when the entire body of evidence is again a biased sample of studies with high effects, the estimate is again overestimating the true effect.
-There is extensive literature on publication bias in meta-analyses, e.g.
-(\citet{pb.clinicalscience.2013}, %\citet{Hopewell02},
+Publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm.
+\\
+There is extensive literature on publication bias in meta-analyses, e.g. (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02}, 
 \citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}). 
-All authors agree in that the inclusion of unpublished results in meta-analyses is insufficient and responsible for overestimation of treatment efficacy.
+All authors agree in that the exclusion of unpublished results in meta-analyses is responsible for overestimation of treatment effects.
 Although there are policies that make it mandatory to make accessible all study results \citep{fda}, it is not clear if the situation has improved yet.\\
 The Cochrane Organisation has specialized on systematic reviews of healthcare interventions.
-Methodological and field experts collect data, review them and try to provide up-to-date information about specific treatment efficacies \citep{cochrane.handbook}.
+Researchers that write a systematic review collect data across studies, review them and try to provide up-to-date information about specific treatment efficacies \citep{cochrane.handbook}.
 By extensive literature scrutinization, they try to circumvent the issue of publication bias.
-Earlier research however suggests that the efforts are only partially succesfull, and that there still is publication bias within the reviews (\citet{Egger}, \citet{Ioannidis2007}, \citet{kicinsky}, \citet{vanAert.2019}).
-However, none of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods.
+Earlier research however suggests that the efforts are only partially succesful, and that there still is publication bias within the reviews (\citet{Egger}, \citet{Ioannidis2007}, \citet{kicinsky}, \citet{vanAert.2019}).
+In this publications, the results of a part of the Cochrane Database of systematic reviews is analysed with small study effect tests or bayesian hierarchical selection models \citep{kicinsky}.
+They all find moderate to large evidence for publication bias in the Database.
+A more thorough discussion of their methods and results will follow in chapter \ref{ch:Discussion}.
+None of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods.
 Also, the results are often presented in the form of dichotomized hypothesis tests, a practice known to contribute to publication bias itself (cite sb).\\
@@
 
-% 
+\subsection{Analysing publication bias}
+There are multiple ways to assess the amount of publication bias.
+For instance, one can follow studies and control if they are getting published depending on their findings \citep{publication.fate}.
+One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in social sciences: \citet{social.sciences.publication.bias}).
+Another way is to compare results in study registries with results published in journals (\eg \citet{pb.clinicalscience.2013}).
+Again one finds systematic differences between published and unpublished results.
+\\
+A third way is to assess the so-called small study effect in a meta-analysis, that is, a systematic difference between effects of large and small studies.
+Evidence for small study effects can oftentimes be interpreted as evidence for publication bias \citep{Egger}.
+The underlying rational is that journal editors are guided by two simple rules (\citet{excess.significance}, \citet{ioannidis.2019}):
+\begin{itemize}
+\item Publish new and trend-setting findings that lead to many citations, increasing the journal impact factor (JIF).
+\item Publish large trials that are likely to set the standard for a given scientific question, again to increase the JIF.
+\end{itemize}
+This then leads to the so-called asymmetry in the funnel plot of published studies; small studies show larger effect sizes than larger studies do.
+By means of simple linear regression, one can investigate how much evidence there is for this asymmetry.
+For illustration purposes, a meta-analysis with large funnel plot asymmetry is shown %\citep{pre.eclampsia}:
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-1-1}
+
+\end{knitrout}
+\end{figure}
+
+The purpose of a funnel plot is to visualise if an how the estimated treatment effects converge to a common ``real'' treatment effect value (here, the weighted mean treatment effect with weights = inverse variances).
+This is also shown by the triangle depicted by the dotted line (the spire is at the weighted mean).
+\\
+We see that while the studies in the meta-analysis on the left are not filling the triangle evenly, but rather accumulate at the left side, they seem to be more evenly distributed in the left triangle.
+From this, we would ultimately conclude that some sort of bias or heterogeneity is distorting the estimate of the overall treatment effect.\\
+Importantly, this method does not assess publication bias directly.
+But note that publication bias is also not assessable with the other methods if no complete study registries are available.
+Thus, the estimation of small study effects is oftentimes the most efficient and simple way to analyse publication bias.
+
+% Already in 1978, scientists raised concern that effect sizes could be overestimated systematically if journals were ``not willing to drop their policy to use statistical significance as one of their criteria for publication'' \citep{dunlap1978}.
+Scientific findings get more attention and are more likely to be published, read and cited if they are implying large effects.
+The issue has been pin-pointed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}).
+The concern is that overestimated efficacy of the treatments could lead to harm to patients.
+\\
+% A measure to counter the presence of single, overestimated study results is a meta-analysis \citep{metaanalysis}, a practice originally developped in psychology.
+Summarized treatment effects and uncertainities should be more robust and reliable.
+The pitfall is that when the entire body of evidence is again a biased sample of studies with high effects, the estimate is again overestimating the true effect.
+% % 
 % 
@@
 
-\subsection{Adjustment by Regression}
+\subsection{Adjustment by Regression} \label{sec:regression.adjustment}
 \citet{limitmeta} use a random effects model %together with shrinkage procedure 
@@
 % LaTeX file for Chapter 03
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in arrange\_impl(.data, dots): Evaluation error: object 'Study' not found.}}\end{kframe}
-\end{knitrout}
 
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(barbi1, label = "{}barbiturate.row"{}, digits = 0, caption = "{}Example of two results as given in the dataset.
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Jul 14 14:23:32 2019
+\begin{table}[ht]
+\centering
+\begingroup\scriptsize
+\begin{tabular}{lllrrrr}
+  \hline
+study.name & comparison.name & outcome.name & events1 & total1 & events2 & total2 \\ 
+  \hline
+Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11 & 41 & 11 & 41 \\ 
+  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14 & 27 & 13 & 26 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Example of two results as given in the dataset.
 Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
-Further descriptive variables have been ommitted"{}): object 'barbi1' not found}}\end{kframe}
+Further descriptive variables have been ommitted}
+\label{barbiturate.row}
+\end{table}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Jul 12 10:30:39 2019
+% Sun Jul 14 14:23:32 2019
 \begin{table}[ht]
@@
   \hline
-Study & Comparison & Outcome \\ 
+study.name & comparison.name & outcome.name \\ 
   \hline
@@
 {\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Jul 12 10:30:39 2019
+% Sun Jul 14 14:23:32 2019
 \begin{table}[ht]
@@
     \node [ublock, below of=7, node distance=4cm] (8) {Binary data: \\
-    2,226 meta-analyses};
+    2,217 meta-analyses};
 
     \node [ublock, right of=8, node distance=5cm] (9) {Continuous data: \\
-    629 meta-analyses};
+    604 meta-analyses};
 
@@
     \node [final, below of=8, node distance=2.4cm] (11) {Analysis dataset (2):
-    860 reviews,
-    18,238 studies,
-    49,568 results,
-    2,855 meta-analyses};
+    848 reviews,
+    18,101 studies,
+    49,010 results,
+    2,821 meta-analyses};
 
@@
 \subsubsection{Exclusions due to Computational Errors}
-There has been cases where meta-analyses could not be analysed with Copas selection model because the likelihood function could not be optimized based on the settings.
-It was ommitted in this case.
-The analysis failed when using $z$-scores, but not standardized mean differences, and in that case, it was not ommitted.\\
-The specific information about the meta-analysis is: \texttt{meta.id} = 220949, \texttt{id} = ``CD009908'', \texttt{subgroup.id} = ``CMP-001.05.02''.
+There has been cases where meta-analyses could not be analysed with Copas selection model because the likelihood function could not be optimized based on the settings. It was ommitted in this case.\\
+\begin{itemize}
+\item Meta-analysis with \texttt{meta.id} = 93868,  \texttt{id} = ``CD004072'', \texttt{subgroup.id} = ``CMP-006.08.01''.
+One small meta-analysis (\texttt{se.new} = 1.02) with a risk ratio 0.072, while the remaining risk ratios were all larger than 0.45.
+(and the fixed effects estimate close to 1).
+It failed when analysed based on log risk ratios.
+\item Meta-analysis with \texttt{meta.id} = 144568,  \texttt{id} = ``CD006109'', \texttt{outcome.id} = ``CMP-001.06'' and \texttt{outcome.measure} ``MD''.
+$z$-score based analysis failed, although funnel plot looks more or less symmetric.
+Small studies with very similar \texttt{var.z} with $z$-scores 0.3 and -0.1.
+\item Meta-analysis with \texttt{meta.id} = 35673,  \texttt{id} = ``CD001790'', \texttt{outcome.id} = ``CMP-001.03'' and \texttt{outcome.measure} = ``PETO.OR''.
+Analysis failed when using Hedges $g$ transformed effects.
+Large studies have $g \sim 0$ while one smaller study ($\se = 0.3$) has $g = 1$ (and another with a little larger $\se$ has $g \sim 0$).
+\end{itemize}
+Because the number of errors is low, the meta-analyses have only been ommitted for the specific outcome measures, but are kept in the others.
 
@@
 The dataset that was ultimately tested and adjusted for publication bias comprises 1 meta-analyses and 53012 results.
-The mean number of participants in the treatment group is 212.6072021 vs 256.7062871 in the unrestricted dataset and the mean total number of participants 465.5000189 vs 623.15692.
+The mean number of participants in the treatment group is 212.6 vs 256.7 in the unrestricted dataset and the mean total number of participants 465.5 vs 623.2.
 The mean publication year is 2000.0251806 vs 2000.9710727 in the unrestricted dataset.
 \\
-From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}}), there are 1 with \texttt{outcome.measure.new} = ..., 1 ...,  1 ... and 2 ... .
+From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}), there are 55 with \\ \texttt{outcome.measure.new} = ``Risk Ratio'', 47 ``Std.
+Mean Difference'',  35 ``Hazard Ratio'' and 22 ``Odds Ratio'' (and 25 additional, different outcome measures).
 
@@
 The tests are applied on the original effect size measures, i.e.
-risk ratios, Hedges $g$ or log hazard ratios.
-Different tests are applied depending on the outcome type being binary, continuous or survival.\\
+risk ratios, Hedges $g$ or other effect measures (\texttt{outcome.flag} = \texttt{IV}).
+Different tests are applied depending on the outcome type being binary, continuous or IV.\\
 Thus, multiple tests are applied on the same data.
@@
 ``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}.
-For continuous and survival outcomes, the names refer to:
+For continuous and IV outcomes, the names refer to:
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-10-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-11-1}
+
+}
 
@@
 The histograms in Figure \ref{fig:test} show that most distributions are clearly skewed to the right, indicating evidence for small study effects.
-Exceptions from this are the excess significance and Schwarzer's test, and the tests for survival outcomes.
+Exceptions from this are the excess significance and Schwarzer's test, and the tests for IV outcomes.
 There, there is no evidence for publication bias, and the histograms are even skewed to the left (Schwarzer).
-But note that the sample size of survival outcomes is small ($n$ = 238).
+But note that the sample size of IV outcomes is small ($n$ = 238).
 \\
@@
 This is done in Figure \ref{fig:test.agreement}.
-Here, there is no separation between survival and continuous outcomes.
-The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results.
+Here, there is no separation between IV and continuous outcomes.
+The upper left rectangle is displaying binary outcome results and the lower right continuous and IV outcomes results.
 Also, the $I^2$ statistic is included.
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-11-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-12-1}
+
+}
 
@@
 Regression based tests as Egger and Thompsons test which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients.
-Continuous and survival outcome type tests align more closely than binary outcome tests.
+Continuous and IV outcome type tests align more closely than binary outcome tests.
 While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics.\\
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-12-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-13-1}
+
+}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Jul 12 20:14:43 2019
+% Sun Jul 14 14:40:23 2019
 \begin{table}[ht]
@@
   \hline
-Count & Binary Outcomes & Continuous and Survival \\ 
+Count & Binary Outcomes & Continuous and IV \\ 
   \hline
@@
 \caption{Counts Number of significant test results per meta-analysis, separated
-       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
+       for outcome types. Last entry for continuous and IV outcomes is empty since one test less was 
        applied} 
@@
 
-Here, it is difficult to say if continuous and survival or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and survival outcome type tests have in general more positive findings.
+Here, it is difficult to say if continuous and IV or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and IV outcome type tests have in general more positive findings.
 Very few meta-analyses are significant, irrespective of the test used, but around 67\% of the dataset is not significant, no matter which test is used.
 \\
-When only looking at small study effect tests, 29.5\% of binary outcome tests and 29.5\% of survival and continuous outcome tests had at least one significant result.
-After applying the Bonferroni correction for multiple testing, this shrinks to 12.6\% for binary and 12.7\% for continuous and survival outcomes.
+When only looking at small study effect tests, 29.5\% of binary outcome tests and 29.5\% of IV and continuous outcome tests had at least one significant result.
+After applying the Bonferroni correction for multiple testing, this shrinks to 12.6\% for binary and 12.7\% for continuous and IV outcomes.
 \\
 % To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test.
-mean.min.bin2\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, mean.min.else2\% for continuous and survival outcomes.
-The numbers change to mean.min.bin2.b\% for binary outcomes and mean.min.else2.b\% for continuous and survival outcomes after applying the Bonferroni correction.
+mean.min.bin2\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, mean.min.else2\% for continuous and IV outcomes.
+The numbers change to mean.min.bin2.b\% for binary outcomes and mean.min.else2.b\% for continuous and IV outcomes after applying the Bonferroni correction.
 \\
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-15-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-16-1}
+
+}
 
@@
 We see that more treatment effect sizes are negatively adjusted and diminished.
-Furthermore, we see that large adjustment is not necessarily connected with evidence for small study effects, but there is of course strong coincidence.
-The cases with no evidence and large adjustment indicate that between-study heterogeneity was not resolved by adjustment for small study effects.
+Furthermore, we see that large adjustment is not necessarily connected with evidence for small study effects, but there is coincidence.
 Adjustment was larger when random effects meta-analysis effect is used as reference, because there larger weights are given to small studies.\\
+The cases with no evidence (clear green color) and large adjustment indicate that between-study heterogeneity was not resolved by adjustment for small study effects.
+The regression adjustment method as described in section \ref{sec:regression.adjustment} adjusts for small study effects even if there is no evidence for small study effects.
+Thus, a large change in effect sizes does not necessarily have to be accompained by evidence for small study effects, because the unceratinity of the small study effect is not taken into account by the adjustment method.
+The uncertainity of the adjusted estimates is consequently larger in the clear green fraction of the histogramm than in the deeper green fraction.\\
 Figure \ref{fig:adjustment.copas} shows the same for effect sizes adjusted by Copas; Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-16-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-17-1}
+
+}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Jul 12 20:15:09 2019
+% Sun Jul 14 14:40:50 2019
 \begin{table}[ht]
@@
 Thus, also the evidence for efficacy of a treatment can be obtained, which is usually summarized in a suitable test statistic or $p$-value.
-It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.\\
+It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.
+There is an important difference between Copas selection model and regression adjustment.
+The regression adjustment method incorporates an additional parameter with corresponding uncertainity in the treatment effect estimate, while the application of the Copas algorithm does not so.
+Instead, the copas selection model derives the uncertainity of the estimate from the inverse of the fisher information matrix of the likelihood.
+Additionally, the Copas selection model algorithm provides only an estimate when it can detect a small study effect with reasonable precision at the first place (see \ref{sec:copas}).\\
 The Wald test statistics $p$-value for fixed and random effects meta-analyses and Copas and regression adjusted treatment effects have been calculated.
-They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and log hazard ratios.
+They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and other effect measures (\texttt{outcome.flag} = \texttt{IV}).
 \\
@@
 %Also, the evidence decreases for random effects meta-analyses compared to fixed effects meta-analyses. 
-In the case of log-hazard ratio adjustment, the adjustment has only negligible impact on the $p$-values. \\
+In the case of other effect measures (\texttt{outcome.flag} = \texttt{IV}) adjustment, the adjustment has only negligible impact on the $p$-values. \\
 Also, Copas selection method has a very small impact on the evidence compared to random effects meta-analysis, at least using $z$-scores (again, we should rely on comparisons to random effects meta-analysis to evaluate Copas method).
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-18-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-19-1}
+
+}
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-19-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-20-1}
+
+}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Jul 12 20:15:10 2019
+% Sun Jul 14 14:40:51 2019
 \begin{table}[ht]
@@
 original measure, $z$-score and Hedges $g$ in Figure \ref{fig:adjustment.mean.diff}.
-Note that the 39 survival outcome data is not included when using $z$-score and Hedges $g$.
+Note that the 238 IV outcome data is not included when using $z$-score and Hedges $g$.
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-22-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-23-1}
+
+}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Jul 12 20:15:11 2019
+% Sun Jul 14 14:40:52 2019
 \begin{table}[ht]
@@
   Egger, Begg & 0.84 & 0.72 \\ 
-  Excess significance, Egger (survival) & 0.84 & 0.08 \\ 
-  Excess significance, Thompson (survival) & 0.86 & 0.09 \\ 
-  Excess significance, Begg (survival) & 0.86 & 0.09 \\ 
-  Thompson, Egger (survival) & 0.96 & 0.94 \\ 
-  Thompson, Begg (survival) & 0.88 & 0.56 \\ 
-  Egger, Begg (survival) & 0.87 & 0.59 \\ 
+  Excess significance, Egger (IV) & 0.84 & 0.08 \\ 
+  Excess significance, Thompson (IV) & 0.86 & 0.09 \\ 
+  Excess significance, Begg (IV) & 0.86 & 0.09 \\ 
+  Thompson, Egger (IV) & 0.96 & 0.94 \\ 
+  Thompson, Begg (IV) & 0.88 & 0.56 \\ 
+  Egger, Begg (IV) & 0.87 & 0.59 \\ 
    \hline

### 2019-07-14 report/chapter01.Rnw
introduction update

@@
 A more thorough discussion of their methods and results will follow in chapter \ref{ch:Discussion}.
-However, none of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods.
+None of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods.
 Also, the results are often presented in the form of dichotomized hypothesis tests, a practice known to contribute to publication bias itself (cite sb).\\
@@
 
-Already in 1978, scientists raised concern that effect sizes could be overestimated systematically if journals were ``not willing to drop their policy to use statistical significance as one of their criteria for publication'' \citep{dunlap1978}.
+\subsection{Analysing publication bias}
+There are multiple ways to assess the amount of publication bias.
+For instance, one can follow studies and control if they are getting published depending on their findings \citep{publication.fate}.
+One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in social sciences: \citet{social.sciences.publication.bias}).
+Another way is to compare results in study registries with results published in journals (\eg \citet{pb.clinicalscience.2013}).
+Again one finds systematic differences between published and unpublished results.
+\\
+A third way is to assess the so-called small study effect in a meta-analysis, that is, a systematic difference between effects of large and small studies.
+Evidence for small study effects can oftentimes be interpreted as evidence for publication bias \citep{Egger}.
+The underlying rational is that journal editors are guided by two simple rules (\citet{excess.significance}, \citet{ioannidis.2019}):
+\begin{itemize}
+\item Publish new and trend-setting findings that lead to many citations, increasing the journal impact factor (JIF).
+\item Publish large trials that are likely to set the standard for a given scientific question, again to increase the JIF.
+\end{itemize}
+This then leads to the so-called asymmetry in the funnel plot of published studies; small studies show larger effect sizes than larger studies do.
+By means of simple linear regression, one can investigate how much evidence there is for this asymmetry.
+For illustration purposes, a meta-analysis with large funnel plot asymmetry is shown %\citep{pre.eclampsia}:
+
+\begin{figure}
+<<echo = FALSE, fig.height = 3>>=
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2019-07-04.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results_new')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+
+pb.ex <- 111673
+require(meta)
+require(tidyverse)
+par(mfrow = c(1,2))
+tp <- data.ext2 %>% filter(meta.id == pb.ex)
+funnel(metabin(event.e = events1, event.c = events2, n.e = total1, n.c = total2, data = tp),
+       comb.fixed = F, comb.random = F)
+
+nopb.ex <- meta.f$meta.id[32]
+tp <- data.ext2 %>% filter(meta.id == nopb.ex)
+funnel(metabin(event.e = events1, event.c = events2, n.e = total1, n.c = total2, data = tp),
+       comb.fixed = F, comb.random = F)
+@
+\end{figure}
+
+The purpose of a funnel plot is to visualise if an how the estimated treatment effects converge to a common ``real'' treatment effect value (here, the weighted mean treatment effect with weights = inverse variances).
+This is also shown by the triangle depicted by the dotted line (the spire is at the weighted mean).
+\\
+We see that while the studies in the meta-analysis on the left are not filling the triangle evenly, but rather accumulate at the left side, they seem to be more evenly distributed in the left triangle.
+From this, we would ultimately conclude that some sort of bias or heterogeneity is distorting the estimate of the overall treatment effect.\\
+Importantly, this method does not assess publication bias directly.
+But note that publication bias is also not assessable with the other methods if no complete study registries are available.
+Thus, the estimation of small study effects is oftentimes the most efficient and simple way to analyse publication bias.
+
+% Already in 1978, scientists raised concern that effect sizes could be overestimated systematically if journals were ``not willing to drop their policy to use statistical significance as one of their criteria for publication'' \citep{dunlap1978}.
 Scientific findings get more attention and are more likely to be published, read and cited if they are implying large effects.
@@
 \\
-A measure to counter the presence of single, overestimated study results is a meta-analysis \citep{metaanalysis}, a practice originally developped in psychology.
+% A measure to counter the presence of single, overestimated study results is a meta-analysis \citep{metaanalysis}, a practice originally developped in psychology.
 Summarized treatment effects and uncertainities should be more robust and reliable.
 The pitfall is that when the entire body of evidence is again a biased sample of studies with high effects, the estimate is again overestimating the true effect.
-% 
+% % 
 % 

### 2019-07-14 report/chapter02.Rnw
Report based on the new data
introduction update

@@
 
-\section{Transformation between effect sizes} \label{sec:transformation.effectsizes}
+\section{Transformation between Effect Measures} \label{sec:transformation.effectsizes}
 Assuming that binary outcomes result from a dichotomization of originally continuous random variables, in this case, the logistic distribution, a transformation from typical binary effect measures to Cohen's $d$ can be achieved \cite[47]{Intro.meta}.

### 2019-07-14 report/chapter03.Rnw
introduction update

@@
                  events1, total1, events2, total2) %>% 
-            slice(c(1,3)), Study) 
+            slice(c(1,3)), study.name) 
 barbi2 <- arrange(filter(data, id == "CD000033") %>% 
-          select(Study = study.name, Comparison = comparison.name,Outcome = outcome.name), Study)
-barbi2[barbi2$Study == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
+          select(study.name, comparison.name, outcome.name), study.name)
+barbi2[barbi2$study.name == "P\303\251rez-B\303\241rcena 2008", 1] = "Perez-Barcena 2008"
 #----------------------------------------------------------------------------------------------#
@@
 # "IV" outcome.flag meta-analyses
-dt <- meta.iv %>% group_by(outcome.measure.new) %>% count
+dt <- meta.iv %>% group_by(outcome.measure.new) %>% count %>% arrange(desc(n))
 first.iv.outcome.count <- dt$n[1]
@@
 The dataset that was ultimately tested and adjusted for publication bias comprises \Sexpr{length(meta.id.vector)} meta-analyses and \Sexpr{dim(meta.data)[1]} results.
-The mean number of participants in the treatment group is \Sexpr{mean(meta.data$total1, na.rm = T)} vs \Sexpr{mean(data.ext2$total1, na.rm = T)} in the unrestricted dataset and the mean total number of participants \Sexpr{mean(meta.data$total1 + meta.data$total2)} vs \Sexpr{mean(data.ext2$total1 + data.ext2$total2)}.
+The mean number of participants in the treatment group is \Sexpr{round(mean(meta.data$total1, na.rm = T),1)} vs \Sexpr{round(mean(data.ext2$total1, na.rm = T),1)} in the unrestricted dataset and the mean total number of participants \Sexpr{round(mean(meta.data$total1 + meta.data$total2),1)} vs \Sexpr{round(mean(data.ext2$total1 + data.ext2$total2),1)}.
 The mean publication year is \Sexpr{mean(meta.data$study.year, na.rm = TRUE)} vs \Sexpr{mean(data.ext2$study.year, na.rm = TRUE)} in the unrestricted dataset.
 \\
-From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}}), there are \Sexpr{first.iv.outcome.count} with \texttt{outcome.measure.new} = ..., \Sexpr{second.iv.outcome.count} ...,  \Sexpr{third.iv.outcome.count} ...
-and \Sexpr{fourth.iv.outcome.count} ...
-.
+From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}), there are \Sexpr{first.iv.outcome.count} with \\ \texttt{outcome.measure.new} = ``Risk Ratio'', \Sexpr{second.iv.outcome.count} ``Std.
+Mean Difference'',  \Sexpr{third.iv.outcome.count} ``Hazard Ratio'' and \Sexpr{fourth.iv.outcome.count} ``Odds Ratio'' (and 25 additional, different outcome measures).
 

### 2019-07-14 report/chapter04.Rnw
introduction update

@@
                                                 tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
-agreement.surv <- meta.iv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
+agreement.iv <- meta.iv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
                                                          thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
@@
                                                 tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
-agreement.sig.surv <- meta.iv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
+agreement.sig.iv <- meta.iv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
                                                              thompson.tes.d = sum(thompson.tes.d == "agree")/sum(thompson.test),
@@
 
-surv.tests.agreement <- rbind(agreement.surv, agreement.sig.surv)
-rownames(surv.tests.agreement) <- c("Agreement (overall)","Agreement (significance)")
-colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)",
-                                    "Excess significance, Begg (survival)", "Thompson, Egger (survival)",
-                                    "Thompson, Begg (survival)", "Egger, Begg (survival)")
+iv.tests.agreement <- rbind(agreement.iv, agreement.sig.iv)
+rownames(iv.tests.agreement) <- c("Agreement (overall)","Agreement (significance)")
+colnames(iv.tests.agreement) <- c("Excess significance, Egger (IV)", "Excess significance, Thompson (IV)",
+                                    "Excess significance, Begg (IV)", "Thompson, Egger (IV)",
+                                    "Thompson, Begg (IV)", "Egger, Begg (IV)")
 
@@
 #Merging:
-test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))
+test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(iv.tests.agreement))
 #--------------------------------------------------------------------------------------------------------------------#
@@
   gather(key = "test.type", value = "p.value", pval1.harbord:pval1.schwarzer) %>% 
-  ggplot(aes(x = p.value, fill = i2f)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
+  ggplot(aes(x = p.value, fill = i2f)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
+  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
   geom_text(data = dat_text, mapping = aes(x = 0.5, y = 200, label = label), color = "black") + 
@@
 
-p.dist.surv <- meta.iv %>% ungroup() %>% 
+p.dist.iv <- meta.iv %>% ungroup() %>% 
   select(i2f, pval1.egger, pval1.thompson, pval1.begg, pval1.d.tes) %>% 
@@
   guides(fill=guide_legend(title=expression(paste(I^2, " Heterogeneity")))) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 10, label = label),  color = "black")  + 
+  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 40, label = label),  color = "black")  + 
   scale_fill_discrete(labels = c("> 0", "= 0")) +
   theme(strip.text.x = element_text(size=7)) + 
-  ggtitle("Survival Outcomes") 
+  ggtitle("IV Outcomes") 
 #--------------------------------------------------------------------------------------------------------------------#
@@
          difference = logit(pval1.egger) - logit(pval1.thompson)) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point() + 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
   geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
@@
          difference = logit(pval1.egger) - logit(pval1.d.tes)) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point() + 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
   geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
@@
          difference = logit(pval1.harbord) - logit(pval1.rucker)) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = .4) + 
   geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
@@
          difference = logit(pval1.harbord) - logit(pval1.d.tes)) %>% 
-  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
+  ggplot(aes(x = mean, y = difference)) + geom_point(size = .4) + 
   geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
@@
 
-colnames(number.sig.tests) <- c("Count", "Binary Outcomes", "Continuous and Survival")
+colnames(number.sig.tests) <- c("Count", "Binary Outcomes", "Continuous and IV")
 
@@
              p.dist.cont,
-             p.dist.surv, ncol = 1)
+             p.dist.iv, ncol = 1)
 @
@@
 The histograms in Figure \ref{fig:test} show that most distributions are clearly skewed to the right, indicating evidence for small study effects.
-Exceptions from this are the excess significance and Schwarzer's test, and the tests for survival outcomes.
+Exceptions from this are the excess significance and Schwarzer's test, and the tests for IV outcomes.
 There, there is no evidence for publication bias, and the histograms are even skewed to the left (Schwarzer).
-But note that the sample size of survival outcomes is small ($n$ = \Sexpr{dim(meta.iv)[1]}).
+But note that the sample size of IV outcomes is small ($n$ = \Sexpr{dim(meta.iv)[1]}).
 \\
@@
 print(xtable(number.sig.tests, caption = "Counts Number of significant test results per meta-analysis, separated
-       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
+       for outcome types. Last entry for continuous and IV outcomes is empty since one test less was 
        applied", label = "number.sig.tests", align = "lccc"), include.rownames = F, size = "footnotesize")
@@
 
-Here, it is difficult to say if continuous and survival or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and survival outcome type tests have in general more positive findings.
+Here, it is difficult to say if continuous and IV or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and IV outcome type tests have in general more positive findings.
 Very few meta-analyses are significant, irrespective of the test used, but around 67\% of the dataset is not significant, no matter which test is used.
 \\
-When only looking at small study effect tests, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of survival and continuous outcome tests had at least one significant result.
-After applying the Bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\% for binary and \Sexpr{mean.min.else.b}\% for continuous and survival outcomes.
+When only looking at small study effect tests, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of IV and continuous outcome tests had at least one significant result.
+After applying the Bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\% for binary and \Sexpr{mean.min.else.b}\% for continuous and IV outcomes.
 \\
 % To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test.
-\Sexpr{mean.min.bin2}\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, \Sexpr{mean.min.else2}\% for continuous and survival outcomes.
-The numbers change to \Sexpr{mean.min.bin2.b}\% for binary outcomes and \Sexpr{mean.min.else2.b}\% for continuous and survival outcomes after applying the Bonferroni correction.
+\Sexpr{mean.min.bin2}\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, \Sexpr{mean.min.else2}\% for continuous and IV outcomes.
+The numbers change to \Sexpr{mean.min.bin2.b}\% for binary outcomes and \Sexpr{mean.min.else2.b}\% for continuous and IV outcomes after applying the Bonferroni correction.
 \\
@@
   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-  geom_text(data = sig.d, aes(x = 0.00003, y = 20, label = label), position = "dodge") + 
+  geom_text(data = sig.d, aes(x = 0.5, y = 100, label = label), position = "dodge") + 
   xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
-  ggtitle(expression(paste("Log hazard ratio ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+  ggtitle(expression(paste("Log IV outcome measures ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
 #--------------------------------------------------------------------------------------------------------------------#
@@
   geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + xlab("Fixed effects - adjusted log hazard ratio") + geom_vline(xintercept = 0, linetype = "dashed" )
+  facet_wrap(~method) + theme_bw() + xlab("Fixed effects - adjusted log effect") + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
   geom_histogram(binwidth = 0.1, center = 0) +
-  facet_wrap(~method) + theme_bw() + xlab("Random effects - adjusted log hazard ratio") + geom_vline(xintercept = 0, linetype = "dashed" )
+  facet_wrap(~method) + theme_bw() + xlab("Random effects - adjusted log effect") + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
 
-adjustmend.diff.surv <- meta.iv %>% 
+adjustmend.diff.iv <- meta.iv %>% 
   transmute(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
@@
 
-  transmute(copas.surv.f = est.fixef - est.copas.f,
-            copas.surv.r = est.ranef - est.copas.r,
-
-            reg.surv.f =  est.fixef - est.reg.f,
-            reg.surv.r = est.ranef - est.reg.r)
-
-m.adjustment.diff.surv <- as.matrix(adjustmend.diff.surv)
+  transmute(copas.iv.f = est.fixef - est.copas.f,
+            copas.iv.r = est.ranef - est.copas.r,
+
+            reg.iv.f =  est.fixef - est.reg.f,
+            reg.iv.r = est.ranef - est.reg.r)
+
+m.adjustment.diff.iv <- as.matrix(adjustmend.diff.iv)
 
@@
 
-adjustment.diff.quantile.table.surv <- apply(m.adjustment.diff.surv, 2, 
+adjustment.diff.quantile.table.iv <- apply(m.adjustment.diff.iv, 2, 
                                              FUN = function(column){quantile(x = column, 
                                                                              probs = c(0.05, 0.25, 0.5, 0.75, 0.95), na.rm = T)})
-adjustment.diff.mean.surv <- apply(m.adjustment.diff.surv, 2, FUN = function(column) mean(column, na.rm = T))
-adjustment.diff.largerzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
-adjustment.diff.equalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
-adjustment.diff.largerequalzero.surv <- (apply(m.adjustment.diff.surv, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
-adjustment.diff.comp.errors.surv <- c(0,0,0,0)
-adjustment.diff.noest.surv <- c(sum(meta.iv$est.copas.na), sum(meta.iv$est.copas.na),
+adjustment.diff.mean.iv <- apply(m.adjustment.diff.iv, 2, FUN = function(column) mean(column, na.rm = T))
+adjustment.diff.largerzero.iv <- (apply(m.adjustment.diff.iv, 2, FUN = function(column) length(which(column >= 0)))/apply(m.adjustment.diff.iv, 2, FUN = function(column) length(column)))*100
+adjustment.diff.equalzero.iv <- (apply(m.adjustment.diff.iv, 2, FUN = function(column) length(which(column == 0)))/apply(m.adjustment.diff.iv, 2, FUN = function(column) length(column)))*100
+adjustment.diff.largerequalzero.iv <- (apply(m.adjustment.diff.iv, 2, FUN = function(column) length(which(column > 0)))/apply(m.adjustment.diff.iv, 2, FUN = function(column) length(column)))*100
+adjustment.diff.comp.errors.iv <- c(0,0,0,0)
+adjustment.diff.noest.iv <- c(sum(meta.iv$est.copas.na), sum(meta.iv$est.copas.na),
                                 sum(meta.iv$est.reg.na), sum(meta.iv$est.reg.na))
-adjustment.diff.missing.surv <- ((adjustment.diff.comp.errors.surv + adjustment.diff.noest.surv)/apply(m.adjustment.diff.surv, 2, FUN = function(column) length(column)))*100
-
-adjustment.diff.table.surv <- rbind(adjustment.diff.quantile.table.surv, mean = adjustment.diff.mean.surv,
-                                    equalzero = adjustment.diff.equalzero.surv,
-                                    largerequal = adjustment.diff.largerequalzero.surv, larger = adjustment.diff.largerzero.surv,
-                                    missing = adjustment.diff.missing.surv)
-
-adjustment.diff.table <- cbind(adjustment.diff.table, (adjustment.diff.table.surv))
+adjustment.diff.missing.iv <- ((adjustment.diff.comp.errors.iv + adjustment.diff.noest.iv)/apply(m.adjustment.diff.iv, 2, FUN = function(column) length(column)))*100
+
+adjustment.diff.table.iv <- rbind(adjustment.diff.quantile.table.iv, mean = adjustment.diff.mean.iv,
+                                    equalzero = adjustment.diff.equalzero.iv,
+                                    largerequal = adjustment.diff.largerequalzero.iv, larger = adjustment.diff.largerzero.iv,
+                                    missing = adjustment.diff.missing.iv)
+
+adjustment.diff.table <- cbind(adjustment.diff.table, (adjustment.diff.table.iv))
 
@@
   mutate(mean = (est.copas + est.reg)/2, 
-         difference = est.copas - est.reg) %>% 
+         difference = est.copas - est.reg) %>% filter(difference < 10 & mean < 20) %>% 
   ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
@@
   mutate(mean = (est.z.copas + est.z.reg)/2, 
-         difference = est.z.copas - est.z.reg) %>% filter(mean < 7) %>% 
+         difference = est.z.copas - est.z.reg) %>% filter(mean < 2.5 & difference < 5) %>% 
   ggplot(aes(x = mean, y = difference)) + geom_point(size = 0.5) + 
@@
 original measure, $z$-score and Hedges $g$ in Figure \ref{fig:adjustment.mean.diff}.
-Note that the 39 survival outcome data is not included when using $z$-score and Hedges $g$.
+Note that the \Sexpr{dim(meta.iv)[1]} IV outcome data is not included when using $z$-score and Hedges $g$.
 

### 2019-07-14 code/Meta_meta_regression.R

@@ -17,6 +17,8 @@ load(file.path(PATH_RESULTS, "data2.RData"))
 # data.ext2 <- pb.process3(data)
 load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
 
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+
 load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
 
 reg.dat <- data.ext2 %>% filter(meta.id %in% meta.id.vector) #Filter meta-analysis data
@@ -51,23 +53,42 @@ reg.dat <- reg.dat %>% group_by(meta.id) %>%
 reg.dat <- reg.dat %>% filter(se.smd != 0) %>% filter(!is.na(smd)) %>% 
   filter(!is.na(se.smd))
 
-reg.dat <- reg.dat %>% mutate(study.year.center = scale(scale = F, center = T, x = study.year),
-                              study.year.scale = scale(scale = T, center = T, x = study.year))
+reg.dat <- reg.dat %>% group_by(meta.id) %>% 
+  mutate(study.year.center = scale(scale = F, center = T, x = study.year)) %>% 
+  ungroup() %>% mutate(study.year.center.ov = scale(scale = T, center = T, x = study.year))
 
-plot(y = reg.dat$smd, x = reg.dat$se.smd)
+par(mfrow = c(1,1))
+# plot(y = reg.dat$smd, x = reg.dat$se.smd, cex = .1)
+# plot(y = reg.dat$smd, x = reg.dat$study.year.center, cex = .1)
 
-reg.dat <- reg.dat %>% filter(meta.id %in% meta.id.vector[c(1:2)])
-print(round(c(meta.f$est.reg, meta.f$est.d.reg, meta.f$est.se, meta.f$est.d.se)),1)
+#Check how largest m.a. looks like..
+# largest.id <- meta.f$meta.id[2957]
+# reg.dat <- reg.dat %>%  filter(meta.id == largest.id)
+# plot(y = reg.dat$smd, x = reg.dat$se.smd, cex = .1, xlim = c(0, 1.3), ylim = c(-2.4, 6))
+# plot(y = reg.dat$smd, x = reg.dat$study.year.center, cex = .1, xlim = c(-45, 38), ylim = c(-2.4, 6))
+
[…]

### 2019-07-14 code/analysis.R

@@ -152,11 +152,11 @@ meta.info.extended <- data.ext2 %>%
 settings.meta(method.tau = "PM", method = "Inverse")
 
 #Load previously constructed lists (to skip analysis):
-# load(file.path(PATH_RESULTS, "meta_complete_list_bin.RData"))
-# load(file.path(PATH_RESULTS, "meta_complete_list_cont.RData"))
-# load(file.path(PATH_RESULTS, "meta_complete_list_iv.RData"))
-# load(file.path(PATH_RESULTS, "meta_complete_list_zscore.RData"))
-# load(file.path(PATH_RESULTS, "meta_complete_list_cohensd.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_bin.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_cont.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_iv.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_zscore.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_cohensd.RData"))
 
 
 
@@ -422,41 +422,41 @@ cont.results <- data.frame(
 
 
 # # -------- Uncomment to run analysis ----------
-meta.id.vector.iv <- meta.info.extended$meta.id[which(meta.info.extended$outcome.flag == "IV")]
-meta.analyses <- list()
-meta.analyses.reg <- list()
-meta.analyses.copas <- list()
-meta.analyses.trimfill <- list()
-meta.tests.linreg <- list()
-meta.tests.begg <- list()
-meta.tests.mm <- list()
-meta.tests.excess <- list()
-counter <- 0
-for(u in meta.id.vector.iv){
-	counter <- counter + 1
-
-	meta.analyses[[counter]] <- metagen(TE = effect, seTE = se, studlab = study.name, sm = "HR",
-                           data = data.ext2[data.ext2$meta.id == u,])
-	print(c(u, counter))
-	# print(c(u, counter, unlist(lapply(meta.analyses, FUN = function(meta.analysis){meta.analysis$TE.fixed}))[counter]))
-	meta.analyses.reg[[counter]] <- limitmeta(meta.analyses[[counter]])
-	meta.analyses.trimfill[[counter]] <- trimfill(meta.analyses[[counter]])
-	meta.analyses.copas[[counter]] <- auto.copas(meta.analyses[[counter]], sig.level = 0.1)
-
[…]

### 2019-07-23 report/MSc_Report.tex
report correction

@@
   \vspace*{6cm}{\bfseries\Huge
-  Publication Bias in the Cochrane \vspace{3mm} Database of Systematic Reviews
+  Statistical Assessment and Adjustment of Publication Bias in the Cochrane Database of Systematic Reviews
   }
@@
 
-Studies get more attention and are more likely to be published, read and cited if they are implying large effects.
+Studies get more attention and are more likely to be published, read and cited if they are implying significant effects.
 Studies with no evidence for an effect are less likely to get published.
-This generates a bias called ``publication bias'', which distorts the view of the evidence for an effect.
+This generates a bias called ``publication bias'', a distorted view of the evidence for an effect.
 Recently, publication bias has been identified as one of the major concerns in irreproducible research \citep{Bishop.2019}.
-The issue has been pin-pointed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}).
+The issue has been discussed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}).
+\\
 In medical research, clinical trials study the efficacy of therapies and drugs.
@@
 Results from such clinical studies influence the treatment of patients in daily clinical practice.
-The results from multiple intervention studies are summarized in meta-analyses and reflect the overall evidence for a treatment effect.
-Summarized treatment effects and uncertainities should be more robust and reliable.
-Publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm.
-\\
-There is extensive literature on publication bias in meta-analyses, e.g. (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02}, 
-\citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}). 
-All authors agree in that the exclusion of unpublished results in meta-analyses is responsible for overestimation of treatment effects.
-Although there are policies that make it mandatory to make accessible all study results \citep{fda}, it is not clear if the situation has improved yet.\\
-The Cochrane Organisation has specialized on systematic reviews of healthcare interventions.
-Researchers that write a systematic review collect data across studies, review them and try to provide up-to-date information about specific treatment efficacies \citep{cochrane.handbook}.
-By extensive literature scrutinization, they try to circumvent the issue of publication bias.
-Earlier research however suggests that the efforts are only partially succesful, and that there still is publication bias within the reviews (\citet{Egger}, \citet{Ioannidis2007}, \citet{kicinsky}, \citet{vanAert.2019}).
-In this publications, the results of a part of the Cochrane Database of systematic reviews is analysed with small study effect tests or bayesian hierarchical selection models \citep{kicinsky}.
-They all find moderate to large evidence for publication bias in the Database.
-A more thorough discussion of their methods and results will follow in chapter \ref{ch:Discussion}.
-None of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods.
-Also, the results are often presented in the form of dichotomized hypothesis tests, a practice known to contribute to publication bias itself (cite sb).\\
-The aim of this thesis is to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides.
-At the end, an up-to-date estimate of the prevalence of publication bias in the data shall be given, as well as its implications regarding the effect sizes of the treatments.
-To achieve this, methods to detect and adjust for publication bias in meta-analysis are applied on the data.
-
-\subsection{Analysing publication bias}
+The results from multiple intervention studies are However, publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm.
+\\
 There are multiple ways to assess the amount of publication bias.
@@
 \end{itemize}
-This then leads to the so-called asymmetry in the funnel plot of published studies; small studies show larger effect sizes than larger studies do.
+This then leads to the asymmetry in the funnel plot of published studies; small studies show larger effect sizes than larger studies do.
+A funnel plot allows visual inspection of small study effects by plotting the effects against their standard error.
+For illustration purposes, one meta-analysis with large funnel plot asymmetry and one with no asymmetry is shown in Figure \ref{small.study.effect.example}.
+%\citep{pre.eclampsia}:
 By means of simple linear regression, one can investigate how much evidence there is for this asymmetry.
-For illustration purposes, a meta-analysis with large funnel plot asymmetry is shown %\citep{pre.eclampsia}:
 
@@
 \end{knitrout}
+\caption{Funnel plots of two meta-analyses: On the left, the improvement in depression syndroms after application of tricyclic antidepressants is compared to placebo.
+The meta-analysis on the right measures the occurence of intracranial haemoerrhage by CT after application of any anti-thrombolytic agent.
+All studies are RCT's.}
+\label{small.study.effect.examples}
 \end{figure}
@@
 Thus, the estimation of small study effects is oftentimes the most efficient and simple way to analyse publication bias.
+
+\section{Aim of the study}
+
+There is extensive literature on publication bias in meta-analyses, e.g. (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02},
+\citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}).
+The authors agree on that the exclusion of unpublished results in meta-analyses is responsible for overestimation of treatment effects.
+Although there are policies that make it mandatory to make all study results publicly accessible \citep{fda}, it is not clear if the situation has improved yet.\\
+The Cochrane Organisation has specialized on systematic reviews of healthcare interventions.
+Researchers that write a systematic review collect data across studies, review them and try to provide up-to-date information about specific treatment efficacies \citep{cochrane.handbook}.
+By extensive literature scrutinization, they try to circumvent the issue of publication bias.
+Earlier research however suggests that the efforts are only partially succesful, and that there still is publication bias within the reviews (\citet{Egger}, \citet{Ioannidis2007}, \citet{kicinsky}, \citet{vanAert.2019}).
+In these publications, Cochrane systematic reviews is analysed with methods to detect publication bias, for example small study effect tests or bayesian hierarchical selection models \citep{kicinsky}.
+They all find moderate to large evidence for publication bias in the Database.
+Their results will be compared to the results of this study in the last chapter.\\
+None of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods.
+Also, the results are ironically often presented in the form of dichotomized hypothesis tests, a practice that is partly responsible for publication bias.\\
+The aim of this thesis is to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides.
+At the end, an up-to-date estimate of the prevalence of publication bias in the data shall be given, as well as its implications regarding the effect sizes of the treatments.
+To achieve this, methods to detect and adjust for publication bias in meta-analysis are applied on the data.
 
@@
 \begin{align}
-\theta &= \beta_0 + \beta_1 \se + \epsilon, & \epsilon \sim N(0, w^{-1}\sigma^2) \label{eq:egger.plot}
+\theta &= \beta_0 + \beta_1 \se + \epsilon, & \epsilon \sim N(0, w^{-2}\sigma^2) \label{eq:egger.plot}
 \end{align}
@@
 \item $\beta_0$ the treatment effect without any influence of study precision with standard error $s_{\beta_0}$
-\item $\beta_0 + \beta_1 \tau$ the treatment effect of a hypothetical study with infinite precision, corresponding standard error $s_{\beta_0} + s_{\beta_1}$
+\item $\beta_0 + \beta_1 \tau$ the treatment effect of a hypothetical study with infinite precision, corresponding standard error $\se = s_{\beta_0} + s_{\beta_1}$
 \end{itemize}
@@
 \subsection{Structure and Content}
-The dataset consists of 6353 systematic reviews from the Cochrane Library with 70662 studies and 744717 results.
+The dataset consists of 6354 systematic reviews from the Cochrane Library with 70662 studies and 744720 results.
 The results all stem from comparisons of a healthcare interventions or treatments to a reference.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Jul 14 14:23:32 2019
+% Tue Jul 23 08:53:36 2019
 \begin{table}[ht]
@@
 RR & 361902 & 48.6\% \\ 
-  MD & 164920 & 22.1\% \\ 
-  OR & 72012 & 9.7\% \\ 
+  MD & 164923 & 22.1\% \\ 
+  OR & 76067 & 10.2\% \\ 
   SMD & 70717 & 9.5\% \\ 
@@
   Hazard Ratio & 8054 & 1.1\% \\ 
-  Odds Ratio & 4055 & 0.5\% \\ 
-  other & 12279 & 1.6\% \\ 
+  Rate Ratio & 3724 & 0.5\% \\ 
+  other & 8555 & 1.1\% \\ 
    \hline
@@
 Analogously, the quantiles of the total sample size are: 5\% quantile = 17, first quartile = 44, median = 94, third quartile = 223 and 95\% = 983.
-The mean is 623.16.
-\\
-There are 518 reviews with five or fewer results.
+The mean is 623.15.
+\\
+There are 519 reviews with five or fewer results.
 The 5\% and 95\% quantiles are 4 and 447.
 The mean and median number of results per review are 13.6 and 8, and the quartiles are 16 and 109.
-Similarly, the number of reviews with a maximum of two studies included is 1039, the mean study number is 13.6, the median 8 and the interquartile range 4 and 16 and the 95\% quantile 45.
+Similarly, the number of reviews with a maximum of two studies included is 1040, the mean study number is 13.6, the median 8 and the interquartile range 4 and 16 and the 95\% quantile 45.
 The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citet{largest.review}
@@
 {\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Jul 14 14:23:32 2019
+% Tue Jul 23 08:53:36 2019
 \begin{table}[ht]
@@
   \hline
-1 & 143375 & 268903 \\ 
+1 & 143378 & 268906 \\ 
   2 & 45459 & 125528 \\ 
@@
 \begin{itemize}
-\item \texttt{outcome.measure.new}: Outcome measure specifications given in \texttt{outcome.measure} were standardized whenever they were supposed to denote the same outcome measure.
+\item \texttt{outcome.measure.merged}: Outcome measure specifications given in \texttt{outcome.measure} were standardized whenever they were supposed to denote the same outcome measure.
 An example would be the formally different notations for odds ratios: ``Odds Ratio'', ``odds ratio'', ``OR'', which were all denoted as ``Odds Ratio''.
-% \item \texttt{outcome.flag}: A simplification of \texttt{outcome.measure.new}.
-The outcome.flag ``bin'' indicates if \texttt{outcome.measure.new} is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
-``cont'' is equivalent to \texttt{outcome.measure.new} equal to "Std.
+% \item \texttt{outcome.flag}: A simplification of \texttt{outcome.measure.merged}.
+The outcome.flag ``bin'' indicates if \texttt{outcome.measure.merged} is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
+``cont'' is equivalent to \texttt{outcome.measure.merged} equal to "Std.
 Mean Difference'' or ``Mean Difference''.
@@
 \item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.flag ``cont''. 
-% If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.new} was equal to ``Std.
+% If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.merged} was equal to ``Std.
 Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  length(inpute.given.ind)).
@@
 binary, continuous and survival outcomes.
-This corresponds to 734951 out of a total of 744717 results.
+This corresponds to 734954 out of a total of 744720 results.
 \citet{Ioannidis2007} outlined criteria for application of small study effect tests:
 \begin{itemize}
-\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = 11463 remaining). 
-\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 10830 remaining).
-\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 8575 remaining)
-\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 3075 remaining).
+\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = 9916 remaining). 
+\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 9334 remaining).
+\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 7509 remaining)
+\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 1403 remaining).
 \end{itemize}
@@
 \begin{center}
-\tikzstyle{block} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=2.5em]
-\tikzstyle{btw} = [rectangle, node distance=0cm, minimum height =2em, fill= white]
+\tikzstyle{block} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=2.3em]
+\tikzstyle{btw} = [rectangle, node distance=0cm, minimum height =1.8em, fill= white]
 \tikzstyle{ublock} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=4em, text width = 10em]
@@
         \node [final] (1) {Inital dataset: 
-    6,353 reviews,
+    6,354 reviews,
     70,662 studies,
-    744,717 results};
-
-    \node [block, below of=1, node distance=2.2cm] (2) {
-    6,324 reviews,
-    69,873 studies,
-    734,951 results};
-
-    \node [block, below of=2, node distance=2.2cm] (3) {
-    1,262 reviews,
-    29,109 studies,
-    208,391 results,
-    11,463 meta-analyses};
-
-    \node [block, below of=3, node distance=2.2cm] (4) {
-    1,241 reviews,
-    28,698 studies,
-    196,539 results,
-    10,830 meta-analyses};
-
-    \node [block, below of=4, node distance=2.2cm] (5) {
-    1,157 reviews,
-    26,590 studies,
-    162,298 results,
-    8,575 meta-analyses};
-
-    \node [block, below of=5, node distance=2.2cm] (6) {
-    1,150 reviews,
-    26,261 studies,
-    92,956 results,
-    5,244 meta-analyses};
-
-    \node [final, below of=6, node distance=2.2cm] (7) {Analysis dataset (1):
-    912 reviews,
-    19,342 studies,
-    53,012 results,
-    3,075 meta-analyses};
+    744,720 results};
+
+        \node [block, below of=1, node distance=2cm] (12) {
+    5,971 reviews,
+    66,574 studies,
+    705,002 results};
+
+        \node [block, below of=12, node distance=2cm] (13) {
+    5,952 reviews,
+    65,774 studies,
+    632,438 results};
+
+    \node [block, below of=13, node distance=2cm] (2) {
+    5,948 reviews,
+    65,962 studies,
+    695,992 results};
+
+    \node [block, below of=2, node distance=2cm] (3) {
+    1,156 reviews,
+    26,580 studies,
+    175,351 results,
+    9,916 meta-analyses};
+
+    \node [block, below of=3, node distance=2cm] (4) {
+    1,133 reviews,
+    26,101 studies,
+    164,222 results,
+    9,334 meta-analyses};
+
+    \node [block, below of=4, node distance=2cm] (5) {
+    1,056 reviews,
+    24,149 studies,
+    136,537 results,
+    7,509 meta-analyses};
+
+    \node [block, below of=5, node distance=2cm] (6) {
+    1,024 reviews,
+    22,502 studies,
+    47,092 results,
+    2,694 meta-analyses};
+
+    \node [final, below of=6, node distance=2cm] (7) {Analysis dataset (1):
+    740 reviews,
+    14,467 studies,
+    23,243 results,
+    1,403 meta-analyses};
 
@@
     \node [ublock, below of=7, node distance=4cm] (8) {Binary data: \\
-    2,217 meta-analyses};
+    924 meta-analyses};
 
     \node [ublock, right of=8, node distance=5cm] (9) {Continuous data: \\
-    604 meta-analyses};
+    336 meta-analyses};
 
     \node [ublock, left of=8, node distance=5cm] (10) {Other data (IV): \\
-    238 meta-analyses};
+    140 meta-analyses};
 
     \node [final, below of=8, node distance=2.4cm] (11) {Analysis dataset (2):
-    848 reviews,
-    18,101 studies,
-    49,010 results,
-    2,821 meta-analyses};
+    678 reviews,
+    13,357 studies,
+    20,984 results,
+    1,260 meta-analyses};
 
     % Draw edges
-    \path [line] (1) -- node [btw, xshift = -1.8cm] {\texttt{outcome.flag} restriction} (2);
+    \path [line] (1) -- node [btw, xshift = -1.95cm] {no withdrawn reviews} (12);
+    \path [line] (12) -- node [btw, xshift = -2.1cm] {only efficacy outcomes} (13);
+    \path [line] (13) -- node [btw, xshift = -2cm] {\texttt{outcome.flag} restriction} (2);
     \path [line] (2) -- node [btw, xshift = -1.7cm] {study number $\geq$ 10}(3);
@@
 \subsubsection{The Analysis Dataset}
-The dataset that was ultimately tested and adjusted for publication bias comprises 1 meta-analyses and 53012 results.
-The mean number of participants in the treatment group is 212.6 vs 256.7 in the unrestricted dataset and the mean total number of participants 465.5 vs 623.2.
-The mean publication year is 2000.0251806 vs 2000.9710727 in the unrestricted dataset.
-\\
-From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}), there are 55 with \\ \texttt{outcome.measure.new} = ``Risk Ratio'', 47 ``Std.
-Mean Difference'',  35 ``Hazard Ratio'' and 22 ``Odds Ratio'' (and 25 additional, different outcome measures).
+The dataset that was ultimately tested and adjusted for publication bias comprises 1 meta-analyses and 23243 results.
+The mean number of participants in the treatment group is 251.9 vs 256.7 in the unrestricted dataset and the mean total number of participants 584.7 vs 623.2.
+The mean publication year is 2000.3028869 vs 2000.9711014 in the unrestricted dataset.
+\\
+From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}), there are 34 with \\ \texttt{outcome.measure.merged} = ``Risk Ratio'', 27 ``Std.
+Mean Difference'',  26 ``Hazard Ratio'' and 13 ``Odds Ratio'' (and 25 additional, different outcome measures).
 
@@
 There, there is no evidence for publication bias, and the histograms are even skewed to the left (Schwarzer).
-But note that the sample size of IV outcomes is small ($n$ = 238).
+But note that the sample size of IV outcomes is small ($n$ = 140).
 \\
@@
 The colors indicate magnitude and direction of the correlation coefficients.
-The rectangle with white borders displays the area within which both tests have absolute value < 1.64 (dots outside are statistically significant by 0.1 $p$-value threshold).}
+The rectangle with white borders displays the area within which both tests have absolute value < 1.64 (dots inside are statistically not significant by 0.1 $p$-value threshold).}
 \label{fig:test.agreement}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Jul 14 14:40:23 2019
+% Tue Jul 23 08:53:48 2019
 \begin{table}[ht]
@@
   \hline
-0 & 66.3 \% & 68.1 \% \\ 
-  1 & 13.7 \% & 11.8 \% \\ 
-  2 & 7.7 \% & 6.8 \% \\ 
-  3 & 6.2 \% & 11.4 \% \\ 
-  4 & 5.2 \% & 2 \% \\ 
-  5 & 0.9 \% & - \\ 
+0 & 66.1 \% & 67.9 \% \\ 
+  1 & 12.3 \% & 11.8 \% \\ 
+  2 & 7.7 \% & 6.9 \% \\ 
+  3 & 6.8 \% & 12.2 \% \\ 
+  4 & 5.7 \% & 1.3 \% \\ 
+  5 & 1.3 \% & - \\ 
    \hline
@@
 \\
-When only looking at small study effect tests, 29.5\% of binary outcome tests and 29.5\% of IV and continuous outcome tests had at least one significant result.
-After applying the Bonferroni correction for multiple testing, this shrinks to 12.6\% for binary and 12.7\% for continuous and IV outcomes.
+When only looking at small study effect tests, 29.5\% of binary outcome tests and 29.8\% of IV and continuous outcome tests had at least one significant result.
+After applying the Bonferroni correction for multiple testing, this shrinks to 12.3\% for binary and 12.4\% for continuous and IV outcomes.
 \\
@@
 \section{Small Study Effects Adjustment}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in Math.data.frame(structure(list(meta.id = c(9957L, 12985L, 49559L, : non-numeric variable(s) in data frame: id}}\end{kframe}
-\end{knitrout}
 
@@
 The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 152 cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or 152 increased by -0.13, fixed effects reference).
-Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or 152 meta-analyses (or increased by 0.24).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 70 cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or 70 increased by -0.13, fixed effects reference).
+Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or 70 meta-analyses (or increased by 0.24).
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Jul 14 14:40:50 2019
+% Tue Jul 23 08:54:03 2019
 \begin{table}[ht]
@@
   \hline
-z: Fixed - Copas & -0.05 & -0.01 & -0.00 & 0.01 & 0.05 & -252.84 & 4.97 & 45.54 & 40.57 & 66.17 \\ 
-  z: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.05 & -100.49 & 66.75 & 84.18 & 17.42 & 66.17 \\ 
-  z: Fixed - Regression & -0.12 & -0.03 & 0.01 & 0.05 & 0.14 & 0.01 & 0.00 & 49.98 & 49.98 & 0.03 \\ 
-  z: Random - Regression & -0.14 & -0.03 & 0.02 & 0.07 & 0.17 & 0.02 & 0.00 & 55.15 & 55.15 & 0.03 \\ 
-  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.09 & 0.03 & 21.25 & 56.72 & 35.47 & 55.90 \\ 
-  g: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.15 & 0.04 & 58.03 & 82.15 & 24.13 & 55.90 \\ 
-  g: Fixed - Regression & -0.22 & -0.04 & 0.04 & 0.13 & 0.39 & 0.06 & 0.00 & 58.52 & 58.52 & 0.03 \\ 
-  g: Random - Regression & -0.22 & -0.03 & 0.05 & 0.16 & 0.42 & 0.07 & 0.00 & 60.31 & 60.31 & 0.03 \\ 
-  Log h.r.: Fixed - Copas & -0.14 & -0.00 & 0.00 & 0.00 & 0.11 & 0.16 & 31.51 & 35.29 & 66.81 & 57.98 \\ 
-  Log h.r.: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.13 & 0.22 & 63.45 & 23.53 & 86.97 & 57.98 \\ 
-  Log h.r.: Fixed - Regression & -0.39 & -0.08 & -0.00 & 0.07 & 0.97 & 0.27 & 0.00 & 47.90 & 47.90 & 0.00 \\ 
-  Log h.r.: Random - Regression & -0.41 & -0.08 & -0.01 & 0.08 & 1.44 & 0.33 & 0.00 & 48.32 & 48.32 & 0.00 \\ 
+z: Fixed - Copas & -0.06 & -0.01 & 0.00 & 0.02 & 0.13 & 0.01 & 4.71 & 47.79 & 43.07 & 63.93 \\ 
+  z: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.15 & 0.02 & 62.93 & 82.21 & 19.29 & 63.93 \\ 
+  z: Fixed - Regression & -0.12 & -0.03 & 0.01 & 0.05 & 0.14 & 0.01 & 0.00 & 48.00 & 48.00 & 1.14 \\ 
+  z: Random - Regression & -0.15 & -0.02 & 0.02 & 0.07 & 0.17 & 0.02 & 0.00 & 54.43 & 54.43 & 1.14 \\ 
+  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.10 & -0.01 & 19.36 & 53.93 & 34.57 & 56.71 \\ 
+  g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.16 & 0.00 & 57.79 & 80.79 & 23.00 & 56.71 \\ 
+  g: Fixed - Regression & -0.21 & -0.03 & 0.04 & 0.14 & 0.39 & 0.06 & 0.00 & 57.36 & 57.36 & 1.14 \\ 
+  g: Random - Regression & -0.21 & -0.03 & 0.05 & 0.16 & 0.44 & 0.07 & 0.00 & 59.57 & 59.57 & 1.14 \\ 
+  Log h.r.: Fixed - Copas & -0.05 & -0.00 & 0.00 & 0.01 & 0.07 & 0.16 & 30.71 & 41.43 & 72.14 & 57.86 \\ 
+  Log h.r.: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.10 & 0.21 & 62.86 & 25.71 & 88.57 & 57.86 \\ 
+  Log h.r.: Fixed - Regression & -0.52 & -0.09 & -0.01 & 0.05 & 0.69 & 0.34 & 0.00 & 44.29 & 44.29 & 0.00 \\ 
+  Log h.r.: Random - Regression & -0.52 & -0.09 & -0.01 & 0.07 & 0.76 & 0.39 & 0.00 & 45.00 & 45.00 & 0.00 \\ 
    \hline
@@
 The Copas selection model also gives an estimate of the number of missing studies.
-It finds that 0 are missing, which corresponds to 0\% from all \ensuremath{5.2733\times 10^{4}} analysed studies.
+It finds that 0 are missing, which corresponds to 11.3\% from all \ensuremath{2.3183\times 10^{4}} analysed studies.
 Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
-Note that we have excluded 0 out of 3059, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
+Note that we have excluded 0 out of 1400, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Jul 14 14:40:51 2019
+% Tue Jul 23 08:54:04 2019
 \begin{table}[ht]
@@
   \hline
-Missing fraction & 576 & 0 & 0 & 0.1 & 0.3 & 0.9 & 0.2 \\ 
-  Missing study number & 576 & 0 & 0 & 1.2 & 5.3 & 17.9 & 4.4 \\ 
+Missing fraction & 239 & 0 & 0 & 0.1 & 0.4 & 1.1 & 0.3 \\ 
+  Missing study number & 239 & 0 & 0 & 1.3 & 5.6 & 21.0 & 4.6 \\ 
    \hline
@@
   \hline
-9957 & 9957 & 8 & 2 & 0.80 & 0.81 & 0.80 & 0.97 & 1.59 & 1.59 & 1.40 & 0.28 \\ 
-  12985 & 12985 & 3 & 1 & -0.24 & -0.05 & -0.12 & -0.16 & -0.08 & -0.26 & 33.85 & -0.03 \\ 
-  49559 & 49559 & 2 & 1 & -0.13 & -0.11 & -0.13 & 0.04 & -0.47 & -0.42 & -0.41 & -3.00 \\ 
-  71800 & 71800 & 7 & 1 & -0.08 & 0.05 & 56.48 & 0.27 & 0.09 & 0.07 & 0.60 & 1.15 \\ 
-  79309 & 79309 & 1 & 0 & -0.75 & -0.69 & -0.50 & -0.26 & -1.19 & -1.53 & 0.18 & -0.52 \\ 
-  90890 & 90890 & 1 & 1 & 0.17 & 0.24 & 0.17 & 0.34 & 0.53 & 0.53 & 0.53 & 1.65 \\ 
-  111673 & 111673 & 3 & 1 & -0.14 & 0.00 & 214760.42 & -0.04 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
-  132957 & 132957 & 1 & 1 & -0.26 & -0.14 & 77.99 & -0.12 & -0.25 & -0.33 & -0.16 & 0.08 \\ 
-  141198 & 141198 & 2 & 0 & -0.08 & -0.33 & -0.08 & -0.17 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
-  158380 & 158380 & 1 & 9 & -0.91 & -0.90 & -0.70 & -0.24 & -2.02 & -2.02 & -2.02 & -0.97 \\ 
-  158415 & 158415 & 1 & 6 & -0.71 & -0.70 & -0.71 & -0.38 & -1.28 & -1.34 & -0.21 & -0.35 \\ 
-  169175 & 169175 & 2 & 2 & 0.40 & 0.36 & 34.40 & 0.13 & 0.74 & 0.74 & 0.70 & 0.23 \\ 
-  171013 & 171013 & 4 & 1 & 0.25 & 0.23 & 71.80 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
-  172921 & 172921 & 3 & 0 & 0.07 & 0.15 & 0.07 & 0.29 & 0.50 & 0.50 & 1.43 & 1.81 \\ 
-  173202 & 173202 & 3 & 3 & -0.25 & -0.25 & -0.11 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
-  197677 & 197677 & 3 & 1 & -0.56 & -0.56 & -0.40 & -0.07 & -1.31 & -1.34 & 0.02 & -0.08 \\ 
-  206994 & 206994 & 1 & 0 & 0.14 & 0.26 & 498188.34 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
-  217028 & 217028 & 7 & 1 & 0.38 & 0.37 & 0.38 & 0.07 & 0.66 & 0.69 & -0.38 & 0.09 \\ 
-  217032 & 217032 & 8 & 1 & 0.38 & 0.38 & 0.38 & 0.10 & 0.69 & 0.71 & 20.28 & 0.12 \\ 
-  222624 & 222624 & 2 & 1 & -0.19 & -0.12 & 13.72 & -0.01 & -0.20 & -0.24 & 0.06 & 0.08 \\ 
-  222764 & 222764 & 1 & 0 & 0.33 & 0.34 & 0.33 & 0.25 & 0.50 & 0.52 & 0.20 & -0.49 \\ 
-  245139 & 245139 & 2 & 4 & -0.10 & -0.09 & -0.10 & -0.08 & -0.09 & -0.09 & 8.25 & -0.02 \\ 
-  247940 & 247940 & 10 & 0 & -0.16 & 0.03 & -0.16 & -0.07 & 0.05 & 0.05 & 2.81 & 0.11 \\ 
-  255734 & 255734 & 1 & 0 & -0.32 & -0.29 & -0.15 & -0.08 & -0.56 & -0.58 & 16.55 & -0.25 \\ 
+9957 & CD000370 & 8 & 2 & 0.80 & 0.81 & 0.80 & 0.97 & 1.59 & 1.59 & 1.40 & 0.28 \\ 
+  49559 & CD002307 & 2 & 1 & -0.13 & -0.11 & -0.13 & 0.04 & -0.47 & -0.42 & -0.41 & -3.00 \\ 
+  186028 & CD007964 & 1 & 2 & -0.18 & -0.10 & 1.01 & -0.19 & -0.07 & -0.06 & -0.06 & -0.16 \\ 
+  217035 & CD009676 & 8 & 1 & -0.09 & -0.08 & -0.09 & -0.07 & 0.69 & 0.71 & 20.28 & 0.12 \\ 
+  222767 & CD010060 & 1 & 0 & 0.36 & 0.49 & 0.36 & 0.54 & 0.50 & 0.52 & 0.20 & -0.49 \\ 
    \hline
@@
 original measure, $z$-score and Hedges $g$ in Figure \ref{fig:adjustment.mean.diff}.
-Note that the 238 IV outcome data is not included when using $z$-score and Hedges $g$.
+Note that the 140 IV outcome data is not included when using $z$-score and Hedges $g$.
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Jul 14 14:40:52 2019
+% Tue Jul 23 08:54:05 2019
 \begin{table}[ht]
@@
   \hline
-Excess significance, Schwarzer & 0.85 & 0.20 \\ 
-  Excess significance, Peter & 0.78 & 0.32 \\ 
-  Excess significance, Rucker & 0.78 & 0.39 \\ 
-  Excess significance, Harbord & 0.81 & 0.39 \\ 
-  Peter, Schwarzer & 0.84 & 0.62 \\ 
-  Schwarzer, Rucker & 0.84 & 0.71 \\ 
-  Schwarzer, Harbord & 0.88 & 0.74 \\ 
+Excess significance, Schwarzer & 0.85 & 0.27 \\ 
+  Excess significance, Peter & 0.77 & 0.32 \\ 
+  Excess significance, Rucker & 0.79 & 0.43 \\ 
+  Excess significance, Harbord & 0.81 & 0.46 \\ 
+  Peter, Schwarzer & 0.84 & 0.63 \\ 
+  Schwarzer, Rucker & 0.85 & 0.72 \\ 
+  Schwarzer, Harbord & 0.87 & 0.78 \\ 
   Rucker, Peter & 0.88 & 0.67 \\ 
-  Harbord, Peter & 0.87 & 0.59 \\ 
-  Excess significance, Egger & 0.75 & 0.55 \\ 
-  Excess significance, Thompson & 0.78 & 0.53 \\ 
-  Excess significance, Begg & 0.77 & 0.37 \\ 
-  Thompson, Egger & 0.94 & 0.93 \\ 
-  Thompson, Begg & 0.87 & 0.73 \\ 
-  Egger, Begg & 0.84 & 0.72 \\ 
-  Excess significance, Egger (IV) & 0.84 & 0.08 \\ 
-  Excess significance, Thompson (IV) & 0.86 & 0.09 \\ 
-  Excess significance, Begg (IV) & 0.86 & 0.09 \\ 
-  Thompson, Egger (IV) & 0.96 & 0.94 \\ 
-  Thompson, Begg (IV) & 0.88 & 0.56 \\ 
-  Egger, Begg (IV) & 0.87 & 0.59 \\ 
+  Harbord, Peter & 0.87 & 0.63 \\ 
+  Excess significance, Egger & 0.74 & 0.50 \\ 
+  Excess significance, Thompson & 0.78 & 0.50 \\ 
+  Excess significance, Begg & 0.76 & 0.30 \\ 
+  Thompson, Egger & 0.93 & 0.92 \\ 
+  Thompson, Begg & 0.86 & 0.69 \\ 
+  Egger, Begg & 0.83 & 0.69 \\ 
+  Excess significance, Egger (IV) & 0.84 & 0.09 \\ 
+  Excess significance, Thompson (IV) & 0.84 & 0.10 \\ 
+  Excess significance, Begg (IV) & 0.85 & 0.10 \\ 
+  Thompson, Egger (IV) & 0.98 & 0.95 \\ 
+  Thompson, Begg (IV) & 0.86 & 0.55 \\ 
+  Egger, Begg (IV) & 0.87 & 0.60 \\ 
    \hline

### 2019-07-23 report/chapter01.Rnw
report correction

@@
 Results from such clinical studies influence the treatment of patients in daily clinical practice.
-The results from multiple intervention studies are summarized in meta-analyses and reflect the overall evidence for a treatment effect.
-Summarized treatment effects and uncertainities should be more robust and reliable.
-Publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm.
+The results from multiple intervention studies are However, publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm.
 \\
-There is extensive literature on publication bias in meta-analyses, e.g. (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02}, 
-\citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}). 
-All authors agree in that the exclusion of unpublished results in meta-analyses is responsible for overestimation of treatment effects.
-Although there are policies that make it mandatory to make accessible all study results \citep{fda}, it is not clear if the situation has improved yet.\\
-The Cochrane Organisation has specialized on systematic reviews of healthcare interventions.
-Researchers that write a systematic review collect data across studies, review them and try to provide up-to-date information about specific treatment efficacies \citep{cochrane.handbook}.
-By extensive literature scrutinization, they try to circumvent the issue of publication bias.
-Earlier research however suggests that the efforts are only partially succesful, and that there still is publication bias within the reviews (\citet{Egger}, \citet{Ioannidis2007}, \citet{kicinsky}, \citet{vanAert.2019}).
-In this publications, the results of a part of the Cochrane Database of systematic reviews is analysed with small study effect tests or bayesian hierarchical selection models \citep{kicinsky}.
-They all find moderate to large evidence for publication bias in the Database.
-A more thorough discussion of their methods and results will follow in chapter \ref{ch:Discussion}.
-None of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods.
-Also, the results are often presented in the form of dichotomized hypothesis tests, a practice known to contribute to publication bias itself (cite sb).\\
-The aim of this thesis is to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides.
-At the end, an up-to-date estimate of the prevalence of publication bias in the data shall be given, as well as its implications regarding the effect sizes of the treatments.
-To achieve this, methods to detect and adjust for publication bias in meta-analysis are applied on the data.
-
-\subsection{Analysing publication bias}
 There are multiple ways to assess the amount of publication bias.
@@
 
-pb.ex <- 111673
-require(meta)
-require(tidyverse)
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+ex.se <- meta.f$meta.id[395]
+ex.nose <- meta.f$meta.id[36]
 par(mfrow = c(1,2))
-tp <- data.ext2 %>% filter(meta.id == pb.ex)
-funnel(metabin(event.e = events1, event.c = events2, n.e = total1, n.c = total2, data = tp),
-       comb.fixed = F, comb.random = F)
-
-nopb.ex <- meta.f$meta.id[32]
-tp <- data.ext2 %>% filter(meta.id == nopb.ex)
-funnel(metabin(event.e = events1, event.c = events2, n.e = total1, n.c = total2, data = tp),
-       comb.fixed = F, comb.random = F)
+funnel(x = meta.id(ex.se), ylim = c(1.60, 0), comb.fixed = F, comb.random = F)
+funnel(x = meta.id(ex.nose), ylim = c(1.60, 0), comb.fixed = F, comb.random = F, ylab = NULL)
 @
+\caption{Funnel plots of two meta-analyses: On the left, the improvement in depression syndroms after application of tricyclic antidepressants is compared to placebo.
+The meta-analysis on the right measures the occurence of intracranial haemoerrhage by CT after application of any anti-thrombolytic agent.
+All studies are RCT's.}
+\label{small.study.effect.examples}
 \end{figure}

### 2019-07-23 report/chapter03.Rnw
report correction

@@
 <<echo = FALSE, warning=FALSE, message=FALSE, cache = TRUE>>=
+#Load data:
 rm(list = ls())
@@
 PATH_RESULTS = file.path(PATH2, 'results_new')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-file_results = "pb.RData"
+# PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
 
@@
 
-file.dat <- "data.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData2(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
-
+load(file.path(PATH_DATA, "PubBias_2019-07-19.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
 load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
+load(file.path(PATH_RESULTS, "meta_id_I2.RData"))
 load(file.path(PATH_RESULTS, "meta.bin.RData"))
@@
 load(file.path(PATH_RESULTS, "meta.iv.RData"))
-load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
-load(file.path(PATH_RESULTS, "meta_id_I2.RData"))
 
@@
 #Outcome.measure frequency table:
-outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.new) %>% count() %>% 
+outcome.measure.frequencies <- rbind(data %>% group_by(outcome.measure.merged) %>% count() %>% 
                                        arrange(desc(n)) %>% ungroup() %>% filter(row_number() < 9),
-                                     data %>% group_by(outcome.measure.new) %>% count() %>% arrange(desc(n)) %>% 
+                                     data %>% group_by(outcome.measure.merged) %>% count() %>% arrange(desc(n)) %>% 
                                        ungroup() %>% filter(row_number() > 8) %>% 
-                                       summarise(outcome.measure.new = "other", n = sum(n)))
+                                       summarise(outcome.measure.merged = "other", n = sum(n)))
 
@@
 
+#No withdrawn reviews:
+tp7 <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) 
+nowith.id.count <- length(unique(tp7$id))
+nowith.study.count <- length(unique(tp7$study.name))
+nowith.result.count <- dim(tp7)[1]
+
+#Only efficacy outcomes:
+tp8 <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
+  filter(outcome.desired == "efficacy")
+efficacy.id.count <- length(unique(tp8$id))
+efficacy.study.count <- length(unique(tp8$study.name))
+efficacy.result.count <- dim(tp8)[1]
+
 #outcome.flag reduction:
-tp <- data %>% filter(outcome.flag == "DICH" | outcome.flag == "CONT" | outcome.flag == "IV")
+tp <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
+  filter(outcome.flag == "DICH" | outcome.flag == "CONT" | outcome.flag == "IV")
 flag.id.count <- length(unique(tp$id))
@@
 flag.result.count <- dim(tp)[1]
-
 #----------------------------------------------------------------------------------------------#
@@
 #Counts of meta-analyses with n larger ten:
-m.a.largerten.bin <- data.ext2 %>% filter(outcome.flag == "DICH") %>% 
+m.a.largerten.bin <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
+  filter(outcome.desired == "efficacy") %>% 
+  filter(outcome.flag == "DICH") %>% 
   filter(total1 != 0 & total2 != 0) %>% 
@@
 
-m.a.largerten.cont <- data.ext2 %>% filter(outcome.flag == "CONT") %>% 
+m.a.largerten.cont <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
+  filter(outcome.desired == "efficacy") %>% 
+  filter(outcome.flag == "CONT") %>% 
   filter(sd1 != 0 & sd2 != 0) %>% 
@@
 
-m.a.largerten.iv <- data.ext2 %>% filter(outcome.flag == "IV") %>% 
+m.a.largerten.iv <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
+  filter(outcome.desired == "efficacy") %>% 
+  filter(outcome.flag == "IV") %>% 
   filter(se != 0) %>% group_by(meta.id) %>% filter(n() > 9) %>% 
@@
 # "IV" outcome.flag meta-analyses
-dt <- meta.iv %>% group_by(outcome.measure.new) %>% count %>% arrange(desc(n))
+dt <- meta.iv %>% group_by(outcome.measure.merged) %>% count %>% arrange(desc(n))
 first.iv.outcome.count <- dt$n[1]
@@
 \item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.flag ``cont''. 
-% If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.new} was equal to ``Std.
+% If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.merged} was equal to ``Std.
 Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  \Sexpr{length(inpute.given.ind)}).
@@
 
-    \node [block, below of=1, node distance=2.2cm] (2) {
+        \node [block, below of=1, node distance=2cm] (12) {
+    \Sexpr{format(nowith.id.count, big.mark = ",")} reviews,
+    \Sexpr{format(nowith.study.count, big.mark = ",")} studies,
+    \Sexpr{format(nowith.result.count, big.mark = ",")} results};
+
+        \node [block, below of=12, node distance=2cm] (13) {
+    \Sexpr{format(efficacy.id.count, big.mark = ",")} reviews,
+    \Sexpr{format(efficacy.study.count, big.mark = ",")} studies,
+    \Sexpr{format(efficacy.result.count, big.mark = ",")} results};
+
+    \node [block, below of=13, node distance=2cm] (2) {
     \Sexpr{format(flag.id.count, big.mark = ",")} reviews,
@@
 
-    \node [block, below of=2, node distance=2.2cm] (3) {
+    \node [block, below of=2, node distance=2cm] (3) {
     \Sexpr{format(ten.id.count, big.mark = ",")} reviews,
@@
 
-    \node [block, below of=3, node distance=2.2cm] (4) {
+    \node [block, below of=3, node distance=2cm] (4) {
     \Sexpr{format(var.id.count, big.mark = ",")} reviews,
@@
 
-    \node [block, below of=4, node distance=2.2cm] (5) {
+    \node [block, below of=4, node distance=2cm] (5) {
     \Sexpr{format(sig.id.count, big.mark = ",")} reviews,
@@
 
-    \node [block, below of=5, node distance=2.2cm] (6) {
+    \node [block, below of=5, node distance=2cm] (6) {
     \Sexpr{format(dupl.id.count, big.mark = ",")} reviews,
@@
 
-    \node [final, below of=6, node distance=2.2cm] (7) {Analysis dataset (1):
+    \node [final, below of=6, node distance=2cm] (7) {Analysis dataset (1):
     \Sexpr{format(I2.id.count, big.mark = ",")} reviews,
@@
     % Draw edges
-    \path [line] (1) -- node [btw, xshift = -1.8cm] {\texttt{outcome.flag} restriction} (2);
+    \path [line] (1) -- node [btw, xshift = -1.95cm] {no withdrawn reviews} (12);
+    \path [line] (12) -- node [btw, xshift = -2.1cm] {only efficacy outcomes} (13);
+    \path [line] (13) -- node [btw, xshift = -2cm] {\texttt{outcome.flag} restriction} (2);
     \path [line] (2) -- node [btw, xshift = -1.7cm] {study number $\geq$ 10}(3);
@@
 \\
-From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}), there are \Sexpr{first.iv.outcome.count} with \\ \texttt{outcome.measure.new} = ``Risk Ratio'', \Sexpr{second.iv.outcome.count} ``Std.
+From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}), there are \Sexpr{first.iv.outcome.count} with \\ \texttt{outcome.measure.merged} = ``Risk Ratio'', \Sexpr{second.iv.outcome.count} ``Std.
 Mean Difference'',  \Sexpr{third.iv.outcome.count} ``Hazard Ratio'' and \Sexpr{fourth.iv.outcome.count} ``Odds Ratio'' (and 25 additional, different outcome measures).

### 2019-07-23 report/chapter04.Rnw
report correction

@@
 <<'Data03', echo=FALSE, warning=FALSE>>= 
+#Load data:
 rm(list = ls())
@@
 PATH_RESULTS = file.path(PATH2, 'results_new')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-file_results = "pb.RData"
+# PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
 
 source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-file.dat <- "data.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
-
+require(corrgram)
+
+load(file.path(PATH_DATA, "PubBias_2019-07-19.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
 load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
+load(file.path(PATH_RESULTS, "meta_id_I2.RData"))
 load(file.path(PATH_RESULTS, "meta.bin.RData"))
@@
 load(file.path(PATH_RESULTS, "meta.iv.RData"))
-load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
-
-require(corrgram)
-
-# data.ext2 <- pb.process3(data)
+
 @
@@
          difference = logit(pval1.egger) - logit(pval1.thompson)) %>% 
+  filter(difference < 10) %>% 
   ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
@@
 
-missing.differences <- round(missing.differences, 2)
-
-missing.differences <- missing.differences %>% mutate(meta.id = as.character(meta.id), id = as.character(meta.id),
+missing.differences[, c("est.z.ranef", "est.z.fixef", "est.z.copas", "est.z.reg", 
+          "est.d.fixef", "est.d.ranef", "est.d.copas", "est.d.reg")] <- round(missing.differences[, c("est.z.ranef", "est.z.fixef", "est.z.copas", "est.z.reg", 
+          "est.d.fixef", "est.d.ranef", "est.d.copas", "est.d.reg")], 2)
+
+missing.differences <- missing.differences %>% mutate(meta.id = as.character(meta.id), id = as.character(id),
                                                       comparison.nr = as.character(comparison.nr), subgroup.nr = as.character(subgroup.nr))
@@
 The Copas selection model also gives an estimate of the number of missing studies.
-It finds that \Sexpr{round(sum(meta.f$missing.Copas, na.rm = T))} are missing, which corresponds to \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% from all \Sexpr{round(sum(meta.f$k))} analysed studies.
+It finds that \Sexpr{round(sum(meta.f$missing.Copas, na.rm = T))} are missing, which corresponds to \Sexpr{round((sum(meta.f$missing.copas, na.rm = T)/sum(meta.f$k))*100,1)}\% from all \Sexpr{round(sum(meta.f$k))} analysed studies.
 Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.

### 2019-07-23 report/chapter05.Rnw
Report based on the new data
introduction update
report correction

@@
 PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2018-06-09.csv'
+FILE = 'cochrane_2019-07-04.csv'
 PATH_DATA = file.path(PATH, 'data')
 PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-file_results = "pb.RData"
+PATH_RESULTS = file.path(PATH2, 'results_new')
+# PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
 
@@
 
-file.dat <- "data.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
-
+load(file.path(PATH_DATA, "PubBias_2019-07-19.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
 load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
-load(file.path(PATH_RESULTS, "meta.bin.RData"))
-load(file.path(PATH_RESULTS, "meta.cont.RData"))
-load(file.path(PATH_RESULTS, "meta.surv.RData"))
-load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
 load(file.path(PATH_RESULTS, "meta_id_I2.RData"))
+#----------------------------------------------------------------------------------------------------#
 
@@
 
-\chapter{Discussion}
+\chapter{Discussion} \label{ch:Discussion}
 

### 2019-07-25 report/MSc_Report.tex
updates

@@
 The $p$-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
+
+\subsection{Generalized linear model} \label{random.intecepts}
+The introduction of group-sepific random effects allows to analyze grouped or repeated measurements by linear regression \citep{Glm}. Let $i$ be the group index, and
+
+\begin{align}
+\mathbf{Y}{_{ij}}|U{_i},\epsilon{_{ij}} = (1,x{_i}^\top)\beta + U{_i} + \epsilon{_{ij}} \label{eq:one.random.intercept}
+\end{align}
+
+the marginal distribution of $\mathbf{Y}{_{ij}}$ depending on $U{_i},\epsilon{_{ij}}$.
+The random effects $U{_i} \sim N(0, g)$ and the residual error term $\epsilon{_{ij}} \sim N(0, \tau^{2})$ are considered independent.
+If there are more groups in the data we can extend \eqref{eq:one.random.intercept} by adding a second random term $Q$ with an index $k$:
+
+\begin{align}
+\mathbf{Y}{_{ij}}|U_i, Q_k \epsilon{_{ij}} = (1,x_i^\top)\beta + U_i + Q_k + \epsilon{_{ij}} \label{eq:two.random.intercepts}
+\end{align}
+
+Again, $U, K, \epsilon$ are distributed independently. The random intercepts model will account for a nested group structure by accordingly indexing the groups. \\
+The conditional distribution in equations \eqref{eq:one.random.intercept} and \eqref{eq:two.random.intercepts} can be used to construct a conditional likelihood; A bayesian posterior distribution is integrated with respect to the random effects, such that it can be used for restricted or unrestricted maximum likelihood estimation.
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Jul 23 08:53:36 2019
+% Wed Jul 24 16:42:40 2019
 \begin{table}[ht]
@@
 {\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Jul 23 08:53:36 2019
+% Wed Jul 24 16:42:40 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Jul 23 08:53:48 2019
+% Tue Jul 23 11:07:27 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Jul 23 08:54:03 2019
+% Tue Jul 23 11:07:42 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Jul 23 08:54:04 2019
+% Tue Jul 23 11:07:44 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Jul 23 08:54:05 2019
+% Tue Jul 23 11:07:45 2019
 \begin{table}[ht]

### 2019-07-25 report/chapter02.Rnw
updates

@@
 
+\subsection{Generalized linear model} \label{random.intecepts}
+The introduction of group-sepific random effects allows to analyze grouped or repeated measurements by linear regression \citep{Glm}. Let $i$ be the group index, and
+
+\begin{align}
+\mathbf{Y}{_{ij}}|U{_i},\epsilon{_{ij}} = (1,x{_i}^\top)\beta + U{_i} + \epsilon{_{ij}} \label{eq:one.random.intercept}
+\end{align}
+
+the marginal distribution of $\mathbf{Y}{_{ij}}$ depending on $U{_i},\epsilon{_{ij}}$.
+The random effects $U{_i} \sim N(0, g)$ and the residual error term $\epsilon{_{ij}} \sim N(0, \tau^{2})$ are considered independent.
+If there are more groups in the data we can extend \eqref{eq:one.random.intercept} by adding a second random term $Q$ with an index $k$:
+
+\begin{align}
+\mathbf{Y}{_{ij}}|U_i, Q_k \epsilon{_{ij}} = (1,x_i^\top)\beta + U_i + Q_k + \epsilon{_{ij}} \label{eq:two.random.intercepts}
+\end{align}
+
+Again, $U, K, \epsilon$ are distributed independently. The random intercepts model will account for a nested group structure by accordingly indexing the groups. \\
+The conditional distribution in equations \eqref{eq:one.random.intercept} and \eqref{eq:two.random.intercepts} can be used to construct a conditional likelihood; A bayesian posterior distribution is integrated with respect to the random effects, such that it can be used for restricted or unrestricted maximum likelihood estimation.
+
 \subsection{Dichotomous Outcomes Tests}

### 2019-07-25 report/chapter04.Rnw
updates

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+<<echo=FALSE, warning=FALSE>>=
+p.samplesize.z  <- data.ext2 %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% ungroup() %>%
+  mutate(std.z = abs(z), sample.size = total1 + total2) %>%
+  group_by(sample.size) %>%
+  summarize(median.effect = median(std.z, na.rm = T)) %>%
+  ggplot(aes(x = sample.size, y = median.effect)) + geom_point(size = 0.8) +
+  theme_bw() + xlab("sample size") + ylab("median absolute z-score") +
+  xlim(c(15, 300)) + ylim(c(0, 0.25)) +
+  scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
+
+p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>%
+  filter(outcome.measure.new == "Risk Ratio" |
+           outcome.measure.new == "Odds Ratio" |
+           outcome.measure.new == "Mean Difference" |
+           outcome.measure.new == "Std. Mean Difference") %>%
+  group_by(outcome.measure.new) %>%
+  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
+  group_by(sample.size, outcome.measure.new) %>%
+  summarize(median.effect = median(scaled.effect, na.rm = T)) %>%
+  ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point(size = .5) + facet_wrap(~outcome.measure.new, scales = "free") +
+  theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size") +
+  xlim(c(15, 300)) +
+  scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
+@
+
+The median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
+It is clearly visible that the absolute value decreases with increasing sample size, i.e.
+that the effect size is becoming smaller.
+The trend flattens off after $\sim$ sample size = 400 (not shown).
+-- Appendix -- \\
+
+\begin{figure}
+<<echo=FALSE, warning=FALSE>>=
+plot(p.samplesize.z)
+@
+\caption{Median of the absolute $z$-score plotted against the total sample size.}
+\label{z.samplesize}
+\end{figure}
+
+Only for illustration, the same trend is reproduced in Figure \ref{effect.samplesize.separated} with a similar method, using the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std.
+Mean Difference'' (the most commonly used in the dataset).
+The ``normalized effect'' is the original effect size, normalized with respect to all other effect sizes of the same measure (i.e.
+subtraction of mean and division through standard error of the mean).
+
+\begin{figure}
+<<echo=FALSE>>=
+plot(p.samplesize.effect.sep)
+@
+\caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
+\label{effect.samplesize.separated}
+\end{figure}
 

### 2019-07-25 code/additional_plots.R

@@ -405,8 +405,25 @@ p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 10 & total1 + total
   ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point() + facet_wrap(~outcome.measure.new, scales = "free") + 
   theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size")
 
+#--------------------------------------------------------------------------------------------------------------------#
 
+meta.f$heterogeneity <- ifelse(meta.f$I2 == 0, 1, 0)
+meta.f <- meta.f %>% mutate(p.value = case_when(outcome.flag == "DICH" & heterogeneity == 1 ~ pval1.rucker,
+                                                outcome.flag == "DICH" & heterogeneity == 0 ~ pval1.rucker.linreg,
+                                                outcome.flag == "CONT" & heterogeneity == 1 ~ pval1.thompson,
+                                                outcome.flag == "CONT" & heterogeneity == 0 ~ pval1.egger,
+                                                outcome.flag == "IV" & heterogeneity == 1 ~ pval1.thompson,
+                                                outcome.flag == "IV" & heterogeneity == 0 ~ pval1.egger),
+                            
+                            classes = case_when(outcome.flag == "DICH" & heterogeneity == 1 ~ 1,
+                                                outcome.flag == "DICH" & heterogeneity == 0 ~ 2,
+                                                outcome.flag == "CONT" & heterogeneity == 1 ~ 3,
+                                                outcome.flag == "CONT" & heterogeneity == 0 ~ 4,
+                                                outcome.flag == "IV" & heterogeneity == 1 ~ 5,
+                                                outcome.flag == "IV" & heterogeneity == 0 ~ 6))
+levels(meta.f$outcome.flag) <- list("CONT" = "CONT", "DICH" = "DICH", "IV" = "IV")
 
-
+meta.f %>% ggplot(aes(x = p.value)) + facet_wrap(~ classes, nrow = 2) + geom_histogram(boundary = 0, binwidth = 0.1)
+#----------------------------------------------------------------------------------------------#
 
 

### 2019-07-25 code/analysis.R

@@ -37,12 +37,13 @@ load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
 #   mutate(n.pre = n()) %>% filter(n.pre >= 10) %>%
 #   # filter(meta.id != 94519 & meta.id != 62301) %>%  #Copas convergence..
 #   filter(!all(events1 == 0) & !all(events2 == 0)) %>% #No events
+#   mutate(se.lrr = sqrt(var.lrr)) %>%
 #   summarize(dupl.remove = unique(dupl.remove),
 #             id = unique(id),
 #             outcome.desired = unique(outcome.desired),
 #             n.sig.single = sum(sig.single, na.rm = T),
-#             se.min = min(se.new, na.rm = T),
-#             se.max = max(se.new, na.rm = T))
+#             se.min = min(se.lrr, na.rm = T),
+#             se.max = max(se.lrr, na.rm = T))
 # 
 # meta.info.cont <- data.ext2 %>% filter(outcome.flag == "CONT") %>%
 #   group_by(meta.id) %>%
@@ -54,10 +55,10 @@ load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
 #             id = unique(id),
 #             outcome.desired = unique(outcome.desired),
 #             n.sig.single = sum(sig.single, na.rm = T),
-#             se.min = min(se.new, na.rm = T),
-#             se.max = max(se.new, na.rm = T))
+#             se.min = min(se, na.rm = T),
+#             se.max = max(se, na.rm = T))
 # 
-# meta.info.surv <- data.ext2 %>%
+# meta.info.iv <- data.ext2 %>%
 #   group_by(meta.id) %>%
 #   mutate(n.pre = n()) %>% filter(n.pre >= 10) %>%
 #   filter(outcome.flag == "IV") %>%
@@ -65,12 +66,12 @@ load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
 #             id = unique(id),
 #             outcome.desired = unique(outcome.desired),
 #             n.sig.single = sum(sig.single, na.rm = T),
-#             se.min = min(se.new, na.rm = T),
-#             se.max = max(se.new, na.rm = T))
+#             se.min = min(se, na.rm = T),
+#             se.max = max(se, na.rm = T))
 # 
-# meta.info.pre <- rbind(meta.info.bin, meta.info.cont, meta.info.surv) #To save to control how many are excluded
[…]

### 2019-07-25 code/plot_point_assemblies.R

@@ -1,0 +1,40 @@
+reg.dat %>% filter(se.smd > 1.08 & se.smd < 1.15) %>% distinct(meta.id)
+
+
+reg.dat %>% filter(se.smd > 1.08 & se.smd < 1.15) %>% distinct(id)
+
+
+x <- reg.dat %>% filter(se.smd > 0.75 & se.smd < 0.85) %>% filter(smd > -0.1 & smd < 0.1)
+x %>% distinct(meta.id)
+x %>% distinct(id)
+
+
+
+plot(x$smd, x = x$se.smd, col = x$meta.id, pch = 20)
+
+x$n <- x$total1 + x$total2
+
+hist(x$n)
+
+x %>% ggplot(aes(x = se.smd, y = smd, color = factor(meta.id))) + geom_point() + theme(legend.position = "none")
+
+
+x %>% ggplot(aes(x = se.smd, y = smd, color = n)) + geom_point() +
+  scale_color_continuous(low = "darkgreen", high = "green")#+ theme(legend.position = "none")
+
+x %>% ggplot(aes(x = se.smd, y = smd, color = factor(outcome.measure.merged))) + geom_point() 
+  
+x %>% ggplot(aes(x = se.smd, y = smd, color = factor(events1 + events2))) + geom_point() 
+
+x %>% ggplot(aes(x = se.smd, y = smd, color = factor(events1 + events2))) + geom_point() 
+
+  
+ct <- x %>% filter(outcome.flag == "DICH")
+plot(ct$events1, ct$n)
+plot(ct$events1, ct$events2)
+hist(ct$events1 + ct$events2, breaks = 55)
+
+
+x %>% ggplot(aes(x = se.smd, y = smd, color = factor(events1))) + geom_point() 
+
+x %>% ggplot(aes(x = se.smd, y = smd, color = factor(events2))) + geom_point() 

### 2019-07-27 report/MSc_Report.tex
results correction

@@
 
-Studies get more attention and are more likely to be published, read and cited if they are implying significant effects.
+Studies get more attention and are more likely to be published, read and cited if they contain significant effects.
 Studies with no evidence for an effect are less likely to get published.
@@
 The issue has been discussed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}).
+Consensus is that publication bias exists in clinical science.
 \\
 In medical research, clinical trials study the efficacy of therapies and drugs.
-The gold standard in such intervention studies are randomized, (placebo) controlled, trials (RCTs).
-Results from such clinical studies influence the treatment of patients in daily clinical practice.
-The results from multiple intervention studies are However, publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm.
-\\
+The gold standard in such intervention studies are randomized controlled trials (RCTs).
+Results from RCTs influence the treatment of patients in daily clinical practice.
+The results from multiple intervention studies can be summarized in a meta-analysis to estimate an overall treatment effect (access all studies).
+However, publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm, distortion and financial expenses.
+\\
+There is extensive literature on publication bias in meta-analyses, e.g. (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02},
+\citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}).
+The authors agree on that the exclusion of unpublished results in meta-analyses is responsible for overestimation of treatment effects.
+Although there are policies that make it mandatory to make all study results publicly accessible \citep{fda}, it is not clear if the situation has improved yet.\\
 There are multiple ways to assess the amount of publication bias.
-For instance, one can follow studies and control if they are getting published depending on their findings \citep{publication.fate}.
+For instance, it is possible to follow studies and assess if they are getting published depending on their findings \citep{publication.fate}.
 One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in social sciences: \citet{social.sciences.publication.bias}).
@@
 \\
-A third way is to assess the so-called small study effect in a meta-analysis, that is, a systematic difference between effects of large and small studies.
-Evidence for small study effects can oftentimes be interpreted as evidence for publication bias \citep{Egger}.
-The underlying rational is that journal editors are guided by two simple rules (\citet{excess.significance}, \citet{ioannidis.2019}):
+A third way is to assess the so-called small study effect in a meta-analysis, that is, smaller studies sometimes showing different, often larger treatment effects than large ones (cite sb).
+Importantly, this method does not assess publication bias directly.
+But the estimation of small study effects is oftentimes the most efficient way to investigate publication bias in a large number of meta-analyses.
+However, evidence for small study effects can oftentimes be interpreted as evidence for publication bias \citep{Egger}, as this is the most likely cause, even though there may also be other explanations.
+The underlying rationale is that journal editors are guided by two simple rules (\citet{excess.significance}, \citet{ioannidis.2019}):
 \begin{itemize}
@@
 \end{itemize}
-This then leads to the asymmetry in the funnel plot of published studies; small studies show larger effect sizes than larger studies do.
-A funnel plot allows visual inspection of small study effects by plotting the effects against their standard error.
-For illustration purposes, one meta-analysis with large funnel plot asymmetry and one with no asymmetry is shown in Figure \ref{small.study.effect.example}.
+
+This then leads to an asymmetry in published studies; small studies show larger effect sizes than larger studies do.
+A funnel plot(cite sb) allows visual inspection of small study effects by plotting the effects against their standard error.
+For illustration purposes, one meta-analysis with large funnel plot asymmetry and one with no asymmetry is shown in Figure \ref{small.study.effect.examples }.
 %\citep{pre.eclampsia}:
@@
 \\
-We see that while the studies in the meta-analysis on the left are not filling the triangle evenly, but rather accumulate at the left side, they seem to be more evenly distributed in the left triangle.
+We see that while the studies in the meta-analysis on the left are not symmetrically distributed, but rather accumulate at the left side, they seem to be more evenly distributed in the left triangle.
 From this, we would ultimately conclude that some sort of bias or heterogeneity is distorting the estimate of the overall treatment effect.\\
-Importantly, this method does not assess publication bias directly.
-But note that publication bias is also not assessable with the other methods if no complete study registries are available.
-Thus, the estimation of small study effects is oftentimes the most efficient and simple way to analyse publication bias.
-
-\section{Aim of the study}
-
-There is extensive literature on publication bias in meta-analyses, e.g. (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02},
-\citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}).
-The authors agree on that the exclusion of unpublished results in meta-analyses is responsible for overestimation of treatment effects.
-Although there are policies that make it mandatory to make all study results publicly accessible \citep{fda}, it is not clear if the situation has improved yet.\\
 The Cochrane Organisation has specialized on systematic reviews of healthcare interventions.
@@
 By extensive literature scrutinization, they try to circumvent the issue of publication bias.
+They do not apply funnel plot asymmetry tests to analyse publication bias.
 Earlier research however suggests that the efforts are only partially succesful, and that there still is publication bias within the reviews (\citet{Egger}, \citet{Ioannidis2007}, \citet{kicinsky}, \citet{vanAert.2019}).
@@
 Their results will be compared to the results of this study in the last chapter.\\
+
+\section{Aim of the Study}
 None of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods.
@@
 The aim of this thesis is to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides.
-At the end, an up-to-date estimate of the prevalence of publication bias in the data shall be given, as well as its implications regarding the effect sizes of the treatments.
+At the end, an approximate, up-to-date estimate of the prevalence of publication bias in the data shall be given.
 To achieve this, methods to detect and adjust for publication bias in meta-analysis are applied on the data.
+\\
+It is also possible to adjust for publication bias with suitable methods.
+These methods are applied on the dataset as well, to achieve publication bias adjusted treatment effect estimates.
+It will be shown if and to what extent treatment effects are overestimated due to publication bias in the Cochrane systematic reviews.
 
@@
 The analysis has already been said to be restricted on clinical or health care interventions.
-The interventions are restricted to comparisons of two treatment arms by some measure of sanity or worsening of health.
+The interventions are restricted to comparisons of two treatment groups by some measure of melioration or worsening of health.
 The difference in this measure between the groups is referred to as the treatment effect.
-Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or Hedges $g$, Fisher's z score or Pearsons correlation coefficient.
-\\
+Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or standardized mean difference, Fisher's z score or Pearsons correlation coefficient.\\
 Let us consider a meta-analysis with $n$ study treatment effects ($n > 1$, but typically small).
@@
 $n_t$ and $n_c$ are the total number of participants in the groups.
-In the case of binary outcomes, let $e_t$ be the count of events in the treatment arm $e_c$ the count of events in the control group.
+In the case of binary outcomes, let $e_t$ be the count of events in the treatment arm $e_c$ the events in the control group.
 The observed counts in a study $i$ are referred to as $e_{t,i}$ and analogously $e_{c,i}$.
@@
 \subsection{Continuous Outcomes}
-For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Hedges $g$) and  a standard error thereof.
-Note that the definition of Hedges $g$ and its standard error $\se$ varies among the literature, the following applies for this report:
+For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Cohen's $d$) and a standard error thereof.
+The mean difference can $\theta$ and its standard error $\se$ can be obtained as
+
+\begin{align}
+\theta &= m_t - m_c & \se &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_t}
+\end{align}
+
+The standardized mean difference $d$ and its standard error $\se$ can similarly be obtained by
 
@@
 \se &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}} & g &= \frac{m_t - m_c}{\se} \label{eq:hedges.g}
-\end{align}
-
-The mean difference $\theta$ and its standard error $\se$ can similarly be obtained by
-
-\begin{align}
-\theta &= m_t - m_c & \se &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_t}
 \end{align}
@@
 A $p$-value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$ test.
-The $t$ statistic is obtained, using $s$ and $g$ from \ref{eq:hedges.g}, by
-
-\begin{align}
-t &= g/(s\sqrt{(1/n_t)+(1/n_c)}) \nonumber
+The $t$ statistic is obtained, using $\se$ and $d$ from \eqref{eq:hedges.g}, by
+
+\begin{align}
+t &= d/(\se\sqrt{(1/n_t)+(1/n_c)}) \nonumber
 \end{align}
@@
 \begin{align}
-\theta &= \log(\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}) \nonumber \\
+\hat{\theta} &= \log(\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}) \nonumber \\
 \se^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
@@
 \begin{align}
-\theta &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
-\se^2&= 1/e_t + 1/n_t + 1/e_c + 1/e_t \label{eq:risk.ratio.variance}
+\hat{\theta} &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
+\se^2&= 1/e_t - 1/n_t + 1/e_c - 1/e_t \label{eq:risk.ratio.variance}
 \end{align}
@@
 $\tau^2$ is often referred to as a population variance or between-study variance, whereas $\se_i^2$ can be interpreted as sampling error.
-The pooled treatment effect estimate $\theta_M$ of the random effects model and its variance is obtained by replacing the weights $w_i$ in equation \ref{eq:fixed.effects} with $w_i = 1/(\se_i^2 + \tau^2)$.
+The pooled treatment effect estimate $\theta_M$ of the random effects model and its variance is obtained by replacing the weights $w_i$ in equation \eqref{eq:fixed.effects} with $w_i = 1/(\se_i^2 + \tau^2)$.
 \\
@@
 
-$\theta_M$ can be estimated using equation \ref{eq:fixed.effects}, the only problem is to estimate $\tau^2$. It can be obtained through an iterative process, using a newly defined function
+$\theta_M$ can be estimated using equation \eqref{eq:fixed.effects}, the only problem is to estimate $\tau^2$. It can be obtained through an iterative process, using a newly defined function
 
@@
 
-In view of equation \ref{eq:paulemandel}, $\tau^2$ must be such that $F(\tau^2) = 0$.
+In view of equation \eqref{eq:paulemandel}, $\tau^2$ must be such that $F(\tau^2) = 0$.
 Then, we start with a arbitrary $\tau^2$ and repeatedly add a term $\tau_0^2$ to update $\tau^2$ until $F(\tau^2 + \tau_0^2)$ is close to zero (using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{\theta}_M$).
@@
 A common procedure is to test if it is there is significant heterogeneity between the studies \cite[109]{Intro.meta}.
-Compute $Q$, as given in \ref{eq:Q.heterogeneity}, based on one of the estimators of $\tau^2$.
+Compute $Q$, as given in \eqref{eq:Q.heterogeneity}, based on one of the estimators of $\tau^2$.
 It is assumed that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equally distributed effect sizes.
@@
 \citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
-A standardized effect size $\theta_i^\star$ can be computed as in \ref{begg.stand.eff}.
-$\se_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \ref{begg.stand.var}, $\theta_M$ being the fixed effects pooled treatment effect (\ref{eq:fixed.effects}.
-
-\begin{align}
-\theta_i^\star &= (\theta_i - \theta_M)/\se_i^{2\star} \label{begg.stand.eff}  \\
-\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2}1 \label{begg.stand.var} 
+A standardized effect size $\theta_i^\star$ can be computed as in \eqref{eq:begg.stand.eff}.
+$\se_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \eqref{eq:begg.stand.var}, $\theta_M$ being the fixed effects pooled treatment effect (\eqref{eq:fixed.effects}.
+
+\begin{align}
+\theta_i^\star &= (\theta_i - \theta_M)/\se_i^{2\star} \label{eq:begg.stand.eff}  \\
+\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2}1 \label{eq:begg.stand.var} 
 \end{align}
@@
 Weighted linear regression may be used if the residuals $\mathbf{r}$ have unequal variances, which is equivalent to ascribe different precision to the observed $y$.
-The least squares equation \ref{eq:least.squares} is extended to
+The least squares equation \eqref{eq:least.squares} is extended to
 
@@
 Let $\mathbf{W}$ be a $n \times n$ matrix with $\mathbf{W}_{ii} = w_i$, the weights on the diagonal and zeros on the off-diagonals.
-The estimates in \ref{eq:regression.parameters} and \ref{eq:regression.variances} can still be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$.
+The estimates in \eqref{eq:regression.parameters} and \eqref{eq:regression.variances} can still be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$.
 \label{weighted.regression} \\
@@
 If plotted, this corresponds to a radial or Galbraith plot \citep{galbraith}.
-The linear regression equation as introduced before in \ref{eq:simple.regression} can be written in two ways:
+The linear regression equation as introduced before in \eqref{eq:simple.regression} can be written in two ways:
 
@@
 with weights $w = 1/\se^2$.
-Thus testing $\beta_0$ of \ref{eq:radial.plot} or $\beta_1$ is equivalent.
+Thus testing $\beta_0$ of \eqref{eq:radial.plot} or $\beta_1$ is equivalent.
 The corresponding $p$-value is then used as evidence for a small study effect.
-Plugging in  $\theta_i/\se_i, 1/\se_i$ as $y_i, x_i$ into equation \ref{eq:regression.parameters} and \ref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{\se}_{\beta_0}$ and $\hat{\se}_{\beta_1}$.
+Plugging in  $\theta_i/\se_i, 1/\se_i$ as $y_i, x_i$ into equation \eqref{eq:regression.parameters} and \eqref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{\se}_{\beta_0}$ and $\hat{\se}_{\beta_1}$.
 
@@
 
-$\tau^2$ is estimated as in equation \ref{eq:Tau.definition} (method of moments). %or \ref{eq:paule.mandel}. 
+$\tau^2$ is estimated as in equation \eqref{eq:Tau.definition} (method of moments). %or \eqref{eq:paule.mandel}. 
 The weights are set as $w_i = 1/\sqrt{\se_i^2 + \tau^2})$.
@@
 
-The issue with dichotomous outcomes is that effect size and variance of effect size are correlated, which can readily be seen in \ref{eq:risk.ratio} and \ref{eq:risk.ratio.variance}.
+The issue with dichotomous outcomes is that effect size and variance of effect size are correlated, which can readily be seen in \eqref{eq:risk.ratio} and \eqref{eq:risk.ratio.variance}.
 For example, a small number of event counts in one or group will inflate the variance and the effect size.
@@
 \\
-We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated by fixed effects Meta-Analysis \ref{eq:fixed.effects}.
+We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated by fixed effects Meta-Analysis \eqref{eq:fixed.effects}.
 Let $O$ be the number of significant study results out of $n$ studies and $\alpha$ the significance threshold.
@@
 to obtain an unbiased estimate. Similarly to 
-%what has been seen in Copas selection model, we let $y_i$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_i}$ as in \ref{limitmeta.regression}.
+%what has been seen in Copas selection model, we let $y_i$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_i}$ as in \eqref{limitmeta.regression}.
 regression based tests for small study effects, we have
@@
 $\theta$ is the population mean effect, $\sigma_i^2$ the within study variance and $\tau^2$ the between study variance.
-Equations in \ref{eq:population.model} are termed the \textit{population model}.
+Equations in \eqref{eq:population.model} are termed the \textit{population model}.
 \\
@@
 Although one has to evaluate the likelihood for fixed pairs $(a,b)$, one can compare the fit of the model to evaluate which one is more suitable:
-With equation \ref{eq:copas.expectation}, one can obtain fitted values of $\theta_i$ based on $\se_i$. Also, for two different pairs $(a,b)$, $(a^\star, b^\star)$,
+With equation \eqref{eq:copas.expectation}, one can obtain fitted values of $\theta_i$ based on $\se_i$. Also, for two different pairs $(a,b)$, $(a^\star, b^\star)$,
 
@@
 \citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes. \\
-A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \ref{eq:copas.small.study} is applied.
+A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \eqref{eq:copas.small.study} is applied.
 If all obtained $p$-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for modelling, and the standard, classical random effects meta-analysis is retained.
@@
 
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Scale for 'x' is already present.
+Adding another scale for 'x', which\\\#\# will replace the existing scale.\\\#\# Scale for 'x' is already present.
+Adding another scale for 'x', which\\\#\# will replace the existing scale.}}\end{kframe}
+\end{knitrout}
+
+Using Fisher's $z$ transformation, we can transform all effect sizes of the dataset on the same scale such that they are comparable to each other.
+Thus, as a first step, an exploratory plot of the median effect size and it's dependence on the study sample size can be shown.
+\\
+The absolute value of the median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
+It is clearly visible that the absolute value decreases with increasing sample size, i.e.
+that the effect size is becoming smaller.
+The trend flattens off after $\sim$ sample size = 400 (not shown).
+\\
+The pattern is similar in Figure \ref{effect.samplesize.separated}, where the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std.
+Mean Difference'' are used (the most common measurs in the dataset).
+Here, the effect sizes are scaled (mean subtraction and divison through standard error) with respect to all other effects of the same measure.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-11-1}
+
+\end{knitrout}
+\caption{Median of the absolute $z$-score plotted against the total sample size.}
+\label{z.samplesize}
+\end{figure}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-12-1}
+
+\end{knitrout}
+\caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
+\label{effect.samplesize.separated}
+\end{figure}
+
 \section{Publication Bias Test Results} \label{sec:publication.bias.tests}
 
-The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with one-sided small study effects tests and excess significance tests.
+The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with one-sided small publication bias tests and excess significance tests.
 The direction in which bias is expected is the one on which more significant results are ($p$-value < 0.05, two-sided).
-The tests are applied on the original effect size measures, i.e.
-risk ratios, Hedges $g$ or other effect measures (\texttt{outcome.flag} = \texttt{IV}).
-Different tests are applied depending on the outcome type being binary, continuous or IV.\\
-Thus, multiple tests are applied on the same data.
-The results can then be displayed separately to compare the results from the different tests.
-A histogram of $p$-values will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.
-\\
+The tests are applied on the original effect size measures, since the journal editors and the researchers also base their decisions on them.
+Different tests are applied depending on the outcome being binary or continuous.\\
+Multiple tests are applied on the same data to compare their results.
+A histogram of $p$-values for each test and all meta-analyses will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.
+Skewedness indicates evidence for publication bias.\\
+The abbreviations in Figure \ref{fig:test}  are shortly explained with references to chapter \ref{ch:methods}: \\
 ``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}.
-For continuous and IV outcomes, the names refer to:
+For continuous and \texttt{IV} outcomes, the names refer to:
 
 \begin{itemize}
-\item Egger's test, the weighted linear regression test as described in section \ref{sec:Egger}
-\item Thompson and Sharp's test, the weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
-\item Begg and Mazumdar's test, the rank test described in section \ref{sec:Begg}
+\item Egger's test, weighted linear regression test described in section \ref{sec:Egger}
+\item Thompson and Sharp's test, weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
+\item Begg and Mazumdar's test, rank test described in section \ref{sec:Begg}
 \end{itemize}
@@
 \begin{itemize}
-\item Harbord's test, the likelihood score based test (section \ref{sec:Harbord})
-\item Peter's test, the weighted linear regression with inverse sample size as explanatory variable (study size proxy) described in section \ref{sec:Peter}
-\item R\"ucker's test, the test based on the arcsine transformation of proportions, in combination with Thompson and Sharp's regression test (section \ref{sec:Rucker})
-\item Schwarzer's test, the rank based test using the expected event counts computed with the hypergeometric distribution (section \ref{sec:Schwarzer})
+\item Harbord's test, likelihood score based test (section \ref{sec:Harbord})
+\item Peter's test, weighted linear regression with inverse sample size as explanatory variable described in section \ref{sec:Peter}
+\item R\"ucker's test, test based on the arcsine transformation of proportions, in combination with Thompson and Sharp's regression test (section \ref{sec:Rucker})
+\item Schwarzer's test, rank based test using the expected event counts computed with the hypergeometric distribution (section \ref{sec:Schwarzer})
 \end{itemize}
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-11-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-14-1}
 
@@
 %Agreement table -> Chunck 1
-The histograms in Figure \ref{fig:test} show that most distributions are clearly skewed to the right, indicating evidence for small study effects.
-Exceptions from this are the excess significance and Schwarzer's test, and the tests for IV outcomes.
-There, there is no evidence for publication bias, and the histograms are even skewed to the left (Schwarzer).
-But note that the sample size of IV outcomes is small ($n$ = 140).
-\\
-There is discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger.
-Also, we see that the $I^2$ statistic of the proportion of overall between-study heterogeneity is distributed differently for the tests, with results with $I^2 = 0$ being evenly distributed in binary outcomes along the range of $p$-values, while they are more similar to the meta-analyses with larger heterogeneity for continuous outcome.\\
-In the literature, the excess significance test is advised to be used in the case of no between study heterogeneity.
-Since there are no small $p$-values for such meta-analyses, one must conclude that there is no excess significance in the dataset.
-The obvious correspondence with the heterogeneity statistic however rather suggests that the test is another way to assess between study heterogeneity.
-Thompson test and R\"ucker's test are designed such that they take into account the between study heterogeneity when assessing small study effects.
-When no heterogeneity is given, Thompson's test results and Egger's test result should be equal, however, the $I^2$ statistic is computed by a more suitable estimator \citep{paulemandel} of $\tau^2$ as the estimator that Thompson and Sharp's test uses (method of moment estimator of \citet{tau.estimator}, which is more conservative by usually finding larger $\tau^2$).
-In the part of the histogram with $I^2 > 0$, the two tests are more reliable than the remaining tests, while the opposite is expected from simulations \citep{limitmeta} when $I^2 = 0$.\\
+The histograms in Figure \ref{fig:test} show that the tests are not alway in agreement if publication bias is present in the data.
+The $p$-values of excess significance and Schwarzer's test and the $p$-values for \texttt{IV} outcomes are rather uniformly distributed, or even skewed to the right.
+Notably, excess significance test, Schwarzer's test and rank tests have been shown to lack power.
+The tests that are more suitable (regression based tests in general) all have proportions of significant $p$-values ($p$ > 0.1) clearly above 10 \% which would be the expected false positive rate.
+The conclusion is that there is publication bias, however the extent can be debated.
+The meta-analyses with \texttt{outcome.flag} = \texttt{IV} seem to differ from the other meta-analyses.
+\\
+In Figure \ref{fig:test}, the meta-analyses with an estimated $I^2$ of zero are depicted, because some methods are known to only be suitable when no heterogeneity is present (excess significance test and also Egger's test).
+Others are specially constructed to adjust for between study heterogeneity (Thompson and Sharp's test and R\"ucker's test).
+In continuous outcomes, when Thompson and Sharp's test is applied, the evidence for publication bias decreases, as can be seen in the smaller proportion of blue on the left corner in Figure \ref{fig:test}.
+However, this is also due to application to meta-analyses with $I^2$ equal zero, in which case the method is known to lack power.
+Similarly, the evidence decreases somewhat when R\"ucker's test is extended by Thompson and Sharp's method to account for heterogeneity.
+The moderate decrease indicates however that the previous restriction to meta-analyses with $I^2 < 0.5$ is sufficient to remove meta-analyses with large heterogeneity and that the test results are not heavily influenced by unaccounted between study heterogeneity.
+\\
+The $p$-values of tests can be summarized by computing their harmonic mean.
+In the case of binary tests, the $p$-values of R\"ucker's, Peters, Harbord's, Schwarzer's and excess significance tests are used, in the case of continuous and \texttt{outcome.flag} = \texttt{IV} outcomes, Egger's, Thompson and Sharp's, Begg and Mazumdar's and excess significance tests are used.
+This lead's to an overall of 19.1\% significant results ($p_\textrm{harmonic}$ < 0.1, 19.7\% \texttt{outcome.flag} = \texttt{DICH}, 20.1\% \texttt{outcome.flag} = \texttt{CONT}, 12.9\% \texttt{outcome.flag} = \texttt{IV}).
 
@@
 This is done in Figure \ref{fig:test.agreement}.
-Here, there is no separation between IV and continuous outcomes.
-The upper left rectangle is displaying binary outcome results and the lower right continuous and IV outcomes results.
+Here, there is no separation between \texttt{IV} and continuous outcomes.
+The upper left rectangle is displaying binary outcome results and the lower right continuous and \texttt{IV} outcomes results.
 Also, the $I^2$ statistic is included.
-Since no test statistic is used for excess significance tests, it is not shown here
+Since no approximately normally distributed test statistic is used for excess significance tests, it is not shown here
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-12-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-15-1}
 
@@
 Regression based tests as Egger and Thompsons test which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients.
-Continuous and IV outcome type tests align more closely than binary outcome tests.
+Continuous and\texttt{IV} outcome type tests align more closely than binary outcome tests.
 While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics.\\
@@
 This can be justified since all tests are supposed to measure the evidence for publication bias.
-For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation $f(x)  = \log\frac{p}{1-p}$).
+For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation $f(x)  = \log(\frac{p}{1-p}$).
 The mean $p$-value (($f$($p$-value no.
@@
 \item the mean of the differences should be around zero (no systematic error) 
-\item the points should scatter independently on the $y$-axis and no general increase or decrease with the mean of the transformed $p$-values should be visible
+\item the points should scatter independently on the $y$-axis and no general increase or decrease with the mean of the transformed $p$-values should be visible (and the linear regression fit is flat)
 \end{itemize}
 
-Although this is not formally tested, there are likely systematic errors and bias between excess significance tests, although more so for continuous tests.
--- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- \\
+There are likely systematic errors and bias between the tests, although the extent seems to vary.
+Most error seems to be between small study effect tests and excess significance tests, because the slope of the linear regression fit is likely positive.
+This means that the excess significance test finds less evidence in cases when both $p$-values are small and more evidence when both $p$-values are large, on average.\\
 The confidence intervals from Figure \ref{fig:mean.diff.test} can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests.
-This suggests that correspondence between the tests is not very good in general.
+This suggests that additionally to the bias correspondence between the tests is not very good in general.
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-13-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-16-1}
 
@@
 The mean of logit transformed $p$-values is displayed on the $x$-axis and the difference on the $y$-axis.
-Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).}
+Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).
+In green, a linear regression fit is shown with 95\% CI bands.}
 \label{fig:mean.diff.test}
@@
 The previous results suggest that the results will also differ substantially after applying the common dichotomization of $p$-values.
-We expect that some proportion of the meta-analysis will only be significant for a certain test, and this is indeed observed in Table \ref{number.sig.tests}.
+Some proportion of the meta-analyses will only be significant using a single test, while being non-significant otherwise.
+This can be seen in Table \ref{number.sig.tests}.
 It displays the percentage of meta-analyses with a certain number of significant test results.
+For both outcome types, there is only marginal agreement, very few cases are significant in any test.
+Around 67\% of the dataset is not significant, no matter which test is used.
+When only using small study effect tests, 29.5\% of binary outcome tests and 29\% of \texttt{IV} and continuous outcome tests had at least one significant result.
+After applying the Bonferroni correction for multiple testing, this shrinks to 12.3\% for binary and 12\% for continuous and \texttt{IV} outcomes.
+To compare significant findings for small study effect tests and excess significance tests, Harbord's or Egger's test results are compared with excess significane tests.
+24.1\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 24.4\% for continuous and \texttt{IV} outcomes.
+The numbers change to 13.9\% for binary outcomes and 14.7\% for continuous and \texttt{IV} outcomes after applying the Bonferroni correction.
+5.1\% have significant Harbord's test result and significant excess significance test result  (2.3\% with Bonferroni).
+Of the continuous outcomes, we have 3.3\% with Egger's test and 1.4\% with Bonferroni correction.
+\\
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Jul 23 11:07:27 2019
+% Sat Jul 27 15:44:17 2019
 \begin{table}[ht]
@@
   \hline
-0 & 66.1 \% & 67.9 \% \\ 
-  1 & 12.3 \% & 11.8 \% \\ 
-  2 & 7.7 \% & 6.9 \% \\ 
-  3 & 6.8 \% & 12.2 \% \\ 
-  4 & 5.7 \% & 1.3 \% \\ 
+0 & 66.1 \% & 68.9 \% \\ 
+  1 & 12.3 \% & 11.2 \% \\ 
+  2 & 7.7 \% & 6.6 \% \\ 
+  3 & 6.8 \% & 11.4 \% \\ 
+  4 & 5.7 \% & 1.9 \% \\ 
   5 & 1.3 \% & - \\ 
@@
 
-Here, it is difficult to say if continuous and IV or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and IV outcome type tests have in general more positive findings.
-Very few meta-analyses are significant, irrespective of the test used, but around 67\% of the dataset is not significant, no matter which test is used.
-\\
-When only looking at small study effect tests, 29.5\% of binary outcome tests and 29.8\% of IV and continuous outcome tests had at least one significant result.
-After applying the Bonferroni correction for multiple testing, this shrinks to 12.3\% for binary and 12.4\% for continuous and IV outcomes.
-\\
-% To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test.
-mean.min.bin2\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, mean.min.else2\% for continuous and IV outcomes.
-The numbers change to mean.min.bin2.b\% for binary outcomes and mean.min.else2.b\% for continuous and IV outcomes after applying the Bonferroni correction.
-\\
-% both.bin\% have significant Harbord's test result and significant excess significance test result  (both.bin.b\% with Bonferroni).
-Of the continuous outcomes, we have both.else\% with Egger's test and both.else.b\% with Bonferroni correction.
+The precise proportions of agreement are provided in table \ref{test.agreement}.
+We see that only in few cases when excess significance test indicates statistical significance, small study effect tests do so.
+Correspondence between excess significance tests and small study effects thus has to be considered rather random.
+Linear regression based tests agree more often with other linear regression based tests, and agreement between small study effect tests is in general well above 60 \% (at best, 95 \% test agreement in significance for \texttt{IV} \texttt{outcome.flag}).
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sat Jul 27 15:44:17 2019
+\begin{table}[ht]
+\centering
+\begingroup\scriptsize
+\begin{tabular}{lcc}
+  \hline
+ & Agreement (overall) & Agreement (significance) \\ 
+  \hline
+Excess significance, Schwarzer & 0.85 & 0.27 \\ 
+  Excess significance, Peter & 0.77 & 0.32 \\ 
+  Excess significance, Rucker & 0.79 & 0.43 \\ 
+  Excess significance, Harbord & 0.81 & 0.46 \\ 
+  Peter, Schwarzer & 0.84 & 0.63 \\ 
+  Schwarzer, Rucker & 0.85 & 0.72 \\ 
+  Schwarzer, Harbord & 0.87 & 0.78 \\ 
+  Rucker, Peter & 0.88 & 0.67 \\ 
+  Harbord, Peter & 0.87 & 0.63 \\ 
+  Excess significance, Egger & 0.77 & 0.64 \\ 
+  Excess significance, Thompson & 0.80 & 0.59 \\ 
+  Excess significance, Begg & 0.78 & 0.36 \\ 
+  Thompson, Egger & 0.93 & 0.92 \\ 
+  Thompson, Begg & 0.87 & 0.70 \\ 
+  Egger, Begg & 0.84 & 0.70 \\ 
+  Excess significance, Egger (IV) & 0.84 & 0.09 \\ 
+  Excess significance, Thompson (IV) & 0.84 & 0.10 \\ 
+  Excess significance, Begg (IV) & 0.85 & 0.10 \\ 
+  Thompson, Egger (IV) & 0.98 & 0.95 \\ 
+  Thompson, Begg (IV) & 0.86 & 0.55 \\ 
+  Egger, Begg (IV) & 0.87 & 0.60 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Overall proportion of agreement if significant or unsignificant, and for significance only.
+Horizontal lines separate binary, continuous and IV outcomes (order as in table).
+The reference significance test is the one with more significant results.}
+\label{test.agreement}
+\end{table}
 
@@
 
-Since there's evidence for publication bias when applying small study effect and excess significance tests, we apply small study effect adjustment methods to take into account that small studies are likely overestimating the treatment effect.
-\\
-However, we will see that consequences of adjustment can be; 
-\begin{itemize}
-\item first, the absolute size of the treatment effect can be smaller than the classical meta-analysis treatment effect, which is expected if publication bias
-is the cause for the small study effect.
-\item secondly, the effect can be larger than before in meta-analysis.
-In this case, the small study effect must be not due to publication bias for large effects (``true'' publication bias), but due to bias for small effects (``null effect publication bias'' or even ``reversed effect publication bias'', sometimes refer erred to as ``Proteus phenomenon'' \citep{proteus}).
-\end{itemize}
-
-This is because, in contrast to the small study effect tests, the applied adjustment method does not pre-specify the direction in which bias is expected. \\
-To compare the effects of adjustment between meta-analyses, the outcome measures are transformed to Hedges $g$ (standardized mean differences) and Fisher's $z$-score (see section \ref{sec:transformation.effectsizes} for details).
-The effect of adjustments can be compared to either random or fixed effects meta-analysis estimates.
-\\
-Figure \ref{fig:adjustment.reg} displays the difference $\delta$ between the observed meta-analysis pooled treatment effect and the regression adjusted treatment effect, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
-The absolute value $|\hat{\theta}_M|$ is taken and the sign of $\hat{\theta}_\textrm{Adj.}$ is adjusted accordingly such that all effects are mirrored to one side.
-$\delta > 0$ is equivalent to $\hat{\theta}_\textrm{Adj} < \hat{\theta}_M$, a reduction of the original effect size.
-Additionally, the test statistic of heterogeneity adjusted small study effect tests (R\"ucker's and Thompson's test) is displayed with green color.
-Test statitics smaller $< 1$ are equivalent to no evidence for small study effect, test statistics between one and two to weak evidence, and above two they indicate evidence for small study effects.
-Some very large and very small differences have been omitted in the $z$-score and Hedges $g$ histograms; they are shown in Table \ref{missing.differences}.
+There are methods that can take into account the presence of publication bias in meta-analyses when estimating the overall treatment effect.
+The methods work in a semi-automatic manner; they will not only adjust for publication bias if smaller studies show larger effects, but also in the opposite case.
+The latter results in the adjusted overall treatment effect being \textit{larger} than the unadjusted, overall treatment effect.
+\\
+To compare the effects of adjustment between meta-analyses of different outcomes, the outcome measures are transformed to standardized mean differences and Fisher's $z$-scores (see section \ref{sec:transformation.effectsizes} for details).
+When comparing to unadjusted effects, fixed or random effects meta-analysis estimates are used as references\\
+Figure \ref{fig:adjustment.reg} displays the difference $\delta$ between the estimated meta-analysis treatment effect and the regression adjusted treatment effect \ref{sec:regression.adjustment}, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
+The absolute value $|\hat{\theta}_M|$ is taken and $\hat{\theta}_\textrm{Adj.}$ is negative if the signs change in the original $\theta$.
+Thus, a positive difference indicates a reduction of the original effect size, and the magnitude of the difference indicates the extent of the adjustment.
+\\
+Additionally, the test statistic of heterogeneity adjusted publication bias tests (R\"ucker's and Thompson's test) are displayed with green color.
+Test statitics smaller $< 1$ (light green colored) are equivalent to no evidence for publication test, test statistics between one and two to weak evidence, and above two they indicate evidence for publication bias (dark green).
+An adjusted effect with evidence for publication bias can be regarded as a more realistic estimate of treatment efficacy.
+Some very large and very small differences have been omitted in the $z$-score and std.
+mean difference histograms; they are shown in Table \ref{missing.differences}.
+\\
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-16-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-20-1}
 
@@
 
-We see that more treatment effect sizes are negatively adjusted and diminished.
-Furthermore, we see that large adjustment is not necessarily connected with evidence for small study effects, but there is coincidence.
-Adjustment was larger when random effects meta-analysis effect is used as reference, because there larger weights are given to small studies.\\
-The cases with no evidence (clear green color) and large adjustment indicate that between-study heterogeneity was not resolved by adjustment for small study effects.
-The regression adjustment method as described in section \ref{sec:regression.adjustment} adjusts for small study effects even if there is no evidence for small study effects.
-Thus, a large change in effect sizes does not necessarily have to be accompained by evidence for small study effects, because the unceratinity of the small study effect is not taken into account by the adjustment method.
-The uncertainity of the adjusted estimates is consequently larger in the clear green fraction of the histogramm than in the deeper green fraction.\\
-Figure \ref{fig:adjustment.copas} shows the same for effect sizes adjusted by Copas; Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
-Therefore, the effect of adjustment by Copas can be seen when comparing adjusted with random effects estimates.
-Again, we clearly see that more effect sizes are adjusted downwards.
-Additionally, there is more coincidence with the small study effect test statistics and adjustment, which is as expected.
-\\
+Most often, adjustment leads to a reduction of overall treatment effect estimates, because the bins on the positive side of the histograms are larger.
+Adjustment is stronger when random effects meta-analysis is used as reference, because it gives larger weights to small studies.\\
+Contrary to naive expectation, we see cases with large adjustment, but no evidence for small study effects.
+This is because the linear regression parameter estimates are large, but estimated with high uncertainity, such that there will be few evidence for small study effects (publication bias), but nonetheless, the adjustment will be large.
+The authors that developped the methods also recommend to use the methods in cases where there is clear evidence for publication bias.
+The color legend in Figure \ref{fig:adjustment.reg} thus gives a sense of confidence that there is in the credibility of the adjustment.
+\\
+Additionally, some meta-analyses with positively adjusted, larger overall treatment effects after adjustment (left side of the histogram) have at the same time evidence for publication bias.
+This is no wrong result, although the $p$-value of the test is one-sided, \ie only allowing for publication bias for large effects (small studies with large effects).
+But the effects and their variances have been transformed, and it is possible that the shape of the funnel plot changes upon transformation; Figure \ref{fig:funnel.plot.change} shows this for illustratory purposes.
+From the left to the right, the funnel plot is shown for mean differences (the original measure), standardized mean differences and Fisher's $z$ scores.
+This is quite the most extreme case, with three different effects of adjustment, depending on outcome measure; there is no change with mean differences, reduction of effect sizes with std.
+mean differences and increase with Fisher's $z$ transformed correlation.
+Note that while the rank of the effect sizes is usually preserved after transformation, the relative size and especially the variance may vary.
+One effect of the Fisher's $z$-transformation is that the effect sizes are bounded on $[-1,1]$, and thus, very large effect sizes will influence the fit of the linear regression less than for example in std.
+mean differences which are not bounded.
+In contrast, the variance of the correlation is directly tied to the sample size, which makes it a suitable proxy for study size (variance of the mean difference is in contrast strongly influenced by the standard deviations).
+Thus, cases where the direction of adjustment changes upon transformation are not very rare.
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-17-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-21-1}
+
+\end{knitrout}
+\caption{Funnel plots for a meta-analysis based on three different effect size measures: Mean differences, std.
+mean differences and Fisher's z transformed correlations and corresponding standard errors.
+Vertical dashed lines indicate meta-analysis estimates, the rhombus with the curved blue line the adjusted treatment effect.}
+\label{fig:funnel.plot.change}
+\end{figure}
+
+Figure \ref{fig:adjustment.copas} shows the same for effect sizes adjusted by Copas; Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
+Therefore, the effect of adjustment by Copas can be seen when comparing adjusted with random effects meta analysis estimates.
+Again, we clearly see that more effect sizes are adjusted downwards.
+Additionally, there is more coincidence between the publication bias test statistics and adjustment, which is as expected.
+\\
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-22-1}
 
@@
 
-Table \ref{adjustment.difference} shows the quantiles and means for the various differences and additional information.
+Table \ref{adjustment.difference} shows quantiles and means for the various differences and the overall proportion of downward adjusted effect sizes.
 When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
-The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
+The means in Table \ref{adjustment.difference} suggest that the average reduction is small.
 To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 70 cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or 70 increased by -0.13, fixed effects reference).
-Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or 70 meta-analyses (or increased by 0.24).
+Also, std.
+mean difference is reduced by 0.39 compared to fixed effects estimates in 5\% or 70 meta-analyses (or increased by 0.24).
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Jul 23 11:07:42 2019
+% Sat Jul 27 15:44:32 2019
 \begin{table}[ht]
@@
   \hline
-z: Fixed - Copas & -0.06 & -0.01 & 0.00 & 0.02 & 0.13 & 0.01 & 4.71 & 47.79 & 43.07 & 63.93 \\ 
-  z: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.15 & 0.02 & 62.93 & 82.21 & 19.29 & 63.93 \\ 
-  z: Fixed - Regression & -0.12 & -0.03 & 0.01 & 0.05 & 0.14 & 0.01 & 0.00 & 48.00 & 48.00 & 1.14 \\ 
-  z: Random - Regression & -0.15 & -0.02 & 0.02 & 0.07 & 0.17 & 0.02 & 0.00 & 54.43 & 54.43 & 1.14 \\ 
-  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.10 & -0.01 & 19.36 & 53.93 & 34.57 & 56.71 \\ 
-  g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.16 & 0.00 & 57.79 & 80.79 & 23.00 & 56.71 \\ 
-  g: Fixed - Regression & -0.21 & -0.03 & 0.04 & 0.14 & 0.39 & 0.06 & 0.00 & 57.36 & 57.36 & 1.14 \\ 
-  g: Random - Regression & -0.21 & -0.03 & 0.05 & 0.16 & 0.44 & 0.07 & 0.00 & 59.57 & 59.57 & 1.14 \\ 
-  Log h.r.: Fixed - Copas & -0.05 & -0.00 & 0.00 & 0.01 & 0.07 & 0.16 & 30.71 & 41.43 & 72.14 & 57.86 \\ 
-  Log h.r.: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.10 & 0.21 & 62.86 & 25.71 & 88.57 & 57.86 \\ 
-  Log h.r.: Fixed - Regression & -0.52 & -0.09 & -0.01 & 0.05 & 0.69 & 0.34 & 0.00 & 44.29 & 44.29 & 0.00 \\ 
-  Log h.r.: Random - Regression & -0.52 & -0.09 & -0.01 & 0.07 & 0.76 & 0.39 & 0.00 & 45.00 & 45.00 & 0.00 \\ 
+z: Fixed - Copas & -0.04 & -0.01 & 0.00 & 0.01 & 0.04 & -0.02 & 8.03 & 49.40 & 41.36 & 64.61 \\ 
+  z: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.04 & -0.01 & 66.24 & 84.01 & 17.77 & 64.61 \\ 
+  z: Fixed - Regression & -0.11 & -0.03 & 0.01 & 0.05 & 0.13 & 0.01 & 0.00 & 51.31 & 51.31 & 0.00 \\ 
+  z: Random - Regression & -0.13 & -0.02 & 0.02 & 0.06 & 0.16 & 0.02 & 0.00 & 55.79 & 55.79 & 0.00 \\ 
+  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.11 & -0.00 & 19.12 & 55.58 & 36.46 & 56.15 \\ 
+  g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.16 & 0.01 & 59.28 & 83.80 & 24.52 & 56.15 \\ 
+  g: Fixed - Regression & -0.21 & -0.03 & 0.04 & 0.14 & 0.40 & 0.06 & 0.00 & 59.35 & 59.35 & 0.00 \\ 
+  g: Random - Regression & -0.20 & -0.02 & 0.05 & 0.17 & 0.44 & 0.08 & 0.00 & 61.83 & 61.83 & 0.00 \\ 
+  IV: Fixed - Copas & -0.05 & -0.00 & 0.00 & 0.01 & 0.07 & 0.16 & 30.71 & 41.43 & 72.14 & 57.86 \\ 
+  IV: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.10 & 0.21 & 62.86 & 25.71 & 88.57 & 57.86 \\ 
+  IV: Fixed - Regression & -0.52 & -0.09 & -0.01 & 0.05 & 0.69 & 0.34 & 0.00 & 44.29 & 44.29 & 0.00 \\ 
+  IV: Random - Regression & -0.52 & -0.09 & -0.01 & 0.07 & 0.76 & 0.39 & 0.00 & 45.00 & 45.00 & 0.00 \\ 
    \hline
@@
 The Wald test statistics $p$-value for fixed and random effects meta-analyses and Copas and regression adjusted treatment effects have been calculated.
-They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, Hedges $g$ and other effect measures (\texttt{outcome.flag} = \texttt{IV}).
+They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, std.
+mean difference and other effect measures (\texttt{outcome.flag} = \texttt{IV}).
 \\
@@
 % Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
-%Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted Hedges $g$ and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.
+%Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted std.
+mean difference and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-19-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-24-1}
 
@@
 The Copas selection model also gives an estimate of the number of missing studies.
-It finds that 0 are missing, which corresponds to 11.3\% from all \ensuremath{2.3183\times 10^{4}} analysed studies.
+It finds that 0 are missing, which corresponds to 11.3\% from all \ensuremath{2.3274\times 10^{4}} analysed studies.
 Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
-Note that we have excluded 0 out of 1400, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
+Note that we have excluded 0 out of 1407, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-20-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-25-1}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Jul 23 11:07:44 2019
+% Sat Jul 27 15:44:33 2019
 \begin{table}[ht]
@@
   \hline
-Missing fraction & 239 & 0 & 0 & 0.1 & 0.4 & 1.1 & 0.3 \\ 
-  Missing study number & 239 & 0 & 0 & 1.3 & 5.6 & 21.0 & 4.6 \\ 
+Missing fraction & 240 & 0 & 0 & 0.1 & 0.4 & 1.1 & 0.3 \\ 
+  Missing study number & 240 & 0 & 0 & 1.3 & 5.4 & 21.0 & 4.6 \\ 
    \hline
@@
   \hline
-9957 & CD000370 & 8 & 2 & 0.80 & 0.81 & 0.80 & 0.97 & 1.59 & 1.59 & 1.40 & 0.28 \\ 
-  49559 & CD002307 & 2 & 1 & -0.13 & -0.11 & -0.13 & 0.04 & -0.47 & -0.42 & -0.41 & -3.00 \\ 
-  186028 & CD007964 & 1 & 2 & -0.18 & -0.10 & 1.01 & -0.19 & -0.07 & -0.06 & -0.06 & -0.16 \\ 
-  217035 & CD009676 & 8 & 1 & -0.09 & -0.08 & -0.09 & -0.07 & 0.69 & 0.71 & 20.28 & 0.12 \\ 
-  222767 & CD010060 & 1 & 0 & 0.36 & 0.49 & 0.36 & 0.54 & 0.50 & 0.52 & 0.20 & -0.49 \\ 
+9957 & CD000370 & 8 & 2 & 0.66 & 0.66 & 0.66 & 0.82 & 1.59 & 1.59 & 1.40 & 0.28 \\ 
+  22324 & CD001183 & 7 & 0 & -0.48 & -0.48 & -0.48 & -0.21 & -1.10 & -1.12 & -0.50 & -0.11 \\ 
+  49559 & CD002307 & 2 & 1 & -0.10 & -0.08 & -0.10 & 0.03 & -0.47 & -0.42 & -0.41 & -3.00 \\ 
+  169178 & CD007076 & 2 & 2 & 0.37 & 0.34 & 21.92 & 0.14 & 0.74 & 0.74 & 0.70 & 0.23 \\ 
+  197675 & CD008625 & 2 & 2 & -0.60 & -0.60 & -0.60 & -0.39 & -1.72 & -2.02 & -1.01 & -0.69 \\ 
+  217035 & CD009676 & 8 & 1 & 0.36 & 0.35 & 0.36 & 0.08 & 0.69 & 0.71 & 20.28 & 0.12 \\ 
+  222767 & CD010060 & 1 & 0 & 0.31 & 0.32 & 0.31 & 0.23 & 0.50 & 0.52 & 0.20 & -0.49 \\ 
    \hline
@@
 We will compare estimates based on all three outcome measures, i.e.
-original measure, $z$-score and Hedges $g$ in Figure \ref{fig:adjustment.mean.diff}.
-Note that the 140 IV outcome data is not included when using $z$-score and Hedges $g$.
+original measure, $z$-score and std.
+mean difference in Figure \ref{fig:adjustment.mean.diff}.
+Note that the 140 \texttt{IV} outcome data is not included when using $z$-score and std.
+mean difference.
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-23-1}
-
-}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/unnamed-chunk-28-1}
 
@@
 Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).
-Two values have been omitted in the middle plot for Hedges $g$ and one for $z$-score (see Table \ref{missing.differences}).}
+Two values have been omitted in the middle plot for std.
+mean difference and one for $z$-score (see Table \ref{missing.differences}).}
 \label{fig:adjustment.mean.diff}
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Jul 23 11:07:45 2019
-\begin{table}[ht]
-\centering
-\begingroup\scriptsize
-\begin{tabular}{lcc}
-  \hline
- & Agreement (overall) & Agreement (significance) \\ 
-  \hline
-Excess significance, Schwarzer & 0.85 & 0.27 \\ 
-  Excess significance, Peter & 0.77 & 0.32 \\ 
-  Excess significance, Rucker & 0.79 & 0.43 \\ 
-  Excess significance, Harbord & 0.81 & 0.46 \\ 
-  Peter, Schwarzer & 0.84 & 0.63 \\ 
-  Schwarzer, Rucker & 0.85 & 0.72 \\ 
-  Schwarzer, Harbord & 0.87 & 0.78 \\ 
-  Rucker, Peter & 0.88 & 0.67 \\ 
-  Harbord, Peter & 0.87 & 0.63 \\ 
-  Excess significance, Egger & 0.74 & 0.50 \\ 
-  Excess significance, Thompson & 0.78 & 0.50 \\ 
-  Excess significance, Begg & 0.76 & 0.30 \\ 
-  Thompson, Egger & 0.93 & 0.92 \\ 
-  Thompson, Begg & 0.86 & 0.69 \\ 
-  Egger, Begg & 0.83 & 0.69 \\ 
-  Excess significance, Egger (IV) & 0.84 & 0.09 \\ 
-  Excess significance, Thompson (IV) & 0.84 & 0.10 \\ 
-  Excess significance, Begg (IV) & 0.85 & 0.10 \\ 
-  Thompson, Egger (IV) & 0.98 & 0.95 \\ 
-  Thompson, Begg (IV) & 0.86 & 0.55 \\ 
-  Egger, Begg (IV) & 0.87 & 0.60 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Overall proportion of agreement if significant or unsignificant, and for significance only.
-Horizontal lines separate binary, continuous and IV outcomes (order as in table).
-The reference significance test is the one with more significant results.}
-\label{test.agreement}
-\end{table}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-07-27 report/chapter01.Rnw
results correction

@@
 The issue has been discussed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}).
+Consensus is that publication bias exists in clinical science.
 \\
 In medical research, clinical trials study the efficacy of therapies and drugs.
-The gold standard in such intervention studies are randomized, (placebo) controlled, trials (RCTs).
-Results from such clinical studies influence the treatment of patients in daily clinical practice.
-The results from multiple intervention studies are However, publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm.
+The gold standard in such intervention studies are randomized controlled trials (RCTs).
+Results from RCTs influence the treatment of patients in daily clinical practice.
+The results from multiple intervention studies can be summarized in a meta-analysis to estimate an overall treatment effect (access all studies).
+However, publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm, distortion and financial expenses.
 \\
+There is extensive literature on publication bias in meta-analyses, e.g. (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02},
+\citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}).
+The authors agree on that the exclusion of unpublished results in meta-analyses is responsible for overestimation of treatment effects.
+Although there are policies that make it mandatory to make all study results publicly accessible \citep{fda}, it is not clear if the situation has improved yet.\\
 There are multiple ways to assess the amount of publication bias.
-For instance, one can follow studies and control if they are getting published depending on their findings \citep{publication.fate}.
+For instance, it is possible to follow studies and assess if they are getting published depending on their findings \citep{publication.fate}.
 One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in social sciences: \citet{social.sciences.publication.bias}).
@@
 
-ex.se <- meta.f$meta.id[395]
-ex.nose <- meta.f$meta.id[36]
+ex.se <- meta.f$meta.id[which(meta.f$id == "CD003246" & meta.f$subgroup.nr == 0
+                              & meta.f$outcome.nr == 3 & meta.f$comparison.nr == 9)]
+ex.nose <- meta.f$meta.id[which(meta.f$id == "CD000213" & meta.f$subgroup.nr == 1
+                              & meta.f$outcome.nr == 15 & meta.f$comparison.nr == 1)]
 par(mfrow = c(1,2))

### 2019-07-27 report/chapter04.Rnw
results correction

--- 2019-07-23 report/chapter04.Rnw
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+<<echo=FALSE, warning=FALSE>>=
+p.samplesize.z  <- data.ext2 %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% ungroup() %>%
+  mutate(std.z = abs(z), sample.size = total1 + total2) %>%
+  group_by(sample.size) %>%
+  summarize(median.effect = median(std.z, na.rm = T)) %>%
+  ggplot(aes(x = sample.size, y = median.effect)) + geom_point(size = 0.8) +
+  theme_bw() + xlab("sample size") + ylab("median absolute z-score") +
+  xlim(c(15, 300)) + ylim(c(0, 0.25)) +
+  scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
+
+labels <- c(RR = "Risk Ratio", OR = "Odds Ratio", MD = "Mean Difference", SMD = "Std. Mean Difference")
+
+p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>%
+  filter(id != "CD001293") %>%  #filter out this crazy review..
+  filter(outcome.measure.merged == "RR" |
+           outcome.measure.merged == "OR" |
+           outcome.measure.merged == "MD" |
+           outcome.measure.merged == "SMD") %>%
+  group_by(outcome.measure.merged) %>%
+  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
+  group_by(sample.size, outcome.measure.merged) %>%
+  summarize(median.effect = median(scaled.effect, na.rm = T)) %>%
+  ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.merged)) + geom_point(size = .5) + facet_wrap(~outcome.measure.merged, scales = "free", labeller = labeller(outcome.measure.merged = labels)) +
+  theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size") +
+  xlim(c(15, 300)) +
+  scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
+@
+
+Using Fisher's $z$ transformation, we can transform all effect sizes of the dataset on the same scale such that they are comparable to each other.
+Thus, as a first step, an exploratory plot of the median effect size and it's dependence on the study sample size can be shown.
+\\
+The absolute value of the median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
+It is clearly visible that the absolute value decreases with increasing sample size, i.e.
+that the effect size is becoming smaller.
+The trend flattens off after $\sim$ sample size = 400 (not shown).
+\\
+The pattern is similar in Figure \ref{effect.samplesize.separated}, where the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std.
+Mean Difference'' are used (the most common measurs in the dataset).
+Here, the effect sizes are scaled (mean subtraction and divison through standard error) with respect to all other effects of the same measure.
+
+\begin{figure}
+<<echo=FALSE, warning=FALSE>>=
+plot(p.samplesize.z)
+@
+\caption{Median of the absolute $z$-score plotted against the total sample size.}
+\label{z.samplesize}
+\end{figure}
+
+\begin{figure}
+<<echo=FALSE>>=
+plot(p.samplesize.effect.sep)
+@
+\caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
+\label{effect.samplesize.separated}
+\end{figure}
 
@@
   label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
-                  sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test), sum(meta.bin$tes.d.test, na.rm = T)), "< 0.1,",
+                  sum(meta.bin$rucker.test), sum(meta.bin$rucker.test.linreg), 
+                  sum(meta.bin$schwarzer.test), sum(meta.bin$tes.d.test, na.rm = T)), "< 0.1,",
                 round(c(mean(meta.bin$harbord.test), mean(meta.bin$peter.test), 
-                        mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test), mean(meta.bin$tes.d.test, na.rm = T)),2)*100, "%"),
-  test.type   = c("pval1.harbord", "pval1.peter", "pval1.rucker", "pval1.schwarzer", "pval1.d.tes"),
-  i2f = factor(rep(0, times = 5)))
-
-labels <- c(pval1.harbord = "Harbord", pval1.peter = "Peter", pval1.rucker = "Rucker", pval1.schwarzer = "Schwarzer", pval1.d.tes = "Excess Significance")
+                        mean(meta.bin$rucker.test), mean(meta.bin$rucker.test.linreg), 
+                        mean(meta.bin$schwarzer.test), mean(meta.bin$tes.d.test, na.rm = T)),2)*100, "%"),
+  test.type   = c("pval1.harbord", "pval1.peter", "pval1.rucker", "pval1.rucker.linreg", "pval1.schwarzer", "pval1.d.tes"),
+  i2f = factor(rep(0, times = 6)))
+
+labels <- c(pval1.harbord = "Harbord", pval1.peter = "Peter", pval1.rucker = "Rucker (thompson)", pval1.rucker.linreg = "Rucker (egger)", pval1.schwarzer = "Schwarzer", pval1.d.tes = "Excess Significance")
 
 p.dist.bin <- meta.bin %>% ungroup() %>% 
-  select(i2f, pval1.harbord, pval1.peter, pval1.rucker, pval1.d.tes, pval1.schwarzer) %>% 
+  select(i2f, pval1.harbord, pval1.peter, pval1.rucker, pval1.rucker.linreg, pval1.d.tes, pval1.schwarzer) %>% 
   gather(key = "test.type", value = "p.value", pval1.harbord:pval1.schwarzer) %>% 
@@
   facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 200, label = label), color = "black") + 
+  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 125, label = label), color = "black") + 
   theme(strip.text.x = element_text(size=7)) + ggtitle("Binary Outcomes") + 
@@
   guides(fill=guide_legend(title=expression(paste(I^2, " Heterogeneity")))) + 
-  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 40, label = label),  color = "black")  + 
+  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 25, label = label),  color = "black")  + 
   scale_fill_discrete(labels = c("> 0", "= 0")) +
@@
                      values = c("red", "blue")) +
-  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value Thompson)" )))
+  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value Thompson)" ))) + geom_smooth(method = "lm", col = "green")
 #--------------------------------------------------------------------------------------------------------------------#
@@
          difference = logit(pval1.egger) - logit(pval1.d.tes)) %>% 
+  filter(difference > -Inf & difference < 10) %>% 
   ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
@@
                      values = c("red", "blue")) +
-  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value excess significance)" )))
+  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value excess significance)" ))) + geom_smooth(method = "lm", col = "green")
 #--------------------------------------------------------------------------------------------------------------------#
@@
                      values = c("red", "blue")) +
-  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value Rucker)" )))
+  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value Rucker)" ))) + geom_smooth(method = "lm", col = "green")
 #--------------------------------------------------------------------------------------------------------------------#
@@
                      values = c("red", "blue")) +
-  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value excess significance)" )))
+  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value excess significance)" ))) + geom_smooth(method = "lm", col = "green")
 #--------------------------------------------------------------------------------------------------------------------#
@@
 #--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-#--------------------------------------------------------------------------------------------------------------------#
-
-@
-
-The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with one-sided small study effects tests and excess significance tests.
+#Calculate harmonic mean of p-values of pb tests: 
+meta.f <- meta.f %>% mutate(hmean = case_when(
+  outcome.flag == "DICH" ~ 5/sum(pval1.rucker^-1 + pval1.harbord^-1 + pval1.schwarzer^-1 + pval1.peter^-1 + pval1.d.tes^-1),
+  outcome.flag != "DICH" ~ 4/sum(pval1.egger^-1 + pval1.thompson^-1 + pval1.begg^-1 + pval1.d.tes^-1)))
+
+harmonic.means <- c(length(which(meta.f$hmean < 0.1))/dim(meta.f)[1], 
+length(which(meta.f$hmean[which(meta.f$outcome.flag == "DICH")] < 0.1))/dim(meta.f[which(meta.f$outcome.flag == "DICH"),])[1],
+length(which(meta.f$hmean[which(meta.f$outcome.flag == "CONT")] < 0.1))/dim(meta.f[which(meta.f$outcome.flag == "CONT"),])[1],
+length(which(meta.f$hmean[which(meta.f$outcome.flag == "IV")] < 0.1))/dim(meta.f[which(meta.f$outcome.flag == "IV"),])[1])
+harmonic.means <- round(harmonic.means*100, 1)
+
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+#--------------------------------------------------------------------------------------------------------------------#
+
+@
+
+The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with one-sided small publication bias tests and excess significance tests.
 The direction in which bias is expected is the one on which more significant results are ($p$-value < 0.05, two-sided).
-The tests are applied on the original effect size measures, i.e.
-risk ratios, Hedges $g$ or other effect measures (\texttt{outcome.flag} = \texttt{IV}).
-Different tests are applied depending on the outcome type being binary, continuous or IV.\\
-Thus, multiple tests are applied on the same data.
-The results can then be displayed separately to compare the results from the different tests.
-A histogram of $p$-values will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.
-\\
+The tests are applied on the original effect size measures, since the journal editors and the researchers also base their decisions on them.
+Different tests are applied depending on the outcome being binary or continuous.\\
+Multiple tests are applied on the same data to compare their results.
+A histogram of $p$-values for each test and all meta-analyses will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.
+Skewedness indicates evidence for publication bias.\\
+The abbreviations in Figure \ref{fig:test}  are shortly explained with references to chapter \ref{ch:methods}: \\
 ``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}.
-For continuous and IV outcomes, the names refer to:
+For continuous and \texttt{IV} outcomes, the names refer to:
 
 \begin{itemize}
-\item Egger's test, the weighted linear regression test as described in section \ref{sec:Egger}
-\item Thompson and Sharp's test, the weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
-\item Begg and Mazumdar's test, the rank test described in section \ref{sec:Begg}
+\item Egger's test, weighted linear regression test described in section \ref{sec:Egger}
+\item Thompson and Sharp's test, weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
+\item Begg and Mazumdar's test, rank test described in section \ref{sec:Begg}
 \end{itemize}
@@
 %Agreement table -> Chunck 1
-The histograms in Figure \ref{fig:test} show that most distributions are clearly skewed to the right, indicating evidence for small study effects.
-Exceptions from this are the excess significance and Schwarzer's test, and the tests for IV outcomes.
-There, there is no evidence for publication bias, and the histograms are even skewed to the left (Schwarzer).
-But note that the sample size of IV outcomes is small ($n$ = \Sexpr{dim(meta.iv)[1]}).
+The histograms in Figure \ref{fig:test} show that the tests are not alway in agreement if publication bias is present in the data.
+The $p$-values of excess significance and Schwarzer's test and the $p$-values for \texttt{IV} outcomes are rather uniformly distributed, or even skewed to the right.
+Notably, excess significance test, Schwarzer's test and rank tests have been shown to lack power.
+The tests that are more suitable (regression based tests in general) all have proportions of significant $p$-values ($p$ > 0.1) clearly above 10 \% which would be the expected false positive rate.
+The conclusion is that there is publication bias, however the extent can be debated.
+The meta-analyses with \texttt{outcome.flag} = \texttt{IV} seem to differ from the other meta-analyses.
 \\
-There is discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger.
-Also, we see that the $I^2$ statistic of the proportion of overall between-study heterogeneity is distributed differently for the tests, with results with $I^2 = 0$ being evenly distributed in binary outcomes along the range of $p$-values, while they are more similar to the meta-analyses with larger heterogeneity for continuous outcome.\\
-In the literature, the excess significance test is advised to be used in the case of no between study heterogeneity.
-Since there are no small $p$-values for such meta-analyses, one must conclude that there is no excess significance in the dataset.
-The obvious correspondence with the heterogeneity statistic however rather suggests that the test is another way to assess between study heterogeneity.
-Thompson test and R\"ucker's test are designed such that they take into account the between study heterogeneity when assessing small study effects.
-When no heterogeneity is given, Thompson's test results and Egger's test result should be equal, however, the $I^2$ statistic is computed by a more suitable estimator \citep{paulemandel} of $\tau^2$ as the estimator that Thompson and Sharp's test uses (method of moment estimator of \citet{tau.estimator}, which is more conservative by usually finding larger $\tau^2$).
-In the part of the histogram with $I^2 > 0$, the two tests are more reliable than the remaining tests, while the opposite is expected from simulations \citep{limitmeta} when $I^2 = 0$.\\
+In Figure \ref{fig:test}, the meta-analyses with an estimated $I^2$ of zero are depicted, because some methods are known to only be suitable when no heterogeneity is present (excess significance test and also Egger's test).
+Others are specially constructed to adjust for between study heterogeneity (Thompson and Sharp's test and R\"ucker's test).
+In continuous outcomes, when Thompson and Sharp's test is applied, the evidence for publication bias decreases, as can be seen in the smaller proportion of blue on the left corner in Figure \ref{fig:test}.
+However, this is also due to application to meta-analyses with $I^2$ equal zero, in which case the method is known to lack power.
+Similarly, the evidence decreases somewhat when R\"ucker's test is extended by Thompson and Sharp's method to account for heterogeneity.
+The moderate decrease indicates however that the previous restriction to meta-analyses with $I^2 < 0.5$ is sufficient to remove meta-analyses with large heterogeneity and that the test results are not heavily influenced by unaccounted between study heterogeneity.
+\\
+The $p$-values of tests can be summarized by computing their harmonic mean.
+In the case of binary tests, the $p$-values of R\"ucker's, Peters, Harbord's, Schwarzer's and excess significance tests are used, in the case of continuous and \texttt{outcome.flag} = \texttt{IV} outcomes, Egger's, Thompson and Sharp's, Begg and Mazumdar's and excess significance tests are used.
+This lead's to an overall of \Sexpr{harmonic.means[1]}\% significant results ($p_\textrm{harmonic}$ < 0.1, \Sexpr{harmonic.means[2]}\% \texttt{outcome.flag} = \texttt{DICH}, \Sexpr{harmonic.means[3]}\% \texttt{outcome.flag} = \texttt{CONT}, \Sexpr{harmonic.means[4]}\% \texttt{outcome.flag} = \texttt{IV}).
 
@@
 The previous results suggest that the results will also differ substantially after applying the common dichotomization of $p$-values.
-We expect that some proportion of the meta-analysis will only be significant for a certain test, and this is indeed observed in Table \ref{number.sig.tests}.
+Some proportion of the meta-analyses will only be significant using a single test, while being non-significant otherwise.
+This can be seen in Table \ref{number.sig.tests}.
 It displays the percentage of meta-analyses with a certain number of significant test results.
+For both outcome types, there is only marginal agreement, very few cases are significant in any test.
+Around 67\% of the dataset is not significant, no matter which test is used.
+When only using small study effect tests, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of \texttt{IV} and continuous outcome tests had at least one significant result.
+After applying the Bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\% for binary and \Sexpr{mean.min.else.b}\% for continuous and \texttt{IV} outcomes.
+To compare significant findings for small study effect tests and excess significance tests, Harbord's or Egger's test results are compared with excess significane tests.
+\Sexpr{mean.min.bin2}\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, \Sexpr{mean.min.else2}\% for continuous and \texttt{IV} outcomes.
+The numbers change to \Sexpr{mean.min.bin2.b}\% for binary outcomes and \Sexpr{mean.min.else2.b}\% for continuous and \texttt{IV} outcomes after applying the Bonferroni correction.
+\Sexpr{both.bin}\% have significant Harbord's test result and significant excess significance test result  (\Sexpr{both.bin.b}\% with Bonferroni).
+Of the continuous outcomes, we have \Sexpr{both.else}\% with Egger's test and \Sexpr{both.else.b}\% with Bonferroni correction.
+\\
 
@@
 
-Here, it is difficult to say if continuous and IV or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and IV outcome type tests have in general more positive findings.
-Very few meta-analyses are significant, irrespective of the test used, but around 67\% of the dataset is not significant, no matter which test is used.
-\\
-When only looking at small study effect tests, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of IV and continuous outcome tests had at least one significant result.
-After applying the Bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\% for binary and \Sexpr{mean.min.else.b}\% for continuous and IV outcomes.
-\\
-% To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test.
-\Sexpr{mean.min.bin2}\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, \Sexpr{mean.min.else2}\% for continuous and IV outcomes.
-The numbers change to \Sexpr{mean.min.bin2.b}\% for binary outcomes and \Sexpr{mean.min.else2.b}\% for continuous and IV outcomes after applying the Bonferroni correction.
-\\
-% \Sexpr{both.bin}\% have significant Harbord's test result and significant excess significance test result  (\Sexpr{both.bin.b}\% with Bonferroni).
-Of the continuous outcomes, we have \Sexpr{both.else}\% with Egger's test and \Sexpr{both.else.b}\% with Bonferroni correction.
+The precise proportions of agreement are provided in table \ref{test.agreement}.
+We see that only in few cases when excess significance test indicates statistical significance, small study effect tests do so.
+Correspondence between excess significance tests and small study effects thus has to be considered rather random.
+Linear regression based tests agree more often with other linear regression based tests, and agreement between small study effect tests is in general well above 60 \% (at best, 95 \% test agreement in significance for \texttt{IV} \texttt{outcome.flag}).
+
+<<echo = FALSE, results = 'asis'>>=
+print(xtable(test.agreement, align = "lcc", caption = "Overall proportion of agreement if significant or unsignificant, and for significance only.
+Horizontal lines separate binary, continuous and IV outcomes (order as in table).
+The reference significance test is the one with more significant results.",
+             label = "test.agreement"),, size = "scriptsize")
+@
 
@@
   geom_text(data = sig.d, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
-  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
-  ggtitle(expression(paste("Hedges ", italic(g), " ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+  xlab(expression(paste(italic(p),"-value of test statistic of std. mean differences"))) +
+  ggtitle(expression(paste("std. mean difference ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
 #--------------------------------------------------------------------------------------------------------------------#
@@
   geom_text(data = sig.d, aes(x = 0.5, y = 100, label = label), position = "dodge") + 
-  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
+  xlab(expression(paste(italic(p),"-value of test statistic of Hedges"))) +
   ggtitle(expression(paste("Log IV outcome measures ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
@@
   scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + 
-  xlab(expression(paste("Fixed effects - adjusted Hedges ", g))) + geom_vline(xintercept = 0, linetype = "dashed" )
+  xlab(expression(paste("Fixed effects - adjusted Hedges"))) + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
   scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + 
-  xlab(expression(paste("Fixed effects - adjusted Hedges ", g))) + geom_vline(xintercept = 0, linetype = "dashed" )
+  xlab(expression(paste("Fixed effects - adjusted std. mean difference"))) + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
   scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) +  ylab("") +
-xlab(expression(paste("Random effects - adjusted Hedges ", g))) + geom_vline(xintercept = 0, linetype = "dashed" )
+xlab(expression(paste("Random effects - adjusted Hedges"))) + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
   scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + ylab("") +
-xlab(expression(paste("Random effects - adjusted Hedges ", italic(g)))) + geom_vline(xintercept = 0, linetype = "dashed" )
+xlab(expression(paste("Random effects - adjusted std. mean difference"))) + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
                                      paste("g:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
-                                     paste("Log h.r.:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")))
+                                     paste("IV:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")))
 
@@
                      values = c("red", "blue")) + guides(fill=guide_legend(title=NULL)) +
-  ggtitle(expression(paste("Copas adjusted Hedges ", italic(g)," estimate - Regression adjusted Hedges ", italic(g), " estimate (original)" )))
+  ggtitle(expression(paste("Copas adjusted std. mean difference estimate - Regression adjusted std. mean difference estimate (original)" )))
 
@@
 
-Since there's evidence for publication bias when applying small study effect and excess significance tests, we apply small study effect adjustment methods to take into account that small studies are likely overestimating the treatment effect.
+There are methods that can take into account the presence of publication bias in meta-analyses when estimating the overall treatment effect.
+The methods work in a semi-automatic manner; they will not only adjust for publication bias if smaller studies show larger effects, but also in the opposite case.
+The latter results in the adjusted overall treatment effect being \textit{larger} than the unadjusted, overall treatment effect.
 \\
-However, we will see that consequences of adjustment can be; 
-\begin{itemize}
-\item first, the absolute size of the treatment effect can be smaller than the classical meta-analysis treatment effect, which is expected if publication bias
-is the cause for the small study effect.
-\item secondly, the effect can be larger than before in meta-analysis.
-In this case, the small study effect must be not due to publication bias for large effects (``true'' publication bias), but due to bias for small effects (``null effect publication bias'' or even ``reversed effect publication bias'', sometimes refer erred to as ``Proteus phenomenon'' \citep{proteus}).
-\end{itemize}
-
-This is because, in contrast to the small study effect tests, the applied adjustment method does not pre-specify the direction in which bias is expected. \\
-To compare the effects of adjustment between meta-analyses, the outcome measures are transformed to Hedges $g$ (standardized mean differences) and Fisher's $z$-score (see section \ref{sec:transformation.effectsizes} for details).
-The effect of adjustments can be compared to either random or fixed effects meta-analysis estimates.
+To compare the effects of adjustment between meta-analyses of different outcomes, the outcome measures are transformed to standardized mean differences and Fisher's $z$-scores (see section \ref{sec:transformation.effectsizes} for details).
+When comparing to unadjusted effects, fixed or random effects meta-analysis estimates are used as references\\
+Figure \ref{fig:adjustment.reg} displays the difference $\delta$ between the estimated meta-analysis treatment effect and the regression adjusted treatment effect \ref{sec:regression.adjustment}, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
+The absolute value $|\hat{\theta}_M|$ is taken and $\hat{\theta}_\textrm{Adj.}$ is negative if the signs change in the original $\theta$.
+Thus, a positive difference indicates a reduction of the original effect size, and the magnitude of the difference indicates the extent of the adjustment.
 \\
-Figure \ref{fig:adjustment.reg} displays the difference $\delta$ between the observed meta-analysis pooled treatment effect and the regression adjusted treatment effect, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
-The absolute value $|\hat{\theta}_M|$ is taken and the sign of $\hat{\theta}_\textrm{Adj.}$ is adjusted accordingly such that all effects are mirrored to one side.
-$\delta > 0$ is equivalent to $\hat{\theta}_\textrm{Adj} < \hat{\theta}_M$, a reduction of the original effect size.
-Additionally, the test statistic of heterogeneity adjusted small study effect tests (R\"ucker's and Thompson's test) is displayed with green color.
-Test statitics smaller $< 1$ are equivalent to no evidence for small study effect, test statistics between one and two to weak evidence, and above two they indicate evidence for small study effects.
-Some very large and very small differences have been omitted in the $z$-score and Hedges $g$ histograms; they are shown in Table \ref{missing.differences}.
+Additionally, the test statistic of heterogeneity adjusted publication bias tests (R\"ucker's and Thompson's test) are displayed with green color.
+Test statitics smaller $< 1$ (light green colored) are equivalent to no evidence for publication test, test statistics between one and two to weak evidence, and above two they indicate evidence for publication bias (dark green).
+An adjusted effect with evidence for publication bias can be regarded as a more realistic estimate of treatment efficacy.
+Some very large and very small differences have been omitted in the $z$-score and std.
+mean difference histograms; they are shown in Table \ref{missing.differences}.
+\\
 
@@
 
-We see that more treatment effect sizes are negatively adjusted and diminished.
-Furthermore, we see that large adjustment is not necessarily connected with evidence for small study effects, but there is coincidence.
-Adjustment was larger when random effects meta-analysis effect is used as reference, because there larger weights are given to small studies.\\
-The cases with no evidence (clear green color) and large adjustment indicate that between-study heterogeneity was not resolved by adjustment for small study effects.
-The regression adjustment method as described in section \ref{sec:regression.adjustment} adjusts for small study effects even if there is no evidence for small study effects.
-Thus, a large change in effect sizes does not necessarily have to be accompained by evidence for small study effects, because the unceratinity of the small study effect is not taken into account by the adjustment method.
-The uncertainity of the adjusted estimates is consequently larger in the clear green fraction of the histogramm than in the deeper green fraction.\\
+Most often, adjustment leads to a reduction of overall treatment effect estimates, because the bins on the positive side of the histograms are larger.
+Adjustment is stronger when random effects meta-analysis is used as reference, because it gives larger weights to small studies.\\
+Contrary to naive expectation, we see cases with large adjustment, but no evidence for small study effects.
+This is because the linear regression parameter estimates are large, but estimated with high uncertainity, such that there will be few evidence for small study effects (publication bias), but nonetheless, the adjustment will be large.
+The authors that developped the methods also recommend to use the methods in cases where there is clear evidence for publication bias.
+The color legend in Figure \ref{fig:adjustment.reg} thus gives a sense of confidence that there is in the credibility of the adjustment.
+\\
+Additionally, some meta-analyses with positively adjusted, larger overall treatment effects after adjustment (left side of the histogram) have at the same time evidence for publication bias.
+This is no wrong result, although the $p$-value of the test is one-sided, \ie only allowing for publication bias for large effects (small studies with large effects).
+But the effects and their variances have been transformed, and it is possible that the shape of the funnel plot changes upon transformation; Figure \ref{fig:funnel.plot.change} shows this for illustratory purposes.
+From the left to the right, the funnel plot is shown for mean differences (the original measure), standardized mean differences and Fisher's $z$ scores.
+This is quite the most extreme case, with three different effects of adjustment, depending on outcome measure; there is no change with mean differences, reduction of effect sizes with std.
+mean differences and increase with Fisher's $z$ transformed correlation.
+Note that while the rank of the effect sizes is usually preserved after transformation, the relative size and especially the variance may vary.
+One effect of the Fisher's $z$-transformation is that the effect sizes are bounded on $[-1,1]$, and thus, very large effect sizes will influence the fit of the linear regression less than for example in std.
+mean differences which are not bounded.
+In contrast, the variance of the correlation is directly tied to the sample size, which makes it a suitable proxy for study size (variance of the mean difference is in contrast strongly influenced by the standard deviations).
+Thus, cases where the direction of adjustment changes upon transformation are not very rare.
+
+\begin{figure}
+<<echo = FALSE, warning=FALSE>>=
+par(mfrow = c(1,3))
+example <- data.ext2 %>% filter(id == "CD003236", subgroup.nr == 2, outcome.nr == 1, comparison.nr == 1)
+funnel(limitmeta(metagen(TE = effect, se = se, studlab = study.name, sm = "MD", data = example)), col.adjust = "blue", col.line = "blue")
+funnel(limitmeta(metagen(TE = smd.pool, se = se.smd.pool, studlab = study.name, sm = "SMD", data = example)), col.adjust = "blue", col.line = "blue")
+funnel(limitmeta(metacor(cor = z, n = total1 + total2, studlab = study.name, sm = "ZCOR", data = example)), col.adjust = "blue", col.line = "blue")
+par(mfrow = c(1,1))
+@
+\caption{Funnel plots for a meta-analysis based on three different effect size measures: Mean differences, std.
+mean differences and Fisher's z transformed correlations and corresponding standard errors.
+Vertical dashed lines indicate meta-analysis estimates, the rhombus with the curved blue line the adjusted treatment effect.}
+\label{fig:funnel.plot.change}
+\end{figure}
+
 Figure \ref{fig:adjustment.copas} shows the same for effect sizes adjusted by Copas; Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
-Therefore, the effect of adjustment by Copas can be seen when comparing adjusted with random effects estimates.
+Therefore, the effect of adjustment by Copas can be seen when comparing adjusted with random effects meta analysis estimates.
 Again, we clearly see that more effect sizes are adjusted downwards.
-Additionally, there is more coincidence with the small study effect test statistics and adjustment, which is as expected.
+Additionally, there is more coincidence between the publication bias test statistics and adjustment, which is as expected.
 \\
@@
 
-Table \ref{adjustment.difference} shows the quantiles and means for the various differences and additional information.
+Table \ref{adjustment.difference} shows quantiles and means for the various differences and the overall proportion of downward adjusted effect sizes.
 When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
-The means in Table \ref{adjustment.difference} suggest that the average reduction is small (the means of Copas in the first two rows for $z$-score are caused by one very large value, see Table \ref{missing.differences}).
+The means in Table \ref{adjustment.difference} suggest that the average reduction is small.
 To recall some other findings out of Table \ref{adjustment.difference}: 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} increased by -0.13, fixed effects reference).
-Also, Hedges $g$ is reduced by 0.39 compared to fixed effects estimates in 5\% or \Sexpr{floor(length(!is.na(meta.f$est.d.reg))*0.05)} meta-analyses (or increased by 0.24).
+Also, std.
+mean difference is reduced by 0.39 compared to fixed effects estimates in 5\% or \Sexpr{floor(length(!is.na(meta.f$est.d.reg))*0.05)} meta-analyses (or increased by 0.24).
 
@@
 We will compare estimates based on all three outcome measures, i.e.
-original measure, $z$-score and Hedges $g$ in Figure \ref{fig:adjustment.mean.diff}.
-Note that the \Sexpr{dim(meta.iv)[1]} IV outcome data is not included when using $z$-score and Hedges $g$.
+original measure, $z$-score and std.
+mean difference in Figure \ref{fig:adjustment.mean.diff}.
+Note that the \Sexpr{dim(meta.iv)[1]} \texttt{IV} outcome data is not included when using $z$-score and std.
+mean difference.
 
@@
 \\
-
-<<echo = FALSE, results = 'asis'>>=
-print(xtable(test.agreement, align = "lcc", caption = "Overall proportion of agreement if significant or unsignificant, and for significance only.
-Horizontal lines separate binary, continuous and IV outcomes (order as in table).
-The reference significance test is the one with more significant results.",
-             label = "test.agreement"),, size = "scriptsize")
-@

### 2019-07-27 code/Meandifference_issue.R

@@ -32,5 +32,55 @@ funnel(metagen(TE = effect, seTE = se, data = mtd))
 #                method = "FE", data = dt))
 
 
+mtd <- data.ext2 %>% filter(meta.id == meta.bin$meta.id[33])
+funnel(metagen(TE = smd.pool, seTE = se.smd.pool, data = mtd))
+funnel(metacor(cor = z, n = total1 + total2, studlab = study.name, data = dt, sm = "ZCOR"))
+funnel(metagen(TE = lrr, seTE = sqrt(var.lrr), data = mtd))
 
+plot(mtd$smd.pool, x = mtd$se.smd.pool, col = factor(mtd$study.id), pch = 20)
+plot(mtd$z, x = sqrt(mtd$var.z), col = factor(mtd$study.id), pch = 20)
+rank(mtd$z); rank(mtd$smd.pool); rank(mtd$effect)
+rank(1/mtd$n); rank(sqrt(mtd$var.z)); rank(sqrt(mtd$var.smd.ordl))
+
+
+#Variance/study sample size check: 
+#Correspondance of variance of different measures with study sample size:
+#----------------------------------------------------------------------------------------------#
+data.ext2 <- data.ext2 %>% mutate(n = total1 + total2)
+
+#Play through two scenarios; large difference, large error and vice versa:
+mean1 <- c(30, 15); mean2 <- c(10, 10)
+sd1 <- c(10, 10); sd2 <- c(10, 10)
+total1 <- c(20, 100); total2 <- c(20, 100)
+
+escalc(measure = "MD", m1i = mean1, m2i = mean2, sd1i = sd1, sd2i = sd2, n1i = total1, n2i = total2)
+escalc(measure = "SMD", m1i = mean1, m2i = mean2, sd1i = sd1, sd2i = sd2, n1i = total1, n2i = total2)
+
+
+#----------------------------------------------------------------------------------------------#
+# examples <- data.ext2 %>% filter(outcome.measure.merged == "MD")
+# examples <- examples[c(4987, 33200, 660),]
+examples <- data.ext2 %>% filter(meta.id == meta.cont$meta.id[59])
+
+plot(x = examples$se, y = examples$effect)
+abline(lm(effect~ se, data = examples))
+plot(x = examples$se.smd.pool, y = examples$smd.pool)
+abline(lm(smd.pool ~ se.smd.pool, data = examples))
+plot(x = examples$n, y = examples$effect)
+abline(lm(effect ~ n, data = examples))
[…]

### 2019-07-27 code/Meta_meta_regression.R

@@ -27,29 +27,20 @@ load(file.path(PATH_DATA, "PubBias_2019-07-19.RData"))
 ##-------Prepare data--------#
 reg.dat <- data.ext2 %>% filter(meta.id %in% meta.id.vector) #Filter meta-analysis data
 
-reg.dat <- reg.dat %>%  mutate(smd = case_when(outcome.flag == "DICH" ~ smd.ordl,
-                                         outcome.flag == "CONT" ~ smd),
-                         var.smd = case_when(outcome.flag == "DICH" ~ var.smd.ordl,
-                                             outcome.flag == "CONT" ~ var.smd),
-                         smd = case_when(outcome.measure.merged == "SMD" ~ effect, 
-                                         TRUE ~ smd),
-                         var.smd = case_when(outcome.measure.merged == "SMD" ~ se^2,
-                                             TRUE ~ var.smd)) #put smd's all together
-
 #Mirror all effects on one positive side:
 reg.dat <- reg.dat %>% group_by(meta.id) %>% 
-  mutate(bias.side = bias.side.fct2(outcome = outcome.flag, lrr = lrr, var.lrr = var.lrr, 
-                                    smd = smd, var.smd = var.smd, effect = effect, se = se),
-  smd = smd * bias.side, #Mirror effect sizes on one side
-  se.smd = sqrt(var.smd)) 
+  mutate(bias.side = bias.side.fct2(outcome = outcome.flag, outcome.measure.merged = outcome.measure.merged,
+                                    lrr = lrr, var.lrr = var.lrr, smd = cohensd, var.smd = var.cohensd, 
+                                    effect = effect, se = se),
+  smd.pool = smd.pool * bias.side) #Mirror effect sizes on one side
 
 #Get tau^2 based on smd's and introduce new study se:
 reg.dat <- reg.dat %>% group_by(meta.id) %>% 
-  mutate(tau.squared = metagen(TE = smd, seTE = se.smd)$tau^2,
-         new.se.smd = sqrt(se.smd^2 + tau.squared))
[…]

### 2019-07-27 code/analysis.R

@@ -35,7 +35,6 @@ load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
 # meta.info.bin <- data.ext2 %>% filter(outcome.flag == "DICH") %>%
 #   group_by(meta.id) %>%
 #   mutate(n.pre = n()) %>% filter(n.pre >= 10) %>%
-#   # filter(meta.id != 94519 & meta.id != 62301) %>%  #Copas convergence..
 #   filter(!all(events1 == 0) & !all(events2 == 0)) %>% #No events
 #   mutate(se.lrr = sqrt(var.lrr)) %>%
 #   summarize(dupl.remove = unique(dupl.remove),
@@ -48,7 +47,6 @@ load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
 # meta.info.cont <- data.ext2 %>% filter(outcome.flag == "CONT") %>%
 #   group_by(meta.id) %>%
 #   mutate(n.pre = n()) %>% filter(n.pre >= 10) %>%
-#   # filter(meta.id < 42716 | meta.id > 42725) %>% #Single patient data
 #   filter(!all(mean1 == 0) & !all(mean2 == 0)) %>% #No means
 #   filter(!all(sd1 == 0) | !all(sd2 == 0)) %>% #No sd's
 #   summarize(dupl.remove = unique(dupl.remove),
@@ -692,6 +690,7 @@ meta.f <- meta.f %>% rowwise() %>%
          
          schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
          rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
+         rucker.test.linreg = ifelse(pval1.rucker.linreg < sig.level, 1, 0),
          harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
          peter.test = ifelse(pval1.peter < sig.level, 1, 0))
 #--------------------------------------------------------------------------------------------------------------------#

### 2019-07-28 report/MSc_Report.tex
results first complete draft

@@
 
-\subsection{Analysis Procedure}
+\subsection{Analysis Procedure} \label{sec:procedure}
 All compuations were performed in the \texttt{R} computing environment \citep{R.base}.
@@
 
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Scale for 'x' is already present.
-Adding another scale for 'x', which\\\#\# will replace the existing scale.\\\#\# Scale for 'x' is already present.
-Adding another scale for 'x', which\\\#\# will replace the existing scale.}}\end{kframe}
-\end{knitrout}
-
 Using Fisher's $z$ transformation, we can transform all effect sizes of the dataset on the same scale such that they are comparable to each other.
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-11-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-11-1}
+
+}
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-12-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-12-1}
+
+}
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-14-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-14-1}
+
+}
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-15-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-15-1}
+
+}
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-16-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-16-1}
+
+}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sat Jul 27 15:44:17 2019
+% Sun Jul 28 15:12:47 2019
 \begin{table}[ht]
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-20-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-20-1}
+
+}
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-21-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-21-1}
+
+}
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-22-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-22-1}
+
+}
 
@@
 Table \ref{adjustment.difference} shows quantiles and means for the various differences and the overall proportion of downward adjusted effect sizes.
-When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
+When std.
+mean difference is used as an effect measure, there are (substantially) more reduced effect sizes.
 The means in Table \ref{adjustment.difference} suggest that the average reduction is small.
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 70 cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or 70 increased by -0.13, fixed effects reference).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 70 meta-analyses have their $z$-score reduced by more than 0.13 by regression adjustment (and 5\% or 70 increased by -0.11 or more, fixed effects reference).
 Also, std.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sat Jul 27 15:44:32 2019
+% Sun Jul 28 15:13:01 2019
 \begin{table}[ht]
@@
 The row names indicate which outcome measure, meta-analysis method and adjustment method is used.
-Abbreviations are used for z-score (= z) and Hedges g (= g).}
+Abbreviations are used for z-score (= z) and std.
+mean difference (= d).}
 \label{adjustment.difference}
@@
 
-\subsection{Change in Evidence for Treatment Effects} \label{sec:change.evidence}
-Adjustment for small study effects in meta-analysis will not only provide new effect sizes, but also standard errors thereof.
-Thus, also the evidence for efficacy of a treatment can be obtained, which is usually summarized in a suitable test statistic or $p$-value.
-It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.
-There is an important difference between Copas selection model and regression adjustment.
-The regression adjustment method incorporates an additional parameter with corresponding uncertainity in the treatment effect estimate, while the application of the Copas algorithm does not so.
-Instead, the copas selection model derives the uncertainity of the estimate from the inverse of the fisher information matrix of the likelihood.
-Additionally, the Copas selection model algorithm provides only an estimate when it can detect a small study effect with reasonable precision at the first place (see \ref{sec:copas}).\\
-The Wald test statistics $p$-value for fixed and random effects meta-analyses and Copas and regression adjusted treatment effects have been calculated.
-They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, std.
-mean difference and other effect measures (\texttt{outcome.flag} = \texttt{IV}).
-\\
-It can be seen that evidence for a treatment effect decreases after adjusting for publication bias.
-It does so more for Hedge's $g$ compared to $z$-scores, and for regression adjustment compared to Copas selection model.
-%Also, the evidence decreases for random effects meta-analyses compared to fixed effects meta-analyses. 
-In the case of other effect measures (\texttt{outcome.flag} = \texttt{IV}) adjustment, the adjustment has only negligible impact on the $p$-values. \\
-Also, Copas selection method has a very small impact on the evidence compared to random effects meta-analysis, at least using $z$-scores (again, we should rely on comparisons to random effects meta-analysis to evaluate Copas method).
-\\
-% Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
-%Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted std.
-mean difference and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.
+\subsection{Comparison of adjustment methods}
+Regression adjusted estimates are compared to the estimates of Copas selection model if these are not equal to random effects meta-analysis in Figure \ref{fig:adjustment.mean.diff}.
+A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
+Note that most 140 \texttt{IV} outcome data is not included when using $z$-score and std.
+mean difference.
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-24-1}
-
-\end{knitrout}
-\caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
-The method is indicated in the header, bin width is set to 0.05.
-The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
-\label{fig:adjustment.stat}
-\end{figure}
-
-The Copas selection model also gives an estimate of the number of missing studies.
-It finds that 0 are missing, which corresponds to 11.3\% from all \ensuremath{2.3274\times 10^{4}} analysed studies.
-Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
-Note that we have excluded 0 out of 1407, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-25-1}
-
-\end{knitrout}
-\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ 0)}
-\label{fig:copas.missing}
-\end{figure}
-
-We can see that in some occasions, the method finds more than half of all studies are missing.
-In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
-The discrepancy between mean and median may indicate that the estimate of 0\% missing studies depends somewhat on these extreme cases.
-As can be written of from Table \ref{copas.missing}, 5\%, \ie 0 meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for 0, more than 30\% of missing studies.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sat Jul 27 15:44:33 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lrrrrrrr}
-  \hline
- & = 0 & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
-  \hline
-Missing fraction & 240 & 0 & 0 & 0.1 & 0.4 & 1.1 & 0.3 \\ 
-  Missing study number & 240 & 0 & 0 & 1.3 & 5.4 & 21.0 & 4.6 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.} 
-\label{copas.missing}
-\end{table}
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sat Jul 27 15:44:33 2019
-\begin{table}[ht]
-\centering
-\begingroup\tiny
-\begin{tabular}{lcccrrrrrrrr}
-  \hline
-meta.id & id & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
-  \hline
-9957 & CD000370 & 8 & 2 & 0.66 & 0.66 & 0.66 & 0.82 & 1.59 & 1.59 & 1.40 & 0.28 \\ 
-  22324 & CD001183 & 7 & 0 & -0.48 & -0.48 & -0.48 & -0.21 & -1.10 & -1.12 & -0.50 & -0.11 \\ 
-  49559 & CD002307 & 2 & 1 & -0.10 & -0.08 & -0.10 & 0.03 & -0.47 & -0.42 & -0.41 & -3.00 \\ 
-  169178 & CD007076 & 2 & 2 & 0.37 & 0.34 & 21.92 & 0.14 & 0.74 & 0.74 & 0.70 & 0.23 \\ 
-  197675 & CD008625 & 2 & 2 & -0.60 & -0.60 & -0.60 & -0.39 & -1.72 & -2.02 & -1.01 & -0.69 \\ 
-  217035 & CD009676 & 8 & 1 & 0.36 & 0.35 & 0.36 & 0.08 & 0.69 & 0.71 & 20.28 & 0.12 \\ 
-  222767 & CD010060 & 1 & 0 & 0.31 & 0.32 & 0.31 & 0.23 & 0.50 & 0.52 & 0.20 & -0.49 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects. Abbreviations are used for z-score (= z) and Hedges g (= g).} 
-\label{missing.differences}
-\end{table}
-
-\subsection{Comparison of adjustment methods}
-Regression adjusted estimates are compared to the estimates of Copas selection model if these are not equal to random effects meta-analysis.
-A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
-We will compare estimates based on all three outcome measures, i.e.
-original measure, $z$-score and std.
-mean difference in Figure \ref{fig:adjustment.mean.diff}.
-Note that the 140 \texttt{IV} outcome data is not included when using $z$-score and std.
-mean difference.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{figure/unnamed-chunk-28-1}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-24-1}
+
+}
 
@@
 We conclude thus that the impact of regression adjustment on the effect sizes is in general not substantially larger than the impact of Copas selection model in the subset of data where the estimate of the Copas selection model is not equal to a random effects estimate.
-There is however a small difference, with regression estimates to have a little bit a larger absolute value.
+There is however a small difference, indicating that regression estimates have a little bit a larger absolute value.
 There might be some bias between adjusted $z$-scores, where regression estimates seem to be somewhat smaller when the mean is a little above zero, and somewhat larger when the mean is a little below zero.
 \\
+
+\subsection{Change in Evidence for Treatment Effects} \label{sec:change.evidence}
+Adjustment for small study effects in meta-analysis will provide new effect sizes and standard errors.
+The evidence for the treatment effect being different from zero can be computed.
+It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.
+The test statistics of random effects and fixed effects meta-analysis and the corresponding adjusted test statistics are shown in Figure \ref{fig:evidence.adjustment}.
+The original scale of the effects sizes is used since it is the measure on which policy-makers assess efficacy.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-25-1}
+
+}
+
+\end{knitrout}
+\caption{Absolute value of z test statistics of meta-analyses and adjustment methods.
+The color indicates the evidence for publication bias (\textit{p} value of R\\"ucker's or Egger's test), and the dotted line depicts the diagonal through the origin.}
+\label{fig:evidence.adjustment}
+\end{figure}
+
+Points on the upper left side of the diagonal in Figure \ref{fig:evidence.adjustment} indicate that less evidence for a treatment effect is found in the corresponding evidence.
+Because by and large, the points are on this left side, adjustment leads mostly to smaller test statistics and $p$-values.
+The decrease in evidence is larger when using adjustment with regression, which can be expected as the uncertainity of the additional parameter from the linear regression fit to estimate publication bias is included in the uncertainity in the estimate.
+In contrast, as the Copas selection model algorithm does a sensitivity analysis, the uncertainity of additional model parameters does not affect the estimate as they are not estimated but treated as fixed (see section \ref{sec:procedure} and section \ref{sec:copas}).
+\\
+Also, because the algorithm returns a random effects meta-analysis estimate if no publication bias can be detected, it is hard to compare the test statistics of Copas selection model to fixed effects meta-analysis estimates, as it is not clear when the test statistic has been adjusted.
+The effect of adjustment by copas can be seen when comparing it to random effects meta-analysis.
+There, less of an effect of adjustment on the evidence can be seen.
+\\
+Large adjustment in effect sizes and test statistics is not necessarily accompained by evidence for publication bias in regression adjustment, as discussed previously.
+It is also illustrated by the clear green dots in Figure \ref{fig:evidence.adjustment} far off from the diagonal.
+Evidence for publication bias and large decrease in evidence seem to be correlated.\\
+Some cases which have more evidence for treatment efficacy after adjustment (dots below the diagonal) have evidence for publication bias, which is not expected, since the publication bias tests applied are one-sided and only test for bias towards large effects.
+Thus, dots below the diagonal should all be clear green.
+\\
+After investigation, it has been found that the increase in evidence for treatment effect is most often because the sign of the treatment effect changes, which can not be seen when the absolute value of the z statistic is plotted (24 out of 37 cases where evidence increased after adjustment by regression compared to fixed effects meta-analysis and the $p$-value for publication bias was below 0.1).
+In other cases, the automatic detection of the side on which publication bias was expected (section \ref{sec:procedure}) may failed, because few significant effects are given (used to define side of bias) and the weighted mean effect is close to zero, in which case it is difficult to detect the side of publication bias beforehand.\\
+However, there are some adjustments with large increase in evidence and clear dark orange color, as in the left plot in Figure \ref{fig:adjusted.evidence} (the three points close to x = 10). 
+\begin{itemize}
+\item z-value of regression adjustment 10.5 vs fixed effects z-value 5.7: When the funnnel plot of these meta-analyses are investigated, it becomes clear that there is no reason to assume publication bias since the smaller studies are near to risk ratios equal to one, and larger studies show larger ratios.
+Publication bias tests disagree in their findings (R\"ucker's and Harbord's tests: 0.058 and 0.05, and Peters and Schwarzer's test: 0.467 and 0.79).
+\item z-value of regression adjustment 9.24 vs fixed effects z-value 2.51: Asymmetry of the funnel plot could be confirmed when analysing it with mean differences.
+The change to a larger treatment effect is rather due to large between study heterogeneity and the specific routine of the regression adjustment.
+Because it takes into account between-study heterogeneity, while fixed effects meta-analysis does not, it returns a larger treatment effect.
+The adjusted effect (MD = - 10.3) lies between the fixed effect estimate (-2.56) and the random effects estimate (-18.7).
+\item z-value of regression adjustment 9.5 vs fixed effects z-value 1.3: The increase of evidence is also because of the change of the sign of the effects, in combination with high confidence in the estimated publication bias parameters: the standard erros from the mean differences lie between 0.03 and 70 and the effects are somewhat aligned in the funnel plot.
+\end{itemize}
+In the case of Copas selection model and when both test statistics are large (> 10), the explanation lies in a specialty of the model.
+The adjusted treatment effect estimates are not larger than the unadjusted, but their standard errors are different and sometimes smaller, because they are obtained from the Fisher information matrix of the log-likelihood (see section \ref{sec:copas}).
+\\
+The Copas selection model also allows to compute the number of missing studies, given that the model's assumptions are correct.
+It finds that 2,622 are missing, which corresponds to 11.3\% from all 23,274 analysed studies.
+Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
+Note that random effects meta-analysis substitutes have been excluded (837 out of 1,407.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-26-1}
+
+}
+
+\end{knitrout}
+\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ 0)}
+\label{fig:copas.missing}
+\end{figure}
+
+We can see that in some occasions, the method finds more than half of all studies are missing.
+In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
+The discrepancy between mean and median may indicate that the estimate of 11.3\% missing studies depends somewhat on these extreme cases.
+As can be written of from Table \ref{copas.missing}, 5\%, \ie 28 meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for 1,125, more than 30\% of missing studies.
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Jul 28 15:13:03 2019
+\begin{table}[ht]
+\centering
+\begingroup\footnotesize
+\begin{tabular}{lrrrrrrr}
+  \hline
+ & = 0 & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
+  \hline
+Missing fraction & 240 & 0 & 0 & 0.1 & 0.4 & 1.1 & 0.3 \\ 
+  Missing study number & 240 & 0 & 0 & 1.3 & 5.4 & 21.0 & 4.6 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.} 
+\label{copas.missing}
+\end{table}
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Sun Jul 28 15:13:03 2019
+\begin{table}[ht]
+\centering
+\begingroup\tiny
+\begin{tabular}{lcccrrrrrrrr}
+  \hline
+meta.id & id & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
+  \hline
+9957 & CD000370 & 8 & 2 & 0.66 & 0.66 & 0.66 & 0.82 & 1.59 & 1.59 & 1.40 & 0.28 \\ 
+  22324 & CD001183 & 7 & 0 & -0.48 & -0.48 & -0.48 & -0.21 & -1.10 & -1.12 & -0.50 & -0.11 \\ 
+  49559 & CD002307 & 2 & 1 & -0.10 & -0.08 & -0.10 & 0.03 & -0.47 & -0.42 & -0.41 & -3.00 \\ 
+  169178 & CD007076 & 2 & 2 & 0.37 & 0.34 & 21.92 & 0.14 & 0.74 & 0.74 & 0.70 & 0.23 \\ 
+  197675 & CD008625 & 2 & 2 & -0.60 & -0.60 & -0.60 & -0.39 & -1.72 & -2.02 & -1.01 & -0.69 \\ 
+  217035 & CD009676 & 8 & 1 & 0.36 & 0.35 & 0.36 & 0.08 & 0.69 & 0.71 & 20.28 & 0.12 \\ 
+  222767 & CD010060 & 1 & 0 & 0.31 & 0.32 & 0.31 & 0.23 & 0.50 & 0.52 & 0.20 & -0.49 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects. Abbreviations are used for z-score (= z) and std. mean difference (= d).} 
+\label{missing.differences}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \begin{figure}
+% <<echo=FALSE, fig.height = 9, warning=FALSE>>=
+% #HISTOGRAMS:  
+% 
+% #Comparison of treatment effect p-values:
+% sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+%                               z.ranef = est.z.ranef/se.est.z.ranef,
+%                               z.reg = est.z.reg/se.est.z.reg,
+%                               z.copas = est.z.copas/se.est.z.copas) %>%
+%   select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>%
+%   mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>%
+%   group_by(method) %>%
+%   summarise(significant = length(which(abs(fisher.z) > 1.96)),
+%             p.significant = significant/length(fisher.z))
+% sig.zcor <- data.frame(method = sig.zcor$method,
+%                        label = paste(round(sig.zcor$p.significant,3)*100, "% significant", ", (n = ", sig.zcor$significant, ")", sep = ""))
+% 
+% method_names <- c(
+%   z.fixef = "Fixed Effects",
+%   z.ranef = "Random Effects",
+%   z.reg = "Regression",
+%   z.copas = "Copas"
+% )
+% 
+% adjustment.p.z <- meta.f %>%
+%   mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+%          z.ranef = est.z.ranef/se.est.z.ranef,
+%          z.reg = est.z.reg/se.est.z.reg,
+%          z.copas = est.z.copas/se.est.z.copas) %>%
+%   select(z.fixef, z.ranef, z.reg, z.copas) %>%
+%   gather(key = "method", value = "fisher.z") %>%
+%   mutate(method = factor(method, levels = c("z.fixef", "z.ranef", "z.reg", "z.copas"))) %>%
+%   mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>%
+%   ggplot(aes(x = p.fisher.z)) +
+%   geom_histogram(boundary = 0, bins = 20) +
+%   theme_bw() +
+%   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+%   geom_text(data = sig.zcor, aes(x = 0.5, y = 750, label = label), position = "dodge") +
+%   xlab(expression(paste(italic(p),"-value of test statistic of the ", italic(z),"-score"))) +
+%   ggtitle(expression(paste(italic(z), " Score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Comparison of SMD's:
+% sig.d <- meta.f %>% mutate(d.fixef = est.d.fixef/se.est.d.fixef,
+%                            d.ranef = est.d.ranef/se.est.d.ranef,
+%                            d.reg = est.d.reg/se.est.d.reg,
+%                            d.copas = est.d.copas/se.est.d.copas) %>%  
+%   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+%   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+%   group_by(method) %>% 
+%   summarise(significant = length(which(abs(smd) > 1.96)),
+%             p.significant = significant/length(smd))
+% sig.d <- data.frame(method = sig.d$method,
+%                     label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
+% 
+% method_names <- c(
+%   d.fixef = "Fixed Effects",
+%   d.ranef = "Random Effects",
+%   d.reg = "Regression",
+%   d.copas = "Copas"
+% )
+% 
+% adjustment.p.d <- meta.f %>% 
+%   mutate(d.fixef = est.d.fixef/se.est.d.fixef,
+%          d.ranef = est.d.ranef/se.est.d.ranef,
+%          d.reg = est.d.reg/se.est.d.reg,
+%          d.copas = est.d.copas/se.est.d.copas) %>%  
+%   select(d.fixef, d.ranef, d.reg, d.copas) %>% 
+%   gather(key = "method", value = "smd") %>% 
+%   mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
+%   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+%   ggplot(aes(x = p.smd)) + 
+%   geom_histogram(boundary = 0, bins = 20) + 
+%   theme_bw() + 
+%   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+%   geom_text(data = sig.d, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
+%   xlab(expression(paste(italic(p),"-value of test statistic of std. mean differences"))) +
+%   ggtitle(expression(paste("std. mean difference ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Comparison of log hazard ratios:
+% sig.d <- meta.f %>% filter(outcome.flag == "IV") %>% 
+%   mutate(d.fixef = est.fixef/se.est.fixef,
+%          d.ranef = est.ranef/se.est.ranef,
+%          d.reg = est.reg/se.est.reg,
+%          d.copas = est.copas/se.est.copas) %>%  
+%   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+%   group_by(method) %>% 
+%   summarise(significant = length(which(abs(smd) > 1.96)),
+%             p.significant = (significant + sum(is.na(smd)))/(length(smd)))
+% sig.d <- data.frame(method = sig.d$method,
+%                     label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
+% 
+% method_names <- c(
+%   d.fixef = "Fixed Effects",
+%   d.ranef = "Random Effects",
+%   d.reg = "Regression",
+%   d.copas = "Copas"
+% )
+% 
+% adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.flag == "IV") %>% 
+%   mutate(d.fixef = est.fixef/se.est.fixef,
+%          d.ranef = est.ranef/se.est.ranef,
+%          d.reg = est.reg/se.est.reg,
+%          d.copas = est.copas/se.est.copas) %>%  
+%   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+%   mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
+%   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+%   ggplot(aes(x = p.smd)) + 
+%   geom_histogram(boundary = 0, bins = 20) + 
+%   theme_bw() + 
+%   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+%   geom_text(data = sig.d, aes(x = 0.5, y = 100, label = label), position = "dodge") + 
+%   xlab(expression(paste(italic(p),"-value of test statistic of std. mean difference"))) +
+%   ggtitle(expression(paste("Log IV outcome measures ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% grid.arrange(adjustment.p.z,
+%              adjustment.p.d,
+%              adjustment.p.log.hazard.ratio, ncol = 1)
+% @
+% \caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
+The method is indicated in the header, bin width is set to 0.05.
+The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
+% \label{fig:adjustment.stat}
+% \end{figure}
 

### 2019-07-28 report/chapter04.Rnw
results first complete draft

@@
 
-<<echo=FALSE, warning=FALSE>>=
+<<echo=FALSE, warning=FALSE, message = FALSE>>=
 p.samplesize.z  <- data.ext2 %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% ungroup() %>%
@@
 \section{Publication Bias Test Results} \label{sec:publication.bias.tests}
-<<echo=FALSE, warning=FALSE>>=
+<<echo=FALSE, warning=FALSE, message = FALSE>>=
 #Agreement proportions of publication bias tests:
@@
 
-#HISTOGRAMS:
-
-#Comparison of treatment effect p-values:
-sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
-                              z.ranef = est.z.ranef/se.est.z.ranef,
-                              z.reg = est.z.reg/se.est.z.reg,
-                              z.copas = est.z.copas/se.est.z.copas) %>%  
-  select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>% 
-  mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>% 
-  group_by(method) %>% 
-  summarise(significant = length(which(abs(fisher.z) > 1.96)),
-            p.significant = significant/length(fisher.z))
-sig.zcor <- data.frame(method = sig.zcor$method,
-                       label = paste(round(sig.zcor$p.significant,3)*100, "% significant", ", (n = ", sig.zcor$significant, ")", sep = ""))
-
-method_names <- c(
-  z.fixef = "Fixed Effects",
-  z.ranef = "Random Effects",
-  z.reg = "Regression",
-  z.copas = "Copas"
-)
-
-adjustment.p.z <- meta.f %>% 
-  mutate(z.fixef = est.z.fixef/se.est.z.fixef,
-         z.ranef = est.z.ranef/se.est.z.ranef,
-         z.reg = est.z.reg/se.est.z.reg,
-         z.copas = est.z.copas/se.est.z.copas) %>%  
-  select(z.fixef, z.ranef, z.reg, z.copas) %>% 
-  gather(key = "method", value = "fisher.z") %>% 
-  mutate(method = factor(method, levels = c("z.fixef", "z.ranef", "z.reg", "z.copas"))) %>% 
-  mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>% 
-  ggplot(aes(x = p.fisher.z)) + 
-  geom_histogram(boundary = 0, bins = 20) + 
-  theme_bw() + 
-  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-  geom_text(data = sig.zcor, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
-  xlab(expression(paste(italic(p),"-value of test statistic of the ", italic(z),"-score"))) +
-  ggtitle(expression(paste(italic(z), " Score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Comparison of SMD's:
-sig.d <- meta.f %>% mutate(d.fixef = est.d.fixef/se.est.d.fixef,
-                           d.ranef = est.d.ranef/se.est.d.ranef,
-                           d.reg = est.d.reg/se.est.d.reg,
-                           d.copas = est.d.copas/se.est.d.copas) %>%  
-  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-  group_by(method) %>% 
-  summarise(significant = length(which(abs(smd) > 1.96)),
-            p.significant = significant/length(smd))
-sig.d <- data.frame(method = sig.d$method,
-                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
-
-method_names <- c(
-  d.fixef = "Fixed Effects",
-  d.ranef = "Random Effects",
-  d.reg = "Regression",
-  d.copas = "Copas"
-)
-
-adjustment.p.d <- meta.f %>% 
-  mutate(d.fixef = est.d.fixef/se.est.d.fixef,
-         d.ranef = est.d.ranef/se.est.d.ranef,
-         d.reg = est.d.reg/se.est.d.reg,
-         d.copas = est.d.copas/se.est.d.copas) %>%  
-  select(d.fixef, d.ranef, d.reg, d.copas) %>% 
-  gather(key = "method", value = "smd") %>% 
-  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
-  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-  ggplot(aes(x = p.smd)) + 
-  geom_histogram(boundary = 0, bins = 20) + 
-  theme_bw() + 
-  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-  geom_text(data = sig.d, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
-  xlab(expression(paste(italic(p),"-value of test statistic of std. mean differences"))) +
-  ggtitle(expression(paste("std. mean difference ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-#--------------------------------------------------------------------------------------------------------------------#
-
-#Comparison of log hazard ratios:
-sig.d <- meta.f %>% filter(outcome.flag == "IV") %>% 
-  mutate(d.fixef = est.fixef/se.est.fixef,
-         d.ranef = est.ranef/se.est.ranef,
-         d.reg = est.reg/se.est.reg,
-         d.copas = est.copas/se.est.copas) %>%  
-  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-  group_by(method) %>% 
-  summarise(significant = length(which(abs(smd) > 1.96)),
-            p.significant = (significant + sum(is.na(smd)))/(length(smd)))
-sig.d <- data.frame(method = sig.d$method,
-                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
-
-method_names <- c(
-  d.fixef = "Fixed Effects",
-  d.ranef = "Random Effects",
-  d.reg = "Regression",
-  d.copas = "Copas"
-)
-
-adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.flag == "IV") %>% 
-  mutate(d.fixef = est.fixef/se.est.fixef,
-         d.ranef = est.ranef/se.est.ranef,
-         d.reg = est.reg/se.est.reg,
-         d.copas = est.copas/se.est.copas) %>%  
-  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
-  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-  ggplot(aes(x = p.smd)) + 
-  geom_histogram(boundary = 0, bins = 20) + 
-  theme_bw() + 
-  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-  geom_text(data = sig.d, aes(x = 0.5, y = 100, label = label), position = "dodge") + 
-  xlab(expression(paste(italic(p),"-value of test statistic of Hedges"))) +
-  ggtitle(expression(paste("Log IV outcome measures ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-#--------------------------------------------------------------------------------------------------------------------#
-
 #Plots separated by effect measure:
@@
   scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + 
-  xlab(expression(paste("Fixed effects - adjusted Hedges"))) + geom_vline(xintercept = 0, linetype = "dashed" )
+  xlab(expression(paste("Fixed effects - adjusted std. mean difference"))) + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
   scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) +  ylab("") +
-xlab(expression(paste("Random effects - adjusted Hedges"))) + geom_vline(xintercept = 0, linetype = "dashed" )
+xlab(expression(paste("Random effects - adjusted std. mean difference"))) + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
 
+#--------------------------------------------------------------------------------------------------------------------#
+#Change in evidence of treatment effect scatterplots:
+
+mid <- median(meta.f$pval.se)
+method.names <- c(z.reg = "Regression", z.copas = "Copas Selection Model")
+adjusted.evidence.fixed <- meta.f %>% 
+  select(pval.se, z.fixef, z.ranef, z.reg, z.copas) %>% 
+  gather(key = "method", value = "test.stat", z.reg:z.copas) %>%
+  ggplot(aes(x = test.stat, y = z.fixef, colour = pval.se)) + 
+  facet_wrap(~ method, labeller = as_labeller(method.names)) + 
+  scale_color_gradient2(midpoint=mid, low="firebrick4", mid = "gold",
+                        high="chartreuse2", space ="Lab") +
+  geom_point(size = .7) + theme_bw() + theme(legend.position = "none") + 
+  geom_abline(slope = 1, intercept = 0, linetype = 2, size = .3) +
+  xlab("Adjusted z test statistic") + ylab("Fixed effects test statistic")
+
+adjusted.evidence.ranef <- meta.f %>% 
+  select(pval.se, z.fixef, z.ranef, z.reg, z.copas) %>% 
+  gather(key = "method", value = "test.stat", z.reg:z.copas) %>%
+  ggplot(aes(x = test.stat, y = z.ranef, colour = pval.se)) + 
+  facet_wrap(~ method, labeller = as_labeller(method.names)) + 
+  scale_color_gradient2(midpoint=mid, low="firebrick4", mid = "gold",
+                          high="chartreuse2", space ="Lab", name = expression(paste(italic(p),"-value"))) +
+  geom_point(size = .7) + theme_bw() + guides(fill=guide_legend(title="p-value")) +
+  geom_abline(slope = 1, intercept = 0, linetype = 2, size = .3) +
+  xlab("Adjusted z test statistic") + ylab("Random effects test statistic")
 #--------------------------------------------------------------------------------------------------------------------#
@@
 Table \ref{adjustment.difference} shows quantiles and means for the various differences and the overall proportion of downward adjusted effect sizes.
-When Hedge's $g$ is used as an effect measure, there are (substantially) more reduced effect sizes.
+When std.
+mean difference is used as an effect measure, there are (substantially) more reduced effect sizes.
 The means in Table \ref{adjustment.difference} suggest that the average reduction is small.
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} cases have their $z$-score reduced by more than 0.15 by regression adjustment (and 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} increased by -0.13, fixed effects reference).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} meta-analyses have their $z$-score reduced by more than 0.13 by regression adjustment (and 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} increased by -0.11 or more, fixed effects reference).
 Also, std.
@@
 The row names indicate which outcome measure, meta-analysis method and adjustment method is used.
-Abbreviations are used for z-score (= z) and Hedges g (= g).", align = "lcccccccccr"), include.rownames = T, size = "scriptsize",# sanitize.text.function=function(x){x},
+Abbreviations are used for z-score (= z) and std.
+mean difference (= d).", align = "lcccccccccr"), include.rownames = T, size = "scriptsize",# sanitize.text.function=function(x){x},
       # table.placement = "p"
@@
 
-\subsection{Change in Evidence for Treatment Effects} \label{sec:change.evidence}
-Adjustment for small study effects in meta-analysis will not only provide new effect sizes, but also standard errors thereof.
-Thus, also the evidence for efficacy of a treatment can be obtained, which is usually summarized in a suitable test statistic or $p$-value.
-It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.
-There is an important difference between Copas selection model and regression adjustment.
-The regression adjustment method incorporates an additional parameter with corresponding uncertainity in the treatment effect estimate, while the application of the Copas algorithm does not so.
-Instead, the copas selection model derives the uncertainity of the estimate from the inverse of the fisher information matrix of the likelihood.
-Additionally, the Copas selection model algorithm provides only an estimate when it can detect a small study effect with reasonable precision at the first place (see \ref{sec:copas}).\\
-The Wald test statistics $p$-value for fixed and random effects meta-analyses and Copas and regression adjusted treatment effects have been calculated.
-They are shown in Figure \ref{fig:adjustment.stat} for meta-analysis based on $z$-score, std.
-mean difference and other effect measures (\texttt{outcome.flag} = \texttt{IV}).
-\\
-It can be seen that evidence for a treatment effect decreases after adjusting for publication bias.
-It does so more for Hedge's $g$ compared to $z$-scores, and for regression adjustment compared to Copas selection model.
-%Also, the evidence decreases for random effects meta-analyses compared to fixed effects meta-analyses. 
-In the case of other effect measures (\texttt{outcome.flag} = \texttt{IV}) adjustment, the adjustment has only negligible impact on the $p$-values. \\
-Also, Copas selection method has a very small impact on the evidence compared to random effects meta-analysis, at least using $z$-scores (again, we should rely on comparisons to random effects meta-analysis to evaluate Copas method).
-\\
-% Interestingly, in contrast to the small study effect tests, there seems to be no large difference between adjusted continuous and binary meta-analysis test statistics --appendix--
-%Figures \ref{fig:adjustment.stat.z} for the adjusted $z$-scores, \ref{fig:adjustment.stat.smd} for the adjusted std.
-mean difference and Cohen's d and \ref{fig:adjustment.stat.log.hazard.ratio} for the adjusted log hazard ratios.
+\subsection{Comparison of adjustment methods}
+Regression adjusted estimates are compared to the estimates of Copas selection model if these are not equal to random effects meta-analysis in Figure \ref{fig:adjustment.mean.diff}.
+A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
+Note that most \Sexpr{dim(meta.iv)[1]} \texttt{IV} outcome data is not included when using $z$-score and std.
+mean difference.
 
 \begin{figure}
-<<echo=FALSE, fig.height = 9, warning=FALSE>>=
-grid.arrange(adjustment.p.z,
-             adjustment.p.d,
-             adjustment.p.log.hazard.ratio, ncol = 1)
-@
-\caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
-The method is indicated in the header, bin width is set to 0.05.
-The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
-\label{fig:adjustment.stat}
-\end{figure}
-
-The Copas selection model also gives an estimate of the number of missing studies.
-It finds that \Sexpr{round(sum(meta.f$missing.Copas, na.rm = T))} are missing, which corresponds to \Sexpr{round((sum(meta.f$missing.copas, na.rm = T)/sum(meta.f$k))*100,1)}\% from all \Sexpr{round(sum(meta.f$k))} analysed studies.
-Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
-Note that we have excluded \Sexpr{sum(is.na(meta.f$missing.Copas))} out of \Sexpr{dim(meta.f)[1]}, for which no Copas selection model estimate, but a random effects estimate was retained because the algorithm initially found no evidence for small study effects.
-
-\begin{figure}
-<<echo = FALSE, warning = FALSE>>=
-missing.copas.histogram
-@
-\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ \Sexpr{sum(!is.na(meta.f$missing.Copas))})}
-\label{fig:copas.missing}
-\end{figure}
-
-We can see that in some occasions, the method finds more than half of all studies are missing.
-In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
-The discrepancy between mean and median may indicate that the estimate of \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% missing studies depends somewhat on these extreme cases.
-As can be written of from Table \ref{copas.missing}, 5\%, \ie \Sexpr{round(sum(!is.na(meta.f$missing.Copas))*0.05)} meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for \Sexpr{sum(meta.f$missing.Copas[which(meta.f$missing.Copas >= 17.60)], na.rm = T)}, more than 30\% of missing studies.
-
-<<echo= FALSE, results='asis'>>=
-print(xtable(missing.copas.table, caption = "Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.",
-             label = "copas.missing", align = "lrrrrrrr", digits = c(0,0,0,0,1,1,1,1)),
-      size = "footnotesize")
-@
-
-<<echo=FALSE, results='asis'>>=
-print(xtable(missing.differences, 
-             caption = "Missing meta-analysis pooled treatment effect and adjusted treatment effects.
-Abbreviations are used for z-score (= z) and Hedges g (= g).", label = "missing.differences", align = "llcccrrrrrrrr"),
-      include.rownames = F, size = "tiny")
-@
-
-\subsection{Comparison of adjustment methods}
-Regression adjusted estimates are compared to the estimates of Copas selection model if these are not equal to random effects meta-analysis.
-A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
-We will compare estimates based on all three outcome measures, i.e.
-original measure, $z$-score and std.
-mean difference in Figure \ref{fig:adjustment.mean.diff}.
-Note that the \Sexpr{dim(meta.iv)[1]} \texttt{IV} outcome data is not included when using $z$-score and std.
-mean difference.
-
-\begin{figure}
-<<echo = FALSE, fig.height = 7.5>>=
-grid.arrange(adjustment.mean.diff.orig,
-             adjustment.mean.diff.z,
+<<echo = FALSE, fig.height = 5>>=
+grid.arrange(adjustment.mean.diff.z,
              adjustment.mean.diff.d, ncol = 1)
@@
 We conclude thus that the impact of regression adjustment on the effect sizes is in general not substantially larger than the impact of Copas selection model in the subset of data where the estimate of the Copas selection model is not equal to a random effects estimate.
-There is however a small difference, with regression estimates to have a little bit a larger absolute value.
+There is however a small difference, indicating that regression estimates have a little bit a larger absolute value.
 There might be some bias between adjusted $z$-scores, where regression estimates seem to be somewhat smaller when the mean is a little above zero, and somewhat larger when the mean is a little below zero.
 \\
+
+\subsection{Change in Evidence for Treatment Effects} \label{sec:change.evidence}
+Adjustment for small study effects in meta-analysis will provide new effect sizes and standard errors.
+The evidence for the treatment effect being different from zero can be computed.
+It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.
+The test statistics of random effects and fixed effects meta-analysis and the corresponding adjusted test statistics are shown in Figure \ref{fig:evidence.adjustment}.
+The original scale of the effects sizes is used since it is the measure on which policy-makers assess efficacy.
+
+\begin{figure}
+<<echo = FALSE, warning = FALSE, fig.height = 6>>=
+grid.arrange(adjusted.evidence.fixed,
+             adjusted.evidence.ranef)
+@
+\caption{Absolute value of z test statistics of meta-analyses and adjustment methods.
+The color indicates the evidence for publication bias (\textit{p} value of R\\"ucker's or Egger's test), and the dotted line depicts the diagonal through the origin.}
+\label{fig:evidence.adjustment}
+\end{figure}
+
+Points on the upper left side of the diagonal in Figure \ref{fig:evidence.adjustment} indicate that less evidence for a treatment effect is found in the corresponding evidence.
+Because by and large, the points are on this left side, adjustment leads mostly to smaller test statistics and $p$-values.
+The decrease in evidence is larger when using adjustment with regression, which can be expected as the uncertainity of the additional parameter from the linear regression fit to estimate publication bias is included in the uncertainity in the estimate.
+In contrast, as the Copas selection model algorithm does a sensitivity analysis, the uncertainity of additional model parameters does not affect the estimate as they are not estimated but treated as fixed (see section \ref{sec:procedure} and section \ref{sec:copas}).
+\\
+Also, because the algorithm returns a random effects meta-analysis estimate if no publication bias can be detected, it is hard to compare the test statistics of Copas selection model to fixed effects meta-analysis estimates, as it is not clear when the test statistic has been adjusted.
+The effect of adjustment by copas can be seen when comparing it to random effects meta-analysis.
+There, less of an effect of adjustment on the evidence can be seen.
+\\
+Large adjustment in effect sizes and test statistics is not necessarily accompained by evidence for publication bias in regression adjustment, as discussed previously.
+It is also illustrated by the clear green dots in Figure \ref{fig:evidence.adjustment} far off from the diagonal.
+Evidence for publication bias and large decrease in evidence seem to be correlated.\\
+Some cases which have more evidence for treatment efficacy after adjustment (dots below the diagonal) have evidence for publication bias, which is not expected, since the publication bias tests applied are one-sided and only test for bias towards large effects.
+Thus, dots below the diagonal should all be clear green.
+\\
+After investigation, it has been found that the increase in evidence for treatment effect is most often because the sign of the treatment effect changes, which can not be seen when the absolute value of the z statistic is plotted (24 out of 37 cases where evidence increased after adjustment by regression compared to fixed effects meta-analysis and the $p$-value for publication bias was below 0.1).
+In other cases, the automatic detection of the side on which publication bias was expected (section \ref{sec:procedure}) may failed, because few significant effects are given (used to define side of bias) and the weighted mean effect is close to zero, in which case it is difficult to detect the side of publication bias beforehand.\\
+However, there are some adjustments with large increase in evidence and clear dark orange color, as in the left plot in Figure \ref{fig:evidence.adjustment} (the three points close to x = 10). 
+\begin{itemize}
+\item z-value of regression adjustment 10.5 vs fixed effects z-value 5.7: When the funnnel plot of these meta-analyses are investigated, it becomes clear that there is no reason to assume publication bias since the smaller studies are near to risk ratios equal to one, and larger studies show larger ratios.
+Publication bias tests disagree in their findings (R\"ucker's and Harbord's tests: 0.058 and 0.05, and Peters and Schwarzer's test: 0.467 and 0.79).
+\item z-value of regression adjustment 9.24 vs fixed effects z-value 2.51: Asymmetry of the funnel plot could be confirmed when analysing it with mean differences.
+The change to a larger treatment effect is rather due to large between study heterogeneity and the specific routine of the regression adjustment.
+Because it takes into account between-study heterogeneity, while fixed effects meta-analysis does not, it returns a larger treatment effect.
+The adjusted effect (MD = - 10.3) lies between the fixed effect estimate (-2.56) and the random effects estimate (-18.7).
+\item z-value of regression adjustment 9.5 vs fixed effects z-value 1.3: The increase of evidence is also because of the change of the sign of the effects, in combination with high confidence in the estimated publication bias parameters: the standard erros from the mean differences lie between 0.03 and 70 and the effects are somewhat aligned in the funnel plot.
+\end{itemize}
+In the case of Copas selection model and when both test statistics are large (> 10), the explanation lies in a specialty of the model.
+The adjusted treatment effect estimates are not larger than the unadjusted, but their standard errors are different and sometimes smaller, because they are obtained from the Fisher information matrix of the log-likelihood (see section \ref{sec:copas}).
+\\
+The Copas selection model also allows to compute the number of missing studies, given that the model's assumptions are correct.
+It finds that \Sexpr{format(round(sum(meta.f$missing.copas, na.rm = T)), big.mark = ",")} are missing, which corresponds to \Sexpr{round((sum(meta.f$missing.copas, na.rm = T)/sum(meta.f$k))*100,1)}\% from all \Sexpr{format(round(sum(meta.f$k)), big.mark = ",")} analysed studies.
+Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
+Note that random effects meta-analysis substitutes have been excluded (\Sexpr{sum(is.na(meta.f$missing.copas))} out of \Sexpr{format(dim(meta.f)[1], big.mark = ",")}.
+
+\begin{figure}
+<<echo = FALSE, warning = FALSE>>=
+missing.copas.histogram
+@
+\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ \Sexpr{sum(!is.na(meta.f$missing.Copas))})}
+\label{fig:copas.missing}
+\end{figure}
+
+We can see that in some occasions, the method finds more than half of all studies are missing.
+In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
+The discrepancy between mean and median may indicate that the estimate of \Sexpr{round((sum(meta.f$missing.copas, na.rm = T)/sum(meta.f$k))*100,1)}\% missing studies depends somewhat on these extreme cases.
+As can be written of from Table \ref{copas.missing}, 5\%, \ie \Sexpr{round(sum(!is.na(meta.f$missing.copas))*0.05)} meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for \Sexpr{format(round(sum(meta.f$missing.copas[which(meta.f$missing.copas >= 17.60)], na.rm = T)), big.mark = ",")}, more than 30\% of missing studies.
+
+<<echo= FALSE, results='asis'>>=
+print(xtable(missing.copas.table, caption = "Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.",
+             label = "copas.missing", align = "lrrrrrrr", digits = c(0,0,0,0,1,1,1,1)),
+      size = "footnotesize")
+@
+
+<<echo=FALSE, results='asis'>>=
+print(xtable(missing.differences, 
+             caption = "Missing meta-analysis pooled treatment effect and adjusted treatment effects.
+Abbreviations are used for z-score (= z) and std.
+mean difference (= d).", label = "missing.differences", align = "llcccrrrrrrrr"),
+      include.rownames = F, size = "tiny")
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \begin{figure}
+% <<echo=FALSE, fig.height = 9, warning=FALSE>>=
+% #HISTOGRAMS:  
+% 
+% #Comparison of treatment effect p-values:
+% sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+%                               z.ranef = est.z.ranef/se.est.z.ranef,
+%                               z.reg = est.z.reg/se.est.z.reg,
+%                               z.copas = est.z.copas/se.est.z.copas) %>%
+%   select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>%
+%   mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>%
+%   group_by(method) %>%
+%   summarise(significant = length(which(abs(fisher.z) > 1.96)),
+%             p.significant = significant/length(fisher.z))
+% sig.zcor <- data.frame(method = sig.zcor$method,
+%                        label = paste(round(sig.zcor$p.significant,3)*100, "% significant", ", (n = ", sig.zcor$significant, ")", sep = ""))
+% 
+% method_names <- c(
+%   z.fixef = "Fixed Effects",
+%   z.ranef = "Random Effects",
+%   z.reg = "Regression",
+%   z.copas = "Copas"
+% )
+% 
+% adjustment.p.z <- meta.f %>%
+%   mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+%          z.ranef = est.z.ranef/se.est.z.ranef,
+%          z.reg = est.z.reg/se.est.z.reg,
+%          z.copas = est.z.copas/se.est.z.copas) %>%
+%   select(z.fixef, z.ranef, z.reg, z.copas) %>%
+%   gather(key = "method", value = "fisher.z") %>%
+%   mutate(method = factor(method, levels = c("z.fixef", "z.ranef", "z.reg", "z.copas"))) %>%
+%   mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>%
+%   ggplot(aes(x = p.fisher.z)) +
+%   geom_histogram(boundary = 0, bins = 20) +
+%   theme_bw() +
+%   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+%   geom_text(data = sig.zcor, aes(x = 0.5, y = 750, label = label), position = "dodge") +
+%   xlab(expression(paste(italic(p),"-value of test statistic of the ", italic(z),"-score"))) +
+%   ggtitle(expression(paste(italic(z), " Score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Comparison of SMD's:
+% sig.d <- meta.f %>% mutate(d.fixef = est.d.fixef/se.est.d.fixef,
+%                            d.ranef = est.d.ranef/se.est.d.ranef,
+%                            d.reg = est.d.reg/se.est.d.reg,
+%                            d.copas = est.d.copas/se.est.d.copas) %>%  
+%   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+%   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+%   group_by(method) %>% 
+%   summarise(significant = length(which(abs(smd) > 1.96)),
+%             p.significant = significant/length(smd))
+% sig.d <- data.frame(method = sig.d$method,
+%                     label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
+% 
+% method_names <- c(
+%   d.fixef = "Fixed Effects",
+%   d.ranef = "Random Effects",
+%   d.reg = "Regression",
+%   d.copas = "Copas"
+% )
+% 
+% adjustment.p.d <- meta.f %>% 
+%   mutate(d.fixef = est.d.fixef/se.est.d.fixef,
+%          d.ranef = est.d.ranef/se.est.d.ranef,
+%          d.reg = est.d.reg/se.est.d.reg,
+%          d.copas = est.d.copas/se.est.d.copas) %>%  
+%   select(d.fixef, d.ranef, d.reg, d.copas) %>% 
+%   gather(key = "method", value = "smd") %>% 
+%   mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
+%   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+%   ggplot(aes(x = p.smd)) + 
+%   geom_histogram(boundary = 0, bins = 20) + 
+%   theme_bw() + 
+%   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+%   geom_text(data = sig.d, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
+%   xlab(expression(paste(italic(p),"-value of test statistic of std. mean differences"))) +
+%   ggtitle(expression(paste("std. mean difference ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Comparison of log hazard ratios:
+% sig.d <- meta.f %>% filter(outcome.flag == "IV") %>% 
+%   mutate(d.fixef = est.fixef/se.est.fixef,
+%          d.ranef = est.ranef/se.est.ranef,
+%          d.reg = est.reg/se.est.reg,
+%          d.copas = est.copas/se.est.copas) %>%  
+%   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+%   group_by(method) %>% 
+%   summarise(significant = length(which(abs(smd) > 1.96)),
+%             p.significant = (significant + sum(is.na(smd)))/(length(smd)))
+% sig.d <- data.frame(method = sig.d$method,
+%                     label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
+% 
+% method_names <- c(
+%   d.fixef = "Fixed Effects",
+%   d.ranef = "Random Effects",
+%   d.reg = "Regression",
+%   d.copas = "Copas"
+% )
+% 
+% adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.flag == "IV") %>% 
+%   mutate(d.fixef = est.fixef/se.est.fixef,
+%          d.ranef = est.ranef/se.est.ranef,
+%          d.reg = est.reg/se.est.reg,
+%          d.copas = est.copas/se.est.copas) %>%  
+%   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+%   mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
+%   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+%   ggplot(aes(x = p.smd)) + 
+%   geom_histogram(boundary = 0, bins = 20) + 
+%   theme_bw() + 
+%   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+%   geom_text(data = sig.d, aes(x = 0.5, y = 100, label = label), position = "dodge") + 
+%   xlab(expression(paste(italic(p),"-value of test statistic of std. mean difference"))) +
+%   ggtitle(expression(paste("Log IV outcome measures ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% grid.arrange(adjustment.p.z,
+%              adjustment.p.d,
+%              adjustment.p.log.hazard.ratio, ncol = 1)
+% @
+% \caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
+The method is indicated in the header, bin width is set to 0.05.
+The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
+% \label{fig:adjustment.stat}
+% \end{figure}

### 2019-07-28 code/analysis.R

@@ -673,13 +673,14 @@ meta.f <- meta.f %>% rowwise() %>% mutate(pval1.egger = onesided.p(stat = stat.e
                                           pval1.schwarzer = onesided.p(stat = stat.schwarzer, side = side, n = k, test.type = "rank"),
                                           pval1.d.tes = pval.d.tes)
 
+#Summarise different tests for binary and continuous variables to one:
 meta.f <- meta.f %>% rowwise() %>% mutate(I2  = max(0, (Q - k + 1)/Q),
                             var.ratio = (se.max^2)/(se.min^2),
                             pval.se = case_when(outcome.flag == "DICH" ~ pval1.rucker.linreg, 
                                                 TRUE ~ pval1.egger),
                             pval.se.het = case_when(outcome.flag == "DICH" ~ pval1.rucker, 
                                                     TRUE ~ pval1.thompson))
-
+#significance of pb tests:
 sig.level <- 0.1
 meta.f <- meta.f %>% rowwise() %>% 
   mutate(egger.test = ifelse(pval1.egger < sig.level, 1, 0),
@@ -693,6 +694,57 @@ meta.f <- meta.f %>% rowwise() %>%
          rucker.test.linreg = ifelse(pval1.rucker.linreg < sig.level, 1, 0),
          harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
          peter.test = ifelse(pval1.peter < sig.level, 1, 0))
+
+#Calculate test statistics for treatment effect - special IV outcomes need subtraction of 1:
+meta.f <- meta.f %>% mutate(
+  z.fixef = case_when(outcome.flag != "IV" ~ abs(est.fixef/se.est.fixef),
+                      outcome.flag == "IV" & outcome.measure.merged == "SMD" ~ abs(est.fixef/se.est.fixef),
+                      outcome.flag == "IV" & outcome.measure.merged == "Hazard Ratio" ~ abs((est.fixef - 1)/se.est.fixef),
+                      outcome.flag == "IV" & outcome.measure.merged == "Rate Ratio" ~ abs((est.fixef - 1)/se.est.fixef),
+                      outcome.flag == "IV" & outcome.measure.merged == "Ratio of means" ~ abs((est.fixef - 1)/se.est.fixef),
+                      outcome.flag == "IV" & outcome.measure.merged == "OR" ~ abs((est.fixef - 1)/se.est.fixef),
[…]

### 2019-08-02 report/MSc_Report.tex
appendix, corrected IV results

@@
 This generates a bias called ``publication bias'', a distorted view of the evidence for an effect.
-Recently, publication bias has been identified as one of the major concerns in irreproducible research \citep{Bishop.2019}.
-The issue has been discussed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}).
+Publication bias has been identified as one of the major concerns in irreproducible research \citep{Bishop.2019}.
+The issue has been discussed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}, \citet{Dwan2013}).
 Consensus is that publication bias exists in clinical science.
@@
 Results from RCTs influence the treatment of patients in daily clinical practice.
-The results from multiple intervention studies can be summarized in a meta-analysis to estimate an overall treatment effect (access all studies).
+The results from multiple intervention studies can be summarized in a meta-analysis to estimate an overall treatment effect (access all studies) \citep{Cochran}.
 However, publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm, distortion and financial expenses.
@@
 There are multiple ways to assess the amount of publication bias.
-For instance, it is possible to follow studies and assess if they are getting published depending on their findings \citep{publication.fate}.
+For instance, it is possible to follow studies and assess if they are getting published depending on their findings (\citet{Dwan2013}, \citet{publication.fate}, \citet{Lee.2008}).
 One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in social sciences: \citet{social.sciences.publication.bias}).
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Jul 24 16:42:40 2019
+% Thu Aug  1 15:37:26 2019
 \begin{table}[ht]
@@
 {\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Jul 24 16:42:40 2019
+% Thu Aug  1 15:37:26 2019
 \begin{table}[ht]
@@
 \item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = 9916 remaining). 
-\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 9334 remaining).
-\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 7509 remaining)
-\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 1403 remaining).
+\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 9616 remaining).
+\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 7586 remaining)
+\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 405 remaining).
 \end{itemize}
@@
     \node [block, below of=3, node distance=2cm] (4) {
-    1,133 reviews,
-    26,101 studies,
-    164,222 results,
-    9,334 meta-analyses};
+    1,140 reviews,
+    26,306 studies,
+    170,096 results,
+    9,616 meta-analyses};
 
     \node [block, below of=4, node distance=2cm] (5) {
-    1,056 reviews,
-    24,149 studies,
-    136,537 results,
-    7,509 meta-analyses};
+    1,064 reviews,
+    24,277 studies,
+    137,613 results,
+    7,586 meta-analyses};
 
     \node [block, below of=5, node distance=2cm] (6) {
-    1,024 reviews,
-    22,502 studies,
-    47,092 results,
-    2,694 meta-analyses};
+    1,033 reviews,
+    22,668 studies,
+    47,607 results,
+    2,729 meta-analyses};
 
     \node [final, below of=6, node distance=2cm] (7) {Analysis dataset (1):
-    740 reviews,
-    14,467 studies,
-    23,243 results,
-    1,403 meta-analyses};
+    303 reviews,
+    5,355 studies,
+    6,592 results,
+    405 meta-analyses};
 
@@
     \node [ublock, right of=8, node distance=5cm] (9) {Continuous data: \\
-    336 meta-analyses};
+    343 meta-analyses};
 
     \node [ublock, left of=8, node distance=5cm] (10) {Other data (IV): \\
-    140 meta-analyses};
+    121 meta-analyses};
 
     \node [final, below of=8, node distance=2.4cm] (11) {Analysis dataset (2):
-    678 reviews,
-    13,357 studies,
-    20,984 results,
-    1,260 meta-analyses};
+    685 reviews,
+    13,396 studies,
+    21,074 results,
+    1,267 meta-analyses};
 
@@
 \subsubsection{The Analysis Dataset}
-The dataset that was ultimately tested and adjusted for publication bias comprises 1 meta-analyses and 23243 results.
-The mean number of participants in the treatment group is 251.9 vs 256.7 in the unrestricted dataset and the mean total number of participants 584.7 vs 623.2.
-The mean publication year is 2000.3028869 vs 2000.9711014 in the unrestricted dataset.
-\\
-From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}), there are 34 with \\ \texttt{outcome.measure.merged} = ``Risk Ratio'', 27 ``Std.
-Mean Difference'',  26 ``Hazard Ratio'' and 13 ``Odds Ratio'' (and 25 additional, different outcome measures).
+The dataset that was ultimately tested and adjusted for publication bias comprises 1 meta-analyses and 6592 results.
+The mean number of participants in the treatment group is 206.9 vs 256.7 in the unrestricted dataset and the mean total number of participants 393.2 vs 623.2.
+The mean publication year is 1999.8575604 vs 2000.9711014 in the unrestricted dataset.
+\\
+From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}), there are 36 with \\ \texttt{outcome.measure.merged} = ``Risk Ratio'', 26 ``Std.
+Mean Difference'',  25 ``Hazard Ratio'' and 15 ``Odds Ratio'' (and 25 additional, different outcome measures).
 
@@
 Notably, excess significance test, Schwarzer's test and rank tests have been shown to lack power.
-The tests that are more suitable (regression based tests in general) all have proportions of significant $p$-values ($p$ > 0.1) clearly above 10 \% which would be the expected false positive rate.
-The conclusion is that there is publication bias, however the extent can be debated.
-The meta-analyses with \texttt{outcome.flag} = \texttt{IV} seem to differ from the other meta-analyses.
-\\
+The tests that are more suitable (regression based tests in general) all have proportions of significant $p$-values ($p$ > 0.1) clearly above 10 \% which would be the expected false positive rate.\\
 In Figure \ref{fig:test}, the meta-analyses with an estimated $I^2$ of zero are depicted, because some methods are known to only be suitable when no heterogeneity is present (excess significance test and also Egger's test).
@@
 In the case of binary tests, the $p$-values of R\"ucker's, Peters, Harbord's, Schwarzer's and excess significance tests are used, in the case of continuous and \texttt{outcome.flag} = \texttt{IV} outcomes, Egger's, Thompson and Sharp's, Begg and Mazumdar's and excess significance tests are used.
-This lead's to an overall of 19.1\% significant results ($p_\textrm{harmonic}$ < 0.1, 19.7\% \texttt{outcome.flag} = \texttt{DICH}, 20.1\% \texttt{outcome.flag} = \texttt{CONT}, 12.9\% \texttt{outcome.flag} = \texttt{IV}).
+This lead's to an overall of 20.3\% significant results ($p_\textrm{harmonic}$ < 0.1, 19.7\% \texttt{outcome.flag} = \texttt{DICH}, 20.1\% \texttt{outcome.flag} = \texttt{CONT}, 25.6\% \texttt{outcome.flag} = \texttt{IV}).
 
@@
 Around 67\% of the dataset is not significant, no matter which test is used.
-When only using small study effect tests, 29.5\% of binary outcome tests and 29\% of \texttt{IV} and continuous outcome tests had at least one significant result.
-After applying the Bonferroni correction for multiple testing, this shrinks to 12.3\% for binary and 12\% for continuous and \texttt{IV} outcomes.
+When only using small study effect tests, 29.5\% of binary outcome tests and 31.9\% of \texttt{IV} and continuous outcome tests had at least one significant result.
+After applying the Bonferroni correction for multiple testing, this shrinks to 12.3\% for binary and 14.4\% for continuous and \texttt{IV} outcomes.
 To compare significant findings for small study effect tests and excess significance tests, Harbord's or Egger's test results are compared with excess significane tests.
-24.1\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 24.4\% for continuous and \texttt{IV} outcomes.
-The numbers change to 13.9\% for binary outcomes and 14.7\% for continuous and \texttt{IV} outcomes after applying the Bonferroni correction.
+24.1\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 28.4\% for continuous and \texttt{IV} outcomes.
+The numbers change to 13.9\% for binary outcomes and 18.1\% for continuous and \texttt{IV} outcomes after applying the Bonferroni correction.
 5.1\% have significant Harbord's test result and significant excess significance test result  (2.3\% with Bonferroni).
-Of the continuous outcomes, we have 3.3\% with Egger's test and 1.4\% with Bonferroni correction.
+Of the continuous outcomes, we have 3.9\% with Egger's test and 1.3\% with Bonferroni correction.
 \\
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Jul 28 15:12:47 2019
+% Fri Aug  2 14:32:32 2019
 \begin{table}[ht]
@@
   \hline
-0 & 66.1 \% & 68.9 \% \\ 
-  1 & 12.3 \% & 11.2 \% \\ 
-  2 & 7.7 \% & 6.6 \% \\ 
-  3 & 6.8 \% & 11.4 \% \\ 
-  4 & 5.7 \% & 1.9 \% \\ 
+0 & 66.1 \% & 65.3 \% \\ 
+  1 & 12.3 \% & 11.9 \% \\ 
+  2 & 7.7 \% & 6.9 \% \\ 
+  3 & 6.8 \% & 14.2 \% \\ 
+  4 & 5.7 \% & 1.7 \% \\ 
   5 & 1.3 \% & - \\ 
@@
 We see that only in few cases when excess significance test indicates statistical significance, small study effect tests do so.
-Correspondence between excess significance tests and small study effects thus has to be considered rather random.
+Correspondence between excess significance tests and small study effects thus is considered rather random.
 Linear regression based tests agree more often with other linear regression based tests, and agreement between small study effect tests is in general well above 60 \% (at best, 95 \% test agreement in significance for \texttt{IV} \texttt{outcome.flag}).
@@
   Egger, Begg & 0.84 & 0.70 \\ 
-  Excess significance, Egger (IV) & 0.84 & 0.09 \\ 
-  Excess significance, Thompson (IV) & 0.84 & 0.10 \\ 
-  Excess significance, Begg (IV) & 0.85 & 0.10 \\ 
-  Thompson, Egger (IV) & 0.98 & 0.95 \\ 
-  Thompson, Begg (IV) & 0.86 & 0.55 \\ 
-  Egger, Begg (IV) & 0.87 & 0.60 \\ 
+  Excess significance, Egger (IV) & 0.71 & 0.12 \\ 
+  Excess significance, Thompson (IV) & 0.71 & 0.10 \\ 
+  Excess significance, Begg (IV) & 0.74 & 0.04 \\ 
+  Thompson, Egger (IV) & 0.95 & 0.94 \\ 
+  Thompson, Begg (IV) & 0.86 & 0.79 \\ 
+  Egger, Begg (IV) & 0.86 & 0.83 \\ 
    \hline
@@
 The means in Table \ref{adjustment.difference} suggest that the average reduction is small.
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 70 meta-analyses have their $z$-score reduced by more than 0.13 by regression adjustment (and 5\% or 70 increased by -0.11 or more, fixed effects reference).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 69 meta-analyses have their $z$-score reduced by more than 0.13 by regression adjustment (and 5\% or 69 increased by -0.11 or more, fixed effects reference).
 Also, std.
-mean difference is reduced by 0.39 compared to fixed effects estimates in 5\% or 70 meta-analyses (or increased by 0.24).
+mean difference is reduced by 0.39 compared to fixed effects estimates in 5\% or 69 meta-analyses (or increased by 0.24).
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Jul 28 15:13:01 2019
+% Fri Aug  2 14:32:47 2019
 \begin{table}[ht]
@@
   \hline
-z: Fixed - Copas & -0.04 & -0.01 & 0.00 & 0.01 & 0.04 & -0.02 & 8.03 & 49.40 & 41.36 & 64.61 \\ 
-  z: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.04 & -0.01 & 66.24 & 84.01 & 17.77 & 64.61 \\ 
-  z: Fixed - Regression & -0.11 & -0.03 & 0.01 & 0.05 & 0.13 & 0.01 & 0.00 & 51.31 & 51.31 & 0.00 \\ 
-  z: Random - Regression & -0.13 & -0.02 & 0.02 & 0.06 & 0.16 & 0.02 & 0.00 & 55.79 & 55.79 & 0.00 \\ 
-  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.11 & -0.00 & 19.12 & 55.58 & 36.46 & 56.15 \\ 
-  g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.16 & 0.01 & 59.28 & 83.80 & 24.52 & 56.15 \\ 
-  g: Fixed - Regression & -0.21 & -0.03 & 0.04 & 0.14 & 0.40 & 0.06 & 0.00 & 59.35 & 59.35 & 0.00 \\ 
-  g: Random - Regression & -0.20 & -0.02 & 0.05 & 0.17 & 0.44 & 0.08 & 0.00 & 61.83 & 61.83 & 0.00 \\ 
-  IV: Fixed - Copas & -0.05 & -0.00 & 0.00 & 0.01 & 0.07 & 0.16 & 30.71 & 41.43 & 72.14 & 57.86 \\ 
-  IV: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.10 & 0.21 & 62.86 & 25.71 & 88.57 & 57.86 \\ 
-  IV: Fixed - Regression & -0.52 & -0.09 & -0.01 & 0.05 & 0.69 & 0.34 & 0.00 & 44.29 & 44.29 & 0.00 \\ 
-  IV: Random - Regression & -0.52 & -0.09 & -0.01 & 0.07 & 0.76 & 0.39 & 0.00 & 45.00 & 45.00 & 0.00 \\ 
+z: Fixed - Copas & -0.04 & -0.01 & 0.00 & 0.01 & 0.04 & 0.00 & 8.14 & 50.14 & 42.00 & 65.49 \\ 
+  z: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.04 & 0.00 & 67.15 & 85.23 & 18.08 & 65.49 \\ 
+  z: Fixed - Regression & -0.11 & -0.03 & 0.01 & 0.05 & 0.13 & 0.01 & 0.00 & 52.02 & 52.02 & 0.00 \\ 
+  z: Random - Regression & -0.13 & -0.02 & 0.02 & 0.06 & 0.16 & 0.02 & 0.00 & 56.56 & 56.56 & 0.00 \\ 
+  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.11 & 0.01 & 19.38 & 56.41 & 37.03 & 56.92 \\ 
+  g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.16 & 0.02 & 60.09 & 85.01 & 24.93 & 56.92 \\ 
+  g: Fixed - Regression & -0.21 & -0.03 & 0.04 & 0.14 & 0.40 & 0.06 & 0.00 & 60.16 & 60.16 & 0.00 \\ 
+  g: Random - Regression & -0.20 & -0.02 & 0.05 & 0.17 & 0.44 & 0.08 & 0.00 & 62.68 & 62.68 & 0.00 \\ 
+  IV: Fixed - Copas & -0.06 & -0.01 & 0.00 & 0.01 & 0.07 & 0.00 & 23.97 & 42.15 & 66.12 & 59.50 \\ 
+  IV: Random - Copas & -0.00 & 0.00 & 0.00 & 0.01 & 0.08 & 0.01 & 61.98 & 28.93 & 90.91 & 59.50 \\ 
+  IV: Fixed - Regression & -0.24 & -0.02 & 0.03 & 0.11 & 0.36 & 0.03 & 0.00 & 66.12 & 66.12 & 0.00 \\ 
+  IV: Random - Regression & -0.25 & -0.02 & 0.04 & 0.13 & 0.49 & 0.05 & 0.00 & 68.59 & 68.59 & 0.00 \\ 
    \hline
@@
 
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Fri Aug  2 14:32:47 2019
+\begin{table}[ht]
+\centering
+\begingroup\tiny
+\begin{tabular}{lcccrrrrrrrr}
+  \hline
+meta.id & id & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
+  \hline
+9957 & CD000370 & 8 & 2 & 0.66 & 0.66 & 0.66 & 0.82 & 1.59 & 1.59 & 1.40 & 0.28 \\ 
+  22324 & CD001183 & 7 & 0 & -0.48 & -0.48 & -0.48 & -0.21 & -1.10 & -1.12 & -0.50 & -0.11 \\ 
+  49559 & CD002307 & 2 & 1 & -0.10 & -0.08 & -0.10 & 0.03 & -0.47 & -0.42 & -0.41 & -3.00 \\ 
+  197675 & CD008625 & 2 & 2 & -0.60 & -0.60 & -0.60 & -0.39 & -1.72 & -2.02 & -1.01 & -0.69 \\ 
+  222767 & CD010060 & 1 & 0 & 0.31 & 0.32 & 0.31 & 0.23 & 0.50 & 0.52 & 0.20 & -0.49 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects. Abbreviations are used for z-score (= z) and std. mean difference (= d).} 
+\label{missing.differences}
+\end{table}
+
 \subsection{Comparison of adjustment methods}
@@
 A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
-Note that most 140 \texttt{IV} outcome data is not included when using $z$-score and std.
+Note that most 121 \texttt{IV} outcome data is not included when using $z$-score and std.
 mean difference.
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-24-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-25-1}
 
@@
 Adjustment for small study effects in meta-analysis will provide new effect sizes and standard errors.
-The evidence for the treatment effect being different from zero can be computed.
-It is of interest if and how the evidence for treatment effects changes if adjusted for publication bias.
-The test statistics of random effects and fixed effects meta-analysis and the corresponding adjusted test statistics are shown in Figure \ref{fig:evidence.adjustment}.
-The original scale of the effects sizes is used since it is the measure on which policy-makers assess efficacy.
+The evidence against the null hypothesis of no treatment effect can be computed newly.
+The test statistics $\frac{\theta}{\se(\theta)}$ of random effects and fixed effects meta-analysis and the corresponding adjusted test statistics are shown in Figure \ref{fig:evidence.adjustment}.
+The original scale of the effects sizes is used, since it is the measure on which policy-makers assess the treatment efficacy.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-25-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-26-1}
 
@@
 \end{knitrout}
-\caption{Absolute value of z test statistics of meta-analyses and adjustment methods.
+\caption{Test statistics of meta-analyses and adjustment methods.
 The color indicates the evidence for publication bias (\textit{p} value of R\\"ucker's or Egger's test), and the dotted line depicts the diagonal through the origin.}
@@
 
-Points on the upper left side of the diagonal in Figure \ref{fig:evidence.adjustment} indicate that less evidence for a treatment effect is found in the corresponding evidence.
-Because by and large, the points are on this left side, adjustment leads mostly to smaller test statistics and $p$-values.
-The decrease in evidence is larger when using adjustment with regression, which can be expected as the uncertainity of the additional parameter from the linear regression fit to estimate publication bias is included in the uncertainity in the estimate.
-In contrast, as the Copas selection model algorithm does a sensitivity analysis, the uncertainity of additional model parameters does not affect the estimate as they are not estimated but treated as fixed (see section \ref{sec:procedure} and section \ref{sec:copas}).
-\\
-Also, because the algorithm returns a random effects meta-analysis estimate if no publication bias can be detected, it is hard to compare the test statistics of Copas selection model to fixed effects meta-analysis estimates, as it is not clear when the test statistic has been adjusted.
+% Points lying on the diagonal through the origin indicate that there is no change in evidence after adjustment.
+In a hypothetical study with all treatment effects being artifacts of publication bias and perfect adjustment methods, all points should be distibuted on a vertical line at $x = 0$.
+A mitigation of evidence against the null hypothesis after adjustment thus is indicated by the adjusted test statistics being closer to zero.
+\\
+
+It can be seen that the alignment on the diagonal changes depending on the adjustment method.
 The effect of adjustment by copas can be seen when comparing it to random effects meta-analysis.
@@
 \\
-Large adjustment in effect sizes and test statistics is not necessarily accompained by evidence for publication bias in regression adjustment, as discussed previously.
-It is also illustrated by the clear green dots in Figure \ref{fig:evidence.adjustment} far off from the diagonal.
-Evidence for publication bias and large decrease in evidence seem to be correlated.\\
-Some cases which have more evidence for treatment efficacy after adjustment (dots below the diagonal) have evidence for publication bias, which is not expected, since the publication bias tests applied are one-sided and only test for bias towards large effects.
-Thus, dots below the diagonal should all be clear green.
-\\
-After investigation, it has been found that the increase in evidence for treatment effect is most often because the sign of the treatment effect changes, which can not be seen when the absolute value of the z statistic is plotted (24 out of 37 cases where evidence increased after adjustment by regression compared to fixed effects meta-analysis and the $p$-value for publication bias was below 0.1).
-In other cases, the automatic detection of the side on which publication bias was expected (section \ref{sec:procedure}) may failed, because few significant effects are given (used to define side of bias) and the weighted mean effect is close to zero, in which case it is difficult to detect the side of publication bias beforehand.\\
-However, there are some adjustments with large increase in evidence and clear dark orange color, as in the left plot in Figure \ref{fig:adjusted.evidence} (the three points close to x = 10). 
+Thus, the decrease in evidence is larger when using adjustment with regression, which can be expected as the uncertainity of the additional parameter from the linear regression fit to estimate publication bias is included in the uncertainity of the estimate.
+In contrast, as the Copas selection model algorithm does a sensitivity analysis, the uncertainity of additional model parameters does not affect the estimate as they are not estimated but treated as fixed (see section \ref{sec:procedure} and section \ref{sec:copas}).\\
+Large adjustment in effect sizes and test statistics is not necessarily accompained by evidence for publication bias (color of the dots) in regression adjustment, as already discussed.
+The dark dots can be found more often far away from the diagonal.
+Some cases which have more evidence for treatment efficacy after adjustment have evidence for publication bias, which is not expected, since the publication bias tests applied are one-sided and only test for bias towards large effects.
+\\
+In some cases, the automatic detection of the side on which publication bias was expected (section \ref{sec:procedure}) might failed, because few significant effects are given (used to define side of bias) and the weighted mean effect is close to zero, in which case it is difficult to detect the side of publication bias beforehand.
+There are some adjustments with large increase in evidence and clear dark orange color, as in the plots on the right hand side in Figure \ref{fig:evidence.adjustment}.
+Two of them are investigated in detail.
 \begin{itemize}
@@
 The change to a larger treatment effect is rather due to large between study heterogeneity and the specific routine of the regression adjustment.
-Because it takes into account between-study heterogeneity, while fixed effects meta-analysis does not, it returns a larger treatment effect.
+Because it takes into account between-study heterogeneity (bias parameter times $\tau^2$), while fixed effects meta-analysis does not, it returns a larger treatment effect.
 The adjusted effect (MD = - 10.3) lies between the fixed effect estimate (-2.56) and the random effects estimate (-18.7).
-\item z-value of regression adjustment 9.5 vs fixed effects z-value 1.3: The increase of evidence is also because of the change of the sign of the effects, in combination with high confidence in the estimated publication bias parameters: the standard erros from the mean differences lie between 0.03 and 70 and the effects are somewhat aligned in the funnel plot.
 \end{itemize}
@@
 The Copas selection model also allows to compute the number of missing studies, given that the model's assumptions are correct.
-It finds that 2,622 are missing, which corresponds to 11.3\% from all 23,274 analysed studies.
+It finds that 2,618 are missing, which corresponds to 11.4\% from all 22,916 analysed studies.
 Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
-Note that random effects meta-analysis substitutes have been excluded (837 out of 1,407.
+Note that random effects meta-analysis substitutes have been excluded (828 out of 1,388.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-26-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-27-1}
 
@@
 In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
-The discrepancy between mean and median may indicate that the estimate of 11.3\% missing studies depends somewhat on these extreme cases.
-As can be written of from Table \ref{copas.missing}, 5\%, \ie 28 meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for 1,125, more than 30\% of missing studies.
+The discrepancy between mean and median may indicate that the estimate of 11.4\% missing studies depends somewhat on these extreme cases.
+As can be written of from Table \ref{copas.missing}, 5\%, \ie 28 meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for 1,060, more than 30\% of missing studies.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Jul 28 15:13:03 2019
+% Fri Aug  2 14:32:48 2019
 \begin{table}[ht]
@@
   \hline
-Missing fraction & 240 & 0 & 0 & 0.1 & 0.4 & 1.1 & 0.3 \\ 
-  Missing study number & 240 & 0 & 0 & 1.3 & 5.4 & 21.0 & 4.6 \\ 
+Missing fraction & 226 & 0 & 0 & 0.1 & 0.4 & 1.0 & 0.3 \\ 
+  Missing study number & 226 & 0 & 0 & 1.5 & 5.9 & 20.1 & 4.7 \\ 
    \hline
@@
 
+\section{Publication Bias over Time}
+To test if publication bias in meta-analses has decreased over time and newer meta-analyses have less bias, a generalized linear model has been set up. \\
+The dependent variable is the standardized mean differences (therefore, from \texttt{outcome.flag} = \texttt{IV}, only the std.
+mean differences are used).
+As before, the std.
+mean difference is mirrored to one side by multiplying with the sign of the expected side of bias, \ie -1 or 1.
+The explanatory variable is the standard error, and the weights are the inverse of the variance of the std.
+mean difference.
+Additionally, random effects for the meta-analysis and for the review are added, the former being nested in the latter.
+Figure \ref{fig:smds} shows the complete dataset with the fit of the previously described model (dotted red line).
+The details and evidence for the small study effects in the generalized linear model are given in table \ref{anova.small.study}, the coefficients in table \ref{coefficients.small.study}
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-29-1}
+
+}
+
+\end{knitrout}
+\caption{Std. mean differences of all meta-analyses plotted against their standard error, with the fit of a generalized linear model (dotted red line).}
+\label{fig:smds}
+\end{figure}
+
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Jul 28 15:13:03 2019
+% Fri Aug  2 14:32:57 2019
 \begin{table}[ht]
 \centering
-\begingroup\tiny
-\begin{tabular}{lcccrrrrrrrr}
-  \hline
-meta.id & id & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
-  \hline
-9957 & CD000370 & 8 & 2 & 0.66 & 0.66 & 0.66 & 0.82 & 1.59 & 1.59 & 1.40 & 0.28 \\ 
-  22324 & CD001183 & 7 & 0 & -0.48 & -0.48 & -0.48 & -0.21 & -1.10 & -1.12 & -0.50 & -0.11 \\ 
-  49559 & CD002307 & 2 & 1 & -0.10 & -0.08 & -0.10 & 0.03 & -0.47 & -0.42 & -0.41 & -3.00 \\ 
-  169178 & CD007076 & 2 & 2 & 0.37 & 0.34 & 21.92 & 0.14 & 0.74 & 0.74 & 0.70 & 0.23 \\ 
-  197675 & CD008625 & 2 & 2 & -0.60 & -0.60 & -0.60 & -0.39 & -1.72 & -2.02 & -1.01 & -0.69 \\ 
-  217035 & CD009676 & 8 & 1 & 0.36 & 0.35 & 0.36 & 0.08 & 0.69 & 0.71 & 20.28 & 0.12 \\ 
-  222767 & CD010060 & 1 & 0 & 0.31 & 0.32 & 0.31 & 0.23 & 0.50 & 0.52 & 0.20 & -0.49 \\ 
+\begingroup\scriptsize
+\begin{tabular}{rrrrrrlrr}
+  \hline
+ & Model & df & AIC & BIC & logLik & Test & L.Ratio & p-value \\ 
+  \hline
+null.fit &   1 & 4.00 & 18768.23 & 18800.12 & -9380.11 &  &  &  \\ 
+  small.study.fit &   2 & 5.00 & 18230.52 & 18270.39 & -9110.26 & 1 vs 2 & 539.71 & 0.00 \\ 
    \hline
@@
 \endgroup
-\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects. Abbreviations are used for z-score (= z) and std. mean difference (= d).} 
-\label{missing.differences}
+\caption{Anova table for a generalized linear model for small study effects compared to the null model. 'small.study.fit' denotes the model with random intercepts for meta-analyses and reviews.} 
+\label{anova.small.study}
 \end{table}
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Fri Aug  2 14:32:58 2019
+\begin{table}[ht]
+\centering
+\begingroup\scriptsize
+\begin{tabular}{lccc}
+  \hline
+ & estimate & 2.5\%CL & 97.5\%CL \\ 
+  \hline
+(Intercept) & 0.18 & 0.16 & 0.19 \\ 
+  se.smd.pool & 0.38 & 0.35 & 0.41 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Coefficients and 95\% confidence limits of the generalized linear model. 'se.smd.pool' denotes the standard error of the std. mean difference.} 
+\label{coefficients.small.study}
+\end{table}
+
+It is possible to include meta-analysis specific random slopes.
+Before continuing, it is tested if incorporation of random slopes improves model fit.
+Table \ref{anova.random.slopes} shows the anova table for a model with and without random slopes.
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Fri Aug  2 14:32:59 2019
+\begin{table}[ht]
+\centering
+\begingroup\scriptsize
+\begin{tabular}{rrrrrrlrr}
+  \hline
+ & Model & df & AIC & BIC & logLik & Test & L.Ratio & p-value \\ 
+  \hline
+small.study.fit &   1 & 5.00 & 18230.52 & 18270.39 & -9110.26 &  &  &  \\ 
+  small.study.rs.fit &   2 & 7.00 & 18233.07 & 18288.88 & -9109.53 & 1 vs 2 & 1.46 & 0.48 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Anova table for two generalized linear model fits.
+'small.study.fit' denotes the model with random intercepts for meta-analyses and reviews, 'small.study.rs.fit' the model with additional random slopes per review.}
+\label{anova.random.slopes}
+\end{table}
+
+Model diagnostics indicate that there is no benefit in including random slopes for the single meta-analysis. \\
+To test if publication bias varies over time, we include the year of the publication of the review as an additional explanatory variable.
+Ulitmately, it is of interest if there is an interaction between the small study effect (publication bias) and time, i.e.
+if the slope varies depending on the year.
+Because such a model is nested in a more simpler model where the study year is only an additive effect, all these models are fitted.
+Table \ref{anova.lme} displays model fit diagnostics.
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Fri Aug  2 14:33:01 2019
+\begin{table}[ht]
+\centering
+\begingroup\scriptsize
+\begin{tabular}{rrrrrrlrr}
+  \hline
+ & Model & df & AIC & BIC & logLik & Test & L.Ratio & p-value \\ 
+  \hline
+small.study.fit &   1 & 5.00 & 18230.52 & 18270.39 & -9110.26 &  &  &  \\ 
+  year.fit &   2 & 6.00 & 18231.61 & 18279.46 & -9109.81 & 1 vs 2 & 0.91 & 0.34 \\ 
+  year.int.fit &   3 & 7.00 & 18233.59 & 18289.40 & -9109.79 & 2 vs 3 & 0.03 & 0.87 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Anova table for three generalized linear model fits.
+'small.study.fit' denotes the model with the standard error as explanatory variable, 'year.fit' the model with standard error and the centered (- 2013) review year as explanatory variable, and 'year.int.fit' the model with interaction between the two.}
+\label{anova.lme}
+\end{table}
+
+Because neither AIC, BIC ot the F-test do show any improvement of model fit, it does not seem as if publication bias has substantially decreased or increased over the years.
+The review publication year is however not directly tied to the publication year of the studies that are affected by publication bias.
+Thus, using another measure of time, the results may be different.
+Thus, the models are re-fitted with the study publication years.
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Fri Aug  2 14:33:05 2019
+\begin{table}[ht]
+\centering
+\begingroup\scriptsize
+\begin{tabular}{rrrrrrlrr}
+  \hline
+ & Model & df & AIC & BIC & logLik & Test & L.Ratio & p-value \\ 
+  \hline
+small.study.fit &   1 & 5.00 & 18115.23 & 18155.05 & -9052.62 &  &  &  \\ 
+  year.fit &   2 & 6.00 & 18095.04 & 18142.83 & -9041.52 & 1 vs 2 & 22.19 & 0.00 \\ 
+  year.int.fit &   3 & 7.00 & 18096.90 & 18152.65 & -9041.45 & 2 vs 3 & 0.14 & 0.71 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Anova table for three generalized linear model fits.
+'Small study fit' denots the model with the standard error as explanatory variable, 'year.fit' the model with standard error and the centered (- 2000) study year as explanatory variable, and 'year.int.fit' the model with interaction between the two.}
+\label{anova.lme}
+\end{table}
+
+The analysis of model fit indicates that there is an improvement when using the study year as a covariate, but only as an additive effect.
+AIC and BIC are smaller and the $p$-value of the F-test is very small.
+However, not the size of the effect, but the slope of the linear regression fit would have to be decreased to ultimatively conclude a decrease of publication bias over the years.
 
@@
 
-%<<'child-chapter05', child='chapter05.Rnw'>>=
-%@
+% LaTeX file for Chapter 05
+
+\chapter{Discussion} \label{ch:Discussion}
+
+\section{Results in the light of the Literature}\label{sec:discussion.results}
+
+Before discussing the results of the previous analyses, some results of similar studies are discussed briefly and compared to the results of this study, if possible.
+When clear methodological drawbacks are found in the analysis, the reader is referred to chapter \ref{ch:methods} for comments on the disadvantages.
+The amount of studies analysing publication bias makes it not possible to discuss any of them, and thus we only some interesting and/or representative examples are shown.
+
+\subsection{\citet{Egger}}
+The Cochrane database (1996 issue 2) and publications from the four leading medicine journals (the Lancet, BMJ, JAMA and Annals of Internal Medicine) between 1993 and 1996 were used to find systematic reviews with randomized controlled trials for the application of Egger's small study effect test.
+They included 38 meta-analyses with at least 5 studies and binary outcomes from the Cochrane Library and 37 from the journals.
+Five (13\%) meta-analyses from Cochrane and 13 (38\%) from the journals had significant two sided small study effect test results ($p$-value < 0.1).
+Also, they found that test-statistics were more often negative, which correspondend in their setup to larger effects in small studies.
+(63.2 among Cochrane meta-analyses and 70.3 for journal meta-analyses).
+The results from this report with R\"ucker's test are: 14.8\%, and when using regression adjustment to decide about the direction of publication bias, we get 80.7\%.
+
+\subsection{\citet{sutton.2000}}
+Out of 397 systematic reviews from the Cochrane database (complete number for 1998, issue 3), 49 had more than ten included studies and binary outcomes and 48 compared two treatments.
+They were analysed by trim-and-fill method \citep{trimfill} to detect and adjust for funnel plot asymmetry (similar to small study effect tests, but the method is known to overestimate bias).
+23 were found to have missing studies, and eight had more than three missing studies which was considered to be significant publication bias.
+Additionally, they found that three estimates of random effects meta-analysis became non-significant after adjustment, and one became significant (by negative adjustment).
+The results are difficult to compare, but the methodological limitations make this findings unreliable.
+
+\subsection{\citet{Ioannidis2007}}
+Data processing steps were however different, and only binary outcomes as used in two-by-two tables were analysed.
+The approximately corresponding numbers are put in parentheses for comparison.
+The Cochrane Library from 2003 (issue 2) was used.
+After removal of duplicates and intractable meta-analyses, they had 6,873 meta-analyses with more than two studies left (20,219).
+When only using one meta-analysis per review, this reduced to 846 (3,555.
+Then, the criteria that have also been applied in this masters thesis are applied: $I^2 < 0.5$, variance ratio of smallest and largest effects > 4, at least one significant study result and at least 10 studies to be used.
+Afterwards, they applied Harbord's, Egger's and Begg's Test to the dataset.
+The reader can compare some corresponding numbers in Table \ref{ioannidis}.
+% The results seem to be similar enough to claim that neither the methods nor the data and it's results are differing substantially.
+Because the thesis relies on more data, it is likely to be more accurate and can possibly add to the findings of \citet{Ioannidis2007}.
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Fri Aug  2 14:33:49 2019
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrr}
+  \hline
+ & Ioannidis & Thesis \\ 
+  \hline
+Wider dataset (n) & 6873 & 20219 \\ 
+  study number $>$ 10 & 13\% & 12\% \\ 
+  variance ratio $>$ 4 & 72\% & 75\% \\ 
+  study sig. number $>$ 1 & 55\% & 52\% \\ 
+  all exclusion criteria & 5\% & 5\% \\ 
+  harbord test p-value $<$ 0.1 & 12\% & 16\% \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of results from Ioannidis et.al.
+(2007) to the results of the thesis.
+The percentage of meta-analysis which match all exclusion criteria denotes the ones that apply to all criteria in the table plus the small heterogeneity criterium.
+Harbord test is two-sided.}
+\label{ioannidis}
+\end{table}
+
+\subsection{\citet{souza.2007}}
+Reviews of the World Health Organization (WHO) Reproductive Health Library (RHL), issue 9, were analysed with the trim-and-fill method.
+The RHL reproduces and expands reviews from the Cochrane Library with implications for developping countries.
+21 of 105 reviews contained more than ten studies and were used.
+Trim-and-fill found asymmetry in 18 of 21 studies, and 10 had more than 3 missing studies (``significance'').
+Two of those and one with one missing studies found no evidence for treatment effects after the 0.05 $p$-value threshold after adjustment by trim-and-fill.
+
+\subsection{\citet{kicinsky}}
+The author uses a bayesian hierarchical selection model, but does not analyse treatment effects, but the parameters of the weight function of the selection model, which is estimated with a bayesian approach and MCMC sampling.
+\\
+The author provides an estimate of the probability of including significant findings versus non-significant findings in Cochrane meta-analyses over time.
+The data is from the Cochrane Library from 2013 (issue number not provided).
+The author excluded treatment - treatment comparisons and analysed safety and efficacy meta-analyses separately (how this was achieved is not documented in the paper).
+\\
+From 3845 reviews, the author separated 907 reviews with more than ten studies.
+From those, 539 compared placebo to treatment.
+After removing duplicates and sensitivity analyses, 358 analyses with 1297 meta-analyses remained.
+From these 191 were excluded because they comprised overall mortality and withdrawal, because these could not clearly be specified as safety or efficacy, respectively.
+\\
+1106 meta-analyses from 329 meta-analyses, containing 802 efficacy and 304 safety meta-analyses.
+The median publication year per meta-analysis was 1997 for efficacy meta-analyses and 1999 for safety meta-analyses.
+Then, a bayesian two-step hierarchical selection model was applied (\citet{bayesian.selection.model}, \citet{bayesian.selection.model.2}).
+It assumes that the selection process is a two-step weight, which assigns different probabilities to non-significant and significant effects.
+Thus, a ratio of publication probability between significant and non-significant study estimates using a two-step weight function.
+The model was fitted with the Monte-Carlo Markov-Chain algorithm STAN and the geometric mean was used as an estimate for the publication probability ratio.
+Simulations performed in \citep{bayesian.selection.model} indicate that the method performes well if the true mean effect size was not small, and also robust to small study effects.
+It outperformed Egger's test and Begg's test in assessing publication bias, especially when small study effects were absent, and had lower false-positive rates.
+\\
+The results showed a clear publication bias for significant results for efficacy meta-analyses (27\% higher for significant studies, 95\%CI credible intervals: 1.18 to 1.36).
+The probability was more than twice as high in 27\% of the meta-analyses (95\% CI: 23\% to 31\%).
+But the probability decreased: from 1.65 (95\% CI: 1.31 to 2.15) in 1980 (average publication year) to 1.36 (95\% CI: 1.17 to 1.62) in 1990 to 1.18 (95\% CI: 1.04 to 1.33) in 2000.
+For sake of completeness, the probability of inclusion was  1.78 (95\% CI: 1.51 to 2.13) larger for non-significant safety effect estimates, but again, decreased with time (1.77, 95\% CI: 1.46 to 2.21 in 2000).
+The results are in line with the results from this study, but it was not possible to reafirm the finding of weaker publication bias in reviews published more frequently.\\
+
+\subsection{\citet{vanAert.2019}}
+The Authors of this recent study sample 366 meta-analyses randomly from the Cochrane Library (supposedly 2018 or 2019, not mentioned).
+They exclude any meta-analysis which include effect sizes identical to effect sizes in other meta-analyses (the larger meta-analysis is retained).
+Additional criteria were: $I^2 < 0.5$ and at least 5 studies.
+The meta-analyses were analysed using standardized mean differences and four different tests for publication bias: Egger's test, p-uniform test \citep{p.uniform}, Begg and Mazumdar's rank correlation test and the excess significance test.
+\\
+The authors found, based on the significance threshold of $p$ < 0.1, the following results (own results in brackets):
+12.2 \% significant results from Egger's test (16.3),
+8.5 \% significant results from Begg and Mazumdar's rank correlation test (10.5) and
+4.4 \% significant excess significance test results (9.7).
+It is known that the publication bias tests are lacking power in general as sample size is usually small.
+Decreasing sample size will result in lower power, especially if the maximal sample size is $n \geq 5$.
+Additionally, it was also not taken into consideration that it may be difficult to state that publication bias is present in a meta-analysis when no result within it is statistically significant (only 18.8 \% of the effects of the sampled meta-analyses were).
+This, together that it has not been tried to exclude safety outcomes, may account for the large differences between the results.
+\\
+The author's come to the conclusion in their study that in contrast to other studies, they find few evidence for publication
+
+\subsection{Further Studies on Publication Bias}
+\citet{Zhang.2013} find publication bias in critical care studies with similar methods.
+\citet{Nusch} report publication bias in clinical osteoarthritis research because of funnel plot asymmetry and pledge for routine assessment of publication bias.
+\citet{Dechartres.2013} analyse publication bias based on sample size in meta-analyses from top journals and Cochrane reviews in 93 Meta-analyses and find that, for example, effects in trials with less than 50 patients were 48\% larger than in larger trials.
+\citet{Onishi.2014} find that in 36 Meta-Analyses without comprehensive literature research, there ar 19.4\% significant publication bias tests (Egger's test).
+
+\section{Interpretation}
+In this study, a proportion of the meta-analyses that have been scrutinized have publication bias.
+Since regression and rank test have been applied one-sided, they have very likely larger effects in smaller studies that in larger studies.
+\\
+There have been proposed a number of reasons for this tendencies in smaller studies (see \citet{Egger} for a thorough discussion).
+In clinical settings, it might be that the requirement for more study participants in large studies might systematically change the study population.
+However, this systematic differences could influence the results in two ways: If recruitement of participants with a disease is difficult, and thus, also participants with less severe types of the disease are included, it might be that the effect of treatment is larger in the smaller study.
+But one could also argue that the opposite could eventually be the case.
+\\
+The main cause for funnel plot asymmetry with smaller studies having larger effects is publication bias.
+Publication bias enforces questionable research practices from researchers such as selective outcome reporting, $p$-hacking and data fabrication.
+Larger studies are less affected, and have also in general higher methodological quality \citep{Egger}, which leads to smaller effect sizes.\\
+Presence of publication bias in meta-analyses can ultimately lead to patient harm, because decision makers in clinical practice use the meta-analyses to take decisions if they use a treatment.
+On the swiss Cochrane website, it is stated that Cochrane is the ``single most reliable source of evidence on the effects of health care''.
+However, publication bias does in general lead to too large confidence in the results of the meta-analyses.
+In some cases, it might be that the  evidence for a treatment in a meta-analysis is an artifact of publication bias.
+Besides harm to patient, this can cause a waste of ressources.
+\\
+The comparison of the results with previous analyses of publication bias in the Cochrane Database of Systematic Reviews implies gives more confidence in the results of this study, because they are largely in line.
+\\
+
+\section{Limitations}
+After application of the criteria of \citet{Ioannidis2007}, there are left 11.6 \% of the reviews and 32.9\% of the studies.
+It is not clear how the results would be in the remaining dataset if tests were applicable.
+The most restrictive criterium of exclusion was that a meta-analysis has to have at least ten studies.
+Thus, in the data that is scrutinized, there has been enforced and ongoing research.
+\citet{ioannidis.2005} state that publication bias is also a consequence of modern discovery oriented research, and thus it may well be that publication bias is also an issue when the number of studies are lower.\\
+It also has to be said that the removal of safety outcomes is only partially successfull.
+This is an issue, because it is not well known if and how publication bias affect safety outcomes.
+\citet{kicinsky} suggests that they are inversely affected, with editors publishing in favor of non-significant adverse effects.
+\\
+Also, it has been previously discussed that the method to detect the side on which bias is to be expected can fail and provide meaningless results, in which case a two-sided test is more meaningful.
+However, one could also discuss in more general terms if one can speak of publication bias in meta-analyses that have only one significant effect out of ten ($n$ = 417).
+\\
+There is also criticism that one can address on the methods.
+It is possible that the results are caused by systematic differences in the population of study participants only.
+This is considered rather unlikely.
+Other cirticism is more severe.
+The small study effect tests fail to account for statistical significance, however, this is a major component of publication bias.
+Small study effect test work because they take into account that smaller studies need larger effects to be significant.
+The only test that is applied that takes into account statistical significance per se is the excess significance test.
+When looking at it's results, it seems as if it is rather a test for between study heterogeneity per se, because it does agree very poorly with small study effect tests, and finds almost no excess significance in tests with $I^2 = 0$.
+The choice of the effect size and proxy of the study size is crucial when assessing publication bias.
+It is not clear which measure of effect size should be used when applying the test; the original measure (\eg a mean difference) may have standard errors that do not only depend on study size, but journal editors use this measure as the basis for their decision of publication.
+Fisher's $z$ transformed correlations have standard errors that are a function of study participant number only, but in contrast the effect size is bounded at$[-1,1]$, making it less suitable for linear regression.
+Standardized mean differences are possibly a good compromise.\\
+The ciriticism also applies for adjustment methods, as they also do not use statistical significance but the size of the effects.
+A weakness of the regression adjustment is that it also adjusts if the uncertainity in the small study effect is large.
+To compare it in this case with the meta-analysis estimate is difficult because the uncertainity in estimating the small study effect affects the uncertainity of the treatment effect.
+It is not clear how to proceed when one wants to adjust for publication bias.
+Copas selection model uses the $p$-value threshold of 0.1 to decide if adjustment is necessary or not.
+One can argue that this threshold is arbitrary.
+Additionally, the threshold is used in two manners: first to decide if adjustment is necessary at all, and secondly, if the adjusted model does suitably account for publication bias ($p$ > 0.1).
+Hypothesis tests against the null hypothesis can however not be used to decide in favor of the null-hypothesis, and a separate test would be needed there.
+\\
+With Copas selection model, it is in general the issue that it the model is not estimating, but rather applying some criteria of parsimony (the model with least publication bias with $p$-value for small study effect > 0.1 is chosen).
+Some authors find in their simulation studies that regression methods overperform the Copas selection model \citep{limitmeta}.
+\\
+Thus, the results are not exact and could be improved if more suitable methods are applied.
+The bayesian approach taken by \citet{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions.
+\\
+
+\section{Outlook}
+Given the size and abundancy of information in the dataset, the possibilities to investigate sources of bias in the Cochrane Database of Systematic Reviews are not exhausted (see for example in \citet{ioannidis.2017}).
+In particular, one could easily come up with more hypotheses that could be tested in meta meta-regression, as introduced in the last section of the results.
+\\
+There are numerous suggestions for diffeerent measures of publication bias and small study effects, which could be applied on the dataset (see \citet{mueller.2016}).
+This study mainly relies on suggestions from \citet{Sterne}, \citet{Ioannidis2007} and \citet{limitmeta}.
+It uses most often methods that are well integrated in packages (\citet{metafor.package}, \citet{meta.package}).
+Although there are well addressed, mathematical justifications for these methods, there might be better methods not yet tested on large datasets.
+An evaluation of all suggested methods was far beyond the scope of this study.
+
+\section{Implications}
+This study is so far the largest assessment of publication bias by small study effects and uses data that has been collected after major efforts have been made to curb publication bias.
+The results indicate, similarly to other studies, that the efforts did not yet resolve the issue.
+\\
+The findings further imply that when using meta-analyses, it is key to investigate sources of between-study heterogeneity; an alternative is to rely solely on the largest trials \citep{largest.study.only}.
+Since the Cochrane Organization uses results from grey literature to limit the effects of publication bias, but still does not manage to abolish it, there is also the need for journal editors to change their publication policies.
 
@@
 
-Maybe some R code here, probably a \rr{sessionInfo()}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlkwd{sessionInfo}\hlstd{()}
+\end{alltt}
+\begin{verbatim}
+## R version 3.5.1 (2018-07-02)
+## Platform: x86_64-apple-darwin15.6.0 (64-bit)
+## Running under: macOS  10.14.4
+## 
+## Matrix products: default
+## BLAS: /Library/Frameworks/R.framework/Versions/3.5/Resources/lib/libRblas.0.dylib
+## LAPACK: /Library/Frameworks/R.framework/Versions/3.5/Resources/lib/libRlapack.dylib
+## 
+## locale:
+## [1] en_US.UTF-8/en_US.UTF-8/en_US.UTF-8/C/en_US.UTF-8/en_US.UTF-8
+## 
+## attached base packages:
+## [1] stats     graphics  grDevices utils     datasets  methods   base     
+## 
+## other attached packages:
+##  [1] nlme_3.1-137    corrgram_1.13   bindrcpp_0.2.2  rvest_0.3.2    
+##  [5] xml2_1.2.0      xtable_1.8-3    metafor_2.1-0   Matrix_1.2-15  
+##  [9] gridExtra_2.3   metasens_0.3-2  meta_4.9-4      forcats_0.3.0  
+## [13] stringr_1.3.1   dplyr_0.7.8     purrr_0.2.5     readr_1.2.1    
+## [17] tidyr_0.8.2     tibble_1.4.2    ggplot2_3.1.0   tidyverse_1.2.1
+## [21] testit_0.9      knitr_1.20     
+## 
+## loaded via a namespace (and not attached):
+##  [1] Rcpp_1.0.0         lubridate_1.7.4    lattice_0.20-38   
+##  [4] gtools_3.8.1       assertthat_0.2.0   digest_0.6.18     
+##  [7] foreach_1.4.4      R6_2.3.0           cellranger_1.1.0  
+## [10] plyr_1.8.4         backports_1.1.2    evaluate_0.12     
+## [13] httr_1.3.1         highr_0.7          pillar_1.3.0      
+## [16] gplots_3.0.1.1     rlang_0.3.0.1      lazyeval_0.2.1    
+## [19] readxl_1.1.0       gdata_2.18.0       rstudioapi_0.8    
+## [22] labeling_0.3       munsell_0.5.0      broom_0.5.0       
+## [25] compiler_3.5.1     modelr_0.1.2       pkgconfig_2.0.2   
+## [28] tidyselect_0.2.5   seriation_1.2-7    codetools_0.2-15  
+## [31] dendextend_1.12.0  viridisLite_0.3.0  crayon_1.3.4      
+## [34] withr_2.1.2        bitops_1.0-6       MASS_7.3-51.1     
+## [37] grid_3.5.1         jsonlite_1.5       gtable_0.2.0      
+## [40] registry_0.5-1     magrittr_1.5       scales_1.0.0      
+## [43] KernSmooth_2.23-15 cli_1.0.1          stringi_1.2.4     
+## [46] viridis_0.5.1      iterators_1.0.10   tools_3.5.1       
+## [49] glue_1.3.0         gclus_1.3.2        hms_0.4.2         
+## [52] colorspace_1.3-2   cluster_2.0.7-1    caTools_1.17.1.1  
+## [55] TSP_1.1-7          bindr_0.1.1        haven_2.0.0
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\section{Data Pre-processing}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlcom{#Dataset processing function to get transformed effect sizes, p-values, event }
+\hlcom{# counts with increments, etc. :}
+\hlstd{pb.process3} \hlkwb{<-} \hlkwa{function}\hlstd{(}\hlkwc{data}\hlstd{)\{}
+  \hlstd{data} \hlkwb{<-} \hlstd{data} \hlopt{%>%} \hlkwd{mutate}\hlstd{(}\hlkwc{meta.id} \hlstd{=}
+            \hlkwd{group_indices}\hlstd{(., id, comparison.id, outcome.id, subgroup.id))} \hlopt{%>%}
+    \hlkwd{group_by}\hlstd{(meta.id)} \hlopt{%>%} \hlkwd{mutate}\hlstd{(}\hlkwc{study.id2} \hlstd{=} \hlkwd{row_number}\hlstd{())} \hlopt{%>%} \hlkwd{ungroup}\hlstd{()}
+
+  \hlcom{#Mark duplicate effects between meta-analyses:}
+  \hlstd{data} \hlkwb{<-} \hlstd{data} \hlopt{%>%} \hlkwd{group_by}\hlstd{(meta.id)} \hlopt{%>%}
+    \hlkwd{mutate}\hlstd{(}\hlkwc{n} \hlstd{=} \hlkwd{n}\hlstd{())}  \hlopt{%>%} \hlkwd{ungroup}\hlstd{()} \hlopt{%>%} \hlkwd{group_by}\hlstd{(id)} \hlopt{%>%}
+    \hlkwd{mutate}\hlstd{(}\hlkwc{dupl.id} \hlstd{=}
+         \hlkwd{dupl.finder}\hlstd{(}\hlkwc{effects} \hlstd{= effect,} \hlkwc{names} \hlstd{= study.name,} \hlkwc{metas} \hlstd{= meta.id),}
+           \hlkwc{dupl.remove} \hlstd{=}
+  \hlkwd{dupl.max.finder}\hlstd{(}\hlkwc{duplicate.index} \hlstd{= dupl.id,} \hlkwc{study.number} \hlstd{= n,} \hlkwc{metas} \hlstd{= meta.id))} \hlopt{%>%}
+    \hlkwd{ungroup}\hlstd{()}
+
+  \hlstd{data} \hlkwb{<-} \hlstd{data} \hlopt{%>%} \hlkwd{mutate}\hlstd{(}\hlkwc{lrr} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{var.lrr} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{hedgesg} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{var.hedgesg} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{cohensd} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{var.cohensd} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{smd.ordl} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{var.smd.ordl} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{pval.single} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{cor.pearson} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{var.cor.pearson} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{z} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{var.z} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{events1c} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{events2c} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{sig.single} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{smd.pool} \hlstd{=} \hlnum{NA}\hlstd{,}
+    \hlkwc{se.smd.pool} \hlstd{=} \hlnum{NA}\hlstd{)}
+
+  \hlstd{cont.ind} \hlkwb{<-} \hlkwd{which}\hlstd{(data}\hlopt{$}\hlstd{outcome.flag} \hlopt{==} \hlstr{"CONT"}\hlstd{)}
+  \hlstd{bin.ind} \hlkwb{<-} \hlkwd{which}\hlstd{(data}\hlopt{$}\hlstd{outcome.flag} \hlopt{==} \hlstr{"DICH"}\hlstd{)}
+  \hlstd{IV.ind} \hlkwb{<-} \hlkwd{which}\hlstd{(data}\hlopt{$}\hlstd{outcome.flag} \hlopt{==} \hlstr{"IV"}\hlstd{)}
+  \hlcom{#----------------------------------------------------------------------------------------------#}
+
+  \hlcom{#Outcome.flag == "DICH"}
+  \hlstd{data[bin.ind,]} \hlkwb{<-} \hlkwd{escalc}\hlstd{(}\hlkwc{data} \hlstd{= data[bin.ind,],} \hlkwc{ai} \hlstd{= events1,} \hlkwc{n2i} \hlstd{= total2,}
+                           \hlkwc{ci} \hlstd{= events2,} \hlkwc{n1i} \hlstd{= total1,}
+                           \hlkwc{to} \hlstd{=} \hlstr{"only0"}\hlstd{,}
+                           \hlkwc{add} \hlstd{=} \hlnum{1}\hlopt{/}\hlnum{2}\hlstd{,}
+                           \hlkwc{measure} \hlstd{=} \hlstr{"RR"}\hlstd{,} \hlkwc{append} \hlstd{= T,}
+                      \hlkwc{var.names} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"lrr"}\hlstd{,} \hlstr{"var.lrr"}\hlstd{))} \hlcom{#Calculate Risk Ratios}
+
+  \hlstd{data[bin.ind,]} \hlkwb{<-} \hlkwd{escalc}\hlstd{(}\hlkwc{data} \hlstd{= data[bin.ind,],} \hlkwc{ai} \hlstd{= events1,} \hlkwc{n2i} \hlstd{= total2,}
+                           \hlkwc{ci} \hlstd{= events2,} \hlkwc{n1i} \hlstd{= total1,}
+                           \hlkwc{to} \hlstd{=} \hlstr{"only0"}\hlstd{,}
+                           \hlkwc{add} \hlstd{=} \hlnum{1}\hlopt{/}\hlnum{2}\hlstd{,}
+                           \hlkwc{measure} \hlstd{=} \hlstr{"OR2DL"}\hlstd{,} \hlkwc{append} \hlstd{= T,}
+  \hlkwc{var.names} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"smd.ordl"}\hlstd{,} \hlstr{"var.smd.ordl"}\hlstd{))} \hlcom{#Calculate SMD (w. logistic transf.)}
+
+  \hlcom{#What to do if there are 0/total cells:}
+  \hlstd{data[bin.ind,]} \hlkwb{<-} \hlstd{data[bin.ind,]} \hlopt{%>%}
+    \hlkwd{mutate}\hlstd{(}\hlkwc{events1c}  \hlstd{=} \hlkwd{case_when}\hlstd{(events1} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events1} \hlopt{+} \hlnum{0.5}\hlstd{,}
+                                 \hlstd{events2} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events1} \hlopt{+} \hlnum{0.5}\hlstd{,}
+                                 \hlstd{events1} \hlopt{-} \hlstd{total1} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events1} \hlopt{-} \hlnum{0.5}\hlstd{,}
+                                 \hlstd{events2} \hlopt{-} \hlstd{total2} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events1} \hlopt{-} \hlnum{0.5}\hlstd{,}
+                                 \hlnum{TRUE} \hlopt{~} \hlstd{events1),}
+           \hlkwc{events2c} \hlstd{=} \hlkwd{case_when}\hlstd{(events2} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events2} \hlopt{+} \hlnum{0.5}\hlstd{,}
+                                \hlstd{events1} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events2} \hlopt{+} \hlnum{0.5}\hlstd{,}
+                                \hlstd{events2} \hlopt{-} \hlstd{total2} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events2} \hlopt{-} \hlnum{0.5}\hlstd{,}
+                                \hlstd{events1} \hlopt{-} \hlstd{total1} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events2} \hlopt{-} \hlnum{0.5}\hlstd{,}
+                                \hlnum{TRUE} \hlopt{~} \hlstd{events2))}
+
+  \hlcom{#What to do if there is one zero and one total:}
+  \hlstd{data[bin.ind,]} \hlkwb{<-} \hlstd{data[bin.ind,]} \hlopt{%>%}
+    \hlkwd{mutate}\hlstd{(}\hlkwc{events1c}  \hlstd{=} \hlkwd{case_when}\hlstd{(events2} \hlopt{==} \hlnum{0} \hlopt{&} \hlstd{events1} \hlopt{-} \hlstd{total1} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events1,}
+                                 \hlstd{events1} \hlopt{==} \hlnum{0} \hlopt{&} \hlstd{events2} \hlopt{-} \hlstd{total2} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events1,}
+                                 \hlnum{TRUE} \hlopt{~} \hlstd{events1c),}
+           \hlkwc{events2c} \hlstd{=} \hlkwd{case_when}\hlstd{(events2} \hlopt{==} \hlnum{0} \hlopt{&} \hlstd{events1} \hlopt{-} \hlstd{total1} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events2,}
+                                \hlstd{events1} \hlopt{==} \hlnum{0} \hlopt{&} \hlstd{events2} \hlopt{-} \hlstd{total2} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events2,}
+                                \hlnum{TRUE} \hlopt{~} \hlstd{events2c))}
+  \hlstd{data[bin.ind,} \hlstr{"pval.single"}\hlstd{]} \hlkwb{<-} \hlstd{data[bin.ind, ]} \hlopt{%>%}
+    \hlkwd{mutate}\hlstd{(}\hlkwc{pval.single} \hlstd{=} \hlnum{2}\hlopt{*}\hlstd{(}\hlnum{1}\hlopt{-}\hlkwd{pnorm}\hlstd{(}\hlkwd{abs}\hlstd{(lrr}\hlopt{/}\hlkwd{sqrt}\hlstd{(var.lrr)))))} \hlopt{%>%} \hlkwd{select}\hlstd{(pval.single)}
+  \hlcom{#----------------------------------------------------------------------------------------------#}
+
+  \hlcom{#Outcome.flag == "CONT"}
+  \hlstd{data[cont.ind,]} \hlkwb{<-} \hlkwd{escalc}\hlstd{(}\hlkwc{data} \hlstd{= data[cont.ind,],} \hlkwc{m1i} \hlstd{= mean1,} \hlkwc{m2i} \hlstd{= mean2,}
+                            \hlkwc{sd1i} \hlstd{= sd1,} \hlkwc{sd2i} \hlstd{= sd2,} \hlkwc{n1i} \hlstd{= total1,} \hlkwc{n2i} \hlstd{= total2,}
+                            \hlkwc{measure} \hlstd{=} \hlstr{"SMD"} \hlstd{,} \hlkwc{append} \hlstd{= T,}
+                \hlkwc{var.names} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"hedgesg"}\hlstd{,} \hlstr{"var.hedgesg"}\hlstd{))} \hlcom{#Calculate Hedge's g}
+
+  \hlstd{data[cont.ind, ]} \hlkwb{<-} \hlstd{data[cont.ind, ]} \hlopt{%>%}
+    \hlkwd{mutate}\hlstd{(}\hlkwc{cohensd} \hlstd{= (mean1} \hlopt{-} \hlstd{mean2)}\hlopt{/}\hlkwd{sqrt}\hlstd{((((total1} \hlopt{-} \hlnum{1}\hlstd{)}\hlopt{*}\hlstd{sd1}\hlopt{^}\hlnum{2}\hlstd{)} \hlopt{+}
+                    \hlstd{(total2} \hlopt{-} \hlnum{1}\hlstd{)}\hlopt{*}\hlstd{sd2}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}\hlstd{(total1} \hlopt{+} \hlstd{total2} \hlopt{-} \hlnum{2}\hlstd{)),}
+           \hlkwc{var.cohensd} \hlstd{= ((total1} \hlopt{+} \hlstd{total2)}\hlopt{/}\hlstd{(total1} \hlopt{*} \hlstd{total2))} \hlopt{+}
+             \hlstd{(cohensd}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}\hlstd{(}\hlnum{2}\hlopt{*}\hlstd{(total1} \hlopt{+} \hlstd{total2)))}
+
+  \hlstd{data[cont.ind, ]} \hlkwb{<-} \hlstd{data[cont.ind, ]} \hlopt{%>%}
+    \hlkwd{mutate}\hlstd{(}\hlkwc{cohensd} \hlstd{=} \hlkwd{case_when}\hlstd{(sd1} \hlopt{==} \hlnum{0} \hlopt{~} \hlnum{NA_real_}\hlstd{,}
+                               \hlstd{sd2} \hlopt{==} \hlnum{0} \hlopt{~} \hlnum{NA_real_}\hlstd{,}
+                               \hlstd{total2} \hlopt{==} \hlnum{0} \hlopt{~} \hlnum{NA_real_}\hlstd{,}
+                               \hlstd{total1} \hlopt{==} \hlnum{0} \hlopt{~} \hlnum{NA_real_}\hlstd{,}
+                               \hlnum{TRUE} \hlopt{~} \hlstd{cohensd))}
+
+  \hlcom{#p-value for continuous outcomes (Student):}
+  \hlstd{data[cont.ind,} \hlstr{"pval.single"}\hlstd{]} \hlkwb{<-} \hlstd{data[cont.ind, ]} \hlopt{%>%}
+    \hlkwd{mutate}\hlstd{(}\hlkwc{t} \hlstd{= (mean1} \hlopt{-} \hlstd{mean2)}\hlopt{/}\hlstd{(}\hlkwd{sqrt}\hlstd{((((total1}\hlopt{-}\hlnum{1}\hlstd{)}\hlopt{*}\hlstd{sd1}\hlopt{^}\hlnum{2}\hlstd{)} \hlopt{+} \hlstd{(total2}\hlopt{-}\hlnum{1}\hlstd{)}\hlopt{*}\hlstd{sd2}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}
+                          \hlstd{(total1} \hlopt{+} \hlstd{total2} \hlopt{-}\hlnum{2}\hlstd{))}\hlopt{*}\hlkwd{sqrt}\hlstd{((}\hlnum{1}\hlopt{/}\hlstd{total1)}\hlopt{+}\hlstd{(}\hlnum{1}\hlopt{/}\hlstd{total2))),}
+           \hlkwc{pval.single} \hlstd{=} \hlnum{2}\hlopt{*}\hlstd{(}\hlnum{1}\hlopt{-}\hlkwd{pt}\hlstd{(}\hlkwd{abs}\hlstd{(t),} \hlkwc{df} \hlstd{= total1} \hlopt{+} \hlstd{total2} \hlopt{-} \hlnum{2}\hlstd{)))} \hlopt{%>%}
+    \hlkwd{select}\hlstd{(pval.single)}
+
+  \hlstd{sd1.0} \hlkwb{<-} \hlkwd{which}\hlstd{(data}\hlopt{$}\hlstd{outcome.flag} \hlopt{==} \hlstr{"CONT"} \hlopt{&} \hlstd{data}\hlopt{$}\hlstd{sd1} \hlopt{==} \hlnum{0}\hlstd{)}
+  \hlstd{sd2.0} \hlkwb{<-} \hlkwd{which}\hlstd{(data}\hlopt{$}\hlstd{outcome.flag} \hlopt{==} \hlstr{"CONT"} \hlopt{&} \hlstd{data}\hlopt{$}\hlstd{sd2} \hlopt{==} \hlnum{0}\hlstd{)}
+  \hlstd{sd.0} \hlkwb{<-} \hlkwd{union}\hlstd{(sd1.0, sd2.0)}
+  \hlstd{data[sd.0,} \hlstr{"pval.single"}\hlstd{]} \hlkwb{<-} \hlnum{NA} \hlcom{#Such that p-value here is not equal to zero}
+  \hlcom{#----------------------------------------------------------------------------------------------#}
+
+  \hlcom{#Outcome.flag == "IV"}
+  \hlstd{data[IV.ind,} \hlstr{"pval.single"}\hlstd{]} \hlkwb{<-} \hlstd{data[IV.ind, ]} \hlopt{%>%}
+    \hlkwd{mutate}\hlstd{(}\hlkwc{pval.single} \hlstd{=} \hlnum{2}\hlopt{*}\hlstd{(}\hlnum{1}\hlopt{-}\hlkwd{pnorm}\hlstd{(}\hlkwd{abs}\hlstd{((effect)}\hlopt{/}\hlstd{se))))} \hlopt{%>%}
+    \hlkwd{select}\hlstd{(pval.single)}
+  \hlcom{#----------------------------------------------------------------------------------------------#}
+
+  \hlcom{#Declare smd.ordl, cohensd and SMD of IV flag all as "smd.pool":}
+  \hlstd{data} \hlkwb{<-} \hlstd{data} \hlopt{%>%}
+    \hlkwd{mutate}\hlstd{(}\hlkwc{smd.pool} \hlstd{=} \hlkwd{case_when}\hlstd{(outcome.flag} \hlopt{==} \hlstr{"DICH"} \hlopt{~} \hlstd{smd.ordl,}
+                                \hlstd{outcome.flag} \hlopt{==} \hlstr{"CONT"} \hlopt{~} \hlstd{cohensd,}
+                                \hlstd{outcome.flag} \hlopt{==} \hlstr{"IV"} \hlopt{&}
+                                  \hlstd{outcome.measure.merged} \hlopt{==} \hlstr{"SMD"} \hlopt{~} \hlstd{effect,}
+                                \hlnum{TRUE} \hlopt{~} \hlnum{NA_real_}\hlstd{),}
+           \hlkwc{se.smd.pool} \hlstd{=} \hlkwd{case_when}\hlstd{(outcome.flag} \hlopt{==} \hlstr{"DICH"} \hlopt{~} \hlkwd{sqrt}\hlstd{(var.smd.ordl),}
+                                   \hlstd{outcome.flag} \hlopt{==} \hlstr{"CONT"} \hlopt{~} \hlkwd{sqrt}\hlstd{(var.cohensd),}
+                                   \hlstd{outcome.flag} \hlopt{==} \hlstr{"IV"} \hlopt{&}
+                                     \hlstd{outcome.measure.merged} \hlopt{==} \hlstr{"SMD"} \hlopt{~} \hlstd{se,}
+                                   \hlnum{TRUE} \hlopt{~} \hlnum{NA_real_}\hlstd{))}
+  \hlcom{#----------------------------------------------------------------------------------------------#}
+
+  \hlcom{#Transform effect sizes:}
+  \hlstd{smd.pool.ind} \hlkwb{<-} \hlkwd{which}\hlstd{(}\hlopt{!}\hlkwd{is.na}\hlstd{(data}\hlopt{$}\hlstd{smd.pool))}
+
+  \hlcom{#Pearson correlation:}
+  \hlstd{data[smd.pool.ind,} \hlstr{"cor.pearson"}\hlstd{]}\hlkwb{<-} \hlstd{data[smd.pool.ind, ]} \hlopt{%>%} \hlkwd{mutate}\hlstd{(}
+    \hlkwc{a} \hlstd{= ((total1} \hlopt{+} \hlstd{total2)}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}\hlstd{(total1}\hlopt{*}\hlstd{total2),}
+    \hlkwc{cor.pearson}  \hlstd{= smd.pool}\hlopt{/}\hlkwd{sqrt}\hlstd{((smd.pool}\hlopt{^}\hlnum{2}\hlstd{)} \hlopt{+} \hlstd{a),}
+    \hlkwc{var.cor.pearson} \hlstd{= ((a}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{*}\hlstd{se.smd.pool}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}\hlstd{(((smd.pool}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{+}\hlstd{a)}\hlopt{^}\hlnum{3}\hlstd{))} \hlopt{%>%}
+    \hlkwd{select}\hlstd{(cor.pearson)}
+
+  \hlstd{data[smd.pool.ind,} \hlstr{"var.cor.pearson"}\hlstd{]}\hlkwb{<-} \hlstd{data[smd.pool.ind, ]} \hlopt{%>%}
+    \hlkwd{mutate}\hlstd{(}
+    \hlkwc{a} \hlstd{= ((total1} \hlopt{+} \hlstd{total2)}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}\hlstd{(total1}\hlopt{*}\hlstd{total2),}
+    \hlkwc{cor.pearson}  \hlstd{= smd.pool}\hlopt{/}\hlkwd{sqrt}\hlstd{((smd.pool}\hlopt{^}\hlnum{2}\hlstd{)} \hlopt{+} \hlstd{a),}
+    \hlkwc{var.cor.pearson} \hlstd{= ((a}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{*}\hlstd{se.smd.pool}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}\hlstd{(((smd.pool}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{+}\hlstd{a)}\hlopt{^}\hlnum{3}\hlstd{))} \hlopt{%>%}
+    \hlkwd{select}\hlstd{(var.cor.pearson)}
+
+  \hlcom{#Fisher's z-score:}
+  \hlstd{data[smd.pool.ind,} \hlstr{"z"}\hlstd{]} \hlkwb{<-} \hlstd{data[smd.pool.ind, ]} \hlopt{%>%}
+    \hlkwd{mutate}\hlstd{(}\hlkwc{z} \hlstd{=} \hlkwd{atan}\hlstd{(}\hlkwc{x} \hlstd{= cor.pearson),}
+           \hlkwc{var.z}\hlstd{=} \hlnum{1}\hlopt{/}\hlstd{(total1} \hlopt{+} \hlstd{total2} \hlopt{-} \hlnum{3}\hlstd{))} \hlopt{%>%} \hlkwd{select}\hlstd{(z)}
+  \hlstd{data[smd.pool.ind,} \hlstr{"var.z"}\hlstd{]} \hlkwb{<-} \hlstd{data[smd.pool.ind, ]} \hlopt{%>%}
+    \hlkwd{mutate}\hlstd{(}\hlkwc{z} \hlstd{=} \hlkwd{atan}\hlstd{(}\hlkwc{x} \hlstd{= cor.pearson),}
+           \hlkwc{var.z}\hlstd{=} \hlnum{1}\hlopt{/}\hlstd{(total1} \hlopt{+} \hlstd{total2} \hlopt{-} \hlnum{3}\hlstd{))} \hlopt{%>%} \hlkwd{select}\hlstd{(var.z)}
+
+  \hlcom{#----------------------------------------------------------------------------------------------#}
+  \hlstd{data}\hlopt{$}\hlstd{sig.single} \hlkwb{<-} \hlkwd{ifelse}\hlstd{(data}\hlopt{$}\hlstd{pval.single} \hlopt{<} \hlnum{0.05}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{0}\hlstd{)}
+
+  \hlkwd{return}\hlstd{(data)}
+\hlstd{\}}
+
+\hlcom{########################################################################################################}
+
+\hlcom{#Function to find sensitivity analyses.  The function gives all meta-analyses }
+\hlcom{#that are subdivided}
+\hlcom{#into sensitivity analyses a common number. }
+\hlcom{#*to use with "data %>% mutate(.. = dupl.finder(..))"*}
+\hlstd{dupl.finder} \hlkwb{<-} \hlkwa{function}\hlstd{(}\hlkwc{effects}\hlstd{,} \hlkwc{names}\hlstd{,} \hlkwc{metas}\hlstd{)\{}
+
+  \hlstd{results} \hlkwb{<-} \hlkwd{rep}\hlstd{(}\hlnum{NA}\hlstd{,} \hlkwc{times} \hlstd{=} \hlkwd{length}\hlstd{(effects))}
+  \hlstd{meta.double.marker} \hlkwb{<-} \hlnum{1}
+
+  \hlkwa{for}\hlstd{(u} \hlkwa{in} \hlkwd{seq_along}\hlstd{(effects))\{}
+
+    \hlkwa{if}\hlstd{(}\hlkwd{is.na}\hlstd{(results[u]))\{}
+
+      \hlstd{double.indices} \hlkwb{<-} \hlkwd{which}\hlstd{(effects[u]} \hlopt{==} \hlstd{effects} \hlopt{&} \hlstd{names[u]} \hlopt{==} \hlstd{names)}
+
+      \hlkwa{if}\hlstd{(}\hlkwd{length}\hlstd{(double.indices)} \hlopt{>} \hlnum{1}\hlstd{)\{}
+    \hlcom{#If any meta-analysis has already duplicates, give all the same double marker}
+        \hlkwa{if}\hlstd{(}\hlkwd{any}\hlstd{(}\hlopt{!}\hlkwd{is.na}\hlstd{(results[double.indices])))\{}
+
+          \hlstd{already.marked} \hlkwb{<-} \hlkwd{which}\hlstd{(}\hlopt{!}\hlkwd{is.na}\hlstd{(results[double.indices]))}
+          \hlstd{meta.double.marker.2} \hlkwb{<-} \hlkwd{unique}\hlstd{(results[double.indices[already.marked]])}
+          \hlcom{#Collect meta.ids with same double markers}
+          \hlstd{meta.ids.2} \hlkwb{<-} \hlkwd{unique}\hlstd{(metas[}\hlkwd{which}\hlstd{(results} \hlopt{%in%} \hlstd{meta.double.marker.2)])}
+          \hlstd{meta.ids} \hlkwb{<-} \hlstd{metas[double.indices]} \hlcom{#Collect metas with the same results}
+
+          \hlstd{meta.ids.pooled} \hlkwb{<-} \hlkwd{union}\hlstd{(meta.ids, meta.ids.2)}
+          \hlstd{meta.indices} \hlkwb{<-} \hlkwd{which}\hlstd{(metas} \hlopt{%in%} \hlstd{meta.ids.pooled)}
+          \hlstd{results[meta.indices]} \hlkwb{<-} \hlstd{meta.double.marker}
+
+        \hlstd{\}} \hlkwa{else}\hlstd{\{}
+
+          \hlstd{meta.ids} \hlkwb{<-} \hlstd{metas[double.indices]}
+          \hlstd{meta.indices} \hlkwb{<-} \hlkwd{which}\hlstd{(metas} \hlopt{%in%} \hlstd{meta.ids)}
+          \hlstd{results[meta.indices]} \hlkwb{<-} \hlstd{meta.double.marker}
+
+        \hlstd{\}}
+      \hlstd{\}} \hlkwa{else} \hlstd{results[u]} \hlkwb{<-} \hlnum{0}
+
+      \hlstd{meta.double.marker} \hlkwb{<-} \hlstd{meta.double.marker} \hlopt{+} \hlnum{1}
+    \hlstd{\}\}}
+  \hlkwd{return}\hlstd{(results)}
+\hlstd{\}}
+
+\hlcom{#Function picks the largest meta-analysis within a set of sensitivity analyses,}
+\hlcom{#and assigns it a "0" *to use with "data %>% mutate(.. = dupl.finder(..))":*}
+\hlstd{dupl.max.finder} \hlkwb{<-} \hlkwa{function}\hlstd{(}\hlkwc{duplicate.index}\hlstd{,} \hlkwc{study.number}\hlstd{,} \hlkwc{metas}\hlstd{)\{}
+  \hlstd{results} \hlkwb{<-} \hlkwd{rep}\hlstd{(}\hlnum{NA}\hlstd{,} \hlkwd{length}\hlstd{(duplicate.index))}
+
+  \hlkwa{for}\hlstd{(u} \hlkwa{in} \hlkwd{seq_along}\hlstd{((duplicate.index)))\{}
+
+    \hlstd{duplicate.indices} \hlkwb{<-} \hlkwd{which}\hlstd{(duplicate.index} \hlopt{%in%} \hlstd{duplicate.index[u])}
+
+    \hlkwa{if}\hlstd{(duplicate.index[u]} \hlopt{!=} \hlnum{0}\hlstd{)\{}
+
+      \hlstd{meta.ids} \hlkwb{<-} \hlstd{metas[duplicate.indices]}
+
+      \hlstd{max.meta.id} \hlkwb{<-} \hlstd{meta.ids[}\hlkwd{which.max}\hlstd{(study.number[duplicate.indices])]}
+      \hlstd{max.meta.indices} \hlkwb{<-} \hlkwd{which}\hlstd{(metas} \hlopt{%in%} \hlstd{max.meta.id)}
+      \hlkwa{if}\hlstd{(}\hlkwd{length}\hlstd{(}\hlkwd{unique}\hlstd{(max.meta.id))} \hlopt{<} \hlnum{2}\hlstd{)\{}
+        \hlstd{results[max.meta.indices]} \hlkwb{<-} \hlnum{0}
+      \hlstd{\}} \hlkwa{else} \hlkwd{print}\hlstd{(}\hlstr{"error"}\hlstd{)}
+
+    \hlstd{\}} \hlkwa{else} \hlstd{results[duplicate.indices]} \hlkwb{<-} \hlnum{0}
+
+  \hlstd{\}}
+
+  \hlstd{results[}\hlkwd{is.na}\hlstd{(results)]} \hlkwb{<-} \hlnum{1}
+
+  \hlkwd{return}\hlstd{(results)}
+\hlstd{\}}
+\end{alltt}
+\end{kframe}
+\end{knitrout}
+
+\section{Analysis}
+
+Data is subdivided into meta-analyses, and after all meta-analyses are excluded that are not suited for analysis, meta-analyses are done and saved.
+"data.ext2" is the dataset processed with the previously introduced "pb.process3" function. Functions defined in the global environment are marked with
+a "*USER.DEF*". They can be find in the next section.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlcom{#Load data:}
+\hlcom{# rm(list = ls())}
+\hlcom{# PATH_HOME = path.expand("~") # user home}
+\hlcom{# PATH = file.path(PATH_HOME, 'Data/PubBias')}
+\hlcom{# PATH2 = file.path(PATH_HOME, 'PubBias')}
+\hlcom{# FILE = 'cochrane_2019-07-04.csv'}
+\hlcom{# PATH_DATA = file.path(PATH, 'data')}
+\hlcom{# PATH_CODE = file.path(PATH2, 'code')}
+\hlcom{# PATH_RESULTS = file.path(PATH2, 'results_new')}
+\hlcom{# PATH_FIGURES = file.path(PATH_RESULTS, 'figures')}
+
+\hlkwd{source}(\hlkwd{file.path}(PATH_CODE, \hlstr{'PubBias_functions.R'})) \hlcom{#Load user defined functions}
+\hlkwd{load}(\hlkwd{file.path}(PATH_DATA, \hlstr{"PubBias_2019-07-19.RData"})) #Load data as contributed 
+\hlcom{#by Simon Schwab.}
+\hlcom{# load(file.path(PATH_RESULTS, "data_used_for_analysis.RData")) }
+data.ext2 <- \hlkwd{pb.process3}(data) \hlcom{#*USER.DEF*}
+
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+\hlcom{# PRE-ANALYSIS PART - EXCLUDE UNSUITABLE META-ANALYSES:}
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{#To skip pre-analysis:}
+\hlcom{# load(file.path(PATH_RESULTS, "meta_id_vector.RData"))}
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{# # ---------- Uncomment to run pre-analysis --------------}
+\hlcom{# # Get exclusion critetia (I-squared, n. sig. findings, s.e. ratio, dupl.index):}
+meta.info.bin <- data.ext2 %>% \hlkwd{filter}(outcome.flag == \hlstr{"DICH"}) %>%
+  \hlkwd{group_by}(meta.id) %>%
+  \hlkwd{mutate}(n.pre = \hlkwd{n}()) %>% \hlkwd{filter}(n.pre >= 10) %>%
+  \hlkwd{filter}(!\hlkwd{all}(events1 == 0) & !\hlkwd{all}(events2 == 0)) %>% \hlcom{#No events}
+  \hlkwd{mutate}(se.lrr = \hlkwd{sqrt}(var.lrr)) %>%
+  \hlkwd{summarize}(dupl.remove = \hlkwd{unique}(dupl.remove),
+            id = \hlkwd{unique}(id),
+            outcome.desired = \hlkwd{unique}(outcome.desired),
+            n.sig.single = \hlkwd{sum}(sig.single, na.rm = T),
+            se.min = \hlkwd{min}(se.lrr, na.rm = T),
+            se.max = \hlkwd{max}(se.lrr, na.rm = T))
+
+meta.info.cont <- data.ext2 %>% \hlkwd{filter}(outcome.flag == \hlstr{"CONT"}) %>%
+  \hlkwd{group_by}(meta.id) %>%
+  \hlkwd{mutate}(n.pre = \hlkwd{n}()) %>% \hlkwd{filter}(n.pre >= 10) %>%
+  \hlkwd{filter}(!\hlkwd{all}(mean1 == 0) & !\hlkwd{all}(mean2 == 0)) %>% \hlcom{#No means}
+  \hlkwd{filter}(!\hlkwd{all}(sd1 == 0) | !\hlkwd{all}(sd2 == 0)) %>% \hlcom{#No sd's}
+  \hlkwd{summarize}(dupl.remove = \hlkwd{unique}(dupl.remove),
+            id = \hlkwd{unique}(id),
+            outcome.desired = \hlkwd{unique}(outcome.desired),
+            n.sig.single = \hlkwd{sum}(sig.single, na.rm = T),
+            se.min = \hlkwd{min}(se, na.rm = T),
+            se.max = \hlkwd{max}(se, na.rm = T))
+
+meta.info.iv <- data.ext2 %>%
+  \hlkwd{group_by}(meta.id) %>%
+  \hlkwd{mutate}(n.pre = \hlkwd{n}()) %>% \hlkwd{filter}(n.pre >= 10) %>%
+  \hlkwd{filter}(outcome.flag == \hlstr{"IV"}) %>%
+  \hlkwd{filter}(outcome.measure.merged == \hlstr{"Rate Ratio"} | 
+           outcome.measure.merged == \hlstr{"SMD"} |
+           outcome.measure.merged == \hlstr{"MD"} | 
+           outcome.measure.merged == \hlstr{"Hazard Ratio"} |
+           outcome.measure.merged == \hlstr{"OR"} | 
+           outcome.measure.merged == \hlstr{"RR"}) %>% #Remove outcomes w. unclear def.
+  \hlkwd{summarize}(dupl.remove = \hlkwd{unique}(dupl.remove),
+            id = \hlkwd{unique}(id),
+            outcome.desired = \hlkwd{unique}(outcome.desired),
+            n.sig.single = \hlkwd{sum}(sig.single, na.rm = T),
+            se.min = \hlkwd{min}(se, na.rm = T),
+            se.max = \hlkwd{max}(se, na.rm = T))
+
+meta.info.pre <- \hlkwd{rbind}(meta.info.bin, meta.info.cont, meta.info.iv) 
+\hlcom{#To save to control how many are excluded}
+
+meta.info.pre <- meta.info.pre %>%
+  \hlkwd{filter}(id %in% data.review$id[\hlkwd{which}(data.review$withdrawn == FALSE)]) 
+\hlcom{#No withdrawn meta-analyses}
+
+meta.info <- meta.info.pre %>% 
+  \hlkwd{filter}(n.sig.single > 0) %>% \hlcom{#At least one significant result}
+  \hlkwd{filter}((se.max^2)/(se.min^2) > 4) %>% \hlcom{#variance ratio > 4}
+  \hlkwd{filter}(dupl.remove == 0) %>% \hlcom{#no duplicates}
+  \hlkwd{filter}(outcome.desired == \hlstr{"efficacy"}) #Only efficacy outcomes
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{#Meta-analysis to get I2 (random effects meta-analysis):}
+meta.id.vector.org.ranef <- meta.info$meta.id \hlcom{#Do meta-analysis for each of those}
+
+meta.org.ranef.list <- \hlkwd{list}()
+counter <- 0
+\hlkwd{for}(u in meta.id.vector.org.ranef)\{
+  counter <- counter + 1
+  temp <- data.ext2 %>% \hlkwd{filter}(meta.id == u)
+  \hlkwd{print}(\hlkwd{c}(u, counter))
+  meta.org.ranef.list[[counter]] <- \hlkwd{meta.fct.ranef.mom}(temp)
+\}
+
+exclusion.estimates <- \hlkwd{cbind}(
+  meta.id = meta.id.vector.org.ranef,
+  n = \hlkwd{unlist}(\hlkwd{lapply}(meta.org.ranef.list, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$k\})),
+  Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.org.ranef.list, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$QE\})))
+
+meta.info.pre2 <- \hlkwd{merge}(meta.info, exclusion.estimates, by = \hlstr{"meta.id"})
+meta.info.I2 <- meta.info.pre2 %>% 
+  \hlkwd{rowwise}() %>% \hlkwd{mutate}(I2  = \hlkwd{max}(0, (Q - n + 1)/Q)) \hlcom{#calculate I2}
+meta.info <- meta.info.I2 %>% \hlkwd{filter}(n > 9) %>% 
+  \hlkwd{filter}(I2 < 0.5) \hlcom{#exclude I2 >= 0.5}
+meta.id.vector <- meta.info$meta.id \hlcom{#Vector of meta-ids that match the criteria.}
+
+\hlkwd{save}(meta.id.vector, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta_id_vector.RData"}))
+\hlkwd{save}(meta.info.I2, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta_id_I2.RData"}))
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{#Get more extensive information from the original dataset about the meta-analyses:}
+meta.info.extended <- data.ext2 %>% 
+  \hlkwd{filter}(meta.id %in% meta.id.vector) %>% 
+  \hlkwd{group_by}(meta.id) %>%
+  \hlkwd{summarize}(id = \hlkwd{unique}(id),
+            outcome.flag = \hlkwd{unique}(outcome.flag),
+            comparison.nr = \hlkwd{unique}(comparison.nr),
+            comparison.name = \hlkwd{unique}(comparison.name),
+            outcome.name = \hlkwd{unique}(outcome.name),
+            outcome.nr = \hlkwd{unique}(outcome.nr),
+            subgroup.name = \hlkwd{unique}(subgroup.name),
+            subgroup.nr = \hlkwd{unique}(subgroup.nr),
+            outcome.measure.merged = \hlkwd{unique}(outcome.measure.merged),
+            outcome.measure = \hlkwd{unique}(outcome.measure),
+            outcome.desired = \hlkwd{unique}(outcome.desired),
+            mean.samplesize = \hlkwd{mean}(total1 + total2, na.rm = T),
+            total.samplesize = \hlkwd{sum}(total1 + total2),
+            var.samplesize = \hlkwd{var}(total1 + total2, na.rm = T),
+            min.samplesize = \hlkwd{min}(\hlkwd{min}(total1, na.rm = T), \hlkwd{min}(total2, na.rm = T)),
+            total.events = \hlkwd{sum}(events1 + events2),
+            mean.events = \hlkwd{mean}(events1 + events2),
+            mean.publication.year = \hlkwd{mean}(study.year, na.rm = TRUE),
+            first.publication.year = \hlkwd{min}(study.year, na.rm = T),
+\hlcom{            #*USER.DEF* function to detect the expected side of bias}
+            side = \hlkwd{bias.side.fct2}(outcome = outcome.flag, outcome.measure.merged, 
+                                  lrr = lrr, var.lrr = var.lrr, smd = cohensd, 
+                                  var.smd = var.cohensd, effect = effect, se = se),
+
+            n.sig.single = \hlkwd{sum}(sig.single, na.rm = T),
+            NA.sig.single = \hlkwd{sum}(\hlkwd{is.na}(sig.single)),
+            se.min = \hlkwd{min}(se, na.rm = T),
+            se.max = \hlkwd{max}(se, na.rm = T))
+
+\hlcom{######################################################################################}
+\hlcom{######################################################################################}
+\hlcom{######################################################################################}
+\hlcom{# ANALYSIS PART: META-ANALYSES, TESTS AND ADJUSTMENTS: ###############################}
+\hlcom{######################################################################################}
+\hlcom{######################################################################################}
+\hlcom{######################################################################################}
+
+\hlcom{#Do all analyses with Fixed effects meta-analysis method and paule mandel tau^2 }
+\hlcom{#estimator}
+\hlkwd{settings.meta}(method.tau = \hlstr{"PM"}, method = \hlstr{"Inverse"})
+
+\hlcom{#Load previously constructed lists (to skip analysis):}
+\hlcom{# load(file.path(PATH_RESULTS, "meta_complete_list_bin.RData"))}
+\hlcom{# load(file.path(PATH_RESULTS, "meta_complete_list_cont.RData"))}
+\hlcom{# load(file.path(PATH_RESULTS, "meta_complete_list_iv.RData"))}
+\hlcom{# load(file.path(PATH_RESULTS, "meta_complete_list_zscore.RData"))}
+\hlcom{# load(file.path(PATH_RESULTS, "meta_complete_list_cohensd.RData"))}
+
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+\hlcom{# BINARY DATA META-ANALYSES: ----------------------------------------------------------------------------------------#}
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{# # -------- Uncomment to run analysis ----------}
+meta.id.vector.bin <- 
+  meta.info.extended$meta.id[\hlkwd{which}(meta.info.extended$outcome.flag == \hlstr{"DICH"})]
+meta.analyses <- \hlkwd{list}()
+meta.analyses.asd <- \hlkwd{list}()
+meta.analyses.reg <- \hlkwd{list}()
+meta.analyses.copas <- \hlkwd{list}()
+meta.tests.harbord <- \hlkwd{list}()
+meta.tests.peter <- \hlkwd{list}()
+meta.tests.rucker.mm <- \hlkwd{list}()
+meta.tests.rucker.linreg <- \hlkwd{list}()
+meta.tests.schwarzer <- \hlkwd{list}()
+meta.tests.excess <- \hlkwd{list}()
+counter <- 0
+\hlkwd{for}(u in meta.id.vector.bin)\{
+	counter <- counter + 1
+	\hlkwd{print}(\hlkwd{c}(u, counter))
+	meta.analyses[[counter]] <- 
+	  \hlkwd{metabin}(event.e = events1c, n.e = total1, event.c = events2c, n.c = total2,
+	          studlab = study.name, sm = \hlstr{"RR"},
+	          method = \hlstr{"Inverse"}, data = data.ext2[data.ext2$meta.id == u,])
+
+\hlcom{	#Arcsine transformed proportions to use in combination with Rücker's test:}
+	meta.analyses.asd[[counter]] <- 
+	  \hlkwd{metabin}(event.e = events1c, n.e = total1, event.c = events2c, n.c = total2,
+	          studlab = study.name, sm = \hlstr{"ASD"}, 
+	          method = \hlstr{"Inverse"}, data = data.ext2[data.ext2$meta.id == u,])
+
+\hlcom{	#Adjustment for publication bias}
+	meta.analyses.reg[[counter]] <- \hlkwd{limitmeta}(meta.analyses[[counter]])
+	meta.analyses.copas[[counter]] <- \hlkwd{auto.copas}(meta.analyses[[counter]], 
+	                         sig.level = 0.1) \hlcom{#*USER.DEF* Copas selection model.}
+
+\hlcom{	#Publication bias tests.}
+	meta.tests.excess[[counter]] <- \hlkwd{tes.fct2}(data = data.ext2[data.ext2$meta.id == u,])
+	meta.tests.harbord[[counter]] <- 
+	  \hlkwd{metabias}(meta.analyses[[counter]], method.bias = \hlstr{"score"}, k.min = 2)
+	meta.tests.peter[[counter]] <- 
+	  \hlkwd{metabias}(meta.analyses[[counter]], method.bias = \hlstr{"peters"}, k.min = 2)
+	meta.tests.schwarzer[[counter]] <- 
+	  \hlkwd{metabias}(meta.analyses[[counter]], method.bias = \hlstr{"count"}, k.min = 2)
+	meta.tests.rucker.mm[[counter]] <- 
+	  \hlkwd{metabias}(meta.analyses.asd[[counter]], method.bias = \hlstr{"mm"}, k.min = 2)
+	meta.tests.rucker.linreg[[counter]] <- 
+	  \hlkwd{metabias}(meta.analyses.asd[[counter]], method.bias = \hlstr{"linreg"}, k.min = 2)
+\}
+
+\hlcom{# counter.unknown.bin.copas.error <- 0}
+\hlcom{# for(u in meta.id.vector.bin)\{}
+\hlcom{# 	if(length(meta.analyses.copas[[counter]]) < 3)\{}
+\hlcom{# 		meta.analyses.copas[[counter]] <- c(NA, NA, NA)}
+\hlcom{# 		counter.unknown.bin.copas.error <- counter.unknown.bin.copas.error + 1}
+\hlcom{# 	\}}
+\hlcom{# \}}
+\hlcom{# print(c("unknown.bin.copas.errors = ", counter.unknown.bin.copas.error))}
+\hlcom{#}
+\hlcom{# bin.meta.list <- list(data.ext2, meta.id.vector.bin, meta.analyses,}
+\hlcom{# 											meta.analyses.asd,}
+\hlcom{# 											meta.analyses.reg,}
+\hlcom{# 											meta.analyses.copas,}
+\hlcom{# 											meta.tests.excess,}
+\hlcom{# 											meta.tests.harbord,}
+\hlcom{# 											meta.tests.peter,}
+\hlcom{# 											meta.tests.rucker.mm,}
+\hlcom{# 											meta.tests.schwarzer,}
+\hlcom{# 											meta.tests.excess,}
+\hlcom{# 											meta.tests.rucker.linreg)}
+\hlcom{# save(bin.meta.list, file =  file.path(PATH_RESULTS, "meta_complete_list_bin.RData"))}
+\hlcom{# #--------------------------------------------------------------------------------------------------------------------#}
+\hlcom{# }
+\hlcom{# #Load analysis data:}
+\hlcom{# meta.id.vector.bin <- bin.meta.list[[2]]}
+\hlcom{# meta.analyses <- bin.meta.list[[3]]}
+\hlcom{# meta.analyses.reg <- bin.meta.list[[5]]}
+\hlcom{# meta.analyses.copas <- bin.meta.list[[6]]}
+\hlcom{# meta.analyses.trimfill <- bin.meta.list[[7]]}
+\hlcom{# meta.tests.harbord <- bin.meta.list[[8]]}
+\hlcom{# meta.tests.peter <- bin.meta.list[[9]]}
+\hlcom{# meta.tests.rucker.mm <- bin.meta.list[[10]]}
+\hlcom{# meta.tests.schwarzer <- bin.meta.list[[11]]}
+\hlcom{# meta.tests.excess <- bin.meta.list[[12]]}
+\hlcom{# meta.tests.rucker.linreg <- bin.meta.list[[13]]}
+
+\hlcom{#Extract from lists:}
+bin.results <- \hlkwd{data.frame}(
+  meta.id = meta.id.vector.bin,
+  meta.es.measure = \hlkwd{rep}(times = \hlkwd{length}(meta.id.vector.bin), \hlstr{"log risk ratio"}),
+
+  n.sig.single2 = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{\hlkwd{length}(\hlkwd{which}(meta.analysis$pval < 0.05))\})),
+
+\hlcom{  #Meta-analysis:}
+  est.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.fixed\})),
+  est.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.random\})),
+  zval.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$zval.fixed\})),
+  zval.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$zval.random\})),
+
+  pval.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                   FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.fixed\})),
+  pval.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.random\})),
+
+  se.est.fixef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.fixed\})),
+  se.est.ranef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.random\})),
+
+  Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$Q\})),
+  pval.Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                         FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.Q\})),
+\hlcom{  #I2 = unlist(lapply(meta.analyses, FUN = function(meta.analysis)\{meta.analysis$I2.w\})),}
+  tau = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                      FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$tau\})),
+\hlcom{  #se.tau = unlist(lapply(meta.analyses, FUN = function(meta.analysis)\{meta.analysis$se.tau\})),}
+  sparse = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                         FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$sparse\})),
+  k = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$k\})),
+
+\hlcom{  #Adjustment:}
+  method.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$method.adjust\})),
+  est.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$TE.adjust\})),
+  se.est.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$seTE.adjust\})),
+  zval.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$zval.adjust\})),
+  pval.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
+  alpha.r = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
+  beta.r = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
+  Q.small = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$Q.small\})),
+  Q.resid = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$Q.resid\})),
+  G.squared = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$G.squared\})),
+
+  est.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[1]\})),
+  se.est.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[2]\})),
+  missing.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[3]\})),
+
+\hlcom{  #Tests;}
+  pval.d.tes.org = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                                 FUN = \hlkwd{function}(object)\{object[3]\})),
+  pval.d.tes = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                             FUN = \hlkwd{function}(object)\{object[4]\})),
+  stat.d.tes = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                             FUN = \hlkwd{function}(object)\{object[2]\})),
+  excess.d = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                           FUN = \hlkwd{function}(object)\{object[5]\})) - 
+    \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                  FUN = \hlkwd{function}(object)\{object[6]\})),
+  pval.harbord = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.harbord, 
+                               FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
+  stat.harbord = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.harbord, 
+                               FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
+  pval.peter = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.peter, 
+                             FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
+  stat.peter = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.peter, 
+                             FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
+  pval.rucker = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.rucker.mm, 
+                              FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
+  stat.rucker = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.rucker.mm, 
+                              FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
+  pval.rucker.linreg = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.rucker.linreg, 
+                              FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
+  stat.rucker.linreg = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.rucker.linreg, 
+                              FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
+  pval.schwarzer = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.schwarzer, 
+                              FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
+  stat.schwarzer = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.schwarzer, 
+                              FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\}))
+)
+
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+\hlcom{# CONTINUOUS DATA META-ANALYSES: ------------------------------------------------------------------------------------#}
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{# # -------- Uncomment to run analysis ----------}
+meta.id.vector.cont <- 
+  meta.info.extended$meta.id[\hlkwd{which}(meta.info.extended$outcome.flag == \hlstr{"CONT"})]
+meta.analyses <- \hlkwd{list}()
+meta.analyses.reg <- \hlkwd{list}()
+meta.analyses.copas <- \hlkwd{list}()
+meta.analyses.trimfill <- \hlkwd{list}()
+meta.tests.excess <- \hlkwd{list}()
+meta.tests.linreg <- \hlkwd{list}()
+meta.tests.begg <- \hlkwd{list}()
+meta.tests.mm <- \hlkwd{list}()
+counter <- 0
+\hlkwd{for}(u in meta.id.vector.cont)\{
+	counter <- counter + 1
+	\hlkwd{print}(\hlkwd{c}(u, counter))
+	outcome.measure.merged <- 
+	  \hlkwd{as.character}(\hlkwd{unique}(data.ext2[data.ext2$meta.id == u,
+	                 \hlstr{"outcome.measure.merged"}])$outcome.measure.merged)
+	meta.analyses[[counter]] <- 
+	  \hlkwd{metacont}(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2,
+						mean.c = mean2, sd.c = sd2, sm = outcome.measure.merged, 
+						studlab = study.name, data = data.ext2[data.ext2$meta.id == u,])
+	meta.analyses.reg[[counter]] <- \hlkwd{limitmeta}(meta.analyses[[counter]])
+	meta.analyses.trimfill[[counter]] <- \hlkwd{trimfill}(meta.analyses[[counter]])
+	meta.analyses.copas[[counter]] <- \hlkwd{auto.copas}(meta.analyses[[counter]], 
+	                                             sig.level = 0.1)
+
+	meta.tests.excess[[counter]] <- 
+	  \hlkwd{tes.fct2}(data = data.ext2[data.ext2$meta.id == u,])
+	meta.tests.linreg[[counter]] <- \hlkwd{metabias}(meta.analyses[[counter]], 
+	                                         method.bias = \hlstr{"linreg"}, k.min = 2)
+	meta.tests.begg[[counter]] <- \hlkwd{metabias}(meta.analyses[[counter]], 
+	                                       method.bias = \hlstr{"rank"}, k.min = 2)
+	meta.tests.mm[[counter]] <- \hlkwd{metabias}(meta.analyses[[counter]], 
+	                                     method.bias = \hlstr{"mm"}, k.min = 2)
+\hlcom{# \}}
+\hlcom{# cont.meta.list <- list(data.ext2, meta.id.vector.cont, meta.analyses,}
+\hlcom{# 											 meta.analyses.reg,}
+\hlcom{# 											 meta.analyses.copas,}
+\hlcom{# 											 meta.analyses.trimfill,}
+\hlcom{# 											 meta.tests.linreg,}
+\hlcom{# 											 meta.tests.begg,}
+\hlcom{# 											 meta.tests.mm,}
+\hlcom{# 											 meta.tests.excess)}
+\hlcom{# save(cont.meta.list, file =  file.path(PATH_RESULTS, "meta_complete_list_cont.RData"))}
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{#Load analysis data:}
+\hlcom{# meta.id.vector.cont <- cont.meta.list[[2]]}
+\hlcom{# meta.analyses <- cont.meta.list[[3]]}
+\hlcom{# meta.analyses.reg <- cont.meta.list[[4]]}
+\hlcom{# meta.analyses.copas <- cont.meta.list[[5]]}
+\hlcom{# meta.analyses.trimfill <- cont.meta.list[[6]]}
+\hlcom{# meta.tests.linreg <- cont.meta.list[[7]]}
+\hlcom{# meta.tests.begg <- cont.meta.list[[8]]}
+\hlcom{# meta.tests.mm <- cont.meta.list[[9]]}
+\hlcom{# meta.tests.excess <- cont.meta.list[[10]]}
+
+\hlcom{#Extract from lists:}
+cont.results <- \hlkwd{data.frame}(
+  meta.id = meta.id.vector.cont,
+  meta.es.measure = \hlkwd{rep}(\hlstr{"std. mean difference"}, times = \hlkwd{length}(meta.id.vector.cont)),
+
+  n.sig.single2 = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, FUN = \hlkwd{function}(meta.analysis)\{\hlkwd{length}(\hlkwd{which}(meta.analysis$pval < 0.05))\})),
+
+\hlcom{  #Meta-Analysis}
+  est.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.fixed\})),
+  est.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.random\})),
+
+  zval.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$zval.fixed\})),
+  zval.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$zval.random\})),
+
+  pval.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.fixed\})),
+  pval.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.random\})),
+
+  se.est.fixef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.fixed\})),
+  se.est.ranef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.random\})),
+
+  Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$Q\})),
+  pval.Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.Q\})),
+  tau = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$tau\})),
+  k = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$k\})),
+
+\hlcom{  #Adjustment:}
+  method.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$method.adjust\})),
+  est.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$TE.adjust\})),
+  se.est.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$seTE.adjust\})),
+  zval.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$zval.adjust\})),
+  pval.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
+  alpha.r = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
+  beta.r = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
+  Q.small = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$Q.small\})),
+  Q.resid = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$Q.resid\})),
+  G.squared = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$G.squared\})),
+
+  est.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
+                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[1]\})),
+  se.est.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
+                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[2]\})),
+  missing.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
+                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[3]\})),
+
+\hlcom{  #Tests:}
+  pval.d.tes.org = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                              FUN = \hlkwd{function}(object)\{object[3]\})),
+  pval.d.tes = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                              FUN = \hlkwd{function}(object)\{object[4]\})),
+  stat.d.tes = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                              FUN = \hlkwd{function}(object)\{object[2]\})),
+  excess.d = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                              FUN = \hlkwd{function}(object)\{object[5]\})) - 
+    \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                              FUN = \hlkwd{function}(object)\{object[6]\})),
+  pval.egger = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.linreg, 
+                             FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
+  stat.egger = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.linreg, 
+                             FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
+  pval.begg = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.begg, 
+                            FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
+  stat.begg = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.begg, 
+                            FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
+  pval.thompson = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.mm, 
+                            FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
+  stat.thompson = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.mm, 
+                            FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\}))
+)
+
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+\hlcom{# IV OUTCOME META-ANALYSIS: -----------------------------------------------------------------------------------#}
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{# # -------- Uncomment to run analysis ----------}
+meta.id.vector.iv <- 
+  meta.info.extended$meta.id[\hlkwd{which}(meta.info.extended$outcome.flag == \hlstr{"IV"})]
+meta.analyses <- \hlkwd{list}()
+meta.analyses.reg <- \hlkwd{list}()
+meta.analyses.copas <- \hlkwd{list}()
+meta.analyses.trimfill <- \hlkwd{list}()
+meta.tests.linreg <- \hlkwd{list}()
+meta.tests.begg <- \hlkwd{list}()
+meta.tests.mm <- \hlkwd{list}()
+meta.tests.excess <- \hlkwd{list}()
+counter <- 0
+\hlkwd{for}(u in meta.id.vector.iv)\{
+	counter <- counter + 1
+	meta.analyses[[counter]] <- \hlkwd{metagen.iv}(data = data.ext2[data.ext2$meta.id == u,])
+	\hlkwd{print}(\hlkwd{c}(u, counter))
+
+	meta.analyses.reg[[counter]] <- \hlkwd{limitmeta}(meta.analyses[[counter]])
+	meta.analyses.trimfill[[counter]] <- \hlkwd{trimfill}(meta.analyses[[counter]])
+	meta.analyses.copas[[counter]] <- \hlkwd{auto.copas}(meta.analyses[[counter]], 
+	                                             sig.level = 0.1)
+
+	meta.tests.excess[[counter]] <- 
+	  \hlkwd{tes.fct2}(data = data.ext2[data.ext2$meta.id == u,])
+	meta.tests.linreg[[counter]] <- \hlkwd{metabias}(meta.analyses[[counter]], 
+	                               method.bias = \hlstr{"linreg"}, k.min = 2)
+	meta.tests.begg[[counter]] <- \hlkwd{metabias}(meta.analyses[[counter]], 
+	                               method.bias = \hlstr{"rank"}, k.min = 2)
+	meta.tests.mm[[counter]] <- \hlkwd{metabias}(meta.analyses[[counter]], 
+	                               method.bias = \hlstr{"mm"}, k.min = 2)
+\}
+\hlcom{# iv.meta.list <- list(data.ext2, meta.id.vector.iv, meta.analyses,}
+\hlcom{# 											 meta.analyses.reg,}
+\hlcom{# 											 meta.analyses.copas,}
+\hlcom{# 											 meta.analyses.trimfill,}
+\hlcom{# 											 meta.tests.linreg,}
+\hlcom{# 											 meta.tests.begg,}
+\hlcom{# 											 meta.tests.mm,}
+\hlcom{# 											 meta.tests.excess)}
+\hlcom{# save(iv.meta.list, file =  file.path(PATH_RESULTS, "meta_complete_list_iv.RData"))}
+\hlcom{# #--------------------------------------------------------------------------------------------------------------------#}
+\hlcom{# }
+\hlcom{# #Load analysis data:}
+\hlcom{# meta.id.vector.iv <- iv.meta.list[[2]]}
+\hlcom{# meta.analyses <- iv.meta.list[[3]]}
+\hlcom{# meta.analyses.reg <- iv.meta.list[[4]]}
+\hlcom{# meta.analyses.copas <- iv.meta.list[[5]]}
+\hlcom{# meta.analyses.trimfill <- iv.meta.list[[6]]}
+\hlcom{# meta.tests.linreg <- iv.meta.list[[7]]}
+\hlcom{# meta.tests.begg <- iv.meta.list[[8]]}
+\hlcom{# meta.tests.mm <- iv.meta.list[[9]]}
+\hlcom{# meta.tests.excess <- iv.meta.list[[10]]}
+
+\hlcom{#Extract from lists:}
+iv.results <- \hlkwd{data.frame}(
+  meta.id = meta.id.vector.iv,
+  meta.es.measure = \hlkwd{rep}(times = \hlkwd{length}(meta.id.vector.iv), \hlstr{"\hlkwd{unknown.effect}(IV)"}),
+
+  n.sig.single2 = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{\hlkwd{length}(\hlkwd{which}(meta.analysis$pval < 0.05))\})),
+\hlcom{  #Meta-Analysis}
+  est.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.fixed\})),
+  est.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.random\})),
+
+  zval.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$zval.fixed\})),
+  zval.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$zval.random\})),
+
+  pval.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.fixed\})),
+  pval.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.random\})),
+
+  se.est.fixef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.fixed\})),
+  se.est.ranef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.random\})),
+
+  Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$Q\})),
+  pval.Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.Q\})),
+  tau = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$tau\})),
+  k = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$k\})),
+
+\hlcom{  #Adjustment:}
+  method.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$method.adjust\})),
+  est.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$TE.adjust\})),
+  se.est.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$seTE.adjust\})),
+  zval.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$zval.adjust\})),
+  pval.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
+  alpha.r = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
+  beta.r = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
+  Q.small = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$Q.small\})),
+  Q.resid = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$Q.resid\})),
+  G.squared = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$G.squared\})),
+
+  est.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
+                           FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[1]\})),
+  se.est.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
+                           FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[2]\})),
+  missing.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
+                           FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[3]\})),
+
+\hlcom{  #Tests:}
+  pval.d.tes.org = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                             FUN = \hlkwd{function}(object)\{object[3]\})),
+  pval.d.tes = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                             FUN = \hlkwd{function}(object)\{object[4]\})),
+  stat.d.tes = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                             FUN = \hlkwd{function}(object)\{object[2]\})),
+  excess.d = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                             FUN = \hlkwd{function}(object)\{object[5]\})) - 
+    \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
+                  FUN = \hlkwd{function}(object)\{object[6]\})),
+  pval.egger = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.linreg, 
+                             FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
+  stat.egger = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.linreg, 
+                             FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
+  pval.begg = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.begg, 
+                             FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
+  stat.begg = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.begg, 
+                             FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
+  pval.thompson = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.mm, 
+                             FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
+  stat.thompson = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.mm, 
+                             FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\}))
+)
+
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+\hlcom{# Z-SCORE BASED META-ANALYSES: --------------------------------------------------------------------------------------#}
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{# # -------- Uncomment to run analysis ----------}
+meta.id.vector.noiv <- 
+  meta.info.extended$meta.id[-\hlkwd{which}(meta.info.extended$outcome.flag == \hlstr{"IV"})]
+meta.id.vector.smd <- 
+  meta.info.extended$meta.id[\hlkwd{which}(meta.info.extended$outcome.measure.merged == \hlstr{"SMD"})]
+meta.id.vector.z <- \hlkwd{union}(meta.id.vector.smd, meta.id.vector.noiv)
+meta.id.vector.z.c <- meta.id.vector.z[-\hlkwd{c}(\hlkwd{which}(meta.id.vector.z == 104613),
+                                          \hlkwd{which}(meta.id.vector.z == 104616),
+                                          \hlkwd{which}(meta.id.vector.z == 153452),
+                                          \hlkwd{which}(meta.id.vector.z == 163246),
+                      \hlkwd{which}(meta.id.vector.z == 182958))] \hlcom{#Have zero total1..}
+tmp.z <- data.ext2 %>% \hlkwd{group_by}(meta.id) %>% \hlkwd{mutate}(n = \hlkwd{n}()) %>% \hlkwd{filter}(n > 9) %>%
+  \hlkwd{filter}(total1 + total2 > 3) %>% \hlkwd{filter}(total1 != 0 & total2 != 0)
+meta.analyses <- \hlkwd{list}()
+meta.analyses.reg <- \hlkwd{list}()
+meta.analyses.copas <- \hlkwd{list}()
+counter <- 0
+\hlkwd{for}(u in meta.id.vector.z.c)\{
+	counter <- counter + 1
+	\hlkwd{print}(\hlkwd{c}(u,counter))
+	meta.analyses[[counter]] <- \hlkwd{metacor}(cor = z, n = total1 + total2, 
+	                   studlab = study.name, tmp.z[tmp.z$meta.id == u,])
+	meta.analyses.reg[[counter]] <- \hlkwd{limitmeta}(meta.analyses[[counter]])
+	meta.analyses.copas[[counter]] <- \hlkwd{auto.copas}(meta.analyses[[counter]], 
+	                                             sig.level = 0.1)
+\}
+\hlcom{# zscore.meta.list <- list(tmp.z, meta.id.vector.z.c, meta.analyses, }
+\hlcom{#meta.analyses.reg, meta.analyses.copas)}
+\hlcom{# save(zscore.meta.list, file =  file.path(PATH_RESULTS, }
+\hlcom{#"meta_complete_list_zscore.RData"))}
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{#Load analysis data:}
+meta.id.vector.z.c <- zscore.meta.list[[2]]
+meta.analyses <- zscore.meta.list[[3]]
+meta.analyses.reg <- zscore.meta.list[[4]]
+meta.analyses.copas <- zscore.meta.list[[5]]
+
+\hlcom{#List extraction:}
+zscore.meta.analysis.estimates <- \hlkwd{cbind}(
+  meta.id = meta.id.vector.z.c,
+  est.z.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.fixed\})),
+  est.z.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.random\})),
+  se.est.z.fixef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.fixed\})),
+  se.est.z.ranef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.random\})),
+
+  est.z.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$TE.adjust\})),
+  se.est.z.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$seTE.adjust\})),
+
+  est.z.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
+                    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[1]\})),
+  se.est.z.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
+                    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[2]\})))
+
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+\hlcom{# HEDGES G BASED META-ANALYSES: -------------------------------------------------------------------------------------#}
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{# # -------- Uncomment to run analysis ----------}
+meta.id.vector.d <- meta.id.vector.z[-\hlkwd{c}(\hlkwd{which}(meta.id.vector.z == 25407))]
+meta.analyses <- \hlkwd{list}()
+meta.analyses.reg <- \hlkwd{list}()
+meta.analyses.copas <- \hlkwd{list}()
+counter <- 0
+\hlkwd{for}(u in meta.id.vector.d)\{
+  counter <- counter + 1
+  \hlkwd{print}(\hlkwd{c}(u,counter))
+  meta.analyses[[counter]] <- \hlkwd{metagen.bincont2}(data.ext2[data.ext2$meta.id == u,])
+  meta.analyses.reg[[counter]] <- \hlkwd{limitmeta}(meta.analyses[[counter]])
+  meta.analyses.copas[[counter]] <- \hlkwd{auto.copas}(meta.analyses[[counter]], 
+                                               sig.level = 0.1)
+\}
+\hlcom{# cohensd.meta.list <- list(data.ext2, meta.id.vector.d, meta.analyses, }
+\hlcom{#meta.analyses.reg, meta.analyses.copas)}
+\hlcom{# save(cohensd.meta.list, file =  file.path(PATH_RESULTS, }
+\hlcom{#"meta_complete_list_cohensd.RData"))}
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{#Load analysis data:}
+meta.id.vector.d <- cohensd.meta.list[[2]]
+meta.analyses <- cohensd.meta.list[[3]]
+meta.analyses.reg <- cohensd.meta.list[[4]]
+meta.analyses.copas <- cohensd.meta.list[[5]]
+
+\hlcom{#List extraction:}
+cohensd.meta.analysis.estimates <- \hlkwd{cbind}(
+  meta.id = meta.id.vector.d,
+  est.d.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.fixed\})),
+  est.d.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.random\})),
+  se.est.d.fixef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.fixed\})),
+  se.est.d.ranef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
+                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.random\})),
+
+  est.d.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$TE.adjust\})),
+  se.est.d.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$seTE.adjust\})),
+
+  est.d.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[1]\})),
+  se.est.d.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
+                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[2]\})))
+
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+\hlcom{# BUILD FINAL DATASET OF RESULTS}
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+meta.tp5 <- \hlkwd{bind_rows}(bin.results, cont.results, iv.results)
+meta.tp1 <- \hlkwd{merge}(meta.info.extended, meta.tp5, 
+                  by = \hlkwd{c}(\hlstr{"meta.id"})) #Temporary versions
+meta.tp4 <- \hlkwd{merge}(by = \hlstr{"meta.id"}, x = meta.tp1, 
+                  y = zscore.meta.analysis.estimates, all.x = T)
+meta.f <- \hlkwd{merge}(by = \hlstr{"meta.id"}, x = meta.tp4, 
+                y = cohensd.meta.analysis.estimates, all.x = T)
+
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+\hlcom{# ROUND-UP: DETECT AND REPLACE MISSING VALUES}
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{#se.est.copas.na = 1 -> is missing}
+meta.f$se.est.copas.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$se.est.copas), 1, 0) 
+meta.f$se.est.z.copas.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$se.est.z.copas), 1, 0)
+meta.f$se.est.d.copas.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$se.est.d.copas), 1, 0)
+
+meta.f$se.est.reg.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$se.est.reg), 1, 0)
+meta.f$se.est.z.reg.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$se.est.z.reg), 1, 0)
+meta.f$se.est.d.reg.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$se.est.d.reg), 1, 0)
+
+meta.f$est.copas.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$est.copas), 1, 0)
+meta.f$est.z.copas.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$est.z.copas), 1, 0)
+meta.f$est.d.copas.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$est.d.copas), 1, 0)
+
+meta.f$est.reg.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$est.reg), 1, 0)
+meta.f$est.z.reg.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$est.z.reg), 1, 0)
+meta.f$est.d.reg.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$est.d.reg), 1, 0)
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{#Inpute random effect estimate for missing copas:}
+copas.names <- \hlkwd{c}(\hlstr{"est.copas"}, \hlstr{"se.est.copas"}, \hlstr{"est.z.copas"}, \hlstr{"se.est.z.copas"}, 
+                 \hlstr{"est.d.copas"}, \hlstr{"se.est.d.copas"})
+ranef.names <- \hlkwd{c}(\hlstr{"est.ranef"}, \hlstr{"se.est.ranef"}, \hlstr{"est.z.ranef"}, \hlstr{"se.est.z.ranef"}, 
+                 \hlstr{"est.d.ranef"}, \hlstr{"se.est.d.ranef"})
+missing.names <- \hlkwd{paste}(copas.names, \hlstr{".missing"}, sep = \hlstr{""})
+missing <- \hlkwd{c}()
+
+\hlkwd{for}(u in 1:\hlkwd{length}(copas.names))\{
+  missing.count <- 0
+  \hlkwd{for}(k in 1:\hlkwd{dim}(meta.f)[1])\{
+    \hlkwd{if}(\hlkwd{is.na}(meta.f[k, copas.names[u]]))\{
+      missing.count <- missing.count + 1
+      meta.f[k, copas.names[u]] <- meta.f[k, ranef.names[u]]
+    \}
+  \}
+  missing[u] <- missing.count
+  meta.f[, missing.names[u]] <- missing.count
+\}
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{#Some useful variables:}
+meta.f <- meta.f %>% \hlkwd{rowwise}() %>% 
+  \hlkwd{mutate}(pval1.egger = \hlkwd{onesided.p}(stat = stat.egger, side = side, n = k, 
+                                  test.type = \hlstr{"reg"}),
+         pval1.thompson = \hlkwd{onesided.p}(stat = stat.thompson, side = side, n = k, 
+                                     test.type = \hlstr{"reg"}),
+         pval1.begg = \hlkwd{onesided.p}(stat = stat.begg, side = side, n = k, 
+                                 test.type = \hlstr{"rank"}),
+
+         pval1.harbord = \hlkwd{onesided.p}(stat = stat.harbord, side = side, n = k, 
+                                    test.type = \hlstr{"reg"}),
+         pval1.rucker = \hlkwd{onesided.p}(stat = stat.rucker, side = side, n = k, 
+                                   test.type = \hlstr{"reg"}),
+         pval1.rucker.linreg = \hlkwd{onesided.p}(stat = stat.rucker.linreg, side = side, n = k, 
+                                          test.type = \hlstr{"reg"}),
+         pval1.peter = \hlkwd{onesided.p}(stat = stat.peter, side = side, n = k, 
+                                  test.type = \hlstr{"reg"}),
+         pval1.schwarzer = \hlkwd{onesided.p}(stat = stat.schwarzer, side = side, n = k, 
+                                      test.type = \hlstr{"rank"}),
+         pval1.d.tes = pval.d.tes)
+
+\hlcom{#Summarise different tests for binary and continuous variables to one:}
+meta.f <- meta.f %>% \hlkwd{rowwise}() %>% 
+  \hlkwd{mutate}(I2  = \hlkwd{max}(0, (Q - k + 1)/Q),
+         var.ratio = (se.max^2)/(se.min^2),
+         pval.se = \hlkwd{case_when}(outcome.flag == \hlstr{"DICH"} ~ pval1.rucker.linreg, 
+                             TRUE ~ pval1.egger),
+         pval.se.het = \hlkwd{case_when}(outcome.flag == \hlstr{"DICH"} ~ pval1.rucker, 
+                                 TRUE ~ pval1.thompson))
+\hlcom{#significance of pb tests:}
+sig.level <- 0.1
+meta.f <- meta.f %>% \hlkwd{rowwise}() %>% 
+  \hlkwd{mutate}(egger.test = \hlkwd{ifelse}(pval1.egger < sig.level, 1, 0),
+         thompson.test = \hlkwd{ifelse}(pval1.thompson < sig.level, 1, 0),
+         begg.test = \hlkwd{ifelse}(pval1.begg < sig.level, 1, 0),
+
+         tes.d.test = \hlkwd{ifelse}(pval1.d.tes < sig.level, 1, 0),
+
+         schwarzer.test = \hlkwd{ifelse}(pval1.schwarzer < sig.level, 1, 0),
+         rucker.test = \hlkwd{ifelse}(pval1.rucker < sig.level, 1, 0),
+         rucker.test.linreg = \hlkwd{ifelse}(pval1.rucker.linreg < sig.level, 1, 0),
+         harbord.test = \hlkwd{ifelse}(pval1.harbord < sig.level, 1, 0),
+         peter.test = \hlkwd{ifelse}(pval1.peter < sig.level, 1, 0))
+
+\hlcom{#calculate test statistics:}
+meta.f <- meta.f %>% \hlkwd{mutate}(
+  z.fixef = (est.fixef/se.est.fixef)
+  z.ranef = (est.ranef/se.est.ranef),
+  z.reg =   (est.reg/se.est.reg),
+  z.copas = ((est.copas)/se.est.copas))
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{#Separate outcome.types:}
+meta.bin <- meta.f %>% \hlkwd{filter}(outcome.flag == \hlstr{"DICH"})
+meta.cont <- meta.f %>% \hlkwd{filter}(outcome.flag == \hlstr{"CONT"})
+meta.iv <- meta.f %>% \hlkwd{filter}(outcome.flag == \hlstr{"IV"})
+\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
+
+\hlcom{#Save the result datasets:}
+\hlkwd{save}(meta.f, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta_analyses_summary_complete.RData"}))
+\hlkwd{save}(meta.bin, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta.bin.RData"}))
+\hlkwd{save}(meta.cont, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta.cont.RData"}))
+\hlkwd{save}(meta.iv, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta.iv.RData"}))
+\hlkwd{save}(meta.id.vector, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta_id_vector.RData"}))
+\hlkwd{save}(data.ext2, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"data_used_for_analysis.RData"})) #Save data used for analysis
+
+\hlcom{# x <- foreach(i = 1:length(meta.id.vector.bin)) %dopar% }
+\hlcom{#   # u <- meta.id.vector.bin[i]}
+\hlcom{#   # counter <- counter + 1}
+\hlcom{#   metabin(event.e = events1c, n.e = total1, event.c = events2c, n.c = total2,}
+\hlcom{#           studlab = study.name, sm = "RR",}
+\hlcom{#           method = "Inverse", data = data.ext2[data.ext2$meta.id == meta.id.vector.bin[i],])}
+\hlcom{# }
+\hlcom{# cl<-makeCluster(7)}
+\hlcom{# registerDoParallel(cl)}
+\hlcom{# }
+\hlcom{# foreach(i = 1:length(meta.id.vector.bin)) %dopar%}
+\hlcom{#   sqrt(i)}
+
+\hlcom{########################################################################################################}
+\hlcom{########################################################################################################}
+\hlcom{########################################################################################################}
+\hlcom{########################################################################################################}
+\hlcom{########################################################################################################}
+\hlcom{########################################################################################################}
+\hlcom{########################################################################################################}
+\hlcom{########################################################################################################}
+\end{alltt}
+\end{kframe}
+\end{knitrout}
 

### 2019-08-02 report/chapter03.Rnw
results first complete draft
appendix, corrected IV results

@@
 m.a.variance4.count <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
-  group_by(meta.id) %>% summarise(ratio = (max(se.new)^2)/(min(se.new)^2)) %>% 
+  group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
+                                                  TRUE ~ se)) %>% 
+  summarise(ratio = (max(se.new)^2)/(min(se.new)^2)) %>% 
   filter(ratio >= 4) %>% count
 tp3 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
-  group_by(meta.id) %>% mutate(ratio = (max(se.new)^2)/(min(se.new)^2)) %>% 
+  group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
+                                                  TRUE ~ se)) %>% 
+  mutate(ratio = (max(se.new)^2)/(min(se.new)^2)) %>% 
   filter(ratio >= 4)
@@
 m.a.one.sig.count <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
-  group_by(meta.id) %>% summarise(ratio = (max(se.new)^2)/(min(se.new)^2),
+  group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
+                                                  TRUE ~ se)) %>% 
+  summarise(ratio = (max(se.new)^2)/(min(se.new)^2),
                                   n.sig = sum(sig.single)) %>% 
@@
 tp4 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
-  group_by(meta.id) %>% mutate(ratio = (max(se.new)^2)/(min(se.new)^2),
+  group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
+                                                  TRUE ~ se)) %>% 
+  mutate(ratio = (max(se.new)^2)/(min(se.new)^2),
                                   n.sig = sum(sig.single)) %>% 
@@
 m.a.no.dupl.number <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
-  group_by(meta.id) %>% summarise(ratio = (max(se.new)^2)/(min(se.new)^2),
+  group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
+                                                  TRUE ~ se)) %>% 
+  summarise(ratio = (max(se.new)^2)/(min(se.new)^2),
                                   n.sig = sum(sig.single),
@@
 tp5 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
-  group_by(meta.id) %>% mutate(ratio = (max(se.new)^2)/(min(se.new)^2),
+  group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
+                                                  TRUE ~ se)) %>% 
+  mutate(ratio = (max(se.new)^2)/(min(se.new)^2),
                                   n.sig = sum(sig.single),

### 2019-08-02 report/chapter04.Rnw
appendix, corrected IV results

@@
 require(corrgram)
+require(nlme)
 
@@
 method.names <- c(z.reg = "Regression", z.copas = "Copas Selection Model")
-adjusted.evidence.fixed <- meta.f %>% 
+adjusted.evidence.fixed <- meta.f %>% filter(z.reg > -40) %>% 
   select(pval.se, z.fixef, z.ranef, z.reg, z.copas) %>% 
@@
 
-adjusted.evidence.ranef <- meta.f %>% 
+adjusted.evidence.ranef <- meta.f %>% filter(z.reg > -40) %>% 
   select(pval.se, z.fixef, z.ranef, z.reg, z.copas) %>% 
@@
 
+<<echo=FALSE, results='asis'>>=
+print(xtable(missing.differences, 
+             caption = "Missing meta-analysis pooled treatment effect and adjusted treatment effects.
+Abbreviations are used for z-score (= z) and std.
+mean difference (= d).", label = "missing.differences", align = "llcccrrrrrrrr"),
+      include.rownames = F, size = "tiny")
+@
+
 \subsection{Comparison of adjustment methods}
@@
 @
-\caption{Absolute value of z test statistics of meta-analyses and adjustment methods.
+\caption{Test statistics of meta-analyses and adjustment methods.
 The color indicates the evidence for publication bias (\textit{p} value of R\\"ucker's or Egger's test), and the dotted line depicts the diagonal through the origin.}
@@
 
-Points on the upper left side of the diagonal in Figure \ref{fig:evidence.adjustment} indicate that less evidence for a treatment effect is found in the corresponding evidence.
-Because by and large, the points are on this left side, adjustment leads mostly to smaller test statistics and $p$-values.
-The decrease in evidence is larger when using adjustment with regression, which can be expected as the uncertainity of the additional parameter from the linear regression fit to estimate publication bias is included in the uncertainity in the estimate.
-In contrast, as the Copas selection model algorithm does a sensitivity analysis, the uncertainity of additional model parameters does not affect the estimate as they are not estimated but treated as fixed (see section \ref{sec:procedure} and section \ref{sec:copas}).
+% Points lying on the diagonal through the origin indicate that there is no change in evidence after adjustment.
+In a hypothetical study with all treatment effects being artifacts of publication bias and perfect adjustment methods, all points should be distibuted on a vertical line at $x = 0$.
+A mitigation of evidence against the null hypothesis after adjustment thus is indicated by the adjusted test statistics being closer to zero.
 \\
-Also, because the algorithm returns a random effects meta-analysis estimate if no publication bias can be detected, it is hard to compare the test statistics of Copas selection model to fixed effects meta-analysis estimates, as it is not clear when the test statistic has been adjusted.
+
+It can be seen that the alignment on the diagonal changes depending on the adjustment method.
 The effect of adjustment by copas can be seen when comparing it to random effects meta-analysis.
@@
 \\
-Large adjustment in effect sizes and test statistics is not necessarily accompained by evidence for publication bias in regression adjustment, as discussed previously.
-It is also illustrated by the clear green dots in Figure \ref{fig:evidence.adjustment} far off from the diagonal.
-Evidence for publication bias and large decrease in evidence seem to be correlated.\\
-Some cases which have more evidence for treatment efficacy after adjustment (dots below the diagonal) have evidence for publication bias, which is not expected, since the publication bias tests applied are one-sided and only test for bias towards large effects.
-Thus, dots below the diagonal should all be clear green.
+Thus, the decrease in evidence is larger when using adjustment with regression, which can be expected as the uncertainity of the additional parameter from the linear regression fit to estimate publication bias is included in the uncertainity of the estimate.
+In contrast, as the Copas selection model algorithm does a sensitivity analysis, the uncertainity of additional model parameters does not affect the estimate as they are not estimated but treated as fixed (see section \ref{sec:procedure} and section \ref{sec:copas}).\\
+Large adjustment in effect sizes and test statistics is not necessarily accompained by evidence for publication bias (color of the dots) in regression adjustment, as already discussed.
+The dark dots can be found more often far away from the diagonal.
+Some cases which have more evidence for treatment efficacy after adjustment have evidence for publication bias, which is not expected, since the publication bias tests applied are one-sided and only test for bias towards large effects.
 \\
-After investigation, it has been found that the increase in evidence for treatment effect is most often because the sign of the treatment effect changes, which can not be seen when the absolute value of the z statistic is plotted (24 out of 37 cases where evidence increased after adjustment by regression compared to fixed effects meta-analysis and the $p$-value for publication bias was below 0.1).
-In other cases, the automatic detection of the side on which publication bias was expected (section \ref{sec:procedure}) may failed, because few significant effects are given (used to define side of bias) and the weighted mean effect is close to zero, in which case it is difficult to detect the side of publication bias beforehand.\\
-However, there are some adjustments with large increase in evidence and clear dark orange color, as in the left plot in Figure \ref{fig:evidence.adjustment} (the three points close to x = 10). 
+In some cases, the automatic detection of the side on which publication bias was expected (section \ref{sec:procedure}) might failed, because few significant effects are given (used to define side of bias) and the weighted mean effect is close to zero, in which case it is difficult to detect the side of publication bias beforehand.
+There are some adjustments with large increase in evidence and clear dark orange color, as in the plots on the right hand side in Figure \ref{fig:evidence.adjustment}.
+Two of them are investigated in detail.
 \begin{itemize}
@@
 
-<<echo=FALSE, results='asis'>>=
-print(xtable(missing.differences, 
-             caption = "Missing meta-analysis pooled treatment effect and adjusted treatment effects.
-Abbreviations are used for z-score (= z) and std.
-mean difference (= d).", label = "missing.differences", align = "llcccrrrrrrrr"),
-      include.rownames = F, size = "tiny")
-@
+\section{Publication Bias over Time}
+To test if publication bias in meta-analses has decreased over time and newer meta-analyses have less bias, a generalized linear model has been set up. \\
+The dependent variable is the standardized mean differences (therefore, from \texttt{outcome.flag} = \texttt{IV}, only the std.
+mean differences are used).
+As before, the std.
+mean difference is mirrored to one side by multiplying with the sign of the expected side of bias, \ie -1 or 1.
+The explanatory variable is the standard error, and the weights are the inverse of the variance of the std.
+mean difference.
+Additionally, random effects for the meta-analysis and for the review are added, the former being nested in the latter.
+Figure \ref{fig:smds} shows the complete dataset with the fit of the previously described model (dotted red line).
+The details and evidence for the small study effects in the generalized linear model are given in table \ref{anova.small.study}, the coefficients in table \ref{coefficients.small.study}
+
+\begin{figure}
+<<echo = FALSE, message = FALSE, warning = FALSE, fig.height=4>>=
+##-------Prepare data--------#
+reg.dat <- data.ext2 %>% filter(meta.id %in% meta.id.vector) #Filter meta-analysis data
+
+#Mirror all effects on one positive side:
+reg.dat <- reg.dat %>% group_by(meta.id) %>% 
+  mutate(bias.side = bias.side.fct2(outcome = outcome.flag, 
+                                    outcome.measure.merged = outcome.measure.merged, 
+                                    lrr = lrr, var.lrr = var.lrr, smd = cohensd, 
+                                    var.smd = var.cohensd, effect = effect, se = se),
+  smd.pool = smd.pool * bias.side) #Mirror effect sizes on one side
+
+#Get tau^2 based on smd's and introduce new study se:
+reg.dat <- reg.dat %>% group_by(meta.id) %>% 
+  mutate(tau.squared = metagen(TE = smd.pool, seTE = se.smd.pool)$tau^2,
+         new.se.smd = sqrt(se.smd.pool^2 + tau.squared))
+
+reg.dat <- reg.dat %>% filter(se.smd.pool != 0) %>% filter(!is.na(smd.pool)) %>% 
+  filter(!is.na(se.smd.pool))
+
+#Get review publication year:
+reg.dat <- merge(reg.dat, data.review[,c("id", "year")], by = "id")
+reg.dat <- reg.dat %>% filter(se.smd.pool < 3)
+
+reg.dat <- reg.dat %>% ungroup() %>% 
+  mutate(rev.year.center = scale(scale = F, center = T, x = year)[,1]) 
+study.number.review.model <- dim(reg.dat)[1]
+small.study.fit <- lme(fixed = smd.pool ~ se.smd.pool, random = list(~ 1 | id, ~ 1 | meta.id),
+                       weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
+plot(y = reg.dat$smd.pool, x = reg.dat$se.smd.pool, cex = .1, xlab = "standard error", ylab = "std. mean difference")
+small.study.fit.coef <- summary(small.study.fit)$coefficients$fixed
+abline(a = small.study.fit.coef, col = "red", lty = 2)
+
+lmer.table <- function(model){
+  sum <- summary(model)
+  estimate <- round(sum$coefficients$fixed)
+  ci <- intervals(model)
+  tb <- data.frame(estimate = round(ci$fixed[,2], 3), CI = round(ci$fixed[,c(1,3)], 3))
+  colnames(tb)[c(2,3)] <- c("2.5%CL", "97.5%CL")
+  return(tb)
+}
+@
+\caption{Std. mean differences of all meta-analyses plotted against their standard error, with the fit of a generalized linear model (dotted red line).}
+\label{fig:smds}
+\end{figure}
+
+<<echo =FALSE, results='asis', warning=FALSE>>=
+null.fit <- lme(fixed = smd.pool ~ 1, random = list(~ 1 | id, ~ 1 | meta.id),
+                       weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
+print(xtable(anova(null.fit, small.study.fit)[,-1], caption = "Anova table for a generalized linear model for small study effects compared to the null model.
+'small.study.fit' denotes the model with random intercepts for meta-analyses and reviews.", label = "anova.small.study"), size = "scriptsize")
+@
+
+<<echo =FALSE, results='asis', warning=FALSE>>=
+print(xtable(lmer.table(small.study.fit), align = "lccc", 
+             caption = "Coefficients and 95\\% confidence limits of the generalized linear model.
+'se.smd.pool' denotes the standard error of the std.
+mean difference.", label = "coefficients.small.study"),  size = "scriptsize")
+@
+
+It is possible to include meta-analysis specific random slopes.
+Before continuing, it is tested if incorporation of random slopes improves model fit.
+Table \ref{anova.random.slopes} shows the anova table for a model with and without random slopes.
+
+<<echo =FALSE, results='asis', warning=FALSE>>=
+small.study.rs.fit <- lme(fixed = smd.pool ~ se.smd.pool, 
+                          random = list(~ 1 | id, ~ meta.id | meta.id),
+                       weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
+print(xtable(anova(small.study.fit, small.study.rs.fit)[,-1], caption = "Anova table for two generalized linear model fits.
+'small.study.fit' denotes the model with random intercepts for meta-analyses and reviews, 'small.study.rs.fit' the model with additional random slopes per review.",
+             label = "anova.random.slopes"), size = "scriptsize")
+@
+
+Model diagnostics indicate that there is no benefit in including random slopes for the single meta-analysis. \\
+To test if publication bias varies over time, we include the year of the publication of the review as an additional explanatory variable.
+Ulitmately, it is of interest if there is an interaction between the small study effect (publication bias) and time, i.e.
+if the slope varies depending on the year.
+Because such a model is nested in a more simpler model where the study year is only an additive effect, all these models are fitted.
+Table \ref{anova.lme} displays model fit diagnostics.
+
+<<results = 'asis', echo = FALSE>>=
+year.fit <- lme(fixed = smd.pool ~ se.smd.pool + rev.year.center, 
+                random = list(~ 1 | id, ~ 1 | meta.id),
+                weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
+year.int.fit <- lme(fixed = smd.pool ~ se.smd.pool * rev.year.center, 
+                    random = list(~ 1 | id, ~ 1 | meta.id),
+                weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
+print(xtable(anova(small.study.fit, year.fit, year.int.fit)[,-1], caption = "Anova table for three generalized linear model fits.
+'small.study.fit' denotes the model with the standard error as explanatory variable, 'year.fit' the model with standard error and the centered (- 2013) review year as explanatory variable, and 'year.int.fit' the model with interaction between the two.",
+             label = "anova.lme"), size = "scriptsize")
+@
+
+Because neither AIC, BIC ot the F-test do show any improvement of model fit, it does not seem as if publication bias has substantially decreased or increased over the years.
+The review publication year is however not directly tied to the publication year of the studies that are affected by publication bias.
+Thus, using another measure of time, the results may be different.
+Thus, the models are re-fitted with the study publication years.
+
+<<results = 'asis', echo = FALSE>>=
+reg.dat <- reg.dat %>% filter(!is.na(study.year)) %>% ungroup() %>%  
+  mutate(study.year.center = study.year - mean(study.year))
+study.number.study.model <- dim(reg.dat)[1]
+small.study.fit <- lme(fixed = smd.pool ~ se.smd.pool, random = list(~ 1 | id, ~ 1 | meta.id),
+                       weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
+year.fit <- lme(fixed = smd.pool ~ se.smd.pool + study.year.center, 
+                random = list(~ 1 | id, ~ 1 | meta.id),
+                weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
+year.int.fit <- lme(fixed = smd.pool ~ se.smd.pool * study.year.center, 
+                    random = list(~ 1 | id, ~ 1 | meta.id),
+                weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
+print(xtable(anova(small.study.fit, year.fit, year.int.fit)[,-1], caption = "Anova table for three generalized linear model fits.
+'Small study fit' denots the model with the standard error as explanatory variable, 'year.fit' the model with standard error and the centered (- 2000) study year as explanatory variable, and 'year.int.fit' the model with interaction between the two.",
+             label = "anova.lme"), size = "scriptsize")
+@
+
+The analysis of model fit indicates that there is an improvement when using the study year as a covariate, but only as an additive effect.
+AIC and BIC are smaller and the $p$-value of the F-test is very small.
+However, not the size of the effect, but the slope of the linear regression fit would have to be decreased to ultimatively conclude a decrease of publication bias over the years.
 

### 2019-08-02 report/chapter05.Rnw
appendix, corrected IV results

--- 2019-05-13 report/chapter05.Rnw
@@
 
-\chapter{Discussion}
+<<echo=FALSE, warning=FALSE>>= 
+#Load data:
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2019-07-04.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results_new')
+# PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
 
-It is tempting to claim to have a perspective that spans the entire clinical research when looking at the cochrane dataset.
-Several points can be made to argue in this favor (see chapter 2 CITE for details).
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
 
-\begin{itemize}
-\item Size: Over 52,000 studies, 20,000 comparisons and 47 millions study participants.
-A vast diversity of topics and studies that stem from different institutions and researchers and have been conducted in different countries.
-\item Quality: An organization of field and analysis experts controls quality of both studies and methods.
-\end{itemize}
+load(file.path(PATH_DATA, "PubBias_2019-07-19.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
+load(file.path(PATH_RESULTS, "meta_id_I2.RData"))
+load(file.path(PATH_RESULTS, "meta.bin.RData"))
+load(file.path(PATH_RESULTS, "meta.cont.RData"))
+load(file.path(PATH_RESULTS, "meta.iv.RData"))
+#----------------------------------------------------------------------------------------------------#
 
-The dataset is certainly unique with respect to this features.
-The effort of the Cochrane Organization in reprocession, classification and integration of studies in a larger scientific framework is unmatched, not only in clinical science, but in empirical science in general CITE?CITE.
-Regardless whether it is representative of the field of clinical research, it thus provides an exceptional perspective, not only on clinical science, but on empirical science in general.
+adjustment.diff.keep <- meta.f %>% 
+  mutate(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
+                                 sign(est.copas) != sign(est.fixef) ~ -abs(est.copas)),
+         est.reg.f = case_when(sign(est.reg) == sign(est.fixef) ~  abs(est.reg),
+                               sign(est.reg) != sign(est.fixef) ~ -abs(est.reg)),
+         est.copas.r = case_when(sign(est.copas) == sign(est.ranef) ~  abs(est.copas),
+                                 sign(est.copas) != sign(est.ranef) ~ -abs(est.copas)),
+         est.reg.r = case_when(sign(est.reg) == sign(est.ranef) ~  abs(est.reg),
+                               sign(est.reg) != sign(est.ranef) ~ -abs(est.reg)),
 
-\vspace{0mm}
-Concerning the generalizability of results of this thesis on clinical science, there are important caveats.
-First of all, intrinisically, the Cochrane Organization focuses on established research of public interest.
-By definition, it can not comprise the full diversity of the field, and especially where research and evidence is new, sparse and not established, it is almost certainly not included.
-The aim of Cochrane is to concentrate scientifical knowledge, thus it can not incorporate studies that are unique in their research subjects and are on the ``periphery'' of science.
+         est.d.copas.f = case_when(sign(est.d.copas) == sign(est.d.fixef) ~  abs(est.d.copas),
+                                   sign(est.d.copas) != sign(est.d.fixef) ~ -abs(est.d.copas)),
+         est.d.reg.f = case_when(sign(est.d.reg) == sign(est.d.fixef) ~  abs(est.d.reg),
+                                 sign(est.d.reg) != sign(est.d.fixef) ~ -abs(est.d.reg)),
+         est.d.copas.r = case_when(sign(est.d.copas) == sign(est.d.ranef) ~  abs(est.d.copas),
+                                   sign(est.d.copas) != sign(est.d.ranef) ~ -abs(est.d.copas)),
+         est.d.reg.r = case_when(sign(est.d.reg) == sign(est.d.ranef) ~  abs(est.d.reg),
+                                 sign(est.d.reg) != sign(est.d.ranef) ~ -abs(est.d.reg)),
 
-\vspace{0mm}
-It is said in the Cochrane Handbook that Cochrane Field groups orchestrate the efforts of their groups and set emphasis on certain research.
-It is thus clear, that the Cochrane Library only comprises a selective fraction of clinical research.
+         est.z.copas.f = case_when(sign(est.z.copas) == sign(est.z.fixef) ~  abs(est.z.copas),
+                                   sign(est.z.copas) != sign(est.z.fixef) ~ -abs(est.z.copas)),
+         est.z.reg.f = case_when(sign(est.z.reg) == sign(est.z.fixef) ~  abs(est.z.reg),
+                                 sign(est.z.reg) != sign(est.z.fixef) ~ -abs(est.z.reg)),
+         est.z.copas.r = case_when(sign(est.z.copas) == sign(est.z.ranef) ~  abs(est.z.copas),
+                                   sign(est.z.copas) != sign(est.z.ranef) ~ -abs(est.z.copas)),
+         est.z.reg.r = case_when(sign(est.z.reg) == sign(est.z.ranef) ~  abs(est.z.reg),
+                                 sign(est.z.reg) != sign(est.z.ranef) ~ -abs(est.z.reg)),
 
-\vspace{0mm}
-Although Cochrane strives to include unpublished study results, it almost certainly provides a selective view by including more published studies.
-Apart from language issues, publication bias might be the largest source of bias.
-This leads us to the main topic of this masters thesis: small study effects and publication bias in the Cochrane Library.
-Thus, the research question of this thesis is in fact connected to the question of how representative the Cochrane Library is for clinical research.
-The answer to this question is insofar important, as that the issues treated in this thesis have to be addressed to the Cochrane Organization or to clinical science in general.
-This distinction is very important and will be encountered throughout the next pages.
+         est.fixef = abs(est.fixef),
+         est.ranef = abs(est.ranef),
+         est.z.fixef = abs(est.z.fixef),
+         est.z.ranef = abs(est.z.ranef),
+         est.d.fixef = abs(est.d.fixef),
+         est.d.ranef = abs(est.d.ranef))
 
-%The conclusions to which one comes with regard to this question directly influence the meaning of the results. 
-% If one decides that the results can not be representative for clinical science, the results mainly concern the work of the Cochrane organization.
-If one decides that the results do at least partially hold for clinical science and science in general, the interpretation of the results change also.
+truebias.bin.percentage <- round(adjustment.diff.keep %>% filter(outcome.flag == "DICH") %>% filter(est.fixef - est.reg > 0) %>% count()/(dim(meta.bin)[1])*100,1)
 
-\section{Meta-analyses}
-If one investigates the success of a treatment, the first way of doing so is to investigate to what extent the treatment effect estimate differs from no treatment effect.
-This is usually done by a hypothesis test, where the null hypothesis of no treatment effect is rejected if the p-value of the treatment effect estimate is above a given threshold.
-One decides in this case in favor of the treatment.
+wider.dataset.ioannidis.comparison <- data.ext2 %>% filter(outcome.flag == "DICH") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% summarise(n()) %>% ungroup() %>% count()
 
-\vspace{0mm}
-The aim of a meta-analysis is to re-calculate the treatment effect based on multiple results.
-The treatment effects are pooled and the pooled treatment effect estimate can then again be tested based on the null-hypothesis.
-Although not commonly accepted, this may be a stronger argument for the success of treatment, because meta-analysis can capture consistency among treatment effect estimates among different studies and will result in rejection of a null hypothesis if consistency is given.
-It is thus in line with the empirical principle that experimental findings should be validated based on their reproducibility.
-Consequently, a meta-analysis may provide a significant treatment effect estimate, even if the single results do not.
+restr.dataset.ioannidis.comparison.count <- data.ext2 %>% filter(outcome.flag == "DICH") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>%  ungroup() %>% distinct(id, .keep_all = T) %>% count()
 
-\vspace{0mm}
-It was the aim of the first section CITE of the results part to compare significance of the treatment effect of single studies with the significance of the pooled effect.
-So the question to be answered was: How does significance in single studies relate to significance when all evidence is included?
-The first kind of significance has been termed primary significance and the second, secondary significance.
-One can imagine 3 scenarios:
-\begin{itemize}
-\item A primary significant study belongs to a group which, overall, can not reject the null-hypothesis of no treatment effect in meta-analysis.
-The study result is then overruled by the result of the meta-analysis (if one is to accept that meta-analysis is a more stringent rule for decision about treatment effects).
-\item The opposite: A non-significant primary study belongs to a group which has a significant pooled treatment effect estimate. The study failed to find evidence for a ``true'' effect.
-\item Primary and secondary significance remain unchanged after meta-analysis.
-\end{itemize}
+restr.dataset.ioannidis.comparison <- (data.ext2 %>% filter(outcome.flag == "DICH") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>%  ungroup() %>% distinct(id, .keep_all = T) %>% count() / wider.dataset.ioannidis.comparison)*100
 
-The amount of overlap between primary and secondary significance was moderate, as it had to be expected based on the methodology of meta-analysis.
-The vast amount of non-significant primary results that contribute in the end to a significant secondary meta-analysis result is compelling.
-This links to the topic of the masters thesis of small study effects and publication bias.
-One ad-hoc interpretation of publication bias is that results that are not significant are less likely to be published (arguably because they show no treatment effect).
+largerten.ioannidis.comparison <- (data.ext2 %>% filter(outcome.flag == "DICH") %>% group_by(meta.id) %>% filter(n() > 9) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>% summarise(n()) %>% ungroup() %>% count() / wider.dataset.ioannidis.comparison)*100
 
-\vspace{0mm}
-If one is to prefer, or accept meta-analysis as a way to assess treatment effect evidence, the result provides a strong argument for publication of non-significant results, because they can contribute to evidence for treatment effects in meta-analysis (in a Cochrane review).
-Significant treatment effects that are found may find their into clinical practice and potentially benefit there patients and consumers.
+variance.ratio.ioannidis.comparison <- (data.ext2 %>% filter(outcome.flag == "DICH") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>% filter((max(se)^2)/(min(se)^2) > 4) %>% summarise(n()) %>% ungroup() %>% count() / wider.dataset.ioannidis.comparison)*100
+
+onesig.ioannidis.comparison <- (data.ext2 %>% filter(outcome.flag == "DICH") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>%
+  filter(sum(pval.single < 0.05, na.rm = T) > 0) %>% summarise(n()) %>% ungroup() %>% count() / wider.dataset.ioannidis.comparison)*100
+
+allcriteria <- (dim(meta.bin)[1]/wider.dataset.ioannidis.comparison)*100
+
+harbord.ioannidis.comparison <- (meta.bin %>% filter(pval.harbord < 0.1) %>% count()/dim(meta.bin)[1])*100
+
+own.results <- c(wider.dataset.ioannidis.comparison$n, paste(round(c(largerten.ioannidis.comparison$n, variance.ratio.ioannidis.comparison$n, onesig.ioannidis.comparison$n, allcriteria$n,
+                       harbord.ioannidis.comparison$n)), "%", sep = ""))
+
+ioannidis.results <- c(6873, paste(c(13, 72, 55, 5, 12), "%", sep = ""))
+
+comparison.ioannidis <- data.frame(Ioannidis = ioannidis.results, Thesis = own.results)
+rownames(comparison.ioannidis) <- c("Wider dataset (n)", "study number > 10", "variance ratio > 4",
+                                    "study sig. number > 1", "all exclusion criteria", "harbord test p-value < 0.1")
+
+@
+
+\chapter{Discussion} \label{ch:Discussion}
+
+\section{Results in the light of the Literature}\label{sec:discussion.results}
+
+Before discussing the results of the previous analyses, some results of similar studies are discussed briefly and compared to the results of this study, if possible.
+When clear methodological drawbacks are found in the analysis, the reader is referred to chapter \ref{ch:methods} for comments on the disadvantages.
+The amount of studies analysing publication bias makes it not possible to discuss any of them, and thus we only some interesting and/or representative examples are shown.
+
+\subsection{\citet{Egger}}
+The Cochrane database (1996 issue 2) and publications from the four leading medicine journals (the Lancet, BMJ, JAMA and Annals of Internal Medicine) between 1993 and 1996 were used to find systematic reviews with randomized controlled trials for the application of Egger's small study effect test.
+They included 38 meta-analyses with at least 5 studies and binary outcomes from the Cochrane Library and 37 from the journals.
+Five (13\%) meta-analyses from Cochrane and 13 (38\%) from the journals had significant two sided small study effect test results ($p$-value < 0.1).
+Also, they found that test-statistics were more often negative, which correspondend in their setup to larger effects in small studies.
+(\Sexpr{round(((24/38))*100, 1)} among Cochrane meta-analyses and \Sexpr{round(((26/37))*100, 1)} for journal meta-analyses).
+The results from this report with R\"ucker's test are: \Sexpr{round((length(which(meta.bin$pval.rucker < 0.1))/dim(meta.bin)[1])*100,1)}\%, and when using regression adjustment to decide about the direction of publication bias, we get \Sexpr{truebias.bin.percentage$n}\%.
+
+\subsection{\citet{sutton.2000}}
+Out of 397 systematic reviews from the Cochrane database (complete number for 1998, issue 3), 49 had more than ten included studies and binary outcomes and 48 compared two treatments.
+They were analysed by trim-and-fill method \citep{trimfill} to detect and adjust for funnel plot asymmetry (similar to small study effect tests, but the method is known to overestimate bias).
+23 were found to have missing studies, and eight had more than three missing studies which was considered to be significant publication bias.
+Additionally, they found that three estimates of random effects meta-analysis became non-significant after adjustment, and one became significant (by negative adjustment).
+The results are difficult to compare, but the methodological limitations make this findings unreliable.
+
+\subsection{\citet{Ioannidis2007}}
+Data processing steps were however different, and only binary outcomes as used in two-by-two tables were analysed.
+The approximately corresponding numbers are put in parentheses for comparison.
+The Cochrane Library from 2003 (issue 2) was used.
+After removal of duplicates and intractable meta-analyses, they had 6,873 meta-analyses with more than two studies left (\Sexpr{format(wider.dataset.ioannidis.comparison$n, big.mark = ",")}).
+When only using one meta-analysis per review, this reduced to 846 (\Sexpr{format(restr.dataset.ioannidis.comparison.count$nn, big.mark = ",")}.
+Then, the criteria that have also been applied in this masters thesis are applied: $I^2 < 0.5$, variance ratio of smallest and largest effects > 4, at least one significant study result and at least 10 studies to be used.
+Afterwards, they applied Harbord's, Egger's and Begg's Test to the dataset.
+The reader can compare some corresponding numbers in Table \ref{ioannidis}.
+% The results seem to be similar enough to claim that neither the methods nor the data and it's results are differing substantially.
+Because the thesis relies on more data, it is likely to be more accurate and can possibly add to the findings of \citet{Ioannidis2007}.
+
+<<echo = FALSE, results = 'asis'>>=
+print(xtable(comparison.ioannidis, caption = "Comparison of results from Ioannidis et.al.
+(2007) to the results of the thesis.
+The percentage of meta-analysis which match all exclusion criteria denotes the ones that apply to all criteria in the table plus the small heterogeneity criterium.
+Harbord test is two-sided.", label = "ioannidis", align = "lrr"))
+@
+
+\subsection{\citet{souza.2007}}
+Reviews of the World Health Organization (WHO) Reproductive Health Library (RHL), issue 9, were analysed with the trim-and-fill method.
+The RHL reproduces and expands reviews from the Cochrane Library with implications for developping countries.
+21 of 105 reviews contained more than ten studies and were used.
+Trim-and-fill found asymmetry in 18 of 21 studies, and 10 had more than 3 missing studies (``significance'').
+Two of those and one with one missing studies found no evidence for treatment effects after the 0.05 $p$-value threshold after adjustment by trim-and-fill.
+
+\subsection{\citet{kicinsky}}
+The author uses a bayesian hierarchical selection model, but does not analyse treatment effects, but the parameters of the weight function of the selection model, which is estimated with a bayesian approach and MCMC sampling.
+\\
+The author provides an estimate of the probability of including significant findings versus non-significant findings in Cochrane meta-analyses over time.
+The data is from the Cochrane Library from 2013 (issue number not provided).
+The author excluded treatment - treatment comparisons and analysed safety and efficacy meta-analyses separately (how this was achieved is not documented in the paper).
+\\
+From 3845 reviews, the author separated 907 reviews with more than ten studies.
+From those, 539 compared placebo to treatment.
+After removing duplicates and sensitivity analyses, 358 analyses with 1297 meta-analyses remained.
+From these 191 were excluded because they comprised overall mortality and withdrawal, because these could not clearly be specified as safety or efficacy, respectively.
+\\
+1106 meta-analyses from 329 meta-analyses, containing 802 efficacy and 304 safety meta-analyses.
+The median publication year per meta-analysis was 1997 for efficacy meta-analyses and 1999 for safety meta-analyses.
+Then, a bayesian two-step hierarchical selection model was applied (\citet{bayesian.selection.model}, \citet{bayesian.selection.model.2}).
+It assumes that the selection process is a two-step weight, which assigns different probabilities to non-significant and significant effects.
+Thus, a ratio of publication probability between significant and non-significant study estimates using a two-step weight function.
+The model was fitted with the Monte-Carlo Markov-Chain algorithm STAN and the geometric mean was used as an estimate for the publication probability ratio.
+Simulations performed in \citep{bayesian.selection.model} indicate that the method performes well if the true mean effect size was not small, and also robust to small study effects.
+It outperformed Egger's test and Begg's test in assessing publication bias, especially when small study effects were absent, and had lower false-positive rates.
+\\
+The results showed a clear publication bias for significant results for efficacy meta-analyses (27\% higher for significant studies, 95\%CI credible intervals: 1.18 to 1.36).
+The probability was more than twice as high in 27\% of the meta-analyses (95\% CI: 23\% to 31\%).
+But the probability decreased: from 1.65 (95\% CI: 1.31 to 2.15) in 1980 (average publication year) to 1.36 (95\% CI: 1.17 to 1.62) in 1990 to 1.18 (95\% CI: 1.04 to 1.33) in 2000.
+For sake of completeness, the probability of inclusion was  1.78 (95\% CI: 1.51 to 2.13) larger for non-significant safety effect estimates, but again, decreased with time (1.77, 95\% CI: 1.46 to 2.21 in 2000).
+The results are in line with the results from this study, but it was not possible to reafirm the finding of weaker publication bias in reviews published more frequently.\\
+
+\subsection{\citet{vanAert.2019}}
+The Authors of this recent study sample 366 meta-analyses randomly from the Cochrane Library (supposedly 2018 or 2019, not mentioned).
+They exclude any meta-analysis which include effect sizes identical to effect sizes in other meta-analyses (the larger meta-analysis is retained).
+Additional criteria were: $I^2 < 0.5$ and at least 5 studies.
+The meta-analyses were analysed using standardized mean differences and four different tests for publication bias: Egger's test, p-uniform test \citep{p.uniform}, Begg and Mazumdar's rank correlation test and the excess significance test.
+\\
+The authors found, based on the significance threshold of $p$ < 0.1, the following results (own results in brackets):
+12.2 \% significant results from Egger's test (\Sexpr{round((length(which(meta.bin$pval.rucker < 0.1)) + length(which(meta.cont$pval.egger < 0.1)) + length(which(meta.iv$pval.egger < 0.1)))/dim(meta.f)[1]*100,1)}),
+8.5 \% significant results from Begg and Mazumdar's rank correlation test (\Sexpr{round((length(which(meta.bin$pval.schwarzer < 0.1)) + length(which(meta.cont$pval.begg < 0.1)) + length(which(meta.iv$pval.begg < 0.1)))/dim(meta.f)[1]*100,1)}) and
+4.4 \% significant excess significance test results (\Sexpr{round((length(which(meta.f$pval.d.tes < 0.1))/dim(meta.f)[1])*100, 1)}).
+It is known that the publication bias tests are lacking power in general as sample size is usually small.
+Decreasing sample size will result in lower power, especially if the maximal sample size is $n \geq 5$.
+Additionally, it was also not taken into consideration that it may be difficult to state that publication bias is present in a meta-analysis when no result within it is statistically significant (only 18.8 \% of the effects of the sampled meta-analyses were).
+This, together that it has not been tried to exclude safety outcomes, may account for the large differences between the results.
+\\
+The author's come to the conclusion in their study that in contrast to other studies, they find few evidence for publication
+
+\subsection{Further Studies on Publication Bias}
+\citet{Zhang.2013} find publication bias in critical care studies with similar methods.
+\citet{Nusch} report publication bias in clinical osteoarthritis research because of funnel plot asymmetry and pledge for routine assessment of publication bias.
+\citet{Dechartres.2013} analyse publication bias based on sample size in meta-analyses from top journals and Cochrane reviews in 93 Meta-analyses and find that, for example, effects in trials with less than 50 patients were 48\% larger than in larger trials.
+\citet{Onishi.2014} find that in 36 Meta-Analyses without comprehensive literature research, there ar 19.4\% significant publication bias tests (Egger's test).
+
+\section{Interpretation}
+In this study, a proportion of the meta-analyses that have been scrutinized have publication bias.
+Since regression and rank test have been applied one-sided, they have very likely larger effects in smaller studies that in larger studies.
+\\
+There have been proposed a number of reasons for this tendencies in smaller studies (see \citet{Egger} for a thorough discussion).
+In clinical settings, it might be that the requirement for more study participants in large studies might systematically change the study population.
+However, this systematic differences could influence the results in two ways: If recruitement of participants with a disease is difficult, and thus, also participants with less severe types of the disease are included, it might be that the effect of treatment is larger in the smaller study.
+But one could also argue that the opposite could eventually be the case.
+\\
+The main cause for funnel plot asymmetry with smaller studies having larger effects is publication bias.
+Publication bias enforces questionable research practices from researchers such as selective outcome reporting, $p$-hacking and data fabrication.
+Larger studies are less affected, and have also in general higher methodological quality \citep{Egger}, which leads to smaller effect sizes.\\
+Presence of publication bias in meta-analyses can ultimately lead to patient harm, because decision makers in clinical practice use the meta-analyses to take decisions if they use a treatment.
+On the swiss Cochrane website, it is stated that Cochrane is the ``single most reliable source of evidence on the effects of health care''.
+However, publication bias does in general lead to too large confidence in the results of the meta-analyses.
+In some cases, it might be that the  evidence for a treatment in a meta-analysis is an artifact of publication bias.
+Besides harm to patient, this can cause a waste of ressources.
+\\
+The comparison of the results with previous analyses of publication bias in the Cochrane Database of Systematic Reviews implies gives more confidence in the results of this study, because they are largely in line.
+\\
+
+\section{Limitations}
+After application of the criteria of \citet{Ioannidis2007}, there are left \Sexpr{round((740/6354)*100, 1)} \% of the reviews and \Sexpr{round((23243/70662)*100, 1)}\% of the studies.
+It is not clear how the results would be in the remaining dataset if tests were applicable.
+The most restrictive criterium of exclusion was that a meta-analysis has to have at least ten studies.
+Thus, in the data that is scrutinized, there has been enforced and ongoing research.
+\citet{ioannidis.2005} state that publication bias is also a consequence of modern discovery oriented research, and thus it may well be that publication bias is also an issue when the number of studies are lower.\\
+It also has to be said that the removal of safety outcomes is only partially successfull.
+This is an issue, because it is not well known if and how publication bias affect safety outcomes.
+\citet{kicinsky} suggests that they are inversely affected, with editors publishing in favor of non-significant adverse effects.
+\\
+Also, it has been previously discussed that the method to detect the side on which bias is to be expected can fail and provide meaningless results, in which case a two-sided test is more meaningful.
+However, one could also discuss in more general terms if one can speak of publication bias in meta-analyses that have only one significant effect out of ten ($n$ = \Sexpr{length(which(meta.f$n.sig.single == 1))}).
+\\
+There is also criticism that one can address on the methods.
+It is possible that the results are caused by systematic differences in the population of study participants only.
+This is considered rather unlikely.
+Other cirticism is more severe.
+The small study effect tests fail to account for statistical significance, however, this is a major component of publication bias.
+Small study effect test work because they take into account that smaller studies need larger effects to be significant.
+The only test that is applied that takes into account statistical significance per se is the excess significance test.
+When looking at it's results, it seems as if it is rather a test for between study heterogeneity per se, because it does agree very poorly with small study effect tests, and finds almost no excess significance in tests with $I^2 = 0$.
+The choice of the effect size and proxy of the study size is crucial when assessing publication bias.
+It is not clear which measure of effect size should be used when applying the test; the original measure (\eg a mean difference) may have standard errors that do not only depend on study size, but journal editors use this measure as the basis for their decision of publication.
+Fisher's $z$ transformed correlations have standard errors that are a function of study participant number only, but in contrast the effect size is bounded at$[-1,1]$, making it less suitable for linear regression.
+Standardized mean differences are possibly a good compromise.\\
+The ciriticism also applies for adjustment methods, as they also do not use statistical significance but the size of the effects.
+A weakness of the regression adjustment is that it also adjusts if the uncertainity in the small study effect is large.
+To compare it in this case with the meta-analysis estimate is difficult because the uncertainity in estimating the small study effect affects the uncertainity of the treatment effect.
+It is not clear how to proceed when one wants to adjust for publication bias.
+Copas selection model uses the $p$-value threshold of 0.1 to decide if adjustment is necessary or not.
+One can argue that this threshold is arbitrary.
+Additionally, the threshold is used in two manners: first to decide if adjustment is necessary at all, and secondly, if the adjusted model does suitably account for publication bias ($p$ > 0.1).
+Hypothesis tests against the null hypothesis can however not be used to decide in favor of the null-hypothesis, and a separate test would be needed there.
+\\
+With Copas selection model, it is in general the issue that it the model is not estimating, but rather applying some criteria of parsimony (the model with least publication bias with $p$-value for small study effect > 0.1 is chosen).
+Some authors find in their simulation studies that regression methods overperform the Copas selection model \citep{limitmeta}.
+\\
+Thus, the results are not exact and could be improved if more suitable methods are applied.
+The bayesian approach taken by \citet{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions.
+\\
+
+\section{Outlook}
+Given the size and abundancy of information in the dataset, the possibilities to investigate sources of bias in the Cochrane Database of Systematic Reviews are not exhausted (see for example in \citet{ioannidis.2017}).
+In particular, one could easily come up with more hypotheses that could be tested in meta meta-regression, as introduced in the last section of the results.
+\\
+There are numerous suggestions for diffeerent measures of publication bias and small study effects, which could be applied on the dataset (see \citet{mueller.2016}).
+This study mainly relies on suggestions from \citet{Sterne}, \citet{Ioannidis2007} and \citet{limitmeta}.
+It uses most often methods that are well integrated in packages (\citet{metafor.package}, \citet{meta.package}).
+Although there are well addressed, mathematical justifications for these methods, there might be better methods not yet tested on large datasets.
+An evaluation of all suggested methods was far beyond the scope of this study.
+
+\section{Implications}
+This study is so far the largest assessment of publication bias by small study effects and uses data that has been collected after major efforts have been made to curb publication bias.
+The results indicate, similarly to other studies, that the efforts did not yet resolve the issue.
+\\
+The findings further imply that when using meta-analyses, it is key to investigate sources of between-study heterogeneity; an alternative is to rely solely on the largest trials \citep{largest.study.only}.
+Since the Cochrane Organization uses results from grey literature to limit the effects of publication bias, but still does not manage to abolish it, there is also the need for journal editors to change their publication policies.

### 2019-08-02 code/Poster Plots.R

@@ -1,0 +1,139 @@
+mid <- median(meta.f$pval.se)
+
+meta.f <- meta.f %>% mutate(pval.se1 = case_when(outcome.flag == "DICH" ~ pval.harbord,
+                                                 outcome.flag == "CONT" ~ pval.egger,
+                                                 TRUE ~ NA_real_))
+
+
+method.names <- c(z.reg = "regression", z.copas = "selection model")
+
+p <- meta.f %>% filter(outcome.flag != "IV") %>% 
+  select(pval.se1, z.fixef, z.ranef, z.reg, z.copas) %>% 
+  gather(key = "method", value = "test.stat", z.reg:z.copas) %>%
+  ggplot(aes(x = test.stat, y = z.fixef, colour = pval.se1)) + 
+  facet_wrap(~ method, labeller = as_labeller(method.names)) + 
+  scale_color_gradient2(midpoint=mid, low="firebrick4", mid = "gold",
+                        high="chartreuse2", space ="Lab") +
+  geom_point(size = .7) + theme_bw() + theme(legend.position = "none") + 
+  geom_abline(slope = 1, intercept = 0, linetype = 2, size = .3) +
+  xlab("adjusted test statistic") + ylab("fixed effects test statistic")
+
+p <- meta.f %>% filter(outcome.flag != "IV") %>% 
+  select(pval.se1, z.fixef, z.ranef, z.reg, z.copas) %>% 
+  gather(key = "method", value = "test.stat", z.reg:z.copas) %>%
+  ggplot(aes(x = test.stat, y = z.ranef#, colour = pval.se1
+             )) + 
+  facet_wrap(~ method, labeller = as_labeller(method.names)) + 
+  #scale_color_gradient2(midpoint=mid, low="firebrick4", mid = "gold",
+  #                      high="chartreuse2", space ="Lab", name = expression(paste(italic(p),"-value"))) +
+  geom_point(size = 1, color = "gray29") + theme_bw() + 
+  ggtitle("Evidence for treatment efficacy") +
+  theme(legend.position = "none",
+    axis.title=element_text(size=20, margin = margin(r = 20, b = 20)), 
+    axis.title.y = element_text(size=40, margin = margin(r = 20)), 
+    axis.title.x = element_text(size=40, margin = margin(t = 20)), 
+    legend.text = element_text(size = 20), 
+        legend.title = element_text(size = 40, face = "bold"), title = element_text(size = 22),
[…]

### 2019-08-02 code/analysis.R

@@ -59,7 +59,11 @@ load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
 # meta.info.iv <- data.ext2 %>%
 #   group_by(meta.id) %>%
 #   mutate(n.pre = n()) %>% filter(n.pre >= 10) %>%
-#   filter(outcome.flag == "IV") %>%
+#   filter(outcome.flag == "IV") %>% 
+#   filter(!all(effect == 0)) %>%  #Has no effects != 0
+#   filter(outcome.measure.merged == "Rate Ratio" | outcome.measure.merged == "SMD" |
+#            outcome.measure.merged == "MD" | outcome.measure.merged == "Hazard Ratio" |
+#            outcome.measure.merged == "OR" | outcome.measure.merged == "RR") %>%
 #   summarize(dupl.remove = unique(dupl.remove),
 #             id = unique(id),
 #             outcome.desired = unique(outcome.desired),
@@ -95,13 +99,14 @@ load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
 # exclusion.estimates <- cbind(
 #   meta.id = meta.id.vector.org.ranef,
 #   n = unlist(lapply(meta.org.ranef.list, FUN = function(meta.analysis){meta.analysis$k})),
-#   Q = unlist(lapply(meta.org.ranef.list, FUN = function(meta.analysis){meta.analysis$QE})))
+#   Q = unlist(lapply(meta.org.ranef.list, FUN = function(meta.analysis){meta.analysis$QE})),
+#   I2 = unlist(lapply(meta.org.ranef.list, FUN = function(meta.analysis){meta.analysis$I2})))
 # 
 # 
 # meta.info.pre2 <- merge(meta.info, exclusion.estimates, by = "meta.id")
-# meta.info.I2 <- meta.info.pre2 %>% rowwise() %>% mutate(I2  = max(0, (Q - n + 1)/Q)) #calculate I2
-# meta.info <- meta.info.I2 %>% filter(n > 9) %>% filter(I2 < 0.5)
-# meta.id.vector <- meta.info$meta.id #Vector of meta-ids that match the criteria.
+# #meta.info.I2 <- meta.info.pre2 %>% rowwise() %>% mutate(I2  = max(0, (Q - n + 1)/Q)) #calculate I2
+# meta.info.I2 <- meta.info.pre2 %>% filter(n > 9) %>% filter(I2 < 50)
[…]

### 2019-08-04 report/MSc_Report.tex
Rewrite Chapter 03, analysis procedure and add some to discussion

@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  1 15:37:26 2019
+% Sun Aug  4 15:56:33 2019
 \begin{table}[ht]
@@
 
-A complete listing of the variables of a result is given in Table \ref{variable}.
-Depending on the type of the data, \eg if it is binary or continuous, some variables are missing for the specific results.
-
-\begin{table}[ht]
-  \begin{center}
-    \begin{tabular}{l l}
-      \textbf{Variable} & \textbf{Description}\\
-      \hline
-      \texttt{id} & An id of the review for identification purposes \\
-      %\texttt{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
-      % \texttt{file.index} & Internal index of the file in the Cochrane library.\\
-      % \texttt{file.version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
-      %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
-      \hline
-      \texttt{study.name} & Name of the study to which the result belongs\\
-      \texttt{study.year} & Year in which the study was published \\
-      \texttt{study.data.source} & Source of the study, either ``Publ \\
-      \hline
-      \texttt{comparison.name/.nr} & Specification of the interventions compared in the study  \\ &and a unique number for the comparison\\
-      \texttt{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ &and a unique number for the outcome\\
-      \texttt{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a \\ &unique number for the subgroup\\
-      \texttt{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
-      \texttt{effect} & Measure of the effect given in the quantity denoted by \\ &\texttt{outcome measure}.\\
-      \texttt{se} & Standard error of the measure of the effect,\\
-      \texttt{events1/events2} & The counts of patients with an outcome \textit{if}\\ &measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
-      \texttt{total1/total2} & Number of patients in groups.\\
-      \texttt{mean1/mean2} & Mean of patient measurements \textit{if} outcome is continuous.\\
-      \texttt{sd1/sd2} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
-    \end{tabular}
-  \caption{Dataset variable names and descriptions  \label{variable}}
-  \label{variable}
-  \end{center}
-\end{table}
-
-Results are part of studies that are again part of a (systematic) review. This structure of a review is shown in Figure \ref{review}.
+Results are part of studies that are again part of a (systematic) review. This structure of a review is shown in Figure \ref{review.structure}.
 
@@
 
+A listing of important variables of a result is given in Table \ref{variable}.
+Depending on the type of the data, \eg if it is binary or continuous, some variables are missing for the specific results.
+
+\begin{table}[ht]
+  \begin{center}
+    \begin{tabular}{l l}
+      \textbf{Variable} & \textbf{Description}\\
+      \hline
+      \texttt{id} & An id of the review for identification purposes.\\
+      \hline
+      \texttt{study.name} & Name of the study to which the result belongs.\\
+      \texttt{study.year} & Year in which the study was published.\\
+      \hline
+      \texttt{comparison.name/.nr} & Specification of the interventions compared in the study and a \\ &unique number for the comparison.\\
+      \texttt{comparison.id} & Specification of the comparison by a string of the type ``CMP-xxx'' \\ &for the xxx. comparison within the review.\\
+      \texttt{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ &and a unique number for the outcome.\\
+      \texttt{outcome.id} & Specification of the outcome by a string of the type \\ &``CMP-xxx.xx'' for the xx. outcome of the xxx. comparison \\ &within the review.\\
+      \texttt{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a unique \\ &number for the subgroup.\\
+      \texttt{subgroup.id} & Specification of the comparison by a string of the type \\ &``CMP-xxx.yy.xx'' for the xx. subgroup for the yy. outcome \\ & of the xxx. comparison within the review.\\
+      \texttt{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
+      \texttt{outcome.measure.merged} & Indication of the quantification method of the effect, \\ &merged such that each method is uniquely classified.\\
+      \texttt{outcome.flag} & A outcome flag to simplify programming; \\ &\texttt{DICH} for binary outcomes with fully available information \\ &on event counts,
+      as given in a two-by-two \\ &table.
+\\ &\texttt{CONT} for continuous outcomes with available means and \\ &standard deviations.
+\\ & \texttt{IV} for all results with effects and standard errors but without \\ & the data necessary for their computation.
+\\ &\texttt{IPD} for individual patient data.\\
+      \texttt{effect} & Measure of the effect given in the quantity denoted by \\ &\texttt{outcome measure}.\\
+      \texttt{se} & Standard error of the measure of the effect.\\
+      \texttt{events1/events2} & The counts of patients with an outcome if measurement/outcome \\ &is binary or dichotomous (1 for treatment group and 2 for control group).\\
+      \texttt{total1/total2} & Number of patients in groups.\\
+      \texttt{mean1/mean2} & Mean of patient measurements if outcome is continuous.\\
+      \texttt{sd1/sd2} & Standard deviation of mean if outcome is continuous.
+    \end{tabular}
+  \caption{Dataset variable names and descriptions  \label{variable}}
+  \label{variable}
+  \end{center}
+\end{table}
+
 \vspace{0mm}
 The structure of a review will now be outlined based on an example of the dataset.
-Let us consider the previously mentioned barbiturate and head injury review.
+The previously mentioned barbiturate and head injury review will be outlined.
 The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates'' %\citep{barbiturate}.
@@
 One study split up outcomes for patients with and without haematoma, which would be subgroups.
-Thus, it is important not to confuse results with studies.
+%It is important not to confuse results with studies.
 A study can contribute multiple results to a systematic review, for example, primary and secondary outcomes and adverse effects.
@@
 The median of the publication years is 2003, the mean 2000.97 and the quartiles are 1996 and 2008.
-1075 studies have been published in 2018, none in 2019.
-\\
+1075 studies have been published in 2018, none in 2019.\\
 The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}.
@@
 {\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  1 15:37:26 2019
+% Sun Aug  4 15:56:33 2019
 \begin{table}[ht]
@@
 \section{Data Tidying and Processing} \label{sec:Processing}
-The dataset was scraped from the Cochrane Database of Systematic Reviews at the ... . A specialized code was used to convert the xtml. files from the webpage into the data at hand cite... .
 
@@
 \begin{itemize}
-\item \texttt{outcome.measure.merged}: Outcome measure specifications given in \texttt{outcome.measure} were standardized whenever they were supposed to denote the same outcome measure.
-An example would be the formally different notations for odds ratios: ``Odds Ratio'', ``odds ratio'', ``OR'', which were all denoted as ``Odds Ratio''.
-% \item \texttt{outcome.flag}: A simplification of \texttt{outcome.measure.merged}.
-The outcome.flag ``bin'' indicates if \texttt{outcome.measure.merged} is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
-``cont'' is equivalent to \texttt{outcome.measure.merged} equal to "Std.
-Mean Difference'' or ``Mean Difference''.
-``surv'' equal to ``Hazard Ratio'' and ``rate'' equal to ''Rate Ratio'' or ``Rate Difference''.
-\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.flag ``bin''.
-\item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.flag ``cont''. 
-% If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.merged} was equal to ``Std.
-Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  length(inpute.given.ind)).
-\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.flag ``bin''.
-\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.flag ``bin'') or $g$ (for outcome.flag ``cont'') to $r$ transformation.
+\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for \texttt{outcome.flag} \texttt{DICH}.
+\item \texttt{cohensd} and \texttt{var.cohensd}: Cohen's $d$ and the variance for \texttt{outcome.flag} \texttt{CONT}'. 
+\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for \texttt{outcome.flag} \texttt{DICH}.
+\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for \texttt{outcome.flag} \texttt{DICH}) or $d$ (for \texttt{outcome.flag} \texttt{CONT}') to $r$ transformation.
 \item \texttt{z} and \texttt{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
-\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.flag ``cont'' or Wald test for outcome.flag ``bin''.
+\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for \texttt{outcome.flag} \texttt{CONT}' or Wald test for \texttt{outcome.flag} \texttt{DICH}.
 \item \texttt{events1c} and \texttt{events2c}: Correction of \texttt{events1} and \texttt{events2} zero event counts or event counts = patient number.
@@
 Consistent to what has been discussed before, all results that share a common comparison, outcome and subgroup (optional, subgroups not given in any case) may be combined in a meta-analysis.
-\item \texttt{se.new}: Depending on \texttt{outcome.flag}, \texttt{se.new} is equal to the square-root of \texttt{var.lrr} (\texttt{outcome.flag} = \texttt{DICH}), square-root of \texttt{var.smd} (\texttt{CONT})
+\item \texttt{smd.pool} and \texttt{se.smd.pool}: Depending on \texttt{outcome.flag}, \texttt{smd.pool} is equal to \texttt{smd.ordl} (\texttt{outcome.flag} = \texttt{DICH}), \texttt{cohensd} (\texttt{CONT}), or \texttt{effect} (\texttt{IV} and \texttt{outcome.measure.merged} = \texttt{SMD}).
 or \texttt{se} (\texttt{IV}).
-% \item \texttt{}:
 \end{itemize}
@@
 Initially, the analysis is restricted to results with \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}.
-binary, continuous and survival outcomes.
-This corresponds to 734954 out of a total of 744720 results.
+If \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR}, \texttt{RR}, \texttt{SMD}, \texttt{MD}, \texttt{Hazard Ratio} and \texttt{Rate Ratio} are used.
 \citet{Ioannidis2007} outlined criteria for application of small study effect tests:
 \begin{itemize}
-\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = 9916 remaining). 
-\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 9616 remaining).
-\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 7586 remaining)
-\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 405 remaining).
+\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = 9772 remaining). 
+\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 9473 remaining).
+\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 7452 remaining)
+\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 1388 remaining).
 \end{itemize}
@@
 \item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = 20 out of meta-analyses with at least ten studies).
+\item \textbf{No withdrawn reviews}: Reviews that have been withdrawn are not included.
+\item \textbf{No adverse effects}: No results of adverse effects of treatment are used for meta-analyses.
+Exclusion is incomplete because only results with ``adverse'' in the comparison or outcome name could be removed, but not all adverse effect results are classified as such.
 \end{itemize}
 
-The results of this reduction of the dataset are shown in the flow-chart in Figure \ref{Inclusion.criteria}. By applying the criteria, we are only able to analyse a subset of the original data. \\
+The results of this reduction of the dataset are shown in the flow-chart in Figure \ref{Inclusion.criteria}.
 Only the data that had accesible all results data available was used for adjustment.
-Thus, all meta-analyses with \texttt{outcome.flag} == \texttt{IV} are ommitted in a second step of the analysis (Analysis dataset (1) and (2) in Figure \ref{Inclusion.criteria}).
+Thus, all meta-analyses with \texttt{outcome.flag} == \texttt{IV} and \texttt{outcome.measure.merged} not equal to \texttt{SMD} are ommitted in a second step of the analysis (Analysis dataset (1) and (2) in Figure \ref{Inclusion.criteria}).
 
@@
     \node [block, below of=13, node distance=2cm] (2) {
-    5,948 reviews,
-    65,962 studies,
-    695,992 results};
+    5,936 reviews,
+    65,296 studies,
+    687,517 results};
 
     \node [block, below of=2, node distance=2cm] (3) {
-    1,156 reviews,
-    26,580 studies,
-    175,351 results,
-    9,916 meta-analyses};
+    1,145 reviews,
+    26,094 studies,
+    172,212 results,
+    9,772 meta-analyses};
 
     \node [block, below of=3, node distance=2cm] (4) {
-    1,140 reviews,
-    26,306 studies,
-    170,096 results,
-    9,616 meta-analyses};
+    1,129 reviews,
+    25,819 studies,
+    166,968 results,
+    9,473 meta-analyses};
 
     \node [block, below of=4, node distance=2cm] (5) {
-    1,064 reviews,
-    24,277 studies,
-    137,613 results,
-    7,586 meta-analyses};
+    1,052 reviews,
+    23,781 studies,
+    134,596 results,
+    7,452 meta-analyses};
 
     \node [block, below of=5, node distance=2cm] (6) {
-    1,033 reviews,
-    22,668 studies,
-    47,607 results,
-    2,729 meta-analyses};
+    1,021 reviews,
+    22,183 studies,
+    45,888 results,
+    2,665 meta-analyses};
 
     \node [final, below of=6, node distance=2cm] (7) {Analysis dataset (1):
-    303 reviews,
-    5,355 studies,
-    6,592 results,
-    405 meta-analyses};
+    738 reviews,
+    14,320 studies,
+    22,937 results,
+    1,388 meta-analyses};
 
@@
     \node [final, below of=8, node distance=2.4cm] (11) {Analysis dataset (2):
-    685 reviews,
-    13,396 studies,
-    21,074 results,
+    694 reviews,
+    13,581 studies,
+    21,482 results,
     1,267 meta-analyses};
@@
     \path [line] (9) -- (11);
+    \path [line] (10) -- node [btw, xshift = -2.6cm, yshift = -0.5cm] {\texttt{outcome.measure.merged} = \texttt{SMD}} (11);
 
@@
 
-\subsubsection{Exclusions due to Computational Errors}
-There has been cases where meta-analyses could not be analysed with Copas selection model because the likelihood function could not be optimized based on the settings. It was ommitted in this case.\\
-\begin{itemize}
-\item Meta-analysis with \texttt{meta.id} = 93868,  \texttt{id} = ``CD004072'', \texttt{subgroup.id} = ``CMP-006.08.01''.
-One small meta-analysis (\texttt{se.new} = 1.02) with a risk ratio 0.072, while the remaining risk ratios were all larger than 0.45.
-(and the fixed effects estimate close to 1).
-It failed when analysed based on log risk ratios.
-\item Meta-analysis with \texttt{meta.id} = 144568,  \texttt{id} = ``CD006109'', \texttt{outcome.id} = ``CMP-001.06'' and \texttt{outcome.measure} ``MD''.
-$z$-score based analysis failed, although funnel plot looks more or less symmetric.
-Small studies with very similar \texttt{var.z} with $z$-scores 0.3 and -0.1.
-\item Meta-analysis with \texttt{meta.id} = 35673,  \texttt{id} = ``CD001790'', \texttt{outcome.id} = ``CMP-001.03'' and \texttt{outcome.measure} = ``PETO.OR''.
-Analysis failed when using Hedges $g$ transformed effects.
-Large studies have $g \sim 0$ while one smaller study ($\se = 0.3$) has $g = 1$ (and another with a little larger $\se$ has $g \sim 0$).
-\end{itemize}
-Because the number of errors is low, the meta-analyses have only been ommitted for the specific outcome measures, but are kept in the others.
+\subsubsection{Exclusions for other Reasons}
+In some more cases, meta-analyses were excluded because their results seemed to be erroneous (1) or because participant numbers were missing (5), necessary to compute the variance of Fisher's z transformed correlation coefficient.
+The latter meta-analyses (all \texttt{outcome.flag} = \texttt{IV}) were only ommitted when doing the adjustment based on the $z$-scores, but kept when adjusting based on std.
+mean differences.
+The meta-analysis that is considered erroneous is from a review with the title ``School-based programs for preventing smoking''.
+The reason why it is suspected to be erroneous is because there are results from one study (Severson, 1991) with rather large effects (13, 0.4, 6.3, 2.4) compared to a mean std.
+mean difference in 12 other results of 0.22 (max.: 0.91) and very large standard errors (64, 60, 46, 70) compared to a mean \texttt{se} of 0.6 (max.: 3.8).
+It is not included in the analysis.
 
 \subsubsection{The Analysis Dataset}
-The dataset that was ultimately tested and adjusted for publication bias comprises 1 meta-analyses and 6592 results.
-The mean number of participants in the treatment group is 206.9 vs 256.7 in the unrestricted dataset and the mean total number of participants 393.2 vs 623.2.
-The mean publication year is 1999.8575604 vs 2000.9711014 in the unrestricted dataset.
+The dataset that was ultimately tested and adjusted for publication bias comprises 1 meta-analyses and 22937 results.
+The mean number of participants in the treatment group is 253.5 vs 256.7 in the unrestricted dataset and the mean total number of participants 589.3 vs 623.2.
+The mean publication year is 2000.4408025 vs 2000.9711014 in the unrestricted dataset.
 \\
@@
 \subsection{Analysis Procedure} \label{sec:procedure}
-All compuations were performed in the \texttt{R} computing environment \citep{R.base}.
-The \texttt{R} packages \texttt{meta} \citep{meta.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments.
-The excess significance test was adapted from \citet{vanAert.2019}.
-For data manipulation procedures, the \texttt{tidyverse} packages were used \citep{tidyverse.package}, and for plotting the \texttt{ggplot2} package \citep{ggplot2}.\\
-The methods described in the methods chapter \ref{ch:methods} most often apply directly to the algorithms used in \texttt{meta} and \texttt{metafor}.
-For binary outcomes, log risk ratios were used as treatment effect estimates in the meta-analysis, and for continuous outcomes, Hedge's $g$.
-For the other outcomes, the \texttt{effect} and \texttt{se} as provided in the dataset was passed to \texttt{meta::metagen}.
-\\
-The effect sizes were transformed for adjustment in the way described in section \ref{sec:transformation.effectsizes}.
+Meta-analysis groups within a review were obtained by grouping by comparison, outcome and subgroup.
+The last step is optional, and the Cochrane groups do also meta-analysis without taking into account subgroups.
+Subgroups are often specificaions of treatment, \eg the form of the medication or the protocoll.
+Thus, using the subgroups should increase the within-study homogeneity.
+However, the Cochrane Organisation disencourages meta-analyses based on subgroups only, because subgroups are often set up after the collection of the data analysis.
+Since the main interest of this study is not to precisely assess the efficacy of treatments, but the interest is merely on systematic differences between single studies investigating the same scientific question and not in the effect per se, it has been decided that the increase in precision is worthwile the loss of a number of studies.
+While it is possible that the use of subgroups introduces bias in the meta-analysis, it is also possible that ignoring subgroups will do (which is one of the reasons why subgroups are analyses as well).
+When one subgroup has substantially different real treatment effects, and the specific properties influence study size, publication bias assessment fails.
+Subgroups are not indicated in 50.8\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane review groups did.
+The methods described in the methods chapter \ref{ch:methods} most often apply directly to the algorithms used in \texttt{meta} and \texttt{metafor}. \\
+For applying publication bias tests and adjustment methods, the analysis was applied such that the effects used are similar or identical to the effects on which journal editors decided upon publication bias.
+For \texttt{outcome.flag} = \texttt{DICH}, log risk ratios were used as treatment effect estimates in the meta-analysis, for \texttt{outcome.flag} = \texttt{CONT}, mean difference or standardised mean difference, depending on \texttt{outcome.measure.merged}.
+For \texttt{outcome.flag} = \texttt{IV}, the \texttt{effect} and \texttt{se} as provided in the dataset was passed to \texttt{meta::metagen}.
+\\
+To be able to compare the effects of adjustment among meta-analyses, the effect sizes were transformed on a common scale, as described in section \ref{sec:transformation.effectsizes}.
+As shown in the flow-chart in Figure \ref{Inclusion.criteria}, this leads to a reduced dataset (compare analysis dataset (1) and (2)).
 The $p$-values for adjusted treatment effect estimates were calculated by the Wald method.
@@
 If there is still no non-significant small study effect, the result was \texttt{NA}.
+All compuations were performed in the \texttt{R} computing environment \citep{R.base}.
+The \texttt{R} packages \texttt{meta} \citep{meta.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments.
+The excess significance test was adapted from \citet{vanAert.2019}.
+For data manipulation procedures, the \texttt{tidyverse} packages were used \citep{tidyverse.package}, and for plotting the \texttt{ggplot2} package \citep{ggplot2}.\\
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug  2 14:32:32 2019
+% Sun Aug  4 16:15:09 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug  2 14:32:47 2019
+% Sun Aug  4 16:15:36 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug  2 14:32:48 2019
+% Sun Aug  4 16:15:38 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug  2 14:32:57 2019
+% Sun Aug  4 16:15:46 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug  2 14:32:58 2019
+% Sun Aug  4 16:15:47 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug  2 14:32:59 2019
+% Sun Aug  4 16:15:49 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug  2 14:33:01 2019
+% Sun Aug  4 16:15:51 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug  2 14:33:05 2019
+% Sun Aug  4 16:15:54 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug  2 14:33:49 2019
+% Sun Aug  4 16:16:35 2019
 \begin{table}[ht]
@@
 \\
+The term publication bias is frequently used in this study, but 1.7\% of the analysis dataset (1) are unpublished results.
+This mitigates the estimated extent of publication bias in this study since it has been shown repeatedly that effects in the grey literature are smaller.
 
@@
 Thus, in the data that is scrutinized, there has been enforced and ongoing research.
-\citet{ioannidis.2005} state that publication bias is also a consequence of modern discovery oriented research, and thus it may well be that publication bias is also an issue when the number of studies are lower.\\
+\citet{ioannidis.2005} state that publication bias is also a consequence of modern discovery oriented research, and thus it may well be that publication bias is also an issue when the number of studies are lower.
+Also, it is possible that by excluding meta-analyses where $I^2 \geq 0.5$, the most extreme cases of publication bias are removed since publication bias increases the between-study heterogeneity.\\
+Furthermore, the sub-partitioning of meta-analyses based on conparison, outcome and subgroup is only one possibility%, which is in fact not recommended by the Cochrane Organisation. 
+Cochrane usually performs multiple meta-analyses with the same results, for example by doing sensitivity analyses (not an issue in this study, since they are removed) and subgroup analyses and overall analyses.
+One can as well repeat the analysis without considering subbgroups.
+This will have the advantage of increasing the sample size, but it will also result in increased heterogeneity in meta-analyses, and if one subgroup with small studies yields large effects, the cause must not be publication bias.
+\\
 It also has to be said that the removal of safety outcomes is only partially successfull.

### 2019-08-04 report/chapter03.Rnw
Rewrite Chapter 03, analysis procedure and add some to discussion

@@
 #outcome.flag reduction:
-tp <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
-  filter(outcome.flag == "DICH" | outcome.flag == "CONT" | outcome.flag == "IV")
+tp.2 <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
+  filter(outcome.flag == "IV") %>% 
+  filter(!all(effect == 0)) %>% 
+  filter(outcome.measure.merged == "Rate Ratio" | outcome.measure.merged == "SMD" |
+           outcome.measure.merged == "MD" | outcome.measure.merged == "Hazard Ratio" |
+           outcome.measure.merged == "OR" | outcome.measure.merged == "RR")
+tp.1 <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
+  filter(outcome.flag == "DICH" | outcome.flag == "CONT")
+tp <- bind_rows(tp.1, tp.2)
 flag.id.count <- length(unique(tp$id))
@@
   filter(outcome.flag == "IV") %>% 
+  filter(!all(effect == 0)) %>% 
+  filter(outcome.measure.merged == "Rate Ratio" | outcome.measure.merged == "SMD" |
+           outcome.measure.merged == "MD" | outcome.measure.merged == "Hazard Ratio" |
+           outcome.measure.merged == "OR" | outcome.measure.merged == "RR") %>% 
   filter(se != 0) %>% group_by(meta.id) %>% filter(n() > 9) %>% 
@@
 #smaller I2 than 0.5:
-m.a.smaller.5.count <- meta.info.I2 %>% filter(I2 < 0.5) %>% ungroup %>% count()
+m.a.smaller.5.count <- meta.info.I2 %>% filter(I2 < 50) %>% ungroup %>% count()
 
-meta.id.vector <- meta.info.I2 %>% filter(I2 < 0.5) %>% select(meta.id)
+meta.id.vector <- meta.info.I2 %>% filter(I2 < 50) %>% select(meta.id)
 meta.data <- data.ext2 %>% filter(meta.id %in% meta.id.vector$meta.id)
@@
 #Adjustment dataset:
-meta.adj <- meta.f %>% filter(outcome.flag == "DICH" | outcome.flag == "CONT")
-tp6 <- data.ext2 %>% filter(meta.id %in% meta.adj$meta.id)
-#----------------------------------------------------------------------------------------------#
-
-#Adjustment dataset:
-meta.adj <- meta.f %>% filter(outcome.flag == "DICH" | outcome.flag == "CONT")
+meta.adj.2 <- meta.f %>% filter(outcome.flag == "IV") %>%
+  filter(outcome.measure.merged == "SMD")
+meta.adj.1 <- meta.f %>% filter(outcome.flag == "DICH" | outcome.flag == "CONT") 
+meta.adj <- bind_rows(meta.adj.2, meta.adj.1)
 tp6 <- data.ext2 %>% filter(meta.id %in% meta.adj$meta.id)
@@
 fourth.iv.outcome.count <- dt$n[4]
+fifth.iv.outcome.count <- dt$n[5]
+sixth.iv.outcome.count <- dt$n[6]
 
+#----------------------------------------------------------------------------------------------#
+#Meta-analyses without sungroups in the analysis dataset (1)
+no.subgroup <- round((meta.data %>% group_by(meta.id) %>% filter(is.na(subgroup.id)) %>% distinct(meta.id) %>% ungroup() %>% count/dim(meta.f)[1])*100, 1)$n
 @
@@
 The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{publication.year.range[5]} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}.
-\Sexpr{publication.year.2018} studies have been published in 2018, none in 2019.
-\\
+\Sexpr{publication.year.2018} studies have been published in 2018, none in 2019.\\
 The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}.
@@
 \begin{itemize}
-\item \texttt{outcome.measure.merged}: Outcome measure specifications given in \texttt{outcome.measure} were standardized whenever they were supposed to denote the same outcome measure.
-An example would be the formally different notations for odds ratios: ``Odds Ratio'', ``odds ratio'', ``OR'', which were all denoted as ``Odds Ratio''.
-% \item \texttt{outcome.flag}: A simplification of \texttt{outcome.measure.merged}.
-The outcome.flag ``bin'' indicates if \texttt{outcome.measure.merged} is either one of ``Risk Ratio'', ''Odds Ratio'', ``Risk difference'' or ``Peto Odds Ratio''.
-``cont'' is equivalent to \texttt{outcome.measure.merged} equal to "Std.
-Mean Difference'' or ``Mean Difference''.
-``surv'' equal to ``Hazard Ratio'' and ``rate'' equal to ''Rate Ratio'' or ``Rate Difference''.
-\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for outcome.flag ``bin''.
-\item \texttt{smd} and \texttt{var.smd}: Hedges $g$ and the variance of Hedges $g$ for outcome.flag ``cont''. 
-% If not computable from \texttt{mean1}, \texttt{mean2}, \texttt{sd1} and \texttt{sd2}, and \texttt{outcome.measure.merged} was equal to ``Std.
-Mean Difference'', it was set equal to \texttt{effect} (and \texttt{var.smd} equal to \texttt{se} squared, $n$ =  \Sexpr{length(inpute.given.ind)}).
-\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for outcome.flag ``bin''.
-\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for outcome.flag ``bin'') or $g$ (for outcome.flag ``cont'') to $r$ transformation.
+\item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for \texttt{outcome.flag} \texttt{DICH}.
+\item \texttt{cohensd} and \texttt{var.cohensd}: Cohen's $d$ and the variance for \texttt{outcome.flag} \texttt{CONT}'. 
+\item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for \texttt{outcome.flag} \texttt{DICH}.
+\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for \texttt{outcome.flag} \texttt{DICH}) or $d$ (for \texttt{outcome.flag} \texttt{CONT}') to $r$ transformation.
 \item \texttt{z} and \texttt{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
-\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for outcome.flag ``cont'' or Wald test for outcome.flag ``bin''.
+\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for \texttt{outcome.flag} \texttt{CONT}' or Wald test for \texttt{outcome.flag} \texttt{DICH}.
 \item \texttt{events1c} and \texttt{events2c}: Correction of \texttt{events1} and \texttt{events2} zero event counts or event counts = patient number.
@@
 Initially, the analysis is restricted to results with \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}.
-binary, continuous and survival outcomes.
-This corresponds to \Sexpr{length(data.ext2$outcome.flag[which(data.ext2$outcome.flag == "DICH" | data.ext2$outcome.flag == "CONT" | data.ext2$outcome.flag == "IV")])} out of a total of \Sexpr{length(data.ext2$outcome.flag)} results.
+If \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR}, \texttt{RR}, \texttt{SMD}, \texttt{MD}, \texttt{Hazard Ratio} and \texttt{Rate Ratio} are used.
 \citet{Ioannidis2007} outlined criteria for application of small study effect tests:
@@
 \item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = \Sexpr{both.arms.zero.events.count} out of meta-analyses with at least ten studies).
+\item \textbf{No withdrawn reviews}: Reviews that have been withdrawn are not included.
+\item \textbf{No adverse effects}: No results of adverse effects of treatment are used for meta-analyses.
+Exclusion is incomplete because only results with ``adverse'' in the comparison or outcome name could be removed, but not all adverse effect results are classified as such.
 \end{itemize}
 
-The results of this reduction of the dataset are shown in the flow-chart in Figure \ref{Inclusion.criteria}. By applying the criteria, we are only able to analyse a subset of the original data. \\
+The results of this reduction of the dataset are shown in the flow-chart in Figure \ref{Inclusion.criteria}.
 Only the data that had accesible all results data available was used for adjustment.
-Thus, all meta-analyses with \texttt{outcome.flag} == \texttt{IV} are ommitted in a second step of the analysis (Analysis dataset (1) and (2) in Figure \ref{Inclusion.criteria}).
+Thus, all meta-analyses with \texttt{outcome.flag} == \texttt{IV} and \texttt{outcome.measure.merged} not equal to \texttt{SMD} are ommitted in a second step of the analysis (Analysis dataset (1) and (2) in Figure \ref{Inclusion.criteria}).
 
@@
 
-\subsubsection{Exclusions due to Computational Errors}
-There has been cases where meta-analyses could not be analysed with Copas selection model because the likelihood function could not be optimized based on the settings. It was ommitted in this case.\\
-\begin{itemize}
-\item Meta-analysis with \texttt{meta.id} = 93868,  \texttt{id} = ``CD004072'', \texttt{subgroup.id} = ``CMP-006.08.01''.
-One small meta-analysis (\texttt{se.new} = 1.02) with a risk ratio 0.072, while the remaining risk ratios were all larger than 0.45.
-(and the fixed effects estimate close to 1).
-It failed when analysed based on log risk ratios.
-\item Meta-analysis with \texttt{meta.id} = 144568,  \texttt{id} = ``CD006109'', \texttt{outcome.id} = ``CMP-001.06'' and \texttt{outcome.measure} ``MD''.
-$z$-score based analysis failed, although funnel plot looks more or less symmetric.
-Small studies with very similar \texttt{var.z} with $z$-scores 0.3 and -0.1.
-\item Meta-analysis with \texttt{meta.id} = 35673,  \texttt{id} = ``CD001790'', \texttt{outcome.id} = ``CMP-001.03'' and \texttt{outcome.measure} = ``PETO.OR''.
-Analysis failed when using Hedges $g$ transformed effects.
-Large studies have $g \sim 0$ while one smaller study ($\se = 0.3$) has $g = 1$ (and another with a little larger $\se$ has $g \sim 0$).
-\end{itemize}
-Because the number of errors is low, the meta-analyses have only been ommitted for the specific outcome measures, but are kept in the others.
+\subsubsection{Exclusions for other Reasons}
+In some more cases, meta-analyses were excluded because their results seemed to be erroneous (1) or because participant numbers were missing (5), necessary to compute the variance of Fisher's z transformed correlation coefficient.
+The latter meta-analyses (all \texttt{outcome.flag} = \texttt{IV}) were only ommitted when doing the adjustment based on the $z$-scores, but kept when adjusting based on std.
+mean differences.
+The meta-analysis that is considered erroneous is from a review with the title ``School-based programs for preventing smoking''.
+The reason why it is suspected to be erroneous is because there are results from one study (Severson, 1991) with rather large effects (13, 0.4, 6.3, 2.4) compared to a mean std.
+mean difference in 12 other results of 0.22 (max.: 0.91) and very large standard errors (64, 60, 46, 70) compared to a mean \texttt{se} of 0.6 (max.: 3.8).
+It is not included in the analysis.
 
@@
 \subsection{Analysis Procedure} \label{sec:procedure}
-All compuations were performed in the \texttt{R} computing environment \citep{R.base}.
-The \texttt{R} packages \texttt{meta} \citep{meta.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments.
-The excess significance test was adapted from \citet{vanAert.2019}.
-For data manipulation procedures, the \texttt{tidyverse} packages were used \citep{tidyverse.package}, and for plotting the \texttt{ggplot2} package \citep{ggplot2}.\\
-The methods described in the methods chapter \ref{ch:methods} most often apply directly to the algorithms used in \texttt{meta} and \texttt{metafor}.
-For binary outcomes, log risk ratios were used as treatment effect estimates in the meta-analysis, and for continuous outcomes, Hedge's $g$.
-For the other outcomes, the \texttt{effect} and \texttt{se} as provided in the dataset was passed to \texttt{meta::metagen}.
+Meta-analysis groups within a review were obtained by grouping by comparison, outcome and subgroup.
+The last step is optional, and the Cochrane groups do also meta-analysis without taking into account subgroups.
+Subgroups are often specificaions of treatment, \eg the form of the medication or the protocoll.
+Thus, using the subgroups should increase the within-study homogeneity.
+However, the Cochrane Organisation disencourages meta-analyses based on subgroups only, because subgroups are often set up after the collection of the data analysis.
+Since the main interest of this study is not to precisely assess the efficacy of treatments, but the interest is merely on systematic differences between single studies investigating the same scientific question and not in the effect per se, it has been decided that the increase in precision is worthwile the loss of a number of studies.
+While it is possible that the use of subgroups introduces bias in the meta-analysis, it is also possible that ignoring subgroups will do (which is one of the reasons why subgroups are analyses as well).
+When one subgroup has substantially different real treatment effects, and the specific properties influence study size, publication bias assessment fails.
+Subgroups are not indicated in \Sexpr{no.subgroup}\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane review groups did.
+The methods described in the methods chapter \ref{ch:methods} most often apply directly to the algorithms used in \texttt{meta} and \texttt{metafor}. \\
+For applying publication bias tests and adjustment methods, the analysis was applied such that the effects used are similar or identical to the effects on which journal editors decided upon publication bias.
+For \texttt{outcome.flag} = \texttt{DICH}, log risk ratios were used as treatment effect estimates in the meta-analysis, for \texttt{outcome.flag} = \texttt{CONT}, mean difference or standardised mean difference, depending on \texttt{outcome.measure.merged}.
+For \texttt{outcome.flag} = \texttt{IV}, the \texttt{effect} and \texttt{se} as provided in the dataset was passed to \texttt{meta::metagen}.
 \\
-The effect sizes were transformed for adjustment in the way described in section \ref{sec:transformation.effectsizes}.
+To be able to compare the effects of adjustment among meta-analyses, the effect sizes were transformed on a common scale, as described in section \ref{sec:transformation.effectsizes}.
+As shown in the flow-chart in Figure \ref{Inclusion.criteria}, this leads to a reduced dataset (compare analysis dataset (1) and (2)).
 The $p$-values for adjusted treatment effect estimates were calculated by the Wald method.

### 2019-08-04 report/chapter05.Rnw
Rewrite Chapter 03, analysis procedure and add some to discussion

@@
                                     "study sig. number > 1", "all exclusion criteria", "harbord test p-value < 0.1")
+
+meta.data <- data.ext2 %>% filter(meta.id %in% meta.f$meta.id)
 
@@
 \\
+The term publication bias is frequently used in this study, but \Sexpr{round((length(which(meta.data$study.data_source == "UNPUB"))/dim(meta.data)[1])*100, 1)}\% of the analysis dataset (1) are unpublished results.
+This mitigates the estimated extent of publication bias in this study since it has been shown repeatedly that effects in the grey literature are smaller.
 

### 2019-08-04 code/analysis.R

@@ -572,7 +572,7 @@ zscore.meta.analysis.estimates <- cbind(
 
 
 #--------------------------------------------------------------------------------------------------------------------#
-# HEDGES G BASED META-ANALYSES: -------------------------------------------------------------------------------------#
+# SMD BASED META-ANALYSES: ------------------------------------------------------------------------------------------#
 #--------------------------------------------------------------------------------------------------------------------#
 
 # # -------- Uncomment to run analysis ----------

### 2019-08-05 report/MSc_Report.tex
mixed models theory

@@
 
-\section{Small Study Effects Tests}
-The tests that will be presented on the following pages are a common way to detect publication bias.
-Importantly, they are however not interpretable directly as evidence for publication bias, but this is left for the discussion chapter.
-The tests are also often referred to as funnel plot asymmetry tests, because of the popularity of a recent test that has been used frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill}.
-However, it is known for some time that the method has disadvantageous properties, therefore, it will not be discussed here, as well as the funnel plot (the radial plot will be used as an alternative).\\
-A test for small study effects will test in some ways if the size of the estimated treatment effect of a study depends on some measure of its size.
-An association between study size and treatment effect size can be interpreted as an artifact of publication bias.
-
-\subsection{Continuous Outcome Tests}
-For a continuous outcomes that are normally distributed, the sample mean and variance are independent of each other \cite[120]{meta.w.R}.
-Thus, the estimated standard errors of treatment effects can be used as a proxy for study size, as they should in principle not be tied to the effect size.
-
-\subsubsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
-\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
-A standardized effect size $\theta_i^\star$ can be computed as in \eqref{eq:begg.stand.eff}.
-$\se_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \eqref{eq:begg.stand.var}, $\theta_M$ being the fixed effects pooled treatment effect (\eqref{eq:fixed.effects}.
-
-\begin{align}
-\theta_i^\star &= (\theta_i - \theta_M)/\se_i^{2\star} \label{eq:begg.stand.eff}  \\
-\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2}1 \label{eq:begg.stand.var} 
-\end{align}
-
-A rank correlation test based on Kendall's tau is then used.
-First, the pairs are ordered after their ranks based on $s^{2\star}$.
-Then, for each $s^{2\star}$ rank, the corresponding ranks based on $\theta^{2\star}$ that are larger are counted and summed up to $u$.
-The number of ranks based on $\theta^{2\star}$ that are in contrary, smaller, are counted and summed up to $l$.
-Then the normalized test statistic $Z$ is given as
-
-\begin{align}
-Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \nonumber
-\end{align}
-
-Thus, large number of concordance between pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$.
-The $p$-value is obtained using the standard normal distribution $\Phi$:
-\begin{align}
-p &= 2\cdot(1-\Phi(\abs{Z})) \nonumber
-\end{align}
-
-The changes that have to be made int the case of ties are small and can be found in \cite[410]{begg.ties}.
-
-\subsubsection{Egger's Test: Weighted Linear Regression Test} \label{sec:Egger}
-First, the concept of simple linear regression is introduced. In short, the model assumes a dependent variable $y$ to be a linear function of another explanatory variable $x$:
+\section{Linear, Weighted and Linear Mixed Regression Models} \label{sec:regression}
+First, the concept of simple linear regression is introduced \citep{fahrmeir2007}.
+In short, the model assumes a dependent variable $y$ to be a linear function of another explanatory variable $x$, with the residuals being distributed independently and identically and following a normal distribution:
 
@@
 \begin{align}
-\operatorname*{argmin}_{\beta_0, \beta_1}\big(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i\big) \label{eq:least.squares}
+\operatorname*{argmin}_{\beta_0, \beta_1}\Big(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i\Big) \label{eq:least.squares}
 \end{align}
@@
 
-$\bar{x}, \bar{y}$ denoting the sample means of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$. Thus, $\hat{\beta}_0$ is also called global mean.
+$\bar{x}$ and $\bar{y}$ denoting the sample means of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$. Thus, $\hat{\beta}_0$ is also called the global mean.
 To test whether there is evidence for the intercept $\beta_0$ to be unequal to some value $\beta_{H0}$, a $t$-test can be used.
@@
 The concept is extendable to weighted linear regression.
-Weighted linear regression may be used if the residuals $\mathbf{r}$ have unequal variances, which is equivalent to ascribe different precision to the observed $y$.
-The least squares equation \eqref{eq:least.squares} is extended to
-
-\begin{align}
-\operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
-\end{align}
-
-with positive weights $w_i$ that penalize large squared residuals for some $i$ more if $w_i$ is larger compared to other $w_i$. \\
+Weighted linear regression may be used if the residuals $\mathbf{r}$ have unequal variances, which is equivalent to ascribe different precision to the observed $y$ (heteroscedasticity).
+The least squares equation \eqref{eq:least.squares} is extended as follows:
+
+\begin{align}
+\operatorname*{argmin}_{\beta_0, \beta_1}\Big(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)\Big) \nonumber
+\end{align}
+
+with the positive weights $w_i$ penalizing large squared residuals for some $i$ more if $w_i$ is larger. \\
 Let $\mathbf{W}$ be a $n \times n$ matrix with $\mathbf{W}_{ii} = w_i$, the weights on the diagonal and zeros on the off-diagonals.
-The estimates in \eqref{eq:regression.parameters} and \eqref{eq:regression.variances} can still be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$.
+The estimates in \eqref{eq:regression.parameters} and \eqref{eq:regression.variances} can again be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$.
 \label{weighted.regression} \\
-Now it is shown how linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citet{Egger}.
+The introduction of group-specific random effects allows to analyze grouped or repeated measurements by linear regression.
+Let $i$ be the group index, $j$ the index of the single observation from the group $i$ and $x_j$ the $j^\textrm{th}$ row of $\mathbf{X}$.
+Then the equation
+
+\begin{align}
+\mathbf{y}_{j}|U_i,\epsilon_{j} =  x_j\beta + U_i + \epsilon_{j} \label{eq:one.random.intercept}
+\end{align}
+
+gives the marginal distribution of $\mathbf{y}{_{j}}$ depending on $U{_i}$ and $\epsilon{_{j}}$.
+The random effects $U{_i} \sim N(0, \mathbf{G})$ and the residual error term $\epsilon{_{j}} \sim N(0, \tau^{2})$ are independent from eahc other.
+The expectation $\mathbb{E}(\mathbf{y}_{j})$ is still $x_j \beta$, but now, the covariance between the observations within a group $i$, $\mathbf{y}_i$, is modeled as
+
+\begin{align}
+\Cov(\mathbf{y}_i) &= \mathbf{D}_i \mathbf{G} \mathbf{D}_i^\top + \tau^2 \mathbf{I}_{n_i} \label{eq:random.intercepts.covariance}
+\end{align}
+
+where $\D_i$ is in the case of the random intercept model a $1 \times n_i$ matrix of 1's and $\mathbf{G}$ is a scalar to be estimated.
+Thus, if $\mathbf{G} \neq 0$, the observations within a group will be uniformly correlated (uniform correlation between each observation).
+Nested groups are achieved by extending the design matrix $\mathbf{X}$ with an additional column of 1's and using according indices that specify the nesting structure.\\
+An extension of the random intercepts model is the random slopes model, which allows for additional, group-specific slopes with respect to a explanatory variable $x$.
+It can be implemented by modifying \eqref{eq:one.random.intercept}.
+Let $\mathbf{U}_i$ be a two-dimensional random vector with a $2 \times 2$ covariance matrix $\mathbf{G}$.
+Again, we can specify the marginal distribution of a observation $j$ within a group $i$:
+
+\begin{align}
+\mathbf{y}_j|U_i,\epsilon_j =  x_j\beta + x_j \mathbf{U}_i + \epsilon_j \label{eq:one.random.intercept.and.slope}
+\end{align}
+
+$\mathbf{D}_i$ is a $p + 1 \times n_i$ matrix where the $j^\textrm{th}$ column is equal to $(x_j)^\top$.
+The covariance matrix $\mathbf{V_i}$ for group $i$ is defined as in equation \eqref{eq:random.intercepts.covariance}, using the new $\mathbf{D}_i$.
+Defining $\mathbf{x}_i$ as all observations from group $i$ of $\mathbf{X}$, and equivalently $\mathbf{y}_i$, the estimated vector $\hat{\beta}$ is obtained by computing
+
+\begin{align}
+\hat{\beta} &= \Big( \sum_{i = 1}^m \mathbf{x}_i^\top \hat{\mathbf{V}}_i^{-1} \mathbf{x}_i \Big)^{-1} \sum_{i = 1}^m \mathbf{x}_i^\top \hat{\mathbf{V}}_i^{-1} \mathbf{y}_i
+\end{align}
+
+whith $m$ being the number of groups and $\hat{\mathbf{V}}_i$ being the estimated covariance, obtained by maximizing the log likelihood of the normal distribution, as $\mathbf{y}_i$ is distributed as
+
+\begin{align}
+\mathbf{y}_i \sim N(\mathbf{x}_i \beta, \mathbf{V}_i)
+\end{align}
+
+$\Big( \sum_{i = 1}^m \mathbf{x}_i^\top \hat{\mathbf{V}}_i^{-1} \mathbf{x}_i \Big)$ are assumed to be positive definite, as well as  $\hat{\mathbf{V}}_i^{-1}$.
+The approximate covariance matrix of $\hat{\beta}$ is given by
+
+\begin{align}
+\hat{\Cov(\hat{\beta})} &= \Big( \sum_{i = 1}^m \mathbf{x}_i^\top \hat{\mathbf{V}}_i^{-1} \mathbf{x}_i \Big)^{-1}
+\end{align}
+
+Weights can be introduced by replacing $\mathbf{I}_{n_i}$ in \eqref{eq:random.intercepts.covariance} with the previously introduced weight matrix $\mathbf{W}_i$ .Hypothesis tests for $\beta = \beta_\textrm{H0}$ can be made using the wald method.
+
+\section{Small Study Effects Tests}
+The tests that will be presented on the following pages are a common way to detect publication bias.
+Importantly, they are however not interpretable directly as evidence for publication bias, but this is left for the discussion chapter.
+The tests are also often referred to as funnel plot asymmetry tests, because of the popularity of a recent test that has been used frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill}.
+However, it is known for some time that the method has disadvantageous properties, therefore, it will not be discussed here, as well as the funnel plot (the radial plot will be used as an alternative).\\
+A test for small study effects will test in some ways if the size of the estimated treatment effect of a study depends on some measure of its size.
+An association between study size and treatment effect size can be interpreted as an artifact of publication bias.
+
+\subsection{Continuous Outcome Tests}
+For a continuous outcomes that are normally distributed, the sample mean and variance are independent of each other \cite[120]{meta.w.R}.
+Thus, the estimated standard errors of treatment effects can be used as a proxy for study size, as they should in principle not be tied to the effect size.
+
+\subsubsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
+\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+A standardized effect size $\theta_i^\star$ can be computed as in \eqref{eq:begg.stand.eff}.
+$\se_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \eqref{eq:begg.stand.var}, $\theta_M$ being the fixed effects pooled treatment effect (\eqref{eq:fixed.effects}.
+
+\begin{align}
+\theta_i^\star &= (\theta_i - \theta_M)/\se_i^{2\star} \label{eq:begg.stand.eff}  \\
+\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2}1 \label{eq:begg.stand.var} 
+\end{align}
+
+A rank correlation test based on Kendall's tau is then used.
+First, the pairs are ordered after their ranks based on $s^{2\star}$.
+Then, for each $s^{2\star}$ rank, the corresponding ranks based on $\theta^{2\star}$ that are larger are counted and summed up to $u$.
+The number of ranks based on $\theta^{2\star}$ that are in contrary, smaller, are counted and summed up to $l$.
+Then the normalized test statistic $Z$ is given as
+
+\begin{align}
+Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \nonumber
+\end{align}
+
+Thus, large number of concordance between pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$.
+The $p$-value is obtained using the standard normal distribution $\Phi$:
+\begin{align}
+p &= 2\cdot(1-\Phi(\abs{Z})) \nonumber
+\end{align}
+
+The changes that have to be made int the case of ties are small and can be found in \cite[410]{begg.ties}.
+
+\subsubsection{Egger's Test: Weighted Linear Regression Test} \label{sec:Egger}
+Linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citet{Egger}.
 Let $\theta/s$ be the dependent variable $y$ and $1/\se$ the explanatory variable $x$.
@@
 The $p$-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
-
-\subsection{Generalized linear model} \label{random.intecepts}
-The introduction of group-sepific random effects allows to analyze grouped or repeated measurements by linear regression \citep{Glm}. Let $i$ be the group index, and
-
-\begin{align}
-\mathbf{Y}{_{ij}}|U{_i},\epsilon{_{ij}} = (1,x{_i}^\top)\beta + U{_i} + \epsilon{_{ij}} \label{eq:one.random.intercept}
-\end{align}
-
-the marginal distribution of $\mathbf{Y}{_{ij}}$ depending on $U{_i},\epsilon{_{ij}}$.
-The random effects $U{_i} \sim N(0, g)$ and the residual error term $\epsilon{_{ij}} \sim N(0, \tau^{2})$ are considered independent.
-If there are more groups in the data we can extend \eqref{eq:one.random.intercept} by adding a second random term $Q$ with an index $k$:
-
-\begin{align}
-\mathbf{Y}{_{ij}}|U_i, Q_k \epsilon{_{ij}} = (1,x_i^\top)\beta + U_i + Q_k + \epsilon{_{ij}} \label{eq:two.random.intercepts}
-\end{align}
-
-Again, $U, K, \epsilon$ are distributed independently. The random intercepts model will account for a nested group structure by accordingly indexing the groups. \\
-The conditional distribution in equations \eqref{eq:one.random.intercept} and \eqref{eq:two.random.intercepts} can be used to construct a conditional likelihood; A bayesian posterior distribution is integrated with respect to the random effects, such that it can be used for restricted or unrestricted maximum likelihood estimation.
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Aug  4 15:56:33 2019
+% Mon Aug  5 12:24:17 2019
 \begin{table}[ht]
@@
 {\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Aug  4 15:56:33 2019
+% Mon Aug  5 12:24:17 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Aug  4 16:15:09 2019
+% Mon Aug  5 16:02:46 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Aug  4 16:15:36 2019
+% Mon Aug  5 16:02:59 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Aug  4 16:15:38 2019
+% Mon Aug  5 16:03:01 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Aug  4 16:15:46 2019
+% Mon Aug  5 16:03:10 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Aug  4 16:15:47 2019
+% Mon Aug  5 16:03:10 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Aug  4 16:15:49 2019
+% Mon Aug  5 16:03:12 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Aug  4 16:15:51 2019
+% Mon Aug  5 16:03:14 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Aug  4 16:15:54 2019
+% Mon Aug  5 16:03:17 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Sun Aug  4 16:16:35 2019
+% Mon Aug  5 16:03:57 2019
 \begin{table}[ht]
@@
 \appendix
-
-% LaTeX file for Chapter 01
-
-\chapter{Appendix}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlkwd{sessionInfo}\hlstd{()}
-\end{alltt}
-\begin{verbatim}
-## R version 3.5.1 (2018-07-02)
-## Platform: x86_64-apple-darwin15.6.0 (64-bit)
-## Running under: macOS  10.14.4
-## 
-## Matrix products: default
-## BLAS: /Library/Frameworks/R.framework/Versions/3.5/Resources/lib/libRblas.0.dylib
-## LAPACK: /Library/Frameworks/R.framework/Versions/3.5/Resources/lib/libRlapack.dylib
-## 
-## locale:
-## [1] en_US.UTF-8/en_US.UTF-8/en_US.UTF-8/C/en_US.UTF-8/en_US.UTF-8
-## 
-## attached base packages:
-## [1] stats     graphics  grDevices utils     datasets  methods   base     
-## 
-## other attached packages:
-##  [1] nlme_3.1-137    corrgram_1.13   bindrcpp_0.2.2  rvest_0.3.2    
-##  [5] xml2_1.2.0      xtable_1.8-3    metafor_2.1-0   Matrix_1.2-15  
-##  [9] gridExtra_2.3   metasens_0.3-2  meta_4.9-4      forcats_0.3.0  
-## [13] stringr_1.3.1   dplyr_0.7.8     purrr_0.2.5     readr_1.2.1    
-## [17] tidyr_0.8.2     tibble_1.4.2    ggplot2_3.1.0   tidyverse_1.2.1
-## [21] testit_0.9      knitr_1.20     
-## 
-## loaded via a namespace (and not attached):
-##  [1] Rcpp_1.0.0         lubridate_1.7.4    lattice_0.20-38   
-##  [4] gtools_3.8.1       assertthat_0.2.0   digest_0.6.18     
-##  [7] foreach_1.4.4      R6_2.3.0           cellranger_1.1.0  
-## [10] plyr_1.8.4         backports_1.1.2    evaluate_0.12     
-## [13] httr_1.3.1         highr_0.7          pillar_1.3.0      
-## [16] gplots_3.0.1.1     rlang_0.3.0.1      lazyeval_0.2.1    
-## [19] readxl_1.1.0       gdata_2.18.0       rstudioapi_0.8    
-## [22] labeling_0.3       munsell_0.5.0      broom_0.5.0       
-## [25] compiler_3.5.1     modelr_0.1.2       pkgconfig_2.0.2   
-## [28] tidyselect_0.2.5   seriation_1.2-7    codetools_0.2-15  
-## [31] dendextend_1.12.0  viridisLite_0.3.0  crayon_1.3.4      
-## [34] withr_2.1.2        bitops_1.0-6       MASS_7.3-51.1     
-## [37] grid_3.5.1         jsonlite_1.5       gtable_0.2.0      
-## [40] registry_0.5-1     magrittr_1.5       scales_1.0.0      
-## [43] KernSmooth_2.23-15 cli_1.0.1          stringi_1.2.4     
-## [46] viridis_0.5.1      iterators_1.0.10   tools_3.5.1       
-## [49] glue_1.3.0         gclus_1.3.2        hms_0.4.2         
-## [52] colorspace_1.3-2   cluster_2.0.7-1    caTools_1.17.1.1  
-## [55] TSP_1.1-7          bindr_0.1.1        haven_2.0.0
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-
-\section{Data Pre-processing}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlcom{#Dataset processing function to get transformed effect sizes, p-values, event }
-\hlcom{# counts with increments, etc. :}
-\hlstd{pb.process3} \hlkwb{<-} \hlkwa{function}\hlstd{(}\hlkwc{data}\hlstd{)\{}
-  \hlstd{data} \hlkwb{<-} \hlstd{data} \hlopt{%>%} \hlkwd{mutate}\hlstd{(}\hlkwc{meta.id} \hlstd{=}
-            \hlkwd{group_indices}\hlstd{(., id, comparison.id, outcome.id, subgroup.id))} \hlopt{%>%}
-    \hlkwd{group_by}\hlstd{(meta.id)} \hlopt{%>%} \hlkwd{mutate}\hlstd{(}\hlkwc{study.id2} \hlstd{=} \hlkwd{row_number}\hlstd{())} \hlopt{%>%} \hlkwd{ungroup}\hlstd{()}
-
-  \hlcom{#Mark duplicate effects between meta-analyses:}
-  \hlstd{data} \hlkwb{<-} \hlstd{data} \hlopt{%>%} \hlkwd{group_by}\hlstd{(meta.id)} \hlopt{%>%}
-    \hlkwd{mutate}\hlstd{(}\hlkwc{n} \hlstd{=} \hlkwd{n}\hlstd{())}  \hlopt{%>%} \hlkwd{ungroup}\hlstd{()} \hlopt{%>%} \hlkwd{group_by}\hlstd{(id)} \hlopt{%>%}
-    \hlkwd{mutate}\hlstd{(}\hlkwc{dupl.id} \hlstd{=}
-         \hlkwd{dupl.finder}\hlstd{(}\hlkwc{effects} \hlstd{= effect,} \hlkwc{names} \hlstd{= study.name,} \hlkwc{metas} \hlstd{= meta.id),}
-           \hlkwc{dupl.remove} \hlstd{=}
-  \hlkwd{dupl.max.finder}\hlstd{(}\hlkwc{duplicate.index} \hlstd{= dupl.id,} \hlkwc{study.number} \hlstd{= n,} \hlkwc{metas} \hlstd{= meta.id))} \hlopt{%>%}
-    \hlkwd{ungroup}\hlstd{()}
-
-  \hlstd{data} \hlkwb{<-} \hlstd{data} \hlopt{%>%} \hlkwd{mutate}\hlstd{(}\hlkwc{lrr} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{var.lrr} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{hedgesg} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{var.hedgesg} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{cohensd} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{var.cohensd} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{smd.ordl} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{var.smd.ordl} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{pval.single} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{cor.pearson} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{var.cor.pearson} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{z} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{var.z} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{events1c} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{events2c} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{sig.single} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{smd.pool} \hlstd{=} \hlnum{NA}\hlstd{,}
-    \hlkwc{se.smd.pool} \hlstd{=} \hlnum{NA}\hlstd{)}
-
-  \hlstd{cont.ind} \hlkwb{<-} \hlkwd{which}\hlstd{(data}\hlopt{$}\hlstd{outcome.flag} \hlopt{==} \hlstr{"CONT"}\hlstd{)}
-  \hlstd{bin.ind} \hlkwb{<-} \hlkwd{which}\hlstd{(data}\hlopt{$}\hlstd{outcome.flag} \hlopt{==} \hlstr{"DICH"}\hlstd{)}
-  \hlstd{IV.ind} \hlkwb{<-} \hlkwd{which}\hlstd{(data}\hlopt{$}\hlstd{outcome.flag} \hlopt{==} \hlstr{"IV"}\hlstd{)}
-  \hlcom{#----------------------------------------------------------------------------------------------#}
-
-  \hlcom{#Outcome.flag == "DICH"}
-  \hlstd{data[bin.ind,]} \hlkwb{<-} \hlkwd{escalc}\hlstd{(}\hlkwc{data} \hlstd{= data[bin.ind,],} \hlkwc{ai} \hlstd{= events1,} \hlkwc{n2i} \hlstd{= total2,}
-                           \hlkwc{ci} \hlstd{= events2,} \hlkwc{n1i} \hlstd{= total1,}
-                           \hlkwc{to} \hlstd{=} \hlstr{"only0"}\hlstd{,}
-                           \hlkwc{add} \hlstd{=} \hlnum{1}\hlopt{/}\hlnum{2}\hlstd{,}
-                           \hlkwc{measure} \hlstd{=} \hlstr{"RR"}\hlstd{,} \hlkwc{append} \hlstd{= T,}
-                      \hlkwc{var.names} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"lrr"}\hlstd{,} \hlstr{"var.lrr"}\hlstd{))} \hlcom{#Calculate Risk Ratios}
-
-  \hlstd{data[bin.ind,]} \hlkwb{<-} \hlkwd{escalc}\hlstd{(}\hlkwc{data} \hlstd{= data[bin.ind,],} \hlkwc{ai} \hlstd{= events1,} \hlkwc{n2i} \hlstd{= total2,}
-                           \hlkwc{ci} \hlstd{= events2,} \hlkwc{n1i} \hlstd{= total1,}
-                           \hlkwc{to} \hlstd{=} \hlstr{"only0"}\hlstd{,}
-                           \hlkwc{add} \hlstd{=} \hlnum{1}\hlopt{/}\hlnum{2}\hlstd{,}
-                           \hlkwc{measure} \hlstd{=} \hlstr{"OR2DL"}\hlstd{,} \hlkwc{append} \hlstd{= T,}
-  \hlkwc{var.names} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"smd.ordl"}\hlstd{,} \hlstr{"var.smd.ordl"}\hlstd{))} \hlcom{#Calculate SMD (w. logistic transf.)}
-
-  \hlcom{#What to do if there are 0/total cells:}
-  \hlstd{data[bin.ind,]} \hlkwb{<-} \hlstd{data[bin.ind,]} \hlopt{%>%}
-    \hlkwd{mutate}\hlstd{(}\hlkwc{events1c}  \hlstd{=} \hlkwd{case_when}\hlstd{(events1} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events1} \hlopt{+} \hlnum{0.5}\hlstd{,}
-                                 \hlstd{events2} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events1} \hlopt{+} \hlnum{0.5}\hlstd{,}
-                                 \hlstd{events1} \hlopt{-} \hlstd{total1} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events1} \hlopt{-} \hlnum{0.5}\hlstd{,}
-                                 \hlstd{events2} \hlopt{-} \hlstd{total2} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events1} \hlopt{-} \hlnum{0.5}\hlstd{,}
-                                 \hlnum{TRUE} \hlopt{~} \hlstd{events1),}
-           \hlkwc{events2c} \hlstd{=} \hlkwd{case_when}\hlstd{(events2} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events2} \hlopt{+} \hlnum{0.5}\hlstd{,}
-                                \hlstd{events1} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events2} \hlopt{+} \hlnum{0.5}\hlstd{,}
-                                \hlstd{events2} \hlopt{-} \hlstd{total2} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events2} \hlopt{-} \hlnum{0.5}\hlstd{,}
-                                \hlstd{events1} \hlopt{-} \hlstd{total1} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events2} \hlopt{-} \hlnum{0.5}\hlstd{,}
-                                \hlnum{TRUE} \hlopt{~} \hlstd{events2))}
-
-  \hlcom{#What to do if there is one zero and one total:}
-  \hlstd{data[bin.ind,]} \hlkwb{<-} \hlstd{data[bin.ind,]} \hlopt{%>%}
-    \hlkwd{mutate}\hlstd{(}\hlkwc{events1c}  \hlstd{=} \hlkwd{case_when}\hlstd{(events2} \hlopt{==} \hlnum{0} \hlopt{&} \hlstd{events1} \hlopt{-} \hlstd{total1} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events1,}
-                                 \hlstd{events1} \hlopt{==} \hlnum{0} \hlopt{&} \hlstd{events2} \hlopt{-} \hlstd{total2} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events1,}
-                                 \hlnum{TRUE} \hlopt{~} \hlstd{events1c),}
-           \hlkwc{events2c} \hlstd{=} \hlkwd{case_when}\hlstd{(events2} \hlopt{==} \hlnum{0} \hlopt{&} \hlstd{events1} \hlopt{-} \hlstd{total1} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events2,}
-                                \hlstd{events1} \hlopt{==} \hlnum{0} \hlopt{&} \hlstd{events2} \hlopt{-} \hlstd{total2} \hlopt{==} \hlnum{0} \hlopt{~} \hlstd{events2,}
-                                \hlnum{TRUE} \hlopt{~} \hlstd{events2c))}
-  \hlstd{data[bin.ind,} \hlstr{"pval.single"}\hlstd{]} \hlkwb{<-} \hlstd{data[bin.ind, ]} \hlopt{%>%}
-    \hlkwd{mutate}\hlstd{(}\hlkwc{pval.single} \hlstd{=} \hlnum{2}\hlopt{*}\hlstd{(}\hlnum{1}\hlopt{-}\hlkwd{pnorm}\hlstd{(}\hlkwd{abs}\hlstd{(lrr}\hlopt{/}\hlkwd{sqrt}\hlstd{(var.lrr)))))} \hlopt{%>%} \hlkwd{select}\hlstd{(pval.single)}
-  \hlcom{#----------------------------------------------------------------------------------------------#}
-
-  \hlcom{#Outcome.flag == "CONT"}
-  \hlstd{data[cont.ind,]} \hlkwb{<-} \hlkwd{escalc}\hlstd{(}\hlkwc{data} \hlstd{= data[cont.ind,],} \hlkwc{m1i} \hlstd{= mean1,} \hlkwc{m2i} \hlstd{= mean2,}
-                            \hlkwc{sd1i} \hlstd{= sd1,} \hlkwc{sd2i} \hlstd{= sd2,} \hlkwc{n1i} \hlstd{= total1,} \hlkwc{n2i} \hlstd{= total2,}
-                            \hlkwc{measure} \hlstd{=} \hlstr{"SMD"} \hlstd{,} \hlkwc{append} \hlstd{= T,}
-                \hlkwc{var.names} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"hedgesg"}\hlstd{,} \hlstr{"var.hedgesg"}\hlstd{))} \hlcom{#Calculate Hedge's g}
-
-  \hlstd{data[cont.ind, ]} \hlkwb{<-} \hlstd{data[cont.ind, ]} \hlopt{%>%}
-    \hlkwd{mutate}\hlstd{(}\hlkwc{cohensd} \hlstd{= (mean1} \hlopt{-} \hlstd{mean2)}\hlopt{/}\hlkwd{sqrt}\hlstd{((((total1} \hlopt{-} \hlnum{1}\hlstd{)}\hlopt{*}\hlstd{sd1}\hlopt{^}\hlnum{2}\hlstd{)} \hlopt{+}
-                    \hlstd{(total2} \hlopt{-} \hlnum{1}\hlstd{)}\hlopt{*}\hlstd{sd2}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}\hlstd{(total1} \hlopt{+} \hlstd{total2} \hlopt{-} \hlnum{2}\hlstd{)),}
-           \hlkwc{var.cohensd} \hlstd{= ((total1} \hlopt{+} \hlstd{total2)}\hlopt{/}\hlstd{(total1} \hlopt{*} \hlstd{total2))} \hlopt{+}
-             \hlstd{(cohensd}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}\hlstd{(}\hlnum{2}\hlopt{*}\hlstd{(total1} \hlopt{+} \hlstd{total2)))}
-
-  \hlstd{data[cont.ind, ]} \hlkwb{<-} \hlstd{data[cont.ind, ]} \hlopt{%>%}
-    \hlkwd{mutate}\hlstd{(}\hlkwc{cohensd} \hlstd{=} \hlkwd{case_when}\hlstd{(sd1} \hlopt{==} \hlnum{0} \hlopt{~} \hlnum{NA_real_}\hlstd{,}
-                               \hlstd{sd2} \hlopt{==} \hlnum{0} \hlopt{~} \hlnum{NA_real_}\hlstd{,}
-                               \hlstd{total2} \hlopt{==} \hlnum{0} \hlopt{~} \hlnum{NA_real_}\hlstd{,}
-                               \hlstd{total1} \hlopt{==} \hlnum{0} \hlopt{~} \hlnum{NA_real_}\hlstd{,}
-                               \hlnum{TRUE} \hlopt{~} \hlstd{cohensd))}
-
-  \hlcom{#p-value for continuous outcomes (Student):}
-  \hlstd{data[cont.ind,} \hlstr{"pval.single"}\hlstd{]} \hlkwb{<-} \hlstd{data[cont.ind, ]} \hlopt{%>%}
-    \hlkwd{mutate}\hlstd{(}\hlkwc{t} \hlstd{= (mean1} \hlopt{-} \hlstd{mean2)}\hlopt{/}\hlstd{(}\hlkwd{sqrt}\hlstd{((((total1}\hlopt{-}\hlnum{1}\hlstd{)}\hlopt{*}\hlstd{sd1}\hlopt{^}\hlnum{2}\hlstd{)} \hlopt{+} \hlstd{(total2}\hlopt{-}\hlnum{1}\hlstd{)}\hlopt{*}\hlstd{sd2}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}
-                          \hlstd{(total1} \hlopt{+} \hlstd{total2} \hlopt{-}\hlnum{2}\hlstd{))}\hlopt{*}\hlkwd{sqrt}\hlstd{((}\hlnum{1}\hlopt{/}\hlstd{total1)}\hlopt{+}\hlstd{(}\hlnum{1}\hlopt{/}\hlstd{total2))),}
-           \hlkwc{pval.single} \hlstd{=} \hlnum{2}\hlopt{*}\hlstd{(}\hlnum{1}\hlopt{-}\hlkwd{pt}\hlstd{(}\hlkwd{abs}\hlstd{(t),} \hlkwc{df} \hlstd{= total1} \hlopt{+} \hlstd{total2} \hlopt{-} \hlnum{2}\hlstd{)))} \hlopt{%>%}
-    \hlkwd{select}\hlstd{(pval.single)}
-
-  \hlstd{sd1.0} \hlkwb{<-} \hlkwd{which}\hlstd{(data}\hlopt{$}\hlstd{outcome.flag} \hlopt{==} \hlstr{"CONT"} \hlopt{&} \hlstd{data}\hlopt{$}\hlstd{sd1} \hlopt{==} \hlnum{0}\hlstd{)}
-  \hlstd{sd2.0} \hlkwb{<-} \hlkwd{which}\hlstd{(data}\hlopt{$}\hlstd{outcome.flag} \hlopt{==} \hlstr{"CONT"} \hlopt{&} \hlstd{data}\hlopt{$}\hlstd{sd2} \hlopt{==} \hlnum{0}\hlstd{)}
-  \hlstd{sd.0} \hlkwb{<-} \hlkwd{union}\hlstd{(sd1.0, sd2.0)}
-  \hlstd{data[sd.0,} \hlstr{"pval.single"}\hlstd{]} \hlkwb{<-} \hlnum{NA} \hlcom{#Such that p-value here is not equal to zero}
-  \hlcom{#----------------------------------------------------------------------------------------------#}
-
-  \hlcom{#Outcome.flag == "IV"}
-  \hlstd{data[IV.ind,} \hlstr{"pval.single"}\hlstd{]} \hlkwb{<-} \hlstd{data[IV.ind, ]} \hlopt{%>%}
-    \hlkwd{mutate}\hlstd{(}\hlkwc{pval.single} \hlstd{=} \hlnum{2}\hlopt{*}\hlstd{(}\hlnum{1}\hlopt{-}\hlkwd{pnorm}\hlstd{(}\hlkwd{abs}\hlstd{((effect)}\hlopt{/}\hlstd{se))))} \hlopt{%>%}
-    \hlkwd{select}\hlstd{(pval.single)}
-  \hlcom{#----------------------------------------------------------------------------------------------#}
-
-  \hlcom{#Declare smd.ordl, cohensd and SMD of IV flag all as "smd.pool":}
-  \hlstd{data} \hlkwb{<-} \hlstd{data} \hlopt{%>%}
-    \hlkwd{mutate}\hlstd{(}\hlkwc{smd.pool} \hlstd{=} \hlkwd{case_when}\hlstd{(outcome.flag} \hlopt{==} \hlstr{"DICH"} \hlopt{~} \hlstd{smd.ordl,}
-                                \hlstd{outcome.flag} \hlopt{==} \hlstr{"CONT"} \hlopt{~} \hlstd{cohensd,}
-                                \hlstd{outcome.flag} \hlopt{==} \hlstr{"IV"} \hlopt{&}
-                                  \hlstd{outcome.measure.merged} \hlopt{==} \hlstr{"SMD"} \hlopt{~} \hlstd{effect,}
-                                \hlnum{TRUE} \hlopt{~} \hlnum{NA_real_}\hlstd{),}
-           \hlkwc{se.smd.pool} \hlstd{=} \hlkwd{case_when}\hlstd{(outcome.flag} \hlopt{==} \hlstr{"DICH"} \hlopt{~} \hlkwd{sqrt}\hlstd{(var.smd.ordl),}
-                                   \hlstd{outcome.flag} \hlopt{==} \hlstr{"CONT"} \hlopt{~} \hlkwd{sqrt}\hlstd{(var.cohensd),}
-                                   \hlstd{outcome.flag} \hlopt{==} \hlstr{"IV"} \hlopt{&}
-                                     \hlstd{outcome.measure.merged} \hlopt{==} \hlstr{"SMD"} \hlopt{~} \hlstd{se,}
-                                   \hlnum{TRUE} \hlopt{~} \hlnum{NA_real_}\hlstd{))}
-  \hlcom{#----------------------------------------------------------------------------------------------#}
-
-  \hlcom{#Transform effect sizes:}
-  \hlstd{smd.pool.ind} \hlkwb{<-} \hlkwd{which}\hlstd{(}\hlopt{!}\hlkwd{is.na}\hlstd{(data}\hlopt{$}\hlstd{smd.pool))}
-
-  \hlcom{#Pearson correlation:}
-  \hlstd{data[smd.pool.ind,} \hlstr{"cor.pearson"}\hlstd{]}\hlkwb{<-} \hlstd{data[smd.pool.ind, ]} \hlopt{%>%} \hlkwd{mutate}\hlstd{(}
-    \hlkwc{a} \hlstd{= ((total1} \hlopt{+} \hlstd{total2)}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}\hlstd{(total1}\hlopt{*}\hlstd{total2),}
-    \hlkwc{cor.pearson}  \hlstd{= smd.pool}\hlopt{/}\hlkwd{sqrt}\hlstd{((smd.pool}\hlopt{^}\hlnum{2}\hlstd{)} \hlopt{+} \hlstd{a),}
-    \hlkwc{var.cor.pearson} \hlstd{= ((a}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{*}\hlstd{se.smd.pool}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}\hlstd{(((smd.pool}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{+}\hlstd{a)}\hlopt{^}\hlnum{3}\hlstd{))} \hlopt{%>%}
-    \hlkwd{select}\hlstd{(cor.pearson)}
-
-  \hlstd{data[smd.pool.ind,} \hlstr{"var.cor.pearson"}\hlstd{]}\hlkwb{<-} \hlstd{data[smd.pool.ind, ]} \hlopt{%>%}
-    \hlkwd{mutate}\hlstd{(}
-    \hlkwc{a} \hlstd{= ((total1} \hlopt{+} \hlstd{total2)}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}\hlstd{(total1}\hlopt{*}\hlstd{total2),}
-    \hlkwc{cor.pearson}  \hlstd{= smd.pool}\hlopt{/}\hlkwd{sqrt}\hlstd{((smd.pool}\hlopt{^}\hlnum{2}\hlstd{)} \hlopt{+} \hlstd{a),}
-    \hlkwc{var.cor.pearson} \hlstd{= ((a}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{*}\hlstd{se.smd.pool}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{/}\hlstd{(((smd.pool}\hlopt{^}\hlnum{2}\hlstd{)}\hlopt{+}\hlstd{a)}\hlopt{^}\hlnum{3}\hlstd{))} \hlopt{%>%}
-    \hlkwd{select}\hlstd{(var.cor.pearson)}
-
-  \hlcom{#Fisher's z-score:}
-  \hlstd{data[smd.pool.ind,} \hlstr{"z"}\hlstd{]} \hlkwb{<-} \hlstd{data[smd.pool.ind, ]} \hlopt{%>%}
-    \hlkwd{mutate}\hlstd{(}\hlkwc{z} \hlstd{=} \hlkwd{atan}\hlstd{(}\hlkwc{x} \hlstd{= cor.pearson),}
-           \hlkwc{var.z}\hlstd{=} \hlnum{1}\hlopt{/}\hlstd{(total1} \hlopt{+} \hlstd{total2} \hlopt{-} \hlnum{3}\hlstd{))} \hlopt{%>%} \hlkwd{select}\hlstd{(z)}
-  \hlstd{data[smd.pool.ind,} \hlstr{"var.z"}\hlstd{]} \hlkwb{<-} \hlstd{data[smd.pool.ind, ]} \hlopt{%>%}
-    \hlkwd{mutate}\hlstd{(}\hlkwc{z} \hlstd{=} \hlkwd{atan}\hlstd{(}\hlkwc{x} \hlstd{= cor.pearson),}
-           \hlkwc{var.z}\hlstd{=} \hlnum{1}\hlopt{/}\hlstd{(total1} \hlopt{+} \hlstd{total2} \hlopt{-} \hlnum{3}\hlstd{))} \hlopt{%>%} \hlkwd{select}\hlstd{(var.z)}
-
-  \hlcom{#----------------------------------------------------------------------------------------------#}
-  \hlstd{data}\hlopt{$}\hlstd{sig.single} \hlkwb{<-} \hlkwd{ifelse}\hlstd{(data}\hlopt{$}\hlstd{pval.single} \hlopt{<} \hlnum{0.05}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{0}\hlstd{)}
-
-  \hlkwd{return}\hlstd{(data)}
-\hlstd{\}}
-
-\hlcom{########################################################################################################}
-
-\hlcom{#Function to find sensitivity analyses.  The function gives all meta-analyses }
-\hlcom{#that are subdivided}
-\hlcom{#into sensitivity analyses a common number. }
-\hlcom{#*to use with "data %>% mutate(.. = dupl.finder(..))"*}
-\hlstd{dupl.finder} \hlkwb{<-} \hlkwa{function}\hlstd{(}\hlkwc{effects}\hlstd{,} \hlkwc{names}\hlstd{,} \hlkwc{metas}\hlstd{)\{}
-
-  \hlstd{results} \hlkwb{<-} \hlkwd{rep}\hlstd{(}\hlnum{NA}\hlstd{,} \hlkwc{times} \hlstd{=} \hlkwd{length}\hlstd{(effects))}
-  \hlstd{meta.double.marker} \hlkwb{<-} \hlnum{1}
-
-  \hlkwa{for}\hlstd{(u} \hlkwa{in} \hlkwd{seq_along}\hlstd{(effects))\{}
-
-    \hlkwa{if}\hlstd{(}\hlkwd{is.na}\hlstd{(results[u]))\{}
-
-      \hlstd{double.indices} \hlkwb{<-} \hlkwd{which}\hlstd{(effects[u]} \hlopt{==} \hlstd{effects} \hlopt{&} \hlstd{names[u]} \hlopt{==} \hlstd{names)}
-
-      \hlkwa{if}\hlstd{(}\hlkwd{length}\hlstd{(double.indices)} \hlopt{>} \hlnum{1}\hlstd{)\{}
-    \hlcom{#If any meta-analysis has already duplicates, give all the same double marker}
-        \hlkwa{if}\hlstd{(}\hlkwd{any}\hlstd{(}\hlopt{!}\hlkwd{is.na}\hlstd{(results[double.indices])))\{}
-
-          \hlstd{already.marked} \hlkwb{<-} \hlkwd{which}\hlstd{(}\hlopt{!}\hlkwd{is.na}\hlstd{(results[double.indices]))}
-          \hlstd{meta.double.marker.2} \hlkwb{<-} \hlkwd{unique}\hlstd{(results[double.indices[already.marked]])}
-          \hlcom{#Collect meta.ids with same double markers}
-          \hlstd{meta.ids.2} \hlkwb{<-} \hlkwd{unique}\hlstd{(metas[}\hlkwd{which}\hlstd{(results} \hlopt{%in%} \hlstd{meta.double.marker.2)])}
-          \hlstd{meta.ids} \hlkwb{<-} \hlstd{metas[double.indices]} \hlcom{#Collect metas with the same results}
-
-          \hlstd{meta.ids.pooled} \hlkwb{<-} \hlkwd{union}\hlstd{(meta.ids, meta.ids.2)}
-          \hlstd{meta.indices} \hlkwb{<-} \hlkwd{which}\hlstd{(metas} \hlopt{%in%} \hlstd{meta.ids.pooled)}
-          \hlstd{results[meta.indices]} \hlkwb{<-} \hlstd{meta.double.marker}
-
-        \hlstd{\}} \hlkwa{else}\hlstd{\{}
-
-          \hlstd{meta.ids} \hlkwb{<-} \hlstd{metas[double.indices]}
-          \hlstd{meta.indices} \hlkwb{<-} \hlkwd{which}\hlstd{(metas} \hlopt{%in%} \hlstd{meta.ids)}
-          \hlstd{results[meta.indices]} \hlkwb{<-} \hlstd{meta.double.marker}
-
-        \hlstd{\}}
-      \hlstd{\}} \hlkwa{else} \hlstd{results[u]} \hlkwb{<-} \hlnum{0}
-
-      \hlstd{meta.double.marker} \hlkwb{<-} \hlstd{meta.double.marker} \hlopt{+} \hlnum{1}
-    \hlstd{\}\}}
-  \hlkwd{return}\hlstd{(results)}
-\hlstd{\}}
-
-\hlcom{#Function picks the largest meta-analysis within a set of sensitivity analyses,}
-\hlcom{#and assigns it a "0" *to use with "data %>% mutate(.. = dupl.finder(..))":*}
-\hlstd{dupl.max.finder} \hlkwb{<-} \hlkwa{function}\hlstd{(}\hlkwc{duplicate.index}\hlstd{,} \hlkwc{study.number}\hlstd{,} \hlkwc{metas}\hlstd{)\{}
-  \hlstd{results} \hlkwb{<-} \hlkwd{rep}\hlstd{(}\hlnum{NA}\hlstd{,} \hlkwd{length}\hlstd{(duplicate.index))}
-
-  \hlkwa{for}\hlstd{(u} \hlkwa{in} \hlkwd{seq_along}\hlstd{((duplicate.index)))\{}
-
-    \hlstd{duplicate.indices} \hlkwb{<-} \hlkwd{which}\hlstd{(duplicate.index} \hlopt{%in%} \hlstd{duplicate.index[u])}
-
-    \hlkwa{if}\hlstd{(duplicate.index[u]} \hlopt{!=} \hlnum{0}\hlstd{)\{}
-
-      \hlstd{meta.ids} \hlkwb{<-} \hlstd{metas[duplicate.indices]}
-
-      \hlstd{max.meta.id} \hlkwb{<-} \hlstd{meta.ids[}\hlkwd{which.max}\hlstd{(study.number[duplicate.indices])]}
-      \hlstd{max.meta.indices} \hlkwb{<-} \hlkwd{which}\hlstd{(metas} \hlopt{%in%} \hlstd{max.meta.id)}
-      \hlkwa{if}\hlstd{(}\hlkwd{length}\hlstd{(}\hlkwd{unique}\hlstd{(max.meta.id))} \hlopt{<} \hlnum{2}\hlstd{)\{}
-        \hlstd{results[max.meta.indices]} \hlkwb{<-} \hlnum{0}
-      \hlstd{\}} \hlkwa{else} \hlkwd{print}\hlstd{(}\hlstr{"error"}\hlstd{)}
-
-    \hlstd{\}} \hlkwa{else} \hlstd{results[duplicate.indices]} \hlkwb{<-} \hlnum{0}
-
-  \hlstd{\}}
-
-  \hlstd{results[}\hlkwd{is.na}\hlstd{(results)]} \hlkwb{<-} \hlnum{1}
-
-  \hlkwd{return}\hlstd{(results)}
-\hlstd{\}}
-\end{alltt}
-\end{kframe}
-\end{knitrout}
-
-\section{Analysis}
-
-Data is subdivided into meta-analyses, and after all meta-analyses are excluded that are not suited for analysis, meta-analyses are done and saved.
-"data.ext2" is the dataset processed with the previously introduced "pb.process3" function. Functions defined in the global environment are marked with
-a "*USER.DEF*". They can be find in the next section.
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
-\begin{alltt}
-\hlcom{#Load data:}
-\hlcom{# rm(list = ls())}
-\hlcom{# PATH_HOME = path.expand("~") # user home}
-\hlcom{# PATH = file.path(PATH_HOME, 'Data/PubBias')}
-\hlcom{# PATH2 = file.path(PATH_HOME, 'PubBias')}
-\hlcom{# FILE = 'cochrane_2019-07-04.csv'}
-\hlcom{# PATH_DATA = file.path(PATH, 'data')}
-\hlcom{# PATH_CODE = file.path(PATH2, 'code')}
-\hlcom{# PATH_RESULTS = file.path(PATH2, 'results_new')}
-\hlcom{# PATH_FIGURES = file.path(PATH_RESULTS, 'figures')}
-
-\hlkwd{source}(\hlkwd{file.path}(PATH_CODE, \hlstr{'PubBias_functions.R'})) \hlcom{#Load user defined functions}
-\hlkwd{load}(\hlkwd{file.path}(PATH_DATA, \hlstr{"PubBias_2019-07-19.RData"})) #Load data as contributed 
-\hlcom{#by Simon Schwab.}
-\hlcom{# load(file.path(PATH_RESULTS, "data_used_for_analysis.RData")) }
-data.ext2 <- \hlkwd{pb.process3}(data) \hlcom{#*USER.DEF*}
-
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-\hlcom{# PRE-ANALYSIS PART - EXCLUDE UNSUITABLE META-ANALYSES:}
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{#To skip pre-analysis:}
-\hlcom{# load(file.path(PATH_RESULTS, "meta_id_vector.RData"))}
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{# # ---------- Uncomment to run pre-analysis --------------}
-\hlcom{# # Get exclusion critetia (I-squared, n. sig. findings, s.e. ratio, dupl.index):}
-meta.info.bin <- data.ext2 %>% \hlkwd{filter}(outcome.flag == \hlstr{"DICH"}) %>%
-  \hlkwd{group_by}(meta.id) %>%
-  \hlkwd{mutate}(n.pre = \hlkwd{n}()) %>% \hlkwd{filter}(n.pre >= 10) %>%
-  \hlkwd{filter}(!\hlkwd{all}(events1 == 0) & !\hlkwd{all}(events2 == 0)) %>% \hlcom{#No events}
-  \hlkwd{mutate}(se.lrr = \hlkwd{sqrt}(var.lrr)) %>%
-  \hlkwd{summarize}(dupl.remove = \hlkwd{unique}(dupl.remove),
-            id = \hlkwd{unique}(id),
-            outcome.desired = \hlkwd{unique}(outcome.desired),
-            n.sig.single = \hlkwd{sum}(sig.single, na.rm = T),
-            se.min = \hlkwd{min}(se.lrr, na.rm = T),
-            se.max = \hlkwd{max}(se.lrr, na.rm = T))
-
-meta.info.cont <- data.ext2 %>% \hlkwd{filter}(outcome.flag == \hlstr{"CONT"}) %>%
-  \hlkwd{group_by}(meta.id) %>%
-  \hlkwd{mutate}(n.pre = \hlkwd{n}()) %>% \hlkwd{filter}(n.pre >= 10) %>%
-  \hlkwd{filter}(!\hlkwd{all}(mean1 == 0) & !\hlkwd{all}(mean2 == 0)) %>% \hlcom{#No means}
-  \hlkwd{filter}(!\hlkwd{all}(sd1 == 0) | !\hlkwd{all}(sd2 == 0)) %>% \hlcom{#No sd's}
-  \hlkwd{summarize}(dupl.remove = \hlkwd{unique}(dupl.remove),
-            id = \hlkwd{unique}(id),
-            outcome.desired = \hlkwd{unique}(outcome.desired),
-            n.sig.single = \hlkwd{sum}(sig.single, na.rm = T),
-            se.min = \hlkwd{min}(se, na.rm = T),
-            se.max = \hlkwd{max}(se, na.rm = T))
-
-meta.info.iv <- data.ext2 %>%
-  \hlkwd{group_by}(meta.id) %>%
-  \hlkwd{mutate}(n.pre = \hlkwd{n}()) %>% \hlkwd{filter}(n.pre >= 10) %>%
-  \hlkwd{filter}(outcome.flag == \hlstr{"IV"}) %>%
-  \hlkwd{filter}(outcome.measure.merged == \hlstr{"Rate Ratio"} | 
-           outcome.measure.merged == \hlstr{"SMD"} |
-           outcome.measure.merged == \hlstr{"MD"} | 
-           outcome.measure.merged == \hlstr{"Hazard Ratio"} |
-           outcome.measure.merged == \hlstr{"OR"} | 
-           outcome.measure.merged == \hlstr{"RR"}) %>% #Remove outcomes w. unclear def.
-  \hlkwd{summarize}(dupl.remove = \hlkwd{unique}(dupl.remove),
-            id = \hlkwd{unique}(id),
-            outcome.desired = \hlkwd{unique}(outcome.desired),
-            n.sig.single = \hlkwd{sum}(sig.single, na.rm = T),
-            se.min = \hlkwd{min}(se, na.rm = T),
-            se.max = \hlkwd{max}(se, na.rm = T))
-
-meta.info.pre <- \hlkwd{rbind}(meta.info.bin, meta.info.cont, meta.info.iv) 
-\hlcom{#To save to control how many are excluded}
-
-meta.info.pre <- meta.info.pre %>%
-  \hlkwd{filter}(id %in% data.review$id[\hlkwd{which}(data.review$withdrawn == FALSE)]) 
-\hlcom{#No withdrawn meta-analyses}
-
-meta.info <- meta.info.pre %>% 
-  \hlkwd{filter}(n.sig.single > 0) %>% \hlcom{#At least one significant result}
-  \hlkwd{filter}((se.max^2)/(se.min^2) > 4) %>% \hlcom{#variance ratio > 4}
-  \hlkwd{filter}(dupl.remove == 0) %>% \hlcom{#no duplicates}
-  \hlkwd{filter}(outcome.desired == \hlstr{"efficacy"}) #Only efficacy outcomes
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{#Meta-analysis to get I2 (random effects meta-analysis):}
-meta.id.vector.org.ranef <- meta.info$meta.id \hlcom{#Do meta-analysis for each of those}
-
-meta.org.ranef.list <- \hlkwd{list}()
-counter <- 0
-\hlkwd{for}(u in meta.id.vector.org.ranef)\{
-  counter <- counter + 1
-  temp <- data.ext2 %>% \hlkwd{filter}(meta.id == u)
-  \hlkwd{print}(\hlkwd{c}(u, counter))
-  meta.org.ranef.list[[counter]] <- \hlkwd{meta.fct.ranef.mom}(temp)
-\}
-
-exclusion.estimates <- \hlkwd{cbind}(
-  meta.id = meta.id.vector.org.ranef,
-  n = \hlkwd{unlist}(\hlkwd{lapply}(meta.org.ranef.list, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$k\})),
-  Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.org.ranef.list, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$QE\})))
-
-meta.info.pre2 <- \hlkwd{merge}(meta.info, exclusion.estimates, by = \hlstr{"meta.id"})
-meta.info.I2 <- meta.info.pre2 %>% 
-  \hlkwd{rowwise}() %>% \hlkwd{mutate}(I2  = \hlkwd{max}(0, (Q - n + 1)/Q)) \hlcom{#calculate I2}
-meta.info <- meta.info.I2 %>% \hlkwd{filter}(n > 9) %>% 
-  \hlkwd{filter}(I2 < 0.5) \hlcom{#exclude I2 >= 0.5}
-meta.id.vector <- meta.info$meta.id \hlcom{#Vector of meta-ids that match the criteria.}
-
-\hlkwd{save}(meta.id.vector, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta_id_vector.RData"}))
-\hlkwd{save}(meta.info.I2, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta_id_I2.RData"}))
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{#Get more extensive information from the original dataset about the meta-analyses:}
-meta.info.extended <- data.ext2 %>% 
-  \hlkwd{filter}(meta.id %in% meta.id.vector) %>% 
-  \hlkwd{group_by}(meta.id) %>%
-  \hlkwd{summarize}(id = \hlkwd{unique}(id),
-            outcome.flag = \hlkwd{unique}(outcome.flag),
-            comparison.nr = \hlkwd{unique}(comparison.nr),
-            comparison.name = \hlkwd{unique}(comparison.name),
-            outcome.name = \hlkwd{unique}(outcome.name),
-            outcome.nr = \hlkwd{unique}(outcome.nr),
-            subgroup.name = \hlkwd{unique}(subgroup.name),
-            subgroup.nr = \hlkwd{unique}(subgroup.nr),
-            outcome.measure.merged = \hlkwd{unique}(outcome.measure.merged),
-            outcome.measure = \hlkwd{unique}(outcome.measure),
-            outcome.desired = \hlkwd{unique}(outcome.desired),
-            mean.samplesize = \hlkwd{mean}(total1 + total2, na.rm = T),
-            total.samplesize = \hlkwd{sum}(total1 + total2),
-            var.samplesize = \hlkwd{var}(total1 + total2, na.rm = T),
-            min.samplesize = \hlkwd{min}(\hlkwd{min}(total1, na.rm = T), \hlkwd{min}(total2, na.rm = T)),
-            total.events = \hlkwd{sum}(events1 + events2),
-            mean.events = \hlkwd{mean}(events1 + events2),
-            mean.publication.year = \hlkwd{mean}(study.year, na.rm = TRUE),
-            first.publication.year = \hlkwd{min}(study.year, na.rm = T),
-\hlcom{            #*USER.DEF* function to detect the expected side of bias}
-            side = \hlkwd{bias.side.fct2}(outcome = outcome.flag, outcome.measure.merged, 
-                                  lrr = lrr, var.lrr = var.lrr, smd = cohensd, 
-                                  var.smd = var.cohensd, effect = effect, se = se),
-
-            n.sig.single = \hlkwd{sum}(sig.single, na.rm = T),
-            NA.sig.single = \hlkwd{sum}(\hlkwd{is.na}(sig.single)),
-            se.min = \hlkwd{min}(se, na.rm = T),
-            se.max = \hlkwd{max}(se, na.rm = T))
-
-\hlcom{######################################################################################}
-\hlcom{######################################################################################}
-\hlcom{######################################################################################}
-\hlcom{# ANALYSIS PART: META-ANALYSES, TESTS AND ADJUSTMENTS: ###############################}
-\hlcom{######################################################################################}
-\hlcom{######################################################################################}
-\hlcom{######################################################################################}
-
-\hlcom{#Do all analyses with Fixed effects meta-analysis method and paule mandel tau^2 }
-\hlcom{#estimator}
-\hlkwd{settings.meta}(method.tau = \hlstr{"PM"}, method = \hlstr{"Inverse"})
-
-\hlcom{#Load previously constructed lists (to skip analysis):}
-\hlcom{# load(file.path(PATH_RESULTS, "meta_complete_list_bin.RData"))}
-\hlcom{# load(file.path(PATH_RESULTS, "meta_complete_list_cont.RData"))}
-\hlcom{# load(file.path(PATH_RESULTS, "meta_complete_list_iv.RData"))}
-\hlcom{# load(file.path(PATH_RESULTS, "meta_complete_list_zscore.RData"))}
-\hlcom{# load(file.path(PATH_RESULTS, "meta_complete_list_cohensd.RData"))}
-
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-\hlcom{# BINARY DATA META-ANALYSES: ----------------------------------------------------------------------------------------#}
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{# # -------- Uncomment to run analysis ----------}
-meta.id.vector.bin <- 
-  meta.info.extended$meta.id[\hlkwd{which}(meta.info.extended$outcome.flag == \hlstr{"DICH"})]
-meta.analyses <- \hlkwd{list}()
-meta.analyses.asd <- \hlkwd{list}()
-meta.analyses.reg <- \hlkwd{list}()
-meta.analyses.copas <- \hlkwd{list}()
-meta.tests.harbord <- \hlkwd{list}()
-meta.tests.peter <- \hlkwd{list}()
-meta.tests.rucker.mm <- \hlkwd{list}()
-meta.tests.rucker.linreg <- \hlkwd{list}()
-meta.tests.schwarzer <- \hlkwd{list}()
-meta.tests.excess <- \hlkwd{list}()
-counter <- 0
-\hlkwd{for}(u in meta.id.vector.bin)\{
-	counter <- counter + 1
-	\hlkwd{print}(\hlkwd{c}(u, counter))
-	meta.analyses[[counter]] <- 
-	  \hlkwd{metabin}(event.e = events1c, n.e = total1, event.c = events2c, n.c = total2,
-	          studlab = study.name, sm = \hlstr{"RR"},
-	          method = \hlstr{"Inverse"}, data = data.ext2[data.ext2$meta.id == u,])
-
-\hlcom{	#Arcsine transformed proportions to use in combination with Rücker's test:}
-	meta.analyses.asd[[counter]] <- 
-	  \hlkwd{metabin}(event.e = events1c, n.e = total1, event.c = events2c, n.c = total2,
-	          studlab = study.name, sm = \hlstr{"ASD"}, 
-	          method = \hlstr{"Inverse"}, data = data.ext2[data.ext2$meta.id == u,])
-
-\hlcom{	#Adjustment for publication bias}
-	meta.analyses.reg[[counter]] <- \hlkwd{limitmeta}(meta.analyses[[counter]])
-	meta.analyses.copas[[counter]] <- \hlkwd{auto.copas}(meta.analyses[[counter]], 
-	                         sig.level = 0.1) \hlcom{#*USER.DEF* Copas selection model.}
-
-\hlcom{	#Publication bias tests.}
-	meta.tests.excess[[counter]] <- \hlkwd{tes.fct2}(data = data.ext2[data.ext2$meta.id == u,])
-	meta.tests.harbord[[counter]] <- 
-	  \hlkwd{metabias}(meta.analyses[[counter]], method.bias = \hlstr{"score"}, k.min = 2)
-	meta.tests.peter[[counter]] <- 
-	  \hlkwd{metabias}(meta.analyses[[counter]], method.bias = \hlstr{"peters"}, k.min = 2)
-	meta.tests.schwarzer[[counter]] <- 
-	  \hlkwd{metabias}(meta.analyses[[counter]], method.bias = \hlstr{"count"}, k.min = 2)
-	meta.tests.rucker.mm[[counter]] <- 
-	  \hlkwd{metabias}(meta.analyses.asd[[counter]], method.bias = \hlstr{"mm"}, k.min = 2)
-	meta.tests.rucker.linreg[[counter]] <- 
-	  \hlkwd{metabias}(meta.analyses.asd[[counter]], method.bias = \hlstr{"linreg"}, k.min = 2)
-\}
-
-\hlcom{# counter.unknown.bin.copas.error <- 0}
-\hlcom{# for(u in meta.id.vector.bin)\{}
-\hlcom{# 	if(length(meta.analyses.copas[[counter]]) < 3)\{}
-\hlcom{# 		meta.analyses.copas[[counter]] <- c(NA, NA, NA)}
-\hlcom{# 		counter.unknown.bin.copas.error <- counter.unknown.bin.copas.error + 1}
-\hlcom{# 	\}}
-\hlcom{# \}}
-\hlcom{# print(c("unknown.bin.copas.errors = ", counter.unknown.bin.copas.error))}
-\hlcom{#}
-\hlcom{# bin.meta.list <- list(data.ext2, meta.id.vector.bin, meta.analyses,}
-\hlcom{# 											meta.analyses.asd,}
-\hlcom{# 											meta.analyses.reg,}
-\hlcom{# 											meta.analyses.copas,}
-\hlcom{# 											meta.tests.excess,}
-\hlcom{# 											meta.tests.harbord,}
-\hlcom{# 											meta.tests.peter,}
-\hlcom{# 											meta.tests.rucker.mm,}
-\hlcom{# 											meta.tests.schwarzer,}
-\hlcom{# 											meta.tests.excess,}
-\hlcom{# 											meta.tests.rucker.linreg)}
-\hlcom{# save(bin.meta.list, file =  file.path(PATH_RESULTS, "meta_complete_list_bin.RData"))}
-\hlcom{# #--------------------------------------------------------------------------------------------------------------------#}
-\hlcom{# }
-\hlcom{# #Load analysis data:}
-\hlcom{# meta.id.vector.bin <- bin.meta.list[[2]]}
-\hlcom{# meta.analyses <- bin.meta.list[[3]]}
-\hlcom{# meta.analyses.reg <- bin.meta.list[[5]]}
-\hlcom{# meta.analyses.copas <- bin.meta.list[[6]]}
-\hlcom{# meta.analyses.trimfill <- bin.meta.list[[7]]}
-\hlcom{# meta.tests.harbord <- bin.meta.list[[8]]}
-\hlcom{# meta.tests.peter <- bin.meta.list[[9]]}
-\hlcom{# meta.tests.rucker.mm <- bin.meta.list[[10]]}
-\hlcom{# meta.tests.schwarzer <- bin.meta.list[[11]]}
-\hlcom{# meta.tests.excess <- bin.meta.list[[12]]}
-\hlcom{# meta.tests.rucker.linreg <- bin.meta.list[[13]]}
-
-\hlcom{#Extract from lists:}
-bin.results <- \hlkwd{data.frame}(
-  meta.id = meta.id.vector.bin,
-  meta.es.measure = \hlkwd{rep}(times = \hlkwd{length}(meta.id.vector.bin), \hlstr{"log risk ratio"}),
-
-  n.sig.single2 = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{\hlkwd{length}(\hlkwd{which}(meta.analysis$pval < 0.05))\})),
-
-\hlcom{  #Meta-analysis:}
-  est.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.fixed\})),
-  est.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.random\})),
-  zval.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$zval.fixed\})),
-  zval.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$zval.random\})),
-
-  pval.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                   FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.fixed\})),
-  pval.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.random\})),
-
-  se.est.fixef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.fixed\})),
-  se.est.ranef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.random\})),
-
-  Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$Q\})),
-  pval.Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                         FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.Q\})),
-\hlcom{  #I2 = unlist(lapply(meta.analyses, FUN = function(meta.analysis)\{meta.analysis$I2.w\})),}
-  tau = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                      FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$tau\})),
-\hlcom{  #se.tau = unlist(lapply(meta.analyses, FUN = function(meta.analysis)\{meta.analysis$se.tau\})),}
-  sparse = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                         FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$sparse\})),
-  k = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$k\})),
-
-\hlcom{  #Adjustment:}
-  method.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$method.adjust\})),
-  est.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$TE.adjust\})),
-  se.est.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$seTE.adjust\})),
-  zval.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$zval.adjust\})),
-  pval.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
-  alpha.r = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
-  beta.r = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
-  Q.small = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$Q.small\})),
-  Q.resid = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$Q.resid\})),
-  G.squared = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$G.squared\})),
-
-  est.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[1]\})),
-  se.est.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[2]\})),
-  missing.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[3]\})),
-
-\hlcom{  #Tests;}
-  pval.d.tes.org = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                                 FUN = \hlkwd{function}(object)\{object[3]\})),
-  pval.d.tes = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                             FUN = \hlkwd{function}(object)\{object[4]\})),
-  stat.d.tes = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                             FUN = \hlkwd{function}(object)\{object[2]\})),
-  excess.d = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                           FUN = \hlkwd{function}(object)\{object[5]\})) - 
-    \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                  FUN = \hlkwd{function}(object)\{object[6]\})),
-  pval.harbord = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.harbord, 
-                               FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
-  stat.harbord = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.harbord, 
-                               FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
-  pval.peter = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.peter, 
-                             FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
-  stat.peter = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.peter, 
-                             FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
-  pval.rucker = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.rucker.mm, 
-                              FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
-  stat.rucker = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.rucker.mm, 
-                              FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
-  pval.rucker.linreg = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.rucker.linreg, 
-                              FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
-  stat.rucker.linreg = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.rucker.linreg, 
-                              FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
-  pval.schwarzer = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.schwarzer, 
-                              FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
-  stat.schwarzer = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.schwarzer, 
-                              FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\}))
-)
-
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-\hlcom{# CONTINUOUS DATA META-ANALYSES: ------------------------------------------------------------------------------------#}
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{# # -------- Uncomment to run analysis ----------}
-meta.id.vector.cont <- 
-  meta.info.extended$meta.id[\hlkwd{which}(meta.info.extended$outcome.flag == \hlstr{"CONT"})]
-meta.analyses <- \hlkwd{list}()
-meta.analyses.reg <- \hlkwd{list}()
-meta.analyses.copas <- \hlkwd{list}()
-meta.analyses.trimfill <- \hlkwd{list}()
-meta.tests.excess <- \hlkwd{list}()
-meta.tests.linreg <- \hlkwd{list}()
-meta.tests.begg <- \hlkwd{list}()
-meta.tests.mm <- \hlkwd{list}()
-counter <- 0
-\hlkwd{for}(u in meta.id.vector.cont)\{
-	counter <- counter + 1
-	\hlkwd{print}(\hlkwd{c}(u, counter))
-	outcome.measure.merged <- 
-	  \hlkwd{as.character}(\hlkwd{unique}(data.ext2[data.ext2$meta.id == u,
-	                 \hlstr{"outcome.measure.merged"}])$outcome.measure.merged)
-	meta.analyses[[counter]] <- 
-	  \hlkwd{metacont}(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2,
-						mean.c = mean2, sd.c = sd2, sm = outcome.measure.merged, 
-						studlab = study.name, data = data.ext2[data.ext2$meta.id == u,])
-	meta.analyses.reg[[counter]] <- \hlkwd{limitmeta}(meta.analyses[[counter]])
-	meta.analyses.trimfill[[counter]] <- \hlkwd{trimfill}(meta.analyses[[counter]])
-	meta.analyses.copas[[counter]] <- \hlkwd{auto.copas}(meta.analyses[[counter]], 
-	                                             sig.level = 0.1)
-
-	meta.tests.excess[[counter]] <- 
-	  \hlkwd{tes.fct2}(data = data.ext2[data.ext2$meta.id == u,])
-	meta.tests.linreg[[counter]] <- \hlkwd{metabias}(meta.analyses[[counter]], 
-	                                         method.bias = \hlstr{"linreg"}, k.min = 2)
-	meta.tests.begg[[counter]] <- \hlkwd{metabias}(meta.analyses[[counter]], 
-	                                       method.bias = \hlstr{"rank"}, k.min = 2)
-	meta.tests.mm[[counter]] <- \hlkwd{metabias}(meta.analyses[[counter]], 
-	                                     method.bias = \hlstr{"mm"}, k.min = 2)
-\hlcom{# \}}
-\hlcom{# cont.meta.list <- list(data.ext2, meta.id.vector.cont, meta.analyses,}
-\hlcom{# 											 meta.analyses.reg,}
-\hlcom{# 											 meta.analyses.copas,}
-\hlcom{# 											 meta.analyses.trimfill,}
-\hlcom{# 											 meta.tests.linreg,}
-\hlcom{# 											 meta.tests.begg,}
-\hlcom{# 											 meta.tests.mm,}
-\hlcom{# 											 meta.tests.excess)}
-\hlcom{# save(cont.meta.list, file =  file.path(PATH_RESULTS, "meta_complete_list_cont.RData"))}
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{#Load analysis data:}
-\hlcom{# meta.id.vector.cont <- cont.meta.list[[2]]}
-\hlcom{# meta.analyses <- cont.meta.list[[3]]}
-\hlcom{# meta.analyses.reg <- cont.meta.list[[4]]}
-\hlcom{# meta.analyses.copas <- cont.meta.list[[5]]}
-\hlcom{# meta.analyses.trimfill <- cont.meta.list[[6]]}
-\hlcom{# meta.tests.linreg <- cont.meta.list[[7]]}
-\hlcom{# meta.tests.begg <- cont.meta.list[[8]]}
-\hlcom{# meta.tests.mm <- cont.meta.list[[9]]}
-\hlcom{# meta.tests.excess <- cont.meta.list[[10]]}
-
-\hlcom{#Extract from lists:}
-cont.results <- \hlkwd{data.frame}(
-  meta.id = meta.id.vector.cont,
-  meta.es.measure = \hlkwd{rep}(\hlstr{"std. mean difference"}, times = \hlkwd{length}(meta.id.vector.cont)),
-
-  n.sig.single2 = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, FUN = \hlkwd{function}(meta.analysis)\{\hlkwd{length}(\hlkwd{which}(meta.analysis$pval < 0.05))\})),
-
-\hlcom{  #Meta-Analysis}
-  est.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.fixed\})),
-  est.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.random\})),
-
-  zval.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$zval.fixed\})),
-  zval.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$zval.random\})),
-
-  pval.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.fixed\})),
-  pval.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.random\})),
-
-  se.est.fixef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.fixed\})),
-  se.est.ranef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.random\})),
-
-  Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$Q\})),
-  pval.Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.Q\})),
-  tau = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$tau\})),
-  k = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$k\})),
-
-\hlcom{  #Adjustment:}
-  method.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$method.adjust\})),
-  est.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$TE.adjust\})),
-  se.est.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$seTE.adjust\})),
-  zval.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$zval.adjust\})),
-  pval.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
-  alpha.r = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
-  beta.r = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
-  Q.small = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$Q.small\})),
-  Q.resid = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$Q.resid\})),
-  G.squared = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$G.squared\})),
-
-  est.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
-                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[1]\})),
-  se.est.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
-                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[2]\})),
-  missing.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
-                      FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[3]\})),
-
-\hlcom{  #Tests:}
-  pval.d.tes.org = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                              FUN = \hlkwd{function}(object)\{object[3]\})),
-  pval.d.tes = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                              FUN = \hlkwd{function}(object)\{object[4]\})),
-  stat.d.tes = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                              FUN = \hlkwd{function}(object)\{object[2]\})),
-  excess.d = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                              FUN = \hlkwd{function}(object)\{object[5]\})) - 
-    \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                              FUN = \hlkwd{function}(object)\{object[6]\})),
-  pval.egger = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.linreg, 
-                             FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
-  stat.egger = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.linreg, 
-                             FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
-  pval.begg = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.begg, 
-                            FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
-  stat.begg = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.begg, 
-                            FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
-  pval.thompson = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.mm, 
-                            FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
-  stat.thompson = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.mm, 
-                            FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\}))
-)
-
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-\hlcom{# IV OUTCOME META-ANALYSIS: -----------------------------------------------------------------------------------#}
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{# # -------- Uncomment to run analysis ----------}
-meta.id.vector.iv <- 
-  meta.info.extended$meta.id[\hlkwd{which}(meta.info.extended$outcome.flag == \hlstr{"IV"})]
-meta.analyses <- \hlkwd{list}()
-meta.analyses.reg <- \hlkwd{list}()
-meta.analyses.copas <- \hlkwd{list}()
-meta.analyses.trimfill <- \hlkwd{list}()
-meta.tests.linreg <- \hlkwd{list}()
-meta.tests.begg <- \hlkwd{list}()
-meta.tests.mm <- \hlkwd{list}()
-meta.tests.excess <- \hlkwd{list}()
-counter <- 0
-\hlkwd{for}(u in meta.id.vector.iv)\{
-	counter <- counter + 1
-	meta.analyses[[counter]] <- \hlkwd{metagen.iv}(data = data.ext2[data.ext2$meta.id == u,])
-	\hlkwd{print}(\hlkwd{c}(u, counter))
-
-	meta.analyses.reg[[counter]] <- \hlkwd{limitmeta}(meta.analyses[[counter]])
-	meta.analyses.trimfill[[counter]] <- \hlkwd{trimfill}(meta.analyses[[counter]])
-	meta.analyses.copas[[counter]] <- \hlkwd{auto.copas}(meta.analyses[[counter]], 
-	                                             sig.level = 0.1)
-
-	meta.tests.excess[[counter]] <- 
-	  \hlkwd{tes.fct2}(data = data.ext2[data.ext2$meta.id == u,])
-	meta.tests.linreg[[counter]] <- \hlkwd{metabias}(meta.analyses[[counter]], 
-	                               method.bias = \hlstr{"linreg"}, k.min = 2)
-	meta.tests.begg[[counter]] <- \hlkwd{metabias}(meta.analyses[[counter]], 
-	                               method.bias = \hlstr{"rank"}, k.min = 2)
-	meta.tests.mm[[counter]] <- \hlkwd{metabias}(meta.analyses[[counter]], 
-	                               method.bias = \hlstr{"mm"}, k.min = 2)
-\}
-\hlcom{# iv.meta.list <- list(data.ext2, meta.id.vector.iv, meta.analyses,}
-\hlcom{# 											 meta.analyses.reg,}
-\hlcom{# 											 meta.analyses.copas,}
-\hlcom{# 											 meta.analyses.trimfill,}
-\hlcom{# 											 meta.tests.linreg,}
-\hlcom{# 											 meta.tests.begg,}
-\hlcom{# 											 meta.tests.mm,}
-\hlcom{# 											 meta.tests.excess)}
-\hlcom{# save(iv.meta.list, file =  file.path(PATH_RESULTS, "meta_complete_list_iv.RData"))}
-\hlcom{# #--------------------------------------------------------------------------------------------------------------------#}
-\hlcom{# }
-\hlcom{# #Load analysis data:}
-\hlcom{# meta.id.vector.iv <- iv.meta.list[[2]]}
-\hlcom{# meta.analyses <- iv.meta.list[[3]]}
-\hlcom{# meta.analyses.reg <- iv.meta.list[[4]]}
-\hlcom{# meta.analyses.copas <- iv.meta.list[[5]]}
-\hlcom{# meta.analyses.trimfill <- iv.meta.list[[6]]}
-\hlcom{# meta.tests.linreg <- iv.meta.list[[7]]}
-\hlcom{# meta.tests.begg <- iv.meta.list[[8]]}
-\hlcom{# meta.tests.mm <- iv.meta.list[[9]]}
-\hlcom{# meta.tests.excess <- iv.meta.list[[10]]}
-
-\hlcom{#Extract from lists:}
-iv.results <- \hlkwd{data.frame}(
-  meta.id = meta.id.vector.iv,
-  meta.es.measure = \hlkwd{rep}(times = \hlkwd{length}(meta.id.vector.iv), \hlstr{"\hlkwd{unknown.effect}(IV)"}),
-
-  n.sig.single2 = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{\hlkwd{length}(\hlkwd{which}(meta.analysis$pval < 0.05))\})),
-\hlcom{  #Meta-Analysis}
-  est.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.fixed\})),
-  est.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.random\})),
-
-  zval.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$zval.fixed\})),
-  zval.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$zval.random\})),
-
-  pval.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.fixed\})),
-  pval.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.random\})),
-
-  se.est.fixef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.fixed\})),
-  se.est.ranef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.random\})),
-
-  Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$Q\})),
-  pval.Q = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$pval.Q\})),
-  tau = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$tau\})),
-  k = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$k\})),
-
-\hlcom{  #Adjustment:}
-  method.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$method.adjust\})),
-  est.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$TE.adjust\})),
-  se.est.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$seTE.adjust\})),
-  zval.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$zval.adjust\})),
-  pval.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
-  alpha.r = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
-  beta.r = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$pval.adjust\})),
-  Q.small = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$Q.small\})),
-  Q.resid = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$Q.resid\})),
-  G.squared = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$G.squared\})),
-
-  est.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
-                           FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[1]\})),
-  se.est.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
-                           FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[2]\})),
-  missing.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
-                           FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[3]\})),
-
-\hlcom{  #Tests:}
-  pval.d.tes.org = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                             FUN = \hlkwd{function}(object)\{object[3]\})),
-  pval.d.tes = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                             FUN = \hlkwd{function}(object)\{object[4]\})),
-  stat.d.tes = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                             FUN = \hlkwd{function}(object)\{object[2]\})),
-  excess.d = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                             FUN = \hlkwd{function}(object)\{object[5]\})) - 
-    \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.excess, 
-                  FUN = \hlkwd{function}(object)\{object[6]\})),
-  pval.egger = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.linreg, 
-                             FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
-  stat.egger = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.linreg, 
-                             FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
-  pval.begg = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.begg, 
-                             FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
-  stat.begg = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.begg, 
-                             FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\})),
-  pval.thompson = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.mm, 
-                             FUN = \hlkwd{function}(meta.test)\{meta.test$p.value\})),
-  stat.thompson = \hlkwd{unlist}(\hlkwd{lapply}(meta.tests.mm, 
-                             FUN = \hlkwd{function}(meta.test)\{meta.test$statistic\}))
-)
-
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-\hlcom{# Z-SCORE BASED META-ANALYSES: --------------------------------------------------------------------------------------#}
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{# # -------- Uncomment to run analysis ----------}
-meta.id.vector.noiv <- 
-  meta.info.extended$meta.id[-\hlkwd{which}(meta.info.extended$outcome.flag == \hlstr{"IV"})]
-meta.id.vector.smd <- 
-  meta.info.extended$meta.id[\hlkwd{which}(meta.info.extended$outcome.measure.merged == \hlstr{"SMD"})]
-meta.id.vector.z <- \hlkwd{union}(meta.id.vector.smd, meta.id.vector.noiv)
-meta.id.vector.z.c <- meta.id.vector.z[-\hlkwd{c}(\hlkwd{which}(meta.id.vector.z == 104613),
-                                          \hlkwd{which}(meta.id.vector.z == 104616),
-                                          \hlkwd{which}(meta.id.vector.z == 153452),
-                                          \hlkwd{which}(meta.id.vector.z == 163246),
-                      \hlkwd{which}(meta.id.vector.z == 182958))] \hlcom{#Have zero total1..}
-tmp.z <- data.ext2 %>% \hlkwd{group_by}(meta.id) %>% \hlkwd{mutate}(n = \hlkwd{n}()) %>% \hlkwd{filter}(n > 9) %>%
-  \hlkwd{filter}(total1 + total2 > 3) %>% \hlkwd{filter}(total1 != 0 & total2 != 0)
-meta.analyses <- \hlkwd{list}()
-meta.analyses.reg <- \hlkwd{list}()
-meta.analyses.copas <- \hlkwd{list}()
-counter <- 0
-\hlkwd{for}(u in meta.id.vector.z.c)\{
-	counter <- counter + 1
-	\hlkwd{print}(\hlkwd{c}(u,counter))
-	meta.analyses[[counter]] <- \hlkwd{metacor}(cor = z, n = total1 + total2, 
-	                   studlab = study.name, tmp.z[tmp.z$meta.id == u,])
-	meta.analyses.reg[[counter]] <- \hlkwd{limitmeta}(meta.analyses[[counter]])
-	meta.analyses.copas[[counter]] <- \hlkwd{auto.copas}(meta.analyses[[counter]], 
-	                                             sig.level = 0.1)
-\}
-\hlcom{# zscore.meta.list <- list(tmp.z, meta.id.vector.z.c, meta.analyses, }
-\hlcom{#meta.analyses.reg, meta.analyses.copas)}
-\hlcom{# save(zscore.meta.list, file =  file.path(PATH_RESULTS, }
-\hlcom{#"meta_complete_list_zscore.RData"))}
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{#Load analysis data:}
-meta.id.vector.z.c <- zscore.meta.list[[2]]
-meta.analyses <- zscore.meta.list[[3]]
-meta.analyses.reg <- zscore.meta.list[[4]]
-meta.analyses.copas <- zscore.meta.list[[5]]
-
-\hlcom{#List extraction:}
-zscore.meta.analysis.estimates <- \hlkwd{cbind}(
-  meta.id = meta.id.vector.z.c,
-  est.z.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.fixed\})),
-  est.z.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.random\})),
-  se.est.z.fixef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.fixed\})),
-  se.est.z.ranef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                    FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.random\})),
-
-  est.z.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$TE.adjust\})),
-  se.est.z.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$seTE.adjust\})),
-
-  est.z.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
-                    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[1]\})),
-  se.est.z.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
-                    FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[2]\})))
-
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-\hlcom{# HEDGES G BASED META-ANALYSES: -------------------------------------------------------------------------------------#}
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{# # -------- Uncomment to run analysis ----------}
-meta.id.vector.d <- meta.id.vector.z[-\hlkwd{c}(\hlkwd{which}(meta.id.vector.z == 25407))]
-meta.analyses <- \hlkwd{list}()
-meta.analyses.reg <- \hlkwd{list}()
-meta.analyses.copas <- \hlkwd{list}()
-counter <- 0
-\hlkwd{for}(u in meta.id.vector.d)\{
-  counter <- counter + 1
-  \hlkwd{print}(\hlkwd{c}(u,counter))
-  meta.analyses[[counter]] <- \hlkwd{metagen.bincont2}(data.ext2[data.ext2$meta.id == u,])
-  meta.analyses.reg[[counter]] <- \hlkwd{limitmeta}(meta.analyses[[counter]])
-  meta.analyses.copas[[counter]] <- \hlkwd{auto.copas}(meta.analyses[[counter]], 
-                                               sig.level = 0.1)
-\}
-\hlcom{# cohensd.meta.list <- list(data.ext2, meta.id.vector.d, meta.analyses, }
-\hlcom{#meta.analyses.reg, meta.analyses.copas)}
-\hlcom{# save(cohensd.meta.list, file =  file.path(PATH_RESULTS, }
-\hlcom{#"meta_complete_list_cohensd.RData"))}
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{#Load analysis data:}
-meta.id.vector.d <- cohensd.meta.list[[2]]
-meta.analyses <- cohensd.meta.list[[3]]
-meta.analyses.reg <- cohensd.meta.list[[4]]
-meta.analyses.copas <- cohensd.meta.list[[5]]
-
-\hlcom{#List extraction:}
-cohensd.meta.analysis.estimates <- \hlkwd{cbind}(
-  meta.id = meta.id.vector.d,
-  est.d.fixef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.fixed\})),
-  est.d.ranef = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$TE.random\})),
-  se.est.d.fixef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.fixed\})),
-  se.est.d.ranef =  \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses, 
-                  FUN = \hlkwd{function}(meta.analysis)\{meta.analysis$seTE.random\})),
-
-  est.d.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$TE.adjust\})),
-  se.est.d.reg = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.reg, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust$seTE.adjust\})),
-
-  est.d.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[1]\})),
-  se.est.d.copas = \hlkwd{unlist}(\hlkwd{lapply}(meta.analyses.copas, 
-                  FUN = \hlkwd{function}(meta.adjust)\{meta.adjust[2]\})))
-
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-\hlcom{# BUILD FINAL DATASET OF RESULTS}
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-meta.tp5 <- \hlkwd{bind_rows}(bin.results, cont.results, iv.results)
-meta.tp1 <- \hlkwd{merge}(meta.info.extended, meta.tp5, 
-                  by = \hlkwd{c}(\hlstr{"meta.id"})) #Temporary versions
-meta.tp4 <- \hlkwd{merge}(by = \hlstr{"meta.id"}, x = meta.tp1, 
-                  y = zscore.meta.analysis.estimates, all.x = T)
-meta.f <- \hlkwd{merge}(by = \hlstr{"meta.id"}, x = meta.tp4, 
-                y = cohensd.meta.analysis.estimates, all.x = T)
-
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-\hlcom{# ROUND-UP: DETECT AND REPLACE MISSING VALUES}
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{#se.est.copas.na = 1 -> is missing}
-meta.f$se.est.copas.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$se.est.copas), 1, 0) 
-meta.f$se.est.z.copas.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$se.est.z.copas), 1, 0)
-meta.f$se.est.d.copas.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$se.est.d.copas), 1, 0)
-
-meta.f$se.est.reg.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$se.est.reg), 1, 0)
-meta.f$se.est.z.reg.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$se.est.z.reg), 1, 0)
-meta.f$se.est.d.reg.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$se.est.d.reg), 1, 0)
-
-meta.f$est.copas.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$est.copas), 1, 0)
-meta.f$est.z.copas.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$est.z.copas), 1, 0)
-meta.f$est.d.copas.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$est.d.copas), 1, 0)
-
-meta.f$est.reg.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$est.reg), 1, 0)
-meta.f$est.z.reg.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$est.z.reg), 1, 0)
-meta.f$est.d.reg.na <- \hlkwd{ifelse}(\hlkwd{is.na}(meta.f$est.d.reg), 1, 0)
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{#Inpute random effect estimate for missing copas:}
-copas.names <- \hlkwd{c}(\hlstr{"est.copas"}, \hlstr{"se.est.copas"}, \hlstr{"est.z.copas"}, \hlstr{"se.est.z.copas"}, 
-                 \hlstr{"est.d.copas"}, \hlstr{"se.est.d.copas"})
-ranef.names <- \hlkwd{c}(\hlstr{"est.ranef"}, \hlstr{"se.est.ranef"}, \hlstr{"est.z.ranef"}, \hlstr{"se.est.z.ranef"}, 
-                 \hlstr{"est.d.ranef"}, \hlstr{"se.est.d.ranef"})
-missing.names <- \hlkwd{paste}(copas.names, \hlstr{".missing"}, sep = \hlstr{""})
-missing <- \hlkwd{c}()
-
-\hlkwd{for}(u in 1:\hlkwd{length}(copas.names))\{
-  missing.count <- 0
-  \hlkwd{for}(k in 1:\hlkwd{dim}(meta.f)[1])\{
-    \hlkwd{if}(\hlkwd{is.na}(meta.f[k, copas.names[u]]))\{
-      missing.count <- missing.count + 1
-      meta.f[k, copas.names[u]] <- meta.f[k, ranef.names[u]]
-    \}
-  \}
-  missing[u] <- missing.count
-  meta.f[, missing.names[u]] <- missing.count
-\}
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{#Some useful variables:}
-meta.f <- meta.f %>% \hlkwd{rowwise}() %>% 
-  \hlkwd{mutate}(pval1.egger = \hlkwd{onesided.p}(stat = stat.egger, side = side, n = k, 
-                                  test.type = \hlstr{"reg"}),
-         pval1.thompson = \hlkwd{onesided.p}(stat = stat.thompson, side = side, n = k, 
-                                     test.type = \hlstr{"reg"}),
-         pval1.begg = \hlkwd{onesided.p}(stat = stat.begg, side = side, n = k, 
-                                 test.type = \hlstr{"rank"}),
-
-         pval1.harbord = \hlkwd{onesided.p}(stat = stat.harbord, side = side, n = k, 
-                                    test.type = \hlstr{"reg"}),
-         pval1.rucker = \hlkwd{onesided.p}(stat = stat.rucker, side = side, n = k, 
-                                   test.type = \hlstr{"reg"}),
-         pval1.rucker.linreg = \hlkwd{onesided.p}(stat = stat.rucker.linreg, side = side, n = k, 
-                                          test.type = \hlstr{"reg"}),
-         pval1.peter = \hlkwd{onesided.p}(stat = stat.peter, side = side, n = k, 
-                                  test.type = \hlstr{"reg"}),
-         pval1.schwarzer = \hlkwd{onesided.p}(stat = stat.schwarzer, side = side, n = k, 
-                                      test.type = \hlstr{"rank"}),
-         pval1.d.tes = pval.d.tes)
-
-\hlcom{#Summarise different tests for binary and continuous variables to one:}
-meta.f <- meta.f %>% \hlkwd{rowwise}() %>% 
-  \hlkwd{mutate}(I2  = \hlkwd{max}(0, (Q - k + 1)/Q),
-         var.ratio = (se.max^2)/(se.min^2),
-         pval.se = \hlkwd{case_when}(outcome.flag == \hlstr{"DICH"} ~ pval1.rucker.linreg, 
-                             TRUE ~ pval1.egger),
-         pval.se.het = \hlkwd{case_when}(outcome.flag == \hlstr{"DICH"} ~ pval1.rucker, 
-                                 TRUE ~ pval1.thompson))
-\hlcom{#significance of pb tests:}
-sig.level <- 0.1
-meta.f <- meta.f %>% \hlkwd{rowwise}() %>% 
-  \hlkwd{mutate}(egger.test = \hlkwd{ifelse}(pval1.egger < sig.level, 1, 0),
-         thompson.test = \hlkwd{ifelse}(pval1.thompson < sig.level, 1, 0),
-         begg.test = \hlkwd{ifelse}(pval1.begg < sig.level, 1, 0),
-
-         tes.d.test = \hlkwd{ifelse}(pval1.d.tes < sig.level, 1, 0),
-
-         schwarzer.test = \hlkwd{ifelse}(pval1.schwarzer < sig.level, 1, 0),
-         rucker.test = \hlkwd{ifelse}(pval1.rucker < sig.level, 1, 0),
-         rucker.test.linreg = \hlkwd{ifelse}(pval1.rucker.linreg < sig.level, 1, 0),
-         harbord.test = \hlkwd{ifelse}(pval1.harbord < sig.level, 1, 0),
-         peter.test = \hlkwd{ifelse}(pval1.peter < sig.level, 1, 0))
-
-\hlcom{#calculate test statistics:}
-meta.f <- meta.f %>% \hlkwd{mutate}(
-  z.fixef = (est.fixef/se.est.fixef)
-  z.ranef = (est.ranef/se.est.ranef),
-  z.reg =   (est.reg/se.est.reg),
-  z.copas = ((est.copas)/se.est.copas))
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{#Separate outcome.types:}
-meta.bin <- meta.f %>% \hlkwd{filter}(outcome.flag == \hlstr{"DICH"})
-meta.cont <- meta.f %>% \hlkwd{filter}(outcome.flag == \hlstr{"CONT"})
-meta.iv <- meta.f %>% \hlkwd{filter}(outcome.flag == \hlstr{"IV"})
-\hlcom{#--------------------------------------------------------------------------------------------------------------------#}
-
-\hlcom{#Save the result datasets:}
-\hlkwd{save}(meta.f, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta_analyses_summary_complete.RData"}))
-\hlkwd{save}(meta.bin, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta.bin.RData"}))
-\hlkwd{save}(meta.cont, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta.cont.RData"}))
-\hlkwd{save}(meta.iv, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta.iv.RData"}))
-\hlkwd{save}(meta.id.vector, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"meta_id_vector.RData"}))
-\hlkwd{save}(data.ext2, file =  \hlkwd{file.path}(PATH_RESULTS, \hlstr{"data_used_for_analysis.RData"})) #Save data used for analysis
-
-\hlcom{# x <- foreach(i = 1:length(meta.id.vector.bin)) %dopar% }
-\hlcom{#   # u <- meta.id.vector.bin[i]}
-\hlcom{#   # counter <- counter + 1}
-\hlcom{#   metabin(event.e = events1c, n.e = total1, event.c = events2c, n.c = total2,}
-\hlcom{#           studlab = study.name, sm = "RR",}
-\hlcom{#           method = "Inverse", data = data.ext2[data.ext2$meta.id == meta.id.vector.bin[i],])}
-\hlcom{# }
-\hlcom{# cl<-makeCluster(7)}
-\hlcom{# registerDoParallel(cl)}
-\hlcom{# }
-\hlcom{# foreach(i = 1:length(meta.id.vector.bin)) %dopar%}
-\hlcom{#   sqrt(i)}
-
-\hlcom{########################################################################################################}
-\hlcom{########################################################################################################}
-\hlcom{########################################################################################################}
-\hlcom{########################################################################################################}
-\hlcom{########################################################################################################}
-\hlcom{########################################################################################################}
-\hlcom{########################################################################################################}
-\hlcom{########################################################################################################}
-\end{alltt}
-\end{kframe}
-\end{knitrout}
+%<<'child-chapterA1', child='chapterA1.Rnw'>>=
+%@
 

### 2019-08-06 report/MSc_Report.tex
Grammar, anova tables, discussion

@@
 For instance, it is possible to follow studies and assess if they are getting published depending on their findings (\citet{Dwan2013}, \citet{publication.fate}, \citet{Lee.2008}).
-One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in social sciences: \citet{social.sciences.publication.bias}).
+One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in the social sciences: \citet{social.sciences.publication.bias}).
 Another way is to compare results in study registries with results published in journals (\eg \citet{pb.clinicalscience.2013}).
@@
 \begin{itemize}
-\item Publish new and trend-setting findings that lead to many citations, increasing the journal impact factor (JIF).
+\item Publish new and trend-setting positive findings that lead to many citations, increasing the journal impact factor (JIF).
+Statistically significant effects are oftentimes interpreted as confirming an effect.
 \item Publish large trials that are likely to set the standard for a given scientific question, again to increase the JIF.
@@
 
-This then leads to an asymmetry in published studies; small studies show larger effect sizes than larger studies do.
-A funnel plot(cite sb) allows visual inspection of small study effects by plotting the effects against their standard error.
+Publication bias thus leads to larger effects in studies with larger uncertainities, in order for them to be statistically significant.
+A funnel plot \citep{funnel.plot} allows visual inspection of small study effects by plotting the effects against their standard error.
 For illustration purposes, one meta-analysis with large funnel plot asymmetry and one with no asymmetry is shown in Figure \ref{small.study.effect.examples }.
@@
 gives the marginal distribution of $\mathbf{y}{_{j}}$ depending on $U{_i}$ and $\epsilon{_{j}}$.
-The random effects $U{_i} \sim N(0, \mathbf{G})$ and the residual error term $\epsilon{_{j}} \sim N(0, \tau^{2})$ are independent from eahc other.
+The random effects $U{_i} \sim N(0, \mathbf{G})$ and the residual error term $\epsilon{_{j}} \sim N(0, \tau^{2})$ are independent from each other.
 The expectation $\mathbb{E}(\mathbf{y}_{j})$ is still $x_j \beta$, but now, the covariance between the observations within a group $i$, $\mathbf{y}_i$, is modeled as
@@
 
-whith $m$ being the number of groups and $\hat{\mathbf{V}}_i$ being the estimated covariance, obtained by maximizing the log likelihood of the normal distribution, as $\mathbf{y}_i$ is distributed as
+with $m$ being the number of groups and $\hat{\mathbf{V}}_i$ being the estimated covariance, obtained by maximizing the log likelihood of the normal distribution, as $\mathbf{y}_i$ is distributed as
 
@@
 
-Weights can be introduced by replacing $\mathbf{I}_{n_i}$ in \eqref{eq:random.intercepts.covariance} with the previously introduced weight matrix $\mathbf{W}_i$ .Hypothesis tests for $\beta = \beta_\textrm{H0}$ can be made using the wald method.
+Weights can be introduced by replacing $\mathbf{I}_{n_i}$ in \eqref{eq:random.intercepts.covariance} with the previously introduced weight matrix $\mathbf{W}_i$ .Hypothesis tests for $\beta = \beta_\textrm{H0}$ can be made using the Wald method.
 
@@
 \theta_i &= \arcsin{e_t/n_t} - \arcsin{e_c/n_c} \nonumber &
-\se_i^2 &= 1/4n_t + /4n_c \nonumber
+\se_i^2 &= 1/4n_t + 1/4n_c \nonumber
 \end{align}
@@
 
-\section{Small Study Effect and Publication Bias Adjustment}
+\section{Publication Bias Adjustment}
 There are different approaches to correct for small study effects and publication bias.
@@
 \subsection{Adjustment by Regression} \label{sec:regression.adjustment}
-\citet{limitmeta} use a random effects model %together with shrinkage procedure 
-to obtain an unbiased estimate. Similarly to 
-%what has been seen in Copas selection model, we let $y_i$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_i}$ as in \eqref{limitmeta.regression}.
-regression based tests for small study effects, we have
+In \citet{limitmeta.2} and \citet{limitmeta}, a random effects model is proposed to obtain unbiased treatment effect estimates. Similarly to regression based tests for small study effects, we have
 
@@
 
-Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior with respect to coverage (and mean squared error).
+Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior to the former, because it showed a smaller mean-squared error in simulation studies \citet{limitmeta.2}.
+Also, this simulation study emphasizes that adjustment is more reliable when effects of publication bias are strong within a meta-analysis.
+When no publication bias affects the meta-analysis, and event rates are low, the method will provide biased estimates and the mean squared error is large.
+Coverage of the confidence is always larger or equal to meta-analysis.
+It outperforms or is equal to classical meta-analysis estimates if there is publication bias, especially if event rates in the control group are small.
 
@@
 Selection models are in general not recommended for inference (\eg \citet{selection.assessment}).
-\citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes. \\
+\citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes.
+However, in the simulations, the method was outperformed by the regression adjustment method when publication bias was present.
+Especially when event rates in the control group were small and publication bias was strong, bias, mean squared error and coverage was substantially worse.\\
 A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \eqref{eq:copas.small.study} is applied.
@@
 Initially, the analysis is restricted to results with \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}.
-If \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR}, \texttt{RR}, \texttt{SMD}, \texttt{MD}, \texttt{Hazard Ratio} and \texttt{Rate Ratio} are used.
+If \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR} / \texttt{RR} / \texttt{SMD} / \texttt{MD} / \texttt{Hazard Ratio} / \texttt{Rate Ratio} are used.
 \citet{Ioannidis2007} outlined criteria for application of small study effect tests:
@@
 The results of this reduction of the dataset are shown in the flow-chart in Figure \ref{Inclusion.criteria}.
-Only the data that had accesible all results data available was used for adjustment.
-Thus, all meta-analyses with \texttt{outcome.flag} == \texttt{IV} and \texttt{outcome.measure.merged} not equal to \texttt{SMD} are ommitted in a second step of the analysis (Analysis dataset (1) and (2) in Figure \ref{Inclusion.criteria}).
+Only the data that had accessible all results data available was used for adjustment.
+Thus, all meta-analyses with \texttt{outcome.flag} == \texttt{IV} and \texttt{outcome.measure.merged} not equal to \texttt{SMD} are omitted in a second step of the analysis (Analysis dataset (1) and (2) in Figure \ref{Inclusion.criteria}).
 
@@
 In some more cases, meta-analyses were excluded because their results seemed to be erroneous (1) or because participant numbers were missing (5), necessary to compute the variance of Fisher's z transformed correlation coefficient.
-The latter meta-analyses (all \texttt{outcome.flag} = \texttt{IV}) were only ommitted when doing the adjustment based on the $z$-scores, but kept when adjusting based on std.
+The latter meta-analyses (all \texttt{outcome.flag} = \texttt{IV}) were only omitted when doing the adjustment based on the $z$-scores, but kept when adjusting based on std.
 mean differences.
@@
 \subsubsection{The Analysis Dataset}
-The dataset that was ultimately tested and adjusted for publication bias comprises 1 meta-analyses and 22937 results.
+The dataset that was ultimately tested and adjusted for publication bias comprises 1388 meta-analyses and 22,937 results.
 The mean number of participants in the treatment group is 253.5 vs 256.7 in the unrestricted dataset and the mean total number of participants 589.3 vs 623.2.
-The mean publication year is 2000.4408025 vs 2000.9711014 in the unrestricted dataset.
-\\
-From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}), there are 36 with \\ \texttt{outcome.measure.merged} = ``Risk Ratio'', 26 ``Std.
-Mean Difference'',  25 ``Hazard Ratio'' and 15 ``Odds Ratio'' (and 25 additional, different outcome measures).
+The mean publication year is 2000 vs 2001 in the unrestricted dataset.
+\\
+From the meta-analyses with incomplete data (\texttt{outcome.flag} == \texttt{IV}), there are 36 with \\ \texttt{outcome.measure.merged} = \texttt{RR}, 26 \texttt{SMD},  25 \texttt{Hazard Ratio}, 15 \texttt{OR}, 11 \texttt{MD} and 8 \texttt{Rate Ratio}.
 
@@
 The last step is optional, and the Cochrane groups do also meta-analysis without taking into account subgroups.
-Subgroups are often specificaions of treatment, \eg the form of the medication or the protocoll.
+Subgroups are often specifications of treatment, \eg the form of the medication or the protocol.
 Thus, using the subgroups should increase the within-study homogeneity.
 However, the Cochrane Organisation disencourages meta-analyses based on subgroups only, because subgroups are often set up after the collection of the data analysis.
-Since the main interest of this study is not to precisely assess the efficacy of treatments, but the interest is merely on systematic differences between single studies investigating the same scientific question and not in the effect per se, it has been decided that the increase in precision is worthwile the loss of a number of studies.
+Since the main interest of this study is not to precisely assess the efficacy of treatments, but the interest is merely on systematic differences between single studies investigating the same scientific question and not in the effect per se, it has been decided that the increase in precision is worthwhile the loss of a number of studies.
 While it is possible that the use of subgroups introduces bias in the meta-analysis, it is also possible that ignoring subgroups will do (which is one of the reasons why subgroups are analyses as well).
@@
 For applying publication bias tests and adjustment methods, the analysis was applied such that the effects used are similar or identical to the effects on which journal editors decided upon publication bias.
-For \texttt{outcome.flag} = \texttt{DICH}, log risk ratios were used as treatment effect estimates in the meta-analysis, for \texttt{outcome.flag} = \texttt{CONT}, mean difference or standardised mean difference, depending on \texttt{outcome.measure.merged}.
+For \texttt{outcome.flag} = \texttt{DICH}, log risk ratios were used as treatment effect estimates in the meta-analysis, for \texttt{outcome.flag} = \texttt{CONT}, mean difference or standardized mean difference, depending on \texttt{outcome.measure.merged}.
 For \texttt{outcome.flag} = \texttt{IV}, the \texttt{effect} and \texttt{se} as provided in the dataset was passed to \texttt{meta::metagen}.
-\\
+Since the intuition behind small study effect tests is that effects with larger standard errors have to be larger to reach significance, the publication bias tests and adjustments are most meaningful if the effects are used in their original scale.
+Transformation will change the relative size of uncertainty estimates and effects.\\
 To be able to compare the effects of adjustment among meta-analyses, the effect sizes were transformed on a common scale, as described in section \ref{sec:transformation.effectsizes}.
@@
 \\
-In the case of the one-sided test procedure (small study effect and excess significance tests), the effect side in which bias was expected had to be prespecified.
+In the case of the one-sided test procedure (small study effect and excess significance tests), the effect side in which bias was expected had to be pre-specified.
 This was solved by comparing the number of significant findings on each side (original effect scale, i.e.
@@
 If there is still no non-significant small study effect, the result was \texttt{NA}.
-All compuations were performed in the \texttt{R} computing environment \citep{R.base}.
+All computations were performed in the \texttt{R} computing environment \citep{R.base}.
 The \texttt{R} packages \texttt{meta} \citep{meta.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments.
@@
 The pattern is similar in Figure \ref{effect.samplesize.separated}, where the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std.
-Mean Difference'' are used (the most common measurs in the dataset).
-Here, the effect sizes are scaled (mean subtraction and divison through standard error) with respect to all other effects of the same measure.
+Mean Difference'' are used (the most common measures in the dataset).
+Here, the effect sizes are scaled (mean subtraction and division through standard error) with respect to all other effects of the same measure.
 
@@
 The tests are applied on the original effect size measures, since the journal editors and the researchers also base their decisions on them.
-Different tests are applied depending on the outcome being binary or continuous.\\
-Multiple tests are applied on the same data to compare their results.
-A histogram of $p$-values for each test and all meta-analyses will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.
-Skewedness indicates evidence for publication bias.\\
+Different tests are applied depending on the outcome being binary or continuous or if the data is only partially available.\\
+Multiple tests are applied in order to compare their results.
+A histogram of $p$-values for each test will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.\\
 The abbreviations in Figure \ref{fig:test}  are shortly explained with references to chapter \ref{ch:methods}: \\
@@
 The testing method is indicated in the header, bin width is equal to 0.1.
-The proportion of meta-analyses with signifiant publication bias based on the threshold of 0.1 is displayed inside the figures.}
+The proportion of meta-analyses with significant publication bias based on the threshold of 0.1 is displayed inside the figures.}
 \label{fig:test}
@@
 %Agreement table -> Chunck 1
-The histograms in Figure \ref{fig:test} show that the tests are not alway in agreement if publication bias is present in the data.
-The $p$-values of excess significance and Schwarzer's test and the $p$-values for \texttt{IV} outcomes are rather uniformly distributed, or even skewed to the right.
+The histograms in Figure \ref{fig:test} show that the tests do not coherently find evidence for publication bias in the dataset.
+The $p$-values of excess significance and Schwarzer's test are rather uniformly distributed.
 Notably, excess significance test, Schwarzer's test and rank tests have been shown to lack power.
@@
 In Figure \ref{fig:test}, the meta-analyses with an estimated $I^2$ of zero are depicted, because some methods are known to only be suitable when no heterogeneity is present (excess significance test and also Egger's test).
-Others are specially constructed to adjust for between study heterogeneity (Thompson and Sharp's test and R\"ucker's test).
-In continuous outcomes, when Thompson and Sharp's test is applied, the evidence for publication bias decreases, as can be seen in the smaller proportion of blue on the left corner in Figure \ref{fig:test}.
-However, this is also due to application to meta-analyses with $I^2$ equal zero, in which case the method is known to lack power.
+Other tests are specially constructed to adjust for between study heterogeneity (Thompson and Sharp's test and R\"ucker's test).
+It can be seen that these tests find a smaller proportion of significant results in Figure \ref{fig:test}.
+However, this is also due to application to meta-analyses with no between-study heterogeneity, where the methods lack statistical power.
 Similarly, the evidence decreases somewhat when R\"ucker's test is extended by Thompson and Sharp's method to account for heterogeneity.
-The moderate decrease indicates however that the previous restriction to meta-analyses with $I^2 < 0.5$ is sufficient to remove meta-analyses with large heterogeneity and that the test results are not heavily influenced by unaccounted between study heterogeneity.
-\\
+The moderate decrease indicates however that the previous restriction to meta-analyses with $I^2 < 0.5$ is sufficient to remove meta-analyses with large heterogeneity and that the test results are not heavily influenced by unaccounted between-study heterogeneity.\\
 The $p$-values of tests can be summarized by computing their harmonic mean.
@@
 After applying the Bonferroni correction for multiple testing, this shrinks to 12.3\% for binary and 14.4\% for continuous and \texttt{IV} outcomes.
-To compare significant findings for small study effect tests and excess significance tests, Harbord's or Egger's test results are compared with excess significane tests.
+To compare significant findings for small study effect tests and excess significance tests, Harbord's or Egger's test results are compared with excess significance tests.
 24.1\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 28.4\% for continuous and \texttt{IV} outcomes.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Aug  5 16:02:46 2019
+% Tue Aug  6 17:32:17 2019
 \begin{table}[ht]
@@
 Contrary to naive expectation, we see cases with large adjustment, but no evidence for small study effects.
-This is because the linear regression parameter estimates are large, but estimated with high uncertainity, such that there will be few evidence for small study effects (publication bias), but nonetheless, the adjustment will be large.
-The authors that developped the methods also recommend to use the methods in cases where there is clear evidence for publication bias.
+This is because the linear regression parameter estimates are large, but estimated with high uncertainty, such that there will be few evidence for small study effects (publication bias), but nonetheless, the adjustment will be large.
+The authors that developed the methods also recommend to use the methods in cases where there is clear evidence for publication bias.
 The color legend in Figure \ref{fig:adjustment.reg} thus gives a sense of confidence that there is in the credibility of the adjustment.
 \\
-Additionally, some meta-analyses with positively adjusted, larger overall treatment effects after adjustment (left side of the histogram) have at the same time evidence for publication bias.
-This is no wrong result, although the $p$-value of the test is one-sided, \ie only allowing for publication bias for large effects (small studies with large effects).
-But the effects and their variances have been transformed, and it is possible that the shape of the funnel plot changes upon transformation; Figure \ref{fig:funnel.plot.change} shows this for illustratory purposes.
+Additionally, some meta-analyses with positively adjusted, larger overall treatment effects after adjustment (left side of the histogram) have also evidence for publication bias (remember that publication bias was defined as the tendency of small studies to show \textit{larger} results).
+This is not a wrong result, because the effects and their variances have been transformed, and it is possible that the shape of the funnel plot changes upon transformation; Figure \ref{fig:funnel.plot.change} shows this for illustrative purposes.
 From the left to the right, the funnel plot is shown for mean differences (the original measure), standardized mean differences and Fisher's $z$ scores.
@@
 In contrast, the variance of the correlation is directly tied to the sample size, which makes it a suitable proxy for study size (variance of the mean difference is in contrast strongly influenced by the standard deviations).
-Thus, cases where the direction of adjustment changes upon transformation are not very rare.
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Aug  5 16:02:59 2019
+% Tue Aug  6 17:32:30 2019
 \begin{table}[ht]
@@
 \begingroup\tiny
-\begin{tabular}{lcccrrrrrrrr}
-  \hline
-meta.id & id & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
-  \hline
-9957 & CD000370 & 8 & 2 & 0.66 & 0.66 & 0.66 & 0.82 & 1.59 & 1.59 & 1.40 & 0.28 \\ 
-  22324 & CD001183 & 7 & 0 & -0.48 & -0.48 & -0.48 & -0.21 & -1.10 & -1.12 & -0.50 & -0.11 \\ 
-  49559 & CD002307 & 2 & 1 & -0.10 & -0.08 & -0.10 & 0.03 & -0.47 & -0.42 & -0.41 & -3.00 \\ 
-  197675 & CD008625 & 2 & 2 & -0.60 & -0.60 & -0.60 & -0.39 & -1.72 & -2.02 & -1.01 & -0.69 \\ 
-  222767 & CD010060 & 1 & 0 & 0.31 & 0.32 & 0.31 & 0.23 & 0.50 & 0.52 & 0.20 & -0.49 \\ 
+\begin{tabular}{cccrrrrrrrr}
+  \hline
+id & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z reg. & smd fixed & smd random & smd Copas & smd reg. \\ 
+  \hline
+CD000370 & 8 & 2 & 0.66 & 0.66 & 0.66 & 0.82 & 1.59 & 1.59 & 1.40 & 0.28 \\ 
+  CD001183 & 7 & 0 & -0.48 & -0.48 & -0.48 & -0.21 & -1.10 & -1.12 & -0.50 & -0.11 \\ 
+  CD002307 & 2 & 1 & -0.10 & -0.08 & -0.10 & 0.03 & -0.47 & -0.42 & -0.41 & -3.00 \\ 
+  CD008625 & 2 & 2 & -0.60 & -0.60 & -0.60 & -0.39 & -1.72 & -2.02 & -1.01 & -0.69 \\ 
+  CD010060 & 1 & 0 & 0.31 & 0.32 & 0.31 & 0.23 & 0.50 & 0.52 & 0.20 & -0.49 \\ 
    \hline
@@
 A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
-Note that most 121 \texttt{IV} outcome data is not included when using $z$-score and std.
-mean difference.
+Note that only 26 out of 121 \texttt{IV} outcome data is included when using $z$-score and std.
+mean differences, since not all effects could be transformed.
 
@@
 There, less of an effect of adjustment on the evidence can be seen.
-\\
-Thus, the decrease in evidence is larger when using adjustment with regression, which can be expected as the uncertainity of the additional parameter from the linear regression fit to estimate publication bias is included in the uncertainity of the estimate.
-In contrast, as the Copas selection model algorithm does a sensitivity analysis, the uncertainity of additional model parameters does not affect the estimate as they are not estimated but treated as fixed (see section \ref{sec:procedure} and section \ref{sec:copas}).\\
-Large adjustment in effect sizes and test statistics is not necessarily accompained by evidence for publication bias (color of the dots) in regression adjustment, as already discussed.
-The dark dots can be found more often far away from the diagonal.
+The adjustment is more likely to be more reliable than the unadjusted estimate when publication bias is strong.
+The dots with darker color are thus more likely to provide less biased estimates.\\
+The decrease in evidence is larger when using adjustment with regression, which can be expected as the uncertainty of the additional parameter from the linear regression fit to estimate publication bias is included in the uncertainty of the estimate.
+In contrast, as the Copas selection model algorithm does a sensitivity analysis, the uncertainty of additional model parameters does not affect the estimate as they are not estimated but treated as fixed (see section \ref{sec:procedure} and section \ref{sec:copas}).\\
+Large adjustment in effect sizes and test statistics is not necessarily accompanied by evidence for publication bias (color of the dots) in regression adjustment, as already discussed.
+But the dark dots can be found more often far away from the diagonal.
 Some cases which have more evidence for treatment efficacy after adjustment have evidence for publication bias, which is not expected, since the publication bias tests applied are one-sided and only test for bias towards large effects.
@@
 \begin{itemize}
-\item z-value of regression adjustment 10.5 vs fixed effects z-value 5.7: When the funnnel plot of these meta-analyses are investigated, it becomes clear that there is no reason to assume publication bias since the smaller studies are near to risk ratios equal to one, and larger studies show larger ratios.
+\item z-value of regression adjustment 10.5 vs fixed effects z-value 5.7: When the funnel plot of these meta-analyses are investigated, it becomes clear that there is no reason to assume publication bias since the smaller studies are near to risk ratios equal to one, and larger studies show larger ratios.
 Publication bias tests disagree in their findings (R\"ucker's and Harbord's tests: 0.058 and 0.05, and Peters and Schwarzer's test: 0.467 and 0.79).
-\item z-value of regression adjustment 9.24 vs fixed effects z-value 2.51: Asymmetry of the funnel plot could be confirmed when analysing it with mean differences.
+\item z-value of regression adjustment 9.24 vs fixed effects z-value 2.51: Asymmetry of the funnel plot could be confirmed when analyzing it with mean differences.
 The change to a larger treatment effect is rather due to large between study heterogeneity and the specific routine of the regression adjustment.
@@
 The Copas selection model also allows to compute the number of missing studies, given that the model's assumptions are correct.
-It finds that 2,618 are missing, which corresponds to 11.4\% from all 22,916 analysed studies.
+It finds that 0 are missing, which corresponds to 0\% from all 22,916 analysed studies.
 Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
-Note that random effects meta-analysis substitutes have been excluded (828 out of 1,388.
+Note that random effects meta-analysis substitutes have been excluded (0 out of 1,388.
 
@@
 In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
-The discrepancy between mean and median may indicate that the estimate of 11.4\% missing studies depends somewhat on these extreme cases.
-As can be written of from Table \ref{copas.missing}, 5\%, \ie 28 meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for 1,060, more than 30\% of missing studies.
+The discrepancy between mean and median may indicate that the estimate of 0\% missing studies depends somewhat on these extreme cases.
+As can be written of from Table \ref{copas.missing}, 5\%, \ie 0 meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for 0, more than 30\% of missing studies.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Aug  5 16:03:01 2019
+% Tue Aug  6 17:32:32 2019
 \begin{table}[ht]
@@
 \section{Publication Bias over Time}
-To test if publication bias in meta-analses has decreased over time and newer meta-analyses have less bias, a generalized linear model has been set up. \\
+To test if publication bias in meta-analyses has decreased over time and newer meta-analyses have less bias, a generalized linear model has been set up. \\
 The dependent variable is the standardized mean differences (therefore, from \texttt{outcome.flag} = \texttt{IV}, only the std.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Aug  5 16:03:10 2019
+% Tue Aug  6 17:32:40 2019
 \begin{table}[ht]
@@
 \begingroup\scriptsize
-\begin{tabular}{rrrrrrlrr}
+\begin{tabular}{rrrrrrlrl}
   \hline
@@
   \hline
-null.fit &   1 & 4.00 & 18768.23 & 18800.12 & -9380.11 &  &  &  \\ 
-  small.study.fit &   2 & 5.00 & 18230.52 & 18270.39 & -9110.26 & 1 vs 2 & 539.71 & 0.00 \\ 
+null.fit &  1 & 4.0 & 18768.2 & 18800.1 & -9380.1 &  &  &  \\ 
+  small.study.fit &  2 & 5.0 & 18230.5 & 18270.4 & -9110.3 & 1 vs 2 & 539.7 & $<$0.00001 \\ 
    \hline
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Aug  5 16:03:10 2019
+% Tue Aug  6 17:32:41 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Aug  5 16:03:12 2019
+% Tue Aug  6 17:32:43 2019
 \begin{table}[ht]
@@
   \hline
-small.study.fit &   1 & 5.00 & 18230.52 & 18270.39 & -9110.26 &  &  &  \\ 
-  small.study.rs.fit &   2 & 7.00 & 18233.07 & 18288.88 & -9109.53 & 1 vs 2 & 1.46 & 0.48 \\ 
+small.study.fit &  1 & 5.0 & 18230.5 & 18270.4 & -9110.3 &  &  &  \\ 
+  small.study.rs.fit &  2 & 7.0 & 18233.1 & 18288.9 & -9109.5 & 1 vs 2 & 1.5 & 0.5 \\ 
    \hline
@@
 To test if publication bias varies over time, we include the year of the publication of the review as an additional explanatory variable.
-Ulitmately, it is of interest if there is an interaction between the small study effect (publication bias) and time, i.e.
+Ultimately, it is of interest if there is an interaction between the small study effect (publication bias) and time, i.e.
 if the slope varies depending on the year.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Aug  5 16:03:14 2019
+% Tue Aug  6 17:32:45 2019
 \begin{table}[ht]
@@
   \hline
-small.study.fit &   1 & 5.00 & 18230.52 & 18270.39 & -9110.26 &  &  &  \\ 
-  year.fit &   2 & 6.00 & 18231.61 & 18279.46 & -9109.81 & 1 vs 2 & 0.91 & 0.34 \\ 
-  year.int.fit &   3 & 7.00 & 18233.59 & 18289.40 & -9109.79 & 2 vs 3 & 0.03 & 0.87 \\ 
+small.study.fit &  1 & 5.0 & 18230.5 & 18270.4 & -9110.3 &  &  &  \\ 
+  review.year.fit &  2 & 6.0 & 18231.6 & 18279.5 & -9109.8 & 1 vs 2 & 0.9 & 0.34 \\ 
+  review.year.int.fit &  3 & 7.0 & 18233.6 & 18289.4 & -9109.8 & 2 vs 3 & 0.0 & 0.87 \\ 
    \hline
@@
 \caption{Anova table for three generalized linear model fits.
-'small.study.fit' denotes the model with the standard error as explanatory variable, 'year.fit' the model with standard error and the centered (- 2013) review year as explanatory variable, and 'year.int.fit' the model with interaction between the two.}
+'small.study.fit' denotes the model with the standard error as explanatory variable, 'review.year.fit' the model with standard error and the centered (- 2013) review year as explanatory variable, and 'review.year.int.fit' the model with interaction between the two.}
 \label{anova.lme}
@@
 
-Because neither AIC, BIC ot the F-test do show any improvement of model fit, it does not seem as if publication bias has substantially decreased or increased over the years.
+Because neither AIC, BIC or the F-test do show any improvement of model fit, it does not seem as if publication bias has substantially decreased or increased over the years.
 The review publication year is however not directly tied to the publication year of the studies that are affected by publication bias.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Aug  5 16:03:17 2019
+% Tue Aug  6 17:32:48 2019
 \begin{table}[ht]
@@
   \hline
-small.study.fit &   1 & 5.00 & 18115.23 & 18155.05 & -9052.62 &  &  &  \\ 
-  year.fit &   2 & 6.00 & 18095.04 & 18142.83 & -9041.52 & 1 vs 2 & 22.19 & 0.00 \\ 
-  year.int.fit &   3 & 7.00 & 18096.90 & 18152.65 & -9041.45 & 2 vs 3 & 0.14 & 0.71 \\ 
+small.study.fit &  1 & 5.0 & 18115.2 & 18155.1 & -9052.6 &  &  &  \\ 
+  study.year.fit &  2 & 6.0 & 18095.0 & 18142.8 & -9041.5 & 1 vs 2 & 22.2 & 0.000002 \\ 
+  study.year.int.fit &  3 & 7.0 & 18096.9 & 18152.7 & -9041.5 & 2 vs 3 & 0.1 & 0.705909 \\ 
    \hline
@@
 \caption{Anova table for three generalized linear model fits.
-'Small study fit' denots the model with the standard error as explanatory variable, 'year.fit' the model with standard error and the centered (- 2000) study year as explanatory variable, and 'year.int.fit' the model with interaction between the two.}
+'Small study fit' denotes the model with the standard error as explanatory variable, 'study.year.fit' the model with standard error and the centered (- 2000) study year as explanatory variable, and 'study.year.int.fit' the model with interaction between the two.}
 \label{anova.lme}
@@
 The analysis of model fit indicates that there is an improvement when using the study year as a covariate, but only as an additive effect.
+The coefficients of the model are given in Table \ref{coefficients.study.year.fit}.
 AIC and BIC are smaller and the $p$-value of the F-test is very small.
-However, not the size of the effect, but the slope of the linear regression fit would have to be decreased to ultimatively conclude a decrease of publication bias over the years.
+However, not the size of the effect, but the slope of the linear regression fit would have to be decreased to ultimately conclude a decrease of publication bias over the years.
+
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Tue Aug  6 17:32:49 2019
+\begin{table}[ht]
+\centering
+\begingroup\scriptsize
+\begin{tabular}{lccc}
+  \hline
+ & estimate & 2.5\%CL & 97.5\%CL \\ 
+  \hline
+(Intercept) & 0.1791 & 0.1608 & 0.1974 \\ 
+  se.smd.pool & 0.3692 & 0.3371 & 0.4013 \\ 
+  study.year.center & -0.0012 & -0.0017 & -0.0007 \\ 
+   \hline
+\end{tabular}
+\endgroup
+\caption{Coefficients and 95\% confidence limits of the generalized linear model. 'se.smd.pool' denotes the standard error of the std. mean difference.} 
+\label{coefficients.study.year.fit}
+\end{table}
 
@@
 When clear methodological drawbacks are found in the analysis, the reader is referred to chapter \ref{ch:methods} for comments on the disadvantages.
-The amount of studies analysing publication bias makes it not possible to discuss any of them, and thus we only some interesting and/or representative examples are shown.
+The amount of studies analyzing publication bias makes it not possible to discuss any of them, and thus we only some interesting and/or representative examples are shown.
 
@@
 Five (13\%) meta-analyses from Cochrane and 13 (38\%) from the journals had significant two sided small study effect test results ($p$-value < 0.1).
-Also, they found that test-statistics were more often negative, which correspondend in their setup to larger effects in small studies.
+Also, they found that test-statistics were more often negative, which corresponded in their setup to larger effects in small studies.
 (63.2 among Cochrane meta-analyses and 70.3 for journal meta-analyses).
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Aug  5 16:03:57 2019
+% Tue Aug  6 17:33:26 2019
 \begin{table}[ht]
@@
 Reviews of the World Health Organization (WHO) Reproductive Health Library (RHL), issue 9, were analysed with the trim-and-fill method.
-The RHL reproduces and expands reviews from the Cochrane Library with implications for developping countries.
+The RHL reproduces and expands reviews from the Cochrane Library with implications for developing countries.
 21 of 105 reviews contained more than ten studies and were used.
@@
 \subsection{\citet{kicinsky}}
-The author uses a bayesian hierarchical selection model, but does not analyse treatment effects, but the parameters of the weight function of the selection model, which is estimated with a bayesian approach and MCMC sampling.
+The author uses a Bayesian hierarchical selection model, but does not analyse treatment effects, but the parameters of the weight function of the selection model, which is estimated with a Bayesian approach and MCMC sampling.
 \\
@@
 The median publication year per meta-analysis was 1997 for efficacy meta-analyses and 1999 for safety meta-analyses.
-Then, a bayesian two-step hierarchical selection model was applied (\citet{bayesian.selection.model}, \citet{bayesian.selection.model.2}).
+Then, a Bayesian two-step hierarchical selection model was applied (\citet{bayesian.selection.model}, \citet{bayesian.selection.model.2}).
 It assumes that the selection process is a two-step weight, which assigns different probabilities to non-significant and significant effects.
@@
 The model was fitted with the Monte-Carlo Markov-Chain algorithm STAN and the geometric mean was used as an estimate for the publication probability ratio.
-Simulations performed in \citep{bayesian.selection.model} indicate that the method performes well if the true mean effect size was not small, and also robust to small study effects.
+Simulations performed in \citep{bayesian.selection.model} indicate that the method performs well if the true mean effect size was not small, and also robust to small study effects.
 It outperformed Egger's test and Begg's test in assessing publication bias, especially when small study effects were absent, and had lower false-positive rates.
@@
 For sake of completeness, the probability of inclusion was  1.78 (95\% CI: 1.51 to 2.13) larger for non-significant safety effect estimates, but again, decreased with time (1.77, 95\% CI: 1.46 to 2.21 in 2000).
-The results are in line with the results from this study, but it was not possible to reafirm the finding of weaker publication bias in reviews published more frequently.\\
+The results are in line with the results from this study, but it was not possible to reaffirm the finding of weaker publication bias in reviews published more frequently.\\
 
@@
 \citet{Dechartres.2013} analyse publication bias based on sample size in meta-analyses from top journals and Cochrane reviews in 93 Meta-analyses and find that, for example, effects in trials with less than 50 patients were 48\% larger than in larger trials.
-\citet{Onishi.2014} find that in 36 Meta-Analyses without comprehensive literature research, there ar 19.4\% significant publication bias tests (Egger's test).
+\citet{Onishi.2014} find that in 36 Meta-Analyses without comprehensive literature research, there are 19.4\% significant publication bias tests (Egger's test).
 
 \section{Interpretation}
-In this study, a proportion of the meta-analyses that have been scrutinized have publication bias.
-Since regression and rank test have been applied one-sided, they have very likely larger effects in smaller studies that in larger studies.
-\\
-There have been proposed a number of reasons for this tendencies in smaller studies (see \citet{Egger} for a thorough discussion).
+In this study, evidence for publication bias has been found in approximately 20\% of the meta-analyses.
+The results are often times consistent among different tests and subsets of the data.
+A mixed effects meta regression confirms these findings with very large evidence for small study effects (indicating publication bias).
+Since the results of two-sided tests do not differ substantially from previous findings, the results are in line with previous research.\\
+% There have been proposed a number of reasons for this tendencies in smaller studies (see \citet{Egger} for a thorough discussion).
 In clinical settings, it might be that the requirement for more study participants in large studies might systematically change the study population.
-However, this systematic differences could influence the results in two ways: If recruitement of participants with a disease is difficult, and thus, also participants with less severe types of the disease are included, it might be that the effect of treatment is larger in the smaller study.
+However, this systematic differences could influence the results in two ways: If recruitment of participants with a disease is difficult, and thus, also participants with less severe types of the disease are included, it might be that the effect of treatment is larger in the smaller study.
 But one could also argue that the opposite could eventually be the case.
 \\
-The main cause for funnel plot asymmetry with smaller studies having larger effects is publication bias.
+% The main cause for funnel plot asymmetry with smaller studies having larger effects is publication bias.
 Publication bias enforces questionable research practices from researchers such as selective outcome reporting, $p$-hacking and data fabrication.
 Larger studies are less affected, and have also in general higher methodological quality \citep{Egger}, which leads to smaller effect sizes.\\
-Presence of publication bias in meta-analyses can ultimately lead to patient harm, because decision makers in clinical practice use the meta-analyses to take decisions if they use a treatment.
+Presence of publication bias in meta-analyses can ultimately lead to patient harm if decision makers in clinical practice use the meta-analyses to decide about application of a treatment.
 On the swiss Cochrane website, it is stated that Cochrane is the ``single most reliable source of evidence on the effects of health care''.
@@
 In some cases, it might be that the  evidence for a treatment in a meta-analysis is an artifact of publication bias.
-Besides harm to patient, this can cause a waste of ressources.
-\\
-The comparison of the results with previous analyses of publication bias in the Cochrane Database of Systematic Reviews implies gives more confidence in the results of this study, because they are largely in line.
+This also leads to a waste of resources in science.
 \\
@@
 After application of the criteria of \citet{Ioannidis2007}, there are left 11.6 \% of the reviews and 32.9\% of the studies.
-It is not clear how the results would be in the remaining dataset if tests were applicable.
-The most restrictive criterium of exclusion was that a meta-analysis has to have at least ten studies.
-Thus, in the data that is scrutinized, there has been enforced and ongoing research.
-\citet{ioannidis.2005} state that publication bias is also a consequence of modern discovery oriented research, and thus it may well be that publication bias is also an issue when the number of studies are lower.
-Also, it is possible that by excluding meta-analyses where $I^2 \geq 0.5$, the most extreme cases of publication bias are removed since publication bias increases the between-study heterogeneity.\\
-Furthermore, the sub-partitioning of meta-analyses based on conparison, outcome and subgroup is only one possibility%, which is in fact not recommended by the Cochrane Organisation. 
-Cochrane usually performs multiple meta-analyses with the same results, for example by doing sensitivity analyses (not an issue in this study, since they are removed) and subgroup analyses and overall analyses.
-One can as well repeat the analysis without considering subbgroups.
+It is not clear if the results also apply for the excluded data, \ie if the extent of publication bias is similar.
+The most restrictive criterium of exclusion was that a meta-analysis had to have at least ten studies.
+The included studies are thus likely to be part of enforced and sustained research efforts.
+When fewer and unparalleled studies are available, the quality of the research is not necessarily better.
+Publication bias may be even more of an issue in more discovery oriented research \citet{ioannidis.2005}.
+By excluding meta-analyses where $I^2 \geq 0.5$, the most extreme cases of publication bias are possibly removed since publication bias increases the between-study heterogeneity.\\
+% Furthermore, the sub-partitioning of meta-analyses based on comparison, outcome and subgroup is only one possibility%, which is in fact not recommended by the Cochrane Organisation. 
+% Cochrane usually performs multiple meta-analyses with the same results, for example by doing sensitivity analyses (not an issue in this study, since they are removed) and subgroup analyses and overall analyses.
+One can as well repeat the analysis without considering subgroups.
 This will have the advantage of increasing the sample size, but it will also result in increased heterogeneity in meta-analyses, and if one subgroup with small studies yields large effects, the cause must not be publication bias.
 \\
-It also has to be said that the removal of safety outcomes is only partially successfull.
-This is an issue, because it is not well known if and how publication bias affect safety outcomes.
-\citet{kicinsky} suggests that they are inversely affected, with editors publishing in favor of non-significant adverse effects.
-\\
-Also, it has been previously discussed that the method to detect the side on which bias is to be expected can fail and provide meaningless results, in which case a two-sided test is more meaningful.
-However, one could also discuss in more general terms if one can speak of publication bias in meta-analyses that have only one significant effect out of ten ($n$ = 417).
-\\
+It also has to be said that the removal of safety outcomes is only partially successful.
+This is an issue, because it is not well known if and how the publication probability is affected by the size of safety outcomes.
+\citet{kicinsky} suggests that they may inversely affect publication (\ie non-significant effects are preferred).\\
+Also, it has been previously discussed that the method to detect the side on which bias is to be expected can fail and provide meaningless results.
+One could also discuss in more general terms if one can speak of publication bias in meta-analyses that have only one significant effect out of ten ($n$ = 417), \ie if statistical significance is largely absent in a meta-analysis.\\
 There is also criticism that one can address on the methods.
@@
 This is considered rather unlikely.
-Other cirticism is more severe.
-The small study effect tests fail to account for statistical significance, however, this is a major component of publication bias.
-Small study effect test work because they take into account that smaller studies need larger effects to be significant.
-The only test that is applied that takes into account statistical significance per se is the excess significance test.
-When looking at it's results, it seems as if it is rather a test for between study heterogeneity per se, because it does agree very poorly with small study effect tests, and finds almost no excess significance in tests with $I^2 = 0$.
-The choice of the effect size and proxy of the study size is crucial when assessing publication bias.
-It is not clear which measure of effect size should be used when applying the test; the original measure (\eg a mean difference) may have standard errors that do not only depend on study size, but journal editors use this measure as the basis for their decision of publication.
-Fisher's $z$ transformed correlations have standard errors that are a function of study participant number only, but in contrast the effect size is bounded at$[-1,1]$, making it less suitable for linear regression.
-Standardized mean differences are possibly a good compromise.\\
-The ciriticism also applies for adjustment methods, as they also do not use statistical significance but the size of the effects.
-A weakness of the regression adjustment is that it also adjusts if the uncertainity in the small study effect is large.
-To compare it in this case with the meta-analysis estimate is difficult because the uncertainity in estimating the small study effect affects the uncertainity of the treatment effect.
-It is not clear how to proceed when one wants to adjust for publication bias.
+Other criticism is more severe.
+The small study effect tests applied do not account for statistical significance of effects directly.
+They work because smaller studies with larger errors need larger effects to be significant.
+The only test that is applied that takes into account statistical significance per se is the excess significance test, which is underpowered.\\
+The criticism also applies for adjustment methods, as they also rely on small study effects.
+A weakness of the regression adjustment is that it also adjusts if the uncertainty in the small study effect is large.
+To compare it in this case with the meta-analysis estimate is difficult because the uncertainty in estimating the small study effect affects the uncertainty of the treatment effect.
 Copas selection model uses the $p$-value threshold of 0.1 to decide if adjustment is necessary or not.
-One can argue that this threshold is arbitrary.
+One could argue that this threshold is arbitrary.
 Additionally, the threshold is used in two manners: first to decide if adjustment is necessary at all, and secondly, if the adjusted model does suitably account for publication bias ($p$ > 0.1).
@@
 \\
-With Copas selection model, it is in general the issue that it the model is not estimating, but rather applying some criteria of parsimony (the model with least publication bias with $p$-value for small study effect > 0.1 is chosen).
-Some authors find in their simulation studies that regression methods overperform the Copas selection model \citep{limitmeta}.
-\\
-Thus, the results are not exact and could be improved if more suitable methods are applied.
-The bayesian approach taken by \citet{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions.
+With Copas selection model, it is in general the issue that the model is not estimating the selection process parameters, but rather applying some criteria of parsimony (the model with least publication bias/selection with $p$-value for small study effect > 0.1 is chosen).
+\\
+Publication bias can also be present if a meta-analysis lacks a small study effect, for example if by chance, the smaller studies were published irrespectively of the statistical significance of their findinfs.
+Methods as the excess significance test of \citet{excess.significance} are applied to overcome this issue, but the method is known to lack power.
+No methods exist so far to adjust for excess significance.\\
+Therefore, the results are not exact and could be improved if more suitable methods are applied.
+The Bayesian approach taken by \citet{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions.
 \\
@@
 \section{Outlook}
-Given the size and abundancy of information in the dataset, the possibilities to investigate sources of bias in the Cochrane Database of Systematic Reviews are not exhausted (see for example in \citet{ioannidis.2017}).
+Given the size and abundance of information in the dataset, the possibilities to investigate sources of bias in the Cochrane Database of Systematic Reviews are not exhausted (see for example in \citet{ioannidis.2017}).
 In particular, one could easily come up with more hypotheses that could be tested in meta meta-regression, as introduced in the last section of the results.
-\\
-There are numerous suggestions for diffeerent measures of publication bias and small study effects, which could be applied on the dataset (see \citet{mueller.2016}).
+Many researchers have come up with hypotheses about the reasons and circumstances that promote publication bias, which could be tested if the information is extended.\\
+There are numerous suggestions for different measures of publication bias and small study effects, which could be applied on the dataset (see \citet{mueller.2016}).
 This study mainly relies on suggestions from \citet{Sterne}, \citet{Ioannidis2007} and \citet{limitmeta}.
@@
 Although there are well addressed, mathematical justifications for these methods, there might be better methods not yet tested on large datasets.
-An evaluation of all suggested methods was far beyond the scope of this study.
+An evaluation of all suggested methods was unfortunately beyond the scope of this study.
 
@@
 This study is so far the largest assessment of publication bias by small study effects and uses data that has been collected after major efforts have been made to curb publication bias.
+It is the first analysis of the Cochrane Database of Systematic Reviews also analyzing publication bias using hazard and rate ratios.
 The results indicate, similarly to other studies, that the efforts did not yet resolve the issue.

### 2019-08-06 report/chapter03.Rnw
Grammar, anova tables, discussion

@@
 \subsubsection{The Analysis Dataset}
-The dataset that was ultimately tested and adjusted for publication bias comprises \Sexpr{length(meta.id.vector)} meta-analyses and \Sexpr{dim(meta.data)[1]} results.
+The dataset that was ultimately tested and adjusted for publication bias comprises \Sexpr{dim(meta.f)[1]} meta-analyses and \Sexpr{format(dim(meta.data)[1], big.mark = ",")} results.
 The mean number of participants in the treatment group is \Sexpr{round(mean(meta.data$total1, na.rm = T),1)} vs \Sexpr{round(mean(data.ext2$total1, na.rm = T),1)} in the unrestricted dataset and the mean total number of participants \Sexpr{round(mean(meta.data$total1 + meta.data$total2),1)} vs \Sexpr{round(mean(data.ext2$total1 + data.ext2$total2),1)}.
-The mean publication year is \Sexpr{mean(meta.data$study.year, na.rm = TRUE)} vs \Sexpr{mean(data.ext2$study.year, na.rm = TRUE)} in the unrestricted dataset.
+The mean publication year is \Sexpr{round(mean(meta.data$study.year, na.rm = TRUE))} vs \Sexpr{round(mean(data.ext2$study.year, na.rm = TRUE))} in the unrestricted dataset.
 \\
-From the meta-analyses with incomplete data (\texttt{outcome.type} == \texttt{IV}), there are \Sexpr{first.iv.outcome.count} with \\ \texttt{outcome.measure.merged} = ``Risk Ratio'', \Sexpr{second.iv.outcome.count} ``Std.
-Mean Difference'',  \Sexpr{third.iv.outcome.count} ``Hazard Ratio'' and \Sexpr{fourth.iv.outcome.count} ``Odds Ratio'' (and 25 additional, different outcome measures).
+From the meta-analyses with incomplete data (\texttt{outcome.flag} == \texttt{IV}), there are \Sexpr{first.iv.outcome.count} with \\ \texttt{outcome.measure.merged} = \texttt{RR}, \Sexpr{second.iv.outcome.count} \texttt{SMD},  \Sexpr{third.iv.outcome.count} \texttt{Hazard Ratio}, \Sexpr{fourth.iv.outcome.count} \texttt{OR}, \Sexpr{fifth.iv.outcome.count} \texttt{MD} and \Sexpr{sixth.iv.outcome.count} \texttt{Rate Ratio}.
 

### 2019-08-06 report/chapter04.Rnw
Grammar, anova tables, discussion

@@
 After applying the Bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\% for binary and \Sexpr{mean.min.else.b}\% for continuous and \texttt{IV} outcomes.
-To compare significant findings for small study effect tests and excess significance tests, Harbord's or Egger's test results are compared with excess significane tests.
+To compare significant findings for small study effect tests and excess significance tests, Harbord's or Egger's test results are compared with excess significance tests.
 \Sexpr{mean.min.bin2}\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, \Sexpr{mean.min.else2}\% for continuous and \texttt{IV} outcomes.
@@
 
-colnames(missing.differences) <- c("meta.id", "id", "comparison.nr", "subgroup.nr",
-                                   "z fixed", "z random", "z Copas", "z regression",
-                                   "g fixed", "g random", "g Copas", "g regression")
+missing.differences <- missing.differences[,-1]
+colnames(missing.differences) <- c("id", "comparison.nr", "subgroup.nr",
+                                   "z fixed", "z random", "z Copas", "z reg.",
+                                   "smd fixed", "smd random", "smd Copas", "smd reg.")
 
@@
 Abbreviations are used for z-score (= z) and std.
-mean difference (= d).", label = "missing.differences", align = "llcccrrrrrrrr"),
+mean difference (= d).", label = "missing.differences", align = "lcccrrrrrrrr"),
       include.rownames = F, size = "tiny")
@@
 A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
-Note that most \Sexpr{dim(meta.iv)[1]} \texttt{IV} outcome data is not included when using $z$-score and std.
-mean difference.
+Note that only 26 out of \Sexpr{dim(meta.iv)[1]} \texttt{IV} outcome data is included when using $z$-score and std.
+mean differences, since not all effects could be transformed.
 
@@
 The Copas selection model also allows to compute the number of missing studies, given that the model's assumptions are correct.
-It finds that \Sexpr{format(round(sum(meta.f$missing.copas, na.rm = T)), big.mark = ",")} are missing, which corresponds to \Sexpr{round((sum(meta.f$missing.copas, na.rm = T)/sum(meta.f$k))*100,1)}\% from all \Sexpr{format(round(sum(meta.f$k)), big.mark = ",")} analysed studies.
+It finds that \Sexpr{format(round(sum(meta.f$missing.Copas, na.rm = T)), big.mark = ",")} are missing, which corresponds to \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% from all \Sexpr{format(round(sum(meta.f$k)), big.mark = ",")} analysed studies.
 Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
-Note that random effects meta-analysis substitutes have been excluded (\Sexpr{sum(is.na(meta.f$missing.copas))} out of \Sexpr{format(dim(meta.f)[1], big.mark = ",")}.
+Note that random effects meta-analysis substitutes have been excluded (\Sexpr{sum(is.na(meta.f$missing.Copas))} out of \Sexpr{format(dim(meta.f)[1], big.mark = ",")}.
 
@@
 In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
-The discrepancy between mean and median may indicate that the estimate of \Sexpr{round((sum(meta.f$missing.copas, na.rm = T)/sum(meta.f$k))*100,1)}\% missing studies depends somewhat on these extreme cases.
-As can be written of from Table \ref{copas.missing}, 5\%, \ie \Sexpr{round(sum(!is.na(meta.f$missing.copas))*0.05)} meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for \Sexpr{format(round(sum(meta.f$missing.copas[which(meta.f$missing.copas >= 17.60)], na.rm = T)), big.mark = ",")}, more than 30\% of missing studies.
+The discrepancy between mean and median may indicate that the estimate of \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% missing studies depends somewhat on these extreme cases.
+As can be written of from Table \ref{copas.missing}, 5\%, \ie \Sexpr{round(sum(!is.na(meta.f$missing.Copas))*0.05)} meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for \Sexpr{format(round(sum(meta.f$missing.Copas[which(meta.f$missing.Copas >= 17.60)], na.rm = T)), big.mark = ",")}, more than 30\% of missing studies.
 
@@
                        weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-print(xtable(anova(null.fit, small.study.fit)[,-1], caption = "Anova table for a generalized linear model for small study effects compared to the null model.
-'small.study.fit' denotes the model with random intercepts for meta-analyses and reviews.", label = "anova.small.study"), size = "scriptsize")
+small.study.fit.anova <- anova(null.fit, small.study.fit)
+small.study.fit.anova[2,9] <- "<0.00001"
+print(xtable(small.study.fit.anova[,-1], caption = "Anova table for a generalized linear model for small study effects compared to the null model.
+'small.study.fit' denotes the model with random intercepts for meta-analyses and reviews.",
+             label = "anova.small.study", digits = c(1,1,1,1,1,1,1,1,5)), 
+      size = "scriptsize")
 @
@@
 'small.study.fit' denotes the model with random intercepts for meta-analyses and reviews, 'small.study.rs.fit' the model with additional random slopes per review.",
-             label = "anova.random.slopes"), size = "scriptsize")
+             label = "anova.random.slopes", digits = c(1,1,1,1,1,1,1,1,1)), 
+      size = "scriptsize")
 @
@@
 <<results = 'asis', echo = FALSE>>=
-year.fit <- lme(fixed = smd.pool ~ se.smd.pool + rev.year.center, 
+review.year.fit <- lme(fixed = smd.pool ~ se.smd.pool + rev.year.center, 
                 random = list(~ 1 | id, ~ 1 | meta.id),
                 weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-year.int.fit <- lme(fixed = smd.pool ~ se.smd.pool * rev.year.center, 
+review.year.int.fit <- lme(fixed = smd.pool ~ se.smd.pool * rev.year.center, 
                     random = list(~ 1 | id, ~ 1 | meta.id),
                 weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-print(xtable(anova(small.study.fit, year.fit, year.int.fit)[,-1], caption = "Anova table for three generalized linear model fits.
-'small.study.fit' denotes the model with the standard error as explanatory variable, 'year.fit' the model with standard error and the centered (- 2013) review year as explanatory variable, and 'year.int.fit' the model with interaction between the two.",
-             label = "anova.lme"), size = "scriptsize")
-@
-
-Because neither AIC, BIC ot the F-test do show any improvement of model fit, it does not seem as if publication bias has substantially decreased or increased over the years.
+print(xtable(anova(small.study.fit, review.year.fit, review.year.int.fit)[,-1], caption = "Anova table for three generalized linear model fits.
+'small.study.fit' denotes the model with the standard error as explanatory variable, 'review.year.fit' the model with standard error and the centered (- 2013) review year as explanatory variable, and 'review.year.int.fit' the model with interaction between the two.",
+             label = "anova.lme", digits = c(1,1,1,1,1,1,1,1,2)), size = "scriptsize")
+@
+
+Because neither AIC, BIC or the F-test do show any improvement of model fit, it does not seem as if publication bias has substantially decreased or increased over the years.
 The review publication year is however not directly tied to the publication year of the studies that are affected by publication bias.
@@
                        weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-year.fit <- lme(fixed = smd.pool ~ se.smd.pool + study.year.center, 
+study.year.fit <- lme(fixed = smd.pool ~ se.smd.pool + study.year.center, 
                 random = list(~ 1 | id, ~ 1 | meta.id),
                 weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-year.int.fit <- lme(fixed = smd.pool ~ se.smd.pool * study.year.center, 
+study.year.int.fit <- lme(fixed = smd.pool ~ se.smd.pool * study.year.center, 
                     random = list(~ 1 | id, ~ 1 | meta.id),
                 weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-print(xtable(anova(small.study.fit, year.fit, year.int.fit)[,-1], caption = "Anova table for three generalized linear model fits.
-'Small study fit' denots the model with the standard error as explanatory variable, 'year.fit' the model with standard error and the centered (- 2000) study year as explanatory variable, and 'year.int.fit' the model with interaction between the two.",
-             label = "anova.lme"), size = "scriptsize")
+print(xtable(anova(small.study.fit, study.year.fit, study.year.int.fit)[,-1], caption = "Anova table for three generalized linear model fits.
+'Small study fit' denotes the model with the standard error as explanatory variable, 'study.year.fit' the model with standard error and the centered (- 2000) study year as explanatory variable, and 'study.year.int.fit' the model with interaction between the two.",
+             label = "anova.lme", digits = c(1,1,1,1,1,1,1,1,6)), size = "scriptsize")
 @
@@
 The analysis of model fit indicates that there is an improvement when using the study year as a covariate, but only as an additive effect.
+The coefficients of the model are given in Table \ref{coefficients.study.year.fit}.
 AIC and BIC are smaller and the $p$-value of the F-test is very small.
-However, not the size of the effect, but the slope of the linear regression fit would have to be decreased to ultimatively conclude a decrease of publication bias over the years.
+However, not the size of the effect, but the slope of the linear regression fit would have to be decreased to ultimately conclude a decrease of publication bias over the years.
+
+<<echo =FALSE, results='asis', warning=FALSE>>=
+lmer.table <- function(model){
+  sum <- summary(model)
+  estimate <- round(sum$coefficients$fixed)
+  ci <- intervals(model)
+  tb <- data.frame(estimate = round(ci$fixed[,2], 5), CI = round(ci$fixed[,c(1,3)], 5))
+  colnames(tb)[c(2,3)] <- c("2.5%CL", "97.5%CL")
+  return(tb)
+}
+print(xtable(lmer.table(study.year.fit), align = "lccc", 
+             caption = "Coefficients and 95\\% confidence limits of the generalized linear model. 'se.smd.pool' denotes the standard error of the std. mean difference.", 
+             label = "coefficients.study.year.fit", digits = c(4,4,4,4)),  size = "scriptsize")
+@
 

### 2019-08-06 report/chapter05.Rnw
Grammar, anova tables, discussion

--- 2019-08-02 report/chapter05.Rnw
@@
 
+meta.data <- data.ext2 %>% filter(meta.id %in% meta.f$meta.id)
+
 @
@@
 Five (13\%) meta-analyses from Cochrane and 13 (38\%) from the journals had significant two sided small study effect test results ($p$-value < 0.1).
-Also, they found that test-statistics were more often negative, which correspondend in their setup to larger effects in small studies.
+Also, they found that test-statistics were more often negative, which corresponded in their setup to larger effects in small studies.
 (\Sexpr{round(((24/38))*100, 1)} among Cochrane meta-analyses and \Sexpr{round(((26/37))*100, 1)} for journal meta-analyses).
@@
 In some cases, it might be that the  evidence for a treatment in a meta-analysis is an artifact of publication bias.
-Besides harm to patient, this can cause a waste of ressources.
+This also leads to a waste of resources in science.
 \\
-The comparison of the results with previous analyses of publication bias in the Cochrane Database of Systematic Reviews implies gives more confidence in the results of this study, because they are largely in line.
-\\
+The term publication bias is frequently used in this study, but \Sexpr{round((length(which(meta.data$study.data_source == "UNPUB"))/dim(meta.data)[1])*100, 1)}\% of the analysis dataset (1) are unpublished results.
+This mitigates the estimated extent of publication bias in this study since it has been shown repeatedly that effects in the grey literature are smaller.
 
@@
 After application of the criteria of \citet{Ioannidis2007}, there are left \Sexpr{round((740/6354)*100, 1)} \% of the reviews and \Sexpr{round((23243/70662)*100, 1)}\% of the studies.
-It is not clear how the results would be in the remaining dataset if tests were applicable.
-The most restrictive criterium of exclusion was that a meta-analysis has to have at least ten studies.
-Thus, in the data that is scrutinized, there has been enforced and ongoing research.
-\citet{ioannidis.2005} state that publication bias is also a consequence of modern discovery oriented research, and thus it may well be that publication bias is also an issue when the number of studies are lower.\\
-It also has to be said that the removal of safety outcomes is only partially successfull.
-This is an issue, because it is not well known if and how publication bias affect safety outcomes.
-\citet{kicinsky} suggests that they are inversely affected, with editors publishing in favor of non-significant adverse effects.
+It is not clear if the results also apply for the excluded data, \ie if the extent of publication bias is similar.
+The most restrictive criterium of exclusion was that a meta-analysis had to have at least ten studies.
+The included studies are thus likely to be part of enforced and sustained research efforts.
+When fewer and unparalleled studies are available, the quality of the research is not necessarily better.
+Publication bias may be even more of an issue in more discovery oriented research \citet{ioannidis.2005}.
+By excluding meta-analyses where $I^2 \geq 0.5$, the most extreme cases of publication bias are possibly removed since publication bias increases the between-study heterogeneity.\\
+% Furthermore, the sub-partitioning of meta-analyses based on comparison, outcome and subgroup is only one possibility%, which is in fact not recommended by the Cochrane Organisation. 
+% Cochrane usually performs multiple meta-analyses with the same results, for example by doing sensitivity analyses (not an issue in this study, since they are removed) and subgroup analyses and overall analyses.
+One can as well repeat the analysis without considering subgroups.
+This will have the advantage of increasing the sample size, but it will also result in increased heterogeneity in meta-analyses, and if one subgroup with small studies yields large effects, the cause must not be publication bias.
 \\
-Also, it has been previously discussed that the method to detect the side on which bias is to be expected can fail and provide meaningless results, in which case a two-sided test is more meaningful.
-However, one could also discuss in more general terms if one can speak of publication bias in meta-analyses that have only one significant effect out of ten ($n$ = \Sexpr{length(which(meta.f$n.sig.single == 1))}).
-\\
+It also has to be said that the removal of safety outcomes is only partially successful.
+This is an issue, because it is not well known if and how the publication probability is affected by the size of safety outcomes.
+\citet{kicinsky} suggests that they may inversely affect publication (\ie non-significant effects are preferred).\\
+Also, it has been previously discussed that the method to detect the side on which bias is to be expected can fail and provide meaningless results.
+One could also discuss in more general terms if one can speak of publication bias in meta-analyses that have only one significant effect out of ten ($n$ = \Sexpr{length(which(meta.f$n.sig.single == 1))}), \ie if statistical significance is largely absent in a meta-analysis.\\
 There is also criticism that one can address on the methods.
@@
 \\
-With Copas selection model, it is in general the issue that it the model is not estimating, but rather applying some criteria of parsimony (the model with least publication bias with $p$-value for small study effect > 0.1 is chosen).
-Some authors find in their simulation studies that regression methods overperform the Copas selection model \citep{limitmeta}.
+With Copas selection model, it is in general the issue that the model is not estimating the selection process parameters, but rather applying some criteria of parsimony (the model with least publication bias/selection with $p$-value for small study effect > 0.1 is chosen).
 \\
-Thus, the results are not exact and could be improved if more suitable methods are applied.
-The bayesian approach taken by \citet{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions.
+Publication bias can also be present if a meta-analysis lacks a small study effect, for example if by chance, the smaller studies were published irrespectively of the statistical significance of their findinfs.
+Methods as the excess significance test of \citet{excess.significance} are applied to overcome this issue, but the method is known to lack power.
+No methods exist so far to adjust for excess significance.\\
+Therefore, the results are not exact and could be improved if more suitable methods are applied.
+The Bayesian approach taken by \citet{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions.
 \\

### 2019-08-09 report/MSc_Report.tex
results and methods correction

@@
 \section{Introduction and Notation}
-The analysis has already been said to be restricted on clinical or health care interventions.
 The interventions are restricted to comparisons of two treatment groups by some measure of melioration or worsening of health.
 The difference in this measure between the groups is referred to as the treatment effect.
-Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or standardized mean difference, Fisher's z score or Pearsons correlation coefficient.\\
+Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, log rate ratio, Cohen's $d$ or standardized mean difference, Fisher's z transformed score.\\
 Let us consider a meta-analysis with $n$ study treatment effects ($n > 1$, but typically small).
@@
 For continuous outcomes, let $m_t$ be the mean of the treatment group, $m_c$ the mean of the control group, and equivalently $\textrm{sd}_t$ and $\textrm{sd}_c$ the corresponding standard deviations. 
-$n_t$ and $n_c$ are the total number of participants in the groups.
 In the case of binary outcomes, let $e_t$ be the count of events in the treatment arm $e_c$ the events in the control group.
-The observed counts in a study $i$ are referred to as $e_{t,i}$ and analogously $e_{c,i}$.
-
-\section{Effect Measures and $p$-values}
+$n_t$ and $n_c$ are the total number of participants in the groups ($c$ for control and $t$ for treatment).%The observed counts in a study $i$ are referred to as $e_{t,i}$ and analogously $e_{c,i}$.
+
+\section{Effect Measures and $p$\hspace{0.4mm}-values}
 \subsection{Continuous Outcomes}
 For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Cohen's $d$) and a standard error thereof.
-The mean difference can $\theta$ and its standard error $\se$ can be obtained as
+The mean difference $\theta$ and its standard error $\se$ can be obtained as
 
@@
 
-The standardized mean difference $d$ and its standard error $\se$ can similarly be obtained by
-
-\begin{align}
-\se &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}} & g &= \frac{m_t - m_c}{\se} \label{eq:hedges.g}
-\end{align}
-
-Both estimators take into account that the two groups might have unequal variances.
-A $p$-value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$ test.
+Cohen's $d$ and its standard error $\se$ can similarly be obtained by
+
+\begin{align}
+\se &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}} & d &= \frac{m_t - m_c}{\se} \label{eq:hedges.g}
+\end{align}
+
+Both estimators take into account that the two groups might have unequal variances. \\ 
+A $p$\hspace{0.4mm}-value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$ test.
 The $t$ statistic is obtained, using $\se$ and $d$ from \eqref{eq:hedges.g}, by
@@
 \end{align}
-and the $p$-value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
+and the $p$\hspace{0.4mm}-value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
 
@@
 
-The t-test is known to be not very reliable if combined sample size is small ($n < 30$), see for example \citet{t.test}.
+The t-test is known to be not very reliable if combined sample size is small ($n_t + n_c < 30$).
 
 \subsection{Binary Outcomes}
-Two commonly used effect measures for binary outcome data are risk ratios and odds ratios between treatment and control group. 
+Two commonly used effect measures for binary outcome data are risk ratios and odds ratios between treatment and control groups. 
 The methods presented here can also be found, for example, in \cite[34]{Intro.meta}.
-Let $\theta$ be the natural logarithm of the odds ratio. $\theta$ and its variance $\se^2$ can be obtained by
+Let $\theta$ be the natural logarithm of the odds ratio. $\hat{\theta}$ and its variance $\hat{\se}^2$ can be obtained by computing
 
@@
 \hat{\theta} &= \log(\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}) \nonumber \\
-\se^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
+\hat{\se}^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
 \end{align}
@@
 
-Using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$-value, \eg \cite[98]{held2014}.
-\\
+Asuming binomial distribution of the events and using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$\hspace{0.4mm}-value, \eg \cite[98]{held2014}.
+The approximation is only good if there are enough events and sample size is large enough.\\
 Thus, with $\Phi$ as the cumulative standard normal distribution, we get
 \begin{align}
-p &= 2\cdot(1-\Phi(\abs{\hat{\theta}/\hat{\se}}), \nonumber
-\end{align}
-a $p$-value for the corresponding estimate, which summarizes the evidence against $\hat{\theta}$ being zero (\ie the true risk/odds ratio being 1). \\
-Binary and continuous effect measures can be converted into each other, as described in Section \ref{sec:transformation.effectsizes}.
-
-\subsection{Survival Outcomes}
+p &= 2\cdot(1-\Phi(|\hat{\theta}/\hat{\se}|), \nonumber
+\end{align}
+a $p$\hspace{0.4mm}-value for the corresponding estimate, which summarizes the evidence against $\hat{\theta}$ being zero (\ie the true risk/odds ratio being 1). \\
+Odds ratios can be transformed to std. mean differences, which will be described in Section \ref{sec:transformation.effectsizes}.
+
+\subsection{Time-to-Event Outcomes}
+Usually, time-to-event data of two experimental groups can be compared by rate ratios. The normal approximations of the maximum likelihood estimators also works here when using the log rate ratio.
 Time-to-event data with censoring has to be analyzed by special means.
@@
 \begin{align}
-p &= 2\cdot(1-\phi(\abs{\hat{\theta}/\hat{\se}(\hat{\theta})}) \nonumber
-\end{align}
-will give a $p$-value for the evidence against the null hypothesis.
+p &= 2\cdot(1-\Phi(|\hat{\theta}/\hat{\se}(\hat{\theta})|) \nonumber
+\end{align}
+will give a $p$\hspace{0.4mm}-value for the evidence against the null hypothesis.
 
@@
 The fixed effects meta-analysis estimator of the pooled treatment effect is a mean of the single treatment effect estimators, weighted by their standard errors \citep{fixed.effects.rosenthal}.
-Let $w_i = 1/\se_i^2$ be the weights, and $\theta_M$ be the pooled estimator and $s_M^2$ its variance.
+Let $w_i = 1/\se_i^2$ be the weights, and $\theta_M$ be the pooled estimator and $\se_M^2$ its variance.
 Then
@@
 \theta_M &= \frac{\sum_{i = 1}^n w_i \theta_i}{\sum_{i = 1}^n w_i} &
-s_M^2 &= \frac{1}{\sum_{i = 1}^n w_i} \label{eq:fixed.effects}
+\se_M^2 &= \frac{1}{\sum_{i = 1}^n w_i} \label{eq:fixed.effects}
 \end{align}
@@
 $\tau^2$ is often referred to as a population variance or between-study variance, whereas $\se_i^2$ can be interpreted as sampling error.
-The pooled treatment effect estimate $\theta_M$ of the random effects model and its variance is obtained by replacing the weights $w_i$ in equation \eqref{eq:fixed.effects} with $w_i = 1/(\se_i^2 + \tau^2)$.
-\\
+The pooled treatment effect estimate $\theta_M$ of the random effects model and its variance is obtained by replacing the weights $w_i$ in equation \eqref{eq:fixed.effects} with $w_i = 1/(\se_i^2 + \tau^2)$.\\
 The model is superior to the fixed effects model whenever the standard errors of the treatment effects alone are unlikely to fully account for the entire variability observed between studies.
-Note that as $\tau^2$ increases, each $\theta_i$ will eventually get equal weights, irrespective of it's sampling error $\se_i^2$.\\
-The estimation of $\tau^2$ has been subject to some debate in the statistical literature. Oftentimes, the method of moment estimator of \citet{tau.estimator} is used.
+The method assigns larger weights to studies with larger standard errors.\\
+The estimation of $\tau^2$ has been subject to some debate in the statistical literature.
+Oftentimes, the method of moment estimator of \citet{tau.estimator} is used.
 We use the measure of heterogeneity, $Q$, and divide by $C$ after having subtracted the degrees of freedom $n-1$:
@@
 \begin{align}
-Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i}\label{eq:Q.heterogeneity} \\
+Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i} \label{eq:Q.heterogeneity} \\
 \tau^2 &= \max\big(0, \frac{Q - (n-1)}{C}\big) \label{eq:Tau.definition}
@@
 
-Again, $w_i, \theta_i ...$ have to be replaced by their estimates in order to get an estimate $\hat{\tau}^2$. \\
-The Paule-Mandel estimator \citep{paulemandel} is considered to have most often better properties than the method of moments estimator (\eg \citet{tau.estimator.evaluation}).
+The estimators have to be replaced by their estimates in order to get an estimate $\hat{\tau}^2$.\\
+The Paule-Mandel estimator \citep{paulemandel} is considered to have better properties than the method of moments estimator (\eg \citet{tau.estimator.evaluation}).
 Since we defined $w_i = 1/(\se_i^2 + \tau^2)$, it also holds that
@@
 
-$\theta_M$ can be estimated using equation \eqref{eq:fixed.effects}, the only problem is to estimate $\tau^2$. It can be obtained through an iterative process, using a newly defined function
+After estimating $\theta_M$ with equation \eqref{eq:fixed.effects}, the only problem remaining is to estimate $\tau^2$.
+$\hat{\tau}^2$ can be obtained through an iterative process, using a newly defined function
 
@@
 Using a truncated Taylor series expansion, one can obtain the partial derivative after $\tau^2$, which is a reasonable choice for $\tau_0^2$.
-\\
-%Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{theta}$, we can update $F(\tau^2)$ and check convergence to zero. \\
+Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{theta}$, we can update $F(\tau^2)$ and check convergence to zero.
+\\
 The estimation of $\tau^2$ is accompanied by uncertainty.
 A common procedure is to test if it is there is significant heterogeneity between the studies \cite[109]{Intro.meta}.
-Compute $Q$, as given in \eqref{eq:Q.heterogeneity}, based on one of the estimators of $\tau^2$.
+For this, $Q$ has to be computed as given in \eqref{eq:Q.heterogeneity}.
 It is assumed that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equally distributed effect sizes.
 Thus, the expected value of $Q$ is $n-1$, and the excess dispersion is $Q - n + 1$.
-The $p$-value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
+The $p$\hspace{0.4mm}-value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
 = $n-1$.
 \\
-An advantage of the $\tau^2$ is that it is directly linked to the variability in the data.
-Additionally, one can use the $I^2$ statistic to see what portion the between study variance has of the overall variance.
+$\tau^2$ is  is directly linked to the variability in the data.
+The $I^2$ statistic of excess/total dispersion can be used alternatively to assess the extent of additional variance to the variances of the primary study estimates.
 It is computed as
@@
 
-%Large values for $\hat{I}^2$ are of great importance when analyzing \eg small study effects. \\
+The statistic takes value between zero and one, and is easily interpretable.
+0 is equal to 0\% excess dispersion and \eg 0.5 equal to 50\% additional between-study variance of the total variance of the estimates.
+\\
 Importantly, all proposed methods above assume normally distributed effect sizes and proper estimates $\hat{\se}$ of the true standard error.
@@
 $\epsilon$ is the residual noise term that becomes necessary when $n$ pairs $(x_i, y_i)$ are given and there is no exact solution.
-Then it is common to look for the solution that minimizes the squared residuals, the least-squares solution.
+We look for the solution that minimizes the squared residuals, the least-squares solution.
 Formally,
@@
 
+\vspace{2mm}
+
 Let $\mathbf{\beta} = (\beta_0, \beta_1)^\top$. It can be shown that
@@
 
-The estimate $\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the regression line. Furthermore, in the simple linear regression setting, $\hat{\beta}_0$ can also be obtained by:
+If one plots the values of $y$ and $x$, the estimate $\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the regression line.
+Furthermore, in the simple linear regression setting, $\hat{\beta}_0$ can also be obtained by:
 
@@
 
-where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. $p$ will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
+where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. The $p$\hspace{0.4mm}-value will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
 The concept is extendable to weighted linear regression.
@@
 The introduction of group-specific random effects allows to analyze grouped or repeated measurements by linear regression.
-Let $i$ be the group index, $j$ the index of the single observation from the group $i$ and $x_j$ the $j^\textrm{th}$ row of $\mathbf{X}$.
+Let $j$ be the group index, $i$ the index of the single observation from the group $j$ and $x_i$ the $i^\textrm{th}$ row of $\mathbf{X}$, $(1, \mathbf{X}_{i2})$.
 Then the equation
@@
 \begin{align}
-\mathbf{y}_{j}|U_i,\epsilon_{j} =  x_j\beta + U_i + \epsilon_{j} \label{eq:one.random.intercept}
-\end{align}
-
-gives the marginal distribution of $\mathbf{y}{_{j}}$ depending on $U{_i}$ and $\epsilon{_{j}}$.
-The random effects $U{_i} \sim N(0, \mathbf{G})$ and the residual error term $\epsilon{_{j}} \sim N(0, \tau^{2})$ are independent from each other.
-The expectation $\mathbb{E}(\mathbf{y}_{j})$ is still $x_j \beta$, but now, the covariance between the observations within a group $i$, $\mathbf{y}_i$, is modeled as
-
-\begin{align}
-\Cov(\mathbf{y}_i) &= \mathbf{D}_i \mathbf{G} \mathbf{D}_i^\top + \tau^2 \mathbf{I}_{n_i} \label{eq:random.intercepts.covariance}
-\end{align}
-
-where $\D_i$ is in the case of the random intercept model a $1 \times n_i$ matrix of 1's and $\mathbf{G}$ is a scalar to be estimated.
+\mathbf{y}_i|U_j,\epsilon_{i} =  x_i\beta + U_j + \epsilon_{i} \label{eq:one.random.intercept}
+\end{align}
+
+gives the marginal distribution of $\mathbf{y}_i$ depending on $U{_j}$ and $\epsilon_i$.
+The random effects $U_j \sim N(0, \mathbf{G})$ and the residual error term $\epsilon_i \sim N(0, \tau^{2})$ are independent from each other.
+Let $\mathbf{y}_j$ be a vector of all observations of group $j$.
+The expectation $\mathbb{E}(\mathbf{y}_i)$ is still $x_i \beta$, but the covariance between the observations within a group $j$, is modeled as
+
+\begin{align}
+\Cov(\mathbf{y}_j) &= \mathbf{D}_j \mathbf{G} \mathbf{D}_j^\top + \tau^2 \mathbf{I}_{n_j} \label{eq:random.intercepts.covariance}
+\end{align}
+
+where $\D_j$ is in the case of the random intercept model a $n_j \times 1$ matrix of 1's, $\mathbf{G}$ is a scalar to be estimated and $\mathbf{I}_{n_j}$ is an $n_j \times n_j$ identity matrix.
 Thus, if $\mathbf{G} \neq 0$, the observations within a group will be uniformly correlated (uniform correlation between each observation).
-Nested groups are achieved by extending the design matrix $\mathbf{X}$ with an additional column of 1's and using according indices that specify the nesting structure.\\
+\\
+Nested groups can be modelled by extending the design matrix $\mathbf{X}$ with an additional column of 1's and using according indices that specify the nesting structure.\\
 An extension of the random intercepts model is the random slopes model, which allows for additional, group-specific slopes with respect to a explanatory variable $x$.
 It can be implemented by modifying \eqref{eq:one.random.intercept}.
-Let $\mathbf{U}_i$ be a two-dimensional random vector with a $2 \times 2$ covariance matrix $\mathbf{G}$.
-Again, we can specify the marginal distribution of a observation $j$ within a group $i$:
-
-\begin{align}
-\mathbf{y}_j|U_i,\epsilon_j =  x_j\beta + x_j \mathbf{U}_i + \epsilon_j \label{eq:one.random.intercept.and.slope}
-\end{align}
-
-$\mathbf{D}_i$ is a $p + 1 \times n_i$ matrix where the $j^\textrm{th}$ column is equal to $(x_j)^\top$.
-The covariance matrix $\mathbf{V_i}$ for group $i$ is defined as in equation \eqref{eq:random.intercepts.covariance}, using the new $\mathbf{D}_i$.
-Defining $\mathbf{x}_i$ as all observations from group $i$ of $\mathbf{X}$, and equivalently $\mathbf{y}_i$, the estimated vector $\hat{\beta}$ is obtained by computing
-
-\begin{align}
-\hat{\beta} &= \Big( \sum_{i = 1}^m \mathbf{x}_i^\top \hat{\mathbf{V}}_i^{-1} \mathbf{x}_i \Big)^{-1} \sum_{i = 1}^m \mathbf{x}_i^\top \hat{\mathbf{V}}_i^{-1} \mathbf{y}_i
-\end{align}
-
-with $m$ being the number of groups and $\hat{\mathbf{V}}_i$ being the estimated covariance, obtained by maximizing the log likelihood of the normal distribution, as $\mathbf{y}_i$ is distributed as
-
-\begin{align}
-\mathbf{y}_i \sim N(\mathbf{x}_i \beta, \mathbf{V}_i)
-\end{align}
-
-$\Big( \sum_{i = 1}^m \mathbf{x}_i^\top \hat{\mathbf{V}}_i^{-1} \mathbf{x}_i \Big)$ are assumed to be positive definite, as well as  $\hat{\mathbf{V}}_i^{-1}$.
+Let $\mathbf{U}_j$ be a two-dimensional random vector with a $2 \times 2$ covariance matrix $\mathbf{G}$.
+Again, we can specify the marginal distribution of a observation $i$ within a group $j$:
+
+\begin{align}
+\mathbf{y}_i|U_j,\epsilon_i =  x_i\beta + x_i \mathbf{U}_j + \epsilon_i \label{eq:one.random.intercept.and.slope}
+\end{align}
+
+$\mathbf{D}_j$ is a $n_i \times 2$ equal to all rows of observations of $j$ in $\mathbf{X}$.
+The covariance matrix $\mathbf{V_j}$ for group $j$ is defined as in equation \eqref{eq:random.intercepts.covariance}, using the new $\mathbf{D}_j$.
+Defining $\mathbf{x}_j$ as the matrix with all observations from group $j$ of $\mathbf{X}$, and equivalently the vector $\mathbf{y}_j$, $\hat{\beta}$ is obtained by computing
+
+\begin{align}
+\hat{\beta} &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1} \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{y}_j
+\end{align}
+
+with $m$ being the number of groups and $\hat{\mathbf{V}}_j$ being the estimated covariance, obtained by maximizing the log likelihood of the normal distribution, as $\mathbf{y}_j$ is distributed as
+
+\begin{align}
+\mathbf{y}_j \sim N(\mathbf{x}_j \beta, \mathbf{V}_j)
+\end{align}
+
+The matrices $\sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j$ and $\hat{\mathbf{V}}_j$ are assumed to be positive definite  .
 The approximate covariance matrix of $\hat{\beta}$ is given by
@@
 \begin{align}
-\hat{\Cov(\hat{\beta})} &= \Big( \sum_{i = 1}^m \mathbf{x}_i^\top \hat{\mathbf{V}}_i^{-1} \mathbf{x}_i \Big)^{-1}
-\end{align}
-
-Weights can be introduced by replacing $\mathbf{I}_{n_i}$ in \eqref{eq:random.intercepts.covariance} with the previously introduced weight matrix $\mathbf{W}_i$ .Hypothesis tests for $\beta = \beta_\textrm{H0}$ can be made using the Wald method.
-
-\section{Small Study Effects Tests}
+\hat{\Cov}(\hat{\beta}) &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1}
+\end{align}
+
+Weights can be introduced by replacing $\mathbf{I}_{n_j}$ in \eqref{eq:random.intercepts.covariance} with the previously introduced weight matrix $\mathbf{W}_j$.
+Hypothesis tests for $\beta = \beta_\textrm{H0}$ can be made using the Wald method.
+
+\section{Publication Bias Tests}
 The tests that will be presented on the following pages are a common way to detect publication bias.
-Importantly, they are however not interpretable directly as evidence for publication bias, but this is left for the discussion chapter.
-The tests are also often referred to as funnel plot asymmetry tests, because of the popularity of a recent test that has been used frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill}.
-However, it is known for some time that the method has disadvantageous properties, therefore, it will not be discussed here, as well as the funnel plot (the radial plot will be used as an alternative).\\
-A test for small study effects will test in some ways if the size of the estimated treatment effect of a study depends on some measure of its size.
-An association between study size and treatment effect size can be interpreted as an artifact of publication bias.
-
-\subsection{Continuous Outcome Tests}
-For a continuous outcomes that are normally distributed, the sample mean and variance are independent of each other \cite[120]{meta.w.R}.
-Thus, the estimated standard errors of treatment effects can be used as a proxy for study size, as they should in principle not be tied to the effect size.
-
-\subsubsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
+A frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill} is not discussed because of its disadvantageous properties, therefore, it will not be discussed here (see \eg \citet{Moreno.2009}).\\
+
+\subsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
 \citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
 A standardized effect size $\theta_i^\star$ can be computed as in \eqref{eq:begg.stand.eff}.
-$\se_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \eqref{eq:begg.stand.var}, $\theta_M$ being the fixed effects pooled treatment effect (\eqref{eq:fixed.effects}.
+$\se_i^{2\star}$ is the variance of $\theta_i - \theta_M$ as defined in \eqref{eq:begg.stand.var} and $\theta_M$ is the fixed effects pooled treatment effect (\eqref{eq:fixed.effects}.
 
@@
 A rank correlation test based on Kendall's tau is then used.
-First, the pairs are ordered after their ranks based on $s^{2\star}$.
-Then, for each $s^{2\star}$ rank, the corresponding ranks based on $\theta^{2\star}$ that are larger are counted and summed up to $u$.
+First, the pairs are ordered after their ranks based on $\se^{2\star}$.
+Then, for each $\se^{2\star}$ rank, the corresponding ranks based on $\theta^{2\star}$ that are larger are counted and summed up to $u$.
 The number of ranks based on $\theta^{2\star}$ that are in contrary, smaller, are counted and summed up to $l$.
@@
 
-Thus, large number of concordance between pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$.
-The $p$-value is obtained using the standard normal distribution $\Phi$:
+Thus, large number of concordant pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$.
+A two-sided $p$\hspace{0.4mm}-value is obtained using the standard normal distribution $\Phi$:
 \begin{align}
@@
 
+A one-sided test for positive correlation is obtained by computing $1-\Phi(Z)$ instead.
 The changes that have to be made int the case of ties are small and can be found in \cite[410]{begg.ties}.
 
-\subsubsection{Egger's Test: Weighted Linear Regression Test} \label{sec:Egger}
+\subsection{Egger's Test: Weighted Linear Regression Test} \label{sec:Egger}
 Linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citet{Egger}.
-Let $\theta/s$ be the dependent variable $y$ and $1/\se$ the explanatory variable $x$.
+Let $\theta/\se$ be the dependent variable $y$ and $1/\se$ the explanatory variable $x$.
 If plotted, this corresponds to a radial or Galbraith plot \citep{galbraith}.
@@
 with weights $w = 1/\se^2$.
-Thus testing $\beta_0$ of \eqref{eq:radial.plot} or $\beta_1$ is equivalent.
-The corresponding $p$-value is then used as evidence for a small study effect.
-Plugging in  $\theta_i/\se_i, 1/\se_i$ as $y_i, x_i$ into equation \eqref{eq:regression.parameters} and \eqref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{\se}_{\beta_0}$ and $\hat{\se}_{\beta_1}$.
+Thus testing $\beta_0$ of \eqref{eq:radial.plot} or $\beta_1$ of \eqref{eq:egger.plot} is equivalent.
+The corresponding $p$\hspace{0.4mm}-value is then used as evidence for a small study effect.
+Plugging in  $\theta_i/\se_i, 1/\se_i$ as $y_i, x_i$ into equations \eqref{eq:regression.parameters} and \eqref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{\se}_{\beta_0}$ and $\hat{\se}_{\beta_1}$.
 
@@
 
-\subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{sec:Thompson}
+\subsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{sec:Thompson}
 A method proposed in \citet{thompson.sharp} allows for between study variance $\tau^2$, as introduced before in section \ref{sec:meta.analysis}.
-It extends the previously seen linear regression approach with $x = 1/\se$ and $y = \theta/s$ by introducing weights.
+It extends the previously seen linear regression approach with $x = 1/\se$ and $y = \theta/\se$ by introducing new weights.
 The effect size $\theta_i$ is assumed to be distributed as
@@
 After adjusting for the weights as described in \ref{weighted.regression}, we can proceed analogous to Egger's test.
-The $p$-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
-
-\subsection{Dichotomous Outcomes Tests}
-
-The issue with dichotomous outcomes is that effect size and variance of effect size are correlated, which can readily be seen in \eqref{eq:risk.ratio} and \eqref{eq:risk.ratio.variance}.
-For example, a small number of event counts in one or group will inflate the variance and the effect size.
-Consequently, the tests above will tend to reject the null-hypothesis too often, \ie report false positives.
-A number of solutions to this problem are provided in the literature.
-
-\subsubsection{Peters Test: Weighted Linear Regression Test} \label{sec:Peter}
-Instead of taking the standard error $s$ as explanatory variable $x$ as in Egger's Test, the inverse of the total sample size is used.
+The $p$\hspace{0.4mm}-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
+
+\subsection{Peters Test: Weighted Linear Regression Test} \label{sec:Peter}
+When the outcome is dichotomous, effect sizes and variances of effect size are correlated, which can readily be seen in \eqref{eq:risk.ratio} and \eqref{eq:risk.ratio.variance} (see also \cite[120]{meta.w.R}).
+A small number of event counts in one or group will inflate the variance and the effect size.
+Consequently, the tests above will tend to reject the null-hypothesis too often, \ie report false positives.\\
+Instead of taking the standard error $\se$ as explanatory variable $x$ as in Egger's Test, the inverse of the total sample size is used.
 Additionally, the variances $\se_i^2$ are used as weights.
@@
 Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
-
-\subsubsection{Harbord's Test: Score based Test} \label{sec:Harbord}
+\\
+
+\subsection{Harbord's Test: Score based Test} \label{sec:Harbord}
 A rank based alternative to Peters test for binary outcomes is Harbord's test \citep{Harbord}.
-It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated at log odds ratio $\theta_0 = 0$ and its inverse Fisher information $s^2$. Formally,
+It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated at log odds ratio $\theta_\textrm{H0} = 0$ and its inverse Fisher information $s^2$.
+Formally,
 
@@
 It can be shown that they are both good approximations of the log odds ratio and its variance if the real $\theta$ is not too far from zero.
-The standardized estimator $r_i/v_i$ is also known as Peto odds ratio.
+The standardized estimator $\varphi_i/\se_i^2$ is also known as Peto odds ratio.
 The obtained scores and variances can be used in Egger's test as treatment effects and variances.
 
-\subsubsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
-\citet{Schwarzer} developed a test for the correlation between $E_t - \mathbb{E}(E_t)$ and the variance of $E_t$, $E_t$ being a random variable from the non-central hypergeometric distribution, assuming a fixed log odds ratio.
-\\
-$\mathbb{E}(E_t)$ and variance of $E_t$ are then estimated based on $e_t$. The standardized cell count deviation 
+\subsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
+\citet{Schwarzer} developed a test for the correlation between the event counts in the treatment group and the expected event counts $E_t - \mathbb{E}(E_t)$.
+When the marginals in a two-by-two table and the log odds ratio is fixed, it can be shown that $E_t$ follows a non-central hypergeometric distribution.
+Using the Mantel-Haenszel log odds ratio and the marginal total parameters, the variance and the expectation of $E_t$ is calculated.
+The inverse of the variance $\se(E_t)^2$ and the standardized event count
+
 \begin{align}
@@
 \end{align}
-and the inverse of $\se_i^2$ is then used as before in Begg and Mazumdar's test.
-
-\subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables} \label{sec:Rucker}
+
+are then used as before in Begg and Mazumdar's test.
+
+\subsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables} \label{sec:Rucker}
 The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables.
@@
 \citet{excess.significance} developed an exploratory test to detect if the proportion of significant findings is larger than expected. 
-Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study.
-\\
+%Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study. \\
 We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated by fixed effects Meta-Analysis \eqref{eq:fixed.effects}.
 Let $O$ be the number of significant study results out of $n$ studies and $\alpha$ the significance threshold.
-Corresponding to the study effect $\theta_i$, we can specify the power $1 - \beta_i$, the probability to accepting a true result.
+Corresponding to the study effect $\theta_i$, we can specify the power $1 - \beta_i$, the probability to be accepting a true result.
 Let $z_{\alpha,i}$ be the $1-\alpha$ quantile of a normal distribution with standard error $\hat{\se}_i$.
@@
 
-with $F$ being the cumulative distribution of a normal with mean $\hat{\theta}_M$ and standard deviation $\hat{\se}_i$. \\
+with $F$ being the cumulative normal distribution with mean $\hat{\theta}_M$ and standard deviation $\hat{\se}_i$. \\
 If we assume no bias in $\theta_i$ and $\theta_M$, the expected number of significant study results is then just
@@
 \begin{align}
-\chi  &= \big( \frac{(O - E)^2}{E} + \frac{(O - E)^2}{n - E}\big) \nonumber
-\end{align}
-
-and consecutively, calculating a $p$-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
+\chi  &= \bigg( \frac{(O - E)^2}{E} + \frac{(O - E)^2}{n - E}\bigg) \nonumber
+\end{align}
+
+and consecutively, calculating a $p$\hspace{0.4mm}-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
 Alternatively, one can also use a binomial test, which is encouraged when $n$ and $O$ is small.
-We will get a one sided $p$-value for excess significance, $\P(X \geq O)$, by
+We will get a one sided $p$\hspace{0.4mm}-value for excess significance, $\P(X \geq O)$, by computing
 
@@
 They can mainly be distinguished by their underlying methods: regression based approaches aim to regress the effect to a study with infinite precision (\ie very small standard error) or to a summary effect, corrected for publication bias.
-Selection models aim to simulate different, hypothetical selection processes and attain a approximate treatment effect by sensitivity analysis:
+Selection models are used for a sensitivity analysis, where the selection parameters are assumed to be fixed.
 
@@
 \begin{align}
-\theta_i & = \beta_0 + \beta_1\sqrt{\se_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \epsilon_i \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{eq:limitmeta.regression}
-\end{align}
-
-The only difference between Thompson and Sharp's variant is $x = \sqrt{\se^2 + \tau^2}$ instead of $x = \sqrt{\se^2}$.
-$\beta_{1}$ represents the bias introduced by small study effects, as illustrated in the following equations:
+\theta_i & = \beta_0 + \beta_1\sqrt{\se_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \label{eq:limitmeta.regression} \\
+\epsilon_i \stackrel{\textrm{iid}}{\sim} N(0,1)
+\end{align}
+
+The only difference between Thompson and Sharp's variant and this method is that $x = \sqrt{\se^2 + \tau^2}$ is used instead of $x = \sqrt{\se^2}$.
+$\beta_{1}$ is the bias parameter and can be interpreted as the bias introduced by small study effects, as illustrated in the following equations:
 
@@
 
-After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before in the simple linear regression framework. Now we have basically two possible estimates at hand:
+After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before in the simple linear regression framework.There are two possible estimates at hand:
 \begin{itemize}
-\item $\beta_0$ the treatment effect without any influence of study precision with standard error $s_{\beta_0}$
-\item $\beta_0 + \beta_1 \tau$ the treatment effect of a hypothetical study with infinite precision, corresponding standard error $\se = s_{\beta_0} + s_{\beta_1}$
+\item $\beta_0$ the treatment effect without any influence of study precision with standard error $\se_{\beta_0}$
+\item $\beta_0 + \beta_1 \tau$ the treatment effect of a hypothetical study with infinite precision, corresponding standard error $\se = \se_{\beta_0} + \se_{\beta_1}$
 \end{itemize}
@@
 Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior to the former, because it showed a smaller mean-squared error in simulation studies \citet{limitmeta.2}.
-Also, this simulation study emphasizes that adjustment is more reliable when effects of publication bias are strong within a meta-analysis.
-When no publication bias affects the meta-analysis, and event rates are low, the method will provide biased estimates and the mean squared error is large.
-Coverage of the confidence is always larger or equal to meta-analysis.
-It outperforms or is equal to classical meta-analysis estimates if there is publication bias, especially if event rates in the control group are small.
+From the formulas above, it becomes clear that is has a larger standard error.
+The results of the simulation furthermore emphasize that adjustment is more reliable when effects of publication bias are strong within a meta-analysis.
+When no publication bias affects the meta-analysis, and event rates are low, the method provided biased estimates and the mean squared error was large.
+The coverage of the confidence intervals was always larger or equal to meta-analysis.
+It outperforms or is equal to classical meta-analysis estimates with respect to coverage, mean squared error and bias if there is publication bias, especially if event rates in the control group are small.
 
@@
 
-A method proposed in \cite{Copas1,Copas2,Copas3} 
-assumes that the given sample of treatment effects and standard errors is a selected part of a larger random sample.
-Selection of studies depends on their effect size and variance.
-Smaller variance is always accompanied by larger selection probability.
-\\
+A method proposed in \cite{Copas1,Copas2,Copas3} assumes that study results are selected based on the specific properties of their effect sizes and variances. \\
 Let $\theta_i$ be the effect size estimate of study $i$. Then
@@
 \begin{align}
-\theta_i \sim N(\mu_i, \sigma_i^2) &
+\theta_i &\sim N(\mu_i, \sigma_i^2) &
 \mu_i \sim N(\theta, \tau^2) \label{eq:population.model}
@@
 
-which is similar to the random-effects meta-analysis setting.
+which is identical to the random-effects meta-analysis setting.
 $\theta$ is the population mean effect, $\sigma_i^2$ the within study variance and $\tau^2$ the between study variance.
-Equations in \eqref{eq:population.model} are termed the \textit{population model}.
-\\
-The \textit{selection model} is defined as follows.
-Suppose a selection of studies with reported ($\neq$ estimated) standard errors $s$ (likely different from $\sigma$).
-Only a proportion of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
-Formally,
-
-\begin{align}
-P(\textrm{select}\given s) &= \Phi(a + b/s) \nonumber %\label{copas.selection1}
+This is termed the \textit{population model}.
+\\
+The \textit{selection model} is defined as follows. Suppose a selection of studies with reported %($\neq$ estimated) 
+standard errors $\se$ (possibly different from $\sigma$).
+Only a proportion of the selection will be published, with the parameter $a$ defining the overall proportion of published studies and $b$ (assumed to be positive) defining how fast this proportion increases with $\se$ becoming smaller.
+Formally, the probability of selection given a reported standard error $\se$ is defined as
+
+\begin{align}
+P(\textrm{select}\given \se) &= \Phi(a + b/\se) \nonumber %\label{copas.selection1}
 \end{align}
@@
 \begin{align}
-z = a + b/s + \delta \nonumber %\label{copas.selection2}
-\end{align}
-
-with $\delta \sim N(0,1)$.
-$z$ is interpreted as the \textit{propensity for selection}.
-It's sign must be positive in order for the study to be selected.
-Thus, the larger $z$, the more likely the study will be selected.
-Also, $a$ is somewhat like to global retention or selection rate for each study, while $b$ decides about the decline of selection probability with increasing $s$.\\
+z = a + b/\se + \delta \nonumber %\label{copas.selection2}
+\end{align}
+
+with $\delta \sim N(0,1)$. $z$ is interpreted as the \textit{propensity for selection}. It is defined that the sign of $z$ must be positive in order for the study to be selected.
+$a$ is some kind of global selection rate for each study and $b$ decides about the decline of selection probability with increasing $\se$.\\
 So far, we have, for a study $i$
@@
 %Every given study $i$ in the meta-analysis has $z_i > 0$. 
-if $\rho_i$ is large and positive and $z_i > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_i$ and $\delta_i$ and thus, the true mean $\mu$ is likely to be overestimated.
+if $\rho_i$ is unequal to zero and positive and $z_i > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\delta_i$ and thus positive $\epsilon_i$, such that the true mean $\mu$ is likely to be overestimated.
 \\
@@
 P(\textrm{select} \given \se_i, \theta_i) = %P(a,b,s,y) = 
-\Phi\big(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i^2}}}\big) \nonumber
-\end{align}
-
-Which again shows that larger $\se_i$ and $\theta_i$ lead to a larger selection probability. It can also be shown that the expected value
+\Phi\bigg(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i^2}}}\bigg) \nonumber
+\end{align}
+
+Which shows that larger $\se_i$ and $\theta_i$ lead to a larger selection probability. It can also be shown that the expected value
 
@@
 
-which shows that the expected value for a study is larger for larger $\sigma$. \\
+increases for larger $\sigma$.\\
 A likelihood for $\theta_i$, conditional on $z>0$ can be formulated to estimate the parameters of the model.
-Regarding $a$ and $b$, there is no way that they can be estimated because the number of missing studies and their effect sizes is not known.
-Instead, fixed values for $a$ and $b$ have to be chosen.
-The nuisance parameter $\sigma_i$ can be replaced by an estimate if the sample size in the studies is large enough. Since
+$a$ and $b$ are not estimated because the number of missing studies and their effect sizes is not known.
+Instead, fixed values for $a$ and $b$ have to be imputed.
+The nuisance parameter $\sigma_i$ can be estimated, as
 
@@
 
-with $c^2 = \lambda(u_i)(u_i + \lambda(u_i))$, we can replace $\sigma_i^2$ by $\hat{\sigma}_i^2 = \frac{1}{1-c_i^2\rho_i^2}$.
-Although one has to evaluate the likelihood for fixed pairs $(a,b)$, one can compare the fit of the model to evaluate which one is more suitable:
-With equation \eqref{eq:copas.expectation}, one can obtain fitted values of $\theta_i$ based on $\se_i$. Also, for two different pairs $(a,b)$, $(a^\star, b^\star)$,
+with $c^2 = \lambda(u_i)(u_i + \lambda(u_i))$. Thus we can replace $\sigma_i^2$ by $\hat{\sigma}_i^2 = \frac{1}{1-c_i^2\rho_i^2}$. \\ 
+With equation \eqref{eq:copas.expectation}, one can obtain fitted values of $\theta_i$ based on $\se_i$ and fixed $a$ and $b$. For two different pairs $(a,b)$, $(a^\star, b^\star)$,
 
@@
 
-and that local departures of $\theta_i$ can be approximated by adding a linear term in $\se_i$ to the expectation of $\theta_i$.
-Thus, to test a pair $(a,b)$, it is sufficient to test $\beta \neq 0$ in
+Local departures of two fitted values of $\theta_i$ can be approximated by adding a linear term in $\se_i$ to the expectation of $\theta_i$.
+Thus, to test a single pair $(a,b)$ (chosen such that $\rho \geq 0$), it is sufficient to test $\beta \neq 0$ in
 
@@
 
-with restriction that $\rho \geq 0$.
-To test some pair $(a,b)$ against the scenario with no selection, we set $a^\star = \infty$ (or $\rho = 0$).
-A likelihood ratio test will give a test statistic to test against $H0 =$ no selection:
+If $\beta \neq 0$, there is still bias in the fitted values.
+To test a pair $(a,b)$ against the scenario with no selection, we set $a^\star = \infty$ (or $\rho = 0$) and $b^\star = 0$.
+A likelihood ratio test will give a test statistic to test against $H0 =$ no selection ($\beta \neq 0$):
 
@@
 
-$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$-value.
-Note that the test is almost equivalent to Egger's small study effect test with $\tau^2 = 0$.
-Thus, although the copas selection model models publication bias, it is dependent on the small study effects to find the most suitable pair $(a,b)$.
-\\
-If one applies the model to a single meta-analysis, a sensitivity analysis is suggested.
-One can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process.
-Selection models are in general not recommended for inference (\eg \citet{selection.assessment}).
-\citet{limitmeta} have shown how the method can be implemented in a simulation for inference purposes.
+$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$\hspace{0.4mm}-value.
+Note that the test is very similar to Egger's small study effect test when $\tau^2 = 0$.\\
+In practice ne can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process, and how the choice of the parameters affect the evidence for remaining publication bias (selection).
+\citet{limitmeta} used the method in a simulation for inference purposes, and have implemented it in the \citet{meta.package}.
 However, in the simulations, the method was outperformed by the regression adjustment method when publication bias was present.
-Especially when event rates in the control group were small and publication bias was strong, bias, mean squared error and coverage was substantially worse.\\
-A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \eqref{eq:copas.small.study} is applied.
-If all obtained $p$-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for modelling, and the standard, classical random effects meta-analysis is retained.
-If none of the $p$-values is above the threshold, a wider range of values for $(a,b)$ is used.
-When some $p$-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the least intense underlying selection model is chosen).\\
-Currently, there is no test to detect miss-specifications in the model itself, the authors themselves have argued that a non-parametric test of the residuals would lack power.
+Especially when event rates in the control group were small and publication bias was strong, bias, mean squared error and coverage was substantially worse.
+Other authors argue that selection models should in general not be used for inference (\eg \citet{selection.assessment}).\\
+The procedure in \citet{limitmeta} is the following: A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \eqref{eq:copas.small.study} is applied.
+If all obtained $p$\hspace{0.4mm}-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for adjustment, and the standard, classical random effects meta-analysis is retained.
+If none of the $p$\hspace{0.4mm}-values is above the threshold, a wider range of values for $(a,b)$ is used.
+When some $p$\hspace{0.4mm}-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the pair of $a$ and $b$ that implies the fewest publication bias is chosen).\\
+Currently, there is no test to detect miss-specifications in the model itself and the authors themselves have argued that a non-parametric test of the residuals would lack power.
 
 \section{Transformation between Effect Measures} \label{sec:transformation.effectsizes}
-Assuming that binary outcomes result from a dichotomization of originally continuous random variables, in this case, the logistic distribution, a transformation from typical binary effect measures to Cohen's $d$ can be achieved \cite[47]{Intro.meta}.
-\\
-Let $\theta$ be a log odds ratio and $s$ it's standard error. Cohen's $d$ and it's variance $s_d^2$ is obtained by
-
-\begin{align}
-d &= \theta \frac{\sqrt{3}}{\pi} & s_d^2 =  \se^2\frac{\sqrt{3}}{\pi} \nonumber
+Assuming that binary outcomes result from a dichotomization of originally continuous random variables, binary outcome measure can be transformed into continuous outcome measures.
+Here, the logistic distribution is used to achieve the transformation from a typical binary effect measures to a std.
+mean difference \cite[47]{Intro.meta}.\\
+Let $\theta$ be a log odds ratio and $\se$ it's standard error. The std. mean difference $d$ and it's variance $\se_d^2$ can be obtained as
+
+\begin{align}
+d &= \theta \frac{\sqrt{3}}{\pi} & \se_d^2 =  \se^2\frac{\sqrt{3}}{\pi} \nonumber
 \end{align}
@@
 The approximation works only well if $e_t$ and $e_c$ are not very small, especially in the case of $s_d^2$.
-Plugging in the observed log odds ratio $\hat{\theta}$ and $\hat{\se}^2$ will give an estimate of Cohen's $d$.\\
-Pearson's correlation can be attained by the formulas (\citet{olkin1985dtor}, \cite[48]{Intro.meta})
+\\
+The Pearson's correlation coefficient can be attained by the formulas (\citet{olkin1985dtor}, \cite[48]{Intro.meta})
 
@@
 \end{align}
-where $a$ is a correction factor if $n_t \neq n_c$. The variance of $r$, $s_r^2$ is computed by
+
+where $a$ is a correction factor if $n_t \neq n_c$. The variance of $r$, $\se_r^2$ is computed by
+
 \begin{align}
@@
 
-Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $s_z^2$ by using
-\begin{align}
-z &= 0.5 \ln\big(\frac{1 + r}{1 - r}\big) & \nonumber
+Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $\se_z^2$ by using
+\begin{align}
+% z &= 0.5 \ln\big(\frac{1 + r}{1 - r}\big) & \nonumber
+z &= \arctan(r) & \nonumber
 s_z^2 &= \frac{1}{n-3}
@@
 % where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom.
-The $p$-value will give the evidence against the null-hypothesis $\beta_0 = 0$.
+The $p$\hspace{0.4mm}-value will give the evidence against the null-hypothesis $\beta_0 = 0$.
 The procedure for $\beta_1$ is equivalent.
@@
 Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
-$1 - F(Q)$ will provide the $p$-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
+$1 - F(Q)$ will provide the $p$\hspace{0.4mm}-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
 % 
@@
 % 
-% A $p$-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
+% A $p$\hspace{0.4mm}-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
 % 
@@
 % If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
-The $p$-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
+The $p$\hspace{0.4mm}-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
 % 
@@
 Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
-The $p$-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
+The $p$\hspace{0.4mm}-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
 % 
@@
 For those values, the quantities above can be calculated and illustrated.
-Values for $\mu$ that have $p$-values over a predefined significance threshold can be used for inference of the effect size.
+Values for $\mu$ that have $p$\hspace{0.4mm}-values over a predefined significance threshold can be used for inference of the effect size.
 % 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Aug  5 12:24:17 2019
+% Thu Aug  8 09:08:07 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Aug  5 12:24:17 2019
+% Thu Aug  8 09:08:08 2019
 \begin{table}[ht]
@@
 {\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Mon Aug  5 12:24:17 2019
+% Thu Aug  8 09:08:08 2019
 \begin{table}[ht]
@@
 
-Using Fisher's $z$ transformation, we can transform all effect sizes of the dataset on the same scale such that they are comparable to each other.
-Thus, as a first step, an exploratory plot of the median effect size and it's dependence on the study sample size can be shown.
-\\
+Meta analyis are based on results of primary studies. Therefore, in a first step, an exploratory plot of the median effect size and it's dependence on the study sample size can be shown. \\
 The absolute value of the median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
-It is clearly visible that the absolute value decreases with increasing sample size, i.e.
-that the effect size is becoming smaller.
-The trend flattens off after $\sim$ sample size = 400 (not shown).
-\\
-The pattern is similar in Figure \ref{effect.samplesize.separated}, where the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std.
-Mean Difference'' are used (the most common measures in the dataset).
-Here, the effect sizes are scaled (mean subtraction and division through standard error) with respect to all other effects of the same measure.
+The medians are calculated separately for efficacy and safety outcomes.
+It is clearly visible that the absolute value of the medians for efficacy decreases with increasing sample size.
+The sample size is much smaller for safety outcomes, such that it is not clear if the median effect sizes of safety outcomes do not decrease with increasing sample size, or the variation between medians is just too large to detect a decrease.\\
+The pattern for efficacy outcomes is the same for all common outcome measures as shown in Figure \ref{effect.samplesize.separated}, where the original effect size measures ``log Odds Ratio'', ``log Risk Ratio'', ``Mean Difference'' and ``Std.
+Mean Difference'' are used (the most common measures in the dataset, ~ 98\%).
 
@@
 \end{knitrout}
-\caption{Median of the absolute $z$-score plotted against the total sample size.}
+\caption{Median of the absolute $z$-score across sample size plotted against the total sample size.}
 \label{z.samplesize}
@@
 \end{knitrout}
-\caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
+\caption{Median of the absolute value of the original effect size across sample size plotted against the total sample size.}
 \label{effect.samplesize.separated}
@@
 
-The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with one-sided small publication bias tests and excess significance tests.
-The direction in which bias is expected is the one on which more significant results are ($p$-value < 0.05, two-sided).
+The meta-analyses fulfilling the criteria from Chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with one-sided small publication bias tests and excess significance tests.
+The direction in which bias is expected is the one on which more significant results of primary studies are (two-sided $p$-value < 0.05).
 The tests are applied on the original effect size measures, since the journal editors and the researchers also base their decisions on them.
-Different tests are applied depending on the outcome being binary or continuous or if the data is only partially available.\\
+Different tests are applied depending on the outcome being binary or continuous or if the data is only partially available (\texttt{outcome.flag} = \texttt{IV}).\\
 Multiple tests are applied in order to compare their results.
 A histogram of $p$-values for each test will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}.\\
-The abbreviations in Figure \ref{fig:test}  are shortly explained with references to chapter \ref{ch:methods}: \\
+The abbreviations in Figure \ref{fig:test}  are shortly explained with references to Chapter \ref{ch:methods}: \\
 ``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}.
@@
 \begin{itemize}
-\item Egger's test, weighted linear regression test described in section \ref{sec:Egger}
-\item Thompson and Sharp's test, weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
-\item Begg and Mazumdar's test, rank test described in section \ref{sec:Begg}
+\item Egger's test, weighted linear regression test described in Section \ref{sec:Egger}
+\item Thompson and Sharp's test, weighted linear regression test adjusted for between-study heterogeneity, Section \ref{sec:Thompson}
+\item Begg and Mazumdar's test, rank test described in Section \ref{sec:Begg}
 \end{itemize}
@@
 \begin{itemize}
-\item Harbord's test, likelihood score based test (section \ref{sec:Harbord})
-\item Peter's test, weighted linear regression with inverse sample size as explanatory variable described in section \ref{sec:Peter}
-\item R\"ucker's test, test based on the arcsine transformation of proportions, in combination with Thompson and Sharp's regression test (section \ref{sec:Rucker})
-\item Schwarzer's test, rank based test using the expected event counts computed with the hypergeometric distribution (section \ref{sec:Schwarzer})
+\item Harbord's test, likelihood score based test (Section \ref{sec:Harbord})
+\item Peter's test, weighted linear regression with inverse sample size as explanatory variable described in Section \ref{sec:Peter}
+\item R\"ucker's test, test based on the arcsine transformation of proportions, in combination with Thompson and Sharp's regression test (Section \ref{sec:Rucker})
+\item Schwarzer's test, rank based test using the expected event counts computed with the hypergeometric distribution (Section \ref{sec:Schwarzer})
 \end{itemize}
@@
 %Agreement table -> Chunck 1
-The histograms in Figure \ref{fig:test} show that the tests do not coherently find evidence for publication bias in the dataset.
-The $p$-values of excess significance and Schwarzer's test are rather uniformly distributed.
-Notably, excess significance test, Schwarzer's test and rank tests have been shown to lack power.
+The histograms in Figure \ref{fig:test} show that the tests mostly find evidence for publication bias in the dataset.
+The $p$-values of excess significance and Schwarzer's test are rather uniformly distributed, but notably, excess significance test, Schwarzer's test and rank tests have been shown to lack statistical power.
 The tests that are more suitable (regression based tests in general) all have proportions of significant $p$-values ($p$ > 0.1) clearly above 10 \% which would be the expected false positive rate.\\
@@
 Other tests are specially constructed to adjust for between study heterogeneity (Thompson and Sharp's test and R\"ucker's test).
-It can be seen that these tests find a smaller proportion of significant results in Figure \ref{fig:test}.
+These tests find a smaller proportion of significant results in Figure \ref{fig:test}.
 However, this is also due to application to meta-analyses with no between-study heterogeneity, where the methods lack statistical power.
@@
 The moderate decrease indicates however that the previous restriction to meta-analyses with $I^2 < 0.5$ is sufficient to remove meta-analyses with large heterogeneity and that the test results are not heavily influenced by unaccounted between-study heterogeneity.\\
-The $p$-values of tests can be summarized by computing their harmonic mean.
+The $p$-values of tests can be summarized by computing their harmonic mean \citep{harmonic.p}.
 In the case of binary tests, the $p$-values of R\"ucker's, Peters, Harbord's, Schwarzer's and excess significance tests are used, in the case of continuous and \texttt{outcome.flag} = \texttt{IV} outcomes, Egger's, Thompson and Sharp's, Begg and Mazumdar's and excess significance tests are used.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug  6 17:32:17 2019
+% Thu Aug  8 11:45:37 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug  6 17:32:30 2019
+% Thu Aug  8 11:45:51 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug  6 17:32:32 2019
+% Thu Aug  8 11:45:52 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug  6 17:32:40 2019
+% Thu Aug  8 11:46:01 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug  6 17:32:41 2019
+% Thu Aug  8 11:46:01 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug  6 17:32:43 2019
+% Thu Aug  8 11:46:03 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug  6 17:32:45 2019
+% Thu Aug  8 11:46:05 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug  6 17:32:48 2019
+% Thu Aug  8 11:46:08 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug  6 17:32:49 2019
+% Thu Aug  8 11:46:10 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug  6 17:33:26 2019
+% Thu Aug  8 11:46:51 2019
 \begin{table}[ht]

### 2019-08-09 report/chapter02.Rnw
results and methods correction

@@
 Using a truncated Taylor series expansion, one can obtain the partial derivative after $\tau^2$, which is a reasonable choice for $\tau_0^2$.
+Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{theta}$, we can update $F(\tau^2)$ and check convergence to zero.
 \\
-%Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{theta}$, we can update $F(\tau^2)$ and check convergence to zero. \\
 The estimation of $\tau^2$ is accompanied by uncertainty.
 A common procedure is to test if it is there is significant heterogeneity between the studies \cite[109]{Intro.meta}.
-Compute $Q$, as given in \eqref{eq:Q.heterogeneity}, based on one of the estimators of $\tau^2$.
+For this, $Q$ has to be computed as given in \eqref{eq:Q.heterogeneity}.
 It is assumed that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equally distributed effect sizes.
 Thus, the expected value of $Q$ is $n-1$, and the excess dispersion is $Q - n + 1$.
-The $p$-value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
+The $p$\hspace{0.4mm}-value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
 = $n-1$.
 \\
-An advantage of the $\tau^2$ is that it is directly linked to the variability in the data.
-Additionally, one can use the $I^2$ statistic to see what portion the between study variance has of the overall variance.
+$\tau^2$ is  is directly linked to the variability in the data.
+The $I^2$ statistic of excess/total dispersion can be used alternatively to assess the extent of additional variance to the variances of the primary study estimates.
 It is computed as
@@
 
-A method proposed in \cite{Copas1,Copas2,Copas3} 
-assumes that the given sample of treatment effects and standard errors is a selected part of a larger random sample.
-Selection of studies depends on their effect size and variance.
-Smaller variance is always accompanied by larger selection probability.
+A method proposed in \cite{Copas1,Copas2,Copas3} assumes that study results are selected based on the specific properties of their effect sizes and variances. \\
+Let $\theta_i$ be the effect size estimate of study $i$. Then
+
+\begin{align}
+\theta_i &\sim N(\mu_i, \sigma_i^2) &
+\mu_i \sim N(\theta, \tau^2) \label{eq:population.model}
+\end{align}
+
+which is identical to the random-effects meta-analysis setting.
+$\theta$ is the population mean effect, $\sigma_i^2$ the within study variance and $\tau^2$ the between study variance.
+This is termed the \textit{population model}.
 \\
-Let $\theta_i$ be the effect size estimate of study $i$. Then
-
-\begin{align}
-\theta_i \sim N(\mu_i, \sigma_i^2) &
-\mu_i \sim N(\theta, \tau^2) \label{eq:population.model}
-\end{align}
-
-which is similar to the random-effects meta-analysis setting.
-$\theta$ is the population mean effect, $\sigma_i^2$ the within study variance and $\tau^2$ the between study variance.
-Equations in \eqref{eq:population.model} are termed the \textit{population model}.
-\\
-The \textit{selection model} is defined as follows.
-Suppose a selection of studies with reported ($\neq$ estimated) standard errors $s$ (likely different from $\sigma$).
-Only a proportion of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
-Formally,
-
-\begin{align}
-P(\textrm{select}\given s) &= \Phi(a + b/s) \nonumber %\label{copas.selection1}
+The \textit{selection model} is defined as follows. Suppose a selection of studies with reported %($\neq$ estimated) 
+standard errors $\se$ (possibly different from $\sigma$).
+Only a proportion of the selection will be published, with the parameter $a$ defining the overall proportion of published studies and $b$ (assumed to be positive) defining how fast this proportion increases with $\se$ becoming smaller.
+Formally, the probability of selection given a reported standard error $\se$ is defined as
+
+\begin{align}
+P(\textrm{select}\given \se) &= \Phi(a + b/\se) \nonumber %\label{copas.selection1}
 \end{align}

### 2019-08-09 report/chapter03.Rnw
results and methods correction

@@
 The dataset consists of \Sexpr{length(unique(data$id))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(data$study.name))} studies and \Sexpr{dim(data)[1]} results.
-The results all stem from comparisons of a healthcare interventions or treatments to a reference.
-The reference may be a placebo control group or a other intervention or treatment.
+A result is a outcome of a study, thus studies can contribute multiple results.
+The studies too a very large extent randomized and investigate the effects of healthcare and medical interventions and treatments.
+The reference to the treatment may be a placebo control or a different intervention or treatment.
 A result can not only be about efficacy of the treatments, but also about safety (adverse effects).\\
+It will be continued with an example form the dataset.
 In Table \ref{barbiturate.row}, two results from a systematic review about barbiturates are shown as they are given in the dataset.

### 2019-08-09 report/chapter04.Rnw
results and methods correction

@@
 
-<<'Data03', echo=FALSE, warning=FALSE>>= 
+<<'Data03', echo=FALSE, warning=FALSE, cache = TRUE>>= 
 #Load data:
@@
 <<echo=FALSE, warning=FALSE, message = FALSE>>=
-p.samplesize.z  <- data.ext2 %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% ungroup() %>%
+p.samplesize.z  <- data.ext2 %>% 
+  filter(total1 + total2 > 15 & total1 + total2 < 300) %>% ungroup() %>%
   mutate(std.z = abs(z), sample.size = total1 + total2) %>%
-  group_by(sample.size) %>%
+  group_by(sample.size, outcome.desired) %>%
   summarize(median.effect = median(std.z, na.rm = T)) %>%
-  ggplot(aes(x = sample.size, y = median.effect)) + geom_point(size = 0.8) +
+  ggplot(aes(x = sample.size, y = median.effect)) + 
+  geom_point(size = 0.8) + facet_wrap(~outcome.desired) +
   theme_bw() + xlab("sample size") + ylab("median absolute z-score") +
@@
 
-labels <- c(RR = "Risk Ratio", OR = "Odds Ratio", MD = "Mean Difference", SMD = "Std. Mean Difference")
-
-p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>%
+labels <- c(RR = "log Risk Ratio", OR = "log Odds Ratio", MD = "Mean Difference", SMD = "Std. Mean Difference")
+
+p.samplesize.effect.sep <- data %>% 
+  filter(total1 + total2 > 15 & total1 + total2 < 300) %>%
+  filter(outcome.desired == "efficacy") %>% 
   filter(id != "CD001293") %>%  #filter out this crazy review..
@@
   group_by(outcome.measure.merged) %>%
-  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
+  mutate(sample.size = total1 + total2, 
+         scaled.effect = case_when(outcome.measure.merged == "RR" ~ abs(log(effect)),
+                                   outcome.measure.merged == "OR" ~ abs(log(effect)),
+                                   TRUE ~ abs(effect))) %>% 
   group_by(sample.size, outcome.measure.merged) %>%
@@
   ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.merged)) + geom_point(size = .5) + facet_wrap(~outcome.measure.merged, scales = "free", labeller = labeller(outcome.measure.merged = labels)) +
-  theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size") +
+  theme_bw() + xlab("sample size") + ylab("median absolute effect size") +
   xlim(c(15, 300)) +
@@
 @
-\caption{Median of the absolute $z$-score plotted against the total sample size.}
+\caption{Median of the absolute $z$-score across sample size plotted against the total sample size.}
 \label{z.samplesize}
@@
 @
-\caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
+\caption{Median of the absolute value of the original effect size across sample size plotted against the total sample size.}
 \label{effect.samplesize.separated}
@@
 
-labels <- c(pval1.harbord = "Harbord", pval1.peter = "Peter", pval1.rucker = "Rucker (thompson)", pval1.rucker.linreg = "Rucker (egger)", pval1.schwarzer = "Schwarzer", pval1.d.tes = "Excess Significance")
+labels <- c(pval1.harbord = "Harbord", pval1.peter = "Peter", pval1.rucker = "Rucker (Thompson)", pval1.rucker.linreg = "Rucker (Egger)", pval1.schwarzer = "Schwarzer", pval1.d.tes = "Excess significance")
 
@@
          upper.panel=panel.pts.new, lower.panel=panel.cor, 
-         cex.labels = 1, cex = .25, cex.cor = 2, pch = 1,
+         cex.labels = 2, cex = .25, cex.cor = 2, pch = 1,
          text.panel=panel.txt, cor.method = "spearman")
@@
 This means that the excess significance test finds less evidence in cases when both $p$-values are small and more evidence when both $p$-values are large, on average.\\
-The confidence intervals from Figure \ref{fig:mean.diff.test} can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests.
-This suggests that additionally to the bias correspondence between the tests is not very good in general.
+However, the confidence intervals from Figure \ref{fig:mean.diff.test} are very large. This suggests that additionally to the bias correspondence between the tests is not very good in general.
 
@@
 It displays the percentage of meta-analyses with a certain number of significant test results.
-For both outcome types, there is only marginal agreement, very few cases are significant in any test.
+Very few meta-analyses are give a significant result, independently of the test applied.
 Around 67\% of the dataset is not significant, no matter which test is used.
-When only using small study effect tests, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of \texttt{IV} and continuous outcome tests had at least one significant result.
-After applying the Bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\% for binary and \Sexpr{mean.min.else.b}\% for continuous and \texttt{IV} outcomes.
+When leaving away the excess significance test, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of \texttt{IV} and continuous outcome tests had at least one significant result.
+%After applying the Bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\% for binary and \Sexpr{mean.min.else.b}\% for continuous and \texttt{IV} outcomes. 
 To compare significant findings for small study effect tests and excess significance tests, Harbord's or Egger's test results are compared with excess significance tests.
@@
 
-The precise proportions of agreement are provided in table \ref{test.agreement}.
-We see that only in few cases when excess significance test indicates statistical significance, small study effect tests do so.
-Correspondence between excess significance tests and small study effects thus is considered rather random.
-Linear regression based tests agree more often with other linear regression based tests, and agreement between small study effect tests is in general well above 60 \% (at best, 95 \% test agreement in significance for \texttt{IV} \texttt{outcome.flag}).
+The precise proportions of agreement are provided in table \ref{test.agreement}. %Correspondence between excess significance tests and small study effects thus is considered rather random. 
+Linear regression based tests agree more often with other linear regression based tests, and agreement between small study effect tests is in general well above 60 \% (at best, 95\% test agreement in significance for \texttt{IV} \texttt{outcome.flag}).
+The agreement on statistical significance between small study effect tests and excess significance tests ranges from 64\% to 4\% (for \texttt{IV} and rank tests).
 
@@
 When comparing to unadjusted effects, fixed or random effects meta-analysis estimates are used as references\\
-Figure \ref{fig:adjustment.reg} displays the difference $\delta$ between the estimated meta-analysis treatment effect and the regression adjusted treatment effect \ref{sec:regression.adjustment}, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
-The absolute value $|\hat{\theta}_M|$ is taken and $\hat{\theta}_\textrm{Adj.}$ is negative if the signs change in the original $\theta$.
+Figure \ref{fig:adjustment.reg} displays the difference between the estimated meta-analysis treatment effect and the regression adjusted treatment effect \ref{sec:regression.adjustment}, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
+The absolute value $|\hat{\theta}_M|$ is taken and $\hat{\theta}_\textrm{Adj.}$ is negative if it's sign is different from the sign of the original $\theta$.
 Thus, a positive difference indicates a reduction of the original effect size, and the magnitude of the difference indicates the extent of the adjustment.
 \\
-Additionally, the test statistic of heterogeneity adjusted publication bias tests (R\"ucker's and Thompson's test) are displayed with green color.
-Test statitics smaller $< 1$ (light green colored) are equivalent to no evidence for publication test, test statistics between one and two to weak evidence, and above two they indicate evidence for publication bias (dark green).
-An adjusted effect with evidence for publication bias can be regarded as a more realistic estimate of treatment efficacy.
+Additionally, the test statistics of heterogeneity adjusted publication bias tests (R\"ucker's and Thompson's test) are displayed with green color.
+Test statitics smaller $< 1$ (light green colored) are equivalent to no evidence for publication bias, test statistics between one and two to weak evidence, and above two they indicate evidence for publication bias (dark green).
+An adjusted effect with evidence for publication bias can be regarded as a more realistic estimate of the treatment effect.
 Some very large and very small differences have been omitted in the $z$-score and std.
 mean difference histograms; they are shown in Table \ref{missing.differences}.
+\\
+Most often, adjustment leads to a reduction of overall treatment effect estimates, which can be seen by the size of the bins on the positive side of the histograms.
+Adjustment is stronger when random effects meta-analysis is used as reference, because it gives larger weights to small studies.\\
+Contrary to naive expectation, we see cases with large negative adjustment, but no evidence for small study effects.
+This is because the linear regression parameter estimates are large, but estimated with high uncertainty, such that there will be few evidence for small study effects (publication bias), but nonetheless, the adjustment will be large.
+It is recommended to use the methods only in cases where there is clear evidence for publication bias.
+The color legend in Figure \ref{fig:adjustment.reg} thus gives a sense of the confidence that is put into the adjusted effects.
 \\
@@
 
-Most often, adjustment leads to a reduction of overall treatment effect estimates, because the bins on the positive side of the histograms are larger.
-Adjustment is stronger when random effects meta-analysis is used as reference, because it gives larger weights to small studies.\\
-Contrary to naive expectation, we see cases with large adjustment, but no evidence for small study effects.
-This is because the linear regression parameter estimates are large, but estimated with high uncertainty, such that there will be few evidence for small study effects (publication bias), but nonetheless, the adjustment will be large.
-The authors that developed the methods also recommend to use the methods in cases where there is clear evidence for publication bias.
-The color legend in Figure \ref{fig:adjustment.reg} thus gives a sense of confidence that there is in the credibility of the adjustment.
-\\
 Additionally, some meta-analyses with positively adjusted, larger overall treatment effects after adjustment (left side of the histogram) have also evidence for publication bias (remember that publication bias was defined as the tendency of small studies to show \textit{larger} results).
-This is not a wrong result, because the effects and their variances have been transformed, and it is possible that the shape of the funnel plot changes upon transformation; Figure \ref{fig:funnel.plot.change} shows this for illustrative purposes.
-From the left to the right, the funnel plot is shown for mean differences (the original measure), standardized mean differences and Fisher's $z$ scores.
-This is quite the most extreme case, with three different effects of adjustment, depending on outcome measure; there is no change with mean differences, reduction of effect sizes with std.
+However, this is not wrong, because the effects and their variances have been transformed, and it is possible that the shape of the funnel plot changes upon transformation; Figure \ref{fig:funnel.plot.change} shows this for illustrative purposes.
+From the left to the right, the funnel plot is shown for mean differences (the original measure), standardized mean differences and Fisher's $z$ scores; there is no change upon adjustment using mean differences (blue line), reduction of the effect with std.
 mean differences and increase with Fisher's $z$ transformed correlation.
@@
 One effect of the Fisher's $z$-transformation is that the effect sizes are bounded on $[-1,1]$, and thus, very large effect sizes will influence the fit of the linear regression less than for example in std.
-mean differences which are not bounded.
+mean differences, which are not bounded.
 In contrast, the variance of the correlation is directly tied to the sample size, which makes it a suitable proxy for study size (variance of the mean difference is in contrast strongly influenced by the standard deviations).
@@
 Figure \ref{fig:adjustment.copas} shows the same for effect sizes adjusted by Copas; Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
-Therefore, the effect of adjustment by Copas can be seen when comparing adjusted with random effects meta analysis estimates.
+Therefore, the effect of adjustment by Copas can better be seen when comparing adjusted with random effects meta analysis estimates.
 Again, we clearly see that more effect sizes are adjusted downwards.
@@
 \\
-
-\begin{figure}
-<<echo=FALSE, fig.height = 4, warning=FALSE>>=
-grid.arrange(diff.z.ranef.copas, diff.d.ranef.copas, ncol = 2)
-@
-\caption{Histogram of the treatment effect differences between meta-analysis and Copas adjusted meta-analysis.
-Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes.
-The bins are centered at zero and binwidth is equal to 0.1.
-Deeper green color indicates more evidence for small study effects.}
-\label{fig:adjustment.copas}
-\end{figure}
-
 Table \ref{adjustment.difference} shows quantiles and means for the various differences and the overall proportion of downward adjusted effect sizes.
@@
 mean difference is reduced by 0.39 compared to fixed effects estimates in 5\% or \Sexpr{floor(length(!is.na(meta.f$est.d.reg))*0.05)} meta-analyses (or increased by 0.24).
+
+\begin{figure}
+<<echo=FALSE, fig.height = 4, warning=FALSE>>=
+grid.arrange(diff.z.ranef.copas, diff.d.ranef.copas, ncol = 2)
+@
+\caption{Histogram of the treatment effect differences between meta-analysis and Copas adjusted meta-analysis.
+Negative differences indicate greater adjusted effect sizes than meta-analysis effect sizes.
+The bins are centered at zero and binwidth is equal to 0.1.
+Deeper green color indicates more evidence for small study effects.}
+\label{fig:adjustment.copas}
+\end{figure}
 

### 2019-08-09 report/chapter05.Rnw
results and methods correction

@@
 
-<<echo=FALSE, warning=FALSE>>= 
+<<echo=FALSE, warning=FALSE, cache = TRUE>>= 
 #Load data:

### 2019-08-13 report/MSc_Report.tex
Corrected version, discussion, introduction

@@
 \\
-There is extensive literature on publication bias in meta-analyses, e.g. (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02},
+There is extensive literature on publication bias in meta-analyses, \eg (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02},
 \citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}).
-The authors agree on that the exclusion of unpublished results in meta-analyses is responsible for overestimation of treatment effects.
-Although there are policies that make it mandatory to make all study results publicly accessible \citep{fda}, it is not clear if the situation has improved yet.\\
+The authors agree on that the exclusion of unpublished results in meta-analyses can lead to overestimation of treatment effects (\eg \citet{Egger}).
+Although there are policies that make it mandatory to make all study results publicly accessible \citep{fda}, it is not clear if the situation has improved yet.
+There are also notable efforts from both journals \citep{Abbasi.2004} and researchers (?) in the same direction.\\
 There are multiple ways to assess the amount of publication bias.
@@
 \\
-A third way is to assess the so-called small study effect in a meta-analysis, that is, smaller studies sometimes showing different, often larger treatment effects than large ones (cite sb).
-Importantly, this method does not assess publication bias directly.
-But the estimation of small study effects is oftentimes the most efficient way to investigate publication bias in a large number of meta-analyses.
-However, evidence for small study effects can oftentimes be interpreted as evidence for publication bias \citep{Egger}, as this is the most likely cause, even though there may also be other explanations.
-The underlying rationale is that journal editors are guided by two simple rules (\citet{excess.significance}, \citet{ioannidis.2019}):
-\begin{itemize}
-\item Publish new and trend-setting positive findings that lead to many citations, increasing the journal impact factor (JIF).
-Statistically significant effects are oftentimes interpreted as confirming an effect.
-\item Publish large trials that are likely to set the standard for a given scientific question, again to increase the JIF.
-\end{itemize}
-
-Publication bias thus leads to larger effects in studies with larger uncertainities, in order for them to be statistically significant.
+A third way is to assess the so-called small study effect in a meta-analysis, that is, smaller studies sometimes showing different, often larger treatment effects than large ones.
+The rationale is that studies with larger standard errors have to have larger effects in order to be significant.
+The estimation of small study effects is an efficient way to investigate publication bias in a large number of meta-analyses.
+Although there are other reasons for small study effects as well, evidence for small study effects can oftentimes be interpreted as evidence for publication bias \citep{Egger}, as it is the most likely cause.
+\\
+% 
+% The underlying rationale is that journal editors are guided by two simple rules (\citet{excess.significance}, \citet{ioannidis.2019}): 
+% \begin{itemize}
+% \item Publish new and trend-setting positive findings that lead to many citations, increasing the journal impact factor (JIF).
+Statistical significance is oftentimes interpreted as confirmation for treatment efficacy.
+% \item Publish large trials that are likely to set the standard for a given scientific question, again to increase the JIF.
+% \end{itemize}
+% 
+% Publication bias thus leads to larger effects in studies with larger uncertainities, in order for them to be statistically significant. 
 A funnel plot \citep{funnel.plot} allows visual inspection of small study effects by plotting the effects against their standard error.
@@
 
-The purpose of a funnel plot is to visualise if an how the estimated treatment effects converge to a common ``real'' treatment effect value (here, the weighted mean treatment effect with weights = inverse variances).
-This is also shown by the triangle depicted by the dotted line (the spire is at the weighted mean).
-\\
+The purpose of a funnel plot is to visualise if the findings of the studies disperse on both sides of the combined ``true'' effect or if they accumulate with increasing standard error on one particular side.\\
 We see that while the studies in the meta-analysis on the left are not symmetrically distributed, but rather accumulate at the left side, they seem to be more evenly distributed in the left triangle.
@@
 By extensive literature scrutinization, they try to circumvent the issue of publication bias.
-They do not apply funnel plot asymmetry tests to analyse publication bias.
+%They do not apply funnel plot asymmetry tests to analyse publication bias.
 Earlier research however suggests that the efforts are only partially succesful, and that there still is publication bias within the reviews (\citet{Egger}, \citet{Ioannidis2007}, \citet{kicinsky}, \citet{vanAert.2019}).
@@
 Consequently, the tests above will tend to reject the null-hypothesis too often, \ie report false positives.\\
-Instead of taking the standard error $\se$ as explanatory variable $x$ as in Egger's Test, the inverse of the total sample size is used.
+Instead of taking the standard error $\se$ as explanatory variable $x$ as in Egger's test, the inverse of the total sample size is used.
 Additionally, the variances $\se_i^2$ are used as weights.
@@
 \\
+The method will give less false positives than Egger's test, but will be more imprecise, because total sample size is not a very good approximation for statistical power (the overall rate of events in both groups plays an important role as well).
 
@@
 \subsection{Excess Significance Test} \label{sec:excess.significance}
+Publication bias does not need to be accompained by small study effects.
+In the absence of any treatment effect, significant effects could be included in a meta-analysis on both directions of treatment effects (\ie large \textit{and} small effects) are published.
+Also, the afore-mentioned methods do not use statistical significance directly to investigate publication bias.
+Thus, a different test is introduced.
+\\
 \citet{excess.significance} developed an exploratory test to detect if the proportion of significant findings is larger than expected. 
@@
 \section{Cochrane Systematic Reviews}
-The Cochrane Group has specialized on systematic reviews in clinical science.
-Certain knowledge of standards and principles of the Cochrane Group may help to assess the quality and the properties of the dataset.
+Cochrane has specialized on systematic reviews in clinical science.
+Certain knowledge of standards and principles of the organization may help to assess the quality and the properties of the dataset.
 The following information stems from the Cochrane Handbook for Systematic Reviews \citep{cochrane.handbook}.
@@
 \\
-In order to avoid potential conflicts of interests, there is a code of conduct that all entities of the Cochrane Organization have to agree on: conflicts of interest must be disclosed and possibly be forwarded to the Cochrane Center, and participation of review authors in the studies used have to be acknowledged.
+In order to avoid potential conflicts of interests, there is a code of conduct that all entities of Cochrane have to agree on: conflicts of interest must be disclosed and possibly be forwarded to the Cochrane Center, and participation of review authors in the studies used have to be acknowledged.
 Additionally, a Steering Group publishes a report of potential conflicts of interests based on information about external funding of Cochrane Groups.
@@
 In addition to inclusion of new evidence in a field, the revision and maintenance process may as well includes change in analysis methods.
-This can reflect some advance in clinical science as for example new information about important subgroups, as well as new methods for conducting a Cochrane Review.
+This can reflect some advance in clinical science as for example new information about important subgroups, as well as new methods for conducting a Cochrane review.
 However, there are no clear guidelines and the Cochrane Groups are free in the rate and extent of up-dating their reviews.
@@
 The type of study is an important eligibility criterium.
-The Cochrane Collaboration focuses ``primarily on randomized controlled trials'', and also, the methods of study identification in literature search are focused on randomized trials.
+Cochrane focuses ``primarily on randomized controlled trials'', and also, the methods of study identification in literature search are focused on randomized trials.
 Furthermore, study characteristics such as blinding of study operators with respect to treatment and cluster-randomizing might be additional eligibility criteria which have to be chosen by the review authors.
@@
 \item Grey Literature Databases.
-Approximately 10\% of the results in the Cochrane Database stems from conference abstracts and other grey literature.
+Approximately 10\% of the results in the Cochrane Library stems from conference abstracts and other grey literature.
 The Institute for Scientific and Technical Information in France provides access to entries of the previously closed System for Information on Grey Literature database of the European Association for Grey Literature Exploitation).
@@
 The dataset consists of 6354 systematic reviews from the Cochrane Library with 70662 studies and 744720 results.
-The results all stem from comparisons of a healthcare interventions or treatments to a reference.
-The reference may be a placebo control group or a other intervention or treatment.
+A result is a outcome of a study, thus studies can contribute multiple results.
+The studies too a very large extent randomized and investigate the effects of healthcare and medical interventions and treatments.
+The reference to the treatment may be a placebo control or a different intervention or treatment.
 A result can not only be about efficacy of the treatments, but also about safety (adverse effects).\\
+It will be continued with an example form the dataset.
 In Table \ref{barbiturate.row}, two results from a systematic review about barbiturates are shown as they are given in the dataset.
@@
 The studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis.
-This distinction is also used by the Cochrane Organization itself, \ie the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
+This distinction is also used by Cochrane, \ie the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
 The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.
@@
 Meta-analysis groups within a review were obtained by grouping by comparison, outcome and subgroup.
-The last step is optional, and the Cochrane groups do also meta-analysis without taking into account subgroups.
+The last step is optional, and the Cochrane Groups do also meta-analysis without taking into account subgroups.
 Subgroups are often specifications of treatment, \eg the form of the medication or the protocol.
 Thus, using the subgroups should increase the within-study homogeneity.
-However, the Cochrane Organisation disencourages meta-analyses based on subgroups only, because subgroups are often set up after the collection of the data analysis.
+However, the Cochrane disencourages meta-analyses based on subgroups only, because subgroups are often set up after the collection of the data analysis.
 Since the main interest of this study is not to precisely assess the efficacy of treatments, but the interest is merely on systematic differences between single studies investigating the same scientific question and not in the effect per se, it has been decided that the increase in precision is worthwhile the loss of a number of studies.
@@
 When one subgroup has substantially different real treatment effects, and the specific properties influence study size, publication bias assessment fails.
-Subgroups are not indicated in 50.8\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane review groups did.
+Subgroups are not indicated in 50.8\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane Review Groups did.
 The methods described in the methods chapter \ref{ch:methods} most often apply directly to the algorithms used in \texttt{meta} and \texttt{metafor}. \\
@@
 \subsection{Publication Bias Test Consistency}
-It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects for the same meta-analyses.
-A simple method to check the consistency of test results is to compare scatterplots and empirical Spearman correlations between the test statistics.
+In a next step, the consistency between the tests is examined, \eg if the tests identify significant publication bias in the same meta-analyses.
+There is, so far, no agreement in the literature about which of the methods are to prefer, even non regression based tests have generally low power.
+The following analysis will reveal if there are \eg testing methods that are coming to identical results and are thus compatible/interchangeable.
+\\
+A simple method to check the consistency of test results is to compare scatterplots and Spearman correlations between the test statistics.
 This is done in Figure \ref{fig:test.agreement}.
-Here, there is no separation between \texttt{IV} and continuous outcomes.
+Here, there is no separation between \texttt{IV} and continuous outcomes because the same publication bias tests have been used.
 The upper left rectangle is displaying binary outcome results and the lower right continuous and \texttt{IV} outcomes results.
 Also, the $I^2$ statistic is included.
-Since no approximately normally distributed test statistic is used for excess significance tests, it is not shown here
+Since no normally distributed test statistic under the null hypothesis is used for excess significance tests, it is not shown here.
 
@@
 \end{knitrout}
-\caption{Pairs-plot for test statistics of small study effect and excess significance.
+\caption{Pairs-plot for test statistics of small study effects.
 The lower panel gives the Spearman correlations for the different test statistics, and the upper panel displays a scatterplot.
@@
 
-The observed patterns on the scatterplots differ, and some small study effect test statistics do align better than others.
+The observed patterns on the scatterplots differ, and some methods do align better than others.
 Regression based tests as Egger and Thompsons test which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients.
-Continuous and\texttt{IV} outcome type tests align more closely than binary outcome tests.
+Continuous and \texttt{IV} outcome type tests align more closely than binary outcome tests.
 While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics.\\
@@
 \begin{itemize}
-\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
-\item For Egger's and excess significance tests
-\item For Harbord's and R\"ucker's tests
-\item For Harbord's and excess significance tests
+\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors.
+\item For Egger's and excess significance tests.
+\item For Harbord's and R\"ucker's tests.
+\item For Harbord's and excess significance tests.
 \end{itemize}
@@
 It displays the percentage of meta-analyses with a certain number of significant test results.
-For both outcome types, there is only marginal agreement, very few cases are significant in any test.
+Very few meta-analyses are give a significant result, independently of the test applied.
 Around 67\% of the dataset is not significant, no matter which test is used.
-When only using small study effect tests, 29.5\% of binary outcome tests and 31.9\% of \texttt{IV} and continuous outcome tests had at least one significant result.
-After applying the Bonferroni correction for multiple testing, this shrinks to 12.3\% for binary and 14.4\% for continuous and \texttt{IV} outcomes.
-To compare significant findings for small study effect tests and excess significance tests, Harbord's or Egger's test results are compared with excess significance tests.
-24.1\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 28.4\% for continuous and \texttt{IV} outcomes.
-The numbers change to 13.9\% for binary outcomes and 18.1\% for continuous and \texttt{IV} outcomes after applying the Bonferroni correction.
-5.1\% have significant Harbord's test result and significant excess significance test result  (2.3\% with Bonferroni).
-Of the continuous outcomes, we have 3.9\% with Egger's test and 1.3\% with Bonferroni correction.
 \\
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 11:45:37 2019
+% Tue Aug 13 10:24:59 2019
 \begin{table}[ht]
@@
 
-The precise proportions of agreement are provided in table \ref{test.agreement}.
-We see that only in few cases when excess significance test indicates statistical significance, small study effect tests do so.
-Correspondence between excess significance tests and small study effects thus is considered rather random.
-Linear regression based tests agree more often with other linear regression based tests, and agreement between small study effect tests is in general well above 60 \% (at best, 95 \% test agreement in significance for \texttt{IV} \texttt{outcome.flag}).
+When leaving away the excess significance test, 29.5\% of binary outcome tests and 31.9\% of \texttt{IV} and continuous outcome tests had at least one significant result. 
+%After applying the Bonferroni correction for multiple testing, this shrinks to mean.min.bin.b\% for binary and mean.min.else.b\% for continuous and \texttt{IV} outcomes. 
+To compare significant findings for small study effect tests and excess significance tests, Harbord's or Egger's test results are compared with excess significance tests.
+24.1\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 28.4\% for continuous and \texttt{IV} outcomes.
+The numbers change to 13.9\% for binary outcomes and 18.1\% for continuous and \texttt{IV} outcomes after applying the Bonferroni correction.
+5.1\% have significant Harbord's test result and significant excess significance test result  (2.3\% with Bonferroni).
+Of the continuous outcomes, we have 3.9\% with Egger's test and 1.3\% with Bonferroni correction.
+\\
+The precise proportions of agreement in significance/non-significance are provided in Table \ref{test.agreement}.
+A separate column provides the proportion of significant results of the test with fewer significant results that are also significant using the test with more significant results.
+Linear regression based tests agree more often with other linear regression based tests, and agreement between small study effect tests is in general well above 60 \% (at best, 95\% test agreement in significance for \texttt{IV} \texttt{outcome.flag}).
+The agreement on statistical significance between small study effect tests and excess significance tests ranges from 64\% to 4\% (for \texttt{IV} and rank tests).
+Note that these numbers are difficult to interpret because there are substantially less significant results of the excess significance tests, and thus, a agreement of 100\% still does not indicate perfect compatibility/replaceability of the tests.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 11:45:37 2019
+% Tue Aug 13 10:24:59 2019
 \begin{table}[ht]
@@
 \endgroup
-\caption{Overall proportion of agreement if significant or unsignificant, and for significance only.
-Horizontal lines separate binary, continuous and IV outcomes (order as in table).
-The reference significance test is the one with more significant results.}
+\caption{Overall proportion of agreement if publication bias is significant or non-significant, and if significant only.
+When comparing agreement if significant only, the proportion of the test with fewer significant results that is significant with another test as well is shown.}
 \label{test.agreement}
@@
 When comparing to unadjusted effects, fixed or random effects meta-analysis estimates are used as references\\
-Figure \ref{fig:adjustment.reg} displays the difference $\delta$ between the estimated meta-analysis treatment effect and the regression adjusted treatment effect \ref{sec:regression.adjustment}, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
-The absolute value $|\hat{\theta}_M|$ is taken and $\hat{\theta}_\textrm{Adj.}$ is negative if the signs change in the original $\theta$.
+Figure \ref{fig:adjustment.reg} displays the difference between the estimated meta-analysis treatment effect and the regression adjusted treatment effect \ref{sec:regression.adjustment}, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
+The absolute value $|\hat{\theta}_M|$ is taken and $\hat{\theta}_\textrm{Adj.}$ is negative if it's sign is different from the sign of the original $\hat{\theta}_M$.
 Thus, a positive difference indicates a reduction of the original effect size, and the magnitude of the difference indicates the extent of the adjustment.
 \\
-Additionally, the test statistic of heterogeneity adjusted publication bias tests (R\"ucker's and Thompson's test) are displayed with green color.
-Test statitics smaller $< 1$ (light green colored) are equivalent to no evidence for publication test, test statistics between one and two to weak evidence, and above two they indicate evidence for publication bias (dark green).
-An adjusted effect with evidence for publication bias can be regarded as a more realistic estimate of treatment efficacy.
+Additionally, the test statistics of heterogeneity adjusted publication bias tests (R\"ucker's and Thompson's test) are displayed with green color.
+Test statitics smaller $t < 1$ (light green colored) are equivalent to no evidence for publication bias, test statistics $t$ between one and two to weak evidence, and above two they indicate evidence for publication bias (dark green).
+An adjusted effect with evidence for publication bias can be regarded as a more realistic estimate of the treatment effect.
 Some very large and very small differences have been omitted in the $z$-score and std.
 mean difference histograms; they are shown in Table \ref{missing.differences}.
+\\
+Most often, adjustment leads to a reduction of overall treatment effect estimates, which can be seen by the size of the bins on the positive side of the histograms.
+Adjustment is stronger when random effects meta-analysis is used as reference, because it gives larger weights to small studies.\\
+Contrary to naive expectation, we see cases with large negative adjustment, but no evidence for small study effects.
+This is because the linear regression parameter estimates are large, but estimated with high uncertainty, such that there will be few evidence for small study effects (publication bias), but nonetheless, the adjustment will be large.
+It is recommended to use the methods only in cases where there is clear evidence for publication bias.
+The color legend in Figure \ref{fig:adjustment.reg} thus gives a sense of the confidence that is put into the adjusted effects.
 \\
@@
 
-Most often, adjustment leads to a reduction of overall treatment effect estimates, because the bins on the positive side of the histograms are larger.
-Adjustment is stronger when random effects meta-analysis is used as reference, because it gives larger weights to small studies.\\
-Contrary to naive expectation, we see cases with large adjustment, but no evidence for small study effects.
-This is because the linear regression parameter estimates are large, but estimated with high uncertainty, such that there will be few evidence for small study effects (publication bias), but nonetheless, the adjustment will be large.
-The authors that developed the methods also recommend to use the methods in cases where there is clear evidence for publication bias.
-The color legend in Figure \ref{fig:adjustment.reg} thus gives a sense of confidence that there is in the credibility of the adjustment.
-\\
-Additionally, some meta-analyses with positively adjusted, larger overall treatment effects after adjustment (left side of the histogram) have also evidence for publication bias (remember that publication bias was defined as the tendency of small studies to show \textit{larger} results).
-This is not a wrong result, because the effects and their variances have been transformed, and it is possible that the shape of the funnel plot changes upon transformation; Figure \ref{fig:funnel.plot.change} shows this for illustrative purposes.
-From the left to the right, the funnel plot is shown for mean differences (the original measure), standardized mean differences and Fisher's $z$ scores.
-This is quite the most extreme case, with three different effects of adjustment, depending on outcome measure; there is no change with mean differences, reduction of effect sizes with std.
+Additionally, some meta-analyses with positively adjusted, larger overall treatment effects after adjustment (left side of the histogram) have also evidence for publication bias (defined as the tendency of small studies to show \textit{larger} results because only significant results are published).
+However, this is not wrong, because the effects and their variances have been transformed, and it is possible that the shape of the funnel plot changes upon transformation; Figure \ref{fig:funnel.plot.change} shows this for illustrative purposes.
+From the left to the right, the funnel plot is shown for mean differences (the original measure), standardized mean differences and Fisher's $z$ scores; there is no change upon adjustment using mean differences (blue line), reduction of the effect with std.
 mean differences and increase with Fisher's $z$ transformed correlation.
@@
 
-Figure \ref{fig:adjustment.copas} shows the same for effect sizes adjusted by Copas; Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
-Therefore, the effect of adjustment by Copas can be seen when comparing adjusted with random effects meta analysis estimates.
+Figure \ref{fig:adjustment.copas} shows the differences between Meta-analysis and adjusted effect sizes adjusted by Copas selection model; the model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
+Therefore, the effect of adjustment by Copas can better be seen when comparing adjusted with random effects meta analysis estimates.
 Again, we clearly see that more effect sizes are adjusted downwards.
-Additionally, there is more coincidence between the publication bias test statistics and adjustment, which is as expected.
-\\
+Additionally, there is more coincidence between publication bias test statistics and adjustment, \ie positive differences are accompained by large positive test statistics, which is as expected.
+\\
+Table \ref{adjustment.difference} shows quantiles and means for the various differences and the overall proportion of downward adjusted effect sizes.
+When std.
+mean difference is used as an effect measure, there are (substantially) more reduced effect sizes.
+The means in Table \ref{adjustment.difference} suggest that the average reduction is small.
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 69 meta-analyses have their $z$-score reduced by more than 0.13 by regression adjustment (and 5\% or 69 increased by -0.11 or more, fixed effects reference).
+Also, std.
+mean difference is reduced by 0.39 compared to fixed effects estimates in 5\% or 69 meta-analyses (or increased by 0.24).
 
@@
 
-Table \ref{adjustment.difference} shows quantiles and means for the various differences and the overall proportion of downward adjusted effect sizes.
-When std.
-mean difference is used as an effect measure, there are (substantially) more reduced effect sizes.
-The means in Table \ref{adjustment.difference} suggest that the average reduction is small.
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 69 meta-analyses have their $z$-score reduced by more than 0.13 by regression adjustment (and 5\% or 69 increased by -0.11 or more, fixed effects reference).
-Also, std.
-mean difference is reduced by 0.39 compared to fixed effects estimates in 5\% or 69 meta-analyses (or increased by 0.24).
-
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 11:45:51 2019
+% Tue Aug 13 10:25:12 2019
 \begin{table}[ht]
@@
   z: Random - Regression & -0.13 & -0.02 & 0.02 & 0.06 & 0.16 & 0.02 & 0.00 & 56.56 & 56.56 & 0.00 \\ 
-  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.11 & 0.01 & 19.38 & 56.41 & 37.03 & 56.92 \\ 
-  g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.16 & 0.02 & 60.09 & 85.01 & 24.93 & 56.92 \\ 
-  g: Fixed - Regression & -0.21 & -0.03 & 0.04 & 0.14 & 0.40 & 0.06 & 0.00 & 60.16 & 60.16 & 0.00 \\ 
-  g: Random - Regression & -0.20 & -0.02 & 0.05 & 0.17 & 0.44 & 0.08 & 0.00 & 62.68 & 62.68 & 0.00 \\ 
+  d: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.11 & 0.01 & 19.38 & 56.41 & 37.03 & 56.92 \\ 
+  d: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.16 & 0.02 & 60.09 & 85.01 & 24.93 & 56.92 \\ 
+  d: Fixed - Regression & -0.21 & -0.03 & 0.04 & 0.14 & 0.40 & 0.06 & 0.00 & 60.16 & 60.16 & 0.00 \\ 
+  d: Random - Regression & -0.20 & -0.02 & 0.05 & 0.17 & 0.44 & 0.08 & 0.00 & 62.68 & 62.68 & 0.00 \\ 
   IV: Fixed - Copas & -0.06 & -0.01 & 0.00 & 0.01 & 0.07 & 0.00 & 23.97 & 42.15 & 66.12 & 59.50 \\ 
@@
 \endgroup
-\caption{Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects.
+\caption{Quantiles and means of the differences between meta-analysis combined treatment effects and small study adjusted treatment effects.
 The column with the names ``> 0'' give the percentages of estimates larger than zero or larger or equal zero.
@@
 The row names indicate which outcome measure, meta-analysis method and adjustment method is used.
-Abbreviations are used for z-score (= z) and std.
-mean difference (= d).}
+Abbreviations are used for z-score (z) and std.
+mean difference (d).
+Separate rows give the results for IV outcomes, where the original effect sizes (log rate ratios, hazard ratios, etc.) are used.}
 \label{adjustment.difference}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 11:45:51 2019
+% Tue Aug 13 10:25:12 2019
 \begin{table}[ht]
@@
 \endgroup
-\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects. Abbreviations are used for z-score (= z) and std. mean difference (= d).} 
+\caption{Missing meta-analysis combined treatment effect and adjusted treatment effects. Abbreviations are used for z-score (= z) and std. mean difference (= d).} 
 \label{missing.differences}
@@
 Regression adjusted estimates are compared to the estimates of Copas selection model if these are not equal to random effects meta-analysis in Figure \ref{fig:adjustment.mean.diff}.
-A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
+A Tukey mean difference plot can reveal systematic differences and biases between the two measurement methods.
 Note that only 26 out of 121 \texttt{IV} outcome data is included when using $z$-score and std.
@@
 \end{knitrout}
-\caption{Test statistics of meta-analyses and adjustment methods.
-The color indicates the evidence for publication bias (\textit{p} value of R\\"ucker's or Egger's test), and the dotted line depicts the diagonal through the origin.}
+\caption{Test statistics of meta-analyses before and after adjustment.
+The color indicates the evidence for publication bias (\textit{p}-value of R\"ucker's or Egger's test), and the dotted line depicts the diagonal through the origin.
+Together with the horizontal dotted lines, the area which it borders indicates the consequences of adjustment for the evidence for a treatment effect.
+``decrease'' means that the test statistic is smaller upon adjustment, ''increase'' that it is larger.}
 \label{fig:evidence.adjustment}
@@
 
+The areas that are bordered by the diagonal and horizontal lines indicate which are the consequences of adjustment for a dot within.
+``decrease'' indicates fewer evidence for treatment effect is given after adjustment, ''increase'' that adjustment led to larger evidence for treatment effects.
+\\
 It can be seen that the alignment on the diagonal changes depending on the adjustment method.
@@
 There, less of an effect of adjustment on the evidence can be seen.
-The adjustment is more likely to be more reliable than the unadjusted estimate when publication bias is strong.
+The adjustment is more likely to be more reliable than the unadjusted estimate when publication bias is strong (see \ref{ch:Methods}).
 The dots with darker color are thus more likely to provide less biased estimates.\\
@@
 But the dark dots can be found more often far away from the diagonal.
-Some cases which have more evidence for treatment efficacy after adjustment have evidence for publication bias, which is not expected, since the publication bias tests applied are one-sided and only test for bias towards large effects.
-\\
-In some cases, the automatic detection of the side on which publication bias was expected (section \ref{sec:procedure}) might failed, because few significant effects are given (used to define side of bias) and the weighted mean effect is close to zero, in which case it is difficult to detect the side of publication bias beforehand.
+Some cases which have more evidence for treatment efficacy after adjustment have evidence for publication bias, although the publication bias tests applied are one-sided and only test for bias towards large effects.
+This is because the algorithm to detect the side on which publication bias was expected (section \ref{sec:procedure}) has failed, \eg because few significant effects are given (used to define side of bias) and the weighted mean effect is close to zero, in which case it is difficult to decide upon the side of publication bias.
 There are some adjustments with large increase in evidence and clear dark orange color, as in the plots on the right hand side in Figure \ref{fig:evidence.adjustment}.
@@
 \end{itemize}
-In the case of Copas selection model and when both test statistics are large (> 10), the explanation lies in a specialty of the model.
-The adjusted treatment effect estimates are not larger than the unadjusted, but their standard errors are different and sometimes smaller, because they are obtained from the Fisher information matrix of the log-likelihood (see section \ref{sec:copas}).
-\\
-The Copas selection model also allows to compute the number of missing studies, given that the model's assumptions are correct.
-It finds that 0 are missing, which corresponds to 0\% from all 22,916 analysed studies.
+In the case of Copas selection model and when both test statistics are large (> 10), the explanation lies in a specialty of the model; the adjusted treatment effect estimates are not larger than the unadjusted, but their standard errors are different and sometimes smaller, because they are obtained from the Fisher information matrix of the log-likelihood (see subsection \ref{sec:copas}).
+\\
+The Copas selection model also allows to compute the number of missing (\ie unpublished) studies in a given meta-analysis, given that the model's assumptions are correct.
+It finds that 2,618 are missing, which corresponds to 11.4\% from all 22,916 analysed studies.
 Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
-Note that random effects meta-analysis substitutes have been excluded (0 out of 1,388.
+Note that random effects meta-analysis substitutes have been excluded (828 out of 1,388 to limit the size of the bin at no.
+missing studies = 0.
 
@@
 \end{knitrout}
-\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ 0)}
+\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ 560)}
 \label{fig:copas.missing}
@@
 
-We can see that in some occasions, the method finds more than half of all studies are missing.
-In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
-The discrepancy between mean and median may indicate that the estimate of 0\% missing studies depends somewhat on these extreme cases.
-As can be written of from Table \ref{copas.missing}, 5\%, \ie 0 meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for 0, more than 30\% of missing studies.
+We can see that in some occasions, the method finds more than half of all studies in a meta-analysis are missing.
+In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}, where both the absolute number of missing studies and the fraction of missing studies in a meta-analysis are given.
+The discrepancy between mean and median may indicate that the estimate of 11.4\% missing studies depends somewhat on these extreme cases.
+As can be written of from Table \ref{copas.missing}, 5\%, \ie 28 meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for 1,060, more than 30\% of all missing studies.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 11:45:52 2019
+% Tue Aug 13 10:25:14 2019
 \begin{table}[ht]
@@
 
-\section{Publication Bias over Time}
-To test if publication bias in meta-analyses has decreased over time and newer meta-analyses have less bias, a generalized linear model has been set up. \\
-The dependent variable is the standardized mean differences (therefore, from \texttt{outcome.flag} = \texttt{IV}, only the std.
+\section{Mixed Effect Models and Publication Bias over Time}
+To test if publication bias in meta-analyses has decreased over time and newer meta-analyses have less bias, a generalized linear model has been set up to analyze all meta-analyses jointly and estimate a single parameter denoting publication bias.\\
+The dependent variable is the standardized mean differences(therefore, from \texttt{outcome.flag} = \texttt{IV}, only the std.
 mean differences are used).
-As before, the std.
+As before in section \ref{sec:change.size}, the std.
 mean difference is mirrored to one side by multiplying with the sign of the expected side of bias, \ie -1 or 1.
-The explanatory variable is the standard error, and the weights are the inverse of the variance of the std.
+\\
+In a first step, the explanatory variable is the standard error, and the weights are the inverse of the variance of the std.
 mean difference.
@@
 Figure \ref{fig:smds} shows the complete dataset with the fit of the previously described model (dotted red line).
-The details and evidence for the small study effects in the generalized linear model are given in table \ref{anova.small.study}, the coefficients in table \ref{coefficients.small.study}
+The details and evidence for the small study effects in the generalized linear model are given in Table \ref{anova.small.study}, the coefficients in Table \ref{coefficients.small.study}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 11:46:01 2019
+% Tue Aug 13 10:25:22 2019
 \begin{table}[ht]
@@
 null.fit &  1 & 4.0 & 18768.2 & 18800.1 & -9380.1 &  &  &  \\ 
-  small.study.fit &  2 & 5.0 & 18230.5 & 18270.4 & -9110.3 & 1 vs 2 & 539.7 & $<$0.00001 \\ 
+  publication.bias.fit &  2 & 5.0 & 18230.5 & 18270.4 & -9110.3 & 1 vs 2 & 539.7 & $<$0.00001 \\ 
    \hline
@@
 \endgroup
-\caption{Anova table for a generalized linear model for small study effects compared to the null model. 'small.study.fit' denotes the model with random intercepts for meta-analyses and reviews.} 
+\caption{Anova table for a generalized linear model for small study effects compared to the null model ('null.fit').
+'publication.bias.fit' denotes the model with random intercepts for meta-analyses and reviews.}
 \label{anova.small.study}
@@
 Table \ref{anova.random.slopes} shows the anova table for a model with and without random slopes.
+Model diagnostics indicate that there is no benefit in including random slopes for the single meta-analysis.
+\\
+To test if publication bias varies over time, we include the year of the publication of the review as an additional explanatory variable.
+Ultimately, it is of interest if there is an interaction between the small study effect (publication bias) and time of publication, i.e.
+if the slope varies depending on the year.
+Because such a model is nested in a more simpler model where the study year is only an additive effect, all these models are fitted.
+Table \ref{anova.lme} displays model fit diagnostics.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 11:46:03 2019
+% Tue Aug 13 10:25:24 2019
 \begin{table}[ht]
@@
   \hline
-small.study.fit &  1 & 5.0 & 18230.5 & 18270.4 & -9110.3 &  &  &  \\ 
-  small.study.rs.fit &  2 & 7.0 & 18233.1 & 18288.9 & -9109.5 & 1 vs 2 & 1.5 & 0.5 \\ 
+publication.bias.fit &  1 & 5.0 & 18230.5 & 18270.4 & -9110.3 &  &  &  \\ 
+  publication.bias.rs.fit &  2 & 7.0 & 18233.1 & 18288.9 & -9109.5 & 1 vs 2 & 1.5 & 0.5 \\ 
    \hline
@@
 \caption{Anova table for two generalized linear model fits.
-'small.study.fit' denotes the model with random intercepts for meta-analyses and reviews, 'small.study.rs.fit' the model with additional random slopes per review.}
+'publication.bias.fit' denotes the model with random intercepts for meta-analyses and reviews, 'publication.bias.rs.fit' the model with additional random slopes per review.}
 \label{anova.random.slopes}
@@
 
-Model diagnostics indicate that there is no benefit in including random slopes for the single meta-analysis. \\
-To test if publication bias varies over time, we include the year of the publication of the review as an additional explanatory variable.
-Ultimately, it is of interest if there is an interaction between the small study effect (publication bias) and time, i.e.
-if the slope varies depending on the year.
-Because such a model is nested in a more simpler model where the study year is only an additive effect, all these models are fitted.
-Table \ref{anova.lme} displays model fit diagnostics.
-
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 11:46:05 2019
+% Tue Aug 13 10:25:26 2019
 \begin{table}[ht]
@@
   \hline
-small.study.fit &  1 & 5.0 & 18230.5 & 18270.4 & -9110.3 &  &  &  \\ 
+publication.bias.fit &  1 & 5.0 & 18230.5 & 18270.4 & -9110.3 &  &  &  \\ 
   review.year.fit &  2 & 6.0 & 18231.6 & 18279.5 & -9109.8 & 1 vs 2 & 0.9 & 0.34 \\ 
@@
 \caption{Anova table for three generalized linear model fits.
-'small.study.fit' denotes the model with the standard error as explanatory variable, 'review.year.fit' the model with standard error and the centered (- 2013) review year as explanatory variable, and 'review.year.int.fit' the model with interaction between the two.}
+'publication.bias.fit' denotes the model with the standard error as explanatory variable, 'review.year.fit' the model with standard error and the centered (- 2013) review year as explanatory variable, and 'review.year.int.fit' the model with interaction between the two.}
 \label{anova.lme}
@@
 
-Because neither AIC, BIC or the F-test do show any improvement of model fit, it does not seem as if publication bias has substantially decreased or increased over the years.
-The review publication year is however not directly tied to the publication year of the studies that are affected by publication bias.
-Thus, using another measure of time, the results may be different.
-Thus, the models are re-fitted with the study publication years.
+Because neither AIC, BIC nor the F-test do show any improvement of model fit, we can not reject the null hypothesis that publication bias has not decreased or increased over the years.
+The review publication year is however only one measure of time, and possibly imprecise.
+Thus, the models are re-fitted with the mean centered study publication year of a meta-analysis.
+The mean of the study years is 2000.3.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 11:46:08 2019
+% Tue Aug 13 10:25:29 2019
 \begin{table}[ht]
@@
   \hline
-small.study.fit &  1 & 5.0 & 18115.2 & 18155.1 & -9052.6 &  &  &  \\ 
-  study.year.fit &  2 & 6.0 & 18095.0 & 18142.8 & -9041.5 & 1 vs 2 & 22.2 & 0.000002 \\ 
-  study.year.int.fit &  3 & 7.0 & 18096.9 & 18152.7 & -9041.5 & 2 vs 3 & 0.1 & 0.705909 \\ 
+publication.bias.fit &  1 & 5.0 & 18115.2 & 18155.1 & -9052.6 &  &  &  \\ 
+  study.year.fit &  2 & 6.0 & 18117.2 & 18165.0 & -9052.6 & 1 vs 2 & 0.0 & 0.958789 \\ 
+  study.year.int.fit &  3 & 7.0 & 18118.9 & 18174.7 & -9052.5 & 2 vs 3 & 0.3 & 0.591536 \\ 
    \hline
@@
 \caption{Anova table for three generalized linear model fits.
-'Small study fit' denotes the model with the standard error as explanatory variable, 'study.year.fit' the model with standard error and the centered (- 2000) study year as explanatory variable, and 'study.year.int.fit' the model with interaction between the two.}
+'Small study fit' denotes the model with the standard error as explanatory variable, 'study.year.fit' the model with standard error and the centered (- 2000) mean study year of the meta-analysis as explanatory variable, and 'study.year.int.fit' the model with interaction between the two.}
 \label{anova.lme}
@@
 The analysis of model fit indicates that there is an improvement when using the study year as a covariate, but only as an additive effect.
+It finds that effect sizes are in general little bit smaller in latter mean publication years (after the year 2000).
 The coefficients of the model are given in Table \ref{coefficients.study.year.fit}.
 AIC and BIC are smaller and the $p$-value of the F-test is very small.
-However, not the size of the effect, but the slope of the linear regression fit would have to be decreased to ultimately conclude a decrease of publication bias over the years.
+However, not the size of the effect, but the slope of the linear regression fit would have to be decreased in latter years to ultimately conclude a decrease of publication bias over the years.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 11:46:10 2019
+% Tue Aug 13 10:25:31 2019
 \begin{table}[ht]
@@
   \hline
-(Intercept) & 0.1791 & 0.1608 & 0.1974 \\ 
-  se.smd.pool & 0.3692 & 0.3371 & 0.4013 \\ 
-  study.year.center & -0.0012 & -0.0017 & -0.0007 \\ 
+(Intercept) & 0.1758 & 0.1575 & 0.1940 \\ 
+  se.smd.pool & 0.3800 & 0.3482 & 0.4118 \\ 
+  mean.study.year & -0.0001 & -0.0020 & 0.0019 \\ 
    \hline
@@
 % @
-% \caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted pooled treatment effect, based on different treatment effect measures.
+% \caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted combined treatment effect, based on different treatment effect measures.
 The method is indicated in the header, bin width is set to 0.05.
@@
 When clear methodological drawbacks are found in the analysis, the reader is referred to chapter \ref{ch:methods} for comments on the disadvantages.
-The amount of studies analyzing publication bias makes it not possible to discuss any of them, and thus we only some interesting and/or representative examples are shown.
+The amount of studies analyzing publication bias makes it not possible to discuss each of them, and thus only some interesting and/or representative examples are shown.
 
 \subsection{\citet{Egger}}
-The Cochrane database (1996 issue 2) and publications from the four leading medicine journals (the Lancet, BMJ, JAMA and Annals of Internal Medicine) between 1993 and 1996 were used to find systematic reviews with randomized controlled trials for the application of Egger's small study effect test.
+The Cochrane Library (1996 issue 2) and publications from the four leading medicine journals (the Lancet, BMJ, JAMA and Annals of Internal Medicine) between 1993 and 1996 were used to find systematic reviews with randomized controlled trials for the application of Egger's small study effect test.
 They included 38 meta-analyses with at least 5 studies and binary outcomes from the Cochrane Library and 37 from the journals.
@@
 \subsection{\citet{sutton.2000}}
-Out of 397 systematic reviews from the Cochrane database (complete number for 1998, issue 3), 49 had more than ten included studies and binary outcomes and 48 compared two treatments.
+Out of 397 systematic reviews from the Cochrane Library (complete number for 1998, issue 3), 49 had more than ten included studies and binary outcomes and 48 compared two treatments.
 They were analysed by trim-and-fill method \citep{trimfill} to detect and adjust for funnel plot asymmetry (similar to small study effect tests, but the method is known to overestimate bias).
@@
 When only using one meta-analysis per review, this reduced to 846 (3,555.
-Then, the criteria that have also been applied in this masters thesis are applied: $I^2 < 0.5$, variance ratio of smallest and largest effects > 4, at least one significant study result and at least 10 studies to be used.
+Then, the criteria that have also been applied in this masters study are applied: $I^2 < 0.5$, variance ratio of smallest and largest effects > 4, at least one significant study result and at least 10 studies to be used.
 Afterwards, they applied Harbord's, Egger's and Begg's Test to the dataset.
@@
 % The results seem to be similar enough to claim that neither the methods nor the data and it's results are differing substantially.
-Because the thesis relies on more data, it is likely to be more accurate and can possibly add to the findings of \citet{Ioannidis2007}.
+Because the study relies on more data, it is likely to be more accurate and can possibly add to the findings of \citet{Ioannidis2007}.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 11:46:51 2019
+% Tue Aug 13 10:26:07 2019
 \begin{table}[ht]
@@
   \hline
- & Ioannidis & Thesis \\ 
+ & Ioannidis & Study \\ 
   \hline
@@
 \caption{Comparison of results from Ioannidis et.al.
-(2007) to the results of the thesis.
+(2007) to the results of this study.
 The percentage of meta-analysis which match all exclusion criteria denotes the ones that apply to all criteria in the table plus the small heterogeneity criterium.
@@
 There is also criticism that one can address on the methods.
+The small study effect which is used as a indication for publication bias can be caused by other biases such as; selective outcome reporting and poor methodological quality of smaller studies.
+It can also be caused by true heterogeneity between studies; early and small studies are more likely to include high-risk patients for which treatment can have larger benefits.
+\\
+
 It is possible that the results are caused by systematic differences in the population of study participants only.
@@
 \section{Outlook}
-Given the size and abundance of information in the dataset, the possibilities to investigate sources of bias in the Cochrane Database of Systematic Reviews are not exhausted (see for example in \citet{ioannidis.2017}).
+Given the size and abundance of information in the dataset, the possibilities to investigate sources of bias in the Cochrane Library of Systematic Reviews are not exhausted (see for example in \citet{ioannidis.2017}).
 In particular, one could easily come up with more hypotheses that could be tested in meta meta-regression, as introduced in the last section of the results.
@@
 This study is so far the largest assessment of publication bias by small study effects and uses data that has been collected after major efforts have been made to curb publication bias.
-It is the first analysis of the Cochrane Database of Systematic Reviews also analyzing publication bias using hazard and rate ratios.
+It is the first analysis of the Cochrane Library of Systematic Reviews also analyzing publication bias using hazard and rate ratios.
 The results indicate, similarly to other studies, that the efforts did not yet resolve the issue.
 \\
-The findings further imply that when using meta-analyses, it is key to investigate sources of between-study heterogeneity; an alternative is to rely solely on the largest trials \citep{largest.study.only}.
-Since the Cochrane Organization uses results from grey literature to limit the effects of publication bias, but still does not manage to abolish it, there is also the need for journal editors to change their publication policies.
+Also, it is the first study to extensively adjust the combined effect sizes from meta-analyses for publication bias.
+It has been found repeatedly that publication bias might threaten the validity of the findings of some meta-analyses from Cochrane systematic reviews.
+Cochrane did so far not extend their protocols to publication bias tests or adjustment methods.
+Especially when a lot of studies are available, the use of adjustment methods might resolve this issue.
+\\
+Since Cochrane uses results from grey literature to limit the effects of publication bias, but still does not manage to abolish it, there is also the need for journal editors to change their publication policies.
 

### 2019-08-13 report/chapter03.Rnw
Corrected version, discussion, introduction

@@
 When one subgroup has substantially different real treatment effects, and the specific properties influence study size, publication bias assessment fails.
-Subgroups are not indicated in \Sexpr{no.subgroup}\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane review groups did.
+Subgroups are not indicated in \Sexpr{no.subgroup}\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane Review Groups did.
 The methods described in the methods chapter \ref{ch:methods} most often apply directly to the algorithms used in \texttt{meta} and \texttt{metafor}. \\

### 2019-08-13 report/chapter04.Rnw
Corrected version, discussion, introduction

@@
          upper.panel=panel.pts.new, lower.panel=panel.cor, 
-         cex.labels = 2, cex = .25, cex.cor = 2, pch = 1,
+         col.regions = colorRampPalette(c("red", "red", "chartreuse", "royalblue", "navy")),
+         cex.labels = 1.65, cex = .25, cex.cor = 2, pch = 1,
          text.panel=panel.txt, cor.method = "spearman")
 @
-\caption{Pairs-plot for test statistics of small study effect and excess significance.
+\caption{Pairs-plot for test statistics of small study effects.
 The lower panel gives the Spearman correlations for the different test statistics, and the upper panel displays a scatterplot.
@@
 Around 67\% of the dataset is not significant, no matter which test is used.
+\\
+
+<<echo = FALSE, results='asis'>>=
+print(xtable(number.sig.tests, caption = "Counts Number of significant test results per meta-analysis, separated
+       for outcome types. Last entry for continuous and IV outcomes is empty since one test less was 
+       applied", label = "number.sig.tests", align = "lccc"), include.rownames = F, size = "footnotesize")
+@
+
 When leaving away the excess significance test, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of \texttt{IV} and continuous outcome tests had at least one significant result.
@@
 \\
-
-<<echo = FALSE, results='asis'>>=
-print(xtable(number.sig.tests, caption = "Counts Number of significant test results per meta-analysis, separated
-       for outcome types. Last entry for continuous and IV outcomes is empty since one test less was 
-       applied", label = "number.sig.tests", align = "lccc"), include.rownames = F, size = "footnotesize")
-@
-
-The precise proportions of agreement are provided in table \ref{test.agreement}. %Correspondence between excess significance tests and small study effects thus is considered rather random. 
+The precise proportions of agreement in significance/non-significance are provided in Table \ref{test.agreement}.
+A separate column provides the proportion of significant results of the test with fewer significant results that are also significant using the test with more significant results.
 Linear regression based tests agree more often with other linear regression based tests, and agreement between small study effect tests is in general well above 60 \% (at best, 95\% test agreement in significance for \texttt{IV} \texttt{outcome.flag}).
 The agreement on statistical significance between small study effect tests and excess significance tests ranges from 64\% to 4\% (for \texttt{IV} and rank tests).
+Note that these numbers are difficult to interpret because there are substantially less significant results of the excess significance tests, and thus, a agreement of 100\% still does not indicate perfect compatibility/replaceability of the tests.
 
 <<echo = FALSE, results = 'asis'>>=
-print(xtable(test.agreement, align = "lcc", caption = "Overall proportion of agreement if significant or unsignificant, and for significance only.
-Horizontal lines separate binary, continuous and IV outcomes (order as in table).
-The reference significance test is the one with more significant results.",
+print(xtable(test.agreement, align = "lcc", caption = "Overall proportion of agreement if publication bias is significant or non-significant, and if significant only.
+When comparing agreement if significant only, the proportion of the test with fewer significant results that is significant with another test as well is shown.",
              label = "test.agreement"),, size = "scriptsize")
@@
 rownames(adjustment.diff.table) <- c(paste("z:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
-                                     paste("g:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
+                                     paste("d:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
                                      paste("IV:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")))
@@
 #Change in evidence of treatment effect scatterplots:
-
 mid <- median(meta.f$pval.se)
 method.names <- c(z.reg = "Regression", z.copas = "Copas Selection Model")
+
+decrease_text <- data.frame(label = c("decrease", "decrease"),
+  method   = c("z.reg", "z.copas"))
+increase_text <- data.frame(label = c("increase", "increase"),
+                            method   = c("z.reg", "z.copas"))
+
 adjusted.evidence.fixed <- meta.f %>% filter(z.reg > -40) %>% 
@@
   geom_abline(slope = 1, intercept = 0, linetype = 2, size = .3) +
-  xlab("Adjusted z test statistic") + ylab("Fixed effects test statistic")
+  geom_abline(slope = 0, intercept = 0, linetype = 2, size = .3) +
+  geom_text(data = decrease_text, mapping = aes(x = -9, y = 6, label = label), 
+            color = "tan3") + 
+  geom_text(data = decrease_text, mapping = aes(x = 9, y = -6, label = label), 
+            color = "tan3") + 
+  geom_text(data = increase_text, mapping = aes(x = 15, y = 4, label = label), 
+            color = "chartreuse3") + 
+  geom_text(data = increase_text, mapping = aes(x = -15, y = -4, label = label), 
+            color = "chartreuse3") + 
+  xlab("Adjusted z test statistic") + ylab("Fixed effects z test statistic")
 
@@
   geom_abline(slope = 1, intercept = 0, linetype = 2, size = .3) +
-  xlab("Adjusted z test statistic") + ylab("Random effects test statistic")
+  geom_abline(slope = 0, intercept = 0, linetype = 2, size = .3) +
+  geom_text(data = decrease_text, mapping = aes(x = -11, y = 6, label = label), 
+            color = "tan3") + 
+  geom_text(data = decrease_text, mapping = aes(x = 11, y = -6, label = label), 
+            color = "tan3") + 
+  geom_text(data = increase_text, mapping = aes(x = 15, y = 4, label = label), 
+            color = "chartreuse3") + 
+  geom_text(data = increase_text, mapping = aes(x = -15, y = -4, label = label), 
+            color = "chartreuse3") + 
+  xlab("Adjusted z test statistic") + ylab("Random effects z test statistic")
 #--------------------------------------------------------------------------------------------------------------------#
@@
 Figure \ref{fig:adjustment.reg} displays the difference between the estimated meta-analysis treatment effect and the regression adjusted treatment effect \ref{sec:regression.adjustment}, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
-The absolute value $|\hat{\theta}_M|$ is taken and $\hat{\theta}_\textrm{Adj.}$ is negative if it's sign is different from the sign of the original $\theta$.
+The absolute value $|\hat{\theta}_M|$ is taken and $\hat{\theta}_\textrm{Adj.}$ is negative if it's sign is different from the sign of the original $\hat{\theta}_M$.
 Thus, a positive difference indicates a reduction of the original effect size, and the magnitude of the difference indicates the extent of the adjustment.
@@
 Additionally, the test statistics of heterogeneity adjusted publication bias tests (R\"ucker's and Thompson's test) are displayed with green color.
-Test statitics smaller $< 1$ (light green colored) are equivalent to no evidence for publication bias, test statistics between one and two to weak evidence, and above two they indicate evidence for publication bias (dark green).
+Test statitics smaller $t < 1$ (light green colored) are equivalent to no evidence for publication bias, test statistics $t$ between one and two to weak evidence, and above two they indicate evidence for publication bias (dark green).
 An adjusted effect with evidence for publication bias can be regarded as a more realistic estimate of the treatment effect.
@@
 
-Additionally, some meta-analyses with positively adjusted, larger overall treatment effects after adjustment (left side of the histogram) have also evidence for publication bias (remember that publication bias was defined as the tendency of small studies to show \textit{larger} results).
+Additionally, some meta-analyses with positively adjusted, larger overall treatment effects after adjustment (left side of the histogram) have also evidence for publication bias (defined as the tendency of small studies to show \textit{larger} results because only significant results are published).
 However, this is not wrong, because the effects and their variances have been transformed, and it is possible that the shape of the funnel plot changes upon transformation; Figure \ref{fig:funnel.plot.change} shows this for illustrative purposes.
@@
 
-Figure \ref{fig:adjustment.copas} shows the same for effect sizes adjusted by Copas; Copas selection model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
+Figure \ref{fig:adjustment.copas} shows the differences between Meta-analysis and adjusted effect sizes adjusted by Copas selection model; the model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
 Therefore, the effect of adjustment by Copas can better be seen when comparing adjusted with random effects meta analysis estimates.
 Again, we clearly see that more effect sizes are adjusted downwards.
-Additionally, there is more coincidence between the publication bias test statistics and adjustment, which is as expected.
+Additionally, there is more coincidence between publication bias test statistics and adjustment, \ie positive differences are accompained by large positive test statistics, which is as expected.
 \\
@@
 <<echo=FALSE, results='asis'>>=
-print(xtable(adjustment.diff.table, label = "adjustment.difference", caption = "Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects.
+print(xtable(adjustment.diff.table, label = "adjustment.difference", caption = "Quantiles and means of the differences between meta-analysis combined treatment effects and small study adjusted treatment effects.
 The column with the names ``> 0'' give the percentages of estimates larger than zero or larger or equal zero.
@@
 The row names indicate which outcome measure, meta-analysis method and adjustment method is used.
-Abbreviations are used for z-score (= z) and std.
-mean difference (= d).", align = "lcccccccccr"), include.rownames = T, size = "scriptsize",# sanitize.text.function=function(x){x},
+Abbreviations are used for z-score (z) and std.
+mean difference (d).
+Separate rows give the results for IV outcomes, where the original effect sizes (log rate ratios, hazard ratios, etc.) are used.", align = "lcccccccccr"), include.rownames = T, size = "scriptsize",# sanitize.text.function=function(x){x},
       # table.placement = "p"
@@
 print(xtable(missing.differences, 
-             caption = "Missing meta-analysis pooled treatment effect and adjusted treatment effects.
+             caption = "Missing meta-analysis combined treatment effect and adjusted treatment effects.
 Abbreviations are used for z-score (= z) and std.
@@
 Regression adjusted estimates are compared to the estimates of Copas selection model if these are not equal to random effects meta-analysis in Figure \ref{fig:adjustment.mean.diff}.
-A Tukey mean difference plot can serve to reveal systematic differences and biases between the two measurement methods.
+A Tukey mean difference plot can reveal systematic differences and biases between the two measurement methods.
 Note that only 26 out of \Sexpr{dim(meta.iv)[1]} \texttt{IV} outcome data is included when using $z$-score and std.
@@
 @
-\caption{Test statistics of meta-analyses and adjustment methods.
-The color indicates the evidence for publication bias (\textit{p} value of R\\"ucker's or Egger's test), and the dotted line depicts the diagonal through the origin.}
+\caption{Test statistics of meta-analyses before and after adjustment.
+The color indicates the evidence for publication bias (\textit{p}-value of R\"ucker's or Egger's test), and the dotted line depicts the diagonal through the origin.
+Together with the horizontal dotted lines, the area which it borders indicates the consequences of adjustment for the evidence for a treatment effect.
+``decrease'' means that the test statistic is smaller upon adjustment, ''increase'' that it is larger.}
 \label{fig:evidence.adjustment}
@@
 \end{itemize}
-In the case of Copas selection model and when both test statistics are large (> 10), the explanation lies in a specialty of the model.
-The adjusted treatment effect estimates are not larger than the unadjusted, but their standard errors are different and sometimes smaller, because they are obtained from the Fisher information matrix of the log-likelihood (see section \ref{sec:copas}).
+In the case of Copas selection model and when both test statistics are large (> 10), the explanation lies in a specialty of the model; the adjusted treatment effect estimates are not larger than the unadjusted, but their standard errors are different and sometimes smaller, because they are obtained from the Fisher information matrix of the log-likelihood (see subsection \ref{sec:copas}).
 \\
-The Copas selection model also allows to compute the number of missing studies, given that the model's assumptions are correct.
-It finds that \Sexpr{format(round(sum(meta.f$missing.Copas, na.rm = T)), big.mark = ",")} are missing, which corresponds to \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% from all \Sexpr{format(round(sum(meta.f$k)), big.mark = ",")} analysed studies.
+The Copas selection model also allows to compute the number of missing (\ie unpublished) studies in a given meta-analysis, given that the model's assumptions are correct.
+It finds that \Sexpr{format(round(sum(meta.f$missing.copas, na.rm = T)), big.mark = ",")} are missing, which corresponds to \Sexpr{round((sum(meta.f$missing.copas, na.rm = T)/sum(meta.f$k))*100,1)}\% from all \Sexpr{format(round(sum(meta.f$k)), big.mark = ",")} analysed studies.
 Figure \ref{fig:copas.missing} shows a histogram of the overall fraction of missing studies.
-Note that random effects meta-analysis substitutes have been excluded (\Sexpr{sum(is.na(meta.f$missing.Copas))} out of \Sexpr{format(dim(meta.f)[1], big.mark = ",")}.
+Note that random effects meta-analysis substitutes have been excluded (\Sexpr{sum(is.na(meta.f$missing.copas))} out of \Sexpr{format(dim(meta.f)[1], big.mark = ",")} to limit the size of the bin at no.
+missing studies = 0.
 
@@
 @
-\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ \Sexpr{sum(!is.na(meta.f$missing.Copas))})}
+\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ \Sexpr{sum(!is.na(meta.f$missing.copas))})}
 \label{fig:copas.missing}
@@
 
-We can see that in some occasions, the method finds more than half of all studies are missing.
-In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}.
-The discrepancy between mean and median may indicate that the estimate of \Sexpr{round((sum(meta.f$missing.Copas, na.rm = T)/sum(meta.f$k))*100,1)}\% missing studies depends somewhat on these extreme cases.
-As can be written of from Table \ref{copas.missing}, 5\%, \ie \Sexpr{round(sum(!is.na(meta.f$missing.Copas))*0.05)} meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for \Sexpr{format(round(sum(meta.f$missing.Copas[which(meta.f$missing.Copas >= 17.60)], na.rm = T)), big.mark = ",")}, more than 30\% of missing studies.
+We can see that in some occasions, the method finds more than half of all studies in a meta-analysis are missing.
+In most occasions, the estimate of missing studies is zero, as can be seen in Table \ref{copas.missing}, where both the absolute number of missing studies and the fraction of missing studies in a meta-analysis are given.
+The discrepancy between mean and median may indicate that the estimate of \Sexpr{round((sum(meta.f$missing.copas, na.rm = T)/sum(meta.f$k))*100,1)}\% missing studies depends somewhat on these extreme cases.
+As can be written of from Table \ref{copas.missing}, 5\%, \ie \Sexpr{round(sum(!is.na(meta.f$missing.copas))*0.05)} meta-analyses have 17.6 or more studies missing: in fact, these 5\% most extreme make up for \Sexpr{format(round(sum(meta.f$missing.copas[which(meta.f$missing.copas >= 17.60)], na.rm = T)), big.mark = ",")}, more than 30\% of all missing studies.
 
@@
 study.number.review.model <- dim(reg.dat)[1]
-small.study.fit <- lme(fixed = smd.pool ~ se.smd.pool, random = list(~ 1 | id, ~ 1 | meta.id),
+publication.bias.fit <- lme(fixed = smd.pool ~ se.smd.pool, random = list(~ 1 | id, ~ 1 | meta.id),
                        weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
 plot(y = reg.dat$smd.pool, x = reg.dat$se.smd.pool, cex = .1, xlab = "standard error", ylab = "std. mean difference")
-small.study.fit.coef <- summary(small.study.fit)$coefficients$fixed
-abline(a = small.study.fit.coef, col = "red", lty = 2)
+publication.bias.fit.coef <- summary(publication.bias.fit)$coefficients$fixed
+abline(a = publication.bias.fit.coef, col = "red", lty = 2)
 
@@
                        weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-small.study.fit.anova <- anova(null.fit, small.study.fit)
-small.study.fit.anova[2,9] <- "<0.00001"
-print(xtable(small.study.fit.anova[,-1], caption = "Anova table for a generalized linear model for small study effects compared to the null model.
-'small.study.fit' denotes the model with random intercepts for meta-analyses and reviews.",
+publication.bias.fit.anova <- anova(null.fit, publication.bias.fit)
+publication.bias.fit.anova[2,9] <- "<0.00001"
+print(xtable(publication.bias.fit.anova[,-1], caption = "Anova table for a generalized linear model for small study effects compared to the null model ('null.fit').
+'publication.bias.fit' denotes the model with random intercepts for meta-analyses and reviews.",
              label = "anova.small.study", digits = c(1,1,1,1,1,1,1,1,5)), 
@@
 <<echo =FALSE, results='asis', warning=FALSE>>=
-print(xtable(lmer.table(small.study.fit), align = "lccc", 
+print(xtable(lmer.table(publication.bias.fit), align = "lccc", 
              caption = "Coefficients and 95\\% confidence limits of the generalized linear model.
@@
 Table \ref{anova.random.slopes} shows the anova table for a model with and without random slopes.
-
-<<echo =FALSE, results='asis', warning=FALSE>>=
-small.study.rs.fit <- lme(fixed = smd.pool ~ se.smd.pool, 
-                          random = list(~ 1 | id, ~ meta.id | meta.id),
-                       weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-print(xtable(anova(small.study.fit, small.study.rs.fit)[,-1], caption = "Anova table for two generalized linear model fits.
-'small.study.fit' denotes the model with random intercepts for meta-analyses and reviews, 'small.study.rs.fit' the model with additional random slopes per review.",
-             label = "anova.random.slopes", digits = c(1,1,1,1,1,1,1,1,1)), 
-      size = "scriptsize")
-@
-
-Model diagnostics indicate that there is no benefit in including random slopes for the single meta-analysis. \\
+Model diagnostics indicate that there is no benefit in including random slopes for the single meta-analysis.
+\\
 To test if publication bias varies over time, we include the year of the publication of the review as an additional explanatory variable.
-Ultimately, it is of interest if there is an interaction between the small study effect (publication bias) and time, i.e.
+Ultimately, it is of interest if there is an interaction between the small study effect (publication bias) and time of publication, i.e.
 if the slope varies depending on the year.
@@
 Table \ref{anova.lme} displays model fit diagnostics.
+
+<<echo =FALSE, results='asis', warning=FALSE>>=
+publication.bias.rs.fit <- lme(fixed = smd.pool ~ se.smd.pool, 
+                          random = list(~ 1 | id, ~ meta.id | meta.id),
+                       weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
+print(xtable(anova(publication.bias.fit, publication.bias.rs.fit)[,-1], caption = "Anova table for two generalized linear model fits.
+'publication.bias.fit' denotes the model with random intercepts for meta-analyses and reviews, 'publication.bias.rs.fit' the model with additional random slopes per review.",
+             label = "anova.random.slopes", digits = c(1,1,1,1,1,1,1,1,1)), 
+      size = "scriptsize")
+@
 
@@
                 weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-print(xtable(anova(small.study.fit, review.year.fit, review.year.int.fit)[,-1], caption = "Anova table for three generalized linear model fits.
-'small.study.fit' denotes the model with the standard error as explanatory variable, 'review.year.fit' the model with standard error and the centered (- 2013) review year as explanatory variable, and 'review.year.int.fit' the model with interaction between the two.",
+print(xtable(anova(publication.bias.fit, review.year.fit, review.year.int.fit)[,-1], caption = "Anova table for three generalized linear model fits.
+'publication.bias.fit' denotes the model with the standard error as explanatory variable, 'review.year.fit' the model with standard error and the centered (- 2013) review year as explanatory variable, and 'review.year.int.fit' the model with interaction between the two.",
              label = "anova.lme", digits = c(1,1,1,1,1,1,1,1,2)), size = "scriptsize")
@@
 
-Because neither AIC, BIC or the F-test do show any improvement of model fit, it does not seem as if publication bias has substantially decreased or increased over the years.
-The review publication year is however not directly tied to the publication year of the studies that are affected by publication bias.
-Thus, using another measure of time, the results may be different.
-Thus, the models are re-fitted with the study publication years.
+Because neither AIC, BIC nor the F-test do show any improvement of model fit, we can not reject the null hypothesis that publication bias has not decreased or increased over the years.
+The review publication year is however only one measure of time, and possibly imprecise.
+Thus, the models are re-fitted with the mean centered study publication year of a meta-analysis.
+The mean of the study years is 2000.3.
 
@@
 reg.dat <- reg.dat %>% filter(!is.na(study.year)) %>% ungroup() %>%  
-  mutate(study.year.center = study.year - mean(study.year))
+  mutate(study.year.center = study.year - mean(study.year)) %>% 
+  group_by(meta.id) %>% mutate(mean.study.year = mean(study.year.center))
 study.number.study.model <- dim(reg.dat)[1]
-small.study.fit <- lme(fixed = smd.pool ~ se.smd.pool, random = list(~ 1 | id, ~ 1 | meta.id),
+publication.bias.fit <- lme(fixed = smd.pool ~ se.smd.pool, random = list(~ 1 | id, ~ 1 | meta.id),
                        weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-study.year.fit <- lme(fixed = smd.pool ~ se.smd.pool + study.year.center, 
+study.year.fit <- lme(fixed = smd.pool ~ se.smd.pool + mean.study.year, 
                 random = list(~ 1 | id, ~ 1 | meta.id),
                 weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-study.year.int.fit <- lme(fixed = smd.pool ~ se.smd.pool * study.year.center, 
+study.year.int.fit <- lme(fixed = smd.pool ~ se.smd.pool * mean.study.year, 
                     random = list(~ 1 | id, ~ 1 | meta.id),
                 weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-print(xtable(anova(small.study.fit, study.year.fit, study.year.int.fit)[,-1], caption = "Anova table for three generalized linear model fits.
-'Small study fit' denotes the model with the standard error as explanatory variable, 'study.year.fit' the model with standard error and the centered (- 2000) study year as explanatory variable, and 'study.year.int.fit' the model with interaction between the two.",
+print(xtable(anova(publication.bias.fit, study.year.fit, study.year.int.fit)[,-1], caption = "Anova table for three generalized linear model fits.
+'Small study fit' denotes the model with the standard error as explanatory variable, 'study.year.fit' the model with standard error and the centered (- 2000) mean study year of the meta-analysis as explanatory variable, and 'study.year.int.fit' the model with interaction between the two.",
              label = "anova.lme", digits = c(1,1,1,1,1,1,1,1,6)), size = "scriptsize")
@@
 The analysis of model fit indicates that there is an improvement when using the study year as a covariate, but only as an additive effect.
+It finds that effect sizes are in general little bit smaller in latter mean publication years (after the year 2000).
 The coefficients of the model are given in Table \ref{coefficients.study.year.fit}.
 AIC and BIC are smaller and the $p$-value of the F-test is very small.
-However, not the size of the effect, but the slope of the linear regression fit would have to be decreased to ultimately conclude a decrease of publication bias over the years.
+However, not the size of the effect, but the slope of the linear regression fit would have to be decreased in latter years to ultimately conclude a decrease of publication bias over the years.
 

### 2019-08-13 report/chapter05.Rnw
Corrected version, discussion, introduction

@@
 
-comparison.ioannidis <- data.frame(Ioannidis = ioannidis.results, Thesis = own.results)
+comparison.ioannidis <- data.frame(Ioannidis = ioannidis.results, Study = own.results)
 rownames(comparison.ioannidis) <- c("Wider dataset (n)", "study number > 10", "variance ratio > 4",
@@
 When only using one meta-analysis per review, this reduced to 846 (\Sexpr{format(restr.dataset.ioannidis.comparison.count$nn, big.mark = ",")}.
-Then, the criteria that have also been applied in this masters thesis are applied: $I^2 < 0.5$, variance ratio of smallest and largest effects > 4, at least one significant study result and at least 10 studies to be used.
+Then, the criteria that have also been applied in this masters study are applied: $I^2 < 0.5$, variance ratio of smallest and largest effects > 4, at least one significant study result and at least 10 studies to be used.
 Afterwards, they applied Harbord's, Egger's and Begg's Test to the dataset.
@@
 % The results seem to be similar enough to claim that neither the methods nor the data and it's results are differing substantially.
-Because the thesis relies on more data, it is likely to be more accurate and can possibly add to the findings of \citet{Ioannidis2007}.
+Because the study relies on more data, it is likely to be more accurate and can possibly add to the findings of \citet{Ioannidis2007}.
 
@@
 print(xtable(comparison.ioannidis, caption = "Comparison of results from Ioannidis et.al.
-(2007) to the results of the thesis.
+(2007) to the results of this study.
 The percentage of meta-analysis which match all exclusion criteria denotes the ones that apply to all criteria in the table plus the small heterogeneity criterium.
@@
 This study is so far the largest assessment of publication bias by small study effects and uses data that has been collected after major efforts have been made to curb publication bias.
-It is the first analysis of the Cochrane Database of Systematic Reviews also analyzing publication bias using hazard and rate ratios.
+It is the first analysis of the Cochrane Library of Systematic Reviews also analyzing publication bias using hazard and rate ratios.
 The results indicate, similarly to other studies, that the efforts did not yet resolve the issue.
 \\
-The findings further imply that when using meta-analyses, it is key to investigate sources of between-study heterogeneity; an alternative is to rely solely on the largest trials \citep{largest.study.only}.
-Since the Cochrane Organization uses results from grey literature to limit the effects of publication bias, but still does not manage to abolish it, there is also the need for journal editors to change their publication policies.
+Also, it is the first study to extensively adjust the combined effect sizes from meta-analyses for publication bias.
+It has been found repeatedly that publication bias might threaten the validity of the findings of some meta-analyses from Cochrane systematic reviews.
+Cochrane did so far not extend their protocols to publication bias tests or adjustment methods.
+Especially when a lot of studies are available, the use of adjustment methods might resolve this issue.
+\\
+Since Cochrane uses results from grey literature to limit the effects of publication bias, but still does not manage to abolish it, there is also the need for journal editors to change their publication policies.

### 2019-08-14 report/MSc_Report.Rnw
Update
Methods update
Results section update
Results first draft
update
Report based on the new data
report correction
appendix, corrected IV results
mixed models theory
Draft for Simon and Prof. Held

@@
 \usepackage{tikz}
+\usepackage{amssymb}
 \usetikzlibrary{trees}
+\usetikzlibrary{shapes,arrows}
 
@@
 \thispagestyle{empty}
-\begin{center}
-  \vspace*{6cm}{\bfseries\Huge
-  $p$-values:\\[5mm] their use, abuse and proper use \\[5mm]
-  illustrated with seven facets 
-  }
-  \vfill
-  \rm
+\newpage
 
-  \LARGE
-  M\"axli Musterli\\[12mm]
+\pagenumbering{roman}
 
-  \normalsize
-  Version \today
-\end{center}
-\newpage
-\thispagestyle{empty}~
-\newpage
-\pagenumbering{roman}
+\chapter*{Abstract}
+% \addtocontents{toc}{\protect \vspace*{13.mm}}
+% \addcontentsline{toc}{chapter}{\bfseries{Preface}}
+\thispagestyle{plain}\markboth{Abstract}{Abstract}
+It is well known that the part of scientific findings that are published in journals are a 
+biased sample of the overall amount of research that is done. Often, editors aim to publish
+new and influential results that will be distributed further by other researchers and
+heighten their journal impact factor. The downside of it is that some of these results
+might only be positive by chance, or because of poor study design. When decision
+makers use this information to take decisions, they are likely to be mislead. \\
+In this study, the prevalence and impact of publication bias is assessed in 
+a large scale analysis. The data stems from the Cochrane Library of Systematic Reviews, the biggest collection
+of clinical trial and public health intervention data. Meta-Analyses of Cochrane
+are scrutinized for small-study effects and excess significance, both signs
+of publication bias. We also adjust the treatment effects from the meta-analysis for publication bias 
+and compare the newly obtained effects with unadjusted treatment effects. In a exploratory analysis, we find
+that around 20\% of meta-analyses are subject to publication bias, and that the
+evidence for treatment efficacy decreases after adjustment. Publication bias
+thus remains a threat to the validity of findings in Cochrane and in clinical research.
+% Because of the
+% amount of data that underlies this analysis, we suggest that previous measures 
+% to curb publication bias need to be enforced and possibly, that new measures have 
+% to be taken to prevent patient harm and strengthen the reliability of clinical research.
+
+\chapter*{Acknowledgments}
+\thispagestyle{plain}\markboth{Acknowledgments}{Acknowledgments}
+I would like to thank all members of the Department of Biostatistics for promoting me along my studies and making this thesis possible.
+Special thanks goes to Dr. Simon Schwab, for thorough support, and to Prof. Dr. Leonhard Held for advice. \\
+Among my friends, I would to thank all students of biostatistics in the years 2018 and 2019 for making this time so pleasant. Samuel
+Pawel was a very good friend with lots of advice and understanding throughout this time, and it was for Eleftheria Michalopoulou 
+that writing this thesis was also fun.\\
+Most important, my family always supported me and gave me confidence in myself. Denise Sternlicht and
+Annatina Kreiliger are two of the main reasons why this thesis has been done, and I would like to dedicate this
+thesis to them.
+
+\bigskip
+
+\begin{flushright}
+  Giuachin Kreiliger\\
+  June 2019
+\end{flushright}
+
+%\addtocontents{toc}{\protect \vspace*{10mm}}
+% \addtocontents{toc}{\protect \vspace*{13.mm}}
+% \addcontentsline{toc}{chapter}{\bfseries{Preface}}
 
@@
 
-\chapter*{Preface}
-\addtocontents{toc}{\protect \vspace*{13.mm}}
-\addcontentsline{toc}{chapter}{\bfseries{Preface}}
-\thispagestyle{plain}\markboth{Preface}{Preface}
+% Howdy!
 
-Howdy!
-
-\bigskip
-
-\begin{flushright}
-  Max Muster\\
-  June 2018
-\end{flushright}
-
-\addtocontents{toc}{\protect \vspace*{10mm}}
-
-\cleardoublepage
+%\cleardoublepage
 \pagenumbering{arabic}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2019-08-14 report/MSc_Report.tex
Draft for Simon and Prof. Held

@@
 \thispagestyle{empty}
-\begin{center}
-  \vspace*{6cm}{\bfseries\Huge
-  Statistical Assessment and Adjustment of Publication Bias in the Cochrane Database of Systematic Reviews
-  }
-  \vfill
-  \rm
-
-  \LARGE
-  Giuachin Kreiliger\\[12mm]
-
-  \normalsize
-  Version \today
-\end{center}
 \newpage
-\thispagestyle{empty}~
-\newpage
+
 \pagenumbering{roman}
 
-\thispagestyle{plain}\markboth{Contents}{Contents}
-\tableofcontents
-\setkeys{Gin}{width=.8\textwidth}
-
-\chapter*{Preface}
-\addtocontents{toc}{\protect \vspace*{13.mm}}
-\addcontentsline{toc}{chapter}{\bfseries{Preface}}
-\thispagestyle{plain}\markboth{Preface}{Preface}
-
-% Howdy!
+\chapter*{Abstract}
+% \addtocontents{toc}{\protect \vspace*{13.mm}}
+% \addcontentsline{toc}{chapter}{\bfseries{Preface}}
+\thispagestyle{plain}\markboth{Abstract}{Abstract}
+It is well known that the part of scientific findings that are published in journals are a 
+biased sample of the overall amount of research that is done. Often, editors aim to publish
+new and influential results that will be distributed further by other researchers and
+heighten their journal impact factor. The downside of it is that some of these results
+might only be positive by chance, or because of poor study design. When decision
+makers use this information to take decisions, they are likely to be mislead. \\
+In this study, the prevalence and impact of publication bias is assessed in 
+a large scale analysis. The data stems from the Cochrane Library of Systematic Reviews, the biggest collection
+of clinical trial and public health intervention data. Meta-Analyses of Cochrane
+are scrutinized for small-study effects and excess significance, both signs
+of publication bias. We also adjust the treatment effects from the meta-analysis for publication bias 
+and compare the newly obtained effects with unadjusted treatment effects. In a exploratory analysis, we find
+that around 20\% of meta-analyses are subject to publication bias, and that the
+evidence for treatment efficacy decreases after adjustment. Publication bias
+thus remains a threat to the validity of findings in Cochrane and in clinical research.
+% Because of the
+% amount of data that underlies this analysis, we suggest that previous measures 
+% to curb publication bias need to be enforced and possibly, that new measures have 
+% to be taken to prevent patient harm and strengthen the reliability of clinical research.
+
+\chapter*{Acknowledgments}
+\thispagestyle{plain}\markboth{Acknowledgments}{Acknowledgments}
+I would like to thank all members of the Department of Biostatistics for promoting me along my studies and making this thesis possible.
+Special thanks goes to Dr. Simon Schwab, for thorough support, and to Prof. Dr. Leonhard Held for advice. \\
+Among my friends, I would to thank all students of biostatistics in the years 2018 and 2019 for making this time so pleasant. Samuel
+Pawel was a very good friend with lots of advice and understanding throughout this time, and it was for Eleftheria Michalopoulou 
+that writing this thesis was also fun.\\
+Most important, my family always supported me and gave me confidence in myself. Denise Sternlicht and
+Annatina Kreiliger are two of the main reasons why this thesis has been done, and I would like to dedicate this
+thesis to them.
 
@@
 
-\addtocontents{toc}{\protect \vspace*{10mm}}
-
-\cleardoublepage
+%\addtocontents{toc}{\protect \vspace*{10mm}}
+% \addtocontents{toc}{\protect \vspace*{13.mm}}
+% \addcontentsline{toc}{chapter}{\bfseries{Preface}}
+
+\thispagestyle{plain}\markboth{Contents}{Contents}
+\tableofcontents
+\setkeys{Gin}{width=.8\textwidth}
+
+% Howdy!
+
+%\cleardoublepage
 \pagenumbering{arabic}
@@
 Publication bias has been identified as one of the major concerns in irreproducible research \citep{Bishop.2019}.
-The issue has been discussed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}, \citet{Dwan2013}).
+The issue has been discussed in clinical science by many researchers (\citealp{pb.clinicalscience1}, \citealp{sterne2001}, \citealp{Dwan2013}).
 Consensus is that publication bias exists in clinical science.
@@
 \\
-There is extensive literature on publication bias in meta-analyses, \eg (\citet{pb.clinicalscience.2013}, %\citet{Hopewell02},
-\citet{grey.literature.4}, \citet{grey.literature.3}, \citet{grey.literature.2}).
-The authors agree on that the exclusion of unpublished results in meta-analyses can lead to overestimation of treatment effects (\eg \citet{Egger}).
+There is extensive literature on publication bias in meta-analyses, \eg (\citealp{pb.clinicalscience.2013}, %\citealp{Hopewell02},
+\citealp{grey.literature.4}, \citealp{grey.literature.3}, \citealp{grey.literature.2}).
+The authors agree on that the exclusion of unpublished results in meta-analyses can lead to overestimation of treatment effects (\eg \citealp{Egger}).
 Although there are policies that make it mandatory to make all study results publicly accessible \citep{fda}, it is not clear if the situation has improved yet.
-There are also notable efforts from both journals \citep{Abbasi.2004} and researchers (?) in the same direction.\\
+There are also notable efforts from both journals \citep{Abbasi.2004} and researchers (DORA: San Francisco declaration of research assessment).\\
 There are multiple ways to assess the amount of publication bias.
-For instance, it is possible to follow studies and assess if they are getting published depending on their findings (\citet{Dwan2013}, \citet{publication.fate}, \citet{Lee.2008}).
-One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in the social sciences: \citet{social.sciences.publication.bias}).
-Another way is to compare results in study registries with results published in journals (\eg \citet{pb.clinicalscience.2013}).
+For instance, it is possible to follow studies and assess if they are getting published depending on their findings (\citealp{Dwan2013}, \citealp{publication.fate}, \citealp{Lee.2008}).
+One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in the social sciences: \citealp{social.sciences.publication.bias}).
+Another way is to compare results in study registries with results published in journals (\eg \citealp{pb.clinicalscience.2013}).
 Again one finds systematic differences between published and unpublished results.
@@
 % 
-% The underlying rationale is that journal editors are guided by two simple rules (\citet{excess.significance}, \citet{ioannidis.2019}): 
+% The underlying rationale is that journal editors are guided by two simple rules (\citealp{excess.significance}, \citealp{ioannidis.2019}): 
 % \begin{itemize}
@@
 \end{knitrout}
-\caption{Funnel plots of two meta-analyses: On the left, the improvement in depression syndroms after application of tricyclic antidepressants is compared to placebo.
-The meta-analysis on the right measures the occurence of intracranial haemoerrhage by CT after application of any anti-thrombolytic agent.
+\caption{Funnel plots of two meta-analyses: On the left, the improvement in depression syndromes after application of tricyclic antidepressants is compared to placebo.
+The meta-analysis on the right measures the occurrence of intracranial haemoerrhage by CT after application of any anti-thrombolytic agent.
 All studies are RCT's.}
@@
 
-The purpose of a funnel plot is to visualise if the findings of the studies disperse on both sides of the combined ``true'' effect or if they accumulate with increasing standard error on one particular side.\\
+The purpose of a funnel plot is to visualize if the findings of the studies disperse on both sides of the combined ``true'' effect or if they accumulate with increasing standard error on one particular side.\\
 We see that while the studies in the meta-analysis on the left are not symmetrically distributed, but rather accumulate at the left side, they seem to be more evenly distributed in the left triangle.
@@
 The Cochrane Organisation has specialized on systematic reviews of healthcare interventions.
-Researchers that write a systematic review collect data across studies, review them and try to provide up-to-date information about specific treatment efficacies \citep{cochrane.handbook}.
-By extensive literature scrutinization, they try to circumvent the issue of publication bias.
-%They do not apply funnel plot asymmetry tests to analyse publication bias.
-Earlier research however suggests that the efforts are only partially succesful, and that there still is publication bias within the reviews (\citet{Egger}, \citet{Ioannidis2007}, \citet{kicinsky}, \citet{vanAert.2019}).
-In these publications, Cochrane systematic reviews is analysed with methods to detect publication bias, for example small study effect tests or bayesian hierarchical selection models \citep{kicinsky}.
+Researchers that write a systematic review collect data across studies, review them and try to provide up-to-date information about specific treatment efficacious \citep{cochrane.handbook}.
+By extensive literature examination, they try to circumvent the issue of publication bias.
+Earlier research however suggests that the efforts are only partially successful, and that there still is publication bias within the reviews (\citealp{Egger}, \citealp{Ioannidis2007}, \citealp{kicinsky}, \citealp{vanAert.2019}).
+In these publications, Cochrane systematic reviews is analysed with methods to detect publication bias, for example small study effect tests or Bayesian hierarchical selection models \citep{kicinsky}.
 They all find moderate to large evidence for publication bias in the Database.
@@
 None of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods.
-Also, the results are ironically often presented in the form of dichotomized hypothesis tests, a practice that is partly responsible for publication bias.\\
+Also, the results are ironically often presented in the form of dichotomous hypothesis tests, a practice that is partly responsible for publication bias.\\
 The aim of this thesis is to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides.
-At the end, an approximate, up-to-date estimate of the prevalence of publication bias in the data shall be given.
-To achieve this, methods to detect and adjust for publication bias in meta-analysis are applied on the data.
-\\
-It is also possible to adjust for publication bias with suitable methods.
-These methods are applied on the dataset as well, to achieve publication bias adjusted treatment effect estimates.
-It will be shown if and to what extent treatment effects are overestimated due to publication bias in the Cochrane systematic reviews.
-
-% Already in 1978, scientists raised concern that effect sizes could be overestimated systematically if journals were ``not willing to drop their policy to use statistical significance as one of their criteria for publication'' \citep{dunlap1978}.
-Scientific findings get more attention and are more likely to be published, read and cited if they are implying large effects.
-The issue has been pin-pointed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}).
-The concern is that overestimated efficacy of the treatments could lead to harm to patients.
-\\
-% A measure to counter the presence of single, overestimated study results is a meta-analysis \citep{metaanalysis}, a practice originally developped in psychology.
-Summarized treatment effects and uncertainities should be more robust and reliable.
-The pitfall is that when the entire body of evidence is again a biased sample of studies with high effects, the estimate is again overestimating the true effect.
-% % 
-% 
-% Also after the introduction of mandatory registration of clinical trials
-% 
-% 
-% 
-% Typically, we expect empirical scientific results to be distorted by random noise, such that the results are not equal to the real process that they describe.
-Additionally, one can reasonably assume that the results are also biased to some extent, as the statistical paradigm of precision versus bias would predict: The smaller the noise part of distortion, the more the result should be distorted by bias.
-However, the trade-off is not inevitable and can be minimized by scientific rigor and foresightfull experimental design.
-Large efforts have been made both in theory and practice to improve the quality of experiments and their analysis, such as defining experimental settings that prohibit influence of expectations of the researcher (e.g.
-blinding) or increase sample size in experiments.
-The introduction of randomized clinical trials is for example seen nowadays as a benchmark in clinical science, heavily improving the reliability of its findings.
-\\
-% It is more and more considered a new scientific field by itself to think of and argue about circumstances that improve the quality of scientific findings.
-Statistics is in some sense predestined to contribute to it, because probability and chance concepts are key to understanding of any empirical science.
-\\
-% There are also issues, in which statistics is not thought to be able to contribute much to understanding and to be of little help for solving them.
-For example, the selective attention that the agents in science are paying to new, strong and clear findings in each science is considered merely a psychological and social %, socioeconomic
-% issue.
-It is often explained by the affinity of humans for stories rather than mere facts and for novelties.
-The issue that scientific findings get more attention and are more likely to be published, read and cited is known for many years, but has gained new traction in meta science when the so-called reproducibility crisis emerged in (2003 to 2005).
-Studies such as ...
-showed that even rigid prosecution of study protocols did often not lead to reproduction of previous results when experiments were repeated, which struck empirical science in its core.
-Most reasonably, some concluded that it was a large misunderstanding of statistical tools such as the p-value in the scientific community that lead to this situation (...).
-Although that some measures have been taken since then, and some progress is made, the non-reproducibility of scientific findings remain an acute threat to the relevance and reliability of science.
-Some even argue that certain scientific fields sooner or later will repeat the experience that for example psychology or medicine have made, and are yet to encounter their own reproducibility crisis (...).
-\\
-% Clearly, reproduction of experimental results is the gold standard of testing empirical science, because it reassures the universality and reliability by which certain procedures or effects appear if measured in the correct experimental context.
-However, there are also problems there.
-One can almost never fully exclude chance events to have played a major role in negating or reaffirming the experimental findings (which is of course always the case where noise is present in the data).
-Furthermore, reproduction studies are generally costly and the precise experimental conditions might be hard to reproduce because of lack of information or other reasons.
-\\
-% There is another way to assess the strength of scientific results if the experiment has been conducted more than once (however not with exactly identical protocol as in reproduction studies): Meta-analyses.
-In a meta-analyses, results of multiple (fairly identical) experiments (studies) are summarized to a single result.
-Very often, meta-analyses are not only regarded to be a synthesis of results, but of evidence, thus reflecting the overall and summarized evidence regarding to a scientific question.
-It is on purpose that selective attention to positive, strong results in the scientific literature have been mentioned beforehand, because it is clear how they will affect this second way of reassurance of scientific findings: The meta-analysis will again lead to irreproducible findings if it is based on a set of results that is itself biased.
-Thus, meta-analysis will in this case not reach its purpose of assessing reliability of science, but worsen the problem by reinforcing the confidence in the overestimated over-optimistic effects.
-However, and this is the main topic in this masters thesis, there are some ways to detect irregularities in the body of results that can provide indirect hints that a selective rather than a random sample from a hypothetical population of experiments is present.
-The abundance of the methods to link some features of the sample of experiments to publication bias, as the tendency of scientific literature to over-proportionally include large effects is generally called, also speaks for the relevance of the topic.
-A review in 2017 (...) for example identified 147 (!) conceptually differing methods.\\
-% This speaks as well for the inevitable difficulties that such methods encounter.
-First of all, it is most often impossible to estimate the real selection process, that is the rate by which smaller effects go unnoticed because of selective publication and reporting, because the number of missing results in the studies is not known at the first place and impossible to retrieve.
-Secondly, there is almost no real world data of complete and unbiased meta-analyses, such that evaluations of methods is dependent on simulations.
-So we have, after applying the methods, only indirect information of publication bias, and the extent to what it might influences scientific findings.
-Almost all the time, alternative explanations for the results of the methods might relieve the operators and publishers from the reproval of publication bias.
-However, given the large body of evidence for publication bias collected from other sources (...), in many cases, the results from these methods indeed give a quantitative measure of publication bias.\\
-% In this masters thesis, the answers for two questions are investigated: What is the extent and effect of publication bias in clinical science?
-For this purpose, a dataset from the Cochrane Organization is analysed with commonly used techniques to detect and adjust for publication bias (more precisely, small study effects, as it will be seen later).
-The discussion of the results of the analysis will result in the light of the literature to publication bias.
-%Because the extent of the analysis that is operated here is, to my knowledge, unmatched so far, this dataset
-
-%Before beginning with the main part of this masters thesis, I want to recall some of the most pointed evidence for publication bias that has been collected for publication bias so far. \\
-
-% Meta-analysis is at the core of evidence based medicine because it allows to summarise evidence over multiple studies and provide a more broad view on success and effectivity of clinical treatments.
-The necessity of meta-analyses is also increased by the abundance of data and publications.
-Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to make decisions based on quantitative and scientific criteria.
-% 
-% \vspace{0mm}
-% For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention.
-However, the usefulness of meta-analysis does not restrict to clinical science, but to any empirical and quantiative science.
-% 
-% \vspace{0mm}
-% Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question.
-Meta-analysis can be applied to all studies that are approximately identical in their experimental setup and the way the outcome of the experiments is measured.
-In systematic reviews where meta-analyses are used, the conclusions are most often strongly based on the results and the interpretation of the meta-analysis.
-% 
-% \vspace{0mm}
-% However, there are problems that potentially limit the validity of meta-analysis; the number of studies available can be incomplete or the results of the studies can be biased.
-Some of those problems can be solved or asserted by special statistical methods.
-% 
-% \subsection{Small Study Effects or Publication Bias}
-% When study sample size decreases, the probability of extreme and missleading results in a study increases.
-This becomes a problem if results are selectively published, and therefore available, based on their results.
-When this is the case, one speaks of a small study effect or of ``Publication bias''.
-% 
-% \vspace{0mm}
-% The issue has been discussed extensively in the last years, most often in the context of what has came to be known as the replication crisis.
-The reasons for small study effects are manifold, but originate most often in the myopical acting of agents in science and the lack of statistical education.
-Studies are reported by scientists, published by journals and noticed by readers more often if their findigs are positive and find e.g.
-a substantive difference or effect.
-When doing a meta-analysis, one again obtains biased results.
-% 
-% \vspace{0mm}
-% The reason why that is less of an issue for larger studies is that extreme results are in general less likely and that due to larger effort, a result is published although there has been no clear and positive findings.
-% 
-% \vspace{0mm}
-% While there is generally no way to assert poor study quality, small study effect can in principle be asserted and corrected for statistically.
-This masters thesis will mainly be about statistical methods to detect and adjust for small study effects.
-It can furthermore be divided in two parts:
-% \begin{itemize}
-% \item Methodological part: Collection and discussion of statistical tests and correction methods for small study effects.
-% \item Applied part: Application of the methods to studies of the Cochrane Library of systematic Reviews. Subsequent discussion of the implications
-% of the results for clinical science.
-% \end{itemize}
-% 
-% In contrast to simulation studies, it is not possible to assess critical properties of the methods such as the power of a test, since the truth is not known.
-But based on the amount of data, one can of course try to make extrapolation to tendencies in clinical science in general.
-Moreover, it is still interesting to see how the methods behave in general, especially with respect to each other.
-It may, as an example, be possible to answer the question which statistical test is most conservative and which pooling method is most optimistic on average.
-Comparison with results from simulations may allow to speculate about the reasons when simulation and real world results diverge.
-% 
-% 
-% \subsection{Cochrane and the Cochrane Database of Systematic Reviews}
-% The Cochrane Organization has specialized on systematic reviews in clinical science.
-It publishes and maintains a library with a large number of systematic reviews that are available in some countries to the public.
-% 
-% \vspace{0mm}
-% The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite). 
-% 
-% \vspace{0mm}
-% The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests.
-This might further improve the validity and precision of findings and conclusions that have been made based on this data.
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The research questions are: ``Are effects in meta-analyses \textit{larger} if their standard errors are small, and are there \textit{more} significant effects than expected?'' and ``How can this affect the combined treatment effects as commonly obtained by meta-analysis?''.
+To answer these questions, methods to detect and adjust for publication bias in meta-analysis are applied on the data.\\
+At the end, it will be given an estimate of the extent of publication bias in the Cochrane Library.
+It will also be shown if and to what extent treatment effects are overestimated due to publication bias in Cochrane systematic reviews.
+Because the analysis is exploratory, the results should rather be used in a suggestive than in a confirmatory manner.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-Asuming binomial distribution of the events and using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$\hspace{0.4mm}-value, \eg \cite[98]{held2014}.
+Assuming binomial distribution of the events and using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$\hspace{0.4mm}-value, \eg \cite[98]{held2014}.
 The approximation is only good if there are enough events and sample size is large enough.\\
@@
 One frequently used method to take into account right-censoring is the Cox proportional hazards regression model \citep{Cox}.
-Because the method itself is not applied in this thesis, but only the resulting estimates of the parameters are used, the reader is referred to the extensive literature covering this topic (\eg \citet{Surv}).
+Because the method itself is not applied in this thesis, but only the resulting estimates of the parameters are used, the reader is referred to the extensive literature covering this topic (\eg \citealp{Surv}).
 \\
@@
 The estimation of $\tau^2$ has been subject to some debate in the statistical literature.
-Oftentimes, the method of moment estimator of \citet{tau.estimator} is used.
+Oftentimes, the method of moment estimator of \citealp{tau.estimator} is used.
 We use the measure of heterogeneity, $Q$, and divide by $C$ after having subtracted the degrees of freedom $n-1$:
@@
 The estimators have to be replaced by their estimates in order to get an estimate $\hat{\tau}^2$.\\
-The Paule-Mandel estimator \citep{paulemandel} is considered to have better properties than the method of moments estimator (\eg \citet{tau.estimator.evaluation}).
+The Paule-Mandel estimator \citep{paulemandel} is considered to have better properties than the method of moments estimator (\eg \citealp{tau.estimator.evaluation}).
 Since we defined $w_i = 1/(\se_i^2 + \tau^2)$, it also holds that
@@
 This assumptions are not met for very small sample sizes and very few event counts.
-Alternatively, the Mantel-Haenszel method for risk and odds ratios (see \eg \citet{mantel.haenszel}) could be used in the latter case.
+Alternatively, the Mantel-Haenszel method for risk and odds ratios (see \eg \citealp{mantel.haenszel}) could be used in the latter case.
 
@@
 \\
-Nested groups can be modelled by extending the design matrix $\mathbf{X}$ with an additional column of 1's and using according indices that specify the nesting structure.\\
+Nested groups can be modeled by extending the design matrix $\mathbf{X}$ with an additional column of 1's and using according indices that specify the nesting structure.\\
 An extension of the random intercepts model is the random slopes model, which allows for additional, group-specific slopes with respect to a explanatory variable $x$.
@@
 Hypothesis tests for $\beta = \beta_\textrm{H0}$ can be made using the Wald method.
-
-\section{Publication Bias Tests}
+\\
+It is necessary to check the model assumptions after fitting a linear regression.
+For this purpose, fitted values can be plotted against standardized residuals.
+If the standardized residuals are not dispersed evenly around zero for any size of fitted values, the assumption of the residuals being independently and equally distributed around zero is violated and estimates are biased.
+\\
+
+\section{Publication Bias Assessment}
 The tests that will be presented on the following pages are a common way to detect publication bias.
-A frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill} is not discussed because of its disadvantageous properties, therefore, it will not be discussed here (see \eg \citet{Moreno.2009}).\\
+A frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill} is not discussed because of its disadvantageous properties, therefore, it will not be discussed here (see \eg \citealp{Moreno.2009}).\\
 
 \subsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
-\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+\citealp{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
 A standardized effect size $\theta_i^\star$ can be computed as in \eqref{eq:begg.stand.eff}.
@@
 \subsection{Egger's Test: Weighted Linear Regression Test} \label{sec:Egger}
-Linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citet{Egger}.
+Linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citealp{Egger}.
 Let $\theta/\se$ be the dependent variable $y$ and $1/\se$ the explanatory variable $x$.
@@
 \subsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{sec:Thompson}
-A method proposed in \citet{thompson.sharp} allows for between study variance $\tau^2$, as introduced before in section \ref{sec:meta.analysis}.
+A method proposed in \citealp{thompson.sharp} allows for between study variance $\tau^2$, as introduced before in section \ref{sec:meta.analysis}.
 It extends the previously seen linear regression approach with $x = 1/\se$ and $y = \theta/\se$ by introducing new weights.
@@
 \subsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
-\citet{Schwarzer} developed a test for the correlation between the event counts in the treatment group and the expected event counts $E_t - \mathbb{E}(E_t)$.
+\citealp{Schwarzer} developed a test for the correlation between the event counts in the treatment group and the expected event counts $E_t - \mathbb{E}(E_t)$.
 When the marginals in a two-by-two table and the log odds ratio is fixed, it can be shown that $E_t$ follows a non-central hypergeometric distribution.
@@
 \subsection{Excess Significance Test} \label{sec:excess.significance}
-Publication bias does not need to be accompained by small study effects.
+Publication bias does not need to be accompanied by small study effects.
 In the absence of any treatment effect, significant effects could be included in a meta-analysis on both directions of treatment effects (\ie large \textit{and} small effects) are published.
@@
 \\
-\citet{excess.significance} developed an exploratory test to detect if the proportion of significant findings is larger than expected. 
+\citealp{excess.significance} developed an exploratory test to detect if the proportion of significant findings is larger than expected. 
 %Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study. \\
@@
 \subsection{Adjustment by Regression} \label{sec:regression.adjustment}
-In \citet{limitmeta.2} and \citet{limitmeta}, a random effects model is proposed to obtain unbiased treatment effect estimates. Similarly to regression based tests for small study effects, we have
+In \citealp{limitmeta.2} and \citealp{limitmeta}, a random effects model is proposed to obtain unbiased treatment effect estimates. Similarly to regression based tests for small study effects, we have
 
@@
 
-Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior to the former, because it showed a smaller mean-squared error in simulation studies \citet{limitmeta.2}.
+Simulations in \citealp{limitmeta} suggested that the latter estimate is slightly superior to the former, because it showed a smaller mean-squared error in simulation studies \citealp{limitmeta.2}.
 From the formulas above, it becomes clear that is has a larger standard error.
@@
 Note that the test is very similar to Egger's small study effect test when $\tau^2 = 0$.\\
-In practice ne can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process, and how the choice of the parameters affect the evidence for remaining publication bias (selection).
-\citet{limitmeta} used the method in a simulation for inference purposes, and have implemented it in the \citet{meta.package}.
+In practice one can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process, and how the choice of the parameters affect the evidence for remaining publication bias (selection).
+\citealp{limitmeta} used the method in a simulation for inference purposes, and have implemented it in the \citealp{meta.package}.
 However, in the simulations, the method was outperformed by the regression adjustment method when publication bias was present.
 Especially when event rates in the control group were small and publication bias was strong, bias, mean squared error and coverage was substantially worse.
-Other authors argue that selection models should in general not be used for inference (\eg \citet{selection.assessment}).\\
-The procedure in \citet{limitmeta} is the following: A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \eqref{eq:copas.small.study} is applied.
+Other authors argue that selection models should in general not be used for inference (\eg \citealp{selection.assessment}).\\
+The procedure in \citealp{limitmeta} is the following: A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \eqref{eq:copas.small.study} is applied.
 If all obtained $p$\hspace{0.4mm}-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for adjustment, and the standard, classical random effects meta-analysis is retained.
@@
 \\
-The Pearson's correlation coefficient can be attained by the formulas (\citet{olkin1985dtor}, \cite[48]{Intro.meta})
+The Pearson's correlation coefficient can be attained by the formulas (\citealp{olkin1985dtor}, \cite[48]{Intro.meta})
 
@@
 \begin{align}
-s_r^2 &= \frac{a^2 s_d^2}{(d^2 + a)^3} \nonumber
+\se_r^2 &= \frac{a^2 \se_d^2}{(d^2 + a)^3} \nonumber
 \end{align}
@@
 \end{align}
-
-%SIMPLE LINEAR REGRESSION
-% \begin{align}
-% \hat{\mathbf{\beta}} &= (\mathbf{X}^\top  \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
-% \end{align}
-
-% There is a closed form solution for $\hat{\beta_0}, \hat{\beta}_1$ that minimize the sum of squares:
-% 
-% \begin{align}
-% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} & 
-% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
-% \end{align}
-% 
-% $\bar{x}, \bar{y}$ denotes the sample mean of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$.
-$\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the fitted line.
-Let $\hat{y}_i = \beta_0 + \beta_1 x_i$ and $e_i = y_i - \hat{y}_i$.
-The variances $\se^2_\beta$
-% 
-% 
-% 
-% To test whether the intercept or the slope is close to a certain value, a $t$-test can be used. Simply taking the absolute value of $\beta_0/s_\beta_0$,
-% \begin{align}
-% p &= 2(1-F(|\beta_0/s_\beta_0|)) \nonumber
-% \end{align}
-% 
-% where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom.
-The $p$\hspace{0.4mm}-value will give the evidence against the null-hypothesis $\beta_0 = 0$.
-The procedure for $\beta_1$ is equivalent.
-\\
-% To extend the model to weighted simple linear regression is straightforward.
-Let $w_i$ be the corresponding weight that will be attributed to the pair $x_i, y_i$.
-The least squares minimization problem can be restated
-% 
-% \begin{align}
-% \operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
-% \end{align}
-% 
-% And the corresponding estimators are thus
-% 
-% \begin{align}
-% \hat{\beta_1} &= \frac{\sum_{i = 1}^n w_i(x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n w_i(x_i - \bar{x})^2} & 
-% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
-% \end{align}
-%
-
-% LIMITMETa
-% \vspace{0mm}
-% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
-% 
-% \begin{align}
-% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
-% \end{align}
-% 
-% Letting $M \rightarrow \infty$, we obtain:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
-% \end{align}
-% 
-% Note that:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
-% \end{align}
-% 
-% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
-% 
-% \begin{align}
-% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
-% \end{align}
-% 
-% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-% \end{align}
-% 
-% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
-
-% \section{Basic notation}
-% The notation used here will be used throughout the chapter and exceptions will be noted.
-Let $i$ be the number of a study of a meta analysis with $n$ being the total number of studies.
-$y_{i}$ is then the effect size estimate (usually log odds ratio or mean difference) and $v_{i}$ the variance of the estimate of study $i$.
-$w_{i}$ is used for weights which are defined when necessary, and $\Delta$ usually denotes the summarized or pooled effect estimate of the meta-analysis, and $\eta$ the variance thereof.
-% 
-% \vspace{0mm}
-% In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
-% 
-% 
-% \section{Transformation between effect sizes}
-% Binary and continuous outcome measures can both be transformed into correlations and fishers z-scaled correlations in order to be compared.
-Let $\theta$ be a log odds ratio.
-A standardized mean difference $d$ (also known as Cohen's $d$) is calculated by multiplying $\theta$ with $\sqrt{3}/\pi$.
-The variance of the standardized mean difference is attained as $v_d = v_\theta \sqrt{3}/\pi$.\\
-% We get from a standardized mean difference $d$ to a correlation $r$ by using 
-% \begin{align}
-% r &= \frac{d}{\sqrt{d^2 + a}} \nonumber
-% \end{align}
-% where $a$ is a correction factor if $n_t \neq n_c, a = (n_c + n_t)^2 / n_c n_t$. The variance of $r$ is computed by using 
-% \begin{align}
-% v_r &= v_d
-% \end{align}
-% 
-% Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $v_z$ by using
-% \begin{align}
-% z &= 0.5 \ln(\frac{1 + r}{1 - r}) \nonumber
-% v_z &= \frac{1}{n-3}
-% \end{align}
-% 
-% 
-% 
-% \section{Heterogeneity}
-% In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
-This is called between study variation in contrast to within study variation (noise).
-% 
-% 
-% \vspace{0mm}
-% The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
-Let $w_i$ be the inverse of the variance and $\Delta$ be a summarized effect estimate of your choice as for example a variance-weighted mean \ref{weighted.mean}.
-Then $Q$ can be calculated as in \ref{Q.heterogeneity}
-% 
-% \begin{align}
-% \Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-% Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
-% \end{align}
-% 
-% Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
-Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
-$1 - F(Q)$ will provide the $p$\hspace{0.4mm}-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
-% 
-% \vspace{0mm}
-% Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
-For this purpose, $\tau^2$, the variance of true effects, can be calculated.
-$\tau^2$ is on the same scale as the effect size and reflects the absolute amount of dispersion.
-In practice, $\tau^2$ can be smaller than zero, then it is set to zero.
-% 
-% \begin{align}
-% C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
-% \tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
-% \end{align}
-% 
-% The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
-Note that their estimate can differ substantially and consequently also the estimate of the pooled effect size estimate.
-% 
-% \vspace{0mm}
-% To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
-% 
-% \begin{align}
-% I^2 &= (Q - n + 1)/Q \label{I2.proportion}
-% \end{align}
-% 
-% There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
-% 
-% \section{Meta Analysis}
-% There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
-% First the fixed effect meta-analysis will be explained.
-Note that both methods can be used for continuous or dichotomous outcomes.
-For more details about the methods, see chapter 11 and 12 in \citet{metaanalysis}
-% 
-% 
-% \vspace{0mm}
-% Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
-The pooled estimate $\Delta_{f}$ of the fixed effects model is then the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
-The variance $\eta_{f}$ is the reciprocal of the sum of the weights as shown in \ref{reciproce.variance}.
-% 
-% \begin{align}
-% \Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-% \eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
-% \end{align}
-% 
-% The computation of random effects meta-analysis is more complicated.
-Random effects meta-analysis will give smaller studies with larger variance more weight in the pooled estimate.
-Shortly, the idea is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
-% 
-% \vspace{0mm}
-% The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
-It is used to calculate a new weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
-The variance of $\Delta_{r}$, $\eta_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
-% 
-% \begin{align}
-% v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
-% \Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
-% \eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
-% \end{align}
-% 
-% A $p$\hspace{0.4mm}-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
-% 
-% \begin{align}
-% Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
-% p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
-% \end{align}
-% 
-% \section{Small Study Effects Tests}
-% One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
-If this is not given, one often speaks of publication bias.
-In fact, there can also be other reasons for this (see discussion section).
-A more appropriate term for the phenomenon is small study effect.
-If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
-% 
-% \subsection{Continuous Outcome Tests}
-% % Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. 
-% % First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
-% 
-% \subsubsection{Begg and Mazumdar: Rank Correlation Test}
-% \citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
-% A standardized effect size $y_{i}^\star$ can be computed as in \ref{begg.stand.eff}.
-$v_{i}^\star$ is the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
-$\Delta_{f}$ is the pooled estimate for fixed effect estimate defined in \ref{weighted.mean}.
-% 
-% \begin{align}
-% y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff} \\
-% v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} 
-% \end{align}
-% 
-% A rank correlation test based on Kendall's tau is then used.
-The pairs $(y_{i}^\star, v_{i}^\star)$ that are ranked in the same order are enumerated.
-Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (\eg larger standardized effect size and smaller variance).
-Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
-% 
-% \begin{align}
-% Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
-% \end{align}
-% 
-% The changes in the case of ties are negligible \cite[410]{begg.ties}.
-% 
-% \subsubsection{Egger's Test: Linear Regression Test}
-% Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
-% Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope. 
-% 
-% \vspace{0mm}
-% If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
-The $p$\hspace{0.4mm}-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
-% 
-% \begin{align}
-% p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
-% \end{align}
-% 
-% \subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{Thompson}
-% A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
-Let $\tau^2$ be equal to \ref{Tau.definition}.
-The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
-% 
-% \begin{align}
-% y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
-% \end{align}
-% 
-% Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
-Analogous to Egger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta_{0} = 0$.
-% 
-% \subsection{Dichotomous Outcomes Tests}
-% 
-% The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
-Consequently, the tests above will tend to reject the null-hypothesis too often, \ie that they are not conservative enough.
-A number of solutions to this problem are existing in the literature.
-% 
-% 
-% \subsubsection{Peters Test: Weighted Linear Regression Test}
-% A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
-% 
-% \vspace{0mm}
-% Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
-% 
-% \begin{align}
-% y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
-% v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
-% \end{align}
-% 
-% and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
-Instead of taking the variance as explanatory or independent variable in regression as in Egger's Test, the inverse of the total sample size $x_{i}$ is used, and the variance $v_{i}$ is used as a weight.
-The subsequent test procedure is then identical to Egger's test.
-% 
-% \vspace{0mm}
-% Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
-% 
-% 
-% \subsubsection{Harbord's Test: Score based Test}
-% A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
-The score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
-% 
-% \begin{align}
-% r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
-% v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
-% \end{align}
-% 
-% Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
-Note that $r_{i}/v_{i}$ is also known as peto odds ratio.
-% 
-% \subsubsection{Schwarzer's Test: Rank Correlation Test}
-% \citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
-$\mathbb{E}(E_{t})$ and variance of $E_{t}$ are then estimated based on $e_{t}$.
-% 
-% \vspace{0mm}
-% The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
-% 
-% \subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
-% The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let 
-% 
-% \begin{align}
-% y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}} \\
-% v_{i} = 1/4n_{t} + +/4n_{c}
-% \end{align}
-% 
-% Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances. 
-% 
-% 
-% \section{Small Study Effect Adjustment}
-% \subsection{Trim and Fill}
-% One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
-It is a nonparametric test based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
-% %If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
-% 
-% \vspace{0mm}
-% The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
-First, $\Delta$ is estimated using a fixed or random effects model.
-Then, the $k$ effect size estimates with the smallest standard errors are trimmed, and $\Delta$ is estimated again.
-The procedure is repeated until $k$ is 0 and the funnel plot is symmetric.
-The total number of missing studies is then mirrored with respect to the final effect size estimate $\Delta$, and $\Delta$ and its standard error is then computed to obtain an unbiased estimate.
-% 
-% \subsection{Copas Selection Model}
-% 
-% A method proposed in \cite{Copas1,Copas2,Copas3} assumes that there is a population of studies of which only a part has been published dependent on the variance and size of their estimated effects.
-Studies with small variance and large effect sizes are more likely to be published than studies with large variance and small effect sizes.
-Note that small effect size means here a treatment effect close to the control effect.
-% 
-% Let $y_i$ be the effect size estimate of study $i$. Then 
-% 
-% \begin{align}
-% y_{i} \sim N(\mu_{i}, \sigma_{i}^2) \\
-% \mu_{i} \sim N(\mu, \tau^2)
-% \end{align}
-% 
-% corresponding to a standard random effects meta-analysis.
-$\mu$ is the overall mean effect, $\sigma_{i}^2$ the within study variance and $\tau^2$ the between study variance.
-This is the \textit{population model}.
-% 
-% \vspace{0mm}
-% The \textit{selection model} is defined as follows. Suppose a selection of studies with reported standard errors $s$ (likely different from $\sigma$). Only a proportion 
-% 
-% \begin{align}
-% P(\textrm{select}|s) &= \Phi(a + b/s) \label{copas.selection1}
-% \end{align}
-% 
-% of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
-\ref{copas.selection1} can be rewritten as
-% 
-% \begin{align}
-% z = a + b/s + \delta \label{copas.selection2}
-% \end{align}
-% 
-% with $\delta \sim N(0,1)$. The study with standard error $s$ is only selected if $z$ is positive. Therefore, the larger $z$, the more likely the study is selected.
-% Combining population and selection model for study $i$, we have 
-% 
-% \begin{align}
-% y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \\
-% \mu_{i} \sim N(\mu, \tau^2) \\
-% z_{i} = a + b/s_{i} + \delta_{i}
-% \end{align}
-% 
-% where $(\epsilon_{i}, \delta_{i})$ are standard normal residuals and jointly normal with correlation $\rho = cor(y_{i}, z_{i})$.
-Every given study $i$ in the meta-analysis has $z_{i} > 0$.
-If $\rho$ is large and positive and $z_{i} > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_{i}$ and $\delta_{i}$.
-Thus, the true mean $\mu$ is likely to be overestimated.
-% 
-% \vspace{0mm}
-% Let $u = a + b/s$, $\lambda(u) = \phi(u)/\Phi(u)$ ($\phi$ is the standard normal density function) and $\tilde{\rho} = \sigma/\sqrt(\tau^2 + \sigma^2) \rho$.
-The probability of a study being selected is
-% 
-% \begin{align}
-% P(\textrm{select}|s, y) = P(a,b,s,y) = \Phi(\frac{u + \tilde{\rho}((y - \mu)/\sqrt(\tau^2 + \sigma^2))}{\sqrt{1 - \tilde{\rho^2}}})
-% \end{align}
-% 
-% It can also be shown that the expected value 
-% 
-% \begin{align}
-% \mathbb{E}(y|s, select) = \mu + \rho\sigma\lambda(u) \label{copas.expectation}
-% \end{align}
-% 
-% which shows that the expected value for a study is larger for larger $\sigma$. 
-% 
-% \vspace{0mm}
-% One can compute a likelihood function based on the distribution of $y$ conditional on $z > 0$.
-The likelihood can be maximized for any given pair $a,b$ (can not be estimated since the number of missing studies is not known), and a maximum likelihood estimate $\hat{\mu}$ for the true mean $\mu$ can be obtained.
-One can then perform a sensitivity analysis.
-First, one looks how $\hat{\mu}$ changes for different values of $a,b$.
-One can then compare the fitted values in \ref{copas.expectation} with the real values.
-To test the fit of the model (while keeping all other parts unchanged), the model can be extended in the following way :
-% 
-% \begin{align}
-% y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
-% \end{align}
-% 
-% If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
-Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
-The $p$\hspace{0.4mm}-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
-% 
-% \vspace{0mm}
-% To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
-% 
-% \vspace{0mm}
-% In practice, only a range of values for $a,b$ are reasonable.
-For those values, the quantities above can be calculated and illustrated.
-Values for $\mu$ that have $p$\hspace{0.4mm}-values over a predefined significance threshold can be used for inference of the effect size.
-% 
-% \subsection{Adjustment by Regression}
-% There are multiple ways to adjust for small study effects by regression.
-The general idea is to extrapolate the effect size of a study with a variance of zero based on the given effects and variances.
-% 
-% \citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
-Similarly to what has been seen in Copas selection model, we let $y_{i}$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_{i}}$ as in \ref{limitmeta.regression}.
-% 
-% \begin{align}
-% y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{v_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
-% \end{align}
-% 
-% $\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
-% 
-% \begin{align}
-% \mathbb{E}((y_{i} - \beta_{0})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{ if } \sqrt{v_{i}} \rightarrow \infty \label{limitmeta.infinitesample} \\
-% \mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
-% \end{align}
-% 
-% After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before \eg in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test (see \ref{Thompson}).
-% 
-% \vspace{0mm}
-% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
-% 
-% \begin{align}
-% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
-% \end{align}
-% 
-% Letting $M \rightarrow \infty$, we obtain:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
-% \end{align}
-% 
-% Note that:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
-% \end{align}
-% 
-% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
-% 
-% \begin{align}
-% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
-% \end{align}
-% 
-% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-% \end{align}
-% 
-% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
-
-% \begin{align} \label{cox reg}
-% P(Y < y|\mathbf{x}) = 1 - exp(-exp(h(y) - (\mathbf{x})^\top\beta)
-% \end{align}
-% 
-% See \cite{hothorn} for further information. It specifies the instantaneous risk of an event at time t to be
-% 
-% \begin{align}
-% \lambda_{0}(t)exp((\mathbf{x})^\top\beta) \nonumber
-% \end{align}
-% 
-% The model is regarded as a semi parametric model since it includes the covariates in a linear fashion but leaves the baseline hazard $\lambda_{0}(t)$ unspecified.
-The factor $exp((\mathbf{x})^\top\beta)$ has the interpretation of a hazard ratio between the reference with $\mathbf{x} = 0$.
-The formal definition of the hazard is
-% 
-% \begin{align}
-% h(t) = \lim_{h \to 0} \frac{P(t < T < t + h| T > t)}{h}
-% \end{align}
-% 
-% 
-% \begin{align} \label{generalized linear model}
-% \mathbf{Y}{_{ij}}|U{_i},\epsilon{_{ij}} = (1,x{_i}^\top)\beta + U{_i} + \epsilon{_{ij}}
-% \end{align}
 
@@
 Therefore, the search process is crucial, as a selective search result may impose bias on the sample of studies available, making it a non-random sample.
-For this purpose, the Cochrane Groups are advised to go beyond MEDLINE !!cite!!, because a search restricted to it has been shown to deliver only 30\% to 80\% of available studies.
+For this purpose, the Cochrane Groups are advised to go beyond MEDLINE, because a search restricted to it has been shown to deliver only 30\% to 80\% of available studies.
 ``Time and budget restraints require the review author to balance the thoroughness of the search with efficiency in use of time and funds and the best way of achieving this balance is to be aware of, and try to minimize, the biases such as publication bias and language bias that can result from restricting searches in different ways.'' It is important to note that not only studies, but also study reports are occasionally used in the reviews, as they may provide useful information.
@@
 
-\subsection{Structure and Content}
+\section{Structure and Variables}
 The dataset consists of 6354 systematic reviews from the Cochrane Library with 70662 studies and 744720 results.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 09:08:07 2019
+% Wed Aug 14 09:50:11 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 09:08:08 2019
+% Wed Aug 14 09:50:11 2019
 \begin{table}[ht]
@@
 Similarly, the number of reviews with a maximum of two studies included is 1040, the mean study number is 13.6, the median 8 and the interquartile range 4 and 16 and the 95\% quantile 45.
-The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citet{largest.review}
+The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citealp{largest.review}
 which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1,497 results in total.\\
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Setting row names on a tibble is deprecated.}}\end{kframe}% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug  8 09:08:08 2019
+% latex table generated in R 3.5.1 by xtable 1.8-3 package
+% Wed Aug 14 09:50:11 2019
 \begin{table}[ht]
@@
 If \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR} / \texttt{RR} / \texttt{SMD} / \texttt{MD} / \texttt{Hazard Ratio} / \texttt{Rate Ratio} are used.
-\citet{Ioannidis2007} outlined criteria for application of small study effect tests:
+\citealp{Ioannidis2007} outlined criteria for application of small study effect tests:
 \begin{itemize}
@@
     \path [line] (9) -- (11);
-    \path [line] (10) -- node [btw, xshift = -2.6cm, yshift = -0.5cm] {\texttt{outcome.measure.merged} = \texttt{SMD}} (11);
+    \path [line] (10) -- node [btw, xshift = -3cm, yshift = -0.3cm] {\texttt{outcome.measure.merged} = \texttt{SMD}} (11);
 
@@
 In some more cases, meta-analyses were excluded because their results seemed to be erroneous (1) or because participant numbers were missing (5), necessary to compute the variance of Fisher's z transformed correlation coefficient.
-The latter meta-analyses (all \texttt{outcome.flag} = \texttt{IV}) were only omitted when doing the adjustment based on the $z$-scores, but kept when adjusting based on std.
+The latter meta-analyses (all \texttt{outcome.flag} = \texttt{IV}) were only omitted when doing the adjustment based on the Fisher's $z$ transformed correlations, but kept when adjusting based on std.
 mean differences.
@@
 Subgroups are not indicated in 50.8\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane Review Groups did.
+\\
 The methods described in the methods chapter \ref{ch:methods} most often apply directly to the algorithms used in \texttt{meta} and \texttt{metafor}. \\
@@
 \\
-Details to Copas selection model algorithm and its application can be found in \citet{limitmeta}.
+Details to Copas selection model algorithm and its application can be found in \citealp{limitmeta}.
 In short, two values for $a$ and $b$ in section \ref{sec:copas} were used; a limited range with $a$ between -1.7 and 2, and $b$ between 0.16 and 0.32 was applied first (analog to a most extreme selection process of $P$(select|small trial with sd = 0.4) = 0.1 and P(select|large trial w.
@@
 If there is still no non-significant small study effect, the result was \texttt{NA}.
+
+\section{Software}
 All computations were performed in the \texttt{R} computing environment \citep{R.base}.
 The \texttt{R} packages \texttt{meta} \citep{meta.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments.
-The excess significance test was adapted from \citet{vanAert.2019}.
+The excess significance test was adapted from \citealp{vanAert.2019}.
 For data manipulation procedures, the \texttt{tidyverse} packages were used \citep{tidyverse.package}, and for plotting the \texttt{ggplot2} package \citep{ggplot2}.\\
+
+\section{Data and Code Availability}
+The data of the Cochrane Library of Systematic Reviews is freely available in some countries, in others, the rights are reserved by the Wiley publishing company.
+The code for data processing and analysis can be found osf.io, the DOI of the project is (project not yet online).
 
@@
 
-Meta analyis are based on results of primary studies. Therefore, in a first step, an exploratory plot of the median effect size and it's dependence on the study sample size can be shown. \\
-The absolute value of the median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
+Meta analysis are based on results of primary studies. Therefore, in a first step, an exploratory plot of the median effect size and it's dependence on the study sample size can be shown. \\
+The absolute value of the median Fisher's $z$ transformed correlation for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
 The medians are calculated separately for efficacy and safety outcomes.
@@
 \end{knitrout}
-\caption{Median of the absolute $z$-score across sample size plotted against the total sample size.}
+\caption{Median of the absolute Fisher's $z$ transformed correlation across sample size plotted against the total sample size.}
 \label{z.samplesize}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 13 10:24:59 2019
+% Wed Aug 14 15:13:27 2019
 \begin{table}[ht]
@@
 \\
-To compare the effects of adjustment between meta-analyses of different outcomes, the outcome measures are transformed to standardized mean differences and Fisher's $z$-scores (see section \ref{sec:transformation.effectsizes} for details).
+To compare the effects of adjustment between meta-analyses of different outcomes, the outcome measures are transformed to standardized mean differences and Fisher's $z$ transformed correlations (see section \ref{sec:transformation.effectsizes} for details).
 When comparing to unadjusted effects, fixed or random effects meta-analysis estimates are used as references\\
@@
 An adjusted effect with evidence for publication bias can be regarded as a more realistic estimate of the treatment effect.
-Some very large and very small differences have been omitted in the $z$-score and std.
+Some very large and very small differences have been omitted in the Fisher's $z$ transformed correlation and std.
 mean difference histograms; they are shown in Table \ref{missing.differences}.
@@
 Again, we clearly see that more effect sizes are adjusted downwards.
-Additionally, there is more coincidence between publication bias test statistics and adjustment, \ie positive differences are accompained by large positive test statistics, which is as expected.
+Additionally, there is more coincidence between publication bias test statistics and adjustment, \ie positive differences are accompanied by large positive test statistics, which is as expected.
 \\
@@
 The means in Table \ref{adjustment.difference} suggest that the average reduction is small.
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 69 meta-analyses have their $z$-score reduced by more than 0.13 by regression adjustment (and 5\% or 69 increased by -0.11 or more, fixed effects reference).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 69 meta-analyses have their Fisher's $z$ transformed correlation reduced by more than 0.13 by regression adjustment (and 5\% or 69 increased by -0.11 or more, fixed effects reference).
 Also, std.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 13 10:25:12 2019
+% Wed Aug 14 15:13:41 2019
 \begin{table}[ht]
@@
 The row names indicate which outcome measure, meta-analysis method and adjustment method is used.
-Abbreviations are used for z-score (z) and std.
+Abbreviations are used for Fisher's z transformed correlation (z) and std.
 mean difference (d).
@@
 \endgroup
-\caption{Missing meta-analysis combined treatment effect and adjusted treatment effects. Abbreviations are used for z-score (= z) and std. mean difference (= d).} 
+\caption{Missing meta-analysis combined treatment effect and adjusted treatment effects. Abbreviations are used for Fisher's z transformed correlation (= z) and std. mean difference (= d).} 
 \label{missing.differences}
@@
 A Tukey mean difference plot can reveal systematic differences and biases between the two measurement methods.
-Note that only 26 out of 121 \texttt{IV} outcome data is included when using $z$-score and std.
+Note that only 26 out of 121 \texttt{IV} outcome data is included when using Fisher's $z$ transformed correlation and std.
 mean differences, since not all effects could be transformed.
@@
 Two values have been omitted in the middle plot for std.
-mean difference and one for $z$-score (see Table \ref{missing.differences}).}
+mean difference and one for Fisher's $z$ transformed correlation (see Table \ref{missing.differences}).}
 \label{fig:adjustment.mean.diff}
@@
 There is however a small difference, indicating that regression estimates have a little bit a larger absolute value.
-There might be some bias between adjusted $z$-scores, where regression estimates seem to be somewhat smaller when the mean is a little above zero, and somewhat larger when the mean is a little below zero.
+There might be some bias between adjusted Fisher's $z$ transformed correlations, where regression estimates seem to be somewhat smaller when the mean is a little above zero, and somewhat larger when the mean is a little below zero.
 \\
@@
 It can be seen that the alignment on the diagonal changes depending on the adjustment method.
-The effect of adjustment by copas can be seen when comparing it to random effects meta-analysis.
+The effect of adjustment by Copas can be seen when comparing it to random effects meta-analysis.
 There, less of an effect of adjustment on the evidence can be seen.
@@
 \begin{itemize}
-\item z-value of regression adjustment 10.5 vs fixed effects z-value 5.7: When the funnel plot of these meta-analyses are investigated, it becomes clear that there is no reason to assume publication bias since the smaller studies are near to risk ratios equal to one, and larger studies show larger ratios.
+\item z test statistic of regression adjustment 10.5 vs fixed effects z test statistic 5.7: When the funnel plot of these meta-analyses are investigated, it becomes clear that there is no reason to assume publication bias since the smaller studies are near to risk ratios equal to one, and larger studies show larger ratios.
 Publication bias tests disagree in their findings (R\"ucker's and Harbord's tests: 0.058 and 0.05, and Peters and Schwarzer's test: 0.467 and 0.79).
-\item z-value of regression adjustment 9.24 vs fixed effects z-value 2.51: Asymmetry of the funnel plot could be confirmed when analyzing it with mean differences.
+\item z test statistic of regression adjustment 9.24 vs fixed effects z test statistic 2.51: Asymmetry of the funnel plot could be confirmed when analyzing it with mean differences.
 The change to a larger treatment effect is rather due to large between study heterogeneity and the specific routine of the regression adjustment.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 13 10:25:14 2019
+% Wed Aug 14 15:13:43 2019
 \begin{table}[ht]
@@
 \section{Mixed Effect Models and Publication Bias over Time}
-To test if publication bias in meta-analyses has decreased over time and newer meta-analyses have less bias, a generalized linear model has been set up to analyze all meta-analyses jointly and estimate a single parameter denoting publication bias.\\
+To test if publication bias in meta-analyses has changed over time and newer meta-analyses have less bias, a generalized linear model has been set up to analyze all meta-analyses jointly and estimate a single parameter denoting publication bias.
+The procedure is to first start with the simplest model and consecutively add more explanatory variables and check by means of the AIC, BIC and F-test if the fit of the model has improved.\\
 The dependent variable is the standardized mean differences(therefore, from \texttt{outcome.flag} = \texttt{IV}, only the std.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 13 10:25:22 2019
+% Wed Aug 14 15:13:52 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 13 10:25:24 2019
+% Wed Aug 14 15:13:54 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 13 10:25:26 2019
+% Wed Aug 14 15:13:56 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 13 10:25:29 2019
+% Wed Aug 14 15:13:59 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 13 10:25:31 2019
+% Wed Aug 14 15:14:01 2019
 \begin{table}[ht]
@@
 
-\section{Results in the light of the Literature}\label{sec:discussion.results}
-
-Before discussing the results of the previous analyses, some results of similar studies are discussed briefly and compared to the results of this study, if possible.
+The aim of this study was to assess publication bias in the Cochrane Library, ``the single, most reliable source of evidence in healthcare'' (citation from Cochrane).
+We applied a series of methods to test and adjust for publication bias in meta-analyses that matched our criteria.
+\\
+The main result was that among the analysed meta-analyses, approximately 20\% beared evidence for publication bias.
+Adjustment for publication bias lead to a decrease in evidence for treatment efficacy.
+After comparison with previous studies that analysed publication bias in the Cochrane Library, we found that our results were similar to the results of these studies (\eg \citealp{Egger}, \citealp{Ioannidis2007}).
+Further information can be found in the Appendix\\
+% In this study, evidence for publication bias has been found in approximately 20\% of the meta-analyses.
+The results are oftentimes consistent among different tests and subsets of the data.
+A mixed effects meta regression confirms these findings with very large evidence for small study effects (indicating publication bias).
+Since the results of two-sided tests do not differ substantially from previous findings, the results are in line with previous research.\\
+% There have been proposed a number of reasons for this tendencies in smaller studies (see \citealp{Egger} for a thorough discussion).
+In clinical settings, it might be that the requirement for more study participants in large studies might systematically change the study population.
+However, this systematic differences could influence the results in two ways: If recruitment of participants with a disease is difficult, and thus, also participants with less severe types of the disease are included, it might be that the effect of treatment is larger in the smaller study.
+But one could also argue that the opposite could eventually be the case.
+\\
+% The main cause for funnel plot asymmetry with smaller studies having larger effects is publication bias.
+Publication bias enforces questionable research practices from researchers such as selective outcome reporting, $p$-hacking and data fabrication.
+Larger studies are less affected, and have also in general higher methodological quality \citep{Egger}, which leads to smaller effect sizes.\\
+Presence of publication bias in meta-analyses can ultimately lead to patient harm if decision makers in clinical practice use the meta-analyses to decide about application of a treatment.
+However, publication bias does in general lead to too large confidence in the results of the meta-analyses.
+In some cases, it might be that the  evidence for a treatment in a meta-analysis is an artifact of publication bias.
+This also leads to a waste of resources in science.
+\\
+The fact that Cochrane also uses study reports from Grey literature and other unpublished data (1.5\% of the analysed data), which contain usually smaller effect sizes, likely mitigates our estimate of publication bias.
+% The term publication bias is frequently used in this study, but round((length(which(meta.data$study.data_source == "UNPUB"))/dim(meta.data)[1])*100, 1)\% of the analysis dataset (1) are unpublished results.
+This mitigates the estimated extent of publication bias in this study since it has been shown repeatedly that effects in the grey literature are smaller.
+
+\section{Limitations}
+This is an exploratory study, and the results are rather suggestive than confirmatory.
+As a part of evidence it is supposed to strengthen previous assessments of publication bias and possibly, guide further research.
+\\
+It is clear that publication bias could only be assessed in a part of all meta-analyses of the Cochrane Library and that the extent of publication bias in the remaining data is unknown.
+Because one inclusion criterion was that more than ten study results had to be available for a given research question, the analysed dataset contains rather the part of data with established and enduring research.
+When research is more experimental and exploratory, it may well be that publication bias is an issue as well, or even more of an issue.
+Publication bias is possibly related to more discovery oriented, modern research \citet{ioannidis.2005}.\\
+There is an unknown amount of meta-analyses with secondary outcomes in the analysis.
+It is not well investigated if and how secondary outcomes are affected by publication bias, and how much they are affected by between-study heterogeneity, as researchers might not follow the same stringent protocols when assessing secondary outcomes.
+Together with unremoved adverse effect meta-analyses, which are likely subject to different kinds of publication bias, they can distort or mitigate the estimated extent of publication bias in this study.
+If one assumes that publication bias is not as strong in secondary outcomes as in primary outcomes, and that adverse effects are subject to bias for small effects (as suggested by \citealp{kicinsky}), the extent of publication bias will be underestimated.\\
+Some criticism can be addressed on the methods.
+The small study effect which is used as an indication for publication bias can be caused by other biases such as selective outcome reporting, or poor methodological quality of smaller studies.
+It can also be caused by true heterogeneity between studies; early and small studies are more likely to include high-risk patients for which treatment can have larger benefits.
+Where effect size estimates and their standard errors are not independent (\eg log risk ratios, std.
+mean differences), small study effect can be a statistical artifact.
+However, true heterogeneity between smaller and larger studies might as well mask the presence of publication bias, for example if smaller studies have smaller effects due to true between-study heterogeneity.\\
+Also, small study effect tests do not use statistical significance directly.
+They will fail when there are no significant results, but the smaller studies have larger effects than the larger studies, in which case no publication bias for significant results could exist.
+The only test that is applied that takes into account statistical significance per se is the excess significance test, which is underpowered.
+However, we restricted the meta-analyses such that at least one significant effect had to be included.
+\\
+Most small study effect tests rely on linear regression.
+Linear regression is prone to outliers, especially if the sample size is small.
+The issue is partially resolved by weighting, but the usual procedure to assess if the model assumptions are fulfilled are not possible for such a large number of model fits.\\
+All the criticism also applies for adjustment methods, as they also rely on small study effects.
+A weakness of the regression adjustment is that it also adjusts if the uncertainty in the small study effect is large.
+To compare it in this case with the meta-analysis estimate is difficult because the uncertainty in estimating the small study effect affects the uncertainty of the treatment effect.
+Copas selection model uses the $p$-value threshold of 0.1 to decide if adjustment is necessary or not.
+One could argue that this threshold is somewhat arbitrary.
+When assessing the evidence for the treatment effect being different from the effect under the null, a likelihood ratio test would provide more appropriate results than the Wald test.
+%Selection models do not account for the uncertainity that is contained in the selection process parameters they use, which makes it difficult to use their results to test against the null hypothesis of no treatment effect.\\
+Another issue that the model is not estimating the selection process parameters, but rather applying some criteria of parsimony (the model with least publication bias/selection with $p$-value for small study effect > 0.1 is chosen).
+As the regression model, this model also comes with various assumptions that likely affect the results.
+But in simulations, the methods all had fewer mean-squared error and bias than the classical meta-analysis methods when publication bias was present.\\
+Publication bias can also be present if a meta-analysis lacks a small study effect, for example if significant results are published irrespective of the sign of the effect estimate.
+Methods as the excess significance test of \citealp{excess.significance} are applied to overcome this issue, but the method is known to lack power.
+No methods exist so far to adjust for excess significance.
+This would be a reason to assume that publication bias is underestimated.\\
+Given the large body of evidence for publication bias by other means, it is unlikely that the unexpectedly large proportion of significant test results and the downward corrected treatment effect estimates are merely false positives.
+Of course, the general practice is to apply all the methods in this study carefully, and with background knowledge about each single study in the meta-analyses, to differentiate between true heterogeneity and publication bias.
+But this does not disqualify these results, but stress the necessity that authors of meta-analyses investigate possible publication bias thoroughly.
+% Therefore, the results are not exact and could be improved if more suitable methods are applied.
+The Bayesian approach taken by \citealp{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions.
+\\
+% Furthermore, the sub-partitioning of meta-analyses based on comparison, outcome and subgroup is only one possibility%, which is in fact not recommended by the Cochrane Organisation. 
+% Cochrane usually performs multiple meta-analyses with the same results, for example by doing sensitivity analyses (not an issue in this study, since they are removed) and subgroup analyses and overall analyses.
+One can as well repeat the analysis without considering subgroups.
+This will have the advantage of increasing the sample size, but it will also result in increased heterogeneity in meta-analyses, and if one subgroup with small studies yields large effects, the cause must not be publication bias.
+\\
+% It also has to be said that the removal of safety outcomes is only partially successful.
+This is an issue, because it is not well known if and how the publication probability is affected by the size of safety outcomes.
+\citealp{kicinsky} suggests that they may inversely affect publication (\ie non-significant effects are preferred).\\
+% Also, it has been previously discussed that the method to detect the side on which bias is not working perfectly.
+One could also discuss in more general terms if one can speak of publication bias in meta-analyses %that have only one significant effect out of ten ($n$ = length(which(meta.f$n.sig.single == 1))), \ie
+% if statistical significance is largely absent in a meta-analysis.\\
+
+\subsection{A Note on the Use of Effect Size Measures}
+An inevitable issue for the analysis of publication bias and adjustment for it is the choice of the effect size measure.
+Researchers and journal editors rely on effect sizes as mean differences or log odds ratios to assess treatment efficacy and statistical significance.
+Transformation of the effect sizes might change a significant result to non-significant or vice-versa.
+Thus transformation will lead to a loss of accuracy.
+Furthermore, transformation of mean differences to std.
+mean differences also comes with the unpleasant consequence that effect size and std.
+mean difference are no longer independent (smaller differences for large std.
+errors).
+When transforming odds ratios to std.
+mean differences, the interdependence between effect size and std.
+mean difference is also retained.\\
+Transformation to Fisher's $z$ transformed correlation will abolish this dependency, but since correlations are bounded, linear regression will no longer be suitable to detect very large effect sizes.
+Furthermore, the applied adjustment methods which are based on Fisher's $z$ transformed correlations are not adapted to correlation coefficients and sometimes provide meaningless results (coefficients $> 1$ or $< -1$).
+Thus, one transformation will tend to underestimate publication bias, while the other likely overestimates it, and both are not accurate.
+
+\section{Outlook}
+Given the size and abundance of information in the dataset, the possibilities to investigate sources of bias in the Cochrane Library of Systematic Reviews are not exhausted.
+In particular, one could easily come up with more hypotheses that could be tested in meta meta-regression, as introduced in the last section of the results.
+Many researchers have come up with hypotheses about the reasons and circumstances that promote publication bias, which could be tested if the dataset is extended.\\
+There are numerous suggestions for different measures of publication bias and small study effects, which could be applied on the dataset (see \citealp{mueller.2016}).
+This study mainly relies on suggestions from \citealp{Sterne}, \citealp{Ioannidis2007} and \citealp{limitmeta}.
+It uses most often methods that are well integrated in packages (\citealp{metafor.package}, \citealp{meta.package}).
+Although there are well addressed, mathematical justifications for these methods, there might be better methods not yet tested on large datasets.
+An evaluation of all suggested methods was unfortunately beyond the scope of this study.
+
+\section{Implications}
+As far as we know, this study is so far the largest assessment of publication bias by small study effects and uses also data that has been collected after major efforts have been made to curb publication bias.
+%It is the first analysis of the Cochrane Library of Systematic Reviews also analyzing publication bias using hazard and rate ratios.
+Furthermore, the analysis includes time-to-event data which is, as far as we are aware of, unprecedented, and continuous outcomes, which is unusual.
+Thus we assume that it is so far the most complete, thorough analysis of publication bias in the Cochrane library.
+\\
+We are not aware of any use of one-sided tests for publication bias as used in this study, which allows to look more specifically for publication bias for ``positive'' or desired treatment effects.
+The results indicate that the efforts to curb down publication bias are only partially successful.\\
+Also, it is the first study to extensively adjust the combined effect sizes from meta-analyses for publication bias.
+It has been found repeatedly that publication bias might threaten the validity of the findings of some meta-analyses from Cochrane systematic reviews.
+Cochrane did so far not extend their protocols to publication bias adjustment methods.\\
+Therefore, we suggest that publication bias in meta-analyses of clinical trials remains an important issue to be considered while doing meta-analyses. 
+% Since Cochrane uses results from grey literature to limit the effects of publication bias, but still does not manage to abolish it, there is also the need for journal editors to change their publication policies.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\appendix
+
+% LaTeX file for Chapter 01
+
+\chapter{Appendix}
+
+\section{Comparison of Results with previous Studies}
+
+For the interested reader, some results of similar studies are discussed briefly and compared to the results of this study, if possible. 
 When clear methodological drawbacks are found in the analysis, the reader is referred to chapter \ref{ch:methods} for comments on the disadvantages.
@@
 
-\subsection{\citet{Egger}}
+\subsection{\citealp{Egger}}
 The Cochrane Library (1996 issue 2) and publications from the four leading medicine journals (the Lancet, BMJ, JAMA and Annals of Internal Medicine) between 1993 and 1996 were used to find systematic reviews with randomized controlled trials for the application of Egger's small study effect test.
@@
 
-\subsection{\citet{sutton.2000}}
+\subsection{\citealp{sutton.2000}}
 Out of 397 systematic reviews from the Cochrane Library (complete number for 1998, issue 3), 49 had more than ten included studies and binary outcomes and 48 compared two treatments.
@@
 
-\subsection{\citet{Ioannidis2007}}
+\subsection{\citealp{Ioannidis2007}}
 Data processing steps were however different, and only binary outcomes as used in two-by-two tables were analysed.
@@
 % The results seem to be similar enough to claim that neither the methods nor the data and it's results are differing substantially.
-Because the study relies on more data, it is likely to be more accurate and can possibly add to the findings of \citet{Ioannidis2007}.
+Because the study relies on more data, it is likely to be more accurate and can possibly add to the findings of \citealp{Ioannidis2007}.
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 13 10:26:07 2019
+% Wed Aug 14 15:14:39 2019
 \begin{table}[ht]
@@
 
-\subsection{\citet{souza.2007}}
+\subsection{\citealp{souza.2007}}
 Reviews of the World Health Organization (WHO) Reproductive Health Library (RHL), issue 9, were analysed with the trim-and-fill method.
@@
 
-\subsection{\citet{kicinsky}}
+\subsection{\citealp{kicinsky}}
 The author uses a Bayesian hierarchical selection model, but does not analyse treatment effects, but the parameters of the weight function of the selection model, which is estimated with a Bayesian approach and MCMC sampling.
@@
 The median publication year per meta-analysis was 1997 for efficacy meta-analyses and 1999 for safety meta-analyses.
-Then, a Bayesian two-step hierarchical selection model was applied (\citet{bayesian.selection.model}, \citet{bayesian.selection.model.2}).
+Then, a Bayesian two-step hierarchical selection model was applied (\citealp{bayesian.selection.model}, \citealp{bayesian.selection.model.2}).
 It assumes that the selection process is a two-step weight, which assigns different probabilities to non-significant and significant effects.
@@
 
-\subsection{\citet{vanAert.2019}}
+\subsection{\citealp{vanAert.2019}}
 The Authors of this recent study sample 366 meta-analyses randomly from the Cochrane Library (supposedly 2018 or 2019, not mentioned).
@@
 \subsection{Further Studies on Publication Bias}
-\citet{Zhang.2013} find publication bias in critical care studies with similar methods.
-\citet{Nusch} report publication bias in clinical osteoarthritis research because of funnel plot asymmetry and pledge for routine assessment of publication bias.
-\citet{Dechartres.2013} analyse publication bias based on sample size in meta-analyses from top journals and Cochrane reviews in 93 Meta-analyses and find that, for example, effects in trials with less than 50 patients were 48\% larger than in larger trials.
-\citet{Onishi.2014} find that in 36 Meta-Analyses without comprehensive literature research, there are 19.4\% significant publication bias tests (Egger's test).
-
-\section{Interpretation}
-In this study, evidence for publication bias has been found in approximately 20\% of the meta-analyses.
-The results are often times consistent among different tests and subsets of the data.
-A mixed effects meta regression confirms these findings with very large evidence for small study effects (indicating publication bias).
-Since the results of two-sided tests do not differ substantially from previous findings, the results are in line with previous research.\\
-% There have been proposed a number of reasons for this tendencies in smaller studies (see \citet{Egger} for a thorough discussion).
-In clinical settings, it might be that the requirement for more study participants in large studies might systematically change the study population.
-However, this systematic differences could influence the results in two ways: If recruitment of participants with a disease is difficult, and thus, also participants with less severe types of the disease are included, it might be that the effect of treatment is larger in the smaller study.
-But one could also argue that the opposite could eventually be the case.
-\\
-% The main cause for funnel plot asymmetry with smaller studies having larger effects is publication bias.
-Publication bias enforces questionable research practices from researchers such as selective outcome reporting, $p$-hacking and data fabrication.
-Larger studies are less affected, and have also in general higher methodological quality \citep{Egger}, which leads to smaller effect sizes.\\
-Presence of publication bias in meta-analyses can ultimately lead to patient harm if decision makers in clinical practice use the meta-analyses to decide about application of a treatment.
-On the swiss Cochrane website, it is stated that Cochrane is the ``single most reliable source of evidence on the effects of health care''.
-However, publication bias does in general lead to too large confidence in the results of the meta-analyses.
-In some cases, it might be that the  evidence for a treatment in a meta-analysis is an artifact of publication bias.
-This also leads to a waste of resources in science.
-\\
-The term publication bias is frequently used in this study, but 1.7\% of the analysis dataset (1) are unpublished results.
-This mitigates the estimated extent of publication bias in this study since it has been shown repeatedly that effects in the grey literature are smaller.
-
-\section{Limitations}
-After application of the criteria of \citet{Ioannidis2007}, there are left 11.6 \% of the reviews and 32.9\% of the studies.
-It is not clear if the results also apply for the excluded data, \ie if the extent of publication bias is similar.
-The most restrictive criterium of exclusion was that a meta-analysis had to have at least ten studies.
-The included studies are thus likely to be part of enforced and sustained research efforts.
-When fewer and unparalleled studies are available, the quality of the research is not necessarily better.
-Publication bias may be even more of an issue in more discovery oriented research \citet{ioannidis.2005}.
-By excluding meta-analyses where $I^2 \geq 0.5$, the most extreme cases of publication bias are possibly removed since publication bias increases the between-study heterogeneity.\\
-% Furthermore, the sub-partitioning of meta-analyses based on comparison, outcome and subgroup is only one possibility%, which is in fact not recommended by the Cochrane Organisation. 
-% Cochrane usually performs multiple meta-analyses with the same results, for example by doing sensitivity analyses (not an issue in this study, since they are removed) and subgroup analyses and overall analyses.
-One can as well repeat the analysis without considering subgroups.
-This will have the advantage of increasing the sample size, but it will also result in increased heterogeneity in meta-analyses, and if one subgroup with small studies yields large effects, the cause must not be publication bias.
-\\
-It also has to be said that the removal of safety outcomes is only partially successful.
-This is an issue, because it is not well known if and how the publication probability is affected by the size of safety outcomes.
-\citet{kicinsky} suggests that they may inversely affect publication (\ie non-significant effects are preferred).\\
-Also, it has been previously discussed that the method to detect the side on which bias is to be expected can fail and provide meaningless results.
-One could also discuss in more general terms if one can speak of publication bias in meta-analyses that have only one significant effect out of ten ($n$ = 417), \ie if statistical significance is largely absent in a meta-analysis.\\
-There is also criticism that one can address on the methods.
-The small study effect which is used as a indication for publication bias can be caused by other biases such as; selective outcome reporting and poor methodological quality of smaller studies.
-It can also be caused by true heterogeneity between studies; early and small studies are more likely to include high-risk patients for which treatment can have larger benefits.
-\\
-
-It is possible that the results are caused by systematic differences in the population of study participants only.
-This is considered rather unlikely.
-Other criticism is more severe.
-The small study effect tests applied do not account for statistical significance of effects directly.
-They work because smaller studies with larger errors need larger effects to be significant.
-The only test that is applied that takes into account statistical significance per se is the excess significance test, which is underpowered.\\
-The criticism also applies for adjustment methods, as they also rely on small study effects.
-A weakness of the regression adjustment is that it also adjusts if the uncertainty in the small study effect is large.
-To compare it in this case with the meta-analysis estimate is difficult because the uncertainty in estimating the small study effect affects the uncertainty of the treatment effect.
-Copas selection model uses the $p$-value threshold of 0.1 to decide if adjustment is necessary or not.
-One could argue that this threshold is arbitrary.
-Additionally, the threshold is used in two manners: first to decide if adjustment is necessary at all, and secondly, if the adjusted model does suitably account for publication bias ($p$ > 0.1).
-Hypothesis tests against the null hypothesis can however not be used to decide in favor of the null-hypothesis, and a separate test would be needed there.
-\\
-With Copas selection model, it is in general the issue that the model is not estimating the selection process parameters, but rather applying some criteria of parsimony (the model with least publication bias/selection with $p$-value for small study effect > 0.1 is chosen).
-\\
-Publication bias can also be present if a meta-analysis lacks a small study effect, for example if by chance, the smaller studies were published irrespectively of the statistical significance of their findinfs.
-Methods as the excess significance test of \citet{excess.significance} are applied to overcome this issue, but the method is known to lack power.
-No methods exist so far to adjust for excess significance.\\
-Therefore, the results are not exact and could be improved if more suitable methods are applied.
-The Bayesian approach taken by \citet{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions.
-\\
-
-\section{Outlook}
-Given the size and abundance of information in the dataset, the possibilities to investigate sources of bias in the Cochrane Library of Systematic Reviews are not exhausted (see for example in \citet{ioannidis.2017}).
-In particular, one could easily come up with more hypotheses that could be tested in meta meta-regression, as introduced in the last section of the results.
-Many researchers have come up with hypotheses about the reasons and circumstances that promote publication bias, which could be tested if the information is extended.\\
-There are numerous suggestions for different measures of publication bias and small study effects, which could be applied on the dataset (see \citet{mueller.2016}).
-This study mainly relies on suggestions from \citet{Sterne}, \citet{Ioannidis2007} and \citet{limitmeta}.
-It uses most often methods that are well integrated in packages (\citet{metafor.package}, \citet{meta.package}).
-Although there are well addressed, mathematical justifications for these methods, there might be better methods not yet tested on large datasets.
-An evaluation of all suggested methods was unfortunately beyond the scope of this study.
-
-\section{Implications}
-This study is so far the largest assessment of publication bias by small study effects and uses data that has been collected after major efforts have been made to curb publication bias.
-It is the first analysis of the Cochrane Library of Systematic Reviews also analyzing publication bias using hazard and rate ratios.
-The results indicate, similarly to other studies, that the efforts did not yet resolve the issue.
-\\
-Also, it is the first study to extensively adjust the combined effect sizes from meta-analyses for publication bias.
-It has been found repeatedly that publication bias might threaten the validity of the findings of some meta-analyses from Cochrane systematic reviews.
-Cochrane did so far not extend their protocols to publication bias tests or adjustment methods.
-Especially when a lot of studies are available, the use of adjustment methods might resolve this issue.
-\\
-Since Cochrane uses results from grey literature to limit the effects of publication bias, but still does not manage to abolish it, there is also the need for journal editors to change their publication policies.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-%<<'child-chapterA1', child='chapterA1.Rnw'>>=
-%@
+\citealp{Zhang.2013} find publication bias in critical care studies with similar methods.
+\citealp{Nusch} report publication bias in clinical osteoarthritis research because of funnel plot asymmetry and pledge for routine assessment of publication bias.
+\citealp{Dechartres.2013} analyse publication bias based on sample size in meta-analyses from top journals and Cochrane reviews in 93 Meta-analyses and find that, for example, effects in trials with less than 50 patients were 48\% larger than in larger trials.
+\citealp{Onishi.2014} find that in 36 Meta-Analyses without comprehensive literature research, there are 19.4\% significant publication bias tests (Egger's test).
+
+\section{R Session information}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlkwd{sessionInfo}\hlstd{()}
+\end{alltt}
+\begin{verbatim}
+## R version 3.5.1 (2018-07-02)
+## Platform: x86_64-apple-darwin15.6.0 (64-bit)
+## Running under: macOS  10.14.5
+## 
+## Matrix products: default
+## BLAS: /Library/Frameworks/R.framework/Versions/3.5/Resources/lib/libRblas.0.dylib
+## LAPACK: /Library/Frameworks/R.framework/Versions/3.5/Resources/lib/libRlapack.dylib
+## 
+## locale:
+## [1] en_US.UTF-8/en_US.UTF-8/en_US.UTF-8/C/en_US.UTF-8/en_US.UTF-8
+## 
+## attached base packages:
+## [1] stats     graphics  grDevices utils     datasets  methods   base     
+## 
+## other attached packages:
+##  [1] nlme_3.1-137    corrgram_1.13   bindrcpp_0.2.2  rvest_0.3.2    
+##  [5] xml2_1.2.0      xtable_1.8-3    metafor_2.1-0   Matrix_1.2-15  
+##  [9] gridExtra_2.3   metasens_0.3-2  meta_4.9-4      forcats_0.3.0  
+## [13] stringr_1.3.1   dplyr_0.7.8     purrr_0.2.5     readr_1.2.1    
+## [17] tidyr_0.8.2     tibble_1.4.2    ggplot2_3.1.0   tidyverse_1.2.1
+## [21] testit_0.9      knitr_1.20     
+## 
+## loaded via a namespace (and not attached):
+##  [1] Rcpp_1.0.0         lubridate_1.7.4    lattice_0.20-38   
+##  [4] gtools_3.8.1       assertthat_0.2.0   digest_0.6.18     
+##  [7] foreach_1.4.4      R6_2.3.0           cellranger_1.1.0  
+## [10] plyr_1.8.4         backports_1.1.2    evaluate_0.12     
+## [13] httr_1.3.1         highr_0.7          pillar_1.3.0      
+## [16] gplots_3.0.1.1     rlang_0.3.0.1      lazyeval_0.2.1    
+## [19] readxl_1.1.0       gdata_2.18.0       rstudioapi_0.8    
+## [22] labeling_0.3       munsell_0.5.0      broom_0.5.0       
+## [25] compiler_3.5.1     modelr_0.1.2       pkgconfig_2.0.2   
+## [28] tidyselect_0.2.5   seriation_1.2-7    codetools_0.2-15  
+## [31] dendextend_1.12.0  viridisLite_0.3.0  crayon_1.3.4      
+## [34] withr_2.1.2        bitops_1.0-6       MASS_7.3-51.1     
+## [37] grid_3.5.1         jsonlite_1.5       gtable_0.2.0      
+## [40] registry_0.5-1     magrittr_1.5       scales_1.0.0      
+## [43] KernSmooth_2.23-15 cli_1.0.1          stringi_1.2.4     
+## [46] viridis_0.5.1      iterators_1.0.10   tools_3.5.1       
+## [49] glue_1.3.0         gclus_1.3.2        hms_0.4.2         
+## [52] colorspace_1.3-2   cluster_2.0.7-1    caTools_1.17.1.1  
+## [55] TSP_1.1-7          bindr_0.1.1        haven_2.0.0
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+% 
+% 
+% \section{Data Pre-processing}
+% 
+% <<eval=FALSE>>=
+% #Dataset processing function to get transformed effect sizes, p-values, event 
+% # counts with increments, etc. :
+% pb.process3 <- function(data){
+%   data <- data %>% mutate(meta.id = 
+%             group_indices(., id, comparison.id, outcome.id, subgroup.id)) %>%
+%     group_by(meta.id) %>% mutate(study.id2 = row_number()) %>% ungroup()
+%   
+%   #Mark duplicate effects between meta-analyses:
+%   data <- data %>% group_by(meta.id) %>%
+%     mutate(n = n())  %>% ungroup() %>% group_by(id) %>% 
+%     mutate(dupl.id = 
+%          dupl.finder(effects = effect, names = study.name, metas = meta.id), 
+%            dupl.remove = 
+%   dupl.max.finder(duplicate.index = dupl.id, study.number = n, metas = meta.id)) %>% 
+%     ungroup()
+%   
+%   data <- data %>% mutate(lrr = NA,
+%     var.lrr = NA,
+%     hedgesg = NA,
+%     var.hedgesg = NA,
+%     cohensd = NA,
+%     var.cohensd = NA,
+%     smd.ordl = NA,
+%     var.smd.ordl = NA,
+%     pval.single = NA, 
+%     cor.pearson = NA,
+%     var.cor.pearson = NA,
+%     z = NA,
+%     var.z = NA,
+%     events1c = NA,
+%     events2c = NA,
+%     sig.single = NA,
+%     smd.pool = NA,
+%     se.smd.pool = NA)
+% 
+%   
+%   cont.ind <- which(data$outcome.flag == "CONT")
+%   bin.ind <- which(data$outcome.flag == "DICH")
+%   IV.ind <- which(data$outcome.flag == "IV")
+%   #----------------------------------------------------------------------------------------------#
+%   
+%   #Outcome.flag == "DICH"
+%   data[bin.ind,] <- escalc(data = data[bin.ind,], ai = events1, n2i = total2, 
+%                            ci = events2, n1i = total1, 
+%                            to = "only0",
+%                            add = 1/2,
+%                            measure = "RR", append = T, 
+%                       var.names = c("lrr", "var.lrr")) #Calculate Risk Ratios
+% 
+%   data[bin.ind,] <- escalc(data = data[bin.ind,], ai = events1, n2i = total2, 
+%                            ci = events2, n1i = total1, 
+%                            to = "only0",
+%                            add = 1/2,
+%                            measure = "OR2DL", append = T, 
+%   var.names = c("smd.ordl", "var.smd.ordl")) #Calculate SMD (w. logistic transf.)
+% 
+%   #What to do if there are 0/total cells:
+%   data[bin.ind,] <- data[bin.ind,] %>% 
+%     mutate(events1c  = case_when(events1 == 0 ~ events1 + 0.5,
+%                                  events2 == 0 ~ events1 + 0.5,
+%                                  events1 - total1 == 0 ~ events1 - 0.5,
+%                                  events2 - total2 == 0 ~ events1 - 0.5,
+%                                  TRUE ~ events1),
+%            events2c = case_when(events2 == 0 ~ events2 + 0.5,
+%                                 events1 == 0 ~ events2 + 0.5,
+%                                 events2 - total2 == 0 ~ events2 - 0.5,
+%                                 events1 - total1 == 0 ~ events2 - 0.5,
+%                                 TRUE ~ events2))
+%   
+%   #What to do if there is one zero and one total:
+%   data[bin.ind,] <- data[bin.ind,] %>% 
+%     mutate(events1c  = case_when(events2 == 0 & events1 - total1 == 0 ~ events1,
+%                                  events1 == 0 & events2 - total2 == 0 ~ events1,
+%                                  TRUE ~ events1c),
+%            events2c = case_when(events2 == 0 & events1 - total1 == 0 ~ events2,
+%                                 events1 == 0 & events2 - total2 == 0 ~ events2,
+%                                 TRUE ~ events2c))
+%   data[bin.ind, "pval.single"] <- data[bin.ind, ] %>% 
+%     mutate(pval.single = 2*(1-pnorm(abs(lrr/sqrt(var.lrr))))) %>% select(pval.single)
+%   #----------------------------------------------------------------------------------------------#
+%   
+%   #Outcome.flag == "CONT"
+%   data[cont.ind,] <- escalc(data = data[cont.ind,], m1i = mean1, m2i = mean2, 
+%                             sd1i = sd1, sd2i = sd2, n1i = total1, n2i = total2,
+%                             measure = "SMD" , append = T, 
+%                 var.names = c("hedgesg", "var.hedgesg")) #Calculate Hedge's g
+%   
+%   data[cont.ind, ] <- data[cont.ind, ] %>% 
+%     mutate(cohensd = (mean1 - mean2)/sqrt((((total1 - 1)*sd1^2) + 
+%                     (total2 - 1)*sd2^2)/(total1 + total2 - 2)),
+%            var.cohensd = ((total1 + total2)/(total1 * total2)) + 
+%              (cohensd^2)/(2*(total1 + total2)))
+% 
+%   data[cont.ind, ] <- data[cont.ind, ] %>% 
+%     mutate(cohensd = case_when(sd1 == 0 ~ NA_real_,
+%                                sd2 == 0 ~ NA_real_,
+%                                total2 == 0 ~ NA_real_,
+%                                total1 == 0 ~ NA_real_,
+%                                TRUE ~ cohensd))
+%   
+%   #p-value for continuous outcomes (Student):
+%   data[cont.ind, "pval.single"] <- data[cont.ind, ] %>% 
+%     mutate(t = (mean1 - mean2)/(sqrt((((total1-1)*sd1^2) + (total2-1)*sd2^2)/
+%                           (total1 + total2 -2))*sqrt((1/total1)+(1/total2))), 
+%            pval.single = 2*(1-pt(abs(t), df = total1 + total2 - 2))) %>% 
+%     select(pval.single)
+%   
+%   sd1.0 <- which(data$outcome.flag == "CONT" & data$sd1 == 0) 
+%   sd2.0 <- which(data$outcome.flag == "CONT" & data$sd2 == 0)
+%   sd.0 <- union(sd1.0, sd2.0)
+%   data[sd.0, "pval.single"] <- NA #Such that p-value here is not equal to zero
+%   #----------------------------------------------------------------------------------------------#
+%   
+%   #Outcome.flag == "IV"
+%   data[IV.ind, "pval.single"] <- data[IV.ind, ] %>% 
+%     mutate(pval.single = 2*(1-pnorm(abs((effect)/se)))) %>% 
+%     select(pval.single)
+%   #----------------------------------------------------------------------------------------------#
+%   
+%   #Declare smd.ordl, cohensd and SMD of IV flag all as "smd.pool":
+%   data <- data %>% 
+%     mutate(smd.pool = case_when(outcome.flag == "DICH" ~ smd.ordl,
+%                                 outcome.flag == "CONT" ~ cohensd,
+%                                 outcome.flag == "IV" & 
+%                                   outcome.measure.merged == "SMD" ~ effect,
+%                                 TRUE ~ NA_real_),
+%            se.smd.pool = case_when(outcome.flag == "DICH" ~ sqrt(var.smd.ordl),
+%                                    outcome.flag == "CONT" ~ sqrt(var.cohensd),
+%                                    outcome.flag == "IV" & 
+%                                      outcome.measure.merged == "SMD" ~ se,
+%                                    TRUE ~ NA_real_))
+%   #----------------------------------------------------------------------------------------------#
+%   
+%   #Transform effect sizes:
+%   smd.pool.ind <- which(!is.na(data$smd.pool))
+%   
+%   #Pearson correlation:
+%   data[smd.pool.ind, "cor.pearson"]<- data[smd.pool.ind, ] %>% mutate(
+%     a = ((total1 + total2)^2)/(total1*total2),
+%     cor.pearson  = smd.pool/sqrt((smd.pool^2) + a),
+%     var.cor.pearson = ((a^2)*se.smd.pool^2)/(((smd.pool^2)+a)^3)) %>% 
+%     select(cor.pearson)
+%   
+%   data[smd.pool.ind, "var.cor.pearson"]<- data[smd.pool.ind, ] %>% 
+%     mutate(
+%     a = ((total1 + total2)^2)/(total1*total2),
+%     cor.pearson  = smd.pool/sqrt((smd.pool^2) + a),
+%     var.cor.pearson = ((a^2)*se.smd.pool^2)/(((smd.pool^2)+a)^3)) %>% 
+%     select(var.cor.pearson)
+%   
+%   #Fisher's z-score:
+%   data[smd.pool.ind, "z"] <- data[smd.pool.ind, ] %>% 
+%     mutate(z = atan(x = cor.pearson),
+%            var.z= 1/(total1 + total2 - 3)) %>% select(z)
+%   data[smd.pool.ind, "var.z"] <- data[smd.pool.ind, ] %>% 
+%     mutate(z = atan(x = cor.pearson), 
+%            var.z= 1/(total1 + total2 - 3)) %>% select(var.z)
+%   
+%   #----------------------------------------------------------------------------------------------#
+%   data$sig.single <- ifelse(data$pval.single < 0.05, 1, 0)
+%   
+%   return(data)
+% }
+% 
+% 
+% ########################################################################################################
+% 
+% #Function to find sensitivity analyses.  The function gives all meta-analyses 
+% #that are subdivided
+% #into sensitivity analyses a common number. 
+% #*to use with "data %>% mutate(.. = dupl.finder(..))"*
+% dupl.finder <- function(effects, names, metas){
+%   
+%   results <- rep(NA, times = length(effects))
+%   meta.double.marker <- 1
+%   
+%   
+%   for(u in seq_along(effects)){
+%     
+%     if(is.na(results[u])){
+%       
+%       double.indices <- which(effects[u] == effects & names[u] == names)
+%       
+%       if(length(double.indices) > 1){
+%     #If any meta-analysis has already duplicates, give all the same double marker
+%         if(any(!is.na(results[double.indices]))){ 
+%           
+%           already.marked <- which(!is.na(results[double.indices]))
+%           meta.double.marker.2 <- unique(results[double.indices[already.marked]])
+%           #Collect meta.ids with same double markers
+%           meta.ids.2 <- unique(metas[which(results %in% meta.double.marker.2)]) 
+%           meta.ids <- metas[double.indices] #Collect metas with the same results
+%           
+%           meta.ids.pooled <- union(meta.ids, meta.ids.2)
+%           meta.indices <- which(metas %in% meta.ids.pooled)
+%           results[meta.indices] <- meta.double.marker
+%           
+%         } else{
+%           
+%           meta.ids <- metas[double.indices]
+%           meta.indices <- which(metas %in% meta.ids)
+%           results[meta.indices] <- meta.double.marker
+%           
+%         }
+%       } else results[u] <- 0
+%       
+%       meta.double.marker <- meta.double.marker + 1
+%     }}
+%   return(results)
+% }
+% 
+% #Function picks the largest meta-analysis within a set of sensitivity analyses,
+% #and assigns it a "0" *to use with "data %>% mutate(.. = dupl.finder(..))":*
+% dupl.max.finder <- function(duplicate.index, study.number, metas){
+%   results <- rep(NA, length(duplicate.index))
+%   
+%   for(u in seq_along((duplicate.index))){
+%     
+%     duplicate.indices <- which(duplicate.index %in% duplicate.index[u])
+%     
+%     if(duplicate.index[u] != 0){
+%       
+%       meta.ids <- metas[duplicate.indices]
+%       
+%       max.meta.id <- meta.ids[which.max(study.number[duplicate.indices])]
+%       max.meta.indices <- which(metas %in% max.meta.id)
+%       if(length(unique(max.meta.id)) < 2){
+%         results[max.meta.indices] <- 0
+%       } else print("error")
+%       
+%     } else results[duplicate.indices] <- 0
+%     
+%   }
+%   
+%   results[is.na(results)] <- 1
+%   
+%   return(results)
+% }
+% @
+% 
+% \section{Analysis}
+% 
+% Data is subdivided into meta-analyses, and after all meta-analyses are excluded that are not suited for analysis, meta-analyses are done and saved.
+% "data.ext2" is the dataset processed with the previously introduced "pb.process3" function. Functions defined in the global environment are marked with
+% a "*USER.DEF*". They can be found at the end of the section.
+% 
+% <<eval = FALSE>>=
+% #Load data:
+% # rm(list = ls())
+% # PATH_HOME = path.expand("~") # user home
+% # PATH = file.path(PATH_HOME, 'Data/PubBias')
+% # PATH2 = file.path(PATH_HOME, 'PubBias')
+% # FILE = 'cochrane_2019-07-04.csv'
+% # PATH_DATA = file.path(PATH, 'data')
+% # PATH_CODE = file.path(PATH2, 'code')
+% # PATH_RESULTS = file.path(PATH2, 'results_new')
+% # PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+% 
+% source(file.path(PATH_CODE, 'PubBias_functions.R')) #Load user defined functions
+% load(file.path(PATH_DATA, "PubBias_2019-07-19.RData")) #Load data as contributed 
+% #by Simon Schwab.
+% # load(file.path(PATH_RESULTS, "data_used_for_analysis.RData")) 
+% data.ext2 <- pb.process3(data) #*USER.DEF*
+% 
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% # PRE-ANALYSIS PART - EXCLUDE UNSUITABLE META-ANALYSES:
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #To skip pre-analysis:
+% # load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% # # ---------- Uncomment to run pre-analysis --------------
+% # # Get exclusion critetia (I-squared, n. sig. findings, s.e. ratio, dupl.index):
+% meta.info.bin <- data.ext2 %>% filter(outcome.flag == "DICH") %>%
+%   group_by(meta.id) %>%
+%   mutate(n.pre = n()) %>% filter(n.pre >= 10) %>%
+%   filter(!all(events1 == 0) & !all(events2 == 0)) %>% #No events
+%   mutate(se.lrr = sqrt(var.lrr)) %>%
+%   summarize(dupl.remove = unique(dupl.remove),
+%             id = unique(id),
+%             outcome.desired = unique(outcome.desired),
+%             n.sig.single = sum(sig.single, na.rm = T),
+%             se.min = min(se.lrr, na.rm = T),
+%             se.max = max(se.lrr, na.rm = T))
+% 
+% meta.info.cont <- data.ext2 %>% filter(outcome.flag == "CONT") %>%
+%   group_by(meta.id) %>%
+%   mutate(n.pre = n()) %>% filter(n.pre >= 10) %>%
+%   filter(!all(mean1 == 0) & !all(mean2 == 0)) %>% #No means
+%   filter(!all(sd1 == 0) | !all(sd2 == 0)) %>% #No sd's
+%   summarize(dupl.remove = unique(dupl.remove),
+%             id = unique(id),
+%             outcome.desired = unique(outcome.desired),
+%             n.sig.single = sum(sig.single, na.rm = T),
+%             se.min = min(se, na.rm = T),
+%             se.max = max(se, na.rm = T))
+% 
+% meta.info.iv <- data.ext2 %>%
+%   group_by(meta.id) %>%
+%   mutate(n.pre = n()) %>% filter(n.pre >= 10) %>%
+%   filter(outcome.flag == "IV") %>%
+%   filter(outcome.measure.merged == "Rate Ratio" | 
+%            outcome.measure.merged == "SMD" |
+%            outcome.measure.merged == "MD" | 
+%            outcome.measure.merged == "Hazard Ratio" |
+%            outcome.measure.merged == "OR" | 
+%            outcome.measure.merged == "RR") %>% #Remove outcomes w. unclear def.
+%   summarize(dupl.remove = unique(dupl.remove),
+%             id = unique(id),
+%             outcome.desired = unique(outcome.desired),
+%             n.sig.single = sum(sig.single, na.rm = T),
+%             se.min = min(se, na.rm = T),
+%             se.max = max(se, na.rm = T))
+% 
+% meta.info.pre <- rbind(meta.info.bin, meta.info.cont, meta.info.iv) 
+% #To save to control how many are excluded
+% 
+% meta.info.pre <- meta.info.pre %>%
+%   filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) 
+% #No withdrawn meta-analyses
+% 
+% 
+% meta.info <- meta.info.pre %>% 
+%   filter(n.sig.single > 0) %>% #At least one significant result
+%   filter((se.max^2)/(se.min^2) > 4) %>% #variance ratio > 4
+%   filter(dupl.remove == 0) %>% #no duplicates
+%   filter(outcome.desired == "efficacy") #Only efficacy outcomes
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Meta-analysis to get I2 (random effects meta-analysis):
+% meta.id.vector.org.ranef <- meta.info$meta.id #Do meta-analysis for each of those
+% 
+% meta.org.ranef.list <- list()
+% counter <- 0
+% for(u in meta.id.vector.org.ranef){
+%   counter <- counter + 1
+%   temp <- data.ext2 %>% filter(meta.id == u)
+%   print(c(u, counter))
+%   meta.org.ranef.list[[counter]] <- meta.fct.ranef.mom(temp)
+% }
+% 
+% exclusion.estimates <- cbind(
+%   meta.id = meta.id.vector.org.ranef,
+%   n = unlist(lapply(meta.org.ranef.list, 
+%                     FUN = function(meta.analysis){meta.analysis$k})),
+%   Q = unlist(lapply(meta.org.ranef.list, 
+%                     FUN = function(meta.analysis){meta.analysis$QE})))
+% 
+% 
+% meta.info.pre2 <- merge(meta.info, exclusion.estimates, by = "meta.id")
+% meta.info.I2 <- meta.info.pre2 %>% 
+%   rowwise() %>% mutate(I2  = max(0, (Q - n + 1)/Q)) #calculate I2
+% meta.info <- meta.info.I2 %>% filter(n > 9) %>% 
+%   filter(I2 < 0.5) #exclude I2 >= 0.5
+% meta.id.vector <- meta.info$meta.id #Vector of meta-ids that match the criteria.
+% 
+% save(meta.id.vector, file =  file.path(PATH_RESULTS, "meta_id_vector.RData"))
+% save(meta.info.I2, file =  file.path(PATH_RESULTS, "meta_id_I2.RData"))
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Get more extensive information from the original dataset about the meta-analyses:
+% meta.info.extended <- data.ext2 %>% 
+%   filter(meta.id %in% meta.id.vector) %>% 
+%   group_by(meta.id) %>%
+%   summarize(id = unique(id),
+%             outcome.flag = unique(outcome.flag),
+%             comparison.nr = unique(comparison.nr),
+%             comparison.name = unique(comparison.name),
+%             outcome.name = unique(outcome.name),
+%             outcome.nr = unique(outcome.nr),
+%             subgroup.name = unique(subgroup.name),
+%             subgroup.nr = unique(subgroup.nr),
+%             outcome.measure.merged = unique(outcome.measure.merged),
+%             outcome.measure = unique(outcome.measure),
+%             outcome.desired = unique(outcome.desired),
+%             mean.samplesize = mean(total1 + total2, na.rm = T),
+%             total.samplesize = sum(total1 + total2),
+%             var.samplesize = var(total1 + total2, na.rm = T),
+%             min.samplesize = min(min(total1, na.rm = T), min(total2, na.rm = T)),
+%             total.events = sum(events1 + events2),
+%             mean.events = mean(events1 + events2),
+%             mean.publication.year = mean(study.year, na.rm = TRUE),
+%             first.publication.year = min(study.year, na.rm = T),
+%             #*USER.DEF* function to detect the expected side of bias
+%             side = bias.side.fct2(outcome = outcome.flag, outcome.measure.merged, 
+%                                   lrr = lrr, var.lrr = var.lrr, smd = cohensd, 
+%                                   var.smd = var.cohensd, effect = effect, se = se), 
+% 
+%             n.sig.single = sum(sig.single, na.rm = T),
+%             NA.sig.single = sum(is.na(sig.single)),
+%             se.min = min(se, na.rm = T),
+%             se.max = max(se, na.rm = T))
+% 
+% ######################################################################################
+% ######################################################################################
+% ######################################################################################
+% # ANALYSIS PART: META-ANALYSES, TESTS AND ADJUSTMENTS: ###############################
+% ######################################################################################
+% ######################################################################################
+% ######################################################################################
+% 
+% #Do all analyses with Fixed effects meta-analysis method and paule mandel tau^2 
+% #estimator
+% settings.meta(method.tau = "PM", method = "Inverse") 
+% 
+% #Load previously constructed lists (to skip analysis):
+% # load(file.path(PATH_RESULTS, "meta_complete_list_bin.RData"))
+% # load(file.path(PATH_RESULTS, "meta_complete_list_cont.RData"))
+% # load(file.path(PATH_RESULTS, "meta_complete_list_iv.RData"))
+% # load(file.path(PATH_RESULTS, "meta_complete_list_zscore.RData"))
+% # load(file.path(PATH_RESULTS, "meta_complete_list_cohensd.RData"))
+% 
+% 
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% # BINARY DATA META-ANALYSES: ----------------------------------------------------------------------------------------#
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% # # -------- Uncomment to run analysis ----------
+% meta.id.vector.bin <- 
+%   meta.info.extended$meta.id[which(meta.info.extended$outcome.flag == "DICH")]
+% meta.analyses <- list()
+% meta.analyses.asd <- list()
+% meta.analyses.reg <- list()
+% meta.analyses.copas <- list()
+% meta.tests.harbord <- list()
+% meta.tests.peter <- list()
+% meta.tests.rucker.mm <- list()
+% meta.tests.rucker.linreg <- list()
+% meta.tests.schwarzer <- list()
+% meta.tests.excess <- list()
+% counter <- 0
+% for(u in meta.id.vector.bin){
+% 	counter <- counter + 1
+% 	print(c(u, counter))
+% 	meta.analyses[[counter]] <- 
+% 	  metabin(event.e = events1c, n.e = total1, event.c = events2c, n.c = total2,
+% 	          studlab = study.name, sm = "RR",
+% 	          method = "Inverse", data = data.ext2[data.ext2$meta.id == u,])
+% 	
+% 	#Arcsine transformed proportions to use in combination with Rücker's test:
+% 	meta.analyses.asd[[counter]] <- 
+% 	  metabin(event.e = events1c, n.e = total1, event.c = events2c, n.c = total2,
+% 	          studlab = study.name, sm = "ASD", 
+% 	          method = "Inverse", data = data.ext2[data.ext2$meta.id == u,])
+%   
+% 	#Adjustment for publication bias
+% 	meta.analyses.reg[[counter]] <- limitmeta(meta.analyses[[counter]])
+% 	meta.analyses.copas[[counter]] <- auto.copas(meta.analyses[[counter]], 
+% 	                         sig.level = 0.1) #*USER.DEF* Copas selection model.
+% 
+% 	#Publication bias tests.
+% 	meta.tests.excess[[counter]] <- 
+% 	  tes.fct2(data = data.ext2[data.ext2$meta.id == u,]) #*USER.DEF* excess sig. test
+% 	meta.tests.harbord[[counter]] <- 
+% 	  metabias(meta.analyses[[counter]], method.bias = "score", k.min = 2)
+% 	meta.tests.peter[[counter]] <- 
+% 	  metabias(meta.analyses[[counter]], method.bias = "peters", k.min = 2)
+% 	meta.tests.schwarzer[[counter]] <- 
+% 	  metabias(meta.analyses[[counter]], method.bias = "count", k.min = 2)
+% 	meta.tests.rucker.mm[[counter]] <- 
+% 	  metabias(meta.analyses.asd[[counter]], method.bias = "mm", k.min = 2)
+% 	meta.tests.rucker.linreg[[counter]] <- 
+% 	  metabias(meta.analyses.asd[[counter]], method.bias = "linreg", k.min = 2)
+% }
+% 
+% 
+% # counter.unknown.bin.copas.error <- 0
+% # for(u in meta.id.vector.bin){
+% # 	if(length(meta.analyses.copas[[counter]]) < 3){
+% # 		meta.analyses.copas[[counter]] <- c(NA, NA, NA)
+% # 		counter.unknown.bin.copas.error <- counter.unknown.bin.copas.error + 1
+% # 	}
+% # }
+% # print(c("unknown.bin.copas.errors = ", counter.unknown.bin.copas.error))
+% #
+% # bin.meta.list <- list(data.ext2, meta.id.vector.bin, meta.analyses,
+% # 											meta.analyses.asd,
+% # 											meta.analyses.reg,
+% # 											meta.analyses.copas,
+% # 											meta.tests.excess,
+% # 											meta.tests.harbord,
+% # 											meta.tests.peter,
+% # 											meta.tests.rucker.mm,
+% # 											meta.tests.schwarzer,
+% # 											meta.tests.excess,
+% # 											meta.tests.rucker.linreg)
+% # save(bin.meta.list, file =  file.path(PATH_RESULTS, "meta_complete_list_bin.RData"))
+% # #--------------------------------------------------------------------------------------------------------------------#
+% # 
+% # #Load analysis data:
+% # meta.id.vector.bin <- bin.meta.list[[2]]
+% # meta.analyses <- bin.meta.list[[3]]
+% # meta.analyses.reg <- bin.meta.list[[5]]
+% # meta.analyses.copas <- bin.meta.list[[6]]
+% # meta.analyses.trimfill <- bin.meta.list[[7]]
+% # meta.tests.harbord <- bin.meta.list[[8]]
+% # meta.tests.peter <- bin.meta.list[[9]]
+% # meta.tests.rucker.mm <- bin.meta.list[[10]]
+% # meta.tests.schwarzer <- bin.meta.list[[11]]
+% # meta.tests.excess <- bin.meta.list[[12]]
+% # meta.tests.rucker.linreg <- bin.meta.list[[13]]
+% 
+% 
+% #Extract from lists:
+% bin.results <- data.frame(
+%   meta.id = meta.id.vector.bin,
+%   meta.es.measure = rep(times = length(meta.id.vector.bin), "log risk ratio"),
+%   
+%   n.sig.single2 = unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){length(which(meta.analysis$pval < 0.05))})),
+%   
+%   #Meta-analysis:
+%   est.fixef = unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){meta.analysis$TE.fixed})),
+%   est.ranef = unlist(lapply(meta.analyses, 
+%                   FUN = function(meta.analysis){meta.analysis$TE.random})),
+%   zval.fixef = unlist(lapply(meta.analyses, 
+%                   FUN = function(meta.analysis){meta.analysis$zval.fixed})),
+%   zval.ranef = unlist(lapply(meta.analyses, 
+%                   FUN = function(meta.analysis){meta.analysis$zval.random})),
+%   
+%   pval.fixef = unlist(lapply(meta.analyses, 
+%                    FUN = function(meta.analysis){meta.analysis$pval.fixed})),
+%   pval.ranef = unlist(lapply(meta.analyses, 
+%                   FUN = function(meta.analysis){meta.analysis$pval.random})),
+%   
+%   se.est.fixef =  unlist(lapply(meta.analyses, 
+%                   FUN = function(meta.analysis){meta.analysis$seTE.fixed})),
+%   se.est.ranef =  unlist(lapply(meta.analyses, 
+%                   FUN = function(meta.analysis){meta.analysis$seTE.random})),
+%   
+%   Q = unlist(lapply(meta.analyses, FUN = function(meta.analysis){meta.analysis$Q})),
+%   pval.Q = unlist(lapply(meta.analyses, 
+%                          FUN = function(meta.analysis){meta.analysis$pval.Q})),
+%   tau = unlist(lapply(meta.analyses, 
+%                       FUN = function(meta.analysis){meta.analysis$tau})),
+%   sparse = unlist(lapply(meta.analyses, 
+%                          FUN = function(meta.analysis){meta.analysis$sparse})),
+%   k = unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$k})),
+%   
+%   #Adjustment:
+%   method.reg = unlist(lapply(meta.analyses.reg, 
+%                   FUN = function(meta.adjust){meta.adjust$method.adjust})),
+%   est.reg = unlist(lapply(meta.analyses.reg, 
+%                   FUN = function(meta.adjust){meta.adjust$TE.adjust})),
+%   se.est.reg = unlist(lapply(meta.analyses.reg, 
+%                   FUN = function(meta.adjust){meta.adjust$seTE.adjust})),
+%   zval.reg = unlist(lapply(meta.analyses.reg, 
+%                   FUN = function(meta.adjust){meta.adjust$zval.adjust})),
+%   pval.reg = unlist(lapply(meta.analyses.reg, 
+%                   FUN = function(meta.adjust){meta.adjust$pval.adjust})),
+%   alpha.r = unlist(lapply(meta.analyses.reg, 
+%                   FUN = function(meta.adjust){meta.adjust$pval.adjust})),
+%   beta.r = unlist(lapply(meta.analyses.reg, 
+%                   FUN = function(meta.adjust){meta.adjust$pval.adjust})),
+%   Q.small = unlist(lapply(meta.analyses.reg, 
+%                   FUN = function(meta.adjust){meta.adjust$Q.small})),
+%   Q.resid = unlist(lapply(meta.analyses.reg, 
+%                   FUN = function(meta.adjust){meta.adjust$Q.resid})),
+%   G.squared = unlist(lapply(meta.analyses.reg, 
+%                   FUN = function(meta.adjust){meta.adjust$G.squared})),
+%   
+%   est.copas = unlist(lapply(meta.analyses.copas, 
+%                   FUN = function(meta.adjust){meta.adjust[1]})),
+%   se.est.copas = unlist(lapply(meta.analyses.copas, 
+%                   FUN = function(meta.adjust){meta.adjust[2]})),
+%   missing.copas = unlist(lapply(meta.analyses.copas, 
+%                   FUN = function(meta.adjust){meta.adjust[3]})),
+%   
+%   #Tests;
+%   pval.d.tes.org = unlist(lapply(meta.tests.excess, 
+%                                  FUN = function(object){object[3]})),
+%   pval.d.tes = unlist(lapply(meta.tests.excess, 
+%                              FUN = function(object){object[4]})),
+%   stat.d.tes = unlist(lapply(meta.tests.excess, 
+%                              FUN = function(object){object[2]})),
+%   excess.d = unlist(lapply(meta.tests.excess, 
+%                            FUN = function(object){object[5]})) - 
+%     unlist(lapply(meta.tests.excess, 
+%                   FUN = function(object){object[6]})),
+%   pval.harbord = unlist(lapply(meta.tests.harbord, 
+%                                FUN = function(meta.test){meta.test$p.value})),
+%   stat.harbord = unlist(lapply(meta.tests.harbord, 
+%                                FUN = function(meta.test){meta.test$statistic})),
+%   pval.peter = unlist(lapply(meta.tests.peter, 
+%                              FUN = function(meta.test){meta.test$p.value})),
+%   stat.peter = unlist(lapply(meta.tests.peter, 
+%                              FUN = function(meta.test){meta.test$statistic})),
+%   pval.rucker = unlist(lapply(meta.tests.rucker.mm, 
+%                               FUN = function(meta.test){meta.test$p.value})),
+%   stat.rucker = unlist(lapply(meta.tests.rucker.mm, 
+%                               FUN = function(meta.test){meta.test$statistic})),
+%   pval.rucker.linreg = unlist(lapply(meta.tests.rucker.linreg, 
+%                               FUN = function(meta.test){meta.test$p.value})),
+%   stat.rucker.linreg = unlist(lapply(meta.tests.rucker.linreg, 
+%                               FUN = function(meta.test){meta.test$statistic})),
+%   pval.schwarzer = unlist(lapply(meta.tests.schwarzer, 
+%                               FUN = function(meta.test){meta.test$p.value})),
+%   stat.schwarzer = unlist(lapply(meta.tests.schwarzer, 
+%                               FUN = function(meta.test){meta.test$statistic}))
+% )
+% 
+% 
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% # CONTINUOUS DATA META-ANALYSES: ------------------------------------------------------------------------------------#
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% 
+% # # -------- Uncomment to run analysis ----------
+% meta.id.vector.cont <- 
+%   meta.info.extended$meta.id[which(meta.info.extended$outcome.flag == "CONT")]
+% meta.analyses <- list()
+% meta.analyses.reg <- list()
+% meta.analyses.copas <- list()
+% meta.analyses.trimfill <- list()
+% meta.tests.excess <- list()
+% meta.tests.linreg <- list()
+% meta.tests.begg <- list()
+% meta.tests.mm <- list()
+% counter <- 0
+% for(u in meta.id.vector.cont){
+% 	counter <- counter + 1
+% 	print(c(u, counter))
+% 	outcome.measure.merged <- 
+% 	  as.character(unique(data.ext2[data.ext2$meta.id == u,
+% 	                 "outcome.measure.merged"])$outcome.measure.merged)
+% 	meta.analyses[[counter]] <- 
+% 	  metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2,
+% 						mean.c = mean2, sd.c = sd2, sm = outcome.measure.merged, 
+% 						studlab = study.name, data = data.ext2[data.ext2$meta.id == u,])
+% 	meta.analyses.reg[[counter]] <- limitmeta(meta.analyses[[counter]])
+% 	meta.analyses.trimfill[[counter]] <- trimfill(meta.analyses[[counter]])
+% 	meta.analyses.copas[[counter]] <- auto.copas(meta.analyses[[counter]], 
+% 	                                             sig.level = 0.1)
+% 
+% 	meta.tests.excess[[counter]] <- 
+% 	  tes.fct2(data = data.ext2[data.ext2$meta.id == u,])
+% 	meta.tests.linreg[[counter]] <- metabias(meta.analyses[[counter]], 
+% 	                                         method.bias = "linreg", k.min = 2)
+% 	meta.tests.begg[[counter]] <- metabias(meta.analyses[[counter]], 
+% 	                                       method.bias = "rank", k.min = 2)
+% 	meta.tests.mm[[counter]] <- metabias(meta.analyses[[counter]], 
+% 	                                     method.bias = "mm", k.min = 2)
+% # }
+% # cont.meta.list <- list(data.ext2, meta.id.vector.cont, meta.analyses,
+% # 											 meta.analyses.reg,
+% # 											 meta.analyses.copas,
+% # 											 meta.analyses.trimfill,
+% # 											 meta.tests.linreg,
+% # 											 meta.tests.begg,
+% # 											 meta.tests.mm,
+% # 											 meta.tests.excess)
+% # save(cont.meta.list, file =  file.path(PATH_RESULTS, "meta_complete_list_cont.RData"))
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Load analysis data:
+% # meta.id.vector.cont <- cont.meta.list[[2]]
+% # meta.analyses <- cont.meta.list[[3]]
+% # meta.analyses.reg <- cont.meta.list[[4]]
+% # meta.analyses.copas <- cont.meta.list[[5]]
+% # meta.analyses.trimfill <- cont.meta.list[[6]]
+% # meta.tests.linreg <- cont.meta.list[[7]]
+% # meta.tests.begg <- cont.meta.list[[8]]
+% # meta.tests.mm <- cont.meta.list[[9]]
+% # meta.tests.excess <- cont.meta.list[[10]]
+% 
+% #Extract from lists:
+% cont.results <- data.frame(
+%   meta.id = meta.id.vector.cont,
+%   meta.es.measure = rep("std. mean difference", times = length(meta.id.vector.cont)),
+%   
+%   n.sig.single2 = unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){length(which(meta.analysis$pval < 0.05))})),
+%   #Meta-Analysis
+%   est.fixef = unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$TE.fixed})),
+%   est.ranef = unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$TE.random})),
+%   
+%   zval.fixef = unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$zval.fixed})),
+%   zval.ranef = unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$zval.random})),
+%   
+%   pval.fixef = unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$pval.fixed})),
+%   pval.ranef = unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$pval.random})),
+%   
+%   se.est.fixef =  unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$seTE.fixed})),
+%   se.est.ranef =  unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$seTE.random})),
+%   
+%   Q = unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$Q})),
+%   pval.Q = unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$pval.Q})),
+%   tau = unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$tau})),
+%   k = unlist(lapply(meta.analyses, FUN = function(meta.analysis){meta.analysis$k})),
+%   
+%   #Adjustment:
+%   method.reg = unlist(lapply(meta.analyses.reg, 
+%                       FUN = function(meta.adjust){meta.adjust$method.adjust})),
+%   est.reg = unlist(lapply(meta.analyses.reg, 
+%                       FUN = function(meta.adjust){meta.adjust$TE.adjust})),
+%   se.est.reg = unlist(lapply(meta.analyses.reg, 
+%                       FUN = function(meta.adjust){meta.adjust$seTE.adjust})),
+%   zval.reg = unlist(lapply(meta.analyses.reg, 
+%                       FUN = function(meta.adjust){meta.adjust$zval.adjust})),
+%   pval.reg = unlist(lapply(meta.analyses.reg, 
+%                       FUN = function(meta.adjust){meta.adjust$pval.adjust})),
+%   alpha.r = unlist(lapply(meta.analyses.reg, 
+%                       FUN = function(meta.adjust){meta.adjust$pval.adjust})),
+%   beta.r = unlist(lapply(meta.analyses.reg, 
+%                       FUN = function(meta.adjust){meta.adjust$pval.adjust})),
+%   Q.small = unlist(lapply(meta.analyses.reg, 
+%                       FUN = function(meta.adjust){meta.adjust$Q.small})),
+%   Q.resid = unlist(lapply(meta.analyses.reg, 
+%                       FUN = function(meta.adjust){meta.adjust$Q.resid})),
+%   G.squared = unlist(lapply(meta.analyses.reg, 
+%                       FUN = function(meta.adjust){meta.adjust$G.squared})),
+%   
+%   est.copas = unlist(lapply(meta.analyses.copas, 
+%                       FUN = function(meta.adjust){meta.adjust[1]})),
+%   se.est.copas = unlist(lapply(meta.analyses.copas, 
+%                       FUN = function(meta.adjust){meta.adjust[2]})),
+%   missing.copas = unlist(lapply(meta.analyses.copas, 
+%                       FUN = function(meta.adjust){meta.adjust[3]})),
+%   
+%   #Tests:
+%   pval.d.tes.org = unlist(lapply(meta.tests.excess, 
+%                               FUN = function(object){object[3]})),
+%   pval.d.tes = unlist(lapply(meta.tests.excess, 
+%                               FUN = function(object){object[4]})),
+%   stat.d.tes = unlist(lapply(meta.tests.excess, 
+%                               FUN = function(object){object[2]})),
+%   excess.d = unlist(lapply(meta.tests.excess, 
+%                               FUN = function(object){object[5]})) - 
+%     unlist(lapply(meta.tests.excess, 
+%                               FUN = function(object){object[6]})),
+%   pval.egger = unlist(lapply(meta.tests.linreg, 
+%                              FUN = function(meta.test){meta.test$p.value})),
+%   stat.egger = unlist(lapply(meta.tests.linreg, 
+%                              FUN = function(meta.test){meta.test$statistic})),
+%   pval.begg = unlist(lapply(meta.tests.begg, 
+%                             FUN = function(meta.test){meta.test$p.value})),
+%   stat.begg = unlist(lapply(meta.tests.begg, 
+%                             FUN = function(meta.test){meta.test$statistic})),
+%   pval.thompson = unlist(lapply(meta.tests.mm, 
+%                             FUN = function(meta.test){meta.test$p.value})),
+%   stat.thompson = unlist(lapply(meta.tests.mm, 
+%                             FUN = function(meta.test){meta.test$statistic}))
+% )
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% # IV OUTCOME META-ANALYSIS: -----------------------------------------------------------------------------------#
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% 
+% # # -------- Uncomment to run analysis ----------
+% meta.id.vector.iv <- 
+%   meta.info.extended$meta.id[which(meta.info.extended$outcome.flag == "IV")]
+% meta.analyses <- list()
+% meta.analyses.reg <- list()
+% meta.analyses.copas <- list()
+% meta.analyses.trimfill <- list()
+% meta.tests.linreg <- list()
+% meta.tests.begg <- list()
+% meta.tests.mm <- list()
+% meta.tests.excess <- list()
+% counter <- 0
+% for(u in meta.id.vector.iv){
+% 	counter <- counter + 1
+% 	meta.analyses[[counter]] <- metagen.iv(data = data.ext2[data.ext2$meta.id == u,])
+% 	print(c(u, counter))
+% 	
+% 	meta.analyses.reg[[counter]] <- limitmeta(meta.analyses[[counter]])
+% 	meta.analyses.trimfill[[counter]] <- trimfill(meta.analyses[[counter]])
+% 	meta.analyses.copas[[counter]] <- auto.copas(meta.analyses[[counter]], 
+% 	                                             sig.level = 0.1)
+% 
+% 	meta.tests.excess[[counter]] <- 
+% 	  tes.fct2(data = data.ext2[data.ext2$meta.id == u,])
+% 	meta.tests.linreg[[counter]] <- metabias(meta.analyses[[counter]], 
+% 	                               method.bias = "linreg", k.min = 2)
+% 	meta.tests.begg[[counter]] <- metabias(meta.analyses[[counter]], 
+% 	                               method.bias = "rank", k.min = 2)
+% 	meta.tests.mm[[counter]] <- metabias(meta.analyses[[counter]], 
+% 	                               method.bias = "mm", k.min = 2)
+% }
+% # iv.meta.list <- list(data.ext2, meta.id.vector.iv, meta.analyses,
+% # 											 meta.analyses.reg,
+% # 											 meta.analyses.copas,
+% # 											 meta.analyses.trimfill,
+% # 											 meta.tests.linreg,
+% # 											 meta.tests.begg,
+% # 											 meta.tests.mm,
+% # 											 meta.tests.excess)
+% # save(iv.meta.list, file =  file.path(PATH_RESULTS, "meta_complete_list_iv.RData"))
+% # #--------------------------------------------------------------------------------------------------------------------#
+% # 
+% # #Load analysis data:
+% # meta.id.vector.iv <- iv.meta.list[[2]]
+% # meta.analyses <- iv.meta.list[[3]]
+% # meta.analyses.reg <- iv.meta.list[[4]]
+% # meta.analyses.copas <- iv.meta.list[[5]]
+% # meta.analyses.trimfill <- iv.meta.list[[6]]
+% # meta.tests.linreg <- iv.meta.list[[7]]
+% # meta.tests.begg <- iv.meta.list[[8]]
+% # meta.tests.mm <- iv.meta.list[[9]]
+% # meta.tests.excess <- iv.meta.list[[10]]
+% 
+% #Extract from lists:
+% iv.results <- data.frame(
+%   meta.id = meta.id.vector.iv,
+%   meta.es.measure = rep(times = length(meta.id.vector.iv), "unknown.effect(IV)"),
+%   
+%   n.sig.single2 = unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){length(which(meta.analysis$pval < 0.05))})),
+%   #Meta-Analysis
+%   est.fixef = unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){meta.analysis$TE.fixed})),
+%   est.ranef = unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){meta.analysis$TE.random})),
+%   
+%   zval.fixef = unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){meta.analysis$zval.fixed})),
+%   zval.ranef = unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){meta.analysis$zval.random})),
+%   
+%   pval.fixef = unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){meta.analysis$pval.fixed})),
+%   pval.ranef = unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){meta.analysis$pval.random})),
+%   
+%   se.est.fixef =  unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){meta.analysis$seTE.fixed})),
+%   se.est.ranef =  unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){meta.analysis$seTE.random})),
+%   
+%   Q = unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){meta.analysis$Q})),
+%   pval.Q = unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){meta.analysis$pval.Q})),
+%   tau = unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){meta.analysis$tau})),
+%   k = unlist(lapply(meta.analyses, 
+%     FUN = function(meta.analysis){meta.analysis$k})),
+%   
+%   #Adjustment:
+%   method.reg = unlist(lapply(meta.analyses.reg, 
+%     FUN = function(meta.adjust){meta.adjust$method.adjust})),
+%   est.reg = unlist(lapply(meta.analyses.reg, 
+%     FUN = function(meta.adjust){meta.adjust$TE.adjust})),
+%   se.est.reg = unlist(lapply(meta.analyses.reg, 
+%     FUN = function(meta.adjust){meta.adjust$seTE.adjust})),
+%   zval.reg = unlist(lapply(meta.analyses.reg, 
+%     FUN = function(meta.adjust){meta.adjust$zval.adjust})),
+%   pval.reg = unlist(lapply(meta.analyses.reg, 
+%     FUN = function(meta.adjust){meta.adjust$pval.adjust})),
+%   alpha.r = unlist(lapply(meta.analyses.reg, 
+%     FUN = function(meta.adjust){meta.adjust$pval.adjust})),
+%   beta.r = unlist(lapply(meta.analyses.reg, 
+%     FUN = function(meta.adjust){meta.adjust$pval.adjust})),
+%   Q.small = unlist(lapply(meta.analyses.reg, 
+%     FUN = function(meta.adjust){meta.adjust$Q.small})),
+%   Q.resid = unlist(lapply(meta.analyses.reg, 
+%     FUN = function(meta.adjust){meta.adjust$Q.resid})),
+%   G.squared = unlist(lapply(meta.analyses.reg, 
+%     FUN = function(meta.adjust){meta.adjust$G.squared})),
+%   
+%   est.copas = unlist(lapply(meta.analyses.copas, 
+%                            FUN = function(meta.adjust){meta.adjust[1]})),
+%   se.est.copas = unlist(lapply(meta.analyses.copas, 
+%                            FUN = function(meta.adjust){meta.adjust[2]})),
+%   missing.copas = unlist(lapply(meta.analyses.copas, 
+%                            FUN = function(meta.adjust){meta.adjust[3]})),
+%   
+%   #Tests:
+%   pval.d.tes.org = unlist(lapply(meta.tests.excess, 
+%                              FUN = function(object){object[3]})),
+%   pval.d.tes = unlist(lapply(meta.tests.excess, 
+%                              FUN = function(object){object[4]})),
+%   stat.d.tes = unlist(lapply(meta.tests.excess, 
+%                              FUN = function(object){object[2]})),
+%   excess.d = unlist(lapply(meta.tests.excess, 
+%                              FUN = function(object){object[5]})) - 
+%     unlist(lapply(meta.tests.excess, 
+%                   FUN = function(object){object[6]})),
+%   pval.egger = unlist(lapply(meta.tests.linreg, 
+%                              FUN = function(meta.test){meta.test$p.value})),
+%   stat.egger = unlist(lapply(meta.tests.linreg, 
+%                              FUN = function(meta.test){meta.test$statistic})),
+%   pval.begg = unlist(lapply(meta.tests.begg, 
+%                              FUN = function(meta.test){meta.test$p.value})),
+%   stat.begg = unlist(lapply(meta.tests.begg, 
+%                              FUN = function(meta.test){meta.test$statistic})),
+%   pval.thompson = unlist(lapply(meta.tests.mm, 
+%                              FUN = function(meta.test){meta.test$p.value})),
+%   stat.thompson = unlist(lapply(meta.tests.mm, 
+%                              FUN = function(meta.test){meta.test$statistic}))
+% )
+% 
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% # Z-SCORE BASED META-ANALYSES: --------------------------------------------------------------------------------------#
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% # # -------- Uncomment to run analysis ----------
+% meta.id.vector.noiv <- 
+%   meta.info.extended$meta.id[-which(meta.info.extended$outcome.flag == "IV")]
+% meta.id.vector.smd <- 
+%   meta.info.extended$meta.id[which(meta.info.extended$outcome.measure.merged == "SMD")]
+% meta.id.vector.z <- union(meta.id.vector.smd, meta.id.vector.noiv)
+% meta.id.vector.z.c <- meta.id.vector.z[-c(which(meta.id.vector.z == 104613),
+%                                           which(meta.id.vector.z == 104616),
+%                                           which(meta.id.vector.z == 153452),
+%                                           which(meta.id.vector.z == 163246),
+%                       which(meta.id.vector.z == 182958))] #Have zero total1..
+% #Dataset with total sample size > 3:
+% tmp.z <- data.ext2 %>% group_by(meta.id) %>% mutate(n = n()) %>% filter(n > 9) %>%
+%   filter(total1 + total2 > 3) %>% filter(total1 != 0 & total2 != 0) 
+% meta.analyses <- list()
+% meta.analyses.reg <- list()
+% meta.analyses.copas <- list()
+% counter <- 0
+% for(u in meta.id.vector.z.c){
+% 	counter <- counter + 1
+% 	print(c(u,counter))
+% 	meta.analyses[[counter]] <- metacor(cor = z, n = total1 + total2, 
+% 	                   studlab = study.name, tmp.z[tmp.z$meta.id == u,])
+% 	meta.analyses.reg[[counter]] <- limitmeta(meta.analyses[[counter]])
+% 	meta.analyses.copas[[counter]] <- auto.copas(meta.analyses[[counter]], 
+% 	                                             sig.level = 0.1)
+% }
+% # zscore.meta.list <- list(tmp.z, meta.id.vector.z.c, meta.analyses, 
+% #meta.analyses.reg, meta.analyses.copas)
+% # save(zscore.meta.list, file =  file.path(PATH_RESULTS, 
+% #"meta_complete_list_zscore.RData"))
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Load analysis data:
+% meta.id.vector.z.c <- zscore.meta.list[[2]]
+% meta.analyses <- zscore.meta.list[[3]]
+% meta.analyses.reg <- zscore.meta.list[[4]]
+% meta.analyses.copas <- zscore.meta.list[[5]]
+% 
+% #List extraction:
+% zscore.meta.analysis.estimates <- cbind(
+%   meta.id = meta.id.vector.z.c,
+%   est.z.fixef = unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$TE.fixed})),
+%   est.z.ranef = unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$TE.random})),
+%   se.est.z.fixef =  unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$seTE.fixed})),
+%   se.est.z.ranef =  unlist(lapply(meta.analyses, 
+%                     FUN = function(meta.analysis){meta.analysis$seTE.random})),
+%   
+%   est.z.reg = unlist(lapply(meta.analyses.reg, 
+%                     FUN = function(meta.adjust){meta.adjust$TE.adjust})),
+%   se.est.z.reg = unlist(lapply(meta.analyses.reg, 
+%                     FUN = function(meta.adjust){meta.adjust$seTE.adjust})),
+%   
+%   est.z.copas = unlist(lapply(meta.analyses.copas, 
+%                     FUN = function(meta.adjust){meta.adjust[1]})),
+%   se.est.z.copas = unlist(lapply(meta.analyses.copas, 
+%                     FUN = function(meta.adjust){meta.adjust[2]})))
+% 
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% # HEDGES G BASED META-ANALYSES: -------------------------------------------------------------------------------------#
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% # # -------- Uncomment to run analysis ----------
+% meta.id.vector.d <- meta.id.vector.z[-c(which(meta.id.vector.z == 25407))]
+% meta.analyses <- list()
+% meta.analyses.reg <- list()
+% meta.analyses.copas <- list()
+% counter <- 0
+% for(u in meta.id.vector.d){
+%   counter <- counter + 1
+%   print(c(u,counter))
+%   meta.analyses[[counter]] <- metagen.bincont2(data.ext2[data.ext2$meta.id == u,]) 
+%   #*USER.DEF*, meta-analysis based on std. mean differences.
+%   meta.analyses.reg[[counter]] <- limitmeta(meta.analyses[[counter]])
+%   meta.analyses.copas[[counter]] <- auto.copas(meta.analyses[[counter]], 
+%                                                sig.level = 0.1)
+% }
+% # cohensd.meta.list <- list(data.ext2, meta.id.vector.d, meta.analyses, 
+% #meta.analyses.reg, meta.analyses.copas)
+% # save(cohensd.meta.list, file =  file.path(PATH_RESULTS, 
+% #"meta_complete_list_cohensd.RData"))
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Load analysis data:
+% meta.id.vector.d <- cohensd.meta.list[[2]]
+% meta.analyses <- cohensd.meta.list[[3]]
+% meta.analyses.reg <- cohensd.meta.list[[4]]
+% meta.analyses.copas <- cohensd.meta.list[[5]]
+% 
+% #List extraction:
+% cohensd.meta.analysis.estimates <- cbind(
+%   meta.id = meta.id.vector.d,
+%   est.d.fixef = unlist(lapply(meta.analyses, 
+%                   FUN = function(meta.analysis){meta.analysis$TE.fixed})),
+%   est.d.ranef = unlist(lapply(meta.analyses, 
+%                   FUN = function(meta.analysis){meta.analysis$TE.random})),
+%   se.est.d.fixef =  unlist(lapply(meta.analyses, 
+%                   FUN = function(meta.analysis){meta.analysis$seTE.fixed})),
+%   se.est.d.ranef =  unlist(lapply(meta.analyses, 
+%                   FUN = function(meta.analysis){meta.analysis$seTE.random})),
+%   
+%   est.d.reg = unlist(lapply(meta.analyses.reg, 
+%                   FUN = function(meta.adjust){meta.adjust$TE.adjust})),
+%   se.est.d.reg = unlist(lapply(meta.analyses.reg, 
+%                   FUN = function(meta.adjust){meta.adjust$seTE.adjust})),
+%   
+%   est.d.copas = unlist(lapply(meta.analyses.copas, 
+%                   FUN = function(meta.adjust){meta.adjust[1]})),
+%   se.est.d.copas = unlist(lapply(meta.analyses.copas, 
+%                   FUN = function(meta.adjust){meta.adjust[2]})))
+% 
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% # BUILD FINAL DATASET OF RESULTS
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% meta.tp5 <- bind_rows(bin.results, cont.results, iv.results)
+% meta.tp1 <- merge(meta.info.extended, meta.tp5, 
+%                   by = c("meta.id")) #Temporary versions
+% meta.tp4 <- merge(by = "meta.id", x = meta.tp1, 
+%                   y = zscore.meta.analysis.estimates, all.x = T)
+% meta.f <- merge(by = "meta.id", x = meta.tp4, 
+%                 y = cohensd.meta.analysis.estimates, all.x = T)
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% # ROUND-UP: DETECT AND REPLACE MISSING VALUES
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #se.est.copas.na = 1 -> is missing
+% meta.f$se.est.copas.na <- ifelse(is.na(meta.f$se.est.copas), 1, 0) 
+% meta.f$se.est.z.copas.na <- ifelse(is.na(meta.f$se.est.z.copas), 1, 0)
+% meta.f$se.est.d.copas.na <- ifelse(is.na(meta.f$se.est.d.copas), 1, 0)
+% 
+% meta.f$se.est.reg.na <- ifelse(is.na(meta.f$se.est.reg), 1, 0)
+% meta.f$se.est.z.reg.na <- ifelse(is.na(meta.f$se.est.z.reg), 1, 0)
+% meta.f$se.est.d.reg.na <- ifelse(is.na(meta.f$se.est.d.reg), 1, 0)
+% 
+% meta.f$est.copas.na <- ifelse(is.na(meta.f$est.copas), 1, 0)
+% meta.f$est.z.copas.na <- ifelse(is.na(meta.f$est.z.copas), 1, 0)
+% meta.f$est.d.copas.na <- ifelse(is.na(meta.f$est.d.copas), 1, 0)
+% 
+% meta.f$est.reg.na <- ifelse(is.na(meta.f$est.reg), 1, 0)
+% meta.f$est.z.reg.na <- ifelse(is.na(meta.f$est.z.reg), 1, 0)
+% meta.f$est.d.reg.na <- ifelse(is.na(meta.f$est.d.reg), 1, 0)
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Inpute random effect estimate for missing copas:
+% copas.names <- c("est.copas", "se.est.copas", "est.z.copas", "se.est.z.copas", 
+%                  "est.d.copas", "se.est.d.copas")
+% ranef.names <- c("est.ranef", "se.est.ranef", "est.z.ranef", "se.est.z.ranef", 
+%                  "est.d.ranef", "se.est.d.ranef")
+% missing.names <- paste(copas.names, ".missing", sep = "")
+% missing <- c()
+% 
+% for(u in 1:length(copas.names)){
+%   missing.count <- 0
+%   for(k in 1:dim(meta.f)[1]){
+%     if(is.na(meta.f[k, copas.names[u]])){
+%       missing.count <- missing.count + 1
+%       meta.f[k, copas.names[u]] <- meta.f[k, ranef.names[u]]
+%     }
+%   }
+%   missing[u] <- missing.count
+%   meta.f[, missing.names[u]] <- missing.count
+% }
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Some useful variables:
+% meta.f <- meta.f %>% rowwise() %>% 
+%   mutate(pval1.egger = onesided.p(stat = stat.egger, side = side, n = k, 
+%                                   test.type = "reg"), 
+%          #*USER.DEF* calculate the one-sided p-value from a rank correlation 
+%          #coefficient or regression test statistic.
+%          pval1.thompson = onesided.p(stat = stat.thompson, side = side, n = k, 
+%                                      test.type = "reg"),
+%          pval1.begg = onesided.p(stat = stat.begg, side = side, n = k, 
+%                                  test.type = "rank"),
+%          
+%          pval1.harbord = onesided.p(stat = stat.harbord, side = side, n = k, 
+%                                     test.type = "reg"),
+%          pval1.rucker = onesided.p(stat = stat.rucker, side = side, n = k, 
+%                                    test.type = "reg"),
+%          pval1.rucker.linreg = onesided.p(stat = stat.rucker.linreg, 
+%                                       side = side, n = k, test.type = "reg"),
+%          pval1.peter = onesided.p(stat = stat.peter, side = side, n = k, 
+%                                   test.type = "reg"),
+%          pval1.schwarzer = onesided.p(stat = stat.schwarzer, side = side, 
+%                                       n = k, test.type = "rank"),
+%          pval1.d.tes = pval.d.tes)
+% 
+% #Summarise different tests for binary and continuous variables to one:
+% meta.f <- meta.f %>% rowwise() %>% 
+%   mutate(I2  = max(0, (Q - k + 1)/Q), #calculate I-squared.
+%          var.ratio = (se.max^2)/(se.min^2),
+%          pval.se = case_when(outcome.flag == "DICH" ~ pval1.rucker.linreg, 
+%                              TRUE ~ pval1.egger),
+%          pval.se.het = case_when(outcome.flag == "DICH" ~ pval1.rucker, 
+%                                  TRUE ~ pval1.thompson))
+% #significance of pb tests:
+% sig.level <- 0.1
+% meta.f <- meta.f %>% rowwise() %>% 
+%   mutate(egger.test = ifelse(pval1.egger < sig.level, 1, 0),
+%          thompson.test = ifelse(pval1.thompson < sig.level, 1, 0),
+%          begg.test = ifelse(pval1.begg < sig.level, 1, 0),
+%          
+%          tes.d.test = ifelse(pval1.d.tes < sig.level, 1, 0),
+%          
+%          schwarzer.test = ifelse(pval1.schwarzer < sig.level, 1, 0),
+%          rucker.test = ifelse(pval1.rucker < sig.level, 1, 0),
+%          rucker.test.linreg = ifelse(pval1.rucker.linreg < sig.level, 1, 0),
+%          harbord.test = ifelse(pval1.harbord < sig.level, 1, 0),
+%          peter.test = ifelse(pval1.peter < sig.level, 1, 0))
+% 
+% #calculate test statistics:
+% meta.f <- meta.f %>% mutate(
+%   z.fixef = (est.fixef/se.est.fixef)
+%   z.ranef = (est.ranef/se.est.ranef),
+%   z.reg =   (est.reg/se.est.reg),
+%   z.copas = ((est.copas)/se.est.copas))
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Separate outcome.types:
+% meta.bin <- meta.f %>% filter(outcome.flag == "DICH")
+% meta.cont <- meta.f %>% filter(outcome.flag == "CONT")
+% meta.iv <- meta.f %>% filter(outcome.flag == "IV")
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Save the result datasets:
+% # save(meta.f, file =  file.path(PATH_RESULTS, 
+% #"meta_analyses_summary_complete.RData"))
+% # save(meta.bin, file =  file.path(PATH_RESULTS, "meta.bin.RData"))
+% # save(meta.cont, file =  file.path(PATH_RESULTS, "meta.cont.RData"))
+% # save(meta.iv, file =  file.path(PATH_RESULTS, "meta.iv.RData"))
+% # save(meta.id.vector, file =  file.path(PATH_RESULTS, "meta_id_vector.RData"))
+% # save(data.ext2, file =  file.path(PATH_RESULTS, 
+% #"data_used_for_analysis.RData")) #Save data used for analysis
+% 
+% 
+% 
+% 
+% ########################################################################################################
+% ########################################################################################################
+% ########################################################################################################
+% #--------USER DEFINED FUNCTIONS------------------------------------------------------------------------#
+% ########################################################################################################
+% ########################################################################################################
+% ########################################################################################################
+% 
+% #Random effects meta-analysis function. 
+% #When outcome.flag = IV, effects have sometimes be log-transformed before usage.
+% 
+% meta.fct.ranef.mom <- function(data){
+%   outcome.flag <- unique(data$outcome.flag)
+%   outcome.measure.merged <- unique(data$outcome.measure.merged)
+%   
+%   if(outcome.flag == "DICH"){
+%     meta.result <- rma.uni(yi = lrr, sei = sqrt(var.lrr),
+%                            method = "DL", measure = "RR",  data = data)
+%   }
+%   
+%   if(outcome.flag == "CONT"){
+%     if(outcome.measure.merged == "SMD"){
+%       meta.result <- rma.uni(yi = cohensd, sei = sqrt(var.cohensd),
+%                              method = "DL", measure = "SMD",  data = data)
+%     }
+%     else{
+%     data <- data %>% filter(se != 0)
+%     meta.result <- rma.uni(yi = effect, sei = se,
+%                              method = "DL", data = data)
+%     }
+%   }
+%   
+%   if(outcome.flag == "IV"){
+%     if(outcome.measure.merged == "SMD" | outcome.measure.merged == "MD"){
+%       meta.result <- rma.uni(yi = effect, sei = se,
+%                              method = "DL", measure = outcome.measure.merged,  
+%                              data = data[data$se != 0,])
+%     } else {
+%       if(outcome.measure.merged == "RR" | outcome.measure.merged == "OR"){
+%         meta.result <- rma.uni(yi = log(effect), sei = se,
+%                                method = "DL", measure = outcome.measure.merged,  
+%                                data = data[data$effect != 0 & data$se != 0,])
+%       } else{
+%         if(outcome.measure.merged == "Hazard Ratio"){
+%           meta.result <- rma.uni(yi = log(effect), sei = se,
+%                                  method = "DL",  
+%                                  data = data[data$effect != 0 & data$se != 0,])
+%         } else{
+%           if(outcome.measure.merged == "Rate Ratio"){
+%             meta.result <- rma.uni(yi = log(effect), sei = se,
+%                                    method = "DL", measure = "IRR",  
+%                                    data = data[data$effect != 0 & data$se != 0,])
+%           } else{
+%             yi = NA
+%             sei = NA
+%           }
+%         }
+%       }
+%     }
+%   }
+%   
+%   return(meta.result)
+% }
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Function to use with "data %>% mutate(.. = dupl.finder(..))"
+% dupl.finder <- function(effects, names, metas){
+%   
+%   results <- rep(NA, times = length(effects))
+%   meta.double.marker <- 1
+%   
+%   
+%   for(u in seq_along(effects)){
+%     
+%     if(is.na(results[u])){
+%       
+%       double.indices <- which(effects[u] == effects & names[u] == names)
+%       
+%       if(length(double.indices) > 1){
+%         #If any meta-analysis has already duplicates give all the same double marker
+%         if(any(!is.na(results[double.indices]))){ 
+%           
+%           already.marked <- which(!is.na(results[double.indices]))
+%           meta.double.marker.2 <- unique(results[double.indices[already.marked]])
+%           #Collect meta.ids with same double markers
+%           meta.ids.2 <- unique(metas[which(results %in% meta.double.marker.2)]) 
+%           #Collect metas with the same results
+%           meta.ids <- metas[double.indices] 
+%           
+%           meta.ids.pooled <- union(meta.ids, meta.ids.2)
+%           meta.indices <- which(metas %in% meta.ids.pooled)
+%           results[meta.indices] <- meta.double.marker
+%           
+%         } else{
+%           
+%           meta.ids <- metas[double.indices]
+%           meta.indices <- which(metas %in% meta.ids)
+%           results[meta.indices] <- meta.double.marker
+%           
+%         }
+%       } else results[u] <- 0
+%       
+%       meta.double.marker <- meta.double.marker + 1
+%     }}
+%   return(results)
+% }
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Find the biggest meta-analysis within a duplicate set, 
+% #again as "data %>% mutate(.. = dupl.finder(..))":
+% dupl.max.finder <- function(duplicate.index, study.number, metas){
+%   results <- rep(NA, length(duplicate.index))
+%   
+%   for(u in seq_along((duplicate.index))){
+%     
+%     duplicate.indices <- which(duplicate.index %in% duplicate.index[u])
+%     
+%     if(duplicate.index[u] != 0){
+%       
+%       meta.ids <- metas[duplicate.indices]
+%       
+%       max.meta.id <- meta.ids[which.max(study.number[duplicate.indices])]
+%       max.meta.indices <- which(metas %in% max.meta.id)
+%       if(length(unique(max.meta.id)) < 2){
+%         results[max.meta.indices] <- 0
+%       } else print("error")
+%       
+%     } else results[duplicate.indices] <- 0
+%     
+%   }
+%   
+%   results[is.na(results)] <- 1
+%   
+%   return(results)
+% }
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Meta-analysis for IV outcomes:
+% metagen.iv <- function(data){
+%   if(all(data$outcome.measure.merged == "SMD") | 
+%      all(data$outcome.measure.merged == "MD")){
+%     meta <- metagen(TE = effect, seTE = se, studlab = study.name, 
+%                     sm = unique(data$outcome.measure.merged), data = data)
+%   } else {
+%     if(all(data$outcome.measure.merged == "RR") | 
+%        all(data$outcome.measure.merged == "OR")){
+%       meta <- metagen(TE = log(effect), seTE = se, studlab = study.name, 
+%                       sm = unique(data$outcome.measure.merged), data = data)
+%     } else{
+%       if(all(data$outcome.measure.merged == "Hazard Ratio")){
+%         meta <- metagen(TE = log(effect), seTE = se, studlab = study.name, 
+%                         sm = "HR", data = data)
+%       } else{
+%         if(all(data$outcome.measure.merged == "Rate Ratio")){
+%           meta <- metagen(TE = log(effect), seTE = se, studlab = study.name, 
+%                           data = data)
+%         } else{
+%           meta <- NA
+%         }
+%       }
+%     }
+%   }
+%   return(meta)
+% }
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Meta-analysis for standardized mean difference
+% metagen.bincont2 <- function(data){
+%   if (all(data$outcome.flag == "DICH")){
+%     meta <- metagen(TE = smd.ordl, seTE = sqrt(var.smd.ordl), 
+%                     studlab = study.name, data, sm = "SMD")
+%   } else{
+%     if(all(data$outcome.flag == "CONT")){
+%       meta <- metagen(TE = cohensd, seTE = sqrt(var.cohensd), 
+%                       studlab = study.name, data, sm = "SMD")
+%     } else{
+%       meta <- metagen(TE = effect, seTE = se, 
+%                       studlab = study.name, data, sm = "SMD")
+%     }
+%   }
+% }
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Excess significance test function:
+% tes.fct2 <- function(data){
+%   outcome.flag <- unique(data$outcome.flag)
+%   outcome <- unique(data$outcome.measure.merged)
+%   
+%   if(outcome.flag == "DICH"){
+%     yi <- data$lrr
+%     sei <- sqrt(data$var.lrr)
+%   }
+%   
+%   if(outcome.flag == "CONT"){
+%     if(outcome == "MD"){
+%       yi = data$effect
+%       sei = data$se
+%     } else{
+%       yi <- data$cohensd
+%       sei <- sqrt(data$var.cohensd)
+%     }
+%   }
+%   
+%   if(outcome.flag == "IV"){
+%     if(outcome == "SMD" | outcome == "MD"){
+%       yi = data$effect
+%       sei = data$se
+%     } else {
+%       if(outcome == "RR" | outcome == "OR"){
+%         yi = log(data$effect)
+%         sei = data$se
+%       } else{
+%         if(outcome == "Hazard Ratio"){
+%           yi = log(data$effect)
+%           sei = data$se
+%         } else{
+%           if(outcome == "Rate Ratio"){
+%             yi = log(data$effect)
+%             sei = data$se
+%           } else{
+%             yi = NA
+%             sei = NA
+%           }
+%         }
+%       }
+%     }
+%   }
+%   
+%   
+%   alpha = 0.05
+%   
+%   to.ommit <- which(is.na(yi) | is.na(sei))
+%   
+%   if(length(to.ommit) > 0){
+%     yi <-  yi[-to.ommit]
+%     sei <- sei[-to.ommit]
+%   }
+%   
+%   to.ommit <- which(sei == 0)
+%   
+%   if(length(to.ommit) > 0){
+%     yi <-  yi[-to.ommit]
+%     sei <- sei[-to.ommit]
+%   }
+%   
+%   ### FE meta-analysis for statistical power analysis
+%   est.fe <- rma(yi = yi, sei = sei, method = "FE")$b[1] 
+%   
+%   side = ifelse(sum(pnorm(yi/sei) < .05) > sum(pnorm(yi/sei, lower.tail=FALSE) < .05), 
+%                 "left", "right")
+%   
+%   ### Compute statistical power and determine the number of observed 
+%   # statistically significant results
+%   if (side == "right") { 
+%     pow <- pnorm(qnorm(alpha, lower.tail = FALSE, sd = sei), mean = est.fe,
+%                  sd = sei, lower.tail = FALSE) #Probability to 
+%     O <- sum(pnorm(yi/sei, lower.tail = FALSE) < alpha)
+%   } else if (side == "left") {
+%     pow <- pnorm(qnorm(alpha, sd = sei), mean = est.fe, sd = sei)
+%     O <- sum(pnorm(yi/sei) < alpha)
+%   }
+%   
+%   n <- length(yi) # Number of studies in meta-analysis
+%   E <- sum(pow) # Expected number of statistically significant result  
+%   
+%   A <- (O - E)^2/E + (O - E)^2/(n - E) # Compute chi-square statistic
+%   pval.chi <- pchisq(A, 1, lower.tail = FALSE) # Compute p-value
+%   #Van Aert's test
+%   pval.chi <- ifelse(pval.chi < 0.5, pval.chi*2, (1-pval.chi)*2) 
+%   
+%   pval.bin <- pbinom(q = O-1, size = n, prob = E/n, lower.tail = F)
+%   
+%   return(c(A = A, Expected = E, pval.chi = pval.chi, pval.bin = pval.bin, 
+%            O = O, E = E, n = n))
+% }
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Copas selection model automatic estimate and std. error and N.unpubl extraction:
+% #The estimate with smallest N.unpubl and a p-value larger than 
+% # sig.level + 0.05 is chosen.
+% auto.copas <- function(meta.obj, sig.level){
+%   sig.level <- sig.level
+%   #analog to P(select|small trial w. sd = 0.4) = 0.1 and P(select|large trial 
+%   #w. sd  = 0.05) = 0.9
+%   #from limitmeta paper (Rücker 2011): "small range" procedure - if no 
+%   #nonsignificance - "broad range"
+%   gamma0 <- -1.7 
+%   gamma1 <- 0.16 
+%   copas <- copas(meta.obj, gamma0.range = c(gamma0, 2), 
+%                  gamma1.range = c(0, gamma1))
+%   pval.rsb <- copas$pval.rsb
+%   N.unpubl <- copas$N.unpubl
+%   if(all(pval.rsb < sig.level)){
+%     copas <- copas(meta.obj, gamma0.range = c(2*gamma0 - 2, 2), 
+%                    gamma1.range = c(0, 2*gamma1))
+%     pval.rsb <- copas$pval.rsb
+%     N.unpubl <- copas$N.unpubl
+%     if(all(pval.rsb < sig.level)){
+%       corr.est <- NA
+%       se.corr.est <- NA
+%       N.unpubl <- NA
+%     } else{ 
+%       ind.nonsig <- which(pval.rsb > sig.level)
+%       ind.estimate <- which.min(N.unpubl[ind.nonsig])
+%       corr.est <- copas$TE.slope[ind.nonsig[ind.estimate]]
+%       se.corr.est <- copas$seTE.slope[ind.nonsig[ind.estimate]]
+%       N.unpubl <- copas$N.unpubl[ind.nonsig[ind.estimate]]
+%     }
+%   } else{
+%     if(all(pval.rsb > sig.level)){
+%       corr.est <- NA
+%       se.corr.est <- NA
+%       N.unpubl <- NA
+%     } else{
+%       ind.nonsig <- which(pval.rsb > sig.level)
+%       ind.estimate <- which.min(N.unpubl[ind.nonsig])
+%       corr.est <- copas$TE.slope[ind.nonsig[ind.estimate]]
+%       se.corr.est <- copas$seTE.slope[ind.nonsig[ind.estimate]]
+%       N.unpubl <- copas$N.unpubl[ind.nonsig[ind.estimate]]
+%     }
+%   }
+%   result <- c(est = corr.est, se =  se.corr.est, missing =  N.unpubl)
+%   return(result)
+% }
+% 
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Get sign of expected bias side direction:
+% bias.side.fct2 <- function(outcome, outcome.measure.merged, lrr, 
+%                            var.lrr, smd, var.smd, effect, se){
+%   alpha = 0.05
+%   outcome <- unique(outcome)
+%   
+%   if(outcome == "DICH"){
+%     yi <- lrr
+%     sei <- sqrt(var.lrr)
+%   }
+%   
+%   if(outcome == "CONT"){
+%     if(all(outcome.measure.merged == "MD")){
+%       yi = effect
+%       sei = se
+%     } else{
+%       yi <- smd
+%       sei <- sqrt(var.smd)
+%     }
+%   }
+%   
+%   if(outcome == "IV"){
+%     if(outcome.measure.merged == "SMD" | outcome.measure.merged == "MD"){
+%       yi = effect
+%       sei = se
+%     } else {
+%       if(outcome.measure.merged == "RR" | outcome.measure.merged == "OR"){
+%         yi = log(effect)
+%         sei = se
+%       } else{
+%         if(outcome.measure.merged == "Hazard Ratio"){
+%           yi = log(effect)
+%           sei = se
+%         } else{
+%           if(outcome.measure.merged == "Rate Ratio"){
+%             yi = log(effect)
+%             sei = se
+%           } else{
+%             yi = NA
+%             sei = NA
+%           }
+%         }
+%       }
+%     }
+%   }
+%   
+%   to.ommit <- which(is.na(yi) | is.na(sei))
+%   
+%   if(length(to.ommit) > 0){
+%     yi <-  yi[-to.ommit]
+%     sei <- sei[-to.ommit]
+%   }
+%   
+%   to.ommit <- which(sei == 0)
+%   
+%   if(length(to.ommit) > 0){
+%     yi <-  yi[-to.ommit]
+%     sei <- sei[-to.ommit]
+%   }
+%   
+%   
+%   if(sum(pnorm(yi/sei) < .05) == sum(pnorm(yi/sei, lower.tail=FALSE) < .05)){
+%       side <- sign(est.fe <- rma(yi = yi, sei = sei, method = "FE")$b[1] )
+%   } else{
+%     side = ifelse(sum(pnorm(yi/sei) < .05) > 
+%                     sum(pnorm(yi/sei, lower.tail=FALSE) < .05), -1, 1)
+%     }
+%   
+%   return(side)
+%   
+% }
+% #--------------------------------------------------------------------------------------------------------------------#
+% 
+% #Function to get one-sided p-value from publication bias test:
+% onesided.p <- function(stat, side, n, test.type){
+%   if(test.type == "reg"){
+%     if(side == -1){
+%       p <- pt(stat, df = n - 2)
+%     } else{
+%       p <- 1 - pt(stat, df = n -2)
+%     }
+%   } else if(side == -1){
+%     p <- pnorm(stat)
+%   } else{
+%     p <- 1 - pnorm(stat)
+%   }
+%   return(p)
+% }
+% @
+% 
+% 
+% 
+% \section{Report Code}
+% After the analysis, a .RData file is loaded containing all important information about the meta-analyses.
+The name of the complete file is \texttt{meta.f}, and it is subdivided into \texttt{meta.bin} for meta-analyses with \texttt{outcome.flag} = \texttt{DICH}, \texttt{meta.cont} for \texttt{CONT} and \texttt{meta.iv} for \texttt{IV}.
+Furthermore, a vector with the \texttt{meta.id} is loaded (\texttt{meta.id.vector}) and a vector with the \texttt{meta.id} and the $I^2$ values used for excluding the meta-analyses with $I^2 > 0.5$.
+% 
+% \subsection{Chapter 03 Code}
+% Exploratory data analysis, properties of the report
+% <<eval = FALSE>>=
+% #Barbiturate Examples
+% barbi1 <- arrange(filter(data, id == "CD000033") %>% 
+%           select(study.name, comparison.name, outcome.name, 
+%                  events1, total1, events2, total2) %>% 
+%             slice(c(1,3)), study.name) 
+% barbi2 <- arrange(filter(data, id == "CD000033") %>% 
+%           select(study.name, comparison.name, outcome.name), study.name)
+% barbi2[barbi2$study.name == "P\303\251rez-B\303\241rcena 2008", 1] = 
+%   "Perez-Barcena 2008"
+% #----------------------------------------------------------------------------------------------#
+% 
+% #Missing values
+% cont.out <- data %>% filter(outcome.flag == "CONT") 
+% 
+% #Cont.results that have only zeros
+% zero.effect.cont <- which(cont.out$mean1 == 0 & cont.out$mean2 == 0 & 
+%                             cont.out$effect == 0) 
+% #Cont.results that have only zeros
+% zero.sds.cont <- which(cont.out$sd1 == 0 & cont.out$sd2 == 0 & cont.out$se == 0) 
+% zero.both.cont <- intersect(zero.effect.cont, zero.sds.cont)
+% zero.counts.cont <- length(zero.both.cont)
+% 
+% missing.arm <- which(data$total1 == 0 | data$total2 == 0) #One arm without patients..
+% missing.arm.count <- length(missing.arm)
+% 
+% missing.year.count <- sum(is.na(data$study.year)) + 
+%   length(c(which(data$study.year < 1920), which(data$study.year > 2019)))
+% 
+% missing.table <- rbind("Neither means nor standard deviations (CONT)" = 
+%                          zero.counts.cont,
+%                          "Zero participants in one group" = 
+%                          missing.arm.count,
+%                          "Missing study publication year" = 
+%                          missing.year.count)
+% #----------------------------------------------------------------------------------------------#
+% 
+% #Mean and median number of different outcome types of reviews
+% mean.diff.out <- data %>% group_by(id, comparison.nr) %>% 
+%   distinct(outcome.name) %>%
+%   ungroup() %>% group_by(id) %>%
+%   count() %>% ungroup %>% summarise(mean = mean(n))
+% 
+% median.diff.out <- data %>% group_by(id, comparison.nr) %>% 
+%   distinct(outcome.name) %>%
+%   ungroup() %>% group_by(id) %>%
+%   count() %>% ungroup %>% summarise(mean = median(n))
+% #----------------------------------------------------------------------------------------------#
+% 
+% #Study.year quantiles:
+% publication.year.range <- c(quantile(data.ext2$study.year, 0.05, na.rm = T), 
+%                             quantile(data.ext2$study.year, 0.25, na.rm = T), 
+%                             quantile(data.ext2$study.year, 0.5, na.rm = T), 
+%                             quantile(data.ext2$study.year, 0.75, na.rm = T),
+%                             round(mean(data.ext2$study.year, na.rm = T), 2), 
+%                             quantile(data.ext2$study.year, 0.95, na.rm = T))
+% publication.year.2018 <- data.ext2 %>% filter(study.year == 2018) %>% count
+% publication.year.2019 <- data.ext2 %>% filter(study.year == 2019) %>% count
+% #----------------------------------------------------------------------------------------------#
+% 
+% #Outcome.measure frequency table:
+% outcome.measure.frequencies <- 
+%   rbind(data %>% group_by(outcome.measure.merged) %>% 
+%           count() %>% arrange(desc(n)) %>% 
+%           ungroup() %>% filter(row_number() < 9),
+%         data %>% group_by(outcome.measure.merged) %>% 
+%           count() %>% arrange(desc(n)) %>% 
+%           ungroup() %>% filter(row_number() > 8) %>% 
+%           summarise(outcome.measure.merged = "other", n = sum(n)))
+% 
+% outcome.measure.frequencies <- outcome.measure.frequencies %>% 
+%   mutate(percentage = round(n/sum(n),3)*100)
+% names(outcome.measure.frequencies) <- c("Outcome measure", "n", "Percentage")
+% outcome.measure.frequencies$Percentage <- 
+%   paste(outcome.measure.frequencies$Percentage, "%", sep = "")
+% #----------------------------------------------------------------------------------------------#
+% 
+% #Total and group size quantiles:
+% data.ext2 <- data.ext2 %>% ungroup() %>%  mutate(total.n = total1 + total2)
+% samplesize.range <- c(quantile(data.ext2$total.n, 0.05, na.rm = T), 
+%                       quantile(data.ext2$total.n, 0.25, na.rm = T), 
+%                             quantile(data.ext2$total.n, 0.5, na.rm = T), 
+%                       quantile(data.ext2$total.n, 0.75, na.rm = T),
+%                             round(mean(data.ext2$total.n, na.rm = T), 2), 
+%                       quantile(data.ext2$total.n, 0.95, na.rm = T))
+% treatment.group.size.range <- c(quantile(data.ext2$total1, 0.05, na.rm = T), 
+%                                 quantile(data.ext2$total1, 0.25, na.rm = T), 
+%                       quantile(data.ext2$total1, 0.5, na.rm = T), 
+%                       quantile(data.ext2$total1, 0.75, na.rm = T),
+%                       round(mean(data.ext2$total1, na.rm = T), 2), 
+%                       quantile(data.ext2$total1, 0.95, na.rm = T))
+% #----------------------------------------------------------------------------------------------#
+% 
+% #Frequencies of results:
+% comp.freq <- data %>% group_by(id) %>% summarise(n = n())
+% comp.range <- c(length(which(comp.freq$n < 6)), 
+%                 quantile(comp.freq$n, 0.25, na.rm = T), 
+%                       quantile(comp.freq$n, 0.5, na.rm = T), 
+%                 quantile(comp.freq$n, 0.75, na.rm = T),
+%                       round(mean(comp.freq$n, na.rm = T), 2), 
+%                 quantile(comp.freq$n, 0.95, na.rm = T),
+%                 quantile(comp.freq$n, 0.05, na.rm = T))
+% #----------------------------------------------------------------------------------------------#
+% 
+% #Frequencies of studies:
+% study.freq <- data %>% group_by(id) %>% distinct(study.name) %>% count()
+% study.range <- c(length(which(study.freq$n < 3)), 
+%                  quantile(study.freq$n, 0.25, na.rm = T), 
+%                       quantile(study.freq$n, 0.5, na.rm = T), 
+%                  quantile(study.freq$n, 0.75, na.rm = T),
+%                       round(mean(study.freq$n, na.rm = T), 2), 
+%                  quantile(study.freq$n, 0.95, na.rm = T))
+% #----------------------------------------------------------------------------------------------#
+% 
+% #Pooling studies
+% cum.repr.trials.subg <- data %>% 
+%   group_by(id, comparison.nr, outcome.nr, subgroup.nr) %>% count %>% group_by(n) %>% 
+%   count %>% filter(n < 15) %>%
+%   full_join( data %>% group_by(id, comparison.nr, outcome.nr) %>% count %>% 
+%                group_by(n) %>% count %>%  filter(n > 14) %>% ungroup %>% 
+%                summarise(n = 15, nn = sum(nn))) %>% 
+%   ungroup() %>% arrange(desc(n)) %>% mutate(csum  = cumsum(nn)) %>% arrange(n)
+% 
+% colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
+% #----------------------------------------------------------------------------------------------#
+% 
+% 	#Counts of meta-analyses with only zeros:
+% both.arms.zero.events.count <- data.ext2 %>% filter(outcome.flag == "DICH") %>% 
+%   group_by(meta.id) %>% 
+%     mutate(n = n()) %>% filter(n >= 10) %>% 
+%   filter(all(events1 == 0) & all(events2 == 0)) %>% 
+%   distinct(meta.id) %>% ungroup() %>%  count()
+% #----------------------------------------------------------------------------------------------#
+% 
+% #Inital dataset properties:
+% initial.id.count <- length(unique(data$id))
+% initial.study.count <- length(unique(data$study.name))
+% initial.result.count <- dim(data)[1]
+% 
+% #No withdrawn reviews:
+% tp7 <- data.ext2 %>% filter(id %in% 
+%                         data.review$id[which(data.review$withdrawn == FALSE)]) 
+% nowith.id.count <- length(unique(tp7$id))
+% nowith.study.count <- length(unique(tp7$study.name))
+% nowith.result.count <- dim(tp7)[1]
+% 
+% #Only efficacy outcomes:
+% tp8 <- data.ext2 %>% filter(id %in% 
+%                         data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
+%   filter(outcome.desired == "efficacy")
+% efficacy.id.count <- length(unique(tp8$id))
+% efficacy.study.count <- length(unique(tp8$study.name))
+% efficacy.result.count <- dim(tp8)[1]
+% 
+% #outcome.flag reduction:
+% tp.2 <- data.ext2 %>% filter(id %in% 
+%                         data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
+%   filter(outcome.flag == "IV") %>% 
+%   filter(!all(effect == 0)) %>% 
+%   filter(outcome.measure.merged == "Rate Ratio" | outcome.measure.merged == "SMD" |
+%            outcome.measure.merged == "MD" | outcome.measure.merged == "Hazard Ratio" |
+%            outcome.measure.merged == "OR" | outcome.measure.merged == "RR")
+% tp.1 <- data.ext2 %>% filter(id %in%
+%                         data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
+%   filter(outcome.flag == "DICH" | outcome.flag == "CONT")
+% tp <- bind_rows(tp.1, tp.2)
+% flag.id.count <- length(unique(tp$id))
+% flag.study.count <- length(unique(tp$study.name))
+% flag.result.count <- dim(tp)[1]
+% #----------------------------------------------------------------------------------------------#
+% 
+% #Counts of meta-analyses with n larger ten:
+% m.a.largerten.bin <- data.ext2 %>% filter(id %in%
+%                         data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
+%   filter(outcome.desired == "efficacy") %>% 
+%   filter(outcome.flag == "DICH") %>% 
+%   filter(total1 != 0 & total2 != 0) %>% 
+%   group_by(meta.id) %>% filter(n() > 9) %>%  filter(any(events1 != 0) | 
+%                                                     any(events2 != 0)) %>% 
+%   distinct(meta.id) %>% ungroup() %>% mutate(n = n())
+% 
+% m.a.largerten.cont <- data.ext2 %>% filter(id %in% 
+%                       data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
+%   filter(outcome.desired == "efficacy") %>% 
+%   filter(outcome.flag == "CONT") %>% 
+%   filter(sd1 != 0 & sd2 != 0) %>% 
+%   filter(total1 > 0 & total2 > 0) %>% group_by(meta.id) %>% 
+%   filter(n() > 9) %>% distinct(meta.id) %>% ungroup() %>% mutate(n = n())
+%   
+% 
+% m.a.largerten.iv <- data.ext2 %>% filter(id %in% 
+%                       data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
+%   filter(outcome.desired == "efficacy") %>% 
+%   filter(outcome.flag == "IV") %>% 
+%   filter(!all(effect == 0)) %>% 
+%   filter(outcome.measure.merged == "Rate Ratio" | outcome.measure.merged == "SMD" |
+%            outcome.measure.merged == "MD" | outcome.measure.merged == "Hazard Ratio" |
+%            outcome.measure.merged == "OR" | outcome.measure.merged == "RR") %>% 
+%   filter(se != 0) %>% group_by(meta.id) %>% filter(n() > 9) %>% 
+%   distinct(meta.id) %>% ungroup() %>% mutate(n = n())
+% 
+% m.a.largerten.id <- rbind(m.a.largerten.bin, m.a.largerten.cont, m.a.largerten.iv)
+% tp2 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) 
+% 
+% ten.id.count <- length(unique(tp2$id))
+% ten.study.count <- length(unique(tp2$study.name))
+% ten.result.count <- dim(tp2)[1]
+% m.a.largerten.count <- unique(m.a.largerten.bin$n) + 
+%   unique(m.a.largerten.cont$n) + unique(m.a.largerten.iv$n)
+% 
+% 
+% #----------------------------------------------------------------------------------------------#
+% 
+% 
+% #variance ratio > 4:
+% m.a.variance4.count <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
+%   group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
+%                                                   TRUE ~ se)) %>% 
+%   summarise(ratio = (max(se.new)^2)/(min(se.new)^2)) %>% 
+%   filter(ratio >= 4) %>% count
+% tp3 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
+%   group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
+%                                                   TRUE ~ se)) %>% 
+%   mutate(ratio = (max(se.new)^2)/(min(se.new)^2)) %>% 
+%   filter(ratio >= 4)
+% var.id.count <- length(unique(tp3$id))
+% var.study.count <- length(unique(tp3$study.name))
+% var.result.count <- dim(tp3)[1]
+% 
+% #At least on sig. estimate:
+% m.a.one.sig.count <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
+%   group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
+%                                                   TRUE ~ se)) %>% 
+%   summarise(ratio = (max(se.new)^2)/(min(se.new)^2),
+%                                   n.sig = sum(sig.single)) %>% 
+%   filter(ratio >= 4 & n.sig > 0) %>% count
+% tp4 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
+%   group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
+%                                                   TRUE ~ se)) %>% 
+%   mutate(ratio = (max(se.new)^2)/(min(se.new)^2),
+%                                   n.sig = sum(sig.single)) %>% 
+%   filter(ratio >= 4 & n.sig > 0)
+% sig.id.count <- length(unique(tp4$id))
+% sig.study.count <- length(unique(tp4$study.name))
+% sig.result.count <- dim(tp4)[1]
+% 
+% #Without duplicates:
+% m.a.no.dupl.number <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
+%   group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
+%                                                   TRUE ~ se)) %>% 
+%   summarise(ratio = (max(se.new)^2)/(min(se.new)^2),
+%                                   n.sig = sum(sig.single),
+%                                   dupl = unique(dupl.remove)) %>% 
+%   filter(ratio >= 4 & n.sig > 0 & dupl == 0) %>% count
+% tp5 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
+%   group_by(meta.id) %>% 
+%   mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
+%                                                   TRUE ~ se)) %>% 
+%   mutate(ratio = (max(se.new)^2)/(min(se.new)^2),
+%                                   n.sig = sum(sig.single),
+%                                   dupl = unique(dupl.remove)) %>% 
+%   filter(ratio >= 4 & n.sig > 0 & dupl == 0)
+% dupl.id.count <- length(unique(tp5$id))
+% dupl.study.count <- length(unique(tp5$study.name))
+% dupl.result.count <- dim(tp5)[1]
+% 
+% #smaller I2 than 0.5:
+% m.a.smaller.5.count <- meta.info.I2 %>% filter(I2 < 50) %>% ungroup %>% count()
+% 
+% meta.id.vector <- meta.info.I2 %>% filter(I2 < 50) %>% select(meta.id)
+% meta.data <- data.ext2 %>% filter(meta.id %in% meta.id.vector$meta.id)
+% 
+% I2.id.count <- length(unique(meta.data$id))
+% I2.study.count <- length(unique(meta.data$study.name))
+% I2.result.count <- dim(meta.data)[1]
+% #----------------------------------------------------------------------------------------------#
+% 
+% #Adjustment dataset:
+% meta.adj.2 <- meta.f %>% filter(outcome.flag == "IV") %>%
+%   filter(outcome.measure.merged == "SMD")
+% meta.adj.1 <- meta.f %>% filter(outcome.flag == "DICH" | outcome.flag == "CONT") 
+% meta.adj <- bind_rows(meta.adj.2, meta.adj.1)
+% tp6 <- data.ext2 %>% filter(meta.id %in% meta.adj$meta.id)
+% 
+% adj.id.count <- length(unique(tp6$id))
+% adj.study.count <- length(unique(tp6$study.name))
+% adj.result.count <- dim(tp6)[1]
+% #----------------------------------------------------------------------------------------------#
+% # "IV" outcome.flag meta-analyses
+% dt <- meta.iv %>% group_by(outcome.measure.merged) %>% count %>% arrange(desc(n))
+% first.iv.outcome.count <- dt$n[1]
+% second.iv.outcome.count <- dt$n[2]
+% third.iv.outcome.count <- dt$n[3]
+% fourth.iv.outcome.count <- dt$n[4]
+% fifth.iv.outcome.count <- dt$n[5]
+% sixth.iv.outcome.count <- dt$n[6]
+% 
+% #----------------------------------------------------------------------------------------------#
+% #Meta-analyses without sungroups in the analysis dataset (1)
+% no.subgroup <- round((meta.data %>% group_by(meta.id) %>% 
+%               filter(is.na(subgroup.id)) %>% distinct(meta.id) %>% 
+%                 ungroup() %>% count/dim(meta.f)[1])*100, 1)$n
+% @
+% 
+% 
+% \subsection{Chapter 04 Code}
+% <<eval = FALSE>>=
+% 
+% @
+% 
+%
 

### 2019-08-14 report/chapter01.Rnw
Draft for Simon and Prof. Held

@@
 \begin{figure}
-<<echo = FALSE, fig.height = 3>>=
+<<echo = FALSE, fig.height = 3, warning=FALSE>>=
 PATH_HOME = path.expand("~") # user home
@@
 @
-\caption{Funnel plots of two meta-analyses: On the left, the improvement in depression syndroms after application of tricyclic antidepressants is compared to placebo.
-The meta-analysis on the right measures the occurence of intracranial haemoerrhage by CT after application of any anti-thrombolytic agent.
+\caption{Funnel plots of two meta-analyses: On the left, the improvement in depression syndromes after application of tricyclic antidepressants is compared to placebo.
+The meta-analysis on the right measures the occurrence of intracranial haemoerrhage by CT after application of any anti-thrombolytic agent.
 All studies are RCT's.}
@@
 None of the research so far has estimated the amount and impact of publication bias on meta-analytical findings thoroughly and with the most suitable methods.
-Also, the results are ironically often presented in the form of dichotomized hypothesis tests, a practice that is partly responsible for publication bias.\\
+Also, the results are ironically often presented in the form of dichotomous hypothesis tests, a practice that is partly responsible for publication bias.\\
 The aim of this thesis is to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides.
-At the end, an approximate, up-to-date estimate of the prevalence of publication bias in the data shall be given.
-To achieve this, methods to detect and adjust for publication bias in meta-analysis are applied on the data.
-\\
-It is also possible to adjust for publication bias with suitable methods.
-These methods are applied on the dataset as well, to achieve publication bias adjusted treatment effect estimates.
-It will be shown if and to what extent treatment effects are overestimated due to publication bias in the Cochrane systematic reviews.
-
-% Already in 1978, scientists raised concern that effect sizes could be overestimated systematically if journals were ``not willing to drop their policy to use statistical significance as one of their criteria for publication'' \citep{dunlap1978}.
-Scientific findings get more attention and are more likely to be published, read and cited if they are implying large effects.
-The issue has been pin-pointed in clinical science by many researchers (\citet{pb.clinicalscience1}, \citet{sterne2001}).
-The concern is that overestimated efficacy of the treatments could lead to harm to patients.
-\\
-% A measure to counter the presence of single, overestimated study results is a meta-analysis \citep{metaanalysis}, a practice originally developped in psychology.
-Summarized treatment effects and uncertainities should be more robust and reliable.
-The pitfall is that when the entire body of evidence is again a biased sample of studies with high effects, the estimate is again overestimating the true effect.
-% % 
-% 
-% Also after the introduction of mandatory registration of clinical trials
-% 
-% 
-% 
-% Typically, we expect empirical scientific results to be distorted by random noise, such that the results are not equal to the real process that they describe.
-Additionally, one can reasonably assume that the results are also biased to some extent, as the statistical paradigm of precision versus bias would predict: The smaller the noise part of distortion, the more the result should be distorted by bias.
-However, the trade-off is not inevitable and can be minimized by scientific rigor and foresightfull experimental design.
-Large efforts have been made both in theory and practice to improve the quality of experiments and their analysis, such as defining experimental settings that prohibit influence of expectations of the researcher (e.g.
-blinding) or increase sample size in experiments.
-The introduction of randomized clinical trials is for example seen nowadays as a benchmark in clinical science, heavily improving the reliability of its findings.
-\\
-% It is more and more considered a new scientific field by itself to think of and argue about circumstances that improve the quality of scientific findings.
-Statistics is in some sense predestined to contribute to it, because probability and chance concepts are key to understanding of any empirical science.
-\\
-% There are also issues, in which statistics is not thought to be able to contribute much to understanding and to be of little help for solving them.
-For example, the selective attention that the agents in science are paying to new, strong and clear findings in each science is considered merely a psychological and social %, socioeconomic
-% issue.
-It is often explained by the affinity of humans for stories rather than mere facts and for novelties.
-The issue that scientific findings get more attention and are more likely to be published, read and cited is known for many years, but has gained new traction in meta science when the so-called reproducibility crisis emerged in (2003 to 2005).
-Studies such as ...
-showed that even rigid prosecution of study protocols did often not lead to reproduction of previous results when experiments were repeated, which struck empirical science in its core.
-Most reasonably, some concluded that it was a large misunderstanding of statistical tools such as the p-value in the scientific community that lead to this situation (...).
-Although that some measures have been taken since then, and some progress is made, the non-reproducibility of scientific findings remain an acute threat to the relevance and reliability of science.
-Some even argue that certain scientific fields sooner or later will repeat the experience that for example psychology or medicine have made, and are yet to encounter their own reproducibility crisis (...).
-\\
-% Clearly, reproduction of experimental results is the gold standard of testing empirical science, because it reassures the universality and reliability by which certain procedures or effects appear if measured in the correct experimental context.
-However, there are also problems there.
-One can almost never fully exclude chance events to have played a major role in negating or reaffirming the experimental findings (which is of course always the case where noise is present in the data).
-Furthermore, reproduction studies are generally costly and the precise experimental conditions might be hard to reproduce because of lack of information or other reasons.
-\\
-% There is another way to assess the strength of scientific results if the experiment has been conducted more than once (however not with exactly identical protocol as in reproduction studies): Meta-analyses.
-In a meta-analyses, results of multiple (fairly identical) experiments (studies) are summarized to a single result.
-Very often, meta-analyses are not only regarded to be a synthesis of results, but of evidence, thus reflecting the overall and summarized evidence regarding to a scientific question.
-It is on purpose that selective attention to positive, strong results in the scientific literature have been mentioned beforehand, because it is clear how they will affect this second way of reassurance of scientific findings: The meta-analysis will again lead to irreproducible findings if it is based on a set of results that is itself biased.
-Thus, meta-analysis will in this case not reach its purpose of assessing reliability of science, but worsen the problem by reinforcing the confidence in the overestimated over-optimistic effects.
-However, and this is the main topic in this masters thesis, there are some ways to detect irregularities in the body of results that can provide indirect hints that a selective rather than a random sample from a hypothetical population of experiments is present.
-The abundance of the methods to link some features of the sample of experiments to publication bias, as the tendency of scientific literature to over-proportionally include large effects is generally called, also speaks for the relevance of the topic.
-A review in 2017 (...) for example identified 147 (!) conceptually differing methods.\\
-% This speaks as well for the inevitable difficulties that such methods encounter.
-First of all, it is most often impossible to estimate the real selection process, that is the rate by which smaller effects go unnoticed because of selective publication and reporting, because the number of missing results in the studies is not known at the first place and impossible to retrieve.
-Secondly, there is almost no real world data of complete and unbiased meta-analyses, such that evaluations of methods is dependent on simulations.
-So we have, after applying the methods, only indirect information of publication bias, and the extent to what it might influences scientific findings.
-Almost all the time, alternative explanations for the results of the methods might relieve the operators and publishers from the reproval of publication bias.
-However, given the large body of evidence for publication bias collected from other sources (...), in many cases, the results from these methods indeed give a quantitative measure of publication bias.\\
-% In this masters thesis, the answers for two questions are investigated: What is the extent and effect of publication bias in clinical science?
-For this purpose, a dataset from the Cochrane Organization is analysed with commonly used techniques to detect and adjust for publication bias (more precisely, small study effects, as it will be seen later).
-The discussion of the results of the analysis will result in the light of the literature to publication bias.
-%Because the extent of the analysis that is operated here is, to my knowledge, unmatched so far, this dataset
-
-%Before beginning with the main part of this masters thesis, I want to recall some of the most pointed evidence for publication bias that has been collected for publication bias so far. \\
-
-% Meta-analysis is at the core of evidence based medicine because it allows to summarise evidence over multiple studies and provide a more broad view on success and effectivity of clinical treatments.
-The necessity of meta-analyses is also increased by the abundance of data and publications.
-Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to make decisions based on quantitative and scientific criteria.
-% 
-% \vspace{0mm}
-% For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention.
-However, the usefulness of meta-analysis does not restrict to clinical science, but to any empirical and quantiative science.
-% 
-% \vspace{0mm}
-% Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question.
-Meta-analysis can be applied to all studies that are approximately identical in their experimental setup and the way the outcome of the experiments is measured.
-In systematic reviews where meta-analyses are used, the conclusions are most often strongly based on the results and the interpretation of the meta-analysis.
-% 
-% \vspace{0mm}
-% However, there are problems that potentially limit the validity of meta-analysis; the number of studies available can be incomplete or the results of the studies can be biased.
-Some of those problems can be solved or asserted by special statistical methods.
-% 
-% \subsection{Small Study Effects or Publication Bias}
-% When study sample size decreases, the probability of extreme and missleading results in a study increases.
-This becomes a problem if results are selectively published, and therefore available, based on their results.
-When this is the case, one speaks of a small study effect or of ``Publication bias''.
-% 
-% \vspace{0mm}
-% The issue has been discussed extensively in the last years, most often in the context of what has came to be known as the replication crisis.
-The reasons for small study effects are manifold, but originate most often in the myopical acting of agents in science and the lack of statistical education.
-Studies are reported by scientists, published by journals and noticed by readers more often if their findigs are positive and find e.g.
-a substantive difference or effect.
-When doing a meta-analysis, one again obtains biased results.
-% 
-% \vspace{0mm}
-% The reason why that is less of an issue for larger studies is that extreme results are in general less likely and that due to larger effort, a result is published although there has been no clear and positive findings.
-% 
-% \vspace{0mm}
-% While there is generally no way to assert poor study quality, small study effect can in principle be asserted and corrected for statistically.
-This masters thesis will mainly be about statistical methods to detect and adjust for small study effects.
-It can furthermore be divided in two parts:
-% \begin{itemize}
-% \item Methodological part: Collection and discussion of statistical tests and correction methods for small study effects.
-% \item Applied part: Application of the methods to studies of the Cochrane Library of systematic Reviews. Subsequent discussion of the implications
-% of the results for clinical science.
-% \end{itemize}
-% 
-% In contrast to simulation studies, it is not possible to assess critical properties of the methods such as the power of a test, since the truth is not known.
-But based on the amount of data, one can of course try to make extrapolation to tendencies in clinical science in general.
-Moreover, it is still interesting to see how the methods behave in general, especially with respect to each other.
-It may, as an example, be possible to answer the question which statistical test is most conservative and which pooling method is most optimistic on average.
-Comparison with results from simulations may allow to speculate about the reasons when simulation and real world results diverge.
-% 
-% 
-% \subsection{Cochrane and the Cochrane Database of Systematic Reviews}
-% The Cochrane Organization has specialized on systematic reviews in clinical science.
-It publishes and maintains a library with a large number of systematic reviews that are available in some countries to the public.
-% 
-% \vspace{0mm}
-% The data analyzed in this thesis stems completely from the Cochrane Library of systematic Reviews (cite). 
-% 
-% \vspace{0mm}
-% The reviews are arguably of good quality, since the authors are following elaborated guidelines, and there are control-mechanisms within the organisation that should prohibit conflicts of interests.
-This might further improve the validity and precision of findings and conclusions that have been made based on this data.
-%
+The research questions are: ``Are effects in meta-analyses \textit{larger} if their standard errors are small, and are there \textit{more} significant effects than expected?'' and ``How can this affect the combined treatment effects as commonly obtained by meta-analysis?''.
+To answer these questions, methods to detect and adjust for publication bias in meta-analysis are applied on the data.\\
+At the end, it will be given an estimate of the extent of publication bias in the Cochrane Library.
+It will also be shown if and to what extent treatment effects are overestimated due to publication bias in Cochrane systematic reviews.
+Because the analysis is exploratory, the results should rather be used in a suggestive than in a confirmatory manner.

### 2019-08-14 report/chapter02.Rnw
Draft for Simon and Prof. Held

@@
 Hypothesis tests for $\beta = \beta_\textrm{H0}$ can be made using the Wald method.
+\\
+It is necessary to check the model assumptions after fitting a linear regression.
+For this purpose, fitted values can be plotted against standardized residuals.
+If the standardized residuals are not dispersed evenly around zero for any size of fitted values, the assumption of the residuals being independently and equally distributed around zero is violated and estimates are biased.
+\\
 
-\section{Publication Bias Tests}
+\section{Publication Bias Assessment}
 The tests that will be presented on the following pages are a common way to detect publication bias.
-A frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill} is not discussed because of its disadvantageous properties, therefore, it will not be discussed here (see \eg \citet{Moreno.2009}).\\
+A frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill} is not discussed because of its disadvantageous properties, therefore, it will not be discussed here (see \eg \citealp{Moreno.2009}).\\
 
 \subsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
-\citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+\citealp{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
 A standardized effect size $\theta_i^\star$ can be computed as in \eqref{eq:begg.stand.eff}.
@@
 \end{align}
-
-%SIMPLE LINEAR REGRESSION
-% \begin{align}
-% \hat{\mathbf{\beta}} &= (\mathbf{X}^\top  \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
-% \end{align}
-
-% There is a closed form solution for $\hat{\beta_0}, \hat{\beta}_1$ that minimize the sum of squares:
-% 
-% \begin{align}
-% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} & 
-% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
-% \end{align}
-% 
-% $\bar{x}, \bar{y}$ denotes the sample mean of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$.
-$\hat{\beta}_0$ is the intercept and $\hat{\beta}_1$ the slope of the fitted line.
-Let $\hat{y}_i = \beta_0 + \beta_1 x_i$ and $e_i = y_i - \hat{y}_i$.
-The variances $\se^2_\beta$
-% 
-% 
-% 
-% To test whether the intercept or the slope is close to a certain value, a $t$-test can be used. Simply taking the absolute value of $\beta_0/s_\beta_0$,
-% \begin{align}
-% p &= 2(1-F(|\beta_0/s_\beta_0|)) \nonumber
-% \end{align}
-% 
-% where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom.
-The $p$\hspace{0.4mm}-value will give the evidence against the null-hypothesis $\beta_0 = 0$.
-The procedure for $\beta_1$ is equivalent.
-\\
-% To extend the model to weighted simple linear regression is straightforward.
-Let $w_i$ be the corresponding weight that will be attributed to the pair $x_i, y_i$.
-The least squares minimization problem can be restated
-% 
-% \begin{align}
-% \operatorname*{argmin}_{\beta_0, \beta_1}(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)) \nonumber
-% \end{align}
-% 
-% And the corresponding estimators are thus
-% 
-% \begin{align}
-% \hat{\beta_1} &= \frac{\sum_{i = 1}^n w_i(x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n w_i(x_i - \bar{x})^2} & 
-% \hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \label{eq:regression.estimator}
-% \end{align}
-%
-
-% LIMITMETa
-% \vspace{0mm}
-% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
-% 
-% \begin{align}
-% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
-% \end{align}
-% 
-% Letting $M \rightarrow \infty$, we obtain:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
-% \end{align}
-% 
-% Note that:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
-% \end{align}
-% 
-% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
-% 
-% \begin{align}
-% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
-% \end{align}
-% 
-% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-% \end{align}
-% 
-% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
-
-% \section{Basic notation}
-% The notation used here will be used throughout the chapter and exceptions will be noted.
-Let $i$ be the number of a study of a meta analysis with $n$ being the total number of studies.
-$y_{i}$ is then the effect size estimate (usually log odds ratio or mean difference) and $v_{i}$ the variance of the estimate of study $i$.
-$w_{i}$ is used for weights which are defined when necessary, and $\Delta$ usually denotes the summarized or pooled effect estimate of the meta-analysis, and $\eta$ the variance thereof.
-% 
-% \vspace{0mm}
-% In the case of binary outcomes, let $e_{t}$ be the number of events and $n_{t}$ be the total number of patients in the treatment arm and $n_{c}$ and $e_{c}$ analogously for the control arm in a two-armed study $i$.
-% 
-% 
-% \section{Transformation between effect sizes}
-% Binary and continuous outcome measures can both be transformed into correlations and fishers z-scaled correlations in order to be compared.
-Let $\theta$ be a log odds ratio.
-A standardized mean difference $d$ (also known as Cohen's $d$) is calculated by multiplying $\theta$ with $\sqrt{3}/\pi$.
-The variance of the standardized mean difference is attained as $v_d = v_\theta \sqrt{3}/\pi$.\\
-% We get from a standardized mean difference $d$ to a correlation $r$ by using 
-% \begin{align}
-% r &= \frac{d}{\sqrt{d^2 + a}} \nonumber
-% \end{align}
-% where $a$ is a correction factor if $n_t \neq n_c, a = (n_c + n_t)^2 / n_c n_t$. The variance of $r$ is computed by using 
-% \begin{align}
-% v_r &= v_d
-% \end{align}
-% 
-% Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $v_z$ by using
-% \begin{align}
-% z &= 0.5 \ln(\frac{1 + r}{1 - r}) \nonumber
-% v_z &= \frac{1}{n-3}
-% \end{align}
-% 
-% 
-% 
-% \section{Heterogeneity}
-% In addition to sampling error, there can be additional, ``real'' variation between estimates of different studies, indicating real differences between the studies.
-This is called between study variation in contrast to within study variation (noise).
-% 
-% 
-% \vspace{0mm}
-% The $Q$ statistic is a weighted sum of squares that quantifies the deviation from the weighted mean of study effect estimates.
-Let $w_i$ be the inverse of the variance and $\Delta$ be a summarized effect estimate of your choice as for example a variance-weighted mean \ref{weighted.mean}.
-Then $Q$ can be calculated as in \ref{Q.heterogeneity}
-% 
-% \begin{align}
-% \Delta &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-% Q &= \sum_{i = 1}^n w_{i}(y_{i} - \Delta)^2 \label{Q.heterogeneity}
-% \end{align}
-% 
-% Because $Q$ is a standardized measure, it does not depend on the effect size, but only on the study number $n$.
-Under the assumption of equal effect sizes of all studies, the expected value of $Q$ is $n-1$, so the excess dispersion is just $Q - n + 1$.To test the assumption of equal effect sizes one uses that $Q$ follows a central Chi-squared distribution with $n -1$ degrees of freedom under the null hypothesis of equal effect sizes.
-$1 - F(Q)$ will provide the $p$\hspace{0.4mm}-value for the significance test with $F$ being the cumulative distribution function of the Chi-squared distribution with the corresponding degrees of freedom.
-% 
-% \vspace{0mm}
-% Since $Q$ is a standardized metric, it gives no impression of the real dispersion of the effect sizes.
-For this purpose, $\tau^2$, the variance of true effects, can be calculated.
-$\tau^2$ is on the same scale as the effect size and reflects the absolute amount of dispersion.
-In practice, $\tau^2$ can be smaller than zero, then it is set to zero.
-% 
-% \begin{align}
-% C &= \sum_{i = 1}^n w_{i} - \frac{\sum_{i = 1}^n w_{i}^2}{\sum_{i = 1}^n w_{i}} \label{C.definition} \\
-% \tau^2 &= \max(0, \frac{Q - d}{C}) \label{Tau.definition}
-% \end{align}
-% 
-% The estimation method for $\tau^2$ is known as DerSimonian and Laird method, but others, such as restricted maximum likelihood can be used.
-Note that their estimate can differ substantially and consequently also the estimate of the pooled effect size estimate.
-% 
-% \vspace{0mm}
-% To estimate the proportion of real variance between effect estimates of the observed variance, the $I^2$ can be used. The calculation is given in \ref{I2.proportion}
-% 
-% \begin{align}
-% I^2 &= (Q - n + 1)/Q \label{I2.proportion}
-% \end{align}
-% 
-% There are ways to compute confidence intervals for $I^2$ and $\tau^2$ that are not shown (see \cite[122]{metaanalysis}).
-% 
-% \section{Meta Analysis}
-% There are numerous methods to pool the estimates of multiple studies into one estimate, and two will be introduced here; fixed and random effects meta-analysis.
-% First the fixed effect meta-analysis will be explained.
-Note that both methods can be used for continuous or dichotomous outcomes.
-For more details about the methods, see chapter 11 and 12 in \citet{metaanalysis}
-% 
-% 
-% \vspace{0mm}
-% Let $w_i = 1/v_{i}$ be the inverse of the variance of the estimate from study $i$.
-The pooled estimate $\Delta_{f}$ of the fixed effects model is then the weighted average with the weights given by the inverses of the variances, $w_{i}$, given in \ref{weighted.mean}.
-The variance $\eta_{f}$ is the reciprocal of the sum of the weights as shown in \ref{reciproce.variance}.
-% 
-% \begin{align}
-% \Delta_{f} &= \frac{\sum_{i = 1}^n w_{i}y_{i}}{\sum_{i = 1}^n w_{i}} \label{weighted.mean} \\
-% \eta_{f} &= \frac{1}{\sum_{i = 1}^n w_{i}} \label{reciproce.variance}
-% \end{align}
-% 
-% The computation of random effects meta-analysis is more complicated.
-Random effects meta-analysis will give smaller studies with larger variance more weight in the pooled estimate.
-Shortly, the idea is that the estimates are allowed to vary randomly around the true estimate $\Delta$, and additionally, the estimates are subject to noise or sampling error themselves.
-% 
-% \vspace{0mm}
-% The variance of a study estimate $y_{i}$ of study $i$, $v_{i}^\star$ is defined as in \ref{ranef.study.variance}, with $w_{i}^\star$ being the inverse of $v_{i}^\star$.
-It is used to calculate a new weighted mean to obtain a pooled estimate $\Delta_{r}$ as in \ref{ranef.weighted.mean}.
-The variance of $\Delta_{r}$, $\eta_{r}$ is then the sum of the reciprocal variances (\ref{ranef.reciproce.variance}).
-% 
-% \begin{align}
-% v_{i}^\star &= v_{i} + \tau^2 \label{ranef.study.variance} \\
-% \Delta_{r} &= \frac{\sum_{i = 1}^n w_{i}^\star y_{i}}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.weighted.mean} \\
-% \eta_{r} &= \frac{1}{\sum_{i = 1}^n w_{i}^\star} \label{ranef.reciproce.variance}
-% \end{align}
-% 
-% A $p$\hspace{0.4mm}-value under the Null-hypothesis of $\Delta = 0$ can be obtained by calculating the $Z$-value (\ref{Zvalue}) and using the distribution function of a standard normal as shown in (\ref{p.value.calculation}), $\Phi$ being the distribution function of a standard normal distribution.
-% 
-% \begin{align}
-% Z &= \frac{\Delta}{\sqrt{\nu}} \label{Zvalue} \\
-% p &= 2(1 - \Phi(|{Z}|) \label{p.value.calculation}
-% \end{align}
-% 
-% \section{Small Study Effects Tests}
-% One crucial assumption in meta analysis is that the availability and publication of studies does not depend on their effect and the variance of the effect.
-If this is not given, one often speaks of publication bias.
-In fact, there can also be other reasons for this (see discussion section).
-A more appropriate term for the phenomenon is small study effect.
-If small study effects are present in a meta-analysis, the classical approaches to merge single study results in to an overall intervention effect fails to provide an appropriate estimate of the treatment effect.
-% 
-% \subsection{Continuous Outcome Tests}
-% % Essentially, there are two kinds of tests for reporting bias, non-parametrical or rank-based tests or regression based tests. 
-% % First, tests for continuous outcome studies are described, and special modifications of those for binary outcomes will be introduced later.
-% 
-% \subsubsection{Begg and Mazumdar: Rank Correlation Test}
-% \citet{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
-% A standardized effect size $y_{i}^\star$ can be computed as in \ref{begg.stand.eff}.
-$v_{i}^\star$ is the variance of $y_{i} - \Delta_{f}$ as defined in \ref{begg.stand.var}.
-$\Delta_{f}$ is the pooled estimate for fixed effect estimate defined in \ref{weighted.mean}.
-% 
-% \begin{align}
-% y_{i}^\star &= (y_{i} - \Delta_{f})/v_{i}^\star \label{begg.stand.eff} \\
-% v_{i}^\star &= v_{i} - 1/\sum_{i = 1}^n v_{i}^-1 \label{begg.stand.var} 
-% \end{align}
-% 
-% A rank correlation test based on Kendall's tau is then used.
-The pairs $(y_{i}^\star, v_{i}^\star)$ that are ranked in the same order are enumerated.
-Let $u$ be the number of pairs ranked in the same order, and $l$ the number of pairs ranked in the opposite order (\eg larger standardized effect size and smaller variance).
-Then the normalized test statistic $Z$ is given in \ref{begg.teststat}.
-% 
-% \begin{align}
-% Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \label{begg.teststat}
-% \end{align}
-% 
-% The changes in the case of ties are negligible \cite[410]{begg.ties}.
-% 
-% \subsubsection{Egger's Test: Linear Regression Test}
-% Alternatively, one can use Eggers test \citep{Egger} that is based on linear regression. Let $y_{i}^\star = y_{i}/\sqrt{v_{i}}$ and $x_{i} = 1/\sqrt{v_{i}}$. 
-% Using $y_{i}^\star$ as dependent, and  $x_{i}$ as explanatory variable in linear regression, one obtains an intercept $\beta_{0}$ and a slope. 
-% 
-% \vspace{0mm}
-% If $\beta_{0} \ne 0$, the null hypothesis of no small study effect may be contested, using that $\beta_{0} \sim t_{n-1}$, $n-1$ being the degrees of freedom of the $t$-distribution.
-The $p$\hspace{0.4mm}-value for $\beta_{0} = 0$ (no reporting bias) is then given by \ref{egger.pvalue}.
-% 
-% \begin{align}
-% p &= 2*(1 - t_{n-1}(\beta_{0}/se(\beta_{0}))) \label{egger.pvalue}
-% \end{align}
-% 
-% \subsubsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{Thompson}
-% A method proposed in \citet{thompson.sharp} allows for between study heterogeneity.
-Let $\tau^2$ be equal to \ref{Tau.definition}.
-The effect size estimates are then assumed to be distributed as in \ref{t.sharp.regression}.
-% 
-% \begin{align}
-% y_{i} \sim N(\beta_{0} + \beta_{1}x_{i}, v_{i} + \tau^2) \label{t.sharp.regression}
-% \end{align}
-% 
-% Then, a weighted regression is carried out with weights $1/v_{i}^\star$ based on the inverse of the variance as in \ref{ranef.study.variance}.
-Analogous to Egger's test, $\beta_{0}$ is then tested with respect to the null hypothesis $\beta_{0} = 0$.
-% 
-% \subsection{Dichotomous Outcomes Tests}
-% 
-% The issue with dichotomous outcomes is that effect size and variance of effect size are not independent.
-Consequently, the tests above will tend to reject the null-hypothesis too often, \ie that they are not conservative enough.
-A number of solutions to this problem are existing in the literature.
-% 
-% 
-% \subsubsection{Peters Test: Weighted Linear Regression Test}
-% A modification of the weighted linear regression test that takes into account effect size and variance interdependence for dichotomous outcomes is proposed in \citet{Peters}.
-% 
-% \vspace{0mm}
-% Let $y_i$ be the log-odds ratio estimate \ref{log.odds.ratio} and $v_{i}$ its variance \ref{variance.log.odds.ratio}
-% 
-% \begin{align}
-% y_{i} &= \log(e_{t}*(n_{c} - e_{c})/e_{c}*(n_{t} - e_{t})) \label{log.odds.ratio}\\
-% v_{i} &= 1/(e_{t}+(n_{t} - e_{t}) + 1/(e_{c}+(n_{c} - e_{c}) \label{variance.log.odds.ratio}
-% \end{align}
-% 
-% and $x_{i}$ be the total sample size $n_{t} + n_{c}$.
-Instead of taking the variance as explanatory or independent variable in regression as in Egger's Test, the inverse of the total sample size $x_{i}$ is used, and the variance $v_{i}$ is used as a weight.
-The subsequent test procedure is then identical to Egger's test.
-% 
-% \vspace{0mm}
-% Peters test is a a small modification of Macaskill's test where the explanatory variable is the sample size instead of its inverse.
-% 
-% 
-% \subsubsection{Harbord's Test: Score based Test}
-% A rank based alternative to Peters test for binary outcomes is the Harbord's test \citep{Harbord}.
-The score $r_{i}$ (the first derivative of the log-likelihood of a proportion with treatment effect equal 0) and its variance $v_{i}$ can be computed as shown in \ref{harbord.score} and \ref{harbord.variance}.
-% 
-% \begin{align}
-% r_{i} &= e_{t} - (e_{t} - e_{c})(e_{t} + (n_{t} - e_{t}))/(n_{t} + n_{c}) \label{harbord.score} \\
-% v_{i} &= \frac{(e_{t} + e_{c})(e_{t} + (n_{t} - e_{t}))(e_{c} + (n_{c} - e_{c}))((n_{t} - e_{t}) + (n_{c} - e_{c}))}{(n_{t} + n_{c})^2(n_{t} + n_{c} - 1)} \label{harbord.variance}
-% \end{align}
-% 
-% Similarly to Egger's or Peters Test, now a weighted linear regression can be performed on $r_{i}/v_{i}$ with the standard error $1/\sqrt{v_{i}}$ as explanatory variable and $1/v_{i}$ as a weight.
-Note that $r_{i}/v_{i}$ is also known as peto odds ratio.
-% 
-% \subsubsection{Schwarzer's Test: Rank Correlation Test}
-% \citet{Schwarzer} developed a test for the correlation between $e_{t} - \mathbb{E}(E_{t})$ and the variance of $E_{t}$, $E_{t}$ being a random variable from the non-central hypergeometric distribution with fixed log odds ratio.
-$\mathbb{E}(E_{t})$ and variance of $E_{t}$ are then estimated based on $e_{t}$.
-% 
-% \vspace{0mm}
-% The standardized cell count deviation $(e_{t} - \mathbb{E}(E_{t}))/\sqrt(v_{i})$ and the inverse of $v_{i}$ is then used in the way as before in Begg and Mazumdar's test.
-% 
-% \subsubsection{R\"ucker's Test: Using the Variance Stabilizing Transformation for Binomial Random Variables}
-% The correlation between variance and effect size of dichotomous outcome measures can be abolished by the variance stabilizing transformation for binomial random variables. Let 
-% 
-% \begin{align}
-% y_{i} = \arcsin{e_{t}/n_{t}} - \arcsin{e_{c}/n_{c}} \\
-% v_{i} = 1/4n_{t} + +/4n_{c}
-% \end{align}
-% 
-% Then one can for example apply Begg and Mazumdar's rank correlation test or Thompson and Sharp's test using the newly obtained variances. 
-% 
-% 
-% \section{Small Study Effect Adjustment}
-% \subsection{Trim and Fill}
-% One method to account for reporting bias in meta-analysis is to apply the Trim and Fill adjustment method \citep{trimfill}.
-It is a nonparametric test based on a funnel plot, on which the effect size estimates of studies are plotted against their standard error.
-% %If reporting bias is present, the estimate will shift in average towards higher or lower efffect sizes compared to the estimates of larger studies
-% 
-% \vspace{0mm}
-% The algorithm for the method tries to estimate the number of studies $k$ that are not available due to reporting bias (different estimators are available for $k$).
-First, $\Delta$ is estimated using a fixed or random effects model.
-Then, the $k$ effect size estimates with the smallest standard errors are trimmed, and $\Delta$ is estimated again.
-The procedure is repeated until $k$ is 0 and the funnel plot is symmetric.
-The total number of missing studies is then mirrored with respect to the final effect size estimate $\Delta$, and $\Delta$ and its standard error is then computed to obtain an unbiased estimate.
-% 
-% \subsection{Copas Selection Model}
-% 
-% A method proposed in \cite{Copas1,Copas2,Copas3} assumes that there is a population of studies of which only a part has been published dependent on the variance and size of their estimated effects.
-Studies with small variance and large effect sizes are more likely to be published than studies with large variance and small effect sizes.
-Note that small effect size means here a treatment effect close to the control effect.
-% 
-% Let $y_i$ be the effect size estimate of study $i$. Then 
-% 
-% \begin{align}
-% y_{i} \sim N(\mu_{i}, \sigma_{i}^2) \\
-% \mu_{i} \sim N(\mu, \tau^2)
-% \end{align}
-% 
-% corresponding to a standard random effects meta-analysis.
-$\mu$ is the overall mean effect, $\sigma_{i}^2$ the within study variance and $\tau^2$ the between study variance.
-This is the \textit{population model}.
-% 
-% \vspace{0mm}
-% The \textit{selection model} is defined as follows. Suppose a selection of studies with reported standard errors $s$ (likely different from $\sigma$). Only a proportion 
-% 
-% \begin{align}
-% P(\textrm{select}|s) &= \Phi(a + b/s) \label{copas.selection1}
-% \end{align}
-% 
-% of the selection will be published, with a defining the overall proportion of published studies and b (assumed to be positive) defining how fast this proportion increases with $s$ becoming smaller.
-\ref{copas.selection1} can be rewritten as
-% 
-% \begin{align}
-% z = a + b/s + \delta \label{copas.selection2}
-% \end{align}
-% 
-% with $\delta \sim N(0,1)$. The study with standard error $s$ is only selected if $z$ is positive. Therefore, the larger $z$, the more likely the study is selected.
-% Combining population and selection model for study $i$, we have 
-% 
-% \begin{align}
-% y_{i} = \mu_{i} + \sigma_{i}\epsilon_{i} \\
-% \mu_{i} \sim N(\mu, \tau^2) \\
-% z_{i} = a + b/s_{i} + \delta_{i}
-% \end{align}
-% 
-% where $(\epsilon_{i}, \delta_{i})$ are standard normal residuals and jointly normal with correlation $\rho = cor(y_{i}, z_{i})$.
-Every given study $i$ in the meta-analysis has $z_{i} > 0$.
-If $\rho$ is large and positive and $z_{i} > 0$, then the estimate of a study $i$ that is selected is likely to have positive $\epsilon_{i}$ and $\delta_{i}$.
-Thus, the true mean $\mu$ is likely to be overestimated.
-% 
-% \vspace{0mm}
-% Let $u = a + b/s$, $\lambda(u) = \phi(u)/\Phi(u)$ ($\phi$ is the standard normal density function) and $\tilde{\rho} = \sigma/\sqrt(\tau^2 + \sigma^2) \rho$.
-The probability of a study being selected is
-% 
-% \begin{align}
-% P(\textrm{select}|s, y) = P(a,b,s,y) = \Phi(\frac{u + \tilde{\rho}((y - \mu)/\sqrt(\tau^2 + \sigma^2))}{\sqrt{1 - \tilde{\rho^2}}})
-% \end{align}
-% 
-% It can also be shown that the expected value 
-% 
-% \begin{align}
-% \mathbb{E}(y|s, select) = \mu + \rho\sigma\lambda(u) \label{copas.expectation}
-% \end{align}
-% 
-% which shows that the expected value for a study is larger for larger $\sigma$. 
-% 
-% \vspace{0mm}
-% One can compute a likelihood function based on the distribution of $y$ conditional on $z > 0$.
-The likelihood can be maximized for any given pair $a,b$ (can not be estimated since the number of missing studies is not known), and a maximum likelihood estimate $\hat{\mu}$ for the true mean $\mu$ can be obtained.
-One can then perform a sensitivity analysis.
-First, one looks how $\hat{\mu}$ changes for different values of $a,b$.
-One can then compare the fitted values in \ref{copas.expectation} with the real values.
-To test the fit of the model (while keeping all other parts unchanged), the model can be extended in the following way :
-% 
-% \begin{align}
-% y_{i} &= \mu_{i} + \beta s_{i} + \sigma_{i}\epsilon_{i}
-% \end{align}
-% 
-% If we accept $\beta = 0$, then we accept that the selection model has satisfactorily explained any relationship between $y$ and $s$.
-Only if the value is large enough, typically $p > 0.05$, one concludes that the selection model has explained the observed data.
-The $p$\hspace{0.4mm}-value is obtained by a likelihood ratio test comparing the maximum of the likelihood with the $\beta$ term added and without it, and by a likelihood ratio test.
-% 
-% \vspace{0mm}
-% To find out if the null-hypothesis of, say, $\mu = 0$ can be rejected, another likelihood ratio test can be performed, this time with imputing $\mu = 0$ and comparing the two maximum likelihoods.
-% 
-% \vspace{0mm}
-% In practice, only a range of values for $a,b$ are reasonable.
-For those values, the quantities above can be calculated and illustrated.
-Values for $\mu$ that have $p$\hspace{0.4mm}-values over a predefined significance threshold can be used for inference of the effect size.
-% 
-% \subsection{Adjustment by Regression}
-% There are multiple ways to adjust for small study effects by regression.
-The general idea is to extrapolate the effect size of a study with a variance of zero based on the given effects and variances.
-% 
-% \citet{limitmeta} use a random effects model together with shrinkage procedure to obtain an unbiased estimate.
-Similarly to what has been seen in Copas selection model, we let $y_{i}$ depend on the intercept $\beta_{0}$ and on its standard error $\sqrt{v_{i}}$ as in \ref{limitmeta.regression}.
-% 
-% \begin{align}
-% y_{i}& = \beta_{0} + \beta_{1}(\sqrt{v_{i} + \tau^2}) + \epsilon_{i}(\sqrt{v_{i} + \tau^2}), \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1)  \label{limitmeta.regression}
-% \end{align}
-% 
-% $\beta_{1}$ represents the bias introduced by small study effects, as can be seen when looking at \ref{limitmeta.infinitesample}
-% 
-% \begin{align}
-% \mathbb{E}((y_{i} - \beta_{0})/\sqrt{v_{i}}) \rightarrow \beta_{1} \textrm{ if } \sqrt{v_{i}} \rightarrow \infty \label{limitmeta.infinitesample} \\
-% \mathbb{E}(y_{i}) \rightarrow \beta_{0} + \beta_{1}\tau \textrm{if} \sqrt{v_{i}} \rightarrow 0 
-% \end{align}
-% 
-% After estimating $\tau^2$, one can estimate $\beta_{0}$ and $\beta_{1}$ as seen before \eg in Thompson and Sharp's Test with weights also equal to Thompson and Sharp's Test (see \ref{Thompson}).
-% 
-% \vspace{0mm}
-% To diminuish the random variation within studies, but keep the variation between studies, we change \ref{limitmeta.regression} to a scenario where each study has $M$-fold increased precision:
-% 
-% \begin{align}
-% y_{M,i} &= \beta_{0}^\star + \beta_{1}^\star(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{v_{i}/M + \tau^2}) \label{limitmeta.regression}
-% \end{align}
-% 
-% Letting $M \rightarrow \infty$, we obtain:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau(\beta_{1}^\star + \epsilon_{i}),  \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \label{limitmeta.regression.infinity}
-% \end{align}
-% 
-% Note that:
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \tau\beta_{1}^\star = \beta_{0}
-% \end{align}
-% 
-% $\beta_{0}$ is termed the limit meta analysis expectation. Now, the random errors from \ref{limitmeta.regression} are rewritten as:
-% 
-% \begin{align}
-% \epsilon_{i} &= \frac{y_{i} - \beta_{0}^\star}{\sqrt{v_{i} + \tau^2}} - \beta_{1}^\star
-% \end{align}
-% 
-% Assuming $\epsilon_{i}$ to be fixed, we can plug it into \ref{limitmeta.regression.infinity} and get 
-% 
-% \begin{align}
-% y_{\infty,i} &= \beta_{0}^\star + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_{i} - \beta_{0}^\star)
-% \end{align}
-% 
-% By estimating $\tau^2, v_{i}$ and  $\beta_{0}^\star$, we can use the formula to obtain a new study means, adjusted for small study effects and shrunken to a common mean.
-
-% \begin{align} \label{cox reg}
-% P(Y < y|\mathbf{x}) = 1 - exp(-exp(h(y) - (\mathbf{x})^\top\beta)
-% \end{align}
-% 
-% See \cite{hothorn} for further information. It specifies the instantaneous risk of an event at time t to be
-% 
-% \begin{align}
-% \lambda_{0}(t)exp((\mathbf{x})^\top\beta) \nonumber
-% \end{align}
-% 
-% The model is regarded as a semi parametric model since it includes the covariates in a linear fashion but leaves the baseline hazard $\lambda_{0}(t)$ unspecified.
-The factor $exp((\mathbf{x})^\top\beta)$ has the interpretation of a hazard ratio between the reference with $\mathbf{x} = 0$.
-The formal definition of the hazard is
-% 
-% \begin{align}
-% h(t) = \lim_{h \to 0} \frac{P(t < T < t + h| T > t)}{h}
-% \end{align}
-% 
-% 
-% \begin{align} \label{generalized linear model}
-% \mathbf{Y}{_{ij}}|U{_i},\epsilon{_{ij}} = (1,x{_i}^\top)\beta + U{_i} + \epsilon{_{ij}}
-% \end{align}

### 2019-08-14 report/chapter03.Rnw
Draft for Simon and Prof. Held

@@
 
-<<echo = FALSE, warning=FALSE, message=FALSE, cache = TRUE>>=
+<<echo = FALSE, warning = FALSE, message=FALSE, cache = TRUE>>=
 #Load data:
@@
 
-\subsection{Structure and Content}
+\section{Structure and Variables}
 The dataset consists of \Sexpr{length(unique(data$id))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(data$study.name))} studies and \Sexpr{dim(data)[1]} results.
@@
 
-<<echo=FALSE, results = 'asis'>>=
+<<echo=FALSE, results = 'asis', warning =FALSE, message = FALSE>>=
 print(xtable(barbi1, label = "barbiturate.row", digits = 0,
@@
 
-<<echo=FALSE, results='asis'>>=
+<<echo=FALSE, results='asis', warning =FALSE, message = FALSE>>=
 print(xtable(barbi2, label = "barbiturates", caption = "Barbiturate and head injury review.
@@
 
-<<echo=FALSE, results='asis'>>=
+<<echo=FALSE, results='asis', warning =FALSE, message = FALSE>>=
 print(xtable(missing.table, label = "missing", caption = "Number of missing variables and measurements in the dataset", align = "lr"), include.colnames = F,
@@
 
-<<echo=FALSE, results='asis'>>=
+<<echo=FALSE, results='asis', warning =FALSE, message = FALSE>>=
 print(xtable(outcome.measure.frequencies, label = "outcome.measure.frequencies", 
@@
 Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]} and the 95\% quantile \Sexpr{study.range[6]}.
-The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citet{largest.review}
+The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citealp{largest.review}
 which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1,497 results in total.\\
@@
 
-<<echo=FALSE, results='asis'>>=
+<<echo=FALSE, results='asis', warning =FALSE, message = FALSE>>=
 rownames(cum.repr.trials.subg)[15] <- "$\\geq$ 15"
@@
 Subgroups are not indicated in \Sexpr{no.subgroup}\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane Review Groups did.
+\\
 The methods described in the methods chapter \ref{ch:methods} most often apply directly to the algorithms used in \texttt{meta} and \texttt{metafor}. \\

### 2019-08-14 report/chapter04.Rnw
Draft for Simon and Prof. Held

@@
 @
-\caption{Median of the absolute $z$-score across sample size plotted against the total sample size.}
+\caption{Median of the absolute Fisher's $z$ transformed correlation across sample size plotted against the total sample size.}
 \label{z.samplesize}
@@
 The means in Table \ref{adjustment.difference} suggest that the average reduction is small.
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} meta-analyses have their $z$-score reduced by more than 0.13 by regression adjustment (and 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} increased by -0.11 or more, fixed effects reference).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} meta-analyses have their Fisher's $z$ transformed correlation reduced by more than 0.13 by regression adjustment (and 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} increased by -0.11 or more, fixed effects reference).
 Also, std.
@@
              caption = "Missing meta-analysis combined treatment effect and adjusted treatment effects.
-Abbreviations are used for z-score (= z) and std.
+Abbreviations are used for Fisher's z transformed correlation (= z) and std.
 mean difference (= d).", label = "missing.differences", align = "lcccrrrrrrrr"),
@@
 A Tukey mean difference plot can reveal systematic differences and biases between the two measurement methods.
-Note that only 26 out of \Sexpr{dim(meta.iv)[1]} \texttt{IV} outcome data is included when using $z$-score and std.
+Note that only 26 out of \Sexpr{dim(meta.iv)[1]} \texttt{IV} outcome data is included when using Fisher's $z$ transformed correlation and std.
 mean differences, since not all effects could be transformed.

### 2019-08-14 report/chapter05.Rnw
Draft for Simon and Prof. Held

--- 2019-08-06 report/chapter05.Rnw
@@
 
-<<echo=FALSE, warning=FALSE>>= 
-#Load data:
-rm(list = ls())
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'Data/PubBias')
-PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2019-07-04.csv'
-PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results_new')
-# PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-load(file.path(PATH_DATA, "PubBias_2019-07-19.RData"))
-load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
-load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
-load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
-load(file.path(PATH_RESULTS, "meta_id_I2.RData"))
-load(file.path(PATH_RESULTS, "meta.bin.RData"))
-load(file.path(PATH_RESULTS, "meta.cont.RData"))
-load(file.path(PATH_RESULTS, "meta.iv.RData"))
-#----------------------------------------------------------------------------------------------------#
-
-adjustment.diff.keep <- meta.f %>% 
-  mutate(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
-                                 sign(est.copas) != sign(est.fixef) ~ -abs(est.copas)),
-         est.reg.f = case_when(sign(est.reg) == sign(est.fixef) ~  abs(est.reg),
-                               sign(est.reg) != sign(est.fixef) ~ -abs(est.reg)),
-         est.copas.r = case_when(sign(est.copas) == sign(est.ranef) ~  abs(est.copas),
-                                 sign(est.copas) != sign(est.ranef) ~ -abs(est.copas)),
-         est.reg.r = case_when(sign(est.reg) == sign(est.ranef) ~  abs(est.reg),
-                               sign(est.reg) != sign(est.ranef) ~ -abs(est.reg)),
-
-         est.d.copas.f = case_when(sign(est.d.copas) == sign(est.d.fixef) ~  abs(est.d.copas),
-                                   sign(est.d.copas) != sign(est.d.fixef) ~ -abs(est.d.copas)),
-         est.d.reg.f = case_when(sign(est.d.reg) == sign(est.d.fixef) ~  abs(est.d.reg),
-                                 sign(est.d.reg) != sign(est.d.fixef) ~ -abs(est.d.reg)),
-         est.d.copas.r = case_when(sign(est.d.copas) == sign(est.d.ranef) ~  abs(est.d.copas),
-                                   sign(est.d.copas) != sign(est.d.ranef) ~ -abs(est.d.copas)),
-         est.d.reg.r = case_when(sign(est.d.reg) == sign(est.d.ranef) ~  abs(est.d.reg),
-                                 sign(est.d.reg) != sign(est.d.ranef) ~ -abs(est.d.reg)),
-
-         est.z.copas.f = case_when(sign(est.z.copas) == sign(est.z.fixef) ~  abs(est.z.copas),
-                                   sign(est.z.copas) != sign(est.z.fixef) ~ -abs(est.z.copas)),
-         est.z.reg.f = case_when(sign(est.z.reg) == sign(est.z.fixef) ~  abs(est.z.reg),
-                                 sign(est.z.reg) != sign(est.z.fixef) ~ -abs(est.z.reg)),
-         est.z.copas.r = case_when(sign(est.z.copas) == sign(est.z.ranef) ~  abs(est.z.copas),
-                                   sign(est.z.copas) != sign(est.z.ranef) ~ -abs(est.z.copas)),
-         est.z.reg.r = case_when(sign(est.z.reg) == sign(est.z.ranef) ~  abs(est.z.reg),
-                                 sign(est.z.reg) != sign(est.z.ranef) ~ -abs(est.z.reg)),
-
-         est.fixef = abs(est.fixef),
-         est.ranef = abs(est.ranef),
-         est.z.fixef = abs(est.z.fixef),
-         est.z.ranef = abs(est.z.ranef),
-         est.d.fixef = abs(est.d.fixef),
-         est.d.ranef = abs(est.d.ranef))
-
-truebias.bin.percentage <- round(adjustment.diff.keep %>% filter(outcome.flag == "DICH") %>% filter(est.fixef - est.reg > 0) %>% count()/(dim(meta.bin)[1])*100,1)
-
-wider.dataset.ioannidis.comparison <- data.ext2 %>% filter(outcome.flag == "DICH") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% summarise(n()) %>% ungroup() %>% count()
-
-restr.dataset.ioannidis.comparison.count <- data.ext2 %>% filter(outcome.flag == "DICH") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>%  ungroup() %>% distinct(id, .keep_all = T) %>% count()
-
-restr.dataset.ioannidis.comparison <- (data.ext2 %>% filter(outcome.flag == "DICH") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>%  ungroup() %>% distinct(id, .keep_all = T) %>% count() / wider.dataset.ioannidis.comparison)*100
-
-largerten.ioannidis.comparison <- (data.ext2 %>% filter(outcome.flag == "DICH") %>% group_by(meta.id) %>% filter(n() > 9) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>% summarise(n()) %>% ungroup() %>% count() / wider.dataset.ioannidis.comparison)*100
-
-variance.ratio.ioannidis.comparison <- (data.ext2 %>% filter(outcome.flag == "DICH") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>% filter((max(se)^2)/(min(se)^2) > 4) %>% summarise(n()) %>% ungroup() %>% count() / wider.dataset.ioannidis.comparison)*100
-
-onesig.ioannidis.comparison <- (data.ext2 %>% filter(outcome.flag == "DICH") %>% group_by(meta.id) %>% filter(n() > 2) %>% filter(dupl.remove == 0) %>% filter(!all(events1 == 0) & !all(events2 == 0)) %>% filter(!all(events1 == total1) & !(all(events2 == total2))) %>% filter(se > 0) %>%
-  filter(sum(pval.single < 0.05, na.rm = T) > 0) %>% summarise(n()) %>% ungroup() %>% count() / wider.dataset.ioannidis.comparison)*100
-
-allcriteria <- (dim(meta.bin)[1]/wider.dataset.ioannidis.comparison)*100
-
-harbord.ioannidis.comparison <- (meta.bin %>% filter(pval.harbord < 0.1) %>% count()/dim(meta.bin)[1])*100
-
-own.results <- c(wider.dataset.ioannidis.comparison$n, paste(round(c(largerten.ioannidis.comparison$n, variance.ratio.ioannidis.comparison$n, onesig.ioannidis.comparison$n, allcriteria$n,
-                       harbord.ioannidis.comparison$n)), "%", sep = ""))
-
-ioannidis.results <- c(6873, paste(c(13, 72, 55, 5, 12), "%", sep = ""))
-
-comparison.ioannidis <- data.frame(Ioannidis = ioannidis.results, Thesis = own.results)
-rownames(comparison.ioannidis) <- c("Wider dataset (n)", "study number > 10", "variance ratio > 4",
-                                    "study sig. number > 1", "all exclusion criteria", "harbord test p-value < 0.1")
-
-meta.data <- data.ext2 %>% filter(meta.id %in% meta.f$meta.id)
-
-@
-
 \chapter{Discussion} \label{ch:Discussion}
 
-\section{Results in the light of the Literature}\label{sec:discussion.results}
-
-Before discussing the results of the previous analyses, some results of similar studies are discussed briefly and compared to the results of this study, if possible.
-When clear methodological drawbacks are found in the analysis, the reader is referred to chapter \ref{ch:methods} for comments on the disadvantages.
-The amount of studies analyzing publication bias makes it not possible to discuss any of them, and thus we only some interesting and/or representative examples are shown.
-
-\subsection{\citet{Egger}}
-The Cochrane database (1996 issue 2) and publications from the four leading medicine journals (the Lancet, BMJ, JAMA and Annals of Internal Medicine) between 1993 and 1996 were used to find systematic reviews with randomized controlled trials for the application of Egger's small study effect test.
-They included 38 meta-analyses with at least 5 studies and binary outcomes from the Cochrane Library and 37 from the journals.
-Five (13\%) meta-analyses from Cochrane and 13 (38\%) from the journals had significant two sided small study effect test results ($p$-value < 0.1).
-Also, they found that test-statistics were more often negative, which corresponded in their setup to larger effects in small studies.
-(\Sexpr{round(((24/38))*100, 1)} among Cochrane meta-analyses and \Sexpr{round(((26/37))*100, 1)} for journal meta-analyses).
-The results from this report with R\"ucker's test are: \Sexpr{round((length(which(meta.bin$pval.rucker < 0.1))/dim(meta.bin)[1])*100,1)}\%, and when using regression adjustment to decide about the direction of publication bias, we get \Sexpr{truebias.bin.percentage$n}\%.
-
-\subsection{\citet{sutton.2000}}
-Out of 397 systematic reviews from the Cochrane database (complete number for 1998, issue 3), 49 had more than ten included studies and binary outcomes and 48 compared two treatments.
-They were analysed by trim-and-fill method \citep{trimfill} to detect and adjust for funnel plot asymmetry (similar to small study effect tests, but the method is known to overestimate bias).
-23 were found to have missing studies, and eight had more than three missing studies which was considered to be significant publication bias.
-Additionally, they found that three estimates of random effects meta-analysis became non-significant after adjustment, and one became significant (by negative adjustment).
-The results are difficult to compare, but the methodological limitations make this findings unreliable.
-
-\subsection{\citet{Ioannidis2007}}
-Data processing steps were however different, and only binary outcomes as used in two-by-two tables were analysed.
-The approximately corresponding numbers are put in parentheses for comparison.
-The Cochrane Library from 2003 (issue 2) was used.
-After removal of duplicates and intractable meta-analyses, they had 6,873 meta-analyses with more than two studies left (\Sexpr{format(wider.dataset.ioannidis.comparison$n, big.mark = ",")}).
-When only using one meta-analysis per review, this reduced to 846 (\Sexpr{format(restr.dataset.ioannidis.comparison.count$nn, big.mark = ",")}.
-Then, the criteria that have also been applied in this masters thesis are applied: $I^2 < 0.5$, variance ratio of smallest and largest effects > 4, at least one significant study result and at least 10 studies to be used.
-Afterwards, they applied Harbord's, Egger's and Begg's Test to the dataset.
-The reader can compare some corresponding numbers in Table \ref{ioannidis}.
-% The results seem to be similar enough to claim that neither the methods nor the data and it's results are differing substantially.
-Because the thesis relies on more data, it is likely to be more accurate and can possibly add to the findings of \citet{Ioannidis2007}.
-
-<<echo = FALSE, results = 'asis'>>=
-print(xtable(comparison.ioannidis, caption = "Comparison of results from Ioannidis et.al.
-(2007) to the results of the thesis.
-The percentage of meta-analysis which match all exclusion criteria denotes the ones that apply to all criteria in the table plus the small heterogeneity criterium.
-Harbord test is two-sided.", label = "ioannidis", align = "lrr"))
-@
-
-\subsection{\citet{souza.2007}}
-Reviews of the World Health Organization (WHO) Reproductive Health Library (RHL), issue 9, were analysed with the trim-and-fill method.
-The RHL reproduces and expands reviews from the Cochrane Library with implications for developing countries.
-21 of 105 reviews contained more than ten studies and were used.
-Trim-and-fill found asymmetry in 18 of 21 studies, and 10 had more than 3 missing studies (``significance'').
-Two of those and one with one missing studies found no evidence for treatment effects after the 0.05 $p$-value threshold after adjustment by trim-and-fill.
-
-\subsection{\citet{kicinsky}}
-The author uses a Bayesian hierarchical selection model, but does not analyse treatment effects, but the parameters of the weight function of the selection model, which is estimated with a Bayesian approach and MCMC sampling.
+The aim of this study was to assess publication bias in the Cochrane Library, ``the single, most reliable source of evidence in healthcare'' (citation from Cochrane).
+We applied a series of methods to test and adjust for publication bias in meta-analyses that matched our criteria.
 \\
-The author provides an estimate of the probability of including significant findings versus non-significant findings in Cochrane meta-analyses over time.
-The data is from the Cochrane Library from 2013 (issue number not provided).
-The author excluded treatment - treatment comparisons and analysed safety and efficacy meta-analyses separately (how this was achieved is not documented in the paper).
-\\
-From 3845 reviews, the author separated 907 reviews with more than ten studies.
-From those, 539 compared placebo to treatment.
-After removing duplicates and sensitivity analyses, 358 analyses with 1297 meta-analyses remained.
-From these 191 were excluded because they comprised overall mortality and withdrawal, because these could not clearly be specified as safety or efficacy, respectively.
-\\
-1106 meta-analyses from 329 meta-analyses, containing 802 efficacy and 304 safety meta-analyses.
-The median publication year per meta-analysis was 1997 for efficacy meta-analyses and 1999 for safety meta-analyses.
-Then, a Bayesian two-step hierarchical selection model was applied (\citet{bayesian.selection.model}, \citet{bayesian.selection.model.2}).
-It assumes that the selection process is a two-step weight, which assigns different probabilities to non-significant and significant effects.
-Thus, a ratio of publication probability between significant and non-significant study estimates using a two-step weight function.
-The model was fitted with the Monte-Carlo Markov-Chain algorithm STAN and the geometric mean was used as an estimate for the publication probability ratio.
-Simulations performed in \citep{bayesian.selection.model} indicate that the method performs well if the true mean effect size was not small, and also robust to small study effects.
-It outperformed Egger's test and Begg's test in assessing publication bias, especially when small study effects were absent, and had lower false-positive rates.
-\\
-The results showed a clear publication bias for significant results for efficacy meta-analyses (27\% higher for significant studies, 95\%CI credible intervals: 1.18 to 1.36).
-The probability was more than twice as high in 27\% of the meta-analyses (95\% CI: 23\% to 31\%).
-But the probability decreased: from 1.65 (95\% CI: 1.31 to 2.15) in 1980 (average publication year) to 1.36 (95\% CI: 1.17 to 1.62) in 1990 to 1.18 (95\% CI: 1.04 to 1.33) in 2000.
-For sake of completeness, the probability of inclusion was  1.78 (95\% CI: 1.51 to 2.13) larger for non-significant safety effect estimates, but again, decreased with time (1.77, 95\% CI: 1.46 to 2.21 in 2000).
-The results are in line with the results from this study, but it was not possible to reaffirm the finding of weaker publication bias in reviews published more frequently.\\
-
-\subsection{\citet{vanAert.2019}}
-The Authors of this recent study sample 366 meta-analyses randomly from the Cochrane Library (supposedly 2018 or 2019, not mentioned).
-They exclude any meta-analysis which include effect sizes identical to effect sizes in other meta-analyses (the larger meta-analysis is retained).
-Additional criteria were: $I^2 < 0.5$ and at least 5 studies.
-The meta-analyses were analysed using standardized mean differences and four different tests for publication bias: Egger's test, p-uniform test \citep{p.uniform}, Begg and Mazumdar's rank correlation test and the excess significance test.
-\\
-The authors found, based on the significance threshold of $p$ < 0.1, the following results (own results in brackets):
-12.2 \% significant results from Egger's test (\Sexpr{round((length(which(meta.bin$pval.rucker < 0.1)) + length(which(meta.cont$pval.egger < 0.1)) + length(which(meta.iv$pval.egger < 0.1)))/dim(meta.f)[1]*100,1)}),
-8.5 \% significant results from Begg and Mazumdar's rank correlation test (\Sexpr{round((length(which(meta.bin$pval.schwarzer < 0.1)) + length(which(meta.cont$pval.begg < 0.1)) + length(which(meta.iv$pval.begg < 0.1)))/dim(meta.f)[1]*100,1)}) and
-4.4 \% significant excess significance test results (\Sexpr{round((length(which(meta.f$pval.d.tes < 0.1))/dim(meta.f)[1])*100, 1)}).
-It is known that the publication bias tests are lacking power in general as sample size is usually small.
-Decreasing sample size will result in lower power, especially if the maximal sample size is $n \geq 5$.
-Additionally, it was also not taken into consideration that it may be difficult to state that publication bias is present in a meta-analysis when no result within it is statistically significant (only 18.8 \% of the effects of the sampled meta-analyses were).
-This, together that it has not been tried to exclude safety outcomes, may account for the large differences between the results.
-\\
-The author's come to the conclusion in their study that in contrast to other studies, they find few evidence for publication
-
-\subsection{Further Studies on Publication Bias}
-\citet{Zhang.2013} find publication bias in critical care studies with similar methods.
-\citet{Nusch} report publication bias in clinical osteoarthritis research because of funnel plot asymmetry and pledge for routine assessment of publication bias.
-\citet{Dechartres.2013} analyse publication bias based on sample size in meta-analyses from top journals and Cochrane reviews in 93 Meta-analyses and find that, for example, effects in trials with less than 50 patients were 48\% larger than in larger trials.
-\citet{Onishi.2014} find that in 36 Meta-Analyses without comprehensive literature research, there are 19.4\% significant publication bias tests (Egger's test).
-
-\section{Interpretation}
-In this study, evidence for publication bias has been found in approximately 20\% of the meta-analyses.
-The results are often times consistent among different tests and subsets of the data.
+The main result was that among the analysed meta-analyses, approximately 20\% beared evidence for publication bias.
+Adjustment for publication bias lead to a decrease in evidence for treatment efficacy.
+After comparison with previous studies that analysed publication bias in the Cochrane Library, we found that our results were similar to the results of these studies (\eg \citealp{Egger}, \citealp{Ioannidis2007}).
+Further information can be found in the Appendix\\
+% In this study, evidence for publication bias has been found in approximately 20\% of the meta-analyses.
+The results are oftentimes consistent among different tests and subsets of the data.
 A mixed effects meta regression confirms these findings with very large evidence for small study effects (indicating publication bias).
 Since the results of two-sided tests do not differ substantially from previous findings, the results are in line with previous research.\\
-% There have been proposed a number of reasons for this tendencies in smaller studies (see \citet{Egger} for a thorough discussion).
+% There have been proposed a number of reasons for this tendencies in smaller studies (see \citealp{Egger} for a thorough discussion).
 In clinical settings, it might be that the requirement for more study participants in large studies might systematically change the study population.
@@
 Presence of publication bias in meta-analyses can ultimately lead to patient harm if decision makers in clinical practice use the meta-analyses to decide about application of a treatment.
-On the swiss Cochrane website, it is stated that Cochrane is the ``single most reliable source of evidence on the effects of health care''.
 However, publication bias does in general lead to too large confidence in the results of the meta-analyses.
@@
 \\
-The term publication bias is frequently used in this study, but \Sexpr{round((length(which(meta.data$study.data_source == "UNPUB"))/dim(meta.data)[1])*100, 1)}\% of the analysis dataset (1) are unpublished results.
+The fact that Cochrane also uses study reports from Grey literature and other unpublished data (1.5\% of the analysed data), which contain usually smaller effect sizes, likely mitigates our estimate of publication bias.
+% The term publication bias is frequently used in this study, but \Sexpr{round((length(which(meta.data$study.data_source == "UNPUB"))/dim(meta.data)[1])*100, 1)}\% of the analysis dataset (1) are unpublished results.
 This mitigates the estimated extent of publication bias in this study since it has been shown repeatedly that effects in the grey literature are smaller.
@@
 \section{Limitations}
-After application of the criteria of \citet{Ioannidis2007}, there are left \Sexpr{round((740/6354)*100, 1)} \% of the reviews and \Sexpr{round((23243/70662)*100, 1)}\% of the studies.
-It is not clear if the results also apply for the excluded data, \ie if the extent of publication bias is similar.
-The most restrictive criterium of exclusion was that a meta-analysis had to have at least ten studies.
-The included studies are thus likely to be part of enforced and sustained research efforts.
-When fewer and unparalleled studies are available, the quality of the research is not necessarily better.
-Publication bias may be even more of an issue in more discovery oriented research \citet{ioannidis.2005}.
-By excluding meta-analyses where $I^2 \geq 0.5$, the most extreme cases of publication bias are possibly removed since publication bias increases the between-study heterogeneity.\\
+This is an exploratory study, and the results are rather suggestive than confirmatory.
+As a part of evidence it is supposed to strengthen previous assessments of publication bias and possibly, guide further research.
+\\
+It is clear that publication bias could only be assessed in a part of all meta-analyses of the Cochrane Library and that the extent of publication bias in the remaining data is unknown.
+Because one inclusion criterion was that more than ten study results had to be available for a given research question, the analysed dataset contains rather the part of data with established and enduring research.
+When research is more experimental and exploratory, it may well be that publication bias is an issue as well, or even more of an issue.
+Publication bias is possibly related to more discovery oriented, modern research \citet{ioannidis.2005}.\\
+There is an unknown amount of meta-analyses with secondary outcomes in the analysis.
+It is not well investigated if and how secondary outcomes are affected by publication bias, and how much they are affected by between-study heterogeneity, as researchers might not follow the same stringent protocols when assessing secondary outcomes.
+Together with unremoved adverse effect meta-analyses, which are likely subject to different kinds of publication bias, they can distort or mitigate the estimated extent of publication bias in this study.
+If one assumes that publication bias is not as strong in secondary outcomes as in primary outcomes, and that adverse effects are subject to bias for small effects (as suggested by \citealp{kicinsky}), the extent of publication bias will be underestimated.\\
+Some criticism can be addressed on the methods.
+The small study effect which is used as an indication for publication bias can be caused by other biases such as selective outcome reporting, or poor methodological quality of smaller studies.
+It can also be caused by true heterogeneity between studies; early and small studies are more likely to include high-risk patients for which treatment can have larger benefits.
+Where effect size estimates and their standard errors are not independent (\eg log risk ratios, std.
+mean differences), small study effect can be a statistical artifact.
+However, true heterogeneity between smaller and larger studies might as well mask the presence of publication bias, for example if smaller studies have smaller effects due to true between-study heterogeneity.\\
+Also, small study effect tests do not use statistical significance directly.
+They will fail when there are no significant results, but the smaller studies have larger effects than the larger studies, in which case no publication bias for significant results could exist.
+The only test that is applied that takes into account statistical significance per se is the excess significance test, which is underpowered.
+However, we restricted the meta-analyses such that at least one significant effect had to be included.
+\\
+Most small study effect tests rely on linear regression.
+Linear regression is prone to outliers, especially if the sample size is small.
+The issue is partially resolved by weighting, but the usual procedure to assess if the model assumptions are fulfilled are not possible for such a large number of model fits.\\
+All the criticism also applies for adjustment methods, as they also rely on small study effects.
+A weakness of the regression adjustment is that it also adjusts if the uncertainty in the small study effect is large.
+To compare it in this case with the meta-analysis estimate is difficult because the uncertainty in estimating the small study effect affects the uncertainty of the treatment effect.
+Copas selection model uses the $p$-value threshold of 0.1 to decide if adjustment is necessary or not.
+One could argue that this threshold is somewhat arbitrary.
+When assessing the evidence for the treatment effect being different from the effect under the null, a likelihood ratio test would provide more appropriate results than the Wald test.
+%Selection models do not account for the uncertainity that is contained in the selection process parameters they use, which makes it difficult to use their results to test against the null hypothesis of no treatment effect.\\
+Another issue that the model is not estimating the selection process parameters, but rather applying some criteria of parsimony (the model with least publication bias/selection with $p$-value for small study effect > 0.1 is chosen).
+As the regression model, this model also comes with various assumptions that likely affect the results.
+But in simulations, the methods all had fewer mean-squared error and bias than the classical meta-analysis methods when publication bias was present.\\
+Publication bias can also be present if a meta-analysis lacks a small study effect, for example if significant results are published irrespective of the sign of the effect estimate.
+Methods as the excess significance test of \citealp{excess.significance} are applied to overcome this issue, but the method is known to lack power.
+No methods exist so far to adjust for excess significance.
+This would be a reason to assume that publication bias is underestimated.\\
+Given the large body of evidence for publication bias by other means, it is unlikely that the unexpectedly large proportion of significant test results and the downward corrected treatment effect estimates are merely false positives.
+Of course, the general practice is to apply all the methods in this study carefully, and with background knowledge about each single study in the meta-analyses, to differentiate between true heterogeneity and publication bias.
+But this does not disqualify these results, but stress the necessity that authors of meta-analyses investigate possible publication bias thoroughly.
+% Therefore, the results are not exact and could be improved if more suitable methods are applied.
+The Bayesian approach taken by \citealp{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions.
+\\
 % Furthermore, the sub-partitioning of meta-analyses based on comparison, outcome and subgroup is only one possibility%, which is in fact not recommended by the Cochrane Organisation. 
@@
 \\
-It also has to be said that the removal of safety outcomes is only partially successful.
+% It also has to be said that the removal of safety outcomes is only partially successful.
 This is an issue, because it is not well known if and how the publication probability is affected by the size of safety outcomes.
-\citet{kicinsky} suggests that they may inversely affect publication (\ie non-significant effects are preferred).\\
-Also, it has been previously discussed that the method to detect the side on which bias is to be expected can fail and provide meaningless results.
-One could also discuss in more general terms if one can speak of publication bias in meta-analyses that have only one significant effect out of ten ($n$ = \Sexpr{length(which(meta.f$n.sig.single == 1))}), \ie if statistical significance is largely absent in a meta-analysis.\\
-There is also criticism that one can address on the methods.
-It is possible that the results are caused by systematic differences in the population of study participants only.
-This is considered rather unlikely.
-Other criticism is more severe.
-The small study effect tests applied do not account for statistical significance of effects directly.
-They work because smaller studies with larger errors need larger effects to be significant.
-The only test that is applied that takes into account statistical significance per se is the excess significance test, which is underpowered.\\
-The criticism also applies for adjustment methods, as they also rely on small study effects.
-A weakness of the regression adjustment is that it also adjusts if the uncertainty in the small study effect is large.
-To compare it in this case with the meta-analysis estimate is difficult because the uncertainty in estimating the small study effect affects the uncertainty of the treatment effect.
-Copas selection model uses the $p$-value threshold of 0.1 to decide if adjustment is necessary or not.
-One could argue that this threshold is arbitrary.
-Additionally, the threshold is used in two manners: first to decide if adjustment is necessary at all, and secondly, if the adjusted model does suitably account for publication bias ($p$ > 0.1).
-Hypothesis tests against the null hypothesis can however not be used to decide in favor of the null-hypothesis, and a separate test would be needed there.
-\\
-With Copas selection model, it is in general the issue that the model is not estimating the selection process parameters, but rather applying some criteria of parsimony (the model with least publication bias/selection with $p$-value for small study effect > 0.1 is chosen).
-\\
-Publication bias can also be present if a meta-analysis lacks a small study effect, for example if by chance, the smaller studies were published irrespectively of the statistical significance of their findinfs.
-Methods as the excess significance test of \citet{excess.significance} are applied to overcome this issue, but the method is known to lack power.
-No methods exist so far to adjust for excess significance.\\
-Therefore, the results are not exact and could be improved if more suitable methods are applied.
-The Bayesian approach taken by \citet{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions.
-\\
+\citealp{kicinsky} suggests that they may inversely affect publication (\ie non-significant effects are preferred).\\
+% Also, it has been previously discussed that the method to detect the side on which bias is not working perfectly.
+One could also discuss in more general terms if one can speak of publication bias in meta-analyses %that have only one significant effect out of ten ($n$ = \Sexpr{length(which(meta.f$n.sig.single == 1))}), \ie
+% if statistical significance is largely absent in a meta-analysis.\\
+
+\subsection{A Note on the Use of Effect Size Measures}
+An inevitable issue for the analysis of publication bias and adjustment for it is the choice of the effect size measure.
+Researchers and journal editors rely on effect sizes as mean differences or log odds ratios to assess treatment efficacy and statistical significance.
+Transformation of the effect sizes might change a significant result to non-significant or vice-versa.
+Thus transformation will lead to a loss of accuracy.
+Furthermore, transformation of mean differences to std.
+mean differences also comes with the unpleasant consequence that effect size and std.
+mean difference are no longer independent (smaller differences for large std.
+errors).
+When transforming odds ratios to std.
+mean differences, the interdependence between effect size and std.
+mean difference is also retained.\\
+Transformation to Fisher's $z$ transformed correlation will abolish this dependency, but since correlations are bounded, linear regression will no longer be suitable to detect very large effect sizes.
+Furthermore, the applied adjustment methods which are based on Fisher's $z$ transformed correlations are not adapted to correlation coefficients and sometimes provide meaningless results (coefficients $> 1$ or $< -1$).
+Thus, one transformation will tend to underestimate publication bias, while the other likely overestimates it, and both are not accurate.
 
 \section{Outlook}
-Given the size and abundance of information in the dataset, the possibilities to investigate sources of bias in the Cochrane Database of Systematic Reviews are not exhausted (see for example in \citet{ioannidis.2017}).
+Given the size and abundance of information in the dataset, the possibilities to investigate sources of bias in the Cochrane Library of Systematic Reviews are not exhausted.
 In particular, one could easily come up with more hypotheses that could be tested in meta meta-regression, as introduced in the last section of the results.
-Many researchers have come up with hypotheses about the reasons and circumstances that promote publication bias, which could be tested if the information is extended.\\
-There are numerous suggestions for different measures of publication bias and small study effects, which could be applied on the dataset (see \citet{mueller.2016}).
-This study mainly relies on suggestions from \citet{Sterne}, \citet{Ioannidis2007} and \citet{limitmeta}.
-It uses most often methods that are well integrated in packages (\citet{metafor.package}, \citet{meta.package}).
+Many researchers have come up with hypotheses about the reasons and circumstances that promote publication bias, which could be tested if the dataset is extended.\\
+There are numerous suggestions for different measures of publication bias and small study effects, which could be applied on the dataset (see \citealp{mueller.2016}).
+This study mainly relies on suggestions from \citealp{Sterne}, \citealp{Ioannidis2007} and \citealp{limitmeta}.
+It uses most often methods that are well integrated in packages (\citealp{metafor.package}, \citealp{meta.package}).
 Although there are well addressed, mathematical justifications for these methods, there might be better methods not yet tested on large datasets.
@@
 \section{Implications}
-This study is so far the largest assessment of publication bias by small study effects and uses data that has been collected after major efforts have been made to curb publication bias.
-It is the first analysis of the Cochrane Database of Systematic Reviews also analyzing publication bias using hazard and rate ratios.
-The results indicate, similarly to other studies, that the efforts did not yet resolve the issue.
+As far as we know, this study is so far the largest assessment of publication bias by small study effects and uses also data that has been collected after major efforts have been made to curb publication bias.
+%It is the first analysis of the Cochrane Library of Systematic Reviews also analyzing publication bias using hazard and rate ratios.
+Furthermore, the analysis includes time-to-event data which is, as far as we are aware of, unprecedented, and continuous outcomes, which is unusual.
+Thus we assume that it is so far the most complete, thorough analysis of publication bias in the Cochrane library.
 \\
-The findings further imply that when using meta-analyses, it is key to investigate sources of between-study heterogeneity; an alternative is to rely solely on the largest trials \citep{largest.study.only}.
-Since the Cochrane Organization uses results from grey literature to limit the effects of publication bias, but still does not manage to abolish it, there is also the need for journal editors to change their publication policies.
+We are not aware of any use of one-sided tests for publication bias as used in this study, which allows to look more specifically for publication bias for ``positive'' or desired treatment effects.
+The results indicate that the efforts to curb down publication bias are only partially successful.\\
+Also, it is the first study to extensively adjust the combined effect sizes from meta-analyses for publication bias.
+It has been found repeatedly that publication bias might threaten the validity of the findings of some meta-analyses from Cochrane systematic reviews.
+Cochrane did so far not extend their protocols to publication bias adjustment methods.\\
+Therefore, we suggest that publication bias in meta-analyses of clinical trials remains an important issue to be considered while doing meta-analyses. 
+% Since Cochrane uses results from grey literature to limit the effects of publication bias, but still does not manage to abolish it, there is also the need for journal editors to change their publication policies.

### 2019-08-15 report/MSc_Report.Rnw
Update thesis

@@
 might only be positive by chance, or because of poor study design. When decision
-makers use this information to take decisions, they are likely to be mislead. \\
+makers use this information to take actions, they are likely to be mislead. \\
 In this study, the prevalence and impact of publication bias is assessed in 
@@
 I would like to thank all members of the Department of Biostatistics for promoting me along my studies and making this thesis possible.
-Special thanks goes to Dr. Simon Schwab, for thorough support, and to Prof. Dr. Leonhard Held for advice. \\
+Special thanks goes to Dr. Simon Schwab, for thorough support, and to Prof. Dr. Leonhard Held for advice.\\
 Among my friends, I would to thank all students of biostatistics in the years 2018 and 2019 for making this time so pleasant. Samuel

### 2019-08-15 report/MSc_Report.tex
Update thesis

@@
 Results from RCTs influence the treatment of patients in daily clinical practice.
-The results from multiple intervention studies can be summarized in a meta-analysis to estimate an overall treatment effect (access all studies) \citep{Cochran}.
+The results from multiple intervention studies can be summarized in a meta-analysis to estimate an overall treatment effect (across all studies) \citep{Cochran}.
 However, publication bias can bias the overall effect estimates from meta-analyses and eventually lead to ineffective treatments that could lead to patient harm, distortion and financial expenses.
@@
 For instance, it is possible to follow studies and assess if they are getting published depending on their findings (\citealp{Dwan2013}, \citealp{publication.fate}, \citealp{Lee.2008}).
-One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in the social sciences: \citealp{social.sciences.publication.bias}).
+One often finds that positive findings (\ie large effects) are reported and published more often (see also an example in the social sciences: \citet{social.sciences.publication.bias}).
 Another way is to compare results in study registries with results published in journals (\eg \citealp{pb.clinicalscience.2013}).
@@
 A funnel plot \citep{funnel.plot} allows visual inspection of small study effects by plotting the effects against their standard error.
-For illustration purposes, one meta-analysis with large funnel plot asymmetry and one with no asymmetry is shown in Figure \ref{small.study.effect.examples }.
+For illustration purposes, one meta-analysis with large funnel plot asymmetry and one with no asymmetry is shown in Figure \ref{small.study.effect.examples}.
 %\citep{pre.eclampsia}:
-By means of simple linear regression, one can investigate how much evidence there is for this asymmetry.
+The purpose of a funnel plot is to visualize if there are missing study results on one lower side of the funnel plot.
+By means of simple linear regression, one can investigate how much evidence there is for asymmetry.
 
@@
 
-The purpose of a funnel plot is to visualize if the findings of the studies disperse on both sides of the combined ``true'' effect or if they accumulate with increasing standard error on one particular side.\\
-We see that while the studies in the meta-analysis on the left are not symmetrically distributed, but rather accumulate at the left side, they seem to be more evenly distributed in the left triangle.
+We see that while the studies in the meta-analysis on the right rather accumulate on the right side, they seem to be more evenly distributed in the right triangle.
 From this, we would ultimately conclude that some sort of bias or heterogeneity is distorting the estimate of the overall treatment effect.\\
 The Cochrane Organisation has specialized on systematic reviews of healthcare interventions.
-Researchers that write a systematic review collect data across studies, review them and try to provide up-to-date information about specific treatment efficacious \citep{cochrane.handbook}.
-By extensive literature examination, they try to circumvent the issue of publication bias.
+Researchers that write a systematic review collect data across studies, review them and try to provide up-to-date information about specific treatment efficacy \citep{cochrane.handbook}.
+By systematic literature review, they try to circumvent the issue of publication bias.
 Earlier research however suggests that the efforts are only partially successful, and that there still is publication bias within the reviews (\citealp{Egger}, \citealp{Ioannidis2007}, \citealp{kicinsky}, \citealp{vanAert.2019}).
 In these publications, Cochrane systematic reviews is analysed with methods to detect publication bias, for example small study effect tests or Bayesian hierarchical selection models \citep{kicinsky}.
-They all find moderate to large evidence for publication bias in the Database.
-Their results will be compared to the results of this study in the last chapter.\\
+They all find moderate to large evidence for publication bias in the database.\\
 
@@
 Also, the results are ironically often presented in the form of dichotomous hypothesis tests, a practice that is partly responsible for publication bias.\\
-The aim of this thesis is to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides.
-The research questions are: ``Are effects in meta-analyses \textit{larger} if their standard errors are small, and are there \textit{more} significant effects than expected?'' and ``How can this affect the combined treatment effects as commonly obtained by meta-analysis?''.
+The aim of this thesis was to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides.
+The research questions are: Are effects in meta-analyses \textit{larger} if their standard errors are small, and are there \textit{more} significant effects than expected?
+and How can this affect the combined treatment effects as commonly obtained by meta-analysis?.
 To answer these questions, methods to detect and adjust for publication bias in meta-analysis are applied on the data.\\
-At the end, it will be given an estimate of the extent of publication bias in the Cochrane Library.
-It will also be shown if and to what extent treatment effects are overestimated due to publication bias in Cochrane systematic reviews.
-Because the analysis is exploratory, the results should rather be used in a suggestive than in a confirmatory manner.
+At the end, we will not only give an estimate of publication bias in the Cochrane Library but also show to what extent treatment effects are overestimated.
+The analyses are exploratory, but may generate new hypotheses and stimulate future directions for confirmatory research.
 
@@
 \subsection{Continuous Outcomes}
-For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Cohen's $d$) and a standard error thereof.
-The mean difference $\theta$ and its standard error $\se$ can be obtained as
-
-\begin{align}
-\theta &= m_t - m_c & \se &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_t}
+For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (also known as Cohen's $d$) and the standard error thereof.
+
+\begin{align}
+\theta &= m_t - m_c & \se &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_c}
 \end{align}
@@
 \begin{align}
-\se &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}} & d &= \frac{m_t - m_c}{\se} \label{eq:hedges.g}
+d &= \frac{m_t - m_c}{\se} \label{eq:hedges.g} & \se &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}}
 \end{align}
@@
 Both estimators take into account that the two groups might have unequal variances. \\ 
-A $p$\hspace{0.4mm}-value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$ test.
+A  $p$\hspace{0.4mm}~-~value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$-test.
 The $t$ statistic is obtained, using $\se$ and $d$ from \eqref{eq:hedges.g}, by
@@
 \end{align}
-and the $p$\hspace{0.4mm}-value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
+and the  $p$\hspace{0.4mm}~-~value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
 
@@
 
-The t-test is known to be not very reliable if combined sample size is small ($n_t + n_c < 30$).
+%The $t$-test is known to be reliable if combined sample size is small ($n_t + n_c < 30$), larger.
 
@@
 \hat{\theta} &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
-\se^2&= 1/e_t - 1/n_t + 1/e_c - 1/e_t \label{eq:risk.ratio.variance}
-\end{align}
-
-Assuming binomial distribution of the events and using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$\hspace{0.4mm}-value, \eg \cite[98]{held2014}.
+\se^2&= 1/e_t - 1/n_t + 1/e_c - 1/n_c \label{eq:risk.ratio.variance}
+\end{align}
+
+Assuming binomial distribution of the events and using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a  $p$\hspace{0.4mm}~-~value, \eg \cite[98]{held2014}.
 The approximation is only good if there are enough events and sample size is large enough.\\
@@
 \end{align}
-a $p$\hspace{0.4mm}-value for the corresponding estimate, which summarizes the evidence against $\hat{\theta}$ being zero (\ie the true risk/odds ratio being 1). \\
+a  $p$\hspace{0.4mm}~-~value for the corresponding estimate, which summarizes the evidence against $\hat{\theta}$ being zero (\ie the true risk/odds ratio being 1). \\
 Odds ratios can be transformed to std. mean differences, which will be described in Section \ref{sec:transformation.effectsizes}.
@@
 \end{align}
-will give a $p$\hspace{0.4mm}-value for the evidence against the null hypothesis.
+will give a  $p$\hspace{0.4mm}~-~value for the evidence against the null hypothesis.
 
@@
 The estimation of $\tau^2$ has been subject to some debate in the statistical literature.
-Oftentimes, the method of moment estimator of \citealp{tau.estimator} is used.
+Oftentimes, the method of moment estimator of \citet{tau.estimator} is used.
 We use the measure of heterogeneity, $Q$, and divide by $C$ after having subtracted the degrees of freedom $n-1$:
@@
 Using a truncated Taylor series expansion, one can obtain the partial derivative after $\tau^2$, which is a reasonable choice for $\tau_0^2$.
-Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{theta}$, we can update $F(\tau^2)$ and check convergence to zero.
+Using $\tau^2 + \tau_0^2$ for $\hat{w}_i, \hat{\theta}$, we can update $F(\tau^2)$ and check convergence to zero.
 \\
 The estimation of $\tau^2$ is accompanied by uncertainty.
-A common procedure is to test if it is there is significant heterogeneity between the studies \cite[109]{Intro.meta}.
+A common procedure is to test if it is there is significant heterogeneity between the studies \cite[p.
+109]{Intro.meta}.
 For this, $Q$ has to be computed as given in \eqref{eq:Q.heterogeneity}.
@@
 Thus, the expected value of $Q$ is $n-1$, and the excess dispersion is $Q - n + 1$.
-The $p$\hspace{0.4mm}-value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
+The  $p$\hspace{0.4mm}~-~value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
 = $n-1$.
@@
 
-The statistic takes value between zero and one, and is easily interpretable.
+The statistic takes values between zero and one, and is easily interpretable.
 0 is equal to 0\% excess dispersion and \eg 0.5 equal to 50\% additional between-study variance of the total variance of the estimates.
@@
 
-where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. The $p$\hspace{0.4mm}-value will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
+where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. The  $p$\hspace{0.4mm}~-~value will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
 The concept is extendable to weighted linear regression.
@@
 The tests that will be presented on the following pages are a common way to detect publication bias.
-A frequently to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill} is not discussed because of its disadvantageous properties, therefore, it will not be discussed here (see \eg \citealp{Moreno.2009}).\\
+A frequently used method to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill} is not discussed because of its disadvantageous properties (see \eg \citealp{Moreno.2009}).\\
 
@@
 \theta_i^\star &= (\theta_i - \theta_M)/\se_i^{2\star} \label{eq:begg.stand.eff}  \\
-\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2}1 \label{eq:begg.stand.var} 
+\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2} \label{eq:begg.stand.var} 
 \end{align}
@@
 Thus, large number of concordant pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$.
-A two-sided $p$\hspace{0.4mm}-value is obtained using the standard normal distribution $\Phi$:
+A two-sided  $p$\hspace{0.4mm}~-~value is obtained using the standard normal distribution $\Phi$:
 \begin{align}
@@
 A one-sided test for positive correlation is obtained by computing $1-\Phi(Z)$ instead.
-The changes that have to be made int the case of ties are small and can be found in \cite[410]{begg.ties}.
+The changes that have to be made in the case of ties are small and can be found in \cite[p. 410]{begg.ties}.
 
 \subsection{Egger's Test: Weighted Linear Regression Test} \label{sec:Egger}
-Linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citealp{Egger}.
+Linear regression can be used to test dependency of effect sizes on study sizes. The simplest application was introduced by \citet{Egger}.
 Let $\theta/\se$ be the dependent variable $y$ and $1/\se$ the explanatory variable $x$.
@@
 \begin{align}
-\theta/s &= \beta_0 + \beta_1/\se + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:radial.plot} 
+\theta/\se &= \beta_0 + \beta_1/\se + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:radial.plot} 
 \end{align}
@@
 Thus testing $\beta_0$ of \eqref{eq:radial.plot} or $\beta_1$ of \eqref{eq:egger.plot} is equivalent.
-The corresponding $p$\hspace{0.4mm}-value is then used as evidence for a small study effect.
+The corresponding  $p$\hspace{0.4mm}~-~value is then used as evidence for a small study effect.
 Plugging in  $\theta_i/\se_i, 1/\se_i$ as $y_i, x_i$ into equations \eqref{eq:regression.parameters} and \eqref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{\se}_{\beta_0}$ and $\hat{\se}_{\beta_1}$.
@@
 \subsection{Thompson and Sharp's Test: Weighted Linear Regression Random Effects Test} \label{sec:Thompson}
-A method proposed in \citealp{thompson.sharp} allows for between study variance $\tau^2$, as introduced before in section \ref{sec:meta.analysis}.
+A method proposed in \citet{thompson.sharp} allows for between study variance $\tau^2$, as introduced before in section \ref{sec:meta.analysis}.
 It extends the previously seen linear regression approach with $x = 1/\se$ and $y = \theta/\se$ by introducing new weights.
@@
 After adjusting for the weights as described in \ref{weighted.regression}, we can proceed analogous to Egger's test.
-The $p$\hspace{0.4mm}-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
+The  $p$\hspace{0.4mm}~-~value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
 
 \subsection{Peters Test: Weighted Linear Regression Test} \label{sec:Peter}
-When the outcome is dichotomous, effect sizes and variances of effect size are correlated, which can readily be seen in \eqref{eq:risk.ratio} and \eqref{eq:risk.ratio.variance} (see also \cite[120]{meta.w.R}).
+When the outcome is dichotomous, effect sizes and variances of effect size are correlated, which can readily be seen in \eqref{eq:risk.ratio} and \eqref{eq:risk.ratio.variance} (see also \cite[p.
+120]{meta.w.R}).
 A small number of event counts in one or group will inflate the variance and the effect size.
@@
 A rank based alternative to Peters test for binary outcomes is Harbord's test \citep{Harbord}.
-It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated at log odds ratio $\theta_\textrm{H0} = 0$ and its inverse Fisher information $s^2$.
+It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated as log odds ratio $\theta_\textrm{H0} = 0$ and its inverse Fisher information $s^2$.
 Formally,
@@
 \citealp{Schwarzer} developed a test for the correlation between the event counts in the treatment group and the expected event counts $E_t - \mathbb{E}(E_t)$.
-When the marginals in a two-by-two table and the log odds ratio is fixed, it can be shown that $E_t$ follows a non-central hypergeometric distribution.
+When the marginals in a two-by-two table and the log odds ratio are fixed, it can be shown that $E_t$ follows a non-central hypergeometric distribution.
 Using the Mantel-Haenszel log odds ratio and the marginal total parameters, the variance and the expectation of $E_t$ is calculated.
@@
 %Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study. \\
-We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated by fixed effects Meta-Analysis \eqref{eq:fixed.effects}.
+We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated by fixed effects meta-Analysis \eqref{eq:fixed.effects}.
 Let $O$ be the number of significant study results out of $n$ studies and $\alpha$ the significance threshold.
@@
 
-and consecutively, calculating a $p$\hspace{0.4mm}-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
+and consecutively, calculating a $p$\hspace{0.4mm}~-~value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
 Alternatively, one can also use a binomial test, which is encouraged when $n$ and $O$ is small.
-We will get a one sided $p$\hspace{0.4mm}-value for excess significance, $\P(X \geq O)$, by computing
+We will get a one sided $p$\hspace{0.4mm}~-value for excess significance, $\P(X \geq O)$, by computing
 
@@
 \subsection{Adjustment by Regression} \label{sec:regression.adjustment}
-In \citealp{limitmeta.2} and \citealp{limitmeta}, a random effects model is proposed to obtain unbiased treatment effect estimates. Similarly to regression based tests for small study effects, we have
+In \citet{limitmeta.2} and \citet{limitmeta}, a random effects model is proposed to obtain unbiased treatment effect estimates. Similarly to regression based tests for small study effects, we have
 
@@
 \theta_i & = \beta_0 + \beta_1\sqrt{\se_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \label{eq:limitmeta.regression} \\
-\epsilon_i \stackrel{\textrm{iid}}{\sim} N(0,1)
+\epsilon_i &\stackrel{\textrm{iid}}{\sim} N(0,1)
 \end{align}
@@
 \begin{align}
-\mathbb{E}((\theta_i - \beta_0)/\sqrt{\se_i^2}) \rightarrow \beta_1 \textrm{ if } \se_i \rightarrow \infty \nonumber \\ %\label{limitmeta.infinitesample} \\
-\mathbb{E}(theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} \se_i \rightarrow 0 \nonumber
+\mathbb{E}\big((\theta_i - \beta_0)/\sqrt{\se_i^2}\big) \rightarrow \beta_1 \textrm{ if } \se_i \rightarrow \infty \nonumber \\ %\label{limitmeta.infinitesample} \\
+\mathbb{E}(\theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} \se_i \rightarrow 0 \nonumber
 \end{align}
@@
 
-Simulations in \citealp{limitmeta} suggested that the latter estimate is slightly superior to the former, because it showed a smaller mean-squared error in simulation studies \citealp{limitmeta.2}.
+Simulations in \citet{limitmeta} suggested that the latter estimate is slightly superior to the former, because it showed a smaller mean-squared error in simulation studies \citet{limitmeta.2}.
 From the formulas above, it becomes clear that is has a larger standard error.
@@
 
-$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$\hspace{0.4mm}-value.
+$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$\hspace{0.4mm}~-~value.
 Note that the test is very similar to Egger's small study effect test when $\tau^2 = 0$.\\
 In practice one can observe how $\theta$ and it's confidence intervals change dependent on the underlying selection process, and how the choice of the parameters affect the evidence for remaining publication bias (selection).
-\citealp{limitmeta} used the method in a simulation for inference purposes, and have implemented it in the \citealp{meta.package}.
+\citet{limitmeta} used the method in a simulation for inference purposes, and have implemented it in the \citet{meta.package}.
 However, in the simulations, the method was outperformed by the regression adjustment method when publication bias was present.
@@
 Other authors argue that selection models should in general not be used for inference (\eg \citealp{selection.assessment}).\\
-The procedure in \citealp{limitmeta} is the following: A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \eqref{eq:copas.small.study} is applied.
-If all obtained $p$\hspace{0.4mm}-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for adjustment, and the standard, classical random effects meta-analysis is retained.
-If none of the $p$\hspace{0.4mm}-values is above the threshold, a wider range of values for $(a,b)$ is used.
-When some $p$\hspace{0.4mm}-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the pair of $a$ and $b$ that implies the fewest publication bias is chosen).\\
+The procedure in \citet{limitmeta} is the following: A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \eqref{eq:copas.small.study} is applied.
+If all obtained  $p$\hspace{0.4mm}~-~values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for adjustment, and the standard, classical random effects meta-analysis is retained.
+If none of the  $p$\hspace{0.4mm}~-~values is above the threshold, a wider range of values for $(a,b)$ is used.
+When some  $p$\hspace{0.4mm}~-~values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the pair of $a$ and $b$ that implies the fewest publication bias is chosen).\\
 Currently, there is no test to detect miss-specifications in the model itself and the authors themselves have argued that a non-parametric test of the residuals would lack power.
@@
 The factor $\frac{\pi}{\sqrt{3}} = 1.81$ is the standard deviation of the logistic distribution $L(\mu, \eta)$ with scale parameter $\eta = 1$, so we just divide the log odds ratio and it's variance through the standard deviation.
-The approximation works only well if $e_t$ and $e_c$ are not very small, especially in the case of $s_d^2$.
+The approximation works only well if $e_t$ and $e_c$ are not very small, especially in the case of $\se_d^2$.
 \\
@@
 
-Finally, we can get to a fisher's z-scaled correlation $z$ and it's variance $\se_z^2$ by using
+Finally, we can get to a fisher's z-transformed correlation $z$ and it's variance $\se_z^2$ by using
 \begin{align}
@@
 z &= \arctan(r) & \nonumber
-s_z^2 &= \frac{1}{n-3}
+\se_z^2 &= \frac{1}{n-3}
 \end{align}
@@
 Cochrane has specialized on systematic reviews in clinical science.
-Certain knowledge of standards and principles of the organization may help to assess the quality and the properties of the dataset.
+Certain knowledge of standards and principles of the organization may help to understand the dataset.
 The following information stems from the Cochrane Handbook for Systematic Reviews \citep{cochrane.handbook}.
@@
 ``As of January 2008 (Issue 1, 2008), CENTRAL contains nearly 530,000 citations to reports of trials and other studies potentially eligible for inclusion in Cochrane reviews, of which 310,000 trial reports are from MEDLINE, 50,000 additional trial reports are from EMBASE and the remaining 170,000 are from other sources such as other databases and handsearching.'' It includes citations published in many languages, citations only available in conference proceedings, citations from trials registers and trials results registers.
-\item MEDLINE.
-MEDLINE includes over 16 million references to journal articles.
+\item MEDLINE includes over 16 million references to journal articles.
 5,200 journals publishing in 27 languages are indexed for MEDLINE.
@@
 \item EMBASE.
-4,800 Journals publishing in 30 languages are indexed to EMBASE, which includes more than 11 million records from 1974 onward.
+4,800 journals publishing in 30 languages are indexed in EMBASE, which includes more than 11 million records from 1974 onward.
 EMBASE.com also includes 7 million unique records from MEDLINE (1966 up to date) together with its own records.
 Additionally, EMBASE Classic allows access to digitized records from 1947 to 1973.
-EMBASE and MEDLINE each have around 1,800 journals not indexed in the other database.
+EMBASE and MEDLINE each have around 1,800 journals not indexed in any other database.
 \item Regional or national and subject specific databases can additionally be consulted and often provide important information. Financial considerations may limit the use of such databases.
@@
 \item Citation Indexes.
-The database lists articles published in around 6,000 Journals with articles in which they have been cited and is available online as SciSearch.
+The database lists articles published in around 6,000 journals with articles in which they have been cited and is available online as SciSearch.
 This form of search is known as cited reference searching.
@@
 Approximately 10\% of the results in the Cochrane Library stems from conference abstracts and other grey literature.
-The Institute for Scientific and Technical Information in France provides access to entries of the previously closed System for Information on Grey Literature database of the European Association for Grey Literature Exploitation).
+The Institute for Scientific and Technical Information in France provides access to entries of the previously closed System for Information on Grey Literature database of the European Association for Grey Literature Exploitation.
 Another source is the Healthcare Management Information Consortium (HMIC) database containing records from the Library and Information Services department of the Department of Health (DH) in England and the King's Fund Information and Library Service.
@@
 \section{Structure and Variables}
-The dataset consists of 6354 systematic reviews from the Cochrane Library with 70662 studies and 744720 results.
-A result is a outcome of a study, thus studies can contribute multiple results.
+The dataset consists of 6,354 systematic reviews from the Cochrane Library with 70,662 studies and 744,720 results.
+A result of a study can be a primary or secondary or safety outcome, thus studies can contribute multiple results.
 The studies too a very large extent randomized and investigate the effects of healthcare and medical interventions and treatments.
@@
 \\
-The \texttt{comparison.name} variable specifies \textit{what kind} of treatments or interventions are compared, the \texttt{outcome.name} variable \textit{how} it is compared, and the \texttt{subgroup.name} variable (not indicated in table) \textit{if and to what experimental subgroup} the result belongs.
+The \texttt{comparison.name} variable specifies \textit{what kind} of treatments or interventions are compared, the \texttt{outcome.name} variable \textit{how} it is compared, and the \texttt{subgroup.name} variable (not indicated in table) if and to \textit{what experimental subgroup} the result belongs to.
 \\
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 14 09:50:11 2019
+% Thu Aug 15 21:26:39 2019
 \begin{table}[ht]
@@
 \endgroup
-\caption{Example of two results as given in the dataset.
+\caption{Example of results from two primary studies that belong to the same comparison and outcome.
 Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
@@
 
-Results are part of studies that are again part of a (systematic) review. This structure of a review is shown in Figure \ref{review.structure}.
+Results are part of studies that are again part of a (systematic) review. The general structure of a review is shown in Figure \ref{review.structure}.
 
@@
 \end{tikzpicture}
-\caption{Structure of a hypothetical review with two different comparisons}
+\caption{General structure of the database. Results from primary studies belong to the same comparison, outcome and subgroups, and can be used to estimate a combined effect in a meta-analysis.}
 \label{review.structure}
@@
       \texttt{subgroup.id} & Specification of the comparison by a string of the type \\ &``CMP-xxx.yy.xx'' for the xx. subgroup for the yy. outcome \\ & of the xxx. comparison within the review.\\
-      \texttt{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
-      \texttt{outcome.measure.merged} & Indication of the quantification method of the effect, \\ &merged such that each method is uniquely classified.\\
+      \texttt{outcome.measure} & Outcome measure, \eg risk ratio.\\
+      \texttt{outcome.measure.merged} & Outcome measure, \eg risk ratio, merged such that each method is uniquely classified.\\
       \texttt{outcome.flag} & A outcome flag to simplify programming; \\ &\texttt{DICH} for binary outcomes with fully available information \\ &on event counts,
@@
 \\ &\texttt{IPD} for individual patient data.\\
-      \texttt{effect} & Measure of the effect given in the quantity denoted by \\ &\texttt{outcome measure}.\\
+      \texttt{effect} & Magnitude of the effect given in the quantity denoted by \\ &\texttt{outcome measure}.\\
       \texttt{se} & Standard error of the measure of the effect.\\
@@
       \texttt{mean1/mean2} & Mean of patient measurements if outcome is continuous.\\
-      \texttt{sd1/sd2} & Standard deviation of mean if outcome is continuous.
+      \texttt{sd1/sd2} & Standard deviation if outcome is continuous.
     \end{tabular}
@@
   Zero participants in one group & 15162 \\ 
-  Missing study publication year & 7942 \\ 
+  Missing study publication year & 7834 \\ 
    \hline
@@
 
-The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982, 95\% quantile = 2014,).
-The median of the publication years is 2003, the mean 2000.97 and the quartiles are 1996 and 2008.
-1075 studies have been published in 2018, none in 2019.\\
-The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}.
+The primary studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982, 95\% quantile = 2014,).
+The median of the publication years is 2003, the mean 2001 and the quartiles are 1996 and 2008.
+1,075 studies have been published in 2018.\\
+The most frequent outcome measures are summarized in Table \ref{outcome.measure.frequencies}.
 One can conclude of the table that roughly 31 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (more than 65\%).
@@
 \endgroup
-\caption{Frequencies of outcome measures among results. n denotes the total number 
-             of results with the outcome measure and percentage the percentage of the outcome measure,} 
+\caption{Frequencies of outcome measures among results.} 
 \label{outcome.measure.frequencies}
@@
 There are 5\% of treatment group sample sizes that are smaller than 9, 95\% smaller than 510.
-The first quartile is 23, the median 48, the mean 256.71 and the third quartile 116.
+The first quartile is 23, the median 48, the mean 257 and the third quartile 116.
 The large difference between median and mean is caused by very large groups with over 2,000,000 participants.
 Analogously, the quantiles of the total sample size are: 5\% quantile = 17, first quartile = 44, median = 94, third quartile = 223 and 95\% = 983.
-The mean is 623.15.
+The mean is 623.
 \\
@@
 The mean and median number of results per review are 13.6 and 8, and the quartiles are 16 and 109.
-Similarly, the number of reviews with a maximum of two studies included is 1040, the mean study number is 13.6, the median 8 and the interquartile range 4 and 16 and the 95\% quantile 45.
+Similarly, the number of reviews with a maximum of two studies included is 1,040, the mean study number is 13.6, the median 8 and the interquartile range 4 and 16 and the 95\% quantile 45.
 The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citealp{largest.review}
@@
 
-Initially, the analysis is restricted to results with \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}.
-If \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR} / \texttt{RR} / \texttt{SMD} / \texttt{MD} / \texttt{Hazard Ratio} / \texttt{Rate Ratio} are used.
+The analysis includes all results with \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}.
+If outcome is \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR} / \texttt{RR} / \texttt{SMD} / \texttt{MD} / \texttt{Hazard Ratio} / \texttt{Rate Ratio} are used.
 \citealp{Ioannidis2007} outlined criteria for application of small study effect tests:
 \begin{itemize}
-\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = 9772 remaining). 
-\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 9473 remaining).
-\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 7452 remaining)
-\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 1388 remaining).
+\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = 9,772 remaining). 
+\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = 9,473 remaining).
+\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = 7,452 remaining)
+\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = 1,388 remaining).
 \end{itemize}
@@
 \item \textbf{No withdrawn reviews}: Reviews that have been withdrawn are not included.
-\item \textbf{No adverse effects}: No results of adverse effects of treatment are used for meta-analyses.
-Exclusion is incomplete because only results with ``adverse'' in the comparison or outcome name could be removed, but not all adverse effect results are classified as such.
+\item \textbf{No adverse effects}: No results of adverse effects of treatment are used for meta-analyses.we could thus clearly identify many safety results but this may be incomplete when safety outcomes are insufficiently declared, for example ``headache''.
 \end{itemize}
@@
     % Draw edges
-    \path [line] (1) -- node [btw, xshift = -1.95cm] {no withdrawn reviews} (12);
+    \path [line] (1) -- node [btw, xshift = -2.3cm] {exclusion of withdrawn reviews} (12);
     \path [line] (12) -- node [btw, xshift = -2.1cm] {only efficacy outcomes} (13);
@@
 \subsubsection{The Analysis Dataset}
-The dataset that was ultimately tested and adjusted for publication bias comprises 1388 meta-analyses and 22,937 results.
-The mean number of participants in the treatment group is 253.5 vs 256.7 in the unrestricted dataset and the mean total number of participants 589.3 vs 623.2.
-The mean publication year is 2000 vs 2001 in the unrestricted dataset.
+The dataset that was ultimately tested and adjusted for publication bias comprises 1,388 meta-analyses and 22,937 results.
+The mean number of participants in the treatment group is 253.5 vs 256.7 in the complete dataset and the mean total number of participants 589.3 vs 623.2.
+The mean publication year is 2000 vs 2001 in the complete dataset.
 \\
@@
 \subsection{Analysis Procedure} \label{sec:procedure}
-Meta-analysis groups within a review were obtained by grouping by comparison, outcome and subgroup.
+Meta-analysis within a review were obtained by grouping by comparison, outcome and subgroup.
 The last step is optional, and the Cochrane Groups do also meta-analysis without taking into account subgroups.
@@
 \\
-Details to Copas selection model algorithm and its application can be found in \citealp{limitmeta}.
+Details to Copas selection model algorithm and its application can be found in \citet{limitmeta}.
 In short, two values for $a$ and $b$ in section \ref{sec:copas} were used; a limited range with $a$ between -1.7 and 2, and $b$ between 0.16 and 0.32 was applied first (analog to a most extreme selection process of $P$(select|small trial with sd = 0.4) = 0.1 and P(select|large trial w.
@@
 The \texttt{R} packages \texttt{meta} \citep{meta.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments.
-The excess significance test was adapted from \citealp{vanAert.2019}.
+The excess significance test was adapted from \citet{vanAert.2019}.
 For data manipulation procedures, the \texttt{tidyverse} packages were used \citep{tidyverse.package}, and for plotting the \texttt{ggplot2} package \citep{ggplot2}.\\
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 14 15:13:27 2019
+% Thu Aug 15 22:03:09 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 14 15:13:41 2019
+% Thu Aug 15 22:03:23 2019
 \begin{table}[ht]
@@
 There, less of an effect of adjustment on the evidence can be seen.
-The adjustment is more likely to be more reliable than the unadjusted estimate when publication bias is strong (see \ref{ch:Methods}).
+The adjustment is more likely to be more reliable than the unadjusted estimate when publication bias is strong (see \ref{ch:methods}).
 The dots with darker color are thus more likely to provide less biased estimates.\\
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 14 15:13:43 2019
+% Thu Aug 15 22:03:25 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 14 15:13:52 2019
+% Thu Aug 15 22:03:33 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 14 15:13:52 2019
+% Thu Aug 15 22:03:34 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 14 15:13:54 2019
+% Thu Aug 15 22:03:35 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 14 15:13:56 2019
+% Thu Aug 15 22:03:37 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 14 15:13:59 2019
+% Thu Aug 15 22:03:41 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 14 15:14:01 2019
+% Thu Aug 15 22:03:42 2019
 \begin{table}[ht]
@@
 Publication bias can also be present if a meta-analysis lacks a small study effect, for example if significant results are published irrespective of the sign of the effect estimate.
-Methods as the excess significance test of \citealp{excess.significance} are applied to overcome this issue, but the method is known to lack power.
+Methods as the excess significance test of \citet{excess.significance} are applied to overcome this issue, but the method is known to lack power.
 No methods exist so far to adjust for excess significance.
@@
 % Therefore, the results are not exact and could be improved if more suitable methods are applied.
-The Bayesian approach taken by \citealp{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions.
+The Bayesian approach taken by \citet{kicinsky} has many advantages over the applied methods, \eg by accounting for statistical significance, but relies on assumptions over the weight function and is at least somewhat sensible on the choice of the prior distributions.
 \\
@@
 This is an issue, because it is not well known if and how the publication probability is affected by the size of safety outcomes.
-\citealp{kicinsky} suggests that they may inversely affect publication (\ie non-significant effects are preferred).\\
+\citet{kicinsky} suggests that they may inversely affect publication (\ie non-significant effects are preferred).\\
 % Also, it has been previously discussed that the method to detect the side on which bias is not working perfectly.
@@
 There are numerous suggestions for different measures of publication bias and small study effects, which could be applied on the dataset (see \citealp{mueller.2016}).
-This study mainly relies on suggestions from \citealp{Sterne}, \citealp{Ioannidis2007} and \citealp{limitmeta}.
+This study mainly relies on suggestions from \citet{Sterne}, \citet{Ioannidis2007} and \citet{limitmeta}.
 It uses most often methods that are well integrated in packages (\citealp{metafor.package}, \citealp{meta.package}).
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 14 15:14:39 2019
+% Thu Aug 15 22:04:20 2019
 \begin{table}[ht]

### 2019-08-15 report/chapter01.Rnw
Update thesis

@@
 Also, the results are ironically often presented in the form of dichotomous hypothesis tests, a practice that is partly responsible for publication bias.\\
-The aim of this thesis is to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides.
-The research questions are: ``Are effects in meta-analyses \textit{larger} if their standard errors are small, and are there \textit{more} significant effects than expected?'' and ``How can this affect the combined treatment effects as commonly obtained by meta-analysis?''.
+The aim of this thesis was to use prevailed methods to detect publication bias, and make use of the full amount of data that the Cochrane Organisation provides.
+The research questions are: Are effects in meta-analyses \textit{larger} if their standard errors are small, and are there \textit{more} significant effects than expected?
+and How can this affect the combined treatment effects as commonly obtained by meta-analysis?.
 To answer these questions, methods to detect and adjust for publication bias in meta-analysis are applied on the data.\\
-At the end, it will be given an estimate of the extent of publication bias in the Cochrane Library.
-It will also be shown if and to what extent treatment effects are overestimated due to publication bias in Cochrane systematic reviews.
-Because the analysis is exploratory, the results should rather be used in a suggestive than in a confirmatory manner.
+At the end, we will not only give an estimate of publication bias in the Cochrane Library but also show to what extent treatment effects are overestimated.
+The analyses are exploratory, but may generate new hypotheses and stimulate future directions for confirmatory research.

### 2019-08-15 report/chapter02.Rnw
Update thesis

@@
 \subsection{Continuous Outcomes}
-For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (here: Cohen's $d$) and a standard error thereof.
-The mean difference $\theta$ and its standard error $\se$ can be obtained as
+For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (also known as Cohen's $d$) and the standard error thereof.
 
 \begin{align}
-\theta &= m_t - m_c & \se &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_t}
+\theta &= m_t - m_c & \se &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_c}
 \end{align}
@@
 \hat{\theta} &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
-\se^2&= 1/e_t - 1/n_t + 1/e_c - 1/e_t \label{eq:risk.ratio.variance}
+\se^2&= 1/e_t - 1/n_t + 1/e_c - 1/n_c \label{eq:risk.ratio.variance}
 \end{align}
 
-Assuming binomial distribution of the events and using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a $p$\hspace{0.4mm}-value, \eg \cite[98]{held2014}.
+Assuming binomial distribution of the events and using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a  $p$\hspace{0.4mm}~-~value, \eg \cite[98]{held2014}.
 The approximation is only good if there are enough events and sample size is large enough.\\

### 2019-08-15 report/chapter03.Rnw
Update thesis

@@
 
-missing.year.count <- sum(is.na(data$study.year)) + length(c(which(data$study.year < 1920), which(data$study.year > 2019)))
+missing.year.count <- sum(is.na(data$study.year)) #+ length(c(which(data$study.year < 1920), which(data$study.year > 2019)))
 
@@
 \section{Structure and Variables}
-The dataset consists of \Sexpr{length(unique(data$id))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(data$study.name))} studies and \Sexpr{dim(data)[1]} results.
-A result is a outcome of a study, thus studies can contribute multiple results.
+The dataset consists of \Sexpr{format(length(unique(data$id)), big.mark = ",")} systematic reviews from the Cochrane Library with \Sexpr{format(length(unique(data$study.name)), big.mark = ",")} studies and \Sexpr{format(dim(data)[1], big.mark = ",")} results.
+A result of a study can be a primary or secondary or safety outcome, thus studies can contribute multiple results.
 The studies too a very large extent randomized and investigate the effects of healthcare and medical interventions and treatments.
@@
 print(xtable(barbi1, label = "barbiturate.row", digits = 0,
-             caption = "Example of two results as given in the dataset.
+             caption = "Example of results from two primary studies that belong to the same comparison and outcome.
 Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
@@
 
-The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = \Sexpr{publication.year.range[1]}, 95\% quantile = \Sexpr{publication.year.range[6]},).
-The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{publication.year.range[5]} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}.
-\Sexpr{publication.year.2018} studies have been published in 2018, none in 2019.\\
-The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}.
+The primary studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = \Sexpr{publication.year.range[1]}, 95\% quantile = \Sexpr{publication.year.range[6]},).
+The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{round(publication.year.range[5])} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}.
+\Sexpr{format(publication.year.2018$n, big.mark = ",")} studies have been published in 2018.\\
+The most frequent outcome measures are summarized in Table \ref{outcome.measure.frequencies}.
 One can conclude of the table that roughly 31 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (more than 65\%).
@@
 print(xtable(outcome.measure.frequencies, label = "outcome.measure.frequencies", 
-             caption = "Frequencies of outcome measures among results. n denotes the total number 
-             of results with the outcome measure and percentage the percentage of the outcome measure,", 
+             caption = "Frequencies of outcome measures among results.", 
              align = "llrr", digits = 1), include.rownames = F, size = "footnotesize")
@@
 There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, 95\% smaller than \Sexpr{treatment.group.size.range[6]}.
-The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{treatment.group.size.range[5]} and the third quartile \Sexpr{treatment.group.size.range[4]}.
+The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{round(treatment.group.size.range[5])} and the third quartile \Sexpr{treatment.group.size.range[4]}.
 The large difference between median and mean is caused by very large groups with over 2,000,000 participants.
 Analogously, the quantiles of the total sample size are: 5\% quantile = \Sexpr{samplesize.range[1]}, first quartile = \Sexpr{samplesize.range[2]}, median = \Sexpr{samplesize.range[3]}, third quartile = \Sexpr{samplesize.range[4]} and 95\% = \Sexpr{samplesize.range[6]}.
-The mean is \Sexpr{samplesize.range[5]}.
+The mean is \Sexpr{round(samplesize.range[5])}.
 \\
@@
 The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}.
-Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]} and the 95\% quantile \Sexpr{study.range[6]}.
+Similarly, the number of reviews with a maximum of two studies included is \Sexpr{format(study.range[1], big.mark = ",")}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]} and the 95\% quantile \Sexpr{study.range[6]}.
 The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citealp{largest.review}
@@
 
-Initially, the analysis is restricted to results with \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}.
-If \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR} / \texttt{RR} / \texttt{SMD} / \texttt{MD} / \texttt{Hazard Ratio} / \texttt{Rate Ratio} are used.
+The analysis includes all results with \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}.
+If outcome is \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR} / \texttt{RR} / \texttt{SMD} / \texttt{MD} / \texttt{Hazard Ratio} / \texttt{Rate Ratio} are used.
 \citealp{Ioannidis2007} outlined criteria for application of small study effect tests:
 \begin{itemize}
-\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = \Sexpr{m.a.largerten.count} remaining). 
-\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = \Sexpr{m.a.variance4.count} remaining).
-\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = \Sexpr{m.a.one.sig.count} remaining)
-\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = \Sexpr{m.a.smaller.5.count} remaining).
+\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = \Sexpr{format(m.a.largerten.count, big.mark = ",")} remaining). 
+\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = \Sexpr{format(m.a.variance4.count, big.mark = ",")} remaining).
+\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = \Sexpr{format(m.a.one.sig.count, big.mark = ",")} remaining)
+\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = \Sexpr{format(m.a.smaller.5.count, big.mark = ",")} remaining).
 \end{itemize}
@@
 \subsubsection{The Analysis Dataset}
-The dataset that was ultimately tested and adjusted for publication bias comprises \Sexpr{dim(meta.f)[1]} meta-analyses and \Sexpr{format(dim(meta.data)[1], big.mark = ",")} results.
-The mean number of participants in the treatment group is \Sexpr{round(mean(meta.data$total1, na.rm = T),1)} vs \Sexpr{round(mean(data.ext2$total1, na.rm = T),1)} in the unrestricted dataset and the mean total number of participants \Sexpr{round(mean(meta.data$total1 + meta.data$total2),1)} vs \Sexpr{round(mean(data.ext2$total1 + data.ext2$total2),1)}.
-The mean publication year is \Sexpr{round(mean(meta.data$study.year, na.rm = TRUE))} vs \Sexpr{round(mean(data.ext2$study.year, na.rm = TRUE))} in the unrestricted dataset.
+The dataset that was ultimately tested and adjusted for publication bias comprises \Sexpr{format(dim(meta.f)[1], big.mark = ",")} meta-analyses and \Sexpr{format(dim(meta.data)[1], big.mark = ",")} results.
+The mean number of participants in the treatment group is \Sexpr{round(mean(meta.data$total1, na.rm = T),1)} vs \Sexpr{round(mean(data.ext2$total1, na.rm = T),1)} in the complete dataset and the mean total number of participants \Sexpr{round(mean(meta.data$total1 + meta.data$total2),1)} vs \Sexpr{round(mean(data.ext2$total1 + data.ext2$total2),1)}.
+The mean publication year is \Sexpr{round(mean(meta.data$study.year, na.rm = TRUE))} vs \Sexpr{round(mean(data.ext2$study.year, na.rm = TRUE))} in the complete dataset.
 \\

### 2019-08-15 code/Poster Plots.R

@@ -8,9 +8,9 @@ meta.f <- meta.f %>% mutate(pval.se1 = case_when(outcome.flag == "DICH" ~ pval.h
 method.names <- c(z.reg = "regression", z.copas = "selection model")
 
 p <- meta.f %>% filter(outcome.flag != "IV") %>% 
-  select(pval.se1, z.fixef, z.ranef, z.reg, z.copas) %>% 
+  select(pval.se, z.fixef, z.ranef, z.reg, z.copas) %>% 
   gather(key = "method", value = "test.stat", z.reg:z.copas) %>%
-  ggplot(aes(x = test.stat, y = z.fixef, colour = pval.se1)) + 
+  ggplot(aes(x = test.stat, y = z.fixef, colour = pval.se)) + 
   facet_wrap(~ method, labeller = as_labeller(method.names)) + 
   scale_color_gradient2(midpoint=mid, low="firebrick4", mid = "gold",
                         high="chartreuse2", space ="Lab") +
@@ -18,8 +18,8 @@ p <- meta.f %>% filter(outcome.flag != "IV") %>%
   geom_abline(slope = 1, intercept = 0, linetype = 2, size = .3) +
   xlab("adjusted test statistic") + ylab("fixed effects test statistic")
 
-p <- meta.f %>% filter(outcome.flag != "IV") %>% 
-  select(pval.se1, z.fixef, z.ranef, z.reg, z.copas) %>% 
+meta.f %>% filter(outcome.flag != "IV") %>% 
+  select(pval.se, z.fixef, z.ranef, z.reg, z.copas) %>% 
   gather(key = "method", value = "test.stat", z.reg:z.copas) %>%
   ggplot(aes(x = test.stat, y = z.ranef#, colour = pval.se1
              )) + 
@@ -71,6 +71,7 @@ p.s <- meta.f %>% filter(outcome.flag != "IV") %>%
              )) + geom_histogram(binwidth = 0.1, center = 0) +
   theme_bw() + #guides(fill=guide_legend(title="test stat.")) + 
   ggtitle("Selection model") +
+  xlim(c(-0.7, 1)) +
   theme(legend.position = "none",
         axis.title=element_text(size=20), 
         axis.title.y = element_text(size=40, margin = margin(r = 20)), 
@@ -90,7 +91,7 @@ p.s <- meta.f %>% filter(outcome.flag != "IV") %>%
         axis.line = element_line(size = 1, linetype = "solid"),
         panel.border = element_blank()) +
[…]

### 2019-08-20 report/MSc_Report.Rnw
final draft

@@
 of publication bias. We also adjust the treatment effects from the meta-analysis for publication bias 
-and compare the newly obtained effects with unadjusted treatment effects. In a exploratory analysis, we find
+and compare the newly obtained effects with unadjusted treatment effects. In an exploratory analysis, we find
 that around 20\% of meta-analyses are subject to publication bias, and that the
@@
 Among my friends, I would to thank all students of biostatistics in the years 2018 and 2019 for making this time so pleasant. Samuel
-Pawel was a very good friend with lots of advice and understanding throughout this time, and it was for Eleftheria Michalopoulou 
+Pawel was a very good friend with lots of advice and understanding throughout, and it was for Eleftheria Michalopoulou 
 that writing this thesis was also fun.\\
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2019-08-20 report/MSc_Report.tex
final draft

@@
 Publication bias has been identified as one of the major concerns in irreproducible research \citep{Bishop.2019}.
-The issue has been discussed in clinical science by many researchers (\citealp{pb.clinicalscience1}, \citealp{sterne2001}, \citealp{Dwan2013}).
+The issue has been discussed in clinical science by many researchers (\citealp{pb.clinicalscience1}, \citealp{Sterne}, \citealp{Dwan2013}).
 Consensus is that publication bias exists in clinical science.
@@
 \subsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
-\citealp{begg.ties} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+\citealp{Begg} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
 A standardized effect size $\theta_i^\star$ can be computed as in \eqref{eq:begg.stand.eff}.
@@
 
-Finally, we can get to a fisher's z-transformed correlation $z$ and it's variance $\se_z^2$ by using
-\begin{align}
-% z &= 0.5 \ln\big(\frac{1 + r}{1 - r}\big) & \nonumber
-z &= \arctan(r) & \nonumber
+Because $r$ and $\se_r$ are not independent, we can apply a variance stabilizing transformation. Finally, we can get to a Fisher's $z$-score and it's variance $\se_z^2$ by using:
+\begin{align}
+z &= 0.5 \ln\big(\frac{1 + r}{1 - r}\big) & \nonumber
+%z &= \arctan(r) & \nonumber
 \se_z^2 &= \frac{1}{n-3}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+$z$ is approximately normally distributed with around the mean $z$ and with standard error $\se_z$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 At the end of a systematic review, ``a systematic presentation, and synthesis, of the characteristics and findings of the included studies'' is done. \\
-53 Cochrane Review Groups prepare and maintain the reviews within specific areas of health care.
+Fifty three Cochrane Review Groups prepare and maintain the reviews within specific areas of health care.
 A group consists of ``researchers, healthcare professionals and people using healthcare services (consumers)''.
@@
 ``As of January 2008 (Issue 1, 2008), CENTRAL contains nearly 530,000 citations to reports of trials and other studies potentially eligible for inclusion in Cochrane reviews, of which 310,000 trial reports are from MEDLINE, 50,000 additional trial reports are from EMBASE and the remaining 170,000 are from other sources such as other databases and handsearching.'' It includes citations published in many languages, citations only available in conference proceedings, citations from trials registers and trials results registers.
-\item MEDLINE includes over 16 million references to journal articles.
+\item MEDLINE.
+MEDLINE includes over 16 million references to journal articles.
 5,200 journals publishing in 27 languages are indexed for MEDLINE.
@@
 \\
-The \texttt{comparison.name} variable specifies \textit{what kind} of treatments or interventions are compared, the \texttt{outcome.name} variable \textit{how} it is compared, and the \texttt{subgroup.name} variable (not indicated in table) if and to \textit{what experimental subgroup} the result belongs to.
+The \texttt{comparison.name} variable specifies \textit{what kind} of treatments or interventions are compared, the \texttt{outcome.name} variable \textit{how} it is compared, and the \texttt{subgroup.name} variable (not indicated in table) if and to \textit{what experimental subgroups} the results belong to.
 \\
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 15 21:26:39 2019
+% Tue Aug 20 13:54:20 2019
 \begin{table}[ht]
@@
 \end{tikzpicture}
-\caption{General structure of the database. Results from primary studies belong to the same comparison, outcome and subgroups, and can be used to estimate a combined effect in a meta-analysis.}
+\caption{General structure of the database. Results from primary studies that belong to the same comparison, outcome and subgroup can be used to estimate a combined effect in a meta-analysis.}
 \label{review.structure}
@@
   \begin{center}
-    \begin{tabular}{l l}
+    \begin{tabular}{ll}
       \textbf{Variable} & \textbf{Description}\\
@@
       \texttt{subgroup.id} & Specification of the comparison by a string of the type \\ &``CMP-xxx.yy.xx'' for the xx. subgroup for the yy. outcome \\ & of the xxx. comparison within the review.\\
-      \texttt{outcome.measure} & Outcome measure, \eg risk ratio.\\
-      \texttt{outcome.measure.merged} & Outcome measure, \eg risk ratio, merged such that each method is uniquely classified.\\
+      \texttt{outcome.measure} & Outcome measure, for example risk ratio.\\
+      \texttt{outcome.measure.merged} & Outcome measure, for example risk ratio, merged such \\ &that each method is uniquely classified.\\
       \texttt{outcome.flag} & A outcome flag to simplify programming; \\ &\texttt{DICH} for binary outcomes with fully available information \\ &on event counts,
@@
 The review comprises five studies in total.
-Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental.
+Three of them compared barbiturate treatment to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental.
 The studies have different outcomes, for example, death or death and severe disability at follow up, but also dropout counts or adverse effects (secondary outcomes).
@@
 The median of the publication years is 2003, the mean 2001 and the quartiles are 1996 and 2008.
-1,075 studies have been published in 2018.\\
+NULL studies have been published in 2018.\\
 The most frequent outcome measures are summarized in Table \ref{outcome.measure.frequencies}.
-One can conclude of the table that roughly 31 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (more than 65\%).
+One can conclude of the table that roughly 31\% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (more than 65\%).
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 15 21:26:39 2019
+% Tue Aug 20 13:54:20 2019
 \begin{table}[ht]
@@
 This distinction is also used by Cochrane, \ie the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
-The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 15 21:26:39 2019
-\begin{table}[ht]
-\centering
-\begingroup\footnotesize
-\begin{tabular}{lrr}
-  \hline
-n & Number of groups & Cumulative sum of groups \\ 
-  \hline
-1 & 143378 & 268906 \\ 
-  2 & 45459 & 125528 \\ 
-  3 & 23232 & 80069 \\ 
-  4 & 14184 & 56837 \\ 
-  5 & 9493 & 42653 \\ 
-  6 & 6449 & 33160 \\ 
-  7 & 4583 & 26711 \\ 
-  8 & 3412 & 22128 \\ 
-  9 & 2585 & 18716 \\ 
-  10 & 2046 & 16131 \\ 
-  11 & 1524 & 14085 \\ 
-  12 & 1197 & 12561 \\ 
-  13 & 1022 & 11364 \\ 
-  14 & 785 & 10342 \\ 
-  15 & 9557 & 9557 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Number and cumulative number of groups with meta-analysis size n.} 
-\label{repr.groups}
-\end{table}
+% The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.
+
+% 
+% <<echo = FALSE, results = 'asis'>>=
+% print(xtable(cum.repr.trials.subg[,-2], label = "repr.groups", caption = "Cumulative number of meta-analyses with $n$ or more results.", align = "llr", digits = 0), include.rownames = F,  size = "footnotesize", floating = TRUE)
+% @
+%
+
+% 
+% <<echo=FALSE, results='asis', warning =FALSE, message = FALSE>>=
+% # rownames(cum.repr.trials.subg)[15] <- "$\\geq$ 15"
+% cum.repr.trials.subg <- cum.repr.trials.subg[,-2]
+% print(xtable(cum.repr.trials.subg[,-2], label = "repr.groups", caption = "Cumulative number of groups with n results.", align = "llr", digits = 0), include.rownames = F,  size = "footnotesize", sanitize.rownames.function = identity)
+% @
 
@@
 \item \textbf{No withdrawn reviews}: Reviews that have been withdrawn are not included.
-\item \textbf{No adverse effects}: No results of adverse effects of treatment are used for meta-analyses.we could thus clearly identify many safety results but this may be incomplete when safety outcomes are insufficiently declared, for example ``headache''.
+\item \textbf{No adverse effects}: No results of adverse effects of treatment are used for meta-analysis.
+We could thus clearly identify many safety results but this may be incomplete when safety outcomes are insufficiently declared, for example ``headache''.
 \end{itemize}
@@
 \end{tikzpicture}
-\caption{Flow-chart of the exclusion of meta-analyses for the final analysis. The exclusion criteria are given at the right of the arrows.}
+\caption{Flow-chart of the inclusion of meta-analyses for the final analysis. The exclusion criteria are given at the right of the arrows.}
 \label{Inclusion.criteria}
@@
 All computations were performed in the \texttt{R} computing environment \citep{R.base}.
-The \texttt{R} packages \texttt{meta} \citep{meta.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments.
+The \texttt{R} packages \texttt{meta} \citep{meta.package}, \texttt{metasens} \citep{metasens.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments.
 The excess significance test was adapted from \citet{vanAert.2019}.
@@
 
-\section{Data and Code Availability}
-The data of the Cochrane Library of Systematic Reviews is freely available in some countries, in others, the rights are reserved by the Wiley publishing company.
-The code for data processing and analysis can be found osf.io, the DOI of the project is (project not yet online).
+% \section{Data and Code Availability}
+% The data of the Cochrane Library of Systematic Reviews is freely available in some countries, in others, the rights are reserved by the Wiley publishing company.
+The code for data processing and analysis can be found at \url{https://osf.io/dbp2r/}.
 
@@
 
-Meta analysis are based on results of primary studies. Therefore, in a first step, an exploratory plot of the median effect size and it's dependence on the study sample size can be shown. \\
-The absolute value of the median Fisher's $z$ transformed correlation for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
+Meta analysis are based on results of primary studies.
+Therefore, in a first step, an exploratory plot of the median effect size from primary studies and it's dependence on the study sample size can be shown.
+\\
+The absolute value of the median Fisher's $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}.
 The medians are calculated separately for efficacy and safety outcomes.
 It is clearly visible that the absolute value of the medians for efficacy decreases with increasing sample size.
-The sample size is much smaller for safety outcomes, such that it is not clear if the median effect sizes of safety outcomes do not decrease with increasing sample size, or the variation between medians is just too large to detect a decrease.\\
+The sample size is much smaller for safety outcomes, and there appears to be no clear relationship between effect sizes of primary studies and their standard errors.\\
 The pattern for efficacy outcomes is the same for all common outcome measures as shown in Figure \ref{effect.samplesize.separated}, where the original effect size measures ``log Odds Ratio'', ``log Risk Ratio'', ``Mean Difference'' and ``Std.
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-11-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-10-1}
 
@@
 \end{knitrout}
-\caption{Median of the absolute Fisher's $z$ transformed correlation across sample size plotted against the total sample size.}
+\caption{Median of the absolute Fisher's $z$-score across sample size plotted against the total sample size.}
 \label{z.samplesize}
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-12-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-11-1}
 
@@
 
-The meta-analyses fulfilling the criteria from Chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with one-sided small publication bias tests and excess significance tests.
+The meta-analyses fulfilling the criteria from Chapter \ref{ch:dataset}, Section \ref{sec:Processing}, are analysed with one-sided publication bias tests and excess significance tests.
 The direction in which bias is expected is the one on which more significant results of primary studies are (two-sided $p$-value < 0.05).
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-14-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-13-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-15-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-14-1}
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-16-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-15-1}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 15 22:03:09 2019
+% Tue Aug 20 13:54:35 2019
 \begin{table}[ht]
@@
 \endgroup
-\caption{Counts Number of significant test results per meta-analysis, separated
+\caption{Number of significant test results per meta-analysis, separated
        for outcome types. Last entry for continuous and IV outcomes is empty since one test less was 
@@
 \\
-The precise proportions of agreement in significance/non-significance are provided in Table \ref{test.agreement}.
+The precise proportions of agreement in significance/non-significance are provided in Table \ref{test.agreement}, \ie the proportion of results where both tests agree on if publication bias is significant or non-significant.
 A separate column provides the proportion of significant results of the test with fewer significant results that are also significant using the test with more significant results.
+If the proportion is 1, then all significant results of one test are also significant using the other test.
+\\
 Linear regression based tests agree more often with other linear regression based tests, and agreement between small study effect tests is in general well above 60 \% (at best, 95\% test agreement in significance for \texttt{IV} \texttt{outcome.flag}).
@@
 \\
-To compare the effects of adjustment between meta-analyses of different outcomes, the outcome measures are transformed to standardized mean differences and Fisher's $z$ transformed correlations (see section \ref{sec:transformation.effectsizes} for details).
-When comparing to unadjusted effects, fixed or random effects meta-analysis estimates are used as references\\
+To compare the effects of adjustment between meta-analyses of different outcomes, the outcome measures are transformed to standardized mean differences and Fisher's $z$-scores (see section \ref{sec:transformation.effectsizes} for details).
+When comparing to unadjusted effects, fixed or random effects meta-analysis estimates are used as references.\\
 Figure \ref{fig:adjustment.reg} displays the difference between the estimated meta-analysis treatment effect and the regression adjusted treatment effect \ref{sec:regression.adjustment}, $\hat{\theta}_M - \hat{\theta}_\textrm{Adj.}$.
@@
 An adjusted effect with evidence for publication bias can be regarded as a more realistic estimate of the treatment effect.
-Some very large and very small differences have been omitted in the Fisher's $z$ transformed correlation and std.
+Some very large and very small differences have been omitted in the Fisher's $z$-scores and std.
 mean difference histograms; they are shown in Table \ref{missing.differences}.
@@
 \\
+Additionally, some meta-analyses with positively adjusted, larger overall treatment effects after adjustment (left side of the histogram) have also evidence for publication bias (defined as the tendency of small studies to show \textit{larger} results because only significant results are published).
+However, this is not wrong, because the effects and their variances have been transformed, and it is possible that the shape of the funnel plot changes upon transformation; Figure \ref{fig:funnel.plot.change} shows this for illustrative purposes.
+From the left to the right, the funnel plots of meta-analyses with binary and continuous outcomes are shown.
+We see that the direction of adjustment changes depending on the effect size measure used.
+Note that while the rank of the effect sizes is preserved after transformation, the relative size and especially the ranks of the variances may vary.
+Therefore, the shape of the funnel plot may also change after transformation.
+Also, std.
+mean differences and risk ratios and their standard errors are correlated, which is not the case for Fisher's $z$-scores.
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-20-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-19-1}
 
@@
 
-Additionally, some meta-analyses with positively adjusted, larger overall treatment effects after adjustment (left side of the histogram) have also evidence for publication bias (defined as the tendency of small studies to show \textit{larger} results because only significant results are published).
-However, this is not wrong, because the effects and their variances have been transformed, and it is possible that the shape of the funnel plot changes upon transformation; Figure \ref{fig:funnel.plot.change} shows this for illustrative purposes.
-From the left to the right, the funnel plot is shown for mean differences (the original measure), standardized mean differences and Fisher's $z$ scores; there is no change upon adjustment using mean differences (blue line), reduction of the effect with std.
-mean differences and increase with Fisher's $z$ transformed correlation.
-Note that while the rank of the effect sizes is usually preserved after transformation, the relative size and especially the variance may vary.
-One effect of the Fisher's $z$-transformation is that the effect sizes are bounded on $[-1,1]$, and thus, very large effect sizes will influence the fit of the linear regression less than for example in std.
-mean differences, which are not bounded.
-In contrast, the variance of the correlation is directly tied to the sample size, which makes it a suitable proxy for study size (variance of the mean difference is in contrast strongly influenced by the standard deviations).
-
 \begin{figure}
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-21-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-20-1}
 
@@
 \end{knitrout}
-\caption{Funnel plots for a meta-analysis based on three different effect size measures: Mean differences, std.
-mean differences and Fisher's z transformed correlations and corresponding standard errors.
+\caption{Funnel plots for two meta-analyses and different effect size measures.
+In the first row, a meta-analysis with a continuous outcome, with mean differences, std.
+mean differences and Fisher's $z$-scores and corresponding standard errors.
+In the second row for binary outcomes, a meta-analysis with binary outcomes and risk ratios, std.
+mean differences and $z$-scores and corresponding standard errors.
 Vertical dashed lines indicate meta-analysis estimates, the rhombus with the curved blue line the adjusted treatment effect.}
@@
 
-Figure \ref{fig:adjustment.copas} shows the differences between Meta-analysis and adjusted effect sizes adjusted by Copas selection model; the model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
+Figure \ref{fig:adjustment.copas} shows the differences between meta-analysis and adjusted effect sizes adjusted by Copas selection model; the model substitutes its estimates with random effect estimates when it finds no evidence for small study effects.
 Therefore, the effect of adjustment by Copas can better be seen when comparing adjusted with random effects meta analysis estimates.
@@
 The means in Table \ref{adjustment.difference} suggest that the average reduction is small.
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 69 meta-analyses have their Fisher's $z$ transformed correlation reduced by more than 0.13 by regression adjustment (and 5\% or 69 increased by -0.11 or more, fixed effects reference).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or 69 meta-analyses have their Fisher's $z$-score reduced by more than 0.13 by regression adjustment (and 5\% or 69 increased by -0.11 or more, fixed effects reference).
 Also, std.
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-22-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-21-1}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 15 22:03:23 2019
+% Tue Aug 20 13:54:49 2019
 \begin{table}[ht]
@@
   \hline
- & 5\% & 25\% & 50\% & 75\% & 95\% & mean & = 0 (\%) & $>$= 0 (\%) & $>$ 0 (\%) & No adj. est. (\%) \\ 
-  \hline
-z: Fixed - Copas & -0.04 & -0.01 & 0.00 & 0.01 & 0.04 & 0.00 & 8.14 & 50.14 & 42.00 & 65.49 \\ 
-  z: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.04 & 0.00 & 67.15 & 85.23 & 18.08 & 65.49 \\ 
-  z: Fixed - Regression & -0.11 & -0.03 & 0.01 & 0.05 & 0.13 & 0.01 & 0.00 & 52.02 & 52.02 & 0.00 \\ 
-  z: Random - Regression & -0.13 & -0.02 & 0.02 & 0.06 & 0.16 & 0.02 & 0.00 & 56.56 & 56.56 & 0.00 \\ 
-  d: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.11 & 0.01 & 19.38 & 56.41 & 37.03 & 56.92 \\ 
-  d: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.16 & 0.02 & 60.09 & 85.01 & 24.93 & 56.92 \\ 
-  d: Fixed - Regression & -0.21 & -0.03 & 0.04 & 0.14 & 0.40 & 0.06 & 0.00 & 60.16 & 60.16 & 0.00 \\ 
-  d: Random - Regression & -0.20 & -0.02 & 0.05 & 0.17 & 0.44 & 0.08 & 0.00 & 62.68 & 62.68 & 0.00 \\ 
+ & 5\% & 25\% & 50\% & 75\% & 95\% & mean & = 0 (\%) & $\geq$ 0 (\%) & > 0 (\%) & No adj. est. (\%) \\ 
+  \hline
+$z$: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.05 & 0.00 & 6.20 & 48.70 & 42.51 & 65.20 \\ 
+  $z$: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.05 & 0.00 & 66.43 & 85.66 & 19.24 & 65.20 \\ 
+  $z$: Fixed - Regression & -0.12 & -0.03 & 0.01 & 0.05 & 0.14 & 0.01 & 0.00 & 51.37 & 51.37 & 0.00 \\ 
+  $z$: Random - Regression & -0.14 & -0.02 & 0.02 & 0.07 & 0.17 & 0.02 & 0.00 & 57.06 & 57.06 & 0.00 \\ 
+  $d$: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.11 & 0.01 & 19.38 & 56.41 & 37.03 & 56.92 \\ 
+  $d$: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.16 & 0.02 & 60.09 & 85.01 & 24.93 & 56.92 \\ 
+  $d$: Fixed - Regression & -0.21 & -0.03 & 0.04 & 0.14 & 0.40 & 0.06 & 0.00 & 60.16 & 60.16 & 0.00 \\ 
+  $d$: Random - Regression & -0.20 & -0.02 & 0.05 & 0.17 & 0.44 & 0.08 & 0.00 & 62.68 & 62.68 & 0.00 \\ 
   IV: Fixed - Copas & -0.06 & -0.01 & 0.00 & 0.01 & 0.07 & 0.00 & 23.97 & 42.15 & 66.12 & 59.50 \\ 
@@
 The row names indicate which outcome measure, meta-analysis method and adjustment method is used.
-Abbreviations are used for Fisher's z transformed correlation (z) and std.
-mean difference (d).
-Separate rows give the results for IV outcomes, where the original effect sizes (log rate ratios, hazard ratios, etc.) are used.}
+Abbreviations are used for Fisher's $z$-scores ($z$) and std.
+mean difference ($d$).
+Separate rows give the results for IV outcomes, where the original effect sizes (log risk ratios, log rate ratios, hazard ratios, etc.) are used.}
 \label{adjustment.difference}
@@
   \hline
-id & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z reg. & smd fixed & smd random & smd Copas & smd reg. \\ 
-  \hline
-CD000370 & 8 & 2 & 0.66 & 0.66 & 0.66 & 0.82 & 1.59 & 1.59 & 1.40 & 0.28 \\ 
-  CD001183 & 7 & 0 & -0.48 & -0.48 & -0.48 & -0.21 & -1.10 & -1.12 & -0.50 & -0.11 \\ 
-  CD002307 & 2 & 1 & -0.10 & -0.08 & -0.10 & 0.03 & -0.47 & -0.42 & -0.41 & -3.00 \\ 
-  CD008625 & 2 & 2 & -0.60 & -0.60 & -0.60 & -0.39 & -1.72 & -2.02 & -1.01 & -0.69 \\ 
-  CD010060 & 1 & 0 & 0.31 & 0.32 & 0.31 & 0.23 & 0.50 & 0.52 & 0.20 & -0.49 \\ 
+id & comparison.nr & subgroup.nr & $z$ fixed & $z$ random & $z$ Copas & $z$ reg. & $d$ fixed & $d$ random & $d$ Copas & $d$ reg. \\ 
+  \hline
+CD000370 & 8 & 2 & 0.80 & 0.81 & 0.80 & 0.97 & 1.59 & 1.59 & 1.40 & 0.28 \\ 
+  CD001183 & 7 & 0 & -0.54 & -0.54 & -0.54 & -0.21 & -1.10 & -1.12 & -0.50 & -0.11 \\ 
+  CD002307 & 2 & 1 & -0.13 & -0.11 & -0.13 & 0.04 & -0.47 & -0.42 & -0.41 & -3.00 \\ 
+  CD008625 & 2 & 2 & -0.76 & -0.72 & -0.67 & -0.48 & -1.72 & -2.02 & -1.01 & -0.69 \\ 
+  CD010060 & 1 & 0 & 0.33 & 0.34 & 0.33 & 0.25 & 0.50 & 0.52 & 0.20 & -0.49 \\ 
    \hline
@@
 \endgroup
-\caption{Missing meta-analysis combined treatment effect and adjusted treatment effects. Abbreviations are used for Fisher's z transformed correlation (= z) and std. mean difference (= d).} 
+\caption{Missing meta-analysis combined treatment effect and adjusted treatment effects. Abbreviations are used for Fisher's $z$-scores (= $z$) and std. mean differences (= $d$).} 
 \label{missing.differences}
@@
 A Tukey mean difference plot can reveal systematic differences and biases between the two measurement methods.
-Note that only 26 out of 121 \texttt{IV} outcome data is included when using Fisher's $z$ transformed correlation and std.
+Note that only 26 out of 121 \texttt{IV} outcome data is included when using Fisher's $z$-score and std.
 mean differences, since not all effects could be transformed.
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-25-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-24-1}
 
@@
 Two values have been omitted in the middle plot for std.
-mean difference and one for Fisher's $z$ transformed correlation (see Table \ref{missing.differences}).}
+mean difference and one for Fisher's $z$-score (see Table \ref{missing.differences}).}
 \label{fig:adjustment.mean.diff}
@@
 There is however a small difference, indicating that regression estimates have a little bit a larger absolute value.
-There might be some bias between adjusted Fisher's $z$ transformed correlations, where regression estimates seem to be somewhat smaller when the mean is a little above zero, and somewhat larger when the mean is a little below zero.
+There might be some bias between adjusted Fisher's $z$-scores, where regression estimates seem to be somewhat smaller when the mean is a little above zero, and somewhat larger when the mean is a little below zero.
 \\
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-26-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-25-1}
 
@@
 Together with the horizontal dotted lines, the area which it borders indicates the consequences of adjustment for the evidence for a treatment effect.
-``decrease'' means that the test statistic is smaller upon adjustment, ''increase'' that it is larger.}
+``Decrease'' means that the test statistic is smaller upon adjustment, ''increase'' that it is larger.}
 \label{fig:evidence.adjustment}
@@
 The decrease in evidence is larger when using adjustment with regression, which can be expected as the uncertainty of the additional parameter from the linear regression fit to estimate publication bias is included in the uncertainty of the estimate.
-In contrast, as the Copas selection model algorithm does a sensitivity analysis, the uncertainty of additional model parameters does not affect the estimate as they are not estimated but treated as fixed (see section \ref{sec:procedure} and section \ref{sec:copas}).\\
+In contrast, as the Copas selection model algorithm does a sensitivity analysis, the uncertainty of additional model parameters does not affect the estimate as they are not estimated but treated as fixed (see Section \ref{sec:procedure} and Section \ref{sec:copas}).\\
 Large adjustment in effect sizes and test statistics is not necessarily accompanied by evidence for publication bias (color of the dots) in regression adjustment, as already discussed.
@@
 Some cases which have more evidence for treatment efficacy after adjustment have evidence for publication bias, although the publication bias tests applied are one-sided and only test for bias towards large effects.
-This is because the algorithm to detect the side on which publication bias was expected (section \ref{sec:procedure}) has failed, \eg because few significant effects are given (used to define side of bias) and the weighted mean effect is close to zero, in which case it is difficult to decide upon the side of publication bias.
+This is because the algorithm to detect the side on which publication bias was expected (Section \ref{sec:procedure}) has failed, \eg because few significant effects are given (used to define side of bias) and the weighted mean effect is close to zero, in which case it is difficult to decide upon the side of publication bias.
 There are some adjustments with large increase in evidence and clear dark orange color, as in the plots on the right hand side in Figure \ref{fig:evidence.adjustment}.
@@
 \end{itemize}
-In the case of Copas selection model and when both test statistics are large (> 10), the explanation lies in a specialty of the model; the adjusted treatment effect estimates are not larger than the unadjusted, but their standard errors are different and sometimes smaller, because they are obtained from the Fisher information matrix of the log-likelihood (see subsection \ref{sec:copas}).
+In the case of Copas selection model and when both test statistics are large (> 10), the explanation lies in a specialty of the model; the adjusted treatment effect estimates are not larger than the unadjusted, but their standard errors are different and sometimes smaller, because they are obtained from the Fisher information matrix of the log-likelihood (see Subsection \ref{sec:copas}).
 \\
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-27-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-26-1}
 
@@
 
+\vspace{-2mm}
 We can see that in some occasions, the method finds more than half of all studies in a meta-analysis are missing.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 15 22:03:25 2019
+% Tue Aug 20 13:54:50 2019
 \begin{table}[ht]
@@
 
-\section{Mixed Effect Models and Publication Bias over Time}
-To test if publication bias in meta-analyses has changed over time and newer meta-analyses have less bias, a generalized linear model has been set up to analyze all meta-analyses jointly and estimate a single parameter denoting publication bias.
-The procedure is to first start with the simplest model and consecutively add more explanatory variables and check by means of the AIC, BIC and F-test if the fit of the model has improved.\\
-The dependent variable is the standardized mean differences(therefore, from \texttt{outcome.flag} = \texttt{IV}, only the std.
-mean differences are used).
-As before in section \ref{sec:change.size}, the std.
-mean difference is mirrored to one side by multiplying with the sign of the expected side of bias, \ie -1 or 1.
-\\
-In a first step, the explanatory variable is the standard error, and the weights are the inverse of the variance of the std.
-mean difference.
+\section{Mixed Effects Models and Publication Bias over Time}
+To test if publication bias in meta-analyses has changed over time and newer meta-analyses have less bias, a mixed linear model with random effects will be fitted (see Section \ref{sec:regression}).
+In terms of \eqref{eq:one.random.intercept}, with random effects $U$, the formula is
+
+\begin{align}
+\mathbf{y}_i|U_j,U_k,\epsilon_{i} =  x_i\beta + U_j + U_k + \epsilon_{i} \nonumber
+\end{align}
+
+where $j$ and $k$ are corresponding indexes for the meta-analysis and the review, and $y_i$ is the effect size and $x_i$ the standard error belonging to result $i$.
+Additionally, weights equal to the inverse of the standard errors are introduced.
+The framework allows to analyze all meta-analyses jointly, such that statistical power is increased.\\
+First, it is investigated if the model fit improves if we allow for random slopes within a meta-analysis,.
+Then, we will introduce an interaction term between the year of review publication or the mean study publication year and publication bias.
+If the interaction term improves model fit, we will analyse the sign and the size of the interaction term, and otherwise state that no evidence could be found that publication bias in meta-analyses changed over the years.
+Because it is a exploratory analysis, the procedure is to first start with the simplest model and consecutively add more explanatory variables and check by means of the AIC, BIC and F-test if the fit of the model has improved.
+Fisher's $z$-score are and its standard error is used for analysis.
+One model will be fitted with review publication year and one with mean study publication year.\\
+The dependent variable is the effect size $z$.
+As before in Section \ref{sec:change.size}, the effect sizes are mirrored to one side by multiplying with the sign of the expected side of bias, \ie -1 or 1.
+Taking the absolute values might obscure cases where the sign of the effect size changes but its absolute value is equal.\\
+In a first step, the explanatory variable is the standard error, and the weights are the inverse of the variance of $z$.
 Additionally, random effects for the meta-analysis and for the review are added, the former being nested in the latter.
 Figure \ref{fig:smds} shows the complete dataset with the fit of the previously described model (dotted red line).
-The details and evidence for the small study effects in the generalized linear model are given in Table \ref{anova.small.study}, the coefficients in Table \ref{coefficients.small.study}
+The details and evidence for the small study effects in the mixed linear model are given in Table \ref{anova.small.study}, the coefficients in Table \ref{coefficients.small.study}:
 
@@
 
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-29-1}
+{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-28-1}
 
@@
 \end{knitrout}
-\caption{Std. mean differences of all meta-analyses plotted against their standard error, with the fit of a generalized linear model (dotted red line).}
+\caption{$z$-scores of all meta-analyses plotted against their standard error, with the fit of a mixed linear model (dotted red line).}
 \label{fig:smds}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 15 22:03:33 2019
+% Tue Aug 20 13:54:59 2019
 \begin{table}[ht]
@@
   \hline
-null.fit &  1 & 4.0 & 18768.2 & 18800.1 & -9380.1 &  &  &  \\ 
-  publication.bias.fit &  2 & 5.0 & 18230.5 & 18270.4 & -9110.3 & 1 vs 2 & 539.7 & $<$0.00001 \\ 
+null.fit &  1 & 4.0 & 1480.7 & 1512.6 & -736.4 &  &  &  \\ 
+  publication.bias.fit &  2 & 5.0 & 1306.2 & 1346.1 & -648.1 & 1 vs 2 & 176.5 & $<$0.00001 \\ 
    \hline
@@
 \endgroup
-\caption{Anova table for a generalized linear model for small study effects compared to the null model ('null.fit').
+\caption{Anova table for a mixed linear model for small study effects compared to the null model ('null.fit').
 'publication.bias.fit' denotes the model with random intercepts for meta-analyses and reviews.}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 15 22:03:34 2019
+% Tue Aug 20 13:54:59 2019
 \begin{table}[ht]
@@
   \hline
-(Intercept) & 0.18 & 0.16 & 0.19 \\ 
-  se.smd.pool & 0.38 & 0.35 & 0.41 \\ 
+(Intercept) & 0.10 & 0.09 & 0.11 \\ 
+  se.z.mirrored & 0.52 & 0.44 & 0.59 \\ 
    \hline
@@
 \endgroup
-\caption{Coefficients and 95\% confidence limits of the generalized linear model. 'se.smd.pool' denotes the standard error of the std. mean difference.} 
+\caption{Coefficients and 95\% confidence limits of the mixed linear model. 'se.z.mirrored' denotes the standard error of the $z$-score.} 
 \label{coefficients.small.study}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 15 22:03:35 2019
+% Tue Aug 20 13:55:02 2019
 \begin{table}[ht]
@@
   \hline
-publication.bias.fit &  1 & 5.0 & 18230.5 & 18270.4 & -9110.3 &  &  &  \\ 
-  publication.bias.rs.fit &  2 & 7.0 & 18233.1 & 18288.9 & -9109.5 & 1 vs 2 & 1.5 & 0.5 \\ 
+publication.bias.fit &  1 & 5.0 & 1306.2 & 1346.1 & -648.1 &  &  &  \\ 
+  publication.bias.rs.fit &  2 & 7.0 & 1310.2 & 1366.0 & -648.1 & 1 vs 2 & 0.0 & 1.0 \\ 
    \hline
@@
 \endgroup
-\caption{Anova table for two generalized linear model fits.
+\caption{Anova table for two mixed linear model fits.
 'publication.bias.fit' denotes the model with random intercepts for meta-analyses and reviews, 'publication.bias.rs.fit' the model with additional random slopes per review.}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 15 22:03:37 2019
+% Tue Aug 20 13:55:04 2019
 \begin{table}[ht]
@@
   \hline
-publication.bias.fit &  1 & 5.0 & 18230.5 & 18270.4 & -9110.3 &  &  &  \\ 
-  review.year.fit &  2 & 6.0 & 18231.6 & 18279.5 & -9109.8 & 1 vs 2 & 0.9 & 0.34 \\ 
-  review.year.int.fit &  3 & 7.0 & 18233.6 & 18289.4 & -9109.8 & 2 vs 3 & 0.0 & 0.87 \\ 
+publication.bias.fit &  1 & 5.0 & 1306.2 & 1346.1 & -648.1 &  &  &  \\ 
+  review.year.fit &  2 & 6.0 & 1307.0 & 1354.8 & -647.5 & 1 vs 2 & 1.2 & 0.27 \\ 
+  review.year.int.fit &  3 & 7.0 & 1308.4 & 1364.2 & -647.2 & 2 vs 3 & 0.6 & 0.44 \\ 
    \hline
@@
 \endgroup
-\caption{Anova table for three generalized linear model fits.
+\caption{Anova table for three mixed linear model fits.
 'publication.bias.fit' denotes the model with the standard error as explanatory variable, 'review.year.fit' the model with standard error and the centered (- 2013) review year as explanatory variable, and 'review.year.int.fit' the model with interaction between the two.}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 15 22:03:41 2019
+% Tue Aug 20 13:55:08 2019
 \begin{table}[ht]
@@
   \hline
-publication.bias.fit &  1 & 5.0 & 18115.2 & 18155.1 & -9052.6 &  &  &  \\ 
-  study.year.fit &  2 & 6.0 & 18117.2 & 18165.0 & -9052.6 & 1 vs 2 & 0.0 & 0.958789 \\ 
-  study.year.int.fit &  3 & 7.0 & 18118.9 & 18174.7 & -9052.5 & 2 vs 3 & 0.3 & 0.591536 \\ 
+publication.bias.fit &  1 & 5.0 & 1404.0 & 1443.8 & -697.0 &  &  &  \\ 
+  study.year.fit &  2 & 6.0 & 1405.1 & 1452.8 & -696.5 & 1 vs 2 & 0.9 & 0.334873 \\ 
+  study.year.int.fit &  3 & 7.0 & 1406.8 & 1462.6 & -696.4 & 2 vs 3 & 0.2 & 0.639192 \\ 
    \hline
@@
 \endgroup
-\caption{Anova table for three generalized linear model fits.
+\caption{Anova table for three mixed linear model fits.
 'Small study fit' denotes the model with the standard error as explanatory variable, 'study.year.fit' the model with standard error and the centered (- 2000) mean study year of the meta-analysis as explanatory variable, and 'study.year.int.fit' the model with interaction between the two.}
@@
 
-The analysis of model fit indicates that there is an improvement when using the study year as a covariate, but only as an additive effect.
-It finds that effect sizes are in general little bit smaller in latter mean publication years (after the year 2000).
-The coefficients of the model are given in Table \ref{coefficients.study.year.fit}.
-AIC and BIC are smaller and the $p$-value of the F-test is very small.
-However, not the size of the effect, but the slope of the linear regression fit would have to be decreased in latter years to ultimately conclude a decrease of publication bias over the years.
-
-% latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 15 22:03:42 2019
-\begin{table}[ht]
-\centering
-\begingroup\scriptsize
-\begin{tabular}{lccc}
-  \hline
- & estimate & 2.5\%CL & 97.5\%CL \\ 
-  \hline
-(Intercept) & 0.1758 & 0.1575 & 0.1940 \\ 
-  se.smd.pool & 0.3800 & 0.3482 & 0.4118 \\ 
-  mean.study.year & -0.0001 & -0.0020 & 0.0019 \\ 
-   \hline
-\end{tabular}
-\endgroup
-\caption{Coefficients and 95\% confidence limits of the generalized linear model. 'se.smd.pool' denotes the standard error of the std. mean difference.} 
-\label{coefficients.study.year.fit}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \begin{figure}
-% <<echo=FALSE, fig.height = 9, warning=FALSE>>=
-% #HISTOGRAMS:  
-% 
-% #Comparison of treatment effect p-values:
-% sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
-%                               z.ranef = est.z.ranef/se.est.z.ranef,
-%                               z.reg = est.z.reg/se.est.z.reg,
-%                               z.copas = est.z.copas/se.est.z.copas) %>%
-%   select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>%
-%   mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>%
-%   group_by(method) %>%
-%   summarise(significant = length(which(abs(fisher.z) > 1.96)),
-%             p.significant = significant/length(fisher.z))
-% sig.zcor <- data.frame(method = sig.zcor$method,
-%                        label = paste(round(sig.zcor$p.significant,3)*100, "% significant", ", (n = ", sig.zcor$significant, ")", sep = ""))
-% 
-% method_names <- c(
-%   z.fixef = "Fixed Effects",
-%   z.ranef = "Random Effects",
-%   z.reg = "Regression",
-%   z.copas = "Copas"
-% )
-% 
-% adjustment.p.z <- meta.f %>%
-%   mutate(z.fixef = est.z.fixef/se.est.z.fixef,
-%          z.ranef = est.z.ranef/se.est.z.ranef,
-%          z.reg = est.z.reg/se.est.z.reg,
-%          z.copas = est.z.copas/se.est.z.copas) %>%
-%   select(z.fixef, z.ranef, z.reg, z.copas) %>%
-%   gather(key = "method", value = "fisher.z") %>%
-%   mutate(method = factor(method, levels = c("z.fixef", "z.ranef", "z.reg", "z.copas"))) %>%
-%   mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>%
-%   ggplot(aes(x = p.fisher.z)) +
-%   geom_histogram(boundary = 0, bins = 20) +
-%   theme_bw() +
-%   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-%   geom_text(data = sig.zcor, aes(x = 0.5, y = 750, label = label), position = "dodge") +
-%   xlab(expression(paste(italic(p),"-value of test statistic of the ", italic(z),"-score"))) +
-%   ggtitle(expression(paste(italic(z), " Score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-% #--------------------------------------------------------------------------------------------------------------------#
-% 
-% #Comparison of SMD's:
-% sig.d <- meta.f %>% mutate(d.fixef = est.d.fixef/se.est.d.fixef,
-%                            d.ranef = est.d.ranef/se.est.d.ranef,
-%                            d.reg = est.d.reg/se.est.d.reg,
-%                            d.copas = est.d.copas/se.est.d.copas) %>%  
-%   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-%   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-%   group_by(method) %>% 
-%   summarise(significant = length(which(abs(smd) > 1.96)),
-%             p.significant = significant/length(smd))
-% sig.d <- data.frame(method = sig.d$method,
-%                     label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
-% 
-% method_names <- c(
-%   d.fixef = "Fixed Effects",
-%   d.ranef = "Random Effects",
-%   d.reg = "Regression",
-%   d.copas = "Copas"
-% )
-% 
-% adjustment.p.d <- meta.f %>% 
-%   mutate(d.fixef = est.d.fixef/se.est.d.fixef,
-%          d.ranef = est.d.ranef/se.est.d.ranef,
-%          d.reg = est.d.reg/se.est.d.reg,
-%          d.copas = est.d.copas/se.est.d.copas) %>%  
-%   select(d.fixef, d.ranef, d.reg, d.copas) %>% 
-%   gather(key = "method", value = "smd") %>% 
-%   mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
-%   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-%   ggplot(aes(x = p.smd)) + 
-%   geom_histogram(boundary = 0, bins = 20) + 
-%   theme_bw() + 
-%   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-%   geom_text(data = sig.d, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
-%   xlab(expression(paste(italic(p),"-value of test statistic of std. mean differences"))) +
-%   ggtitle(expression(paste("std. mean difference ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-% #--------------------------------------------------------------------------------------------------------------------#
-% 
-% #Comparison of log hazard ratios:
-% sig.d <- meta.f %>% filter(outcome.flag == "IV") %>% 
-%   mutate(d.fixef = est.fixef/se.est.fixef,
-%          d.ranef = est.ranef/se.est.ranef,
-%          d.reg = est.reg/se.est.reg,
-%          d.copas = est.copas/se.est.copas) %>%  
-%   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-%   group_by(method) %>% 
-%   summarise(significant = length(which(abs(smd) > 1.96)),
-%             p.significant = (significant + sum(is.na(smd)))/(length(smd)))
-% sig.d <- data.frame(method = sig.d$method,
-%                     label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
-% 
-% method_names <- c(
-%   d.fixef = "Fixed Effects",
-%   d.ranef = "Random Effects",
-%   d.reg = "Regression",
-%   d.copas = "Copas"
-% )
-% 
-% adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.flag == "IV") %>% 
-%   mutate(d.fixef = est.fixef/se.est.fixef,
-%          d.ranef = est.ranef/se.est.ranef,
-%          d.reg = est.reg/se.est.reg,
-%          d.copas = est.copas/se.est.copas) %>%  
-%   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-%   mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
-%   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-%   ggplot(aes(x = p.smd)) + 
-%   geom_histogram(boundary = 0, bins = 20) + 
-%   theme_bw() + 
-%   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-%   geom_text(data = sig.d, aes(x = 0.5, y = 100, label = label), position = "dodge") + 
-%   xlab(expression(paste(italic(p),"-value of test statistic of std. mean difference"))) +
-%   ggtitle(expression(paste("Log IV outcome measures ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-% #--------------------------------------------------------------------------------------------------------------------#
-% 
-% grid.arrange(adjustment.p.z,
-%              adjustment.p.d,
-%              adjustment.p.log.hazard.ratio, ncol = 1)
-% @
-% \caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted combined treatment effect, based on different treatment effect measures.
+The analysis of model fit indicates that there is no improvement when using the study year as a covariate.
+Thus, there is no evidence for a interaction between small study effects and mean study publication year
+
+% % # <<echo =FALSE, results='asis', warning=FALSE>>=
+% % # lmer.table <- function(model){
+% % #   sum <- summary(model)
+% % #   estimate <- round(sum$coefficients$fixed)
+% % #   ci <- intervals(model)
+% % #   tb <- data.frame(estimate = round(ci$fixed[,2], 5), CI = round(ci$fixed[,c(1,3)], 5))
+% % #   colnames(tb)[c(2,3)] <- c("2.5%CL", "97.5%CL")
+% % #   return(tb)
+% % # }
+% % # print(xtable(lmer.table(study.year.fit), align = "lccc", 
+% % #              caption = "Coefficients and 95\\% confidence limits of the mixed linear model. 'se.z.mirrored' denotes the standard error of the $z$-score.", 
+% % #              label = "coefficients.study.year.fit", digits = c(4,4,4,4)),  size = "scriptsize")
+% % # @
+% 
+% 
+% 
+% 
+% 
+% 
+% 
+% 
+% 
+% 
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% % \begin{figure}
+% % <<echo=FALSE, fig.height = 9, warning=FALSE>>=
+% % #HISTOGRAMS:  
+% % 
+% % #Comparison of treatment effect p-values:
+% % sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+% %                               z.ranef = est.z.ranef/se.est.z.ranef,
+% %                               z.reg = est.z.reg/se.est.z.reg,
+% %                               z.copas = est.z.copas/se.est.z.copas) %>%
+% %   select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>%
+% %   mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>%
+% %   group_by(method) %>%
+% %   summarise(significant = length(which(abs(fisher.z) > 1.96)),
+% %             p.significant = significant/length(fisher.z))
+% % sig.zcor <- data.frame(method = sig.zcor$method,
+% %                        label = paste(round(sig.zcor$p.significant,3)*100, "% significant", ", (n = ", sig.zcor$significant, ")", sep = ""))
+% % 
+% % method_names <- c(
+% %   z.fixef = "Fixed Effects",
+% %   z.ranef = "Random Effects",
+% %   z.reg = "Regression",
+% %   z.copas = "Copas"
+% % )
+% % 
+% % adjustment.p.z <- meta.f %>%
+% %   mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+% %          z.ranef = est.z.ranef/se.est.z.ranef,
+% %          z.reg = est.z.reg/se.est.z.reg,
+% %          z.copas = est.z.copas/se.est.z.copas) %>%
+% %   select(z.fixef, z.ranef, z.reg, z.copas) %>%
+% %   gather(key = "method", value = "fisher.z") %>%
+% %   mutate(method = factor(method, levels = c("z.fixef", "z.ranef", "z.reg", "z.copas"))) %>%
+% %   mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>%
+% %   ggplot(aes(x = p.fisher.z)) +
+% %   geom_histogram(boundary = 0, bins = 20) +
+% %   theme_bw() +
+% %   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+% %   geom_text(data = sig.zcor, aes(x = 0.5, y = 750, label = label), position = "dodge") +
+% %   xlab(expression(paste(italic(p),"-value of test statistic of the ", italic(z),"-score"))) +
+% %   ggtitle(expression(paste(italic(z), " Score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+% % #--------------------------------------------------------------------------------------------------------------------#
+% % 
+% % #Comparison of SMD's:
+% % sig.d <- meta.f %>% mutate(d.fixef = est.d.fixef/se.est.d.fixef,
+% %                            d.ranef = est.d.ranef/se.est.d.ranef,
+% %                            d.reg = est.d.reg/se.est.d.reg,
+% %                            d.copas = est.d.copas/se.est.d.copas) %>%  
+% %   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+% %   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+% %   group_by(method) %>% 
+% %   summarise(significant = length(which(abs(smd) > 1.96)),
+% %             p.significant = significant/length(smd))
+% % sig.d <- data.frame(method = sig.d$method,
+% %                     label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
+% % 
+% % method_names <- c(
+% %   d.fixef = "Fixed Effects",
+% %   d.ranef = "Random Effects",
+% %   d.reg = "Regression",
+% %   d.copas = "Copas"
+% % )
+% % 
+% % adjustment.p.d <- meta.f %>% 
+% %   mutate(d.fixef = est.d.fixef/se.est.d.fixef,
+% %          d.ranef = est.d.ranef/se.est.d.ranef,
+% %          d.reg = est.d.reg/se.est.d.reg,
+% %          d.copas = est.d.copas/se.est.d.copas) %>%  
+% %   select(d.fixef, d.ranef, d.reg, d.copas) %>% 
+% %   gather(key = "method", value = "smd") %>% 
+% %   mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
+% %   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+% %   ggplot(aes(x = p.smd)) + 
+% %   geom_histogram(boundary = 0, bins = 20) + 
+% %   theme_bw() + 
+% %   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+% %   geom_text(data = sig.d, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
+% %   xlab(expression(paste(italic(p),"-value of test statistic of $z$-scores"))) +
+% %   ggtitle(expression(paste("$z$-score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+% % #--------------------------------------------------------------------------------------------------------------------#
+% % 
+% % #Comparison of log hazard ratios:
+% % sig.d <- meta.f %>% filter(outcome.flag == "IV") %>% 
+% %   mutate(d.fixef = est.fixef/se.est.fixef,
+% %          d.ranef = est.ranef/se.est.ranef,
+% %          d.reg = est.reg/se.est.reg,
+% %          d.copas = est.copas/se.est.copas) %>%  
+% %   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+% %   group_by(method) %>% 
+% %   summarise(significant = length(which(abs(smd) > 1.96)),
+% %             p.significant = (significant + sum(is.na(smd)))/(length(smd)))
+% % sig.d <- data.frame(method = sig.d$method,
+% %                     label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
+% % 
+% % method_names <- c(
+% %   d.fixef = "Fixed Effects",
+% %   d.ranef = "Random Effects",
+% %   d.reg = "Regression",
+% %   d.copas = "Copas"
+% % )
+% % 
+% % adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.flag == "IV") %>% 
+% %   mutate(d.fixef = est.fixef/se.est.fixef,
+% %          d.ranef = est.ranef/se.est.ranef,
+% %          d.reg = est.reg/se.est.reg,
+% %          d.copas = est.copas/se.est.copas) %>%  
+% %   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+% %   mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
+% %   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+% %   ggplot(aes(x = p.smd)) + 
+% %   geom_histogram(boundary = 0, bins = 20) + 
+% %   theme_bw() + 
+% %   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+% %   geom_text(data = sig.d, aes(x = 0.5, y = 100, label = label), position = "dodge") + 
+% %   xlab(expression(paste(italic(p),"-value of test statistic of $z$-score"))) +
+% %   ggtitle(expression(paste("Log IV outcome measures ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+% % #--------------------------------------------------------------------------------------------------------------------#
+% % 
+% % grid.arrange(adjustment.p.z,
+% %              adjustment.p.d,
+% %              adjustment.p.log.hazard.ratio, ncol = 1)
+% % @
+% % \caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted combined treatment effect, based on different treatment effect measures.
 The method is indicated in the header, bin width is set to 0.05.
 The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
-% \label{fig:adjustment.stat}
-% \end{figure}
+% % \label{fig:adjustment.stat}
+% % \end{figure}
+% 
+% 
+% 
+%
 
@@
 After comparison with previous studies that analysed publication bias in the Cochrane Library, we found that our results were similar to the results of these studies (\eg \citealp{Egger}, \citealp{Ioannidis2007}).
-Further information can be found in the Appendix\\
+A summary and comparison of this work to most relevant research can be found in the appendix Chapter \ref{ch:Appendix}.\\
 % In this study, evidence for publication bias has been found in approximately 20\% of the meta-analyses.
@@
 Presence of publication bias in meta-analyses can ultimately lead to patient harm if decision makers in clinical practice use the meta-analyses to decide about application of a treatment.
-However, publication bias does in general lead to too large confidence in the results of the meta-analyses.
-In some cases, it might be that the  evidence for a treatment in a meta-analysis is an artifact of publication bias.
+Publication bias does in general lead to exaggerated confidence in the results of the meta-analyses.
+It is possible that the  evidence for a treatment in a meta-analysis is merely an artifact of publication bias.
 This also leads to a waste of resources in science.
@@
 When research is more experimental and exploratory, it may well be that publication bias is an issue as well, or even more of an issue.
-Publication bias is possibly related to more discovery oriented, modern research \citet{ioannidis.2005}.\\
+Publication bias is possibly related to more discovery oriented, modern research \citep{ioannidis.2005}.\\
 There is an unknown amount of meta-analyses with secondary outcomes in the analysis.
-It is not well investigated if and how secondary outcomes are affected by publication bias, and how much they are affected by between-study heterogeneity, as researchers might not follow the same stringent protocols when assessing secondary outcomes.
+It is not well investigated if and how secondary outcomes are affected by publication bias, and how much they are affected by between-study heterogeneity, as researchers might not follow common protocols as rigidly when assessing secondary outcomes.
 Together with unremoved adverse effect meta-analyses, which are likely subject to different kinds of publication bias, they can distort or mitigate the estimated extent of publication bias in this study.
@@
 Some criticism can be addressed on the methods.
-The small study effect which is used as an indication for publication bias can be caused by other biases such as selective outcome reporting, or poor methodological quality of smaller studies.
+The small study effect which is used as an indication for publication bias can be caused by other biases such as selective outcome reporting, data fabrication, poor methodological quality of smaller studies or delayed publication of non-significant results.
 It can also be caused by true heterogeneity between studies; early and small studies are more likely to include high-risk patients for which treatment can have larger benefits.
-Where effect size estimates and their standard errors are not independent (\eg log risk ratios, std.
+However, true heterogeneity between smaller and larger studies might as well mask the presence of publication bias, for example if smaller studies have smaller effects due to true between-study heterogeneity.
+Where effect size estimates and their standard errors are not independent (\eg log risk ratios and std.
 mean differences), small study effect can be a statistical artifact.
-However, true heterogeneity between smaller and larger studies might as well mask the presence of publication bias, for example if smaller studies have smaller effects due to true between-study heterogeneity.\\
+However, methods to avoid this issue have largely been applied.\\
 Also, small study effect tests do not use statistical significance directly.
@@
 The only test that is applied that takes into account statistical significance per se is the excess significance test, which is underpowered.
-However, we restricted the meta-analyses such that at least one significant effect had to be included.
+Therefore, we restricted the meta-analyses such that at least one significant effect had to be included.
 \\
@@
 Linear regression is prone to outliers, especially if the sample size is small.
-The issue is partially resolved by weighting, but the usual procedure to assess if the model assumptions are fulfilled are not possible for such a large number of model fits.\\
+The issue is partially resolved by weighting, but the usual procedure to assess if the model assumptions are fulfilled is not applicable for such a large number of model fits.\\
 All the criticism also applies for adjustment methods, as they also rely on small study effects.
 A weakness of the regression adjustment is that it also adjusts if the uncertainty in the small study effect is large.
-To compare it in this case with the meta-analysis estimate is difficult because the uncertainty in estimating the small study effect affects the uncertainty of the treatment effect.
+To compare it in this case with the meta-analysis estimate is difficult because the uncertainty in estimating the small study effect is added to the uncertainty of the treatment effect, which inflates the uncertainity of the adjusted treatment effect.
+\\
 Copas selection model uses the $p$-value threshold of 0.1 to decide if adjustment is necessary or not.
 One could argue that this threshold is somewhat arbitrary.
-When assessing the evidence for the treatment effect being different from the effect under the null, a likelihood ratio test would provide more appropriate results than the Wald test.
+%When assessing the evidence for the treatment effect being different from the effect under the null, a likelihood ratio test would provide more appropriate results than the Wald test.
 %Selection models do not account for the uncertainity that is contained in the selection process parameters they use, which makes it difficult to use their results to test against the null hypothesis of no treatment effect.\\
-Another issue that the model is not estimating the selection process parameters, but rather applying some criteria of parsimony (the model with least publication bias/selection with $p$-value for small study effect > 0.1 is chosen).
-As the regression model, this model also comes with various assumptions that likely affect the results.
+Another issue that the model is not estimating the selection process parameters, but rather applying some criteria of parsimony (the model that assumes fewest publication bias with $p$-value for small study effect > 0.1 is chosen).
+\\
+Both models use various assumptions that likely affect the results.
 But in simulations, the methods all had fewer mean-squared error and bias than the classical meta-analysis methods when publication bias was present.\\
@@
 No methods exist so far to adjust for excess significance.
-This would be a reason to assume that publication bias is underestimated.\\
-Given the large body of evidence for publication bias by other means, it is unlikely that the unexpectedly large proportion of significant test results and the downward corrected treatment effect estimates are merely false positives.
+This could lead to  underestimated.\\
+Given the large body of evidence for publication bias by other means, it is unlikely that the unexpectedly large proportion of significant test results and the downward corrected treatment effect estimates are merely false positives or caused by other biases.
 Of course, the general practice is to apply all the methods in this study carefully, and with background knowledge about each single study in the meta-analyses, to differentiate between true heterogeneity and publication bias.
@@
 Transformation of the effect sizes might change a significant result to non-significant or vice-versa.
-Thus transformation will lead to a loss of accuracy.
+Thus, transformation will lead to a loss of accuracy.
 Furthermore, transformation of mean differences to std.
@@
 When transforming odds ratios to std.
-mean differences, the interdependence between effect size and std.
-mean difference is also retained.\\
-Transformation to Fisher's $z$ transformed correlation will abolish this dependency, but since correlations are bounded, linear regression will no longer be suitable to detect very large effect sizes.
-Furthermore, the applied adjustment methods which are based on Fisher's $z$ transformed correlations are not adapted to correlation coefficients and sometimes provide meaningless results (coefficients $> 1$ or $< -1$).
-Thus, one transformation will tend to underestimate publication bias, while the other likely overestimates it, and both are not accurate.
+mean differences, the dependence between effect size and std.
+mean difference is also retained.
+Analyzing publication bias with
+std. mean differences might lead to false positives and false negatives. Using Fisher's $z$-score is more appropriate since standard errors and effect sizes are independent.\\
 
 \section{Outlook}
-Given the size and abundance of information in the dataset, the possibilities to investigate sources of bias in the Cochrane Library of Systematic Reviews are not exhausted.
-In particular, one could easily come up with more hypotheses that could be tested in meta meta-regression, as introduced in the last section of the results.
-Many researchers have come up with hypotheses about the reasons and circumstances that promote publication bias, which could be tested if the dataset is extended.\\
+It would be possible to further narrow the subset of meta-analyses where publication bias is likely.
+For example, one could choose meta-analyses with large proportions of significant results.
+Treatment effect adjustment and consequences of adjustment for evidence for treatment effect could subsequently be analysed more carefully.
+Related to this, implementation of a likelihood ratio test in Copas selection model, as proposed by the Authors, would be feasible and increase accuracy.
+\\
+Many researchers have come up with hypotheses about the reasons and circumstances that promote publication bias, which could be tested if the dataset is extended.
+Meta meta-regression as introduced in the last chapter might be a suitable way to test these hypotheses in an exploratory manner.\\
 There are numerous suggestions for different measures of publication bias and small study effects, which could be applied on the dataset (see \citealp{mueller.2016}).
@@
 \\
-We are not aware of any use of one-sided tests for publication bias as used in this study, which allows to look more specifically for publication bias for ``positive'' or desired treatment effects.
-The results indicate that the efforts to curb down publication bias are only partially successful.\\
+We are not aware of any use of one-sided tests for publication bias as used in this study, which allows to look more specifically for publication bias for significant, ``positive'' or ``desired'' treatment effects in a large scale.
+We find a proportion of significant test results well above the expected false positive rate of the tests of 10\%.\\
 Also, it is the first study to extensively adjust the combined effect sizes from meta-analyses for publication bias.
@@
 
-\chapter{Appendix}
+\chapter{Appendix}\label{ch:Appendix}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 15 22:04:20 2019
+% Tue Aug 20 13:55:52 2019
 \begin{table}[ht]

### 2019-08-20 report/chapter02.Rnw
final draft

@@
 
-Finally, we can get to a fisher's z-transformed correlation $z$ and it's variance $\se_z^2$ by using
+Because $r$ and $\se_r$ are not independent, we can apply a variance stabilizing transformation. Finally, we can get to a Fisher's $z$-score and it's variance $\se_z^2$ by using:
 \begin{align}
-% z &= 0.5 \ln\big(\frac{1 + r}{1 - r}\big) & \nonumber
-z &= \arctan(r) & \nonumber
+z &= 0.5 \ln\big(\frac{1 + r}{1 - r}\big) & \nonumber
+%z &= \arctan(r) & \nonumber
 \se_z^2 &= \frac{1}{n-3}
 \end{align}
+
+$z$ is approximately normally distributed with around the mean $z$ and with standard error $\se_z$.

### 2019-08-20 report/chapter03.Rnw
final draft

@@
 
-colnames(cum.repr.trials.subg)  <- c("n","Number of groups", "Cumulative sum of groups")
+colnames(cum.repr.trials.subg)  <- c("n","", "cumulative number")
 #----------------------------------------------------------------------------------------------#
@@
 The most frequent outcome measures are summarized in Table \ref{outcome.measure.frequencies}.
-One can conclude of the table that roughly 31 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (more than 65\%).
+One can conclude of the table that roughly 31\% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (more than 65\%).
 
@@
 This distinction is also used by Cochrane, \ie the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
-The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.
+% The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.
 
-<<echo=FALSE, results='asis', warning =FALSE, message = FALSE>>=
-rownames(cum.repr.trials.subg)[15] <- "$\\geq$ 15"
-print(xtable(cum.repr.trials.subg, label = "repr.groups", caption = "Number and cumulative number of groups with meta-analysis size n.", align = "llrr", digits = 0), include.rownames = F, size = "footnotesize")
-@
+% 
+% <<echo = FALSE, results = 'asis'>>=
+% print(xtable(cum.repr.trials.subg[,-2], label = "repr.groups", caption = "Cumulative number of meta-analyses with $n$ or more results.", align = "llr", digits = 0), include.rownames = F,  size = "footnotesize", floating = TRUE)
+% @
+%
+
+% 
+% <<echo=FALSE, results='asis', warning =FALSE, message = FALSE>>=
+% # rownames(cum.repr.trials.subg)[15] <- "$\\geq$ 15"
+% cum.repr.trials.subg <- cum.repr.trials.subg[,-2]
+% print(xtable(cum.repr.trials.subg[,-2], label = "repr.groups", caption = "Cumulative number of groups with n results.", align = "llr", digits = 0), include.rownames = F,  size = "footnotesize", sanitize.rownames.function = identity)
+% @
 
@@
 \item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = \Sexpr{format(m.a.largerten.count, big.mark = ",")} remaining). 
-\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = \Sexpr{format(m.a.variance4.count, big.mark = ",")} remaining).
-\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = \Sexpr{format(m.a.one.sig.count, big.mark = ",")} remaining)
-\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = \Sexpr{format(m.a.smaller.5.count, big.mark = ",")} remaining).
+\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = \Sexpr{format(m.a.variance4.count$n, big.mark = ",")} remaining).
+\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = \Sexpr{format(m.a.one.sig.count$n, big.mark = ",")} remaining)
+\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = \Sexpr{format(m.a.smaller.5.count$nn, big.mark = ",")} remaining).
 \end{itemize}

### 2019-08-20 report/chapter04.Rnw
final draft

--- 2019-08-14 report/chapter04.Rnw
@@
 
-<<echo=FALSE, warning=FALSE, message = FALSE>>=
+<<echo=FALSE, warning=FALSE, message = FALSE, cache = TRUE>>=
 p.samplesize.z  <- data.ext2 %>% 
@@
   geom_point(size = 0.8) + facet_wrap(~outcome.desired) +
-  theme_bw() + xlab("sample size") + ylab("median absolute z-score") +
+  theme_bw() + xlab("sample size") + 
+  ylab(expression(paste("median absolute ",  italic(z), "-score"))) +
   xlim(c(15, 300)) + ylim(c(0, 0.25)) +
@@
 @
-\caption{Median of the absolute Fisher's $z$ transformed correlation across sample size plotted against the total sample size.}
+\caption{Median of the absolute Fisher's $z$-score across sample size plotted against the total sample size.}
 \label{z.samplesize}
@@
 <<echo = FALSE, results='asis'>>=
-print(xtable(number.sig.tests, caption = "Counts Number of significant test results per meta-analysis, separated
+print(xtable(number.sig.tests, caption = "Number of significant test results per meta-analysis, separated
        for outcome types. Last entry for continuous and IV outcomes is empty since one test less was 
@@
   scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) +
-  xlab(expression(paste("Fixed effects - adjusted ", z, "-score"))) + geom_vline(xintercept = 0, linetype = "dashed" )
+  xlab(expression(paste("Fixed effects", italic(z), "- adjusted ", italic(z)))) + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
   scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) +
-  xlab(expression(paste("Fixed effects - adjusted ", z, "-score"))) + geom_vline(xintercept = 0, linetype = "dashed" )
+  xlab(expression(paste("Fixed effects ", italic(z), " - adjusted ", italic(z)))) + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
   scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + ylab("") + 
-  xlab(expression(paste("Random effects - adjusted ", z, "-score"))) + geom_vline(xintercept = 0, linetype = "dashed" )
+  xlab(expression(paste("Random effects ", italic(z), " - adjusted ", italic(z)))) + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
   scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + 
-  xlab(expression(paste("Random effects - adjusted ", z, "-score"))) + geom_vline(xintercept = 0, linetype = "dashed" )
+  xlab(expression(paste("Random effects ", italic(z), " - adjusted ", italic(z)))) + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
   scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + 
-  xlab(expression(paste("Fixed effects - adjusted std. mean difference"))) + geom_vline(xintercept = 0, linetype = "dashed" )
+  xlab(expression(paste("Fixed effects ", italic(d), " - adjusted ", italic(d)))) + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
   scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) +  ylab("") +
-xlab(expression(paste("Random effects - adjusted std. mean difference"))) + geom_vline(xintercept = 0, linetype = "dashed" )
+xlab(expression(paste("Random effects ", italic(d), " - adjusted ", italic(d)))) + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
   scale_fill_manual(values  = c("seagreen1", "seagreen3", "green4")) + ylab("") +
-xlab(expression(paste("Random effects - adjusted std. mean difference"))) + geom_vline(xintercept = 0, linetype = "dashed" )
+xlab(expression(paste("Random effects ", italic(d)," - adjusted ", italic(d)))) + geom_vline(xintercept = 0, linetype = "dashed" )
 #--------------------------------------------------------------------------------------------------------------------#
@@
 
-rownames(adjustment.diff.table) <- c(paste("z:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
-                                     paste("d:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
+rownames(adjustment.diff.table) <- c(paste("$z$:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
+                                     paste("$d$:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")),
                                      paste("IV:", c("Fixed - Copas", "Random - Copas", "Fixed - Regression", "Random - Regression")))
 
-colnames(adjustment.diff.table) <- c(colnames(adjustment.diff.table)[1:6], "= 0 (%)", ">= 0 (%)", "> 0 (%)", "No adj. est. (%)")
+colnames(adjustment.diff.table) <- c("5\\%", "25\\%", "50\\%", "75\\%", "95\\%", "mean", "= 0 (\\%)", "$\\geq$ 0 (\\%)", "> 0 (\\%)", "No adj. est. (\\%)")
 
@@
 colnames(missing.differences) <- c("id", "comparison.nr", "subgroup.nr",
-                                   "z fixed", "z random", "z Copas", "z reg.",
-                                   "smd fixed", "smd random", "smd Copas", "smd reg.")
+                                   "$z$ fixed", "$z$ random", "$z$ Copas", "$z$ reg.",
+                                   "$d$ fixed", "$d$ random", "$d$ Copas", "$d$ reg.")
 
@@
             color = "chartreuse3") + 
-  xlab("Adjusted z test statistic") + ylab("Fixed effects z test statistic")
+  xlab(expression(paste("Adjusted ",  italic(z),  " test statistic"), sep = "")) + 
+  ylab(expression(paste("Fixed effects z ", italic(z), " test statistic"), sep = ""))
 
@@
             color = "chartreuse3") + 
-  xlab("Adjusted z test statistic") + ylab("Random effects z test statistic")
+  xlab(expression(paste("Adjusted ",  italic(z),  " test statistic"), sep = "")) + 
+  ylab(expression(paste("Random effects z ", italic(z), " test statistic"), sep = ""))
 #--------------------------------------------------------------------------------------------------------------------#
@@
 
-Additionally, some meta-analyses with positively adjusted, larger overall treatment effects after adjustment (left side of the histogram) have also evidence for publication bias (defined as the tendency of small studies to show \textit{larger} results because only significant results are published).
-However, this is not wrong, because the effects and their variances have been transformed, and it is possible that the shape of the funnel plot changes upon transformation; Figure \ref{fig:funnel.plot.change} shows this for illustrative purposes.
-From the left to the right, the funnel plot is shown for mean differences (the original measure), standardized mean differences and Fisher's $z$ scores; there is no change upon adjustment using mean differences (blue line), reduction of the effect with std.
-mean differences and increase with Fisher's $z$ transformed correlation.
-Note that while the rank of the effect sizes is usually preserved after transformation, the relative size and especially the variance may vary.
-One effect of the Fisher's $z$-transformation is that the effect sizes are bounded on $[-1,1]$, and thus, very large effect sizes will influence the fit of the linear regression less than for example in std.
-mean differences, which are not bounded.
-In contrast, the variance of the correlation is directly tied to the sample size, which makes it a suitable proxy for study size (variance of the mean difference is in contrast strongly influenced by the standard deviations).
-
 \begin{figure}
-<<echo = FALSE, warning=FALSE>>=
-par(mfrow = c(1,3))
-example <- data.ext2 %>% filter(id == "CD003236", subgroup.nr == 2, outcome.nr == 1, comparison.nr == 1)
+<<echo = FALSE, warning=FALSE, fig.height=5>>=
+par(mfrow = c(2,3), cex.lab = 1.5, cex.axis = 1.5)
+example <- data.ext2 %>% filter(meta.id == 81244)
 funnel(limitmeta(metagen(TE = effect, se = se, studlab = study.name, sm = "MD", data = example)), col.adjust = "blue", col.line = "blue")
 funnel(limitmeta(metagen(TE = smd.pool, se = se.smd.pool, studlab = study.name, sm = "SMD", data = example)), col.adjust = "blue", col.line = "blue")
-funnel(limitmeta(metacor(cor = z, n = total1 + total2, studlab = study.name, sm = "ZCOR", data = example)), col.adjust = "blue", col.line = "blue")
-par(mfrow = c(1,1))
-@
-\caption{Funnel plots for a meta-analysis based on three different effect size measures: Mean differences, std.
-mean differences and Fisher's z transformed correlations and corresponding standard errors.
+funnel(limitmeta(metagen(TE = z, seTE = sqrt(var.z), studlab = study.name, sm = "ZCOR", data = example)), col.adjust = "blue", col.line = "blue")
+
+example <- data.ext2 %>% filter(meta.id == 32532)
+funnel(limitmeta(metagen(TE = log(effect), se = se, studlab = study.name, sm = "RR", data = example)), col.adjust = "blue", col.line = "blue")
+funnel(limitmeta(metagen(TE = smd.pool, se = se.smd.pool, studlab = study.name, sm = "SMD", data = example)), col.adjust = "blue", col.line = "blue")
+funnel(limitmeta(metagen(TE = z, seTE = sqrt(var.z), studlab = study.name, sm = "ZCOR", data = example)), col.adjust = "blue", col.line = "blue")
+@
+\caption{Funnel plots for two meta-analyses and different effect size measures.
+In the first row, a meta-analysis with a continuous outcome, with mean differences, std.
+mean differences and Fisher's $z$-scores and corresponding standard errors.
+In the second row for binary outcomes, a meta-analysis with binary outcomes and risk ratios, std.
+mean differences and $z$-scores and corresponding standard errors.
 Vertical dashed lines indicate meta-analysis estimates, the rhombus with the curved blue line the adjusted treatment effect.}
@@
 The means in Table \ref{adjustment.difference} suggest that the average reduction is small.
-To recall some other findings out of Table \ref{adjustment.difference}: 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} meta-analyses have their Fisher's $z$ transformed correlation reduced by more than 0.13 by regression adjustment (and 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} increased by -0.11 or more, fixed effects reference).
+To recall some other findings out of Table \ref{adjustment.difference}: 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} meta-analyses have their Fisher's $z$-score reduced by more than 0.13 by regression adjustment (and 5\% or \Sexpr{floor(length(!is.na(meta.f$est.z.reg))*0.05)} increased by -0.11 or more, fixed effects reference).
 Also, std.
@@
 The row names indicate which outcome measure, meta-analysis method and adjustment method is used.
-Abbreviations are used for Fisher's z transformed correlation (z) and std.
-mean difference (d).
-Separate rows give the results for IV outcomes, where the original effect sizes (log rate ratios, hazard ratios, etc.) are used.", align = "lcccccccccr"), include.rownames = T, size = "scriptsize",# sanitize.text.function=function(x){x},
-      # table.placement = "p"
-      )
+Abbreviations are used for Fisher's $z$-scores ($z$) and std.
+mean difference ($d$).
+Separate rows give the results for IV outcomes, where the original effect sizes (log risk ratios, log rate ratios, hazard ratios, etc.) are used.", align = "lcccccccccr"), include.rownames = T, size = "scriptsize", floating = TRUE,
+      sanitize.rownames.function = identity, sanitize.colnames.function = identity)
 @
@@
              caption = "Missing meta-analysis combined treatment effect and adjusted treatment effects.
-Abbreviations are used for Fisher's z transformed correlation (= z) and std.
-mean difference (= d).", label = "missing.differences", align = "lcccrrrrrrrr"),
-      include.rownames = F, size = "tiny")
+Abbreviations are used for Fisher's $z$-scores (= $z$) and std.
+mean differences (= $d$).", label = "missing.differences", align = "lcccrrrrrrrr"),
+      include.rownames = F, size = "tiny",
+      sanitize.colnames.function = identity)
 @
@@
 A Tukey mean difference plot can reveal systematic differences and biases between the two measurement methods.
-Note that only 26 out of \Sexpr{dim(meta.iv)[1]} \texttt{IV} outcome data is included when using Fisher's $z$ transformed correlation and std.
+Note that only 26 out of \Sexpr{dim(meta.iv)[1]} \texttt{IV} outcome data is included when using Fisher's $z$-score and std.
 mean differences, since not all effects could be transformed.
@@
 \begin{figure}
-<<echo = FALSE, warning = FALSE, fig.height = 6>>=
+<<echo = FALSE, warning = FALSE, fig.height = 6.5>>=
 grid.arrange(adjusted.evidence.fixed,
@@
 There, less of an effect of adjustment on the evidence can be seen.
-The adjustment is more likely to be more reliable than the unadjusted estimate when publication bias is strong (see \ref{ch:Methods}).
+The adjustment is more likely to be more reliable than the unadjusted estimate when publication bias is strong (see \ref{ch:methods}).
 The dots with darker color are thus more likely to provide less biased estimates.\\
 The decrease in evidence is larger when using adjustment with regression, which can be expected as the uncertainty of the additional parameter from the linear regression fit to estimate publication bias is included in the uncertainty of the estimate.
-In contrast, as the Copas selection model algorithm does a sensitivity analysis, the uncertainty of additional model parameters does not affect the estimate as they are not estimated but treated as fixed (see section \ref{sec:procedure} and section \ref{sec:copas}).\\
+In contrast, as the Copas selection model algorithm does a sensitivity analysis, the uncertainty of additional model parameters does not affect the estimate as they are not estimated but treated as fixed (see Section \ref{sec:procedure} and Section \ref{sec:copas}).\\
 Large adjustment in effect sizes and test statistics is not necessarily accompanied by evidence for publication bias (color of the dots) in regression adjustment, as already discussed.
@@
 
+bias.side.z <- function(yi, sei){
+  alpha = 0.05
+  to.ommit <- which(is.na(yi) | is.na(sei))
+
+  if(length(to.ommit) > 0){
+    yi <-  yi[-to.ommit]
+    sei <- sei[-to.ommit]
+  }
+
+  to.ommit <- which(sei == 0)
+
+  if(length(to.ommit) > 0){
+    yi <-  yi[-to.ommit]
+    sei <- sei[-to.ommit]
+  }
+
+  if(sum(pnorm(yi/sei) < .05) == sum(pnorm(yi/sei, lower.tail=FALSE) < .05)){
+      side <- sign(est.fe <- rma(yi = yi, sei = sei, method = "FE")$b[1] )
+  } else{
+    side = ifelse(sum(pnorm(yi/sei) < .05) > sum(pnorm(yi/sei, lower.tail=FALSE) < .05),
+                  -1, 1)
+    }
+  return(side)
+}
+
 #Mirror all effects on one positive side:
 reg.dat <- reg.dat %>% group_by(meta.id) %>%
-  mutate(bias.side = bias.side.fct2(outcome = outcome.flag, 
-                                    outcome.measure.merged = outcome.measure.merged, 
-                                    lrr = lrr, var.lrr = var.lrr, smd = cohensd, 
-                                    var.smd = var.cohensd, effect = effect, se = se),
-  smd.pool = smd.pool * bias.side) #Mirror effect sizes on one side
+  filter(var.z != 0) %>% filter(!is.na(z)) %>% filter(!is.na(var.z)) %>%
+  mutate(se.z.mirrored = sqrt(var.z)) %>% filter(!is.na(se.z.mirrored)) %>%
+  mutate(bias.side.z = bias.side.z(yi = z, sei = se.z.mirrored),
+  z.mirrored = z * bias.side.z) #Mirror effect sizes on one side
+
+reg.dat <- reg.dat %>%  filter(!is.na(z.mirrored)) %>%
+  filter(!is.na(se.z.mirrored))
 
@@
 reg.dat <- reg.dat %>% group_by(meta.id) %>%
-  mutate(tau.squared = metagen(TE = smd.pool, seTE = se.smd.pool)$tau^2,
-         new.se.smd = sqrt(se.smd.pool^2 + tau.squared))
-
-reg.dat <- reg.dat %>% filter(se.smd.pool != 0) %>% filter(!is.na(smd.pool)) %>% 
-  filter(!is.na(se.smd.pool))
+  mutate(tau.squared = metagen(TE = z.mirrored, seTE = se.z.mirrored)$tau^2,
+         new.se.smd = sqrt(se.z.mirrored^2 + tau.squared))
 
@@
 reg.dat <- merge(reg.dat, data.review[,c("id", "year")], by = "id")
-reg.dat <- reg.dat %>% filter(se.smd.pool < 3)
+reg.dat <- reg.dat %>% filter(se.z.mirrored < 3)
 
@@
 study.number.review.model <- dim(reg.dat)[1]
-publication.bias.fit <- lme(fixed = smd.pool ~ se.smd.pool, random = list(~ 1 | id, ~ 1 | meta.id),
-                       weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-plot(y = reg.dat$smd.pool, x = reg.dat$se.smd.pool, cex = .1, xlab = "standard error", ylab = "std. mean difference")
+publication.bias.fit <- lme(fixed = z.mirrored ~ se.z.mirrored, random = list(~ 1 | id, ~ 1 | meta.id),
+                       weights = ~ se.z.mirrored^2, method = "ML", data = reg.dat)
+plot(y = reg.dat$z.mirrored, x = reg.dat$se.z.mirrored, cex = .1, xlab = "standard error", ylab = "z mirrored")
 publication.bias.fit.coef <- summary(publication.bias.fit)$coefficients$fixed
@@
 @
-\caption{Std. mean differences of all meta-analyses plotted against their standard error, with the fit of a generalized linear model (dotted red line).}
+\caption{$z$-scores of all meta-analyses plotted against their standard error, with the fit of a mixed linear model (dotted red line).}
 \label{fig:smds}
@@
 <<echo =FALSE, results='asis', warning=FALSE>>=
-null.fit <- lme(fixed = smd.pool ~ 1, random = list(~ 1 | id, ~ 1 | meta.id),
-                       weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
+null.fit <- lme(fixed = z.mirrored ~ 1, random = list(~ 1 | id, ~ 1 | meta.id),
+                       weights = ~ se.z.mirrored^2, method = "ML", data = reg.dat)
 publication.bias.fit.anova <- anova(null.fit, publication.bias.fit)
 publication.bias.fit.anova[2,9] <- "<0.00001"
-print(xtable(publication.bias.fit.anova[,-1], caption = "Anova table for a generalized linear model for small study effects compared to the null model ('null.fit').
+print(xtable(publication.bias.fit.anova[,-1], caption = "Anova table for a mixed linear model for small study effects compared to the null model ('null.fit').
 'publication.bias.fit' denotes the model with random intercepts for meta-analyses and reviews.",
@@
 print(xtable(lmer.table(publication.bias.fit), align = "lccc",
-             caption = "Coefficients and 95\\% confidence limits of the generalized linear model.
-'se.smd.pool' denotes the standard error of the std.
-mean difference.", label = "coefficients.small.study"),  size = "scriptsize")
+             caption = "Coefficients and 95\\% confidence limits of the mixed linear model.
+'se.z.mirrored' denotes the standard error of the $z$-score.", label = "coefficients.small.study"),  size = "scriptsize")
 @
@@
 <<echo =FALSE, results='asis', warning=FALSE>>=
-publication.bias.rs.fit <- lme(fixed = smd.pool ~ se.smd.pool, 
+publication.bias.rs.fit <- lme(fixed = z.mirrored ~ se.z.mirrored,
                           random = list(~ 1 | id, ~ meta.id | meta.id),
-                       weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-print(xtable(anova(publication.bias.fit, publication.bias.rs.fit)[,-1], caption = "Anova table for two generalized linear model fits.
+                       weights = ~ se.z.mirrored^2, method = "ML", data = reg.dat)
+print(xtable(anova(publication.bias.fit, publication.bias.rs.fit)[,-1], caption = "Anova table for two mixed linear model fits.
 'publication.bias.fit' denotes the model with random intercepts for meta-analyses and reviews, 'publication.bias.rs.fit' the model with additional random slopes per review.",
@@
 <<results = 'asis', echo = FALSE>>=
-review.year.fit <- lme(fixed = smd.pool ~ se.smd.pool + rev.year.center, 
+review.year.fit <- lme(fixed = z.mirrored ~ se.z.mirrored + rev.year.center,
                 random = list(~ 1 | id, ~ 1 | meta.id),
-                weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-review.year.int.fit <- lme(fixed = smd.pool ~ se.smd.pool * rev.year.center, 
+                weights = ~ se.z.mirrored^2, method = "ML", data = reg.dat)
+review.year.int.fit <- lme(fixed = z.mirrored ~ se.z.mirrored * rev.year.center,
                     random = list(~ 1 | id, ~ 1 | meta.id),
-                weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-print(xtable(anova(publication.bias.fit, review.year.fit, review.year.int.fit)[,-1], caption = "Anova table for three generalized linear model fits.
+                weights = ~ se.z.mirrored^2, method = "ML", data = reg.dat)
+print(xtable(anova(publication.bias.fit, review.year.fit, review.year.int.fit)[,-1], caption = "Anova table for three mixed linear model fits.
 'publication.bias.fit' denotes the model with the standard error as explanatory variable, 'review.year.fit' the model with standard error and the centered (- 2013) review year as explanatory variable, and 'review.year.int.fit' the model with interaction between the two.",
@@
 study.number.study.model <- dim(reg.dat)[1]
-publication.bias.fit <- lme(fixed = smd.pool ~ se.smd.pool, random = list(~ 1 | id, ~ 1 | meta.id),
-                       weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-study.year.fit <- lme(fixed = smd.pool ~ se.smd.pool + mean.study.year, 
+publication.bias.fit <- lme(fixed = z.mirrored ~ se.z.mirrored, random = list(~ 1 | id, ~ 1 | meta.id),
+                       weights = ~ se.z.mirrored^2, method = "ML", data = reg.dat)
+study.year.fit <- lme(fixed = z.mirrored ~ se.z.mirrored + mean.study.year,
                 random = list(~ 1 | id, ~ 1 | meta.id),
-                weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-study.year.int.fit <- lme(fixed = smd.pool ~ se.smd.pool * mean.study.year, 
+                weights = ~ se.z.mirrored^2, method = "ML", data = reg.dat)
+study.year.int.fit <- lme(fixed = z.mirrored ~ se.z.mirrored * mean.study.year,
                     random = list(~ 1 | id, ~ 1 | meta.id),
-                weights = ~ se.smd.pool^2, method = "ML", data = reg.dat)
-print(xtable(anova(publication.bias.fit, study.year.fit, study.year.int.fit)[,-1], caption = "Anova table for three generalized linear model fits.
+                weights = ~ se.z.mirrored^2, method = "ML", data = reg.dat)
+print(xtable(anova(publication.bias.fit, study.year.fit, study.year.int.fit)[,-1], caption = "Anova table for three mixed linear model fits.
 'Small study fit' denotes the model with the standard error as explanatory variable, 'study.year.fit' the model with standard error and the centered (- 2000) mean study year of the meta-analysis as explanatory variable, and 'study.year.int.fit' the model with interaction between the two.",
@@
 
-The analysis of model fit indicates that there is an improvement when using the study year as a covariate, but only as an additive effect.
-It finds that effect sizes are in general little bit smaller in latter mean publication years (after the year 2000).
-The coefficients of the model are given in Table \ref{coefficients.study.year.fit}.
-AIC and BIC are smaller and the $p$-value of the F-test is very small.
-However, not the size of the effect, but the slope of the linear regression fit would have to be decreased in latter years to ultimately conclude a decrease of publication bias over the years.
-
-<<echo =FALSE, results='asis', warning=FALSE>>=
-lmer.table <- function(model){
-  sum <- summary(model)
-  estimate <- round(sum$coefficients$fixed)
-  ci <- intervals(model)
-  tb <- data.frame(estimate = round(ci$fixed[,2], 5), CI = round(ci$fixed[,c(1,3)], 5))
-  colnames(tb)[c(2,3)] <- c("2.5%CL", "97.5%CL")
-  return(tb)
-}
-print(xtable(lmer.table(study.year.fit), align = "lccc", 
-             caption = "Coefficients and 95\\% confidence limits of the generalized linear model. 'se.smd.pool' denotes the standard error of the std. mean difference.", 
-             label = "coefficients.study.year.fit", digits = c(4,4,4,4)),  size = "scriptsize")
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \begin{figure}
-% <<echo=FALSE, fig.height = 9, warning=FALSE>>=
-% #HISTOGRAMS:  
+The analysis of model fit indicates that there is no improvement when using the study year as a covariate.
+Thus, there is no evidence for a interaction between small study effects and mean study publication year
+
+% % # <<echo =FALSE, results='asis', warning=FALSE>>=
+% % # lmer.table <- function(model){
+% % #   sum <- summary(model)
+% % #   estimate <- round(sum$coefficients$fixed)
+% % #   ci <- intervals(model)
+% % #   tb <- data.frame(estimate = round(ci$fixed[,2], 5), CI = round(ci$fixed[,c(1,3)], 5))
+% % #   colnames(tb)[c(2,3)] <- c("2.5%CL", "97.5%CL")
+% % #   return(tb)
+% % # }
+% % # print(xtable(lmer.table(study.year.fit), align = "lccc", 
+% % #              caption = "Coefficients and 95\\% confidence limits of the mixed linear model. 'se.z.mirrored' denotes the standard error of the $z$-score.", 
+% % #              label = "coefficients.study.year.fit", digits = c(4,4,4,4)),  size = "scriptsize")
+% % # @
 % 
-% #Comparison of treatment effect p-values:
-% sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
-%                               z.ranef = est.z.ranef/se.est.z.ranef,
-%                               z.reg = est.z.reg/se.est.z.reg,
-%                               z.copas = est.z.copas/se.est.z.copas) %>%
-%   select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>%
-%   mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>%
-%   group_by(method) %>%
-%   summarise(significant = length(which(abs(fisher.z) > 1.96)),
-%             p.significant = significant/length(fisher.z))
-% sig.zcor <- data.frame(method = sig.zcor$method,
-%                        label = paste(round(sig.zcor$p.significant,3)*100, "% significant", ", (n = ", sig.zcor$significant, ")", sep = ""))
 % 
-% method_names <- c(
-%   z.fixef = "Fixed Effects",
-%   z.ranef = "Random Effects",
-%   z.reg = "Regression",
-%   z.copas = "Copas"
-% )
 % 
-% adjustment.p.z <- meta.f %>%
-%   mutate(z.fixef = est.z.fixef/se.est.z.fixef,
-%          z.ranef = est.z.ranef/se.est.z.ranef,
-%          z.reg = est.z.reg/se.est.z.reg,
-%          z.copas = est.z.copas/se.est.z.copas) %>%
-%   select(z.fixef, z.ranef, z.reg, z.copas) %>%
-%   gather(key = "method", value = "fisher.z") %>%
-%   mutate(method = factor(method, levels = c("z.fixef", "z.ranef", "z.reg", "z.copas"))) %>%
-%   mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>%
-%   ggplot(aes(x = p.fisher.z)) +
-%   geom_histogram(boundary = 0, bins = 20) +
-%   theme_bw() +
-%   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-%   geom_text(data = sig.zcor, aes(x = 0.5, y = 750, label = label), position = "dodge") +
-%   xlab(expression(paste(italic(p),"-value of test statistic of the ", italic(z),"-score"))) +
-%   ggtitle(expression(paste(italic(z), " Score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-% #--------------------------------------------------------------------------------------------------------------------#
 % 
-% #Comparison of SMD's:
-% sig.d <- meta.f %>% mutate(d.fixef = est.d.fixef/se.est.d.fixef,
-%                            d.ranef = est.d.ranef/se.est.d.ranef,
-%                            d.reg = est.d.reg/se.est.d.reg,
-%                            d.copas = est.d.copas/se.est.d.copas) %>%  
-%   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-%   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-%   group_by(method) %>% 
-%   summarise(significant = length(which(abs(smd) > 1.96)),
-%             p.significant = significant/length(smd))
-% sig.d <- data.frame(method = sig.d$method,
-%                     label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
 % 
-% method_names <- c(
-%   d.fixef = "Fixed Effects",
-%   d.ranef = "Random Effects",
-%   d.reg = "Regression",
-%   d.copas = "Copas"
-% )
 % 
-% adjustment.p.d <- meta.f %>% 
-%   mutate(d.fixef = est.d.fixef/se.est.d.fixef,
-%          d.ranef = est.d.ranef/se.est.d.ranef,
-%          d.reg = est.d.reg/se.est.d.reg,
-%          d.copas = est.d.copas/se.est.d.copas) %>%  
-%   select(d.fixef, d.ranef, d.reg, d.copas) %>% 
-%   gather(key = "method", value = "smd") %>% 
-%   mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
-%   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-%   ggplot(aes(x = p.smd)) + 
-%   geom_histogram(boundary = 0, bins = 20) + 
-%   theme_bw() + 
-%   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-%   geom_text(data = sig.d, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
-%   xlab(expression(paste(italic(p),"-value of test statistic of std. mean differences"))) +
-%   ggtitle(expression(paste("std. mean difference ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-% #--------------------------------------------------------------------------------------------------------------------#
 % 
-% #Comparison of log hazard ratios:
-% sig.d <- meta.f %>% filter(outcome.flag == "IV") %>% 
-%   mutate(d.fixef = est.fixef/se.est.fixef,
-%          d.ranef = est.ranef/se.est.ranef,
-%          d.reg = est.reg/se.est.reg,
-%          d.copas = est.copas/se.est.copas) %>%  
-%   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-%   group_by(method) %>% 
-%   summarise(significant = length(which(abs(smd) > 1.96)),
-%             p.significant = (significant + sum(is.na(smd)))/(length(smd)))
-% sig.d <- data.frame(method = sig.d$method,
-%                     label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
 % 
-% method_names <- c(
-%   d.fixef = "Fixed Effects",
-%   d.ranef = "Random Effects",
-%   d.reg = "Regression",
-%   d.copas = "Copas"
-% )
 % 
-% adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.flag == "IV") %>% 
-%   mutate(d.fixef = est.fixef/se.est.fixef,
-%          d.ranef = est.ranef/se.est.ranef,
-%          d.reg = est.reg/se.est.reg,
-%          d.copas = est.copas/se.est.copas) %>%  
-%   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
-%   mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
-%   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
-%   ggplot(aes(x = p.smd)) + 
-%   geom_histogram(boundary = 0, bins = 20) + 
-%   theme_bw() + 
-%   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
-%   geom_text(data = sig.d, aes(x = 0.5, y = 100, label = label), position = "dodge") + 
-%   xlab(expression(paste(italic(p),"-value of test statistic of std. mean difference"))) +
-%   ggtitle(expression(paste("Log IV outcome measures ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
-% #--------------------------------------------------------------------------------------------------------------------#
 % 
-% grid.arrange(adjustment.p.z,
-%              adjustment.p.d,
-%              adjustment.p.log.hazard.ratio, ncol = 1)
-% @
-% \caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted combined treatment effect, based on different treatment effect measures.
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% % \begin{figure}
+% % <<echo=FALSE, fig.height = 9, warning=FALSE>>=
+% % #HISTOGRAMS:  
+% % 
+% % #Comparison of treatment effect p-values:
+% % sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+% %                               z.ranef = est.z.ranef/se.est.z.ranef,
+% %                               z.reg = est.z.reg/se.est.z.reg,
+% %                               z.copas = est.z.copas/se.est.z.copas) %>%
+% %   select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>%
+% %   mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>%
+% %   group_by(method) %>%
+% %   summarise(significant = length(which(abs(fisher.z) > 1.96)),
+% %             p.significant = significant/length(fisher.z))
+% % sig.zcor <- data.frame(method = sig.zcor$method,
+% %                        label = paste(round(sig.zcor$p.significant,3)*100, "% significant", ", (n = ", sig.zcor$significant, ")", sep = ""))
+% % 
+% % method_names <- c(
+% %   z.fixef = "Fixed Effects",
+% %   z.ranef = "Random Effects",
+% %   z.reg = "Regression",
+% %   z.copas = "Copas"
+% % )
+% % 
+% % adjustment.p.z <- meta.f %>%
+% %   mutate(z.fixef = est.z.fixef/se.est.z.fixef,
+% %          z.ranef = est.z.ranef/se.est.z.ranef,
+% %          z.reg = est.z.reg/se.est.z.reg,
+% %          z.copas = est.z.copas/se.est.z.copas) %>%
+% %   select(z.fixef, z.ranef, z.reg, z.copas) %>%
+% %   gather(key = "method", value = "fisher.z") %>%
+% %   mutate(method = factor(method, levels = c("z.fixef", "z.ranef", "z.reg", "z.copas"))) %>%
+% %   mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>%
+% %   ggplot(aes(x = p.fisher.z)) +
+% %   geom_histogram(boundary = 0, bins = 20) +
+% %   theme_bw() +
+% %   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+% %   geom_text(data = sig.zcor, aes(x = 0.5, y = 750, label = label), position = "dodge") +
+% %   xlab(expression(paste(italic(p),"-value of test statistic of the ", italic(z),"-score"))) +
+% %   ggtitle(expression(paste(italic(z), " Score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+% % #--------------------------------------------------------------------------------------------------------------------#
+% % 
+% % #Comparison of SMD's:
+% % sig.d <- meta.f %>% mutate(d.fixef = est.d.fixef/se.est.d.fixef,
+% %                            d.ranef = est.d.ranef/se.est.d.ranef,
+% %                            d.reg = est.d.reg/se.est.d.reg,
+% %                            d.copas = est.d.copas/se.est.d.copas) %>%  
+% %   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+% %   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+% %   group_by(method) %>% 
+% %   summarise(significant = length(which(abs(smd) > 1.96)),
+% %             p.significant = significant/length(smd))
+% % sig.d <- data.frame(method = sig.d$method,
+% %                     label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
+% % 
+% % method_names <- c(
+% %   d.fixef = "Fixed Effects",
+% %   d.ranef = "Random Effects",
+% %   d.reg = "Regression",
+% %   d.copas = "Copas"
+% % )
+% % 
+% % adjustment.p.d <- meta.f %>% 
+% %   mutate(d.fixef = est.d.fixef/se.est.d.fixef,
+% %          d.ranef = est.d.ranef/se.est.d.ranef,
+% %          d.reg = est.d.reg/se.est.d.reg,
+% %          d.copas = est.d.copas/se.est.d.copas) %>%  
+% %   select(d.fixef, d.ranef, d.reg, d.copas) %>% 
+% %   gather(key = "method", value = "smd") %>% 
+% %   mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
+% %   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+% %   ggplot(aes(x = p.smd)) + 
+% %   geom_histogram(boundary = 0, bins = 20) + 
+% %   theme_bw() + 
+% %   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+% %   geom_text(data = sig.d, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
+% %   xlab(expression(paste(italic(p),"-value of test statistic of $z$-scores"))) +
+% %   ggtitle(expression(paste("$z$-score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+% % #--------------------------------------------------------------------------------------------------------------------#
+% % 
+% % #Comparison of log hazard ratios:
+% % sig.d <- meta.f %>% filter(outcome.flag == "IV") %>% 
+% %   mutate(d.fixef = est.fixef/se.est.fixef,
+% %          d.ranef = est.ranef/se.est.ranef,
+% %          d.reg = est.reg/se.est.reg,
+% %          d.copas = est.copas/se.est.copas) %>%  
+% %   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+% %   group_by(method) %>% 
+% %   summarise(significant = length(which(abs(smd) > 1.96)),
+% %             p.significant = (significant + sum(is.na(smd)))/(length(smd)))
+% % sig.d <- data.frame(method = sig.d$method,
+% %                     label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))
+% % 
+% % method_names <- c(
+% %   d.fixef = "Fixed Effects",
+% %   d.ranef = "Random Effects",
+% %   d.reg = "Regression",
+% %   d.copas = "Copas"
+% % )
+% % 
+% % adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.flag == "IV") %>% 
+% %   mutate(d.fixef = est.fixef/se.est.fixef,
+% %          d.ranef = est.ranef/se.est.ranef,
+% %          d.reg = est.reg/se.est.reg,
+% %          d.copas = est.copas/se.est.copas) %>%  
+% %   select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
+% %   mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
+% %   mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
+% %   ggplot(aes(x = p.smd)) + 
+% %   geom_histogram(boundary = 0, bins = 20) + 
+% %   theme_bw() + 
+% %   facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
+% %   geom_text(data = sig.d, aes(x = 0.5, y = 100, label = label), position = "dodge") + 
+% %   xlab(expression(paste(italic(p),"-value of test statistic of $z$-score"))) +
+% %   ggtitle(expression(paste("Log IV outcome measures ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
+% % #--------------------------------------------------------------------------------------------------------------------#
+% % 
+% % grid.arrange(adjustment.p.z,
+% %              adjustment.p.d,
+% %              adjustment.p.log.hazard.ratio, ncol = 1)
+% % @
+% % \caption{Histogram of the Wald test-statistic $p$-value of meta-analysis and adjusted combined treatment effect, based on different treatment effect measures.
 The method is indicated in the header, bin width is set to 0.05.
 The significant proportion based on the threshold of 0.05 is displayed inside the figures.}
-% \label{fig:adjustment.stat}
-% \end{figure}
+% % \label{fig:adjustment.stat}
+% % \end{figure}
+% 
+% 
+% 
+%

### 2019-08-20 code/analysis.R

@@ -19,7 +19,9 @@ source(file.path(PATH_CODE, 'PubBias_functions.R'))
 
 load(file.path(PATH_DATA, "PubBias_2019-07-19.RData"))
 load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
-# data.ext2 <- pb.process3(data)
+#data.ext2 <- pb.process3(data)
+
+set.seed(489579)
 
 
 #--------------------------------------------------------------------------------------------------------------------#
@@ -542,7 +544,7 @@ iv.results <- data.frame(
 # for(u in meta.id.vector.z.c){
 # 	counter <- counter + 1
 # 	print(c(u,counter))
-# 	meta.analyses[[counter]] <- metacor(cor = z, n = total1 + total2, studlab = study.name, tmp.z[tmp.z$meta.id == u,])
+# 	meta.analyses[[counter]] <- metagen(TE = z, seTE = sqrt(var.z), studlab = study.name, tmp.z[tmp.z$meta.id == u,])
 # 	meta.analyses.reg[[counter]] <- limitmeta(meta.analyses[[counter]])
 # 	meta.analyses.copas[[counter]] <- auto.copas(meta.analyses[[counter]], sig.level = 0.1)
 # }
@@ -717,19 +719,3 @@ save(meta.cont, file =  file.path(PATH_RESULTS, "meta.cont.RData"))
 save(meta.iv, file =  file.path(PATH_RESULTS, "meta.iv.RData"))
 save(meta.id.vector, file =  file.path(PATH_RESULTS, "meta_id_vector.RData"))
 save(data.ext2, file =  file.path(PATH_RESULTS, "data_used_for_analysis.RData")) #Save data used for analysis
-
-
-
-
-# x <- foreach(i = 1:length(meta.id.vector.bin)) %dopar% 
-#   # u <- meta.id.vector.bin[i]
-#   # counter <- counter + 1
-#   metabin(event.e = events1c, n.e = total1, event.c = events2c, n.c = total2,
-#           studlab = study.name, sm = "RR",
-#           method = "Inverse", data = data.ext2[data.ext2$meta.id == meta.id.vector.bin[i],])
-# 
-# cl<-makeCluster(7)
-# registerDoParallel(cl)
-# 
-# foreach(i = 1:length(meta.id.vector.bin)) %dopar%
-#   sqrt(i)

### 2019-08-21 Presentation copy/present.Rnw
Corrections

\documentclass[english]{beamer}
%% The most common packages are already included in:
\usetheme{biostat}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\usepackage{amsmath,amsfonts,tikz, amssymb}
\usetikzlibrary{trees}

%% Header data: (adjust to your needs:
\def\uzhunit{Biostatistics}             %% if (not) needed comment/uncomment
%\def\uzhunitext{STA480}

\title{Publication Bias in Cochrane Meta-Analyses}%[Publication Bias]
%% Optional Argument in [Brackets]: Short Title for Footline

%% The following are all optional, simply comment them
%\subtitle{Publication Bias in the Cochrane Libary}
%\institute{Biostatistics Journal Club}  %% optional
\author{Giuachin Kreiliger}
\date{\today}

\input{newCommands.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
<<include = FALSE, cache = TRUE>>= 
#Load data:
rm(list = ls())
library(knitr)
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2019-07-04.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH2, 'results_new')
# PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

source(file.path(PATH_CODE, 'PubBias_functions.R'))
require(corrgram)
require(nlme)

load(file.path(PATH_DATA, "PubBias_2019-07-19.RData"))
load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
load(file.path(PATH_RESULTS, "meta_id_I2.RData"))
load(file.path(PATH_RESULTS, "meta.bin.RData"))
load(file.path(PATH_RESULTS, "meta.cont.RData"))
load(file.path(PATH_RESULTS, "meta.iv.RData"))

#Inital dataset properties:
initial.id.count <- length(unique(data$id))
initial.study.count <- length(unique(data$study.name))
initial.result.count <- dim(data)[1]

#No withdrawn reviews:
tp7 <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) 
nowith.id.count <- length(unique(tp7$id))
nowith.study.count <- length(unique(tp7$study.name))
nowith.result.count <- dim(tp7)[1]

#Only efficacy outcomes:
tp8 <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
  filter(outcome.desired == "efficacy")
efficacy.id.count <- length(unique(tp8$id))
efficacy.study.count <- length(unique(tp8$study.name))
efficacy.result.count <- dim(tp8)[1]

#outcome.flag reduction:
tp.2 <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
  filter(outcome.flag == "IV") %>% 
  filter(!all(effect == 0)) %>% 
  filter(outcome.measure.merged == "Rate Ratio" | outcome.measure.merged == "SMD" |
           outcome.measure.merged == "MD" | outcome.measure.merged == "Hazard Ratio" |
           outcome.measure.merged == "OR" | outcome.measure.merged == "RR")
tp.1 <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
  filter(outcome.flag == "DICH" | outcome.flag == "CONT")
tp <- bind_rows(tp.1, tp.2)
flag.id.count <- length(unique(tp$id))
flag.study.count <- length(unique(tp$study.name))
flag.result.count <- dim(tp)[1]
#----------------------------------------------------------------------------------------------#

#Counts of meta-analyses with n larger ten:
m.a.largerten.bin <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
  filter(outcome.desired == "efficacy") %>% 
  filter(outcome.flag == "DICH") %>% 
  filter(total1 != 0 & total2 != 0) %>% 
  group_by(meta.id) %>% filter(n() > 9) %>%  filter(any(events1 != 0) | any(events2 != 0)) %>% 
  distinct(meta.id) %>% ungroup() %>% mutate(n = n())

m.a.largerten.cont <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
  filter(outcome.desired == "efficacy") %>% 
  filter(outcome.flag == "CONT") %>% 
  filter(sd1 != 0 & sd2 != 0) %>% 
  filter(total1 > 0 & total2 > 0) %>% group_by(meta.id) %>% 
  filter(n() > 9) %>% distinct(meta.id) %>% ungroup() %>% mutate(n = n())

m.a.largerten.iv <- data.ext2 %>% filter(id %in% data.review$id[which(data.review$withdrawn == FALSE)]) %>% 
  filter(outcome.desired == "efficacy") %>% 
  filter(outcome.flag == "IV") %>% 
  filter(!all(effect == 0)) %>% 
  filter(outcome.measure.merged == "Rate Ratio" | outcome.measure.merged == "SMD" |
           outcome.measure.merged == "MD" | outcome.measure.merged == "Hazard Ratio" |
           outcome.measure.merged == "OR" | outcome.measure.merged == "RR") %>% 
  filter(se != 0) %>% group_by(meta.id) %>% filter(n() > 9) %>% 
  distinct(meta.id) %>% ungroup() %>% mutate(n = n())

m.a.largerten.id <- rbind(m.a.largerten.bin, m.a.largerten.cont, m.a.largerten.iv)
tp2 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id)

ten.id.count <- length(unique(tp2$id))
ten.study.count <- length(unique(tp2$study.name))
ten.result.count <- dim(tp2)[1]
m.a.largerten.count <- unique(m.a.largerten.bin$n) + unique(m.a.largerten.cont$n) + unique(m.a.largerten.iv$n)

#----------------------------------------------------------------------------------------------#

#variance ratio > 4:
m.a.variance4.count <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
  group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
                                                  TRUE ~ se)) %>% 
  summarise(ratio = (max(se.new)^2)/(min(se.new)^2)) %>% 
  filter(ratio >= 4) %>% count
tp3 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
  group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
                                                  TRUE ~ se)) %>% 
  mutate(ratio = (max(se.new)^2)/(min(se.new)^2)) %>% 
  filter(ratio >= 4)
var.id.count <- length(unique(tp3$id))
var.study.count <- length(unique(tp3$study.name))
var.result.count <- dim(tp3)[1]

#At least on sig. estimate:
m.a.one.sig.count <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
  group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
                                                  TRUE ~ se)) %>% 
  summarise(ratio = (max(se.new)^2)/(min(se.new)^2),
                                  n.sig = sum(sig.single)) %>% 
  filter(ratio >= 4 & n.sig > 0) %>% count
tp4 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
  group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
                                                  TRUE ~ se)) %>% 
  mutate(ratio = (max(se.new)^2)/(min(se.new)^2),
                                  n.sig = sum(sig.single)) %>% 
  filter(ratio >= 4 & n.sig > 0)
sig.id.count <- length(unique(tp4$id))
sig.study.count <- length(unique(tp4$study.name))
sig.result.count <- dim(tp4)[1]

#Without duplicates:
m.a.no.dupl.number <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
  group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
                                                  TRUE ~ se)) %>% 
  summarise(ratio = (max(se.new)^2)/(min(se.new)^2),
                                  n.sig = sum(sig.single),
                                  dupl = unique(dupl.remove)) %>% 
  filter(ratio >= 4 & n.sig > 0 & dupl == 0) %>% count
tp5 <- data.ext2 %>% filter(meta.id %in% m.a.largerten.id$meta.id) %>% 
  group_by(meta.id) %>% mutate(se.new = case_when(outcome.flag == "DICH" ~ sqrt(var.lrr),
                                                  TRUE ~ se)) %>% 
  mutate(ratio = (max(se.new)^2)/(min(se.new)^2),
                                  n.sig = sum(sig.single),
                                  dupl = unique(dupl.remove)) %>% 
  filter(ratio >= 4 & n.sig > 0 & dupl == 0)
dupl.id.count <- length(unique(tp5$id))
dupl.study.count <- length(unique(tp5$study.name))
dupl.result.count <- dim(tp5)[1]

#smaller I2 than 0.5:
m.a.smaller.5.count <- meta.info.I2 %>% filter(I2 < 50) %>% ungroup %>% count()

meta.id.vector <- meta.info.I2 %>% filter(I2 < 50) %>% select(meta.id)
meta.data <- data.ext2 %>% filter(meta.id %in% meta.id.vector$meta.id)

I2.id.count <- length(unique(meta.data$id))
I2.study.count <- length(unique(meta.data$study.name))
I2.result.count <- dim(meta.data)[1]
#----------------------------------------------------------------------------------------------#

#Adjustment dataset:
meta.adj.2 <- meta.f %>% filter(outcome.flag == "IV") %>%
  filter(outcome.measure.merged == "SMD")
meta.adj.1 <- meta.f %>% filter(outcome.flag == "DICH" | outcome.flag == "CONT") 
meta.adj <- bind_rows(meta.adj.2, meta.adj.1)
tp6 <- data.ext2 %>% filter(meta.id %in% meta.adj$meta.id)

adj.id.count <- length(unique(tp6$id))
adj.study.count <- length(unique(tp6$study.name))
adj.result.count <- dim(tp6)[1]
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{document}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Publication Bias}
\begin{itemize}
\item Preference of journal editors to publish significant study results
\end{itemize}
\hspace{2mm} $\rightarrow$ \hspace{2mm} non-significant results remain in file-drawer
\end{frame}

\begin{frame}{Systematic Reviews}
\begin{itemize}
\item Summarise all evidence with regard to treatment with meta-analysis
\item Biased if non-significant results are not available and included
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Funnel Plot}
Look for funnel plot asymmetry:

\vspace{-5mm}
\begin{figure}
<<echo = FALSE, fig.height = 4, warning=FALSE, cache = TRUE>>=
ex.se <- meta.f$meta.id[which(meta.f$id == "CD003246" & meta.f$subgroup.nr == 0
                              & meta.f$outcome.nr == 3 & meta.f$comparison.nr == 9)]
ex.nose <- meta.f$meta.id[which(meta.f$id == "CD000213" & meta.f$subgroup.nr == 1
                              & meta.f$outcome.nr == 15 & meta.f$comparison.nr == 1)]
par(mfrow = c(1,2))
funnel(x = meta.id(ex.se), ylim = c(1.60, 0), comb.fixed = F, comb.random = F)
funnel(x = meta.id(ex.nose), ylim = c(1.60, 0), comb.fixed = F, comb.random = F, ylab = NULL)
@
\end{figure}

\end{frame}

\begin{frame}[fragile]{Funnel Plot}
Effects with large standard errors have larger effect sizes (because they are only published
if significant)

\vspace{-10mm}
\begin{figure}
<<echo = FALSE, fig.height = 4, warning=FALSE, cache = TRUE>>=
par(mfrow = c(1,2))
funnel(x = meta.id(ex.se), ylim = c(1.60, 0), comb.fixed = F, comb.random = F, contour.levels = 0.975)
funnel(x = meta.id(ex.nose), ylim = c(1.60, 0), comb.fixed = F, comb.random = F, ylab = NULL)
@
\end{figure}
\end{frame}

\begin{frame}{Detect Publication Bias}
\begin{itemize}
\item Small study effect tests (funnel plot asymmetry)
\item Excess significance tests
\end{itemize}
\end{frame}

\begin{frame}{Excess Significance Test}
Calculate power of each study, given that true effect size is
fixed effects meta-analysis estimate.

Calculate:
\begin{align}
p &= \sum_{i = O}^n\Big({n \choose i} p^i (1-p)^{n - i}\Big) \nonumber
\end{align}

\vspace{-1mm}
$O = $ observed no. of significant results, $E$ expected based on power of studies.
\end{frame}

\begin{frame}{Analysis}
\begin{itemize}
\item Use meta-analyses from Cochrane.
\item ``The single most reliable source of evidence in clinical science
\end{itemize}

Analyse meta-analyses with publication bias tests.
\end{frame}

%------------------------------------------------------------------------------------------------%
\begin{frame}{The Cochrane Dataset}
\small
\begin{figure}
\begin{center}
\tikzstyle{block} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=2.3em]
\tikzstyle{btw} = [rectangle, node distance=0cm, minimum height =1.8em, fill= white]
\tikzstyle{ublock} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=4em, text width = 10em]
\tikzstyle{line} = [draw, ->, thick]
\tikzstyle{final} = [rectangle, draw, fill=red!20, text centered, rounded corners, minimum height=2.8em]

\begin{tikzpicture}[node distance = 2cm, auto]

        \node [final] (1) {Inital dataset:
    \Sexpr{format(initial.id.count, big.mark = ",")} reviews,
    \Sexpr{format(initial.study.count, big.mark = ",")} studies,
    \Sexpr{format(initial.result.count, big.mark = ",")} results};

    \node [final, below of=1, node distance=2cm] (7) {Analysis dataset: 
    \Sexpr{format(I2.id.count, big.mark = ",")} reviews,
    \Sexpr{format(I2.study.count, big.mark = ",")} studies,
    \Sexpr{format(I2.result.count, big.mark = ",")} results};

    \path [line] (1) -- node [btw, xshift = -2.8cm] {exclusion of unsuitable meta-analyses} (7);
\end{tikzpicture}
\label{Inclusion.criteria}
\end{center}
\end{figure}
\end{frame}

\begin{frame}{The Analysis dataset}
\footnotesize
\begin{figure}
\begin{center}
\tikzstyle{block} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=2.3em]
\tikzstyle{btw} = [rectangle, node distance=0cm, minimum height =1.8em, fill= white]
\tikzstyle{ublock} = [rectangle, draw, fill=blue!20, text centered, rounded corners, minimum height=4em, text width = 10em]
\tikzstyle{line} = [draw, ->, thick]
\tikzstyle{final} = [rectangle, draw, fill=red!20, text centered, rounded corners, minimum height=2.8em]

\begin{tikzpicture}[node distance = 2cm, auto]

    \node [final, node distance=1cm] (7) {Analysis dataset:
    \Sexpr{format(m.a.smaller.5.count$nn, big.mark = ",")} meta-analyses};

    \node [ublock, below of=7, node distance=3.5cm] (8) {Binary data: \\
    \Sexpr{format(dim(meta.bin)[1], big.mark = ",")} meta-analyses};

    \node [ublock, right of=8, node distance=3.5cm] (9) {Continuous data: \\
    \Sexpr{format(dim(meta.cont)[1], big.mark = ",")} meta-analyses};

    \node [ublock, left of=8, node distance=3.5cm] (10) {Other data (IV): \\
    \Sexpr{format(dim(meta.iv[1])[1], big.mark = ",")} meta-analyses};

    \path [line] (7) -- (8);
    \path [line] (7) --  (9);
    \path [line] (7) --  (10);

\end{tikzpicture}

\end{center}
\end{figure}
\end{frame}

\begin{frame}{Small Study Effect Tests}
\vspace{-4mm}
Weighted linear regression with std. error $x_i$ and effect size $y_i$:
\begin{align}
y_i &= \beta_0 + \beta_1 x_i + \epsilon, & \epsilon \sim N(0, x_i \sigma^2) \nonumber
\end{align}
Test for $H0: \beta_1 = 0$, no funnel plot asymmetry
\end{frame}

\begin{frame}{Adjustments for Binary Data}
As recommended by \citet{Sterne}
\begin{itemize}
\item Log odds ratio and risk ratio $\theta$ and standard error $\se_\theta$ are not independent
\item Use score of binomial likelihood at log odds ratio $\theta_{\textrm{H0}} = 0$ instead of 
log odds ratio and the inverse Fisher information instead of $\se_\theta$
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Small Study Effect Tests}
\begin{figure}
<<echo = FALSE, warnings = FALSE, cache = TRUE, fig.height = 4>>=
dat_text <- data.frame(
  label = paste(sum(meta.bin$harbord.test), "< 0.1,",
                round(mean(meta.bin$harbord.test),2)*100, "%"))
p.dist.bin <- meta.bin%>% 
  ggplot(aes(x = pval1.harbord)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 125, label = label), 
  					color = "red", size = 4.5) + 
  ggtitle("Binary data (Harbord)") + 
	xlab(expression(paste(italic(p), "-value"))) + theme(
        plot.title = element_text(hjust = 0.5, face = "bold", size = 12, margin = margin(b = 20)),
        axis.title.y = element_text(size=16, margin = margin(r = 10)), 
        axis.title.x = element_text(size=16, margin = margin(t = 10)), 
        axis.text= element_text(size=12),
        strip.text.x = element_text(size = 30))

dat_text <- data.frame(
  label = paste(sum(meta.cont$egger.test), "< 0.1,", round(mean(meta.cont$egger.test),2)*100, "%"))

p.dist.cont <- meta.cont %>% 
  ggplot(aes(x = pval1.egger)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 63, label = label),  
  					color = "red", size = 4.5) + 
  ggtitle("Cont. Data (Egger)") + ylab("") + 
	xlab(expression(paste(italic(p), "-value"))) + theme(
        plot.title = element_text(hjust = 0.5, face = "bold", size = 12, margin = margin(b = 20)),
        #axis.title.y = element_text(size=16, margin = margin(r = 10)), 
        axis.title.x = element_text(size=16, margin = margin(t = 10)), 
        axis.text= element_text(size=12),
        strip.text.x = element_text(size = 30))

dat_text <- data.frame(
  label = paste(sum(meta.iv$egger.test), "< 0.1,", round(mean(meta.iv$egger.test),2)*100, "%"))

p.dist.iv <- meta.iv %>%  ggplot(aes(x = pval1.egger)) + 
	geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 24.5, label = label),  
  					color = "red", size = 4.5) + 
  ggtitle("Other Data (Egger)") + ylab("") +
	xlab(expression(paste(italic(p), "-value")))  + theme(
        plot.title = element_text(hjust = 0.5, face = "bold", size = 12, margin = margin(b = 20)),
        #axis.title.y = element_text(size=16, margin = margin(r = 10)), 
        axis.title.x = element_text(size=16, margin = margin(t = 10)), 
        axis.text= element_text(size=12),
        strip.text.x = element_text(size = 30))

grid.arrange(p.dist.bin, p.dist.cont, p.dist.iv, ncol = 3)
@
\end{figure}
\end{frame}

\begin{frame}[fragile]{Excess Significance Test}
\begin{figure}
<<echo = FALSE, cache = TRUE, fig.height = 4>>=
dat_text <- data.frame(
  label = paste(sum(meta.f$tes.d.test), "< 0.1,", round(mean(meta.iv$tes.d.test),2)*100, "%"))

meta.f %>% ggplot(aes(x = pval1.d.tes)) +  
	geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
  ggtitle("All Data") +
  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 100, label = label),  
  					color = "red", size = 5.5) + 
	xlab(expression(paste(italic(p), "-value")))  + theme(
        plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 20)),
        axis.title.y = element_text(size=16, margin = margin(r = 10)), 
        axis.title.x = element_text(size=16, margin = margin(t = 10)), 
        axis.text= element_text(size=12),
        strip.text.x = element_text(size = 30))

@
\end{figure}
\end{frame}

% 
% \begin{frame}{Fixed Effects Meta-Analysis}
% Study $i$ of $n$ studies, effects $\theta_i$ and variances $v_i$, s.e. $s_i$
% 
% Fixed effects estimate: weighted mean with $w_i = 1/\hat{v_i}$: 
% 
% \begin{align}
% \theta_f &= \frac{\sum_{i = 1}^n w_{i}\theta_i}{\sum_{i = 1}^n w_i} \nonumber \\ 
% \textrm{se}(\theta_f) &= \frac{1}{\sqrt{\sum_{i = 1}^n w_i}} \nonumber
% \end{align}
% \end{frame}
% 
% \begin{frame}{Random Effects Meta-Analysis}
% Let $\hat{\theta_i}|\theta_i \sim N(\theta_i, v_i) 
% \theta_i \sim N(\theta, \tau^2)$
% 
% Random effects estimate: weigthed mean of $\hat{\theta_i}$ with weights $w_i = 1/(\hat{v_i} + \tau^2)$
% \end{frame}
% 
% \begin{frame}{Evidence Based Medicine}
% Likely to base decisions on over-optimistic findings
% 
% Direct consequences: patient harm and unnecessary research
% \end{frame}
% 
% 
% \begin{frame}{Cochrane Organisation}
% Aim: summarise findings in primary clinical research and health care
% 
% Provide peer-reviewed, systematic reviews
% 
% Public access (for some countries)
% \end{frame}
% 
% \begin{frame}{Research Question}
% Quantify the abundance and impact of publication bias in the Cochrane Library
% \end{frame}
% 
% 
% \begin{frame}{Cochrane Library Dataset}
% \Sexpr{format(length(unique(data$file.nr)), big.mark=",")} systematic reviews with studies published until 2018.
% 
% \Sexpr{format(length(unique(data$study.name)), big.mark=",")} studies.
% 
% \Sexpr{format(dim(data)[1], big.mark=",")} study results.
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Review Example: Binary Outcome}
% Barbiturate efficacy for head injury treatment
% \vspace{-5mm}
% <<echo = FALSE, results = 'asis'>>=
% print(xtable(barbi2, label = "barbiturates", digits = 0), include.rownames = F, size = "tiny")
% @
% \end{frame}
% 
% 
% 
% \begin{frame}{Dataset Structure}
% 
% \begin{figure}
% \tikzstyle{every node}=[draw=black,thick,anchor=west,scale=.65]
% \tikzstyle{selected}=[draw=red,fill=red!30]
% \tikzstyle{optional}=[dashed,fill=gray!50]
% \begin{tikzpicture}
% [grow = right, anchor = west,
%   growth parent anchor=east, % added code
%   parent anchor=east, level distance=.5cm,
%   sibling distance=2em, level 1/.style={sibling distance=2em}, level 2/.style={sibling distance=2em},
%   level 3/.style={sibling distance=2em}, level 4/.style={sibling distance=1.2em}]
%   \node {Review} [edge from parent fork right]
%     child { node {Comparison 2}
%       child { node {Outcome 2}}
%       child { node {Outcome 1}
%         child { node {Subgroup 2}}
%         child { node {Subgroup 1}
%           child  { node {Result 3}}
%           child  { node {Result 2}}
%           child  { node {Result 1}}
%           }}
%     }
%     child [missing] {}
%     child { node {Comparison 1}};
% \end{tikzpicture}
% %\caption{Structure of a hypothetical review with two different comparisons\label{review.structure}}
% \label{review.structure}
% \end{figure}
% \end{frame}
% 
% 
% 
% 
% 
% \begin{frame}[fragile]{Dataset Properties}
% Review or study level:
% <<echo=FALSE, results = 'asis'>>=
% print(xtable(dataset.properties, digits = 0, align = "lrrrr"), include.rownames = T, size = "footnotesize", hline = c(0,1,1,3))
% @
% \end{frame}
% 
% 
% 
% \begin{frame}{Small Study Effects}
% ``The tendency for the smaller studies to show larger treatment effects'' \citep{Sterne}
% \end{frame}
% 
% 
% \begin{frame}{Small Study Effects}
% Causes:
% \begin{itemize}
% \item Selective publication of studies with significant results - publication bias
% \item Systematic differences in study settings
% \end{itemize}
% \end{frame}
% 
% 
% \begin{frame}{Small Study Effect Tests}
% Different approaches:
% \begin{itemize}
% \item Simple linear regression
% \item Rank correlation
% \end{itemize}
% 
% Special methods for binary outcomes	
% \end{frame}
% 
% 
% % \begin{frame}[fragile]{Small Study Effect Tests}
% % Funnel plots (continuous outcome examples):
% % 
% % \vspace{-1.2cm}
% % 
% % <<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
% % par(las = 1, mfrow = c(1, 2))
% % funnel(meta.example)
% % funnel(meta.nexample)
% % @
% % 
% % \end{frame}
% % 
% % 
% % \begin{frame}[fragile]{Regression based Tests}
% % Radial plots (continuous outcome examples):
% % 
% % \vspace{-1.1cm}
% % 
% % <<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
% % par(las = 1, mfrow = c(1,2))
% % biased.rev$inv <- 1/biased.rev$se
% % plot(y = (biased.rev$effect/biased.rev$se), x = (biased.rev$se^-1), xlim = c(0, 6), xlab = "inverse standard error", 
% % 		 ylab = "mean diff. / std. error")
% % 
% % unbiased.rev$inv <- 1/unbiased.rev$se
% % plot(y = (unbiased.rev$effect/unbiased.rev$se), x = (unbiased.rev$inv), xlim = c(0, 1.2), 
% % 		 ylim = c(-18, 0), xlab = "inverse standard error", ylab = "mean diff. / std. error")
% % @
% % 
% % \end{frame}
% 
% 
% \begin{frame}{Regression based Tests}
% study $i$ of $n$ studies, effects $\theta_i$ and variances $v_i$, s.e. $s_i$
% 
% $\theta_M$ is the pooled effect and $\tau^2$ the between-study variance.
% 
% Let $y_{i} = \theta_{i}/_{i}$ and $x_i = 1/s_i$
% \begin{itemize}
% \item \citet{Egger} : Simple linear regression \\ $y_i = \beta_0 + \beta_1 x_i, \epsilon_i \sim N(0, \sigma)$
% \item \citet{thompson.sharp} : extension of Egger with study weights $v_{i} + \tau^2$ 
% \end{itemize}
% 
% \end{frame}
% 
% \begin{frame}[fragile]{Egger's Test examples}
% Test for non-zero intercept $\beta_{0}$
% 
% \vspace{-1.1cm}
% <<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
% par(las = 1, mfrow = c(1,2))
% biased.rev$inv <- 1/biased.rev$se
% m.ex <- lm(formula = (biased.rev$effect/biased.rev$se) ~ (biased.rev$inv))
% plot(y = (biased.rev$effect/biased.rev$se), x = (biased.rev$se^-1), xlim = c(0, 6), xlab = "inverse standard error", 
% 		 ylab = "mean diff. / std. error")
% abline(coef = coef(m.ex), lty = 2, col = 2)
% 
% 
% unbiased.rev$inv <- 1/unbiased.rev$se
% m.nex <- lm(formula = (unbiased.rev$effect/unbiased.rev$se) ~ (unbiased.rev$inv))
% plot(y = (unbiased.rev$effect/unbiased.rev$se), x = (unbiased.rev$inv), xlim = c(0, 1.2), 
% 		 ylim = c(-18, 0), xlab = "inverse standard error", ylab = "mean diff. / std. error")
% abline(coef = coef(m.nex), lty = 2, col = 2)
% @
% \end{frame}
% 
% 
% \begin{frame}{Regression Tests for Binary Outcomes}
% 
% \begin{itemize}
% \item \citet{Peters} :$x_i = 1/n_i$ instead $1/s_i$, inverse variances as weight.
% \item \citet{Harbord} :$x_i$ = score of the log-likelihood of a proportion and inverse variances as weights.
% \item \citet{Rucker} :Use arcsine variance stabilizing transformation for variances and effects, do e.g. Egger's test.
% \end{itemize}
% \end{frame}
% 
% 
% \begin{frame}{Rank based tests}
% \citet{begg.ties}: \\
% Let $y_{i}$ be $\frac{\theta_i - \theta_M}{v_i}$ and $x_i$ its variance ($\neq v_i$)
% 
% $u$ the number of pairs $(y_{i}, x_{i})$ ranked in the same order, $l$
% the number of pairs in the opposite order
% 
% $Z = \frac{(u - l)}{\sqrt{n(n-1)(2n + 5)/18}}$  is a test statistic
% \end{frame}
% 
% \begin{frame}{Rank based tests}
% \citet{Schwarzer}: \\
% $e_t$ number of events in the treatment group
% 
% $E_t$ follows hypergeometric distribution: calculate $\mathbb{E}(E_{t})$ and variances
% 
% proceed as in \citet{begg.ties}
% \end{frame}
% 
% 
% \begin{frame}{Test Results}
% Inclusion criteria (from \citet{Ioannidis2007}):
% \begin{itemize}
% \item $n \geq 10$
% \item at least one statistically significant effect in a study
% \item $\frac{\hat{v_{\textrm{max}}}^2}{\hat{v_{\textrm{min}}}^2} > 4$
% \item $I^2 < 0.5$
% \end{itemize}
% 
% From \Sexpr{dim(meta)[1]} with $n \geq 10$, \Sexpr{dim(meta.f)[1]} remain.
% \end{frame}
% 
% 
% 
% \begin{frame}[fragile]{Continuous Outcome Test Results}
% $p$-values distribution, $n$ = \Sexpr{dim(meta.cont)[1]}:
% 
% \vspace{-2mm}
% <<echo = FALSE, fig.height = 4, message = FALSE>>=
% plot(p.dist.cont)
% @
% \end{frame}
% 
% \begin{frame}[fragile]{Binary Outcome Test Results}
% $p$-values distribution, $n$ = \Sexpr{dim(meta.bin)[1]}:
% 
% \vspace{-2mm}
% <<echo = FALSE, fig.height = 3.6, message = FALSE>>=
% plot(p.dist.bin)
% @
% \end{frame}
% 
% \begin{frame}[fragile]{Agreement in significance}
% Number of significant test results per meta-analysis:
% 
% \vspace{-2mm}
% <<echo = FALSE, fig.height = 3.2, message = FALSE>>=
% grid.arrange(agree.cont, agree.bin, ncol = 2)
% @
% \end{frame}
% 
% \begin{frame}{Small Study Effect Adjustment}
% Three methods:
% \begin{itemize}
% \item Regression
% \item Copas selection model
% \item Trim-and-fill
% \end{itemize}
% \end{frame}
% 
% \begin{frame}{Adjustment by regression}
% $y_i = \theta_i/s_i, x_i = 1/s_i$
% 
% $y_i = \beta_0 + \beta_1 x_i, \epsilon_i \sim N(0, \sigma)$
% 
% $\beta_1$ is the weighted mean treatment effect if $\beta_0 = 0$
% \end{frame}
% 
% 
% \begin{frame}{Adjustment by regression}
% Radial plots (continuous outcome examples):
% 
% \vspace{-1.1cm}
% 
% <<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
% par(las = 1, mfrow = c(1,2))
% biased.rev$inv <- 1/biased.rev$se
% m.ex.0 <- lm(formula = (biased.rev$effect/biased.rev$se) ~ 0 + (biased.rev$inv))
% m.ex <- lm(formula = (biased.rev$effect/biased.rev$se) ~ (biased.rev$inv))
% plot(y = (biased.rev$effect/biased.rev$se), x = (biased.rev$se^-1), xlim = c(0, 6), xlab = "inverse standard error", 
% 		 ylab = "mean diff. / std. error")
% abline(coef = c(0,coef(m.ex.0)), lty = 2)
% abline(coef = coef(m.ex), lty = 2, col = 2)
% 
% 
% unbiased.rev$inv <- 1/unbiased.rev$se
% m.nex.0 <- lm(formula = (unbiased.rev$effect/unbiased.rev$se) ~ 0 + (unbiased.rev$inv))
% m.nex <- lm(formula = (unbiased.rev$effect/unbiased.rev$se) ~ (unbiased.rev$inv))
% plot(y = (unbiased.rev$effect/unbiased.rev$se), x = (unbiased.rev$inv), xlim = c(0, 1), 
% 		 ylim = c(-18, 0), xlab = "inverse standard error", ylab = "mean diff. / std. error")
% abline(coef = c(0,coef(m.nex.0)), lty = 2)
% abline(coef = coef(m.nex), lty = 2, col = 2)
% @
% \end{frame}
% 
% 
% 
% \begin{frame}[fragile]{Limit Meta-Analysis}
% Extended random effects model:
% 
% \vspace{-4mm}
% \begin{align}
% \theta_i = \beta_0 + \beta_1(\sqrt{v_i + \tau^2}) + \epsilon_i(\sqrt{v_i + \tau^2}), \nonumber \\
% \epsilon_{i} \stackrel{\textrm{iid}}{\sim} N(0,1) \nonumber
% \end{align}
% 
% Use $\mathbb{E}(\theta_{i}) \rightarrow \beta_{0} + \beta_{1}\tau$ for $\sqrt{v_{i}} \rightarrow 0$
% as corrected treatment efffect.
% \end{frame}
% 
% 
% 
% \begin{frame}[fragile]{Limit Meta-Analysis}
% Funnel plot with effect with infinite precision:
% 
% \vspace{-1.1cm}
% <<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
% par(las = 1, mfrow = c(1,2))
% funnel(limitmeta(meta.example))
% funnel(limitmeta(meta.nexample))
% @
% \end{frame}
% 
% 
% 
% \begin{frame}{Selection model}
% \citet{Copas1}: model based on a bivariate normal distribution:
% 
% \vspace{-8mm}
% \begin{align}
% \hat{\theta_i} = \theta_{i} + \sigma_i\epsilon_i \label{population.model2} \\
% \theta_i \sim N(\theta, \tau^2) \label{population.model} \\
% z_i = a + b/\hat{s_i} + \delta_i \label{selection.model}
% \end{align}
% 
% \ref{population.model2},\ref{population.model} is called population model, \ref{selection.model} the selection model
% 
% $(\epsilon_i, \delta_i)$ are standard normal residuals with correlation $\rho = cor(y_i, z_i)$.
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Sensitivity Analysis}
% Model the selection process with different $a,b$
% 
% Test if small study effect is significant, by including \\ $\theta_i = \theta_i + \beta s_i + v_{i}\epsilon_i$
% 
% Estimation: Select $a, b$ such that $H0$ can not be rejected and estimated
% number of unpublished studies is minimal.
% \end{frame}
% 
% 
% \begin{frame}{Trim-and-Fill}
% Mirror studies that cause asymmetry:
% \vspace{-1.2cm}
% 
% <<message = FALSE, echo=FALSE, warning = FALSE, fig.height=4>>=
% par(las = 1, mfrow = c(1, 2))
% funnel(meta.example)
% funnel(meta.nexample)
% @
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Results:}
% Difference between random and fixed effects meta-analysis estimate: $|\theta_f - \theta_{r}|$
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 3.6, message = FALSE, warning=FALSE>>=
% plot(hist.ranef)
% @
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Adjustment Results: Trim-and-fill}
% Absolute difference between adjusted and fixed effects meta-analysis estimate: $|{\theta_f} - {\theta_{\textrm{adjusted}}}|$
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 3.6, message = FALSE, warning=FALSE>>=
% plot(hist.trimfill1)
% @
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Adjustment Results: Copas}
% Absolute difference between adjusted and fixed effects meta-analysis estimate: $|{\theta_f} - {\theta_{\textrm{adjusted}}}|$
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 3.6, message = FALSE, warning=FALSE>>=
% plot(hist.copas1)
% @
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Adjustment Results: Regression}
% Absolute difference between adjusted and fixed effects meta-analysis estimate: $|{\theta_f} - {\theta_{\textrm{adjusted}}}|$
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 3.6, message = FALSE, warning=FALSE>>=
% plot(hist.reg1)
% @
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Results:}
% Random and fixed effects meta-analyses test statistics:
% 
% \vspace{-3mm} 
% <<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
% plot(ranef.fixef.sc.zval)
% @
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Adjustment Results: Trim-and-fill}
% Adjusted and meta-analysis test statistics:
% 
% \vspace{-3mm} 
% <<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
% grid.arrange(trimfill.fixef.sc.zval, trimfill.ranef.sc.zval, ncol = 2)
% @
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Adjustment Results: Copas}
% Adjusted and meta-analysis test statistics:
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
% grid.arrange(copas.fixef.sc.zval, copas.ranef.sc.zval, ncol = 2)
% @
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Adjustment Results: Regression}
% Adjusted and meta-analysis test statistics:
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
% grid.arrange(reg.fixef.sc.zval, reg.ranef.sc.zval, ncol = 2)
% @
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Adjustment Results}
% Missing study proportions:
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 3.8, message = FALSE, warning=FALSE>>=
% grid.arrange(p.missing.copas, p.missing.trim, ncol = 2) 
% @
% \end{frame}
% 
% \begin{frame}[fragile]{Extreme Results}
% RR reduction by trimfill (-3.9), side effects
% 
% <<echo = FALSE, fig.height = 3.5>>=
% trimfill.id(165815)
% @
% \end{frame}
% 
% \begin{frame}[fragile]{Extreme Results}
% RR Reduction by copas selection model (-4), pain relief
% 
% <<echo = FALSE, fig.height = 3.5>>=
% funnel.id(73169)
% @
% \end{frame}
% 
% \begin{frame}[fragile]{Extreme Results}
% RR Amplification by regression (+14), side effects
% 
% <<echo = FALSE, fig.height = 3.5, warning=FALSE>>=
% limitmeta.id(119537)
% @
% \end{frame}
% 
% \begin{frame}[fragile]{Discussion}
% \begin{itemize}
% \item Proportion of positive tests is well above 10\%
% \item Effect sizes and evidence for treatment effect is diminishued
% \item Limitations: not only primary outcomes, adjustment methods known to
% perform poorly under the 0
% \end{itemize}
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Outlook}
% \begin{itemize}
% \item Connect results with different medical fields, look for differences
% \item Connect results with single studies and journals (?)
% \end{itemize}
% \end{frame}
% 
% 
% 
% 
% 
% 
% 
% 
% 
% 
% 
% 
% 
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %Backup Slides%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% \begin{frame}[fragile]{Adjustment Results: Trim-and-fill}
% Treatment effect difference:
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
% plot(hist.trimfill)
% @
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Adjustment Results: Copas}
% Treatment effect difference:
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
% plot(hist.copas)
% @
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Adjustment Results: Regression}
% Treatment effect difference:
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
% plot(hist.reg)
% @
% \end{frame}
% 
% \begin{frame}[fragile]{Results}
% log treatment effect estimates:
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
% plot(ranef.fixef.sc.effect)
% @
% \end{frame}
% 
% \begin{frame}[fragile]{Adjustment Results: Trim-and-fill}
% log treatment effect estimates:
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
% grid.arrange(trimfill.fixef.sc.effect, trimfill.ranef.sc.effect, ncol = 2)
% @
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Adjustment Results: Copas}
% log treatment effect estimates:
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
% grid.arrange(copas.fixef.sc.effect, copas.ranef.sc.effect, ncol = 2)
% @
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Adjustment Results: Regression}
% log treatment effect estimates:
% 
% \vspace{-3mm}
% <<echo = FALSE, fig.height = 4, message = FALSE, warning=FALSE>>=
% grid.arrange(reg.fixef.sc.effect, reg.ranef.sc.effect, ncol = 2)
% @
% \end{frame}
% 
% 
% 
%

\begin{frame}{References}
  \small
  \bibliographystyle{apalike}
\bibliography{illustration}
\end{frame}

%\appendix
%% Possible backup slides...

%% chapter division is accomplished with:
%% \part{Appendix}

% \begin{frame}[fragile]{Test Results: Significance}
% 
% <<echo = FALSE, fig.height = 4>>=
% grid.arrange(p.bin, p.cont, ncol = 2)
% @
% \end{frame}

% \begin{frame}[fragile]{Pooling Studies - Meta-Analysis}
% Multiple results in a meta-analysis group can be pooled:
% <<echo=FALSE, results = 'asis'>>=
% print(xtable(cum.repr.trials.subg, label = "repr.groups", align = "lrrr", digits = 0), include.rownames = F, size = "footnotesize")
% @
% \end{frame}

% \begin{frame}{Dataset Structure}
% \begin{itemize}
% \item Comparison: What is compared, e.g. treatment vs. control
% \item Outcome: How it is compared
% \item Subgroup: Subgroup affiliation
% \item Meta-Analysis Group: Results from same comparison, outcome and subgroup
% \end{itemize}
% \end{frame}

% \begin{frame}[fragile]{Dataset Properties}
% Missing data:
% <<echo=FALSE, results = 'asis'>>=
% print(xtable(missing.table, align = "lr"), include.rownames = T, include.colnames = F)
% @
% \end{frame}

% \begin{frame}{Adjustment by regression}
% Similar to the tests, but with unnormalized effect $y_{i}$:
% 
% \begin{align}
% y_{i} = \beta_{0} + \beta_{1}x_{i}
% \end{align}
% 
% $\beta_{0}$	 corresponds to $y_{i}$ with $x_{i} = 0$
% \end{frame}
% 
% \begin{frame}[fragile]{Adjustment by regression}
% Linear regression method:
% 
% <<echo = FALSE, fig.height = 3>>=
% grid.arrange(reg.1, reg.2, ncol = 2)
% @
% \end{frame}

% \begin{frame}[fragile]{Thompson and Sharp's Tests}
% Generalised radial plot with new standard error $x_i = s_i + \tau$
% 
% \vspace{-1.1cm}
% <<message = FALSE, echo=FALSE, warning = FALSE, fig.height= 4>>=
% par(las = 1, mfrow = c(1,2))
% tau.ex <- meta.example$tau
% biased.rev$inv <- 1/sqrt((biased.rev$se^2 + tau.ex^2))
% m.ex <- lm(formula = (biased.rev$effect*biased.rev$inv) ~ (biased.rev$inv), weights = biased.rev$se)
% biased.rev$inv <- 1/biased.rev$se
% plot(y = (biased.rev$effect/biased.rev$se), x = (biased.rev$inv), xlim = c(0, 4), xlab = "inverse standard error", 
% 		 ylab = "mean diff. / std. error")
% abline(coef = coef(m.ex), lty = 2, col = 2)
% 
% tau.nex <- meta.nexample$tau
% unbiased.rev$inv <- 1/sqrt((unbiased.rev$se^2 + tau.nex^2))
% m.nex <- lm(formula = (unbiased.rev$effect*unbiased.rev$inv) ~ (unbiased.rev$inv), weights = unbiased.rev$se)
% plot(y = (unbiased.rev$effect/unbiased.rev$se), x = (unbiased.rev$inv), xlim = c(0, .6), 
% 		 ylim = c(-18, 0), xlab = "inverse standard error", ylab = "mean diff. / std. error")
% abline(coef = coef(m.nex), lty = 2, col = 2)
% @
% 
% \end{frame}
% 
% 
% \begin{frame}[fragile]{Limit Meta-Analysis}
% \begin{align}
% y_{M,i} &= \beta_{0} + \beta_{1}(\sqrt{v_{i}/M + \tau^2}) + \epsilon_{i}(\sqrt{s_{i}/M + \tau^2}) \nonumber
% \end{align}
% 
% Letting $M \rightarrow \infty$ and substituting for all parameters and the observed residual
% 
% \vspace{-8mm}
% \begin{align}
% y_{\infty,i} &= \beta_{0} + \sqrt{\frac{\tau^2}{v_{i} + \tau^2}}(y_i - \beta_0)
% \end{align}
% \end{frame}
% 
% \begin{frame}[fragile]{Limit Meta-Analysis}
% By plugging in $s_i$ for $v_i$, $\hat{tau}$ for $\tau$ and $\hat{\beta_0}$, get new study effects:
% 
% Three different treatment effect estimates:
% \begin{itemize}
% \item Expectated adjusted treatment effect with infinite precision: $\hat{\beta_{0}^\star} + \hat{\beta_{1}}\hat{\tau}$
% \item Fixed effect estimate based on $(y_{\infty,1},.. , y_{\infty,n}$
% \item Slope $\beta_{\textrm{lim}}$ of best-fitting regression line in radial plot with $(y_{\infty,i}, s_{i})$
% \end{itemize}
% \end{frame}

\end{document}

### 2019-08-21 report/MSc_Report.tex
Corrections

@@
 \subsection{Harbord's Test: Score based Test} \label{sec:Harbord}
-A rank based alternative to Peters test for binary outcomes is Harbord's test \citep{Harbord}.
-It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated as log odds ratio $\theta_\textrm{H0} = 0$ and its inverse Fisher information $s^2$.
+An alternative to Peters test for binary outcomes is Harbord's test \citep{Harbord}.
+It uses a different treatment effect and variance estimate: the score $\varphi$ of the log-likelihood, evaluated as log odds ratio $\theta_\textrm{H0} = 0$ and its inverse Fisher information $\se^2$.
 Formally,
@@
 \begin{align}
-\varphi &= e_t - (e_t - e_c)(e_t + (n_t - e_t))/(n_t + n_c) \label{harbord.score} \\
- s^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \label{harbord.variance}
+\varphi &= e_t - (e_t - e_c)(e_t + (n_t - e_t))/(n_t + n_c) \nonumber \\
+ \se^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \nonumber
 \end{align}
@@
 It can be shown that they are both good approximations of the log odds ratio and its variance if the real $\theta$ is not too far from zero.
-The standardized estimator $\varphi_i/\se_i^2$ is also known as Peto odds ratio.
+The standardized estimate $\varphi/\se^2$ is also known as Peto odds ratio.
 The obtained scores and variances can be used in Egger's test as treatment effects and variances.
@@
 \begin{align}
-p &= \sum_{i = O}^n\Big({n \choose i} p^i (1-p)^{n - i}\Big)
+p &= \sum_{i = O}^n\Big({n \choose i} p^i (1-p)^{n - i}\Big) \nonumber
 \end{align}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 20 13:54:20 2019
+% Wed Aug 21 08:49:49 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 20 13:54:35 2019
+% Wed Aug 21 08:50:02 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 20 13:54:49 2019
+% Wed Aug 21 08:50:17 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 20 13:54:50 2019
+% Wed Aug 21 08:50:18 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 20 13:54:59 2019
+% Wed Aug 21 08:50:27 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 20 13:54:59 2019
+% Wed Aug 21 08:50:28 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 20 13:55:02 2019
+% Wed Aug 21 08:50:31 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 20 13:55:04 2019
+% Wed Aug 21 08:50:33 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 20 13:55:08 2019
+% Wed Aug 21 08:50:36 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Tue Aug 20 13:55:52 2019
+% Wed Aug 21 08:51:20 2019
 \begin{table}[ht]

### 2019-08-21 code/Meta_meta_regression.R

@@ -1,238 +1,0 @@
-#Load data:
-rm(list = ls())
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'Data/PubBias')
-PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2019-07-04.csv'
-PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results_new')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-require(nlme)
-
-source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-load(file.path(PATH_RESULTS, "data2.RData"))
-# data.ext2 <- pb.process3(data)
-load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
-
-load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
-
-load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
-
-load(file.path(PATH_DATA, "PubBias_2019-07-19.RData"))
-#----------------------------------------------------------------------------------------------#
-
-##-------Prepare data--------#
-reg.dat <- data.ext2 %>% filter(meta.id %in% meta.id.vector) #Filter meta-analysis data
-
-#Mirror all effects on one positive side:
-reg.dat <- reg.dat %>% group_by(meta.id) %>% 
-  mutate(bias.side = bias.side.fct2(outcome = outcome.flag, outcome.measure.merged = outcome.measure.merged,
-                                    lrr = lrr, var.lrr = var.lrr, smd = cohensd, var.smd = var.cohensd, 
-                                    effect = effect, se = se),
-  smd.pool = smd.pool * bias.side) #Mirror effect sizes on one side
-
-#Get tau^2 based on smd's and introduce new study se:
-reg.dat <- reg.dat %>% group_by(meta.id) %>% 
-  mutate(tau.squared = metagen(TE = smd.pool, seTE = se.smd.pool)$tau^2,
-         new.se.smd = sqrt(se.smd.pool^2 + tau.squared))
-
-reg.dat <- reg.dat %>% filter(se.smd.pool != 0) %>% filter(!is.na(smd.pool)) %>% 
-  filter(!is.na(se.smd.pool))
-
[…]

### 2019-08-21 code/explore.R

@@ -1,465 +1,0 @@
-rm(list = ls())
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'Data/PubBias')
-PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2018-06-09.csv'
-PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-file_results = "pb.RData"
-
-source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-file.dat <- "data.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
-load(file.path(PATH_RESULTS, "meta.bin.RData"))
-load(file.path(PATH_RESULTS, "meta.cont.RData"))
-load(file.path(PATH_RESULTS, "meta.surv.RData"))
-load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
-
-
-
-#Explanation of coding: 0 = (unsig, unsig), 1 = (unsig, sig), 2 = (sig, sig), 3 = (sig, unsig)
-sig.level <- 0.05
-meta.f <- meta.f %>% rowwise() %>% 
-	mutate(
-		pval.copas = 2*(1-pnorm(abs(est.copas/se.est.copas))),
-		
-		sig.fixef = ifelse(pval.fixef > sig.level, 0, 1),
-		sig.ranef = ifelse(pval.ranef > sig.level, 0, 1),
-		sig.reg.ranef = ifelse(pval.reg > sig.level, 0, 1),
-		sig.copas = ifelse(pval.copas > sig.level, 0, 1),
-		
-		sig.change.ranef.reg = sig.change(sig.before = sig.ranef, sig.after =  sig.reg), #Function to register if significance of estimate has changed after correction
[…]

### 2019-08-21 code/new_meta_analysis.R

@@ -1,825 +1,0 @@
-rm(list = ls())
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'Data/PubBias')
-PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2018-06-09.csv'
-PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-file_results = "pb.RData"
-
-source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-file.dat <- "data.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-# data.ext2 <- pb.process2(data)
-
-load(file.path(PATH_RESULTS, "meta_analyses_summary_bin_cont_surv.RData"))
-load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
-load(file.path(PATH_RESULTS, "data_used_for_summary.RData"))
-load(file.path(PATH_RESULTS, "meta_complete_list_bin.RData"))
-load(file.path(PATH_RESULTS, "meta_complete_list_cont.RData"))
-load(file.path(PATH_RESULTS, "meta_complete_list_surv.RData"))
-load(file.path(PATH_RESULTS, "meta_complete_list_cor.RData"))
-load(file.path(PATH_RESULTS, "meta_complete_list_zscore.RData"))
-load(file.path(PATH_RESULTS, "meta_complete_list_cohensd.RData"))
-load(file.path(PATH_RESULTS, "excess_significance_list.RData"))
-# load(file.path(PATH_RESULTS, "meta_complete_list_cum.RData"))
-
-settings.meta(hakn=TRUE, method.tau="PM", method = "Inverse")
-
-##########################################################################################
-##########################################################################################
-##########################################################################################
-##########################################################################################
[…]

### 2019-08-21 code/plot_point_assemblies.R

@@ -1,40 +1,0 @@
-reg.dat %>% filter(se.smd > 1.08 & se.smd < 1.15) %>% distinct(meta.id)
-
-
-reg.dat %>% filter(se.smd > 1.08 & se.smd < 1.15) %>% distinct(id)
-
-
-x <- reg.dat %>% filter(se.smd > 0.75 & se.smd < 0.85) %>% filter(smd > -0.1 & smd < 0.1)
-x %>% distinct(meta.id)
-x %>% distinct(id)
-
-
-
-plot(x$smd, x = x$se.smd, col = x$meta.id, pch = 20)
-
-x$n <- x$total1 + x$total2
-
-hist(x$n)
-
-x %>% ggplot(aes(x = se.smd, y = smd, color = factor(meta.id))) + geom_point() + theme(legend.position = "none")
-
-
-x %>% ggplot(aes(x = se.smd, y = smd, color = n)) + geom_point() +
-  scale_color_continuous(low = "darkgreen", high = "green")#+ theme(legend.position = "none")
-
-x %>% ggplot(aes(x = se.smd, y = smd, color = factor(outcome.measure.merged))) + geom_point() 
-  
-x %>% ggplot(aes(x = se.smd, y = smd, color = factor(events1 + events2))) + geom_point() 
-
-x %>% ggplot(aes(x = se.smd, y = smd, color = factor(events1 + events2))) + geom_point() 
-
-  
-ct <- x %>% filter(outcome.flag == "DICH")
-plot(ct$events1, ct$n)
-plot(ct$events1, ct$events2)
-hist(ct$events1 + ct$events2, breaks = 55)
-
-
-x %>% ggplot(aes(x = se.smd, y = smd, color = factor(events1))) + geom_point() 
-
-x %>% ggplot(aes(x = se.smd, y = smd, color = factor(events2))) + geom_point() 

### 2019-08-21 code/subsetting_m.a..R

@@ -1,61 +1,0 @@
-rm(list = ls())
-PATH_HOME = path.expand("~") # user home
-PATH = file.path(PATH_HOME, 'Data/PubBias')
-PATH2 = file.path(PATH_HOME, 'PubBias')
-FILE = 'cochrane_2018-06-09.csv'
-PATH_DATA = file.path(PATH, 'data')
-PATH_CODE = file.path(PATH2, 'code')
-PATH_RESULTS = file.path(PATH2, 'results')
-PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
-
-file_results = "pb.RData"
-
-source(file.path(PATH_CODE, 'PubBias_functions.R'))
-
-file.dat <- "data.RData"
-if (file.exists(file.path(PATH_RESULTS, file.dat))) {
-	load(file.path(PATH_RESULTS, file.dat))
-} else {
-	data = pb.readData(path = PATH_DATA, file = FILE)
-	tmp = pb.clean(data)
-	data = tmp[[1]]
-	aliases = tmp[[2]]
-	save(data, file =  file.path(PATH_RESULTS, file.dat))
-}
-
-load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
-load(file.path(PATH_RESULTS, "meta.bin.RData"))
-load(file.path(PATH_RESULTS, "meta.cont.RData"))
-load(file.path(PATH_RESULTS, "meta.surv.RData"))
-load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
-
-
-
-comp <- metac %>% select(meta.id, comparison.name) #%>% distinct(comparison.name)
-
-comp$isin <- mapply(FUN = grepl, x = comp$comparison.name, pattern = "sensitivity")
-length(which(comp$isin == TRUE))
-comp$isin2 <- mapply(FUN = grepl, x = comp$comparison.name, pattern = "Sensitivity")
-length(which(comp$isin2 == TRUE))
-
-meta.wout.sensitivity <- metac %>% filter(!grepl(pattern = "sensitivity", comparison.name) | !grepl(pattern = "Sensitivity", comparison.name))
-
-
-comp <- metac %>% select(meta.id, outcome.name) #%>% distinct(outcome.name)
-
-comp$isin <- mapply(FUN = grepl, x = comp$outcome.name, pattern = "sensitivity")
-length(which(comp$isin == TRUE))
[…]

### 2019-08-21 code/tes.R

@@ -1,91 +1,0 @@
-################################################################################
-##### FUNCTION FOR USING THE TEST OF EXCESS SIGNIFICANCE AS DESCRIBED IN   #####
-##### IOANNIDIS AND TRIKALINOS (2007)                                      #####
-##### Author: Robbie C.M. van Aert                                         #####
-################################################################################
-
-tes <- function(yi, sei, alpha, side) 
-{
-  
-  ### FE meta-analysis for statistical power analysis
-  est.fe <- rma(yi = yi, sei = sei, method = "FE")$b[1] 
-  
-  ### Compute statistical power and determine the number of observed 
-  # statistically significant results
-  if (side == "right") { 
-    pow <- pnorm(qnorm(alpha, lower.tail = FALSE, sd = sei), mean = est.fe,
-                 sd = sei, lower.tail = FALSE) #Probability to 
-    O <- sum(pnorm(yi/sei, lower.tail = FALSE) < alpha)
-  } else if (side == "left") {
-    pow <- pnorm(qnorm(alpha, sd = sei), mean = est.fe, sd = sei)
-    O <- sum(pnorm(yi/sei) < alpha)
-  }
-  
-  E <- sum(pow) # Expected number of statistically significant result  
-  n <- length(yi) # Number of studies in meta-analysis
-  A <- (O - E)^2/E + (O - E)^2/(n - E) # Compute chi-square statistic
-  pval.tes <- pchisq(A, 1, lower.tail = FALSE) # Compute p-value
-  pval.tes <- ifelse(pval.tes < 0.5, pval.tes*2, (1-pval.tes)*2)
-  
-  return(data.frame(A = A, pval.tes = pval.tes, O = O, E = E, n = n))
-  
-}
-
-
-
-data <- data.ext2 %>% filter(meta.id == 168988)
-168988 171006 171029 171032 171592 178208 178210
-tes(ts)
-
-tes <- function(data){
-  yi = data$z
-  sei = sqrt(data$var.z)
-  alpha = 0.05
-  
-  ### FE meta-analysis for statistical power analysis
-  est.fe <- rma(yi = yi, sei = sei, method = "FE")$b[1] 
-  
-  side <- ifelse(sign(est.fe) == -1, "left", "right")
-  
[…]

### 2019-08-21 code/z_score_issues.R

@@ -1,61 +1,0 @@
-idt <- meta.cont$meta.id[1]
-
-idt <- meta.bin$meta.id[1]
-
-
-mtd <- data.ext2 %>% filter(meta.id == idt)
-
-# mtd <- escalc(measure = "PBIT", ai = events1, n2i = total2, ci = events2, n1i = total1, 
-#               to = "only0",
-#               add = 1/2, append = T, var.names = c("smd.pbit", "var.smd.pbit"), data = mtd)
-
-#Issue starts here:
-forest(rma.uni(yi = cor.pearson, vi = var.cor.pearson, measure = "COR",
-               method = "FE", data = mtd))
-forest(rma.uni(yi = z, vi = var.z, measure = "ZCOR",
-               method = "FE", data = mtd), layout = "JAMA")
-
-# mtd$smd.ordl[1] <- 1.1547
-# mtd$var.smd.ordl[1] <- 0.055
-# mtd$total1[1] <- 100; mtd$total2[1] <- 100
-# 
-# mtd <- mtd %>% mutate(
-#   a = ((total1 + total2)^2)/(total1*total2),
-#   cor.pearson  = smd.ordl/sqrt((smd.ordl^2) + a),
-#   var.cor.pearson = ((a^2)*var.smd.ordl)/(((smd.ordl^2)+a)^3))
-# 
-# mtd <- mtd %>% 
-#   mutate(z = 0.5 * log( (1 + cor.pearson)/(1 - cor.pearson) , base = exp(1)), 
-#          var.z= 1/(total1 + total2 - 3))
-
-
-par(mfrow = c(1,2))
-forest(rma.uni(yi = lrr, vi = var.lrr,
-               measure = "RR", method = "FE", data = mtd))
-forest(rma.uni(yi = smd.ordl, vi = var.smd.ordl, measure = "SMD",
-               method = "FE", data = mtd))
-forest(rma.uni(yi = smd.ordl, vi = var.smd.ordl, measure = "SMD",
-               method = "FE", data = mtd))
-
-
-par(mfrow = c(1, 1))
-funnel(metagen(TE = smd, seTE = sqrt(var.smd), data = mtd))
-funnel(metagen(TE = effect, seTE = se, data = mtd))
-funnel.id(idt)
-funnel(metagen(TE = z, seTE = sqrt(var.z), data = mtd))
-
-# forest.meta(metabin(event.e = events1c, n.e = total1, event.c = events2c, n.c = total2,
-#                     studlab = study.name, sm = "RR",
[…]

### 2019-08-21 code_excess/Meandifference_issue.R

@@ -1,0 +1,86 @@
+dt <- data.ext2 %>% filter(meta.id == meta.bin$meta.id[33])
+forest.meta(metacor(cor = z, n = total1 + total2, studlab = study.name, data = dt, sm = "ZCOR"))
+forest.meta(metabin(event.e = events1c, n.e = total1, event.c = events2c, n.c = total2,
+                    studlab = study.name, sm = "RR",
+                    method = "Inverse", data = dt))
+
+
+dt <- data.ext2 %>% filter(meta.id == meta.cont[which(meta.cont$outcome.measure.merged == "MD")[33],]$meta.id)
+
+forest.meta(metacor(cor = z, n = total1 + total2, studlab = study.name, data = dt, sm = "ZCOR"))
+forest.meta(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2,
+                     mean.c = mean2, sd.c = sd2, sm = "MD", studlab = study.name,
+                     data = dt))
+forest.meta(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2,
+                     mean.c = mean2, sd.c = sd2, sm = "SMD", studlab = study.name,
+                     data = dt))
+
+par(mfrow= c(1,2))
+forest(rma.uni(yi = z, vi = var.z, measure = "ZCOR", slab = study.name, data = dt))
+forest(rma.uni(yi = effect, vi = se^2, measure = "MD", slab = study.name,
+               method = "FE", data = dt))
+forest(rma.uni(yi = cohensd, vi = var.cohensd, measure = "SMD", slab = study.name,
+               method = "FE", data = dt))
+dt %>% mutate(se.smd = sqrt(var.smd)) %>% ggplot(aes(x = se.smd, y = smd, col = total1 + total2)) + geom_point()
+dt %>% ggplot(aes(x = se, y = effect, col = total1 + total2)) + geom_point()
+
+
+
+funnel(metagen(TE = smd, seTE = sqrt(var.smd), data = mtd))
+funnel(metagen(TE = effect, seTE = se, data = mtd))
+# forest(rma.uni(yi = z, vi = var.z, measure = "ZCOR", slab = study.name,
+#                method = "FE", data = dt))
+
+
+mtd <- data.ext2 %>% filter(meta.id == meta.bin$meta.id[33])
+funnel(metagen(TE = smd.pool, seTE = se.smd.pool, data = mtd))
[…]

### 2019-08-21 code_excess/Meta_meta_regression.R

@@ -1,0 +1,238 @@
+#Load data:
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2019-07-04.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results_new')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+require(nlme)
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+load(file.path(PATH_RESULTS, "data2.RData"))
+# data.ext2 <- pb.process3(data)
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+
+load(file.path(PATH_RESULTS, "meta_id_vector.RData"))
+
+load(file.path(PATH_DATA, "PubBias_2019-07-19.RData"))
+#----------------------------------------------------------------------------------------------#
+
+##-------Prepare data--------#
+reg.dat <- data.ext2 %>% filter(meta.id %in% meta.id.vector) #Filter meta-analysis data
+
+#Mirror all effects on one positive side:
+reg.dat <- reg.dat %>% group_by(meta.id) %>% 
+  mutate(bias.side = bias.side.fct2(outcome = outcome.flag, outcome.measure.merged = outcome.measure.merged,
+                                    lrr = lrr, var.lrr = var.lrr, smd = cohensd, var.smd = var.cohensd, 
+                                    effect = effect, se = se),
+  smd.pool = smd.pool * bias.side) #Mirror effect sizes on one side
+
+#Get tau^2 based on smd's and introduce new study se:
+reg.dat <- reg.dat %>% group_by(meta.id) %>% 
+  mutate(tau.squared = metagen(TE = smd.pool, seTE = se.smd.pool)$tau^2,
+         new.se.smd = sqrt(se.smd.pool^2 + tau.squared))
+
+reg.dat <- reg.dat %>% filter(se.smd.pool != 0) %>% filter(!is.na(smd.pool)) %>% 
+  filter(!is.na(se.smd.pool))
+
[…]

### 2019-08-21 code_excess/new_meta_analysis.R

@@ -1,0 +1,825 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+# data.ext2 <- pb.process2(data)
+
+load(file.path(PATH_RESULTS, "meta_analyses_summary_bin_cont_surv.RData"))
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_summary.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_bin.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_cont.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_surv.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_cor.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_zscore.RData"))
+load(file.path(PATH_RESULTS, "meta_complete_list_cohensd.RData"))
+load(file.path(PATH_RESULTS, "excess_significance_list.RData"))
+# load(file.path(PATH_RESULTS, "meta_complete_list_cum.RData"))
+
+settings.meta(hakn=TRUE, method.tau="PM", method = "Inverse")
+
+##########################################################################################
+##########################################################################################
+##########################################################################################
+##########################################################################################
[…]

### 2019-08-21 code_excess/special_cases.R

@@ -1,0 +1,43 @@
+rm(list = ls())
+PATH_HOME = path.expand("~") # user home
+PATH = file.path(PATH_HOME, 'Data/PubBias')
+PATH2 = file.path(PATH_HOME, 'PubBias')
+FILE = 'cochrane_2018-06-09.csv'
+PATH_DATA = file.path(PATH, 'data')
+PATH_CODE = file.path(PATH2, 'code')
+PATH_RESULTS = file.path(PATH2, 'results')
+PATH_FIGURES = file.path(PATH_RESULTS, 'figures')
+
+file_results = "pb.RData"
+
+source(file.path(PATH_CODE, 'PubBias_functions.R'))
+
+file.dat <- "data.RData"
+if (file.exists(file.path(PATH_RESULTS, file.dat))) {
+	load(file.path(PATH_RESULTS, file.dat))
+} else {
+	data = pb.readData(path = PATH_DATA, file = FILE)
+	tmp = pb.clean(data)
+	data = tmp[[1]]
+	aliases = tmp[[2]]
+	save(data, file =  file.path(PATH_RESULTS, file.dat))
+}
+
+load(file.path(PATH_RESULTS, "meta_analyses_summary_complete.RData"))
+load(file.path(PATH_RESULTS, "meta.bin.RData"))
+load(file.path(PATH_RESULTS, "meta.cont.RData"))
+load(file.path(PATH_RESULTS, "meta.surv.RData"))
+load(file.path(PATH_RESULTS, "data_used_for_analysis.RData"))
+
+funnel(meta.id(56200))#Copas effect size change
+
+meta.f %>% filter(meta.id == 101436) %>% 
+	select(comparison.name, outcome.name, sungroup.name, est.fixef, est.reg, est.copas) #Regression effect size change
+par(mfrow = c(1,3))
+funnel(meta.id(101436))
+funnel(trimfill(meta.id(101436)))
+funnel(limitmeta(meta.id(101436)))
+
+#Odds ratio reduction by 3.9
+funnel(trimfill(meta.id(165815)))
+

### 2019-08-21 code_excess/tes.R

@@ -1,0 +1,91 @@
+################################################################################
+##### FUNCTION FOR USING THE TEST OF EXCESS SIGNIFICANCE AS DESCRIBED IN   #####
+##### IOANNIDIS AND TRIKALINOS (2007)                                      #####
+##### Author: Robbie C.M. van Aert                                         #####
+################################################################################
+
+tes <- function(yi, sei, alpha, side) 
+{
+  
+  ### FE meta-analysis for statistical power analysis
+  est.fe <- rma(yi = yi, sei = sei, method = "FE")$b[1] 
+  
+  ### Compute statistical power and determine the number of observed 
+  # statistically significant results
+  if (side == "right") { 
+    pow <- pnorm(qnorm(alpha, lower.tail = FALSE, sd = sei), mean = est.fe,
+                 sd = sei, lower.tail = FALSE) #Probability to 
+    O <- sum(pnorm(yi/sei, lower.tail = FALSE) < alpha)
+  } else if (side == "left") {
+    pow <- pnorm(qnorm(alpha, sd = sei), mean = est.fe, sd = sei)
+    O <- sum(pnorm(yi/sei) < alpha)
+  }
+  
+  E <- sum(pow) # Expected number of statistically significant result  
+  n <- length(yi) # Number of studies in meta-analysis
+  A <- (O - E)^2/E + (O - E)^2/(n - E) # Compute chi-square statistic
+  pval.tes <- pchisq(A, 1, lower.tail = FALSE) # Compute p-value
+  pval.tes <- ifelse(pval.tes < 0.5, pval.tes*2, (1-pval.tes)*2)
+  
+  return(data.frame(A = A, pval.tes = pval.tes, O = O, E = E, n = n))
+  
+}
+
+
+
+data <- data.ext2 %>% filter(meta.id == 168988)
+168988 171006 171029 171032 171592 178208 178210
+tes(ts)
+
+tes <- function(data){
+  yi = data$z
+  sei = sqrt(data$var.z)
+  alpha = 0.05
+  
+  ### FE meta-analysis for statistical power analysis
+  est.fe <- rma(yi = yi, sei = sei, method = "FE")$b[1] 
+  
+  side <- ifelse(sign(est.fe) == -1, "left", "right")
+  
[…]

### 2019-08-21 code_excess/z_score_issues.R

@@ -1,0 +1,61 @@
+idt <- meta.cont$meta.id[1]
+
+idt <- meta.bin$meta.id[1]
+
+
+mtd <- data.ext2 %>% filter(meta.id == idt)
+
+# mtd <- escalc(measure = "PBIT", ai = events1, n2i = total2, ci = events2, n1i = total1, 
+#               to = "only0",
+#               add = 1/2, append = T, var.names = c("smd.pbit", "var.smd.pbit"), data = mtd)
+
+#Issue starts here:
+forest(rma.uni(yi = cor.pearson, vi = var.cor.pearson, measure = "COR",
+               method = "FE", data = mtd))
+forest(rma.uni(yi = z, vi = var.z, measure = "ZCOR",
+               method = "FE", data = mtd), layout = "JAMA")
+
+# mtd$smd.ordl[1] <- 1.1547
+# mtd$var.smd.ordl[1] <- 0.055
+# mtd$total1[1] <- 100; mtd$total2[1] <- 100
+# 
+# mtd <- mtd %>% mutate(
+#   a = ((total1 + total2)^2)/(total1*total2),
+#   cor.pearson  = smd.ordl/sqrt((smd.ordl^2) + a),
+#   var.cor.pearson = ((a^2)*var.smd.ordl)/(((smd.ordl^2)+a)^3))
+# 
+# mtd <- mtd %>% 
+#   mutate(z = 0.5 * log( (1 + cor.pearson)/(1 - cor.pearson) , base = exp(1)), 
+#          var.z= 1/(total1 + total2 - 3))
+
+
+par(mfrow = c(1,2))
+forest(rma.uni(yi = lrr, vi = var.lrr,
+               measure = "RR", method = "FE", data = mtd))
+forest(rma.uni(yi = smd.ordl, vi = var.smd.ordl, measure = "SMD",
+               method = "FE", data = mtd))
+forest(rma.uni(yi = smd.ordl, vi = var.smd.ordl, measure = "SMD",
+               method = "FE", data = mtd))
+
+
+par(mfrow = c(1, 1))
+funnel(metagen(TE = smd, seTE = sqrt(var.smd), data = mtd))
+funnel(metagen(TE = effect, seTE = se, data = mtd))
+funnel.id(idt)
+funnel(metagen(TE = z, seTE = sqrt(var.z), data = mtd))
+
+# forest.meta(metabin(event.e = events1c, n.e = total1, event.c = events2c, n.c = total2,
+#                     studlab = study.name, sm = "RR",
[…]

### 2019-08-22 report/MSc_Report.tex
Theory corrected

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \subsection{Continuous Outcomes}
-For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (also known as Cohen's $d$) and the standard error thereof.
-
-\begin{align}
-\theta &= m_t - m_c & \se &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_c}
-\end{align}
-
-Cohen's $d$ and its standard error $\se$ can similarly be obtained by
-
-\begin{align}
-d &= \frac{m_t - m_c}{\se} \label{eq:hedges.g} & \se &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}}
+For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference $\theta$ as well as a standardized mean difference (also known as Cohen's $d$) and the standard error thereof.
+
+\begin{align}
+\theta &= m_t - m_c & \se_\theta &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_c}
+\end{align}
+
+Cohen's $d$ and its standard error $\se_d$ can similarly be obtained by
+
+\begin{align}
+d &= \frac{m_t - m_c}{\se} \label{eq:hedges.g} & \se_d &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}}
 \end{align}
@@
 Both estimators take into account that the two groups might have unequal variances. \\ 
-A  $p$\hspace{0.4mm}~-~value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$-test.
-The $t$ statistic is obtained, using $\se$ and $d$ from \eqref{eq:hedges.g}, by
-
-\begin{align}
-t &= d/(\se\sqrt{(1/n_t)+(1/n_c)}) \nonumber
-\end{align}
-and the  $p$\hspace{0.4mm}~-~value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
+A  $p$\hspace{0.4mm}-value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$-test.
+The $t$ statistic is obtained, using $\se_d$ and $d$ from \eqref{eq:hedges.g}, by
+
+\begin{align}
+t &= d/(\se_d\sqrt{(1/n_t)+(1/n_c)}) \nonumber
+\end{align}
+and the  $p$\hspace{0.4mm}-value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
 
@@
 \begin{align}
-\hat{\theta} &= \log(\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}) \nonumber \\
+\hat{\theta} &= \log\bigg[\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}\bigg] \nonumber \\
 \hat{\se}^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
@@
 \begin{align}
-\hat{\theta} &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
+\hat{\theta} &= \log\bigg(\frac{e_t/n_t}{e_c/n_c}\bigg) \label{eq:risk.ratio} \\
 \se^2&= 1/e_t - 1/n_t + 1/e_c - 1/n_c \label{eq:risk.ratio.variance}
@@
 
-Assuming binomial distribution of the events and using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a  $p$\hspace{0.4mm}~-~value, \eg \cite[98]{held2014}.
+Assuming binomial distribution of the events and using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a  $p$\hspace{0.4mm}-value, \eg \cite[98]{held2014}.
 The approximation is only good if there are enough events and sample size is large enough.\\
@@
 \begin{align}
-p &= 2\cdot(1-\Phi(|\hat{\theta}/\hat{\se}|), \nonumber
-\end{align}
-a  $p$\hspace{0.4mm}~-~value for the corresponding estimate, which summarizes the evidence against $\hat{\theta}$ being zero (\ie the true risk/odds ratio being 1). \\
+p &= 2\cdot(1-\Phi(|\hat{\theta}/\hat{\se}|)), \nonumber
+\end{align}
+a  $p$\hspace{0.4mm}-value for the corresponding estimate, which summarizes the evidence against $\hat{\theta}$ being zero (\ie the true risk/odds ratio being 1). \\
 Odds ratios can be transformed to std. mean differences, which will be described in Section \ref{sec:transformation.effectsizes}.
@@
 \end{align}
-will give a  $p$\hspace{0.4mm}~-~value for the evidence against the null hypothesis.
+will give a  $p$\hspace{0.4mm}-value for the evidence against the null hypothesis.
 
@@
 Let $w_i = 1/\se_i^2$ be the weights, and $\theta_M$ be the pooled estimator and $\se_M^2$ its variance.
-Then
+Then the estimates are given by
 
@@
 \theta_M &= \frac{\sum_{i = 1}^n w_i \theta_i}{\sum_{i = 1}^n w_i} &
-\se_M^2 &= \frac{1}{\sum_{i = 1}^n w_i} \label{eq:fixed.effects}
-\end{align}
-
+\se_M^2 &= \frac{1}{\sum_{i = 1}^n w_i}. \label{eq:fixed.effects}
+\end{align}
 This estimator minimizes the variance between the effects.
 An estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and variances $\hat{\theta}_i$ and $\hat{\se}_i^2$.
-The underlying idea is that we assume $\theta_i \sim N(\theta_M, \se_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.
-\\
+The underlying idea is that we assume $\theta_i \sim N(\theta_M, \se_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.\\
 The random effects model \citep{whitehead} assumes instead that 
@@
 Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i} \label{eq:Q.heterogeneity} \\
-\tau^2 &= \max\big(0, \frac{Q - (n-1)}{C}\big) \label{eq:Tau.definition}
+\tau^2 &= \max\bigg[0, \frac{Q - (n-1)}{C}\bigg] \label{eq:Tau.definition}
 \end{align}
@@
 Thus, the expected value of $Q$ is $n-1$, and the excess dispersion is $Q - n + 1$.
-The  $p$\hspace{0.4mm}~-~value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
+The  $p$\hspace{0.4mm}-value against the null hypothesis of equally distributed effect sizes is $1 - F(Q)$, using $F$ as the cumulative distribution function of the Chi-squared distribution with d.f.
 = $n-1$.
@@
 \begin{align}
-y &= \beta_0 + \beta_1 x + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:simple.regression}
-\end{align}
-
+y &= \beta_0 + \beta_1 x + \epsilon, & \epsilon \sim N(0, \sigma^2). \label{eq:simple.regression}
+\end{align}
 $\epsilon$ is the residual noise term that becomes necessary when $n$ pairs $(x_i, y_i)$ are given and there is no exact solution.
@@
 $\bar{x}$ and $\bar{y}$ denoting the sample means of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$. Thus, $\hat{\beta}_0$ is also called the global mean.
-To test whether there is evidence for the intercept $\beta_0$ to be unequal to some value $\beta_{H0}$, a $t$-test can be used.
-
-\begin{align}
-p &= 2(1-F(\abs{(\beta_0 - \beta_{H0})/s_{\beta_0}})) \nonumber
-\end{align}
-
-where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. The  $p$\hspace{0.4mm}~-~value will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
+To test whether there is evidence for the intercept $\beta_0$ to be unequal to some value $\beta_{H0}$, a $t$-test can be used:
+
+\begin{align}
+p &= 2(1-F(\abs{(\beta_0 - \beta_{H0})/s_{\beta_0}})), \nonumber
+\end{align}
+where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. The  $p$\hspace{0.4mm}-value will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
 The concept is extendable to weighted linear regression.
@@
 \begin{align}
-\mathbf{y}_i|U_j,\epsilon_{i} =  x_i\beta + U_j + \epsilon_{i} \label{eq:one.random.intercept}
+\mathbf{y}_i \given U_j,\epsilon_{i} =  x_i\beta + U_j + \epsilon_{i} \label{eq:one.random.intercept}
 \end{align}
@@
 \begin{align}
-\mathbf{y}_i|U_j,\epsilon_i =  x_i\beta + x_i \mathbf{U}_j + \epsilon_i \label{eq:one.random.intercept.and.slope}
+\mathbf{y}_i \given U_j,\epsilon_i =  x_i\beta + x_i \mathbf{U}_j + \epsilon_i \label{eq:one.random.intercept.and.slope}
 \end{align}
@@
 \begin{align}
-\hat{\beta} &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1} \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{y}_j
+\hat{\mathbf{\beta}} &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1} \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{y}_j
 \end{align}
@@
 \begin{align}
-\mathbf{y}_j \sim N(\mathbf{x}_j \beta, \mathbf{V}_j)
-\end{align}
-
+\mathbf{y}_j \sim N(\mathbf{x}_j \mathbf{\beta}, \mathbf{V}_j).
+\end{align}
 The matrices $\sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j$ and $\hat{\mathbf{V}}_j$ are assumed to be positive definite  .
@@
 The tests that will be presented on the following pages are a common way to detect publication bias.
-A frequently used method to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill} is not discussed because of its disadvantageous properties (see \eg \citealp{Moreno.2009}).\\
+A frequently used method to test and adjust for publication bias, which goes under the name of trim-and-fill \citep{trimfill}, is not discussed because of its disadvantageous properties (see \eg \citealp{Moreno.2009}).\\
 
 \subsection{Begg and Mazumdar: Rank Correlation Test} \label{sec:Begg}
-\citealp{Begg} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
+\citet{Begg} proposed a rank based test to test the null hypothesis of no correlation between effect size and variance.
 A standardized effect size $\theta_i^\star$ can be computed as in \eqref{eq:begg.stand.eff}.
@@
 Thus, large number of concordant pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$.
-A two-sided  $p$\hspace{0.4mm}~-~value is obtained using the standard normal distribution $\Phi$:
+A two-sided  $p$\hspace{0.4mm}-value is obtained using the standard normal distribution $\Phi$:
 \begin{align}
@@
 A one-sided test for positive correlation is obtained by computing $1-\Phi(Z)$ instead.
-The changes that have to be made in the case of ties are small and can be found in \cite[p. 410]{begg.ties}.
+The changes that have to be made in the case of ties are small and can be found in \citet{begg.ties}.
 
@@
 Thus testing $\beta_0$ of \eqref{eq:radial.plot} or $\beta_1$ of \eqref{eq:egger.plot} is equivalent.
-The corresponding  $p$\hspace{0.4mm}~-~value is then used as evidence for a small study effect.
+The corresponding  $p$\hspace{0.4mm}-value is then used as evidence for a small study effect.
 Plugging in  $\theta_i/\se_i, 1/\se_i$ as $y_i, x_i$ into equations \eqref{eq:regression.parameters} and \eqref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{\se}_{\beta_0}$ and $\hat{\se}_{\beta_1}$.
@@
 After adjusting for the weights as described in \ref{weighted.regression}, we can proceed analogous to Egger's test.
-The  $p$\hspace{0.4mm}~-~value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
+The  $p$\hspace{0.4mm}-value for $\beta_{0} \neq 0$ reflects the evidence for a small study effect.
 
@@
 \subsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
-\citealp{Schwarzer} developed a test for the correlation between the event counts in the treatment group and the expected event counts $E_t - \mathbb{E}(E_t)$.
+\citealp{Schwarzer} developed a test for the correlation between the event counts in the treatment group and the expected event counts $E_t - \mathbb{E}(E_t)$, where $E_t$ is a random variable.
 When the marginals in a two-by-two table and the log odds ratio are fixed, it can be shown that $E_t$ follows a non-central hypergeometric distribution.
@@
 \begin{align}
-(e_t - \mathbb{E}(E_t))/\sqrt(\se_i^2)
+(e_t - \mathbb{E}(E_t))/\se_i
 \end{align}
@@
 \begin{align}
-\theta_i &= \arcsin{e_t/n_t} - \arcsin{e_c/n_c} \nonumber &
-\se_i^2 &= 1/4n_t + 1/4n_c \nonumber
+\theta_i &= \arcsin{(e_t/n_t)} - \arcsin{(e_c/n_c)} \nonumber &
+\se_i^2 &= 1/(4n_t) + 1/(4n_c) \nonumber
 \end{align}
@@
 
-and consecutively, calculating a $p$\hspace{0.4mm}~-~value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
+and consecutively, calculating a $p$\hspace{0.4mm}-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
 Alternatively, one can also use a binomial test, which is encouraged when $n$ and $O$ is small.
@@
 
-A method proposed in \cite{Copas1,Copas2,Copas3} assumes that study results are selected based on the specific properties of their effect sizes and variances. \\
+A method proposed in \citet{Copas1}, \citet{Copas2} and \citet{Copas3} assumes that study results are selected based on the specific properties of their effect sizes and variances. \\
 Let $\theta_i$ be the effect size estimate of study $i$. Then
@@
 \end{align}
-
 which is identical to the random-effects meta-analysis setting.
@@
 P(\textrm{select} \given \se_i, \theta_i) = %P(a,b,s,y) = 
-\Phi\bigg(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i^2}}}\bigg) \nonumber
+\Phi\bigg(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i}^2}}\bigg) \nonumber
 \end{align}
@@
 \begin{align}
-\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta \se_i)^2}{(\tau^2 + \sigma_i^2)}] \nonumber
-\end{align}
-
-$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$\hspace{0.4mm}~-~value.
+\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n\bigg[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta \se_i)^2}{(\tau^2 + \sigma_i^2)}\bigg] \nonumber
+\end{align}
+
+$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$\hspace{0.4mm}-value.
 Note that the test is very similar to Egger's small study effect test when $\tau^2 = 0$.\\
@@
 The procedure in \citet{limitmeta} is the following: A range of values of $(a,b)$ are applied, and the test for residual small study effect as described in equation \eqref{eq:copas.small.study} is applied.
-If all obtained  $p$\hspace{0.4mm}~-~values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for adjustment, and the standard, classical random effects meta-analysis is retained.
-If none of the  $p$\hspace{0.4mm}~-~values is above the threshold, a wider range of values for $(a,b)$ is used.
-When some  $p$\hspace{0.4mm}~-~values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the pair of $a$ and $b$ that implies the fewest publication bias is chosen).\\
+If all obtained  $p$\hspace{0.4mm}-values from the test are above a threshold 0.1, this is interpreted as no evidence, and no need for adjustment, and the standard, classical random effects meta-analysis is retained.
+If none of the  $p$\hspace{0.4mm}-values is above the threshold, a wider range of values for $(a,b)$ is used.
+When some  $p$\hspace{0.4mm}-values are above, and some below the threshold, the pair $(a,b)$ with the smallest number of missing studies is retained (that is, the pair of $a$ and $b$ that implies the fewest publication bias is chosen).\\
 Currently, there is no test to detect miss-specifications in the model itself and the authors themselves have argued that a non-parametric test of the residuals would lack power.
@@
 \begin{align}
-z &= 0.5 \ln\big(\frac{1 + r}{1 - r}\big) & \nonumber
+z &= 0.5 \ln\bigg(\frac{1 + r}{1 - r}\bigg) & \nonumber
 %z &= \arctan(r) & \nonumber
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 21 08:49:49 2019
+% Thu Aug 22 13:59:23 2019
 \begin{table}[ht]
@@
 Then, a Bayesian two-step hierarchical selection model was applied (\citealp{bayesian.selection.model}, \citealp{bayesian.selection.model.2}).
-It assumes that the selection process is a two-step weight, which assigns different probabilities to non-significant and significant effects.
+It assumes that the selection process is a two-step weight function, which assigns different probabilities to non-significant and significant effects.
 Thus, a ratio of publication probability between significant and non-significant study estimates using a two-step weight function.
@@
 \\
-The author's come to the conclusion in their study that in contrast to other studies, they find few evidence for publication
+The author's come to the conclusion in their study that in contrast to other studies, they find few evidence for publication bias.
 

### 2019-08-22 code/PubBias_functions.R

@@ -1,0 +1,880 @@
+# by Simon Schwab, 2019
+
+library(testit)
+require(tidyverse)
+require(meta)
+require(metasens)
+# require(biostatUZH)
+require(gridExtra)
+require(metafor)
+require(xtable)
+
+# Reads the data
+pb.readData = function(path, file) {
+  
+  data = read.csv(file.path(path, file),
+                  colClasses=c("integer", "character", "character",  # file       :  nr, name, doi
+                               "integer", "integer",                 # file       :  index, version
+                               "integer", "character",               # comparison :  nr, name
+                               "integer", "character", "character",  # outcome    :  nr, name, measure
+                               "integer", "character",               # subgroup   :  nr, name
+                               "character", "integer",               # study      :  name, year
+                               "numeric", "numeric",                 # effect, std.err.
+                               "numeric", "numeric",                 # group 1    :  events, total
+                               "numeric", "numeric",                 # group 1    :  mean, se
+                               "numeric", "numeric",                 # group 2    :  events, total
+                               "numeric", "numeric",                 # group 2    :  mean, se
+                               "numeric"))                           # total N
+  # some cleanup
+  data$N = NULL # this colums has all NA's
+  data$outcome.measure[grep("&#223;-agonist", data$outcome.measure)] = "beta-agonist"
+  data$outcome.measure[grep("Hedge[s ]*&#180", data$outcome.measure)] = "Hedges' g"
+  
+  return(data)
+}
+
+# Reads the data
+pb.readData2 = function(path, file) {
+  
+  data = read.csv(file.path(path, file),
+                  colClasses=c("character",                          # id
+                               "integer", "character", "character",  # comparison :  nr, name, id
+                               "integer", "character", "character",  # outcome    :  nr, name, measure
+                               "character", "character",             #               id, flag
[…]

### 2019-08-22 report/MSc_Report.tex
osf URL

@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 22 13:59:23 2019
+% Thu Aug 22 14:26:58 2019
 \begin{table}[ht]
@@
 
-% \section{Data and Code Availability}
-% The data of the Cochrane Library of Systematic Reviews is freely available in some countries, in others, the rights are reserved by the Wiley publishing company.
+\section{Data and Code Availability}
+The data of the Cochrane Library of Systematic Reviews is freely available in some countries, in others, the rights are reserved by the Wiley publishing company.
 The code for data processing and analysis can be found at \url{https://osf.io/dbp2r/}.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 21 08:51:20 2019
+% Thu Aug 22 14:27:36 2019
 \begin{table}[ht]
@@
   all exclusion criteria & 5\% & 5\% \\ 
-  harbord test p-value $<$ 0.1 & 12\% & 16\% \\ 
+  Harbord test p-value $<$ 0.1 & 12\% & 16\% \\ 
    \hline
@@
 ## [19] readxl_1.1.0       gdata_2.18.0       rstudioapi_0.8    
-## [22] labeling_0.3       munsell_0.5.0      broom_0.5.0       
-## [25] compiler_3.5.1     modelr_0.1.2       pkgconfig_2.0.2   
-## [28] tidyselect_0.2.5   seriation_1.2-7    codetools_0.2-15  
-## [31] dendextend_1.12.0  viridisLite_0.3.0  crayon_1.3.4      
-## [34] withr_2.1.2        bitops_1.0-6       MASS_7.3-51.1     
-## [37] grid_3.5.1         jsonlite_1.5       gtable_0.2.0      
-## [40] registry_0.5-1     magrittr_1.5       scales_1.0.0      
-## [43] KernSmooth_2.23-15 cli_1.0.1          stringi_1.2.4     
-## [46] viridis_0.5.1      iterators_1.0.10   tools_3.5.1       
-## [49] glue_1.3.0         gclus_1.3.2        hms_0.4.2         
-## [52] colorspace_1.3-2   cluster_2.0.7-1    caTools_1.17.1.1  
-## [55] TSP_1.1-7          bindr_0.1.1        haven_2.0.0
+## [22] munsell_0.5.0      broom_0.5.0        compiler_3.5.1    
+## [25] modelr_0.1.2       pkgconfig_2.0.2    tidyselect_0.2.5  
+## [28] seriation_1.2-7    codetools_0.2-15   dendextend_1.12.0 
+## [31] viridisLite_0.3.0  crayon_1.3.4       withr_2.1.2       
+## [34] bitops_1.0-6       MASS_7.3-51.1      grid_3.5.1        
+## [37] jsonlite_1.5       gtable_0.2.0       registry_0.5-1    
+## [40] magrittr_1.5       scales_1.0.0       KernSmooth_2.23-15
+## [43] cli_1.0.1          stringi_1.2.4      viridis_0.5.1     
+## [46] iterators_1.0.10   tools_3.5.1        glue_1.3.0        
+## [49] gclus_1.3.2        hms_0.4.2          colorspace_1.3-2  
+## [52] cluster_2.0.7-1    caTools_1.17.1.1   TSP_1.1-7         
+## [55] bindr_0.1.1        haven_2.0.0
 \end{verbatim}

### 2019-08-23 report/MSc_Report.tex
corrections

--- 2019-08-22 report/MSc_Report.tex
@@
 \begin{align}
-\theta &= m_t - m_c & \se_\theta &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_c}
-\end{align}
-
-Cohen's $d$ and its standard error $\se_d$ can similarly be obtained by
-
-\begin{align}
-d &= \frac{m_t - m_c}{\se} \label{eq:hedges.g} & \se_d &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}}
+\theta &= m_t - m_c & \textrm{sd}_\theta &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_c}.
+\end{align}
+
+Cohen's $d$ and its standard error $\textrm{sd}_d$ can similarly be obtained by
+
+\begin{align}
+d &= \frac{m_t - m_c}{\textrm{sd}_\theta} & 
+\textrm{sd}_d &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}}. \label{eq:cohensd}
 \end{align}
@@
 A  $p$\hspace{0.4mm}-value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$-test.
-The $t$ statistic is obtained, using $\se_d$ and $d$ from \eqref{eq:hedges.g}, by
-
-\begin{align}
-t &= d/(\se_d\sqrt{(1/n_t)+(1/n_c)}) \nonumber
+The $t$ statistic is obtained, using $\textrm{sd}_d$ and $d$ from \eqref{eq:cohensd}, by
+
+\begin{align}
+t &= d/(\textrm{sd}_d\sqrt{(1/n_t)+(1/n_c)}) \nonumber
 \end{align}
@@
 \begin{align}
-p &= 2(1-F(\abs{t})) \nonumber
+p &= 2(1-F(\abs{t})). \nonumber
 \end{align}
@@
 \hat{\theta} &= \log\bigg[\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}\bigg] \nonumber \\
-\hat{\se}^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
+\hat{\se}^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c). \nonumber
 \end{align}
@@
 \hat{\theta} &= \log\bigg(\frac{e_t/n_t}{e_c/n_c}\bigg) \label{eq:risk.ratio} \\
-\se^2&= 1/e_t - 1/n_t + 1/e_c - 1/n_c \label{eq:risk.ratio.variance}
+\se^2&= 1/e_t - 1/n_t + 1/e_c - 1/n_c. \label{eq:risk.ratio.variance}
 \end{align}
@@
 \end{align}
+
 This estimator minimizes the variance between the effects.
@@
 \theta_i \sim N(\mu_i, \se_i^2) &&
-\mu_i \sim N(\theta_M, \tau^2) \label{eq:random.effects} 
+\mu_i \sim N(\theta_M, \tau^2). \label{eq:random.effects} 
 \end{align}
@@
 \begin{align}
-\theta_i \given \mu_i \sim N(\theta_M, \se_i^2 + \tau^2) \nonumber %\label{eq:random.effects.marginal}
+\theta_i \given \mu_i \sim N(\theta_M, \se_i^2 + \tau^2). \nonumber %\label{eq:random.effects.marginal}
 \end{align}
@@
 Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i} \label{eq:Q.heterogeneity} \\
-\tau^2 &= \max\bigg[0, \frac{Q - (n-1)}{C}\bigg] \label{eq:Tau.definition}
+\tau^2 &= \max\bigg[0, \frac{Q - (n-1)}{C}\bigg]. \label{eq:Tau.definition}
 \end{align}
@@
 \begin{align}
-w_i \textrm{Var}(\theta_i) &= 1 & \textrm{Var}(\sqrt{w_i}\theta_i) = 1 \nonumber
+w_i \textrm{Var}(\theta_i) &= 1 & \textrm{Var}(\sqrt{w_i}\theta_i) = 1. \nonumber
 \end{align}
@@
 \begin{align}
-\se^2(w_i\theta_i) &= \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} & \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} = 1 \label{eq:paulemandel}
+\se^2(w_i\theta_i) &= \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} & \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} = 1. \label{eq:paulemandel}
 \end{align}
@@
 \begin{align}
-F(\tau^2) &= \sum_{i = 1}^n w_i(\theta_i - \theta_M)^2 - (n-1) \nonumber
+F(\tau^2) &= \sum_{i = 1}^n w_i(\theta_i - \theta_M)^2 - (n-1). \nonumber
 \end{align}
@@
 \end{align}
+
 $\epsilon$ is the residual noise term that becomes necessary when $n$ pairs $(x_i, y_i)$ are given and there is no exact solution.
 We look for the solution that minimizes the squared residuals, the least-squares solution.
-Formally,
-
-\begin{align}
-\operatorname*{argmin}_{\beta_0, \beta_1}\Big(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i\Big) \label{eq:least.squares}
+Formally, we write:
+
+\begin{align}
+\operatorname*{argmin}_{\beta_0, \beta_1}\Big(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i\Big). \label{eq:least.squares}
 \end{align}
@@
 \end{align}
-
-Is an estimator of $\mathbf{\beta}$ that minimizes the squared residuals.
+is an estimator of $\mathbf{\beta}$ that minimizes the squared residuals.
 Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\mathbf{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$.
@@
 \begin{align}
-\hat{\sigma}^2 &= \frac{1}{n-2}\mathbf{r}^\top \hat{\mathbf{r}} & \hat{\mathbf{s}}_\beta^2 &= \hat{\sigma}^2 (\mathbf{X}^\top \mathbf{X})^{-1} \label{eq:regression.variances}
+\hat{\sigma}^2 &= \frac{1}{n-2}\mathbf{r}^\top \hat{\mathbf{r}} & \hat{\mathbf{s}}_\beta^2 &= \hat{\sigma}^2 (\mathbf{X}^\top \mathbf{X})^{-1}. \label{eq:regression.variances}
 \end{align}
@@
 % \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} &
-\hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \nonumber
+\hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x}. \nonumber
 \end{align}
@@
 \end{align}
-
 with the positive weights $w_i$ penalizing large squared residuals for some $i$ more if $w_i$ is larger. \\
@@
 \begin{align}
-\mathbf{y}_i \given U_j,\epsilon_{i} =  x_i\beta + U_j + \epsilon_{i} \label{eq:one.random.intercept}
-\end{align}
-
+\mathbf{y}_i \given U_j,\epsilon_{i} =  x_i\beta + U_j + \epsilon_{i}. \label{eq:one.random.intercept}
+\end{align}
 gives the marginal distribution of $\mathbf{y}_i$ depending on $U{_j}$ and $\epsilon_i$.
@@
 \begin{align}
-\Cov(\mathbf{y}_j) &= \mathbf{D}_j \mathbf{G} \mathbf{D}_j^\top + \tau^2 \mathbf{I}_{n_j} \label{eq:random.intercepts.covariance}
-\end{align}
-
+\Cov(\mathbf{y}_j) &= \mathbf{D}_j \mathbf{G} \mathbf{D}_j^\top + \tau^2 \mathbf{I}_{n_j}. \label{eq:random.intercepts.covariance}
+\end{align}
 where $\D_j$ is in the case of the random intercept model a $n_j \times 1$ matrix of 1's, $\mathbf{G}$ is a scalar to be estimated and $\mathbf{I}_{n_j}$ is an $n_j \times n_j$ identity matrix.
@@
 \begin{align}
-\mathbf{y}_i \given U_j,\epsilon_i =  x_i\beta + x_i \mathbf{U}_j + \epsilon_i \label{eq:one.random.intercept.and.slope}
+\mathbf{y}_i \given U_j,\epsilon_i =  x_i\beta + x_i \mathbf{U}_j + \epsilon_i. \label{eq:one.random.intercept.and.slope}
 \end{align}
@@
 \end{align}
-
 with $m$ being the number of groups and $\hat{\mathbf{V}}_j$ being the estimated covariance, obtained by maximizing the log likelihood of the normal distribution, as $\mathbf{y}_j$ is distributed as
@@
 \begin{align}
-\mathbf{y}_j \sim N(\mathbf{x}_j \mathbf{\beta}, \mathbf{V}_j).
-\end{align}
+\mathbf{y}_j \sim N(\mathbf{x}_j \mathbf{\beta}, \mathbf{V}_j). \nonumber
+\end{align}
+
 The matrices $\sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j$ and $\hat{\mathbf{V}}_j$ are assumed to be positive definite  .
@@
 \begin{align}
-\hat{\Cov}(\hat{\beta}) &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1}
+\hat{\Cov}(\hat{\beta}) &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1}. \nonumber
 \end{align}
@@
 \theta_i^\star &= (\theta_i - \theta_M)/\se_i^{2\star} \label{eq:begg.stand.eff}  \\
-\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2} \label{eq:begg.stand.var} 
+\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2}. \label{eq:begg.stand.var} 
 \end{align}
@@
 \begin{align}
-Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \nonumber
+Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18}. \nonumber
 \end{align}
@@
 \begin{align}
-p &= 2\cdot(1-\Phi(\abs{Z})) \nonumber
+p &= 2\cdot(1-\Phi(\abs{Z})). \nonumber
 \end{align}
@@
 \begin{align}
-\theta/\se &= \beta_0 + \beta_1/\se + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:radial.plot} 
+\theta/\se &= \beta_0 + \beta_1/\se + \epsilon, & \epsilon \sim N(0, \sigma^2). \label{eq:radial.plot} 
 \end{align}
@@
 \end{align}
-
 with weights $w = 1/\se^2$.
@@
 \begin{align}
-\theta_i \sim N(\beta_0 + \beta_1 \se_i, \se_i^2 + \tau^2) \label{t.sharp.regression}
+\theta_i \sim N(\beta_0 + \beta_1 \se_i, \se_i^2 + \tau^2). \label{t.sharp.regression}
 \end{align}
@@
 \varphi &= e_t - (e_t - e_c)(e_t + (n_t - e_t))/(n_t + n_c) \nonumber \\
- \se^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \nonumber
+ \se^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)}. \nonumber
 \end{align}
@@
 \subsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
-\citealp{Schwarzer} developed a test for the correlation between the event counts in the treatment group and the expected event counts $E_t - \mathbb{E}(E_t)$, where $E_t$ is a random variable.
+\citet{Schwarzer} developed a test for the correlation between the event counts in the treatment group and the expected event counts $E_t - \mathbb{E}(E_t)$, where $E_t$ is a random variable.
 When the marginals in a two-by-two table and the log odds ratio are fixed, it can be shown that $E_t$ follows a non-central hypergeometric distribution.
@@
 \end{align}
-
 are then used as before in Begg and Mazumdar's test.
@@
 \theta_i &= \arcsin{(e_t/n_t)} - \arcsin{(e_c/n_c)} \nonumber &
-\se_i^2 &= 1/(4n_t) + 1/(4n_c) \nonumber
+\se_i^2 &= 1/(4n_t) + 1/(4n_c). \nonumber
 \end{align}
@@
 \\
-\citealp{excess.significance} developed an exploratory test to detect if the proportion of significant findings is larger than expected. 
+\citet{excess.significance} developed an exploratory test to detect if the proportion of significant findings is larger than expected. 
 %Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study. \\
@@
 \end{align}
-
 with $F$ being the cumulative normal distribution with mean $\hat{\theta}_M$ and standard deviation $\hat{\se}_i$. \\
@@
 \begin{align}
-E &= \sum_{i = 1}^n (1 - \beta_i) \nonumber
+E &= \sum_{i = 1}^n (1 - \beta_i). \nonumber
 \end{align}
@@
 \end{align}
-
 and consecutively, calculating a $p$\hspace{0.4mm}-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
@@
 \end{align}
-
 with $p = E/n$ and $X$ being a binomial random variable with probability $p$.
@@
 \theta_i & = \beta_0 + \beta_1\sqrt{\se_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \label{eq:limitmeta.regression} \\
-\epsilon_i &\stackrel{\textrm{iid}}{\sim} N(0,1)
+\epsilon_i &\stackrel{\textrm{iid}}{\sim} N(0,1).
 \end{align}
@@
 \mathbb{E}\big((\theta_i - \beta_0)/\sqrt{\se_i^2}\big) \rightarrow \beta_1 \textrm{ if } \se_i \rightarrow \infty \nonumber \\ %\label{limitmeta.infinitesample} \\
-\mathbb{E}(\theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} \se_i \rightarrow 0 \nonumber
+\mathbb{E}(\theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} \se_i \rightarrow 0. \nonumber
 \end{align}
@@
 Formally, the probability of selection given a reported standard error $\se$ is defined as
-
-\begin{align}
-P(\textrm{select}\given \se) &= \Phi(a + b/\se) \nonumber %\label{copas.selection1}
+\begin{align}
+P(\textrm{select}\given \se) &= \Phi(a + b/\se). \nonumber %\label{copas.selection1}
 \end{align}
@@
 \end{align}
-
 with $\delta \sim N(0,1)$. $z$ is interpreted as the \textit{propensity for selection}. It is defined that the sign of $z$ must be positive in order for the study to be selected.
@@
 \end{align}
-
 where $(\epsilon_i, \delta_i)$ are standard normal residuals.
@@
 P(\textrm{select} \given \se_i, \theta_i) = %P(a,b,s,y) = 
-\Phi\bigg(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i}^2}}\bigg) \nonumber
+\Phi\bigg(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i}^2}}\bigg). \nonumber
 \end{align}
@@
 \end{align}
-
 increases for larger $\sigma$.\\
@@
 \begin{align}
-\textrm{Var}(\theta_i\given \se_i, z_i > 0) = \sigma_i^2 (1 - c_i^2\rho_i^2) \nonumber
+\textrm{Var}(\theta_i\given \se_i, z_i > 0) = \sigma_i^2 (1 - c_i^2\rho_i^2). \nonumber
 \end{align}
@@
 \begin{align}
-\mathbb{E}(\theta_i\given z_i > 0, a^\star, b^\star) - \mathbb{E}(\theta_i\given z_i > 0, a, b) \approx c^\star + \rho(\lambda(a^\star) - \lambda(a))\se_i \nonumber
+\mathbb{E}(\theta_i\given z_i > 0, a^\star, b^\star) - \mathbb{E}(\theta_i\given z_i > 0, a, b) \approx c^\star + \rho(\lambda(a^\star) - \lambda(a))\se_i. \nonumber
 \end{align}
@@
 \begin{align}
-\theta_i &= \theta + \beta \se_i + \sigma_i \epsilon_i \nonumber
+\theta_i &= \theta + \beta \se_i + \sigma_i \epsilon_i. \nonumber
 \end{align}
@@
 \begin{align}
-\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n\bigg[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta \se_i)^2}{(\tau^2 + \sigma_i^2)}\bigg] \nonumber
+\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n\bigg[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta \se_i)^2}{(\tau^2 + \sigma_i^2)}\bigg]. \nonumber
 \end{align}
@@
 \begin{align}
-d &= \theta \frac{\sqrt{3}}{\pi} & \se_d^2 =  \se^2\frac{\sqrt{3}}{\pi} \nonumber
+d &= \theta \frac{\sqrt{3}}{\pi} & \se_d^2 =  \se^2\frac{\sqrt{3}}{\pi}. \nonumber
 \end{align}
@@
 \\
-The Pearson's correlation coefficient can be attained by the formulas (\citealp{olkin1985dtor}, \cite[48]{Intro.meta})
+The Pearson's correlation coefficient can be attained by the formulas:
 
@@
 
-where $a$ is a correction factor if $n_t \neq n_c$. The variance of $r$, $\se_r^2$ is computed by
-
-\begin{align}
-\se_r^2 &= \frac{a^2 \se_d^2}{(d^2 + a)^3} \nonumber
+where $a$ is a correction factor if $n_t \neq n_c$ (\citealp{olkin1985dtor}, \citealp{Intro.meta}). The variance of $r$, $\se_r^2$ is computed by
+
+\begin{align}
+\se_r^2 &= \frac{a^2 \se_d^2}{(d^2 + a)^3}. \nonumber
 \end{align}
@@
 %z &= \arctan(r) & \nonumber
-\se_z^2 &= \frac{1}{n-3}
+\se_z^2 &= \frac{1}{n-3}.
 \end{align}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Thu Aug 22 13:59:23 2019
+% Fri Aug 23 14:07:28 2019
 \begin{table}[ht]
@@
 Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
-Further descriptive variables have been ommitted}
+Further descriptive variables have been ommitted.}
 \label{barbiturate.row}
@@
     \end{tabular}
-  \caption{Dataset variable names and descriptions  \label{variable}}
+  \caption{Dataset variable names and descriptions.  \label{variable}}
   \label{variable}
@@
 \endgroup
-\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given} 
+\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given.} 
 \label{barbiturates}
@@
 \endgroup
-\caption{Number of missing variables and measurements in the dataset} 
+\caption{Number of missing variables and measurements in the dataset.} 
 \label{missing}
@@
 If outcome is \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR} / \texttt{RR} / \texttt{SMD} / \texttt{MD} / \texttt{Hazard Ratio} / \texttt{Rate Ratio} are used.
-\citealp{Ioannidis2007} outlined criteria for application of small study effect tests:
+\citet{Ioannidis2007} outlined criteria for application of small study effect tests:
 \begin{itemize}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 21 08:50:02 2019
+% Fri Aug 23 14:07:42 2019
 \begin{table}[ht]
@@
        for outcome types. Last entry for continuous and IV outcomes is empty since one test less was 
-       applied} 
+       applied.} 
 \label{number.sig.tests}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 21 08:50:17 2019
+% Fri Aug 23 14:07:57 2019
 \begin{table}[ht]
@@
 \end{knitrout}
-\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ 560)}
+\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ 560).}
 \label{fig:copas.missing}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 21 08:50:18 2019
+% Fri Aug 23 13:57:11 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 21 08:50:27 2019
+% Fri Aug 23 13:57:19 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 21 08:50:28 2019
+% Fri Aug 23 13:57:20 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 21 08:50:31 2019
+% Fri Aug 23 13:57:23 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 21 08:50:33 2019
+% Fri Aug 23 13:57:25 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 21 08:50:36 2019
+% Fri Aug 23 13:57:28 2019
 \begin{table}[ht]
@@
 Furthermore, transformation of mean differences to std.
-mean differences also comes with the unpleasant consequence that effect size and std.
-mean difference are no longer independent (smaller differences for large std.
-errors).
+mean differences also comes with the unpleasant consequence that the estimates of effect size and std.
+mean difference are no longer independent (as for mean differences, where the effect size and standard error is not mathematically linked).
+This will lead to false positives.
 When transforming odds ratios to std.
-mean differences, the dependence between effect size and std.
-mean difference is also retained.
-Analyzing publication bias with
-std. mean differences might lead to false positives and false negatives. Using Fisher's $z$-score is more appropriate since standard errors and effect sizes are independent.\\
+mean differences, the dependence between the estimated log odds ratio and std.
+error is also retained, again leading to false positives.
+See \citet{deeks.2005} for a thorough discussion of correlation between effect sizes and standard errors in publication bias tests.
+Using Fisher's $z$-score is more appropriate since standard errors and effect sizes are independent.\\
 
@@
 Treatment effect adjustment and consequences of adjustment for evidence for treatment effect could subsequently be analysed more carefully.
-Related to this, implementation of a likelihood ratio test in Copas selection model, as proposed by the Authors, would be feasible and increase accuracy.
+Related to this, implementation of a likelihood ratio test in Copas selection model, as proposed by the authors, would be feasible and increase accuracy.
 \\
@@
 \section{Implications}
-As far as we know, this study is so far the largest assessment of publication bias by small study effects and uses also data that has been collected after major efforts have been made to curb publication bias.
+As far as we know, this study is so far one of the largest assessment of publication bias by small study effects and uses also data that has been collected after major efforts have been made to curb publication bias.
 %It is the first analysis of the Cochrane Library of Systematic Reviews also analyzing publication bias using hazard and rate ratios.
-Furthermore, the analysis includes time-to-event data which is, as far as we are aware of, unprecedented, and continuous outcomes, which is unusual.
-Thus we assume that it is so far the most complete, thorough analysis of publication bias in the Cochrane library.
+Furthermore, the analysis includes time-to-event data which is, as far as we are aware of, unprecedented, and continuous outcomes, which are often not considered.
+Thus, we assume that it is so far the most complete, thorough analysis of publication bias in the Cochrane library.
 \\
@@
 We find a proportion of significant test results well above the expected false positive rate of the tests of 10\%.\\
-Also, it is the first study to extensively adjust the combined effect sizes from meta-analyses for publication bias.
+Also, it is among the first study to extensively adjust the combined effect sizes from meta-analyses for publication bias.
 It has been found repeatedly that publication bias might threaten the validity of the findings of some meta-analyses from Cochrane systematic reviews.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Wed Aug 21 08:51:20 2019
+% Fri Aug 23 13:58:08 2019
 \begin{table}[ht]

### 2019-08-23 report/chapter01.Rnw
final draft
corrections

@@
 par(mfrow = c(1,2))
-funnel(x = meta.id(ex.se), ylim = c(1.60, 0), comb.fixed = F, comb.random = F)
-funnel(x = meta.id(ex.nose), ylim = c(1.60, 0), comb.fixed = F, comb.random = F, ylab = NULL)
+funnel(x = meta.id(ex.se), ylim = c(1.60, 0), comb.fixed = F, comb.random = F, pch = 20, las = 1)
+funnel(x = meta.id(ex.nose), ylim = c(1.60, 0), comb.fixed = F, comb.random = F, ylab = NULL, pch = 20, las = 1)
 @

### 2019-08-23 report/chapter02.Rnw
corrections

@@
 \subsection{Continuous Outcomes}
-For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference as well as a standardized mean difference (also known as Cohen's $d$) and the standard error thereof.
+For given $(m_t, m_c), (\textrm{sd}_t, \textrm{sd}_c)$ and $(n_t, n_c)$, one can compute mean difference $\theta$ as well as a standardized mean difference (also known as Cohen's $d$) and the standard error thereof.
 
 \begin{align}
-\theta &= m_t - m_c & \se &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_c}
+\theta &= m_t - m_c & \textrm{sd}_\theta &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_c}.
 \end{align}
 
-Cohen's $d$ and its standard error $\se$ can similarly be obtained by
+Cohen's $d$ and its standard error $\textrm{sd}_d$ can similarly be obtained by
 
 \begin{align}
-d &= \frac{m_t - m_c}{\se} \label{eq:hedges.g} & \se &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}}
+d &= \frac{m_t - m_c}{\textrm{sd}_\theta} & 
+\textrm{sd}_d &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}}. \label{eq:cohensd}
 \end{align}
@@
 Both estimators take into account that the two groups might have unequal variances. \\ 
-A  $p$\hspace{0.4mm}~-~value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$-test.
-The $t$ statistic is obtained, using $\se$ and $d$ from \eqref{eq:hedges.g}, by
+A  $p$\hspace{0.4mm}-value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$-test.
+The $t$ statistic is obtained, using $\textrm{sd}_d$ and $d$ from \eqref{eq:cohensd}, by
 
 \begin{align}
-t &= d/(\se\sqrt{(1/n_t)+(1/n_c)}) \nonumber
+t &= d/(\textrm{sd}_d\sqrt{(1/n_t)+(1/n_c)}) \nonumber
 \end{align}
-and the  $p$\hspace{0.4mm}~-~value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
+and the  $p$\hspace{0.4mm}-value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:
 
 \begin{align}
-p &= 2(1-F(\abs{t})) \nonumber
+p &= 2(1-F(\abs{t})). \nonumber
 \end{align}
@@
 \begin{align}
-\hat{\theta} &= \log(\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}) \nonumber \\
-\hat{\se}^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
+\hat{\theta} &= \log\bigg[\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}\bigg] \nonumber \\
+\hat{\se}^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c). \nonumber
 \end{align}
@@
 \begin{align}
-\hat{\theta} &= \log(\frac{e_t/n_t}{e_c/n_c}) \label{eq:risk.ratio} \\
-\se^2&= 1/e_t - 1/n_t + 1/e_c - 1/n_c \label{eq:risk.ratio.variance}
+\hat{\theta} &= \log\bigg(\frac{e_t/n_t}{e_c/n_c}\bigg) \label{eq:risk.ratio} \\
+\se^2&= 1/e_t - 1/n_t + 1/e_c - 1/n_c. \label{eq:risk.ratio.variance}
 \end{align}
 
-Assuming binomial distribution of the events and using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a  $p$\hspace{0.4mm}~-~value, \eg \cite[98]{held2014}.
+Assuming binomial distribution of the events and using likelihood theory, one could show that the estimators are maximum likelihood estimators and that one can use the asymptotic normal distribution of the maximum likelihood estimator to calculate a  $p$\hspace{0.4mm}-value, \eg \cite[98]{held2014}.
 The approximation is only good if there are enough events and sample size is large enough.\\
@@
 \begin{align}
-p &= 2\cdot(1-\Phi(|\hat{\theta}/\hat{\se}|), \nonumber
+p &= 2\cdot(1-\Phi(|\hat{\theta}/\hat{\se}|)), \nonumber
 \end{align}
-a  $p$\hspace{0.4mm}~-~value for the corresponding estimate, which summarizes the evidence against $\hat{\theta}$ being zero (\ie the true risk/odds ratio being 1). \\
+a $p$\hspace{0.4mm}-value for the corresponding estimate, which summarizes the evidence against $\hat{\theta}$ being zero (\ie the true risk/odds ratio being 1). \\
 Odds ratios can be transformed to std. mean differences, which will be described in Section \ref{sec:transformation.effectsizes}.
@@
 \theta_M &= \frac{\sum_{i = 1}^n w_i \theta_i}{\sum_{i = 1}^n w_i} &
-\se_M^2 &= \frac{1}{\sum_{i = 1}^n w_i} \label{eq:fixed.effects}
+\se_M^2 &= \frac{1}{\sum_{i = 1}^n w_i}. \label{eq:fixed.effects}
 \end{align}
@@
 An estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and variances $\hat{\theta}_i$ and $\hat{\se}_i^2$.
-The underlying idea is that we assume $\theta_i \sim N(\theta_M, \se_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.
-\\
+The underlying idea is that we assume $\theta_i \sim N(\theta_M, \se_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.\\
 The random effects model \citep{whitehead} assumes instead that 
@@
 Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i} \label{eq:Q.heterogeneity} \\
-\tau^2 &= \max\big(0, \frac{Q - (n-1)}{C}\big) \label{eq:Tau.definition}
+\tau^2 &= \max\bigg[0, \frac{Q - (n-1)}{C}\bigg]. \label{eq:Tau.definition}
 \end{align}
@@
 \begin{align}
-y &= \beta_0 + \beta_1 x + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:simple.regression}
+y &= \beta_0 + \beta_1 x + \epsilon, & \epsilon \sim N(0, \sigma^2). \label{eq:simple.regression}
 \end{align}
@@
 We look for the solution that minimizes the squared residuals, the least-squares solution.
-Formally,
+Formally, we write:
 
 \begin{align}
-\operatorname*{argmin}_{\beta_0, \beta_1}\Big(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i\Big) \label{eq:least.squares}
+\operatorname*{argmin}_{\beta_0, \beta_1}\Big(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i\Big). \label{eq:least.squares}
 \end{align}
@@
 $\bar{x}$ and $\bar{y}$ denoting the sample means of the corresponding values $x_1, .., x_n$ and $y_1, ..., y_n$. Thus, $\hat{\beta}_0$ is also called the global mean.
-To test whether there is evidence for the intercept $\beta_0$ to be unequal to some value $\beta_{H0}$, a $t$-test can be used.
+To test whether there is evidence for the intercept $\beta_0$ to be unequal to some value $\beta_{H0}$, a $t$-test can be used:
 
 \begin{align}
-p &= 2(1-F(\abs{(\beta_0 - \beta_{H0})/s_{\beta_0}})) \nonumber
+p &= 2(1-F(\abs{(\beta_0 - \beta_{H0})/s_{\beta_0}})), \nonumber
 \end{align}
-
-where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. The  $p$\hspace{0.4mm}~-~value will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
+where $F$ is the cumulative $t$ distribution with $n-2$ degrees of freedom. The  $p$\hspace{0.4mm}-value will give the evidence against the null hypothesis $\beta_0 = \beta_{H0}$. \\
 The concept is extendable to weighted linear regression.
@@
 \begin{align}
-\mathbf{y}_i|U_j,\epsilon_{i} =  x_i\beta + U_j + \epsilon_{i} \label{eq:one.random.intercept}
+\mathbf{y}_i \given U_j,\epsilon_{i} =  x_i\beta + U_j + \epsilon_{i}. \label{eq:one.random.intercept}
 \end{align}
-
 gives the marginal distribution of $\mathbf{y}_i$ depending on $U{_j}$ and $\epsilon_i$.
@@
 \begin{align}
-\Cov(\mathbf{y}_j) &= \mathbf{D}_j \mathbf{G} \mathbf{D}_j^\top + \tau^2 \mathbf{I}_{n_j} \label{eq:random.intercepts.covariance}
+\Cov(\mathbf{y}_j) &= \mathbf{D}_j \mathbf{G} \mathbf{D}_j^\top + \tau^2 \mathbf{I}_{n_j}. \label{eq:random.intercepts.covariance}
 \end{align}
-
 where $\D_j$ is in the case of the random intercept model a $n_j \times 1$ matrix of 1's, $\mathbf{G}$ is a scalar to be estimated and $\mathbf{I}_{n_j}$ is an $n_j \times n_j$ identity matrix.
@@
 \begin{align}
-\mathbf{y}_i|U_j,\epsilon_i =  x_i\beta + x_i \mathbf{U}_j + \epsilon_i \label{eq:one.random.intercept.and.slope}
+\mathbf{y}_i \given U_j,\epsilon_i =  x_i\beta + x_i \mathbf{U}_j + \epsilon_i. \label{eq:one.random.intercept.and.slope}
 \end{align}
@@
 \begin{align}
-\hat{\beta} &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1} \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{y}_j
+\hat{\mathbf{\beta}} &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1} \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{y}_j
 \end{align}
-
 with $m$ being the number of groups and $\hat{\mathbf{V}}_j$ being the estimated covariance, obtained by maximizing the log likelihood of the normal distribution, as $\mathbf{y}_j$ is distributed as
@@
 \begin{align}
-\mathbf{y}_j \sim N(\mathbf{x}_j \beta, \mathbf{V}_j)
+\mathbf{y}_j \sim N(\mathbf{x}_j \mathbf{\beta}, \mathbf{V}_j). \nonumber
 \end{align}
@@
 Thus, large number of concordant pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$.
-A two-sided  $p$\hspace{0.4mm}~-~value is obtained using the standard normal distribution $\Phi$:
+A two-sided  $p$\hspace{0.4mm}-value is obtained using the standard normal distribution $\Phi$:
 \begin{align}
-p &= 2\cdot(1-\Phi(\abs{Z})) \nonumber
+p &= 2\cdot(1-\Phi(\abs{Z})). \nonumber
 \end{align}
@@
 \end{align}
-
 with weights $w = 1/\se^2$.
 Thus testing $\beta_0$ of \eqref{eq:radial.plot} or $\beta_1$ of \eqref{eq:egger.plot} is equivalent.
-The corresponding  $p$\hspace{0.4mm}~-~value is then used as evidence for a small study effect.
+The corresponding  $p$\hspace{0.4mm}-value is then used as evidence for a small study effect.
 Plugging in  $\theta_i/\se_i, 1/\se_i$ as $y_i, x_i$ into equations \eqref{eq:regression.parameters} and \eqref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{\se}_{\beta_0}$ and $\hat{\se}_{\beta_1}$.
@@
 \subsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
-\citealp{Schwarzer} developed a test for the correlation between the event counts in the treatment group and the expected event counts $E_t - \mathbb{E}(E_t)$.
+\citet{Schwarzer} developed a test for the correlation between the event counts in the treatment group and the expected event counts $E_t - \mathbb{E}(E_t)$, where $E_t$ is a random variable.
 When the marginals in a two-by-two table and the log odds ratio are fixed, it can be shown that $E_t$ follows a non-central hypergeometric distribution.
@@
 \begin{align}
-(e_t - \mathbb{E}(E_t))/\sqrt(\se_i^2)
+(e_t - \mathbb{E}(E_t))/\se_i
 \end{align}
-
 are then used as before in Begg and Mazumdar's test.
@@
 \begin{align}
-\theta_i &= \arcsin{e_t/n_t} - \arcsin{e_c/n_c} \nonumber &
-\se_i^2 &= 1/4n_t + 1/4n_c \nonumber
+\theta_i &= \arcsin{(e_t/n_t)} - \arcsin{(e_c/n_c)} \nonumber &
+\se_i^2 &= 1/(4n_t) + 1/(4n_c). \nonumber
 \end{align}
@@
 \end{align}
-
-and consecutively, calculating a $p$\hspace{0.4mm}~-~value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
+and consecutively, calculating a $p$\hspace{0.4mm}-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom.
 Alternatively, one can also use a binomial test, which is encouraged when $n$ and $O$ is small.
@@
 Formally, the probability of selection given a reported standard error $\se$ is defined as
-
 \begin{align}
-P(\textrm{select}\given \se) &= \Phi(a + b/\se) \nonumber %\label{copas.selection1}
+P(\textrm{select}\given \se) &= \Phi(a + b/\se). \nonumber %\label{copas.selection1}
 \end{align}
@@
 P(\textrm{select} \given \se_i, \theta_i) = %P(a,b,s,y) = 
-\Phi\bigg(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i^2}}}\bigg) \nonumber
+\Phi\bigg(\frac{u_i + \tilde{\rho_i}((\theta_i - \mu)/\sqrt(\tau^2 + \sigma_i^2))}{\sqrt{1 - \tilde{\rho_i}^2}}\bigg). \nonumber
 \end{align}
@@
 \begin{align}
-\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta \se_i)^2}{(\tau^2 + \sigma_i^2)}] \nonumber
+\tilde{L}(\theta, \tau, \beta) = -\frac{1}{2}\sum_{i = 1}^n\bigg[\log(\tau^2 + \sigma_i^2) + \frac{(\theta_i - \theta - \beta \se_i)^2}{(\tau^2 + \sigma_i^2)}\bigg]. \nonumber
 \end{align}
 
-$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$\hspace{0.4mm}~-~value.
+$\chi^2$ can be used with a $\chi^2$ distribution with one degree of freedom to obtain a $p$\hspace{0.4mm}-value.
 Note that the test is very similar to Egger's small study effect test when $\tau^2 = 0$.\\
@@
 
-where $a$ is a correction factor if $n_t \neq n_c$. The variance of $r$, $\se_r^2$ is computed by
+where $a$ is a correction factor if $n_t \neq n_c$ (\citealp{olkin1985dtor}, \citealp{Intro.meta}). The variance of $r$, $\se_r^2$ is computed by
 
 \begin{align}
-\se_r^2 &= \frac{a^2 \se_d^2}{(d^2 + a)^3} \nonumber
+\se_r^2 &= \frac{a^2 \se_d^2}{(d^2 + a)^3}. \nonumber
 \end{align}
@@
 \begin{align}
-z &= 0.5 \ln\big(\frac{1 + r}{1 - r}\big) & \nonumber
+z &= 0.5 \ln\bigg(\frac{1 + r}{1 - r}\bigg) & \nonumber
 %z &= \arctan(r) & \nonumber
-\se_z^2 &= \frac{1}{n-3}
+\se_z^2 &= \frac{1}{n-3}.
 \end{align}

### 2019-08-23 report/chapter03.Rnw
osf URL
corrections

@@
 Events denotes the count of events in the treatment group while Events c the count of events in the group compared to.
-Further descriptive variables have been ommitted"),
+Further descriptive variables have been ommitted."),
       include.rownames = F, size = "scriptsize")
@@
 print(xtable(barbi2, label = "barbiturates", caption = "Barbiturate and head injury review.
-In the columns, study names, comparison and outcome measure of the results are given"), include.rownames = F, size = "footnotesize")
+In the columns, study names, comparison and outcome measure of the results are given."), include.rownames = F, size = "footnotesize")
 @
@@
 <<echo=FALSE, results='asis', warning =FALSE, message = FALSE>>=
-print(xtable(missing.table, label = "missing", caption = "Number of missing variables and measurements in the dataset", align = "lr"), include.colnames = F,
+print(xtable(missing.table, label = "missing", caption = "Number of missing variables and measurements in the dataset.", align = "lr"), include.colnames = F,
       size = "footnotesize", digits = 0)

### 2019-08-23 report/chapter04.Rnw
corrections

@@
        for outcome types. Last entry for continuous and IV outcomes is empty since one test less was 
-       applied", label = "number.sig.tests", align = "lccc"), include.rownames = F, size = "footnotesize")
+       applied.", label = "number.sig.tests", align = "lccc"), include.rownames = F, size = "footnotesize")
 @
@@
 <<echo = FALSE, warning=FALSE, fig.height=5>>=
-par(mfrow = c(2,3), cex.lab = 1.5, cex.axis = 1.5)
+par(mfrow = c(2,3), cex.lab = 1.5, cex.axis = 1.5, las = 1, mar = c(5.1,6,4.1,2.1),mgp=c(4,1,0))
 example <- data.ext2 %>% filter(meta.id == 81244)
@@
 @
-\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ \Sexpr{sum(!is.na(meta.f$missing.copas))})}
+\caption{Histogram of the fraction of missing studies from the total number of studies in a meta-analyses (only data shown where Copas estimate was obtained, thus \\$n =$ \Sexpr{sum(!is.na(meta.f$missing.copas))}).}
 \label{fig:copas.missing}
@@
                        weights = ~ se.z.mirrored^2, method = "ML", data = reg.dat)
-plot(y = reg.dat$z.mirrored, x = reg.dat$se.z.mirrored, cex = .1, xlab = "standard error", ylab = "z mirrored")
+plot(y = reg.dat$z.mirrored, x = reg.dat$se.z.mirrored, cex = .1, xlab = "standard error", ylab = "z mirrored", las = 1)
 publication.bias.fit.coef <- summary(publication.bias.fit)$coefficients$fixed

### 2019-08-28 report/MSc_Report.tex
Final Version

@@
 The research questions are: Are effects in meta-analyses \textit{larger} if their standard errors are small, and are there \textit{more} significant effects than expected?
-and How can this affect the combined treatment effects as commonly obtained by meta-analysis?.
+How can this affect the combined treatment effects as commonly obtained by meta-analysis?
 To answer these questions, methods to detect and adjust for publication bias in meta-analysis are applied on the data.\\
@@
 The difference in this measure between the groups is referred to as the treatment effect.
-Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, log rate ratio, Cohen's $d$ or standardized mean difference, Fisher's z transformed score.\\
+Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, log rate ratio, Cohen's $d$ or standardized mean difference, Fisher's $z$ transformed score.\\
 Let us consider a meta-analysis with $n$ study treatment effects ($n > 1$, but typically small).
@@
 
-Let $\mathbf{\beta} = (\beta_0, \beta_1)^\top$. It can be shown that
-
-\begin{align}
-\hat{\mathbf{\beta}} &= (\mathbf{X}^\top \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
-\end{align}
-is an estimator of $\mathbf{\beta}$ that minimizes the squared residuals.
-Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\mathbf{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$.
+Let $\boldsymbol{\beta} = (\beta_0, \beta_1)^\top$. It can be shown that
+
+\begin{align}
+\hat{\boldsymbol{\beta}} &= (\mathbf{X}^\top \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
+\end{align}
+is an estimator of $\boldsymbol{\beta}$ that minimizes the squared residuals.
+Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\boldsymbol{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$.
 The variance estimates $\hat{\sigma}^2$ and $\hat{\mathbf{s}}_\beta^2$ are
@@
 \begin{align}
-\mathbf{y}_i \given U_j,\epsilon_{i} =  x_i\beta + U_j + \epsilon_{i}. \label{eq:one.random.intercept}
+\mathbf{y}_i \given U_j,\epsilon_{i} =  x_i\boldsymbol{\beta}+ U_j + \epsilon_{i}. \label{eq:one.random.intercept}
 \end{align}
@@
 \begin{align}
-\mathbf{y}_i \given U_j,\epsilon_i =  x_i\beta + x_i \mathbf{U}_j + \epsilon_i. \label{eq:one.random.intercept.and.slope}
+\mathbf{y}_i \given U_j,\epsilon_i =  x_i\boldsymbol{\beta}+ x_i \mathbf{U}_j + \epsilon_i. \label{eq:one.random.intercept.and.slope}
 \end{align}
@@
 \begin{align}
-\hat{\mathbf{\beta}} &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1} \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{y}_j
+\hat{\boldsymbol{\beta}} &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1} \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{y}_j
 \end{align}
@@
 \begin{align}
-\mathbf{y}_j \sim N(\mathbf{x}_j \mathbf{\beta}, \mathbf{V}_j). \nonumber
+\mathbf{y}_j \sim N(\mathbf{x}_j \boldsymbol{\beta}, \mathbf{V}_j). \nonumber
 \end{align}
@@
 Weights can be introduced by replacing $\mathbf{I}_{n_j}$ in \eqref{eq:random.intercepts.covariance} with the previously introduced weight matrix $\mathbf{W}_j$.
-Hypothesis tests for $\beta = \beta_\textrm{H0}$ can be made using the Wald method.
+Hypothesis tests for $\boldsymbol{\beta}= \boldsymbol{\beta}_\textrm{H0}$ can be made using the Wald method.
 \\
@@
 At the end of a systematic review, ``a systematic presentation, and synthesis, of the characteristics and findings of the included studies'' is done. \\
-Fifty three Cochrane Review Groups prepare and maintain the reviews within specific areas of health care.
+Fifty three Cochrane Review groups prepare and maintain the reviews within specific areas of health care.
 A group consists of ``researchers, healthcare professionals and people using healthcare services (consumers)''.
 \\
-The groups are supported by Method Groups, Centers and Fields.
-The Cochrane Method Groups aim to discuss and consult the groups in methodological questions concerning review preparation.
-The Centers play a main role in training and support of the Groups.
-The Fields are responsible for broad medical research areas and follow priorities in those areas by advice and control of the groups.
+The groups are supported by Method groups, centers and fields.
+The Cochrane Method groups aim to discuss and consult the groups in methodological questions concerning review preparation.
+The centers play a main role in training and support of the groups.
+The fields are responsible for broad medical research areas and follow priorities in those areas by advice and control of the groups.
 \\
@@
 \\
-In order to avoid potential conflicts of interests, there is a code of conduct that all entities of Cochrane have to agree on: conflicts of interest must be disclosed and possibly be forwarded to the Cochrane Center, and participation of review authors in the studies used have to be acknowledged.
-Additionally, a Steering Group publishes a report of potential conflicts of interests based on information about external funding of Cochrane Groups.
+In order to avoid potential conflicts of interests, there is a code of conduct that all entities of Cochrane have to agree on: conflicts of interest must be disclosed and possibly be forwarded to the Cochrane center, and participation of review authors in the studies used have to be acknowledged.
+Additionally, a Steering group publishes a report of potential conflicts of interests based on information about external funding of Cochrane groups.
 \\
@@
 This can reflect some advance in clinical science as for example new information about important subgroups, as well as new methods for conducting a Cochrane review.
-However, there are no clear guidelines and the Cochrane Groups are free in the rate and extent of up-dating their reviews.
+However, there are no clear guidelines and the Cochrane groups are free in the rate and extent of up-dating their reviews.
 
@@
 Therefore, the search process is crucial, as a selective search result may impose bias on the sample of studies available, making it a non-random sample.
-For this purpose, the Cochrane Groups are advised to go beyond MEDLINE, because a search restricted to it has been shown to deliver only 30\% to 80\% of available studies.
+For this purpose, the Cochrane groups are advised to go beyond MEDLINE, because a search restricted to it has been shown to deliver only 30\% to 80\% of available studies.
 ``Time and budget restraints require the review author to balance the thoroughness of the search with efficiency in use of time and funds and the best way of achieving this balance is to be aware of, and try to minimize, the biases such as publication bias and language bias that can result from restricting searches in different ways.'' It is important to note that not only studies, but also study reports are occasionally used in the reviews, as they may provide useful information.
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug 23 14:07:28 2019
+% Wed Aug 28 08:50:16 2019
 \begin{table}[ht]
@@
     \end{tabular}
-  \caption{Dataset variable names and descriptions.  \label{variable}}
+  \caption{Dataset variable names and descriptions.}
   \label{variable}
@@
 The median of the publication years is 2003, the mean 2001 and the quartiles are 1996 and 2008.
-NULL studies have been published in 2018.\\
+1,075 studies have been published in 2018.\\
 The most frequent outcome measures are summarized in Table \ref{outcome.measure.frequencies}.
@@
 \item \texttt{lrr} and \texttt{var.lrr}: log risk ratio and variance of the log risk ratio for \texttt{outcome.flag} \texttt{DICH}.
-\item \texttt{cohensd} and \texttt{var.cohensd}: Cohen's $d$ and the variance for \texttt{outcome.flag} \texttt{CONT}'. 
+\item \texttt{cohensd} and \texttt{var.cohensd}: Cohen's $d$ and the variance for \texttt{outcome.flag} \texttt{CONT}. 
 \item \texttt{smd.ordl} and \texttt{var.smd.ordl}: Cohen's $d$ and its variance as obtained by transformation of a log odds ratio for \texttt{outcome.flag} \texttt{DICH}.
-\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for \texttt{outcome.flag} \texttt{DICH}) or $d$ (for \texttt{outcome.flag} \texttt{CONT}') to $r$ transformation.
-\item \texttt{z} and \texttt{var.z}: Fisher's z score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
-\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for \texttt{outcome.flag} \texttt{CONT}' or Wald test for \texttt{outcome.flag} \texttt{DICH}.
+\item \texttt{cor.Pearson} and \texttt{var.cor.Pearson}: Pearson correlation coefficient and variance as obtained from the $d$ (for \texttt{outcome.flag} \texttt{DICH}) or $d$ (for \texttt{outcome.flag} \texttt{CONT}) to $r$ transformation.
+\item \texttt{z} and \texttt{var.z}: Fisher's $z$ score and it's variance obtained from the Pearson correlation $r$ to $z$ transformation.
+\item \texttt{pval.single}: $p$-value against the null hypothesis of no treatment effect, derived by a $t$-test for \texttt{outcome.flag} \texttt{CONT} or Wald test for \texttt{outcome.flag} \texttt{DICH}.
 \item \texttt{events1c} and \texttt{events2c}: Correction of \texttt{events1} and \texttt{events2} zero event counts or event counts = patient number.
@@
 \subsubsection{Exclusions for other Reasons}
-In some more cases, meta-analyses were excluded because their results seemed to be erroneous (1) or because participant numbers were missing (5), necessary to compute the variance of Fisher's z transformed correlation coefficient.
+In some more cases, meta-analyses were excluded because their results seemed to be erroneous (1) or because participant numbers were missing (5), necessary to compute the variance of Fisher's $z$ transformed correlation coefficient.
 The latter meta-analyses (all \texttt{outcome.flag} = \texttt{IV}) were only omitted when doing the adjustment based on the Fisher's $z$ transformed correlations, but kept when adjusting based on std.
@@
 \\
-From the meta-analyses with incomplete data (\texttt{outcome.flag} == \texttt{IV}), there are 36 with \\ \texttt{outcome.measure.merged} = \texttt{RR}, 26 \texttt{SMD},  25 \texttt{Hazard Ratio}, 15 \texttt{OR}, 11 \texttt{MD} and 8 \texttt{Rate Ratio}.
+From the meta-analyses with incomplete data (\texttt{outcome.flag} == \texttt{IV}), there are 36 meta-analyses with \\ \texttt{outcome.measure.merged} = \texttt{RR}, 26 \texttt{SMD},  25 \texttt{Hazard Ratio}, 15 \texttt{OR}, 11 \texttt{MD} and 8 \texttt{Rate Ratio}.
 
@@
 Meta-analysis within a review were obtained by grouping by comparison, outcome and subgroup.
-The last step is optional, and the Cochrane Groups do also meta-analysis without taking into account subgroups.
+The last step is optional, and the Cochrane groups do also meta-analysis without taking into account subgroups.
 Subgroups are often specifications of treatment, \eg the form of the medication or the protocol.
@@
 When one subgroup has substantially different real treatment effects, and the specific properties influence study size, publication bias assessment fails.
-Subgroups are not indicated in 50.8\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane Review Groups did.
+Subgroups are not indicated in 50.8\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane Review groups did.
 \\
@@
 
-The meta-analyses fulfilling the criteria from Chapter \ref{ch:dataset}, Section \ref{sec:Processing}, are analysed with one-sided publication bias tests and excess significance tests.
+The meta-analyses fulfilling the criteria from Section \ref{sec:Processing}, are analysed with one-sided publication bias tests and excess significance tests.
 The direction in which bias is expected is the one on which more significant results of primary studies are (two-sided $p$-value < 0.05).
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug 23 14:07:42 2019
+% Wed Aug 28 09:15:48 2019
 \begin{table}[ht]
@@
   Excess significance, Peter & 0.77 & 0.32 \\ 
-  Excess significance, Rucker & 0.79 & 0.43 \\ 
+  Excess significance, R\"ucker & 0.79 & 0.43 \\ 
   Excess significance, Harbord & 0.81 & 0.46 \\ 
   Peter, Schwarzer & 0.84 & 0.63 \\ 
-  Schwarzer, Rucker & 0.85 & 0.72 \\ 
+  Schwarzer, R\"ucker & 0.85 & 0.72 \\ 
   Schwarzer, Harbord & 0.87 & 0.78 \\ 
-  Rucker, Peter & 0.88 & 0.67 \\ 
+  R\"ucker, Peter & 0.88 & 0.67 \\ 
   Harbord, Peter & 0.87 & 0.63 \\ 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
+\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## [1] 5.1 6.0 4.1 2.1
+\end{verbatim}
+\end{kframe}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug 23 14:07:57 2019
+% Wed Aug 28 09:16:02 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug 23 13:57:11 2019
+% Wed Aug 28 09:16:04 2019
 \begin{table}[ht]
@@
 The dependent variable is the effect size $z$.
-As before in Section \ref{sec:change.size}, the effect sizes are mirrored to one side by multiplying with the sign of the expected side of bias, \ie -1 or 1.
+As before in Section \ref{sec:change.size}, the effect sizes are mirrored to one side by multiplying with the sign of the expected side of bias, \ie \vspace{1mm}-1 or 1.
 Taking the absolute values might obscure cases where the sign of the effect size changes but its absolute value is equal.\\
@@
 Additionally, random effects for the meta-analysis and for the review are added, the former being nested in the latter.
-Figure \ref{fig:smds} shows the complete dataset with the fit of the previously described model (dotted red line).
 The details and evidence for the small study effects in the mixed linear model are given in Table \ref{anova.small.study}, the coefficients in Table \ref{coefficients.small.study}:
 
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}
-
-{\centering \includegraphics[width=\textwidth-3cm]{figure/ch03_figunnamed-chunk-28-1}
-
-}
-
-\end{knitrout}
-\caption{$z$-scores of all meta-analyses plotted against their standard error, with the fit of a mixed linear model (dotted red line).}
-\label{fig:smds}
-\end{figure}
+% \begin{figure}
+
+% \caption{$z$-scores of all meta-analyses plotted against their standard error, with the fit of a mixed linear model (dotted red line).}
+% \label{fig:smds}
+% \end{figure}
 
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug 23 13:57:19 2019
+% Wed Aug 28 09:16:11 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug 23 13:57:20 2019
+% Wed Aug 28 09:16:12 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug 23 13:57:23 2019
+% Wed Aug 28 09:16:15 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug 23 13:57:25 2019
+% Wed Aug 28 09:16:17 2019
 \begin{table}[ht]
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug 23 13:57:28 2019
+% Wed Aug 28 09:16:20 2019
 \begin{table}[ht]
@@
 'Small study fit' denotes the model with the standard error as explanatory variable, 'study.year.fit' the model with standard error and the centered (- 2000) mean study year of the meta-analysis as explanatory variable, and 'study.year.int.fit' the model with interaction between the two.}
-\label{anova.lme}
+\label{anova.lme.2}
 \end{table}
 
-The analysis of model fit indicates that there is no improvement when using the study year as a covariate.
-Thus, there is no evidence for a interaction between small study effects and mean study publication year
+The analysis of model fit in Table \ref{anova.lme.2} indicates that there is no improvement when using the study year as a covariate.
+Thus, there is no evidence for an interaction between small study effects and mean study publication year.
 
@@
 
-\section{Comparison of Results with previous Studies}
+\section{Comparison of Results with Previous Studies}
 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-3 package
-% Fri Aug 23 13:58:08 2019
+% Wed Aug 28 09:17:02 2019
 \begin{table}[ht]
@@
 
-\section{R Session information}
+\section{R Session Information}
 

### 2019-08-28 report/chapter02.Rnw
Final Version

@@
 
-Let $\mathbf{\beta} = (\beta_0, \beta_1)^\top$. It can be shown that
+Let $\boldsymbol{\beta} = (\beta_0, \beta_1)^\top$. It can be shown that
 
 \begin{align}
-\hat{\mathbf{\beta}} &= (\mathbf{X}^\top \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
+\hat{\boldsymbol{\beta}} &= (\mathbf{X}^\top \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
 \end{align}
-is an estimator of $\mathbf{\beta}$ that minimizes the squared residuals.
-Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\mathbf{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$.
+is an estimator of $\boldsymbol{\beta}$ that minimizes the squared residuals.
+Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\boldsymbol{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$.
 The variance estimates $\hat{\sigma}^2$ and $\hat{\mathbf{s}}_\beta^2$ are

### 2019-08-28 report/chapter03.Rnw
Final Version

@@
 \\
-From the meta-analyses with incomplete data (\texttt{outcome.flag} == \texttt{IV}), there are \Sexpr{first.iv.outcome.count} with \\ \texttt{outcome.measure.merged} = \texttt{RR}, \Sexpr{second.iv.outcome.count} \texttt{SMD},  \Sexpr{third.iv.outcome.count} \texttt{Hazard Ratio}, \Sexpr{fourth.iv.outcome.count} \texttt{OR}, \Sexpr{fifth.iv.outcome.count} \texttt{MD} and \Sexpr{sixth.iv.outcome.count} \texttt{Rate Ratio}.
+From the meta-analyses with incomplete data (\texttt{outcome.flag} == \texttt{IV}), there are \Sexpr{first.iv.outcome.count} meta-analyses with \\ \texttt{outcome.measure.merged} = \texttt{RR}, \Sexpr{second.iv.outcome.count} \texttt{SMD},  \Sexpr{third.iv.outcome.count} \texttt{Hazard Ratio}, \Sexpr{fourth.iv.outcome.count} \texttt{OR}, \Sexpr{fifth.iv.outcome.count} \texttt{MD} and \Sexpr{sixth.iv.outcome.count} \texttt{Rate Ratio}.
 
@@
 When one subgroup has substantially different real treatment effects, and the specific properties influence study size, publication bias assessment fails.
-Subgroups are not indicated in \Sexpr{no.subgroup}\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane Review Groups did.
+Subgroups are not indicated in \Sexpr{no.subgroup}\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane Review groups did.
 \\

### 2019-08-28 report/chapter04.Rnw
Final Version

@@
 colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
-                                      "Excess significance, Rucker", "Excess significance, Harbord",
-                                      "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
-                                      "Rucker, Peter", "Harbord, Peter")
+                                      "Excess significance, R\\\"ucker", "Excess significance, Harbord",
+                                      "Peter, Schwarzer", 'Schwarzer, R\\\"ucker', "Schwarzer, Harbord",
+                                      "R\\\"ucker, Peter", "Harbord, Peter")
 #--------------------------------------------------------------------------------------------------------------------#
@@
 
-labels <- c(pval1.harbord = "Harbord", pval1.peter = "Peter", pval1.rucker = "Rucker (Thompson)", pval1.rucker.linreg = "Rucker (Egger)", pval1.schwarzer = "Schwarzer", pval1.d.tes = "Excess significance")
+labels <- c(pval1.harbord = "Harbord", pval1.peter = "Peter", pval1.rucker = "Rücker (Thompson)", pval1.rucker.linreg = "Rücker (Egger)", pval1.schwarzer = "Schwarzer", pval1.d.tes = "Excess significance")
 
@@
   geom_text(data = dat_text, mapping = aes(x = 0.5, y = 125, label = label), color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + ggtitle("Binary Outcomes") + 
+  theme(strip.text.x = element_text(size=9)) + ggtitle("Binary Outcomes") + 
   theme(legend.position = "none")
@@
   geom_text(data = dat_text, mapping = aes(x = 0.5, y = 60, label = label),  color = "black") + 
-  theme(strip.text.x = element_text(size=7)) + ggtitle("Continuous Outcomes") + 
+  theme(strip.text.x = element_text(size=9)) + ggtitle("Continuous Outcomes") + 
   theme(legend.position = "none")
@@
   scale_fill_discrete(labels = c("> 0", "= 0")) +
-  theme(strip.text.x = element_text(size=7)) + 
+  theme(strip.text.x = element_text(size=9)) + 
   ggtitle("IV Outcomes") 
@@
                              stat.egger, stat.thompson, stat.begg, I2)
-colnames(cor.data) <- c("Rucker", "Harbord", "Peter", "Schwarzer", "Egger", "Thompson",
+colnames(cor.data) <- c("Rücker", "Harbord", "Peter", "Schwarzer", "Egger", "Thompson",
                         "Begg", "I-squared")
@@
                      values = c("red", "blue")) +
-  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value Rucker)" ))) + geom_smooth(method = "lm", col = "green")
+  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value Rücker)" ))) + geom_smooth(method = "lm", col = "green")
 #--------------------------------------------------------------------------------------------------------------------#
@@
 When comparing agreement if significant only, the proportion of the test with fewer significant results that is significant with another test as well is shown.",
-             label = "test.agreement"),, size = "scriptsize")
+             label = "test.agreement"), size = "scriptsize", sanitize.rownames.function = identity)
 @
@@
 <<echo = FALSE, warning=FALSE, fig.height=5>>=
-par(mfrow = c(2,3), cex.lab = 1.5, cex.axis = 1.5, las = 1, mar = c(5.1,6,4.1,2.1),mgp=c(4,1,0))
+c(5.1,6,4.1,2.1)
+par(mfrow = c(2,3), cex.lab = 1.3, cex.axis = 1.5, las = 1, mar = c(5.1,6,4.1,2.1),mgp=c(4,1,0))
 example <- data.ext2 %>% filter(meta.id == 81244)
@@
 Additionally, random effects for the meta-analysis and for the review are added, the former being nested in the latter.
-Figure \ref{fig:smds} shows the complete dataset with the fit of the previously described model (dotted red line).
 The details and evidence for the small study effects in the mixed linear model are given in Table \ref{anova.small.study}, the coefficients in Table \ref{coefficients.small.study}:
 
-\begin{figure}
-<<echo = FALSE, message = FALSE, warning = FALSE, fig.height=4>>=
+% \begin{figure}
+<<echo = FALSE, message = FALSE, warning = FALSE>>=
 ##-------Prepare data--------#
@@
                        weights = ~ se.z.mirrored^2, method = "ML", data = reg.dat)
-plot(y = reg.dat$z.mirrored, x = reg.dat$se.z.mirrored, cex = .1, xlab = "standard error", ylab = "z mirrored", las = 1)
-publication.bias.fit.coef <- summary(publication.bias.fit)$coefficients$fixed
-abline(a = publication.bias.fit.coef, col = "red", lty = 2)
+# plot(y = reg.dat$z.mirrored, x = reg.dat$se.z.mirrored, cex = .1, xlab = "standard error", ylab = "z mirrored", las = 1)
+# publication.bias.fit.coef <- summary(publication.bias.fit)$coefficients$fixed
+# abline(a = publication.bias.fit.coef, col = "red", lty = 2)
 
@@
 @
-\caption{$z$-scores of all meta-analyses plotted against their standard error, with the fit of a mixed linear model (dotted red line).}
-\label{fig:smds}
-\end{figure}
+% \caption{$z$-scores of all meta-analyses plotted against their standard error, with the fit of a mixed linear model (dotted red line).}
+% \label{fig:smds}
+% \end{figure}
 
@@
 'Small study fit' denotes the model with the standard error as explanatory variable, 'study.year.fit' the model with standard error and the centered (- 2000) mean study year of the meta-analysis as explanatory variable, and 'study.year.int.fit' the model with interaction between the two.",
-             label = "anova.lme", digits = c(1,1,1,1,1,1,1,1,6)), size = "scriptsize")
-@
-
-The analysis of model fit indicates that there is no improvement when using the study year as a covariate.
-Thus, there is no evidence for a interaction between small study effects and mean study publication year
+             label = "anova.lme.2", digits = c(1,1,1,1,1,1,1,1,6)), size = "scriptsize")
+@
+
+The analysis of model fit in Table \ref{anova.lme.2} indicates that there is no improvement when using the study year as a covariate.
+Thus, there is no evidence for an interaction between small study effects and mean study publication year.
 

### 2019-08-28 Presentation Final/present.Rnw
Deletion of unnecessary files

--- 2019-08-21 Presentation copy/present.Rnw
@@
 load(file.path(PATH_RESULTS, "meta.iv.RData"))
+
+bias.side.z <- function(yi, sei){
+  alpha = 0.05
+  to.ommit <- which(is.na(yi) | is.na(sei))
+
+  if(length(to.ommit) > 0){
+    yi <-  yi[-to.ommit]
+    sei <- sei[-to.ommit]
+  }
+
+  to.ommit <- which(sei == 0)
+
+  if(length(to.ommit) > 0){
+    yi <-  yi[-to.ommit]
+    sei <- sei[-to.ommit]
+  }
+
+  if(sum(pnorm(yi/sei) < .05) == sum(pnorm(yi/sei, lower.tail=FALSE) < .05)){
+      side <- sign(est.fe <- rma(yi = yi, sei = sei, method = "FE")$b[1] )
+  } else{
+    side = ifelse(sum(pnorm(yi/sei) < .05) > sum(pnorm(yi/sei, lower.tail=FALSE) < .05),
+                  -1, 1)
+    }
+  return(side)
+}
 
@@
 adj.result.count <- dim(tp6)[1]
+
+#----------------------------------------------------------------------------------------------#
+# missing.copas.histogram <- meta.f %>% ggplot(aes(x = missing.copas/k)) + geom_histogram(binwidth = 0.05, boundary = 0) + theme_bw() + xlab("Missing study fraction")
+missing.copas.zeros <- length(which(meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)] == 0))
+missing.copas.range.frac <- c(missing.copas.zeros, quantile(x = meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)], c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(meta.f$missing.copas[!is.na(meta.f$missing.copas)]/meta.f$k[!is.na(meta.f$missing.copas)],na.rm = T) )
+missing.copas.range.count <- c(missing.copas.zeros, quantile(x = meta.f$missing.copas[!is.na(meta.f$missing.copas)], c(0.05, 0.25, 0.5, 0.75, 0.95)), mean(na.rm = T,meta.f$missing.copas[!is.na(meta.f$missing.copas)]))
+missing.copas.table <- rbind(missing.copas.range.frac, missing.copas.range.count)
+rownames(missing.copas.table) <- c("Overall fraction", "Missing number")
+colnames(missing.copas.table) <- c("= 0", colnames(missing.copas.table)[2:6], "mean")
+missing.copas.table <- missing.copas.table[c(2,1),]
 @
@@
 \begin{itemize}
-\item Summarise all evidence with regard to treatment with meta-analysis
+\item Summarize all evidence with regard to treatment with meta-analysis
 \item Biased if non-significant results are not available and included
@@
 \vspace{-1mm}
-$O = $ observed no. of significant results, $E$ expected based on power of studies.
+$O = $ observed no. of significant results, $E$ expected based on power of studies, $p$ = $E/n$.
 \end{frame}
@@
 \begin{align}
-y_i &= \beta_0 + \beta_1 x_i + \epsilon, & \epsilon \sim N(0, x_i \sigma^2) \nonumber
+y_i &= \beta_0 + \beta_1 x_i + \epsilon_i, & \epsilon_i \sim N(0, x_i \sigma^2) \nonumber
 \end{align}
@@
 \item Use score of binomial likelihood at log odds ratio $\theta_{\textrm{H0}} = 0$ instead of 
-log odds ratio and the inverse Fisher information instead of $\se_\theta$
+log odds ratio, and the inverse Fisher information instead of $\se_\theta$
 \end{itemize}
@@
         plot.title = element_text(hjust = 0.5, face = "bold", size = 12, margin = margin(b = 20)),
-        #axis.title.y = element_text(size=16, margin = margin(r = 10)), 
         axis.title.x = element_text(size=16, margin = margin(t = 10)), 
@@
 \end{figure}
+\end{frame}
+
+\begin{frame}{Adjustment}
+Calculate unbiased estimates by
+\begin{itemize}
+\item Sensitivity analysis
+\item Regression approach
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Selection Model}
+\citet{Copas2}
+\begin{align}
+\theta_i &\sim N(\mu_i, \sigma_i^2) &
+\mu_i \sim N(\theta, \tau^2) \nonumber
+\end{align}
+So we have $\theta_i = \mu_i + \sigma_i\epsilon_i \nonumber$. Introduce
+\begin{itemize}
+\item Baseline study retention rate $a$
+\item Std. error dependent retention rate $b$
+\item introduces correlation between $\epsilon_i$ and selection probability
+\end{itemize}
+%Model the selection process for increasing $a$ and $b$
+\end{frame}
+
+\begin{frame}{Sensitivity analysis}
+To test a pair $a$,$b$,	include $\beta$:
+\begin{align}
+\theta_i &= \theta + \beta \se_i + \sigma_i \epsilon_i \nonumber
+\end{align}
+\vspace{-10mm}
+\begin{itemize}
+\item $\theta_i$ is the effect size of study $i$ and right-hand side is the fitted 
+value of the model. 
+\item Repeatedly test for $\beta_{\textrm{H0}} = 0$ %and estimate $\theta_{\textrm{Adj.}}$
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Regression}
+Correct for small study effect \citep{Limitmeta}:
+\begin{itemize}
+\item Use global mean of regression $\beta_0$ from $y_i = \beta_0 + \beta_1 x_i + \epsilon_i, \epsilon_i \sim N(0, x_i \sigma^2) \nonumber$
+\item Add minimal bias term $\beta_1 \cdot \tau$
+\end{itemize}
+$\theta_{\textrm{Adj.}} = \beta_0 + \beta_1\tau$
+\end{frame}
+
+\begin{frame}{Adjustment Methods}
+Differences:
+\begin{itemize}
+\item Regression: uncertainty of bias parameter retained
+\item Sensitivity analysis: Bias itself is not estimated, but most parsimonious scenario is chosen
+\item Sensitivity analysis: No adjustment if no evidence for bias
+\end{itemize}
+Regression adjustment leads to higher uncertainty of $\theta_{\textrm{Adj.}}$
+\end{frame}
+
+\begin{frame}{Effect Measure Transformation}
+\vspace{-3mm}
+\begin{align}
+d &= \theta \frac{\sqrt{3}}{\pi} & \se_d^2 =  \se^2\frac{\sqrt{3}}{\pi} \nonumber
+\end{align}
+\begin{align}
+r &= \frac{d}{\sqrt{d^2 + a}} & a = (n_c + n_t)^2 / n_c n_t \nonumber
+\end{align}
+\begin{align}
+z &= 0.5 \ln\bigg(\frac{1 + r}{1 - r}\bigg) & \nonumber
+%z &= \arctan(r) & \nonumber
+\se_z^2 &= \frac{1}{n-3}
+\end{align}
+\end{frame}
+
+\begin{frame}[fragile]{Results}
+<<echo = FALSE, cache = TRUE, fig.height = 4, message = FALSE, warning = FALSE>>=
+diff.z.ranef.reg <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", regression) %>% 
+  mutate(difference = ranef - adjusted.z.score) %>% 
+  filter(difference > -.75 & difference < .75) %>% 
+  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + ggtitle("Regression") +
+  xlab(expression(paste("Random effects ", italic(hat(z)), " - adjusted ", italic(hat(z))))) + 
+	geom_vline(xintercept = 0, linetype = "dashed" ) + theme(
+		axis.title.y = element_text(size=16, margin = margin(r = 10)), 
+        plot.title = element_text(hjust = 0.5, face = "bold", size = 15, margin = margin(b = 22)),
+        axis.title.x = element_text(size=14, margin = margin(t = 10)), 
+        axis.text= element_text(size=12),
+        strip.text.x = element_text(size = 30)) + xlim(c(-0.8, 0.7))
+#--------------------------------------------------------------------------------------------------------------------#
+
+diff.z.ranef.copas <- meta.f %>% 
+  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
+         copas = est.z.copas, regression = est.z.reg) %>% 
+  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
+                           sign(copas) != sign(ranef) ~ -abs(copas)),
+         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
+                                sign(regression) != sign(ranef) ~ -abs(regression)),
+         fixef = abs(fixef),
+         ranef = abs(ranef)) %>% 
+  select(fixef, ranef, copas, regression) %>% 
+  gather(key = "method", value = "adjusted.z.score", copas) %>% 
+  mutate(difference = ranef - adjusted.z.score) %>% 
+  filter(difference > -.75 & difference < .75) %>% 
+  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
+  theme_bw() + ylab("") + ggtitle("Selection Model") +
+  xlab(expression(paste("Random effects ", italic(hat(z)), " - adjusted ", italic(hat(z))))) + 
+  	geom_vline(xintercept = 0, linetype = "dashed" ) + theme(
+        plot.title = element_text(hjust = 0.5, face = "bold", size = 15, margin = margin(b = 22)),
+        axis.title.x = element_text(size=14, margin = margin(t = 10)), 
+        axis.text= element_text(size=12),
+        strip.text.x = element_text(size = 30)) + xlim(c(-0.8, 0.7))
+
+grid.arrange(diff.z.ranef.reg, diff.z.ranef.copas, ncol = 2)
+@
+\end{frame}
+
+\begin{frame}{Results}
+% \vspace{-3mm}
+% Compare wald test statistics (original effect size measures):
+% 
+% \vspace{-2mm}
+<<echo = FALSE, warning = FALSE, cache = TRUE, fig.height = 4>>=
+mid <- median(meta.f$pval.se)
+method.names <- c(z.reg = "Regression", z.copas = "Selection Model")
+
+decrease_text <- data.frame(label = c("decrease", "decrease"),
+  method   = c("z.reg", "z.copas"))
+increase_text <- data.frame(label = c("increase", "increase"),
+                            method   = c("z.reg", "z.copas"))
+meta.f %>% filter(z.reg > -40) %>% 
+  select(pval.se, z.fixef, z.ranef, z.reg, z.copas) %>% 
+  gather(key = "method", value = "test.stat", z.reg:z.copas) %>%
+  ggplot(aes(x = test.stat, y = z.ranef, colour = pval.se)) + 
+  facet_wrap(~ method, labeller = as_labeller(method.names)) + 
+  scale_color_gradient2(midpoint=mid, low="firebrick4", mid = "gold",
+                        high="chartreuse2", space ="Lab", name = expression(paste(italic(p),"-value"))) +
+  geom_point(size = .6) + theme_bw() + guides(fill=guide_legend(title="p-value")) +
+  geom_abline(slope = 1, intercept = 0, linetype = 2, size = .3) +
+  geom_abline(slope = 0, intercept = 0, linetype = 2, size = .3) +
+  geom_text(data = decrease_text, mapping = aes(x = -11, y = 6, label = label), 
+            color = "tan3") + 
+  geom_text(data = decrease_text, mapping = aes(x = 11, y = -6, label = label), 
+            color = "tan3") + 
+  geom_text(data = increase_text, mapping = aes(x = 15, y = 4, label = label), 
+            color = "chartreuse3") + 
+  geom_text(data = increase_text, mapping = aes(x = -15, y = -4, label = label), 
+            color = "chartreuse3") + 
+  xlab(expression(paste("Adjusted ",  italic(z),  " test statistic"), sep = "")) + 
+  ylab(expression(paste("Random effects z ", italic(z), " test statistic"), sep = "")) +
+  theme(legend.title = element_text(size=14),
+        axis.title.y = element_text(size=14, margin = margin(r = 20)), 
+        axis.title.x = element_text(size=14, margin = margin(t = 20)), 
+        legend.text = element_text(size =10), 
+        axis.text= element_text(size=12),
+        strip.text.x = element_text(size = 15),
+        #plot.title = element_text(hjust = 0.5, face = "bold", size = 40, margin = margin(b = 20)),
+  			strip.background = element_rect(fill = "white"))
+@
+
+\end{frame}
+
+\begin{frame}{Missing Study Number}
+Missing study number according to selection model parameters: \Sexpr{format(round(sum(meta.f$missing.copas, na.rm = T)),big.mark = ",")}, \Sexpr{round(sum(meta.f$missing.copas, na.rm = T)/sum(meta.f$k),3)*100}\%
+
+<<echo= FALSE, results='asis', cache = TRUE>>=
+print(xtable(missing.copas.table, caption = "Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.",
+             label = "copas.missing", align = "lrrrrrrr", digits = c(0,0,0,0,1,1,1,1)),
+      size = "footnotesize")
+@
+\end{frame}
+
+\begin{frame}{Additional Results}
+Linear mixed model with random effects for meta-analyses and reviews:
+
+\begin{align}
+\mathbf{y}_i \given U_j,U_k,\epsilon_{i} =  \beta_0 + x_i\beta_1 + U_j + U_k + \epsilon_{i} \nonumber
+\end{align}
+
+$\rightarrow$ Increased power to estimate $\beta$
+\end{frame}
+
+\begin{frame}{Mixed Linear Model}
+AIC improvement to null fit: 1820 to 1306. \\
+Bias parameter $\beta_1$ = 0.52 (95\%CI: 0.44,0.59)
+
+\vspace{-12mm}
+\begin{figure}
+<<echo = FALSE, warning=FALSE, cache = TRUE, fig.height = 4>>=
+reg.dat <- data.ext2 %>% filter(meta.id %in% meta.f$meta.id) #Filter meta-analysis data
+reg.dat <- reg.dat %>% group_by(meta.id) %>%
+  filter(var.z != 0) %>% filter(!is.na(z)) %>% filter(!is.na(var.z)) %>%
+  mutate(se.z.mirrored = sqrt(var.z)) %>% filter(!is.na(se.z.mirrored)) %>%
+  mutate(bias.side.z = bias.side.z(yi = z, sei = se.z.mirrored),
+  z.mirrored = z * bias.side.z) #Mirror effect sizes on one side
+reg.dat <- reg.dat %>%  filter(!is.na(z.mirrored)) %>%
+  filter(!is.na(se.z.mirrored))
+reg.dat <- reg.dat %>% filter(se.z.mirrored < 3)
+publication.bias.fit <- lme(fixed = z.mirrored ~ se.z.mirrored, 
+														random = list(~ 1 | id, ~ 1 | meta.id), 
+														weights = ~ se.z.mirrored^2, method = "ML", data = reg.dat)
+publication.bias.rs.fit <- lme(fixed = z.mirrored ~ se.z.mirrored,
+                          random = list(~ 1 | id, ~ meta.id | meta.id),
+                       weights = ~ se.z.mirrored^2, method = "ML", data = reg.dat)
+plot(y = reg.dat$z.mirrored, x = reg.dat$se.z.mirrored, cex = .1, cex.lab = 1.3,
+		 xlab = "standard error", ylab = "z mirrored")
+publication.bias.fit.coef <- summary(publication.bias.fit)$coefficients$fixed
+abline(a = publication.bias.fit.coef, col = "red", lty = 2, lwd = 1.5)
+publication.bias.rs.fit.coef <- summary(publication.bias.rs.fit)$coefficients$fixed
+abline(a = publication.bias.rs.fit.coef, col = "blue", lty = 3, lwd = 1.5)
+@
+\end{figure}
+\end{frame}
+
+\begin{frame}{Limitations}
+Small study effect $\neq$ publication bias. Also:
+\begin{itemize}
+\item True heterogeneity
+\item Selective outcome reporting
+\item Delayed publication
+\item ...
+\end{itemize}
+\vspace{-3mm}
+Small study effect tests do not take into account significance directly.
+\end{frame}
+
+\begin{frame}{Limitations}
+\begin{itemize}
+\item Unknown amount of secondary outcomes
+\item Small amount of adverse outcomes
+\item Publication bias unknown for excluded data
+\item Exploratory Analysis!
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Implications}
+\begin{itemize}
+\item Results are largely in line with previous research
+\item Underline the need for examination of publication and other biases in meta-analyses
+\item Otherwise, validity of meta-analyses can be contested
+\end{itemize}
+\end{frame}
+
+\begin{frame}{References}
+  \small
+  \bibliographystyle{apalike}
+\bibliography{illustration}
+\end{frame}
+
+\begin{frame}
+Backup slides:
+\end{frame}
+
+\begin{frame}[fragile]{Transformation}
+
+\vspace{-6mm}
+<<echo = FALSE, warning=FALSE, fig.height=4.8, cache = TRUE>>=
+par(mfrow = c(2,3), cex.lab = 1.5, cex.axis = 1.5)
+example <- data.ext2 %>% filter(meta.id == 81244)
+funnel(limitmeta(metagen(TE = effect, se = se, studlab = study.name, sm = "MD", data = example)), col.adjust = "blue", col.line = "blue")
+funnel(limitmeta(metagen(TE = smd.pool, se = se.smd.pool, studlab = study.name, sm = "SMD", data = example)), col.adjust = "blue", col.line = "blue")
+funnel(limitmeta(metagen(TE = z, seTE = sqrt(var.z), studlab = study.name, sm = "ZCOR", data = example)), col.adjust = "blue", col.line = "blue")
+
+example <- data.ext2 %>% filter(meta.id == 32532)
+funnel(limitmeta(metagen(TE = log(effect), se = se, studlab = study.name, sm = "RR", data = example)), col.adjust = "blue", col.line = "blue")
+funnel(limitmeta(metagen(TE = smd.pool, se = se.smd.pool, studlab = study.name, sm = "SMD", data = example)), col.adjust = "blue", col.line = "blue")
+funnel(limitmeta(metagen(TE = z, seTE = sqrt(var.z), studlab = study.name, sm = "ZCOR", data = example)), col.adjust = "blue", col.line = "blue")
+@
 \end{frame}
@@
 
-\begin{frame}{References}
-  \small
-  \bibliographystyle{apalike}
-\bibliography{illustration}
-\end{frame}
-
 %\appendix
